---
title: "Sex"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/sexDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/sexDS.R')
```




<!-- ########################################################## --> 

# Data process


## Mexico

### Wave 1 

#### Study-specific variable description


| **Name** | `sexo`|
|-|-|
| **Label** | `Respondent's sex`|
| **Table name** |`MHAS-2001`|
| **Categories** |`1 = Man`<br/>`2 = Woman`|
| **Description** |  |



```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'MHAS_w1_sex','Mexican Health Aging Study.MHAS-2001',
                         variables=list('sexo'), missings = TRUE)
MHAS_w1_sex <- opal.execute(o,'MHAS_w1_sex')
```

```{r local1, echo=FALSE}
vari <- MHAS_w1_sex$sexo
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "sexo") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(MHAS_w1_sex, aes(x=factor(sexo))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 "Man" into 1`
* `2 "Woman" into 0`

**R script:**

```{r harmo1, echo=TRUE}
MHAS_ds_w1 <- tibble(id=MHAS_w1_sex$id)
MHAS_ds_w1$sex <- car::recode(MHAS_w1_sex$sexo, "2=0; NA=999")
MHAS_ds_w1$sex <- labelled(MHAS_ds_w1$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- MHAS_ds_w1$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w1, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=FALSE}
AfterH <- table(MHAS_ds_w1$sex)
BeforeH <- table(MHAS_w1_sex$sexo)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)
```






### Wave 2 

#### Study-specific variable description

| **Name** | `sexo`|
|-|-|
| **Label** | `Respondent's sex`|
| **Table name** |`MHAS-2001`|
| **Categories** |`1 = Man`<br/>`2 = Woman`|
| **Description** |  |


```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'MHAS_w1_sex','Mexican Health Aging Study.MHAS-2001',
                         variables=list('sexo'), missings = TRUE)
opal.assign.table.tibble(o, 'MHAS_w2_id','Mexican Health Aging Study.MHAS_2003',
                         variables=list('cunicah'), missings = TRUE)
```

```{r local2, echo=FALSE}
MHAS_w1_sex <- opal.execute(o,'MHAS_w1_sex')
MHAS_w2_id <- opal.execute(o,'MHAS_w2_id')

Same_indiv <- function(W1, W2){
  
  W1_2 <- matrix(rep(NA, dim(W1)[1]*dim(W1)[2] ), nrow = dim(W1)[1])
  W1m <- as.matrix(W1)
  
  for(i in 1:length(W1$id)){
    if(sum(W1$id[i]==W2$id)>=1){
      W1_2[i,] <- W1m[i,]
    } else {
      W1_2[i,] <- W1_2[i,]
    }
  }
  
  W1_22 <- data.frame(id=W1_2[,1], sexo=as.numeric(W1_2[,2]))
  W1_22[-which(is.na(W1_22$id)),]
}


MHAS_w2_sex <- Same_indiv(W1 = MHAS_w1_sex, W2 = MHAS_w2_id)

Add_indiv <- function(old, new){
  
  new_2 <- matrix(rep(NA, dim(new)[1]*dim(new)[2] ), nrow = dim(new)[1])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], sexo=as.numeric(new_2[,2]))
  new_22
}

MHAS_w2_sex <- Add_indiv(old = MHAS_w2_sex, new = MHAS_w2_id)

vari <- MHAS_w2_sex$sexo
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "sexo") 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(MHAS_w2_sex, aes(x=factor(sexo))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 "Man" into 1`
* `2 "Woman" into 0`

**R script:**

```{r harmo2, echo=TRUE}
MHAS_ds_w2 <- tibble(id=MHAS_w2_sex$id)
MHAS_ds_w2$sex <- car::recode(MHAS_w2_sex$sexo, "2=0; NA=999")
MHAS_ds_w2$sex <- labelled(MHAS_ds_w2$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- MHAS_ds_w2$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w2, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=FALSE}
BeforeH <- table(MHAS_w2_sex$sexo, useNA = "ifany")[c(2,1,3)]
AfterH <- table(MHAS_ds_w2$sex)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1", "NA->999")
kable(C)
```






### Wave 3 

#### Study-specific variable description

| **Name** | `sexo`|`sex_12`|
|-|-|-|
| **Label** | `Respondent's sex`|`Sex (Male=1)`|
| **Table name** |`MHAS-2001`|`MHAS_2012_new`|
| **Categories** |`1 = Man`<br/>`2 = Woman`| `1 = Male`<br/>`2 = Female`|
| **Description** |  |  |



```{r assign3, echo=FALSE}
opal.assign.table.tibble(o, 'MHAS_w3_sex','Mexican Health Aging Study.MHAS_2012_new',
                         variables=list('sex_12'), missings = TRUE)
MHAS_w3_sex <- opal.execute(o,'MHAS_w3_sex')
opal.assign.table.tibble(o, 'MHAS_w1_sex','Mexican Health Aging Study.MHAS-2001',
                         variables=list('sexo'), missings = TRUE)
MHAS_w1_sex <- opal.execute(o,'MHAS_w1_sex')


Add_indiv <- function(old, new){
  
  new_2 <- matrix(rep(NA, dim(new)[1]*dim(new)[2] ), nrow = dim(new)[1])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], sexo=as.numeric(new_2[,2]))
  new_22
}

MHAS_w3_sex$sex_w1 <- Add_indiv(old = MHAS_w1_sex, new = MHAS_w3_sex)$sexo
MHAS_w3_sex$sex_def <- MHAS_w3_sex$sex_12
MHAS_w3_sex$sex_def[is.na(MHAS_w3_sex$sex_def)] <- MHAS_w3_sex$sex_w1[is.na(MHAS_w3_sex$sex_def)]
```

```{r local3, echo=FALSE}
vari <- MHAS_w3_sex$sex_def
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(MHAS_w3_sex, aes(x=factor(sex_def))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 "Man" into 1`
* `2 "Woman" into 0`

**R script:**

```{r harmo3, echo=TRUE}
MHAS_ds_w3 <- tibble(id=MHAS_w3_sex$id)
MHAS_ds_w3$sex <- car::recode(MHAS_w3_sex$sex_def, "2=0; NA=999")
MHAS_ds_w3$sex <- labelled(MHAS_ds_w3$sex, labels = c("Female"=0, "Male"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=FALSE}
vari <- MHAS_ds_w3$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w3, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=FALSE}
AfterH <- table(MHAS_ds_w3$sex)
BeforeH <- c(table(MHAS_w3_sex$sex_def)[c(2,1)], sum(is.na(MHAS_w3_sex$sex_def)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1", "NA->999")
kable(C)
```



## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.




```{r helpfunctions, echo=F}
source("../../helpfunctions.r")
```



```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


mhas.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"))

# Consider only harmonised waves
l.hds <- lapply(mhas.cw, function(wname) if(exists(paste0("MHAS_ds_",wname[1]))){wname = list(get(paste0("MHAS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)

}
```


# Quality estimation

No comments.


```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
