---
title: "Marital Status"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `marital_status`
* Variable label: `The current marital status of the participant`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
1        | single
2        | married-cohabitating
3        | divorced-separated
4        | widow

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




<!-- ########################################################## --> 

# Data process

## Mexico

### Wave 1 

#### Study-specific variable description

 

* Name: `a10`
* Label: `Current marital status`
* Categories: 
    + `1 = single`
    + `2 = married`
    + `3 = in a consensual union`
    + `4 = divorced`
    + `5 = separated from a union`
    + `6 = separated from a marriage`
    + `7 = widowed from a union`
    + `8 = widowed from a marriage`


* Description: 
```{r assign1,  echo=FALSE}
opal.assign.table.tibble(o, 'MHAS_w1_ms','Mexican Health Aging Study.MHAS-2001',
                         variables=list('a10'), missings = TRUE)
```

```{r local1,  echo=FALSE}
MHAS_w1_ms <- opal.execute(o,'MHAS_w1_ms')
vari <- MHAS_w1_ms$a10
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = MHAS_w1_ms$a10, missing_values = NA)
ggplot(MHAS_w1_ms, aes(x=factor(a10))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep "single" into 1`
* `keep "married" into 2`
* `recode 3 "in a consensual union" into 2`
* `recode 4 "divorced" into 3`
* `recode 5 "separated from a union" into 3`
* `recode 6 "separated from a marriage" into 3`
* `recode 7 "widowed from a union" into 4`
* `recode 8 "widowed from a marriage" into 4`
* `recode NA into 999`

**R script:**

```{r harmo1,   echo=TRUE}
MHAS_ds_w1 <- tibble(id=MHAS_w1_ms$id)
MHAS_ds_w1$marital_status <- car::recode(MHAS_w1_ms$a10, "3=2; 4=3; 5=3; 6=3; 7=4; 8=4; NA=999")
MHAS_ds_w1$marital_status <- labelled(MHAS_ds_w1$marital_status, labels = c("single"=1, "married cohabitating"=2, "divorced separated"=3, "widow"=4, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1,  echo=FALSE}
vari <- MHAS_ds_w1$marital_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_ds_w1$marital_status, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w1, aes(x=factor(marital_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1,  echo=FALSE}
BeforeH <- table(MHAS_w1_ms$a10)
BeforeH <- c(BeforeH[1], sum(BeforeH[c(2,3)]), sum(BeforeH[c(4, 5, 6)]), sum(BeforeH[c(7, 8)]), sum(is.na(MHAS_w1_ms$a10)) )
AfterH <- table(MHAS_ds_w1$marital_status)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1","(2,3)->2", "(4,5,6)->3", "(7,8)->4", "NA->999")
kable(C)
```

 
 

 
```{r importOPAL1,  echo=FALSE}
val_labels(MHAS_ds_w1) <- NULL
opal.assign.data(o, 'MHAS_ds_w1', MHAS_ds_w1)
#opal.symbol_import(o,'MHAS_ds_w1', project='_Athlos_Harm_Dataset')
marital_status <- MHAS_ds_w1
save(marital_status, file = "../RData/w1/marital_status.RData")
rm(marital_status)

MHAS_m_ds_w1 <- MHAS_ds_w1
MHAS_m_ds_w1$marital_status <- car::recode(MHAS_m_ds_w1$marital_status, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'MHAS_m_ds_w1', MHAS_m_ds_w1)
#opal.symbol_import(o,'MHAS_m_ds_w1', project='_Athlos_Harm_Dataset')
```






### Wave 2 

#### Study-specific variable description

 

* Name: `a3`
* Label: `Respondent's Marital status`
* Categories: 
    + `1 = single`
    + `2 = married`
    + `3 = in a consensual union`
    + `4 = divorced`
    + `5 = separated from a union`
    + `6 = separated from a marriage`
    + `7 = widowed from a union`
    + `8 = widowed from a marriage`
    
* Description: 
```{r assign2,  echo=FALSE}
opal.assign.table.tibble(o, 'MHAS_w2_ms','Mexican Health Aging Study.MHAS_2003',
                         variables=list('a3'), missings = TRUE)
```

```{r local2,  echo=FALSE}
MHAS_w2_ms <- opal.execute(o,'MHAS_w2_ms')
vari <- MHAS_w2_ms$a3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = MHAS_w2_ms$a3, missing_values = NA)
ggplot(MHAS_w2_ms, aes(x=factor(a3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "single" into 1`
* `keep "married" into 2`
* `recode 3 "in a consensual union" into 2`
* `recode 4 "divorced" into 3`
* `recode 5 "separated from a union" into 3`
* `recode 6 "separated from a marriage" into 3`
* `recode 7 "widowed from a union" into 4`
* `recode 8 "widowed from a marriage" into 4`
* `recode NA into 999`

**R script:**

```{r harmo2,   echo=TRUE}
MHAS_ds_w2 <- tibble(id=MHAS_w2_ms$id)
MHAS_ds_w2$marital_status <- car::recode(MHAS_w2_ms$a3, "3=2; 4=3; 5=3; 6=3; 7=4; 8=4; NA=999")
MHAS_ds_w2$marital_status <- labelled(MHAS_ds_w2$marital_status, labels = c("single"=1, "married cohabitating"=2, "divorced separated"=3, "widow"=4, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2,  echo=FALSE}
vari <- MHAS_ds_w2$marital_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_ds_w2$marital_status, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w2, aes(x=factor(marital_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2,  echo=FALSE}
BeforeH <- table(MHAS_w2_ms$a3)
BeforeH <- c(BeforeH[1], sum(BeforeH[c(2,3)]), sum(BeforeH[c(4, 5, 6)]), sum(BeforeH[c(7, 8)]), sum(is.na(MHAS_w2_ms$a3)) )
AfterH <- table(MHAS_ds_w2$marital_status)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1","(2,3)->2", "(4,5,6)->3", "(7,8)->4", "NA->999")
kable(C)
```

 
 

 
```{r importOPAL2,  echo=FALSE}
val_labels(MHAS_ds_w2) <- NULL
opal.assign.data(o, 'MHAS_ds_w2', MHAS_ds_w2)
#opal.symbol_import(o,'MHAS_ds_w2', project='_Athlos_Harm_Dataset')
marital_status <- MHAS_ds_w2
save(marital_status, file = "../RData/w2/marital_status.RData")
rm(marital_status)

MHAS_m_ds_w2 <- MHAS_ds_w2
MHAS_m_ds_w2$marital_status <- car::recode(MHAS_m_ds_w2$marital_status, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'MHAS_m_ds_w2', MHAS_m_ds_w2)
#opal.symbol_import(o,'MHAS_m_ds_w2', project='_Athlos_Harm_Dataset')
```






### Wave 3 

#### Study-specific variable description

 

* Name: `a3_12`
* Label: `Current marital status`
* Categories: 
    + `1 = Single`
    + `2 = Married`
    + `3 = In a consensual union`
    + `4 = Divorced`
    + `5 = Separated from a civil union`
    + `6 = Separated from a marriage`
    + `7 = Widowed froma civil union`
    + `8 = Widowed from marriage`

* Description: 
```{r assign3,  echo=FALSE}
opal.assign.table.tibble(o, 'MHAS_w3_ms','Mexican Health Aging Study.MHAS_2012_new',
                         variables=list('a3_12'), missings = TRUE)
```

```{r local3,  echo=FALSE}
MHAS_w3_ms <- opal.execute(o,'MHAS_w3_ms')
vari <- MHAS_w3_ms$a3_12
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = MHAS_w3_ms$a3_12, missing_values = NA)
ggplot(MHAS_w3_ms, aes(x=factor(a3_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "Single" into 1`
* `keep "Married" into 2`
* `recode 3 "In a consensual union" into 2`
* `recode 4 "Divorced" into 3`
* `recode 5 "Separated from a civil union" into 3`
* `recode 6 "Separated from a marriage" into 3`
* `recode 7 "Widowed froma civil union" into 4`
* `recode 8 "Widowed from marriage" into 4`
* `recode NA into 999`


**R script:**

```{r harmo3,   echo=TRUE}
MHAS_ds_w3 <- tibble(id=MHAS_w3_ms$id)
MHAS_ds_w3$marital_status <- car::recode(MHAS_w3_ms$a3_12, "3=2; 4=3; 5=3; 6=3; 7=4; 8=4; NA=999")
MHAS_ds_w3$marital_status <- labelled(MHAS_ds_w3$marital_status, labels = c("single"=1, "married cohabitating"=2, "divorced separated"=3, "widow"=4, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3,  echo=FALSE}
vari <- MHAS_ds_w3$marital_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_ds_w3$marital_status, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w3, aes(x=factor(marital_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3,  echo=FALSE}
BeforeH <- table(MHAS_w3_ms$a3_12)
BeforeH <- c(BeforeH[1], sum(BeforeH[c(2,3)]), sum(BeforeH[c(4, 5, 6)]), sum(BeforeH[c(7, 8)]), sum(is.na(MHAS_w3_ms$a3_12)) )
AfterH <- table(MHAS_ds_w3$marital_status)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1","(2,3)->2", "(4,5,6)->3", "(7,8)->4", "NA->999")
kable(C)
```

 
 

 
```{r importOPAL3,  echo=FALSE}
val_labels(MHAS_ds_w3) <- NULL
opal.assign.data(o, 'MHAS_ds_w3', MHAS_ds_w3)
#opal.symbol_import(o,'MHAS_ds_w3', project='_Athlos_Harm_Dataset')
marital_status <- MHAS_ds_w3
save(marital_status, file = "../RData/w3/marital_status.RData")
rm(marital_status)

MHAS_m_ds_w3 <- MHAS_ds_w3
MHAS_m_ds_w3$marital_status <- car::recode(MHAS_m_ds_w3$marital_status, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'MHAS_m_ds_w3', MHAS_m_ds_w3)
#opal.symbol_import(o,'MHAS_m_ds_w3', project='_Athlos_Harm_Dataset')
```



# Quality estimation

'3=in a consensual union' was considered as 2=married-cohabitating in the harmonized variable

```{r closeRsession, echo=FALSE,  echo=FALSE} 
opal.logout(o)
```


