---
title: "Day of interview"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```

# Description of DataSchema variable

The description of harmonised variable is the following:




* Short name: `dintw`
* Variable label: `day of interview`
* Variable description: `day of interview`
* Domain: `Other administrative variables`
* Value type:`continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done 
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


# Data process

## Spain
    
### ENRICA - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `w1d_interview`
* Label: 
* Type of variable: `countinous`

```{r assign1}
opal.assign.table.tibble(o, 'ENRICA_w1_dinter','ENRICA.ENRICA_spss_wave1',
                         variables=list('w1d_interview'), missings = TRUE)
```

```{r local1}
ENRICA_w1_dinter <- opal.execute(o,'ENRICA_w1_dinter')
ENRICA_w1_dinter$dinter <- as.numeric(format(ENRICA_w1_dinter$w1d_interview, '%d'))
Continuous_summary(var = ENRICA_w1_dinter$dinter, missing_values = NA)
ggplot(ENRICA_w1_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo1}
ENRICA_ds_w1 <- tibble(id=ENRICA_w1_dinter$id)
ENRICA_ds_w1$dintw <- car::recode(ENRICA_w1_dinter$dinter, "NA=999")
ENRICA_ds_w1$dintw <- labelled(ENRICA_ds_w1$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1}
Continuous_summary(var = ENRICA_ds_w1$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ENRICA_ds_w1, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1}
BeforeH <- table(ENRICA_w1_dinter$dinter, useNA = "ifany")
AfterH <- table(ENRICA_ds_w1$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH))
C
```

```{r importOPAL1}
#val_labels(ENRICA_ds_w1) <- NULL
#opal.assign.data(o, 'ENRICA_ds_w1', ENRICA_ds_w1)
#opal.symbol_import(o,'ENRICA_ds_w1', project='_Athlos_Harm_Dataset')
dintw <- ENRICA_ds_w1
save(dintw, file = "../RData/w1/dintw.RData")
rm(dintw)
```






### ENRICA - Wave 2 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `w2d_interview`
* Label: 
* Type of variable: `countinous`

```{r assign2}
opal.assign.table.tibble(o, 'ENRICA_w2_dinter','ENRICA.ENRICA_spss_wave2',
                         variables=list('w2d_interview'), missings = TRUE)
```

```{r local2}
ENRICA_w2_dinter <- opal.execute(o,'ENRICA_w2_dinter')
ENRICA_w2_dinter$dinter <- as.numeric(format(ENRICA_w2_dinter$w2d_interview, '%d'))
Continuous_summary(var = ENRICA_w2_dinter$dinter, missing_values = NA)
ggplot(ENRICA_w2_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo2}
ENRICA_ds_w2 <- tibble(id=ENRICA_w2_dinter$id)
ENRICA_ds_w2$dintw <- car::recode(ENRICA_w2_dinter$dinter, "NA=999")
ENRICA_ds_w2$dintw <- labelled(ENRICA_ds_w2$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2}
Continuous_summary(var = ENRICA_ds_w2$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ENRICA_ds_w2, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2}
BeforeH <- table(ENRICA_w2_dinter$dinter, useNA = "ifany")
AfterH <- table(ENRICA_ds_w2$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH))
C
```

```{r importOPAL2}
#val_labels(ENRICA_ds_w2) <- NULL
#opal.assign.data(o, 'ENRICA_ds_w2', ENRICA_ds_w2)
#opal.symbol_import(o,'ENRICA_ds_w2', project='_Athlos_Harm_Dataset')
dintw <- ENRICA_ds_w2
save(dintw, file = "../RData/w2/dintw.RData")
rm(dintw)
```




### ENRICA - Wave 3 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `	w3d_interview`
* Label: `
* Type of variable: `countinous`

```{r assign3}
opal.assign.table.tibble(o, 'ENRICA_w3_dinter','ENRICA.ENRICA_spss_wave3',
                         variables=list('w3d_interview'), missings = TRUE)
```

```{r local3}
ENRICA_w3_dinter <- opal.execute(o,'ENRICA_w3_dinter')
ENRICA_w3_dinter$dinter <- as.numeric(format(ENRICA_w3_dinter$w3d_interview, '%d'))
Continuous_summary(var = ENRICA_w3_dinter$dinter, missing_values = NA)
ggplot(ENRICA_w3_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`


R code of the ALGORITHM:

```{r harmo3}
ENRICA_ds_w3 <- tibble(id=ENRICA_w3_dinter$id)
ENRICA_ds_w3$dintw <- car::recode(ENRICA_w3_dinter$dinter, "NA=999")
ENRICA_ds_w3$dintw <- labelled(ENRICA_ds_w3$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3}
Continuous_summary(var = ENRICA_ds_w3$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ENRICA_ds_w3, aes(x=factor(dintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3}
BeforeH <- table(ENRICA_w3_dinter$dinter, useNA = "ifany")
AfterH <- table(ENRICA_ds_w3$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
C
```
#### Quality estimation
No comments.



#### Import to OPAL
```{r importOPAL3}
#val_labels(ENRICA_ds_w3) <- NULL
#opal.assign.data(o, 'ENRICA_ds_w3', ENRICA_ds_w3)
#opal.symbol_import(o,'ENRICA_ds_w3', project='_Athlos_Harm_Dataset')
dintw <- ENRICA_ds_w3
save(dintw, file = "../RData/w3/dintw.RData")
rm(dintw)
```


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
