---
title: "Year of interview"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```

# Description of DataSchema variable

The description of harmonised variable is the following:




* Short name: `yintw`
* Variable label: `year of interview`
* Variable description: `year of interview`
* Domain: `Other administrative variables`
* Value type:`continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done 
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


# Data process

## Spain
    
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `W1_date_of_interview`
* Label: 
* Type of variable: `countinous`

```{r assign1, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w1_dinter','ENRICA.ENRICA_spss_wave1',
                         variables=list('w1d_interview'), missings = TRUE)
ENRICA_w1_dinter <- opal.execute(o,'ENRICA_w1_dinter')
```


**R script:**

```{r preharm}
ENRICA_w1_dinter$yinter <- format(ENRICA_w1_dinter$w1d_interview, '%Y')
```

```{r local1, echo=F}
Categorical_summary(var = ENRICA_w1_dinter$yinter, missing_values = NA)
ggplot(ENRICA_w1_dinter, aes(x=factor(yinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable.

**R script:**

```{r harmo1}
ENRICA_ds_w1 <- tibble(id=ENRICA_w1_dinter$id)
ENRICA_ds_w1$yintw <- as.numeric(ENRICA_w1_dinter$yinter)
ENRICA_ds_w1$yintw <- labelled(ENRICA_ds_w1$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
Categorical_summary(var = ENRICA_ds_w1$yintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ENRICA_ds_w1, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
BeforeH <- table(ENRICA_w1_dinter$yinter, useNA = "ifany")
AfterH <- table(ENRICA_ds_w1$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```


```{r importOPAL1, echo=F}
#val_labels(ENRICA_ds_w1) <- NULL
#opal.assign.data(o, 'ENRICA_ds_w1', ENRICA_ds_w1)
#opal.symbol_import(o,'ENRICA_ds_w1', project='_Athlos_Harm_Dataset')

yintw <- ENRICA_ds_w1
save(yintw, file = "../RData/w1/yintw.RData")
rm(yintw)
```






### Wave 2 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w2d_interview`
* Label: 
* Type of variable: `countinous`

```{r assign2, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w2_dinter','ENRICA.ENRICA_spss_wave2',
                         variables=list('w2d_interview'), missings = TRUE)
ENRICA_w2_dinter <- opal.execute(o,'ENRICA_w2_dinter')
```



**R script:**
```{r preharm2}
ENRICA_w2_dinter$yinter <- format(ENRICA_w2_dinter$w2d_interview, '%Y')
```


```{r local2, echo=F}
Categorical_summary(var = ENRICA_w2_dinter$yinter, missing_values = NA)
ggplot(ENRICA_w2_dinter, aes(x=factor(yinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is the same of the study-specific variable.


**R script:**

```{r harmo2}
ENRICA_ds_w2 <- tibble(id=ENRICA_w2_dinter$id)
ENRICA_ds_w2$yintw <- as.numeric(ENRICA_w2_dinter$yinter)
ENRICA_ds_w2$yintw <- labelled(ENRICA_ds_w2$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
Categorical_summary(var = ENRICA_ds_w2$yintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ENRICA_ds_w2, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
BeforeH <- table(ENRICA_w2_dinter$yinter, useNA = "ifany")
AfterH <- table(ENRICA_ds_w2$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```



```{r importOPAL2, echo=F}
#val_labels(ENRICA_ds_w2) <- NULL
#opal.assign.data(o, 'ENRICA_ds_w2', ENRICA_ds_w2)
#opal.symbol_import(o,'ENRICA_ds_w2', project='_Athlos_Harm_Dataset')

yintw <- ENRICA_ds_w2
save(yintw, file = "../RData/w2/yintw.RData")
rm(yintw)

```




### Wave 3 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `	w3d_interview`
* Label: `
* Type of variable: `countinous`

```{r assign3, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w3_dinter','ENRICA.ENRICA_spss_wave3',
                         variables=list('w3d_interview'), missings = TRUE)
ENRICA_w3_dinter <- opal.execute(o,'ENRICA_w3_dinter')
```

**R script:**

```{r preharm3}
ENRICA_w3_dinter$yinter <- format(ENRICA_w3_dinter$w3d_interview, '%Y')
```

```{r local3, echo=F}
Categorical_summary(var = ENRICA_w3_dinter$yinter, missing_values = NA)
ggplot(ENRICA_w3_dinter, aes(x=factor(yinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values will be recoded as follows:

`NA into 999`

**R script:**

```{r harmo3}
ENRICA_ds_w3 <- tibble(id=ENRICA_w3_dinter$id)
ENRICA_ds_w3$yintw <- car::recode(ENRICA_w3_dinter$yinter, "NA=999")
ENRICA_ds_w3$yintw <- labelled(ENRICA_ds_w3$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}
Categorical_summary(var = ENRICA_ds_w3$yintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ENRICA_ds_w3, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=F}
BeforeH <- table(ENRICA_w3_dinter$yinter, useNA = "ifany")
AfterH <- table(ENRICA_ds_w3$yintw)[c(2,3,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2014", "2015", "NA->999")
kable(C)
```



```{r importOPAL3, echo=F}
#val_labels(ENRICA_ds_w3) <- NULL
#opal.assign.data(o, 'ENRICA_ds_w3', ENRICA_ds_w3)
#opal.symbol_import(o,'ENRICA_ds_w3', project='_Athlos_Harm_Dataset')

yintw <- ENRICA_ds_w3
save(yintw, file = "../RData/w3/yintw.RData")
rm(yintw)

```













```{r summ, echo=F}

ds_label <- "Year of interview"
cont_label <- c("Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)


ENRICA_ds_w1$yintw <- labelled(ENRICA_ds_w1$yintw, labels = cont_label)
label(ENRICA_ds_w1$yintw) <- ds_label
ENRICA_ds_w2$yintw <- labelled(ENRICA_ds_w2$yintw, labels = cont_label)
label(ENRICA_ds_w2$yintw) <- ds_label
ENRICA_ds_w3$yintw <- labelled(ENRICA_ds_w3$yintw, labels = cont_label)
label(ENRICA_ds_w3$yintw) <- ds_label

ENRICA_m_ds_w1 <- ENRICA_ds_w1
ENRICA_m_ds_w1$yintw <- car::recode(ENRICA_m_ds_w1$yintw, "miss_values_vector=NA")
ENRICA_m_ds_w2 <- ENRICA_ds_w2
ENRICA_m_ds_w2$yintw <- car::recode(ENRICA_m_ds_w2$yintw, "miss_values_vector=NA")
ENRICA_m_ds_w3 <- ENRICA_ds_w3
ENRICA_m_ds_w3$yintw <- car::recode(ENRICA_m_ds_w3$yintw, "miss_values_vector=NA")

# 
# tt <-    frq(ENRICA_ds_w1$yintw)[[1]][,c(1:2,4)]
# tt[4] <- frq(ENRICA_ds_w2$yintw)[[1]][,c(4)]
# tt[5] <- frq(ENRICA_ds_w3$yintw)[[1]][,c(4)]
# tt[13,] <- c("n", "sample size", 
#              length(ENRICA_ds_w1$yintw), length(ENRICA_ds_w2$yintw), length(ENRICA_ds_w3$yintw)
#              )
# names(tt)<-c("val", "label", "w1", "w2", "w3")
# kable(tt)

dbb <- merge(ENRICA_m_ds_w1[,c("id","yintw")], ENRICA_m_ds_w2[,c("id","yintw")], by="id", suffixes = c(".w1",".w2"), all=T)
dbb <- merge(dbb, ENRICA_m_ds_w3[,c("id","yintw")], by="id", all=T)
names(dbb) <- c("id", "w1", "w2", "w3")
v.dbb <- paste(dbb[,2],dbb[,3],dbb[,4],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb)
```



#### Quality estimation
* The date was the same as the study specific variable taking into account the wave time lapse information.
* There are 9 individuals whose year of interview for the first wave appears to be 2009 and for the second wave appears to be 2008.





```{r closeRsession, echo=FALSE}
opal.logout(o)
```
