---
title: "Respondent"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/respondentDS.Rmd'}
```

```{r global, echo=F}
source('../../_DS_Rmd/respondentDS.R')
```



<!-- ########################################################## --> 

# Data process

## Spain

### Wave 1 

#### Study-specific variable description

```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'ENRICA_w1','ENRICA.ENRICA_spss_wave1',
                         variables=list('sex'), missings = TRUE)
ENRICA_w1 <- opal.execute(o,'ENRICA_w1')
```


#### Harmonisation algorithm

All the interviewed individuals are considered as participants. 

**R script:**

```{r harmo1, echo=TRUE}
ENRICA_ds_w1 <- tibble(id=ENRICA_w1$id)
ENRICA_ds_w1$respondent <- 0
ENRICA_ds_w1$respondent <- labelled(ENRICA_ds_w1$respondent, labels = cat_label)
label(ENRICA_ds_w1$respondent) <- ds_label
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- ENRICA_ds_w1$respondent
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ENRICA_ds_w1, aes(x=factor(respondent))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

```{r importOPAL1, echo=FALSE}
#opal.assign.data(o, 'ENRICA_ds_w1', ENRICA_ds_w1)
#opal.symbol_import(o,'ENRICA_ds_w1', project='_Athlos_Harm_Dataset')

respondent <- ENRICA_ds_w1
save(respondent, file = "../RData/w1/respondent.RData")
rm(respondent)
```






### Wave 2 

#### Study-specific variable description

```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'ENRICA_w2','ENRICA.ENRICA_spss_wave2',
                         variables=list('sex'), missings = TRUE)
ENRICA_w2 <- opal.execute(o,'ENRICA_w2')
```

#### Harmonisation algorithm
All the interviewed individuals are considered as participants. 

**R script:**

```{r harmo2, echo=TRUE}
ENRICA_ds_w2 <- tibble(id=ENRICA_w2$id)
ENRICA_ds_w2$respondent <- 0
ENRICA_ds_w2$respondent <- labelled(ENRICA_ds_w2$respondent, labels = cat_label)
label(ENRICA_ds_w2$respondent) <- ds_label
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- ENRICA_ds_w2$respondent
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ENRICA_ds_w2, aes(x=factor(respondent))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL2, echo=FALSE}
#opal.assign.data(o, 'ENRICA_ds_w2', ENRICA_ds_w2)
#opal.symbol_import(o,'ENRICA_ds_w2', project='_Athlos_Harm_Dataset')

respondent <- ENRICA_ds_w2
save(respondent, file = "../RData/w2/respondent.RData")
rm(respondent)
```




### Wave 3 

#### Study-specific variable description

```{r assign3, echo=FALSE}
opal.assign.table.tibble(o, 'ENRICA_w3','ENRICA.ENRICA_spss_wave3',
                         variables=list('sex'), missings = TRUE)
ENRICA_w3 <- opal.execute(o,'ENRICA_w3')
```


#### Harmonisation algorithm
All the interviewed individuals are considered as participants. 

**R script:**

```{r harmo3, echo=TRUE}
ENRICA_ds_w3 <- tibble(id=ENRICA_w3$id)
ENRICA_ds_w1$respondent <- 0
ENRICA_ds_w1$respondent <- labelled(ENRICA_ds_w1$respondent, labels = cat_label)
label(ENRICA_ds_w1$respondent) <- ds_label
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=FALSE}
vari <- ENRICA_ds_w1$respondent
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ENRICA_ds_w1, aes(x=factor(respondent))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL3, echo=FALSE}
#opal.assign.data(o, 'ENRICA_ds_w3', ENRICA_ds_w3)
#opal.symbol_import(o,'ENRICA_ds_w3', project='_Athlos_Harm_Dataset')
respondent <- ENRICA_ds_w3
save(respondent, file = "../RData/w3/respondent.RData")
rm(respondent)
```

# Quality estimation

No comments.


```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
