---
title: "Vigorous Physical Activity"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/vig_paDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/vig_paDS.R')
```


# Data process






## South Africa

### Wave 1 

#### Study-specific variable description

| **Name** | `q3016` | `q3025` |
|-|-|-|
| **Label** | `vigorous fitness/leisure` | `vigorous work` |
| **Table name** | `southAfricaINDdata` | `southAfricaINDdata` |
| **Categories:**| `1 = yes` <br/> `2 = no` |  `1 = yes` <br/> `2 = no`|
| **Missings:**| `8 = don't know` <br/> `NA`|  `8 = don't know` <br/> `NA`| 
| **Description** |  | | 


```{r assign SA w1, echo=F}
opal.assign.table.tibble(o, 'SAGE_SA_w1','SAGE.southAfricaINDdata', variables=list('q3016','q3025'), missings = TRUE)
SAGE_SA_w1 <- opal.execute(o,'SAGE_SA_w1')
```

```{r local SA w1, echo=F}
vbl <- SAGE_SA_w1$q3016
vbl_miss <- c(8)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(SAGE_SA_w1)[2])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(SAGE_SA_w1, aes(x=factor(q3016))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_SA_w1$q3025
vbl_miss <- c(8)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(SAGE_SA_w1)[3])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(SAGE_SA_w1, aes(x=factor(q3016))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `q3016=2&q3025=2 into 0` 
* `q3016=1|q3025=1 into 1`
* `8 into 998`
* `NA into 999`

**R script:**

```{r harmo SA w1}
SAGE_ds_SA_w1 <- tibble(id=SAGE_SA_w1$id)
SAGE_ds_SA_w1$vig_pa <- rep(999,length(SAGE_ds_SA_w1$id))
SAGE_ds_SA_w1$vig_pa[which(SAGE_SA_w1$q3016==8|SAGE_SA_w1$q3025==8)] <- 998
SAGE_ds_SA_w1$vig_pa[which(SAGE_SA_w1$q3016==2&SAGE_SA_w1$q3025==2)] <- 0
SAGE_ds_SA_w1$vig_pa[which(SAGE_SA_w1$q3016==1|SAGE_SA_w1$q3025==1)] <- 1
```

#### Statistical description of the new harmonised variable
```{r descript SA w1, echo=F}
vbl <- SAGE_ds_SA_w1$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_SA_w1, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation SA w1, echo=F}

```






## China

### Wave 1 

#### Study-specific variable description

| **Name** | `q3016` | `q3025` |
|-|-|-|
| **Label** | `vigorous fitness/leisure` | `vigorous work` |
| **Table name** | `chinaINDData` | `chinaINDData` |
| **Categories:**| `1 = yes` <br/> `2 = no` |  `1 = yes` <br/> `2 = no`|
| **Missings:**| `NA`|  `NA`| 
| **Description** |  | | 


```{r assign china w1, echo=F}
opal.assign.table.tibble(o, 'SAGE_china_w1','SAGE.chinaINDData', variables=list('q3016','q3025'), missings = TRUE)
SAGE_china_w1 <- opal.execute(o,'SAGE_china_w1')
```

```{r local china w1, echo=F}
vbl <- SAGE_china_w1$q3016
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(SAGE_china_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(SAGE_china_w1, aes(x=factor(q3016))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_china_w1$q3025
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(SAGE_china_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(SAGE_china_w1, aes(x=factor(q3016))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `q3016=2&q3025=2 into 0` 
* `q3016=1|q3025=1 into 1` 
* `NA into 999`

**R script:**

```{r harmo china w1}
SAGE_ds_china_w1 <- tibble(id=SAGE_china_w1$id)
SAGE_ds_china_w1$vig_pa <- rep(999,length(SAGE_ds_china_w1$id))
SAGE_ds_china_w1$vig_pa[which(SAGE_china_w1$q3016==2&SAGE_china_w1$q3025==2)] <- 0
SAGE_ds_china_w1$vig_pa[which(SAGE_china_w1$q3016==1|SAGE_china_w1$q3025==1)] <- 1
```

#### Statistical description of the new harmonised variable
```{r descript china w1, echo=F}
vbl <- SAGE_ds_china_w1$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_china_w1, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation china w1, echo=F}
AfterH <- table(SAGE_ds_china_w1$vig_pa)
X<-c(sum(na.omit(SAGE_china_w1$q3016==2&SAGE_china_w1$q3025==2)),sum(na.omit(SAGE_china_w1$q3016==1|SAGE_china_w1$q3025==1)))
BeforeH <- c(X,length(SAGE_china_w1$q3016)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("q3016=2&q3025=2->0","q3016=1|q3025=1->1","NA->999") 
kable(C)
```





## Ghana

### Wave 1 

#### Study-specific variable description

| **Name** | `q3016` | `q3025` |
|-|-|-|
| **Label** | `vigorous fitness/leisure` | `vigorous work` |
| **Table name** | `ghanaINDData` | `ghanaINDData` | 
| **Categories:**| `1 = yes` <br/> `2 = no` |  `1 = yes` <br/> `2 = no`|
| **Missings:**| `8 = don't know` <br/> `9 = not applicable` <br/> `NA`|  `8 = don't know` <br/> `9 = not applicable` <br/> `NA`|
| **Description** |  | | 


```{r assign ghana w1, echo=F}
opal.assign.table.tibble(o, 'SAGE_ghana_w1','SAGE.ghanaINDData', variables=list('q3016','q3025'), missings = TRUE)
SAGE_ghana_w1 <- opal.execute(o,'SAGE_ghana_w1')
```

```{r local ghana w1, echo=F}
vbl <- SAGE_ghana_w1$q3016
vbl_miss <- c(8,9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(SAGE_ghana_w1)[2])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(SAGE_ghana_w1, aes(x=factor(q3016))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_ghana_w1$q3025
vbl_miss <- c(8,9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(SAGE_ghana_w1)[3])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(SAGE_ghana_w1, aes(x=factor(q3016))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `q3016=2&q3025=2 into 0` 
* `q3016=1|q3025=1 into 1`
* `8 into 998`
* `NA into 999`

**R script:**

```{r harmo ghana w1}
SAGE_ds_ghana_w1 <- tibble(id=SAGE_ghana_w1$id)
SAGE_ds_ghana_w1$vig_pa <- rep(999,length(SAGE_ds_ghana_w1$id))
SAGE_ds_ghana_w1$vig_pa[which(SAGE_ghana_w1$q3016==8|SAGE_ghana_w1$q3025==8)] <- 998
SAGE_ds_ghana_w1$vig_pa[which(SAGE_ghana_w1$q3016==2&SAGE_ghana_w1$q3025==2)] <- 0
SAGE_ds_ghana_w1$vig_pa[which(SAGE_ghana_w1$q3016==1|SAGE_ghana_w1$q3025==1)] <- 1
```

#### Statistical description of the new harmonised variable
```{r descript ghana w1, echo=F}
vbl <- SAGE_ds_ghana_w1$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_ghana_w1, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation ghana w1, echo=F}
AfterH <- table(SAGE_ds_ghana_w1$vig_pa)
X<-c(sum(na.omit(SAGE_ghana_w1$q3016==2&SAGE_ghana_w1$q3025==2)),sum(na.omit(SAGE_ghana_w1$q3016==1|SAGE_ghana_w1$q3025==1)),sum(na.omit(SAGE_ghana_w1$q3016==8|SAGE_ghana_w1$q3025==8)))
BeforeH <- c(X,length(SAGE_ghana_w1$q3016)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("q3016=2&q3025=2->0","q3016=1|q3025=1->1","8->998","NA->999") 
kable(C)
```





## India

### Wave 1 

#### Study-specific variable description

| **Name** | `q3016` | `q3025` |
|-|-|-|
| **Label** | `vigorous fitness/leisure` | `vigorous work` |
| **Table name** | `indiaINDData` | `indiaINDData` | 
| **Categories:**| `1 = yes` <br/> `2 = no` |  `1 = yes` <br/> `2 = no`|
| **Missings:**| `9 = not applicable` <br/> `NA`| `9 = not applicable` <br/> `NA`|
| **Description** |  | | 


```{r assign india w1, echo=F}
opal.assign.table.tibble(o, 'SAGE_india_w1','SAGE.indiaINDData', variables=list('q3016','q3025'), missings = TRUE)
SAGE_india_w1 <- opal.execute(o,'SAGE_india_w1')
```

```{r local india w1, echo=F}
vbl <- SAGE_india_w1$q3016
vbl_miss <- c(9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(SAGE_india_w1)[2])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(SAGE_india_w1, aes(x=factor(q3016))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_india_w1$q3025
vbl_miss <- c(9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(SAGE_india_w1)[3])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(SAGE_india_w1, aes(x=factor(q3016))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `q3016=2&q3025=2 into 0` 
* `q3016=1|q3025=1 into 1`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo india w1}
SAGE_ds_india_w1 <- tibble(id=SAGE_india_w1$id)
SAGE_ds_india_w1$vig_pa <- rep(999,length(SAGE_ds_india_w1$id))
SAGE_ds_india_w1$vig_pa[which(SAGE_india_w1$q3016==9|SAGE_india_w1$q3025==9)] <- 996
SAGE_ds_india_w1$vig_pa[which(SAGE_india_w1$q3016==2&SAGE_india_w1$q3025==2)] <- 0
SAGE_ds_india_w1$vig_pa[which(SAGE_india_w1$q3016==1|SAGE_india_w1$q3025==1)] <- 1
```

#### Statistical description of the new harmonised variable
```{r descript india w1, echo=F}
vbl <- SAGE_ds_india_w1$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_india_w1, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation india w1, echo=F}
AfterH <- table(SAGE_ds_india_w1$vig_pa)
X<-c(sum(na.omit(SAGE_india_w1$q3016==2&SAGE_india_w1$q3025==2)),sum(na.omit(SAGE_india_w1$q3016==1|SAGE_india_w1$q3025==1)),sum(na.omit(SAGE_india_w1$q3016==9|SAGE_india_w1$q3025==9)))
BeforeH <- c(X,length(SAGE_india_w1$q3016)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("q3016=2&q3025=2->0","q3016=1|q3025=1->1","9->996","NA->999") 
kable(C)
```






## Mexico

### Wave 1 

#### Study-specific variable description

| **Name** | `q3016` | `q3025` |
|-|-|-|
| **Label** | `vigorous fitness/leisure` | `vigorous work` |
| **Table name** | `mexicoINDdata` | `mexicoINDdata` | 
| **Categories:**| `1 = yes` <br/> `2 = no` |  `1 = yes` <br/> `2 = no`|
| **Missings:**| `NA`| `NA`|
| **Description** |  | | 


```{r assign mexico w1, echo=F}
opal.assign.table.tibble(o, 'SAGE_mexico_w1','SAGE.mexicoINDdata', variables=list('q3016','q3025'), missings = TRUE)
SAGE_mexico_w1 <- opal.execute(o,'SAGE_mexico_w1')
```

```{r local mexico w1, echo=F}
vbl <- SAGE_mexico_w1$q3016
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(SAGE_mexico_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(SAGE_mexico_w1, aes(x=factor(q3016))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_mexico_w1$q3025
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(SAGE_mexico_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(SAGE_mexico_w1, aes(x=factor(q3016))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `q3016=2&q3025=2 into 0` 
* `q3016=1|q3025=1 into 1`
* `NA into 999`

**R script:**

```{r harmo mexico w1}
SAGE_ds_mexico_w1 <- tibble(id=SAGE_mexico_w1$id)
SAGE_ds_mexico_w1$vig_pa <- rep(999,length(SAGE_ds_mexico_w1$id))
SAGE_ds_mexico_w1$vig_pa[which(SAGE_mexico_w1$q3016==2&SAGE_mexico_w1$q3025==2)] <- 0
SAGE_ds_mexico_w1$vig_pa[which(SAGE_mexico_w1$q3016==1|SAGE_mexico_w1$q3025==1)] <- 1
```

#### Statistical description of the new harmonised variable
```{r descript mexico w1, echo=F}
vbl <- SAGE_ds_mexico_w1$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_mexico_w1, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation mexico w1, echo=F}
AfterH <- table(SAGE_ds_mexico_w1$vig_pa)
X<-c(sum(na.omit(SAGE_mexico_w1$q3016==2&SAGE_mexico_w1$q3025==2)),sum(na.omit(SAGE_mexico_w1$q3016==1|SAGE_mexico_w1$q3025==1)))
BeforeH <- c(X,length(SAGE_mexico_w1$q3016)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("q3016=2&q3025=2->0","q3016=1|q3025=1->1","NA->999") 
kable(C)
```





## Russian Federation

### Wave 1 

#### Study-specific variable description

| **Name** | `q3016` | `q3025` |
|-|-|-|
| **Label** | `vigorous fitness/leisure` | `vigorous work` |
| **Table name** | `russiaINDdata` | `russiaINDdata` |
| **Categories:**| `1 = yes` <br/> `2 = no` |  `1 = yes` <br/> `2 = no`|
| **Missings:**| `8 = don't know` <br/> `NA`|  `8 = don't know` <br/> `NA`|
| **Description** |  | | 


```{r assign russia w1, echo=F}
opal.assign.table.tibble(o, 'SAGE_russia_w1','SAGE.russiaINDdata', variables=list('q3016','q3025'), missings = TRUE)
SAGE_russia_w1 <- opal.execute(o,'SAGE_russia_w1')
```

```{r local russia w1, echo=F}
vbl <- SAGE_russia_w1$q3016
vbl_miss <- c(8)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(SAGE_russia_w1)[2])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(SAGE_russia_w1, aes(x=factor(q3016))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_russia_w1$q3025
vbl_miss <- c(8)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(SAGE_russia_w1)[3])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(SAGE_russia_w1, aes(x=factor(q3016))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `q3016=2&q3025=2 into 0` 
* `q3016=1|q3025=1 into 1`
* `8 into 998`
* `NA into 999`

**R script:**

```{r harmo russia w1}
SAGE_ds_russia_w1 <- tibble(id=SAGE_russia_w1$id)
SAGE_ds_russia_w1$vig_pa <- rep(999,length(SAGE_ds_russia_w1$id))
SAGE_ds_russia_w1$vig_pa[which(SAGE_russia_w1$q3016==8|SAGE_russia_w1$q3025==8)] <- 998
SAGE_ds_russia_w1$vig_pa[which(SAGE_russia_w1$q3016==2&SAGE_russia_w1$q3025==2)] <- 0
SAGE_ds_russia_w1$vig_pa[which(SAGE_russia_w1$q3016==1|SAGE_russia_w1$q3025==1)] <- 1
```

#### Statistical description of the new harmonised variable
```{r descript russia w1, echo=F}
vbl <- SAGE_ds_russia_w1$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_russia_w1, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation russia w1, echo=F}
AfterH <- table(SAGE_ds_russia_w1$vig_pa)
X<-c(sum(na.omit(SAGE_russia_w1$q3016==2&SAGE_russia_w1$q3025==2)),sum(na.omit(SAGE_russia_w1$q3016==1|SAGE_russia_w1$q3025==1)),sum(na.omit(SAGE_russia_w1$q3016==8|SAGE_russia_w1$q3025==8)))
BeforeH <- c(X,length(SAGE_russia_w1$q3016)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("q3016=2&q3025=2->0","q3016=1|q3025=1->1","8->998","NA->999") 
kable(C)
```


## Summary of descriptive statistics of the harmonised variable accross populations and waves




```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


sage.cw <- list(SA_w1 = c("SA_w1","South Africa w1"), ghana_w1 = c("ghana_w1","Ghana w1"), china_w1 = c("china_w1","China w1"), india_w1 = c("india_w1","India w1"), russia_w1 = c("russia_w1","Russian Federation w1"), mexico_w1 = c("mexico_w1","Mexico w1"))

# Consider only harmonised waves
l.hds <- lapply(sage.cw, function(wname) if(exists(paste0("SAGE_ds_",wname[1]))){wname = list(get(paste0("SAGE_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```




# Quality estimation



<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
