---
title: "Ever smoked"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/ever_smokedDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/ever_smokedDS.R')
```

# Data process





## South Africa

### Wave 1

#### Study-specific variable description




| **Name** | ``q3001``|
|-|-|
| **Label** |`ever used tobacco?` |
| **Table name** |`southAfricaINDdata`|
| **Categories** |`1 = yes`<br/>`2 = no`|
| **Missings** |`8 = don't know`<br/>`NA`|
| **Description** |  |



```{r assign africa w1, echo=F}
opal.assign.table.tibble(o, 'SAGE_SA_w1_ever_smoked','SAGE.southAfricaINDdata', variables=list('q3001'), missings = TRUE)
```

```{r local africa w1, echo=F}
SAGE_SA_w1_ever_smoked <- opal.execute(o,'SAGE_SA_w1_ever_smoked')
vbl <- SAGE_SA_w1_ever_smoked$q3001
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = "q3001")
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(SAGE_SA_w1_ever_smoked, aes(x=factor(q3001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever smoked") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0` 
* `8 into 998`
* `NA into 999`

```{r harmo africa w1}
SAGE_ds_SA_w1 <- tibble(id=SAGE_SA_w1_ever_smoked$id)
SAGE_ds_SA_w1$ever_smoked <- Recode(SAGE_SA_w1_ever_smoked$q3001, "1 = '1';2 = '0';8 = '998';NA = '999' ")
SAGE_ds_SA_w1$ever_smoked <- labelled(SAGE_ds_SA_w1$ever_smoked, labels = c(No=0, Yes=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript africa w1, echo=F}
vbl <- SAGE_ds_SA_w1$ever_smoked
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(SAGE_ds_SA_w1, aes(x=factor(ever_smoked))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever smoked") + ylab("Frequency")
```

#### Validation
```{r crosstabulation africa w1, echo=F}
AfterH <- table(SAGE_ds_SA_w1$ever_smoked)
X<-table(SAGE_SA_w1_ever_smoked$q3001)
BeforeH <- c(X[c(2,1,3)],sum(is.na(SAGE_SA_w1_ever_smoked$q3001)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","8->998","NA->999") 
kable(C)
```





## China

### Wave 1

#### Study-specific variable description




| **Name** | ``q3001``|
|-|-|
| **Label** |`ever used tobacco?` |
| **Table name** |`chinaINDData`|
| **Categories** |`1 = yes`<br/>`2 = no`|
| **Missings** |`NA`|
| **Description** |  |

```{r assign china w1, echo=F}
opal.assign.table.tibble(o, 'SAGE_china_w1_ever_smoked','SAGE.chinaINDData', variables=list('q3001'), missings = TRUE)
```

```{r local china w1, echo=F}
SAGE_china_w1_ever_smoked <- opal.execute(o,'SAGE_china_w1_ever_smoked')
vbl <- SAGE_china_w1_ever_smoked$q3001
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = "q3001")
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(SAGE_china_w1_ever_smoked, aes(x=factor(q3001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever smoked") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0` 
* `NA into 999`

```{r harmo china w1}
SAGE_ds_china_w1 <- tibble(id=SAGE_china_w1_ever_smoked$id)
SAGE_ds_china_w1$ever_smoked <- Recode(SAGE_china_w1_ever_smoked$q3001, "1 = '1';2 = '0';NA = '999' ")
SAGE_ds_china_w1$ever_smoked <- labelled(SAGE_ds_china_w1$ever_smoked, labels = c(No=0, Yes=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript china w1, echo=F}
vbl <- SAGE_ds_china_w1$ever_smoked
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(SAGE_ds_china_w1, aes(x=factor(ever_smoked))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever smoked") + ylab("Frequency")
```

#### Validation
```{r crosstabulation china w1, echo=F}
AfterH <- table(SAGE_ds_china_w1$ever_smoked)
X<-table(SAGE_china_w1_ever_smoked$q3001)
BeforeH <- c(X[2:1],sum(is.na(SAGE_china_w1_ever_smoked$q3001)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1", "NA->999") 
kable(C)
```


## Ghana

### Wave 1

#### Study-specific variable description




| **Name** | ``q3001``|
|-|-|
| **Label** |`ever used tobacco?` |
| **Table name** |`ghanaINDData`|
| **Categories** |`1 = yes`<br/>`2 = no`|
| **Missings** |`8 = don't know`<br/>`9 = not applicable`<br/>`NA`|
| **Description** |  |

```{r assign ghana w1, echo=F}
opal.assign.table.tibble(o, 'SAGE_ghana_w1_ever_smoked','SAGE.ghanaINDData', variables=list('q3001'), missings = TRUE)
```

```{r local ghana w1, echo=F}
SAGE_ghana_w1_ever_smoked <- opal.execute(o,'SAGE_ghana_w1_ever_smoked')
vbl <- SAGE_ghana_w1_ever_smoked$q3001
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = "q3001")
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(SAGE_ghana_w1_ever_smoked, aes(x=factor(q3001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever smoked") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0` 
* `8 into 998`
* `9 into 996`
* `NA into 999`

```{r harmo ghana w1}
SAGE_ds_ghana_w1 <- tibble(id=SAGE_ghana_w1_ever_smoked$id)
SAGE_ds_ghana_w1$ever_smoked <- Recode(SAGE_ghana_w1_ever_smoked$q3001, "1 = '1';2 = '0';8 = '998';9 = '996';NA = '999' ")
SAGE_ds_ghana_w1$ever_smoked <- labelled(SAGE_ds_ghana_w1$ever_smoked, labels = c(No=0, Yes=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript ghana w1, echo=F}
vbl <- SAGE_ds_ghana_w1$ever_smoked
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(SAGE_ds_ghana_w1, aes(x=factor(ever_smoked))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever smoked") + ylab("Frequency")
```

#### Validation
```{r crosstabulation ghana w1, echo=F}
AfterH <- table(SAGE_ds_ghana_w1$ever_smoked)
X<-table(SAGE_ghana_w1_ever_smoked$q3001)
BeforeH <- c(X[c(2,1,4,3)],sum(is.na(SAGE_ghana_w1_ever_smoked$q3001)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","9->996","8->998","NA->999") 
kable(C)
```



## India

### Wave 1

#### Study-specific variable description




| **Name** | ``q3001``|
|-|-|
| **Label** |`ever used tobacco?` |
| **Table name** |`indiaINDData`|
| **Categories** |`1 = yes`<br/>`2 = no`|
| **Missings** |`8 = don't know`<br/>`9 = not applicable`<br/>`NA`|
| **Description** |  |

```{r assign india w1, echo=F}
opal.assign.table.tibble(o, 'SAGE_india_w1_ever_smoked','SAGE.indiaINDData', variables=list('q3001'), missings = TRUE)
```

```{r local india w1, echo=F}
SAGE_india_w1_ever_smoked <- opal.execute(o,'SAGE_india_w1_ever_smoked')
vbl <- SAGE_india_w1_ever_smoked$q3001
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = "q3001")
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(SAGE_india_w1_ever_smoked, aes(x=factor(q3001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever smoked") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0` 
* `8 into 998`
* `9 into 996`
* `NA into 999`

```{r harmo india w1}
SAGE_ds_india_w1 <- tibble(id=SAGE_india_w1_ever_smoked$id)
SAGE_ds_india_w1$ever_smoked <- Recode(SAGE_india_w1_ever_smoked$q3001, "1 = '1';2 = '0';8 = '998';9 = '996';NA = '999' ")
SAGE_ds_india_w1$ever_smoked <- labelled(SAGE_ds_india_w1$ever_smoked, labels = c(No=0, Yes=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript india w1, echo=F}
vbl <- SAGE_ds_india_w1$ever_smoked
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(SAGE_ds_india_w1, aes(x=factor(ever_smoked))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever smoked") + ylab("Frequency")
```

#### Validation
```{r crosstabulation india w1, echo=F}
AfterH <- table(SAGE_ds_india_w1$ever_smoked)
X<-table(SAGE_india_w1_ever_smoked$q3001)
BeforeH <- c(X[c(2,1,4,3)],sum(is.na(SAGE_india_w1_ever_smoked$q3001)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","9->996","8->998","NA->999") 
kable(C)
```



## Mexico

### Wave 1

#### Study-specific variable description




| **Name** | ``q3001``|
|-|-|
| **Label** |`ever used tobacco?` |
| **Table name** |`mexicoINDdata`|
| **Categories** |`1 = yes`<br/>`2 = no`|
| **Missings** |`NA`|
| **Description** |  |

```{r assign mexico w1, echo=F}
opal.assign.table.tibble(o, 'SAGE_mexico_w1_ever_smoked','SAGE.mexicoINDdata', variables=list('q3001'), missings = TRUE)
```

```{r local mexico w1, echo=F}
SAGE_mexico_w1_ever_smoked <- opal.execute(o,'SAGE_mexico_w1_ever_smoked')
vbl <- SAGE_mexico_w1_ever_smoked$q3001
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = "q3001")
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(SAGE_mexico_w1_ever_smoked, aes(x=factor(q3001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever smoked") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0` 
* `NA into 999`

```{r harmo mexico w1}
SAGE_ds_mexico_w1 <- tibble(id=SAGE_mexico_w1_ever_smoked$id)
SAGE_ds_mexico_w1$ever_smoked <- Recode(SAGE_mexico_w1_ever_smoked$q3001, "1 = '1';2 = '0';NA = '999' ")
SAGE_ds_mexico_w1$ever_smoked <- labelled(SAGE_ds_mexico_w1$ever_smoked, labels = c(No=0, Yes=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript mexico w1, echo=F}
vbl <- SAGE_ds_mexico_w1$ever_smoked
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(SAGE_ds_mexico_w1, aes(x=factor(ever_smoked))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever smoked") + ylab("Frequency")
```

#### Validation
```{r crosstabulation mexico w1, echo=F}
AfterH <- table(SAGE_ds_mexico_w1$ever_smoked)
X<-table(SAGE_mexico_w1_ever_smoked$q3001)
BeforeH <- c(X[2:1],sum(is.na(SAGE_mexico_w1_ever_smoked$q3001)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1", "NA->999") 
kable(C)
```



## Russian Federation

### Wave 1

#### Study-specific variable description




| **Name** | ``q3001``|
|-|-|
| **Label** |`ever used tobacco?` |
| **Table name** |`russiaINDdata`|
| **Categories** |`1 = yes`<br/>`2 = no`|
| **Missings** |`8 = don't know`<br/>`9 = not applicable`<br/>`NA`|
| **Description** |  |


```{r assign russia w1, echo=F}
opal.assign.table.tibble(o, 'SAGE_russia_w1_ever_smoked','SAGE.russiaINDdata', variables=list('q3001'), missings = TRUE)
```

```{r local russia w1, echo=F}
SAGE_russia_w1_ever_smoked <- opal.execute(o,'SAGE_russia_w1_ever_smoked')
vbl <- SAGE_russia_w1_ever_smoked$q3001
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = "q3001")
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(SAGE_russia_w1_ever_smoked, aes(x=factor(q3001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever smoked") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0` 
* `8 into 998`
* `9 into 996`
* `NA into 999`

```{r harmo russia w1}
SAGE_ds_russia_w1 <- tibble(id=SAGE_russia_w1_ever_smoked$id)
SAGE_ds_russia_w1$ever_smoked <- Recode(SAGE_russia_w1_ever_smoked$q3001, "1 = '1';2 = '0';8 = '998';9 = '996';NA = '999' ")
SAGE_ds_russia_w1$ever_smoked <- labelled(SAGE_ds_russia_w1$ever_smoked, labels = c(No=0, Yes=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript russia w1, echo=F}
vbl <- SAGE_ds_russia_w1$ever_smoked
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(SAGE_ds_russia_w1, aes(x=factor(ever_smoked))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever smoked") + ylab("Frequency")
```

#### Validation
```{r crosstabulation russia w1, echo=F}
AfterH <- table(SAGE_ds_russia_w1$ever_smoked)
X<-table(SAGE_russia_w1_ever_smoked$q3001)
BeforeH <- c(X[c(2,1,4,3)],sum(is.na(SAGE_russia_w1_ever_smoked$q3001)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","9->996","8->998","NA->999") 
kable(C)
```




## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable:


**R script:**

```{r summ}

l.hds <- list(SA_w1 = SAGE_ds_SA_w1 , ghana_w1 = SAGE_ds_ghana_w1, china_w1 = SAGE_ds_china_w1, india_w1=SAGE_ds_india_w1, russia_w1=SAGE_ds_russia_w1, mexico_w1=SAGE_ds_mexico_w1)

for(name in names(l.hds)) {
  m_name <- paste0("SAGE_m_ds_",name)
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  assign(m_name, aux_object)
  rm(aux_object)
}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]])) )
names(t.hds)<-c("val", "label", "South_Africa_w1", "Ghana_W1", "China_W1", "India_W1", "Russia_W1", "Mexico_W1")
kable(t.hds, caption = 'ever_smoked')

```



# Quality estimation



<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(l.hds)){
  ever_smoked <- l.hds[[index]]
  save(ever_smoked, file = paste0(datafolder,names(l.hds)[index],"/ever_smoked.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





