---
title: "Number of cigarettes"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/n_cigarettesDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/n_cigarettesDS.R')
```


# Data process






## South Africa

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `q3004a`
* Label: `manufact. cigarettes`
* Categories:
   + `Continuous variable`
* Missings
   + `-8 = don't know`
   + `NA`
   
   
* Name: `q3004b`
* Label: `hand-rolled cigarettes`
* Categories:
   + `Continuous variable`
* Missings
   + `-8 = don't know`
   + `NA`
   

```{r assign SA w1, echo=F}
opal.assign.table.tibble(o, 'SAGE_SA_w1_n_cigarettes','SAGE.southAfricaINDdata', variables=list('q3004a','q3004b'), missings = TRUE)
```

```{r local SA w1, echo=F}
SAGE_SA_w1_n_cigarettes <- opal.execute(o,'SAGE_SA_w1_n_cigarettes')
vbl <- SAGE_SA_w1_n_cigarettes$q3004a
kable(Continuous_summary(vbl, missing_values = c(-8))[3], caption = "q3004a")
pander(Continuous_summary(vbl, missing_values = c(-8))$summary, caption = "Summary")
ggplot(SAGE_SA_w1_n_cigarettes, aes(x=factor(q3004a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of cigarettes smoked") + ylab("Frequency")
vbl <- SAGE_SA_w1_n_cigarettes$q3004b
kable(Continuous_summary(vbl, missing_values = c(-8))[3], caption = "q3004b")
pander(Continuous_summary(vbl, missing_values = c(-8))$summary, caption = "Summary")
ggplot(SAGE_SA_w1_n_cigarettes, aes(x=factor(q3004b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of cigarettes smoked") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `(q3004a+q3004b)*7` 
* `-8 into 998`
* `NA into 999`

```{r harmo SA w1}
SAGE_ds_SA_w1 <- tibble(id=SAGE_SA_w1_n_cigarettes$id)
SAGE_ds_SA_w1$n_cigarettes <- rep(888,length(SAGE_ds_SA_w1$id))
for(i in 1:length(SAGE_ds_SA_w1$id))
{
  if(is.na(SAGE_SA_w1_n_cigarettes$q3004a[i])==TRUE|is.na(SAGE_SA_w1_n_cigarettes$q3004b[i])==TRUE)
    SAGE_ds_SA_w1$n_cigarettes[i] <- 999
  else{
      if(SAGE_SA_w1_n_cigarettes$q3004a[i]==-8|SAGE_SA_w1_n_cigarettes$q3004b[i]==-8)
    SAGE_ds_SA_w1$n_cigarettes[i] <- 998
    else{
      SAGE_ds_SA_w1$n_cigarettes[i] <- (SAGE_SA_w1_n_cigarettes$q3004a[i]+SAGE_SA_w1_n_cigarettes$q3004b[i])*7
    }
}
}
#SAGE_ds_SA_w1$n_cigarettes <- Recode(rowSums(cbind(SAGE_SA_w1_n_cigarettes$q3004a,SAGE_SA_w1_n_cigarettes$q3004b),na.rm = TRUE)*7, "0 = '999' ")
SAGE_ds_SA_w1$n_cigarettes <- labelled(SAGE_ds_SA_w1$n_cigarettes, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript SA w1, echo=F}
vbl <- SAGE_ds_SA_w1$n_cigarettes
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(SAGE_ds_SA_w1,!vbl %in% miss_values_vector), aes(n_cigarettes)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of cigarettes smoked per week") + ylab("Frequency")
```

#### Validation
```{r crosstabulation SA w1, echo=F}
#AfterH <- table(SAGE_ds_SA_w1$n_cigarettes)
#X <- table(rowSums(cbind(SAGE_SA_w1_n_cigarettes$q3004a,SAGE_SA_w1_n_cigarettes$q3004b))*7)
#BeforeH <- c(X[-c(1:8)],sum(X[1:8]),length(SAGE_SA_w1_n_cigarettes$q3004a)-sum(X))
#C <- rbind(BeforeH,AfterH)
#colnames(C) <- c(paste(sort(c(unique(na.omit(SAGE_SA_w1_n_cigarettes$q3004a+SAGE_SA_w1_n_cigarettes$q3004b))))[-c(1:8)],"->",sort(unique(na.omit(SAGE_ds_SA_w1$n_cigarettes)))[-c(28:29)],sep=""),"-8->998","NA->999")
#kable(C)
```






## China

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `q3004a`
* Label: `manufact. cigarettes`
* Categories:
   + `Continuous variable`
* Missings
   + `NA`
   
   
* Name: `q3004b`
* Label: `hand-rolled cigarettes`
* Categories:
   + `Continuous variable`
* Missings
   + `NA`
   

```{r assign china w1, echo=F}
opal.assign.table.tibble(o, 'SAGE_china_w1_n_cigarettes','SAGE.chinaINDData', variables=list('q3004a','q3004b'), missings = TRUE)
```

```{r local china w1, echo=F}
SAGE_china_w1_n_cigarettes <- opal.execute(o,'SAGE_china_w1_n_cigarettes')
vbl <- SAGE_china_w1_n_cigarettes$q3004a
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "q3004a")
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(SAGE_china_w1_n_cigarettes, aes(x=factor(q3004a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of cigarettes smoked") + ylab("Frequency")
vbl <- SAGE_china_w1_n_cigarettes$q3004b
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "q3004b")
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(SAGE_china_w1_n_cigarettes, aes(x=factor(q3004b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of cigarettes smoked") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `(q3004a+q3004b)*7` 
* `NA into 999`

```{r harmo china w1}
SAGE_ds_china_w1 <- tibble(id=SAGE_china_w1_n_cigarettes$id)
SAGE_ds_china_w1$n_cigarettes <- Recode(rowSums(cbind(SAGE_china_w1_n_cigarettes$q3004a,SAGE_china_w1_n_cigarettes$q3004b),na.rm = TRUE)*7, "0 = '999' ")
SAGE_ds_china_w1$n_cigarettes <- labelled(SAGE_ds_china_w1$n_cigarettes, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript china w1, echo=F}
vbl <- SAGE_ds_china_w1$n_cigarettes
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(SAGE_ds_china_w1,!vbl %in% miss_values_vector), aes(n_cigarettes)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of cigarettes smoked per week") + ylab("Frequency")
```

#### Validation
```{r crosstabulation china w1, echo=F}
AfterH <- table(SAGE_ds_china_w1$n_cigarettes)
X <- table(rowSums(cbind(SAGE_china_w1_n_cigarettes$q3004a,SAGE_china_w1_n_cigarettes$q3004b),na.rm = TRUE)*7)
BeforeH <- c(X[2:43],length(SAGE_china_w1_n_cigarettes$q3004a)-sum(X[2:43]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(paste(sort(c(unique(na.omit(SAGE_china_w1_n_cigarettes$q3004a+SAGE_china_w1_n_cigarettes$q3004b)),36))[-1],"->",sort(unique(na.omit(SAGE_ds_china_w1$n_cigarettes)))[-43],sep=""),"NA->999")
kable(C)
```




## Ghana

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `q3004a`
* Label: `manufact. cigarettes`
* Categories:
   + `Continuous variable`
* Missings
   + `-8 = don't know`
   + `NA`
   
   
* Name: `q3004b`
* Label: `hand-rolled cigarettes`
* Categories:
   + `Continuous variable`
* Missings
   + `-8 = don't know`
   + `NA`
   

```{r assign ghana w1, echo=F}
opal.assign.table.tibble(o, 'SAGE_ghana_w1_n_cigarettes','SAGE.ghanaINDData', variables=list('q3004a','q3004b'), missings = TRUE)
```

```{r local ghana w1, echo=F}
SAGE_ghana_w1_n_cigarettes <- opal.execute(o,'SAGE_ghana_w1_n_cigarettes')
vbl <- SAGE_ghana_w1_n_cigarettes$q3004a
kable(Continuous_summary(vbl, missing_values = c(-8))[3], caption = "q3004a")
pander(Continuous_summary(vbl, missing_values = c(-8))$summary, caption = "Summary")
ggplot(SAGE_ghana_w1_n_cigarettes, aes(x=factor(q3004a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of cigarettes smoked") + ylab("Frequency")
vbl <- SAGE_ghana_w1_n_cigarettes$q3004b
kable(Continuous_summary(vbl, missing_values = c(-8))[3], caption = "q3004b")
pander(Continuous_summary(vbl, missing_values = c(-8))$summary, caption = "Summary")
ggplot(SAGE_ghana_w1_n_cigarettes, aes(x=factor(q3004b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of cigarettes smoked") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `(q3004a+q3004b)*7` 
* `-8 into 998`
* `NA into 999`

```{r harmo ghana w1}
SAGE_ds_ghana_w1 <- tibble(id=SAGE_ghana_w1_n_cigarettes$id)
SAGE_ds_ghana_w1$n_cigarettes <- rep(888,length(SAGE_ds_ghana_w1$id))
for(i in 1:length(SAGE_ds_ghana_w1$id))
{
  if(is.na(SAGE_ghana_w1_n_cigarettes$q3004a[i])==TRUE|is.na(SAGE_ghana_w1_n_cigarettes$q3004b[i])==TRUE)
    SAGE_ds_ghana_w1$n_cigarettes[i] <- 999
  else{
    if(SAGE_ghana_w1_n_cigarettes$q3004a[i]==-8|SAGE_ghana_w1_n_cigarettes$q3004b[i]==-8)
    SAGE_ds_ghana_w1$n_cigarettes[i] <- 998
    else{
      SAGE_ds_ghana_w1$n_cigarettes[i] <- (SAGE_ghana_w1_n_cigarettes$q3004a[i]+SAGE_ghana_w1_n_cigarettes$q3004b[i])*7
    }
      }

}
#SAGE_ds_ghana_w1$n_cigarettes <- Recode(rowSums(cbind(SAGE_ghana_w1_n_cigarettes$q3004a,SAGE_ghana_w1_n_cigarettes$q3004b),na.rm = TRUE)*7, "0 = '999' ")
SAGE_ds_ghana_w1$n_cigarettes <- labelled(SAGE_ds_ghana_w1$n_cigarettes, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript ghana w1, echo=F}
vbl <- SAGE_ds_ghana_w1$n_cigarettes
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(SAGE_ds_ghana_w1,!vbl %in% miss_values_vector), aes(n_cigarettes)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of cigarettes smoked per week") + ylab("Frequency")
```

#### Validation
```{r crosstabulation ghana w1, echo=F}
#AfterH <- table(SAGE_ds_ghana_w1$n_cigarettes)
#X <- table(rowSums(cbind(SAGE_ghana_w1_n_cigarettes$q3004a,SAGE_ghana_w1_n_cigarettes$q3004b))*7)
#BeforeH <- c(X[-c(1:6)],sum(X[1:6]),length(SAGE_ghana_w1_n_cigarettes$q3004a)-sum(X))
#C <- rbind(BeforeH,AfterH)
#colnames(C) <- c(paste(sort(c(unique(na.omit(SAGE_ghana_w1_n_cigarettes$q3004a+SAGE_ghana_w1_n_cigarettes$q3004b))))[-c(1:6)],"->",sort(unique(na.omit(SAGE_ds_ghana_w1$n_cigarettes)))[-c(18:19)],sep=""),"-8->998","NA->999")
#kable(C)
```





## India

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `q3004a`
* Label: `manufact. cigarettes`
* Categories:
   + `Continuous variable`
* Missings
   + `-8 = don't know`
   + `-9 = not applicable`
   + `NA`
   
   
* Name: `q3004b`
* Label: `hand-rolled cigarettes`
* Categories:
   + `Continuous variable`
* Missings
   + `-8 = don't know`
   + `-9 = not applicable`
   + `NA`
   

```{r assign india w1, echo=F}
opal.assign.table.tibble(o, 'SAGE_india_w1_n_cigarettes','SAGE.indiaINDData', variables=list('q3004a','q3004b'), missings = TRUE)
```

```{r local india w1, echo=F}
SAGE_india_w1_n_cigarettes <- opal.execute(o,'SAGE_india_w1_n_cigarettes')
vbl <- SAGE_india_w1_n_cigarettes$q3004a
kable(Continuous_summary(vbl, missing_values = c(-8,-9))[3], caption = "q3004a")
pander(Continuous_summary(vbl, missing_values = c(-8,-9))$summary, caption = "Summary")
ggplot(SAGE_india_w1_n_cigarettes, aes(x=factor(q3004a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of cigarettes smoked") + ylab("Frequency")
vbl <- SAGE_india_w1_n_cigarettes$q3004b
kable(Continuous_summary(vbl, missing_values = c(-8,-9))[3], caption = "q3004b")
pander(Continuous_summary(vbl, missing_values = c(-8,-9))$summary, caption = "Summary")
ggplot(SAGE_india_w1_n_cigarettes, aes(x=factor(q3004b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of cigarettes smoked") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `(q3004a+q3004b)*7` 
* `-8 into 998`
* `-9 into 996`
* `NA into 999`

```{r harmo india w1}
SAGE_ds_india_w1 <- tibble(id=SAGE_india_w1_n_cigarettes$id)
SAGE_ds_india_w1$n_cigarettes <- rep(888,length(SAGE_ds_india_w1$id))
for(i in 1:length(SAGE_ds_india_w1$id))
{
  if(is.na(SAGE_india_w1_n_cigarettes$q3004a[i])==TRUE|is.na(SAGE_india_w1_n_cigarettes$q3004b[i])==TRUE)
    SAGE_ds_india_w1$n_cigarettes[i] <- 999
  else{
    if(SAGE_india_w1_n_cigarettes$q3004a[i]==-9|SAGE_india_w1_n_cigarettes$q3004b[i]==-9)
    SAGE_ds_india_w1$n_cigarettes[i] <- 996
    else{
      if(SAGE_india_w1_n_cigarettes$q3004a[i]==-8|SAGE_india_w1_n_cigarettes$q3004b[i]==-8)
    SAGE_ds_india_w1$n_cigarettes[i] <- 998
    else{
      SAGE_ds_india_w1$n_cigarettes[i] <- (SAGE_india_w1_n_cigarettes$q3004a[i]+SAGE_india_w1_n_cigarettes$q3004b[i])*7
    }
      }
}
}
#SAGE_ds_india_w1$n_cigarettes <- Recode(rowSums(cbind(SAGE_india_w1_n_cigarettes$q3004a,SAGE_india_w1_n_cigarettes$q3004b),na.rm = TRUE)*7, "0 = '999' ")
SAGE_ds_india_w1$n_cigarettes <- labelled(SAGE_ds_india_w1$n_cigarettes, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript india w1, echo=F}
vbl <- SAGE_ds_india_w1$n_cigarettes
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(SAGE_ds_india_w1,!vbl %in% miss_values_vector), aes(n_cigarettes)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of cigarettes smoked per week") + ylab("Frequency")
```

#### Validation
```{r crosstabulation india w1, echo=F}
AfterH <- table(SAGE_ds_india_w1$n_cigarettes)
X <- table(rowSums(cbind(SAGE_india_w1_n_cigarettes$q3004a,SAGE_india_w1_n_cigarettes$q3004b))*7)
BeforeH <- c(X[-c(1:2)],X[1:2],length(SAGE_india_w1_n_cigarettes$q3004a)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(paste(sort(c(unique(na.omit(SAGE_india_w1_n_cigarettes$q3004a+SAGE_india_w1_n_cigarettes$q3004b))))[-c(1:2)],"->",sort(unique(na.omit(SAGE_ds_india_w1$n_cigarettes)))[-c(22:24)],sep=""),"-9->996","-8->998","NA->999")
kable(C)
```






## Mexico

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `q3004a`
* Label: `manufact. cigarettes`
* Categories:
   + `Continuous variable`
* Missings
   + `NA`
   
   
* Name: `q3004b`
* Label: `hand-rolled cigarettes`
* Categories:
   + `Continuous variable`
* Missings
   + `NA`
   

```{r assign mexico w1, echo=F}
opal.assign.table.tibble(o, 'SAGE_mexico_w1_n_cigarettes','SAGE.mexicoINDdata', variables=list('q3004a','q3004b'), missings = TRUE)
```

```{r local mexico w1, echo=F}
SAGE_mexico_w1_n_cigarettes <- opal.execute(o,'SAGE_mexico_w1_n_cigarettes')
vbl <- SAGE_mexico_w1_n_cigarettes$q3004a
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "q3004a")
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(SAGE_mexico_w1_n_cigarettes, aes(x=factor(q3004a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of cigarettes smoked") + ylab("Frequency")
vbl <- SAGE_mexico_w1_n_cigarettes$q3004b
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "q3004b")
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(SAGE_mexico_w1_n_cigarettes, aes(x=factor(q3004b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of cigarettes smoked") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `(q3004a+q3004b)*7` 
* `NA into 999`

```{r harmo mexico w1}
SAGE_ds_mexico_w1 <- tibble(id=SAGE_mexico_w1_n_cigarettes$id)
SAGE_ds_mexico_w1$n_cigarettes <- Recode(rowSums(cbind(SAGE_mexico_w1_n_cigarettes$q3004a,SAGE_mexico_w1_n_cigarettes$q3004b),na.rm = TRUE)*7, "0 = '999' ")
SAGE_ds_mexico_w1$n_cigarettes <- labelled(SAGE_ds_mexico_w1$n_cigarettes, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript mexico w1, echo=F}
vbl <- SAGE_ds_mexico_w1$n_cigarettes
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(SAGE_ds_mexico_w1,!vbl %in% miss_values_vector), aes(n_cigarettes)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of cigarettes smoked per week") + ylab("Frequency")
```

#### Validation
```{r crosstabulation mexico w1, echo=F}
AfterH <- table(SAGE_ds_mexico_w1$n_cigarettes)
X <- table(rowSums(cbind(SAGE_mexico_w1_n_cigarettes$q3004a,SAGE_mexico_w1_n_cigarettes$q3004b),na.rm = TRUE)*7)
BeforeH <- c(X[2:28],length(SAGE_mexico_w1_n_cigarettes$q3004a)-sum(X[2:28]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(paste(sort(c(unique(na.omit(SAGE_mexico_w1_n_cigarettes$q3004a+SAGE_mexico_w1_n_cigarettes$q3004b))))[-1],"->",sort(unique(na.omit(SAGE_ds_mexico_w1$n_cigarettes)))[-28],sep=""),"NA->999")
kable(C)
```






## Russian Federation

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `q3004a`
* Label: `manufact. cigarettes`
* Categories:
   + `Continuous variable`
* Missings
   + `-8 = don't know`
   + `-9 = not applicable`
   + `NA`
   
   
* Name: `q3004b`
* Label: `hand-rolled cigarettes`
* Categories:
   + `Continuous variable`
* Missings
   + `-8 = don't know`
   + `-9 = not applicable`
   + `NA`
   

```{r assign russia w1, echo=F}
opal.assign.table.tibble(o, 'SAGE_russia_w1_n_cigarettes','SAGE.russiaINDdata', variables=list('q3004a','q3004b'), missings = TRUE)
```

```{r local russia w1, echo=F}
SAGE_russia_w1_n_cigarettes <- opal.execute(o,'SAGE_russia_w1_n_cigarettes')
vbl <- SAGE_russia_w1_n_cigarettes$q3004a
kable(Continuous_summary(vbl, missing_values = c(-8,-9))[3], caption = "q3004a")
pander(Continuous_summary(vbl, missing_values = c(-8,-9))$summary, caption = "Summary")
ggplot(SAGE_russia_w1_n_cigarettes, aes(x=factor(q3004a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of cigarettes smoked") + ylab("Frequency")
vbl <- SAGE_russia_w1_n_cigarettes$q3004b
kable(Continuous_summary(vbl, missing_values = c(-8,-9))[3], caption = "q3004b")
pander(Continuous_summary(vbl, missing_values = c(-8,-9))$summary, caption = "Summary")
ggplot(SAGE_russia_w1_n_cigarettes, aes(x=factor(q3004b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of cigarettes smoked") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `(q3004a+q3004b)*7` 
* `-8 into 998`
* `-9 into 996`
* `NA into 999`

```{r harmo russia w1}
SAGE_ds_russia_w1 <- tibble(id=SAGE_russia_w1_n_cigarettes$id)
SAGE_ds_russia_w1$n_cigarettes <- rep(888,length(SAGE_ds_russia_w1$id))
for(i in 1:length(SAGE_ds_russia_w1$id))
{
  if(is.na(SAGE_russia_w1_n_cigarettes$q3004a[i])==TRUE|is.na(SAGE_russia_w1_n_cigarettes$q3004b[i])==TRUE)
    SAGE_ds_russia_w1$n_cigarettes[i] <- 999
  else{
    if(SAGE_russia_w1_n_cigarettes$q3004a[i]==-9|SAGE_russia_w1_n_cigarettes$q3004b[i]==-9)
    SAGE_ds_russia_w1$n_cigarettes[i] <- 996
    else{
      if(SAGE_russia_w1_n_cigarettes$q3004a[i]==-8|SAGE_russia_w1_n_cigarettes$q3004b[i]==-8)
    SAGE_ds_russia_w1$n_cigarettes[i] <- 998
    else{
      SAGE_ds_russia_w1$n_cigarettes[i] <- (SAGE_russia_w1_n_cigarettes$q3004a[i]+SAGE_russia_w1_n_cigarettes$q3004b[i])*7
    }
      }
}
}
#SAGE_ds_russia_w1$n_cigarettes <- Recode(rowSums(cbind(SAGE_russia_w1_n_cigarettes$q3004a,SAGE_russia_w1_n_cigarettes$q3004b),na.rm = TRUE)*7, "0 = '999' ")
SAGE_ds_russia_w1$n_cigarettes <- labelled(SAGE_ds_russia_w1$n_cigarettes, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript russia w1, echo=F}
vbl <- SAGE_ds_russia_w1$n_cigarettes
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(SAGE_ds_russia_w1,!vbl %in% miss_values_vector), aes(n_cigarettes)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of cigarettes smoked per week") + ylab("Frequency")
```

#### Validation
```{r crosstabulation russia w1, echo=F}
AfterH <- table(SAGE_ds_russia_w1$n_cigarettes)
X <- table(rowSums(cbind(SAGE_russia_w1_n_cigarettes$q3004a,SAGE_russia_w1_n_cigarettes$q3004b))*7)
BeforeH <- c(X[-c(1:4)],X[1],sum(X[2:4]),length(SAGE_russia_w1_n_cigarettes$q3004a)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(paste(sort(c(unique(na.omit(SAGE_russia_w1_n_cigarettes$q3004a+SAGE_russia_w1_n_cigarettes$q3004b))))[-c(1:4)],"->",sort(unique(na.omit(SAGE_ds_russia_w1$n_cigarettes)))[-c(30:33)],sep=""),"-9->996","-8->998","NA->999")
kable(C)
```









```{r final, echo=F}

l.hds <- list(SA_w1 = SAGE_ds_SA_w1 , ghana_w1 = SAGE_ds_ghana_w1, china_w1 = SAGE_ds_china_w1, india_w1=SAGE_ds_india_w1, russia_w1=SAGE_ds_russia_w1, mexico_w1=SAGE_ds_mexico_w1)

for(name in names(l.hds)) {
  label(l.hds[[name]][[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
}

```


# Quality estimation
[Comments on the quality of the new harmonised variable.]


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  n_cigarettes <- l.hds[[index]]
  save(n_cigarettes, file = paste0(datafolder,names(l.hds)[index],"/n_cigarettes.RData"))
}

```
<!-- ########################################################## --> 
<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
