---
title: "Alcohol drinking"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/alcoholDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/alcoholDS.R')
```



# Data process




## South Africa


### Wave 1


#### Study-specific variable description

| **Name** | `q3010` |`q3007`|
|-|-|-|
| **Label** | `q3010: drinking pattern`|`q3007: ever used alcohol?`|
| **Table name**  | `southAfricaINDdata`| `southAfricaINDdata`|
| **Categories** | `0 = no days`<br/>`1 = < 1 per month`<br/>`2 = 1-3 days per month`<br/>`3 = 1-4 days per week`<br/>`4 = 5+ days per week` |`1 = yes`<br/>`2 = no`|
| **Missings** | `9 = not applicable`<br/>`8 = don't know`<br/>`NA` |`9 = not applicable`<br/>`8 = don't know`<br/>`NA` |
| **Description** |  |  |

```{r assign SA_w1, echo=F}

opal.assign.table.tibble(o, 'SAGE_SA_w1','SAGE.southAfricaINDdata',variables=list('q3010','q3007'), missings = T)
SAGE_SA_w1 <- opal.execute(o,'SAGE_SA_w1')

```

```{r local SA_w1, echo=F}

vbl <- SAGE_SA_w1$q3010
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = 'q3010')
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(SAGE_SA_w1, aes(x=factor(q3010))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_SA_w1$q3007
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = 'q3007')
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(SAGE_SA_w1, aes(x=factor(q3007))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable `q3010` it has to be recoded as follows:

* `0 into 0`
* `1 to 4 into 1`
* `8 into 998`
* `9 into 996`
* `q3007 == 2 into 0`
* `NA into 999`

To compute `freq_oh` from the study-specific variable `q3010` it has to be recoded as follows:

* `0 into 0`
* `1,2 into 1`
* `3,4 into 2`
* `8 into 998`
* `9 into 996`
* `q3007 == 2 into 0`
* `NA into 999`

To compute `past_oh` from the study-specific variable it has to be recoded as follows:

* `q3007 == 1 and q3010 != 1,2,3,4 into 1`
* `q3007 == 2 into 0`
* `q3007 == 1 and q3010 == 1,2,3,4 into 996`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo SA_w1}

# Categorical variable harmonization
SAGE_ds_SA_w1 <- tibble(id=SAGE_SA_w1$id)
SAGE_ds_SA_w1$current_oh <- car::recode(SAGE_SA_w1$q3010,"c(2,3,4)=1;8=998;9=996;NA=999")
SAGE_ds_SA_w1$current_oh[which(SAGE_SA_w1$q3007==2)] <- 0
SAGE_ds_SA_w1$freq_oh <- car::recode(SAGE_SA_w1$q3010,"c(3,4)=2; 2=1; 8=998;9=996;NA=999")
SAGE_ds_SA_w1$freq_oh[which(SAGE_SA_w1$q3007==2)] <- 0
SAGE_ds_SA_w1$past_oh <- car::recode(SAGE_SA_w1$q3007,"2=0;8=998;9=996;NA=999")
SAGE_ds_SA_w1$past_oh[which(SAGE_SA_w1$q3007==1 & SAGE_SA_w1$q3010 %in% c(1,2,3,4))] <- 996

```


#### Statistics of the new harmonized variable

```{r descript SA_w1, echo=F}

vbl <- SAGE_ds_SA_w1$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_SA_w1, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- SAGE_ds_SA_w1$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_SA_w1, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

vbl <- SAGE_ds_SA_w1$past_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_past)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_SA_w1, aes(x=factor(past_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_past) + ylab("Frequency")

```


#### Validation

```{r crosstabulation SA_w1, echo=F}

```




## Ghana


### Wave 1


#### Study-specific variable description

| **Name** | `q3010` |`q3007`|
|-|-|-|
| **Label** | `q3010: drinking pattern`|`q3007: ever used alcohol?`|
| **Table name**  | `ghanaINDData`| `ghanaINDData`|
| **Categories** | `0 = no days`<br/>`1 = < 1 per month`<br/>`2 = 1-3 days per month`<br/>`3 = 1-4 days per week`<br/>`4 = 5+ days per week` |`1 = yes`<br/>`2 = no`|
| **Missings** | `9 = not applicable`<br/>`8 = don't know`<br/>`NA` |`9 = not applicable`<br/>`8 = don't know`<br/>`NA` |
| **Description** |  |  |

```{r assign ghana_w1, echo=F}

opal.assign.table.tibble(o, 'SAGE_ghana_w1','SAGE.ghanaINDData',variables=list('q3010','q3007'), missings = T)
SAGE_ghana_w1 <- opal.execute(o,'SAGE_ghana_w1')

```

```{r local ghana_w1, echo=F}

vbl <- SAGE_ghana_w1$q3010
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = 'q3010')
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(SAGE_ghana_w1, aes(x=factor(q3010))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_ghana_w1$q3007
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = 'q3007')
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(SAGE_ghana_w1, aes(x=factor(q3007))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable `q3010` it has to be recoded as follows:

* `0 into 0`
* `1 to 4 into 1`
* `8 into 998`
* `9 into 996`
* `q3007 == 2 into 0`
* `NA into 999`

To compute `freq_oh` from the study-specific variable `q3010` it has to be recoded as follows:

* `0 into 0`
* `1,2 into 1`
* `3,4 into 2`
* `8 into 998`
* `9 into 996`
* `q3007 == 2 into 0`
* `NA into 999`

To compute `past_oh` from the study-specific variable it has to be recoded as follows:

* `q3007 == 1 and q3010 != 1,2,3,4 into 1`
* `q3007 == 2 into 0`
* `q3007 == 1 and q3010 == 1,2,3,4 into 996`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo ghana_w1}

# Categorical variable harmonization
SAGE_ds_ghana_w1 <- tibble(id=SAGE_ghana_w1$id)
SAGE_ds_ghana_w1$current_oh <- car::recode(SAGE_ghana_w1$q3010,"c(2,3,4)=1;8=998;9=996;NA=999")
SAGE_ds_ghana_w1$current_oh[which(SAGE_ghana_w1$q3007==2)] <- 0
SAGE_ds_ghana_w1$freq_oh <- car::recode(SAGE_ghana_w1$q3010,"c(3,4)=2; 2=1; 8=998;9=996;NA=999")
SAGE_ds_ghana_w1$freq_oh[which(SAGE_ghana_w1$q3007==2)] <- 0
SAGE_ds_ghana_w1$past_oh <- car::recode(SAGE_ghana_w1$q3007,"2=0;8=998;9=996;NA=999")
SAGE_ds_ghana_w1$past_oh[which(SAGE_ghana_w1$q3007==1 & SAGE_ghana_w1$q3010 %in% c(1,2,3,4))] <- 996

```


#### Statistics of the new harmonized variable

```{r descript ghana_w1, echo=F}

vbl <- SAGE_ds_ghana_w1$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_ghana_w1, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- SAGE_ds_ghana_w1$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_ghana_w1, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

vbl <- SAGE_ds_ghana_w1$past_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_past)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_ghana_w1, aes(x=factor(past_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_past) + ylab("Frequency")

```


#### Validation

```{r crosstabulation ghana_w1, echo=F}

```





## China


### Wave 1


#### Study-specific variable description

| **Name** | `q3010` |`q3007`|
|-|-|-|
| **Label** | `q3010: drinking pattern`|`q3007: ever used alcohol?`|
| **Table name**  | `chinaINDData`| `chinaINDData`|
| **Categories** | `0 = no days`<br/>`1 = < 1 per month`<br/>`2 = 1-3 days per month`<br/>`3 = 1-4 days per week`<br/>`4 = 5+ days per week` |`1 = yes`<br/>`2 = no`|
| **Missings** | `9 = not applicable`<br/>`8 = don't know`<br/>`NA` |`9 = not applicable`<br/>`8 = don't know`<br/>`NA` |
| **Description** |  |  |

```{r assign china_w1, echo=F}

opal.assign.table.tibble(o, 'SAGE_china_w1','SAGE.chinaINDData',variables=list('q3010','q3007'), missings = T)
SAGE_china_w1 <- opal.execute(o,'SAGE_china_w1')

```

```{r local china_w1, echo=F}

vbl <- SAGE_china_w1$q3010
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'q3010')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(SAGE_china_w1, aes(x=factor(q3010))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_china_w1$q3007
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = 'q3007')
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(SAGE_china_w1, aes(x=factor(q3007))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable `q3010` it has to be recoded as follows:

* `0 into 0`
* `1 to 4 into 1`
* `8 into 998`
* `9 into 996`
* `q3007 == 2 into 0`
* `NA into 999`

To compute `freq_oh` from the study-specific variable `q3010` it has to be recoded as follows:

* `0 into 0`
* `1,2 into 1`
* `3,4 into 2`
* `8 into 998`
* `9 into 996`
* `q3007 == 2 into 0`
* `NA into 999`

To compute `past_oh` from the study-specific variable it has to be recoded as follows:

* `q3007 == 1 and q3010 != 1,2,3,4 into 1`
* `q3007 == 2 into 0`
* `q3007 == 1 and q3010 == 1,2,3,4 into 996`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo china_w1}

# Categorical variable harmonization
SAGE_ds_china_w1 <- tibble(id=SAGE_china_w1$id)
SAGE_ds_china_w1$current_oh <- car::recode(SAGE_china_w1$q3010,"c(2,3,4)=1;8=998;9=996;NA=999")
SAGE_ds_china_w1$current_oh[which(SAGE_china_w1$q3007==2)] <- 0
SAGE_ds_china_w1$freq_oh <- car::recode(SAGE_china_w1$q3010,"c(3,4)=2; 2=1; 8=998;9=996;NA=999")
SAGE_ds_china_w1$freq_oh[which(SAGE_china_w1$q3007==2)] <- 0
SAGE_ds_china_w1$past_oh <- car::recode(SAGE_china_w1$q3007,"2=0;8=998;9=996;NA=999")
SAGE_ds_china_w1$past_oh[which(SAGE_china_w1$q3007==1 & SAGE_china_w1$q3010 %in% c(1,2,3,4))] <- 996

```


#### Statistics of the new harmonized variable

```{r descript china_w1, echo=F}

vbl <- SAGE_ds_china_w1$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_china_w1, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- SAGE_ds_china_w1$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_china_w1, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

vbl <- SAGE_ds_china_w1$past_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_past)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_china_w1, aes(x=factor(past_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_past) + ylab("Frequency")

```


#### Validation

```{r crosstabulation china_w1, echo=F}

```




## India


### Wave 1


#### Study-specific variable description

| **Name** | `q3010` |`q3007`|
|-|-|-|
| **Label** | `q3010: drinking pattern`|`q3007: ever used alcohol?`|
| **Table name**  | `indiaINDData`| `indiaINDData`|
| **Categories** | `0 = no days`<br/>`1 = < 1 per month`<br/>`2 = 1-3 days per month`<br/>`3 = 1-4 days per week`<br/>`4 = 5+ days per week` |`1 = yes`<br/>`2 = no`|
| **Missings** | `9 = not applicable`<br/>`8 = don't know`<br/>`NA` |`9 = not applicable`<br/>`8 = don't know`<br/>`NA` |
| **Description** |  |  |

```{r assign india_w1, echo=F}

opal.assign.table.tibble(o, 'SAGE_india_w1','SAGE.indiaINDData',variables=list('q3010','q3007'), missings = T)
SAGE_india_w1 <- opal.execute(o,'SAGE_india_w1')

```

```{r local india_w1, echo=F}

vbl <- SAGE_india_w1$q3010
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'q3010')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(SAGE_india_w1, aes(x=factor(q3010))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_india_w1$q3007
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = 'q3007')
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(SAGE_india_w1, aes(x=factor(q3007))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable `q3010` it has to be recoded as follows:

* `0 into 0`
* `1 to 4 into 1`
* `8 into 998`
* `9 into 996`
* `q3007 == 2 into 0`
* `NA into 999`

To compute `freq_oh` from the study-specific variable `q3010` it has to be recoded as follows:

* `0 into 0`
* `1,2 into 1`
* `3,4 into 2`
* `8 into 998`
* `9 into 996`
* `q3007 == 2 into 0`
* `NA into 999`

To compute `past_oh` from the study-specific variable it has to be recoded as follows:

* `q3007 == 1 and q3010 != 1,2,3,4 into 1`
* `q3007 == 2 into 0`
* `q3007 == 1 and q3010 == 1,2,3,4 into 996`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo india_w1}

# Categorical variable harmonization
SAGE_ds_india_w1 <- tibble(id=SAGE_india_w1$id)
SAGE_ds_india_w1$current_oh <- car::recode(SAGE_india_w1$q3010,"c(2,3,4)=1;8=998;9=996;NA=999")
SAGE_ds_india_w1$current_oh[which(SAGE_india_w1$q3007==2)] <- 0
SAGE_ds_india_w1$freq_oh <- car::recode(SAGE_india_w1$q3010,"c(3,4)=2; 2=1; 8=998;9=996;NA=999")
SAGE_ds_india_w1$freq_oh[which(SAGE_india_w1$q3007==2)] <- 0
SAGE_ds_india_w1$past_oh <- car::recode(SAGE_india_w1$q3007,"2=0;8=998;9=996;NA=999")
SAGE_ds_india_w1$past_oh[which(SAGE_india_w1$q3007==1 & SAGE_india_w1$q3010 %in% c(1,2,3,4))] <- 996

```


#### Statistics of the new harmonized variable

```{r descript india_w1, echo=F}

vbl <- SAGE_ds_india_w1$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_india_w1, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- SAGE_ds_india_w1$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_india_w1, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

vbl <- SAGE_ds_india_w1$past_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_past)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_india_w1, aes(x=factor(past_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_past) + ylab("Frequency")

```


#### Validation

```{r crosstabulation india_w1, echo=F}

```





## Russian Federation


### Wave 1


#### Study-specific variable description

| **Name** | `q3010` |`q3007`|
|-|-|-|
| **Label** | `q3010: drinking pattern`|`q3007: ever used alcohol?`|
| **Table name**  | `russiaINDdata`| `russiaINDdata`|
| **Categories** | `0 = no days`<br/>`1 = < 1 per month`<br/>`2 = 1-3 days per month`<br/>`3 = 1-4 days per week`<br/>`4 = 5+ days per week` |`1 = yes`<br/>`2 = no`|
| **Missings** | `9 = not applicable`<br/>`8 = don't know`<br/>`NA` |`9 = not applicable`<br/>`8 = don't know`<br/>`NA` |
| **Description** |  |  |

```{r assign russia_w1, echo=F}

opal.assign.table.tibble(o, 'SAGE_russia_w1','SAGE.russiaINDdata',variables=list('q3010','q3007'), missings = T)
SAGE_russia_w1 <- opal.execute(o,'SAGE_russia_w1')

```

```{r local russia_w1, echo=F}

vbl <- SAGE_russia_w1$q3010
kable(Categorical_summary(vbl, missing_values = c(9))[3], caption = 'q3010')
kable(Categorical_summary(vbl, missing_values = c(9))[1], caption = "Category")
ggplot(SAGE_russia_w1, aes(x=factor(q3010))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_russia_w1$q3007
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = 'q3007')
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(SAGE_russia_w1, aes(x=factor(q3007))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable `q3010` it has to be recoded as follows:

* `0 into 0`
* `1 to 4 into 1`
* `8 into 998`
* `9 into 996`
* `q3007 == 2 into 0`
* `NA into 999`

To compute `freq_oh` from the study-specific variable `q3010` it has to be recoded as follows:

* `0 into 0`
* `1,2 into 1`
* `3,4 into 2`
* `8 into 998`
* `9 into 996`
* `q3007 == 2 into 0`
* `NA into 999`

To compute `past_oh` from the study-specific variable it has to be recoded as follows:

* `q3007 == 1 and q3010 != 1,2,3,4 into 1`
* `q3007 == 2 into 0`
* `q3007 == 1 and q3010 == 1,2,3,4 into 996`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo russia_w1}

# Categorical variable harmonization
SAGE_ds_russia_w1 <- tibble(id=SAGE_russia_w1$id)
SAGE_ds_russia_w1$current_oh <- car::recode(SAGE_russia_w1$q3010,"c(2,3,4)=1;8=998;9=996;NA=999")
SAGE_ds_russia_w1$current_oh[which(SAGE_russia_w1$q3007==2)] <- 0
SAGE_ds_russia_w1$freq_oh <- car::recode(SAGE_russia_w1$q3010,"c(3,4)=2; 2=1; 8=998;9=996;NA=999")
SAGE_ds_russia_w1$freq_oh[which(SAGE_russia_w1$q3007==2)] <- 0
SAGE_ds_russia_w1$past_oh <- car::recode(SAGE_russia_w1$q3007,"2=0;8=998;9=996;NA=999")
SAGE_ds_russia_w1$past_oh[which(SAGE_russia_w1$q3007==1 & SAGE_russia_w1$q3010 %in% c(1,2,3,4))] <- 996

```


#### Statistics of the new harmonized variable

```{r descript russia_w1, echo=F}

vbl <- SAGE_ds_russia_w1$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_russia_w1, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- SAGE_ds_russia_w1$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_russia_w1, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

vbl <- SAGE_ds_russia_w1$past_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_past)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_russia_w1, aes(x=factor(past_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_past) + ylab("Frequency")

```


#### Validation

```{r crosstabulation russia_w1, echo=F}

```




## Mexico


### Wave 1


#### Study-specific variable description

| **Name** | `q3010` |`q3007`|
|-|-|-|
| **Label** | `q3010: drinking pattern`|`q3007: ever used alcohol?`|
| **Table name**  | `mexicoINDdata`| `mexicoINDdata`|
| **Categories** | `0 = no days`<br/>`1 = < 1 per month`<br/>`2 = 1-3 days per month`<br/>`3 = 1-4 days per week`<br/>`4 = 5+ days per week` |`1 = yes`<br/>`2 = no`|
| **Missings** | `9 = not applicable`<br/>`8 = don't know`<br/>`NA` |`9 = not applicable`<br/>`8 = don't know`<br/>`NA` |
| **Description** |  |  |


```{r assign mexico_w1, echo=F}

opal.assign.table.tibble(o, 'SAGE_mexico_w1','SAGE.mexicoINDdata',variables=list('q3010','q3007'), missings = T)
SAGE_mexico_w1 <- opal.execute(o,'SAGE_mexico_w1')

```

```{r local mexico_w1, echo=F}

vbl <- SAGE_mexico_w1$q3010
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'q3010')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(SAGE_mexico_w1, aes(x=factor(q3010))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_mexico_w1$q3007
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = 'q3007')
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(SAGE_mexico_w1, aes(x=factor(q3007))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable `q3010` it has to be recoded as follows:

* `0 into 0`
* `1 to 4 into 1`
* `8 into 998`
* `9 into 996`
* `q3007 == 2 into 0`
* `NA into 999`

To compute `freq_oh` from the study-specific variable `q3010` it has to be recoded as follows:

* `0 into 0`
* `1,2 into 1`
* `3,4 into 2`
* `8 into 998`
* `9 into 996`
* `q3007 == 2 into 0`
* `NA into 999`

To compute `past_oh` from the study-specific variable it has to be recoded as follows:

* `q3007 == 1 and q3010 != 1,2,3,4 into 1`
* `q3007 == 2 into 0`
* `q3007 == 1 and q3010 == 1,2,3,4 into 996`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo mexico_w1}

# Categorical variable harmonization
SAGE_ds_mexico_w1 <- tibble(id=SAGE_mexico_w1$id)
SAGE_ds_mexico_w1$current_oh <- car::recode(SAGE_mexico_w1$q3010,"c(2,3,4)=1;8=998;9=996;NA=999")
SAGE_ds_mexico_w1$current_oh[which(SAGE_mexico_w1$q3007==2)] <- 0
SAGE_ds_mexico_w1$freq_oh <- car::recode(SAGE_mexico_w1$q3010,"c(3,4)=2; 2=1; 8=998;9=996;NA=999")
SAGE_ds_mexico_w1$freq_oh[which(SAGE_mexico_w1$q3007==2)] <- 0
SAGE_ds_mexico_w1$past_oh <- car::recode(SAGE_mexico_w1$q3007,"2=0;8=998;9=996;NA=999")
SAGE_ds_mexico_w1$past_oh[which(SAGE_mexico_w1$q3007==1 & SAGE_mexico_w1$q3010 %in% c(1,2,3,4))] <- 996

```


#### Statistics of the new harmonized variable

```{r descript mexico_w1, echo=F}

vbl <- SAGE_ds_mexico_w1$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_mexico_w1, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- SAGE_ds_mexico_w1$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_mexico_w1, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

vbl <- SAGE_ds_mexico_w1$past_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_past)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_mexico_w1, aes(x=factor(past_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_past) + ylab("Frequency")

```


#### Validation

```{r crosstabulation mexico_w1, echo=F}

```





## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable:


**R script:**

```{r summ}

l.hds <- list(SA_w1 = SAGE_ds_SA_w1 , ghana_w1 = SAGE_ds_ghana_w1, china_w1 = SAGE_ds_china_w1, india_w1=SAGE_ds_india_w1, russia_w1=SAGE_ds_russia_w1, mexico_w1=SAGE_ds_mexico_w1)

for(name in names(l.hds)) {
  m_name <- paste0("SAGE_m_ds_",name)
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label_curr # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  label(l.hds[[name]][[3]]) <- label(aux_object[[3]]) <- ds_label_freq # Text value assigned at the DS description, at the top
  l.hds[[name]][[3]] <- labelled(l.hds[[name]][[3]], labels = freq_label)
  aux_object[[3]] <- car::recode(aux_object[[3]], "miss_values_vector=NA")
  aux_object[[3]] <- labelled(aux_object[[3]], labels = freq_label[1:3])
  label(l.hds[[name]][[4]]) <- label(aux_object[[4]]) <- ds_label_past # Text value assigned at the DS description, at the top
  l.hds[[name]][[4]] <- labelled(l.hds[[name]][[4]], labels = cat_label)
  aux_object[[4]] <- car::recode(aux_object[[4]], "miss_values_vector=NA")
  aux_object[[4]] <- labelled(aux_object[[4]], labels = cat_label[1:2])
  assign(m_name, aux_object)
  rm(aux_object)
}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]])) )
names(t.hds)<-c("val", "label", "South_Africa_w1", "Ghana_W1", "China_W1", "India_W1", "Russia_W1", "Mexico_W1")
kable(t.hds, caption = 'current_oh')

t.hds <- frq(l.hds[[1]][3])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][3])[[1]][,4] 
}
t.hds[14,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]])) )
names(t.hds)<-c("val", "label", "South_Africa_w1", "Ghana_W1", "China_W1", "India_W1", "Russia_W1", "Mexico_W1")
kable(t.hds, caption = 'freq_oh')

t.hds <- frq(l.hds[[1]][4])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][4])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]])) )
names(t.hds)<-c("val", "label", "South_Africa_w1", "Ghana_W1", "China_W1", "India_W1", "Russia_W1", "Mexico_W1")
kable(t.hds, caption = 'past_oh')

```



# Quality estimation

If an individual is current drinker, it is codified as not applicable since we do not know its past-drinking condition.


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(l.hds)){
  alcohol <- l.hds[[index]]
  save(alcohol, file = paste0(datafolder,names(l.hds)[index],"/alcohol.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





