---
title: "Month of interview"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```


# Description of DataSchema variable

The description of harmonised variable is the following:




* Short name: `mintw`
* Variable label: `month of interview`
* Variable description: `month of interview`
* Domain: `Other administrative variables`
* Value type:`continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done 
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


# Data process

## Finland
### Health2000-2011 - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `KOKO_VPVM`
* Label: `koko tutkimuksen viitep?iv?`
* Type of variable: `countinous`

```{r assign1}
opal.assign.table.tibble(o, 'Health20002011_w1_dbirth','Health2000-2011.Date_of_interview_wave1',
                         variables=list('dinterview'), missings = TRUE)
```

```{r local1}
Health20002011_w1_dbirth <- opal.execute(o,'Health20002011_w1_dbirth')
Health20002011_w1_dbirth$minter <- as.numeric(format(Health20002011_w1_dbirth$dinterview, '%m'))
Categorical_summary(var = Health20002011_w1_dbirth$minter, missing_values = NA)
ggplot(Health20002011_w1_dbirth, aes(x=factor(minter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo1}
Health20002011_ds_w1 <- tibble(id=Health20002011_w1_dbirth$id)
Health20002011_ds_w1$mintw <- car::recode(Health20002011_w1_dbirth$minter, "NA=999")
Health20002011_ds_w1$mintw <- labelled(Health20002011_ds_w1$mintw, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1}
Categorical_summary(var = Health20002011_ds_w1$mintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(Health20002011_ds_w1, aes(x=factor(mintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1}
BeforeH <- table(Health20002011_w1_dbirth$minter, useNA = "ifany")
AfterH <- table(Health20002011_ds_w1$mintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```


#### Import to OPAL
```{r importOPAL1}
val_labels(Health20002011_ds_w1) <- NULL
#opal.assign.data(o, 'Health20002011_ds_w1', Health20002011_ds_w1)
#opal.symbol_import(o,'Health20002011_ds_w1', project='_Athlos_Harm_Dataset')
mintw <- Health20002011_ds_w1
save(mintw, file = "../RData/w1/mintw.RData")
rm(mintw)

Health20002011_m_ds_w1 <- Health20002011_ds_w1
Health20002011_m_ds_w1$mintw <- car::recode(Health20002011_m_ds_w1$mintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'Health20002011_m_ds_w1', Health20002011_m_ds_w1)
#opal.symbol_import(o,'Health20002011_m_ds_w1', project='_Athlos_Harm_Dataset')
```








### Health2000-2011 - Wave 2 

#### Study-specific variables

The study-specific variable elected to be harmonised is:
* Name: `KOKO_VPVM`
* Label: `Participation date`
* Type of variable: `countinous`

```{r assign2}
opal.assign.table.tibble(o, 'Health20002011_w2_dinter','Health2000-2011.Date_of_interview_wave2',
                         variables=list('dinterview'), missings = TRUE)
```


```{r local2}
Health20002011_w2_dinter <- opal.execute(o,'Health20002011_w2_dinter')
Health20002011_w2_dinter$minter <- as.numeric(format(Health20002011_w2_dinter$ dinterview, '%m'))
Categorical_summary(var = Health20002011_w2_dinter$minter, missing_values = NA)
ggplot(Health20002011_w2_dinter, aes(x=factor(minter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo2}
Health20002011_ds_w2 <- tibble(id=Health20002011_w2_dinter$id)
Health20002011_ds_w2$mintw <- car::recode(Health20002011_w2_dinter$minter, "NA=999")
Health20002011_ds_w2$mintw <- labelled(Health20002011_ds_w2$mintw, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2}
Categorical_summary(var = Health20002011_ds_w2$mintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(Health20002011_ds_w2, aes(x=factor(mintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2}
BeforeH <- table(Health20002011_w2_dinter$minter, useNA = "ifany")
AfterH <- table(Health20002011_ds_w2$mintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```

#### Quality estimation
No comments.


#### Import to OPAL
```{r importOPAL2}
val_labels(Health20002011_ds_w2) <- NULL
#opal.assign.data(o, 'Health20002011_ds_w2', Health20002011_ds_w2)
#opal.symbol_import(o,'Health20002011_ds_w2', project='_Athlos_Harm_Dataset')
mintw <- Health20002011_ds_w2
save(mintw, file = "../RData/w2/mintw.RData")
rm(mintw)

Health20002011_m_ds_w2 <- Health20002011_ds_w2
Health20002011_m_ds_w2$mintw <- car::recode(Health20002011_m_ds_w2$mintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'Health20002011_m_ds_w2', Health20002011_m_ds_w2)
#opal.symbol_import(o,'Health20002011_m_ds_w2', project='_Athlos_Harm_Dataset')
```

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
