---
title: "Sample weights"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/weightsDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/weightsDS.R')
```


# Data process

## Finland

### Wave 1 

#### Study-specific variable description


| **Name** | `PAINOT_UNIONI`|
|-|-|
| **Label** | `ANALYSIS WEIGHT`|
| **Table name** | `t00_athlos_2017_02_23` |
| **Description** |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'HEALTH2000_w1','Health2000-2011.t00_athlos_2017_02_23', variables=list('PAINOT_UNIONI'), missings = TRUE)
HEALTH2000_w1 <- opal.execute(o,'HEALTH2000_w1')

```


```{r local w1, echo=F}

vbl <- HEALTH2000_w1$PAINOT_UNIONI
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = attr(vbl, "spss::shortName"))
pander(Continuous_summary(var = vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HEALTH2000_w1, aes(vbl)) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

**R script:**

```{r harmo w1}

Health20002011_ds_w1   <- tibble(id=HEALTH2000_w1$id)
Health20002011_ds_w1$w <- car::recode(HEALTH2000_w1$PAINOT_UNIONI, "NA=999")

```


#### Statistical description of the new harmonised variable

```{r descript w1, echo=F}

vbl <- Health20002011_ds_w1$w
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(Health20002011_ds_w1 %>% filter(!vbl %in% miss_values_vector), aes(x=w)) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w1, echo=F}

```



### Wave 2

#### Study-specific variable description


| **Name** | `ALL_ANALYSIS_W`|
|-|-|
| **Label** | `H2011 all: analysis weight`|
| **Table name** | `t11_athlos_2017_02_27` |
| **Description** |  |

```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'HEALTH2000_w2','Health2000-2011.t11_athlos_2017_02_27', variables=list('ALL_ANALYSIS_W'), missings = TRUE)
HEALTH2000_w2 <- opal.execute(o,'HEALTH2000_w2')

```


```{r local w2, echo=F}

vbl <- HEALTH2000_w2$ALL_ANALYSIS_W
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = attr(vbl, "spss::shortName"))
pander(Continuous_summary(var = vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HEALTH2000_w2, aes(vbl)) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

**R script:**

```{r harmo w2}

Health20002011_ds_w2   <- tibble(id=HEALTH2000_w2$id)
Health20002011_ds_w2$w <- car::recode(HEALTH2000_w2$ALL_ANALYSIS_W, "NA=999")

```


#### Statistical description of the new harmonised variable

```{r descript w2, echo=F}

vbl <- Health20002011_ds_w2$w
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(Health20002011_ds_w2 %>% filter(!vbl %in% miss_values_vector), aes(x=w)) + geom_bar(stat="count", width=0.01, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w2, echo=F}

```




## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

source("../../helpfunctions.r")
rm(labelling)
labelling <- labelling_c
rm(summaries)
summaries <- summaries_c


```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


health2000.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"))

# Consider only harmonised waves
l.hds <- lapply(health2000.cw, function(wname) if(exists(paste0("Health20002011_ds_",wname[1]))){wname = list(get(paste0("Health20002011_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```







# Quality estimation


```{r closeRsession, echo=FALSE}
opal.logout(o)
```


