---
title: "Respondent"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/respondentDS.Rmd'}
```

```{r global, echo=F}
source('../../_DS_Rmd/respondentDS.R')
```

<!-- ########################################################## --> 

# Data process

## Finland

### Wave 1 

#### Study-specific variable description


```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'Health20002011_w1','Health2000-2011.t00_athlos_2017_02_23',
                         variables=list('SP2'), missings = TRUE)
Health20002011_w1 <- opal.execute(o,'Health20002011_w1')
```


#### Harmonisation algorithm
All the interviewed individuals are considered as participants. 

**R script:**

```{r harmo1, echo=TRUE}
Health20002011_ds_w1 <- tibble(id=Health20002011_w1$id)
Health20002011_ds_w1$respondent <- 0
Health20002011_ds_w1$respondent <- labelled(Health20002011_ds_w1$respondent, labels = cat_label)
label(Health20002011_ds_w1$respondent) <- ds_label
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- Health20002011_ds_w1$respondent
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(Health20002011_ds_w1, aes(x=factor(respondent))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL1, echo=FALSE}
#opal.assign.data(o, 'Health20002011_ds_w1', Health20002011_ds_w1)
#opal.symbol_import(o,'Health20002011_ds_w1', project='_Athlos_Harm_Dataset')

respondent <- Health20002011_ds_w1
save(respondent, file = "../RData/w1/respondent.RData")
rm(respondent)
```







### Wave 2 

#### Study-specific variable description

```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'Health20002011_w2','Health2000-2011.t11_athlos_2017_02_27',
                         variables=list('SP2'), missings = TRUE)
Health20002011_w2 <- opal.execute(o,'Health20002011_w2')
```

#### Harmonisation algorithm
All the interviewed individuals are considered as participants. 

**R script:**

```{r harmo2, echo=TRUE}
Health20002011_ds_w2 <- tibble(id=Health20002011_w2$id)
Health20002011_ds_w2$respondent <- 0
Health20002011_ds_w2$respondent <- labelled(Health20002011_ds_w2$respondent, labels = cat_label)
label(Health20002011_ds_w2$respondent) <- ds_label
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- Health20002011_ds_w2$respondent
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(Health20002011_ds_w2, aes(x=factor(respondent))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL2, echo=FALSE}
#opal.assign.data(o, 'Health20002011_ds_w2', Health20002011_ds_w2)
#opal.symbol_import(o,'Health20002011_ds_w2', project='_Athlos_Harm_Dataset')
respondent <- Health20002011_ds_w2
save(respondent, file = "../RData/w2/respondent.RData")
rm(respondent)
```

# Quality estimation

No comments.



```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
