---
title: "Weight"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/weightDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/weightDS.R')
```

# Data process

## Finland

### Wave 1 

#### Study-specific variable description



| **Name** |`q2507_weight`|
|-|-|
| **Label** |`weight`|
| **Table name** |`Courage_Finland_w1`|
| **Units** |`kg`|
| **Missings** |`997 = Disable to measure`<br/>`998 = Refusal`|
| **Description** |  |

```{r assign_fin, echo=F}
opal.assign.table.tibble(o, 'COURAGE_fin_w1','Courage.Courage_Finland_w1',variables=list('q2507_weight'), missings = TRUE)
COURAGE_fin_w1 <- opal.execute(o,'COURAGE_fin_w1')
```

```{r local_fin, echo=F}
vbl <- COURAGE_fin_w1$q2507_weight
vbl_miss <- c(997,998)
kable(Continuous_summary(vbl, missing_values = vbl_miss)[3], caption = "q2507_weight")
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(COURAGE_fin_w1, aes(q2507_weight)) + geom_histogram(stat="count", fill="steelblue",data = .%>% filter(!vbl %in% vbl_miss)) + xlab("Weight") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`
* `997 into 993`
* `998 into 997`
* `q2507_weight<30 into 999`

**R script:**

```{r harmo_fin}
COURAGE_ds_fin_w1 <- tibble(id=COURAGE_fin_w1$id)
COURAGE_ds_fin_w1$weight <- car::recode(COURAGE_fin_w1$q2507_weight, "NA=999; 997=993; 998=997; 0:30=999")
COURAGE_ds_fin_w1$weight <- labelled(COURAGE_ds_fin_w1$weight, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_fin, echo=F}
vbl <- COURAGE_ds_fin_w1$weight
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(COURAGE_ds_fin_w1, aes(weight)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab("weight") + ylab("Frequency") 
```

#### Validation

There are unusual values lower than 30
```{r crosstabulation_fin, echo=F}

kable(COURAGE_fin_w1[which(COURAGE_fin_w1$q2507_weight<30),])
```






## Poland

### Wave 1 

#### Study-specific variable description



| **Name** |`q2507_weight`|
|-|-|
| **Label** |`weight`|
| **Table name** |`Courage_Poland_w1`|
| **Units** |`kg`|
| **Missings** |`997 = Disable to measure`<br/>`998 = Refusal`|
| **Description** |  |



```{r assign_pol1, echo=F}
opal.assign.table.tibble(o, 'COURAGE_pol_w1','Courage.Courage_Poland_w1', variables=list('q2507_weight'), missings = TRUE)
COURAGE_pol_w1 <- opal.execute(o,'COURAGE_pol_w1')
```

```{r local_pol1, echo=F}
vbl <- COURAGE_pol_w1$q2507_weight
vbl_miss <- c(997,998)
kable(Continuous_summary(vbl, missing_values = vbl_miss)[3], caption = "q2507_weight")
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(COURAGE_pol_w1, aes(q2507_weight)) + geom_histogram(stat="count", fill="steelblue",data = .%>% filter(!vbl %in% vbl_miss)) + xlab("weight") + ylab("Frequency")+xlim(29,200)

```


#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`
* `997 into 993`
* `998 into 997`
* `q2507_weight<30 into 999`
* `q2507_weight` between 400 and 1200 is considered to be measured in [hectograms](https://www.bipm.org/en/measurement-units/) instead of kilograms
* `q2507_weight == 8740` is considered to be measured in [decagrams](https://www.bipm.org/en/measurement-units/) instead of kilograms


**R script:**

```{r harmo_pol1}
COURAGE_ds_pol_w1 <- tibble(id=COURAGE_pol_w1$id)

COURAGE_pol_w1$q2507_weight[which(COURAGE_pol_w1$q2507_weight>400 & !COURAGE_pol_w1$q2507_weight %in% c(997,998))] <- COURAGE_pol_w1$q2507_weight[which(COURAGE_pol_w1$q2507_weight>400 & !COURAGE_pol_w1$q2507_weight %in% c(997,998))]*0.1

COURAGE_pol_w1$q2507_weight[which(COURAGE_pol_w1$q2507_weight==874)] <- COURAGE_pol_w1$q2507_weight[which(COURAGE_pol_w1$q2507_weight==874)]*0.1

COURAGE_ds_pol_w1$weight <- car::recode(as.numeric(COURAGE_pol_w1$q2507_weight), " lo:30=999; NA=999; 997=993; 998=997")

```

#### Statistics of the new harmonised variable
```{r descript_pol1, echo=F}

vbl <- COURAGE_ds_pol_w1$weight
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(COURAGE_ds_pol_w1, aes(weight)) + geom_histogram(stat="bin", fill="steelblue", binwidth=0.4, data = .%>% filter(!vbl %in% miss_values_vector)) + xlab("weight") + ylab("Frequency") 

```

#### Validation
There are some unusual values that are lower than 30 and higher than 250 kg
```{r crosstabulation_pol1, echo=F}
kable(COURAGE_pol_w1[which(COURAGE_pol_w1$q2507_weight<30 | (COURAGE_pol_w1$q2507_weight>250 & !COURAGE_pol_w1$q2507_weight %in% c(997,998))),])
```



### Wave 2 

#### Study-specific variable description



| **Name** |`q2507_weight_s1`|
|-|-|
| **Label** |`weight`|
| **Table name** |`Courage_Poland_w2`|
| **Units** |`kg`|
| **Missings** |`997 = Disable to measure`<br/>`998 = Refusal`|
| **Description** |  |




```{r assign_pol2, echo=F}
opal.assign.table.tibble(o, 'COURAGE_pol_w2','Courage.Courage_Poland_w2', variables=list('q2507_weight_s1'), missings = TRUE)
COURAGE_pol_w2 <- opal.execute(o,'COURAGE_pol_w2')
```

```{r local_pol2, echo=F}
vbl <- COURAGE_pol_w2$q2507_weight_s1
vbl_miss <- c(997,998)
kable(Continuous_summary(vbl, missing_values = vbl_miss)[3], caption = "q2507_weight_s1")
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(COURAGE_pol_w2, aes(q2507_weight_s1)) + geom_histogram(stat="count", fill="steelblue",data = .%>% filter(!vbl %in% vbl_miss)) + xlab("weight") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`
* `997 into 993`
* `998 into 997`

**R script:**

```{r harmo_pol2}
COURAGE_ds_pol_w2 <- tibble(id=COURAGE_pol_w2$id)
COURAGE_ds_pol_w2$weight <- car::recode(COURAGE_pol_w2$q2507_weight_s1, "NA=999; 997=993; 998=997")
COURAGE_ds_pol_w2$weight <- labelled(COURAGE_ds_pol_w2$weight, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_pol2, echo=F}
vbl <- COURAGE_ds_pol_w2$weight
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(COURAGE_ds_pol_w2, aes(weight)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab("weight") + ylab("Frequency")

```

#### Validation
```{r crosstabulation_pol2, echo=F}

```





## Spain

### Wave 1 

#### Study-specific variable description



| **Name** |`q2507_weight`|
|-|-|
| **Label** |`weight`|
| **Table name** |`Courage_Spain_w1`|
| **Units** |`kg`|
| **Missings** |`997 = Disable to measure`<br/>`998 = Refusal`|
| **Description** |  |


```{r assign_spain1, echo=F}
opal.assign.table.tibble(o, 'COURAGE_spain_w1','Courage.Courage_Spain_w1', variables=list('q2507_weight'), missings = TRUE)
COURAGE_spain_w1 <- opal.execute(o,'COURAGE_spain_w1')
```

```{r local_spain1, echo=F}
vbl <- COURAGE_spain_w1$q2507_weight
vbl_miss <- c(997,998)
kable(Continuous_summary(vbl, missing_values = vbl_miss)[3], caption = "q2507_weight")
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(COURAGE_spain_w1, aes(q2507_weight)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% c(889,vbl_miss))) + xlab("weight") + ylab("Frequency")
```


#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`
* `997 into 993`
* `998 into 997`
There are values 889 that are going to be considered as mistake instead of 998, therefore they will be recoded as 997.


**R script:**

```{r harmo_spain1}
COURAGE_ds_spain_w1 <- tibble(id=COURAGE_spain_w1$id)
COURAGE_ds_spain_w1$weight <- car::recode(COURAGE_spain_w1$q2507_weight, "889=997; NA=999; 997=993; 998=997")
COURAGE_ds_spain_w1$weight <- labelled(COURAGE_ds_spain_w1$weight, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_spain1, echo=F}
vbl <- COURAGE_ds_spain_w1$weight
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(COURAGE_ds_spain_w1, aes(weight)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab("weight") + ylab("Frequency")

```

#### Validation
```{r crosstabulation_spain1, echo=F}
```






### Wave 2 

#### Study-specific variable description



| **Name** |`q2507_weight_s1`|
|-|-|
| **Label** |`weight`|
| **Table name** |`Courage_Spain_w2_1`|
| **Units** |`kg`|
| **Missings** |`997 = Disable to measure`<br/>`998 = Refusal`|
| **Description** |  |

```{r assign_spain2, echo=F}
opal.assign.table.tibble(o, 'COURAGE_spain_w2','Courage.Courage_Spain_w2_1',variables=list('q2507_weight_s1'), missings = TRUE)
COURAGE_spain_w2 <- opal.execute(o,'COURAGE_spain_w2')
```

```{r local_spain2, echo=F}
vbl <- COURAGE_spain_w2$q2507_weight_s1
vbl_miss <- c(997,998)
kable(Continuous_summary(vbl, missing_values = vbl_miss)[3], caption = "q2507_weight_s1")
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(COURAGE_spain_w2, aes(q2507_weight_s1)) + geom_histogram(stat="count", fill="steelblue",data = .%>% filter(!vbl %in% vbl_miss)) + xlab("weight") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`
* `997 into 993`
* `998 into 997`


**R script:**

```{r harmo_spain2}
COURAGE_ds_spain_w2 <- tibble(id=COURAGE_spain_w2$id)
COURAGE_ds_spain_w2$weight <- car::recode(COURAGE_spain_w2$q2507_weight_s1, "NA=999; 997=993; 998=997")
COURAGE_ds_spain_w2$weight <- labelled(COURAGE_ds_spain_w2$weight, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_spain2, echo=F}
vbl <- COURAGE_ds_spain_w2$weight
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(COURAGE_ds_spain_w2, aes(weight)) + geom_histogram(stat="bin", fill="steelblue",binwidth = 0.4,data = .%>% filter(!vbl %in% miss_values_vector)) + xlab("weight") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_spain2, echo=F}
```








## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for continuous data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][2])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[2]],missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][2])[1:6]
    # Next, missing/no-missing values
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[2]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


courage.cw <- list(fin_w1 = c("fin_w1","Finland w1"), pol_w1 = c("pol_w1","Poland w1"), pol_w2 = c("pol_w2","Poland w2"), spain_w1 = c("spain_w1","Spain w1"), spain_w2 = c("spain_w2","Spain w2"))

# Consider only harmonised waves
l.hds <- lapply(courage.cw, function(wname) if(exists(paste0("COURAGE_ds_",wname[1]))){wname = list(get(paste0("COURAGE_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```




# Quality estimation
Anthropometric measure.




```{r closeRsession, echo=FALSE} 
opal.logout(o)
```

