---
title: "BMI"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_albert.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:
  
* Name: `bmi`
* Label: `Body Mass Index calculated as weight(kg)/height(m)^2`
* Type of variable: `countinous`
* Missings: 
    + `991 = CAPI/interviewer error`
    + `992 = Impute`
    + `993 = Disable to measure`
    + `994 = Not attempt/not done`
    + `995 = Does not answer`
    + `996 = Not applicable`
    + `997 = Refuse`
    + `998 = Do not know`
    + `999 = Missing`
* Comments: `the BMI variable should be created by dividing weight and heigh variables with the following equation= weight (kg)/height(m)^2.`


### COURAGE - Finnish - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q2507_weight`
* Label: `weight`
* Type of variable: `countinous`
* Missings
    + `997 = Disable to measure`
    + `998 = Refusal`

* Name: `q2506_height`
* Label: `height`
* Type of variable: `countinous`
* Missings
    + `997 = Disable to measure`
    + `998 = Refusal`


```{r assign_fin}
opal.assign.table.tibble(o, 'COURAGE_fin_w1_bmi','Courage.Courage_Finland_w1',
                         variables=list('q2507_weight', 'q2506_height'), missings = TRUE)
```

```{r local_fin}
COURAGE_fin_w1_bmi <- opal.execute(o,'COURAGE_fin_w1_bmi')

Continuous_summary(var = COURAGE_fin_w1_bmi$q2507_weight, missing_values = c(997, 998))
ggplot(COURAGE_fin_w1_bmi, aes(q2507_weight)) + geom_histogram(stat="count", fill="steelblue") + xlab("Weight") + ylab("Frequency") + xlim(50,100)

Continuous_summary(var = COURAGE_fin_w1_bmi$q2506_height, missing_values = c(997, 998))
ggplot(COURAGE_fin_w1_bmi, aes(q2506_height)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency") + xlim(50,100)
```

#### Harmonisation algorithm
The harmonized variable will be calculate from the study-specific variables using this formula

bmi=weight/height^2

The missing values have to be recoded as follows:

* `NA into 999`
* `997 into 993`
* `998 into 997`

R code of the ALGORITHM:

```{r harmo_fin}
COURAGE_ds_fin_w1 <- tibble(id=COURAGE_fin_w1_bmi$id)
COURAGE_ds_fin_w1$bmi  <- car::recode(round(COURAGE_fin_w1_bmi$q2507_weight /((COURAGE_fin_w1_bmi$q2506_height/100)^2), 3), "NA=999; 997=993; 998=997")
COURAGE_ds_fin_w1$bmi  <- labelled(COURAGE_ds_fin_w1$bmi , labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_fin}
Continuous_summary(var = COURAGE_ds_fin_w1$bmi, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_fin_w1, aes(bmi)) + geom_histogram(stat="count", fill="steelblue") + xlab("BMI") + ylab("Frequency") + xlim(10,100)
```

#### Validation
There are some unusual values that are lower than 12:
```{r crosstabulation_fin}
COURAGE_fin_w1_bmi$bmi <- COURAGE_ds_fin_w1$bmi
COURAGE_fin_w1_bmi[which(COURAGE_fin_w1_bmi$bmi<13),]
```






### COURAGE - Polish - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q2507_weight`
* Label: `weight`
* Type of variable: `countinous`
* Missings
    + `997 = Disable to measure`
    + `998 = Refusal`

* Name: `q2506_height`
* Label: `height`
* Type of variable: `countinous`
* Missings
    + `997 = Disable to measure`
    + `998 = Refusal`

```{r assign_pol1}
opal.assign.table.tibble(o, 'COURAGE_pol_w1_bmi','Courage.Courage_Poland_w1',
                         variables=list('q2507_weight', 'q2506_height'), missings = TRUE)
```

```{r local_pol1}
COURAGE_pol_w1_bmi <- opal.execute(o,'COURAGE_pol_w1_bmi')

Continuous_summary(var = COURAGE_pol_w1_bmi$q2507_weight, missing_values = c(997, 998))
ggplot(COURAGE_pol_w1_bmi, aes(q2507_weight)) + geom_histogram(stat="count", fill="steelblue") + xlab("Weight") + ylab("Frequency") + xlim(50,100)

Continuous_summary(var = COURAGE_pol_w1_bmi$q2506_height, missing_values = c(997, 998))
ggplot(COURAGE_pol_w1_bmi, aes(q2506_height)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency") + xlim(50,100)

```

#### Harmonisation algorithm
The harmonized variable will be calculate from the study-specific variables using this formula

bmi=weight/height^2

The missing values have to be recoded as follows:

* `NA into 999`
* `997 into 993`
* `998 into 997`

R code of the ALGORITHM:

```{r harmo_pol1}
compute_bmi <- function(Heigth, Weigth, miss, heigth_m = TRUE){
  Heigth <- car::recode(Heigth, "NA=999")
  Weigth <- car::recode(Weigth, "NA=999")
  
  if(heigth_m){
    bmi <- Weigth/(Heigth^2)
    
    bmi[Heigth==999] <- 999
    bmi[Heigth==miss[1]] <- Heigth[Heigth==miss[1]]
    bmi[Heigth==miss[2]] <- Heigth[Heigth==miss[2]]
    
    bmi[Weigth==999] <- 999
    bmi[Weigth==miss[1]] <- Weigth[Weigth==miss[1]]
    bmi[Weigth==miss[2]] <- Weigth[Weigth==miss[2]]
  } else {
    bmi <- Weigth/((Heigth/100)^2)
    
    bmi[Heigth==999] <- 999
    bmi[Heigth==miss[1]] <- Heigth[Heigth==miss[1]]
    bmi[Heigth==miss[2]] <- Heigth[Heigth==miss[2]]
    
    bmi[Weigth==999] <- 999
    bmi[Weigth==miss[1]] <- Weigth[Weigth==miss[1]]
    bmi[Weigth==miss[2]] <- Weigth[Weigth==miss[2]]
  }
  bmi
}

COURAGE_pol_w1_bmi$bmi <- compute_bmi(Heigth = COURAGE_pol_w1_bmi$q2506_height, 
            Weigth = COURAGE_pol_w1_bmi$q2507_weight, miss = c(997, 998), 
            heigth_m = FALSE)

COURAGE_ds_pol_w1 <- tibble(id=COURAGE_pol_w1_bmi$id)
COURAGE_ds_pol_w1$bmi  <- car::recode(COURAGE_pol_w1_bmi$bmi, "NA=999; 997=993; 998=997")
COURAGE_ds_pol_w1$bmi  <- labelled(COURAGE_ds_pol_w1$bmi , labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_pol1}
Continuous_summary(var = COURAGE_ds_pol_w1$bmi, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_pol_w1, aes(bmi)) + geom_histogram(stat="count", fill="steelblue") + xlab("BMI") + ylab("Frequency") + xlim(10,100)
```

#### Validation
There are some unusual values that are lower than 12:
```{r crosstabulation_pol1}
COURAGE_pol_w1_bmi$bmi <- COURAGE_ds_pol_w1$bmi
COURAGE_pol_w1_bmi[which(COURAGE_pol_w1_bmi$bmi<13),]
```







### COURAGE - Polish - Wave 2 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q2507_weight_s1`
* Label: `weight`
* Type of variable: `countinous`
* Missings
    + `997 = Disable to measure`
    + `998 = Refusal`
    
* Name: `q2506_height_s1`
* Label: `height`
* Type of variable: `countinous`
* Missings
    + `997 = Disable to measure`
    + `998 = Refusal`

```{r assign_pol2}
opal.assign.table.tibble(o, 'COURAGE_pol_w2_bmi','Courage.Courage_Poland_w2',
                         variables=list('q2507_weight_s1', 'q2506_height_s1'), missings = TRUE)
```

```{r local_pol2}
COURAGE_pol_w2_bmi <- opal.execute(o,'COURAGE_pol_w2_bmi')

Continuous_summary(var = COURAGE_pol_w2_bmi$q2507_weight_s1, missing_values = c(997, 998))
ggplot(COURAGE_pol_w2_bmi, aes(q2507_weight_s1)) + geom_histogram(stat="count", fill="steelblue") + xlab("Weight") + ylab("Frequency") + xlim(50,100)

Continuous_summary(var = COURAGE_pol_w2_bmi$q2506_height_s1, missing_values = c(997, 998))
ggplot(COURAGE_pol_w2_bmi, aes(q2506_height_s1)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency") + xlim(50,100)
```

#### Harmonisation algorithm
The harmonized variable will be calculate from the study-specific variables using this formula

bmi=weight/height^2

The missing values have to be recoded as follows:

* `NA into 999`
* `997 into 993`
* `998 into 997`

R code of the ALGORITHM:

```{r harmo_pol2}
compute_bmi <- function(Heigth, Weigth, miss, heigth_m = TRUE){
  Heigth <- car::recode(Heigth, "NA=999")
  Weigth <- car::recode(Weigth, "NA=999")
  
  if(heigth_m){
    bmi <- Weigth/(Heigth^2)
    
    bmi[Heigth==999] <- 999
    bmi[Heigth==miss[1]] <- Heigth[Heigth==miss[1]]
    bmi[Heigth==miss[2]] <- Heigth[Heigth==miss[2]]
    
    bmi[Weigth==999] <- 999
    bmi[Weigth==miss[1]] <- Weigth[Weigth==miss[1]]
    bmi[Weigth==miss[2]] <- Weigth[Weigth==miss[2]]
  } else {
    bmi <- Weigth/((Heigth/100)^2)
    
    bmi[Heigth==999] <- 999
    bmi[Heigth==miss[1]] <- Heigth[Heigth==miss[1]]
    bmi[Heigth==miss[2]] <- Heigth[Heigth==miss[2]]
    
    bmi[Weigth==999] <- 999
    bmi[Weigth==miss[1]] <- Weigth[Weigth==miss[1]]
    bmi[Weigth==miss[2]] <- Weigth[Weigth==miss[2]]
  }
  bmi
}

COURAGE_pol_w2_bmi$bmi <- compute_bmi(Heigth = COURAGE_pol_w2_bmi$q2506_height_s1,             Weigth = COURAGE_pol_w2_bmi$q2507_weight_s1, miss = c(997, 998), 
            heigth_m = FALSE)

COURAGE_ds_pol_w2 <- tibble(id=COURAGE_pol_w2_bmi$id)
COURAGE_ds_pol_w2$bmi  <- car::recode(COURAGE_pol_w2_bmi$bmi, "NA=999; 997=993; 998=997")
COURAGE_ds_pol_w2$bmi  <- labelled(COURAGE_ds_pol_w2$bmi , labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_pol2}
Continuous_summary(var = COURAGE_ds_pol_w2$bmi, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_pol_w2, aes(bmi)) + geom_histogram(stat="count", fill="steelblue") + xlab("BMI") + ylab("Frequency") + xlim(10,100)
```

#### Validation

```{r crosstabulation_pol2}


```








### COURAGE - Spain - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q2507_weight`
* Label: `weight`
* Type of variable: `countinous`
* Missings
    + `997 = Disable to measure`
    + `998 = Refusal`

* Name: `q2506_height`
* Label: `height`
* Type of variable: `countinous`
* Missings
    + `997 = Disable to measure`
    + `998 = Refusal`


```{r assign_spain1}
opal.assign.table.tibble(o, 'COURAGE_spain_w1_bmi','Courage.Courage_Spain_w1',
                         variables=list('q2507_weight', 'q2506_height'), missings = TRUE)
```

```{r local_spain1}
COURAGE_spain_w1_bmi <- opal.execute(o,'COURAGE_spain_w1_bmi')

Continuous_summary(var = COURAGE_spain_w1_bmi$q2507_weight, missing_values = c(997, 998))
ggplot(COURAGE_spain_w1_bmi, aes(q2507_weight)) + geom_histogram(stat="count", fill="steelblue") + xlab("Weight") + ylab("Frequency") + xlim(50,100)

Continuous_summary(var = COURAGE_spain_w1_bmi$q2506_height, missing_values = c(997, 998))
ggplot(COURAGE_spain_w1_bmi, aes(q2506_height)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency") + xlim(50,100)
```

#### Harmonisation algorithm
The harmonized variable will be calculate from the study-specific variables using this formula

bmi=weight/height^2

The missing values have to be recoded as follows:

* `NA into 999`
* `997 into 993`
* `998 into 997`

R code of the ALGORITHM:

```{r harmo_spain1}
compute_bmi <- function(Heigth, Weigth, miss, heigth_m = TRUE){
  Heigth <- car::recode(Heigth, "NA=999")
  Weigth <- car::recode(Weigth, "NA=999")
  
  if(heigth_m){
    bmi <- Weigth/(Heigth^2)
    
    bmi[Heigth==999] <- 999
    bmi[Heigth==miss[1]] <- Heigth[Heigth==miss[1]]
    bmi[Heigth==miss[2]] <- Heigth[Heigth==miss[2]]
    bmi[Heigth==miss[3]] <- Heigth[Heigth==miss[3]]
    
    bmi[Weigth==999] <- 999
    bmi[Weigth==miss[1]] <- Weigth[Weigth==miss[1]]
    bmi[Weigth==miss[2]] <- Weigth[Weigth==miss[2]]
    bmi[Weigth==miss[3]] <- Weigth[Weigth==miss[3]]
  } else {
    bmi <- Weigth/((Heigth/100)^2)
    
    bmi[Heigth==999] <- 999
    bmi[Heigth==miss[1]] <- Heigth[Heigth==miss[1]]
    bmi[Heigth==miss[2]] <- Heigth[Heigth==miss[2]]
    bmi[Heigth==miss[3]] <- Heigth[Heigth==miss[3]]
    
    bmi[Weigth==999] <- 999
    bmi[Weigth==miss[1]] <- Weigth[Weigth==miss[1]]
    bmi[Weigth==miss[2]] <- Weigth[Weigth==miss[2]]
    bmi[Weigth==miss[3]] <- Weigth[Weigth==miss[3]]
  }
  bmi
}

COURAGE_spain_w1_bmi$bmi <- compute_bmi(Heigth = COURAGE_spain_w1_bmi$q2506_height, 
            Weigth = COURAGE_spain_w1_bmi$q2507_weight, miss = c(997, 998, 889), 
            heigth_m = FALSE)

COURAGE_ds_spain_w1 <- tibble(id=COURAGE_spain_w1_bmi$id)
COURAGE_ds_spain_w1$bmi  <- car::recode(COURAGE_spain_w1_bmi$bmi, "NA=999; 997=993; 998=997; 889=997")
COURAGE_ds_spain_w1$bmi  <- labelled(COURAGE_ds_spain_w1$bmi , labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_spain1}
Continuous_summary(var = COURAGE_ds_spain_w1$bmi, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_spain_w1, aes(bmi)) + geom_histogram(stat="count", fill="steelblue") + xlab("BMI") + ylab("Frequency") + xlim(10,100)
```

#### Validation

```{r crosstabulation_spain1}
```







### COURAGE - Spain - Wave 2 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `q2507_weight_s1`
* Label: `weight`
* Type of variable: `countinous`
* Missings
    + `997 = Disable to measure`
    + `998 = Refusal`

* Name: `q2506_height_s1`
* Label: `height`
* Type of variable: `countinous`
* Missings
    + `997 = Disable to measure`
    + `998 = Refusal`

```{r assign_spain2}
opal.assign.table.tibble(o, 'COURAGE_spain_w2_bmi','Courage.Courage_Spain_w2_1',
                         variables=list('q2507_weight_s1', 'q2506_height_s1'), missings = TRUE)
```

```{r local_spain2}
COURAGE_spain_w2_bmi <- opal.execute(o,'COURAGE_spain_w2_bmi')

Continuous_summary(var = COURAGE_spain_w2_bmi$q2507_weight_s1, missing_values = c(997, 998))
ggplot(COURAGE_spain_w2_bmi, aes(q2507_weight_s1)) + geom_histogram(stat="count", fill="steelblue") + xlab("Weight") + ylab("Frequency") + xlim(50,100)

Continuous_summary(var = COURAGE_spain_w2_bmi$q2506_height_s1, missing_values = c(997, 998))
ggplot(COURAGE_spain_w2_bmi, aes(q2506_height_s1)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency") + xlim(50,100)
```

#### Harmonisation algorithm

bmi=weight/height^2

The missing values have to be recoded as follows:

* `NA into 999`
* `997 into 993`
* `998 into 997`

R code of the ALGORITHM:

```{r harmo_spain2}
compute_bmi <- function(Heigth, Weigth, miss, heigth_m = TRUE){
  Heigth <- car::recode(Heigth, "NA=999")
  Weigth <- car::recode(Weigth, "NA=999")
  
  if(heigth_m){
    bmi <- Weigth/(Heigth^2)
    
    bmi[Heigth==999] <- 999
    bmi[Heigth==miss[1]] <- Heigth[Heigth==miss[1]]
    bmi[Heigth==miss[2]] <- Heigth[Heigth==miss[2]]
    
    bmi[Weigth==999] <- 999
    bmi[Weigth==miss[1]] <- Weigth[Weigth==miss[1]]
    bmi[Weigth==miss[2]] <- Weigth[Weigth==miss[2]]
  } else {
    bmi <- Weigth/((Heigth/100)^2)
    
    bmi[Heigth==999] <- 999
    bmi[Heigth==miss[1]] <- Heigth[Heigth==miss[1]]
    bmi[Heigth==miss[2]] <- Heigth[Heigth==miss[2]]
    
    bmi[Weigth==999] <- 999
    bmi[Weigth==miss[1]] <- Weigth[Weigth==miss[1]]
    bmi[Weigth==miss[2]] <- Weigth[Weigth==miss[2]]
  }
  bmi
}

COURAGE_spain_w2_bmi$bmi <- compute_bmi(Heigth = COURAGE_spain_w2_bmi$q2506_height_s1, 
            Weigth = COURAGE_spain_w2_bmi$q2507_weight_s1, miss = c(997, 998), 
            heigth_m = FALSE)

COURAGE_ds_spain_w2 <- tibble(id=COURAGE_spain_w2_bmi$id)
COURAGE_ds_spain_w2$bmi  <- car::recode(COURAGE_spain_w2_bmi$bmi, "NA=999; 997=993; 998=997")
COURAGE_ds_spain_w2$bmi  <- labelled(COURAGE_ds_spain_w2$bmi , labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_spain2}
Continuous_summary(var = COURAGE_ds_spain_w2$bmi, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(COURAGE_ds_spain_w2, aes(bmi)) + geom_histogram(stat="count", fill="steelblue") + xlab("BMI") + ylab("Frequency") + xlim(10,100)
```

#### Validation
There are som unusual values that are upper than 70:
```{r crosstabulation_spain2}
COURAGE_spain_w2_bmi[which(COURAGE_spain_w2_bmi$bmi>70 & COURAGE_spain_w2_bmi$bmi<900),]
```


# Quality estimation

No comments.

```{r save, echo=FALSE}
bmi <- COURAGE_ds_spain_w1
save(bmi, file = "../RData/spain_w1/bmi.RData")
rm(bmi)

bmi <- COURAGE_ds_spain_w2
save(bmi, file = "../RData/spain_w2/bmi.RData")
rm(bmi)

bmi <- COURAGE_ds_pol_w1
save(bmi, file = "../RData/pol_w1/bmi.RData")
rm(bmi)

bmi <- COURAGE_ds_pol_w2
save(bmi, file = "../RData/pol_w2/bmi.RData")
rm(bmi)

bmi <- COURAGE_ds_fin_w1
save(bmi, file = "../RData/fin_w1/bmi.RData")
rm(bmi)
```


```{r closeRsession, echo=FALSE} 
opal.logout(o)
```

