---
title: "Close spouse"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/close_spouseDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/close_spouseDS.R')
```

<!-- ########################################################## --> 

# Data process

## England

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scptrg`
* Label: `how close is your relationship with your spouse or partner?`
* Categories:
    + `1 = Very close`
    + `2 = Quite close`
    + `3 = Not very close`
    + `4 = Not at all close`
* Missings:
    + `-9 = Not answered (9)`
    + `-1 = Item not applicable`


```{r assign1, echo=F}
opal.assign.table.tibble(o, 'ELSA_w1_close_spouse','ELSA.wave_1_core_data_v3', variables=list('scptrg'), missings = TRUE)
ELSA_w1_close_spouse <- opal.execute(o,'ELSA_w1_close_spouse')
```

```{r local1, echo=F}
Categorical_summary(var = ELSA_w1_close_spouse$scptrg, missing_values = NA)
ggplot(ELSA_w1_close_spouse, aes(x=factor(scptrg))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("how close is your relationship with your spouse or partner?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `3 or 4 into 0`
* `1 or 2 into 1`
* `-9 into 995`
* `-1 into 996`
* `NA into 999`

**R script:**

```{r harmo1}
ELSA_ds_w1 <- tibble(id=ELSA_w1_close_spouse$id)
ELSA_ds_w1$close_spouse <- car::recode(as.vector(ELSA_w1_close_spouse$scptrg), "1:2='1'; 3:4='0'; -1='996'; -9='995'; NA='999'")
ELSA_ds_w1$close_spouse <- labelled(ELSA_ds_w1$close_spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
Categorical_summary(var = ELSA_ds_w1$close_spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w1, aes(x=factor(close_spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Is the relationship with the spouse close?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(ELSA_ds_w1$close_spouse)
BeforeH <- table(ELSA_w1_close_spouse$scptrg, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- sum(BeforeH[c(3:4)])
BeforeH1[[1]] <- sum(BeforeH[c(5:6)])
BeforeH1[[3]] <- BeforeH[['-9']]
BeforeH1[[4]] <- BeforeH[['-1']]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("3:4->0","1:2->1","-9->995","-1->996")
kable(C)
```







### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scptrg`
* Label: `How close the respondents relationship to their spouse/partner is`
* Categories:
    + `1 = Very close`
    + `2 = Quite close`
    + `3 = Not very close`
    + `4 = Not at all close`
* Missings:
    + `-9 = Not answered`
    + `-1 = Item not applicable`


```{r assign2, echo=F}
opal.assign.table.tibble(o, 'ELSA_w2_close_spouse','ELSA.wave_2_core_data_v4', variables=list('scptrg'), missings = TRUE)
ELSA_w2_close_spouse <- opal.execute(o,'ELSA_w2_close_spouse')
```

```{r local2, echo=F}
Categorical_summary(var = ELSA_w2_close_spouse$scptrg, missing_values = NA)
ggplot(ELSA_w2_close_spouse, aes(x=factor(scptrg))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How close the respondents relationship to their spouse/partner is?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `3 or 4 into 0`
* `1 or 2 into 1`
* `-9 into 995`
* `-1 into 996`
* `NA into 999`

**R script:**

```{r harmo2}
ELSA_ds_w2 <- tibble(id=ELSA_w2_close_spouse$id)
ELSA_ds_w2$close_spouse <- car::recode(as.vector(ELSA_w2_close_spouse$scptrg), "1:2='1'; 3:4='0'; -1='996'; -9='995'; NA='999'")
ELSA_ds_w2$close_spouse <- labelled(ELSA_ds_w2$close_spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
Categorical_summary(var = ELSA_ds_w2$close_spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w2, aes(x=factor(close_spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Is the relationship with the spouse close?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
AfterH <- table(ELSA_ds_w2$close_spouse)
BeforeH <- table(ELSA_w2_close_spouse$scptrg, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- sum(BeforeH[c(3:4)])
BeforeH1[[1]] <- sum(BeforeH[c(5:6)])
BeforeH1[[3]] <- BeforeH[['-9']]
BeforeH1[[4]] <- BeforeH[['-1']]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("3:4->0","1:2->1","-9->995","-1->996")
kable(C)
```






### Wave 3

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scptrg`
* Label: `How close the respondents relationship to their spouse/partner is`
* Categories:
    + `1 = Very close`
    + `2 = Quite close`
    + `3 = Not very close`
    + `4 = Not at all close`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-1 = Item not applicable`


```{r assign3, echo=F}
opal.assign.table.tibble(o, 'ELSA_w3_close_spouse','ELSA.wave_3_elsa_data_v4',variables=list('scptrg'), missings = TRUE)
ELSA_w3_close_spouse <- opal.execute(o,'ELSA_w3_close_spouse')
```

```{r local3, echo=F}
Categorical_summary(var = ELSA_w3_close_spouse$scptrg, missing_values = NA)
ggplot(ELSA_w3_close_spouse, aes(x=factor(scptrg))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How close the respondents relationship to their spouse/partner is?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `3 or 4 into 0`
* `1 or 2 into 1`
* `-9 into 995`
* `-8 into 998`
* `-1 into 996`
* `NA into 999`

**R script:**

```{r harmo3}
ELSA_ds_w3 <- tibble(id=ELSA_w3_close_spouse$id)
ELSA_ds_w3$close_spouse <- car::recode(as.vector(ELSA_w3_close_spouse$scptrg), "1:2='1'; 3:4='0'; -1='996'; -8='998'; -9='995'; NA='999'")
ELSA_ds_w3$close_spouse <- labelled(ELSA_ds_w3$close_spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}
Categorical_summary(var = ELSA_ds_w3$close_spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w3, aes(x=factor(close_spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Is the relationship with the spouse close?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=F}
AfterH <- table(ELSA_ds_w3$close_spouse)
BeforeH <- table(ELSA_w3_close_spouse$scptrg, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- sum(BeforeH[c(3:4)])
BeforeH1[[1]] <- sum(BeforeH[c(5:6)])
BeforeH1[[3]] <- BeforeH[['-9']]
BeforeH1[[4]] <- BeforeH[['-1']]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("3:4->0","1:2->1","-9->995","-1->996")
kable(C)
```






### Wave 4

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scptrg`
* Label: `How close the respondents relationship to their spouse/partner is`
* Categories:
    + `1 = Very close`
    + `2 = Quite close`
    + `3 = Not very close`
    + `4 = Not at all close`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know (8)`
    + `-1 = Item not applicable`


```{r assign4, echo=F}
opal.assign.table.tibble(o, 'ELSA_w4_close_spouse','ELSA.wave_4_elsa_data_v3',variables=list('scptrg'), missings = TRUE)
ELSA_w4_close_spouse <- opal.execute(o,'ELSA_w4_close_spouse')
```

```{r local4, echo=F}
Categorical_summary(var = ELSA_w4_close_spouse$scptrg, missing_values = NA)
ggplot(ELSA_w4_close_spouse, aes(x=factor(scptrg))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How close the respondents relationship to their spouse/partner is?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `3 or 4 into 0`
* `1 or 2 into 1`
* `-9 into 995`
* `-8 into 998`
* `-1 into 996`
* `NA into 999`

**R script:**

```{r harmo4}
ELSA_ds_w4 <- tibble(id=ELSA_w4_close_spouse$id)
ELSA_ds_w4$close_spouse <- car::recode(as.vector(ELSA_w4_close_spouse$scptrg), "1:2='1'; 3:4='0'; -1='996'; -8='998'; -9='995'; NA='999'")
ELSA_ds_w4$close_spouse <- labelled(ELSA_ds_w4$close_spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript4, echo=F}
Categorical_summary(var = ELSA_ds_w4$close_spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w4, aes(x=factor(close_spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Is the relationship with the spouse close?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=F}
AfterH <- table(ELSA_ds_w4$close_spouse)
BeforeH <- table(ELSA_w4_close_spouse$scptrg, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- sum(BeforeH[c(3:4)])
BeforeH1[[1]] <- sum(BeforeH[c(5:6)])
BeforeH1[[3]] <- BeforeH[['-9']]
BeforeH1[[4]] <- BeforeH[['-1']]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("3:4->0","1:2->1","-9->995","-1->996")
kable(C)
```







### Wave 5

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scptrg`
* Label: `How close the respondents relationship to their spouse/partner is`
* Categories:
    + `1 = Very close`
    + `2 = Quite close`
    + `3 = Not very close`
    + `4 = Not at all close`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know (8)`
    + `-2 = Schedule Not Applicable`
    + `-1 = Item not applicable`


```{r assign5, echo=F}
opal.assign.table.tibble(o, 'ELSA_w5_close_spouse','ELSA.wave_5_elsa_data_v4',variables=list('scptrg'), missings = TRUE)
ELSA_w5_close_spouse <- opal.execute(o,'ELSA_w5_close_spouse')
```

```{r local5, echo=F}
Categorical_summary(var = ELSA_w5_close_spouse$scptrg, missing_values = NA)
ggplot(ELSA_w5_close_spouse, aes(x=factor(scptrg))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How close the respondents relationship to their spouse/partner is?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `3 or 4 into 0`
* `1 or 2 into 1`
* `-9 into 995`
* `-8 into 998`
* `-2 into 996`
* `-1 into 996`
* `NA into 999`

**R script:**

```{r harmo5}
ELSA_ds_w5 <- tibble(id=ELSA_w5_close_spouse$id)
ELSA_ds_w5$close_spouse <- car::recode(as.vector(ELSA_w5_close_spouse$scptrg), "1:2='1'; 3:4='0'; -1='996'; -2='996'; -8='998'; -9='995'; NA='999'")
ELSA_ds_w5$close_spouse <- labelled(ELSA_ds_w5$close_spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript5, echo=F}
Categorical_summary(var = ELSA_ds_w5$close_spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w5, aes(x=factor(close_spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Is the relationship with the spouse close?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation5, echo=F}
AfterH <- table(ELSA_ds_w5$close_spouse)
BeforeH <- table(ELSA_w5_close_spouse$scptrg, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- sum(BeforeH[c(4:5)])
BeforeH1[[1]] <- sum(BeforeH[c(6:7)])
BeforeH1[[3]] <- BeforeH[['-9']]
BeforeH1[[4]] <- sum(BeforeH[c('-1','-2')])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("3:4->0","1:2->1","-9->995","-1&-2->996")
kable(C)
```






### Wave 6

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scptrg`
* Label: `How close the respondents relationship to their spouse/partner is`
* Categories:
    + `1 = Very close`
    + `2 = Quite close`
    + `3 = Not very close`
    + `4 = Not at all close`
* Missings:
    + `-9 = Not answered (9)`
    + `-8 = Don't know (8)`
    + `-2 = Schedule Not Applicable`
    + `-1 = Item not applicable`


```{r assign6, echo=F}
opal.assign.table.tibble(o, 'ELSA_w6_close_spouse','ELSA.wave_6_elsa_data_v2',variables=list('scptrg'), missings = TRUE)
ELSA_w6_close_spouse <- opal.execute(o,'ELSA_w6_close_spouse')
```

```{r local6, echo=F}
Categorical_summary(var = ELSA_w6_close_spouse$scptrg, missing_values = NA)
ggplot(ELSA_w6_close_spouse, aes(x=factor(scptrg))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How close the respondents relationship to their spouse/partner is?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `3 or 4 into 0`
* `1 or 2 into 1`
* `-9 into 995`
* `-8 into 998`
* `-2 into 996`
* `-1 into 996`
* `NA into 999`

**R script:**

```{r harmo6}
ELSA_ds_w6 <- tibble(id=ELSA_w6_close_spouse$id)
ELSA_ds_w6$close_spouse <- car::recode(as.vector(ELSA_w6_close_spouse$scptrg), "1:2='1'; 3:4='0'; -1='996'; -2='996'; -8='998'; -9='995'; NA='999'")
ELSA_ds_w6$close_spouse <- labelled(ELSA_ds_w6$close_spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript6, echo=F}
Categorical_summary(var = ELSA_ds_w6$close_spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w6, aes(x=factor(close_spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Is the relationship with the spouse close?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation6, echo=F}
AfterH <- table(ELSA_ds_w6$close_spouse)
BeforeH <- table(ELSA_w6_close_spouse$scptrg, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- sum(BeforeH[c(4:5)])
BeforeH1[[1]] <- sum(BeforeH[c(6:7)])
BeforeH1[[3]] <- BeforeH[['-9']]
BeforeH1[[4]] <- sum(BeforeH[c('-1','-2')])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("3:4->0","1:2->1","-9->995","-1&-2->996")
kable(C)
```






	


### Wave 7

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scptrh`
* Label: `How close the respondents relationship to their spouse/partner is`
* Categories:
    + `1 = Very close`
    + `2 = Quite close`
    + `3 = Not very close`
    + `4 = Not at all close`
* Missings:
    + `-9 = Not answered (9)`
    + `-8 = Don't know (8)`
    + `-2 = Schedule Not Applicable`
    + `-1 = Item not applicable`


```{r assign7, echo=F}
opal.assign.table.tibble(o, 'ELSA_w7_close_spouse','ELSA.wave_7_elsa_data',variables=list('scptrh'), missings = TRUE)
ELSA_w7_close_spouse <- opal.execute(o,'ELSA_w7_close_spouse')
```

```{r local7, echo=F}
Categorical_summary(var = ELSA_w7_close_spouse$scptrh, missing_values = NA)
ggplot(ELSA_w7_close_spouse, aes(x=factor(scptrh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How close the respondents relationship to their spouse/partner is?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `3 or 4 into 0`
* `1 or 2 into 1`
* `-9 into 995`
* `-8 into 998`
* `-2 into 996`
* `-1 into 996`
* `NA into 999`

**R script:**

```{r harmo7}
ELSA_ds_w7 <- tibble(id=ELSA_w7_close_spouse$id)
ELSA_ds_w7$close_spouse <- car::recode(as.vector(ELSA_w7_close_spouse$scptrh), "1:2='1'; 3:4='0'; -1='996'; -2='996'; -8='998'; -9='995'; NA='999'")
ELSA_ds_w7$close_spouse <- labelled(ELSA_ds_w7$close_spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript7, echo=F}
Categorical_summary(var = ELSA_ds_w7$close_spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w7, aes(x=factor(close_spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Is the relationship with the spouse close?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation7, echo=F}
AfterH <- table(ELSA_ds_w7$close_spouse)
BeforeH <- table(ELSA_w7_close_spouse$scptrh, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- sum(BeforeH[c(4:5)])
BeforeH1[[1]] <- sum(BeforeH[c(6:7)])
BeforeH1[[3]] <- BeforeH[['-9']]
BeforeH1[[4]] <- sum(BeforeH[c('-1','-2')])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("3:4->0","1:2->1","-9->995","-1&-2->996")
kable(C)
```



```{r final, echo=F}

l.hds <- list(w1 = ELSA_ds_w1, w2 = ELSA_ds_w2, w3 = ELSA_ds_w3, w4 = ELSA_ds_w4, w5 = ELSA_ds_w5, w6 = ELSA_ds_w6, w7 = ELSA_ds_w7)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("ELSA_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

```

## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.


```{r summ}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",names(l.hds))
kable(t.hds)

dbb <- get(paste0("ELSA_m_ds_",names(l.hds)[1]))[,c("id","close_spouse")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("ELSA_m_ds_",names(l.hds)[ind]))[,c("id","close_spouse")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", names(l.hds))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])

```


# Quality estimation
[Comments on the quality of the new harmonised variable.]


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  close_spouse <- l.hds[[index]]
  save(close_spouse, file = paste0(datafolder,names(l.hds)[index],"/close_spouse.RData"))
}

```
<!-- ########################################################## --> 

<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
