---
title: "Any participation in organized/group sport activities (like sport clubs, do sport with other people, membership of gyms, exercise classes etc.)"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup_iago.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `sport`
* Variable label: `Sport activities`
* Domain: `Social environment`
* Value type: `categorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process

## England



### Wave 1

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scorg7`
* Label: `Sports clubs, gyms, exercise classes`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-1 = Item not applicable`


* Description: 
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'ELSA_w1_sport','ELSA.wave_1_core_data_v3', variables=list('scorg7'), missings = TRUE)
```

```{r local1, echo=F}
ELSA_w1_sport <- opal.execute(o,'ELSA_w1_sport')
vari <- ELSA_w1_sport$scorg7
kable(Categorical_summary(vari, missing_values = c(-1,-9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-9))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w1_sport$scorg7, missing_values = NA)
ggplot(ELSA_w1_sport, aes(x=factor(scorg7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sports clubs, gyms, exercise classes") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1, 0 into 0`
* `-1 into 996`
* `-9 into 995`
* `NA into 999`

 **R script:**

```{r harmo1, echo=TRUE}
ELSA_ds_w1 <- tibble(id=ELSA_w1_sport$id)
ELSA_ds_w1$sport <- car::recode(as.vector(ELSA_w1_sport$scorg7), "0='0'; 1='1'; -1='996'; -9='995'; NA='999'")
ELSA_ds_w1$sport <- labelled(ELSA_ds_w1$sport, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995, "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <- ELSA_ds_w1$sport
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w1$sport, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w1, aes(x=factor(sport))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sport activities") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(ELSA_ds_w1$sport)
BeforeH <- table(ELSA_w1_sport$scorg7, useNA='ifany')[c(3,4,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","-9->995","-1->996")
kable(C)
```

 
 



### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scorg07`
* Label: `Organisational membership: member of a sports clubs, gym, or exercise class`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-1 = Item not applicable`


* Description: 
```{r assign2, echo=F}
opal.assign.table.tibble(o, 'ELSA_w2_sport','ELSA.wave_2_core_data_v4',variables=list('scorg07'), missings = TRUE)
```

```{r local2, echo=F}
ELSA_w2_sport <- opal.execute(o,'ELSA_w2_sport')
vari <-  ELSA_w2_sport$scorg07
kable(Categorical_summary(vari, missing_values = c(-1,-9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-9))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w2_sport$scorg07, missing_values = NA)
ggplot(ELSA_w2_sport, aes(x=factor(scorg07))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sports clubs, gyms, exercise classes") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1, 0 into 0`
* `-1 into 996`
* `-9 into 995`
* `NA into 999`

 **R script:**

```{r harmo2, echo=TRUE}
ELSA_ds_w2 <- tibble(id=ELSA_w2_sport$id)
ELSA_ds_w2$sport <- car::recode(as.vector(ELSA_w2_sport$scorg07), "0='0'; 1='1'; -1='996'; -9='995'; NA='999'")
ELSA_ds_w2$sport <- labelled(ELSA_ds_w2$sport, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995, "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}
vari <- ELSA_ds_w2$sport
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w2$sport, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w2, aes(x=factor(sport))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sport activities") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
AfterH <- table(ELSA_ds_w2$sport)
BeforeH <- table(ELSA_w2_sport$scorg07, useNA='ifany')[c(3,4,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","-9->995","-1->996")
kable(C)
```

 
 



### Wave 3

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scorg07`
* Label: `Respondent is a member of a sports clubs, gym, or exercise class`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-1 = Item not applicable`


* Description: 
```{r assign3, echo=F}
opal.assign.table.tibble(o, 'ELSA_w3_sport','ELSA.wave_3_elsa_data_v4',variables=list('scorg07'), missings = TRUE)
```

```{r local3, echo=F}
ELSA_w3_sport <- opal.execute(o,'ELSA_w3_sport')
vari <-  ELSA_w3_sport$scorg07
kable(Categorical_summary(vari, missing_values = c(-1,-8,-9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-8,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-8,-9))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w3_sport$scorg07, missing_values = NA)
ggplot(ELSA_w3_sport, aes(x=factor(scorg07))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sports clubs, gyms, exercise classes") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1, 0 into 0`
* `-1 into 996`
* `-8 into 998`
* `-9 into 995`
* `NA into 999`

 **R script:**

```{r harmo3, echo=TRUE}
ELSA_ds_w3 <- tibble(id=ELSA_w3_sport$id)
ELSA_ds_w3$sport <- car::recode(as.vector(ELSA_w3_sport$scorg07), "0='0'; 1='1'; -1='996'; -8='998'; -9='995'; NA='999'")
ELSA_ds_w3$sport <- labelled(ELSA_ds_w3$sport, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995, "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=F}
vari <- ELSA_ds_w3$sport
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w3$sport, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w3, aes(x=factor(sport))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sport activities") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=F}
AfterH <- table(ELSA_ds_w3$sport)
BeforeH <- table(ELSA_w3_sport$scorg07, useNA='ifany')[c(3,4,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","-9->995","-1->996")
kable(C)
```

 
 



### Wave 4

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scorg07`
* Label: `Respondent is a member of a sports clubs, gym, or exercise class`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-1 = Item not applicable`


* Description: 
```{r assign4, echo=F}
opal.assign.table.tibble(o, 'ELSA_w4_sport','ELSA.wave_4_elsa_data_v3', variables=list('scorg07'), missings = TRUE)
```

```{r local4, echo=F}
ELSA_w4_sport <- opal.execute(o,'ELSA_w4_sport')
vari <-  ELSA_w4_sport$scorg07
kable(Categorical_summary(vari, missing_values = c(-1,-8,-9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-8,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-8,-9))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w4_sport$scorg07, missing_values = NA)
ggplot(ELSA_w4_sport, aes(x=factor(scorg07))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sports clubs, gyms, exercise classes") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1, 0 into 0`
* `-1 into 996`
* `-8 into 998`
* `-9 into 995`
* `NA into 999`

 **R script:**

```{r harmo4, echo=TRUE}
ELSA_ds_w4 <- tibble(id=ELSA_w4_sport$id)
ELSA_ds_w4$sport <- car::recode(as.vector(ELSA_w4_sport$scorg07), "0='0'; 1='1'; -1='996'; -8='998'; -9='995'; NA='999'")
ELSA_ds_w4$sport <- labelled(ELSA_ds_w4$sport, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995, "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4, echo=F}
vari <- ELSA_ds_w4$sport
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w4$sport, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w4, aes(x=factor(sport))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sport activities") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=F}
AfterH <- table(ELSA_ds_w4$sport)
BeforeH <- table(ELSA_w4_sport$scorg07, useNA='ifany')[c(3,4,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","-9->995","-1->996")
kable(C)
```

 
 



### Wave 5

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scorg07`
* Label: `Respondent is a member of a sports clubs, gym, or exercise class`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-2 = Schedule Not Applicable`
    + `-1 = Item not applicable`


* Description: 
```{r assign5, echo=F}
opal.assign.table.tibble(o, 'ELSA_w5_sport','ELSA.wave_5_elsa_data_v4',variables=list('scorg07'), missings = TRUE)
```

```{r local5, echo=F}
ELSA_w5_sport <- opal.execute(o,'ELSA_w5_sport')
vari <-  ELSA_w5_sport$scorg07
kable(Categorical_summary(vari, missing_values = c(-1,-2,-8,-9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-2,-8,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2,-8,-9))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w5_sport$scorg07, missing_values = NA)
ggplot(ELSA_w5_sport, aes(x=factor(scorg07))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sports clubs, gyms, exercise classes") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1, 0 into 0`
* `-1 or -2 into 996`
* `-8 into 998`
* `-9 into 995`
* `NA into 999`

 **R script:**

```{r harmo5, echo=TRUE}
ELSA_ds_w5 <- tibble(id=ELSA_w5_sport$id)
ELSA_ds_w5$sport <- car::recode(as.vector(ELSA_w5_sport$scorg07), "0='0'; 1='1'; -1='996'; -2='996'; -8='998'; -9='995'; NA='999'")
ELSA_ds_w5$sport <- labelled(ELSA_ds_w5$sport, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995, "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript5, echo=F}
vari <- ELSA_ds_w5$sport
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w5$sport, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w5, aes(x=factor(sport))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sport activities") + ylab("Frequency")
```

#### Validation
```{r crosstabulation5, echo=F}
AfterH <- table(ELSA_ds_w5$sport)
BeforeH <- table(ELSA_w5_sport$scorg07, useNA='ifany')[c(3,4,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","-9->995","-2->996")
kable(C)
```

 
 



### Wave 6

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scorg07`
* Label: `Respondent is a member of a sports clubs, gym, or exercise class`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-2 = Schedule Not Applicable`
    + `-1 = Item not applicable`


* Description: 
```{r assign6, echo=F}
opal.assign.table.tibble(o, 'ELSA_w6_sport','ELSA.wave_6_elsa_data_v2', variables=list('scorg07'), missings = TRUE)
```

```{r local6, echo=F}
ELSA_w6_sport <- opal.execute(o,'ELSA_w6_sport')
vari <-  ELSA_w6_sport$scorg07
kable(Categorical_summary(vari, missing_values = c(-1,-2,-8,-9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-2,-8,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2,-8,-9))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w6_sport$scorg07, missing_values = NA)
ggplot(ELSA_w6_sport, aes(x=factor(scorg07))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sports clubs, gyms, exercise classes") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1, 0 into 0`
* `-1 or -2 into 996`
* `-8 into 998`
* `-9 into 995`
* `NA into 999`

 **R script:**

```{r harmo6, echo=TRUE}
ELSA_ds_w6 <- tibble(id=ELSA_w6_sport$id)
ELSA_ds_w6$sport <- car::recode(as.vector(ELSA_w6_sport$scorg07), "0='0'; 1='1'; -1='996'; -2='996'; -8='998'; -9='995'; NA='999'")
ELSA_ds_w6$sport <- labelled(ELSA_ds_w6$sport, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995, "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript6, echo=F}
vari <- ELSA_ds_w6$sport
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w6$sport, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w6, aes(x=factor(sport))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sport activities") + ylab("Frequency")
```

#### Validation
```{r crosstabulation6, echo=F}
AfterH <- table(ELSA_ds_w6$sport)
BeforeH <- table(ELSA_w6_sport$scorg07, useNA='ifany')[c(3,4,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","-9->995","-2->996")
kable(C)
```

 
 



### Wave 7

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scorg07`
* Label: `Respondent is a member of a sports clubs, gym, or exercise class`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-2 = Schedule Not Applicable`
    + `-1 = Item not applicable`


* Description: 
```{r assign7, echo=F}
opal.assign.table.tibble(o, 'ELSA_w7_sport','ELSA.wave_7_elsa_data', variables=list('scorg07'), missings = TRUE)
```

```{r local7, echo=F}
ELSA_w7_sport <- opal.execute(o,'ELSA_w7_sport')
vari <-  ELSA_w7_sport$scorg07
kable(Categorical_summary(vari, missing_values = c(-1,-2,-8,-9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-2,-8,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2,-8,-9))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w7_sport$scorg07, missing_values = NA)
ggplot(ELSA_w7_sport, aes(x=factor(scorg07))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sports clubs, gyms, exercise classes") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1, 0 into 0`
* `-1 or -2 into 996`
* `-8 into 998`
* `-9 into 995`
* `NA into 999`

 **R script:**

```{r harmo7, echo=TRUE}
ELSA_ds_w7 <- tibble(id=ELSA_w7_sport$id)
ELSA_ds_w7$sport <- car::recode(as.vector(ELSA_w7_sport$scorg07), "0='0'; 1='1'; -1='996'; -2='996'; -8='998'; -9='995'; NA='999'")
ELSA_ds_w7$sport <- labelled(ELSA_ds_w7$sport, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995, "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript7, echo=F}
vari <- ELSA_ds_w7$sport
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w7$sport, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w7, aes(x=factor(sport))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sport activities") + ylab("Frequency")
```

#### Validation
```{r crosstabulation7, echo=F}
AfterH <- table(ELSA_ds_w7$sport)
BeforeH <- table(ELSA_w7_sport$scorg07, useNA='ifany')[c(3,4,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","-9->995","-2->996")
kable(C)
```

```{r save, echo=FALSE}
sport <- ELSA_ds_w1
save(sport, file = "../RData/w1/sport.RData")
rm(sport)

sport <- ELSA_ds_w2
save(sport, file = "../RData/w2/sport.RData")
rm(sport)

sport <- ELSA_ds_w3
save(sport, file = "../RData/w3/sport.RData")
rm(sport)

sport <- ELSA_ds_w4
save(sport, file = "../RData/w4/sport.RData")
rm(sport)

sport <- ELSA_ds_w5
save(sport, file = "../RData/w5/sport.RData")
rm(sport)

sport <- ELSA_ds_w6
save(sport, file = "../RData/w6/sport.RData")
rm(sport)

sport <- ELSA_ds_w7
save(sport, file = "../RData/w7/sport.RData")
rm(sport)

```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
 
