---
title: "Sport Activities"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/sportDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/sportDS.R')
```

<!-- ########################################################## --> 


# Data process

## England



### Wave 1

#### Study-specific variable description



| **Name** | `scorg7`|
|-|-|
| **Label** | `Sports clubs, gyms, exercise classes`|
| **Table name** |`wave_1_core_data_v3`|
| **Categories** |`0 = No`<br/>`1 = Yes`|
| **Missings** |`-9 = Not answered`<br/>`-1 = Item not applicable`|
| **Description** |  |


```{r assign1, echo=F}
opal.assign.table.tibble(o, 'ELSA_w1_sport','ELSA.wave_1_core_data_v3', variables=list('scorg7'), missings = TRUE)
ELSA_w1_sport <- opal.execute(o,'ELSA_w1_sport')
```

```{r local1, echo=F}
vari <- ELSA_w1_sport$scorg7
kable(Categorical_summary(vari, missing_values = c(-1,-9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-9))[2], caption = "Type of missing")

ggplot(ELSA_w1_sport, aes(x=factor(scorg7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sports clubs, gyms, exercise classes") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1, 0 into 0`
* `-1 into 996`
* `-9 into 995`
* `NA into 999`

 **R script:**

```{r harmo1, echo=TRUE}
ELSA_ds_w1 <- tibble(id=ELSA_w1_sport$id)
ELSA_ds_w1$sport <- car::recode(as.vector(ELSA_w1_sport$scorg7), "0='0'; 1='1'; -1='996'; -9='995'; NA='999'")
ELSA_ds_w1$sport <- labelled(ELSA_ds_w1$sport, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995, "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <- ELSA_ds_w1$sport
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3],caption = ds_label)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ELSA_ds_w1, aes(x=factor(sport))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sport activities") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(ELSA_ds_w1$sport)
BeforeH <- table(ELSA_w1_sport$scorg7, useNA='ifany')[c(3,4,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","-9->995","-1->996")
kable(C)
```

 
 



### Wave 2

#### Study-specific variable description



| **Name** | `scorg07`|
|-|-|
| **Label** | `Organisational membership: member of a sports clubs, gym, or exercise class`|
| **Table name** |`wave_2_core_data_v4`|
| **Categories** |`0 = No`<br/>`1 = Yes`|
| **Missings** |`-9 = Not answered`<br/>`-1 = Item not applicable`|
| **Description** |  |

 
```{r assign2, echo=F}
opal.assign.table.tibble(o, 'ELSA_w2_sport','ELSA.wave_2_core_data_v4',variables=list('scorg07'), missings = TRUE)
ELSA_w2_sport <- opal.execute(o,'ELSA_w2_sport')
```

```{r local2, echo=F}
vari <-  ELSA_w2_sport$scorg07
kable(Categorical_summary(vari, missing_values = c(-1,-9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-9))[2], caption = "Type of missing")

ggplot(ELSA_w2_sport, aes(x=factor(scorg07))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sports clubs, gyms, exercise classes") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1, 0 into 0`
* `-1 into 996`
* `-9 into 995`
* `NA into 999`

 **R script:**

```{r harmo2, echo=TRUE}
ELSA_ds_w2 <- tibble(id=ELSA_w2_sport$id)
ELSA_ds_w2$sport <- car::recode(as.vector(ELSA_w2_sport$scorg07), "0='0'; 1='1'; -1='996'; -9='995'; NA='999'")
ELSA_ds_w2$sport <- labelled(ELSA_ds_w2$sport, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995, "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}
vari <- ELSA_ds_w2$sport
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3],caption = ds_label)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ELSA_ds_w2, aes(x=factor(sport))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sport activities") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
AfterH <- table(ELSA_ds_w2$sport)
BeforeH <- table(ELSA_w2_sport$scorg07, useNA='ifany')[c(3,4,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","-9->995","-1->996")
kable(C)
```

 
 



### Wave 3

#### Study-specific variable description



| **Name** | `scorg07`|
|-|-|
| **Label** | `Respondent is a member of a sports clubs, gym, or exercise class`|
| **Table name** |`wave_3_elsa_data_v4`|
| **Categories** |`0 = No`<br/>`1 = Yes`|
| **Missings** |`-9 = Not answered`<br/>`-8 = Don't know`<br/>`-1 = Item not applicable`|
| **Description** |  |


```{r assign3, echo=F}
opal.assign.table.tibble(o, 'ELSA_w3_sport','ELSA.wave_3_elsa_data_v4',variables=list('scorg07'), missings = TRUE)
ELSA_w3_sport <- opal.execute(o,'ELSA_w3_sport')
```

```{r local3, echo=F}
vari <-  ELSA_w3_sport$scorg07
kable(Categorical_summary(vari, missing_values = c(-1,-8,-9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-8,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-8,-9))[2], caption = "Type of missing")

ggplot(ELSA_w3_sport, aes(x=factor(scorg07))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sports clubs, gyms, exercise classes") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1, 0 into 0`
* `-1 into 996`
* `-8 into 998`
* `-9 into 995`
* `NA into 999`

 **R script:**

```{r harmo3, echo=TRUE}
ELSA_ds_w3 <- tibble(id=ELSA_w3_sport$id)
ELSA_ds_w3$sport <- car::recode(as.vector(ELSA_w3_sport$scorg07), "0='0'; 1='1'; -1='996'; -8='998'; -9='995'; NA='999'")
ELSA_ds_w3$sport <- labelled(ELSA_ds_w3$sport, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995, "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=F}
vari <- ELSA_ds_w3$sport
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3],caption = ds_label)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ELSA_ds_w3, aes(x=factor(sport))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sport activities") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=F}
AfterH <- table(ELSA_ds_w3$sport)
BeforeH <- table(ELSA_w3_sport$scorg07, useNA='ifany')[c(3,4,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","-9->995","-1->996")
kable(C)
```

 
 



### Wave 4

#### Study-specific variable description



| **Name** | `scorg07`|
|-|-|
| **Label** | `Respondent is a member of a sports clubs, gym, or exercise class`|
| **Table name** |`wave_4_elsa_data_v3`|
| **Categories** |`0 = No`<br/>`1 = Yes`|
| **Missings** |`-9 = Not answered`<br/>`-8 = Don't know`<br/>`-1 = Item not applicable`|
| **Description** |  |


```{r assign4, echo=F}
opal.assign.table.tibble(o, 'ELSA_w4_sport','ELSA.wave_4_elsa_data_v3', variables=list('scorg07'), missings = TRUE)
ELSA_w4_sport <- opal.execute(o,'ELSA_w4_sport')
```

```{r local4, echo=F}
vari <-  ELSA_w4_sport$scorg07
kable(Categorical_summary(vari, missing_values = c(-1,-8,-9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-8,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-8,-9))[2], caption = "Type of missing")

ggplot(ELSA_w4_sport, aes(x=factor(scorg07))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sports clubs, gyms, exercise classes") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1, 0 into 0`
* `-1 into 996`
* `-8 into 998`
* `-9 into 995`
* `NA into 999`

 **R script:**

```{r harmo4, echo=TRUE}
ELSA_ds_w4 <- tibble(id=ELSA_w4_sport$id)
ELSA_ds_w4$sport <- car::recode(as.vector(ELSA_w4_sport$scorg07), "0='0'; 1='1'; -1='996'; -8='998'; -9='995'; NA='999'")
ELSA_ds_w4$sport <- labelled(ELSA_ds_w4$sport, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995, "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4, echo=F}
vari <- ELSA_ds_w4$sport
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3],caption = ds_label)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ELSA_ds_w4, aes(x=factor(sport))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sport activities") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=F}
AfterH <- table(ELSA_ds_w4$sport)
BeforeH <- table(ELSA_w4_sport$scorg07, useNA='ifany')[c(3,4,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","-9->995","-1->996")
kable(C)
```

 
 



### Wave 5

#### Study-specific variable description



| **Name** | `scorg07`|
|-|-|
| **Label** | `Respondent is a member of a sports clubs, gym, or exercise class`|
| **Table name** |`wave_5_elsa_data_v4`|
| **Categories** |`0 = No`<br/>`1 = Yes`|
| **Missings** |`-9 = Not answered`<br/>`-8 = Don't know`<br/>`-2 = Schedule Not Applicable`<br/>`-1 = Item not applicable`|
| **Description** |  |


```{r assign5, echo=F}
opal.assign.table.tibble(o, 'ELSA_w5_sport','ELSA.wave_5_elsa_data_v4',variables=list('scorg07'), missings = TRUE)
ELSA_w5_sport <- opal.execute(o,'ELSA_w5_sport')
```

```{r local5, echo=F}
vari <-  ELSA_w5_sport$scorg07
kable(Categorical_summary(vari, missing_values = c(-1,-2,-8,-9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-2,-8,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2,-8,-9))[2], caption = "Type of missing")

ggplot(ELSA_w5_sport, aes(x=factor(scorg07))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sports clubs, gyms, exercise classes") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1, 0 into 0`
* `-1 or -2 into 996`
* `-8 into 998`
* `-9 into 995`
* `NA into 999`

 **R script:**

```{r harmo5, echo=TRUE}
ELSA_ds_w5 <- tibble(id=ELSA_w5_sport$id)
ELSA_ds_w5$sport <- car::recode(as.vector(ELSA_w5_sport$scorg07), "0='0'; 1='1'; -1='996'; -2='996'; -8='998'; -9='995'; NA='999'")
ELSA_ds_w5$sport <- labelled(ELSA_ds_w5$sport, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995, "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript5, echo=F}
vari <- ELSA_ds_w5$sport
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3],caption = ds_label)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ELSA_ds_w5, aes(x=factor(sport))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sport activities") + ylab("Frequency")
```

#### Validation
```{r crosstabulation5, echo=F}
AfterH <- table(ELSA_ds_w5$sport)
BeforeH <- table(ELSA_w5_sport$scorg07, useNA='ifany')[c(3,4,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","-9->995","-2->996")
kable(C)
```

 
 



### Wave 6

#### Study-specific variable description



| **Name** | `scorg07`|
|-|-|
| **Label** | `Respondent is a member of a sports clubs, gym, or exercise class`|
| **Table name** |`wave_6_elsa_data_v2`|
| **Categories** |`0 = No`<br/>`1 = Yes`|
| **Missings** |`-9 = Not answered`<br/>`-8 = Don't know`<br/>`-2 = Schedule Not Applicable`<br/>`-1 = Item not applicable`|
| **Description** |  |


```{r assign6, echo=F}
opal.assign.table.tibble(o, 'ELSA_w6_sport','ELSA.wave_6_elsa_data_v2', variables=list('scorg07'), missings = TRUE)
ELSA_w6_sport <- opal.execute(o,'ELSA_w6_sport')
```

```{r local6, echo=F}
vari <-  ELSA_w6_sport$scorg07
kable(Categorical_summary(vari, missing_values = c(-1,-2,-8,-9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-2,-8,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2,-8,-9))[2], caption = "Type of missing")

ggplot(ELSA_w6_sport, aes(x=factor(scorg07))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sports clubs, gyms, exercise classes") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1, 0 into 0`
* `-1 or -2 into 996`
* `-8 into 998`
* `-9 into 995`
* `NA into 999`

 **R script:**

```{r harmo6, echo=TRUE}
ELSA_ds_w6 <- tibble(id=ELSA_w6_sport$id)
ELSA_ds_w6$sport <- car::recode(as.vector(ELSA_w6_sport$scorg07), "0='0'; 1='1'; -1='996'; -2='996'; -8='998'; -9='995'; NA='999'")
ELSA_ds_w6$sport <- labelled(ELSA_ds_w6$sport, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995, "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript6, echo=F}
vari <- ELSA_ds_w6$sport
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3],caption = ds_label)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ELSA_ds_w6, aes(x=factor(sport))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sport activities") + ylab("Frequency")
```

#### Validation
```{r crosstabulation6, echo=F}
AfterH <- table(ELSA_ds_w6$sport)
BeforeH <- table(ELSA_w6_sport$scorg07, useNA='ifany')[c(3,4,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","-9->995","-2->996")
kable(C)
```

 
 



### Wave 7

#### Study-specific variable description



| **Name** | `scorg07`|
|-|-|
| **Label** | `Respondent is a member of a sports clubs, gym, or exercise class`|
| **Table name** |`wave_7_elsa_data`|
| **Categories** |`0 = No`<br/>`1 = Yes`|
| **Missings** |`-9 = Not answered`<br/>`-8 = Don't know`<br/>`-2 = Schedule Not Applicable`<br/>`-1 = Item not applicable`|
| **Description** |  |


```{r assign7, echo=F}
opal.assign.table.tibble(o, 'ELSA_w7_sport','ELSA.wave_7_elsa_data', variables=list('scorg07'), missings = TRUE)
ELSA_w7_sport <- opal.execute(o,'ELSA_w7_sport')
```

```{r local7, echo=F}
vari <-  ELSA_w7_sport$scorg07
kable(Categorical_summary(vari, missing_values = c(-1,-2,-8,-9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-2,-8,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2,-8,-9))[2], caption = "Type of missing")

ggplot(ELSA_w7_sport, aes(x=factor(scorg07))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sports clubs, gyms, exercise classes") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1, 0 into 0`
* `-1 or -2 into 996`
* `-8 into 998`
* `-9 into 995`
* `NA into 999`

 **R script:**

```{r harmo7, echo=TRUE}
ELSA_ds_w7 <- tibble(id=ELSA_w7_sport$id)
ELSA_ds_w7$sport <- car::recode(as.vector(ELSA_w7_sport$scorg07), "0='0'; 1='1'; -1='996'; -2='996'; -8='998'; -9='995'; NA='999'")
ELSA_ds_w7$sport <- labelled(ELSA_ds_w7$sport, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995, "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript7, echo=F}
vari <- ELSA_ds_w7$sport
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3],caption = ds_label)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")

ggplot(ELSA_ds_w7, aes(x=factor(sport))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sport activities") + ylab("Frequency")
```

#### Validation
```{r crosstabulation7, echo=F}
AfterH <- table(ELSA_ds_w7$sport)
BeforeH <- table(ELSA_w7_sport$scorg07, useNA='ifany')[c(3,4,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","-9->995","-2->996")
kable(C)
```


## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.




```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```



```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


elsa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"), w6 = c("w6","W6"), w7 = c("w7","W7"))

# Consider only harmonised waves
l.hds <- lapply(elsa.cw, function(wname) if(exists(paste0("ELSA_ds_",wname[1]))){wname = list(get(paste0("ELSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```




# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
 
