---
title: "Participation in club groups"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/part_clubsDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/part_clubsDS.R')
```




# Data process


## England

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised are:

* Name: `scorg1`
* Label: `Are you a member of: Political party, trade union or environmental groups`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-1 = Item not applicable`
    
* Name: `scorga2`
* Label: `Tenants groups, resident groups, neighbourhoold watch`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-1 = Item not applicable`
    
* Name: `scorg3`
* Label: `Church or other religious groups`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-1 = Item not applicable`
    
* Name: `scorg4`
* Label: `Charitable associations`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-1 = Item not applicable`
    
* Name: `scorg5`
* Label: `Education, art or music groups or evening classes`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-1 = Item not applicable`
    
* Name: `scorg6`
* Label: `Social club`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-1 = Item not applicable`
    
* Name: `scorg7`
* Label: `Sports clubs, gym, exercise classes`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-1 = Item not applicable`
    
* Name: `scorg8`
* Label: `Any other organisations, club or societies`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-1 = Item not applicable`
    
* Name: `scorg9`
* Label: `No, I am not a member of any organisations, clubs or societies`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-1 = Item not applicable`
    
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'ELSA_w1_part_clubs','ELSA.wave_1_core_data_v3', 
                        variables=list('scorg1','scorga2','scorg3','scorg4','scorg5','scorg6',
                                       'scorg7','scorg8','scorg9'), missings = TRUE)
```

```{r local1, echo=F}
ELSA_w1_part_clubs <- opal.execute(o,'ELSA_w1_part_clubs')
Categorical_summary(var = ELSA_w1_part_clubs$scorg1, missing_values = NA)
ggplot(ELSA_w1_part_clubs, aes(x=factor(scorg1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are you a member of: Political party, trade union or environmental groups?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any of scorg1-scorg8 equals 1 then 1`
* `if scorg9=1 or all of scorg1-scorg8 are equal 0 then 0`
* `-1 into 996`
* `-9 into 995`
* `NA into 999`

**R script:**

```{r harmo1}
ELSA_ds_w1 <- tibble(id=ELSA_w1_part_clubs$id)

ELSA_w1_part_clubs$scorg1 <- car::recode(as.vector(ELSA_w1_part_clubs$scorg1), "NA='-999'")
ELSA_w1_part_clubs$scorga2 <- car::recode(as.vector(ELSA_w1_part_clubs$scorga2), "NA='-999'")
ELSA_w1_part_clubs$scorg3 <- car::recode(as.vector(ELSA_w1_part_clubs$scorg3), "NA='-999'")
ELSA_w1_part_clubs$scorg4 <- car::recode(as.vector(ELSA_w1_part_clubs$scorg4), "NA='-999'")
ELSA_w1_part_clubs$scorg5 <- car::recode(as.vector(ELSA_w1_part_clubs$scorg5), "NA='-999'")
ELSA_w1_part_clubs$scorg6 <- car::recode(as.vector(ELSA_w1_part_clubs$scorg6), "NA='-999'")
ELSA_w1_part_clubs$scorg7 <- car::recode(as.vector(ELSA_w1_part_clubs$scorg7), "NA='-999'")
ELSA_w1_part_clubs$scorg8 <- car::recode(as.vector(ELSA_w1_part_clubs$scorg8), "NA='-999'")
ELSA_w1_part_clubs$scorg9 <- car::recode(as.vector(ELSA_w1_part_clubs$scorg9), "NA='-999'")

ELSA_ds_w1$part_clubs <- c(NA)
for(i in 1:dim(ELSA_w1_part_clubs)[1]){
  if( ELSA_w1_part_clubs$scorg1[i] == 1 | ELSA_w1_part_clubs$scorga2[i] == 1 | ELSA_w1_part_clubs$scorg3[i] == 1 | 
      ELSA_w1_part_clubs$scorg4[i] == 1 | ELSA_w1_part_clubs$scorg5[i] == 1 | ELSA_w1_part_clubs$scorg6[i] == 1 | 
      ELSA_w1_part_clubs$scorg7[i] == 1 | ELSA_w1_part_clubs$scorg8[i] == 1 ) { 
    ELSA_ds_w1$part_clubs[i] = 1 }
  else if( ELSA_w1_part_clubs$scorg9[i] == 1 | ( ELSA_w1_part_clubs$scorg1[i] == 0 & ELSA_w1_part_clubs$scorga2[i] == 0 & 
           ELSA_w1_part_clubs$scorg3[i] == 0 & ELSA_w1_part_clubs$scorg4[i] == 0 & ELSA_w1_part_clubs$scorg5[i] == 0 & 
           ELSA_w1_part_clubs$scorg6[i] == 0 & ELSA_w1_part_clubs$scorg7[i] == 0 & ELSA_w1_part_clubs$scorg8[i] == 0 ) ) { 
    ELSA_ds_w1$part_clubs[i] = 0 }
  else if( ELSA_w1_part_clubs$scorg1[i] == -1 | ELSA_w1_part_clubs$scorga2[i] == -1 | ELSA_w1_part_clubs$scorg3[i] == -1 | 
      ELSA_w1_part_clubs$scorg4[i] == -1 | ELSA_w1_part_clubs$scorg5[i] == -1 | ELSA_w1_part_clubs$scorg6[i] == -1 | 
      ELSA_w1_part_clubs$scorg7[i] == -1 | ELSA_w1_part_clubs$scorg8[i] == -1 | ELSA_w1_part_clubs$scorg9[i] == -1 ) { 
    ELSA_ds_w1$part_clubs[i] = 996 }
  else if( ELSA_w1_part_clubs$scorg1[i] == -9 | ELSA_w1_part_clubs$scorga2[i] == -9 | ELSA_w1_part_clubs$scorg3[i] == -9 | 
      ELSA_w1_part_clubs$scorg4[i] == -9 | ELSA_w1_part_clubs$scorg5[i] == -9 | ELSA_w1_part_clubs$scorg6[i] == -9 | 
      ELSA_w1_part_clubs$scorg7[i] == -9 | ELSA_w1_part_clubs$scorg8[i] == -9 | ELSA_w1_part_clubs$scorg9[i] == -9 ) { 
    ELSA_ds_w1$part_clubs[i] = 995 }
}

ELSA_ds_w1$part_clubs <- car::recode(as.vector(ELSA_ds_w1$part_clubs), "NA='999'")
ELSA_ds_w1$part_clubs <- labelled(ELSA_ds_w1$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995, "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
Categorical_summary(var = ELSA_ds_w1$part_clubs, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w1, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}

```


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scorg01`
* Label: `Are you a member of: Political party, trade union or environmental groups`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-1 = Item not applicable`
    
* Name: `scorg02`
* Label: `Tenants groups, resident groups, neighbourhoold watch`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-1 = Item not applicable`
    
* Name: `scorg03`
* Label: `Church or other religious groups`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-1 = Item not applicable`
    
* Name: `scorg04`
* Label: `Charitable associations`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-1 = Item not applicable`
    
* Name: `scorg05`
* Label: `Education, art or music groups or evening classes`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-1 = Item not applicable`
    
* Name: `scorg06`
* Label: `Social club`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-1 = Item not applicable`
    
* Name: `scorg07`
* Label: `Sports clubs, gym, exercise classes`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-1 = Item not applicable`
    
* Name: `scorg08`
* Label: `Any other organisations, club or societies`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-1 = Item not applicable`
    
* Name: `scorg09`
* Label: `No, I am not a member of any organisations, clubs or societies`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-1 = Item not applicable`
    
```{r assign2, echo=F}
opal.assign.table.tibble(o, 'ELSA_w2_part_clubs','ELSA.wave_2_core_data_v4', 
                        variables=list('scorg01','scorg02','scorg03','scorg04','scorg05','scorg06',
                                       'scorg07','scorg08','scorg09'), missings = TRUE)
```

```{r local2, echo=F}
ELSA_w2_part_clubs <- opal.execute(o,'ELSA_w2_part_clubs')
Categorical_summary(var = ELSA_w2_part_clubs$scorg01, missing_values = NA)
ggplot(ELSA_w2_part_clubs, aes(x=factor(scorg01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are you a member of: Political party, trade union or environmental groups?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any of scorg01-scorg08 equals 1 then 1`
* `if scorg09=1 or all of scorg01-scorg08 are equal 0 then 0`
* `-1 into 996`
* `-9 into 995`
* `NA into 999`

**R script:**

```{r harmo2}
ELSA_ds_w2 <- tibble(id=ELSA_w2_part_clubs$id)

ELSA_w2_part_clubs$scorg01 <- car::recode(as.vector(ELSA_w2_part_clubs$scorg01), "NA='-999'")
ELSA_w2_part_clubs$scorg02 <- car::recode(as.vector(ELSA_w2_part_clubs$scorg02), "NA='-999'")
ELSA_w2_part_clubs$scorg03 <- car::recode(as.vector(ELSA_w2_part_clubs$scorg03), "NA='-999'")
ELSA_w2_part_clubs$scorg04 <- car::recode(as.vector(ELSA_w2_part_clubs$scorg04), "NA='-999'")
ELSA_w2_part_clubs$scorg05 <- car::recode(as.vector(ELSA_w2_part_clubs$scorg05), "NA='-999'")
ELSA_w2_part_clubs$scorg06 <- car::recode(as.vector(ELSA_w2_part_clubs$scorg06), "NA='-999'")
ELSA_w2_part_clubs$scorg07 <- car::recode(as.vector(ELSA_w2_part_clubs$scorg07), "NA='-999'")
ELSA_w2_part_clubs$scorg08 <- car::recode(as.vector(ELSA_w2_part_clubs$scorg08), "NA='-999'")
ELSA_w2_part_clubs$scorg09 <- car::recode(as.vector(ELSA_w2_part_clubs$scorg09), "NA='-999'")

ELSA_ds_w2$part_clubs <- c(NA)
for(i in 1:dim(ELSA_w2_part_clubs)[1]){
  if( ELSA_w2_part_clubs$scorg01[i] == 1 | ELSA_w2_part_clubs$scorg02[i] == 1 | ELSA_w2_part_clubs$scorg03[i] == 1 | 
      ELSA_w2_part_clubs$scorg04[i] == 1 | ELSA_w2_part_clubs$scorg05[i] == 1 | ELSA_w2_part_clubs$scorg06[i] == 1 | 
      ELSA_w2_part_clubs$scorg07[i] == 1 | ELSA_w2_part_clubs$scorg08[i] == 1 ) { 
    ELSA_ds_w2$part_clubs[i] = 1 }
  else if( ELSA_w2_part_clubs$scorg09[i] == 1 | ( ELSA_w2_part_clubs$scorg01[i] == 0 & ELSA_w2_part_clubs$scorg02[i] == 0 & 
           ELSA_w2_part_clubs$scorg03[i] == 0 & ELSA_w2_part_clubs$scorg04[i] == 0 & ELSA_w2_part_clubs$scorg05[i] == 0 & 
           ELSA_w2_part_clubs$scorg06[i] == 0 & ELSA_w2_part_clubs$scorg07[i] == 0 & ELSA_w2_part_clubs$scorg08[i] == 0 ) ) { 
    ELSA_ds_w2$part_clubs[i] = 0 }
  else if( ELSA_w2_part_clubs$scorg01[i] == -1 | ELSA_w2_part_clubs$scorg02[i] == -1 | ELSA_w2_part_clubs$scorg03[i] == -1 | 
      ELSA_w2_part_clubs$scorg04[i] == -1 | ELSA_w2_part_clubs$scorg05[i] == -1 | ELSA_w2_part_clubs$scorg06[i] == -1 | 
      ELSA_w2_part_clubs$scorg07[i] == -1 | ELSA_w2_part_clubs$scorg08[i] == -1 | ELSA_w2_part_clubs$scorg09[i] == -1 ) { 
    ELSA_ds_w2$part_clubs[i] = 996 }
  else if( ELSA_w2_part_clubs$scorg01[i] == -9 | ELSA_w2_part_clubs$scorg02[i] == -9 | ELSA_w2_part_clubs$scorg03[i] == -9 | 
      ELSA_w2_part_clubs$scorg04[i] == -9 | ELSA_w2_part_clubs$scorg05[i] == -9 | ELSA_w2_part_clubs$scorg06[i] == -9 | 
      ELSA_w2_part_clubs$scorg07[i] == -9 | ELSA_w2_part_clubs$scorg08[i] == -9 | ELSA_w2_part_clubs$scorg09[i] == -9 ) { 
    ELSA_ds_w2$part_clubs[i] = 995 }
}

ELSA_ds_w2$part_clubs <- car::recode(as.vector(ELSA_ds_w2$part_clubs), "NA='999'")
ELSA_ds_w2$part_clubs <- labelled(ELSA_ds_w2$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995, "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
Categorical_summary(var = ELSA_ds_w2$part_clubs, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w2, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}

```




### Wave 3

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scorg01`
* Label: `Are you a member of: Political party, trade union or environmental groups`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-1 = Item not applicable`
    
* Name: `scorg02`
* Label: `Tenants groups, resident groups, neighbourhoold watch`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-1 = Item not applicable`
    
* Name: `scorg03`
* Label: `Church or other religious groups`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-1 = Item not applicable`
    
  * Name: `scorg04`
* Label: `Charitable associations`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-1 = Item not applicable`
    
* Name: `scorg05`
* Label: `Education, art or music groups or evening classes`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-1 = Item not applicable`
    
* Name: `scorg06`
* Label: `Social club`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-1 = Item not applicable`
    
* Name: `scorg07`
* Label: `Sports clubs, gym, exercise classes`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-1 = Item not applicable`
    
* Name: `scorg08`
* Label: `Any other organisations, club or societies`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-1 = Item not applicable`
    
* Name: `scorg09`
* Label: `No, I am not a member of any organisations, clubs or societies`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-1 = Item not applicable`
    
```{r assign3, echo=F}
opal.assign.table.tibble(o, 'ELSA_w3_part_clubs','ELSA.wave_3_elsa_data_v4', 
                        variables=list('scorg01','scorg02','scorg03','scorg04','scorg05','scorg06',
                                       'scorg07','scorg08','scorg09'), missings = TRUE)
```

```{r local3, echo=F}
ELSA_w3_part_clubs <- opal.execute(o,'ELSA_w3_part_clubs')
Categorical_summary(var = ELSA_w3_part_clubs$scorg01, missing_values = NA)
ggplot(ELSA_w3_part_clubs, aes(x=factor(scorg01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are you a member of: Political party, trade union or environmental groups?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any of scorg01-scorg08 equals 1 then 1`
* `if scorg09=1 or all of scorg01-scorg08 are equal 0 then 0`
* `-1 into 996`
* `-8 into 998`
* `-9 into 995`
* `NA into 999`

**R script:**

```{r harmo3}
ELSA_ds_w3 <- tibble(id=ELSA_w3_part_clubs$id)

ELSA_w3_part_clubs$scorg01 <- car::recode(as.vector(ELSA_w3_part_clubs$scorg01), "NA='-999'")
ELSA_w3_part_clubs$scorg02 <- car::recode(as.vector(ELSA_w3_part_clubs$scorg02), "NA='-999'")
ELSA_w3_part_clubs$scorg03 <- car::recode(as.vector(ELSA_w3_part_clubs$scorg03), "NA='-999'")
ELSA_w3_part_clubs$scorg04 <- car::recode(as.vector(ELSA_w3_part_clubs$scorg04), "NA='-999'")
ELSA_w3_part_clubs$scorg05 <- car::recode(as.vector(ELSA_w3_part_clubs$scorg05), "NA='-999'")
ELSA_w3_part_clubs$scorg06 <- car::recode(as.vector(ELSA_w3_part_clubs$scorg06), "NA='-999'")
ELSA_w3_part_clubs$scorg07 <- car::recode(as.vector(ELSA_w3_part_clubs$scorg07), "NA='-999'")
ELSA_w3_part_clubs$scorg08 <- car::recode(as.vector(ELSA_w3_part_clubs$scorg08), "NA='-999'")
ELSA_w3_part_clubs$scorg09 <- car::recode(as.vector(ELSA_w3_part_clubs$scorg09), "NA='-999'")

ELSA_ds_w3$part_clubs <- c(NA)
for(i in 1:dim(ELSA_w3_part_clubs)[1]){
  if( ELSA_w3_part_clubs$scorg01[i] == 1 | ELSA_w3_part_clubs$scorg02[i] == 1 | ELSA_w3_part_clubs$scorg03[i] == 1 | 
      ELSA_w3_part_clubs$scorg04[i] == 1 | ELSA_w3_part_clubs$scorg05[i] == 1 | ELSA_w3_part_clubs$scorg06[i] == 1 | 
      ELSA_w3_part_clubs$scorg07[i] == 1 | ELSA_w3_part_clubs$scorg08[i] == 1 ) { 
    ELSA_ds_w3$part_clubs[i] = 1 }
  else if( ELSA_w3_part_clubs$scorg09[i] == 1 | ( ELSA_w3_part_clubs$scorg01[i] == 0 & ELSA_w3_part_clubs$scorg02[i] == 0 & 
           ELSA_w3_part_clubs$scorg03[i] == 0 & ELSA_w3_part_clubs$scorg04[i] == 0 & ELSA_w3_part_clubs$scorg05[i] == 0 & 
           ELSA_w3_part_clubs$scorg06[i] == 0 & ELSA_w3_part_clubs$scorg07[i] == 0 & ELSA_w3_part_clubs$scorg08[i] == 0 ) ) { 
    ELSA_ds_w3$part_clubs[i] = 0 }
  else if( ELSA_w3_part_clubs$scorg01[i] == -1 | ELSA_w3_part_clubs$scorg02[i] == -1 | ELSA_w3_part_clubs$scorg03[i] == -1 | 
      ELSA_w3_part_clubs$scorg04[i] == -1 | ELSA_w3_part_clubs$scorg05[i] == -1 | ELSA_w3_part_clubs$scorg06[i] == -1 | 
      ELSA_w3_part_clubs$scorg07[i] == -1 | ELSA_w3_part_clubs$scorg08[i] == -1 | ELSA_w3_part_clubs$scorg09[i] == -1 ) { 
    ELSA_ds_w3$part_clubs[i] = 996 }
  else if( ELSA_w3_part_clubs$scorg01[i] == -8 | ELSA_w3_part_clubs$scorg02[i] == -8 | ELSA_w3_part_clubs$scorg03[i] == -8 | 
      ELSA_w3_part_clubs$scorg04[i] == -8 | ELSA_w3_part_clubs$scorg05[i] == -8 | ELSA_w3_part_clubs$scorg06[i] == -8 | 
      ELSA_w3_part_clubs$scorg07[i] == -8 | ELSA_w3_part_clubs$scorg08[i] == -8 | ELSA_w3_part_clubs$scorg09[i] == -8 ) { 
    ELSA_ds_w3$part_clubs[i] = 998 }
  else if( ELSA_w3_part_clubs$scorg01[i] == -9 | ELSA_w3_part_clubs$scorg02[i] == -9 | ELSA_w3_part_clubs$scorg03[i] == -9 | 
      ELSA_w3_part_clubs$scorg04[i] == -9 | ELSA_w3_part_clubs$scorg05[i] == -9 | ELSA_w3_part_clubs$scorg06[i] == -9 | 
      ELSA_w3_part_clubs$scorg07[i] == -9 | ELSA_w3_part_clubs$scorg08[i] == -9 | ELSA_w3_part_clubs$scorg09[i] == -9 ) { 
    ELSA_ds_w3$part_clubs[i] = 995 }
}

ELSA_ds_w3$part_clubs <- car::recode(as.vector(ELSA_ds_w3$part_clubs), "NA='999'")
ELSA_ds_w3$part_clubs <- labelled(ELSA_ds_w3$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995, "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}
Categorical_summary(var = ELSA_ds_w3$part_clubs, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w3, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=F}

```




### Wave 4

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scorg01`
* Label: `Are you a member of: Political party, trade union or environmental groups`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-1 = Item not applicable`
    
* Name: `scorg02`
* Label: `Tenants groups, resident groups, neighbourhoold watch`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-1 = Item not applicable`
    
* Name: `scorg03`
* Label: `Church or other religious groups`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-1 = Item not applicable`
    
  * Name: `scorg04`
* Label: `Charitable associations`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-1 = Item not applicable`
    
* Name: `scorg05`
* Label: `Education, art or music groups or evening classes`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-1 = Item not applicable`
    
* Name: `scorg06`
* Label: `Social club`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-1 = Item not applicable`
    
* Name: `scorg07`
* Label: `Sports clubs, gym, exercise classes`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-1 = Item not applicable`
    
* Name: `scorg08`
* Label: `Any other organisations, club or societies`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-1 = Item not applicable`
    
* Name: `scorg09`
* Label: `No, I am not a member of any organisations, clubs or societies`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-1 = Item not applicable`
    
```{r assign4, echo=F}
opal.assign.table.tibble(o, 'ELSA_w4_part_clubs','ELSA.wave_4_elsa_data_v3', 
                        variables=list('scorg01','scorg02','scorg03','scorg04','scorg05','scorg06',
                                       'scorg07','scorg08','scorg09'), missings = TRUE)
```

```{r local4, echo=F}
ELSA_w4_part_clubs <- opal.execute(o,'ELSA_w4_part_clubs')
Categorical_summary(var = ELSA_w4_part_clubs$scorg01, missing_values = NA)
ggplot(ELSA_w4_part_clubs, aes(x=factor(scorg01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are you a member of: Political party, trade union or environmental groups?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any of scorg01-scorg08 equals 1 then 1`
* `if scorg09=1 or all of scorg01-scorg08 are equal 0 then 0`
* `-1 into 996`
* `-8 into 998`
* `-9 into 995`
* `NA into 999`

**R script:**

```{r harmo4}
ELSA_ds_w4 <- tibble(id=ELSA_w4_part_clubs$id)

ELSA_w4_part_clubs$scorg01 <- car::recode(as.vector(ELSA_w4_part_clubs$scorg01), "NA='-999'")
ELSA_w4_part_clubs$scorg02 <- car::recode(as.vector(ELSA_w4_part_clubs$scorg02), "NA='-999'")
ELSA_w4_part_clubs$scorg03 <- car::recode(as.vector(ELSA_w4_part_clubs$scorg03), "NA='-999'")
ELSA_w4_part_clubs$scorg04 <- car::recode(as.vector(ELSA_w4_part_clubs$scorg04), "NA='-999'")
ELSA_w4_part_clubs$scorg05 <- car::recode(as.vector(ELSA_w4_part_clubs$scorg05), "NA='-999'")
ELSA_w4_part_clubs$scorg06 <- car::recode(as.vector(ELSA_w4_part_clubs$scorg06), "NA='-999'")
ELSA_w4_part_clubs$scorg07 <- car::recode(as.vector(ELSA_w4_part_clubs$scorg07), "NA='-999'")
ELSA_w4_part_clubs$scorg08 <- car::recode(as.vector(ELSA_w4_part_clubs$scorg08), "NA='-999'")
ELSA_w4_part_clubs$scorg09 <- car::recode(as.vector(ELSA_w4_part_clubs$scorg09), "NA='-999'")

ELSA_ds_w4$part_clubs <- c(NA)
for(i in 1:dim(ELSA_w4_part_clubs)[1]){
  if( ELSA_w4_part_clubs$scorg01[i] == 1 | ELSA_w4_part_clubs$scorg02[i] == 1 | ELSA_w4_part_clubs$scorg03[i] == 1 | 
      ELSA_w4_part_clubs$scorg04[i] == 1 | ELSA_w4_part_clubs$scorg05[i] == 1 | ELSA_w4_part_clubs$scorg06[i] == 1 | 
      ELSA_w4_part_clubs$scorg07[i] == 1 | ELSA_w4_part_clubs$scorg08[i] == 1 ) { 
    ELSA_ds_w4$part_clubs[i] = 1 }
  else if( ELSA_w4_part_clubs$scorg09[i] == 1 | ( ELSA_w4_part_clubs$scorg01[i] == 0 & ELSA_w4_part_clubs$scorg02[i] == 0 & 
           ELSA_w4_part_clubs$scorg03[i] == 0 & ELSA_w4_part_clubs$scorg04[i] == 0 & ELSA_w4_part_clubs$scorg05[i] == 0 & 
           ELSA_w4_part_clubs$scorg06[i] == 0 & ELSA_w4_part_clubs$scorg07[i] == 0 & ELSA_w4_part_clubs$scorg08[i] == 0 ) ) { 
    ELSA_ds_w4$part_clubs[i] = 0 }
  else if( ELSA_w4_part_clubs$scorg01[i] == -1 | ELSA_w4_part_clubs$scorg02[i] == -1 | ELSA_w4_part_clubs$scorg03[i] == -1 | 
      ELSA_w4_part_clubs$scorg04[i] == -1 | ELSA_w4_part_clubs$scorg05[i] == -1 | ELSA_w4_part_clubs$scorg06[i] == -1 | 
      ELSA_w4_part_clubs$scorg07[i] == -1 | ELSA_w4_part_clubs$scorg08[i] == -1 | ELSA_w4_part_clubs$scorg09[i] == -1 ) { 
    ELSA_ds_w4$part_clubs[i] = 996 }
  else if( ELSA_w4_part_clubs$scorg01[i] == -8 | ELSA_w4_part_clubs$scorg02[i] == -8 | ELSA_w4_part_clubs$scorg03[i] == -8 | 
      ELSA_w4_part_clubs$scorg04[i] == -8 | ELSA_w4_part_clubs$scorg05[i] == -8 | ELSA_w4_part_clubs$scorg06[i] == -8 | 
      ELSA_w4_part_clubs$scorg07[i] == -8 | ELSA_w4_part_clubs$scorg08[i] == -8 | ELSA_w4_part_clubs$scorg09[i] == -8 ) { 
    ELSA_ds_w4$part_clubs[i] = 998 }
  else if( ELSA_w4_part_clubs$scorg01[i] == -9 | ELSA_w4_part_clubs$scorg02[i] == -9 | ELSA_w4_part_clubs$scorg03[i] == -9 | 
      ELSA_w4_part_clubs$scorg04[i] == -9 | ELSA_w4_part_clubs$scorg05[i] == -9 | ELSA_w4_part_clubs$scorg06[i] == -9 | 
      ELSA_w4_part_clubs$scorg07[i] == -9 | ELSA_w4_part_clubs$scorg08[i] == -9 | ELSA_w4_part_clubs$scorg09[i] == -9 ) { 
    ELSA_ds_w4$part_clubs[i] = 995 }
}

ELSA_ds_w4$part_clubs <- car::recode(as.vector(ELSA_ds_w4$part_clubs), "NA='999'")
ELSA_ds_w4$part_clubs <- labelled(ELSA_ds_w4$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995, "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript4, echo=F}
Categorical_summary(var = ELSA_ds_w4$part_clubs, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w4, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=F}

```




### Wave 5

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scorg01`
* Label: `Are you a member of: Political party, trade union or environmental groups`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-2 = Schedule Not Applicable`
    + `-1 = Item not applicable`
    
* Name: `scorg02`
* Label: `Tenants groups, resident groups, neighbourhoold watch`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-2 = Schedule Not Applicable`
    + `-1 = Item not applicable`
    
* Name: `scorg03`
* Label: `Church or other religious groups`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-2 = Schedule Not Applicable`
    + `-1 = Item not applicable`
    
  * Name: `scorg04`
* Label: `Charitable associations`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-2 = Schedule Not Applicable`
    + `-1 = Item not applicable`
    
* Name: `scorg05`
* Label: `Education, art or music groups or evening classes`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-2 = Schedule Not Applicable`
    + `-1 = Item not applicable`
    
* Name: `scorg06`
* Label: `Social club`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-1 = Item not applicable`
    
* Name: `scorg07`
* Label: `Sports clubs, gym, exercise classes`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-2 = Schedule Not Applicable`
    + `-1 = Item not applicable`
    
* Name: `scorg08`
* Label: `Any other organisations, club or societies`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-2 = Schedule Not Applicable`
    + `-1 = Item not applicable`
    
* Name: `scorg09`
* Label: `No, I am not a member of any organisations, clubs or societies`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-2 = Schedule Not Applicable`
    + `-1 = Item not applicable`
    
```{r assign5, echo=F}
opal.assign.table.tibble(o, 'ELSA_w5_part_clubs','ELSA.wave_5_elsa_data_v4', 
                        variables=list('scorg01','scorg02','scorg03','scorg04','scorg05','scorg06',
                                       'scorg07','scorg08','scorg09'), missings = TRUE)
```

```{r local5, echo=F}
ELSA_w5_part_clubs <- opal.execute(o,'ELSA_w5_part_clubs')
Categorical_summary(var = ELSA_w5_part_clubs$scorg01, missing_values = NA)
ggplot(ELSA_w5_part_clubs, aes(x=factor(scorg01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are you a member of: Political party, trade union or environmental groups?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any of scorg01-scorg08 equals 1 then 1`
* `if scorg09=1 or all of scorg01-scorg08 are equal 0 then 0`
* `-1 or -2 into 996`
* `-8 into 998`
* `-9 into 995`
* `NA into 999`

**R script:**

```{r harmo5}
ELSA_ds_w5 <- tibble(id=ELSA_w5_part_clubs$id)

ELSA_w5_part_clubs$scorg01 <- car::recode(as.vector(ELSA_w5_part_clubs$scorg01), "NA='-999'")
ELSA_w5_part_clubs$scorg02 <- car::recode(as.vector(ELSA_w5_part_clubs$scorg02), "NA='-999'")
ELSA_w5_part_clubs$scorg03 <- car::recode(as.vector(ELSA_w5_part_clubs$scorg03), "NA='-999'")
ELSA_w5_part_clubs$scorg04 <- car::recode(as.vector(ELSA_w5_part_clubs$scorg04), "NA='-999'")
ELSA_w5_part_clubs$scorg05 <- car::recode(as.vector(ELSA_w5_part_clubs$scorg05), "NA='-999'")
ELSA_w5_part_clubs$scorg06 <- car::recode(as.vector(ELSA_w5_part_clubs$scorg06), "NA='-999'")
ELSA_w5_part_clubs$scorg07 <- car::recode(as.vector(ELSA_w5_part_clubs$scorg07), "NA='-999'")
ELSA_w5_part_clubs$scorg08 <- car::recode(as.vector(ELSA_w5_part_clubs$scorg08), "NA='-999'")
ELSA_w5_part_clubs$scorg09 <- car::recode(as.vector(ELSA_w5_part_clubs$scorg09), "NA='-999'")

ELSA_ds_w5$part_clubs <- c(NA)
for(i in 1:dim(ELSA_w5_part_clubs)[1]){
  if( ELSA_w5_part_clubs$scorg01[i] == 1 | ELSA_w5_part_clubs$scorg02[i] == 1 | ELSA_w5_part_clubs$scorg03[i] == 1 | 
      ELSA_w5_part_clubs$scorg04[i] == 1 | ELSA_w5_part_clubs$scorg05[i] == 1 | ELSA_w5_part_clubs$scorg06[i] == 1 | 
      ELSA_w5_part_clubs$scorg07[i] == 1 | ELSA_w5_part_clubs$scorg08[i] == 1 ) { 
    ELSA_ds_w5$part_clubs[i] = 1 }
  else if( ELSA_w5_part_clubs$scorg09[i] == 1 | ( ELSA_w5_part_clubs$scorg01[i] == 0 & ELSA_w5_part_clubs$scorg02[i] == 0 & 
           ELSA_w5_part_clubs$scorg03[i] == 0 & ELSA_w5_part_clubs$scorg04[i] == 0 & ELSA_w5_part_clubs$scorg05[i] == 0 & 
           ELSA_w5_part_clubs$scorg06[i] == 0 & ELSA_w5_part_clubs$scorg07[i] == 0 & ELSA_w5_part_clubs$scorg08[i] == 0 ) ) { 
    ELSA_ds_w5$part_clubs[i] = 0 }
  else if( ELSA_w5_part_clubs$scorg01[i] %in% c(-1,-2) | ELSA_w5_part_clubs$scorg02[i] %in% c(-1,-2) | ELSA_w5_part_clubs$scorg03[i] %in% c(-1,-2) | 
      ELSA_w5_part_clubs$scorg04[i] %in% c(-1,-2) | ELSA_w5_part_clubs$scorg05[i] %in% c(-1,-2) | ELSA_w5_part_clubs$scorg06[i] %in% c(-1,-2) | 
      ELSA_w5_part_clubs$scorg07[i] %in% c(-1,-2) | ELSA_w5_part_clubs$scorg08[i] %in% c(-1,-2) | ELSA_w5_part_clubs$scorg09[i] %in% c(-1,-2) ) { 
    ELSA_ds_w5$part_clubs[i] = 996 }
  else if( ELSA_w5_part_clubs$scorg01[i] == -8 | ELSA_w5_part_clubs$scorg02[i] == -8 | ELSA_w5_part_clubs$scorg03[i] == -8 | 
      ELSA_w5_part_clubs$scorg04[i] == -8 | ELSA_w5_part_clubs$scorg05[i] == -8 | ELSA_w5_part_clubs$scorg06[i] == -8 | 
      ELSA_w5_part_clubs$scorg07[i] == -8 | ELSA_w5_part_clubs$scorg08[i] == -8 | ELSA_w5_part_clubs$scorg09[i] == -8 ) { 
    ELSA_ds_w5$part_clubs[i] = 998 }
  else if( ELSA_w5_part_clubs$scorg01[i] == -9 | ELSA_w5_part_clubs$scorg02[i] == -9 | ELSA_w5_part_clubs$scorg03[i] == -9 | 
      ELSA_w5_part_clubs$scorg04[i] == -9 | ELSA_w5_part_clubs$scorg05[i] == -9 | ELSA_w5_part_clubs$scorg06[i] == -9 | 
      ELSA_w5_part_clubs$scorg07[i] == -9 | ELSA_w5_part_clubs$scorg08[i] == -9 | ELSA_w5_part_clubs$scorg09[i] == -9 ) { 
    ELSA_ds_w5$part_clubs[i] = 995 }
}

ELSA_ds_w5$part_clubs <- car::recode(as.vector(ELSA_ds_w5$part_clubs), "NA='999'")
ELSA_ds_w5$part_clubs <- labelled(ELSA_ds_w5$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995, "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript5, echo=F}
Categorical_summary(var = ELSA_ds_w5$part_clubs, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w5, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulation5, echo=F}

```



### Wave 6

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scorg01`
* Label: `Are you a member of: Political party, trade union or environmental groups`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-2 = Schedule Not Applicable`
    + `-1 = Item not applicable`
    
* Name: `scorg02`
* Label: `Tenants groups, resident groups, neighbourhoold watch`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-2 = Schedule Not Applicable`
    + `-1 = Item not applicable`
    
* Name: `scorg03`
* Label: `Church or other religious groups`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-2 = Schedule Not Applicable`
    + `-1 = Item not applicable`
    
  * Name: `scorg04`
* Label: `Charitable associations`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-2 = Schedule Not Applicable`
    + `-1 = Item not applicable`
    
* Name: `scorg05`
* Label: `Education, art or music groups or evening classes`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-2 = Schedule Not Applicable`
    + `-1 = Item not applicable`
    
* Name: `scorg06`
* Label: `Social club`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-1 = Item not applicable`
    
* Name: `scorg07`
* Label: `Sports clubs, gym, exercise classes`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-2 = Schedule Not Applicable`
    + `-1 = Item not applicable`
    
* Name: `scorg08`
* Label: `Any other organisations, club or societies`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-2 = Schedule Not Applicable`
    + `-1 = Item not applicable`
    
* Name: `scorg09`
* Label: `No, I am not a member of any organisations, clubs or societies`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-2 = Schedule Not Applicable`
    + `-1 = Item not applicable`
    
```{r assign6, echo=F}
opal.assign.table.tibble(o, 'ELSA_w6_part_clubs','ELSA.wave_6_elsa_data_v2', 
                        variables=list('scorg01','scorg02','scorg03','scorg04','scorg05','scorg06',
                                       'scorg07','scorg08','scorg09'), missings = TRUE)
```

```{r local6, echo=F}
ELSA_w6_part_clubs <- opal.execute(o,'ELSA_w6_part_clubs')
Categorical_summary(var = ELSA_w6_part_clubs$scorg01, missing_values = NA)
ggplot(ELSA_w6_part_clubs, aes(x=factor(scorg01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are you a member of: Political party, trade union or environmental groups?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any of scorg01-scorg08 equals 1 then 1`
* `if scorg09=1 or all of scorg01-scorg08 are equal 0 then 0`
* `-1 or -2 into 996`
* `-8 into 998`
* `-9 into 995`
* `NA into 999`

**R script:**

```{r harmo6}
ELSA_ds_w6 <- tibble(id=ELSA_w6_part_clubs$id)

ELSA_w6_part_clubs$scorg01 <- car::recode(as.vector(ELSA_w6_part_clubs$scorg01), "NA='-999'")
ELSA_w6_part_clubs$scorg02 <- car::recode(as.vector(ELSA_w6_part_clubs$scorg02), "NA='-999'")
ELSA_w6_part_clubs$scorg03 <- car::recode(as.vector(ELSA_w6_part_clubs$scorg03), "NA='-999'")
ELSA_w6_part_clubs$scorg04 <- car::recode(as.vector(ELSA_w6_part_clubs$scorg04), "NA='-999'")
ELSA_w6_part_clubs$scorg05 <- car::recode(as.vector(ELSA_w6_part_clubs$scorg05), "NA='-999'")
ELSA_w6_part_clubs$scorg06 <- car::recode(as.vector(ELSA_w6_part_clubs$scorg06), "NA='-999'")
ELSA_w6_part_clubs$scorg07 <- car::recode(as.vector(ELSA_w6_part_clubs$scorg07), "NA='-999'")
ELSA_w6_part_clubs$scorg08 <- car::recode(as.vector(ELSA_w6_part_clubs$scorg08), "NA='-999'")
ELSA_w6_part_clubs$scorg09 <- car::recode(as.vector(ELSA_w6_part_clubs$scorg09), "NA='-999'")

ELSA_ds_w6$part_clubs <- c(NA)
for(i in 1:dim(ELSA_w6_part_clubs)[1]){
  if( ELSA_w6_part_clubs$scorg01[i] == 1 | ELSA_w6_part_clubs$scorg02[i] == 1 | ELSA_w6_part_clubs$scorg03[i] == 1 | 
      ELSA_w6_part_clubs$scorg04[i] == 1 | ELSA_w6_part_clubs$scorg05[i] == 1 | ELSA_w6_part_clubs$scorg06[i] == 1 | 
      ELSA_w6_part_clubs$scorg07[i] == 1 | ELSA_w6_part_clubs$scorg08[i] == 1 ) { 
    ELSA_ds_w6$part_clubs[i] = 1 }
  else if( ELSA_w6_part_clubs$scorg09[i] == 1 | ( ELSA_w6_part_clubs$scorg01[i] == 0 & ELSA_w6_part_clubs$scorg02[i] == 0 & 
           ELSA_w6_part_clubs$scorg03[i] == 0 & ELSA_w6_part_clubs$scorg04[i] == 0 & ELSA_w6_part_clubs$scorg05[i] == 0 & 
           ELSA_w6_part_clubs$scorg06[i] == 0 & ELSA_w6_part_clubs$scorg07[i] == 0 & ELSA_w6_part_clubs$scorg08[i] == 0 ) ) { 
    ELSA_ds_w6$part_clubs[i] = 0 }
  else if( ELSA_w6_part_clubs$scorg01[i] %in% c(-1,-2) | ELSA_w6_part_clubs$scorg02[i] %in% c(-1,-2) | ELSA_w6_part_clubs$scorg03[i] %in% c(-1,-2) | 
      ELSA_w6_part_clubs$scorg04[i] %in% c(-1,-2) | ELSA_w6_part_clubs$scorg05[i] %in% c(-1,-2) | ELSA_w6_part_clubs$scorg06[i] %in% c(-1,-2) | 
      ELSA_w6_part_clubs$scorg07[i] %in% c(-1,-2) | ELSA_w6_part_clubs$scorg08[i] %in% c(-1,-2) | ELSA_w6_part_clubs$scorg09[i] %in% c(-1,-2) ) { 
    ELSA_ds_w6$part_clubs[i] = 996 }
  else if( ELSA_w6_part_clubs$scorg01[i] == -8 | ELSA_w6_part_clubs$scorg02[i] == -8 | ELSA_w6_part_clubs$scorg03[i] == -8 | 
      ELSA_w6_part_clubs$scorg04[i] == -8 | ELSA_w6_part_clubs$scorg05[i] == -8 | ELSA_w6_part_clubs$scorg06[i] == -8 | 
      ELSA_w6_part_clubs$scorg07[i] == -8 | ELSA_w6_part_clubs$scorg08[i] == -8 | ELSA_w6_part_clubs$scorg09[i] == -8 ) { 
    ELSA_ds_w6$part_clubs[i] = 998 }
  else if( ELSA_w6_part_clubs$scorg01[i] == -9 | ELSA_w6_part_clubs$scorg02[i] == -9 | ELSA_w6_part_clubs$scorg03[i] == -9 | 
      ELSA_w6_part_clubs$scorg04[i] == -9 | ELSA_w6_part_clubs$scorg05[i] == -9 | ELSA_w6_part_clubs$scorg06[i] == -9 | 
      ELSA_w6_part_clubs$scorg07[i] == -9 | ELSA_w6_part_clubs$scorg08[i] == -9 | ELSA_w6_part_clubs$scorg09[i] == -9 ) { 
    ELSA_ds_w6$part_clubs[i] = 995 }
}

ELSA_ds_w6$part_clubs <- car::recode(as.vector(ELSA_ds_w6$part_clubs), "NA='999'")
ELSA_ds_w6$part_clubs <- labelled(ELSA_ds_w6$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995, "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript6, echo=F}
Categorical_summary(var = ELSA_ds_w6$part_clubs, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w6, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulation6, echo=F}

```



### Wave 7

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scorg01`
* Label: `Are you a member of: Political party, trade union or environmental groups`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-2 = Schedule Not Applicable`
    + `-1 = Item not applicable`
    
* Name: `scorg02`
* Label: `Tenants groups, resident groups, neighbourhoold watch`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-2 = Schedule Not Applicable`
    + `-1 = Item not applicable`
    
* Name: `scorg03`
* Label: `Church or other religious groups`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-2 = Schedule Not Applicable`
    + `-1 = Item not applicable`
    
  * Name: `scorg04`
* Label: `Charitable associations`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-2 = Schedule Not Applicable`
    + `-1 = Item not applicable`
    
* Name: `scorg05`
* Label: `Education, art or music groups or evening classes`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-2 = Schedule Not Applicable`
    + `-1 = Item not applicable`
    
* Name: `scorg06`
* Label: `Social club`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-1 = Item not applicable`
    
* Name: `scorg07`
* Label: `Sports clubs, gym, exercise classes`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-2 = Schedule Not Applicable`
    + `-1 = Item not applicable`
    
* Name: `scorg08`
* Label: `Any other organisations, club or societies`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-2 = Schedule Not Applicable`
    + `-1 = Item not applicable`
    
* Name: `scorg09`
* Label: `No, I am not a member of any organisations, clubs or societies`
* Categories: 
    + `0 = No`
    + `1 = Yes`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-2 = Schedule Not Applicable`
    + `-1 = Item not applicable`
    
```{r assign7, echo=F}
opal.assign.table.tibble(o, 'ELSA_w7_part_clubs','ELSA.wave_7_elsa_data', 
                        variables=list('scorg01','scorg02','scorg03','scorg04','scorg05','scorg06',
                                       'scorg07','scorg08','scorg09'), missings = TRUE)
```

```{r local7, echo=F}
ELSA_w7_part_clubs <- opal.execute(o,'ELSA_w7_part_clubs')
Categorical_summary(var = ELSA_w7_part_clubs$scorg01, missing_values = NA)
ggplot(ELSA_w7_part_clubs, aes(x=factor(scorg01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are you a member of: Political party, trade union or environmental groups?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any of scorg01-scorg08 equals 1 then 1`
* `if scorg09=1 or all of scorg01-scorg08 are equal 0 then 0`
* `-1 or -2 into 996`
* `-8 into 998`
* `-9 into 995`
* `NA into 999`

**R script:**

```{r harmo7}
ELSA_ds_w7 <- tibble(id=ELSA_w7_part_clubs$id)

ELSA_w7_part_clubs$scorg01 <- car::recode(as.vector(ELSA_w7_part_clubs$scorg01), "NA='-999'")
ELSA_w7_part_clubs$scorg02 <- car::recode(as.vector(ELSA_w7_part_clubs$scorg02), "NA='-999'")
ELSA_w7_part_clubs$scorg03 <- car::recode(as.vector(ELSA_w7_part_clubs$scorg03), "NA='-999'")
ELSA_w7_part_clubs$scorg04 <- car::recode(as.vector(ELSA_w7_part_clubs$scorg04), "NA='-999'")
ELSA_w7_part_clubs$scorg05 <- car::recode(as.vector(ELSA_w7_part_clubs$scorg05), "NA='-999'")
ELSA_w7_part_clubs$scorg06 <- car::recode(as.vector(ELSA_w7_part_clubs$scorg06), "NA='-999'")
ELSA_w7_part_clubs$scorg07 <- car::recode(as.vector(ELSA_w7_part_clubs$scorg07), "NA='-999'")
ELSA_w7_part_clubs$scorg08 <- car::recode(as.vector(ELSA_w7_part_clubs$scorg08), "NA='-999'")
ELSA_w7_part_clubs$scorg09 <- car::recode(as.vector(ELSA_w7_part_clubs$scorg09), "NA='-999'")

ELSA_ds_w7$part_clubs <- c(NA)
for(i in 1:dim(ELSA_w7_part_clubs)[1]){
  if( ELSA_w7_part_clubs$scorg01[i] == 1 | ELSA_w7_part_clubs$scorg02[i] == 1 | ELSA_w7_part_clubs$scorg03[i] == 1 | 
      ELSA_w7_part_clubs$scorg04[i] == 1 | ELSA_w7_part_clubs$scorg05[i] == 1 | ELSA_w7_part_clubs$scorg06[i] == 1 | 
      ELSA_w7_part_clubs$scorg07[i] == 1 | ELSA_w7_part_clubs$scorg08[i] == 1 ) { 
    ELSA_ds_w7$part_clubs[i] = 1 }
  else if( ELSA_w7_part_clubs$scorg09[i] == 1 | ( ELSA_w7_part_clubs$scorg01[i] == 0 & ELSA_w7_part_clubs$scorg02[i] == 0 & 
           ELSA_w7_part_clubs$scorg03[i] == 0 & ELSA_w7_part_clubs$scorg04[i] == 0 & ELSA_w7_part_clubs$scorg05[i] == 0 & 
           ELSA_w7_part_clubs$scorg06[i] == 0 & ELSA_w7_part_clubs$scorg07[i] == 0 & ELSA_w7_part_clubs$scorg08[i] == 0 ) ) { 
    ELSA_ds_w7$part_clubs[i] = 0 }
  else if( ELSA_w7_part_clubs$scorg01[i] %in% c(-1,-2) | ELSA_w7_part_clubs$scorg02[i] %in% c(-1,-2) | ELSA_w7_part_clubs$scorg03[i] %in% c(-1,-2) | 
      ELSA_w7_part_clubs$scorg04[i] %in% c(-1,-2) | ELSA_w7_part_clubs$scorg05[i] %in% c(-1,-2) | ELSA_w7_part_clubs$scorg06[i] %in% c(-1,-2) | 
      ELSA_w7_part_clubs$scorg07[i] %in% c(-1,-2) | ELSA_w7_part_clubs$scorg08[i] %in% c(-1,-2) | ELSA_w7_part_clubs$scorg09[i] %in% c(-1,-2) ) { 
    ELSA_ds_w7$part_clubs[i] = 996 }
  else if( ELSA_w7_part_clubs$scorg01[i] == -8 | ELSA_w7_part_clubs$scorg02[i] == -8 | ELSA_w7_part_clubs$scorg03[i] == -8 | 
      ELSA_w7_part_clubs$scorg04[i] == -8 | ELSA_w7_part_clubs$scorg05[i] == -8 | ELSA_w7_part_clubs$scorg06[i] == -8 | 
      ELSA_w7_part_clubs$scorg07[i] == -8 | ELSA_w7_part_clubs$scorg08[i] == -8 | ELSA_w7_part_clubs$scorg09[i] == -8 ) { 
    ELSA_ds_w7$part_clubs[i] = 998 }
  else if( ELSA_w7_part_clubs$scorg01[i] == -9 | ELSA_w7_part_clubs$scorg02[i] == -9 | ELSA_w7_part_clubs$scorg03[i] == -9 | 
      ELSA_w7_part_clubs$scorg04[i] == -9 | ELSA_w7_part_clubs$scorg05[i] == -9 | ELSA_w7_part_clubs$scorg06[i] == -9 | 
      ELSA_w7_part_clubs$scorg07[i] == -9 | ELSA_w7_part_clubs$scorg08[i] == -9 | ELSA_w7_part_clubs$scorg09[i] == -9 ) { 
    ELSA_ds_w7$part_clubs[i] = 995 }
}

ELSA_ds_w7$part_clubs <- car::recode(as.vector(ELSA_ds_w7$part_clubs), "NA='999'")
ELSA_ds_w7$part_clubs <- labelled(ELSA_ds_w7$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995, "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript7, echo=F}
Categorical_summary(var = ELSA_ds_w7$part_clubs, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w7, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulation7, echo=F}

```



```{r final, echo=F}

l.hds <- list(w1 = ELSA_ds_w1, w2 = ELSA_ds_w2, w3 = ELSA_ds_w3, w4 = ELSA_ds_w4, w5 = ELSA_ds_w5, w6 = ELSA_ds_w6, w7 = ELSA_ds_w7)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("ELSA_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

```

## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.


```{r summ}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",names(l.hds))
kable(t.hds)

dbb <- get(paste0("ELSA_m_ds_",names(l.hds)[1]))[,c("id","part_clubs")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("ELSA_m_ds_",names(l.hds)[ind]))[,c("id","part_clubs")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", names(l.hds))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])

```


# Quality estimation
[Comments on the quality of the new harmonised variable.]


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  part_clubs <- l.hds[[index]]
  save(part_clubs, file = paste0(datafolder,names(l.hds)[index],"/part_clubs.RData"))
}

```
<!-- ########################################################## --> 

<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
