---
title: "Can people be trusted? (generalized trust, i.e. trust in other members of the society, not counting relatives and close friends)"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup_iago.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `trust`
* Variable label: `Generalized trust, i.e. trust in other members of the society, not counting relatives and close friends`
* Domain: `Social environment`
* Value type: `categorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process

## England

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised are:

* Name: `scscd`
* Label: `Most people in this area can be trusted/Most people in this area can't be trusted`
* Categories: 
    + `1 = Most people in this area can be trusted`
    + `2`
    + `3`
    + `4`
    + `5`
    + `6`
    + `7 = Most people in this area can't be trusted`
* Missings:
    + `-9 = Not answered`
    + `-1 = Item not applicable`
    
* Description: 
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'ELSA_w1_trust','ELSA.wave_1_core_data_v3',variables=list('scscd'), missings = TRUE)
```

```{r local1, echo=F}
ELSA_w1_trust <- opal.execute(o,'ELSA_w1_trust')

vari <-  ELSA_w1_trust$scscd
kable(Categorical_summary(vari, missing_values = c(-9,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w1_trust$scscd, missing_values = NA)
ggplot(ELSA_w1_trust, aes(x=factor(scscd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Most people in this area can be trusted/Most people in this area can't be trusted") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2,3 into 1`
* `4,5,6,7 into 0`
* `-9 into 995`
* `-1 into 996`
* `NA into 999`

 
**R script:**
```{r harmo1, echo=TRUE}
ELSA_ds_w1 <- tibble(id=ELSA_w1_trust$id)
ELSA_ds_w1$trust <- car::recode(as.vector(ELSA_w1_trust$scscd), "1:3='1'; 4:7='0'; -9='995'; -1='996'; NA='999'")
ELSA_ds_w1$trust <- labelled(ELSA_ds_w1$trust, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995, "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <- ELSA_ds_w1$trust
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w1$trust, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w1, aes(x=factor(trust))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Generalized trust") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(ELSA_ds_w1$trust)
BeforeH <- table(ELSA_w1_trust$scscd, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(6:9)])
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[c(3,4)] <- BeforeH[c(1,2)]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("4:7->0","1:3->1","-9->995","-1->996")
kable(C)
```

 
 




### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `RFTRUST`
* Label: `I know that I can trust my friends, and they know they can trust me`
* Categories: 
    + `1 = Strongly agree` 
    + `2 = Somewhat agree` 
    + `3 = Agree a little` 
    + `4 = Neither agree nor disagree`
    + `5 = Disagree a little` 
    + `6 = Somewhat disagree` 
    + `7 = Strongly disagree`
* Missings:
    + `-1 = Question not answered `

    
* Description: 
```{r assign2, echo=F}
opal.assign.table.tibble(o, 'ELSA_w2_trust','ELSA.wave_2_ryff_data',variables=list('RFTRUST'), missings = TRUE)
```

```{r local2, echo=F}
ELSA_w2_trust <- opal.execute(o,'ELSA_w2_trust')
vari <-  ELSA_w2_trust$RFTRUST
kable(Categorical_summary(vari, missing_values = c(-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w2_trust$RFTRUST, missing_values = NA)
ggplot(ELSA_w2_trust, aes(x=factor(RFTRUST))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("I know that I can trust my friends, and they know they can trust me") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2,3 into 1`
* `4,5,6,7 into 0`
* `-1 into 995`
* `NA into 999`

 
**R script:**
```{r harmo2, echo=TRUE}
ELSA_ds_w2 <- tibble(id=ELSA_w2_trust$id)
ELSA_ds_w2$trust <- car::recode(as.vector(ELSA_w2_trust$RFTRUST), "1:3='1'; 4:7='0'; -1='995'; NA='999'")
ELSA_ds_w2$trust <- labelled(ELSA_ds_w2$trust, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995, "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}
vari <- ELSA_ds_w2$trust
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w2$trust, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w2, aes(x=factor(trust))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Generalized trust") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
AfterH <- table(ELSA_ds_w2$trust)
BeforeH <- table(ELSA_w2_trust$RFTRUST, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(5:8)])
BeforeH1[[2]] <- sum(BeforeH[c(2:4)])
BeforeH1[[3]] <- BeforeH[[1]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("4:7->0","1:3->1","-1->995")
kable(C)
```

 
 




### Wave 3

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scscd`
* Label: `Most people in this area can be trusted/Most people in this area can~t be trusted`
* Categories: 
    + `1 = Strongly agree` 
    + `2 = Somewhat agree` 
    + `3 = Agree a little` 
    + `4 = Neither agree nor disagree`
    + `5 = Disagree a little` 
    + `6 = Somewhat disagree` 
    + `7 = Strongly disagree`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-1 = Item not applicable`
    
* Description: 
```{r assign3, echo=F}
opal.assign.table.tibble(o, 'ELSA_w3_trust','ELSA.wave_3_elsa_data_v4',variables=list('scscd'), missings = TRUE)
```

```{r local3, echo=F}
ELSA_w3_trust <- opal.execute(o,'ELSA_w3_trust')
vari <-  ELSA_w3_trust$scscd
kable(Categorical_summary(vari, missing_values = c(-9,-8,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-8,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w3_trust$scscd, missing_values = NA)
ggplot(ELSA_w3_trust, aes(x=factor(scscd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Most people in this area can be trusted/Most people in this area can~t be trusted") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2,3 into 1`
* `4,5,6,7 into 0`
* `-9 into 995`
* `-8 into 998`
* `-1 into 996`
* `NA into 999`

 
**R script:**
```{r harmo3, echo=TRUE}
ELSA_ds_w3 <- tibble(id=ELSA_w3_trust$id)
ELSA_ds_w3$trust <- car::recode(as.vector(ELSA_w3_trust$scscd), "1:3='1'; 4:7='0'; -9='995'; -8='998'; -1='996'; NA='999'")
ELSA_ds_w3$trust <- labelled(ELSA_ds_w3$trust, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995, "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=F}
vari <- ELSA_ds_w3$trust
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w3$trust, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w3, aes(x=factor(trust))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Generalized trust") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=F}
AfterH <- table(ELSA_ds_w3$trust)
BeforeH <- table(ELSA_w3_trust$scscd, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(6:9)])
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[c(3,4)] <- BeforeH[c(1,2)]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("4:7->0","1:3->1","-9->995","-1->996")
kable(C)
```



### Wave 4

Not found.

### Wave 5

Not found.

### Wave 6

Not found.

### Wave 7

Not found.




```{r save, echo=FALSE}
trust <- ELSA_ds_w1
save(trust, file = "../RData/w1/trust.RData")
rm(trust)

trust <- ELSA_ds_w2
save(trust, file = "../RData/w2/trust.RData")
rm(trust)

trust <- ELSA_ds_w3
save(trust, file = "../RData/w3/trust.RData")
rm(trust)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```

 
