---
title: "Trust"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/trustDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/trustDS.R')
```

# Data process

## England

### Wave 1 

#### Study-specific variable description


| **Name** |`scscd`|
|-|-|
| **Label** |`Most people in this area can be trusted/Most people in this area can't be trusted`|
| **Table name** |`wave_1_core_data_v3`|
| **Categories** |`1 = Most people in this area can be trusted`<br/>`2`<br/>`3`<br/>`4`<br/>`5`<br/>`6`<br/>`7 = Most people in this area can't be trusted`|
| **Missings** |`-9 = Not answered`<br/>`-1 = Item not applicable`|
| **Description** |  |


```{r assign1, echo=F}
opal.assign.table.tibble(o, 'ELSA_w1_trust','ELSA.wave_1_core_data_v3',variables=list('scscd'), missings = TRUE)
ELSA_w1_trust <- opal.execute(o,'ELSA_w1_trust')
```

```{r local1, echo=F}

vari <-  ELSA_w1_trust$scscd
kable(Categorical_summary(vari, missing_values = c(-9,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-1))[2], caption = "Type of missing")
ggplot(ELSA_w1_trust, aes(x=factor(scscd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Most people in this area can be trusted/Most people in this area can't be trusted") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2,3 into 1`
* `4,5,6,7 into 0`
* `-9 into 995`
* `-1 into 996`
* `NA into 999`

 
**R script:**
```{r harmo1, echo=TRUE}
ELSA_ds_w1 <- tibble(id=ELSA_w1_trust$id)
ELSA_ds_w1$trust <- car::recode(as.vector(ELSA_w1_trust$scscd), "1:3='1'; 4:7='0'; -9='995'; -1='996'; NA='999'")
ELSA_ds_w1$trust <- labelled(ELSA_ds_w1$trust, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995, "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <- ELSA_ds_w1$trust
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3]) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w1, aes(x=factor(trust))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Generalized trust") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(ELSA_ds_w1$trust)
BeforeH <- table(ELSA_w1_trust$scscd, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(6:9)])
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[c(3,4)] <- BeforeH[c(1,2)]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("4:7->0","1:3->1","-9->995","-1->996")
kable(C)
```

 
 




### Wave 2

Not found.
 




### Wave 3

#### Study-specific variable description


| **Name** |`scscd`|
|-|-|
| **Label** |`Most people in this area can be trusted/Most people in this area can't be trusted`|
| **Table name** |`wave_3_elsa_data_v4`|
| **Categories** |`1 = Strongly agree`<br/>`2 = Somewhat agree`<br/>`3 = Agree a little`<br/>`4 = Neither agree nor disagree`<br/>`5 = Disagree a little`<br/>`6 = Somewhat disagree`<br/>`7 = Strongly disagree`|
| **Missings** |`-9 = Not answered`<br/>`-8 = Don't know`<br/>`-1 = Item not applicable`|
| **Description** |  |


```{r assign3, echo=F}
opal.assign.table.tibble(o, 'ELSA_w3_trust','ELSA.wave_3_elsa_data_v4',variables=list('scscd'), missings = TRUE)
ELSA_w3_trust <- opal.execute(o,'ELSA_w3_trust')
```

```{r local3, echo=F}
vari <-  ELSA_w3_trust$scscd
kable(Categorical_summary(vari, missing_values = c(-9,-8,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-8,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-1))[2], caption = "Type of missing")
ggplot(ELSA_w3_trust, aes(x=factor(scscd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Most people in this area can be trusted/Most people in this area can~t be trusted") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2,3 into 1`
* `4,5,6,7 into 0`
* `-9 into 995`
* `-8 into 998`
* `-1 into 996`
* `NA into 999`

 
**R script:**
```{r harmo3, echo=TRUE}
ELSA_ds_w3 <- tibble(id=ELSA_w3_trust$id)
ELSA_ds_w3$trust <- car::recode(as.vector(ELSA_w3_trust$scscd), "1:3='1'; 4:7='0'; -9='995'; -8='998'; -1='996'; NA='999'")
ELSA_ds_w3$trust <- labelled(ELSA_ds_w3$trust, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995, "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=F}
vari <- ELSA_ds_w3$trust
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3]) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w3, aes(x=factor(trust))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Generalized trust") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=F}
AfterH <- table(ELSA_ds_w3$trust)
BeforeH <- table(ELSA_w3_trust$scscd, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(6:9)])
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[c(3,4)] <- BeforeH[c(1,2)]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("4:7->0","1:3->1","-9->995","-1->996")
kable(C)
```



### Wave 4

Not found.

### Wave 5

Not found.

### Wave 6

Not found.

### Wave 7


| **Name** |`scarea4`|
|-|-|
| **Label** |`Most people in this area can be trusted`|
| **Table name** |`wave_7_elsa_data`|
| **Categories** |`1 = Most people in this area can be trusted`<br/>`2`<br/>`3`<br/>`4`<br/>`5`<br/>`6`<br/>`7 = Most people in this area can't be trusted`|
| **Missings** |`-9 = Not answered`<br/>`-8 = Don't know`<br/>`-2 = Schedule not applicable`<br/>`-1 = Item not applicable`|
| **Description** |  |


```{r assign w7, echo=F}

opal.assign.table.tibble(o, 'ELSA_w7','ELSA.wave_7_elsa_data',variables=list('scarea4'), missings = TRUE)
ELSA_w7 <- opal.execute(o,'ELSA_w7')

```


```{r local w7, echo=F}

vbl <-  ELSA_w7$scarea4
kable(Categorical_summary(vbl, missing_values = c(-9,-2,-1))[3], caption = "scarea4") 
kable(Categorical_summary(vbl, missing_values = c(-9,-2,-1))[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = c(-9,-2,-1))[2], caption = "Type of missing")
ggplot(ELSA_w7, aes(x=factor(scarea4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```



#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2,3 into 1`
* `4,5,6,7 into 0`
* `-9 into 995`
* `-8 into 998`
* `-1,-2 into 996`
* `NA into 999`

 
**R script:**

```{r harmo w7, echo=TRUE}

ELSA_ds_w7 <- tibble(id=ELSA_w7$id)
ELSA_ds_w7$trust <- car::recode(as.vector(ELSA_w7$scarea4), "1:3='1'; 4:7='0'; -9='995'; -8='998'; -1='996'; -2 = 996; NA='999'")

```



#### Statistical description of the new harmonised variable
```{r descript w7, echo=F}

vbl <- ELSA_ds_w7$trust
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w7, aes(x=factor(trust))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation
```{r crosstabulation w7, echo=F}

```





## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.




```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```



```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


elsa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"), w6 = c("w6","W6"), w7 = c("w7","W7"))

# Consider only harmonised waves
l.hds <- lapply(elsa.cw, function(wname) if(exists(paste0("ELSA_ds_",wname[1]))){wname = list(get(paste0("ELSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```




# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```

 
