---
title: "Experience of a loss of any close person"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `bereav`
* Variable label: `Experience of a loss of any close person`
* Domain: `Social environment`
* Value type: `categorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process
## England

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `marstat`
* Label: `marital status - couple1 combined with dimar`
* Categories: 
    + `1.0 = married (inc civ pship 06 onwards)`
    + `2.0 = cohabiting`
    + `3.0 = single, never married`
    + `4.0 = widowed`
    + `5.0 = divorced`
    + `6.0 = separated`

* Description: 
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'ELSA_w1_bereav','ELSA.wave_1_ifs_derived_variables',variables=list('marstat'), missings = TRUE)
```

```{r local1, echo=F}
ELSA_w1_bereav <- opal.execute(o,'ELSA_w1_bereav')
vari <- ELSA_w1_bereav$marstat
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ELSA_w1_bereav$marstat, missing_values = NA)
ggplot(ELSA_w1_bereav, aes(x=factor(marstat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `4 into 1`
* `1,2,3,5,6 into 0`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
ELSA_ds_w1 <- tibble(id=ELSA_w1_bereav$id)
ELSA_ds_w1$bereav <- car::recode(as.vector(ELSA_w1_bereav$marstat), "4='1'; 1:3='0'; 5:6='0'; NA='999'")
ELSA_ds_w1$bereav <- labelled(ELSA_ds_w1$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <- ELSA_ds_w1$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w1$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w1, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(ELSA_ds_w1$bereav)
BeforeH <- table(ELSA_w1_bereav$marstat, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:3,5:6)])
BeforeH1[[2]] <- BeforeH[[4]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:3&5:6->0","4->1")
kable(C)
```

 
 



### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `marstat`
* Label: `marital status - couple1 combined with dimar`
* Categories: 
    + `1.0 = married (inc civ pship 06 onwards)`
    + `2.0 = cohabiting`
    + `3.0 = single, never married`
    + `4.0 = widowed`
    + `5.0 = divorced`
    + `6.0 = separated`

* Description: 
```{r assign2, echo=F}
opal.assign.table.tibble(o, 'ELSA_w2_bereav','ELSA.wave_2_ifs_derived_variables', variables=list('marstat'), missings = TRUE)
```

```{r local2, echo=F}
ELSA_w2_bereav <- opal.execute(o,'ELSA_w2_bereav')
vari <- ELSA_w2_bereav$marstat
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ELSA_w2_bereav$marstat, missing_values = NA)
ggplot(ELSA_w2_bereav, aes(x=factor(marstat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `4 into 1`
* `1,2,3,5,6 into 0`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
ELSA_ds_w2 <- tibble(id=ELSA_w2_bereav$id)
ELSA_ds_w2$bereav <- car::recode(as.vector(ELSA_w2_bereav$marstat), "4='1'; 1:3='0'; 5:6='0'; NA='999'")
ELSA_ds_w2$bereav <- labelled(ELSA_ds_w2$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}
vari <- ELSA_ds_w2$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w2$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w2, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
AfterH <- table(ELSA_ds_w2$bereav)
BeforeH <- table(ELSA_w2_bereav$marstat, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:3,5:6)])
BeforeH1[[2]] <- BeforeH[[4]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:3&5:6->0","4->1")
kable(C)
```

 
 



### Wave 3

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `rsloswr`
* Label: `Ever lost a very close friend/relative in war or military service`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `-9 = Refusal`
    + `-8 = Don't know`
    + `-7 = Self completion not completed`
    + `-2 = Respondent missed question` 
    + `-1 = Item not applicable` 
    
	
* Name: `rsriskf`
* Label: `Had v close friend/relative at risk of death/died due to illness/serious accid`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `-9 = Refusal`
    + `-8 = Don't know`
    + `-7 = Self completion not completed`
    + `-2 = Respondent missed question` 
    + `-1 = Item not applicable` 


* Description: 
```{r assign3, echo=F}
opal.assign.table.tibble(o, 'ELSA_w3_bereav','ELSA.wave_3_life_history_data',variables=list('rsloswr','rsriskf'), missings = TRUE)
ELSA_w3_bereav <- opal.execute(o,'ELSA_w3_bereav')
# The next IDs are removed since these individuals do not appear in the main tables of ELSA, so we do not have the essential information about them.
specialid <- c("100026", "101418", "101544", "102264", "103505", "110381", "115918", "116000", "121394", "150589", "152048", "152225")
ELSA_w3_bereav <- ELSA_w3_bereav[-match(specialid,ELSA_w3_bereav$id),]

```

```{r local3, echo=F}
vari <- ELSA_w3_bereav$rsloswr
kable(Categorical_summary(vari, missing_values = c(-9,-8,-7,-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-8,-7,-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-7,-2,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w3_bereav$rsloswr, missing_values = NA)
ggplot(ELSA_w3_bereav, aes(x=factor(rsloswr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever lost a very close friend/relative in war or military service") + ylab("Frequency")

vari <- ELSA_w3_bereav$rsriskf
kable(Categorical_summary(vari, missing_values = c(-9,-8,-7,-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-8,-7,-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-7,-2,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w3_bereav$rsriskf, missing_values = NA)
ggplot(ELSA_w3_bereav, aes(x=factor(rsriskf))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Had v close friend/relative at risk of death/died due to illness/serious accid") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `rsloswr=2 AND rsriskf=2 into 0`
* `rsloswr=1 OR rsriskf=1 into 1`
* `NA into 999`

**R script:**

```{r harmo3, echo=TRUE}
ELSA_ds_w3 <- tibble(id=ELSA_w3_bereav$id)

ELSA_w3_bereav$rsloswr <- car::recode(as.vector(ELSA_w3_bereav$rsloswr), "NA='-999'")
ELSA_w3_bereav$rsriskf <- car::recode(as.vector(ELSA_w3_bereav$rsriskf), "NA='-999'")

ELSA_ds_w3$bereav <- c(NA)  
for(i in 1:dim(ELSA_w3_bereav)[1]){
  if(ELSA_w3_bereav$rsloswr[i] == 1 | ELSA_w3_bereav$rsriskf[i] == 1) { 
   ELSA_ds_w3$bereav[i] = 1 }
  else if(ELSA_w3_bereav$rsloswr[i] == 2 & ELSA_w3_bereav$rsriskf[i] == 2) { 
   ELSA_ds_w3$bereav[i] = 0 }
  else if(ELSA_w3_bereav$rsloswr[i] == 2 & ELSA_w3_bereav$rsriskf[i] %in% c(-9,-8,-7,-2,-1)) { 
   ELSA_ds_w3$bereav[i] <- car::recode(as.vector(ELSA_w3_bereav$rsriskf[i]), "-9='997'; -8='998'; -7='994'; -2='999'; -1='996'") }  
  else if(ELSA_w3_bereav$rsloswr[i] %in% c(-9,-8,-7,-2,-1) & ELSA_w3_bereav$rsriskf[i] == 2) { 
    ELSA_ds_w3$bereav[i] <- car::recode(as.vector(ELSA_w3_bereav$rsloswr[i]), "-9='997'; -8='998'; -7='994'; -2='999'; -1='996'") }
  else if(ELSA_w3_bereav$rsloswr[i] %in% c(-9,-8,-7,-2,-1) & ELSA_w3_bereav$rsloswr[i] == ELSA_w3_bereav$rsriskf[i]) { 
    ELSA_ds_w3$bereav[i] <- car::recode(as.vector(ELSA_w3_bereav$rsloswr[i]), "-9='997'; -8='998'; -7='994'; -2='999'; -1='996'") }
}

ELSA_ds_w3$bereav <- car::recode(as.vector(ELSA_ds_w3$bereav), "NA='999'")
ELSA_ds_w3$bereav <- labelled(ELSA_ds_w3$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=F}
vari <- ELSA_ds_w3$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w3$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w3, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Experience of a loss of any close person") + ylab("Frequency")
```

##### Validation
```{r crosstabulation3, echo=F}

```

 
 




### Wave 4

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `marstat`
* Label: `marital status - couple1 combined with dimar`
* Categories: 
    + `1.0 = married (inc civ pship 06 onwards)`
    + `2.0 = cohabiting`
    + `3.0 = single, never married`
    + `4.0 = widowed`
    + `5.0 = divorced`
    + `6.0 = separated`
  
* Description: 
```{r assign4, echo=F}
opal.assign.table.tibble(o, 'ELSA_w4_bereav','ELSA.wave_4_ifs_derived_variables',variables=list('marstat'), missings = TRUE)
```

```{r local4, echo=F}
ELSA_w4_bereav <- opal.execute(o,'ELSA_w4_bereav')
vari <- ELSA_w4_bereav$marstat
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ELSA_w4_bereav$marstat, missing_values = NA)
ggplot(ELSA_w4_bereav, aes(x=factor(marstat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `4 into 1`
* `1,2,3,5,6 into 0`
* `NA into 999`

**R script:**

```{r harmo4, echo=TRUE}
ELSA_ds_w4 <- tibble(id=ELSA_w4_bereav$id)
ELSA_ds_w4$bereav <- car::recode(as.vector(ELSA_w4_bereav$marstat), "4='1'; 1:3='0'; 5:6='0'; NA='999'")
ELSA_ds_w4$bereav <- labelled(ELSA_ds_w4$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4, echo=F}
vari <- ELSA_ds_w4$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w4$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w4, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Experience of a loss of any close person") + ylab("Frequency")
```

##### Validation
```{r crosstabulation4, echo=F}
AfterH <- table(ELSA_ds_w4$bereav)
BeforeH <- table(ELSA_w4_bereav$marstat, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:3,5:6)])
BeforeH1[[2]] <- BeforeH[[4]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:3&5:6->0","4->1")
kable(C)
```

 
 



### Wave 5

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `marstat`
* Label: `marital status - couple1 combined with dimar`
* Categories: 
    + `1.0 = married (inc civ pship 06 onwards)`
    + `2.0 = cohabiting`
    + `3.0 = single, never married`
    + `4.0 = widowed`
    + `5.0 = divorced`
    + `6.0 = separated`

* Description: 
```{r assign5, echo=F}
opal.assign.table.tibble(o, 'ELSA_w5_bereav','ELSA.wave_5_ifs_derived_variables',variables=list('marstat'), missings = TRUE)
```

```{r local5, echo=F}
ELSA_w5_bereav <- opal.execute(o,'ELSA_w5_bereav')
vari <- ELSA_w5_bereav$marstat
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ELSA_w5_bereav$marstat, missing_values = NA)
ggplot(ELSA_w5_bereav, aes(x=factor(marstat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `4 into 1`
* `1,2,3,5,6 into 0`
* `NA into 999`

**R script:**

```{r harmo5, echo=TRUE}
ELSA_ds_w5 <- tibble(id=ELSA_w5_bereav$id)
ELSA_ds_w5$bereav <- car::recode(as.vector(ELSA_w5_bereav$marstat), "4='1'; 1:3='0'; 5:6='0'; NA='999'")
ELSA_ds_w5$bereav <- labelled(ELSA_ds_w5$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript5, echo=F}
vari <- ELSA_ds_w5$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w5$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w5, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Experience of a loss of any close person") + ylab("Frequency")
```

##### Validation
```{r crosstabulation5, echo=F}
AfterH <- table(ELSA_ds_w5$bereav)
BeforeH <- table(ELSA_w5_bereav$marstat, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:3,5:6)])
BeforeH1[[2]] <- BeforeH[[4]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:3&5:6->0","4->1")
kable(C)
```

 
 



### Wave 6

#### Study-specific variable description

The study-specific variable elected to be harmonised is:
    

* Name: `marstat`
* Label: `marital status - couple1 combined with dimar`
* Categories: 
    + `1.0 = married (inc civ pship 06 onwards)`
    + `2.0 = cohabiting`
    + `3.0 = single, never married`
    + `4.0 = widowed`
    + `5.0 = divorced`
    + `6.0 = separated`

* Description: 
```{r assign6, echo=F}
opal.assign.table.tibble(o, 'ELSA_w6_bereav','ELSA.wave_6_ifs_derived_variables',variables=list('marstat'), missings = TRUE)
ELSA_w6_bereav <- opal.execute(o,'ELSA_w6_bereav')
```

```{r local6, echo=F}
vari <- ELSA_w6_bereav$marstat
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ELSA_w6_bereav$marstat, missing_values = NA)
ggplot(ELSA_w6_bereav, aes(x=factor(marstat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `4 into 1`
* `1,2,3,5,6 into 0`
* `NA into 999`

**R script:**

```{r harmo6, echo=TRUE}
ELSA_ds_w6 <- tibble(id=ELSA_w6_bereav$id)
ELSA_ds_w6$bereav <- car::recode(as.vector(ELSA_w6_bereav$marstat), "4='1'; 1:3='0'; 5:6='0'; NA='999'")
ELSA_ds_w6$bereav <- labelled(ELSA_ds_w6$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript6, echo=F}
vari <- ELSA_ds_w6$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w6$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w6, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation6, echo=F}
AfterH <- table(ELSA_ds_w6$bereav)
BeforeH <- table(ELSA_w6_bereav$marstat, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:3,5:6)])
BeforeH1[[2]] <- BeforeH[[4]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:3&5:6->0","4->1")
kable(C)
```

 
 




### Wave 7



#### Study-specific variable description

The study-specific variable elected to be harmonised is:
    

* Name: `marstat`
* Label: `marital status - couple1 combined with dimar`
* Categories: 
    + `1.0 = married (inc civ pship 06 onwards)`
    + `2.0 = cohabiting`
    + `3.0 = single, never married`
    + `4.0 = widowed`
    + `5.0 = divorced`
    + `6.0 = separated`

```{r assign7, echo=F}
opal.assign.table.tibble(o, 'ELSA_w7_bereav','ELSA.wave7_dv',variables=list('marstat'), missings = TRUE)
ELSA_w7_bereav <- opal.execute(o,'ELSA_w7_bereav')
```

```{r local7, echo=F}
vari <- ELSA_w7_bereav$marstat
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ELSA_w7_bereav, aes(x=factor(marstat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `4 into 1`
* `1,2,3,5,6 into 0`
* `NA into 999`

**R script**

```{r harmo7, echo=F}
ELSA_ds_w7 <- tibble(id=ELSA_w7_bereav$id)
ELSA_ds_w7$bereav <- car::recode(as.vector(ELSA_w7_bereav$marstat), "4='1'; 1:3='0'; 5:6='0'; NA='999'")
ELSA_ds_w7$bereav <- labelled(ELSA_ds_w7$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript7, echo=F}
vari <- ELSA_ds_w7$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w7, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation7, echo=F}
AfterH <- table(ELSA_ds_w7$bereav)
BeforeH <- table(ELSA_w7_bereav$marstat, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:3,5:6)])
BeforeH1[[2]] <- BeforeH[[4]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:3&5:6->0","4->1")
kable(C)
```



 
```{r save, echo=FALSE}
bereav <- ELSA_ds_w1
save(bereav, file = "../RData/w1/bereav.RData")
rm(bereav)

bereav <- ELSA_ds_w2
save(bereav, file = "../RData/w2/bereav.RData")
rm(bereav)

bereav <- ELSA_ds_w3
save(bereav, file = "../RData/w3/bereav.RData")
rm(bereav)

bereav <- ELSA_ds_w4
save(bereav, file = "../RData/w4/bereav.RData")
rm(bereav)

bereav <- ELSA_ds_w5
save(bereav, file = "../RData/w5/bereav.RData")
rm(bereav)

bereav <- ELSA_ds_w6
save(bereav, file = "../RData/w6/bereav.RData")
rm(bereav)


bereav <- ELSA_ds_w7
save(bereav, file = "../RData/w7/bereav.RData")
rm(bereav)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```

