---
title: "Has friend(s)/confidant"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup_iago.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `confidant`
* Variable label: `Has friend(s)/confident`
* Domain: `Social environment`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 

# Data process

## England

### Wave 1 

#### Study-specific variable description



* Name: `scfrd`
* Label: `do you have any friends`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`
* Missings:
    + `-9.0 = Not answered`
    + `-1.0 = Item not applicable`


* Description: 
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'ELSA_w1_confidant','ELSA.wave_1_core_data_v3', variables=list('scfrd'), missings = TRUE)
```

```{r local1, echo=F}
ELSA_w1_confidant <- opal.execute(o,'ELSA_w1_confidant')
vari <- ELSA_w1_confidant$scfrd
kable(Categorical_summary(vari, missing_values = c(-1,-9))[3])
kable(Categorical_summary(vari, missing_values = c(-1,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-9))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w1_confidant$scfrd, missing_values = NA)
ggplot(ELSA_w1_confidant, aes(x=factor(scfrd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has friends?") + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 Yes into 1`
* `2 No into 0`
* `-1 Item not applicable into 996`
* `-9 Not answered into 995`
* `NA into 999`

 

**R script:** 
```{r harmo1, echo=TRUE}
ELSA_ds_w1 <- tibble(id=ELSA_w1_confidant$id)
ELSA_ds_w1$confidant <- car::recode(as.vector(ELSA_w1_confidant$scfrd), "1='1'; 2='0'; -1='996'; -9='995'; NA='999'")
ELSA_ds_w1$confidant <- labelled(ELSA_ds_w1$confidant, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <- ELSA_ds_w1$confidant
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w1$confidant, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w1, aes(x=factor(confidant))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has friend(s)/confidant(s)?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(ELSA_ds_w1$confidant)
BeforeH <- table(ELSA_w1_confidant$scfrd, useNA='ifany')[c(4,3,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1","-9->995","-1->996")
kable(C)
```

 
 


### Wave 2

#### Study-specific variable description



* Name: `scfrd`
* Label: `Whether the respondent has any friends`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`
* Missings:
    + `-9.0 = Not answered`
    + `-1.0 = Item not applicable`

* Description: 
```{r assign2, echo=F}
opal.assign.table.tibble(o, 'ELSA_w2_confidant','ELSA.wave_2_core_data_v4', variables=list('scfrd'), missings = TRUE)
```

```{r local2, echo=F}
ELSA_w2_confidant <- opal.execute(o,'ELSA_w2_confidant')
vari <- ELSA_w2_confidant$scfrd
kable(Categorical_summary(vari, missing_values = c(-1,-9))[3])
kable(Categorical_summary(vari, missing_values = c(-1,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-9))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w2_confidant$scfrd, missing_values = NA)
ggplot(ELSA_w2_confidant, aes(x=factor(scfrd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has friends?") + ylab("Frequency")

```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1 Yes into 1`
* `2 No into 0`
* `-1 Item not applicable into 996`
* `-9 Not answered into 995`
* `NA into 999`

 

**R script:** 
```{r harmo2, echo=TRUE}
ELSA_ds_w2 <- tibble(id=ELSA_w2_confidant$id)
ELSA_ds_w2$confidant <- car::recode(as.vector(ELSA_w2_confidant$scfrd), "1='1'; 2='0'; -1='996'; -9='995'; NA='999'")
ELSA_ds_w2$confidant <- labelled(ELSA_ds_w2$confidant, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}
vari <- ELSA_ds_w2$confidant
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w2$confidant, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w2, aes(x=factor(confidant))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has friend(s)/confidant(s)?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
AfterH <- table(ELSA_ds_w2$confidant)
BeforeH <- table(ELSA_w2_confidant$scfrd, useNA='ifany')[c(4,3,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1","-9->995","-1->996")
kable(C)
```

 
 


### Wave 3

#### Study-specific variable description



* Name: `scfrd`
* Label: `Whether the respondent has any friends`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`
* Missings:
    + `-1.0 = Item not applicable`
    + `-8.0 = Don't know`
    + `-9.0 = Not answered`


* Description: 
```{r assign3, echo=F}
opal.assign.table.tibble(o, 'ELSA_w3_confidant','ELSA.wave_3_elsa_data_v4',variables=list('scfrd'), missings = TRUE)
```

```{r local3, echo=F}
ELSA_w3_confidant <- opal.execute(o,'ELSA_w3_confidant')
vari <- ELSA_w3_confidant$scfrd
kable(Categorical_summary(vari, missing_values = c(-1,-8,-9))[3])
kable(Categorical_summary(vari, missing_values = c(-1,-8,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-8,-9))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w3_confidant$scfrd, missing_values = NA)
ggplot(ELSA_w3_confidant, aes(x=factor(scfrd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has any friends?") + ylab("Frequency")

```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1 Yes into 1`
* `2 No into 0`
* `-1 Item not applicable into 996`
* `-8 Don't Know into 998` 
* `-9 Not answered into 995`
* `NA into 999`

 

**R script:** 
```{r harmo3, echo=TRUE}
ELSA_ds_w3 <- tibble(id=ELSA_w3_confidant$id)
ELSA_ds_w3$confidant <- car::recode(as.vector(ELSA_w3_confidant$scfrd), "1='1'; 2='0';-9='995'; -8='998'; -1='996'; NA='999'")
ELSA_ds_w3$confidant <- labelled(ELSA_ds_w3$confidant, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=F}
vari <- ELSA_ds_w3$confidant
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w3$confidant, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w3, aes(x=factor(confidant))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Has friend(s)/confidant(s)?") + ylab("Frequency")
```

##### Validation
```{r crosstabulation3, echo=F}
AfterH <- table(ELSA_ds_w3$confidant)
BeforeH <- table(ELSA_w3_confidant$scfrd)[c(4,3,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1","-9->995","-1->996")
kable(C)
```

 
 



### Wave 4

#### Study-specific variable description



* Name: `scfrd`
* Label: `Whether the respondent has any friends`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`
* Missings:
    + `-1.0 = Item not applicable`
    + `-8.0 = Don't know`
    + `-9.0 = Not answered`

* Description: 
```{r assign4, echo=F}
opal.assign.table.tibble(o, 'ELSA_w4_confidant','ELSA.wave_4_elsa_data_v3',variables=list('scfrd'), missings = TRUE)
```

```{r local4, echo=F}
ELSA_w4_confidant <- opal.execute(o,'ELSA_w4_confidant')
vari <- ELSA_w4_confidant$scfrd
kable(Categorical_summary(vari, missing_values = c(-1,-8,-9))[3])
kable(Categorical_summary(vari, missing_values = c(-1,-8,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-8,-9))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w4_confidant$scfrd, missing_values = NA)
ggplot(ELSA_w4_confidant, aes(x=factor(scfrd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has any friends?") + ylab("Frequency")

```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1 Yes into 1`
* `2 No into 0`
* `-1 Item not applicable into 996`
* `-8 Don't Know into 998` 
* `-9 Not answered into 995`
* `NA into 999`

 

**R script:** 
```{r harmo4, echo=TRUE}
ELSA_ds_w4 <- tibble(id=ELSA_w4_confidant$id)
ELSA_ds_w4$confidant <- car::recode(as.vector(ELSA_w4_confidant$scfrd), "1='1'; 2='0';-9='995'; -8='998'; -1='996'; NA='999'")
ELSA_ds_w4$confidant <- labelled(ELSA_ds_w4$confidant, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4, echo=F}
vari <- ELSA_ds_w4$confidant
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w4$confidant, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w4, aes(x=factor(confidant))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has friend(s)/confidant(s)?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=F}
AfterH <- table(ELSA_ds_w4$confidant)
BeforeH <- table(ELSA_w4_confidant$scfrd)[c(4,3,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1","-9->995","-1->996")
kable(C)
```

 
 

### Wave 5

#### Study-specific variable description



* Name: `scfrd`
* Label: `Whether the respondent has any friends`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`
* Missings:
    + `-1.0 = Item not applicable`
    + `-2.0 = Schedule Not Applicable`
    + `-8.0 = Don't know`
    + `-9.0 = Not answered`
    
* Description: 
```{r assign5, echo=F}
opal.assign.table.tibble(o, 'ELSA_w5_confidant','ELSA.wave_5_elsa_data_v4',variables=list('scfrd'), missings = TRUE)
```

```{r local5, echo=F}
ELSA_w5_confidant <- opal.execute(o,'ELSA_w5_confidant')
vari <- ELSA_w5_confidant$scfrd
kable(Categorical_summary(vari, missing_values = c(-1,-2,-8,-9))[3])
kable(Categorical_summary(vari, missing_values = c(-1,-2,-8,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2,-8,-9))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w5_confidant$scfrd, missing_values = NA)
ggplot(ELSA_w5_confidant, aes(x=factor(scfrd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has any friends?") + ylab("Frequency")

```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows: 

* `1 Yes into 1`
* `2 No into 0`
* `-1 Item not applicable into 996`
* `-2 Schedule Not Applicable into 996`
* `-8 Don't Know into 998` 
* `-9 Not answered into 995`
* `NA into 999`

 

**R script:** 
```{r harmo5, echo=TRUE}
ELSA_ds_w5 <- tibble(id=ELSA_w5_confidant$id)
ELSA_ds_w5$confidant <- car::recode(as.vector(ELSA_w5_confidant$scfrd), "1='1'; 2='0';-9='995'; -8='998'; -2='996'; -1='996'; NA='999'")
ELSA_ds_w5$confidant <- labelled(ELSA_ds_w5$confidant, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript5, echo=F}
vari <- ELSA_ds_w5$confidant
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w5$confidant, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w5, aes(x=factor(confidant))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has friend(s)/confidant(s)?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation5, echo=F}
AfterH <- table(ELSA_ds_w5$confidant)
BeforeH <- table(ELSA_w5_confidant$scfrd,useNA='ifany')[c(4,3,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1","-9->995","-2->996")
kable(C)
```

 
 

### Wave 6

#### Study-specific variable description



* Name: `scfrd`
* Label: `Whether the respondent has any friends`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`
* Missings:
    + `-1.0 = Item not applicable`
    + `-2.0 = Schedule Not Applicable`
    + `-8.0 = Don't know`
    + `-9.0 = Not answered`

* Description: 
```{r assign6, echo=F}
opal.assign.table.tibble(o, 'ELSA_w6_confidant','ELSA.wave_6_elsa_data_v2',variables=list('scfrd'), missings = TRUE)
```

```{r local6, echo=F}
ELSA_w6_confidant <- opal.execute(o,'ELSA_w6_confidant')
vari <- ELSA_w6_confidant$scfrd
kable(Categorical_summary(vari, missing_values = c(-1,-2,-8,-9))[3])
kable(Categorical_summary(vari, missing_values = c(-1,-2,-8,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2,-8,-9))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w6_confidant$scfrd, missing_values = NA)
ggplot(ELSA_w6_confidant, aes(x=factor(scfrd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has any friends?") + ylab("Frequency")

```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1 Yes into 1`
* `2 No into 0`
* `-1 Item not applicable into 996`
* `-2 Schedule Not Applicable into 996`
* `-8 Don't Know into 998` 
* `-9 Not answered into 995`
* `NA into 999`

 

**R script:** 
```{r harmo6, echo=TRUE}
ELSA_ds_w6 <- tibble(id=ELSA_w6_confidant$id)
ELSA_ds_w6$confidant <- car::recode(as.vector(ELSA_w6_confidant$scfrd), "1='1'; 2='0';-9='995'; -8='998'; -2='996'; -1='996'; NA='999'")
ELSA_ds_w6$confidant <- labelled(ELSA_ds_w6$confidant, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript6, echo=F}
vari <- ELSA_ds_w6$confidant
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w6$confidant, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w6, aes(x=factor(confidant))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has friend(s)/confidant(s)?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation6, echo=F}
AfterH <- table(ELSA_ds_w6$confidant)
BeforeH <- table(ELSA_w6_confidant$scfrd,useNA='ifany')[c(4,3,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1","-9->995","-2->996")
kable(C)
```






### Wave 7

#### Study-specific variable description



* Name: `scfrd`
* Label: `Whether the respondent has any friends`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `-1 = Item not applicable`
    + `-2 = Schedule Not Applicable`
    + `-8 = Don't know`
    + `-9 = Not answered`

* Description: 
```{r assign7, echo=F}
opal.assign.table.tibble(o, 'ELSA_w7','ELSA.wave_7_elsa_data',variables=list('scfrd'), missings = TRUE)
```

```{r local7, echo=F}
ELSA_w7 <- opal.execute(o,'ELSA_w7')
vari <- ELSA_w7$scfrd
kable(Categorical_summary(vari, missing_values = c(-1,-2,-8,-9))[3])
kable(Categorical_summary(vari, missing_values = c(-1,-2,-8,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2,-8,-9))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w7$scfrd, missing_values = NA)
ggplot(ELSA_w7, aes(x=factor(scfrd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has any friends?") + ylab("Frequency")

```

#### Harmonisation algorithm

To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1 Yes into 1`
* `2 No into 0`
* `-1 Item not applicable into 996`
* `-2 Schedule Not Applicable into 996`
* `-8 Don't Know into 998` 
* `-9 Not answered into 995`
* `NA into 999`

 

**R script:** 

```{r harmo7, echo=TRUE}
ELSA_ds_w7 <- tibble(id=ELSA_w7$id)
ELSA_ds_w7$confidant <- car::recode(as.vector(ELSA_w7$scfrd), "1='1'; 2='0';-9='995'; -8='998'; -2='996'; -1='996'; NA='999'")
ELSA_ds_w7$confidant <- labelled(ELSA_ds_w7$confidant, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript7, echo=F}
vari <- ELSA_ds_w7$confidant
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w6$confidant, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w7, aes(x=factor(confidant))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has friend(s)/confidant(s)?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation7, echo=F}
AfterH <- table(ELSA_ds_w7$confidant)
BeforeH <- table(ELSA_w7$scfrd,useNA='ifany')[c(4,3,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1","-9->995","-2->996")
kable(C)
```






# Quality estimation


```{r save, echo=FALSE}
confidant <- ELSA_ds_w1
save(confidant, file = "../RData/w1/confidant.RData")
rm(confidant)

confidant <- ELSA_ds_w2
save(confidant, file = "../RData/w2/confidant.RData")
rm(confidant)

confidant <- ELSA_ds_w3
save(confidant, file = "../RData/w3/confidant.RData")
rm(confidant)

confidant <- ELSA_ds_w4
save(confidant, file = "../RData/w4/confidant.RData")
rm(confidant)

confidant <- ELSA_ds_w5
save(confidant, file = "../RData/w5/confidant.RData")
rm(confidant)

confidant <- ELSA_ds_w6
save(confidant, file = "../RData/w6/confidant.RData")
rm(confidant)

confidant <- ELSA_ds_w7
save(confidant, file = "../RData/w7/confidant.RData")
rm(confidant)


```

```{r closeRsession, echo=FALSE} 
opal.logout(o)
```