---
title: "Life-threatening situation"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/lifethreat_sitDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/lifethreat_sitDS.R')
```

<!-- ########################################################## --> 

# Data process

## ELSA

### Wave 1

Not found.

### Wave 2

Not found.

### Wave 3

#### Study-specific variable description


| **Name** |`rsill`|
|-|-|
| **Label** |`Have you ever had a life-threatening illness or accident?`|
| **Table name** |`wave_3_life_history_data`|
| **Categories** |`1 = yes`<br/>`2 = no`|
| **Missings** |`-9 = Refusal`<br/>`-8 = Don't Know`<br/>`-7 = self completion not completed`<br/>`-2 = respondent missed question`<br/>`-1 = Not applicable`|
| **Description** |  |

```{r assign3, echo=F}
opal.assign.table.tibble(o, 'ELSA_w3_life_thr','ELSA.wave_3_life_history_data',variables=list('rsill'), missings = TRUE)
ELSA_w3_life_thr <- opal.execute(o,'ELSA_w3_life_thr')
# The next IDs are removed since these individuals do not appear in the main tables of ELSA, so we do not have the essential information about them.
specialid <- c("100026", "101418", "101544", "102264", "103505", "110381", "115918", "116000", "121394", "150589", "152048", "152225")
ELSA_w3_life_thr <- ELSA_w3_life_thr[-match(specialid,ELSA_w3_life_thr$id),]

```

```{r local3, echo=F}

vbl <- ELSA_w3_life_thr$rsill
vbl_miss <- c(-1,-2,-7,-8,-9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = 'rsill')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w3_life_thr, aes(x=factor(rsill))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1 into 1; 2 into 0`
* `-9 into 997`
* `-8 into 998`
* `-7 into 999`
* `-2 into 994`
* `-1 into 996`
* `NA into 999`

**R script:**

```{r harmo3}

ELSA_ds_w3 <- tibble(id=ELSA_w3_life_thr$id)
ELSA_ds_w3$lifethreat_sit <- car::recode(as.vector(ELSA_w3_life_thr$rsill), "1='1'; 2='0'; -9='997'; -8='998'; -7='999'; -2='994'; -1='996'; NA='999'")

```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}

vbl <- ELSA_ds_w3$lifethreat_sit
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w3, aes(x=factor(lifethreat_sit))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

##### Validation
```{r crosstabulation3, echo=F}
AfterH <- table(ELSA_ds_w3$lifethreat_sit)
BeforeH <- table(ELSA_w3_life_thr$rsill, useNA='ifany')[c(4,3,2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","-2->994","-7->999")
kable(C)
```

### Wave 4

Not found.

### Wave 5

Not found.

### Wave 6

Not found.

### Wave 7

Not found.




```{r final, echo=F}

l.hds <- list(w3 = ELSA_ds_w3)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("ELSA_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

```

## Summary of descriptive statistics of the harmonised variable accross populations and waves


Percentages of categories in each harmonised variable.



```{r summ}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",names(l.hds))
kable(t.hds)

```


# Quality estimation
[Comments on the quality of the new harmonised variable.]


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  lifethreat_sit <- l.hds[[index]]
  save(lifethreat_sit, file = paste0(datafolder,names(l.hds)[index],"/lifethreat_sit.RData"))
}

```
<!-- ########################################################## --> 

<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
