---
title: "Ever experienced any natural disaster"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup_iago.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `nat_dis`
* Variable label: `Ever experienced any natural disaster`
* Domain: `Social environment`
* Value type: `categorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process
## England

### Wave 1

Not found.

### Wave 2

Not found.

### Wave 3

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `rsdisas`
* Label: `Have you ever experienced a major fire, flood, earthquake or other natural disaster?`
* Categories: 
    + `1 = yes`
    + `2 = no`
* Missings:   
    + `-9 = Refusal`
    + `-8 = Don't Know`
    + `-7 = self completion not completed`
    + `-2 = respondent missed question`
    + `-1 = Not applicable`
    
* Description:
```{r assign3, echo=FALSE}

opal.assign.table.tibble(o, 'ELSA_w3_nat_dis','ELSA.wave_3_life_history_data',variables=list('rsdisas'), missings = TRUE)
ELSA_w3_nat_dis <- opal.execute(o,'ELSA_w3_nat_dis')
# The next IDs are removed since these individuals do not appear in the main tables of ELSA, so we do not have the essential information about them.
specialid <- c("100026", "101418", "101544", "102264", "103505", "110381", "115918", "116000", "121394", "150589", "152048", "152225")
ELSA_w3_nat_dis <- ELSA_w3_nat_dis[-match(specialid,ELSA_w3_nat_dis$id),]

```

```{r local3, echo=FALSE}
vari <- ELSA_w3_nat_dis$rsdisas
kable(Categorical_summary(vari, missing_values = c(-9,-8,-7,-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-8,-7,-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-7,-2,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w3_nat_dis$rsdisas, missing_values = NA)
ggplot(ELSA_w3_nat_dis, aes(x=factor(rsdisas))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Have you ever experienced a major fire, flood, earthquake or other natural disaster?") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1 into 1; 2 into 0`
* `-9 into 997`
* `-8 into 998`
* `-7 into 999`
* `-2 into 994`
* `-1 into 996`
* `NA into 999`

**R script:**

```{r harmo3, echo=TRUE}
ELSA_ds_w3 <- tibble(id=ELSA_w3_nat_dis$id)
ELSA_ds_w3$nat_dis <- car::recode(as.vector(ELSA_w3_nat_dis$rsdisas), "1='1'; 2='0'; -9='997'; -8='998'; -7='999'; -2='994'; -1='996'; NA='999'")
ELSA_ds_w3$nat_dis <- labelled(ELSA_ds_w3$nat_dis, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=FALSE}
vari <- ELSA_ds_w3$nat_dis
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w3$nat_dis, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w3, aes(x=factor(nat_dis))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Ever experienced any natural disaster") + ylab("Frequency")
```

##### Validation
```{r crosstabulation3, echo=FALSE}
AfterH <- table(ELSA_ds_w3$nat_dis)
BeforeH <- table(ELSA_w3_nat_dis$rsdisas, useNA='ifany')[c(4,3,2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","-2->994","-7->999")
kable(C)
```


### Wave 4

Not found.


### Wave 5

Not found.

### Wave 6

Not found.

### Wave 7

Not found.

```{r save, echo=FALSE}
nat_dis <- ELSA_ds_w3
save(nat_dis, file = "../RData/w3/nat_dis.RData")
rm(nat_dis)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```


