---
title: "Experience of any type of violence during the lifetime (including domestic violence and assault by a stranger)"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/violenceDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/violenceDS.R')
```

<!-- ########################################################## --> 

# Data process

## England

### Wave 1

Not found.

### Wave 2

Not found.

### Wave 3

#### Study-specific variable description


| **Name** |`rsabuse`|`rsattac`|`rssexas`|
|-|-|-|-|
| **Label** |`Whether when aged <16 was physically abused by your parents`|`Ever been a victim of serious physical attack or assault`|`Ever been a victim of sexual assault (including rape or harassment)`|
| **Table name** |`wave_3_life_history_data`|`wave_3_life_history_data`|`wave_3_life_history_data`|
| **Categories** |`1 = Yes`<br/>`2 = No`|`1 = Yes`<br/>`2 = No`|`1 = Yes`<br/>`2 = No`|
| **Missings** |`-9 = Refusal`<br/>`-8 = Don't Know`<br/>`-7 = Self completion not completed`<br/>`-2 = Respondent missed question`<br/>`-1 = Item not applicable`|`-9 = Refusal`<br/>`-8 = Don't Know`<br/>`-7 = Self completion not completed`<br/>`-2 = Respondent missed question`<br/>`-1 = Item not applicable`|`-9 = Refusal`<br/>`-8 = Don't Know`<br/>`-7 = Self completion not completed`<br/>`-2 = Respondent missed question`<br/>`-1 = Item not applicable`|
| **Description** |  |  |  |



```{r assign3, echo=FALSE}
opal.assign.table.tibble(o, 'ELSA_w3_violence','ELSA.wave_3_life_history_data',variables=list('rsabuse','rsattac','rssexas'), missings = TRUE)
ELSA_w3_violence <- opal.execute(o,'ELSA_w3_violence')
opal.assign.table.tibble(o, 'ELSA_w3_main','ELSA.wave_3_elsa_data_v4',variables=list('indobyr'), missings = TRUE)
ELSA_w3_main <- opal.execute(o,'ELSA_w3_main')

# The next IDs are removed since these individuals do not appear in the main tables of ELSA for wave 3, so we do not have the essential information about them.
ELSA_w3_violence <- ELSA_w3_violence %>% filter(id %in% ELSA_w3_main$id)
```

```{r local3, echo=FALSE}
vari <- ELSA_w3_violence$rsabuse
kable(Categorical_summary(vari, missing_values = c(-9,-8,-7,-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-8,-7,-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-7,-2,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w3_violence$rsabuse, missing_values = NA)
ggplot(ELSA_w3_violence, aes(x=factor(rsabuse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Whether when aged <16 was physically abused by your parents?") + ylab("Frequency")

vari <- ELSA_w3_violence$rsattac
kable(Categorical_summary(vari, missing_values = c(-9,-8,-7,-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-8,-7,-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-7,-2,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w3_violence$rsattac, missing_values = NA)
ggplot(ELSA_w3_violence, aes(x=factor(rsattac))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever been a victim of serious physical attack or assault?") + ylab("Frequency")

vari <- ELSA_w3_violence$rssexas
kable(Categorical_summary(vari, missing_values = c(-9,-8,-7,-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-8,-7,-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-7,-2,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w3_violence$rssexas, missing_values = NA)
ggplot(ELSA_w3_violence, aes(x=factor(rssexas))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Ever been a victim of sexual assault (including rape or harassment)?") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if any eqauls 1 then 1`
* `if all are equal 2 then 0`
* `-9 into 997`
* `-8 into 998`
* `-7 into 999`
* `-2 into 994`
* `-1 into 996`
* `NA into 999`

**R script:**

```{r harmo3, echo=TRUE}
ELSA_ds_w3 <- tibble(id=ELSA_w3_violence$id)

ELSA_w3_violence$rsabuse <- car::recode(as.vector(ELSA_w3_violence$rsabuse), "NA='-999'")
ELSA_w3_violence$rsattac <- car::recode(as.vector(ELSA_w3_violence$rsattac), "NA='-999'")
ELSA_w3_violence$rssexas <- car::recode(as.vector(ELSA_w3_violence$rssexas), "NA='-999'")

ELSA_ds_w3$violence <- c(NA)
for(i in 1:dim(ELSA_w3_violence[1])){
  if( ELSA_w3_violence$rsabuse[i] == 1 | ELSA_w3_violence$rsattac[i] == 1 | ELSA_w3_violence$rssexas[i] == 1 ) { 
    ELSA_ds_w3$violence[i] = 1 }
  else if( ELSA_w3_violence$rsabuse[i] == 2 & ELSA_w3_violence$rsattac[i] == 2 & ELSA_w3_violence$rssexas[i] == 2 ) { 
    ELSA_ds_w3$violence[i] = 0 }
  else if(ELSA_w3_violence$rsabuse[i] == -9 | ELSA_w3_violence$rsattac[i] == -9 | ELSA_w3_violence$rssexas[i] == -9 ) { 
    ELSA_ds_w3$violence[i] = 997 }
  else if( ELSA_w3_violence$rsabuse[i] == -8 | ELSA_w3_violence$rsattac[i] == -8 | ELSA_w3_violence$rssexas[i] == -8 ) { 
    ELSA_ds_w3$violence[i] = 998 }
  else if( ELSA_w3_violence$rsabuse[i] == -7 | ELSA_w3_violence$rsattac[i] == -7 | ELSA_w3_violence$rssexas[i] == -7 ) { 
    ELSA_ds_w3$violence[i] = 999 }
  else if( ELSA_w3_violence$rsabuse[i] == -2 | ELSA_w3_violence$rsattac[i] == -2 | ELSA_w3_violence$rssexas[i] == -2 ) { 
    ELSA_ds_w3$violence[i] = 994 }
  else if( ELSA_w3_violence$rsabuse[i] == -1 | ELSA_w3_violence$rsattac[i] == -1 | ELSA_w3_violence$rssexas[i] == -1 ) { 
    ELSA_ds_w3$violence[i] = 996 }
}

ELSA_ds_w3$violence <- car::recode(as.vector(ELSA_ds_w3$violence), "NA='999'")
ELSA_ds_w3$violence <- labelled(ELSA_ds_w3$violence, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=FALSE}
vari <- ELSA_ds_w3$violence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w3$violence, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w3, aes(x=factor(violence))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Experience of any type of violence during the lifetime") + ylab("Frequency")
```

##### Validation
```{r crosstabulation3, echo=FALSE}

```


### Wave 4

Not found.


### Wave 5

Not found.

### Wave 6

Not found.

### Wave 7

Not found.


```{r final, echo=F}

l.hds <- list(w3 = ELSA_ds_w3)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("ELSA_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

```

## Summary of descriptive statistics of the harmonised variable accross populations and waves


Percentages of categories in each harmonised variable.



```{r summ, echo=FALSE}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",names(l.hds))
kable(t.hds)

```


```{r save, echo=FALSE}
violence <- ELSA_ds_w3
save(violence , file = "../RData/w3/violence.RData")
rm(violence )


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```

