---
title: "Has spouse/partner"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup_iago.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `spouse`
* Variable label: `Has spouse/partner`
* Domain: `Social environment`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 

# Data process

## England

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `marstat`
* Label: `marital status - couple1 combined with dimar`
* Categories: 
    + `1.0 = married (inc civ pship 06 onwards)`
    + `2.0 = cohabiting`
    + `3.0 = single, never married`
    + `4.0 = widowed`
    + `5.0 = divorced`
    + `6.0 = separated`


* Description: 
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'ELSA_w1_spouse','ELSA.wave_1_ifs_derived_variables', variables=list('marstat'), missings = TRUE)
```

```{r local1, echo=F}
ELSA_w1_spouse <- opal.execute(o,'ELSA_w1_spouse')
vari <- ELSA_w1_spouse$marstat
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ELSA_w1_spouse$marstat, missing_values = NA)
ggplot(ELSA_w1_spouse, aes(x=factor(marstat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 OR 2 into 1`
* `3,4,5,6 into 0`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
ELSA_ds_w1 <- tibble(id=ELSA_w1_spouse$id)
ELSA_ds_w1$spouse <- car::recode(as.vector(ELSA_w1_spouse$marstat), "1:2='1'; 3:6='0'; NA='999'")
ELSA_ds_w1$spouse <- labelled(ELSA_ds_w1$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <- ELSA_ds_w1$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w1$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w1, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(ELSA_ds_w1$spouse)
BeforeH <- table(ELSA_w1_spouse$marstat, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[2]])
BeforeH[[2]] <- sum(BeforeH[[3]],BeforeH[[4]],BeforeH[[5]],BeforeH[[6]])
BeforeH <- BeforeH[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1")

kable(C)
```

 
 



### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `marstat`
* Label: `marital status - couple1 combined with dimar`
* Categories: 
    + `1.0 = married (inc civ pship 06 onwards)`
    + `2.0 = cohabiting`
    + `3.0 = single, never married`
    + `4.0 = widowed`
    + `5.0 = divorced`
    + `6.0 = separated`

* Description: 
```{r assign2, echo=F}
opal.assign.table.tibble(o, 'ELSA_w2_spouse','ELSA.wave_2_ifs_derived_variables', variables=list('marstat'), missings = TRUE)
```

```{r local2, echo=F}
ELSA_w2_spouse <- opal.execute(o,'ELSA_w2_spouse')
vari <- ELSA_w2_spouse$marstat
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ELSA_w2_spouse$marstat, missing_values = NA)
ggplot(ELSA_w2_spouse, aes(x=factor(marstat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 OR 2 into 1`
* `3,4,5,6 into 0`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
ELSA_ds_w2 <- tibble(id=ELSA_w2_spouse$id)
ELSA_ds_w2$spouse <- car::recode(as.vector(ELSA_w2_spouse$marstat), "1:2='1'; 3:6='0'; NA='999'")
ELSA_ds_w2$spouse <- labelled(ELSA_ds_w2$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}
vari <- ELSA_ds_w2$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w2$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w2, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
AfterH <- table(ELSA_ds_w2$spouse)
BeforeH <- table(ELSA_w2_spouse$marstat, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[2]])
BeforeH[[2]] <- sum(BeforeH[[3]],BeforeH[[4]],BeforeH[[5]],BeforeH[[6]])
BeforeH <- BeforeH[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1")

kable(C)
```

 
 



### Wave 3

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `marstat`
* Label: `marital status - couple1 combined with dimar`
* Categories: 
    + `1.0 = married (inc civ pship 06 onwards)`
    + `2.0 = cohabiting`
    + `3.0 = single, never married`
    + `4.0 = widowed`
    + `5.0 = divorced`
    + `6.0 = separated`

* Description: 
```{r assign3, echo=F}
opal.assign.table.tibble(o, 'ELSA_w3_spouse','ELSA.wave_3_ifs_derived_variables',variables=list('marstat'), missings = TRUE)
```

```{r local3, echo=F}
ELSA_w3_spouse <- opal.execute(o,'ELSA_w3_spouse')
vari <- ELSA_w3_spouse$marstat
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ELSA_w3_spouse$marstat, missing_values = NA)
ggplot(ELSA_w3_spouse, aes(x=factor(marstat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1 OR 2 into 1`
* `3,4,5,6 into 0`
* `NA into 999`

**R script:**

```{r harmo3, echo=TRUE}
ELSA_ds_w3 <- tibble(id=ELSA_w3_spouse$id)
ELSA_ds_w3$spouse <- car::recode(as.vector(ELSA_w3_spouse$marstat), "1:2='1'; 3:6='0'; NA='999'")
ELSA_ds_w3$spouse <- labelled(ELSA_ds_w3$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=F}
vari <- ELSA_ds_w3$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w3$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w3, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Has spouse/partner") + ylab("Frequency")
```

##### Validation
```{r crosstabulation3, echo=F}
AfterH <- table(ELSA_ds_w3$spouse)
BeforeH <- table(ELSA_w3_spouse$marstat, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[2]])
BeforeH[[2]] <- sum(BeforeH[[3]],BeforeH[[4]],BeforeH[[5]],BeforeH[[6]])
BeforeH <- BeforeH[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1")

kable(C)
```

 
 




### Wave 4

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `marstat`
* Label: `marital status - couple1 combined with dimar`
* Categories: 
    + `1.0 = married (inc civ pship 06 onwards)`
    + `2.0 = cohabiting`
    + `3.0 = single, never married`
    + `4.0 = widowed`
    + `5.0 = divorced`
    + `6.0 = separated`

* Description: 
```{r assign4, echo=F}
opal.assign.table.tibble(o, 'ELSA_w4_spouse','ELSA.wave_4_ifs_derived_variables',variables=list('marstat'), missings = TRUE)
```

```{r local4, echo=F}
ELSA_w4_spouse <- opal.execute(o,'ELSA_w4_spouse')
vari <- ELSA_w4_spouse$marstat
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ELSA_w4_spouse$marstat, missing_values = NA)
ggplot(ELSA_w4_spouse, aes(x=factor(marstat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1 OR 2 into 1`
* `3,4,5,6 into 0`
* `NA into 999`

**R script:**

```{r harmo4, echo=TRUE}
ELSA_ds_w4 <- tibble(id=ELSA_w4_spouse$id)
ELSA_ds_w4$spouse <- car::recode(as.vector(ELSA_w4_spouse$marstat), "1:2='1'; 3:6='0'; NA='999'")
ELSA_ds_w4$spouse <- labelled(ELSA_ds_w4$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4, echo=F}
vari <- ELSA_ds_w4$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w4$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w4, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Has spouse/partner") + ylab("Frequency")
```

##### Validation
```{r crosstabulation4, echo=F}
AfterH <- table(ELSA_ds_w4$spouse)
BeforeH <- table(ELSA_w4_spouse$marstat, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[2]])
BeforeH[[2]] <- sum(BeforeH[[3]],BeforeH[[4]],BeforeH[[5]],BeforeH[[6]])
BeforeH <- BeforeH[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1")

kable(C)
```

 
 



### Wave 5

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `marstat`
* Label: `marital status - couple1 combined with dimar`
* Categories: 
    + `1.0 = married (inc civ pship 06 onwards)`
    + `2.0 = cohabiting`
    + `3.0 = single, never married`
    + `4.0 = widowed`
    + `5.0 = divorced`
    + `6.0 = separated`

* Description: 
```{r assign5, echo=F}
opal.assign.table.tibble(o, 'ELSA_w5_spouse','ELSA.wave_5_ifs_derived_variables',variables=list('marstat'), missings = TRUE)
```

```{r local5, echo=F}
ELSA_w5_spouse <- opal.execute(o,'ELSA_w5_spouse')
vari <- ELSA_w5_spouse$marstat
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ELSA_w5_spouse$marstat, missing_values = NA)
ggplot(ELSA_w5_spouse, aes(x=factor(marstat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1 OR 2 into 1`
* `3,4,5,6 into 0`
* `NA into 999`

**R script:**

```{r harmo5, echo=TRUE}
ELSA_ds_w5 <- tibble(id=ELSA_w5_spouse$id)
ELSA_ds_w5$spouse <- car::recode(as.vector(ELSA_w5_spouse$marstat), "1:2='1'; 3:6='0'; NA='999'")
ELSA_ds_w5$spouse <- labelled(ELSA_ds_w5$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript5, echo=F}
vari <- ELSA_ds_w5$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w5$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w5, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Has spouse/partner") + ylab("Frequency")
```

##### Validation
```{r crosstabulation5, echo=F}
AfterH <- table(ELSA_ds_w5$spouse)
BeforeH <- table(ELSA_w5_spouse$marstat, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[2]])
BeforeH[[2]] <- sum(BeforeH[[3]],BeforeH[[4]],BeforeH[[5]],BeforeH[[6]])
BeforeH <- BeforeH[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1")

kable(C)
```

 
 



### Wave 6

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `marstat`
* Label: `marital status - couple1 combined with dimar`
* Categories: 
    + `1.0 = married (inc civ pship 06 onwards)`
    + `2.0 = cohabiting`
    + `3.0 = single, never married`
    + `4.0 = widowed`
    + `5.0 = divorced`
    + `6.0 = separated`

* Description: 
```{r assign6, echo=F}
opal.assign.table.tibble(o, 'ELSA_w6_spouse','ELSA.wave_6_ifs_derived_variables',variables=list('marstat'), missings = TRUE)
```

```{r local6, echo=F}
ELSA_w6_spouse <- opal.execute(o,'ELSA_w6_spouse')
vari <- ELSA_w6_spouse$marstat
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ELSA_w6_spouse$marstat, missing_values = NA)
ggplot(ELSA_w6_spouse, aes(x=factor(marstat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1 OR 2 into 1`
* `3,4,5,6 into 0`
* `NA into 999`

**R script:**

```{r harmo6, echo=TRUE}
ELSA_ds_w6 <- tibble(id=ELSA_w6_spouse$id)
ELSA_ds_w6$spouse <- car::recode(as.vector(ELSA_w6_spouse$marstat), "1:2='1'; 3:6='0'; NA='999'")
ELSA_ds_w6$spouse <- labelled(ELSA_ds_w6$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript6, echo=F}
vari <- ELSA_ds_w6$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w6$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w6, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r crosstabulation6, echo=F}
AfterH <- table(ELSA_ds_w6$spouse)
BeforeH <- table(ELSA_w6_spouse$marstat, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[2]])
BeforeH[[2]] <- sum(BeforeH[[3]],BeforeH[[4]],BeforeH[[5]],BeforeH[[6]])
BeforeH <- BeforeH[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1")

kable(C)
```

 
 


### Wave 7

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `marstat`
* Label: `marital status - couple1 combined with dimar`
* Categories: 
    + `1.0 = married (inc civ pship 06 onwards)`
    + `2.0 = cohabiting`
    + `3.0 = single, never married`
    + `4.0 = widowed`
    + `5.0 = divorced`
    + `6.0 = separated`

* Description: 
```{r assign7, echo=F}
opal.assign.table.tibble(o, 'ELSA_w7','ELSA.wave7_dv',variables=list('marstat'), missings = TRUE)
```

```{r local7, echo=F}
ELSA_w7 <- opal.execute(o,'ELSA_w7')
vari <- ELSA_w7$marstat
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = ELSA_w7$marstat, missing_values = NA)
ggplot(ELSA_w7, aes(x=factor(marstat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1 OR 2 into 1`
* `3,4,5,6 into 0`
* `NA into 999`

**R script:**

```{r harmo7, echo=TRUE}
ELSA_ds_w7 <- tibble(id=ELSA_w7$id)
ELSA_ds_w7$spouse <- car::recode(as.vector(ELSA_w7$marstat), "1:2='1'; 3:6='0'; NA='999'")
ELSA_ds_w7$spouse <- labelled(ELSA_ds_w7$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript7, echo=F}
vari <- ELSA_ds_w7$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w7$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w7, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r crosstabulation7, echo=F}
AfterH <- table(ELSA_ds_w7$spouse)
BeforeH <- table(ELSA_w7$marstat, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[2]])
BeforeH[[2]] <- sum(BeforeH[[3]],BeforeH[[4]],BeforeH[[5]],BeforeH[[6]])
BeforeH <- BeforeH[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1")

kable(C)
```

 
 
# Quality estimation


```{r save, echo=FALSE}
spouse <- ELSA_ds_w1
save(spouse, file = "../RData/w1/spouse.RData")
rm(spouse)

spouse <- ELSA_ds_w2
save(spouse, file = "../RData/w2/spouse.RData")
rm(spouse)

spouse <- ELSA_ds_w3
save(spouse, file = "../RData/w3/spouse.RData")
rm(spouse)

spouse <- ELSA_ds_w4
save(spouse, file = "../RData/w4/spouse.RData")
rm(spouse)

spouse <- ELSA_ds_w5
save(spouse, file = "../RData/w5/spouse.RData")
rm(spouse)

spouse <- ELSA_ds_w6
save(spouse, file = "../RData/w6/spouse.RData")
rm(spouse)


spouse <- ELSA_ds_w7
save(spouse, file = "../RData/w7/spouse.RData")
rm(spouse)

```

```{r closeRsession, echo=FALSE} 
opal.logout(o)
```