---
title: "The number of close people: friends, neighbours or co-workers"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup_iago.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `clspeop`
* Variable label: `The number of close people: friends, neighbours or co-workers`
* Domain: `Social environment`
* Value type: `continuous`


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 

# Data process

## England

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scfrdm`
* Label: `how many of your friends would you say you have a close relationship`
* Missings:
    + `-9.0 = Not answered`
    + `-1.0 = Item not applicable`


* Description: 
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'ELSA_w1_clspeop','ELSA.wave_1_core_data_v3', variables=list('scfrdm'), missings = TRUE)
```

```{r local1, echo=F}
ELSA_w1_clspeop <- opal.execute(o,'ELSA_w1_clspeop')
vari <- ELSA_w1_clspeop$scfrdm
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = ELSA_w1_clspeop$scfrdm, missing_values = NA)
ggplot(ELSA_w1_clspeop, aes(x=factor(scfrdm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How many of his/her friends he/she has a close relationship") + ylab("Frequency")
## there are two observations with value 98 -> recode into 999, because it's hard to guess what it is
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `-1 Item not applicable into 996`
* `-9 Not answered into 995`
* `98 or NA into 999`
* `other values into themselves`

**R script:**

```{r harmo1, echo=TRUE}
ELSA_ds_w1 <- tibble(id=ELSA_w1_clspeop$id)
ELSA_ds_w1$clspeop <- car::recode(as.vector(ELSA_w1_clspeop$scfrdm), "-1='996'; -9='995'; 98='999'; NA='999'")
ELSA_ds_w1$clspeop <- labelled(ELSA_ds_w1$clspeop, labels = c("lack of close people"=0, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <- ELSA_ds_w1$clspeop
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
#Continuous_summary(var = ELSA_ds_w1$clspeop, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w1, aes(x=factor(clspeop))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The number of close people: friends, neighbours or co-workers") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(ELSA_ds_w1$clspeop)
BeforeH <- table(ELSA_w1_clspeop$scfrdm, useNA='ifany')
BeforeH <- BeforeH[c(4:length(BeforeH)-1,1,2,length(BeforeH))]

C <- rbind(BeforeH,AfterH)
colnames(C)[c(30,31,32)] <- c("-9->995","-1->996","98->999")

kable(C)
```

 
 


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scfrdm`
* Label: `how many of your friends would you say you have a close relationship`
* Missings:
    + `-9.0 = Not answered`
    + `-1.0 = Item not applicable`

* Description: 
```{r assign2, echo=F}
opal.assign.table.tibble(o, 'ELSA_w2_clspeop','ELSA.wave_2_core_data_v4',variables=list('scfrdm'), missings = TRUE)
```

```{r local2, echo=F}
ELSA_w2_clspeop <- opal.execute(o,'ELSA_w2_clspeop')
vari <- ELSA_w2_clspeop$scfrdm
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = ELSA_w2_clspeop$scfrdm, missing_values = NA)
ggplot(ELSA_w2_clspeop, aes(x=factor(scfrdm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How many of his/her friends he/she has a close relationship") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `-1 Item not applicable into 996`
* `-9 Not answered into 995`
* `NA into 999`
* `other values into themselves`

**R script:**

```{r harmo2, echo=TRUE}
ELSA_ds_w2 <- tibble(id=ELSA_w2_clspeop$id)
ELSA_ds_w2$clspeop <- car::recode(as.vector(ELSA_w2_clspeop$scfrdm), "-1='996'; -9='995'; 98='999'; NA='999'")
ELSA_ds_w2$clspeop <- labelled(ELSA_ds_w2$clspeop, labels = c("lack of close people"=0, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
### one wird value of 98 -> recode into 999
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}
vari <- ELSA_ds_w2$clspeop
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
#Continuous_summary(var = ELSA_ds_w2$clspeop, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w2, aes(x=factor(clspeop))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The number of close people: friends, neighbours or co-workers") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
AfterH <- table(ELSA_ds_w2$clspeop)
BeforeH <- table(ELSA_w2_clspeop$scfrdm, useNA='ifany')
BeforeH <- BeforeH[c(4:length(BeforeH)-1,1,2,length(BeforeH))]

C <- rbind(BeforeH,AfterH)
colnames(C)[c(42,43,44)] <- c("-9->995","-1->996","98->999")

kable(C)
```

 
 


### Wave 3

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scfrdm`
* Label: `how many of your friends would you say you have a close relationship`
* Missings:
    + `-1.0 = Item not applicable`
    + `-8.0 = Don't know`
    + `-9.0 = Not answered`


* Description: 
```{r assign3, echo=F}
opal.assign.table.tibble(o, 'ELSA_w3_clspeop','ELSA.wave_3_elsa_data_v4',variables=list('scfrdm'), missings = TRUE)
```

```{r local3, echo=F}
ELSA_w3_clspeop <- opal.execute(o,'ELSA_w3_clspeop')
vari <- ELSA_w3_clspeop$scfrdm
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = ELSA_w3_clspeop$scfrdm, missing_values = NA)
ggplot(ELSA_w3_clspeop, aes(x=factor(scfrdm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How many of his/her friends he/she has a close relationship") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `-1 Item not applicable into 996`
* `-8 Don't Know into 998` 
* `-9 Not answered into 995`
* `NA into 999`
* `other values into themselves`

**R script:**

```{r harmo3, echo=TRUE}
ELSA_ds_w3 <- tibble(id=ELSA_w3_clspeop$id)
ELSA_ds_w3$clspeop <- car::recode(as.vector(ELSA_w3_clspeop$scfrdm), "-9='995'; -8='998'; -1='996'; NA='999'")
ELSA_ds_w3$clspeop <- labelled(ELSA_ds_w3$clspeop, labels = c("lack of close people"=0, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=F}
vari <- ELSA_ds_w3$clspeop
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
#Continuous_summary(var = ELSA_ds_w3$clspeop, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w3, aes(x=factor(clspeop))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("The number of close people: friends, neighbours or co-workers") + ylab("Frequency")
```

##### Validation
```{r crosstabulation3, echo=F}
AfterH <- table(ELSA_ds_w3$clspeop)
BeforeH <- table(ELSA_w3_clspeop$scfrdm, useNA='ifany')
BeforeH <- BeforeH[c(3:length(BeforeH),1,2)]

C <- rbind(BeforeH,AfterH)
colnames(C)[c(55,56)] <- c("-9->995","-1->996")

kable(C)
```

 
 

### Wave 4

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scfrdm`
* Label: `how many of your friends would you say you have a close relationship`
* Missings:
    + `-1.0 = Item not applicable`
    + `-8.0 = Don't know`
    + `-9.0 = Not answered`

* Description: 
```{r assign4, echo=F}
opal.assign.table.tibble(o, 'ELSA_w4_clspeop','ELSA.wave_4_elsa_data_v3',variables=list('scfrdm'), missings = TRUE)
```

```{r local4, echo=F}
ELSA_w4_clspeop <- opal.execute(o,'ELSA_w4_clspeop')
vari <- ELSA_w4_clspeop$scfrdm
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = ELSA_w4_clspeop$scfrdm, missing_values = NA)
ggplot(ELSA_w4_clspeop, aes(x=factor(scfrdm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How many of his/her friends he/she has a close relationship") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `-1 Item not applicable into 996`
* `-8 Don't Know into 998` 
* `-9 Not answered into 995`
* `NA into 999`
* `other values into themselves`

**R script:**

```{r harmo4, echo=TRUE}
ELSA_ds_w4 <- tibble(id=ELSA_w4_clspeop$id)
ELSA_ds_w4$clspeop <- car::recode(as.vector(ELSA_w4_clspeop$scfrdm), "-9='995'; -8='998'; -1='996'; NA='999'")
ELSA_ds_w4$clspeop <- labelled(ELSA_ds_w4$clspeop, labels = c("lack of close people"=0, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4, echo=F}
vari <- ELSA_ds_w4$clspeop
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
#Continuous_summary(var = ELSA_ds_w4$clspeop, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w4, aes(x=factor(clspeop))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The number of close people: friends, neighbours or co-workers") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=F}
AfterH <- table(ELSA_ds_w4$clspeop)
BeforeH <- table(ELSA_w4_clspeop$scfrdm, useNA='ifany')
BeforeH <- BeforeH[c(3:length(BeforeH),1,2)]

C <- rbind(BeforeH,AfterH)
colnames(C)[c(30,31)] <- c("-9->995","-1->996")

kable(C)
```

 
 

### Wave 5

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scfrdm`
* Label: `how many of your friends would you say you have a close relationship`
* Missings:
    + `-1.0 = Item not applicable`
    + `-2.0 = Schedule Not Applicable`
    + `-8.0 = Don't know`
    + `-9.0 = Not answered`
    
* Description: 
```{r assign5, echo=F}
opal.assign.table.tibble(o, 'ELSA_w5_clspeop','ELSA.wave_5_elsa_data_v4',variables=list('scfrdm'), missings = TRUE)
```

```{r local5, echo=F}
ELSA_w5_clspeop <- opal.execute(o,'ELSA_w5_clspeop')
vari <- ELSA_w5_clspeop$scfrdm
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = ELSA_w5_clspeop$scfrdm, missing_values = NA)
ggplot(ELSA_w5_clspeop, aes(x=factor(scfrdm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How many of his/her friends he/she has a close relationship") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows: 

* `-1 Item not applicable into 996`
* `-2 Schedule Not Applicable into 996`
* `-8 Don't Know into 998` 
* `-9 Not answered into 995`
* `NA into 999`
* `other values into themselves`

**R script:**

```{r harmo5, echo=TRUE}
ELSA_ds_w5 <- tibble(id=ELSA_w5_clspeop$id)
ELSA_ds_w5$clspeop <- car::recode(as.vector(ELSA_w5_clspeop$scfrdm), "-9='995'; -8='998'; -2='996'; -1='996'; NA='999'")
ELSA_ds_w5$clspeop <- labelled(ELSA_ds_w5$clspeop, labels = c("lack of close people"=0, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
### What about one value 97???
```

#### Statistical description of the new harmonised variable
```{r descript5, echo=F}
vari <- ELSA_ds_w5$clspeop
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
#Continuous_summary(var = ELSA_ds_w5$clspeop, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w5, aes(x=factor(clspeop))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The number of close people: friends, neighbours or co-workers") + ylab("Frequency")
```

#### Validation
```{r crosstabulation5, echo=F}
AfterH <- table(ELSA_ds_w5$clspeop)
BeforeH <- table(ELSA_w5_clspeop$scfrdm, useNA='ifany')
BeforeH[[2]] <- sum(BeforeH[[2]],BeforeH[[3]])
BeforeH <- BeforeH[c(4:length(BeforeH),1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C)[c(32,33)] <- c("-9->995","-1,-2->996")

kable(C)
```

 
 

### Wave 6

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scfrdm`
* Label: `how many of your friends would you say you have a close relationship`
* Missings:
    + `-1.0 = Item not applicable`
    + `-2.0 = Schedule Not Applicable`
    + `-8.0 = Don't know`
    + `-9.0 = Not answered`

* Description: 
```{r assign6, echo=F}
opal.assign.table.tibble(o, 'ELSA_w6_clspeop','ELSA.wave_6_elsa_data_v2',variables=list('scfrdm'), missings = TRUE)
```

```{r local6, echo=F}
ELSA_w6_clspeop <- opal.execute(o,'ELSA_w6_clspeop')
vari <- ELSA_w6_clspeop$scfrdm
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = ELSA_w6_clspeop$scfrdm, missing_values = NA)
ggplot(ELSA_w6_clspeop, aes(x=factor(scfrdm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How many of his/her friends he/she has a close relationship") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `-1 Item not applicable into 996`
* `-2 Schedule Not Applicable into 996`
* `-8 Don't Know into 998` 
* `-9 Not answered into 995`
* `NA into 999`
* `other values into themselves`

**R script:**

```{r harmo6, echo=TRUE}
ELSA_ds_w6 <- tibble(id=ELSA_w6_clspeop$id)
ELSA_ds_w6$clspeop <- car::recode(as.vector(ELSA_w6_clspeop$scfrdm), "-9='995'; -8='998'; -2='996'; -1='996'; NA='999'")
ELSA_ds_w6$clspeop <- labelled(ELSA_ds_w6$clspeop, labels = c("lack of close people"=0, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript6, echo=F}
vari <- ELSA_ds_w6$clspeop
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
#Continuous_summary(var = ELSA_ds_w6$clspeop, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w6, aes(x=factor(clspeop))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The number of close people: friends, neighbours or co-workers") + ylab("Frequency")
```

#### Validation
```{r crosstabulation6, echo=F}
AfterH <- table(ELSA_ds_w6$clspeop)
BeforeH <- table(ELSA_w6_clspeop$scfrdm, useNA='ifany')
BeforeH[[2]] <- sum(BeforeH[[2]],BeforeH[[3]])
BeforeH <- BeforeH[c(4:length(BeforeH),1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C)[c(28,29)] <- c("-9->995","-1,-2->996")

kable(C)
```

 
 
 
### Wave 7

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scfrdl`
* Label: `How many friends the respondent has a close relationship with`
* Missings:
    + `-1 = Item not applicable`
    + `-2 = Schedule Not Applicable`
    + `-8 = Don't know`
    + `-9 = Not answered`

* Description: 
```{r assign7, echo=F}
opal.assign.table.tibble(o, 'ELSA_w7','ELSA.wave_7_elsa_data',variables=list('scfrdl'), missings = TRUE)
ELSA_w7 <- opal.execute(o,'ELSA_w7')
```

```{r local7, echo=F}
vari <- ELSA_w7$scfrdl
kable(Continuous_summary(vari, missing_values = c(-1,-2,-8,-9))[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = c(-1,-2,-8,-9))$summary, caption = "Summary")
#Continuous_summary(var = ELSA_w7$scfrdm, missing_values = NA)
ggplot(filter(ELSA_w7,!ELSA_w7$scfrdl %in% c(-1,-2,-8,-9)), aes(scfrdl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How many of his/her friends he/she has a close relationship") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `-1 Item not applicable into 996`
* `-2 Schedule Not Applicable into 996`
* `-8 Don't Know into 998` 
* `-9 Not answered into 995`
* `NA into 999`
* `other values into themselves`

**R script:**

```{r harmo7, echo=TRUE}
ELSA_ds_w7 <- tibble(id=ELSA_w7$id)
ELSA_ds_w7$clspeop <- car::recode(as.vector(ELSA_w7$scfrdl), "-9='995'; -8='998'; -2='996'; -1='996'; NA='999'")
ELSA_ds_w7$clspeop <- labelled(ELSA_ds_w7$clspeop, labels = c("lack of close people"=0, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript7, echo=F}
vari <- ELSA_ds_w7$clspeop
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
#Continuous_summary(var = ELSA_ds_w6$clspeop, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w7, aes(x=factor(clspeop))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The number of close people: friends, neighbours or co-workers") + ylab("Frequency")
```

#### Validation
```{r crosstabulation7, echo=F}
AfterH <- table(ELSA_ds_w7$clspeop)
BeforeH <- table(ELSA_w7$scfrdl, useNA='ifany')
BeforeH[[2]] <- sum(BeforeH[[2]],BeforeH[[3]])
BeforeH <- BeforeH[c(4:length(BeforeH),1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C)[c(28,29)] <- c("-9->995","-1,-2->996")

kable(C)
```
 
 
 
# Quality estimation


```{r save, echo=FALSE}
clspeop <- ELSA_ds_w1
save(clspeop, file = "../RData/w1/clspeop.RData")
rm(clspeop)

clspeop <- ELSA_ds_w2
save(clspeop, file = "../RData/w2/clspeop.RData")
rm(clspeop)

clspeop <- ELSA_ds_w3
save(clspeop, file = "../RData/w3/clspeop.RData")
rm(clspeop)

clspeop <- ELSA_ds_w4
save(clspeop, file = "../RData/w4/clspeop.RData")
rm(clspeop)

clspeop <- ELSA_ds_w5
save(clspeop, file = "../RData/w5/clspeop.RData")
rm(clspeop)

clspeop <- ELSA_ds_w6
save(clspeop, file = "../RData/w6/clspeop.RData")
rm(clspeop)

clspeop <- ELSA_ds_w7
save(clspeop, file = "../RData/w7/clspeop.RData")
rm(clspeop)


```

```{r closeRsession, echo=FALSE} 
opal.logout(o)
```