---
title: "Has children and/or grandchildren"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup_iago.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `child`
* Variable label: `Has children`
* Domain: `Social environment`
* Value type: `categorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Short name: `grchild`
* Variable label: `Has grandchildren`
* Domain: `Social environment`
* Value type: `categorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 

# Data process

## England

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scchd` *from 'ELSA.wave_1_core_data_v3'*
* Label: `do you have any children`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `-9 = Not answered `
    + `-1 = Item not applicable`
    
    
* Name: `ngrandch` *from 'wave_1_ifs_derived_variables'* 
* Label: `Number of grandchildren or great-grandchildren inside or outside the household?`
* Missings:
    + `-9 = Refuse`
    + `-8 = Don't Know`
    + `-2 = Not asked`


* Description: 
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'ELSA_w1_child','ELSA.wave_1_core_data_v3',variables=list('scchd'), missings = TRUE)
opal.assign.table.tibble(o, 'ELSA_w1_grchild','ELSA.wave_1_ifs_derived_variables',variables=list('ngrandch'), missings = TRUE)
```

```{r local1, echo=F}
ELSA_w1_child <- opal.execute(o,'ELSA_w1_child')
vari <- ELSA_w1_child$scchd
kable(Categorical_summary(vari, missing_values = c(-9,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w1_child$scchd, missing_values = NA)
ggplot(ELSA_w1_child, aes(x=factor(scchd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Does he/she have any children") + ylab("Frequency")

ELSA_w1_grchild <- opal.execute(o,'ELSA_w1_grchild')
vari <- ELSA_w1_grchild$ngrandch
kable(Continuous_summary(vari, missing_values = c(-9,-8,-2))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Continuous_summary(vari, missing_values = c(-9,-8,-2))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values =c(-9,-8,-2))$summary, caption = "Summary")
#Continuous_summary(var = ELSA_w1_grchild$ngrandch, missing_values = NA)
ggplot(filter(ELSA_w1_grchild,!ELSA_w1_grchild$ngrandch %in% c(-9,-8,-2)), aes(ngrandch)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of grandchildren or great-grandchildren inside or outside the household?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `CHILDREN:`
* `1 into 1`
* `2 into 0`
* `Missings: -9 into 995; -1 into 996`

* `GRANDCHILDREN:`
* `0 INTO 0`
* `1:hi into 1`
* `Missings: -9 into 997; -8 into 998; -2 into 994`

* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
ELSA_ds_w1 <- tibble(id=ELSA_w1_child$id)
ELSA_ds_w1$child <- car::recode(as.vector(ELSA_w1_child$scchd), "1='1'; 2='0'; -9='995'; -1='996'; NA='999'")
ELSA_ds_w1$child <- labelled(ELSA_ds_w1$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))

ELSA_ds_w1$grchild <- car::recode(as.vector(ELSA_w1_grchild$ngrandch), "0='0'; -9='997'; -8='998'; -2='994'; NA='999'; 1:hi='1'")
ELSA_ds_w1$grchild <- labelled(ELSA_ds_w1$grchild, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <- ELSA_ds_w1$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Children") 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w1$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w1, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")

vari <- ELSA_ds_w1$grchild
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Grandchildren") 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w1$grchild, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w1, aes(x=factor(grchild))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has grandchildren") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
AfterH1 <- table(ELSA_ds_w1$child)
BeforeH1 <- table(ELSA_w1_child$scchd, useNA='ifany')[c(4,3,1,2)]
C <- rbind(BeforeH1,AfterH1)
colnames(C) <- c("2->0","1","-9->995","-1->996") 
kable(C)

AfterH2 <- table(ELSA_ds_w1$grchild)
X <- table(ELSA_w1_grchild$ngrandch, useNA='ifany')
BeforeH2 <- c(X[3],sum(X[-c(3,1,2)]),X[1:2])
C <- rbind(BeforeH2,AfterH2)
colnames(C) <- c("2->0","1","-9->997","-8->998") 
kable(C)
```

 
 



### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scchd`
* Label: `Whether the respondent has any children`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `-9 = Not answered`
    + `-1 = Item not applicable`
    
    
* Name: `DiGran`
* Label: `Whether respondent has any grandchildren/greatgrandchildren`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `-9 = Refusal`
    + `-8 = Don't Know`
    + `-1 = Not applicable`

* Description: 
```{r assign2, echo=F}
opal.assign.table.tibble(o, 'ELSA_w2_child','ELSA.wave_2_core_data_v4', variables=list('scchd','DiGran'), missings = TRUE)
```

```{r local2, echo=F}
ELSA_w2_child <- opal.execute(o,'ELSA_w2_child')
vari <- ELSA_w2_child$scchd
kable(Categorical_summary(vari, missing_values = c(-9,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w2_child$scchd, missing_values = NA)
ggplot(ELSA_w2_child, aes(x=factor(scchd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Whether the respondent has any children") + ylab("Frequency")

vari <- ELSA_w2_child$DiGran
kable(Categorical_summary(vari, missing_values = c(-9,-8,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-8,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w2_child$DiGran, missing_values = NA)
ggplot(ELSA_w2_child, aes(x=factor(DiGran))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Whether the respondent has any grandchildren/greatgrandchildren") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0`

* `Missings for CHILD: -9 into 995; -1 into 996`
* `Missings for GRCHILD: -9 into 997; -8 into 998; -1 into 996`

* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
ELSA_ds_w2 <- tibble(id=ELSA_w2_child$id)
ELSA_ds_w2$child <- car::recode(as.vector(ELSA_w2_child$scchd), "1='1'; 2='0'; -9='995'; -1='996'; NA='999'")
ELSA_ds_w2$child <- labelled(ELSA_ds_w2$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))

ELSA_ds_w2$grchild <- car::recode(as.vector(ELSA_w2_child$DiGran), "1='1'; 2='0'; -9='997'; -8='998'; -1='996'; NA='999'")
ELSA_ds_w2$grchild <- labelled(ELSA_ds_w2$grchild, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}
vari <- ELSA_ds_w2$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Children") 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w2$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w2, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")

vari <- ELSA_ds_w2$grchild
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Grandchildren") 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w2$grchild, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w2, aes(x=factor(grchild))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has grandchildren") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
AfterH1 <- table(ELSA_ds_w2$child)
BeforeH1 <- table(ELSA_w2_child$scchd, useNA='ifany')[c(4,3,1,2)]
C <- rbind(BeforeH1,AfterH1)
colnames(C) <- c("2->0","1","-9->995","-1->996") 
kable(C)

AfterH2 <- table(ELSA_ds_w2$grchild)
BeforeH2 <- table(ELSA_w2_child$DiGran, useNA='ifany')[c(4,3,2,1)]
C <- rbind(BeforeH2,AfterH2)
colnames(C) <- c("2->0","1","-1->996","-8->998") 
kable(C)
```

 
 



### Wave 3

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scchd`
* Label: `Whether the respondent has any children`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-1 = Item not applicable`
    
    
* Name: `digran`
* Label: `Whether respondent has any grandchildren/greatgrandchildren`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `-9 = Refusal`
    + `-8 = Don't Know`
    + `-2 = Schedule not applicable`
    + `-1 = Not applicable`

* Description: 
```{r assign3, echo=F}
opal.assign.table.tibble(o, 'ELSA_w3_child','ELSA.wave_3_elsa_data_v4',variables=list('scchd','digran'), missings = TRUE)
```

```{r local3, echo=F}
ELSA_w3_child <- opal.execute(o,'ELSA_w3_child')
vari <- ELSA_w3_child$scchd
kable(Categorical_summary(vari, missing_values = c(-9,-8,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-8,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w3_child$scchd, missing_values = NA)
ggplot(ELSA_w3_child, aes(x=factor(scchd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Whether the respondent has any children") + ylab("Frequency")

vari <- ELSA_w3_child$digran
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w3_child$digran, missing_values = NA)
ggplot(ELSA_w3_child, aes(x=factor(digran))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Whether the respondent has any grandchildren/greatgrandchildren") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1 into 1`
* `2 into 0`

* `Missings for CHILD: -9 into 995; -8 into 998; -1 into 996`
* `Missings for GRCHILD: -9 into 997; -8 into 998; -2 into 996; -1 into 996`

* `NA into 999`

**R script:**

```{r harmo3, echo=TRUE}
ELSA_ds_w3 <- tibble(id=ELSA_w3_child$id)
ELSA_ds_w3$child <- car::recode(as.vector(ELSA_w3_child$scchd), "1='1'; 2='0'; -9='995'; -8='998'; -1='996'; NA='999'")
ELSA_ds_w3$child <- labelled(ELSA_ds_w3$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))

ELSA_ds_w3$grchild <- car::recode(as.vector(ELSA_w3_child$digran), "1='1'; 2='0'; -9='997'; -8='998'; -2='996'; -1='996'; NA='999'")
ELSA_ds_w3$grchild <- labelled(ELSA_ds_w3$grchild, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=F}
vari <- ELSA_ds_w3$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Children") 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w3$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w3, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Has children") + ylab("Frequency")

vari <- ELSA_ds_w3$grchild
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Grandchildren") 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w3$grchild, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w3, aes(x=factor(grchild))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Has grandchildren") + ylab("Frequency")
```

##### Validation
```{r crosstabulation3, echo=F}
AfterH1 <- table(ELSA_ds_w3$child)
BeforeH1 <- table(ELSA_w3_child$scchd, useNA='ifany')[c(4,3,1,2)]
C <- rbind(BeforeH1,AfterH1)
colnames(C) <- c("2->0","1","-9->995","-1->996") 
kable(C)

AfterH2 <- table(ELSA_ds_w3$grchild)
BeforeH2 <- table(ELSA_w3_child$digran, useNA='ifany')[c(4,3,2,1)]
C <- rbind(BeforeH2,AfterH2)
colnames(C) <- c("2->0","1","-1->996","-8->998") 
kable(C)
```

 
 




### Wave 4

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scchd`
* Label: `Whether the respondent has any children`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-1 = Not applicable`
    
* Name: `digran`
* Label: `Whether respondent has any grandchildren/greatgrandchildren`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `-9 = Refusal`
    + `-8 = Don't Know`
    + `-2 = Capi/Interview Error`
    + `-1 = Not applicable`

* Description: 
```{r assign4, echo=F}
opal.assign.table.tibble(o, 'ELSA_w4_child','ELSA.wave_4_elsa_data_v3',variables=list('scchd','digran'), missings = TRUE)
```

```{r local4, echo=F}
ELSA_w4_child <- opal.execute(o,'ELSA_w4_child')
vari <- ELSA_w4_child$scchd
kable(Categorical_summary(vari, missing_values = c(-9,-8,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-8,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w4_child$scchd, missing_values = NA)
ggplot(ELSA_w4_child, aes(x=factor(scchd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Whether the respondent has any children") + ylab("Frequency")

vari <- ELSA_w4_child$digran
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w4_child$digran, missing_values = NA)
ggplot(ELSA_w4_child, aes(x=factor(digran))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Whether respondent has any grandchildren/greatgrandchildren") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1 into 1`
* `2 into 0`

* `Missings for CHILD: -9 into 995; -8 into 998; -1 into 996`
* `Missings for GRCHILD: -9 into 997; -8 into 998; -2 into 991; -1 into 996`

* `NA into 999`

**R script:**

```{r harmo4, echo=TRUE}
ELSA_ds_w4 <- tibble(id=ELSA_w4_child$id)
ELSA_ds_w4$child <- car::recode(as.vector(ELSA_w4_child$scchd), "1='1'; 2='0'; -9='995'; -8='998'; -1='996'; NA='999'")
ELSA_ds_w4$child <- labelled(ELSA_ds_w4$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))

ELSA_ds_w4$grchild <- car::recode(as.vector(ELSA_w4_child$digran), "1='1'; 2='0'; -9='997'; -8='998'; -2='991'; -1='996'; NA='999'")
ELSA_ds_w4$grchild <- labelled(ELSA_ds_w4$grchild, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4, echo=F}
vari <- ELSA_ds_w4$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Children") 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w4$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w4, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Has children") + ylab("Frequency")

vari <- ELSA_ds_w4$grchild
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Grandchildren") 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w4$grchild, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w4, aes(x=factor(grchild))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Has grandchildren") + ylab("Frequency")
```

##### Validation
```{r crosstabulation4, echo=F}
AfterH1 <- table(ELSA_ds_w4$child)
BeforeH1 <- table(ELSA_w4_child$scchd, useNA='ifany')[c(4,3,1,2)]
C <- rbind(BeforeH1,AfterH1)
colnames(C) <- c("2->0","1","-9->995","-1->996") 
kable(C)

AfterH2 <- table(ELSA_ds_w4$grchild)
BeforeH2 <- table(ELSA_w4_child$digran, useNA='ifany')[c(6,5,3,4,1,2)]
C <- rbind(BeforeH2,AfterH2)
colnames(C) <- c("2->0","1","-2->991","-1->996","-9->997","-8->998") 
kable(C)
```

 
 



### Wave 5

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scchd`
* Label: `Whether the respondent has any children`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-2 = Schedule Not Applicable`
    + `-1 = Item not applicable`
    
* Name: `digran`
* Label: `Whether respondent has any grandchildren/greatgrandchildren`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `-9 = Refusal`
    + `-8 = Don't Know`
    + `-2 = Schedule Not Applicable`
    + `-1 = Item not applicable`

* Description: 
```{r assign5, echo=F}
opal.assign.table.tibble(o, 'ELSA_w5_child','ELSA.wave_5_elsa_data_v4',variables=list('scchd','digran'), missings = TRUE)
```

```{r local5, echo=F}
ELSA_w5_child <- opal.execute(o,'ELSA_w5_child')
vari <- ELSA_w5_child$scchd
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w5_child$scchd, missing_values = NA)
ggplot(ELSA_w5_child, aes(x=factor(scchd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Whether the respondent has any children") + ylab("Frequency")

vari <- ELSA_w5_child$digran
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w5_child$digran, missing_values = NA)
ggplot(ELSA_w5_child, aes(x=factor(digran))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Whether respondent has any grandchildren/greatgrandchildren") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1 into 1`
* `2 into 0`

* `Missings for CHILD: -9 into 995; -8 into 998; -2 into 996; -1 into 996`
* `Missings for GRCHILD: -9 into 997; -8 into 998; -2 into 996; -1 into 996`

* `NA into 999`

**R script:**

```{r harmo5, echo=TRUE}
ELSA_ds_w5 <- tibble(id=ELSA_w5_child$id)
ELSA_ds_w5$child <- car::recode(as.vector(ELSA_w5_child$scchd), "1='1'; 2='0'; -9='995'; -8='998'; -2='996'; -1='996'; NA='999'")
ELSA_ds_w5$child <- labelled(ELSA_ds_w5$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))

ELSA_ds_w5$grchild <- car::recode(as.vector(ELSA_w5_child$digran), "1='1'; 2='0'; -9='997'; -8='998'; -2='996'; -1='996'; NA='999'")
ELSA_ds_w5$grchild <- labelled(ELSA_ds_w5$grchild, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript5, echo=F}
vari <- ELSA_ds_w5$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Children") 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w5$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w5, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Has children") + ylab("Frequency")

vari <- ELSA_ds_w5$grchild
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Grandchildren") 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w5$grchild, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w5, aes(x=factor(grchild))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Has grandchildren") + ylab("Frequency")
```

##### Validation
```{r crosstabulation5, echo=F}
AfterH1 <- table(ELSA_ds_w5$child)
BeforeH1 <- table(ELSA_w5_child$scchd, useNA='ifany')[c(4,3,1,2)]
C <- rbind(BeforeH1,AfterH1)
colnames(C) <- c("2->0","1","-9->995","-2->996") 
kable(C)

AfterH2 <- table(ELSA_ds_w5$grchild)
BeforeH2 <- table(ELSA_w5_child$digran, useNA='ifany')[c(5,4,3,1,2)]
C <- rbind(BeforeH2,AfterH2)
colnames(C) <- c("2->0","1","-1->996","-9->997","-8->998") 
kable(C)
```

 
 



### Wave 6

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scchd`
* Label: `Whether the respondent has any children`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-2 = Schedule Not Applicable`
    + `-1 = Item not applicable`
    
* Name: `DiGran`
* Label: `Whether respondent has any grandchildren/greatgrandchildren`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `-9 = Refusal`
    + `-8 = Don't Know`
    + `-2 = Schedule Not Applicable`
    + `-1 = Item not applicable`

* Description: 
```{r assign6, echo=F}
opal.assign.table.tibble(o, 'ELSA_w6_child','ELSA.wave_6_elsa_data_v2',variables=list('scchd','DiGran'), missings = TRUE)
```

```{r local6, echo=F}
ELSA_w6_child <- opal.execute(o,'ELSA_w6_child')
vari <- ELSA_w6_child$scchd
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w6_child$scchd, missing_values = NA)
ggplot(ELSA_w6_child, aes(x=factor(scchd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Whether the respondent has any children") + ylab("Frequency")

vari <- ELSA_w6_child$DiGran
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w6_child$DiGran, missing_values = NA)
ggplot(ELSA_w6_child, aes(x=factor(DiGran))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Whether the respondent has any grandchildren/greatgrandchildren") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1 into 1`
* `2 into 0`

* `Missings for CHILD: -9 into 995; -8 into 998; -2 into 996; -1 into 996`
* `Missings for GRCHILD: -9 into 997; -8 into 998; -2 into 996; -1 into 996`

* `NA into 999`

**R script:**

```{r harmo6, echo=TRUE}
ELSA_ds_w6 <- tibble(id=ELSA_w6_child$id)
ELSA_ds_w6$child <- car::recode(as.vector(ELSA_w6_child$scchd), "1='1'; 2='0'; -9='995'; -8='998'; -2='996'; -1='996'; NA='999'")
ELSA_ds_w6$child <- labelled(ELSA_ds_w6$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))

ELSA_ds_w6$grchild <- car::recode(as.vector(ELSA_w6_child$DiGran), "1='1'; 2='0'; -9='997'; -8='998'; -2='996'; -1='996'; NA='999'")
ELSA_ds_w6$grchild <- labelled(ELSA_ds_w6$grchild, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript6, echo=F}
vari <- ELSA_ds_w6$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Children") 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w6$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w6, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")

vari <- ELSA_ds_w6$grchild
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Grandchildren") 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w6$grchild, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w6, aes(x=factor(grchild))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has grandchildren") + ylab("Frequency")
```

#### Validation
```{r crosstabulation6, echo=F}
AfterH1 <- table(ELSA_ds_w6$child)
BeforeH1 <- table(ELSA_w6_child$scchd, useNA='ifany')[c(4,3,1,2)]
C <- rbind(BeforeH1,AfterH1)
colnames(C) <- c("2->0","1","-9->995","-2->996") 
kable(C)

AfterH2 <- table(ELSA_ds_w6$grchild)
BeforeH2 <- table(ELSA_w6_child$DiGran, useNA='ifany')[c(5,4,3,1,2)]
C <- rbind(BeforeH2,AfterH2)
colnames(C) <- c("2->0","1","-1->996","-9->997","-8->998") 
kable(C)
```

 
 


### Wave 7

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scchd`
* Label: `Whether the respondent has any children`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `-9 = Not answered`
    + `-8 = Don't know`
    + `-2 = Schedule Not Applicable`
    + `-1 = Item not applicable`
    
* Name: `DiGran`
* Label: `Whether respondent has any Whether the respondent has any children`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `-9 = Refusal`
    + `-8 = Don't Know`
    + `-2 = Schedule Not Applicable`
    + `-1 = Item not applicable`

* Description: 
```{r assign7, echo=F}
opal.assign.table.tibble(o, 'ELSA_w7_child','ELSA.wave_7_elsa_data',variables=list('scchd','DiGran'), missings = TRUE)
```

```{r local7, echo=F}
ELSA_w7_child <- opal.execute(o,'ELSA_w7_child')
vari <- ELSA_w7_child$scchd
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w7_child$scchd, missing_values = NA)
ggplot(ELSA_w7_child, aes(x=factor(scchd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Whether the respondent has any children") + ylab("Frequency")

vari <- ELSA_w7_child$DiGran
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w7_child$DiGran, missing_values = NA)
ggplot(ELSA_w7_child, aes(x=factor(DiGran))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Whether the respondent has any Whether the respondent has any children") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1 into 1`
* `2 into 0`

* `Missings for CHILD: -9 into 995; -8 into 998; -2 into 996; -1 into 996`
* `Missings for GRCHILD: -9 into 997; -8 into 998; -2 into 996; -1 into 996`

* `NA into 999`

**R script:**

```{r harmo7, echo=TRUE}
ELSA_ds_w7 <- tibble(id=ELSA_w7_child$id)
ELSA_ds_w7$child <- car::recode(as.vector(ELSA_w7_child$scchd), "1='1'; 2='0'; -9='995'; -8='998'; -2='996'; -1='996'; NA='999'")
ELSA_ds_w7$child <- labelled(ELSA_ds_w7$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))

ELSA_ds_w7$grchild <- car::recode(as.vector(ELSA_w7_child$DiGran), "1='1'; 2='0'; -9='997'; -8='998'; -2='996'; -1='996'; NA='999'")
ELSA_ds_w7$grchild <- labelled(ELSA_ds_w7$grchild, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript7, echo=F}
vari <- ELSA_ds_w7$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Children") 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w7$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w7, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")

vari <- ELSA_ds_w7$grchild
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Grandchildren") 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w7$grchild, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w7, aes(x=factor(grchild))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has grandchildren") + ylab("Frequency")
```

#### Validation
```{r crosstabulation7, echo=F}
AfterH1 <- table(ELSA_ds_w7$child)
BeforeH1 <- table(ELSA_w7_child$scchd, useNA='ifany')[c(4,3,1,2)]
C <- rbind(BeforeH1,AfterH1)
colnames(C) <- c("2->0","1","-9->995","-1->996") 
kable(C)

AfterH2 <- table(ELSA_ds_w7$grchild)
BeforeH2 <- table(ELSA_w7_child$DiGran, useNA='ifany')[c(5,4,3,1,2)]
C <- rbind(BeforeH2,AfterH2)
colnames(C) <- c("2->0","1","-1->996","-9->997","-8->998") 
kable(C)
```

 
# Quality estimation


```{r save, echo=FALSE}
child <- ELSA_ds_w1[,-3]
save(child, file = "../RData/w1/child.RData")
rm(child)

child <- ELSA_ds_w2[,-3]
save(child, file = "../RData/w2/child.RData")
rm(child)

child <- ELSA_ds_w3[,-3]
save(child, file = "../RData/w3/child.RData")
rm(child)

child <- ELSA_ds_w4[,-3]
save(child, file = "../RData/w4/child.RData")
rm(child)

child <- ELSA_ds_w5[,-3]
save(child, file = "../RData/w5/child.RData")
rm(child)

child <- ELSA_ds_w6[,-3]
save(child, file = "../RData/w6/child.RData")
rm(child)

child <- ELSA_ds_w7[,-3]
save(child, file = "../RData/w7/child.RData")
rm(child)

grchild <- ELSA_ds_w1[,-2]
save(grchild, file = "../RData/w1/grchild.RData")
rm(grchild)

grchild <- ELSA_ds_w2[,-2]
save(grchild, file = "../RData/w2/grchild.RData")
rm(grchild)

grchild <- ELSA_ds_w3[,-2]
save(grchild, file = "../RData/w3/grchild.RData")
rm(grchild)

grchild <- ELSA_ds_w4[,-2]
save(grchild, file = "../RData/w4/grchild.RData")
rm(grchild)

grchild <- ELSA_ds_w5[,-2]
save(grchild, file = "../RData/w5/grchild.RData")
rm(grchild)

grchild <- ELSA_ds_w6[,-2]
save(grchild, file = "../RData/w6/grchild.RData")
rm(grchild)

grchild <- ELSA_ds_w7[,-2]
save(grchild, file = "../RData/w7/grchild.RData")
rm(grchild)
```

```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
