---
title: "Has other (living) family members (e.g. parents, siblings, in-laws, etc.)"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup_iago.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `oth_fam`
* Variable label: `Has other (living) family members (e.g. parents, siblings, in-laws, etc.)`
* Domain: `Social environment`
* Value type: `categorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process

## England

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scfam`
* Label: `Do you have any other immediate family?`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `-9 = Not answered`
    + `-1 = Not applicable`
    
* Name: `Dinfa`
* Label: `Is your natural father still alive?`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `-9 = Refusal`
    + `-8 = Don't know`
    + `-1 = Not applicable`
    
* Name: `Dinma`
* Label: `Is your natural mother still alive?`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `-9 = Refusal`
    + `-8 = Don't know`
    + `-1 = Not applicable`

* Name: `Disib`
* Label: `How many living brothers or sisters do you have?`
* Missings:
    + `-9 = Refusal`
    + `-8 = Don't know`
    + `-1 = Not applicable`


* Description: 
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'ELSA_w1_oth_fam','ELSA.wave_1_core_data_v3', 
                        variables=list('scfam','dinfa','dinma','disib'), missings = TRUE)
```

```{r local1, echo=F}
ELSA_w1_oth_fam <- opal.execute(o,'ELSA_w1_oth_fam')

vari <- ELSA_w1_oth_fam$scfam
kable(Categorical_summary(vari, missing_values = c(-9,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w1_oth_fam$scfam, missing_values = NA)
ggplot(ELSA_w1_oth_fam, aes(x=factor(scfam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Do you have any other immediate family?") + ylab("Frequency")

vari <- ELSA_w1_oth_fam$scfam
kable(Categorical_summary(vari, missing_values = c(-9,-8,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-8,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w1_oth_fam$dinfa, missing_values = NA)
ggplot(ELSA_w1_oth_fam, aes(x=factor(dinfa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Is your natural father still alive?") + ylab("Frequency")

vari <- ELSA_w1_oth_fam$scfam
kable(Categorical_summary(vari, missing_values = c(-9,-8,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-8,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w1_oth_fam$dinma, missing_values = NA)
ggplot(ELSA_w1_oth_fam, aes(x=factor(dinma))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Is your natural mother still alive?") + ylab("Frequency")

vari <- ELSA_w1_oth_fam$disib
kable(Continuous_summary(vari, missing_values = c(-9,-8,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Continuous_summary(vari, missing_values = c(-9,-8,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values =c(-9,-8,-1))$summary, caption = "Summary")
#Continuous_summary(var = ELSA_w1_oth_fam$disib, missing_values = NA)
ggplot(ELSA_w1_oth_fam, aes(x=factor(disib))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How many living brothers or sisters do you have?") + ylab("Frequency")

## a lot of '-1=NA'in dinfa and dinma
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any eqauls 1 or disib>0 then 1`
* `if all are equal 2 and disib=0 then 0`
* `-1 into 996`
* `-8 into 998`
* `-9 into 997, but -9 for scfam into 995`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
ELSA_ds_w1 <- tibble(id=ELSA_w1_oth_fam$id)

ELSA_w1_oth_fam$scfam <- car::recode(as.vector(ELSA_w1_oth_fam$scfam), "NA='-999'")
ELSA_w1_oth_fam$dinfa <- car::recode(as.vector(ELSA_w1_oth_fam$dinfa), "NA='-999'")
ELSA_w1_oth_fam$dinma <- car::recode(as.vector(ELSA_w1_oth_fam$dinma), "NA='-999'")
ELSA_w1_oth_fam$disib <- car::recode(as.vector(ELSA_w1_oth_fam$disib), "NA='-999'")

ELSA_ds_w1$oth_fam <- c(NA)
for(i in 1:dim(ELSA_w1_oth_fam)[1]){
  if( ELSA_w1_oth_fam$scfam[i] == 1 | ELSA_w1_oth_fam$dinfa[i] == 1 |
      ELSA_w1_oth_fam$dinma[i] == 1 | ELSA_w1_oth_fam$disib[i] > 0 ){
    ELSA_ds_w1$oth_fam[i] = 1 }
  else if( ELSA_w1_oth_fam$scfam[i] == 2 & ELSA_w1_oth_fam$dinfa[i] %in% c(2,-1) &
      ELSA_w1_oth_fam$dinma[i] %in% c(2,-1) & ELSA_w1_oth_fam$disib[i] == 0 ){
    ELSA_ds_w1$oth_fam[i] = 0 }
  else if( ELSA_w1_oth_fam$scfam[i] == -8 | ELSA_w1_oth_fam$dinfa[i] == -8 |
      ELSA_w1_oth_fam$dinma[i] == -8 | ELSA_w1_oth_fam$disib[i] == -8 ){
    ELSA_ds_w1$oth_fam[i] = 998 }
  else if( ELSA_w1_oth_fam$dinfa[i] == -9 | ELSA_w1_oth_fam$dinma[i] == -9 | ELSA_w1_oth_fam$disib[i] == -9 ){
    ELSA_ds_w1$oth_fam[i] = 997 }
  else if( ELSA_w1_oth_fam$scfam[i] == -9 ){
    ELSA_ds_w1$oth_fam[i] = 995 } 
  else if( ELSA_w1_oth_fam$scfam[i] == -1 | ELSA_w1_oth_fam$dinfa[i] == -1 |
      ELSA_w1_oth_fam$dinma[i] == -1 | ELSA_w1_oth_fam$disib[i] == -1 ){
    ELSA_ds_w1$oth_fam[i] = 996 }
}

ELSA_ds_w1$oth_fam <- car::recode(as.vector(ELSA_ds_w1$oth_fam), "NA='999'")
ELSA_ds_w1$oth_fam <- labelled(ELSA_ds_w1$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <- ELSA_ds_w1$oth_fam
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w1$oth_fam, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w1, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}

```

 
 


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scfam`
* Label: `Whether the respondent has any other immediate family`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `-9 = Not answered`
    + `-1 = Item not applicable`

* Name: `DiNFA`
* Label: `Is your natural father still alive?`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `-9 = Refusal`
    + `-8 = Don't know`
    + `-1 = Not applicable`
    
* Name: `DiNMA`
* Label: `Is your natural mother still alive?`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `-9 = Refusal`
    + `-8 = Don't know`
    + `-1 = Not applicable`

* Name: `DiSib`
* Label: `How many living brothers or sisters do you have?`
* Missings:
    + `-9 = Refusal`
    + `-8 = Don't know`
    + `-1 = Not applicable`

* Description: 
```{r assign2, echo=F}
opal.assign.table.tibble(o, 'ELSA_w2_oth_fam','ELSA.wave_2_core_data_v4',
                         variables=list('scfam','DiNFA','DiNMA','DiSib'), missings = TRUE)
```

```{r local2, echo=F}
ELSA_w2_oth_fam <- opal.execute(o,'ELSA_w2_oth_fam')

vari <- ELSA_w2_oth_fam$scfam
kable(Categorical_summary(vari, missing_values = c(-9,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w2_oth_fam$scfam, missing_values = NA)
ggplot(ELSA_w2_oth_fam, aes(x=factor(scfam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Whether the respondent has any other immediate family") + ylab("Frequency")

vari <-ELSA_w2_oth_fam$DiNFA
kable(Categorical_summary(vari, missing_values = c(-9,-8,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-8,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w2_oth_fam$DiNFA, missing_values = NA)
ggplot(ELSA_w2_oth_fam, aes(x=factor(DiNFA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Is your natural father still alive?") + ylab("Frequency")

vari <- ELSA_w2_oth_fam$DiNMA
kable(Categorical_summary(vari, missing_values = c(-9,-8,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-8,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w2_oth_fam$DiNMA, missing_values = NA)
ggplot(ELSA_w2_oth_fam, aes(x=factor(DiNMA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Is your natural mother still alive?") + ylab("Frequency")

vari <- ELSA_w2_oth_fam$DiSib
kable(Continuous_summary(vari, missing_values = c(-9,-8,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Continuous_summary(vari, missing_values = c(-9,-8,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values =c(-9,-8,-1))$summary, caption = "Summary")
#Continuous_summary(var = ELSA_w2_oth_fam$DiSib, missing_values = NA)
ggplot(ELSA_w2_oth_fam, aes(x=factor(DiSib))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of living brothers/sisters") + ylab("Frequency")

## a lot of '-1=NA'in dinfa and dinma
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if any eqauls 1 or DiSib>0 then 1`
* `if all are equal 2 and DiSib=0 then 0`
* `-1 into 996`
* `-8 into 998`
* `-9 into 997, but -9 for scfam into 995`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
ELSA_ds_w2 <- tibble(id=ELSA_w2_oth_fam$id)

ELSA_w2_oth_fam$scfam <- car::recode(as.vector(ELSA_w2_oth_fam$scfam), "NA='-999'")
ELSA_w2_oth_fam$DiNFA <- car::recode(as.vector(ELSA_w2_oth_fam$DiNFA), "NA='-999'")
ELSA_w2_oth_fam$DiNMA <- car::recode(as.vector(ELSA_w2_oth_fam$DiNMA), "NA='-999'")
ELSA_w2_oth_fam$DiSib <- car::recode(as.vector(ELSA_w2_oth_fam$DiSib), "NA='-999'")

ELSA_ds_w2$oth_fam <- c(NA)
for(i in 1:dim(ELSA_w2_oth_fam)[1]){
  if( ELSA_w2_oth_fam$scfam[i] == 1 | ELSA_w2_oth_fam$DiNFA[i] == 1 |
      ELSA_w2_oth_fam$DiNMA[i] == 1 | ELSA_w2_oth_fam$DiSib[i] > 0 ){
    ELSA_ds_w2$oth_fam[i] = 1 }
  else if( ELSA_w2_oth_fam$scfam[i] == 2 & ELSA_w2_oth_fam$DiNFA[i] %in% c(2,-1) &
      ELSA_w2_oth_fam$DiNMA[i] %in% c(2,-1) & ELSA_w2_oth_fam$DiSib[i] == 0 ){
    ELSA_ds_w2$oth_fam[i] = 0 }
  else if( ELSA_w2_oth_fam$scfam[i] == -8 | ELSA_w2_oth_fam$DiNFA[i] == -8 |
      ELSA_w2_oth_fam$DiNMA[i] == -8 | ELSA_w2_oth_fam$DiSib[i] == -8 ){
    ELSA_ds_w2$oth_fam[i] = 998 }
  else if( ELSA_w2_oth_fam$DiNFA[i] == -9 | ELSA_w2_oth_fam$DiNMA[i] == -9 | ELSA_w2_oth_fam$DiSib[i] == -9 ){
    ELSA_ds_w2$oth_fam[i] = 997 }
  else if( ELSA_w2_oth_fam$scfam[i] == -9 ){
    ELSA_ds_w2$oth_fam[i] = 995 } 
  else if( ELSA_w2_oth_fam$scfam[i] == -1 | ELSA_w2_oth_fam$DiNFA[i] == -1 |
      ELSA_w2_oth_fam$DiNMA[i] == -1 | ELSA_w2_oth_fam$DiSib[i] == -1 ){
    ELSA_ds_w2$oth_fam[i] = 996 }
}

ELSA_ds_w2$oth_fam <- car::recode(as.vector(ELSA_ds_w2$oth_fam), "NA='999'")
ELSA_ds_w2$oth_fam <- labelled(ELSA_ds_w2$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}
vari <- ELSA_ds_w2$oth_fam
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w2$oth_fam, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w2, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}

```

 
 


### Wave 3

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scfam`
* Label: `Whether the respondent has any other immediate family`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `-1 = Item not applicable`
    + `-8 = Don't know`
    + `-9 = Not answered`
    
    
* Name: `dinfa`
* Label: `Is your natural father still alive?`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `-9 = Refusal`
    + `-8 = Don't know`
    + `-2 = Schedule not applicable`
    + `-1 = Not applicable`
    
* Name: `dinma`
* Label: `Is your natural mother still alive?`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `-9 = Refusal`
    + `-8 = Don't know`
    + `-2 = Schedule not applicable`
    + `-1 = Not applicable`

* Name: `disib`
* Label: `Number of living brothers/sisters`
* Missings:
    + `-9 = Refusal`
    + `-8 = Don't know`
    + `-1 = Not applicable`


* Description: 
```{r assign3, echo=F}
opal.assign.table.tibble(o, 'ELSA_w3_oth_fam','ELSA.wave_3_elsa_data_v4',
                         variables=list('scfam','dinfa','dinma','disib'), missings = TRUE)
```

```{r local3, echo=F}
ELSA_w3_oth_fam <- opal.execute(o,'ELSA_w3_oth_fam')

vari <- ELSA_w3_oth_fam$scfam
kable(Categorical_summary(vari, missing_values = c(-9,-8,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-8,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w3_oth_fam$scfam, missing_values = NA)
ggplot(ELSA_w3_oth_fam, aes(x=factor(scfam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Whether the respondent has any other immediate family") + ylab("Frequency")

vari <- ELSA_w3_oth_fam$dinfa
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w3_oth_fam$dinfa, missing_values = NA)
ggplot(ELSA_w3_oth_fam, aes(x=factor(dinfa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Is your natural father still alive?") + ylab("Frequency")

vari <- ELSA_w3_oth_fam$dinma
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w3_oth_fam$dinma, missing_values = NA)
ggplot(ELSA_w3_oth_fam, aes(x=factor(dinma))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Is your natural mother still alive?") + ylab("Frequency")

vari <- ELSA_w3_oth_fam$disib
kable(Continuous_summary(vari, missing_values = c(-9,-8,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Continuous_summary(vari, missing_values = c(-9,-8,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values =c(-9,-8,-1))$summary, caption = "Summary")
#Continuous_summary(var = ELSA_w3_oth_fam$disib, missing_values = NA)
ggplot(ELSA_w3_oth_fam, aes(x=factor(disib))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of living brothers/sisters") + ylab("Frequency")

## a lot of '-1=NA'in dinfa and dinma
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if any eqauls 1 or disib>0 then 1`
* `if all are equal 2 and disib=0 then 0`
* `-1 into 996`
* `-2 into 996`
* `-8 into 998`
* `-9 into 997, but -9 for scfam into 995`
* `NA into 999`

**R script:**

```{r harmo3, echo=TRUE}
ELSA_ds_w3 <- tibble(id=ELSA_w3_oth_fam$id)

ELSA_w3_oth_fam$scfam <- car::recode(as.vector(ELSA_w3_oth_fam$scfam), "NA='-999'")
ELSA_w3_oth_fam$dinfa <- car::recode(as.vector(ELSA_w3_oth_fam$dinfa), "NA='-999'")
ELSA_w3_oth_fam$dinma <- car::recode(as.vector(ELSA_w3_oth_fam$dinma), "NA='-999'")
ELSA_w3_oth_fam$disib <- car::recode(as.vector(ELSA_w3_oth_fam$disib), "NA='-999'")

ELSA_ds_w3$oth_fam <- c(NA)
for(i in 1:dim(ELSA_w3_oth_fam)[1]){
  if( ELSA_w3_oth_fam$scfam[i] == 1 | ELSA_w3_oth_fam$dinfa[i] == 1 |
      ELSA_w3_oth_fam$dinma[i] == 1 | ELSA_w3_oth_fam$disib[i] > 0 ){
    ELSA_ds_w3$oth_fam[i] = 1 }
  else if( ELSA_w3_oth_fam$scfam[i] == 2 & ELSA_w3_oth_fam$dinfa[i] %in% c(2,-1) &
      ELSA_w3_oth_fam$dinma[i] %in% c(2,-1) & ELSA_w3_oth_fam$disib[i] == 0 ){
    ELSA_ds_w3$oth_fam[i] = 0 }
  else if( ELSA_w3_oth_fam$scfam[i] == -8 | ELSA_w3_oth_fam$dinfa[i] == -8 |
      ELSA_w3_oth_fam$dinma[i] == -8 | ELSA_w3_oth_fam$disib[i] == -8 ){
    ELSA_ds_w3$oth_fam[i] = 998 }
  else if(  ELSA_w3_oth_fam$dinfa[i] == -2 | ELSA_w3_oth_fam$dinma[i] == -2 ){
    ELSA_ds_w3$oth_fam[i] = 996 }
  else if( ELSA_w3_oth_fam$dinfa[i] == -9 | ELSA_w3_oth_fam$dinma[i] == -9 | ELSA_w3_oth_fam$disib[i] == -9 ){
    ELSA_ds_w3$oth_fam[i] = 997 }
  else if( ELSA_w3_oth_fam$scfam[i] == -9 ){
    ELSA_ds_w3$oth_fam[i] = 995 } 
  else if( ELSA_w3_oth_fam$scfam[i] == -1 | ELSA_w3_oth_fam$dinfa[i] == -1 |
      ELSA_w3_oth_fam$dinma[i] == -1 | ELSA_w3_oth_fam$disib[i] == -1 ){
    ELSA_ds_w3$oth_fam[i] = 996 }
}

ELSA_ds_w3$oth_fam <- car::recode(as.vector(ELSA_ds_w3$oth_fam), "NA='999'")
ELSA_ds_w3$oth_fam <- labelled(ELSA_ds_w3$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=F}
vari <- ELSA_ds_w3$oth_fam
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w3$oth_fam, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w3, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Has other family members?") + ylab("Frequency")
```

##### Validation
```{r crosstabulation3, echo=F}

```

 
 

### Wave 4

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scfam`
* Label: `Whether the respondent has any other immediate family`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `-1 = Item not applicable`
    + `-8 = Don't know`
    + `-9 = Not answered`
    
* Name: `dinfa`
* Label: `Is your natural father still alive?`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `-9 = Refusal`
    + `-8 = Don't know`
    + `-2 = Capi/Interview Error`
    + `-1 = Not applicable`
    
* Name: `dinma`
* Label: `Is your natural mother still alive?`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `-9 = Refusal`
    + `-8 = Don't know`
    + `-2 = Capi/Interview Error`
    + `-1 = Not applicable`

* Name: `disib`
* Label: `Number of living brothers/sisters`
* Missings:
    + `-9 = Refusal`
    + `-8 = Don't know`
    + `-2 = Capi/Interview Error`
    + `-1 = Not applicable`


* Description: 
```{r assign4, echo=F}
opal.assign.table.tibble(o, 'ELSA_w4_oth_fam','ELSA.wave_4_elsa_data_v3',
                         variables=list('scfam','dinfa','dinma','disib'), missings = TRUE)
```

```{r local4, echo=F}
ELSA_w4_oth_fam <- opal.execute(o,'ELSA_w4_oth_fam')
vari <- ELSA_w4_oth_fam$scfam
kable(Categorical_summary(vari, missing_values = c(-9,-8,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-8,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w4_oth_fam$scfam, missing_values = NA)
ggplot(ELSA_w4_oth_fam, aes(x=factor(scfam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Whether the respondent has any other immediate family") + ylab("Frequency")

vari <- ELSA_w4_oth_fam$dinfa
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w4_oth_fam$dinfa, missing_values = NA)
ggplot(ELSA_w4_oth_fam, aes(x=factor(dinfa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Is your natural father still alive?") + ylab("Frequency")

vari <- ELSA_w4_oth_fam$dinma
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w4_oth_fam$dinma, missing_values = NA)
ggplot(ELSA_w4_oth_fam, aes(x=factor(dinma))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Is your natural mother still alive?") + ylab("Frequency")

vari <- ELSA_w4_oth_fam$disib
kable(Continuous_summary(vari, missing_values = c(-9,-8,-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Continuous_summary(vari, missing_values = c(-9,-8,-2,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values =c(-9,-8,-2,-1))$summary, caption = "Summary")
#Continuous_summary(var = ELSA_w4_oth_fam$disib, missing_values = NA)
ggplot(ELSA_w4_oth_fam, aes(x=factor(disib))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of living brothers/sisters") + ylab("Frequency")

## a lot of '-1=NA'in dinfa and dinma
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if any eqauls 1 or disib>0 then 1`
* `if all are equal 2 and disib=0 then 0`
* `-1 into 996`
* `-2 into 991`
* `-8 into 998`
* `-9 into 997, but -9 for scfam into 995`
* `NA into 999`

**R script:**

```{r harmo4, echo=TRUE}
ELSA_ds_w4 <- tibble(id=ELSA_w4_oth_fam$id)

ELSA_w4_oth_fam$scfam <- car::recode(as.vector(ELSA_w4_oth_fam$scfam), "NA='-999'")
ELSA_w4_oth_fam$dinfa <- car::recode(as.vector(ELSA_w4_oth_fam$dinfa), "NA='-999'")
ELSA_w4_oth_fam$dinma <- car::recode(as.vector(ELSA_w4_oth_fam$dinma), "NA='-999'")
ELSA_w4_oth_fam$disib <- car::recode(as.vector(ELSA_w4_oth_fam$disib), "NA='-999'")

ELSA_ds_w4$oth_fam <- c(NA)
for(i in 1:dim(ELSA_w4_oth_fam)[1]){
  if( ELSA_w4_oth_fam$scfam[i] == 1 | ELSA_w4_oth_fam$dinfa[i] == 1 |
      ELSA_w4_oth_fam$dinma[i] == 1 | ELSA_w4_oth_fam$disib[i] > 0 ){
    ELSA_ds_w4$oth_fam[i] = 1 }
  else if( ELSA_w4_oth_fam$scfam[i] == 2 & ELSA_w4_oth_fam$dinfa[i] %in% c(2,-1) &
      ELSA_w4_oth_fam$dinma[i] %in% c(2,-1) & ELSA_w4_oth_fam$disib[i] == 0 ){
    ELSA_ds_w4$oth_fam[i] = 0 }
  else if( ELSA_w4_oth_fam$scfam[i] == -8 | ELSA_w4_oth_fam$dinfa[i] == -8 |
      ELSA_w4_oth_fam$dinma[i] == -8 | ELSA_w4_oth_fam$disib[i] == -8 ){
    ELSA_ds_w4$oth_fam[i] = 998 }
  else if(  ELSA_w4_oth_fam$dinfa[i] == -2 | ELSA_w4_oth_fam$dinma[i] == -2 | ELSA_w4_oth_fam$disib[i] == -2 ){
    ELSA_ds_w4$oth_fam[i] = 991 }
  else if( ELSA_w4_oth_fam$dinfa[i] == -9 | ELSA_w4_oth_fam$dinma[i] == -9 | ELSA_w4_oth_fam$disib[i] == -9 ){
    ELSA_ds_w4$oth_fam[i] = 997 }
  else if( ELSA_w4_oth_fam$scfam[i] == -9 ){
    ELSA_ds_w4$oth_fam[i] = 995 } 
  else if( ELSA_w4_oth_fam$scfam[i] == -1 | ELSA_w4_oth_fam$dinfa[i] == -1 |
      ELSA_w4_oth_fam$dinma[i] == -1 | ELSA_w4_oth_fam$disib[i] == -1 ){
    ELSA_ds_w4$oth_fam[i] = 996 }
}

ELSA_ds_w4$oth_fam <- car::recode(as.vector(ELSA_ds_w4$oth_fam), "NA='999'")
ELSA_ds_w4$oth_fam <- labelled(ELSA_ds_w4$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4, echo=F}
vari <- ELSA_ds_w4$oth_fam
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w4$oth_fam, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w4, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=F}

```

 
 

### Wave 5

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scfam`
* Label: `Whether the respondent has any other immediate family`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `-1 = Item not applicable`
    + `-2 = Schedule not applicable`
    + `-8 = Don't know`
    + `-9 = Not answered`
    
* Name: `dinfa`
* Label: `Is your natural father still alive?`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `-9 = Refusal`
    + `-8 = Don't know`
    + `-2 = Schedule not applicable`
    + `-1 = Not applicable`
    
* Name: `dinma`
* Label: `Is your natural mother still alive?`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `-9 = Refusal`
    + `-8 = Don't know`
    + `-2 = Schedule not applicable`
    + `-1 = Not applicable`

* Name: `disib`
* Label: `Number of living brothers/sisters`
* Missings:
    + `-9 = Refusal`
    + `-8 = Don't know`
    + `-1 = Not applicable`
    
    
* Description: 
```{r assign5, echo=F}
opal.assign.table.tibble(o, 'ELSA_w5_oth_fam','ELSA.wave_5_elsa_data_v4',
                         variables=list('scfam','dinfa','dinma','disib'), missings = TRUE)
```

```{r local5, echo=F}
ELSA_w5_oth_fam <- opal.execute(o,'ELSA_w5_oth_fam')

vari <- ELSA_w5_oth_fam$scfam
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w5_oth_fam$scfam, missing_values = NA)
ggplot(ELSA_w5_oth_fam, aes(x=factor(scfam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Whether the respondent has any other immediate family") + ylab("Frequency")

vari <- ELSA_w5_oth_fam$dinfa
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w5_oth_fam$dinfa, missing_values = NA)
ggplot(ELSA_w5_oth_fam, aes(x=factor(dinfa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Is your natural father still alive?") + ylab("Frequency")

vari <- ELSA_w5_oth_fam$dinma
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w5_oth_fam$dinma, missing_values = NA)
ggplot(ELSA_w5_oth_fam, aes(x=factor(dinma))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Is your natural mother still alive?") + ylab("Frequency")

vari <- ELSA_w5_oth_fam$disib
kable(Continuous_summary(vari, missing_values = c(-9,-8,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Continuous_summary(vari, missing_values = c(-9,-8,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values =c(-9,-8,-1))$summary, caption = "Summary")
#Continuous_summary(var = ELSA_w5_oth_fam$disib, missing_values = NA)
ggplot(ELSA_w5_oth_fam, aes(x=factor(disib))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of living brothers/sisters") + ylab("Frequency")

## a lot of '-1=NA'in dinfa and dinma
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows: 

* `if any eqauls 1 or disib>0 then 1`
* `if all are equal 2 and disib=0 then 0`
* `-1 or -2 into 996`
* `-8 into 998`
* `-9 into 997, but -9 for scfam into 995`
* `NA into 999`

**R script:**

```{r harmo5, echo=TRUE}
ELSA_ds_w5 <- tibble(id=ELSA_w5_oth_fam$id)

ELSA_w5_oth_fam$scfam <- car::recode(as.vector(ELSA_w5_oth_fam$scfam), "NA='-999'")
ELSA_w5_oth_fam$dinfa <- car::recode(as.vector(ELSA_w5_oth_fam$dinfa), "NA='-999'")
ELSA_w5_oth_fam$dinma <- car::recode(as.vector(ELSA_w5_oth_fam$dinma), "NA='-999'")
ELSA_w5_oth_fam$disib <- car::recode(as.vector(ELSA_w5_oth_fam$disib), "NA='-999'")

ELSA_ds_w5$oth_fam <- c(NA)
for(i in 1:dim(ELSA_w5_oth_fam)[1]){
  if( ELSA_w5_oth_fam$scfam[i] == 1 | ELSA_w5_oth_fam$dinfa[i] == 1 |
      ELSA_w5_oth_fam$dinma[i] == 1 | ELSA_w5_oth_fam$disib[i] > 0 ){
    ELSA_ds_w5$oth_fam[i] = 1 }
  else if( ELSA_w5_oth_fam$scfam[i] == 2 & ELSA_w5_oth_fam$dinfa[i] %in% c(2,-1) &
      ELSA_w5_oth_fam$dinma[i] %in% c(2,-1) & ELSA_w5_oth_fam$disib[i] == 0 ){
    ELSA_ds_w5$oth_fam[i] = 0 }
  else if( ELSA_w5_oth_fam$scfam[i] == -8 | ELSA_w5_oth_fam$dinfa[i] == -8 |
      ELSA_w5_oth_fam$dinma[i] == -8 | ELSA_w5_oth_fam$disib[i] == -8 ){
    ELSA_ds_w5$oth_fam[i] = 998 }
  else if( ELSA_w5_oth_fam$scfam[i] == -2 | ELSA_w5_oth_fam$dinfa[i] == -2 | 
           ELSA_w5_oth_fam$dinma[i] == -2 | ELSA_w5_oth_fam$disib[i] == -2 ){
    ELSA_ds_w5$oth_fam[i] = 996 }
  else if( ELSA_w5_oth_fam$dinfa[i] == -9 | ELSA_w5_oth_fam$dinma[i] == -9 | ELSA_w5_oth_fam$disib[i] == -9 ){
    ELSA_ds_w5$oth_fam[i] = 997 }
  else if( ELSA_w5_oth_fam$scfam[i] == -9 ){
    ELSA_ds_w5$oth_fam[i] = 995 } 
  else if( ELSA_w5_oth_fam$scfam[i] == -1 | ELSA_w5_oth_fam$dinfa[i] == -1 |
      ELSA_w5_oth_fam$dinma[i] == -1 | ELSA_w5_oth_fam$disib[i] == -1 ){
    ELSA_ds_w5$oth_fam[i] = 996 }
}

ELSA_ds_w5$oth_fam <- car::recode(as.vector(ELSA_ds_w5$oth_fam), "NA='999'")
ELSA_ds_w5$oth_fam <- labelled(ELSA_ds_w5$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript5, echo=F}
vari <- ELSA_ds_w5$oth_fam
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w5$oth_fam, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w5, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation5, echo=F}

```

 
 

### Wave 6

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scfam`
* Label: `Whether the respondent has any other immediate family`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `-1 = Item not applicable`
    + `-2 = Schedule not applicable`
    + `-8 = Don't know`
    + `-9 = Not answered`
    
* Name: `DiNFA`
* Label: `Is your natural father still alive?`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `-9 = Refusal`
    + `-8 = Don't know`
    + `-2 = Schedule not applicable`
    + `-1 = Not applicable`
    
* Name: `DiNMA`
* Label: `Is your natural mother still alive?`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `-9 = Refusal`
    + `-8 = Don't know`
    + `-2 = Schedule not applicable`
    + `-1 = Not applicable`

* Name: `DiSib`
* Label: `Number of living brothers/sisters`
* Missings:
    + `-9 = Refusal`
    + `-8 = Don't know`
    + `-2 = Schedule not applicable`
    + `-1 = Not applicable`
    

* Description: 
```{r assign6, echo=F}
opal.assign.table.tibble(o, 'ELSA_w6_oth_fam','ELSA.wave_6_elsa_data_v2',
                         variables=list('scfam','DiNMA','DiNFA','DiSib'), missings = TRUE)
```

```{r local6, echo=F}
ELSA_w6_oth_fam <- opal.execute(o,'ELSA_w6_oth_fam')

vari <- ELSA_w6_oth_fam$scfam
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w6_oth_fam$scfam, missing_values = NA)
ggplot(ELSA_w6_oth_fam, aes(x=factor(scfam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")

vari <- ELSA_w6_oth_fam$DiNMA
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w6_oth_fam$DiNMA, missing_values = NA)
ggplot(ELSA_w6_oth_fam, aes(x=factor(DiNMA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Is your natural mother still alive?") + ylab("Frequency")

vari <- ELSA_w6_oth_fam$DiNFA
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w6_oth_fam$DiNFA, missing_values = NA)
ggplot(ELSA_w6_oth_fam, aes(x=factor(DiNFA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("HIs your natural father still alive?") + ylab("Frequency")

vari <- ELSA_w6_oth_fam$DiSib
kable(Continuous_summary(vari, missing_values = c(-9,-8,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Continuous_summary(vari, missing_values = c(-9,-8,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values =c(-9,-8,-1))$summary, caption = "Summary")
#Categorical_summary(var = ELSA_w6_oth_fam$DiSib, missing_values = NA)
ggplot(ELSA_w6_oth_fam, aes(x=factor(DiSib))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of living brothers/sisters") + ylab("Frequency")

## a lot of '-1=NA'in DiNFA and DiNMA
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if any eqauls 1 or DiSib>0 then 1`
* `if all are equal 2 and DiSib=0 then 0`
* `-1 or -2 into 996`
* `-8 into 998`
* `-9 into 997, but -9 for scfam into 995`
* `NA into 999`

**R script:**

```{r harmo6, echo=TRUE}
ELSA_ds_w6 <- tibble(id=ELSA_w6_oth_fam$id)

ELSA_w6_oth_fam$scfam <- car::recode(as.vector(ELSA_w6_oth_fam$scfam), "NA='-999'")
ELSA_w6_oth_fam$DiNFA <- car::recode(as.vector(ELSA_w6_oth_fam$DiNFA), "NA='-999'")
ELSA_w6_oth_fam$DiNMA <- car::recode(as.vector(ELSA_w6_oth_fam$DiNMA), "NA='-999'")
ELSA_w6_oth_fam$DiSib <- car::recode(as.vector(ELSA_w6_oth_fam$DiSib), "NA='-999'")

ELSA_ds_w6$oth_fam <- c(NA)
for(i in 1:dim(ELSA_w6_oth_fam)[1]){
  if( ELSA_w6_oth_fam$scfam[i] == 1 | ELSA_w6_oth_fam$DiNFA[i] == 1 |
      ELSA_w6_oth_fam$DiNMA[i] == 1 | ELSA_w6_oth_fam$DiSib[i] > 0 ){
    ELSA_ds_w6$oth_fam[i] = 1 }
  else if( ELSA_w6_oth_fam$scfam[i] == 2 & ELSA_w6_oth_fam$DiNFA[i] %in% c(2,-1) &
      ELSA_w6_oth_fam$DiNMA[i] %in% c(2,-1) & ELSA_w6_oth_fam$DiSib[i] == 0 ){
    ELSA_ds_w6$oth_fam[i] = 0 }
  else if( ELSA_w6_oth_fam$scfam[i] == -8 | ELSA_w6_oth_fam$DiNFA[i] == -8 |
      ELSA_w6_oth_fam$DiNMA[i] == -8 | ELSA_w6_oth_fam$DiSib[i] == -8 ){
    ELSA_ds_w6$oth_fam[i] = 998 }
  else if( ELSA_w6_oth_fam$scfam[i] == -2 | ELSA_w6_oth_fam$DiNFA[i] == -2 | 
           ELSA_w6_oth_fam$DiNMA[i] == -2 | ELSA_w6_oth_fam$DiSib[i] == -2 ){
    ELSA_ds_w6$oth_fam[i] = 996 }
  else if( ELSA_w6_oth_fam$DiNFA[i] == -9 | ELSA_w6_oth_fam$DiNMA[i] == -9 | ELSA_w6_oth_fam$DiSib[i] == -9 ){
    ELSA_ds_w6$oth_fam[i] = 997 }
  else if( ELSA_w6_oth_fam$scfam[i] == -9 ){
    ELSA_ds_w6$oth_fam[i] = 995 } 
  else if( ELSA_w6_oth_fam$scfam[i] == -1 | ELSA_w6_oth_fam$DiNFA[i] == -1 |
           ELSA_w6_oth_fam$DiNMA[i] == -1 | ELSA_w6_oth_fam$DiSib[i] == -1 ){
    ELSA_ds_w6$oth_fam[i] = 996 }
}

ELSA_ds_w6$oth_fam <- car::recode(as.vector(ELSA_ds_w6$oth_fam), "NA='999'")
ELSA_ds_w6$oth_fam <- labelled(ELSA_ds_w6$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript6, echo=F}
vari <- ELSA_ds_w6$oth_fam
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w6$oth_fam, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w6, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation6, echo=F}

```

 
 


### Wave 7

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scfam`
* Label: `Whether the respondent has any other immediate family`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `-1 = Item not applicable`
    + `-2 = Schedule not applicable`
    + `-8 = Don't know`
    + `-9 = Not answered`
    
* Name: `DiNFA`
* Label: `Is your natural father still alive?`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `-9 = Refusal`
    + `-8 = Don't know`
    + `-2 = Schedule not applicable`
    + `-1 = Not applicable`
    
* Name: `DiNMA`
* Label: `Is your natural mother still alive?`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `-9 = Refusal`
    + `-8 = Don't know`
    + `-2 = Schedule not applicable`
    + `-1 = Not applicable`

* Name: `DiSib`
* Label: `Number of living brothers/sisters`
* Missings:
    + `-9 = Refusal`
    + `-8 = Don't know`
    + `-2 = Schedule not applicable`
    + `-1 = Not applicable`
    

* Description: 
```{r assign7, echo=F}
opal.assign.table.tibble(o, 'ELSA_w7_oth_fam','ELSA.wave_7_elsa_data',
                         variables=list('scfam','DiNMA','DiNFA','DiSib'), missings = TRUE)
```

```{r local7, echo=F}
ELSA_w7_oth_fam <- opal.execute(o,'ELSA_w7_oth_fam')

vari <- ELSA_w7_oth_fam$scfam
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w7_oth_fam$scfam, missing_values = NA)
ggplot(ELSA_w7_oth_fam, aes(x=factor(scfam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")

vari <- ELSA_w7_oth_fam$DiNMA
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w7_oth_fam$DiNMA, missing_values = NA)
ggplot(ELSA_w7_oth_fam, aes(x=factor(DiNMA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Is your natural mother still alive?") + ylab("Frequency")

vari <- ELSA_w7_oth_fam$DiNFA
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-2,-1))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w7_oth_fam$DiNFA, missing_values = NA)
ggplot(ELSA_w7_oth_fam, aes(x=factor(DiNFA))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("HIs your natural father still alive?") + ylab("Frequency")

vari <- ELSA_w7_oth_fam$DiSib
kable(Continuous_summary(vari, missing_values = c(-9,-8,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Continuous_summary(vari, missing_values = c(-9,-8,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values =c(-9,-8,-1))$summary, caption = "Summary")
#Categorical_summary(var = ELSA_w7_oth_fam$DiSib, missing_values = NA)
ggplot(ELSA_w7_oth_fam, aes(x=factor(DiSib))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of living brothers/sisters") + ylab("Frequency")

## a lot of '-1=NA'in DiNFA and DiNMA
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if any eqauls 1 or DiSib>0 then 1`
* `if all are equal 2 and DiSib=0 then 0`
* `-1 or -2 into 996`
* `-8 into 998`
* `-9 into 997, but -9 for scfam into 995`
* `NA into 999`

**R script:**

```{r harmo7, echo=TRUE}
ELSA_ds_w7 <- tibble(id=ELSA_w7_oth_fam$id)

ELSA_w7_oth_fam$scfam <- car::recode(as.vector(ELSA_w7_oth_fam$scfam), "NA='-999'")
ELSA_w7_oth_fam$DiNFA <- car::recode(as.vector(ELSA_w7_oth_fam$DiNFA), "NA='-999'")
ELSA_w7_oth_fam$DiNMA <- car::recode(as.vector(ELSA_w7_oth_fam$DiNMA), "NA='-999'")
ELSA_w7_oth_fam$DiSib <- car::recode(as.vector(ELSA_w7_oth_fam$DiSib), "NA='-999'")

ELSA_ds_w7$oth_fam <- c(NA)
for(i in 1:dim(ELSA_w7_oth_fam)[1]){
  if( ELSA_w7_oth_fam$scfam[i] == 1 | ELSA_w7_oth_fam$DiNFA[i] == 1 |
      ELSA_w7_oth_fam$DiNMA[i] == 1 | ELSA_w7_oth_fam$DiSib[i] > 0 ){
    ELSA_ds_w7$oth_fam[i] = 1 }
  else if( ELSA_w7_oth_fam$scfam[i] == 2 & ELSA_w7_oth_fam$DiNFA[i] %in% c(2,-1) &
      ELSA_w7_oth_fam$DiNMA[i] %in% c(2,-1) & ELSA_w7_oth_fam$DiSib[i] == 0 ){
    ELSA_ds_w7$oth_fam[i] = 0 }
  else if( ELSA_w7_oth_fam$scfam[i] == -8 | ELSA_w7_oth_fam$DiNFA[i] == -8 |
      ELSA_w7_oth_fam$DiNMA[i] == -8 | ELSA_w7_oth_fam$DiSib[i] == -8 ){
    ELSA_ds_w7$oth_fam[i] = 998 }
  else if( ELSA_w7_oth_fam$scfam[i] == -2 | ELSA_w7_oth_fam$DiNFA[i] == -2 | 
           ELSA_w7_oth_fam$DiNMA[i] == -2 | ELSA_w7_oth_fam$DiSib[i] == -2 ){
    ELSA_ds_w7$oth_fam[i] = 996 }
  else if( ELSA_w7_oth_fam$DiNFA[i] == -9 | ELSA_w7_oth_fam$DiNMA[i] == -9 | ELSA_w7_oth_fam$DiSib[i] == -9 ){
    ELSA_ds_w7$oth_fam[i] = 997 }
  else if( ELSA_w7_oth_fam$scfam[i] == -9 ){
    ELSA_ds_w7$oth_fam[i] = 995 } 
  else if( ELSA_w7_oth_fam$scfam[i] == -1 | ELSA_w7_oth_fam$DiNFA[i] == -1 |
           ELSA_w7_oth_fam$DiNMA[i] == -1 | ELSA_w7_oth_fam$DiSib[i] == -1 ){
    ELSA_ds_w7$oth_fam[i] = 996 }
}

ELSA_ds_w7$oth_fam <- car::recode(as.vector(ELSA_ds_w7$oth_fam), "NA='999'")
ELSA_ds_w7$oth_fam <- labelled(ELSA_ds_w7$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript7, echo=F}
vari <- ELSA_ds_w7$oth_fam
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w7$oth_fam, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w7, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation7, echo=F}

```

 

```{r save, echo=FALSE}
oth_fam <- ELSA_ds_w1
save(oth_fam, file = "../RData/w1/oth_fam.RData")
rm(oth_fam)

oth_fam <- ELSA_ds_w2
save(oth_fam, file = "../RData/w2/oth_fam.RData")
rm(oth_fam)

oth_fam <- ELSA_ds_w3
save(oth_fam, file = "../RData/w3/oth_fam.RData")
rm(oth_fam)

oth_fam <- ELSA_ds_w4
save(oth_fam, file = "../RData/w4/oth_fam.RData")
rm(oth_fam)

oth_fam <- ELSA_ds_w5
save(oth_fam, file = "../RData/w5/oth_fam.RData")
rm(oth_fam)

oth_fam <- ELSA_ds_w6
save(oth_fam, file = "../RData/w6/oth_fam.RData")
rm(oth_fam)

oth_fam <- ELSA_ds_w7
save(oth_fam, file = "../RData/w7/oth_fam.RData")
rm(oth_fam)
```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
