---
title: "Frequency of phone or mail contacts with friends"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/f_other_frDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/f_other_frDS.R')
```

# Data process

## England

### Wave 1 

#### Study-specific variable description



| **Name** |`scfrd`|`scfrdh`|`scfrdi`|
|-|-|-|-|
| **Label** |`do you have any friends`|`on average how often do you speak on the phone with your friends`|`on average how often do you write or email your friends`|
| **Table name** |`wave_1_core_data_v3`|`wave_1_core_data_v3`|`wave_1_core_data_v3`|
| **Categories** |`1 = Yes`<br/>`2 = No`|`1 = Three or more times a week`<br/>`2 = Once or twice a week`<br/>`3 = Once or twice a month`<br/>`4 = Every few months`<br/>`5 = Once or twice a year`<br/>`6 = Less than once a year or never`|`1 = Three or more times a week`<br/>`2 = Once or twice a week`<br/>`3 = Once or twice a month`<br/>`4 = Every few months`<br/>`5 = Once or twice a year`<br/>`6 = Less than once a year or never`|
| **Missings**|`-9 = Not answered`<br/>`-1 = Item not applicable`|`-9 = Not answered`<br/>`-1 = Item not applicable`|`-9 = Not answered`<br/>`-1 = Item not applicable`|
| **Description** |  |  |  |




```{r assign1, echo=F}
opal.assign.table.tibble(o, 'ELSA_w1','ELSA.wave_1_core_data_v3',variables=list('scfrd','scfrdh','scfrdi'), missings = TRUE)
ELSA_w1 <- opal.execute(o,'ELSA_w1')
```

```{r local1, echo=F}
vbl <- ELSA_w1$scfrd
vbl_miss <- c(-9,-1)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = "scfrd")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Type of missing")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(scfrd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has got any friends?") + ylab("Frequency")
vbl <- ELSA_w1$scfrdh
vbl_miss <- c(-9,-1)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = "scfrdh")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Type of missing")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(scfrdh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("on average how often do you speak on the phone with your friends") + ylab("Frequency")
vbl <- ELSA_w1$scfrdi
vbl_miss <- c(-9,-1)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = "scfrdi")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Type of missing")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(scfrdi))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("on average how often do you write or email your friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if scfrdh=1 or scfrdi=1 then 1`
* `if scfrdh=2 or scfrdi=2 then 2`
* `if scfrdh=3 or scfrdi=3 then 3`
* `if scfrdh=4 or 5 or scfrdi=4 or 5 then 4`
* `if scfrd=2 or scfrdh=6 or scfrdi=6 then 5`
* `-9 into 995`
* `-1 into 996`
* `NA into 999`

**R script:**

```{r harmo1}
ELSA_ds_w1 <- tibble(id=ELSA_w1$id)

ELSA_w1$scfrd <- car::recode(as.vector(ELSA_w1$scfrd), "NA='-999'")
ELSA_w1$scfrdh <- car::recode(as.vector(ELSA_w1$scfrdh), "NA='-999'")
ELSA_w1$scfrdi <- car::recode(as.vector(ELSA_w1$scfrdi), "NA='-999'")

ELSA_ds_w1$f_other_fr <- c(NA) # I think it is required
for(i in 1:dim(ELSA_w1)[1]){
  if( ELSA_w1$scfrdh[i] == 1 | ELSA_w1$scfrdi[i] == 1 ) { ELSA_ds_w1$f_other_fr[i] = 1 }
  else if( ELSA_w1$scfrdh[i] == 2 | ELSA_w1$scfrdi[i] == 2 ) { ELSA_ds_w1$f_other_fr[i] = 2 }
  else if( ELSA_w1$scfrdh[i] == 3 | ELSA_w1$scfrdi[i] == 3 ) { ELSA_ds_w1$f_other_fr[i] = 3 }
  else if( ELSA_w1$scfrdh[i] %in% c(4,5) | ELSA_w1$scfrdi[i] %in% c(4,5) ) { ELSA_ds_w1$f_other_fr[i] = 4 }
  else if( ELSA_w1$scfrdh[i] == 6 | ELSA_w1$scfrdi[i] == 6 | ELSA_w1$scfrd[i] == 2 ) { ELSA_ds_w1$f_other_fr[i] = 5 }
  else if( ELSA_w1$scfrdh[i] == -9 | ELSA_w1$scfrdi[i] == -9 | ELSA_w1$scfrd[i] == -9 ) { ELSA_ds_w1$f_other_fr[i] = 995 }
  else if( ELSA_w1$scfrdh[i] == -1 | ELSA_w1$scfrdi[i] == -1 | ELSA_w1$scfrd[i] == -1 ) { ELSA_ds_w1$f_other_fr[i] = 996 }
}

ELSA_ds_w1$f_other_fr <- car::recode(as.vector(ELSA_ds_w1$f_other_fr), "NA='999'")
ELSA_ds_w1$f_other_fr <- labelled(ELSA_ds_w1$f_other_fr, labels = c("Daily/Almost daily"=1, "Once a week"=2, "Once or few times a month"=3, "Less than once a month"=4, "Never/No friends"=5, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vbl <- ELSA_ds_w1$f_other_fr
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w1, aes(x=factor(f_other_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of phone or mail contacts with friends") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}

```


### Wave 2

#### Study-specific variable description



| **Name** |`scfrd`|`scfrdh`|`scfrdi`|
|-|-|-|-|
| **Label** |`do you have any friends`|`on average how often do you speak on the phone with your friends`|`on average how often do you write or email your friends`|
| **Table name** |`wave_2_core_data_v4`|`wave_2_core_data_v4`|`wave_2_core_data_v4`|
| **Categories** |`1 = Yes`<br/>`2 = No`|`1 = Three or more times a week`<br/>`2 = Once or twice a week`<br/>`3 = Once or twice a month`<br/>`4 = Every few months`<br/>`5 = Once or twice a year`<br/>`6 = Less than once a year or never`|`1 = Three or more times a week`<br/>`2 = Once or twice a week`<br/>`3 = Once or twice a month`<br/>`4 = Every few months`<br/>`5 = Once or twice a year`<br/>`6 = Less than once a year or never`|
| **Missings**|`-9 = Not answered`<br/>`-1 = Item not applicable`|`-9 = Not answered`<br/>`-1 = Item not applicable`|`-9 = Not answered`<br/>`-1 = Item not applicable`|
| **Description** |  |  |  |



```{r assign2, echo=F}
opal.assign.table.tibble(o, 'ELSA_w2','ELSA.wave_2_core_data_v4',variables=list('scfrd','scfrdh','scfrdi'), missings = TRUE)
ELSA_w2 <- opal.execute(o,'ELSA_w2')
```

```{r local2, echo=F}
vbl <- ELSA_w2$scfrd
vbl_miss <- c(-9,-1)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = "scfrd")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Type of missing")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(scfrd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has got any friends?") + ylab("Frequency")
vbl <- ELSA_w2$scfrdh
vbl_miss <- c(-9,-1)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = "scfrdh")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Type of missing")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(scfrdh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("on average how often do you speak on the phone with your friends") + ylab("Frequency")
vbl <- ELSA_w2$scfrdi
vbl_miss <- c(-9,-1)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = "scfrdi")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Type of missing")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(scfrdi))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("on average how often do you write or email your friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if scfrdh=1 or scfrdi=1 then 1`
* `if scfrdh=2 or scfrdi=2 then 2`
* `if scfrdh=3 or scfrdi=3 then 3`
* `if scfrdh=4 or 5 or scfrdi=4 or 5 then 4`
* `if scfrd=2 or scfrdh=6 or scfrdi=6 then 5`
* `-9 into 995`
* `-1 into 996`
* `NA into 999`

**R script:**

```{r harmo2}
ELSA_ds_w2 <- tibble(id=ELSA_w2$id)

ELSA_w2$scfrd <- car::recode(as.vector(ELSA_w2$scfrd), "NA='-999'")
ELSA_w2$scfrdh <- car::recode(as.vector(ELSA_w2$scfrdh), "NA='-999'")
ELSA_w2$scfrdi <- car::recode(as.vector(ELSA_w2$scfrdi), "NA='-999'")

ELSA_ds_w2$f_other_fr <- c(NA) # I think it is required
for(i in 1:dim(ELSA_w2)[1]){
  if( ELSA_w2$scfrdh[i] == 1 | ELSA_w2$scfrdi[i] == 1 ) { ELSA_ds_w2$f_other_fr[i] = 1 }
  else if( ELSA_w2$scfrdh[i] == 2 | ELSA_w2$scfrdi[i] == 2 ) { ELSA_ds_w2$f_other_fr[i] = 2 }
  else if( ELSA_w2$scfrdh[i] == 3 | ELSA_w2$scfrdi[i] == 3 ) { ELSA_ds_w2$f_other_fr[i] = 3 }
  else if( ELSA_w2$scfrdh[i] %in% c(4,5) | ELSA_w2$scfrdi[i] %in% c(4,5) ) { ELSA_ds_w2$f_other_fr[i] = 4 }
  else if( ELSA_w2$scfrdh[i] == 6 | ELSA_w2$scfrdi[i] == 6 | ELSA_w2$scfrd[i] == 2 ) { ELSA_ds_w2$f_other_fr[i] = 5 }
  else if( ELSA_w2$scfrdh[i] == -9 | ELSA_w2$scfrdi[i] == -9 | ELSA_w2$scfrd[i] == -9 ) { ELSA_ds_w2$f_other_fr[i] = 995 }
  else if( ELSA_w2$scfrdh[i] == -1 | ELSA_w2$scfrdi[i] == -1 | ELSA_w2$scfrd[i] == -1 ) { ELSA_ds_w2$f_other_fr[i] = 996 }
}

ELSA_ds_w2$f_other_fr <- car::recode(as.vector(ELSA_ds_w2$f_other_fr), "NA='999'")
ELSA_ds_w2$f_other_fr <- labelled(ELSA_ds_w2$f_other_fr, labels = c("Daily/Almost daily"=1, "Once a week"=2, "Once or few times a month"=3, "Less than once a month"=4, "Never/No friends"=5, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vbl <- ELSA_ds_w2$f_other_fr
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w2, aes(x=factor(f_other_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of phone or mail contacts with friends") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}

```



### Wave 3

#### Study-specific variable description



| **Name** |`scfrd`|`scfrdh`|`scfrdi`|
|-|-|-|-|
| **Label** |`do you have any friends`|`on average how often do you speak on the phone with your friends`|`on average how often do you write or email your friends`|
| **Table name** |`wave_3_elsa_data_v4`|`wave_3_elsa_data_v4`|`wave_3_elsa_data_v4`|
| **Categories** |`1 = Yes`<br/>`2 = No`|`1 = Three or more times a week`<br/>`2 = Once or twice a week`<br/>`3 = Once or twice a month`<br/>`4 = Every few months`<br/>`5 = Once or twice a year`<br/>`6 = Less than once a year or never`|`1 = Three or more times a week`<br/>`2 = Once or twice a week`<br/>`3 = Once or twice a month`<br/>`4 = Every few months`<br/>`5 = Once or twice a year`<br/>`6 = Less than once a year or never`|
| **Missings**|`-9 = Not answered`<br/>`-1 = Item not applicable`|`-9 = Not answered`<br/>`-8 = Don't know`<br/>`-1 = Item not applicable`|`-9 = Not answered`<br/>`-1 = Item not applicable`|
| **Description** |  |  |  |



```{r assign3, echo=F}
opal.assign.table.tibble(o, 'ELSA_w3','ELSA.wave_3_elsa_data_v4',variables=list('scfrd','scfrdh','scfrdi'), missings = TRUE)
ELSA_w3 <- opal.execute(o,'ELSA_w3')
```

```{r local3, echo=F}
vbl <- ELSA_w3$scfrd
vbl_miss <- c(-9,-1)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = "scfrd")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Type of missing")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w3, aes(x=factor(scfrd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has got any friends?") + ylab("Frequency")
vbl <- ELSA_w3$scfrdh
vbl_miss <- c(-9,-8,-1)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = "scfrdh")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Type of missing")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w3, aes(x=factor(scfrdh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("on average how often do you speak on the phone with your friends") + ylab("Frequency")
vbl <- ELSA_w3$scfrdi
vbl_miss <- c(-9,-1)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = "scfrdi")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Type of missing")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w3, aes(x=factor(scfrdi))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("on average how often do you write or email your friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if scfrdh=1 or scfrdi=1 then 1`
* `if scfrdh=2 or scfrdi=2 then 2`
* `if scfrdh=3 or scfrdi=3 then 3`
* `if scfrdh=4 or 5 or scfrdi=4 or 5 then 4`
* `if scfrd=2 or scfrdh=6 or scfrdi=6 then 5`
* `-9 into 995`
* `-8 into 998`
* `-1 into 996`
* `NA into 999`

**R script:**

```{r harmo3}
ELSA_ds_w3 <- tibble(id=ELSA_w3$id)

ELSA_w3$scfrd <- car::recode(as.vector(ELSA_w3$scfrd), "NA='-999'")
ELSA_w3$scfrdh <- car::recode(as.vector(ELSA_w3$scfrdh), "NA='-999'")
ELSA_w3$scfrdi <- car::recode(as.vector(ELSA_w3$scfrdi), "NA='-999'")

ELSA_ds_w3$f_other_fr <- c(NA) # I think it is required
for(i in 1:dim(ELSA_w3)[1]){
  if( ELSA_w3$scfrdh[i] == 1 | ELSA_w3$scfrdi[i] == 1 ) { ELSA_ds_w3$f_other_fr[i] = 1 }
  else if( ELSA_w3$scfrdh[i] == 2 | ELSA_w3$scfrdi[i] == 2 ) { ELSA_ds_w3$f_other_fr[i] = 2 }
  else if( ELSA_w3$scfrdh[i] == 3 | ELSA_w3$scfrdi[i] == 3 ) { ELSA_ds_w3$f_other_fr[i] = 3 }
  else if( ELSA_w3$scfrdh[i] %in% c(4,5) | ELSA_w3$scfrdi[i] %in% c(4,5) ) { ELSA_ds_w3$f_other_fr[i] = 4 }
  else if( ELSA_w3$scfrdh[i] == 6 | ELSA_w3$scfrdi[i] == 6 | ELSA_w3$scfrd[i] == 2 ) { ELSA_ds_w3$f_other_fr[i] = 5 }
  else if( ELSA_w3$scfrdh[i] == -9 | ELSA_w3$scfrdi[i] == -9 | ELSA_w3$scfrd[i] == -9 ) { ELSA_ds_w3$f_other_fr[i] = 995 }
  else if( ELSA_w3$scfrdh[i] == -8 | ELSA_w3$scfrdi[i] == -8 | ELSA_w3$scfrd[i] == -8 ) { ELSA_ds_w3$f_other_fr[i] = 998 }
  else if( ELSA_w3$scfrdh[i] == -1 | ELSA_w3$scfrdi[i] == -1 | ELSA_w3$scfrd[i] == -1 ) { ELSA_ds_w3$f_other_fr[i] = 996 }
}

ELSA_ds_w3$f_other_fr <- car::recode(as.vector(ELSA_ds_w3$f_other_fr), "NA='999'")
ELSA_ds_w3$f_other_fr <- labelled(ELSA_ds_w3$f_other_fr, labels = c("Daily/Almost daily"=1, "Once a week"=2, "Once or few times a month"=3, "Less than once a month"=4, "Never/No friends"=5, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}
vbl <- ELSA_ds_w3$f_other_fr
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w3, aes(x=factor(f_other_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of phone or mail contacts with friends") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=F}

```


### Wave 4

#### Study-specific variable description


| **Name** |`scfrd`|`scfrdh`|`scfrdi`|
|-|-|-|-|
| **Label** |`do you have any friends`|`on average how often do you speak on the phone with your friends`|`on average how often do you write or email your friends`|
| **Table name** |`wave_4_elsa_data_v3`|`wave_4_elsa_data_v3`|`wave_4_elsa_data_v3`|
| **Categories** |`1 = Yes`<br/>`2 = No`|`1 = Three or more times a week`<br/>`2 = Once or twice a week`<br/>`3 = Once or twice a month`<br/>`4 = Every few months`<br/>`5 = Once or twice a year`<br/>`6 = Less than once a year or never`|`1 = Three or more times a week`<br/>`2 = Once or twice a week`<br/>`3 = Once or twice a month`<br/>`4 = Every few months`<br/>`5 = Once or twice a year`<br/>`6 = Less than once a year or never`|
| **Missings**|`-9 = Not answered`<br/>`-1 = Item not applicable`|`-9 = Not answered`<br/>`-8 = Don't know`<br/>`-1 = Item not applicable`|`-9 = Not answered`<br/>`-1 = Item not applicable`|
| **Description** |  |  |  |




```{r assign4, echo=F}
opal.assign.table.tibble(o, 'ELSA_w4','ELSA.wave_4_elsa_data_v3',variables=list('scfrd','scfrdh','scfrdi'), missings = TRUE)
ELSA_w4 <- opal.execute(o,'ELSA_w4')
```

```{r local4, echo=F}
vbl <- ELSA_w4$scfrd
vbl_miss <- c(-9,-1)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = "scfrd")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Type of missing")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w4, aes(x=factor(scfrd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has got any friends?") + ylab("Frequency")
vbl <- ELSA_w4$scfrdh
vbl_miss <- c(-9,-1,-8)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = "scfrdh")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Type of missing")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w4, aes(x=factor(scfrdh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("on average how often do you speak on the phone with your friends") + ylab("Frequency")
vbl <- ELSA_w4$scfrdi
vbl_miss <- c(-9,-1)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = "scfrdi")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Type of missing")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w4, aes(x=factor(scfrdi))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("on average how often do you write or email your friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if scfrdh=1 or scfrdi=1 then 1`
* `if scfrdh=2 or scfrdi=2 then 2`
* `if scfrdh=3 or scfrdi=3 then 3`
* `if scfrdh=4 or 5 or scfrdi=4 or 5 then 4`
* `if scfrd=2 or scfrdh=6 or scfrdi=6 then 5`
* `-9 into 995`
* `-8 into 998`
* `-1 into 996`
* `NA into 999`

**R script:**

```{r harmo4}
ELSA_ds_w4 <- tibble(id=ELSA_w4$id)

ELSA_w4$scfrd <- car::recode(as.vector(ELSA_w4$scfrd), "NA='-999'")
ELSA_w4$scfrdh <- car::recode(as.vector(ELSA_w4$scfrdh), "NA='-999'")
ELSA_w4$scfrdi <- car::recode(as.vector(ELSA_w4$scfrdi), "NA='-999'")

ELSA_ds_w4$f_other_fr <- c(NA) # I think it is required
for(i in 1:dim(ELSA_w4)[1]){
  if( ELSA_w4$scfrdh[i] == 1 | ELSA_w4$scfrdi[i] == 1 ) { ELSA_ds_w4$f_other_fr[i] = 1 }
  else if( ELSA_w4$scfrdh[i] == 2 | ELSA_w4$scfrdi[i] == 2 ) { ELSA_ds_w4$f_other_fr[i] = 2 }
  else if( ELSA_w4$scfrdh[i] == 3 | ELSA_w4$scfrdi[i] == 3 ) { ELSA_ds_w4$f_other_fr[i] = 3 }
  else if( ELSA_w4$scfrdh[i] %in% c(4,5) | ELSA_w4$scfrdi[i] %in% c(4,5) ) { ELSA_ds_w4$f_other_fr[i] = 4 }
  else if( ELSA_w4$scfrdh[i] == 6 | ELSA_w4$scfrdi[i] == 6 | ELSA_w4$scfrd[i] == 2 ) { ELSA_ds_w4$f_other_fr[i] = 5 }
  else if( ELSA_w4$scfrdh[i] == -9 | ELSA_w4$scfrdi[i] == -9 | ELSA_w4$scfrd[i] == -9 ) { ELSA_ds_w4$f_other_fr[i] = 995 }
  else if( ELSA_w4$scfrdh[i] == -8 | ELSA_w4$scfrdi[i] == -8 | ELSA_w4$scfrd[i] == -8 ) { ELSA_ds_w4$f_other_fr[i] = 998 }
  else if( ELSA_w4$scfrdh[i] == -1 | ELSA_w4$scfrdi[i] == -1 | ELSA_w4$scfrd[i] == -1 ) { ELSA_ds_w4$f_other_fr[i] = 996 }
}

ELSA_ds_w4$f_other_fr <- car::recode(as.vector(ELSA_ds_w4$f_other_fr), "NA='999'")
ELSA_ds_w4$f_other_fr <- labelled(ELSA_ds_w4$f_other_fr, labels = c("Daily/Almost daily"=1, "Once a week"=2, "Once or few times a month"=3, "Less than once a month"=4, "Never/No friends"=5, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript4, echo=F}
vbl <- ELSA_ds_w4$f_other_fr
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w4, aes(x=factor(f_other_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of phone or mail contacts with friends") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=F}

```



### Wave 5

#### Study-specific variable description


| **Name** |`scfrd`|`scfrdh`|`scfrdi`|
|-|-|-|-|
| **Label** |`do you have any friends`|`on average how often do you speak on the phone with your friends`|`on average how often do you write or email your friends`|
| **Table name** |`wave_5_elsa_data_v4`|`wave_5_elsa_data_v4`|`wave_5_elsa_data_v4`|
| **Categories** |`1 = Yes`<br/>`2 = No`|`1 = Three or more times a week`<br/>`2 = Once or twice a week`<br/>`3 = Once or twice a month`<br/>`4 = Every few months`<br/>`5 = Once or twice a year`<br/>`6 = Less than once a year or never`|`1 = Three or more times a week`<br/>`2 = Once or twice a week`<br/>`3 = Once or twice a month`<br/>`4 = Every few months`<br/>`5 = Once or twice a year`<br/>`6 = Less than once a year or never`|
| **Missings**|`-9 = Not answered`<br/>`-2 = Schedule not applicable`<br/>`-1 = Item not applicable`|`-9 = Not answered`<br/>`-8 = Don't know`<br/>`-2 = Schedule not applicable`<br/>`-1 = Item not applicable`|`-9 = Not answered`<br/>`-8 = Don't know`<br/>`-2 = Schedule not applicable`<br/>`-1 = Item not applicable`|
| **Description** |  |  |  |



```{r assign5, echo=F}
opal.assign.table.tibble(o, 'ELSA_w5','ELSA.wave_5_elsa_data_v4',variables=list('scfrd','scfrdh','scfrdi'), missings = TRUE)
```

```{r local5, echo=F}
ELSA_w5 <- opal.execute(o,'ELSA_w5')
vbl <- ELSA_w5$scfrd
vbl_miss <- c(-9,-1,-2)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = "scfrd")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Type of missing")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w5, aes(x=factor(scfrd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has got any friends?") + ylab("Frequency")
vbl <- ELSA_w5$scfrdh
vbl_miss <- c(-9,-8,-2,-1)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = "scfrdh")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Type of missing")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w5, aes(x=factor(scfrdh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("on average how often do you speak on the phone with your friends") + ylab("Frequency")
vbl <- ELSA_w5$scfrdi
vbl_miss <- c(-9,-8,-2,-1)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = "scfrdi")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Type of missing")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w5, aes(x=factor(scfrdi))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("on average how often do you write or email your friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if scfrdh=1 or scfrdi=1 then 1`
* `if scfrdh=2 or scfrdi=2 then 2`
* `if scfrdh=3 or scfrdi=3 then 3`
* `if scfrdh=4 or 5 or scfrdi=4 or 5 then 4`
* `if scfrd=2 or scfrdh=6 or scfrdi=6 then 5`
* `-9 into 995`
* `-8 into 998`
* `-1 or -2 into 996`
* `NA into 999`

**R script:**

```{r harmo5}
ELSA_ds_w5 <- tibble(id=ELSA_w5$id)

ELSA_w5$scfrd <- car::recode(as.vector(ELSA_w5$scfrd), "NA='-999'")
ELSA_w5$scfrdh <- car::recode(as.vector(ELSA_w5$scfrdh), "NA='-999'")
ELSA_w5$scfrdi <- car::recode(as.vector(ELSA_w5$scfrdi), "NA='-999'")

ELSA_ds_w5$f_other_fr <- c(NA) # I think it is required
for(i in 1:dim(ELSA_w5)[1]){
  if( ELSA_w5$scfrdh[i] == 1 | ELSA_w5$scfrdi[i] == 1 ) { ELSA_ds_w5$f_other_fr[i] = 1 }
  else if( ELSA_w5$scfrdh[i] == 2 | ELSA_w5$scfrdi[i] == 2 ) { ELSA_ds_w5$f_other_fr[i] = 2 }
  else if( ELSA_w5$scfrdh[i] == 3 | ELSA_w5$scfrdi[i] == 3 ) { ELSA_ds_w5$f_other_fr[i] = 3 }
  else if( ELSA_w5$scfrdh[i] %in% c(4,5) | ELSA_w5$scfrdi[i] %in% c(4,5) ) { ELSA_ds_w5$f_other_fr[i] = 4 }
  else if( ELSA_w5$scfrdh[i] == 6 | ELSA_w5$scfrdi[i] == 6 | ELSA_w5$scfrd[i] == 2 ) { ELSA_ds_w5$f_other_fr[i] = 5 }
  else if( ELSA_w5$scfrdh[i] == -9 | ELSA_w5$scfrdi[i] == -9 | ELSA_w5$scfrd[i] == -9 ) { ELSA_ds_w5$f_other_fr[i] = 995 }
  else if( ELSA_w5$scfrdh[i] == -8 | ELSA_w5$scfrdi[i] == -8 | ELSA_w5$scfrd[i] == -8 ) { ELSA_ds_w5$f_other_fr[i] = 998 }
  else if( ELSA_w5$scfrdh[i] %in% c(-1,-2) | ELSA_w5$scfrdi[i] %in% c(-1,-2) | ELSA_w5$scfrd[i]%in% c(-1,-2) ) { ELSA_ds_w5$f_other_fr[i] = 996 }
}

ELSA_ds_w5$f_other_fr <- car::recode(as.vector(ELSA_ds_w5$f_other_fr), "NA='999'")
ELSA_ds_w5$f_other_fr <- labelled(ELSA_ds_w5$f_other_fr, labels = c("Daily/Almost daily"=1, "Once a week"=2, "Once or few times a month"=3, "Less than once a month"=4, "Never/No friends"=5, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript5, echo=F}
vbl <- ELSA_ds_w5$f_other_fr
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w5, aes(x=factor(f_other_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of phone or mail contacts with friends") + ylab("Frequency")
```

#### Validation
```{r crosstabulation5, echo=F}

```



### Wave 6

#### Study-specific variable description



| **Name** |`scfrd`|`scfrdh`|`scfrdi`|
|-|-|-|-|
| **Label** |`do you have any friends`|`on average how often do you speak on the phone with your friends`|`on average how often do you write or email your friends`|
| **Table name** |`wave_6_elsa_data_v2`|`wave_6_elsa_data_v2`|`wave_6_elsa_data_v2`|
| **Categories** |`1 = Yes`<br/>`2 = No`|`1 = Three or more times a week`<br/>`2 = Once or twice a week`<br/>`3 = Once or twice a month`<br/>`4 = Every few months`<br/>`5 = Once or twice a year`<br/>`6 = Less than once a year or never`|`1 = Three or more times a week`<br/>`2 = Once or twice a week`<br/>`3 = Once or twice a month`<br/>`4 = Every few months`<br/>`5 = Once or twice a year`<br/>`6 = Less than once a year or never`|
| **Missings**|`-9 = Not answered`<br/>`-2 = Schedule not applicable`<br/>`-1 = Item not applicable`|`-9 = Not answered`<br/>`-8 = Don't know`<br/>`-2 = Schedule not applicable`<br/>`-1 = Item not applicable`|`-9 = Not answered`<br/>`-8 = Don't know`<br/>`-2 = Schedule not applicable`<br/>`-1 = Item not applicable`|
| **Description** |  |  |  |



```{r assign6, echo=F}
opal.assign.table.tibble(o, 'ELSA_w6','ELSA.wave_6_elsa_data_v2',variables=list('scfrd','scfrdh','scfrdi'), missings = TRUE)
ELSA_w6 <- opal.execute(o,'ELSA_w6')
```

```{r local6, echo=F}
vbl <- ELSA_w6$scfrd
vbl_miss <- c(-9,-1,-2)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = "scfrd")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Type of missing")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w6, aes(x=factor(scfrd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has got any friends?") + ylab("Frequency")
vbl <- ELSA_w6$scfrdh
vbl_miss <- c(-9,-8,-2,-1)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = "scfrdh")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Type of missing")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w6, aes(x=factor(scfrdh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("on average how often do you speak on the phone with your friends") + ylab("Frequency")
vbl <- ELSA_w6$scfrdi
vbl_miss <- c(-9,-8,-2,-1)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = "scfrdi")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Type of missing")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w6, aes(x=factor(scfrdi))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("on average how often do you write or email your friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if scfrdh=1 or scfrdi=1 then 1`
* `if scfrdh=2 or scfrdi=2 then 2`
* `if scfrdh=3 or scfrdi=3 then 3`
* `if scfrdh=4 or 5 or scfrdi=4 or 5 then 4`
* `if scfrd=2 or scfrdh=6 or scfrdi=6 then 5`
* `-9 into 995`
* `-8 into 998`
* `-1 or -2 into 996`
* `NA into 999`

**R script:**

```{r harmo6}
ELSA_ds_w6 <- tibble(id=ELSA_w6$id)

ELSA_w6$scfrd <- car::recode(as.vector(ELSA_w6$scfrd), "NA='-999'")
ELSA_w6$scfrdh <- car::recode(as.vector(ELSA_w6$scfrdh), "NA='-999'")
ELSA_w6$scfrdi <- car::recode(as.vector(ELSA_w6$scfrdi), "NA='-999'")

ELSA_ds_w6$f_other_fr <- c(NA) # I think it is required
for(i in 1:dim(ELSA_w6)[1]){
  if( ELSA_w6$scfrdh[i] == 1 | ELSA_w6$scfrdi[i] == 1 ) { ELSA_ds_w6$f_other_fr[i] = 1 }
  else if( ELSA_w6$scfrdh[i] == 2 | ELSA_w6$scfrdi[i] == 2 ) { ELSA_ds_w6$f_other_fr[i] = 2 }
  else if( ELSA_w6$scfrdh[i] == 3 | ELSA_w6$scfrdi[i] == 3 ) { ELSA_ds_w6$f_other_fr[i] = 3 }
  else if( ELSA_w6$scfrdh[i] %in% c(4,5) | ELSA_w6$scfrdi[i] %in% c(4,5) ) { ELSA_ds_w6$f_other_fr[i] = 4 }
  else if( ELSA_w6$scfrdh[i] == 6 | ELSA_w6$scfrdi[i] == 6 | ELSA_w6$scfrd[i] == 2 ) { ELSA_ds_w6$f_other_fr[i] = 5 }
  else if( ELSA_w6$scfrdh[i] == -9 | ELSA_w6$scfrdi[i] == -9 | ELSA_w6$scfrd[i] == -9 ) { ELSA_ds_w6$f_other_fr[i] = 995 }
  else if( ELSA_w6$scfrdh[i] == -8 | ELSA_w6$scfrdi[i] == -8 | ELSA_w6$scfrd[i] == -8 ) { ELSA_ds_w6$f_other_fr[i] = 998 }
  else if( ELSA_w6$scfrdh[i] %in% c(-1,-2) | ELSA_w6$scfrdi[i] %in% c(-1,-2) | ELSA_w6$scfrd[i]%in% c(-1,-2) ) { ELSA_ds_w6$f_other_fr[i] = 996 }
}

ELSA_ds_w6$f_other_fr <- car::recode(as.vector(ELSA_ds_w6$f_other_fr), "NA='999'")
ELSA_ds_w6$f_other_fr <- labelled(ELSA_ds_w6$f_other_fr, labels = c("Daily/Almost daily"=1, "Once a week"=2, "Once or few times a month"=3, "Less than once a month"=4, "Never/No friends"=5, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript6, echo=F}
vbl <- ELSA_ds_w6$f_other_fr
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w6, aes(x=factor(f_other_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of phone or mail contacts with friends") + ylab("Frequency")
```

#### Validation
```{r crosstabulation6, echo=F}

```


### Wave 7

#### Study-specific variable description




| **Name** |`scfrd`|`scfrdi`|`scfrdj`|
|-|-|-|-|
| **Label** |`Whether the respondent has any friends`|`How often the respondent speaks with their friends on the phone`|`How often the respondent writes to or emails their friends`|
| **Table name** |`wave_7_elsa_data`|`wave_7_elsa_data`|`wave_7_elsa_data`|
| **Categories** |`1 = Yes`<br/>`2 = No`|`1 = Three or more times a week`<br/>`2 = Once or twice a week`<br/>`3 = Once or twice a month`<br/>`4 = Every few months`<br/>`5 = Once or twice a year`<br/>`6 = Less than once a year or never`|`1 = Three or more times a week`<br/>`2 = Once or twice a week`<br/>`3 = Once or twice a month`<br/>`4 = Every few months`<br/>`5 = Once or twice a year`<br/>`6 = Less than once a year or never`|
| **Missings**|`-9 = Not answered`<br/>`-2 = Schedule not applicable`<br/>`-1 = Item not applicable`|`-9 = Not answered`<br/>`-8 = Don't know`<br/>`-2 = Schedule not applicable`<br/>`-1 = Item not applicable`|`-9 = Not answered`<br/>`-8 = Don't know`<br/>`-2 = Schedule not applicable`<br/>`-1 = Item not applicable`|
| **Description** |  |  |  |


```{r assign7, echo=F}
opal.assign.table.tibble(o, 'ELSA_w7','ELSA.wave_7_elsa_data',variables=list('scfrd','scfrdi','scfrdj'), missings = TRUE)
```

```{r local7, echo=F}
ELSA_w7 <- opal.execute(o,'ELSA_w7')
vbl <- ELSA_w7$scfrd
vbl_miss <- c(-9,-2,-1)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = "scfrd")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Type of missing")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w7, aes(x=factor(scfrd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
vbl <- ELSA_w7$scfrdi
vbl_miss <- c(-9,-8,-2,-1)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = "scfrdi")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Type of missing")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w7, aes(x=factor(scfrdi))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
vbl <- ELSA_w7$scfrdj
vbl_miss <- c(-9,-8,-2,-1)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = "scfrdj")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Type of missing")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ELSA_w7, aes(x=factor(scfrdj))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if scfrdi=1 or scfrdj=1 then 1`
* `if scfrdi=2 or scfrdj=2 then 2`
* `if scfrdi=3 or scfrdj=3 then 3`
* `if scfrdi=4 or 5 or scfrdj=4 or 5 then 4`
* `if scfrd=2 or scfrdi=6 or scfrdj=6 then 5`
* `-9 into 995`
* `-8 into 998`
* `-1 or -2 into 996`
* `NA into 999`

**R script:**

```{r harmo7}
ELSA_ds_w7 <- tibble(id=ELSA_w7$id)

ELSA_w7$scfrd <- car::recode(as.vector(ELSA_w7$scfrd), "NA='-999'")
ELSA_w7$scfrdi <- car::recode(as.vector(ELSA_w7$scfrdi), "NA='-999'")
ELSA_w7$scfrdj <- car::recode(as.vector(ELSA_w7$scfrdj), "NA='-999'")

ELSA_ds_w7$f_other_fr <- c(NA) # I think it is required
for(i in 1:dim(ELSA_w7)[1]){
  if( ELSA_w7$scfrdi[i] == 1 | ELSA_w7$scfrdj[i] == 1 ) { ELSA_ds_w7$f_other_fr[i] = 1 }
  else if( ELSA_w7$scfrdi[i] == 2 | ELSA_w7$scfrdj[i] == 2 ) { ELSA_ds_w7$f_other_fr[i] = 2 }
  else if( ELSA_w7$scfrdi[i] == 3 | ELSA_w7$scfrdj[i] == 3 ) { ELSA_ds_w7$f_other_fr[i] = 3 }
  else if( ELSA_w7$scfrdi[i] %in% c(4,5) | ELSA_w7$scfrdj[i] %in% c(4,5) ) { ELSA_ds_w7$f_other_fr[i] = 4 }
  else if( ELSA_w7$scfrdi[i] == 6 | ELSA_w7$scfrdj[i] == 6 | ELSA_w7$scfrd[i] == 2 ) { ELSA_ds_w7$f_other_fr[i] = 5 }
  else if( ELSA_w7$scfrdi[i] == -9 | ELSA_w7$scfrdj[i] == -9 | ELSA_w7$scfrd[i] == -9 ) { ELSA_ds_w7$f_other_fr[i] = 995 }
  else if( ELSA_w7$scfrdi[i] == -8 | ELSA_w7$scfrdj[i] == -8 | ELSA_w7$scfrd[i] == -8 ) { ELSA_ds_w7$f_other_fr[i] = 998 }
  else if( ELSA_w7$scfrdi[i] %in% c(-1,-2) | ELSA_w7$scfrdj[i] %in% c(-1,-2) | ELSA_w7$scfrd[i]%in% c(-1,-2) ) { ELSA_ds_w7$f_other_fr[i] = 996 }
}

ELSA_ds_w7$f_other_fr <- car::recode(as.vector(ELSA_ds_w7$f_other_fr), "NA='999'")
ELSA_ds_w7$f_other_fr <- labelled(ELSA_ds_w7$f_other_fr, labels = c("Daily/Almost daily"=1, "Once a week"=2, "Once or few times a month"=3, "Less than once a month"=4, "Never/No friends"=5, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript7, echo=F}
vbl <- ELSA_ds_w7$f_other_fr
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w7, aes(x=factor(f_other_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of phone or mail contacts with friends") + ylab("Frequency")
```

#### Validation
```{r crosstabulation7, echo=F}

```

## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.




```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:5])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[16,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```



```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


elsa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"), w6 = c("w6","W6"), w7 = c("w7","W7"))

# Consider only harmonised waves
l.hds <- lapply(elsa.cw, function(wname) if(exists(paste0("ELSA_ds_",wname[1]))){wname = list(get(paste0("ELSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```



# Quality estimation
[Comments on the quality of the new harmonised variable.]



<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
