---
title: "Are the contacts with friends/neighbours frequent (i.e. contact once a month or more often)"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup_iago.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `cont_fr`
* Variable label: `Are the contacts with friends/neighbours frequent (i.e. contact once a month or more often)`
* Domain: `Social environment`
* Value type: `categorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process
## England

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:


* Name: `scfrd`
* Label: `do you have any friends`
* Categories:
    + `1	= Yes`
    + `2	= No`
* Missings:
    + `-9	= Not answered`
    + `-1	= Item not applicable`
    
    
* Name: `scfrdg`
* Label: `How often the respondent meets up with their friends`
* Categories:
    + `1	= Three or more times a week`
    + `2	= Once or twice a week`
    + `3	= Once or twice a month`	
    + `4	= Every few months`
    + `5	= Once or twice a year`
    + `6	= Less than once a year or never`
* Missings:
    + `-9	= Not answered`
    + `-1	= Item not applicable`
    
    
* Name: `scfrdh`
* Label: `on average how often do you speak on the phone with your friends`
* Categories:
    + `1	= Three or more times a week`
    + `2	= Once or twice a week`
    + `3	= Once or twice a month`	
    + `4	= Every few months`
    + `5	= Once or twice a year`
    + `6	= Less than once a year or never`
* Missings:
    + `-9	= Not answered`
    + `-1	= Item not applicable`


* Name: `scfrdi`
* Label: `on average how often do you write or email your friends`
* Categories:
    + `1	= Three or more times a week`
    + `2	= Once or twice a week`
    + `3	= Once or twice a month`	
    + `4	= Every few months`
    + `5	= Once or twice a year`
    + `6	= Less than once a year or never`
* Missings:
    + `-9	= Not answered`
    + `-1	= Item not applicable`


* Description: 
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'ELSA_w1_cont_fr','ELSA.wave_1_core_data_v3',variables=list('scfrd','scfrdg','scfrdh','scfrdi'), missings = TRUE)
```

```{r local1, echo=F}
ELSA_w1_cont_fr <- opal.execute(o,'ELSA_w1_cont_fr')
vari <- ELSA_w1_cont_fr$scfrd
kable(Categorical_summary(vari, missing_values = c(-1,-9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-9))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w1_cont_fr$scfrd, missing_values = NA)
ggplot(ELSA_w1_cont_fr, aes(x=factor(scfrd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has got any friends?") + ylab("Frequency")

vari <- ELSA_w1_cont_fr$scfrdg
kable(Categorical_summary(vari, missing_values = c(-1,-9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-9))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w1_cont_fr$scfrdg, missing_values = NA)
ggplot(ELSA_w1_cont_fr, aes(x=factor(scfrdg))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How often the respondent meets up with their friends") + ylab("Frequency")

vari <- ELSA_w1_cont_fr$scfrdh
kable(Categorical_summary(vari, missing_values = c(-1,-9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-9))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w1_cont_fr$scfrdh, missing_values = NA)
ggplot(ELSA_w1_cont_fr, aes(x=factor(scfrdh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("on average how often do you speak on the phone with your friends") + ylab("Frequency")

vari <- ELSA_w1_cont_fr$scfrdi
kable(Categorical_summary(vari, missing_values = c(-1,-9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-9))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w1_cont_fr$scfrdi, missing_values = NA)
ggplot(ELSA_w1_cont_fr, aes(x=factor(scfrdi))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("on average how often do you write or email your friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `scfrdg in (1,2,3) OR scfrdh in (1,2,3) OR scfrdi in (1,2,3) into 1`
* `scfrdg in (4,5,6) AND scfrdh in (4,5,6) AND scfrdi in (4,5,6) into 0`
* `scfrd=2 into 996`
* `scfrdg = -9 OR scfrdh = -9 OR scfrdi  = -9 into 995`
* `scfrdg = -1 OR scfrdh = -1 OR scfrdi  = -1 into 996`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
ELSA_ds_w1 <- tibble(id=ELSA_w1_cont_fr$id)

ELSA_w1_cont_fr$scfrd <- car::recode(as.vector(ELSA_w1_cont_fr$scfrd), "NA='-999'")
ELSA_w1_cont_fr$scfrdg <- car::recode(as.vector(ELSA_w1_cont_fr$scfrdg), "NA='-999'")
ELSA_w1_cont_fr$scfrdh <- car::recode(as.vector(ELSA_w1_cont_fr$scfrdh), "NA='-999'")
ELSA_w1_cont_fr$scfrdi <- car::recode(as.vector(ELSA_w1_cont_fr$scfrdi), "NA='-999'")

ELSA_ds_w1$cont_fr <- c(NA)  
for(i in 1:dim(ELSA_w1_cont_fr)[1]){
  if( ELSA_w1_cont_fr$scfrdg[i] %in% c(1,2,3) | ELSA_w1_cont_fr$scfrdh[i] %in% c(1,2,3) | ELSA_w1_cont_fr$scfrdi[i] %in% c(1,2,3) ) { 
    ELSA_ds_w1$cont_fr[i] = 1 }
  else if( ELSA_w1_cont_fr$scfrdg[i] %in% c(4,5,6) & ELSA_w1_cont_fr$scfrdh[i] %in% c(4,5,6) & ELSA_w1_cont_fr$scfrdi[i] %in% c(4,5,6) ){ 
    ELSA_ds_w1$cont_fr[i] = 0 }
  else if( ELSA_w1_cont_fr$scfrd[i] == 2 ){ 
    ELSA_ds_w1$cont_fr[i] = 996 }
  else if( ELSA_w1_cont_fr$scfrdg[i] == -9 | ELSA_w1_cont_fr$scfrdh[i] == -9 | ELSA_w1_cont_fr$scfrdi[i] == -9 ){ 
    ELSA_ds_w1$cont_fr[i] = 995 }
  else if( ELSA_w1_cont_fr$scfrdg[i] == -1 | ELSA_w1_cont_fr$scfrdh[i] == -1 | ELSA_w1_cont_fr$scfrdi[i] == -1 ){ 
    ELSA_ds_w1$cont_fr[i] = 996 }
}

ELSA_ds_w1$cont_fr <- car::recode(as.vector(ELSA_ds_w1$cont_fr), "NA='999'")
ELSA_ds_w1$cont_fr <- labelled(ELSA_ds_w1$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <-  ELSA_ds_w1$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w1$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w1, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}

```

 
 


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scfrd`
* Label: `do you have any friends`
* Categories:
    + `1	= Yes`
    + `2	= No`
* Missings:
    + `-9	= Not answered`
    + `-1	= Item not applicable`
    
    
* Name: `scfrdg`
* Label: `How often the respondent meets up with their friends`
* Categories:
    + `1	= Three or more times a week`
    + `2	= Once or twice a week`
    + `3	= Once or twice a month`	
    + `4	= Every few months`
    + `5	= Once or twice a year`
    + `6	= Less than once a year or never`
* Missings:
    + `-9	= Not answered`
    + `-1	= Item not applicable`
    
    
* Name: `scfrdh`
* Label: `on average how often do you speak on the phone with your friends`
* Categories:
    + `1	= Three or more times a week`
    + `2	= Once or twice a week`
    + `3	= Once or twice a month`	
    + `4	= Every few months`
    + `5	= Once or twice a year`
    + `6	= Less than once a year or never`
* Missings:
    + `-9	= Not answered`
    + `-1	= Item not applicable`


* Name: `scfrdi`
* Label: `on average how often do you write or email your friends`
* Categories:
    + `1	= Three or more times a week`
    + `2	= Once or twice a week`
    + `3	= Once or twice a month`	
    + `4	= Every few months`
    + `5	= Once or twice a year`
    + `6	= Less than once a year or never`
* Missings:
    + `-9	= Not answered`
    + `-1	= Item not applicable`

* Description: 
```{r assign2, echo=F}
opal.assign.table.tibble(o, 'ELSA_w2_cont_fr','ELSA.wave_2_core_data_v4',
                         variables=list('scfrd','scfrdg','scfrdh','scfrdi'), missings = TRUE)
```

```{r local2, echo=F}
ELSA_w2_cont_fr <- opal.execute(o,'ELSA_w2_cont_fr')
vari <- ELSA_w2_cont_fr$scfrd
kable(Categorical_summary(vari, missing_values = c(-1,-9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-9))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w2_cont_fr$scfrd, missing_values = NA)
ggplot(ELSA_w2_cont_fr, aes(x=factor(scfrd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has got any friends?") + ylab("Frequency")
vari <- ELSA_w2_cont_fr$scfrdg
kable(Categorical_summary(vari, missing_values = c(-1,-9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-9))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w2_cont_fr$scfrdg, missing_values = NA)
ggplot(ELSA_w2_cont_fr, aes(x=factor(scfrdg))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How often the respondent meets up with their friends") + ylab("Frequency")
vari <- ELSA_w2_cont_fr$scfrdh
kable(Categorical_summary(vari, missing_values = c(-1,-9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-9))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w2_cont_fr$scfrdh, missing_values = NA)
ggplot(ELSA_w2_cont_fr, aes(x=factor(scfrdh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("on average how often do you speak on the phone with your friends") + ylab("Frequency")
vari <- ELSA_w2_cont_fr$scfrdi
kable(Categorical_summary(vari, missing_values = c(-1,-9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-9))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_w2_cont_fr$scfrdi, missing_values = NA)
ggplot(ELSA_w2_cont_fr, aes(x=factor(scfrdi))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("on average how often do you write or email your friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `scfrdg in (1,2,3) OR scfrdh in (1,2,3) OR scfrdi in (1,2,3) into 1`
* `scfrdg in (4,5,6) AND scfrdh in (4,5,6) AND scfrdi in (4,5,6) into 0`
* `scfrd=2 into 990`
* `scfrdg = -9 OR scfrdh = -9 OR scfrdi  = -9 into 995`
* `scfrdg = -1 OR scfrdh = -1 OR scfrdi  = -1 into 996`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
ELSA_ds_w2 <- tibble(id=ELSA_w2_cont_fr$id)

ELSA_w2_cont_fr$scfrd <- car::recode(as.vector(ELSA_w2_cont_fr$scfrd), "NA='-999'")
ELSA_w2_cont_fr$scfrdg <- car::recode(as.vector(ELSA_w2_cont_fr$scfrdg), "NA='-999'")
ELSA_w2_cont_fr$scfrdh <- car::recode(as.vector(ELSA_w2_cont_fr$scfrdh), "NA='-999'")
ELSA_w2_cont_fr$scfrdi <- car::recode(as.vector(ELSA_w2_cont_fr$scfrdi), "NA='-999'")

ELSA_ds_w2$cont_fr <- c(NA)  
for(i in 1:dim(ELSA_w2_cont_fr)[1]){
  if( ELSA_w2_cont_fr$scfrdg[i] %in% c(1,2,3) | ELSA_w2_cont_fr$scfrdh[i] %in% c(1,2,3) | ELSA_w2_cont_fr$scfrdi[i] %in% c(1,2,3) ) { 
    ELSA_ds_w2$cont_fr[i] = 1 }
  else if( ELSA_w2_cont_fr$scfrdg[i] %in% c(4,5,6) & ELSA_w2_cont_fr$scfrdh[i] %in% c(4,5,6) & ELSA_w2_cont_fr$scfrdi[i] %in% c(4,5,6) ){ 
    ELSA_ds_w2$cont_fr[i] = 0 }
  else if( ELSA_w2_cont_fr$scfrd[i] == 2 ){ 
    ELSA_ds_w2$cont_fr[i] = 990 }
  else if( ELSA_w2_cont_fr$scfrdg[i] == -9 |  ELSA_w2_cont_fr$scfrdh[i] == -9  |  ELSA_w2_cont_fr$scfrdi[i] == -9 ){ 
    ELSA_ds_w2$cont_fr[i] = 995 }
  else if( ELSA_w2_cont_fr$scfrdg[i] == -1 |  ELSA_w2_cont_fr$scfrdh[i] == -1  |  ELSA_w2_cont_fr$scfrdi[i] == -1 ){ 
    ELSA_ds_w2$cont_fr[i] = 996 }
}

ELSA_ds_w2$cont_fr <- car::recode(as.vector(ELSA_ds_w2$cont_fr), "NA='999'")
ELSA_ds_w2$cont_fr <- labelled(ELSA_ds_w2$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991, "NOT APPLICABLE - HAS NOT GOT ANY FRIENDS"=990))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}
vari <- ELSA_ds_w2$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w2$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w2, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}

```

 
 


### Wave 3

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scfrd`
* Label: `do you have any friends`
* Categories:
    + `1	= Yes`
    + `2	= No`
* Missings:
    + `-9	= Not answered`
    + `-1	= Item not applicable`
    
    
* Name: `scfrdg`
* Label: `How often the respondent meets up with their friends`
* Categories:
    + `1	= Three or more times a week`
    + `2	= Once or twice a week`
    + `3	= Once or twice a month`	
    + `4	= Every few months`
    + `5	= Once or twice a year`
    + `6	= Less than once a year or never`
* Missings:
    + `-9	= Not answered`
    + `-8	= Don't know`
    + `-1	= Item not applicable`
    
    
* Name: `scfrdh`
* Label: `on average how often do you speak on the phone with your friends`
* Categories:
    + `1	= Three or more times a week`
    + `2	= Once or twice a week`
    + `3	= Once or twice a month`	
    + `4	= Every few months`
    + `5	= Once or twice a year`
    + `6	= Less than once a year or never`
* Missings:
    + `-9	= Not answered`
    + `-8	= Don't know`    
    + `-1	= Item not applicable`


* Name: `scfrdi`
* Label: `on average how often do you write or email your friends`
* Categories:
    + `1	= Three or more times a week`
    + `2	= Once or twice a week`
    + `3	= Once or twice a month`	
    + `4	= Every few months`
    + `5	= Once or twice a year`
    + `6	= Less than once a year or never`
* Missings:
    + `-9	= Not answered`
    + `-8	= Don't know`    
    + `-1	= Item not applicable`


* Description: 
```{r assign3, echo=F}
opal.assign.table.tibble(o, 'ELSA_w3_cont_fr','ELSA.wave_3_elsa_data_v4',
                         variables=list('scfrd','scfrdg','scfrdh','scfrdi'), missings = TRUE)
```

```{r local3, echo=F}
ELSA_w3_cont_fr <- opal.execute(o,'ELSA_w3_cont_fr')
Categorical_summary(var = ELSA_w3_cont_fr$scfrd, missing_values = NA)
ggplot(ELSA_w3_cont_fr, aes(x=factor(scfrd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has got any friends?") + ylab("Frequency")
Categorical_summary(var = ELSA_w3_cont_fr$scfrdg, missing_values = NA)
ggplot(ELSA_w3_cont_fr, aes(x=factor(scfrdg))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How many of his/her friends he/she has a close relationship") + ylab("Frequency")
Categorical_summary(var = ELSA_w3_cont_fr$scfrdh, missing_values = NA)
ggplot(ELSA_w3_cont_fr, aes(x=factor(scfrdh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("on average how often do you speak on the phone with your friends") + ylab("Frequency")
Categorical_summary(var = ELSA_w3_cont_fr$scfrdi, missing_values = NA)
ggplot(ELSA_w3_cont_fr, aes(x=factor(scfrdi))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("on average how often do you write or email your friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `scfrdg in (1,2,3) OR scfrdh in (1,2,3) OR scfrdi in (1,2,3) into 1`
* `scfrdg in (4,5,6) AND scfrdh in (4,5,6) AND scfrdi in (4,5,6) into 0`
* `scfrd=2 into 990`
* `scfrdg = -9 OR scfrdh = -9 OR scfrdi  = -9 into 995`
* `scfrdg = -8 OR scfrdh = -8 OR scfrdi  = -8 into 998`
* `scfrdg = -1 OR scfrdh = -1 OR scfrdi  = -1 into 996`
* `NA into 999`

**R script:**

```{r harmo3, echo=TRUE}
ELSA_ds_w3 <- tibble(id=ELSA_w3_cont_fr$id)

ELSA_w3_cont_fr$scfrd <- car::recode(as.vector(ELSA_w3_cont_fr$scfrd), "NA='-999'")
ELSA_w3_cont_fr$scfrdg <- car::recode(as.vector(ELSA_w3_cont_fr$scfrdg), "NA='-999'")
ELSA_w3_cont_fr$scfrdh <- car::recode(as.vector(ELSA_w3_cont_fr$scfrdh), "NA='-999'")
ELSA_w3_cont_fr$scfrdi <- car::recode(as.vector(ELSA_w3_cont_fr$scfrdi), "NA='-999'")

ELSA_ds_w3$cont_fr <- c(NA)  
for(i in 1:dim(ELSA_w3_cont_fr)[1]){
  if( ELSA_w3_cont_fr$scfrdg[i] %in% c(1,2,3) | ELSA_w3_cont_fr$scfrdh[i] %in% c(1,2,3) | ELSA_w3_cont_fr$scfrdi[i] %in% c(1,2,3) ) { 
    ELSA_ds_w3$cont_fr[i] = 1 }
  else if( ELSA_w3_cont_fr$scfrdg[i] %in% c(4,5,6) & ELSA_w3_cont_fr$scfrdh[i] %in% c(4,5,6) & ELSA_w3_cont_fr$scfrdi[i] %in% c(4,5,6) ){ 
    ELSA_ds_w3$cont_fr[i] = 0 }
  else if( ELSA_w3_cont_fr$scfrd[i] == 2 ){ 
    ELSA_ds_w3$cont_fr[i] = 990 }
  else if( ELSA_w3_cont_fr$scfrdg[i] == -9 | ELSA_w3_cont_fr$scfrdh[i] == -9 | ELSA_w3_cont_fr$scfrdi[i] == -9 ){ 
    ELSA_ds_w3$cont_fr[i] = 995 }
  else if( ELSA_w3_cont_fr$scfrdg[i] == -8 | ELSA_w3_cont_fr$scfrdh[i] == -8 | ELSA_w3_cont_fr$scfrdi[i] == -8 ){ 
    ELSA_ds_w3$cont_fr[i] = 998 }
  else if( ELSA_w3_cont_fr$scfrdg[i] == -1 | ELSA_w3_cont_fr$scfrdh[i] == -1 | ELSA_w3_cont_fr$scfrdi[i] == -1 ){ 
    ELSA_ds_w3$cont_fr[i] = 996 }
}

ELSA_ds_w3$cont_fr <- car::recode(as.vector(ELSA_ds_w3$cont_fr), "NA='999'")
ELSA_ds_w3$cont_fr <- labelled(ELSA_ds_w3$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991, "NOT APPLICABLE - HAS NOT GOT ANY FRIENDS"=990))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=F}
vari <- ELSA_ds_w3$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w3$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w3, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

##### Validation
```{r crosstabulation3, echo=F}

```

 
 


###  Wave 4

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scfrd`
* Label: `do you have any friends`
* Categories:
    + `1	= Yes`
    + `2	= No`
* Missings:
    + `-9	= Not answered`
    + `-1	= Item not applicable`
    
    
* Name: `scfrdg`
* Label: `How often the respondent meets up with their friends`
* Categories:
    + `1	= Three or more times a week`
    + `2	= Once or twice a week`
    + `3	= Once or twice a month`	
    + `4	= Every few months`
    + `5	= Once or twice a year`
    + `6	= Less than once a year or never`
* Missings:
    + `-9	= Not answered`
    + `-8	= Don't know`
    + `-1	= Item not applicable`
    
    
* Name: `scfrdh`
* Label: `on average how often do you speak on the phone with your friends`
* Categories:
    + `1	= Three or more times a week`
    + `2	= Once or twice a week`
    + `3	= Once or twice a month`	
    + `4	= Every few months`
    + `5	= Once or twice a year`
    + `6	= Less than once a year or never`
* Missings:
    + `-9	= Not answered`
    + `-8	= Don't know`    
    + `-1	= Item not applicable`


* Name: `scfrdi`
* Label: `on average how often do you write or email your friends`
* Categories:
    + `1	= Three or more times a week`
    + `2	= Once or twice a week`
    + `3	= Once or twice a month`	
    + `4	= Every few months`
    + `5	= Once or twice a year`
    + `6	= Less than once a year or never`
* Missings:
    + `-9	= Not answered`
    + `-8	= Don't know`    
    + `-1	= Item not applicable`


* Description: 
```{r assign4, echo=F}
opal.assign.table.tibble(o, 'ELSA_w4_cont_fr','ELSA.wave_4_elsa_data_v3',
                         variables=list('scfrd','scfrdg','scfrdh','scfrdi'), missings = TRUE)
```

```{r local4, echo=F}
ELSA_w4_cont_fr <- opal.execute(o,'ELSA_w4_cont_fr')
Categorical_summary(var = ELSA_w4_cont_fr$scfrd, missing_values = NA)
ggplot(ELSA_w4_cont_fr, aes(x=factor(scfrd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has got any friends?") + ylab("Frequency")
Categorical_summary(var = ELSA_w4_cont_fr$scfrdg, missing_values = NA)
ggplot(ELSA_w4_cont_fr, aes(x=factor(scfrdg))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How many of his/her friends he/she has a close relationship") + ylab("Frequency")
Categorical_summary(var = ELSA_w4_cont_fr$scfrdh, missing_values = NA)
ggplot(ELSA_w4_cont_fr, aes(x=factor(scfrdh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("on average how often do you speak on the phone with your friends") + ylab("Frequency")
Categorical_summary(var = ELSA_w4_cont_fr$scfrdi, missing_values = NA)
ggplot(ELSA_w4_cont_fr, aes(x=factor(scfrdi))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("on average how often do you write or email your friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `scfrdg in (1,2,3) OR scfrdh in (1,2,3) OR scfrdi in (1,2,3) into 1`
* `scfrdg in (4,5,6) AND scfrdh in (4,5,6) AND scfrdi in (4,5,6) into 0`
* `scfrd=2 into 990`
* `scfrdg = -9 OR scfrdh = -9 OR scfrdi  = -9 into 995`
* `scfrdg = -8 OR scfrdh = -8 OR scfrdi  = -8 into 998`
* `scfrdg = -1 OR scfrdh = -1 OR scfrdi  = -1 into 996`
* `NA into 999`

**R script:**

```{r harmo4, echo=TRUE}
ELSA_ds_w4 <- tibble(id=ELSA_w4_cont_fr$id)

ELSA_w4_cont_fr$scfrd <- car::recode(as.vector(ELSA_w4_cont_fr$scfrd), "NA='-999'")
ELSA_w4_cont_fr$scfrdg <- car::recode(as.vector(ELSA_w4_cont_fr$scfrdg), "NA='-999'")
ELSA_w4_cont_fr$scfrdh <- car::recode(as.vector(ELSA_w4_cont_fr$scfrdh), "NA='-999'")
ELSA_w4_cont_fr$scfrdi <- car::recode(as.vector(ELSA_w4_cont_fr$scfrdi), "NA='-999'")

ELSA_ds_w4$cont_fr <- c(NA)  
for(i in 1:dim(ELSA_w4_cont_fr)[1]){
  if( ELSA_w4_cont_fr$scfrdg[i] %in% c(1,2,3) | ELSA_w4_cont_fr$scfrdh[i] %in% c(1,2,3) | ELSA_w4_cont_fr$scfrdi[i] %in% c(1,2,3) ) { 
    ELSA_ds_w4$cont_fr[i] = 1 }
  else if( ELSA_w4_cont_fr$scfrdg[i] %in% c(4,5,6) & ELSA_w4_cont_fr$scfrdh[i] %in% c(4,5,6) & ELSA_w4_cont_fr$scfrdi[i] %in% c(4,5,6) ){ 
    ELSA_ds_w4$cont_fr[i] = 0 }
  else if( ELSA_w4_cont_fr$scfrd[i] == 2 ){ 
    ELSA_ds_w4$cont_fr[i] = 990 }
  else if( ELSA_w4_cont_fr$scfrdg[i] == -9 | ELSA_w4_cont_fr$scfrdh[i] == -9 | ELSA_w4_cont_fr$scfrdi[i] == -9 ){ 
    ELSA_ds_w4$cont_fr[i] = 995 }
  else if( ELSA_w4_cont_fr$scfrdg[i] == -8 | ELSA_w4_cont_fr$scfrdh[i] == -8 | ELSA_w4_cont_fr$scfrdi[i] == -8 ){ 
    ELSA_ds_w4$cont_fr[i] = 998 }
  else if( ELSA_w4_cont_fr$scfrdg[i] == -1 | ELSA_w4_cont_fr$scfrdh[i] == -1 | ELSA_w4_cont_fr$scfrdi[i] == -1 ){ 
    ELSA_ds_w4$cont_fr[i] = 996 }
}

ELSA_ds_w4$cont_fr <- car::recode(as.vector(ELSA_ds_w4$cont_fr), "NA='999'")
ELSA_ds_w4$cont_fr <- labelled(ELSA_ds_w4$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991, "NOT APPLICABLE - HAS NOT GOT ANY FRIENDS"=990))
```

#### Statistical description of the new harmonised variable
```{r descript4, echo=F}
vari <- ELSA_ds_w4$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w4$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w4, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

##### Validation
```{r crosstabulation4, echo=F}

```

 
 


### Wave 5

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scfrd`
* Label: `do you have any friends`
* Categories:
    + `1	= Yes`
    + `2	= No`
* Missings:
    + `-9	= Not answered`
    + `-1	= Item not applicable`
    
    
* Name: `scfrdg`
* Label: `How often the respondent meets up with their friends`
* Categories:
    + `1	= Three or more times a week`
    + `2	= Once or twice a week`
    + `3	= Once or twice a month`	
    + `4	= Every few months`
    + `5	= Once or twice a year`
    + `6	= Less than once a year or never`
* Missings:
    + `-9	= Not answered`
    + `-8	= Don't know`
    + `-2 = Schedule not applicable`
    + `-1	= Item not applicable`
    
    
* Name: `scfrdh`
* Label: `on average how often do you speak on the phone with your friends`
* Categories:
    + `1	= Three or more times a week`
    + `2	= Once or twice a week`
    + `3	= Once or twice a month`	
    + `4	= Every few months`
    + `5	= Once or twice a year`
    + `6	= Less than once a year or never`
* Missings:
    + `-9	= Not answered`
    + `-8	= Don't know`    
    + `-2 = Schedule not applicable`
    + `-1	= Item not applicable`


* Name: `scfrdi`
* Label: `on average how often do you write or email your friends`
* Categories:
    + `1	= Three or more times a week`
    + `2	= Once or twice a week`
    + `3	= Once or twice a month`	
    + `4	= Every few months`
    + `5	= Once or twice a year`
    + `6	= Less than once a year or never`
* Missings:
    + `-9	= Not answered`
    + `-8	= Don't know`    
    + `-2 = Schedule not applicable`
    + `-1	= Item not applicable`


* Description: 
```{r assign5, echo=F}
opal.assign.table.tibble(o, 'ELSA_w5_cont_fr','ELSA.wave_5_elsa_data_v4',
                         variables=list('scfrd','scfrdg','scfrdh','scfrdi'), missings = TRUE)
```

```{r local5, echo=F}
ELSA_w5_cont_fr <- opal.execute(o,'ELSA_w5_cont_fr')
Categorical_summary(var = ELSA_w5_cont_fr$scfrd, missing_values = NA)
ggplot(ELSA_w5_cont_fr, aes(x=factor(scfrd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has got any friends?") + ylab("Frequency")
Categorical_summary(var = ELSA_w5_cont_fr$scfrdg, missing_values = NA)
ggplot(ELSA_w5_cont_fr, aes(x=factor(scfrdg))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How many of his/her friends he/she has a close relationship") + ylab("Frequency")
Categorical_summary(var = ELSA_w5_cont_fr$scfrdh, missing_values = NA)
ggplot(ELSA_w5_cont_fr, aes(x=factor(scfrdh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("on average how often do you speak on the phone with your friends") + ylab("Frequency")
Categorical_summary(var = ELSA_w5_cont_fr$scfrdi, missing_values = NA)
ggplot(ELSA_w5_cont_fr, aes(x=factor(scfrdi))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("on average how often do you write or email your friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `scfrdg in (1,2,3) OR scfrdh in (1,2,3) OR scfrdi in (1,2,3) into 1`
* `scfrdg in (4,5,6) AND scfrdh in (4,5,6) AND scfrdi in (4,5,6) into 0`
* `scfrd=2 into 990`
* `scfrdg = -9 OR scfrdh = -9 OR scfrdi  = -9 into 995`
* `scfrdg = -8 OR scfrdh = -8 OR scfrdi  = -8 into 998`
* `scfrdg in (-1, -2) OR scfrdh in (-1, -2) OR scfrdi in (-1, -2) into 996`
* `NA into 999`

**R script:**

```{r harmo5, echo=TRUE}
ELSA_ds_w5 <- tibble(id=ELSA_w5_cont_fr$id)

ELSA_w5_cont_fr$scfrd <- car::recode(as.vector(ELSA_w5_cont_fr$scfrd), "NA='-999'")
ELSA_w5_cont_fr$scfrdg <- car::recode(as.vector(ELSA_w5_cont_fr$scfrdg), "NA='-999'")
ELSA_w5_cont_fr$scfrdh <- car::recode(as.vector(ELSA_w5_cont_fr$scfrdh), "NA='-999'")
ELSA_w5_cont_fr$scfrdi <- car::recode(as.vector(ELSA_w5_cont_fr$scfrdi), "NA='-999'")

ELSA_ds_w5$cont_fr <- c(NA)  
for(i in 1:dim(ELSA_w5_cont_fr)[1]){
  if( ELSA_w5_cont_fr$scfrdg[i] %in% c(1,2,3) | ELSA_w5_cont_fr$scfrdh[i] %in% c(1,2,3) | ELSA_w5_cont_fr$scfrdi[i] %in% c(1,2,3) ) { 
    ELSA_ds_w5$cont_fr[i] = 1 }
  else if( ELSA_w5_cont_fr$scfrdg[i] %in% c(4,5,6) & ELSA_w5_cont_fr$scfrdh[i] %in% c(4,5,6) & ELSA_w5_cont_fr$scfrdi[i] %in% c(4,5,6) ){ 
    ELSA_ds_w5$cont_fr[i] = 0 }
  else if( ELSA_w5_cont_fr$scfrd[i] == 2 ){ 
    ELSA_ds_w5$cont_fr[i] = 990 }
  else if( ELSA_w5_cont_fr$scfrdg[i] == -9 | ELSA_w5_cont_fr$scfrdh[i] == -9 | ELSA_w5_cont_fr$scfrdi[i] == -9 ){ 
    ELSA_ds_w5$cont_fr[i] = 995 }
  else if( ELSA_w5_cont_fr$scfrdg[i] == -8 | ELSA_w5_cont_fr$scfrdh[i] == -8 | ELSA_w5_cont_fr$scfrdi[i] == -8 ){ 
    ELSA_ds_w5$cont_fr[i] = 998 }
  else if( ELSA_w5_cont_fr$scfrdg[i] %in% c(-1, -2) | ELSA_w5_cont_fr$scfrdh[i] %in% c(-1, -2) |  
           ELSA_w5_cont_fr$scfrdi[i] %in% c(-1, -2) ){ 
    ELSA_ds_w5$cont_fr[i] = 996 }
}

ELSA_ds_w5$cont_fr <- car::recode(as.vector(ELSA_ds_w5$cont_fr), "NA='999'")
ELSA_ds_w5$cont_fr <- labelled(ELSA_ds_w5$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991, "NOT APPLICABLE - HAS NOT GOT ANY FRIENDS"=990))
```

#### Statistical description of the new harmonised variable
```{r descript5, echo=F}
vari <- ELSA_ds_w5$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w5$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w5, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

##### Validation
```{r crosstabulation5, echo=F}

```

 
 


### Wave 6

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scfrd`
* Label: `do you have any friends`
* Categories:
    + `1	= Yes`
    + `2	= No`
* Missings:
    + `-9	= Not answered`
    + `-1	= Item not applicable`
    
    
* Name: `scfrdg`
* Label: `How often the respondent meets up with their friends`
* Categories:
    + `1	= Three or more times a week`
    + `2	= Once or twice a week`
    + `3	= Once or twice a month`	
    + `4	= Every few months`
    + `5	= Once or twice a year`
    + `6	= Less than once a year or never`
* Missings:
    + `-9	= Not answered`
    + `-8	= Don't know`
    + `-2 = Schedule not applicable`
    + `-1	= Item not applicable`
    
* Name: `scfrdh`
* Label: `on average how often do you speak on the phone with your friends`
* Categories:
    + `1	= Three or more times a week`
    + `2	= Once or twice a week`
    + `3	= Once or twice a month`	
    + `4	= Every few months`
    + `5	= Once or twice a year`
    + `6	= Less than once a year or never`
* Missings:
    + `-9	= Not answered`
    + `-8	= Don't know`    
    + `-2 = Schedule not applicable`
    + `-1	= Item not applicable`

* Name: `scfrdi`
* Label: `on average how often do you write or email your friends`
* Categories:
    + `1	= Three or more times a week`
    + `2	= Once or twice a week`
    + `3	= Once or twice a month`	
    + `4	= Every few months`
    + `5	= Once or twice a year`
    + `6	= Less than once a year or never`
* Missings:
    + `-9	= Not answered`
    + `-8	= Don't know`    
    + `-2 = Schedule not applicable`
    + `-1	= Item not applicable`
    
* Name: `scfrdt`
* Label: `How often the respondent sends or receives text messsages to/from their friends`
* Categories:
    + `1	= Three or more times a week`
    + `2	= Once or twice a week`
    + `3	= Once or twice a month`	
    + `4	= Every few months`
    + `5	= Once or twice a year`
    + `6	= Less than once a year or never`
* Missings:
    + `-9	= Not answered`
    + `-8	= Don't know`    
    + `-2 = Schedule not applicable`
    + `-1	= Item not applicable`


* Description: 
```{r assign6, echo=F}
opal.assign.table.tibble(o, 'ELSA_w6_cont_fr','ELSA.wave_6_elsa_data_v2',
                         variables=list('scfrd','scfrdg','scfrdh','scfrdi','scfrdt'), missings = TRUE)
```

```{r local6, echo=F}
ELSA_w6_cont_fr <- opal.execute(o,'ELSA_w6_cont_fr')
Categorical_summary(var = ELSA_w6_cont_fr$scfrd, missing_values = NA)
ggplot(ELSA_w6_cont_fr, aes(x=factor(scfrd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has got any friends?") + ylab("Frequency")
Categorical_summary(var = ELSA_w6_cont_fr$scfrdg, missing_values = NA)
ggplot(ELSA_w6_cont_fr, aes(x=factor(scfrdg))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How many of his/her friends he/she has a close relationship") + ylab("Frequency")
Categorical_summary(var = ELSA_w6_cont_fr$scfrdh, missing_values = NA)
ggplot(ELSA_w6_cont_fr, aes(x=factor(scfrdh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("on average how often do you speak on the phone with your friends") + ylab("Frequency")
Categorical_summary(var = ELSA_w6_cont_fr$scfrdi, missing_values = NA)
ggplot(ELSA_w6_cont_fr, aes(x=factor(scfrdi))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("on average how often do you write or email your friends") + ylab("Frequency")
Categorical_summary(var = ELSA_w6_cont_fr$scfrdt, missing_values = NA)
ggplot(ELSA_w6_cont_fr, aes(x=factor(scfrdt))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How often the respondent sends or receives text messsages to/from their friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `scfrdg in (1,2,3) OR scfrdh in (1,2,3) OR scfrdi in (1,2,3) OR scfrdt in (1,2,3) into 1`
* `scfrdg in (4,5,6) AND scfrdh in (4,5,6) AND scfrdi in (4,5,6) AND scfrdt in (4,5,6) into 0`
* `scfrd=2 into 990`
* `scfrdg = -9 OR scfrdh = -9 OR scfrdi  = -9 OR scfrdt  = -9 into 995`
* `scfrdg = -8 OR scfrdh = -8 OR scfrdi  = -8 OR scfrdt  = -8 into 998`
* `scfrdg in (-1, -2) OR scfrdh in (-1, -2) OR scfrdi in (-1, -2) OR scfrdt in (-1, -2) into 996`
* `NA into 999`

**R script:**

```{r harmo6, echo=TRUE}
ELSA_ds_w6 <- tibble(id=ELSA_w6_cont_fr$id)

ELSA_w6_cont_fr$scfrd <- car::recode(as.vector(ELSA_w6_cont_fr$scfrd), "NA='-999'")
ELSA_w6_cont_fr$scfrdg <- car::recode(as.vector(ELSA_w6_cont_fr$scfrdg), "NA='-999'")
ELSA_w6_cont_fr$scfrdh <- car::recode(as.vector(ELSA_w6_cont_fr$scfrdh), "NA='-999'")
ELSA_w6_cont_fr$scfrdi <- car::recode(as.vector(ELSA_w6_cont_fr$scfrdi), "NA='-999'")
ELSA_w6_cont_fr$scfrdt <- car::recode(as.vector(ELSA_w6_cont_fr$scfrdt), "NA='-999'")

ELSA_ds_w6$cont_fr <- c(NA)  
for(i in 1:dim(ELSA_w6_cont_fr)[1]){
  if( ELSA_w6_cont_fr$scfrdg[i] %in% c(1,2,3) | ELSA_w6_cont_fr$scfrdh[i] %in% c(1,2,3) |  
      ELSA_w6_cont_fr$scfrdi[i] %in% c(1,2,3) | ELSA_w6_cont_fr$scfrdt[i] %in% c(1,2,3) ) { 
    ELSA_ds_w6$cont_fr[i] = 1 }
  else if( ELSA_w6_cont_fr$scfrdg[i] %in% c(4,5,6) & ELSA_w6_cont_fr$scfrdh[i] %in% c(4,5,6) &  
           ELSA_w6_cont_fr$scfrdi[i] %in% c(4,5,6) & ELSA_w6_cont_fr$scfrdt[i] %in% c(4,5,6) ){ 
    ELSA_ds_w6$cont_fr[i] = 0 }
  else if( ELSA_w6_cont_fr$scfrd[i] == 2 ){ 
    ELSA_ds_w6$cont_fr[i] = 990 }
  else if( ELSA_w6_cont_fr$scfrdg[i] == -9 | ELSA_w6_cont_fr$scfrdh[i] == -9 |  
           ELSA_w6_cont_fr$scfrdi[i] == -9 | ELSA_w6_cont_fr$scfrdt[i] == -9 ){ 
    ELSA_ds_w6$cont_fr[i] = 995 }
  else if( ELSA_w6_cont_fr$scfrdg[i] == -8 | ELSA_w6_cont_fr$scfrdh[i] == -8 |
           ELSA_w6_cont_fr$scfrdi[i] == -8 | ELSA_w6_cont_fr$scfrdt[i] == -8 ){ 
    ELSA_ds_w6$cont_fr[i] = 998 }
  else if( ELSA_w6_cont_fr$scfrdg[i] %in% c(-1,-2) | ELSA_w6_cont_fr$scfrdh[i] %in% c(-1,-2) | 
         ELSA_w6_cont_fr$scfrdi[i] %in% c(-1,-2) | ELSA_w6_cont_fr$scfrdt[i] %in% c(-1,-2) ){ 
    ELSA_ds_w6$cont_fr[i] = 996 }
}

ELSA_ds_w6$cont_fr <- car::recode(as.vector(ELSA_ds_w6$cont_fr), "NA='999'")
ELSA_ds_w6$cont_fr <- labelled(ELSA_ds_w6$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991, "NOT APPLICABLE - HAS NOT GOT ANY FRIENDS"=990))
```

#### Statistical description of the new harmonised variable
```{r descript6, echo=F}
vari <- ELSA_ds_w6$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w6$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w6, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

##### Validation
```{r crosstabulation6, echo=F}

```

 
 



### Wave 7

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `scfrd`
* Label: `do you have any friends`
* Categories:
    + `1	= Yes`
    + `2	= No`
* Missings:
    + `-9	= Not answered`
    + `-1	= Item not applicable`
    
    
* Name: `scfrdg`
* Label: `How often the respondent meets up with their friends`
* Categories:
    + `1	= Three or more times a week`
    + `2	= Once or twice a week`
    + `3	= Once or twice a month`	
    + `4	= Every few months`
    + `5	= Once or twice a year`
    + `6	= Less than once a year or never`
* Missings:
    + `-9	= Not answered`
    + `-8	= Don't know`
    + `-2 = Schedule not applicable`
    + `-1	= Item not applicable`
    
* Name: `scfrdh`
* Label: `on average how often do you speak on the phone with your friends`
* Categories:
    + `1	= Three or more times a week`
    + `2	= Once or twice a week`
    + `3	= Once or twice a month`	
    + `4	= Every few months`
    + `5	= Once or twice a year`
    + `6	= Less than once a year or never`
* Missings:
    + `-9	= Not answered`
    + `-8	= Don't know`    
    + `-2 = Schedule not applicable`
    + `-1	= Item not applicable`

* Name: `scfrdi`
* Label: `on average how often do you write or email your friends`
* Categories:
    + `1	= Three or more times a week`
    + `2	= Once or twice a week`
    + `3	= Once or twice a month`	
    + `4	= Every few months`
    + `5	= Once or twice a year`
    + `6	= Less than once a year or never`
* Missings:
    + `-9	= Not answered`
    + `-8	= Don't know`    
    + `-2 = Schedule not applicable`
    + `-1	= Item not applicable`


* Description: 
```{r assign7, echo=F}
opal.assign.table.tibble(o, 'ELSA_w7_cont_fr','ELSA.wave_7_elsa_data',
                         variables=list('scfrd','scfrdg','scfrdh','scfrdi'), missings = TRUE)
```

```{r local7, echo=F}
ELSA_w7_cont_fr <- opal.execute(o,'ELSA_w7_cont_fr')
Categorical_summary(var = ELSA_w7_cont_fr$scfrd, missing_values = NA)
ggplot(ELSA_w7_cont_fr, aes(x=factor(scfrd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has got any friends?") + ylab("Frequency")
Categorical_summary(var = ELSA_w7_cont_fr$scfrdg, missing_values = NA)
ggplot(ELSA_w7_cont_fr, aes(x=factor(scfrdg))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How many of his/her friends he/she has a close relationship") + ylab("Frequency")
Categorical_summary(var = ELSA_w7_cont_fr$scfrdh, missing_values = NA)
ggplot(ELSA_w7_cont_fr, aes(x=factor(scfrdh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("on average how often do you speak on the phone with your friends") + ylab("Frequency")
Categorical_summary(var = ELSA_w7_cont_fr$scfrdi, missing_values = NA)
ggplot(ELSA_w7_cont_fr, aes(x=factor(scfrdi))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("on average how often do you write or email your friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `scfrdg in (1,2,3) OR scfrdh in (1,2,3) OR scfrdi in (1,2,3) into 1`
* `scfrdg in (4,5,6) AND scfrdh in (4,5,6) AND scfrdi in (4,5,6) into 0`
* `scfrd=2 into 990`
* `scfrdg = -9 OR scfrdh = -9 OR scfrdi  = -9 into 995`
* `scfrdg = -8 OR scfrdh = -8 OR scfrdi  = -8 into 998`
* `scfrdg in (-1, -2) OR scfrdh in (-1, -2) OR scfrdi in (-1, -2) into 996`
* `NA into 999`

**R script:**

```{r harmo7, echo=TRUE}
ELSA_ds_w7 <- tibble(id=ELSA_w7_cont_fr$id)

ELSA_w7_cont_fr$scfrd <- car::recode(as.vector(ELSA_w7_cont_fr$scfrd), "NA='-999'")
ELSA_w7_cont_fr$scfrdg <- car::recode(as.vector(ELSA_w7_cont_fr$scfrdg), "NA='-999'")
ELSA_w7_cont_fr$scfrdh <- car::recode(as.vector(ELSA_w7_cont_fr$scfrdh), "NA='-999'")
ELSA_w7_cont_fr$scfrdi <- car::recode(as.vector(ELSA_w7_cont_fr$scfrdi), "NA='-999'")

ELSA_ds_w7$cont_fr <- c(NA)  
for(i in 1:dim(ELSA_w7_cont_fr)[1]){
  if( ELSA_w7_cont_fr$scfrdg[i] %in% c(1,2,3) | ELSA_w7_cont_fr$scfrdh[i] %in% c(1,2,3) | ELSA_w7_cont_fr$scfrdi[i] %in% c(1,2,3) ) { 
    ELSA_ds_w7$cont_fr[i] = 1 }
  else if( ELSA_w7_cont_fr$scfrdg[i] %in% c(4,5,6) & ELSA_w7_cont_fr$scfrdh[i] %in% c(4,5,6) & ELSA_w7_cont_fr$scfrdi[i] %in% c(4,5,6) ){ 
    ELSA_ds_w7$cont_fr[i] = 0 }
  else if( ELSA_w7_cont_fr$scfrd[i] == 2 ){ 
    ELSA_ds_w7$cont_fr[i] = 990 }
  else if( ELSA_w7_cont_fr$scfrdg[i] == -9 | ELSA_w7_cont_fr$scfrdh[i] == -9 | ELSA_w7_cont_fr$scfrdi[i] == -9 ){ 
    ELSA_ds_w7$cont_fr[i] = 995 }
  else if( ELSA_w7_cont_fr$scfrdg[i] == -8 | ELSA_w7_cont_fr$scfrdh[i] == -8 | ELSA_w7_cont_fr$scfrdi[i] == -8 ){ 
    ELSA_ds_w7$cont_fr[i] = 998 }
  else if( ELSA_w7_cont_fr$scfrdg[i] %in% c(-1,-2) | ELSA_w7_cont_fr$scfrdh[i] %in% c(-1,-2) | 
           ELSA_w7_cont_fr$scfrdi[i] %in% c(-1,-2) ){ 
    ELSA_ds_w7$cont_fr[i] = 996 }
}

ELSA_ds_w7$cont_fr <- car::recode(as.vector(ELSA_ds_w7$cont_fr), "NA='999'")
ELSA_ds_w7$cont_fr <- labelled(ELSA_ds_w7$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991, "NOT APPLICABLE - HAS NOT GOT ANY FRIENDS"=990))
```

#### Statistical description of the new harmonised variable
```{r descript7, echo=F}
vari <- ELSA_ds_w7$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w7$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w7, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

##### Validation
```{r crosstabulation7, echo=F}

```

 
```{r save, echo=FALSE}
cont_fr <- ELSA_ds_w1
save(cont_fr, file = "../RData/w1/cont_fr.RData")
rm(cont_fr)

cont_fr <- ELSA_ds_w2
save(cont_fr, file = "../RData/w2/cont_fr.RData")
rm(cont_fr)

cont_fr <- ELSA_ds_w3
save(cont_fr, file = "../RData/w3/cont_fr.RData")
rm(cont_fr)

cont_fr <- ELSA_ds_w4
save(cont_fr, file = "../RData/w4/cont_fr.RData")
rm(cont_fr)

cont_fr <- ELSA_ds_w5
save(cont_fr, file = "../RData/w5/cont_fr.RData")
rm(cont_fr)

cont_fr <- ELSA_ds_w6
save(cont_fr, file = "../RData/w6/cont_fr.RData")
rm(cont_fr)

cont_fr <- ELSA_ds_w7
save(cont_fr, file = "../RData/w7/cont_fr.RData")
rm(cont_fr)


```


# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
