---
title: "Any voluntary/charitable activity"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/volunDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/volunDS.R')
```

<!-- ########################################################## --> 

# Data process

## Mexico

### Wave 1

#### Study-specific variable description

* Name: `a40`
* Label: `Volunteered last two years`
* Categories:
    + `1 = YES`
    + `2 = NO`
* Missings:
    + `8 = RF`
    + `9 = DK`
    
    
* Description: 
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'MHAS_w1_volun','Mexican Health Aging Study.MHAS-2001',variables=list('a40'), missings = TRUE)
```

```{r local1, echo=F}
MHAS_w1_volun <- opal.execute(o,'MHAS_w1_volun')
vari <- MHAS_w1_volun$a40
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w1_volun$a40, missing_values = NA)
ggplot(MHAS_w1_volun, aes(x=factor(a40))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Volunteered last two years") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1 INTO 1, 2 INTO 0`
* `8 into 997`
* `9 into 998`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
MHAS_ds_w1 <- tibble(id=MHAS_w1_volun$id)
MHAS_ds_w1$volun <- car::recode(as.vector(MHAS_w1_volun$a40), "1='1'; 2='0'; 8='997'; 9='998'; NA='999'")
MHAS_ds_w1$volun <- labelled(MHAS_ds_w1$volun, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <- MHAS_ds_w1$volun
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_ds_w1$volun, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w1, aes(x=factor(volun))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any voluntary/charitable activity") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(MHAS_ds_w1$volun)
BeforeH <- table(MHAS_w1_volun$a40, useNA='ifany')[c(2,1,3,4,5)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","8->997","9->998","NA->999")
kable(C)
```

 
 




### Wave 2

#### Study-specific variable description

* Name: `aa40`
* Label: `Any volunteer work in last 2 years`
* Categories:
    + `1 = YES`
    + `2 = NO`
* Missings:
    + `8 = RF`
    + `9 = DK`

* Name: `a40`
* Label: `In last 2 years-volunteer`
* Categories:
    + `1 = YES`
    + `2 = NO`
* Missings:
    + `8 = RF`
    + `9 = DK`
    
    
* Description: 
```{r assign2, echo=F}
opal.assign.table.tibble(o, 'MHAS_w2_volun','Mexican Health Aging Study.MHAS_2003',variables=list('aa40','a40'), missings = TRUE)
```

```{r local2, echo=F}
MHAS_w2_volun <- opal.execute(o,'MHAS_w2_volun')
vari <- MHAS_w2_volun$aa40
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w2_volun$aa40, missing_values = NA)
ggplot(MHAS_w2_volun, aes(x=factor(aa40))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any volunteer work in last 2 years") + ylab("Frequency")
vari <- MHAS_w2_volun$a40
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w2_volun$a40, missing_values = NA)
ggplot(MHAS_w2_volun, aes(x=factor(a40))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("In last 2 years-volunteer") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if aa40=1 or a40=1 then 1`
* `if aa40=2 and a40=2 then 0`
* `8 into 997`
* `9 into 998`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
MHAS_ds_w2 <- tibble(id=MHAS_w2_volun$id)

MHAS_w2_volun$aa40 <- car::recode(as.vector(MHAS_w2_volun$aa40), "NA='-999'")
MHAS_w2_volun$a40 <- car::recode(as.vector(MHAS_w2_volun$a40), "NA='-999'")

MHAS_ds_w2$volun <- c(NA)
for(i in 1:dim(MHAS_w2_volun)[1]){
  if( MHAS_w2_volun$aa40[i] == 1 | MHAS_w2_volun$a40[i] == 1 ) {
    MHAS_ds_w2$volun[i] = 1 }
  else if( MHAS_w2_volun$aa40[i] == 2 | MHAS_w2_volun$a40[i] == 2 ) {
    MHAS_ds_w2$volun[i] = 0 }
  else if( MHAS_w2_volun$aa40[i] == 8 | MHAS_w2_volun$a40[i] == 8 ) {
    MHAS_ds_w2$volun[i] = 997 }
  else if( MHAS_w2_volun$aa40[i] == 9 | MHAS_w2_volun$a40[i] == 9 ) {
    MHAS_ds_w2$volun[i] = 998 }
}

MHAS_ds_w2$volun <- car::recode(as.vector(MHAS_ds_w2$volun), "NA='999'")
MHAS_ds_w2$volun <- labelled(MHAS_ds_w2$volun, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}
vari <- MHAS_ds_w2$volun
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_ds_w2$volun, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w2, aes(x=factor(volun))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any voluntary/charitable activity") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}

```

 
 



### Wave 3

#### Study-specific variable description

The study-specific variable elected to be harmonised is:
  
* Name: `aa40_12`
* Label: `Any volunteer work in last 2 years`
* Categories:
    + `1 = YES`
    + `2 = NO`
* Missings:
    + `8 = RF`
    + `9 = DK`

* Name: `a37_12`
* Label: `In last 2 years-volunteer`
* Categories:
    + `1 = YES`
    + `2 = NO`
* Missings:
    + `8 = RF`
    + `9 = DK`
    
    
* Description: 
```{r assign3, echo=F}
opal.assign.table.tibble(o, 'MHAS_w3_volun','Mexican Health Aging Study.MHAS_2012_new',variables=list('aa40_12','a37_12'), missings = TRUE)
```

```{r local3, echo=F}
MHAS_w3_volun <- opal.execute(o,'MHAS_w3_volun')
vari <- MHAS_w3_volun$aa40_12
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w3_volun$aa40_12, missing_values = NA)
ggplot(MHAS_w3_volun, aes(x=factor(aa40_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any volunteer work in last 2 years") + ylab("Frequency")
vari <- MHAS_w3_volun$a37_12
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w3_volun$a37_12, missing_values = NA)
ggplot(MHAS_w3_volun, aes(x=factor(a37_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("In last 2 years-volunteer") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if aa40_12=1 or a37_12=1 then 1`
* `if aa40_12=2 and a37_12=2 then 0`
* `8 into 997`
* `9 into 998`
* `NA into 999`

**R script:**

```{r harmo3, echo=TRUE}
MHAS_ds_w3 <- tibble(id=MHAS_w3_volun$id)

MHAS_w3_volun$aa40_12 <- car::recode(as.vector(MHAS_w3_volun$aa40_12), "NA='-999'")
MHAS_w3_volun$a37_12 <- car::recode(as.vector(MHAS_w3_volun$a37_12), "NA='-999'")

MHAS_ds_w3$volun <- c(NA)
for(i in 1:dim(MHAS_w3_volun)[1]){
  if( MHAS_w3_volun$aa40_12[i] == 1 | MHAS_w3_volun$a37_12[i] == 1 ) {
    MHAS_ds_w3$volun[i] = 1 }
  else if( MHAS_w3_volun$aa40_12[i] == 2 | MHAS_w3_volun$a37_12[i] == 2 ) {
    MHAS_ds_w3$volun[i] = 0 }
  else if( MHAS_w3_volun$aa40_12[i] == 8 | MHAS_w3_volun$a37_12[i] == 8 ) {
    MHAS_ds_w3$volun[i] = 997 }
  else if( MHAS_w3_volun$aa40_12[i] == 9 | MHAS_w3_volun$a37_12[i] == 9 ) {
    MHAS_ds_w3$volun[i] = 998 }
}

MHAS_ds_w3$volun <- car::recode(as.vector(MHAS_ds_w3$volun), "NA='999'")
MHAS_ds_w3$volun <- labelled(MHAS_ds_w3$volun, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=F}
vari <- MHAS_ds_w3$volun
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_ds_w3$volun, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w3, aes(x=factor(volun))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any voluntary/charitable activity") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=F}

```

```{r save, echo=FALSE}
volun <- MHAS_ds_w1
save(volun, file = "../RData/w1/volun.RData")
rm(volun)

volun <- MHAS_ds_w2
save(volun, file = "../RData/w2/volun.RData")
rm(volun)

volun <- MHAS_ds_w3
save(volun, file = "../RData/w3/volun.RData")
rm(volun)

```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```






 