---
title: "Experience of a loss of any close person"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `bereav`
* Variable label: `Experience of a loss of any close person`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process

## Mexican population

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `a10`
* Label: `Current marital status`
* Categories: 
    + `1 = Single`
    + `2 = Married`
    + `3 = In a consensual union`
    + `4 = Divorced`
    + `5 = Separated from a union`
    + `6 = Separated from a marriage`
    + `7 = Widowed from a union`
    + `8 = Widowed from a marriage`
    
* Name: `f7`
* Label: `Age mother when died`

* Name: `f14`
* Label: `Age father when died`


* Description: 
```{r assign1}
opal.assign.table.tibble(o, 'MHAS_w1_bereav','Mexican Health Aging Study.MHAS-2001',variables=list('a10','f7','f14'), missings = TRUE)
```

```{r local1}
MHAS_w1_bereav <- opal.execute(o,'MHAS_w1_bereav')
vari <- MHAS_w1_bereav$a10
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = MHAS_w1_bereav$a10, missing_values = NA)
ggplot(MHAS_w1_bereav, aes(x=factor(a10))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Current marital status") + ylab("Frequency")

vari <- MHAS_w1_bereav$f7

kable(Continuous_summary(vari, missing_values = c(999))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Continuous_summary(vari, missing_values = c(999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values =c(999))$summary, caption = "Summary")
#Continuous_summary(var = MHAS_w1_bereav$f7, missing_values = NA)
ggplot(MHAS_w1_bereav, aes(f7)) + geom_histogram(stat="count", width=0.4, fill="steelblue") + xlab("Age mother when died") + ylab("Frequency")+ theme(axis.text.x = element_text(angle = 45, hjust=1, vjust=1)) + scale_x_continuous(limits = c(0, 130))

vari <- MHAS_w1_bereav$f14
kable(Continuous_summary(vari, missing_values = c(999))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Continuous_summary(vari, missing_values = c(999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values =c(999))$summary, caption = "Summary")
#Continuous_summary(var = MHAS_w1_bereav$f14, missing_values = NA)
ggplot(MHAS_w1_bereav, aes(f14)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Age father when died") + ylab("Frequency")+ theme(axis.text.x = element_text(angle = 45, hjust=1, vjust=1, size=6))+ scale_x_continuous(limits = c(0, 130))
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to becar::recode(as.vector(d as follows:

* `a10 in (7,8) OR (f7 != NA AND f7<150 because there are some values 999) OR   `
`  (f14 != NA AND f14<150 because there are some values 999) into 1`
* `a10 in (1,.,6) AND f7=NA AND f14=NA into 0`
* `NA into 999`
Note: it was observed that some individuals reported to large ages of death of parents. These individuals were used anyway.

**R script:**

```{r harmo1, echo=TRUE}
MHAS_ds_w1 <- tibble(id=MHAS_w1_bereav$id)

MHAS_w1_bereav$a10 <-car::recode(as.vector(MHAS_w1_bereav$a10), "NA='-999'")
MHAS_w1_bereav$f7 <-car::recode(as.vector(MHAS_w1_bereav$f7), "NA='-999'")
MHAS_w1_bereav$f14 <-car::recode(as.vector(MHAS_w1_bereav$f14), "NA='-999'")

MHAS_ds_w1$bereav <- c(NA)  
for(i in 1:dim(MHAS_w1_bereav)[1]){
  if(MHAS_w1_bereav$a10[i] %in% c(7,8) | (!(MHAS_w1_bereav$f7[i] == -999) & MHAS_w1_bereav$f7[i] < 150) |
    (!(MHAS_w1_bereav$f14[i] == -999) & MHAS_w1_bereav$f14[i] < 150) ){ 
    MHAS_ds_w1$bereav[i] = 1 }
  else if(MHAS_w1_bereav$a10[i] %in% c(1,2,3,4,5,6) & MHAS_w1_bereav$f7[i] == -999 & MHAS_w1_bereav$f14[i] == -999 ) { 
    MHAS_ds_w1$bereav[i] = 0 }
}

MHAS_ds_w1$bereav <-car::recode(as.vector(MHAS_ds_w1$bereav), "NA='999'")
MHAS_ds_w1$bereav <- labelled(MHAS_ds_w1$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1}
vari <- MHAS_ds_w1$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_ds_w1$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w1, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1}

```

 
 


### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `a3`
* Label: `Respondent's Marital status`
* Categories: 
    + `1 = single?`
    + `2 = married?`
    + `3 = in a consensual union?`
    + `4 = divorced?` 
    + `5 = separated from a union?`
    + `6 = separated from a marriage?`
    + `7 = widowed from a union?` 
    + `8 = widowed from a marriage?`

* Name: `f7`
* Label: `Mother passed away in these last two years`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `9 `

* Name: `f16`
* Label: `Father passed away in these last two years`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `9 `

* Name: `f35`
* Label: `Have any siblings passed away since 2001`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `9`


* Description: 
```{r assign2}
opal.assign.table.tibble(o, 'MHAS_w2_bereav','Mexican Health Aging Study.MHAS_2003',
                         variables=list('a3','f7','f16','f35'), missings = TRUE)
```

```{r local2}
MHAS_w2_bereav <- opal.execute(o,'MHAS_w2_bereav')

vari <- MHAS_w2_bereav$a3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = MHAS_w2_bereav$a3, missing_values = NA)
ggplot(MHAS_w2_bereav, aes(x=factor(a3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Respondent's Marital status") + ylab("Frequency")


vari <-  MHAS_w2_bereav$f7
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w2_bereav$f7, missing_values = NA)
ggplot(MHAS_w2_bereav, aes(x=factor(f7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mother passed away in these last two years") + ylab("Frequency")

vari <-  MHAS_w2_bereav$f16
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w2_bereav$f16, missing_values = NA)
ggplot(MHAS_w2_bereav, aes(x=factor(f16))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Father passed away in these last two years") + ylab("Frequency")

vari <-  MHAS_w2_bereav$f35
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w2_bereav$f35, missing_values = NA)
ggplot(MHAS_w2_bereav, aes(x=factor(f35))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Have any siblings passed away since 2001") + ylab("Frequency")
```

#### Harmonisation algorithm
Tocar::recode(as.vector( the harmonize variable from the study-specific variable it has to becar::recode(as.vector(d as follows:  

* `A3 in (7,8) OR f7=1 OR f16=1 OR f35=1 into 1`
* `A3 in (1,.,6) AND f7=2 AND f16=2 AND f35=2 into 0`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
MHAS_ds_w2 <- tibble(id=MHAS_w2_bereav$id)

MHAS_w2_bereav$a3 <-car::recode(as.vector(MHAS_w2_bereav$a3), "NA='-999'")
MHAS_w2_bereav$f7 <-car::recode(as.vector(MHAS_w2_bereav$f7), "NA='-999'")
MHAS_w2_bereav$f16 <-car::recode(as.vector(MHAS_w2_bereav$f16), "NA='-999'")
MHAS_w2_bereav$f35 <-car::recode(as.vector(MHAS_w2_bereav$f35), "NA='-999'")

MHAS_ds_w2$bereav <- c(NA)  
for(i in 1:dim(MHAS_w2_bereav)[1]){
  if(MHAS_w2_bereav$a3[i] %in% c(7,8) | MHAS_w2_bereav$f7[i] == 1 | MHAS_w2_bereav$f16[i] == 1 | MHAS_w2_bereav$f35[i] == 1){ 
    MHAS_ds_w2$bereav[i] = 1 }
  else if(MHAS_w2_bereav$a3[i] %in% c(1,2,3,4,5,6) & MHAS_w2_bereav$f7[i] == 2 & MHAS_w2_bereav$f16[i] == 2 &
        MHAS_w2_bereav$f35[i] == 2){ 
    MHAS_ds_w2$bereav[i] = 0 }
}

MHAS_ds_w2$bereav <-car::recode(as.vector(MHAS_ds_w2$bereav), "NA='999'")
MHAS_ds_w2$bereav <- labelled(MHAS_ds_w2$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2}
vari <- MHAS_ds_w2$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_ds_w2$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w2, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2}

```

 
 


### Wave 3

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `a3_12`
* Label: `Current marital status`
* Categories: 
    + `1 = Single`
    + `2 = Married`
    + `3 = In civil union`
    + `4 = Divorced` 
    + `5 = Separated from a civil union`
    + `6 = Separated from a marriage`
    + `7 = Widowed from civil union` 
    + `8 = Widowed from marriage`
    
* Name: `f1a_12`
* Label: `Last interview:Was respondent's mother living`
* Categories: 
    + `1 = Was alive 1`
    + `2 = Passed away 2`
* Missings:
    + `8 = RF 8`
    + `9 = DK 9`
    
* Name: `f10a_12`
* Label: `Last interview:Was respondent's father living`
* Categories: 
    + `1 = Was alive 1`
    + `2 = Passed away 2`
* Missings:
    + `8 = RF 8`
    + `9 = DK 9`
    
* Name: `sa19_12`
* Label: `Major event since 2001:Did any of deceased's children die`
* Categories: 
    + `1 = Was alive 1`
    + `2 = Passed away 2`
* Missings:
    + `8 = RF 8`
    + `9 = DK 9`  
    
* Name: `f35_12`
* Label: `Last 2 years:Has any of the respondent's siblings passed away`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `8 = RF`
    + `9 = DK`


* Description: 
```{r assign3}
opal.assign.table.tibble(o, 'MHAS_w3_bereav','Mexican Health Aging Study.MHAS_2012_new',
                         variables=list('a3_12','f1a_12','f10a_12','sa19_12','f35_12'), missings = TRUE)
```

```{r local3}
MHAS_w3_bereav <- opal.execute(o,'MHAS_w3_bereav')
vari <- MHAS_w3_bereav$a3_12
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = MHAS_w3_bereav$a3_12, missing_values = NA)
ggplot(MHAS_w3_bereav, aes(x=factor(a3_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Current marital status") + ylab("Frequency")

vari <- MHAS_w3_bereav$f1a_12
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w3_bereav$f1a_12, missing_values = NA)
ggplot(MHAS_w3_bereav, aes(x=factor(f1a_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Last interview:Was respondent's mother living") + ylab("Frequency")

vari <- MHAS_w3_bereav$f10a_12
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w3_bereav$f10a_12, missing_values = NA)
ggplot(MHAS_w3_bereav, aes(x=factor(f10a_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Last interview:Was respondent's father living") + ylab("Frequency")

vari <- MHAS_w3_bereav$sa19_12
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w3_bereav$sa19_12, missing_values = NA)
ggplot(MHAS_w3_bereav, aes(x=factor(sa19_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Major event since 2001:Did any of deceased's children die") + ylab("Frequency")

vari <- MHAS_w3_bereav$f35_12
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w3_bereav$f35_12, missing_values = NA)
ggplot(MHAS_w3_bereav, aes(x=factor(f35_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Last 2 years:Has any of the respondent's siblings passed away") + ylab("Frequency")
```

#### Harmonisation algorithm
Tocar::recode(as.vector( the harmonize variable from the study-specific variable it has to becar::recode(as.vector(d as follows:  

* `a3_12 in (7,8) OR f1a_12=2 OR f10a_12=2 OR sa19_12=2 OR f35_12=2 into 1`
* `a3_12 in (1,.,6) AND f1a_12=1 AND f10a_12=1 AND sa19_12=1 AND f35_12=1 into 0`
* `f1a_12=8 OR f10a_12=8 OR sa19_12=8 OR f35_12=8 into 997`
* `f1a_12=9 OR f10a_12=9 OR sa19_12=9 OR f35_12=9 into 998`
* `NA into 999`

**R script:**

```{r harmo3, echo=TRUE}
MHAS_ds_w3 <- tibble(id=MHAS_w3_bereav$id)

MHAS_w3_bereav$a3_12 <-car::recode(as.vector(MHAS_w3_bereav$a3_12), "NA='-999'")
MHAS_w3_bereav$f1a_12 <-car::recode(as.vector(MHAS_w3_bereav$f1a_12), "NA='-999'")
MHAS_w3_bereav$f10a_12 <-car::recode(as.vector(MHAS_w3_bereav$f10a_12), "NA='-999'")
MHAS_w3_bereav$f35_12 <-car::recode(as.vector(MHAS_w3_bereav$f35_12), "NA='-999'")
MHAS_w3_bereav$sa19_12 <-car::recode(as.vector(MHAS_w3_bereav$sa19_12), "NA='-999'")


MHAS_ds_w3$bereav <- c(NA)  
for(i in 1:dim(MHAS_w3_bereav)[1]){
  if(MHAS_w3_bereav$a3_12[i] %in% c(7,8) | MHAS_w3_bereav$f1a_12[i] == 2 | MHAS_w3_bereav$f10a_12[i] == 2 |
     MHAS_w3_bereav$f35_12[i] == 2 | MHAS_w3_bereav$sa19_12[i] == 2 ){ 
    MHAS_ds_w3$bereav[i] = 1 }
  else if(MHAS_w3_bereav$a3_12[i] == -999 & MHAS_w3_bereav$f1a_12[i]== -999 & MHAS_w3_bereav$f10a_12[i] == -999 &
          MHAS_w3_bereav$f35_12[i] == -999 & MHAS_w3_bereav$sa19_12[i] == -999 ){ 
    MHAS_ds_w3$bereav[i] = 999 }
  else if(MHAS_w3_bereav$a3_12[i] %in% c(1,2,3,4,5,6,-999) & MHAS_w3_bereav$f1a_12[i] %in% c(1,-999) & 
          MHAS_w3_bereav$f10a_12[i] %in% c(1,-999) & MHAS_w3_bereav$f35_12[i] %in% c(1,-999) & 
          MHAS_w3_bereav$sa19_12[i] %in% c(1,-999) ){ 
    MHAS_ds_w3$bereav[i] = 0 }
  else if(MHAS_w3_bereav$f1a_12[i] == 8 | MHAS_w3_bereav$f10a_12[i] == 8 |
          MHAS_w3_bereav$f35_12[i] == 8 | MHAS_w3_bereav$sa19_12[i] == 8 ){ 
    MHAS_ds_w3$bereav[i] = 997 }
  else if(MHAS_w3_bereav$f1a_12[i] == 9 | MHAS_w3_bereav$f10a_12[i] == 9 |
          MHAS_w3_bereav$f35_12[i] == 9 | MHAS_w3_bereav$sa19_12[i] == 9 ){ 
    MHAS_ds_w3$bereav[i] = 998 }
}

MHAS_ds_w3$bereav <-car::recode(as.vector(MHAS_ds_w3$bereav), "NA='999'")
MHAS_ds_w3$bereav <- labelled(MHAS_ds_w3$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3}
vari <- MHAS_ds_w3$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_ds_w3$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w3, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Experience of a loss of any close person") + ylab("Frequency")
```

##### Validation
```{r crosstabulation3}

```

 
```{r save, echo=FALSE}
bereav <- MHAS_ds_w1
save(bereav, file = "../RData/w1/bereav.RData")
rm(bereav)

bereav <- MHAS_ds_w2
save(bereav, file = "../RData/w2/bereav.RData")
rm(bereav)

bereav <- MHAS_ds_w3
save(bereav, file = "../RData/w3/bereav.RData")
rm(bereav)

```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
``` 
