---
title: "Has friend(s)/confidant"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/confidantDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/confidantDS.R')
```



<!-- ########################################################## --> 

# Data process

## Mexico

### Wave 1

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `G28`
* Label: `Friends in neighborhood`
* Categories: 
    + `1.0 = Yes` 
    + `2.0 = No` 
* Missings:
    + `8 = RF` 
    + `9 = DK` 


* Description: 
```{r assign1, echo=F}

opal.assign.table.tibble(o, 'MHAS_w1_confidant','Mexican Health Aging Study.g_house',variables=list('G28','G1'), missings = TRUE)
MHAS_w1_confidant <- opal.execute(o,'MHAS_w1_confidant')
opal.assign.table.tibble(o, 'MHAS_w1_id','Mexican Health Aging Study.MHAS-2001',variables=list('unhhid'), missings = T)
MHAS_w1_id <- opal.execute(o,'MHAS_w1_id')
MHAS_w1_id$unhhid <- paste0(as.character(MHAS_w1_id$unhhid),".0")
MHAS_w1 <- left_join(MHAS_w1_id,MHAS_w1_confidant,by=c("unhhid"="id"))

```


<!-- Code to check the 41 individuals of difference:

#Instead of the last line above, the next one:
MHAS_w1 <- left_join(MHAS_w1_id,MHAS_w1_confidant,by=c("unhhid"="id"))

MHAS_w1[which(sapply(paste0("^",substr(MHAS_w1$id,1,nchar(MHAS_w1$id)-4),"[12]0\\.0"),function(x) length(grep(x,MHAS_w1$id)))==1 & MHAS_w1$G1 %in% c(1,2) & MHAS_w1$G1!=as.numeric(substr(MHAS_w1$id,nchar(MHAS_w1$id)-3,nchar(MHAS_w1$id)-3))),]

-->


```{r local1, echo=F}

vari <- MHAS_w1_confidant$G28
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = MHAS_w1_confidant$G28, missing_values = NA)
ggplot(MHAS_w1_confidant, aes(x=factor(G28))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has friends in neighbourhood?") + ylab("Frequency")

```

#### Harmonisation algorithm


To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

The interviewer manual specifies:

`When both interviews are conducted with proxies, the TR-habitual residents, TR-Children (section B), and the section on Help and Children (section G) will be filled out only for the first interview. In order to facilitate this, Interview Control Sheets are included in the questionnaire.`

* `For each household id we get the id corresponding to the respondent from the household id (substring of the id's) and the interview code (G1). For them:`
* `keep up G28 == 1 into 1`
* `change G28 == 2 into 0`
* `change G28 == 8 into 997`
* `change G28 == 9 into 998`
* `otherwise into 999`

 

**R script:** 


```{r harmo1, echo=TRUE}

MHAS_ds_w1 <- tibble(id=MHAS_w1$id)
MHAS_ds_w1$confidant <- rep(999,length(MHAS_ds_w1$id))
MHAS_ds_w1$confidant[which(paste0(substr(MHAS_w1$id,1,nchar(MHAS_w1$id)-4),as.character(MHAS_w1$G1),"0.0")==MHAS_w1$id)] <- car::recode(as.vector(MHAS_w1$G28[which(paste0(substr(MHAS_w1$id,1,nchar(MHAS_w1$id)-4),as.character(MHAS_w1$G1),"0.0")==MHAS_w1$id)]), "1='1'; 2='0'; 8='997'; 9='998'; NA='999'")
MHAS_ds_w1$confidant <- labelled(MHAS_ds_w1$confidant, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))

```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <- MHAS_ds_w1$confidant
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_ds_w1$confidant, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w1, aes(x=factor(confidant))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has any friend(s)/confidants(s)?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}

```

 
 





### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `d6`
* Label: `Have friends and companions`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`
* Missings:
    + `8.0 = RF`
    + `9.0 = DK` 

* Description: 
```{r assign2, echo=F}
opal.assign.table.tibble(o, 'MHAS_w2_confidant','Mexican Health Aging Study.MHAS_2003',variables=list('d6'), missings = TRUE)
```

```{r local2, echo=F}
MHAS_w2_confidant <- opal.execute(o,'MHAS_w2_confidant')
vari <- MHAS_w2_confidant$d6
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = MHAS_w2_confidant$d6, missing_values = NA)
ggplot(MHAS_w2_confidant, aes(x=factor(d6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has friends and companions?") + ylab("Frequency")

```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1 Yes into 1`
* `2 No into 0`
* `8 RF into 997`
* `9 DK into 998`
* `NA into 999`

 

**R script:** 
```{r harmo2, echo=TRUE}
MHAS_ds_w2 <- tibble(id=MHAS_w2_confidant$id)
MHAS_ds_w2$confidant <- car::recode(as.vector(MHAS_w2_confidant$d6), "1='1'; 2='0'; 8='997'; 9='998'; NA='999'")
MHAS_ds_w2$confidant <- labelled(MHAS_ds_w2$confidant, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}
vari <- MHAS_ds_w2$confidant
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_ds_w2$confidant, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w2, aes(x=factor(confidant))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has any friend(s)/confidants(s)?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
AfterH <- table(MHAS_ds_w2$confidant)
BeforeH <- table(MHAS_w2_confidant$d6, useNA='ifany')[c(2,1,3,4,5)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1","8->997","9->998","NA->999")
kable(C)
```

 
 


### Wave 3

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `d23_12`
* Label: `Does respondent have friends,acquaintances or work colleagues`
* Categories: 
    + `1.0 = Yes`
    + `2.0 = No`
* Missings:
    + `8.0 = RF`
    + `9.0 = DK`


* Description: 
```{r assign3, echo=F}
opal.assign.table.tibble(o, 'MHAS_w3_confidant','Mexican Health Aging Study.MHAS_2012_new',variables=list('d23_12'), missings = TRUE)
```

```{r local3, echo=F}
MHAS_w3_confidant <- opal.execute(o,'MHAS_w3_confidant')
vari <- MHAS_w3_confidant$d23_12
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = MHAS_w3_confidant$d23_12, missing_values = NA)
ggplot(MHAS_w3_confidant, aes(x=factor(d23_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has any friends, acquaintances or work colleagues?") + ylab("Frequency")

```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1 Yes into 1`
* `2 No into 0`
* `8 Don't Know into 997` 
* `9 Not answered into 998`
* `NA into 999`

 

**R script:** 
```{r harmo3, echo=TRUE}
MHAS_ds_w3 <- tibble(id=MHAS_w3_confidant$id)
MHAS_ds_w3$confidant <- car::recode(as.vector(MHAS_w3_confidant$d23_12), "1='1'; 2='0'; 8='997'; 9='998'; NA='999'")
MHAS_ds_w3$confidant <- labelled(MHAS_ds_w3$confidant, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=F}
vari <- MHAS_ds_w3$confidant
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_ds_w3$confidant, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w3, aes(x=factor(confidant))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Has any friend(s)/confidants(s)?") + ylab("Frequency")
```

##### Validation
```{r crosstabulation3, echo=F}
AfterH <- table(MHAS_ds_w3$confidant)
BeforeH <- table(MHAS_w3_confidant$d23_12, useNA='ifany')[c(2,1,3,4,5)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1","8->997","9->998","NA->999")
kable(C)
```




## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.

**R script:**

```{r summ}

l.hds <- list(w1 = MHAS_ds_w1, w2 = MHAS_ds_w2, w3 = MHAS_ds_w3)


for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("MHAS_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}


t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label", names(l.hds))
kable(t.hds)


dbb <- get(paste0("MHAS_m_ds_",names(l.hds)[1]))[,c("id","confidant")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("MHAS_m_ds_",names(l.hds)[ind]))[,c("id","confidant")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", names(l.hds))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste0(v.dbb,dbb[,ind+1])
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb)

```






```{r save, echo=FALSE}
confidant <- MHAS_ds_w1
save(confidant, file = "../RData/w1/confidant.RData")
rm(confidant)

confidant <- MHAS_ds_w2
save(confidant, file = "../RData/w2/confidant.RData")
rm(confidant)

confidant <- MHAS_ds_w3
save(confidant, file = "../RData/w3/confidant.RData")
rm(confidant)

```

# Quality estimation

```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
