---
title: "Life-threatening situation"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/lifethreat_sitDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/lifethreat_sitDS.R')
```

<!-- ########################################################## --> 

# Data process

## MHAS

### Wave 1

Not found.

### Wave 2

Not found.

### Wave 3

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `sa22_12`
* Label: `Major event since 2001:Accident or..affected deceased's health/family situation`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings: 
    + `8 = RF`
    + `9 = DK`
    
* Name: `m4_1_12`
* Label: `Major event since 2001: respondent had a stroke`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings: 
    + `8 = Refused`
    + `9 = DK`
    
* Name: `m5_1_12`
* Label: `Major event since 2001: respondent had a heart attack`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings: 
    + `8 = Refused`
    + `9 = DK`
    
* Name: `m6_1_12`
* Label: `Major event since 2001: respondent had major surgery`
* Categories: 
    + `1 = Yes`
    + `2 = No`
    + `8 = Refused`
    + `9 = DK`
    
* Name: `m8_1_12`
* Label: `Major event since 2001: respondent was diagnosed with new cancer`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings: 
    + `8 = Refused`
    + `9 = DK`
    
* Name: `m10_1_12`
* Label: `Major event since 2001: respondent had accident .. affect health/family situation`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings: 
    + `8 = Refused`
    + `9 = DK`
    

```{r assign3, echo=F}

opal.assign.table.tibble(o, 'MHAS_w3_life_thr','Mexican Health Aging Study.MHAS_2012_new',variables=list('sa22_12','m4_1_12','m5_1_12','m6_1_12','m8_1_12','m10_1_12'), missings = TRUE)
MHAS_w3_life_thr <- opal.execute(o,'MHAS_w3_life_thr')

```

```{r local3, echo=F}
Categorical_summary(var = MHAS_w3_life_thr$sa22_12, missing_values = NA)
ggplot(MHAS_w3_life_thr, aes(x=factor(sa22_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Major event since 2001:Accident or..affected deceased's health/family situation") + ylab("Frequency")
Categorical_summary(var = MHAS_w3_life_thr$m4_1_12, missing_values = NA)
ggplot(MHAS_w3_life_thr, aes(x=factor(m4_1_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Major event since 2001: respondent had a stroke") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if any equal 1 then 1`
* `if all are equal 2 then 0`
* `8 into 997`
* `9 into 998`
* `NA into 999`

**R script:**

```{r harmo3}

MHAS_ds_w3 <- tibble(id=MHAS_w3_life_thr$id)

MHAS_w3_life_thr$sa22_12 <- car::recode(as.vector(MHAS_w3_life_thr$sa22_12), "NA='-999'")
MHAS_w3_life_thr$m4_1_12 <- car::recode(as.vector(MHAS_w3_life_thr$m4_1_12), "NA='-999'")
MHAS_w3_life_thr$m5_1_12 <- car::recode(as.vector(MHAS_w3_life_thr$m5_1_12), "NA='-999'")
MHAS_w3_life_thr$m6_1_12 <- car::recode(as.vector(MHAS_w3_life_thr$m6_1_12), "NA='-999'")
MHAS_w3_life_thr$m8_1_12 <- car::recode(as.vector(MHAS_w3_life_thr$m8_1_12), "NA='-999'")
MHAS_w3_life_thr$m10_1_12 <- car::recode(as.vector(MHAS_w3_life_thr$m10_1_12), "NA='-999'")

MHAS_ds_w3$lifethreat_sit <- c(NA)
for(i in 1:dim(MHAS_w3_life_thr)[1]){
  if( MHAS_w3_life_thr$sa22_12[i] == 1 | MHAS_w3_life_thr$m4_1_12[i] == 1 | MHAS_w3_life_thr$m5_1_12[i] == 1 |
      MHAS_w3_life_thr$m6_1_12[i] == 1 | MHAS_w3_life_thr$m8_1_12[i] == 1 | MHAS_w3_life_thr$m10_1_12[i] == 1 ) {
    MHAS_ds_w3$lifethreat_sit[i] = 1 }
  else if( MHAS_w3_life_thr$sa22_12[i] == -999 & MHAS_w3_life_thr$m4_1_12[i] == -999 & MHAS_w3_life_thr$m5_1_12[i] == -999 &
      MHAS_w3_life_thr$m6_1_12[i] == -999 & MHAS_w3_life_thr$m8_1_12[i] == -999 & MHAS_w3_life_thr$m10_1_12[i] == -999 ) {
    MHAS_ds_w3$lifethreat_sit[i] = 999 }
  else if( MHAS_w3_life_thr$sa22_12[i] %in% c(2, -999) & MHAS_w3_life_thr$m4_1_12[i] %in% c(2, -999) & MHAS_w3_life_thr$m5_1_12[i] %in% c(2, -999) &
      MHAS_w3_life_thr$m6_1_12[i] %in% c(2, -999) & MHAS_w3_life_thr$m8_1_12[i] %in% c(2, -999) & MHAS_w3_life_thr$m10_1_12[i] %in% c(2, -999) ) {
    MHAS_ds_w3$lifethreat_sit[i] = 0 }
  else if(  MHAS_w3_life_thr$sa22_12[i] == 8 | MHAS_w3_life_thr$m4_1_12[i] == 8 | MHAS_w3_life_thr$m5_1_12[i] == 8 |
      MHAS_w3_life_thr$m6_1_12[i] == 8 | MHAS_w3_life_thr$m8_1_12[i] == 8 | MHAS_w3_life_thr$m10_1_12[i] == 8 ) { 
    MHAS_ds_w3$lifethreat_sit[i] = 997 }
  else if( MHAS_w3_life_thr$sa22_12[i] == 9 | MHAS_w3_life_thr$m4_1_12[i] == 9 | MHAS_w3_life_thr$m5_1_12[i] == 9 |
      MHAS_w3_life_thr$m6_1_12[i] == 9 | MHAS_w3_life_thr$m8_1_12[i] == 9 | MHAS_w3_life_thr$m10_1_12[i] == 9 ) { 
    MHAS_ds_w3$lifethreat_sit[i] = 998 }
}

MHAS_ds_w3$lifethreat_sit <- car::recode(as.vector(MHAS_ds_w3$lifethreat_sit), "NA='999'")

```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}

vbl <- MHAS_ds_w3$lifethreat_sit
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w3, aes(x=factor(lifethreat_sit))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

##### Validation
```{r crosstabulation3, echo=F}

```



```{r final, echo=F}

l.hds <- list(w3 = MHAS_ds_w3)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("MHAS_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

```

## Summary of descriptive statistics of the harmonised variable accross populations and waves


Percentages of categories in each harmonised variable.



```{r summ}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",names(l.hds))
kable(t.hds)

```


# Quality estimation
[Comments on the quality of the new harmonised variable.]


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  lifethreat_sit <- l.hds[[index]]
  save(lifethreat_sit, file = paste0(datafolder,names(l.hds)[index],"/lifethreat_sit.RData"))
}

```
<!-- ########################################################## --> 

<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
