---
title: "Natural disaster"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 


<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/nat_disDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/nat_disDS.R')
```


<!-- ########################################################## --> 

# Data process

## Mexico

### Wave 1

Not found.

### Wave 2

Not found.

### Wave 3

#### Study-specific variable description

The study-specific variable elected to be harmonised is:
    
* Name: `m9_1_12`
* Label: `Major event since 2001: Disaster damaged respondent's home`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings: 
    + `8 = Refused`
    + `9 = DK`
    
* Name: `sa21_12`
* Label: `Major event since 2001: Disaster affected deceased's house`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings: 
    + `8 = RF`
    + `9 = DK`
  
* Description: 
```{r assign3, echo=F}
opal.assign.table.tibble(o, 'MHAS_w3_nat_dis','Mexican Health Aging Study.MHAS_2012_new',variables=list('m9_1_12','sa21_12'), missings = TRUE)
```

```{r local3, echo=F}
MHAS_w3_nat_dis <- opal.execute(o,'MHAS_w3_nat_dis')
vari <- MHAS_w3_nat_dis$m9_1_12
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w3_nat_dis$m9_1_12, missing_values = NA)
ggplot(MHAS_w3_nat_dis, aes(x=factor(m9_1_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Major event since 2001: Disaster damaged respondent's home") + ylab("Frequency")

vari <- MHAS_w3_nat_dis$sa21_12
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w3_nat_dis$sa21_12, missing_values = NA)
ggplot(MHAS_w3_nat_dis, aes(x=factor(sa21_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Major event since 2001: Disaster affected deceased's house") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if any equal 1 then 1`
* `if all are equal 2 then 0`
* `8 into 997`
* `9 into 998`
* `NA into 999`

**R script:**

```{r harmo3, echo=TRUE}
MHAS_ds_w3 <- tibble(id=MHAS_w3_nat_dis$id)

MHAS_w3_nat_dis$sa21_12 <- car::recode(as.vector(MHAS_w3_nat_dis$sa21_12), "NA='-999'")
MHAS_w3_nat_dis$m9_1_12 <- car::recode(as.vector(MHAS_w3_nat_dis$m9_1_12), "NA='-999'")

MHAS_ds_w3$nat_dis <- c(NA)
for(i in 1:dim(MHAS_w3_nat_dis)[1]){
  if( MHAS_w3_nat_dis$sa21_12[i] == 1 | MHAS_w3_nat_dis$m9_1_12[i] == 1 ) {
    MHAS_ds_w3$nat_dis[i] = 1 }
  else if( MHAS_w3_nat_dis$sa21_12[i] == -999 & MHAS_w3_nat_dis$m9_1_12[i] == -999 ) {
    MHAS_ds_w3$nat_dis[i] = 999 }
  else if( MHAS_w3_nat_dis$sa21_12[i] == 2 | MHAS_w3_nat_dis$m9_1_12[i] == 2 ) {
    MHAS_ds_w3$nat_dis[i] = 0 }
  else if( MHAS_w3_nat_dis$sa21_12[i] == 8 | MHAS_w3_nat_dis$m9_1_12[i] == 8 ) { 
    MHAS_ds_w3$nat_dis[i] = 997 }
  else if( MHAS_w3_nat_dis$sa21_12[i] == 9 | MHAS_w3_nat_dis$m9_1_12[i] == 9 ) { 
    MHAS_ds_w3$nat_dis[i] = 998 }
}

MHAS_ds_w3$nat_dis <- car::recode(as.vector(MHAS_ds_w3$nat_dis), "NA='999'")
MHAS_ds_w3$nat_dis <- labelled(MHAS_ds_w3$nat_dis, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=F}
vari <- MHAS_ds_w3$nat_dis 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_ds_w3$nat_dis, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w3, aes(x=factor(nat_dis))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Ever experienced any natural disaster") + ylab("Frequency")
```

##### Validation
```{r crosstabulation3, echo=F}
AfterH <- table(MHAS_ds_w3$nat_dis)
BeforeH <- table(MHAS_w3_nat_dis$sa21_12,MHAS_w3_nat_dis$m9_1_12, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- sum(sum(BeforeH[2,]), sum(BeforeH[c(1,3,4),2]))
BeforeH1[[1]] <- sum(sum(BeforeH[3,]), sum(BeforeH[c(1,2,4),3]))
BeforeH1[[3]] <- sum(BeforeH[4,1],BeforeH[1,4])
BeforeH1[[4]] <- BeforeH[1,1]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","9->998","NA->999")
kable(C)
```


```{r save, echo=FALSE}
nat_dis <- MHAS_ds_w3
save(nat_dis, file = "../RData/w3/nat_dis.RData")
rm(nat_dis)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```

