---
title: "Loneliness"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/lonelinessDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/lonelinessDS.R')
```

# Data process


## Mexico

### Wave 1 

#### Study-specific variable description



| **Name** | `c52e`|
|-|-|
| **Label** | `Loneliness (You felt lonely [In the majority of the time in the last week])`|
| **Table name** |`MHAS-2001`|
| **Categories** |`1 = Yes`<br/>`2 = No`|
| **Missings** |`8 = RF`<br/>`9 = DK`|
| **Description** |  |


```{r assign1, echo=F}

opal.assign.table.tibble(o, 'MHAS_w1','Mexican Health Aging Study.MHAS-2001',variables=list('c52e'), missings = TRUE)
MHAS_w1 <- opal.execute(o,'MHAS_w1')

```

```{r local1, echo=F}

vbl <- MHAS_w1$c52e
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = "c52e")
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(MHAS_w1, aes(x=factor(c52e))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0`
* `8 into 997; 9 into 998`
* `NA into 999`

**R script:**

```{r harmo1}
MHAS_ds_w1 <- tibble(id=MHAS_w1$id)
MHAS_ds_w1$loneliness <- car::recode(as.vector(MHAS_w1$c52e), "1='1'; 2='0'; 8='997'; 9='998'; NA='999'")

```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}

vbl <- MHAS_ds_w1$loneliness
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w1, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(MHAS_ds_w1$loneliness)
BeforeH <- table(MHAS_w1$c52e, useNA='ifany')[c(2,1,3,4,5)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","8->997","9->998","NA->999")
kable(C)
```





### Wave 2

#### Study-specific variable description



| **Name** | `c49_5`|
|-|-|
| **Label** | `Last week's majority emotions - alone`|
| **Table name** |`MHAS_2003`|
| **Categories** |`1 = Yes`<br/>`2 = No`|
| **Missings** |`8 = RF`<br/>`9 = DK`|
| **Description** |  |


```{r assign2, echo=F}

opal.assign.table.tibble(o, 'MHAS_w2','Mexican Health Aging Study.MHAS_2003',variables=list('c49_5'), missings = TRUE)
MHAS_w2 <- opal.execute(o,'MHAS_w2')

```

```{r local2, echo=F}

vbl <- MHAS_w2$c49_5
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = "c49_5")
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(MHAS_w2, aes(x=factor(c49_5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0`
* `8 into 997; 9 into 998`
* `NA into 999`

**R script:**

```{r harmo2}

MHAS_ds_w2 <- tibble(id=MHAS_w2$id)
MHAS_ds_w2$loneliness <- car::recode(as.vector(MHAS_w2$c49_5), "1='1'; 2='0'; 8='997'; 9='998'; NA='999'")

```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}

vbl <- MHAS_ds_w2$loneliness
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w2, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation2, echo=F}
AfterH <- table(MHAS_ds_w2$loneliness)
BeforeH <- table(MHAS_w2$c49_5, useNA='ifany')[c(2,1,3,4,5)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","8->997","9->998","NA->999")
kable(C)
```






### Wave 3

#### Study-specific variable description



| **Name** | `c49_5_12`|
|-|-|
| **Label** | `Last week's majority emotions - alone`|
| **Table name** |`MHAS_2012_new`|
| **Categories** |`1 = Yes`<br/>`2 = No`|
| **Missings** |`8 = RF`<br/>`9 = DK`|
| **Description** |  |



```{r assign3, echo=F}

opal.assign.table.tibble(o, 'MHAS_w3','Mexican Health Aging Study.MHAS_2012_new',variables=list('c49_5_12'), missings = TRUE)
MHAS_w3 <- opal.execute(o,'MHAS_w3')

```

```{r local3, echo=F}

vbl <- MHAS_w3$c49_5_12
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = "c49_5_12")
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(MHAS_w3, aes(x=factor(c49_5_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `2 into 0`
* `8 into 997; 9 into 998`
* `NA into 999`

**R script:**

```{r harmo3}
MHAS_ds_w3 <- tibble(id=MHAS_w3$id)
MHAS_ds_w3$loneliness <- car::recode(as.vector(MHAS_w3$c49_5_12), "1='1'; 2='0'; 8='997'; 9='998'; NA='999'")

```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}

vbl <- MHAS_ds_w3$loneliness
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w3, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=F}
AfterH <- table(MHAS_ds_w3$loneliness)
BeforeH <- table(MHAS_w3$c49_5_12, useNA='ifany')[c(2,1,3,4,5)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","8->997","9->998","NA->999")
kable(C)
```










## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.


```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


mhas.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"))

# Consider only harmonised waves
l.hds <- lapply(mhas.cw, function(wname) if(exists(paste0("MHAS_ds_",wname[1]))){wname = list(get(paste0("MHAS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```



# Quality estimation



<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
