---
title: "Has children and/or grandchildren"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 


<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/childrenDS.Rmd'}
```


```{r global, echo=F}
source('../../_DS_Rmd/childrenDS.R')
```




<!-- ########################################################## --> 

# Data process

## Mexico

### Wave 1 

#### Study-specific variable description

| **Name** |`a20`|
|-|-|
| **Label** | `Number of children still alive`|
| **Table name** |`MHAS-2001`|
| **Categories** |`continuous`<br/>`0 = None`<br/>`30 = 30 children and more`<br/>`96 = All`|
| **Missings** |`88 = Doesn't answer`<br/>`99 = Doesn't know`|
| **Description** |  |


| **Name** |`trh15`|`trh1`|`unhhid`|
|-|-|-|-|
| **Label** |`Number of children of household member`|`Respondent's Code`|`Unique household ID`|
| **Table name** |`sect_trh`|`sect_trh`|`sect_trh`|
| **Categries** |`continuous`|`1 = Selected person`<br/>`2 = Selected person’s spouse`|`text`|
| **Missings** |`88 = Doesn't answer`<br/>`99 = Doesn't know`|  |  |
| **Description** |  |  |  |


| **Name** |`b16`|`b1`|`unhhid`|
|-|-|-|-|
| **Label** |`Number of children of nonresident child`|`Code of respondent who answered questions`|`Unique household ID`|
| **Table name** |`b_nores`|`b_nores`|`b_nores`|
| **Categries** |`continuous till 30`<br/>`30 = 30 children or more`|`1 = Selected person`<br/>`2 = Selected person’s spouse`|`text`|
| **Missings** |`88 = Doesn't answer`<br/>`99 = Doesn't know`|  |  |
| **Description** |  |  |  |


```{r assign1, echo=F}

opal.assign.table.tibble(o, 'MHAS_w1_child','Mexican Health Aging Study.MHAS-2001',variables=list('a20'), missings = TRUE)
MHAS_w1_child <- opal.execute(o,'MHAS_w1_child')

opal.assign.table.tibble(o, 'MHAS_w1_trh','Mexican Health Aging Study.sect_trh',variables=list('trh15','trh1','unhhid'), missings = TRUE)
MHAS_w1_trh <- opal.execute(o,'MHAS_w1_trh')

opal.assign.table.tibble(o, 'MHAS_w1_bnr','Mexican Health Aging Study.b_nores',variables=list('b16','b1','unhhid'), missings = TRUE)
MHAS_w1_bnr <- opal.execute(o,'MHAS_w1_bnr')

```

```{r local1, echo=F}

vari <- MHAS_w1_child$a20
kable(Continuous_summary(var = vari, missing_values = c(88,99))[3], caption = 'a20')
kable(Continuous_summary(vari, missing_values = c(88,99))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(88,99))$summary, caption = "Summary")
ggplot(filter(MHAS_w1_child,!vari %in% c(88,99,96)), aes(a20)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of children still alive") + ylab("Frequency")

vbl <- MHAS_w1_trh$trh15
vbl_miss <- c(88,99)
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = "trh15")
kable(Continuous_summary(vbl, missing_values = vbl_miss)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(MHAS_w1_trh,!vbl %in% vbl_miss), aes(trh15)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w1_bnr$b16
vbl_miss <- c(88,99)
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = "b16")
kable(Continuous_summary(vbl, missing_values = vbl_miss)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(MHAS_w1_bnr,!vbl %in% vbl_miss), aes(b16)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute the harmonised variable `child` from the study-specific variable `a20` it has to be recoded as follows:

* `1:30 or 96 into 1`
* `0 into 0`
* `88 into 995`
* `99 into 998`
* `NA into 999`

To compute the harmonised variable `grchild` from the study-specific variables `b16`,`trh15` it has to be recoded as follows:

The interviewer manual specifies:

`This survey has the following registration lists:`
`a) Household residents, in the section Household Residents in the first interview.`
`b) Non-resident children, in section B of the first interview.`


* `1:30 into 1`
* `0 into 0`
* `88 into 995`
* `99 into 998`
* `NA into 999`


**R script:**

```{r harmo1, echo=TRUE}

# CHILD HARMONIZATION
MHAS_ds_w1 <- tibble(id=MHAS_w1_child$id)
MHAS_ds_w1$child <- car::recode(as.vector(MHAS_w1_child$a20), "1:30='1'; 96='1'; 0='0'; 88='995'; 99='998'; NA='999'")

# GRCHILD HARMONIZATION
# Build corresponding (respondent grandparent) IDs:

# JOIN (HH)ID TOGETHER WITH CODE NUMBER OF THE RESPONDENT
MHAS_w1_bnr$newid <- paste0(substr(MHAS_w1_bnr$unhhid,1,nchar(MHAS_w1_bnr$unhhid)),as.character(MHAS_w1_bnr$b1),"0.0")
MHAS_w1_trh$newid <- paste0(substr(MHAS_w1_trh$unhhid,1,nchar(MHAS_w1_trh$unhhid)),as.character(MHAS_w1_trh$trh1),"0.0")


MHAS_ds_w1$grchild <- rep(999,length(MHAS_ds_w1$id))
MHAS_ds_w1$grchild[which(sapply(MHAS_ds_w1$id,function(x)   88 %in% union(MHAS_w1_trh$trh15[which(MHAS_w1_trh$newid==x)],MHAS_w1_bnr$b16[which(MHAS_w1_bnr$newid==x)])  ))] <- 995
MHAS_ds_w1$grchild[which(sapply(MHAS_ds_w1$id,function(x)   99 %in% union(MHAS_w1_trh$trh15[which(MHAS_w1_trh$newid==x)],MHAS_w1_bnr$b16[which(MHAS_w1_bnr$newid==x)])  ))] <- 998
MHAS_ds_w1$grchild[which(sapply(MHAS_ds_w1$id,function(x)  sum(MHAS_w1_bnr$b16[which(MHAS_w1_bnr$newid==x)]!=0)==0 & sum(MHAS_w1_trh$trh15[which(MHAS_w1_trh$newid==x)]!=0)==0 ))] <- 0
MHAS_ds_w1$grchild[which(sapply(MHAS_ds_w1$id,function(x) length(intersect(1:30,union(MHAS_w1_bnr$b16[which(MHAS_w1_bnr$newid==x)],MHAS_w1_trh$trh15[which(MHAS_w1_trh$newid==x)])))>=1))] <- 1



```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}

vbl <- MHAS_ds_w1$child
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w1, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- MHAS_ds_w1$grchild
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_gr) 
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w1, aes(x=factor(grchild))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_gr) + ylab("Frequency")

```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(MHAS_ds_w1$child)
BeforeH <- table(MHAS_w1_child$a20, useNA='ifany')
BeforeH[[2]] <- sum(BeforeH[c(2:(length(BeforeH)-4),length(BeforeH)-2)])
BeforeH <- BeforeH[c(1,2,length(BeforeH)-3,length(BeforeH)-1,length(BeforeH))]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","88->995","99->998","NA->999")
kable(C)
```

 
 


### Wave 2

#### Study-specific variable description


| **Name** |`aa19`|`aa20`|`d4`|
|-|-|-|-|
| **Label** |`How many children born alive do you have`|`Of those, how many still alive`|`Person has living children`|
| **Table name** |`MHAS_2003`|`MHAS_2003`|`MHAS_2003`|
| **Categories** |`continuous`|`continuous`<br/>`0 = None`<br/>`96 = All`|`1 = Yes`<br/>`2 = No`|
| **Missings** |`99 = Doesn't know`|`88 = Doesn't answer`<br/>`99 = Doesn't know`|`NA`|
| **Description** |  |  |  |



| **Name** |`trh17`|`trh1`|`cunicah`|
|-|-|-|-|
| **Label** |`Number of children - resident children`|`Code of respondent`|`Unique Household ID - 2001`|
| **Table name** |`sect_trh_2003`|`sect_trh_2003`|`sect_trh_2003`|
| **Categries** |`continuous`|`1 = Sampled person`<br/>`2 = Spouse of the sampled person in 2001`<br/>`3 = New spouse of the sampled person`<br/>`4 = New spouse of the selected person’s spouse`<br/> `103-121 = Other resident`<br/>`201-219;666 = Other, non-resident`|`text`|
| **Missings** |`88 = Doesn't answer`<br/>`99 = Doesn't know`|  |  |
| **Description** |  |  |  |


| **Name** |`b15`|`b1`|`cunicah`|
|-|-|-|-|
| **Label** |`Number of children of nonresident child`|`Code of respondent`|`Unique household ID`|
| **Table name** |`b_nores_2003`|`b_nores_2003`|`b_nores_2003`|
| **Categries** |`continuous till 30`<br/>`30 = 30 children or more`|`001 = Sampled person`<br/>`002 = Spouse of the sampled person in 2001`<br/>`003 = New spouse of the sampled person`<br/>`004 = New spouse of the selected person’s spouse`<br/> `103-121 = Other resident`<br/>`201-219;666 = Other, non-resident`|`text`|
| **Missings** |`88 = Doesn't answer`<br/>`99 = Doesn't know`|  |  |
| **Description** |  |  |  |


```{r assign2, echo=F}

opal.assign.table.tibble(o, 'MHAS_w2_child','Mexican Health Aging Study.MHAS_2003',variables=list('aa19','aa20','d4'), missings = TRUE)
MHAS_w2_child <- opal.execute(o,'MHAS_w2_child')

opal.assign.table.tibble(o, 'MHAS_w2_trh','Mexican Health Aging Study.sect_trh_2003',variables=list('trh17','trh1','cunicah'), missings = TRUE)
MHAS_w2_trh <- opal.execute(o,'MHAS_w2_trh')
MHAS_w2_trh$cunicah <- as.character(MHAS_w2_trh$cunicah)

opal.assign.table.tibble(o, 'MHAS_w2_bnr','Mexican Health Aging Study.b_nores_2003',variables=list('b15','b1','cunicah'), missings = TRUE)
MHAS_w2_bnr <- opal.execute(o,'MHAS_w2_bnr')
MHAS_w2_bnr$cunicah <- as.character(MHAS_w2_bnr$cunicah)
MHAS_w2_bnr$b1 <- as.numeric(MHAS_w2_bnr$b1)

```

```{r local2, echo=F}

vbl <- MHAS_w2_child$aa19
vbl_miss <- c(88,99)
kable(Continuous_summary(vbl, missing_values = vbl_miss)[3], caption = "aa19") 
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(MHAS_w2_child,!vbl %in% vbl_miss), aes(aa19)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <-  MHAS_w2_child$aa20
kable(Continuous_summary(vari, missing_values = c(88,99))[3], caption = "aa20") 
kable(Continuous_summary(vari, missing_values = c(88,99))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(88,99))$summary, caption = "Summary")
#Continuous_summary(var = MHAS_w2_child$aa20, missing_values = NA)
ggplot(filter(MHAS_w2_child,!vari %in% c(88,99,96)), aes(aa20)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How many of children are still alive") + ylab("Frequency")+scale_x_continuous(breaks = c(2,4,6,8,10,12))

vbl <- MHAS_w2_child$d4
kable(Categorical_summary(vbl, missing_values = NA)[3], caption = "d4") 
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(MHAS_w2_child, aes(x=factor(d4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w2_trh$trh17
vbl_miss <- c(88,99)
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = "trh17")
kable(Continuous_summary(vbl, missing_values = vbl_miss)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(MHAS_w2_trh,!vbl %in% vbl_miss), aes(trh17)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w2_bnr$b15
vbl_miss <- c(88,99)
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = "b15")
kable(Continuous_summary(vbl, missing_values = vbl_miss)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(MHAS_w2_bnr,!vbl %in% vbl_miss), aes(b15)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To recode the harmonised variable `child` from the study-specific variable `aa20` it has to be recoded as follows:  

* `aa19 == 0 into 0`
* `1:30 or 96 into 1`
* `d4 == 1 into 1`
* `d4 == 2 into 0`
* `NA into 999`


To compute the harmonised variable `grchild` from the study-specific variables `b15`,`trh17` it has to be recoded as follows:

The interviewer manual specifies:

`This survey has the following registration lists:`
`a) Household residents, in the section Household Residents in the first interview.`
`b) Non-resident children, in section B of the first interview.`


* `1:30 into 1`
* `0 into 0`
* `88 into 995`
* `99 into 998`
* `NA into 999`


**R script:**

```{r harmo2, echo=TRUE}

# CHILD HARMONIZATION
MHAS_ds_w2 <- tibble(id=MHAS_w2_child$id)
MHAS_ds_w2$child <- car::recode(as.vector(MHAS_w2_child$aa20), "1:30='1'; 96='1'; 0='0'; NA='999'")
MHAS_ds_w2$child[which(MHAS_ds_w2$child == 999)] <- car::recode(MHAS_w2_child$d4[which(MHAS_ds_w2$child == 999)],"2=0; NA=999")
MHAS_ds_w2$child[which(MHAS_w2_child$aa19==0)] <- 0


# GRCHILD HARMONIZATION
# Build corresponding (respondent grandparent) IDs:

MHAS_w2_trh$tid <- car::recode(MHAS_w2_trh$trh1, "1=10;2=20;3=11;4=21;103:hi=NA")
# JOIN (HH)ID TOGETHER WITH CODE NUMBER OF THE RESPONDENT
MHAS_w2_trh$newid <- paste0(substr(MHAS_w2_trh$cunicah,1,nchar(MHAS_w2_trh$cunicah)),as.character(MHAS_w2_trh$tid),".0")
MHAS_w2_bnr$tid <- car::recode(MHAS_w2_bnr$b1, "1=10;2=20;3=11;4=21;103:hi=NA")
MHAS_w2_bnr$newid <- paste0(substr(MHAS_w2_bnr$cunicah,1,nchar(MHAS_w2_bnr$cunicah)),as.character(MHAS_w2_bnr$tid),".0")

MHAS_ds_w2$grchild <- rep(999,length(MHAS_ds_w2$id))

MHAS_ds_w2$grchild[which(sapply(MHAS_ds_w2$id,function(x)   88 %in% union(MHAS_w2_trh$trh17[which(MHAS_w2_trh$newid==x)],MHAS_w2_bnr$b15[which(MHAS_w2_bnr$newid==x)])  ))] <- 995
MHAS_ds_w2$grchild[which(sapply(MHAS_ds_w2$id,function(x)   99 %in% union(MHAS_w2_trh$trh17[which(MHAS_w2_trh$newid==x)],MHAS_w2_bnr$b15[which(MHAS_w2_bnr$newid==x)])  ))] <- 998
MHAS_ds_w2$grchild[which(sapply(MHAS_ds_w2$id,function(x)  sum(MHAS_w2_bnr$b15[which(MHAS_w2_bnr$newid==x)]!=0)==0 & sum(MHAS_w2_trh$trh17[which(MHAS_w2_trh$newid==x)]!=0)==0 ))] <- 0
MHAS_ds_w2$grchild[which(sapply(MHAS_ds_w2$id,function(x) length(intersect(1:30,union(MHAS_w2_bnr$b15[which(MHAS_w2_bnr$newid==x)],MHAS_w2_trh$trh17[which(MHAS_w2_trh$newid==x)])))>=1))] <- 1

```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}

vbl <- MHAS_ds_w2$child
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w2, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- MHAS_ds_w2$grchild
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_gr) 
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w2, aes(x=factor(grchild))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_gr) + ylab("Frequency")

```

#### Validation
```{r crosstabulation2, echo=F}

```

 
 


### Wave 3

#### Study-specific variable description


| **Name** |`a8_12`|`subhog_12`|`cunicah`|
|-|-|-|-|
| **Label** |`Number of children currently living`|`2012 sub-household identifier`|`Clave Unica del Hogar (=unhhid)`|
| **Table name** |`MHAS_2012_new`|`MHAS_2012_new`|`MHAS_2012_new`|
| **Categories** |`continuous`<br/>`0 = None`<br/>`96 = All`|`BASELINE HOUSEHOLD`<br/>`00 For all households that are new sample (in their baseline year)`<br/>`NO CHANGES IN THE HOUSEHOLD`<br/>`01 The household contains an individual NP = 010 (first selected subject that entered the sample)`<br/>`02 The household contains an individual NP=020 (subject in this household that entered to the sample first)`<br/>`CHANGES IN THE HOUSEHOLD`<br/>`11 The new household contains an individual NP=010 (subject in this new household that entered to the sample first)`<br/>`12 The new household contains an individual NP=020 (subject in this new household that entered to the sample first)`<br/>`13 The new household contains an individual NP=011 (subject in this new household that entered to the sample first)`<br/>`14 The new household contains an individual NP=021 (subject in this new household that entered to the sample first)`<br/>`RE-UNION`<br/>`70 Two individuals (NP=010 y NP=020) part of the study, they were together, separated, and got back together`<br/>`71 Two individuals, from the family of 10, they were together, separated, and got back together`|`text`|
| **Missings** |`88 = Doesn't answer`<br/>`99 = Doesn't know`|`31 The deceased is NP=010`<br/>`32 The deceased is NP=020`<br/>`33 The deceased is NP=011`<br/>`34 The deceased is NP=021`<br/>`77 To the individuals not contacted (whole household)`|  |
| **Description** |  |  |  |



| **Name** |`trh17_12`|`subhog_12`|`cunicah`|
|-|-|-|-|
| **Label** |`Resident CHILD age 12+: number of children`|`2012 sub-household identifier`|`Clave Unica del Hogar (=unhhid)`|
| **Table name** |`sect_trh_follow_up_2012`|`sect_trh_follow_up_2012`|`sect_trh_follow_up_2012`|
| **Categries** |`continuous`|`BASELINE HOUSEHOLD`<br/>`00 For all households that are new sample (in their baseline year)`<br/>`NO CHANGES IN THE HOUSEHOLD`<br/>`01 The household contains an individual NP = 010 (first selected subject that entered the sample)`<br/>`02 The household contains an individual NP=020 (subject in this household that entered to the sample first)`<br/>`CHANGES IN THE HOUSEHOLD`<br/>`11 The new household contains an individual NP=010 (subject in this new household that entered to the sample first)`<br/>`12 The new household contains an individual NP=020 (subject in this new household that entered to the sample first)`<br/>`13 The new household contains an individual NP=011 (subject in this new household that entered to the sample first)`<br/>`14 The new household contains an individual NP=021 (subject in this new household that entered to the sample first)`<br/>`RE-UNION`<br/>`70 Two individuals (NP=010 y NP=020) part of the study, they were together, separated, and got back together`<br/>`71 Two individuals, from the family of 10, they were together, separated, and got back together`|`text`|
| **Missings** |`88 = Doesn't answer`<br/>`99 = Doesn't know`|`31 The deceased is NP=010`<br/>`32 The deceased is NP=020`<br/>`33 The deceased is NP=011`<br/>`34 The deceased is NP=021`<br/>`77 To the individuals not contacted (whole household)`|  |
| **Description** |  |  |  |


| **Name** |`ntrh15_12`|`subhog_12`|`cunicah`|
|-|-|-|-|
| **Label** |`Number of children resident has`|`2012 sub-household identifier`|`Clave Unica del Hogar (=unhhid)`|
| **Table name** |`sect_trh_new_sample_2012`|`sect_trh_new_sample_2012`|`sect_trh_new_sample_2012`|
| **Categries** |`continuous`|`BASELINE HOUSEHOLD`<br/>`00 For all households that are new sample (in their baseline year)`<br/>`NO CHANGES IN THE HOUSEHOLD`<br/>`01 The household contains an individual NP = 010 (first selected subject that entered the sample)`<br/>`02 The household contains an individual NP=020 (subject in this household that entered to the sample first)`<br/>`CHANGES IN THE HOUSEHOLD`<br/>`11 The new household contains an individual NP=010 (subject in this new household that entered to the sample first)`<br/>`12 The new household contains an individual NP=020 (subject in this new household that entered to the sample first)`<br/>`13 The new household contains an individual NP=011 (subject in this new household that entered to the sample first)`<br/>`14 The new household contains an individual NP=021 (subject in this new household that entered to the sample first)`<br/>`RE-UNION`<br/>`70 Two individuals (NP=010 y NP=020) part of the study, they were together, separated, and got back together`<br/>`71 Two individuals, from the family of 10, they were together, separated, and got back together`|`text`|
| **Missings** |`88 = Doesn't answer`<br/>`99 = Doesn't know`|`31 The deceased is NP=010`<br/>`32 The deceased is NP=020`<br/>`33 The deceased is NP=011`<br/>`34 The deceased is NP=021`<br/>`77 To the individuals not contacted (whole household)`|  |
| **Description** |  |  |  |


| **Name** |`b15_12`|`subhog_12`|`cunicah`|
|-|-|-|-|
| **Label** |`How many children does non-resident child 12 years or older have`|`2012 sub-household identifier`|`Clave Unica del Hogar (=unhhid)`|
| **Table name** |`sect_b_non_resident_follow_up_2012`|`sect_b_non_resident_follow_up_2012`|`sect_b_non_resident_follow_up_2012`|
| **Categries** |`continuous`<br/>`96 = All`|`BASELINE HOUSEHOLD`<br/>`00 For all households that are new sample (in their baseline year)`<br/>`NO CHANGES IN THE HOUSEHOLD`<br/>`01 The household contains an individual NP = 010 (first selected subject that entered the sample)`<br/>`02 The household contains an individual NP=020 (subject in this household that entered to the sample first)`<br/>`CHANGES IN THE HOUSEHOLD`<br/>`11 The new household contains an individual NP=010 (subject in this new household that entered to the sample first)`<br/>`12 The new household contains an individual NP=020 (subject in this new household that entered to the sample first)`<br/>`13 The new household contains an individual NP=011 (subject in this new household that entered to the sample first)`<br/>`14 The new household contains an individual NP=021 (subject in this new household that entered to the sample first)`<br/>`RE-UNION`<br/>`70 Two individuals (NP=010 y NP=020) part of the study, they were together, separated, and got back together`<br/>`71 Two individuals, from the family of 10, they were together, separated, and got back together`|`text`|
| **Missings** |`88 = Doesn't answer`<br/>`99 = Doesn't know`|`31 The deceased is NP=010`<br/>`32 The deceased is NP=020`<br/>`33 The deceased is NP=011`<br/>`34 The deceased is NP=021`<br/>`77 To the individuals not contacted (whole household)`|  |
| **Description** |  |  |  |


| **Name** |`nb16_12`|`subhog_12`|`cunicah`|
|-|-|-|-|
| **Label** |`How many children does non-resident child have`|`2012 sub-household identifier`|`Clave Unica del Hogar (=unhhid)`|
| **Table name** |`sect_b_non_resident_new_sample_2012`|`sect_b_non_resident_new_sample_2012`|`sect_b_non_resident_new_sample_2012`|
| **Categries** |`continuous`<br/>`96 = All`|`BASELINE HOUSEHOLD`<br/>`00 For all households that are new sample (in their baseline year)`<br/>`NO CHANGES IN THE HOUSEHOLD`<br/>`01 The household contains an individual NP = 010 (first selected subject that entered the sample)`<br/>`02 The household contains an individual NP=020 (subject in this household that entered to the sample first)`<br/>`CHANGES IN THE HOUSEHOLD`<br/>`11 The new household contains an individual NP=010 (subject in this new household that entered to the sample first)`<br/>`12 The new household contains an individual NP=020 (subject in this new household that entered to the sample first)`<br/>`13 The new household contains an individual NP=011 (subject in this new household that entered to the sample first)`<br/>`14 The new household contains an individual NP=021 (subject in this new household that entered to the sample first)`<br/>`RE-UNION`<br/>`70 Two individuals (NP=010 y NP=020) part of the study, they were together, separated, and got back together`<br/>`71 Two individuals, from the family of 10, they were together, separated, and got back together`|`text`|
| **Missings** |`88 = Doesn't answer`<br/>`99 = Doesn't know`|`31 The deceased is NP=010`<br/>`32 The deceased is NP=020`<br/>`33 The deceased is NP=011`<br/>`34 The deceased is NP=021`<br/>`77 To the individuals not contacted (whole household)`|  |
| **Description** |  |  |  |




```{r assign3, echo=F}

opal.assign.table.tibble(o, 'MHAS_w3_child','Mexican Health Aging Study.MHAS_2012_new',variables=list('a8_12','subhog_12','cunicah'), missings = TRUE)
MHAS_w3_child <- opal.execute(o,'MHAS_w3_child')
MHAS_w3_child$cunicah <- as.character(MHAS_w3_child$cunicah)


opal.assign.table.tibble(o, 'MHAS_w3_futrh','Mexican Health Aging Study.sect_trh_follow_up_2012', variables=list('trh17_12','subhog_12','cunicah'), missings = TRUE)
MHAS_w3_futrh <- opal.execute(o,'MHAS_w3_futrh')
MHAS_w3_futrh$cunicah <- as.character(MHAS_w3_futrh$cunicah)

opal.assign.table.tibble(o, 'MHAS_w3_nstrh','Mexican Health Aging Study.sect_trh_new_sample_2012',variables=list('ntrh15_12','subhog_12','cunicah'), missings = TRUE)
MHAS_w3_nstrh <- opal.execute(o,'MHAS_w3_nstrh')
MHAS_w3_nstrh$cunicah <- as.character(MHAS_w3_nstrh$cunicah)

opal.assign.table.tibble(o, 'MHAS_w3_fub','Mexican Health Aging Study.sect_b_non_resident_follow_up_2012', variables=list('b15_12','subhog_12','cunicah'), missings = TRUE)
MHAS_w3_fub <- opal.execute(o,'MHAS_w3_fub')
MHAS_w3_fub$cunicah <- as.character(MHAS_w3_fub$cunicah)

opal.assign.table.tibble(o, 'MHAS_w3_nsb','Mexican Health Aging Study.sect_b_non_resident_new_sample_2012',variables=list('nb16_12','subhog_12','cunicah'), missings = TRUE)
MHAS_w3_nsb <- opal.execute(o,'MHAS_w3_nsb')
MHAS_w3_nsb$cunicah <- as.character(MHAS_w3_nsb$cunicah)

```

```{r local3, echo=F}

vari <- MHAS_w3_child$a8_12
kable(Continuous_summary(var = vari, missing_values = c(88,99))[3])
kable(Continuous_summary(vari, missing_values = c(88,99))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(88,99))$summary, caption = "Summary")
#Continuous_summary(var = MHAS_w3_child$a8_12, missing_values = NA)
ggplot(filter(MHAS_w3_child,!vari %in% c(88,99,96)), aes(a8_12)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of children currently living") + ylab("Frequency")

vbl <- MHAS_w3_futrh$trh17_12
vbl_miss <- c(88,99)
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = "trh17_12")
kable(Continuous_summary(vbl, missing_values = vbl_miss)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(MHAS_w3_futrh,!vbl %in% vbl_miss), aes(trh17_12)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w3_nstrh$ntrh15_12
vbl_miss <- c(88,99)
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = "ntrh15_12")
kable(Continuous_summary(vbl, missing_values = vbl_miss)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(MHAS_w3_nstrh,!vbl %in% vbl_miss), aes(ntrh15_12)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w3_fub$b15_12
vbl_miss <- c(88,99)
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = "b15_12")
kable(Continuous_summary(vbl, missing_values = vbl_miss)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(MHAS_w3_fub,!vbl %in% vbl_miss), aes(b15_12)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w3_nsb$nb16_12
vbl_miss <- c(88,99)
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = "nb16_12")
kable(Continuous_summary(vbl, missing_values = vbl_miss)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(MHAS_w3_nsb,!vbl %in% vbl_miss), aes(nb16_12)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To recode the harmonised variable `child` from the study-specific variable `a8_12` it has to be recoded as follows:  

* `1:30 or 96 into 1`
* `0 into 0`
* `88 RF into 997`
* `99 DK into 998`
* `NA into 999`


To compute the harmonised variable `grchild` from the study-specific variables `b15_12`,`trh17`,`nb16_12`,`ntrh15_12` it has to be recoded as follows:



* `1:30 into 1`
* `0 into 0`
* `88 into 995`
* `99 into 998`
* `NA into 999`

**R script:**

```{r harmo3, echo=TRUE}

# CHILD HARMONIZATION
MHAS_ds_w3 <- tibble(id=MHAS_w3_child$id)
MHAS_ds_w3$child <- car::recode(as.vector(MHAS_w3_child$a8_12), "1:30='1'; 96='1'; 0='0'; 88='997'; 99='998'; NA='999'")

# GRCHILD HARMONIZATION
# Build corresponding (household grandparent) IDs:

MHAS_ds_w3$grchild <- rep(999,length(MHAS_ds_w3$id))

MHAS_ds_w3$grchild[which(sapply(1:length(MHAS_ds_w3$id),function(x) 99 %in% Reduce(union,list(
  MHAS_w3_nsb$nb16_12[which(MHAS_w3_nsb$cunicah==MHAS_w3_child$cunicah[x] & MHAS_w3_nsb$subhog_12==MHAS_w3_child$subhog_12[x])],
  MHAS_w3_fub$b15_12[which(MHAS_w3_fub$cunicah==MHAS_w3_child$cunicah[x] & MHAS_w3_fub$subhog_12==MHAS_w3_child$subhog_12[x])],
  MHAS_w3_nstrh$ntrh15_12[which(MHAS_w3_nstrh$cunicah==MHAS_w3_child$cunicah[x] & MHAS_w3_nstrh$subhog_12==MHAS_w3_child$subhog_12[x])],
  MHAS_w3_futrh$trh17_12[which(MHAS_w3_futrh$cunicah==MHAS_w3_child$cunicah[x] & MHAS_w3_futrh$subhog_12==MHAS_w3_child$subhog_12[x])]
  ))))] <- 998

MHAS_ds_w3$grchild[which(sapply(1:length(MHAS_ds_w3$id),function(x) 88 %in% Reduce(union,list(
  MHAS_w3_nsb$nb16_12[which(MHAS_w3_nsb$cunicah==MHAS_w3_child$cunicah[x] & MHAS_w3_nsb$subhog_12==MHAS_w3_child$subhog_12[x])],
  MHAS_w3_fub$b15_12[which(MHAS_w3_fub$cunicah==MHAS_w3_child$cunicah[x] & MHAS_w3_fub$subhog_12==MHAS_w3_child$subhog_12[x])],
  MHAS_w3_nstrh$ntrh15_12[which(MHAS_w3_nstrh$cunicah==MHAS_w3_child$cunicah[x] & MHAS_w3_nstrh$subhog_12==MHAS_w3_child$subhog_12[x])],
  MHAS_w3_futrh$trh17_12[which(MHAS_w3_futrh$cunicah==MHAS_w3_child$cunicah[x] & MHAS_w3_futrh$subhog_12==MHAS_w3_child$subhog_12[x])]
  ))))] <- 995

MHAS_ds_w3$grchild[which(sapply(1:length(MHAS_ds_w3$id),function(x) 
  sum(MHAS_w3_nsb$nb16_12[which(MHAS_w3_nsb$cunicah==MHAS_w3_child$cunicah[x] & MHAS_w3_nsb$subhog_12==MHAS_w3_child$subhog_12[x])]!=0)==0 &
  sum(MHAS_w3_fub$b15_12[which(MHAS_w3_fub$cunicah==MHAS_w3_child$cunicah[x] & MHAS_w3_fub$subhog_12==MHAS_w3_child$subhog_12[x])]!=0)==0 &
  sum(MHAS_w3_nstrh$ntrh15_12[which(MHAS_w3_nstrh$cunicah==MHAS_w3_child$cunicah[x] & MHAS_w3_nstrh$subhog_12==MHAS_w3_child$subhog_12[x])]!=0)==0 &
  sum(MHAS_w3_futrh$trh17_12[which(MHAS_w3_futrh$cunicah==MHAS_w3_child$cunicah[x] & MHAS_w3_futrh$subhog_12==MHAS_w3_child$subhog_12[x])]!=0)==0
  ))] <- 0


MHAS_ds_w3$grchild[which(sapply(1:length(MHAS_ds_w3$id),function(x)  length(intersect(c(1:30,96),Reduce(union,list(
  MHAS_w3_nsb$nb16_12[which(MHAS_w3_nsb$cunicah==MHAS_w3_child$cunicah[x] & MHAS_w3_nsb$subhog_12==MHAS_w3_child$subhog_12[x])],
  MHAS_w3_fub$b15_12[which(MHAS_w3_fub$cunicah==MHAS_w3_child$cunicah[x] & MHAS_w3_fub$subhog_12==MHAS_w3_child$subhog_12[x])],
  MHAS_w3_nstrh$ntrh15_12[which(MHAS_w3_nstrh$cunicah==MHAS_w3_child$cunicah[x] & MHAS_w3_nstrh$subhog_12==MHAS_w3_child$subhog_12[x])],
  MHAS_w3_futrh$trh17_12[which(MHAS_w3_futrh$cunicah==MHAS_w3_child$cunicah[x] & MHAS_w3_futrh$subhog_12==MHAS_w3_child$subhog_12[x])]
))))>=1))] <- 1






```

#### Statistical description of the new harmonised variable
```{r descript3, echo=F}

vbl <- MHAS_ds_w3$child
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w3, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab(ds_label) + ylab("Frequency")

vbl <- MHAS_ds_w3$grchild
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_gr) 
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w3, aes(x=factor(grchild))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab(ds_label_gr) + ylab("Frequency")

```

##### Validation
```{r crosstabulation3, echo=F}
AfterH <- table(MHAS_ds_w3$child)
BeforeH <- table(MHAS_w3_child$a8_12, useNA='ifany')
BeforeH[[2]] <- sum(BeforeH[c(2:(length(BeforeH)-4),length(BeforeH)-2)])
BeforeH <- BeforeH[c(1,2,length(BeforeH)-3,length(BeforeH)-1,length(BeforeH))]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","88->995","99->998","NA->999")
kable(C)
```

 

```{r final, echo=F}

l.hds <- list(w1 = MHAS_ds_w1, w2 = MHAS_ds_w2, w3 = MHAS_ds_w3)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  label(l.hds[[name]][[3]]) <- label(aux_object[[3]]) <- ds_label_gr # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  l.hds[[name]][[3]] <- labelled(l.hds[[name]][[3]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  aux_object[[3]] <- car::recode(aux_object[[3]], "miss_values_vector=NA")
  aux_object[[3]] <- labelled(aux_object[[3]], labels = cat_label[1:2])
  m_name <- paste0("MHAS_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

```



## Summary of descriptive statistics of the harmonised variable `child` accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.


```{r summ}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",names(l.hds))
kable(t.hds)

dbb <- get(paste0("MHAS_m_ds_",names(l.hds)[1]))[,c("id","child")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("MHAS_m_ds_",names(l.hds)[ind]))[,c("id","child")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", names(l.hds))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb)

```


## Summary of descriptive statistics of the harmonised variable `grchild` accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.


```{r summ gr}

t.hds <- frq(l.hds[[1]][3])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][3])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",names(l.hds))
kable(t.hds)

dbb <- get(paste0("MHAS_m_ds_",names(l.hds)[1]))[,c("id","grchild")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("MHAS_m_ds_",names(l.hds)[ind]))[,c("id","grchild")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", names(l.hds))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb)

```


 
```{r save, echo=FALSE}

child <- MHAS_ds_w1[,c("id","child")]
save(child, file = "../RData/w1/child.RData")
rm(child)

child <- MHAS_ds_w2[,c("id","child")]
save(child, file = "../RData/w2/child.RData")
rm(child)

child <- MHAS_ds_w3[,c("id","child")]
save(child, file = "../RData/w3/child.RData")
rm(child)

grchild <- MHAS_ds_w1[,c("id","grchild")]
save(grchild, file = "../RData/w1/grchild.RData")
rm(grchild)

grchild <- MHAS_ds_w2[,c("id","grchild")]
save(grchild, file = "../RData/w2/grchild.RData")
rm(grchild)

grchild <- MHAS_ds_w3[,c("id","grchild")]
save(grchild, file = "../RData/w3/grchild.RData")
rm(grchild)

```

# Quality estimation

In wave 2 we use the variable `d4` since `aa19` and `aa20` have a lot of missings; there are also the variables `trh3` and `b3` (used in g2aging to count number of children). Another option would be to assume that if there are grandchildren, there are also living children, since the data on the grandchildren is got from variables asked to the children (could it be answered not by the children, but by proxies?).


```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
