---
title: "Has children and/or grandchildren"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 


<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/childrenDS.Rmd'}
```


```{r global, echo=F}
source('../../_DS_Rmd/childrenDS.R')
```




<!-- ########################################################## --> 

# Data process

## Mexico

### Wave 1 

#### Study-specific variable description

| **Name** |`a20`|
|-|-|
| **Label** | `Number of children still alive`|
| **Table name** |`MHAS-2001`|
| **Categories** |`continuous`<br/>`0 = None`<br/>`30 = 30 children and more`<br/>`96 = All`|
| **Missings** |`88 = Doesn't answer`<br/>`99 = Doesn't know`|
| **Description** |  |


```{r assign1, echo=F}
opal.assign.table.tibble(o, 'MHAS_w1_child','Mexican Health Aging Study.MHAS-2001',variables=list('a20'), missings = TRUE)
```

```{r local1, echo=F}
MHAS_w1_child <- opal.execute(o,'MHAS_w1_child')
vari <- MHAS_w1_child$a20
kable(Continuous_summary(var = vari, missing_values = c(88,99))[3])
kable(Continuous_summary(vari, missing_values = c(88,99))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(88,99))$summary, caption = "Summary")
#Continuous_summary(var = MHAS_w1_child$a20, missing_values = NA)
ggplot(filter(MHAS_w1_child,!vari %in% c(88,99,96)), aes(a20)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of children still alive") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1:30 or 96 into 1`
* `0 into 0`
* `88 into 995`
* `99 into 998`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
MHAS_ds_w1 <- tibble(id=MHAS_w1_child$id)
MHAS_ds_w1$child <- car::recode(as.vector(MHAS_w1_child$a20), "1:30='1'; 96='1'; 0='0'; 88='995'; 99='998'; NA='999'")
MHAS_ds_w1$child <- labelled(MHAS_ds_w1$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <- MHAS_ds_w1$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_ds_w1$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w1, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(MHAS_ds_w1$child)
BeforeH <- table(MHAS_w1_child$a20, useNA='ifany')
BeforeH[[2]] <- sum(BeforeH[c(2:(length(BeforeH)-4),length(BeforeH)-2)])
BeforeH <- BeforeH[c(1,2,length(BeforeH)-3,length(BeforeH)-1,length(BeforeH))]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","88->995","99->998","NA->999")
kable(C)
```

 
 


### Wave 2

#### Study-specific variable description


| **Name** |`aa19`|`aa20`|
|-|-|-|
| **Label** |`How many children born alive do you have`|`Of those, how many still alive`|
| **Table name** |`MHAS_2003`|`MHAS_2003`|
| **Categories** |`continuous`|`continuous`<br/>`0 = None`<br/>`96 = All`|
| **Missings** |`99 = Doesn't know`|`88 = Doesn't answer`<br/>`99 = Doesn't know`|
| **Description** |  |  |

```{r assign2, echo=F}
opal.assign.table.tibble(o, 'MHAS_w2_child','Mexican Health Aging Study.MHAS_2003',variables=list('aa19','aa20'), missings = TRUE)
MHAS_w2_child <- opal.execute(o,'MHAS_w2_child')
```

```{r local2, echo=F}

vbl <- MHAS_w2_child$aa19
vbl_miss <- c(88,99)
kable(Continuous_summary(vbl, missing_values = vbl_miss)[3], caption = "aa19") 
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(MHAS_w2_child,!vbl %in% vbl_miss), aes(aa19)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <-  MHAS_w2_child$aa20
kable(Continuous_summary(vari, missing_values = c(88,99))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Continuous_summary(vari, missing_values = c(88,99))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(88,99))$summary, caption = "Summary")
#Continuous_summary(var = MHAS_w2_child$aa20, missing_values = NA)
ggplot(filter(MHAS_w2_child,!vari %in% c(88,99,96)), aes(aa20)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How many of children are still alive") + ylab("Frequency")
```

#### Harmonisation algorithm

To recode the harmonize variable from the study-specific variable `aa20` it has to be recoded as follows:  

* `aa19 == 0 into 0`
* `1:30 or 96 into 1`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
MHAS_ds_w2 <- tibble(id=MHAS_w2_child$id)
MHAS_ds_w2$child <- car::recode(as.vector(MHAS_w2_child$aa20), "1:30='1'; 96='1'; 0='0'; NA='999'")
MHAS_ds_w2$child[which(MHAS_w2_child$aa19==0)] <- 0
MHAS_ds_w2$child <- labelled(MHAS_ds_w2$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}
vari <- MHAS_ds_w2$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_ds_w2$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w2, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}

```

 
 


### Wave 3

#### Study-specific variable description


| **Name** |`a8_12`|
|-|-|
| **Label** |`Number of children currently living`|
| **Table name** |`MHAS_2012_new`|
| **Categories** |`continuous`<br/>`0 = None`<br/>`96 = All`|
| **Missings** |`88 = Doesn't answer`<br/>`99 = Doesn't know`|
| **Description** |  |


```{r assign3, echo=F}
opal.assign.table.tibble(o, 'MHAS_w3_child','Mexican Health Aging Study.MHAS_2012_new',variables=list('a8_12'), missings = TRUE)
MHAS_w3_child <- opal.execute(o,'MHAS_w3_child')
```

```{r local3, echo=F}
vari <- MHAS_w3_child$a8_12
kable(Continuous_summary(var = vari, missing_values = c(88,99))[3])
kable(Continuous_summary(vari, missing_values = c(88,99))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(88,99))$summary, caption = "Summary")
#Continuous_summary(var = MHAS_w3_child$a8_12, missing_values = NA)
ggplot(filter(MHAS_w3_child,!vari %in% c(88,99,96)), aes(a8_12)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of children currently living") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1:30 or 96 into 1`
* `0 into 0`
* `88 RF into 997`
* `99 DK into 998`
* `NA into 999`

**R script:**

```{r harmo3, echo=TRUE}
MHAS_ds_w3 <- tibble(id=MHAS_w3_child$id)
MHAS_ds_w3$child <- car::recode(as.vector(MHAS_w3_child$a8_12), "1:30='1'; 96='1'; 0='0'; 88='997'; 99='998'; NA='999'")
MHAS_ds_w3$child <- labelled(MHAS_ds_w3$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=F}
vari <- MHAS_ds_w3$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_ds_w3$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w3, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Has children") + ylab("Frequency")
```

##### Validation
```{r crosstabulation3, echo=F}
AfterH <- table(MHAS_ds_w3$child)
BeforeH <- table(MHAS_w3_child$a8_12, useNA='ifany')
BeforeH[[2]] <- sum(BeforeH[c(2:(length(BeforeH)-4),length(BeforeH)-2)])
BeforeH <- BeforeH[c(1,2,length(BeforeH)-3,length(BeforeH)-1,length(BeforeH))]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","88->995","99->998","NA->999")
kable(C)
```

 
 
```{r save, echo=FALSE}
child <- MHAS_ds_w1
save(child, file = "../RData/w1/child.RData")
rm(child)

child <- MHAS_ds_w2
save(child, file = "../RData/w2/child.RData")
rm(child)

child <- MHAS_ds_w3
save(child, file = "../RData/w3/child.RData")
rm(child)

```

# Quality estimation

* In wave 2 there are also the variables `d4` (`Person has living children`) or `t3h3` and `b3` (used in g2aging to count number of children).


```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
