---
title: "Has other (living) family members (e.g. parents, siblings, in-laws, etc.)"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `oth_fam`
* Variable label: `Has other (living) family members (e.g. parents, siblings, in-laws, etc.)`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process

## Mexican population
### Wave 1

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `f3`
* Label: `Mother alive`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `8 = RF`
    + `9 = DK`
    
* Name: `f10`
* Label: `Father alive`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `8 = RF`
    + `9 = DK`

* Name: `f30`
* Label: `Siblings born alive`
* Categories: 
    + `0 = None`
* Missings:
    + `88 = RF`
    + `99 = DK`
    
* Name: `f31`
* Label: `Siblings still alive`
* Categories: 
    + `0 = None`
    + `96 = All`
* Missings:
    + `88 = RF`
    + `99 = DK`
    

* Description: 
```{r assign1}
opal.assign.table.tibble(o, 'MHAS_w1_oth_fam','Mexican Health Aging Study.MHAS-2001',
                         variables=list('f3','f10','f30','f31'), missings = TRUE)
```

```{r local1}
MHAS_w1_oth_fam <- opal.execute(o,'MHAS_w1_oth_fam')
vari <- MHAS_w1_oth_fam$f3
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w1_oth_fam$f3, missing_values = NA)
ggplot(MHAS_w1_oth_fam, aes(x=factor(f3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mother alive?") + ylab("Frequency")

vari <- MHAS_w1_oth_fam$f10
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w1_oth_fam$f10, missing_values = NA)
ggplot(MHAS_w1_oth_fam, aes(x=factor(f10))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Father alive?") + ylab("Frequency")

vari <- MHAS_w1_oth_fam$f30
kable(Continuous_summary(vari, missing_values = c(88,99))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Continuous_summary(vari, missing_values = c(88,99))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values =c(88,99))$summary, caption = "Summary")
#Continuous_summary(var = MHAS_w1_oth_fam$f30, missing_values = NA)
ggplot(MHAS_w1_oth_fam, aes(x=factor(f30))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of siblings born alive") + ylab("Frequency")

vari <- MHAS_w1_oth_fam$f31
kable(Continuous_summary(vari, missing_values = c(88,96,99))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Continuous_summary(vari, missing_values = c(88,96,99))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values =c(88,96,99))$summary, caption = "Summary")
#Continuous_summary(var = MHAS_w1_oth_fam$f31, missing_values = NA)
ggplot(MHAS_w1_oth_fam, aes(x=factor(f31))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of siblings still alive") + ylab("Frequency")

```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if f3=1 or f10=1 or f31>0 then 1`
* `if f3=2 and f10=2 and (f30=0 or f31=0) then 0`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
MHAS_ds_w1 <- tibble(id=MHAS_w1_oth_fam$id)

MHAS_w1_oth_fam$f3 <- car::recode(as.vector(MHAS_w1_oth_fam$f3), "NA='-999'")
MHAS_w1_oth_fam$f10 <- car::recode(as.vector(MHAS_w1_oth_fam$f10), "NA='-999'")
MHAS_w1_oth_fam$f30 <- car::recode(as.vector(MHAS_w1_oth_fam$f30), "NA='-999'")
MHAS_w1_oth_fam$f31 <- car::recode(as.vector(MHAS_w1_oth_fam$f31), "NA='-999'")

MHAS_ds_w1$oth_fam <- c(NA) 
for(i in 1:dim(MHAS_w1_oth_fam)[1]){
  if(MHAS_w1_oth_fam$f3[i] == 1 | MHAS_w1_oth_fam$f10[i] == 1 | MHAS_w1_oth_fam$f31[i] > 0 ){
    MHAS_ds_w1$oth_fam[i] = 1 } 
  else if(MHAS_w1_oth_fam$f3[i] == 2 & MHAS_w1_oth_fam$f10[i] == 2 & (MHAS_w1_oth_fam$f30[i] == 0 | MHAS_w1_oth_fam$f31[i] == 0) ){
    MHAS_ds_w1$oth_fam[i] = 0 }
  else if(MHAS_w1_oth_fam$f3[i] == 8 | MHAS_w1_oth_fam$f10[i] == 8 | MHAS_w1_oth_fam$f30[i] == 88 | MHAS_w1_oth_fam$f31[i] == 88 ){
    MHAS_ds_w1$oth_fam[i] = 997 }
  else if(MHAS_w1_oth_fam$f3[i] == 9 | MHAS_w1_oth_fam$f10[i] == 9 | MHAS_w1_oth_fam$f30[i] == 99 | MHAS_w1_oth_fam$f31[i] == 99 ){
    MHAS_ds_w1$oth_fam[i] = 998 }
}

MHAS_ds_w1$oth_fam <- car::recode(as.vector(MHAS_ds_w1$oth_fam), "NA='999'")
MHAS_ds_w1$oth_fam <- labelled(MHAS_ds_w1$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1}
vari <- MHAS_ds_w1$oth_fam
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_ds_w1$oth_fam, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w1, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1}

```

 
 




### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `f3`
* Label: `Mother presently alive`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `8 = RF`
    + `9 = DK`
    
* Name: `f12`
* Label: `Father presently alive`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `8 = RF`
    + `9 = DK`

* Name: `f34`
* Label: `How many siblings were born alive?`
* Categories: 
    + `0 = None`
* Missings:
    + `88 = RF`
    + `99 = DK`
    
* Name: `f36`
* Label: `How many siblings are still alive`
* Categories: 
    + `0 = None`
* Missings:
    + `88 = RF`
    + `96 = All`
    + `99 = DK`
    

* Description: 
```{r assign2}
opal.assign.table.tibble(o, 'MHAS_w2_oth_fam','Mexican Health Aging Study.MHAS_2003',
                         variables=list('f3','f12','f34','f36'), missings = TRUE)
```

```{r local2}
MHAS_w2_oth_fam <- opal.execute(o,'MHAS_w2_oth_fam')
vari <- MHAS_w2_oth_fam$f3
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w2_oth_fam$f3, missing_values = NA)
ggplot(MHAS_w2_oth_fam, aes(x=factor(f3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mother presently alive?") + ylab("Frequency")

vari <- MHAS_w2_oth_fam$f12
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w2_oth_fam$f12, missing_values = NA)
ggplot(MHAS_w2_oth_fam, aes(x=factor(f12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Father presently alive?") + ylab("Frequency")

vari <- MHAS_w2_oth_fam$f34
kable(Continuous_summary(vari, missing_values = c(88,99))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Continuous_summary(vari, missing_values = c(88,99))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values =c(88,99))$summary, caption = "Summary")
#Continuous_summary(var = MHAS_w2_oth_fam$f34, missing_values = NA)
ggplot(MHAS_w2_oth_fam, aes(x=factor(f34))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How many siblings were born alive?") + ylab("Frequency")

vari <- MHAS_w2_oth_fam$f36
kable(Continuous_summary(vari, missing_values = c(88,96,99))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Continuous_summary(vari, missing_values = c(88,96,99))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values =c(88,96,99))$summary, caption = "Summary")
#Continuous_summary(var = MHAS_w2_oth_fam$f36, missing_values = NA)
ggplot(MHAS_w2_oth_fam, aes(x=factor(f36))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How many siblings are still alive?") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if f3=1 or f12=1 or f36>0 then 1`
* `if f3=2 and f12=2 and (f34=0 or f36=0) then 0`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
MHAS_ds_w2 <- tibble(id=MHAS_w2_oth_fam$id)

MHAS_w2_oth_fam$f3 <- car::recode(as.vector(MHAS_w2_oth_fam$f3), "NA='-999'")
MHAS_w2_oth_fam$f12 <- car::recode(as.vector(MHAS_w2_oth_fam$f12), "NA='-999'")
MHAS_w2_oth_fam$f34 <- car::recode(as.vector(MHAS_w2_oth_fam$f34), "NA='-999'")
MHAS_w2_oth_fam$f36 <- car::recode(as.vector(MHAS_w2_oth_fam$f36), "NA='-999'")

MHAS_ds_w2$oth_fam <- c(NA)
for(i in 1:dim(MHAS_w2_oth_fam)[1]){
  if(MHAS_w2_oth_fam$f3[i] == 1 | MHAS_w2_oth_fam$f12[i] == 1 | MHAS_w2_oth_fam$f36[i] > 0 ){
    MHAS_ds_w2$oth_fam[i] = 1 } 
  else if(MHAS_w2_oth_fam$f3[i] == 2 & MHAS_w2_oth_fam$f12[i] == 2 & (MHAS_w2_oth_fam$f34[i] == 0 | MHAS_w2_oth_fam$f36[i] == 0) ){
    MHAS_ds_w2$oth_fam[i] = 0 }
  else if(MHAS_w2_oth_fam$f3[i] == 8 | MHAS_w2_oth_fam$f12[i] == 8 | MHAS_w2_oth_fam$f34[i] == 88 | MHAS_w2_oth_fam$f36[i] == 88 ){
    MHAS_ds_w2$oth_fam[i] = 997 }
  else if(MHAS_w2_oth_fam$f3[i] == 9 | MHAS_w2_oth_fam$f12[i] == 9 | MHAS_w2_oth_fam$f34[i] == 99 | MHAS_w2_oth_fam$f36[i] == 99 ){
    MHAS_ds_w2$oth_fam[i] = 998 }
}

MHAS_ds_w2$oth_fam <- car::recode(as.vector(MHAS_ds_w2$oth_fam), "NA='999'")
MHAS_ds_w2$oth_fam <- labelled(MHAS_ds_w2$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2}
vari <- MHAS_ds_w2$oth_fam
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_ds_w2$oth_fam, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w2, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2}

```

 
 


### Wave 3

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `f3_12`
* Label: `Currently:Is respondent's mother living`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `8 = RF`
    + `9 = DK`
    
* Name: `f12_12`
* Label: `Currently:Is respondent's father living`
* Categories: 
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `8 = RF`
    + `9 = DK`

* Name: `f34_12`
* Label: `Respondent's number of siblings born alive`
* Categories: 
    + `0 = None`
* Missings:
    + `88 = RF`
    + `99 = DK`
    
* Name: `f36_12`
* Label: ` Currently:How many of the respondent's siblings are living`
* Categories: 
    + `0 = None`
* Missings:
    + `88 = RF`
    + `96 = All`
    + `99 = DK`
    

* Description: 
```{r assign3}
opal.assign.table.tibble(o, 'MHAS_w3_oth_fam','Mexican Health Aging Study.MHAS_2012_new',
                         variables=list('f3_12','f12_12','f34_12','f36_12'), missings = TRUE)
```

```{r local3}
MHAS_w3_oth_fam <- opal.execute(o,'MHAS_w3_oth_fam')
vari <- MHAS_w3_oth_fam$f3_12
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w3_oth_fam$f3_12, missing_values = NA)
ggplot(MHAS_w3_oth_fam, aes(x=factor(f3_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Currently:Is respondent's mother living?") + ylab("Frequency")

vari <- MHAS_w3_oth_fam$f12_12
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w3_oth_fam$f12_12, missing_values = NA)
ggplot(MHAS_w3_oth_fam, aes(x=factor(f12_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Currently:Is respondent's father living?") + ylab("Frequency")

vari <- MHAS_w3_oth_fam$f34_12
kable(Continuous_summary(vari, missing_values = c(88,99))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Continuous_summary(vari, missing_values = c(88,99))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values =c(88,99))$summary, caption = "Summary")
#Continuous_summary(var = MHAS_w3_oth_fam$f34_12, missing_values = NA)
ggplot(MHAS_w3_oth_fam, aes(x=factor(f34_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Respondent's number of siblings born alive") + ylab("Frequency")

vari <- MHAS_w3_oth_fam$f36_12
kable(Continuous_summary(vari, missing_values = c(88,96,99))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Continuous_summary(vari, missing_values = c(88,96,99))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values =c(88,96,99))$summary, caption = "Summary")
#Continuous_summary(var = MHAS_w3_oth_fam$f36_12, missing_values = NA)
ggplot(MHAS_w3_oth_fam, aes(x=factor(f36_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Currently:How many of the respondent's siblings are living?") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if f3_12=1 or f12_12=1 or f36_12>0 then 1`
* `if f3_12=2 and f12_12=2 and (f34_12=0 or f36_12=0) then 0`
* `NA into 999`

**R script:**

```{r harmo3, echo=TRUE}
MHAS_ds_w3 <- tibble(id=MHAS_w3_oth_fam$id)

MHAS_w3_oth_fam$f3_12 <- car::recode(as.vector(MHAS_w3_oth_fam$f3_12), "NA='-999'")
MHAS_w3_oth_fam$f12_12 <- car::recode(as.vector(MHAS_w3_oth_fam$f12_12), "NA='-999'")
MHAS_w3_oth_fam$f34_12 <- car::recode(as.vector(MHAS_w3_oth_fam$f34_12), "NA='-999'")
MHAS_w3_oth_fam$f36_12 <- car::recode(as.vector(MHAS_w3_oth_fam$f36_12), "NA='-999'")

MHAS_ds_w3$oth_fam <- c(NA)
for(i in 1:dim(MHAS_w3_oth_fam)[1]){
  if(MHAS_w3_oth_fam$f3_12[i] == 1 | MHAS_w3_oth_fam$f12_12[i] == 1 | MHAS_w3_oth_fam$f36_12[i] > 0 ){
    MHAS_ds_w3$oth_fam[i] = 1 } 
  else if(MHAS_w3_oth_fam$f3_12[i] == 2 & MHAS_w3_oth_fam$f12_12[i] == 2 & (MHAS_w3_oth_fam$f34_12[i] == 0 | MHAS_w3_oth_fam$f36_12[i] == 0) ){
    MHAS_ds_w3$oth_fam[i] = 0 }
  else if(MHAS_w3_oth_fam$f3_12[i] == 8 | MHAS_w3_oth_fam$f12_12[i] == 8 | MHAS_w3_oth_fam$f34_12[i] == 88 | MHAS_w3_oth_fam$f36_12[i] == 88 ){
    MHAS_ds_w3$oth_fam[i] = 997 }
  else if(MHAS_w3_oth_fam$f3_12[i] == 9 | MHAS_w3_oth_fam$f12_12[i] == 9 | MHAS_w3_oth_fam$f34_12[i] == 99 | MHAS_w3_oth_fam$f36_12[i] == 99 ){
    MHAS_ds_w3$oth_fam[i] = 998 }
}

MHAS_ds_w3$oth_fam <- car::recode(as.vector(MHAS_ds_w3$oth_fam), "NA='999'")
MHAS_ds_w3$oth_fam <- labelled(MHAS_ds_w3$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3}
vari <- MHAS_ds_w3$oth_fam
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_ds_w3$oth_fam, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w3, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Has other family members?") + ylab("Frequency")
```

##### Validation
```{r crosstabulation3}

```

 
 
```{r save, echo=FALSE}
oth_fam <- MHAS_ds_w1
save(oth_fam, file = "../RData/w1/oth_fam.RData")
rm(oth_fam)

oth_fam <- MHAS_ds_w2
save(oth_fam, file = "../RData/w2/oth_fam.RData")
rm(oth_fam)

oth_fam <- MHAS_ds_w3
save(oth_fam, file = "../RData/w3/oth_fam.RData")
rm(oth_fam)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```

