---
title: "Are the contacts with friends/neighbours frequent (i.e. contact once a month or more often)"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/cont_frDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/cont_frDS.R')
```


<!-- ########################################################## --> 

# Data process

## Mexico

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `G29`
* Label: `Social talks and visits`
* Categories: 
    + `1 - 29 times`
    + `30 = Every day`
* Missings:
    + `88 = RF`
    + `98 = Invalid code`
    + `99 = DK`
* Description:

```{r assign1, echo=F}

opal.assign.table.tibble(o, 'MHAS_w1_cont_fr','Mexican Health Aging Study.g_house',variables=list('G29','G1'), missings = TRUE)
MHAS_w1_cont_fr <- opal.execute(o,'MHAS_w1_cont_fr')
opal.assign.table.tibble(o, 'MHAS_w1_id','Mexican Health Aging Study.MHAS-2001',variables=list('unhhid'), missings = T)
MHAS_w1_id <- opal.execute(o,'MHAS_w1_id')
MHAS_w1_id$unhhid <- paste0(as.character(MHAS_w1_id$unhhid),".0")
MHAS_w1 <- left_join(MHAS_w1_id,MHAS_w1_cont_fr,by=c("unhhid"="id"))

```

```{r local1, echo=F}

vari <- MHAS_w1_cont_fr$G29
kable(Continuous_summary(var = vari, missing_values = c(88,98,99))[3], caption = attributes(vari)$`spss::shortName`)
kable(Continuous_summary(vari, missing_values = c(88,98,99))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(88,98,99))$summary, caption = "Summary")
ggplot(MHAS_w1_cont_fr, aes(x=factor(G29))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Social talks and visits") + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

The interviewer manual specifies:

`When both interviews are conducted with proxies, the TR-habitual residents, TR-Children (section B), and the section on Help and Children (section G) will be filled out only for the first interview. In order to facilitate this, Interview Control Sheets are included in the questionnaire.`

* `For each household id we get the id corresponding to the respondent from the household id (substring of the id's) and the interview code (G1). For them:`
* `0 -> 0`
* `1:30 -> 1`
* `88 -> 997`
* `99 -> 998`
* `98,NA into 999`

**R script:**

```{r harmo1, echo=TRUE}

MHAS_ds_w1 <- tibble(id=MHAS_w1$id)
MHAS_ds_w1$cont_fr <- rep(999,length(MHAS_ds_w1$id))
MHAS_ds_w1$cont_fr[which(paste0(substr(MHAS_w1$id,1,nchar(MHAS_w1$id)-4),as.character(MHAS_w1$G1),"0.0")==MHAS_w1$id)] <- car::recode(as.vector(MHAS_w1$G29[which(paste0(substr(MHAS_w1$id,1,nchar(MHAS_w1$id)-4),as.character(MHAS_w1$G1),"0.0")==MHAS_w1$id)]), "1:30='1'; 0='0'; 88='997'; 98='999'; 99='998'; NA='999'")
MHAS_ds_w1$cont_fr <- labelled(MHAS_ds_w1$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <- MHAS_ds_w1$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_ds_w1$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w1, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}

```




### Wave 2

Not found.


### Wave 3



#### Study-specific variable description


| **Name** |`g30_12`|
|-|-|
| **Label** |`Number of times per month respondent communicates or visits with neighors`|
| **Table name**  | `sect_g_j_k_sa_2012`|
| **Categories** |`1 - 29 times`<br/>`30 = Every day`|
| **Missings** |`88 = RF`<br/>`99 = DK`|
| **Description** |  |


<!--

By contrast with `subhog_01`, `subhog_03`, `subhog_12` and `id`, the values `103, 104, 105, 107, 108, 109, 202` of `g34_12` may be generically imputed to `10`. The value `110` seems to be `20`. The other values could be `10` or in some cases `20`.

-->


```{r assign w3, echo=F}

opal.assign.table.tibble(o, 'MHAS_w3_cont_fr','Mexican Health Aging Study.sect_g_j_k_sa_2012',variables=list('g30_12','g34_12'), missings = TRUE)
MHAS_w3_cont_fr <- opal.execute(o,'MHAS_w3_cont_fr')
MHAS_w3_cont_fr$aux <- car::recode(MHAS_w3_cont_fr$g34_12, "103:999=NA")
# JOIN (HH)ID TOGETHER WITH REGISTRATION NUMBER OF THE RESPONDENT
MHAS_w3_cont_fr$newid <- paste0(substr(MHAS_w3_cont_fr$id,1,nchar(MHAS_w3_cont_fr$id)-2),as.character(MHAS_w3_cont_fr$aux),".0")
# Remove duplicated rows
MHAS_w3_cont_fr <- MHAS_w3_cont_fr[-which(duplicated(MHAS_w3_cont_fr)),]

opal.assign.table.tibble(o, 'MHAS_w3_id','Mexican Health Aging Study.MHAS_2012_new',variables=list('cunicah'), missings = T)
MHAS_w3_id <- opal.execute(o,'MHAS_w3_id')
MHAS_w3_id$cunicah <- paste0(as.character(MHAS_w3_id$cunicah),".0")

MHAS_w3 <- left_join(MHAS_w3_id,MHAS_w3_cont_fr,by=c("id"="newid"))

```

<!--
CHECK FUNCTION:

MHAS_w3[which(sapply(MHAS_w3$id, function(x) !paste0(substr(x,1,nchar(x)-4),as.character(MHAS_w3$g34_12[match(x,MHAS_w3$id)]),".0") %in% grep(paste0("^",substr(x,1,nchar(x)-4),"[0-9][0-9]\\.0"),MHAS_w3$id,value = T)) & MHAS_w3$g34_12 %in% c(10,11,12,20,21)),]

DOES NOT WORK WELL

-->


```{r local w3, echo=F}

vbl <- MHAS_w3$g30_12
kable(Continuous_summary(var = vbl, missing_values = c(88,99))[3], caption = 'g30_12')
kable(Continuous_summary(vbl, missing_values = c(88,99))[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = c(88,99))$summary, caption = "Summary")
ggplot(MHAS_w3, aes(x=factor(g30_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:


* `0 -> 0`
* `1:30 -> 1`
* `88 -> 997`
* `99 -> 998`
* `98,NA into 999`


**R script:**

```{r harmo w3}

MHAS_ds_w3 <- tibble(id=MHAS_w3$id)
MHAS_ds_w3$cont_fr <- rep(999,length(MHAS_ds_w3$id))
MHAS_ds_w3$cont_fr <- car::recode(as.vector(MHAS_w3$g30_12), "1:30='1'; 0='0'; 88='997'; 99='998'; NA='999'")

```


#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}

vari <- MHAS_ds_w3$cont_fr
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3]) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w3, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=F}

```






## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.


**R script:**

```{r summ}

l.hds <- list(w1 = MHAS_ds_w1, w3 = MHAS_ds_w3)


for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("MHAS_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}


t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label", names(l.hds))
kable(t.hds)

dbb <- get(paste0("MHAS_m_ds_",names(l.hds)[1]))[,c("id","cont_fr")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("MHAS_m_ds_",names(l.hds)[ind]))[,c("id","cont_fr")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", names(l.hds))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste0(v.dbb,dbb[,ind+1])
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb)

```




```{r save, echo=FALSE}

cont_fr <- MHAS_ds_w1
save(cont_fr, file = "../RData/w1/cont_fr.RData")
rm(cont_fr)

cont_fr <- MHAS_ds_w3
save(cont_fr, file = "../RData/w3/cont_fr.RData")
rm(cont_fr)

```



# Quality estimation

* In wave 2 there is the variable `G28`, similar to the one in wave 1, but we did not found it in databasis.


```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
