---
title: "Are any form of contact ( face-to-face/phone/mail/Internet communicators) with family members/relatives frequent (i.e. contact once a week or more often)?"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/cont_relDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/cont_relDS.R')
```



<!-- ########################################################## --> 

# Data process


## Mexico


### Wave 1

#### Study-specific variable description

The study-specific variable elected to be harmonised are:

* Name: `b10_2` **from table 'Mexican Health Aging Study.b_nores'**
* Label: `In the last 2 years, how often did you/your spouse contact nonresident child? (Period)`
* Categories:
    + `0 = never`
    + `1 = week`
    + `2 = month`
    + `3 = year`
    + `4 = less than once a year`
    + `5 = infrequently`
* Missings:
    + `8 = RF`
    + `9 = DK`
    
* Name: `f28b1` **from table 'Mexican Health Aging Study.MHAS-2001'**
* Label: `Period contact with mother`
* Categories:
    + `1 = week`
    + `2 = month`
    + `3 = year`
    + `4 = less than once a year`
    + `5 = never`
* Missings:
    + `8 = RF`
    + `9 = DK`

* Name: `f28b2` **from table 'Mexican Health Aging Study.MHAS-2001'**
* Label: `Period contact with father`
* Categories:
    + `1 = week`
    + `2 = month`
    + `3 = year`
    + `4 = less than once a year`
    + `5 = never`
* Missings:
    + `8 = RF`
    + `9 = DK`
    
* Name: `f28b3` **from table 'Mexican Health Aging Study.MHAS-2001'**
* Label: `Period contact with parents`
* Categories:
    + `1 = week`
    + `2 = month`
    + `3 = year`
    + `4 = less than once a year`
    + `5 = never`
* Missings:
    + `8 = RF`
    + `9 = DK`
    
* Name: `trh6`
* Label: `Relationship of household member to selected person`
* Categories:
    + `02 = spouse`
    + `03 = child`
    + `04 = stepchild`
    + `05 = adoptive child`
    + `06 = foster child`
    + `07 = parent`
    + `08 = parent-in-law`
    + `09 = grandparent`
    + `10 = grandchild`
    + `11 = great-grandchild`
    + `12 = child-in-law`
    + `13 = sibling/stepsibling`
    + `14 = sibling-in-law/cousin`
    + `15 = ancle/aunt`
    + `16 = nephew/niece`
    + `17 = other relative`
    + `18 = non-relative`
    + `66 = selected person died`
    + `00 = without spouse`
        

```{r assign1, echo=F}

opal.assign.table.tibble(o, 'MHAS_w1_cont_rel1','Mexican Health Aging Study.b_nores',  variables=list('b10_2','b1'), missings = TRUE)
MHAS_w1_cont_rel1 <- opal.execute(o,'MHAS_w1_cont_rel1')

opal.assign.table.tibble(o, 'MHAS_w1_cont_rel2','Mexican Health Aging Study.MHAS-2001', variables=list('f28b1','f28b2','f28b3','unhhid'), missings = TRUE)
MHAS_w1_cont_rel2 <- opal.execute(o,'MHAS_w1_cont_rel2')
MHAS_w1_cont_rel2$unhhid <- paste0(as.character(MHAS_w1_cont_rel2$unhhid),".0")

MHAS_w1 <- left_join(MHAS_w1_cont_rel2,MHAS_w1_cont_rel1,by=c("unhhid"="id"))

opal.assign.table.tibble(o, 'MHAS_w1_cont_rel3','Mexican Health Aging Study.sect_trh',  variables=list('trh6'), missings = TRUE)
MHAS_w1_cont_rel3 <- opal.execute(o, 'MHAS_w1_cont_rel3')

```

```{r local1, echo=F}
vari <- MHAS_w1_cont_rel1$b10_2
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w1_cont_rel1$b10_2, missing_values = NA)
ggplot(MHAS_w1_cont_rel1, aes(x=factor(b10_2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("In the last 2 years, how often did you/your spouse contact nonresident child? (Period)") + ylab("Frequency")

vari <- MHAS_w1_cont_rel2$f28b1
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w1_cont_rel2$f28b1, missing_values = NA)
ggplot(MHAS_w1_cont_rel2, aes(x=factor(f28b1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Period contact with mother") + ylab("Frequency")

vari <- MHAS_w1_cont_rel2$f28b2
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w1_cont_rel2$f28b1, missing_values = NA)
ggplot(MHAS_w1_cont_rel2, aes(x=factor(f28b1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Period contact with mother") + ylab("Frequency")


vari <- MHAS_w1_cont_rel3$trh6
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(MHAS_w1_cont_rel3, aes(x=factor(trh6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Relationship of household member to selected person") + ylab("Frequency")

```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

The interviewer manual specifies:

`When both interviews are conducted with proxies, the TR-habitual residents, TR-Children (section B), and the section on Help and Children (section G) will be filled out only for the first interview. In order to facilitate this, Interview Control Sheets are included in the questionnaire.`


* `For each household id we get the id corresponding to the respondent from the household id (substring of the id's) and the interview code (B1). For them:`
* `week into 1`
* `trh6 from 2 to 17 into 1 `
* `NA into 999`

**R script:**

```{r harmo1}

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  colnames(new_2) <- colnames(old)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){ # copy values from old or NA
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], rep_len(NA,dim(old)[2]-1))
    }
  }
  new_2 <- data.frame(new_2)
  new_22 <- data.frame(id=new_2$id, b10_2=new_2$b10_2, f28b1=new$f28b1, f28b2=new$f28b2, f28b3=new$f28b3) # add variables from new
                       # id = new_2$id
                       # colname_form_OLD_table = new_2$colname_form_OLD_table 
                       # colname_form_NEW_table = new$colname_form_NEW_table
  new_22
}

# old = MHAS_w1_cont_rel1 (b10_2) 36850
# new = MHAS_w1_cont_rel2 (f28b1,f28b2,f28b3) 15146

MHAS_w1_cont_rel <- same_indiv(MHAS_w1_cont_rel1, MHAS_w1_cont_rel2)

same_indiv2 <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  colnames(new_2) <- colnames(old)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], rep_len(NA,dim(old)[2]-1))
    }
  }
  new_2 <- data.frame(new_2)
  new_22 <- data.frame(id=new_2$id, trh6=new_2$trh6,b10_2=new$b10_2, f28b1=new$f28b1, f28b2=new$f28b2, f28b3=new$f28b3) 
                       # id = new_2$id
                       # colname_form_OLD_table = new_2$colname_form_OLD_table 
                       # colname_form_NEW_table = new$colname_form_NEW_table
  new_22
}


# old = MHAS_w1_cont_rel3 (trh6) 
# new = MHAS_w1_cont_rel (b10_2,f28b1,f28b2,f28b3) 15146
MHAS_w1_cont_rel <- same_indiv2(MHAS_w1_cont_rel3, MHAS_w1_cont_rel)

MHAS_ds_w1 <- tibble(id=MHAS_w1_cont_rel$id)

MHAS_w1_cont_rel$f28b1 <- car::recode(as.vector(MHAS_w1_cont_rel$f28b1), "NA='-999'")
MHAS_w1_cont_rel$f28b2 <- car::recode(as.vector(MHAS_w1_cont_rel$f28b2), "NA='-999'")
MHAS_w1_cont_rel$f28b3 <- car::recode(as.vector(MHAS_w1_cont_rel$f28b3), "NA='-999'")
MHAS_w1_cont_rel$b10_2 <- car::recode(as.vector(MHAS_w1_cont_rel$b10_2), "NA='-999'")
MHAS_w1_cont_rel$trh6 <- car::recode(as.vector(MHAS_w1_cont_rel$trh6), "NA='-999'")

MHAS_ds_w1$cont_rel <- c(NA) 
for(i in 1:dim(MHAS_w1_cont_rel)[1]){
  if( MHAS_w1_cont_rel$f28b1[i] == 1 | MHAS_w1_cont_rel$f28b2[i] == 1 | MHAS_w1_cont_rel$f28b3[i] == 1 | MHAS_w1_cont_rel$b10_2[i] == 1 | MHAS_w1_cont_rel$trh6[i] %in% 2:17) {
    MHAS_ds_w1$cont_rel[i] = 1 }
  else if( MHAS_w1_cont_rel$f28b1[i] == -999 & MHAS_w1_cont_rel$f28b2[i] == -999 & MHAS_w1_cont_rel$f28b3[i] == -999 & MHAS_w1_cont_rel$b10_2[i] == -999 ) {
    MHAS_ds_w1$cont_rel[i] = 999 }
  else if( !( MHAS_w1_cont_rel$f28b1[i] == 1 | MHAS_w1_cont_rel$f28b2[i] == 1 | MHAS_w1_cont_rel$f28b3[i] == 1 | MHAS_w1_cont_rel$b10_2[i] == 1 ) ) {
    MHAS_ds_w1$cont_rel[i] = 0 }
}


MHAS_ds_w1$cont_rel <- car::recode(as.vector(MHAS_ds_w1$cont_rel), "NA='999'")
MHAS_ds_w1$cont_rel <- labelled(MHAS_ds_w1$cont_rel, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- MHAS_ds_w1$cont_rel
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_ds_w1$cont_rel, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w1, aes(x=factor(cont_rel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are any form of contact ( face-to-face/phone/mail/Internet communicators) with family members/relatives frequent?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}

```




### Wave 2

#### Study-specific variables

The study-specific variables elected to be harmonised are:

    
* Name: `f32_1b`
* Label: `Frequency of contact with mother - period`
* Categories:
    + `1 = week`
    + `2 = month`
    + `3 = year`
    + `4 = less than once a year`
    + `5 = never`
* Missings:
    + `8 = RF`
    + `9 = DK`

* Name: `f32_2b`
* Label: `Frequency of contact with father - period`
* Categories:
    + `1 = week`
    + `2 = month`
    + `3 = year`
    + `4 = less than once a year`
    + `5 = never`
* Missings:
    + `8 = RF`
    + `9 = DK`
    
* Name: `f32_3b`
* Label: `Frequency of contact with parents - period`
* Categories:
    + `1 = week`
    + `2 = month`
    + `3 = year`
    + `4 = less than once a year`
    + `5 = never`
* Missings:
    + `8 = RF`
    + `9 = DK`
    


```{r assign2, echo=F}
opal.assign.table.tibble(o, 'MHAS_w2_cont_rel','Mexican Health Aging Study.MHAS_2003',
                         variables=list('f32_1b','f32_2b','f32_3b'), missings = TRUE)
```

```{r local2, echo=F}
MHAS_w2_cont_rel <- opal.execute(o,'MHAS_w2_cont_rel')

vari <- MHAS_w2_cont_rel$f32_1b
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w2_cont_rel$f32_1b, missing_values = NA)
ggplot(MHAS_w2_cont_rel, aes(x=factor(f32_1b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of contact with mother - period") + ylab("Frequency")

vari <- MHAS_w2_cont_rel$f32_2b
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w2_cont_rel$f32_1b, missing_values = NA)
ggplot(MHAS_w2_cont_rel, aes(x=factor(f32_2b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of contact with father - period") + ylab("Frequency")


vari <- MHAS_w2_cont_rel$f32_3b
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w2_cont_rel$f32_1b, missing_values = NA)
ggplot(MHAS_w2_cont_rel, aes(x=factor(f32_3b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of contact with parents - period") + ylab("Frequency")

```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `week into 1`
* `NA into 999`

**R script:**

```{r harmo2}
MHAS_ds_w2 <- tibble(id=MHAS_w2_cont_rel$id)

MHAS_w2_cont_rel$f32_1b <- car::recode(as.vector(MHAS_w2_cont_rel$f32_1b), "NA='-999'")
MHAS_w2_cont_rel$f32_2b <- car::recode(as.vector(MHAS_w2_cont_rel$f32_2b), "NA='-999'")
MHAS_w2_cont_rel$f32_3b <- car::recode(as.vector(MHAS_w2_cont_rel$f32_3b), "NA='-999'")

MHAS_ds_w2$cont_rel <- c(NA) # I think it is required
for(i in 1:dim(MHAS_w2_cont_rel)[1]){
  if( MHAS_w2_cont_rel$f32_1b[i] == 1 | MHAS_w2_cont_rel$f32_2b[i] == 1 | MHAS_w2_cont_rel$f32_3b[i] == 1 ) {
   MHAS_ds_w2$cont_rel[i] = 1 }
  else if( MHAS_w2_cont_rel$f32_1b[i] == -999 & MHAS_w2_cont_rel$f32_2b[i] == -999 & MHAS_w2_cont_rel$f32_3b[i] == -999 ) {
   MHAS_ds_w2$cont_rel[i] = 999 }
  else if( !( MHAS_w2_cont_rel$f32_1b[i] == 1 | MHAS_w2_cont_rel$f32_2b[i] == 1 | MHAS_w2_cont_rel$f32_3b[i] == 1 ) ) {
   MHAS_ds_w2$cont_rel[i] = 0 }
}

MHAS_ds_w2$cont_rel <- car::recode(as.vector(MHAS_ds_w2$cont_rel), "NA='999'")
MHAS_ds_w2$cont_rel <- labelled(MHAS_ds_w2$cont_rel, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- MHAS_ds_w2$cont_rel
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_ds_w2$cont_rel, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w2, aes(x=factor(cont_rel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are any form of contact ( face-to-face/phone/mail/Internet communicators) with family members/relatives frequent?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}

```



### Wave 3

#### Study-specific variables

The study-specific variables elected to be harmonised are:
  
  
* Name: `f32_1_2_12`
* Label: `Last 2 years: respondent's period to report contact with mother`
* Categories:
    + `1 = week`
    + `2 = month`
    + `3 = year`
    + `4 = less than once a year`
    + `5 = never`
* Missings:
    + `8 = RF`
    + `9 = DK`

* Name: `f32_2_2_12`
* Label: `Last 2 years: respondent's period to report contact with father`
* Categories:
    + `1 = week`
    + `2 = month`
    + `3 = year`
    + `4 = less than once a year`
    + `5 = never`
* Missings:
    + `8 = RF`
    + `9 = DK`



* Name: `trh9_12` **from "sect_trh_follow_up_2012"**
* Label: `Resident's relationship to respondent`
* Categories:
    + `02 = child`
    + `03 = step child`
    + `04 = adopted child`
    + `05 = foster child`
    + `06 = mother/father`
    + `07 = parent-in-law`
    + `08 = grandparent`
    + `09 = grandchild`
    + `10 = great-grandchild`
    + `11 = son/daughter-in-law`
    + `12 = brother/sister, step B/S`
    + `13 = brother/sister-in-law/cousin`
    + `14 = ancle/aunt`
    + `15 = nephew/niece`
    + `16 = other relative`
    + `17 = non-relative`


* Name: `ntrh6_12` **from "sect_trh_new_sample_2012"**
* Label: `Resident's relationship to respondent`
* Categories:
    + `03 = child`
    + `04 = step child`
    + `05 = adopted child`
    + `06 = foster child`
    + `07 = mother/father`
    + `08 = parent-in-law`
    + `09 = grandparent`
    + `10 = grandchild`
    + `11 = great-grandchild`
    + `12 = son/daughter-in-law`
    + `13 = brother/sister, step B/S`
    + `14 = brother/sister-in-law/cousin`
    + `15 = ancle/aunt`
    + `16 = nephew/niece`
    + `17 = other relative`
    + `18 = non-relative`


```{r assign3, echo=F}
opal.assign.table.tibble(o, 'MHAS_w3_cont_rel','Mexican Health Aging Study.MHAS_2012_new',
                         variables=list('f32_1_2_12','f32_2_2_12'), missings = TRUE)

opal.assign.table.tibble(o, 'MHAS_w3_cont_rel1','Mexican Health Aging Study.sect_trh_follow_up_2012',
                         variables=list('trh9_12'), missings = TRUE)

opal.assign.table.tibble(o, 'MHAS_w3_cont_rel2','Mexican Health Aging Study.sect_trh_new_sample_2012',
                         variables=list('ntrh6_12'), missings = TRUE)

```

```{r local3, echo=F}
MHAS_w3_cont_rel <- opal.execute(o,'MHAS_w3_cont_rel')

vari <- MHAS_w3_cont_rel$f32_1_2_12
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w3_cont_rel$f32_1_2_12, missing_values = NA)
ggplot(MHAS_w3_cont_rel, aes(x=factor(f32_1_2_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Last 2 years: respondent's period to report contact with mother") + ylab("Frequency")


vari <- MHAS_w3_cont_rel$f32_2_2_12
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w3_cont_rel$f32_1_2_12, missing_values = NA)
ggplot(MHAS_w3_cont_rel, aes(x=factor(f32_2_2_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Last 2 years: respondent's period to report contact with father") + ylab("Frequency")


MHAS_w3_cont_rel1 <- opal.execute(o,'MHAS_w3_cont_rel1')

vari <- MHAS_w3_cont_rel1$trh9_12
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w3_cont_rel$f32_1_2_12, missing_values = NA)
ggplot(MHAS_w3_cont_rel1, aes(x=factor(trh9_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Resident's relationship to respondent") + ylab("Frequency")

MHAS_w3_cont_rel2 <- opal.execute(o,'MHAS_w3_cont_rel2')

vari <- MHAS_w3_cont_rel2$ntrh6_12
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w3_cont_rel$f32_1_2_12, missing_values = NA)
ggplot(MHAS_w3_cont_rel2, aes(x=factor(ntrh6_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Resident's relationship to respondent") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  
  
* `week into 1`
* `if trh9_12 in 2:16 or ntrh6_12 in 3:17 then 1`
* `NA into 999`

**R script:**
  
```{r harmo3}
MHAS_w3_cont_rel
MHAS_w3_cont_rel1
MHAS_w3_cont_rel2
# los ids y dimensiones no coinciden. Habra que usar same_ind() pero no se si enteindo bien cual hay que coger como old y como new, ni que ids quedarse... PREGUNTAR A LAIA


MHAS_ds_w3 <- tibble(id=MHAS_w3_cont_rel$id)

MHAS_w3_cont_rel$f32_1_2_12 <- car::recode(as.vector(MHAS_w3_cont_rel$f32_1_2_12), "NA='-999'")
MHAS_w3_cont_rel$f32_2_2_12 <- car::recode(as.vector(MHAS_w3_cont_rel$f32_2_2_12), "NA='-999'")
MHAS_w3_cont_rel$f32_3_2_12 <- car::recode(as.vector(MHAS_w3_cont_rel$f32_3_2_12), "NA='-999'")


MHAS_ds_w3$cont_rel <- c(NA) # I think it is required
for(i in 1:dim(MHAS_w3_cont_rel)[1]){
  if( MHAS_w3_cont_rel$f32_1_2_12[i] == 1 | MHAS_w3_cont_rel$f32_2_2_12[i] == 1 | MHAS_w3_cont_rel$f32_3_2_12[i] == 1 ) {
    MHAS_ds_w3$cont_rel[i] = 1 }
  else if( MHAS_w3_cont_rel$f32_1_2_12[i] == -999 & MHAS_w3_cont_rel$f32_2_2_12[i] == -999 & MHAS_w3_cont_rel$f32_3_2_12[i] == -999 ) {
    MHAS_ds_w3$cont_rel[i] = 999 }
  else if( !( MHAS_w3_cont_rel$f32_1_2_12[i] == 1 | MHAS_w3_cont_rel$f32_2_2_12[i] == 1 | MHAS_w3_cont_rel$f32_3_2_12[i] == 1 ) ) {
    MHAS_ds_w3$cont_rel[i] = 0 }
}

MHAS_ds_w3$cont_rel <- car::recode(as.vector(MHAS_ds_w3$cont_rel), "NA='999'")
MHAS_ds_w3$cont_rel <- labelled(MHAS_ds_w3$cont_rel, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}
Categorical_summary(var = MHAS_ds_w3$cont_rel, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w3, aes(x=factor(cont_rel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are any form of contact ( face-to-face/phone/mail/Internet communicators) with family members/relatives frequent?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=F}

```












# Quality estimation


```{r closeRsession, echo=FALSE} 
opal.logout(o)
```

