---
title: "Are any form of contact ( face-to-face/phone/mail/Internet communicators) with family members/relatives frequent (i.e. contact once a week or more often)?"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/cont_relDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/cont_relDS.R')
```



<!-- ########################################################## --> 

# Data process


## Mexico


### Wave 1

#### Study-specific variable description

| **Name** |`b10_2`|`b1`|`unhhid`|
|-|-|-|-|
| **Label** |`In the last 2 years, how often did you/your spouse contact nonresident child? (Period)`|`Code of respondent who answered questions`|`Unique household ID`|
| **Table name** |`b_nores`|`b_nores`|`b_nores`|
| **Categries** |`0 = never`<br/>`1 = week`<br/>`2 = month`<br/>`3 = year`<br/>`4 = less than once a year`<br/>`5 = infrequently`|`1 = Selected person`<br/>`2 = Selected person’s spouse`|`text`|
| **Missings** |`8 = RF`<br/>`9 = DK`|  |  |
| **Description** |  |  |  |

| **Name** |`f28b1`|`f28b2`|`f28b3`|
|-|-|-|-|
| **Label** |`Period contact with mother`|`Period contact with father`|`Period contact with parents`|
| **Table name** |`MHAS-2001`|`MHAS-2001`|`MHAS-2001`|
| **Categries** |`1 = week`<br/>`2 = month`<br/>`3 = year`<br/>`4 = less than once a year`<br/>`5 = never`|`1 = week`<br/>`2 = month`<br/>`3 = year`<br/>`4 = less than once a year`<br/>`5 = never`|`1 = week`<br/>`2 = month`<br/>`3 = year`<br/>`4 = less than once a year`<br/>`5 = never`|
| **Missings** |`8 = RF`<br/>`9 = DK`|`8 = RF`<br/>`9 = DK`|`8 = RF`<br/>`9 = DK`|
| **Description** |  |  |  |


| **Name** |`trh6`|`trh1`|`unhhid`|
|-|-|-|-|
| **Label** |`Relationship of household member to selected person`|`Respondent's Code`|`Unique household ID`|
| **Table name** |`sect_trh`|`sect_trh`|`sect_trh`|
| **Categries** |`02 = spouse`<br/>`03 = child`<br/>`04 = stepchild`<br/>`05 = adoptive child`<br/>`06 = foster child`<br/>`07 = parent`<br/>`08 = parent-in-law`<br/>`09 = grandparent`<br/>`10 = grandchild`<br/>`11 = great-grandchild`<br/>`12 = child-in-law`<br/>`13 = sibling/stepsibling`<br/>`14 = sibling-in-law/cousin`<br/>`15 = ancle/aunt`<br/>`16 = nephew/niece`<br/>`17 = other relative`<br/>`18 = non-relative`<br/>`66 = selected person died`<br/>`00 = without spouse`|`1 = Selected person`<br/>`2 = Selected person’s spouse`|`text`|
| **Missings** |  |  |  |
| **Description** |  |  |  |


        

```{r assign1, echo=F}

opal.assign.table.tibble(o, 'MHAS_w1_cont_rel1','Mexican Health Aging Study.b_nores',  variables=list('b10_2','b1','unhhid'), missings = TRUE)
MHAS_w1_cont_rel1 <- opal.execute(o,'MHAS_w1_cont_rel1')
MHAS_w1_cont_rel1$unhhid <- as.character(MHAS_w1_cont_rel1$unhhid)

opal.assign.table.tibble(o, 'MHAS_w1_cont_rel2','Mexican Health Aging Study.MHAS-2001', variables=list('f28b1','f28b2','f28b3'), missings = TRUE)
MHAS_w1_cont_rel2 <- opal.execute(o,'MHAS_w1_cont_rel2')



opal.assign.table.tibble(o, 'MHAS_w1_cont_rel3','Mexican Health Aging Study.sect_trh',  variables=list('trh6','unhhid','trh1'), missings = TRUE)
MHAS_w1_cont_rel3 <- opal.execute(o, 'MHAS_w1_cont_rel3')
MHAS_w1_cont_rel3$unhhid <- as.character(MHAS_w1_cont_rel3$unhhid)

```

```{r local1, echo=F}
vari <- MHAS_w1_cont_rel1$b10_2
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w1_cont_rel1$b10_2, missing_values = NA)
ggplot(MHAS_w1_cont_rel1, aes(x=factor(b10_2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("In the last 2 years, how often did you/your spouse contact nonresident child? (Period)") + ylab("Frequency")

vari <- MHAS_w1_cont_rel2$f28b1
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w1_cont_rel2$f28b1, missing_values = NA)
ggplot(MHAS_w1_cont_rel2, aes(x=factor(f28b1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Period contact with mother") + ylab("Frequency")

vari <- MHAS_w1_cont_rel2$f28b2
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w1_cont_rel2$f28b1, missing_values = NA)
ggplot(MHAS_w1_cont_rel2, aes(x=factor(f28b2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Period contact with mother") + ylab("Frequency")

vari <- MHAS_w1_cont_rel2$f28b3
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w1_cont_rel2$f28b1, missing_values = NA)
ggplot(MHAS_w1_cont_rel2, aes(x=factor(f28b3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Period contact with mother") + ylab("Frequency")


vari <- MHAS_w1_cont_rel3$trh6
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(MHAS_w1_cont_rel3, aes(x=factor(trh6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Relationship of household member to selected person") + ylab("Frequency")

```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  


* `week into 1`
* `trh6 from 2 to 17 into 1 `
* `9 into 998`
* `8 into 997`
* `NA into 999`

**R script:**

```{r harmo1}


# JOIN (HH)ID TOGETHER WITH CODE NUMBER OF THE RESPONDENT
MHAS_w1_cont_rel1$newid <- paste0(substr(MHAS_w1_cont_rel1$unhhid,1,nchar(MHAS_w1_cont_rel1$unhhid)),as.character(MHAS_w1_cont_rel1$b1),"0.0")


# JOIN (HH)ID TOGETHER WITH CODE NUMBER OF THE RESPONDENT
MHAS_w1_cont_rel3$newid <- paste0(substr(MHAS_w1_cont_rel3$unhhid,1,nchar(MHAS_w1_cont_rel3$unhhid)),as.character(MHAS_w1_cont_rel3$trh1),"0.0")


MHAS_w1_cont_rel <- MHAS_w1_cont_rel2

# In bnr we codify if respondent has contact (or not) with some non-resident children
MHAS_w1_cont_rel$bnr <- rep(999,length(MHAS_w1_cont_rel$id))

# Contact with some non-resident children is DK:
# sapply(MHAS_w1_cont_rel$id,function(x) 9 %in% MHAS_w1_cont_rel1$b10_2[which(MHAS_w1_cont_rel1$newid==x)])
MHAS_w1_cont_rel$bnr[which(sapply(MHAS_w1_cont_rel$id,function(x) 9 %in% MHAS_w1_cont_rel1$b10_2[which(MHAS_w1_cont_rel1$newid==x)]))] <- 9
# Contact with some non-resident children is RF:
# sapply(MHAS_w1_cont_rel$id,function(x) 8 %in% MHAS_w1_cont_rel1$b10_2[which(MHAS_w1_cont_rel1$newid==x)])
MHAS_w1_cont_rel$bnr[which(sapply(MHAS_w1_cont_rel$id,function(x) 8 %in% MHAS_w1_cont_rel1$b10_2[which(MHAS_w1_cont_rel1$newid==x)]))] <- 8
# Contact with some non-resident child is weekly:
#sapply(MHAS_w1_cont_rel$id,function(x) 1 %in% MHAS_w1_cont_rel1$b10_2[which(MHAS_w1_cont_rel1$newid==x)])
MHAS_w1_cont_rel$bnr[which(sapply(MHAS_w1_cont_rel$id,function(x) 1 %in% MHAS_w1_cont_rel1$b10_2[which(MHAS_w1_cont_rel1$newid==x)]))] <- 1
# Contact with all non-resident children is less than weekly:
#sapply(MHAS_w1_cont_rel$id, function(x)  sum(!HAS_w1_cont_rel1$b10_2[which(MHAS_w1_cont_rel1$newid==x)] %in% c(2,3,4)) == 0 )
MHAS_w1_cont_rel$bnr[which(sapply(MHAS_w1_cont_rel$id, function(x)  sum(!MHAS_w1_cont_rel1$b10_2[which(MHAS_w1_cont_rel1$newid==x)] %in% c(2,3,4)) == 0 ))] <- 0

# In trh we codify if some household habitual resident is relative of the respondent
MHAS_w1_cont_rel$trh <- rep(999,length(MHAS_w1_cont_rel$id))

# Some habitual household resident is relative
# sapply(MHAS_w1_cont_rel$id, function(x) length(intersect(2:17,MHAS_w1_cont_rel3$trh6[which(MHAS_w1_cont_rel3$newid==x)]))>=1)
MHAS_w1_cont_rel$trh[which(sapply(MHAS_w1_cont_rel$id, function(x) length(intersect(2:17,MHAS_w1_cont_rel3$trh6[which(MHAS_w1_cont_rel3$newid==x)]))>=1))] <- 1
# None habitual household resident is relative:
# sapply(MHAS_w1_cont_rel$id, function(x)  sum(!HAS_w1_cont_rel1$trh6[which(MHAS_w1_cont_rel1$newid==x)] %in% c(0,18,66)) == 0 )
MHAS_w1_cont_rel$trh[which(sapply(MHAS_w1_cont_rel$id, function(x)  sum(!MHAS_w1_cont_rel3$trh6[which(MHAS_w1_cont_rel3$newid==x)] %in% c(0,18,66)) == 0 ))] <- 0




MHAS_ds_w1 <- tibble(id=MHAS_w1_cont_rel$id)
MHAS_ds_w1$cont_rel <- rep(0,length(MHAS_ds_w1$id))
MHAS_ds_w1$cont_rel[which(is.na(MHAS_w1_cont_rel$f28b1) & is.na(MHAS_w1_cont_rel$f28b2) & is.na(MHAS_w1_cont_rel$f28b3) & MHAS_w1_cont_rel$bnr==999 & MHAS_w1_cont_rel$trh==999)] <- 999


MHAS_ds_w1$cont_rel[which(MHAS_w1_cont_rel$f28b1==8 | MHAS_w1_cont_rel$f28b2==8 | MHAS_w1_cont_rel$f28b3==8 | MHAS_w1_cont_rel$bnr==8)] <- 997
MHAS_ds_w1$cont_rel[which(MHAS_w1_cont_rel$f28b1==9 | MHAS_w1_cont_rel$f28b2==9 | MHAS_w1_cont_rel$f28b3==9 | MHAS_w1_cont_rel$bnr==9)] <- 998
MHAS_ds_w1$cont_rel[which(MHAS_w1_cont_rel$f28b1==1 | MHAS_w1_cont_rel$f28b2==1 | MHAS_w1_cont_rel$f28b3==1 | MHAS_w1_cont_rel$bnr==1 | MHAS_w1_cont_rel$trh==1)] <- 1



```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- MHAS_ds_w1$cont_rel
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_ds_w1$cont_rel, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w1, aes(x=factor(cont_rel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are any form of contact ( face-to-face/phone/mail/Internet communicators) with family members/relatives frequent?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}

```




### Wave 2

#### Study-specific variable description


| **Name** |`f32_1b`|`f32_2b`|`f32_3b`|
|-|-|-|-|
| **Label** |`Frequency of contact with mother - period`|`Frequency of contact with father - period`|`Frequency of contact with parents - period`|
| **Table name** |`MHAS_2003`|`MHAS_2003`|`MHAS_2003`|
| **Categries** |`1 = week`<br/>`2 = month`<br/>`3 = year`<br/>`4 = less than once a year`<br/>`5 = never`|`1 = week`<br/>`2 = month`<br/>`3 = year`<br/>`4 = less than once a year`<br/>`5 = never`|`1 = week`<br/>`2 = month`<br/>`3 = year`<br/>`4 = less than once a year`<br/>`5 = never`|
| **Missings** |`8 = RF`<br/>`9 = DK`|`8 = RF`<br/>`9 = DK`|`8 = RF`<br/>`9 = DK`|
| **Description** |  |  |  |


| **Name** |`trh9`|`trh1`|`cunicah`|
|-|-|-|-|
| **Label** |`Relationship of household member to selected person`|`Respondent's Code`|`Unique Household ID - 2001`|
| **Table name** |`sect_trh`|`sect_trh`|`sect_trh`|
| **Categries** |`02 = child`<br/>`03 = step child`<br/>`04 = adopted child`<br/>`05 = foster child`<br/>`06 = mother/father`<br/>`07 = parent-in-law`<br/>`08 = grandparent`<br/>`09 = grandchild`<br/>`10 = great-grandchild`<br/>`11 = great-grandchild`<br/>`12 = brother/sister, step B/S`<br/>`13 = brother/sister-in-law/cousin`<br/>`14 = ancle/aunt`<br/>`15 = nephew/niece`<br/>`16 = other relative`<br/>`17 = non-relative`<br/>`66 = without spouse`|`1 = Sampled person`<br/>`2 = Spouse of the sampled person in 2001`<br/>`3 = New spouse of the sampled person`<br/>`4 = New spouse of the selected person’s spouse`<br/> `103-121 = Other resident`<br/>`201-219;666 = Other, non-resident`|`text`|
| **Missings** |  |  |  |
| **Description** |  |  |  |




```{r assign2, echo=F}

opal.assign.table.tibble(o, 'MHAS_w2_cont_rel','Mexican Health Aging Study.MHAS_2003', variables=list('f32_1b','f32_2b','f32_3b'), missings = TRUE)
MHAS_w2_cont_rel <- opal.execute(o,'MHAS_w2_cont_rel')

opal.assign.table.tibble(o, 'MHAS_w2_cont_rel1','Mexican Health Aging Study.sect_trh_2003', variables=list('trh9','trh1','cunicah'), missings = TRUE)
MHAS_w2_cont_rel1 <- opal.execute(o,'MHAS_w2_cont_rel1')

```

```{r local2, echo=F}

vari <- MHAS_w2_cont_rel$f32_1b
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w2_cont_rel$f32_1b, missing_values = NA)
ggplot(MHAS_w2_cont_rel, aes(x=factor(f32_1b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of contact with mother - period") + ylab("Frequency")

vari <- MHAS_w2_cont_rel$f32_2b
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w2_cont_rel$f32_1b, missing_values = NA)
ggplot(MHAS_w2_cont_rel, aes(x=factor(f32_2b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of contact with father - period") + ylab("Frequency")

vari <- MHAS_w2_cont_rel$f32_3b
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w2_cont_rel$f32_1b, missing_values = NA)
ggplot(MHAS_w2_cont_rel, aes(x=factor(f32_3b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of contact with parents - period") + ylab("Frequency")

vari <- MHAS_w2_cont_rel1$trh9
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(MHAS_w2_cont_rel1, aes(x=factor(trh9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `week into 1`
* `NA into 999`

**R script:**

```{r harmo2}


# To get understanding of the relation among trh1, acthog, cunicah and the id, one has to take into account the meaning of trh1 (study document 'Interviewer Manual (2003)') the meaning of acthog, cunicah and their relation with the id (study document 'Data File Description'), and the possible categories for acthog (https://g2aging.org/?section=item&itemid=320156):

# 00. Neither separation nor death; no new spouse
# 01. Neither separation nor death; new spouse
# 10. Had a separation and contains sampled resp. 2001, no new spouse
# 11. Had a separation and contains sampled resp. 2001, new spouse
# 20. Had a separation and contains spouse 2001, no new spouse
# 21. Had a separation and contains spouse 2001, new spouse
# 30. One 2001 respondent died, no new spouse
# 31. One 2001 respondent died, new spouse

MHAS_w2_cont_rel1$tid <- car::recode(MHAS_w2_cont_rel1$trh1, "1=10;2=20;3=11;4=21;103:hi=NA")
MHAS_w2_cont_rel1$cunicah <- as.character(MHAS_w2_cont_rel1$cunicah)

# JOIN (HH)ID TOGETHER WITH CODE NUMBER OF THE RESPONDENT
MHAS_w2_cont_rel1$newid <- paste0(substr(MHAS_w2_cont_rel1$cunicah,1,nchar(MHAS_w2_cont_rel1$cunicah)),as.character(MHAS_w2_cont_rel1$tid),".0")



# In trh we codify if some household habitual resident is relative of the respondent
MHAS_w2_cont_rel$trh <- rep(999,length(MHAS_w2_cont_rel$id))

# Some habitual household resident is relative
MHAS_w2_cont_rel$trh[which(sapply(MHAS_w2_cont_rel$id, function(x) length(intersect(2:16,MHAS_w2_cont_rel1$trh9[which(MHAS_w2_cont_rel1$newid==x)]))>=1))] <- 1
# None habitual household resident is relative:
MHAS_w2_cont_rel$trh[which(sapply(MHAS_w2_cont_rel$id, function(x)  sum(!MHAS_w2_cont_rel1$trh9[which(MHAS_w2_cont_rel1$newid==x)] %in% c(17,66)) == 0 ))] <- 0

MHAS_ds_w2 <- tibble(id=MHAS_w2_cont_rel$id)
MHAS_ds_w2$cont_rel <- rep(0,length(MHAS_ds_w2$id))
MHAS_ds_w2$cont_rel[which(is.na(MHAS_w2_cont_rel$f32_1b) & is.na(MHAS_w2_cont_rel$f32_2b) & is.na(MHAS_w2_cont_rel$f32_3b) & MHAS_w2_cont_rel$trh==999)] <- 999
MHAS_ds_w2$cont_rel[which(MHAS_w2_cont_rel$f32_1b==8 | MHAS_w2_cont_rel$f32_2b==8 | MHAS_w2_cont_rel$f32_3b==8)] <- 997
MHAS_ds_w2$cont_rel[which(MHAS_w2_cont_rel$f32_1b==9 | MHAS_w2_cont_rel$f32_2b==9 | MHAS_w2_cont_rel$f32_3b==9)] <- 998
MHAS_ds_w2$cont_rel[which(MHAS_w2_cont_rel$f32_1b==1 | MHAS_w2_cont_rel$f32_2b==1 | MHAS_w2_cont_rel$f32_3b==1 | MHAS_w2_cont_rel$trh==1)] <- 1


```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- MHAS_ds_w2$cont_rel
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(MHAS_ds_w2, aes(x=factor(cont_rel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are any form of contact ( face-to-face/phone/mail/Internet communicators) with family members/relatives frequent?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}

```



### Wave 3

#### Study-specific variable description


| **Name** |`f32_1_2_12`|`f32_2_2_12`|`f32_3_2_12`|`subhog_12`|`cunicah`|
|-|-|-|-|-|-|
| **Label** |`Last 2 years: respondent's period to report contact with mother`|`Last 2 years: respondent's period to report contact with father`|`Last 2 years: respondent's period to report contact with parents`|`2012 sub-household identifier`|`Clave Unica del Hogar (=unhhid)`|
| **Table name** |`MHAS_2012_new`|`MHAS_2012_new`|`MHAS_2012_new`|`MHAS_2012_new`|`MHAS_2012_new`|
| **Categries** |`1 = week`<br/>`2 = month`<br/>`3 = year`<br/>`4 = less than once a year`<br/>`5 = never`|`1 = week`<br/>`2 = month`<br/>`3 = year`<br/>`4 = less than once a year`<br/>`5 = never`|`1 = week`<br/>`2 = month`<br/>`3 = year`<br/>`4 = less than once a year`<br/>`5 = never`|`BASELINE HOUSEHOLD`<br/>`00 For all households that are new sample (in their baseline year)`<br/>`NO CHANGES IN THE HOUSEHOLD`<br/>`01 The household contains an individual NP = 010 (first selected subject that entered the sample)`<br/>`02 The household contains an individual NP=020 (subject in this household that entered to the sample first)`<br/>`CHANGES IN THE HOUSEHOLD`<br/>`11 The new household contains an individual NP=010 (subject in this new household that entered to the sample first)`<br/>`12 The new household contains an individual NP=020 (subject in this new household that entered to the sample first)`<br/>`13 The new household contains an individual NP=011 (subject in this new household that entered to the sample first)`<br/>`14 The new household contains an individual NP=021 (subject in this new household that entered to the sample first)`<br/>`RE-UNION`<br/>`70 Two individuals (NP=010 y NP=020) part of the study, they were together, separated, and got back together`<br/>`71 Two individuals, from the family of 10, they were together, separated, and got back together`|`text`|
| **Missings** |`8 = RF`<br/>`9 = DK`|`8 = RF`<br/>`9 = DK`|`8 = RF`<br/>`9 = DK`|`31 The deceased is NP=010`<br/>`32 The deceased is NP=020`<br/>`33 The deceased is NP=011`<br/>`34 The deceased is NP=021`<br/>`77 To the individuals not contacted (whole household)`|  |
| **Description** |  |  |  |  |  |




| **Name** |`trh9_12`|`subhog_12`|`cunicah`|
|-|-|-|-|
| **Label** |`Resident's relationship to respondent`|`2012 sub-household identifier`|`Clave Unica del Hogar (=unhhid)`|
| **Table name** |`sect_trh_follow_up_2012`|`sect_trh_follow_up_2012`|`sect_trh_follow_up_2012`|
| **Categries** |`02 = child`<br/>`03 = step child`<br/>`04 = adopted child`<br/>`05 = foster child`<br/>`06 = mother/father`<br/>`07 = parent-in-law`<br/>`08 = grandparent`<br/>`09 = grandchild`<br/>`10 = great-grandchild`<br/>`11 = great-grandchild`<br/>`12 = brother/sister, step B/S`<br/>`13 = brother/sister-in-law/cousin`<br/>`14 = ancle/aunt`<br/>`15 = nephew/niece`<br/>`16 = other relative`<br/>`17 = non-relative`|`BASELINE HOUSEHOLD`<br/>`00 For all households that are new sample (in their baseline year)`<br/>`NO CHANGES IN THE HOUSEHOLD`<br/>`01 The household contains an individual NP = 010 (first selected subject that entered the sample)`<br/>`02 The household contains an individual NP=020 (subject in this household that entered to the sample first)`<br/>`CHANGES IN THE HOUSEHOLD`<br/>`11 The new household contains an individual NP=010 (subject in this new household that entered to the sample first)`<br/>`12 The new household contains an individual NP=020 (subject in this new household that entered to the sample first)`<br/>`13 The new household contains an individual NP=011 (subject in this new household that entered to the sample first)`<br/>`14 The new household contains an individual NP=021 (subject in this new household that entered to the sample first)`<br/>`RE-UNION`<br/>`70 Two individuals (NP=010 y NP=020) part of the study, they were together, separated, and got back together`<br/>`71 Two individuals, from the family of 10, they were together, separated, and got back together`|`text`|
| **Missings** |  |`31 The deceased is NP=010`<br/>`32 The deceased is NP=020`<br/>`33 The deceased is NP=011`<br/>`34 The deceased is NP=021`<br/>`77 To the individuals not contacted (whole household)`|  |
| **Description** |  |  |  |


| **Name** |`ntrh6_12`|`subhog_12`|`cunicah`|
|-|-|-|-|
| **Label** |`Resident's relationship to respondent`|`2012 sub-household identifier`|`Clave Unica del Hogar (=unhhid)`|
| **Table name** |`sect_trh_new_sample_2012`|`sect_trh_new_sample_2012`|`sect_trh_new_sample_2012`|
| **Categries** |`03 = child`<br/>`04 = stepchild`<br/>`05 = adoptive child`<br/>`06 = foster child`<br/>`07 = parent`<br/>`08 = parent-in-law`<br/>`09 = grandparent`<br/>`10 = grandchild`<br/>`11 = great-grandchild`<br/>`12 = child-in-law`<br/>`13 = sibling/stepsibling`<br/>`14 = sibling-in-law/cousin`<br/>`15 = ancle/aunt`<br/>`16 = nephew/niece`<br/>`17 = other relative`<br/>`18 = non-relative`|`BASELINE HOUSEHOLD`<br/>`00 For all households that are new sample (in their baseline year)`<br/>`NO CHANGES IN THE HOUSEHOLD`<br/>`01 The household contains an individual NP = 010 (first selected subject that entered the sample)`<br/>`02 The household contains an individual NP=020 (subject in this household that entered to the sample first)`<br/>`CHANGES IN THE HOUSEHOLD`<br/>`11 The new household contains an individual NP=010 (subject in this new household that entered to the sample first)`<br/>`12 The new household contains an individual NP=020 (subject in this new household that entered to the sample first)`<br/>`13 The new household contains an individual NP=011 (subject in this new household that entered to the sample first)`<br/>`14 The new household contains an individual NP=021 (subject in this new household that entered to the sample first)`<br/>`RE-UNION`<br/>`70 Two individuals (NP=010 y NP=020) part of the study, they were together, separated, and got back together`<br/>`71 Two individuals, from the family of 10, they were together, separated, and got back together`|`text`|
| **Missings** |  |`31 The deceased is NP=010`<br/>`32 The deceased is NP=020`<br/>`33 The deceased is NP=011`<br/>`34 The deceased is NP=021`<br/>`77 To the individuals not contacted (whole household)`|  |
| **Description** |  |  |  |



```{r assign3, echo=F}

opal.assign.table.tibble(o, 'MHAS_w3_cont_rel','Mexican Health Aging Study.MHAS_2012_new', variables=list('f32_1_2_12','f32_2_2_12','f32_3_2_12','subhog_12','cunicah'), missings = TRUE)
MHAS_w3_cont_rel <- opal.execute(o,'MHAS_w3_cont_rel')
MHAS_w3_cont_rel$cunicah <- as.character(MHAS_w3_cont_rel$cunicah)

# 'cunicah' = substr(MHAS_w3_cont_rel$id,1,nchar(MHAS_w3_cont_rel$id)-4)
# 'tid' = substr(MHAS_w3_cont_rel$id,nchar(MHAS_w3_cont_rel$id)-3,nchar(MHAS_w3_cont_rel$id)-2)

opal.assign.table.tibble(o, 'MHAS_w3_cont_rel1','Mexican Health Aging Study.sect_trh_follow_up_2012', variables=list('trh9_12','subhog_12','cunicah'), missings = TRUE)
MHAS_w3_cont_rel1 <- opal.execute(o,'MHAS_w3_cont_rel1')
MHAS_w3_cont_rel1$cunicah <- as.character(MHAS_w3_cont_rel1$cunicah)

opal.assign.table.tibble(o, 'MHAS_w3_cont_rel2','Mexican Health Aging Study.sect_trh_new_sample_2012',variables=list('ntrh6_12','subhog_12','cunicah'), missings = TRUE)
MHAS_w3_cont_rel2 <- opal.execute(o,'MHAS_w3_cont_rel2')
MHAS_w3_cont_rel2$cunicah <- as.character(MHAS_w3_cont_rel2$cunicah)


```

```{r local3, echo=F}

vari <- MHAS_w3_cont_rel$f32_1_2_12
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w3_cont_rel$f32_1_2_12, missing_values = NA)
ggplot(MHAS_w3_cont_rel, aes(x=factor(f32_1_2_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Last 2 years: respondent's period to report contact with mother") + ylab("Frequency")


vari <- MHAS_w3_cont_rel$f32_2_2_12
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w3_cont_rel$f32_1_2_12, missing_values = NA)
ggplot(MHAS_w3_cont_rel, aes(x=factor(f32_2_2_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Last 2 years: respondent's period to report contact with father") + ylab("Frequency")


vari <- MHAS_w3_cont_rel$f32_3_2_12
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w3_cont_rel$f32_1_2_12, missing_values = NA)
ggplot(MHAS_w3_cont_rel, aes(x=factor(f32_3_2_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Last 2 years: respondent's period to report contact with parents") + ylab("Frequency")


vari <- MHAS_w3_cont_rel1$trh9_12
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w3_cont_rel$f32_1_2_12, missing_values = NA)
ggplot(MHAS_w3_cont_rel1, aes(x=factor(trh9_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Resident's relationship to respondent") + ylab("Frequency")


vari <- MHAS_w3_cont_rel2$ntrh6_12
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_w3_cont_rel$f32_1_2_12, missing_values = NA)
ggplot(MHAS_w3_cont_rel2, aes(x=factor(ntrh6_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Resident's relationship to respondent") + ylab("Frequency")

```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  
  
* `week into 1`
* `if trh9_12 in 2:16 or ntrh6_12 in 3:17 then 1`
* `NA into 999`

**R script:**
  
```{r harmo3}

# In futrh we codify if some household habitual resident from the follow up sample is relative of the respondent
MHAS_w3_cont_rel$futrh <- rep(999,length(MHAS_w3_cont_rel$id))

# Some habitual household resident is relative
MHAS_w3_cont_rel$futrh[which(sapply(1:length(MHAS_w3_cont_rel$id), function(x) length(intersect(2:16,MHAS_w3_cont_rel1$trh9_12[which(MHAS_w3_cont_rel1$cunicah==MHAS_w3_cont_rel$cunicah[x] & MHAS_w3_cont_rel1$subhog_12==MHAS_w3_cont_rel$subhog_12[x])]))>=1))] <- 1
# None habitual household resident is relative:
MHAS_w3_cont_rel$futrh[which(sapply(1:length(MHAS_w3_cont_rel$id), function(x)  sum(!MHAS_w3_cont_rel1$trh9_12[which(MHAS_w3_cont_rel1$cunicah==MHAS_w3_cont_rel$cunicah[x] & MHAS_w3_cont_rel1$subhog_12==MHAS_w3_cont_rel$subhog_12[x])] %in% c(17)) == 0 ))] <- 0


# In nstrh we codify if some household habitual resident from the new sample is relative of the respondent
MHAS_w3_cont_rel$nstrh <- rep(999,length(MHAS_w3_cont_rel$id))

# Some habitual household resident is relative
MHAS_w3_cont_rel$nstrh[which(sapply(1:length(MHAS_w3_cont_rel$id), function(x) length(intersect(3:17,MHAS_w3_cont_rel2$ntrh6_12[which(MHAS_w3_cont_rel2$cunicah==MHAS_w3_cont_rel$cunicah[x] & MHAS_w3_cont_rel2$subhog_12==MHAS_w3_cont_rel$subhog_12[x])]))>=1))] <- 1
# None habitual household resident is relative:
MHAS_w3_cont_rel$nstrh[which(sapply(1:length(MHAS_w3_cont_rel$id), function(x)  sum(!MHAS_w3_cont_rel2$ntrh6_12[which(MHAS_w3_cont_rel2$cunicah==MHAS_w3_cont_rel$cunicah[x] & MHAS_w3_cont_rel2$subhog_12==MHAS_w3_cont_rel$subhog_12[x])] %in% c(18)) == 0 ))] <- 0


MHAS_ds_w3 <- tibble(id=MHAS_w3_cont_rel$id)

MHAS_ds_w3$cont_rel <- rep(0,length(MHAS_ds_w3$id))

MHAS_ds_w3$cont_rel[which(is.na(MHAS_w3_cont_rel$f32_1_2_12) & is.na(MHAS_w3_cont_rel$f32_2_2_12) & is.na(MHAS_w3_cont_rel$f32_3_2_12) & MHAS_w3_cont_rel$futrh==999 & MHAS_w3_cont_rel$nstrh==999)] <- 999
MHAS_ds_w3$cont_rel[which(MHAS_w3_cont_rel$f32_1_2_12==8 | MHAS_w3_cont_rel$f32_2_2_12==8 | MHAS_w3_cont_rel$f32_3_2_12==8)] <- 997
MHAS_ds_w3$cont_rel[which(MHAS_w3_cont_rel$f32_1_2_12==9 | MHAS_w3_cont_rel$f32_2_2_12==9 | MHAS_w3_cont_rel$f32_3_2_12==9)] <- 998
MHAS_ds_w3$cont_rel[which(MHAS_w3_cont_rel$f32_1_2_12==1 | MHAS_w3_cont_rel$f32_2_2_12==1 | MHAS_w3_cont_rel$f32_3_2_12==1 | MHAS_w3_cont_rel$futrh==1 | MHAS_w3_cont_rel$nstrh==1)] <- 1


```


#### Statistics of the new harmonised variable

```{r descript3, echo=F}

vari <- MHAS_ds_w3$cont_rel
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_ds_w1$cont_rel, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w3, aes(x=factor(cont_rel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are any form of contact ( face-to-face/phone/mail/Internet communicators) with family members/relatives frequent?") + ylab("Frequency")

```

#### Validation
```{r crosstabulation3, echo=F}

```










```{r final, echo=F}

l.hds <- list(w1 = MHAS_ds_w1, w2 = MHAS_ds_w2, w3 = MHAS_ds_w3)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("MHAS_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

```

## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.


```{r summ}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",names(l.hds))
kable(t.hds)

dbb <- get(paste0("MHAS_m_ds_",names(l.hds)[1]))[,c("id","cont_rel")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("MHAS_m_ds_",names(l.hds)[ind]))[,c("id","cont_rel")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", names(l.hds))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb)

```


# Quality estimation
[Comments on the quality of the new harmonised variable.]


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  cont_rel <- l.hds[[index]]
  save(cont_rel, file = paste0(datafolder,names(l.hds)[index],"/cont_rel.RData"))
}

```
<!-- ########################################################## --> 



<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
