---
title: "Are any form of contact ( face-to-face/phone/mail/Internet communicators) with family members/relatives frequent (i.e. contact once a week or more often)?"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `cont_rel`
* Variable label: `Are any form of contact ( face-to-face/phone/mail/Internet communicators) with family members/relatives frequent (i.e. contact once a week or more often)?`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process


### MHAS - Wave 1

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `b10_2` **from table 'Mexican Health Aging Study.b_nores'**
* Label: `In the last 2 years, how often did you/your spouse contact nonresident child? (Period)`
* Categories:
    + `0 = never`
    + `1 = week`
    + `2 = month`
    + `3 = year`
    + `4 = less than once a year`
    + `5 = infrequently`
* Missings:
    + `8 = RF`
    + `9 = DK`
    
* Name: `f28b1` **from table 'Mexican Health Aging Study.MHAS-2001'**
* Label: `Period contact with mother`
* Categories:
    + `1 = week`
    + `2 = month`
    + `3 = year`
    + `4 = less than once a year`
    + `5 = never`
* Missings:
    + `8 = RF`
    + `9 = DK`

* Name: `f28b2` **from table 'Mexican Health Aging Study.MHAS-2001'**
* Label: `Period contact with father`
* Categories:
    + `1 = week`
    + `2 = month`
    + `3 = year`
    + `4 = less than once a year`
    + `5 = never`
* Missings:
    + `8 = RF`
    + `9 = DK`
    
* Name: `f28b3` **from table 'Mexican Health Aging Study.MHAS-2001'**
* Label: `Period contact with parents`
* Categories:
    + `1 = week`
    + `2 = month`
    + `3 = year`
    + `4 = less than once a year`
    + `5 = never`
* Missings:
    + `8 = RF`
    + `9 = DK`
    
* Name: `trh6` **from table 'Mexican Health Aging Study.sect_trh'**
* Label: `Relationship of household member to selected person`
* Categories:
    + `02 = spouse`
    + `03 = child`
    + `04 = stepchild`
    + `05 = adoptive child`
    + `06 = foster child`
    + `07 = parent`
    + `08 = parent-in-law`
    + `09 = grandparent`
    + `10 = grandchild`
    + `11 = great-grandchild`
    + `12 = child-in-law`
    + `13 = sibling/stepsibling`
    + `14 = sibling-in-law/cousin`
    + `15 = ancle/aunt`
    + `16 = nephew/niece`
    + `17 = other relative`
    + `18 = non-relative`
    + `66 = selected person died`
    + `00 = without spouse`

```{r assign1}
opal.assign.table.tibble(o, 'MHAS_w1_cont_rel1','Mexican Health Aging Study.b_nores',
                         variables=list('b10_2'), missings = TRUE)

opal.assign.table.tibble(o, 'MHAS_w1_cont_rel2','Mexican Health Aging Study.MHAS-2001',
                         variables=list('f28b1','f28b2','f28b3'), missings = TRUE)

opal.assign.table.tibble(o, 'MHAS_w1_home_rel','Mexican Health Aging Study.sect_trh',
                         variables=list('trh6'), missings = TRUE)
```

```{r local1}
MHAS_w1_cont_rel1 <- opal.execute(o,'MHAS_w1_cont_rel1')
Categorical_summary(var = MHAS_w1_cont_rel1$b10_2, missing_values = NA)
ggplot(MHAS_w1_cont_rel1, aes(x=factor(b10_2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("In the last 2 years, how often did you/your spouse contact nonresident child? (Period)") + ylab("Frequency")

MHAS_w1_cont_rel2 <- opal.execute(o,'MHAS_w1_cont_rel2')
Categorical_summary(var = MHAS_w1_cont_rel2$f28b1, missing_values = NA)
ggplot(MHAS_w1_cont_rel2, aes(x=factor(f28b1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Period contact with mother") + ylab("Frequency")

MHAS_w1_home_rel <- opal.execute(o,'MHAS_w1_home_rel')
Categorical_summary(var = MHAS_w1_home_rel$trh6, missing_values = NA)
ggplot(MHAS_w1_home_rel, aes(x=factor(trh6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Relationship of household member to selected person") + ylab("Frequency")
```
# PROBLEMS WITH IDs
```{r}
head(MHAS_w1_cont_rel1)
head(MHAS_w1_cont_rel2)
head(MHAS_w1_home_rel)

nrow(MHAS_w1_cont_rel1)
nrow(MHAS_w1_cont_rel2)
nrow(MHAS_w1_home_rel)

length(which(MHAS_w1_cont_rel2$id %in% MHAS_w1_cont_rel1$id))
length(which(MHAS_w1_home_rel$id %in% MHAS_w1_cont_rel1$id))
length(which(MHAS_w1_home_rel$id %in% MHAS_w1_cont_rel2$id))

```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `week into 1`
* `NA into 999`

R code of the ALGORITHM:

```{r harmo1}

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  colnames(new_2) <- colnames(old)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], rep_len(NA,dim(old)[2]-1))
    }
  }
  new_2 <- data.frame(new_2)
  new_22 <- data.frame(id=new_2$id, b10_2=new_2$b10_2, f28b1=new$f28b1, f28b2=new$f28b2, f28b3=new$f28b3) 
                       # id = new_2$id
                       # colname_form_OLD_table = new_2$colname_form_OLD_table 
                       # colname_form_NEW_table = new$colname_form_NEW_table
  new_22
}

# old = MHAS_w1_cont_rel1 (b10_2)
# new = MHAS_w1_cont_rel2 (f28b1,f28b2,f28b3)

MHAS_w1_cont_rel <- same_indiv(MHAS_w1_cont_rel1, MHAS_w1_cont_rel2)

MHAS_ds_w1 <- tibble(id=MHAS_w1_cont_rel$id)

MHAS_w1_cont_rel$f28b1 <- car::recode(as.vector(MHAS_w1_cont_rel$f28b1), "NA='-999'")
MHAS_w1_cont_rel$f28b2 <- car::recode(as.vector(MHAS_w1_cont_rel$f28b2), "NA='-999'")
MHAS_w1_cont_rel$f28b3 <- car::recode(as.vector(MHAS_w1_cont_rel$f28b3), "NA='-999'")
MHAS_w1_cont_rel$b10_2 <- car::recode(as.vector(MHAS_w1_cont_rel$b10_2), "NA='-999'")

MHAS_ds_w1$cont_rel <- c(NA) # I think it is required
for(i in 1:dim(MHAS_w1_cont_rel)[1]){
  if( MHAS_w1_cont_rel$f28b1[i] == 1 | MHAS_w1_cont_rel$f28b2[i] == 1 | MHAS_w1_cont_rel$f28b3[i] == 1 | MHAS_w1_cont_rel$b10_2[i] == 1 ) {
    MHAS_ds_w1$cont_rel[i] = 1 }
  else if( MHAS_w1_cont_rel$f28b1[i] == -999 & MHAS_w1_cont_rel$f28b2[i] == -999 & MHAS_w1_cont_rel$f28b3[i] == -999 & MHAS_w1_cont_rel$b10_2[i] == -999 ) {
    MHAS_ds_w1$cont_rel[i] = 999 }
  else if( !( MHAS_w1_cont_rel$f28b1[i] == 1 | MHAS_w1_cont_rel$f28b2[i] == 1 | MHAS_w1_cont_rel$f28b3[i] == 1 | MHAS_w1_cont_rel$b10_2[i] == 1 ) ) {
    MHAS_ds_w1$cont_rel[i] = 0 }
}

MHAS_ds_w1$cont_rel <- car::recode(as.vector(MHAS_ds_w1$cont_rel), "NA='999'")
MHAS_ds_w1$cont_rel <- labelled(MHAS_ds_w1$cont_rel, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1}
Categorical_summary(var = MHAS_ds_w1$cont_rel, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w1, aes(x=factor(cont_rel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are any form of contact ( face-to-face/phone/mail/Internet communicators) with family members/relatives frequent?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1}

```

#### Quality estimation
[Comments on the quality of the new harmonised variable.]




### MHAS - Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

    
* Name: `f32_1b`
* Label: `Frequency of contact with mother - period`
* Categories:
    + `1 = week`
    + `2 = month`
    + `3 = year`
    + `4 = less than once a year`
    + `5 = never`
* Missings:
    + `8 = RF`
    + `9 = DK`

* Name: `f32_2b`
* Label: `Frequency of contact with father - period`
* Categories:
    + `1 = week`
    + `2 = month`
    + `3 = year`
    + `4 = less than once a year`
    + `5 = never`
* Missings:
    + `8 = RF`
    + `9 = DK`
    
* Name: `f32_3b`
* Label: `Frequency of contact with parents - period`
* Categories:
    + `1 = week`
    + `2 = month`
    + `3 = year`
    + `4 = less than once a year`
    + `5 = never`
* Missings:
    + `8 = RF`
    + `9 = DK`
    


```{r assign2}
opal.assign.table.tibble(o, 'MHAS_w2_cont_rel','Mexican Health Aging Study.MHAS_2003',
                         variables=list('f32_1b','f32_2b','f32_3b'), missings = TRUE)
```

```{r local2}
MHAS_w2_cont_rel <- opal.execute(o,'MHAS_w2_cont_rel')
Categorical_summary(var = MHAS_w2_cont_rel$f32_1b, missing_values = NA)
ggplot(MHAS_w2_cont_rel, aes(x=factor(f32_1b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Frequency of contact with mother - period") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `week into 1`
* `NA into 999`

R code of the ALGORITHM:

```{r harmo2}
MHAS_ds_w2 <- tibble(id=MHAS_w2_cont_rel$id)

MHAS_w2_cont_rel$f32_1b <- car::recode(as.vector(MHAS_w2_cont_rel$f32_1b), "NA='-999'")
MHAS_w2_cont_rel$f32_2b <- car::recode(as.vector(MHAS_w2_cont_rel$f32_2b), "NA='-999'")
MHAS_w2_cont_rel$f32_3b <- car::recode(as.vector(MHAS_w2_cont_rel$f32_3b), "NA='-999'")

MHAS_ds_w2$cont_rel <- c(NA) # I think it is required
for(i in 1:dim(MHAS_w2_cont_rel)[1]){
  if( MHAS_w2_cont_rel$f32_1b[i] == 1 | MHAS_w2_cont_rel$f32_2b[i] == 1 | MHAS_w2_cont_rel$f32_3b[i] == 1 ) {
   MHAS_ds_w2$cont_rel[i] = 1 }
  else if( MHAS_w2_cont_rel$f32_1b[i] == -999 & MHAS_w2_cont_rel$f32_2b[i] == -999 & MHAS_w2_cont_rel$f32_3b[i] == -999 ) {
   MHAS_ds_w2$cont_rel[i] = 999 }
  else if( !( MHAS_w2_cont_rel$f32_1b[i] == 1 | MHAS_w2_cont_rel$f32_2b[i] == 1 | MHAS_w2_cont_rel$f32_3b[i] == 1 ) ) {
   MHAS_ds_w2$cont_rel[i] = 0 }
}

MHAS_ds_w2$cont_rel <- car::recode(as.vector(MHAS_ds_w2$cont_rel), "NA='999'")
MHAS_ds_w2$cont_rel <- labelled(MHAS_ds_w2$cont_rel, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2}
Categorical_summary(var = MHAS_ds_w2$cont_rel, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w2, aes(x=factor(cont_rel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are any form of contact ( face-to-face/phone/mail/Internet communicators) with family members/relatives frequent?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2}

```

#### Quality estimation
[Comments on the quality of the new harmonised variable.]



### MHAS - Wave 3

#### Study-specific variables

The study-specific variable elected to be harmonised is:
  
  
* Name: `f32_1_2_12`
* Label: `Last 2 years: respondent's period to report contact with mother`
* Categories:
    + `1 = week`
    + `2 = month`
    + `3 = year`
    + `4 = less than once a year`
    + `5 = never`
* Missings:
    + `8 = RF`
    + `9 = DK`

* Name: `f32_2_2_12`
* Label: `Last 2 years: respondent's period to report contact with father`
* Categories:
    + `1 = week`
    + `2 = month`
    + `3 = year`
    + `4 = less than once a year`
    + `5 = never`
* Missings:
    + `8 = RF`
    + `9 = DK`

* Name: `f32_3_2_12`
* Label: `Last 2 years: respondent's period to report contact with father`
* Categories:
    + `1 = week`
    + `2 = month`
    + `3 = year`
    + `4 = less than once a year`
    + `5 = never`
* Missings:
    + `8 = RF`
    + `9 = DK`



```{r assign3}
opal.assign.table.tibble(o, 'MHAS_w3_cont_rel','Mexican Health Aging Study.MHAS_2012_new',
                         variables=list('f32_1_2_12','f32_2_2_12','f32_3_2_12'), missings = TRUE)
```

```{r local3}
MHAS_w3_cont_rel <- opal.execute(o,'MHAS_w3_cont_rel')
Categorical_summary(var = MHAS_w3_cont_rel$f32_1_2_12, missing_values = NA)
ggplot(MHAS_w3_cont_rel, aes(x=factor(f32_1_2_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Last 2 years: respondent's period to report contact with mother") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  
  
* `week into 1`
* `NA into 999`

R code of the ALGORITHM:
  
```{r harmo3}
MHAS_ds_w3 <- tibble(id=MHAS_w3_cont_rel$id)

MHAS_w3_cont_rel$f32_1_2_12 <- car::recode(as.vector(MHAS_w3_cont_rel$f32_1_2_12), "NA='-999'")
MHAS_w3_cont_rel$f32_2_2_12 <- car::recode(as.vector(MHAS_w3_cont_rel$f32_2_2_12), "NA='-999'")
MHAS_w3_cont_rel$f32_3_2_12 <- car::recode(as.vector(MHAS_w3_cont_rel$f32_3_2_12), "NA='-999'")


MHAS_ds_w3$cont_rel <- c(NA) # I think it is required
for(i in 1:dim(MHAS_w3_cont_rel)[1]){
  if( MHAS_w3_cont_rel$f32_1_2_12[i] == 1 | MHAS_w3_cont_rel$f32_2_2_12[i] == 1 | MHAS_w3_cont_rel$f32_3_2_12[i] == 1 ) {
    MHAS_ds_w3$cont_rel[i] = 1 }
  else if( MHAS_w3_cont_rel$f32_1_2_12[i] == -999 & MHAS_w3_cont_rel$f32_2_2_12[i] == -999 & MHAS_w3_cont_rel$f32_3_2_12[i] == -999 ) {
    MHAS_ds_w3$cont_rel[i] = 999 }
  else if( !( MHAS_w3_cont_rel$f32_1_2_12[i] == 1 | MHAS_w3_cont_rel$f32_2_2_12[i] == 1 | MHAS_w3_cont_rel$f32_3_2_12[i] == 1 ) ) {
    MHAS_ds_w3$cont_rel[i] = 0 }
}

MHAS_ds_w3$cont_rel <- car::recode(as.vector(MHAS_ds_w3$cont_rel), "NA='999'")
MHAS_ds_w3$cont_rel <- labelled(MHAS_ds_w3$cont_rel, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3}
Categorical_summary(var = MHAS_ds_w3$cont_rel, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w3, aes(x=factor(cont_rel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are any form of contact ( face-to-face/phone/mail/Internet communicators) with family members/relatives frequent?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3}

```

#### Quality estimation
[Comments on the quality of the new harmonised variable.]


