---
title: "Instrumental support"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/inst_supDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/inst_supDS.R')
```


<!-- ########################################################## --> 

# Data process

## Mexico

### Wave 1

Not found.


### Wave 2



| **Name** |`g29`|
|-|-|
| **Label**|`Have neighbors or friends can count on for help`|
| **Table name** |`g_house_2003`|
| **Categories** |`1 = Yes`<br/>`2 = No`|
| **Missings**  |`8 = Doesn't Answer`<br/>`9 = Doesn't Know`|
| **Description** |  |

```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'MHAS_w2','Mexican Health Aging Study.g_house_2003',variables=list('g29','g32','cunicah','acthog'), missings = TRUE)
MHAS_w2 <- opal.execute(o,'MHAS_w2')

# To get understanding of the relation among g29, acthog, cunicah and the id, one has to take into account the meaning of g32 (study document 'Interviewer Manual (2003)') the meaning of acthog, cunicah and their relation with the id (study document 'Data File Description'), and the possible categories for acthog (https://g2aging.org/?section=item&itemid=320156):

# 00. Neither separation nor death; no new spouse
# 01. Neither separation nor death; new spouse
# 10. Had a separation and contains sampled resp. 2001, no new spouse
# 11. Had a separation and contains sampled resp. 2001, new spouse
# 20. Had a separation and contains spouse 2001, no new spouse
# 21. Had a separation and contains spouse 2001, new spouse
# 30. One 2001 respondent died, no new spouse
# 31. One 2001 respondent died, new spouse

MHAS_w2$cunicah <- as.character(MHAS_w2$cunicah)
MHAS_w2$g320 <- 10*MHAS_w2$g32
MHAS_w2$g320[which(MHAS_w2$g32==3)] <- 11
MHAS_w2$g320[which(MHAS_w2$g32==3 & MHAS_w2$acthog==21)] <- 21
# JOIN (HH)ID TOGETHER WITH CODE NUMBER OF THE RESPONDENT
MHAS_w2$newid <- paste0(substr(MHAS_w2$cunicah,1,nchar(MHAS_w2$cunicah)),as.character(MHAS_w2$g320),".0")


opal.assign.table.tibble(o, 'MHAS_w2_id','Mexican Health Aging Study.MHAS_2003',variables=list('cunicah','acthog'), missings = T)
MHAS_w2_id <- opal.execute(o,'MHAS_w2_id')
#MHAS_w2_id$cunicah <- paste0(as.character(MHAS_w2_id$cunicah),".0")


MHAS_w2 <- left_join(MHAS_w2_id,MHAS_w2,by=c("id"="newid"))

```


```{r local w2, echo=F}

vbl <- MHAS_w2$g29
vbl_miss <- c(8,9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = 'g29`') 
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Type of missing")
ggplot(MHAS_w2, aes(x=factor(g29))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```



#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:


* `1 -> 1`
* `2 -> 0`
* `8 -> 995`
* `9 -> 998`
* `NA into 999`


**R script:**

```{r harmo w2}

MHAS_ds_w2 <- tibble(id=MHAS_w2$id)
MHAS_ds_w2$inst_sup <- car::recode(MHAS_w2$g29, "1=1; 2=0; 8=995; 9=998; NA=999")

```


#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}

vari <- MHAS_ds_w2$inst_sup
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w2, aes(x=factor(inst_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}

```



### Wave 3



| **Name** |`g31_12`|
|-|-|
| **Label**|`Do you have neighbors or friends you can count on for daily activities, such as bringing food if you are sick, or bringing you something from the store?`|
| **Table name** |`sect_g_j_k_sa_2012`|
| **Categories** |`1 = Yes`<br/>`2 = No`|
| **Missings**  |`8 = Doesn't Answer`<br/>`9 = Doesn't Know`|
| **Description** |  |


<!--By contrast with `subhog_01`, `subhog_03`, `subhog_12` and `id`, the values `103, 104, 105, 107, 108, 109, 202` of `g34_12` may be generically imputed to `10`. The value `110` seems to be `20`. The other values could be `10` or in some cases `20`.-->

```{r assign w3, echo=F}

opal.assign.table.tibble(o, 'MHAS_w3','Mexican Health Aging Study.sect_g_j_k_sa_2012',variables=list('g31_12','g34_12'), missings = TRUE)
MHAS_w3 <- opal.execute(o,'MHAS_w3')
MHAS_w3$aux <- car::recode(MHAS_w3$g34_12, "103:999=NA")
# JOIN (HH)ID TOGETHER WITH REGISTRATION NUMBER OF THE RESPONDENT
MHAS_w3$newid <- paste0(substr(MHAS_w3$id,1,nchar(MHAS_w3$id)-2),as.character(MHAS_w3$aux),".0")
# Remove duplicated rows
MHAS_w3 <- MHAS_w3[-which(duplicated(MHAS_w3)),]

opal.assign.table.tibble(o, 'MHAS_w3_id','Mexican Health Aging Study.MHAS_2012_new',variables=list('cunicah'), missings = T)
MHAS_w3_id <- opal.execute(o,'MHAS_w3_id')
MHAS_w3_id$cunicah <- paste0(as.character(MHAS_w3_id$cunicah),".0")

MHAS_w3 <- left_join(MHAS_w3_id,MHAS_w3,by=c("id"="newid"))

```


```{r local w3, echo=F}

vbl <- MHAS_w3$g31_12
vbl_miss <- c(8,9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = 'g31_12`') 
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Type of missing")
ggplot(MHAS_w3, aes(x=factor(g31_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```



#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:


* `1 -> 1`
* `2 -> 0`
* `8 -> 995`
* `9 -> 998`
* `NA into 999`


**R script:**

```{r harmo w3}

MHAS_ds_w3 <- tibble(id=MHAS_w3$id)
MHAS_ds_w3$inst_sup <- car::recode(MHAS_w3$g31_12, "1=1; 2=0; 8=995; 9=998; NA=999")

```


#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}

vari <- MHAS_ds_w3$inst_sup
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w3, aes(x=factor(inst_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w3, echo=F}

```




```{r final, echo=F}

l.hds <- list(w2 = MHAS_ds_w2, w3 = MHAS_ds_w3)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("MHAS_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

```

## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.


```{r summ}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",names(l.hds))
kable(t.hds)

dbb <- get(paste0("MHAS_m_ds_",names(l.hds)[1]))[,c("id","inst_sup")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("MHAS_m_ds_",names(l.hds)[ind]))[,c("id","inst_sup")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", names(l.hds))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb)

```



<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  inst_sup <- l.hds[[index]]
  save(inst_sup, file = paste0(datafolder,names(l.hds)[index],"/inst_sup.RData"))
}

```
<!-- ########################################################## --> 


# Quality estimation


```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
