---
title: "Mobility - Extending arms"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `mob_arm`
* Variable label: `Difficulty for reaching / extending arms`
* Variable description: `Difficulty for reaching / extending arms`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


# Data process

## Mexico



### Wave 1 

#### Study-specific variable description




| **Name** | `h9`|
|-|-|
| **Label** | `EXTENDING ARMS` |
| **Table name** |`MHAS-2001`|
| **Categories** |`1 = Yes; 2 = No; 6 = Can't do`|
| **Missings** |`7 = Doesn't do; 8 = Doesn't answer; 9 = Doesn't know; NA`|
| **Description** |  |


```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'MHAS_w1_mob_arm','Mexican Health Aging Study.MHAS-2001', variables=list('h9'), missings = TRUE)
```

```{r local w1, echo=F}
MHAS_w1_mob_arm <- opal.execute(o,'MHAS_w1_mob_arm')
vari <- MHAS_w1_mob_arm$h9
kable(Categorical_summary(vari, missing_values = c(7,8,9))[3], caption = "h9")
kable(Categorical_summary(vari, missing_values = c(7,8,9))[1], caption = "Category")
ggplot(MHAS_w1_mob_arm, aes(x=factor(h9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Extending arms") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 1`
* `6 Can't do into 0`
* `7 Doesn't do into 994`
* `8 Doesn't answer into 995`
* `9 Doesn't know into 998`
* `NA into 999`

**R script:**
```{r harmo w1}
MHAS_ds_w1 <- tibble(id=MHAS_w1_mob_arm$id)
MHAS_ds_w1$mob_arm <- car::recode(MHAS_w1_mob_arm$h9, "1 = '0';2 = '1';NA = '999';6 = '0';7 = '994';8 = '995';9 = '998' ")
MHAS_ds_w1$mob_arm <- labelled(MHAS_ds_w1$mob_arm, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vari <- MHAS_ds_w1$mob_arm
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_arm")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(MHAS_ds_w1, aes(x=factor(mob_arm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Extending arms") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(MHAS_ds_w1$mob_arm)
X<-table(MHAS_w1_mob_arm$h9)
BeforeH <- c(sum(X[c(1,3)]),X[c(2,4,5,6)],sum(is.na(MHAS_w1_mob_arm$h9)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,6->0","2->1","7->994","8->995","9->998","NA->999") 
kable(C)
```






```{r importOPAL w1, echo=FALSE}

label(MHAS_ds_w1$mob_arm) <- "Difficulty for reaching / extending arms"
#opal.assign.data(o, 'MHAS_ds_w1', MHAS_ds_w1)
#opal.symbol_import(o,'MHAS_ds_w1', project='_Athlos_Harm_Dataset')
mob_arm <- MHAS_ds_w1
save(mob_arm, file = "../RData/w1/mob_arm.RData")

MHAS_m_ds_w1 <- MHAS_ds_w1
MHAS_m_ds_w1$mob_arm <- car::recode(MHAS_m_ds_w1$mob_arm, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'MHAS_m_ds_w1', MHAS_m_ds_w1)
#opal.symbol_import(o,'MHAS_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2

#### Study-specific variable description




| **Name** | `h9`|
|-|-|
| **Label** | `Health problems-trouble lifting arms` |
| **Table name** |`MHAS_2003`|
| **Categories** |`1 = Yes; 2 = No; 6 = Can't do`|
| **Missings** |`7 = Doesn't do; 8 = Doesn't answer; NA`|
| **Description** |  |



```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'MHAS_w2_mob_arm','Mexican Health Aging Study.MHAS_2003', variables=list('h9'), missings = TRUE)
```

```{r local w2, echo=F}
MHAS_w2_mob_arm <- opal.execute(o,'MHAS_w2_mob_arm')
vari <- MHAS_w2_mob_arm$h9
kable(Categorical_summary(vari, missing_values = c(7,8,9))[3], caption = "h9")
kable(Categorical_summary(vari, missing_values = c(7,8,9))[1], caption = "Category")
ggplot(MHAS_w2_mob_arm, aes(x=factor(h9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Extending arms") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 1`
* `6 Can't do into 0`
* `7 Doesn't do into 994`
* `8 Doesn't answer into 995`
* `NA into 999`

**R script:**
```{r harmo w2}
MHAS_ds_w2 <- tibble(id=MHAS_w2_mob_arm$id)
MHAS_ds_w2$mob_arm <- car::recode(MHAS_w2_mob_arm$h9, "1 = '0';2 = '1';NA = '999';6 = '0';7 = '994';8 = '995' ")
MHAS_ds_w2$mob_arm <- labelled(MHAS_ds_w2$mob_arm, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vari <- MHAS_ds_w2$mob_arm
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_arm")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(MHAS_ds_w2, aes(x=factor(mob_arm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Extending arms") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
AfterH <- table(MHAS_ds_w2$mob_arm)
X<-table(MHAS_w2_mob_arm$h9)
BeforeH <- c(sum(X[c(1,3)]),X[c(2,4,5)],sum(is.na(MHAS_w2_mob_arm$h9)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,6->0","2->1","7->994","8->995","NA->999") 
kable(C)
```






```{r importOPAL w2, echo=FALSE}

label(MHAS_ds_w2$mob_arm) <- "Difficulty for reaching / extending arms"
#opal.assign.data(o, 'MHAS_ds_w2', MHAS_ds_w2)
#opal.symbol_import(o,'MHAS_ds_w2', project='_Athlos_Harm_Dataset')
mob_arm <- MHAS_ds_w2
save(mob_arm, file = "../RData/w2/mob_arm.RData")

MHAS_m_ds_w2 <- MHAS_ds_w2
MHAS_m_ds_w2$mob_arm <- car::recode(MHAS_m_ds_w2$mob_arm, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'MHAS_m_ds_w2', MHAS_m_ds_w2)
#opal.symbol_import(o,'MHAS_m_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 3

#### Study-specific variable description




| **Name** | `h9_12`|
|-|-|
| **Label** | `Because of health problem, difficulty lifting arms` |
| **Table name** |`MHAS_2012_new`|
| **Categories** |`1 = Yes; 2 = No; 6 = Can't do`|
| **Missings** |`7 = Doesn't do; 8 = Doesn't answer; 9 = Doesn't know; NA`|
| **Description** |  |



```{r assign w3, echo=F}
opal.assign.table.tibble(o, 'MHAS_w3_mob_arm','Mexican Health Aging Study.MHAS_2012_new', variables=list('h9_12'), missings = TRUE)
```

```{r local w3, echo=F}
MHAS_w3_mob_arm <- opal.execute(o,'MHAS_w3_mob_arm')
vari <- MHAS_w3_mob_arm$h9_12
kable(Categorical_summary(vari, missing_values = c(7,8,9))[3], caption = "h9_12")
kable(Categorical_summary(vari, missing_values = c(7,8,9))[1], caption = "Category")
ggplot(MHAS_w3_mob_arm, aes(x=factor(h9_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Extending arms") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 1`
* `6 Can't do into 0`
* `7 Doesn't do into 994`
* `8 Doesn't answer into 995`
* `9 Doesn't know into 998`
* `NA into 999`

**R script:**
```{r harmo w3}
MHAS_ds_w3 <- tibble(id=MHAS_w3_mob_arm$id)
MHAS_ds_w3$mob_arm <- car::recode(MHAS_w3_mob_arm$h9_12, "1 = '0';2 = '1';NA = '999';6 = '0';7 = '994';8 = '995';9 = '998' ")
MHAS_ds_w3$mob_arm <- labelled(MHAS_ds_w3$mob_arm, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}
vari <- MHAS_ds_w3$mob_arm
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_arm")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(MHAS_ds_w3, aes(x=factor(mob_arm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Extending arms") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=F}
AfterH <- table(MHAS_ds_w3$mob_arm)
X<-table(MHAS_w3_mob_arm$h9_12)
BeforeH <- c(sum(X[c(1,3)]),X[c(2,4,5,6)],sum(is.na(MHAS_w3_mob_arm$h9_12)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,6->0","2->1","7->994","8->995","9->998","NA->999") 
kable(C)
```






```{r importOPAL w3, echo=FALSE}

label(MHAS_ds_w3$mob_arm) <- "Difficulty for reaching / extending arms"
#opal.assign.data(o, 'MHAS_ds_w3', MHAS_ds_w3)
#opal.symbol_import(o,'MHAS_ds_w3', project='_Athlos_Harm_Dataset')
mob_arm <- MHAS_ds_w3
save(mob_arm, file = "../RData/w3/mob_arm.RData")

MHAS_m_ds_w3 <- MHAS_ds_w3
MHAS_m_ds_w3$mob_arm <- car::recode(MHAS_m_ds_w3$mob_arm, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'MHAS_m_ds_w3', MHAS_m_ds_w3)
#opal.symbol_import(o,'MHAS_m_ds_w3', project='_Athlos_Harm_Dataset')
```




# Quality estimation
No comments.

```{r closeRsession, echo=FALSE}
opal.logout(o)
```