---
title: "Memory"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 

# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `memory`
* Variable label: `Difficulties with memory`
* Variable description: `Difficulties with memory`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Presence of difficulties with memory
1        | Absence of memory difficulties

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process 

## Mexico

### Wave 1 

#### Study-specific variable description




| **Name** | `pc1`|
|-|-|
| **Label** | `How would you rate (NAME's) memory at the present time?` |
| **Table name** | `MHAS-2001` |
| **Categories** | `1 = Excellent; 2 = Very good; 3 = Good; 4 = Fair; 5 = Poor` |
| **Missings** | `8 = Refused; 9 = Don't know; NA` |
| **Description** |  |



```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'MHAS_w1_memory','Mexican Health Aging Study.MHAS-2001', variables=list('pc1'), missings = TRUE)
```

```{r local w1, echo=F}
MHAS_w1_memory <- opal.execute(o,'MHAS_w1_memory')
vari <- MHAS_w1_memory$pc1
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = "pc1")
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
ggplot(MHAS_w1_memory, aes(x=factor(pc1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("memory") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 Excellent into 1` 
* `2 Very good into 1` 
* `3 Good into 1` 
* `4 Fair into 0` 
* `5 Poor into 0`
* `8 Refused into 997`
* `9 Don't know into 998`
* `NA into 999`


**R script:**
```{r harmo w1}
MHAS_ds_w1 <- tibble(id=MHAS_w1_memory$id)
MHAS_ds_w1$memory <- car::recode(MHAS_w1_memory$pc1, "1 = '1';2 = '1';3 = '1';4 = '0';5 = '0';8 =  '997';9 = '998';NA = '999' ")
MHAS_ds_w1$memory <- labelled(MHAS_ds_w1$memory, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vari <- MHAS_ds_w1$memory
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "memory")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(MHAS_ds_w1, aes(x=factor(memory))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("memory") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(MHAS_ds_w1$memory)
X<- table(MHAS_w1_memory$pc1)
BeforeH <- c(sum(X[4:5]),sum(X[1:3]),X[c(6,7)],sum(is.na(MHAS_w1_memory$pc1)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4,5->0","1,2,3->1","8->997","9->998","NA->999") 
kable(C)
```






```{r importOPAL w1, echo=FALSE}

label(MHAS_ds_w1$memory) <- "Difficulties with memory"
#opal.assign.data(o, 'MHAS_ds_w1', MHAS_ds_w1)
#opal.symbol_import(o,'MHAS_ds_w1', project='_Athlos_Harm_Dataset')
memory <- MHAS_ds_w1
save(memory, file = "../RData/w1/memory.RData")

MHAS_m_ds_w1 <- MHAS_ds_w1
MHAS_m_ds_w1$memory <- car::recode(MHAS_m_ds_w1$memory, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'MHAS_m_ds_w1', MHAS_m_ds_w1)
#opal.symbol_import(o,'MHAS_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2

#### Study-specific variable description




| **Name** | `pc1`|
|-|-|
| **Label** | `How would you rate (NAME's) memory at the present time?` |
| **Table name** | `MHAS_2003` |
| **Categories** | `1 = Excellent; 2 = Very good; 3 = Good; 4 = Fair; 5 = Poor` |
| **Missings** | `9 = Don't know; NA` |
| **Description** |  |



```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'MHAS_w2_memory','Mexican Health Aging Study.MHAS_2003', variables=list('pc1'), missings = TRUE)
```

```{r local w2, echo=F}
MHAS_w2_memory <- opal.execute(o,'MHAS_w2_memory')
vari <- MHAS_w2_memory$pc1
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "pc1")
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
ggplot(MHAS_w2_memory, aes(x=factor(pc1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("memory") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 Excellent into 1` 
* `2 Very good into 1` 
* `3 Good into 1` 
* `4 Fair into 0` 
* `5 Poor into 0`
* `9 Don't know into 998`
* `NA into 999`


**R script:**
```{r harmo w2}
MHAS_ds_w2 <- tibble(id=MHAS_w2_memory$id)
MHAS_ds_w2$memory <- car::recode(MHAS_w2_memory$pc1, "1 = '1';2 = '1';3 = '1';4 = '0';5 = '0';9 = '998';NA = '999' ")
MHAS_ds_w2$memory <- labelled(MHAS_ds_w2$memory, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vari <- MHAS_ds_w2$memory
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "memory")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(MHAS_ds_w2, aes(x=factor(memory))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("memory") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
AfterH <- table(MHAS_ds_w2$memory)
X<- table(MHAS_w2_memory$pc1)
BeforeH <- c(sum(X[4:5]),sum(X[1:3]),X[6],sum(is.na(MHAS_w2_memory$pc1)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4,5->0","1,2,3->1","9->998","NA->999") 
kable(C)
```






```{r importOPAL w2, echo=FALSE}

label(MHAS_ds_w2$memory) <- "Difficulties with memory"
#opal.assign.data(o, 'MHAS_ds_w2', MHAS_ds_w2)
#opal.symbol_import(o,'MHAS_ds_w2', project='_Athlos_Harm_Dataset')
memory <- MHAS_ds_w2
save(memory, file = "../RData/w2/memory.RData")

MHAS_m_ds_w2 <- MHAS_ds_w2
MHAS_m_ds_w2$memory <- car::recode(MHAS_m_ds_w2$memory, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'MHAS_m_ds_w2', MHAS_m_ds_w2)
#opal.symbol_import(o,'MHAS_m_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 3 

#### Study-specific variable description




| **Name** | `pc1_12`|
|-|-|
| **Label** | `Present time:Report the subject's memory quality` |
| **Table name** | `MHAS_2012_new` |
| **Categories** | `1 = Excellent; 2 = Very good; 3 = Good; 4 = Fair; 5 = Poor` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign w3, echo=F}
opal.assign.table.tibble(o, 'MHAS_w3_memory','Mexican Health Aging Study.MHAS_2012_new', variables=list('pc1_12'), missings = TRUE)
```

```{r local w3, echo=F}
MHAS_w3_memory <- opal.execute(o,'MHAS_w3_memory')
vari <- MHAS_w3_memory$pc1_12
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "pc1_12")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(MHAS_w3_memory, aes(x=factor(pc1_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("memory") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 Excellent into 1` 
* `2 Very good into 1` 
* `3 Good into 1` 
* `4 Fair into 0` 
* `5 Poor into 0`
* `NA into 999`


**R script:**
```{r harmo w3}
MHAS_ds_w3 <- tibble(id=MHAS_w3_memory$id)
MHAS_ds_w3$memory <- car::recode(MHAS_w3_memory$pc1_12, "1 = '1';2 = '1';3 = '1';4 = '0';5 = '0';8 =  '997';9 = '998';NA = '999' ")
MHAS_ds_w3$memory <- labelled(MHAS_ds_w3$memory, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}
vari <- MHAS_ds_w3$memory
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "memory")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(MHAS_ds_w3, aes(x=factor(memory))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("memory") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=F}
AfterH <- table(MHAS_ds_w3$memory)
X<- table(MHAS_w3_memory$pc1_12)
BeforeH <- c(sum(X[4:5]),sum(X[1:3]),sum(is.na(MHAS_w3_memory$pc1_12)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4,5->0","1,2,3->1","NA->999") 
kable(C)
```






```{r importOPAL w3, echo=FALSE}

label(MHAS_ds_w3$memory) <- "Difficulties with memory"
#opal.assign.data(o, 'MHAS_ds_w3', MHAS_ds_w3)
#opal.symbol_import(o,'MHAS_ds_w3', project='_Athlos_Harm_Dataset')
memory <- MHAS_ds_w3
save(memory, file = "../RData/w3/memory.RData")

MHAS_m_ds_w3 <- MHAS_ds_w3
MHAS_m_ds_w3$memory <- car::recode(MHAS_m_ds_w3$memory, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'MHAS_m_ds_w3', MHAS_m_ds_w3)
#opal.symbol_import(o,'MHAS_m_ds_w3', project='_Athlos_Harm_Dataset')
```



# Quality estimation

The high percentage of missing values is due to `pc1` is a proxy variable.
(Also maybe category 4=0: self reported memory: fair=difficulties 
with memory could be revised... not sure whether it shout be recodified as 1= no difficulties).



```{r closeRsession, echo=FALSE}
opal.logout(o)
```

