---
title: "ADL - Bathing or showering"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_ania.r")
```
```{r, dataDirectory, echo=FALSE}
datafolder <- "../RData"
``` 
<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `adl_bathing`
* Variable label: `ADL-Difficulties for bathing or showering`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | yes
1        | no

* Category missings: 


**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



```{r, jumping list, echo=FALSE}
l <- list('h1', 'h3', 'h4', 'h5', 'h7', 'h8', 'h9', 'h10', 'h11', 'h12', 'h13' )
```

<!-- ########################################################## --> 

# Data process


## Mexican population
### Wave 1 

#### Study-specific variable description

 


* Name: `h16_1`
* Label: `Difficult bathing`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `6 = Can't do`
* Missings
    + `7 = Doesn't do`
    + `8 = Doesn't answer`
    + `9 = DK`
    + `NA`


* Description: 
```{r assign w1,  echo=FALSE}
m <- append(l, 'h16_1')
opal.assign.table.tibble(o, 'MHAS_w1_adl_bathing','Mexican Health Aging Study.MHAS-2001', variables=m, missings = TRUE)
```

```{r local w1,  echo=FALSE}
MHAS_w1_adl_bathing <- opal.execute(o,'MHAS_w1_adl_bathing')
vari <- MHAS_w1_adl_bathing$h16_1 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(MHAS_w1_adl_bathing$h16_1)
ggplot(MHAS_w1_adl_bathing, aes(x=factor(h16_1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty bathing or showering") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 1`
* `6 Can't do into 0`
* `7 Doesn't do into 994`
* `8 Doesn't answer into 995`
* `9 DK into 998`
* `NA into 999`

**R script:** 

```{r, echo=FALSE, eval=FALSE}
#Checking whether this question was skaped for any subject:
length(which((MHAS_w1_adl_bathing$h1==2)&
                              (MHAS_w1_adl_bathing$h3==2)&
                              (MHAS_w1_adl_bathing$h4==2)&
                              (MHAS_w1_adl_bathing$h5==2)&
                              (MHAS_w1_adl_bathing$h7==2)&
                              (MHAS_w1_adl_bathing$h8==2)&
                              (MHAS_w1_adl_bathing$h9==2)&
                              (MHAS_w1_adl_bathing$h10==2)&
                              (MHAS_w1_adl_bathing$h11==2)&
                              (MHAS_w1_adl_bathing$h12==2)&
                              (MHAS_w1_adl_bathing$h13==2)))
```



```{r harmo w1,   echo=TRUE}
MHAS_ds_w1 <- tibble(id=MHAS_w1_adl_bathing$id)
MHAS_ds_w1$adl_bathing <- car::recode(MHAS_w1_adl_bathing$h16_1, "1 = '0';2 = '1';NA = '999';6 = '0';7 = '994';8 = '995';9 = '998' ")
MHAS_ds_w1$adl_bathing <- labelled(MHAS_ds_w1$adl_bathing, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1,  echo=FALSE}
vari <- MHAS_ds_w1$adl_bathing # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_ds_w1$adl_bathing, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w1, aes(x=factor(adl_bathing))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty bathing or showering") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1,  echo=FALSE}
AfterH <- table(MHAS_ds_w1$adl_bathing)
X<-table(MHAS_w1_adl_bathing$h16_1)
BeforeH <- c(sum(X[1],X[3]),X[c(2,4,5,6)],sum(is.na(MHAS_w1_adl_bathing$h16_1)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","2->1","7->994","8->995","9->998","NA->999") 
kable(C)
```


```{r importOPAL w1, echo=FALSE,  echo=FALSE}
val_labels(MHAS_ds_w1) <- NULL
label(MHAS_ds_w1$adl_bathing) <- "Difficulties for bathing or showering"
opal.assign.data(o, 'MHAS_ds_w1', MHAS_ds_w1)
#opal.symbol_import(o,'MHAS_ds_w1', project='_Athlos_Harm_Dataset')

MHAS_m_ds_w1 <- MHAS_ds_w1
MHAS_m_ds_w1$adl_bathing <- car::recode(MHAS_m_ds_w1$adl_bathing, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'MHAS_m_ds_w1', MHAS_m_ds_w1)
#opal.symbol_import(o,'MHAS_m_ds_w1', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
adl_bathing <- MHAS_ds_w1
save(adl_bathing, file = paste0(datafolder, "/w1/adl_bathing.RData"))
```

### Wave 2

#### Study-specific variable description

 


* Name: `h16a`
* Label: `Health problem-have trouble bathing`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `6 = Can't do`
* Missings
    + `7 = Doesn't do`
    + `8 = Doesn't answer`
    + `NA`


* Description: 
```{r assign w2,  echo=FALSE}
m <- append(l, 'h16a')
opal.assign.table.tibble(o, 'MHAS_w2_adl_bathing','Mexican Health Aging Study.MHAS_2003', variables=m, missings = TRUE)
```

```{r local w2,  echo=FALSE}
MHAS_w2_adl_bathing <- opal.execute(o,'MHAS_w2_adl_bathing')
vari <- MHAS_w2_adl_bathing$h16a # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(MHAS_w2_adl_bathing$h16a)
ggplot(MHAS_w2_adl_bathing, aes(x=factor(h16a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty bathing or showering") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 1`
* `6 Can't do into 0`
* `7 Doesn't do into 994`
* `8 Doesn't answer into 995`
* `NA into 999`

**R script:** 

```{r, echo=FALSE, eval=FALSE}
#Checking whether this question was skaped for any subject:
length(which((MHAS_w2_adl_bathing$h1==2)&
                              (MHAS_w2_adl_bathing$h3==2)&
                              (MHAS_w2_adl_bathing$h4==2)&
                              (MHAS_w2_adl_bathing$h5==2)&
                              (MHAS_w2_adl_bathing$h7==2)&
                              (MHAS_w2_adl_bathing$h8==2)&
                              (MHAS_w2_adl_bathing$h9==2)&
                              (MHAS_w2_adl_bathing$h10==2)&
                              (MHAS_w2_adl_bathing$h11==2)&
                              (MHAS_w2_adl_bathing$h12==2)&
                              (MHAS_w2_adl_bathing$h13==2)))
```

As it wasn't, the variable is recoded as follows:

```{r harmo w2,   echo=TRUE}
MHAS_ds_w2 <- tibble(id=MHAS_w2_adl_bathing$id)
MHAS_ds_w2$adl_bathing <- car::recode(MHAS_w2_adl_bathing$h16a, "1 = '0';2 = '1';NA = '999';6 = '0';7 = '994';8 = '995';9 = '998' ")
MHAS_ds_w2$adl_bathing <- labelled(MHAS_ds_w2$adl_bathing, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2,  echo=FALSE}
vari <- MHAS_ds_w2$adl_bathing # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_ds_w2$adl_bathing, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w2, aes(x=factor(adl_bathing))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty bathing or showering") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2,  echo=FALSE}
AfterH <- table(MHAS_ds_w2$adl_bathing)
X<-table(MHAS_w2_adl_bathing$h16a)
BeforeH <- c(sum(X[1],X[3]),X[c(2,4,5)],sum(is.na(MHAS_w2_adl_bathing$h16a)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","2->1","7->994","8->995","NA->999") 
kable(C)
```


```{r importOPAL w2, echo=FALSE,  echo=FALSE}
val_labels(MHAS_ds_w2) <- NULL
label(MHAS_ds_w2$adl_bathing) <- "Difficulties for bathing or showering"
opal.assign.data(o, 'MHAS_ds_w2', MHAS_ds_w2)
#opal.symbol_import(o,'MHAS_ds_w2', project='_Athlos_Harm_Dataset')

MHAS_m_ds_w2 <- MHAS_ds_w2
MHAS_m_ds_w2$adl_bathing <- car::recode(MHAS_m_ds_w2$adl_bathing, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'MHAS_m_ds_w2', MHAS_m_ds_w2)
#opal.symbol_import(o,'MHAS_m_ds_w2', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
adl_bathing <- MHAS_ds_w2
save(adl_bathing, file = paste0(datafolder, "/w2/adl_bathing.RData"))
```

### Wave 3

#### Study-specific variable description

 


* Name: `h16a_12`
* Label: `Because of health problem, difficulty bathing`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `6 = Can't do`
* Missings
    + `7 = Doesn't do`
    + `8 = RF`
    + `9 = DK`
    + `NA`


* Description: 


```{r, jumping list w3, echo=FALSE}
l2 <- list('h1', 'h4', 'h5', 'h6', 'h8', 'h9', 'h10', 'h11', 'h12', 'h13' )
```


```{r assign w3,  echo=FALSE}
m2 <- append(l2, 'h16a_12')
opal.assign.table.tibble(o, 'MHAS_w3_adl_bathing','Mexican Health Aging Study.MHAS_2012_new', variables=m2, missings = TRUE)
```

```{r local w3,  echo=FALSE}
MHAS_w3_adl_bathing <- opal.execute(o,'MHAS_w3_adl_bathing')
vari <- MHAS_w3_adl_bathing$h16a_12 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(MHAS_w3_adl_bathing$h16a_12)
ggplot(MHAS_w3_adl_bathing, aes(x=factor(h16a_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty bathing or showering") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 1`
* `6 Can't do into 0`
* `7 Doesn't do into 994`
* `8 RF into 997`
* `9 DK into 998`
* `NA into 999`

**R script:** 

```{r, echo=FALSE, eval=FALSE}
#Checking whether this question was skaped for any subject:
length(which((MHAS_w3_adl_bathing$h1==2)&
                              (MHAS_w3_adl_bathing$h4==2)&
                              (MHAS_w3_adl_bathing$h5==2)&
                              (MHAS_w3_adl_bathing$h8==2)&
                              (MHAS_w3_adl_bathing$h9==2)&
                              (MHAS_w3_adl_bathing$h10==2)&
                              (MHAS_w3_adl_bathing$h11==2)&
                              (MHAS_w3_adl_bathing$h12==2)&
                              (MHAS_w3_adl_bathing$h13==2)))
```




```{r harmo w3,   echo=TRUE}
MHAS_ds_w3 <- tibble(id=MHAS_w3_adl_bathing$id)
MHAS_ds_w3$adl_bathing <- car::recode(MHAS_w3_adl_bathing$h16a_12, "1 = '0';2 = '1';NA = '999';6 = '0';7 = '994';8 = '997';9 = '998' ")
MHAS_ds_w3$adl_bathing <- labelled(MHAS_ds_w3$adl_bathing, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3,  echo=FALSE}
vari <- MHAS_ds_w3$adl_bathing # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_ds_w3$adl_bathing, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w3, aes(x=factor(adl_bathing))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty bathing or showering") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3,  echo=FALSE}
AfterH <- table(MHAS_ds_w3$adl_bathing)
X<-table(MHAS_w3_adl_bathing$h16a_12)
BeforeH <- c(sum(X[1], X[3]),X[c(2,4,5,6)],sum(is.na(MHAS_w3_adl_bathing$h16a_12)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","2->1","7->994","8->997","9->998","NA->999") 
kable(C)
```


```{r importOPAL w3, echo=FALSE,  echo=FALSE}
val_labels(MHAS_ds_w3) <- NULL
label(MHAS_ds_w3$adl_bathing) <- "Difficulties for bathing or showering"
opal.assign.data(o, 'MHAS_ds_w3', MHAS_ds_w3)
#opal.symbol_import(o,'MHAS_ds_w3', project='_Athlos_Harm_Dataset')

MHAS_m_ds_w3 <- MHAS_ds_w3
MHAS_m_ds_w3$adl_bathing <- car::recode(MHAS_m_ds_w3$adl_bathing, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'MHAS_m_ds_w3', MHAS_m_ds_w3)
#opal.symbol_import(o,'MHAS_m_ds_w3', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
adl_bathing <- MHAS_ds_w3
save(adl_bathing, file = paste0(datafolder, "/w3/adl_bathing.RData"))
```

# Quality control


'Can’t do = 6' was considered as maximum difficulty

```{r closeRsession, echo=FALSE,  echo=FALSE}
opal.logout(o)
```
