---
title: "ADL - Getting dressed"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_ania.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `adl_dressing`
* Variable label: `ADL-Difficulties for getting dressed`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | yes
1        | no

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




<!-- ########################################################## --> 

# Data process
```{r, dataDirectory, echo=FALSE}
datafolder <- "../RData"
``` 

## Mexican population

### Wave 1 

#### Study-specific variable description

 


* Name: `h13`
* Label: `Dressing`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `6 = Can't do`
* Missings
    + `7 = Doesn't do`
    + `8 = Doesn't answer`
    + `9 = DK`
    + `NA`

* Note: this question was skaped when variable `h_ent_tip` took values 21 or 22.

* Description: 
```{r assign w1,  echo=FALSE}
opal.assign.table.tibble(o, 'MHAS_w1_adl_dressing','Mexican Health Aging Study.MHAS-2001', variables=list('h13', 'h_ent_tip'), missings = TRUE)
```

```{r local w1,  echo=FALSE}
MHAS_w1_adl_dressing <- opal.execute(o,'MHAS_w1_adl_dressing')
vari <- MHAS_w1_adl_dressing$h13 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(MHAS_w1_adl_dressing$h13)
ggplot(MHAS_w1_adl_dressing, aes(x=factor(h13))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

```{r local2 w1,  echo=FALSE}
MHAS_w1_adl_dressing <- opal.execute(o,'MHAS_w1_adl_dressing')
vari <- MHAS_w1_adl_dressing$h_ent_tip # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(MHAS_w1_adl_dressing$h13)
ggplot(MHAS_w1_adl_dressing, aes(x=factor(h_ent_tip))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:
* `h_ent_tip = 11 or 12 and`
    * `1 into 0` 
    * `2 into 1`
    * `6 Can't do into 0`
    * `7 Doesn't do into 994`
    * `8 Doesn't answer into 995`
    * `9 DK into 998`
    * `NA into 999`
    
* `h_ent_tip = 21 or 22 into 996`

**R script:** 
```{r harmo w1,   echo=TRUE}
MHAS_ds_w1 <- tibble(id=MHAS_w1_adl_dressing$id)
MHAS_ds_w1$adl_dressing <- rep(0, length(MHAS_w1_adl_dressing$id))


MHAS_ds_w1$adl_dressing[which((MHAS_w1_adl_dressing$h_ent_tip==21)|(MHAS_w1_adl_dressing$h_ent_tip==22))] <- 996
for(i in which((MHAS_w1_adl_dressing$h_ent_tip==11)|(MHAS_w1_adl_dressing$h_ent_tip==12))){
  MHAS_ds_w1$adl_dressing[i] <- MHAS_w1_adl_dressing$h13[i]
}
MHAS_ds_w1$adl_dressing <- car::recode(MHAS_ds_w1$adl_dressing, "1 = '0';2 = '1';NA = '999';6 = '0';7 = '994';8 = '995';9 = '998' ")
MHAS_ds_w1$adl_dressing <- labelled(MHAS_ds_w1$adl_dressing, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```




#### Statistical description of the new harmonised variable
```{r descript w1,  echo=FALSE}
vari <- MHAS_ds_w1$adl_dressing # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_ds_w1$adl_dressing, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w1, aes(x=factor(adl_dressing))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1,  echo=FALSE}
AfterH <- table(MHAS_ds_w1$adl_dressing)
X<-table(MHAS_w1_adl_dressing$h13)
BeforeH <- c(sum(X[1], X[3]),X[c(2,4,5)], length(which((MHAS_w1_adl_dressing$h_ent_tip==21)|(MHAS_w1_adl_dressing$h_ent_tip==22))),X[6])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,6->0","2->1","7->994","8->995","h_ent_tip = 21 or 22 -> 996","9->998") 
kable(C)
```

 
 


 
```{r importOPAL w1, echo=FALSE,  echo=FALSE}
val_labels(MHAS_ds_w1) <- NULL
label(MHAS_ds_w1$adl_dressing) <- "Difficulties for getting dressed"
#opal.assign.data(o, 'MHAS_ds_w1', MHAS_ds_w1)
#opal.symbol_import(o,'MHAS_ds_w1', project='_Athlos_Harm_Dataset')

MHAS_m_ds_w1 <- MHAS_ds_w1
MHAS_m_ds_w1$adl_dressing <- car::recode(MHAS_m_ds_w1$adl_dressing, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'MHAS_m_ds_w1', MHAS_m_ds_w1)
#opal.symbol_import(o,'MHAS_m_ds_w1', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
adl_dressing <- MHAS_ds_w1
save(adl_dressing, file = paste0(datafolder, "/w1/adl_dressing.RData"))
```


### Wave 2

#### Study-specific variable description

 


* Name: `h13`
* Label: `Health problems-trouble dressing self`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `6 = Can't do`
* Missings
    + `7 = Doesn't do`
    + `NA`

* Note: this question was skaped when variable `ent_tipent` took values 21 or 22.

* Description: 
```{r assign w2,  echo=FALSE}
opal.assign.table.tibble(o, 'MHAS_w2_adl_dressing','Mexican Health Aging Study.MHAS_2003', variables=list('h13', 'ent_tipent'), missings = TRUE)
```

```{r local w2,  echo=FALSE}
MHAS_w2_adl_dressing <- opal.execute(o,'MHAS_w2_adl_dressing')
vari <- MHAS_w2_adl_dressing$h13 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(MHAS_w2_adl_dressing$h13)
ggplot(MHAS_w2_adl_dressing, aes(x=factor(h13))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

```{r local2 w2,  echo=FALSE}
vari <- MHAS_w2_adl_dressing$ent_tipent # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(MHAS_w2_adl_dressing$h13)
ggplot(MHAS_w2_adl_dressing, aes(x=factor(ent_tipent))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:
* `ent_tipent = 11 or 12 and`
    * `1 into 0` 
    * `2 into 1`
    * `6 Can't do into 0`
    * `7 Doesn't do into 994`
    * `NA into 999`
    
* `ent_tipent = 21 or 22 into 996`

**R script:** 
```{r harmo w2,   echo=TRUE}
MHAS_ds_w2 <- tibble(id=MHAS_w2_adl_dressing$id)
MHAS_ds_w2$adl_dressing <- rep(0, length(MHAS_w2_adl_dressing$id))
MHAS_ds_w2$adl_dressing[which((MHAS_w2_adl_dressing$ent_tipent==21)|(MHAS_w2_adl_dressing$ent_tipent==22))] <- 996

for(i in which((MHAS_w2_adl_dressing$ent_tipent==11)|(MHAS_w2_adl_dressing$ent_tipent==12))){
  MHAS_ds_w2$adl_dressing[i] <- MHAS_w2_adl_dressing$h13[i]
}
MHAS_ds_w2$adl_dressing <- car::recode(MHAS_ds_w2$adl_dressing, "1 = '0';2 = '1';NA = '999';6 = '0';7 = '994';8 = '995';9 = '998' ")
MHAS_ds_w2$adl_dressing <- labelled(MHAS_ds_w2$adl_dressing, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))

```

#### Statistical description of the new harmonised variable
```{r descript w2,  echo=FALSE}
vari <- MHAS_ds_w2$adl_dressing # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_ds_w2$adl_dressing, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w2, aes(x=factor(adl_dressing))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2,  echo=FALSE}
AfterH <- table(MHAS_ds_w2$adl_dressing)
X<-table(MHAS_w2_adl_dressing$h13)
BeforeH <- c(sum(X[1],X[3]),X[c(2,4)],length(which((MHAS_w2_adl_dressing$ent_tipent==21)|(MHAS_w2_adl_dressing$ent_tipent==22))))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,6->0","2->1","7->994","ent_tipent = 21 or 22 -> 996") 
kable(C)
```

 
 


 
```{r importOPAL w2, echo=FALSE,  echo=FALSE}
val_labels(MHAS_ds_w2) <- NULL
label(MHAS_ds_w2$adl_dressing) <- "Difficulties for getting dressed"
#opal.assign.data(o, 'MHAS_ds_w2', MHAS_ds_w2)
#opal.symbol_import(o,'MHAS_ds_w2', project='_Athlos_Harm_Dataset')

MHAS_m_ds_w2 <- MHAS_ds_w2
MHAS_m_ds_w2$adl_dressing <- car::recode(MHAS_m_ds_w2$adl_dressing, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'MHAS_m_ds_w2', MHAS_m_ds_w2)
#opal.symbol_import(o,'MHAS_m_ds_w2', project='_Athlos_Harm_Dataset')
```


```{r,  echo=FALSE}
adl_dressing <- MHAS_ds_w2
save(adl_dressing, file = paste0(datafolder, "/w2/adl_dressing.RData"))
```

### Wave 3

#### Study-specific variable description

 


* Name: `h13_12`
* Label: `Because of health problem, difficulty dressing self`
* Categories:
    + `1 = Yes`
    + `2 = No`
    + `6 = Can't do`
* Missings
    + `7 = Doesn't do`
    + `8 = RF`
    + `9 = DK`
    + `NA`

* Note: this question was skaped when variable `tipent_12` took values 3, 4 or 5.

* Description: 
```{r assign w3,  echo=FALSE}
opal.assign.table.tibble(o, 'MHAS_w3_adl_dressing','Mexican Health Aging Study.MHAS_2012_new', variables=list('h13_12', 'tipent_12'), missings = TRUE)
```

```{r local w3,  echo=FALSE}
MHAS_w3_adl_dressing <- opal.execute(o,'MHAS_w3_adl_dressing')
vari <- MHAS_w3_adl_dressing$h13_12 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(MHAS_w3_adl_dressing$h13_12)
ggplot(MHAS_w3_adl_dressing, aes(x=factor(h13_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

```{r local2 w3,  echo=FALSE}
MHAS_w3_adl_dressing <- opal.execute(o,'MHAS_w3_adl_dressing')
vari <- MHAS_w3_adl_dressing$tipent_12 # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(MHAS_w3_adl_dressing$h13_12)
ggplot(MHAS_w3_adl_dressing, aes(x=factor(tipent_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:
* `tipent_12 = 1 or 2 and`
    * `1 into 0` 
    * `2 into 1`
    * `6 Can't do into 0`
    * `7 Doesn't do into 994`
    * `8 RF into 997`
    * `9 DK into 998`
    * `NA into 999`
    
* `tipent_12 = 3, 4, or 5 into 996`

**R script:** 
```{r harmo w3,   echo=TRUE}
MHAS_ds_w3 <- tibble(id=MHAS_w3_adl_dressing$id)
MHAS_ds_w3$adl_dressing <- rep(0, length(MHAS_w3_adl_dressing$id))

MHAS_ds_w3$adl_dressing[which((MHAS_w3_adl_dressing$tipent_12==3)|(MHAS_w3_adl_dressing$tipent_12==4)|(MHAS_w3_adl_dressing$tipent_12==5))] <- 996
for(i in which((MHAS_w3_adl_dressing$tipent_12==1)|(MHAS_w3_adl_dressing$tipent_12==2))){
  MHAS_ds_w3$adl_dressing[i] <- MHAS_w3_adl_dressing$h13_12[i]
}
MHAS_ds_w3$adl_dressing <- car::recode(MHAS_ds_w3$adl_dressing, "1 = '0';2 = '1';NA = '999';6 = '0';7 = '994';8 = '995';9 = '998' ")
MHAS_ds_w1$adl_dressing <- labelled(MHAS_ds_w1$adl_dressing, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))

```

#### Statistical description of the new harmonised variable
```{r descript w3,  echo=FALSE}
vari <- MHAS_ds_w3$adl_dressing # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = MHAS_ds_w3$adl_dressing, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(MHAS_ds_w3, aes(x=factor(adl_dressing))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3,  echo=FALSE}
AfterH <- table(MHAS_ds_w3$adl_dressing)
X<-table(MHAS_w3_adl_dressing$h13_12)
BeforeH <- c(sum(X[1],X[3]),X[c(2,4,5)],length(which((MHAS_w3_adl_dressing$tipent_12==3)|
                                                       (MHAS_w3_adl_dressing$tipent_12==4)|
                                                       (MHAS_w3_adl_dressing$tipent_12==5))),X[6])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,6->0","2->1","7->994","8->997","tipent_12 = 3,4 or5-> 996","9->998") 
kable(C)
```

 
 


 
```{r importOPAL w3, echo=FALSE,  echo=FALSE}
val_labels(MHAS_ds_w3) <- NULL
label(MHAS_ds_w3$adl_dressing) <- "Difficulties for getting dressed"
#opal.assign.data(o, 'MHAS_ds_w3', MHAS_ds_w3)
#opal.symbol_import(o,'MHAS_ds_w3', project='_Athlos_Harm_Dataset')

MHAS_m_ds_w3 <- MHAS_ds_w3
MHAS_m_ds_w3$adl_dressing <- car::recode(MHAS_m_ds_w3$adl_dressing, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'MHAS_m_ds_w3', MHAS_m_ds_w3)
#opal.symbol_import(o,'MHAS_m_ds_w3', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
adl_dressing <- MHAS_ds_w3
save(adl_dressing, file = paste0(datafolder, "/w3/adl_dressing.RData"))
```

# Quality control


'Can’t do = 6' was considered as maximum difficulty

```{r closeRsession, echo=FALSE,  echo=FALSE}
opal.logout(o)
```
