---
title: "Verbal fluency"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_laia.r")
```

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `cog_verb_c`
* Variable label: `Cognition - verbal fluency - Continuous`
* Variable description: `Cognition - verbal fluency - Continuous. Test that assesses verbal (semantic) fluency: name as many animals as they could think of in 1 minute`
* Domain: `Health status and functional limitations`
* Value type: `Countinous`
* Comments: `Means of all sistolic blood pressure measures.`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Short name: `cog_verb`
* Variable label: `Cognition - verbal fluency`
* Variable description: `Cognition - verbal fluency. Test that assesses verbal (semantic) fluency: name as many animals as they could think of in 1 minute. Discrete variable: value 0 = <=25%; value 1 = >25%.`
* Domain: `Health status and functional limitations`
* Value type: `Categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | <=25%
1        | >25%

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Verbal fluency"
ds_label_cog_verb_c <- "Cognition - verbal fluency - Continuous. Test that assesses verbal (semantic) fluency: name as many animals as they could think of in 1 minute"
ds_label_cog_verb <- "Cognition - verbal fluency. Test that assesses verbal (semantic) fluency: name as many animals as they could think of in 1 minute. Discrete variable: value 0 = <=25%; value 1 = >25%"
```

# Data process

## Mexico

### Wave 1 

Not found



### Wave 2 

Not found




### Wave 3 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `e9a_12`
* Label: `Number of different animals`
* Categories:
    + `Continuous Variable 0-66`
* Missings
   + `88 = No Response`
   + `NA`

```{r assign w3, echo=FALSE}
opal.assign.table.tibble(o, 'MHAS_w3_cog_verb','Mexican Health Aging Study.MHAS_2012_new', variables=list('e9a_12'), missings = TRUE)
MHAS_w3_cog_verb <- opal.execute(o,'MHAS_w3_cog_verb')
```

```{r local w3, echo=FALSE}
vari <- MHAS_w3_cog_verb$e9a_12
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(MHAS_w3_cog_verb, aes(x=factor(e9a_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_verb_c` from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

To compute the harmonized variable `cog_verb` from `cog_verb_c` it has to be recoded as follows:

* `cog_verb_c <=25% into 0`
* `cog_verb_c >25% into 1`

**R script:**

```{r harmo w3}
#cog_verb_c
MHAS_ds_w3 <- tibble(id=MHAS_w3_cog_verb$id)
MHAS_ds_w3$cog_verb_c <- car::recode(MHAS_w3_cog_verb$e9a_12, "88=995; NA=999")
MHAS_ds_w3$cog_verb_c <- labelled(MHAS_ds_w3$cog_verb_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(MHAS_ds_w3$cog_verb_c, "999=NA; 995=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

MHAS_ds_w3$cog_verb <- car::recode(MHAS_ds_w3[[2]], "0:Q=0; (Q+1):900=1")
MHAS_ds_w3$cog_verb <- labelled(MHAS_ds_w3[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=FALSE}
vari <- MHAS_ds_w3$cog_verb_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(MHAS_ds_w3, aes(x=factor(cog_verb_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")

vari <- MHAS_ds_w3$cog_verb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(MHAS_ds_w3, aes(x=factor(cog_verb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=FALSE}
Continous <- c(sum(na.omit(MHAS_ds_w3[[2]])<=Q), sum(na.omit(MHAS_ds_w3[[2]])>Q & na.omit(MHAS_ds_w3[[2]])<900), sum(na.omit(MHAS_ds_w3[[2]])==995), sum(na.omit(MHAS_ds_w3[[2]])==999))
Dicotomic <- table(MHAS_ds_w3[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:11->0","12:160->1", "88->995", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL w3, echo=FALSE}
#label(MHAS_ds_w3$cog_verb) <- "Cognition - verbal fluency"
#opal.assign.data(o, 'MHAS_ds_w3', MHAS_ds_w3)
#opal.symbol_import(o,'MHAS_ds_w3', project='_Athlos_Harm_Dataset')

label(MHAS_ds_w3$cog_verb_c) <- ds_label_cog_verb_c
label(MHAS_ds_w3$cog_verb) <- ds_label_cog_verb
cog_verb <- MHAS_ds_w3
save(cog_verb, file = "../RData/w3/cog_verb.RData")
```



# Quality estimation

No comments

[Comments on the quality of the new harmonised variable. This section can be done in a later stage, once all variables are harmonised.]

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
