---
title: "Recent falls"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_laia.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `recent_falls`
* Variable label: `Recent falls in the last 6-24 months`
* Variable description: `Recent falls in the last 6-24 months`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Recent falls"
ds_label_all <- "Recent falls in the last 6-24 months"
```


# Data process

## MHAS

### Wave 1

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `c40`
* Label: `Fallen down`
* Categories:
   + `1 = Yes`
   + `2 = No`
* Missings
   + `8 = Doesn't answer`
   + `9 = Doesn't know`

```{r assign w1, echo=FALSE}
opal.assign.table.tibble(o, 'MHAS_w1_recent_falls','Mexican Health Aging Study.MHAS-2001', variables=list('c40'), missings = TRUE)
MHAS_w1_recent_falls <- opal.execute(o,'MHAS_w1_recent_falls')
```

```{r local w1, echo=FALSE}
vari <- MHAS_w1_recent_falls$c40
kable(Categorical_summary(vari, missing_values = c(9,8))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(9,8))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9,8))[2], caption = "Type of missing")
ggplot(MHAS_w1_recent_falls, aes(x=factor(c40))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0`
* `8 into 995`
* `9 into 998`

**R script:**

```{r harmo w1}
MHAS_ds_w1 <- tibble(id=MHAS_w1_recent_falls$id)
MHAS_ds_w1$recent_falls <- car::recode(MHAS_w1_recent_falls$c40, "1 = '1';2 = '0';8 = '995';9 = '998' ")
MHAS_ds_w1$recent_falls <- labelled(MHAS_ds_w1$recent_falls, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=FALSE}
vari <- MHAS_ds_w1$recent_falls
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(MHAS_ds_w1, aes(x=factor(recent_falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=FALSE}
AfterH <- table(MHAS_ds_w1$recent_falls)
X<-table(MHAS_w1_recent_falls$c40)
BeforeH <- c(X[c(2,1,3,4)])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1","8->995","9->998") 
kable(C)
```

```{r importOPAL w1, echo=FALSE}
label(MHAS_ds_w1$recent_falls) <- "Recent falls in the last 6-24 months"
recent_falls <- MHAS_ds_w1
save(recent_falls, file = "../RData/w1/recent_falls.RData")
#opal.assign.data(o, 'MHAS_ds_w1', MHAS_ds_w1)
#opal.symbol_import(o,'MHAS_ds_w1', project='_Athlos_Harm_Dataset')

MHAS_m_ds_w1 <- MHAS_ds_w1
MHAS_m_ds_w1$recent_falls <- car::recode(MHAS_m_ds_w1$recent_falls, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'MHAS_m_ds_w1', MHAS_m_ds_w1)
#opal.symbol_import(o,'MHAS_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `c37`
* Label: `Fell in last two years`
* Categories:
   + `1 = Yes`
   + `2 = No`
* Missings
   + `8 = Doesn't answer`
   + `9 = Doesn't know`

```{r assign w2, echo=FALSE}
opal.assign.table.tibble(o, 'MHAS_w2_recent_falls','Mexican Health Aging Study.MHAS_2003', variables=list('c37'), missings = TRUE)
MHAS_w2_recent_falls <- opal.execute(o,'MHAS_w2_recent_falls')
```

```{r local w2, echo=FALSE}
vari <- MHAS_w2_recent_falls$c37
kable(Categorical_summary(vari, missing_values = c(9,8))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(9,8))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9,8))[2], caption = "Type of missing")
ggplot(MHAS_w2_recent_falls, aes(x=factor(c37))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0`
* `8 into 995`
* `9 into 998`

**R script:**

```{r harmo w2}
MHAS_ds_w2 <- tibble(id=MHAS_w2_recent_falls$id)
MHAS_ds_w2$recent_falls <- car::recode(MHAS_w2_recent_falls$c37, "1 = '1';2 = '0';8 = '995';9 = '998' ")
MHAS_ds_w2$recent_falls <- labelled(MHAS_ds_w2$recent_falls, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=FALSE}
vari <- MHAS_ds_w2$recent_falls
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(MHAS_ds_w2, aes(x=factor(recent_falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=FALSE}
AfterH <- table(MHAS_ds_w2$recent_falls)
X<-table(MHAS_w2_recent_falls$c37)
BeforeH <- c(X[c(2,1,3,4)])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1","8->995","9->998") 
kable(C)
```

```{r importOPAL w2, echo=FALSE}
label(MHAS_ds_w2$recent_falls) <- "Recent falls in the last 6-24 months"
recent_falls <- MHAS_ds_w2
save(recent_falls, file = "../RData/w2/recent_falls.RData")
#opal.assign.data(o, 'MHAS_ds_w2', MHAS_ds_w2)
#opal.symbol_import(o,'MHAS_ds_w2', project='_Athlos_Harm_Dataset')

MHAS_m_ds_w2 <- MHAS_ds_w2
MHAS_m_ds_w2$recent_falls <- car::recode(MHAS_m_ds_w2$recent_falls, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'MHAS_m_ds_w2', MHAS_m_ds_w2)
#opal.symbol_import(o,'MHAS_m_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 3

#### Study-specific variable description


The study-specific variables elected to be harmonised is:


* Name: `c37_12`
* Label: `Last 2 years:Has respondent fallen down`
* Categories:
   + `1 = Yes`
   + `2 = No`
* Missings
   + `8 = Doesn't answer`
   + `9 = Doesn't know`
   + `NA`

```{r assign w3, echo=FALSE}
opal.assign.table.tibble(o, 'MHAS_w3_recent_falls','Mexican Health Aging Study.MHAS_2012_new', variables=list('c37_12'), missings = TRUE)
MHAS_w3_recent_falls <- opal.execute(o,'MHAS_w3_recent_falls')
```

```{r local w3, echo=FALSE}
vari <- MHAS_w3_recent_falls$c37_12
kable(Categorical_summary(vari, missing_values = c(9,8))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(9,8))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(9,8))[2], caption = "Type of missing")
ggplot(MHAS_w3_recent_falls, aes(x=factor(c37_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0`
* `8 into 995`
* `9 into 998`
* `NA into 999`

**R script:**

```{r harmo w3}
MHAS_ds_w3 <- tibble(id=MHAS_w3_recent_falls$id)
MHAS_ds_w3$recent_falls <- car::recode(MHAS_w3_recent_falls$c37_12, "1 = '1';2 = '0';8 = '995';9 = '998';NA = '999' ")
MHAS_ds_w3$recent_falls <- labelled(MHAS_ds_w3$recent_falls, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=FALSE}
vari <- MHAS_ds_w3$recent_falls
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(MHAS_ds_w3, aes(x=factor(recent_falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=FALSE}
AfterH <- table(MHAS_ds_w3$recent_falls)
X<-table(MHAS_w3_recent_falls$c37_12)
BeforeH <- c(X[c(2,1,3,4)],sum(is.na(MHAS_w3_recent_falls$c37_12)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1","8->995","9->998","NA->999") 
kable(C)
```

```{r importOPAL w3, echo=FALSE}
label(MHAS_ds_w3$recent_falls) <- "Recent falls in the last 6-24 months"
recent_falls <- MHAS_ds_w3
save(recent_falls, file = "../RData/w3/recent_falls.RData")
#opal.assign.data(o, 'MHAS_ds_w3', MHAS_ds_w3)
#opal.symbol_import(o,'MHAS_ds_w3', project='_Athlos_Harm_Dataset')

MHAS_m_ds_w3 <- MHAS_ds_w3
MHAS_m_ds_w3$recent_falls <- car::recode(MHAS_m_ds_w3$recent_falls, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'MHAS_m_ds_w3', MHAS_m_ds_w3)
#opal.symbol_import(o,'MHAS_m_ds_w3', project='_Athlos_Harm_Dataset')
```

# Quality estimation
Information retrieved from proxy. 

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
