---
title: "Evaluative well-being"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE}
source("../../setup_laia.r")
```

<!-- ########################################################## --> 

```{r main, child='../../_DS_Rmd/evaluative_wbDS.Rmd'}
```


```{r global, echo=F}
source('../../_DS_Rmd/evaluative_wbDS.R')
```


# Data process

## Mexico

### Wave 1

There is no variable. 


### Wave 2

There is no variable. 


### Wave 3

#### Study-specific variable description

| **Name** | `d33c_12` |
|-|-|
| **Label** | `Respondent is satisfied with his/her life`|
| **Table name**  | `MHAS_2012_new`|
| **Categories** | `1 = Agree 1 <br/> 2 = Neutral 2` <br/> `3 = Disagree 3` |
| **Missings** | `8 = RF 8` <br/> `9 = DK 9` |
| **Description** |  | 

```{r assign w3, echo=F}
opal.assign.table.tibble(o, 'MHAS_w3','Mexican Health Aging Study.MHAS_2012_new', variables=list('d33c_12'), missings = T)
MHAS_w3 <- opal.execute(o,'MHAS_w3')
```

```{r local w3, echo=F}

vbl <- MHAS_w3$d33c_12
vbl_miss <- 8:9
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(MHAS_w3)[3])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Missigns Categories")
ggplot(MHAS_w3, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```


#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 2`
* `2 into 1`
* `3 into 0`
* `8 into 998`
* `9 into 997` 
* `NA into 999`

**R script:**

```{r harmo w3}
MHAS_ds_w3 <- tibble(id=MHAS_w3$id)
MHAS_ds_w3$evaluative_wb <- car::recode(MHAS_w3$d33c_12, "1=2; 2=1; 3=0; 8=998; 9=997; NA=999")
```


#### Statistics of the new harmonized variable

```{r descript w3, echo=F}
vbl <- MHAS_ds_w3$evaluative_wb
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w3, aes(x=factor(evaluative_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


#### Validation


# Quality estimation


<!-- # Save -->
```{r save, include=FALSE, echo=F}
evaluative_wb <- MHAS_ds_w3
save(evaluative_wb, file = "M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/MHAS/RData/w3/evaluative_wb.RData")
```

<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





