---
title: "Energy"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `energy`
* Variable label: `Self-reported level of energy`
* Variable description: `Self-reported high level of energy experienced at the time of the interview. Dichotomous variable: 0 refers to lack of energy or presence of fatigue/being listless, and 1 refers to energy in a high level or most of the time`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Lack of energy
1        | High level of energy

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## Mexico

### Wave 1 

#### Study-specific variable description




| **Name** | `c52i`|
|-|-|
| **Label** | `Energy` |
| **Table name** | `MHAS-2001` |
| **Categories** | `1 = Yes; 2 = No` |
| **Missings** | `8 = Doesn't anwser; 9 = Doesn't know; NA` |
| **Description** |  |


```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'MHAS_w1_energy','Mexican Health Aging Study.MHAS-2001', variables=list('c52i'), missings = TRUE)
```

```{r local w1, echo=F}
MHAS_w1_energy <- opal.execute(o,'MHAS_w1_energy')
vari <- MHAS_w1_energy$c52i
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = "c52i")
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
ggplot(MHAS_w1_energy, aes(x=factor(c52i))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Energy") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

  * `1 into 1` 
  * `2 into 0`
  * `8 Doesn't anwser into 995`
  * `9 Doesn't know into 998`
  * `NA into 999`

**R script:**
```{r harmo w1}
MHAS_ds_w1 <- tibble(id=MHAS_w1_energy$id)
MHAS_ds_w1$energy <- car::recode(MHAS_w1_energy$c52i, "1 = '1';2 = '0';8 = '995';9 = '998'; NA = '999' ")
MHAS_ds_w1$energy <- labelled(MHAS_ds_w1$energy, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991, Do_not_know=998))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vari <- MHAS_ds_w1$energy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "energy")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(MHAS_ds_w1, aes(x=factor(energy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Energy") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(MHAS_ds_w1$energy)
X<-table(MHAS_w1_energy$c52i)
BeforeH <- c(X[c(2,1,3,4)],sum(is.na(MHAS_w1_energy$c52i)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1->1","8->995","9->998","NA->999") 
kable(C)
```






```{r importOPAL w1, echo=FALSE}

label(MHAS_ds_w1$energy) <- "Self-reported high level of energy"
#opal.assign.data(o, 'MHAS_ds_w1', MHAS_ds_w1)
#opal.symbol_import(o,'MHAS_ds_w1', project='_Athlos_Harm_Dataset')
energy <- MHAS_ds_w1
save(energy, file = "../RData/w1/energy.RData")

MHAS_m_ds_w1 <- MHAS_ds_w1
MHAS_m_ds_w1$energy <- car::recode(MHAS_m_ds_w1$energy, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'MHAS_m_ds_w1', MHAS_m_ds_w1)
#opal.symbol_import(o,'MHAS_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2

#### Study-specific variable description




| **Name** | `c49_9`|
|-|-|
| **Label** | `Last week's majority emotions - had a lot of energy` |
| **Table name** | `MHAS_2003` |
| **Categories** | `1 = Yes; 2 = No` |
| **Missings** | `8 = Doesn't anwser; 9 = Doesn't know; NA` |
| **Description** |  |


```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'MHAS_w2_energy','Mexican Health Aging Study.MHAS_2003', variables=list('c49_9'), missings = TRUE)
```

```{r local w2, echo=F}
MHAS_w2_energy <- opal.execute(o,'MHAS_w2_energy')
vari <- MHAS_w2_energy$c49_9
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = "c49_9")
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
ggplot(MHAS_w2_energy, aes(x=factor(c49_9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Energy") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

  * `1 into 1` 
  * `2 into 0`
  * `8 Doesn't anwser into 995`
  * `9 Doesn't know into 998`
  * `NA into 999`

**R script:**
```{r harmo w2}
MHAS_ds_w2 <- tibble(id=MHAS_w2_energy$id)
MHAS_ds_w2$energy <- car::recode(MHAS_w2_energy$c49_9, "1 = '1';2 = '0';8 = '995';9 = '998'; NA = '999' ")
MHAS_ds_w2$energy <- labelled(MHAS_ds_w2$energy, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991, Do_not_know=998))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vari <- MHAS_ds_w2$energy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "energy")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(MHAS_ds_w2, aes(x=factor(energy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Energy") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
AfterH <- table(MHAS_ds_w2$energy)
X<-table(MHAS_w2_energy$c49_9)
BeforeH <- c(X[c(2,1,3,4)],sum(is.na(MHAS_w2_energy$c49_9)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1->1","8->995","9->998","NA->999") 
kable(C)
```






```{r importOPAL w2, echo=FALSE}

label(MHAS_ds_w2$energy) <- "Self-reported high level of energy"
#opal.assign.data(o, 'MHAS_ds_w2', MHAS_ds_w2)
#opal.symbol_import(o,'MHAS_ds_w2', project='_Athlos_Harm_Dataset')
energy <- MHAS_ds_w2
save(energy, file = "../RData/w2/energy.RData")

MHAS_m_ds_w2 <- MHAS_ds_w2
MHAS_m_ds_w2$energy <- car::recode(MHAS_m_ds_w2$energy, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'MHAS_m_ds_w2', MHAS_m_ds_w2)
#opal.symbol_import(o,'MHAS_m_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 3

#### Study-specific variable description




| **Name** | `c49_9_12`|
|-|-|
| **Label** | `Within the past week:Respondent was energetic` |
| **Table name** | `MHAS_2012_new` |
| **Categories** | `1 = Yes; 2 = No` |
| **Missings** | `8 = Doesn't anwser; 9 = Doesn't know; NA` |
| **Description** |  |


```{r assign w3, echo=F}
opal.assign.table.tibble(o, 'MHAS_w3_energy','Mexican Health Aging Study.MHAS_2012_new', variables=list('c49_9_12'), missings = TRUE)
```

```{r local w3, echo=F}
MHAS_w3_energy <- opal.execute(o,'MHAS_w3_energy')
vari <- MHAS_w3_energy$c49_9_12
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = "c49_9_12")
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
ggplot(MHAS_w3_energy, aes(x=factor(c49_9_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Energy") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

  * `1 into 1` 
  * `2 into 0`
  * `8 Doesn't anwser into 995`
  * `9 Doesn't know into 998`
  * `NA into 999`

**R script:**
```{r harmo w3}
MHAS_ds_w3 <- tibble(id=MHAS_w3_energy$id)
MHAS_ds_w3$energy <- car::recode(MHAS_w3_energy$c49_9_12, "1 = '1';2 = '0';8 = '995';9 = '998'; NA = '999' ")
MHAS_ds_w3$energy <- labelled(MHAS_ds_w3$energy, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991, Do_not_know=998))
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}
vari <- MHAS_ds_w3$energy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "energy")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(MHAS_ds_w3, aes(x=factor(energy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Energy") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=F}
AfterH <- table(MHAS_ds_w3$energy)
X<-table(MHAS_w3_energy$c49_9_12)
BeforeH <- c(X[c(2,1,3,4)],sum(is.na(MHAS_w3_energy$c49_9_12)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1->1","8->995","9->998","NA->999") 
kable(C)
```






```{r importOPAL w3, echo=FALSE}

label(MHAS_ds_w3$energy) <- "Self-reported high level of energy"
#opal.assign.data(o, 'MHAS_ds_w3', MHAS_ds_w3)
#opal.symbol_import(o,'MHAS_ds_w3', project='_Athlos_Harm_Dataset')
energy <- MHAS_ds_w3
save(energy, file = "../RData/w3/energy.RData")

MHAS_m_ds_w3 <- MHAS_ds_w3
MHAS_m_ds_w3$energy <- car::recode(MHAS_m_ds_w3$energy, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'MHAS_m_ds_w3', MHAS_m_ds_w3)
#opal.symbol_import(o,'MHAS_m_ds_w3', project='_Athlos_Harm_Dataset')
```




# Quality estimation
No comments.



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
