---
title: "Sleep"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `sleep`
* Variable label: `Sleep`
* Variable description: `Sleeping problems.`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## Mexico

### Wave 1 

#### Study-specific variable description




| **Name** | `c52c`|
|-|-|
| **Label** | `restless sleep` |
| **Table name** | `MHAS-2001` |
| **Categories** | `1 = Yes; 2 = No` |
| **Missings** | `8 = Doesn’t answer; 9 = Doesn't know; NA` |
| **Description** |  |


```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'MHAS_w1_sleep','Mexican Health Aging Study.MHAS-2001', variables=list('c52c'), missings = TRUE)
```

```{r local w1, echo=F}
MHAS_w1_sleep <- opal.execute(o,'MHAS_w1_sleep')
vari <- MHAS_w1_sleep$c52c
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = "c52c")
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
ggplot(MHAS_w1_sleep, aes(x=factor(c52c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("restless Sleep") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 1`
* `8 Doesn't answer into 995`
* `9 Doesn't know into 998`
* `NA into 999`

**R script:**
```{r harmo w1}
MHAS_ds_w1 <- tibble(id=MHAS_w1_sleep$id)
MHAS_ds_w1$sleep <- car::recode(MHAS_w1_sleep$c52c, "1 = '0';2 = '1';NA = '999';8 = '995';9 = '998' ")
MHAS_ds_w1$sleep <- labelled(MHAS_ds_w1$sleep, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vari <- MHAS_ds_w1$sleep
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sleep")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(MHAS_ds_w1, aes(x=factor(sleep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sleep") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(MHAS_ds_w1$sleep)
X<-table(MHAS_w1_sleep$c52c)
BeforeH <- c(X[1:4],sum(is.na(MHAS_w1_sleep$c52c)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","2->1","8->995","9->998","NA->999") 
kable(C)
```






```{r importOPAL w1, echo=FALSE}

label(MHAS_ds_w1$sleep) <- "Sleeping problems"
#opal.assign.data(o, 'MHAS_ds_w1', MHAS_ds_w1)
#opal.symbol_import(o,'MHAS_ds_w1', project='_Athlos_Harm_Dataset')
sleep <- MHAS_ds_w1
save(sleep, file = "../RData/w1/sleep.RData")

MHAS_m_ds_w1 <- MHAS_ds_w1
MHAS_m_ds_w1$sleep <- car::recode(MHAS_m_ds_w1$sleep, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'MHAS_m_ds_w1', MHAS_m_ds_w1)
#opal.symbol_import(o,'MHAS_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2

#### Study-specific variable description




| **Name** | `c49_3`|
|-|-|
| **Label** | `Last week's majority emotions - disturbed sleep` |
| **Table name** | `MHAS_2003` |
| **Categories** | `1 = Yes; 2 = No` |
| **Missings** | `8 = Doesn’t answer; 9 = Doesn't know; NA` |
| **Description** |  |


```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'MHAS_w2_sleep','Mexican Health Aging Study.MHAS_2003', variables=list('c49_3'), missings = TRUE)
```

```{r local w2, echo=F}
MHAS_w2_sleep <- opal.execute(o,'MHAS_w2_sleep')
vari <- MHAS_w2_sleep$c49_3
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = "c49_3")
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
ggplot(MHAS_w2_sleep, aes(x=factor(c49_3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("disturbed sleep") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 1`
* `8 Doesn't answer into 995`
* `9 Doesn't know into 998`
* `NA into 999`

**R script:**
```{r harmo w2}
MHAS_ds_w2 <- tibble(id=MHAS_w2_sleep$id)
MHAS_ds_w2$sleep <- car::recode(MHAS_w2_sleep$c49_3, "1 = '0';2 = '1';NA = '999';8 = '995';9 = '998' ")
MHAS_ds_w2$sleep <- labelled(MHAS_ds_w2$sleep, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vari <- MHAS_ds_w2$sleep
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sleep")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(MHAS_ds_w2, aes(x=factor(sleep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sleep") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
AfterH <- table(MHAS_ds_w2$sleep)
X<-table(MHAS_w2_sleep$c49_3)
BeforeH <- c(X[1:4],sum(is.na(MHAS_w2_sleep$c49_3)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","2->1","8->995","9->998","NA->999") 
kable(C)
```






```{r importOPAL w2, echo=FALSE}

label(MHAS_ds_w2$sleep) <- "Sleeping problems"
#opal.assign.data(o, 'MHAS_ds_w2', MHAS_ds_w2)
#opal.symbol_import(o,'MHAS_ds_w2', project='_Athlos_Harm_Dataset')
sleep <- MHAS_ds_w2
save(sleep, file = "../RData/w2/sleep.RData")

MHAS_m_ds_w2 <- MHAS_ds_w2
MHAS_m_ds_w2$sleep <- car::recode(MHAS_m_ds_w2$sleep, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'MHAS_m_ds_w2', MHAS_m_ds_w2)
#opal.symbol_import(o,'MHAS_m_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 3

#### Study-specific variable description




| **Name** | `c49_3_12`|
|-|-|
| **Label** | `Within the past week:Respondent experienced restless sleep` |
| **Table name** | `MHAS_2012_new` |
| **Categories** | `1 = Yes; 2 = No` |
| **Missings** | `8 = Doesn't anwser; 9 = Don't know; NA` |
| **Description** |  |


```{r assign w3, echo=F}
opal.assign.table.tibble(o, 'MHAS_w3_sleep','Mexican Health Aging Study.MHAS_2012_new', variables=list('c49_3_12'), missings = TRUE)
```

```{r local w3, echo=F}
MHAS_w3_sleep <- opal.execute(o,'MHAS_w3_sleep')
vari <- MHAS_w3_sleep$c49_3_12
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = "c49_3_12")
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
ggplot(MHAS_w3_sleep, aes(x=factor(c49_3_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("restless sleep") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `2 into 1`
* `8 Doesn't anwser into 995`
* `9 Don't know into 998`
* `NA into 999`

**R script:**
```{r harmo w3}
MHAS_ds_w3 <- tibble(id=MHAS_w3_sleep$id)
MHAS_ds_w3$sleep <- car::recode(MHAS_w3_sleep$c49_3_12, "1 = '0';2 = '1';3 = '1';NA = '999';8 = '995';9 = '998' ")
MHAS_ds_w3$sleep <- labelled(MHAS_ds_w3$sleep, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}
vari <- MHAS_ds_w3$sleep
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sleep")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(MHAS_ds_w3, aes(x=factor(sleep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Sleep") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=F}
AfterH <- table(MHAS_ds_w3$sleep)
X<-table(MHAS_w3_sleep$c49_3_12)
BeforeH <- c(X[1:4],sum(is.na(MHAS_w3_sleep$c49_3_12)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","2->1","8->995","9->998","NA->999") 
kable(C)
```






```{r importOPAL w3, echo=FALSE}

label(MHAS_ds_w3$sleep) <- "Sleeping problems"
#opal.assign.data(o, 'MHAS_ds_w3', MHAS_ds_w3)
#opal.symbol_import(o,'MHAS_ds_w3', project='_Athlos_Harm_Dataset')
sleep <- MHAS_ds_w3
save(sleep, file = "../RData/w3/sleep.RData")

MHAS_m_ds_w3 <- MHAS_ds_w3
MHAS_m_ds_w3$sleep <- car::recode(MHAS_m_ds_w3$sleep, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'MHAS_m_ds_w3', MHAS_m_ds_w3)
#opal.symbol_import(o,'MHAS_m_ds_w3', project='_Athlos_Harm_Dataset')
```


# Quality estimation
No comments.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
