---
title: "Hearing general"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `hearing_gen`
* Variable label: `Difficulty for hearing`
* Variable description: `It measures if the participant experiences some difficulty for hearing (i.e., hearing someone talking on the other side of the room in a normal voice) or not, using a hearing aid as usual`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## Mexico

### Wave 1 

#### Study-specific variable description




| **Name** | `c47`|
|-|-|
| **Label** | `How is your hearing/auditory range (using hearing aid or auditory device)?` |
| **Table name** | `MHAS-2001` |
| **Categories** | `1 = Excellent; 2 = Very good; 3 = Good; 4 = Fair; 5 = Poor; 6 = Legally deaf` |
| **Missings** | `8 = Non-response; 9 = Don't know; NA` |
| **Description** |  |


```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'MHAS_w1_hearing_gen','Mexican Health Aging Study.MHAS-2001', variables=list('c47'), missings = TRUE)
```

```{r local w1, echo=F}
MHAS_w1_hearing_gen <- opal.execute(o,'MHAS_w1_hearing_gen')
vari <- MHAS_w1_hearing_gen$c47
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = "c47")
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
ggplot(MHAS_w1_hearing_gen, aes(x=factor(c47))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `4,5,6 into 0` 
* `1,2,3 into 1` 
* `8 Non-response into 995`
* `9 Doesn't know into 998`
* `NA into 999`

**R script:**
```{r harmo w1}
MHAS_ds_w1 <- tibble(id=MHAS_w1_hearing_gen$id)
MHAS_ds_w1$hearing_gen <- car::recode(MHAS_w1_hearing_gen$c47, "4 = '0';5 = '0';6 = '0';1 = '1';2 = '1';3 = '1';NA = '999';8 = '995';9 = '998'  ")
MHAS_ds_w1$hearing_gen <- labelled(MHAS_ds_w1$hearing_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vari <- MHAS_ds_w1$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(MHAS_ds_w1, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(MHAS_ds_w1$hearing_gen)
X<-table(MHAS_w1_hearing_gen$c47)
BeforeH <- c(sum(X[4:6]),sum(X[1:3]),X[7:8],sum(is.na(MHAS_w1_hearing_gen$c47)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4,5,6->0","1,2,3->1","8->995","9->998","NA->999")  
kable(C)
```






```{r importOPAL w1, echo=FALSE}

label(MHAS_ds_w1$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 'MHAS_ds_w1', MHAS_ds_w1)
#opal.symbol_import(o,'MHAS_ds_w1', project='_Athlos_Harm_Dataset')
hearing_gen <- MHAS_ds_w1
save(hearing_gen, file = "../RData/w1/hearing_gen.RData")

MHAS_m_ds_w1 <- MHAS_ds_w1
MHAS_m_ds_w1$hearing_gen <- car::recode(MHAS_m_ds_w1$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'MHAS_m_ds_w1', MHAS_m_ds_w1)
#opal.symbol_import(o,'MHAS_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2

#### Study-specific variable description




| **Name** | `c44`|
|-|-|
| **Label** | `How is your hearing/auditory range (using hearing aid or auditory device)?` |
| **Table name** | `MHAS_2003` |
| **Categories** | `1 = Excellent; 2 = Very good; 3 = Good; 4 = Fair; 5 = Poor; 6 = Legally deaf` |
| **Missings** | `8 = Non-response; 9 = Don't know; NA` |
| **Description** |  |

```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'MHAS_w2_hearing_gen','Mexican Health Aging Study.MHAS_2003', variables=list('c44'), missings = TRUE)
```

```{r local w2, echo=F}
MHAS_w2_hearing_gen <- opal.execute(o,'MHAS_w2_hearing_gen')
vari <- MHAS_w2_hearing_gen$c44
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = "c44")
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
ggplot(MHAS_w2_hearing_gen, aes(x=factor(c44))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `4,5,6 into 0` 
* `1,2,3 into 1` 
* `8 Non-response into 995`
* `9 Doesn't know into 998`
* `NA into 999`

**R script:**
```{r harmo w2}
MHAS_ds_w2 <- tibble(id=MHAS_w2_hearing_gen$id)
MHAS_ds_w2$hearing_gen <- car::recode(MHAS_w2_hearing_gen$c44, "4 = '0';5 = '0';6 = '0';1 = '1';2 = '1';3 = '1';NA = '999';8 = '995';9 = '998'  ")
MHAS_ds_w2$hearing_gen <- labelled(MHAS_ds_w2$hearing_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vari <- MHAS_ds_w2$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(MHAS_ds_w2, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
AfterH <- table(MHAS_ds_w2$hearing_gen)
X<-table(MHAS_w2_hearing_gen$c44)
BeforeH <- c(sum(X[4:6]),sum(X[1:3]),X[7:8],sum(is.na(MHAS_w2_hearing_gen$c44)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4,5,6->0","1,2,3->1","8->995","9->998","NA->999")  
kable(C)
```






```{r importOPAL w2, echo=FALSE}

label(MHAS_ds_w2$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 'MHAS_ds_w2', MHAS_ds_w2)
#opal.symbol_import(o,'MHAS_ds_w2', project='_Athlos_Harm_Dataset')
hearing_gen <- MHAS_ds_w2
save(hearing_gen, file = "../RData/w2/hearing_gen.RData")

MHAS_m_ds_w2 <- MHAS_ds_w2
MHAS_m_ds_w2$hearing_gen <- car::recode(MHAS_m_ds_w2$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'MHAS_m_ds_w2', MHAS_m_ds_w2)
#opal.symbol_import(o,'MHAS_m_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 3
In his wave the variable could not be harmonized.



# Quality estimation
The variable which should be harmonized, `c44_12` in the third wave, is not usable since it has an extremely high 
percentage of missing values (99,11%). They are due to a jump from the previous question, 
asking on the hearing difficulty only to the people using auditory devices, which is not a 
representative sample, and not using them does not allow to assume an individual does not suffer hearing difficulty.



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
