---
title: "Eye sight - Near vision"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `eye_near`
* Variable label: `Eyesight - Near vision`
* Variable description: `Difficulties for near vision.`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## India


### Wave 1 

#### Study-specific variable description



| **Name** | `ht078`|`ht076`|
|-|-|-|
| **Label** | `how good is eyesight for things up close` |`glasses or corrective lenses`|
| **Table name** | `LASI-Pilot_all` |`LASI-Pilot_all` |
| **Categories** |`1 = very good; 2 = good; 3 = fair; 4 = poor; 5 = very poor`|`1 = yes; 2 = blind; 3 = no` |
| **Missings** |`NA` |`NA` |
| **Description** |  |  |





```{r assign w1, echo=FALSE}
opal.assign.table.tibble(o, 'LASI_w1_eye_near','LASI.LASI-Pilot_all', variables=list('ht078','ht076'), missings = TRUE)
```

```{r local w1, echo=FALSE}
LASI_w1_eye_near <- opal.execute(o,'LASI_w1_eye_near')
vari <- LASI_w1_eye_near$ht078
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "ht078")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(LASI_w1_eye_near, aes(x=factor(ht078))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Near Vision") + ylab("Frequency")
vari <- LASI_w1_eye_near$ht076
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "ht076")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(LASI_w1_eye_near, aes(x=factor(ht076))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Glasses") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `ht076==2 blind into 0`
* `1, 2 into 1` 
* `3, 4, 5 into 0`
* `NA into 999` 

**R script:**

```{r harmo w1}
LASI_ds_w1 <- tibble(id=LASI_w1_eye_near$id)
LASI_ds_w1$eye_near <- car::recode(LASI_w1_eye_near$ht078, "1 = '1';2 = '1';3 = '0';4 = '0'; 5 = '0';NA = '999' ")
LASI_ds_w1$eye_near[which(LASI_w1_eye_near$ht076==2)] <- 0
LASI_ds_w1$eye_near <- labelled(LASI_ds_w1$eye_near, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

We remark that the blind individuals of the variable `ht076` are missings for the variable `ht078`.


#### Statistical description of the new harmonised variable
```{r descript w1, echo=FALSE}
vari <- LASI_ds_w1$eye_near
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "eye_near")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(LASI_ds_w1, aes(x=factor(eye_near))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Near Vision") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=FALSE}
AfterH <- table(LASI_ds_w1$eye_near)
X<-table(LASI_w1_eye_near$ht078)
BeforeH <- c(sum(X[3:5],length(which(LASI_w1_eye_near$ht076==2))),sum(X[1:2]),sum(is.na(LASI_w1_eye_near$ht078),-length(which(LASI_w1_eye_near$ht076==2))))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3,4,5,blind->0","1,2->1","NA->999")
kable(C)
```


```{r importOPAL w1, echo=FALSE}
label(LASI_ds_w1$eye_near) <- "Eyesight - Near vision"
#opal.assign.data(o, 'LASI_ds_w1', LASI_ds_w1)
#opal.symbol_import(o,'LASI_ds_w1', project='_Athlos_Harm_Dataset')
eye_near <- LASI_ds_w1
save(eye_near, file = "../RData/w1/eye_near.RData")


LASI_m_ds_w1 <- LASI_ds_w1
LASI_m_ds_w1$eye_near <- car::recode(LASI_m_ds_w1$eye_near, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'LASI_m_ds_w1', LASI_m_ds_w1)
#opal.symbol_import(o,'LASI_m_ds_w1', project='_Athlos_Harm_Dataset')
```



# Quality estimation
No comments.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
