---
title: "Mobility - Walking"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `mob_walk`
* Variable label: `Mobility - walking`
* Variable description: `Difficulty for walking by yourself and without using any special equipment`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


# Data process

## India

### Wave 1 

#### Study-specific variable description



| **Name** | `ht402`|
|-|-|
| **Label** | `difficulty walking`|
| **Table name** | `LASI-Pilot_all` |
| **Categories** | `1 = yes; 2 = no` |
| **Missings** | `3 = can't do; 4 = don't want to do; NA` |
| **Description** |  |



```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'LASI_w1_mob_walk','LASI.LASI-Pilot_all', variables=list('ht402'), missings = TRUE)
```

```{r local w1, echo=F}
LASI_w1_mob_walk <- opal.execute(o,'LASI_w1_mob_walk')
vari <- LASI_w1_mob_walk$ht402
kable(Categorical_summary(vari, missing_values = c(3,4))[3], caption = "ht402")
kable(Categorical_summary(vari, missing_values = c(3,4))[1], caption = "Category")
ggplot(LASI_w1_mob_walk, aes(x=factor(ht402))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 yes into 0` 
* `2 no into 1`
* `3 can't do into 996`
* `4 don't want to do into 997`
* `NA into 999`

**R script:**


```{r harmo w1}
LASI_ds_w1 <- tibble(id=LASI_w1_mob_walk$id)
LASI_ds_w1$mob_walk <- car::recode(LASI_w1_mob_walk$ht402, "1 = '0';2 = '1';NA = '999';3 = '996';4 = '997' ")
LASI_ds_w1$mob_walk <- labelled(LASI_ds_w1$mob_walk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vari <- LASI_ds_w1$mob_walk
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_walk")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(LASI_ds_w1, aes(x=factor(mob_walk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(LASI_ds_w1$mob_walk)
X<-table(LASI_w1_mob_walk$ht402)
BeforeH <- c(X[c(1,2,3,4)],sum(is.na(LASI_w1_mob_walk$ht402)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","2->1","3->996","4->997","NA->999") 
kable(C)
```


```{r importOPAL w1, echo=FALSE}
label(LASI_ds_w1$mob_walk) <- "Mobility - walking"
#opal.assign.data(o, 'LASI_ds_w1', LASI_ds_w1)
#opal.symbol_import(o,'LASI_ds_w1', project='_Athlos_Harm_Dataset')
mob_walk <- LASI_ds_w1
save(mob_walk, file = "../RData/w1/mob_walk.RData")

LASI_m_ds_w1 <- LASI_ds_w1
LASI_m_ds_w1$mob_walk <- car::recode(LASI_m_ds_w1$mob_walk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'LASI_m_ds_w1', LASI_m_ds_w1)
#opal.symbol_import(o,'LASI_m_ds_w1', project='_Athlos_Harm_Dataset')
```



# Quality estimation
No unit is given in this study.

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
