---
title: "Cognition - Immediate recall"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `cog_imm_c`
* Variable label: `Cognition - Immediate recall - Continuous`
* Variable description: `Immediate recall of a list of common nouns. The number of words is exactly the same as in the study-specific variable.`
* Domain: `Health status and functional limitations`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


* Short name: `cog_imm`
* Variable label: `Cognition - Immediate recall`
* Variable description: `Immediate recall of a list of common nouns. Discrete variable: value 0 = <=25%; value 1 = >25%.`
* Domain: `Health status and functional limitations`
* Value type: `Categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | <=25%
1        | >25%

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Immediate recall"
ds_label_cog_imm_c <- "Immediate recall of a list of common nouns. The number of words is exactly the same as in the study-specific variable"
ds_label_cog_imm <- "Immediate recall of a list of common nouns. Discrete variable: value 0 = <=25%; value 1 = >25%"
```

# Data process

## India

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `ht505`
* Label: `number of words r correctly recalls`
* Categories:
    + `Continuous Variable 0-10`
* Missings
   + `12 = possible miscoding`
   + `NA` 

```{r assign w1}
opal.assign.table.tibble(o, 'LASI_w1_cog_imm','LASI.LASI-Pilot_all', variables=list('ht505'), missings = TRUE)
LASI_w1_cog_imm <- opal.execute(o,'LASI_w1_cog_imm')
LASI_w1_cog_imm$ht505 <- as.numeric(LASI_w1_cog_imm$ht505)
```

```{r local w1}
vari <- LASI_w1_cog_imm$ht505
kable(Continuous_summary(var = vari, missing_values = c(-8))[3], caption = "Immediate recall continuous")
kable(Continuous_summary(vari, missing_values = c(-8))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-8))$summary, caption = "Summary")
ggplot(LASI_w1_cog_imm, aes(x=factor(ht505))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_imm_c` from the study-specific variable the missing values have to be recoded as follows:

* `12 into 999`
* `NA into 999`

To compute the harmonized variable `cog_imm` from `cog_imm_c` it has to be recoded as follows:

* `cog_imm_c <=25% into 0`
* `cog_imm_c >25% into 1`


```{r harmo w1}
##cog_imm_c
LASI_ds_w1 <- tibble(id=LASI_w1_cog_imm$id)
LASI_ds_w1$cog_imm_c <- car::recode(LASI_w1_cog_imm$ht505, "12=999; NA=999")
LASI_ds_w1$cog_imm_c <- labelled(LASI_ds_w1$cog_imm_c, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))

##cog_imm
Q <- quantile(car::recode(LASI_ds_w1$cog_imm_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

LASI_ds_w1$cog_imm <- car::recode(LASI_ds_w1[[2]], "0:Q=0; (Q+1):10=1")
LASI_ds_w1$cog_imm <- labelled(LASI_ds_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1}
vari <- LASI_ds_w1$cog_imm_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Immediate recall continuous")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(LASI_ds_w1, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- LASI_ds_w1$cog_imm
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Cognition - Immediate recall")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(LASI_ds_w1, aes(x=factor(cog_imm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Immediate recall") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1}
Continous <- c(sum(na.omit(LASI_ds_w1[[2]])<=Q), sum(na.omit(LASI_ds_w1[[2]])>Q & na.omit(LASI_ds_w1[[2]])<900), sum(na.omit(LASI_ds_w1[[2]])==999))
Dicotomic <- table(LASI_ds_w1[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:3->0","4:20->1", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```

#### Quality estimation
[Comments on the quality of the new harmonised variable. This section can be done in a later stage, once all variables are harmonised.]


#### Import to OPAL
```{r importOPAL w1, echo=FALSE}
label(LASI_ds_w1$cog_imm_c) <- ds_label_cog_imm_c
label(LASI_ds_w1$cog_imm) <- ds_label_cog_imm
#opal.assign.data(o, 'LASI_ds_w1', LASI_ds_w1)
#opal.symbol_import(o,'LASI_ds_w1', project='_Athlos_Harm_Dataset')
cog_imm <- LASI_ds_w1
save(cog_imm, file = "../RData/w1/cog_imm.RData")
rm(cog_imm)

LASI_m_ds_w1 <- LASI_ds_w1
LASI_m_ds_w1$cog_imm <- car::recode(LASI_m_ds_w1$cog_imm, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
LASI_m_ds_w1$cog_imm_c <- car::recode(LASI_m_ds_w1$cog_imm_c, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'LASI_m_ds_w1', LASI_m_ds_w1)
#opal.symbol_import(o,'LASI_m_ds_w1', project='_Athlos_Harm_Dataset')
```




# Quality estimation

No commments

[Comments on the quality of the new harmonised variable. This section can be done in a later stage, once all variables are harmonised.]



```{r closeRsession, echo=FALSE}
opal.logout(o)
```

