---
title: "Verbal fluency"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/cog_verbDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/cog_verbDS.R')
```

# Data process

## India

### Wave 1 

#### Study-specific variable description


| **Name** |`ht509`|
|-|-|
| **Label** |`total number of animals named`|
| **Table name** |`LASI-Pilot_all`|
| **Measure** |`Continuous Variable 0-160`|
| **Missings** |`NA`|
| **Description** |  |

```{r assign w1, echo=FALSE}
opal.assign.table.tibble(o, 'LASI_w1_cog_verb','LASI.LASI-Pilot_all', variables=list('ht509'), missings = TRUE)
LASI_w1_cog_verb <- opal.execute(o,'LASI_w1_cog_verb')
```

```{r local w1, echo=FALSE}
vari <- LASI_w1_cog_verb$ht509
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "ht509") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(LASI_w1_cog_verb, aes(x=ht509)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_verb_c` from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

To compute the harmonized variable `cog_verb` from `cog_verb_c` it has to be recoded as follows:

* `cog_verb_c <=25% into 0`
* `cog_verb_c >25% into 1`

**R script:**

```{r harmo w1}
#cog_verb_c
LASI_ds_w1 <- tibble(id=LASI_w1_cog_verb$id)
LASI_ds_w1$cog_verb_c <- car::recode(LASI_w1_cog_verb$ht509, "NA = 999")
LASI_ds_w1$cog_verb_c <- labelled(LASI_ds_w1[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(LASI_ds_w1$cog_verb_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

LASI_ds_w1$cog_verb <- car::recode(LASI_ds_w1[[2]], "0:Q=0; (Q+1):900=1")
LASI_ds_w1$cog_verb <- labelled(LASI_ds_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=FALSE}
vari <- LASI_ds_w1$cog_verb_c
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_verb_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(LASI_ds_w1 %>% filter(!vari %in% miss_values_vector), aes(x=cog_verb_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- LASI_ds_w1$cog_verb
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_verb) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(LASI_ds_w1, aes(x=factor(cog_verb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=FALSE}
Continuous <- c(sum(na.omit(LASI_ds_w1[[2]])<=Q), sum(na.omit(LASI_ds_w1[[2]])>Q & na.omit(LASI_ds_w1[[2]])<900), sum(na.omit(LASI_ds_w1[[2]])==999))
Dichotomous <- table(LASI_ds_w1[[3]], useNA = "ifany")
C <- rbind(Continuous,Dichotomous)
colnames(C) <- c("0:6->0","7:160->1", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```


```{r importOPAL w1, echo=FALSE}
#label(LASI_ds_w1$cog_verb) <- "Cognition - verbal fluency"
#opal.assign.data(o, 'LASI_ds_w1', LASI_ds_w1)
#opal.symbol_import(o,'LASI_ds_w1', project='_Athlos_Harm_Dataset')

label(LASI_ds_w1$cog_verb_c) <- ds_label_cog_verb_c
label(LASI_ds_w1$cog_verb) <- ds_label_cog_verb
cog_verb <- LASI_ds_w1
save(cog_verb, file = "../RData/w1/cog_verb.RData")
```


# Quality estimation

No comments




```{r closeRsession, echo=FALSE}
opal.logout(o)
```

