---
title: "Orientation in time"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `orientation`
* Variable label: `Orientation in time`
* Variable description: `Difficulties for orientation in time, evaluated by a set of questions about the date and day of the week.`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


# Data process

## India

### Wave 1

#### Study-specific variable description


| **Name** |`ht501_day`|`ht501_month`|`ht501_year`|
|-|-|-|-|
| **Label** |`today's day`|`today's month`|`today's year`|
| **Table name** |`LASI-Pilot_all`|`LASI-Pilot_all`|`LASI-Pilot_all`|
| **Categories** |`1 = yes; 2 = no`|`1 = yes; 2 = no`|`1 = yes; 2 = no`|
| **Missings** |`NA`|`NA`|`NA`|
| **Description** |  |  |  |


```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'LASI_w1_orientation','LASI.LASI-Pilot_all', variables=list('ht501_day','ht501_month','ht501_year'), missings = TRUE)
```

```{r local w1, echo=F}
LASI_w1_orientation <- opal.execute(o,'LASI_w1_orientation')
vari <- LASI_w1_orientation$ht501_day
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "ht501_day")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(LASI_w1_orientation, aes(x=factor(ht501_day))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-Day") + ylab("Frequency")
vari <- LASI_w1_orientation$ht501_month
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "ht501_month")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(LASI_w1_orientation, aes(x=factor(ht501_month))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-Month") + ylab("Frequency")
vari <- LASI_w1_orientation$ht501_year
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "ht501_year")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(LASI_w1_orientation, aes(x=factor(ht501_year))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-Year") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `all 1 into 1` 
* `some 2 into 0`
* `NA into 999`

**R script:**

```{r harmo w1}
LASI_ds_w1 <- tibble(id=LASI_w1_orientation$id)
LASI_ds_w1$orientation <- rep(999,length(LASI_ds_w1$id))
LASI_ds_w1$orientation[((LASI_w1_orientation$ht501_day==1)&(LASI_w1_orientation$ht501_month==1)&(LASI_w1_orientation$ht501_year==1))]<-1
LASI_ds_w1$orientation[((LASI_w1_orientation$ht501_day==2)|(LASI_w1_orientation$ht501_month==2)|(LASI_w1_orientation$ht501_year==2))]<- 0
LASI_ds_w1$orientation <- labelled(LASI_ds_w1$orientation, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vari <- LASI_ds_w1$orientation
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "orientation")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(LASI_ds_w1, aes(x=factor(orientation))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(LASI_ds_w1$orientation)
combi<-sum(na.omit((LASI_w1_orientation$ht501_day==1)&(LASI_w1_orientation$ht501_month==1)&(LASI_w1_orientation$ht501_year==1)))
nota<-length(LASI_w1_orientation$ht501_day)-length(na.omit(LASI_w1_orientation$ht501_day))
BeforeH <- c(length(LASI_w1_orientation$ht501_day)-combi-nota,combi,nota)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("some 2->0","all 1->1","NA->999") 
kable(C)
```



```{r importOPAL w1, echo=FALSE}
label(LASI_ds_w1$orientation) <- "Difficulties for orientation in time, evaluated by a set of questions about the date and day of the week"
#opal.assign.data(o, 'LASI_ds_w1', LASI_ds_w1)
#opal.symbol_import(o,'LASI_ds_w1', project='_Athlos_Harm_Dataset')
orientation <- LASI_ds_w1
save(orientation, file = "../RData/w1/orientation.RData")

LASI_m_ds_w1 <- LASI_ds_w1
LASI_m_ds_w1$orientation <- car::recode(LASI_m_ds_w1$orientation, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'LASI_m_ds_w1', LASI_m_ds_w1)
#opal.symbol_import(o,'LASI_m_ds_w1', project='_Athlos_Harm_Dataset')
```




# Quality estimation
For this study, the variable is a composed combining day, month, 
and year which is different from the 
calculation performed in other studies other variables are also available 
(or some of these variables are not).



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
