---
title: "Delayed recall"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/cog_delDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/cog_delDS.R')
```

# Data process

## India

### Wave 1 

#### Study-specific variable description



| **Name** |`ht520`|
|-|-|
| **Label** |`number of words r correctly recalls`|
| **Table name** |`LASI-Pilot_all`|
| **Categories** |`Continuous Variable 0-10`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign w1, echo=FALSE}
opal.assign.table.tibble(o, 'LASI_w1_cog_del','LASI.LASI-Pilot_all', variables=list('ht520'), missings = TRUE)
LASI_w1_cog_del <- opal.execute(o,'LASI_w1_cog_del')
```

```{r local w1, echo=FALSE}
vari <- LASI_w1_cog_del$ht520
kable(Continuous_summary(var = vari, missing_values = NA)[3], caption = "ht520")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(LASI_w1_cog_del, aes(x=factor(ht520))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable `cog_del_c` from the study-specific variables you have to sum the total of words and the missing values have to be recoded as follows:

* `NA into 999`

To compute the harmonized variable `cog_del` from `cog_del_c` it has to be recoded as follows:

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**

```{r harmo w1}
##cog_del_c
LASI_ds_w1 <- tibble(id=LASI_w1_cog_del$id)
LASI_ds_w1$cog_del_c <- car::recode(LASI_w1_cog_del$ht520, "NA = '999' ")
LASI_ds_w1$cog_del_c <- labelled(LASI_ds_w1$cog_del_c, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995, Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))

##cog_del
Q <- quantile(car::recode(LASI_ds_w1$cog_del_c, "999=NA; 998=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

LASI_ds_w1$cog_del <- car::recode(LASI_ds_w1[[2]], "0:Q=0; (Q+1):10=1")
LASI_ds_w1$cog_del <- labelled(LASI_ds_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995, "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=FALSE}
vari <- LASI_ds_w1$cog_del_c
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(LASI_ds_w1 %>% filter(!vari %in% miss_values_vector), aes(x=cog_del_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- LASI_ds_w1$cog_del
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_del) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(LASI_ds_w1, aes(x=factor(cog_del))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=FALSE}
Continuous <- c(sum(na.omit(LASI_ds_w1[[2]])<=Q), sum(na.omit(LASI_ds_w1[[2]])>Q&na.omit(LASI_ds_w1[[2]])<900), sum(na.omit(LASI_ds_w1[[2]])==999))
Dichotomous <- table(LASI_ds_w1[[3]], useNA = "ifany")
C <- rbind(Continuous,Dichotomous)
colnames(C) <- c("0:3->0","4:20->1", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```




```{r importOPAL w1, echo=FALSE}

cog_del <- LASI_ds_w1
save(cog_del, file = "../RData/w1/cog_del.RData")
rm(cog_del)

```



# Quality estimation

No comments





```{r closeRsession, echo=FALSE}
opal.logout(o)
```

