---
title: "Numeracy"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_laia.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `cog_num_c`
* Variable label: `Cognition - numeracy test - Continuous. It is assessed by means of a numeracy test, composed by six numeracy questions`
* Domain: `Health status and functional limitations`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



* Short name: `cog_num`
* Variable label: `Cognition - numeracy test. It is assessed by means of a numeracy test, composed by six numeracy questions. Discrete variable: value 0 = <=25%; value 1 = >25%.`
* Domain: `Health status and functional limitations`
* Value type: `Categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | <=25%
1        | >25%

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Cognition - numeracy test"
ds_label_cog_num_c <- "Cognition - numeracy test - Continuous. It is assessed by means of a numeracy test, composed by six numeracy questions"
ds_label_cog_num <- "Cognition - numeracy test. It is assessed by means of a numeracy test, composed by six numeracy questions. Discrete variable: value 0 = <=25%; value 1 = >25%"
```



<!-- ########################################################## --> 

# Data process

## India

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `ht518`
* Label: `sari math problem "How much does 300 Rs sari cost at half price?"`
* Categories:
    + `1 = the correct answer of 150 rs`
    + `2 = incorrect answer`
* Missings
   + `NA` 

* Name: `ht519`
* Label: `lottery problem "If 5 people have  the winning numbers in the lottery how much of the 1,000 Rs prize will each get?"`
* Categories:
    + `1 = the correct answer of 200 rs`
    + `2 = incorrect answer`
* Missings
   + `NA` 


```{r assign w1, echo=FALSE}
opal.assign.table.tibble(o, 'LASI_w1_cog_num','LASI.LASI-Pilot_all', variables=list('ht518','ht519'), missings = TRUE)
LASI_w1_cog_num <- opal.execute(o,'LASI_w1_cog_num')
```

```{r local w1, echo=FALSE}
vari <- LASI_w1_cog_num$ht518
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(LASI_w1_cog_num, aes(x=factor(ht518))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Numeracy") + ylab("Frequency")

vari <- LASI_w1_cog_num$ht519
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(LASI_w1_cog_num, aes(x=factor(ht519))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Numeracy") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_num_c` from the study-specific variables sum them after recoded as follows

* `keep 1 into 1`
* `recode 2 into 0`

and the missing values have to be recoded as follows:

* `NA into 999`

To compute the harmonized variable `cog_num` from `cog_num_c` it has to be recoded as follows:

* `all 1 into 1` 
* `other into 0` 
* `NA into 999`

**R script:**

```{r harmo w1}
LASI_w1_cog_num$ht518_2 <- car::recode(LASI_w1_cog_num$ht518, "2=0")
LASI_w1_cog_num$ht519_2 <- car::recode(LASI_w1_cog_num$ht519, "2=0")
LASI_w1_cog_num$sum <- apply(LASI_w1_cog_num[,c(4,5)], MARGIN = 1, FUN = sum)

#all the individuals have all missing or all no missing
LASI_w1_cog_num$comp <- apply(LASI_w1_cog_num[,c(4,5)], MARGIN = 1, FUN = function(x) sum(is.na(x)) )

#cog_num_c
LASI_ds_w1 <- tibble(id=LASI_w1_cog_num$id)
LASI_ds_w1$cog_num_c <- car::recode(LASI_w1_cog_num$sum, "NA=999")
LASI_ds_w1$cog_num_c <- labelled(LASI_ds_w1[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_num
LASI_ds_w1$cog_num <- car::recode(LASI_ds_w1$cog_num_c, "2=1; 1=0")
LASI_ds_w1$cog_num <- labelled(LASI_ds_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=FALSE}
vari <- LASI_ds_w1$cog_num_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(LASI_ds_w1, aes(x=factor(cog_num_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Numeracy") + ylab("Frequency")

vari <- LASI_ds_w1$cog_num
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(LASI_ds_w1, aes(x=factor(cog_num))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Numeracy") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=FALSE}
Continous <- table(LASI_ds_w1$cog_num_c)
Continous <- c(sum(Continous[1:2]),Continous[3], Continous[4])
Dicotomic <- table(LASI_ds_w1[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("(0,1)->0","2->1", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL w1, echo=FALSE}
#opal.assign.data(o, 'LASI_ds_w1', LASI_ds_w1)
#opal.symbol_import(o,'LASI_ds_w1', project='_Athlos_Harm_Dataset')

label(LASI_ds_w1$cog_num_c) <- ds_label_cog_num_c
label(LASI_ds_w1$cog_num) <- ds_label_cog_num
cog_num <- LASI_ds_w1
save(cog_num, file = "../RData/w1/cog_num.RData")
```



# Quality estimation

No comments

[Comments on the quality of the new harmonised variable. This section can be done in a later stage, once all variables are harmonised.]



```{r closeRsession, echo=FALSE}
opal.logout(o)
```

