---
title: "Consequences of falls"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_laia.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `conseq_falls`
* Variable label: `Consequences of falls`
* Variable description: `Consequences of falls (injury, treatment,.)`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Consequences of falls"
ds_label_all <- "Consequences of falls (injury, treatment,.)"
```

# Data process

## LASI

### Wave 1 	

#### Study-specific variable description


The study-specific variables elected to be harmonised is:

* Name: `ht063`
* Label: `medical treatment for injury from recent fall`
* Categories:
   + `1 = yes`
   + `2 = no`
* Missings
   + `NA`

```{r assign w1, echo=FALSE}
opal.assign.table.tibble(o, 'LASI_w1_conseq_falls','LASI.LASI-Pilot_all', variables=list('ht063'), missings = TRUE)
LASI_w1_conseq_falls <- opal.execute(o,'LASI_w1_conseq_falls')
```

```{r local w1, echo=FALSE}
vari <- LASI_w1_conseq_falls$ht063
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(LASI_w1_conseq_falls, aes(x=factor(ht063))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Consequences of Falls") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0`
* `NA into 999`

**R script:**

```{r harmo w1}
LASI_ds_w1 <- tibble(id=LASI_w1_conseq_falls$id)
LASI_ds_w1$conseq_falls <- car::recode(LASI_w1_conseq_falls$ht063, "1 = '1';2 = '0';NA = '999' ")
LASI_ds_w1$conseq_falls <- labelled(LASI_ds_w1$conseq_falls, labels = c("No"=0, "Yes"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=FALSE}
vari <- LASI_ds_w1$conseq_falls
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(LASI_ds_w1, aes(x=factor(conseq_falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Consequences of Falls") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=FALSE}
AfterH <- table(LASI_ds_w1$conseq_falls)
X<-table(LASI_w1_conseq_falls$ht063)
BeforeH <- c(X[c(2,1)],sum(is.na(LASI_w1_conseq_falls$ht063)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1","NA->999") 
kable(C)
```


```{r importOPAL w1, echo=FALSE}
label(LASI_ds_w1$conseq_falls) <- "Consequences of falls (injury, treatment,.)"
conseq_falls <- LASI_ds_w1
save(conseq_falls, file = "../RData/w1/conseq_falls.RData")
#opal.assign.data(o, 'LASI_ds_w1', LASI_ds_w1)
#opal.symbol_import(o,'LASI_ds_w1', project='_Athlos_Harm_Dataset')

LASI_m_ds_w1 <- LASI_ds_w1
LASI_m_ds_w1$conseq_falls <- car::recode(LASI_m_ds_w1$conseq_falls, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'LASI_m_ds_w1', LASI_m_ds_w1)
#opal.symbol_import(o,'LASI_m_ds_w1', project='_Athlos_Harm_Dataset')
```


# Quality estimation
The variable selected in this study refers to medical treatment for injury from recent fall" but does not collect other consecuences of falls.

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
