---
title: "Eudaimonic well-being"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/eudaimonic_wbDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/eudaimonic_wbDS.R')
```


# Data process

## India

### Wave 1 

#### Study-specific variable description

| **Name** | `fs611` |
|-|-|
| **Label** | `so far, i have gotten the important things i want in life` |
| **Table name** | `LASI-Pilot_all` |
| **Categories:**| `1 =  strongly disagree` <br/> `2 = somewhat disagree` <br/> `3 = slightly disagree` <br/> `4 = neither agree nor disagree` <br/> `5 = slightly agree` <br/> `6 = somewhat agree` <br/> `7 = strongly agree`|
| **Missings:**| `8 = dk` <br/> `9 = rf` |
| **Description** |  | 


```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'LASI_w1','LASI.LASI-Pilot_all', variables=list('fs611'), missings = TRUE)
LASI_w1 <- opal.execute(o,'LASI_w1')
```

```{r local w1, echo=F}
vbl <- LASI_w1$fs611
vbl_miss <- 8:9
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(LASI_w1)[2])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Missigns Categories")
ggplot(LASI_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") 
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 0`
* `3,4,5 into 1`
* `6,7 into 2`
* `8 into 998`
* `9 into 997` 
* `NA into 999`

**R script:**

```{r harmo w1}
LASI_ds_w1 <- tibble(id=LASI_w1$id)
LASI_ds_w1$eudaimonic_wb <- car::recode(LASI_w1$fs611, "1=0; 2=0; 3=1; 4=1; 5=1; 6=2; 7=2; 8=998; 9=997; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vbl <- LASI_ds_w1$eudaimonic_wb
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(LASI_ds_w1, aes(x=factor(eudaimonic_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
```




## Summary of descriptive statistics of the harmonised variable accross populations and waves


Percentages of categories in each harmonised variable.




```{r helpfunctions, echo=F}

source("../../helpfunctions.r")

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


lasi.cw <- list(w1 = c("w1","W1"))

# Consider only harmonised waves
l.hds <- lapply(lasi.cw, function(wname) if(exists(paste0("LASI_ds_",wname[1]))){wname = list(get(paste0("LASI_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],sapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  # f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  # print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```



# Quality estimation
 


<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
