---
title: "Energy"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `energy`
* Variable label: `Self-reported level of energy`
* Variable description: `Self-reported high level of energy experienced at the time of the interview. Dichotomous variable: 0 refers to lack of energy or presence of fatigue/being listless, and 1 refers to energy in a high level or most of the time`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Lack of energy
1        | High level of energy

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## India

### Wave 1 

##### Study-specific variable description





| **Name** | `ht307`|
|-|-|
| **Label** | `felt everything was an effort` |
| **Table name** | `LASI-Pilot_all` |
| **Categories** | `1 = rarely or none of the time; less than 1 day; 2 = some or little of the time; 1 to 2 days; 3 = occasionally or a moderate amount of the time; 3 to 4 days; 4 = most or all of the time; 5 to 7 days` |
| **Missings** | `5 = dk; 6 = rf; NA` |
| **Description** |  |

```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'LASI_w1_energy','LASI.LASI-Pilot_all', variables=list('ht307'), missings = TRUE)
```

```{r local w1, echo=F}
LASI_w1_energy <- opal.execute(o,'LASI_w1_energy')

vari <- LASI_w1_energy$ht307
kable(Categorical_summary(vari, missing_values = c(5,6))[3], caption = "ht307") # SI NO HAY ATRIBUTO SHORT-NAME, A MANO
kable(Categorical_summary(vari, missing_values = c(5,6))[1], caption = "Category")


ggplot(LASI_w1_energy, aes(x=factor(ht307))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Energy") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

  * `1 into 1` 
  * `2,3,4 into 0`
  * `5 dk into 998`
  * `6 rf into 997`
  * `NA into 999`

**R script:**

```{r harmo w1}
LASI_ds_w1 <- tibble(id=LASI_w1_energy$id)
LASI_ds_w1$energy <- car::recode(LASI_w1_energy$ht307, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '998';6 = '997'; NA = '999' ")
LASI_ds_w1$energy <- labelled(LASI_ds_w1$energy, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991, Do_not_know=998))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}

vari <- LASI_ds_w1$energy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "energy")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")

ggplot(LASI_ds_w1, aes(x=factor(energy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Energy") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(LASI_ds_w1$energy)
X<-table(LASI_w1_energy$ht307)
BeforeH <- c(sum(X[2:4]),X[c(1,6,5)],sum(is.na(LASI_w1_energy$ht307)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4->0","1->1","6->997","5->998","NA->999") 
kable(C)
```


```{r importOPAL w1, echo=FALSE}
label(LASI_ds_w1$energy) <- "Self-reported high level of energy"
#opal.assign.data(o, 'LASI_ds_w1', LASI_ds_w1)
#opal.symbol_import(o,'LASI_ds_w1', project='_Athlos_Harm_Dataset')
energy <- LASI_ds_w1
save(energy, file = "../RData/w1/energy.RData")

LASI_m_ds_w1 <- LASI_ds_w1
LASI_m_ds_w1$energy <- car::recode(LASI_m_ds_w1$energy, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'LASI_m_ds_w1', LASI_m_ds_w1)
#opal.symbol_import(o,'LASI_m_ds_w1', project='_Athlos_Harm_Dataset')
```



# Quality estimation
No comments.



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
