---
title: "Hearing general"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `hearing_gen`
* Variable label: `Difficulty for hearing`
* Variable description: `It measures if the participant experiences some difficulty for hearing (i.e., hearing someone talking on the other side of the room in a normal voice) or not, using a hearing aid as usual`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## India


### Wave 1 

#### Study-specific variable description




| **Name** | `ht082`|
|-|-|
| **Label** | `can you hear normal voice with hearing aid` |
| **Table name** | `LASI-Pilot_all` |
| **Categories** | `1 = yes; 2 = no` |
| **Missings** | `NA` |
| **Description** |  |



```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'LASI_w1_hearing_gen','LASI.LASI-Pilot_all', variables=list('ht082'), missings = TRUE)
```

```{r local w1, echo=F}
LASI_w1_hearing_gen <- opal.execute(o,'LASI_w1_hearing_gen')
vari <- LASI_w1_hearing_gen$ht082
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "ht082")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(LASI_w1_hearing_gen, aes(x=factor(ht082))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 0` 
* `NA into 999`

**R script:**

```{r harmo w1}
LASI_ds_w1 <- tibble(id=LASI_w1_hearing_gen$id)
LASI_ds_w1$hearing_gen <- car::recode(LASI_w1_hearing_gen$ht082, "1 = '1';2 = '0';NA = '999' ")
LASI_ds_w1$hearing_gen <- labelled(LASI_ds_w1$hearing_gen, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vari <- LASI_ds_w1$hearing_gen
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_gen")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(LASI_ds_w1, aes(x=factor(hearing_gen))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - General") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(LASI_ds_w1$hearing_gen)
X<-table(LASI_w1_hearing_gen$ht082)
BeforeH <- c(X[2:1],sum(is.na(LASI_w1_hearing_gen$ht082)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","NA->999")  
kable(C)
```


```{r importOPAL w1, echo=FALSE}
label(LASI_ds_w1$hearing_gen) <- "Difficulty for hearing"
#opal.assign.data(o, 'LASI_ds_w1', LASI_ds_w1)
#opal.symbol_import(o,'LASI_ds_w1', project='_Athlos_Harm_Dataset')
hearing_gen <- LASI_ds_w1
save(hearing_gen, file = "../RData/w1/hearing_gen.RData")

LASI_m_ds_w1 <- LASI_ds_w1
LASI_m_ds_w1$hearing_gen <- car::recode(LASI_m_ds_w1$hearing_gen, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'LASI_m_ds_w1', LASI_m_ds_w1)
#opal.symbol_import(o,'LASI_m_ds_w1', project='_Athlos_Harm_Dataset')
```



# Quality estimation
In this study the variable collects the hearing/auditory range of the respondent "using hearing aid 
or auditory device", while in other studies the exact question is "with or without it".



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
