---
title: "Emotional support"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/emot_supDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/emot_supDS.R')
```

<!-- ########################################################## --> 

# Data process


## Finland

### Wave 1 

#### Study-specific variable description


| **Name** |`KYS1_K680201`|`KYS1_K680202`|`KYS1_K680203`|`KYS1_K680204`|`KYS1_K680205`|`KYS1_K680206`|`KYS1_K680301`|`KYS1_K680302`|`KYS1_K680303`|`KYS1_K680304`|`KYS1_K680305`|`KYS1_K680306`|
|-|-|-|-|-|-|-|-|-|-|-|-|-|
| **Label** |`Help no matter what happened: spouse`|`Help no matter what happened: other relative`|`Help no matter what happened: close friend`|`Help no matter what happened: close colleague`|`Help no matter what happened: close neighbour`|`Help no matter what happened: other close person`|`Reliable help: spouse`|`Reliable help: other relative`|`Reliable help: close friend`|`Reliable help: close colleague`|`Reliable help: close neighbour`|`Reliable help: other close person`|
| **Table name** |`t00_athlos_2017_02_23`|`t00_athlos_2017_02_23`|`t00_athlos_2017_02_23`|`t00_athlos_2017_02_23`|`t00_athlos_2017_02_23`|`t00_athlos_2017_02_23`|`t00_athlos_2017_02_23`|`t00_athlos_2017_02_23`|`t00_athlos_2017_02_23`|`t00_athlos_2017_02_23`|`t00_athlos_2017_02_23`|`t00_athlos_2017_02_23`|
| **Categories** |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|
| **Description** |  |  |  |  |  |  |  |  |  |  |  |  |



    
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'Health20002011_w1_emot_sup','Health2000-2011.t00_athlos_2017_02_23', variables=list('KYS1_K680201','KYS1_K680202','KYS1_K680203','KYS1_K680204','KYS1_K680205','KYS1_K680206','KYS1_K680301','KYS1_K680302','KYS1_K680303','KYS1_K680304','KYS1_K680305','KYS1_K680306'), missings = TRUE)
Health20002011_w1_emot_sup <- opal.execute(o,'Health20002011_w1_emot_sup')
```

```{r local1, echo=F}

vbl_miss<- c(NA)

vbl <- Health20002011_w1_emot_sup$KYS1_K680201
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'KYS1_K680201')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(Health20002011_w1_emot_sup, aes(x=factor(KYS1_K680201))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w1_emot_sup$KYS1_K680202
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'KYS1_K680202')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(Health20002011_w1_emot_sup, aes(x=factor(KYS1_K680202))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w1_emot_sup$KYS1_K680203
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'KYS1_K680203')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(Health20002011_w1_emot_sup, aes(x=factor(KYS1_K680203))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w1_emot_sup$KYS1_K680204
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'KYS1_K680204')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(Health20002011_w1_emot_sup, aes(x=factor(KYS1_K680204))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w1_emot_sup$KYS1_K680205
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'KYS1_K680205')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(Health20002011_w1_emot_sup, aes(x=factor(KYS1_K680205))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w1_emot_sup$KYS1_K680206
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'KYS1_K680206')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(Health20002011_w1_emot_sup, aes(x=factor(KYS1_K680206))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w1_emot_sup$KYS1_K680301
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'KYS1_K680301')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(Health20002011_w1_emot_sup, aes(x=factor(KYS1_K680301))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w1_emot_sup$KYS1_K680302
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'KYS1_K680302')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(Health20002011_w1_emot_sup, aes(x=factor(KYS1_K680302))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w1_emot_sup$KYS1_K680303
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'KYS1_K680303')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(Health20002011_w1_emot_sup, aes(x=factor(KYS1_K680303))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w1_emot_sup$KYS1_K680304
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'KYS1_K680304')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(Health20002011_w1_emot_sup, aes(x=factor(KYS1_K680304))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w1_emot_sup$KYS1_K680305
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'KYS1_K680305')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(Health20002011_w1_emot_sup, aes(x=factor(KYS1_K680305))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w1_emot_sup$KYS1_K680306
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'KYS1_K680306')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(Health20002011_w1_emot_sup, aes(x=factor(KYS1_K680306))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 then 1`
* `else if all are equal 0 then 0`
* `NA into 999`

**R script:**

```{r harmo1}
Health20002011_ds_w1 <- tibble(id=Health20002011_w1_emot_sup$id)

Health20002011_w1_emot_sup$KYS1_K680201 <- car::recode(as.vector(Health20002011_w1_emot_sup$KYS1_K680201), "NA='-999'")
Health20002011_w1_emot_sup$KYS1_K680202 <- car::recode(as.vector(Health20002011_w1_emot_sup$KYS1_K680202), "NA='-999'")
Health20002011_w1_emot_sup$KYS1_K680203 <- car::recode(as.vector(Health20002011_w1_emot_sup$KYS1_K680203), "NA='-999'")
Health20002011_w1_emot_sup$KYS1_K680204 <- car::recode(as.vector(Health20002011_w1_emot_sup$KYS1_K680204), "NA='-999'")
Health20002011_w1_emot_sup$KYS1_K680205 <- car::recode(as.vector(Health20002011_w1_emot_sup$KYS1_K680205), "NA='-999'")
Health20002011_w1_emot_sup$KYS1_K680206 <- car::recode(as.vector(Health20002011_w1_emot_sup$KYS1_K680206), "NA='-999'")
Health20002011_w1_emot_sup$KYS1_K680301 <- car::recode(as.vector(Health20002011_w1_emot_sup$KYS1_K680301), "NA='-999'")
Health20002011_w1_emot_sup$KYS1_K680302 <- car::recode(as.vector(Health20002011_w1_emot_sup$KYS1_K680302), "NA='-999'")
Health20002011_w1_emot_sup$KYS1_K680303 <- car::recode(as.vector(Health20002011_w1_emot_sup$KYS1_K680303), "NA='-999'")
Health20002011_w1_emot_sup$KYS1_K680304 <- car::recode(as.vector(Health20002011_w1_emot_sup$KYS1_K680304), "NA='-999'")
Health20002011_w1_emot_sup$KYS1_K680305 <- car::recode(as.vector(Health20002011_w1_emot_sup$KYS1_K680305), "NA='-999'")
Health20002011_w1_emot_sup$KYS1_K680306 <- car::recode(as.vector(Health20002011_w1_emot_sup$KYS1_K680306), "NA='-999'")

Health20002011_ds_w1$emot_sup <- c(NA)
for(i in 1:dim(Health20002011_w1_emot_sup)[1]){
  if( Health20002011_w1_emot_sup$KYS1_K680201[i] == 1 | Health20002011_w1_emot_sup$KYS1_K680202[i] == 1 | Health20002011_w1_emot_sup$KYS1_K680203[i] == 1 | 
    Health20002011_w1_emot_sup$KYS1_K680204[i] == 1 | Health20002011_w1_emot_sup$KYS1_K680205[i] == 1 | Health20002011_w1_emot_sup$KYS1_K680206[i] == 1 | 
    Health20002011_w1_emot_sup$KYS1_K680301[i] == 1 | Health20002011_w1_emot_sup$KYS1_K680302[i] == 1 | Health20002011_w1_emot_sup$KYS1_K680303[i] == 1 | 
    Health20002011_w1_emot_sup$KYS1_K680304[i] == 1 | Health20002011_w1_emot_sup$KYS1_K680305[i] == 1 | Health20002011_w1_emot_sup$KYS1_K680306[i] == 1 ) { 
  Health20002011_ds_w1$emot_sup[i] = 1 }
  else if( Health20002011_w1_emot_sup$KYS1_K680201[i] == -999 & Health20002011_w1_emot_sup$KYS1_K680202[i] == -999 & Health20002011_w1_emot_sup$KYS1_K680203[i] == -999 & 
    Health20002011_w1_emot_sup$KYS1_K680204[i] == -999 & Health20002011_w1_emot_sup$KYS1_K680205[i] == -999 & Health20002011_w1_emot_sup$KYS1_K680206[i] == -999 & 
    Health20002011_w1_emot_sup$KYS1_K680301[i] == -999 & Health20002011_w1_emot_sup$KYS1_K680302[i] == -999 & Health20002011_w1_emot_sup$KYS1_K680303[i] == -999 & 
    Health20002011_w1_emot_sup$KYS1_K680304[i] == -999 & Health20002011_w1_emot_sup$KYS1_K680305[i] == -999 & Health20002011_w1_emot_sup$KYS1_K680306[i] == -999 ) { 
  Health20002011_ds_w1$emot_sup[i] = 999 }
  else if( Health20002011_w1_emot_sup$KYS1_K680201[i] == 0 | Health20002011_w1_emot_sup$KYS1_K680202[i] == 0 | Health20002011_w1_emot_sup$KYS1_K680203[i] == 0 | 
    Health20002011_w1_emot_sup$KYS1_K680204[i] == 0 | Health20002011_w1_emot_sup$KYS1_K680205[i] == 0 | Health20002011_w1_emot_sup$KYS1_K680206[i] == 0 |
    Health20002011_w1_emot_sup$KYS1_K680301[i] == 0 | Health20002011_w1_emot_sup$KYS1_K680302[i] == 0 | Health20002011_w1_emot_sup$KYS1_K680303[i] == 0 | 
    Health20002011_w1_emot_sup$KYS1_K680304[i] == 0 | Health20002011_w1_emot_sup$KYS1_K680305[i] == 0 | Health20002011_w1_emot_sup$KYS1_K680306[i] == 0 ) { 
  Health20002011_ds_w1$emot_sup[i] = 0 }
}

Health20002011_ds_w1$emot_sup <- car::recode(as.vector(Health20002011_ds_w1$emot_sup), "NA='999'")
Health20002011_ds_w1$emot_sup <- labelled(Health20002011_ds_w1$emot_sup, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}

vbl <- Health20002011_ds_w1$emot_sup
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(Health20002011_ds_w1, aes(x=factor(emot_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation1, echo=F}

```



### Wave 2

#### Study-specific variable description


| **Name** |`KYS1_K680201`|`KYS1_K680202`|`KYS1_K680203`|`KYS1_K680204`|`KYS1_K680205`|`KYS1_K680206`|`KYS1_K680301`|`KYS1_K680302`|`KYS1_K680303`|`KYS1_K680304`|`KYS1_K680305`|`KYS1_K680306`|
|-|-|-|-|-|-|-|-|-|-|-|-|-|
| **Label** |`Help no matter what happened: spouse`|`Help no matter what happened: other relative`|`Help no matter what happened: close friend`|`Help no matter what happened: close colleague`|`Help no matter what happened: close neighbour`|`Help no matter what happened: other close person`|`Reliable help: spouse`|`Reliable help: other relative`|`Reliable help: close friend`|`Reliable help: close colleague`|`Reliable help: close neighbour`|`Reliable help: other close person`|
| **Table name** |`t11_athlos_2017_02_27`|`t11_athlos_2017_02_27`|`t11_athlos_2017_02_27`|`t11_athlos_2017_02_27`|`t11_athlos_2017_02_27`|`t11_athlos_2017_02_27`|`t11_athlos_2017_02_27`|`t11_athlos_2017_02_27`|`t11_athlos_2017_02_27`|`t11_athlos_2017_02_27`|`t11_athlos_2017_02_27`|`t11_athlos_2017_02_27`|
| **Categories** |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|
| **Description** |  |  |  |  |  |  |  |  |  |  |  |  |


    
```{r assign2, echo=F}

opal.assign.table.tibble(o, 'Health20002011_w2_emot_sup','Health2000-2011.t11_athlos_2017_02_27', variables=list('KYS1_K680201','KYS1_K680202','KYS1_K680203','KYS1_K680204','KYS1_K680205','KYS1_K680206','KYS1_K680301','KYS1_K680302','KYS1_K680303','KYS1_K680304','KYS1_K680305','KYS1_K680306' ), missings = TRUE)
Health20002011_w2_emot_sup <- opal.execute(o,'Health20002011_w2_emot_sup')

```

```{r local2, echo=F}

vbl_miss<- c(NA)

vbl <- Health20002011_w2_emot_sup$KYS1_K680201
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'KYS1_K680201')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(Health20002011_w2_emot_sup, aes(x=factor(KYS1_K680201))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w2_emot_sup$KYS1_K680202
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'KYS1_K680202')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(Health20002011_w2_emot_sup, aes(x=factor(KYS1_K680202))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w2_emot_sup$KYS1_K680203
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'KYS1_K680203')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(Health20002011_w2_emot_sup, aes(x=factor(KYS1_K680203))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w2_emot_sup$KYS1_K680204
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'KYS1_K680204')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(Health20002011_w2_emot_sup, aes(x=factor(KYS1_K680204))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w2_emot_sup$KYS1_K680205
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'KYS1_K680205')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(Health20002011_w2_emot_sup, aes(x=factor(KYS1_K680205))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w2_emot_sup$KYS1_K680206
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'KYS1_K680206')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(Health20002011_w2_emot_sup, aes(x=factor(KYS1_K680206))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w2_emot_sup$KYS1_K680301
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'KYS1_K680301')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(Health20002011_w2_emot_sup, aes(x=factor(KYS1_K680301))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w2_emot_sup$KYS1_K680302
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'KYS1_K680302')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(Health20002011_w2_emot_sup, aes(x=factor(KYS1_K680302))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w2_emot_sup$KYS1_K680303
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'KYS1_K680303')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(Health20002011_w2_emot_sup, aes(x=factor(KYS1_K680303))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w2_emot_sup$KYS1_K680304
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'KYS1_K680304')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(Health20002011_w2_emot_sup, aes(x=factor(KYS1_K680304))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w2_emot_sup$KYS1_K680305
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'KYS1_K680305')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(Health20002011_w2_emot_sup, aes(x=factor(KYS1_K680305))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w2_emot_sup$KYS1_K680306
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = 'KYS1_K680306')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(Health20002011_w2_emot_sup, aes(x=factor(KYS1_K680306))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 then 1`
* `else if all are equal 0 then 0`
* `NA into 999`

**R script:**

```{r harmo2}
Health20002011_ds_w2 <- tibble(id=Health20002011_w2_emot_sup$id)

Health20002011_w2_emot_sup$KYS1_K680201 <- car::recode(as.vector(Health20002011_w2_emot_sup$KYS1_K680201), "NA='-999'")
Health20002011_w2_emot_sup$KYS1_K680202 <- car::recode(as.vector(Health20002011_w2_emot_sup$KYS1_K680202), "NA='-999'")
Health20002011_w2_emot_sup$KYS1_K680203 <- car::recode(as.vector(Health20002011_w2_emot_sup$KYS1_K680203), "NA='-999'")
Health20002011_w2_emot_sup$KYS1_K680204 <- car::recode(as.vector(Health20002011_w2_emot_sup$KYS1_K680204), "NA='-999'")
Health20002011_w2_emot_sup$KYS1_K680205 <- car::recode(as.vector(Health20002011_w2_emot_sup$KYS1_K680205), "NA='-999'")
Health20002011_w2_emot_sup$KYS1_K680206 <- car::recode(as.vector(Health20002011_w2_emot_sup$KYS1_K680206), "NA='-999'")
Health20002011_w2_emot_sup$KYS1_K680301 <- car::recode(as.vector(Health20002011_w2_emot_sup$KYS1_K680301), "NA='-999'")
Health20002011_w2_emot_sup$KYS1_K680302 <- car::recode(as.vector(Health20002011_w2_emot_sup$KYS1_K680302), "NA='-999'")
Health20002011_w2_emot_sup$KYS1_K680303 <- car::recode(as.vector(Health20002011_w2_emot_sup$KYS1_K680303), "NA='-999'")
Health20002011_w2_emot_sup$KYS1_K680304 <- car::recode(as.vector(Health20002011_w2_emot_sup$KYS1_K680304), "NA='-999'")
Health20002011_w2_emot_sup$KYS1_K680305 <- car::recode(as.vector(Health20002011_w2_emot_sup$KYS1_K680305), "NA='-999'")
Health20002011_w2_emot_sup$KYS1_K680306 <- car::recode(as.vector(Health20002011_w2_emot_sup$KYS1_K680306), "NA='-999'")

Health20002011_ds_w2$emot_sup <- c(NA)
for(i in 1:dim(Health20002011_w2_emot_sup)[1]){
  if( Health20002011_w2_emot_sup$KYS1_K680201[i] == 1 | Health20002011_w2_emot_sup$KYS1_K680202[i] == 1 | Health20002011_w2_emot_sup$KYS1_K680203[i] == 1 | 
    Health20002011_w2_emot_sup$KYS1_K680204[i] == 1 | Health20002011_w2_emot_sup$KYS1_K680205[i] == 1 | Health20002011_w2_emot_sup$KYS1_K680206[i] == 1 | 
    Health20002011_w2_emot_sup$KYS1_K680301[i] == 1 | Health20002011_w2_emot_sup$KYS1_K680302[i] == 1 | Health20002011_w2_emot_sup$KYS1_K680303[i] == 1 | 
    Health20002011_w2_emot_sup$KYS1_K680304[i] == 1 | Health20002011_w2_emot_sup$KYS1_K680305[i] == 1 | Health20002011_w2_emot_sup$KYS1_K680306[i] == 1 ) { 
  Health20002011_ds_w2$emot_sup[i] = 1 }
  else if( Health20002011_w2_emot_sup$KYS1_K680201[i] == -999 & Health20002011_w2_emot_sup$KYS1_K680202[i] == -999 & Health20002011_w2_emot_sup$KYS1_K680203[i] == -999 & 
    Health20002011_w2_emot_sup$KYS1_K680204[i] == -999 & Health20002011_w2_emot_sup$KYS1_K680205[i] == -999 & Health20002011_w2_emot_sup$KYS1_K680206[i] == -999 & 
    Health20002011_w2_emot_sup$KYS1_K680301[i] == -999 & Health20002011_w2_emot_sup$KYS1_K680302[i] == -999 & Health20002011_w2_emot_sup$KYS1_K680303[i] == -999 & 
    Health20002011_w2_emot_sup$KYS1_K680304[i] == -999 & Health20002011_w2_emot_sup$KYS1_K680305[i] == -999 & Health20002011_w2_emot_sup$KYS1_K680306[i] == -999 ) { 
  Health20002011_ds_w2$emot_sup[i] = 999 }
  else if( Health20002011_w2_emot_sup$KYS1_K680201[i] == 0 | Health20002011_w2_emot_sup$KYS1_K680202[i] == 0 | Health20002011_w2_emot_sup$KYS1_K680203[i] == 0 | 
    Health20002011_w2_emot_sup$KYS1_K680204[i] == 0 | Health20002011_w2_emot_sup$KYS1_K680205[i] == 0 | Health20002011_w2_emot_sup$KYS1_K680206[i] == 0 |
    Health20002011_w2_emot_sup$KYS1_K680301[i] == 0 | Health20002011_w2_emot_sup$KYS1_K680302[i] == 0 | Health20002011_w2_emot_sup$KYS1_K680303[i] == 0 | 
    Health20002011_w2_emot_sup$KYS1_K680304[i] == 0 | Health20002011_w2_emot_sup$KYS1_K680305[i] == 0 | Health20002011_w2_emot_sup$KYS1_K680306[i] == 0 ) { 
  Health20002011_ds_w2$emot_sup[i] = 0 }
}

Health20002011_ds_w2$emot_sup <- car::recode(as.vector(Health20002011_ds_w2$emot_sup), "NA='999'")
Health20002011_ds_w2$emot_sup <- labelled(Health20002011_ds_w2$emot_sup, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}

vbl <- Health20002011_ds_w2$emot_sup
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(Health20002011_ds_w2, aes(x=factor(emot_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation2, echo=F}

```

```{r final, echo=F}

l.hds <- list(w1 = Health20002011_ds_w1, w2 = Health20002011_ds_w2)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("Health20002011_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

```

## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.


```{r summ}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",names(l.hds))
kable(t.hds)

dbb <- get(paste0("Health20002011_m_ds_",names(l.hds)[1]))[,c("id","emot_sup")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("Health20002011_m_ds_",names(l.hds)[ind]))[,c("id","emot_sup")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", names(l.hds))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb)

```


# Quality estimation

For wave 1 answers are 1 or NA (there are no zeros in answers!!). It produces only 1 or 999 and there is no other method to receive 0 (or all 999 into zeros).

<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  emot_sup <- l.hds[[index]]
  save(emot_sup, file = paste0(datafolder,names(l.hds)[index],"/emot_sup.RData"))
}

```
<!-- ########################################################## --> 



<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
