---
title: "Any form of religious participation (religious services attendance, religious meetings, religious organization membership, etc.)"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `relig`
* Variable label: `Any form of religious participation`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process

## Finnish population

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `KYS1_K2004`
* Label: `Time use: going to church or other religious events`
* Categories: 
    + `1 = Less frequently or never`
    + `2 = Once or twice a year`
    + `3 = Once or twice a month`
    + `4 = Once or twice a week`
    + `5 = Every day or most days`
    
    
* Description: 
```{r assign1}
opal.assign.table.tibble(o, 'Health20002011_w1_relig','Health2000-2011.t00_athlos_2017_02_23',variables=list('KYS1_K2004'), missings = TRUE)
```

```{r local1}
Health20002011_w1_relig <- opal.execute(o,'Health20002011_w1_relig')
vari <- Health20002011_w1_relig$KYS1_K2004
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = Health20002011_w1_relig$KYS1_K2004, missing_values = NA)
ggplot(Health20002011_w1_relig, aes(x=factor(KYS1_K2004))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Going to church or other religious events") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 0`
* `3,4,5 into 1`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
Health20002011_ds_w1 <- tibble(id=Health20002011_w1_relig$id)
Health20002011_ds_w1$relig <- car::recode(as.vector(Health20002011_w1_relig$KYS1_K2004), "1:2='0'; 3:5='1'; NA='999'")
Health20002011_ds_w1$relig <- labelled(Health20002011_ds_w1$relig, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1}
vari <- Health20002011_ds_w1$relig
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = Health20002011_ds_w1$relig, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(Health20002011_ds_w1, aes(x=factor(relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Religious participation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1}
AfterH <- table(Health20002011_ds_w1$relig)
BeforeH <- table(Health20002011_w1_relig$KYS1_K2004, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:2)])
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[[3]] <- BeforeH[[6]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:2->0","3:5->1","NA->999")
kable(C)
```

 
 


### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `KYS1_K2004`
* Label: `Time use: going to church or other religious events`
* Categories: 
    + `1 = Less frequently or never`
    + `2 = Once or twice a year`
    + `3 = Once or twice a month`
    + `4 = Once or twice a week`
    + `5 = Every day or most days`
    
    
* Description: 
```{r assign2}
opal.assign.table.tibble(o, 'Health20002011_w2_relig','Health2000-2011.t11_athlos_2017_02_27',variables=list('KYS1_K2004'), missings = TRUE)
```

```{r local2}
Health20002011_w2_relig <- opal.execute(o,'Health20002011_w2_relig')
vari <- Health20002011_w2_relig$KYS1_K2004
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = Health20002011_w2_relig$KYS1_K2004, missing_values = NA)
ggplot(Health20002011_w2_relig, aes(x=factor(KYS1_K2004))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Going to church or other religious events") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 0`
* `3,4,5 into 1`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
Health20002011_ds_w2 <- tibble(id=Health20002011_w2_relig$id)
Health20002011_ds_w2$relig <- car::recode(as.vector(Health20002011_w2_relig$KYS1_K2004), "1:2='0'; 3:5='1'; NA='999'")
Health20002011_ds_w2$relig <- labelled(Health20002011_ds_w2$relig, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2}
vari <- Health20002011_ds_w2$relig
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = Health20002011_ds_w2$relig, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(Health20002011_ds_w2, aes(x=factor(relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Religious participation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2}
AfterH <- table(Health20002011_ds_w2$relig)
BeforeH <- table(Health20002011_w2_relig$KYS1_K2004, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1:2)])
BeforeH1[[2]] <- sum(BeforeH[c(3:5)])
BeforeH1[[3]] <- BeforeH[[6]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:2->0","3:5->1","NA->999")
kable(C)
```


```{r save, echo=FALSE}
relig <- Health20002011_ds_w1
save(relig, file = "../RData/w1/relig.RData")
rm(relig)

relig <- Health20002011_ds_w2
save(relig, file = "../RData/w2/relig.RData")
rm(relig)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
 