---
title: "Divorce/Separation"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `divorce`
* Variable label: `Experience of divorce/separation`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process

## Finnish population

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `AA01`
* Label: `Marital status`
* Categories: 
    + `1 = married`
    + `2 = cohabiting`
    + `3 = divorced/separated`
    + `4 = widow`
    + `5 = single`

* Description: 
```{r assign1}
opal.assign.table.tibble(o, 'Health20002011_w1_divorce','Health2000-2011.t00_athlos_2017_02_23',variables=list('AA01'), missings = TRUE)
```

```{r local1}
Health20002011_w1_divorce <- opal.execute(o,'Health20002011_w1_divorce')
vari <- Health20002011_w1_divorce$AA01
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = Health20002011_w1_divorce$AA01, missing_values = NA)
ggplot(Health20002011_w1_divorce, aes(x=factor(AA01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `3 into 1`
* `1,2,4,5 into 0`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
Health20002011_ds_w1 <- tibble(id=Health20002011_w1_divorce$id)
Health20002011_ds_w1$divorce <- car::recode(as.vector(Health20002011_w1_divorce$AA01), "3='1'; 1:2='0'; 4:5='0'; NA='999'")
Health20002011_ds_w1$divorce <- labelled(Health20002011_ds_w1$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1}
vari <- Health20002011_ds_w1$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = Health20002011_ds_w1$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(Health20002011_ds_w1, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1}
AfterH <- table(Health20002011_ds_w1$divorce)
BeforeH <- table(Health20002011_w1_divorce$AA01, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(1,2,4,5)])
BeforeH1[[2]] <- BeforeH[[3]]
BeforeH1[[3]] <- BeforeH[[6]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```


### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `AA01`
* Label: `Marital status`
* Categories: 
    + `1 = married or in a civil union`
    + `2 = living with your partner`
    + `3 = divorced or separated`
    + `4 = widowed`
    + `5 = or single?`
    
* Name: `divorce` from the previous wave


* Description: 
```{r assign2}
opal.assign.table.tibble(o, 'Health20002011_w2_divorce','Health2000-2011.t11_athlos_2017_02_27',variables=list('AA01'), missings = TRUE)
```

```{r local2}
Health20002011_w2_divorce <- opal.execute(o,'Health20002011_w2_divorce')
vari <- Health20002011_w2_divorce$AA01
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = Health20002011_w2_divorce$AA01, missing_values = NA)
ggplot(Health20002011_w2_divorce, aes(x=factor(AA01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if divorce=1 or AA01=3 - into 1`
* `1,2,4,5 into 0`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}

same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  colnames(new_2) <- colnames(old)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], rep_len(NA,dim(old)[2]-1))
    }
  }
  new_2 <- data.frame(new_2)
  new_22 <- data.frame(id=new_2$id, AA01=new$AA01, divorce=new_2$divorce) 
                       # id = new_2$id
                       # colname_form_OLD_table = new_2$colname_form_OLD_table 
                       # colname_form_NEW_table = new$colname_form_NEW_table
  new_22
}

# old = Health20002011_ds_w1 (divorce)
# new = Health20002011_w2_divorce (AA01)

Health20002011_w2_divorce_2 <- same_indiv(Health20002011_ds_w1, Health20002011_w2_divorce)

Health20002011_ds_w2 <- tibble(id=Health20002011_w2_divorce_2$id)

Health20002011_w2_divorce_2$divorce <- car::recode(as.vector(Health20002011_w2_divorce_2$divorce), "NA='-999'")
Health20002011_w2_divorce_2$AA01 <- car::recode(as.vector(Health20002011_w2_divorce_2$AA01), "NA='-999'")

Health20002011_ds_w2$divorce <- c(NA)
for(i in 1:dim(Health20002011_w2_divorce_2[1])){
  if( Health20002011_w2_divorce_2$divorce[i] == 1 | Health20002011_w2_divorce_2$AA01[i] == 3  ) { 
    Health20002011_ds_w2$divorce[i] = 1 }
  else if( Health20002011_w2_divorce_2$AA01[i] %in% c(1,2,4,5) ) { 
    Health20002011_ds_w2$divorce[i] = 0 }
}

Health20002011_ds_w2$divorce <- car::recode(as.vector(Health20002011_ds_w2$divorce), "NA='999'")
Health20002011_ds_w2$divorce <- labelled(Health20002011_ds_w2$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2}
vari <- Health20002011_ds_w2$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = Health20002011_ds_w2$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(Health20002011_ds_w2, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2}
AfterH <- table(Health20002011_ds_w2$divorce)
BeforeH <- table(Health20002011_w2_divorce_2$AA01, Health20002011_w2_divorce_2$divorce, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- sum(sum(BeforeH[4,]),sum(BeforeH[c(1,2,3,5,6),3]))
BeforeH1[[1]] <- sum(BeforeH[c(2,3,5,6),c(1,2,4)])
BeforeH1[[3]] <- sum(BeforeH[1,c(1,2,4)])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```


```{r save, echo=FALSE}
divorce <- Health20002011_ds_w1
save(divorce, file = "../RData/w1/divorce.RData")
rm(divorce)

divorce <- Health20002011_ds_w2
save(divorce, file = "../RData/w2/divorce.RData")
rm(divorce)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
