---
title: "Has spouse/partner"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `spouse`
* Variable label: `Has spouse/partner`
* Domain: `Social environment`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 

# Data process
## Finnish population

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `AA01`
* Label: `Marital status`
* Categories: 
    + `1 = married`
    + `2 = cohabiting`
    + `3 = divorced/separated`
    + `4 = widow`
    + `5 = single`

* Description: 
```{r assign1}
opal.assign.table.tibble(o, 'Health20002011_w1_spouse','Health2000-2011.t00_athlos_2017_02_23',
                         variables=list('AA01'), missings = TRUE)
```

```{r local1}
Health20002011_w1_spouse <- opal.execute(o,'Health20002011_w1_spouse')
vari <- Health20002011_w1_spouse$AA01
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = Health20002011_w1_spouse$AA01, missing_values = NA)
ggplot(Health20002011_w1_spouse, aes(x=factor(AA01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 OR 2 into 1`
* `3,4 OR 5 into 0`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
Health20002011_ds_w1 <- tibble(id=Health20002011_w1_spouse$id)
Health20002011_ds_w1$spouse <- car::recode(as.vector(Health20002011_w1_spouse$AA01), "1:2='1'; 3:5='0'; NA='999'")
Health20002011_ds_w1$spouse <- labelled(Health20002011_ds_w1$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1}
vari <- Health20002011_ds_w1$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = Health20002011_ds_w1$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(Health20002011_ds_w1, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1}
AfterH <- table(Health20002011_ds_w1$spouse)
BeforeH <- table(Health20002011_w1_spouse$AA01, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[2]])
BeforeH[[2]] <- sum(BeforeH[[3]],BeforeH[[4]],BeforeH[[5]])
BeforeH <- BeforeH[c(2,1,6)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3,4,5->0","1,2->1","NA->999")

kable(C)
```

 
 


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `AA01`
* Label: `Marital status`
* Categories: 
    + `1 = married or in a civil union`
    + `2 = living with your partner`
    + `3 = divorced or separated`
    + `4 = widowed`
    + `5 = or single?`

* Description: 
```{r assign2}
opal.assign.table.tibble(o, 'Health20002011_w2_spouse','Health2000-2011.t11_athlos_2017_02_27',
                         variables=list('AA01'), missings = TRUE)
```

```{r local2}
Health20002011_w2_spouse <- opal.execute(o,'Health20002011_w2_spouse')
vari <- Health20002011_w2_spouse$AA01
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = Health20002011_w2_spouse$AA01, missing_values = NA)
ggplot(Health20002011_w2_spouse, aes(x=factor(AA01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1 or 2 into 1`
* `3,4 or 5 into 0`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
Health20002011_ds_w2 <- tibble(id=Health20002011_w2_spouse$id)
Health20002011_ds_w2$spouse <- car::recode(as.vector(Health20002011_w2_spouse$AA01), "1:2='1'; 3:5='0'; NA='999'")
Health20002011_ds_w2$spouse <- labelled(Health20002011_ds_w2$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2}
vari <- Health20002011_ds_w2$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = Health20002011_ds_w2$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(Health20002011_ds_w2, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2}
AfterH <- table(Health20002011_ds_w2$spouse)
BeforeH <- table(Health20002011_w2_spouse$AA01, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[[1]],BeforeH[[2]])
BeforeH[[2]] <- sum(BeforeH[[3]],BeforeH[[4]],BeforeH[[5]])
BeforeH <- BeforeH[c(2,1,6)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3,4,5->0","1,2->1","NA->999")

kable(C)
```

 
 
```{r save, echo=FALSE}
spouse <- Health20002011_ds_w1
save(spouse, file = "../RData/w1/spouse.RData")
rm(spouse)

spouse <- Health20002011_ds_w2
save(spouse, file = "../RData/w2/spouse.RData")
rm(spouse)

```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
