---
title: "Month of death"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:



* Short name: `mdeath`
* Variable label: `month of death`
* Variable description: `Month of death`
* Domain: `Age of death (Life expectancy)`
* Value type: `continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process


### HAPIEE - Poland - Baseline 

There is no variable.




### HAPIEE - Poland - Reexamination

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `mod`
* Label: `Month of death`
* Type of variable: `countinous`

```{r assign_po2}
opal.assign.table.tibble(o, 'HAPIEE_pol_w2_mdeath','HAPIEE.Po_followup_etic',
                         variables=list('mod'), missings = TRUE)
```

```{r local_po2}
HAPIEE_pol_w2_mdeath <- opal.execute(o,'HAPIEE_pol_w2_mdeath')
Categorical_summary(var = HAPIEE_pol_w2_mdeath$mod, missing_values = NA)
ggplot(HAPIEE_pol_w2_mdeath, aes(mod)) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_po2}
HAPIEE_pol_ds_w2 <- tibble(id=HAPIEE_pol_w2_mdeath$id)
HAPIEE_pol_ds_w2$mdeath <- car::recode(HAPIEE_pol_w2_mdeath$mod, "NA=999")
HAPIEE_pol_ds_w2$mdeath <- labelled(HAPIEE_pol_ds_w2$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_po2}
Categorical_summary(var = HAPIEE_pol_ds_w2$mdeath, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_pol_ds_w2, aes(mdeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency") + xlim(0,13)
```

#### Validation
```{r crosstabulation_po2}
BeforeH <- table(HAPIEE_pol_w2_mdeath$mod, useNA = "ifany")
AfterH <- table(HAPIEE_pol_ds_w2$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
C
```

#### Quality estimation
[Comments on the quality of the new harmonised variable.]

#### Import to OPAL
```{r importOPAL_po2}
val_labels(HAPIEE_pol_ds_w2) <- NULL
#opal.assign.data(o, 'HAPIEE_pol_ds_w2', HAPIEE_pol_ds_w2)
#opal.symbol_import(o,'HAPIEE_pol_ds_w2', project='_Athlos_Harm_Dataset')
mdeath <- HAPIEE_pol_ds_w2
save(mdeath, file = "../RData/pol_w2/mdeath.RData")
rm(mdeath)

HAPIEE_pol_m_ds_w2 <- HAPIEE_pol_ds_w2
HAPIEE_pol_m_ds_w2$mdeath <- car::recode(HAPIEE_pol_m_ds_w2$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_pol_m_ds_w2', HAPIEE_pol_m_ds_w2)
#opal.symbol_import(o,'HAPIEE_pol_m_ds_w2', project='_Athlos_Harm_Dataset')
```






### HAPIEE - Czech Republic - Baseline

There is no variable.








### HAPIEE - Czech Republic - Reexamination

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `mod`
* Label: `Month of death`
* Type of variable: `countinous`

```{r assign_cz2}
opal.assign.table.tibble(o, 'HAPIEE_cz_w2_mdeath','HAPIEE.Cz_followup_etic',
                         variables=list('mod'), missings = TRUE)
```

```{r local_cz2}
HAPIEE_cz_w2_mdeath <- opal.execute(o,'HAPIEE_cz_w2_mdeath')
Categorical_summary(var = HAPIEE_cz_w2_mdeath$mod, missing_values = NA)
ggplot(HAPIEE_cz_w2_mdeath, aes(mod)) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_cz2}
HAPIEE_cz_ds_w2 <- tibble(id=HAPIEE_cz_w2_mdeath$id)
HAPIEE_cz_ds_w2$mdeath <- car::recode(HAPIEE_cz_w2_mdeath$mod, "NA=999")
HAPIEE_cz_ds_w2$mdeath <- labelled(HAPIEE_cz_ds_w2$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_cz2}
Categorical_summary(var = HAPIEE_cz_ds_w2$mdeath, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_cz_ds_w2, aes(mdeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency") + xlim(0, 13)
```

#### Validation
```{r crosstabulation_cz2}
BeforeH <- table(HAPIEE_cz_w2_mdeath$mod, useNA = "ifany")
AfterH <- table(HAPIEE_cz_ds_w2$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
C
```

#### Quality estimation
[Comments on the quality of the new harmonised variable.]

#### Import to OPAL
```{r importOPAL_cz2}
val_labels(HAPIEE_cz_ds_w2) <- NULL
#opal.assign.data(o, 'HAPIEE_cz_ds_w2', HAPIEE_cz_ds_w2)
#opal.symbol_import(o,'HAPIEE_cz_ds_w2', project='_Athlos_Harm_Dataset')
mdeath <- HAPIEE_cz_ds_w2
save(mdeath, file = "../RData/cz_w2/mdeath.RData")
rm(mdeath)

HAPIEE_cz_m_ds_w2 <- HAPIEE_cz_ds_w2
HAPIEE_cz_m_ds_w2$mdeath <- car::recode(HAPIEE_cz_m_ds_w2$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_cz_m_ds_w2', HAPIEE_cz_m_ds_w2)
#opal.symbol_import(o,'HAPIEE_cz_m_ds_w2', project='_Athlos_Harm_Dataset')
```









### HAPIEE - Lithuania - Baseline

There is no varibale


### HAPIEE - Lithuania - Followup

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `mod`
* Label: `Month of death`
* Type of variable: `countinous`

```{r assign_li1}
opal.assign.table.tibble(o, 'HAPIEE_li_w1_mbirth','HAPIEE.Li_followup_etic',
                         variables=list('mod'), missings = TRUE)
```

```{r local_li1}
HAPIEE_li_w1_mbirth <- opal.execute(o,'HAPIEE_li_w1_mbirth')
Categorical_summary(var = HAPIEE_li_w1_mbirth$mod, missing_values = NA)
ggplot(HAPIEE_li_w1_mbirth, aes(mod)) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_li1}
HAPIEE_li_ds_w1 <- tibble(id=HAPIEE_li_w1_mbirth$id)
HAPIEE_li_ds_w1$mdeath <- car::recode(HAPIEE_li_w1_mbirth$mod, "NA=999")
HAPIEE_li_ds_w1$mdeath <- labelled(HAPIEE_li_ds_w1$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_li1}
Categorical_summary(var = HAPIEE_li_ds_w1$mdeath, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_li_ds_w1, aes(mdeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency") + xlim(0, 13)
```

#### Validation
```{r crosstabulation_li1}
BeforeH <- table(HAPIEE_li_w1_mbirth$mod, useNA = "ifany")
AfterH <- table(HAPIEE_li_ds_w1$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
C
```

#### Quality estimation

No comments

[Comments on the quality of the new harmonised variable.]

#### Import to OPAL
```{r importOPAL_li1}
val_labels(HAPIEE_li_ds_w1) <- NULL
#opal.assign.data(o, 'HAPIEE_li_ds_w1', HAPIEE_li_ds_w1)
#opal.symbol_import(o,'HAPIEE_li_ds_w1', project='_Athlos_Harm_Dataset')
mdeath <- HAPIEE_li_ds_w1
save(mdeath, file = "../RData/li_w1/mdeath.RData")
rm(mdeath)

HAPIEE_li_m_ds_w1 <- HAPIEE_li_ds_w1
HAPIEE_li_m_ds_w1$mdeath <- car::recode(HAPIEE_li_m_ds_w1$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_li_m_ds_w1', HAPIEE_li_m_ds_w1)
#opal.symbol_import(o,'HAPIEE_li_m_ds_w1', project='_Athlos_Harm_Dataset')
```





```{r closeRsession, echo=FALSE}
opal.logout(o)
```

