---
title: "Year of death"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `ydeath`
* Variable label: `Year of death`
* Variable description: `year of death`
* Domain: `Death`
* Value type: `continous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


```{r lab, echo=FALSE}
ds_label <- "Year of death"
```

# Data process

## ALSA

### Wave 1 

There is no variable.


### Wave 2

#### Study-specific variable description


The study-specific variable elected to be harmonised is:

| **Name** | `deathdate`|
|-|-|
| **Label** | `date of death`|
| **Table name** | `Death_dates_laia` |
| **Description** |  |

    
```{r assign2, echo=F}
opal.assign.table.tibble(o, 'ALSA_death','ALSA.Death_dates_laia',
                         variables=list('deathdate', 'ydeath'), missings = TRUE)
ALSA_death <- opal.execute(o,'ALSA_death')
```

```{r local2, echo=F}
vari <- ALSA_death[[3]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_death, aes(x=ydeath)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo2}
ALSA_ds_w2 <- tibble(id=ALSA_death$id)
ALSA_ds_w2$ydeath <- car::recode(ALSA_death$ydeath, "NA=999")
ALSA_ds_w2$ydeath <- labelled(ALSA_ds_w2$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- ALSA_ds_w2$ydeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w2, aes(x=factor(ydeath))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

### Validation
```{r crosstabulation2, echo=F}
BeforeH <- table(ALSA_death$ydeath, useNA = "ifany")
AfterH <- table(ALSA_ds_w2$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```

## Wave 3 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

| **Name** | `deathdate`|
|-|-|
| **Label** | `date of death`|
| **Table name** | `Death_dates_laia` |
| **Description** |  |

    
```{r assign3, echo=F}
opal.assign.table.tibble(o, 'ALSA_death','ALSA.Death_dates_laia',
                         variables=list('deathdate', 'ydeath'), missings = TRUE)
ALSA_death <- opal.execute(o,'ALSA_death')
```

```{r local3, echo=F}
vari <- ALSA_death[[3]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_death, aes(x=ydeath)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo3}
ALSA_ds_w3 <- tibble(id=ALSA_death$id)
ALSA_ds_w3$ydeath <- car::recode(ALSA_death$ydeath, "NA=999")
ALSA_ds_w3$ydeath <- labelled(ALSA_ds_w3$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

### Statistics of the new harmonised variable
```{r descript3, echo=F}
vari <- ALSA_ds_w3$ydeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w3, aes(x=factor(ydeath))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

### Validation
```{r crosstabulation3, echo=F}
BeforeH <- table(ALSA_death$ydeath, useNA = "ifany")
AfterH <- table(ALSA_ds_w3$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```

## Wave 4 

#### Study-specific variable description


The study-specific variable elected to be harmonised is:

| **Name** | `deathdate`|
|-|-|
| **Label** | `date of death`|
| **Table name** | `Death_dates_laia` |
| **Description** |  |

    
```{r assign4, echo=F}
opal.assign.table.tibble(o, 'ALSA_death','ALSA.Death_dates_laia',
                         variables=list('deathdate', 'ydeath'), missings = TRUE)
ALSA_death <- opal.execute(o,'ALSA_death')
```

```{r local4, echo=F}
vari <- ALSA_death[[3]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_death, aes(x=ydeath)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo4}
ALSA_ds_w4 <- tibble(id=ALSA_death$id)
ALSA_ds_w4$ydeath <- car::recode(ALSA_death$ydeath, "NA=999")
ALSA_ds_w4$ydeath <- labelled(ALSA_ds_w4$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

### Statistics of the new harmonised variable
```{r descript4, echo=F}
vari <- ALSA_ds_w4$ydeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w4, aes(x=factor(ydeath))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

### Validation
```{r crosstabulation4, echo=F}
BeforeH <- table(ALSA_death$ydeath, useNA = "ifany")
AfterH <- table(ALSA_ds_w4$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```


## Wave 5 
#### Study-specific variable description


The study-specific variable elected to be harmonised is:

| **Name** | `deathdate`|
|-|-|
| **Label** | `date of death`|
| **Table name** | `Death_dates_laia` |
| **Description** |  |

    
```{r assign5, echo=F}
opal.assign.table.tibble(o, 'ALSA_death','ALSA.Death_dates_laia',
                         variables=list('deathdate', 'ydeath'), missings = TRUE)
ALSA_death <- opal.execute(o,'ALSA_death')
```

```{r local5, echo=F}
vari <- ALSA_death[[3]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_death, aes(x=ydeath)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo5}
ALSA_ds_w5 <- tibble(id=ALSA_death$id)
ALSA_ds_w5$ydeath <- car::recode(ALSA_death$ydeath, "NA=999")
ALSA_ds_w5$ydeath <- labelled(ALSA_ds_w5$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

### Statistics of the new harmonised variable
```{r descript5, echo=F}
vari <- ALSA_ds_w5$ydeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w5, aes(x=factor(ydeath))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

### Validation
```{r crosstabulation5, echo=F}
BeforeH <- table(ALSA_death$ydeath, useNA = "ifany")
AfterH <- table(ALSA_ds_w5$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```


## Wave 6 
#### Study-specific variable description


The study-specific variable elected to be harmonised is:

| **Name** | `deathdate`|
|-|-|
| **Label** | `date of death`|
| **Table name** | `Death_dates_laia` |
| **Description** |  |

    
```{r assign6, echo=F}
opal.assign.table.tibble(o, 'ALSA_death','ALSA.Death_dates_laia',
                         variables=list('deathdate', 'ydeath'), missings = TRUE)
ALSA_death <- opal.execute(o,'ALSA_death')
```

```{r local6, echo=F}
vari <- ALSA_death[[3]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_death, aes(x=ydeath)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo6}
ALSA_ds_w6 <- tibble(id=ALSA_death$id)
ALSA_ds_w6$ydeath <- car::recode(ALSA_death$ydeath, "NA=999")
ALSA_ds_w6$ydeath <- labelled(ALSA_ds_w6$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

### Statistics of the new harmonised variable
```{r descript6, echo=F}
vari <- ALSA_ds_w6$ydeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w6, aes(x=factor(ydeath))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

### Validation
```{r crosstabulation6, echo=F}
BeforeH <- table(ALSA_death$ydeath, useNA = "ifany")
AfterH <- table(ALSA_ds_w6$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```


## Wave 7 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

| **Name** | `deathdate`|
|-|-|
| **Label** | `date of death`|
| **Table name** | `Death_dates_laia` |
| **Description** |  |

    
```{r assign7, echo=F}
opal.assign.table.tibble(o, 'ALSA_death','ALSA.Death_dates_laia',
                         variables=list('deathdate', 'ydeath'), missings = TRUE)
ALSA_death <- opal.execute(o,'ALSA_death')
```

```{r local7, echo=F}
vari <- ALSA_death[[3]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_death, aes(x=ydeath)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo7}
ALSA_ds_w7 <- tibble(id=ALSA_death$id)
ALSA_ds_w7$ydeath <- car::recode(ALSA_death$ydeath, "NA=999")
ALSA_ds_w7$ydeath <- labelled(ALSA_ds_w7$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

### Statistics of the new harmonised variable
```{r descript7, echo=F}
vari <- ALSA_ds_w7$ydeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w7, aes(x=factor(ydeath))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

### Validation
```{r crosstabulation7, echo=F}
BeforeH <- table(ALSA_death$ydeath, useNA = "ifany")
AfterH <- table(ALSA_ds_w7$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```


## Wave 8 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

| **Name** | `deathdate`|
|-|-|
| **Label** | `date of death`|
| **Table name** | `Death_dates_laia` |
| **Description** |  |

    
```{r assign8, echo=F}
opal.assign.table.tibble(o, 'ALSA_death','ALSA.Death_dates_laia',
                         variables=list('deathdate', 'ydeath'), missings = TRUE)
ALSA_death <- opal.execute(o,'ALSA_death')
```

```{r local8, echo=F}
vari <- ALSA_death[[3]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_death, aes(x=ydeath)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo8}
ALSA_ds_w8 <- tibble(id=ALSA_death$id)
ALSA_ds_w8$ydeath <- car::recode(ALSA_death$ydeath, "NA=999")
ALSA_ds_w8$ydeath <- labelled(ALSA_ds_w8$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

### Statistics of the new harmonised variable
```{r descript8, echo=F}
vari <- ALSA_ds_w8$ydeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w8, aes(x=factor(ydeath))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

### Validation
```{r crosstabulation8, echo=F}
BeforeH <- table(ALSA_death$ydeath, useNA = "ifany")
AfterH <- table(ALSA_ds_w8$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```


## Wave 9 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

| **Name** | `deathdate`|
|-|-|
| **Label** | `date of death`|
| **Table name** | `Death_dates_laia` |
| **Description** |  |

    
```{r assign9, echo=F}
opal.assign.table.tibble(o, 'ALSA_death','ALSA.Death_dates_laia',
                         variables=list('deathdate', 'ydeath'), missings = TRUE)
ALSA_death <- opal.execute(o,'ALSA_death')
```

```{r local9, echo=F}
vari <- ALSA_death[[3]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_death, aes(x=ydeath)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo9}
ALSA_ds_w9 <- tibble(id=ALSA_death$id)
ALSA_ds_w9$ydeath <- car::recode(ALSA_death$ydeath, "NA=999")
ALSA_ds_w9$ydeath <- labelled(ALSA_ds_w9$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

### Statistics of the new harmonised variable
```{r descript9, echo=F}
vari <- ALSA_ds_w9$ydeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w9, aes(x=factor(ydeath))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

### Validation
```{r crosstabulation9, echo=F}
BeforeH <- table(ALSA_death$ydeath, useNA = "ifany")
AfterH <- table(ALSA_ds_w9$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```


## Wave 10 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

| **Name** | `deathdate`|
|-|-|
| **Label** | `date of death`|
| **Table name** | `Death_dates_laia` |
| **Description** |  |

    
```{r assign10, echo=F}
opal.assign.table.tibble(o, 'ALSA_death','ALSA.Death_dates_laia',
                         variables=list('deathdate', 'ydeath'), missings = TRUE)
ALSA_death <- opal.execute(o,'ALSA_death')
```

```{r local10, echo=F}
vari <- ALSA_death[[3]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_death, aes(x=ydeath)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo10}
ALSA_ds_w10 <- tibble(id=ALSA_death$id)
ALSA_ds_w10$ydeath <- car::recode(ALSA_death$ydeath, "NA=999")
ALSA_ds_w10$ydeath <- labelled(ALSA_ds_w10$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

### Statistics of the new harmonised variable
```{r descript10, echo=F}
vari <- ALSA_ds_w10$ydeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w10, aes(x=factor(ydeath))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

### Validation
```{r crosstabulation10, echo=F}
BeforeH <- table(ALSA_death$ydeath, useNA = "ifany")
AfterH <- table(ALSA_ds_w10$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```


## Wave 11 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

| **Name** | `deathdate`|
|-|-|
| **Label** | `date of death`|
| **Table name** | `Death_dates_laia` |
| **Description** |  |

    
```{r assign11, echo=F}
opal.assign.table.tibble(o, 'ALSA_death','ALSA.Death_dates_laia',
                         variables=list('deathdate', 'ydeath'), missings = TRUE)
ALSA_death <- opal.execute(o,'ALSA_death')
```

```{r local11, echo=F}
vari <- ALSA_death[[3]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_death, aes(x=ydeath)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo11}
ALSA_ds_w11 <- tibble(id=ALSA_death$id)
ALSA_ds_w11$ydeath <- car::recode(ALSA_death$ydeath, "NA=999")
ALSA_ds_w11$ydeath <- labelled(ALSA_ds_w11$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

### Statistics of the new harmonised variable
```{r descript11, echo=F}
vari <- ALSA_ds_w11$ydeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w11, aes(x=factor(ydeath))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

### Validation
```{r crosstabulation11, echo=F}
BeforeH <- table(ALSA_death$ydeath, useNA = "ifany")
AfterH <- table(ALSA_ds_w11$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```


## Wave 12 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

| **Name** | `deathdate`|
|-|-|
| **Label** | `date of death`|
| **Table name** | `Death_dates_laia` |
| **Description** |  |

    
```{r assign12, echo=F}
opal.assign.table.tibble(o, 'ALSA_death','ALSA.Death_dates_laia',
                         variables=list('deathdate', 'ydeath'), missings = TRUE)
ALSA_death <- opal.execute(o,'ALSA_death')
```

```{r local12, echo=F}
vari <- ALSA_death[[3]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_death, aes(x=ydeath)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo12}
ALSA_ds_w12 <- tibble(id=ALSA_death$id)
ALSA_ds_w12$ydeath <- car::recode(ALSA_death$ydeath, "NA=999")
ALSA_ds_w12$ydeath <- labelled(ALSA_ds_w12$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

### Statistics of the new harmonised variable
```{r descript12, echo=F}
vari <- ALSA_ds_w12$ydeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w12, aes(x=factor(ydeath))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

### Validation
```{r crosstabulation12, echo=F}
BeforeH <- table(ALSA_death$ydeath, useNA = "ifany")
AfterH <- table(ALSA_ds_w12$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```


## Wave 13 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

| **Name** | `deathdate`|
|-|-|
| **Label** | `date of death`|
| **Table name** | `Death_dates_laia` |
| **Description** |  |

    
```{r assign13, echo=F}
opal.assign.table.tibble(o, 'ALSA_death','ALSA.Death_dates_laia',
                         variables=list('deathdate', 'ydeath'), missings = TRUE)
ALSA_death <- opal.execute(o,'ALSA_death')
```

```{r local13, echo=F}
vari <- ALSA_death[[3]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_death, aes(x=ydeath)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo13}
ALSA_ds_w13 <- tibble(id=ALSA_death$id)
ALSA_ds_w13$ydeath <- car::recode(ALSA_death$ydeath, "NA=999")
ALSA_ds_w13$ydeath <- labelled(ALSA_ds_w13$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

### Statistics of the new harmonised variable
```{r descript13, echo=F}
vari <- ALSA_ds_w13$ydeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ALSA_ds_w13, aes(x=factor(ydeath))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

### Validation
```{r crosstabulation13, echo=F}
BeforeH <- table(ALSA_death$ydeath, useNA = "ifany")
AfterH <- table(ALSA_ds_w13$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```



# Quality estimation
The variable have the same values across waves, that doesn't mean that if the individual have date of death is death in all the waves.

```{r save, echo=FALSE}
ydeath <- ALSA_ds_w2
save(ydeath, file = "../RData/w2/ydeath.RData")
rm(ydeath)

ydeath <- ALSA_ds_w3
save(ydeath, file = "../RData/w3/ydeath.RData")
rm(ydeath)

ydeath <- ALSA_ds_w4
save(ydeath, file = "../RData/w4/ydeath.RData")
rm(ydeath)

ydeath <- ALSA_ds_w5
save(ydeath, file = "../RData/w5/ydeath.RData")
rm(ydeath)

ydeath <- ALSA_ds_w6
save(ydeath, file = "../RData/w6/ydeath.RData")
rm(ydeath)

ydeath <- ALSA_ds_w7
save(ydeath, file = "../RData/w7/ydeath.RData")
rm(ydeath)

ydeath <- ALSA_ds_w8
save(ydeath, file = "../RData/w8/ydeath.RData")
rm(ydeath)

ydeath <- ALSA_ds_w9
save(ydeath, file = "../RData/w9/ydeath.RData")
rm(ydeath)

ydeath <- ALSA_ds_w10
save(ydeath, file = "../RData/w10/ydeath.RData")
rm(ydeath)

ydeath <- ALSA_ds_w11
save(ydeath, file = "../RData/w11/ydeath.RData")
rm(ydeath)

ydeath <- ALSA_ds_w12
save(ydeath, file = "../RData/w12/ydeath.RData")
rm(ydeath)

ydeath <- ALSA_ds_w13
save(ydeath, file = "../RData/w13/ydeath.RData")
rm(ydeath)
```

```{r closeRsession, echo=FALSE}
opal.logout(o)
```

