---
title: "Eye sight - Near vision"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `eye_near`
* Variable label: `Eyesight - Near vision`
* Variable description: `Difficulties for near vision.`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


# Data process

## Spain

### Wave 1 

Not found.


### Wave 2 

#### Study-specific variable description




| **Name** | `w2vision_near`|
|-|-|
| **Label** | `Do you have vision problems (reading, watching television, sewing), even if wear`|
| **Table name** | `ENRICA_spss_wave2` |
| **Categories** | `0 = No; 1 = Yes` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w2_eye_near','ENRICA.ENRICA_spss_wave2', variables=list('w2vision_near'), missings = TRUE)
```

```{r local w2, echo=F}
ENRICA_w2_eye_near <- opal.execute(o,'ENRICA_w2_eye_near')
vari <- ENRICA_w2_eye_near$w2vision_near
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "w2vision_near")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w2_eye_near, aes(x=factor(w2vision_near))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Near Vision") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`

**R script:**
```{r harmo w2}
ENRICA_ds_w2 <- tibble(id=ENRICA_w2_eye_near$id)
ENRICA_ds_w2$eye_near <- car::recode(ENRICA_w2_eye_near$w2vision_near, "0 = '1';1 = '0';NA = '999' ")
ENRICA_ds_w2$eye_near <- labelled(ENRICA_ds_w2$eye_near, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vari <- ENRICA_ds_w2$eye_near
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "eye_near")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ENRICA_ds_w2, aes(x=factor(eye_near))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Near Vision") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
AfterH <- table(ENRICA_ds_w2$eye_near)
X<-table(ENRICA_w2_eye_near$w2vision_near)
BeforeH <- c(X[2:1],sum(is.na(ENRICA_w2_eye_near$w2vision_near)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999")
kable(C)
```


```{r importOPAL w2, echo=FALSE}
#opal.assign.data(o, 'ENRICA_ds_w2', ENRICA_ds_w2)
#opal.symbol_import(o,'ENRICA_ds_w2', project='_Athlos_Harm_Dataset')
eye_near <- ENRICA_ds_w2
save(eye_near, file = "../RData/w2/eye_near.RData")

ENRICA_m_ds_w2 <- ENRICA_ds_w2
ENRICA_m_ds_w2$eye_near <- car::recode(ENRICA_m_ds_w2$eye_near, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ENRICA_m_ds_w2', ENRICA_m_ds_w2)
#opal.symbol_import(o,'ENRICA_m_ds_w2', project='_Athlos_Harm_Dataset')
```



###Wave 3

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


| **Name** | `w3vision_near`|
|-|-|
| **Label** | `Do you have vision problems (reading, watching television, sewing), even if you`|
| **Table name** | `ENRICA_spss_wave3` |
| **Categories** | `0 = No; 1 = Yes` |
| **Missings** | `NA` |
| **Description** |  |



```{r assign w3, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w3_eye_near','ENRICA.ENRICA_spss_wave3', variables=list('w3vision_near'), missings = TRUE)
```

```{r local w3, echo=F}
ENRICA_w3_eye_near <- opal.execute(o,'ENRICA_w3_eye_near')
vari <- ENRICA_w3_eye_near$w3vision_near
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "w3vision_near")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w3_eye_near, aes(x=factor(w3vision_near))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Near Vision") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `NA into 999`

```{r harmo w3}
ENRICA_ds_w3 <- tibble(id=ENRICA_w3_eye_near$id)
ENRICA_ds_w3$eye_near <- car::recode(ENRICA_w3_eye_near$w3vision_near, "0 = '1';1 = '0';NA = '999' ")
ENRICA_ds_w3$eye_near <- labelled(ENRICA_ds_w3$eye_near, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}
vari <- ENRICA_ds_w3$eye_near
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "eye_near")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ENRICA_ds_w3, aes(x=factor(eye_near))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Near Vision") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=F}
AfterH <- table(ENRICA_ds_w3$eye_near)
X<-table(ENRICA_w3_eye_near$w3vision_near)
BeforeH <- c(X[2:1],sum(is.na(ENRICA_w3_eye_near$w3vision_near)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","NA->999")
kable(C)
```


```{r importOPAL w3, echo=FALSE}
label(ENRICA_ds_w3$eye_near) <- "Eyesight - Near vision"
#opal.assign.data(o, 'ENRICA_ds_w3', ENRICA_ds_w3)
#opal.symbol_import(o,'ENRICA_ds_w3', project='_Athlos_Harm_Dataset')
eye_near <- ENRICA_ds_w3
save(eye_near, file = "../RData/w3/eye_near.RData")

ENRICA_m_ds_w3 <- ENRICA_ds_w3
ENRICA_m_ds_w3$eye_near <- car::recode(ENRICA_m_ds_w3$eye_near, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ENRICA_m_ds_w3', ENRICA_m_ds_w3)
#opal.symbol_import(o,'ENRICA_m_ds_w3', project='_Athlos_Harm_Dataset')
```

# Quality estimation
No comments.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
