---
title: "Mobility - getting up from sitting down"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `mob_up`
* Variable label: `Difficulty for getting up from sitting down`
* Variable description: `Difficulty for getting up from sitting down`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## Spain

### Wave 1 

Not found.


### Wave 2 

#### Study-specific variable description




| **Name** | `w2mob_up`|
|-|-|
| **Label** | |
| **Table name** | `ENRICA_spss_wave2` |
| **Categories** | `0 = Unable to complete five stands unasisted/did not try; 1 = completes five stands with no help and this takes >=16.7 seconds; 2 = completes five stands with no help and this takes between 13.7 and 16.7 seconds; 3 = completes five stands with no help and this takes between 11.2 and 13.7 seconds; 4 = completes five stands with no help and this takes less than 11.2 seconds` |
| **Missings** | `NA` |
| **Description** |  |

 

```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w2_mob_up','ENRICA.ENRICA_spss_wave2', variables=list('w2mob_up'), missings = TRUE)
```

```{r local w2, echo=F}
ENRICA_w2_mob_up <- opal.execute(o,'ENRICA_w2_mob_up')
vari <- ENRICA_w2_mob_up$w2mob_up
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "w2mob_up")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w2_mob_up, aes(x=factor(w2mob_up))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - 'Getting up from Sitting") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0,1 into 0` 
* `2,3,4 into 1`
* `NA into 999`

**R script:**
```{r harmo w2}
ENRICA_ds_w2 <- tibble(id=ENRICA_w2_mob_up$id)
ENRICA_ds_w2$mob_up <- car::recode(ENRICA_w2_mob_up$w2mob_up, "0 = '0';1 = '0';2 = '1';3 = '1';4 = '1';NA = '999' ")
ENRICA_ds_w2$mob_up <- labelled(ENRICA_ds_w2$mob_up, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vari <- ENRICA_ds_w2$mob_up
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_up")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ENRICA_ds_w2, aes(x=factor(mob_up))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Getting up from Sitting") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
AfterH <- table(ENRICA_ds_w2$mob_up)
X<-table(ENRICA_w2_mob_up$w2mob_up)
BeforeH <- c(sum(X[1:2]),sum(X[3:5]),sum(is.na(ENRICA_w2_mob_up$w2mob_up)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0,1->0","2,3,4->1","NA->999")
kable(C)
```






```{r importOPAL w2, echo=FALSE}

label(ENRICA_ds_w2$mob_up) <- "Difficulty for getting up from sitting down"
#opal.assign.data(o, 'ENRICA_ds_w2', ENRICA_ds_w2)
#opal.symbol_import(o,'ENRICA_ds_w2', project='_Athlos_Harm_Dataset')
mob_up <- ENRICA_ds_w2
save(mob_up, file = "../RData/w2/mob_up.RData")

ENRICA_m_ds_w2 <- ENRICA_ds_w2
ENRICA_m_ds_w2$mob_up <- car::recode(ENRICA_m_ds_w2$mob_up, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ENRICA_m_ds_w2', ENRICA_m_ds_w2)
#opal.symbol_import(o,'ENRICA_m_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 3

#### Study-specific variable description




| **Name** | `w3mob_up`|
|-|-|
| **Label** | |
| **Table name** | `ENRICA_spss_wave3` |
| **Categories** | `0 = Unable to complete five stands unasisted/did not try; 1 = completes five stands with no help and this takes >=16.7 seconds; 2 = completes five stands with no help and this takes between 13.7 and 16.7 seconds; 3 = completes five stands with no help and this takes between 11.2 and 13.7 seconds; 4 = completes five stands with no help and this takes less than 11.2 seconds` |
| **Missings** | `NA` |
| **Description** |  |

 

```{r assign w3, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w3_mob_up','ENRICA.ENRICA_spss_wave3', variables=list('w3mob_up'), missings = TRUE)
```

```{r local w3, echo=F}
ENRICA_w3_mob_up <- opal.execute(o,'ENRICA_w3_mob_up')
vari <- ENRICA_w3_mob_up$w3mob_up
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "w3mob_up")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w3_mob_up, aes(x=factor(w3mob_up))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - 'Getting up from Sitting") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0,1 into 0` 
* `2,3,4 into 1`
* `NA into 999`

**R script:**
```{r harmo w3}
ENRICA_ds_w3 <- tibble(id=ENRICA_w3_mob_up$id)
ENRICA_ds_w3$mob_up <- car::recode(ENRICA_w3_mob_up$w3mob_up, "0 = '0';1 = '0';2 = '1';3 = '1';4 = '1';NA = '999' ")
ENRICA_ds_w3$mob_up <- labelled(ENRICA_ds_w3$mob_up, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}
vari <- ENRICA_ds_w3$mob_up
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_up")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ENRICA_ds_w3, aes(x=factor(mob_up))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Getting up from Sitting") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=F}
AfterH <- table(ENRICA_ds_w3$mob_up)
X<-table(ENRICA_w3_mob_up$w3mob_up)
BeforeH <- c(sum(X[1:2]),sum(X[3:5]),sum(is.na(ENRICA_w3_mob_up$w3mob_up)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0,1->0","2,3,4->1","NA->999")
kable(C)
```






```{r importOPAL w3, echo=FALSE}

label(ENRICA_ds_w3$mob_up) <- "Difficulty for getting up from sitting down"
#opal.assign.data(o, 'ENRICA_ds_w3', ENRICA_ds_w3)
#opal.symbol_import(o,'ENRICA_ds_w3', project='_Athlos_Harm_Dataset')
mob_up <- ENRICA_ds_w3
save(mob_up, file = "../RData/w3/mob_up.RData")

ENRICA_m_ds_w3 <- ENRICA_ds_w3
ENRICA_m_ds_w3$mob_up <- car::recode(ENRICA_m_ds_w3$mob_up, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ENRICA_m_ds_w3', ENRICA_m_ds_w3)
#opal.symbol_import(o,'ENRICA_m_ds_w3', project='_Athlos_Harm_Dataset')
```



# Quality estimation
No comments.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
