---
title: "ADL - Getting dressed"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_ania.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `adl_dressing`
* Variable label: `ADL-Difficulties for getting dressed`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | yes
1        | no

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




<!-- ########################################################## --> 

# Data process

```{r, dataDirectory, echo=FALSE}
datafolder <- "../RData"
``` 


## Spanish population



### Wave 1

Not found.



### Wave 2

#### Study-specific variable description




| **Name** | `w2adl_dressing`|
|-|-|
| **Label** | `difficulties: dressing, including shoes and socks` |
| **Table name** | `ENRICA_spss_wave2` |
| **Categories** | `0 = Limitations; 1 = No limitations` |
| **Missings** | `NA` |
| **Description** |  |


* Description: 
```{r assign w2, echo=F,  echo=FALSE}
opal.assign.table.tibble(o, 'ENRICA_w2_adl_dressing','ENRICA.ENRICA_spss_wave2', variables=list('w2adl_dressing'), missings = TRUE)
```

```{r local w2, echo=F,  echo=FALSE}
ENRICA_w2_adl_dressing <- opal.execute(o,'ENRICA_w2_adl_dressing')
vari <- ENRICA_w2_adl_dressing$w2adl_dressing # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(ENRICA_w2_adl_dressing$w2adl_dressing)
ggplot(ENRICA_w2_adl_dressing, aes(x=factor(w2adl_dressing))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `NA into 999`

**R script:**
```{r harmo w2,   echo=TRUE}
ENRICA_ds_w2 <- tibble(id=ENRICA_w2_adl_dressing$id)
ENRICA_ds_w2$adl_dressing <- car::recode(ENRICA_w2_adl_dressing$w2adl_dressing, "NA = '999' ")
ENRICA_ds_w2$adl_dressing <- labelled(ENRICA_ds_w2$adl_dressing, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F,  echo=FALSE}
vari <- ENRICA_ds_w2$adl_dressing # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ENRICA_ds_w2$adl_dressing, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ENRICA_ds_w2, aes(x=factor(adl_dressing))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F,  echo=FALSE}
AfterH <- table(ENRICA_ds_w2$adl_dressing)
X<-table(ENRICA_w2_adl_dressing$w2adl_dressing)
BeforeH <- c(X[1:2],sum(is.na(ENRICA_w2_adl_dressing$w2adl_dressing)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```






```{r importOPAL w2, echo=FALSE,  echo=FALSE}

label(ENRICA_ds_w2$adl_dressing) <- "Difficulties for getting dressed"
#opal.assign.data(o, 'ENRICA_ds_w2', ENRICA_ds_w2)
#opal.symbol_import(o,'ENRICA_ds_w2', project='_Athlos_Harm_Dataset')

ENRICA_m_ds_w2 <- ENRICA_ds_w2
ENRICA_m_ds_w2$adl_dressing <- car::recode(ENRICA_m_ds_w2$adl_dressing, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ENRICA_m_ds_w2', ENRICA_m_ds_w2)
#opal.symbol_import(o,'ENRICA_m_ds_w2', project='_Athlos_Harm_Dataset')
```


```{r,  echo=FALSE}
adl_dressing <- ENRICA_ds_w2
save(adl_dressing, file = paste0(datafolder, "/w2/adl_dressing.RData"))
```

### Wave 3

#### Study-specific variable description




| **Name** | `w3adl_dressing`|
|-|-|
| **Label** | `difficulties: dressing, including shoes and socks` |
| **Table name** | `ENRICA_spss_wave3` |
| **Categories** | `0 = Limitations; 1 = No limitations` |
| **Missings** | `NA` |
| **Description** |  |


* Description: 
```{r assign w3, echo=F,  echo=FALSE}
opal.assign.table.tibble(o, 'ENRICA_w3_adl_dressing','ENRICA.ENRICA_spss_wave3', variables=list('w3adl_dressing'), missings = TRUE)
```

```{r local w3, echo=F,  echo=FALSE}
ENRICA_w3_adl_dressing <- opal.execute(o,'ENRICA_w3_adl_dressing')
vari <- ENRICA_w3_adl_dressing$w3adl_dressing # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(ENRICA_w3_adl_dressing$w3adl_dressing)
ggplot(ENRICA_w3_adl_dressing, aes(x=factor(w3adl_dressing))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `NA into 999`

**R script:**
```{r harmo w3,   echo=TRUE}
ENRICA_ds_w3 <- tibble(id=ENRICA_w3_adl_dressing$id)
ENRICA_ds_w3$adl_dressing <- car::recode(ENRICA_w3_adl_dressing$w3adl_dressing, "NA = '999' ")
ENRICA_ds_w3$adl_dressing <- labelled(ENRICA_ds_w3$adl_dressing, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F,  echo=FALSE}
vari <- ENRICA_ds_w3$adl_dressing # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ENRICA_ds_w3$adl_dressing, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ENRICA_ds_w3, aes(x=factor(adl_dressing))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty getting dressed") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=F,  echo=FALSE}
AfterH <- table(ENRICA_ds_w3$adl_dressing)
X<-table(ENRICA_w3_adl_dressing$w3adl_dressing)
BeforeH <- c(X[1:2],sum(is.na(ENRICA_w3_adl_dressing$w3adl_dressing)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999")
kable(C)
```






```{r importOPAL w3, echo=FALSE,  echo=FALSE}

label(ENRICA_ds_w3$adl_dressing) <- "Difficulties for getting dressed"
#opal.assign.data(o, 'ENRICA_ds_w3', ENRICA_ds_w3)
#opal.symbol_import(o,'ENRICA_ds_w3', project='_Athlos_Harm_Dataset')

ENRICA_m_ds_w3 <- ENRICA_ds_w3
ENRICA_m_ds_w3$adl_dressing <- car::recode(ENRICA_m_ds_w3$adl_dressing, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ENRICA_m_ds_w3', ENRICA_m_ds_w3)
#opal.symbol_import(o,'ENRICA_m_ds_w3', project='_Athlos_Harm_Dataset')
```


```{r,  echo=FALSE}
adl_dressing <- ENRICA_ds_w3
save(adl_dressing, file = paste0(datafolder, "/w3/adl_dressing.RData"))
```

# Quality estimation

No comments

[Comments on the quality of the new harmonised variable. This section can be done in a later stage, once all variables are harmonised.]



```{r closeRsession, echo=FALSE,  echo=FALSE}
opal.logout(o)
```
