---
title: "IADL - Doing housework"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_ania.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `iadl_housewk`
* Variable label: `IADL-Difficulties for doing housework`
* Variable description: `IADL-Difficulties for doing housework`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

```{r, dataDirectory, echo=FALSE}
datafolder <- "../RData"
```

## ENRICA

### Wave 1

#### Study-specific variable description




| **Name** | `w1iadl_house`|
|-|-|
| **Label** | `IADL - doing house work and garden` |
| **Table name** | `ENRICA_spss_wave1` |
| **Categories** | `1 = Maintains house alone or with occasional assistance (e.g., "heavy work domestic help")`|  
|                | `2 = Performs light daily tasks such as dishwashing, bed making`|  
|                | `3 = Performs light daily tasks but cannot maintain acceptable level of cleanliness`|  
|                | `4 = Needs help with all home maintenance tasks`|  
|                | `5 = Does not participate in any housekeeping Tasks`| 
| **Missings** | `NA` |
| **Description** |  |


```{r assign w1, echo=F,  echo=FALSE}
opal.assign.table.tibble(o, 'ENRICA_w1_iadl_housewk','ENRICA.ENRICA_spss_wave1', variables=list('w1iadl_house'), missings = TRUE)
```

```{r local w1, echo=F,  echo=FALSE}
ENRICA_w1_iadl_housewk <- opal.execute(o,'ENRICA_w1_iadl_housewk')
vari <- ENRICA_w1_iadl_housewk$w1iadl_house
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(ENRICA_w1_iadl_housewk$w1iadl_house)
ggplot(ENRICA_w1_iadl_housewk, aes(x=factor(w1iadl_house))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2,3,4,5 into 0`
* `NA into 999`

**R script:**
```{r harmo w1,   echo=TRUE}
ENRICA_ds_w1 <- tibble(id=ENRICA_w1_iadl_housewk$id)
ENRICA_ds_w1$iadl_housewk <- car::recode(ENRICA_w1_iadl_housewk$w1iadl_house, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0'; NA = '999' ")
ENRICA_ds_w1$iadl_housewk <- labelled(ENRICA_ds_w1$iadl_housewk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F,  echo=FALSE}
vari <- ENRICA_ds_w1$iadl_housewk # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ENRICA_ds_w1$iadl_housewk, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ENRICA_ds_w1, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F,  echo=FALSE}
AfterH <- table(ENRICA_ds_w1$iadl_housewk)
X<-table(ENRICA_w1_iadl_housewk$w1iadl_house)
BeforeH <- c(sum(X[2:5]),X[1],sum(is.na(ENRICA_w1_iadl_housewk$w1iadl_house)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","NA->999") 
kable(C)
```






```{r importOPAL w1, echo=FALSE,  echo=FALSE}

label(ENRICA_ds_w1$iadl_housewk) <- "Difficulties for doing housework"
#opal.assign.data(o, 'ENRICA_ds_w1', ENRICA_ds_w1)
#opal.symbol_import(o,'ENRICA_ds_w1', project='_Athlos_Harm_Dataset')

ENRICA_m_ds_w1 <- ENRICA_ds_w1
ENRICA_m_ds_w1$iadl_housewk <- car::recode(ENRICA_m_ds_w1$iadl_housewk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ENRICA_m_ds_w1', ENRICA_m_ds_w1)
#opal.symbol_import(o,'ENRICA_m_ds_w1', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
iadl_housewk<- ENRICA_ds_w1
save(iadl_housewk, file = paste0(datafolder, "/w1/iadl_housewk.RData"))
```

### Wave 2

#### Study-specific variable description




| **Name** | `w2iadl_house`|
|-|-|
| **Label** | `IADL - doing house work and garden` |  
| **Table name** | `ENRICA_spss_wave2` |  
| **Categories** | `1 = Maintains house alone or with occasional assistance (e.g., "heavy work domestic help")`|  
|                | `2 = Performs light daily tasks such as dishwashing, bed making`|  
|                | `3 = Performs light daily tasks but cannot maintain acceptable level of cleanliness`|  
|                | `4 = Needs help with all home maintenance tasks`|  
|                | `5 = Does not participate in any housekeeping Tasks`|  
| **Missings** | `NA` |  
| **Description** |  |  


```{r assign w2, echo=F,  echo=FALSE}
opal.assign.table.tibble(o, 'ENRICA_w2_iadl_housewk','ENRICA.ENRICA_spss_wave2', variables=list('w2iadl_house'), missings = TRUE)
```

```{r local w2, echo=F,  echo=FALSE}
ENRICA_w2_iadl_housewk <- opal.execute(o,'ENRICA_w2_iadl_housewk')
vari <- ENRICA_w2_iadl_housewk$w2iadl_house
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(ENRICA_w2_iadl_housewk$w2iadl_house)
ggplot(ENRICA_w2_iadl_housewk, aes(x=factor(w2iadl_house))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2,3,4,5 into 0`
* `NA into 999`

**R script:**
```{r harmo w2,   echo=TRUE}
ENRICA_ds_w2 <- tibble(id=ENRICA_w2_iadl_housewk$id)
ENRICA_ds_w2$iadl_housewk <- car::recode(ENRICA_w2_iadl_housewk$w2iadl_house, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0'; NA = '999' ")
ENRICA_ds_w2$iadl_housewk <- labelled(ENRICA_ds_w2$iadl_housewk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F,  echo=FALSE}
vari <- ENRICA_ds_w2$iadl_housewk # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ENRICA_ds_w2$iadl_housewk, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ENRICA_ds_w2, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F,  echo=FALSE}
AfterH <- table(ENRICA_ds_w2$iadl_housewk)
X<-table(ENRICA_w2_iadl_housewk$w2iadl_house)
BeforeH <- c(sum(X[2:5]),X[1],sum(is.na(ENRICA_w2_iadl_housewk$w2iadl_house)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","NA->999") 
kable(C)
```






```{r importOPAL w2, echo=FALSE,  echo=FALSE}

label(ENRICA_ds_w2$iadl_housewk) <- "Difficulties for doing housework"
#opal.assign.data(o, 'ENRICA_ds_w2', ENRICA_ds_w2)
#opal.symbol_import(o,'ENRICA_ds_w2', project='_Athlos_Harm_Dataset')

ENRICA_m_ds_w2 <- ENRICA_ds_w2
ENRICA_m_ds_w2$iadl_housewk <- car::recode(ENRICA_m_ds_w2$iadl_housewk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ENRICA_m_ds_w2', ENRICA_m_ds_w2)
#opal.symbol_import(o,'ENRICA_m_ds_w2', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
iadl_housewk<- ENRICA_ds_w2
save(iadl_housewk, file = paste0(datafolder, "/w2/iadl_housewk.RData"))
```

### Wave 3

#### Study-specific variable description




| **Name** | `w3iadl_house`|
|-|-|
| **Label** | `IADL - doing house work and garden` |
| **Table name** | `ENRICA_spss_wave3` |
| **Categories** | `1 = Maintains house alone or with occasional assistance (e.g., "heavy work domestic help")`|  
|                | `2 = Performs light daily tasks such as dishwashing, bed making`|  
|                | `3 = Performs light daily tasks but cannot maintain acceptable level of cleanliness`|  
|                | `4 = Needs help with all home maintenance tasks`|  
|                | `5 = Does not participate in any housekeeping Tasks`| 
| **Missings** | `NA` |
| **Description** |  |


```{r assign w3, echo=F,  echo=FALSE}
opal.assign.table.tibble(o, 'ENRICA_w3_iadl_housewk','ENRICA.ENRICA_spss_wave3', variables=list('w3iadl_house'), missings = TRUE)
```

```{r local w3, echo=F,  echo=FALSE}
ENRICA_w3_iadl_housewk <- opal.execute(o,'ENRICA_w3_iadl_housewk')
vari <- ENRICA_w3_iadl_housewk$w3iadl_house
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(ENRICA_w3_iadl_housewk$w3iadl_house)
ggplot(ENRICA_w3_iadl_housewk, aes(x=factor(w3iadl_house))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2,3,4,5 into 0`
* `NA into 999`

**R script:**
```{r harmo w3,   echo=TRUE}
ENRICA_ds_w3 <- tibble(id=ENRICA_w3_iadl_housewk$id)
ENRICA_ds_w3$iadl_housewk <- car::recode(ENRICA_w3_iadl_housewk$w3iadl_house, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0'; NA = '999' ")
ENRICA_ds_w3$iadl_housewk <- labelled(ENRICA_ds_w3$iadl_housewk, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F,  echo=FALSE}
vari <- ENRICA_ds_w3$iadl_housewk # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ENRICA_ds_w3$iadl_housewk, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ENRICA_ds_w3, aes(x=factor(iadl_housewk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Doing housework") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=F,  echo=FALSE}
AfterH <- table(ENRICA_ds_w3$iadl_housewk)
X<-table(ENRICA_w3_iadl_housewk$w3iadl_house)
BeforeH <- c(sum(X[2:5]),X[1],sum(is.na(ENRICA_w3_iadl_housewk$w3iadl_house)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","NA->999") 
kable(C)
```






```{r importOPAL w3, echo=FALSE,  echo=FALSE}

label(ENRICA_ds_w3$iadl_housewk) <- "Difficulties for doing housework"
#opal.assign.data(o, 'ENRICA_ds_w3', ENRICA_ds_w3)
#opal.symbol_import(o,'ENRICA_ds_w3', project='_Athlos_Harm_Dataset')

ENRICA_m_ds_w3 <- ENRICA_ds_w3
ENRICA_m_ds_w3$iadl_housewk <- car::recode(ENRICA_m_ds_w3$iadl_housewk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ENRICA_m_ds_w3', ENRICA_m_ds_w3)
#opal.symbol_import(o,'ENRICA_m_ds_w3', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
iadl_housewk<- ENRICA_ds_w3
save(iadl_housewk, file = paste0(datafolder, "/w3/iadl_housewk.RData"))
```

# Quality estimation

'5. “Does not participate in any housekeeping Tasks” was considered as 0 (difficulty).

[Comments on the quality of the new harmonised variable. This section can be done in a later stage, once all variables are harmonised.]



```{r closeRsession, echo=FALSE,  echo=FALSE}
opal.logout(o)
```
