---
title: "Orientation in time"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `orientation`
* Variable label: `Orientation in time`
* Variable description: `Difficulties for orientation in time, evaluated by a set of questions about the date and day of the week.`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## Spain


### Wave 1

Not found.



### Wave 2

#### Study-specific variable description

| **Name** |`w2mec_oritempo1`|`w2mec_oritempo2`|`w2mec_oritempo3`|`w2mec_oritempo5`|
|-|-|-|-|-|
| **Label** |`What day of the week is it?`|`What is the date today?: day`|`What is the date today?: month`|`What is the date today?: year`|
| **Table name** |`ENRICA_spss_wave2`|`ENRICA_spss_wave2`|`ENRICA_spss_wave2`|`ENRICA_spss_wave2`|
| **Categories** |`0 = fail; 1 = success`|`0 = fail; 1 = success`|`0 = fail; 1 = success`|`0 = fail; 1 = success`|
| **Missings** |`NA`|`NA`|`NA`|`NA`|
| **Description** |  |  |  |  |

```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w2_orientation','ENRICA.ENRICA_spss_wave2', variables=list('w2mec_oritempo1','w2mec_oritempo2','w2mec_oritempo3','w2mec_oritempo5'), missings = TRUE)
```

```{r local w2, echo=F}
ENRICA_w2_orientation <- opal.execute(o,'ENRICA_w2_orientation')
vari <- ENRICA_w2_orientation$w2mec_oritempo1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "w2mec_oritempo1")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w2_orientation, aes(x=factor(w2mec_oritempo1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-Weekday") + ylab("Frequency")
vari <- ENRICA_w2_orientation$w2mec_oritempo2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "w2mec_oritempo2")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w2_orientation, aes(x=factor(w2mec_oritempo2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-Day") + ylab("Frequency")
vari <- ENRICA_w2_orientation$w2mec_oritempo3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "w2mec_oritempo3")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w2_orientation, aes(x=factor(w2mec_oritempo3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-Month") + ylab("Frequency")
vari <- ENRICA_w2_orientation$w2mec_oritempo5
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "w2mec_oritempo5")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w2_orientation, aes(x=factor(w2mec_oritempo5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-Year") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `all 1 into 1` 
* `some 0 into 0`
* `NA into 999`

**R script:**


```{r harmo w2}
ENRICA_ds_w2 <- tibble(id=ENRICA_w2_orientation$id)
ENRICA_ds_w2$orientation <- rep(999,length(ENRICA_ds_w2$id))
ENRICA_ds_w2$orientation[((ENRICA_w2_orientation$w2mec_oritempo1==1)&(ENRICA_w2_orientation$w2mec_oritempo2==1)&(ENRICA_w2_orientation$w2mec_oritempo3==1)&(ENRICA_w2_orientation$w2mec_oritempo5==1))]<-1
ENRICA_ds_w2$orientation[(ENRICA_w2_orientation$w2mec_oritempo1==0)|(ENRICA_w2_orientation$w2mec_oritempo2==0)|(ENRICA_w2_orientation$w2mec_oritempo3==0)|(ENRICA_w2_orientation$w2mec_oritempo5==0)]<-0
ENRICA_ds_w2$orientation <- labelled(ENRICA_ds_w2$orientation, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vari <- ENRICA_ds_w2$orientation
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "orientation")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ENRICA_ds_w2, aes(x=factor(orientation))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
AfterH <- table(ENRICA_ds_w2$orientation)
combi<-sum(na.omit((ENRICA_w2_orientation$w2mec_oritempo1==1)&(ENRICA_w2_orientation$w2mec_oritempo2==1)&(ENRICA_w2_orientation$w2mec_oritempo3==1)&(ENRICA_w2_orientation$w2mec_oritempo5==1)))
nota<-length(ENRICA_w2_orientation$w2mec_oritempo1)-length(na.omit(ENRICA_w2_orientation$w2mec_oritempo1))
BeforeH <- c(length(ENRICA_w2_orientation$w2mec_oritempo1)-combi-nota,combi,nota)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("some 2->0","all 1->1","NA->999") 
kable(C)
```



```{r importOPAL w2, echo=FALSE}
label(ENRICA_ds_w2$orientation) <- "Difficulties for orientation in time, evaluated by a set of questions about the date and day of the week"
#opal.assign.data(o, 'ENRICA_ds_w2', ENRICA_ds_w2)
#opal.symbol_import(o,'ENRICA_ds_w2', project='_Athlos_Harm_Dataset')
orientation <- ENRICA_ds_w2
save(orientation, file = "../RData/w2/orientation.RData")

ENRICA_m_ds_w2 <- ENRICA_ds_w2
ENRICA_m_ds_w2$orientation <- car::recode(ENRICA_m_ds_w2$orientation, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ENRICA_m_ds_w2', ENRICA_m_ds_w2)
#opal.symbol_import(o,'ENRICA_m_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 3

#### Study-specific variable description

| **Name** |`w3mec_oritempo1`|`w3mec_oritempo2`|`w3mec_oritempo3`|`w3mec_oritempo5`|
|-|-|-|-|-|
| **Label** |`What day of the week is it?`|`What is the date today?: day`|`What is the date today?: month`|`What is the date today?: year`|
| **Table name** |`ENRICA_spss_wave3`|`ENRICA_spss_wave3`|`ENRICA_spss_wave3`|`ENRICA_spss_wave3`|
| **Categories** |`0 = fail; 1 = success`|`0 = fail; 1 = success`|`0 = fail; 1 = success`|`0 = fail; 1 = success`|
| **Missings** |`NA`|`NA`|`NA`|`NA`|
| **Description** |  |  |  |  |



```{r assign w3, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w3_orientation','ENRICA.ENRICA_spss_wave3', variables=list('w3mec_oritempo1','w3mec_oritempo2','w3mec_oritempo3','w3mec_oritempo5'), missings = TRUE)
```

```{r local w3, echo=F}
ENRICA_w3_orientation <- opal.execute(o,'ENRICA_w3_orientation')
vari <- ENRICA_w3_orientation$w3mec_oritempo1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "w3mec_oritempo1")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w3_orientation, aes(x=factor(w3mec_oritempo1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-Weekday") + ylab("Frequency")
vari <- ENRICA_w3_orientation$w3mec_oritempo2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "w3mec_oritempo2")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w3_orientation, aes(x=factor(w3mec_oritempo2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-Day") + ylab("Frequency")
vari <- ENRICA_w3_orientation$w3mec_oritempo3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "w3mec_oritempo3")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w3_orientation, aes(x=factor(w3mec_oritempo3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-Month") + ylab("Frequency")
vari <- ENRICA_w3_orientation$w3mec_oritempo5
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "w3mec_oritempo5")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w3_orientation, aes(x=factor(w3mec_oritempo5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time-Year") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `all 1 into 1` 
* `some 0 into 0`
* `NA into 999`

**R script:**

```{r harmo w3}
ENRICA_ds_w3 <- tibble(id=ENRICA_w3_orientation$id)
ENRICA_ds_w3$orientation <- rep(999,length(ENRICA_ds_w3$id))
ENRICA_ds_w3$orientation[((ENRICA_w3_orientation$w3mec_oritempo1==1)&(ENRICA_w3_orientation$w3mec_oritempo2==1)&(ENRICA_w3_orientation$w3mec_oritempo3==1)&(ENRICA_w3_orientation$w3mec_oritempo5==1))]<-1
ENRICA_ds_w3$orientation[(ENRICA_w3_orientation$w3mec_oritempo1==0)|(ENRICA_w3_orientation$w3mec_oritempo2==0)|(ENRICA_w3_orientation$w3mec_oritempo3==0)|(ENRICA_w3_orientation$w3mec_oritempo5==0)]<-0
ENRICA_ds_w3$orientation <- labelled(ENRICA_ds_w3$orientation, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}
vari <- ENRICA_ds_w3$orientation
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "orientation")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ENRICA_ds_w3, aes(x=factor(orientation))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("orientation in time") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=F}
AfterH <- table(ENRICA_ds_w3$orientation)
combi<-sum(na.omit((ENRICA_w3_orientation$w3mec_oritempo1==1)&(ENRICA_w3_orientation$w3mec_oritempo2==1)&(ENRICA_w3_orientation$w3mec_oritempo3==1)&(ENRICA_w3_orientation$w3mec_oritempo5==1)))
nota<-length(ENRICA_w3_orientation$w3mec_oritempo1)-length(na.omit(ENRICA_w3_orientation$w3mec_oritempo1))
BeforeH <- c(length(ENRICA_w3_orientation$w3mec_oritempo1)-combi-nota,combi,nota)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("some 2->0","all 1->1","NA->999") 
kable(C)
```





```{r importOPAL w3, echo=FALSE}
label(ENRICA_ds_w3$orientation) <- "Difficulties for orientation in time, evaluated by a set of questions about the date and day of the week"
#opal.assign.data(o, 'ENRICA_ds_w3', ENRICA_ds_w3)
#opal.symbol_import(o,'ENRICA_ds_w3', project='_Athlos_Harm_Dataset')
orientation <- ENRICA_ds_w3
save(orientation, file = "../RData/w3/orientation.RData")

ENRICA_m_ds_w3 <- ENRICA_ds_w3
ENRICA_m_ds_w3$orientation <- car::recode(ENRICA_m_ds_w3$orientation, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ENRICA_m_ds_w3', ENRICA_m_ds_w3)
#opal.symbol_import(o,'ENRICA_m_ds_w3', project='_Athlos_Harm_Dataset')
```


# Quality estimation
For this study, the variable is a composed combining 4 variables, which might be different from the 
calculation performed in other studies where other variables are also available (or some of these variables are not).


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
