---
title: "Cognition - Delayed recall"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `cog_del`
* Variable label: `Cognition - delayed recall`
* Variable description: `Delayed recall of a list of common nouns. Discrete variable: value 0 = <=25%; value 1 = >25%.`
* Domain: `Health status and functional limitations`
* Value type: `Categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | <=25%
1        | >25%

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process


## ENRICA


### Wave 1

Not found.



### Wave 2

#### Study-specific variable description

| **Name** | `w2mec_cog_del1`|`w2mec_cog_del2`|`w2mec_cog_del3`|
|-|-|-|-|
| **Label** | `What are the 3 objects I asked you to remember afew moments ago?: peseta` |`What are the 3 objects I asked you to remember afew moments ago?: caballo`|`What are the 3 objects I asked you to remember afew moments ago?: manzana`|
| **Table name** | `ENRICA_spss_wave2` |`ENRICA_spss_wave2` |`ENRICA_spss_wave2` |
| **Categories** | `0 = fail; 1 = success` |`0 = fail; 1 = success` |`0 = fail; 1 = success` |
| **Missings** | `NA` |`NA` |`NA` |
| **Description** |  |  |  |


```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w2_cog_del','ENRICA.ENRICA_spss_wave2', variables=list('w2mec_cog_del1','w2mec_cog_del2','w2mec_cog_del3'), missings = TRUE)
```

```{r local w2, echo=F}
ENRICA_w2_cog_del <- opal.execute(o,'ENRICA_w2_cog_del')
Continuous_summary(ENRICA_w2_cog_del$w2mec_cog_del1)
Continuous_summary(ENRICA_w2_cog_del$w2mec_cog_del2)
Continuous_summary(ENRICA_w2_cog_del$w2mec_cog_del3)
ggplot(ENRICA_w2_cog_del, aes(x=factor(w2mec_cog_del1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Delayed recall") + ylab("Frequency")
ggplot(ENRICA_w2_cog_del, aes(x=factor(w2mec_cog_del2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Delayed recall") + ylab("Frequency")
ggplot(ENRICA_w2_cog_del, aes(x=factor(w2mec_cog_del3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Delayed recall") + ylab("Frequency")
```

#### Harmonisation algorithm

No continuous variable can be generated.


To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `all 1 into 1`
* `some 0 into 0`
* `NA into 999`

**R script:**
```{r harmo w2}
ENRICA_ds_w2 <- tibble(id=ENRICA_w2_cog_del$id)
ENRICA_ds_w2$cog_del <- rep(999,length(ENRICA_w2_cog_del$id))
ENRICA_ds_w2$cog_del[which(ENRICA_w2_cog_del$w2mec_cog_del1==1&ENRICA_w2_cog_del$w2mec_cog_del2==1&ENRICA_w2_cog_del$w2mec_cog_del3==1)] <- 1
ENRICA_ds_w2$cog_del[which((ENRICA_w2_cog_del$w2mec_cog_del1==0)|(ENRICA_w2_cog_del$w2mec_cog_del2==0)|(ENRICA_w2_cog_del$w2mec_cog_del3==0))] <- 0
ENRICA_ds_w2$cog_del <- labelled(ENRICA_ds_w2$cog_del, labels = c(Yes=1, No=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
Continuous_summary(var = ENRICA_ds_w2$cog_del, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ENRICA_ds_w2, aes(x=factor(cog_del))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Delayed recall") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
AfterH <- table(ENRICA_ds_w2$cog_del)
X<-c(sum((ENRICA_w2_cog_del$w2mec_cog_del1==0&is.na(ENRICA_w2_cog_del$w2mec_cog_del2)==FALSE&is.na(ENRICA_w2_cog_del$w2mec_cog_del3)==FALSE)|(ENRICA_w2_cog_del$w2mec_cog_del2==0&is.na(ENRICA_w2_cog_del$w2mec_cog_del3)==FALSE&is.na(ENRICA_w2_cog_del$w2mec_cog_del1)==FALSE)|(ENRICA_w2_cog_del$w2mec_cog_del3==0&is.na(ENRICA_w2_cog_del$w2mec_cog_del1)==FALSE&is.na(ENRICA_w2_cog_del$w2mec_cog_del2)==FALSE),na.rm=TRUE),sum(ENRICA_w2_cog_del$w2mec_cog_del1==1&ENRICA_w2_cog_del$w2mec_cog_del2==1&ENRICA_w2_cog_del$w2mec_cog_del3==1,na.rm=TRUE))
BeforeH <- c(X[1:2],sum(is.na(ENRICA_w2_cog_del$w2mec_cog_del1)|is.na(ENRICA_w2_cog_del$w2mec_cog_del2)|is.na(ENRICA_w2_cog_del$w2mec_cog_del3)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("some 0->0","all 1->1","NA->999") 
kable(C)
```






```{r importOPAL w2, echo=FALSE}

label(ENRICA_ds_w2$cog_del) <- "Cognition- delayed recall"
#opal.assign.data(o, 'ENRICA_ds_w2', ENRICA_ds_w2)
#opal.symbol_import(o,'ENRICA_ds_w2', project='_Athlos_Harm_Dataset')
cog_del <- ENRICA_ds_w2
save(cog_del, file = "../RData/w2/cog_del.RData")
rm(cog_del)

ENRICA_m_ds_w2 <- ENRICA_ds_w2
ENRICA_m_ds_w2$cog_del <- car::recode(ENRICA_m_ds_w2$cog_del, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ENRICA_m_ds_w2', ENRICA_m_ds_w2)
#opal.symbol_import(o,'ENRICA_m_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 3

#### Study-specific variable description


| **Name** | `w3mec_cog_del1`|`w3mec_cog_del2`|`w3mec_cog_del3`|
|-|-|-|-|
| **Label** | `What are the 3 objects I asked you to remember afew moments ago?: peseta` |`What are the 3 objects I asked you to remember afew moments ago?: caballo`|`What are the 3 objects I asked you to remember afew moments ago?: manzana`|
| **Table name** | `ENRICA_spss_wave3` |`ENRICA_spss_wave3` |`ENRICA_spss_wave3` |
| **Categories** | `0 = fail; 1 = success` |`0 = fail; 1 = success` |`0 = fail; 1 = success` |
| **Missings** | `NA` |`NA` |`NA` |
| **Description** |  |  |  |

```{r assign w3, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w3_cog_del','ENRICA.ENRICA_spss_wave3', variables=list('w3mec_cog_del1','w3mec_cog_del2','w3mec_cog_del3'), missings = TRUE)
```

```{r local w3, echo=F}
ENRICA_w3_cog_del <- opal.execute(o,'ENRICA_w3_cog_del')
Continuous_summary(ENRICA_w3_cog_del$w3mec_cog_del1)
Continuous_summary(ENRICA_w3_cog_del$w3mec_cog_del2)
Continuous_summary(ENRICA_w3_cog_del$w3mec_cog_del3)
ggplot(ENRICA_w3_cog_del, aes(x=factor(w3mec_cog_del1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Delayed recall") + ylab("Frequency")
ggplot(ENRICA_w3_cog_del, aes(x=factor(w3mec_cog_del2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Delayed recall") + ylab("Frequency")
ggplot(ENRICA_w3_cog_del, aes(x=factor(w3mec_cog_del3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Delayed recall") + ylab("Frequency")
```

#### Harmonisation algorithm

No continuous variable can be generated.


To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `all 1 into 1`
* `some 0 into 0`
* `NA into 999`

**R script:**
```{r harmo w3}
ENRICA_ds_w3 <- tibble(id=ENRICA_w3_cog_del$id)
ENRICA_ds_w3$cog_del <- rep(999,length(ENRICA_w3_cog_del$id))
ENRICA_ds_w3$cog_del[which(ENRICA_w3_cog_del$w3mec_cog_del1==1&ENRICA_w3_cog_del$w3mec_cog_del2==1&ENRICA_w3_cog_del$w3mec_cog_del3==1)] <- 1
ENRICA_ds_w3$cog_del[which((ENRICA_w3_cog_del$w3mec_cog_del1==0)|(ENRICA_w3_cog_del$w3mec_cog_del2==0)|(ENRICA_w3_cog_del$w3mec_cog_del3==0))] <- 0
ENRICA_ds_w3$cog_del <- labelled(ENRICA_ds_w3$cog_del, labels = c(Yes=1, No=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}
Continuous_summary(var = ENRICA_ds_w3$cog_del, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ENRICA_ds_w3, aes(x=factor(cog_del))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Delayed recall") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=F}
AfterH <- table(ENRICA_ds_w3$cog_del)
X<-c(sum((ENRICA_w3_cog_del$w3mec_cog_del1==0&is.na(ENRICA_w3_cog_del$w3mec_cog_del2)==FALSE&is.na(ENRICA_w3_cog_del$w3mec_cog_del3)==FALSE)|(ENRICA_w3_cog_del$w3mec_cog_del2==0&is.na(ENRICA_w3_cog_del$w3mec_cog_del3)==FALSE&is.na(ENRICA_w3_cog_del$w3mec_cog_del1)==FALSE)|(ENRICA_w3_cog_del$w3mec_cog_del3==0&is.na(ENRICA_w3_cog_del$w3mec_cog_del1)==FALSE&is.na(ENRICA_w3_cog_del$w3mec_cog_del2)==FALSE),na.rm=TRUE),sum(ENRICA_w3_cog_del$w3mec_cog_del1==1&ENRICA_w3_cog_del$w3mec_cog_del2==1&ENRICA_w3_cog_del$w3mec_cog_del3==1,na.rm=TRUE))
BeforeH <- c(X[1:2],sum(is.na(ENRICA_w3_cog_del$w3mec_cog_del1)|is.na(ENRICA_w3_cog_del$w3mec_cog_del2)|is.na(ENRICA_w3_cog_del$w3mec_cog_del3)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("some 0->0","all 1->1","NA->999") 
kable(C)
```






```{r importOPAL w3, echo=FALSE}

label(ENRICA_ds_w3$cog_del) <- "Cognition- delayed recall"
#opal.assign.data(o, 'ENRICA_ds_w3', ENRICA_ds_w3)
#opal.symbol_import(o,'ENRICA_ds_w3', project='_Athlos_Harm_Dataset')
cog_del <- ENRICA_ds_w3
save(cog_del, file = "../RData/w3/cog_del.RData")
rm(cog_del)

ENRICA_m_ds_w3 <- ENRICA_ds_w3
ENRICA_m_ds_w3$cog_del <- car::recode(ENRICA_m_ds_w3$cog_del, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ENRICA_m_ds_w3', ENRICA_m_ds_w3)
#opal.symbol_import(o,'ENRICA_m_ds_w3', project='_Athlos_Harm_Dataset')
```



# Quality estimation
[Comments on the quality of the new harmonised variable. This section can be done in a later stage, once all variables are harmonised.]

Since we only have discrete variables from the study we construct just the categorical variable with a specific algorithm.



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
