---
title: "Recent falls"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_laia.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `recent_falls`
* Variable label: `Recent falls in the last 6-24 months`
* Variable description: `Recent falls in the last 6-24 months`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Recent falls"
ds_label_all <- "Recent falls in the last 6-24 months"
```


# Data process


## ENRICA

### Wave 1

Not found.



### Wave 2

#### Study-specific variable description




| **Name** | `w2falls`|
|-|-|
| **Label** | `falls during the last year?` |
| **Table name** | `ENRICA_spss_wave2` |
| **Categories** | `0 = No; 1 = Yes` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w2_recent_falls','ENRICA.ENRICA_spss_wave2', variables=list('w2falls'), missings = TRUE)
ENRICA_w2_recent_falls <- opal.execute(o,'ENRICA_w2_recent_falls')
```

```{r local w2, echo=F}
vari <- ENRICA_w2_recent_falls$w2falls
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w2_recent_falls, aes(x=factor(w2falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo w2}
ENRICA_ds_w2 <- tibble(id=ENRICA_w2_recent_falls$id)
ENRICA_ds_w2$recent_falls <- car::recode(ENRICA_w2_recent_falls$w2falls, "NA = '999' ")
ENRICA_ds_w2$recent_falls <- labelled(ENRICA_ds_w2$recent_falls, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vari <- ENRICA_ds_w2$recent_falls
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ENRICA_ds_w2, aes(x=factor(recent_falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
AfterH <- table(ENRICA_ds_w2$recent_falls)
X<-table(ENRICA_w2_recent_falls$w2falls)
BeforeH <- c(X[1:2],sum(is.na(ENRICA_w2_recent_falls$w2falls)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999") 
kable(C)
```


```{r importOPAL w2, echo=FALSE}
label(ENRICA_ds_w2$recent_falls) <- ds_label_all
recent_falls <- ENRICA_ds_w2
save(recent_falls, file = "../RData/w2/recent_falls.RData")
#opal.assign.data(o, 'ENRICA_ds_w2', ENRICA_ds_w2)
#opal.symbol_import(o,'ENRICA_ds_w2', project='_Athlos_Harm_Dataset')

ENRICA_m_ds_w2 <- ENRICA_ds_w2
ENRICA_m_ds_w2$recent_falls <- car::recode(ENRICA_m_ds_w2$recent_falls, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ENRICA_m_ds_w2', ENRICA_m_ds_w2)
#opal.symbol_import(o,'ENRICA_m_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 3

#### Study-specific variable description




| **Name** | `w3falls`|
|-|-|
| **Label** | `falls during the last year?` |
| **Table name** | `ENRICA_spss_wave3` |
| **Categories** | `0 = No; 1 = Yes` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign w3, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w3_recent_falls','ENRICA.ENRICA_spss_wave3', variables=list('w3falls'), missings = TRUE)
ENRICA_w3_recent_falls <- opal.execute(o,'ENRICA_w3_recent_falls')
```

```{r local w3, echo=F}
vari <- ENRICA_w3_recent_falls$w3falls
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w3_recent_falls, aes(x=factor(w3falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `NA into 999`

**R script:**
```{r harmo w3}
ENRICA_ds_w3 <- tibble(id=ENRICA_w3_recent_falls$id)
ENRICA_ds_w3$recent_falls <- car::recode(ENRICA_w3_recent_falls$w3falls, "NA = '999' ")
ENRICA_ds_w3$recent_falls <- labelled(ENRICA_ds_w3$recent_falls, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}
vari <- ENRICA_ds_w3$recent_falls
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ENRICA_ds_w3, aes(x=factor(recent_falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=F}
AfterH <- table(ENRICA_ds_w3$recent_falls)
X<-table(ENRICA_w3_recent_falls$w3falls)
BeforeH <- c(X[1:2],sum(is.na(ENRICA_w3_recent_falls$w3falls)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","NA->999") 
kable(C)
```



```{r importOPAL w3, echo=FALSE}

label(ENRICA_ds_w3$recent_falls) <- "Recent falls in the last 6-24 months"
recent_falls <- ENRICA_ds_w3
save(recent_falls, file = "../RData/w3/recent_falls.RData")
#opal.assign.data(o, 'ENRICA_ds_w3', ENRICA_ds_w3)
#opal.symbol_import(o,'ENRICA_ds_w3', project='_Athlos_Harm_Dataset')

ENRICA_m_ds_w3 <- ENRICA_ds_w3
ENRICA_m_ds_w3$recent_falls <- car::recode(ENRICA_m_ds_w3$recent_falls, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ENRICA_m_ds_w3', ENRICA_m_ds_w3)
#opal.symbol_import(o,'ENRICA_m_ds_w3', project='_Athlos_Harm_Dataset')
```



# Quality estimation
No comments.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
