---
title: "Walking speed"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `walking_speed_c`
* Variable label: `Walking speed - Continuous`
* Variable description: `Walking speed - Continuous. It is measured assessing the time that is taken to walk a distance.`
* Value type: `continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


* Short name: `walking_speed`
* Variable label: `Walking speed`
* Variable description: `Walking speed. It is measured assessing the time that is taken to walk a distance.Discrete variable: value 0 = <=25%; value 1 = >25%.`
* Value type: `Categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | <=25%
1        | >25%

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Walking speed"
ds_label_walking_speed_c <- "Walking speed - Continuous. It is measured assessing the time that is taken to walk a distance"
ds_label_walking_speed <- "Walking speed. It is measured assessing the time that is taken to walk a distance.Discrete variable: value 0 = <=25%; value 1 = >25%."
```


# Data process

## Spain

### Wave 1 

Not found.



### Wave 2

#### Study-specific variable description



| **Name** | `w2walk_speed`|
|-|-|
| **Label** | |
| **Table name** | `ENRICA_spss_wave2` |
| **Categories** | `Continuous measure` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w2_walking','ENRICA.ENRICA_spss_wave2', variables=list('w2walk_speed'), missings = TRUE)
ENRICA_w2_walking <- opal.execute(o,'ENRICA_w2_walking')
```

```{r local w2, echo=F}
vari <- ENRICA_w2_walking$w2walk_speed # VARIABLE
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ENRICA_w2_walking, aes(w2walk_speed)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Walking time") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `walking_speed_c` from the study-specific variables it has to be recoded as follows:

* `NA into 999`
* `seconds data used to walk the 2.44 metre test are converted to speed as m/s`

To compute the harmonized variable `walking_speed` from `walking_speed_c` it has to be recoded as follows:

* `walking_speed_c <=25% into 0`
* `walking_speed_c >25% into 1`

**R script:**

```{r harmo w2}
#walking_speed_c
ENRICA_ds_w2 <- tibble(id=ENRICA_w2_walking$id)
ENRICA_ds_w2$walking_speed_c <- car::recode(2.44/ENRICA_w2_walking$w2walk_speed, "NA=999")
ENRICA_ds_w2$walking_speed_c <- labelled(ENRICA_ds_w2$walking_speed_c, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))

#walking_speed
Q <- quantile(car::recode(ENRICA_ds_w2$walking_speed_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

ENRICA_ds_w2$walking_speed <- car::recode(ENRICA_ds_w2[[2]], "0:Q=0; (Q+0.0000000000001):900=1")
ENRICA_ds_w2$walking_speed <- labelled(ENRICA_ds_w2[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vari <- ENRICA_ds_w2$walking_speed_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ENRICA_ds_w2, aes(x=(walking_speed_c))) + geom_bar(stat="count", width=0.1, fill="steelblue") + xlab("Walking speed") + ylab("Frequency") + xlim(0,9)

vari <- ENRICA_ds_w2$walking_speed
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ENRICA_ds_w2, aes(x=factor(walking_speed))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
Continous <- c(sum(na.omit(ENRICA_ds_w2[[2]])<=Q), sum(na.omit(ENRICA_ds_w2[[2]])>Q & na.omit(ENRICA_ds_w2[[2]])<900), sum(na.omit(ENRICA_ds_w2[[2]])==999))
Dicotomic <- table(ENRICA_ds_w2[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:Q->0","Q:900->1", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```



```{r importOPAL w2, echo=FALSE}
#opal.assign.data(o, 'ENRICA_ds_w2', ENRICA_ds_w2)
#opal.symbol_import(o,'ENRICA_ds_w2', project='_Athlos_Harm_Dataset')

label(ENRICA_ds_w2$walking_speed_c) <- ds_label_walking_speed_c
label(ENRICA_ds_w2$walking_speed) <- ds_label_walking_speed
walking_speed <- ENRICA_ds_w2
save(walking_speed, file = "../RData/w2/walking_speed.RData")
```



### Wave 3

#### Study-specific variable description


| **Name** | `w3walk_speed`|
|-|-|
| **Label** | |
| **Table name** | `ENRICA_spss_wave3` |
| **Categories** | `Continuous measure` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign w3, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w3_walking','ENRICA.ENRICA_spss_wave3', variables=list('w3walk_speed'), missings = TRUE)
ENRICA_w3_walking <- opal.execute(o,'ENRICA_w3_walking')
```

```{r local w3, echo=F}
vari <- ENRICA_w3_walking$w3walk_speed # VARIABLE
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) # SI NO HAY ATRIBUTO SHORT-NAME, A MANO
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ENRICA_w3_walking, aes(w3walk_speed)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Walking time") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `walking_speed_c` from the study-specific variables it has to be recoded as follows:

* `NA into 999`
* `seconds data used to walk the 2.44 metre test are converted to speed as m/s`

To compute the harmonized variable `walking_speed` from `walking_speed_c` it has to be recoded as follows:

* `walking_speed_c <=25% into 0`
* `walking_speed_c >25% into 1`

**R script:**

```{r harmo w3}
#walking_speed_c
ENRICA_ds_w3 <- tibble(id=ENRICA_w3_walking$id)
ENRICA_ds_w3$walking_speed_c <- car::recode(2.44/ENRICA_w3_walking$w3walk_speed, "NA = '999' ")
ENRICA_ds_w3$walking_speed_c <- labelled(ENRICA_ds_w3$walking_speed_c, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))

#walking_speed
Q <- quantile(car::recode(ENRICA_ds_w3$walking_speed_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

ENRICA_ds_w3$walking_speed <- car::recode(ENRICA_ds_w3[[2]], "0:Q=0; (Q+0.0000000000001):900=1")
ENRICA_ds_w3$walking_speed <- labelled(ENRICA_ds_w3[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}
vari <- ENRICA_ds_w3$walking_speed_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ENRICA_ds_w3, aes(x=(walking_speed_c))) + geom_bar(stat="count", width=0.1, fill="steelblue") + xlab("Walking speed") + ylab("Frequency") + xlim(0,9)

vari <- ENRICA_ds_w3$walking_speed
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ENRICA_ds_w3, aes(x=factor(walking_speed))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=F}
Continous <- c(sum(na.omit(ENRICA_ds_w3[[2]])<=Q), sum(na.omit(ENRICA_ds_w3[[2]])>Q & na.omit(ENRICA_ds_w3[[2]])<900), sum(na.omit(ENRICA_ds_w3[[2]])==999))
Dicotomic <- table(ENRICA_ds_w3[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:Q->0","Q:900->1", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```



```{r importOPAL w3, echo=FALSE}
#opal.assign.data(o, 'ENRICA_ds_w3', ENRICA_ds_w3)
#opal.symbol_import(o,'ENRICA_ds_w3', project='_Athlos_Harm_Dataset')
label(ENRICA_ds_w3$walking_speed_c) <- ds_label_walking_speed_c
label(ENRICA_ds_w3$walking_speed) <- ds_label_walking_speed
walking_speed <- ENRICA_ds_w3
save(walking_speed, file = "../RData/w3/walking_speed.RData")
```


# Quality estimation
The measure is based in one trial test.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
