---
title: "Pain"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `pain`
* Variable label: `Pain`
* Variable description: `Pain. It measures if the participant experiences some degree of pain or if the participant does not present any pain at all.`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## Spain


### Wave 1 

Not found.



### Wave 2

##### Study-specific variables




| **Name** | `w2pain_frequency`|
|-|-|
| **Label** | `How often do you feel pain?`|
| **Table name** | `ENRICA_spss_wave2` |
| **Categories** | `0 = Constantly; 1 = Every day; 2 = >=2 times/week; 3 = 1 time/week; 4 = 1-3 times/month; 5 = <1 time/month` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w2_pain','ENRICA.ENRICA_spss_wave2', variables=list('w2pain_frequency'), missings = TRUE)
```

```{r local w2, echo=F}
ENRICA_w2_pain <- opal.execute(o,'ENRICA_w2_pain')
vari <- ENRICA_w2_pain$w2pain_frequency
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "w2pain_frequency")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w2_pain, aes(x=factor(w2pain_frequency))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Pain") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0,1,2,3 into 0` 
* `4,5 into 1`
* `NA into 999`

**R script:**
```{r harmo w2}
ENRICA_ds_w2 <- tibble(id=ENRICA_w2_pain$id)
ENRICA_ds_w2$pain <- car::recode(ENRICA_w2_pain$w2pain_frequency, "0 = '0';1 = '0';2 = '0';3 = '0';4 = '1';5 = '1';NA = '999' ")
ENRICA_ds_w2$pain <- labelled(ENRICA_ds_w2$pain, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vari <- ENRICA_ds_w2$pain
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "pain")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ENRICA_ds_w2, aes(x=factor(pain))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Pain") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
AfterH <- table(ENRICA_ds_w2$pain)
X<-table(ENRICA_w2_pain$w2pain_frequency)
BeforeH <- c(sum(X[1:4]),sum(X[5:6]),sum(is.na(ENRICA_w2_pain$w2pain_frequency)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0,1,2,3->0","4,5->1","NA->999") 
kable(C)
```


```{r importOPAL w2, echo=FALSE}

label(ENRICA_ds_w2$pain) <- "Pain"
#opal.assign.data(o, 'ENRICA_ds_w2', ENRICA_ds_w2)
#opal.symbol_import(o,'ENRICA_ds_w2', project='_Athlos_Harm_Dataset')
pain <- ENRICA_ds_w2
save(pain, file = "../RData/w2/pain.RData")

ENRICA_m_ds_w2 <- ENRICA_ds_w2
ENRICA_m_ds_w2$pain <- car::recode(ENRICA_m_ds_w2$pain, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ENRICA_m_ds_w2', ENRICA_m_ds_w2)
#opal.symbol_import(o,'ENRICA_m_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 3

##### Study-specific variables




| **Name** | `w3pain_frequency`|
|-|-|
| **Label** | `How often do you feel pain?`|
| **Table name** | `ENRICA_spss_wave3` |
| **Categories** | `0 = Constantly; 1 = Every day; 2 = >=2 times/week; 3 = 1 time/week; 4 = 1-3 times/month; 5 = <1 time/month` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign w3, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w3_pain','ENRICA.ENRICA_spss_wave3', variables=list('w3pain_frequency'), missings = TRUE)
```

```{r local w3, echo=F}
ENRICA_w3_pain <- opal.execute(o,'ENRICA_w3_pain')
vari <- ENRICA_w3_pain$w3pain_frequency
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "w3pain_frequency")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w3_pain, aes(x=factor(w3pain_frequency))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Pain") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0,1,2,3 into 0` 
* `4,5 into 1`
* `NA into 999`

**R script:**
```{r harmo w3}
ENRICA_ds_w3 <- tibble(id=ENRICA_w3_pain$id)
ENRICA_ds_w3$pain <- car::recode(ENRICA_w3_pain$w3pain_frequency, "0 = '0';1 = '0';2 = '0';3 = '0';4 = '1';5 = '1';NA = '999' ")
ENRICA_ds_w3$pain <- labelled(ENRICA_ds_w3$pain, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}
vari <- ENRICA_ds_w3$pain
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "pain")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ENRICA_ds_w3, aes(x=factor(pain))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Pain") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=F}
AfterH <- table(ENRICA_ds_w3$pain)
X<-table(ENRICA_w3_pain$w3pain_frequency)
BeforeH <- c(sum(X[1:4]),sum(X[5:6]),sum(is.na(ENRICA_w3_pain$w3pain_frequency)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0,1,2,3->0","4,5->1","NA->999") 
kable(C)
```




```{r importOPAL w3, echo=FALSE}

label(ENRICA_ds_w3$pain) <- "Pain"
#opal.assign.data(o, 'ENRICA_ds_w3', ENRICA_ds_w3)
#opal.symbol_import(o,'ENRICA_ds_w3', project='_Athlos_Harm_Dataset')
pain <- ENRICA_ds_w3
save(pain, file = "../RData/w3/pain.RData")

ENRICA_m_ds_w3 <- ENRICA_ds_w3
ENRICA_m_ds_w3$pain <- car::recode(ENRICA_m_ds_w3$pain, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ENRICA_m_ds_w3', ENRICA_m_ds_w3)
#opal.symbol_import(o,'ENRICA_m_ds_w3', project='_Athlos_Harm_Dataset')
```



# Quality estimation
No comments.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
