---
title: "LDL cholesterol"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/ldl_cholDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/ldl_cholDS.R')
```


# Data process


## Poland

### Wave 1 

#### Study-specific variable description

| **Name** | `ldl` |
|-|-|
| **Label** | `Ldl (mmol/l) [Calculated with formula from TC, HDL & TG]` |
| **Table name** | `Po_baseline_etic` |
| **Categories:**| `continuous` |
| **Missings:**| `NA` |
| **Description** |  | 

   

```{r assign pol_w1, echo=F }

opal.assign.table.tibble(o, 'HAPIEE_pol_w1','HAPIEE.Po_baseline_etic', variables=list('ldl'), missings = TRUE)
HAPIEE_pol_w1 <- opal.execute(o,'HAPIEE_pol_w1')

```

```{r local pol_w1, echo=F}

vbl <- HAPIEE_pol_w1$ldl
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "ldl") 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HAPIEE_pol_w1, aes(ldl)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `ldl_chol` from the study-specific variable it has to be recoded as follows:

* `multiply mmol/L by 38.67`
* `NA into 999`

**R script:**

```{r harmo pol_w1}

HAPIEE_ds_pol_w1 <- tibble(id=HAPIEE_pol_w1$id)
HAPIEE_ds_pol_w1$ldl_chol <- car::recode(38.67*HAPIEE_pol_w1$ldl, "NA = 999 ")

```

#### Statistical description of the new harmonised variable
```{r descript pol_w1, echo=F}

vbl <- HAPIEE_ds_pol_w1$ldl_chol
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HAPIEE_ds_pol_w1,!vbl %in% miss_values_vector), aes(ldl_chol)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation pol_w1, echo=F}
```





### Wave 2

Not found.


## Czech Republic


### Wave 1 

#### Study-specific variable description

| **Name** | `ldl` |
|-|-|
| **Label** | `Ldl (mmol/l) [Calculated with formula from TC, HDL & TG]` |
| **Table name** | `Cz_baseline_etic` |
| **Categories:**| `continuous` |
| **Missings:**| `NA` |
| **Description** |  | 

   

```{r assign cz_w1, echo=F }

opal.assign.table.tibble(o, 'HAPIEE_cz_w1','HAPIEE.Cz_baseline_etic', variables=list('ldl'), missings = TRUE)
HAPIEE_cz_w1 <- opal.execute(o,'HAPIEE_cz_w1')

```

```{r local cz_w1, echo=F}

vbl <- HAPIEE_cz_w1$ldl
vbl_miss <- NA
kable(Continuous_summary(vbl, missing_values = vbl_miss)[3], caption = "ldl") 
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HAPIEE_cz_w1,!vbl %in% vbl_miss), aes(ldl)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `ldl_chol` from the study-specific variable it has to be recoded as follows:

* `multiply mmol/L by 38.67`
* `NA into 999`

**R script:**

```{r harmo cz_w1}

HAPIEE_ds_cz_w1 <- tibble(id=HAPIEE_cz_w1$id)
HAPIEE_ds_cz_w1$ldl_chol <- car::recode(38.67*HAPIEE_cz_w1$ldl, "NA = 999 ")

```

#### Statistical description of the new harmonised variable
```{r descript cz_w1, echo=F}

vbl <- HAPIEE_ds_cz_w1$ldl_chol
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HAPIEE_ds_cz_w1,!vbl %in% miss_values_vector), aes(ldl_chol)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation cz_w1, echo=F}
```





### Wave 2

Not found.




## Lithuania


### Wave 1 

#### Study-specific variable description

| **Name** | `ldl` |
|-|-|
| **Label** | `Ldl (mmol/l) [Calculated with formula from TC, HDL & TG]` |
| **Table name** | `Li_baseline_etic` |
| **Categories:**| `continuous` |
| **Missings:**| `NA` |
| **Description** |  | 

   

```{r assign li_w1, echo=F }

opal.assign.table.tibble(o, 'HAPIEE_li_w1','HAPIEE.Li_baseline_etic', variables=list('ldl'), missings = TRUE)
HAPIEE_li_w1 <- opal.execute(o,'HAPIEE_li_w1')

```

```{r local li_w1, echo=F}

vbl <- HAPIEE_li_w1$ldl
vbl_miss <- NA
kable(Continuous_summary(vbl, missing_values = vbl_miss)[3], caption = "ldl") 
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(HAPIEE_li_w1,!vbl %in% vbl_miss), aes(ldl)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `ldl_chol` from the study-specific variable it has to be recoded as follows:

* `multiply mmol/L by 38.67`
* `less than 0 or NA into 999`

**R script:**

```{r harmo li_w1}

HAPIEE_ds_li_w1 <- tibble(id=HAPIEE_li_w1$id)
HAPIEE_ds_li_w1$ldl_chol <- car::recode(38.67*HAPIEE_li_w1$ldl, "NA = 999 ")

```

#### Statistical description of the new harmonised variable
```{r descript li_w1, echo=F}

vbl <- HAPIEE_ds_li_w1$ldl_chol
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(HAPIEE_ds_li_w1,!vbl %in% miss_values_vector), aes(ldl_chol)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation li_w1, echo=F}
```


## Summary of descriptive statistics of the harmonised variable accross populations and waves



```{r summ}

l.hds <- list(pol_w1 = HAPIEE_ds_pol_w1, cz_w1 = HAPIEE_ds_cz_w1, li_w1 = HAPIEE_ds_li_w1)
m.hds <- list()

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cont_label)
  m_name <- paste0("HAPIEE_m_ds_",name)
  assign(m_name, aux_object)
  m.hds[[name]] <- get(paste0("HAPIEE_m_ds_",name))
  rm(aux_object)
}

t.summ <- summary(m.hds[[1]][2])[1:6]
t.hds <- substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1)
for (i in seq_along(l.hds)){
  t.summ <- summary(m.hds[[i]][2])[1:6]
  t.hds <- cbind(t.hds,as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))))
}
t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))

dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],names(l.hds))
kable(t.hds)

```


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  ldl_chol <- l.hds[[index]]
  save(ldl_chol, file = paste0(datafolder,names(l.hds)[index],"/ldl_chol.RData"))
}

```
<!-- ########################################################## --> 

# Quality estimation


<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```


