---
title: "Cognition"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `cog_stat`
* Variable label: `Cognitive status of the participant, assessed by the Mini Mental State Examination`
* Domain: `Psycological measures`
* Value type: `categorical`
* Category coding:
* Comments: `The test used is the Mini Mental State Examination (MMSE). Two values have been created for the potential variable: 0=no cognitive impairment (when the score is greater or equal to 23) and 1=cognitive impairment (when the score is lower to 23).`

**Code** | **Category Label**
-------- | ------------------------
0        | no cognitive impairment
1        | cognitive impairment

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


```{r lab, echo=FALSE}
ds_label <- "Cognitive status"
ds_label_all <- "Cognitive status of the participant, assessed by the Mini Mental State Examination"
```

<!-- ########################################################## --> 

# Data process

## Spain

### Wave 1 

There is no varibale. 





### Wave 2 

#### Study-specific variable description

| **Name** | `w2mec`|
|-|-|
| **Label** | |
| **Table name** | `ENRICA_spss_wave2` |
| **Description** |  |

```{r assign2,  echo=FALSE}
opal.assign.table.tibble(o, 'ENRICA_cog','ENRICA.ENRICA_spss_wave2',
                         variables=list('w2mec'), missings = TRUE)
ENRICA_cog <- opal.execute(o,'ENRICA_cog')
```

```{r local2,  echo=FALSE}
vari <- ENRICA_cog$w2mec
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ENRICA_cog, aes(vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `w2mec < 24 into 1` 
* `w2mec >= 24 into 0`
* `NA into 999`

**R script:**

```{r harmo2,   echo=TRUE}
ENRICA_ds_w2 <- tibble(id=ENRICA_cog$id)
ENRICA_ds_w2$cog_stat <- car::recode(ENRICA_cog[[2]], "lo:23=1; 24:900=0; NA=999")
ENRICA_ds_w2$cog_stat <- labelled(ENRICA_ds_w2$cog_stat, labels = c("no cognitive impairment"=0, "cognitive impairment"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2,  echo=FALSE}
vari <- ENRICA_ds_w2$cog_stat
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ENRICA_ds_w2, aes(x=factor(cog_stat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation2,  echo=FALSE}
BeforeH <- c(sum(na.omit(ENRICA_cog[[2]])>23),sum(na.omit(ENRICA_cog[[2]])<=23), sum(is.na(ENRICA_cog[[2]])))
AfterH <- table(ENRICA_ds_w2$cog_stat)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("(24-30)->0","(0-23)->1", "NA->999")
kable(C)
```


 
```{r importOPAL2,  echo=FALSE}
#opal.assign.data(o, 'ENRICA_ds_w2', ENRICA_ds_w2)
#opal.symbol_import(o,'ENRICA_ds_w2', project='_Athlos_Harm_Dataset')
label(ENRICA_ds_w2$cog_stat) <- ds_label_all
cog_stat <- ENRICA_ds_w2
save(cog_stat, file = "../RData/w2/cog_stat.RData")
rm(cog_stat)

ENRICA_m_ds_w2 <- ENRICA_ds_w2
ENRICA_m_ds_w2$cog_stat <- car::recode(ENRICA_m_ds_w2$cog_stat, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ENRICA_m_ds_w2', ENRICA_m_ds_w2)
#opal.symbol_import(o,'ENRICA_m_ds_w2', project='_Athlos_Harm_Dataset')
```






### Wave 3 

#### Study-specific variable description

 

| **Name** | `w3mec`|
|-|-|
| **Label** | |
| **Table name** | `ENRICA_spss_wave3` |
| **Description** |  |

```{r assign3,  echo=FALSE}
opal.assign.table.tibble(o, 'ENRICA_cog','ENRICA.ENRICA_spss_wave3',
                         variables=list('w3mec'), missings = TRUE)
ENRICA_cog <- opal.execute(o,'ENRICA_cog')
```

```{r local3,  echo=FALSE}
vari <- ENRICA_cog$w3mec
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ENRICA_cog, aes(vari)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `w3mec < 24 into 1` 
* `w3mec >= 24 into 0`
* `NA into 999`

**R script:**

```{r harmo3,   echo=TRUE}
ENRICA_ds_w3 <- tibble(id=ENRICA_cog$id)
ENRICA_ds_w3$cog_stat <- car::recode(ENRICA_cog[[2]], "lo:23=1; 24:900=0; NA=999")
ENRICA_ds_w3$cog_stat <- labelled(ENRICA_ds_w3$cog_stat, labels = c("no cognitive impairment"=0, "cognitive impairment"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3,  echo=FALSE}
vari <- ENRICA_ds_w3$cog_stat
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ENRICA_ds_w3, aes(x=factor(cog_stat))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation3,  echo=FALSE}
BeforeH <- c(sum(na.omit(ENRICA_cog[[2]])>23),sum(na.omit(ENRICA_cog[[2]])<=23), sum(is.na(ENRICA_cog[[2]])))
AfterH <- table(ENRICA_ds_w3$cog_stat)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("(24-30)->0","(0-23)->1", "NA->999")
kable(C)
```

 

 
```{r importOPAL3,  echo=FALSE}
#opal.assign.data(o, 'ENRICA_ds_w3', ENRICA_ds_w3)
#opal.symbol_import(o,'ENRICA_ds_w3', project='_Athlos_Harm_Dataset')
label(ENRICA_ds_w3$cog_stat) <- ds_label_all
cog_stat <- ENRICA_ds_w3
save(cog_stat, file = "../RData/w3/cog_stat.RData")
rm(cog_stat)

ENRICA_m_ds_w3 <- ENRICA_ds_w3
ENRICA_m_ds_w3$cog_stat <- car::recode(ENRICA_m_ds_w3$cog_stat, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ENRICA_m_ds_w3', ENRICA_m_ds_w3)
#opal.symbol_import(o,'ENRICA_m_ds_w3', project='_Athlos_Harm_Dataset')
```

# Quality estimation

Variable not available for the first wave

```{r closeRsession, echo=FALSE,  echo=FALSE} 
opal.logout(o)
```