---
title: "Cardiovascular diseases"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `cvd_all`
* Variable label: `History of all Cardiovascular diseases`
* Variable description: `The participant has been diagnosed by one or more of the following conditions: angina, stroke, myocardial infarction, heart attack, coronary heart disease, congestive heart failure, heart murmur, valve disease, cerebral vascular disease`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | No, the participant has not been diagnosed of any of these conditions
1        | Yes, the participant has been diagnosed by any of these conditions

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "History of all Cardiovascular diseases"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process



## Australia


### Wave 1


#### Study-specific variable description

| **Name** | `mi_ha` |`stroke`|
|-|-|-|
| **Label** | `Myocardial infarction or heart attack` |`Stroke`|
| **Table name**  | `mi_ha` |`stroke`|
| **Categories** | `0 = No`<br/>`1 = Yes` | `0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)`|
| **Description** |  |  |

```{r assign w1, echo=F}

load(paste0(datafolder,"w1/mi_ha.RData"))
ALSA_w1 <- tibble(id=mi_ha$id)
ALSA_w1$mi_ha <- mi_ha$mi_ha
rm(mi_ha)
load(paste0(datafolder,"w1/stroke.RData"))
ALSA_w1$stroke <- stroke$stroke
rm(stroke)

```

```{r local w1, echo=F}

vbl <- ALSA_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w1, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w1$stroke
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w1, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd_all` from the study-specific variable it has to be recoded as follows:

* `all 0 into 0`
* `some 1 into 1`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
ALSA_ds_w1 <- tibble(id=ALSA_w1$id)
ALSA_ds_w1$cvd_all <- rep(999,length(ALSA_w1$id))
ALSA_ds_w1$cvd_all[which(ALSA_w1$mi_ha==0 & ALSA_w1$stroke==0)] <- 0
ALSA_ds_w1$cvd_all[which(ALSA_w1$mi_ha==1 | ALSA_w1$stroke==1)] <- 1

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- ALSA_ds_w1$cvd_all
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w1, aes(x=factor(cvd_all))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}

AfterH <- table(ALSA_ds_w1$cvd_all, useNA = "ifany")
X <- c(
  sum(ALSA_w1$mi_ha==0 & ALSA_w1$stroke==0,na.rm=T),
  sum(ALSA_w1$mi_ha==1 | ALSA_w1$stroke==1,na.rm=T)
)
BeforeH <- c(X[1:2])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1")
kable(C)

```



### Wave 2

Not found.




### Wave 3


#### Study-specific variable description

| **Name** | `mi_ha` |`stroke`|
|-|-|-|
| **Label** | `Myocardial infarction or heart attack` |`Stroke`|
| **Table name**  | `mi_ha` |`stroke`|
| **Categories** | `0 = No`<br/>`1 = Yes` | `0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)`|
| **Missings** |`999 = Missing`|`999 = Missing`|
| **Description** |  |  |

```{r assign w3, echo=F}

load(paste0(datafolder,"w3/mi_ha.RData"))
ALSA_w3 <- tibble(id=mi_ha$id)
ALSA_w3$mi_ha <- mi_ha$mi_ha
rm(mi_ha)
load(paste0(datafolder,"w3/stroke.RData"))
ALSA_w3$stroke <- stroke$stroke
rm(stroke)

```

```{r local w3, echo=F}

vbl <- ALSA_w3$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(ALSA_w3)[2])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ALSA_w3, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w3$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(ALSA_w3)[3])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ALSA_w3, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd_all` from the study-specific variable it has to be recoded as follows:

* `all 0 into 0`
* `some 1 into 1`
* `999 into 999`

**R script:**

```{r harmo w3}

# Categorical variable harmonization
ALSA_ds_w3 <- tibble(id=ALSA_w3$id)
ALSA_ds_w3$cvd_all <- rep(999,length(ALSA_w3$id))
ALSA_ds_w3$cvd_all[which(ALSA_w3$mi_ha==0 & ALSA_w3$stroke==0)] <- 0
ALSA_ds_w3$cvd_all[which(ALSA_w3$mi_ha==1 | ALSA_w3$stroke==1)] <- 1

```


#### Statistics of the new harmonized variable

```{r descript w3, echo=F}

vbl <- ALSA_ds_w3$cvd_all
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w3, aes(x=factor(cvd_all))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w3, echo=F}

AfterH <- table(ALSA_ds_w3$cvd_all, useNA = "ifany")
X <- c(
  sum(ALSA_w3$mi_ha==0 & ALSA_w3$stroke==0,na.rm=T),
  sum(ALSA_w3$mi_ha==1 | ALSA_w3$stroke==1,na.rm=T)
)
BeforeH <- c(X[2],length(ALSA_w3$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("some 1->1","999->999")
kable(C)

```


### Wave 4

Not found.

### Wave 5

Not found.



### Wave 6


#### Study-specific variable description

| **Name** | `mi_ha` |`stroke`|`h_angina`|
|-|-|-|-|
| **Label** | `Myocardial infarction or heart attack` |`Stroke`|`History of angina`|
| **Table name**  | `mi_ha` |`stroke`|`h_angina`|
| **Categories** | `0 = No`<br/>`1 = Yes` | `0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)`|`0 = no history of angina`<br/>`1 = history of angina`|
| **Missings** |`999 = Missing`|`999 = Missing`|`999 = Missing`|
| **Description** |  |  |  |

```{r assign w6, echo=F}

load(paste0(datafolder,"w6/mi_ha.RData"))
ALSA_w6 <- tibble(id=mi_ha$id)
ALSA_w6$mi_ha <- mi_ha$mi_ha
rm(mi_ha)
load(paste0(datafolder,"w6/stroke.RData"))
ALSA_w6$stroke <- stroke$stroke
rm(stroke)
load(paste0(datafolder,"w6/h_angina.RData"))
ALSA_w6$h_angina <- h_angina$h_angina
rm(h_angina)

```

```{r local w6, echo=F}

vbl <- ALSA_w6$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(ALSA_w6)[2])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ALSA_w6, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w6$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(ALSA_w6)[3])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ALSA_w6, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w6$h_angina
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(ALSA_w6)[4])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ALSA_w6, aes(x=factor(h_angina))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd_all` from the study-specific variable it has to be recoded as follows:

* `all 0 into 0`
* `some 1 into 1`
* `999 into 999`

**R script:**

```{r harmo w6}

# Categorical variable harmonization
ALSA_ds_w6 <- tibble(id=ALSA_w6$id)
ALSA_ds_w6$cvd_all <- rep(999,length(ALSA_w6$id))
ALSA_ds_w6$cvd_all[which(ALSA_w6$mi_ha==0 & ALSA_w6$stroke==0 & ALSA_w6$h_angina==0)] <- 0
ALSA_ds_w6$cvd_all[which(ALSA_w6$mi_ha==1 | ALSA_w6$stroke==1 | ALSA_w6$h_angina==1)] <- 1

```


#### Statistics of the new harmonized variable

```{r descript w6, echo=F}

vbl <- ALSA_ds_w6$cvd_all
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w6, aes(x=factor(cvd_all))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w6, echo=F}

AfterH <- table(ALSA_ds_w6$cvd_all, useNA = "ifany")
X <- c(
  sum(ALSA_w6$mi_ha==0 & ALSA_w6$stroke==0 & ALSA_w6$h_angina==0,na.rm=T),
  sum(ALSA_w6$mi_ha==1 | ALSA_w6$stroke==1 | ALSA_w6$h_angina==1,na.rm=T)
)
BeforeH <- c(X[2],length(ALSA_w6$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("some 1->1","999->999")
kable(C)

```



### Wave 7


Not found.



### Wave 8

Not found.



### Wave 9

Not found.


### Wave 10

Not found.



### Wave 11


#### Study-specific variable description

| **Name** | `mi_ha` |`stroke`|`h_angina`|
|-|-|-|-|
| **Label** | `Myocardial infarction or heart attack` |`Stroke`|`History of angina`|
| **Table name**  | `mi_ha` |`stroke`|`h_angina`|
| **Categories** | `0 = No`<br/>`1 = Yes` | `0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)`|`0 = no history of angina`<br/>`1 = history of angina`|
| **Missings** |`999 = Missing`|`999 = Missing`|`999 = Missing`|
| **Description** |  |  |  |

```{r assign w11, echo=F}

load(paste0(datafolder,"w11/mi_ha.RData"))
ALSA_w11 <- tibble(id=mi_ha$id)
ALSA_w11$mi_ha <- mi_ha$mi_ha
rm(mi_ha)
load(paste0(datafolder,"w11/stroke.RData"))
ALSA_w11$stroke <- stroke$stroke
rm(stroke)
load(paste0(datafolder,"w11/h_angina.RData"))
ALSA_w11$h_angina <- h_angina$h_angina
rm(h_angina)

```

```{r local w11, echo=F}

vbl <- ALSA_w11$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(ALSA_w11)[2])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ALSA_w11, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w11$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(ALSA_w11)[3])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ALSA_w11, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w11$h_angina
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(ALSA_w11)[4])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ALSA_w11, aes(x=factor(h_angina))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd_all` from the study-specific variable it has to be recoded as follows:

* `all 0 into 0`
* `some 1 into 1`
* `999 into 999`

**R script:**

```{r harmo w11}

# Categorical variable harmonization
ALSA_ds_w11 <- tibble(id=ALSA_w11$id)
ALSA_ds_w11$cvd_all <- rep(999,length(ALSA_w11$id))
ALSA_ds_w11$cvd_all[which(ALSA_w11$mi_ha==0 & ALSA_w11$stroke==0 & ALSA_w11$h_angina==0)] <- 0
ALSA_ds_w11$cvd_all[which(ALSA_w11$mi_ha==1 | ALSA_w11$stroke==1 | ALSA_w11$h_angina==1)] <- 1

```


#### Statistics of the new harmonized variable

```{r descript w11, echo=F}

vbl <- ALSA_ds_w11$cvd_all
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w11, aes(x=factor(cvd_all))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w11, echo=F}

AfterH <- table(ALSA_ds_w11$cvd_all, useNA = "ifany")
X <- c(
  sum(ALSA_w11$mi_ha==0 & ALSA_w11$stroke==0 & ALSA_w11$h_angina==0,na.rm=T),
  sum(ALSA_w11$mi_ha==1 | ALSA_w11$stroke==1 | ALSA_w11$h_angina==1,na.rm=T)
)
BeforeH <- c(X[1:2],length(ALSA_w11$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","999->999")
kable(C)

```



### Wave 12


#### Study-specific variable description

| **Name** | `mi_ha` |`stroke`|`h_angina`|
|-|-|-|-|
| **Label** | `Myocardial infarction or heart attack` |`Stroke`|`History of angina`|
| **Table name**  | `mi_ha` |`stroke`|`h_angina`|
| **Categories** | `0 = No`<br/>`1 = Yes` | `0 = NOT A stroke (cerebral vascular disease)`<br/>`1 = A stroke (cerebral vascular disease)`|`0 = no history of angina`<br/>`1 = history of angina`|
| **Missings** |`999 = Missing`|  |`999 = Missing`|
| **Description** |  |  |  |

```{r assign w12, echo=F}

load(paste0(datafolder,"w12/mi_ha.RData"))
ALSA_w12 <- tibble(id=mi_ha$id)
ALSA_w12$mi_ha <- mi_ha$mi_ha
rm(mi_ha)
load(paste0(datafolder,"w12/stroke.RData"))
ALSA_w12$stroke <- stroke$stroke
rm(stroke)
load(paste0(datafolder,"w12/h_angina.RData"))
ALSA_w12$h_angina <- h_angina$h_angina
rm(h_angina)

```

```{r local w12, echo=F}

vbl <- ALSA_w12$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(ALSA_w12)[2])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ALSA_w12, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w12$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(ALSA_w12)[3])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ALSA_w12, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w12$h_angina
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(ALSA_w12)[4])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ALSA_w12, aes(x=factor(h_angina))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cvd_all` from the study-specific variable it has to be recoded as follows:

* `all 0 into 0`
* `some 1 into 1`
* `999 into 999`

**R script:**

```{r harmo w12}

# Categorical variable harmonization
ALSA_ds_w12 <- tibble(id=ALSA_w12$id)
ALSA_ds_w12$cvd_all <- rep(999,length(ALSA_w12$id))
ALSA_ds_w12$cvd_all[which(ALSA_w12$mi_ha==0 & ALSA_w12$stroke==0 & ALSA_w12$h_angina==0)] <- 0
ALSA_ds_w12$cvd_all[which(ALSA_w12$mi_ha==1 | ALSA_w12$stroke==1 | ALSA_w12$h_angina==1)] <- 1

```


#### Statistics of the new harmonized variable

```{r descript w12, echo=F}

vbl <- ALSA_ds_w12$cvd_all
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w12, aes(x=factor(cvd_all))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w12, echo=F}

AfterH <- table(ALSA_ds_w12$cvd_all, useNA = "ifany")
X <- c(
  sum(ALSA_w12$mi_ha==0 & ALSA_w12$stroke==0 & ALSA_w12$h_angina==0,na.rm=T),
  sum(ALSA_w12$mi_ha==1 | ALSA_w12$stroke==1 | ALSA_w12$h_angina==1,na.rm=T)
)
BeforeH <- c(X[1:2],length(ALSA_w12$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","999->999")
kable(C)

```


### Wave 13

Not found.


<!--
```{r summary, include=F, eval=F, echo=F}
kable(ALSA_ds[ALSA_ds$id %in% strange_id,], align = 'c', caption = 'Individuals with discrepancies')
```
-->

## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.

**R script:**

```{r summ}
ALSA_ds_w1$cvd_all <- labelled(ALSA_ds_w1$cvd_all, labels = cat_label)
label(ALSA_ds_w1$cvd_all) <- ds_label
ALSA_ds_w3$cvd_all <- labelled(ALSA_ds_w3$cvd_all, labels = cat_label)
label(ALSA_ds_w3$cvd_all) <- ds_label
ALSA_ds_w6$cvd_all <- labelled(ALSA_ds_w6$cvd_all, labels = cat_label)
label(ALSA_ds_w6$cvd_all) <- ds_label
ALSA_ds_w11$cvd_all <- labelled(ALSA_ds_w11$cvd_all, labels = cat_label)
label(ALSA_ds_w11$cvd_all) <- ds_label
ALSA_ds_w12$cvd_all <- labelled(ALSA_ds_w12$cvd_all, labels = cat_label)
label(ALSA_ds_w12$cvd_all) <- ds_label

ALSA_m_ds_w1 <- ALSA_ds_w1
ALSA_m_ds_w1$cvd_all <- car::recode(ALSA_m_ds_w1$cvd_all, "miss_values_vector=NA")
ALSA_m_ds_w3 <- ALSA_ds_w3
ALSA_m_ds_w3$cvd_all <- car::recode(ALSA_m_ds_w3$cvd_all, "miss_values_vector=NA")
ALSA_m_ds_w6 <- ALSA_ds_w6
ALSA_m_ds_w6$cvd_all <- car::recode(ALSA_m_ds_w6$cvd_all, "miss_values_vector=NA")
ALSA_m_ds_w11 <- ALSA_ds_w11
ALSA_m_ds_w11$cvd_all <- car::recode(ALSA_m_ds_w11$cvd_all, "miss_values_vector=NA")
ALSA_m_ds_w12 <- ALSA_ds_w12
ALSA_m_ds_w12$cvd_all <- car::recode(ALSA_m_ds_w12$cvd_all, "miss_values_vector=NA")

tt <-    frq(ALSA_ds_w1$cvd_all)[[1]][,c(1:2,4)]
tt[4] <- frq(ALSA_ds_w3$cvd_all)[[1]][,c(4)]
tt[5] <- frq(ALSA_ds_w6$cvd_all)[[1]][,c(4)]
tt[6] <- frq(ALSA_ds_w11$cvd_all)[[1]][,c(4)]
tt[7] <- frq(ALSA_ds_w12$cvd_all)[[1]][,c(4)]
tt[13,] <- c("n", "sample size", 
             length(ALSA_ds_w1$cvd_all), length(ALSA_ds_w3$cvd_all), length(ALSA_ds_w6$cvd_all), 
             length(ALSA_ds_w11$cvd_all), length(ALSA_ds_w12$cvd_all)
             )
names(tt)<-c("val", "label", "w1", "w3", "w6", "w11", "w12")
kable(tt)

dbb <- merge(ALSA_m_ds_w1[,c("id","cvd_all")], ALSA_m_ds_w3[,c("id","cvd_all")], by="id", suffixes = c(".w1",".w3"), all=T)
dbb <- merge(dbb, ALSA_m_ds_w6[,c("id","cvd_all")], by="id", all=T)
dbb <- merge(dbb, ALSA_m_ds_w11[,c("id","cvd_all")], by="id", suffixes = c(".w6",".w11"), all=T)
dbb <- merge(dbb, ALSA_m_ds_w12[,c("id","cvd_all")], by="id", all=T)
names(dbb) <- c("id", "w1", "w3", "w6", "w11", "w12")
v.dbb <- paste(dbb[,2],dbb[,3],dbb[,4],dbb[,5],dbb[,6],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])
```



# Quality estimation

The harmonized variable is about angina, myocardial infarction and stroke. The harmonized variable has been built from the single disease variables. 



<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.ALSA <- list(w1 = ALSA_ds_w1, w3 = ALSA_ds_w3, w6 = ALSA_ds_w6, w11 = ALSA_ds_w11, w12 = ALSA_ds_w12)

for(index in seq_along(l.ALSA)){
  cvd_all <- l.ALSA[[index]]
  save(cvd_all, file = paste0(datafolder,names(l.ALSA)[index],"/cvd_all.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





