---
title: "Cancer"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `cancer`
* Variable label: `Any malignancy (C00-D48) / information about past or current neoplasm (benign, in situ, malignant)`
* Variable description: `cancer diagnosis since the last interview`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | no cancer
1        | cancer

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Short name: `cancer_age`
* Variable label: `Age of cancer diagnosis`
* Variable description: `Age of each episode of cancer`
* Domain: `Diseases`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "Any malignancy (C00-D48) / information about past or current neoplasm (benign, in situ, malignant)"
ds_label_age <- "Age of cancer diagnosis"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
cont_label <- cat_label[3:11]
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process



## Australia


### Wave 1


#### Study-specific variable description

| **Name** | `CANCER` |`WHENTOLD`|`ybirth`|
|-|-|-|-|
| **Label** | `Cancer` |`Year cancer diagnosed`|`Year of birth`|
| **Table name**  | `ALSA-Wave1` | `ALSA-Wave1` |`ybirth`|
| **Categories** | `2 = No`<br/>`1 = Yes` | `continuous` | `continuous` |
| **Missings** | `9`<br/>`NA` | `9999`<br/>`NA`  |  |
| **Description** |  |  |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'ALSA_w1','ALSA.ALSA-Wave1',variables=list('CANCER','WHENTOLD'), missings = T)
ALSA_w1 <- opal.execute(o,'ALSA_w1')
load(paste0(datafolder,"w1/ybirth.RData"))
ALSA_w1 <- left_join(ALSA_w1,ybirth, by="id")

```

```{r local w1, echo=F}

vbl <- ALSA_w1$CANCER
kable(Categorical_summary(vbl, missing_values = c(9))[3], caption = names(ALSA_w1)[2])
kable(Categorical_summary(vbl, missing_values = c(9))[1], caption = "Category")
ggplot(ALSA_w1, aes(x=factor(CANCER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w1$WHENTOLD
kable(Continuous_summary(var = vbl, missing_values = c(9999))[3], caption = names(ALSA_w1)[3])
pander(Continuous_summary(vbl, missing_values = c(9999))$summary, caption = "Summary")
ggplot(ALSA_w1, aes(WHENTOLD)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1920,1995)

vbl <- ALSA_w1$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(ALSA_w1)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_w1, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1885,1930)

```


#### Harmonisation algorithm

To compute `cancer` from the study-specific variable it has to be recoded as follows:

* `change 2 into 0`
* `keep up 1 into 1`
* `9,NA into 999`

To compute `cancer_age` from the study-specific variable it has to be recoded as follows:

* `if cancer == 1, cancer_age = WHENTOLD - ybirth`
* `if cancer == 0, cancer_age = 996`
* `9999 into 999`
* `otherwise into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
ALSA_ds_w1 <- tibble(id=ALSA_w1$id)
ALSA_ds_w1$cancer <- car::recode(ALSA_w1$CANCER, "2=0;9=999;NA = 999")

# Continuous variable harmonization
cancer_age <- ALSA_w1$WHENTOLD[which(ALSA_ds_w1$cancer == 1)]-ALSA_w1$ybirth[which(ALSA_ds_w1$cancer == 1)]
ALSA_ds_w1$cancer_age <- car::recode(ALSA_ds_w1$cancer, "0 = 996; 1 = cancer_age")
ALSA_ds_w1$cancer_age[which(ALSA_w1$WHENTOLD==9999)] <- 999
ALSA_ds_w1$cancer_age <- car::recode(ALSA_ds_w1$cancer_age,"NA=999")

ALSA_ds <- tibble(id=ALSA_w1$id)
ALSA_ds$year_wave <- 1992
ALSA_ds$past_cancer <- ALSA_ds_w1$cancer
ALSA_ds$past_year <- rep(999,length(ALSA_ds_w1$id))
ALSA_ds$past_year[which(ALSA_ds_w1$cancer == 1)] <- car::recode(ALSA_w1$WHENTOLD[which(ALSA_ds_w1$cancer == 1)],"9999=999;NA=999")
row.names(ALSA_ds) <- ALSA_ds$id

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- ALSA_ds_w1$cancer
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w1, aes(x=factor(cancer))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ALSA_ds_w1$cancer_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w1, aes(cancer_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(5,95)

```


#### Validation

```{r crosstabulation w1, echo=F}

continuous <- c(sum(ALSA_ds_w1$cancer_age==996,na.rm=T),sum(ALSA_ds_w1$cancer_age!=996,na.rm=T))
X <- table(ALSA_ds_w1$cancer, useNA = "ifany")
dichotomous <- c(X[1],sum(X[2:3],na.rm=T))
C <- rbind(continuous,dichotomous)
colnames(C) <- c("0<-->996","1<-->(possibly missing) age of diagnostic")
kable(C,caption = "Continuous vs Dichotomous")

```



### Wave 2

Not found.




### Wave 3

Not found.


### Wave 4

Not found.

### Wave 5

Not found.



### Wave 6


#### Study-specific variable description

| **Name** | `CANCEW6` |`WHENTOW6`|`ybirth`|
|-|-|-|-|
| **Label** | `doctor said you have cancer malignancy or tumour` |`year told had cancer`|`Year of birth`|
| **Table name**  | `ALSA-Wave6` | `ALSA-Wave6` |`ybirth`|
| **Categories** | `2 = no`<br/>`1 = yes` |`continuous`|`continuous`|
| **Missings** | `0 = no answer`<br/>`NA` |`NA`|  |
| **Description** |  |  |  |

```{r assign w6, echo=F}

opal.assign.table.tibble(o, 'ALSA_w6','ALSA.ALSA-Wave6',variables=list('CANCEW6','WHENTOW6'), missings = T)
ALSA_w6 <- opal.execute(o,'ALSA_w6')
ALSA_w6$WHENTOW6 <- as.numeric(ALSA_w6$WHENTOW6)
load(paste0(datafolder,"w6/ybirth.RData"))
ALSA_w6 <- left_join(ALSA_w6,ybirth, by="id")

```

```{r local w6, echo=F}

vbl <- ALSA_w6$CANCEW6
kable(Categorical_summary(vbl, missing_values = c(0))[3], caption = names(ALSA_w6)[2])
kable(Categorical_summary(vbl, missing_values = c(0))[1], caption = "Category")
ggplot(ALSA_w6, aes(x=factor(CANCEW6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w6$WHENTOW6
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(ALSA_w6)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_w6, aes(WHENTOW6)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1935,2005)

vbl <- ALSA_w6$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(ALSA_w6)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_w6, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1895,1930)

```


#### Harmonisation algorithm

To compute `cancer` from the study-specific variable it has to be recoded as follows:

* `change 2 into 0`
* `keep up 1, ensuring it does not correspond to previous waves, into 1`
* `0 into 995`
* `otherwise into 999`

To compute `cancer_age` from the study-specific variable it has to be recoded as follows:

* `if cancer == 1, cancer_age = WHENTOW6 - ybirth`
* `if cancer == 0, cancer_age = 996`
* `otherwise into 999`

**R script:**

```{r harmo w6}

ALSA_w6 <- left_join(ALSA_w6,ALSA_w1, by="id",suffix=c("","_w1"))

ALSA_ds_w6 <- tibble(id=ALSA_w6$id)
ALSA_ds_w6$cancer <- rep(999,length(ALSA_w6$id))
ALSA_ds_w6$cancer[which(ALSA_w6$CANCEW6==2)] <- 0
ALSA_ds_w6$cancer[which(ALSA_w6$CANCEW6==0)] <- 995
# Individuals having cancer since wave 1, so their year of diagnostic is at least 1992 or missing but until later previous wave interviewed they had no cancer.
ALSA_ds_w6$cancer[which(ALSA_w6$CANCEW6==1 & (ALSA_w6$CANCER==2 | ALSA_w6$WHENTOW6>=1992 & (ALSA_w6$WHENTOW6>ALSA_w6$WHENTOLD | is.na(ALSA_w6$WHENTOLD))))] <- 1

# Continuous variable harmonization
ALSA_ds_w6$cancer_age <- rep(999,length(ALSA_w6$id))
ALSA_ds_w6$cancer_age[which(ALSA_ds_w6$cancer==0)] <- 996
ALSA_ds_w6$cancer_age[which(ALSA_ds_w6$cancer==1 & ALSA_w6$WHENTOW6>=1992 & (ALSA_w6$WHENTOW6>ALSA_w6$WHENTOLD | is.na(ALSA_w6$WHENTOLD)))] <- ALSA_w6$WHENTOW6[which(ALSA_ds_w6$cancer==1 & ALSA_w6$WHENTOW6>=1992 & (ALSA_w6$WHENTOW6>ALSA_w6$WHENTOLD | is.na(ALSA_w6$WHENTOLD)))] - ALSA_w6$ybirth[which(ALSA_ds_w6$cancer==1 & ALSA_w6$WHENTOW6>=1992 & (ALSA_w6$WHENTOW6>ALSA_w6$WHENTOLD | is.na(ALSA_w6$WHENTOLD)))]
ALSA_ds_w6$cancer_age <- car::recode(ALSA_ds_w6$cancer_age,"NA=999")


ALSA_ds[ALSA_ds_w6$id[which(ALSA_ds_w6$cancer!=999)],"past_cancer"] <- ALSA_ds_w6$cancer[which(ALSA_ds_w6$cancer!=999)]
ALSA_ds[ALSA_ds_w6$id[which(ALSA_ds_w6$cancer==1)],"past_year"] <- car::recode(ALSA_w6$WHENTOW6[which(ALSA_ds_w6$cancer == 1)],"NA=999")
ALSA_ds[ALSA_ds_w6$id[which(ALSA_ds_w6$cancer!=999)],"year_wave"] <- 2000

```

<!--
ALTERNATIVE INSTRUCTIONS:
#ALSA_w6 <- left_join(ALSA_w6,ALSA_ds, by="id")
#The next two lines should be essentially the same.
#ALSA_ds_w6$cancer[which(ALSA_w6$CANCEW6==1 & ((ALSA_w6$WHENTOW6>=ALSA_w6$year_wave & ALSA_w6$WHENTOW6>ALSA_w6$past_year) | ALSA_w6$past_cancer==0))] <- 1

-->


#### Statistics of the new harmonized variable

```{r descript w6, echo=F}

vbl <- ALSA_ds_w6$cancer
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w6, aes(x=factor(cancer))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ALSA_ds_w6$cancer_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w6, aes(cancer_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(60,100)

```


#### Validation

```{r crosstabulation w6, echo=F, results='asis'}

AfterH <- table(ALSA_ds_w6$cancer)
X <- c(table(ALSA_w6$CANCEW6, useNA = "ifany")[c(3,1)],sum(ALSA_w6$CANCEW6==1 & (ALSA_w6$CANCER==2 | ALSA_w6$WHENTOW6>=1992 & (ALSA_w6$WHENTOW6>ALSA_w6$WHENTOLD | is.na(ALSA_w6$WHENTOLD))),na.rm=T))
BeforeH <- c(X[c(1,3,2)],length(ALSA_w6$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","0->995","NA->999")
kable(C)

cat("Individuals which in the first wave told they had no cancer and in the sixth wave told they had cancer and give year of diagnosis previous to the year of interview of first wave. We harmonize them as having cancer but keep missing ages of diagnosis.")
kable(ALSA_w6[which(ALSA_w6$CANCER==2 & (ALSA_w6$WHENTOW6<1992 | ALSA_w6$WHENTOW6<=ALSA_w6$WHENTOLD)),c(1,5,6,2,3,4)], align = 'c')

```



### Wave 7

#### Study-specific variable description


| **Name** | `cancew7` |`whentow7`|`ybirth`|
|-|-|-|-|
| **Label** | `Did the doctor say you had cancer, malignancy or tumour` |`year told you had cancer`|`Year of birth`|
| **Table name**  | `ALSA-Wave7` | `ALSA-Wave7` |`ybirth`|
| **Categories** | `2 = No`<br/>`1 = Yes` |`continuous`|`continuous`|
| **Missings** | `0 = Not Answered`<br/>`NA` |`NA`|  |
| **Description** |  |  |  |

```{r assign w7, echo=F}

opal.assign.table.tibble(o, 'ALSA_w7','ALSA.ALSA-Wave7',variables=list('cancew7','whentow7'), missings = T)
ALSA_w7 <- opal.execute(o,'ALSA_w7')
ALSA_w7$whentow7 <- as.numeric(ALSA_w7$whentow7)
load(paste0(datafolder,"w7/ybirth.RData"))
ALSA_w7 <- left_join(ALSA_w7,ybirth, by="id")

```

```{r local w7, echo=F}

vbl <- ALSA_w7$cancew7
kable(Categorical_summary(vbl, missing_values = c(0))[3], caption = names(ALSA_w7)[2])
kable(Categorical_summary(vbl, missing_values = c(0))[1], caption = "Category")
ggplot(ALSA_w7, aes(x=factor(cancew7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w7$whentow7
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(ALSA_w7)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_w7, aes(whentow7)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1940,2005)

vbl <- ALSA_w7$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(ALSA_w7)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_w7, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1885,1930)

```


#### Harmonisation algorithm

To compute `cancer` from the study-specific variable it has to be recoded as follows:

* `change 2 into 0`
* `keep up 1, ensuring it does not correspond to previous waves, into 1`
* `0 into 995`
* `otherwise into 999`

To compute `cancer_age` from the study-specific variable it has to be recoded as follows:

* `if cancer == 1, cancer_age = whentow7 - ybirth`
* `if cancer == 0, cancer_age = 996`
* `otherwise into 999`

**R script:**

```{r harmo w7}

ALSA_w7 <- left_join(ALSA_w7,ALSA_ds, by="id")

ALSA_ds_w7 <- tibble(id=ALSA_w7$id)
ALSA_ds_w7$cancer <- rep(999,length(ALSA_w7$id))
ALSA_ds_w7$cancer[which(ALSA_w7$cancew7==2)] <- 0
ALSA_ds_w7$cancer[which(ALSA_w7$cancew7==0)] <- 995
# Individuals having cancer since wave 6, so their year of diagnostic is at least 2000 or missing but until later previous wave interviewed they had no cancer.
ALSA_ds_w7$cancer[which(ALSA_w7$cancew7==1 & ((ALSA_w7$whentow7>=ALSA_w7$year_wave & ALSA_w7$whentow7>ALSA_w7$past_year) | ALSA_w7$past_cancer==0))] <- 1

# Continuous variable harmonization
ALSA_ds_w7$cancer_age <- rep(999,length(ALSA_w7$id))
ALSA_ds_w7$cancer_age[which(ALSA_ds_w7$cancer==0)] <- 996
ALSA_ds_w7$cancer_age[which(ALSA_ds_w7$cancer==1 & ALSA_w7$whentow7>=ALSA_w7$year_wave & ALSA_w7$whentow7>ALSA_w7$past_year)] <- ALSA_w7$whentow7[which(ALSA_ds_w7$cancer==1 & ALSA_w7$whentow7>=ALSA_w7$year_wave & ALSA_w7$whentow7>ALSA_w7$past_year)] - ALSA_w7$ybirth[which(ALSA_ds_w7$cancer==1 & ALSA_w7$whentow7>=ALSA_w7$year_wave & ALSA_w7$whentow7>ALSA_w7$past_year)]
ALSA_ds_w7$cancer_age <- car::recode(ALSA_ds_w7$cancer_age,"NA=999")

ALSA_ds[ALSA_ds_w7$id[which(ALSA_ds_w7$cancer!=999)],"past_cancer"] <- ALSA_ds_w7$cancer[which(ALSA_ds_w7$cancer!=999)]
ALSA_ds[ALSA_ds_w7$id[which(ALSA_ds_w7$cancer==1)],"past_year"] <- car::recode(ALSA_w7$whentow7[which(ALSA_ds_w7$cancer == 1)],"NA=999")
ALSA_ds[ALSA_ds_w7$id[which(ALSA_ds_w7$cancer!=999)],"year_wave"] <- 2003

```


#### Statistics of the new harmonized variable

```{r descript w7, echo=F}

vbl <- ALSA_ds_w7$cancer
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w7, aes(x=factor(cancer))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ALSA_ds_w7$cancer_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w7, aes(cancer_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(70,95)

```


#### Validation

```{r crosstabulation w7, echo=F, results='asis'}

AfterH <- table(ALSA_ds_w7$cancer)
X <- c(table(ALSA_w7$cancew7, useNA = "ifany")[c(3,1)],sum(ALSA_w7$cancew7==1 & ((ALSA_w7$whentow7>=ALSA_w7$year_wave & ALSA_w7$whentow7>ALSA_w7$past_year) | ALSA_w7$past_cancer==0),na.rm=T))
BeforeH <- c(X[c(1,3,2)],length(ALSA_w7$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","0->995","NA->999")
kable(C)

cat("Individuals which in the previous interview told they had no cancer and in this wave told they had cancer and give year of diagnosis previous to the past interview. We harmonize them as having cancer but keep missing ages of diagnosis.")
kable(ALSA_w7[which(ALSA_w7$cancew7==1 & ALSA_w7$past_cancer==0 & (ALSA_w7$whentow7<ALSA_w7$year_wave | ALSA_w7$whentow7<=ALSA_w7$past_year)),], align = 'c')

```


### Wave 8

Not found.



### Wave 9


#### Study-specific variable description


| **Name** | `CANCEW9` |`WHENTOW9`|`ybirth`|
|-|-|-|-|
| **Label** | `Did the doctor say you had cancer, malignancy or tumour` |`year told you had cancer`|`Year of birth`|
| **Table name**  | `ALSA-Wave9` | `ALSA-Wave7` |`ybirth`|
| **Categories** | `2 = No`<br/>`1 = Yes` |`continuous`|`continuous`|
| **Missings** | `0 = Not Answered`<br/>`NA` |`NA`|  |
| **Description** |  |  |  |

```{r assign w9, echo=F}

opal.assign.table.tibble(o, 'ALSA_w9','ALSA.ALSA-Wave9',variables=list('CANCEW9','WHENTOW9'), missings = T)
ALSA_w9 <- opal.execute(o,'ALSA_w9')
ALSA_w9$WHENTOW9 <- as.numeric(ALSA_w9$WHENTOW9)
# We remove two id's which are not coincident with any other in the other waves of ALSA and whose data is empty.
ALSA_w9 <- ALSA_w9[!ALSA_w9$id %in% c("3515","43202"),]
load(paste0(datafolder,"w9/ybirth.RData"))
ALSA_w9 <- left_join(ALSA_w9,ybirth, by="id")

```

```{r local w9, echo=F}

vbl <- ALSA_w9$CANCEW9
kable(Categorical_summary(vbl, missing_values = c(0))[3], caption = names(ALSA_w9)[2])
kable(Categorical_summary(vbl, missing_values = c(0))[1], caption = "Category")
ggplot(ALSA_w9, aes(x=factor(CANCEW9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w9$WHENTOW9
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(ALSA_w9)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_w9, aes(WHENTOW9)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1940,2005)

vbl <- ALSA_w9$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(ALSA_w9)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_w9, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1885,1930)

```


#### Harmonisation algorithm

To compute `cancer` from the study-specific variable it has to be recoded as follows:

* `change 2 into 0`
* `keep up 1, ensuring it does not correspond to previous waves, into 1`
* `0 into 995`
* `otherwise into 999`

To compute `cancer_age` from the study-specific variable it has to be recoded as follows:

* `if cancer == 1, cancer_age = WHENTOW9 - ybirth`
* `if cancer == 0, cancer_age = 996`
* `otherwise into 999`

**R script:**

```{r harmo w9}

ALSA_w9 <- left_join(ALSA_w9,ALSA_ds, by="id")

ALSA_ds_w9 <- tibble(id=ALSA_w9$id)
ALSA_ds_w9$cancer <- rep(999,length(ALSA_w9$id))
ALSA_ds_w9$cancer[which(ALSA_w9$CANCEW9==2)] <- 0
ALSA_ds_w9$cancer[which(ALSA_w9$CANCEW9==0)] <- 995
# Individuals having cancer since wave 7, so their year of diagnostic is at least 2003 or missing but until later previous wave interviewed they had no cancer.
ALSA_ds_w9$cancer[which(ALSA_w9$CANCEW9==1 & ((ALSA_w9$WHENTOW9>=ALSA_w9$year_wave & ALSA_w9$WHENTOW9>ALSA_w9$past_year) | ALSA_w9$past_cancer==0))] <- 1

# Continuous variable harmonization
ALSA_ds_w9$cancer_age <- rep(999,length(ALSA_w9$id))
ALSA_ds_w9$cancer_age[which(ALSA_ds_w9$cancer==0)] <- 996
ALSA_ds_w9$cancer_age[which(ALSA_ds_w9$cancer==1 & ALSA_w9$WHENTOW9>=ALSA_w9$year_wave & ALSA_w9$WHENTOW9>ALSA_w9$past_year)] <- ALSA_w9$WHENTOW9[which(ALSA_ds_w9$cancer==1 & ALSA_w9$WHENTOW9>=ALSA_w9$year_wave & ALSA_w9$WHENTOW9>ALSA_w9$past_year)] - ALSA_w9$ybirth[which(ALSA_ds_w9$cancer==1 & ALSA_w9$WHENTOW9>=ALSA_w9$year_wave & ALSA_w9$WHENTOW9>ALSA_w9$past_year)]
ALSA_ds_w9$cancer_age <- car::recode(ALSA_ds_w9$cancer_age,"NA=999")

rm(ALSA_ds)
```


#### Statistics of the new harmonized variable

```{r descript w9, echo=F}

vbl <- ALSA_ds_w9$cancer
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w9, aes(x=factor(cancer))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ALSA_ds_w9$cancer_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w9, aes(cancer_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(70,95)

```


#### Validation

```{r crosstabulation w9, echo=F, results='asis'}

AfterH <- table(ALSA_ds_w9$cancer)
X <- c(table(ALSA_w9$CANCEW9, useNA = "ifany")[c(3,1)],sum(ALSA_w9$CANCEW9==1 & ((ALSA_w9$WHENTOW9>=ALSA_w9$year_wave & ALSA_w9$WHENTOW9>ALSA_w9$past_year) | ALSA_w9$past_cancer==0),na.rm=T))
BeforeH <- c(X[c(1,3,2)],length(ALSA_w7$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","0->995","NA->999")
kable(C)

cat("Individuals which in the previous interview told they had no cancer and in this wave told they had cancer and give year of diagnosis previous to the past interview. We harmonize them as having cancer but keep missing ages of diagnosis.")
kable(ALSA_w9[which(ALSA_w9$CANCEW9==1 & ALSA_w9$past_cancer==0 & (ALSA_w9$WHENTOW9<ALSA_w9$year_wave | ALSA_w9$WHENTOW9<=ALSA_w9$past_year)),], align = 'c')

```


### Wave 10

Not found.


### Wave 11

Not found.


### Wave 12

Not found.


### Wave 13

Not found.


<!--
```{r summary, include=F, eval=F, echo=F}
kable(ALSA_ds[ALSA_ds$id %in% strange_id,], align = 'c', caption = 'Individuals with discrepancies')
```
-->

## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.

**R script:**

```{r summ}
ALSA_ds_w1$cancer <- labelled(ALSA_ds_w1$cancer, labels = cat_label)
label(ALSA_ds_w1$cancer) <- ds_label
ALSA_ds_w1$cancer_age <- labelled(ALSA_ds_w1$cancer_age, labels = cont_label)
label(ALSA_ds_w1$cancer_age) <- ds_label_age
ALSA_ds_w6$cancer <- labelled(ALSA_ds_w6$cancer, labels = cat_label)
label(ALSA_ds_w6$cancer) <- ds_label
ALSA_ds_w6$cancer_age <- labelled(ALSA_ds_w6$cancer_age, labels = cont_label)
label(ALSA_ds_w6$cancer_age) <- ds_label_age
ALSA_ds_w7$cancer <- labelled(ALSA_ds_w7$cancer, labels = cat_label)
label(ALSA_ds_w7$cancer) <- ds_label
ALSA_ds_w7$cancer_age <- labelled(ALSA_ds_w7$cancer_age, labels = cont_label)
label(ALSA_ds_w7$cancer_age) <- ds_label_age
ALSA_ds_w9$cancer <- labelled(ALSA_ds_w9$cancer, labels = cat_label)
label(ALSA_ds_w9$cancer) <- ds_label
ALSA_ds_w9$cancer_age <- labelled(ALSA_ds_w9$cancer_age, labels = cont_label)
label(ALSA_ds_w9$cancer_age) <- ds_label_age

ALSA_m_ds_w1 <- ALSA_ds_w1
ALSA_m_ds_w1$cancer <- car::recode(ALSA_m_ds_w1$cancer, "miss_values_vector=NA")
ALSA_m_ds_w6 <- ALSA_ds_w6
ALSA_m_ds_w6$cancer <- car::recode(ALSA_m_ds_w6$cancer, "miss_values_vector=NA")
ALSA_m_ds_w7 <- ALSA_ds_w7
ALSA_m_ds_w7$cancer <- car::recode(ALSA_m_ds_w7$cancer, "miss_values_vector=NA")
ALSA_m_ds_w9 <- ALSA_ds_w9
ALSA_m_ds_w9$cancer <- car::recode(ALSA_m_ds_w9$cancer, "miss_values_vector=NA")

tt <-    frq(ALSA_ds_w1$cancer)[[1]][,c(1:2,4)]
tt[4] <- frq(ALSA_ds_w6$cancer)[[1]][,c(4)]
tt[5] <- frq(ALSA_ds_w7$cancer)[[1]][,c(4)]
tt[6] <- frq(ALSA_ds_w9$cancer)[[1]][,c(4)]
tt[13,] <- c("n", "sample size", 
             length(ALSA_ds_w1$cancer), length(ALSA_ds_w6$cancer), length(ALSA_ds_w7$cancer), 
             length(ALSA_ds_w9$cancer)
             )
names(tt)<-c("val", "label", "w1", "w6", "w7", "w9")
kable(tt)

dbb <- merge(ALSA_m_ds_w1[,c("id","cancer")], ALSA_m_ds_w6[,c("id","cancer")], by="id", suffixes = c(".w1",".w6"), all=T)
dbb <- merge(dbb, ALSA_m_ds_w7[,c("id","cancer")], by="id", all=T)
dbb <- merge(dbb, ALSA_m_ds_w9[,c("id","cancer")], by="id", suffixes = c(".w7",".w9"), all=T)
names(dbb) <- c("id", "w1", "w6", "w7", "w9")
v.dbb <- paste(dbb[,2],dbb[,3],dbb[,4],dbb[,5],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])
```



# Quality estimation

In wave 3 we cannot harmonize because there are no study-specific variable for general cancer and the variables `W1CDN53` (`LUNG CANCER`), `W1CDN54` (`GYNAECOLOGICAL CANCER`), `W1CDN55` (`BREAST CANCER`), `W1CDN56` (`COLON/RECTAL/BOWEL CANCER`), `W1CDN60` (`PROSTATE CANCER`), `W1CDN61` (`BLADDER CANCER`), `W1CDN62` (`ANOTHER CANCER`), `W3OTH62` (`OTHER TYPE OF CANCER`) arehave all data missing.


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.ALSA <- list(w1 = ALSA_ds_w1, w6 = ALSA_ds_w6, w7 = ALSA_ds_w7, w9 = ALSA_ds_w9)

for(index in seq_along(l.ALSA)){
  cancer <- l.ALSA[[index]]
  save(cancer, file = paste0(datafolder,names(l.ALSA)[index],"/cancer.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





