---
title: "Diabetes"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `h_diabetes`
* Variable label: `History of  Diabetes mellitus`
* Variable description: `History of diabetes or high blood sugar`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Not Diabetes or high blood sugar
1        | Diabetes or high blood sugar

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Short name: `h_diabetes_age`
* Variable label: `Age first diagnosed diabetes`
* Variable description: `The age first told had diabetes or high blood sugar diagnosis`
* Domain: `Diseases`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "History of diabetes"
ds_label_age <- "Age first diagnosed diabetes"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
cont_label <- cat_label[3:11]
datafolder <- "../RData/"
sing_idlist <- c("10162","13292","13321","15262","19001","21732","24102","24371","35861","4712","5392","7412","9121","9131","9172","9542","12192","12131","8532")
```
<!-- ########################################################## --> 



# Data process



## Australia


### Wave 1


#### Study-specific variable description

| **Name** | `DIABETE` |`WHENTLD`|`ybirth`|
|-|-|-|-|
| **Label** | `Diagnosed diabetes` |`Year diabetes diagnosed`|`Year of birth`|
| **Table name**  | `ALSA-Wave1` | `ALSA-Wave1` |`ybirth`|
| **Categories** | `1 = yes; 2 = no` | `continuous` | `continuous` |
| **Missings** | `9; NA` | `9999; NA` | `991 = CAPI/interviewer error; 992 = Impute; 993 = Disable to measure; 994 = Not attempt/not done; 995 = Does not answer; 996 = Not applicable; 997 = Refuse; 998 = Do not know; 999 = Missing` |
| **Description** |  |  |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'ALSA_w1','ALSA.ALSA-Wave1',variables=list('DIABETE','WHENTLD'), missings = T)
ALSA_w1 <- opal.execute(o,'ALSA_w1')
load(paste0(datafolder,"w1/ybirth.RData"))
ALSA_w1 <- left_join(ALSA_w1,ybirth, by="id")

```

```{r local w1, echo=F}

vbl <- ALSA_w1$DIABETE
kable(Categorical_summary(vbl, missing_values = c(9))[3], caption = names(ALSA_w1)[2])
kable(Categorical_summary(vbl, missing_values = c(9))[1], caption = "Category")
ggplot(ALSA_w1, aes(x=factor(DIABETE))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w1$WHENTLD
kable(Continuous_summary(var = vbl, missing_values = c(9999))[3], caption = names(ALSA_w1)[3])
pander(Continuous_summary(vbl, missing_values = c(9999))$summary, caption = "Summary")
ggplot(ALSA_w1, aes(WHENTLD)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1915,1995)

vbl <- ALSA_w1$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(ALSA_w1)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_w1, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1885,1930)

```


#### Harmonisation algorithm

To compute `h_diabetes` from the study-specific variable it has to be recoded as follows:

* `change 2 into 0`
* `keep up 1 into 1`
* `9, NA into 999`

To compute `h_diabetes_age` from the study-specific variable it has to be recoded as follows:

* `if h_diabetes == 1, h_diabetes_age = WHENTLD - ybirth`
* `if h_diabetes == 0, h_diabetes_age = 996`
* `WHENTLD == 9999 or h_diabetes == 999 into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
ALSA_ds_w1 <- tibble(id=ALSA_w1$id)
ALSA_ds_w1$h_diabetes <- car::recode(ALSA_w1$DIABETE, "2 = 0; 9 = 999; NA = 999")

ALSA_ds_w1$h_diabetes <- labelled(ALSA_ds_w1$h_diabetes, labels = cat_label)

# Continuous variable harmonization
ydiabetes <- ALSA_w1$WHENTLD[ALSA_ds_w1$h_diabetes == 1]-ALSA_w1$ybirth[ALSA_ds_w1$h_diabetes == 1]
ALSA_ds_w1$h_diabetes_age <- car::recode(ALSA_ds_w1$h_diabetes, "0 = 996; 1 = ydiabetes")
# The values for which WHENTLD == 9999
ALSA_ds_w1$h_diabetes_age <- car::recode(ALSA_ds_w1$h_diabetes_age, "8092 = 999")

ALSA_ds_w1$h_diabetes_age <- labelled(ALSA_ds_w1$h_diabetes_age, labels = cont_label)

# The individual 9172 answers in the sixth wave it has diabetes diagnosed in 1950, previously to the first wave, so we assume in this one it has been already diagnosed, so we correct this data:
ALSA_ds_w1$h_diabetes[ALSA_ds_w1$id=="9172"] <- 1
ALSA_ds_w1$h_diabetes_age[ALSA_ds_w1$id=="9172"] <- 1950 - ALSA_w1$ybirth[ALSA_w1$id=="9172"]

# We build a global table in order to have updated the diabetes status of all the individuals through the different waves
ALSA_ds <- ALSA_ds_w1

# We integrate the wave results in the global table for possible verifications
# ALSA_ds$h_diabetes_w1 <- car::recode(ALSA_w1$DIABETE, "2 = 0; 9 = 999; NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- ALSA_ds_w1$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w1, aes(x=factor(h_diabetes))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ALSA_ds_w1$h_diabetes_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w1, aes(h_diabetes_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(5,100)

```


#### Validation

```{r crosstabulation w1, echo=F}

# Internal validation of some problematic id's and other potencial incongruences:
# ALSA_w1[ALSA_w1$id %in% sing_idlist,]
# ALSA_w1[!is.na(ALSA_w1$MEDRSNCH) & ALSA_w1$MEDRSNCH==4 & ALSA_w1$DIABETE==2,]
# frq(ALSA_w1$DIABETE[!is.na(ALSA_w1$CURTREAT) & ALSA_w1$CURTREAT==1])

AfterH <- table(ALSA_ds_w1$h_diabetes)
X <- table(ALSA_w1$DIABETE, useNA = "ifany")
BeforeH <- c(X[c(2,1)],sum(X[3:4]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","9,NA->999")
kable(C)

```



### Wave 2

Not found.

### Wave 3

The variable found `W1CDN52` has a 93,75% of missing values.  Not harmonizable.

### Wave 4

Not found.

### Wave 5

Not found.



### Wave 6


#### Study-specific variable description

| **Name** | `DIABETW6` |`WHENTLW6`|`ybirth`|
|-|-|-|-|
| **Label** | `told had diabetes` |`year told had diabetes`|`Year of birth`|
| **Table name**  | `ALSA-Wave6` | `ALSA-Wave6` |`ybirth`|
| **Categories** | `1 = yes; 2 = no` |`continuous`|`continuous`|
| **Missings** | `0 = no answer; NA` |`NA`| `991 = CAPI/interviewer error; 992 = Impute; 993 = Disable to measure; 994 = Not attempt/not done; 995 = Does not answer; 996 = Not applicable; 997 = Refuse; 998 = Do not know; 999 = Missing` |
| **Description** |  |  |  |

```{r assign w6, echo=F}

opal.assign.table.tibble(o, 'ALSA_w6','ALSA.ALSA-Wave6',variables=list('DIABETW6','WHENTLW6'), missings = T)
ALSA_w6 <- opal.execute(o,'ALSA_w6')
ALSA_w6$WHENTLW6 <- as.numeric(ALSA_w6$WHENTLW6)
load(paste0(datafolder,"w6/ybirth.RData"))
ALSA_w6 <- left_join(ALSA_w6,ybirth, by="id")
```

```{r local w6, echo=F}

vbl <- ALSA_w6$DIABETW6
kable(Categorical_summary(vbl, missing_values = c(0))[3], caption = names(ALSA_w6)[2])
kable(Categorical_summary(vbl, missing_values = c(0))[1], caption = "Category")
ggplot(ALSA_w6, aes(x=factor(DIABETW6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w6$WHENTLW6
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(ALSA_w6)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_w6, aes(WHENTLW6)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1950,2000)

vbl <- ALSA_w6$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(ALSA_w6)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_w6, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1895,1930)

```


#### Harmonisation algorithm

To compute `h_diabetes` from the study-specific variable it has to be recoded as follows:

* `DIABETW6 == 2 and DIABETE == 2 into 0`
* `DIABETW6 == 1 or DIABETE == 1 into 1`
* `DIABETW6 == 0 and DIABETE != 1 into 995`
* `otherwise into 999`

To compute `h_diabetes_age` from the study-specific variable it has to be recoded as follows:

* `if h_diabetes == 1, h_diabetes_age = minimum(WHENTLW6 - ybirth, age obtained in previous waves)`
* `if h_diabetes == 0, h_diabetes_age = 996`
* `WHENTLW6 == NA or h_diabetes == missing into 999`

**R script:**

```{r harmo w6}

ALSA_w6 <- left_join(ALSA_w6, ALSA_ds[,1:3], by = "id")
# We use the harmonized variable of wave 1 instead of the study-specific variable
ALSA_ds_w6 <- tibble(id=ALSA_w6$id)
ALSA_ds_w6$h_diabetes <- rep(999,length(ALSA_ds_w6$id))
ALSA_ds_w6$h_diabetes[((!is.na(ALSA_w6$DIABETW6)) & ALSA_w6$DIABETW6 == 2) & ((!is.na(ALSA_w6$h_diabetes)) & ALSA_w6$h_diabetes == 0)] <- 0
ALSA_ds_w6$h_diabetes[((!is.na(ALSA_w6$DIABETW6)) & ALSA_w6$DIABETW6 == 1) | ((!is.na(ALSA_w6$h_diabetes)) & ALSA_w6$h_diabetes == 1)] <- 1
ALSA_ds_w6$h_diabetes[((!is.na(ALSA_w6$DIABETW6)) & ALSA_w6$DIABETW6 == 0) & ((!is.na(ALSA_w6$h_diabetes)) & ALSA_w6$h_diabetes != 1)] <- 995

ALSA_ds_w6$h_diabetes <- labelled(ALSA_ds_w6$h_diabetes, labels = cat_label)

# We update the diabetes status of the individuals in the global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- left_join(endtib,sttib,by="id")
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
ALSA_ds_prov <- ALSA_ds[,c(1,2)]
ALSA_ds_prov <- assign_merge(ALSA_ds_prov,ALSA_ds_w6,log_vec=(ALSA_ds_prov$id %in% ALSA_ds_w6$id),col_end_index = 2, col_st_index = 3)
ALSA_ds$h_diabetes <- ALSA_ds_prov$h_diabetes
# We integrate the wave results in the global table for possible verifications
# ALSA_w6$prov <- car::recode(ALSA_w6$DIABETW6, "2 = 0; 0 = 995; NA = 999")
# ALSA_ds_prov <- left_join(ALSA_ds_prov,ALSA_w6,by="id")
# ALSA_ds$h_diabetes_w6 <- ALSA_ds_prov$prov
# ALSA_w6 <- ALSA_w6[,1:6]
rm(ALSA_ds_prov)

# Continuous variable harmonization
# Obtained ages following diagnosis dates answered in wave 6
diabetes_age_w6 <- ALSA_w6$WHENTLW6[ALSA_ds_w6$h_diabetes == 1]-ALSA_w6$ybirth[ALSA_ds_w6$h_diabetes == 1]
diabetes_age_w6 <- car::recode(diabetes_age_w6,"NA=999")
ALSA_ds_w6$h_diabetes_age <- car::recode(ALSA_ds_w6$h_diabetes, "0 = 996; 1 = diabetes_age_w6; miss_values_vector = 999")
# Obtained ages following diagnosis dates answered in wave 1
ALSA_ds_w6$h_diabetes_age[which(ALSA_ds_w6$h_diabetes==1 & !is.na(ALSA_w6$h_diabetes_age) & !(ALSA_w6$h_diabetes_age %in% miss_values_vector))] <- ALSA_w6$h_diabetes_age[which(ALSA_ds_w6$h_diabetes==1 & !is.na(ALSA_w6$h_diabetes_age) & !(ALSA_w6$h_diabetes_age %in% miss_values_vector))]
ALSA_ds$h_diabetes_age[ALSA_ds$id %in% ALSA_ds_w6$id] <- ALSA_ds_w6$h_diabetes_age

ALSA_ds_w6$h_diabetes_age <- labelled(ALSA_ds_w6$h_diabetes_age, labels = cont_label)

```


#### Statistics of the new harmonized variable

```{r descript w6, echo=F}

vbl <- ALSA_ds_w6$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w6, aes(x=factor(h_diabetes))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ALSA_ds_w6$h_diabetes_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w6, aes(h_diabetes_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(25,95)

```


#### Validation

```{r crosstabulation w6, echo=F, results='asis'}

# Internal validation of some problematic id's and other potencial incongruences:
# ALSA_w6[ALSA_w6$id %in% sing_idlist,]
# frq(ALSA_w6$DIABETW6[!is.na(ALSA_w6$CDN14_W6) & ALSA_w6$CDN14_W6==1])
# ALSA_w6[!is.na(ALSA_w6$CDN14_W6) & ALSA_w6$CDN14_W6==1 & ALSA_w6$DIABETW6==2,]
# frq(ALSA_w6$DIABETW6[!is.na(ALSA_w6$DIA14_W6)])
# ALSA_w6[!is.na(ALSA_w6$DIA14_W6) & is.na(ALSA_w6$DIABETW6),]

AfterH <- table(ALSA_ds_w6$h_diabetes)
X <- c(
  sum(((!is.na(ALSA_w6$DIABETW6)) & ALSA_w6$DIABETW6 == 2) & ((!is.na(ALSA_w6$h_diabetes)) & ALSA_w6$h_diabetes == 0)),
  sum(((!is.na(ALSA_w6$DIABETW6)) & ALSA_w6$DIABETW6 == 1) | ((!is.na(ALSA_w6$h_diabetes)) & ALSA_w6$h_diabetes == 1)),
  sum(((!is.na(ALSA_w6$DIABETW6)) & ALSA_w6$DIABETW6 == 0) & ((!is.na(ALSA_w6$h_diabetes)) & ALSA_w6$h_diabetes != 1))
)
BeforeH <- c(X[1:3],length(ALSA_w6$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 2->0","some 1->1","0->995","NA->999")
kable(C)

# Checking
cat("There are 6 individuals whose answer in the first wave is that they were diagnosed to have diabetes and in the sixth wave is that they were not told to have it. We compute them as having diabetes.")
kable(frq(ALSA_w6$h_diabetes[!is.na(ALSA_w6$DIABETW6) & ALSA_w6$DIABETW6==2]), align = 'c')
kable(ALSA_w6[!is.na(ALSA_w6$DIABETW6) & ALSA_w6$DIABETW6==2 & ALSA_w6$h_diabetes==1,], align = 'c')
#strange_id <- ALSA_w6$id[!is.na(ALSA_w6$DIABETW6) & ALSA_w6$DIABETW6==2 & ALSA_w6$h_diabetes==1]

```



### Wave 7


#### Study-specific variable description

| **Name** | `diabetw7` |`whentlw7`|`ybirth`|
|-|-|-|-|
| **Label** | `Did the doctor tell you you had diabetes` |`what year did he tell you`|`Year of birth`|
| **Table name**  | `ALSA-Wave7` | `ALSA-Wave7` |`ybirth`|
| **Categories** | `1 = Yes; 2 = No` |`continuous`|`continuous`|
| **Missings** | `0 = Not answered; NA` | `NA` | `991 = CAPI/interviewer error; 992 = Impute; 993 = Disable to measure; 994 = Not attempt/not done; 995 = Does not answer; 996 = Not applicable; 997 = Refuse; 998 = Do not know; 999 = Missing` |
| **Description** |  |  |  |

```{r assign w7, echo=F}

opal.assign.table.tibble(o, 'ALSA_w7','ALSA.ALSA-Wave7',variables=list('diabetw7','whentlw7'), missings = T)
ALSA_w7 <- opal.execute(o,'ALSA_w7')
ALSA_w7$whentlw7 <- as.numeric(ALSA_w7$whentlw7)
load(paste0(datafolder,"w7/ybirth.RData"))
ALSA_w7 <- left_join(ALSA_w7,ybirth, by="id")

```

```{r local w7, echo=F}

vbl <- ALSA_w7$diabetw7
kable(Categorical_summary(vbl, missing_values = c(0))[3], caption = names(ALSA_w7)[2])
kable(Categorical_summary(vbl, missing_values = c(0))[1], caption = "Category")
ggplot(ALSA_w7, aes(x=factor(diabetw7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w7$whentlw7
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(ALSA_w7)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_w7, aes(whentlw7)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1955,2005)

vbl <- ALSA_w7$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(ALSA_w7)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_w7, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1885,1930)


```


#### Harmonisation algorithm

To compute `h_diabetes` from the study-specific variable it has to be recoded as follows:

* `DIABETW6 == 2 and DIABETE == 2 (or missings) and diabetw7 == 2 into 0`
* `diabetw7 ==1 or DIABETW6 == 1 or DIABETE == 1 into 1`
* `otherwise into 999`

To compute `h_diabetes_age` from the study-specific variable it has to be recoded as follows:

* `if h_diabetes == 1, h_diabetes_age = minimum(whentlw7 - ybirth, age obtained from previous waves)`
* `if h_diabetes == 0, h_diabetes_age = 996`
* `whentlw7 == NA or h_diabetes == missing into 999`

**R script:**

```{r harmo w7}

# We use the harmonized variable of wave 6 instead of the study-specific variables from all the previous waves
ALSA_ds_w7 <- tibble(id=ALSA_w7$id)
ALSA_w7 <- left_join(ALSA_w7, ALSA_ds[,1:3], by = "id")
ALSA_ds_w7$h_diabetes <- rep(999,length(ALSA_ds_w7$id))
ALSA_ds_w7$h_diabetes[((!is.na(ALSA_w7$diabetw7)) & ALSA_w7$diabetw7 == 2) & ((!is.na(ALSA_w7$h_diabetes)) & ALSA_w7$h_diabetes != 1)] <- 0
ALSA_ds_w7$h_diabetes[((!is.na(ALSA_w7$diabetw7)) & ALSA_w7$diabetw7 == 1) | ((!is.na(ALSA_w7$h_diabetes)) & (!is.na(ALSA_w7$diabetw7)) & ALSA_w7$h_diabetes == 1)] <- 1

ALSA_ds_w7$h_diabetes <- labelled(ALSA_ds_w7$h_diabetes, labels = cat_label)

# We update the diabetes status of the individuals in the global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- left_join(endtib,sttib,by="id")
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
ALSA_ds_prov <- ALSA_ds[,c(1,2)]
ALSA_ds_prov <- assign_merge(ALSA_ds_prov,ALSA_ds_w7,log_vec=(ALSA_ds_prov$id %in% ALSA_ds_w7$id),col_end_index = 2, col_st_index = 3)
ALSA_ds$h_diabetes <- ALSA_ds_prov$h_diabetes
# We integrate the wave results in the global table for possible verifications
# ALSA_w7$prov <- car::recode(ALSA_w7$diabetw7, "2 = 0; NA = 999")
# ALSA_ds_prov <- left_join(ALSA_ds_prov,ALSA_w7,by="id")
# ALSA_ds$h_diabetes_w7 <- ALSA_ds_prov$prov
# ALSA_w7 <- ALSA_w7[,1:6]
rm(ALSA_ds_prov)

# Continuous variable harmonization
# Obtained ages following diagnosis dates answered in wave 7
diabetes_age_w7 <- ALSA_w7$whentlw7[ALSA_ds_w7$h_diabetes == 1]-ALSA_w7$ybirth[ALSA_ds_w7$h_diabetes == 1]
diabetes_age_w7 <- car::recode(diabetes_age_w7,"NA=999")
ALSA_ds_w7$h_diabetes_age <- car::recode(ALSA_ds_w7$h_diabetes, "0 = 996; 1 = diabetes_age_w7; miss_values_vector = 999")
# Obtained ages following diagnosis dates answered in previous waves
ALSA_ds_w7$h_diabetes_age[which(ALSA_ds_w7$h_diabetes == 1 & !is.na(ALSA_w7$h_diabetes_age) & !ALSA_w7$h_diabetes_age %in% miss_values_vector)] <- ALSA_w7$h_diabetes_age[which(ALSA_ds_w7$h_diabetes == 1 & !is.na(ALSA_w7$h_diabetes_age) & !ALSA_w7$h_diabetes_age %in% miss_values_vector)]
ALSA_ds$h_diabetes_age[(ALSA_ds$id %in% ALSA_ds_w7$id) & (ALSA_ds$h_diabetes != 999)] <- ALSA_ds_w7$h_diabetes_age[ALSA_ds_w7$h_diabetes != 999]

ALSA_ds_w7$h_diabetes_age <- labelled(ALSA_ds_w7$h_diabetes_age, labels = cont_label)

```


#### Statistics of the new harmonized variable

```{r descript w7, echo=F}

vbl <- ALSA_ds_w7$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w7, aes(x=factor(h_diabetes))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ALSA_ds_w7$h_diabetes_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w7, aes(h_diabetes_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(5,100)

```


#### Validation

```{r crosstabulation w7, echo=F, results='asis'}

AfterH <- table(ALSA_ds_w7$h_diabetes)
X <- c(
  sum(((!is.na(ALSA_w7$diabetw7)) & ALSA_w7$diabetw7 == 2) & ((!is.na(ALSA_w7$h_diabetes)) & ALSA_w7$h_diabetes != 1)),
  sum(((!is.na(ALSA_w7$diabetw7)) & ALSA_w7$diabetw7 == 1) | ((!is.na(ALSA_w7$h_diabetes)) & (!is.na(ALSA_w7$diabetw7)) & ALSA_w7$h_diabetes == 1))
)
BeforeH <- c(X[1:2],length(ALSA_w7$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 2->0","some 1->1","NA->999")
kable(C)

# Checking
cat("There are 10 individuals who answered in previous waves that they were diagnosed to have diabetes and in the seventh wave that they were not told to have it. We compute them as having diabetes.")
kable(frq(ALSA_w7$h_diabetes[!is.na(ALSA_w7$diabetw7) & ALSA_w7$diabetw7==2]), align = 'c')
kable(ALSA_w7[ALSA_w7$id %in% ALSA_w7$id[ALSA_w7$diabetw7==2 & ALSA_w7$h_diabetes==1],], align = 'c')
#strange_id <- c(strange_id,ALSA_w7$id[ALSA_w7$id %in% ALSA_w7$id[ALSA_w7$diabetw7==2 & ALSA_w7$h_diabetes==1]])

```



### Wave 8

Not found.



### Wave 9


#### Study-specific variable description

| **Name** | `DIABETW9` |`WHENTLW9`|`ybirth`|
|-|-|-|-|
| **Label** | `Did the doctor tell you you had diabetes` |`What year did he/she tell you`|`Year of birth`|
| **Table name**  | `ALSA-Wave9` | `ALSA-Wave9` |`ybirth`|
| **Categories** | `1 = Yes; 2 = No` |`continuous`|`continuous`|
| **Missings** | `0 = Not answered; NA` |`20; NA`| `991 = CAPI/interviewer error; 992 = Impute; 993 = Disable to measure; 994 = Not attempt/not done; 995 = Does not answer; 996 = Not applicable; 997 = Refuse; 998 = Do not know; 999 = Missing` |
| **Description** |  |  |  |

```{r assign w9, echo=F}

opal.assign.table.tibble(o, 'ALSA_w9','ALSA.ALSA-Wave9',variables=list('DIABETW9','WHENTLW9'), missings = T)
ALSA_w9 <- opal.execute(o,'ALSA_w9')
ALSA_w9$WHENTLW9 <- as.numeric(ALSA_w9$WHENTLW9)
# We remove two id's which are not coincident with any other in the other waves of ALSA and whose data is empty.
ALSA_w9 <- ALSA_w9[!ALSA_w9$id %in% c("3515","43202"),]
load(paste0(datafolder,"w9/ybirth.RData"))
ALSA_w9 <- left_join(ALSA_w9,ybirth, by="id")

```

```{r local w9, echo=F}

vbl <- ALSA_w9$DIABETW9
kable(Categorical_summary(vbl, missing_values = c(0))[3], caption = names(ALSA_w9)[2])
kable(Categorical_summary(vbl, missing_values = c(0))[1], caption = "Category")
ggplot(ALSA_w9, aes(x=factor(DIABETW9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w9$WHENTLW9
kable(Continuous_summary(var = vbl, missing_values = c(20))[3], caption = names(ALSA_w9)[3])
pander(Continuous_summary(vbl, missing_values = c(20))$summary, caption = "Summary")
ggplot(ALSA_w9, aes(WHENTLW9)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1975,2010)

vbl <- ALSA_w9$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(ALSA_w9)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_w9, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1885,1930)

```


#### Harmonisation algorithm

To compute `h_diabetes` from the study-specific variable it has to be recoded as follows:

* `diabetw7 == 2 and DIABETW6 == 2 and DIABETE == 2 (or missings) and DIABETW9 == 2 into 0`
* `DIABETW9==1 or diabetw7 ==1 or DIABETW6 == 1 or DIABETE == 1 into 1`
* `previous waves study-specific variables != 1 and DIABETW9 == 0 into 995`
* `otherwise into 999`

To compute `h_diabetes_age` from the study-specific variable it has to be recoded as follows:

* `if h_diabetes == 1, h_diabetes_age = minimum(WHENTLW9 - ybirth, age obtained from previous waves)`
* `if h_diabetes == 0, h_diabetes_age = 996`
* `WHENTLW9 == NA or h_diabetes == missing into 999`
* `WHENTLW9 == 20 into 991`

**R script:**

```{r harmo w9}

# We use the harmonized variable of wave 7 instead of the study-specific variables from all the previous waves
ALSA_ds_w9 <- tibble(id=ALSA_w9$id)
ALSA_w9 <- left_join(ALSA_w9, ALSA_ds[,1:3], by = "id")
ALSA_ds_w9$h_diabetes <- rep(999,length(ALSA_ds_w9$id))
ALSA_ds_w9$h_diabetes[((!is.na(ALSA_w9$DIABETW9)) & ALSA_w9$DIABETW9 == 2) & ((!is.na(ALSA_w9$h_diabetes)) & ALSA_w9$h_diabetes != 1)] <- 0
ALSA_ds_w9$h_diabetes[((!is.na(ALSA_w9$DIABETW9)) & ALSA_w9$DIABETW9 == 1) | ((!is.na(ALSA_w9$h_diabetes)) & (!is.na(ALSA_w9$DIABETW9)) & ALSA_w9$h_diabetes == 1)] <- 1
ALSA_ds_w9$h_diabetes[((!is.na(ALSA_w9$DIABETW9)) & ALSA_w9$DIABETW9 == 0) & ((!is.na(ALSA_w9$h_diabetes)) & ALSA_w9$h_diabetes != 1)] <- 995

ALSA_ds_w9$h_diabetes <- labelled(ALSA_ds_w9$h_diabetes, labels = cat_label)

# We update the diabetes status of the individuals in the global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- left_join(endtib,sttib,by="id")
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
ALSA_ds_prov <- ALSA_ds[,c(1,2)]
ALSA_ds_prov <- assign_merge(ALSA_ds_prov,ALSA_ds_w9,log_vec=(ALSA_ds_prov$id %in% ALSA_ds_w9$id),col_end_index = 2, col_st_index = 3)
ALSA_ds$h_diabetes <- ALSA_ds_prov$h_diabetes
# We integrate the wave results in the global table for possible verifications
# ALSA_w9$prov <- car::recode(ALSA_w9$DIABETW9, "2 = 0; NA = 999")
# ALSA_ds_prov <- left_join(ALSA_ds_prov,ALSA_w9,by="id")
# ALSA_ds$h_diabetes_w9 <- ALSA_ds_prov$prov
# ALSA_w9 <- ALSA_w9[,1:6]
rm(ALSA_ds_prov)

# Continuous variable harmonization
# Obtained ages following diagnosis dates answered in wave 9
diabetes_age_w9 <- ALSA_w9$WHENTLW9[ALSA_ds_w9$h_diabetes == 1]-ALSA_w9$ybirth[ALSA_ds_w9$h_diabetes == 1]
diabetes_age_w9 <- car::recode(diabetes_age_w9,"NA=999; lo:0=991")
ALSA_ds_w9$h_diabetes_age <- car::recode(ALSA_ds_w9$h_diabetes, "0 = 996; 1 = diabetes_age_w9; miss_values_vector = 999")
# Obtained ages following diagnosis dates answered in previous waves
ALSA_ds_w9$h_diabetes_age[which(ALSA_ds_w9$h_diabetes == 1 & !is.na(ALSA_w9$h_diabetes_age) & !ALSA_w9$h_diabetes_age %in% miss_values_vector)] <- ALSA_w9$h_diabetes_age[which(ALSA_ds_w9$h_diabetes == 1 & !is.na(ALSA_w9$h_diabetes_age) & !ALSA_w9$h_diabetes_age %in% miss_values_vector)]
ALSA_ds$h_diabetes_age[ALSA_ds$id %in% ALSA_ds_w9$id & ALSA_ds$h_diabetes != 999] <- ALSA_ds_w9$h_diabetes_age[ALSA_ds_w9$h_diabetes != 999]

ALSA_ds_w9$h_diabetes_age <- labelled(ALSA_ds_w9$h_diabetes_age, labels = cont_label)

```


#### Statistics of the new harmonized variable

```{r descript w9, echo=F}

vbl <- ALSA_ds_w9$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w9, aes(x=factor(h_diabetes))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ALSA_ds_w9$h_diabetes_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w9, aes(h_diabetes_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(5,100)

```


#### Validation

```{r crosstabulation w9, echo=F, results='asis'}

AfterH <- table(ALSA_ds_w9$h_diabetes)
X <- c(
  sum(((!is.na(ALSA_w9$DIABETW9)) & ALSA_w9$DIABETW9 == 2) & ((!is.na(ALSA_w9$h_diabetes)) & ALSA_w9$h_diabetes != 1)),
  sum(((!is.na(ALSA_w9$DIABETW9)) & ALSA_w9$DIABETW9 == 1) | ((!is.na(ALSA_w9$h_diabetes)) & (!is.na(ALSA_w9$DIABETW9)) & ALSA_w9$h_diabetes == 1)),
  sum(((!is.na(ALSA_w9$DIABETW9)) & ALSA_w9$DIABETW9 == 0) & ((!is.na(ALSA_w9$h_diabetes)) & ALSA_w9$h_diabetes != 1))
)
BeforeH <- c(X[1:3],length(ALSA_w9$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 2->0","some 1->1","0->995","NA->999")
kable(C)

cat("There are 3 individuals who answered in previous waves that they were diagnosed to have diabetes and in the ninth wave that they were not told to have it. We compute them as having diabetes.")
kable(frq(ALSA_w9$h_diabetes[!is.na(ALSA_w9$DIABETW9) & ALSA_w9$DIABETW9==2]), align = 'c')
kable(ALSA_w9[ALSA_w9$id %in% ALSA_w9$id[ALSA_w9$DIABETW9==2 & ALSA_w9$h_diabetes==1],], align = 'c')
#strange_id <- c(strange_id,ALSA_w9$id[ALSA_w9$id %in% ALSA_w9$id[ALSA_w9$DIABETW9==2 & ALSA_w9$h_diabetes==1]])

```



### Wave 10

Not found.



### Wave 11


#### Study-specific variable description

| **Name** | `DIAW11` |`DIADIAGW11`|`ybirth`|
|-|-|-|-|
| **Label** | `Diabetes` |`What year first told`|`Year of birth`|
| **Table name**  | `ALSA-Wave11` | `ALSA-Wave11` |`ybirth`|
| **Categories** | `1 = Yes; 0 = No` |`continuous`|`continuous`|
| **Missings** | `NA` |`20-30 years ago; years ago; NA`|`991 = CAPI/interviewer error; 992 = Impute; 993 = Disable to measure; 994 = Not attempt/not done; 995 = Does not answer; 996 = Not applicable; 997 = Refuse; 998 = Do not know; 999 = Missing` |
| **Description** |  |  |  |

```{r assign w11, echo=F}

opal.assign.table.tibble(o, 'ALSA_w11','ALSA.ALSA-Wave11',variables=list('DIAW11','DIADIAGW11'), missings = T)
ALSA_w11 <- opal.execute(o,'ALSA_w11')
age_missing_w11 <- c('20-30 years ago','years ago')
ALSA_w11$DIADIAGW11[ALSA_w11$DIADIAGW11 %in% age_missing_w11] <- 993
ALSA_w11$DIADIAGW11 <- as.numeric(ALSA_w11$DIADIAGW11)
load(paste0(datafolder,"w11/ybirth.RData"))
ALSA_w11 <- left_join(ALSA_w11,ybirth, by="id")

```

```{r local w11, echo=F}

vbl <- ALSA_w11$DIAW11
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w11)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w11, aes(x=factor(DIAW11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w11$DIADIAGW11
kable(Continuous_summary(var = vbl, missing_values = c(993))[3], caption = names(ALSA_w11)[3])
pander(Continuous_summary(vbl, missing_values = c(993))$summary, caption = "Summary")
ggplot(ALSA_w11, aes(DIADIAGW11)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1945,2010)

vbl <- ALSA_w11$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(ALSA_w11)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_w11, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1900,1930)

```


#### Harmonisation algorithm

To compute `h_diabetes` from the study-specific variable it has to be recoded as follows:

* `previous waves study-specific variables != 1 and DIAW11 == 0 into 0`
* `DIAW11 ==1 or DIABETW9 or diabetw7 ==1 or DIABETW6 == 1 or DIABETE == 1 into 1`
* `otherwise into 999`

To compute `h_diabetes_age` from the study-specific variable it has to be recoded as follows:

* `if h_diabetes == 1, h_diabetes_age = minimum(DIADIAGW11 - ybirth, age obtained from previous waves)`
* `if h_diabetes == 0, h_diabetes_age = 996`
* `DIADIAGW11 == NA or h_diabetes == missing into 999`
* `DIADIAGW11 == 20-30 years ago or years ago into 993 (already transformed), even finally they have recorded ages from previous waves`

**R script:**

```{r harmo w11}

# We use the harmonized variable of wave 9 instead of the study-specific variables from all the previous waves
ALSA_ds_w11 <- tibble(id=ALSA_w11$id)
ALSA_w11 <- left_join(ALSA_w11, ALSA_ds[,1:3], by = "id")
ALSA_ds_w11$h_diabetes <- rep(999,length(ALSA_ds_w11$id))
ALSA_ds_w11$h_diabetes[((!is.na(ALSA_w11$DIAW11)) & ALSA_w11$DIAW11 == 0) & ((!is.na(ALSA_w11$h_diabetes)) &  ALSA_w11$h_diabetes != 1)] <- 0
ALSA_ds_w11$h_diabetes[((!is.na(ALSA_w11$DIAW11)) & ALSA_w11$DIAW11 == 1) | ((!is.na(ALSA_w11$h_diabetes)) & (!is.na(ALSA_w11$DIAW11)) & ALSA_w11$h_diabetes == 1)] <- 1

ALSA_ds_w11$h_diabetes <- labelled(ALSA_ds_w11$h_diabetes, labels = cat_label)

# We update the diabetes status of the individuals in the global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- left_join(endtib,sttib,by="id")
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
ALSA_ds_prov <- ALSA_ds[,c(1,2)]
ALSA_ds_prov <- assign_merge(ALSA_ds_prov,ALSA_ds_w11,log_vec=(ALSA_ds_prov$id %in% ALSA_ds_w11$id),col_end_index = 2, col_st_index = 3)
ALSA_ds$h_diabetes <- ALSA_ds_prov$h_diabetes
# We integrate the wave results in the global table for possible validations
# ALSA_w11$prov <- car::recode(ALSA_w11$DIAW11, "2 = 0; NA = 999")
# ALSA_ds_prov <- left_join(ALSA_ds_prov,ALSA_w11,by="id")
# ALSA_ds$h_diabetes_w11 <- ALSA_ds_prov$prov
# ALSA_w11 <- ALSA_w11[,1:6]
rm(ALSA_ds_prov)

# Continuous variable harmonization
# Obtained ages following diagnosis dates answered in wave 11
diabetes_age_w11 <- ALSA_w11$DIADIAGW11[ALSA_ds_w11$h_diabetes == 1]-ALSA_w11$ybirth[ALSA_ds_w11$h_diabetes == 1]
diabetes_age_w11 <- car::recode(diabetes_age_w11,"NA=999; lo:0=993")
ALSA_ds_w11$h_diabetes_age <- car::recode(ALSA_ds_w11$h_diabetes, "0 = 996; 1 = diabetes_age_w11; miss_values_vector = 999")
# Obtained ages following diagnosis dates answered in previous waves
ALSA_ds_w11$h_diabetes_age[which(ALSA_ds_w11$h_diabetes == 1 & !is.na(ALSA_w11$h_diabetes_age) & !ALSA_w11$h_diabetes_age %in% miss_values_vector)] <- ALSA_w11$h_diabetes_age[which(ALSA_ds_w11$h_diabetes == 1 & !is.na(ALSA_w11$h_diabetes_age) & !ALSA_w11$h_diabetes_age %in% miss_values_vector)]
ALSA_ds$h_diabetes_age[ALSA_ds$id %in% ALSA_ds_w11$id & (ALSA_ds$h_diabetes != 999)] <- ALSA_ds_w11$h_diabetes_age[ALSA_ds_w11$h_diabetes != 999]

ALSA_ds_w11$h_diabetes_age <- labelled(ALSA_ds_w11$h_diabetes_age, labels = cont_label)

```


#### Statistics of the new harmonized variable

```{r descript w11, echo=F}

vbl <- ALSA_ds_w11$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w11, aes(x=factor(h_diabetes))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ALSA_ds_w11$h_diabetes_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w11, aes(h_diabetes_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(5,100)

```


#### Validation

```{r crosstabulation w11, echo=F, results='asis'}

AfterH <- table(ALSA_ds_w11$h_diabetes)
X <- c(
  sum(((!is.na(ALSA_w11$DIAW11)) & ALSA_w11$DIAW11 == 0) & ((!is.na(ALSA_w11$h_diabetes)) & ALSA_w11$h_diabetes != 1)),
  sum(((!is.na(ALSA_w11$DIAW11)) & ALSA_w11$DIAW11 == 1) | ((!is.na(ALSA_w11$h_diabetes)) & (!is.na(ALSA_w11$DIAW11)) & ALSA_w11$h_diabetes == 1))
)
BeforeH <- c(X[1:2],length(ALSA_w11$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","NA->999")
kable(C)

cat("There are 3 individuals who answered in previous waves that they were diagnosed to have diabetes and in the eleventh wave that they were not told to have it. We compute them as having diabetes.")
kable(frq(ALSA_w11$h_diabetes[!is.na(ALSA_w11$DIAW11) & ALSA_w11$DIAW11==0]), align = 'c')
kable(ALSA_w11[ALSA_w11$id %in% ALSA_w11$id[ALSA_w11$DIAW11==0 & ALSA_w11$h_diabetes==1],], align = 'c')
#strange_id <- c(strange_id,ALSA_w11$id[ALSA_w11$id %in% ALSA_w11$id[ALSA_w11$DIAW11==0 & ALSA_w11$h_diabetes==1]])

```



### Wave 12


#### Study-specific variable description

| **Name** | `DIAW12` |`age`|
|-|-|-|
| **Label** | `Diabetes` |`age`|
| **Table name**  | `ALSA-Wave12` |`age`|
| **Categories** | `1 = Yes; 0 = No` |`continuous`|
| **Missings** | `2 = not answered` |`991 = CAPI/interviewer error; 992 = Impute; 993 = Disable to measure; 994 = Not attempt/not done; 995 = Does not answer; 996 = Not applicable; 997 = Refuse; 998 = Do not know; 999 = Missing` |
| **Description** |  |  |

```{r assign w12, echo=F}

opal.assign.table.tibble(o, 'ALSA_w12','ALSA.ALSA-Wave12',variables=list('DIAW12'), missings = T)
ALSA_w12 <- opal.execute(o,'ALSA_w12')
load(paste0(datafolder,"w12/age.RData"))
ALSA_w12 <- left_join(ALSA_w12,age, by="id")

```

```{r local w12, echo=F}

vbl <- ALSA_w12$DIAW12
kable(Categorical_summary(vbl, missing_values = c(2))[3], caption = names(ALSA_w12)[2])
kable(Categorical_summary(vbl, missing_values = c(2))[1], caption = "Category")
ggplot(ALSA_w12, aes(x=factor(DIAW12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w12$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(ALSA_w11)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_w12, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(85,105)

```


#### Harmonisation algorithm

To compute `h_diabetes` from the study-specific variable it has to be recoded as follows:

* `previous waves study-specific variables != 1 and DIAW12 == 0 into 0`
* `DIAW12==1 or DIAW11 == 1 or DIABETW9 ==1 or diabetw7 ==1 or DIABETW6 == 1 or DIABETE == 1 into 1`
* `previous waves study-specific variables != 1 and DIAW12 == 2 into 995`
* `otherwise into 999`

To compute `h_diabetes_age` from the study-specific variable it has to be recoded as follows:

* `if h_diabetes == 1 in w12 and 0 in w11, h_diabetes_age = age-(year of interview w12-year of interview w11)/2. Since year of interview w12 == 2013 and year of interview w11 == 2010, the mid difference is 1.5. Since the age is usually given as an integer we would apply the floor, but all together is the same that h_diabetes_age = age-2`
* `if h_diabetes == 1 in w12 and w11, h_diabetes_age = age obtained from previous waves`
* `if h_diabetes == 0, h_diabetes_age = 996`
* `h_diabetes == missing into 999`

**R script:**

```{r harmo w12}

# We use the harmonized variable of wave 11 instead of the study-specific variables from all the previous waves
ALSA_ds_w12 <- tibble(id=ALSA_w12$id)
ALSA_w12 <- left_join(ALSA_w12, ALSA_ds[,1:3], by = "id")
ALSA_ds_w12$h_diabetes <- rep(999,length(ALSA_ds_w12$id))
ALSA_ds_w12$h_diabetes[((!is.na(ALSA_w12$DIAW12)) & ALSA_w12$DIAW12 == 0) & ((!is.na(ALSA_w12$h_diabetes)) & ALSA_w12$h_diabetes != 1)] <- 0
ALSA_ds_w12$h_diabetes[((!is.na(ALSA_w12$DIAW12)) & ALSA_w12$DIAW12 == 1) | ((!is.na(ALSA_w12$h_diabetes)) & (!is.na(ALSA_w12$DIAW12)) & ALSA_w12$h_diabetes == 1)] <- 1
ALSA_ds_w12$h_diabetes[((!is.na(ALSA_w12$DIAW12)) & ALSA_w12$DIAW12 == 2) & ((!is.na(ALSA_w12$h_diabetes)) & ALSA_w12$h_diabetes != 1)] <- 995

ALSA_ds_w12$h_diabetes <- labelled(ALSA_ds_w12$h_diabetes, labels = cat_label)

# We update the diabetes status of the individuals in the global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- left_join(endtib,sttib,by="id")
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
ALSA_ds_prov <- ALSA_ds[,c(1,2)]
ALSA_ds_prov <- assign_merge(ALSA_ds_prov,ALSA_ds_w12,log_vec=(ALSA_ds_prov$id %in% ALSA_ds_w12$id),col_end_index = 2, col_st_index = 3)
ALSA_ds$h_diabetes <- ALSA_ds_prov$h_diabetes
# We integrate the wave results in the global table for possible validations
# ALSA_w12$prov <- car::recode(ALSA_w12$DIAW12, "2 = 0; NA = 999")
# ALSA_ds_prov <- left_join(ALSA_ds_prov,ALSA_w12,by="id")
# ALSA_ds$h_diabetes_w12 <- ALSA_ds_prov$prov
# ALSA_w12 <- ALSA_w12[,1:5]
rm(ALSA_ds_prov)

# Continuous variable harmonization
ALSA_ds_w12$h_diabetes_age <- rep(999,length(ALSA_ds_w12$id))

# Obtained ages following diagnosis dates answered in wave 12
diabetes_age_w12 <- ALSA_w12$age[ALSA_ds_w12$h_diabetes == 1]-2
# Obtained ages following diagnosis dates answered in previous waves
diabetes_age_w1 <- ALSA_w12$h_diabetes_age[ALSA_ds_w12$h_diabetes==1]
diabetes_age_w1 <- car::recode(diabetes_age_w1, "miss_values_vector = 999")
# Computing the minimum age obtained (it agrees with the algorithm at the beginning)
diabetes_age <- pmin(diabetes_age_w12,diabetes_age_w1)
ALSA_ds_w12$h_diabetes_age <- car::recode(ALSA_ds_w12$h_diabetes, "0 = 996; 1 = diabetes_age; miss_values_vector = 999")
ALSA_ds$h_diabetes_age[(ALSA_ds$id %in% ALSA_ds_w12$id) & (ALSA_ds$h_diabetes != 999)] <- ALSA_ds_w12$h_diabetes_age[ALSA_ds_w12$h_diabetes != 999]

ALSA_ds_w12$h_diabetes_age <- labelled(ALSA_ds_w12$h_diabetes_age, labels = cont_label)

```


#### Statistics of the new harmonized variable

```{r descript w12, echo=F}

vbl <- ALSA_ds_w12$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w12, aes(x=factor(h_diabetes))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ALSA_ds_w12$h_diabetes_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w12, aes(h_diabetes_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(5,100)

```


#### Validation

```{r crosstabulation w12, echo=F, results='asis'}

AfterH <- table(ALSA_ds_w12$h_diabetes)
BeforeH <- c(
  sum(((!is.na(ALSA_w12$DIAW12)) & ALSA_w12$DIAW12 == 0) & ((!is.na(ALSA_w12$h_diabetes)) & ALSA_w12$h_diabetes != 1)),
  sum(((!is.na(ALSA_w12$DIAW12)) & ALSA_w12$DIAW12 == 1) | ((!is.na(ALSA_w12$h_diabetes)) & (!is.na(ALSA_w12$DIAW12)) & ALSA_w12$h_diabetes == 1)),
  sum(((!is.na(ALSA_w12$DIAW12)) & ALSA_w12$DIAW12 == 2) & ((!is.na(ALSA_w12$h_diabetes)) & ALSA_w12$h_diabetes != 1))
)

C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","2->995")
kable(C)

cat("There are 3 individuals who answered in previous waves that they were diagnosed to have diabetes and in the twelfth wave that they were not told to have it. We compute them as having diabetes.")
kable(frq(ALSA_w12$h_diabetes[!is.na(ALSA_w12$DIAW12) & ALSA_w12$DIAW12==0]), align = 'c')
kable(ALSA_w12[ALSA_w12$id %in% ALSA_w12$id[ALSA_w12$DIAW12==0 & ALSA_w12$h_diabetes==1],], align = 'c')
#strange_id <- c(strange_id,ALSA_w12$id[ALSA_w12$id %in% ALSA_w12$id[ALSA_w12$DIAW12==0 & ALSA_w12$h_diabetes==1]])

```



### Wave 13

Not found.


<!--
```{r summary, include=F, eval=F, echo=F}
kable(ALSA_ds[ALSA_ds$id %in% strange_id,], align = 'c', caption = 'Individuals with discrepancies')
```
-->

## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.

**R script:**

```{r summ}
ALSA_ds_w1$h_diabetes <- labelled(ALSA_ds_w1$h_diabetes, labels = cat_label)
label(ALSA_ds_w1$h_diabetes) <- ds_label
label(ALSA_ds_w1$h_diabetes_age) <- ds_label_age
ALSA_ds_w6$h_diabetes <- labelled(ALSA_ds_w6$h_diabetes, labels = cat_label)
label(ALSA_ds_w6$h_diabetes) <- ds_label
label(ALSA_ds_w6$h_diabetes_age) <- ds_label_age
ALSA_ds_w7$h_diabetes <- labelled(ALSA_ds_w7$h_diabetes, labels = cat_label)
label(ALSA_ds_w7$h_diabetes) <- ds_label
label(ALSA_ds_w7$h_diabetes_age) <- ds_label_age
ALSA_ds_w9$h_diabetes <- labelled(ALSA_ds_w9$h_diabetes, labels = cat_label)
label(ALSA_ds_w9$h_diabetes) <- ds_label
label(ALSA_ds_w9$h_diabetes_age) <- ds_label_age
ALSA_ds_w11$h_diabetes <- labelled(ALSA_ds_w11$h_diabetes, labels = cat_label)
label(ALSA_ds_w11$h_diabetes) <- ds_label
label(ALSA_ds_w11$h_diabetes_age) <- ds_label_age
ALSA_ds_w12$h_diabetes <- labelled(ALSA_ds_w12$h_diabetes, labels = cat_label)
label(ALSA_ds_w12$h_diabetes) <- ds_label
label(ALSA_ds_w12$h_diabetes_age) <- ds_label_age

ALSA_m_ds_w1 <- ALSA_ds_w1
ALSA_m_ds_w1$h_diabetes <- car::recode(ALSA_m_ds_w1$h_diabetes, "miss_values_vector=NA")
ALSA_m_ds_w6 <- ALSA_ds_w6
ALSA_m_ds_w6$h_diabetes <- car::recode(ALSA_m_ds_w6$h_diabetes, "miss_values_vector=NA")
ALSA_m_ds_w7 <- ALSA_ds_w7
ALSA_m_ds_w7$h_diabetes <- car::recode(ALSA_m_ds_w7$h_diabetes, "miss_values_vector=NA")
ALSA_m_ds_w9 <- ALSA_ds_w9
ALSA_m_ds_w9$h_diabetes <- car::recode(ALSA_m_ds_w9$h_diabetes, "miss_values_vector=NA")
ALSA_m_ds_w11 <- ALSA_ds_w11
ALSA_m_ds_w11$h_diabetes <- car::recode(ALSA_m_ds_w11$h_diabetes, "miss_values_vector=NA")
ALSA_m_ds_w12 <- ALSA_ds_w12
ALSA_m_ds_w12$h_diabetes <- car::recode(ALSA_m_ds_w12$h_diabetes, "miss_values_vector=NA")

tt <-    frq(ALSA_ds_w1$h_diabetes)[[1]][,c(1:2,4)]
tt[4] <- frq(ALSA_ds_w6$h_diabetes)[[1]][,c(4)]
tt[5] <- frq(ALSA_ds_w7$h_diabetes)[[1]][,c(4)]
tt[6] <- frq(ALSA_ds_w9$h_diabetes)[[1]][,c(4)]
tt[7] <- frq(ALSA_ds_w11$h_diabetes)[[1]][,c(4)]
tt[8] <- frq(ALSA_ds_w12$h_diabetes)[[1]][,c(4)]
tt[13,] <- c("n", "sample size", 
             length(ALSA_ds_w1$h_diabetes), length(ALSA_ds_w6$h_diabetes), length(ALSA_ds_w7$h_diabetes),
             length(ALSA_ds_w9$h_diabetes), length(ALSA_ds_w11$h_diabetes), length(ALSA_ds_w12$h_diabetes)
             )
names(tt)<-c("val", "label", "w1", "w6", "w7", "w9", "w11", "w12")
kable(tt)

dbb <- merge(ALSA_m_ds_w1[,c("id","h_diabetes")], ALSA_m_ds_w6[,c("id","h_diabetes")], by="id", suffixes = c(".w1",".w6"), all=T)
dbb <- merge(dbb, ALSA_m_ds_w7[,c("id","h_diabetes")], by="id", all=T)
dbb <- merge(dbb, ALSA_m_ds_w9[,c("id","h_diabetes")], by="id", suffixes = c(".w7",".w9"), all=T)
dbb <- merge(dbb, ALSA_m_ds_w11[,c("id","h_diabetes")], by="id", all=T)
dbb <- merge(dbb, ALSA_m_ds_w12[,c("id","h_diabetes")], by="id", suffixes = c(".w11",".w12"), all=T)
names(dbb) <- c("id", "w1", "w6", "w7", "w9", "w11", "w12")
v.dbb <- paste(dbb[,2],dbb[,3],dbb[,4],dbb[,5],dbb[,6],dbb[,7],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])
```



# Quality estimation

* We assume that if an individual answers it has diabetes in one wave, it has diabetes for all the next waves. Individuals with discrepancies with respect to this criterium are specified at the end of each validation.
* There are individuals with different diagnostic years data across waves. We harmonize diagnostic age taking the first year they answer.


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.ALSA <- list(w1 = ALSA_ds_w1, w6 = ALSA_ds_w6, w7 = ALSA_ds_w7, w9 = ALSA_ds_w9, w11 = ALSA_ds_w11, w12 = ALSA_ds_w12)

for(index in seq_along(l.ALSA)){
  h_diabetes <- l.ALSA[[index]]
  save(h_diabetes, file = paste0(datafolder,names(l.ALSA)[index],"/h_diabetes.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





