---
title: "Chronic pulmonary disorders"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `h_cpd`
* Variable label: `History of chronic pulmonary disorders`
* Variable description: `history of chronic pulmonary disease`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | NO chronic pulmonary disease
1        | chronic pulmonary disease

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Short name: `h_cpd_age`
* Variable label: `Age first diagnosed chronic pulmonary disease`
* Variable description: `The age first told had chronic lung disease diagnosis`
* Domain: `Diseases`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "History of chronic pulmonary disorders"
ds_label_age <- "Age first diagnosed chronic pulmonary disease"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
cont_label <- cat_label[3:11]
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process



## Australia


### Wave 1


#### Study-specific variable description

| **Name** | `MORBID7` |`DIAGYR7`|`ybirth`|
|-|-|-|-|
| **Label** | `Chronic bronchitis` |`Year of diagnosis: Chronic bronchitis`|`Year of birth`|
| **Table name**  | `ALSA-Wave1` | `ALSA-Wave1` |`ybirth`|
| **Categories** | `0 = No`<br/>`1 = Yes` | `continuous` | `continuous` |
| **Missings** |  | `NA` |   |
| **Description** |  |  |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'ALSA_w1','ALSA.ALSA-Wave1',variables=list('MORBID7','DIAGYR7'), missings = T)
ALSA_w1 <- opal.execute(o,'ALSA_w1')
load(paste0(datafolder,"w1/ybirth.RData"))
ALSA_w1 <- left_join(ALSA_w1,ybirth, by="id")

```

```{r local w1, echo=F}

vbl <- ALSA_w1$MORBID7
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w1, aes(x=factor(MORBID7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w1$DIAGYR7
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(ALSA_w1)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_w1, aes(DIAGYR7)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1905,1995)

vbl <- ALSA_w1$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(ALSA_w1)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_w1, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1885,1930)

```


#### Harmonisation algorithm

To compute `h_cpd` from the study-specific variable it has to be recoded as follows:

* `keep up 0 into 0`
* `keep up 1 into 1`

To compute `h_cpd_age` from the study-specific variable it has to be recoded as follows:

* `if h_cpd == 1, h_cpd_age = DIAGYR7 - ybirth`
* `if h_cpd == 0, h_cpd_age = 996`
* `otherwise into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
ALSA_ds_w1 <- tibble(id=ALSA_w1$id)
ALSA_ds_w1$h_cpd <- car::recode(ALSA_w1$MORBID7, "NA = 999")

# Continuous variable harmonization
cpd_age <- ALSA_w1$DIAGYR7[ALSA_ds_w1$h_cpd == 1]-ALSA_w1$ybirth[ALSA_ds_w1$h_cpd == 1]
ALSA_ds_w1$h_cpd_age <- car::recode(ALSA_ds_w1$h_cpd, "0 = 996; 1 = cpd_age")
ALSA_ds_w1$h_cpd_age <- car::recode(ALSA_ds_w1$h_cpd_age,"NA=999")

# We build a global table in order to have updated the status of all the individuals through the different waves
ALSA_ds <- ALSA_ds_w1

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- ALSA_ds_w1$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w1, aes(x=factor(h_cpd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ALSA_ds_w1$h_cpd_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w1, aes(h_cpd_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(0,95)

```


#### Validation

```{r crosstabulation w1, echo=F}

continuous <- c(sum(ALSA_ds_w1$h_cpd_age==996,na.rm=T),sum(ALSA_ds_w1$h_cpd_age!=996,na.rm=T))
X <- table(ALSA_ds_w1$h_cpd, useNA = "ifany")
dichotomous <- c(X[1],sum(X[2:3],na.rm=T))
C <- rbind(continuous,dichotomous)
colnames(C) <- c("0<-->996","1<-->(possibly missing) age of diagnostic")
kable(C,caption = "Continuous vs Dichotomous")

```



### Wave 2

Not found.




### Wave 3


#### Study-specific variable description

| **Name** | `W1CDN7` |
|-|-|
| **Label** | `CHRONIC BRONCHITIS` |
| **Table name**  | `ALSA-Wave3` |
| **Categories** | `1 = Yes`<br/>`0 = No` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign w3, echo=F}

opal.assign.table.tibble(o, 'ALSA_w3','ALSA.ALSA-Wave3',variables=list('W1CDN7'), missings = T)
ALSA_w3 <- opal.execute(o,'ALSA_w3')

```

```{r local w3, echo=F}

vbl <- ALSA_w3$W1CDN7
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w3)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w3, aes(x=factor(W1CDN7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_cpd` from the study-specific variable it has to be recoded as follows:

* `MORBID7 == 0 (or missings) and W1CDN7 == 0 into 0`
* `W1CDN7 ==1 or MORBID7 == 1 into 1`
* `otherwise into 999`

Age of diagnostic cannot be harmonized.

**R script:**

```{r harmo w3}

# We use the harmonized variable of wave 1 instead of the study-specific variables from all the previous waves
ALSA_w3 <- left_join(ALSA_w3, ALSA_ds, by = "id")

ALSA_ds_w3 <- tibble(id=ALSA_w3$id)
ALSA_ds_w3$h_cpd <- rep(999,length(ALSA_ds_w3$id))
ALSA_ds_w3$h_cpd[which(ALSA_w3$W1CDN7 == 0 & ((is.na(ALSA_w3$h_cpd)) | ALSA_w3$h_cpd != 1))] <- 0
ALSA_ds_w3$h_cpd[which(ALSA_w3$W1CDN7 == 1 | ((!is.na(ALSA_w3$W1CDN7)) & ALSA_w3$h_cpd == 1))] <- 1

# We update the status of the individuals in the global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- left_join(endtib,sttib,by="id")
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
ALSA_ds_prov <- ALSA_ds[,c(1,2)]
ALSA_ds_prov <- assign_merge(ALSA_ds_prov,ALSA_ds_w3,log_vec=(ALSA_ds_prov$id %in% ALSA_ds_w3$id),col_end_index = 2, col_st_index = 3)
ALSA_ds$h_cpd <- ALSA_ds_prov$h_cpd
rm(ALSA_ds_prov)

```


#### Statistics of the new harmonized variable

```{r descript w3, echo=F}

vbl <- ALSA_ds_w3$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w3, aes(x=factor(h_cpd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w3, echo=F, results='asis'}

AfterH <- table(ALSA_ds_w3$h_cpd)
X <- c(
  sum(ALSA_w3$W1CDN7 == 0 & ((is.na(ALSA_w3$h_cpd)) | ALSA_w3$h_cpd != 1),na.rm=T),
  sum(ALSA_w3$W1CDN7 == 1 | ((!is.na(ALSA_w3$W1CDN7)) & ALSA_w3$h_cpd == 1),na.rm=T)
)
BeforeH <- c(X[2],length(ALSA_w3$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("some 1->1","NA->999")
kable(C)

# Checking
cat("The 102 individuals which tell in this wave they do not have chronic bronchitis, answered that they had in the first wave. All them are harmonized as having respiratory disorders.")

kable(frq(ALSA_w3$W1CDN7[which(ALSA_w3$h_cpd==1)]), align = 'c')
kable(ALSA_w3[which(ALSA_w3$h_cpd==1 & ALSA_w3$W1CDN7 == 0),],align = 'c')

```

### Wave 4

Not found.

### Wave 5

Not found.



### Wave 6


#### Study-specific variable description

| **Name** | `CDN10_W6` |`DIA10_W6`|`ybirth`|
|-|-|-|-|
| **Label** | `Chronic bronchitis, emphysema` |`year told of: chronic bronchitis, emphysema`|`Year of birth`|
| **Table name**  | `ALSA-Wave6` | `ALSA-Wave6` |`ybirth`|
| **Categories** | `0 = No`<br/>`1 = Yes` |`continuous`|`continuous`|
| **Missings** | `NA` |`NA`|  |
| **Description** |  |  |  |

```{r assign w6, echo=F}

opal.assign.table.tibble(o, 'ALSA_w6','ALSA.ALSA-Wave6',variables=list('CDN10_W6','DIA10_W6'), missings = T)
ALSA_w6 <- opal.execute(o,'ALSA_w6')
ALSA_w6$DIA10_W6[which(ALSA_w6$DIA10_W6=="78")] <-"1978"
ALSA_w6$DIA10_W6 <- as.numeric(ALSA_w6$DIA10_W6)
load(paste0(datafolder,"w6/ybirth.RData"))
ALSA_w6 <- left_join(ALSA_w6,ybirth, by="id")
```

```{r local w6, echo=F}

vbl <- ALSA_w6$CDN10_W6
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w6)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w6, aes(x=factor(CDN10_W6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w6$DIA10_W6
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(ALSA_w6)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_w6, aes(DIA10_W6)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1940,2005)

vbl <- ALSA_w6$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(ALSA_w6)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_w6, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1895,1930)

```


#### Harmonisation algorithm

To compute `h_cpd` from the study-specific variable it has to be recoded as follows:

* `W1CDN7 == 0 and MORBID7 == 0 (or missings) and CDN10_W6 == 0 into 0`
* `CDN10_W6 == 1 or W1CDN7 == 1 or MORBID7 == 1 into 1`
* `otherwise into 999`

To compute `h_cpd_age` from the study-specific variable it has to be recoded as follows:

* `if h_cpd == 1 in w6 and previously, h_cpd_age = as before`
* `if h_cpd == 1 in w6 and 0 previously h_cpd_age = DIA10_W6 - ybirth`
* `if h_cpd == 0, h_cpd_age = 996`
* `otherwise into 999`


**R script:**

```{r harmo w6}

# We use the harmonized variable of previous waves instead of the study-specific variables
ALSA_w6 <- left_join(ALSA_w6, ALSA_ds, by = "id")

ALSA_ds_w6 <- tibble(id=ALSA_w6$id)
ALSA_ds_w6$h_cpd <- rep(999,length(ALSA_ds_w6$id))
ALSA_ds_w6$h_cpd[which(ALSA_w6$CDN10_W6 == 0 & (ALSA_w6$h_cpd != 1 | is.na(ALSA_w6$h_cpd)))] <- 0
ALSA_ds_w6$h_cpd[which(ALSA_w6$CDN10_W6 == 1 | ((!is.na(ALSA_w6$CDN10_W6)) & ALSA_w6$h_cpd == 1))] <- 1

# We update the status of the individuals in the global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- left_join(endtib,sttib,by="id")
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
ALSA_ds_prov <- ALSA_ds[,c(1,2)]
ALSA_ds_prov <- assign_merge(ALSA_ds_prov,ALSA_ds_w6,log_vec=(ALSA_ds_prov$id %in% ALSA_ds_w6$id),col_end_index = 2, col_st_index = 3)
ALSA_ds$h_cpd <- ALSA_ds_prov$h_cpd
rm(ALSA_ds_prov)

# Continuous variable harmonization
# Obtained ages following diagnosis dates answered in wave 6
cpd_age_w6 <- ALSA_w6$DIA10_W6[which(ALSA_ds_w6$h_cpd == 1)]-ALSA_w6$ybirth[which(ALSA_ds_w6$h_cpd == 1)]
cpd_age_w6 <- car::recode(cpd_age_w6,"NA=999")
ALSA_ds_w6$h_cpd_age <- car::recode(ALSA_ds_w6$h_cpd, "0 = 996; 1 = cpd_age_w6; miss_values_vector = 999")
# Obtained ages following diagnosis dates answered in wave 1
ALSA_ds_w6$h_cpd_age[which(ALSA_ds_w6$h_cpd==1 & !is.na(ALSA_w6$h_cpd_age) & !(ALSA_w6$h_cpd_age %in% miss_values_vector))] <- ALSA_w6$h_cpd_age[which(ALSA_ds_w6$h_cpd==1 & !is.na(ALSA_w6$h_cpd_age) & !(ALSA_w6$h_cpd_age %in% miss_values_vector))]

ALSA_ds$h_cpd_age[ALSA_ds$id %in% ALSA_ds_w6$id] <- ALSA_ds_w6$h_cpd_age

```


#### Statistics of the new harmonized variable

```{r descript w6, echo=F}

vbl <- ALSA_ds_w6$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w6, aes(x=factor(h_cpd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ALSA_ds_w6$h_cpd_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w6, aes(h_cpd_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(10,95)

```


#### Validation

```{r crosstabulation w6, echo=F, results='asis'}

ALSA_w6$age_w6 <- ALSA_w6$DIA10_W6-ALSA_w6$ybirth
kable(ALSA_w6[which(!is.na(ALSA_w6$DIA10_W6) & !ALSA_w6$h_cpd_age %in% miss_values_vector & ALSA_w6$h_cpd_age != ALSA_w6$age_w6 & ALSA_w6$age_w6>0),],align = 'c',caption = 'There are individuals which answer different year of diagnostic in waves 1 and 6. We harmonize the age of diagnostic with the first data answered.')

AfterH <- table(ALSA_ds_w6$h_cpd)
X <- c(
  sum(ALSA_w6$CDN10_W6 == 0 & (ALSA_w6$h_cpd != 1 | is.na(ALSA_w6$h_cpd)),na.rm=T),
  sum(ALSA_w6$CDN10_W6 == 1 | ((!is.na(ALSA_w6$CDN10_W6)) & ALSA_w6$h_cpd == 1),na.rm=T)
)
BeforeH <- c(X[2],length(ALSA_w6$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("some 1->1","NA->999")
kable(C)

```



### Wave 7

Not found.


### Wave 8

Not found.



### Wave 9

Not found.



### Wave 10

Not found.



### Wave 11


#### Study-specific variable description

| **Name** | `RD2W11`|`RD3W11`|
|-|-|-|
| **Label** | `Chronic bronchitis`|`Emphysema`|
| **Table name**  | `ALSA-Wave11` | `ALSA-Wave11` |
| **Categories** |  `0 = No`<br/>`1 = Yes` | `0 = No`<br/>`1 = Yes` |
| **Missings** | `NA`| `NA`|
| **Description** |  |  |

```{r assign w11, echo=F}

opal.assign.table.tibble(o, 'ALSA_w11','ALSA.ALSA-Wave11',variables=list('RD2W11','RD3W11'), missings = T)
ALSA_w11 <- opal.execute(o,'ALSA_w11')

```

```{r local w11, echo=F}

vbl <- ALSA_w11$RD2W11
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w11)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w11, aes(x=factor(RD2W11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w11$RD3W11
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w11)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w11, aes(x=factor(RD3W11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_cpd` from the study-specific variable it has to be recoded as follows:

* `previous waves study-specific variables != 1 and RD2W11 == 0 and RD3W11 == 0 into 0`
* `RD2W11 == 1 or RD3W11 == 1 or some previous waves study-specific variable == 1 into 1`
* `otherwise into 999`

Age of diagnostic cannot be harmonized.

**R script:**

```{r harmo w11}

# We use the harmonized variable of previous waves instead of the study-specific variables
ALSA_w11 <- left_join(ALSA_w11, ALSA_ds, by = "id")

ALSA_ds_w11 <- tibble(id=ALSA_w11$id)
ALSA_ds_w11$h_cpd <- rep(999,length(ALSA_ds_w11$id))
ALSA_ds_w11$h_cpd[which((ALSA_w11$h_cpd != 1 | is.na(ALSA_w11$h_cpd)) & ALSA_w11$RD2W11 == 0 & ALSA_w11$RD3W11 == 0)] <- 0
ALSA_ds_w11$h_cpd[which((ALSA_w11$h_cpd == 1 & !(is.na(ALSA_w11$RD2W11 & is.na(ALSA_w11$RD3W11)))) | ALSA_w11$RD2W11 == 1 | ALSA_w11$RD3W11 == 1)] <- 1





# We update the status of the individuals in the global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- left_join(endtib,sttib,by="id")
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
ALSA_ds_prov <- ALSA_ds[,c(1,2)]
ALSA_ds_prov <- assign_merge(ALSA_ds_prov,ALSA_ds_w11,log_vec=(ALSA_ds_prov$id %in% ALSA_ds_w11$id),col_end_index = 2, col_st_index = 3)
ALSA_ds$h_cpd <- ALSA_ds_prov$h_cpd
rm(ALSA_ds_prov)

```


#### Statistics of the new harmonized variable

```{r descript w11, echo=F}

vbl <- ALSA_ds_w11$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w11, aes(x=factor(h_cpd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w11, echo=F, results='asis'}

AfterH <- table(ALSA_ds_w11$h_cpd)
X <- c(
  sum((ALSA_w11$h_cpd != 1 | is.na(ALSA_w11$h_cpd)) & ALSA_w11$RD2W11 == 0 & ALSA_w11$RD3W11 == 0,na.rm=T),
  sum((ALSA_w11$h_cpd == 1 & !(is.na(ALSA_w11$RD2W11 & is.na(ALSA_w11$RD3W11)))) | ALSA_w11$RD2W11 == 1 | ALSA_w11$RD3W11 == 1,na.rm=T)
)
BeforeH <- c(X[1:2],length(ALSA_ds_w11$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","NA->999")
kable(C)
#strange_id <- c(strange_id,ALSA_w11$id[ALSA_w11$id %in% ALSA_w11$id[ALSA_w11$RD1W11==0 & ALSA_w11$h_cpd==1]])

```



### Wave 12


#### Study-specific variable description

| **Name** |`RD2W12`|`RD3W12` |`age`|
|-|-|-|-|
| **Label** | `Chronic bronchitis`|`Emphysema`|`age`|
| **Table name**  | `ALSA-Wave12` | `ALSA-Wave12` |`age`|
| **Categories** | `0 = No`<br/>`1 = Yes` | `0 = No`<br/>`1 = Yes`|`continuous`|
| **Missings** | `NA` | `NA` |  |
| **Description** |  |  |  |

```{r assign w12, echo=F}

opal.assign.table.tibble(o, 'ALSA_w12','ALSA.ALSA-Wave12',variables=list('RD2W12','RD3W12'), missings = T)
ALSA_w12 <- opal.execute(o,'ALSA_w12')
load(paste0(datafolder,"w12/age.RData"))
ALSA_w12 <- left_join(ALSA_w12,age, by="id")

```

```{r local w12, echo=F}

vbl <- ALSA_w12$RD2W12
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w12)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w12, aes(x=factor(RD2W12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w12$RD3W12
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w12)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w12, aes(x=factor(RD3W12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w12$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(ALSA_w11)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_w12, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(85,105)

```


#### Harmonisation algorithm

To compute `h_cpd` from the study-specific variable it has to be recoded as follows:

* `previous waves study-specific variables != 1 and RD2W12 == 0 and RD3W12 == 0 into 0`
* `RD2W12 == 1 or RD3W12 == 1 or some previous waves study-specific variable == 1 into 1`
* `otherwise into 999`

To compute `h_cpd_age` from the study-specific variable it has to be recoded as follows:

* `if h_cpd == 1 in w12 and 0 in w11, h_cpd_age = age-(year of interview w12-year of interview w11)/2. Since year of interview w12 == 2013 and year of interview w11 == 2010, the mid difference is 1.5. Since the age is usually given as an integer we would apply the floor, but all together is the same that h_cpd_age = age-2`
* `if h_cpd == 1 in w12 and previously, h_cpd_age = age obtained from previous waves`
* `if h_cpd == 0, h_cpd_age = 996`
* `h_cpd == missing into 999`

**R script:**

```{r harmo w12}

# We use the harmonized variable of previous waves instead of the study-specific variables
ALSA_w12 <- left_join(ALSA_w12, ALSA_ds, by = "id")

ALSA_ds_w12 <- tibble(id=ALSA_w12$id)
ALSA_ds_w12$h_cpd <- rep(999,length(ALSA_ds_w12$id))
ALSA_ds_w12$h_cpd[which((ALSA_w12$h_cpd != 1 | is.na(ALSA_w12$h_cpd)) & ALSA_w12$RD2W12 == 0 & ALSA_w12$RD3W12 == 0)] <- 0
ALSA_ds_w12$h_cpd[which((ALSA_w12$h_cpd == 1 & !(is.na(ALSA_w12$RD2W12 & is.na(ALSA_w12$RD3W12)))) | ALSA_w12$RD2W12 == 1 | ALSA_w12$RD3W12 == 1)] <- 1


# We update the status of the individuals in the global table
rm(ALSA_ds)

# Continuous variable harmonization
ALSA_ds_w12$h_cpd_age <- rep(999,length(ALSA_ds_w12$id))

ALSA_w12 <- left_join(ALSA_w12, ALSA_ds_w11, by = "id", suffix =c("","_w11"))
# Obtained ages following diagnosis dates answered in wave 12
ALSA_ds_w12$h_cpd_age[which(ALSA_ds_w12$h_cpd == 1 & ALSA_w12$h_cpd_w11 == 0)] <- ALSA_w12$age[which(ALSA_ds_w12$h_cpd == 1 & ALSA_w12$h_cpd_w11 == 0)]-2
ALSA_ds_w12$h_cpd_age[which(ALSA_ds_w12$h_cpd == 0)] <- 996
ALSA_ds_w12$h_cpd_age[which(ALSA_ds_w12$h_cpd == 1 & !is.na(ALSA_w12$h_cpd_age) & !ALSA_w12$h_cpd_age %in% miss_values_vector)] <- ALSA_w12$h_cpd_age[which(ALSA_ds_w12$h_cpd == 1 & !is.na(ALSA_w12$h_cpd_age) & !ALSA_w12$h_cpd_age %in% miss_values_vector)]

```


#### Statistics of the new harmonized variable

```{r descript w12, echo=F}

vbl <- ALSA_ds_w12$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w12, aes(x=factor(h_cpd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ALSA_ds_w12$h_cpd_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w12, aes(h_cpd_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(20,100)

```


#### Validation

```{r crosstabulation w12, echo=F, results='asis'}

AfterH <- table(ALSA_ds_w12$h_cpd)
X <- c(
  sum((ALSA_w12$h_cpd != 1 | is.na(ALSA_w12$h_cpd)) & ALSA_w12$RD2W12 == 0 & ALSA_w12$RD3W12 == 0,na.rm=T),
  sum((ALSA_w12$h_cpd == 1 & !(is.na(ALSA_w12$RD2W12 & is.na(ALSA_w12$RD3W12)))) | ALSA_w12$RD2W12 == 1 | ALSA_w12$RD3W12 == 1,na.rm=T)
)
BeforeH <- c(X[1:2],length(ALSA_ds_w12$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","NA->999")
kable(C)

```



### Wave 13

Not found.


<!--
```{r summary, include=F, eval=F, echo=F}
kable(ALSA_ds[ALSA_ds$id %in% strange_id,], align = 'c', caption = 'Individuals with discrepancies')
```
-->

## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.

**R script:**

```{r summ}
ALSA_ds_w1$h_cpd <- labelled(ALSA_ds_w1$h_cpd, labels = cat_label)
label(ALSA_ds_w1$h_cpd) <- ds_label
ALSA_ds_w1$h_cpd_age <- labelled(ALSA_ds_w1$h_cpd_age, labels = cont_label)
label(ALSA_ds_w1$h_cpd_age) <- ds_label_age
ALSA_ds_w3$h_cpd <- labelled(ALSA_ds_w3$h_cpd, labels = cat_label)
label(ALSA_ds_w3$h_cpd) <- ds_label
ALSA_ds_w6$h_cpd <- labelled(ALSA_ds_w6$h_cpd, labels = cat_label)
label(ALSA_ds_w6$h_cpd) <- ds_label
ALSA_ds_w6$h_cpd_age <- labelled(ALSA_ds_w6$h_cpd_age, labels = cont_label)
label(ALSA_ds_w6$h_cpd_age) <- ds_label_age
ALSA_ds_w11$h_cpd <- labelled(ALSA_ds_w11$h_cpd, labels = cat_label)
label(ALSA_ds_w11$h_cpd) <- ds_label
ALSA_ds_w12$h_cpd <- labelled(ALSA_ds_w12$h_cpd, labels = cat_label)
label(ALSA_ds_w12$h_cpd) <- ds_label
ALSA_ds_w12$h_cpd_age <- labelled(ALSA_ds_w12$h_cpd_age, labels = cont_label)
label(ALSA_ds_w12$h_cpd_age) <- ds_label_age

ALSA_m_ds_w1 <- ALSA_ds_w1
ALSA_m_ds_w1$h_cpd <- car::recode(ALSA_m_ds_w1$h_cpd, "miss_values_vector=NA")
ALSA_m_ds_w3 <- ALSA_ds_w3
ALSA_m_ds_w3$h_cpd <- car::recode(ALSA_m_ds_w3$h_cpd, "miss_values_vector=NA")
ALSA_m_ds_w6 <- ALSA_ds_w6
ALSA_m_ds_w6$h_cpd <- car::recode(ALSA_m_ds_w6$h_cpd, "miss_values_vector=NA")
ALSA_m_ds_w11 <- ALSA_ds_w11
ALSA_m_ds_w11$h_cpd <- car::recode(ALSA_m_ds_w11$h_cpd, "miss_values_vector=NA")
ALSA_m_ds_w12 <- ALSA_ds_w12
ALSA_m_ds_w12$h_cpd <- car::recode(ALSA_m_ds_w12$h_cpd, "miss_values_vector=NA")

tt <-    frq(ALSA_ds_w1$h_cpd)[[1]][,c(1:2,4)]
tt[4] <- frq(ALSA_ds_w3$h_cpd)[[1]][,c(4)]
tt[5] <- frq(ALSA_ds_w6$h_cpd)[[1]][,c(4)]
tt[6] <- frq(ALSA_ds_w11$h_cpd)[[1]][,c(4)]
tt[7] <- frq(ALSA_ds_w12$h_cpd)[[1]][,c(4)]
tt[13,] <- c("n", "sample size", 
             length(ALSA_ds_w1$h_cpd), length(ALSA_ds_w3$h_cpd), length(ALSA_ds_w6$h_cpd),
             length(ALSA_ds_w11$h_cpd), length(ALSA_ds_w12$h_cpd)
             )
names(tt)<-c("val", "label", "w1", "w3", "w6", "w11", "w12")
kable(tt)

dbb <- merge(ALSA_m_ds_w1[,c("id","h_cpd")], ALSA_m_ds_w3[,c("id","h_cpd")], by="id", suffixes = c(".w1",".w3"), all=T)
dbb <- merge(dbb, ALSA_m_ds_w6[,c("id","h_cpd")], by="id", all=T)
dbb <- merge(dbb, ALSA_m_ds_w11[,c("id","h_cpd")], by="id", suffixes = c(".w6",".w11"), all=T)
dbb <- merge(dbb, ALSA_m_ds_w12[,c("id","h_cpd")], by="id", all=T)
names(dbb) <- c("id", "w1", "w3", "w6", "w11", "w12")
v.dbb <- paste(dbb[,2],dbb[,3],dbb[,4],dbb[,5],dbb[,6],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])
```



# Quality estimation

* We assume that if an individual answers it has chronic pulmonary disorders in one wave, it has for all the next waves. Individuals with discrepancies with respect to this criterium are specified at the end of each validation.
* There are individuals with different diagnostic years data across waves. We harmonize diagnostic age taking the first year they answer.
The harmonized variable contains information about "chronic bronchitis" and "emphysema"


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.ALSA <- list(w1 = ALSA_ds_w1, w3 = ALSA_ds_w3, w6 = ALSA_ds_w6, w11 = ALSA_ds_w11, w12 = ALSA_ds_w12)

for(index in seq_along(l.ALSA)){
  h_cpd <- l.ALSA[[index]]
  save(h_cpd, file = paste0(datafolder,names(l.ALSA)[index],"/h_cpd.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





