---
title: "Hypertension"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `h_hypertension`
* Variable label: `History of Hypertension`
* Variable description: `history of hypertension or high blood pressure`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | NOT High blood pressure or hypertension 
1        | High blood pressure or hypertension

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Short name: `h_hypertension_age`
* Variable label: `Age first diagnosed hypertension`
* Variable description: `The age first told had hypertension diagnosis`
* Domain: `Diseases`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "History of Hypertension"
ds_label_age <- "Age first diagnosed hypertension"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
cont_label <- cat_label[3:11]
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process



## Australia


### Wave 1


#### Study-specific variable description

| **Name** | `MORBID18` |`DIAGYR18`|`ybirth`|
|-|-|-|-|
| **Label** | `Hypertension` |`Year of diagnosis: Hypertension`|`Year of birth`|
| **Table name**  | `ALSA-Wave1` | `ALSA-Wave1` |`ybirth`|
| **Categories** | `0 = No`<br/>`1 = Yes` | `continuous` | `continuous` |
| **Missings** |  | `NA` |   |
| **Description** |  |  |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'ALSA_w1','ALSA.ALSA-Wave1',variables=list('MORBID18','DIAGYR18'), missings = T)
ALSA_w1 <- opal.execute(o,'ALSA_w1')
load(paste0(datafolder,"w1/ybirth.RData"))
ALSA_w1 <- left_join(ALSA_w1,ybirth, by="id")

```

```{r local w1, echo=F}

vbl <- ALSA_w1$MORBID18
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w1, aes(x=factor(MORBID18))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w1$DIAGYR18
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(ALSA_w1)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_w1, aes(DIAGYR18)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1925,1995)

vbl <- ALSA_w1$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(ALSA_w1)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_w1, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1885,1930)

```


#### Harmonisation algorithm

To compute `h_hypertension` from the study-specific variable it has to be recoded as follows:

* `keep up 0 into 0`
* `keep up 1 into 1`

To compute `h_hypertension_age` from the study-specific variable it has to be recoded as follows:

* `if h_hypertension == 1, h_hypertension_age = DIAGYR18 - ybirth`
* `if h_hypertension == 0, h_hypertension_age = 996`
* `otherwise into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
ALSA_ds_w1 <- tibble(id=ALSA_w1$id)
ALSA_ds_w1$h_hypertension <- car::recode(ALSA_w1$MORBID18, "NA = 999")

# Continuous variable harmonization
hypertension_age <- ALSA_w1$DIAGYR18[ALSA_ds_w1$h_hypertension == 1]-ALSA_w1$ybirth[ALSA_ds_w1$h_hypertension == 1]
ALSA_ds_w1$h_hypertension_age <- car::recode(ALSA_ds_w1$h_hypertension, "0 = 996; 1 = hypertension_age")
ALSA_ds_w1$h_hypertension_age <- car::recode(ALSA_ds_w1$h_hypertension_age,"NA=999")

# We build a global table in order to have updated the hypertension status of all the individuals through the different waves
ALSA_ds <- ALSA_ds_w1

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- ALSA_ds_w1$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w1, aes(x=factor(h_hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ALSA_ds_w1$h_hypertension_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w1, aes(h_hypertension_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(10,105)

```


#### Validation

```{r crosstabulation w1, echo=F}

continuous <- c(sum(ALSA_ds_w1$h_hypertension_age==996,na.rm=T),sum(ALSA_ds_w1$h_hypertension_age!=996,na.rm=T))
X <- table(ALSA_ds_w1$h_hypertension, useNA = "ifany")
dichotomous <- c(X[1],sum(X[2:3],na.rm=T))
C <- rbind(continuous,dichotomous)
colnames(C) <- c("0<-->996","1<-->(possibly missing) age of diagnostic")
kable(C,caption = "Continuous vs Dichotomous")

```



### Wave 2

Not found.




### Wave 3


#### Study-specific variable description

| **Name** | `W1CDN18` |
|-|-|
| **Label** | `HYPERTENSION` |
| **Table name**  | `ALSA-Wave3` |
| **Categories** | `1 = Yes`<br/>`2 = No` |
| **Missings** | `9`<br/>`NA` |
| **Description** |  |

```{r assign w3, echo=F}

opal.assign.table.tibble(o, 'ALSA_w3','ALSA.ALSA-Wave3',variables=list('W1CDN18'), missings = T)
ALSA_w3 <- opal.execute(o,'ALSA_w3')

```

```{r local w3, echo=F}

vbl <- ALSA_w3$W1CDN18
kable(Categorical_summary(vbl, missing_values = c(9))[3], caption = names(ALSA_w3)[2])
kable(Categorical_summary(vbl, missing_values = c(9))[1], caption = "Category")
ggplot(ALSA_w3, aes(x=factor(W1CDN18))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_hypertension` from the study-specific variable it has to be recoded as follows:

* `MORBID18 == 0 (or missings) and W1CDN18 == 2 into 0`
* `W1CDN18 ==1 or MORBID18 == 1 into 1`
* `otherwise into 999`

Age of diagnostic cannot be harmonized.

**R script:**

```{r harmo w3}

# We use the harmonized variable of wave 1 instead of the study-specific variables from all the previous waves
ALSA_w3 <- left_join(ALSA_w3, ALSA_ds, by = "id")

ALSA_ds_w3 <- tibble(id=ALSA_w3$id)
ALSA_ds_w3$h_hypertension <- rep(999,length(ALSA_ds_w3$id))
ALSA_ds_w3$h_hypertension[which(ALSA_w3$W1CDN18 == 2 & ((is.na(ALSA_w3$h_hypertension)) | ALSA_w3$h_hypertension != 1))] <- 0
ALSA_ds_w3$h_hypertension[which(ALSA_w3$W1CDN18 == 1 | ((!is.na(ALSA_w3$W1CDN18)) & ALSA_w3$h_hypertension == 1))] <- 1

# We update the hypertension status of the individuals in the global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- left_join(endtib,sttib,by="id")
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
ALSA_ds_prov <- ALSA_ds[,c(1,2)]
ALSA_ds_prov <- assign_merge(ALSA_ds_prov,ALSA_ds_w3,log_vec=(ALSA_ds_prov$id %in% ALSA_ds_w3$id),col_end_index = 2, col_st_index = 3)
ALSA_ds$h_hypertension <- ALSA_ds_prov$h_hypertension
rm(ALSA_ds_prov)

```


#### Statistics of the new harmonized variable

```{r descript w3, echo=F}

vbl <- ALSA_ds_w3$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w3, aes(x=factor(h_hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w3, echo=F, results='asis'}

AfterH <- table(ALSA_ds_w3$h_hypertension)
X <- c(
  sum(ALSA_w3$W1CDN18 == 2 & ((is.na(ALSA_w3$h_hypertension)) | ALSA_w3$h_hypertension != 1),na.rm=T),
  sum(ALSA_w3$W1CDN18 == 1 | ((!is.na(ALSA_w3$W1CDN18)) & ALSA_w3$h_hypertension == 1),na.rm=T)
)
BeforeH <- c(X[2],length(ALSA_w3$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("some 1->1","NA->999")
kable(C)

# Checking
cat("All the individuals of this wave which are no missing have answered they have hypertension in the first wave")
kable(frq(ALSA_w3$h_hypertension[!is.na(ALSA_w3$W1CDN18)]), align = 'c')

```

### Wave 4

Not found.

### Wave 5

Not found.



### Wave 6


#### Study-specific variable description

| **Name** | `CDN29_W6` |`DIA29_W6`|`ybirth`|
|-|-|-|-|
| **Label** | `Hypertension or high blood pressure` |`year told of hypertension or high blood pressure`|`Year of birth`|
| **Table name**  | `ALSA-Wave6` | `ALSA-Wave6` |`ybirth`|
| **Categories** | `0 = no`<br/>`1 = yes` |`continuous`|`continuous`|
| **Missings** | `NA` |`NA`|  |
| **Description** |  |  |  |

```{r assign w6, echo=F}

opal.assign.table.tibble(o, 'ALSA_w6','ALSA.ALSA-Wave6',variables=list('CDN29_W6','DIA29_W6'), missings = T)
ALSA_w6 <- opal.execute(o,'ALSA_w6')
ALSA_w6$DIA29_W6[which(ALSA_w6$DIA29_W6=="1940s")] <- "1945"
ALSA_w6$DIA29_W6[which(ALSA_w6$DIA29_W6=="1950s")] <- "1955"
ALSA_w6$DIA29_W6[which(ALSA_w6$DIA29_W6=="1960s")] <- "1965"
ALSA_w6$DIA29_W6[which(ALSA_w6$DIA29_W6=="1980s")] <- "1985"
ALSA_w6$DIA29_W6[which(ALSA_w6$DIA29_W6=="1990s")] <- "1995"
ALSA_w6$DIA29_W6 <- as.numeric(ALSA_w6$DIA29_W6)
load(paste0(datafolder,"w6/ybirth.RData"))
ALSA_w6 <- left_join(ALSA_w6,ybirth, by="id")
```

```{r local w6, echo=F}

vbl <- ALSA_w6$CDN29_W6
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w6)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w6, aes(x=factor(CDN29_W6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w6$DIA29_W6
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(ALSA_w6)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_w6, aes(DIA29_W6)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1940,2000)

vbl <- ALSA_w6$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(ALSA_w6)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_w6, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1895,1930)

```


#### Harmonisation algorithm

To compute `h_hypertension` from the study-specific variable it has to be recoded as follows:

* `W1CDN18 == 2 and MORBID18 == 0 (or missings) and CDN29_W6 == 0 into 0`
* `CDN29_W6 == 1 or W1CDN18 == 1 or MORBID18 == 1 into 1`
* `otherwise into 999`

To compute `h_hypertension_age` from the study-specific variable it has to be recoded as follows:

* `if h_hypertension == 1 in w6 and previously, h_hypertension_age = as before`
* `if h_hypertension == 1 in w6 and 0 previously h_hypertension_age = DIA29_W6 - ybirth`
* `if h_hypertension == 0, h_hypertension_age = 996`
* `otherwise into 999`

The data of year of diagnostic '19' is overwritten by ages of diagnostic from the first wave.

**R script:**

```{r harmo w6}

# We use the harmonized variable of previous waves instead of the study-specific variables
ALSA_w6 <- left_join(ALSA_w6, ALSA_ds, by = "id")

ALSA_ds_w6 <- tibble(id=ALSA_w6$id)
ALSA_ds_w6$h_hypertension <- rep(999,length(ALSA_ds_w6$id))
ALSA_ds_w6$h_hypertension[which(ALSA_w6$CDN29_W6 == 0 & (ALSA_w6$h_hypertension != 1 | is.na(ALSA_w6$h_hypertension)))] <- 0
ALSA_ds_w6$h_hypertension[which(ALSA_w6$CDN29_W6 == 1 | ((!is.na(ALSA_w6$CDN29_W6)) & ALSA_w6$h_hypertension == 1))] <- 1

# We update the hypertension status of the individuals in the global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- left_join(endtib,sttib,by="id")
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
ALSA_ds_prov <- ALSA_ds[,c(1,2)]
ALSA_ds_prov <- assign_merge(ALSA_ds_prov,ALSA_ds_w6,log_vec=(ALSA_ds_prov$id %in% ALSA_ds_w6$id),col_end_index = 2, col_st_index = 3)
ALSA_ds$h_hypertension <- ALSA_ds_prov$h_hypertension
rm(ALSA_ds_prov)

# Continuous variable harmonization
# Obtained ages following diagnosis dates answered in wave 6
hypertension_age_w6 <- ALSA_w6$DIA29_W6[which(ALSA_ds_w6$h_hypertension == 1)]-ALSA_w6$ybirth[which(ALSA_ds_w6$h_hypertension == 1)]
hypertension_age_w6 <- car::recode(hypertension_age_w6,"NA=999")
ALSA_ds_w6$h_hypertension_age <- car::recode(ALSA_ds_w6$h_hypertension, "0 = 996; 1 = hypertension_age_w6; miss_values_vector = 999")
# Obtained ages following diagnosis dates answered in wave 1
ALSA_ds_w6$h_hypertension_age[which(ALSA_ds_w6$h_hypertension==1 & !is.na(ALSA_w6$h_hypertension_age) & !(ALSA_w6$h_hypertension_age %in% miss_values_vector))] <- ALSA_w6$h_hypertension_age[which(ALSA_ds_w6$h_hypertension==1 & !is.na(ALSA_w6$h_hypertension_age) & !(ALSA_w6$h_hypertension_age %in% miss_values_vector))]

ALSA_ds$h_hypertension_age[ALSA_ds$id %in% ALSA_ds_w6$id] <- ALSA_ds_w6$h_hypertension_age

```


#### Statistics of the new harmonized variable

```{r descript w6, echo=F}

vbl <- ALSA_ds_w6$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w6, aes(x=factor(h_hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ALSA_ds_w6$h_hypertension_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w6, aes(h_hypertension_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(10,95)

```


#### Validation

```{r crosstabulation w6, echo=F, results='asis'}

ALSA_w6$age_w6 <- ALSA_w6$DIA29_W6-ALSA_w6$ybirth
kable(ALSA_w6[which(!is.na(ALSA_w6$DIA29_W6) & !ALSA_w6$h_hypertension_age %in% miss_values_vector & ALSA_w6$h_hypertension_age != ALSA_w6$age_w6 & ALSA_w6$age_w6>0),],align = 'c',caption = 'There are individuals which answer different year of diagnostic in waves 1 and 6. We harmonize the age of diagnostic with the first data')

AfterH <- table(ALSA_ds_w6$h_hypertension)
X <- c(
  sum(ALSA_w6$CDN29_W6 == 0 & (ALSA_w6$h_hypertension != 1 | is.na(ALSA_w6$h_hypertension)),na.rm=T),
  sum(ALSA_w6$CDN29_W6 == 1 | ((!is.na(ALSA_w6$CDN29_W6)) & ALSA_w6$h_hypertension == 1),na.rm=T)
)
BeforeH <- c(X[2],length(ALSA_w6$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("some 1->1","NA->999")
kable(C)

```



### Wave 7

Not found.


### Wave 8

Not found.



### Wave 9

Not found.



### Wave 10

Not found.



### Wave 11


#### Study-specific variable description

| **Name** | `HBPW11` |
|-|-|
| **Label** | `High Blood pressure` |
| **Table name**  | `ALSA-Wave11` |
| **Categories** | `0 = No`<br/>`1 = Yes` |
| **Description** |  |

```{r assign w11, echo=F}

opal.assign.table.tibble(o, 'ALSA_w11','ALSA.ALSA-Wave11',variables=list('HBPW11'), missings = T)
ALSA_w11 <- opal.execute(o,'ALSA_w11')

```

```{r local w11, echo=F}

vbl <- ALSA_w11$HBPW11
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w11)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w11, aes(x=factor(HBPW11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_hypertension` from the study-specific variable it has to be recoded as follows:

* `previous waves study-specific variables != 1 and HBPW11 == 0 into 0`
* `HBPW11 ==1 or some previous waves study-specific variable == 1 into 1`
* `otherwise into 999`

Age of diagnostic cannot be harmonized.

**R script:**

```{r harmo w11}

# We use the harmonized variable of previous waves instead of the study-specific variables
ALSA_w11 <- left_join(ALSA_w11, ALSA_ds, by = "id")

ALSA_ds_w11 <- tibble(id=ALSA_w11$id)
ALSA_ds_w11$h_hypertension <- rep(999,length(ALSA_ds_w11$id))
ALSA_ds_w11$h_hypertension[which(ALSA_w11$HBPW11 == 0 & ((is.na(ALSA_w11$h_hypertension)) |  ALSA_w11$h_hypertension != 1))] <- 0
ALSA_ds_w11$h_hypertension[which(ALSA_w11$HBPW11 == 1 | ((!is.na(ALSA_w11$HBPW11)) & ALSA_w11$h_hypertension == 1))] <- 1

# We update the hypertension status of the individuals in the global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- left_join(endtib,sttib,by="id")
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
ALSA_ds_prov <- ALSA_ds[,c(1,2)]
ALSA_ds_prov <- assign_merge(ALSA_ds_prov,ALSA_ds_w11,log_vec=(ALSA_ds_prov$id %in% ALSA_ds_w11$id),col_end_index = 2, col_st_index = 3)
ALSA_ds$h_hypertension <- ALSA_ds_prov$h_hypertension
rm(ALSA_ds_prov)

```


#### Statistics of the new harmonized variable

```{r descript w11, echo=F}

vbl <- ALSA_ds_w11$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w11, aes(x=factor(h_hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w11, echo=F, results='asis'}

AfterH <- table(ALSA_ds_w11$h_hypertension)
X <- c(
  sum(ALSA_w11$HBPW11 == 0 & ((is.na(ALSA_w11$h_hypertension)) |  ALSA_w11$h_hypertension != 1),na.rm=T),
  sum(ALSA_w11$HBPW11 == 1 | ((!is.na(ALSA_w11$HBPW11)) & ALSA_w11$h_hypertension == 1),na.rm=T)
)
BeforeH <- c(X[1:2])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1")
kable(C)

cat("There are 11 individuals who answered in previous waves that they were diagnosed to have hypertension and in the eleventh wave that they were not told to have it. We harmonize them as having hypertension.")
kable(frq(ALSA_w11$HBPW11[which(ALSA_w11$h_hypertension==1)]), align = 'c')
kable(ALSA_w11[ALSA_w11$id %in% ALSA_w11$id[ALSA_w11$HBPW11==0 & ALSA_w11$h_hypertension==1],], align = 'c')
#strange_id <- c(strange_id,ALSA_w11$id[ALSA_w11$id %in% ALSA_w11$id[ALSA_w11$HBPW11==0 & ALSA_w11$h_hypertension==1]])

```



### Wave 12


#### Study-specific variable description

| **Name** | `HBPW12` |`age`|
|-|-|-|
| **Label** | `High Blood pressure` |`age`|
| **Table name**  | `ALSA-Wave12` |`age`|
| **Categories** |  `0 = No`<br/>`1 = Yes` |`continuous`|
| **Description** |  |  |

```{r assign w12, echo=F}

opal.assign.table.tibble(o, 'ALSA_w12','ALSA.ALSA-Wave12',variables=list('HBPW12'), missings = T)
ALSA_w12 <- opal.execute(o,'ALSA_w12')
load(paste0(datafolder,"w12/age.RData"))
ALSA_w12 <- left_join(ALSA_w12,age, by="id")

```

```{r local w12, echo=F}

vbl <- ALSA_w12$HBPW12
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w12)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w12, aes(x=factor(HBPW12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w12$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(ALSA_w11)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_w12, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(85,105)

```


#### Harmonisation algorithm

To compute `h_hypertension` from the study-specific variable it has to be recoded as follows:

* `previous waves study-specific variables != 1 and HBPW12 == 0 into 0`
* `HBPW12==1 or some previous waves study-specific variable == 1 into 1`
* `otherwise into 999`

To compute `h_hypertension_age` from the study-specific variable it has to be recoded as follows:

* `if h_hypertension == 1 in w12 and 0 in w11, h_hypertension_age = age-(year of interview w12-year of interview w11)/2. Since year of interview w12 == 2013 and year of interview w11 == 2010, the mid difference is 1.5. Since the age is usually given as an integer we would apply the floor, but all together is the same that h_hypertension_age = age-2`
* `if h_hypertension == 1 in w12 and previously, h_hypertension_age = age obtained from previous waves`
* `if h_hypertension == 0, h_hypertension_age = 996`
* `h_hypertension == missing into 999`

**R script:**

```{r harmo w12}

# We use the harmonized variable of previous waves instead of the study-specific variables
ALSA_w12 <- left_join(ALSA_w12, ALSA_ds, by = "id")

ALSA_ds_w12 <- tibble(id=ALSA_w12$id)
ALSA_ds_w12$h_hypertension <- rep(999,length(ALSA_ds_w12$id))
ALSA_ds_w12$h_hypertension[which(ALSA_w12$HBPW12 == 0 & ((is.na(ALSA_w12$h_hypertension)) | ALSA_w12$h_hypertension != 1))] <- 0
ALSA_ds_w12$h_hypertension[which(ALSA_w12$HBPW12 == 1 | ((!is.na(ALSA_w12$HBPW12)) & ALSA_w12$h_hypertension == 1))] <- 1

# We update the hypertension status of the individuals in the global table
rm(ALSA_ds)

# Continuous variable harmonization
ALSA_ds_w12$h_hypertension_age <- rep(999,length(ALSA_ds_w12$id))

ALSA_w12 <- left_join(ALSA_w12, ALSA_ds_w11, by = "id", suffix =c("","_w11"))
# Obtained ages following diagnosis dates answered in wave 12
hypertension_age_w12 <- ALSA_w12$age[ALSA_ds_w12$h_hypertension == 1]-2
ALSA_ds_w12$h_hypertension_age[which(ALSA_ds_w12$h_hypertension == 1 & ALSA_w12$h_hypertension_w11 == 0)] <- ALSA_w12$age[which(ALSA_ds_w12$h_hypertension == 1 & ALSA_w12$h_hypertension_w11 == 0)]-2
ALSA_ds_w12$h_hypertension_age[which(ALSA_ds_w12$h_hypertension == 0)] <- 996
ALSA_ds_w12$h_hypertension_age[which(ALSA_ds_w12$h_hypertension == 1 & !is.na(ALSA_w12$h_hypertension_age) & !ALSA_w12$h_hypertension_age %in% miss_values_vector)] <- ALSA_w12$h_hypertension_age[which(ALSA_ds_w12$h_hypertension == 1 & !is.na(ALSA_w12$h_hypertension_age) & !ALSA_w12$h_hypertension_age %in% miss_values_vector)]

```


#### Statistics of the new harmonized variable

```{r descript w12, echo=F}

vbl <- ALSA_ds_w12$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w12, aes(x=factor(h_hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ALSA_ds_w12$h_hypertension_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w12, aes(h_hypertension_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(20,100)

```


#### Validation

```{r crosstabulation w12, echo=F, results='asis'}

AfterH <- table(ALSA_ds_w12$h_hypertension)
X <- c(
  sum(ALSA_w12$HBPW12 == 0 & ((is.na(ALSA_w12$h_hypertension)) | ALSA_w12$h_hypertension != 1),na.rm=T),
  sum(ALSA_w12$HBPW12 == 1 | ((!is.na(ALSA_w12$HBPW12)) & ALSA_w12$h_hypertension == 1),na.rm=T)
)
BeforeH <- c(X[1:2])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1")
kable(C)

cat("There are 14 individuals who answered in previous waves that they were diagnosed to have hypertension and in the twelfth wave that they were not told to have it. We harmonize them as having hypertension.")
kable(frq(ALSA_w12$h_hypertension[!is.na(ALSA_w12$HBPW12) & ALSA_w12$HBPW12==0]), align = 'c')
kable(ALSA_w12[ALSA_w12$id %in% ALSA_w12$id[ALSA_w12$HBPW12==0 & ALSA_w12$h_hypertension==1],], align = 'c')

```



### Wave 13

Not found.


<!--
```{r summary, include=F, eval=F, echo=F}
kable(ALSA_ds[ALSA_ds$id %in% strange_id,], align = 'c', caption = 'Individuals with discrepancies')
```
-->

## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.

**R script:**

```{r summ}
ALSA_ds_w1$h_hypertension <- labelled(ALSA_ds_w1$h_hypertension, labels = cat_label)
label(ALSA_ds_w1$h_hypertension) <- ds_label
ALSA_ds_w1$h_hypertension_age <- labelled(ALSA_ds_w1$h_hypertension_age, labels = cont_label)
label(ALSA_ds_w1$h_hypertension_age) <- ds_label_age
ALSA_ds_w3$h_hypertension <- labelled(ALSA_ds_w3$h_hypertension, labels = cat_label)
label(ALSA_ds_w3$h_hypertension) <- ds_label
ALSA_ds_w6$h_hypertension <- labelled(ALSA_ds_w6$h_hypertension, labels = cat_label)
label(ALSA_ds_w6$h_hypertension) <- ds_label
ALSA_ds_w6$h_hypertension_age <- labelled(ALSA_ds_w6$h_hypertension_age, labels = cont_label)
label(ALSA_ds_w6$h_hypertension_age) <- ds_label_age
ALSA_ds_w11$h_hypertension <- labelled(ALSA_ds_w11$h_hypertension, labels = cat_label)
label(ALSA_ds_w11$h_hypertension) <- ds_label
ALSA_ds_w12$h_hypertension <- labelled(ALSA_ds_w12$h_hypertension, labels = cat_label)
label(ALSA_ds_w12$h_hypertension) <- ds_label
ALSA_ds_w12$h_hypertension_age <- labelled(ALSA_ds_w12$h_hypertension_age, labels = cont_label)
label(ALSA_ds_w12$h_hypertension_age) <- ds_label_age

ALSA_m_ds_w1 <- ALSA_ds_w1
ALSA_m_ds_w1$h_hypertension <- car::recode(ALSA_m_ds_w1$h_hypertension, "miss_values_vector=NA")
ALSA_m_ds_w3 <- ALSA_ds_w3
ALSA_m_ds_w3$h_hypertension <- car::recode(ALSA_m_ds_w3$h_hypertension, "miss_values_vector=NA")
ALSA_m_ds_w6 <- ALSA_ds_w6
ALSA_m_ds_w6$h_hypertension <- car::recode(ALSA_m_ds_w6$h_hypertension, "miss_values_vector=NA")
ALSA_m_ds_w11 <- ALSA_ds_w11
ALSA_m_ds_w11$h_hypertension <- car::recode(ALSA_m_ds_w11$h_hypertension, "miss_values_vector=NA")
ALSA_m_ds_w12 <- ALSA_ds_w12
ALSA_m_ds_w12$h_hypertension <- car::recode(ALSA_m_ds_w12$h_hypertension, "miss_values_vector=NA")

tt <-    frq(ALSA_ds_w1$h_hypertension)[[1]][,c(1:2,4)]
tt[4] <- frq(ALSA_ds_w3$h_hypertension)[[1]][,c(4)]
tt[5] <- frq(ALSA_ds_w6$h_hypertension)[[1]][,c(4)]
tt[6] <- frq(ALSA_ds_w11$h_hypertension)[[1]][,c(4)]
tt[7] <- frq(ALSA_ds_w12$h_hypertension)[[1]][,c(4)]
tt[13,] <- c("n", "sample size", 
             length(ALSA_ds_w1$h_hypertension), length(ALSA_ds_w3$h_hypertension), length(ALSA_ds_w6$h_hypertension),
             length(ALSA_ds_w11$h_hypertension), length(ALSA_ds_w12$h_hypertension)
             )
names(tt)<-c("val", "label", "w1", "w3", "w6", "w11", "w12")
kable(tt)

dbb <- merge(ALSA_m_ds_w1[,c("id","h_hypertension")], ALSA_m_ds_w3[,c("id","h_hypertension")], by="id", suffixes = c(".w1",".w3"), all=T)
dbb <- merge(dbb, ALSA_m_ds_w6[,c("id","h_hypertension")], by="id", all=T)
dbb <- merge(dbb, ALSA_m_ds_w11[,c("id","h_hypertension")], by="id", suffixes = c(".w6",".w11"), all=T)
dbb <- merge(dbb, ALSA_m_ds_w12[,c("id","h_hypertension")], by="id", all=T)
names(dbb) <- c("id", "w1", "w3", "w6", "w11", "w12")
v.dbb <- paste(dbb[,2],dbb[,3],dbb[,4],dbb[,5],dbb[,6],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])
```



# Quality estimation

* We assume that if an individual answers it has hypertension in one wave, it has hypertension for all the next waves. Individuals with discrepancies with respect to this criterium are specified at the end of each validation.
* There are individuals with different diagnostic years data across waves. We harmonize diagnostic age taking the first year they answer.


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.ALSA <- list(w1 = ALSA_ds_w1, w3 = ALSA_ds_w3, w6 = ALSA_ds_w6, w11 = ALSA_ds_w11, w12 = ALSA_ds_w12)

for(index in seq_along(l.ALSA)){
  h_hypertension <- l.ALSA[[index]]
  save(h_hypertension, file = paste0(datafolder,names(l.ALSA)[index],"/h_hypertension.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





