---
title: "Joint disorders"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/joint_disordersDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/joint_disordersDS.R')
```




# Data process



## Australia


### Wave 1


#### Study-specific variable description

| **Name** | `MORBID2` |`DIAGYR2`|`ybirth`|
|-|-|-|-|
| **Label** | `Arthritis` |`Year of diagnosis: Arthritis`|`Year of birth`|
| **Table name**  | `ALSA-Wave1` | `ALSA-Wave1` |`ybirth`|
| **Categories** | `0 = No`<br/>`1 = Yes` | `continuous` | `continuous` |
| **Missings** |  | `NA` |   |
| **Description** |  |  |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'ALSA_w1','ALSA.ALSA-Wave1',variables=list('MORBID2','DIAGYR2'), missings = T)
ALSA_w1 <- opal.execute(o,'ALSA_w1')
load(paste0(datafolder,"w1/ybirth.RData"))
ALSA_w1 <- left_join(ALSA_w1,ybirth, by="id")

```

```{r local w1, echo=F}

vbl <- ALSA_w1$MORBID2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w1, aes(x=factor(MORBID2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w1$DIAGYR2
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(ALSA_w1)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_w1, aes(DIAGYR2)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1910,1995)

vbl <- ALSA_w1$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(ALSA_w1)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_w1, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1885,1930)

```


#### Harmonisation algorithm

To compute `h_joint_disorders` from the study-specific variable it has to be recoded as follows:

* `keep up 0 into 0`
* `keep up 1 into 1`

To compute `h_joint_disorders_age` from the study-specific variable it has to be recoded as follows:

* `if h_joint_disorders == 1, h_joint_disorders_age = DIAGYR2 - ybirth`
* `if h_joint_disorders == 0, h_joint_disorders_age = 996`
* `otherwise into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
ALSA_ds_w1 <- tibble(id=ALSA_w1$id)
ALSA_ds_w1$h_joint_disorders <- car::recode(ALSA_w1$MORBID2, "NA = 999")

# Continuous variable harmonization
joint_disorders_age <- ALSA_w1$DIAGYR2[which(ALSA_ds_w1$h_joint_disorders == 1)]-ALSA_w1$ybirth[which(ALSA_ds_w1$h_joint_disorders == 1)]
ALSA_ds_w1$h_joint_disorders_age <- car::recode(ALSA_ds_w1$h_joint_disorders, "0 = 996; 1 = joint_disorders_age")
ALSA_ds_w1$h_joint_disorders_age <- car::recode(ALSA_ds_w1$h_joint_disorders_age,"NA=999")

# We build a global table in order to have updated the status of all the individuals through the different waves
ALSA_ds <- ALSA_ds_w1

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- ALSA_ds_w1$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w1, aes(x=factor(h_joint_disorders))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ALSA_ds_w1$h_joint_disorders_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w1, aes(h_joint_disorders_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(5,105)

```


#### Validation

```{r crosstabulation w1, echo=F}

continuous <- c(sum(ALSA_ds_w1$h_joint_disorders_age==996,na.rm=T),sum(ALSA_ds_w1$h_joint_disorders_age!=996,na.rm=T))
X <- table(ALSA_ds_w1$h_joint_disorders, useNA = "ifany")
dichotomous <- c(X[1],sum(X[2:3],na.rm=T))
C <- rbind(continuous,dichotomous)
colnames(C) <- c("0<-->996","1<-->(possibly missing) age of diagnostic")
kable(C,caption = "Continuous vs Dichotomous")

```



### Wave 2

Not found.




### Wave 3


#### Study-specific variable description

| **Name** | `W1CDN2` |
|-|-|
| **Label** | `ARTHRITIS` |
| **Table name**  | `ALSA-Wave3` |
| **Categories** | `1 = Yes`<br/>`2 = No` |
| **Missings** | `9`<br/>`NA` |
| **Description** |  |

```{r assign w3, echo=F}

opal.assign.table.tibble(o, 'ALSA_w3','ALSA.ALSA-Wave3',variables=list('W1CDN2'), missings = T)
ALSA_w3 <- opal.execute(o,'ALSA_w3')

```

```{r local w3, echo=F}

vbl <- ALSA_w3$W1CDN2
kable(Categorical_summary(vbl, missing_values = c(9))[3], caption = names(ALSA_w3)[2])
kable(Categorical_summary(vbl, missing_values = c(9))[1], caption = "Category")
ggplot(ALSA_w3, aes(x=factor(W1CDN2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_joint_disorders` from the study-specific variable it has to be recoded as follows:

* `MORBID2 == 0 (or missings) and W1CDN2 == 2 into 0`
* `W1CDN2 ==1 or MORBID2 == 1 into 1`
* `otherwise into 999`

Age of diagnostic cannot be harmonized.

**R script:**

```{r harmo w3}

# We use the harmonized variable of wave 1 instead of the study-specific variables from all the previous waves
ALSA_w3 <- left_join(ALSA_w3, ALSA_ds, by = "id")

ALSA_ds_w3 <- tibble(id=ALSA_w3$id)
ALSA_ds_w3$h_joint_disorders <- rep(999,length(ALSA_ds_w3$id))
ALSA_ds_w3$h_joint_disorders[which(ALSA_w3$W1CDN2 == 2 & ((is.na(ALSA_w3$h_joint_disorders)) | ALSA_w3$h_joint_disorders != 1))] <- 0
ALSA_ds_w3$h_joint_disorders[which(ALSA_w3$W1CDN2 == 1 | ((!is.na(ALSA_w3$W1CDN2)) & ALSA_w3$h_joint_disorders == 1))] <- 1

# We update the status of the individuals in the global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- left_join(endtib,sttib,by="id")
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
ALSA_ds_prov <- ALSA_ds[,c(1,2)]
ALSA_ds_prov <- assign_merge(ALSA_ds_prov,ALSA_ds_w3,log_vec=(ALSA_ds_prov$id %in% ALSA_ds_w3$id),col_end_index = 2, col_st_index = 3)
ALSA_ds$h_joint_disorders <- ALSA_ds_prov$h_joint_disorders
rm(ALSA_ds_prov)

```


#### Statistics of the new harmonized variable

```{r descript w3, echo=F}

vbl <- ALSA_ds_w3$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w3, aes(x=factor(h_joint_disorders))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w3, echo=F, results='asis'}

AfterH <- table(ALSA_ds_w3$h_joint_disorders)
X <- c(
  sum(ALSA_w3$W1CDN2 == 2 & ((is.na(ALSA_w3$h_joint_disorders)) | ALSA_w3$h_joint_disorders != 1),na.rm=T),
  sum(ALSA_w3$W1CDN2 == 1 | ((!is.na(ALSA_w3$W1CDN2)) & ALSA_w3$h_joint_disorders == 1),na.rm=T)
)
BeforeH <- c(X[2],length(ALSA_w3$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("some 1->1","NA->999")
kable(C)

# Checking
cat("All the individuals of this wave which are no missing have answered they have joint disorders in the first wave")
kable(frq(ALSA_w3$h_joint_disorders[!is.na(ALSA_w3$W1CDN2)]), align = 'c')

```

### Wave 4

Not found.

### Wave 5

Not found.



### Wave 6


#### Study-specific variable description

| **Name** | `CDN3_W6` |`DIA3_W6`|`ybirth`|
|-|-|-|-|
| **Label** | `Arthritis` |`year told of: Arthritis`|`Year of birth`|
| **Table name**  | `ALSA-Wave6` | `ALSA-Wave6` |`ybirth`|
| **Categories** | `0 = no`<br/>`1 = yes` |`continuous`|`continuous`|
| **Missings** | `NA` |`NA`|  |
| **Description** |  |  |  |

```{r assign w6, echo=F}

opal.assign.table.tibble(o, 'ALSA_w6','ALSA.ALSA-Wave6',variables=list('CDN3_W6','DIA3_W6'), missings = T)
ALSA_w6 <- opal.execute(o,'ALSA_w6')
ALSA_w6$DIA3_W6[which(ALSA_w6$DIA3_W6=="1970s")] <- "1975"
ALSA_w6$DIA3_W6[which(ALSA_w6$DIA3_W6=="1980s")] <- "1985"
ALSA_w6$DIA3_W6 <- as.numeric(ALSA_w6$DIA3_W6)
load(paste0(datafolder,"w6/ybirth.RData"))
ALSA_w6 <- left_join(ALSA_w6,ybirth, by="id")
```

```{r local w6, echo=F}

vbl <- ALSA_w6$CDN3_W6
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w6)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w6, aes(x=factor(CDN3_W6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w6$DIA3_W6
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(ALSA_w6)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_w6, aes(DIA3_W6)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1935,2005)

vbl <- ALSA_w6$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(ALSA_w6)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_w6, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1895,1930)

```


#### Harmonisation algorithm

To compute `h_joint_disorders` from the study-specific variable it has to be recoded as follows:

* `W1CDN2 == 2 and MORBID2 == 0 (or missings) and CDN3_W6 == 0 into 0`
* `CDN3_W6 == 1 or W1CDN2 == 1 or MORBID2 == 1 into 1`
* `otherwise into 999`

To compute `h_joint_disorders_age` from the study-specific variable it has to be recoded as follows:

* `if h_joint_disorders == 1 in w6 and previously, h_joint_disorders_age = as before`
* `if h_joint_disorders == 1 in w6 and 0 previously h_joint_disorders_age = DIA3_W6 - ybirth`
* `if h_joint_disorders == 0, h_joint_disorders_age = 996`
* `DIA3_W6 == 197 into 991`
* `otherwise into 999`

The data of year of diagnostic '19' and '15' is overwritten by ages of diagnostic from the first wave.

**R script:**

```{r harmo w6}

# We use the harmonized variable of previous waves instead of the study-specific variables
ALSA_w6 <- left_join(ALSA_w6, ALSA_ds, by = "id")

ALSA_ds_w6 <- tibble(id=ALSA_w6$id)
ALSA_ds_w6$h_joint_disorders <- rep(999,length(ALSA_ds_w6$id))
ALSA_ds_w6$h_joint_disorders[which(ALSA_w6$CDN3_W6 == 0 & (ALSA_w6$h_joint_disorders != 1 | is.na(ALSA_w6$h_joint_disorders)))] <- 0
ALSA_ds_w6$h_joint_disorders[which(ALSA_w6$CDN3_W6 == 1 | ((!is.na(ALSA_w6$CDN3_W6)) & ALSA_w6$h_joint_disorders == 1))] <- 1

# We update the status of the individuals in the global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- left_join(endtib,sttib,by="id")
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
ALSA_ds_prov <- ALSA_ds[,c(1,2)]
ALSA_ds_prov <- assign_merge(ALSA_ds_prov,ALSA_ds_w6,log_vec=(ALSA_ds_prov$id %in% ALSA_ds_w6$id),col_end_index = 2, col_st_index = 3)
ALSA_ds$h_joint_disorders <- ALSA_ds_prov$h_joint_disorders
rm(ALSA_ds_prov)

# Continuous variable harmonization
# Obtained ages following diagnosis dates answered in wave 6
joint_disorders_age_w6 <- ALSA_w6$DIA3_W6[which(ALSA_ds_w6$h_joint_disorders == 1)]-ALSA_w6$ybirth[which(ALSA_ds_w6$h_joint_disorders == 1)]
joint_disorders_age_w6 <- car::recode(joint_disorders_age_w6,"NA=999")
ALSA_ds_w6$h_joint_disorders_age <- car::recode(ALSA_ds_w6$h_joint_disorders, "0 = 996; 1 = joint_disorders_age_w6; miss_values_vector = 999")
# Obtained ages following diagnosis dates answered in wave 1
ALSA_ds_w6$h_joint_disorders_age[which(ALSA_ds_w6$h_joint_disorders==1 & !is.na(ALSA_w6$h_joint_disorders_age) & !(ALSA_w6$h_joint_disorders_age %in% miss_values_vector))] <- ALSA_w6$h_joint_disorders_age[which(ALSA_ds_w6$h_joint_disorders==1 & !is.na(ALSA_w6$h_joint_disorders_age) & !(ALSA_w6$h_joint_disorders_age %in% miss_values_vector))]

ALSA_ds_w6$h_joint_disorders_age[which(ALSA_w6$DIA3_W6==197)] <- 991

ALSA_ds$h_joint_disorders_age[which(ALSA_ds$id %in% ALSA_ds_w6$id)] <- ALSA_ds_w6$h_joint_disorders_age

```


#### Statistics of the new harmonized variable

```{r descript w6, echo=F}

vbl <- ALSA_ds_w6$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w6, aes(x=factor(h_joint_disorders))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ALSA_ds_w6$h_joint_disorders_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w6, aes(h_joint_disorders_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(10,95)

```


#### Validation

```{r crosstabulation w6, echo=F, results='asis'}

ALSA_w6$age_w6 <- ALSA_w6$DIA3_W6-ALSA_w6$ybirth
kable(ALSA_w6[which(!is.na(ALSA_w6$DIA3_W6) & !ALSA_w6$h_joint_disorders_age %in% miss_values_vector & ALSA_w6$h_joint_disorders_age != ALSA_w6$age_w6 & ALSA_w6$age_w6>0),],align = 'c',caption = 'There are individuals which answer different year of diagnostic in waves 1 and 6. We harmonize the age of diagnostic with the first data')

AfterH <- table(ALSA_ds_w6$h_joint_disorders)
X <- c(
  sum(ALSA_w6$CDN3_W6 == 0 & (ALSA_w6$h_joint_disorders != 1 | is.na(ALSA_w6$h_joint_disorders)),na.rm=T),
  sum(ALSA_w6$CDN3_W6 == 1 | ((!is.na(ALSA_w6$CDN3_W6)) & ALSA_w6$h_joint_disorders == 1),na.rm=T)
)
BeforeH <- c(X[2],length(ALSA_w6$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("some 1->1","NA->999")
kable(C)

```



### Wave 7



#### Study-specific variable description

| **Name** | `arthriw7` |`age`|`yintw (w6)`|`yintw (w7)`|
|-|-|-|-|-|
| **Label** | `What form of arthritis do you have` |`age`|`year of interview`|`year of interview`|
| **Table name**  | `ALSA-Wave7` | `age` |`yintw`|`yintw`|
| **Categories** | `1 = Rheumatism or rheumatic`<br/>`2 = Rheumatoid arthritis`<br/>`3 = Osteoarthritis`<br/>`4 = Other form, SPECIFY BELOW`<br/>`9 = No arthritis` |`continuous`|`continuous`|
| **Missings** | `0 = Not Answered`<br/>`NA` |  |  |  |
| **Description** |  |  |  |  |

```{r assign w7, echo=F}

opal.assign.table.tibble(o, 'ALSA_w7','ALSA.ALSA-Wave7',variables=list('arthriw7'), missings = T)
ALSA_w7 <- opal.execute(o,'ALSA_w7')
load(paste0(datafolder,"w7/age.RData"))
ALSA_w7 <- left_join(ALSA_w7,age, by="id")
rm(age)
load(paste0(datafolder,"w6/yintw.RData"))
ALSA_w7 <- left_join(ALSA_w7,yintw, by="id")
names(ALSA_w7)[4] <- "yintw_w6"
rm(yintw)
load(paste0(datafolder,"w7/yintw.RData"))
ALSA_w7 <- left_join(ALSA_w7,yintw, by="id")
names(ALSA_w7)[5] <- "yintw_w7"
rm(yintw)

```

```{r local w7, echo=F}

vbl <- ALSA_w7$arthriw7
kable(Categorical_summary(vbl, missing_values = c(0))[3], caption = names(ALSA_w7)[2])
kable(Categorical_summary(vbl, missing_values = c(0))[1], caption = "Category")
ggplot(ALSA_w7, aes(x=factor(arthriw7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w7$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(ALSA_w7)[3])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_w7, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(70,115)

vbl <- ALSA_w7$yintw_w6
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w7)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w7, aes(x=factor(yintw_w6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w7$yintw_w7
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w7)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w7, aes(x=factor(yintw_w7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_joint_disorders` from the study-specific variable it has to be recoded as follows:

* `W1CDN2 == 2 and MORBID2 == 0 and CDN3_W6 == 0 (or missings) and arthriw7 == 9 into 0`
* `arthriw7 == 1 or 2 or 3 or 4 or W1CDN2 == 1 or MORBID2 == 1 or CDN3_W6 == 1 into 1`
* `W1CDN2 == 2 and MORBID2 == 0 and CDN3_W6 == 0 (or missings) and arthriw7 == 0 into 995`
* `otherwise into 999`

To compute `h_joint_disorders_age` from the study-specific variable it has to be recoded as follows:

* `if h_joint_disorders == 1 in w7 and previously, h_joint_disorders_age = as before`
* `if h_joint_disorders == 1 in w7 and 0 in w6 h_joint_disorders_age = age - (year of interview w7 - year of interview w6)/2`
* `if h_joint_disorders == 0, h_joint_disorders_age = 996`
* `otherwise into 999`

**R script:**

```{r harmo w7}

# We use the harmonized variable of previous waves instead of the study-specific variables
ALSA_w7 <- left_join(ALSA_w7, ALSA_ds, by = "id")

ALSA_ds_w7 <- tibble(id=ALSA_w7$id)
ALSA_ds_w7$h_joint_disorders <- rep(999,length(ALSA_ds_w7$id))
ALSA_ds_w7$h_joint_disorders[which(ALSA_w7$arthriw7 == 9 & (ALSA_w7$h_joint_disorders != 1 | is.na(ALSA_w7$h_joint_disorders)))] <- 0
ALSA_ds_w7$h_joint_disorders[which(ALSA_w7$arthriw7 %in% c(1,2,3,4) | ((!is.na(ALSA_w7$arthriw7)) & ALSA_w7$h_joint_disorders == 1))] <- 1
ALSA_ds_w7$h_joint_disorders[which(ALSA_w7$arthriw7 == 0 & (ALSA_w7$h_joint_disorders != 1 | is.na(ALSA_w7$h_joint_disorders)))] <- 995

# We update the status of the individuals in the global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- left_join(endtib,sttib,by="id")
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
ALSA_ds_prov <- ALSA_ds[,c(1,2)]
ALSA_ds_prov <- assign_merge(ALSA_ds_prov,ALSA_ds_w7,log_vec=(ALSA_ds_prov$id %in% ALSA_ds_w7$id),col_end_index = 2, col_st_index = 3)
ALSA_ds$h_joint_disorders <- ALSA_ds_prov$h_joint_disorders
rm(ALSA_ds_prov)

# Continuous variable harmonization
ALSA_ds_w7$h_joint_disorders_age <- rep(999,length(ALSA_ds_w7$id))
ALSA_w7 <- left_join(ALSA_w7, ALSA_ds_w6, by = "id", suffix =c("","_w6"))
# Obtained ages following diagnosis dates answered in wave 7
ALSA_ds_w7$h_joint_disorders_age[which(ALSA_ds_w7$h_joint_disorders == 1 & ALSA_w7$h_joint_disorders_w6 == 0)] <- ALSA_w7$age[which(ALSA_ds_w7$h_joint_disorders == 1 & ALSA_w7$h_joint_disorders_w6 == 0)] - (ALSA_w7$yintw_w7[which(ALSA_ds_w7$h_joint_disorders == 1 & ALSA_w7$h_joint_disorders_w6 == 0)] - ALSA_w7$yintw_w6[which(ALSA_ds_w7$h_joint_disorders == 1 & ALSA_w7$h_joint_disorders_w6 == 0)])/2
ALSA_ds_w7$h_joint_disorders_age[which(ALSA_ds_w7$h_joint_disorders == 0)] <- 996
# Obtained ages following diagnosis dates answered in previous waves
ALSA_ds_w7$h_joint_disorders_age[which(ALSA_ds_w7$h_joint_disorders == 1 & !is.na(ALSA_w7$h_joint_disorders_age) & !ALSA_w7$h_joint_disorders_age %in% miss_values_vector)] <- ALSA_w7$h_joint_disorders_age[which(ALSA_ds_w7$h_joint_disorders == 1 & !is.na(ALSA_w7$h_joint_disorders_age) & !ALSA_w7$h_joint_disorders_age %in% miss_values_vector)]

```


#### Statistics of the new harmonized variable

```{r descript w7, echo=F}

vbl <- ALSA_ds_w7$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w7, aes(x=factor(h_joint_disorders))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ALSA_ds_w7$h_joint_disorders_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w7, aes(h_joint_disorders_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(10,95)

```


#### Validation

```{r crosstabulation w7, echo=F, results='asis'}

AfterH <- table(ALSA_ds_w7$h_joint_disorders)
X <- c(
  sum(ALSA_w7$arthriw7 == 9 & (ALSA_w7$h_joint_disorders != 1 | is.na(ALSA_w7$h_joint_disorders)),na.rm=T),
  sum(ALSA_w7$arthriw7 %in% c(1,2,3,4) | ((!is.na(ALSA_w7$arthriw7)) & ALSA_w7$h_joint_disorders == 1),na.rm=T),
  sum(ALSA_w7$arthriw7 == 0 & (ALSA_w7$h_joint_disorders != 1 | is.na(ALSA_w7$h_joint_disorders)),na.rm=T)
)
BeforeH <- c(X[1:3],length(ALSA_w7$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("9 into 0","1,2,3,4->1","0->995","NA->999")
kable(C)

cat("There are 57 individuals which tell that they have no arthritis and previously answered they had arthritis. They are harmonized as having joint disorders.")
kable(frq(ALSA_w7$arthriw7[which(ALSA_w7$h_joint_disorders==1)]),align = 'c')

```



### Wave 8

Not found.



### Wave 9



#### Study-specific variable description

| **Name** | `ARTHRIW9` |
|-|-|
| **Label** | `What form of arthritis do you have` |
| **Table name**  | `ALSA-Wave9` |
| **Categories** | `1 = Rheumatism or rheumatic`<br/>`2 = Rheumatoid arthritis`<br/>`3 = Osteoarthritis`<br/>`4 = Other form, SPECIFY BELOW` |
| **Missings** | `0 = Not Answered`<br/>`NA` |  |  |  |
| **Description** |  |  |  |  |

```{r assign w9, echo=F}

opal.assign.table.tibble(o, 'ALSA_w9','ALSA.ALSA-Wave9',variables=list('ARTHRIW9'), missings = T)
ALSA_w9 <- opal.execute(o,'ALSA_w9')
# We remove two id's which are not coincident with any other in the other waves of ALSA and whose data is empty.
ALSA_w9 <- ALSA_w9[!ALSA_w9$id %in% c("3515","43202"),]

```

```{r local w9, echo=F}

vbl <- ALSA_w9$ARTHRIW9
kable(Categorical_summary(vbl, missing_values = c(0))[3], caption = names(ALSA_w9)[2])
kable(Categorical_summary(vbl, missing_values = c(0))[1], caption = "Category")
ggplot(ALSA_w9, aes(x=factor(ARTHRIW9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_joint_disorders` from the study-specific variable it has to be recoded as follows:

* `W1CDN2 == 2 and MORBID2 == 0 and CDN3_W6 == 0 and arthriw7 == 9 (or missings) and ARTHRIW9 == 9 into 0`
* `ARTHRIW9 == 1 or 2 or 3 or 4 or W1CDN2 == 1 or MORBID2 == 1 or CDN3_W6 == 1 or arthriw7 == 1 or 2 or 3 or 4 into 1`
* `W1CDN2 == 2 and MORBID2 == 0 and CDN3_W6 == 0 and ARTHRIW9 == 9 (or missings) and ARTHRIW9 == 0 into 995`
* `otherwise into 999`

Age of diagnostic cannot be harmonized.


**R script:**

```{r harmo w9}

# We use the harmonized variable of previous waves instead of the study-specific variables
ALSA_w9 <- left_join(ALSA_w9, ALSA_ds, by = "id")

ALSA_ds_w9 <- tibble(id=ALSA_w9$id)
ALSA_ds_w9$h_joint_disorders <- rep(999,length(ALSA_ds_w9$id))
ALSA_ds_w9$h_joint_disorders[which(ALSA_w9$ARTHRIW9 == 9 & (ALSA_w9$h_joint_disorders != 1 | is.na(ALSA_w9$h_joint_disorders)))] <- 0
ALSA_ds_w9$h_joint_disorders[which(ALSA_w9$ARTHRIW9 %in% c(1,2,3,4) | ((!is.na(ALSA_w9$ARTHRIW9)) & ALSA_w9$h_joint_disorders == 1))] <- 1
ALSA_ds_w9$h_joint_disorders[which(ALSA_w9$ARTHRIW9 == 0 & (ALSA_w9$h_joint_disorders != 1 | is.na(ALSA_w9$h_joint_disorders)))] <- 995

# We update the status of the individuals in the global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- left_join(endtib,sttib,by="id")
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
ALSA_ds_prov <- ALSA_ds[,c(1,2)]
ALSA_ds_prov <- assign_merge(ALSA_ds_prov,ALSA_ds_w9,log_vec=(ALSA_ds_prov$id %in% ALSA_ds_w9$id),col_end_index = 2, col_st_index = 3)
ALSA_ds$h_joint_disorders <- ALSA_ds_prov$h_joint_disorders
rm(ALSA_ds_prov)

```


#### Statistics of the new harmonized variable

```{r descript w9, echo=F}

vbl <- ALSA_ds_w9$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w9, aes(x=factor(h_joint_disorders))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w9, echo=F, results='asis'}

AfterH <- table(ALSA_ds_w9$h_joint_disorders)
X <- c(
  sum(ALSA_w9$ARTHRIW9 %in% c(1,2,3,4) | ((!is.na(ALSA_w9$ARTHRIW9)) & ALSA_w9$h_joint_disorders == 1),na.rm=T),
  sum(ALSA_w9$ARTHRIW9 == 0 & (ALSA_w9$h_joint_disorders != 1 | is.na(ALSA_w9$h_joint_disorders)),na.rm=T)
)
BeforeH <- c(X[1:2],length(ALSA_w9$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->1","0->995","NA->999")
kable(C)

```



### Wave 10

Not found.



### Wave 11


#### Study-specific variable description

| **Name** | `ARTHW11` |
|-|-|
| **Label** | `Arthritis` |
| **Table name**  | `ALSA-Wave11` |
| **Categories** | `0 = No`<br/>`1 = Yes` |
| **Description** |  |

```{r assign w11, echo=F}

opal.assign.table.tibble(o, 'ALSA_w11','ALSA.ALSA-Wave11',variables=list('ARTHW11'), missings = T)
ALSA_w11 <- opal.execute(o,'ALSA_w11')

```

```{r local w11, echo=F}

vbl <- ALSA_w11$ARTHW11
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w11)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w11, aes(x=factor(ARTHW11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_joint_disorders` from the study-specific variable it has to be recoded as follows:

* `ARTHW11 (w11)=0 AND ARTHRIW7 (W7)=9 AND CDN3_W6 (w6)=0 AND W1CDN2 (w3)=2 AND MORBID2 (w1)=0 into 0`
* `ARTHW11 (w11)=1 OR (ARTHRIW9 (w9)= 1 OR 2 OR 3 OR 4) OR (ARTHRIW7 (W7)=1 OR 2 OR 3 OR 4) OR CDN3_W6 (w6)=1 OR W1CDN2 (w3)=1 OR MORBID2 (w1)=1 into 1`
* `otherwise into 999`

Age of diagnostic cannot be harmonized.

**R script:**

```{r harmo w11}

# We use the harmonized variable of previous waves instead of the study-specific variables
ALSA_w11 <- left_join(ALSA_w11, ALSA_ds, by = "id")

ALSA_ds_w11 <- tibble(id=ALSA_w11$id)
ALSA_ds_w11$h_joint_disorders <- rep(999,length(ALSA_ds_w11$id))
ALSA_ds_w11$h_joint_disorders[which(ALSA_w11$ARTHW11 == 0 & ((is.na(ALSA_w11$h_joint_disorders)) |  ALSA_w11$h_joint_disorders != 1))] <- 0
ALSA_ds_w11$h_joint_disorders[which(ALSA_w11$ARTHW11 == 1 | ((!is.na(ALSA_w11$ARTHW11)) & ALSA_w11$h_joint_disorders == 1))] <- 1

# We update the status of the individuals in the global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- left_join(endtib,sttib,by="id")
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
ALSA_ds_prov <- ALSA_ds[,c(1,2)]
ALSA_ds_prov <- assign_merge(ALSA_ds_prov,ALSA_ds_w11,log_vec=(ALSA_ds_prov$id %in% ALSA_ds_w11$id),col_end_index = 2, col_st_index = 3)
ALSA_ds$h_joint_disorders <- ALSA_ds_prov$h_joint_disorders
rm(ALSA_ds_prov)

```


#### Statistics of the new harmonized variable

```{r descript w11, echo=F}

vbl <- ALSA_ds_w11$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w11, aes(x=factor(h_joint_disorders))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w11, echo=F, results='asis'}

AfterH <- table(ALSA_ds_w11$h_joint_disorders)
X <- c(
  sum(ALSA_w11$ARTHW11 == 0 & ((is.na(ALSA_w11$h_joint_disorders)) |  ALSA_w11$h_joint_disorders != 1),na.rm=T),
  sum(ALSA_w11$ARTHW11 == 1 | ((!is.na(ALSA_w11$ARTHW11)) & ALSA_w11$h_joint_disorders == 1),na.rm=T)
)
BeforeH <- c(X[1:2])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1")
kable(C)

cat("There are 26 individuals who answered in previous waves that they were diagnosed to have joint disorders and in the eleventh wave that they were not told to have it. We harmonize them as having joint disorders.")
kable(frq(ALSA_w11$ARTHW11[which(ALSA_w11$h_joint_disorders==1)]), align = 'c')
kable(ALSA_w11[ALSA_w11$id %in% ALSA_w11$id[ALSA_w11$ARTHW11==0 & ALSA_w11$h_joint_disorders==1],], align = 'c')
#strange_id <- c(strange_id,ALSA_w11$id[ALSA_w11$id %in% ALSA_w11$id[ALSA_w11$ARTHW11==0 & ALSA_w11$h_joint_disorders==1]])

```



### Wave 12


#### Study-specific variable description

| **Name** | `ARTHW12` |`age`|
|-|-|-|
| **Label** | `Arthritis` |`age`|
| **Table name**  | `ALSA-Wave12` |`age`|
| **Categories** |  `0 = No`<br/>`1 = Yes` |`continuous`|
| **Description** |  |  |

```{r assign w12, echo=F}

opal.assign.table.tibble(o, 'ALSA_w12','ALSA.ALSA-Wave12',variables=list('ARTHW12'), missings = T)
ALSA_w12 <- opal.execute(o,'ALSA_w12')
load(paste0(datafolder,"w12/age.RData"))
ALSA_w12 <- left_join(ALSA_w12,age, by="id")

```

```{r local w12, echo=F}

vbl <- ALSA_w12$ARTHW12
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w12)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w12, aes(x=factor(ARTHW12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w12$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(ALSA_w11)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_w12, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(85,105)

```


#### Harmonisation algorithm

To compute `h_joint_disorders` from the study-specific variable it has to be recoded as follows:

* `ARTHW12 (w12)=0 AND ARTHW11 (w11)=0 AND ARTHRIW7 (W7)=9 AND CDN3_W6 (w6)=0 AND W1CDN2 (w3)=2 AND MORBID2 (w1)=0 into 0`
* ` ARTHW12 (w12)=1 OR ARTHW11 (w11)=1 OR (ARTHRIW9 (w9)= 1 OR 2 OR 3 OR 4) OR (ARTHRIW7 (W7)=1 OR 2 OR 3 OR 4) OR CDN3_W6 (w6)=1 OR W1CDN2 (w3)=1 OR MORBID2 (w1)=1 into 1`
* `otherwise into 999`

To compute `h_joint_disorders_age` from the study-specific variable it has to be recoded as follows:

* `if h_joint_disorders == 1 in w12 and 0 in w11, h_joint_disorders_age = age-(year of interview w12-year of interview w11)/2. Since year of interview w12 == 2013 and year of interview w11 == 2010, the mid difference is 1.5. Since the age is usually given as an integer we would apply the floor, but all together is the same that h_joint_disorders_age = age-2`
* `if h_joint_disorders == 1 in w12 and previously, h_joint_disorders_age = age obtained from previous waves`
* `if h_joint_disorders == 0, h_joint_disorders_age = 996`
* `h_joint_disorders == missing into 999`

**R script:**

```{r harmo w12}

# We use the harmonized variable of previous waves instead of the study-specific variables
ALSA_w12 <- left_join(ALSA_w12, ALSA_ds, by = "id")

ALSA_ds_w12 <- tibble(id=ALSA_w12$id)
ALSA_ds_w12$h_joint_disorders <- rep(999,length(ALSA_ds_w12$id))
ALSA_ds_w12$h_joint_disorders[which(ALSA_w12$ARTHW12 == 0 & ((is.na(ALSA_w12$h_joint_disorders)) | ALSA_w12$h_joint_disorders != 1))] <- 0
ALSA_ds_w12$h_joint_disorders[which(ALSA_w12$ARTHW12 == 1 | ((!is.na(ALSA_w12$ARTHW12)) & ALSA_w12$h_joint_disorders == 1))] <- 1

# We update the status of the individuals in the global table
rm(ALSA_ds)

# Continuous variable harmonization
ALSA_ds_w12$h_joint_disorders_age <- rep(999,length(ALSA_ds_w12$id))

ALSA_w12 <- left_join(ALSA_w12, ALSA_ds_w11, by = "id", suffix =c("","_w11"))
# Obtained ages following diagnosis dates answered in wave 12
ALSA_ds_w12$h_joint_disorders_age[which(ALSA_ds_w12$h_joint_disorders == 1 & ALSA_w12$h_joint_disorders_w11 == 0)] <- ALSA_w12$age[which(ALSA_ds_w12$h_joint_disorders == 1 & ALSA_w12$h_joint_disorders_w11 == 0)]-2
ALSA_ds_w12$h_joint_disorders_age[which(ALSA_ds_w12$h_joint_disorders == 0)] <- 996
ALSA_ds_w12$h_joint_disorders_age[which(ALSA_ds_w12$h_joint_disorders == 1 & !is.na(ALSA_w12$h_joint_disorders_age) & !ALSA_w12$h_joint_disorders_age %in% miss_values_vector)] <- ALSA_w12$h_joint_disorders_age[which(ALSA_ds_w12$h_joint_disorders == 1 & !is.na(ALSA_w12$h_joint_disorders_age) & !ALSA_w12$h_joint_disorders_age %in% miss_values_vector)]

```


#### Statistics of the new harmonized variable

```{r descript w12, echo=F}

vbl <- ALSA_ds_w12$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w12, aes(x=factor(h_joint_disorders))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ALSA_ds_w12$h_joint_disorders_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w12, aes(h_joint_disorders_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(20,100)

```


#### Validation

```{r crosstabulation w12, echo=F, results='asis'}

AfterH <- table(ALSA_ds_w12$h_joint_disorders)
X <- c(
  sum(ALSA_w12$ARTHW12 == 0 & ((is.na(ALSA_w12$h_joint_disorders)) | ALSA_w12$h_joint_disorders != 1),na.rm=T),
  sum(ALSA_w12$ARTHW12 == 1 | ((!is.na(ALSA_w12$ARTHW12)) & ALSA_w12$h_joint_disorders == 1),na.rm=T)
)
BeforeH <- c(X[1:2])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1")
kable(C)

cat("There are 17 individuals who answered in previous waves that they were diagnosed to have joint disorders and in the twelfth wave that they were not told to have it. We harmonize them as having joint disorders.")
kable(frq(ALSA_w12$h_joint_disorders[!is.na(ALSA_w12$ARTHW12) & ALSA_w12$ARTHW12==0]), align = 'c')
kable(ALSA_w12[ALSA_w12$id %in% ALSA_w12$id[ALSA_w12$ARTHW12==0 & ALSA_w12$h_joint_disorders==1],], align = 'c')

```



### Wave 13

Not found.


<!--
```{r summary, include=F, eval=F, echo=F}
kable(ALSA_ds[ALSA_ds$id %in% strange_id,], align = 'c', caption = 'Individuals with discrepancies')
```
-->

<!--AUXILIAR FUNCTIONS-->



```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds,vbl_name,ds_lab = ds_label){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    if(vbl_name %in% names(l.hds[[name]])){
      # In the aux_object we copy the old tibble to recodify all missing values as NA.
      aux_object <- l.hds[[name]]
      # Labelling of variables
      label(l.hds[[name]][[vbl_name]]) <- label(aux_object[[vbl_name]]) <- ds_lab
      # Labelling of categories (for continues variables, only missing values)
      l.hds[[name]][[vbl_name]] <- labelled(l.hds[[name]][[vbl_name]], labels = cat_label)
      aux_object[[vbl_name]] <- car::recode(aux_object[[vbl_name]], "miss_values_vector=NA")
      # Labelling of categories (for categorical variables, only non-missing values)
      aux_object[[vbl_name]] <- labelled(aux_object[[vbl_name]], labels = cat_label[1:(length(cat_label)-9)])
      # Saving the recodified tibble in list m.hds
      m.hds[[name]] <- aux_object
      rm(aux_object)
    }
  }
  return(list(l.hds,m.hds))

}


labelling_c <- function(l.hds,m.hds,vbl_name,ds_lab=ds_label){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    if(vbl_name %in% names(l.hds[[name]])){
      # In the aux_object we copy the old tibble to recodify all missing values as NA.
      aux_object <- m.hds[[name]]
      # Labelling of variables
      label(l.hds[[name]][[vbl_name]]) <- label(aux_object[[vbl_name]]) <- ds_lab
      # Labelling of categories (for continues variables, only missing values)
      l.hds[[name]][[vbl_name]] <- labelled(l.hds[[name]][[vbl_name]], labels = cont_label)
      aux_object[[vbl_name]] <- car::recode(aux_object[[vbl_name]], "miss_values_vector=NA")
      aux_object[[vbl_name]] <- remove_val_labels(aux_object[[vbl_name]])
      # Saving the recodified tibble in list m.hds
      m.hds[[name]] <- aux_object
      rm(aux_object)
    }
  }
  return(list(l.hds,m.hds))

}


# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames,vbl_name){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][vbl_name])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][vbl_name])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[2+length(cat_label),] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}


# Creation of summary tables for continuous data

summaries_c <- function(l.hds,m.hds,lnames,vbl_name){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][vbl_name])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[vbl_name]], missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][vbl_name])[1:6]
    # Next, missing/no-missing values (the 1 in $values_table[1,] stands for absolute values, while a 2 would stand for percentages)
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[vbl_name]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][vbl_name]))[[2]],lnames)
  return(t.hds)
  
}



# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }
  
}

```



```{r populations-waves, echo=F}


# All study waves and populations with abbreviated and descriptive names

alsa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"), w6 = c("w6","W6"), w7 = c("w7","W7"), w8 = c("w8","W8"), w9 = c("w9","W9"), w10 = c("w10","W10"), w11 = c("w11","W11"), w12 = c("w12","W12"), w13 = c("w13","W13"))



```


<!--Labelling and saving-->

```{r, echo=FALSE}


# Consider only waves with some variable harmonised

l.hds <- lapply(alsa.cw, function(wname) if(exists(paste0("ALSA_ds_",wname[1]))){wname = list(get(paste0("ALSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling categorical variable of tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]],hd_vbl,ds_label)
  # Labelling continuous variable of tibbles
  lmlist <- labelling_c(lmlist[[1]],lmlist[[2]],hd_age_vbl,ds_label_age)
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}

alsalist <- lmlist # ALSA list




```



<!--Descriptives-->

## Descriptive statistics of the harmonised variable `h_joint_disorders` accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.

```{r summ, echo=F}


# Consider only harmonised waves
l.hds <- lapply(alsa.cw, function(wname) if(hd_vbl %in% names(get0(paste0("ALSA_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- alsalist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- alsalist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))

}



```






## Summary of descriptive statistics of the harmonised variable `h_joint_disorders_age` accross populations and waves






```{r summ_c, echo=F}


# Consider only harmonised waves
l.hds <- lapply(alsa.cw, function(wname) if(hd_age_vbl %in% names(get0(paste0("ALSA_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- alsalist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- alsalist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries_c(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_age_vbl),caption=ds_label_age))
}





```


# Quality estimation

* We assume that if an individual answers it has joint disorders in one wave, it has for all the next waves. Individuals with discrepancies with respect to this criterium are specified at the end of each validation.
* There are individuals with different diagnostic years data across waves. We harmonize diagnostic age taking the first year they answer.







<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





