---
title: "Angina"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `h_angina`
* Variable label: `History of angina`
* Variable description: `history of angina`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | no history of angina
1        | history of angina

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Short name: `h_angina_age`
* Variable label: `Age first diagnosed angina`
* Variable description: `The age first told had angina diagnosis`
* Domain: `Diseases`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "History of angina"
ds_label_age <- "Age first diagnosed angina"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
cont_label <- cat_label[3:11]
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process



## Australia


### Wave 1

Not found.

### Wave 2

Not found.

### Wave 3

Not found.

### Wave 4

Not found.

### Wave 5

Not found.



### Wave 6


#### Study-specific variable description

| **Name** | `CDN2_W6` |`DIA2_W6`|`ybirth`|
|-|-|-|-|
| **Label** | `Angina` |`year told of: Angina`|`Year of birth`|
| **Table name**  | `ALSA-Wave6` | `ALSA-Wave6` |`ybirth`|
| **Categories** | `0 = no`<br/>`1 = yes` |`continuous`|`continuous`|
| **Missings** | `NA` |`NA`|  |
| **Description** |  |  |  |

```{r assign w6, echo=F}

opal.assign.table.tibble(o, 'ALSA_w6','ALSA.ALSA-Wave6',variables=list('CDN2_W6','DIA2_W6'), missings = T)
ALSA_w6 <- opal.execute(o,'ALSA_w6')
ALSA_w6$DIA2_W6 <- as.numeric(ALSA_w6$DIA2_W6)
load(paste0(datafolder,"w6/ybirth.RData"))
ALSA_w6 <- left_join(ALSA_w6,ybirth, by="id")
```

```{r local w6, echo=F}

vbl <- ALSA_w6$CDN2_W6
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w6)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w6, aes(x=factor(CDN2_W6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w6$DIA2_W6
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(ALSA_w6)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_w6, aes(DIA2_W6)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1935,2005)

vbl <- ALSA_w6$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(ALSA_w6)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_w6, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1895,1930)

```


#### Harmonisation algorithm

To compute `h_angina` from the study-specific variable it has to be recoded as follows:

* `CDN2_W6 == 0 into 0`
* `CDN2_W6 == 1 into 1`
* `otherwise into 999`

To compute `h_angina_age` from the study-specific variable it has to be recoded as follows:

* `if h_angina == 1, h_angina_age = DIA2_W6 - ybirth`
* `if h_angina == 0, h_angina_age = 996`
* `DIA2_W6 == 197 into 991`
* `otherwise into 999`

**R script:**

```{r harmo w6}

ALSA_ds_w6 <- tibble(id=ALSA_w6$id)
ALSA_ds_w6$h_angina <-car::recode(ALSA_w6$CDN2_W6,"NA=999")

# Continuous variable harmonization
angina_age <- ALSA_w6$DIA2_W6[which(ALSA_ds_w6$h_angina == 1)]-ALSA_w6$ybirth[which(ALSA_ds_w6$h_angina == 1)]
ALSA_ds_w6$h_angina_age <- car::recode(ALSA_ds_w6$h_angina, "0 = 996; 1 = angina_age")
ALSA_ds_w6$h_angina_age <- car::recode(ALSA_ds_w6$h_angina_age,"NA=999")

# We build a global table in order to have updated the status of all the individuals through the different waves
ALSA_ds <- ALSA_ds_w6

```


#### Statistics of the new harmonized variable

```{r descript w6, echo=F}

vbl <- ALSA_ds_w6$h_angina
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w6, aes(x=factor(h_angina))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ALSA_ds_w6$h_angina_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w6, aes(h_angina_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(40,90)

```


#### Validation

```{r crosstabulation w6, echo=F, results='asis'}

AfterH <- table(ALSA_ds_w6$h_angina)
BeforeH <- table(ALSA_w6$CDN2_W6,useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("some 1->1","NA->999")
kable(C)

```



### Wave 7

Not found.


### Wave 8

Not found.


### Wave 9

Not found.


### Wave 10

Not found.



### Wave 11


#### Study-specific variable description

| **Name** | `HCDN2W11` |
|-|-|
| **Label** | `Angina` |
| **Table name**  | `ALSA-Wave11` |
| **Categories** | `0 = No`<br/>`1 = Yes` |
| **Description** |  |

```{r assign w11, echo=F}

opal.assign.table.tibble(o, 'ALSA_w11','ALSA.ALSA-Wave11',variables=list('HCDN2W11'), missings = T)
ALSA_w11 <- opal.execute(o,'ALSA_w11')

```

```{r local w11, echo=F}

vbl <- ALSA_w11$HCDN2W11
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w11)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w11, aes(x=factor(HCDN2W11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_angina` from the study-specific variable it has to be recoded as follows:

* `HCDN2W11 (w11)=0 AND CDN2_W6 (w6)=0 into 0`
* `HCDN2W11 (w11)=1 OR CDN2_W6 (w6)=1 into 1`
* `otherwise into 999`

Age of diagnostic cannot be harmonized.

**R script:**

```{r harmo w11}

# We use the harmonized variable of previous waves instead of the study-specific variables
ALSA_w11 <- left_join(ALSA_w11, ALSA_ds, by = "id")

ALSA_ds_w11 <- tibble(id=ALSA_w11$id)
ALSA_ds_w11$h_angina <- rep(999,length(ALSA_ds_w11$id))
ALSA_ds_w11$h_angina[which(ALSA_w11$HCDN2W11 == 0 & ((is.na(ALSA_w11$h_angina)) |  ALSA_w11$h_angina != 1))] <- 0
ALSA_ds_w11$h_angina[which(ALSA_w11$HCDN2W11 == 1 | ((!is.na(ALSA_w11$HCDN2W11)) & ALSA_w11$h_angina == 1))] <- 1

# We update the status of the individuals in the global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- full_join(endtib,sttib,by="id")
  row.names(newtib) <- newtib$id
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
ALSA_ds_prov <- ALSA_ds[,c(1,2)]
ALSA_ds_prov <- assign_merge(ALSA_ds_prov,ALSA_ds_w11,log_vec=ALSA_ds_w11$id,col_end_index = 2, col_st_index = 3)
ALSA_ds_prov <- full_join(ALSA_ds_prov,ALSA_ds[,c(1,3)])
ALSA_ds <- ALSA_ds_prov
rm(ALSA_ds_prov)

```


#### Statistics of the new harmonized variable

```{r descript w11, echo=F}

vbl <- ALSA_ds_w11$h_angina
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w11, aes(x=factor(h_angina))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w11, echo=F, results='asis'}

AfterH <- table(ALSA_ds_w11$h_angina)
X <- c(
  sum(ALSA_w11$HCDN2W11 == 0 & ((is.na(ALSA_w11$h_angina)) |  ALSA_w11$h_angina != 1),na.rm=T),
  sum(ALSA_w11$HCDN2W11 == 1 | ((!is.na(ALSA_w11$HCDN2W11)) & ALSA_w11$h_angina == 1),na.rm=T)
)
BeforeH <- c(X[1:2],length(ALSA_ds_w11$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","NA->999")
kable(C)

cat("There is 1 individual who answered in the previous wave that was diagnosed to have angina and in the eleventh wave that was not told to have it. We harmonize it as having angina.")
kable(frq(ALSA_w11$HCDN2W11[which(ALSA_w11$h_angina==1)]), align = 'c')
kable(ALSA_w11[ALSA_w11$id %in% ALSA_w11$id[ALSA_w11$HCDN2W11==0 & ALSA_w11$h_angina==1],], align = 'c')
#strange_id <- c(strange_id,ALSA_w11$id[ALSA_w11$id %in% ALSA_w11$id[ALSA_w11$HCDN2W11==0 & ALSA_w11$h_angina==1]])

```



### Wave 12


#### Study-specific variable description

| **Name** | `HCDN2W12` |`age`|
|-|-|-|
| **Label** | `Angina` |`age`|
| **Table name**  | `ALSA-Wave12` |`age`|
| **Categories** |  `0 = No`<br/>`1 = Yes` |`continuous`|
| **Description** |  |  |

```{r assign w12, echo=F}

opal.assign.table.tibble(o, 'ALSA_w12','ALSA.ALSA-Wave12',variables=list('HCDN2W12'), missings = T)
ALSA_w12 <- opal.execute(o,'ALSA_w12')
load(paste0(datafolder,"w12/age.RData"))
ALSA_w12 <- left_join(ALSA_w12,age, by="id")

```

```{r local w12, echo=F}

vbl <- ALSA_w12$HCDN2W12
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w12)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w12, aes(x=factor(HCDN2W12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w12$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(ALSA_w11)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_w12, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(85,105)

```


#### Harmonisation algorithm

To compute `h_angina` from the study-specific variable it has to be recoded as follows:

* `HCDN2W12 (w12)=0 AND HCDN2W11 (w11)=0 AND CDN2_W6 (w6)=0 into 0`
* `HCDN2W12 (w12)=1 OR HCDN2W11 (w11)=1 OR CDN2_W6 (w6)=1 into 1`
* `otherwise into 999`

To compute `h_angina_age` from the study-specific variable it has to be recoded as follows:

* `if h_angina == 1 in w12 and 0 in w11, h_angina_age = age-(year of interview w12-year of interview w11)/2. Since year of interview w12 == 2013 and year of interview w11 == 2010, the mid difference is 1.5. Since the age is usually given as an integer we would apply the floor, but all together is the same that h_angina_age = age-2`
* `if h_angina == 1 in w12 and previously, h_angina_age = age obtained from previous waves`
* `if h_angina == 0, h_angina_age = 996`
* `h_angina == missing into 999`

**R script:**

```{r harmo w12}

# We use the harmonized variable of previous waves instead of the study-specific variables
ALSA_w12 <- left_join(ALSA_w12, ALSA_ds, by = "id")

ALSA_ds_w12 <- tibble(id=ALSA_w12$id)
ALSA_ds_w12$h_angina <- rep(999,length(ALSA_ds_w12$id))
ALSA_ds_w12$h_angina[which(ALSA_w12$HCDN2W12 == 0 & ((is.na(ALSA_w12$h_angina)) | ALSA_w12$h_angina != 1))] <- 0
ALSA_ds_w12$h_angina[which(ALSA_w12$HCDN2W12 == 1 | ((!is.na(ALSA_w12$HCDN2W12)) & ALSA_w12$h_angina == 1))] <- 1

# We update the status of the individuals in the global table
rm(ALSA_ds)

# Continuous variable harmonization
ALSA_ds_w12$h_angina_age <- rep(999,length(ALSA_ds_w12$id))

ALSA_w12 <- left_join(ALSA_w12, ALSA_ds_w11, by = "id", suffix =c("","_w11"))
# Obtained ages following diagnosis dates answered in wave 12
ALSA_ds_w12$h_angina_age[which(ALSA_ds_w12$h_angina == 1 & ALSA_w12$h_angina_w11 == 0)] <- ALSA_w12$age[which(ALSA_ds_w12$h_angina == 1 & ALSA_w12$h_angina_w11 == 0)]-2
ALSA_ds_w12$h_angina_age[which(ALSA_ds_w12$h_angina == 0)] <- 996
ALSA_ds_w12$h_angina_age[which(ALSA_ds_w12$h_angina == 1 & !is.na(ALSA_w12$h_angina_age) & !ALSA_w12$h_angina_age %in% miss_values_vector)] <- ALSA_w12$h_angina_age[which(ALSA_ds_w12$h_angina == 1 & !is.na(ALSA_w12$h_angina_age) & !ALSA_w12$h_angina_age %in% miss_values_vector)]

```


#### Statistics of the new harmonized variable

```{r descript w12, echo=F}

vbl <- ALSA_ds_w12$h_angina
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w12, aes(x=factor(h_angina))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ALSA_ds_w12$h_angina_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w12, aes(h_angina_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(55,90)

```


#### Validation

```{r crosstabulation w12, echo=F, results='asis'}

AfterH <- table(ALSA_ds_w12$h_angina)
X <- c(
  sum(ALSA_w12$HCDN2W12 == 0 & ((is.na(ALSA_w12$h_angina)) | ALSA_w12$h_angina != 1),na.rm=T),
  sum(ALSA_w12$HCDN2W12 == 1 | ((!is.na(ALSA_w12$HCDN2W12)) & ALSA_w12$h_angina == 1),na.rm=T)
)
BeforeH <- c(X[1:2],length(ALSA_ds_w12$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","NA->999")
kable(C)

```



### Wave 13

Not found.


<!--
```{r summary, include=F, eval=F, echo=F}
kable(ALSA_ds[ALSA_ds$id %in% strange_id,], align = 'c', caption = 'Individuals with discrepancies')
```
-->

## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.

**R script:**

```{r summ}
ALSA_ds_w6$h_angina <- labelled(ALSA_ds_w6$h_angina, labels = cat_label)
label(ALSA_ds_w6$h_angina) <- ds_label
ALSA_ds_w6$h_angina_age <- labelled(ALSA_ds_w6$h_angina_age, labels = cont_label)
label(ALSA_ds_w6$h_angina_age) <- ds_label_age
ALSA_ds_w11$h_angina <- labelled(ALSA_ds_w11$h_angina, labels = cat_label)
label(ALSA_ds_w11$h_angina) <- ds_label
ALSA_ds_w12$h_angina <- labelled(ALSA_ds_w12$h_angina, labels = cat_label)
label(ALSA_ds_w12$h_angina) <- ds_label
ALSA_ds_w12$h_angina_age <- labelled(ALSA_ds_w12$h_angina_age, labels = cont_label)
label(ALSA_ds_w12$h_angina_age) <- ds_label_age

ALSA_m_ds_w6 <- ALSA_ds_w6
ALSA_m_ds_w6$h_angina <- car::recode(ALSA_m_ds_w6$h_angina, "miss_values_vector=NA")
ALSA_m_ds_w11 <- ALSA_ds_w11
ALSA_m_ds_w11$h_angina <- car::recode(ALSA_m_ds_w11$h_angina, "miss_values_vector=NA")
ALSA_m_ds_w12 <- ALSA_ds_w12
ALSA_m_ds_w12$h_angina <- car::recode(ALSA_m_ds_w12$h_angina, "miss_values_vector=NA")

tt <-    frq(ALSA_ds_w6$h_angina)[[1]][,c(1:2,4)]
tt[4] <- frq(ALSA_ds_w11$h_angina)[[1]][,c(4)]
tt[5] <- frq(ALSA_ds_w12$h_angina)[[1]][,c(4)]
tt[13,] <- c("n", "sample size", 
             length(ALSA_ds_w6$h_angina), length(ALSA_ds_w11$h_angina), length(ALSA_ds_w12$h_angina)
             )
names(tt)<-c("val", "label", "w6", "w11", "w12")
kable(tt)

dbb <- merge(ALSA_m_ds_w6[,c("id","h_angina")], ALSA_m_ds_w11[,c("id","h_angina")], by="id", suffixes = c(".w6",".w11"), all=T)
dbb <- merge(dbb, ALSA_m_ds_w12[,c("id","h_angina")], by="id", all=T)
names(dbb) <- c("id", "w6", "w11", "w12")
v.dbb <- paste(dbb[,2],dbb[,3],dbb[,4],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])
```



# Quality estimation

* We assume that if an individual answers it has angina in one wave, it has for all the next waves. Individuals with discrepancies with respect to this criterium are specified at the end of each validation.


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.ALSA <- list(w6 = ALSA_ds_w6, w11 = ALSA_ds_w11, w12 = ALSA_ds_w12)

for(index in seq_along(l.ALSA)){
  h_angina <- l.ALSA[[index]]
  save(h_angina, file = paste0(datafolder,names(l.ALSA)[index],"/h_angina.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





