---
title: "Myocardial infarction or heart attack"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/mi_haDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/mi_haDS.R')
```


# Data process



## Australia


### Wave 1


#### Study-specific variable description

| **Name** | `MORBID14` |`DIAGYR14`|`ybirth`|
|-|-|-|-|
| **Label** | `Heart attack` |`Year of diagnosis: Heart attack`|`Year of birth`|
| **Table name**  | `ALSA-Wave1` | `ALSA-Wave1` |`ybirth`|
| **Categories** | `0 = No`<br/>`1 = Yes` | `continuous` | `continuous` |
| **Missings** |  | `NA` |   |
| **Description** |  |  |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'ALSA_w1','ALSA.ALSA-Wave1',variables=list('MORBID14','DIAGYR14'), missings = T)
ALSA_w1 <- opal.execute(o,'ALSA_w1')
load(paste0(datafolder,"w1/ybirth.RData"))
ALSA_w1 <- left_join(ALSA_w1,ybirth, by="id")

```

```{r local w1, echo=F}

vbl <- ALSA_w1$MORBID14
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w1, aes(x=factor(MORBID14))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w1$DIAGYR14
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(ALSA_w1)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_w1, aes(DIAGYR14)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1915,1995)

vbl <- ALSA_w1$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(ALSA_w1)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_w1, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1885,1930)

```


#### Harmonisation algorithm

To compute `mi_ha` from the study-specific variable it has to be recoded as follows:

* `keep up 0 into 0`
* `keep up 1 into 1`

To compute `mi_ha_age` from the study-specific variable it has to be recoded as follows:

* `if mi_ha == 1, mi_ha_age = DIAGYR14 - ybirth`
* `if mi_ha == 0, mi_ha_age = 996`
* `otherwise into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
ALSA_ds_w1 <- tibble(id=ALSA_w1$id)
ALSA_ds_w1$mi_ha <- car::recode(ALSA_w1$MORBID14, "NA = 999")

# Continuous variable harmonization
mi_ha_age <- ALSA_w1$DIAGYR14[which(ALSA_ds_w1$mi_ha == 1)]-ALSA_w1$ybirth[which(ALSA_ds_w1$mi_ha == 1)]
ALSA_ds_w1$mi_ha_age <- car::recode(ALSA_ds_w1$mi_ha, "0 = 996; 1 = mi_ha_age")
ALSA_ds_w1$mi_ha_age <- car::recode(ALSA_ds_w1$mi_ha_age,"NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- ALSA_ds_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w1, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ALSA_ds_w1$mi_ha_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w1, aes(mi_ha_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(5,95)

```


#### Validation

```{r crosstabulation w1, echo=F}

continuous <- c(sum(ALSA_ds_w1$mi_ha_age==996,na.rm=T),sum(ALSA_ds_w1$mi_ha_age!=996,na.rm=T))
X <- table(ALSA_ds_w1$mi_ha, useNA = "ifany")
dichotomous <- c(X[1],sum(X[2:3],na.rm=T))
C <- rbind(continuous,dichotomous)
colnames(C) <- c("0<-->996","1<-->(possibly missing) age of diagnostic")
kable(C,caption = "Continuous vs Dichotomous")

```



### Wave 2

Not found.




### Wave 3


#### Study-specific variable description

| **Name** | `W1CDN14` |
|-|-|
| **Label** | `HEART ATTACK` |
| **Table name**  | `ALSA-Wave3` |
| **Categories** | `1 = Yes`<br/>`2 = No` |
| **Missings** | `9`<br/>`NA` |
| **Description** |  |

```{r assign w3, echo=F}

opal.assign.table.tibble(o, 'ALSA_w3','ALSA.ALSA-Wave3',variables=list('W1CDN14'), missings = T)
ALSA_w3 <- opal.execute(o,'ALSA_w3')

```

```{r local w3, echo=F}

vbl <- ALSA_w3$W1CDN14
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w3)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w3, aes(x=factor(W1CDN14))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `mi_ha` from the study-specific variable it has to be recoded as follows:

* `change 2 into 0`
* `keep up 1 into 1`
* `otherwise into 999`

Age of diagnostic cannot be harmonized.

**R script:**

```{r harmo w3}

ALSA_ds_w3 <- tibble(id=ALSA_w3$id)
ALSA_ds_w3$mi_ha <- car::recode(ALSA_w3$W1CDN14, "2=0;9=999;NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript w3, echo=F}

vbl <- ALSA_ds_w3$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w3, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w3, echo=F, results='asis'}

AfterH <- table(ALSA_ds_w3$mi_ha)
X <- table(ALSA_w3$W1CDN14, useNA = "ifany")
BeforeH <- c(X[2:1],sum(X[3:4]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","9,NA->999")
kable(C)

```

### Wave 4

Not found.

### Wave 5

Not found.



### Wave 6


#### Study-specific variable description

| **Name** | `CDN25_W6` |`DIA25_W6`|`ybirth`|
|-|-|-|-|
| **Label** | `Heart attack` |`year told of condition: Heart attack`|`Year of birth`|
| **Table name**  | `ALSA-Wave6` | `ALSA-Wave6` |`ybirth`|
| **Categories** | `0 = no`<br/>`1 = yes` |`continuous`|`continuous`|
| **Missings** | `NA` |`NA`|  |
| **Description** |  |  |  |

```{r assign w6, echo=F}

opal.assign.table.tibble(o, 'ALSA_w6','ALSA.ALSA-Wave6',variables=list('CDN25_W6','DIA25_W6'), missings = T)
ALSA_w6 <- opal.execute(o,'ALSA_w6')
ALSA_w6$DIA25_W6 <- as.numeric(ALSA_w6$DIA25_W6)
load(paste0(datafolder,"w6/ybirth.RData"))
ALSA_w6 <- left_join(ALSA_w6,ybirth, by="id")

```

```{r local w6, echo=F}

vbl <- ALSA_w6$CDN25_W6
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w6)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w6, aes(x=factor(CDN25_W6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w6$DIA25_W6
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(ALSA_w6)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_w6, aes(DIA25_W6)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1965,2005)

vbl <- ALSA_w6$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(ALSA_w6)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_w6, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1895,1930)

```


#### Harmonisation algorithm

To compute `mi_ha` from the study-specific variable it has to be recoded as follows:

* `keep up 0 into 0`
* `keep up 1, ensuring it does not correspond to previous waves, into 1`
* `otherwise into 999`

To compute `mi_ha_age` from the study-specific variable it has to be recoded as follows:

* `if mi_ha == 1, mi_ha_age = DIA25_W6 - ybirth`
* `if mi_ha == 0, mi_ha_age = 996`
* `otherwise into 999`

**R script:**

```{r harmo w6}

ALSA_w6 <- left_join(ALSA_w6,ALSA_w1, by="id",suffix=c("","_w1"))
ALSA_w6 <- left_join(ALSA_w6,ALSA_w3, by="id")

ALSA_ds_w6 <- tibble(id=ALSA_w6$id)
ALSA_ds_w6$mi_ha <- rep(999,length(ALSA_w6$id))
ALSA_ds_w6$mi_ha[which(ALSA_w6$CDN25_W6==0)] <- 0
# Individuals having mi_ha since wave 3, so their year of diagnostic is at least 1994 or missing but until later previous wave interviewed they had no mi_ha.
ALSA_ds_w6$mi_ha[which(ALSA_w6$CDN25_W6==1 & (ALSA_w6$DIA25_W6>=1994 | ALSA_w6$W1CDN14==2 | (is.na(ALSA_w6$W1CDN14) & ALSA_w6$MORBID14==0)))] <- 1

# Continuous variable harmonization
ALSA_ds_w6$mi_ha_age <- rep(999,length(ALSA_w6$id))
ALSA_ds_w6$mi_ha_age[which(ALSA_ds_w6$mi_ha==0)] <- 996
ALSA_ds_w6$mi_ha_age[which(ALSA_ds_w6$mi_ha==1 & ALSA_w6$DIA25_W6>=1994)] <- ALSA_w6$DIA25_W6[which(ALSA_ds_w6$mi_ha == 1 & ALSA_w6$DIA25_W6>=1994)] - ALSA_w6$ybirth[which(ALSA_ds_w6$mi_ha == 1 & ALSA_w6$DIA25_W6>=1994)]
ALSA_ds_w6$mi_ha_age <- car::recode(ALSA_ds_w6$mi_ha_age,"NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w6, echo=F}

vbl <- ALSA_ds_w6$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w6, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- ALSA_ds_w6$mi_ha_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w6, aes(mi_ha_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(70,95)

```


#### Validation

```{r crosstabulation w6, echo=F, results='asis'}

AfterH <- table(ALSA_ds_w6$mi_ha)
X <- c(
  sum(ALSA_w6$CDN25_W6==0,na.rm=T),
  sum(ALSA_w6$CDN25_W6==1 & (ALSA_w6$DIA25_W6>=1994 | ALSA_w6$W1CDN14==2 | (is.na(ALSA_w6$W1CDN14) & ALSA_w6$MORBID14==0)),na.rm=T)
)
BeforeH <- c(X[2],length(ALSA_w6$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->1","NA->999")
kable(C)

cat("There are seven individuals which told they had myocardial infarction in the first and the present waves and in the last one give year of diagnosis previous to first wave. We harmonize as having myocardial infarction but keep missing age of diagnosis the individual which told in third wave did not have a heart attack.")
kable(ALSA_w6[which(ALSA_w6$DIA25_W6<1994),], align = 'c')
```



### Wave 7


Not found.



### Wave 8

Not found.



### Wave 9

Not found.


### Wave 10

Not found.



### Wave 11


#### Study-specific variable description

| **Name** | `HCDN1W11` |
|-|-|
| **Label** | `Heart Attack` |
| **Table name**  | `ALSA-Wave11` |
| **Categories** | `0 = No`<br/>`1 = Yes` |
| **Missings** |`NA`|
| **Description** |  |

```{r assign w11, echo=F}

opal.assign.table.tibble(o, 'ALSA_w11','ALSA.ALSA-Wave11',variables=list('HCDN1W11'), missings = T)
ALSA_w11 <- opal.execute(o,'ALSA_w11')

```

```{r local w11, echo=F}

vbl <- ALSA_w11$HCDN1W11
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w11)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w11, aes(x=factor(HCDN1W11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `mi_ha` from the study-specific variable it has to be recoded as follows:

* `keep up 0 into 0`
* `keep up 1 into 1`
* `NA into 999`

Age of diagnostic cannot be harmonized.

**R script:**

```{r harmo w11}

ALSA_ds_w11 <- tibble(id=ALSA_w11$id)
ALSA_ds_w11$mi_ha <- car::recode(ALSA_w11$HCDN1W11,"NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w11, echo=F}

vbl <- ALSA_ds_w11$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w11, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w11, echo=F, results='asis'}

AfterH <- table(ALSA_ds_w11$mi_ha)
BeforeH <- table(ALSA_w11$HCDN1W11, useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999")
kable(C)

```



### Wave 12


#### Study-specific variable description

| **Name** | `HCDN1W12` |
|-|-|
| **Label** | `Heart Attack`|
| **Table name**  | `ALSA-Wave12` |
| **Categories** |  `0 = No`<br/>`1 = Yes` |
| **Description** |  |

```{r assign w12, echo=F}

opal.assign.table.tibble(o, 'ALSA_w12','ALSA.ALSA-Wave12',variables=list('HCDN1W12'), missings = T)
ALSA_w12 <- opal.execute(o,'ALSA_w12')

```

```{r local w12, echo=F}

vbl <- ALSA_w12$HCDN1W12
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w12)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w12, aes(x=factor(HCDN1W12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `mi_ha` from the study-specific variable it has to be recoded as follows:

* `keep up 0 into 0`
* `keep up 1 into 1`
* `NA into 999`

Age of diagnostic cannot be harmonized.

**R script:**

```{r harmo w12}

ALSA_ds_w12 <- tibble(id=ALSA_w12$id)
ALSA_ds_w12$mi_ha <- car::recode(ALSA_w12$HCDN1W12,"NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w12, echo=F}

vbl <- ALSA_ds_w12$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w12, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w12, echo=F, results='asis'}

AfterH <- table(ALSA_ds_w12$mi_ha)
BeforeH <- table(ALSA_w12$HCDN1W12, useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999")
kable(C)

```



### Wave 13

Not found.


<!--
```{r summary, include=F, eval=F, echo=F}
kable(ALSA_ds[ALSA_ds$id %in% strange_id,], align = 'c', caption = 'Individuals with discrepancies')
```
-->

<!--AUXILIAR FUNCTIONS-->



```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds,vbl_name,ds_lab = ds_label){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    if(vbl_name %in% names(l.hds[[name]])){
      # In the aux_object we copy the old tibble to recodify all missing values as NA.
      aux_object <- l.hds[[name]]
      # Labelling of variables
      label(l.hds[[name]][[vbl_name]]) <- label(aux_object[[vbl_name]]) <- ds_lab
      # Labelling of categories (for continues variables, only missing values)
      l.hds[[name]][[vbl_name]] <- labelled(l.hds[[name]][[vbl_name]], labels = cat_label)
      aux_object[[vbl_name]] <- car::recode(aux_object[[vbl_name]], "miss_values_vector=NA")
      # Labelling of categories (for categorical variables, only non-missing values)
      aux_object[[vbl_name]] <- labelled(aux_object[[vbl_name]], labels = cat_label[1:(length(cat_label)-9)])
      # Saving the recodified tibble in list m.hds
      m.hds[[name]] <- aux_object
      rm(aux_object)
    }
  }
  return(list(l.hds,m.hds))

}


labelling_c <- function(l.hds,m.hds,vbl_name,ds_lab=ds_label){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    if(vbl_name %in% names(l.hds[[name]])){
      # In the aux_object we copy the old tibble to recodify all missing values as NA.
      aux_object <- m.hds[[name]]
      # Labelling of variables
      label(l.hds[[name]][[vbl_name]]) <- label(aux_object[[vbl_name]]) <- ds_lab
      # Labelling of categories (for continues variables, only missing values)
      l.hds[[name]][[vbl_name]] <- labelled(l.hds[[name]][[vbl_name]], labels = cont_label)
      aux_object[[vbl_name]] <- car::recode(aux_object[[vbl_name]], "miss_values_vector=NA")
      aux_object[[vbl_name]] <- remove_val_labels(aux_object[[vbl_name]])
      # Saving the recodified tibble in list m.hds
      m.hds[[name]] <- aux_object
      rm(aux_object)
    }
  }
  return(list(l.hds,m.hds))

}


# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames,vbl_name){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][vbl_name])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][vbl_name])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[2+length(cat_label),] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}


# Creation of summary tables for continuous data

summaries_c <- function(l.hds,m.hds,lnames,vbl_name){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][vbl_name])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[vbl_name]], missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][vbl_name])[1:6]
    # Next, missing/no-missing values (the 1 in $values_table[1,] stands for absolute values, while a 2 would stand for percentages)
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[vbl_name]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][vbl_name]))[[2]],lnames)
  return(t.hds)
  
}



# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }
  
}

```



```{r populations-waves, echo=F}


# All study waves and populations with abbreviated and descriptive names

alsa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"), w6 = c("w6","W6"), w7 = c("w7","W7"), w8 = c("w8","W8"), w9 = c("w9","W9"), w10 = c("w10","W10"), w11 = c("w11","W11"), w12 = c("w12","W12"), w13 = c("w13","W13"))



```


<!--Labelling and saving-->

```{r, echo=FALSE}


# Consider only waves with some variable harmonised

l.hds <- lapply(alsa.cw, function(wname) if(exists(paste0("ALSA_ds_",wname[1]))){wname = list(get(paste0("ALSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling categorical variable of tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]],hd_vbl,ds_label)
  # Labelling continuous variable of tibbles
  lmlist <- labelling_c(lmlist[[1]],lmlist[[2]],hd_age_vbl,ds_label_age)
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}

alsalist <- lmlist # ALSA list




```



<!--Descriptives-->

## Descriptive statistics of the harmonised variable `mi_ha` accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.

```{r summ, echo=F}


# Consider only harmonised waves
l.hds <- lapply(alsa.cw, function(wname) if(hd_vbl %in% names(get0(paste0("ALSA_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- alsalist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- alsalist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))

}



```






## Summary of descriptive statistics of the harmonised variable `mi_ha_age` accross populations and waves






```{r summ_c, echo=F}


# Consider only harmonised waves
l.hds <- lapply(alsa.cw, function(wname) if(hd_age_vbl %in% names(get0(paste0("ALSA_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- alsalist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- alsalist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries_c(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_age_vbl),caption=ds_label_age))
}





```


# Quality estimation

No comments







<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





