---
title: "Year of death"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `ydeath`
* Variable label: `Year of death`
* Variable description: `year of death`
* Domain: `Death`
* Value type: `continous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


```{r lab, echo=FALSE}
ds_label <- "Year of death"
```


# Data process

## Adachi-Kanazawa-Shirakawa-Sendai-Takikawa

### Wave 1

There is no variable. 



### Wave 2

#### Study-specific variable description

The study-specific variables elected to be harmonised are:

| **Name** | `ex_4_b`|
|-|-|
| **Label** | `EX-4:WHEN THE SUBJECT PERSON PASSED AWAY, YEAR`|
| **Table name** | `jstar_2009_5cities` |
| **Description** |  |


```{r read_aksst2, include=FALSE}
opal.assign.table.tibble(o, 'JSTAR_death','JSTAR_datasets_restricted.jstar_2009_5cities', variables=list( 'ex_4_b'), missings = TRUE)
JSTAR_death <- opal.execute(o,'JSTAR_death')
```

```{r local_aksst2, echo=F}
vari <- JSTAR_death$ex_4_b
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_death, aes(x=factor(ex_4_b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_aksst2}
JSTAR_aksst_ds_w2 <- tibble(id=JSTAR_death$id)
JSTAR_aksst_ds_w2$ydeath <- car::recode(JSTAR_death$ex_4_b, "NA=999")
JSTAR_aksst_ds_w2$ydeath <- labelled(JSTAR_aksst_ds_w2$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_aksst2, echo=F}
vari <- JSTAR_aksst_ds_w2$ydeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_aksst_ds_w2, aes(x=factor(ydeath))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_aksst2, echo=F}
BeforeH <- table(JSTAR_death[[2]], useNA = "ifany")
AfterH <- table(JSTAR_aksst_ds_w2$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```




### Wave 3

#### Study-specific variable description

The study-specific variables elected to be harmonised are:

| **Name** | `ex_4_f`|
|-|-|
| **Label** | `11EX-4:DATE THE SUBJECT PERSON PASSED AWAY, YEAR`|
| **Table name** | `jstar_2011_5cities` |
| **Description** |  |


    
```{r read_aksst3, include=FALSE}
opal.assign.table.tibble(o, 'JSTAR_death','JSTAR_datasets_restricted.jstar_2011_5cities', variables=list('ex_4_f'), missings = TRUE)
JSTAR_death <- opal.execute(o,'JSTAR_death')
```

```{r local_aksst3, echo=F}
vari <- JSTAR_death$ex_4_f
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_death, aes(x=factor(ex_4_f))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_aksst3}
JSTAR_aksst_ds_w3 <- tibble(id=JSTAR_death$id)
JSTAR_aksst_ds_w3$ydeath <- car::recode(JSTAR_death$ex_4_f, "NA=999")
JSTAR_aksst_ds_w3$ydeath <- labelled(JSTAR_aksst_ds_w3$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_aksst3, echo=FALSE}
vari <- JSTAR_aksst_ds_w3$ydeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_aksst_ds_w3, aes(x=factor(ydeath))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_aksst3, echo=FALSE}
BeforeH <- table(JSTAR_death[[2]], useNA = "ifany")
AfterH <- table(JSTAR_aksst_ds_w3$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```



## Tosu-Naha

### Wave 1

There is no variable. 


### Wave 2

#### Study-specific variable description

The study-specific variables elected to be harmonised are:

| **Name** | `ex_4_f`|
|-|-|
| **Label** | `11EX-4:DATE THE SUBJECT PERSON PASSED AWAY, YEAR`|
| **Table name** | `jstar_2011_2cities` |
| **Description** |  |

    
```{r read_tn2, include=FALSE}
opal.assign.table.tibble(o, 'JSTAR_death','JSTAR_datasets_restricted.jstar_2011_2cities', variables=list('ex_4_f'), missings = TRUE)
JSTAR_death <- opal.execute(o,'JSTAR_death')
```

```{r local_tn2, echo=F}
vari <- JSTAR_death$ex_4_g
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_death, aes(x=factor(ex_4_f))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**


```{r harmo_tn2}
JSTAR_tn_ds_w2 <- tibble(id=JSTAR_death$id)
JSTAR_tn_ds_w2$ydeath <- car::recode(JSTAR_death$ex_4_f, "NA=999")
JSTAR_tn_ds_w2$ydeath <- labelled(JSTAR_tn_ds_w2$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_tn2, echo=FALSE}
vari <- JSTAR_tn_ds_w2$ydeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_tn_ds_w2, aes(x=factor(ydeath))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_tn2, echo=FALSE}
BeforeH <- table(JSTAR_death[[2]], useNA = "ifany")
AfterH <- table(JSTAR_tn_ds_w2$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





## Chofu-Tondabayashi-Hiroshima

### Wave 1

There is no variable. 


<!--- ######################### Import to OPAL #######################-->
```{r importOPAL, echo=FALSE}
ydeath <- JSTAR_aksst_ds_w2
save(ydeath, file = "../RData/aksst_w2/ydeath.RData")
rm(ydeath)

ydeath <- JSTAR_aksst_ds_w3
save(ydeath, file = "../RData/aksst_w3/ydeath.RData")
rm(ydeath)

ydeath <- JSTAR_tn_ds_w2
save(ydeath, file = "../RData/tn_w2/ydeath.RData")
rm(ydeath)
```



# Quality estimation

No comments

[...]


```{r closeRsession, echo=FALSE}
opal.logout(o)
```

