---
title: "Living Status"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/living_statusDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/living_statusDS.R')
```



# Data process



## Adachi-Kanazawa-Shirakawa-Sendai-Takikawa

### Wave 1

All participants are alive at the baseline.

```{r read_aksst1, include=FALSE}
opal.assign.table.tibble(o, 'ds.ls','JSTAR_datasets_restricted.jstar_2007_5cities', variables=list('a_000_0'), missings = TRUE)
ds.ls <- opal.execute(o,'ds.ls')
```


#### Harmonisation algorithm

The harmonized variable is all 0.
 
**R script:**

```{r harmo_aksst1}
JSTAR_ds_aksst_w1 <- tibble(id=ds.ls$id)
JSTAR_ds_aksst_w1$living_status <- 0
```

#### Statistical description of the new harmonised variable
```{r descript_aksst1, echo=F}
vbl <- JSTAR_ds_aksst_w1$living_status
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w1, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


### Wave 2

#### Study-specific variable description



| **Name** |`k_000`|`nonresponse`|`ex_4_b`|
|-|-|-|-|
| **Label** |`STATUS OF THE SURVEY SUBJECT`|`REASON OF NONRESPONSE`|`EX-4:WHEN THE SUBJECT PERSON PASSED AWAY, YEAR`|
| **Table name** |`jstar_2009_5cities`|`jstar_2009_5cities`|`jstar_2009_5cities`|
| **Categories** |`1 = Alive and he/she (or his/her relative) can answer`<br/>`2 = Alive but he/she cannot answer`<br/>`3 = Deceased/absence and his/her relative can answer`<br/>`4 = Whereabouts unknown and he/she or his/her relative cannot answer`<br/>`5 = Other (specify)`|`1 = move`<br/>`2 = long absence`<br/>`3 = absence`<br/>`4 = refusal`<br/>`5 = adress unknown`<br/>`6 = not aligible`<br/>`7 = unknown`|`Continuous`|
| **Missings** |`NA`|`NA`|  |
| **Description** |  |  |  |




```{r read_aksst2, include=FALSE}
opal.assign.table.tibble(o, 'ds.ls','JSTAR_datasets_restricted.jstar_2009_5cities', variables=list('k_000', 'nonresponse', 'ex_4_b'), missings = TRUE)
ds.ls <- opal.execute(o,'ds.ls')
```

```{r local_aksst2, echo=F}
vbl <- ds.ls[[3]]
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ds.ls)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ds.ls, aes(x=factor(ds.ls[[4]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("STATUS OF THE SURVEY SUBJECT") + ylab("Frequency")

vbl <- ds.ls[[4]]
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ds.ls)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ds.ls, aes(x=factor(ds.ls[[4]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("REASON OF NONRESPONSE") + ylab("Frequency")

kable(table(ds.ls[[3]],ds.ls[[4]], useNA="ifany"))

vbl <- ds.ls[[2]]
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ds.ls)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ds.ls, aes(x=factor(ds.ls[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of death") + ylab("Frequency")

kable(table(ds.ls[[2]],ds.ls[[3]], useNA="ifany"))
```

#### Harmonisation algorithm

Only variable "k_000"" is used. Variables "nonresponse" and "ex_4_b" were to verify whether "k_000" was reliable.

Values are recoded as follows:

* `if k_000 = 1 or 2 => living_status = 0 (alive)`
* `if k_000 = 3 => living_status = 1 (died)`
* `if k_000 = 4, 5 or NA => living_status = 2 (dropout)`

**R script:**

```{r harmo_aksst2}
JSTAR_ds_aksst_w2 <- tibble(id=ds.ls$id)
JSTAR_ds_aksst_w2$living_status <- car::recode(ds.ls[[3]], "c(1,2)=0; 3=1; c(4,5,NA)=2")
```

#### Statistical description of the new harmonised variable
```{r descript_aksst2, echo=F}
vbl <- JSTAR_ds_aksst_w2$living_status
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w2, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_aksst2, echo=F}

newT <- full_join( ds.ls[c(1,3)], JSTAR_ds_aksst_w2, by="id")
unclass(with(newT, table(k_000, living_status, useNA="ifany")))

```


### Wave 3

#### Study-specific variable description


| **Name** |`k_000`|`ex_4_f`|
|-|-|-|
| **Label** |`11K-000:STATUS OF THE SURVEY SUBJECT`|`EX-4:WHEN THE SUBJECT PERSON PASSED AWAY, YEAR`|
| **Table name** |`jstar_2011_5cities`|`jstar_2011_5cities`|`jstar_2011_5cities`|
| **Categories** |`1 = Alive and eligible to respond`<br/>`2 = Alive but ineligible to respond; his/her proxy will respond`<br/>`3 = Alive but refused to cooperate`<br/>`4 = Deceased but his/her proxy (family members, relatives, etc.) will cooperate`<br/>`5 = Whereabouts unknown`<br/>`6 = Other`|`Continuous`|
| **Missings** |`NA`|  |
| **Description** |  |  |


    
```{r read_aksst3, include=FALSE}
opal.assign.table.tibble(o, 'ds.ls','JSTAR_datasets_restricted.jstar_2011_5cities', variables=list('k_000', 'ex_4_f'), missings = TRUE)
ds.ls <- opal.execute(o,'ds.ls')
```

```{r local_aksst3, echo=F}
vbl <- ds.ls[[3]]
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ds.ls)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ds.ls, aes(x=factor(ds.ls[[3]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("STATUS OF THE SURVEY SUBJECT") + ylab("Frequency")

vbl <- ds.ls[[2]]
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ds.ls)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ds.ls, aes(x=factor(ds.ls[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of death") + ylab("Frequency")

kable(table(ds.ls[[2]],ds.ls[[3]], useNA="ifany"))
```

#### Harmonisation algorithm

Only variable "k_000"" is used. Variable "ex_4_f" was to verify whether "k_000" was reliable.

Values are recoded as follows:

* `if k_000 = 1, 2 or 3 => living_status = 0 (alive)`
* `if k_000 = 4 => living_status = 1 (died)`
* `if k_000 = 5, 6 or NA => living_status = 2 (dropout)`
 
 **R script:**

```{r harmo_aksst3}
JSTAR_ds_aksst_w3 <- tibble(id=ds.ls$id)
JSTAR_ds_aksst_w3$living_status <- car::recode(ds.ls[[3]], "c(1,2,3)=0; 4=1; c(5,6,NA)=2")
```

#### Statistical description of the new harmonised variable
```{r descript_aksst3, echo=F}
vbl <- JSTAR_ds_aksst_w3$living_status
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w3, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_aksst3, echo=F}
newT <- full_join( ds.ls[c(1,3)], JSTAR_ds_aksst_w3, by="id")
kable(with(newT, table(k_000, living_status, useNA="ifany")))
```

### Validation throughout waves

```{r valid_ws_hrs, echo=F}
dbb <- merge(JSTAR_ds_aksst_w1, JSTAR_ds_aksst_w2, by = "id", suffixes = c(".w1", ".w2"), all = T)
dbb <- merge(dbb, JSTAR_ds_aksst_w3, by = "id", all = T)
names(dbb) <- c("id", "w1", "w2", "w3")
v.dbb <- paste(dbb[, 2], dbb[, 3], dbb[, 4], sep = "")
f.dbb <- frq(v.dbb)[[1]][, c(1, 2, 4)]
kable(f.dbb)
```


## Tosu-Naha

### Wave 1

All participants are alive at the baseline.

```{r read_tn1, include=FALSE}
opal.assign.table.tibble(o, 'ds.ls','JSTAR_datasets_restricted.jstar_2009_2cities', variables=list('a_000_0'), missings = TRUE)
ds.ls <- opal.execute(o,'ds.ls')
```

#### Harmonisation algorithm

The harmonize variable is all 0.

**R script:**

```{r harmo_tn1}
JSTAR_ds_tn_w1 <- tibble(id=ds.ls$id)
JSTAR_ds_tn_w1$living_status <- 0
```

#### Statistical description of the new harmonised variable
```{r descript_tn1, echo=F}
vbl <- JSTAR_ds_tn_w1$living_status
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_tn_w1, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


### Wave 2

#### Study-specific variable description


| **Name** |`k_000`|`ex_4_f`|
|-|-|-|
| **Label** |`11K-000:STATUS OF THE SURVEY SUBJECT`|`EX-4:WHEN THE SUBJECT PERSON PASSED AWAY, YEAR`|
| **Table name** |`jstar_2011_2cities`|`jstar_2011_2cities`|`jstar_2011_2cities`|
| **Categories** |`1 = Alive and eligible to respond`<br/>`2 = Alive but ineligible to respond; his/her proxy will respond`<br/>`3 = Alive but refused to cooperate`<br/>`4 = Deceased but his/her proxy (family members, relatives, etc.) will cooperate`<br/>`5 = Whereabouts unknown`<br/>`6 = Other`|`Continuous`|
| **Missings** |`NA`|  |
| **Description** |  |  |



    
```{r read_tn2, include=FALSE}
opal.assign.table.tibble(o, 'ds.ls','JSTAR_datasets_restricted.jstar_2011_2cities', variables=list('k_000', 'ex_4_f'), missings = TRUE)
ds.ls <- opal.execute(o,'ds.ls')
```

```{r local_tn2, echo=F}
vbl <- ds.ls[[3]]
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ds.ls)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ds.ls, aes(x=factor(ds.ls[[3]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("STATUS OF THE SURVEY SUBJECT") + ylab("Frequency")

vbl <- ds.ls[[2]]
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ds.ls)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ds.ls, aes(x=factor(ds.ls[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of death") + ylab("Frequency")

kable(table(ds.ls[[2]],ds.ls[[3]], useNA="ifany"))
```

#### Harmonisation algorithm

Only variable "k_000"" is used. Variable "ex_4_f" was to verify whether "k_000" was reliable.

Values are recoded as follows:

* `if k_000 = 1, 2 or 3 => living_status = 0 (alive)`
* `if k_000 = 4 => living_status = 1 (died)`
* `if k_000 = 5, 6 or NA => living_status = 2 (dropout)`

**R script:**

```{r harmo_tn2}
JSTAR_ds_tn_w2 <- tibble(id=ds.ls$id)
JSTAR_ds_tn_w2$living_status <- car::recode(ds.ls[[3]], "c(1,2,3)=0; 4=1; c(5,6,NA)=2")
```

#### Statistical description of the new harmonised variable
```{r descript_tn2, echo=F}
vbl <- JSTAR_ds_tn_w2$living_status
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_tn_w2, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_tn2, echo=F}
newT <- full_join( ds.ls[c(1,3)], JSTAR_ds_tn_w2, by="id")
kable(with(newT, table(k_000, living_status, useNA="ifany")))
```

### Validation throughout waves

```{r valid_ws_tn, echo=F}
dbb <- merge(JSTAR_ds_tn_w1, JSTAR_ds_tn_w2, by = "id", suffixes = c(".w1", ".w2"), all = T)
names(dbb) <- c("id", "w1", "w2")
v.dbb <- paste(dbb[, 2], dbb[, 3], sep = "")
f.dbb <- frq(v.dbb)[[1]][, c(1, 2, 4)]
kable(f.dbb)
```




## Chofu-Tondabayashi-Hiroshima

### Wave 1

All participants are alive at the baseline.

```{r read_cth1, include=FALSE}
opal.assign.table.tibble(o, 'ds.ls','JSTAR_datasets_restricted.jstar_2011_3cities', variables=list('a_000_0'), missings = TRUE)
ds.ls <- opal.execute(o,'ds.ls')
```

#### Harmonisation algorithm

The harmonize variable is all 0.

**R script:**

```{r harmo_cth1}
JSTAR_ds_cth_w1 <- tibble(id=ds.ls$id)
JSTAR_ds_cth_w1$living_status <- 0
```

#### Statistical description of the new harmonised variable
```{r descript_cth1, echo=F}
vbl <- JSTAR_ds_cth_w1$living_status
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_cth_w1, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```







## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable by cohort:





```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:3])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[14,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}


# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


jstar.cw <- list(aksst_w1 = c("aksst_w1","AKSST w1"), aksst_w2 = c("aksst_w2","AKSST w2"), aksst_w3 = c("aksst_w3","AKSST w3"), tn_w1 = c("tn_w1","TN w1"), tn_w2 = c("tn_w2","TN w2"), cth_w1 = c("cth_w1","CTH w1"))

# Consider only harmonised waves
l.hds <- lapply(jstar.cw, function(wname) if(exists(paste0("JSTAR_ds_",wname[1]))){wname = list(get(paste0("JSTAR_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```









# Quality estimation
No comments.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```

