---
title: "Living status"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ############################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_albert.r")
```
<!-- ############################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `living_status`
* Variable label: `Living status`
* Variable description: `The individual is dead or alive?`
* Domain: `Life expectancy`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | alive
1        | dead
2        | dropout / unknown


# Data process

```{r lab, echo=FALSE}
ds_label <- "Living status"
v_label <- c("Alive"=0, "Dead"=1, "Dropout"=2)
```

## Adachi-Kanazawa-Shirakawa-Sendai-Takikawa

### Wave 1

All participants are alive at the baseline.

```{r read_aksst1, include=FALSE}
opal.assign.table.tibble(o, 'ds.ls','JSTAR_datasets_restricted.jstar_2007_5cities', variables=list('a_000_0'), missings = TRUE)
ds.ls <- opal.execute(o,'ds.ls')
```


#### Harmonisation algorithm

The harmonize variable is all 0.
 
**R script:**

```{r harmo_aksst1}
JSTAR_aksst_ds_w1 <- tibble(id=ds.ls$id)
JSTAR_aksst_ds_w1$living_status <- 0
JSTAR_aksst_ds_w1$living_status <- labelled(JSTAR_aksst_ds_w1[[2]], labels = v_label)
```

#### Statistical description of the new harmonised variable
```{r descript_aksst1, echo=F}
Categorical_summary(var = JSTAR_aksst_ds_w1[[2]])
ggplot(JSTAR_aksst_ds_w1, aes(x=as_factor(JSTAR_aksst_ds_w1[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


### Wave 2

#### Study-specific variable description

The study-specific variables elected to be harmonised are:

* Name: `k_000`
* Label: `STATUS OF THE SURVEY SUBJECT`
* Categories: 
    + `1 = Alive and he/she (or his/her relative) can answer`
    + `2 = Alive but he/she cannot answer`
    + `3 = Deceased/absence and his/her relative can answer`
    + `4 = Whereabouts unknown and he/she or his/her relative cannot answer`
    + `5 = Other (specify)`
* Missings
   + `NA` 
   
* Name: `nonresponse`
* Label: `REASON OF NONRESPONSE`
* Categories: 
    + `1 = move`
    + `2 = long absence`
    + `3 = absence`
    + `4 = refusal`
    + `5 = adress unknown`
    + `6 = not aligible`
    + `7 = unknown`
* Missings
   + `NA` 

* Name: `ex_4_b`
* Label: `EX-4:WHEN THE SUBJECT PERSON PASSED AWAY, YEAR`
* Type: `Continuous`


```{r read_aksst2, include=FALSE}
opal.assign.table.tibble(o, 'ds.ls','JSTAR_datasets_restricted.jstar_2009_5cities', variables=list('k_000', 'nonresponse', 'ex_4_b'), missings = TRUE)
ds.ls <- opal.execute(o,'ds.ls')
```

```{r local_aksst2, echo=F}
Categorical_summary(ds.ls[[3]])
ggplot(ds.ls, aes(x=as_factor(ds.ls[[4]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("STATUS OF THE SURVEY SUBJECT") + ylab("Frequency")

Categorical_summary(ds.ls[[4]])
ggplot(ds.ls, aes(x=as_factor(ds.ls[[4]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("REASON OF NONRESPONSE") + ylab("Frequency")

table(ds.ls[[3]],ds.ls[[4]], useNA="ifany")

Categorical_summary(ds.ls[[2]])
ggplot(ds.ls, aes(x=factor(ds.ls[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of death") + ylab("Frequency")

table(ds.ls[[2]],ds.ls[[3]], useNA="ifany")
```

#### Harmonisation algorithm

Only variable "k_000"" is used. Variables "nonresponse" and "ex_4_b" were to verify whether "k_000" was reliable.

Values are recoded as follows:

* `if k_000 = 1 or 2 => living_status = 0 (alive)`
* `if k_000 = 3 => living_status = 1 (died)`
* `if k_000 = 4, 5 or NA => living_status = 2 (dropout)`

**R script:**

```{r harmo_aksst2}
JSTAR_aksst_ds_w2 <- tibble(id=ds.ls$id)
JSTAR_aksst_ds_w2$living_status <- car::recode(ds.ls[[3]], "c(1,2)=0; 3=1; c(4,5,NA)=2")
JSTAR_aksst_ds_w2$living_status <- labelled(JSTAR_aksst_ds_w2[[2]], labels = v_label)
```

#### Statistical description of the new harmonised variable
```{r descript_aksst2, echo=F}
Categorical_summary(var = JSTAR_aksst_ds_w2[[2]])
ggplot(JSTAR_aksst_ds_w2, aes(x=as_factor(JSTAR_aksst_ds_w2[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_aksst2, echo=F}

newT <- full_join( ds.ls[c(1,3)], JSTAR_aksst_ds_w2, by="id")
unclass(with(newT, table(k_000, living_status, useNA="ifany")))

```


### Wave 3

#### Study-specific variable description

The study-specific variables elected to be harmonised are:

* Name: `k_000`
* Label: `11K-000:STATUS OF THE SURVEY SUBJECT`
* Categories: 
    + `1 = Alive and eligible to respond`
    + `2 = Alive but ineligible to respond; his/her proxy will respond`
    + `3 = Alive but refused to cooperate`
    + `4 = Deceased but his/her proxy (family members, relatives, etc.) will cooperate`
    + `5 = Whereabouts unknown`
    + `6 = Other`
* Missings
    + `NA` 
   
* Name: `ex_4_f`
* Label: `EX-4:WHEN THE SUBJECT PERSON PASSED AWAY, YEAR`
* Type: `Continuous`

    
```{r read_aksst3, include=FALSE}
opal.assign.table.tibble(o, 'ds.ls','JSTAR_datasets_restricted.jstar_2011_5cities', variables=list('k_000', 'ex_4_f'), missings = TRUE)
ds.ls <- opal.execute(o,'ds.ls')
```

```{r local_aksst3, echo=F}
Categorical_summary(ds.ls[[3]])
ggplot(ds.ls, aes(x=factor(ds.ls[[3]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("STATUS OF THE SURVEY SUBJECT") + ylab("Frequency")

Categorical_summary(ds.ls[[2]])
ggplot(ds.ls, aes(x=factor(ds.ls[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of death") + ylab("Frequency")

table(ds.ls[[2]],ds.ls[[3]], useNA="ifany")
```

#### Harmonisation algorithm

Only variable "k_000"" is used. Variable "ex_4_f" was to verify whether "k_000" was reliable.

Values are recoded as follows:

* `if k_000 = 1, 2 or 3 => living_status = 0 (alive)`
* `if k_000 = 4 => living_status = 1 (died)`
* `if k_000 = 5, 6 or NA => living_status = 2 (dropout)`
 
 **R script:**

```{r harmo_aksst3}
JSTAR_aksst_ds_w3 <- tibble(id=ds.ls$id)
JSTAR_aksst_ds_w3$living_status <- car::recode(ds.ls[[3]], "c(1,2,3)=0; 4=1; c(5,6,NA)=2")
JSTAR_aksst_ds_w3$living_status <- labelled(JSTAR_aksst_ds_w3[[2]], labels = v_label)
```

#### Statistical description of the new harmonised variable
```{r descript_aksst3, echo=F}
Categorical_summary(var = JSTAR_aksst_ds_w3[[2]])
ggplot(JSTAR_aksst_ds_w3, aes(x=as_factor(JSTAR_aksst_ds_w3[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_aksst3, echo=F}
newT <- full_join( ds.ls[c(1,3)], JSTAR_aksst_ds_w3, by="id")
with(newT, table(k_000, living_status, useNA="ifany"))
```

### Validation throughout waves

```{r valid_ws_hrs, echo=F}
dbb <- merge(JSTAR_aksst_ds_w1, JSTAR_aksst_ds_w2, by = "id", suffixes = c(".w1", ".w2"), all = T)
dbb <- merge(dbb, JSTAR_aksst_ds_w3, by = "id", all = T)
names(dbb) <- c("id", "w1", "w2", "w3")
v.dbb <- paste(dbb[, 2], dbb[, 3], dbb[, 4], sep = "")
f.dbb <- frq(v.dbb)[[1]][, c(1, 2, 4)]
kable(f.dbb)
#kable(f.dbb[f.dbb[, 3] >= 0.3, ])
```


## Tosu-Naha

### Wave 1

All participants are alive at the baseline.

```{r read_tn1, include=FALSE}
opal.assign.table.tibble(o, 'ds.ls','JSTAR_datasets_restricted.jstar_2009_2cities', variables=list('a_000_0'), missings = TRUE)
ds.ls <- opal.execute(o,'ds.ls')
```

#### Harmonisation algorithm

The harmonize variable is all 0.

**R script:**

```{r harmo_tn1}
JSTAR_tn_ds_w1 <- tibble(id=ds.ls$id)
JSTAR_tn_ds_w1$living_status <- 0
JSTAR_tn_ds_w1$living_status <- labelled(JSTAR_tn_ds_w1[[2]], labels = v_label)
```

#### Statistical description of the new harmonised variable
```{r descript_tn1, echo=F}
Categorical_summary(var = JSTAR_tn_ds_w1[[2]])
ggplot(JSTAR_tn_ds_w1, aes(x=as_factor(JSTAR_tn_ds_w1[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


### Wave 2

#### Study-specific variable description

The study-specific variables elected to be harmonised are:

* Name: `k_000`
* Label: `11K-000:STATUS OF THE SURVEY SUBJECT`
* Categories: 
    + `1 = Alive and eligible to respond`
    + `2 = Alive but ineligible to respond; his/her proxy will respond`
    + `3 = Alive but refused to cooperate`
    + `4 = Deceased but his/her proxy (family members, relatives, etc.) will cooperate`
    + `5 = Whereabouts unknown`
    + `6 = Other`
* Missings
   + `NA` 
   
* Name: `ex_4_f`
* Label: `EX-4:WHEN THE SUBJECT PERSON PASSED AWAY, YEAR`
* Type: `Continuous`

    
```{r read_tn2, include=FALSE}
opal.assign.table.tibble(o, 'ds.ls','JSTAR_datasets_restricted.jstar_2011_2cities', variables=list('k_000', 'ex_4_f'), missings = TRUE)
ds.ls <- opal.execute(o,'ds.ls')
```

```{r local_tn2, echo=F}
Categorical_summary(ds.ls[[3]])
ggplot(ds.ls, aes(x=factor(ds.ls[[3]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("STATUS OF THE SURVEY SUBJECT") + ylab("Frequency")

Categorical_summary(ds.ls[[2]])
ggplot(ds.ls, aes(x=factor(ds.ls[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of death") + ylab("Frequency")

table(ds.ls[[2]],ds.ls[[3]], useNA="ifany")
```

#### Harmonisation algorithm

Only variable "k_000"" is used. Variable "ex_4_f" was to verify whether "k_000" was reliable.

Values are recoded as follows:

* `if k_000 = 1, 2 or 3 => living_status = 0 (alive)`
* `if k_000 = 4 => living_status = 1 (died)`
* `if k_000 = 5, 6 or NA => living_status = 2 (dropout)`

**R script:**

```{r harmo_tn2}
JSTAR_tn_ds_w2 <- tibble(id=ds.ls$id)
JSTAR_tn_ds_w2$living_status <- car::recode(ds.ls[[3]], "c(1,2,3)=0; 4=1; c(5,6,NA)=2")
JSTAR_tn_ds_w2$living_status <- labelled(JSTAR_tn_ds_w2[[2]], labels = v_label)
```

#### Statistical description of the new harmonised variable
```{r descript_tn2, echo=F}
Categorical_summary(var = JSTAR_tn_ds_w2[[2]])
ggplot(JSTAR_tn_ds_w2, aes(x=as_factor(JSTAR_tn_ds_w2[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstab_tn2, echo=F}
newT <- full_join( ds.ls[c(1,3)], JSTAR_tn_ds_w2, by="id")
with(newT, table(k_000, living_status, useNA="ifany"))
```

### Validation throughout waves

```{r valid_ws_tn, echo=F}
dbb <- merge(JSTAR_tn_ds_w1, JSTAR_tn_ds_w2, by = "id", suffixes = c(".w1", ".w2"), all = T)
names(dbb) <- c("id", "w1", "w2")
v.dbb <- paste(dbb[, 2], dbb[, 3], sep = "")
f.dbb <- frq(v.dbb)[[1]][, c(1, 2, 4)]
kable(f.dbb)
#kable(f.dbb[f.dbb[, 3] >= 0.3, ])
```




## Chofu-Tondabayashi-Hiroshima

### Wave 1

All participants are alive at the baseline.

```{r read_cth1, include=FALSE}
opal.assign.table.tibble(o, 'ds.ls','JSTAR_datasets_restricted.jstar_2011_3cities', variables=list('a_000_0'), missings = TRUE)
ds.ls <- opal.execute(o,'ds.ls')
```

#### Harmonisation algorithm

The harmonize variable is all 0.

**R script:**

```{r harmo_cth1}
JSTAR_cth_ds_w1 <- tibble(id=ds.ls$id)
JSTAR_cth_ds_w1$living_status <- 0
JSTAR_cth_ds_w1$living_status <- labelled(JSTAR_cth_ds_w1[[2]], labels = v_label)
```

#### Statistical description of the new harmonised variable
```{r descript_cth1, echo=F}
Categorical_summary(var = JSTAR_cth_ds_w1[[2]])
ggplot(JSTAR_cth_ds_w1, aes(x=as_factor(JSTAR_cth_ds_w1[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```



<!--- ######################### Import to OPAL #######################-->
```{r importOPAL, echo=FALSE}
living_status <- JSTAR_aksst_ds_w1
save(living_status, file = "../RData/aksst_w1/living_status.RData")
rm(living_status)

living_status <- JSTAR_aksst_ds_w2
save(living_status, file = "../RData/aksst_w2/living_status.RData")
rm(living_status)

living_status <- JSTAR_aksst_ds_w3
save(living_status, file = "../RData/aksst_w3/living_status.RData")
rm(living_status)

living_status <- JSTAR_tn_ds_w1
save(living_status, file = "../RData/tn_w1/living_status.RData")
rm(living_status)

living_status <- JSTAR_tn_ds_w2
save(living_status, file = "../RData/tn_w2/living_status.RData")
rm(living_status)

living_status <- JSTAR_cth_ds_w1
save(living_status, file = "../RData/cth_w1/living_status.RData")
rm(living_status)
```




# Quality estimation
No comments.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```

