---
title: "Any voluntary/charitable activity"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/CHARLS/9_Social_env_life_events/CHARLS_ids.r")

```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `volun`
* Variable label: `Any voluntary/charitable activity`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process

## China (All counties with the exception of Tibet)
### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `da056s3`
* Label: `Do Activities LM of Provided Help to People Who Lived Apart`
* Categories:
    + `1 = Interacted with friends`
    + `2 = Played Ma-jong, etc, or went to community club`
    + `3 = Provided help to family, friends, or neighbors`
    + `4 = Went to a sport, social, or other kind of club`
    + `5 = Took part in a community-related organization`
    + `6 = Done voluntary or charity work`
    + `7 = Cared for a sick or disabled adult`
    + `8 = Attended an educational or training course`
    + `9 = Stock investment`
    + `10 = Used the Internet`
    + `11 = Other`
    + `12 = None of these`

* Name: `da056s6`
* Label: `Do Activities LM of Voluntary or Charity`
* Categories:
    + `1 = Interacted with friends`
    + `2 = Played Ma-jong, etc, or went to community club`
    + `3 = Provided help to family, friends, or neighbors`
    + `4 = Went to a sport, social, or other kind of club`
    + `5 = Took part in a community-related organization`
    + `6 = Done voluntary or charity work`
    + `7 = Cared for a sick or disabled adult`
    + `8 = Attended an educational or training course`
    + `9 = Stock investment`
    + `10 = Used the Internet`
    + `11 = Other`
    + `12 = None of these`

* Name: `da056s7`
* Label: `Do Activities LM of Cared for A Sick or Disabled Adult Who Lived Apart`
* Categories:
    + `1 = Interacted with friends`
    + `2 = Played Ma-jong, etc, or went to community club`
    + `3 = Provided help to family, friends, or neighbors`
    + `4 = Went to a sport, social, or other kind of club`
    + `5 = Took part in a community-related organization`
    + `6 = Done voluntary or charity work`
    + `7 = Cared for a sick or disabled adult`
    + `8 = Attended an educational or training course`
    + `9 = Stock investment`
    + `10 = Used the Internet`
    + `11 = Other`
    + `12 = None of these`


* Description: 
```{r assign1}
opal.assign.table.tibble(o, 'CHARLS_w1_volun','CHARLS.health_status_and_functioning_wave1', 
                        variables=list('da056s3','da056s6','da056s7'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids',
                         variables=list('var'), missings = TRUE)

```

```{r local1}
CHARLS_w1_volun <- opal.execute(o,'CHARLS_w1_volun')
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')

CHARLS_w1_volun$oldid <- CHARLS_w1_volun$id
CHARLS_w1_volun$id <- CHARLS_ids(ids = CHARLS_w1_volun$oldid)

CHARLS_w1_volun <- left_join(CHARLS_w1_id, CHARLS_w1_volun, by="id")[,-2]


vari <- CHARLS_w1_volun$da056s3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w1_volun$da056s3, missing_values = NA)
ggplot(CHARLS_w1_volun, aes(x=factor(da056s3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Have you done any of these activities in the last month: Provided Help to People Who Lived Apart") + ylab("Frequency")

vari <- CHARLS_w1_volun$da056s6
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w1_volun$da056s6, missing_values = NA)
ggplot(CHARLS_w1_volun, aes(x=factor(da056s6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Have you done any of these activities in the last month: Voluntary or Charity") + ylab("Frequency")

vari <- CHARLS_w1_volun$da056s7
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w1_volun$da056s7, missing_values = NA)
ggplot(CHARLS_w1_volun, aes(x=factor(da056s7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Have you done any of these activities in the last month: Cared for A Sick or Disabled Adult Who Lived Apart") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any da056si=i then 1`
* `if all are equal NA then 0`

**R script:**

```{r harmo1, echo=TRUE}
CHARLS_ds_w1 <- tibble(id=CHARLS_w1_volun$id)

CHARLS_w1_volun$da056s3 <- car::recode(as.vector(CHARLS_w1_volun$da056s3), "NA='-999'")
CHARLS_w1_volun$da056s6 <- car::recode(as.vector(CHARLS_w1_volun$da056s6), "NA='-999'")
CHARLS_w1_volun$da056s7 <- car::recode(as.vector(CHARLS_w1_volun$da056s7), "NA='-999'")

CHARLS_ds_w1$volun <- c(NA)
for(i in 1:dim(CHARLS_w1_volun)[1]){
  if( CHARLS_w1_volun$da056s3[i] == 3 | CHARLS_w1_volun$da056s6[i] == 6 | CHARLS_w1_volun$da056s7[i] == 7 ){
    CHARLS_ds_w1$volun[i] = 1 }
  else if( CHARLS_w1_volun$da056s3[i] == -999 & CHARLS_w1_volun$da056s6[i] == -999 & CHARLS_w1_volun$da056s7[i] == -999 ){
    CHARLS_ds_w1$volun[i] = 0 }
}

# there are no NA's anymore...
CHARLS_ds_w1$volun <- labelled(CHARLS_ds_w1$volun, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1}

vari <- CHARLS_ds_w1$volun
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = CHARLS_ds_w1$volun, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(CHARLS_ds_w1, aes(x=factor(volun))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any voluntary/charitable activity") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1}

```



### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `da056s3`
* Label: `Do Activities LM of Provided Help to People Who Lived Apart`
* Categories:
    + `1 = Interacted with friends`
    + `2 = Played Ma-jong, etc, or went to community club`
    + `3 = Provided help to family, friends, or neighbors`
    + `4 = Went to a sport, social, or other kind of club`
    + `5 = Took part in a community-related organization`
    + `6 = Done voluntary or charity work`
    + `7 = Cared for a sick or disabled adult`
    + `8 = Attended an educational or training course`
    + `9 = Stock investment`
    + `10 = Used the Internet`
    + `11 = Other`
    + `12 = None of these`

* Name: `da056s6`
* Label: `Do Activities LM of Voluntary or Charity`
* Categories:
    + `1 = Interacted with friends`
    + `2 = Played Ma-jong, etc, or went to community club`
    + `3 = Provided help to family, friends, or neighbors`
    + `4 = Went to a sport, social, or other kind of club`
    + `5 = Took part in a community-related organization`
    + `6 = Done voluntary or charity work`
    + `7 = Cared for a sick or disabled adult`
    + `8 = Attended an educational or training course`
    + `9 = Stock investment`
    + `10 = Used the Internet`
    + `11 = Other`
    + `12 = None of these`

* Name: `da056s7`
* Label: `Do Activities LM of Cared for A Sick or Disabled Adult Who Lived Apart`
* Categories:
    + `1 = Interacted with friends`
    + `2 = Played Ma-jong, etc, or went to community club`
    + `3 = Provided help to family, friends, or neighbors`
    + `4 = Went to a sport, social, or other kind of club`
    + `5 = Took part in a community-related organization`
    + `6 = Done voluntary or charity work`
    + `7 = Cared for a sick or disabled adult`
    + `8 = Attended an educational or training course`
    + `9 = Stock investment`
    + `10 = Used the Internet`
    + `11 = Other`
    + `12 = None of these`


* Description: 
```{r assign2}
opal.assign.table.tibble(o, 'CHARLS_w2_volun','CHARLS.Health_Status_and_Functioning_wave2', 
                        variables=list('da056s3','da056s6','da056s7'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids',
                         variables=list('var'), missings = TRUE)
```

```{r local2}
CHARLS_w2_volun <- opal.execute(o,'CHARLS_w2_volun')
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')

CHARLS_w2_volun <- left_join(CHARLS_w2_id, CHARLS_w2_volun, by="id")[,-2]

vari <- CHARLS_w2_volun$da056s3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_volun$da056s3, missing_values = NA)
ggplot(CHARLS_w2_volun, aes(x=factor(da056s3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Have you done any of these activities in the last month: Provided Help to People Who Lived Apart") + ylab("Frequency")
vari <- CHARLS_w2_volun$da056s6
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_volun$da056s6, missing_values = NA)
ggplot(CHARLS_w2_volun, aes(x=factor(da056s6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Have you done any of these activities in the last month: Voluntary or Charity") + ylab("Frequency")
vari <- CHARLS_w2_volun$da056s7
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_volun$da056s7, missing_values = NA)
ggplot(CHARLS_w2_volun, aes(x=factor(da056s7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Have you done any of these activities in the last month: Cared for A Sick or Disabled Adult Who Lived Apart") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any da056si=i then 1`
* `if all are equal NA then 0`

**R script:**

```{r harmo2, echo=TRUE}
CHARLS_ds_w2 <- tibble(id=CHARLS_w2_volun$id)

CHARLS_w2_volun$da056s3 <- car::recode(as.vector(CHARLS_w2_volun$da056s3), "NA='-999'")
CHARLS_w2_volun$da056s6 <- car::recode(as.vector(CHARLS_w2_volun$da056s6), "NA='-999'")
CHARLS_w2_volun$da056s7 <- car::recode(as.vector(CHARLS_w2_volun$da056s7), "NA='-999'")

CHARLS_ds_w2$volun <- c(NA)
for(i in 1:dim(CHARLS_w2_volun)[1]){
  if( CHARLS_w2_volun$da056s3[i] == 3 | CHARLS_w2_volun$da056s6[i] == 6 | CHARLS_w2_volun$da056s7[i] == 7 ){
    CHARLS_ds_w2$volun[i] = 1 }
  else if( CHARLS_w2_volun$da056s3[i] == -999 & CHARLS_w2_volun$da056s6[i] == -999 & CHARLS_w2_volun$da056s7[i] == -999 ){
    CHARLS_ds_w2$volun[i] = 0 }
}

# there are no NA's anymore...
CHARLS_ds_w2$volun <- labelled(CHARLS_ds_w2$volun, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2}
vari <- CHARLS_ds_w2$volun
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = CHARLS_ds_w2$volun, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(CHARLS_ds_w2, aes(x=factor(volun))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any voluntary/charitable activity") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2}

```


```{r save, echo=FALSE}
volun <- CHARLS_ds_w1
save(volun, file = "../RData/w1/volun.RData")
rm(volun)

volun <- CHARLS_ds_w2
save(volun, file = "../RData/w2/volun.RData")
rm(volun)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```



