---
title: "Participation in club groups"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
source("../CHARLS_ids.R")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/part_clubsDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/part_clubsDS.R')
```

# Data process

## China


### Wave 1 

#### Study-specific variable description

| **Name** |`da056s4`|`da056s5`|
|-|-|-|
| **Label** |`Have you done any of these activities in the last month: Went to Club`|`Have you done any of these activities in the last month: Took Part In A Community-related Organization`|
| **Table name** |`health_status_and_functioning_wave1`|`health_status_and_functioning_wave1`|
| **Categories** |`1 = Interacted with friends`<br/>`2 = Played Ma-jong, etc, or went to community club`<br/>`3 = Provided help to family, friends, or neighbors`<br/>`4 = Went to a sport, social, or other kind of club`<br/>`5 = Took part in a community-related organization`<br/>`6 = Done voluntary or charity work`<br/>`7 = Cared for a sick or disabled adult`<br/>`8 = Attended an educational or training course`<br/>`9 = Stock investment`<br/>`10 = Used the Internet`<br/>`11 = Other`<br/>`12 = None of these`|`1 = Interacted with friends`<br/>`2 = Played Ma-jong, etc, or went to community club`<br/>`3 = Provided help to family, friends, or neighbors`<br/>`4 = Went to a sport, social, or other kind of club`<br/>`5 = Took part in a community-related organization`<br/>`6 = Done voluntary or charity work`<br/>`7 = Cared for a sick or disabled adult`<br/>`8 = Attended an educational or training course`<br/>`9 = Stock investment`<br/>`10 = Used the Internet`<br/>`11 = Other`<br/>`12 = None of these`|
| **Description** |  |  |



```{r assign1, echo=F}

opal.assign.table.tibble(o, 'CHARLS_w1_part_clubs','CHARLS.health_status_and_functioning_wave1',variables=list('da056s4','da056s5'), missings = TRUE)
CHARLS_w1_part_clubs <- opal.execute(o,'CHARLS_w1_part_clubs')


opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids', variables=list('var'), missings = TRUE)
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')

CHARLS_w1_part_clubs$oldid <- CHARLS_w1_part_clubs$id
CHARLS_w1_part_clubs$id <- CHARLS_ids(ids = CHARLS_w1_part_clubs$oldid)

CHARLS_w1_part_clubs <- left_join(CHARLS_w1_id,CHARLS_w1_part_clubs,by="id")
```

```{r local1, echo=F}
Categorical_summary(var = CHARLS_w1_part_clubs$da056s4, missing_values = NA)
ggplot(CHARLS_w1_part_clubs, aes(x=factor(da056s4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Have you done any of these activities in the last month: Went to Club") + ylab("Frequency")
Categorical_summary(var = CHARLS_w1_part_clubs$da056s5, missing_values = NA)
ggplot(CHARLS_w1_part_clubs, aes(x=factor(da056s5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Have you done any of these activities in the last month: Took part in a Community-related Organization") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if da056s4=4 or da065s5=5 then 1`
* `if both are equal NA then 0`

**R script:**

```{r harmo1}
CHARLS_ds_w1 <- tibble(id=CHARLS_w1_part_clubs$id)

CHARLS_w1_part_clubs$da056s4 <- car::recode(as.vector(CHARLS_w1_part_clubs$da056s4), "NA='-999'")
CHARLS_w1_part_clubs$da056s5 <- car::recode(as.vector(CHARLS_w1_part_clubs$da056s5), "NA='-999'")

CHARLS_ds_w1$part_clubs <- c(NA)
for(i in 1:dim(CHARLS_w1_part_clubs)[1]){
  if( CHARLS_w1_part_clubs$da056s4[i] == 4 | CHARLS_w1_part_clubs$da056s5[i] == 5 ){
    CHARLS_ds_w1$part_clubs[i] = 1 }
  else if( CHARLS_w1_part_clubs$da056s4[i] == -999 & CHARLS_w1_part_clubs$da056s5[i] == -999 ){
    CHARLS_ds_w1$part_clubs[i] = 0 }
}

```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
Categorical_summary(var = CHARLS_ds_w1$part_clubs, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(CHARLS_ds_w1, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(CHARLS_ds_w1$part_clubs)
BeforeH <- table(CHARLS_w1_part_clubs$da056s4, CHARLS_w1_part_clubs$da056s5, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[1,1]
BeforeH1[[2]] <- sum( sum(BeforeH[2,]), sum(BeforeH[1,2]) )
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1")
kable(C)
```



### Wave 2

#### Study-specific variable description


| **Name** |`da056s4`|`da056s5`|
|-|-|-|
| **Label** |`Have you done any of these activities in the last month: Went to Club`|`Have you done any of these activities in the last month: Took Part In A Community-related Organization`|
| **Table name** |`Health_Status_and_Functioning_wave2`|`Health_Status_and_Functioning_wave2`|
| **Categories** |`1 = Interacted with friends`<br/>`2 = Played Ma-jong, etc, or went to community club`<br/>`3 = Provided help to family, friends, or neighbors`<br/>`4 = Went to a sport, social, or other kind of club`<br/>`5 = Took part in a community-related organization`<br/>`6 = Done voluntary or charity work`<br/>`7 = Cared for a sick or disabled adult`<br/>`8 = Attended an educational or training course`<br/>`9 = Stock investment`<br/>`10 = Used the Internet`<br/>`11 = Other`<br/>`12 = None of these`|`1 = Interacted with friends`<br/>`2 = Played Ma-jong, etc, or went to community club`<br/>`3 = Provided help to family, friends, or neighbors`<br/>`4 = Went to a sport, social, or other kind of club`<br/>`5 = Took part in a community-related organization`<br/>`6 = Done voluntary or charity work`<br/>`7 = Cared for a sick or disabled adult`<br/>`8 = Attended an educational or training course`<br/>`9 = Stock investment`<br/>`10 = Used the Internet`<br/>`11 = Other`<br/>`12 = None of these`|
| **Description** |  |  |





```{r assign2, echo=F}

opal.assign.table.tibble(o, 'CHARLS_w2_part_clubs','CHARLS.Health_Status_and_Functioning_wave2',variables=list('da056s4','da056s5'), missings = TRUE)
CHARLS_w2_part_clubs <- opal.execute(o,'CHARLS_w2_part_clubs')

opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids', variables=list('var'), missings = TRUE)
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')

CHARLS_w2_part_clubs <- left_join(CHARLS_w2_id,CHARLS_w2_part_clubs,by="id")

```

```{r local2, echo=F}
Categorical_summary(var = CHARLS_w2_part_clubs$da056s4, missing_values = NA)
ggplot(CHARLS_w2_part_clubs, aes(x=factor(da056s4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Have you done any of these activities in the last month: Went to Club") + ylab("Frequency")
Categorical_summary(var = CHARLS_w2_part_clubs$da056s5, missing_values = NA)
ggplot(CHARLS_w2_part_clubs, aes(x=factor(da056s5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Have you done any of these activities in the last month: Took part in a Community-related Organization") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if da056s4=4 or da065s5=5 then 1`
* `if both are equal NA then 0`

**R script:**

```{r harmo2}
CHARLS_ds_w2 <- tibble(id=CHARLS_w2_part_clubs$id)

CHARLS_w2_part_clubs$da056s4 <- car::recode(as.vector(CHARLS_w2_part_clubs$da056s4), "NA='-999'")
CHARLS_w2_part_clubs$da056s5 <- car::recode(as.vector(CHARLS_w2_part_clubs$da056s5), "NA='-999'")

CHARLS_ds_w2$part_clubs <- c(NA) # I think it is required
for(i in 1:dim(CHARLS_w2_part_clubs)[1]){
  if( CHARLS_w2_part_clubs$da056s4[i] == 4 | CHARLS_w2_part_clubs$da056s5[i] == 5 ){
    CHARLS_ds_w2$part_clubs[i] = 1 }
  else if( CHARLS_w2_part_clubs$da056s4[i] == -999 & CHARLS_w2_part_clubs$da056s5[i] == -999 ){
    CHARLS_ds_w2$part_clubs[i] = 0 }
}

# there are no NA's anymore...
CHARLS_ds_w2$part_clubs <- labelled(CHARLS_ds_w2$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
Categorical_summary(var = CHARLS_ds_w2$part_clubs, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(CHARLS_ds_w2, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
AfterH <- table(CHARLS_ds_w2$part_clubs)
BeforeH <- table(CHARLS_w2_part_clubs$da056s4, CHARLS_w2_part_clubs$da056s5, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[1,1]
BeforeH1[[2]] <- sum( sum(BeforeH[2,]), sum(BeforeH[1,2]) )
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1")
kable(C)
```


## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.

**R script:**

```{r summ}
CHARLS_ds_w1$part_clubs <- labelled(CHARLS_ds_w1$part_clubs, labels = cat_label)
label(CHARLS_ds_w1$part_clubs) <- ds_label
CHARLS_ds_w2$part_clubs <- labelled(CHARLS_ds_w2$part_clubs, labels = cat_label)
label(CHARLS_ds_w2$part_clubs) <- ds_label


CHARLS_m_ds_w1 <- CHARLS_ds_w1
CHARLS_m_ds_w1$part_clubs <- car::recode(CHARLS_m_ds_w1$part_clubs, "miss_values_vector=NA")
CHARLS_m_ds_w2 <- CHARLS_ds_w2
CHARLS_m_ds_w2$part_clubs <- car::recode(CHARLS_m_ds_w2$part_clubs, "miss_values_vector=NA")


tt <-    frq(CHARLS_ds_w1$part_clubs)[[1]][,c(1:2,4)]
tt[4] <- frq(CHARLS_ds_w2$part_clubs)[[1]][,c(4)]
tt[13,] <- c("n", "sample size", 
             length(CHARLS_ds_w1$part_clubs), length(CHARLS_ds_w2$part_clubs)
             )
names(tt)<-c("val", "label", "w1", "w2")
kable(tt)

dbb <- merge(CHARLS_m_ds_w1[,c("id","part_clubs")], CHARLS_m_ds_w2[,c("id","part_clubs")], by="id", suffixes = c(".w1",".w2"), all=T)
names(dbb) <- c("id", "w1", "w2")
v.dbb <- paste(dbb[,2],dbb[,3],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb)
```



# Quality estimation


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.CHARLS <- list(w1 = CHARLS_ds_w1, w2 = CHARLS_ds_w2)

for(index in seq_along(l.CHARLS)){
  part_clubs <- l.CHARLS[[index]]
  save(part_clubs, file = paste0(datafolder,names(l.CHARLS)[index],"/part_clubs.RData"))
}

```
<!-- ########################################################## --> 



<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
