---
title: "Experience of a loss of any close person"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/CHARLS/9_Social_env_life_events/CHARLS_ids.r")

```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `bereav`
* Variable label: `Experience of a loss of any close person`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process
## China (All counties with the exception of Tibet)


### Wave 1 

#### Study-specific variables

The study-specific variables elected to be harmonised are:

* Name: `ca008_1_1_`
* Label: `Year Parent Passed Away`

* Name: `bf007_1`
* Label: `Year Spouse Passed Away`

* `Selected variables come from 2 different Opal tables!`

* Description: 
```{r assign1}
opal.assign.table.tibble(o, 'CHARLS_w1_bereav1','CHARLS.family_information_wave1', 
                        variables=list( 'ca008_1_1_'), missings = TRUE)

opal.assign.table.tibble(o, 'CHARLS_w1_bereav2','CHARLS.demographic_background_wave1', 
                        variables=list('bf007_1'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids',
                         variables=list('var'), missings = TRUE)
```

```{r local1}
CHARLS_w1_bereav1 <- opal.execute(o,'CHARLS_w1_bereav1')
CHARLS_w1_bereav2 <- opal.execute(o,'CHARLS_w1_bereav2')
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')

CHARLS_w1_bereav1$oldid <- CHARLS_w1_bereav1$id
CHARLS_w1_bereav1$id <- CHARLS_ids(ids = CHARLS_w1_bereav1$oldid)
CHARLS_w1_bereav1 <- left_join(CHARLS_w1_id, CHARLS_w1_bereav1, by="id")[,-2]


CHARLS_w1_bereav2$oldid <- CHARLS_w1_bereav2$id
CHARLS_w1_bereav2$id <- CHARLS_ids(ids = CHARLS_w1_bereav2$oldid)
CHARLS_w1_bereav2 <- left_join(CHARLS_w1_id, CHARLS_w1_bereav2, by="id")[,-2]

vari <-  CHARLS_w1_bereav1$ca008_1_1_
kable(Continuous_summary(vari, missing_values = c(-9999,9999))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Continuous_summary(vari, missing_values = c(-9999,9999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values =c(-9999,9999))$summary, caption = "Summary")
#Categorical_summary(var = CHARLS_w1_bereav1$ca008_1_1_, missing_values = NA)
ggplot(CHARLS_w1_bereav1, aes(x=(ca008_1_1_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year Parent Passed Away") + ylab("Frequency")+xlim(1890,2019)

vari <- CHARLS_w1_bereav2$bf007_1
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Categorical_summary(var = CHARLS_w1_bereav2$bf007_1, missing_values = NA)
ggplot(CHARLS_w1_bereav2, aes(x=(bf007_1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year Spouse Passed Away") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `If any provides anwer, then 1`
* `If both don't provide answers, then 0`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
CHARLS_w1_bereav <- left_join(CHARLS_w1_bereav1, CHARLS_w1_bereav2, by="id")[,-c(3,5)]
CHARLS_ds_w1 <- tibble(id=CHARLS_w1_bereav$id)

CHARLS_w1_bereav$ca008_1_1_ <- car::recode(as.vector(CHARLS_w1_bereav$ca008_1_1_), "NA='-999'")
CHARLS_w1_bereav$bf007_1 <- car::recode(as.vector(CHARLS_w1_bereav$bf007_1), "NA='-999'")

CHARLS_ds_w1$bereav <- c(NA) 
for(i in 1:dim(CHARLS_w1_bereav)[1]){
  if(CHARLS_w1_bereav$ca008_1_1_[i] == -999 & CHARLS_w1_bereav$bf007_1[i] == -999 ) { 
    CHARLS_ds_w1$bereav[i] = 0 }
  else if(!(CHARLS_w1_bereav$ca008_1_1_[i] == -999) | !(CHARLS_w1_bereav$bf007_1[i] == -999) ) { 
    CHARLS_ds_w1$bereav[i] = 1 }
}

CHARLS_ds_w1$bereav <- car::recode(as.vector(CHARLS_ds_w1$bereav), "NA='999'")
CHARLS_ds_w1$bereav <- labelled(CHARLS_ds_w1$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))


```

#### Statistical description of the new harmonised variable
```{r descript1}
vari <- CHARLS_ds_w1$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = CHARLS_ds_w1$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(CHARLS_ds_w1, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1}

```




### Wave 2

#### Study-specific variables

The study-specific variables elected to be harmonised are:

* Name: `ca008_1_`
* Label: `When Father Pass Away`

* Name: `ca008_2_`
* Label: `When Mother Pass Away`

* Name: `ca008_3_`
* Label: `When Father-in-law Pass Away`

* Name: `ca008_4_`
* Label: `When Mother-in-law Pass Away`

* Name: `bf007_1`
* Label: `Year Spouse Passed Away`

* `Selected variables come from 2 different Opal tables`

* Description: 
```{r assign2}
opal.assign.table.tibble(o, 'CHARLS_w2_bereav1','CHARLS.Family_Information_wave2', 
                        variables=list('ca008_1_','ca008_2_','ca008_3_','ca008_4_'), missings = TRUE)

opal.assign.table.tibble(o, 'CHARLS_w2_bereav2','CHARLS.Demographic_Background_wave2', 
                        variables=list('bf007_1'), missings = TRUE)

opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids',
                         variables=list('var'), missings = TRUE)

```

```{r local2}
CHARLS_w2_bereav1 <- opal.execute(o,'CHARLS_w2_bereav1')
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')
CHARLS_w2_bereav2 <- opal.execute(o,'CHARLS_w2_bereav2')

CHARLS_w2_bereav1 <- left_join(CHARLS_w2_id, CHARLS_w2_bereav1, by="id")[,-2]
CHARLS_w2_bereav2 <- left_join(CHARLS_w2_id, CHARLS_w2_bereav2, by="id")[,-2]

vari <- CHARLS_w2_bereav1$ca008_1_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_bereav1$ca008_1_, missing_values = NA)
ggplot(CHARLS_w2_bereav1, aes(x=factor(ca008_1_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("When Father Pass Away") + ylab("Frequency")

vari <- CHARLS_w2_bereav1$ca008_2_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_bereav1$ca008_2_, missing_values = NA)
ggplot(CHARLS_w2_bereav1, aes(x=factor(ca008_2_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("When Mother Pass Away") + ylab("Frequency")

vari <- CHARLS_w2_bereav1$ca008_3_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_bereav1$ca008_3_, missing_values = NA)
ggplot(CHARLS_w2_bereav1, aes(x=factor(ca008_3_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("When Father-in-law Pass Away") + ylab("Frequency")

vari <- CHARLS_w2_bereav1$ca008_1_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_bereav1$ca008_4_, missing_values = NA)
ggplot(CHARLS_w2_bereav1, aes(x=factor(ca008_4_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("When Mother-in-law Pass Away") + ylab("Frequency")


vari <- CHARLS_w2_bereav2$bf007_1
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Categorical_summary(var = CHARLS_w2_bereav2$bf007_1, missing_values = NA)
ggplot(CHARLS_w2_bereav2, aes(x=(bf007_1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year Spouse Passed Away") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `If any provides anwer, then 1`
* `If every one doesn't provide answer, then 0`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}

CHARLS_w2_bereav <- left_join(CHARLS_w2_bereav1, CHARLS_w1_bereav2, by="id")[,-7]


CHARLS_w2_bereav$ca008_1_ <- car::recode(as.vector(CHARLS_w2_bereav$ca008_1_), "NA='-999'")
CHARLS_w2_bereav$ca008_2_ <- car::recode(as.vector(CHARLS_w2_bereav$ca008_2_), "NA='-999'")
CHARLS_w2_bereav$ca008_3_ <- car::recode(as.vector(CHARLS_w2_bereav$ca008_3_), "NA='-999'")
CHARLS_w2_bereav$ca008_4_ <- car::recode(as.vector(CHARLS_w2_bereav$ca008_4_), "NA='-999'")
CHARLS_w2_bereav$bf007_1 <- car::recode(as.vector(CHARLS_w2_bereav$bf007_1), "NA='-999'")

CHARLS_ds_w2 <- tibble(id=CHARLS_w2_bereav$id)

CHARLS_ds_w2$bereav <- c(NA) 
for(i in 1:dim(CHARLS_w2_bereav)[1]){
  if(CHARLS_w2_bereav$ca008_1_[i] == -999 & CHARLS_w2_bereav$ca008_2_[i] == -999 & 
   CHARLS_w2_bereav$ca008_3_[i] == -999 & CHARLS_w2_bereav$ca008_4_[i] == -999 &
   CHARLS_w2_bereav$bf007_1[i] == -999) { CHARLS_ds_w2$bereav[i] = 0 }
  else if(!(CHARLS_w2_bereav$ca008_1_[i] == -999) | !(CHARLS_w2_bereav$ca008_2_[i] == -999) |
        !(CHARLS_w2_bereav$ca008_3_[i] == -999) | !(CHARLS_w2_bereav$ca008_4_[i] == -999) |
        !(CHARLS_w2_bereav$bf007_1[i] == -999) ) { CHARLS_ds_w2$bereav[i] = 1 }
}

CHARLS_ds_w2$bereav <- car::recode(as.vector(CHARLS_ds_w2$bereav), "NA='999'")
CHARLS_ds_w2$bereav <- labelled(CHARLS_ds_w2$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))


```

#### Statistical description of the new harmonised variable
```{r descript2}
vari <- CHARLS_ds_w2$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = CHARLS_ds_w2$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(CHARLS_ds_w2, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of a loss of any close person") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2}

```


```{r save, echo=FALSE}
bereav <- CHARLS_ds_w1
save(bereav, file = "../RData/w1/bereav.RData")
rm(bereav)

bereav <- CHARLS_ds_w2
save(bereav, file = "../RData/w2/bereav.RData")
rm(bereav)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```


