---
title: "Divorce/Separation"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/CHARLS/9_Social_env_life_events/CHARLS_ids.r")

```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `divorce`
* Variable label: `Experience of divorce/separation`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process

## China (All counties with the exception of Tibet)

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `be001`
* Label: `Marital Status`
* Categories: 
    + `1.0 = Married with divorce present`
    + `2.0 = Married but not living with divorce temporarily for reasons such as work`
    + `3.0 = Separated`
    + `4.0 = Divorced`
    + `5.0 = Widowed`
    + `6.0 = Never married`

    

* Description: 
```{r assign1}
opal.assign.table.tibble(o, 'CHARLS_w1_divorce','CHARLS.demographic_background_modif_Laia_baseline',variables=list('be001'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids',
                         variables=list('var'), missings = TRUE)

```

```{r local1}
CHARLS_w1_divorce <- opal.execute(o,'CHARLS_w1_divorce')
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')
CHARLS_w1_divorce$oldid <- CHARLS_w1_divorce$id
CHARLS_w1_divorce$id <- CHARLS_ids(ids = CHARLS_w1_divorce$oldid)
CHARLS_w1_divorce <- left_join(CHARLS_w1_id, CHARLS_w1_divorce, by="id")[,-2]

vari <- CHARLS_w1_divorce$be001
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w1_divorce$be001, missing_values = NA)
ggplot(CHARLS_w1_divorce, aes(x=factor(be001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `3 or 4 into 1`
* `1,2,5,6 into 0`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
CHARLS_ds_w1 <- tibble(id=CHARLS_w1_divorce$id)
CHARLS_ds_w1$divorce <- car::recode(as.vector(CHARLS_w1_divorce$be001), " 3:4='1'; 1:2='0'; 5:6='0'; NA='999'")
CHARLS_ds_w1$divorce <- labelled(CHARLS_ds_w1$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1}
vari <- CHARLS_ds_w1$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = CHARLS_ds_w1$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(CHARLS_ds_w1, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1}
AfterH <- table(CHARLS_ds_w1$divorce)
BeforeH <- table(CHARLS_w1_divorce$be001, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- sum(BeforeH[c(3,4)])
BeforeH1[[1]] <- sum(BeforeH[c(1,2,5,6)])
BeforeH1[[3]] <- BeforeH[[7]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1,2,5,6->0","3:4->1","NA->999")
kable(C)
```



### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `be001`
* Label: `Marital Status`
* Categories: 
    + `1.0 = Married with divorce present`
    + `2.0 = Married but not living with divorce temporarily for reasons such as work`
    + `3.0 = Separated`
    + `4.0 = Divorced`
    + `5.0 = Widowed`
    + `6.0 = Never married`
    + `7.0 = Cohabitated`
    
* Name: divorce *harmonized in Wave1*

* Description: 
```{r assign2}
opal.assign.table.tibble(o, 'CHARLS_w2_divorce','CHARLS.Demographic_Background_wave2',variables=list('be001'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids',
                         variables=list('var'), missings = TRUE)

```

```{r local2}
CHARLS_w2_divorce <- opal.execute(o,'CHARLS_w2_divorce')
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')
CHARLS_w2_divorce <- left_join(CHARLS_w2_id, CHARLS_w2_divorce, by="id")[,-2]

vari <-  CHARLS_w2_divorce$be001
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_divorce$be001, missing_values = NA)
ggplot(CHARLS_w2_divorce, aes(x=factor(be001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if divorce=1 then (no matter what is be001) OR be001 equals 3 or 4 then recode into 1`
* `else if be001 in {1,2,5,6,7} then recode into 0`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
CHARLS_w2_divorce_2 <- left_join(CHARLS_w2_divorce,CHARLS_ds_w1, by="id")
CHARLS_ds_w2 <- tibble(id=CHARLS_w2_divorce_2$id)

CHARLS_w2_divorce_2$divorce <- car::recode(as.vector(CHARLS_w2_divorce_2$divorce), "NA='-999'")
CHARLS_w2_divorce_2$be001 <- car::recode(as.vector(CHARLS_w2_divorce_2$be001), "NA='-999'")

CHARLS_ds_w2$divorce <- c(NA)  
for(i in 1:dim(CHARLS_w2_divorce_2[1])){
  if( CHARLS_w2_divorce_2$divorce[i] == 1 | CHARLS_w2_divorce_2$be001[i] %in% c(3,4) ) { CHARLS_ds_w2$divorce[i] = 1 }
  else if( CHARLS_w2_divorce_2$be001[i] %in% c(1,2,5,6,7) ) { CHARLS_ds_w2$divorce[i] = 0 }
}


CHARLS_ds_w2$divorce <- car::recode(as.vector(CHARLS_ds_w2$divorce), "NA='999'")
CHARLS_ds_w2$divorce <- labelled(CHARLS_ds_w2$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2}
vari <- CHARLS_ds_w2$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = CHARLS_ds_w2$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(CHARLS_ds_w2, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2}
AfterH <- table(CHARLS_ds_w2$divorce)
BeforeH <- table(CHARLS_w2_divorce_2$divorce, CHARLS_w2_divorce_2$be001, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- sum(BeforeH[,c(4,5)])
BeforeH1[[1]] <- sum(BeforeH[,c(2,3,6,7,8)])
BeforeH1[[3]] <- BeforeH[1,1]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1,2,5,6,7->0","3:4->1","NA->999")
kable(C)
```

```{r save, echo=FALSE}
divorce <- CHARLS_ds_w1
save(divorce, file = "../RData/w1/divorce.RData")
rm(divorce)

divorce <- CHARLS_ds_w2
save(divorce, file = "../RData/w2/divorce.RData")
rm(divorce)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
