---
title: "Felt loneliness"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
source("../../CHARLS/CHARLS_ids.R")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/lonelinessDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/lonelinessDS.R')
```


<!-- ########################################################## --> 

# Data process

## China (All counties with the exception of Tibet)

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `dc017`
* Label: `Felt loneliness`
* Categories: 
    + `1 = Rarely or none of the time <1 day`
    + `2 = Some or a little of the time 1-2 days`
    + `3 = Occasionally or a moderate amount of the time 3-4 days`
    + `4 = Most or all of the time 5-7 days`
    

* Description: 
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'CHARLS_w1_loneliness','CHARLS.health_status_and_functioning_wave1',variables=list('dc017'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids',  variables=list('var'), missings = TRUE)
CHARLS_w1_loneliness <- opal.execute(o,'CHARLS_w1_loneliness')
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')

# adding a zero to the old id's in CHARLS_w1 with CHARLS_ids
CHARLS_w1_loneliness$oldid <- CHARLS_w1_loneliness$id
CHARLS_w1_loneliness$id <- CHARLS_ids(ids = CHARLS_w1_loneliness$oldid)

CHARLS_w1_loneliness <- left_join(CHARLS_w1_id, CHARLS_w1_loneliness, by="id")[,-2]


```

```{r local1, echo=F}

vari <- CHARLS_w1_loneliness$dc017
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w1_loneliness$dc017, missing_values = NA)
ggplot(CHARLS_w1_loneliness, aes(x=factor(dc017))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Felt loneliness") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3,4 into 1`
* `1 into 0`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
CHARLS_ds_w1 <- tibble(id=CHARLS_w1_loneliness$id)
CHARLS_ds_w1$loneliness <- car::recode(as.vector(CHARLS_w1_loneliness$dc017), "2:4='1'; 1='0'; NA='999'")
CHARLS_ds_w1$loneliness <- labelled(CHARLS_ds_w1$loneliness, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <- CHARLS_ds_w1$loneliness
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = CHARLS_ds_w1$loneliness, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(CHARLS_ds_w1, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("felt loneliness?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(CHARLS_ds_w1$loneliness)
BeforeH <- table(CHARLS_w1_loneliness$dc017, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2:4)])
BeforeH1[[3]] <- BeforeH[[5]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1->0","2:4->1","NA->999")
kable(C)
```



### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `dc017`
* Label: `Felt loneliness`
* Categories: 
    + `1 = Rarely or none of the time <1 day`
    + `2 = Some or a little of the time 1-2 days`
    + `3 = Occasionally or a moderate amount of the time 3-4 days`
    + `4 = Most or all of the time 5-7 days`

* Description: 
```{r assign2, echo=F}
opal.assign.table.tibble(o, 'CHARLS_w2_loneliness','CHARLS.Health_Status_and_Functioning_wave2',variables=list('dc017'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids', variables=list('var'), missings = TRUE)

CHARLS_w2_loneliness <- opal.execute(o,'CHARLS_w2_loneliness')
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')

CHARLS_w2_loneliness <- left_join(CHARLS_w2_id, CHARLS_w2_loneliness, by="id")[,-2]

```

```{r local2, echo=F}

vari <- CHARLS_w2_loneliness$dc017
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_loneliness$dc017, missing_values = NA)
ggplot(CHARLS_w2_loneliness, aes(x=factor(dc017))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Felt loneliness") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `2,3,4 into 1`
* `1 into 0`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
CHARLS_ds_w2 <- tibble(id=CHARLS_w2_loneliness$id)
CHARLS_ds_w2$loneliness <- car::recode(as.vector(CHARLS_w2_loneliness$dc017), "2:4='1'; 1='0'; NA='999'")
CHARLS_ds_w2$loneliness <- labelled(CHARLS_ds_w2$loneliness, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}
vari <- CHARLS_ds_w2$loneliness
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = CHARLS_ds_w2$loneliness, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(CHARLS_ds_w2, aes(x=factor(loneliness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("felt loneliness?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
AfterH <- table(CHARLS_ds_w2$loneliness)
BeforeH <- table(CHARLS_w2_loneliness$dc017, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH[[1]]
BeforeH1[[2]] <- sum(BeforeH[c(2:4)])
BeforeH1[[3]] <- BeforeH[[5]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1->0","2:4->1","NA->999")
kable(C)
```



```{r save, echo=FALSE}
loneliness <- CHARLS_ds_w1
save(loneliness, file = "../RData/w1/loneliness.RData")
rm(loneliness)

loneliness <- CHARLS_ds_w2
save(loneliness, file = "../RData/w2/loneliness.RData")
rm(loneliness)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```


