---
title: "Has children and/or grandchildren"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/CHARLS/9_Social_env_life_events/CHARLS_ids.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `child`
* Variable label: `Has children`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Short name: `grchild`
* Variable label: `Has grandchildren`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 

# Data process

##China (All counties with the exception of Tibet)

### Wave 1 

#### Study-specific variables

The study-specific variables elected to be harmonised are:

* Name: `cb001` *from the table "family_information_wave1"*
* Label: `How Many Biological Children`
    
* Name: `cb009` *from the table "family_information_wave1"*
* Label: `Num. of Adopted or Fostered Children Currently Living but Not Living with You`

* Name: `a006_1_` UP TO `a006_16_` *from the table "household_roster_wave1"*
* Label: `Relationship to FamilyR`
* Categories:
    * `1 = Mother`
    * `2 = Father`
    * `3 = Mother-in-law`
    * `4 = Father-in-law`
    * `5 = Sibling`
    * `6 = Brother-in-law, sister-in-law`
    * `7 = Child`
    * `8 = Spouse of child`
    * `9 = Grandchild`
    * `10 = Other relative specify`

	
* Name: `cb065_1_` UP TO 	`cb065_14_` *from the table "family_information_wave1"*
* Label: `Num. of Sons this Child has`

	
* Name: `cb067_1_` UP TO 	`cb067_14_` *from the table "family_information_wave1"*
* Label: `Num. of Daughters this Child has`

* Description: 
```{r assign1}
opal.assign.table.tibble(o, 'CHARLS_w1_child1','CHARLS.family_information_wave1',
                         variables=list('cb001','cb009',
                                        'cb065_1_','cb065_2_','cb065_3_','cb065_4_','cb065_5_',
                                        'cb065_6_','cb065_7_','cb065_8_','cb065_9_','cb065_10_',
                                        'cb065_11_','cb065_12_','cb065_13_','cb065_14_',
                                        'cb067_1_','cb067_2_','cb067_3_','cb067_4_','cb067_5_',
                                        'cb067_6_','cb067_7_','cb067_8_','cb067_9_','cb067_10_',
                                        'cb067_11_','cb067_12_','cb067_13_','cb067_14_'), missings = TRUE)

opal.assign.table.tibble(o, 'CHARLS_w1_child2','CHARLS.household_roster_wave1',
                         variables=list('a006_1_','a006_2_','a006_3_','a006_4_','a006_5_',
                                        'a006_6_','a006_7_','a006_8_','a006_9_','a006_10_',
                                        'a006_11_','a006_12_','a006_13_','a006_14_','a006_15_',
                                        'a006_16_'), missings = TRUE)

opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids',
                         variables=list('var'), missings = TRUE)

```

```{r local1}
CHARLS_w1_child1 <- opal.execute(o,'CHARLS_w1_child1')
CHARLS_w1_child2 <- opal.execute(o,'CHARLS_w1_child2')
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')


CHARLS_w1_child1$oldid <- CHARLS_w1_child1$id
CHARLS_w1_child1$id <- CHARLS_ids(ids = CHARLS_w1_child1$oldid)
CHARLS_w1_child1 <- left_join(CHARLS_w1_id, CHARLS_w1_child1, by="id")[,-2]

CHARLS_w1_child2$oldid <- CHARLS_w1_child2$id
CHARLS_w1_child2$id <- CHARLS_ids(ids = CHARLS_w1_child2$oldid)
CHARLS_w1_child2 <- left_join(CHARLS_w1_id, CHARLS_w1_child2, by="id")[,-2]



vari <- CHARLS_w1_child1$cb001
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = CHARLS_w1_child1$cb001, missing_values = NA)
ggplot(CHARLS_w1_child1, aes(x=factor(cb001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of biological children") + ylab("Frequency")

vari <- CHARLS_w1_child1$cb009
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = CHARLS_w1_child1$cb009, missing_values = NA)
ggplot(CHARLS_w1_child1, aes(x=factor(cb009))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of adopted or fostered children (living but not living with him/her)") + ylab("Frequency")

vari <- CHARLS_w1_child1$cb065_1_
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = CHARLS_w1_child1$cb065_1_, missing_values = NA)
ggplot(CHARLS_w1_child1, aes(x=factor(cb065_1_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Num. of Sons this Child has") + ylab("Frequency")

vari <- CHARLS_w1_child1$cb067_1_
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = CHARLS_w1_child1$cb067_1_, missing_values = NA)
ggplot(CHARLS_w1_child1, aes(x=factor(cb067_1_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Num. of Daughters this Child has") + ylab("Frequency")


vari <- CHARLS_w1_child2$a006_1_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w1_child2$a006_1_, missing_values = NA)
ggplot(CHARLS_w1_child2, aes(x=factor(a006_1_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Relationship to FamilyR") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `CHILDREN`
* `cb001=0 AND cb009=0 into 0`
* `cb001>0 OR cb009>0 OR if any of a006_1_, ..., a006_16_ = 7 into 1`

* `GRANDCHILDREN`
*`if any of a006_1_, ..., a006_16_ = 9 OR `
  ` any of cb065_1_,...,cb065_14_ >0 OR any of cb067_1_,...cb067_14_ > 0 into 1`
*`if all of cb065_1_,...,cb065_14_ AND cb067_1_,...cb067_14_ are equal 0, then 0`

* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
# CHILDREN
CHARLS_ds_w1 <- tibble(id=CHARLS_w1_child1$id)

CHARLS_w1_child1$cb001 <- car::recode(as.vector(CHARLS_w1_child1$cb001), "NA='-999'")
CHARLS_w1_child1$cb009 <- car::recode(as.vector(CHARLS_w1_child1$cb009), "NA='-999'")
CHARLS_w1_child2$a006_1_ <- car::recode(as.vector(CHARLS_w1_child2$a006_1_), "NA='-999'")
CHARLS_w1_child2$a006_2_ <- car::recode(as.vector(CHARLS_w1_child2$a006_2_), "NA='-999'")
CHARLS_w1_child2$a006_3_ <- car::recode(as.vector(CHARLS_w1_child2$a006_3_), "NA='-999'")
CHARLS_w1_child2$a006_4_ <- car::recode(as.vector(CHARLS_w1_child2$a006_4_), "NA='-999'")
CHARLS_w1_child2$a006_5_ <- car::recode(as.vector(CHARLS_w1_child2$a006_5_), "NA='-999'")
CHARLS_w1_child2$a006_6_ <- car::recode(as.vector(CHARLS_w1_child2$a006_6_), "NA='-999'")
CHARLS_w1_child2$a006_7_ <- car::recode(as.vector(CHARLS_w1_child2$a006_7_), "NA='-999'")
CHARLS_w1_child2$a006_8_ <- car::recode(as.vector(CHARLS_w1_child2$a006_8_), "NA='-999'")
CHARLS_w1_child2$a006_9_ <- car::recode(as.vector(CHARLS_w1_child2$a006_9_), "NA='-999'")
CHARLS_w1_child2$a006_10_ <- car::recode(as.vector(CHARLS_w1_child2$a006_10_), "NA='-999'")
CHARLS_w1_child2$a006_11_ <- car::recode(as.vector(CHARLS_w1_child2$a006_11_), "NA='-999'")
CHARLS_w1_child2$a006_12_ <- car::recode(as.vector(CHARLS_w1_child2$a006_12_), "NA='-999'")
CHARLS_w1_child2$a006_13_ <- car::recode(as.vector(CHARLS_w1_child2$a006_13_), "NA='-999'")
CHARLS_w1_child2$a006_14_ <- car::recode(as.vector(CHARLS_w1_child2$a006_14_), "NA='-999'")
CHARLS_w1_child2$a006_15_ <- car::recode(as.vector(CHARLS_w1_child2$a006_15_), "NA='-999'")
CHARLS_w1_child2$a006_16_ <- car::recode(as.vector(CHARLS_w1_child2$a006_16_), "NA='-999'")





CHARLS_ds_w1$child <- c(NA) 
for(i in 1:dim(CHARLS_w1_child1)[1]){
  if(CHARLS_w1_child1$cb001[i] == 0 & CHARLS_w1_child1$cb009[i] == 0) {
    CHARLS_ds_w1$child[i] = 0 }
  else if(CHARLS_w1_child1$cb001[i] > 0 | CHARLS_w1_child1$cb009[i] > 0 |
        CHARLS_w1_child2$a006_1_[i] == 7 | CHARLS_w1_child2$a006_2_[i] == 7 | CHARLS_w1_child2$a006_3_[i] == 7 | 
        CHARLS_w1_child2$a006_4_[i] == 7 | CHARLS_w1_child2$a006_5_[i] == 7 | CHARLS_w1_child2$a006_6_[i] == 7 |
        CHARLS_w1_child2$a006_7_[i] == 7 | CHARLS_w1_child2$a006_8_[i] == 7 | CHARLS_w1_child2$a006_9_[i] == 7 |
        CHARLS_w1_child2$a006_10_[i] == 7 | CHARLS_w1_child2$a006_11_[i] == 7 | CHARLS_w1_child2$a006_12_[i] == 7 |
        CHARLS_w1_child2$a006_13_[i] == 7 | CHARLS_w1_child2$a006_14_[i] == 7 | CHARLS_w1_child2$a006_15_[i] == 7 |
        CHARLS_w1_child2$a006_16_[i] == 7) {
    CHARLS_ds_w1$child[i] = 1 }
}
CHARLS_ds_w1$child <- car::recode(as.vector(CHARLS_ds_w1$child), "NA='999'")
CHARLS_ds_w1$child <- labelled(CHARLS_ds_w1$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))




# GRANDCHILDREN


CHARLS_w1_child1$cb065_1_ <- car::recode(as.vector(CHARLS_w1_child1$cb065_1_), "NA='-999'")
CHARLS_w1_child1$cb065_2_ <- car::recode(as.vector(CHARLS_w1_child1$cb065_2_), "NA='-999'")
CHARLS_w1_child1$cb065_3_ <- car::recode(as.vector(CHARLS_w1_child1$cb065_3_), "NA='-999'")
CHARLS_w1_child1$cb065_4_ <- car::recode(as.vector(CHARLS_w1_child1$cb065_4_), "NA='-999'")
CHARLS_w1_child1$cb065_5_ <- car::recode(as.vector(CHARLS_w1_child1$cb065_5_), "NA='-999'")
CHARLS_w1_child1$cb065_6_ <- car::recode(as.vector(CHARLS_w1_child1$cb065_6_), "NA='-999'")
CHARLS_w1_child1$cb065_7_ <- car::recode(as.vector(CHARLS_w1_child1$cb065_7_), "NA='-999'")
CHARLS_w1_child1$cb065_8_ <- car::recode(as.vector(CHARLS_w1_child1$cb065_8_), "NA='-999'")
CHARLS_w1_child1$cb065_9_ <- car::recode(as.vector(CHARLS_w1_child1$cb065_9_), "NA='-999'")
CHARLS_w1_child1$cb065_10_ <- car::recode(as.vector(CHARLS_w1_child1$cb065_10_), "NA='-999'")
CHARLS_w1_child1$cb065_11_ <- car::recode(as.vector(CHARLS_w1_child1$cb065_11_), "NA='-999'")
CHARLS_w1_child1$cb065_12_ <- car::recode(as.vector(CHARLS_w1_child1$cb065_12_), "NA='-999'")
CHARLS_w1_child1$cb065_13_ <- car::recode(as.vector(CHARLS_w1_child1$cb065_13_), "NA='-999'")
CHARLS_w1_child1$cb065_14_ <- car::recode(as.vector(CHARLS_w1_child1$cb065_14_), "NA='-999'")

CHARLS_w1_child1$cb067_1_ <- car::recode(as.vector(CHARLS_w1_child1$cb067_1_), "NA='-999'")
CHARLS_w1_child1$cb067_2_ <- car::recode(as.vector(CHARLS_w1_child1$cb067_2_), "NA='-999'")
CHARLS_w1_child1$cb067_3_ <- car::recode(as.vector(CHARLS_w1_child1$cb067_3_), "NA='-999'")
CHARLS_w1_child1$cb067_4_ <- car::recode(as.vector(CHARLS_w1_child1$cb067_4_), "NA='-999'")
CHARLS_w1_child1$cb067_5_ <- car::recode(as.vector(CHARLS_w1_child1$cb067_5_), "NA='-999'")
CHARLS_w1_child1$cb067_6_ <- car::recode(as.vector(CHARLS_w1_child1$cb067_6_), "NA='-999'")
CHARLS_w1_child1$cb067_7_ <- car::recode(as.vector(CHARLS_w1_child1$cb067_7_), "NA='-999'")
CHARLS_w1_child1$cb067_8_ <- car::recode(as.vector(CHARLS_w1_child1$cb067_8_), "NA='-999'")
CHARLS_w1_child1$cb067_9_ <- car::recode(as.vector(CHARLS_w1_child1$cb067_9_), "NA='-999'")
CHARLS_w1_child1$cb067_10_ <- car::recode(as.vector(CHARLS_w1_child1$cb067_10_), "NA='-999'")
CHARLS_w1_child1$cb067_11_ <- car::recode(as.vector(CHARLS_w1_child1$cb067_11_), "NA='-999'")
CHARLS_w1_child1$cb067_12_ <- car::recode(as.vector(CHARLS_w1_child1$cb067_12_), "NA='-999'")
CHARLS_w1_child1$cb067_13_ <- car::recode(as.vector(CHARLS_w1_child1$cb067_13_), "NA='-999'")
CHARLS_w1_child1$cb067_14_ <- car::recode(as.vector(CHARLS_w1_child1$cb067_14_), "NA='-999'")



CHARLS_ds_w1$grchild <- c(NA) 
for(i in 1:dim(CHARLS_w1_child1)[1]){
  
  if(CHARLS_w1_child1$cb065_1_[i] == 0 & CHARLS_w1_child1$cb065_2_[i] == 0 & CHARLS_w1_child1$cb065_3_[i] == 0 & 
        CHARLS_w1_child1$cb065_4_[i] == 0 & CHARLS_w1_child1$cb065_5_[i] == 0 & CHARLS_w1_child1$cb065_6_[i] == 0 & 
        CHARLS_w1_child1$cb065_7_[i] == 0 & CHARLS_w1_child1$cb065_8_[i] == 0 & CHARLS_w1_child1$cb065_9_[i] == 0 & 
        CHARLS_w1_child1$cb065_10_[i] == 0 & CHARLS_w1_child1$cb065_11_[i] == 0 & CHARLS_w1_child1$cb065_12_[i] == 0 & 
        CHARLS_w1_child1$cb065_13_[i] == 0 & CHARLS_w1_child1$cb065_14_[i] == 0 & 
        
        CHARLS_w1_child1$cb067_1_[i] == 0 & CHARLS_w1_child1$cb067_2_[i] == 0 & CHARLS_w1_child1$cb067_3_[i] == 0 & 
        CHARLS_w1_child1$cb067_4_[i] == 0 & CHARLS_w1_child1$cb067_5_[i] == 0 & CHARLS_w1_child1$cb067_6_[i] == 0 & 
        CHARLS_w1_child1$cb067_7_[i] == 0 & CHARLS_w1_child1$cb067_8_[i] == 0 & CHARLS_w1_child1$cb067_9_[i] == 0 & 
        CHARLS_w1_child1$cb067_10_[i] == 0 & CHARLS_w1_child1$cb067_11_[i] == 0 & CHARLS_w1_child1$cb067_12_[i] == 0 & 
        CHARLS_w1_child1$cb067_13_[i] == 0 & CHARLS_w1_child1$cb067_14_[i] == 0
        ) { 
  CHARLS_ds_w1$grchild[i] = 0 }
  
  else if(CHARLS_w1_child2$a006_1_[i] == 9 | CHARLS_w1_child2$a006_2_[i] == 9 | CHARLS_w1_child2$a006_3_[i] == 9 | 
        CHARLS_w1_child2$a006_4_[i] == 9 | CHARLS_w1_child2$a006_5_[i] == 9 | CHARLS_w1_child2$a006_6_[i] == 9 |
        CHARLS_w1_child2$a006_7_[i] == 9 | CHARLS_w1_child2$a006_8_[i] == 9 | CHARLS_w1_child2$a006_9_[i] == 9 |
        CHARLS_w1_child2$a006_10_[i] == 9 | CHARLS_w1_child2$a006_11_[i] == 9 | CHARLS_w1_child2$a006_12_[i] == 9 |
        CHARLS_w1_child2$a006_13_[i] == 9 | CHARLS_w1_child2$a006_14_[i] == 9 | CHARLS_w1_child2$a006_15_[i] == 9 |
        CHARLS_w1_child2$a006_16_[i] == 9 |
        
        CHARLS_w1_child1$cb065_1_[i] > 0 | CHARLS_w1_child1$cb065_2_[i] > 0 | CHARLS_w1_child1$cb065_3_[i] > 0 | 
        CHARLS_w1_child1$cb065_4_[i] > 0 | CHARLS_w1_child1$cb065_5_[i] > 0 | CHARLS_w1_child1$cb065_6_[i] > 0 | 
        CHARLS_w1_child1$cb065_7_[i] > 0 | CHARLS_w1_child1$cb065_8_[i] > 0 | CHARLS_w1_child1$cb065_9_[i] > 0 | 
        CHARLS_w1_child1$cb065_10_[i] > 0 | CHARLS_w1_child1$cb065_11_[i] > 0 | CHARLS_w1_child1$cb065_12_[i] > 0 | 
        CHARLS_w1_child1$cb065_13_[i] > 0 | CHARLS_w1_child1$cb065_14_[i] > 0 | 
        
        CHARLS_w1_child1$cb067_1_[i] > 0 | CHARLS_w1_child1$cb067_2_[i] > 0 | CHARLS_w1_child1$cb067_3_[i] > 0 | 
        CHARLS_w1_child1$cb067_4_[i] > 0 | CHARLS_w1_child1$cb067_5_[i] > 0 | CHARLS_w1_child1$cb067_6_[i] > 0 | 
        CHARLS_w1_child1$cb067_7_[i] > 0 | CHARLS_w1_child1$cb067_8_[i] > 0 | CHARLS_w1_child1$cb067_9_[i] > 0 | 
        CHARLS_w1_child1$cb067_10_[i] > 0 | CHARLS_w1_child1$cb067_11_[i] > 0 | CHARLS_w1_child1$cb067_12_[i] > 0 | 
        CHARLS_w1_child1$cb067_13_[i] > 0 | CHARLS_w1_child1$cb067_14_[i] > 0
        ) {
  CHARLS_ds_w1$grchild[i] = 1 }
}

CHARLS_ds_w1$grchild <- car::recode(as.vector(CHARLS_ds_w1$grchild), "NA='999'")
CHARLS_ds_w1$grchild <- labelled(CHARLS_ds_w1$grchild, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1}
vari <- CHARLS_ds_w1$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = CHARLS_ds_w1$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(CHARLS_ds_w1, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")

vari <- CHARLS_ds_w1$grchild
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = CHARLS_ds_w1$grchild, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(CHARLS_ds_w1, aes(x=factor(grchild))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has grandchildren") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1}

```

 
 


### Wave 2

#### Study-specific variables

The study-specific variables elected to be harmonised are:

* Name: `cb001`
* Label: `Number of Alive Children`
    
* Name: `cb009`
* Label: `Number of Alive Adopted/Foster/Step Children`

* Name: `a006_1_` UP TO a006_16_
* Label: `Relationship to You`
* Categories:
    * `1 = Mother`
    * `2 = Father`
    * `3 = Mother-in-law`
    * `4 = Father-in-law`
    * `5 = Sibling`
    * `6 = Brother/Sister-in-law`
    * `7 = Child`
    * `8 = Spouse of Child`
    * `9 = Grandchild`
    * `10 = Nanny`
    * `11 = Driver`
    * `12 = Other Relative`

* Name: `cb065_1_` UP TO `cb065_11_`
* Label: `How Many Children Does Child Have`


* Description: 
```{r assign2}
opal.assign.table.tibble(o, 'CHARLS_w2_child','CHARLS.Family_Information_wave2',
                         variables=list('cb001','cb009', 
                                        'a006_1_','a006_2_','a006_3_','a006_4_','a006_5_','a006_6_',
                                        'a006_7_','a006_8_','a006_9_','a006_10_','a006_11_','a006_12_',
                                        'a006_13_','a006_14_','a006_15_','a006_16_',
                                        'cb065_1_','cb065_2_','cb065_3_','cb065_4_','cb065_5_','cb065_6_',
                                        'cb065_7_','cb065_8_','cb065_9_','cb065_10_','cb065_11_'
                                        ), missings = TRUE)

opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids',
                         variables=list('var'), missings = TRUE)
```

```{r local2}
CHARLS_w2_child <- opal.execute(o,'CHARLS_w2_child')
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')
CHARLS_w2_child <- left_join(CHARLS_w2_id, CHARLS_w2_child, by="id")[,-2]

vari <- CHARLS_w2_child$cb001
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = CHARLS_w2_child$cb001, missing_values = NA)
ggplot(CHARLS_w2_child, aes(x=factor(cb001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of Alive Children") + ylab("Frequency")


vari <- CHARLS_w2_child$cb009
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = CHARLS_w2_child$cb009, missing_values = NA)
ggplot(CHARLS_w2_child, aes(x=factor(cb009))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of Alive Adopted/Foster/Step Children") + ylab("Frequency")


vari <- CHARLS_w2_child$a006_1_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w2_child$a006_1_, missing_values = NA)
ggplot(CHARLS_w2_child, aes(x=factor(a006_1_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Relationship to You") + ylab("Frequency")


vari <- CHARLS_w2_child$cb065_1_
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = CHARLS_w2_child$cb065_1_, missing_values = NA)
ggplot(CHARLS_w2_child, aes(x=factor(cb065_1_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How Many Children Does Child Have") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `CHILDREN`
* `cb001=0 AND cb009=0 into 0`
* `cb001>0 OR cb009>0 OR any of a006_1_,...,a006_16_ = 7 into 1`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}

# CHILDREN


CHARLS_w2_child$cb001 <- car::recode(as.vector(CHARLS_w2_child$cb001), "NA='-999'")
CHARLS_w2_child$cb009 <- car::recode(as.vector(CHARLS_w2_child$cb009), "NA='-999'")
CHARLS_w2_child$a006_1_ <- car::recode(as.vector(CHARLS_w2_child$a006_1_), "NA='-999'")
CHARLS_w2_child$a006_2_ <- car::recode(as.vector(CHARLS_w2_child$a006_2_), "NA='-999'")
CHARLS_w2_child$a006_3_ <- car::recode(as.vector(CHARLS_w2_child$a006_3_), "NA='-999'")
CHARLS_w2_child$a006_4_ <- car::recode(as.vector(CHARLS_w2_child$a006_4_), "NA='-999'")
CHARLS_w2_child$a006_5_ <- car::recode(as.vector(CHARLS_w2_child$a006_5_), "NA='-999'")
CHARLS_w2_child$a006_6_ <- car::recode(as.vector(CHARLS_w2_child$a006_6_), "NA='-999'")
CHARLS_w2_child$a006_7_ <- car::recode(as.vector(CHARLS_w2_child$a006_7_), "NA='-999'")
CHARLS_w2_child$a006_8_ <- car::recode(as.vector(CHARLS_w2_child$a006_8_), "NA='-999'")
CHARLS_w2_child$a006_9_ <- car::recode(as.vector(CHARLS_w2_child$a006_9_), "NA='-999'")
CHARLS_w2_child$a006_10_ <- car::recode(as.vector(CHARLS_w2_child$a006_10_), "NA='-999'")
CHARLS_w2_child$a006_11_ <- car::recode(as.vector(CHARLS_w2_child$a006_11_), "NA='-999'")
CHARLS_w2_child$a006_12_ <- car::recode(as.vector(CHARLS_w2_child$a006_12_), "NA='-999'")
CHARLS_w2_child$a006_13_ <- car::recode(as.vector(CHARLS_w2_child$a006_13_), "NA='-999'")
CHARLS_w2_child$a006_14_ <- car::recode(as.vector(CHARLS_w2_child$a006_14_), "NA='-999'")
CHARLS_w2_child$a006_15_ <- car::recode(as.vector(CHARLS_w2_child$a006_15_), "NA='-999'")
CHARLS_w2_child$a006_16_ <- car::recode(as.vector(CHARLS_w2_child$a006_16_), "NA='-999'")

CHARLS_ds_w2 <- tibble(id=CHARLS_w2_child$id)
CHARLS_ds_w2$child <- c(NA) 

for(i in 1:dim(CHARLS_w2_child)[1]){
  if(CHARLS_w2_child$cb001[i] == 0 & CHARLS_w2_child$cb009[i] == 0) {
    CHARLS_ds_w2$child[i] = 0 }
  
  else if(CHARLS_w2_child$cb001[i] > 0 | CHARLS_w2_child$cb009[i] > 0 |
        CHARLS_w2_child$a006_1_[i] == 7 | CHARLS_w2_child$a006_2_[i] == 7 | CHARLS_w2_child$a006_3_[i] == 7 | 
        CHARLS_w2_child$a006_4_[i] == 7 | CHARLS_w2_child$a006_5_[i] == 7 | CHARLS_w2_child$a006_6_[i] == 7 | 
        CHARLS_w2_child$a006_7_[i] == 7 | CHARLS_w2_child$a006_8_[i] == 7 | CHARLS_w2_child$a006_9_[i] == 7 | 
        CHARLS_w2_child$a006_10_[i] == 7 | CHARLS_w2_child$a006_11_[i] == 7 | CHARLS_w2_child$a006_12_[i] == 7 | 
        CHARLS_w2_child$a006_13_[i] == 7 | CHARLS_w2_child$a006_14_[i] == 7 | CHARLS_w2_child$a006_15_[i] == 7 | 
        CHARLS_w2_child$a006_16_[i] == 7
        ) {
  CHARLS_ds_w2$child[i] = 1 }
}
CHARLS_ds_w2$child <- car::recode(as.vector(CHARLS_ds_w2$child), "NA='999'")
CHARLS_ds_w2$child <- labelled(CHARLS_ds_w2$child, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=996, "Does not answer"=995,  "Not applicable"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2}
vari <- CHARLS_ds_w2$child
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = CHARLS_ds_w2$child, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(CHARLS_ds_w2, aes(x=factor(child))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has children") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2}

```

 
 
```{r save, echo=FALSE}
child <- CHARLS_ds_w1[,-3]
save(child, file = "../RData/w1/child.RData")
rm(child)

child <- CHARLS_ds_w2
save(child, file = "../RData/w2/child.RData")
rm(child)


grchild <- CHARLS_ds_w1[,-2]
save(grchild, file = "../RData/w1/grchild.RData")
rm(grchild)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```

