---
title: "Has other (living) family members (e.g. parents, siblings, in-laws, etc.)"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/CHARLS/9_Social_env_life_events/CHARLS_ids.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `oth_fam`
* Variable label: `Has other (living) family members (e.g. parents, siblings, in-laws, etc.)`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process
## China (All counties with the exception of Tibet)
### Wave 1 



#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `cc001`
* Label: `Num. of Your Siblings are Still Alive`

* Name: `cc006`
* Label: `Num. of Your Spouse's Siblings are Still Alive`

* Name: `ca001_1_` UP TO `ca001_4_` **probably father, mother, father-in-law, mother-in-law ??**
* Label: `Whether Parent Still Living`
* Categories:
    + `1 = Yes`
    + `2 = No`


* Description: 
```{r assign1}
opal.assign.table.tibble(o, 'CHARLS_w1_oth_fam','CHARLS.family_information_wave1', 
                        variables=list('cc001','cc006','ca001_1_','ca001_2_','ca001_3_','ca001_4_'), missings = TRUE)


opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids',
                         variables=list('var'), missings = TRUE)
```

```{r local1}
CHARLS_w1_oth_fam <- opal.execute(o,'CHARLS_w1_oth_fam')
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')


CHARLS_w1_oth_fam$oldid <- CHARLS_w1_oth_fam$id
CHARLS_w1_oth_fam$id <- CHARLS_ids(ids = CHARLS_w1_oth_fam$oldid)

CHARLS_w1_oth_fam <- left_join(CHARLS_w1_id, CHARLS_w1_oth_fam, by="id")[,-2]



vari <- CHARLS_w1_oth_fam$cc001
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = CHARLS_w1_oth_fam$cc001, missing_values = NA)
ggplot(CHARLS_w1_oth_fam, aes(x=factor(cc001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Num. of Your Siblings are Still Alive") + ylab("Frequency")

vari <- CHARLS_w1_oth_fam$cc006
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = CHARLS_w1_oth_fam$cc006, missing_values = NA)
ggplot(CHARLS_w1_oth_fam, aes(x=factor(cc006))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Num. of Your Spouse's Siblings are Still Alive") + ylab("Frequency")

vari <- CHARLS_w1_oth_fam$ca001_1_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w1_oth_fam$ca001_1_, missing_values = NA)
ggplot(CHARLS_w1_oth_fam, aes(x=factor(ca001_1_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Whether Parent Still Living") + ylab("Frequency")

vari <- CHARLS_w1_oth_fam$ca001_2_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w1_oth_fam$ca001_2_, missing_values = NA)
ggplot(CHARLS_w1_oth_fam, aes(x=factor(ca001_2_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Whether Parent Still Living") + ylab("Frequency")

vari <- CHARLS_w1_oth_fam$ca001_3_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w1_oth_fam$ca001_3_, missing_values = NA)
ggplot(CHARLS_w1_oth_fam, aes(x=factor(ca001_3_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Whether Parent Still Living") + ylab("Frequency")

vari <- CHARLS_w1_oth_fam$ca001_4_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = CHARLS_w1_oth_fam$ca001_4_, missing_values = NA)
ggplot(CHARLS_w1_oth_fam, aes(x=factor(ca001_4_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Whether Parent Still Living") + ylab("Frequency")

## more and more NAs from ca001_1_ to ca001_4_ - it should be taken into account in the algorithm (not to produce too many 999 instead of zeros)
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if cc001 or cc006 > 0 or any of ca001_i_=1 then 1`
* `if cc001 and cc006 are 0 and all of ca001_i_=2 (or NA!!) then 0`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
CHARLS_ds_w1 <- tibble(id=CHARLS_w1_oth_fam$id)

CHARLS_w1_oth_fam$cc001 <- car::recode(as.vector(CHARLS_w1_oth_fam$cc001), "NA='-999'")
CHARLS_w1_oth_fam$cc006 <- car::recode(as.vector(CHARLS_w1_oth_fam$cc006), "NA='-999'")
CHARLS_w1_oth_fam$ca001_1_ <- car::recode(as.vector(CHARLS_w1_oth_fam$ca001_1_), "NA='-999'")
CHARLS_w1_oth_fam$ca001_2_ <- car::recode(as.vector(CHARLS_w1_oth_fam$ca001_2_), "NA='-999'")
CHARLS_w1_oth_fam$ca001_3_ <- car::recode(as.vector(CHARLS_w1_oth_fam$ca001_3_), "NA='-999'")
CHARLS_w1_oth_fam$ca001_4_ <- car::recode(as.vector(CHARLS_w1_oth_fam$ca001_4_), "NA='-999'")

CHARLS_ds_w1$oth_fam <- c(NA) 
for(i in 1:dim(CHARLS_w1_oth_fam)[1]){
  if( CHARLS_w1_oth_fam$cc001[i] >0 | CHARLS_w1_oth_fam$cc006[i] >0 | 
      CHARLS_w1_oth_fam$ca001_1_[i] ==1 | CHARLS_w1_oth_fam$ca001_2_[i] ==1 | 
      CHARLS_w1_oth_fam$ca001_3_[i] ==1 | CHARLS_w1_oth_fam$ca001_4_[i] ==1 ){
    CHARLS_ds_w1$oth_fam[i] = 1 }
  else if( CHARLS_w1_oth_fam$cc001[i] ==0 & CHARLS_w1_oth_fam$cc006[i] ==0 & 
      CHARLS_w1_oth_fam$ca001_1_[i] ==2 & CHARLS_w1_oth_fam$ca001_2_[i] %in% c(2,-999) & 
      CHARLS_w1_oth_fam$ca001_3_[i] %in% c(2,-999) & CHARLS_w1_oth_fam$ca001_4_[i] %in% c(2,-999) ){
    CHARLS_ds_w1$oth_fam[i] = 0 }
}
  
CHARLS_ds_w1$oth_fam <- car::recode(as.vector(CHARLS_ds_w1$oth_fam), "NA='999'")
CHARLS_ds_w1$oth_fam <- labelled(CHARLS_ds_w1$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1}
vari <- CHARLS_ds_w1$oth_fam
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = CHARLS_ds_w1$oth_fam, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(CHARLS_ds_w1, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1}

```


### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `cc002_1_1_`
* Label: `Number of Your Alive Older Brothers`

* Name: `cc002_2_1_`
* Label: `Number of Your Alive Younger Brothers`

* Name: `cc002_3_1_`
* Label: `Number of Your Alive Older Sisters`

* Name: `cc002_4_1_`
* Label: `Number of Your Alive Younger Sisters`


* Name: `cc002_1_2_`
* Label: `Number of Your Spouse's Alive Older Brothers`

* Name: `cc002_2_2_`
* Label: `Number of Your Spouse's Alive Younger Brothers`

* Name: `cc002_3_2_`
* Label: `Number of Your Spouse's Alive Older Sisters`

* Name: `cc002_4_2_`
* Label: `Number of Your Spouse's Alive Younger Sisters`


* Name: `ca001_1_`
* Label: `Is Your Father Living`
* Categories:
    + `1 = Yes`
    + `2 = No`
    
* Name: `ca001_2_`
* Label: `Is Your Mother Living`
* Categories:
    + `1 = Yes`
    + `2 = No`
    
* Name: `ca001_3_`
* Label: `Is Your Father-in-law Living`
* Categories:
    + `1 = Yes`
    + `2 = No`
    
* Name: `ca001_4_`
* Label: `Is Your Mother-in-law Living`
* Categories:
    + `1 = Yes`
    + `2 = No`


* Description: 
```{r assign2}
opal.assign.table.tibble(o, 'CHARLS_w2_oth_fam','CHARLS.Family_Information_wave2', 
                        variables=list('cc002_1_1_','cc002_2_1_','cc002_3_1_','cc002_4_1_',
                                       'cc002_1_2_','cc002_2_2_','cc002_3_2_','cc002_4_2_',
                                       'ca001_1_','ca001_2_','ca001_3_','ca001_4_'), missings = TRUE)

opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids',
                         variables=list('var'), missings = TRUE)
```

```{r local2}
CHARLS_w2_oth_fam <- opal.execute(o,'CHARLS_w2_oth_fam')
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')

CHARLS_w2_oth_fam <- left_join(CHARLS_w2_id, CHARLS_w2_oth_fam, by="id")[,-2]

vari <- CHARLS_w2_oth_fam$cc002_1_1_
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = CHARLS_w2_oth_fam$cc002_1_1_, missing_values = NA)
ggplot(CHARLS_w2_oth_fam, aes(x=factor(cc002_1_1_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of Your Spouse's Alive Older Brothers") + ylab("Frequency")

vari <- CHARLS_w2_oth_fam$cc002_2_1_
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = CHARLS_w2_oth_fam$cc002_2_1_, missing_values = NA)
ggplot(CHARLS_w2_oth_fam, aes(x=factor(cc002_2_1_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of Your Spouse's Alive Younger Brothers") + ylab("Frequency")

vari <- CHARLS_w2_oth_fam$cc002_3_1_
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = CHARLS_w2_oth_fam$cc002_3_1_, missing_values = NA)
ggplot(CHARLS_w2_oth_fam, aes(x=factor(cc002_3_1_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of Your Spouse's Alive Older Sisters") + ylab("Frequency")

vari <- CHARLS_w2_oth_fam$cc002_4_1_
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = CHARLS_w2_oth_fam$cc002_4_1_, missing_values = NA)
ggplot(CHARLS_w2_oth_fam, aes(x=factor(cc002_4_1_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of Your Spouse's Alive Younger Sisters") + ylab("Frequency")

vari <- CHARLS_w2_oth_fam$cc002_1_2_
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = CHARLS_w2_oth_fam$cc002_1_2_, missing_values = NA)
ggplot(CHARLS_w2_oth_fam, aes(x=factor(cc002_1_2_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of Your Spouse's Alive Older Brothers") + ylab("Frequency")

vari <- CHARLS_w2_oth_fam$cc002_2_2_
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = CHARLS_w2_oth_fam$cc002_2_2_, missing_values = NA)
ggplot(CHARLS_w2_oth_fam, aes(x=factor(cc002_2_2_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of Your Spouse's Alive Younger Brothers") + ylab("Frequency")

vari <- CHARLS_w2_oth_fam$cc002_3_2_
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = CHARLS_w2_oth_fam$cc002_3_2_, missing_values = NA)
ggplot(CHARLS_w2_oth_fam, aes(x=factor(cc002_3_2_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of Your Spouse's Alive Older Sisters") + ylab("Frequency")

vari <- CHARLS_w2_oth_fam$cc002_4_2_
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = CHARLS_w2_oth_fam$cc002_4_2_, missing_values = NA)
ggplot(CHARLS_w2_oth_fam, aes(x=factor(cc002_4_2_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Number of Your Spouse's Alive Younger Sisters") + ylab("Frequency")

vari <- CHARLS_w2_oth_fam$ca001_1_
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = CHARLS_w2_oth_fam$ca001_1_, missing_values = NA)
ggplot(CHARLS_w2_oth_fam, aes(x=factor(ca001_1_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Is Your Father Living") + ylab("Frequency")

vari <- CHARLS_w2_oth_fam$ca001_2_
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = CHARLS_w2_oth_fam$ca001_2_, missing_values = NA)
ggplot(CHARLS_w2_oth_fam, aes(x=factor(ca001_2_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Is Your Mother Living") + ylab("Frequency")

vari <- CHARLS_w2_oth_fam$ca001_3_
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = CHARLS_w2_oth_fam$ca001_3_, missing_values = NA)
ggplot(CHARLS_w2_oth_fam, aes(x=factor(ca001_3_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Is Your Father-in-law Living") + ylab("Frequency")

vari <- CHARLS_w2_oth_fam$ca001_4_
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = CHARLS_w2_oth_fam$ca001_4_, missing_values = NA)
ggplot(CHARLS_w2_oth_fam, aes(x=factor(ca001_4_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Is Your Mother-in-law Living") + ylab("Frequency")

## A lot of NAs in ca001_3_, ca001_4_, cc002_1_2_, cc002_2_2_, cc002_3_2_, cc002_4_2_ - take it into account in the algorithm
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any of cc00 > 0 or any of caa00 = 1 then 1`
* `if all of cc00 =0 and all fo caa00 =2 then 0`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
CHARLS_ds_w2 <- tibble(id=CHARLS_w2_oth_fam$id)

CHARLS_w2_oth_fam$cc002_1_1_ <- car::recode(as.vector(CHARLS_w2_oth_fam$cc002_1_1_), "NA='-999'")
CHARLS_w2_oth_fam$cc002_2_1_ <- car::recode(as.vector(CHARLS_w2_oth_fam$cc002_2_1_), "NA='-999'")
CHARLS_w2_oth_fam$cc002_3_1_ <- car::recode(as.vector(CHARLS_w2_oth_fam$cc002_3_1_), "NA='-999'")
CHARLS_w2_oth_fam$cc002_4_1_ <- car::recode(as.vector(CHARLS_w2_oth_fam$cc002_4_1_), "NA='-999'")
CHARLS_w2_oth_fam$cc002_1_2_ <- car::recode(as.vector(CHARLS_w2_oth_fam$cc002_1_2_), "NA='-999'")
CHARLS_w2_oth_fam$cc002_2_2_ <- car::recode(as.vector(CHARLS_w2_oth_fam$cc002_2_2_), "NA='-999'")
CHARLS_w2_oth_fam$cc002_3_2_ <- car::recode(as.vector(CHARLS_w2_oth_fam$cc002_3_2_), "NA='-999'")
CHARLS_w2_oth_fam$cc002_4_2_ <- car::recode(as.vector(CHARLS_w2_oth_fam$cc002_4_2_), "NA='-999'")
CHARLS_w2_oth_fam$ca001_1_ <- car::recode(as.vector(CHARLS_w2_oth_fam$ca001_1_), "NA='-999'")
CHARLS_w2_oth_fam$ca001_2_ <- car::recode(as.vector(CHARLS_w2_oth_fam$ca001_2_), "NA='-999'")
CHARLS_w2_oth_fam$ca001_3_ <- car::recode(as.vector(CHARLS_w2_oth_fam$ca001_3_), "NA='-999'")
CHARLS_w2_oth_fam$ca001_4_ <- car::recode(as.vector(CHARLS_w2_oth_fam$ca001_4_), "NA='-999'")

CHARLS_ds_w2$oth_fam <- c(NA)

for(i in 1:dim(CHARLS_w2_oth_fam)[1]){
  if( CHARLS_w2_oth_fam$cc002_1_1_[i] >0 | CHARLS_w2_oth_fam$cc002_2_1_[i] >0 | 
      CHARLS_w2_oth_fam$cc002_3_1_[i] >0 | CHARLS_w2_oth_fam$cc002_4_1_[i] >0 |
      CHARLS_w2_oth_fam$cc002_1_2_[i] >0 | CHARLS_w2_oth_fam$cc002_2_2_[i] >0 | 
      CHARLS_w2_oth_fam$cc002_3_2_[i] >0 | CHARLS_w2_oth_fam$cc002_4_2_[i] >0 |
      CHARLS_w2_oth_fam$ca001_1_[i] == 1 | CHARLS_w2_oth_fam$ca001_2_[i] == 1 | 
      CHARLS_w2_oth_fam$ca001_3_[i] == 1 | CHARLS_w2_oth_fam$ca001_4_[i] == 1 ){
    CHARLS_ds_w2$oth_fam[i] = 1 }
  else if( CHARLS_w2_oth_fam$cc002_1_1_[i] == 0 & CHARLS_w2_oth_fam$cc002_2_1_[i] == 0 &
           CHARLS_w2_oth_fam$cc002_3_1_[i] == 0 & CHARLS_w2_oth_fam$cc002_4_1_[i] == 0 &
           CHARLS_w2_oth_fam$cc002_1_2_[i] %in% c(0,-999) & CHARLS_w2_oth_fam$cc002_2_2_[i] %in% c(0,-999) &
           CHARLS_w2_oth_fam$cc002_3_2_[i] %in% c(0,-999) & CHARLS_w2_oth_fam$cc002_4_2_[i] %in% c(0,-999) &
           CHARLS_w2_oth_fam$ca001_1_[i] == 2 & CHARLS_w2_oth_fam$ca001_2_[i] == 2 & 
           CHARLS_w2_oth_fam$ca001_3_[i] %in% c(2,-999) & CHARLS_w2_oth_fam$ca001_4_[i] %in% c(2,-999) ){
    CHARLS_ds_w2$oth_fam[i] = 0 }
}
  
CHARLS_ds_w2$oth_fam <- car::recode(as.vector(CHARLS_ds_w2$oth_fam), "NA='999'")
CHARLS_ds_w2$oth_fam <- labelled(CHARLS_ds_w2$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2}
vari <- CHARLS_ds_w2$oth_fam
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = CHARLS_ds_w2$oth_fam, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(CHARLS_ds_w2, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2}

```


```{r save, echo=FALSE}
oth_fam <- CHARLS_ds_w1
save(oth_fam, file = "../RData/w1/oth_fam.RData")
rm(oth_fam)

oth_fam <- CHARLS_ds_w2
save(oth_fam, file = "../RData/w2/oth_fam.RData")
rm(oth_fam)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```

