---
title: "Frequency of Vigorous Physical Activity"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/f_vig_paDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/f_vig_paDS.R')
```




# Data process

## Korea

### Wave 1 

#### Study-specific variable description

| **Name** | `w01C098` |`w01C096`|
|-|-|-|
| **Label** | `Number of times that exercise per a week` |`Whether or not regular exercise (more than a week 1th)`|
| **Table name** | `w01_main_e` | `w01_main_e` |
| **Categories:**| `continuous`|`1 = Yes`<br/>`5 = No`|
| **Missings:**| `NA` |  |
| **Description** |  |  |

```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w1','KLOSA.w01_main_e', variables=list('w01C098','w01C096'), missings = TRUE)
KLOSA_w1 <- opal.execute(o,'KLOSA_w1')
```

```{r local w1, echo=F}

vbl <- KLOSA_w1$w01C098
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "w01C098") 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(KLOSA_w1, aes(w01C098)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") 

vbl <- KLOSA_w1$w01C096
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "w01C096")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w1, aes(x=factor(w01C096))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") 

```

#### Harmonisation algorithm

To compute `f_vig_pa` from the study-specific variable `w01C098` it has to be recoded as follows:

* `1 into 1`
* `2,3 into 2`
* `4,5 into 3`
* `>5 into 4`
* `NA into 999`
* `w01C096 == 5 into 0`

**R script:**

```{r harmo w1}

KLOSA_ds_w1 <- tibble(id=KLOSA_w1$id)
KLOSA_ds_w1$f_vig_pa <- car::recode(KLOSA_w1$w01C098, "3 = 2;4 = 3;5 = 3; 6:hi = 4; NA = 999 ")
KLOSA_ds_w1$f_vig_pa[which(KLOSA_w1$w01C096==5)] <- 0

```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vbl <- KLOSA_ds_w1$f_vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w1, aes(x=factor(f_vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}

```





### Wave 2

#### Study-specific variable description

| **Name** | `w02C111` |`w02C108`|
|-|-|-|
| **Label** | `A time of exercise per a week (unit: a time/ a week)` |`Whether take regular exercise or not(more than one time in a week)`|
| **Table name** | `w02_main_e_spss` | `w02_main_e_spss` |
| **Categories:**| `continuous`|`1 = Yes`<br/>`5 = No`|
| **Missings:**| `-8 = refuse to answer` <br/> `NA` |  |
| **Description** |  |  |

```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w2','KLOSA.w02_main_e_spss', variables=list('w02C111','w02C108'), missings = TRUE)
KLOSA_w2 <- opal.execute(o,'KLOSA_w2')
```

```{r local w2, echo=F}

vbl <- KLOSA_w2$w02C111
vbl_miss <- c(-8)
kable(Continuous_summary(vbl, missing_values = vbl_miss)[3], caption = "w02C111") 
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(KLOSA_w2, aes(w02C111)) + geom_histogram(stat="count", fill="steelblue", data = . %>% filter(!vbl %in% vbl_miss)) + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w2$w02C108
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "w02C108")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2, aes(x=factor(w02C108))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") 

```

#### Harmonisation algorithm

To compute `f_vig_pa` from the study-specific variable `w02C111` it has to be recoded as follows:

* `1 into 1`
* `2,3 into 2`
* `4,5 into 3`
* `>5 into 4`
* `-8 into 997`
* `NA into 999`
* `w02C108 == 5 into 0`

**R script:**

```{r harmo w2}

KLOSA_ds_w2 <- tibble(id=KLOSA_w2$id)
KLOSA_ds_w2$f_vig_pa <- car::recode(KLOSA_w2$w02C111, "3 = 2;4 = 3;5 = 3;6:hi = 4;-8 = 997;NA = 999 ")
KLOSA_ds_w2$f_vig_pa[which(KLOSA_w2$w02C108==5)] <- 0

```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vbl <- KLOSA_ds_w2$f_vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w2, aes(x=factor(f_vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}

```







### Wave 3

#### Study-specific variable description

| **Name** | `w03C111` |`w03C108`|
|-|-|-|
| **Label** | `Number of times that exercise per a week (unit : inning/a week)` |`Whether or not regular exercise (more than a week 1th)`|
| **Table name** | `w03_main_e_spss_albert` |`w03_main_e_spss_albert` |
| **Categories:**| `continuous`|`1 = Yes`<br/>`5 = No`|
| **Missings:**| `NA` |  |
| **Description** |  |  |

```{r assign w3, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w3','KLOSA.w03_main_e_spss_albert', variables=list('w03C111','w03C108'), missings = TRUE)
KLOSA_w3 <- opal.execute(o,'KLOSA_w3')
# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_w3$id <- substr(KLOSA_w3$id,1,nchar(KLOSA_w3$id)-2)

```

```{r local w3, echo=F}

vbl <- KLOSA_w3$w03C111
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "w03C111") 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(KLOSA_w3, aes(w03C111)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w3$w03C108
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "w03C108")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w3, aes(x=factor(w03C108))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") 

```

#### Harmonisation algorithm

To compute `f_vig_pa` from the study-specific variable `w03C111` it has to be recoded as follows:

* `1 into 1`
* `2,3 into 2`
* `4,5 into 3`
* `>5 into 4`
* `NA into 999`
* `w03C108 == 5 into 0`

**R script:**

```{r harmo w3}

KLOSA_ds_w3 <- tibble(id=KLOSA_w3$id)
KLOSA_ds_w3$f_vig_pa <- car::recode(KLOSA_w3$w03C111, "3 = 2;4 = 3;5 = 3;6:hi = 4;NA = 999 ")
KLOSA_ds_w3$f_vig_pa[which(KLOSA_w3$w03C108==5)] <- 0

```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}
vbl <- KLOSA_ds_w3$f_vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w3, aes(x=factor(f_vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=F}

```






### Wave 4

#### Study-specific variable description

| **Name** | `w04C111` |`w04C108`|
|-|-|-|
| **Label** | `Number of times that exercise per a week (unit : inning/a week)` |`Whether or not regular exercise (more than a week 1th)`|
| **Table name** | `w04_main_e_spss` | `w04_main_e_spss` |
| **Categories:**| `continuous`|`1 = Yes`<br/>`5 = No`|
| **Missings:**| `NA` |  |
| **Description** |  |  |

```{r assign w4, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w4','KLOSA.w04_main_e_spss', variables=list('w04C111','w04C108'), missings = TRUE)
KLOSA_w4 <- opal.execute(o,'KLOSA_w4')
```

```{r local w4, echo=F}

vbl <- KLOSA_w4$w04C111
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "w04C111") 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(KLOSA_w4, aes(w04C111)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w4$w04C108
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "w04C108")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w4, aes(x=factor(w04C108))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") 

```

#### Harmonisation algorithm

To compute `f_vig_pa` from the study-specific variable `w04C111` it has to be recoded as follows:

* `1 into 1`
* `2,3 into 2`
* `4,5 into 3`
* `6,7 into 4`
* `NA into 999`
* `w04C108 == 5 into 0`

**R script:**

```{r harmo w4}

KLOSA_ds_w4 <- tibble(id=KLOSA_w4$id)
KLOSA_ds_w4$f_vig_pa <- car::recode(KLOSA_w4$w04C111, "3 = 2;4 = 3;5 = 3;6:hi = 4;NA = 999 ")
KLOSA_ds_w4$f_vig_pa[which(KLOSA_w4$w04C108==5)] <- 0

```

#### Statistical description of the new harmonised variable
```{r descript w4, echo=F}
vbl <- KLOSA_ds_w4$f_vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w4, aes(x=factor(f_vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w4, echo=F}

```






## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.



```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:5])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[16,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


klosa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"))

# Consider only harmonised waves
l.hds <- lapply(klosa.cw, function(wname) if(exists(paste0("KLOSA_ds_",wname[1]))){wname = list(get(paste0("KLOSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],sapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```





# Quality estimation


<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
