---
title: "Current smoker"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/current_smokingDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/current_smokingDS.R')
```



# Data process

## Korea

### Wave 1 

#### Study-specific variable description

| **Name** | `w01C104` |
|-|-|
| **Label** | `Present, whether or not smoking` |
| **Table name** | `w01_main_e` |
| **Categories:**| `1 = Yes` <br/> `5 = No` |
| **Missings:**|`-9 = Do not know` <br/> `NA` |
| **Description** |  |

   

```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w1','KLOSA.w01_main_e', variables=list('w01C104'), missings = TRUE)
KLOSA_w1 <- opal.execute(o,'KLOSA_w1')
```

```{r local w1, echo=F}
vbl <- KLOSA_w1$w01C104
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(KLOSA_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w1, aes(x=factor(w01C104))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `current_smoking` from the study-specific variable it has to be recoded as follows:

* `5 into 0` 
* `-9 into 998`
* `NA into 999`

**R script:**

```{r harmo w1}
KLOSA_ds_w1 <- tibble(id=KLOSA_w1$id)
KLOSA_ds_w1$current_smoking <- car::recode(KLOSA_w1$w01C104, "5 = 0;-9 = 998;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vbl <- KLOSA_ds_w1$current_smoking
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w1, aes(x=factor(current_smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
```




### Wave 2

#### Study-specific variable description

| **Name** | `w02C117` |
|-|-|
| **Label** | `Present, whether or not smoking` |
| **Table name** | `w02_main_e_spss` |
| **Categories:**| `1 = Yes` <br/> `5 = No` |
| **Missings:**|`NA` |
| **Description** |  |

   

```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w2','KLOSA.w02_main_e_spss', variables=list('w02C117'), missings = TRUE)
KLOSA_w2 <- opal.execute(o,'KLOSA_w2')
```

```{r local w2, echo=F}
vbl <- KLOSA_w2$w02C117
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(KLOSA_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2, aes(x=factor(w02C117))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `current_smoking` from the study-specific variable it has to be recoded as follows:

* `5 into 0` 
* `NA into 999`

**R script:**

```{r harmo w2}
KLOSA_ds_w2 <- tibble(id=KLOSA_w2$id)
KLOSA_ds_w2$current_smoking <- car::recode(KLOSA_w2$w02C117, "5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vbl <- KLOSA_ds_w2$current_smoking
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w2, aes(x=factor(current_smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
```




### Wave 3

#### Study-specific variable description

| **Name** | `w03C117` |
|-|-|
| **Label** | `Present, whether or not smoking` |
| **Table name** | `w03_main_e_spss_albert` |
| **Categories:**| `1 = Yes` <br/> `5 = No` |
| **Missings:**|`NA` |
| **Description** |  |

   

```{r assign w3, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w3','KLOSA.w03_main_e_spss_albert', variables=list('w03C117'), missings = TRUE)
KLOSA_w3 <- opal.execute(o,'KLOSA_w3')
# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_w3$id <- substr(KLOSA_w3$id,1,nchar(KLOSA_w3$id)-2)

```

```{r local w3, echo=F}
vbl <- KLOSA_w3$w03C117
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(KLOSA_w3)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w3, aes(x=factor(w03C117))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `current_smoking` from the study-specific variable it has to be recoded as follows:

* `5 into 0` 
* `NA into 999`

**R script:**

```{r harmo w3}
KLOSA_ds_w3 <- tibble(id=KLOSA_w3$id)
KLOSA_ds_w3$current_smoking <- car::recode(KLOSA_w3$w03C117, "5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}
vbl <- KLOSA_ds_w3$current_smoking
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w3, aes(x=factor(current_smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=F}
```




### Wave 4

#### Study-specific variable description

| **Name** | `w04C117` |
|-|-|
| **Label** | `Present, whether or not smoking` |
| **Table name** | `w04_main_e_spss` |
| **Categories:**| `1 = Yes` <br/> `5 = No` |
| **Missings:**| `NA` |
| **Description** |  |

   

```{r assign w4, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w4','KLOSA.w04_main_e_spss', variables=list('w04C117'), missings = TRUE)
KLOSA_w4 <- opal.execute(o,'KLOSA_w4')
```

```{r local w4, echo=F}
vbl <- KLOSA_w4$w04C117
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(KLOSA_w4)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w4, aes(x=factor(w04C117))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `current_smoking` from the study-specific variable it has to be recoded as follows:

* `5 into 0` 
* `NA into 999`

**R script:**

```{r harmo w4}
KLOSA_ds_w4 <- tibble(id=KLOSA_w4$id)
KLOSA_ds_w4$current_smoking <- car::recode(KLOSA_w4$w04C117, "5 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w4, echo=F}
vbl <- KLOSA_ds_w4$current_smoking
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w4, aes(x=factor(current_smoking))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w4, echo=F}
```




```{r final, echo=F}

l.hds <- list(w1 = KLOSA_ds_w1, w2 = KLOSA_ds_w2, w3 = KLOSA_ds_w3, w4 = KLOSA_ds_w4)


for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("KLOSA_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

```




## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.

**R script:**

```{r summ}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",names(l.hds))
kable(t.hds)


dbb <- get(paste0("KLOSA_m_ds_",names(l.hds)[1]))[,c("id","current_smoking")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("KLOSA_m_ds_",names(l.hds)[ind]))[,c("id","current_smoking")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", names(l.hds))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb)


```


# Quality estimation

<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  current_smoking <- l.hds[[index]]
  save(current_smoking, file = paste0(datafolder,names(l.hds)[index],"/current_smoking.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





