---
title: "Alcohol drinking"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/alcoholDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/alcoholDS.R')
```



# Data process



## Korea


### Wave 1


#### Study-specific variable description

| **Name** | `w01C109` |`w01C116`|`w01C118`|`w01C120`|`w01C122`|`w01C124`|`w01C110`|
|-|-|-|-|-|-|-|-|
| **Label** | `At ordinary times, whether or not drinking`|`Drinking frequency (soju)`|`Drinking frequency (beer)`|`Drinking frequency (unstrained rice wine)`|`Drinking frequency (whisky or liquor)`|`Drinking frequency (wine)`|`Have you never had alcoholic beverages due to some reasons (e.g., religious, health‐related, etc), or you used to have some drinks in the past?`|
| **Table name**  | `w01_main_e`| `w01_main_e`| `w01_main_e`| `w01_main_e`| `w01_main_e`| `w01_main_e`| `w01_main_e`|
| **Categories** | `1 = Yes`<br/>`5 = no` |`1 = None or less than once a month`<br/>`2 = Once a month`<br>`3 = 2-3 times a month`<br/>`4 = Once a week`<br/>`5 = 2-3 times a week`<br/>`6 = 4-6 times a week`<br/>`7 = Once a day`<br/>`8 = More than twice a day`|`1 = None or less than once a month`<br/>`2 = Once a month`<br>`3 = 2-3 times a month`<br/>`4 = Once a week`<br/>`5 = 2-3 times a week`<br/>`6 = 4-6 times a week`<br/>`7 = Once a day`<br/>`8 = More than twice a day`|`1 = None or less than once a month`<br/>`2 = Once a month`<br>`3 = 2-3 times a month`<br/>`4 = Once a week`<br/>`5 = 2-3 times a week`<br/>`6 = 4-6 times a week`<br/>`7 = Once a day`<br/>`8 = More than twice a day`|`1 = None or less than once a month`<br/>`2 = Once a month`<br>`3 = 2-3 times a month`<br/>`4 = Once a week`<br/>`5 = 2-3 times a week`<br/>`6 = 4-6 times a week`<br/>`7 = Once a day`<br/>`8 = More than twice a day`|`1 = None or less than once a month`<br/>`2 = Once a month`<br>`3 = 2-3 times a month`<br/>`4 = Once a week`<br/>`5 = 2-3 times a week`<br/>`6 = 4-6 times a week`<br/>`7 = Once a day`<br/>`8 = More than twice a day`| `1 = No, I never had a drink`<br/>`5 = Yes, I used to drink` |
| **Missings** |  | `-9 = Do not know`<br/>`NA` | `-9 = Do not know`<br/>`NA` | `-9 = Do not know`<br/>`NA` | `-9 = Do not know`<br/>`NA` | `-9 = Do not know`<br/>`NA` |`NA` |
| **Description** |  |  |  |  |  |  |  |


```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w1','KLOSA.w01_main_e',variables=list('w01C109','w01C116','w01C118','w01C120','w01C122','w01C124','w01C110'), missings = T)
KLOSA_w1 <- opal.execute(o,'KLOSA_w1')

```

```{r local w1, echo=F}

vbl <- KLOSA_w1$w01C109
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w01C109')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w1, aes(x=factor(w01C109))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl_miss <- c(-9)

vbl <- KLOSA_w1$w01C116
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = 'w01C116')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(KLOSA_w1, aes(x=factor(w01C116))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w1$w01C118
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = 'w01C118')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(KLOSA_w1, aes(x=factor(w01C118))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w1$w01C120
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = 'w01C120')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(KLOSA_w1, aes(x=factor(w01C120))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w1$w01C122
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = 'w01C122')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(KLOSA_w1, aes(x=factor(w01C122))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w1$w01C124
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = 'w01C124')
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(KLOSA_w1, aes(x=factor(w01C124))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w1$w01C110
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w01C110')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w1, aes(x=factor(w01C110))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable `w01C109` it has to be recoded as follows:

* `change 5 into 0`
* `keep up 1 into 1`

To compute `freq_oh` from the study-specific variable it has to be recoded as follows:

* `compute maximum(w01C116,w01C118,w01C120,w01C122,w01C124). Then transform as follows:`
* `1 into 0`
* `2,3,4 into 1`
* `5,6,7,8 into 2`
* `-9 into 998`
* `NA into 999`

To compute `past_oh` from the study-specific variable `w01C110` it has to be recoded as follows:

* `1 into 0`
* `5 into 1`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
KLOSA_ds_w1 <- tibble(id=KLOSA_w1$id)
KLOSA_ds_w1$current_oh <- car::recode(KLOSA_w1$w01C109,"5=0")
KLOSA_w1$maxfreq <- pmax(KLOSA_w1$w01C116,KLOSA_w1$w01C118,KLOSA_w1$w01C120,KLOSA_w1$w01C122,KLOSA_w1$w01C124,na.rm=T)
KLOSA_ds_w1$freq_oh <- car::recode(KLOSA_w1$maxfreq, "1 = 0; c(2,3,4) = 1; c(5,6,7,8) = 2; -9 = 998; NA = 999")
KLOSA_ds_w1$past_oh <- car::recode(KLOSA_w1$w01C110,"5=1; 1=0; NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- KLOSA_ds_w1$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w1, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- KLOSA_ds_w1$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w1, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

vbl <- KLOSA_ds_w1$past_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_past)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w1, aes(x=factor(past_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_past) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}

```



### Wave 2

#### Study-specific variable description


| **Name** | `w02C122` |`w02C126`|`w02C128`|`w02C130`|`w02C132`|`w02C134`|`w02C123`|
|-|-|-|-|-|-|-|-|
| **Label** | `Usually, whether drink some alcohol or not`|`Average drinking frequency (Korean distilled spirits: Soju) per a month`|`Average drinking frequency (Beer) per a month`|`Average drinking frequency Makgeolli(unstrained rice wine) per a month`|`Average drinking frequency (Whisky or Liquor) per a month`|`Average drinking frequency (Wine) per a month`|`The time of quit drinking (yyyy/mm)`|
| **Table name**  | `w02_main_e_spss`| `w02_main_e_spss`| `w02_main_e_spss`| `w02_main_e_spss`| `w02_main_e_spss`| `w02_main_e_spss`|`w02_main_e_spss`|
| **Categories** | `1 = yes; 5 = no` |`1 = None or less than once a month`<br/>`2 = Once a month`<br>`3 = 2-3 times a month`<br/>`4 = Once a week`<br/>`5 = 2-3 times a week`<br/>`6 = 4-6 times a week`<br/>`7 = Once a day`<br/>`8 = More than twice a day`|`1 = None or less than once a month`<br/>`2 = Once a month`<br>`3 = 2-3 times a month`<br/>`4 = Once a week`<br/>`5 = 2-3 times a week`<br/>`6 = 4-6 times a week`<br/>`7 = Once a day`<br/>`8 = More than twice a day`|`1 = None or less than once a month`<br/>`2 = Once a month`<br>`3 = 2-3 times a month`<br/>`4 = Once a week`<br/>`5 = 2-3 times a week`<br/>`6 = 4-6 times a week`<br/>`7 = Once a day`<br/>`8 = More than twice a day`|`1 = None or less than once a month`<br/>`2 = Once a month`<br>`3 = 2-3 times a month`<br/>`4 = Once a week`<br/>`5 = 2-3 times a week`<br/>`6 = 4-6 times a week`<br/>`7 = Once a day`<br/>`8 = More than twice a day`|`1 = None or less than once a month`<br/>`2 = Once a month`<br>`3 = 2-3 times a month`<br/>`4 = Once a week`<br/>`5 = 2-3 times a week`<br/>`6 = 4-6 times a week`<br/>`7 = Once a day`<br/>`8 = More than twice a day`|`continuous`|
| **Missings** | `NA` | `NA` | `NA` | `NA` | `NA` | `NA` |`-9 = Don't know`<br/>`-8 = Refuse to answer`<br/>`NA`|
| **Description** |  |  |  |  |  |  |  |

```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w2','KLOSA.w02_main_e_spss',variables=list('w02C122','w02C126','w02C128','w02C130','w02C132','w02C134','w02C123'), missings = T)
KLOSA_w2 <- opal.execute(o,'KLOSA_w2')

```

```{r local w2, echo=F}

vbl <- KLOSA_w2$w02C122
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w02C122')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2, aes(x=factor(w02C122))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w2$w02C126
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w02C126')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2, aes(x=factor(w02C126))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w2$w02C128
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w02C128')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2, aes(x=factor(w02C128))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w2$w02C130
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w02C130')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2, aes(x=factor(w02C130))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w2$w02C132
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w02C132')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2, aes(x=factor(w02C132))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w2$w02C134
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w02C134')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2, aes(x=factor(w02C134))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w2$w02C123
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w02C123')

```


#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable `w02C122` it has to be recoded as follows:

* `change 5 into 0`
* `keep up 1 into 1`

To compute `freq_oh` from the study-specific variable it has to be recoded as follows:

* `compute maximum(w02C126,w02C128,w02C130,w02C132,w02C134). Then transform as follows:`
* `1 into 0`
* `2,3,4 into 1`
* `5,6,7,8 into 2`
* `NA into 999`

To compute `past_oh` from the study-specific variable `w02C123` it has to be recoded as follows:

* `NA into 0 No past drinker`
* `not NA into 1 past drinker`

**R script:**

```{r harmo w2}

# Categorical variable harmonization
KLOSA_ds_w2 <- tibble(id=KLOSA_w2$id)
KLOSA_ds_w2$current_oh <- car::recode(KLOSA_w2$w02C122,"5=0; NA=999")
KLOSA_w2$maxfreq <- pmax(KLOSA_w2$w02C126,KLOSA_w2$w02C128,KLOSA_w2$w02C130,KLOSA_w2$w02C132,KLOSA_w2$w02C134,na.rm=T)
KLOSA_ds_w2$freq_oh <- car::recode(KLOSA_w2$maxfreq, "1 = 0; c(2,3,4) = 1; c(5,6,7,8) = 2; NA = 999")
KLOSA_ds_w2$past_oh <- rep(0,length(KLOSA_w2$id))
KLOSA_ds_w2$past_oh[which(!is.na(KLOSA_w2$w02C123))] <- 1

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- KLOSA_ds_w2$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w2, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- KLOSA_ds_w2$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w2, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

vbl <- KLOSA_ds_w2$past_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_past)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w2, aes(x=factor(past_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_past) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w2, echo=F}

```



### Wave 3


#### Study-specific variable description

| **Name** | `w03C122` |`w03C126`|`w03C128`|`w03C130`|`w03C132`|`w03C134`|`w03C123`|
|-|-|-|-|-|-|-|-|
| **Label** | `At ordinary times, whether or not drinking`|`Drinking frequency (soju)`|`Drinking frequency (beer)`|`Drinking frequency (unstrained rice wine)`|`Drinking frequency (whisky or liquor)`|`Drinking frequency (wine)`|`The time when do not drink (yyyy/mm)`|
| **Table name**  | `w03_main_e_spss_albert`| `w03_main_e_spss_albert`| `w03_main_e_spss_albert`| `w03_main_e_spss_albert`| `w03_main_e_spss_albert`| `w03_main_e_spss_albert`| `w03_main_e_spss_albert`|
| **Categories** | `1 = yes; 5 = no` |`1 = None or less than once a month`<br/>`2 = Once a month`<br>`3 = 2-3 times a month`<br/>`4 = Once a week`<br/>`5 = 2-3 times a week`<br/>`6 = 4-6 times a week`<br/>`7 = Once a day`<br/>`8 = More than twice a day`|`1 = None or less than once a month`<br/>`2 = Once a month`<br>`3 = 2-3 times a month`<br/>`4 = Once a week`<br/>`5 = 2-3 times a week`<br/>`6 = 4-6 times a week`<br/>`7 = Once a day`<br/>`8 = More than twice a day`|`1 = None or less than once a month`<br/>`2 = Once a month`<br>`3 = 2-3 times a month`<br/>`4 = Once a week`<br/>`5 = 2-3 times a week`<br/>`6 = 4-6 times a week`<br/>`7 = Once a day`<br/>`8 = More than twice a day`|`1 = None or less than once a month`<br/>`2 = Once a month`<br>`3 = 2-3 times a month`<br/>`4 = Once a week`<br/>`5 = 2-3 times a week`<br/>`6 = 4-6 times a week`<br/>`7 = Once a day`<br/>`8 = More than twice a day`|`1 = None or less than once a month`<br/>`2 = Once a month`<br>`3 = 2-3 times a month`<br/>`4 = Once a week`<br/>`5 = 2-3 times a week`<br/>`6 = 4-6 times a week`<br/>`7 = Once a day`<br/>`8 = More than twice a day`|`continuous`|
| **Missings** | `NA` | `NA` | `NA` | `NA` | `NA` | `NA` |`-9 = Don't know`<br/>`-8 = Refuse to answer`<br/>`NA`|
| **Description** |  |  |  |  |  |  |  |

```{r assign w3, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w3','KLOSA.w03_main_e_spss_albert',variables=list('w03C122','w03C126','w03C128','w03C130','w03C132','w03C134','w03C123'), missings = T)
KLOSA_w3 <- opal.execute(o,'KLOSA_w3')
# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_w3$id <- substr(KLOSA_w3$id,1,nchar(KLOSA_w3$id)-2)

```

```{r local w3, echo=F}

vbl <- KLOSA_w3$w03C122
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w03C122')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w3, aes(x=factor(w03C122))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w3$w03C126
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w03C126')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w3, aes(x=factor(w03C126))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w3$w03C128
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w03C128')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w3, aes(x=factor(w03C128))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w3$w03C130
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w03C130')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w3, aes(x=factor(w03C130))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w3$w03C132
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w03C132')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w3, aes(x=factor(w03C132))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w3$w03C134
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w03C134')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w3, aes(x=factor(w03C134))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w3$w03C123
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w03C123')

```


#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable `w03C122` it has to be recoded as follows:

* `change 5 into 0`
* `keep up 1 into 1`

To compute `freq_oh` from the study-specific variable it has to be recoded as follows:

* `compute maximum(w03C126,w03C128,w03C130,w03C132,w03C134). Then transform as follows:`
* `1 into 0`
* `2,3,4 into 1`
* `5,6,7,8 into 2`
* `NA into 999`

To compute `past_oh` from the study-specific variable `w03C123` it has to be recoded as follows:

* `NA into 0 No past drinker`
* `not NA into 1 past drinker`

**R script:**

```{r harmo w3}

# Categorical variable harmonization
KLOSA_ds_w3 <- tibble(id=KLOSA_w3$id)
KLOSA_ds_w3$current_oh <- car::recode(KLOSA_w3$w03C122,"5=0; NA=999")
KLOSA_w3$maxfreq <- pmax(KLOSA_w3$w03C126,KLOSA_w3$w03C128,KLOSA_w3$w03C130,KLOSA_w3$w03C132,KLOSA_w3$w03C134,na.rm=T)
KLOSA_ds_w3$freq_oh <- car::recode(KLOSA_w3$maxfreq, "1 = 0; c(2,3,4) = 1; c(5,6,7,8) = 2; NA = 999")
KLOSA_ds_w3$past_oh <- rep(0,length(KLOSA_w3$id))
KLOSA_ds_w3$past_oh[which(!is.na(KLOSA_w3$w03C123))] <- 1

```


#### Statistics of the new harmonized variable

```{r descript w3, echo=F}

vbl <- KLOSA_ds_w3$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w3, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- KLOSA_ds_w3$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w3, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

vbl <- KLOSA_ds_w3$past_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_past)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w3, aes(x=factor(past_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_past) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w3, echo=F, results='asis'}

```



### Wave 4


#### Study-specific variable description

| **Name** | `w04C122` |`w04C126`|`w04C128`|`w04C130`|`w04C132`|`w04C134`|`w04C123`|
|-|-|-|-|-|-|-|-|
| **Label** | `At ordinary times, whether or not drinking`|`Drinking frequency (soju)`|`Drinking frequency (beer)`|`Drinking frequency (unstrained rice wine)`|`Drinking frequency (whisky or liquor)`|`Drinking frequency (wine)`|`The time when do not drink (yyyy/mm)`|
| **Table name**  | `w04_main_e_spss`|`w04_main_e_spss`|`w04_main_e_spss`|`w04_main_e_spss`|`w04_main_e_spss`|`w04_main_e_spss`|`w04_main_e_spss`|
| **Categories** | `1 = yes; 5 = no` |`1 = None or less than once a month`<br/>`2 = Once a month`<br>`3 = 2-3 times a month`<br/>`4 = Once a week`<br/>`5 = 2-3 times a week`<br/>`6 = 4-6 times a week`<br/>`7 = Once a day`<br/>`8 = More than twice a day`|`1 = None or less than once a month`<br/>`2 = Once a month`<br>`3 = 2-3 times a month`<br/>`4 = Once a week`<br/>`5 = 2-3 times a week`<br/>`6 = 4-6 times a week`<br/>`7 = Once a day`<br/>`8 = More than twice a day`|`1 = None or less than once a month`<br/>`2 = Once a month`<br>`3 = 2-3 times a month`<br/>`4 = Once a week`<br/>`5 = 2-3 times a week`<br/>`6 = 4-6 times a week`<br/>`7 = Once a day`<br/>`8 = More than twice a day`|`1 = None or less than once a month`<br/>`2 = Once a month`<br>`3 = 2-3 times a month`<br/>`4 = Once a week`<br/>`5 = 2-3 times a week`<br/>`6 = 4-6 times a week`<br/>`7 = Once a day`<br/>`8 = More than twice a day`|`1 = None or less than once a month`<br/>`2 = Once a month`<br>`3 = 2-3 times a month`<br/>`4 = Once a week`<br/>`5 = 2-3 times a week`<br/>`6 = 4-6 times a week`<br/>`7 = Once a day`<br/>`8 = More than twice a day`|`continuous`|
| **Missings** | `NA` | `NA` | `NA` | `NA` | `NA` | `NA` |`-9 = Don't know`<br/>`-8 = Refuse to answer`<br/>`NA`|
| **Description** |  |  |  |  |  |  |  |

```{r assign w4, echo=F}

opal.assign.table.tibble(o, 'KLOSA_w4','KLOSA.w04_main_e_spss',variables=list('w04C122','w04C126','w04C128','w04C130','w04C132','w04C134','w04C123'), missings = T)
KLOSA_w4 <- opal.execute(o,'KLOSA_w4')

```

```{r local w4, echo=F}

vbl <- KLOSA_w4$w04C122
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w04C122')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w4, aes(x=factor(w04C122))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w4$w04C126
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w04C126')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w4, aes(x=factor(w04C126))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w4$w04C128
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w04C128')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w4, aes(x=factor(w04C128))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w4$w04C130
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w04C130')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w4, aes(x=factor(w04C130))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w4$w04C132
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w04C132')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w4, aes(x=factor(w04C132))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w4$w04C134
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w04C134')
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w4, aes(x=factor(w04C134))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- KLOSA_w4$w04C123
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = 'w04C123')

```


#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable `w03C122` it has to be recoded as follows:

* `change 5 into 0`
* `keep up 1 into 1`

To compute `freq_oh` from the study-specific variable it has to be recoded as follows:

* `compute maximum(w04C126,w04C128,w04C130,w04C132,w04C134). Then transform as follows:`
* `1 into 0`
* `2,3,4 into 1`
* `5,6,7,8 into 2`
* `NA into 999`

To compute `past_oh` from the study-specific variable `w04C123` it has to be recoded as follows:

* `NA into 0 No past drinker`
* `not NA into 1 past drinker`

**R script:**

```{r harmo w4}

# Categorical variable harmonization
KLOSA_ds_w4 <- tibble(id=KLOSA_w4$id)
KLOSA_ds_w4$current_oh <- car::recode(KLOSA_w4$w04C122,"5=0; NA=999")
KLOSA_w4$maxfreq <- pmax(KLOSA_w4$w04C126,KLOSA_w4$w04C128,KLOSA_w4$w04C130,KLOSA_w4$w04C132,KLOSA_w4$w04C134,na.rm=T)
KLOSA_ds_w4$freq_oh <- car::recode(KLOSA_w4$maxfreq, "1 = 0; c(2,3,4) = 1; c(5,6,7,8) = 2; NA = 999")
KLOSA_ds_w4$past_oh <- rep(0,length(KLOSA_w4$id))
KLOSA_ds_w4$past_oh[which(!is.na(KLOSA_w4$w04C123))] <- 1

```


#### Statistics of the new harmonized variable

```{r descript w4, echo=F}

vbl <- KLOSA_ds_w4$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w4, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- KLOSA_ds_w4$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w4, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

vbl <- KLOSA_ds_w4$past_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_past)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(KLOSA_ds_w4, aes(x=factor(past_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_past) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w4, echo=F, results='asis'}

```



```{r final, echo=F}

l.hds <- list(w1 = KLOSA_ds_w1, w2 = KLOSA_ds_w2, w3 = KLOSA_ds_w3, w4 = KLOSA_ds_w4)


for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label_curr # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  label(l.hds[[name]][[3]]) <- label(aux_object[[3]]) <- ds_label_freq # Text value assigned at the DS description, at the top
  l.hds[[name]][[3]] <- labelled(l.hds[[name]][[3]], labels = freq_label)
  aux_object[[3]] <- car::recode(aux_object[[3]], "miss_values_vector=NA")
  aux_object[[3]] <- labelled(aux_object[[3]], labels = freq_label[1:3])
  label(l.hds[[name]][[4]]) <- label(aux_object[[4]]) <- ds_label_past # Text value assigned at the DS description, at the top
  l.hds[[name]][[4]] <- labelled(l.hds[[name]][[4]], labels = cat_label)
  aux_object[[4]] <- car::recode(aux_object[[4]], "miss_values_vector=NA")
  aux_object[[4]] <- labelled(aux_object[[4]], labels = cat_label[1:2])
  m_name <- paste0("KLOSA_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

```




## Summary of descriptive statistics of the harmonised variable `current_oh` accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.

**R script:**

```{r summ current}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",names(l.hds))
kable(t.hds)


dbb <- get(paste0("KLOSA_m_ds_",names(l.hds)[1]))[,c("id","current_oh")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("KLOSA_m_ds_",names(l.hds)[ind]))[,c("id","current_oh")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", names(l.hds))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb)


```




## Summary of descriptive statistics of the harmonised variable `freq_oh` accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.

**R script:**

```{r summ freq}

t.hds <- frq(l.hds[[1]][3])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][3])[[1]][,4] 
}
t.hds[14,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",names(l.hds))
kable(t.hds)


dbb <- get(paste0("KLOSA_m_ds_",names(l.hds)[1]))[,c("id","freq_oh")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("KLOSA_m_ds_",names(l.hds)[ind]))[,c("id","freq_oh")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", names(l.hds))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb)


```





## Summary of descriptive statistics of the harmonised variable `past_oh` accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.

**R script:**

```{r summ past}

t.hds <- frq(l.hds[[1]][4])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][4])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",names(l.hds))
kable(t.hds)


dbb <- get(paste0("KLOSA_m_ds_",names(l.hds)[1]))[,c("id","past_oh")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("KLOSA_m_ds_",names(l.hds)[ind]))[,c("id","past_oh")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", names(l.hds))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb)


```





# Quality estimation

* To get the harmonized variable `past_oh`, the missings of the variables `w02C123`, `w03C123`, `w04C123` in the waves 2, 3 and 4 are codified as non current drinkers, since there is a jump in the corresponding question according to which only past drinkers and currently no drinkers answer it. Nevertheless, an individual which is past drinker and currently drinker also is missing for those variables. It also could happen that an individual should answer the question (it is not skipped by the jump) but is missing for another reason.


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  alcohol <- l.hds[[index]]
  save(alcohol, file = paste0(datafolder,names(l.hds)[index],"/alcohol.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





