---
title: "Cancer"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/cancerDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/cancerDS.R')
```


# Data process



## Mexico


### Wave 1


#### Study-specific variable description

| **Name** | `c12` |`c18`|`ybirth`|
|-|-|-|-|
| **Label** | `Cancer or tumor`|`Year of cancer`|`year of birth`|
| **Table name**  | `MHAS-2001`|`MHAS-2001`|`ybirth`|
| **Categories** | `1 = Yes`<br/>`2 = No` |`continuous`|`continuous`|
| **Missings** | `8 = Doesn't answer`<br/>`9 = Doesn't know`<br/>`NA` | `8888 = Doesn't answer`<br/>`9999 = Doesn't know`<br/>`NA` |  |
| **Description** |  |  |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'MHAS_w1','Mexican Health Aging Study.MHAS-2001',variables=list('c12','c18'), missings = T)
MHAS_w1 <- opal.execute(o,'MHAS_w1')
load(paste0(datafolder,"w1/ybirth.RData"))
MHAS_w1 <- left_join(MHAS_w1,ybirth, by="id")
rm(ybirth)

```

```{r local w1, echo=F}

vbl <- MHAS_w1$c12
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = names(MHAS_w1)[2])
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(MHAS_w1, aes(x=factor(c12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w1$c18
vbl_miss <- c(8888,9999)
kable(Continuous_summary(var = vbl, missing_values = c(8888,9999))[3], caption = names(MHAS_w1)[3])
pander(Continuous_summary(vbl, missing_values = c(8888,9999))$summary, caption = "Summary")
ggplot(MHAS_w1 %>% filter(!vbl %in% vbl_miss), aes(c18)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w1$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(MHAS_w1)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(MHAS_w1 %>% filter(!vbl %in% miss_values_vector), aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cancer` from the study-specific variable it has to be recoded as follows:

* `change 2 into 0`
* `keep up 1 into 1`
* `change 8 into 995`
* `change 9 into 998`
* `NA into 999`

To compute `cancer_age` from the study-specific variable it has to be recoded as follows:

* `if cancer == 1, cancer_age = c18 - ybirth`
* `if cancer == 0, cancer_age = 996`
* `change 8888 into 995`
* `change 9999 into 998`
* `otherwise into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
MHAS_ds_w1 <- tibble(id=MHAS_w1$id)
MHAS_ds_w1$cancer <- car::recode(MHAS_w1$c12, "2=0; 8=995; 9=998; NA=999")

# Continuous variable harmonization
MHAS_ds_w1$cancer_age <- rep(999,length(MHAS_w1$id))
MHAS_ds_w1$cancer_age[which(MHAS_ds_w1$cancer==0)] <- 996
MHAS_ds_w1$cancer_age[which(MHAS_ds_w1$cancer==1 & !MHAS_w1$c18 %in% c(8888,9999))] <- MHAS_w1$c18[which(MHAS_ds_w1$cancer==1 & !MHAS_w1$c18 %in% c(8888,9999))] - MHAS_w1$ybirth[which(MHAS_ds_w1$cancer==1 & !MHAS_w1$c18 %in% c(8888,9999))]
MHAS_ds_w1$cancer_age[which(MHAS_ds_w1$cancer==1 & MHAS_w1$c18 == 8888)] <- 995
MHAS_ds_w1$cancer_age[which(MHAS_ds_w1$cancer==1 & MHAS_w1$c18 == 9999)] <- 998
MHAS_ds_w1$cancer_age <- car::recode(MHAS_ds_w1$cancer_age,"NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- MHAS_ds_w1$cancer
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w1, aes(x=factor(cancer))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- MHAS_ds_w1$cancer_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(MHAS_ds_w1 %>% filter(!vbl %in% miss_values_vector), aes(cancer_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}

AfterH <- table(MHAS_ds_w1$cancer)
BeforeH <- table(MHAS_w1$c12, useNA = "ifany")[c(2,1,3,4,5)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","8->995","9->998","NA->999")
kable(C)

```



### Wave 2

#### Study-specific variable description

| **Name** | `c12` |`c18`|`ybirth`|
|-|-|-|-|-|
| **Label** | `Doctor ever say you have cancer`|`When was most recent cancer diagnosed`|`year of birth`|
| **Table name**  | `MHAS_2003`|`age`|`ybirth`|
| **Categories** | `1 = Yes`<br/>`2 = No` |`continuous`|`continuous`|
| **Missings** |`9 = Doesn't know` | `9999 = Doesn't know`<br/>`NA`  | `998 = Do not know`<br/>`999 = Missing` |
| **Description** |  |  |  |  |


The label of `c12` is probably uncomplete, since the questionnaire tells:

The interviewer must always be aware that various questions of this section are worded to be adequate depending on the type of interview being given (tracking or new person). In other words, if this is a tracking interview, the interviewer must read:

`During the past two years have you seen a doctor or personal physician that said you have ...`

When interviewing a new person, the interview must ask in the following manner:

`Have you ever seen a doctor or personal physician that said you have ...`

```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'MHAS_w2','Mexican Health Aging Study.MHAS_2003',variables=list('c12','c18'), missings = T)
MHAS_w2 <- opal.execute(o,'MHAS_w2')
load(paste0(datafolder,"w2/ybirth.RData"))
MHAS_w2 <- left_join(MHAS_w2,ybirth, by="id")
rm(ybirth)

```

```{r local w2, echo=F}

vbl <- MHAS_w2$c12
kable(Categorical_summary(vbl, missing_values = c(9))[3], caption = names(MHAS_w2)[2])
kable(Categorical_summary(vbl, missing_values = c(9))[1], caption = "Category")
ggplot(MHAS_w2, aes(x=factor(c12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w2$c18
vbl_miss <- c(9999)
kable(Continuous_summary(var = vbl, missing_values = c(9999))[3], caption = names(MHAS_w2)[3])
pander(Continuous_summary(vbl, missing_values = c(9999))$summary, caption = "Summary")
ggplot(MHAS_w2 %>% filter(!vbl %in% vbl_miss), aes(c18)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w2$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(MHAS_w2)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(MHAS_w2 %>% filter(!vbl %in% miss_values_vector), aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cancer` from the study-specific variable it has to be recoded as follows:

* `change 2 into 0`
* `c12 == 1 & (c18>=2002 | new individuals) into 1`
* `change 9 into 998`
* `NA into 999`

To compute `cancer_age` from the study-specific variable it has to be recoded as follows:

* `if cancer == 1, cancer_age = c18-ybirth`
* `if cancer == 0, cancer_age = 996`
* `change 9999 into 998`
* `cancer == missing into 999`

**R script:**

<!--
Harmonization should be done globally at the beginning since in this wave are answered years previous to wave 1 which could be assigned already in it.
-->

```{r harmo w2}

MHAS_w2 <- left_join(MHAS_w2,MHAS_ds_w1,by="id")

# Categorical variable harmonization
MHAS_ds_w2 <- tibble(id=MHAS_w2$id)
MHAS_ds_w2$cancer <- rep(999,length(MHAS_w2$id))
MHAS_ds_w2$cancer[which(MHAS_w2$c12==2)] <- 0
MHAS_ds_w2$cancer[which(MHAS_w2$c12==9)] <- 998
MHAS_ds_w2$cancer[which(MHAS_w2$c12 == 1 & (MHAS_w2$c18>=2002 | !MHAS_w2$id %in% MHAS_w1$id | (MHAS_w2$c18==2001 & MHAS_w2$cancer==0)))] <- 1


# Continuous variable harmonization
MHAS_ds_w2$cancer_age <- rep(999,length(MHAS_w2$id))
MHAS_ds_w2$cancer_age[which(MHAS_ds_w2$cancer == 0)] <- 996
MHAS_ds_w2$cancer_age[which(MHAS_ds_w2$cancer == 1 & !MHAS_w2$ybirth %in% miss_values_vector & MHAS_w2$c18!=9999)] <- MHAS_w2$c18[which(MHAS_ds_w2$cancer == 1 & !MHAS_w2$ybirth %in% miss_values_vector & MHAS_w2$c18!=9999)] - MHAS_w2$ybirth[which(MHAS_ds_w2$cancer == 1 & !MHAS_w2$ybirth %in% miss_values_vector & MHAS_w2$c18!=9999)]
MHAS_ds_w2$cancer_age[which(MHAS_w2$c18==9999)] <- 998
MHAS_ds_w2$cancer_age <- car::recode(MHAS_ds_w2$cancer_age,"NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- MHAS_ds_w2$cancer
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w2, aes(x=factor(cancer))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- MHAS_ds_w2$cancer_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(MHAS_ds_w2 %>% filter(!vbl %in% miss_values_vector), aes(cancer_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w2, echo=F, results='asis'}

AfterH <- table(MHAS_ds_w2$cancer, useNA = "ifany")
X <- c(
  sum(MHAS_w2$c12==2,na.rm=T),
  sum(MHAS_w2$c12 == 1 & (MHAS_w2$c18>=2002 | !MHAS_w2$id %in% MHAS_w1$id | (MHAS_w2$c18==2001 & MHAS_w2$cancer==0)),na.rm=T),
  sum(MHAS_w2$c12==9,na.rm = T)
)
BeforeH <- c(X[1:3],length(MHAS_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","9->998","NA->999")
kable(C)


```



### Wave 3

#### Study-specific variable description

| **Name** | `c12_12` |`ybirth`|`c18_1_12`|
|-|-|-|-|
| **Label** | `Has a physician diagnosed respondent...cancer`|`year of birth`|`Respondent's year of most recent cancer diagnosis`|
| **Table name**  | `MHAS_2012_new`|`ybirth`|`MHAS_2012_new`|
| **Categories** | `1 = Yes`<br/>`2 = No` |`continuous`|`continuous`|
| **Missings** | `8 = Doesn't answer`<br/>`9 = Doesn't know`<br/>`NA` | `998 = Do not know`<br/>`999 = Missing` | `NA`<br/>`9999 = DK` |
| **Description** |  |  |  |



```{r assign w3, echo=F}

opal.assign.table.tibble(o, 'MHAS_w3','Mexican Health Aging Study.MHAS_2012_new',variables=list('c12_12','c18_1_12'), missings = T)
MHAS_w3 <- opal.execute(o,'MHAS_w3')
load(paste0(datafolder,"w3/ybirth.RData"))
MHAS_w3 <- left_join(MHAS_w3,ybirth, by="id")
rm(ybirth)

```

```{r local w3, echo=F}

vbl <- MHAS_w3$c12_12
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = names(MHAS_w3)[2])
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(MHAS_w3, aes(x=factor(c12_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w3$c18_1_12
vbl_miss <- c(9999)
kable(Continuous_summary(var = vbl, missing_values = c(9999))[3], caption = names(MHAS_w3)[3])
pander(Continuous_summary(vbl, missing_values = c(9999))$summary, caption = "Summary")
ggplot(MHAS_w3 %>% filter(!vbl %in% vbl_miss), aes(c18_1_12)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w3$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(MHAS_w3)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(MHAS_w3 %>% filter(!vbl %in% miss_values_vector), aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cancer` from the study-specific variable it has to be recoded as follows:

* `change 2 into 0`
* `c12_12 == 1 & (c18_1_12>=2004 | new individuals) into 1`
* `change 8 into 995`
* `change 9 into 998`
* `NA into 999`

To compute `cancer_age` from the study-specific variable it has to be recoded as follows:

* `if cancer == 1, cancer_age = c18_1_12 - ybirth`
* `if cancer == 0, cancer_age = 996`
* `change 9999 into 998`
* `otherwise into 999`

**R script:**

<!--
Harmonization should be done globally at the beginning since in this wave are answered years between waves 1 and 2 which could be assigned already in wave 2.
-->

```{r harmo w3}

MHAS_w3 <- left_join(MHAS_w3,MHAS_ds_w2,by="id")

# Categorical variable harmonization
MHAS_ds_w3 <- tibble(id=MHAS_w3$id)
MHAS_ds_w3$cancer <- rep(999,length(MHAS_w3$id))
MHAS_ds_w3$cancer[which(MHAS_w3$c12_12==2)] <- 0
MHAS_ds_w3$cancer[which(MHAS_w3$c12_12==8)] <- 995
MHAS_ds_w3$cancer[which(MHAS_w3$c12_12==9)] <- 998
# Individuals with cancer after the past time interviewed or from refreshment
MHAS_ds_w3$cancer[which(MHAS_w3$c12_12==1 & (MHAS_w3$c18_1_12>=2004 | ((!MHAS_w3$id %in% MHAS_w2$id | MHAS_w3$cancer==0) & MHAS_w3$c18_1_12>=2002) | !MHAS_w3$id %in% union(MHAS_w1$id,MHAS_w2$id)))] <- 1


# Continuous variable harmonization
MHAS_ds_w3$cancer_age <- rep(999,length(MHAS_w3$id))
MHAS_ds_w3$cancer_age[which(MHAS_ds_w3$cancer == 0)] <- 996
MHAS_ds_w3$cancer_age[which(MHAS_ds_w3$cancer == 1 & !MHAS_w3$ybirth %in% miss_values_vector & !MHAS_w3$c18_1_12 %in% c(8888,9999))] <- MHAS_w3$c18_1_12[which(MHAS_ds_w3$cancer == 1 & !MHAS_w3$ybirth %in% miss_values_vector & !MHAS_w3$c18_1_12 %in% c(8888,9999))] - MHAS_w3$ybirth[which(MHAS_ds_w3$cancer == 1 & !MHAS_w3$ybirth %in% miss_values_vector & !MHAS_w3$c18_1_12 %in% c(8888,9999))]
MHAS_ds_w3$cancer_age[which(MHAS_w3$c18_1_12==8888)] <- 995
MHAS_ds_w3$cancer_age[which(MHAS_w3$c18_1_12==9999)] <- 998
MHAS_ds_w3$cancer_age <- car::recode(MHAS_ds_w3$cancer_age, "NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w3, echo=F}

vbl <- MHAS_ds_w3$cancer
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w3, aes(x=factor(cancer))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- MHAS_ds_w3$cancer_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(MHAS_ds_w3 %>% filter(!vbl %in% miss_values_vector), aes(cancer_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w3, echo=F, results='asis'}

AfterH <- table(MHAS_ds_w3$cancer, useNA = "ifany")
X <- c(
  sum(MHAS_w3$c12_12==2,na.rm=T),
  sum(MHAS_w3$c12_12==1 & (MHAS_w3$c18_1_12>=2004 | ((!MHAS_w3$id %in% MHAS_w2$id | MHAS_w3$cancer==0) & MHAS_w3$c18_1_12>=2002) | !MHAS_w3$id %in% union(MHAS_w1$id,MHAS_w2$id)),na.rm=T),
  sum(MHAS_w3$c12_12==8,na.rm=T),
  sum(MHAS_w3$c12_12==9,na.rm=T)
)
BeforeH <- c(X[1:4],length(MHAS_w3$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","8->995","9->998","NA->999")
kable(C)

```



<!--AUXILIAR FUNCTIONS-->



```{r helpfunctions, echo=F}

source("../../helpfunctions.r")

```



```{r populations-waves, echo=F}


# All study waves and populations with abbreviated and descriptive names

mhas.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"))



```


<!--Labelling and saving-->

```{r, echo=FALSE}


# Consider only waves with some variable harmonised

l.hds <- lapply(mhas.cw, function(wname) if(exists(paste0("MHAS_ds_",wname[1]))){wname = list(get(paste0("MHAS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling categorical variable of tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]],hd_vbl,ds_label)
  # Labelling continuous variable of tibbles
  lmlist <- labelling_c(lmlist[[1]],lmlist[[2]],hd_age_vbl,ds_label_age)
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}

mhaslist <- lmlist # MHAS list




```



<!--Descriptives-->

## Descriptive statistics of the harmonised variable `cancer` accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.


```{r summ, echo=F}


# Consider only harmonised waves
l.hds <- lapply(mhas.cw, function(wname) if(hd_vbl %in% names(get0(paste0("MHAS_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- mhaslist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- mhaslist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))

}



```






## Summary of descriptive statistics of the harmonised variable `cancer_age` accross populations and waves






```{r summ_c, echo=F}


# Consider only harmonised waves
l.hds <- lapply(mhas.cw, function(wname) if(hd_age_vbl %in% names(get0(paste0("MHAS_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- mhaslist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- mhaslist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries_c(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_age_vbl),caption=ds_label_age))
}





```



# Quality estimation

Minor skin cancers are excluded.






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





