---
title: "Multimorbidity"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/multimorbidDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/multimorbidDS.R')
```



# Data process


## Mexico

### Wave 1


#### Study-specific variable description

| **Name** |`h_diabetes`|`h_respiratory`|`h_hypertension`|`h_joint_disorders`| `stroke` |`mi_ha`|
|-|-|-|-|-|-|-|
| **Label** |`History of diabetes mellitus`|`Chronic respiratory diseases such respiratory, CPD, COPD, bronchitis, emphysema`|`History of hypertension`|`History of arthritis, rheumatism or osteoarthritis`| `Stroke` |`Myocardial infarction or heart attack`|
| **Table name**  |`mhas_w1_hd`|`mhas_w1_hd`|`mhas_w1_hd`|`mhas_w1_hd`|`mhas_w1_hd`| `mhas_w1_hd` |
| **Categories** |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`| `0 = No`<br/>`1 = Yes` |
| **Missings** | `995 = Does not answer`<br/>`998 = Do not know`<br/>`999 = Missing` | `995 = Does not answer`<br/>`998 = Do not know`<br/>`999 = Missing` |`995 = Does not answer`<br/>`998 = Do not know`<br/>`999 = Missing`|  `995 = Does not answer`<br/>`998 = Do not know`<br/>`999 = Missing` |  `995 = Does not answer`<br/>`998 = Do not know`<br/>`999 = Missing` |  `995 = Does not answer`<br/>`998 = Do not know`<br/>`999 = Missing` |
| **Description** |  |  |  |  |  |  |  |  |


```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'MHAS_w1','MHAS_HD.mhas_w1_hd',variables=list('h_diabetes','h_respiratory','h_hypertension','h_joint_disorders','stroke','mi_ha'), missings = T)
MHAS_w1 <- opal.execute(o,'MHAS_w1') %>%
  mutate(id = paste0(id,".0"))

```



```{r local w1, echo=F}

vbl <- MHAS_w1$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_diabetes")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(MHAS_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w1$h_respiratory
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_respiratory")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(MHAS_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w1$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_hypertension")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(MHAS_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w1$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_joint_disorders")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(MHAS_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "stroke")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(MHAS_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "mi_ha")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(MHAS_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `multimorbid` from the study-specific variables they have to be recoded as follows:

* `Multimorbid_score = sum(h_diabetes, h_respiratory, h_hypertension,mi_ha, h_joint_disorders, stroke)`
* `Multimorbid_status = 1 if multimorbid_score > = 2`
* `Multimorbid_status = 0 if multimorbid_score < 2`
* `otherwise into 999`

**R script:**

```{r harmo w1, tidy=FALSE}

MHAS_ds_w1 <- MHAS_w1 %>% 
  mutate(dead = purrr::pmap(mutate_at(., vars(-id), `==`, 996) %>% select(., -id), all) %>% unlist()) %>%
  mutate_at(names(MHAS_w1[,-1]), ~replace(., list = which(. %in% 991:999), values = NA)) %>% 
  mutate(multimorbid_score = rowSums(select(., -1, -dead), na.rm = T)) %>%
  mutate(cardNA = rowSums(!is.na(select(., -1, -dead, -multimorbid_score)))) %>%
  mutate(cardNA = cardNA/cardNA) %>%
  mutate(multimorbid_score = multimorbid_score * cardNA) %>%
  mutate(multimorbid = case_when(multimorbid_score >= 2 ~ 1, multimorbid_score < 2 ~ 0, dead ~ 996, TRUE ~ 999)) %>%
  select(id, multimorbid)

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- MHAS_ds_w1$multimorbid
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}
```


### Wave 2


#### Study-specific variable description

| **Name** |`h_diabetes`|`h_respiratory`|`h_hypertension`|`h_joint_disorders`| `stroke` |`mi_ha`|
|-|-|-|-|-|-|-|
| **Label** |`History of diabetes mellitus`|`Chronic respiratory diseases such respiratory, CPD, COPD, bronchitis, emphysema`|`History of hypertension`|`History of arthritis, rheumatism or osteoarthritis`| `Stroke` |`Myocardial infarction or heart attack`|
| **Table name**  |`mhas_w2_hd`|`mhas_w2_hd`|`mhas_w2_hd`|`mhas_w2_hd`|`mhas_w2_hd`| `mhas_w2_hd` |
| **Categories** |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`| `0 = No`<br/>`1 = Yes` |
| **Missings** | `995 = Does not answer`<br/>`996 = Not applicable`<br/>`998 = Do not know`<br/>`999 = Missing` |  `995 = Does not answer`<br/>`996 = Not applicable`<br/>`998 = Do not know` |`996 = Not applicable`<br/>`998 = Do not know`|`996 = Not applicable`<br/>`998 = Do not know`|  `995 = Does not answer`<br/>`996 = Not applicable`<br/>`998 = Do not know` |  `995 = Does not answer`<br/>`996 = Not applicable`<br/>`998 = Do not know`<br/>`999 = Missing` |
| **Description** |  |  |  |  |  |  |  |  |


```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'MHAS_w2','MHAS_HD.mhas_w2_hd',variables=list('h_diabetes','h_respiratory','h_hypertension','h_joint_disorders','stroke','mi_ha'), missings = T)
MHAS_w2 <- opal.execute(o,'MHAS_w2') %>%
  mutate(id = paste0(id,".0"))

```



```{r local w2, echo=F}

vbl <- MHAS_w2$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_diabetes")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(MHAS_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w2$h_respiratory
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_respiratory")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(MHAS_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w2$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_hypertension")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(MHAS_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w2$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_joint_disorders")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(MHAS_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w2$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "stroke")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(MHAS_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w2$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "mi_ha")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(MHAS_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `multimorbid` from the study-specific variables they have to be recoded as follows:

* `Multimorbid_score = sum(h_diabetes, h_respiratory, h_hypertension,mi_ha, h_joint_disorders, stroke)`
* `Multimorbid_status = 1 if multimorbid_score > = 2`
* `Multimorbid_status = 0 if multimorbid_score < 2`
* `otherwise into 999`

**R script:**

```{r harmo w2, tidy=FALSE}

MHAS_ds_w2 <- MHAS_w2 %>% 
  mutate(dead = purrr::pmap(mutate_at(., vars(-id), `==`, 996) %>% select(., -id), all) %>% unlist()) %>%
  mutate_at(names(MHAS_w2[,-1]), ~replace(., list = which(. %in% 991:999), values = NA)) %>% 
  mutate(multimorbid_score = rowSums(select(., -1, -dead), na.rm = T)) %>%
  mutate(cardNA = rowSums(!is.na(select(., -1, -dead, -multimorbid_score)))) %>%
  mutate(cardNA = cardNA/cardNA) %>%
  mutate(multimorbid_score = multimorbid_score * cardNA) %>%
  mutate(multimorbid = case_when(multimorbid_score >= 2 ~ 1, multimorbid_score < 2 ~ 0, dead ~ 996, TRUE ~ 999)) %>%
  select(id, multimorbid)

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- MHAS_ds_w2$multimorbid
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w2, echo=F}
```


### Wave 3


#### Study-specific variable description

| **Name** |`h_diabetes`|`h_respiratory`|`h_hypertension`|`h_joint_disorders`| `stroke` |`mi_ha`|
|-|-|-|-|-|-|-|
| **Label** |`History of diabetes mellitus`|`Chronic respiratory diseases such respiratory, CPD, COPD, bronchitis, emphysema`|`History of hypertension`|`History of arthritis, rheumatism or osteoarthritis`| `Stroke` |`Myocardial infarction or heart attack`|
| **Table name**  |`mhas_w3_hd`|`mhas_w3_hd`|`mhas_w3_hd`|`mhas_w3_hd`|`mhas_w3_hd`| `mhas_w3_hd` |
| **Categories** |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`| `0 = No`<br/>`1 = Yes` |
| **Missings** | `995 = Does not answer`<br/>`996 = Not applicable`<br/>`998 = Do not know`<br/>`999 = Missing` | `995 = Does not answer`<br/>`996 = Not applicable`<br/>`998 = Do not know`<br/>`999 = Missing` |`995 = Does not answer`<br/>`996 = Not applicable`<br/>`998 = Do not know`<br/>`999 = Missing`|`995 = Does not answer`<br/>`996 = Not applicable`<br/>`998 = Do not know`<br/>`999 = Missing` |`995 = Does not answer`<br/>`996 = Not applicable`<br/>`998 = Do not know`<br/>`999 = Missing` |`995 = Does not answer`<br/>`996 = Not applicable`<br/>`998 = Do not know`<br/>`999 = Missing` |
| **Description** |  |  |  |  |  |  |  |  |


```{r assign w3, echo=F}

opal.assign.table.tibble(o, 'MHAS_w3','MHAS_HD.mhas_w3_hd',variables=list('h_diabetes','h_respiratory','h_hypertension','h_joint_disorders','stroke','mi_ha'), missings = T)
MHAS_w3 <- opal.execute(o,'MHAS_w3') %>%
  mutate(id = paste0(id,".0"))

```



```{r local w3, echo=F}

vbl <- MHAS_w3$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_diabetes")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(MHAS_w3, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w3$h_respiratory
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_respiratory")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(MHAS_w3, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w3$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_hypertension")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(MHAS_w3, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w3$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_joint_disorders")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(MHAS_w3, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w3$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "stroke")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(MHAS_w3, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w3$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "mi_ha")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(MHAS_w3, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `multimorbid` from the study-specific variables they have to be recoded as follows:

* `Multimorbid_score = sum(h_diabetes, h_respiratory, h_hypertension,mi_ha, h_joint_disorders, stroke)`
* `Multimorbid_status = 1 if multimorbid_score > = 2`
* `Multimorbid_status = 0 if multimorbid_score < 2`
* `otherwise into 999`

**R script:**

```{r harmo w3, tidy=FALSE}

MHAS_ds_w3 <- MHAS_w3 %>% 
  mutate(dead = purrr::pmap(mutate_at(., vars(-id), `==`, 996) %>% select(., -id), all) %>% unlist()) %>%
  mutate_at(names(MHAS_w3[,-1]), ~replace(., list = which(. %in% 991:999), values = NA)) %>% 
  mutate(multimorbid_score = rowSums(select(., -1, -dead), na.rm = T)) %>%
  mutate(cardNA = rowSums(!is.na(select(., -1, -dead, -multimorbid_score)))) %>%
  mutate(cardNA = cardNA/cardNA) %>%
  mutate(multimorbid_score = multimorbid_score * cardNA) %>%
  mutate(multimorbid = case_when(multimorbid_score >= 2 ~ 1, multimorbid_score < 2 ~ 0, dead ~ 996, TRUE ~ 999)) %>%
  select(id, multimorbid)

```


#### Statistics of the new harmonized variable

```{r descript w3, echo=F}

vbl <- MHAS_ds_w3$multimorbid
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w3, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w3, echo=F}
```





## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.




```{r helpfunctions, echo=F}

source("../../helpfunctions.r")

```



```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


mhas.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"))

# Consider only harmonised waves
l.hds <- lapply(mhas.cw, function(wname) if(exists(paste0("MHAS_ds_",wname[1]))){wname = list(get(paste0("MHAS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```




# Quality estimation


```{r closeRsession, echo=FALSE} 
opal.logout(o)
```