---
title: "Hypertension"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `h_hypertension`
* Variable label: `History of Hypertension`
* Variable description: `history of hypertension or high blood pressure`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | NOT High blood pressure or hypertension 
1        | High blood pressure or hypertension

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Short name: `h_hypertension_age`
* Variable label: `Age first diagnosed hypertension`
* Variable description: `The age first told had hypertension diagnosis`
* Domain: `Diseases`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "History of Hypertension"
ds_label_age <- "Age first diagnosed hypertension"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
cont_label <- cat_label[3:11]
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process



## Mexico


### Wave 1


#### Study-specific variable description

| **Name** | `c4` |
|-|-|
| **Label** | `Hypertension`|
| **Table name**  | `MHAS-2001`|
| **Categories** | `1 = Yes`<br/>`2 = No` |
| **Missings** | `8 = Doesn't answer`<br/>`9 = Doesn't know`<br/>`NA` |
| **Description** |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'MHAS_w1','Mexican Health Aging Study.MHAS-2001',variables=list('c4'), missings = T)
MHAS_w1 <- opal.execute(o,'MHAS_w1')

```

```{r local w1, echo=F}

vbl <- MHAS_w1$c4
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = names(MHAS_w1)[2])
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(MHAS_w1, aes(x=factor(c4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_hypertension` from the study-specific variable it has to be recoded as follows:

* `change 2 into 0`
* `keep up 1 into 1`
* `change 8 into 995`
* `change 9 into 998`
* `NA into 999`

Age of diagnosis cannot be harmonized.

**R script:**

```{r harmo w1}

# Categorical variable harmonization
MHAS_ds_w1 <- tibble(id=MHAS_w1$id)
MHAS_ds_w1$h_hypertension <- car::recode(MHAS_w1$c4, "2=0; 8=995; 9=998; NA=999")

# We build a global table in order to have updated the hypertension status of all the individuals through the different waves
MHAS_ds <- MHAS_ds_w1

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- MHAS_ds_w1$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w1, aes(x=factor(h_hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}

AfterH <- table(MHAS_ds_w1$h_hypertension)
BeforeH <- table(MHAS_w1$c4, useNA = "ifany")[c(2,1,3,4,5)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","8->995","9->998","NA->999")
kable(C)

```



### Wave 2

#### Study-specific variable description

| **Name** | `c4` |`age`|`yintw (w1)`|`yintw (w2)`|
|-|-|-|-|-|
| **Label** | `Doctor ever say you have hypertension`|`age`|`year of interview`|`year of interview`|
| **Table name**  | `MHAS_2003`|`age`|`yintw`|`yintw`|
| **Categories** | `1 = Yes`<br/>`2 = No` |`continuous`|`continuous`|`continuous`|
| **Missings** | `9 = Doesn't know`<br/>`NA` | `995 = Does not answer`<br/>`998 = Do not know`<br/>`999 = Missing` |  |  |
| **Description** |  |  |  |  |

```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'MHAS_w2','Mexican Health Aging Study.MHAS_2003',variables=list('c4'), missings = T)
MHAS_w2 <- opal.execute(o,'MHAS_w2')
load(paste0(datafolder,"w2/age.RData"))
MHAS_w2 <- left_join(MHAS_w2,age, by="id")
rm(age)
load(paste0(datafolder,"w1/yintw.RData"))
MHAS_w2 <- left_join(MHAS_w2,yintw, by="id")
names(MHAS_w2)[4] <- "yintw_w1"
rm(yintw)
load(paste0(datafolder,"w2/yintw.RData"))
MHAS_w2 <- left_join(MHAS_w2,yintw, by="id")
names(MHAS_w2)[5] <- "yintw_w2"
rm(yintw)

```

```{r local w2, echo=F}

vbl <- MHAS_w2$c4
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = names(MHAS_w2)[2])
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(MHAS_w2, aes(x=factor(c4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w2$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(MHAS_w2)[3])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(MHAS_w2, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(20,110)

vbl <- MHAS_w2$yintw_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(MHAS_w2)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(MHAS_w2, aes(x=factor(yintw_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w2$yintw_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(MHAS_w2)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(MHAS_w2, aes(x=factor(yintw_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_hypertension` from the study-specific variable it has to be recoded as follows:

* `c4 (w1) == 2 and c4 (w2) == 2 into 0`
* `c4 (w1) == 1 or c4 (w2) == 1 into 1`
* `9 into 998`
* `otherwise into 999`

To compute `h_hypertension_age` from the study-specific variable it has to be recoded as follows:

* `if h_hypertension == 1 in w2 and 0 in w1, h_hypertension_age = age-(year of interview w2-year of interview w1)/2`
* `if h_hypertension == 0, h_hypertension_age = 996`
* `h_hypertension == missing into 999`

**R script:**

```{r harmo w2}

# We use the harmonized variable of wave 1 instead of its study-specific variable
MHAS_w2 <- left_join(MHAS_w2, MHAS_ds, by = "id")

# Categorical variable harmonization
MHAS_ds_w2 <- tibble(id=MHAS_w2$id)
MHAS_ds_w2$h_hypertension <- rep(999,length(MHAS_w2$id))
MHAS_ds_w2$h_hypertension[which(MHAS_w2$c4 == 2 & (MHAS_w2$h_hypertension != 1 | is.na(MHAS_w2$h_hypertension)))] <- 0
MHAS_ds_w2$h_hypertension[which(MHAS_w2$c4 == 1 | ((!is.na(MHAS_w2$c4)) & MHAS_w2$h_hypertension == 1))] <- 1
MHAS_ds_w2$h_hypertension[which(MHAS_w2$c4 == 9 & (MHAS_w2$h_hypertension != 1 | is.na(MHAS_w2$h_hypertension)))] <- 998

# Continuous variable harmonization
MHAS_ds_w2$h_hypertension_age <- rep(999,length(MHAS_w2$id))
MHAS_ds_w2$h_hypertension_age[which(MHAS_ds_w2$h_hypertension == 0)] <- 996
MHAS_ds_w2$h_hypertension_age[which(MHAS_ds_w2$h_hypertension == 1 & MHAS_w2$h_hypertension==0 & !MHAS_w2$age %in% miss_values_vector)] <- MHAS_w2$age[which(MHAS_ds_w2$h_hypertension == 1 & MHAS_w2$h_hypertension==0 & !MHAS_w2$age %in% miss_values_vector)]-(MHAS_w2$yintw_w2[which(MHAS_ds_w2$h_hypertension == 1 & MHAS_w2$h_hypertension==0 & !MHAS_w2$age %in% miss_values_vector)]-MHAS_w2$yintw_w1[which(MHAS_ds_w2$h_hypertension == 1 & MHAS_w2$h_hypertension==0 & !MHAS_w2$age %in% miss_values_vector)])/2

# We update the hypertension status of the individuals in the global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- full_join(endtib,sttib,by="id")
  row.names(newtib) <- newtib$id
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
MHAS_ds_prov <- MHAS_ds[,c(1,2)]
MHAS_ds_prov <- assign_merge(MHAS_ds_prov,MHAS_ds_w2,log_vec=MHAS_ds_w2$id,col_end_index = 2, col_st_index = 3)
MHAS_ds <- MHAS_ds_prov
MHAS_ds_prov <- MHAS_ds_w2[,c(1,3)]
MHAS_ds <- full_join(MHAS_ds,MHAS_ds_prov,by="id")
rm(MHAS_ds_prov)

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- MHAS_ds_w2$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w2, aes(x=factor(h_hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- MHAS_ds_w2$h_hypertension_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(MHAS_ds_w2, aes(h_hypertension_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(25,100)

```


#### Validation

```{r crosstabulation w2, echo=F, results='asis'}

AfterH <- table(MHAS_ds_w2$h_hypertension, useNA = "ifany")
X <- c(
  sum(((!is.na(MHAS_w2$c4)) & MHAS_w2$c4 == 2) & (MHAS_w2$h_hypertension != 1 | is.na(MHAS_w2$h_hypertension)),na.rm=T),
  sum(((!is.na(MHAS_w2$c4)) & MHAS_w2$c4 == 1) | ((!is.na(MHAS_w2$h_hypertension)) & (!is.na(MHAS_w2$c4)) & MHAS_w2$h_hypertension == 1),na.rm=T),
  sum(((!is.na(MHAS_w2$c4)) & MHAS_w2$c4 == 9) & (MHAS_w2$h_hypertension != 1 | is.na(MHAS_w2$h_hypertension)),na.rm=T)
)
BeforeH <- c(X[1:3])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","9->998")
kable(C)

cat("There are 1600 individuals who answered in wave 1 they had hypertension and in wave 2 they did not. We harmonize them as having it")
kable(frq(MHAS_w2$h_hypertension[which(MHAS_w2$c4==2)]),align='c')
# kable(MHAS_w2[which(MHAS_w2$c4==2 & MHAS_w2$h_hypertension==1),],align = 'c')

```



### Wave 3

#### Study-specific variable description

| **Name** | `c4_12` |`ybirth`|`yintw (w3)`|`yintw (w2)`|
|-|-|-|-|-|
| **Label** | `Has a physician diagnosed...hypertension/high blood pressure`|`year of birth`|`year of interview`|`year of interview`|
| **Table name**  | `MHAS_2012_new`|`ybirth`|`yintw`|`yintw`|
| **Categories** | `1 = Yes`<br/>`2 = No` |`continuous`|`continuous`|`continuous`|
| **Missings** | `8 = Doesn't answer`<br/>`9 = Doesn't know`<br/>`NA` | `999 = Missing` |  |  |
| **Description** |  |  |  |  |

```{r assign w3, echo=F}

opal.assign.table.tibble(o, 'MHAS_w3','Mexican Health Aging Study.MHAS_2012_new',variables=list('c4_12'), missings = T)
MHAS_w3 <- opal.execute(o,'MHAS_w3')
load(paste0(datafolder,"w3/ybirth.RData"))
MHAS_w3 <- left_join(MHAS_w3,ybirth, by="id")
rm(ybirth)
load(paste0(datafolder,"w3/yintw.RData"))
MHAS_w3 <- left_join(MHAS_w3,yintw, by="id")
names(MHAS_w3)[4] <- "yintw_w3"
rm(yintw)
load(paste0(datafolder,"w2/yintw.RData"))
MHAS_w3 <- left_join(MHAS_w3,yintw, by="id")
names(MHAS_w3)[5] <- "yintw_w2"
rm(yintw)

```

```{r local w3, echo=F}

vbl <- MHAS_w3$c4_12
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = names(MHAS_w3)[2])
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(MHAS_w3, aes(x=factor(c4_12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w3$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(MHAS_w3)[3])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(MHAS_w3, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1895,1980)

vbl <- MHAS_w3$yintw_w3
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(MHAS_w3)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(MHAS_w3, aes(x=factor(yintw_w3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- MHAS_w3$yintw_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(MHAS_w3)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(MHAS_w3, aes(x=factor(yintw_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_hypertension` from the study-specific variable it has to be recoded as follows:

* `c4 (w1) == 2 and c4 (w2) == 2 and c4_12 == 2 into 0`
* `c4 == 1 or c4 == 1 or c4_12 == 1 into 1`
* `8 into 995`
* `9 into 998`
* `otherwise into 999`

To compute `h_hypertension_age` from the study-specific variable it has to be recoded as follows:

* `if h_hypertension == 1 in w3 and 0 in w2, h_hypertension_age = (year of interview w3-year of interview w2)/2+(year of interview w2 - ybirth)`
* `if h_hypertension == 1 in w3 and other wave, h_hypertension_age as previously`
* `if h_hypertension == 0, h_hypertension_age = 996`
* `h_hypertension == missing into 999`

**R script:**

```{r harmo w3}

# We use the harmonized variable of wave 2 instead of the study-specific variables from all the previous waves
MHAS_w3 <- left_join(MHAS_w3, MHAS_ds, by = "id")

# Categorical variable harmonization
MHAS_ds_w3 <- tibble(id=MHAS_w3$id)
MHAS_ds_w3$h_hypertension <- rep(999,length(MHAS_w3$id))
MHAS_ds_w3$h_hypertension[which(MHAS_w3$c4_12 == 2 & (MHAS_w3$h_hypertension != 1 | is.na(MHAS_w3$h_hypertension)))] <- 0
MHAS_ds_w3$h_hypertension[which(MHAS_w3$c4_12 == 1 | ((!is.na(MHAS_w3$c4_12)) & MHAS_w3$h_hypertension == 1))] <- 1
MHAS_ds_w3$h_hypertension[which(MHAS_w3$c4_12 == 8 & (MHAS_w3$h_hypertension != 1 | is.na(MHAS_w3$h_hypertension)))] <- 995
MHAS_ds_w3$h_hypertension[which(MHAS_w3$c4_12 == 9 & (MHAS_w3$h_hypertension != 1 | is.na(MHAS_w3$h_hypertension)))] <- 998

# Continuous variable harmonization
MHAS_ds_w3$h_hypertension_age <- rep(999,length(MHAS_w3$id))
MHAS_ds_w3$h_hypertension_age[which(MHAS_ds_w3$h_hypertension == 0)] <- 996
MHAS_ds_w3$h_hypertension_age[which(MHAS_ds_w3$h_hypertension == 1 & !MHAS_w3$h_hypertension_age %in% miss_values_vector & !is.na(MHAS_w3$h_hypertension_age))] <- MHAS_w3$h_hypertension_age[which(MHAS_ds_w3$h_hypertension == 1 & !MHAS_w3$h_hypertension %in% miss_values_vector & !is.na(MHAS_w3$h_hypertension_age))]
MHAS_w3 <- left_join(MHAS_w3, MHAS_ds_w2[,c(1,2)], by = "id", suffix = c("","_w2"))
MHAS_ds_w3$h_hypertension_age[which(MHAS_ds_w3$h_hypertension == 1 & MHAS_w3$h_hypertension_w2==0 & MHAS_w3$ybirth != 999)] <- (MHAS_w3$yintw_w3[which(MHAS_ds_w3$h_hypertension == 1 & MHAS_w3$h_hypertension_w2==0 & MHAS_w3$ybirth != 999)]+MHAS_w3$yintw_w2[which(MHAS_ds_w3$h_hypertension == 1 & MHAS_w3$h_hypertension_w2==0 & MHAS_w3$ybirth != 999)])/2-MHAS_w3$ybirth[which(MHAS_ds_w3$h_hypertension == 1 & MHAS_w3$h_hypertension_w2==0 & MHAS_w3$ybirth != 999)]
MHAS_ds_w3$h_hypertension_age <- car::recode(MHAS_ds_w3$h_hypertension_age, "NA=999")
rm(MHAS_ds)

```


#### Statistics of the new harmonized variable

```{r descript w3, echo=F}

vbl <- MHAS_ds_w3$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(MHAS_ds_w3, aes(x=factor(h_hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- MHAS_ds_w3$h_hypertension_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(MHAS_ds_w3, aes(h_hypertension_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(25,100)

```


#### Validation

```{r crosstabulation w3, echo=F, results='asis'}

AfterH <- table(MHAS_ds_w3$h_hypertension, useNA = "ifany")
X <- c(
  sum(((!is.na(MHAS_w3$c4_12)) & MHAS_w3$c4_12 == 2) & (MHAS_w3$h_hypertension != 1 | is.na(MHAS_w3$h_hypertension)),na.rm=T),
  sum(((!is.na(MHAS_w3$c4_12)) & MHAS_w3$c4_12 == 1) | ((!is.na(MHAS_w3$h_hypertension)) & (!is.na(MHAS_w3$c4_12)) & MHAS_w3$h_hypertension == 1),na.rm=T),
  sum(((!is.na(MHAS_w3$c4_12)) & MHAS_w3$c4_12 == 8) & (MHAS_w3$h_hypertension != 1 | is.na(MHAS_w3$h_hypertension)),na.rm=T),
  sum(((!is.na(MHAS_w3$c4_12)) & MHAS_w3$c4_12 == 9) & (MHAS_w3$h_hypertension != 1 | is.na(MHAS_w3$h_hypertension)),na.rm=T)
)
BeforeH <- c(X[1:4],length(MHAS_w3$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","8->995","9->998","NA->999")
kable(C)

cat("There are 1237 individuals who answered in previous waves they had hypertension and in wave 3 they did not. We harmonize them as having hypertension.")
kable(frq(MHAS_w3$h_hypertension[MHAS_w3$c4_12==2]),align='c')
# kable(MHAS_w2[which(MHAS_w3$c4_12==2 & MHAS_w3$h_hypertension==1),],align = 'c')

```




## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.

**R script:**

```{r summ}
MHAS_ds_w1$h_hypertension <- labelled(MHAS_ds_w1$h_hypertension, labels = cat_label)
label(MHAS_ds_w1$h_hypertension) <- ds_label
MHAS_ds_w2$h_hypertension <- labelled(MHAS_ds_w2$h_hypertension, labels = cat_label)
label(MHAS_ds_w2$h_hypertension) <- ds_label
MHAS_ds_w2$h_hypertension_age <- labelled(MHAS_ds_w2$h_hypertension_age, labels = cont_label)
label(MHAS_ds_w2$h_hypertension_age) <- ds_label_age
MHAS_ds_w3$h_hypertension <- labelled(MHAS_ds_w3$h_hypertension, labels = cat_label)
label(MHAS_ds_w3$h_hypertension) <- ds_label
MHAS_ds_w3$h_hypertension_age <- labelled(MHAS_ds_w3$h_hypertension_age, labels = cont_label)
label(MHAS_ds_w3$h_hypertension_age) <- ds_label_age


MHAS_m_ds_w1 <- MHAS_ds_w1
MHAS_m_ds_w1$h_hypertension <- car::recode(MHAS_m_ds_w1$h_hypertension, "miss_values_vector=NA")
MHAS_m_ds_w2 <- MHAS_ds_w2
MHAS_m_ds_w2$h_hypertension <- car::recode(MHAS_m_ds_w2$h_hypertension, "miss_values_vector=NA")
MHAS_m_ds_w3 <- MHAS_ds_w3
MHAS_m_ds_w3$h_hypertension <- car::recode(MHAS_m_ds_w3$h_hypertension, "miss_values_vector=NA")


tt <-    frq(MHAS_ds_w1$h_hypertension)[[1]][,c(1:2,4)]
tt[4] <- frq(MHAS_ds_w2$h_hypertension)[[1]][,c(4)]
tt[5] <- frq(MHAS_ds_w3$h_hypertension)[[1]][,c(4)]
tt[13,] <- c("n", "sample size", 
             length(MHAS_ds_w1$h_hypertension), length(MHAS_ds_w2$h_hypertension), length(MHAS_ds_w3$h_hypertension)
             )
names(tt)<-c("val", "label", "w1", "w2", "w3")
kable(tt)

dbb <- merge(MHAS_m_ds_w1[,c("id","h_hypertension")], MHAS_m_ds_w2[,c("id","h_hypertension")], by="id", suffixes = c(".w1",".w2"), all=T)
dbb <- merge(dbb, MHAS_m_ds_w3[,c("id","h_hypertension")], by="id", all=T)
names(dbb) <- c("id", "w1", "w2", "w3")
v.dbb <- paste(dbb[,2],dbb[,3],dbb[,4],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])
```



# Quality estimation

We assume that if an individual answers it has hypertension in one wave, it has hypertension for all the next waves.

<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.MHAS <- list(w1 = MHAS_ds_w1, w2 = MHAS_ds_w2, w3 = MHAS_ds_w3)

for(index in seq_along(l.MHAS)){
  h_hypertension <- l.MHAS[[index]]
  save(h_hypertension, file = paste0(datafolder,names(l.MHAS)[index],"/h_hypertension.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





