---
title: "Age"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/ageDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/ageDS.R')
```


# Data process

## HRS

### Wave 1 

#### Study-specific variable description

| **Name** | `R1AGEY_E` |
|----------|------------|
| **Label** | `W1 R Age (years) at Ivw EndMon` |
| **Table name** | `HRS-HRS-w1`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign_hrs1, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w1_age','HRS.HRS-HRS-w1',variables=list('R1AGEY_E'), missings = TRUE)
HRS_hrs_w1_age <- opal.execute(o,'HRS_hrs_w1_age')


```

```{r local_hrs1, echo=F}

vari <- HRS_hrs_w1_age$R1AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R1AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_hrs_w1_age, aes(R1AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_hrs1}
HRS_ds_hrs_w1 <- tibble(id=HRS_hrs_w1_age$id)
HRS_ds_hrs_w1$age <- car::recode(HRS_hrs_w1_age$R1AGEY_E, "NA=999")

HRS_ds_hrs_w1$age <- labelled(HRS_ds_hrs_w1$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs1, echo=F}
vari <- HRS_ds_hrs_w1$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w1, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100)
```

#### Validation
```{r crosstabulation_hrs1, echo=F}
```





```{r importOPAL_hrs1, echo=F}

#opal.assign.data(o, 'HRS_ds_hrs_w1', HRS_ds_hrs_w1)
#opal.symbol_import(o,'HRS_ds_hrs_w1', project='_Athlos_Harm_Dataset')
age <- HRS_ds_hrs_w1
save(age, file = "../RData/hrs_w1/age.RData")
rm(age)

HRS_m_ds_hrs_w1 <- HRS_ds_hrs_w1
HRS_m_ds_hrs_w1$age <- car::recode(HRS_m_ds_hrs_w1$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w1', HRS_m_ds_hrs_w1)
#opal.symbol_import(o,'HRS_m_ds_hrs_w1', project='_Athlos_Harm_Dataset')
```






### Wave 2 

#### Study-specific variable description

| **Name** | `R2AGEY_E` |`living_status`|
|----------|------------|-|
| **Label** | `W2 R Age (years) at Ivw EndMon` |`Living status`|
| **Table name** | `HRS-HRS-w2`|`hrs_hrs_w2`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|`996 = Not applicable`|
| **Description** |  |  |




```{r assign_hrs2, echo=F}

opal.assign.table.tibble(o, 'HRS_hrs_w2_age','HRS.HRS-HRS-w2',variables=list('R2AGEY_E'), missings = TRUE)
HRS_hrs_w2_age <- opal.execute(o,'HRS_hrs_w2_age')


opal.assign.table.tibble(o, 'HRS_hrs_w2','HRS_HD.hrs_hrs_w2',variables=list('living_status'), missings = TRUE)
HRS_hrs_w2 <- opal.execute(o,'HRS_hrs_w2')
HRS_hrs_w2_age <- left_join(HRS_hrs_w2_age,HRS_hrs_w2,by="id")
```

```{r local_hrs2, echo=F}

vari <- HRS_hrs_w2_age$R2AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R2AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_hrs_w2_age, aes(R2AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100)

vbl <- HRS_hrs_w2_age$living_status
kable(Categorical_summary(vbl, missing_values = c(996))[3], caption = "living_status")
kable(Categorical_summary(vbl, missing_values = c(996))[1], caption = "Category")
ggplot(HRS_hrs_w2_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`
* `living_status = Dead or Dropout into 996`

**R script:**

```{r harmo_hrs2}
HRS_ds_hrs_w2 <- tibble(id=HRS_hrs_w2_age$id)
HRS_ds_hrs_w2$age <- car::recode(HRS_hrs_w2_age$R2AGEY_E, "NA=999")
HRS_ds_hrs_w2$age[which(HRS_hrs_w2_age$living_status %in% c(1,2))] <- 996
HRS_ds_hrs_w2$age <- labelled(HRS_ds_hrs_w2$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs2, echo=F}
vari <- HRS_ds_hrs_w2$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w2, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100)
```

#### Validation
```{r crosstabulation_hrs2, echo=F}

```





```{r importOPAL_hrs2, echo=F}

#opal.assign.data(o, 'HRS_ds_hrs_w2', HRS_ds_hrs_w2)
#opal.symbol_import(o,'HRS_ds_hrs_w2', project='_Athlos_Harm_Dataset')
age <- HRS_ds_hrs_w2
save(age, file = "../RData/hrs_w2/age.RData")
rm(age)

HRS_m_ds_hrs_w2 <- HRS_ds_hrs_w2
HRS_m_ds_hrs_w2$age <- car::recode(HRS_m_ds_hrs_w2$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w2', HRS_m_ds_hrs_w2)
#opal.symbol_import(o,'HRS_m_ds_hrs_w2', project='_Athlos_Harm_Dataset')
```






### Wave 3 

#### Study-specific variable description


| **Name** |`R3AGEY_E`|`living_status`|
|----------|------------|-|
| **Label** |`W3 R Age (years) at Ivw EndMon`|`Living status`|
| **Table name** |`HRS-HRS-w3`|`hrs_hrs_w3`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|`996 = Not applicable`|
| **Description** |  |  |



```{r assign_hrs3, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w3_age','HRS.HRS-HRS-w3',variables=list('R3AGEY_E'), missings = TRUE)
HRS_hrs_w3_age <- opal.execute(o,'HRS_hrs_w3_age')

opal.assign.table.tibble(o, 'HRS_hrs_w3','HRS_HD.hrs_hrs_w3',variables=list('living_status'), missings = TRUE)
HRS_hrs_w3 <- opal.execute(o,'HRS_hrs_w3')
HRS_hrs_w3_age <- left_join(HRS_hrs_w3_age,HRS_hrs_w3,by="id")
```

```{r local_hrs3, echo=F}




vbl <- HRS_hrs_w3_age$living_status
kable(Categorical_summary(vbl, missing_values = c(996))[3], caption = "living_status")
kable(Categorical_summary(vbl, missing_values = c(996))[1], caption = "Category")
ggplot(HRS_hrs_w3_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <- HRS_hrs_w3_age$R3AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R3AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_hrs_w3_age, aes(R3AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`
* `living_status = Dead or Dropout into 996`

**R script:**

```{r harmo_hrs3}
HRS_ds_hrs_w3 <- tibble(id=HRS_hrs_w3_age$id)
HRS_ds_hrs_w3$age <- car::recode(HRS_hrs_w3_age$R3AGEY_E, "NA=999")
HRS_ds_hrs_w3$age[which(HRS_hrs_w3_age$living_status %in% c(1,2))] <- 996

HRS_ds_hrs_w3$age <- labelled(HRS_ds_hrs_w3$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs3, echo=F}
vari <- HRS_ds_hrs_w3$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w3, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100) 
```

#### Validation
```{r crosstabulation_hrs3, echo=F}

```





```{r importOPAL_hrs3, echo=F}

#opal.assign.data(o, 'HRS_ds_hrs_w3', HRS_ds_hrs_w3)
#opal.symbol_import(o,'HRS_ds_hrs_w3', project='_Athlos_Harm_Dataset')
age <- HRS_ds_hrs_w3
save(age, file = "../RData/hrs_w3/age.RData")
rm(age)

HRS_m_ds_hrs_w3 <- HRS_ds_hrs_w3
HRS_m_ds_hrs_w3$age <- car::recode(HRS_m_ds_hrs_w3$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w3', HRS_m_ds_hrs_w3)
#opal.symbol_import(o,'HRS_m_ds_hrs_w3', project='_Athlos_Harm_Dataset')
```





### Wave 4 

#### Study-specific variable description

| **Name** |`R4AGEY_E`|`living_status`|
|----------|------------|-|
| **Label** |`W4 R Age (years) at Ivw EndMon`|`Living status`|
| **Table name** |`HRS-HRS-w4`|`hrs_hrs_w4`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|`996 = Not applicable`|
| **Description** |  |  |



```{r assign_hrs4, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w4_age','HRS.HRS-HRS-w4',
                         variables=list('R4AGEY_E'), missings = TRUE)
```

```{r local_hrs4, echo=F}
HRS_hrs_w4_age <- opal.execute(o,'HRS_hrs_w4_age')

opal.assign.table.tibble(o, 'HRS_hrs_w4','HRS_HD.hrs_hrs_w4',variables=list('living_status'), missings = TRUE)
HRS_hrs_w4 <- opal.execute(o,'HRS_hrs_w4')
HRS_hrs_w4_age <- left_join(HRS_hrs_w4_age,HRS_hrs_w4,by="id")


vbl <- HRS_hrs_w4_age$living_status
kable(Categorical_summary(vbl, missing_values = c(996))[3], caption = "living_status")
kable(Categorical_summary(vbl, missing_values = c(996))[1], caption = "Category")
ggplot(HRS_hrs_w4_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <- HRS_hrs_w4_age$R4AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R4AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_hrs_w4_age, aes(R4AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")+ xlim(20, 100)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`
* `living_status = Dead or Dropout into 996`


**R script:**

```{r harmo_hrs4}
HRS_ds_hrs_w4 <- tibble(id=HRS_hrs_w4_age$id)
HRS_ds_hrs_w4$age <- car::recode(HRS_hrs_w4_age$R4AGEY_E,"NA=999")
HRS_ds_hrs_w4$age[which(HRS_hrs_w4_age$living_status %in% c(1,2))] <- 996

HRS_ds_hrs_w4$age <- labelled(HRS_ds_hrs_w4$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs4, echo=F}
vari <- HRS_ds_hrs_w4$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w4, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")+ xlim(20, 100)
```

#### Validation
```{r crosstabulation_hrs4, echo=F}

```





```{r importOPAL_hrs4, echo=F}

#opal.assign.data(o, 'HRS_ds_hrs_w4', HRS_ds_hrs_w4)
#opal.symbol_import(o,'HRS_ds_hrs_w4', project='_Athlos_Harm_Dataset')
age <- HRS_ds_hrs_w4
save(age, file = "../RData/hrs_w4/age.RData")
rm(age)

HRS_m_ds_hrs_w4 <- HRS_ds_hrs_w4
HRS_m_ds_hrs_w4$age <- car::recode(HRS_m_ds_hrs_w4$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w4', HRS_m_ds_hrs_w4)
#opal.symbol_import(o,'HRS_m_ds_hrs_w4', project='_Athlos_Harm_Dataset')
```






### Wave 5

#### Study-specific variable description



| **Name** |`R5AGEY_E`|`living_status`|
|----------|------------|-|
| **Label** |`W5 R Age (years) at Ivw EndMon`|`Living status`|
| **Table name** |`HRS-HRS-w5`|`hrs_hrs_w5`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|`996 = Not applicable`|
| **Description** |  |  |


```{r assign_hrs5, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w5_age','HRS.HRS-HRS-w5',
                         variables=list('R5AGEY_E'), missings = TRUE)
```

```{r local_hrs5, echo=F}
HRS_hrs_w5_age <- opal.execute(o,'HRS_hrs_w5_age')

opal.assign.table.tibble(o, 'HRS_hrs_w5','HRS_HD.hrs_hrs_w5',variables=list('living_status'), missings = TRUE)
HRS_hrs_w5 <- opal.execute(o,'HRS_hrs_w5')
HRS_hrs_w5_age <- left_join(HRS_hrs_w5_age,HRS_hrs_w5,by="id")


vbl <- HRS_hrs_w5_age$living_status
kable(Categorical_summary(vbl, missing_values = c(996))[3], caption = "living_status")
kable(Categorical_summary(vbl, missing_values = c(996))[1], caption = "Category")
ggplot(HRS_hrs_w5_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <- HRS_hrs_w5_age$R5AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R5AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_hrs_w5_age, aes(R5AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`
* `living_status = Dead or Dropout into 996`


**R script:**

```{r harmo_hrs5}
HRS_ds_hrs_w5 <- tibble(id=HRS_hrs_w5_age$id)
HRS_ds_hrs_w5$age <- car::recode(HRS_hrs_w5_age$R5AGEY_E, "NA=999")
HRS_ds_hrs_w5$age[which(HRS_hrs_w5_age$living_status %in% c(1,2))] <- 996

HRS_ds_hrs_w5$age <- labelled(HRS_ds_hrs_w5$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs5, echo=F}
vari <- HRS_ds_hrs_w5$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w5, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency") + xlim(20, 100)
```

#### Validation
```{r crosstabulation_hrs5, echo=F}

```





```{r importOPAL_hrs5, echo=F}

#opal.assign.data(o, 'HRS_ds_hrs_w5', HRS_ds_hrs_w5)
#opal.symbol_import(o,'HRS_ds_hrs_w5', project='_Athlos_Harm_Dataset')
age <- HRS_ds_hrs_w5
save(age, file = "../RData/hrs_w5/age.RData")
rm(age)

HRS_m_ds_hrs_w5 <- HRS_ds_hrs_w5
HRS_m_ds_hrs_w5$age <- car::recode(HRS_m_ds_hrs_w5$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w5', HRS_m_ds_hrs_w5)
#opal.symbol_import(o,'HRS_m_ds_hrs_w5', project='_Athlos_Harm_Dataset')
```





### Wave 6

#### Study-specific variable description




| **Name** |`R6AGEY_E`|`living_status`|
|----------|------------|-|
| **Label** |`W6 R Age (years) at Ivw EndMon`|`Living status`|
| **Table name** |`HRS-HRS-w6`|`hrs_hrs_w6`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|`996 = Not applicable`|
| **Description** |  |  |



```{r assign_hrs6, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w6_age','HRS.HRS-HRS-w6',
                         variables=list('R6AGEY_E'), missings = TRUE)
```

```{r local_hrs6, echo=F}
HRS_hrs_w6_age <- opal.execute(o,'HRS_hrs_w6_age')

opal.assign.table.tibble(o, 'HRS_hrs_w6','HRS_HD.hrs_hrs_w6',variables=list('living_status'), missings = TRUE)
HRS_hrs_w6 <- opal.execute(o,'HRS_hrs_w6')
HRS_hrs_w6_age <- left_join(HRS_hrs_w6_age,HRS_hrs_w6,by="id")


vbl <- HRS_hrs_w6_age$living_status
kable(Categorical_summary(vbl, missing_values = c(996))[3], caption = "living_status")
kable(Categorical_summary(vbl, missing_values = c(996))[1], caption = "Category")
ggplot(HRS_hrs_w6_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <- HRS_hrs_w6_age$R6AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R6AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_hrs_w6_age, aes(R6AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100)

```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`
* `living_status = Dead or Dropout into 996`

**R script:**

```{r harmo_hrs6}
HRS_ds_hrs_w6 <- tibble(id=HRS_hrs_w6_age$id)
HRS_ds_hrs_w6$age <- car::recode(HRS_hrs_w6_age$R6AGEY_E, "NA=999")
HRS_ds_hrs_w6$age[which(HRS_hrs_w6_age$living_status %in% c(1,2))] <- 996

HRS_ds_hrs_w6$age <- labelled(HRS_ds_hrs_w6$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs6, echo=F}
vari <- HRS_ds_hrs_w6$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w6, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100)
```

#### Validation
```{r crosstabulation_hrs6, echo=F}

```





```{r importOPAL_hrs6, echo=F}

#opal.assign.data(o, 'HRS_ds_hrs_w6', HRS_ds_hrs_w6)
#opal.symbol_import(o,'HRS_ds_hrs_w6', project='_Athlos_Harm_Dataset')
age <- HRS_ds_hrs_w6
save(age, file = "../RData/hrs_w6/age.RData")
rm(age)

HRS_m_ds_hrs_w6 <- HRS_ds_hrs_w6
HRS_m_ds_hrs_w6$age <- car::recode(HRS_m_ds_hrs_w6$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w6', HRS_m_ds_hrs_w6)
#opal.symbol_import(o,'HRS_m_ds_hrs_w6', project='_Athlos_Harm_Dataset')
```






### Wave 7

#### Study-specific variable description


| **Name** |`R7AGEY_E`|`living_status`|
|----------|------------|-|
| **Label** |`W7 R Age (years) at Ivw EndMon`|`Living status`|
| **Table name** |`HRS-HRS-w7`|`hrs_hrs_w7`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|`996 = Not applicable`|
| **Description** |  |  |



```{r assign_hrs7, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w7_age','HRS.HRS-HRS-w7',
                         variables=list('R7AGEY_E'), missings = TRUE)
```

```{r local_hrs7, echo=F}
HRS_hrs_w7_age <- opal.execute(o,'HRS_hrs_w7_age')

opal.assign.table.tibble(o, 'HRS_hrs_w7','HRS_HD.hrs_hrs_w7',variables=list('living_status'), missings = TRUE)
HRS_hrs_w7 <- opal.execute(o,'HRS_hrs_w7')
HRS_hrs_w7_age <- left_join(HRS_hrs_w7_age,HRS_hrs_w7,by="id")


vbl <- HRS_hrs_w7_age$living_status
kable(Categorical_summary(vbl, missing_values = c(996))[3], caption = "living_status")
kable(Categorical_summary(vbl, missing_values = c(996))[1], caption = "Category")
ggplot(HRS_hrs_w7_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <- HRS_hrs_w7_age$R7AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R7AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_hrs_w7_age, aes(R7AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100)
 
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`
* `living_status = Dead or Dropout into 996`


**R script:**

```{r harmo_hrs7}
HRS_ds_hrs_w7 <- tibble(id=HRS_hrs_w7_age$id)
HRS_ds_hrs_w7$age <- car::recode(HRS_hrs_w7_age$R7AGEY_E, "NA=999")
HRS_ds_hrs_w7$age[which(HRS_hrs_w7_age$living_status %in% c(1,2))] <- 996

HRS_ds_hrs_w7$age <- labelled(HRS_ds_hrs_w7$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

```


#### Statistics of the new harmonised variable
```{r descript_hrs7, echo=F}
vari <- HRS_ds_hrs_w7$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w7, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100)

```

#### Validation
```{r crosstabulation_hrs7, echo=F}

```





```{r importOPAL_hrs7, echo=F}

#opal.assign.data(o, 'HRS_ds_hrs_w7', HRS_ds_hrs_w7)
#opal.symbol_import(o,'HRS_ds_hrs_w7', project='_Athlos_Harm_Dataset')
age <- HRS_ds_hrs_w7
save(age, file = "../RData/hrs_w7/age.RData")
rm(age)

HRS_m_ds_hrs_w7 <- HRS_ds_hrs_w7
HRS_m_ds_hrs_w7$age <- car::recode(HRS_m_ds_hrs_w7$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w7', HRS_m_ds_hrs_w7)
#opal.symbol_import(o,'HRS_m_ds_hrs_w7', project='_Athlos_Harm_Dataset')
```






### Wave 8

#### Study-specific variable description



| **Name** |`R8AGEY_E`|`living_status`|
|----------|------------|-|
| **Label** |`W8 R Age (years) at Ivw EndMon`|`Living status`|
| **Table name** |`HRS-HRS-w8`|`hrs_hrs_w8`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|`996 = Not applicable`|
| **Description** |  |  |



```{r assign_hrs8, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w8_age','HRS.HRS-HRS-w8',
                         variables=list('R8AGEY_E'), missings = TRUE)
```

```{r local_hrs8, echo=F}
HRS_hrs_w8_age <- opal.execute(o,'HRS_hrs_w8_age')

opal.assign.table.tibble(o, 'HRS_hrs_w8','HRS_HD.hrs_hrs_w8',variables=list('living_status'), missings = TRUE)
HRS_hrs_w8 <- opal.execute(o,'HRS_hrs_w8')
HRS_hrs_w8_age <- left_join(HRS_hrs_w8_age,HRS_hrs_w8,by="id")


vbl <- HRS_hrs_w8_age$living_status
kable(Categorical_summary(vbl, missing_values = c(996))[3], caption = "living_status")
kable(Categorical_summary(vbl, missing_values = c(996))[1], caption = "Category")
ggplot(HRS_hrs_w8_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <- HRS_hrs_w8_age$R8AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R8AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_hrs_w8_age, aes(R8AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100)

```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`
* `living_status = Dead or Dropout into 996`

**R script:**

```{r harmo_hrs8}
HRS_ds_hrs_w8 <- tibble(id=HRS_hrs_w8_age$id)
HRS_ds_hrs_w8$age <- car::recode(HRS_hrs_w8_age$R8AGEY_E, "NA=999")
HRS_ds_hrs_w8$age[which(HRS_hrs_w8_age$living_status %in% c(1,2))] <- 996

HRS_ds_hrs_w8$age <- labelled(HRS_ds_hrs_w8$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

```


#### Statistics of the new harmonised variable
```{r descript_hrs8, echo=F}
vari <- HRS_ds_hrs_w8$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w8, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100)

```

#### Validation
```{r crosstabulation_hrs8, echo=F}

```





```{r importOPAL_hrs8, echo=F}

#opal.assign.data(o, 'HRS_ds_hrs_w8', HRS_ds_hrs_w8)
#opal.symbol_import(o,'HRS_ds_hrs_w8', project='_Athlos_Harm_Dataset')
age <- HRS_ds_hrs_w8
save(age, file = "../RData/hrs_w8/age.RData")
rm(age)

HRS_m_ds_hrs_w8 <- HRS_ds_hrs_w8
HRS_m_ds_hrs_w8$age <- car::recode(HRS_m_ds_hrs_w8$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w8', HRS_m_ds_hrs_w8)
#opal.symbol_import(o,'HRS_m_ds_hrs_w8', project='_Athlos_Harm_Dataset')
```






### Wave 9

#### Study-specific variable description

| **Name** |`R9AGEY_E`|`living_status`|
|----------|------------|-|
| **Label** |`W9 R Age (years) at Ivw EndMon`|`Living status`|
| **Table name** |`HRS-HRS-w9`|`hrs_hrs_w9`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|`996 = Not applicable`|
| **Description** |  |  |



```{r assign_hrs9, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w9_age','HRS.HRS-HRS-w9',
                         variables=list('R9AGEY_E'), missings = TRUE)
```

```{r local_hrs9, echo=F}
HRS_hrs_w9_age <- opal.execute(o,'HRS_hrs_w9_age')

opal.assign.table.tibble(o, 'HRS_hrs_w9','HRS_HD.hrs_hrs_w9',variables=list('living_status'), missings = TRUE)
HRS_hrs_w9 <- opal.execute(o,'HRS_hrs_w9')
HRS_hrs_w9_age <- left_join(HRS_hrs_w9_age,HRS_hrs_w9,by="id")


vbl <- HRS_hrs_w9_age$living_status
kable(Categorical_summary(vbl, missing_values = c(996))[3], caption = "living_status")
kable(Categorical_summary(vbl, missing_values = c(996))[1], caption = "Category")
ggplot(HRS_hrs_w9_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <- HRS_hrs_w9_age$R9AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R9AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_hrs_w9_age, aes(R9AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`
* `living_status = Dead or Dropout into 996`

**R script:**

```{r harmo_hrs9}
HRS_ds_hrs_w9 <- tibble(id=HRS_hrs_w9_age$id)
HRS_ds_hrs_w9$age <- car::recode(HRS_hrs_w9_age$R9AGEY_E, "NA=999")
HRS_ds_hrs_w9$age[which(HRS_hrs_w9_age$living_status %in% c(1,2))] <- 996

HRS_ds_hrs_w9$age <- labelled(HRS_ds_hrs_w9$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs9, echo=F}
vari <- HRS_ds_hrs_w9$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w9, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100)
```

#### Validation
```{r crosstabulation_hrs9, echo=F}

```





```{r importOPAL_hrs9, echo=F}

#opal.assign.data(o, 'HRS_ds_hrs_w9', HRS_ds_hrs_w9)
#opal.symbol_import(o,'HRS_ds_hrs_w9', project='_Athlos_Harm_Dataset')
age <- HRS_ds_hrs_w9
save(age, file = "../RData/hrs_w9/age.RData")
rm(age)

HRS_m_ds_hrs_w9 <- HRS_ds_hrs_w9
HRS_m_ds_hrs_w9$age <- car::recode(HRS_m_ds_hrs_w9$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w9', HRS_m_ds_hrs_w9)
#opal.symbol_import(o,'HRS_m_ds_hrs_w9', project='_Athlos_Harm_Dataset')
```






### Wave 10

#### Study-specific variable description


| **Name** |`R10AGEY_E`|`living_status`|
|----------|------------|-|
| **Label** |`W10 R Age (years) at Ivw EndMon`|`Living status`|
| **Table name** |`HRS-HRS-w10`|`hrs_hrs_w10`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|`996 = Not applicable`|
| **Description** |  |  |



```{r assign_hrs10, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w10_age','HRS.HRS-HRS-w10',
                         variables=list('R10AGEY_E'), missings = TRUE)
```

```{r local_hrs10, echo=F}
HRS_hrs_w10_age <- opal.execute(o,'HRS_hrs_w10_age')

opal.assign.table.tibble(o, 'HRS_hrs_w10','HRS_HD.hrs_hrs_w10',variables=list('living_status'), missings = TRUE)
HRS_hrs_w10 <- opal.execute(o,'HRS_hrs_w10')
HRS_hrs_w10_age <- left_join(HRS_hrs_w10_age,HRS_hrs_w10,by="id")


vbl <- HRS_hrs_w10_age$living_status
kable(Categorical_summary(vbl, missing_values = c(996))[3], caption = "living_status")
kable(Categorical_summary(vbl, missing_values = c(996))[1], caption = "Category")
ggplot(HRS_hrs_w10_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <- HRS_hrs_w10_age$R10AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R10AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_hrs_w10_age, aes(R10AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`
* `living_status = Dead or Dropout into 996`

**R script:**

```{r harmo_hrs10}
HRS_ds_hrs_w10 <- tibble(id=HRS_hrs_w10_age$id)
HRS_ds_hrs_w10$age <- car::recode(HRS_hrs_w10_age$R10AGEY_E, "NA=999")
HRS_ds_hrs_w10$age[which(HRS_hrs_w10_age$living_status %in% c(1,2))] <- 996

HRS_ds_hrs_w10$age <- labelled(HRS_ds_hrs_w10$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs10, echo=F}
vari <- HRS_ds_hrs_w10$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w10, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100)
```

#### Validation
```{r crosstabulation_hrs10, echo=F}

```





```{r importOPAL_hrs10, echo=F}

#opal.assign.data(o, 'HRS_ds_hrs_w10', HRS_ds_hrs_w10)
#opal.symbol_import(o,'HRS_ds_hrs_w10', project='_Athlos_Harm_Dataset')
age <- HRS_ds_hrs_w10
save(age, file = "../RData/hrs_w10/age.RData")
rm(age)

HRS_m_ds_hrs_w10 <- HRS_ds_hrs_w10
HRS_m_ds_hrs_w10$age <- car::recode(HRS_m_ds_hrs_w10$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w10', HRS_m_ds_hrs_w10)
#opal.symbol_import(o,'HRS_m_ds_hrs_w10', project='_Athlos_Harm_Dataset')
```






### Wave 11

#### Study-specific variable description



| **Name** |`R11AGEY_E`|`living_status`|
|----------|------------|-|
| **Label** |`W11 R Age (years) at Ivw EndMon`|`Living status`|
| **Table name** |`HRS-HRS-w11`|`hrs_hrs_w11`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|`996 = Not applicable`|
| **Description** |  |  |


```{r assign_hrs11, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w11_age','HRS.HRS-HRS-w11',
                         variables=list('R11AGEY_E'), missings = TRUE)
```

```{r local_hrs11, echo=F}
HRS_hrs_w11_age <- opal.execute(o,'HRS_hrs_w11_age')

opal.assign.table.tibble(o, 'HRS_hrs_w11','HRS_HD.hrs_hrs_w11',variables=list('living_status'), missings = TRUE)
HRS_hrs_w11 <- opal.execute(o,'HRS_hrs_w11')
HRS_hrs_w11_age <- left_join(HRS_hrs_w11_age,HRS_hrs_w11,by="id")


vbl <- HRS_hrs_w11_age$living_status
kable(Categorical_summary(vbl, missing_values = c(996))[3], caption = "living_status")
kable(Categorical_summary(vbl, missing_values = c(996))[1], caption = "Category")
ggplot(HRS_hrs_w11_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <- HRS_hrs_w11_age$R11AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R11AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_hrs_w11_age, aes(R11AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`
* `living_status = Dead or Dropout into 996`

**R script:**

```{r harmo_hrs11}
HRS_ds_hrs_w11 <- tibble(id=HRS_hrs_w11_age$id)
HRS_ds_hrs_w11$age <- car::recode(HRS_hrs_w11_age$R11AGEY_E, "NA=999")
HRS_ds_hrs_w11$age[which(HRS_hrs_w11_age$living_status %in% c(1,2))] <- 996

HRS_ds_hrs_w11$age <- labelled(HRS_ds_hrs_w11$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs11, echo=F}
vari <- HRS_ds_hrs_w11$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w11, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100)
```

#### Validation
```{r crosstabulation_hrs11, echo=F}

```





```{r importOPAL_hrs11, echo=F}

#opal.assign.data(o, 'HRS_ds_hrs_w11', HRS_ds_hrs_w11)
#opal.symbol_import(o,'HRS_ds_hrs_w11', project='_Athlos_Harm_Dataset')
age <- HRS_ds_hrs_w11
save(age, file = "../RData/hrs_w11/age.RData")
rm(age)

HRS_m_ds_hrs_w11 <- HRS_ds_hrs_w11
HRS_m_ds_hrs_w11$age <- car::recode(HRS_m_ds_hrs_w11$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w11', HRS_m_ds_hrs_w11)
#opal.symbol_import(o,'HRS_m_ds_hrs_w11', project='_Athlos_Harm_Dataset')
```





## AHEAD

### Wave 2 

#### Study-specific variable description



| **Name** |`R2AGEY_E`|
|----------|------------|
| **Label** |`W2 R Age (years) at Ivw EndMon`|
| **Table name** |`HRS-AHEAD-w2`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign_ahead2, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w2_age','HRS.HRS-AHEAD-w2',
                         variables=list('R2AGEY_E'), missings = TRUE)
```

```{r local_ahead2, echo=F}
HRS_ahead_w2_age <- opal.execute(o,'HRS_ahead_w2_age')


vari <- HRS_ahead_w2_age$R2AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R2AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_ahead_w2_age, aes(R2AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_ahead2}
HRS_ds_ahead_w2 <- tibble(id=HRS_ahead_w2_age$id)
HRS_ds_ahead_w2$age <- car::recode(HRS_ahead_w2_age$R2AGEY_E, "NA=999")

HRS_ds_ahead_w2$age <- labelled(HRS_ds_ahead_w2$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead2, echo=F}
vari <- HRS_ds_ahead_w2$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_ahead_w2, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100)

```

#### Validation
```{r crosstabulation_ahead2, echo=F}

```





```{r importOPAL_ahead2, echo=F}

#opal.assign.data(o, 'HRS_ds_ahead_w2', HRS_ds_ahead_w2)
#opal.symbol_import(o,'HRS_ds_ahead_w2', project='_Athlos_Harm_Dataset')
age <- HRS_ds_ahead_w2
save(age, file = "../RData/ahead_w2/age.RData")
rm(age)

HRS_m_ds_ahead_w2 <- HRS_ds_ahead_w2
HRS_m_ds_ahead_w2$age <- car::recode(HRS_m_ds_ahead_w2$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w2', HRS_m_ds_ahead_w2)
#opal.symbol_import(o,'HRS_m_ds_ahead_w2', project='_Athlos_Harm_Dataset')
```








### Wave 3 

#### Study-specific variable description

| **Name** |`R3AGEY_E`|`living_status`|
|----------|------------|-|
| **Label** |`W3 R Age (years) at Ivw EndMon`|`Living status`|
| **Table name** |`HRS-AHEAD-w3`|`hrs_ahead_w3`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|`996 = Not applicable`|
| **Description** |  |  |



```{r assign_ahead3, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w3_age','HRS.HRS-AHEAD-w3',
                         variables=list('R3AGEY_E'), missings = TRUE)
```

```{r local_ahead3, echo=F}
HRS_ahead_w3_age <- opal.execute(o,'HRS_ahead_w3_age')

opal.assign.table.tibble(o, 'HRS_ahead_w3','HRS_HD.hrs_ahead_w3',variables=list('living_status'), missings = TRUE)
HRS_ahead_w3 <- opal.execute(o,'HRS_ahead_w3')
HRS_ahead_w3_age <- left_join(HRS_ahead_w3_age,HRS_ahead_w3,by="id")


vbl <- HRS_ahead_w3_age$living_status
kable(Categorical_summary(vbl, missing_values = c(996))[3], caption = "living_status")
kable(Categorical_summary(vbl, missing_values = c(996))[1], caption = "Category")
ggplot(HRS_ahead_w3_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <- HRS_ahead_w3_age$R3AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R3AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_ahead_w3_age, aes(R3AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100)

```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`
* `living_status = Dead or Dropout into 996`

**R script:**

```{r harmo_ahead3}
HRS_ds_ahead_w3 <- tibble(id=HRS_ahead_w3_age$id)
HRS_ds_ahead_w3$age <- car::recode(HRS_ahead_w3_age$R3AGEY_E, "NA=999")
HRS_ds_ahead_w3$age[which(HRS_ahead_w3_age$living_status %in% c(1,2))] <- 996

HRS_ds_ahead_w3$age <- labelled(HRS_ds_ahead_w3$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead3, echo=F}
vari <- HRS_ds_ahead_w3$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_ahead_w3, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100)
```

#### Validation
```{r crosstabulation_ahead3, echo=F}

```





```{r importOPAL_ahead3, echo=F}

#opal.assign.data(o, 'HRS_ds_ahead_w3', HRS_ds_ahead_w3)
#opal.symbol_import(o,'HRS_ds_ahead_w3', project='_Athlos_Harm_Dataset')
age <- HRS_ds_ahead_w3
save(age, file = "../RData/ahead_w3/age.RData")
rm(age)

HRS_m_ds_ahead_w3 <- HRS_ds_ahead_w3
HRS_m_ds_ahead_w3$age <- car::recode(HRS_m_ds_ahead_w3$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w3', HRS_m_ds_ahead_w3)
#opal.symbol_import(o,'HRS_m_ds_ahead_w3', project='_Athlos_Harm_Dataset')
```







### Wave 4 

#### Study-specific variable description



| **Name** |`R4AGEY_E`|`living_status`|
|----------|------------|-|
| **Label** |`W4 R Age (years) at Ivw EndMon`|`Living status`|
| **Table name** |`HRS-AHEAD-w4`|`hrs_ahead_w4`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|`996 = Not applicable`|
| **Description** |  |  |


```{r assign_ahead4, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w4_age','HRS.HRS-AHEAD-w4',
                         variables=list('R4AGEY_E'), missings = TRUE)
```

```{r local_ahead4, echo=F}
HRS_ahead_w4_age <- opal.execute(o,'HRS_ahead_w4_age')

opal.assign.table.tibble(o, 'HRS_ahead_w4','HRS_HD.hrs_ahead_w4',variables=list('living_status'), missings = TRUE)
HRS_ahead_w4 <- opal.execute(o,'HRS_ahead_w4')
HRS_ahead_w4_age <- left_join(HRS_ahead_w4_age,HRS_ahead_w4,by="id")


vbl <- HRS_ahead_w4_age$living_status
kable(Categorical_summary(vbl, missing_values = c(996))[3], caption = "living_status")
kable(Categorical_summary(vbl, missing_values = c(996))[1], caption = "Category")
ggplot(HRS_ahead_w4_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <- HRS_ahead_w4_age$R4AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R4AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_ahead_w4_age, aes(R4AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`
* `living_status = Dead or Dropout into 996`

**R script:**

```{r harmo_ahead4}
HRS_ds_ahead_w4 <- tibble(id=HRS_ahead_w4_age$id)
HRS_ds_ahead_w4$age <- car::recode(HRS_ahead_w4_age$R4AGEY_E, "NA=999")
HRS_ds_ahead_w4$age[which(HRS_ahead_w4_age$living_status %in% c(1,2))] <- 996

HRS_ds_ahead_w4$age <- labelled(HRS_ds_ahead_w4$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead4, echo=F}
vari <- HRS_ds_ahead_w4$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_ahead_w4, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100)

```

#### Validation
```{r crosstabulation_ahead4, echo=F}

```





```{r importOPAL_ahead4, echo=F}

#opal.assign.data(o, 'HRS_ds_ahead_w4', HRS_ds_ahead_w4)
#opal.symbol_import(o,'HRS_ds_ahead_w4', project='_Athlos_Harm_Dataset')
age <- HRS_ds_ahead_w4
save(age, file = "../RData/ahead_w4/age.RData")
rm(age)

HRS_m_ds_ahead_w4 <- HRS_ds_ahead_w4
HRS_m_ds_ahead_w4$age <- car::recode(HRS_m_ds_ahead_w4$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w4', HRS_m_ds_ahead_w4)
#opal.symbol_import(o,'HRS_m_ds_ahead_w4', project='_Athlos_Harm_Dataset')
```






### Wave 5 

#### Study-specific variable description



| **Name** |`R5AGEY_E`|`living_status`|
|----------|------------|-|
| **Label** |`W5 R Age (years) at Ivw EndMon`|`Living status`|
| **Table name** |`HRS-AHEAD-w5`|`hrs_ahead_w5`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|`996 = Not applicable`|
| **Description** |  |  |



```{r assign_ahead5, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w5_age','HRS.HRS-AHEAD-w5',
                         variables=list('R5AGEY_E'), missings = TRUE)
```

```{r local_ahead5, echo=F}
HRS_ahead_w5_age <- opal.execute(o,'HRS_ahead_w5_age')

opal.assign.table.tibble(o, 'HRS_ahead_w5','HRS_HD.hrs_ahead_w5',variables=list('living_status'), missings = TRUE)
HRS_ahead_w5 <- opal.execute(o,'HRS_ahead_w5')
HRS_ahead_w5_age <- left_join(HRS_ahead_w5_age,HRS_ahead_w5,by="id")


vbl <- HRS_ahead_w5_age$living_status
kable(Categorical_summary(vbl, missing_values = c(996))[3], caption = "living_status")
kable(Categorical_summary(vbl, missing_values = c(996))[1], caption = "Category")
ggplot(HRS_ahead_w5_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <- HRS_ahead_w5_age$R5AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R5AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_ahead_w5_age, aes(R5AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100)

```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`
* `living_status = Dead or Dropout into 996`

**R script:**

```{r harmo_ahead5}
HRS_ds_ahead_w5 <- tibble(id=HRS_ahead_w5_age$id)
HRS_ds_ahead_w5$age <- car::recode(HRS_ahead_w5_age$R5AGEY_E, "NA=999")
HRS_ds_ahead_w5$age[which(HRS_ahead_w5_age$living_status %in% c(1,2))] <- 996

HRS_ds_ahead_w5$age <- labelled(HRS_ds_ahead_w5$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead5, echo=F}
vari <- HRS_ds_ahead_w5$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_ahead_w5, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100)
```

#### Validation
```{r crosstabulation_ahead5, echo=F}

```





```{r importOPAL_ahead5, echo=F}

#opal.assign.data(o, 'HRS_ds_ahead_w5', HRS_ds_ahead_w5)
#opal.symbol_import(o,'HRS_ds_ahead_w5', project='_Athlos_Harm_Dataset')
age <- HRS_ds_ahead_w5
save(age, file = "../RData/ahead_w5/age.RData")
rm(age)

HRS_m_ds_ahead_w5 <- HRS_ds_ahead_w5
HRS_m_ds_ahead_w5$age <- car::recode(HRS_m_ds_ahead_w5$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w5', HRS_m_ds_ahead_w5)
#opal.symbol_import(o,'HRS_m_ds_ahead_w5', project='_Athlos_Harm_Dataset')
```








### Wave 6 

#### Study-specific variable description



| **Name** |`R6AGEY_E`|`living_status`|
|----------|------------|-|
| **Label** |`W6 R Age (years) at Ivw EndMon`|`Living status`|
| **Table name** |`HRS-AHEAD-w6`|`hrs_ahead_w6`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|`996 = Not applicable`|
| **Description** |  |  |



```{r assign_ahead6, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w6_age','HRS.HRS-AHEAD-w6',
                         variables=list('R6AGEY_E'), missings = TRUE)
```

```{r local_ahead6, echo=F}
HRS_ahead_w6_age <- opal.execute(o,'HRS_ahead_w6_age')

opal.assign.table.tibble(o, 'HRS_ahead_w6','HRS_HD.hrs_ahead_w6',variables=list('living_status'), missings = TRUE)
HRS_ahead_w6 <- opal.execute(o,'HRS_ahead_w6')
HRS_ahead_w6_age <- left_join(HRS_ahead_w6_age,HRS_ahead_w6,by="id")


vbl <- HRS_ahead_w6_age$living_status
kable(Categorical_summary(vbl, missing_values = c(996))[3], caption = "living_status")
kable(Categorical_summary(vbl, missing_values = c(996))[1], caption = "Category")
ggplot(HRS_ahead_w6_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <- HRS_ahead_w6_age$R6AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R6AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_ahead_w6_age, aes(R6AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100)

```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`
* `living_status = Dead or Dropout into 996`

**R script:**

```{r harmo_ahead6}
HRS_ds_ahead_w6 <- tibble(id=HRS_ahead_w6_age$id)
HRS_ds_ahead_w6$age <- car::recode(HRS_ahead_w6_age$R6AGEY_E, "NA=999")
HRS_ds_ahead_w6$age[which(HRS_ahead_w6_age$living_status %in% c(1,2))] <- 996

HRS_ds_ahead_w6$age <- labelled(HRS_ds_ahead_w6$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead6, echo=F}
vari <- HRS_ds_ahead_w6$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_ahead_w6, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100)
```

#### Validation
```{r crosstabulation_ahead6, echo=F}

```





```{r importOPAL_ahead6, echo=F}

#opal.assign.data(o, 'HRS_ds_ahead_w6', HRS_ds_ahead_w6)
#opal.symbol_import(o,'HRS_ds_ahead_w6', project='_Athlos_Harm_Dataset')
age <- HRS_ds_ahead_w6
save(age, file = "../RData/ahead_w6/age.RData")
rm(age)

HRS_m_ds_ahead_w6 <- HRS_ds_ahead_w6
HRS_m_ds_ahead_w6$age <- car::recode(HRS_m_ds_ahead_w6$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w6', HRS_m_ds_ahead_w6)
#opal.symbol_import(o,'HRS_m_ds_ahead_w6', project='_Athlos_Harm_Dataset')
```







### Wave 7 

#### Study-specific variable description



| **Name** |`R7AGEY_E`|`living_status`|
|----------|------------|-|
| **Label** |`W7 R Age (years) at Ivw EndMon`|`Living status`|
| **Table name** |`HRS-AHEAD-w7`|`hrs_ahead_w7`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|`996 = Not applicable`|
| **Description** |  |  |


```{r assign_ahead7, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w7_age','HRS.HRS-AHEAD-w7',
                         variables=list('R7AGEY_E'), missings = TRUE)
```

```{r local_ahead7, echo=F}
HRS_ahead_w7_age <- opal.execute(o,'HRS_ahead_w7_age')

opal.assign.table.tibble(o, 'HRS_ahead_w7','HRS_HD.hrs_ahead_w7',variables=list('living_status'), missings = TRUE)
HRS_ahead_w7 <- opal.execute(o,'HRS_ahead_w7')
HRS_ahead_w7_age <- left_join(HRS_ahead_w7_age,HRS_ahead_w7,by="id")


vbl <- HRS_ahead_w7_age$living_status
kable(Categorical_summary(vbl, missing_values = c(996))[3], caption = "living_status")
kable(Categorical_summary(vbl, missing_values = c(996))[1], caption = "Category")
ggplot(HRS_ahead_w7_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <- HRS_ahead_w7_age$R7AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R7AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_ahead_w7_age, aes(R7AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`
* `living_status = Dead or Dropout into 996`

**R script:**

```{r harmo_ahead7}
HRS_ds_ahead_w7 <- tibble(id=HRS_ahead_w7_age$id)
HRS_ds_ahead_w7$age <- car::recode(HRS_ahead_w7_age$R7AGEY_E, "NA=999")
HRS_ds_ahead_w7$age[which(HRS_ahead_w7_age$living_status %in% c(1,2))] <- 996

HRS_ds_ahead_w7$age <- labelled(HRS_ds_ahead_w7$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead7, echo=F}
vari <- HRS_ds_ahead_w7$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_ahead_w7, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100)
```

#### Validation
```{r crosstabulation_ahead7, echo=F}

```





```{r importOPAL_ahead7, echo=F}

#opal.assign.data(o, 'HRS_ds_ahead_w7', HRS_ds_ahead_w7)
#opal.symbol_import(o,'HRS_ds_ahead_w7', project='_Athlos_Harm_Dataset')
age <- HRS_ds_ahead_w7
save(age, file = "../RData/ahead_w7/age.RData")
rm(age)

HRS_m_ds_ahead_w7 <- HRS_ds_ahead_w7
HRS_m_ds_ahead_w7$age <- car::recode(HRS_m_ds_ahead_w7$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w7', HRS_m_ds_ahead_w7)
#opal.symbol_import(o,'HRS_m_ds_ahead_w7', project='_Athlos_Harm_Dataset')
```






### Wave 8 

#### Study-specific variable description


| **Name** |`R8AGEY_E`|`living_status`|
|----------|------------|-|
| **Label** |`W8 R Age (years) at Ivw EndMon`|`Living status`|
| **Table name** |`HRS-AHEAD-w8`|`hrs_ahead_w8`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|`996 = Not applicable`|
| **Description** |  |  |



```{r assign_ahead8, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w8_age','HRS.HRS-AHEAD-w8',
                         variables=list('R8AGEY_E'), missings = TRUE)
```

```{r local_ahead8, echo=F}
HRS_ahead_w8_age <- opal.execute(o,'HRS_ahead_w8_age')

opal.assign.table.tibble(o, 'HRS_ahead_w8','HRS_HD.hrs_ahead_w8',variables=list('living_status'), missings = TRUE)
HRS_ahead_w8 <- opal.execute(o,'HRS_ahead_w8')
HRS_ahead_w8_age <- left_join(HRS_ahead_w8_age,HRS_ahead_w8,by="id")


vbl <- HRS_ahead_w8_age$living_status
kable(Categorical_summary(vbl, missing_values = c(996))[3], caption = "living_status")
kable(Categorical_summary(vbl, missing_values = c(996))[1], caption = "Category")
ggplot(HRS_ahead_w8_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <- HRS_ahead_w8_age$R8AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R8AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_ahead_w8_age, aes(R8AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`
* `living_status = Dead or Dropout into 996`

**R script:**

```{r harmo_ahead8}
HRS_ds_ahead_w8 <- tibble(id=HRS_ahead_w8_age$id)
HRS_ds_ahead_w8$age <- car::recode(HRS_ahead_w8_age$R8AGEY_E, "NA=999")
HRS_ds_ahead_w8$age[which(HRS_ahead_w8_age$living_status %in% c(1,2))] <- 996

HRS_ds_ahead_w8$age <- labelled(HRS_ds_ahead_w8$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead8, echo=F}
vari <- HRS_ds_ahead_w8$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_ahead_w8, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100)
```

#### Validation
```{r crosstabulation_ahead8, echo=F}

```





```{r importOPAL_ahead8, echo=F}

#opal.assign.data(o, 'HRS_ds_ahead_w8', HRS_ds_ahead_w8)
#opal.symbol_import(o,'HRS_ds_ahead_w8', project='_Athlos_Harm_Dataset')
age <- HRS_ds_ahead_w8
save(age, file = "../RData/ahead_w8/age.RData")
rm(age)

HRS_m_ds_ahead_w8 <- HRS_ds_ahead_w8
HRS_m_ds_ahead_w8$age <- car::recode(HRS_m_ds_ahead_w8$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w8', HRS_m_ds_ahead_w8)
#opal.symbol_import(o,'HRS_m_ds_ahead_w8', project='_Athlos_Harm_Dataset')
```






### Wave 9 

#### Study-specific variable description


| **Name** |`R9AGEY_E`|`living_status`|
|----------|------------|-|
| **Label** |`W9 R Age (years) at Ivw EndMon`|`Living status`|
| **Table name** |`HRS-AHEAD-w9`|`hrs_ahead_w9`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|`996 = Not applicable`|
| **Description** |  |  |



```{r assign_ahead9, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w9_age','HRS.HRS-AHEAD-w9',
                         variables=list('R9AGEY_E'), missings = TRUE)
```

```{r local_ahead9, echo=F}
HRS_ahead_w9_age <- opal.execute(o,'HRS_ahead_w9_age')

opal.assign.table.tibble(o, 'HRS_ahead_w9','HRS_HD.hrs_ahead_w9',variables=list('living_status'), missings = TRUE)
HRS_ahead_w9 <- opal.execute(o,'HRS_ahead_w9')
HRS_ahead_w9_age <- left_join(HRS_ahead_w9_age,HRS_ahead_w9,by="id")


vbl <- HRS_ahead_w9_age$living_status
kable(Categorical_summary(vbl, missing_values = c(996))[3], caption = "living_status")
kable(Categorical_summary(vbl, missing_values = c(996))[1], caption = "Category")
ggplot(HRS_ahead_w9_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <- HRS_ahead_w9_age$R9AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R9AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_ahead_w9_age, aes(R9AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100)

```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`
* `living_status = Dead or Dropout into 996`

**R script:**

```{r harmo_ahead9}
HRS_ds_ahead_w9 <- tibble(id=HRS_ahead_w9_age$id)
HRS_ds_ahead_w9$age <- car::recode(HRS_ahead_w9_age$R9AGEY_E, "NA=999")
HRS_ds_ahead_w9$age[which(HRS_ahead_w9_age$living_status %in% c(1,2))] <- 996

HRS_ds_ahead_w9$age <- labelled(HRS_ds_ahead_w9$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead9, echo=F}
vari <- HRS_ds_ahead_w9$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_ahead_w9, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100)

```

#### Validation
```{r crosstabulation_ahead9, echo=F}

```





```{r importOPAL_ahead9, echo=F}

#opal.assign.data(o, 'HRS_ds_ahead_w9', HRS_ds_ahead_w9)
#opal.symbol_import(o,'HRS_ds_ahead_w9', project='_Athlos_Harm_Dataset')
age <- HRS_ds_ahead_w9
save(age, file = "../RData/ahead_w9/age.RData")
rm(age)

HRS_m_ds_ahead_w9 <- HRS_ds_ahead_w9
HRS_m_ds_ahead_w9$age <- car::recode(HRS_m_ds_ahead_w9$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w9', HRS_m_ds_ahead_w9)
#opal.symbol_import(o,'HRS_m_ds_ahead_w9', project='_Athlos_Harm_Dataset')
```







### Wave 10 

#### Study-specific variable description



| **Name** |`R10AGEY_E`|`living_status`|
|----------|------------|-|
| **Label** |`W10 R Age (years) at Ivw EndMon`|`Living status`|
| **Table name** |`HRS-AHEAD-w10`|`hrs_ahead_w10`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|`996 = Not applicable`|
| **Description** |  |  |



```{r assign_ahead10, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w10_age','HRS.HRS-AHEAD-w10',
                         variables=list('R10AGEY_E'), missings = TRUE)
```

```{r local_ahead10, echo=F}
HRS_ahead_w10_age <- opal.execute(o,'HRS_ahead_w10_age')

opal.assign.table.tibble(o, 'HRS_ahead_w10','HRS_HD.hrs_ahead_w10',variables=list('living_status'), missings = TRUE)
HRS_ahead_w10 <- opal.execute(o,'HRS_ahead_w10')
HRS_ahead_w10_age <- left_join(HRS_ahead_w10_age,HRS_ahead_w10,by="id")


vbl <- HRS_ahead_w10_age$living_status
kable(Categorical_summary(vbl, missing_values = c(996))[3], caption = "living_status")
kable(Categorical_summary(vbl, missing_values = c(996))[1], caption = "Category")
ggplot(HRS_ahead_w10_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <- HRS_ahead_w10_age$R10AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R10AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_ahead_w10_age, aes(R10AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`
* `living_status = Dead or Dropout into 996`

**R script:**

```{r harmo_ahead10}
HRS_ds_ahead_w10 <- tibble(id=HRS_ahead_w10_age$id)
HRS_ds_ahead_w10$age <- car::recode(HRS_ahead_w10_age$R10AGEY_E, "NA=999")
HRS_ds_ahead_w10$age[which(HRS_ahead_w10_age$living_status %in% c(1,2))] <- 996

HRS_ds_ahead_w10$age <- labelled(HRS_ds_ahead_w10$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead10, echo=F}
vari <- HRS_ds_ahead_w10$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_ahead_w10, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100)

```

#### Validation
```{r crosstabulation_ahead10, echo=F}

```





```{r importOPAL_ahead10, echo=F}

#opal.assign.data(o, 'HRS_ds_ahead_w10', HRS_ds_ahead_w10)
#opal.symbol_import(o,'HRS_ds_ahead_w10', project='_Athlos_Harm_Dataset')
age <- HRS_ds_ahead_w10
save(age, file = "../RData/ahead_w10/age.RData")
rm(age)

HRS_m_ds_ahead_w10 <- HRS_ds_ahead_w10
HRS_m_ds_ahead_w10$age <- car::recode(HRS_m_ds_ahead_w10$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w10', HRS_m_ds_ahead_w10)
#opal.symbol_import(o,'HRS_m_ds_ahead_w10', project='_Athlos_Harm_Dataset')
```






### Wave 11 

#### Study-specific variable description

| **Name** |`R11AGEY_E`|`living_status`|
|----------|------------|-|
| **Label** |`W11 R Age (years) at Ivw EndMon`|`Living status`|
| **Table name** |`HRS-AHEAD-w11`|`hrs_ahead_w11`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|`996 = Not applicable`|
| **Description** |  |  |



```{r assign_ahead11, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w11_age','HRS.HRS-AHEAD-w11',
                         variables=list('R11AGEY_E'), missings = TRUE)
```

```{r local_ahead11, echo=F}
HRS_ahead_w11_age <- opal.execute(o,'HRS_ahead_w11_age')

opal.assign.table.tibble(o, 'HRS_ahead_w11','HRS_HD.hrs_ahead_w11',variables=list('living_status'), missings = TRUE)
HRS_ahead_w11 <- opal.execute(o,'HRS_ahead_w11')
HRS_ahead_w11_age <- left_join(HRS_ahead_w11_age,HRS_ahead_w11,by="id")


vbl <- HRS_ahead_w11_age$living_status
kable(Categorical_summary(vbl, missing_values = c(996))[3], caption = "living_status")
kable(Categorical_summary(vbl, missing_values = c(996))[1], caption = "Category")
ggplot(HRS_ahead_w11_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <- HRS_ahead_w11_age$R11AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R11AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_ahead_w11_age, aes(R11AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100)

```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`
* `living_status = Dead or Dropout into 996`

**R script:**

```{r harmo_ahead11}
HRS_ds_ahead_w11 <- tibble(id=HRS_ahead_w11_age$id)
HRS_ds_ahead_w11$age <- car::recode(HRS_ahead_w11_age$R11AGEY_E, "NA=999")
HRS_ds_ahead_w11$age[which(HRS_ahead_w11_age$living_status %in% c(1,2))] <- 996

HRS_ds_ahead_w11$age <- labelled(HRS_ds_ahead_w11$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead11, echo=F}
vari <- HRS_ds_ahead_w11$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_ahead_w11, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 100)

```

#### Validation
```{r crosstabulation_ahead11, echo=F}
```





```{r importOPAL_ahead11, echo=F}

#opal.assign.data(o, 'HRS_ds_ahead_w11', HRS_ds_ahead_w11)
#opal.symbol_import(o,'HRS_ds_ahead_w11', project='_Athlos_Harm_Dataset')
age <- HRS_ds_ahead_w11
save(age, file = "../RData/ahead_w11/age.RData")
rm(age)

HRS_m_ds_ahead_w11 <- HRS_ds_ahead_w11
HRS_m_ds_ahead_w11$age <- car::recode(HRS_m_ds_ahead_w11$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w11', HRS_m_ds_ahead_w11)
#opal.symbol_import(o,'HRS_m_ds_ahead_w11', project='_Athlos_Harm_Dataset')
```





## CODA

### Wave 4 

#### Study-specific variable description


| **Name** |`R4AGEY_E`|
|----------|------------|
| **Label** |`W4 R Age (years) at Ivw EndMon`|
| **Table name** |`HRS-CODA-w4`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign_coda4, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w4_age','HRS.HRS-CODA-w4',
                         variables=list('R4AGEY_E'), missings = TRUE)
```

```{r local_coda4, echo=F}
HRS_coda_w4_age <- opal.execute(o,'HRS_coda_w4_age')


vari <- HRS_coda_w4_age$R4AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R4AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_coda_w4_age, aes(R4AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(40, 80)

```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_coda4}
HRS_ds_coda_w4 <- tibble(id=HRS_coda_w4_age$id)
HRS_ds_coda_w4$age <- car::recode(HRS_coda_w4_age$R4AGEY_E, "NA=999")

HRS_ds_coda_w4$age <- labelled(HRS_ds_coda_w4$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda4, echo=F}
vari <- HRS_ds_coda_w4$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_coda_w4, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(40, 80)

```

#### Validation
```{r crosstabulation_coda4, echo=F}

```





```{r importOPAL_coda4, echo=F}

#opal.assign.data(o, 'HRS_ds_coda_w4', HRS_ds_coda_w4)
#opal.symbol_import(o,'HRS_ds_coda_w4', project='_Athlos_Harm_Dataset')
age <- HRS_ds_coda_w4
save(age, file = "../RData/coda_w4/age.RData")
rm(age)

HRS_m_ds_coda_w4 <- HRS_ds_coda_w4
HRS_m_ds_coda_w4$age <- car::recode(HRS_m_ds_coda_w4$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_coda_w4', HRS_m_ds_coda_w4)
#opal.symbol_import(o,'HRS_m_ds_coda_w4', project='_Athlos_Harm_Dataset')
```







### Wave 5 

#### Study-specific variable description


| **Name** |`R5AGEY_E`|`living_status`|
|----------|------------|-|
| **Label** |`W5 R Age (years) at Ivw EndMon`|`Living status`|
| **Table name** |`HRS-CODA-w5`|`hrs_coda_w5`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|`996 = Not applicable`|
| **Description** |  |  |



```{r assign_coda5, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w5_age','HRS.HRS-CODA-w5',
                         variables=list('R5AGEY_E'), missings = TRUE)
```

```{r local_coda5, echo=F}
HRS_coda_w5_age <- opal.execute(o,'HRS_coda_w5_age')

opal.assign.table.tibble(o, 'HRS_coda_w5','HRS_HD.hrs_coda_w5',variables=list('living_status'), missings = TRUE)
HRS_coda_w5 <- opal.execute(o,'HRS_coda_w5')
HRS_coda_w5_age <- left_join(HRS_coda_w5_age,HRS_coda_w5,by="id")


vbl <- HRS_coda_w5_age$living_status
kable(Categorical_summary(vbl, missing_values = c(996))[3], caption = "living_status")
kable(Categorical_summary(vbl, missing_values = c(996))[1], caption = "Category")
ggplot(HRS_coda_w5_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <- HRS_coda_w5_age$R5AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R5AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_coda_w5_age, aes(R5AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(40, 80)

```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`
* `living_status = Dead or Dropout into 996`

**R script:**

```{r harmo_coda5}
HRS_ds_coda_w5 <- tibble(id=HRS_coda_w5_age$id)
HRS_ds_coda_w5$age <- car::recode(HRS_coda_w5_age$R5AGEY_E, "NA=999")
HRS_ds_coda_w5$age[which(HRS_coda_w5_age$living_status %in% c(1,2))] <- 996

HRS_ds_coda_w5$age <- labelled(HRS_ds_coda_w5$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

```


#### Statistics of the new harmonised variable
```{r descript_coda5, echo=F}
vari <- HRS_ds_coda_w5$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_coda_w5, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(40, 80)

```

#### Validation
```{r crosstabulation_coda5, echo=F}

```





```{r importOPAL_coda5, echo=F}

#opal.assign.data(o, 'HRS_ds_coda_w5', HRS_ds_coda_w5)
#opal.symbol_import(o,'HRS_ds_coda_w5', project='_Athlos_Harm_Dataset')
age <- HRS_ds_coda_w5
save(age, file = "../RData/coda_w5/age.RData")
rm(age)

HRS_m_ds_coda_w5 <- HRS_ds_coda_w5
HRS_m_ds_coda_w5$age <- car::recode(HRS_m_ds_coda_w5$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_coda_w5', HRS_m_ds_coda_w5)
#opal.symbol_import(o,'HRS_m_ds_coda_w5', project='_Athlos_Harm_Dataset')
```








### Wave 6 

#### Study-specific variable description


| **Name** |`R6AGEY_E`|`living_status`|
|----------|------------|-|
| **Label** |`W6 R Age (years) at Ivw EndMon`|`Living status`|
| **Table name** |`HRS-CODA-w6`|`hrs_coda_w6`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|`996 = Not applicable`|
| **Description** |  |  |


```{r assign_coda6, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w6_age','HRS.HRS-CODA-w6',
                         variables=list('R6AGEY_E'), missings = TRUE)
```

```{r local_coda6, echo=F}
HRS_coda_w6_age <- opal.execute(o,'HRS_coda_w6_age')

opal.assign.table.tibble(o, 'HRS_coda_w6','HRS_HD.hrs_coda_w6',variables=list('living_status'), missings = TRUE)
HRS_coda_w6 <- opal.execute(o,'HRS_coda_w6')
HRS_coda_w6_age <- left_join(HRS_coda_w6_age,HRS_coda_w6,by="id")


vbl <- HRS_coda_w6_age$living_status
kable(Categorical_summary(vbl, missing_values = c(996))[3], caption = "living_status")
kable(Categorical_summary(vbl, missing_values = c(996))[1], caption = "Category")
ggplot(HRS_coda_w6_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <- HRS_coda_w6_age$R6AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R6AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_coda_w6_age, aes(R6AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(40, 80)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`
* `living_status = Dead or Dropout into 996`

**R script:**

```{r harmo_coda6}
HRS_ds_coda_w6 <- tibble(id=HRS_coda_w6_age$id)
HRS_ds_coda_w6$age <- car::recode(HRS_coda_w6_age$R6AGEY_E, "NA=999")
HRS_ds_coda_w6$age[which(HRS_coda_w6_age$living_status %in% c(1,2))] <- 996

HRS_ds_coda_w6$age <- labelled(HRS_ds_coda_w6$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda6, echo=F}
vari <- HRS_ds_coda_w6$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_coda_w6, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(40, 80)
```

#### Validation
```{r crosstabulation_coda6, echo=F}
```





```{r importOPAL_coda6, echo=F}

#opal.assign.data(o, 'HRS_ds_coda_w6', HRS_ds_coda_w6)
#opal.symbol_import(o,'HRS_ds_coda_w6', project='_Athlos_Harm_Dataset')
age <- HRS_ds_coda_w6
save(age, file = "../RData/coda_w6/age.RData")
rm(age)

HRS_m_ds_coda_w6 <- HRS_ds_coda_w6
HRS_m_ds_coda_w6$age <- car::recode(HRS_m_ds_coda_w6$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_coda_w6', HRS_m_ds_coda_w6)
#opal.symbol_import(o,'HRS_m_ds_coda_w6', project='_Athlos_Harm_Dataset')
```






### Wave 7 

#### Study-specific variable description


| **Name** |`R7AGEY_E`|`living_status`|
|----------|------------|-|
| **Label** |`W7 R Age (years) at Ivw EndMon`|`Living status`|
| **Table name** |`HRS-CODA-w7`|`hrs_coda_w7`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|`996 = Not applicable`|
| **Description** |  |  |


```{r assign_coda7, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w7_age','HRS.HRS-CODA-w7',
                         variables=list('R7AGEY_E'), missings = TRUE)
```

```{r local_coda7, echo=F}
HRS_coda_w7_age <- opal.execute(o,'HRS_coda_w7_age')

opal.assign.table.tibble(o, 'HRS_coda_w7','HRS_HD.hrs_coda_w7',variables=list('living_status'), missings = TRUE)
HRS_coda_w7 <- opal.execute(o,'HRS_coda_w7')
HRS_coda_w7_age <- left_join(HRS_coda_w7_age,HRS_coda_w7,by="id")


vbl <- HRS_coda_w7_age$living_status
kable(Categorical_summary(vbl, missing_values = c(996))[3], caption = "living_status")
kable(Categorical_summary(vbl, missing_values = c(996))[1], caption = "Category")
ggplot(HRS_coda_w7_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <- HRS_coda_w7_age$R7AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R7AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_coda_w7_age, aes(R7AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(40, 80)

```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`
* `living_status = Dead or Dropout into 996`

**R script:**

```{r harmo_coda7}
HRS_ds_coda_w7 <- tibble(id=HRS_coda_w7_age$id)
HRS_ds_coda_w7$age <- car::recode(HRS_coda_w7_age$R7AGEY_E, "NA=999")
HRS_ds_coda_w7$age[which(HRS_coda_w7_age$living_status %in% c(1,2))] <- 996

HRS_ds_coda_w7$age <- labelled(HRS_ds_coda_w7$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda7, echo=F}
vari <- HRS_ds_coda_w7$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_coda_w7, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(40, 80)
```

#### Validation
```{r crosstabulation_coda7, echo=F}

```





```{r importOPAL_coda7, echo=F}

#opal.assign.data(o, 'HRS_ds_coda_w7', HRS_ds_coda_w7)
#opal.symbol_import(o,'HRS_ds_coda_w7', project='_Athlos_Harm_Dataset')
age <- HRS_ds_coda_w7
save(age, file = "../RData/coda_w7/age.RData")
rm(age)

HRS_m_ds_coda_w7 <- HRS_ds_coda_w7
HRS_m_ds_coda_w7$age <- car::recode(HRS_m_ds_coda_w7$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_coda_w7', HRS_m_ds_coda_w7)
#opal.symbol_import(o,'HRS_m_ds_coda_w7', project='_Athlos_Harm_Dataset')
```





### Wave 8 

#### Study-specific variable description


| **Name** |`R8AGEY_E`|`living_status`|
|----------|------------|-|
| **Label** |`W8 R Age (years) at Ivw EndMon`|`Living status`|
| **Table name** |`HRS-CODA-w8`|`hrs_coda_w8`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|`996 = Not applicable`|
| **Description** |  |  |


```{r assign_coda8, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w8_age','HRS.HRS-CODA-w8',
                         variables=list('R8AGEY_E'), missings = TRUE)
```

```{r local_coda8, echo=F}
HRS_coda_w8_age <- opal.execute(o,'HRS_coda_w8_age')

opal.assign.table.tibble(o, 'HRS_coda_w8','HRS_HD.hrs_coda_w8',variables=list('living_status'), missings = TRUE)
HRS_coda_w8 <- opal.execute(o,'HRS_coda_w8')
HRS_coda_w8_age <- left_join(HRS_coda_w8_age,HRS_coda_w8,by="id")


vbl <- HRS_coda_w8_age$living_status
kable(Categorical_summary(vbl, missing_values = c(996))[3], caption = "living_status")
kable(Categorical_summary(vbl, missing_values = c(996))[1], caption = "Category")
ggplot(HRS_coda_w8_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <- HRS_coda_w8_age$R8AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R8AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_coda_w8_age, aes(R8AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(40, 80)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`
* `living_status = Dead or Dropout into 996`

**R script:**

```{r harmo_coda8}
HRS_ds_coda_w8 <- tibble(id=HRS_coda_w8_age$id)
HRS_ds_coda_w8$age <- car::recode(HRS_coda_w8_age$R8AGEY_E, "NA=999")
HRS_ds_coda_w8$age[which(HRS_coda_w8_age$living_status %in% c(1,2))] <- 996

HRS_ds_coda_w8$age <- labelled(HRS_ds_coda_w8$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda8, echo=F}
vari <- HRS_ds_coda_w8$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_coda_w8, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(40, 80)
```

#### Validation
```{r crosstabulation_coda8, echo=F}

```





```{r importOPAL_coda8, echo=F}

#opal.assign.data(o, 'HRS_ds_coda_w8', HRS_ds_coda_w8)
#opal.symbol_import(o,'HRS_ds_coda_w8', project='_Athlos_Harm_Dataset')
age <- HRS_ds_coda_w8
save(age, file = "../RData/coda_w8/age.RData")
rm(age)

HRS_m_ds_coda_w8 <- HRS_ds_coda_w8
HRS_m_ds_coda_w8$age <- car::recode(HRS_m_ds_coda_w8$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_coda_w8', HRS_m_ds_coda_w8)
#opal.symbol_import(o,'HRS_m_ds_coda_w8', project='_Athlos_Harm_Dataset')
```





### Wave 9 

#### Study-specific variable description


| **Name** |`R9AGEY_E`|`living_status`|
|----------|------------|-|
| **Label** |`W9 R Age (years) at Ivw EndMon`|`Living status`|
| **Table name** |`HRS-CODA-w9`|`hrs_coda_w9`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|`996 = Not applicable`|
| **Description** |  |  |


```{r assign_coda9, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w9_age','HRS.HRS-CODA-w9',
                         variables=list('R9AGEY_E'), missings = TRUE)
```

```{r local_coda9, echo=F}
HRS_coda_w9_age <- opal.execute(o,'HRS_coda_w9_age')

opal.assign.table.tibble(o, 'HRS_coda_w9','HRS_HD.hrs_coda_w9',variables=list('living_status'), missings = TRUE)
HRS_coda_w9 <- opal.execute(o,'HRS_coda_w9')
HRS_coda_w9_age <- left_join(HRS_coda_w9_age,HRS_coda_w9,by="id")


vbl <- HRS_coda_w9_age$living_status
kable(Categorical_summary(vbl, missing_values = c(996))[3], caption = "living_status")
kable(Categorical_summary(vbl, missing_values = c(996))[1], caption = "Category")
ggplot(HRS_coda_w9_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <- HRS_coda_w9_age$R9AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R9AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_coda_w9_age, aes(R9AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(40, 80)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`
* `living_status = Dead or Dropout into 996`

**R script:**

```{r harmo_coda9}
HRS_ds_coda_w9 <- tibble(id=HRS_coda_w9_age$id)
HRS_ds_coda_w9$age <- car::recode(HRS_coda_w9_age$R9AGEY_E, "NA=999")
HRS_ds_coda_w9$age[which(HRS_coda_w9_age$living_status %in% c(1,2))] <- 996

HRS_ds_coda_w9$age <- labelled(HRS_ds_coda_w9$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda9, echo=F}
vari <- HRS_ds_coda_w9$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_coda_w9, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(40, 80)
```

#### Validation
```{r crosstabulation_coda9, echo=F}

```





```{r importOPAL_coda9, echo=F}

#opal.assign.data(o, 'HRS_ds_coda_w9', HRS_ds_coda_w9)
#opal.symbol_import(o,'HRS_ds_coda_w9', project='_Athlos_Harm_Dataset')
age <- HRS_ds_coda_w9
save(age, file = "../RData/coda_w9/age.RData")
rm(age)

HRS_m_ds_coda_w9 <- HRS_ds_coda_w9
HRS_m_ds_coda_w9$age <- car::recode(HRS_m_ds_coda_w9$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_coda_w9', HRS_m_ds_coda_w9)
#opal.symbol_import(o,'HRS_m_ds_coda_w9', project='_Athlos_Harm_Dataset')
```






### Wave 10 

#### Study-specific variable description



| **Name** |`R10AGEY_E`|`living_status`|
|----------|------------|-|
| **Label** |`W10 R Age (years) at Ivw EndMon`|`Living status`|
| **Table name** |`HRS-CODA-w10`|`hrs_coda_w10`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|`996 = Not applicable`|
| **Description** |  |  |


```{r assign_coda10, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w10_age','HRS.HRS-CODA-w10',
                         variables=list('R10AGEY_E'), missings = TRUE)
```

```{r local_coda10, echo=F}
HRS_coda_w10_age <- opal.execute(o,'HRS_coda_w10_age')

opal.assign.table.tibble(o, 'HRS_coda_w10','HRS_HD.hrs_coda_w10',variables=list('living_status'), missings = TRUE)
HRS_coda_w10 <- opal.execute(o,'HRS_coda_w10')
HRS_coda_w10_age <- left_join(HRS_coda_w10_age,HRS_coda_w10,by="id")


vbl <- HRS_coda_w10_age$living_status
kable(Categorical_summary(vbl, missing_values = c(996))[3], caption = "living_status")
kable(Categorical_summary(vbl, missing_values = c(996))[1], caption = "Category")
ggplot(HRS_coda_w10_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <- HRS_coda_w10_age$R10AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R10AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_coda_w10_age, aes(R10AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(40, 80)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`
* `living_status = Dead or Dropout into 996`

**R script:**

```{r harmo_coda10}
HRS_ds_coda_w10 <- tibble(id=HRS_coda_w10_age$id)
HRS_ds_coda_w10$age <- car::recode(HRS_coda_w10_age$R10AGEY_E, "NA=999")
HRS_ds_coda_w10$age[which(HRS_coda_w10_age$living_status %in% c(1,2))] <- 996

HRS_ds_coda_w10$age <- labelled(HRS_ds_coda_w10$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda10, echo=F}
vari <- HRS_ds_coda_w10$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_coda_w10, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(40, 80)
```

#### Validation
```{r crosstabulation_coda10, echo=F}

```





```{r importOPAL_coda10, echo=F}

#opal.assign.data(o, 'HRS_ds_coda_w10', HRS_ds_coda_w10)
#opal.symbol_import(o,'HRS_ds_coda_w10', project='_Athlos_Harm_Dataset')
age <- HRS_ds_coda_w10
save(age, file = "../RData/coda_w10/age.RData")
rm(age)

HRS_m_ds_coda_w10 <- HRS_ds_coda_w10
HRS_m_ds_coda_w10$age <- car::recode(HRS_m_ds_coda_w10$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_coda_w10', HRS_m_ds_coda_w10)
#opal.symbol_import(o,'HRS_m_ds_coda_w10', project='_Athlos_Harm_Dataset')
```






### Wave 11 

#### Study-specific variable description



| **Name** |`R11AGEY_E`|`living_status`|
|----------|------------|-|
| **Label** |`W4 R Age (years) at Ivw EndMon`|`Living status`|
| **Table name** |`HRS-CODA-w11`|`hrs_coda_w11`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|`996 = Not applicable`|
| **Description** |  |  |


```{r assign_coda11, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w11_age','HRS.HRS-CODA-w11',
                         variables=list('R11AGEY_E'), missings = TRUE)
```

```{r local_coda11, echo=F}
HRS_coda_w11_age <- opal.execute(o,'HRS_coda_w11_age')

opal.assign.table.tibble(o, 'HRS_coda_w11','HRS_HD.hrs_coda_w11',variables=list('living_status'), missings = TRUE)
HRS_coda_w11 <- opal.execute(o,'HRS_coda_w11')
HRS_coda_w11_age <- left_join(HRS_coda_w11_age,HRS_coda_w11,by="id")


vbl <- HRS_coda_w11_age$living_status
kable(Categorical_summary(vbl, missing_values = c(996))[3], caption = "living_status")
kable(Categorical_summary(vbl, missing_values = c(996))[1], caption = "Category")
ggplot(HRS_coda_w11_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <- HRS_coda_w11_age$R11AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R11AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_coda_w11_age, aes(R11AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(40, 80)
 
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`
* `living_status = Dead or Dropout into 996`

**R script:**

```{r harmo_coda11}
HRS_ds_coda_w11 <- tibble(id=HRS_coda_w11_age$id)
HRS_ds_coda_w11$age <- car::recode(HRS_coda_w11_age$R11AGEY_E, "NA=999")
HRS_ds_coda_w11$age[which(HRS_coda_w11_age$living_status %in% c(1,2))] <- 996

HRS_ds_coda_w11$age <- labelled(HRS_ds_coda_w11$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda11, echo=F}
vari <- HRS_ds_coda_w11$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_coda_w11, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(40, 80)

```

#### Validation
```{r crosstabulation_coda11, echo=F}

```





```{r importOPAL_coda11, echo=F}

#opal.assign.data(o, 'HRS_ds_coda_w11', HRS_ds_coda_w11)
#opal.symbol_import(o,'HRS_ds_coda_w11', project='_Athlos_Harm_Dataset')
age <- HRS_ds_coda_w11
save(age, file = "../RData/coda_w11/age.RData")
rm(age)

HRS_m_ds_coda_w11 <- HRS_ds_coda_w11
HRS_m_ds_coda_w11$age <- car::recode(HRS_m_ds_coda_w11$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_coda_w11', HRS_m_ds_coda_w11)
#opal.symbol_import(o,'HRS_m_ds_coda_w11', project='_Athlos_Harm_Dataset')
```




## The War Baby (WB)

### Wave 4  

#### Study-specific variable description

| **Name** |`R4AGEY_E`|
|----------|------------|
| **Label** |`W4 R Age (years) at Ivw EndMon`|
| **Table name** |`HRS-WB-w4`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign_wb4, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w4_age','HRS.HRS-WB-w4',
                         variables=list('R4AGEY_E'), missings = TRUE)
```

```{r local_wb4, echo=F}
HRS_wb_w4_age <- opal.execute(o,'HRS_wb_w4_age')


vari <- HRS_wb_w4_age$R4AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R4AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_wb_w4_age, aes(R4AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 80)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_wb4}
HRS_ds_wb_w4 <- tibble(id=HRS_wb_w4_age$id)
HRS_ds_wb_w4$age <- car::recode(HRS_wb_w4_age$R4AGEY_E, "NA=999")

HRS_ds_wb_w4$age <- labelled(HRS_ds_wb_w4$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb4, echo=F}
vari <- HRS_ds_wb_w4$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_wb_w4, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 80)

```

#### Validation
```{r crosstabulation_wb4, echo=F}

```





```{r importOPAL_wb4, echo=F}

#opal.assign.data(o, 'HRS_ds_wb_w4', HRS_ds_wb_w4)
#opal.symbol_import(o,'HRS_ds_wb_w4', project='_Athlos_Harm_Dataset')
age <- HRS_ds_wb_w4
save(age, file = "../RData/wb_w4/age.RData")
rm(age)

HRS_m_ds_wb_w4 <- HRS_ds_wb_w4
HRS_m_ds_wb_w4$age <- car::recode(HRS_m_ds_wb_w4$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w4', HRS_m_ds_wb_w4)
#opal.symbol_import(o,'HRS_m_ds_wb_w4', project='_Athlos_Harm_Dataset')
```










### Wave 5  

#### Study-specific variable description


| **Name** |`R5AGEY_E`|`living_status`|
|----------|------------|-|
| **Label** |`W5 R Age (years) at Ivw EndMon`|`Living status`|
| **Table name** |`HRS-WB-w5`|`hrs_wb_w5`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|`996 = Not applicable`|
| **Description** |  |  |


```{r assign_wb5, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w5_age','HRS.HRS-WB-w5',
                         variables=list('R5AGEY_E'), missings = TRUE)
```

```{r local_wb5, echo=F}
HRS_wb_w5_age <- opal.execute(o,'HRS_wb_w5_age')

opal.assign.table.tibble(o, 'HRS_wb_w5','HRS_HD.hrs_wb_w5',variables=list('living_status'), missings = TRUE)
HRS_wb_w5 <- opal.execute(o,'HRS_wb_w5')
HRS_wb_w5_age <- left_join(HRS_wb_w5_age,HRS_wb_w5,by="id")


vbl <- HRS_wb_w5_age$living_status
kable(Categorical_summary(vbl, missing_values = c(996))[3], caption = "living_status")
kable(Categorical_summary(vbl, missing_values = c(996))[1], caption = "Category")
ggplot(HRS_wb_w5_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <- HRS_wb_w5_age$R5AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R5AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_wb_w5_age, aes(R5AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 80)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`
* `living_status = Dead or Dropout into 996`

**R script:**

```{r harmo_wb5}
HRS_ds_wb_w5 <- tibble(id=HRS_wb_w5_age$id)
HRS_ds_wb_w5$age <- car::recode(HRS_wb_w5_age$R5AGEY_E, "NA=999")
HRS_ds_wb_w5$age[which(HRS_wb_w5_age$living_status %in% c(1,2))] <- 996

HRS_ds_wb_w5$age <- labelled(HRS_ds_wb_w5$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb5, echo=F}
vari <- HRS_ds_wb_w5$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_wb_w5, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 80)

```

#### Validation
```{r crosstabulation_wb5, echo=F}

```





```{r importOPAL_wb5, echo=F}

#opal.assign.data(o, 'HRS_ds_wb_w5', HRS_ds_wb_w5)
#opal.symbol_import(o,'HRS_ds_wb_w5', project='_Athlos_Harm_Dataset')
age <- HRS_ds_wb_w5
save(age, file = "../RData/wb_w5/age.RData")
rm(age)

HRS_m_ds_wb_w5 <- HRS_ds_wb_w5
HRS_m_ds_wb_w5$age <- car::recode(HRS_m_ds_wb_w5$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w5', HRS_m_ds_wb_w5)
#opal.symbol_import(o,'HRS_m_ds_wb_w5', project='_Athlos_Harm_Dataset')
```








### Wave 6  

#### Study-specific variable description



| **Name** |`R6AGEY_E`|`living_status`|
|----------|------------|-|
| **Label** |`W6 R Age (years) at Ivw EndMon`|`Living status`|
| **Table name** |`HRS-WB-w6`|`hrs_wb_w6`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|`996 = Not applicable`|
| **Description** |  |  |


```{r assign_wb6, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w6_age','HRS.HRS-WB-w6',
                         variables=list('R6AGEY_E'), missings = TRUE)
```

```{r local_wb6, echo=F}
HRS_wb_w6_age <- opal.execute(o,'HRS_wb_w6_age')

opal.assign.table.tibble(o, 'HRS_wb_w6','HRS_HD.hrs_wb_w6',variables=list('living_status'), missings = TRUE)
HRS_wb_w6 <- opal.execute(o,'HRS_wb_w6')
HRS_wb_w6_age <- left_join(HRS_wb_w6_age,HRS_wb_w6,by="id")


vbl <- HRS_wb_w6_age$living_status
kable(Categorical_summary(vbl, missing_values = c(996))[3], caption = "living_status")
kable(Categorical_summary(vbl, missing_values = c(996))[1], caption = "Category")
ggplot(HRS_wb_w6_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <- HRS_wb_w6_age$R6AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R6AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_wb_w6_age, aes(R6AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 80)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`
* `living_status = Dead or Dropout into 996`

**R script:**

```{r harmo_wb6}
HRS_ds_wb_w6 <- tibble(id=HRS_wb_w6_age$id)
HRS_ds_wb_w6$age <- car::recode(HRS_wb_w6_age$R6AGEY_E, "NA=999")
HRS_ds_wb_w6$age[which(HRS_wb_w6_age$living_status %in% c(1,2))] <- 996

HRS_ds_wb_w6$age <- labelled(HRS_ds_wb_w6$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb6, echo=F}
vari <- HRS_ds_wb_w6$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_wb_w6, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 80)

```

#### Validation
```{r crosstabulation_wb6, echo=F}

```





```{r importOPAL_wb6, echo=F}

#opal.assign.data(o, 'HRS_ds_wb_w6', HRS_ds_wb_w6)
#opal.symbol_import(o,'HRS_ds_wb_w6', project='_Athlos_Harm_Dataset')
age <- HRS_ds_wb_w6
save(age, file = "../RData/wb_w6/age.RData")
rm(age)

HRS_m_ds_wb_w6 <- HRS_ds_wb_w6
HRS_m_ds_wb_w6$age <- car::recode(HRS_m_ds_wb_w6$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w6', HRS_m_ds_wb_w6)
#opal.symbol_import(o,'HRS_m_ds_wb_w6', project='_Athlos_Harm_Dataset')
```






### Wave 7  

#### Study-specific variable description


| **Name** |`R7AGEY_E`|`living_status`|
|----------|------------|-|
| **Label** |`W7 R Age (years) at Ivw EndMon`|`Living status`|
| **Table name** |`HRS-WB-w7`|`hrs_wb_w7`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|`996 = Not applicable`|
| **Description** |  |  |



```{r assign_wb7, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w7_age','HRS.HRS-WB-w7',
                         variables=list('R7AGEY_E'), missings = TRUE)
```

```{r local_wb7, echo=F}
HRS_wb_w7_age <- opal.execute(o,'HRS_wb_w7_age')

opal.assign.table.tibble(o, 'HRS_wb_w7','HRS_HD.hrs_wb_w7',variables=list('living_status'), missings = TRUE)
HRS_wb_w7 <- opal.execute(o,'HRS_wb_w7')
HRS_wb_w7_age <- left_join(HRS_wb_w7_age,HRS_wb_w7,by="id")


vbl <- HRS_wb_w7_age$living_status
kable(Categorical_summary(vbl, missing_values = c(996))[3], caption = "living_status")
kable(Categorical_summary(vbl, missing_values = c(996))[1], caption = "Category")
ggplot(HRS_wb_w7_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <- HRS_wb_w7_age$R7AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R7AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_wb_w7_age, aes(R7AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 80)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`
* `living_status = Dead or Dropout into 996`

**R script:**

```{r harmo_wb7}
HRS_ds_wb_w7 <- tibble(id=HRS_wb_w7_age$id)
HRS_ds_wb_w7$age <- car::recode(HRS_wb_w7_age$R7AGEY_E, "NA=999")
HRS_ds_wb_w7$age[which(HRS_wb_w7_age$living_status %in% c(1,2))] <- 996

HRS_ds_wb_w7$age <- labelled(HRS_ds_wb_w7$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb7, echo=F}
vari <- HRS_ds_wb_w7$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_wb_w7, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 80)
```

#### Validation
```{r crosstabulation_wb7, echo=F}

```





```{r importOPAL_wb7, echo=F}

#opal.assign.data(o, 'HRS_ds_wb_w7', HRS_ds_wb_w7)
#opal.symbol_import(o,'HRS_ds_wb_w7', project='_Athlos_Harm_Dataset')
age <- HRS_ds_wb_w7
save(age, file = "../RData/wb_w7/age.RData")
rm(age)

HRS_m_ds_wb_w7 <- HRS_ds_wb_w7
HRS_m_ds_wb_w7$age <- car::recode(HRS_m_ds_wb_w7$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w7', HRS_m_ds_wb_w7)
#opal.symbol_import(o,'HRS_m_ds_wb_w7', project='_Athlos_Harm_Dataset')
```







### Wave 8  

#### Study-specific variable description



| **Name** |`R8AGEY_E`|`living_status`|
|----------|------------|-|
| **Label** |`W8 R Age (years) at Ivw EndMon`|`Living status`|
| **Table name** |`HRS-WB-w8`|`hrs_wb_w8`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|`996 = Not applicable`|
| **Description** |  |  |


```{r assign_wb8, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w8_age','HRS.HRS-WB-w8',
                         variables=list('R8AGEY_E'), missings = TRUE)
```

```{r local_wb8, echo=F}
HRS_wb_w8_age <- opal.execute(o,'HRS_wb_w8_age')

opal.assign.table.tibble(o, 'HRS_wb_w8','HRS_HD.hrs_wb_w8',variables=list('living_status'), missings = TRUE)
HRS_wb_w8 <- opal.execute(o,'HRS_wb_w8')
HRS_wb_w8_age <- left_join(HRS_wb_w8_age,HRS_wb_w8,by="id")


vbl <- HRS_wb_w8_age$living_status
kable(Categorical_summary(vbl, missing_values = c(996))[3], caption = "living_status")
kable(Categorical_summary(vbl, missing_values = c(996))[1], caption = "Category")
ggplot(HRS_wb_w8_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <- HRS_wb_w8_age$R8AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R8AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_wb_w8_age, aes(R8AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 80)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`
* `living_status = Dead or Dropout into 996`

**R script:**

```{r harmo_wb8}
HRS_ds_wb_w8 <- tibble(id=HRS_wb_w8_age$id)
HRS_ds_wb_w8$age <- car::recode(HRS_wb_w8_age$R8AGEY_E, "NA=999")
HRS_ds_wb_w8$age[which(HRS_wb_w8_age$living_status %in% c(1,2))] <- 996

HRS_ds_wb_w8$age <- labelled(HRS_ds_wb_w8$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb8, echo=F}
vari <- HRS_ds_wb_w8$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_wb_w8, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 80)
```

#### Validation
```{r crosstabulation_wb8, echo=F}

```





```{r importOPAL_wb8, echo=F}

#opal.assign.data(o, 'HRS_ds_wb_w8', HRS_ds_wb_w8)
#opal.symbol_import(o,'HRS_ds_wb_w8', project='_Athlos_Harm_Dataset')
age <- HRS_ds_wb_w8
save(age, file = "../RData/wb_w8/age.RData")
rm(age)

HRS_m_ds_wb_w8 <- HRS_ds_wb_w8
HRS_m_ds_wb_w8$age <- car::recode(HRS_m_ds_wb_w8$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w8', HRS_m_ds_wb_w8)
#opal.symbol_import(o,'HRS_m_ds_wb_w8', project='_Athlos_Harm_Dataset')
```







### Wave 9  

#### Study-specific variable description

| **Name** |`R9AGEY_E`|`living_status`|
|----------|------------|-|
| **Label** |`W9 R Age (years) at Ivw EndMon`|`Living status`|
| **Table name** |`HRS-WB-w9`|`hrs_wb_w9`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|`996 = Not applicable`|
| **Description** |  |  |



```{r assign_wb9, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w9_age','HRS.HRS-WB-w9',
                         variables=list('R9AGEY_E'), missings = TRUE)
```

```{r local_wb9, echo=F}
HRS_wb_w9_age <- opal.execute(o,'HRS_wb_w9_age')

opal.assign.table.tibble(o, 'HRS_wb_w9','HRS_HD.hrs_wb_w9',variables=list('living_status'), missings = TRUE)
HRS_wb_w9 <- opal.execute(o,'HRS_wb_w9')
HRS_wb_w9_age <- left_join(HRS_wb_w9_age,HRS_wb_w9,by="id")


vbl <- HRS_wb_w9_age$living_status
kable(Categorical_summary(vbl, missing_values = c(996))[3], caption = "living_status")
kable(Categorical_summary(vbl, missing_values = c(996))[1], caption = "Category")
ggplot(HRS_wb_w9_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <- HRS_wb_w9_age$R9AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R9AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_wb_w9_age, aes(R9AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 80)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`
* `living_status = Dead or Dropout into 996`

**R script:**

```{r harmo_wb9}
HRS_ds_wb_w9 <- tibble(id=HRS_wb_w9_age$id)
HRS_ds_wb_w9$age <- car::recode(HRS_wb_w9_age$R9AGEY_E, "NA=999")
HRS_ds_wb_w9$age[which(HRS_wb_w9_age$living_status %in% c(1,2))] <- 996

HRS_ds_wb_w9$age <- labelled(HRS_ds_wb_w9$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb9, echo=F}
vari <- HRS_ds_wb_w9$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_wb_w9, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 80)
```

#### Validation
```{r crosstabulation_wb9, echo=F}

```





```{r importOPAL_wb9, echo=F}

#opal.assign.data(o, 'HRS_ds_wb_w9', HRS_ds_wb_w9)
#opal.symbol_import(o,'HRS_ds_wb_w9', project='_Athlos_Harm_Dataset')
age <- HRS_ds_wb_w9
save(age, file = "../RData/wb_w9/age.RData")
rm(age)

HRS_m_ds_wb_w9 <- HRS_ds_wb_w9
HRS_m_ds_wb_w9$age <- car::recode(HRS_m_ds_wb_w9$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w9', HRS_m_ds_wb_w9)
#opal.symbol_import(o,'HRS_m_ds_wb_w9', project='_Athlos_Harm_Dataset')
```







### Wave 10  

#### Study-specific variable description


| **Name** |`R10AGEY_E`|`living_status`|
|----------|------------|-|
| **Label** |`W10 R Age (years) at Ivw EndMon`|`Living status`|
| **Table name** |`HRS-WB-w10`|`hrs_wb_w10`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|`996 = Not applicable`|
| **Description** |  |  |


```{r assign_wb10, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w10_age','HRS.HRS-WB-w10',
                         variables=list('R10AGEY_E'), missings = TRUE)
```

```{r local_wb10, echo=F}
HRS_wb_w10_age <- opal.execute(o,'HRS_wb_w10_age')

opal.assign.table.tibble(o, 'HRS_wb_w10','HRS_HD.hrs_wb_w10',variables=list('living_status'), missings = TRUE)
HRS_wb_w10 <- opal.execute(o,'HRS_wb_w10')
HRS_wb_w10_age <- left_join(HRS_wb_w10_age,HRS_wb_w10,by="id")


vbl <- HRS_wb_w10_age$living_status
kable(Categorical_summary(vbl, missing_values = c(996))[3], caption = "living_status")
kable(Categorical_summary(vbl, missing_values = c(996))[1], caption = "Category")
ggplot(HRS_wb_w10_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <- HRS_wb_w10_age$R10AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R10AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_wb_w10_age, aes(R10AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 80)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`
* `living_status = Dead or Dropout into 996`

**R script:**

```{r harmo_wb10}
HRS_ds_wb_w10 <- tibble(id=HRS_wb_w10_age$id)
HRS_ds_wb_w10$age <- car::recode(HRS_wb_w10_age$R10AGEY_E, "NA=999")
HRS_ds_wb_w10$age[which(HRS_wb_w10_age$living_status %in% c(1,2))] <- 996

HRS_ds_wb_w10$age <- labelled(HRS_ds_wb_w10$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb10, echo=F}
vari <- HRS_ds_wb_w10$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_wb_w10, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 80)
```

#### Validation
```{r crosstabulation_wb10, echo=F}

```





```{r importOPAL_wb10, echo=F}

#opal.assign.data(o, 'HRS_ds_wb_w10', HRS_ds_wb_w10)
#opal.symbol_import(o,'HRS_ds_wb_w10', project='_Athlos_Harm_Dataset')
age <- HRS_ds_wb_w10
save(age, file = "../RData/wb_w10/age.RData")
rm(age)

HRS_m_ds_wb_w10 <- HRS_ds_wb_w10
HRS_m_ds_wb_w10$age <- car::recode(HRS_m_ds_wb_w10$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w10', HRS_m_ds_wb_w10)
#opal.symbol_import(o,'HRS_m_ds_wb_w10', project='_Athlos_Harm_Dataset')
```







### Wave 11  

#### Study-specific variable description


| **Name** |`R11AGEY_E`|`living_status`|
|----------|------------|-|
| **Label** |`W11 R Age (years) at Ivw EndMon`|`Living status`|
| **Table name** |`HRS-WB-w11`|`hrs_wb_w11`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|`996 = Not applicable`|
| **Description** |  |  |


```{r assign_wb11, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w11_age','HRS.HRS-WB-w11',
                         variables=list('R11AGEY_E'), missings = TRUE)
```

```{r local_wb11, echo=F}
HRS_wb_w11_age <- opal.execute(o,'HRS_wb_w11_age')

opal.assign.table.tibble(o, 'HRS_wb_w11','HRS_HD.hrs_wb_w11',variables=list('living_status'), missings = TRUE)
HRS_wb_w11 <- opal.execute(o,'HRS_wb_w11')
HRS_wb_w11_age <- left_join(HRS_wb_w11_age,HRS_wb_w11,by="id")


vbl <- HRS_wb_w11_age$living_status
kable(Categorical_summary(vbl, missing_values = c(996))[3], caption = "living_status")
kable(Categorical_summary(vbl, missing_values = c(996))[1], caption = "Category")
ggplot(HRS_wb_w11_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <- HRS_wb_w11_age$R11AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R11AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_wb_w11_age, aes(R11AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 80)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`
* `living_status = Dead or Dropout into 996`


**R script:**

```{r harmo_wb11}
HRS_ds_wb_w11 <- tibble(id=HRS_wb_w11_age$id)
HRS_ds_wb_w11$age <- car::recode(HRS_wb_w11_age$R11AGEY_E, "NA=999")
HRS_ds_wb_w11$age[which(HRS_wb_w11_age$living_status %in% c(1,2))] <- 996

HRS_ds_wb_w11$age <- labelled(HRS_ds_wb_w11$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb11, echo=F}
vari <- HRS_ds_wb_w11$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_wb_w11, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 80)
```

#### Validation
```{r crosstabulation_wb11, echo=F}

```





```{r importOPAL_wb11, echo=F}

#opal.assign.data(o, 'HRS_ds_wb_w11', HRS_ds_wb_w11)
#opal.symbol_import(o,'HRS_ds_wb_w11', project='_Athlos_Harm_Dataset')
age <- HRS_ds_wb_w11
save(age, file = "../RData/wb_w11/age.RData")
rm(age)

HRS_m_ds_wb_w11 <- HRS_ds_wb_w11
HRS_m_ds_wb_w11$age <- car::recode(HRS_m_ds_wb_w11$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w11', HRS_m_ds_wb_w11)
#opal.symbol_import(o,'HRS_m_ds_wb_w11', project='_Athlos_Harm_Dataset')
```




## The Early Baby Boomer (EBB)

### Wave 7  

#### Study-specific variable description

| **Name** |`R7AGEY_E`|
|----------|------------|
| **Label** |`W7 R Age (years) at Ivw EndMon`|
| **Table name** |`HRS-EBB-w7`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign_ebb7, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w7_age','HRS.HRS-EBB-w7',
                         variables=list('R7AGEY_E'), missings = TRUE)
```

```{r local_ebb7, echo=F}
HRS_ebb_w7_age <- opal.execute(o,'HRS_ebb_w7_age')


vari <- HRS_ebb_w7_age$R7AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R7AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_ebb_w7_age, aes(R7AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 80)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_ebb7}
HRS_ds_ebb_w7 <- tibble(id=HRS_ebb_w7_age$id)
HRS_ds_ebb_w7$age <- car::recode(HRS_ebb_w7_age$R7AGEY_E, "NA=999")

HRS_ds_ebb_w7$age <- labelled(HRS_ds_ebb_w7$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ebb7, echo=F}
vari <- HRS_ds_ebb_w7$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_ebb_w7, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 80)
```

#### Validation
```{r crosstabulation_ebb7, echo=F}

```





```{r importOPAL_ebb7, echo=F}

#opal.assign.data(o, 'HRS_ds_ebb_w7', HRS_ds_ebb_w7)
#opal.symbol_import(o,'HRS_ds_ebb_w7', project='_Athlos_Harm_Dataset')
age <- HRS_ds_ebb_w7
save(age, file = "../RData/ebb_w7/age.RData")
rm(age)

HRS_m_ds_ebb_w7 <- HRS_ds_ebb_w7
HRS_m_ds_ebb_w7$age <- car::recode(HRS_m_ds_ebb_w7$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ebb_w7', HRS_m_ds_ebb_w7)
#opal.symbol_import(o,'HRS_m_ds_ebb_w7', project='_Athlos_Harm_Dataset')
```








### Wave 8  

#### Study-specific variable description



| **Name** |`R8AGEY_E`|`living_status`|
|----------|------------|-|
| **Label** |`W8 R Age (years) at Ivw EndMon`|`Living status`|
| **Table name** |`HRS-EBB-w8`|`hrs_ebb_w8`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|`996 = Not applicable`|
| **Description** |  |  |


```{r assign_ebb8, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w8_age','HRS.HRS-EBB-w8',
                         variables=list('R8AGEY_E'), missings = TRUE)
```

```{r local_ebb8, echo=F}
HRS_ebb_w8_age <- opal.execute(o,'HRS_ebb_w8_age')

opal.assign.table.tibble(o, 'HRS_ebb_w8','HRS_HD.hrs_ebb_w8',variables=list('living_status'), missings = TRUE)
HRS_ebb_w8 <- opal.execute(o,'HRS_ebb_w8')
HRS_ebb_w8_age <- left_join(HRS_ebb_w8_age,HRS_ebb_w8,by="id")


vbl <- HRS_ebb_w8_age$living_status
kable(Categorical_summary(vbl, missing_values = c(996))[3], caption = "living_status")
kable(Categorical_summary(vbl, missing_values = c(996))[1], caption = "Category")
ggplot(HRS_ebb_w8_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <- HRS_ebb_w8_age$R8AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R8AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_ebb_w8_age, aes(R8AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 80)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`
* `living_status = Dead or Dropout into 996`

**R script:**

```{r harmo_ebb8}
HRS_ds_ebb_w8 <- tibble(id=HRS_ebb_w8_age$id)
HRS_ds_ebb_w8$age <- car::recode(HRS_ebb_w8_age$R8AGEY_E, "NA=999")
HRS_ds_ebb_w8$age[which(HRS_ebb_w8_age$living_status %in% c(1,2))] <- 996

HRS_ds_ebb_w8$age <- labelled(HRS_ds_ebb_w8$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ebb8, echo=F}
vari <- HRS_ds_ebb_w8$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_ebb_w8, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 80)
```

#### Validation
```{r crosstabulation_ebb8, echo=F}

```





```{r importOPAL_ebb8, echo=F}

#opal.assign.data(o, 'HRS_ds_ebb_w8', HRS_ds_ebb_w8)
#opal.symbol_import(o,'HRS_ds_ebb_w8', project='_Athlos_Harm_Dataset')
age <- HRS_ds_ebb_w8
save(age, file = "../RData/ebb_w8/age.RData")
rm(age)

HRS_m_ds_ebb_w8 <- HRS_ds_ebb_w8
HRS_m_ds_ebb_w8$age <- car::recode(HRS_m_ds_ebb_w8$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ebb_w8', HRS_m_ds_ebb_w8)
#opal.symbol_import(o,'HRS_m_ds_ebb_w8', project='_Athlos_Harm_Dataset')
```





### Wave 9  

#### Study-specific variable description


| **Name** |`R9AGEY_E`|`living_status`|
|----------|------------|-|
| **Label** |`W9 R Age (years) at Ivw EndMon`|`Living status`|
| **Table name** |`HRS-EBB-w9`|`hrs_ebb_w9`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|`996 = Not applicable`|
| **Description** |  |  |



```{r assign_ebb9, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w9_age','HRS.HRS-EBB-w9',
                         variables=list('R9AGEY_E'), missings = TRUE)
```

```{r local_ebb9, echo=F}
HRS_ebb_w9_age <- opal.execute(o,'HRS_ebb_w9_age')

opal.assign.table.tibble(o, 'HRS_ebb_w9','HRS_HD.hrs_ebb_w9',variables=list('living_status'), missings = TRUE)
HRS_ebb_w9 <- opal.execute(o,'HRS_ebb_w9')
HRS_ebb_w9_age <- left_join(HRS_ebb_w9_age,HRS_ebb_w9,by="id")


vbl <- HRS_ebb_w9_age$living_status
kable(Categorical_summary(vbl, missing_values = c(996))[3], caption = "living_status")
kable(Categorical_summary(vbl, missing_values = c(996))[1], caption = "Category")
ggplot(HRS_ebb_w9_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <- HRS_ebb_w9_age$R9AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R9AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_ebb_w9_age, aes(R9AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 80)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`
* `living_status = Dead or Dropout into 996`

**R script:**

```{r harmo_ebb9}
HRS_ds_ebb_w9 <- tibble(id=HRS_ebb_w9_age$id)
HRS_ds_ebb_w9$age <- car::recode(HRS_ebb_w9_age$R9AGEY_E, "NA=999")
HRS_ds_ebb_w9$age[which(HRS_ebb_w9_age$living_status %in% c(1,2))] <- 996

HRS_ds_ebb_w9$age <- labelled(HRS_ds_ebb_w9$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ebb9, echo=F}
vari <- HRS_ds_ebb_w9$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_ebb_w9, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 80)
```

#### Validation
```{r crosstabulation_ebb9, echo=F}

```





```{r importOPAL_ebb9, echo=F}

#opal.assign.data(o, 'HRS_ds_ebb_w9', HRS_ds_ebb_w9)
#opal.symbol_import(o,'HRS_ds_ebb_w9', project='_Athlos_Harm_Dataset')
age <- HRS_ds_ebb_w9
save(age, file = "../RData/ebb_w9/age.RData")
rm(age)

HRS_m_ds_ebb_w9 <- HRS_ds_ebb_w9
HRS_m_ds_ebb_w9$age <- car::recode(HRS_m_ds_ebb_w9$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ebb_w9', HRS_m_ds_ebb_w9)
#opal.symbol_import(o,'HRS_m_ds_ebb_w9', project='_Athlos_Harm_Dataset')
```








### Wave 10  

#### Study-specific variable description

| **Name** |`R10AGEY_E`|`living_status`|
|----------|------------|-|
| **Label** |`W10 R Age (years) at Ivw EndMon`|`Living status`|
| **Table name** |`HRS-EBB-w10`|`hrs_ebb_w10`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|`996 = Not applicable`|
| **Description** |  |  |


```{r assign_ebb10, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w10_age','HRS.HRS-EBB-w10',
                         variables=list('R10AGEY_E'), missings = TRUE)
```

```{r local_ebb10, echo=F}
HRS_ebb_w10_age <- opal.execute(o,'HRS_ebb_w10_age')

opal.assign.table.tibble(o, 'HRS_ebb_w10','HRS_HD.hrs_ebb_w10',variables=list('living_status'), missings = TRUE)
HRS_ebb_w10 <- opal.execute(o,'HRS_ebb_w10')
HRS_ebb_w10_age <- left_join(HRS_ebb_w10_age,HRS_ebb_w10,by="id")


vbl <- HRS_ebb_w10_age$living_status
kable(Categorical_summary(vbl, missing_values = c(996))[3], caption = "living_status")
kable(Categorical_summary(vbl, missing_values = c(996))[1], caption = "Category")
ggplot(HRS_ebb_w10_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <- HRS_ebb_w10_age$R10AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R10AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_ebb_w10_age, aes(R10AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 80)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`
* `living_status = Dead or Dropout into 996`

**R script:**

```{r harmo_ebb10}
HRS_ds_ebb_w10 <- tibble(id=HRS_ebb_w10_age$id)
HRS_ds_ebb_w10$age <- car::recode(HRS_ebb_w10_age$R10AGEY_E, "NA=999")
HRS_ds_ebb_w10$age[which(HRS_ebb_w10_age$living_status %in% c(1,2))] <- 996

HRS_ds_ebb_w10$age <- labelled(HRS_ds_ebb_w10$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ebb10, echo=F}
vari <- HRS_ds_ebb_w10$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_ebb_w10, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 80)
```

#### Validation
```{r crosstabulation_ebb10, echo=F}

```





```{r importOPAL_ebb10, echo=F}

#opal.assign.data(o, 'HRS_ds_ebb_w10', HRS_ds_ebb_w10)
#opal.symbol_import(o,'HRS_ds_ebb_w10', project='_Athlos_Harm_Dataset')
age <- HRS_ds_ebb_w10
save(age, file = "../RData/ebb_w10/age.RData")
rm(age)

HRS_m_ds_ebb_w10 <- HRS_ds_ebb_w10
HRS_m_ds_ebb_w10$age <- car::recode(HRS_m_ds_ebb_w10$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ebb_w10', HRS_m_ds_ebb_w10)
#opal.symbol_import(o,'HRS_m_ds_ebb_w10', project='_Athlos_Harm_Dataset')
```






### Wave 11  

#### Study-specific variable description


| **Name** |`R11AGEY_E`|`living_status`|
|----------|------------|-|
| **Label** |`W11 R Age (years) at Ivw EndMon`|`Living status`|
| **Table name** |`HRS-EBB-w11`|`hrs_ebb_w11`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|`996 = Not applicable`|
| **Description** |  |  |



```{r assign_ebb11, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w11_age','HRS.HRS-EBB-w11',
                         variables=list('R11AGEY_E'), missings = TRUE)
```

```{r local_ebb11, echo=F}
HRS_ebb_w11_age <- opal.execute(o,'HRS_ebb_w11_age')

opal.assign.table.tibble(o, 'HRS_ebb_w11','HRS_HD.hrs_ebb_w11',variables=list('living_status'), missings = TRUE)
HRS_ebb_w11 <- opal.execute(o,'HRS_ebb_w11')
HRS_ebb_w11_age <- left_join(HRS_ebb_w11_age,HRS_ebb_w11,by="id")


vbl <- HRS_ebb_w11_age$living_status
kable(Categorical_summary(vbl, missing_values = c(996))[3], caption = "living_status")
kable(Categorical_summary(vbl, missing_values = c(996))[1], caption = "Category")
ggplot(HRS_ebb_w11_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <- HRS_ebb_w11_age$R11AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R11AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_ebb_w11_age, aes(R11AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 80)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`
* `living_status = Dead or Dropout into 996`

**R script:**

```{r harmo_ebb11}
HRS_ds_ebb_w11 <- tibble(id=HRS_ebb_w11_age$id)
HRS_ds_ebb_w11$age <- car::recode(HRS_ebb_w11_age$R11AGEY_E, "NA=999")
HRS_ds_ebb_w11$age[which(HRS_ebb_w11_age$living_status %in% c(1,2))] <- 996

HRS_ds_ebb_w11$age <- labelled(HRS_ds_ebb_w11$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ebb11, echo=F}
vari <- HRS_ds_ebb_w11$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_ebb_w11, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 80)
```

#### Validation
```{r crosstabulation_ebb11, echo=F}

```





```{r importOPAL_ebb11, echo=F}

#opal.assign.data(o, 'HRS_ds_ebb_w11', HRS_ds_ebb_w11)
#opal.symbol_import(o,'HRS_ds_ebb_w11', project='_Athlos_Harm_Dataset')
age <- HRS_ds_ebb_w11
save(age, file = "../RData/ebb_w11/age.RData")
rm(age)

HRS_m_ds_ebb_w11 <- HRS_ds_ebb_w11
HRS_m_ds_ebb_w11$age <- car::recode(HRS_m_ds_ebb_w11$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ebb_w11', HRS_m_ds_ebb_w11)
#opal.symbol_import(o,'HRS_m_ds_ebb_w11', project='_Athlos_Harm_Dataset')
```







## The Mid Baby Boomer (MBB)

### Wave 10  

#### Study-specific variable description


| **Name** |`R10AGEY_E`|
|----------|------------|
| **Label** |`W10 R Age (years) at Ivw EndMon`|
| **Table name** |`HRS-MBB-w10`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign_mbb10, echo=F}
opal.assign.table.tibble(o, 'HRS_mbb_w10_age','HRS.HRS-MBB-w10',
                         variables=list('R10AGEY_E'), missings = TRUE)
```

```{r local_mbb10, echo=F}
HRS_mbb_w10_age <- opal.execute(o,'HRS_mbb_w10_age')


vari <- HRS_mbb_w10_age$R10AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R10AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_mbb_w10_age, aes(R10AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 80)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_mbb10}
HRS_ds_mbb_w10 <- tibble(id=HRS_mbb_w10_age$id)
HRS_ds_mbb_w10$age <- car::recode(HRS_mbb_w10_age$R10AGEY_E, "NA=999")

HRS_ds_mbb_w10$age <- labelled(HRS_ds_mbb_w10$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_mbb10, echo=F}
vari <- HRS_ds_mbb_w10$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_mbb_w10, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 80)
```

#### Validation
```{r crosstabulation_mbb10, echo=F}

```





```{r importOPAL_mbb10, echo=F}

#opal.assign.data(o, 'HRS_ds_mbb_w10', HRS_ds_mbb_w10)
#opal.symbol_import(o,'HRS_ds_mbb_w10', project='_Athlos_Harm_Dataset')
age <- HRS_ds_mbb_w10
save(age, file = "../RData/mbb_w10/age.RData")
rm(age)

HRS_m_ds_mbb_w10 <- HRS_ds_mbb_w10
HRS_m_ds_mbb_w10$age <- car::recode(HRS_m_ds_mbb_w10$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_mbb_w10', HRS_m_ds_mbb_w10)
#opal.symbol_import(o,'HRS_m_ds_mbb_w10', project='_Athlos_Harm_Dataset')
```






### Wave 11  

#### Study-specific variable description


| **Name** |`R11AGEY_E`|`living_status`|
|----------|------------|-|
| **Label** |`W11 R Age (years) at Ivw EndMon`|`Living status`|
| **Table name** |`HRS-MBB-w11`|`hrs_mbb_w11`|
| **Categories** |`continuous`|`0 = Alive`<br/>`1 = Dead`<br/>`2 = Dropout/unknown`|
| **Missings** |`NA`|`996 = Not applicable`|
| **Description** |  |  |


```{r assign_mbb11, echo=F}
opal.assign.table.tibble(o, 'HRS_mbb_w11_age','HRS.HRS-MBB-w11',
                         variables=list('R11AGEY_E'), missings = TRUE)
```

```{r local_mbb11, echo=F}
HRS_mbb_w11_age <- opal.execute(o,'HRS_mbb_w11_age')

opal.assign.table.tibble(o, 'HRS_mbb_w11','HRS_HD.hrs_mbb_w11',variables=list('living_status'), missings = TRUE)
HRS_mbb_w11 <- opal.execute(o,'HRS_mbb_w11')
HRS_mbb_w11_age <- left_join(HRS_mbb_w11_age,HRS_mbb_w11,by="id")


vbl <- HRS_mbb_w11_age$living_status
kable(Categorical_summary(vbl, missing_values = c(996))[3], caption = "living_status")
kable(Categorical_summary(vbl, missing_values = c(996))[1], caption = "Category")
ggplot(HRS_mbb_w11_age, aes(x=factor(living_status))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vari <- HRS_mbb_w11_age$R11AGEY_E
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "R11AGEY_E")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_mbb_w11_age, aes(R11AGEY_E)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 80)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`
* `living_status = Dead or Dropout into 996`

**R script:**

```{r harmo_mbb11}
HRS_ds_mbb_w11 <- tibble(id=HRS_mbb_w11_age$id)
HRS_ds_mbb_w11$age <- car::recode(HRS_mbb_w11_age$R11AGEY_E, "NA=999")
HRS_ds_mbb_w11$age[which(HRS_mbb_w11_age$living_status %in% c(1,2))] <- 996

HRS_ds_mbb_w11$age <- labelled(HRS_ds_mbb_w11$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_mbb11, echo=F}
vari <- HRS_ds_mbb_w11$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "age")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HRS_ds_mbb_w11, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(20, 80)
```

#### Validation
```{r crosstabulation_mbb11, echo=F}

```





```{r importOPAL_mbb11, echo=F}

#opal.assign.data(o, 'HRS_ds_mbb_w11', HRS_ds_mbb_w11)
#opal.symbol_import(o,'HRS_ds_mbb_w11', project='_Athlos_Harm_Dataset')
age <- HRS_ds_mbb_w11
save(age, file = "../RData/mbb_w11/age.RData")
rm(age)

HRS_m_ds_mbb_w11 <- HRS_ds_mbb_w11
HRS_m_ds_mbb_w11$age <- car::recode(HRS_m_ds_mbb_w11$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_mbb_w11', HRS_m_ds_mbb_w11)
#opal.symbol_import(o,'HRS_m_ds_mbb_w11', project='_Athlos_Harm_Dataset')
```





## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for continuous data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][2])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[2]],missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][2])[1:6]
    # Next, missing/no-missing values
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[2]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],lnames)
  return(t.hds)
  
}

# Save data tables
# 
# savingRD <- function(l.hds,vbl_name){
#   
#   for(index in seq_along(l.hds)){
#     assign(vbl_name,l.hds[[index]])
#     save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
#   }
# 
# }

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


hrw.hrw.cw <- list(hrs_w1 = c("hrs_w1","HRS w1"), hrs_w2 = c("hrs_w2","HRS w2"), hrs_w3 = c("hrs_w3","HRS w3"), hrs_w4 = c("hrs_w4","HRS w4"), hrs_w5 = c("hrs_w5","HRS w5"), hrs_w6 = c("hrs_w6","HRS w6"), hrs_w7 = c("hrs_w7","HRS w7"), hrs_w8 = c("hrs_w8","HRS w8"), hrs_w9 = c("hrs_w9","HRS w9"), hrs_w10 = c("hrs_w10","HRS w10"), hrs_w11 = c("hrs_w11","HRS w11"))

hrw.ahead.cw <- list(ahead_w2 = c("ahead_w2","AHEAD w2"), ahead_w3 = c("ahead_w3","AHEAD w3"), ahead_w4 = c("ahead_w4","AHEAD w4"), ahead_w5 = c("ahead_w5","AHEAD w5"), ahead_w6 = c("ahead_w6","AHEAD w6"), ahead_w7 = c("ahead_w7","AHEAD w7"), ahead_w8 = c("ahead_w8","AHEAD w8"), ahead_w9 = c("ahead_w9","AHEAD w9"), ahead_w10 = c("ahead_w10","AHEAD w10"), ahead_w11 = c("ahead_w11","AHEAD w11"))

hrw.coda.cw <- list(coda_w4 = c("coda_w4","CODA w4"), coda_w5 = c("coda_w5","CODA w5"), coda_w6 = c("coda_w6","CODA w6"), coda_w7 = c("coda_w7","CODA w7"), coda_w8 = c("coda_w8","CODA w8"), coda_w9 = c("coda_w9","CODA w9"), coda_w10 = c("coda_w10","CODA w10"), coda_w11 = c("coda_w11","CODA w11"))

hrw.wb.cw <- list(wb_w4 = c("wb_w4","WB w4"), wb_w5 = c("wb_w5","WB w5"), wb_w6 = c("wb_w6","WB w6"), wb_w7 = c("wb_w7","WB w7"), wb_w8 = c("wb_w8","WB w8"), wb_w9 = c("wb_w9","WB w9"), wb_w10 = c("wb_w10","WB w10"), wb_w11 = c("wb_w11","WB w11"))

hrw.ebb.cw <- list(ebb_w7 = c("ebb_w7","EBB w7"), ebb_w8 = c("ebb_w8","EBB w8"), ebb_w9 = c("ebb_w9","EBB w9"), ebb_w10 = c("ebb_w10","EBB w10"), ebb_w11 = c("ebb_w11","EBB w11"))

hrw.mbb.cw <- list(mbb_w10 = c("mbb_w10","MBB w10"), mbb_w11 = c("mbb_w11","MBB w11"))



# HRS

# Consider only harmonised waves
l.hds <- lapply(hrw.hrw.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  #savingRD(lmlist[[1]],vbl_name=hd_vbl)
}






# AHEAD

# Consider only harmonised waves
l.hds <- lapply(hrw.ahead.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)


if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  #savingRD(lmlist[[1]],vbl_name=hd_vbl)
}








# CODA

# Consider only harmonised waves
l.hds <- lapply(hrw.coda.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  #savingRD(lmlist[[1]],vbl_name=hd_vbl)
}





# WB

# Consider only harmonised waves
l.hds <- lapply(hrw.wb.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  #savingRD(lmlist[[1]],vbl_name=hd_vbl)
}





# EBB

# Consider only harmonised waves
l.hds <- lapply(hrw.ebb.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  #savingRD(lmlist[[1]],vbl_name=hd_vbl)
}




# MBB

# Consider only harmonised waves
l.hds <- lapply(hrw.mbb.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  #savingRD(lmlist[[1]],vbl_name=hd_vbl)
}




```





# Quality estimation
No comments.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
