---
title: "Sex"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/sexDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/sexDS.R')
```



<!-- ########################################################## --> 

# Data process

## HRS sub-sample

### Wave 1 

#### Study-specific variable description

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-HRS-w1`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_hrs1, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_hrs_w1_sex','HRS.HRS-HRS-w1',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_hrs_w1_sex <- opal.execute(o,'HRS_hrs_w1_sex')
```

```{r local_hrs1, echo=FALSE}
vari <- HRS_hrs_w1_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w1_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_hrs1, echo=TRUE}
HRS_ds_hrs_w1 <- tibble(id=HRS_hrs_w1_sex$id)
HRS_ds_hrs_w1$sex <- car::recode(HRS_hrs_w1_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_hrs1, echo=FALSE}
vari <- HRS_ds_hrs_w1$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w1, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs1, echo=FALSE}
AfterH <- table(HRS_ds_hrs_w1$sex)
BeforeH <- table(HRS_hrs_w1_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 


### Wave 2 

#### Study-specific variable description


| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-HRS-w2`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_hrs2, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_hrs_w2_sex','HRS.HRS-HRS-w2',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_hrs_w2_sex <- opal.execute(o,'HRS_hrs_w2_sex')
```

```{r local_hrs2, echo=FALSE}
vari <- HRS_hrs_w2_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w2_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_hrs2, echo=TRUE}
HRS_ds_hrs_w2 <- tibble(id=HRS_hrs_w2_sex$id)
HRS_ds_hrs_w2$sex <- car::recode(HRS_hrs_w2_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_hrs2, echo=FALSE}
vari <- HRS_ds_hrs_w2$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w2, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs2, echo=FALSE}
AfterH <- table(HRS_ds_hrs_w2$sex)
BeforeH <- table(HRS_hrs_w2_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 





### Wave 3 

#### Study-specific variable description

 

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-HRS-w3`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_hrs3, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_hrs_w3_sex','HRS.HRS-HRS-w3',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_hrs_w3_sex <- opal.execute(o,'HRS_hrs_w3_sex')
```

```{r local_hrs3, echo=FALSE}
vari <- HRS_hrs_w3_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w3_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_hrs3, echo=TRUE}
HRS_ds_hrs_w3 <- tibble(id=HRS_hrs_w3_sex$id)
HRS_ds_hrs_w3$sex <- car::recode(HRS_hrs_w3_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_hrs3, echo=FALSE}
vari <- HRS_ds_hrs_w3$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w3, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs3, echo=FALSE}
AfterH <- table(HRS_ds_hrs_w3$sex)
BeforeH <- table(HRS_hrs_w3_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 
 






### Wave 4 

#### Study-specific variable description

 

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-HRS-w4`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_hrs4, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_hrs_w4_sex','HRS.HRS-HRS-w4',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_hrs_w4_sex <- opal.execute(o,'HRS_hrs_w4_sex')
```

```{r local_hrs4, echo=FALSE}
vari <- HRS_hrs_w4_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w4_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_hrs4, echo=TRUE}
HRS_ds_hrs_w4 <- tibble(id=HRS_hrs_w4_sex$id)
HRS_ds_hrs_w4$sex <- car::recode(HRS_hrs_w4_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_hrs4, echo=FALSE}
vari <- HRS_ds_hrs_w4$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w4, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs4, echo=FALSE}
AfterH <- table(HRS_ds_hrs_w4$sex)
BeforeH <- table(HRS_hrs_w4_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 
 



### Wave 5

#### Study-specific variable description

 

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-HRS-w5`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_hrs5, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_hrs_w5_sex','HRS.HRS-HRS-w5',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_hrs_w5_sex <- opal.execute(o,'HRS_hrs_w5_sex')
```

```{r local_hrs5, echo=FALSE}
vari <- HRS_hrs_w5_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w5_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_hrs5, echo=TRUE}
HRS_ds_hrs_w5 <- tibble(id=HRS_hrs_w5_sex$id)
HRS_ds_hrs_w5$sex <- car::recode(HRS_hrs_w5_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_hrs5, echo=FALSE}
vari <- HRS_ds_hrs_w5$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w5, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs5, echo=FALSE}
AfterH <- table(HRS_ds_hrs_w5$sex)
BeforeH <- table(HRS_hrs_w5_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 





### Wave 6

#### Study-specific variable description

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-HRS-w6`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_hrs6, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_hrs_w6_sex','HRS.HRS-HRS-w6',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_hrs_w6_sex <- opal.execute(o,'HRS_hrs_w6_sex')
```

```{r local_hrs6, echo=FALSE}
vari <- HRS_hrs_w6_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w6_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_hrs6, echo=TRUE}
HRS_ds_hrs_w6 <- tibble(id=HRS_hrs_w6_sex$id)
HRS_ds_hrs_w6$sex <- car::recode(HRS_hrs_w6_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_hrs6, echo=FALSE}
vari <- HRS_ds_hrs_w6$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w6, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs6, echo=FALSE}
AfterH <- table(HRS_ds_hrs_w6$sex)
BeforeH <- table(HRS_hrs_w6_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 
 




### Wave 7

#### Study-specific variable description

 

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-HRS-w7`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_hrs7, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_hrs_w7_sex','HRS.HRS-HRS-w7',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_hrs_w7_sex <- opal.execute(o,'HRS_hrs_w7_sex')
```

```{r local_hrs7, echo=FALSE}
vari <- HRS_hrs_w7_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w7_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_hrs7, echo=TRUE}
HRS_ds_hrs_w7 <- tibble(id=HRS_hrs_w7_sex$id)
HRS_ds_hrs_w7$sex <- car::recode(HRS_hrs_w7_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_hrs7, echo=FALSE}
vari <- HRS_ds_hrs_w7$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w7, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs7, echo=FALSE}
AfterH <- table(HRS_ds_hrs_w7$sex)
BeforeH <- table(HRS_hrs_w7_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 






### Wave 8

#### Study-specific variable description

 

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-HRS-w8`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_hrs8, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_hrs_w8_sex','HRS.HRS-HRS-w8',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_hrs_w8_sex <- opal.execute(o,'HRS_hrs_w8_sex')
```

```{r local_hrs8, echo=FALSE}
vari <- HRS_hrs_w8_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w8_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_hrs8, echo=TRUE}
HRS_ds_hrs_w8 <- tibble(id=HRS_hrs_w8_sex$id)
HRS_ds_hrs_w8$sex <- car::recode(HRS_hrs_w8_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_hrs8, echo=FALSE}
vari <- HRS_ds_hrs_w8$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w8, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs8, echo=FALSE}
AfterH <- table(HRS_ds_hrs_w8$sex)
BeforeH <- table(HRS_hrs_w8_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 
 

### Wave 9

#### Study-specific variable description

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-HRS-w9`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_hrs9, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_hrs_w9_sex','HRS.HRS-HRS-w9',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_hrs_w9_sex <- opal.execute(o,'HRS_hrs_w9_sex')
```

```{r local_hrs9, echo=FALSE}
vari <- HRS_hrs_w9_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w9_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_hrs9, echo=TRUE}
HRS_ds_hrs_w9 <- tibble(id=HRS_hrs_w9_sex$id)
HRS_ds_hrs_w9$sex <- car::recode(HRS_hrs_w9_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_hrs9, echo=FALSE}
vari <- HRS_ds_hrs_w9$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w9, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs9, echo=FALSE}
AfterH <- table(HRS_ds_hrs_w9$sex)
BeforeH <- table(HRS_hrs_w9_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 
 





### Wave 10

#### Study-specific variable description

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-HRS-w10`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_hrs10, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_hrs_w10_sex','HRS.HRS-HRS-w10',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_hrs_w10_sex <- opal.execute(o,'HRS_hrs_w10_sex')
```

```{r local_hrs10, echo=FALSE}
vari <- HRS_hrs_w10_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w10_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_hrs10, echo=TRUE}
HRS_ds_hrs_w10 <- tibble(id=HRS_hrs_w10_sex$id)
HRS_ds_hrs_w10$sex <- car::recode(HRS_hrs_w10_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_hrs10, echo=FALSE}
vari <- HRS_ds_hrs_w10$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w10, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs10, echo=FALSE}
AfterH <- table(HRS_ds_hrs_w10$sex)
BeforeH <- table(HRS_hrs_w10_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 
 



### Wave 11

#### Study-specific variable description

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-HRS-w11`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_hrs11, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_hrs_w11_sex','HRS.HRS-HRS-w11',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_hrs_w11_sex <- opal.execute(o,'HRS_hrs_w11_sex')
```

```{r local_hrs11, echo=FALSE}
vari <- HRS_hrs_w11_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w11_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_hrs11, echo=TRUE}
HRS_ds_hrs_w11 <- tibble(id=HRS_hrs_w11_sex$id)
HRS_ds_hrs_w11$sex <- car::recode(HRS_hrs_w11_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_hrs11, echo=FALSE}
vari <- HRS_ds_hrs_w11$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w11, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs11, echo=FALSE}
AfterH <- table(HRS_ds_hrs_w11$sex)
BeforeH <- table(HRS_hrs_w11_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 
 

## AHEAD sub-sample

### Wave 2 

#### Study-specific variable description

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-AHEAD-w2`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_ahead2, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ahead_w2_sex','HRS.HRS-AHEAD-w2',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_ahead_w2_sex <- opal.execute(o,'HRS_ahead_w2_sex')
```

```{r local_ahead2, echo=FALSE}
vari <- HRS_ahead_w2_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w2_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_ahead2, echo=TRUE}
HRS_ds_ahead_w2 <- tibble(id=HRS_ahead_w2_sex$id)
HRS_ds_ahead_w2$sex <- car::recode(HRS_ahead_w2_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_ahead2, echo=FALSE}
vari <- HRS_ds_ahead_w2$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w2, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead2, echo=FALSE}
AfterH <- table(HRS_ds_ahead_w2$sex)
BeforeH <- table(HRS_ahead_w2_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 




### Wave 3 

#### Study-specific variable description

 

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-AHEAD-w3`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_ahead3, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ahead_w3_sex','HRS.HRS-AHEAD-w3',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_ahead_w3_sex <- opal.execute(o,'HRS_ahead_w3_sex')
```

```{r local_ahead3, echo=FALSE}
vari <- HRS_ahead_w3_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w3_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_ahead3, echo=TRUE}
HRS_ds_ahead_w3 <- tibble(id=HRS_ahead_w3_sex$id)
HRS_ds_ahead_w3$sex <- car::recode(HRS_ahead_w3_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_ahead3, echo=FALSE}
vari <- HRS_ds_ahead_w3$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w3, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead3, echo=FALSE}
AfterH <- table(HRS_ds_ahead_w3$sex)
BeforeH <- table(HRS_ahead_w3_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 






### Wave 4 

#### Study-specific variable description

 

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-AHEAD-w4`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_ahead4, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ahead_w4_sex','HRS.HRS-AHEAD-w4',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_ahead_w4_sex <- opal.execute(o,'HRS_ahead_w4_sex')
```

```{r local_ahead4, echo=FALSE}
vari <- HRS_ahead_w4_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w4_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_ahead4, echo=TRUE}
HRS_ds_ahead_w4 <- tibble(id=HRS_ahead_w4_sex$id)
HRS_ds_ahead_w4$sex <- car::recode(HRS_ahead_w4_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_ahead4, echo=FALSE}
vari <- HRS_ds_ahead_w4$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w4, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead4, echo=FALSE}
AfterH <- table(HRS_ds_ahead_w4$sex)
BeforeH <- table(HRS_ahead_w4_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 






### Wave 5 

#### Study-specific variable description

 

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-AHEAD-w5`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_ahead5, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ahead_w5_sex','HRS.HRS-AHEAD-w5',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_ahead_w5_sex <- opal.execute(o,'HRS_ahead_w5_sex')
```

```{r local_ahead5, echo=FALSE}
vari <- HRS_ahead_w5_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w5_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_ahead5, echo=TRUE}
HRS_ds_ahead_w5 <- tibble(id=HRS_ahead_w5_sex$id)
HRS_ds_ahead_w5$sex <- car::recode(HRS_ahead_w5_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_ahead5, echo=FALSE}
vari <- HRS_ds_ahead_w5$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w5, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead5, echo=FALSE}
AfterH <- table(HRS_ds_ahead_w5$sex)
BeforeH <- table(HRS_ahead_w5_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 
 



### Wave 6 

#### Study-specific variable description

 

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-AHEAD-w6`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_ahead6, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ahead_w6_sex','HRS.HRS-AHEAD-w6',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_ahead_w6_sex <- opal.execute(o,'HRS_ahead_w6_sex')
```

```{r local_ahead6, echo=FALSE}
vari <- HRS_ahead_w6_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w6_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_ahead6, echo=TRUE}
HRS_ds_ahead_w6 <- tibble(id=HRS_ahead_w6_sex$id)
HRS_ds_ahead_w6$sex <- car::recode(HRS_ahead_w6_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_ahead6, echo=FALSE}
vari <- HRS_ds_ahead_w6$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w6, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead6, echo=FALSE}
AfterH <- table(HRS_ds_ahead_w6$sex)
BeforeH <- table(HRS_ahead_w6_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 
 


### Wave 7 

#### Study-specific variable description

 

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-AHEAD-w7`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_ahead7, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ahead_w7_sex','HRS.HRS-AHEAD-w7',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_ahead_w7_sex <- opal.execute(o,'HRS_ahead_w7_sex')
```

```{r local_ahead7, echo=FALSE}
vari <- HRS_ahead_w7_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w7_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_ahead7, echo=TRUE}
HRS_ds_ahead_w7 <- tibble(id=HRS_ahead_w7_sex$id)
HRS_ds_ahead_w7$sex <- car::recode(HRS_ahead_w7_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_ahead7, echo=FALSE}
vari <- HRS_ds_ahead_w7$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w7, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead7, echo=FALSE}
AfterH <- table(HRS_ds_ahead_w7$sex)
BeforeH <- table(HRS_ahead_w7_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 
 





### Wave 8 

#### Study-specific variable description

 

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-AHEAD-w8`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_ahead8, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ahead_w8_sex','HRS.HRS-AHEAD-w8',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_ahead_w8_sex <- opal.execute(o,'HRS_ahead_w8_sex')
```

```{r local_ahead8, echo=FALSE}
vari <- HRS_ahead_w8_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w8_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`
**R script:**

```{r harmo_ahead8, echo=TRUE}
HRS_ds_ahead_w8 <- tibble(id=HRS_ahead_w8_sex$id)
HRS_ds_ahead_w8$sex <- car::recode(HRS_ahead_w8_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_ahead8, echo=FALSE}
vari <- HRS_ds_ahead_w8$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w8, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead8, echo=FALSE}
AfterH <- table(HRS_ds_ahead_w8$sex)
BeforeH <- table(HRS_ahead_w8_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 
 



### Wave 9 

#### Study-specific variable description

 

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-AHEAD-w9`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_ahead9, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ahead_w9_sex','HRS.HRS-AHEAD-w9',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_ahead_w9_sex <- opal.execute(o,'HRS_ahead_w9_sex')
```

```{r local_ahead9, echo=FALSE}
vari <- HRS_ahead_w9_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w9_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_ahead9, echo=TRUE}
HRS_ds_ahead_w9 <- tibble(id=HRS_ahead_w9_sex$id)
HRS_ds_ahead_w9$sex <- car::recode(HRS_ahead_w9_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_ahead9, echo=FALSE}
vari <- HRS_ds_ahead_w9$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w9, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead9, echo=FALSE}
AfterH <- table(HRS_ds_ahead_w9$sex)
BeforeH <- table(HRS_ahead_w9_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 
 


### Wave 10 

#### Study-specific variable description

 

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-AHEAD-w10`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_ahead10, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ahead_w10_sex','HRS.HRS-AHEAD-w10',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_ahead_w10_sex <- opal.execute(o,'HRS_ahead_w10_sex')
```

```{r local_ahead10, echo=FALSE}
vari <- HRS_ahead_w10_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w10_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_ahead10, echo=TRUE}
HRS_ds_ahead_w10 <- tibble(id=HRS_ahead_w10_sex$id)
HRS_ds_ahead_w10$sex <- car::recode(HRS_ahead_w10_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_ahead10, echo=FALSE}
vari <- HRS_ds_ahead_w10$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w10, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead10, echo=FALSE}
AfterH <- table(HRS_ds_ahead_w10$sex)
BeforeH <- table(HRS_ahead_w10_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 


### Wave 11 

#### Study-specific variable description

 

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-AHEAD-w11`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_ahead11, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ahead_w11_sex','HRS.HRS-AHEAD-w11',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_ahead_w11_sex <- opal.execute(o,'HRS_ahead_w11_sex')
```

```{r local_ahead11, echo=FALSE}
vari <- HRS_ahead_w11_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w11_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_ahead11, echo=TRUE}
HRS_ds_ahead_w11 <- tibble(id=HRS_ahead_w11_sex$id)
HRS_ds_ahead_w11$sex <- car::recode(HRS_ahead_w11_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_ahead11, echo=FALSE}
vari <- HRS_ds_ahead_w11$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w11, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead11, echo=FALSE}
AfterH <- table(HRS_ds_ahead_w11$sex)
BeforeH <- table(HRS_ahead_w11_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 
 


### The Children of the Depression (CODA) sub-sample

### Wave 4 

#### Study-specific variable description

 

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-CODA-w4`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_coda4, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_coda_w4_sex','HRS.HRS-CODA-w4',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_coda_w4_sex <- opal.execute(o,'HRS_coda_w4_sex')
```

```{r local_coda4, echo=FALSE}
vari <- HRS_coda_w4_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w4_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_coda4, echo=TRUE}
HRS_ds_coda_w4 <- tibble(id=HRS_coda_w4_sex$id)
HRS_ds_coda_w4$sex <- car::recode(HRS_coda_w4_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_coda4, echo=FALSE}
vari <- HRS_ds_coda_w4$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w4, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_coda4, echo=FALSE}
AfterH <- table(HRS_ds_coda_w4$sex)
BeforeH <- table(HRS_coda_w4_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 
 




### Wave 5 

#### Study-specific variable description

 

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-CODA-w5`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_coda5, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_coda_w5_sex','HRS.HRS-CODA-w5',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_coda_w5_sex <- opal.execute(o,'HRS_coda_w5_sex')
```

```{r local_coda5, echo=FALSE}
vari <- HRS_coda_w5_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w5_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_coda5, echo=TRUE}
HRS_ds_coda_w5 <- tibble(id=HRS_coda_w5_sex$id)
HRS_ds_coda_w5$sex <- car::recode(HRS_coda_w5_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_coda5, echo=FALSE}
vari <- HRS_ds_coda_w5$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w5, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_coda5, echo=FALSE}
AfterH <- table(HRS_ds_coda_w5$sex)
BeforeH <- table(HRS_coda_w5_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 


### Wave 6 

#### Study-specific variable description

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-CODA-w6`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_coda6, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_coda_w6_sex','HRS.HRS-CODA-w6',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_coda_w6_sex <- opal.execute(o,'HRS_coda_w6_sex')
```

```{r local_coda6, echo=FALSE}
vari <- HRS_coda_w6_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w6_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_coda6, echo=TRUE}
HRS_ds_coda_w6 <- tibble(id=HRS_coda_w6_sex$id)
HRS_ds_coda_w6$sex <- car::recode(HRS_coda_w6_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_coda6, echo=FALSE}
vari <- HRS_ds_coda_w6$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w6, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_coda6, echo=FALSE}
AfterH <- table(HRS_ds_coda_w6$sex)
BeforeH <- table(HRS_coda_w6_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 





### Wave 7 

#### Study-specific variable description

 

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-CODA-w7`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_coda7, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_coda_w7_sex','HRS.HRS-CODA-w7',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_coda_w7_sex <- opal.execute(o,'HRS_coda_w7_sex')
```

```{r local_coda7, echo=FALSE}
vari <- HRS_coda_w7_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w7_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_coda7, echo=TRUE}
HRS_ds_coda_w7 <- tibble(id=HRS_coda_w7_sex$id)
HRS_ds_coda_w7$sex <- car::recode(HRS_coda_w7_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_coda7, echo=FALSE}
vari <- HRS_ds_coda_w7$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w7, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_coda7, echo=FALSE}
AfterH <- table(HRS_ds_coda_w7$sex)
BeforeH <- table(HRS_coda_w7_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 



### Wave 8 

#### Study-specific variable description

 

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-CODA-w8`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_coda8, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_coda_w8_sex','HRS.HRS-CODA-w8',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_coda_w8_sex <- opal.execute(o,'HRS_coda_w8_sex')
```

```{r local_coda8, echo=FALSE}
vari <- HRS_coda_w8_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w8_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_coda8, echo=TRUE}
HRS_ds_coda_w8 <- tibble(id=HRS_coda_w8_sex$id)
HRS_ds_coda_w8$sex <- car::recode(HRS_coda_w8_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_coda8, echo=FALSE}
vari <- HRS_ds_coda_w7$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w8, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_coda8, echo=FALSE}
AfterH <- table(HRS_ds_coda_w8$sex)
BeforeH <- table(HRS_coda_w8_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```




### Wave 9 

#### Study-specific variable description

 

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-CODA-w9`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_coda9, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_coda_w9_sex','HRS.HRS-CODA-w9',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_coda_w9_sex <- opal.execute(o,'HRS_coda_w9_sex')
```

```{r local_coda9, echo=FALSE}
vari <- HRS_coda_w9_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w9_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_coda9, echo=TRUE}
HRS_ds_coda_w9 <- tibble(id=HRS_coda_w9_sex$id)
HRS_ds_coda_w9$sex <- car::recode(HRS_coda_w9_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_coda9, echo=FALSE}
vari <- HRS_ds_coda_w9$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w9, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_coda9, echo=FALSE}
AfterH <- table(HRS_ds_coda_w9$sex)
BeforeH <- table(HRS_coda_w9_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 
 




### Wave 10 

#### Study-specific variable description

 

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-CODA-w10`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_coda10, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_coda_w10_sex','HRS.HRS-CODA-w10',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_coda_w10_sex <- opal.execute(o,'HRS_coda_w10_sex')
```

```{r local_coda10, echo=FALSE}
vari <- HRS_coda_w10_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w10_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_coda10, echo=TRUE}
HRS_ds_coda_w10 <- tibble(id=HRS_coda_w10_sex$id)
HRS_ds_coda_w10$sex <- car::recode(HRS_coda_w10_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_coda10, echo=FALSE}
vari <- HRS_ds_coda_w9$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w10, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_coda10, echo=FALSE}
AfterH <- table(HRS_ds_coda_w10$sex)
BeforeH <- table(HRS_coda_w10_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 





### Wave 11 

#### Study-specific variable description

 

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-CODA-w11`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_coda11, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_coda_w11_sex','HRS.HRS-CODA-w11',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_coda_w11_sex <- opal.execute(o,'HRS_coda_w11_sex')
```

```{r local_coda11, echo=FALSE}
vari <- HRS_coda_w11_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w11_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_coda11, echo=TRUE}
HRS_ds_coda_w11 <- tibble(id=HRS_coda_w11_sex$id)
HRS_ds_coda_w11$sex <- car::recode(HRS_coda_w11_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_coda11, echo=FALSE}
vari <- HRS_ds_coda_w11$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w11, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_coda11, echo=FALSE}
AfterH <- table(HRS_ds_coda_w11$sex)
BeforeH <- table(HRS_coda_w11_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 
 



## The War Baby (WB) sub-sample 

### Wave 4  

#### Study-specific variable description

 

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-WB-w4`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_wb4, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_wb_w4_sex','HRS.HRS-WB-w4',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_wb_w4_sex <- opal.execute(o,'HRS_wb_w4_sex')
```

```{r local_wb4, echo=FALSE}
vari <- HRS_wb_w4_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w4_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_wb4, echo=TRUE}
HRS_ds_wb_w4 <- tibble(id=HRS_wb_w4_sex$id)
HRS_ds_wb_w4$sex <- car::recode(HRS_wb_w4_sex$RAGENDER, "1='1'; 2='0'")


```


#### Statistical description of the new harmonised variable
```{r descript_wb4, echo=FALSE}
vari <- HRS_ds_wb_w4$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w4, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_wb4, echo=FALSE}
AfterH <- table(HRS_ds_wb_w4$sex)
BeforeH <- table(HRS_wb_w4_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 
 



### Wave 5  

#### Study-specific variable description

 

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-WB-w5`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_wb5, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_wb_w5_sex','HRS.HRS-WB-w5',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_wb_w5_sex <- opal.execute(o,'HRS_wb_w5_sex')
```

```{r local_wb5, echo=FALSE}
vari <- HRS_wb_w5_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w5_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_wb5, echo=TRUE}
HRS_ds_wb_w5 <- tibble(id=HRS_wb_w5_sex$id)
HRS_ds_wb_w5$sex <- car::recode(HRS_wb_w5_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_wb5, echo=FALSE}
vari <- HRS_ds_wb_w5$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w5, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_wb5, echo=FALSE}
AfterH <- table(HRS_ds_wb_w5$sex)
BeforeH <- table(HRS_wb_w5_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 
 


### Wave 6  

#### Study-specific variable description

 

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-WB-w6`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_wb6, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_wb_w6_sex','HRS.HRS-WB-w6',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_wb_w6_sex <- opal.execute(o,'HRS_wb_w6_sex')
```

```{r local_wb6, echo=FALSE}
vari <- HRS_wb_w6_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w6_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_wb6, echo=TRUE}
HRS_ds_wb_w6 <- tibble(id=HRS_wb_w6_sex$id)
HRS_ds_wb_w6$sex <- car::recode(HRS_wb_w6_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_wb6, echo=FALSE}
vari <- HRS_ds_wb_w6$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w6, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_wb6, echo=FALSE}
AfterH <- table(HRS_ds_wb_w6$sex)
BeforeH <- table(HRS_wb_w6_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 
 




### Wave 7  

#### Study-specific variable description

 

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-WB-w7`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_wb7, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_wb_w7_sex','HRS.HRS-WB-w7',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_wb_w7_sex <- opal.execute(o,'HRS_wb_w7_sex')
```

```{r local_wb7, echo=FALSE}
vari <- HRS_wb_w7_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w7_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_wb7, echo=TRUE}
HRS_ds_wb_w7 <- tibble(id=HRS_wb_w7_sex$id)
HRS_ds_wb_w7$sex <- car::recode(HRS_wb_w7_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_wb7, echo=FALSE}
vari <- HRS_ds_wb_w7$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w7, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_wb7, echo=FALSE}
AfterH <- table(HRS_ds_wb_w7$sex)
BeforeH <- table(HRS_wb_w7_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 
 


### Wave 8  

#### Study-specific variable description

 

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-WB-w8`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_wb8, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_wb_w8_sex','HRS.HRS-WB-w8',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_wb_w8_sex <- opal.execute(o,'HRS_wb_w8_sex')
```

```{r local_wb8, echo=FALSE}
vari <- HRS_wb_w8_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w8_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_wb8, echo=TRUE}
HRS_ds_wb_w8 <- tibble(id=HRS_wb_w8_sex$id)
HRS_ds_wb_w8$sex <- car::recode(HRS_wb_w8_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_wb8, echo=FALSE}
vari <- HRS_ds_wb_w8$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w8, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_wb8, echo=FALSE}
AfterH <- table(HRS_ds_wb_w8$sex)
BeforeH <- table(HRS_wb_w8_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 
 



### Wave 9  

#### Study-specific variable description

 

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-WB-w9`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_wb9, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_wb_w9_sex','HRS.HRS-WB-w9',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_wb_w9_sex <- opal.execute(o,'HRS_wb_w9_sex')
```

```{r local_wb9, echo=FALSE}
vari <- HRS_wb_w9_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w9_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_wb9, echo=TRUE}
HRS_ds_wb_w9 <- tibble(id=HRS_wb_w9_sex$id)
HRS_ds_wb_w9$sex <- car::recode(HRS_wb_w9_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_wb9, echo=FALSE}
vari <- HRS_ds_wb_w9$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w9, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_wb9, echo=FALSE}
AfterH <- table(HRS_ds_wb_w9$sex)
BeforeH <- table(HRS_wb_w9_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 






### Wave 10  

#### Study-specific variable description

 

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-WB-w10`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_wb10, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_wb_w10_sex','HRS.HRS-WB-w10',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_wb_w10_sex <- opal.execute(o,'HRS_wb_w10_sex')
```

```{r local_wb10, echo=FALSE}
vari <- HRS_wb_w10_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w10_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_wb10, echo=TRUE}
HRS_ds_wb_w10 <- tibble(id=HRS_wb_w10_sex$id)
HRS_ds_wb_w10$sex <- car::recode(HRS_wb_w10_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_wb10, echo=FALSE}
vari <- HRS_ds_wb_w10$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w10, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_wb10, echo=FALSE}
AfterH <- table(HRS_ds_wb_w10$sex)
BeforeH <- table(HRS_wb_w10_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 
 



### Wave 11  

#### Study-specific variable description

 

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-WB-w11`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_wb11, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_wb_w11_sex','HRS.HRS-WB-w11',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_wb_w11_sex <- opal.execute(o,'HRS_wb_w11_sex')
```

```{r local_wb11, echo=FALSE}
vari <- HRS_wb_w11_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w11_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_wb11, echo=TRUE}
HRS_ds_wb_w11 <- tibble(id=HRS_wb_w11_sex$id)
HRS_ds_wb_w11$sex <- car::recode(HRS_wb_w11_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_wb11, echo=FALSE}
vari <- HRS_ds_wb_w11$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w11, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_wb11, echo=FALSE}
AfterH <- table(HRS_ds_wb_w11$sex)
BeforeH <- table(HRS_wb_w11_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 



## The Early Baby Boomer (EBB) sub-sample

### Wave 7  

#### Study-specific variable description

 

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-EBB-w7`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_ebb7, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ebb_w7_sex','HRS.HRS-EBB-w7',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_ebb_w7_sex <- opal.execute(o,'HRS_ebb_w7_sex')
```

```{r local_ebb7, echo=FALSE}
vari <- HRS_ebb_w7_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ebb_w7_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_ebb7, echo=TRUE}
HRS_ds_ebb_w7 <- tibble(id=HRS_ebb_w7_sex$id)
HRS_ds_ebb_w7$sex <- car::recode(HRS_ebb_w7_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_ebb7, echo=FALSE}
vari <- HRS_ds_ebb_w7$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w7, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ebb7, echo=FALSE}
AfterH <- table(HRS_ds_ebb_w7$sex)
BeforeH <- table(HRS_ebb_w7_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 




### Wave 8  

#### Study-specific variable description

 

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-EBB-w8`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_ebb8, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ebb_w8_sex','HRS.HRS-EBB-w8',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_ebb_w8_sex <- opal.execute(o,'HRS_ebb_w8_sex')
```

```{r local_ebb8, echo=FALSE}
vari <- HRS_ebb_w8_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ebb_w8_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_ebb8, echo=TRUE}
HRS_ds_ebb_w8 <- tibble(id=HRS_ebb_w8_sex$id)
HRS_ds_ebb_w8$sex <- car::recode(HRS_ebb_w8_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_ebb8, echo=FALSE}
vari <- HRS_ds_ebb_w8$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w8, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ebb8, echo=FALSE}
AfterH <- table(HRS_ds_ebb_w8$sex)
BeforeH <- table(HRS_ebb_w8_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 





### Wave 9  

#### Study-specific variable description

 

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-EBB-w9`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_ebb9, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ebb_w9_sex','HRS.HRS-EBB-w9',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_ebb_w9_sex <- opal.execute(o,'HRS_ebb_w9_sex')
```

```{r local_ebb9, echo=FALSE}
vari <- HRS_ebb_w9_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ebb_w9_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_ebb9, echo=TRUE}
HRS_ds_ebb_w9 <- tibble(id=HRS_ebb_w9_sex$id)
HRS_ds_ebb_w9$sex <- car::recode(HRS_ebb_w9_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_ebb9, echo=FALSE}
vari <- HRS_ds_ebb_w9$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w9, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ebb9, echo=FALSE}
AfterH <- table(HRS_ds_ebb_w9$sex)
BeforeH <- table(HRS_ebb_w9_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 



### Wave 10  

#### Study-specific variable description

 

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-EBB-w10`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_ebb10, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ebb_w10_sex','HRS.HRS-EBB-w10',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_ebb_w10_sex <- opal.execute(o,'HRS_ebb_w10_sex')
```

```{r local_ebb10, echo=FALSE}
vari <- HRS_ebb_w10_sex$RAGENDER
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ebb_w10_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_ebb10, echo=TRUE}
HRS_ds_ebb_w10 <- tibble(id=HRS_ebb_w10_sex$id)
HRS_ds_ebb_w10$sex <- car::recode(HRS_ebb_w10_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_ebb10, echo=FALSE}
vari <- HRS_ds_ebb_w10$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w10, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ebb10, echo=FALSE}
AfterH <- table(HRS_ds_ebb_w10$sex)
BeforeH <- table(HRS_ebb_w10_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 




### Wave 11  

#### Study-specific variable description

 

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-EBB-w11`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_ebb11, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ebb_w11_sex','HRS.HRS-EBB-w11',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_ebb_w11_sex <- opal.execute(o,'HRS_ebb_w11_sex')
```

```{r local_ebb11, echo=FALSE}
vari <- HRS_ebb_w11_sex$R1AGEY_E
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ebb_w11_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_ebb11, echo=TRUE}
HRS_ds_ebb_w11 <- tibble(id=HRS_ebb_w11_sex$id)
HRS_ds_ebb_w11$sex <- car::recode(HRS_ebb_w11_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_ebb11, echo=FALSE}
vari <- HRS_ds_ebb_w11$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w11, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ebb11, echo=FALSE}
AfterH <- table(HRS_ds_ebb_w11$sex)
BeforeH <- table(HRS_ebb_w11_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 




## The Mid Baby Boomer (MBB) sub-sample

### Wave 10  

#### Study-specific variable description

 

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-MBB-w10`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_mbb10, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_mbb_w10_sex','HRS.HRS-MBB-w10',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_mbb_w10_sex <- opal.execute(o,'HRS_mbb_w10_sex')
```

```{r local_mbb10, echo=FALSE}
vari <- HRS_mbb_w10_sex$R1AGEY_E
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_mbb_w10_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_mbb10, echo=TRUE}
HRS_ds_mbb_w10 <- tibble(id=HRS_mbb_w10_sex$id)
HRS_ds_mbb_w10$sex <- car::recode(HRS_mbb_w10_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_mbb10, echo=FALSE}
vari <- HRS_ds_mbb_w10$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_mbb_w10, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_mbb10, echo=FALSE}
AfterH <- table(HRS_ds_mbb_w10$sex)
BeforeH <- table(HRS_mbb_w10_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 



### Wave 11  

#### Study-specific variable description

 

| **Name** | `RAGENDER`|
|-|-|
| **Label** | `R Gender`|
| **Table name** |`HRS-MBB-w11`|
| **Categories** |`1 = Male`<br/>`2 = Female`|
| **Description** |  |



```{r assign_mbb11, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_mbb_w11_sex','HRS.HRS-MBB-w11',
                         variables=list('RAGENDER'), missings = TRUE)
HRS_mbb_w11_sex <- opal.execute(o,'HRS_mbb_w11_sex')
```

```{r local_mbb11, echo=FALSE}
vari <- HRS_mbb_w11_sex$R1AGEY_E
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attr(vari, "spss::shortName")) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_mbb_w11_sex, aes(x=factor(RAGENDER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `keep 1 "Male" as 1`
* `recode 2 "Female" into 0`
* `NA into 999`

**R script:**

```{r harmo_mbb11, echo=TRUE}
HRS_ds_mbb_w11 <- tibble(id=HRS_mbb_w11_sex$id)
HRS_ds_mbb_w11$sex <- car::recode(HRS_mbb_w11_sex$RAGENDER, "1=1; 2=0; NA=999")


```


#### Statistical description of the new harmonised variable
```{r descript_mbb11, echo=FALSE}
vari <- HRS_ds_mbb_w11$sex
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_mbb_w11, aes(x=factor(sex))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation_mbb11, echo=FALSE}
AfterH <- table(HRS_ds_mbb_w11$sex)
BeforeH <- table(HRS_mbb_w11_sex$RAGENDER)[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1")
kable(C)






```

 
 
 

## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.


```{r helpfunctions, echo=F}
source("../../helpfunctions.r")
```


```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


hrw.hrw.cw <- list(hrs_w1 = c("hrs_w1","HRS w1"), hrs_w2 = c("hrs_w2","HRS w2"), hrs_w3 = c("hrs_w3","HRS w3"), hrs_w4 = c("hrs_w4","HRS w4"), hrs_w5 = c("hrs_w5","HRS w5"), hrs_w6 = c("hrs_w6","HRS w6"), hrs_w7 = c("hrs_w7","HRS w7"), hrs_w8 = c("hrs_w8","HRS w8"), hrs_w9 = c("hrs_w9","HRS w9"), hrs_w10 = c("hrs_w10","HRS w10"), hrs_w11 = c("hrs_w11","HRS w11"))

hrw.ahead.cw <- list(ahead_w2 = c("ahead_w2","AHEAD w2"), ahead_w3 = c("ahead_w3","AHEAD w3"), ahead_w4 = c("ahead_w4","AHEAD w4"), ahead_w5 = c("ahead_w5","AHEAD w5"), ahead_w6 = c("ahead_w6","AHEAD w6"), ahead_w7 = c("ahead_w7","AHEAD w7"), ahead_w8 = c("ahead_w8","AHEAD w8"), ahead_w9 = c("ahead_w9","AHEAD w9"), ahead_w10 = c("ahead_w10","AHEAD w10"), ahead_w11 = c("ahead_w11","AHEAD w11"))

hrw.coda.cw <- list(coda_w4 = c("coda_w4","CODA w4"), coda_w5 = c("coda_w5","CODA w5"), coda_w6 = c("coda_w6","CODA w6"), coda_w7 = c("coda_w7","CODA w7"), coda_w8 = c("coda_w8","CODA w8"), coda_w9 = c("coda_w9","CODA w9"), coda_w10 = c("coda_w10","CODA w10"), coda_w11 = c("coda_w11","CODA w11"))

hrw.wb.cw <- list(wb_w4 = c("wb_w4","WB w4"), wb_w5 = c("wb_w5","WB w5"), wb_w6 = c("wb_w6","WB w6"), wb_w7 = c("wb_w7","WB w7"), wb_w8 = c("wb_w8","WB w8"), wb_w9 = c("wb_w9","WB w9"), wb_w10 = c("wb_w10","WB w10"), wb_w11 = c("wb_w11","WB w11"))

hrw.ebb.cw <- list(ebb_w7 = c("ebb_w7","EBB w7"), ebb_w8 = c("ebb_w8","EBB w8"), ebb_w9 = c("ebb_w9","EBB w9"), ebb_w10 = c("ebb_w10","EBB w10"), ebb_w11 = c("ebb_w11","EBB w11"))

hrw.mbb.cw <- list(mbb_w10 = c("mbb_w10","MBB w10"), mbb_w11 = c("mbb_w11","MBB w11"))



# HRS

# Consider only harmonised waves
l.hds <- lapply(hrw.hrw.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}






# AHEAD

# Consider only harmonised waves
l.hds <- lapply(hrw.ahead.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}





# CODA

# Consider only harmonised waves
l.hds <- lapply(hrw.coda.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}




# WB

# Consider only harmonised waves
l.hds <- lapply(hrw.wb.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



# EBB

# Consider only harmonised waves
l.hds <- lapply(hrw.ebb.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}




# MBB

# Consider only harmonised waves
l.hds <- lapply(hrw.mbb.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}


```




# Quality estimation

No comments.



```{r closeRsession, echo=FALSE} 
opal.logout(o)
```