---
title: "Mobility - Lifting or carrying weights"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `mob_lift`
* Variable label: `Difficulty for lifting or carrying weights`
* Variable description: `Difficulty for lifting or carrying weights`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## Poland

### Wave 1

#### Study-specific variable description


  
  
| **Name** | `h8c`|
|-|-|
| **Label** | `Does your health now limit your ability for lifting or carrying bag of groceries, if so, how much?` |
| **Table name** |`Po_baseline_etic`|
| **Categories** |`Yes, limited a a lot; Yes, limited a little; No, not limited at all`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign pol w1, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_pol_w1_mob_lift','HAPIEE.Po_baseline_etic', variables=list('h8c'), missings = TRUE)
```

```{r local pol w1, echo=F}
HAPIEE_pol_w1_mob_lift <- opal.execute(o,'HAPIEE_pol_w1_mob_lift')
vari <- HAPIEE_pol_w1_mob_lift$h8c
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "h8c")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_pol_w1_mob_lift, aes(x=factor(h8c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Lifting or carrying weights") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

+ `Yes, limited a a lot into 0`
+ `Yes, limited a little into 0`
+ `No, not limited at all into 1`
+ `NA into 999`

**R script:**
```{r harmo pol w1}
HAPIEE_pol_ds_w1 <- tibble(id=HAPIEE_pol_w1_mob_lift$id)
HAPIEE_pol_ds_w1$mob_lift <- car::recode(HAPIEE_pol_w1_mob_lift$h8c, "'Yes, limited a a lot' = '0'; 'Yes, limited a little' = '0'; 'No, not limited at all' = '1';NA = '999' ")
HAPIEE_pol_ds_w1$mob_lift  <- labelled(HAPIEE_pol_ds_w1$mob_lift, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript pol w1, echo=F}
vari <- HAPIEE_pol_ds_w1$mob_lift
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_lift")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HAPIEE_pol_ds_w1, aes(x=factor(mob_lift))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Lifting or carrying weights") + ylab("Frequency")
```

#### Validation
```{r crosstabulation pol w1, echo=F}
AfterH <- table(HAPIEE_pol_ds_w1$mob_lift)
X <- table(HAPIEE_pol_w1_mob_lift$h8c)
BeforeH <- c(sum(X[2:3]),X[1],sum(is.na(HAPIEE_pol_w1_mob_lift$h8c)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("Yes->0","No->1","NA->999") 
kable(C)
```






```{r importOPAL pol w1, echo=FALSE}

label(HAPIEE_pol_ds_w1$mob_lift) <- "Difficulty for lifting or carrying weights"
#opal.assign.data(o, 'HAPIEE_pol_ds_w1', HAPIEE_pol_ds_w1)
#opal.symbol_import(o,'HAPIEE_pol_ds_w1', project='_Athlos_Harm_Dataset')
mob_lift <- HAPIEE_pol_ds_w1
save(mob_lift, file = "../RData/pol_w1/mob_lift.RData")

HAPIEE_pol_m_ds_w1 <- HAPIEE_pol_ds_w1
HAPIEE_pol_m_ds_w1$mob_lift <- car::recode(HAPIEE_pol_m_ds_w1$mob_lift, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_pol_m_ds_w1', HAPIEE_pol_m_ds_w1)
#opal.symbol_import(o,'HAPIEE_pol_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2

#### Study-specific variable description


  
  
| **Name** | ` h2h8c`|
|-|-|
| **Label** | `Does your health now limit your ability for lifting or carrying bag of groceries, if so, how much?` |
| **Table name** |`Po_followup_etic`|
| **Categories** |`Yes, limited a a lot; Yes, limited a little; No, not limited at all`|
| **Missings** |`NA; 9 = Missing`|
| **Description** |  |


```{r assign pol w2, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_pol_w2_mob_lift','HAPIEE.Po_followup_etic', variables=list('h2h8c'), missings = TRUE)
```

```{r local pol w2, echo=F}
HAPIEE_pol_w2_mob_lift <- opal.execute(o,'HAPIEE_pol_w2_mob_lift')
vari <- HAPIEE_pol_w2_mob_lift$h2h8c
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "h2h8c")
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
ggplot(HAPIEE_pol_w2_mob_lift, aes(x=factor(h2h8c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Lifting or carrying weights") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

+ `Yes, limited a lot into 0`
+ `Yes, limited a little into 0`
+ `No, not limited at all into 1`
+ `9 into 999`
+ `NA into 999`

**R script:**
```{r harmo pol w2}
HAPIEE_pol_ds_w2 <- tibble(id=HAPIEE_pol_w2_mob_lift$id)
HAPIEE_pol_ds_w2$mob_lift <- car::recode(HAPIEE_pol_w2_mob_lift$h2h8c, "'Yes, limited a lot' = '0'; 'Yes, limited a little' = '0'; 9 = '999';'No, not limited at all' = '1';NA = '999' ")
HAPIEE_pol_ds_w2$mob_lift  <- labelled(HAPIEE_pol_ds_w2$mob_lift, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript pol w2, echo=F}
vari <- HAPIEE_pol_ds_w2$mob_lift
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_lift")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HAPIEE_pol_ds_w2, aes(x=factor(mob_lift))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Lifting or carrying weights") + ylab("Frequency")
```

#### Validation
```{r crosstabulation pol w2, echo=F}
AfterH <- table(HAPIEE_pol_ds_w2$mob_lift)
X <- table(HAPIEE_pol_w2_mob_lift$h2h8c)
BeforeH <- c(sum(X[3:4]),X[c(2)],sum(X[c(1)],sum(is.na(HAPIEE_pol_w2_mob_lift$h2h8c))))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("Yes->0","No->1","NA->999") 
kable(C)
```






```{r importOPAL pol w2, echo=FALSE}

label(HAPIEE_pol_ds_w2$mob_lift) <- "Difficulty for lifting or carrying weights"
#opal.assign.data(o, 'HAPIEE_pol_ds_w2', HAPIEE_pol_ds_w2)
#opal.symbol_import(o,'HAPIEE_pol_ds_w2', project='_Athlos_Harm_Dataset')
mob_lift <- HAPIEE_pol_ds_w2
save(mob_lift, file = "../RData/pol_w2/mob_lift.RData")

HAPIEE_pol_m_ds_w2 <- HAPIEE_pol_ds_w2
HAPIEE_pol_m_ds_w2$mob_lift <- car::recode(HAPIEE_pol_m_ds_w2$mob_lift, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_pol_m_ds_w2', HAPIEE_pol_m_ds_w2)
#opal.symbol_import(o,'HAPIEE_pol_m_ds_w2', project='_Athlos_Harm_Dataset')
```



## Czech Republic

### Wave 1

#### Study-specific variable description


  
  
| **Name** | `h8c`|
|-|-|
| **Label** | `Does your health now limit your ability for lifting or carrying bag of groceries, if so, how much?` |
| **Table name** |`Cz_baseline_etic`|
| **Categories** |`Yes, limited a a lot; Yes, limited a little; No, not limited at all`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign cz w1, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_cz_w1_mob_lift','HAPIEE.Cz_baseline_etic', variables=list('h8c'), missings = TRUE)
```

```{r local cz w1, echo=F}
HAPIEE_cz_w1_mob_lift <- opal.execute(o,'HAPIEE_cz_w1_mob_lift')
vari <- HAPIEE_cz_w1_mob_lift$h8c
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "h8c")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_cz_w1_mob_lift, aes(x=factor(h8c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Lifting or carrying weights") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:
  
  + `Yes, limited a a lot into 0`
  + `Yes, limited a little into 0`
  + `No, not limited at all into 1`
  + `NA into 999`

**R script:**
```{r harmo cz w1}
HAPIEE_cz_ds_w1 <- tibble(id=HAPIEE_cz_w1_mob_lift$id)
HAPIEE_cz_ds_w1$mob_lift <- car::recode(HAPIEE_cz_w1_mob_lift$h8c, " 'Yes, limited a a lot' = 0; 'Yes, limited a little' = 0; 'No, not limited at all' = 1;NA = '999' ")
HAPIEE_cz_ds_w1$mob_lift  <- labelled(HAPIEE_cz_ds_w1$mob_lift, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript cz w1, echo=F}
vari <- HAPIEE_cz_ds_w1$mob_lift
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_lift")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HAPIEE_cz_ds_w1, aes(x=factor(mob_lift))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Lifting or carrying weights") + ylab("Frequency")
```

#### Validation
```{r crosstabulation cz w1, echo=F}
AfterH <- table(HAPIEE_cz_ds_w1$mob_lift)
X <- table(HAPIEE_cz_w1_mob_lift$h8c)
BeforeH <- c(sum(X[2:3]),X[1],sum(is.na(HAPIEE_cz_w1_mob_lift$h8c)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("Yes->0","No->1","NA->999") 
kable(C)
```






```{r importOPAL cz w1, echo=FALSE}

label(HAPIEE_cz_ds_w1$mob_lift) <- "Difficulty for lifting or carrying weights"
#opal.assign.data(o, 'HAPIEE_cz_ds_w1', HAPIEE_cz_ds_w1)
#opal.symbol_import(o,'HAPIEE_cz_ds_w1', project='_Athlos_Harm_Dataset')
mob_lift <- HAPIEE_cz_ds_w1
save(mob_lift, file = "../RData/cz_w1/mob_lift.RData")

HAPIEE_cz_m_ds_w1 <- HAPIEE_cz_ds_w1
HAPIEE_cz_m_ds_w1$mob_lift <- car::recode(HAPIEE_cz_m_ds_w1$mob_lift, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_cz_m_ds_w1', HAPIEE_cz_m_ds_w1)
#opal.symbol_import(o,'HAPIEE_cz_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2


#### Study-specific variable description


  
  
| **Name** | ` h2h8c`|
|-|-|
| **Label** | `Does your health now limit your ability for lifting or carrying bag of groceries, if so, how much?` |
| **Table name** |`Cz_followup_etic`|
| **Categories** |`Yes, limited a a lot; Yes, limited a little; No, not limited at all`|
| **Missings** |`NA; 9 = Missing`|
| **Description** |  |


```{r assign cz w2, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_cz_w2_mob_lift','HAPIEE.Cz_followup_etic', variables=list('h2h8c'), missings = TRUE)
```

```{r local cz w2, echo=F}
HAPIEE_cz_w2_mob_lift <- opal.execute(o,'HAPIEE_cz_w2_mob_lift')
vari <- HAPIEE_cz_w2_mob_lift$h2h8c
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "h2h8c")
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
ggplot(HAPIEE_cz_w2_mob_lift, aes(x=factor(h2h8c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Lifting or carrying weights") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

+ `Yes, limited a lot into 0`
+ `Yes, limited a little into 0`
+ `No, not limited at all into 1`
+ `9 into 999`
+ `NA into 999`

**R script:**
```{r harmo cz w2}
HAPIEE_cz_ds_w2 <- tibble(id=HAPIEE_cz_w2_mob_lift$id)
HAPIEE_cz_ds_w2$mob_lift <- car::recode(HAPIEE_cz_w2_mob_lift$h2h8c, "'Yes, limited a lot' = '0'; 'Yes, limited a little' = '0'; 9 = '999';'No, not limited at all' = '1';NA = '999' ")
HAPIEE_cz_ds_w2$mob_lift  <- labelled(HAPIEE_cz_ds_w2$mob_lift, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript cz w2, echo=F}
vari <- HAPIEE_cz_ds_w2$mob_lift
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_lift")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HAPIEE_cz_ds_w2, aes(x=factor(mob_lift))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Lifting or carrying weights") + ylab("Frequency")
```

#### Validation
```{r crosstabulation cz w2, echo=F}
AfterH <- table(HAPIEE_cz_ds_w2$mob_lift)
X <- table(HAPIEE_cz_w2_mob_lift$h2h8c)
BeforeH <- c(sum(X[3:4]),X[c(2)],sum(X[c(1)],sum(is.na(HAPIEE_cz_w2_mob_lift$h2h8c))))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("Yes->0","No->1","NA->999") 
kable(C)
```






```{r importOPAL cz w2, echo=FALSE}

label(HAPIEE_cz_ds_w2$mob_lift) <- "Difficulty for lifting or carrying weights"
#opal.assign.data(o, 'HAPIEE_cz_ds_w2', HAPIEE_cz_ds_w2)
#opal.symbol_import(o,'HAPIEE_cz_ds_w2', project='_Athlos_Harm_Dataset')
mob_lift <- HAPIEE_cz_ds_w2
save(mob_lift, file = "../RData/cz_w2/mob_lift.RData")

HAPIEE_cz_m_ds_w2 <- HAPIEE_cz_ds_w2
HAPIEE_cz_m_ds_w2$mob_lift <- car::recode(HAPIEE_cz_m_ds_w2$mob_lift, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_cz_m_ds_w2', HAPIEE_cz_m_ds_w2)
#opal.symbol_import(o,'HAPIEE_cz_m_ds_w2', project='_Athlos_Harm_Dataset')
```



## Lithuania

### Wave 1

#### Study-specific variable description


  
  
| **Name** | `h2h8c`|
|-|-|
| **Label** | `Does your health now limit your ability for lifting or carrying bag of groceries, if so, how much?` |
| **Table name** |`Li_baseline_etic`|
| **Categories** |`Yes, limited a a lot; Yes, limited a little; No, not limited at all`|
| **Missings** |`NA; .c = Don't know`|
| **Description** |  |


```{r assign Li w1, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_Li_w1_mob_lift','HAPIEE.Li_baseline_etic', variables=list('h8c'), missings = TRUE)
```

```{r local Li w1, echo=F}
HAPIEE_Li_w1_mob_lift <- opal.execute(o,'HAPIEE_Li_w1_mob_lift')
vari <- HAPIEE_Li_w1_mob_lift$h8c
kable(Categorical_summary(vari, missing_values = c('.c'))[3], caption = "h8c")
kable(Categorical_summary(vari, missing_values = c('.c'))[1], caption = "Category")
ggplot(HAPIEE_Li_w1_mob_lift, aes(x=factor(h8c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Lifting or carrying weights") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:
  
  + `Yes into 0`
  + `No into 1`
  + `.c into 998`
  + `NA into 999`

**R script:**
```{r harmo Li w1}
HAPIEE_li_ds_w1 <- tibble(id=HAPIEE_Li_w1_mob_lift$id)
HAPIEE_li_ds_w1$mob_lift <- car::recode(HAPIEE_Li_w1_mob_lift$h8c, " 'Yes, limited a a lot' = 0; 'Yes, limited a little' = 0;'.c' = '998'; 'No, not limited at all' = 1;  NA = '999' ")
HAPIEE_li_ds_w1$mob_lift  <- labelled(HAPIEE_li_ds_w1$mob_lift, labels = c(No=1, Yes=0, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Li w1, echo=F}
vari <- HAPIEE_li_ds_w1$mob_lift
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_lift")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HAPIEE_li_ds_w1, aes(x=factor(mob_lift))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Lifting or carrying weights") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Li w1, echo=F}
AfterH <- table(HAPIEE_li_ds_w1$mob_lift)
X <- table(HAPIEE_Li_w1_mob_lift$h8c)
BeforeH <- c(sum(X[3:4]),X[c(2,1)],sum(is.na(HAPIEE_Li_w1_mob_lift$h8c)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("Yes->0","No->1",".c->998","NA->999") 
kable(C)
```






```{r importOPAL Li w1, echo=FALSE}

label(HAPIEE_li_ds_w1$mob_lift) <- "Difficulty for lifting or carrying weights"
#opal.assign.data(o, 'HAPIEE_li_ds_w1', HAPIEE_li_ds_w1)
#opal.symbol_import(o,'HAPIEE_li_ds_w1', project='_Athlos_Harm_Dataset')
mob_lift <- HAPIEE_li_ds_w1
save(mob_lift, file = "../RData/li_w1/mob_lift.RData")

HAPIEE_li_m_ds_w1 <- HAPIEE_li_ds_w1
HAPIEE_li_m_ds_w1$mob_lift <- car::recode(HAPIEE_li_m_ds_w1$mob_lift, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_li_m_ds_w1', HAPIEE_li_m_ds_w1)
#opal.symbol_import(o,'HAPIEE_li_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2

#### Study-specific variable description


  
  
| **Name** | ` h2h8c`|
|-|-|
| **Label** | `Does your health now limit your ability for lifting or carrying bag of groceries, if so, how much?` |
| **Table name** |`Li_followup_etic`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign Li w2, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_Li_w2_mob_lift','HAPIEE.Li_followup_etic', variables=list('h2h8c'), missings = TRUE)
```

```{r local Li w2, echo=F}
HAPIEE_Li_w2_mob_lift <- opal.execute(o,'HAPIEE_Li_w2_mob_lift')
vari <- HAPIEE_Li_w2_mob_lift$h2h8c
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "h2h8c")
#kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#ggplot(HAPIEE_Li_w2_mob_lift, aes(x=factor(h2h8c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Lifting or carrying weights") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:


+ `NA into 999`

**R script:**
```{r harmo Li w2}
HAPIEE_li_ds_w2 <- tibble(id=HAPIEE_Li_w2_mob_lift$id)
HAPIEE_li_ds_w2$mob_lift <- car::recode(HAPIEE_Li_w2_mob_lift$h2h8c, "NA = '999' ")
HAPIEE_li_ds_w2$mob_lift  <- labelled(HAPIEE_li_ds_w2$mob_lift, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Li w2, echo=F}
vari <- HAPIEE_li_ds_w2$mob_lift
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_lift")
#kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
#kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#ggplot(HAPIEE_li_ds_w2, aes(x=factor(mob_lift))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Lifting or carrying weights") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Li w2, echo=F}
AfterH <- table(HAPIEE_li_ds_w2$mob_lift)
X <- table(HAPIEE_Li_w2_mob_lift$h2h8c)
BeforeH <-sum(is.na(HAPIEE_Li_w2_mob_lift$h2h8c))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("NA->999") 
kable(C)
```






```{r importOPAL Li w2, echo=FALSE}

label(HAPIEE_li_ds_w2$mob_lift) <- "Difficulty for lifting or carrying weights"
#opal.assign.data(o, 'HAPIEE_li_ds_w2', HAPIEE_li_ds_w2)
#opal.symbol_import(o,'HAPIEE_li_ds_w2', project='_Athlos_Harm_Dataset')
mob_lift <- HAPIEE_li_ds_w2
save(mob_lift, file = "../RData/li_w2/mob_lift.RData")

HAPIEE_li_m_ds_w2 <- HAPIEE_li_ds_w2
HAPIEE_li_m_ds_w2$mob_lift <- car::recode(HAPIEE_li_m_ds_w2$mob_lift, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_li_m_ds_w2', HAPIEE_li_m_ds_w2)
#opal.symbol_import(o,'HAPIEE_li_m_ds_w2', project='_Athlos_Harm_Dataset')
```



# Quality estimation
No comments.


For the second waves we have chosen the variable `h2h8c` from the 'Postal Ques Survey (2009)'\*, against the variable `h3h8c` from the 'Postal Ques Survey (2012)'\* and against the variable `h4h8c` from the 'Postal Ques Survey (2013)'\* -the last one only available without missings for Czech Republic-.

\* According to the Hapiee_codebook_data_dictionary.

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
