---
title: "Processing speed"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_laia.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `cog_proc_c`
* Variable label: `Cognition - processing speed - Continuous. Test which assesses processing speed`
* Domain: `Health status and functional limitations`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



* Short name: `cog_proc`
* Variable label: `Cognition - processing speed. Test which assesses processing speed. Discrete variable: value 0 = <=25%; value 1 = >25%.`
* Domain: `Health status and functional limitations`
* Value type: `Categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | <=25%
1        | >25%

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Cognition - processing speed"
ds_label_cog_proc_c <- "Cognition - processing speed - Continuous. Test which assesses processing speed"
ds_label_cog_proc <- "Cognition - processing speed. Test which assesses processing speed. Discrete variable: value 0 = <=25%; value 1 = >25%"
```



<!-- ########################################################## --> 

# Data process

## Poland

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:
  
* Name: ` cog10`
* Label: `Concentration task - number of correct letters crossed`
* Categories:
  + `Continuous Variable 0-10`
* Missings
  + `NA` 

```{r assign pol w1, echo=FALSE}
opal.assign.table.tibble(o, 'HAPIEE_pol_w1_cog_proc','HAPIEE.Po_baseline_etic', variables=list('cog10'), missings = TRUE)
HAPIEE_pol_w1_cog_proc <- opal.execute(o,'HAPIEE_pol_w1_cog_proc')
```

```{r local pol w1, echo=FALSE}
vari <- HAPIEE_pol_w1_cog_proc$cog10
kable(Continuous_summary(vari, missing_values = NA)[2], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HAPIEE_pol_w1_cog_proc, aes(x=(cog10))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Processing speed") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_proc_c` from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

To compute the harmonized variable `cog_proc` from `cog_proc_c` it has to be recoded as follows:

* `cog_proc_c <=25% into 0`
* `cog_proc_c >25% into 1`

**R script:**

```{r harmo pol w1}
#cog_proc_c
HAPIEE_pol_ds_w1 <- tibble(id=HAPIEE_pol_w1_cog_proc$id)
HAPIEE_pol_ds_w1$cog_proc_c <- car::recode(HAPIEE_pol_w1_cog_proc$cog10, "NA=999")
HAPIEE_pol_ds_w1$cog_proc_c  <- labelled(HAPIEE_pol_ds_w1$cog_proc_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(HAPIEE_pol_ds_w1$cog_proc_c, "999=NA; 996=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HAPIEE_pol_ds_w1$cog_proc <- car::recode(HAPIEE_pol_ds_w1[[2]], "0:Q=0; (Q+1):65=1")
HAPIEE_pol_ds_w1$cog_proc <- labelled(HAPIEE_pol_ds_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript pol w1, echo=FALSE}
vari <- HAPIEE_pol_ds_w1$cog_proc_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HAPIEE_pol_ds_w1, aes(x=(cog_proc_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency") + xlim(0,60)

vari <- HAPIEE_pol_ds_w1$cog_proc
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HAPIEE_pol_ds_w1, aes(x=factor(cog_proc))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Processing speed") + ylab("Frequency")
```

#### Validation
```{r crosstabulation pol w1, echo=FALSE}
Continous <- c(sum(na.omit(HAPIEE_pol_ds_w1[[2]])<=Q), sum(na.omit(HAPIEE_pol_ds_w1[[2]])>Q & na.omit(HAPIEE_pol_ds_w1[[2]])<900), sum(na.omit(HAPIEE_pol_ds_w1[[2]])==999))
Dicotomic <- table(HAPIEE_pol_ds_w1[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:14->0","15:65->1", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL pol w1, echo=FALSE}
#opal.assign.data(o, 'HAPIEE_pol_ds_w1', HAPIEE_pol_ds_w1)
#opal.symbol_import(o,'HAPIEE_pol_ds_w1', project='_Athlos_Harm_Dataset')

label(HAPIEE_pol_ds_w1$cog_proc_c) <- ds_label_cog_proc_c
label(HAPIEE_pol_ds_w1$cog_proc) <- ds_label_cog_proc
cog_proc <- HAPIEE_pol_ds_w1
save(cog_proc, file = "../RData/pol_w1/cog_proc.RData")
```


### Wave 2

#### Study-specific variable description

The study-specific variables elected to be harmonised is:
  
* Name: ` w2cog10`
* Label: `Number correct`
* Categories:
  + `Continuous Variable 0-10`
* Missings
  + `NA` 

```{r assign pol w2, echo=FALSE}
opal.assign.table.tibble(o, 'HAPIEE_pol_w2_cog_proc','HAPIEE.Po_reexamination_etic', variables=list('w2cog10'), missings = TRUE)
HAPIEE_pol_w2_cog_proc <- opal.execute(o,'HAPIEE_pol_w2_cog_proc')
```

```{r local pol w2, echo=FALSE}
vari <- HAPIEE_pol_w2_cog_proc$w2cog10
kable(Continuous_summary(vari, missing_values = NA)[2], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HAPIEE_pol_w2_cog_proc, aes(x=factor(w2cog10))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Processing speed") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_proc_c` from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

To compute the harmonized variable `cog_proc` from `cog_proc_c` it has to be recoded as follows:

* `cog_proc_c <=25% into 0`
* `cog_proc_c >25% into 1`

**R script:**

```{r harmo pol w2}
#cog_proc_c
HAPIEE_pol_ds_w2 <- tibble(id=HAPIEE_pol_w2_cog_proc$id)
HAPIEE_pol_ds_w2$cog_proc_c <- car::recode(HAPIEE_pol_w2_cog_proc$w2cog10, "NA=999")
HAPIEE_pol_ds_w2$cog_proc_c  <- labelled(HAPIEE_pol_ds_w2$cog_proc_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(HAPIEE_pol_ds_w2$cog_proc_c, "999=NA; 996=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HAPIEE_pol_ds_w2$cog_proc <- car::recode(HAPIEE_pol_ds_w2[[2]], "0:Q=0; (Q+1):65=1")
HAPIEE_pol_ds_w2$cog_proc <- labelled(HAPIEE_pol_ds_w2[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript pol w2, echo=FALSE}
vari <- HAPIEE_pol_ds_w2$cog_proc_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HAPIEE_pol_ds_w2, aes(x=(cog_proc_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency") + xlim(0,60)

vari <- HAPIEE_pol_ds_w2$cog_proc
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HAPIEE_pol_ds_w2, aes(x=factor(cog_proc))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Processing speed") + ylab("Frequency")
```

#### Validation
```{r crosstabulation pol w2, echo=FALSE}
Continous <- c(sum(na.omit(HAPIEE_pol_ds_w2[[2]])<=Q), sum(na.omit(HAPIEE_pol_ds_w2[[2]])>Q & na.omit(HAPIEE_pol_ds_w2[[2]])<900), sum(na.omit(HAPIEE_pol_ds_w2[[2]])==999))
Dicotomic <- table(HAPIEE_pol_ds_w2[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:15->0","16:65->1", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL pol w2, echo=FALSE}
#opal.assign.data(o, 'HAPIEE_pol_ds_w2', HAPIEE_pol_ds_w2)
#opal.symbol_import(o,'HAPIEE_pol_ds_w2', project='_Athlos_Harm_Dataset')

label(HAPIEE_pol_ds_w2$cog_proc_c) <- ds_label_cog_proc_c
label(HAPIEE_pol_ds_w2$cog_proc) <- ds_label_cog_proc
cog_proc <- HAPIEE_pol_ds_w2
save(cog_proc, file = "../RData/pol_w2/cog_proc.RData")
```


## Czech Republic

### Wave 1

#### Study-specific variable description

The study-specific variables elected to be harmonised is:
  
* Name: ` cog10`
* Label: `Concentration task - number of correct letters crossed`
* Categories:
  + `Continuous Variable 0-10`
* Missings
  + `90`
  + `NA` 

```{r assign cz w1, echo=FALSE}
opal.assign.table.tibble(o, 'HAPIEE_cz_w1_cog_proc','HAPIEE.Cz_baseline_etic', variables=list('cog10'), missings = TRUE)
HAPIEE_cz_w1_cog_proc <- opal.execute(o,'HAPIEE_cz_w1_cog_proc')
```

```{r local cz w1, echo=FALSE}
vari <- HAPIEE_cz_w1_cog_proc$cog10
kable(Continuous_summary(var = vari, missing_values = c(90))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(90))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(90))$summary, caption = "Summary")
ggplot(HAPIEE_cz_w1_cog_proc, aes(x=factor(cog10))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Processing speed") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_proc_c` from the study-specific variable the missing values have to be recoded as follows:

* `90 into 999`
* `NA into 999`

To compute the harmonized variable `cog_proc` from `cog_proc_c` it has to be recoded as follows:

* `cog_proc_c <=25% into 0`
* `cog_proc_c >25% into 1`

**R script:**


```{r harmo cz w1}
#cog_proc_c
HAPIEE_cz_ds_w1 <- tibble(id=HAPIEE_cz_w1_cog_proc$id)
HAPIEE_cz_ds_w1$cog_proc_c <- car::recode(HAPIEE_cz_w1_cog_proc$cog10, "90=999; NA=999")
HAPIEE_cz_ds_w1$cog_proc_c  <- labelled(HAPIEE_cz_ds_w1$cog_proc_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(HAPIEE_cz_ds_w1$cog_proc_c, "999=NA; 996=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HAPIEE_cz_ds_w1$cog_proc <- car::recode(HAPIEE_cz_ds_w1[[2]], "0:Q=0; (Q+1):65=1")
HAPIEE_cz_ds_w1$cog_proc <- labelled(HAPIEE_cz_ds_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript cz w1, echo=FALSE}
vari <- HAPIEE_cz_ds_w1$cog_proc_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HAPIEE_cz_ds_w1, aes(x=(cog_proc_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency") + xlim(0,60)

vari <- HAPIEE_cz_ds_w1$cog_proc
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HAPIEE_cz_ds_w1, aes(x=factor(cog_proc))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Processing speed") + ylab("Frequency")
```

#### Validation
```{r crosstabulation cz w1, echo=FALSE}
Continous <- c(sum(na.omit(HAPIEE_cz_ds_w1[[2]])<=Q), sum(na.omit(HAPIEE_cz_ds_w1[[2]])>Q & na.omit(HAPIEE_cz_ds_w1[[2]])<900), sum(na.omit(HAPIEE_cz_ds_w1[[2]])==999))
Dicotomic <- table(HAPIEE_cz_ds_w1[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:15->0","16:65->1", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL cz w1, echo=FALSE}
#opal.assign.data(o, 'HAPIEE_cz_ds_w1', HAPIEE_cz_ds_w1)
#opal.symbol_import(o,'HAPIEE_cz_ds_w1', project='_Athlos_Harm_Dataset')

label(HAPIEE_cz_ds_w1$cog_proc_c) <- ds_label_cog_proc_c
label(HAPIEE_cz_ds_w1$cog_proc) <- ds_label_cog_proc
cog_proc <- HAPIEE_cz_ds_w1
save(cog_proc, file = "../RData/cz_w1/cog_proc.RData")
```




### Wave 2

#### Study-specific variable description

The study-specific variables elected to be harmonised is:
  
* Name: ` w2cog10`
* Label: `Number correct`
* Categories:
  + `Continuous Variable 0-10`
* Missings
  + `NA` 

```{r assign cz w2, echo=FALSE}
opal.assign.table.tibble(o, 'HAPIEE_cz_w2_cog_proc','HAPIEE.Cz_reexamination_etic', variables=list('w2cog10'), missings = TRUE)
HAPIEE_cz_w2_cog_proc <- opal.execute(o,'HAPIEE_cz_w2_cog_proc')
```

```{r local cz w2, echo=FALSE}
vari <- HAPIEE_cz_w2_cog_proc$w2cog10
kable(Continuous_summary(vari, missing_values = NA)[2], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HAPIEE_cz_w2_cog_proc, aes(x=w2cog10)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Processing speed") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_proc_c` from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

To compute the harmonized variable `cog_proc` from `cog_proc_c` it has to be recoded as follows:

* `cog_proc_c <=25% into 0`
* `cog_proc_c >25% into 1`

**R script:**

```{r harmo cz w2}
#cog_proc_c
HAPIEE_cz_ds_w2 <- tibble(id=HAPIEE_cz_w2_cog_proc$id)
HAPIEE_cz_ds_w2$cog_proc_c <- car::recode(HAPIEE_cz_w2_cog_proc$w2cog10, "NA=999")
HAPIEE_cz_ds_w2$cog_proc_c  <- labelled(HAPIEE_cz_ds_w2$cog_proc_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(HAPIEE_cz_ds_w2$cog_proc_c, "999=NA; 996=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HAPIEE_cz_ds_w2$cog_proc <- car::recode(HAPIEE_cz_ds_w2[[2]], "0:Q=0; (Q+1):65=1")
HAPIEE_cz_ds_w2$cog_proc <- labelled(HAPIEE_cz_ds_w2[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript cz w2, echo=FALSE}
vari <- HAPIEE_cz_ds_w2$cog_proc_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HAPIEE_cz_ds_w2, aes(x=(cog_proc_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency") + xlim(0,60)

vari <- HAPIEE_cz_ds_w2$cog_proc
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HAPIEE_cz_ds_w2, aes(x=factor(cog_proc))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Processing speed") + ylab("Frequency")
```

#### Validation
```{r crosstabulation cz w2, echo=FALSE}
Continous <- c(sum(na.omit(HAPIEE_cz_ds_w2[[2]])<=Q), sum(na.omit(HAPIEE_cz_ds_w2[[2]])>Q & na.omit(HAPIEE_cz_ds_w2[[2]])<900), sum(na.omit(HAPIEE_cz_ds_w2[[2]])==999))
Dicotomic <- table(HAPIEE_cz_ds_w2[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:14->0","15:65->1", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```


#### Import to OPAL
```{r importOPAL cz w2, echo=FALSE}
#opal.assign.data(o, 'HAPIEE_cz_ds_w2', HAPIEE_cz_ds_w2)
#opal.symbol_import(o,'HAPIEE_cz_ds_w2', project='_Athlos_Harm_Dataset')

label(HAPIEE_cz_ds_w2$cog_proc_c) <- ds_label_cog_proc_c
label(HAPIEE_cz_ds_w2$cog_proc) <- ds_label_cog_proc
cog_proc <- HAPIEE_cz_ds_w2
save(cog_proc, file = "../RData/cz_w2/cog_proc.RData")
```



## Lithuania 

### Wave 1

#### Study-specific variable description

The study-specific variables elected to be harmonised is:
  
* Name: `cog10`
* Label: `Concentration task - number of correct letters crossed`
* Categories:
  + `Continuous Variable 0-10`
* Missings
  + `NA` 

```{r assign Li w1, echo=FALSE}
opal.assign.table.tibble(o, 'HAPIEE_Li_w1_cog_proc','HAPIEE.Li_baseline_etic', variables=list('cog10'), missings = TRUE)
HAPIEE_Li_w1_cog_proc <- opal.execute(o,'HAPIEE_Li_w1_cog_proc')
```

```{r local Li w1, echo=FALSE}
vari <- HAPIEE_pol_w1_cog_proc$cog10
kable(Continuous_summary(vari, missing_values = NA)[2], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HAPIEE_Li_w1_cog_proc, aes(x=factor(cog10))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Processing speed") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_proc_c` from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

To compute the harmonized variable `cog_proc` from `cog_proc_c` it has to be recoded as follows:

* `cog_proc_c <=25% into 0`
* `cog_proc_c >25% into 1`

**R script:**

```{r harmo Li w1}
#cog_proc_c
HAPIEE_li_ds_w1 <- tibble(id=HAPIEE_Li_w1_cog_proc$id)
HAPIEE_li_ds_w1$cog_proc_c <- car::recode(HAPIEE_Li_w1_cog_proc$cog10, "NA=999")
HAPIEE_li_ds_w1$cog_proc_c  <- labelled(HAPIEE_li_ds_w1$cog_proc_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(HAPIEE_li_ds_w1$cog_proc_c, "999=NA; 996=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HAPIEE_li_ds_w1$cog_proc <- car::recode(HAPIEE_li_ds_w1[[2]], "0:Q=0; (Q+1):65=1")
HAPIEE_li_ds_w1$cog_proc <- labelled(HAPIEE_li_ds_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript Li w1, echo=FALSE}
vari <- HAPIEE_li_ds_w1$cog_proc_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HAPIEE_li_ds_w1, aes(x=(cog_proc_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency") + xlim(0,60)

vari <- HAPIEE_li_ds_w1$cog_proc
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HAPIEE_li_ds_w1, aes(x=factor(cog_proc))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Processing speed") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Li w1, echo=FALSE}
Continous <- c(sum(na.omit(HAPIEE_li_ds_w1[[2]])<=Q), sum(na.omit(HAPIEE_li_ds_w1[[2]])>Q & na.omit(HAPIEE_li_ds_w1[[2]])<900), sum(na.omit(HAPIEE_li_ds_w1[[2]])==999))
Dicotomic <- table(HAPIEE_li_ds_w1[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:13->0","14:65->1", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL Li w1, echo=FALSE}
#opal.assign.data(o, 'HAPIEE_li_ds_w1', HAPIEE_li_ds_w1)
#opal.symbol_import(o,'HAPIEE_li_ds_w1', project='_Athlos_Harm_Dataset')

label(HAPIEE_li_ds_w1$cog_proc_c) <- ds_label_cog_proc_c
label(HAPIEE_li_ds_w1$cog_proc) <- ds_label_cog_proc
cog_proc <- HAPIEE_li_ds_w1
save(cog_proc, file = "../RData/li_w1/cog_proc.RData")
```




# Quality estimation

No comments



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
