---
title: "Delayed recall"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_laia.r")
```

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `cog_del_c`
* Variable label: `Cognition - delayed recall - Continuous`
* Variable description: `Delayed recall of a list previously employed for measuring Immediate recall. The number of words is exactly the same as in the study-specific variable`
* Domain: `Health status and functional limitations`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



* Short name: `cog_del`
* Variable label: `Cognition - delayed recall`
* Variable description: `Delayed recall of a list of common nouns. Discrete variable: value 0 = <=25%; value 1 = >25%.`
* Domain: `Health status and functional limitations`
* Value type: `Categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | <=25%
1        | >25%

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


```{r lab, echo=FALSE}
ds_label <- "Delayed recall"
ds_label_cog_del_c <- "Delayed recall of a list previously employed for measuring Immediate recall. The number of words is exactly the same as in the study-specific variable"
ds_label_cog_del <- "Delayed recall of a list of common nouns. Discrete variable: value 0 = <=25%; value 1 = >25%"
```

# Data process

## Poland

### Baseline

#### Study-specific variable description

The study-specific variables elected to be harmonised is:
  
* Name: `cog12`
* Label: `Word recall 4 - number correct`
* Categories:
  + `Continuous Variable 0-10`
* Missings
  + `NA` 

```{r assign pol w1, echo=FALSE}
opal.assign.table.tibble(o, 'HAPIEE_pol_w1_cog_del','HAPIEE.Po_baseline_etic', variables=list('cog12'), missings = TRUE)
HAPIEE_pol_w1_cog_del <- opal.execute(o,'HAPIEE_pol_w1_cog_del')
```

```{r local pol w1, echo=FALSE}
vari <- HAPIEE_pol_w1_cog_del$cog12
kable(Continuous_summary(var = vari, missing_values = NA)[3], caption = "Immediate recall continuous")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HAPIEE_pol_w1_cog_del, aes(x=factor(cog12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Delayed recall") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable `cog_del_c` from the study-specific variables you have to sum the total of words and the missing values have to be recoded as follows:

* `NA into 999`

To compute the harmonized variable `cog_del` from `cog_del_c` it has to be recoded as follows:

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**

```{r harmo pol w1}
##cog_del_c
HAPIEE_pol_ds_w1 <- tibble(id=HAPIEE_pol_w1_cog_del$id)
HAPIEE_pol_ds_w1$cog_del_c <- recode(HAPIEE_pol_w1_cog_del$cog12, "NA = 999")
HAPIEE_pol_ds_w1$cog_del_c  <- labelled(HAPIEE_pol_ds_w1$cog_del_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

##cog_del
Q <- quantile(car::recode(HAPIEE_pol_ds_w1$cog_del_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HAPIEE_pol_ds_w1$cog_del <- car::recode(HAPIEE_pol_ds_w1[[2]], "0:Q=0; (Q+1):10=1")
HAPIEE_pol_ds_w1$cog_del <- labelled(HAPIEE_pol_ds_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript pol w1, echo=FALSE}
vari <- HAPIEE_pol_ds_w1$cog_del_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Immediate recall continuous")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HAPIEE_pol_ds_w1, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HAPIEE_pol_ds_w1$cog_del
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Cognition - Immediate recall")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HAPIEE_pol_ds_w1, aes(x=factor(cog_del))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Delayed recall") + ylab("Frequency")
```

#### Validation
```{r crosstabulation pol w1, echo=FALSE}
Continous <- c(sum(na.omit(HAPIEE_pol_ds_w1[[2]])<=Q), sum(na.omit(HAPIEE_pol_ds_w1[[2]])>Q & na.omit(HAPIEE_pol_ds_w1[[2]])<900), sum(na.omit(HAPIEE_pol_ds_w1[[2]])==999))
Dicotomic <- table(HAPIEE_pol_ds_w1[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:3->0","4:10->1","NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```


```{r importOPAL pol w1, echo=FALSE}
label(HAPIEE_pol_ds_w1$cog_del_c) <- ds_label_cog_del_c
label(HAPIEE_pol_ds_w1$cog_del) <- ds_label_cog_del
cog_del <- HAPIEE_pol_ds_w1
save(cog_del, file = "../RData/pol_w1/cog_del.RData")
#opal.assign.data(o, 'HAPIEE_pol_ds_w1', HAPIEE_pol_ds_w1)
#opal.symbol_import(o,'HAPIEE_pol_ds_w1', project='_Athlos_Harm_Dataset')

HAPIEE_pol_m_ds_w1 <- HAPIEE_pol_ds_w1
HAPIEE_pol_m_ds_w1$cog_del <- recode(HAPIEE_pol_m_ds_w1$cog_del, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
HAPIEE_pol_m_ds_w1$cog_del_c <- recode(HAPIEE_pol_m_ds_w1$cog_del_c, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_pol_m_ds_w1', HAPIEE_pol_m_ds_w1)
#opal.symbol_import(o,'HAPIEE_pol_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Reexamination 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:
  
* Name: `w2cog12`
* Label: `Word recall 4 - number correct`
* Categories:
  + `Continuous Variable 0-10`
* Missings
  + `NA` 

```{r assign pol w2, echo=FALSE}
opal.assign.table.tibble(o, 'HAPIEE_pol_w2_cog_del','HAPIEE.Po_reexamination_etic', variables=list('w2cog12'), missings = TRUE)
HAPIEE_pol_w2_cog_del <- opal.execute(o,'HAPIEE_pol_w2_cog_del')
```

```{r local pol w2, echo=FALSE}
vari <- HAPIEE_pol_w2_cog_del$w2cog12
kable(Continuous_summary(var = vari, missing_values = NA)[3], caption = "Immediate recall continuous")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HAPIEE_pol_w2_cog_del, aes(x=factor(w2cog12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Delayed recall") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable `cog_del_c` from the study-specific variables you have to sum the total of words and the missing values have to be recoded as follows:

* `NA into 999`

To compute the harmonized variable `cog_del` from `cog_del_c` it has to be recoded as follows:

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**

```{r harmo pol w2}
##cog_del_c
HAPIEE_pol_ds_w2 <- tibble(id=HAPIEE_pol_w2_cog_del$id)
HAPIEE_pol_ds_w2$cog_del_c <- recode(HAPIEE_pol_w2_cog_del$w2cog12, "NA = '999' ")
HAPIEE_pol_ds_w2$cog_del_c  <- labelled(HAPIEE_pol_ds_w2$cog_del_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

##cog_del
Q <- quantile(car::recode(HAPIEE_pol_ds_w2$cog_del_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HAPIEE_pol_ds_w2$cog_del <- car::recode(HAPIEE_pol_ds_w2[[2]], "0:Q=0; (Q+1):10=1")
HAPIEE_pol_ds_w2$cog_del <- labelled(HAPIEE_pol_ds_w2[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript pol w2, echo=FALSE}
vari <- HAPIEE_pol_ds_w2$cog_del_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Immediate recall continuous")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HAPIEE_pol_ds_w2, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HAPIEE_pol_ds_w2$cog_del
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Cognition - Immediate recall")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HAPIEE_pol_ds_w2, aes(x=factor(cog_del))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Delayed recall") + ylab("Frequency")
```

#### Validation
```{r crosstabulation pol w2, echo=FALSE}
Continous <- c(sum(na.omit(HAPIEE_pol_ds_w2[[2]])<=Q), sum(na.omit(HAPIEE_pol_ds_w2[[2]])>Q & na.omit(HAPIEE_pol_ds_w2[[2]])<900), sum(na.omit(HAPIEE_pol_ds_w2[[2]])==999))
Dicotomic <- table(HAPIEE_pol_ds_w2[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:6->0","7:10->1","NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL pol w2, echo=FALSE}
label(HAPIEE_pol_ds_w2$cog_del_c) <- ds_label_cog_del_c
label(HAPIEE_pol_ds_w2$cog_del) <- ds_label_cog_del
cog_del <- HAPIEE_pol_ds_w2
save(cog_del, file = "../RData/pol_w2/cog_del.RData")
#opal.assign.data(o, 'HAPIEE_pol_ds_w2', HAPIEE_pol_ds_w2)
#opal.symbol_import(o,'HAPIEE_pol_ds_w2', project='_Athlos_Harm_Dataset')

HAPIEE_pol_m_ds_w2 <- HAPIEE_pol_ds_w2
HAPIEE_pol_m_ds_w2$cog_del <- recode(HAPIEE_pol_m_ds_w2$cog_del, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
HAPIEE_pol_m_ds_w2$cog_del_c <- recode(HAPIEE_pol_m_ds_w2$cog_del_c, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_pol_m_ds_w2', HAPIEE_pol_m_ds_w2)
#opal.symbol_import(o,'HAPIEE_pol_m_ds_w2', project='_Athlos_Harm_Dataset')
```



## Czech Republic

### Baseline

#### Study-specific variable description

The study-specific variables elected to be harmonised is:
  
* Name: `cog12`
* Label: `Word recall 4 - number correct`
* Categories:
  + `Continuous Variable 0-10`
* Missings
  + `NA` 

```{r assign cz w1, echo=FALSE}
opal.assign.table.tibble(o, 'HAPIEE_cz_w1_cog_del','HAPIEE.Cz_baseline_etic', variables=list('cog12'), missings = TRUE)
HAPIEE_cz_w1_cog_del <- opal.execute(o,'HAPIEE_cz_w1_cog_del')
```

```{r local cz w1, echo=FALSE}
vari <- HAPIEE_cz_w1_cog_del$cog12
kable(Continuous_summary(var = vari, missing_values = NA)[3], caption = "Immediate recall continuous")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HAPIEE_cz_w1_cog_del, aes(x=factor(cog12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Delayed recall") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable `cog_del_c` from the study-specific variables you have to sum the total of words and the missing values have to be recoded as follows:

* `NA into 999`

To compute the harmonized variable `cog_del` from `cog_del_c` it has to be recoded as follows:

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**

```{r harmo cz w1}
##cog_del_c
HAPIEE_cz_ds_w1 <- tibble(id=HAPIEE_cz_w1_cog_del$id)
HAPIEE_cz_ds_w1$cog_del_c <- recode(HAPIEE_cz_w1_cog_del$cog12, "NA = 999")
HAPIEE_cz_ds_w1$cog_del_c  <- labelled(HAPIEE_cz_ds_w1$cog_del_c, labels = c( "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

##cog_del
Q <- quantile(car::recode(HAPIEE_cz_ds_w1$cog_del_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HAPIEE_cz_ds_w1$cog_del <- car::recode(HAPIEE_cz_ds_w1[[2]], "0:Q=0; (Q+1):10=1")
HAPIEE_cz_ds_w1$cog_del <- labelled(HAPIEE_cz_ds_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript cz w1, echo=FALSE}
vari <- HAPIEE_cz_ds_w1$cog_del_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Immediate recall continuous")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HAPIEE_cz_ds_w1, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HAPIEE_cz_ds_w1$cog_del
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Cognition - Immediate recall")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HAPIEE_cz_ds_w1, aes(x=factor(cog_del))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Delayed recall") + ylab("Frequency")
```

#### Validation
```{r crosstabulation cz w1, echo=FALSE}
Continous <- c(sum(na.omit(HAPIEE_cz_ds_w1[[2]])<=Q), sum(na.omit(HAPIEE_cz_ds_w1[[2]])>Q & na.omit(HAPIEE_cz_ds_w1[[2]])<900), sum(na.omit(HAPIEE_cz_ds_w1[[2]])==999))
Dicotomic <- table(HAPIEE_cz_ds_w1[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:7->0","8:10->1","NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL cz w1, echo=FALSE}
label(HAPIEE_cz_ds_w1$cog_del_c) <- ds_label_cog_del_c
label(HAPIEE_cz_ds_w1$cog_del) <- ds_label_cog_del
cog_del <- HAPIEE_cz_ds_w1
save(cog_del, file = "../RData/cz_w1/cog_del.RData")
#opal.assign.data(o, 'HAPIEE_cz_ds_w1', HAPIEE_cz_ds_w1)
#opal.symbol_import(o,'HAPIEE_cz_ds_w1', project='_Athlos_Harm_Dataset')

HAPIEE_cz_m_ds_w1 <- HAPIEE_cz_ds_w1
HAPIEE_cz_m_ds_w1$cog_del <- recode(HAPIEE_cz_m_ds_w1$cog_del, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
HAPIEE_cz_m_ds_w1$cog_del_c <- recode(HAPIEE_cz_m_ds_w1$cog_del_c, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_cz_m_ds_w1', HAPIEE_cz_m_ds_w1)
#opal.symbol_import(o,'HAPIEE_cz_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Reexamination

#### Study-specific variable description

The study-specific variables elected to be harmonised is:
  
* Name: ` w2cog12`
* Label: `Word recall 4 - number correct`
* Categories:
  + `Continuous Variable 0-10`
* Missings
  + `NA` 
  + `9`

```{r assign cz w2, echo=FALSE}
opal.assign.table.tibble(o, 'HAPIEE_cz_w2_cog_del','HAPIEE.Cz_reexamination_etic', variables=list('w2cog12'), missings = TRUE)
HAPIEE_cz_w2_cog_del <- opal.execute(o,'HAPIEE_cz_w2_cog_del')
```

```{r local cz w2, echo=FALSE}
vari <- HAPIEE_cz_w2_cog_del$w2cog12
kable(Continuous_summary(var = vari, missing_values = NA)[3], caption = "Immediate recall continuous")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HAPIEE_cz_w2_cog_del, aes(x=factor(w2cog12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Delayed recall") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable `cog_del_c` from the study-specific variables you have to sum the total of words and the missing values have to be recoded as follows:

* `NA into 999`

To compute the harmonized variable `cog_del` from `cog_del_c` it has to be recoded as follows:

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**

```{r harmo cz w2}
##cog_del_c
HAPIEE_cz_ds_w2 <- tibble(id=HAPIEE_cz_w2_cog_del$id)
HAPIEE_cz_ds_w2$cog_del_c <- recode(HAPIEE_cz_w2_cog_del$w2cog12, "NA = 999")
HAPIEE_cz_ds_w2$cog_del_c  <- labelled(HAPIEE_cz_ds_w2$cog_del_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

##cog_del
Q <- quantile(car::recode(HAPIEE_cz_ds_w2$cog_del_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HAPIEE_cz_ds_w2$cog_del <- car::recode(HAPIEE_cz_ds_w2[[2]], "0:Q=0; (Q+1):10=1")
HAPIEE_cz_ds_w2$cog_del <- labelled(HAPIEE_cz_ds_w2[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript cz w2, echo=FALSE}
vari <- HAPIEE_cz_ds_w2$cog_del_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Immediate recall continuous")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HAPIEE_cz_ds_w2, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HAPIEE_cz_ds_w2$cog_del
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Cognition - Immediate recall")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HAPIEE_cz_ds_w2, aes(x=factor(cog_del))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Delayed recall") + ylab("Frequency")
```

#### Validation
```{r crosstabulation cz w2, echo=FALSE}
Continous <- c(sum(na.omit(HAPIEE_cz_ds_w2[[2]])<=Q), sum(na.omit(HAPIEE_cz_ds_w2[[2]])>Q & na.omit(HAPIEE_cz_ds_w2[[2]])<900), sum(na.omit(HAPIEE_cz_ds_w2[[2]])==999))
Dicotomic <- table(HAPIEE_cz_ds_w2[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:6->0","7:10->1","NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL cz w2, echo=FALSE}
label(HAPIEE_cz_ds_w2$cog_del_c) <- ds_label_cog_del_c
label(HAPIEE_cz_ds_w2$cog_del) <- ds_label_cog_del
cog_del <- HAPIEE_cz_ds_w2
save(cog_del, file = "../RData/cz_w2/cog_del.RData")
#opal.assign.data(o, 'HAPIEE_cz_ds_w2', HAPIEE_cz_ds_w2)
#opal.symbol_import(o,'HAPIEE_cz_ds_w2', project='_Athlos_Harm_Dataset')

HAPIEE_cz_m_ds_w2 <- HAPIEE_cz_ds_w2
HAPIEE_cz_m_ds_w2$cog_del <- recode(HAPIEE_cz_m_ds_w2$cog_del, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
HAPIEE_cz_m_ds_w2$cog_del_c <- recode(HAPIEE_cz_m_ds_w2$cog_del_c, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_cz_m_ds_w2', HAPIEE_cz_m_ds_w2)
#opal.symbol_import(o,'HAPIEE_cz_m_ds_w2', project='_Athlos_Harm_Dataset')
```



## Lithuania 

### Baseline

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `cog12`
* Label: `Word recall 4 - number correct`
* Categories:
  + `Continuous Variable 0-10`
* Missings
  + `NA` 

```{r assign Li w1, echo=FALSE}
opal.assign.table.tibble(o, 'HAPIEE_Li_w1_cog_del','HAPIEE.Li_baseline_etic', variables=list('cog12'), missings = TRUE)
HAPIEE_Li_w1_cog_del <- opal.execute(o,'HAPIEE_Li_w1_cog_del')
```

```{r local Li w1, echo=FALSE}
vari <- HAPIEE_Li_w1_cog_del$cog12
kable(Continuous_summary(var = vari, missing_values = NA)[3], caption = "Immediate recall continuous")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HAPIEE_Li_w1_cog_del, aes(x=factor(cog12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Delayed recall") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable `cog_del_c` from the study-specific variables you have to sum the total of words and the missing values have to be recoded as follows:

* `NA into 999`

To compute the harmonized variable `cog_del` from `cog_del_c` it has to be recoded as follows:

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**

```{r harmo Li w1}
##cog_del_c
HAPIEE_li_ds_w1 <- tibble(id=HAPIEE_Li_w1_cog_del$id)
HAPIEE_li_ds_w1$cog_del_c <- recode(HAPIEE_Li_w1_cog_del$cog12, " NA = 999")
HAPIEE_li_ds_w1$cog_del_c  <- labelled(HAPIEE_li_ds_w1$cog_del_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

##cog_del
Q <- quantile(car::recode(HAPIEE_li_ds_w1$cog_del_c, "999=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

HAPIEE_li_ds_w1$cog_del <- car::recode(HAPIEE_li_ds_w1[[2]], "0:Q=0; (Q+1):10=1")
HAPIEE_li_ds_w1$cog_del <- labelled(HAPIEE_li_ds_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript Li w1, echo=FALSE}
vari <- HAPIEE_li_ds_w1$cog_del_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Immediate recall continuous")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HAPIEE_li_ds_w1, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- HAPIEE_li_ds_w1$cog_del
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Cognition - Immediate recall")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HAPIEE_li_ds_w1, aes(x=factor(cog_del))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Cognition - Delayed recall") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Li w1, echo=FALSE}
Continous <- c(sum(na.omit(HAPIEE_li_ds_w1[[2]])<=Q), sum(na.omit(HAPIEE_li_ds_w1[[2]])>Q & na.omit(HAPIEE_li_ds_w1[[2]])<900), sum(na.omit(HAPIEE_li_ds_w1[[2]])==999))
Dicotomic <- table(HAPIEE_li_ds_w1[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:7->0","8:10->1","NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL Li w1, echo=FALSE}
label(HAPIEE_li_ds_w1$cog_del_c) <- ds_label_cog_del_c
label(HAPIEE_li_ds_w1$cog_del) <- ds_label_cog_del
cog_del <- HAPIEE_li_ds_w1
save(cog_del, file = "../RData/li_w1/cog_del.RData")
#opal.assign.data(o, 'HAPIEE_li_ds_w1', HAPIEE_li_ds_w1)
#opal.symbol_import(o,'HAPIEE_li_ds_w1', project='_Athlos_Harm_Dataset')

HAPIEE_li_m_ds_w1 <- HAPIEE_li_ds_w1
HAPIEE_li_m_ds_w1$cog_del <- recode(HAPIEE_li_m_ds_w1$cog_del, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
HAPIEE_li_m_ds_w1$cog_del_c <- recode(HAPIEE_li_m_ds_w1$cog_del_c, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_li_m_ds_w1', HAPIEE_li_m_ds_w1)
#opal.symbol_import(o,'HAPIEE_li_m_ds_w1', project='_Athlos_Harm_Dataset')
```



