---
title: "Sleep"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `sleep`
* Variable label: `Sleep`
* Variable description: `Sleeping problems.`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process



## Poland

### Wave 1

#### Study-specific variable description


  
  
| **Name** | `p54k`|
|-|-|
| **Label** | `During the past week: My sleep was restless` |
| **Table name** | `Po_baseline_etic` |
| **Categories** | `1-2 days; 3-4 days; 5-7 days; Less than 1 day` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign pol w1, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_pol_w1_sleep','HAPIEE.Po_baseline_etic', variables=list('p54k'), missings = TRUE)
```

```{r local pol w1, echo=F}
HAPIEE_pol_w1_sleep <- opal.execute(o,'HAPIEE_pol_w1_sleep')
vari <- HAPIEE_pol_w1_sleep$p54k
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "p54k")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_pol_w1_sleep, aes(x=factor(p54k))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:
  
+ `1-2 days into 0` 
+ `3-4 days into 0` 
+ `5-7 days into 0` 
+ `Less than 1 day into 1` 
+ `NA into 999`

**R script:**
```{r harmo pol w1}
HAPIEE_pol_ds_w1 <- tibble(id=HAPIEE_pol_w1_sleep$id)
HAPIEE_pol_ds_w1$sleep <- car::recode(HAPIEE_pol_w1_sleep$p54k, " '1-2 days' = '0';'3-4 days' = '0';'5-7 days' = '0';'Less than 1 day' = '1';NA = '999' ")
HAPIEE_pol_ds_w1$sleep  <- labelled(HAPIEE_pol_ds_w1$sleep, labels = c(No=0, Yes=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript pol w1, echo=F}
vari <- HAPIEE_pol_ds_w1$sleep
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sleep")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HAPIEE_pol_ds_w1, aes(x=factor(sleep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Validation
```{r crosstabulation pol w1, echo=F}
AfterH <- table(HAPIEE_pol_ds_w1$sleep)
X <- table(HAPIEE_pol_w1_sleep$p54k)
BeforeH <- c(sum(X[1:3]),X[4],sum(is.na(HAPIEE_pol_w1_sleep$p54k)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1-2,3-4,5-7 days->0","Less than 1 day->1","NA->999") 
kable(C)
```






```{r importOPAL pol w1, echo=FALSE}

label(HAPIEE_pol_ds_w1$sleep) <- "Sleeping problems"
#opal.assign.data(o, 'HAPIEE_pol_ds_w1', HAPIEE_pol_ds_w1)
#opal.symbol_import(o,'HAPIEE_pol_ds_w1', project='_Athlos_Harm_Dataset')
sleep <- HAPIEE_pol_ds_w1
save(sleep, file = "../RData/pol_w1/sleep.RData")

HAPIEE_pol_m_ds_w1 <- HAPIEE_pol_ds_w1
HAPIEE_pol_m_ds_w1$sleep <- car::recode(HAPIEE_pol_m_ds_w1$sleep, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_pol_m_ds_w1', HAPIEE_pol_m_ds_w1)
#opal.symbol_import(o,'HAPIEE_pol_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2

#### Study-specific variable description


  
  
| **Name** | `w2p54k`|
|-|-|
| **Label** | `W2 CESD10 My sleep was restless` |
| **Table name** | `Po_reexamination_etic` |
| **Categories** | `no; yes` |
| **Missings** | `NA; .b = Refused` |
| **Description** |  |


```{r assign pol w2, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_pol_w2_sleep','HAPIEE.Po_reexamination_etic', variables=list('w2p54k'), missings = TRUE)
```

```{r local pol w2, echo=F}
HAPIEE_pol_w2_sleep <- opal.execute(o,'HAPIEE_pol_w2_sleep')
vari <- HAPIEE_pol_w2_sleep$w2p54k
kable(Categorical_summary(vari, missing_values = c('.b'))[3], caption = "w2p54k")
kable(Categorical_summary(vari, missing_values = c('.b'))[1], caption = "Category")
ggplot(HAPIEE_pol_w2_sleep, aes(x=factor(w2p54k))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:
  
  + `no into 1` 
  + `yes into 0` 
  + `.b Refused into 997` 
  + `NA into 999`
**R script:**
```{r harmo pol w2}
HAPIEE_pol_ds_w2 <- tibble(id=HAPIEE_pol_w2_sleep$id)
HAPIEE_pol_ds_w2$sleep <- car::recode(HAPIEE_pol_w2_sleep$w2p54k, " 'yes' = '0';'no' = '1';'.b' = '997';NA = '999' ")
HAPIEE_pol_ds_w2$sleep  <- labelled(HAPIEE_pol_ds_w2$sleep, labels = c(No=0, Yes=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript pol w2, echo=F}
vari <- HAPIEE_pol_ds_w2$sleep
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sleep")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HAPIEE_pol_ds_w2, aes(x=factor(sleep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Validation
```{r crosstabulation pol w2, echo=F}
AfterH <- table(HAPIEE_pol_ds_w2$sleep)
X <- table(HAPIEE_pol_w2_sleep$w2p54k)
BeforeH <- c(X[3:1],sum(is.na(HAPIEE_pol_w2_sleep$w2p54k)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("yes->0","no->1",".b->997","NA->999") 
kable(C)
```






```{r importOPAL pol w2, echo=FALSE}

label(HAPIEE_pol_ds_w2$sleep) <- "Sleeping problems"
#opal.assign.data(o, 'HAPIEE_pol_ds_w2', HAPIEE_pol_ds_w2)
#opal.symbol_import(o,'HAPIEE_pol_ds_w2', project='_Athlos_Harm_Dataset')
sleep <- HAPIEE_pol_ds_w2
save(sleep, file = "../RData/pol_w2/sleep.RData")

HAPIEE_pol_m_ds_w2 <- HAPIEE_pol_ds_w2
HAPIEE_pol_m_ds_w2$sleep <- car::recode(HAPIEE_pol_m_ds_w2$sleep, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_pol_m_ds_w2', HAPIEE_pol_m_ds_w2)
#opal.symbol_import(o,'HAPIEE_pol_m_ds_w2', project='_Athlos_Harm_Dataset')
```



## Czech Republic

### Wave 1

#### Study-specific variable description


  
  
| **Name** | `p54k`|
|-|-|
| **Label** | `During the past week: My sleep was restless` |
| **Table name** | `Cz_baseline_etic` |
| **Categories** | `1-2 days; 3-4 days; 5-7 days; Less than 1 day` |
| **Missings** | `9; NA` |
| **Description** |  |


```{r assign cz w1, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_cz_w1_sleep','HAPIEE.Cz_baseline_etic', variables=list('p54k'), missings = TRUE)
```

```{r local cz w1, echo=F}
HAPIEE_cz_w1_sleep <- opal.execute(o,'HAPIEE_cz_w1_sleep')
vari <- HAPIEE_cz_w1_sleep$p54k
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "p54k")
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
ggplot(HAPIEE_cz_w1_sleep, aes(x=factor(p54k))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:
  
  + `1-2 days into 0` 
  + `3-4 days into 0` 
  + `5-7 days into 0` 
  + `Less than 1 day into 1` 
  + `9 into 999`
  + `NA into 999`

**R script:**
```{r harmo cz w1}
HAPIEE_cz_ds_w1 <- tibble(id=HAPIEE_cz_w1_sleep$id)
HAPIEE_cz_ds_w1$sleep <- car::recode(HAPIEE_cz_w1_sleep$p54k, " '1-2 days' = '0';'3-4 days' = '0';'5-7 days' = '0';'Less than 1 day' = '1';9 = '999'; NA = '999' ")
HAPIEE_cz_ds_w1$sleep  <- labelled(HAPIEE_cz_ds_w1$sleep, labels = c(No=0, Yes=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript cz w1, echo=F}
vari <- HAPIEE_cz_ds_w1$sleep
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sleep")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HAPIEE_cz_ds_w1, aes(x=factor(sleep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Validation
```{r crosstabulation cz w1, echo=F}
AfterH <- table(HAPIEE_cz_ds_w1$sleep)
X <- table(HAPIEE_cz_w1_sleep$p54k)
BeforeH <- c(sum(X[1:3]),X[5],sum(X[4],sum(is.na(HAPIEE_cz_w1_sleep$p54k))))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1-2,3-4,5-7 days->0","Less than 1 day->1","9,NA->999") 
kable(C)
```






```{r importOPAL cz w1, echo=FALSE}

label(HAPIEE_cz_ds_w1$sleep) <- "Sleeping problems"
#opal.assign.data(o, 'HAPIEE_cz_ds_w1', HAPIEE_cz_ds_w1)
#opal.symbol_import(o,'HAPIEE_cz_ds_w1', project='_Athlos_Harm_Dataset')
sleep <- HAPIEE_cz_ds_w1
save(sleep, file = "../RData/cz_w1/sleep.RData")

HAPIEE_cz_m_ds_w1 <- HAPIEE_cz_ds_w1
HAPIEE_cz_m_ds_w1$sleep <- car::recode(HAPIEE_cz_m_ds_w1$sleep, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_cz_m_ds_w1', HAPIEE_cz_m_ds_w1)
#opal.symbol_import(o,'HAPIEE_cz_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2

#### Study-specific variable description


  
  
| **Name** | `w2p54k`|
|-|-|
| **Label** | `W2 CESD10 My sleep was restless` |
| **Table name** | `Cz_reexamination_etic` |
| **Categories** | `no; yes` |
| **Missings** | `8; NA` |
| **Description** |  |

```{r assign cz w2, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_cz_w2_sleep','HAPIEE.Cz_reexamination_etic', variables=list('w2p54k'), missings = TRUE)
```

```{r local cz w2, echo=F}
HAPIEE_cz_w2_sleep <- opal.execute(o,'HAPIEE_cz_w2_sleep')
vari <- HAPIEE_cz_w2_sleep$w2p54k
kable(Categorical_summary(vari, missing_values = c(8))[3], caption = "w2p54k")
kable(Categorical_summary(vari, missing_values = c(8))[1], caption = "Category")
ggplot(HAPIEE_cz_w2_sleep, aes(x=factor(w2p54k))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:
  
  + `no into 1` 
  + `yes into 0` 
  + `8,NA into 999`


**R script:**
```{r harmo cz w2}
HAPIEE_cz_ds_w2 <- tibble(id=HAPIEE_cz_w2_sleep$id)
HAPIEE_cz_ds_w2$sleep <- car::recode(HAPIEE_cz_w2_sleep$w2p54k, " 'yes' = '0';'no' = '1';'8'='999';NA = '999' ")
HAPIEE_cz_ds_w2$sleep  <- labelled(HAPIEE_cz_ds_w2$sleep, labels = c(No=0, Yes=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript cz w2, echo=F}
vari <- HAPIEE_cz_ds_w2$sleep
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sleep")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HAPIEE_cz_ds_w2, aes(x=factor(sleep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Validation
```{r crosstabulation cz w2, echo=F}
AfterH <- table(HAPIEE_cz_ds_w2$sleep)
X <- table(HAPIEE_cz_w2_sleep$w2p54k)
BeforeH <- c(X[3:2],sum(X[1],sum(is.na(HAPIEE_cz_w2_sleep$w2p54k))))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("yes->0","no->1","8,NA->999") 
kable(C)
```






```{r importOPAL cz w2, echo=FALSE}

label(HAPIEE_cz_ds_w2$sleep) <- "Sleeping problems"
#opal.assign.data(o, 'HAPIEE_cz_ds_w2', HAPIEE_cz_ds_w2)
#opal.symbol_import(o,'HAPIEE_cz_ds_w2', project='_Athlos_Harm_Dataset')
sleep <- HAPIEE_cz_ds_w2
save(sleep, file = "../RData/cz_w2/sleep.RData")

HAPIEE_cz_m_ds_w2 <- HAPIEE_cz_ds_w2
HAPIEE_cz_m_ds_w2$sleep <- car::recode(HAPIEE_cz_m_ds_w2$sleep, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_cz_m_ds_w2', HAPIEE_cz_m_ds_w2)
#opal.symbol_import(o,'HAPIEE_cz_m_ds_w2', project='_Athlos_Harm_Dataset')
```



## Lithuania

### Wave 1

#### Study-specific variable description


  
  
| **Name** | `w2p54k`|
|-|-|
| **Label** | `During the past week: My sleep was restless` |
| **Table name** | `Li_baseline_etic` |
| **Categories** | `1-2 days; 3-4 days; 5-7 days; Less than 1 day` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign Li w1, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_Li_w1_sleep','HAPIEE.Li_baseline_etic', variables=list('w2p54k'), missings = TRUE)
```

```{r local Li w1, echo=F}
HAPIEE_Li_w1_sleep <- opal.execute(o,'HAPIEE_Li_w1_sleep')
vari <- HAPIEE_Li_w1_sleep$w2p54k
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "w2p54k")
#kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#ggplot(HAPIEE_Li_w1_sleep, aes(x=factor(w2p54k))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:
  
  + `1-2 days into 0` 
  + `3-4 days into 0` 
  + `5-7 days into 0` 
  + `Less than 1 day into 1` 
  + `NA into 999`

**R script:**
```{r harmo Li w1}
HAPIEE_li_ds_w1 <- tibble(id=HAPIEE_Li_w1_sleep$id)
HAPIEE_li_ds_w1$sleep <- car::recode(HAPIEE_Li_w1_sleep$w2p54k, " '1-2 days' = '0';'3-4 days' = '0';'5-7 days' = '0';'Less than 1 day' = '1'; NA = '999' ")
HAPIEE_li_ds_w1$sleep  <- labelled(HAPIEE_li_ds_w1$sleep, labels = c(No=0, Yes=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Li w1, echo=F}
vari <- HAPIEE_li_ds_w1$sleep
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sleep")
#kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
#kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#ggplot(HAPIEE_li_ds_w1, aes(x=factor(sleep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Li w1, echo=F}
AfterH <- table(HAPIEE_li_ds_w1$sleep)
X <- table(HAPIEE_Li_w1_sleep$w2p54k)
BeforeH <- c(sum(is.na(HAPIEE_Li_w1_sleep$w2p54k)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("NA->999") 
kable(C)
```






```{r importOPAL Li w1, echo=FALSE}

label(HAPIEE_li_ds_w1$sleep) <- "Sleeping problems"
#opal.assign.data(o, 'HAPIEE_li_ds_w1', HAPIEE_li_ds_w1)
#opal.symbol_import(o,'HAPIEE_li_ds_w1', project='_Athlos_Harm_Dataset')
sleep <- HAPIEE_li_ds_w1
save(sleep, file = "../RData/li_w1/sleep.RData")

HAPIEE_li_m_ds_w1 <- HAPIEE_li_ds_w1
HAPIEE_li_m_ds_w1$sleep <- car::recode(HAPIEE_li_m_ds_w1$sleep, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_li_m_ds_w1', HAPIEE_li_m_ds_w1)
#opal.symbol_import(o,'HAPIEE_li_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2

#### Study-specific variable description


  
  
| **Name** | `w2p54k_lt`|
|-|-|
| **Label** | `CESD10 During the past week: My sleep was restless` |
| **Table name** | `Li_followup_etic` |
| **Categories** | `1-2 days; 3-4 days; 5-7 days; Less than 1 day` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign Li w2, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_Li_w2_sleep','HAPIEE.Li_followup_etic', variables=list('w2p54k_lt'), missings = TRUE)
```

```{r local Li w2, echo=F}
HAPIEE_Li_w2_sleep <- opal.execute(o,'HAPIEE_Li_w2_sleep')
vari <- HAPIEE_Li_w2_sleep$w2p54k_lt
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "w2p54k_lt")
# kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
# ggplot(HAPIEE_Li_w2_sleep, aes(x=factor(w2p54k_lt))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:
  
  + `1-2 days into 0` 
  + `3-4 days into 0` 
  + `5-7 days into 0` 
  + `Less than 1 day into 1` 
  + `NA into 999`

**R script:**
```{r harmo Li w2}
HAPIEE_li_ds_w2 <- tibble(id=HAPIEE_Li_w2_sleep$id)
HAPIEE_li_ds_w2$sleep <- car::recode(HAPIEE_Li_w2_sleep$w2p54k_lt, " '1-2 days' = '0';'3-4 days' = '0';'5-7 days' = '0';'Less than 1 day' = '1';NA = '999' ")
HAPIEE_li_ds_w2$sleep  <- labelled(HAPIEE_li_ds_w2$sleep, labels = c(No=0, Yes=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Li w2, echo=F}
vari <- HAPIEE_li_ds_w2$sleep
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "sleep")
# kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
# kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
# ggplot(HAPIEE_li_ds_w2, aes(x=factor(sleep))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sleep") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Li w2, echo=F}
AfterH <- table(HAPIEE_li_ds_w2$sleep)
X <- table(HAPIEE_Li_w2_sleep$w2p54k_lt)
BeforeH <- sum(is.na(HAPIEE_Li_w2_sleep$w2p54k_lt))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("NA->999") 
kable(C)
```






```{r importOPAL Li w2, echo=FALSE}

label(HAPIEE_li_ds_w2$sleep) <- "Sleeping problems"
#opal.assign.data(o, 'HAPIEE_li_ds_w2', HAPIEE_li_ds_w2)
#opal.symbol_import(o,'HAPIEE_li_ds_w2', project='_Athlos_Harm_Dataset')
sleep <- HAPIEE_li_ds_w2
save(sleep, file = "../RData/li_w2/sleep.RData")

HAPIEE_li_m_ds_w2 <- HAPIEE_li_ds_w2
HAPIEE_li_m_ds_w2$sleep <- car::recode(HAPIEE_li_m_ds_w2$sleep, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HAPIEE_li_m_ds_w2', HAPIEE_li_m_ds_w2)
#opal.symbol_import(o,'HAPIEE_li_m_ds_w2', project='_Athlos_Harm_Dataset')
```



# Quality estimation
The Followup waves variable `w2p54k_lt` is full of missings for each country, 
as it can be seen for Lithuania.

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
