---
title: "Anxiety symptoms"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `anxiety_symp`
* Variable label: `Psychological measure of anxiety symptoms`
* Domain: `Psycological measures`
* Value type: `categorical`
* Category coding:
* Comments: `In this template we will collect any anxiety symptom taking individual questions about worry, trembling, anxiety distress or severity, anxiety in general, other body features or scale items that correspond to these anxiety symptoms. In this sense, here we include a broad definition of anxiety symptoms. On a different variable we will have a more strict definition that will collect "anxiety diagnosis" following consensus criteria of strudies or scale manuals. However, only 5 studies include validated scales as such and most of them are different and some of them do not mention cut-off points, are ambiguous about them, or have different criteria depending on their population.`

**Code** | **Category Label**
-------- | --------------------
0        | no anxiety symptoms
1        | presence of anxiety

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


```{r lab, echo=FALSE}
ds_label <- "Anxiety symptoms"
ds_label_all <- "Psychological measure of anxiety symptoms"
```

<!-- ########################################################## --> 

# Data process

## Finland

### Wave 1 

#### Study-specific variable description

| **Name** | `BA25A3`|
|-|-|
| **Label** | `Illness: psychological or mental illness, anxiety`|
| **Table name** | `t00_athlos_2017_02_23` |
| **Categories** |`0 = no`|
| | `1 = yes` |
| **Description** |  |

```{r assign1,  echo=FALSE}
opal.assign.table.tibble(o, 'Health20002011_as','Health2000-2011.t00_athlos_2017_02_23',
                         variables=list('BA25A3'), missings = TRUE)
Health20002011_as <- opal.execute(o,'Health20002011_as')
```

```{r local1,  echo=FALSE}
vari <- Health20002011_as$BA25A3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_as, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo1,   echo=TRUE}
Health20002011_ds_w1 <- tibble(id=Health20002011_as$id)
Health20002011_ds_w1$anxiety_symp <- car::recode(Health20002011_as[[2]], "NA=999")
Health20002011_ds_w1$anxiety_symp <- labelled(Health20002011_ds_w1$anxiety_symp, labels = c("no anxiety symptoms"=0, "presence of anxiety"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1,  echo=FALSE}
vari <- Health20002011_ds_w1$anxiety_symp
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(Health20002011_ds_w1, aes(x=factor(anxiety_symp))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1,  echo=FALSE}
BeforeH <- table(Health20002011_as[[2]], useNA = 'ifany')
AfterH <- table(Health20002011_ds_w1$anxiety_symp)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```

 
 

 
```{r importOPAL1,  echo=FALSE}
#opal.assign.data(o, 'Health20002011_ds_w1', Health20002011_ds_w1)
#opal.symbol_import(o,'Health20002011_ds_w1', project='_Athlos_Harm_Dataset')
label(Health20002011_ds_w1$anxiety_symp) <- ds_label_all
anxiety_symp <- Health20002011_ds_w1
save(anxiety_symp, file = "../RData/w1/anxiety_symp.RData")
rm(anxiety_symp)

Health20002011_m_ds_w1 <- Health20002011_ds_w1
Health20002011_m_ds_w1$anxiety_symp <- car::recode(Health20002011_m_ds_w1$anxiety_symp, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'Health20002011_m_ds_w1', Health20002011_m_ds_w1)
#opal.symbol_import(o,'Health20002011_m_ds_w1', project='_Athlos_Harm_Dataset')
```







### Wave 2 

#### Study-specific variable description

| **Name** | `BA25A3`|
|-|-|
| **Label** | `Illness: psychological or mental illness, anxiety`|
| **Table name** | `t11_athlos_2017_02_27` |
| **Categories** |`0 = no`|
| | `1 = yes` |
| **Description** |  |

```{r assign2,  echo=FALSE}
opal.assign.table.tibble(o, 'Health20002011_as','Health2000-2011.t11_athlos_2017_02_27',
                         variables=list('BA25A3'), missings = TRUE)
Health20002011_as <- opal.execute(o,'Health20002011_as')
```

```{r local2,  echo=FALSE}
vari <- Health20002011_as$BA25A3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_as, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo2,   echo=TRUE}
Health20002011_ds_w2 <- tibble(id=Health20002011_as$id)
Health20002011_ds_w2$anxiety_symp <- car::recode(Health20002011_as[[2]], "NA=999")
Health20002011_ds_w2$anxiety_symp <- labelled(Health20002011_ds_w2$anxiety_symp, labels = c("no anxiety symptoms"=0, "presence of anxiety"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2,  echo=FALSE}
vari <- Health20002011_ds_w2$anxiety_symp
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(Health20002011_ds_w2, aes(x=factor(anxiety_symp))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2,  echo=FALSE}
BeforeH <- table(Health20002011_as[[2]], useNA = 'ifany')
AfterH <- table(Health20002011_ds_w2$anxiety_symp)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```

 
 

 
```{r importOPAL2,  echo=FALSE}
#opal.assign.data(o, 'Health20002011_ds_w2', Health20002011_ds_w2)
#opal.symbol_import(o,'Health20002011_ds_w2', project='_Athlos_Harm_Dataset')
label(Health20002011_ds_w2$anxiety_symp) <- ds_label_all
anxiety_symp <- Health20002011_ds_w2
save(anxiety_symp, file = "../RData/w2/anxiety_symp.RData")
rm(anxiety_symp)

Health20002011_m_ds_w2 <- Health20002011_ds_w2
Health20002011_m_ds_w2$anxiety_symp <- car::recode(Health20002011_m_ds_w2$anxiety_symp, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'Health20002011_m_ds_w2', Health20002011_m_ds_w2)
#opal.symbol_import(o,'Health20002011_m_ds_w2', project='_Athlos_Harm_Dataset')
```


# Quality estimation

This variable was based in the item: Illness: psychological or mental illness, anxiety.


```{r closeRsession, echo=FALSE,  echo=FALSE} 
opal.logout(o)
```
