---
title: "C-reactive protein (CRP)"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/crpDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/crpDS.R')
```


# Data process


## Spain

### Wave 1


#### Study-specific variable description

| **Name** | `w1crp` |
|-|-|
| **Label** | `C-reactive protein (mg/dL)` |
| **Table name** | `ENRICA_spss_wave1` |
| **Categories:**| `continuous` |
| **Missings:**| `NA` |
| **Description** |  | 

   

```{r assign w1, echo=F }

opal.assign.table.tibble(o, 'ENRICA_w1','ENRICA.ENRICA_spss_wave1', variables=list('w1crp'), missings = TRUE)
ENRICA_w1 <- opal.execute(o,'ENRICA_w1')

```

```{r local w1, echo=F}

vbl <- ENRICA_w1$w1crp
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "w1crp") 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(ENRICA_w1, aes(w1crp)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `crp` from the study-specific variable it has to be recoded as follows:

* `crp (mg/l) = w1crp (mg/dl) * 10`
* `NA into 999`

**R script:**

```{r harmo w1}

ENRICA_ds_w1 <- tibble(id=ENRICA_w1$id)
ENRICA_ds_w1$crp <- car::recode(10*ENRICA_w1$w1crp, "NA = 999 ")

```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}

vbl <- ENRICA_ds_w1$crp
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(ENRICA_ds_w1,!vbl %in% miss_values_vector), aes(crp)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w1, echo=F}
```




### Wave 2

Not found.

### Wave 3

Not found.



<!--## Summary of descriptive statistics of the harmonised variable accross populations and waves-->



```{r summ, echo=F}

l.hds <- list(w1 = ENRICA_ds_w1)
m.hds <- list()

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cont_label)
  m_name <- paste0("ENRICA_m_ds_",name)
  assign(m_name, aux_object)
  m.hds[[name]] <- get(paste0("ENRICA_m_ds_",name))
  rm(aux_object)
}

# 
# t.summ <- summary(m.hds[[1]][2])[1:6]
# t.hds <- substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1)
# for (i in seq_along(l.hds)){
#   t.summ <- summary(m.hds[[i]][2])[1:6]
#   t.hds <- cbind(t.hds,as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))))
# }
# t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
# 
# dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],names(l.hds))
# kable(t.hds)

```


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  crp <- l.hds[[index]]
  save(crp, file = paste0(datafolder,names(l.hds)[index],"/crp.RData"))
}

```
<!-- ########################################################## --> 

# Quality estimation


<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```


