---
title: "Any form of religious participation (religious services attendance, religious meetings, religious organization membership, etc.)"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `relig`
* Variable label: `Any form of religious participation`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process

## SHARE

### Wave 1

#### Study-specific variables

The study-specific variables elected to be harmonised are:

* Name: `ac002d6`
* Label: `activities last month: taken part in religious organization?`
* Categories:
    + `0 = not selected`
    + `1 = selected`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`
    

* Name: `ac003_6`
* Label: `How often in the last 4 weeks has he/she taken part in religious organization?`
* Categories:
    + `1 = almost dayli`
    + `2 = almost every week`
    + `3 = less often`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`
 
* Description: 
```{r assign1}
opal.assign.table.tibble(o, 'SHARE_w1_relig','SHARE.sharew1_rel2-6-0_ac',variables=list('ac002d6','ac003_6'), missings = TRUE)
```

```{r local1}
SHARE_w1_relig <- opal.execute(o,'SHARE_w1_relig')
vari <- SHARE_w1_relig$ac002d6
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
#Categorical_summary(var =SHARE_w1_relig$ac002d6, missing_values = NA)
ggplot(SHARE_w1_relig, aes(x=factor(ac002d6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("activities last month: taken part in religious organization?") + ylab("Frequency") 

vari <- SHARE_w1_relig$ac003_6
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
#Categorical_summary(var =SHARE_w1_relig$ac003_6, missing_values = NA)
ggplot(SHARE_w1_relig, aes(x=factor(ac003_6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How often activities in the last 4 weeks has he/she taken part in religious organization?") + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if ac002d6=1 and ac003_6 in c(1,2) then 1`
* `if ac002d6=0 OR ( ac002d6=1 and ac003_6=3 ) then 0`
* `-2 into 997`
* `-1 into 998`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
SHARE_ds_w1 <- tibble(id=SHARE_w1_relig$id)

SHARE_w1_relig$ac002d6 <- car::recode(as.vector(SHARE_w1_relig$ac002d6), "NA='-999'")
SHARE_w1_relig$ac003_6 <- car::recode(as.vector(SHARE_w1_relig$ac003_6), "NA='-999'")

SHARE_ds_w1$relig <- c(NA)  
for(i in 1:dim(SHARE_w1_relig)[1]){
  if( SHARE_w1_relig$ac002d6[i] == 1 & SHARE_w1_relig$ac003_6[i] %in% c(1,2) ) {
    SHARE_ds_w1$relig[i] = 1 }
  else if( SHARE_w1_relig$ac002d6[i] == 0 | ( SHARE_w1_relig$ac002d6[i] == 1 & SHARE_w1_relig$ac003_6[i] == 3 ) ) {
    SHARE_ds_w1$relig[i] = 0 }
  else if( SHARE_w1_relig$ac002d6[i] == -2 | SHARE_w1_relig$ac003_6[i] == -2 ) {
    SHARE_ds_w1$relig[i] = 997 }
  else if( SHARE_w1_relig$ac002d6[i] == -1 | SHARE_w1_relig$ac003_6[i] == -1 ) {
    SHARE_ds_w1$relig[i] = 998 }
}

SHARE_ds_w1$relig <- car::recode(as.vector(SHARE_ds_w1$relig), "NA='999'")
SHARE_ds_w1$relig <- labelled(SHARE_ds_w1$relig, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1}
vari <- SHARE_ds_w1$relig
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_ds_w1$relig, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SHARE_ds_w1, aes(x=factor(relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any form of religious participation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1}
AfterH <- table(SHARE_ds_w1$relig)
BeforeH <- table(SHARE_w1_relig$ac002d6, SHARE_w1_relig$ac003_6, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(sum(BeforeH[4,]), sum(BeforeH[5,5]))
BeforeH1[[2]] <- sum(BeforeH[5,c(3:4)])
BeforeH1[[3]] <- sum(BeforeH[2,1], BeforeH[5,2])
BeforeH1[[4]] <- BeforeH[3,1]
BeforeH1[[5]] <- BeforeH[1,1]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","-2->997","-1->998","NA->999")
kable(C)
```

 
 



### Wave 2

#### Study-specific variables

The study-specific variables elected to be harmonised are:
  
* Name: `ac002d6`
* Label: `activities last month: taken part in religious organization?`
* Categories:
    + `0 = not selected`
    + `1 = selected`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`

* Name: `ac003_6`
* Label: `How often in the last 4 weeks has he/she taken part in religious organization?`
* Categories:
    + `1 = almost dayli`
    + `2 = almost every week`
    + `3 = less often`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`
 
* Description: 
```{r assign2}
opal.assign.table.tibble(o, 'SHARE_w2_relig','SHARE.sharew2_rel2-6-0_ac',variables=list('ac002d6','ac003_6'), missings = TRUE)
```

```{r local2}
SHARE_w2_relig <- opal.execute(o,'SHARE_w2_relig')
vari <- SHARE_w2_relig$ac002d6
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
#Categorical_summary(var =SHARE_w2_relig$ac002d6, missing_values = NA)
ggplot(SHARE_w2_relig, aes(x=factor(ac002d6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("activities last month: taken part in religious organization?") + ylab("Frequency") 

vari <- SHARE_w2_relig$ac003_6
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
#Categorical_summary(var =SHARE_w2_relig$ac003_6, missing_values = NA)
ggplot(SHARE_w2_relig, aes(x=factor(ac003_6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How often activities in the last 4 weeks has he/she taken part in religious organization?") + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if ac002d6=1 and ac003_6 in c(1,2) then 1`
* `if ac002d6=0 OR ( ac002d6=1 and ac003_6=3 ) then 0`
* `-2 into 997`
* `-1 into 998`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
SHARE_ds_w2 <- tibble(id=SHARE_w2_relig$id)

SHARE_w2_relig$ac002d6 <- car::recode(as.vector(SHARE_w2_relig$ac002d6), "NA='-999'")
SHARE_w2_relig$ac003_6 <- car::recode(as.vector(SHARE_w2_relig$ac003_6), "NA='-999'")

SHARE_ds_w2$relig <- c(NA)  
for(i in 1:dim(SHARE_w2_relig)[1]){
  if( SHARE_w2_relig$ac002d6[i] == 1 & SHARE_w2_relig$ac003_6[i] %in% c(1,2) ) {
    SHARE_ds_w2$relig[i] = 1 }
  else if( SHARE_w2_relig$ac002d6[i] == 0 | ( SHARE_w2_relig$ac002d6[i] == 1 & SHARE_w2_relig$ac003_6[i] == 3 ) ) {
    SHARE_ds_w2$relig[i] = 0 }
  else if( SHARE_w2_relig$ac002d6[i] == -2 | SHARE_w2_relig$ac003_6[i] == -2 ) {
    SHARE_ds_w2$relig[i] = 997 }
  else if( SHARE_w2_relig$ac002d6[i] == -1 | SHARE_w2_relig$ac003_6[i] == -1 ) {
    SHARE_ds_w2$relig[i] = 998 }
}

SHARE_ds_w2$relig <- car::recode(as.vector(SHARE_ds_w2$relig), "NA='999'")
SHARE_ds_w2$relig <- labelled(SHARE_ds_w2$relig, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2}
vari <- SHARE_ds_w2$relig
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_ds_w2$relig, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SHARE_ds_w2, aes(x=factor(relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any form of religious participation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2}
AfterH <- table(SHARE_ds_w2$relig)
BeforeH <- table(SHARE_w2_relig$ac002d6, SHARE_w2_relig$ac003_6, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(sum(BeforeH[4,]), sum(BeforeH[5,4]))
BeforeH1[[2]] <- sum(BeforeH[5,c(2:3)])
BeforeH1[[3]] <- BeforeH[2,1]
BeforeH1[[4]] <- BeforeH[3,1]
BeforeH1[[5]] <- BeforeH[1,1]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","-2->997","-1->998","NA->999")
kable(C)
```

 
 


### Wave 3
Not found.

### Wave 4

#### Study-specific variables

The study-specific variables elected to be harmonised are:

* Name: `ac035d6`
* Label: `activities last year: taken part in religious organization?`
* Categories:
    + `0 = not selected`
    + `1 = selected`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`

* Name: `ac036_6`
* Label: `How often activities in the last 12 months (taken part in religious organization)?`
* Categories:
    + `1 = almost every day`
    + `2 = almost every week`
    + `3 = almost every month`
    + `4 = less than every month`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`
 
* Description: 
```{r assign4}
opal.assign.table.tibble(o, 'SHARE_w4_relig','SHARE.sharew4_rel1-1-1_ac',variables=list('ac035d6','ac036_6'), missings = TRUE)
```

```{r local4}
SHARE_w4_relig <- opal.execute(o,'SHARE_w4_relig')

vari <- SHARE_w4_relig$ac035d6
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
#Categorical_summary(var =SHARE_w4_relig$ac035d6, missing_values = NA)
ggplot(SHARE_w4_relig, aes(x=factor(ac035d6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("activities last year: taken part in religious organization?") + ylab("Frequency") 

vari <- SHARE_w4_relig$ac036_6
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
#Categorical_summary(var =SHARE_w4_relig$ac036_6, missing_values = NA)
ggplot(SHARE_w4_relig, aes(x=factor(ac036_6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How often activities in the last 12 months has he/she taken part in religious organization?") + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if ac035d6=1 and ac036_6 in c(1,2,3) then 1`
* `if ac035d6=0 OR ( ac035d6=1 and ac036_6=4 ) then 0`
* `-2 into 997`
* `-1 into 998`
* `NA into 999`

**R script:**

```{r harmo4, echo=TRUE}
SHARE_ds_w4 <- tibble(id=SHARE_w4_relig$id)

SHARE_w4_relig$ac035d6 <- car::recode(as.vector(SHARE_w4_relig$ac035d6), "NA='-999'")
SHARE_w4_relig$ac036_6 <- car::recode(as.vector(SHARE_w4_relig$ac036_6), "NA='-999'")

SHARE_ds_w4$relig <- c(NA)  
for(i in 1:dim(SHARE_w4_relig)[1]){
  if( SHARE_w4_relig$ac035d6[i] == 1 & SHARE_w4_relig$ac036_6[i] %in% c(1,2,3) ) {
    SHARE_ds_w4$relig[i] = 1 }
  else if( SHARE_w4_relig$ac035d6[i] == 0 | ( SHARE_w4_relig$ac035d6[i] == 1 & SHARE_w4_relig$ac036_6[i] == 4 ) ) {
    SHARE_ds_w4$relig[i] = 0 }
  else if( SHARE_w4_relig$ac035d6[i] == -2 | SHARE_w4_relig$ac036_6[i] == -2 ) {
    SHARE_ds_w4$relig[i] = 997 }
  else if( SHARE_w4_relig$ac035d6[i] == -1 | SHARE_w4_relig$ac036_6[i] == -1 ) {
    SHARE_ds_w4$relig[i] = 998 }
}

SHARE_ds_w4$relig <- car::recode(as.vector(SHARE_ds_w4$relig), "NA='999'")
SHARE_ds_w4$relig <- labelled(SHARE_ds_w4$relig, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4}
vari <- SHARE_ds_w4$relig
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_ds_w4$relig, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SHARE_ds_w4, aes(x=factor(relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any form of religious participation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4}
AfterH <- table(SHARE_ds_w4$relig)
BeforeH <- table(SHARE_w4_relig$ac035d6, SHARE_w4_relig$ac036_6, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(sum(BeforeH[4,]), sum(BeforeH[5,5]))
BeforeH1[[2]] <- sum(BeforeH[5,c(2:4)])
BeforeH1[[3]] <- BeforeH[2,1]
BeforeH1[[4]] <- BeforeH[3,1]
BeforeH1[[5]] <- sum(BeforeH[c(1,5),1])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","-2->997","-1->998","NA->999")
kable(C)
```



### Wave 5

Not found.



```{r save, echo=FALSE}
relig <- SHARE_ds_w1
save(relig, file = "../RData/w1/relig.RData")
rm(relig)

relig <- SHARE_ds_w2
save(relig, file = "../RData/w2/relig.RData")
rm(relig)



relig <- SHARE_ds_w4
save(relig, file = "../RData/w4/relig.RData")
rm(relig)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
