---
title: "Any form of religious participation (religious services attendance, religious meetings, religious organization membership, etc.)"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 


<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/religDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/religDS.R')
```

<!-- ########################################################## --> 

# Data process

## SHARE

### Wave 1

#### Study-specific variable description


| **Name** |`ac002d6`|`ac003_6`|
|-|-|-|
| **Label** |`activities last month: taken part in religious organization?`|`How often in the last 4 weeks has he/she taken part in religious organization?`|
| **Table name** |`sharew1_rel2-6-0_ac`|`sharew1_rel2-6-0_ac`|
| **Categories** |`0 = not selected`<br/>`1 = selected`|`1 = almost daily`<br/>`2 = almost every week`<br/>`3 = less often`|
| **Missings** |`-2 = refusal`<br/>`-1 = don't know`|`-2 = refusal`<br/>`-1 = don't know`|
| **Description** |  |  |



```{r assign1, echo=F}
opal.assign.table.tibble(o, 'SHARE_w1_relig','SHARE.sharew1_rel2-6-0_ac',variables=list('ac002d6','ac003_6'), missings = TRUE)
SHARE_w1_relig <- opal.execute(o,'SHARE_w1_relig')
```

```{r local1, echo=F}
vari <- SHARE_w1_relig$ac002d6
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_w1_relig, aes(x=factor(ac002d6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("activities last month: taken part in religious organization?") + ylab("Frequency") 

vari <- SHARE_w1_relig$ac003_6
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_w1_relig, aes(x=factor(ac003_6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How often activities in the last 4 weeks has he/she taken part in religious organization?") + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if ac002d6=1 and ac003_6 in c(1,2) then 1`
* `if ac002d6=0 OR ( ac002d6=1 and ac003_6=3 ) then 0`
* `-2 into 997`
* `-1 into 998`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
SHARE_ds_w1 <- tibble(id=SHARE_w1_relig$id)

SHARE_w1_relig$ac002d6 <- car::recode(as.vector(SHARE_w1_relig$ac002d6), "NA='-999'")
SHARE_w1_relig$ac003_6 <- car::recode(as.vector(SHARE_w1_relig$ac003_6), "NA='-999'")

SHARE_ds_w1$relig <- c(NA)  
for(i in 1:dim(SHARE_w1_relig)[1]){
  if( SHARE_w1_relig$ac002d6[i] == 1 & SHARE_w1_relig$ac003_6[i] %in% c(1,2) ) {
    SHARE_ds_w1$relig[i] = 1 }
  else if( SHARE_w1_relig$ac002d6[i] == 0 | ( SHARE_w1_relig$ac002d6[i] == 1 & SHARE_w1_relig$ac003_6[i] == 3 ) ) {
    SHARE_ds_w1$relig[i] = 0 }
  else if( SHARE_w1_relig$ac002d6[i] == -2 | SHARE_w1_relig$ac003_6[i] == -2 ) {
    SHARE_ds_w1$relig[i] = 997 }
  else if( SHARE_w1_relig$ac002d6[i] == -1 | SHARE_w1_relig$ac003_6[i] == -1 ) {
    SHARE_ds_w1$relig[i] = 998 }
}

SHARE_ds_w1$relig <- car::recode(as.vector(SHARE_ds_w1$relig), "NA='999'")

```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <- SHARE_ds_w1$relig
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SHARE_ds_w1, aes(x=factor(relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any form of religious participation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(SHARE_ds_w1$relig)
BeforeH <- table(SHARE_w1_relig$ac002d6, SHARE_w1_relig$ac003_6, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(sum(BeforeH[4,]), sum(BeforeH[5,5]))
BeforeH1[[2]] <- sum(BeforeH[5,c(3:4)])
BeforeH1[[3]] <- sum(BeforeH[2,1], BeforeH[5,2])
BeforeH1[[4]] <- BeforeH[3,1]
BeforeH1[[5]] <- BeforeH[1,1]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","-2->997","-1->998","NA->999")
kable(C)
```

 
 



### Wave 2

#### Study-specific variable description



| **Name** |`ac002d6`|`ac003_6`|
|-|-|-|
| **Label** |`activities last month: taken part in religious organization?`|`How often in the last 4 weeks has he/she taken part in religious organization?`|
| **Table name** |`sharew2_rel2-6-0_ac`|`sharew2_rel2-6-0_ac`|
| **Categories** |`0 = not selected`<br/>`1 = selected`|`1 = almost daily`<br/>`2 = almost every week`<br/>`3 = less often`|
| **Missings** |`-2 = refusal`<br/>`-1 = don't know`|`-2 = refusal`<br/>`-1 = don't know`|
| **Description** |  |  |
  


```{r assign2, echo=F}
opal.assign.table.tibble(o, 'SHARE_w2_relig','SHARE.sharew2_rel2-6-0_ac',variables=list('ac002d6','ac003_6'), missings = TRUE)
SHARE_w2_relig <- opal.execute(o,'SHARE_w2_relig')
```

```{r local2, echo=F}
vari <- SHARE_w2_relig$ac002d6
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_w2_relig, aes(x=factor(ac002d6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("activities last month: taken part in religious organization?") + ylab("Frequency") 

vari <- SHARE_w2_relig$ac003_6
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_w2_relig, aes(x=factor(ac003_6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How often activities in the last 4 weeks has he/she taken part in religious organization?") + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if ac002d6=1 and ac003_6 in c(1,2) then 1`
* `if ac002d6=0 OR ( ac002d6=1 and ac003_6=3 ) then 0`
* `-2 into 997`
* `-1 into 998`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
SHARE_ds_w2 <- tibble(id=SHARE_w2_relig$id)

SHARE_w2_relig$ac002d6 <- car::recode(as.vector(SHARE_w2_relig$ac002d6), "NA='-999'")
SHARE_w2_relig$ac003_6 <- car::recode(as.vector(SHARE_w2_relig$ac003_6), "NA='-999'")

SHARE_ds_w2$relig <- c(NA)  
for(i in 1:dim(SHARE_w2_relig)[1]){
  if( SHARE_w2_relig$ac002d6[i] == 1 & SHARE_w2_relig$ac003_6[i] %in% c(1,2) ) {
    SHARE_ds_w2$relig[i] = 1 }
  else if( SHARE_w2_relig$ac002d6[i] == 0 | ( SHARE_w2_relig$ac002d6[i] == 1 & SHARE_w2_relig$ac003_6[i] == 3 ) ) {
    SHARE_ds_w2$relig[i] = 0 }
  else if( SHARE_w2_relig$ac002d6[i] == -2 | SHARE_w2_relig$ac003_6[i] == -2 ) {
    SHARE_ds_w2$relig[i] = 997 }
  else if( SHARE_w2_relig$ac002d6[i] == -1 | SHARE_w2_relig$ac003_6[i] == -1 ) {
    SHARE_ds_w2$relig[i] = 998 }
}

SHARE_ds_w2$relig <- car::recode(as.vector(SHARE_ds_w2$relig), "NA='999'")
SHARE_ds_w2$relig <- labelled(SHARE_ds_w2$relig, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}
vari <- SHARE_ds_w2$relig
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_ds_w2$relig, missing_values = miss_values_vector)
ggplot(SHARE_ds_w2, aes(x=factor(relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any form of religious participation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
AfterH <- table(SHARE_ds_w2$relig)
BeforeH <- table(SHARE_w2_relig$ac002d6, SHARE_w2_relig$ac003_6, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(sum(BeforeH[4,]), sum(BeforeH[5,4]))
BeforeH1[[2]] <- sum(BeforeH[5,c(2:3)])
BeforeH1[[3]] <- BeforeH[2,1]
BeforeH1[[4]] <- BeforeH[3,1]
BeforeH1[[5]] <- BeforeH[1,1]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","-2->997","-1->998","NA->999")
kable(C)
```

 
 


### Wave 3
Not found.

### Wave 4

#### Study-specific variable description



| **Name** |`ac035d6`|`ac036_6`|
|-|-|-|
| **Label** |`activities last year: taken part in religious organization?`|`How often in the last 12 months (taken part in religious organization)?`|
| **Table name** |`sharew4_rel1-1-1_ac`|`sharew4_rel1-1-1_ac`|
| **Categories** |`0 = not selected`<br/>`1 = selected`|`1 = almost every day`<br/>`2 = almost every week`<br/>`3 = almost every month`<br/>`4 = less than every month`|
| **Missings** |`-2 = refusal`<br/>`-1 = don't know`|`-2 = refusal`<br/>`-1 = don't know`|
| **Description** |  |  |
  


```{r assign4, echo=F}
opal.assign.table.tibble(o, 'SHARE_w4_relig','SHARE.sharew4_rel1-1-1_ac',variables=list('ac035d6','ac036_6'), missings = TRUE)
SHARE_w4_relig <- opal.execute(o,'SHARE_w4_relig')
```

```{r local4, echo=F}

vari <- SHARE_w4_relig$ac035d6
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_w4_relig, aes(x=factor(ac035d6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("activities last year: taken part in religious organization?") + ylab("Frequency") 

vari <- SHARE_w4_relig$ac036_6
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_w4_relig, aes(x=factor(ac036_6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How often activities in the last 12 months has he/she taken part in religious organization?") + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if ac035d6=1 and ac036_6 in c(1,2,3) then 1`
* `if ac035d6=0 OR ( ac035d6=1 and ac036_6=4 ) then 0`
* `-2 into 997`
* `-1 into 998`
* `NA into 999`

**R script:**

```{r harmo4, echo=TRUE}
SHARE_ds_w4 <- tibble(id=SHARE_w4_relig$id)

SHARE_w4_relig$ac035d6 <- car::recode(as.vector(SHARE_w4_relig$ac035d6), "NA='-999'")
SHARE_w4_relig$ac036_6 <- car::recode(as.vector(SHARE_w4_relig$ac036_6), "NA='-999'")

SHARE_ds_w4$relig <- c(NA)  
for(i in 1:dim(SHARE_w4_relig)[1]){
  if( SHARE_w4_relig$ac035d6[i] == 1 & SHARE_w4_relig$ac036_6[i] %in% c(1,2,3) ) {
    SHARE_ds_w4$relig[i] = 1 }
  else if( SHARE_w4_relig$ac035d6[i] == 0 | ( SHARE_w4_relig$ac035d6[i] == 1 & SHARE_w4_relig$ac036_6[i] == 4 ) ) {
    SHARE_ds_w4$relig[i] = 0 }
  else if( SHARE_w4_relig$ac035d6[i] == -2 | SHARE_w4_relig$ac036_6[i] == -2 ) {
    SHARE_ds_w4$relig[i] = 997 }
  else if( SHARE_w4_relig$ac035d6[i] == -1 | SHARE_w4_relig$ac036_6[i] == -1 ) {
    SHARE_ds_w4$relig[i] = 998 }
}

SHARE_ds_w4$relig <- car::recode(as.vector(SHARE_ds_w4$relig), "NA='999'")
SHARE_ds_w4$relig <- labelled(SHARE_ds_w4$relig, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4, echo=F}
vari <- SHARE_ds_w4$relig
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SHARE_ds_w4, aes(x=factor(relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any form of religious participation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=F}
AfterH <- table(SHARE_ds_w4$relig)
BeforeH <- table(SHARE_w4_relig$ac035d6, SHARE_w4_relig$ac036_6, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(sum(BeforeH[4,]), sum(BeforeH[5,5]))
BeforeH1[[2]] <- sum(BeforeH[5,c(2:4)])
BeforeH1[[3]] <- BeforeH[2,1]
BeforeH1[[4]] <- BeforeH[3,1]
BeforeH1[[5]] <- sum(BeforeH[c(1,5),1])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","-2->997","-1->998","NA->999")
kable(C)
```



### Wave 5

Not found.




## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.


```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names



share.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"))

# Consider only harmonised waves
l.hds <- lapply(share.cw, function(wname) if(exists(paste0("SHARE_ds_",wname[1]))){wname = list(get(paste0("SHARE_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```




# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
