---
title: "Divorce/Separation"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 


<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/divorceDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/divorceDS.R')
```



<!-- ########################################################## --> 

# Data process

## SHARE

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `dn014_`
* Label: `marital status`
* Categories: 
    + `1 = married and living together with spouse`
    + `2 = registered partnership`
    + `3 = married, living separated from spouse`
    + `4 = never married`
    + `5 = divorced`
    + `6 = widowed`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`


* Description: 
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'SHARE_w1_divorce','SHARE.sharew1_rel2-6-0_dn', variables=list('dn014_'), missings = TRUE)
```

```{r local1, echo=F}
SHARE_w1_divorce <- opal.execute(o,'SHARE_w1_divorce')
vari <- SHARE_w1_divorce$dn014_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_w1_divorce$dn014_, missing_values = NA)
ggplot(SHARE_w1_divorce, aes(x=factor(dn014_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `5 into 1`
* `1,2,3,4 or 6 into 0`
* `-2 into 997`
* `-1 into 998`
* `NA into 999`

 **R script:**

```{r harmo1, echo=TRUE}
SHARE_ds_w1 <- tibble(id=SHARE_w1_divorce$id)
SHARE_ds_w1$divorce <- car::recode(as.vector(SHARE_w1_divorce$dn014_), "5='1'; 1:4='0'; 6='0'; -2='997'; -1='998'; NA='999'")
SHARE_ds_w1$divorce <- labelled(SHARE_ds_w1$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}

vari <- SHARE_ds_w1$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_ds_w1$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SHARE_ds_w1, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(SHARE_ds_w1$divorce)
BeforeH <- table(SHARE_w1_divorce$dn014_, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- BeforeH[[7]]
BeforeH1[[1]] <- sum(BeforeH[c(3:6,8)])
BeforeH1[c(3,4,5)] <- BeforeH[c(1,2,9)]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:4&6->0","5->1","-2->997","-1->998","NA->999")
kable(C)
```




### Wave 2

#### Study-specific variable description

The study-specific variables elected to be harmonised are:

* Name: `dn044_`
* Label: `marital status changed`
* Categories: 
    + `1 = yes, marital status has changed`
    + `5 = no, marital status has not changed`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`
    
* Name: `dn014_`
* Label: `marital status`
* Categories: 
    + `1 = married and living together with spouse`
    + `2 = registered partnership`
    + `3 = married, living separated from spouse`
    + `4 = never married`
    + `5 = divorced`
    + `6 = widowed`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`

* Name: `SHARE_ds_w1$divorce` - harmonized variable from Wave1


* Description: 
```{r assign2, echo=F}
opal.assign.table.tibble(o, 'SHARE_w2_divorce','SHARE.sharew2_rel2-6-0_dn',variables=list('dn044_','dn014_'), missings = TRUE)
```

```{r local2, echo=F}
SHARE_w2_divorce <- opal.execute(o,'SHARE_w2_divorce')
vari <-SHARE_w2_divorce$dn044_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_w2_divorce$dn044_, missing_values = NA)
ggplot(SHARE_w2_divorce, aes(x=factor(dn044_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status changed") + ylab("Frequency")

vari <- SHARE_w2_divorce$dn014_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_w2_divorce$dn014_, missing_values = NA)
ggplot(SHARE_w2_divorce, aes(x=factor(dn014_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `NA into 999`

 **R script:**

```{r harmo2, echo=TRUE}
SHARE_w2_divorce_2 <- left_join(SHARE_w2_divorce, SHARE_ds_w1, by = 'id')

SHARE_ds_w2 <- tibble(id=SHARE_w2_divorce_2$id)

SHARE_w2_divorce_2$dn044_ <- car::recode(as.vector(SHARE_w2_divorce_2$dn044_), "NA='-999'")
SHARE_w2_divorce_2$dn014_ <- car::recode(as.vector(SHARE_w2_divorce_2$dn014_), "NA='-999'")
SHARE_w2_divorce_2$divorce <- car::recode(as.vector(SHARE_w2_divorce_2$divorce), "NA='-999'")

SHARE_ds_w2$divorce <- c(NA)

for(i in 1:dim(SHARE_w2_divorce_2)[1]){
  
  #If marital status has not changed, we take it from Wave1:
  if( SHARE_w2_divorce_2$dn044_[i] == 5 ){ 
    if( SHARE_w2_divorce_2$divorce[i] == 0 ){ SHARE_ds_w2$divorce[i] = 0 }
    else if( SHARE_w2_divorce_2$divorce[i] == 1 ){ SHARE_ds_w2$divorce[i] = 1 }
  }
  
  #If marital status has changed OR he/she didn't answer this question (which means that this questionnaire is BASELINE):
  else if( SHARE_w2_divorce_2$dn044_[i] == 1 | !(SHARE_w2_divorce_2$dn044_[i] %in% c(1,5)) ) { 
    if( SHARE_w2_divorce_2$dn014_[i] == 5 | SHARE_w2_divorce_2$divorce[i] == 1 ) { SHARE_ds_w2$divorce[i] = 1 }
    else if( SHARE_w2_divorce_2$dn014_[i] %in% c(1,2,3,4,6) ) { SHARE_ds_w2$divorce[i] = 0 }
  }
  
  #If divorce was reported in Wave1 (in case of some refusals in dn044_):
  else if( SHARE_w2_divorce_2$divorce[i] == 1 ){ SHARE_ds_w2$divorce[i] = 1 }

  #Missings:
  else if( SHARE_w2_divorce_2$dn044_[i] == -2 | SHARE_w2_divorce_2$divorce[i] == 997 ) { 
      SHARE_ds_w2$divorce[i] = 997 }
  else if( SHARE_w2_divorce_2$dn044_[i] == -1 | SHARE_w2_divorce_2$divorce[i] == 998 ) { 
      SHARE_ds_w2$divorce[i] = 998 }
}

SHARE_ds_w2$divorce <- car::recode(as.vector(SHARE_ds_w2$divorce), "NA='999'")
SHARE_ds_w2$divorce <- labelled(SHARE_ds_w2$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}
vari <- SHARE_ds_w2$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_ds_w2$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SHARE_ds_w2, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}

```



### Wave 3

#### Study-specific variable description

The study-specific variables elected to be harmonised are:

* Name: `sl_rp013_1` UP TO `sl_rp013_4`
* Label: `divorced partner`
* Categories: 
    + `1 = yes`
    + `5 = no`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`

* Name: `divorce` from Wave2

* Description: 
```{r assign3, echo=F}
opal.assign.table.tibble(o, 'SHARE_w3_divorce','SHARE.sharew3_rel1_rp',
                         variables=list('sl_rp013_1','sl_rp013_2','sl_rp013_3','sl_rp013_4'),missings = TRUE)
```

```{r local3, echo=F}
SHARE_w3_divorce <- opal.execute(o,'SHARE_w3_divorce')

vari <- SHARE_w3_divorce$sl_rp013_1
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_w3_divorce$sl_rp013_1, missing_values = NA)
ggplot(SHARE_w3_divorce, aes(x=factor(sl_rp013_1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Did you get divorced from this partner(1)?") + ylab("Frequency")

vari <- SHARE_w3_divorce$sl_rp013_2
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_w3_divorce$sl_rp013_1, missing_values = NA)
ggplot(SHARE_w3_divorce, aes(x=factor(sl_rp013_2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Did you get divorced from this partner(2)?") + ylab("Frequency")


vari <- SHARE_w3_divorce$sl_rp013_3
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_w3_divorce$sl_rp013_1, missing_values = NA)
ggplot(SHARE_w3_divorce, aes(x=factor(sl_rp013_3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Did you get divorced from this partner(3)?") + ylab("Frequency")


vari <- SHARE_w3_divorce$sl_rp013_4
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_w3_divorce$sl_rp013_4, missing_values = NA)
ggplot(SHARE_w3_divorce, aes(x=factor(sl_rp013_4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Did you get divorced from this partner(4)?") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if every variable is 1, then 1`
* `NA into 999`

 **R script:**

```{r harmo3, echo=TRUE}
SHARE_w3_divorce <- left_join(SHARE_w3_divorce, SHARE_ds_w2, by= 'id')

SHARE_ds_w3 <- tibble(id=SHARE_w3_divorce$id)
SHARE_w3_divorce$sl_rp013_1 <- car::recode(as.vector(SHARE_w3_divorce$sl_rp013_1), "NA='-999'")
SHARE_w3_divorce$sl_rp013_2 <- car::recode(as.vector(SHARE_w3_divorce$sl_rp013_2), "NA='-999'")
SHARE_w3_divorce$sl_rp013_3 <- car::recode(as.vector(SHARE_w3_divorce$sl_rp013_3), "NA='-999'")
SHARE_w3_divorce$sl_rp013_4 <- car::recode(as.vector(SHARE_w3_divorce$sl_rp013_4), "NA='-999'")
SHARE_w3_divorce$divorce <- car::recode(as.vector(SHARE_w3_divorce$divorce), "NA='-999'")


SHARE_ds_w3$divorce <- c(NA)
for(i in 1:dim(SHARE_w3_divorce)[1]){
  if( SHARE_w3_divorce$divorce[i] == 1 |
      SHARE_w3_divorce$sl_rp013_1[i] == 1 | SHARE_w3_divorce$sl_rp013_2[i] == 1 |
      SHARE_w3_divorce$sl_rp013_3[i] == 1 | SHARE_w3_divorce$sl_rp013_4[i] == 1 ) { 
      SHARE_ds_w3$divorce[i] = 1 }
  else if( SHARE_w3_divorce$sl_rp013_1[i] == -999 & SHARE_w3_divorce$sl_rp013_2[i] == -999 &
      SHARE_w3_divorce$sl_rp013_3[i] == -999 & SHARE_w3_divorce$sl_rp013_4[i] == -999 ) { 
      SHARE_ds_w3$divorce[i] = 999 }
  else if( SHARE_w3_divorce$sl_rp013_1[i] %in% c(5,-999) & SHARE_w3_divorce$sl_rp013_2[i] %in% c(5,-999) &
      SHARE_w3_divorce$sl_rp013_3[i] %in% c(5,-999) & SHARE_w3_divorce$sl_rp013_4[i] %in% c(5,-999) ) { 
      SHARE_ds_w3$divorce[i] = 0 }
  else if(SHARE_w3_divorce$divorce[i] == 997 |
      SHARE_w3_divorce$sl_rp013_1[i] == -2 | SHARE_w3_divorce$sl_rp013_2[i] == -2 |
      SHARE_w3_divorce$sl_rp013_3[i] == -2 | SHARE_w3_divorce$sl_rp013_4[i] == -2 ) { 
      SHARE_ds_w3$divorce[i] = 997 }
  else if(SHARE_w3_divorce$divorce[i] == 998 |
      SHARE_w3_divorce$sl_rp013_1[i] == -1 | SHARE_w3_divorce$sl_rp013_2[i] == -1 |
      SHARE_w3_divorce$sl_rp013_3[i] == -1 | SHARE_w3_divorce$sl_rp013_4[i] == -1 ) { 
      SHARE_ds_w3$divorce[i] = 998 }
}

SHARE_ds_w3$divorce <- car::recode(as.vector(SHARE_ds_w3$divorce), "NA='999'")
SHARE_ds_w3$divorce <- labelled(SHARE_ds_w3$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=F}
vari <- SHARE_ds_w3$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_ds_w3$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SHARE_ds_w3, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Experience of divorce/separation") + ylab("Frequency")
```

##### Validation
```{r crosstabulation3, echo=F}

```




### Wave 4

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `dn044_`
* Label: `marital status changed`
* Categories: 
    + `1 = yes, marital status has changed`
    + `5 = no, marital status has not changed`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`

* Name: `dn014_`
* Label: `marital status`
* Categories: 
    + `1 = married and living together with spouse`
    + `2 = registered partnership`
    + `3 = married, living separated from spouse`
    + `4 = never married`
    + `5 = divorced`
    + `6 = widowed`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`

* Name: `divorce` from Wave3

* Description: 
```{r assign4, echo=F}
opal.assign.table.tibble(o, 'SHARE_w4_divorce','SHARE.sharew4_rel1-1-1_dn',variables=list('dn014_','dn044_'), missings = TRUE)
```

```{r local4, echo=F}
SHARE_w4_divorce <- opal.execute(o,'SHARE_w4_divorce')

vari <- SHARE_w4_divorce$dn044_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_w4_divorce$dn044_, missing_values = NA)
ggplot(SHARE_w4_divorce, aes(x=factor(dn044_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status changed") + ylab("Frequency")

vari <- SHARE_w4_divorce$dn014_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_w4_divorce$dn014_, missing_values = NA)
ggplot(SHARE_w4_divorce, aes(x=factor(dn014_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  


* `NA into 999`

 **R script:**

```{r harmo4, echo=TRUE}
SHARE_w4_divorce_2 <- left_join(SHARE_w4_divorce, SHARE_ds_w3, by='id')

SHARE_ds_w4 <- tibble(id=SHARE_w4_divorce_2$id)

SHARE_w4_divorce_2$dn044_ <- car::recode(as.vector(SHARE_w4_divorce_2$dn044_), "NA='-999'")
SHARE_w4_divorce_2$dn014_ <- car::recode(as.vector(SHARE_w4_divorce_2$dn014_), "NA='-999'")
SHARE_w4_divorce_2$divorce <- car::recode(as.vector(SHARE_w4_divorce_2$divorce), "NA='-999'")

SHARE_ds_w4$divorce <- c(NA) # I think it is required

for(i in 1:dim(SHARE_w4_divorce_2)[1]){
  
  #If marital status has not changed, we take it from Wave1:
  if( SHARE_w4_divorce_2$dn044_[i] == 5 ){ 
    if( SHARE_w4_divorce_2$divorce[i] == 0 ){ SHARE_ds_w4$divorce[i] = 0 }
    else if( SHARE_w4_divorce_2$divorce[i] == 1 ){ SHARE_ds_w4$divorce[i] = 1 }
  }
  
  #If marital status has changed OR he/she didn't answer this question (which means that this questionnaire is BASELINE):
  else if( SHARE_w4_divorce_2$dn044_[i] == 1 | !(SHARE_w4_divorce_2$dn044_[i] %in% c(1,5)) ) { 
    if( SHARE_w4_divorce_2$dn014_[i] == 5 | SHARE_w4_divorce_2$divorce[i] == 1 ) { SHARE_ds_w4$divorce[i] = 1 }
    else if( SHARE_w4_divorce_2$dn014_[i] %in% c(1,2,3,4,6) ) { SHARE_ds_w4$divorce[i] = 0 }
  }
  
  #If divorce was reported in Wave1 (in case of some refusals in dn044_):
  else if( SHARE_w4_divorce_2$divorce[i] == 1 ){ SHARE_ds_w4$divorce[i] = 1 }

  #Missings:
  else if( SHARE_w4_divorce_2$dn044_[i] == -2 | SHARE_w4_divorce_2$divorce[i] == 997 ) { 
      SHARE_ds_w4$divorce[i] = 997 }
  else if( SHARE_w4_divorce_2$dn044_[i] == -1 | SHARE_w4_divorce_2$divorce[i] == 998 ) { 
      SHARE_ds_w4$divorce[i] = 998 }
}

SHARE_ds_w4$divorce <- car::recode(as.vector(SHARE_ds_w4$divorce), "NA='999'")
SHARE_ds_w4$divorce <- labelled(SHARE_ds_w4$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4, echo=F}
vari <- SHARE_ds_w4$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_ds_w4$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SHARE_ds_w4, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Experience of divorce/separation") + ylab("Frequency")
```

##### Validation
```{r crosstabulation4, echo=F}

```



### Wave 5

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `dn044_`
* Label: `marital status changed`
* Categories: 
    + `1 = yes, marital status has changed`
    + `5 = no, marital status has not changed`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`

* Name: `dn014_`
* Label: `marital status`
* Categories: 
    + `1 = married and living together with spouse`
    + `2 = registered partnership`
    + `3 = married, living separated from spouse`
    + `4 = never married`
    + `5 = divorced`
    + `6 = widowed`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`

* Name: `divorce` from Wave4


* Description: 
```{r assign5, echo=F}
opal.assign.table.tibble(o, 'SHARE_w5_divorce','SHARE.sharew5_rel1-0-0_dn',variables=list('dn014_','dn044_'), missings = TRUE)
```

```{r local5, echo=F}
SHARE_w5_divorce <- opal.execute(o,'SHARE_w5_divorce')

vari <- SHARE_w5_divorce$dn014_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_w5_divorce$dn014_, missing_values = NA)
ggplot(SHARE_w5_divorce, aes(x=factor(dn014_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")

vari <- SHARE_w5_divorce$dn044_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_w5_divorce$dn044_, missing_values = NA)
ggplot(SHARE_w5_divorce, aes(x=factor(dn044_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("marital status changed") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `NA into 999`

 **R script:**

```{r harmo5, echo=TRUE}
SHARE_w5_divorce_2 <- left_join(SHARE_w5_divorce, SHARE_ds_w4, by='id')

SHARE_ds_w5 <- tibble(id=SHARE_w5_divorce_2$id)

SHARE_w5_divorce_2$dn044_ <- car::recode(as.vector(SHARE_w5_divorce_2$dn044_), "NA='-999'")
SHARE_w5_divorce_2$dn014_ <- car::recode(as.vector(SHARE_w5_divorce_2$dn014_), "NA='-999'")
SHARE_w5_divorce_2$divorce <- car::recode(as.vector(SHARE_w5_divorce_2$divorce), "NA='-999'")


SHARE_ds_w5$divorce <- c(NA) # I think it is required

for(i in 1:dim(SHARE_w5_divorce_2)[1]){
  
  #If marital status has not changed, we take it from Wave1:
  if( SHARE_w5_divorce_2$dn044_[i] == 5 ){ 
    if( SHARE_w5_divorce_2$divorce[i] == 0 ){ SHARE_ds_w5$divorce[i] = 0 }
    else if( SHARE_w5_divorce_2$divorce[i] == 1 ){ SHARE_ds_w5$divorce[i] = 1 }
  }
  
  #If marital status has changed OR he/she didn't answer this question (which means that this questionnaire is BASELINE):
  else if( SHARE_w5_divorce_2$dn044_[i] == 1 | !(SHARE_w5_divorce_2$dn044_[i] %in% c(1,5)) ) { 
    if( SHARE_w5_divorce_2$dn014_[i] == 5 | SHARE_w5_divorce_2$divorce[i] == 1 ) { SHARE_ds_w5$divorce[i] = 1 }
    else if( SHARE_w5_divorce_2$dn014_[i] %in% c(1,2,3,4,6) ) { SHARE_ds_w5$divorce[i] = 0 }
  }
  
  #If divorce was reported in Wave1 (in case of some refusals in dn044_):
  else if( SHARE_w5_divorce_2$divorce[i] == 1 ){ SHARE_ds_w5$divorce[i] = 1 }

  #Missings:
  else if( SHARE_w5_divorce_2$dn044_[i] == -2 | SHARE_w5_divorce_2$divorce[i] == 997 ) { 
      SHARE_ds_w5$divorce[i] = 997 }
  else if( SHARE_w5_divorce_2$dn044_[i] == -1 | SHARE_w5_divorce_2$divorce[i] == 998 ) { 
      SHARE_ds_w5$divorce[i] = 998 }
}

SHARE_ds_w5$divorce <- car::recode(as.vector(SHARE_ds_w5$divorce), "NA='999'")
SHARE_ds_w5$divorce <- labelled(SHARE_ds_w5$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript5, echo=F}
vari <- SHARE_ds_w5$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_ds_w5$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SHARE_ds_w5, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation5, echo=F}

```



```{r save, echo=FALSE}
divorce <- SHARE_ds_w1
save(divorce, file = "../RData/w1/divorce.RData")
rm(divorce)


divorce <- SHARE_ds_w2
save(divorce, file = "../RData/w2/divorce.RData")
rm(divorce)


divorce <- SHARE_ds_w3
save(divorce, file = "../RData/w3/divorce.RData")
rm(divorce)

divorce <- SHARE_ds_w4
save(divorce, file = "../RData/w4/divorce.RData")
rm(divorce)



divorce <- SHARE_ds_w5
save(divorce, file = "../RData/w5/divorce.RData")
rm(divorce)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```









