---
title: "The number of close relatives"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `clsrel`
* Variable label: `The number of close relatives`
* Domain: `Social environment`
* Value type: `continuous`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | Lack of close relatives


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 

# Data process


## SHARE

### Wave 1
Not found.

### Wave 2
Not found.

### Wave 3
Not found.

### Wave 4 

#### Study-specific variable description

The study-specific variables elected to be harmonised are:

* Name: `sn009_1`
* Label: `network closeness: sn person 1`
* Categories:
    + `1 = Not very close`
    + `2 = Somewhat close`
    + `3 = Very close`
    + `4 = Extremely close`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`
    
* Name: `sn009_2`
* Label: `network closeness: sn person 2`
* Categories:
    + `1 = Not very close`
    + `2 = Somewhat close`
    + `3 = Very close`
    + `4 = Extremely close`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`
    
* Name: `sn009_3`
* Label: `network closeness: sn person 3`
* Categories:
    + `1 = Not very close`
    + `2 = Somewhat close`
    + `3 = Very close`
    + `4 = Extremely close`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`
    
* Name: `sn009_4`
* Label: `network closeness: sn person 4`
* Categories:
    + `1 = Not very close`
    + `2 = Somewhat close`
    + `3 = Very close`
    + `4 = Extremely close`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`
    
* Name: `sn009_5`
* Label: `network closeness: sn person 5`
* Categories:
    + `1 = Not very close`
    + `2 = Somewhat close`
    + `3 = Very close`
    + `4 = Extremely close`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`
    
* Name: `sn009_6`
* Label: `network closeness: sn person 6`
* Categories:
    + `1 = Not very close`
    + `2 = Somewhat close`
    + `3 = Very close`
    + `4 = Extremely close`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`
    
* Name: `sn009_7`
* Label: `network closeness: sn person 7`
* Categories:
    + `1 = Not very close`
    + `2 = Somewhat close`
    + `3 = Very close`
    + `4 = Extremely close`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`
    

* Name: `sn005_1` UP TO `sn005_7`
* Label: `network relationship: sn person 1`
* Categories:
    + `1 = Spouse/Partner`
    + `2 = Mother`
    + `3 = Father`
    + `4 = Mother-in-law``
    + `5 = Father-in-law`
    + `6 = Stepmother`
    + `7 = Stepfather`
    + `8 = Brother`
    + `9 = Sister`
    + `10 = Child`
    + `11 = Step-child/your current partner's child`
    + `12 = Son-in-law``
    + `13 = Daughter-in-law`
    + `14 = Grandchild`
    + `15 = Grandparent`
    + `16 = Aunt`
    + `17 = Uncle`
    + `18 = Niece`
    + `19 = Nephew`
    + `20 = Other relative`
    + `21 = Friend`
    + `22 = (Ex-)colleague/co-worker`
    + `23 = Neighbour`
    + `24 = Ex-spouse/partner`
    + `25 = Minister, priest, or other clergy`
    + `26 = Therapist or other professional helper`
    + `27 = Housekeeper/Home health care provider`
    + `96 = None of these`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`
    
    

* Description: 
```{r assign4}
opal.assign.table.tibble(o, 'SHARE_w4_clsrel','SHARE.sharew4_rel1-1-1_sn', 
                        variables=list('sn009_1','sn009_2','sn009_3','sn009_4','sn009_5','sn009_6','sn009_7',
                                       'sn005_1','sn005_2','sn005_3','sn005_4','sn005_5','sn005_6','sn005_7'), missings = TRUE)
```

```{r local4}
SHARE_w4_clsrel <- opal.execute(o,'SHARE_w4_clsrel')


vari <- SHARE_w4_clsrel$sn009_1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var =SHARE_w4_clsrel$sn009_1, missing_values = NA)
ggplot(SHARE_w4_clsrel, aes(x=factor(sn009_1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Network closeness with person 1") + ylab("Frequency") 

vari <- SHARE_w4_clsrel$sn009_2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var =SHARE_w4_clsrel$sn005_1, missing_values = NA)
ggplot(SHARE_w4_clsrel, aes(x=factor(sn009_2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Network closeness with person 2") + ylab("Frequency") 

vari <- SHARE_w4_clsrel$sn009_3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var =SHARE_w4_clsrel$sn009_1, missing_values = NA)
ggplot(SHARE_w4_clsrel, aes(x=factor(sn009_3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Network closeness with person 3") + ylab("Frequency") 

vari <- SHARE_w4_clsrel$sn009_4
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var =SHARE_w4_clsrel$sn009_1, missing_values = NA)
ggplot(SHARE_w4_clsrel, aes(x=factor(sn009_4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Network closeness with person 4") + ylab("Frequency") 

vari <- SHARE_w4_clsrel$sn009_5
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var =SHARE_w4_clsrel$sn009_1, missing_values = NA)
ggplot(SHARE_w4_clsrel, aes(x=factor(sn009_5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Network closeness with person 5") + ylab("Frequency") 

vari <- SHARE_w4_clsrel$sn009_6
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var =SHARE_w4_clsrel$sn009_1, missing_values = NA)
ggplot(SHARE_w4_clsrel, aes(x=factor(sn009_6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Network closeness with person 6") + ylab("Frequency") 

vari <- SHARE_w4_clsrel$sn009_7
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var =SHARE_w4_clsrel$sn009_1, missing_values = NA)
ggplot(SHARE_w4_clsrel, aes(x=factor(sn009_7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Network closeness with person 7") + ylab("Frequency") 

vari <- SHARE_w4_clsrel$sn005_1
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var =SHARE_w4_clsrel$sn009_1, missing_values = NA)
ggplot(SHARE_w4_clsrel, aes(x=factor(sn005_1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Network relationship: sn person 1") + ylab("Frequency") 

vari <- SHARE_w4_clsrel$sn005_2
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var =SHARE_w4_clsrel$sn009_1, missing_values = NA)
ggplot(SHARE_w4_clsrel, aes(x=factor(sn005_2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Network relationship: sn person 2") + ylab("Frequency") 

vari <- SHARE_w4_clsrel$sn005_3
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var =SHARE_w4_clsrel$sn009_1, missing_values = NA)
ggplot(SHARE_w4_clsrel, aes(x=factor(sn005_3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Network relationship: sn person 3") + ylab("Frequency") 

vari <- SHARE_w4_clsrel$sn005_4
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var =SHARE_w4_clsrel$sn009_1, missing_values = NA)
ggplot(SHARE_w4_clsrel, aes(x=factor(sn005_4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Network relationship: sn person 4") + ylab("Frequency") 

vari <- SHARE_w4_clsrel$sn005_5
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var =SHARE_w4_clsrel$sn009_1, missing_values = NA)
ggplot(SHARE_w4_clsrel, aes(x=factor(sn005_5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Network relationship: sn person 5") + ylab("Frequency") 

vari <- SHARE_w4_clsrel$sn005_6
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var =SHARE_w4_clsrel$sn009_1, missing_values = NA)
ggplot(SHARE_w4_clsrel, aes(x=factor(sn005_6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Network relationship: sn person 6") + ylab("Frequency") 

vari <- SHARE_w4_clsrel$sn005_7
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var =SHARE_w4_clsrel$sn009_1, missing_values = NA)
ggplot(SHARE_w4_clsrel, aes(x=factor(sn005_7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Network relationship: sn person 7") + ylab("Frequency") 

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `clsrel=0.`
  `if sn005_1 in c(1:20) AND sn009_1 in c(2,3,4) then clsrel=clsrel+1.`
  `if sn005_2 in c(1:20) AND sn009_2 in c(2,3,4) then clsrel=clsrel+1.`
  `if sn005_3 in c(1:20) AND sn009_3 in c(2,3,4) then clsrel=clsrel+1.`
  `if sn005_4 in c(1:20) AND sn009_4 in c(2,3,4) then clsrel=clsrel+1.`
  `if sn005_5 in c(1:20) AND sn009_5 in c(2,3,4) then clsrel=clsrel+1.`
  `if sn005_6 in c(1:20) AND sn009_6 in c(2,3,4) then clsrel=clsrel+1.`
  `if sn005_7 in c(1:20) AND sn009_7 in c(2,3,4) then clsrel=clsrel+1.`


**R script:**

```{r harmo4, echo=TRUE}
SHARE_ds_w4 <- tibble(id=SHARE_w4_clsrel$id)

SHARE_w4_clsrel$sn009_1 <- car::recode(as.vector(SHARE_w4_clsrel$sn009_1), "NA='-999'")
SHARE_w4_clsrel$sn009_2 <- car::recode(as.vector(SHARE_w4_clsrel$sn009_2), "NA='-999'")
SHARE_w4_clsrel$sn009_3 <- car::recode(as.vector(SHARE_w4_clsrel$sn009_3), "NA='-999'")
SHARE_w4_clsrel$sn009_4 <- car::recode(as.vector(SHARE_w4_clsrel$sn009_4), "NA='-999'")
SHARE_w4_clsrel$sn009_5 <- car::recode(as.vector(SHARE_w4_clsrel$sn009_5), "NA='-999'")
SHARE_w4_clsrel$sn009_6 <- car::recode(as.vector(SHARE_w4_clsrel$sn009_6), "NA='-999'")
SHARE_w4_clsrel$sn009_7 <- car::recode(as.vector(SHARE_w4_clsrel$sn009_7), "NA='-999'")
SHARE_w4_clsrel$sn005_1 <- car::recode(as.vector(SHARE_w4_clsrel$sn005_1), "NA='-999'")
SHARE_w4_clsrel$sn005_2 <- car::recode(as.vector(SHARE_w4_clsrel$sn005_2), "NA='-999'")
SHARE_w4_clsrel$sn005_3 <- car::recode(as.vector(SHARE_w4_clsrel$sn005_3), "NA='-999'")
SHARE_w4_clsrel$sn005_4 <- car::recode(as.vector(SHARE_w4_clsrel$sn005_4), "NA='-999'")
SHARE_w4_clsrel$sn005_5 <- car::recode(as.vector(SHARE_w4_clsrel$sn005_5), "NA='-999'")
SHARE_w4_clsrel$sn005_6 <- car::recode(as.vector(SHARE_w4_clsrel$sn005_6), "NA='-999'")
SHARE_w4_clsrel$sn005_7 <- car::recode(as.vector(SHARE_w4_clsrel$sn005_7), "NA='-999'")


SHARE_ds_w4$clsrel <- c(NA)
for(i in 1:dim(SHARE_w4_clsrel)[1]){
  
  # 999 if all answers are NAs:
  if( SHARE_w4_clsrel$sn009_1[i] == -999 & SHARE_w4_clsrel$sn009_2[i] == -999 &
      SHARE_w4_clsrel$sn009_3[i] == -999 & SHARE_w4_clsrel$sn009_4[i] == -999 &
      SHARE_w4_clsrel$sn009_5[i] == -999 & SHARE_w4_clsrel$sn009_6[i] == -999 &
      SHARE_w4_clsrel$sn009_7[i] == -999 ) {
    SHARE_ds_w4$clsrel[i] = 999 }
  
  # 997 if there are only NAs and refusals:
  else if( SHARE_w4_clsrel$sn009_1[i] %in% c(-2,-999) & SHARE_w4_clsrel$sn009_2[i] %in% c(-2,-999) &
          SHARE_w4_clsrel$sn009_3[i] %in% c(-2,-999) & SHARE_w4_clsrel$sn009_4[i] %in% c(-2,-999) &
          SHARE_w4_clsrel$sn009_5[i] %in% c(-2,-999) & SHARE_w4_clsrel$sn009_6[i] %in% c(-2,-999) &
          SHARE_w4_clsrel$sn009_7[i] %in% c(-2,-999) ) {
    SHARE_ds_w4$clsrel[i] = 997 }
  
  # 998 if there are only NAs and don't knows:
  else if( SHARE_w4_clsrel$sn009_1[i] %in% c(-1,-999) & SHARE_w4_clsrel$sn009_2[i] %in% c(-1,-999) &
          SHARE_w4_clsrel$sn009_3[i] %in% c(-1,-999) & SHARE_w4_clsrel$sn009_4[i] %in% c(-1,-999) &
          SHARE_w4_clsrel$sn009_5[i] %in% c(-1,-999) & SHARE_w4_clsrel$sn009_6[i] %in% c(-1,-999) &
          SHARE_w4_clsrel$sn009_7[i] %in% c(-1,-999) ) {
    SHARE_ds_w4$clsrel[i] = 998 }
  
  else {  
  # starts from 0 and add 1 for every answer in c(2,3,4) for relatives:
    SHARE_ds_w4$clsrel[i] = 0
    if(SHARE_w4_clsrel$sn005_1[i] %in% c(1:20) & SHARE_w4_clsrel$sn009_1[i] %in% c(2,3,4) ) { 
      SHARE_ds_w4$clsrel[i] = SHARE_ds_w4$clsrel[i] + 1 }
    if(SHARE_w4_clsrel$sn005_2[i] %in% c(1:20) & SHARE_w4_clsrel$sn009_2[i] %in% c(2,3,4) ) { 
      SHARE_ds_w4$clsrel[i] = SHARE_ds_w4$clsrel[i] + 1 }
    if(SHARE_w4_clsrel$sn005_3[i] %in% c(1:20) & SHARE_w4_clsrel$sn009_3[i] %in% c(2,3,4) ) { 
      SHARE_ds_w4$clsrel[i] = SHARE_ds_w4$clsrel[i] + 1 }
    if(SHARE_w4_clsrel$sn005_4[i] %in% c(1:20) & SHARE_w4_clsrel$sn009_4[i] %in% c(2,3,4) ) { 
      SHARE_ds_w4$clsrel[i] = SHARE_ds_w4$clsrel[i] + 1 }
    if(SHARE_w4_clsrel$sn005_5[i] %in% c(1:20) & SHARE_w4_clsrel$sn009_5[i] %in% c(2,3,4) ) { 
      SHARE_ds_w4$clsrel[i] = SHARE_ds_w4$clsrel[i] + 1 }
    if(SHARE_w4_clsrel$sn005_6[i] %in% c(1:20) & SHARE_w4_clsrel$sn009_6[i] %in% c(2,3,4) ) { 
      SHARE_ds_w4$clsrel[i] = SHARE_ds_w4$clsrel[i] + 1 }
    if(SHARE_w4_clsrel$sn005_7[i] %in% c(1:20) & SHARE_w4_clsrel$sn009_7[i] %in% c(2,3,4) ) { 
      SHARE_ds_w4$clsrel[i] = SHARE_ds_w4$clsrel[i] + 1 }
  }
}

SHARE_ds_w4$clsrel <- car::recode(as.vector(SHARE_ds_w4$clsrel), "NA='999'")
SHARE_ds_w4$clsrel <- labelled(SHARE_ds_w4$clsrel, labels = c("lack of close relatives"=0, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4}
vari <- SHARE_ds_w4$clsrel
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
#Continuous_summary(var =SHARE_ds_w4$clsrel, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SHARE_ds_w4, aes(x=factor(clsrel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The number of close relatives") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4}

```


```{r save, echo=FALSE}
clsrel <- SHARE_ds_w4
save(clsrel, file = "../RData/w4/clsrel.RData")
rm(clsrel)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
