---
title: "Has other (living) family members (e.g. parents, siblings, in-laws, etc.)"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/oth_famDS.Rmd'}
```


```{r global, echo=F}
source('../../_DS_Rmd/oth_famDS.R')
```

<!-- ########################################################## --> 

# Data process

## SHARE

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `dn026_1`
* Label: `is natural parent still alive: mother`
* Categories: 
    + `1 = yes`
    + `5 = no`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`
    
* Name: `dn026_2`
* Label: `is natural parent still alive: father`
* Categories: 
    + `1 = yes`
    + `5 = no`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`

* Name: `dn036_`
* Label: `how many brothers alive`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`
    
* Name: `dn037_`
* Label: `how many sisters alive`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`


* Description: 
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'SHARE_w1_oth_fam','SHARE.sharew1_rel2-6-0_dn', 
                        variables=list('dn026_1','dn026_2','dn036_','dn037_'), missings = TRUE)
```

```{r local1, echo=F}
SHARE_w1_oth_fam <- opal.execute(o,'SHARE_w1_oth_fam')
vari <- SHARE_w1_oth_fam$dn026_1
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_w1_oth_fam$dn026_1, missing_values = NA)
ggplot(SHARE_w1_oth_fam, aes(x=factor(dn026_1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("is natural parent still alive: mother") + ylab("Frequency")
vari <- SHARE_w1_oth_fam$dn026_2
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_w1_oth_fam$dn026_2, missing_values = NA)
ggplot(SHARE_w1_oth_fam, aes(x=factor(dn026_2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("is natural parent still alive: father") + ylab("Frequency")
vari <-SHARE_w1_oth_fam$dn036_
kable(Continuous_summary(vari, missing_values = c(-1,-2))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Continuous_summary(vari, missing_values = c(-1,-2))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values =c(-1,-2))$summary, caption = "Summary")
#Continuous_summary(var = SHARE_w1_oth_fam$dn036_, missing_values = NA)
ggplot(SHARE_w1_oth_fam, aes(x=factor(dn036_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("how many brothers alive") + ylab("Frequency")
vari <-SHARE_w1_oth_fam$dn037_
kable(Continuous_summary(vari, missing_values = c(-1,-2))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Continuous_summary(vari, missing_values = c(-1,-2))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values =c(-1,-2))$summary, caption = "Summary")
#Continuous_summary(var = SHARE_w1_oth_fam$dn037_, missing_values = NA)
ggplot(SHARE_w1_oth_fam, aes(x=factor(dn037_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("how many sisters alive") + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any of dn026_1, dn026_2 equals 1 or any of dn036_, dn037_ >0 then 1`
* `if both dn026_1, dn026_2 equal 5 and aboth dn036_, dn037_ equal 0 then 0`
* `-2 into 997`
* `-1 into 998`
* `NA into 999`

 **R script:**

```{r harmo1, echo=TRUE}
SHARE_ds_w1 <- tibble(id=SHARE_w1_oth_fam$id)

SHARE_w1_oth_fam$dn026_1 <- car::recode(as.vector(SHARE_w1_oth_fam$dn026_1), "NA='-999'")
SHARE_w1_oth_fam$dn026_2 <- car::recode(as.vector(SHARE_w1_oth_fam$dn026_2), "NA='-999'")
SHARE_w1_oth_fam$dn036_ <- car::recode(as.vector(SHARE_w1_oth_fam$dn036_), "NA='-999'")
SHARE_w1_oth_fam$dn037_ <- car::recode(as.vector(SHARE_w1_oth_fam$dn037_), "NA='-999'")

SHARE_ds_w1$oth_fam <- c(NA) 
for(i in 1:dim(SHARE_w1_oth_fam)[1]){
  if( SHARE_w1_oth_fam$dn026_1[i] == 1 | SHARE_w1_oth_fam$dn026_2[i] == 1 | SHARE_w1_oth_fam$dn036_[i] > 0 | SHARE_w1_oth_fam$dn037_[i] > 0 ){
    SHARE_ds_w1$oth_fam[i] = 1 } 
  else if( SHARE_w1_oth_fam$dn026_1[i] == 5 & SHARE_w1_oth_fam$dn026_2[i] == 5 & SHARE_w1_oth_fam$dn036_[i] == 0 & SHARE_w1_oth_fam$dn037_[i] == 0 ){
    SHARE_ds_w1$oth_fam[i] = 0 }
  else if( SHARE_w1_oth_fam$dn026_1[i] == -2 | SHARE_w1_oth_fam$dn026_2[i] == -2 | SHARE_w1_oth_fam$dn036_[i] == -2 | SHARE_w1_oth_fam$dn037_[i] == -2 ){
    SHARE_ds_w1$oth_fam[i] = 997 }
  else if( SHARE_w1_oth_fam$dn026_1[i] == -1 | SHARE_w1_oth_fam$dn026_2[i] == -1 | SHARE_w1_oth_fam$dn036_[i] == -1 | SHARE_w1_oth_fam$dn037_[i] == -1 ){
    SHARE_ds_w1$oth_fam[i] = 998 }
}

SHARE_ds_w1$oth_fam <- car::recode(as.vector(SHARE_ds_w1$oth_fam), "NA='999'")
SHARE_ds_w1$oth_fam <- labelled(SHARE_ds_w1$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}

vari <- SHARE_ds_w1$oth_fam
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_ds_w1$oth_fam, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SHARE_ds_w1, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}

```

 
 



### Wave 2

#### Study-specific variable description

The study-specific variables elected to be harmonised are:

* Name: `dn026_1`
* Label: `is natural parent still alive: mother`
* Categories: 
    + `1 = yes`
    + `5 = no`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`
    
* Name: `dn026_2`
* Label: `is natural parent still alive: father`
* Categories: 
    + `1 = yes`
    + `5 = no`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`

* Name: `dn036_`
* Label: `how many brothers alive`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`
    
* Name: `dn037_`
* Label: `how many sisters alive`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`


* Description: 
```{r assign2, echo=F}
opal.assign.table.tibble(o, 'SHARE_w2_oth_fam','SHARE.sharew2_rel2-6-0_dn', 
                        variables=list('dn026_1','dn026_2','dn036_','dn037_'), missings = TRUE)
```

```{r local2, echo=F}
SHARE_w2_oth_fam <- opal.execute(o,'SHARE_w2_oth_fam')

vari <- SHARE_w2_oth_fam$dn026_1
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_w2_oth_fam$dn026_1, missing_values = NA)
ggplot(SHARE_w2_oth_fam, aes(x=factor(dn026_1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("is natural parent still alive: mother") + ylab("Frequency")

vari <- SHARE_w2_oth_fam$dn026_2
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_w2_oth_fam$dn026_2, missing_values = NA)
ggplot(SHARE_w2_oth_fam, aes(x=factor(dn026_2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("is natural parent still alive: father") + ylab("Frequency")

vari <-SHARE_w2_oth_fam$dn036_
kable(Continuous_summary(vari, missing_values = c(-1,-2))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Continuous_summary(vari, missing_values = c(-1,-2))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values =c(-1,-2))$summary, caption = "Summary")
#Continuous_summary(var = SHARE_w2_oth_fam$dn036_, missing_values = NA)
ggplot(SHARE_w2_oth_fam, aes(x=factor(dn036_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("how many brothers alive") + ylab("Frequency")

vari <-SHARE_w2_oth_fam$dn037_
kable(Continuous_summary(vari, missing_values = c(-1,-2))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Continuous_summary(vari, missing_values = c(-1,-2))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values =c(-1,-2))$summary, caption = "Summary")
#Continuous_summary(var = SHARE_w2_oth_fam$dn037_, missing_values = NA)
ggplot(SHARE_w2_oth_fam, aes(x=factor(dn037_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("how many sisters alive") + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any of dn026_1, dn026_2 equals 1 or any of dn036_, dn037_ >0 then 1`
* `if both dn026_1, dn026_2 equal 5 and aboth dn036_, dn037_ equal 0 then 0`
* `-2 into 997`
* `-1 into 998`
* `NA into 999`

 **R script:**

```{r harmo2, echo=TRUE}
SHARE_ds_w2 <- tibble(id=SHARE_w2_oth_fam$id)

SHARE_w2_oth_fam$dn026_1 <- car::recode(as.vector(SHARE_w2_oth_fam$dn026_1), "NA='-999'")
SHARE_w2_oth_fam$dn026_2 <- car::recode(as.vector(SHARE_w2_oth_fam$dn026_2), "NA='-999'")
SHARE_w2_oth_fam$dn036_ <- car::recode(as.vector(SHARE_w2_oth_fam$dn036_), "NA='-999'")
SHARE_w2_oth_fam$dn037_ <- car::recode(as.vector(SHARE_w2_oth_fam$dn037_), "NA='-999'")

SHARE_ds_w2$oth_fam <- c(NA) 
for(i in 1:dim(SHARE_w2_oth_fam)[1]){
  if( SHARE_w2_oth_fam$dn026_1[i] == 1 | SHARE_w2_oth_fam$dn026_2[i] == 1 | 
      SHARE_w2_oth_fam$dn036_[i] > 0 | SHARE_w2_oth_fam$dn037_[i] > 0 ){
    SHARE_ds_w2$oth_fam[i] = 1 } 
  else if( SHARE_w2_oth_fam$dn026_1[i] == -999 & SHARE_w2_oth_fam$dn026_2[i] == -999 & 
           SHARE_w2_oth_fam$dn036_[i] == -999 & SHARE_w2_oth_fam$dn037_[i] == -999 ){
    SHARE_ds_w2$oth_fam[i] = 999 }
  else if( SHARE_w2_oth_fam$dn026_1[i] %in% c(-2,-999) & SHARE_w2_oth_fam$dn026_2[i] %in% c(-2,-999) & 
           SHARE_w2_oth_fam$dn036_[i] %in% c(-2,-999) & SHARE_w2_oth_fam$dn037_[i] %in% c(-2,-999) ){
    SHARE_ds_w2$oth_fam[i] = 997 }
  else if( SHARE_w2_oth_fam$dn026_1[i] %in% c(-1,-999) & SHARE_w2_oth_fam$dn026_2[i] %in% c(-1,-999) & 
           SHARE_w2_oth_fam$dn036_[i] %in% c(-1,-999) & SHARE_w2_oth_fam$dn037_[i] %in% c(-1,-999) ){
    SHARE_ds_w2$oth_fam[i] = 998 }
  else if( SHARE_w2_oth_fam$dn026_1[i] == 5 & SHARE_w2_oth_fam$dn026_2[i] == 5 & 
           SHARE_w2_oth_fam$dn036_[i] == 0 & SHARE_w2_oth_fam$dn037_[i] == 0 ){
    SHARE_ds_w2$oth_fam[i] = 0 }
}

SHARE_ds_w2$oth_fam <- car::recode(as.vector(SHARE_ds_w2$oth_fam), "NA='999'")
SHARE_ds_w2$oth_fam <- labelled(SHARE_ds_w2$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}
vari <- SHARE_ds_w2$oth_fam
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_ds_w2$oth_fam, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SHARE_ds_w2, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}

```

 
 
### Wave 3
Not found.


### Wave 4

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `dn026_1`
* Label: `is natural parent still alive: mother`
* Categories: 
    + `1 = yes`
    + `5 = no`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`
    + `-9 = not applicable (e.g.filtered)`
    + `-5 = not answered`
    
* Name: `dn026_2`
* Label: `is natural parent still alive: father`
* Categories: 
    + `1 = yes`
    + `5 = no`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`
    + `-9 = not applicable (e.g.filtered)`
    + `-5 = not answered`

* Name: `dn036_`
* Label: `how many brothers alive`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`
    
* Name: `dn037_`
* Label: `how many sisters alive`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`


* Description: 
```{r assign4, echo=F}
opal.assign.table.tibble(o, 'SHARE_w4_oth_fam','SHARE.sharew4_rel1-1-1_dn', 
                        variables=list('dn026_1','dn026_2','dn036_','dn037_'), missings = TRUE)
```

```{r local4, echo=F}
SHARE_w4_oth_fam <- opal.execute(o,'SHARE_w4_oth_fam')
vari <- SHARE_w4_oth_fam$dn026_1
kable(Categorical_summary(vari, missing_values = c(-1,-2,-5,-9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-2,-5,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2,-5,-9))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_w4_oth_fam$dn026_1, missing_values = NA)
ggplot(SHARE_w4_oth_fam, aes(x=factor(dn026_1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("is natural parent still alive: mother") + ylab("Frequency")
vari <- SHARE_w4_oth_fam$dn026_2
kable(Categorical_summary(vari, missing_values = c(-1,-2,-5,-9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-2,-5,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2,-5,-9))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_w4_oth_fam$dn026_2, missing_values = NA)
ggplot(SHARE_w4_oth_fam, aes(x=factor(dn026_2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("is natural parent still alive: father") + ylab("Frequency")
vari <-SHARE_w4_oth_fam$dn036_
kable(Continuous_summary(vari, missing_values = c(-1,-2))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Continuous_summary(vari, missing_values = c(-1,-2))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values =c(-1,-2))$summary, caption = "Summary")
#Continuous_summary(var = SHARE_w4_oth_fam$dn036_, missing_values = NA)
ggplot(SHARE_w4_oth_fam, aes(x=factor(dn036_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("how many brothers alive") + ylab("Frequency")
vari <-SHARE_w4_oth_fam$dn037_
kable(Continuous_summary(vari, missing_values = c(-1,-2))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Continuous_summary(vari, missing_values = c(-1,-2))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values =c(-1,-2))$summary, caption = "Summary")
#Continuous_summary(var = SHARE_w4_oth_fam$dn037_, missing_values = NA)
ggplot(SHARE_w4_oth_fam, aes(x=factor(dn037_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("how many sisters alive") + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any of dn026_1, dn026_2 equals 1 or any of dn036_, dn037_ >0 then 1`
* `if both dn026_1, dn026_2 equal 5 and aboth dn036_, dn037_ equal 0 then 0`
* `-2 into 997`
* `-1 into 998`
* `-9 into 996`
* `-5 into 995`
* `NA into 999`

 **R script:**

```{r harmo4, echo=TRUE}
SHARE_ds_w4 <- tibble(id=SHARE_w4_oth_fam$id)

SHARE_w4_oth_fam$dn026_1 <- car::recode(as.vector(SHARE_w4_oth_fam$dn026_1), "NA='-999'")
SHARE_w4_oth_fam$dn026_2 <- car::recode(as.vector(SHARE_w4_oth_fam$dn026_2), "NA='-999'")
SHARE_w4_oth_fam$dn036_ <- car::recode(as.vector(SHARE_w4_oth_fam$dn036_), "NA='-999'")
SHARE_w4_oth_fam$dn037_ <- car::recode(as.vector(SHARE_w4_oth_fam$dn037_), "NA='-999'")

SHARE_ds_w4$oth_fam <- c(NA)
for(i in 1:dim(SHARE_w4_oth_fam)[1]){
  if( SHARE_w4_oth_fam$dn026_1[i] == 1 | SHARE_w4_oth_fam$dn026_2[i] == 1 | 
      SHARE_w4_oth_fam$dn036_[i] > 0 | SHARE_w4_oth_fam$dn037_[i] > 0 ){
    SHARE_ds_w4$oth_fam[i] = 1 } 
  else if( SHARE_w4_oth_fam$dn026_1[i] == -999 & SHARE_w4_oth_fam$dn026_2[i] == -999 & 
           SHARE_w4_oth_fam$dn036_[i] == -999 & SHARE_w4_oth_fam$dn037_[i] == -999 ){
    SHARE_ds_w4$oth_fam[i] = 999 }
  else if( SHARE_w4_oth_fam$dn026_1[i] %in% c(-2,-999) & SHARE_w4_oth_fam$dn026_2[i] %in% c(-2,-999) & 
           SHARE_w4_oth_fam$dn036_[i] %in% c(-2,-999) & SHARE_w4_oth_fam$dn037_[i] %in% c(-2,-999) ){
    SHARE_ds_w4$oth_fam[i] = 997 }
  else if( SHARE_w4_oth_fam$dn026_1[i] %in% c(-1,-999) & SHARE_w4_oth_fam$dn026_2[i] %in% c(-1,-999) & 
           SHARE_w4_oth_fam$dn036_[i] %in% c(-1,-999) & SHARE_w4_oth_fam$dn037_[i] %in% c(-1,-999) ){
    SHARE_ds_w4$oth_fam[i] = 998 }
  else if( SHARE_w4_oth_fam$dn026_1[i] == 5 & SHARE_w4_oth_fam$dn026_2[i] == 5 & 
           SHARE_w4_oth_fam$dn036_[i] == 0 & SHARE_w4_oth_fam$dn037_[i] == 0 ){
    SHARE_ds_w4$oth_fam[i] = 0 }
}

SHARE_ds_w4$oth_fam <- car::recode(as.vector(SHARE_ds_w4$oth_fam), "NA='999'")
SHARE_ds_w4$oth_fam <- labelled(SHARE_ds_w4$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4, echo=F}
vari <- SHARE_ds_w4$oth_fam
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_ds_w4$oth_fam, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SHARE_ds_w4, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Has other family members?") + ylab("Frequency")
```

##### Validation
```{r crosstabulation4, echo=F}

```

 
 



### Wave 5

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `dn026_1`
* Label: `is natural parent still alive: mother`
* Categories: 
    + `1 = yes`
    + `5 = no`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`
    + `-9 = not applicable (e.g.filtered)`
    + `-5 = not answered`
    
* Name: `dn026_2`
* Label: `is natural parent still alive: father`
* Categories: 
    + `1 = yes`
    + `5 = no`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`
    + `-9 = not applicable (e.g.filtered)`
    + `-5 = not answered`

* Name: `dn036_`
* Label: `how many brothers alive`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`
    
* Name: `dn037_`
* Label: `how many sisters alive`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`


* Description: 
```{r assign5, echo=F}
opal.assign.table.tibble(o, 'SHARE_w5_oth_fam','SHARE.sharew5_rel1-0-0_dn', 
                        variables=list('dn026_1','dn026_2','dn036_','dn037_'), missings = TRUE)
```

```{r local5, echo=F}
SHARE_w5_oth_fam <- opal.execute(o,'SHARE_w5_oth_fam')

vari <- SHARE_w5_oth_fam$dn026_1
kable(Categorical_summary(vari, missing_values = c(-1,-2,-5,-9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-2,-5,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2,-5,-9))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_w5_oth_fam$dn026_1, missing_values = NA)
ggplot(SHARE_w5_oth_fam, aes(x=factor(dn026_1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("is natural parent still alive: mother") + ylab("Frequency")

vari <- SHARE_w5_oth_fam$dn026_2
kable(Categorical_summary(vari, missing_values = c(-1,-2,-5,-9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-2,-5,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2,-5,-9))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_w5_oth_fam$dn026_2, missing_values = NA)
ggplot(SHARE_w5_oth_fam, aes(x=factor(dn026_2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("is natural parent still alive: father") + ylab("Frequency")

vari <-SHARE_w5_oth_fam$dn036_
kable(Continuous_summary(vari, missing_values = c(-1,-2))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Continuous_summary(vari, missing_values = c(-1,-2))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values =c(-1,-2))$summary, caption = "Summary")
#Continuous_summary(var = SHARE_w5_oth_fam$dn036_, missing_values = NA)
ggplot(SHARE_w5_oth_fam, aes(x=factor(dn036_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("how many brothers alive") + ylab("Frequency")

vari <-SHARE_w5_oth_fam$dn037_
kable(Continuous_summary(vari, missing_values = c(-1,-2))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Continuous_summary(vari, missing_values = c(-1,-2))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values =c(-1,-2))$summary, caption = "Summary")
#Continuous_summary(var = SHARE_w5_oth_fam$dn037_, missing_values = NA)
ggplot(SHARE_w5_oth_fam, aes(x=factor(dn037_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("how many sisters alive") + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any of dn026_1, dn026_2 equals 1 or any of dn036_, dn037_ >0 then 1`
* `if both dn026_1, dn026_2 equal 5 and aboth dn036_, dn037_ equal 0 then 0`
* `-2 into 997`
* `-1 into 998`
* `-9 into 996`
* `-5 into 995`
* `NA into 999`

 **R script:**

```{r harmo5, echo=TRUE}
SHARE_ds_w5 <- tibble(id=SHARE_w5_oth_fam$id)

SHARE_w5_oth_fam$dn026_1 <- car::recode(as.vector(SHARE_w5_oth_fam$dn026_1), "NA='-999'")
SHARE_w5_oth_fam$dn026_2 <- car::recode(as.vector(SHARE_w5_oth_fam$dn026_2), "NA='-999'")
SHARE_w5_oth_fam$dn036_ <- car::recode(as.vector(SHARE_w5_oth_fam$dn036_), "NA='-999'")
SHARE_w5_oth_fam$dn037_ <- car::recode(as.vector(SHARE_w5_oth_fam$dn037_), "NA='-999'")

for(i in 1:dim(SHARE_w5_oth_fam)[1]){
  if( SHARE_w5_oth_fam$dn026_1[i] == 1 | SHARE_w5_oth_fam$dn026_2[i] == 1 | 
      SHARE_w5_oth_fam$dn036_[i] > 0 | SHARE_w5_oth_fam$dn037_[i] > 0 ){
    SHARE_ds_w5$oth_fam[i] = 1 } 
  else if( SHARE_w5_oth_fam$dn026_1[i] == -999 & SHARE_w5_oth_fam$dn026_2[i] == -999 & 
           SHARE_w5_oth_fam$dn036_[i] == -999 & SHARE_w5_oth_fam$dn037_[i] == -999 ){
    SHARE_ds_w5$oth_fam[i] = 999 }
  else if( SHARE_w5_oth_fam$dn026_1[i] %in% c(-2,-999) & SHARE_w5_oth_fam$dn026_2[i] %in% c(-2,-999) & 
           SHARE_w5_oth_fam$dn036_[i] %in% c(-2,-999) & SHARE_w5_oth_fam$dn037_[i] %in% c(-2,-999) ){
    SHARE_ds_w5$oth_fam[i] = 997 }
  else if( SHARE_w5_oth_fam$dn026_1[i] %in% c(-1,-999) & SHARE_w5_oth_fam$dn026_2[i] %in% c(-1,-999) & 
           SHARE_w5_oth_fam$dn036_[i] %in% c(-1,-999) & SHARE_w5_oth_fam$dn037_[i] %in% c(-1,-999) ){
    SHARE_ds_w5$oth_fam[i] = 998 }
  else if( SHARE_w5_oth_fam$dn026_1[i] %in% c(-9,-999) & SHARE_w5_oth_fam$dn026_2[i] %in% c(-9,-999) & 
           SHARE_w5_oth_fam$dn036_[i] %in% c(-9,-999) & SHARE_w5_oth_fam$dn037_[i] %in% c(-9,-999) ){
    SHARE_ds_w5$oth_fam[i] = 996 }
  else if( SHARE_w5_oth_fam$dn026_1[i] %in% c(-5,-999) & SHARE_w5_oth_fam$dn026_2[i] %in% c(-5,-999) & 
           SHARE_w5_oth_fam$dn036_[i] %in% c(-5,-999) & SHARE_w5_oth_fam$dn037_[i] %in% c(-5,-999) ){
    SHARE_ds_w5$oth_fam[i] = 995 }
  else if( SHARE_w5_oth_fam$dn026_1[i] == 5 & SHARE_w5_oth_fam$dn026_2[i] == 5 & 
           SHARE_w5_oth_fam$dn036_[i] == 0 & SHARE_w5_oth_fam$dn037_[i] == 0 ){
    SHARE_ds_w5$oth_fam[i] = 0 }
}

SHARE_ds_w5$oth_fam <- car::recode(as.vector(SHARE_ds_w5$oth_fam), "NA='999'")
SHARE_ds_w5$oth_fam <- labelled(SHARE_ds_w5$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript5, echo=F}
vari <- SHARE_ds_w5$oth_fam
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_ds_w5$oth_fam, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SHARE_ds_w5, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Has other family members?") + ylab("Frequency")
```

##### Validation
```{r crosstabulation5, echo=F}

```

 
```{r save, echo=FALSE}
oth_fam <- SHARE_ds_w1
save(oth_fam, file = "../RData/w1/oth_fam.RData")
rm(oth_fam)

oth_fam <- SHARE_ds_w2
save(oth_fam, file = "../RData/w2/oth_fam.RData")
rm(oth_fam)

oth_fam <- SHARE_ds_w4
save(oth_fam, file = "../RData/w4/oth_fam.RData")
rm(oth_fam)

oth_fam <- SHARE_ds_w5
save(oth_fam, file = "../RData/w5/oth_fam.RData")
rm(oth_fam)

```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```


