---
title: "Whether receives instrumental support (practical help) from people outside the household (relatives/friends/neighbours)"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `inst_sup`
* Variable label: `Instrumental support (practical help) from people outside the household (relatives/friends/neighbours)`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process

## SHARE

### Wave 1

#### Study-specific variables

The study-specific variable elected to be harmonised is:

    
* Name: `sp002_`
* Label: `received help from outside the household`
* Categories:
    + `1 = yes`
    + `5 = no`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`
 
 
* Description: 
```{r assign1}
opal.assign.table.tibble(o, 'SHARE_w1_inst_sup','SHARE.sharew1_rel2-6-0_sp',variables=list('sp002_'), missings = TRUE)
```

```{r local1}
SHARE_w1_inst_sup <- opal.execute(o,'SHARE_w1_inst_sup')
vari <- SHARE_w1_inst_sup$sp002_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
#Categorical_summary(var =SHARE_w1_inst_sup$sp002_, missing_values = NA)
ggplot(SHARE_w1_inst_sup, aes(x=factor(sp002_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("received help from outside the household") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `5 into 0`
* `-2 into 997`
* `-1 into 998`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
SHARE_ds_w1 <- tibble(id=SHARE_w1_inst_sup$id)
SHARE_ds_w1$inst_sup <- car::recode(as.vector(SHARE_w1_inst_sup$sp002_), "5='0'; 1='1'; -2='997'; -1='998'; NA='999'")
SHARE_ds_w1$inst_sup <- labelled(SHARE_ds_w1$inst_sup, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1}
vari <- SHARE_ds_w1$inst_sup
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_ds_w1$inst_sup, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SHARE_ds_w1, aes(x=factor(inst_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Instrumental support (practical help) from people outside the household (relatives/friends/neighbours)") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1}
AfterH <- table(SHARE_ds_w1$inst_sup)
BeforeH <- table(SHARE_w1_inst_sup$sp002_, useNA='ifany')[c(4,3,1,2,5)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1->1","-2->997","-1->998","NA->999")
kable(C)
```


### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:
 
* Name: `sp002_`
* Label: `received help from outside the household`
* Categories:
    + `1 = yes`
    + `5 = no`
* Missings:
    + `-2 = refusal`
    + `-1 = don't know`
 
 
* Description: 
```{r assign2}
opal.assign.table.tibble(o, 'SHARE_w2_inst_sup','SHARE.sharew2_rel2-6-0_sp',variables=list('sp002_'), missings = TRUE)
```

```{r local2}
SHARE_w2_inst_sup <- opal.execute(o,'SHARE_w2_inst_sup')
vari <- SHARE_w2_inst_sup$sp002_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
#Categorical_summary(var =SHARE_w2_inst_sup$sp002_, missing_values = NA)
ggplot(SHARE_w2_inst_sup, aes(x=factor(sp002_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("received help from outside the household") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `5 into 0`
* `-2 into 997`
* `-1 into 998`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
SHARE_ds_w2 <- tibble(id=SHARE_w2_inst_sup$id)
SHARE_ds_w2$inst_sup <- car::recode(as.vector(SHARE_w2_inst_sup$sp002_), "5='0'; 1='1'; -2='997'; -1='998'; NA='999'")
SHARE_ds_w2$inst_sup <- labelled(SHARE_ds_w2$inst_sup, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2}
vari <- SHARE_ds_w2$inst_sup
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_ds_w2$inst_sup, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SHARE_ds_w2, aes(x=factor(inst_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Instrumental support (practical help) from people outside the household (relatives/friends/neighbours)") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2}
AfterH <- table(SHARE_ds_w2$inst_sup)
BeforeH <- table(SHARE_w2_inst_sup$sp002_, useNA='ifany')[c(4,3,1,2,5)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1->1","-2->997","-1->998","NA->999")
kable(C)
```



### Wave 4

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `sp002_` 
* Label: `received help from outside the household`
* Categories:
    + `1 = yes`
    + `5 = no`
* Missings:
    + `-9 = not applicable (e.g.filtered)`
    + `-5 = not answered`
    + `-2 = refusal`
    + `-1 = don't know`
 
* Description: 
```{r assign4}
opal.assign.table.tibble(o, 'SHARE_w4_inst_sup','SHARE.sharew4_rel1-1-1_sp', variables=list('sp002_'), missings = TRUE)
```

```{r local4}
SHARE_w4_inst_sup <- opal.execute(o,'SHARE_w4_inst_sup')
vari <- SHARE_w4_inst_sup$sp002_
kable(Categorical_summary(vari, missing_values = c(-1,-2, -5,-9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-2,-5,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2,-5,-9))[2], caption = "Type of missing")
#Categorical_summary(var =SHARE_w4_inst_sup$sp002_, missing_values = NA)
ggplot(SHARE_w4_inst_sup, aes(x=factor(sp002_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("received help from outside the household") + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `5 into 0`
* `-9 into 996`
* `-5 into 995`
* `-2 into 997`
* `-1 into 998`
* `NA into 999`

**R script:**

```{r harmo4, echo=TRUE}
SHARE_ds_w4 <- tibble(id=SHARE_w4_inst_sup$id)
SHARE_ds_w4$inst_sup <- car::recode(as.vector(SHARE_w4_inst_sup$sp002_), "1='1'; 5='0'; -9='996'; -5='995'; -2='997'; -1='998'; NA='999'")
SHARE_ds_w4$inst_sup <- labelled(SHARE_ds_w4$inst_sup, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4}
vari <- SHARE_ds_w4$inst_sup
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_ds_w4$inst_sup, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SHARE_ds_w4, aes(x=factor(inst_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Instrumental support (practical help) from people outside the household (relatives/friends/neighbours)") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4}
AfterH <- table(SHARE_ds_w4$inst_sup)
BeforeH <- table(SHARE_w4_inst_sup$sp002_, useNA='ifany')[c(4,3,1,2,5)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1->1","-2->997","-1->998","NA->999")
kable(C)
```





### Wave 5

#### Study-specific variables

The study-specific variable elected to be harmonised is:
  
* Name: `sp002_`
* Label: `received help from outside the household`
* Categories:
    + `1 = yes`
    + `5 = no`
* Missings:
    + `-9 = not applicable (e.g.filtered)`
    + `-5 = not answered`
    + `-2 = refusal`
    + `-1 = don't know`
 
* Description: 
```{r assign5}
opal.assign.table.tibble(o, 'SHARE_w5_inst_sup','SHARE.sharew5_rel1-0-0_sp', variables=list('sp002_'), missings = TRUE)
```

```{r local5}
SHARE_w5_inst_sup <- opal.execute(o,'SHARE_w5_inst_sup')
vari <- SHARE_w5_inst_sup$sp002_
kable(Categorical_summary(vari, missing_values = c(-1,-2, -5,-9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-1,-2,-5,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2,-5,-9))[2], caption = "Type of missing")
#Categorical_summary(var =SHARE_w5_inst_sup$sp002_, missing_values = NA)
ggplot(SHARE_w5_inst_sup, aes(x=factor(sp002_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("received help from outside the household") + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1`
* `5 into 0`
* `-9 into 996`
* `-5 into 995`
* `-2 into 997`
* `-1 into 998`
* `NA into 999`

**R script:**

```{r harmo5, echo=TRUE}
SHARE_ds_w5 <- tibble(id=SHARE_w5_inst_sup$id)
SHARE_ds_w5$inst_sup <- car::recode(as.vector(SHARE_w5_inst_sup$sp002_), "1='1'; 5='0'; -9='996'; -5='995'; -2='997'; -1='998'; NA='999'")
SHARE_ds_w5$inst_sup <- labelled(SHARE_ds_w5$inst_sup, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript5}
vari <- SHARE_ds_w5$inst_sup
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_ds_w5$inst_sup, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SHARE_ds_w5, aes(x=factor(inst_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Instrumental support (practical help) from people outside the household (relatives/friends/neighbours)") + ylab("Frequency")
```

#### Validation
```{r crosstabulation5}
AfterH <- table(SHARE_ds_w5$inst_sup)
BeforeH <- table(SHARE_w5_inst_sup$sp002_, useNA='ifany')[c(4,3,1,2,5)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1->1","-2->997","-1->998","NA->999")
kable(C)
```


```{r save, echo=FALSE}
inst_sup <- SHARE_ds_w1
save(inst_sup, file = "../RData/w1/inst_sup.RData")
rm(inst_sup)

inst_sup <- SHARE_ds_w2
save(inst_sup, file = "../RData/w2/inst_sup.RData")
rm(inst_sup)

inst_sup <- SHARE_ds_w4
save(inst_sup, file = "../RData/w4/inst_sup.RData")
rm(inst_sup)



inst_sup <- SHARE_ds_w5
save(inst_sup, file = "../RData/w5/inst_sup.RData")
rm(inst_sup)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```

