---
title: "Current depressive status"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE, echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_albert.r")
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/CHARLS/CHARLS_ids.r")  
```

<!-- ########################################################## --> 

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `depression`
* Variable label: `Current depressive status of the participant`
* Variable description: `Current depressive status of the participant`
* Domain: `Psycological measures`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | no depression
1        | depression

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


```{r lab, echo=FALSE}
ds_label <- "Current depressive status"
ds_label_all <- "Current depressive status of the participant"
```

# Data process

## CHARLS: China (All counties with the exception of Tibet)

### Wave 1 

#### Study-specific variable description



| **Name** | `dc009`| `dc010` | `dc011` | `dc012` | `dc013` | `dc014` | `dc015` | `dc016` | `dc017` | `dc018` | 
|-|-|-|-|-|-|-|-|-|-|-| 
| **Label** | `Bothered by Things`| `Had Trouble Keeping Mind` | `Felt Depressed` | `Felt Everything I Did Was An Effort` | `Felt Hopeful About the Future` | `Felt fearful` | `Sleep Was Restless` | `Happy` | `Felt Lonely` | `Could Not Get Going` | 
| **Table name** | `health_status_and_functioning_wave1` | `health_status_and_functioning_wave1` | `health_status_and_functioning_wave1` | `health_status_and_functioning_wave1` | `health_status_and_functioning_wave1` | `health_status_and_functioning_wave1` | `health_status_and_functioning_wave1` | `health_status_and_functioning_wave1` | `health_status_and_functioning_wave1` | `health_status_and_functioning_wave1` | 
| **Categories** |`1 = Rarely or none of the time <1 day`| `1 = Rarely or none of the time <1 day` | `1 = Rarely or none of the time <1 day` | `1 = Rarely or none of the time <1 day` | `1 = Rarely or none of the time <1 day` | `1 = Rarely or none of the time <1 day` | `1 = Rarely or none of the time <1 day` | `1 = Rarely or none of the time <1 day` | `1 = Rarely or none of the time <1 day` | `1 = Rarely or none of the time <1 day` | 
| | `2 = Some or a little of the time 1-2 days` | `2 = Some or a little of the time 1-2 days`| `2 = Some or a little of the time 1-2 days` | `2 = Some or a little of the time 1-2 days` | `2 = Some or a little of the time 1-2 days` | `2 = Some or a little of the time 1-2 days` | `2 = Some or a little of the time 1-2 days` | `2 = Some or a little of the time 1-2 days` | `2 = Some or a little of the time 1-2 days` | `2 = Some or a little of the time 1-2 days` | 
| | `3 = Occasionally or a moderate amount of the time 3-4 days` | `3 = Occasionally or a moderate amount of the time 3-4 days` | `3 = Occasionally or a moderate amount of the time 3-4 days` | `3 = Occasionally or a moderate amount of the time 3-4 days` | `3 = Occasionally or a moderate amount of the time 3-4 days` | `3 = Occasionally or a moderate amount of the time 3-4 days` | `3 = Occasionally or a moderate amount of the time 3-4 days` | `3 = Occasionally or a moderate amount of the time 3-4 days` | `3 = Occasionally or a moderate amount of the time 3-4 days` | `3 = Occasionally or a moderate amount of the time 3-4 days` | 
| | `4 = Most or all of the time 5-7 days` | `4 = Most or all of the time 5-7 days` | `4 = Most or all of the time 5-7 days` | `4 = Most or all of the time 5-7 days` | `4 = Most or all of the time 5-7 days` | `4 = Most or all of the time 5-7 days` | `4 = Most or all of the time 5-7 days` | `4 = Most or all of the time 5-7 days` | `4 = Most or all of the time 5-7 days` | `4 = Most or all of the time 5-7 days` | 

```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'CHARLS_dep2','CHARLS.health_status_and_functioning_wave1',
                         variables=list('dc009', 'dc010', 'dc011', 'dc012', 'dc013', 'dc014', 'dc015', 'dc016', 'dc017', 'dc018'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w1_id','CHARLS.CHARLS_w1_ids',
                         variables=list('var'), missings = TRUE)

CHARLS_dep2 <- opal.execute(o,'CHARLS_dep2')
CHARLS_w1_id <- opal.execute(o,'CHARLS_w1_id')

CHARLS_dep2$oldid <- CHARLS_dep2$id
CHARLS_dep2$id <- CHARLS_ids(ids = CHARLS_dep2$oldid)
```

```{r local1, echo=FALSE}
Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], rep(NA,11))
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], oldid=as.numeric(new_2[,12]), dc009=as.numeric(new_2[,2]), dc010=as.numeric(new_2[,3]), dc011=as.numeric(new_2[,4]), dc012=as.numeric(new_2[,5]), dc013=as.numeric(new_2[,6]), dc014=as.numeric(new_2[,7]), dc015=as.numeric(new_2[,8]), dc016=as.numeric(new_2[,9]), dc017=as.numeric(new_2[,10]), dc018=as.numeric(new_2[,11]))
  new_22
}

CHARLS_dep <- Add_indiv(old = CHARLS_dep2, new = CHARLS_w1_id)

vari <- CHARLS_dep$dc009
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- CHARLS_dep$dc010
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- CHARLS_dep$dc011
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- CHARLS_dep$dc012
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- CHARLS_dep$dc013
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- CHARLS_dep$dc014
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- CHARLS_dep$dc015
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- CHARLS_dep$dc016
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- CHARLS_dep$dc017
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- CHARLS_dep$dc018
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

First of all: 

* The reversed items dc013, dc016: 
    + `recode 1 into 3`
    + `keep 2 into 2`
    + `recode 3 into 1`
    + `recode 4 into 0`
  
* The direct items dc009, dc010, dc011, dc012, dc014, dc015, dc017, dc018: 
    + `recode 1 into 0`
    + `recode 2 into 1`
    + `recode 3 into 2`
    + `recode 4 into 3` 

Secondly in order to get the final score the items have to be summed. If one to 2 items are missing, scores on the completed items are summed; the total is divided by the number of items answered and multiplied by 10. If more than 2 items are missing the individual get a missing value in the final score. 

After get the final score, it has to be recoded as follows: 

* `0-9 into 0`
* `>9 into 1`
* `NA into 999`



**R script:**

```{r harmo1, echo=TRUE}
#reversed items
CHARLS_dep$p13 <- car::recode(CHARLS_dep$dc013, "1=3; 3=1; 4=0")
CHARLS_dep$p16 <- car::recode(CHARLS_dep$dc016, "1=3; 3=1; 4=0")

#direct items
CHARLS_dep$p9 <- car::recode(CHARLS_dep$dc009, "1=0; 2=1; 3=2; 4=3")
CHARLS_dep$p10 <- car::recode(CHARLS_dep$dc010, "1=0; 2=1; 3=2; 4=3")
CHARLS_dep$p11 <- car::recode(CHARLS_dep$dc011, "1=0; 2=1; 3=2; 4=3")
CHARLS_dep$p12 <- car::recode(CHARLS_dep$dc012, "1=0; 2=1; 3=2; 4=3")
CHARLS_dep$p14 <- car::recode(CHARLS_dep$dc014, "1=0; 2=1; 3=2; 4=3")
CHARLS_dep$p15 <- car::recode(CHARLS_dep$dc015, "1=0; 2=1; 3=2; 4=3")
CHARLS_dep$p17 <- car::recode(CHARLS_dep$dc017, "1=0; 2=1; 3=2; 4=3")
CHARLS_dep$p18 <- car::recode(CHARLS_dep$dc018, "1=0; 2=1; 3=2; 4=3")


CHARLS_dep$nmiss <- apply(CHARLS_dep[,13:22], MARGIN = 1, FUN = function(x) sum(is.na(x)))

CHARLS_dep$final_score <- apply(CHARLS_dep[,13:22], MARGIN = 1, FUN = function(x) sum(x, na.rm = TRUE))

CHARLS_dep$final_score[which(CHARLS_dep$nmiss==2)] <- (CHARLS_dep$final_score[which(CHARLS_dep$nmiss==2)]/8)*10
CHARLS_dep$final_score[which(CHARLS_dep$nmiss==1)] <- (CHARLS_dep$final_score[which(CHARLS_dep$nmiss==1)]/9)*10

CHARLS_dep$final_score[which(CHARLS_dep$nmiss>2)] <- 999

CHARLS_ds_w1 <- tibble(id=CHARLS_dep$id)
CHARLS_ds_w1$depression <- car::recode(CHARLS_dep$final_score, "0:9=0; 10:900=1")
CHARLS_ds_w1$depression <- labelled(CHARLS_ds_w1[[2]], labels = c("no depression"=0, "depression"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- CHARLS_ds_w1$depression
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(CHARLS_ds_w1, aes(x=factor(CHARLS_ds_w1[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=FALSE}
BeforeH <- c(sum(na.omit(CHARLS_dep$final_score)<10), sum(na.omit(CHARLS_dep$final_score)>=10 & na.omit(CHARLS_dep$final_score)<900),  sum(na.omit(CHARLS_dep$final_score)==999))
AfterH <- table(CHARLS_ds_w1[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<10->0",">=10->1", "NA->999") 
kable(C)
```

```{r importOPAL1, echo=FALSE}
label(CHARLS_ds_w1$depression) <- ds_label_all
depression <- CHARLS_ds_w1
save(depression, file = "../RData/w1/depression.RData")
rm(depression, CHARLS_dep)
```


### Wave 2 

#### Study-specific variable description

| **Name** | `dc009`| `dc010` | `dc011` | `dc012` | `dc013` | `dc014` | `dc015` | `dc016` | `dc017` | `dc018` | 
|-|-|-|-|-|-|-|-|-|-|-| 
| **Label** | `Bothered by Things`| `Had Trouble Keeping Mind` | `Felt Depressed` | `Felt Everything I Did Was An Effort` | `Felt Hopeful About the Future` | `Felt fearful` | `Sleep Was Restless` | `Happy` | `Felt Lonely` | `Could Not Get Going` | 
| **Table name** | `Health_Status_and_Functioning_wave2` | `Health_Status_and_Functioning_wave2` | `Health_Status_and_Functioning_wave2` | `Health_Status_and_Functioning_wave2` | `Health_Status_and_Functioning_wave2` | `Health_Status_and_Functioning_wave2` | `Health_Status_and_Functioning_wave2` | `Health_Status_and_Functioning_wave2` | `Health_Status_and_Functioning_wave2` | `Health_Status_and_Functioning_wave2` | 
| **Categories** |`1 = Rarely or none of the time <1 day`| `1 = Rarely or none of the time <1 day` | `1 = Rarely or none of the time <1 day` | `1 = Rarely or none of the time <1 day` | `1 = Rarely or none of the time <1 day` | `1 = Rarely or none of the time <1 day` | `1 = Rarely or none of the time <1 day` | `1 = Rarely or none of the time <1 day` | `1 = Rarely or none of the time <1 day` | `1 = Rarely or none of the time <1 day` | 
| | `2 = Some or a little of the time 1-2 days` | `2 = Some or a little of the time 1-2 days`| `2 = Some or a little of the time 1-2 days` | `2 = Some or a little of the time 1-2 days` | `2 = Some or a little of the time 1-2 days` | `2 = Some or a little of the time 1-2 days` | `2 = Some or a little of the time 1-2 days` | `2 = Some or a little of the time 1-2 days` | `2 = Some or a little of the time 1-2 days` | `2 = Some or a little of the time 1-2 days` | 
| | `3 = Occasionally or a moderate amount of the time 3-4 days` | `3 = Occasionally or a moderate amount of the time 3-4 days` | `3 = Occasionally or a moderate amount of the time 3-4 days` | `3 = Occasionally or a moderate amount of the time 3-4 days` | `3 = Occasionally or a moderate amount of the time 3-4 days` | `3 = Occasionally or a moderate amount of the time 3-4 days` | `3 = Occasionally or a moderate amount of the time 3-4 days` | `3 = Occasionally or a moderate amount of the time 3-4 days` | `3 = Occasionally or a moderate amount of the time 3-4 days` | `3 = Occasionally or a moderate amount of the time 3-4 days` | 
| | `4 = Most or all of the time 5-7 days` | `4 = Most or all of the time 5-7 days` | `4 = Most or all of the time 5-7 days` | `4 = Most or all of the time 5-7 days` | `4 = Most or all of the time 5-7 days` | `4 = Most or all of the time 5-7 days` | `4 = Most or all of the time 5-7 days` | `4 = Most or all of the time 5-7 days` | `4 = Most or all of the time 5-7 days` | `4 = Most or all of the time 5-7 days` | 

```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'CHARLS_dep2','CHARLS.Health_Status_and_Functioning_wave2',
                         variables=list('dc009', 'dc010', 'dc011', 'dc012', 'dc013', 'dc014', 'dc015', 'dc016', 'dc017', 'dc018'), missings = TRUE)
opal.assign.table.tibble(o, 'CHARLS_w2_id','CHARLS.CHARLS_w2_ids',
                         variables=list('var'), missings = TRUE)
CHARLS_w2_id <- opal.execute(o,'CHARLS_w2_id')
CHARLS_dep2 <- opal.execute(o,'CHARLS_dep2')
```

```{r local2, echo=FALSE}
Add_indiv <- function(old, new){
  
  new_2 <- matrix(rep(NA, dim(new)[1]*dim(old)[2] ), nrow = dim(new)[1])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], rep(NA,10))
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], dc009=as.numeric(new_2[,2]), dc010=as.numeric(new_2[,3]), dc011=as.numeric(new_2[,4]), dc012=as.numeric(new_2[,5]), dc013=as.numeric(new_2[,6]), dc014=as.numeric(new_2[,7]), dc015=as.numeric(new_2[,8]), dc016=as.numeric(new_2[,9]), dc017=as.numeric(new_2[,10]), dc018=as.numeric(new_2[,11]))
  new_22
}

CHARLS_dep <- Add_indiv(old = CHARLS_dep2, new = CHARLS_w2_id)

vari <- CHARLS_dep$dc009
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- CHARLS_dep$dc010
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- CHARLS_dep$dc011
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- CHARLS_dep$dc012
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- CHARLS_dep$dc013
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- CHARLS_dep$dc014
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- CHARLS_dep$dc015
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- CHARLS_dep$dc016
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- CHARLS_dep$dc017
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- CHARLS_dep$dc018
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(CHARLS_dep, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

First of all: 

* The reversed items dc013, dc016: 
    + `recode 1 into 3`
    + `keep 2 into 2`
    + `recode 3 into 1`
    + `recode 4 into 0`
  
* The direct items dc009, dc010, dc011, dc012, dc014, dc015, dc017, dc018: 
    + `recode 1 into 0`
    + `recode 2 into 1`
    + `recode 3 into 2`
    + `recode 4 into 3` 

Secondly in order to get the final score the items have to be summed. If one to 2 items are missing, scores on the completed items are summed; the total is divided by the number of items answered and multiplied by 10. If more than 2 items are missing the individual get a missing value in the final score. 

After get the final score, it has to be recoded as follows: 

* `0-9 into 0`
* `>9 into 1`
* `NA into 999`


**R script:**

```{r harmo2, echo=TRUE}
#reversed items
CHARLS_dep$p13 <- car::recode(CHARLS_dep$dc013, "1=3; 3=1; 4=0")
CHARLS_dep$p16 <- car::recode(CHARLS_dep$dc016, "1=3; 3=1; 4=0")

#direct items
CHARLS_dep$p9 <- car::recode(CHARLS_dep$dc009, "1=0; 2=1; 3=2; 4=3")
CHARLS_dep$p10 <- car::recode(CHARLS_dep$dc010, "1=0; 2=1; 3=2; 4=3")
CHARLS_dep$p11 <- car::recode(CHARLS_dep$dc011, "1=0; 2=1; 3=2; 4=3")
CHARLS_dep$p12 <- car::recode(CHARLS_dep$dc012, "1=0; 2=1; 3=2; 4=3")
CHARLS_dep$p14 <- car::recode(CHARLS_dep$dc014, "1=0; 2=1; 3=2; 4=3")
CHARLS_dep$p15 <- car::recode(CHARLS_dep$dc015, "1=0; 2=1; 3=2; 4=3")
CHARLS_dep$p17 <- car::recode(CHARLS_dep$dc017, "1=0; 2=1; 3=2; 4=3")
CHARLS_dep$p18 <- car::recode(CHARLS_dep$dc018, "1=0; 2=1; 3=2; 4=3")


CHARLS_dep$nmiss <- apply(CHARLS_dep[,12:21], MARGIN = 1, FUN = function(x) sum(is.na(x)))

CHARLS_dep$final_score <- apply(CHARLS_dep[,12:21], MARGIN = 1, FUN = function(x) sum(x, na.rm = TRUE))

CHARLS_dep$final_score[which(CHARLS_dep$nmiss==2)] <- (CHARLS_dep$final_score[which(CHARLS_dep$nmiss==2)]/8)*10
CHARLS_dep$final_score[which(CHARLS_dep$nmiss==1)] <- (CHARLS_dep$final_score[which(CHARLS_dep$nmiss==1)]/9)*10

CHARLS_dep$final_score[which(CHARLS_dep$nmiss>2)] <- 999

CHARLS_ds_w2 <- tibble(id=CHARLS_dep$id)
CHARLS_ds_w2$depression <- car::recode(CHARLS_dep$final_score, "0:9=0; 10:900=1")
CHARLS_ds_w2$depression <- labelled(CHARLS_ds_w2[[2]], labels = c("no depression"=0, "depression"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- CHARLS_ds_w2$depression
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(CHARLS_ds_w2, aes(x=factor(CHARLS_ds_w2[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r crosstabulation2, echo=FALSE}
BeforeH <- c(sum(na.omit(CHARLS_dep$final_score)<10), sum(na.omit(CHARLS_dep$final_score)>=10 & na.omit(CHARLS_dep$final_score)<900),  sum(na.omit(CHARLS_dep$final_score)==999))
AfterH <- table(CHARLS_ds_w2[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<10->0",">=10->1", "NA->999") 
kable(C)
```


```{r importOPAL2, echo=FALSE}
label(CHARLS_ds_w2$depression) <- ds_label_all
depression <- CHARLS_ds_w2
save(depression, file = "../RData/w2/depression.RData")
rm(depression)
```


# Quality estimation

The Center for Epidemiologic Studies Depression Scale (CES-D) 10-item version test (likert response) was used.
We get the harmonized variable using the single items (we didn't have the final score variable).
We follow this criteria regarding the missing items: only two missing items were allowed > score the completed items divided by the number of items answered and multiplied by 10.  


```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
