---
title: "Proxy"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/proxyDS.Rmd'}
```

```{r global, echo=F}
source('../../_DS_Rmd/proxyDS.R')
```



<!-- ########################################################## --> 

# Data process

## India

### Wave 1 

#### Study-specific variable description

| **Name** | `dm035`| `fs512_proxy` | `ht226_proxy` | `ht413_proxy` | `we606_proxy` |
|-|-|-|-|-|-|
| **Label** | `proxy interview`| `is this a proxy interview` | `was this a proxy interview` | `is this a proxy interview` | `proxy interview` |
| **Table name** | `LASI-Pilot_all` |`LASI-Pilot_all` |`LASI-Pilot_all` |`LASI-Pilot_all` |`LASI-Pilot_all` |
| **Categories** |`1 = yes`|`1 = yes`|`1 = yes`|`1 = yes`|`1 = yes`|
| | `2 = no` |`2 = no` |`2 = no` |`2 = no` |`2 = no` |
| **Description** |  |  |  |  |  |

```{r assign1,  echo=FALSE}
opal.assign.table.tibble(o, 'LASI_proxy','LASI.LASI-Pilot_all',
                         variables=list('dm035', 'fs512_proxy', 'ht226_proxy', 'ht413_proxy', 'we606_proxy'), missings = TRUE)
LASI_proxy <- opal.execute(o,'LASI_proxy')

LASI_proxy$all <- apply(LASI_proxy[,-1], MARGIN = 1, function(x) paste0(x[1], x[2], x[3], x[4], x[5]))
```


```{r local1,  echo=FALSE}
vari <- LASI_proxy$dm035
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(LASI_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- LASI_proxy$fs512_proxy
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(LASI_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- LASI_proxy$ht226_proxy
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(LASI_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- LASI_proxy$ht413_proxy
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(LASI_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- LASI_proxy$we606_proxy
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(LASI_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable from the study-specific variables they has to be recoded as follows:

* `if any of the variables is 1 (yes) recode proxy = 1`
* `otherwise proxy = 0`

**R script:**

```{r harmo1,   echo=TRUE}
LASI_proxy$have1 <- apply(LASI_proxy[,-1], MARGIN = 1, FUN = function(x) sum(x==1, na.rm = TRUE)>=1)

LASI_ds_w1 <- tibble(id=LASI_proxy$id)
LASI_ds_w1$proxy <- 0
LASI_ds_w1$proxy[LASI_proxy$have1] <- 1
LASI_ds_w1$proxy <- labelled(LASI_ds_w1$proxy, labels = cat_label)
label(LASI_ds_w1$proxy) <- ds_label_all
```

#### Statistical description of the new harmonised variable
```{r descript1,  echo=FALSE}
vari <- LASI_ds_w1$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(LASI_ds_w1, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL1,  echo=FALSE}
proxy <- LASI_ds_w1
save(proxy, file = "../RData/w1/proxy.RData")
rm(proxy)
```


# Quality estimation
There are two more variables called 'proxy_h' and 'proxy_r' that wasn't take account because they are wrong, the values doesn't fit with the values on the questionnaire.


```{r closeRsession, echo=FALSE,  echo=FALSE} 
opal.logout(o)
```




