---
title: "Month of interview"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `mintw`
* Variable label: `month of interview`
* Domain: `Other administrative variables`
* Value type: `Categorical`
* Categories: 

**Code** | **Category Label**
----| ------------------
1   | january
2   | february
3   | march 
4   | april 
5   | may
6   | june
7   | july
8   | august
9   | september
10  | october
11  | november
12  | december

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process


```{r, dataDirectory, echo=FALSE}
datafolder <- "../RData"
```

## England

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `iintdatm`
* Label: `interview month - individual interview`
* Type of variable: `countinous`

```{r assign1, echo=F}
opal.assign.table.tibble(o,'ELSA_w1_minter','ELSA.wave_1_ifs_derived_variables',
                         variables=list('iintdatm'), missings = TRUE)
```

```{r local1, echo=F}
ELSA_w1_minter <- opal.execute(o,'ELSA_w1_minter')
Categorical_summary(var = ELSA_w1_minter$iintdatm, missing_values = NA)
ggplot(ELSA_w1_minter, aes(x=factor(iintdatm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo1}
ELSA_ds_w1 <- tibble(id=ELSA_w1_minter$id)
ELSA_ds_w1$mintw <- car::recode(ELSA_w1_minter$iintdatm, "NA=999")
ELSA_ds_w1$mintw <- labelled(ELSA_ds_w1$mintw, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
Categorical_summary(var = ELSA_ds_w1$mintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w1, aes(x=factor(mintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
BeforeH <- table(ELSA_w1_minter$iintdatm, useNA = "ifany")
AfterH <- table(ELSA_ds_w1$mintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```





```{r importOPAL1, echo=F}
val_labels(ELSA_ds_w1) <- NULL
#opal.assign.data(o, 'ELSA_ds_w1', ELSA_ds_w1)
#opal.symbol_import(o,'ELSA_ds_w1', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w1 <- ELSA_ds_w1
ELSA_m_ds_w1$mintw <- car::recode(ELSA_m_ds_w1$mintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w1', ELSA_m_ds_w1)
#opal.symbol_import(o,'ELSA_m_ds_w1', project='_Athlos_Harm_Dataset')
```





### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `iintdatm`
* Label: `interview month - individual interview`
* Type of variable: `countinous`

```{r assign2, echo=F}
opal.assign.table.tibble(o, 'ELSA_w2_minter','ELSA.wave_2_ifs_derived_variables',
                         variables=list('iintdatm'), missings = TRUE)
```

```{r local2, echo=F}
ELSA_w2_minter <- opal.execute(o,'ELSA_w2_minter')
Categorical_summary(var = ELSA_w2_minter$iintdatm, missing_values = NA)
ggplot(ELSA_w2_minter, aes(x=factor(iintdatm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo2}
ELSA_ds_w2 <- tibble(id=ELSA_w2_minter$id)
ELSA_ds_w2$mintw <- car::recode(ELSA_w2_minter$iintdatm, "NA=999")
ELSA_ds_w2$mintw <- labelled(ELSA_ds_w2$mintw, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
Categorical_summary(var = ELSA_ds_w2$mintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w2, aes(x=factor(mintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
BeforeH <- table(ELSA_w2_minter$iintdatm, useNA = "ifany")
AfterH <- table(ELSA_ds_w2$mintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```





```{r importOPAL2, echo=F}
val_labels(ELSA_ds_w2) <- NULL
#opal.assign.data(o, 'ELSA_ds_w2', ELSA_ds_w2)
#opal.symbol_import(o,'ELSA_ds_w2', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w2 <- ELSA_ds_w2
ELSA_m_ds_w2$mintw <- car::recode(ELSA_m_ds_w2$mintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w2', ELSA_m_ds_w2)
#opal.symbol_import(o,'ELSA_m_ds_w2', project='_Athlos_Harm_Dataset')
```







### Wave 3

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `iintdatm`
* Label: `interview month - individual interview`
* Type of variable: `countinous`


```{r assign3, echo=F}
opal.assign.table.tibble(o, 'ELSA_w3_yinter','ELSA.wave_3_ifs_derived_variables',
                         variables=list('iintdatm'), missings = TRUE)
```

```{r local3, echo=F}
ELSA_w3_yinter <- opal.execute(o,'ELSA_w3_yinter')
Categorical_summary(var = ELSA_w3_yinter$iintdatm, missing_values = NA)
ggplot(ELSA_w3_yinter, aes(x=factor(iintdatm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo3}
ELSA_ds_w3 <- tibble(id=ELSA_w3_yinter$id)
ELSA_ds_w3$mintw <- car::recode(ELSA_w3_yinter$iintdatm, "NA=999")
ELSA_ds_w3$mintw <- labelled(ELSA_ds_w3$mintw, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}
Categorical_summary(var = ELSA_ds_w3$mintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w3, aes(x=factor(mintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=F}
BeforeH <- table(ELSA_w3_yinter$iintdatm, useNA = "ifany")
AfterH <- table(ELSA_ds_w3$mintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```





```{r importOPAL3, echo=F}
val_labels(ELSA_ds_w3) <- NULL
#opal.assign.data(o, 'ELSA_ds_w3', ELSA_ds_w3)
#opal.symbol_import(o,'ELSA_ds_w3', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w3 <- ELSA_ds_w3
ELSA_m_ds_w3$mintw <- car::recode(ELSA_m_ds_w3$mintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w3', ELSA_m_ds_w3)
#opal.symbol_import(o,'ELSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```






### Wave 4

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `iintdatm`
* Label: `interview month - individual interview`
* Type of variable: `countinous`

```{r assign4, echo=F}
opal.assign.table.tibble(o, 'ELSA_w4_yinter','ELSA.wave_4_ifs_derived_variables',
                         variables=list('iintdatm'), missings = TRUE)
```

```{r local4, echo=F}
ELSA_w4_yinter <- opal.execute(o,'ELSA_w4_yinter')
Categorical_summary(var = ELSA_w4_yinter$iintdatm, missing_values = NA)
ggplot(ELSA_w4_yinter, aes(x=factor(iintdatm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo4}
ELSA_ds_w4 <- tibble(id=ELSA_w4_yinter$id)
ELSA_ds_w4$mintw <- car::recode(ELSA_w4_yinter$iintdatm, "NA=999")
ELSA_ds_w4$mintw <- labelled(ELSA_ds_w4$mintw, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript4, echo=F}
Categorical_summary(var = ELSA_ds_w4$mintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w4, aes(x=factor(mintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=F}
BeforeH <- table(ELSA_w4_yinter$iintdatm, useNA = "ifany")
AfterH <- table(ELSA_ds_w4$mintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```





```{r importOPAL4, echo=F}
val_labels(ELSA_ds_w4) <- NULL
#opal.assign.data(o, 'ELSA_ds_w4', ELSA_ds_w4)
#opal.symbol_import(o,'ELSA_ds_w4', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w4 <- ELSA_ds_w4
ELSA_m_ds_w4$mintw <- car::recode(ELSA_m_ds_w4$mintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w4', ELSA_m_ds_w4)
#opal.symbol_import(o,'ELSA_m_ds_w4', project='_Athlos_Harm_Dataset')
```






### Wave 5

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `iintdatm`
* Label: `interview month - individual interview`
* Type of variable: `countinous`

```{r assign5, echo=F}
opal.assign.table.tibble(o, 'ELSA_w5_minter','ELSA.wave_5_ifs_derived_variables',
                         variables=list('iintdatm'), missings = TRUE)
```

```{r local5, echo=F}
ELSA_w5_minter <- opal.execute(o,'ELSA_w5_minter')
Categorical_summary(var = ELSA_w5_minter$iintdatm, missing_values = NA)
ggplot(ELSA_w5_minter, aes(x=factor(iintdatm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo5}
ELSA_ds_w5 <- tibble(id=ELSA_w5_minter$id)
ELSA_ds_w5$mintw <- car::recode(ELSA_w5_minter$iintdatm, "NA=999")
ELSA_ds_w5$mintw <- labelled(ELSA_ds_w5$mintw, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript5, echo=F}
Categorical_summary(var = ELSA_ds_w5$mintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w5, aes(x=factor(mintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation5, echo=F}
BeforeH <- table(ELSA_w5_minter$iintdatm, useNA = "ifany")
AfterH <- table(ELSA_ds_w5$mintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```





```{r importOPAL5, echo=F}
val_labels(ELSA_ds_w5) <- NULL
#opal.assign.data(o, 'ELSA_ds_w5', ELSA_ds_w5)
#opal.symbol_import(o,'ELSA_ds_w5', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w5 <- ELSA_ds_w5
ELSA_m_ds_w5$mintw <- car::recode(ELSA_m_ds_w5$mintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w5', ELSA_m_ds_w5)
#opal.symbol_import(o,'ELSA_m_ds_w5', project='_Athlos_Harm_Dataset')
```







### Wave 6

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `iintdatm`
* Label: `interview month - individual interview`
* Type of variable: `countinous`

```{r assign6, echo=F}
opal.assign.table.tibble(o, 'ELSA_w6_minter','ELSA.wave_6_ifs_derived_variables',
                         variables=list('iintdatm'), missings = TRUE)
```

```{r local6, echo=F}
ELSA_w6_minter <- opal.execute(o,'ELSA_w6_minter')
Categorical_summary(var = ELSA_w6_minter$iintdatm, missing_values = NA)
ggplot(ELSA_w6_minter, aes(x=factor(iintdatm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo6}
ELSA_ds_w6 <- tibble(id=ELSA_w6_minter$id)
ELSA_ds_w6$mintw <- car::recode(ELSA_w6_minter$iintdatm, "NA=999")
ELSA_ds_w6$mintw <- labelled(ELSA_ds_w6$mintw, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript6, echo=F}
Categorical_summary(var = ELSA_ds_w6$mintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w6, aes(x=factor(mintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation6, echo=F}
BeforeH <- table(ELSA_w6_minter$iintdatm, useNA = "ifany")
AfterH <- table(ELSA_ds_w6$mintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```





```{r importOPAL6, echo=F}
val_labels(ELSA_ds_w6) <- NULL
#opal.assign.data(o, 'ELSA_ds_w6', ELSA_ds_w6)
#opal.symbol_import(o,'ELSA_ds_w6', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w6 <- ELSA_ds_w6
ELSA_m_ds_w6$mintw <- car::recode(ELSA_m_ds_w6$mintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w6', ELSA_m_ds_w6)
#opal.symbol_import(o,'ELSA_m_ds_w6', project='_Athlos_Harm_Dataset')
```




### Wave 7

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `iintdatm`
* Label: `interview month - individual interview`
* Type of variable: `countinous`

```{r assign7, echo=F}
opal.assign.table.tibble(o, 'ELSA_w7','ELSA.wave7_dv',
                         variables=list('iintdatm'), missings = TRUE)
ELSA_w7 <- opal.execute(o,'ELSA_w7')
```

```{r local7, echo=F}
Categorical_summary(var = ELSA_w7$iintdatm, missing_values = NA)
ggplot(ELSA_w7, aes(x=factor(iintdatm))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo7}
ELSA_ds_w7 <- tibble(id=ELSA_w7$id)
ELSA_ds_w7$mintw <- car::recode(ELSA_w7$iintdatm, "NA=999")
ELSA_ds_w7$mintw <- labelled(ELSA_ds_w7$mintw, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript7, echo=F}
Categorical_summary(var = ELSA_ds_w7$mintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w7, aes(x=factor(mintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation7, echo=F}
BeforeH <- table(ELSA_w7$iintdatm, useNA = "ifany")
AfterH <- table(ELSA_ds_w7$mintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```





```{r importOPAL7, echo=F}
val_labels(ELSA_ds_w7) <- NULL
#opal.assign.data(o, 'ELSA_ds_w6', ELSA_ds_w6)
#opal.symbol_import(o,'ELSA_ds_w6', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w7 <- ELSA_ds_w7
ELSA_m_ds_w7$mintw <- car::recode(ELSA_m_ds_w7$mintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w6', ELSA_m_ds_w6)
#opal.symbol_import(o,'ELSA_m_ds_w6', project='_Athlos_Harm_Dataset')
```




# Quality estimation
No comments.


```{r save, echo=F}
s <- list(ELSA_ds_w1, ELSA_ds_w2, ELSA_ds_w3, ELSA_ds_w4, ELSA_ds_w5, ELSA_ds_w6, ELSA_ds_w7)
for(i in 1:7)
{
  mintw <- s[[i]]
  save(mintw, file = paste0(datafolder, "/",paste0("w",i),"/mintw.RData"))
}

```


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
