---
title: "Year of interview"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `yintw`
* Variable label: `year of interview`
* Domain: `Other administrative variables`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process


```{r, dataDirectory, echo=FALSE}
datafolder <- "../RData"
```


## England

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `iintdaty`
* Label: `Year of Individual Interview: Year of date: TODAYS DATE`
* Type of variable: `countinous`

```{r assign1, echo=F}
opal.assign.table.tibble(o,'ELSA_w1_yinter','ELSA.wave_1_ifs_derived_variables',
                         variables=list('iintdaty'), missings = TRUE)
```

```{r local1, echo=F}
ELSA_w1_yinter <- opal.execute(o,'ELSA_w1_yinter')
Categorical_summary(var = ELSA_w1_yinter$iintdaty, missing_values = NA)
ggplot(ELSA_w1_yinter, aes(x=factor(iintdaty))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo1}
ELSA_ds_w1 <- tibble(id=ELSA_w1_yinter$id)
ELSA_ds_w1$yintw <- as.numeric(ELSA_w1_yinter$iintdaty)
ELSA_ds_w1$yintw <- labelled(ELSA_ds_w1$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
Categorical_summary(var = ELSA_ds_w1$yintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w1, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
BeforeH <- table(ELSA_w1_yinter$iintdaty, useNA = "ifany")
AfterH <- table(ELSA_ds_w1$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```



```{r importOPAL1, echo=F}
val_labels(ELSA_ds_w1) <- NULL
#opal.assign.data(o, 'ELSA_ds_w1', ELSA_ds_w1)
#opal.symbol_import(o,'ELSA_ds_w1', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w1 <- ELSA_ds_w1
ELSA_m_ds_w1$yintw <- car::recode(ELSA_m_ds_w1$yintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w1', ELSA_m_ds_w1)
#opal.symbol_import(o,'ELSA_m_ds_w1', project='_Athlos_Harm_Dataset')
```






### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `iintdaty`
* Label: `Year of Individual Interview`
* Type of variable: `countinous`

```{r assign2, echo=F}
opal.assign.table.tibble(o, 'ELSA_w2_yinter','ELSA.wave_2_ifs_derived_variables',
                         variables=list('iintdaty'), missings = TRUE)
```

```{r local2, echo=F}
ELSA_w2_yinter <- opal.execute(o,'ELSA_w2_yinter')
Categorical_summary(var = ELSA_w2_yinter$iintdaty, missing_values = NA)
ggplot(ELSA_w2_yinter, aes(x=factor(iintdaty))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo2}
ELSA_ds_w2 <- tibble(id=ELSA_w2_yinter$id)
ELSA_ds_w2$yintw <- as.numeric(ELSA_w2_yinter$iintdaty)
ELSA_ds_w2$yintw <- labelled(ELSA_ds_w2$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
Categorical_summary(var = ELSA_ds_w2$yintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w2, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
BeforeH <- table(ELSA_w2_yinter$iintdaty, useNA = "ifany")
AfterH <- table(ELSA_ds_w2$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```



```{r importOPAL2, echo=F}
val_labels(ELSA_ds_w2) <- NULL
#opal.assign.data(o, 'ELSA_ds_w2', ELSA_ds_w2)
#opal.symbol_import(o,'ELSA_ds_w2', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w2 <- ELSA_ds_w2
ELSA_m_ds_w2$yintw <- car::recode(ELSA_m_ds_w2$yintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w2', ELSA_m_ds_w2)
#opal.symbol_import(o,'ELSA_m_ds_w2', project='_Athlos_Harm_Dataset')
```







### Wave 3

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `iintdaty`
* Label: `Year of Individual Interview: Year of date: TODAYS DATE`
* Type of variable: `countinous`


```{r assign3, echo=F}
opal.assign.table.tibble(o, 'ELSA_w3_yinter','ELSA.wave_3_ifs_derived_variables',
                         variables=list('iintdaty'), missings = TRUE)
```

```{r local3, echo=F}
ELSA_w3_yinter <- opal.execute(o,'ELSA_w3_yinter')
Categorical_summary(var = ELSA_w3_yinter$iintdaty, missing_values = NA)
ggplot(ELSA_w3_yinter, aes(x=factor(iintdaty))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo3}
ELSA_ds_w3 <- tibble(id=ELSA_w3_yinter$id)
ELSA_ds_w3$yintw <- as.numeric(ELSA_w3_yinter$iintdaty)
ELSA_ds_w3$yintw <- labelled(ELSA_ds_w3$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}
Categorical_summary(var = ELSA_ds_w3$yintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w3, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=F}
BeforeH <- table(ELSA_w3_yinter$iintdaty, useNA = "ifany")
AfterH <- table(ELSA_ds_w3$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```



```{r importOPAL3, echo=F}
val_labels(ELSA_ds_w3) <- NULL
#opal.assign.data(o, 'ELSA_ds_w3', ELSA_ds_w3)
#opal.symbol_import(o,'ELSA_ds_w3', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w3 <- ELSA_ds_w3
ELSA_m_ds_w3$yintw <- car::recode(ELSA_m_ds_w3$yintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w3', ELSA_m_ds_w3)
#opal.symbol_import(o,'ELSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```





### Wave 4

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `iintdaty`
* Label: `Year of Individual Interview: Year of date: TODAYS DATE`
* Type of variable: `countinous`


```{r assign4, echo=F}
opal.assign.table.tibble(o, 'ELSA_w4_yinter','ELSA.wave_4_ifs_derived_variables',
                         variables=list('iintdaty'), missings = TRUE)
ELSA_w4_yinter <- opal.execute(o,'ELSA_w4_yinter')
```

```{r local4, echo=F}
Categorical_summary(var = ELSA_w4_yinter$iintdaty, missing_values = NA)
ggplot(ELSA_w4_yinter, aes(x=factor(iintdaty))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo4}
ELSA_ds_w4 <- tibble(id=ELSA_w4_yinter$id)
ELSA_ds_w4$yintw <- as.numeric(ELSA_w4_yinter$iintdaty)
ELSA_ds_w4$yintw <- labelled(ELSA_ds_w4$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript4, echo=F}
Categorical_summary(var = ELSA_ds_w4$yintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w4, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=F}
BeforeH <- table(ELSA_w4_yinter$iintdaty, useNA = "ifany")
AfterH <- table(ELSA_ds_w4$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```



```{r importOPAL4, echo=F}
val_labels(ELSA_ds_w4) <- NULL
#opal.assign.data(o, 'ELSA_ds_w4', ELSA_ds_w4)
#opal.symbol_import(o,'ELSA_ds_w4', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w4 <- ELSA_ds_w4
ELSA_m_ds_w4$yintw <- car::recode(ELSA_m_ds_w4$yintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w4', ELSA_m_ds_w4)
#opal.symbol_import(o,'ELSA_m_ds_w4', project='_Athlos_Harm_Dataset')
```







### Wave 5

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `iintdaty`
* Label: `Year of Individual Interview: Year of date: TODAYS DATE`
* Type of variable: `countinous`

```{r assign5, echo=F}
opal.assign.table.tibble(o, 'ELSA_w5_yinter','ELSA.wave_5_ifs_derived_variables',
                         variables=list('iintdaty'), missings = TRUE)
ELSA_w5_yinter <- opal.execute(o,'ELSA_w5_yinter')
```

```{r local5, echo=F}
Categorical_summary(var = ELSA_w5_yinter$iintdaty, missing_values = NA)
ggplot(ELSA_w5_yinter, aes(x=factor(iintdaty))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo5}
ELSA_ds_w5 <- tibble(id=ELSA_w5_yinter$id)
ELSA_ds_w5$yintw <- as.numeric(ELSA_w5_yinter$iintdaty)
ELSA_ds_w5$yintw <- labelled(ELSA_ds_w5$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript5, echo=F}
Categorical_summary(var = ELSA_ds_w5$yintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w5, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation5, echo=F}
BeforeH <- table(ELSA_w5_yinter$iintdaty, useNA = "ifany")
AfterH <- table(ELSA_ds_w5$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```



```{r importOPAL5, echo=F}
val_labels(ELSA_ds_w5) <- NULL
#opal.assign.data(o, 'ELSA_ds_w5', ELSA_ds_w5)
#opal.symbol_import(o,'ELSA_ds_w5', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w5 <- ELSA_ds_w5
ELSA_m_ds_w5$yintw <- car::recode(ELSA_m_ds_w5$yintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w5', ELSA_m_ds_w5)
#opal.symbol_import(o,'ELSA_m_ds_w5', project='_Athlos_Harm_Dataset')
```







### Wave 6

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `iintdaty`
* Label: `Year of Individual Interview: Year of date: TODAYS DATE`
* Type of variable: `countinous`

```{r assign6, echo=F}
opal.assign.table.tibble(o, 'ELSA_w6_yinter','ELSA.wave_6_ifs_derived_variables',
                         variables=list('iintdaty'), missings = TRUE)
```

```{r local6, echo=F}
ELSA_w6_yinter <- opal.execute(o,'ELSA_w6_yinter')
Categorical_summary(var = ELSA_w6_yinter$iintdaty, missing_values = NA)
ggplot(ELSA_w6_yinter, aes(x=factor(iintdaty))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo6}
ELSA_ds_w6 <- tibble(id=ELSA_w6_yinter$id)
ELSA_ds_w6$yintw <- as.numeric(ELSA_w6_yinter$iintdaty)
ELSA_ds_w6$yintw <- labelled(ELSA_ds_w6$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript6, echo=F}
Categorical_summary(var = ELSA_ds_w6$yintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w6, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation6, echo=F}
BeforeH <- table(ELSA_w6_yinter$iintdaty, useNA = "ifany")
AfterH <- table(ELSA_ds_w6$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```



```{r importOPAL6, echo=F}
val_labels(ELSA_ds_w6) <- NULL
#opal.assign.data(o, 'ELSA_ds_w6', ELSA_ds_w6)
#opal.symbol_import(o,'ELSA_ds_w6', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w6 <- ELSA_ds_w6
ELSA_m_ds_w6$yintw <- car::recode(ELSA_m_ds_w6$yintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w6', ELSA_m_ds_w6)
#opal.symbol_import(o,'ELSA_m_ds_w6', project='_Athlos_Harm_Dataset')
```




### Wave 7

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `iintdaty`
* Label: `Year of Individual Interview`
* Type of variable: `countinous`

```{r assign7, echo=F}
opal.assign.table.tibble(o, 'ELSA_w7','ELSA.wave7_dv',
                         variables=list('iintdaty'), missings = TRUE)
ELSA_w7 <- opal.execute(o,'ELSA_w7')
```

```{r local7, echo=F}
Categorical_summary(var = ELSA_w7$iintdaty, missing_values = NA)
ggplot(ELSA_w7, aes(x=factor(iintdaty))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo7}
ELSA_ds_w7 <- tibble(id=ELSA_w7$id)
ELSA_ds_w7$yintw <- as.numeric(ELSA_w7$iintdaty)
ELSA_ds_w7$yintw <- labelled(ELSA_ds_w7$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript7, echo=F}
Categorical_summary(var = ELSA_ds_w7$yintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w7, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation7, echo=F}
BeforeH <- table(ELSA_w7$iintdaty, useNA = "ifany")
AfterH <- table(ELSA_ds_w7$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```



```{r importOPAL7, echo=F}
val_labels(ELSA_ds_w7) <- NULL
#opal.assign.data(o, 'ELSA_ds_w7', ELSA_ds_w7)
#opal.symbol_import(o,'ELSA_ds_w7', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w7 <- ELSA_ds_w7
ELSA_m_ds_w7$yintw <- car::recode(ELSA_m_ds_w7$yintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w7', ELSA_m_ds_w7)
#opal.symbol_import(o,'ELSA_m_ds_w7', project='_Athlos_Harm_Dataset')
```




```{r save, echo=F}
s <- list(ELSA_ds_w1, ELSA_ds_w2, ELSA_ds_w3, ELSA_ds_w4, ELSA_ds_w5, ELSA_ds_w6, ELSA_ds_w7)
for(i in 1:7)
{
  yintw <- s[[i]]
  save(yintw, file = paste0(datafolder, "/",paste0("w",i),"/yintw.RData"))
}

```


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
#### Quality estimation
The date was the same as the study specific variable taking into account the wave time lapse information.


