---
title: "Year of interview"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/yintwDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/yintwDS.R')
```

# Data process



## England

### Wave 1 

#### Study-specific variable description



| **Name** | `iintdaty`|
|-|-|
| **Label** | `Year of Individual Interview: Year of date: TODAYS DATE`|
| **Table name** |`wave_1_ifs_derived_variables`|
| **Type of variable** |`date`|
| **Description** |  |

```{r assign1, echo=F}
opal.assign.table.tibble(o,'ELSA_w1','ELSA.wave_1_ifs_derived_variables',
                         variables=list('iintdaty'), missings = TRUE)
```

```{r local1, echo=F}
ELSA_w1 <- opal.execute(o,'ELSA_w1')
vbl <- ELSA_w1$iintdaty
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "iintdaty")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ELSA_w1, aes(x=factor(iintdaty))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo1}
ELSA_ds_w1 <- tibble(id=ELSA_w1$id)
ELSA_ds_w1$yintw <- as.numeric(ELSA_w1$iintdaty)
ELSA_ds_w1$yintw <- labelled(ELSA_ds_w1$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vbl <- ELSA_ds_w1$yintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w1, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
BeforeH <- table(ELSA_w1$iintdaty, useNA = "ifany")
AfterH <- table(ELSA_ds_w1$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```










### Wave 2

#### Study-specific variable description



| **Name** | `iintdaty`|
|-|-|
| **Label** | `Year of Individual Interview`|
| **Table name** |`wave_2_ifs_derived_variables`|
| **Type of variable** |`date`|
| **Description** |  |

```{r assign2, echo=F}
opal.assign.table.tibble(o, 'ELSA_w2','ELSA.wave_2_ifs_derived_variables',
                         variables=list('iintdaty'), missings = TRUE)
```

```{r local2, echo=F}
ELSA_w2 <- opal.execute(o,'ELSA_w2')
vbl <- ELSA_w2$iintdaty
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "iintdaty")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ELSA_w2, aes(x=factor(iintdaty))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo2}
ELSA_ds_w2 <- tibble(id=ELSA_w2$id)
ELSA_ds_w2$yintw <- as.numeric(ELSA_w2$iintdaty)
ELSA_ds_w2$yintw <- labelled(ELSA_ds_w2$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vbl <- ELSA_ds_w2$yintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w2, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
BeforeH <- table(ELSA_w2$iintdaty, useNA = "ifany")
AfterH <- table(ELSA_ds_w2$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```









### Wave 3

#### Study-specific variable description



| **Name** | `iintdaty`|
|-|-|
| **Label** | `Year of Individual Interview: Year of date: TODAYS DATE`|
| **Table name** |`wave_3_ifs_derived_variables`|
| **Type of variable** |`date`|
| **Description** |  |


```{r assign3, echo=F}
opal.assign.table.tibble(o, 'ELSA_w3','ELSA.wave_3_ifs_derived_variables',
                         variables=list('iintdaty'), missings = TRUE)
```

```{r local3, echo=F}
ELSA_w3 <- opal.execute(o,'ELSA_w3')
vbl <- ELSA_w3$iintdaty
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "iintdaty")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ELSA_w3, aes(x=factor(iintdaty))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo3}
ELSA_ds_w3 <- tibble(id=ELSA_w3$id)
ELSA_ds_w3$yintw <- as.numeric(ELSA_w3$iintdaty)
ELSA_ds_w3$yintw <- labelled(ELSA_ds_w3$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}
vbl <- ELSA_ds_w3$yintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w3, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=F}
BeforeH <- table(ELSA_w3$iintdaty, useNA = "ifany")
AfterH <- table(ELSA_ds_w3$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```








### Wave 4

#### Study-specific variable description



| **Name** | `iintdaty`|
|-|-|
| **Label** | `Year of Individual Interview: Year of date: TODAYS DATE`|
| **Table name** |`wave_4_ifs_derived_variables`|
| **Type of variable** |`date`|
| **Description** |  |


```{r assign4, echo=F}
opal.assign.table.tibble(o, 'ELSA_w4','ELSA.wave_4_ifs_derived_variables',
                         variables=list('iintdaty'), missings = TRUE)
ELSA_w4 <- opal.execute(o,'ELSA_w4')
```

```{r local4, echo=F}
vbl <- ELSA_w4$iintdaty
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "iintdaty")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ELSA_w4, aes(x=factor(iintdaty))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo4}
ELSA_ds_w4 <- tibble(id=ELSA_w4$id)
ELSA_ds_w4$yintw <- as.numeric(ELSA_w4$iintdaty)
ELSA_ds_w4$yintw <- labelled(ELSA_ds_w4$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript4, echo=F}
vbl <- ELSA_ds_w4$yintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w4, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=F}
BeforeH <- table(ELSA_w4$iintdaty, useNA = "ifany")
AfterH <- table(ELSA_ds_w4$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```











### Wave 5

#### Study-specific variable description



| **Name** | `iintdaty`|
|-|-|
| **Label** | `Year of Individual Interview: Year of date: TODAYS DATE`|
| **Table name** |`wave_5_ifs_derived_variables`|
| **Type of variable** |`date`|
| **Description** |  |

```{r assign5, echo=F}
opal.assign.table.tibble(o, 'ELSA_w5','ELSA.wave_5_ifs_derived_variables',
                         variables=list('iintdaty'), missings = TRUE)
ELSA_w5 <- opal.execute(o,'ELSA_w5')
```

```{r local5, echo=F}
vbl <- ELSA_w5$iintdaty
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "iintdaty")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ELSA_w5, aes(x=factor(iintdaty))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo5}
ELSA_ds_w5 <- tibble(id=ELSA_w5$id)
ELSA_ds_w5$yintw <- as.numeric(ELSA_w5$iintdaty)
ELSA_ds_w5$yintw <- labelled(ELSA_ds_w5$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript5, echo=F}
vbl <- ELSA_ds_w5$yintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w5, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation5, echo=F}
BeforeH <- table(ELSA_w5$iintdaty, useNA = "ifany")
AfterH <- table(ELSA_ds_w5$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```









### Wave 6

#### Study-specific variable description



| **Name** | `iintdaty`|
|-|-|
| **Label** | `Year of Individual Interview: Year of date: TODAYS DATE`|
| **Table name** |`wave_6_ifs_derived_variables`|
| **Type of variable** |`date`|
| **Description** |  |

```{r assign6, echo=F}
opal.assign.table.tibble(o, 'ELSA_w6','ELSA.wave_6_ifs_derived_variables',
                         variables=list('iintdaty'), missings = TRUE)
```

```{r local6, echo=F}
ELSA_w6 <- opal.execute(o,'ELSA_w6')
vbl <- ELSA_w6$iintdaty
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "iintdaty")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ELSA_w6, aes(x=factor(iintdaty))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo6}
ELSA_ds_w6 <- tibble(id=ELSA_w6$id)
ELSA_ds_w6$yintw <- as.numeric(ELSA_w6$iintdaty)
ELSA_ds_w6$yintw <- labelled(ELSA_ds_w6$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript6, echo=F}
vbl <- ELSA_ds_w6$yintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w6, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation6, echo=F}
BeforeH <- table(ELSA_w6$iintdaty, useNA = "ifany")
AfterH <- table(ELSA_ds_w6$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```







### Wave 7

#### Study-specific variable description



| **Name** | `iintdaty`|
|-|-|
| **Label** | `Year of Individual Interview`|
| **Table name** |`wave7_dv`|
| **Type of variable** |`date`|
| **Description** |  |

```{r assign7, echo=F}
opal.assign.table.tibble(o, 'ELSA_w7','ELSA.wave7_dv',
                         variables=list('iintdaty'), missings = TRUE)
ELSA_w7 <- opal.execute(o,'ELSA_w7')
```

```{r local7, echo=F}
vbl <- ELSA_w7$iintdaty
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "iintdaty")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ELSA_w7, aes(x=factor(iintdaty))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo7}
ELSA_ds_w7 <- tibble(id=ELSA_w7$id)
ELSA_ds_w7$yintw <- as.numeric(ELSA_w7$iintdaty)
ELSA_ds_w7$yintw <- labelled(ELSA_ds_w7$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript7, echo=F}
vbl <- ELSA_ds_w7$yintw
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ELSA_ds_w7, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation7, echo=F}
BeforeH <- table(ELSA_w7$iintdaty, useNA = "ifany")
AfterH <- table(ELSA_ds_w7$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```









## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for continuous data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][2])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[2]],missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][2])[1:6]
    # Next, missing/no-missing values
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[2]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


elsa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"), w6 = c("w6","W6"), w7 = c("w7","W7"))

# Consider only harmonised waves
l.hds <- lapply(elsa.cw, function(wname) if(exists(paste0("ELSA_ds_",wname[1]))){wname = list(get(paste0("ELSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```





```{r closeRsession, echo=FALSE}
opal.logout(o)
```
# Quality estimation
The date was the same as the study specific variable taking into account the wave time lapse information.


