---
title: "Sample weights for generalization to population"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `w`
* Variable label: `Sample weights for generalization to population`
* Domain: `Other administrative variables`
* Value type: `Countinous`
* Category missings: No missings.


<!-- ########################################################## --> 

# Data process


```{r, dataDirectory, echo=FALSE}
datafolder <- "../RData"
```

## England


### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w1wgt`
* Label: `Cross-sectional weight`

```{r assign1, echo=F}
opal.assign.table.tibble(o, 'elsa_w1_w','ELSA.wave_1_core_data_v3', variables=list('w1wgt'), missings = TRUE)
```

```{r local1, echo=F}
elsa_w1_w <- opal.execute(o,'elsa_w1_w')
Continuous_summary(var = elsa_w1_w$w1wgt, missing_values = NA)
```

#### Harmonisation algorithm

**R script:**

```{r harmo1}
ELSA_ds_w1   <- tibble(id=elsa_w1_w$id)
ELSA_ds_w1$w <- elsa_w1_w$w1wgt
ELSA_ds_w1$w <- labelled(ELSA_ds_w1$w, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
names(ELSA_ds_w1) <- c("id","w")
label(ELSA_ds_w1$w) <- "Weights for sample representativeness"
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
Continuous_summary(var = ELSA_ds_w1$w, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
```

#### Validation
```{r crosstabulation1, echo=F}
```





```{r importOPAL1, echo=F}
val_labels(ELSA_ds_w1) <- NULL
#opal.assign.data(o, 'ELSA_ds_w1', ELSA_ds_w1)
#opal.symbol_import(o,'ELSA_ds_w1', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w1 <- ELSA_ds_w1
ELSA_m_ds_w1$w <- car::recode(ELSA_m_ds_w1$w, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w1', ELSA_m_ds_w1)
#opal.symbol_import(o,'ELSA_m_ds_w1', project='_Athlos_Harm_Dataset')
```


### Wave 2 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w2wgt`
* Label: `Cross-sectional weight`

```{r assign2, echo=F}
opal.assign.table.tibble(o, 'elsa_w2_w','ELSA.wave_2_core_data_v4', variables=list('w2wgt'), missings = TRUE)
```

```{r local2, echo=F}
elsa_w2_w <- opal.execute(o,'elsa_w2_w')
Continuous_summary(var = elsa_w2_w$w2wgt, missing_values = NA)
```

#### Harmonisation algorithm

**R script:**

```{r harmo2}
ELSA_ds_w2   <- tibble(id=elsa_w2_w$id)
ELSA_ds_w2$w <- elsa_w2_w$w2wgt
ELSA_ds_w2$w <- labelled(ELSA_ds_w2$w, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
names(ELSA_ds_w2) <- c("id","w")
label(ELSA_ds_w2$w) <- "Weights for sample representativeness"
```

#### Statistics of the new harmonised variable

```{r descript2, echo=F}
Continuous_summary(var = ELSA_ds_w2$w, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
```

#### Validation

```{r crosstabulation2, echo=F}
```





```{r importOPAL2, echo=F}
val_labels(ELSA_ds_w2) <- NULL
#opal.assign.data(o, 'ELSA_ds_w2', ELSA_ds_w2)
#opal.symbol_import(o,'ELSA_ds_w2', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w2 <- ELSA_ds_w2
ELSA_m_ds_w2$w <- car::recode(ELSA_m_ds_w2$w, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w2', ELSA_m_ds_w2)
#opal.symbol_import(o,'ELSA_m_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 3 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w3xwgt`
* Label: `Cross-sectional weight`

```{r assign3, echo=F}
opal.assign.table.tibble(o, 'elsa_w3_w','ELSA.wave_3_elsa_data_v4', variables=list('w3xwgt'), missings = TRUE)
```

```{r local3, echo=F}
elsa_w3_w <- opal.execute(o,'elsa_w3_w')
Continuous_summary(var = elsa_w3_w$w3xwgt, missing_values = NA)
```

#### Harmonisation algorithm

**R script:**

```{r harmo3}
ELSA_ds_w3   <- tibble(id=elsa_w3_w$id)
ELSA_ds_w3$w <- elsa_w3_w$w3xwgt
ELSA_ds_w3$w <- labelled(ELSA_ds_w3$w, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
names(ELSA_ds_w3) <- c("id","w")
label(ELSA_ds_w3$w) <- "Weights for sample representativeness"
```

#### Statistics of the new harmonised variable

```{r descript3, echo=F}
Continuous_summary(var = ELSA_ds_w3$w, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
```

#### Validation

```{r crosstabulation3, echo=F}
```





```{r importOPAL3, echo=F}
val_labels(ELSA_ds_w3) <- NULL
#opal.assign.data(o, 'ELSA_ds_w3', ELSA_ds_w3)
#opal.symbol_import(o,'ELSA_ds_w3', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w3 <- ELSA_ds_w3
ELSA_m_ds_w3$w <- car::recode(ELSA_m_ds_w3$w, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w3', ELSA_m_ds_w3)
#opal.symbol_import(o,'ELSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```


### Wave 4 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w4xwgt`
* Label: `Cross-sectional weight`

```{r assign4, echo=F}
opal.assign.table.tibble(o, 'elsa_w4_w','ELSA.wave_4_elsa_data_v3_modif_Laia', variables=list('w4xwgt'), missings = TRUE)
```

```{r local4, echo=F}
elsa_w4_w <- opal.execute(o,'elsa_w4_w')
Continuous_summary(var = elsa_w4_w$w4xwgt, missing_values = NA)
```

#### Harmonisation algorithm

**R script:**

```{r harmo4}
ELSA_ds_w4   <- tibble(id=elsa_w4_w$id)
ELSA_ds_w4$w <- elsa_w4_w$w4xwgt
ELSA_ds_w4$w <- labelled(ELSA_ds_w4$w, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
names(ELSA_ds_w4) <- c("id","w")
label(ELSA_ds_w4$w) <- "Weights for sample representativeness"
```

#### Statistics of the new harmonised variable

```{r descript4, echo=F}
Continuous_summary(var = ELSA_ds_w4$w, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
```

#### Validation

```{r crosstabulation4, echo=F}
```





```{r importOPAL4, echo=F}
val_labels(ELSA_ds_w4) <- NULL
#opal.assign.data(o, 'ELSA_ds_w4', ELSA_ds_w4)
#opal.symbol_import(o,'ELSA_ds_w4', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w4 <- ELSA_ds_w4
ELSA_m_ds_w4$w <- car::recode(ELSA_m_ds_w4$w, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w4', ELSA_m_ds_w4)
#opal.symbol_import(o,'ELSA_m_ds_w4', project='_Athlos_Harm_Dataset')
```


### Wave 5 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w5xwgt`
* Label: `Cross-sectional weight`

```{r assign5, echo=F}
opal.assign.table.tibble(o, 'elsa_w5_w','ELSA.wave_5_elsa_data_v4_modif_Laia', variables=list('w5xwgt'), missings = TRUE)
```

```{r local5, echo=F}
elsa_w5_w <- opal.execute(o,'elsa_w5_w')
Continuous_summary(var = elsa_w5_w$w5xwgt, missing_values = NA)
```

#### Harmonisation algorithm

**R script:**

```{r harmo5}
ELSA_ds_w5   <- tibble(id=elsa_w5_w$id)
ELSA_ds_w5$w <- elsa_w5_w$w5xwgt
ELSA_ds_w5$w <- labelled(ELSA_ds_w5$w, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
names(ELSA_ds_w5) <- c("id","w")
label(ELSA_ds_w5$w) <- "Weights for sample representativeness"
```

#### Statistics of the new harmonised variable

```{r descript5, echo=F}
Continuous_summary(var = ELSA_ds_w5$w, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
```

#### Validation

```{r crosstabulation5, echo=F}
```





```{r importOPAL5, echo=F}
val_labels(ELSA_ds_w5) <- NULL
#opal.assign.data(o, 'ELSA_ds_w5', ELSA_ds_w5)
#opal.symbol_import(o,'ELSA_ds_w5', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w5 <- ELSA_ds_w5
ELSA_m_ds_w5$w <- car::recode(ELSA_m_ds_w5$w, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w5', ELSA_m_ds_w5)
#opal.symbol_import(o,'ELSA_m_ds_w5', project='_Athlos_Harm_Dataset')
```


### Wave 6 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w6xwgt`
* Label: `Cross-sectional weight`

```{r assign6, echo=F}
opal.assign.table.tibble(o, 'elsa_w6_w','ELSA.wave_6_elsa_data_v2_modif_Laia', variables=list('w6xwgt'), missings = TRUE)
```

```{r local6, echo=F}
elsa_w6_w <- opal.execute(o,'elsa_w6_w')
Continuous_summary(var = elsa_w6_w$w6xwgt, missing_values = NA)
```

#### Harmonisation algorithm

**R script:**

```{r harmo6}
ELSA_ds_w6   <- tibble(id=elsa_w6_w$id)
ELSA_ds_w6$w <- elsa_w6_w$w6xwgt
ELSA_ds_w6$w <- car::recode(ELSA_ds_w6$w, "NA=0")
ELSA_ds_w6$w <- labelled(ELSA_ds_w6$w, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
names(ELSA_ds_w6) <- c("id","w")
label(ELSA_ds_w6$w) <- "Weights for sample representativeness"
```

#### Statistics of the new harmonised variable

```{r descript6, echo=F}
Continuous_summary(var = ELSA_ds_w6$w, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
```

#### Validation

```{r crosstabulation6, echo=F}
```





```{r importOPAL6, echo=F}
val_labels(ELSA_ds_w6) <- NULL
#opal.assign.data(o, 'ELSA_ds_w6', ELSA_ds_w6)
#opal.symbol_import(o,'ELSA_ds_w6', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w6 <- ELSA_ds_w6
ELSA_m_ds_w6$w <- car::recode(ELSA_m_ds_w6$w, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w6', ELSA_m_ds_w6)
#opal.symbol_import(o,'ELSA_m_ds_w6', project='_Athlos_Harm_Dataset')
```





### Wave 7 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `wgt`
* Label: `cross-sectional weight (copy of wXwght)`

```{r assign7, echo=F}
opal.assign.table.tibble(o, 'ELSA_w7','ELSA.wave7_dv', variables=list('wgt'), missings = TRUE)
ELSA_w7 <- opal.execute(o,'ELSA_w7')

```

```{r local7, echo=F}
Continuous_summary(var = ELSA_w7$wgt, missing_values = NA)
```

#### Harmonisation algorithm

**R script:**

```{r harmo7}
ELSA_ds_w7   <- tibble(id=ELSA_w7$id)
ELSA_ds_w7$w <- ELSA_w7$wgt
ELSA_ds_w7$w <- labelled(ELSA_ds_w7$w, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
names(ELSA_ds_w7) <- c("id","w")
label(ELSA_ds_w7$w) <- "Weights for sample representativeness"
```

#### Statistics of the new harmonised variable

```{r descript7, echo=F}
Continuous_summary(var = ELSA_ds_w7$w, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
```

#### Validation

```{r crosstabulation7, echo=F}
```





```{r importOPAL7, echo=F}
val_labels(ELSA_ds_w7) <- NULL
#opal.assign.data(o, 'ELSA_ds_w7', ELSA_ds_w7)
#opal.symbol_import(o,'ELSA_ds_w7', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w7 <- ELSA_ds_w7
ELSA_m_ds_w7$w <- car::recode(ELSA_m_ds_w7$w, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w7', ELSA_m_ds_w7)
#opal.symbol_import(o,'ELSA_m_ds_w7', project='_Athlos_Harm_Dataset')
```






# Quality estimation

```{r save, echo=F}
s <- list(ELSA_ds_w1, ELSA_ds_w2, ELSA_ds_w3, ELSA_ds_w4, ELSA_ds_w5, ELSA_ds_w6, ELSA_ds_w7)
for(i in 1:7)
{
  w <- s[[i]]
  save(w, file = paste0(datafolder, "/",paste0("w",i),"/w.RData"))
}

```


```{r closeRsession, echo=FALSE}
opal.logout(o)
```

