---
title: "Proxy"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/proxyDS.Rmd'}
```

```{r global, echo=F}
source('../../_DS_Rmd/proxyDS.R')
```

# Data process

## England

### Wave 1

#### Study-specific variable description

| **Name** | `proxy` |
|-|-|
| **Label** | `proxy proxy` |
| **Table name** | `wave_1_ifs_derived_variables` |
| **Categories** | `0 = No` |
| | `1 = Yes` | 
| **Description** |  |


```{r assign w1, echo=F}
opal.assign.table.tibble(o,'elsa_proxy1','ELSA.wave_1_core_data_v3',variables=list('askpx1'), missings = TRUE)
elsa_proxy1 <- opal.execute(o,'elsa_proxy1')

opal.assign.table.tibble(o,'elsa_proxy2','ELSA.wave_1_ifs_derived_variables',variables=list('proxy'), missings = TRUE)
elsa_proxy2 <- opal.execute(o,'elsa_proxy2')

elsa_proxy <- full_join(elsa_proxy1, elsa_proxy2, by='id')


opal.assign.table.tibble(o,'elsa_proxy','ELSA.wave_1_ifs_derived_variables',variables=list('proxy'), missings = TRUE)
elsa_proxy <- opal.execute(o,'elsa_proxy')
```

```{r local1,  echo=FALSE}
vari <- elsa_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(elsa_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable but the missing values has to be recoded as forllows

* `Na into 999`

**R script:**

```{r harmo w1}
ELSA_ds_w1 <- tibble(id=elsa_proxy$id)
ELSA_ds_w1$proxy <- car::recode(elsa_proxy[[2]], "NA=999")
ELSA_ds_w1$proxy <- labelled(ELSA_ds_w1$proxy, labels = cat_label)
label(ELSA_ds_w1$proxy) <- ds_label_all
```

#### Statistical description of the new harmonised variable
```{r descript1,  echo=FALSE}
vari <- ELSA_ds_w1$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w1, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL1,  echo=FALSE}
label(ELSA_ds_w1$proxy) <- ds_label
proxy <- ELSA_ds_w1
save(proxy, file = "../RData/w1/proxy.RData")
rm(proxy)
```
 


### Wave 2

#### Study-specific variable description

| **Name** | `proxy` |
|-|-|
| **Label** | `proxy respondent` |
| **Table name** | `wave_2_ifs_derived_variables` |
| **Categories** | `0 = No` |
| | `1 = Yes` | 
| **Description** |  |

```{r assign w2, echo=F}
opal.assign.table.tibble(o,'elsa_proxy','ELSA.wave_2_ifs_derived_variables',variables=list('proxy'), missings = TRUE)
elsa_proxy <- opal.execute(o,'elsa_proxy')
```

```{r local2,  echo=FALSE}
vari <- elsa_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(elsa_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```



#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable but the missing values has to be recoded as forllows

* `NA into 999`

**R script:**

```{r harmo w2}
ELSA_ds_w2 <- tibble(id=elsa_proxy$id)
ELSA_ds_w2$proxy <- car::recode(elsa_proxy[[2]], "NA=999")
ELSA_ds_w2$proxy <- labelled(ELSA_ds_w2$proxy, labels = cat_label)
label(ELSA_ds_w2$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript2,  echo=FALSE}
vari <- ELSA_ds_w2$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w2, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL2,  echo=FALSE}
label(ELSA_ds_w2$proxy) <- ds_label
proxy <- ELSA_ds_w2
save(proxy, file = "../RData/w2/proxy.RData")
rm(proxy)
```


### Wave 3

#### Study-specific variable description

| **Name** | `proxy` |
|-|-|
| **Label** | `proxy respondent` |
| **Table name** | `wave_3_ifs_derived_variables` |
| **Categories** | `0 = No` |
| | `1 = Yes` | 
| **Description** |  |


```{r assign w3, echo=F}
opal.assign.table.tibble(o,'elsa_proxy','ELSA.wave_3_ifs_derived_variables',variables=list('proxy'), missings = TRUE)
elsa_proxy <- opal.execute(o,'elsa_proxy')
```

```{r local3,  echo=FALSE}
vari <- elsa_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(elsa_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```



#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable but the missing values has to be recoded as forllows

* `Na into 999`

**R script:**

```{r harmo w3}
ELSA_ds_w3 <- tibble(id=elsa_proxy$id)
ELSA_ds_w3$proxy <- car::recode(elsa_proxy[[2]], "NA=999")
ELSA_ds_w3$proxy <- labelled(ELSA_ds_w3$proxy, labels = cat_label)
label(ELSA_ds_w3$proxy) <- ds_label_all
```


#### Statistical description of the new harmonised variable
```{r descript3,  echo=FALSE}
vari <- ELSA_ds_w3$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w3, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL3,  echo=FALSE}
label(ELSA_ds_w3$proxy) <- ds_label
proxy <- ELSA_ds_w3
save(proxy, file = "../RData/w3/proxy.RData")
rm(proxy)
```



### Wave 4

#### Study-specific variable description

| **Name** | `proxy` |
|-|-|
| **Label** | `proxy respondent` |
| **Table name** | `wave_4_ifs_derived_variables` |
| **Categories** | `0 = No` |
| | `1 = Yes` | 
| **Description** |  |



```{r assign w4, echo=F}
opal.assign.table.tibble(o,'elsa_proxy','ELSA.wave_4_ifs_derived_variables',variables=list('proxy'), missings = TRUE)
elsa_proxy <- opal.execute(o,'elsa_proxy')
```

```{r local4,  echo=FALSE}
vari <- elsa_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(elsa_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable but the missing values has to be recoded as forllows

* `Na into 999`

**R script:**

```{r harmo w4}
ELSA_ds_w4 <- tibble(id=elsa_proxy$id)
ELSA_ds_w4$proxy <- car::recode(elsa_proxy[[2]], "NA=999")
ELSA_ds_w4$proxy <- labelled(ELSA_ds_w4$proxy, labels = cat_label)
label(ELSA_ds_w4$proxy) <- ds_label_all
```

#### Statistical description of the new harmonised variable
```{r descript4,  echo=FALSE}
vari <- ELSA_ds_w4$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w4, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL4,  echo=FALSE}
label(ELSA_ds_w4$proxy) <- ds_label
proxy <- ELSA_ds_w4
save(proxy, file = "../RData/w4/proxy.RData")
rm(proxy)
```




### Wave 5

#### Study-specific variable description

| **Name** | `proxy` |
|-|-|
| **Label** | `proxy respondent` |
| **Table name** | `wave_5_elsa_data_v4` |
| **Categories** | `0 = No` |
| | `1 = Yes` | 
| **Description** |  |



```{r assign w5, echo=F}
opal.assign.table.tibble(o,'elsa_proxy','ELSA.wave_5_elsa_data_v4',variables=list('proxy'), missings = TRUE)
elsa_proxy <- opal.execute(o,'elsa_proxy')
```

```{r local5,  echo=FALSE}
vari <- elsa_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(elsa_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable but the missing values has to be recoded as forllows

* `NA into 999`

**R script:**

```{r harmo w5}
ELSA_ds_w5 <- tibble(id=elsa_proxy$id)
ELSA_ds_w5$proxy <- car::recode(elsa_proxy[[2]], "NA=999")
ELSA_ds_w5$proxy <- labelled(ELSA_ds_w5$proxy, labels = cat_label)
label(ELSA_ds_w5$proxy) <- ds_label_all
```

#### Statistical description of the new harmonised variable
```{r descript5,  echo=FALSE}
vari <- ELSA_ds_w5$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w5, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL5,  echo=FALSE}
label(ELSA_ds_w5$proxy) <- ds_label
proxy <- ELSA_ds_w5
save(proxy, file = "../RData/w5/proxy.RData")
rm(proxy)
```



### Wave 6

#### Study-specific variable description

| **Name** | `proxy` |
|-|-|
| **Label** | `proxy respondent` |
| **Table name** | `wave_6_ifs_derived_variables` |
| **Categories** | `0 = No` |
| | `1 = Yes` | 
| **Description** |  |


```{r assign w6, echo=F}
opal.assign.table.tibble(o,'elsa_proxy','ELSA.wave_6_ifs_derived_variables',variables=list('proxy'), missings = TRUE)
elsa_proxy <- opal.execute(o,'elsa_proxy')
```

```{r local6,  echo=FALSE}
vari <- elsa_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(elsa_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```



#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable but the missing values has to be recoded as forllows

* `NA into 999`


**R script:**

```{r harmo w6}
ELSA_ds_w6 <- tibble(id=elsa_proxy$id)
ELSA_ds_w6$proxy <- car::recode(elsa_proxy[[2]], "NA=999")
ELSA_ds_w6$proxy <- labelled(ELSA_ds_w6$proxy, labels = cat_label)
label(ELSA_ds_w6$proxy) <- ds_label_all
```

#### Statistical description of the new harmonised variable
```{r descript6,  echo=FALSE}
vari <- ELSA_ds_w6$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w6, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL6,  echo=FALSE}
label(ELSA_ds_w6$proxy) <- ds_label
proxy <- ELSA_ds_w6
save(proxy, file = "../RData/w6/proxy.RData")
rm(proxy)
```



### Wave 7

| **Name** | `askpx` |
|-|-|
| **Label** | `Whether respondent had an interview by proxy` |
| **Table name** | `wave_7_elsa_data` |
| **Categories** | `0 = Respondent did not have interview by proxy` |
| | `1 = Respondent did have interview by proxy` | 
| **Description** |  |


```{r assign w7, echo=F}
opal.assign.table.tibble(o,'elsa_proxy','ELSA.wave_7_elsa_data',variables=list('askpx'), missings = TRUE)
elsa_proxy <- opal.execute(o,'elsa_proxy')
```

```{r local7,  echo=FALSE}
vari <- elsa_proxy[[2]]
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(elsa_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable but the missing values has to be recoded as forllows

* `NA into 999`


**R script:**

```{r harmo w7}
ELSA_ds_w7 <- tibble(id=elsa_proxy$id)
ELSA_ds_w7$proxy <- car::recode(elsa_proxy[[2]], "NA=999")
ELSA_ds_w7$proxy <- labelled(ELSA_ds_w7$proxy, labels = cat_label)
label(ELSA_ds_w7$proxy) <- ds_label_all
```

#### Statistical description of the new harmonised variable
```{r descript7,  echo=FALSE}
vari <- ELSA_ds_w7$proxy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w7, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL7,  echo=FALSE}
label(ELSA_ds_w7$proxy) <- ds_label
proxy <- ELSA_ds_w7
save(proxy, file = "../RData/w7/proxy.RData")
rm(proxy)
```


# Quality estimation

The derived variables has no levels, they were guessed trough the variables from it is computed 'askpxX'.

<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```



