---
title: "LDL cholesterol"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/ldl_cholDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/ldl_cholDS.R')
```


# Data process


## Finland

### Wave 1 

#### Study-specific variable description

| **Name** | `KOL_LDL_S_117` |
|-|-|
| **Label** | `Fasting LDL cholesterol, directly measured` |
| **Table name** | `t00_athlos_2017_02_23` |
| **Categories:**| `continuous` |
| **Missings:**| `NA` |
| **Description** |  | 

   

```{r assign w1, echo=F }

opal.assign.table.tibble(o, 'Health20002011_w1','Health2000-2011.t00_athlos_2017_02_23', variables=list('KOL_LDL_S_117','KOL_LDL_L_116'), missings = TRUE)
Health20002011_w1 <- opal.execute(o,'Health20002011_w1')

```

```{r local w1, echo=F}

vbl <- Health20002011_w1$KOL_LDL_S_117
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "KOL_LDL_S_117") 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(Health20002011_w1, aes(KOL_LDL_S_117)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `ldl_chol` from the study-specific variable it has to be recoded as follows:

* `multiply mmol/L by 38.67`
* `NA into 999`

**R script:**

```{r harmo w1}

Health20002011_ds_w1 <- tibble(id=Health20002011_w1$id)
Health20002011_ds_w1$ldl_chol <- car::recode(38.67*Health20002011_w1$KOL_LDL_S_117, "NA = 999 ")

```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}

vbl <- Health20002011_ds_w1$ldl_chol
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(Health20002011_ds_w1,!vbl %in% miss_values_vector), aes(ldl_chol)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w1, echo=F, results='asis'}

cat("The variable used to harmonise, 'KOL_LDL_S_117' is checked against the variable KOL_LDL_L_116, which keeps Fasting LDL cholesterol, calculated")

Health20002011_w1$diff <- Health20002011_w1$KOL_LDL_S_117 - Health20002011_w1$KOL_LDL_L_116
vbl <- Health20002011_w1$diff
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "diff") 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(Health20002011_w1, aes(diff)) + geom_histogram(stat="bin", fill="steelblue",binwidth = 0.01) + xlab("Difference between measures: KOL_LDL_S_117 - KOL_LDL_L_116") + ylab("Frequency")

```





### Wave 2

#### Study-specific variable description

| **Name** | `FS_KOL_LDL` |
|-|-|
| **Label** | `fS-Chol-LDL` |
| **Table name** | `t11_athlos_2017_02_27` |
| **Categories:**| `continuous` |
| **Missings:**| `NA` |
| **Description** |  | 

   

```{r assign w2, echo=F }

opal.assign.table.tibble(o, 'Health20002011_w2','Health2000-2011.t11_athlos_2017_02_27', variables=list('FS_KOL_LDL'), missings = TRUE)
Health20002011_w2 <- opal.execute(o,'Health20002011_w2')

```

```{r local w2, echo=F}

vbl <- Health20002011_w2$FS_KOL_LDL
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "FS_KOL_LDL") 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(Health20002011_w2, aes(FS_KOL_LDL)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `ldl_chol` from the study-specific variable it has to be recoded as follows:

* `multiply mmol/L by 38.67`
* `NA into 999`

**R script:**

```{r harmo w2}

Health20002011_ds_w2 <- tibble(id=Health20002011_w2$id)
Health20002011_ds_w2$ldl_chol <- car::recode(38.67*Health20002011_w2$FS_KOL_LDL, "NA = 999 ")

```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}

vbl <- Health20002011_ds_w2$ldl_chol
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(Health20002011_ds_w2,!vbl %in% miss_values_vector), aes(ldl_chol)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w2, echo=F}
```


## Summary of descriptive statistics of the harmonised variable accross populations and waves



```{r summ}

l.hds <- list(w1 = Health20002011_ds_w1, w2 = Health20002011_ds_w2)
m.hds <- list()

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cont_label)
  m_name <- paste0("Health20002011_m_ds_",name)
  assign(m_name, aux_object)
  m.hds[[name]] <- get(paste0("Health20002011_m_ds_",name))
  rm(aux_object)
}


t.summ <- summary(m.hds[[1]][2])[1:6]
t.hds <- substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1)
for (i in seq_along(l.hds)){
  t.summ <- summary(m.hds[[i]][2])[1:6]
  t.hds <- cbind(t.hds,as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))))
}
t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))

dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],names(l.hds))
kable(t.hds)

```


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  ldl_chol <- l.hds[[index]]
  save(ldl_chol, file = paste0(datafolder,names(l.hds)[index],"/ldl_chol.RData"))
}

```
<!-- ########################################################## --> 

# Quality estimation

In wave 1 there is another study-specific variable, `KOL_LDL_L_116`, saving `Fasting LDL cholesterol, calculated`. We used it in the validation.


<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```


