---
title: "Arterial hypertension"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `ah`
* Variable label: `Arterial hypertension`
* Variable description: `Arterial hypertension. Means of all diastolic blood pressure measures.`
* Domain: `Physical Measures`
* Value type: `Categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | no hypertension
1        | hypertension

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done 
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Arterial hypertension"
ds_label_all <- "Arterial hypertension. Means of all diastolic blood pressure measures."
```

# Data process


## HRS sub-sample

### Wave 1 

#### Study-specific variable description


* Name: `R1HIBPE`
* Label: `W1 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:

```{r assign_hrs1}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-HRS-w1',
                         variables=list('R1HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_hrs1, echo=FALSE}
vari <- HRS_ah$R1HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs1, echo=TRUE}
HRS_ds_hrs_w1 <- tibble(id=HRS_ah$id)
HRS_ds_hrs_w1$ah <- car::recode(vari, "NA=999")
HRS_ds_hrs_w1$ah <- labelled(HRS_ds_hrs_w1$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_hrs1, echo=FALSE}
vari <- HRS_ds_hrs_w1$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w1, aes(x=factor(vari))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_hrs1, echo=FALSE}
BeforeH <- table(HRS_ah$R1HIBPE, useNA = 'ifany')
AfterH <- table(HRS_ds_hrs_w1$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)

#ggplot(NULL,aes(dat))+
#  geom_bar(data=HRS_ah,aes(x=factor(RAGENDER)),fill="red", position = "dodge")+
#  geom_bar(data=HRS_ds_hrs_w1,aes(x=factor(ah)),fill="steelblue", position = "dodge")
```

 
 

 
```{r importOPAL_hrs1, echo=FALSE}
label(HRS_ds_hrs_w1$ah) <- ds_label_all
ah <- HRS_ds_hrs_w1
save(ah, file = "../RData/hrs_w1/ah.RData")
rm(ah)

HRS_m_ds_hrs_w1 <- HRS_ds_hrs_w1
HRS_m_ds_hrs_w1$ah <- car::recode(HRS_m_ds_hrs_w1$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w1', HRS_m_ds_hrs_w1)
#opal.symbol_import(o,'HRS_m_ds_hrs_w1', project='_Athlos_Harm_Dataset')
```




### Wave 2 

#### Study-specific variable description

* Name: `R2HIBPE`
* Label: `W2 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:

```{r assign_hrs2, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-HRS-w2',
                         variables=list('R2HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_hrs2, echo=FALSE}
vari <- HRS_ah$R2HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

**R script:**


```{r harmo_hrs2, echo=TRUE}
HRS_ds_hrs_w2 <- tibble(id=HRS_ah$id)
HRS_ds_hrs_w2$ah <- car::recode(vari, "NA=999")
HRS_ds_hrs_w2$ah <- labelled(HRS_ds_hrs_w2$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_hrs2, echo=FALSE}
vari <- HRS_ds_hrs_w2$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w2, aes(x=factor(vari))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_hrs2, echo=FALSE}
BeforeH <- table(HRS_ah$R2HIBPE, useNA = 'ifany')
AfterH <- table(HRS_ds_hrs_w2$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)


#ggplot(NULL,aes(dat))+
#  geom_bar(data=HRS_ah,aes(x=factor(RAGENDER)),fill="red", position = "dodge")+
#  geom_bar(data=HRS_ds_hrs_w2_hrs_w2,aes(x=factor(ah)),fill="steelblue", position = "dodge")

```

 
 

 
```{r importOPAL_hrs2, echo=FALSE}
label(HRS_ds_hrs_w2$ah) <- ds_label_all
ah <- HRS_ds_hrs_w2
save(ah, file = "../RData/hrs_w2/ah.RData")
rm(ah)

HRS_m_ds_hrs_w2 <- HRS_ds_hrs_w2
HRS_m_ds_hrs_w2$ah <- car::recode(HRS_m_ds_hrs_w2$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w2', HRS_m_ds_hrs_w2)
#opal.symbol_import(o,'HRS_m_ds_hrs_w2', project='_Athlos_Harm_Dataset')
```






### Wave 3 

#### Study-specific variable description


* Name: `R3HIBPE`
* Label: `W3 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:

```{r assign_hrs3, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-HRS-w3',
                         variables=list('R3HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_hrs3, echo=FALSE}
vari <- HRS_ah$R3HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs3, echo=TRUE}
HRS_ds_hrs_w3 <- tibble(id=HRS_ah$id)
HRS_ds_hrs_w3$ah <- car::recode(vari, "NA=999")
HRS_ds_hrs_w3$ah <- labelled(HRS_ds_hrs_w3$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_hrs3, echo=FALSE}
vari <- HRS_ds_hrs_w3$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w3, aes(x=factor(vari))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_hrs3, echo=FALSE}
BeforeH <- table(HRS_ah$R3HIBPE, useNA = 'ifany')
AfterH <- table(HRS_ds_hrs_w3$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)


#ggplot(NULL,aes(dat))+
#  geom_bar(data=HRS_ah,aes(x=factor(RAGENDER)),fill="red", position = "dodge")+
#  geom_bar(data=HRS_ds_hrs_w1,aes(x=factor(ah)),fill="steelblue", position = "dodge")

```

 
 

 
```{r importOPAL_hrs3, echo=FALSE}
label(HRS_ds_hrs_w3$ah) <- ds_label_all
ah <- HRS_ds_hrs_w3
save(ah, file = "../RData/hrs_w3/ah.RData")
rm(ah)

HRS_m_ds_hrs_w3 <- HRS_ds_hrs_w3
HRS_m_ds_hrs_w3$ah <- car::recode(HRS_m_ds_hrs_w3$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w3', HRS_m_ds_hrs_w3)
#opal.symbol_import(o,'HRS_m_ds_hrs_w3', project='_Athlos_Harm_Dataset')
```








### Wave 4 

#### Study-specific variable description


* Name: `R4HIBPE`
* Label: `W4 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:

```{r assign_hrs4, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-HRS-w4',
                         variables=list('R4HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_hrs4, echo=FALSE}
vari <- HRS_ah$R4HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs4, echo=TRUE}
HRS_ds_hrs_w4 <- tibble(id=HRS_ah$id)
HRS_ds_hrs_w4$ah <- car::recode(vari, "NA=999")
HRS_ds_hrs_w4$ah <- labelled(HRS_ds_hrs_w4$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_hrs4, echo=FALSE}
vari <- HRS_ds_hrs_w4$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w4, aes(x=factor(vari))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_hrs4, echo=FALSE}
BeforeH <- table(HRS_ah$R4HIBPE, useNA = 'ifany')
AfterH <- table(HRS_ds_hrs_w4$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)

#ggplot(NULL,aes(dat))+
#  geom_bar(data=HRS_ah,aes(x=factor(RAGENDER)),fill="red", position = "dodge")+
#  geom_bar(data=HRS_ds_hrs_w1,aes(x=factor(ah)),fill="steelblue", position = "dodge")
```

 
 

 
```{r importOPAL_hrs4, echo=FALSE}
label(HRS_ds_hrs_w4$ah) <- ds_label_all
ah <- HRS_ds_hrs_w4
save(ah, file = "../RData/hrs_w4/ah.RData")
rm(ah)

HRS_m_ds_hrs_w4 <- HRS_ds_hrs_w4
HRS_m_ds_hrs_w4$ah <- car::recode(HRS_m_ds_hrs_w4$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w4', HRS_m_ds_hrs_w4)
#opal.symbol_import(o,'HRS_m_ds_hrs_w4', project='_Athlos_Harm_Dataset')
```





### Wave 5

#### Study-specific variable description


* Name: `R5HIBPE`
* Label: `W5 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:

```{r assign_hrs5, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-HRS-w5',
                         variables=list('R5HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_hrs5, echo=FALSE}
vari <- HRS_ah$R5HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs5, echo=TRUE}
HRS_ds_hrs_w5 <- tibble(id=HRS_ah$id)
HRS_ds_hrs_w5$ah <- car::recode(vari, "NA=999")
HRS_ds_hrs_w5$ah <- labelled(HRS_ds_hrs_w5$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_hrs5, echo=FALSE}
vari <- HRS_ds_hrs_w5$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w5, aes(x=factor(vari))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_hrs5, echo=FALSE}
BeforeH <- table(HRS_ah$R5HIBPE, useNA = 'ifany')
AfterH <- table(HRS_ds_hrs_w5$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)


#ggplot(NULL,aes(dat))+
#  geom_bar(data=HRS_ah,aes(x=factor(RAGENDER)),fill="red", position = "dodge")+
#  geom_bar(data=HRS_ds_hrs_w1,aes(x=factor(ah)),fill="steelblue", position = "dodge")

```

 
 
```{r importOPAL_hrs5, echo=FALSE}
label(HRS_ds_hrs_w5$ah) <- ds_label_all
ah <- HRS_ds_hrs_w5
save(ah, file = "../RData/hrs_w5/ah.RData")
rm(ah)

HRS_m_ds_hrs_w5 <- HRS_ds_hrs_w5
HRS_m_ds_hrs_w5$ah <- car::recode(HRS_m_ds_hrs_w5$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w5', HRS_m_ds_hrs_w5)
#opal.symbol_import(o,'HRS_m_ds_hrs_w5', project='_Athlos_Harm_Dataset')
```





### Wave 6

#### Study-specific variable description

 

* Name: `R6HIBPE`
* Label: `W6 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description: 

```{r assign_hrs6, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-HRS-w6',
                         variables=list('R6HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_hrs6, echo=FALSE}
vari <- HRS_ah$R6HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs6, echo=TRUE}
HRS_ds_hrs_w6 <- tibble(id=HRS_ah$id)
HRS_ds_hrs_w6$ah <- car::recode(vari, "NA=999")
HRS_ds_hrs_w6$ah <- labelled(HRS_ds_hrs_w6$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_hrs6, echo=FALSE}
vari <- HRS_ds_hrs_w6$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w6, aes(x=factor(vari))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_hrs6, echo=FALSE}
BeforeH <- table(HRS_ah$R6HIBPE, useNA = 'ifany')
AfterH <- table(HRS_ds_hrs_w6$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)

#ggplot(NULL,aes(dat))+
#  geom_bar(data=HRS_ah,aes(x=factor(RAGENDER)),fill="red", position = "dodge")+
#  geom_bar(data=HRS_ds_hrs_w1,aes(x=factor(ah)),fill="steelblue", position = "dodge")

```

 

```{r importOPAL_hrs6, echo=FALSE}
label(HRS_ds_hrs_w6$ah) <- ds_label_all
ah <- HRS_ds_hrs_w6
save(ah, file = "../RData/hrs_w6/ah.RData")
rm(ah)

HRS_m_ds_hrs_w6 <- HRS_ds_hrs_w6
HRS_m_ds_hrs_w6$ah <- car::recode(HRS_m_ds_hrs_w6$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w6', HRS_m_ds_hrs_w6)
#opal.symbol_import(o,'HRS_m_ds_hrs_w6', project='_Athlos_Harm_Dataset')
```






### Wave 7

#### Study-specific variable description


* Name: `R7HIBPE`
* Label: `W7 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:

```{r assign_hrs7, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-HRS-w7',
                         variables=list('R7HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_hrs7, echo=FALSE}
vari <- HRS_ah$R7HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs7, echo=TRUE}
HRS_ds_hrs_w7 <- tibble(id=HRS_ah$id)
HRS_ds_hrs_w7$ah <- car::recode(vari, "NA=999")
HRS_ds_hrs_w7$ah <- labelled(HRS_ds_hrs_w7$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_hrs7, echo=FALSE}
vari <- HRS_ds_hrs_w7$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w7, aes(x=factor(vari))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_hrs7, echo=FALSE}
BeforeH <- table(HRS_ah$R7HIBPE, useNA = 'ifany')
AfterH <- table(HRS_ds_hrs_w7$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)


#ggplot(NULL,aes(dat))+
#  geom_bar(data=HRS_ah,aes(x=factor(RAGENDER)),fill="red", position = "dodge")+
#  geom_bar(data=HRS_ds_hrs_w1,aes(x=factor(ah)),fill="steelblue", position = "dodge")

```

 
 

 
```{r importOPAL_hrs7, echo=FALSE}
label(HRS_ds_hrs_w7$ah) <- ds_label_all
ah <- HRS_ds_hrs_w7
save(ah, file = "../RData/hrs_w7/ah.RData")
rm(ah)


HRS_m_ds_hrs_w7 <- HRS_ds_hrs_w7
HRS_m_ds_hrs_w7$ah <- car::recode(HRS_m_ds_hrs_w7$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w7', HRS_m_ds_hrs_w7)
#opal.symbol_import(o,'HRS_m_ds_hrs_w7', project='_Athlos_Harm_Dataset')
```






### Wave 8

#### Study-specific variable description

 

* Name: `R8HIBPE`
* Label: `W8 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:

```{r assign_hrs8, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-HRS-w8',
                         variables=list('R8HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_hrs8, echo=FALSE}
vari <- HRS_ah$R8HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs8, echo=TRUE}
HRS_ds_hrs_w8 <- tibble(id=HRS_ah$id)
HRS_ds_hrs_w8$ah <- car::recode(vari, "NA=999")
HRS_ds_hrs_w8$ah <- labelled(HRS_ds_hrs_w8$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_hrs8, echo=FALSE}
vari <- HRS_ds_hrs_w8$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w8, aes(x=factor(vari))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_hrs8, echo=FALSE}
BeforeH <- table(HRS_ah$R8HIBPE, useNA = 'ifany')
AfterH <- table(HRS_ds_hrs_w8$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)


#ggplot(NULL,aes(dat))+
#  geom_bar(data=HRS_ah,aes(x=factor(RAGENDER)),fill="red", position = "dodge")+
#  geom_bar(data=HRS_ds_hrs_w1,aes(x=factor(ah)),fill="steelblue", position = "dodge")
```


```{r importOPAL_hrs8, echo=FALSE}
label(HRS_ds_hrs_w8$ah) <- ds_label_all
ah <- HRS_ds_hrs_w8
save(ah, file = "../RData/hrs_w8/ah.RData")
rm(ah)

HRS_m_ds_hrs_w8 <- HRS_ds_hrs_w8
HRS_m_ds_hrs_w8$ah <- car::recode(HRS_m_ds_hrs_w8$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w8', HRS_m_ds_hrs_w8)
#opal.symbol_import(o,'HRS_m_ds_hrs_w8', project='_Athlos_Harm_Dataset')
```





### Wave 9

#### Study-specific variable description

 

* Name: `R9HIBPE`
* Label: `W9 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:
```{r assign_hrs9, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-HRS-w9',
                         variables=list('R9HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_hrs9, echo=FALSE}
vari <- HRS_ah$R9HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

**R script:**


```{r harmo_hrs9, echo=TRUE}
HRS_ds_hrs_w9 <- tibble(id=HRS_ah$id)
HRS_ds_hrs_w9$ah <- car::recode(vari, "NA=999")
HRS_ds_hrs_w9$ah <- labelled(HRS_ds_hrs_w9$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_hrs9, echo=FALSE}
vari <- HRS_ds_hrs_w9$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w9, aes(x=factor(vari))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_hrs9, echo=FALSE}
BeforeH <- table(HRS_ah$R9HIBPE, useNA = 'ifany')
AfterH <- table(HRS_ds_hrs_w9$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)


#ggplot(NULL,aes(dat))+
#  geom_bar(data=HRS_ah,aes(x=factor(RAGENDER)),fill="red", position = "dodge")+
#  geom_bar(data=HRS_ds_hrs_w1,aes(x=factor(ah)),fill="steelblue", position = "dodge")

```

 
```{r importOPAL_hrs9, echo=FALSE}
label(HRS_ds_hrs_w9$ah) <- ds_label_all
ah <- HRS_ds_hrs_w9
save(ah, file = "../RData/hrs_w9/ah.RData")
rm(ah)

HRS_m_ds_hrs_w9 <- HRS_ds_hrs_w9
HRS_m_ds_hrs_w9$ah <- car::recode(HRS_m_ds_hrs_w9$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w9', HRS_m_ds_hrs_w9)
#opal.symbol_import(o,'HRS_m_ds_hrs_w9', project='_Athlos_Harm_Dataset')
```







### Wave 10

#### Study-specific variable description

 

* Name: `R10HIBPE`
* Label: `W10 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:


```{r assign_hrs10, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-HRS-w10',
                         variables=list('R10HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_hrs10, echo=FALSE}
vari <- HRS_ah$R10HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs10, echo=TRUE}
HRS_ds_hrs_w10 <- tibble(id=HRS_ah$id)
HRS_ds_hrs_w10$ah <- car::recode(vari, "NA=999")
HRS_ds_hrs_w10$ah <- labelled(HRS_ds_hrs_w10$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_hrs10, echo=FALSE}
vari <- HRS_ds_hrs_w10$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w10, aes(x=factor(vari))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_hrs10, echo=FALSE}
BeforeH <- table(HRS_ah$R10HIBPE, useNA = 'ifany')
AfterH <- table(HRS_ds_hrs_w10$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)


#ggplot(NULL,aes(dat))+
#  geom_bar(data=HRS_ah,aes(x=factor(RAGENDER)),fill="red", position = "dodge")+
#  geom_bar(data=HRS_ds_hrs_w1,aes(x=factor(ah)),fill="steelblue", position = "dodge")

```

 
```{r importOPAL_hrs10, echo=FALSE}
label(HRS_ds_hrs_w10$ah) <- ds_label_all
ah <- HRS_ds_hrs_w10
save(ah, file = "../RData/hrs_w10/ah.RData")
rm(ah)

HRS_m_ds_hrs_w10 <- HRS_ds_hrs_w10
HRS_m_ds_hrs_w10$ah <- car::recode(HRS_m_ds_hrs_w10$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w10', HRS_m_ds_hrs_w10)
#opal.symbol_import(o,'HRS_m_ds_hrs_w10', project='_Athlos_Harm_Dataset')
```





### Wave 11

#### Study-specific variable description

 

* Name: `R11HIBPE`
* Label: `W11 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:

```{r assign_hrs11, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-HRS-w11',
                         variables=list('R11HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_hrs11, echo=FALSE}
vari <- HRS_ah$R11HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs11, echo=TRUE}
HRS_ds_hrs_w11 <- tibble(id=HRS_ah$id)
HRS_ds_hrs_w11$ah <- car::recode(vari, "NA=999")
HRS_ds_hrs_w11$ah <- labelled(HRS_ds_hrs_w11$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_hrs11, echo=FALSE}
vari <- HRS_ds_hrs_w11$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w11, aes(x=factor(vari))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_hrs11, echo=FALSE}
BeforeH <- table(HRS_ah$R11HIBPE, useNA = 'ifany')
AfterH <- table(HRS_ds_hrs_w11$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)


#ggplot(NULL,aes(dat))+
#  geom_bar(data=HRS_ah,aes(x=factor(RAGENDER)),fill="red", position = "dodge")+
#  geom_bar(data=HRS_ds_hrs_w1,aes(x=factor(ah)),fill="steelblue", position = "dodge")

```

 
 

 
```{r importOPAL_hrs11, echo=FALSE}
label(HRS_ds_hrs_w11$ah) <- ds_label_all
ah <- HRS_ds_hrs_w11
save(ah, file = "../RData/hrs_w11/ah.RData")
rm(ah)

HRS_m_ds_hrs_w11 <- HRS_ds_hrs_w11
HRS_m_ds_hrs_w11$ah <- car::recode(HRS_m_ds_hrs_w11$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w11', HRS_m_ds_hrs_w11)
#opal.symbol_import(o,'HRS_m_ds_hrs_w11', project='_Athlos_Harm_Dataset')
```



## AHEAD 

### Wave 2 

#### Study-specific variable description


* Name: `R2HIBPE`
* Label: `W2 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:

```{r assign_ahead2, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-AHEAD-w2',
                         variables=list('R2HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_ahead2, echo=FALSE}
vari <- HRS_ah$R2HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ahead2, echo=TRUE}
HRS_ds_ahead_w2 <- tibble(id=HRS_ah$id)
HRS_ds_ahead_w2$ah <- car::recode(vari, "NA=999")
HRS_ds_ahead_w2$ah <- labelled(HRS_ds_ahead_w2$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_ahead2, echo=FALSE}
vari <- HRS_ds_ahead_w2$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w2, aes(x=factor(vari))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_ahead2, echo=FALSE}
BeforeH <- table(HRS_ah$R2HIBPE, useNA = 'ifany')
AfterH <- table(HRS_ds_ahead_w2$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)


#ggplot(NULL,aes(dat))+
#  geom_bar(data=HRS_ah,aes(x=factor(RAGENDER)),fill="red", position = "dodge")+
#  geom_bar(data=HRS_ds_hrs_w1,aes(x=factor(ah)),fill="steelblue", position = "dodge")

```

 
```{r importOPAL_ahead2, echo=FALSE}
label(HRS_ds_ahead_w2$ah) <- ds_label_all
ah <- HRS_ds_ahead_w2
save(ah, file = "../RData/ahead_w2/ah.RData")
rm(ah)

HRS_m_ds_ahead_w2 <- HRS_ds_ahead_w2
HRS_m_ds_ahead_w2$ah <- car::recode(HRS_m_ds_ahead_w2$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w2', HRS_m_ds_ahead_w2)
#opal.symbol_import(o,'HRS_m_ds_ahead_w2', project='_Athlos_Harm_Dataset')
```





### Wave 3 

#### Study-specific variable description

 

* Name: `R3HIBPE`
* Label: `W3 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:

```{r assign_ahead3, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-AHEAD-w3',
                         variables=list('R3HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_ahead3, echo=FALSE}
vari <- HRS_ah$R3HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ahead3, echo=TRUE}
HRS_ds_ahead_w3 <- tibble(id=HRS_ah$id)
HRS_ds_ahead_w3$ah <- car::recode(vari, "NA=999")
HRS_ds_ahead_w3$ah <- labelled(HRS_ds_ahead_w3$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_ahead3, echo=FALSE}
vari <- HRS_ds_ahead_w3$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w3, aes(x=factor(vari))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_ahead3, echo=FALSE}
BeforeH <- table(HRS_ah$R3HIBPE, useNA = 'ifany')
AfterH <- table(HRS_ds_ahead_w3$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)

#ggplot(NULL,aes(dat))+
#  geom_bar(data=HRS_ah,aes(x=factor(RAGENDER)),fill="red", position = "dodge")+
#  geom_bar(data=HRS_ds_hrs_w1,aes(x=factor(ah)),fill="steelblue", position = "dodge")
```

 
 

 
```{r importOPAL_ahead3, echo=FALSE}
label(HRS_ds_ahead_w3$ah) <- ds_label_all
ah <- HRS_ds_ahead_w3
save(ah, file = "../RData/ahead_w3/ah.RData")
rm(ah)

HRS_m_ds_ahead_w3 <- HRS_ds_ahead_w3
HRS_m_ds_ahead_w3$ah <- car::recode(HRS_m_ds_ahead_w3$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w3', HRS_m_ds_ahead_w3)
#opal.symbol_import(o,'HRS_m_ds_ahead_w3', project='_Athlos_Harm_Dataset')
```





### Wave 4 

#### Study-specific variable description

 

* Name: `R4HIBPE`
* Label: `W4 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:
```{r assign_ahead4, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-AHEAD-w4',
                         variables=list('R4HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_ahead4, echo=FALSE}
vari <- HRS_ah$R4HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ahead4, echo=TRUE}
HRS_ds_ahead_w4 <- tibble(id=HRS_ah$id)
HRS_ds_ahead_w4$ah <- car::recode(vari, "NA=999")
HRS_ds_ahead_w4$ah <- labelled(HRS_ds_ahead_w4$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_ahead4, echo=FALSE}
vari <- HRS_ds_ahead_w4$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w4, aes(x=factor(vari))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_ahead4, echo=FALSE}
BeforeH <- table(HRS_ah$R4HIBPE, useNA = 'ifany')
AfterH <- table(HRS_ds_ahead_w4$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)

#ggplot(NULL,aes(dat))+
#  geom_bar(data=HRS_ah,aes(x=factor(RAGENDER)),fill="red", position = "dodge")+
#  geom_bar(data=HRS_ds_hrs_w1,aes(x=factor(ah)),fill="steelblue", position = "dodge")

```

 
 

 
```{r importOPAL_ahead4, echo=FALSE}
label(HRS_ds_ahead_w4$ah) <- ds_label_all
ah <- HRS_ds_ahead_w4
save(ah, file = "../RData/ahead_w4/ah.RData")
rm(ah)

HRS_m_ds_ahead_w4 <- HRS_ds_ahead_w4
HRS_m_ds_ahead_w4$ah <- car::recode(HRS_m_ds_ahead_w4$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w4', HRS_m_ds_ahead_w4)
#opal.symbol_import(o,'HRS_m_ds_ahead_w4', project='_Athlos_Harm_Dataset')
```






### Wave 5 

#### Study-specific variable description

 

* Name: `R5HIBPE`
* Label: `W5 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:

```{r assign_ahead5, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-AHEAD-w5',
                         variables=list('R5HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_ahead5, echo=FALSE}
vari <- HRS_ah$R5HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ahead5, echo=TRUE}
HRS_ds_ahead_w5 <- tibble(id=HRS_ah$id)
HRS_ds_ahead_w5$ah <- car::recode(vari, "NA=999")
HRS_ds_ahead_w5$ah <- labelled(HRS_ds_ahead_w5$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_ahead5, echo=FALSE}
vari <- HRS_ds_ahead_w5$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w5, aes(x=factor(vari))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_ahead5, echo=FALSE}
BeforeH <- table(HRS_ah$R5HIBPE, useNA = 'ifany')
AfterH <- table(HRS_ds_ahead_w5$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)


#ggplot(NULL,aes(dat))+
#  geom_bar(data=HRS_ah,aes(x=factor(RAGENDER)),fill="red", position = "dodge")+
#  geom_bar(data=HRS_ds_hrs_w1,aes(x=factor(ah)),fill="steelblue", position = "dodge")

```

 
 

 
```{r importOPAL_ahead5, echo=FALSE}
label(HRS_ds_ahead_w5$ah) <- ds_label_all
ah <- HRS_ds_ahead_w5
save(ah, file = "../RData/ahead_w5/ah.RData")
rm(ah)

HRS_m_ds_ahead_w5 <- HRS_ds_ahead_w5
HRS_m_ds_ahead_w5$ah <- car::recode(HRS_m_ds_ahead_w5$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w5', HRS_m_ds_ahead_w5)
#opal.symbol_import(o,'HRS_m_ds_ahead_w5', project='_Athlos_Harm_Dataset')
```






### Wave 6 

#### Study-specific variable description

 

* Name: `R6HIBPE`
* Label: `W6 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:

```{r assign_ahead6, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-AHEAD-w6',
                         variables=list('R6HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_ahead6, echo=FALSE}
vari <- HRS_ah$R6HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ahead6, echo=TRUE}
HRS_ds_ahead_w6 <- tibble(id=HRS_ah$id)
HRS_ds_ahead_w6$ah <- car::recode(vari, "NA=999")
HRS_ds_ahead_w6$ah <- labelled(HRS_ds_ahead_w6$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_ahead6, echo=FALSE}
vari <- HRS_ds_ahead_w6$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w6, aes(x=factor(vari))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_ahead6, echo=FALSE}
BeforeH <- table(HRS_ah$R6HIBPE, useNA = 'ifany')
AfterH <- table(HRS_ds_ahead_w6$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)


#ggplot(NULL,aes(dat))+
#  geom_bar(data=HRS_ah,aes(x=factor(RAGENDER)),fill="red", position = "dodge")+
#  geom_bar(data=HRS_ds_hrs_w1,aes(x=factor(ah)),fill="steelblue", position = "dodge")

```

 
```{r importOPAL_ahead6, echo=FALSE}
label(HRS_ds_ahead_w6$ah) <- ds_label_all
ah <- HRS_ds_ahead_w6
save(ah, file = "../RData/ahead_w6/ah.RData")
rm(ah)

HRS_m_ds_ahead_w6 <- HRS_ds_ahead_w6
HRS_m_ds_ahead_w6$ah <- car::recode(HRS_m_ds_ahead_w6$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w6', HRS_m_ds_ahead_w6)
#opal.symbol_import(o,'HRS_m_ds_ahead_w6', project='_Athlos_Harm_Dataset')
```




### Wave 7 

#### Study-specific variable description

 

* Name: `R7HIBPE`
* Label: `W7 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:

```{r assign_ahead7, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-AHEAD-w7',
                         variables=list('R7HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_ahead7, echo=FALSE}
vari <- HRS_ah$R7HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ahead7, echo=TRUE}
HRS_ds_ahead_w7 <- tibble(id=HRS_ah$id)
HRS_ds_ahead_w7$ah <- car::recode(vari, "NA=999")
HRS_ds_ahead_w7$ah <- labelled(HRS_ds_ahead_w7$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_ahead7, echo=FALSE}
vari <- HRS_ds_ahead_w7$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w7, aes(x=factor(vari))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_ahead7, echo=FALSE}
BeforeH <- table(HRS_ah$R7HIBPE, useNA = 'ifany')
AfterH <- table(HRS_ds_ahead_w7$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)

#ggplot(NULL,aes(dat))+
#  geom_bar(data=HRS_ah,aes(x=factor(RAGENDER)),fill="red", position = "dodge")+
#  geom_bar(data=HRS_ds_hrs_w1,aes(x=factor(ah)),fill="steelblue", position = "dodge")

```

 
 

 
```{r importOPAL_ahead7, echo=FALSE}
label(HRS_ds_ahead_w7$ah) <- ds_label_all
ah <- HRS_ds_ahead_w7
save(ah, file = "../RData/ahead_w7/ah.RData")
rm(ah)

HRS_m_ds_ahead_w7 <- HRS_ds_ahead_w7
HRS_m_ds_ahead_w7$ah <- car::recode(HRS_m_ds_ahead_w7$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'HRS_m_ds_ahead_w7', HRS_m_ds_ahead_w7)
#opal.symbol_import(o,'HRS_m_ds_ahead_w7', project='_Athlos_Harm_Dataset')
```







### Wave 8 

#### Study-specific variable description

 

* Name: `R8HIBPE`
* Label: `W8 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:

```{r assign_ahead8, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-AHEAD-w8',
                         variables=list('R8HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_ahead8, echo=FALSE}
vari <- HRS_ah$R8HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ahead8, echo=TRUE}
HRS_ds_ahead_w8 <- tibble(id=HRS_ah$id)
HRS_ds_ahead_w8$ah <- car::recode(vari, "NA=999")
HRS_ds_ahead_w8$ah <- labelled(HRS_ds_ahead_w8$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_ahead8, echo=FALSE}
vari <- HRS_ds_ahead_w8$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w8, aes(x=factor(vari))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_ahead8, echo=FALSE}
BeforeH <- table(HRS_ah$R8HIBPE, useNA = 'ifany')
AfterH <- table(HRS_ds_ahead_w8$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)

#ggplot(NULL,aes(dat))+
#  geom_bar(data=HRS_ah,aes(x=factor(RAGENDER)),fill="red", position = "dodge")+
#  geom_bar(data=HRS_ds_hrs_w1,aes(x=factor(ah)),fill="steelblue", position = "dodge")

```

 
 

 
```{r importOPAL_ahead8, echo=FALSE}
label(HRS_ds_ahead_w8$ah) <- ds_label_all
ah <- HRS_ds_ahead_w8
save(ah, file = "../RData/ahead_w8/ah.RData")
rm(ah)

HRS_m_ds_ahead_w8 <- HRS_ds_ahead_w8
HRS_m_ds_ahead_w8$ah <- car::recode(HRS_m_ds_ahead_w8$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w8', HRS_m_ds_ahead_w8)
#opal.symbol_import(o,'HRS_m_ds_ahead_w8', project='_Athlos_Harm_Dataset')
```






### Wave 9 

#### Study-specific variable description

 

* Name: `R9HIBPE`
* Label: `W9 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:

```{r assign_ahead9, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-AHEAD-w9',
                         variables=list('R9HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_ahead9, echo=FALSE}
vari <- HRS_ah$R9HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ahead9, echo=TRUE}
HRS_ds_ahead_w9 <- tibble(id=HRS_ah$id)
HRS_ds_ahead_w9$ah <- car::recode(vari, "NA=999")
HRS_ds_ahead_w9$ah <- labelled(HRS_ds_ahead_w9$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_ahead9, echo=FALSE}
vari <- HRS_ds_ahead_w9$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w9, aes(x=factor(vari))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_ahead9, echo=FALSE}
BeforeH <- table(HRS_ah$R9HIBPE, useNA = 'ifany')
AfterH <- table(HRS_ds_ahead_w9$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)


#ggplot(NULL,aes(dat))+
#  geom_bar(data=HRS_ah,aes(x=factor(RAGENDER)),fill="red", position = "dodge")+
#  geom_bar(data=HRS_ds_hrs_w1,aes(x=factor(ah)),fill="steelblue", position = "dodge")

```

 
 

 
```{r importOPAL_ahead9, echo=FALSE}
label(HRS_ds_ahead_w9$ah) <- ds_label_all
ah <- HRS_ds_ahead_w9
save(ah, file = "../RData/ahead_w9/ah.RData")
rm(ah)

HRS_m_ds_ahead_w9 <- HRS_ds_ahead_w9
HRS_m_ds_ahead_w9$ah <- car::recode(HRS_m_ds_ahead_w9$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w9', HRS_m_ds_ahead_w9)
#opal.symbol_import(o,'HRS_m_ds_ahead_w9', project='_Athlos_Harm_Dataset')
```




### Wave 10 

#### Study-specific variable description

 

* Name: `R10HIBPE`
* Label: `W10 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:

```{r assign_ahead10, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-AHEAD-w10',
                         variables=list('R10HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_ahead10, echo=FALSE}
vari <- HRS_ah$R10HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ahead10, echo=TRUE}
HRS_ds_ahead_w10 <- tibble(id=HRS_ah$id)
HRS_ds_ahead_w10$ah <- car::recode(vari, "NA=999")
HRS_ds_ahead_w10$ah <- labelled(HRS_ds_ahead_w10$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_ahead10, echo=FALSE}
vari <- HRS_ds_ahead_w10$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w10, aes(x=factor(vari))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_ahead10, echo=FALSE}
BeforeH <- table(HRS_ah$R10HIBPE, useNA = 'ifany')
AfterH <- table(HRS_ds_ahead_w10$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)

#ggplot(NULL,aes(dat))+
#  geom_bar(data=HRS_ah,aes(x=factor(RAGENDER)),fill="red", position = "dodge")+
#  geom_bar(data=HRS_ds_hrs_w1,aes(x=factor(ah)),fill="steelblue", position = "dodge")

```

 
 

 
```{r importOPAL_ahead10, echo=FALSE}
label(HRS_ds_ahead_w10$ah) <- ds_label_all
ah <- HRS_ds_ahead_w10
save(ah, file = "../RData/ahead_w10/ah.RData")
rm(ah)

HRS_m_ds_ahead_w10 <- HRS_ds_ahead_w10
HRS_m_ds_ahead_w10$ah <- car::recode(HRS_m_ds_ahead_w10$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w10', HRS_m_ds_ahead_w10)
#opal.symbol_import(o,'HRS_m_ds_ahead_w10', project='_Athlos_Harm_Dataset')
```





### Wave 11 

#### Study-specific variable description

 

* Name: `R11HIBPE`
* Label: `W11 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:

```{r assign_ahead11, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-AHEAD-w11',
                         variables=list('R11HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_ahead11, echo=FALSE}
vari <- HRS_ah$R11HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ahead11, echo=TRUE}
HRS_ds_ahead_w11 <- tibble(id=HRS_ah$id)
HRS_ds_ahead_w11$ah <- car::recode(vari, "NA=999")
HRS_ds_ahead_w11$ah <- labelled(HRS_ds_ahead_w11$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_ahead11, echo=FALSE}
vari <- HRS_ds_ahead_w11$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w11, aes(x=factor(vari))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_ahead11, echo=FALSE}
BeforeH <- table(HRS_ah$R11HIBPE, useNA = 'ifany')
AfterH <- table(HRS_ds_ahead_w11$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)

#ggplot(NULL,aes(dat))+
#  geom_bar(data=HRS_ah,aes(x=factor(RAGENDER)),fill="red", position = "dodge")+
#  geom_bar(data=HRS_ds_hrs_w1,aes(x=factor(ah)),fill="steelblue", position = "dodge")
```

 
 

 
```{r importOPAL_ahead11, echo=FALSE}
label(HRS_ds_ahead_w11$ah) <- ds_label_all
ah <- HRS_ds_ahead_w11
save(ah, file = "../RData/ahead_w11/ah.RData")
rm(ah)

HRS_m_ds_ahead_w11 <- HRS_ds_ahead_w11
HRS_m_ds_ahead_w11$ah <- car::recode(HRS_m_ds_ahead_w11$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w11', HRS_m_ds_ahead_w11)
#opal.symbol_import(o,'HRS_m_ds_ahead_w11', project='_Athlos_Harm_Dataset')
```




### The Children of the Depression (CODA) sub-sample

### Wave 4 

#### Study-specific variable description

 

* Name: `R4HIBPE`
* Label: `W4 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:


```{r assign_coda4, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-CODA-w4',
                         variables=list('R4HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_coda4, echo=FALSE}
vari <- HRS_ah$R4HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_coda4, echo=TRUE}
HRS_ds_coda_w4 <- tibble(id=HRS_ah$id)
HRS_ds_coda_w4$ah <- car::recode(vari, "NA=999")
HRS_ds_coda_w4$ah <- labelled(HRS_ds_coda_w4$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_coda4, echo=FALSE}
vari <- HRS_ds_coda_w4$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w4, aes(x=factor(vari))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_coda4, echo=FALSE}
BeforeH <- table(HRS_ah$R4HIBPE, useNA = 'ifany')
AfterH <- table(HRS_ds_coda_w4$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)

#ggplot(NULL,aes(dat))+
#  geom_bar(data=HRS_ah,aes(x=factor(RAGENDER)),fill="red", position = "dodge")+
#  geom_bar(data=HRS_ds_hrs_w1,aes(x=factor(ah)),fill="steelblue", position = "dodge")
```

 
 

 
```{r importOPAL_coda4, echo=FALSE}
label(HRS_ds_coda_w4$ah) <- ds_label_all
ah <- HRS_ds_coda_w4
save(ah, file = "../RData/coda_w4/ah.RData")
rm(ah)


HRS_m_ds_coda_w4 <- HRS_ds_coda_w4
HRS_m_ds_coda_w4$ah <- car::recode(HRS_m_ds_coda_w4$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_coda_w4', HRS_m_ds_coda_w4)
#opal.symbol_import(o,'HRS_m_ds_coda_w4', project='_Athlos_Harm_Dataset')
```







### Wave 5 

#### Study-specific variable description

* Name: `R5HIBPE`
* Label: `W5 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:

```{r assign_coda5, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-CODA-w5',
                         variables=list('R5HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_coda5, echo=FALSE}
vari <- HRS_ah$R5HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`



**R script:**

```{r harmo_coda5, echo=TRUE}
HRS_ds_coda_w5 <- tibble(id=HRS_ah$id)
HRS_ds_coda_w5$ah <- car::recode(vari, "NA=999")
HRS_ds_coda_w5$ah <- labelled(HRS_ds_coda_w5$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_coda5, echo=FALSE}
vari <- HRS_ds_coda_w5$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w5, aes(x=factor(vari))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_coda5, echo=FALSE}
BeforeH <- table(HRS_ah$R5HIBPE, useNA = 'ifany')
AfterH <- table(HRS_ds_coda_w5$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)

#ggplot(NULL,aes(dat))+
#  geom_bar(data=HRS_ah,aes(x=factor(RAGENDER)),fill="red", position = "dodge")+
#  geom_bar(data=HRS_ds_hrs_w1,aes(x=factor(ah)),fill="steelblue", position = "dodge")
```

 
 

 
```{r importOPAL_coda5, echo=FALSE}
label(HRS_ds_coda_w5$ah) <- ds_label_all
ah <- HRS_ds_coda_w5
save(ah, file = "../RData/coda_w5/ah.RData")
rm(ah)

HRS_m_ds_coda_w5 <- HRS_ds_coda_w5
HRS_m_ds_coda_w5$ah <- car::recode(HRS_m_ds_coda_w5$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_coda_w5', HRS_m_ds_coda_w5)
#opal.symbol_import(o,'HRS_m_ds_coda_w5', project='_Athlos_Harm_Dataset')
```





### Wave 6 

#### Study-specific variable description


* Name: `R6HIBPE`
* Label: `W6 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:


```{r assign_coda6, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-CODA-w6',
                         variables=list('R6HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_coda6, echo=FALSE}
vari <- HRS_ah$R6HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_coda6, echo=TRUE}
HRS_ds_coda_w6 <- tibble(id=HRS_ah$id)
HRS_ds_coda_w6$ah <- car::recode(vari, "NA=999")
HRS_ds_coda_w6$ah <- labelled(HRS_ds_coda_w6$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_coda6, echo=FALSE}
vari <- HRS_ds_coda_w6$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w6, aes(x=factor(vari))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_coda6, echo=FALSE}
BeforeH <- table(HRS_ah$R6HIBPE, useNA = 'ifany')
AfterH <- table(HRS_ds_coda_w6$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)


#ggplot(NULL,aes(dat))+
#  geom_bar(data=HRS_ah,aes(x=factor(RAGENDER)),fill="red", position = "dodge")+
#  geom_bar(data=HRS_ds_hrs_w1,aes(x=factor(ah)),fill="steelblue", position = "dodge")

```

 
 

 
```{r importOPAL_coda6, echo=FALSE}
label(HRS_ds_coda_w6$ah) <- ds_label_all
ah <- HRS_ds_coda_w6
save(ah, file = "../RData/coda_w6/ah.RData")
rm(ah)

HRS_m_ds_coda_w6 <- HRS_ds_coda_w6
HRS_m_ds_coda_w6$ah <- car::recode(HRS_m_ds_coda_w6$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'HRS_m_ds_coda_w6', HRS_m_ds_coda_w6)
#opal.symbol_import(o,'HRS_m_ds_coda_w6', project='_Athlos_Harm_Dataset')
```






### Wave 7 

#### Study-specific variable description


* Name: `R7HIBPE`
* Label: `W7 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:

```{r assign_coda7, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-CODA-w7',
                         variables=list('R7HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_coda7, echo=FALSE}
vari <- HRS_ah$R7HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_coda7, echo=TRUE}
HRS_ds_coda_w7 <- tibble(id=HRS_ah$id)
HRS_ds_coda_w7$ah <- car::recode(vari, "NA=999")
HRS_ds_coda_w7$ah <- labelled(HRS_ds_coda_w7$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_coda7, echo=FALSE}
vari <- HRS_ds_coda_w7$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w7, aes(x=factor(vari))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_coda7, echo=FALSE}
BeforeH <- table(HRS_ah$R7HIBPE, useNA = 'ifany')
AfterH <- table(HRS_ds_coda_w7$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)

#ggplot(NULL,aes(dat))+
#  geom_bar(data=HRS_ah,aes(x=factor(RAGENDER)),fill="red", position = "dodge")+
#  geom_bar(data=HRS_ds_hrs_w1,aes(x=factor(ah)),fill="steelblue", position = "dodge")

```

 
 

 
```{r importOPAL_coda7, echo=FALSE}
label(HRS_ds_coda_w7$ah) <- ds_label_all
ah <- HRS_ds_coda_w7
save(ah, file = "../RData/coda_w7/ah.RData")
rm(ah)


HRS_m_ds_coda_w7 <- HRS_ds_coda_w7
HRS_m_ds_coda_w7$ah <- car::recode(HRS_m_ds_coda_w7$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_coda_w7', HRS_m_ds_coda_w7)
#opal.symbol_import(o,'HRS_m_ds_coda_w7', project='_Athlos_Harm_Dataset')
```





### Wave 8 

#### Study-specific variable description


* Name: `R8HIBPE`
* Label: `W8 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:

```{r assign_coda8, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-CODA-w8',
                         variables=list('R8HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_coda8, echo=FALSE}
vari <- HRS_ah$R8HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`


**R script:**

```{r harmo_coda8, echo=TRUE}
HRS_ds_coda_w8 <- tibble(id=HRS_ah$id)
HRS_ds_coda_w8$ah <- car::recode(vari, "NA=999")
HRS_ds_coda_w8$ah <- labelled(HRS_ds_coda_w8$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_coda8, echo=FALSE}
vari <- HRS_ds_coda_w8$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w8, aes(x=factor(ah))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_coda8, echo=FALSE}
BeforeH <- table(HRS_ah[[2]], useNA = 'ifany')
AfterH <- table(HRS_ds_coda_w8$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)

#ggplot(NULL,aes(dat))+
#  geom_bar(data=HRS_ah,aes(x=factor(RAGENDER)),fill="red", position = "dodge")+
#  geom_bar(data=HRS_ds_hrs_w1,aes(x=factor(ah)),fill="steelblue", position = "dodge")

```

 
 

 
```{r importOPAL_coda8, echo=FALSE}
#opal.assign.data(o, 'HRS_ds_coda_w8', HRS_ds_coda_w8)
#opal.symbol_import(o,'HRS_ds_coda_w8', project='_Athlos_Harm_Dataset')
label(HRS_ds_coda_w8$ah) <- ds_label_all
ah <- HRS_ds_coda_w8
save(ah, file = "../RData/coda_w8/ah.RData")
rm(ah)

HRS_m_ds_coda_w8 <- HRS_ds_coda_w8
HRS_m_ds_coda_w8$ah <- car::recode(HRS_m_ds_coda_w8$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
opal.assign.data(o, 'HRS_m_ds_coda_w8', HRS_m_ds_coda_w8)
#opal.symbol_import(o,'HRS_m_ds_coda_w8', project='_Athlos_Harm_Dataset')
```




### Wave 9 

#### Study-specific variable description

* Name: `R9HIBPE`
* Label: `W9 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:

```{r assign_coda9, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-CODA-w9',
                         variables=list('R9HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_coda9, echo=FALSE}
vari <- HRS_ah$R9HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`


**R script:**

```{r harmo_coda9, echo=TRUE}
HRS_ds_coda_w9 <- tibble(id=HRS_ah$id)
HRS_ds_coda_w9$ah <- car::recode(HRS_ah[[2]], "NA=999")
HRS_ds_coda_w9$ah <- labelled(HRS_ds_coda_w9$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_coda9, echo=FALSE}
vari <- HRS_ds_coda_w9$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w9, aes(x=factor(ah))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_coda9, echo=FALSE}
BeforeH <- table(HRS_ah[[2]], useNA = 'ifany')
AfterH <- table(HRS_ds_coda_w9$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```

 
 

 
```{r importOPAL_coda9, echo=FALSE}
#opal.assign.data(o, 'HRS_ds_coda_w9', HRS_ds_coda_w9)
#opal.symbol_import(o,'HRS_ds_coda_w9', project='_Athlos_Harm_Dataset')
label(HRS_ds_coda_w9$ah) <- ds_label_all
ah <- HRS_ds_coda_w9
save(ah, file = "../RData/coda_w9/ah.RData")
rm(ah)

HRS_m_ds_coda_w9 <- HRS_ds_coda_w9
HRS_m_ds_coda_w9$ah <- car::recode(HRS_m_ds_coda_w9$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_coda_w9', HRS_m_ds_coda_w9)
#opal.symbol_import(o,'HRS_m_ds_coda_w9', project='_Athlos_Harm_Dataset')
```






### Wave 10 

#### Study-specific variable description


* Name: `R10HIBPE`
* Label: `W10 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:
```{r assign_coda10, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-CODA-w10',
                         variables=list('R10HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_coda10, echo=FALSE}
vari <- HRS_ah$R10HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_coda10, echo=TRUE}
HRS_ds_coda_w10 <- tibble(id=HRS_ah$id)
HRS_ds_coda_w10$ah <- car::recode(HRS_ah[[2]], "NA=999")
HRS_ds_coda_w10$ah <- labelled(HRS_ds_coda_w10$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_coda10, echo=FALSE}
vari <- HRS_ds_coda_w10$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w10, aes(x=factor(ah))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_coda10, echo=FALSE}
BeforeH <- table(HRS_ah[[2]], useNA = 'ifany')
AfterH <- table(HRS_ds_coda_w10$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```

 
 

 
```{r importOPAL_coda10, echo=FALSE}
#opal.assign.data(o, 'HRS_ds_coda_w10', HRS_ds_coda_w10)
#opal.symbol_import(o,'HRS_ds_coda_w10', project='_Athlos_Harm_Dataset')
label(HRS_ds_coda_w10$ah) <- ds_label_all
ah <- HRS_ds_coda_w10
save(ah, file = "../RData/coda_w10/ah.RData")
rm(ah)

HRS_m_ds_coda_w10 <- HRS_ds_coda_w10
HRS_m_ds_coda_w10$ah <- car::recode(HRS_m_ds_coda_w10$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_coda_w10', HRS_m_ds_coda_w10)
#opal.symbol_import(o,'HRS_m_ds_coda_w10', project='_Athlos_Harm_Dataset')
```






### Wave 11 

#### Study-specific variable description

* Name: `R11HIBPE`
* Label: `W11 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:

```{r assign_coda11, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-CODA-w11',
                         variables=list('R11HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_coda11, echo=FALSE}
vari <- HRS_ah$R11HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`


**R script:**

```{r harmo_coda11, echo=TRUE}
HRS_ds_coda_w11 <- tibble(id=HRS_ah$id)
HRS_ds_coda_w11$ah <- car::recode(HRS_ah[[2]], "NA=999")
HRS_ds_coda_w11$ah <- labelled(HRS_ds_coda_w11$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_coda11, echo=FALSE}
vari <- HRS_ds_coda_w11$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w11, aes(x=factor(ah))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_coda11, echo=FALSE}
BeforeH <- table(HRS_ah[[2]], useNA = 'ifany')
AfterH <- table(HRS_ds_coda_w11$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```

 
 

 
```{r importOPAL_coda11, echo=FALSE}
#opal.assign.data(o, 'HRS_ds_coda_w11', HRS_ds_coda_w11)
#opal.symbol_import(o,'HRS_ds_coda_w11', project='_Athlos_Harm_Dataset')
label(HRS_ds_coda_w11$ah) <- ds_label_all
ah <- HRS_ds_coda_w11
save(ah, file = "../RData/coda_w11/ah.RData")
rm(ah)

HRS_m_ds_coda_w11 <- HRS_ds_coda_w11
HRS_m_ds_coda_w11$ah <- car::recode(HRS_m_ds_coda_w11$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_coda_w11', HRS_m_ds_coda_w11)
#opal.symbol_import(o,'HRS_m_ds_coda_w11', project='_Athlos_Harm_Dataset')
```






## The War Baby (WB) sub-sample 

### Wave 4  

#### Study-specific variable description

* Name: `R4HIBPE`
* Label: `W4 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:

```{r assign_wb4, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-WB-w4',
                         variables=list('R4HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_wb4, echo=FALSE}
vari <- HRS_ah$R4HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_wb4, echo=TRUE}
HRS_ds_wb_w4 <- tibble(id=HRS_ah$id)
HRS_ds_wb_w4$ah <- car::recode(HRS_ah[[2]], "NA=999")
HRS_ds_wb_w4$ah <- labelled(HRS_ds_wb_w4$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_wb4, echo=FALSE}
vari <- HRS_ds_wb_w4$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w4, aes(x=factor(ah))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_wb4, echo=FALSE}
BeforeH <- table(HRS_ah[[2]], useNA = 'ifany')
AfterH <- table(HRS_ds_wb_w4$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```

 
 

 
```{r importOPAL_wb4, echo=FALSE}
#opal.assign.data(o, 'HRS_ds_wb_w4', HRS_ds_wb_w4)
#opal.symbol_import(o,'HRS_ds_wb_w4', project='_Athlos_Harm_Dataset')
label(HRS_ds_wb_w4$ah) <- ds_label_all
ah <- HRS_ds_wb_w4
save(ah, file = "../RData/wb_w4/ah.RData")
rm(ah)

HRS_m_ds_wb_w4 <- HRS_ds_wb_w4
HRS_m_ds_wb_w4$ah <- car::recode(HRS_m_ds_wb_w4$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w4', HRS_m_ds_wb_w4)
#opal.symbol_import(o,'HRS_m_ds_wb_w4', project='_Athlos_Harm_Dataset')
```






### Wave 5  

#### Study-specific variable description

* Name: `R5HIBPE`
* Label: `W5 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:

```{r assign_wb5, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-WB-w5',
                         variables=list('R5HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_wb5, echo=FALSE}
vari <- HRS_ah$R5HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_wb5, echo=TRUE}
HRS_ds_wb_w5 <- tibble(id=HRS_ah$id)
HRS_ds_wb_w5$ah <- car::recode(HRS_ah[[2]], "NA=999")
HRS_ds_wb_w5$ah <- labelled(HRS_ds_wb_w5$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_wb5, echo=FALSE}
vari <- HRS_ds_wb_w5$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w5, aes(x=factor(ah))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_wb5, echo=FALSE}
BeforeH <- table(HRS_ah[[2]], useNA = 'ifany')
AfterH <- table(HRS_ds_wb_w5$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```

 
 

 
```{r importOPAL_wb5, echo=FALSE}
#opal.assign.data(o, 'HRS_ds_wb_w5', HRS_ds_wb_w5)
#opal.symbol_import(o,'HRS_ds_wb_w5', project='_Athlos_Harm_Dataset')
label(HRS_ds_wb_w5$ah) <- ds_label_all
ah <- HRS_ds_wb_w5
save(ah, file = "../RData/wb_w5/ah.RData")
rm(ah)

HRS_m_ds_wb_w5 <- HRS_ds_wb_w5
HRS_m_ds_wb_w5$ah <- car::recode(HRS_m_ds_wb_w5$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w5', HRS_m_ds_wb_w5)
#opal.symbol_import(o,'HRS_m_ds_wb_w5', project='_Athlos_Harm_Dataset')
```





### Wave 6  

#### Study-specific variable description

* Name: `R6HIBPE`
* Label: `W6 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:

```{r assign_wb6, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-WB-w6',
                         variables=list('R6HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_wb6, echo=FALSE}
vari <- HRS_ah$R6HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`


**R script:**

```{r harmo_wb6, echo=TRUE}
HRS_ds_wb_w6 <- tibble(id=HRS_ah$id)
HRS_ds_wb_w6$ah <- car::recode(HRS_ah[[2]], "NA=999")
HRS_ds_wb_w6$ah <- labelled(HRS_ds_wb_w6$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_wb6, echo=FALSE}
vari <- HRS_ds_wb_w6$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w6, aes(x=factor(ah))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_wb6, echo=FALSE}
BeforeH <- table(HRS_ah[[2]], useNA = 'ifany')
AfterH <- table(HRS_ds_wb_w6$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)

#ggplot(NULL,aes(dat))+
#  geom_bar(data=HRS_ah,aes(x=factor(RAGENDER)),fill="red", position = "dodge")+
#  geom_bar(data=HRS_ds_hrs_w1,aes(x=factor(ah)),fill="steelblue", position = "dodge")

```

 
 

 
```{r importOPAL_wb6, echo=FALSE}
#opal.assign.data(o, 'HRS_ds_wb_w6', HRS_ds_wb_w6)
#opal.symbol_import(o,'HRS_ds_wb_w6', project='_Athlos_Harm_Dataset')
label(HRS_ds_wb_w6$ah) <- ds_label_all
ah <- HRS_ds_wb_w6
save(ah, file = "../RData/wb_w6/ah.RData")
rm(ah)

HRS_m_ds_wb_w6 <- HRS_ds_wb_w6
HRS_m_ds_wb_w6$ah <- car::recode(HRS_m_ds_wb_w6$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w6', HRS_m_ds_wb_w6)
#opal.symbol_import(o,'HRS_m_ds_wb_w6', project='_Athlos_Harm_Dataset')
```







### Wave 7  

#### Study-specific variable description

* Name: `R7HIBPE`
* Label: `W7 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:

```{r assign_wb7, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-WB-w7',
                         variables=list('R7HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_wb7, echo=FALSE}
vari <- HRS_ah$R7HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_wb7, echo=TRUE}
HRS_ds_wb_w7 <- tibble(id=HRS_ah$id)
HRS_ds_wb_w7$ah <- car::recode(HRS_ah[[2]], "NA=999")
HRS_ds_wb_w7$ah <- labelled(HRS_ds_wb_w7$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_wb7, echo=FALSE}
vari <- HRS_ds_wb_w7$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w7, aes(x=factor(ah))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_wb7, echo=FALSE}
BeforeH <- table(HRS_ah[[2]], useNA = 'ifany')
AfterH <- table(HRS_ds_wb_w7$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```

 
 

 
```{r importOPAL_wb7, echo=FALSE}
#opal.assign.data(o, 'HRS_ds_wb_w7', HRS_ds_wb_w7)
#opal.symbol_import(o,'HRS_ds_wb_w7', project='_Athlos_Harm_Dataset')
label(HRS_ds_wb_w7$ah) <- ds_label_all
ah <- HRS_ds_wb_w7
save(ah, file = "../RData/wb_w7/ah.RData")
rm(ah)

HRS_m_ds_wb_w7 <- HRS_ds_wb_w7
HRS_m_ds_wb_w7$ah <- car::recode(HRS_m_ds_wb_w7$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w7', HRS_m_ds_wb_w7)
#opal.symbol_import(o,'HRS_m_ds_wb_w7', project='_Athlos_Harm_Dataset')
```






### Wave 8  

#### Study-specific variable description

* Name: `R8HIBPE`
* Label: `W8 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:

```{r assign_wb8, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-WB-w8',
                         variables=list('R8HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_wb8, echo=FALSE}
vari <- HRS_ah$R8HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_wb8, echo=TRUE}
HRS_ds_wb_w8 <- tibble(id=HRS_ah$id)
HRS_ds_wb_w8$ah <- car::recode(HRS_ah[[2]], "NA=999")
HRS_ds_wb_w8$ah <- labelled(HRS_ds_wb_w8$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_wb8, echo=FALSE}
vari <- HRS_ds_wb_w8$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w8, aes(x=factor(ah))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_wb8, echo=FALSE}
BeforeH <- table(HRS_ah[[2]], useNA = 'ifany')
AfterH <- table(HRS_ds_wb_w8$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)

#ggplot(NULL,aes(dat))+
#  geom_bar(data=HRS_ah,aes(x=factor(RAGENDER)),fill="red", position = "dodge")+
#  geom_bar(data=HRS_ds_hrs_w1,aes(x=factor(ah)),fill="steelblue", position = "dodge")

```

 
 

 
```{r importOPAL_wb8, echo=FALSE}
#opal.assign.data(o, 'HRS_ds_wb_w8', HRS_ds_wb_w8)
#opal.symbol_import(o,'HRS_ds_wb_w8', project='_Athlos_Harm_Dataset')
label(HRS_ds_wb_w8$ah) <- ds_label_all
ah <- HRS_ds_wb_w8
save(ah, file = "../RData/wb_w8/ah.RData")
rm(ah)

HRS_m_ds_wb_w8 <- HRS_ds_wb_w8
HRS_m_ds_wb_w8$ah <- car::recode(HRS_m_ds_wb_w8$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w8', HRS_m_ds_wb_w8)
#opal.symbol_import(o,'HRS_m_ds_wb_w8', project='_Athlos_Harm_Dataset')
```





### Wave 9  

#### Study-specific variable description

* Name: `R9HIBPE`
* Label: `W9 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:

```{r assign_wb9, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-WB-w9',
                         variables=list('R9HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_wb9, echo=FALSE}
vari <- HRS_ah$R9HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_wb9, echo=TRUE}
HRS_ds_wb_w9 <- tibble(id=HRS_ah$id)
HRS_ds_wb_w9$ah <- car::recode(HRS_ah[[2]], "NA=999")
HRS_ds_wb_w9$ah <- labelled(HRS_ds_wb_w9$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_wb9, echo=FALSE}
vari <- HRS_ds_wb_w9$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w9, aes(x=factor(ah))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_wb9, echo=FALSE}
BeforeH <- table(HRS_ah[[2]], useNA = 'ifany')
AfterH <- table(HRS_ds_wb_w9$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```

 
 

 
```{r importOPAL_wb9, echo=FALSE}
#opal.assign.data(o, 'HRS_ds_wb_w9', HRS_ds_wb_w9)
#opal.symbol_import(o,'HRS_ds_wb_w9', project='_Athlos_Harm_Dataset')
label(HRS_ds_wb_w9$ah) <- ds_label_all
ah <- HRS_ds_wb_w9
save(ah, file = "../RData/wb_w9/ah.RData")
rm(ah)

HRS_m_ds_wb_w9 <- HRS_ds_wb_w9
HRS_m_ds_wb_w9$ah <- car::recode(HRS_m_ds_wb_w9$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w9', HRS_m_ds_wb_w9)
#opal.symbol_import(o,'HRS_m_ds_wb_w9', project='_Athlos_Harm_Dataset')
```






### Wave 10  

#### Study-specific variable description

* Name: `R10HIBPE`
* Label: `W10 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:

```{r assign_wb10, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-WB-w10',
                         variables=list('R10HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_wb10, echo=FALSE}
vari <- HRS_ah$R10HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_wb10, echo=TRUE}
HRS_ds_wb_w10 <- tibble(id=HRS_ah$id)
HRS_ds_wb_w10$ah <- car::recode(HRS_ah[[2]], "NA=999")
HRS_ds_wb_w10$ah <- labelled(HRS_ds_wb_w10$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_wb10, echo=FALSE}
vari <- HRS_ds_wb_w10$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w10, aes(x=factor(ah))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_wb10, echo=FALSE}
BeforeH <- table(HRS_ah[[2]], useNA = 'ifany')
AfterH <- table(HRS_ds_wb_w10$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```

 
 

 
```{r importOPAL_wb10, echo=FALSE}
#opal.assign.data(o, 'HRS_ds_wb_w10', HRS_ds_wb_w10)
#opal.symbol_import(o,'HRS_ds_wb_w10', project='_Athlos_Harm_Dataset')
label(HRS_ds_wb_w10$ah) <- ds_label_all
ah <- HRS_ds_wb_w10
save(ah, file = "../RData/wb_w10/ah.RData")
rm(ah)

HRS_m_ds_wb_w10 <- HRS_ds_wb_w10
HRS_m_ds_wb_w10$ah <- car::recode(HRS_m_ds_wb_w10$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w10', HRS_m_ds_wb_w10)
#opal.symbol_import(o,'HRS_m_ds_wb_w10', project='_Athlos_Harm_Dataset')
```





### Wave 11  

#### Study-specific variable description

* Name: `R11HIBPE`
* Label: `W11 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:

```{r assign_wb11, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-WB-w11',
                         variables=list('R11HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_wb11, echo=FALSE}
vari <- HRS_ah$R11HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_wb11, echo=TRUE}
HRS_ds_wb_w11 <- tibble(id=HRS_ah$id)
HRS_ds_wb_w11$ah <- car::recode(HRS_ah[[2]], "NA=999")
HRS_ds_wb_w11$ah <- labelled(HRS_ds_wb_w11$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_wb11, echo=FALSE}
vari <- HRS_ds_wb_w11$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w11, aes(x=factor(ah))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_wb11, echo=FALSE}
BeforeH <- table(HRS_ah[[2]], useNA = 'ifany')
AfterH <- table(HRS_ds_wb_w11$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```

 
 

 
```{r importOPAL_wb11, echo=FALSE}
#opal.assign.data(o, 'HRS_ds_wb_w11', HRS_ds_wb_w11)
#opal.symbol_import(o,'HRS_ds_wb_w11', project='_Athlos_Harm_Dataset')
label(HRS_ds_wb_w11$ah) <- ds_label_all
ah <- HRS_ds_wb_w11
save(ah, file = "../RData/wb_w11/ah.RData")
rm(ah)

HRS_m_ds_wb_w11 <- HRS_ds_wb_w11
HRS_m_ds_wb_w11$ah <- car::recode(HRS_m_ds_wb_w11$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w11', HRS_m_ds_wb_w11)
#opal.symbol_import(o,'HRS_m_ds_wb_w11', project='_Athlos_Harm_Dataset')
```





## The Early Baby Boomer (EBB) sub-sample

### Wave 7  

#### Study-specific variable description

* Name: `R7HIBPE`
* Label: `W7 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:

```{r assign_ebb7, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-EBB-w7',
                         variables=list('R7HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_ebb7, echo=FALSE}
vari <- HRS_ah$R7HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ebb7, echo=TRUE}
HRS_ds_ebb_w7 <- tibble(id=HRS_ah$id)
HRS_ds_ebb_w7$ah <- car::recode(HRS_ah[[2]], "NA=999")
HRS_ds_ebb_w7$ah <- labelled(HRS_ds_ebb_w7$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_ebb7, echo=FALSE}
vari <- HRS_ds_ebb_w7$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w7, aes(x=factor(ah))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_ebb7, echo=FALSE}
BeforeH <- table(HRS_ah[[2]], useNA = 'ifany')
AfterH <- table(HRS_ds_ebb_w7$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```

 
 

 
```{r importOPAL_ebb7, echo=FALSE}
#opal.assign.data(o, 'HRS_ds_ebb_w7', HRS_ds_ebb_w7)
#opal.symbol_import(o,'HRS_ds_ebb_w7', project='_Athlos_Harm_Dataset')
label(HRS_ds_ebb_w7$ah) <- ds_label_all
ah <- HRS_ds_ebb_w7
save(ah, file = "../RData/ebb_w7/ah.RData")
rm(ah)

HRS_m_ds_ebb_w7 <- HRS_ds_ebb_w7
HRS_m_ds_ebb_w7$ah <- car::recode(HRS_m_ds_ebb_w7$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ebb_w7', HRS_m_ds_ebb_w7)
#opal.symbol_import(o,'HRS_m_ds_ebb_w7', project='_Athlos_Harm_Dataset')
```





### Wave 8  

#### Study-specific variable description

* Name: `R8HIBPE`
* Label: `W8 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:

```{r assign_ebb8, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-EBB-w8',
                         variables=list('R8HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_ebb8, echo=FALSE}
vari <- HRS_ah$R8HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`



**R script:**

```{r harmo_ebb8, echo=TRUE}
HRS_ds_ebb_w8 <- tibble(id=HRS_ah$id)
HRS_ds_ebb_w8$ah <- car::recode(HRS_ah[[2]], "NA=999")
HRS_ds_ebb_w8$ah <- labelled(HRS_ds_ebb_w8$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_ebb8, echo=FALSE}
vari <- HRS_ds_ebb_w8$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w8, aes(x=factor(ah))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_ebb8, echo=FALSE}
BeforeH <- table(HRS_ah[[2]], useNA = 'ifany')
AfterH <- table(HRS_ds_ebb_w8$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)

```

 
 

 
```{r importOPAL_ebb8, echo=FALSE}
#opal.assign.data(o, 'HRS_ds_ebb_w8', HRS_ds_ebb_w8)
#opal.symbol_import(o,'HRS_ds_ebb_w8', project='_Athlos_Harm_Dataset')
label(HRS_ds_ebb_w8$ah) <- ds_label_all
ah <- HRS_ds_ebb_w8
save(ah, file = "../RData/ebb_w8/ah.RData")
rm(ah)

HRS_m_ds_ebb_w8 <- HRS_ds_ebb_w8
HRS_m_ds_ebb_w8$ah <- car::recode(HRS_m_ds_ebb_w8$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ebb_w8', HRS_m_ds_ebb_w8)
#opal.symbol_import(o,'HRS_m_ds_ebb_w8', project='_Athlos_Harm_Dataset')
```





### Wave 9  

#### Study-specific variable description

* Name: `R9HIBPE`
* Label: `W9 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:

```{r assign_ebb9, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-EBB-w9',
                         variables=list('R9HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_ebb9, echo=FALSE}
vari <- HRS_ah$R9HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`


**R script:**

```{r harmo_ebb9, echo=TRUE}
HRS_ds_ebb_w9 <- tibble(id=HRS_ah$id)
HRS_ds_ebb_w9$ah <- car::recode(HRS_ah[[2]], "NA=999")
HRS_ds_ebb_w9$ah <- labelled(HRS_ds_ebb_w9$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_ebb9, echo=FALSE}
vari <- HRS_ds_ebb_w9$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w9, aes(x=factor(ah))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_ebb9, echo=FALSE}
BeforeH <- table(HRS_ah[[2]], useNA = 'ifany')
AfterH <- table(HRS_ds_ebb_w9$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)
```

 
 

 
```{r importOPAL_ebb9, echo=FALSE}
#opal.assign.data(o, 'HRS_ds_ebb_w9', HRS_ds_ebb_w9)
#opal.symbol_import(o,'HRS_ds_ebb_w9', project='_Athlos_Harm_Dataset')
label(HRS_ds_ebb_w9$ah) <- ds_label_all
ah <- HRS_ds_ebb_w9
save(ah, file = "../RData/ebb_w9/ah.RData")
rm(ah)

HRS_m_ds_ebb_w9 <- HRS_ds_ebb_w9
HRS_m_ds_ebb_w9$ah <- car::recode(HRS_m_ds_ebb_w9$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ebb_w9', HRS_m_ds_ebb_w9)
#opal.symbol_import(o,'HRS_m_ds_ebb_w9', project='_Athlos_Harm_Dataset')
```




### Wave 10  

#### Study-specific variable description

* Name: `R10HIBPE`
* Label: `W10 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:

```{r assign_ebb10, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-EBB-w10',
                         variables=list('R10HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_ebb10, echo=FALSE}
vari <- HRS_ah$R10HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ebb10, echo=TRUE}
HRS_ds_ebb_w10 <- tibble(id=HRS_ah$id)
HRS_ds_ebb_w10$ah <- car::recode(HRS_ah[[2]], "NA=999")
HRS_ds_ebb_w10$ah <- labelled(HRS_ds_ebb_w10$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_ebb10, echo=FALSE}
vari <- HRS_ds_ebb_w10$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w10, aes(x=factor(ah))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_ebb10, echo=FALSE}
BeforeH <- table(HRS_ah[[2]], useNA = 'ifany')
AfterH <- table(HRS_ds_ebb_w10$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)

#ggplot(NULL,aes(dat))+
#  geom_bar(data=HRS_ah,aes(x=factor(RAGENDER)),fill="red", position = "dodge")+
#  geom_bar(data=HRS_ds_hrs_w1,aes(x=factor(ah)),fill="steelblue", position = "dodge")

```

 
 

 
```{r importOPAL_ebb10, echo=FALSE}
#opal.assign.data(o, 'HRS_ds_ebb_w10', HRS_ds_ebb_w10)
#opal.symbol_import(o,'HRS_ds_ebb_w10', project='_Athlos_Harm_Dataset')
label(HRS_ds_ebb_w10$ah) <- ds_label_all
ah <- HRS_ds_ebb_w10
save(ah, file = "../RData/ebb_w10/ah.RData")
rm(ah)

HRS_m_ds_ebb_w10 <- HRS_ds_ebb_w10
HRS_m_ds_ebb_w10$ah <- car::recode(HRS_m_ds_ebb_w10$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ebb_w10', HRS_m_ds_ebb_w10)
#opal.symbol_import(o,'HRS_m_ds_ebb_w10', project='_Athlos_Harm_Dataset')
```




### Wave 11  

#### Study-specific variable description

* Name: `R11HIBPE`
* Label: `W11 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:

```{r assign_ebb11, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-EBB-w11',
                         variables=list('R11HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_ebb11, echo=FALSE}
vari <- HRS_ah$R11HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ebb11, echo=TRUE}
HRS_ds_ebb_w11 <- tibble(id=HRS_ah$id)
HRS_ds_ebb_w11$ah <- car::recode(HRS_ah[[2]], "NA=999")
HRS_ds_ebb_w11$ah <- labelled(HRS_ds_ebb_w11$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_ebb11, echo=FALSE}
vari <- HRS_ds_ebb_w11$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w11, aes(x=factor(ah))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_ebb11, echo=FALSE}
BeforeH <- table(HRS_ah[[2]], useNA = 'ifany')
AfterH <- table(HRS_ds_ebb_w11$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)

#ggplot(NULL,aes(dat))+
#  geom_bar(data=HRS_ah,aes(x=factor(RAGENDER)),fill="red", position = "dodge")+
#  geom_bar(data=HRS_ds_hrs_w1,aes(x=factor(ah)),fill="steelblue", position = "dodge")

```

 
 

 
```{r importOPAL_ebb11, echo=FALSE}
#opal.assign.data(o, 'HRS_ds_ebb_w11', HRS_ds_ebb_w11)
#opal.symbol_import(o,'HRS_ds_ebb_w11', project='_Athlos_Harm_Dataset')
label(HRS_ds_ebb_w11$ah) <- ds_label_all
ah <- HRS_ds_ebb_w11
save(ah, file = "../RData/ebb_w11/ah.RData")
rm(ah)

HRS_m_ds_ebb_w11 <- HRS_ds_ebb_w11
HRS_m_ds_ebb_w11$ah <- car::recode(HRS_m_ds_ebb_w11$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ebb_w11', HRS_m_ds_ebb_w11)
#opal.symbol_import(o,'HRS_m_ds_ebb_w11', project='_Athlos_Harm_Dataset')
```




## The Mid Baby Boomer (MBB) sub-sample

### Wave 10  

#### Study-specific variable description

* Name: `R10HIBPE`
* Label: `W10 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:

```{r assign_mbb10, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-MBB-w10',
                         variables=list('R10HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_mbb10, echo=FALSE}
vari <- HRS_ah$R10HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_mbb10, echo=TRUE}
HRS_ds_mbb_w10 <- tibble(id=HRS_ah$id)
HRS_ds_mbb_w10$ah <- car::recode(HRS_ah[[2]], "NA=999")
HRS_ds_mbb_w10$ah <- labelled(HRS_ds_mbb_w10$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_mbb10, echo=FALSE}
vari <- HRS_ds_mbb_w10$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_mbb_w10, aes(x=factor(ah))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_mbb10, echo=FALSE}
BeforeH <- table(HRS_ah[[2]], useNA = 'ifany')
AfterH <- table(HRS_ds_mbb_w10$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)


#ggplot(NULL,aes(dat))+
#  geom_bar(data=HRS_ah,aes(x=factor(RAGENDER)),fill="red", position = "dodge")+
#  geom_bar(data=HRS_ds_hrs_w1,aes(x=factor(ah)),fill="steelblue", position = "dodge")

```

 
 

 
```{r importOPAL_mbb10, echo=FALSE}
#opal.assign.data(o, 'HRS_ds_mbb_w10', HRS_ds_mbb_w10)
#opal.symbol_import(o,'HRS_ds_mbb_w10', project='_Athlos_Harm_Dataset')
label(HRS_ds_mbb_w10$ah) <- ds_label_all
ah <- HRS_ds_mbb_w10
save(ah, file = "../RData/mbb_w10/ah.RData")
rm(ah)

HRS_m_ds_mbb_w10 <- HRS_ds_mbb_w10
HRS_m_ds_mbb_w10$ah <- car::recode(HRS_m_ds_mbb_w10$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_mbb_w10', HRS_m_ds_mbb_w10)
#opal.symbol_import(o,'HRS_m_ds_mbb_w10', project='_Athlos_Harm_Dataset')
```




### Wave 11  

#### Study-specific variable description

* Name: `R11HIBPE`
* Label: `W11 R ever had high blood pressure`
* Categories: 
    + `0 = no`
    + `1 = yes`
* Description:

```{r assign_mbb11, echo=FALSE}
opal.assign.table.tibble(o, 'HRS_ah','HRS.HRS-MBB-w11',
                         variables=list('R11HIBPE'), missings = TRUE)
HRS_ah <- opal.execute(o,'HRS_ah')
```

```{r local_mbb11, echo=FALSE}
vari <- HRS_ah$R11HIBPE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ah, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_mbb11, echo=TRUE}
HRS_ds_mbb_w11 <- tibble(id=HRS_ah$id)
HRS_ds_mbb_w11$ah <- car::recode(HRS_ah[[2]], "NA=999")
HRS_ds_mbb_w11$ah <- labelled(HRS_ds_mbb_w11$ah, labels = c("no hypertension"=0, "hypertension"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript_mbb11, echo=FALSE}
vari <- HRS_ds_mbb_w11$ah
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_mbb_w11, aes(x=factor(ah))) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_mbb11, echo=FALSE}
BeforeH <- table(HRS_ah[[2]], useNA = 'ifany')
AfterH <- table(HRS_ds_mbb_w11$ah)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1", "NA->999")
kable(C)

#ggplot(NULL,aes(dat))+
#  geom_bar(data=HRS_ah,aes(x=factor(RAGENDER)),fill="red", position = "dodge")+
#  geom_bar(data=HRS_ds_hrs_w1,aes(x=factor(ah)),fill="steelblue", position = "dodge")

```

 
 

 
```{r importOPAL_mbb11, echo=FALSE}
#opal.assign.data(o, 'HRS_ds_mbb_w11', HRS_ds_mbb_w11)
#opal.symbol_import(o,'HRS_ds_mbb_w11', project='_Athlos_Harm_Dataset')
label(HRS_ds_mbb_w11$ah) <- ds_label_all
ah <- HRS_ds_mbb_w11
save(ah, file = "../RData/mbb_w11/ah.RData")
rm(ah)

HRS_m_ds_mbb_w11 <- HRS_ds_mbb_w11
HRS_m_ds_mbb_w11$ah <- car::recode(HRS_m_ds_mbb_w11$ah, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_mbb_w11', HRS_m_ds_mbb_w11)
#opal.symbol_import(o,'HRS_m_ds_mbb_w11', project='_Athlos_Harm_Dataset')
```


# Quality estimation

No comments.

```{r closeRsession, echo=FALSE} 
opal.logout(o)
```