---
title: "Height"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ############################################################################# --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ############################################################################# --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `height`
* Variable label: `height of the participant`
* Variable description: `Anthropometric measure for height should be measured in centimeters`
* Domain: `Physical measures`
* Value type: `continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process




### HRS - Wave 1 

The study-specific variable elected to be harmonised is:

* Name: `R1HEIGHT`
* Label: `W1 Height in meters`
* Type of variable: `countinous`


```{r assign_hrs1, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w1_heig','HRS.HRS-HRS-w1',
                         variables=list('R1HEIGHT'), missings = TRUE)
```

```{r local_hrs1, echo=F}
HRS_hrs_w1_heig <- opal.execute(o,'HRS_hrs_w1_heig')
Continuous_summary(var = HRS_hrs_w1_heig$R1HEIGHT, missing_values = NA)
ggplot(HRS_hrs_w1_heig, aes(R1HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_hrs1}
HRS_ds_hrs_w1 <- tibble(id=HRS_hrs_w1_heig$id)
HRS_ds_hrs_w1$height <- car::recode(HRS_hrs_w1_heig$R1HEIGHT*100, "NA=999")
HRS_ds_hrs_w1$height <- labelled(HRS_ds_hrs_w1$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs1, echo=F}
Continuous_summary(var = HRS_ds_hrs_w1$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w1, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(90,220) 
```

#### Validation
There is an unusual value that is lower than 1m:
```{r crosstabulation_hrs1, echo=F}
HRS_hrs_w1_heig[which(HRS_hrs_w1_heig$R1HEIGHT<1),]
```





```{r importOPAL_hrs1, echo=F}
#val_labels(HRS_ds_hrs_w1) <- NULL
#opal.assign.data(o, 'HRS_ds_hrs_w1', HRS_ds_hrs_w1)
#opal.symbol_import(o,'HRS_ds_hrs_w1', project='_Athlos_Harm_Dataset')
height <- HRS_ds_hrs_w1
save(height, file = "../RData/hrs_w1/height.RData")
rm(height)
```







### HRS - Wave 2 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R2HEIGHT`
* Label: `W2 Height in meters`
* Type of variable: `countinous`


```{r assign_hrs2, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w2_heig','HRS.HRS-HRS-w2',
                         variables=list('R2HEIGHT'), missings = TRUE)
```

```{r local_hrs2, echo=F}
HRS_hrs_w2_heig <- opal.execute(o,'HRS_hrs_w2_heig')
Continuous_summary(var = HRS_hrs_w2_heig$R2HEIGHT, missing_values = NA)
ggplot(HRS_hrs_w2_heig, aes(R2HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_hrs2}
HRS_ds_hrs_w2 <- tibble(id=HRS_hrs_w2_heig$id)
HRS_ds_hrs_w2$height <- car::recode(HRS_hrs_w2_heig$R2HEIGHT*100, "NA=999")
HRS_ds_hrs_w2$height <- labelled(HRS_ds_hrs_w2$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs2, echo=F}
Continuous_summary(var = HRS_ds_hrs_w2$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w2, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(90,220) 
```

#### Validation
There is an unusual value that is lower than 1m:
```{r crosstabulation_hrs2, echo=F}
HRS_hrs_w2_heig[which(HRS_hrs_w2_heig$R2HEIGHT<1),]
```





```{r importOPAL_hrs2, echo=F}
#val_labels(HRS_ds_hrs_w2) <- NULL
#opal.assign.data(o, 'HRS_ds_hrs_w2', HRS_ds_hrs_w2)
#opal.symbol_import(o,'HRS_ds_hrs_w2', project='_Athlos_Harm_Dataset')
height <- HRS_ds_hrs_w2
save(height, file = "../RData/hrs_w2/height.RData")
rm(height)
```







### HRS - Wave 3 

#### Study-specific variables


The study-specific variable elected to be harmonised is:

* Name: `R3HEIGHT`
* Label: `W3 Height in meters`
* Type of variable: `countinous`


```{r assign_hrs3, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w3_heig','HRS.HRS-HRS-w3',
                         variables=list('R3HEIGHT'), missings = TRUE)
```

```{r local_hrs3, echo=F}
HRS_hrs_w3_heig <- opal.execute(o,'HRS_hrs_w3_heig')
Continuous_summary(var = HRS_hrs_w3_heig$R3HEIGHT, missing_values = NA)
ggplot(HRS_hrs_w3_heig, aes(R3HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_hrs3}
HRS_ds_hrs_w3 <- tibble(id=HRS_hrs_w3_heig$id)
HRS_ds_hrs_w3$height <- car::recode(HRS_hrs_w3_heig$R3HEIGHT*100, "NA=999")
HRS_ds_hrs_w3$height <- labelled(HRS_ds_hrs_w3$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs3, echo=F}
Continuous_summary(var = HRS_ds_hrs_w3$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w3, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,230) 
```

#### Validation
```{r crosstabulation_hrs3, echo=F}

```





```{r importOPAL_hrs3, echo=F}
#val_labels(HRS_ds_hrs_w3) <- NULL
#opal.assign.data(o, 'HRS_ds_hrs_w3', HRS_ds_hrs_w3)
#opal.symbol_import(o,'HRS_ds_hrs_w3', project='_Athlos_Harm_Dataset')
height <- HRS_ds_hrs_w3
save(height, file = "../RData/hrs_w3/height.RData")
rm(height)
```







### HRS - Wave 4 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R4HEIGHT`
* Label: `W4 Height in meters`
* Type of variable: `countinous`


```{r assign_hrs4, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w4_heig','HRS.HRS-HRS-w4',
                         variables=list('R4HEIGHT'), missings = TRUE)
```

```{r local_hrs4, echo=F}
HRS_hrs_w4_heig <- opal.execute(o,'HRS_hrs_w4_heig')
Continuous_summary(var = HRS_hrs_w4_heig$R4HEIGHT, missing_values = NA)
ggplot(HRS_hrs_w4_heig, aes(R4HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_hrs4}
HRS_ds_hrs_w4 <- tibble(id=HRS_hrs_w4_heig$id)
HRS_ds_hrs_w4$height <- car::recode(HRS_hrs_w4_heig$R4HEIGHT*100, "NA=999")
HRS_ds_hrs_w4$height <- labelled(HRS_ds_hrs_w4$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs4, echo=F}
Continuous_summary(var = HRS_ds_hrs_w4$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w4, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,230) 
```

#### Validation
```{r crosstabulation_hrs4, echo=F}

```





```{r importOPAL_hrs4, echo=F}
#val_labels(HRS_ds_hrs_w4) <- NULL
#opal.assign.data(o, 'HRS_ds_hrs_w4', HRS_ds_hrs_w4)
#opal.symbol_import(o,'HRS_ds_hrs_w4', project='_Athlos_Harm_Dataset')
height <- HRS_ds_hrs_w4
save(height, file = "../RData/hrs_w4/height.RData")
rm(height)
```








### HRS - Wave 5

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R5HEIGHT`
* Label: `W5 Height in meters`
* Type of variable: `countinous`

```{r assign_hrs5, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w5_heig','HRS.HRS-HRS-w5',
                         variables=list('R5HEIGHT'), missings = TRUE)
```

```{r local_hrs5, echo=F}
HRS_hrs_w5_heig <- opal.execute(o,'HRS_hrs_w5_heig')
Continuous_summary(var = HRS_hrs_w5_heig$R5HEIGHT, missing_values = NA)
ggplot(HRS_hrs_w5_heig, aes(R5HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_hrs5}
HRS_ds_hrs_w5 <- tibble(id=HRS_hrs_w5_heig$id)
HRS_ds_hrs_w5$height <- car::recode(HRS_hrs_w5_heig$R5HEIGHT*100, "NA=999")
HRS_ds_hrs_w5$height <- labelled(HRS_ds_hrs_w5$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs5, echo=F}
Continuous_summary(var = HRS_ds_hrs_w5$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w5, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,230)
```

#### Validation
```{r crosstabulation_hrs5, echo=F}

```





```{r importOPAL_hrs5, echo=F}
#val_labels(HRS_ds_hrs_w5) <- NULL
#opal.assign.data(o, 'HRS_ds_hrs_w5', HRS_ds_hrs_w5)
#opal.symbol_import(o,'HRS_ds_hrs_w5', project='_Athlos_Harm_Dataset')
height <- HRS_ds_hrs_w5
save(height, file = "../RData/hrs_w5/height.RData")
rm(height)
```






### HRS - Wave 6

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R6HEIGHT`
* Label: `W6 Height in meters`
* Type of variable: `countinous`

```{r assign_hrs6, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w6_heig','HRS.HRS-HRS-w6',
                         variables=list('R6HEIGHT'), missings = TRUE)
```

```{r local_hrs6, echo=F}
HRS_hrs_w6_heig <- opal.execute(o,'HRS_hrs_w6_heig')
Continuous_summary(var = HRS_hrs_w6_heig$R6HEIGHT, missing_values = NA)
ggplot(HRS_hrs_w6_heig, aes(R6HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_hrs6}
HRS_ds_hrs_w6 <- tibble(id=HRS_hrs_w6_heig$id)
HRS_ds_hrs_w6$height <- car::recode(HRS_hrs_w6_heig$R6HEIGHT*100, "NA=999")
HRS_ds_hrs_w6$height <- labelled(HRS_ds_hrs_w6$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs6, echo=F}
Continuous_summary(var = HRS_ds_hrs_w6$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w6, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,230)
```

#### Validation
```{r crosstabulation_hrs6, echo=F}
```





```{r importOPAL_hrs6, echo=F}
#val_labels(HRS_ds_hrs_w6) <- NULL
#opal.assign.data(o, 'HRS_ds_hrs_w6', HRS_ds_hrs_w6)
#opal.symbol_import(o,'HRS_ds_hrs_w6', project='_Athlos_Harm_Dataset')
height <- HRS_ds_hrs_w6
save(height, file = "../RData/hrs_w6/height.RData")
rm(height)
```








### HRS - Wave 7

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R7HEIGHT`
* Label: `W7 Height in meters`
* Type of variable: `countinous`


```{r assign_hrs7, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w7_heig','HRS.HRS-HRS-w7',
                         variables=list('R7HEIGHT'), missings = TRUE)
```

```{r local_hrs7, echo=F}
HRS_hrs_w7_heig <- opal.execute(o,'HRS_hrs_w7_heig')
Continuous_summary(var = HRS_hrs_w7_heig$R7HEIGHT, missing_values = NA)
ggplot(HRS_hrs_w7_heig, aes(R7HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_hrs7}
HRS_ds_hrs_w7 <- tibble(id=HRS_hrs_w7_heig$id)
HRS_ds_hrs_w7$height <- car::recode(HRS_hrs_w7_heig$R7HEIGHT*100, "NA=999")
HRS_ds_hrs_w7$height <- labelled(HRS_ds_hrs_w7$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs7, echo=F}
Continuous_summary(var = HRS_ds_hrs_w7$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w7, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,230)
```

#### Validation
```{r crosstabulation_hrs7, echo=F}
```





```{r importOPAL_hrs7, echo=F}
#val_labels(HRS_ds_hrs_w7) <- NULL
#opal.assign.data(o, 'HRS_ds_hrs_w7', HRS_ds_hrs_w7)
#opal.symbol_import(o,'HRS_ds_hrs_w7', project='_Athlos_Harm_Dataset')
height <- HRS_ds_hrs_w7
save(height, file = "../RData/hrs_w7/height.RData")
rm(height)
```








### HRS - Wave 8

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R8HEIGHT`
* Label: `W8 Height in meters`
* Type of variable: `countinous`


```{r assign_hrs8, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w8_heig','HRS.HRS-HRS-w8',
                         variables=list('R8HEIGHT'), missings = TRUE)
```

```{r local_hrs8, echo=F}
HRS_hrs_w8_heig <- opal.execute(o,'HRS_hrs_w8_heig')
Continuous_summary(var = HRS_hrs_w8_heig$R8HEIGHT, missing_values = NA)
ggplot(HRS_hrs_w8_heig, aes(R8HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_hrs8}
HRS_ds_hrs_w8 <- tibble(id=HRS_hrs_w8_heig$id)
HRS_ds_hrs_w8$height <- car::recode(HRS_hrs_w8_heig$R8HEIGHT*100, "NA=999")
HRS_ds_hrs_w8$height <- labelled(HRS_ds_hrs_w8$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs8, echo=F}
Continuous_summary(var = HRS_ds_hrs_w8$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w8, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,230)
```

#### Validation
```{r crosstabulation_hrs8, echo=F}

```





```{r importOPAL_hrs8, echo=F}
#val_labels(HRS_ds_hrs_w8) <- NULL
#opal.assign.data(o, 'HRS_ds_hrs_w8', HRS_ds_hrs_w8)
#opal.symbol_import(o,'HRS_ds_hrs_w8', project='_Athlos_Harm_Dataset')
height <- HRS_ds_hrs_w8
save(height, file = "../RData/hrs_w8/height.RData")
rm(height)
```








### HRS - Wave 9

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R9HEIGHT`
* Label: `W9 Height in meters`
* Type of variable: `countinous`


```{r assign_hrs9, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w9_heig','HRS.HRS-HRS-w9',
                         variables=list('R9HEIGHT'), missings = TRUE)
```

```{r local_hrs9, echo=F}
HRS_hrs_w9_heig <- opal.execute(o,'HRS_hrs_w9_heig')
Continuous_summary(var = HRS_hrs_w9_heig$R9HEIGHT, missing_values = NA)
ggplot(HRS_hrs_w9_heig, aes(R9HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`


**R script:**

```{r harmo_hrs9}
HRS_ds_hrs_w9 <- tibble(id=HRS_hrs_w9_heig$id)
HRS_ds_hrs_w9$height <- car::recode(HRS_hrs_w9_heig$R9HEIGHT*100, "NA=999")
HRS_ds_hrs_w9$height <- labelled(HRS_ds_hrs_w9$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs9, echo=F}
Continuous_summary(var = HRS_ds_hrs_w9$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w9, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,230)
```

#### Validation
```{r crosstabulation_hrs9, echo=F}

```





```{r importOPAL_hrs9, echo=F}
#val_labels(HRS_ds_hrs_w9) <- NULL
#opal.assign.data(o, 'HRS_ds_hrs_w9', HRS_ds_hrs_w9)
#opal.symbol_import(o,'HRS_ds_hrs_w9', project='_Athlos_Harm_Dataset')
height <- HRS_ds_hrs_w9
save(height, file = "../RData/hrs_w9/height.RData")
rm(height)
```







### HRS - Wave 10

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R10HEIGHT`
* Label: `W10 Height in meters`
* Type of variable: `countinous`


```{r assign_hrs10, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w10_heig','HRS.HRS-HRS-w10',
                         variables=list('R10HEIGHT'), missings = TRUE)
```

```{r local_hrs10, echo=F}
HRS_hrs_w10_heig <- opal.execute(o,'HRS_hrs_w10_heig')
Continuous_summary(var = HRS_hrs_w10_heig$R10HEIGHT, missing_values = NA)
ggplot(HRS_hrs_w10_heig, aes(R10HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_hrs10}
HRS_ds_hrs_w10 <- tibble(id=HRS_hrs_w10_heig$id)
HRS_ds_hrs_w10$height <- car::recode(HRS_hrs_w10_heig$R10HEIGHT*100, "NA=999")
HRS_ds_hrs_w10$height <- labelled(HRS_ds_hrs_w10$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs10, echo=F}
Continuous_summary(var = HRS_ds_hrs_w10$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w10, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,240)
```

#### Validation
```{r crosstabulation_hrs10, echo=F}

```





```{r importOPAL_hrs10, echo=F}
#val_labels(HRS_ds_hrs_w10) <- NULL
#opal.assign.data(o, 'HRS_ds_hrs_w10', HRS_ds_hrs_w10)
#opal.symbol_import(o,'HRS_ds_hrs_w10', project='_Athlos_Harm_Dataset')
height <- HRS_ds_hrs_w10
save(height, file = "../RData/hrs_w10/height.RData")
rm(height)
```







### HRS - Wave 11

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R11HEIGHT`
* Label: `W11 Height in meters`
* Type of variable: `countinous`

```{r assign_hrs11, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w11_heig','HRS.HRS-HRS-w11',
                         variables=list('R11HEIGHT'), missings = TRUE)
```

```{r local_hrs11, echo=F}
HRS_hrs_w11_heig <- opal.execute(o,'HRS_hrs_w11_heig')
Continuous_summary(var = HRS_hrs_w11_heig$R11HEIGHT, missing_values = NA)
ggplot(HRS_hrs_w11_heig, aes(R11HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_hrs11}
HRS_ds_hrs_w11 <- tibble(id=HRS_hrs_w11_heig$id)
HRS_ds_hrs_w11$height <- car::recode(HRS_hrs_w11_heig$R11HEIGHT*100, "NA=999")
HRS_ds_hrs_w11$height <- labelled(HRS_ds_hrs_w11$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs11, echo=F}
Continuous_summary(var = HRS_ds_hrs_w11$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w11, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,230)
```

#### Validation
```{r crosstabulation_hrs11, echo=F}

```





```{r importOPAL_hrs11, echo=F}
#val_labels(HRS_ds_hrs_w11) <- NULL
#opal.assign.data(o, 'HRS_ds_hrs_w11', HRS_ds_hrs_w11)
#opal.symbol_import(o,'HRS_ds_hrs_w11', project='_Athlos_Harm_Dataset')
height <- HRS_ds_hrs_w11
save(height, file = "../RData/hrs_w11/height.RData")
rm(height)
```








### AHEAD - Wave 2 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R2HEIGHT`
* Label: `W2 Height in meters`
* Type of variable: `countinous`


```{r assign_ahead2, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w2_heig','HRS.HRS-AHEAD-w2',
                         variables=list('R2HEIGHT'), missings = TRUE)
```

```{r local_ahead2, echo=F}
HRS_ahead_w2_heig <- opal.execute(o,'HRS_ahead_w2_heig')
Continuous_summary(var = HRS_ahead_w2_heig$R2HEIGHT, missing_values = NA)
ggplot(HRS_ahead_w2_heig, aes(R2HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_ahead2}
HRS_ds_ahead_w2 <- tibble(id=HRS_ahead_w2_heig$id)
HRS_ds_ahead_w2$height <- car::recode(HRS_ahead_w2_heig$R2HEIGHT*100, "NA=999")
HRS_ds_ahead_w2$height <- labelled(HRS_ds_ahead_w2$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead2, echo=F}
Continuous_summary(var = HRS_ds_ahead_w2$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w2, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(90,210)
```

#### Validation
There is an unusual value that is lower than 1m:
```{r crosstabulation_ahead2, echo=F}
HRS_ahead_w2_heig[which(HRS_ahead_w2_heig$R2HEIGHT<1),]
```






```{r importOPAL_ahead2, echo=F}
#val_labels(HRS_ds_ahead_w2) <- NULL
#opal.assign.data(o, 'HRS_ds_ahead_w2', HRS_ds_ahead_w2)
#opal.symbol_import(o,'HRS_ds_ahead_w2', project='_Athlos_Harm_Dataset')
height <- HRS_ds_ahead_w2
save(height, file = "../RData/ahead_w2/height.RData")
rm(height)
```





### AHEAD - Wave 3 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R3HEIGHT`
* Label: `W3 Height in meters`
* Type of variable: `countinous`


```{r assign_ahead3, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w3_heig','HRS.HRS-AHEAD-w3',
                         variables=list('R3HEIGHT'), missings = TRUE)
```

```{r local_ahead3, echo=F}
HRS_ahead_w3_heig <- opal.execute(o,'HRS_ahead_w3_heig')
Continuous_summary(var = HRS_ahead_w3_heig$R3HEIGHT, missing_values = NA)
ggplot(HRS_ahead_w3_heig, aes(R3HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`


**R script:**

```{r harmo_ahead3}
HRS_ds_ahead_w3 <- tibble(id=HRS_ahead_w3_heig$id)
HRS_ds_ahead_w3$height <- car::recode(HRS_ahead_w3_heig$R3HEIGHT*100, "NA=999")
HRS_ds_ahead_w3$height <- labelled(HRS_ds_ahead_w3$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead3, echo=F}
Continuous_summary(var = HRS_ds_ahead_w3$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w3, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(90,200)
```

#### Validation
There is an unusual value that is lower than 1m:
```{r crosstabulation_ahead3, echo=F}
HRS_ahead_w2_heig[which(HRS_ahead_w3_heig$R3HEIGHT<1),]
```





```{r importOPAL_ahead3, echo=F}
#val_labels(HRS_ds_ahead_w3) <- NULL
#opal.assign.data(o, 'HRS_ds_ahead_w3', HRS_ds_ahead_w3)
#opal.symbol_import(o,'HRS_ds_ahead_w3', project='_Athlos_Harm_Dataset')
height <- HRS_ds_ahead_w3
save(height, file = "../RData/ahead_w3/height.RData")
rm(height)
```






### AHEAD - Wave 4 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R4HEIGHT`
* Label: `W4 Height in meters`
* Type of variable: `countinous`

```{r assign_ahead4, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w4_heig','HRS.HRS-AHEAD-w4',
                         variables=list('R4HEIGHT'), missings = TRUE)
```

```{r local_ahead4, echo=F}
HRS_ahead_w4_heig <- opal.execute(o,'HRS_ahead_w4_heig')
Continuous_summary(var = HRS_ahead_w4_heig$R4HEIGHT, missing_values = NA)
ggplot(HRS_ahead_w4_heig, aes(R4HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_ahead4}
HRS_ds_ahead_w4 <- tibble(id=HRS_ahead_w4_heig$id)
HRS_ds_ahead_w4$height <- car::recode(HRS_ahead_w4_heig$R4HEIGHT*100, "NA=999")
HRS_ds_ahead_w4$height <- labelled(HRS_ds_ahead_w4$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead4, echo=F}
Continuous_summary(var = HRS_ds_ahead_w4$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w4, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(90,200)
```

#### Validation
There is an unusual value that is lower than 1m:
```{r crosstabulation_ahead4, echo=F}
HRS_ahead_w4_heig[which(HRS_ahead_w4_heig$R4HEIGHT<1),]
```





```{r importOPAL_ahead4, echo=F}
#val_labels(HRS_ds_ahead_w4) <- NULL
#opal.assign.data(o, 'HRS_ds_ahead_w4', HRS_ds_ahead_w4)
#opal.symbol_import(o,'HRS_ds_ahead_w4', project='_Athlos_Harm_Dataset')
height <- HRS_ds_ahead_w4
save(height, file = "../RData/ahead_w4/height.RData")
rm(height)
```







### AHEAD - Wave 5 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R5HEIGHT`
* Label: `W5 Height in meters`
* Type of variable: `countinous`


```{r assign_ahead5, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w5_heig','HRS.HRS-AHEAD-w5',
                         variables=list('R5HEIGHT'), missings = TRUE)
```

```{r local_ahead5, echo=F}
HRS_ahead_w5_heig <- opal.execute(o,'HRS_ahead_w5_heig')
Continuous_summary(var = HRS_ahead_w5_heig$R5HEIGHT, missing_values = NA)
ggplot(HRS_ahead_w5_heig, aes(R5HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_ahead5}
HRS_ds_ahead_w5 <- tibble(id=HRS_ahead_w5_heig$id)
HRS_ds_ahead_w5$height <- car::recode(HRS_ahead_w5_heig$R5HEIGHT*100, "NA=999")
HRS_ds_ahead_w5$height <- labelled(HRS_ds_ahead_w5$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead5, echo=F}
Continuous_summary(var = HRS_ds_ahead_w5$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w5, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(90,200)
```

#### Validation
There is an unusual value that is lower than 1m:
```{r crosstabulation_ahead5, echo=F}
HRS_ahead_w5_heig[which(HRS_ahead_w5_heig$R5HEIGHT<1),]
```





```{r importOPAL_ahead5, echo=F}
#val_labels(HRS_ds_ahead_w5) <- NULL
#opal.assign.data(o, 'HRS_ds_ahead_w5', HRS_ds_ahead_w5)
#opal.symbol_import(o,'HRS_ds_ahead_w5', project='_Athlos_Harm_Dataset')
height <- HRS_ds_ahead_w5
save(height, file = "../RData/ahead_w5/height.RData")
rm(height)
```








### AHEAD - Wave 6 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R6HEIGHT`
* Label: `W6 Height in meters`
* Type of variable: `countinous`


```{r assign_ahead6, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w6_heig','HRS.HRS-AHEAD-w6',
                         variables=list('R6HEIGHT'), missings = TRUE)
```

```{r local_ahead6, echo=F}
HRS_ahead_w6_heig <- opal.execute(o,'HRS_ahead_w6_heig')
Continuous_summary(var = HRS_ahead_w6_heig$R6HEIGHT, missing_values = NA)
ggplot(HRS_ahead_w6_heig, aes(R6HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_ahead6}
HRS_ds_ahead_w6 <- tibble(id=HRS_ahead_w6_heig$id)
HRS_ds_ahead_w6$height <- car::recode(HRS_ahead_w6_heig$R6HEIGHT*100, "NA=999")
HRS_ds_ahead_w6$height <- labelled(HRS_ds_ahead_w6$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead6, echo=F}
Continuous_summary(var = HRS_ds_ahead_w6$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w6, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(90,200)
```

#### Validation
There is an unusual value that is lower than 1m:
```{r crosstabulation_ahead6, echo=F}
HRS_ahead_w6_heig[which(HRS_ahead_w6_heig$R6HEIGHT<1),]
```





```{r importOPAL_ahead6, echo=F}
#val_labels(HRS_ds_ahead_w6) <- NULL
#opal.assign.data(o, 'HRS_ds_ahead_w6', HRS_ds_ahead_w6)
#opal.symbol_import(o,'HRS_ds_ahead_w6', project='_Athlos_Harm_Dataset')
height <- HRS_ds_ahead_w6
save(height, file = "../RData/ahead_w6/height.RData")
rm(height)
```







### AHEAD - Wave 7 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R7HEIGHT`
* Label: `W7 Height in meters`
* Type of variable: `countinous`

```{r assign_ahead7, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w7_heig','HRS.HRS-AHEAD-w7',
                         variables=list('R7HEIGHT'), missings = TRUE)
```

```{r local_ahead7, echo=F}
HRS_ahead_w7_heig <- opal.execute(o,'HRS_ahead_w7_heig')
Continuous_summary(var = HRS_ahead_w7_heig$R7HEIGHT, missing_values = NA)
ggplot(HRS_ahead_w7_heig, aes(R7HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_ahead7}
HRS_ds_ahead_w7 <- tibble(id=HRS_ahead_w7_heig$id)
HRS_ds_ahead_w7$height <- car::recode(HRS_ahead_w7_heig$R7HEIGHT*100, "NA=999")
HRS_ds_ahead_w7$height <- labelled(HRS_ds_ahead_w7$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead7, echo=F}
Continuous_summary(var = HRS_ds_ahead_w7$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w7, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(90,200)
```

#### Validation
There is an unusual value that is lower than 1m:
```{r crosstabulation_ahead7, echo=F}
HRS_ahead_w7_heig[which(HRS_ahead_w7_heig$R7HEIGHT<1),]
```





```{r importOPAL_ahead7, echo=F}
#val_labels(HRS_ds_ahead_w7) <- NULL
#opal.assign.data(o, 'HRS_ds_ahead_w7', HRS_ds_ahead_w7)
#opal.symbol_import(o,'HRS_ds_ahead_w7', project='_Athlos_Harm_Dataset')
height <- HRS_ds_ahead_w7
save(height, file = "../RData/ahead_w7/height.RData")
rm(height)
```








### AHEAD - Wave 8 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R8HEIGHT`
* Label: `W8 Height in meters`
* Type of variable: `countinous`


```{r assign_ahead8, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w8_heig','HRS.HRS-AHEAD-w8',
                         variables=list('R8HEIGHT'), missings = TRUE)
```

```{r local_ahead8, echo=F}
HRS_ahead_w8_heig <- opal.execute(o,'HRS_ahead_w8_heig')
Continuous_summary(var = HRS_ahead_w8_heig$R8HEIGHT, missing_values = NA)
ggplot(HRS_ahead_w8_heig, aes(R8HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_ahead8}
HRS_ds_ahead_w8 <- tibble(id=HRS_ahead_w8_heig$id)
HRS_ds_ahead_w8$height <- car::recode(HRS_ahead_w8_heig$R8HEIGHT*100, "NA=999")
HRS_ds_ahead_w8$height <- labelled(HRS_ds_ahead_w8$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead8, echo=F}
Continuous_summary(var = HRS_ds_ahead_w8$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w8, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,210)
```

#### Validation
```{r crosstabulation_ahead8, echo=F}

```





```{r importOPAL_ahead8, echo=F}
#val_labels(HRS_ds_ahead_w8) <- NULL
#opal.assign.data(o, 'HRS_ds_ahead_w8', HRS_ds_ahead_w8)
#opal.symbol_import(o,'HRS_ds_ahead_w8', project='_Athlos_Harm_Dataset')
height <- HRS_ds_ahead_w8
save(height, file = "../RData/ahead_w8/height.RData")
rm(height)
```








### AHEAD - Wave 9 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R9HEIGHT`
* Label: `W9 Height in meters`
* Type of variable: `countinous`


```{r assign_ahead9, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w9_heig','HRS.HRS-AHEAD-w9',
                         variables=list('R9HEIGHT'), missings = TRUE)
```

```{r local_ahead9, echo=F}
HRS_ahead_w9_heig <- opal.execute(o,'HRS_ahead_w9_heig')
Continuous_summary(var = HRS_ahead_w9_heig$R9HEIGHT, missing_values = NA)
ggplot(HRS_ahead_w9_heig, aes(R9HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_ahead9}
HRS_ds_ahead_w9 <- tibble(id=HRS_ahead_w9_heig$id)
HRS_ds_ahead_w9$height <- car::recode(HRS_ahead_w9_heig$R9HEIGHT*100, "NA=999")
HRS_ds_ahead_w9$height <- labelled(HRS_ds_ahead_w9$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead9, echo=F}
Continuous_summary(var = HRS_ds_ahead_w9$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w9, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(90,200)
```

#### Validation
There is an unusual value that is lower than 1m:
```{r crosstabulation_ahead9, echo=F}
HRS_ahead_w9_heig[which(HRS_ahead_w9_heig$R9HEIGHT<1),]
```





```{r importOPAL_ahead9, echo=F}
#val_labels(HRS_ds_ahead_w9) <- NULL
#opal.assign.data(o, 'HRS_ds_ahead_w9', HRS_ds_ahead_w9)
#opal.symbol_import(o,'HRS_ds_ahead_w9', project='_Athlos_Harm_Dataset')
height <- HRS_ds_ahead_w9
save(height, file = "../RData/ahead_w9/height.RData")
rm(height)
```







### AHEAD - Wave 10 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R10HEIGHT`
* Label: `W10 Height in meters`
* Type of variable: `countinous`


```{r assign_ahead10, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w10_heig','HRS.HRS-AHEAD-w10',
                         variables=list('R10HEIGHT'), missings = TRUE)
```

```{r local_ahead10, echo=F}
HRS_ahead_w10_heig <- opal.execute(o,'HRS_ahead_w10_heig')
Continuous_summary(var = HRS_ahead_w10_heig$R10HEIGHT, missing_values = NA)
ggplot(HRS_ahead_w10_heig, aes(R10HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_ahead10}
HRS_ds_ahead_w10 <- tibble(id=HRS_ahead_w10_heig$id)
HRS_ds_ahead_w10$height <- car::recode(HRS_ahead_w10_heig$R10HEIGHT*100, "NA=999")
HRS_ds_ahead_w10$height <- labelled(HRS_ds_ahead_w10$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead10, echo=F}
Continuous_summary(var = HRS_ds_ahead_w10$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w10, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(00,210)
```

#### Validation
There is an unusual value that is lower than 1m:
```{r crosstabulation_ahead10, echo=F}
HRS_ahead_w10_heig[which(HRS_ahead_w10_heig$R10HEIGHT<1),]
```





```{r importOPAL_ahead10, echo=F}
#val_labels(HRS_ds_ahead_w10) <- NULL
#opal.assign.data(o, 'HRS_ds_ahead_w10', HRS_ds_ahead_w10)
#opal.symbol_import(o,'HRS_ds_ahead_w10', project='_Athlos_Harm_Dataset')
height <- HRS_ds_ahead_w10
save(height, file = "../RData/ahead_w10/height.RData")
rm(height)
```







### AHEAD - Wave 11 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R11HEIGHT`
* Label: `W11 Height in meters`
* Type of variable: `countinous`


```{r assign_ahead11, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w11_heig','HRS.HRS-AHEAD-w11',
                         variables=list('R11HEIGHT'), missings = TRUE)
```

```{r local_ahead11, echo=F}
HRS_ahead_w11_heig <- opal.execute(o,'HRS_ahead_w11_heig')
Continuous_summary(var = HRS_ahead_w11_heig$R11HEIGHT, missing_values = NA)
ggplot(HRS_ahead_w11_heig, aes(R11HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_ahead11}
HRS_ds_ahead_w11 <- tibble(id=HRS_ahead_w11_heig$id)
HRS_ds_ahead_w11$height <- car::recode(HRS_ahead_w11_heig$R11HEIGHT*100, "NA=999")
HRS_ds_ahead_w11$height <- labelled(HRS_ds_ahead_w11$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead11, echo=F}
Continuous_summary(var = HRS_ds_ahead_w11$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w11, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,210)
```

#### Validation
```{r crosstabulation_ahead11, echo=F}

```





```{r importOPAL_ahead11, echo=F}
#val_labels(HRS_ds_ahead_w11) <- NULL
#opal.assign.data(o, 'HRS_ds_ahead_w11', HRS_ds_ahead_w11)
#opal.symbol_import(o,'HRS_ds_ahead_w11', project='_Athlos_Harm_Dataset')
height <- HRS_ds_ahead_w11
save(height, file = "../RData/ahead_w11/height.RData")
rm(height)
```







### CODA - Wave 4 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R4HEIGHT`
* Label: `W4 Height in meters`
* Type of variable: `countinous`


```{r assign_coda4, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w4_heig','HRS.HRS-CODA-w4',
                         variables=list('R4HEIGHT'), missings = TRUE)
```

```{r local_coda4, echo=F}
HRS_coda_w4_heig <- opal.execute(o,'HRS_coda_w4_heig')
Continuous_summary(var = HRS_coda_w4_heig$R4HEIGHT, missing_values = NA)
ggplot(HRS_coda_w4_heig, aes(R4HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_coda4}
HRS_ds_coda_w4 <- tibble(id=HRS_coda_w4_heig$id)
HRS_ds_coda_w4$height <- car::recode(HRS_coda_w4_heig$R4HEIGHT*100, "NA=999")
HRS_ds_coda_w4$height <- labelled(HRS_ds_coda_w4$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda4, echo=F}
Continuous_summary(var = HRS_ds_coda_w4$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_coda_w4, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,220)
```

#### Validation
```{r crosstabulation_coda4, echo=F}

```





```{r importOPAL_coda4, echo=F}
#val_labels(HRS_ds_coda_w4) <- NULL
#opal.assign.data(o, 'HRS_ds_coda_w4', HRS_ds_coda_w4)
#opal.symbol_import(o,'HRS_ds_coda_w4', project='_Athlos_Harm_Dataset')
height <- HRS_ds_coda_w4
save(height, file = "../RData/coda_w4/height.RData")
rm(height)
```








### CODA - Wave 5 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R5HEIGHT`
* Label: `W5 Height in meters`
* Type of variable: `countinous`


```{r assign_coda5, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w5_heig','HRS.HRS-CODA-w5',
                         variables=list('R5HEIGHT'), missings = TRUE)
```

```{r local_coda5, echo=F}
HRS_coda_w5_heig <- opal.execute(o,'HRS_coda_w5_heig')
Continuous_summary(var = HRS_coda_w5_heig$R5HEIGHT, missing_values = NA)
ggplot(HRS_coda_w5_heig, aes(R5HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_coda5}
HRS_ds_coda_w5 <- tibble(id=HRS_coda_w5_heig$id)
HRS_ds_coda_w5$height <- car::recode(HRS_coda_w5_heig$R5HEIGHT*100, "NA=999")
HRS_ds_coda_w5$height <- labelled(HRS_ds_coda_w5$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda5, echo=F}
Continuous_summary(var = HRS_ds_coda_w5$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_coda_w5, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,220)
```

#### Validation
```{r crosstabulation_coda5, echo=F}

```





```{r importOPAL_coda5, echo=F}
#val_labels(HRS_ds_coda_w5) <- NULL
#opal.assign.data(o, 'HRS_ds_coda_w5', HRS_ds_coda_w5)
#opal.symbol_import(o,'HRS_ds_coda_w5', project='_Athlos_Harm_Dataset')
height <- HRS_ds_coda_w5
save(height, file = "../RData/coda_w5/height.RData")
rm(height)
```








### CODA - Wave 6 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R6HEIGHT`
* Label: `W6 Height in meters`
* Type of variable: `countinous`

```{r assign_coda6, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w6_heig','HRS.HRS-CODA-w6',
                         variables=list('R6HEIGHT'), missings = TRUE)
```

```{r local_coda6, echo=F}
HRS_coda_w6_heig <- opal.execute(o,'HRS_coda_w6_heig')
Continuous_summary(var = HRS_coda_w6_heig$R6HEIGHT, missing_values = NA)
ggplot(HRS_coda_w6_heig, aes(R6HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_coda6}
HRS_ds_coda_w6 <- tibble(id=HRS_coda_w6_heig$id)
HRS_ds_coda_w6$height <- car::recode(HRS_coda_w6_heig$R6HEIGHT*100, "NA=999")
HRS_ds_coda_w6$height <- labelled(HRS_ds_coda_w6$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda6, echo=F}
Continuous_summary(var = HRS_ds_coda_w6$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_coda_w6, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,220)
```

#### Validation
```{r crosstabulation_coda6, echo=F}

```





```{r importOPAL_coda6, echo=F}
#val_labels(HRS_ds_coda_w6) <- NULL
#opal.assign.data(o, 'HRS_ds_coda_w6', HRS_ds_coda_w6)
#opal.symbol_import(o,'HRS_ds_coda_w6', project='_Athlos_Harm_Dataset')
height <- HRS_ds_coda_w6
save(height, file = "../RData/coda_w6/height.RData")
rm(height)
```






### CODA - Wave 7 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R7HEIGHT`
* Label: `W7 Height in meters`
* Type of variable: `countinous`

```{r assign_coda7, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w7_heig','HRS.HRS-CODA-w7',
                         variables=list('R7HEIGHT'), missings = TRUE)
```

```{r local_coda7, echo=F}
HRS_coda_w7_heig <- opal.execute(o,'HRS_coda_w7_heig')
Continuous_summary(var = HRS_coda_w7_heig$R7HEIGHT, missing_values = NA)
ggplot(HRS_coda_w7_heig, aes(R7HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_coda7}
HRS_ds_coda_w7 <- tibble(id=HRS_coda_w7_heig$id)
HRS_ds_coda_w7$height <- car::recode(HRS_coda_w7_heig$R7HEIGHT*100, "NA=999")
HRS_ds_coda_w7$height <- labelled(HRS_ds_coda_w7$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda7, echo=F}
Continuous_summary(var = HRS_ds_coda_w7$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_coda_w7, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,220)
```

#### Validation
```{r crosstabulation_coda7, echo=F}

```





```{r importOPAL_coda7, echo=F}
#val_labels(HRS_ds_coda_w7) <- NULL
#opal.assign.data(o, 'HRS_ds_coda_w7', HRS_ds_coda_w7)
#opal.symbol_import(o,'HRS_ds_coda_w7', project='_Athlos_Harm_Dataset')
height <- HRS_ds_coda_w7
save(height, file = "../RData/coda_w7/height.RData")
rm(height)
```







### CODA - Wave 8 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R8HEIGHT`
* Label: `W8 Height in meters`
* Type of variable: `countinous`

```{r assign_coda8, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w8_heig','HRS.HRS-CODA-w8',
                         variables=list('R8HEIGHT'), missings = TRUE)
```

```{r local_coda8, echo=F}
HRS_coda_w8_heig <- opal.execute(o,'HRS_coda_w8_heig')
Continuous_summary(var = HRS_coda_w8_heig$R8HEIGHT, missing_values = NA)
ggplot(HRS_coda_w8_heig, aes(R8HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_coda8}
HRS_ds_coda_w8 <- tibble(id=HRS_coda_w8_heig$id)
HRS_ds_coda_w8$height <- car::recode(HRS_coda_w8_heig$R8HEIGHT*100, "NA=999")
HRS_ds_coda_w8$height <- labelled(HRS_ds_coda_w8$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda8, echo=F}
Continuous_summary(var = HRS_ds_coda_w8$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_coda_w8, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,210)
```

#### Validation
```{r crosstabulation_coda8, echo=F}

```





```{r importOPAL_coda8, echo=F}
#val_labels(HRS_ds_coda_w8) <- NULL
#opal.assign.data(o, 'HRS_ds_coda_w8', HRS_ds_coda_w8)
#opal.symbol_import(o,'HRS_ds_coda_w8', project='_Athlos_Harm_Dataset')
height <- HRS_ds_coda_w8
save(height, file = "../RData/coda_w8/height.RData")
rm(height)
```







### CODA - Wave 9 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R9HEIGHT`
* Label: `W9 Height in meters`
* Type of variable: `countinous`

```{r assign_coda9, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w9_heig','HRS.HRS-CODA-w9',
                         variables=list('R9HEIGHT'), missings = TRUE)
```

```{r local_coda9, echo=F}
HRS_coda_w9_heig <- opal.execute(o,'HRS_coda_w9_heig')
Continuous_summary(var = HRS_coda_w9_heig$R9HEIGHT, missing_values = NA)
ggplot(HRS_coda_w9_heig, aes(R9HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_coda9}
HRS_ds_coda_w9 <- tibble(id=HRS_coda_w9_heig$id)
HRS_ds_coda_w9$height <- car::recode(HRS_coda_w9_heig$R9HEIGHT*100, "NA=999")
HRS_ds_coda_w9$height <- labelled(HRS_ds_coda_w9$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda9, echo=F}
Continuous_summary(var = HRS_ds_coda_w9$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_coda_w9, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,220)
```

#### Validation
```{r crosstabulation_coda9, echo=F}

```





```{r importOPAL_coda9, echo=F}
#val_labels(HRS_ds_coda_w9) <- NULL
#opal.assign.data(o, 'HRS_ds_coda_w9', HRS_ds_coda_w9)
#opal.symbol_import(o,'HRS_ds_coda_w9', project='_Athlos_Harm_Dataset')
height <- HRS_ds_coda_w9
save(height, file = "../RData/coda_w9/height.RData")
rm(height)
```







### CODA - Wave 10 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R10HEIGHT`
* Label: `W10 Height in meters`
* Type of variable: `countinous`

```{r assign_coda10, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w10_heig','HRS.HRS-CODA-w10',
                         variables=list('R10HEIGHT'), missings = TRUE)
```

```{r local_coda10, echo=F}
HRS_coda_w10_heig <- opal.execute(o,'HRS_coda_w10_heig')
Continuous_summary(var = HRS_coda_w10_heig$R10HEIGHT, missing_values = NA)
ggplot(HRS_coda_w10_heig, aes(R10HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_coda10}
HRS_ds_coda_w10 <- tibble(id=HRS_coda_w10_heig$id)
HRS_ds_coda_w10$height <- car::recode(HRS_coda_w10_heig$R10HEIGHT*100, "NA=999")
HRS_ds_coda_w10$height <- labelled(HRS_ds_coda_w10$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda10, echo=F}
Continuous_summary(var = HRS_ds_coda_w10$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_coda_w10, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,220)
```

#### Validation
```{r crosstabulation_coda10, echo=F}

```





```{r importOPAL_coda10, echo=F}
#val_labels(HRS_ds_coda_w10) <- NULL
#opal.assign.data(o, 'HRS_ds_coda_w10', HRS_ds_coda_w10)
#opal.symbol_import(o,'HRS_ds_coda_w10', project='_Athlos_Harm_Dataset')
height <- HRS_ds_coda_w10
save(height, file = "../RData/coda_w10/height.RData")
rm(height)
```







### CODA - Wave 11 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R11HEIGHT`
* Label: `W11 Height in meters`
* Type of variable: `countinous`

```{r assign_coda11, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w11_heig','HRS.HRS-CODA-w11',
                         variables=list('R11HEIGHT'), missings = TRUE)
```

```{r local_coda11, echo=F}
HRS_coda_w11_heig <- opal.execute(o,'HRS_coda_w11_heig')
Continuous_summary(var = HRS_coda_w11_heig$R11HEIGHT, missing_values = NA)
ggplot(HRS_coda_w11_heig, aes(R11HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_coda11}
HRS_ds_coda_w11 <- tibble(id=HRS_coda_w11_heig$id)
HRS_ds_coda_w11$height <- car::recode(HRS_coda_w11_heig$R11HEIGHT*100, "NA=999")
HRS_ds_coda_w11$height <- labelled(HRS_ds_coda_w11$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda11, echo=F}
Continuous_summary(var = HRS_ds_coda_w11$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_coda_w11, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,200)
```

#### Validation
```{r crosstabulation_coda11, echo=F}

```





```{r importOPAL_coda11, echo=F}
#val_labels(HRS_ds_coda_w11) <- NULL
#opal.assign.data(o, 'HRS_ds_coda_w11', HRS_ds_coda_w11)
#opal.symbol_import(o,'HRS_ds_coda_w11', project='_Athlos_Harm_Dataset')
height <- HRS_ds_coda_w11
save(height, file = "../RData/coda_w11/height.RData")
rm(height)
```







### The War Baby (WB) - Wave 4  

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R4HEIGHT`
* Label: `W4 Height in meters`
* Type of variable: `countinous`


```{r assign_wb4, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w4_heig','HRS.HRS-WB-w4',
                         variables=list('R4HEIGHT'), missings = TRUE)
```

```{r local_wb4, echo=F}
HRS_wb_w4_heig <- opal.execute(o,'HRS_wb_w4_heig')
Continuous_summary(var = HRS_wb_w4_heig$R4HEIGHT, missing_values = NA)
ggplot(HRS_wb_w4_heig, aes(R4HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_wb4}
HRS_ds_wb_w4 <- tibble(id=HRS_wb_w4_heig$id)
HRS_ds_wb_w4$height <- car::recode(HRS_wb_w4_heig$R4HEIGHT*100, "NA=999")
HRS_ds_wb_w4$height <- labelled(HRS_ds_wb_w4$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb4, echo=F}
Continuous_summary(var = HRS_ds_wb_w4$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_wb_w4, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,210)
```

#### Validation
```{r crosstabulation_wb4, echo=F}

```





```{r importOPAL_wb4, echo=F}
#val_labels(HRS_ds_wb_w4) <- NULL
#opal.assign.data(o, 'HRS_ds_wb_w4', HRS_ds_wb_w4)
#opal.symbol_import(o,'HRS_ds_wb_w4', project='_Athlos_Harm_Dataset')
height <- HRS_ds_wb_w4
save(height, file = "../RData/wb_w4/height.RData")
rm(height)
```









### The War Baby (WB) - Wave 5  

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R5HEIGHT`
* Label: `W5 Height in meters`
* Type of variable: `countinous`

```{r assign_wb5, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w5_heig','HRS.HRS-WB-w5',
                         variables=list('R5HEIGHT'), missings = TRUE)
```

```{r local_wb5, echo=F}
HRS_wb_w5_heig <- opal.execute(o,'HRS_wb_w5_heig')
Continuous_summary(var = HRS_wb_w5_heig$R5HEIGHT, missing_values = NA)
ggplot(HRS_wb_w5_heig, aes(R5HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_wb5}
HRS_ds_wb_w5 <- tibble(id=HRS_wb_w5_heig$id)
HRS_ds_wb_w5$height <- car::recode(HRS_wb_w5_heig$R5HEIGHT*100, "NA=999")
HRS_ds_wb_w5$height <- labelled(HRS_ds_wb_w5$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb5, echo=F}
Continuous_summary(var = HRS_ds_wb_w5$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_wb_w5, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,210)
```

#### Validation
```{r crosstabulation_wb5, echo=F}

```





```{r importOPAL_wb5, echo=F}
#val_labels(HRS_ds_wb_w5) <- NULL
#opal.assign.data(o, 'HRS_ds_wb_w5', HRS_ds_wb_w5)
#opal.symbol_import(o,'HRS_ds_wb_w5', project='_Athlos_Harm_Dataset')
height <- HRS_ds_wb_w5
save(height, file = "../RData/wb_w5/height.RData")
rm(height)
```








### The War Baby (WB) - Wave 6  

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R6HEIGHT`
* Label: `W6 Height in meters`
* Type of variable: `countinous`

```{r assign_wb6, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w6_heig','HRS.HRS-WB-w6',
                         variables=list('R6HEIGHT'), missings = TRUE)
```

```{r local_wb6, echo=F}
HRS_wb_w6_heig <- opal.execute(o,'HRS_wb_w6_heig')
Continuous_summary(var = HRS_wb_w6_heig$R6HEIGHT, missing_values = NA)
ggplot(HRS_wb_w6_heig, aes(R6HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_wb6}
HRS_ds_wb_w6 <- tibble(id=HRS_wb_w6_heig$id)
HRS_ds_wb_w6$height <- car::recode(HRS_wb_w6_heig$R6HEIGHT*100, "NA=999")
HRS_ds_wb_w6$height <- labelled(HRS_ds_wb_w6$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb6, echo=F}
Continuous_summary(var = HRS_ds_wb_w6$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_wb_w6, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,202)
```

#### Validation
```{r crosstabulation_wb6, echo=F}

```





```{r importOPAL_wb6, echo=F}
#val_labels(HRS_ds_wb_w6) <- NULL
#opal.assign.data(o, 'HRS_ds_wb_w6', HRS_ds_wb_w6)
#opal.symbol_import(o,'HRS_ds_wb_w6', project='_Athlos_Harm_Dataset')
height <- HRS_ds_wb_w6
save(height, file = "../RData/wb_w6/height.RData")
rm(height)
```






### The War Baby (WB) - Wave 7  

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R7HEIGHT`
* Label: `W7 Height in meters`
* Type of variable: `countinous`


```{r assign_wb7, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w7_heig','HRS.HRS-WB-w7',
                         variables=list('R7HEIGHT'), missings = TRUE)
```

```{r local_wb7, echo=F}
HRS_wb_w7_heig <- opal.execute(o,'HRS_wb_w7_heig')
Continuous_summary(var = HRS_wb_w7_heig$R7HEIGHT, missing_values = NA)
ggplot(HRS_wb_w7_heig, aes(R7HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_wb7}
HRS_ds_wb_w7 <- tibble(id=HRS_wb_w7_heig$id)
HRS_ds_wb_w7$height <- car::recode(HRS_wb_w7_heig$R7HEIGHT*100, "NA=999")
HRS_ds_wb_w7$height <- labelled(HRS_ds_wb_w7$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb7, echo=F}
Continuous_summary(var = HRS_ds_wb_w7$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_wb_w7, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,201)
```

#### Validation
```{r crosstabulation_wb7, echo=F}

```





```{r importOPAL_wb7, echo=F}
#val_labels(HRS_ds_wb_w7) <- NULL
#opal.assign.data(o, 'HRS_ds_wb_w7', HRS_ds_wb_w7)
#opal.symbol_import(o,'HRS_ds_wb_w7', project='_Athlos_Harm_Dataset')
height <- HRS_ds_wb_w7
save(height, file = "../RData/wb_w7/height.RData")
rm(height)
```








### The War Baby (WB) - Wave 8  

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R8HEIGHT`
* Label: `W8 Height in meters`
* Type of variable: `countinous`

```{r assign_wb8, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w8_heig','HRS.HRS-WB-w8',
                         variables=list('R8HEIGHT'), missings = TRUE)
```

```{r local_wb8, echo=F}
HRS_wb_w8_heig <- opal.execute(o,'HRS_wb_w8_heig')
Continuous_summary(var = HRS_wb_w8_heig$R8HEIGHT, missing_values = NA)
ggplot(HRS_wb_w8_heig, aes(R8HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_wb8}
HRS_ds_wb_w8 <- tibble(id=HRS_wb_w8_heig$id)
HRS_ds_wb_w8$height <- car::recode(HRS_wb_w8_heig$R8HEIGHT*100, "NA=999")
HRS_ds_wb_w8$height <- labelled(HRS_ds_wb_w8$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb8, echo=F}
Continuous_summary(var = HRS_ds_wb_w8$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_wb_w8, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,200)
```

#### Validation
```{r crosstabulation_wb8, echo=F}

```





```{r importOPAL_wb8, echo=F}
#val_labels(HRS_ds_wb_w8) <- NULL
#opal.assign.data(o, 'HRS_ds_wb_w8', HRS_ds_wb_w8)
#opal.symbol_import(o,'HRS_ds_wb_w8', project='_Athlos_Harm_Dataset')
height <- HRS_ds_wb_w8
save(height, file = "../RData/wb_w8/height.RData")
rm(height)
```








### The War Baby (WB) - Wave 9  

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R9HEIGHT`
* Label: `W9 Height in meters`
* Type of variable: `countinous`


```{r assign_wb9, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w9_heig','HRS.HRS-WB-w9',
                         variables=list('R9HEIGHT'), missings = TRUE)
```

```{r local_wb9, echo=F}
HRS_wb_w9_heig <- opal.execute(o,'HRS_wb_w9_heig')
Continuous_summary(var = HRS_wb_w9_heig$R9HEIGHT, missing_values = NA)
ggplot(HRS_wb_w9_heig, aes(R9HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_wb9}
HRS_ds_wb_w9 <- tibble(id=HRS_wb_w9_heig$id)
HRS_ds_wb_w9$height <- car::recode(HRS_wb_w9_heig$R9HEIGHT*100, "NA=999")
HRS_ds_wb_w9$height <- labelled(HRS_ds_wb_w9$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb9, echo=F}
Continuous_summary(var = HRS_ds_wb_w9$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_wb_w9, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,240)
```

#### Validation
```{r crosstabulation_wb9, echo=F}

```





```{r importOPAL_wb9, echo=F}
#val_labels(HRS_ds_wb_w9) <- NULL
#opal.assign.data(o, 'HRS_ds_wb_w9', HRS_ds_wb_w9)
#opal.symbol_import(o,'HRS_ds_wb_w9', project='_Athlos_Harm_Dataset')
height <- HRS_ds_wb_w9
save(height, file = "../RData/wb_w9/height.RData")
rm(height)
```







### The War Baby (WB) - Wave 10  

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R10HEIGHT`
* Label: `W10 Height in meters`
* Type of variable: `countinous`

```{r assign_wb10, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w10_heig','HRS.HRS-WB-w10',
                         variables=list('R10HEIGHT'), missings = TRUE)
```

```{r local_wb10, echo=F}
HRS_wb_w10_heig <- opal.execute(o,'HRS_wb_w10_heig')
Continuous_summary(var = HRS_wb_w10_heig$R10HEIGHT, missing_values = NA)
ggplot(HRS_wb_w10_heig, aes(R10HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_wb10}
HRS_ds_wb_w10 <- tibble(id=HRS_wb_w10_heig$id)
HRS_ds_wb_w10$height <- car::recode(HRS_wb_w10_heig$R10HEIGHT*100, "NA=999")
HRS_ds_wb_w10$height <- labelled(HRS_ds_wb_w10$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb10, echo=F}
Continuous_summary(var = HRS_ds_wb_w10$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_wb_w10, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,235)
```

#### Validation
```{r crosstabulation_wb10, echo=F}

```





```{r importOPAL_wb10, echo=F}
#val_labels(HRS_ds_wb_w10) <- NULL
#opal.assign.data(o, 'HRS_ds_wb_w10', HRS_ds_wb_w10)
#opal.symbol_import(o,'HRS_ds_wb_w10', project='_Athlos_Harm_Dataset')
height <- HRS_ds_wb_w10
save(height, file = "../RData/wb_w10/height.RData")
rm(height)
```







### The War Baby (WB) - Wave 11  

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R11HEIGHT`
* Label: `W11 Height in meters`
* Type of variable: `countinous`


```{r assign_wb11, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w11_heig','HRS.HRS-WB-w11',
                         variables=list('R11HEIGHT'), missings = TRUE)
```

```{r local_wb11, echo=F}
HRS_wb_w11_heig <- opal.execute(o,'HRS_wb_w11_heig')
Continuous_summary(var = HRS_wb_w11_heig$R11HEIGHT, missing_values = NA)
ggplot(HRS_wb_w11_heig, aes(R11HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_wb11}
HRS_ds_wb_w11 <- tibble(id=HRS_wb_w11_heig$id)
HRS_ds_wb_w11$height <- car::recode(HRS_wb_w11_heig$R11HEIGHT*100, "NA=999")
HRS_ds_wb_w11$height <- labelled(HRS_ds_wb_w11$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb11, echo=F}
Continuous_summary(var = HRS_ds_wb_w11$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_wb_w11, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,205)
```

#### Validation
```{r crosstabulation_wb11, echo=F}

```





```{r importOPAL_wb11, echo=F}
#val_labels(HRS_ds_wb_w11) <- NULL
#opal.assign.data(o, 'HRS_ds_wb_w11', HRS_ds_wb_w11)
#opal.symbol_import(o,'HRS_ds_wb_w11', project='_Athlos_Harm_Dataset')
height <- HRS_ds_wb_w11
save(height, file = "../RData/wb_w11/height.RData")
rm(height)
```







### The Early Baby Boomer (EBB) - Wave 7  

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R7HEIGHT`
* Label: `W7 Height in meters`
* Type of variable: `countinous`



```{r assign_ebb7, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w7_heig','HRS.HRS-EBB-w7',
                         variables=list('R7HEIGHT'), missings = TRUE)
```

```{r local_ebb7, echo=F}
HRS_ebb_w7_heig <- opal.execute(o,'HRS_ebb_w7_heig')
Continuous_summary(var = HRS_ebb_w7_heig$R7HEIGHT, missing_values = NA)
ggplot(HRS_ebb_w7_heig, aes(R7HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_ebb7}
HRS_ds_ebb_w7 <- tibble(id=HRS_ebb_w7_heig$id)
HRS_ds_ebb_w7$height <- car::recode(HRS_ebb_w7_heig$R7HEIGHT*100, "NA=999")
HRS_ds_ebb_w7$height <- labelled(HRS_ds_ebb_w7$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ebb7, echo=F}
Continuous_summary(var = HRS_ds_ebb_w7$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ebb_w7, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,235)
```

#### Validation
```{r crosstabulation_ebb7, echo=F}

```





```{r importOPAL_ebb7, echo=F}
#val_labels(HRS_ds_ebb_w7) <- NULL
#opal.assign.data(o, 'HRS_ds_ebb_w7', HRS_ds_ebb_w7)
#opal.symbol_import(o,'HRS_ds_ebb_w7', project='_Athlos_Harm_Dataset')
height <- HRS_ds_ebb_w7
save(height, file = "../RData/ebb_w7/height.RData")
rm(height)
```







### The Early Baby Boomer (EBB) - Wave 8  

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R8HEIGHT`
* Label: `W8 Height in meters`
* Type of variable: `countinous`

```{r assign_ebb8, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w8_heig','HRS.HRS-EBB-w8',
                         variables=list('R8HEIGHT'), missings = TRUE)
```

```{r local_ebb8, echo=F}
HRS_ebb_w8_heig <- opal.execute(o,'HRS_ebb_w8_heig')
Continuous_summary(var = HRS_ebb_w8_heig$R8HEIGHT, missing_values = NA)
ggplot(HRS_ebb_w8_heig, aes(R8HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_ebb8}
HRS_ds_ebb_w8 <- tibble(id=HRS_ebb_w8_heig$id)
HRS_ds_ebb_w8$height <- car::recode(HRS_ebb_w8_heig$R8HEIGHT*100, "NA=999")
HRS_ds_ebb_w8$height <- labelled(HRS_ds_ebb_w8$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ebb8, echo=F}
Continuous_summary(var = HRS_ds_ebb_w8$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ebb_w8, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,210)
```

#### Validation
```{r crosstabulation_ebb8, echo=F}

```





```{r importOPAL_ebb8, echo=F}
#val_labels(HRS_ds_ebb_w8) <- NULL
#opal.assign.data(o, 'HRS_ds_ebb_w8', HRS_ds_ebb_w8)
#opal.symbol_import(o,'HRS_ds_ebb_w8', project='_Athlos_Harm_Dataset')
height <- HRS_ds_ebb_w8
save(height, file = "../RData/ebb_w8/height.RData")
rm(height)
```







### The Early Baby Boomer (EBB) - Wave 9  

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R9HEIGHT`
* Label: `W9 Height in meters`
* Type of variable: `countinous`


```{r assign_ebb9, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w9_heig','HRS.HRS-EBB-w9',
                         variables=list('R9HEIGHT'), missings = TRUE)
```

```{r local_ebb9, echo=F}
HRS_ebb_w9_heig <- opal.execute(o,'HRS_ebb_w9_heig')
Continuous_summary(var = HRS_ebb_w9_heig$R9HEIGHT, missing_values = NA)
ggplot(HRS_ebb_w9_heig, aes(R9HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_ebb9}
HRS_ds_ebb_w9 <- tibble(id=HRS_ebb_w9_heig$id)
HRS_ds_ebb_w9$height <- car::recode(HRS_ebb_w9_heig$R9HEIGHT*100, "NA=999")
HRS_ds_ebb_w9$height <- labelled(HRS_ds_ebb_w9$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ebb9, echo=F}
Continuous_summary(var = HRS_ds_ebb_w9$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ebb_w9, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,215)
```

#### Validation
```{r crosstabulation_ebb9, echo=F}

```





```{r importOPAL1, echo=F}
#val_labels(HRS_ds_ebb_w9) <- NULL
#opal.assign.data(o, 'HRS_ds_ebb_w9', HRS_ds_ebb_w9)
#opal.symbol_import(o,'HRS_ds_ebb_w9', project='_Athlos_Harm_Dataset')
height <- HRS_ds_ebb_w9
save(height, file = "../RData/ebb_w9/height.RData")
rm(height)
```







### The Early Baby Boomer (EBB) - Wave 10  

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R10HEIGHT`
* Label: `W10 Height in meters`
* Type of variable: `countinous`

```{r assign_ebb10, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w10_heig','HRS.HRS-EBB-w10',
                         variables=list('R10HEIGHT'), missings = TRUE)
```

```{r local_ebb10, echo=F}
HRS_ebb_w10_heig <- opal.execute(o,'HRS_ebb_w10_heig')
Continuous_summary(var = HRS_ebb_w10_heig$R10HEIGHT, missing_values = NA)
ggplot(HRS_ebb_w10_heig, aes(R10HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_ebb10}
HRS_ds_ebb_w10 <- tibble(id=HRS_ebb_w10_heig$id)
HRS_ds_ebb_w10$height <- car::recode(HRS_ebb_w10_heig$R10HEIGHT*100, "NA=999")
HRS_ds_ebb_w10$height <- labelled(HRS_ds_ebb_w10$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ebb10, echo=F}
Continuous_summary(var = HRS_ds_ebb_w10$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ebb_w10, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,230)
```

#### Validation
```{r crosstabulation_ebb10, echo=F}

```





```{r importOPAL_ebb10, echo=F}
#val_labels(HRS_ds_ebb_w10) <- NULL
#opal.assign.data(o, 'HRS_ds_ebb_w10', HRS_ds_ebb_w10)
#opal.symbol_import(o,'HRS_ds_ebb_w10', project='_Athlos_Harm_Dataset')
height <- HRS_ds_ebb_w10
save(height, file = "../RData/ebb_w10/height.RData")
rm(height)
```








### The Early Baby Boomer (EBB) - Wave 11  

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R11HEIGHT`
* Label: `W11 Height in meters`
* Type of variable: `countinous`


```{r assign_ebb11, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w11_heig','HRS.HRS-EBB-w11',
                         variables=list('R11HEIGHT'), missings = TRUE)
```

```{r local_ebb11, echo=F}
HRS_ebb_w11_heig <- opal.execute(o,'HRS_ebb_w11_heig')
Continuous_summary(var = HRS_ebb_w11_heig$R11HEIGHT, missing_values = NA)
ggplot(HRS_ebb_w11_heig, aes(R11HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_ebb11}
HRS_ds_ebb_w11 <- tibble(id=HRS_ebb_w11_heig$id)
HRS_ds_ebb_w11$height <- car::recode(HRS_ebb_w11_heig$R11HEIGHT*100, "NA=999")
HRS_ds_ebb_w11$height <- labelled(HRS_ds_ebb_w11$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ebb11, echo=F}
Continuous_summary(var = HRS_ds_ebb_w11$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ebb_w11, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,230)
```

#### Validation
```{r crosstabulation_ebb11, echo=F}

```





```{r importOPAL_ebb11, echo=F}
#val_labels(HRS_ds_ebb_w11) <- NULL
#opal.assign.data(o, 'HRS_ds_ebb_w11', HRS_ds_ebb_w11)
#opal.symbol_import(o,'HRS_ds_ebb_w11', project='_Athlos_Harm_Dataset')
height <- HRS_ds_ebb_w11
save(height, file = "../RData/ebb_w11/height.RData")
rm(height)
```






### The Mid Baby Boomer (MBB) - Wave 10  

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R10HEIGHT`
* Label: `W10 Height in meters`
* Type of variable: `countinous`

```{r assign_mbb10, echo=F}
opal.assign.table.tibble(o, 'HRS_mbb_w10_heig','HRS.HRS-MBB-w10',
                         variables=list('R10HEIGHT'), missings = TRUE)
```

```{r local_mbb10, echo=F}
HRS_mbb_w10_heig <- opal.execute(o,'HRS_mbb_w10_heig')
Continuous_summary(var = HRS_mbb_w10_heig$R10HEIGHT, missing_values = NA)
ggplot(HRS_mbb_w10_heig, aes(R10HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_mbb10}
HRS_ds_mbb_w10 <- tibble(id=HRS_mbb_w10_heig$id)
HRS_ds_mbb_w10$height <- car::recode(HRS_mbb_w10_heig$R10HEIGHT*100, "NA=999")
HRS_ds_mbb_w10$height <- labelled(HRS_ds_mbb_w10$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_mbb10, echo=F}
Continuous_summary(var = HRS_ds_mbb_w10$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_mbb_w10, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,210)
```

#### Validation
```{r crosstabulation_mbb10, echo=F}

```





```{r importOPAL_mbb10, echo=F}
#val_labels(HRS_ds_mbb_w10) <- NULL
#opal.assign.data(o, 'HRS_ds_mbb_w10', HRS_ds_mbb_w10)
#opal.symbol_import(o,'HRS_ds_mbb_w10', project='_Athlos_Harm_Dataset')
height <- HRS_ds_mbb_w10
save(height, file = "../RData/mbb_w10/height.RData")
rm(height)
```






### The Mid Baby Boomer (MBB) - Wave 11  

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `R11HEIGHT`
* Label: `W11 Height in meters`
* Type of variable: `countinous`

```{r assign_mbb11, echo=F}
opal.assign.table.tibble(o, 'HRS_mbb_w11_heig','HRS.HRS-MBB-w11',
                         variables=list('R11HEIGHT'), missings = TRUE)
```

```{r local_mbb11, echo=F}
HRS_mbb_w11_heig <- opal.execute(o,'HRS_mbb_w11_heig')
Continuous_summary(var = HRS_mbb_w11_heig$R11HEIGHT, missing_values = NA)
ggplot(HRS_mbb_w11_heig, aes(R11HEIGHT)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same as the study-specific variable converted into cms, therefore the study-specific variable has to be multiplied by 100 and the missing values have to be recoded as follows:

* `NA as 999`


**R script:**

```{r harmo_mbb11}
HRS_ds_mbb_w11 <- tibble(id=HRS_mbb_w11_heig$id)
HRS_ds_mbb_w11$height <- car::recode(HRS_mbb_w11_heig$R11HEIGHT*100, "NA=999")
HRS_ds_mbb_w11$height <- labelled(HRS_ds_mbb_w11$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_mbb11, echo=F}
Continuous_summary(var = HRS_ds_mbb_w11$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_mbb_w11, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,210)
```

#### Validation
```{r crosstabulation_mbb11, echo=F}

```





```{r importOPAL_mbb11, echo=F}
#val_labels(HRS_ds_mbb_w11) <- NULL
#opal.assign.data(o, 'HRS_ds_mbb_w11', HRS_ds_mbb_w11)
#opal.symbol_import(o,'HRS_ds_mbb_w11', project='_Athlos_Harm_Dataset')
height <- HRS_ds_mbb_w11
save(height, file = "../RData/mbb_w11/height.RData")
rm(height)
```

# Quality estimation
Units were converted for this variable.



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
