---
title: "Obesity"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ############################################ --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ############################################ --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `obesity`
* Variable label: `Presence of obesity based in Body Mass Index classification according to the WHO BMI classification (http://apps.who.int/bmi/index.jsp?introPage=intro_3.html): BMI value equal to or above 30Kg/m^2`
* Variable description: `the BMI variable should be created by dividing weight and hiegh variables by means of the following equation= weight (kg)/height(m)^2. Then, the Obesity variable should be generated according to the WHO cutoff point for BMI classification`
* Domain: `Physical measures`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | not obese
1        | obese

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process


```{r lab, echo=FALSE}
ds_label <- "Precense of obesity based in Body Mass Index classification according to the WHO BMI classification (http://apps.who.int/bmi/index.jsp?introPage=intro_3.html): BMI value equal to or above 30Kg/m^2"
```




### HRS

### Wave 1

#### Study-specific variable description

The study-specific variables elected to be harmonised are:

* Name: `R1BMI`
* Label: `W1 Body Mass Index=kg/m2`
* Type of variable: `countinous`


```{r assign_hrs1, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-HRS-w1',
                         variables=list('R1BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_hrs1, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_hrs1}
HRS_ds_hrs_w1 <- tibble(id=HRS_bmi$id)
HRS_ds_hrs_w1$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_hrs_w1$obesity <- labelled(HRS_ds_hrs_w1[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_hrs1, echo=F}
Categorical_summary(var = HRS_ds_hrs_w1[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w1, aes(x=factor(HRS_ds_hrs_w1[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_hrs1, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_hrs_w1[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_hrs1, include=FALSE}
rm(HRS_bmi)
```


### Wave 2

#### Study-specific variable description

The study-specific variables elected to be harmonised are:

* Name: `R2BMI`
* Label: `W2 Body Mass Index=kg/m2`
* Type of variable: `countinous`


```{r assign_hrs2, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-HRS-w2',
                         variables=list('R2BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_hrs2, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_hrs2}
HRS_ds_hrs_w2 <- tibble(id=HRS_bmi$id)
HRS_ds_hrs_w2$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_hrs_w2$obesity <- labelled(HRS_ds_hrs_w2[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_hrs2, echo=F}
Categorical_summary(var = HRS_ds_hrs_w2[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w2, aes(x=factor(HRS_ds_hrs_w2[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_hrs2, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_hrs_w2[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_hrs2, include=FALSE}
rm(HRS_bmi)
```

### Wave 3

#### Study-specific variable description

The study-specific variables elected to be harmonised are:

* Name: `R3BMI`
* Label: `W3 Body Mass Index=kg/m2`
* Type of variable: `countinous`


```{r assign_hrs3, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-HRS-w3',
                         variables=list('R3BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_hrs3, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_hrs3}
HRS_ds_hrs_w3 <- tibble(id=HRS_bmi$id)
HRS_ds_hrs_w3$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_hrs_w3$obesity <- labelled(HRS_ds_hrs_w3[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_hrs3, echo=F}
Categorical_summary(var = HRS_ds_hrs_w3[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w3, aes(x=factor(HRS_ds_hrs_w3[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_hrs3, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_hrs_w3[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_hrs3, include=FALSE}
rm(HRS_bmi)
```


### Wave 4

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R4BMI`
* Label: `W4 Body Mass Index=kg/m2`
* Type of variable: `countinous`


```{r assign_hrs4, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-HRS-w4',
                         variables=list('R4BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_hrs4, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_hrs4}
HRS_ds_hrs_w4 <- tibble(id=HRS_bmi$id)
HRS_ds_hrs_w4$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_hrs_w4$obesity <- labelled(HRS_ds_hrs_w4[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_hrs4, echo=F}
Categorical_summary(var = HRS_ds_hrs_w4[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w4, aes(x=factor(HRS_ds_hrs_w4[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_hrs4, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_hrs_w4[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_hrs4, include=FALSE}
rm(HRS_bmi)
```


### Wave 5

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R5BMI`
* Label: `W5 Body Mass Index=kg/m2`
* Type of variable: `countinous`

```{r assign_hrs5, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-HRS-w5',
                         variables=list('R5BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_hrs5, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_hrs5}
HRS_ds_hrs_w5 <- tibble(id=HRS_bmi$id)
HRS_ds_hrs_w5$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_hrs_w5$obesity <- labelled(HRS_ds_hrs_w5[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_hrs5, echo=F}
Categorical_summary(var = HRS_ds_hrs_w5[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w5, aes(x=factor(HRS_ds_hrs_w5[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_hrs5, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_hrs_w5[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_hrs5, include=FALSE}
rm(HRS_bmi)
```






### Wave 6

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R6BMI`
* Label: `W6 Body Mass Index=kg/m2`
* Type of variable: `countinous`


```{r assign_hrs6, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-HRS-w6',
                         variables=list('R6BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_hrs6, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_hrs6}
HRS_ds_hrs_w6 <- tibble(id=HRS_bmi$id)
HRS_ds_hrs_w6$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_hrs_w6$obesity <- labelled(HRS_ds_hrs_w6[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_hrs6, echo=F}
Categorical_summary(var = HRS_ds_hrs_w6[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w6, aes(x=factor(HRS_ds_hrs_w6[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_hrs6, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_hrs_w6[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_hrs6, include=FALSE}
rm(HRS_bmi)
```


### Wave 7

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R7BMI`
* Label: `W7 Body Mass Index=kg/m2`
* Type of variable: `countinous`


```{r assign_hrs7, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-HRS-w7',
                         variables=list('R7BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_hrs7, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_hrs7}
HRS_ds_hrs_w7 <- tibble(id=HRS_bmi$id)
HRS_ds_hrs_w7$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_hrs_w7$obesity <- labelled(HRS_ds_hrs_w7[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_hrs7, echo=F}
Categorical_summary(var = HRS_ds_hrs_w7[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w7, aes(x=factor(HRS_ds_hrs_w7[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_hrs7, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_hrs_w7[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_hrs7, include=FALSE}
rm(HRS_bmi)
```



### Wave 8

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R8BMI`
* Label: `W8 Body Mass Index=kg/m2`
* Type of variable: `countinous`


```{r assign_hrs8, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-HRS-w8',
                         variables=list('R8BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_hrs8, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_hrs8}
HRS_ds_hrs_w8 <- tibble(id=HRS_bmi$id)
HRS_ds_hrs_w8$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_hrs_w8$obesity <- labelled(HRS_ds_hrs_w8[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_hrs8, echo=F}
Categorical_summary(var = HRS_ds_hrs_w8[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w8, aes(x=factor(HRS_ds_hrs_w8[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_hrs8, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_hrs_w8[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_hrs8, include=FALSE}
rm(HRS_bmi)
```

### Wave 9

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R9BMI`
* Label: `W9 Body Mass Index=kg/m2`
* Type of variable: `countinous`


```{r assign_hrs9, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-HRS-w9',
                         variables=list('R9BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_hrs9, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_hrs9}
HRS_ds_hrs_w9 <- tibble(id=HRS_bmi$id)
HRS_ds_hrs_w9$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_hrs_w9$obesity <- labelled(HRS_ds_hrs_w9[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_hrs9, echo=F}
Categorical_summary(var = HRS_ds_hrs_w9[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w9, aes(x=factor(HRS_ds_hrs_w9[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_hrs9, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_hrs_w9[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_hrs9, include=FALSE}
rm(HRS_bmi)
```



### Wave 10

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R10BMI`
* Label: `W10 Body Mass Index=kg/m2`
* Type of variable: `countinous`


```{r assign_hrs10, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-HRS-w10',
                         variables=list('R10BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_hrs10, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_hrs10}
HRS_ds_hrs_w10 <- tibble(id=HRS_bmi$id)
HRS_ds_hrs_w10$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_hrs_w10$obesity <- labelled(HRS_ds_hrs_w10[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_hrs10, echo=F}
Categorical_summary(var = HRS_ds_hrs_w10[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w10, aes(x=factor(HRS_ds_hrs_w10[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_hrs10, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_hrs_w10[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_hrs10, include=FALSE}
rm(HRS_bmi)
```

### Wave 11

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R11BMI`
* Label: `W11 Body Mass Index=kg/m2`
* Type of variable: `countinous`

```{r assign_hrs11, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-HRS-w11',
                         variables=list('R11BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_hrs11, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_hrs11}
HRS_ds_hrs_w11 <- tibble(id=HRS_bmi$id)
HRS_ds_hrs_w11$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_hrs_w11$obesity <- labelled(HRS_ds_hrs_w11[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_hrs11, echo=F}
Categorical_summary(var = HRS_ds_hrs_w11[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_hrs_w11, aes(x=factor(HRS_ds_hrs_w11[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_hrs11, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_hrs_w11[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_hrs11, include=FALSE}
rm(HRS_bmi)
```




### AHEAD

### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R2BMI`
* Label: `W2 Body Mass Index=kg/m2`
* Type of variable: `countinous`


```{r assign_ahead2, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-AHEAD-w2',
                         variables=list('R2BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_ahead2, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_ahead2}
HRS_ds_ahead_w2 <- tibble(id=HRS_bmi$id)
HRS_ds_ahead_w2$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_ahead_w2$obesity <- labelled(HRS_ds_ahead_w2[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ahead2, echo=F}
Categorical_summary(var = HRS_ds_ahead_w2[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w2, aes(x=factor(HRS_ds_ahead_w2[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_ahead2, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_ahead_w2[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_ahead2, include=FALSE}
rm(HRS_bmi)
```


### Wave 3

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R3BMI`
* Label: `W3 Body Mass Index=kg/m2`
* Type of variable: `countinous`


```{r assign_ahead3, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-AHEAD-w3',
                         variables=list('R3BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_ahead3, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_ahead3}
HRS_ds_ahead_w3 <- tibble(id=HRS_bmi$id)
HRS_ds_ahead_w3$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_ahead_w3$obesity <- labelled(HRS_ds_ahead_w3[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ahead3, echo=F}
Categorical_summary(var = HRS_ds_ahead_w3[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w3, aes(x=factor(HRS_ds_ahead_w3[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_ahead3, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_ahead_w3[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_ahead3, include=FALSE}
rm(HRS_bmi)
```


### Wave 4

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R4BMI`
* Label: `W4 Body Mass Index=kg/m2`
* Type of variable: `countinous`

```{r assign_ahead4, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-AHEAD-w4',
                         variables=list('R4BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_ahead4, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_ahead4}
HRS_ds_ahead_w4 <- tibble(id=HRS_bmi$id)
HRS_ds_ahead_w4$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_ahead_w4$obesity <- labelled(HRS_ds_ahead_w4[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ahead4, echo=F}
Categorical_summary(var = HRS_ds_ahead_w4[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w4, aes(x=factor(HRS_ds_ahead_w4[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_ahead4, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_ahead_w4[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_ahead4, include=FALSE}
rm(HRS_bmi)
```

### Wave 5

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R5BMI`
* Label: `W5 Body Mass Index=kg/m2`
* Type of variable: `countinous`


```{r assign_ahead5, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-AHEAD-w5',
                         variables=list('R5BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_ahead5, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_ahead5}
HRS_ds_ahead_w5 <- tibble(id=HRS_bmi$id)
HRS_ds_ahead_w5$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_ahead_w5$obesity <- labelled(HRS_ds_ahead_w5[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ahead5, echo=F}
Categorical_summary(var = HRS_ds_ahead_w5[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w5, aes(x=factor(HRS_ds_ahead_w5[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_ahead5, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_ahead_w5[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_ahead5, include=FALSE}
rm(HRS_bmi)
```




### Wave 6

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R6BMI`
* Label: `W6 Body Mass Index=kg/m2`
* Type of variable: `countinous`


```{r assign_ahead6, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-AHEAD-w6',
                         variables=list('R6BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_ahead6, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_ahead6}
HRS_ds_ahead_w6 <- tibble(id=HRS_bmi$id)
HRS_ds_ahead_w6$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_ahead_w6$obesity <- labelled(HRS_ds_ahead_w6[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ahead6, echo=F}
Categorical_summary(var = HRS_ds_ahead_w6[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w6, aes(x=factor(HRS_ds_ahead_w6[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_ahead6, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_ahead_w6[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_ahead6, include=FALSE}
rm(HRS_bmi)
```



### Wave 7

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R7BMI`
* Label: `W7 Body Mass Index=kg/m2`
* Type of variable: `countinous`

```{r assign_ahead7, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-AHEAD-w7',
                         variables=list('R7BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_ahead7, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_ahead7}
HRS_ds_ahead_w7 <- tibble(id=HRS_bmi$id)
HRS_ds_ahead_w7$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_ahead_w7$obesity <- labelled(HRS_ds_ahead_w7[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ahead7, echo=F}
Categorical_summary(var = HRS_ds_ahead_w7[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w7, aes(x=factor(HRS_ds_ahead_w7[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_ahead7, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_ahead_w7[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_ahead7, include=FALSE}
rm(HRS_bmi)
```



### Wave 8

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R8BMI`
* Label: `W8 Body Mass Index=kg/m2`
* Type of variable: `countinous`


```{r assign_ahead8, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-AHEAD-w8',
                         variables=list('R8BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_ahead8, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_ahead8}
HRS_ds_ahead_w8 <- tibble(id=HRS_bmi$id)
HRS_ds_ahead_w8$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_ahead_w8$obesity <- labelled(HRS_ds_ahead_w8[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ahead8, echo=F}
Categorical_summary(var = HRS_ds_ahead_w8[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w8, aes(x=factor(HRS_ds_ahead_w8[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_ahead8, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_ahead_w8[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_ahead8, include=FALSE}
rm(HRS_bmi)
```


### Wave 9

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R9BMI`
* Label: `W9 Body Mass Index=kg/m2`
* Type of variable: `countinous`


```{r assign_ahead9, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-AHEAD-w9',
                         variables=list('R9BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_ahead9, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_ahead9}
HRS_ds_ahead_w9 <- tibble(id=HRS_bmi$id)
HRS_ds_ahead_w9$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_ahead_w9$obesity <- labelled(HRS_ds_ahead_w9[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ahead9, echo=F}
Categorical_summary(var = HRS_ds_ahead_w9[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w9, aes(x=factor(HRS_ds_ahead_w9[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_ahead9, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_ahead_w9[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_ahead9, include=FALSE}
rm(HRS_bmi)
```



### Wave 10

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R10BMI`
* Label: `W10 Body Mass Index=kg/m2`
* Type of variable: `countinous`


```{r assign_ahead10, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-AHEAD-w10',
                         variables=list('R10BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_ahead10, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_ahead10}
HRS_ds_ahead_w10 <- tibble(id=HRS_bmi$id)
HRS_ds_ahead_w10$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_ahead_w10$obesity <- labelled(HRS_ds_ahead_w10[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ahead10, echo=F}
Categorical_summary(var = HRS_ds_ahead_w10[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w10, aes(x=factor(HRS_ds_ahead_w10[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_ahead10, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_ahead_w10[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_ahead10, include=FALSE}
rm(HRS_bmi)
```


### Wave 11

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R11BMI`
* Label: `W11 Body Mass Index=kg/m2`
* Type of variable: `countinous`


```{r assign_ahead11, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-AHEAD-w11',
                         variables=list('R11BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_ahead11, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_ahead11}
HRS_ds_ahead_w11 <- tibble(id=HRS_bmi$id)
HRS_ds_ahead_w11$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_ahead_w11$obesity <- labelled(HRS_ds_ahead_w11[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ahead11, echo=F}
Categorical_summary(var = HRS_ds_ahead_w11[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ahead_w11, aes(x=factor(HRS_ds_ahead_w11[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_ahead11, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_ahead_w11[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_ahead11, include=FALSE}
rm(HRS_bmi)
```


### CODA

### Wave 4

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R4BMI`
* Label: `W4 Body Mass Index=kg/m2`
* Type of variable: `countinous`


```{r assign_coda4, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-CODA-w4',
                         variables=list('R4BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_coda4, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_coda4}
HRS_ds_coda_w4 <- tibble(id=HRS_bmi$id)
HRS_ds_coda_w4$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_coda_w4$obesity <- labelled(HRS_ds_coda_w4[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_coda4, echo=F}
Categorical_summary(var = HRS_ds_coda_w4[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_coda_w4, aes(x=factor(HRS_ds_coda_w4[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_coda4, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_coda_w4[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_coda4, include=FALSE}
rm(HRS_bmi)
```



### Wave 5

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R5BMI`
* Label: `W5 Body Mass Index=kg/m2`
* Type of variable: `countinous`


```{r assign_coda5, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-CODA-w5',
                         variables=list('R5BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_coda5, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_coda5}
HRS_ds_coda_w5 <- tibble(id=HRS_bmi$id)
HRS_ds_coda_w5$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_coda_w5$obesity <- labelled(HRS_ds_coda_w5[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_coda5, echo=F}
Categorical_summary(var = HRS_ds_coda_w5[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_coda_w5, aes(x=factor(HRS_ds_coda_w5[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_coda5, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_coda_w5[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_coda5, include=FALSE}
rm(HRS_bmi)
```


### Wave 6

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R6BMI`
* Label: `W6 Body Mass Index=kg/m2`
* Type of variable: `countinous`

```{r assign_coda6, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-CODA-w6',
                         variables=list('R6BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_coda6, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_coda6}
HRS_ds_coda_w6 <- tibble(id=HRS_bmi$id)
HRS_ds_coda_w6$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_coda_w6$obesity <- labelled(HRS_ds_coda_w6[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_coda6, echo=F}
Categorical_summary(var = HRS_ds_coda_w6[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_coda_w6, aes(x=factor(HRS_ds_coda_w6[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_coda6, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_coda_w6[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_coda6, include=FALSE}
rm(HRS_bmi)
```


### Wave 7

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R7BMI`
* Label: `W7 Body Mass Index=kg/m2`
* Type of variable: `countinous`

```{r assign_coda7, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-CODA-w7',
                         variables=list('R7BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_coda7, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_coda7}
HRS_ds_coda_w7 <- tibble(id=HRS_bmi$id)
HRS_ds_coda_w7$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_coda_w7$obesity <- labelled(HRS_ds_coda_w7[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_coda7, echo=F}
Categorical_summary(var = HRS_ds_coda_w7[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_coda_w7, aes(x=factor(HRS_ds_coda_w7[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_coda7, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_coda_w7[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_coda7, include=FALSE}
rm(HRS_bmi)
```


### Wave 8

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R8BMI`
* Label: `W8 Body Mass Index=kg/m2`
* Type of variable: `countinous`

```{r assign_coda8, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-CODA-w8',
                         variables=list('R8BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_coda8, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_coda8}
HRS_ds_coda_w8 <- tibble(id=HRS_bmi$id)
HRS_ds_coda_w8$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_coda_w8$obesity <- labelled(HRS_ds_coda_w8[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_coda8, echo=F}
Categorical_summary(var = HRS_ds_coda_w8[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_coda_w8, aes(x=factor(HRS_ds_coda_w8[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_coda8, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_coda_w8[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_coda8, include=FALSE}
rm(HRS_bmi)
```

### Wave 9

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R9BMI`
* Label: `W9 Body Mass Index=kg/m2`
* Type of variable: `countinous`

```{r assign_coda9, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-CODA-w9',
                         variables=list('R9BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_coda9, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_coda9}
HRS_ds_coda_w9 <- tibble(id=HRS_bmi$id)
HRS_ds_coda_w9$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_coda_w9$obesity <- labelled(HRS_ds_coda_w9[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_coda9, echo=F}
Categorical_summary(var = HRS_ds_coda_w9[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_coda_w9, aes(x=factor(HRS_ds_coda_w9[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_coda9, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_coda_w9[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_coda9, include=FALSE}
rm(HRS_bmi)
```




### Wave 10

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R10BMI`
* Label: `W10 Body Mass Index=kg/m2`
* Type of variable: `countinous`

```{r assign_coda10, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-CODA-w10',
                         variables=list('R10BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_coda10, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_coda10}
HRS_ds_coda_w10 <- tibble(id=HRS_bmi$id)
HRS_ds_coda_w10$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_coda_w10$obesity <- labelled(HRS_ds_coda_w10[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_coda10, echo=F}
Categorical_summary(var = HRS_ds_coda_w10[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_coda_w10, aes(x=factor(HRS_ds_coda_w10[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_coda10, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_coda_w10[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_coda10, include=FALSE}
rm(HRS_bmi)
```


### Wave 11

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R11BMI`
* Label: `W11 Body Mass Index=kg/m2`
* Type of variable: `countinous`

```{r assign_coda11, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-CODA-w11',
                         variables=list('R11BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_coda11, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_coda11}
HRS_ds_coda_w11 <- tibble(id=HRS_bmi$id)
HRS_ds_coda_w11$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_coda_w11$obesity <- labelled(HRS_ds_coda_w11[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_coda11, echo=F}
Categorical_summary(var = HRS_ds_coda_w11[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_coda_w11, aes(x=factor(HRS_ds_coda_w11[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_coda11, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_coda_w11[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_coda11, include=FALSE}
rm(HRS_bmi)
```


### The War Baby (WB)

### Wave 4

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R4BMI`
* Label: `W4 Body Mass Index=kg/m2`
* Type of variable: `countinous`


```{r assign_wb4, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-WB-w4',
                         variables=list('R4BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_wb4, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_wb4}
HRS_ds_wb_w4 <- tibble(id=HRS_bmi$id)
HRS_ds_wb_w4$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_wb_w4$obesity <- labelled(HRS_ds_wb_w4[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_wb4, echo=F}
Categorical_summary(var = HRS_ds_wb_w4[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_wb_w4, aes(x=factor(HRS_ds_wb_w4[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_wb4, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_wb_w4[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_wb4, include=FALSE}
rm(HRS_bmi)
```


### Wave 5

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R5BMI`
* Label: `W5 Body Mass Index=kg/m2`
* Type of variable: `countinous`

```{r assign_wb5, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-WB-w5',
                         variables=list('R5BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_wb5, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_wb5}
HRS_ds_wb_w5 <- tibble(id=HRS_bmi$id)
HRS_ds_wb_w5$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_wb_w5$obesity <- labelled(HRS_ds_wb_w5[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_wb5, echo=F}
Categorical_summary(var = HRS_ds_wb_w5[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_wb_w5, aes(x=factor(HRS_ds_wb_w5[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_wb5, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_wb_w5[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_wb5, include=FALSE}
rm(HRS_bmi)
```


### Wave 6

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R6BMI`
* Label: `W6 Body Mass Index=kg/m2`
* Type of variable: `countinous`

```{r assign_wb6, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-WB-w6',
                         variables=list('R6BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_wb6, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_wb6}
HRS_ds_wb_w6 <- tibble(id=HRS_bmi$id)
HRS_ds_wb_w6$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_wb_w6$obesity <- labelled(HRS_ds_wb_w6[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_wb6, echo=F}
Categorical_summary(var = HRS_ds_wb_w6[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_wb_w6, aes(x=factor(HRS_ds_wb_w6[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_wb6, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_wb_w6[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_wb6, include=FALSE}
rm(HRS_bmi)
```


### Wave 7

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R7BMI`
* Label: `W7 Body Mass Index=kg/m2`
* Type of variable: `countinous`

```{r assign_wb7, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-WB-w7',
                         variables=list('R7BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_wb7, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_wb7}
HRS_ds_wb_w7 <- tibble(id=HRS_bmi$id)
HRS_ds_wb_w7$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_wb_w7$obesity <- labelled(HRS_ds_wb_w7[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_wb7, echo=F}
Categorical_summary(var = HRS_ds_wb_w7[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_wb_w7, aes(x=factor(HRS_ds_wb_w7[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_wb7, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_wb_w7[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_wb7, include=FALSE}
rm(HRS_bmi)
```



### Wave 8

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R8BMI`
* Label: `W8 Body Mass Index=kg/m2`
* Type of variable: `countinous`

```{r assign_wb8, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-WB-w8',
                         variables=list('R8BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_wb8, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_wb8}
HRS_ds_wb_w8 <- tibble(id=HRS_bmi$id)
HRS_ds_wb_w8$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_wb_w8$obesity <- labelled(HRS_ds_wb_w8[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_wb8, echo=F}
Categorical_summary(var = HRS_ds_wb_w8[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_wb_w8, aes(x=factor(HRS_ds_wb_w8[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_wb8, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_wb_w8[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_wb8, include=FALSE}
rm(HRS_bmi)
```




### Wave 9

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R9BMI`
* Label: `W9 Body Mass Index=kg/m2`
* Type of variable: `countinous`


```{r assign_wb9, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-WB-w9',
                         variables=list('R9BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_wb9, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_wb9}
HRS_ds_wb_w9 <- tibble(id=HRS_bmi$id)
HRS_ds_wb_w9$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_wb_w9$obesity <- labelled(HRS_ds_wb_w9[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_wb9, echo=F}
Categorical_summary(var = HRS_ds_wb_w9[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_wb_w9, aes(x=factor(HRS_ds_wb_w9[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_wb9, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_wb_w9[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_wb9, include=FALSE}
rm(HRS_bmi)
```


### Wave 10

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R10BMI`
* Label: `W10 Body Mass Index=kg/m2`
* Type of variable: `countinous`

```{r assign_wb10, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-WB-w10',
                         variables=list('R10BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_wb10, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_wb10}
HRS_ds_wb_w10 <- tibble(id=HRS_bmi$id)
HRS_ds_wb_w10$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_wb_w10$obesity <- labelled(HRS_ds_wb_w10[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_wb10, echo=F}
Categorical_summary(var = HRS_ds_wb_w10[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_wb_w10, aes(x=factor(HRS_ds_wb_w10[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_wb10, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_wb_w10[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_wb10, include=FALSE}
rm(HRS_bmi)
```


### Wave 11

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R11BMI`
* Label: `W11 Body Mass Index=kg/m2`
* Type of variable: `countinous`

```{r assign_wb11, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-WB-w11',
                         variables=list('R11BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_wb11, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_wb11}
HRS_ds_wb_w11 <- tibble(id=HRS_bmi$id)
HRS_ds_wb_w11$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_wb_w11$obesity <- labelled(HRS_ds_wb_w11[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_wb11, echo=F}
Categorical_summary(var = HRS_ds_wb_w11[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_wb_w11, aes(x=factor(HRS_ds_wb_w11[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_wb11, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_wb_w11[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_wb11, include=FALSE}
rm(HRS_bmi)
```


### The Early Baby Boomer (EBB)

### Wave 7

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R7BMI`
* Label: `W7 Body Mass Index=kg/m2`
* Type of variable: `countinous`

```{r assign_ebb7, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-EBB-w7',
                         variables=list('R7BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_ebb7, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_ebb7}
HRS_ds_ebb_w7 <- tibble(id=HRS_bmi$id)
HRS_ds_ebb_w7$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_ebb_w7$obesity <- labelled(HRS_ds_ebb_w7[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ebb7, echo=F}
Categorical_summary(var = HRS_ds_ebb_w7[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ebb_w7, aes(x=factor(HRS_ds_ebb_w7[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_ebb7, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_ebb_w7[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_ebb7, include=FALSE}
rm(HRS_bmi)
```

### Wave 8

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R8BMI`
* Label: `W8 Body Mass Index=kg/m2`
* Type of variable: `countinous`

```{r assign_ebb8, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-EBB-w8',
                         variables=list('R8BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_ebb8, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_ebb8}
HRS_ds_ebb_w8 <- tibble(id=HRS_bmi$id)
HRS_ds_ebb_w8$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_ebb_w8$obesity <- labelled(HRS_ds_ebb_w8[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ebb8, echo=F}
Categorical_summary(var = HRS_ds_ebb_w8[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ebb_w8, aes(x=factor(HRS_ds_ebb_w8[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_ebb8, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_ebb_w8[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_ebb8, include=FALSE}
rm(HRS_bmi)
```


### Wave 9

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R9BMI`
* Label: `W9 Body Mass Index=kg/m2`
* Type of variable: `countinous`


```{r assign_ebb9, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-EBB-w9',
                         variables=list('R9BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_ebb9, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_ebb9}
HRS_ds_ebb_w9 <- tibble(id=HRS_bmi$id)
HRS_ds_ebb_w9$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_ebb_w9$obesity <- labelled(HRS_ds_ebb_w9[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ebb9, echo=F}
Categorical_summary(var = HRS_ds_ebb_w9[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ebb_w9, aes(x=factor(HRS_ds_ebb_w9[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_ebb9, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_ebb_w9[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_ebb9, include=FALSE}
rm(HRS_bmi)
```


### Wave 10

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R10BMI`
* Label: `W10 Body Mass Index=kg/m2`
* Type of variable: `countinous`

```{r assign_ebb10, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-EBB-w10',
                         variables=list('R10BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_ebb10, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_ebb10}
HRS_ds_ebb_w10 <- tibble(id=HRS_bmi$id)
HRS_ds_ebb_w10$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_ebb_w10$obesity <- labelled(HRS_ds_ebb_w10[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ebb10, echo=F}
Categorical_summary(var = HRS_ds_ebb_w10[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ebb_w10, aes(x=factor(HRS_ds_ebb_w10[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_ebb10, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_ebb_w10[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_ebb10, include=FALSE}
rm(HRS_bmi)
```


### Wave 11

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R11BMI`
* Label: `W11 Weight in kilograms`
* Type of variable: `countinous`


```{r assign_ebb11, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-EBB-w11',
                         variables=list('R11BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_ebb11, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_ebb11}
HRS_ds_ebb_w11 <- tibble(id=HRS_bmi$id)
HRS_ds_ebb_w11$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_ebb_w11$obesity <- labelled(HRS_ds_ebb_w11[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ebb11, echo=F}
Categorical_summary(var = HRS_ds_ebb_w11[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_ebb_w11, aes(x=factor(HRS_ds_ebb_w11[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_ebb11, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_ebb_w11[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_ebb11, include=FALSE}
rm(HRS_bmi)
```



### The Mid Baby Boomer (MBB)


### Wave 10

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R10BMI`
* Label: `W10 Body Mass Index=kg/m2`
* Type of variable: `countinous`


```{r assign_mbb10, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-MBB-w10',
                         variables=list('R10BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_mbb10, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_mbb10}
HRS_ds_mbb_w10 <- tibble(id=HRS_bmi$id)
HRS_ds_mbb_w10$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_mbb_w10$obesity <- labelled(HRS_ds_mbb_w10[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_mbb10, echo=F}
Categorical_summary(var = HRS_ds_mbb_w10[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_mbb_w10, aes(x=factor(HRS_ds_mbb_w10[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_mbb10, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_mbb_w10[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_mbb10, include=FALSE}
rm(HRS_bmi)
```

### Wave 11

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `R11BMI`
* Label: `W11 Body Mass Index=kg/m2`
* Type of variable: `countinous`

```{r assign_mbb11, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-MBB-w11',
                         variables=list('R11BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_mbb11, echo=F}
Continuous_summary(HRS_bmi[[2]])
ggplot(HRS_bmi, aes(x=factor(HRS_bmi[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_mbb11}
HRS_ds_mbb_w11 <- tibble(id=HRS_bmi$id)
HRS_ds_mbb_w11$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_mbb_w11$obesity <- labelled(HRS_ds_mbb_w11[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_mbb11, echo=F}
Categorical_summary(var = HRS_ds_mbb_w11[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HRS_ds_mbb_w11, aes(x=factor(HRS_ds_mbb_w11[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_mbb11, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_mbb_w11[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_mbb11, include=FALSE}
rm(HRS_bmi)
```




<!--- ########################### Import to OPAL #########################-->
```{r importOPAL, echo=FALSE}
obesity <- HRS_m_ds_hrs_w1 <- HRS_ds_hrs_w1
save(obesity, file = "../RData/hrs_w1/obesity.RData")
rm(obesity)

obesity <- HRS_m_ds_hrs_w2 <- HRS_ds_hrs_w2
save(obesity, file = "../RData/hrs_w2/obesity.RData")
rm(obesity)

obesity <- HRS_m_ds_hrs_w3 <- HRS_ds_hrs_w3
save(obesity, file = "../RData/hrs_w3/obesity.RData")
rm(obesity)

obesity <- HRS_m_ds_hrs_w4 <- HRS_ds_hrs_w4
save(obesity, file = "../RData/hrs_w4/obesity.RData")
rm(obesity)

obesity <- HRS_m_ds_hrs_w5 <- HRS_ds_hrs_w5
save(obesity, file = "../RData/hrs_w5/obesity.RData")
rm(obesity)

obesity <- HRS_m_ds_hrs_w6 <- HRS_ds_hrs_w6
save(obesity, file = "../RData/hrs_w6/obesity.RData")
rm(obesity)

obesity <- HRS_m_ds_hrs_w7 <- HRS_ds_hrs_w7
save(obesity, file = "../RData/hrs_w7/obesity.RData")
rm(obesity)

obesity <- HRS_m_ds_hrs_w8 <- HRS_ds_hrs_w8
save(obesity, file = "../RData/hrs_w8/obesity.RData")
rm(obesity)

obesity <- HRS_m_ds_hrs_w9 <- HRS_ds_hrs_w9
save(obesity, file = "../RData/hrs_w9/obesity.RData")
rm(obesity)

obesity <- HRS_m_ds_hrs_w10 <- HRS_ds_hrs_w10
save(obesity, file = "../RData/hrs_w10/obesity.RData")
rm(obesity)

obesity <- HRS_m_ds_hrs_w11 <- HRS_ds_hrs_w11
save(obesity, file = "../RData/hrs_w11/obesity.RData")
rm(obesity)


obesity <- HRS_m_ds_ahead_w2 <- HRS_ds_ahead_w2
save(obesity, file = "../RData/ahead_w2/obesity.RData")
rm(obesity)

obesity <- HRS_m_ds_ahead_w3 <- HRS_ds_ahead_w3
save(obesity, file = "../RData/ahead_w3/obesity.RData")
rm(obesity)

obesity <- HRS_m_ds_ahead_w4 <- HRS_ds_ahead_w4
save(obesity, file = "../RData/ahead_w4/obesity.RData")
rm(obesity)

obesity <- HRS_m_ds_ahead_w5 <- HRS_ds_ahead_w5
save(obesity, file = "../RData/ahead_w5/obesity.RData")
rm(obesity)

obesity <- HRS_m_ds_ahead_w6 <- HRS_ds_ahead_w6
save(obesity, file = "../RData/ahead_w6/obesity.RData")
rm(obesity)

obesity <- HRS_m_ds_ahead_w7 <- HRS_ds_ahead_w7
save(obesity, file = "../RData/ahead_w7/obesity.RData")
rm(obesity)

obesity <- HRS_m_ds_ahead_w8 <- HRS_ds_ahead_w8
save(obesity, file = "../RData/ahead_w8/obesity.RData")
rm(obesity)

obesity <- HRS_m_ds_ahead_w9 <- HRS_ds_ahead_w9
save(obesity, file = "../RData/ahead_w9/obesity.RData")
rm(obesity)

obesity <- HRS_m_ds_ahead_w10 <- HRS_ds_ahead_w10
save(obesity, file = "../RData/ahead_w10/obesity.RData")
rm(obesity)

obesity <- HRS_m_ds_ahead_w11 <- HRS_ds_ahead_w11
save(obesity, file = "../RData/ahead_w11/obesity.RData")
rm(obesity)


obesity <- HRS_m_ds_coda_w4 <- HRS_ds_coda_w4
save(obesity, file = "../RData/coda_w4/obesity.RData")
rm(obesity)

obesity <- HRS_m_ds_coda_w5 <- HRS_ds_coda_w5
save(obesity, file = "../RData/coda_w5/obesity.RData")
rm(obesity)

obesity <- HRS_m_ds_coda_w6 <- HRS_ds_coda_w6
save(obesity, file = "../RData/coda_w6/obesity.RData")
rm(obesity)

obesity <- HRS_m_ds_coda_w7 <- HRS_ds_coda_w7
save(obesity, file = "../RData/coda_w7/obesity.RData")
rm(obesity)

obesity <- HRS_m_ds_coda_w8 <- HRS_ds_coda_w8
save(obesity, file = "../RData/coda_w8/obesity.RData")
rm(obesity)

obesity <- HRS_m_ds_coda_w9 <- HRS_ds_coda_w9
save(obesity, file = "../RData/coda_w9/obesity.RData")
rm(obesity)

obesity <- HRS_m_ds_coda_w10 <- HRS_ds_coda_w10
save(obesity, file = "../RData/coda_w10/obesity.RData")
rm(obesity)

obesity <- HRS_m_ds_coda_w11 <- HRS_ds_coda_w11
save(obesity, file = "../RData/coda_w11/obesity.RData")
rm(obesity)


obesity <- HRS_m_ds_wb_w4 <- HRS_ds_wb_w4
save(obesity, file = "../RData/wb_w4/obesity.RData")
rm(obesity)

obesity <- HRS_m_ds_wb_w5 <- HRS_ds_wb_w5
save(obesity, file = "../RData/wb_w5/obesity.RData")
rm(obesity)

obesity <- HRS_m_ds_wb_w6 <- HRS_ds_wb_w6
save(obesity, file = "../RData/wb_w6/obesity.RData")
rm(obesity)

obesity <- HRS_m_ds_wb_w7 <- HRS_ds_wb_w7
save(obesity, file = "../RData/wb_w7/obesity.RData")
rm(obesity)

obesity <- HRS_m_ds_wb_w8 <- HRS_ds_wb_w8
save(obesity, file = "../RData/wb_w8/obesity.RData")
rm(obesity)

obesity <- HRS_m_ds_wb_w9 <- HRS_ds_wb_w9
save(obesity, file = "../RData/wb_w9/obesity.RData")
rm(obesity)

obesity <- HRS_m_ds_wb_w10 <- HRS_ds_wb_w10
save(obesity, file = "../RData/wb_w10/obesity.RData")
rm(obesity)

obesity <- HRS_m_ds_wb_w11 <- HRS_ds_wb_w11
save(obesity, file = "../RData/wb_w11/obesity.RData")
rm(obesity)


obesity <- HRS_m_ds_ebb_w7 <- HRS_ds_ebb_w7
save(obesity, file = "../RData/ebb_w7/obesity.RData")
rm(obesity)

obesity <- HRS_m_ds_ebb_w8 <- HRS_ds_ebb_w8
save(obesity, file = "../RData/ebb_w8/obesity.RData")
rm(obesity)

obesity <- HRS_m_ds_ebb_w9 <- HRS_ds_ebb_w9
save(obesity, file = "../RData/ebb_w9/obesity.RData")
rm(obesity)

obesity <- HRS_m_ds_ebb_w10 <- HRS_ds_ebb_w10
save(obesity, file = "../RData/ebb_w10/obesity.RData")
rm(obesity)

obesity <- HRS_m_ds_ebb_w11 <- HRS_ds_ebb_w11
save(obesity, file = "../RData/ebb_w11/obesity.RData")
rm(obesity)


obesity <- HRS_m_ds_mbb_w10 <- HRS_ds_mbb_w10
save(obesity, file = "../RData/mbb_w10/obesity.RData")
rm(obesity)

obesity <- HRS_m_ds_mbb_w11 <- HRS_ds_mbb_w11
save(obesity, file = "../RData/mbb_w11/obesity.RData")
rm(obesity)


l.hds <- list(HRS_ds_hrs_w1 = HRS_ds_hrs_w1, HRS_ds_hrs_w2=HRS_ds_hrs_w2, HRS_ds_hrs_w3=HRS_ds_hrs_w3, HRS_ds_hrs_w4=HRS_ds_hrs_w4, HRS_ds_hrs_w5=HRS_ds_hrs_w5, HRS_ds_hrs_w6=HRS_ds_hrs_w6, HRS_ds_hrs_w7=HRS_ds_hrs_w7, HRS_ds_hrs_w8=HRS_ds_hrs_w8, HRS_ds_hrs_w9=HRS_ds_hrs_w9, HRS_ds_hrs_w10=HRS_ds_hrs_w10, HRS_ds_hrs_w11=HRS_ds_hrs_w11, HRS_ds_ahead_w2=HRS_ds_ahead_w2, HRS_ds_ahead_w3=HRS_ds_ahead_w3, HRS_ds_ahead_w4=HRS_ds_ahead_w4, HRS_ds_ahead_w5=HRS_ds_ahead_w5, HRS_ds_ahead_w6=HRS_ds_ahead_w6, HRS_ds_ahead_w7=HRS_ds_ahead_w7, HRS_ds_ahead_w8=HRS_ds_ahead_w8, HRS_ds_ahead_w9=HRS_ds_ahead_w9, HRS_ds_ahead_w10=HRS_ds_ahead_w10, HRS_ds_ahead_w11=HRS_ds_ahead_w11, HRS_ds_coda_w4=HRS_ds_coda_w4, HRS_ds_coda_w5=HRS_ds_coda_w5, HRS_ds_coda_w6=HRS_ds_coda_w6, HRS_ds_coda_w7=HRS_ds_coda_w7, HRS_ds_coda_w8=HRS_ds_coda_w8, HRS_ds_coda_w9=HRS_ds_coda_w9, HRS_ds_coda_w10=HRS_ds_coda_w10, HRS_ds_coda_w11=HRS_ds_coda_w11, HRS_ds_wb_w4=HRS_ds_wb_w4, HRS_ds_wb_w5=HRS_ds_wb_w5, HRS_ds_wb_w6=HRS_ds_wb_w6, HRS_ds_wb_w7=HRS_ds_wb_w7, HRS_ds_wb_w8=HRS_ds_wb_w8, HRS_ds_wb_w9=HRS_ds_wb_w9, HRS_ds_wb_w10=HRS_ds_wb_w10, HRS_ds_wb_w11=HRS_ds_wb_w11, HRS_ds_ebb_w7=HRS_ds_ebb_w7, HRS_ds_ebb_w8=HRS_ds_ebb_w8, HRS_ds_ebb_w9=HRS_ds_ebb_w9, HRS_ds_ebb_w10=HRS_ds_ebb_w10, HRS_ds_ebb_w11=HRS_ds_ebb_w11, HRS_ds_mbb_w10=HRS_ds_mbb_w10, HRS_ds_mbb_w11=HRS_ds_mbb_w11)

m.hds <- list(HRS_m_ds_hrs_w1 = HRS_m_ds_hrs_w1,  HRS_m_ds_hrs_w2=HRS_m_ds_hrs_w2, HRS_m_ds_hrs_w3=HRS_m_ds_hrs_w3, HRS_m_ds_hrs_w4=HRS_m_ds_hrs_w4, HRS_m_ds_hrs_w5=HRS_m_ds_hrs_w5, HRS_m_ds_hrs_w6=HRS_m_ds_hrs_w6, HRS_m_ds_hrs_w7=HRS_m_ds_hrs_w7, HRS_m_ds_hrs_w8=HRS_m_ds_hrs_w8, HRS_m_ds_hrs_w9=HRS_m_ds_hrs_w9, HRS_m_ds_hrs_w10=HRS_m_ds_hrs_w10, HRS_m_ds_hrs_w11=HRS_m_ds_hrs_w11, HRS_m_ds_ahead_w2=HRS_m_ds_ahead_w2, HRS_m_ds_ahead_w3=HRS_m_ds_ahead_w3, HRS_m_ds_ahead_w4=HRS_m_ds_ahead_w4, HRS_m_ds_ahead_w5=HRS_m_ds_ahead_w5, HRS_m_ds_ahead_w6=HRS_m_ds_ahead_w6, HRS_m_ds_ahead_w7=HRS_m_ds_ahead_w7, HRS_m_ds_ahead_w8=HRS_m_ds_ahead_w8, HRS_m_ds_ahead_w9=HRS_m_ds_ahead_w9, HRS_m_ds_ahead_w10=HRS_m_ds_ahead_w10, HRS_m_ds_ahead_w11=HRS_m_ds_ahead_w11, HRS_m_ds_coda_w4=HRS_m_ds_coda_w4, HRS_m_ds_coda_w5=HRS_m_ds_coda_w5, HRS_m_ds_coda_w6=HRS_m_ds_coda_w6, HRS_m_ds_coda_w7=HRS_m_ds_coda_w7, HRS_m_ds_coda_w8=HRS_m_ds_coda_w8, HRS_m_ds_coda_w9=HRS_m_ds_coda_w9, HRS_m_ds_coda_w10=HRS_m_ds_coda_w10, HRS_m_ds_coda_w11=HRS_m_ds_coda_w11, HRS_m_ds_wb_w4=HRS_m_ds_wb_w4, HRS_m_ds_wb_w5=HRS_m_ds_wb_w5, HRS_m_ds_wb_w6=HRS_m_ds_wb_w6, HRS_m_ds_wb_w7=HRS_m_ds_wb_w7, HRS_m_ds_wb_w8=HRS_m_ds_wb_w8, HRS_m_ds_wb_w9=HRS_m_ds_wb_w9, HRS_m_ds_wb_w10=HRS_m_ds_wb_w10, HRS_m_ds_wb_w11=HRS_m_ds_wb_w11, HRS_m_ds_ebb_w7=HRS_m_ds_ebb_w7, HRS_m_ds_ebb_w8=HRS_m_ds_ebb_w8, HRS_m_ds_ebb_w9=HRS_m_ds_ebb_w9, HRS_m_ds_ebb_w10=HRS_m_ds_ebb_w10, HRS_m_ds_ebb_w11=HRS_m_ds_ebb_w11, HRS_m_ds_mbb_w10=HRS_m_ds_mbb_w10, HRS_m_ds_mbb_w11=HRS_m_ds_mbb_w11)


for(i in 1:length(l.hds)) {
  label(l.hds[[i]][[2]]) <- label(m.hds[[i]][[2]]) <- ds_label # Text value assigned at the DS description, at the top.
    
  m.hds[[i]][[2]] <- car::recode(m.hds[[i]][[2]], "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
  m.hds[[i]][[2]] <- labelled(m.hds[[i]][[2]], labels = c("not obese"=0, "obese"=1))

  nl <- names(l.hds[i])
  #opal.assign.data(o, nl , l.hds[[i]])
  #opal.symbol_import(o, nl , project='_Athlos_Harm_Dataset')  

  ml <- names(m.hds[i])
  #opal.assign.data(o, ml , m.hds[[i]]) 
  #opal.symbol_import(o, ml , project='_Athlos_Harm_Dataset')  

}

```


## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable by cohort and wave:

```{r summ}

t.hds <- frq(l.hds[[2]][2])[[1]][,c(1,2)] 
for (i in 1:length(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", 
             length(l.hds[[1]][[2]]) ,length(l.hds[[2]][[2]]), length(l.hds[[3]][[2]]), length(l.hds[[4]][[2]]), length(l.hds[[5]][[2]]), length(l.hds[[6]][[2]]), length(l.hds[[7]][[2]]),length(l.hds[[8]][[2]]), length(l.hds[[9]][[2]]), length(l.hds[[10]][[2]]), length(l.hds[[11]][[2]]), length(l.hds[[12]][[2]]), length(l.hds[[13]][[2]]), length(l.hds[[14]][[2]]), length(l.hds[[15]][[2]]), length(l.hds[[16]][[2]]), length(l.hds[[17]][[2]]), length(l.hds[[18]][[2]]), length(l.hds[[19]][[2]]), length(l.hds[[20]][[2]]), length(l.hds[[21]][[2]]), length(l.hds[[22]][[2]]), length(l.hds[[23]][[2]]), length(l.hds[[24]][[2]]), length(l.hds[[25]][[2]]), length(l.hds[[26]][[2]]), length(l.hds[[27]][[2]]), length(l.hds[[28]][[2]]), length(l.hds[[29]][[2]]), length(l.hds[[30]][[2]]), length(l.hds[[31]][[2]]), length(l.hds[[32]][[2]]), length(l.hds[[33]][[2]]), length(l.hds[[34]][[2]]), length(l.hds[[35]][[2]]), length(l.hds[[36]][[2]]), length(l.hds[[37]][[2]]), length(l.hds[[38]][[2]]), length(l.hds[[39]][[2]]), length(l.hds[[40]][[2]]), length(l.hds[[41]][[2]]), length(l.hds[[42]][[2]]), length(l.hds[[43]][[2]]), length(l.hds[[44]][[2]]))
names(t.hds)<-c("val", "label", "HRS_W1", "HRS_W2", "HRS_W3", "HRS_W4", "HRS_W5", "HRS_W6", "HRS_W7", "HRS_W8", "HRS_W9", "HRS_W10", "HRS_W11", "AHEAD_W2", "AHEAD_W3", "AHEAD_W4", "AHEAD_W5", "AHEAD_W6", "AHEAD_W7", "AHEAD_W8", "AHEAD_W9", "AHEAD_W10", "AHEAD_W11", "CODA_W4", "CODA_W5", "CODA_W6", "CODA_W7", "CODA_W8", "CODA_W9", "CODA_W10", "CODA_W11", "WB_W4", "WB_W5", "WB_W6", "WB_W7", "WB_W8", "WB_W9", "WB_W10", "WB_W11", "EBB_W7", "EBB_W8", "EBB_W9", "EBB_W10", "EBB_W11", "MBB_W10", "MBB_W11")
kable(t.hds)
```


# Quality estimation
Once BMI has been calculated using weight (Kg) and Height (m^2),
Obesity was calculated by using the BMI cutoff>=30kg/m2 following the WHO 
classification. Finally, the resulting BMI variable was coded as follows: 
BMI>30kg/m2 =1 (obese); BMI<30kg/m2 =0 (not obese) to generate two categories.



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
