---
title: "Obesity"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/obesityDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/obesityDS.R')
```
# Data process



## HRS

### Wave 1

#### Study-specific variable description



| **Name** | `R1BMI`|
|-|-|
| **Label** |`W1 Body Mass Index=kg/m2`|
| **Table name** |`HRS-HRS-W1`|
| **Units** |`kg/m2`|
| **Description** |  |


```{r assign_hrs1, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-HRS-w1',
                         variables=list('R1BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_hrs1, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_hrs1}
HRS_ds_hrs_w1 <- tibble(id=HRS_bmi$id)
HRS_ds_hrs_w1$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_hrs_w1$obesity <- labelled(HRS_ds_hrs_w1[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_hrs1, echo=F}
vbl <- HRS_ds_hrs_w1[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w1, aes(x=factor(HRS_ds_hrs_w1[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_hrs1, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_hrs_w1[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_hrs1, include=FALSE}
rm(HRS_bmi)
```


### Wave 2

#### Study-specific variable description



| **Name** | `R2BMI`|
|-|-|
| **Label** |`W2 Body Mass Index=kg/m2`|
| **Table name** |`HRS-HRS-W2`|
| **Units** |`kg/m2`|
| **Description** |  |


```{r assign_hrs2, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-HRS-w2',
                         variables=list('R2BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_hrs2, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_hrs2}
HRS_ds_hrs_w2 <- tibble(id=HRS_bmi$id)
HRS_ds_hrs_w2$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_hrs_w2$obesity <- labelled(HRS_ds_hrs_w2[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_hrs2, echo=F}
vbl <- HRS_ds_hrs_w2[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w2, aes(x=factor(HRS_ds_hrs_w2[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_hrs2, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_hrs_w2[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_hrs2, include=FALSE}
rm(HRS_bmi)
```

### Wave 3

#### Study-specific variable description



| **Name** | `R3BMI`|
|-|-|
| **Label** |`W3 Body Mass Index=kg/m2`|
| **Table name** |`HRS-HRS-W3`|
| **Units** |`kg/m2`|
| **Description** |  |


```{r assign_hrs3, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-HRS-w3',
                         variables=list('R3BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_hrs3, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_hrs3}
HRS_ds_hrs_w3 <- tibble(id=HRS_bmi$id)
HRS_ds_hrs_w3$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_hrs_w3$obesity <- labelled(HRS_ds_hrs_w3[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_hrs3, echo=F}
vbl <- HRS_ds_hrs_w3[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w3, aes(x=factor(HRS_ds_hrs_w3[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_hrs3, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_hrs_w3[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_hrs3, include=FALSE}
rm(HRS_bmi)
```


### Wave 4

#### Study-specific variable description



| **Name** | `R4BMI`|
|-|-|
| **Label** |`W4 Body Mass Index=kg/m2`|
| **Table name** |`HRS-HRS-W4`|
| **Units** |`kg/m2`|
| **Description** |  |


```{r assign_hrs4, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-HRS-w4',
                         variables=list('R4BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_hrs4, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_hrs4}
HRS_ds_hrs_w4 <- tibble(id=HRS_bmi$id)
HRS_ds_hrs_w4$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_hrs_w4$obesity <- labelled(HRS_ds_hrs_w4[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_hrs4, echo=F}
vbl <- HRS_ds_hrs_w4[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w4, aes(x=factor(HRS_ds_hrs_w4[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_hrs4, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_hrs_w4[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_hrs4, include=FALSE}
rm(HRS_bmi)
```


### Wave 5

#### Study-specific variable description



| **Name** | `R5BMI`|
|-|-|
| **Label** |`W5 Body Mass Index=kg/m2`|
| **Table name** |`HRS-HRS-W5`|
| **Units** |`kg/m2`|
| **Description** |  |

```{r assign_hrs5, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-HRS-w5',
                         variables=list('R5BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_hrs5, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_hrs5}
HRS_ds_hrs_w5 <- tibble(id=HRS_bmi$id)
HRS_ds_hrs_w5$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_hrs_w5$obesity <- labelled(HRS_ds_hrs_w5[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_hrs5, echo=F}
vbl <- HRS_ds_hrs_w5[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w5, aes(x=factor(HRS_ds_hrs_w5[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_hrs5, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_hrs_w5[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_hrs5, include=FALSE}
rm(HRS_bmi)
```






### Wave 6

#### Study-specific variable description



| **Name** | `R6BMI`|
|-|-|
| **Label** |`W6 Body Mass Index=kg/m2`|
| **Table name** |`HRS-HRS-W6`|
| **Units** |`kg/m2`|
| **Description** |  |


```{r assign_hrs6, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-HRS-w6',
                         variables=list('R6BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_hrs6, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_hrs6}
HRS_ds_hrs_w6 <- tibble(id=HRS_bmi$id)
HRS_ds_hrs_w6$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_hrs_w6$obesity <- labelled(HRS_ds_hrs_w6[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_hrs6, echo=F}
vbl <- HRS_ds_hrs_w6[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w6, aes(x=factor(HRS_ds_hrs_w6[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_hrs6, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_hrs_w6[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_hrs6, include=FALSE}
rm(HRS_bmi)
```


### Wave 7

#### Study-specific variable description



| **Name** | `R7BMI`|
|-|-|
| **Label** |`W7 Body Mass Index=kg/m2`|
| **Table name** |`HRS-HRS-W7`|
| **Units** |`kg/m2`|
| **Description** |  |


```{r assign_hrs7, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-HRS-w7',
                         variables=list('R7BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_hrs7, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_hrs7}
HRS_ds_hrs_w7 <- tibble(id=HRS_bmi$id)
HRS_ds_hrs_w7$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_hrs_w7$obesity <- labelled(HRS_ds_hrs_w7[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_hrs7, echo=F}
vbl <- HRS_ds_hrs_w7[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w7, aes(x=factor(HRS_ds_hrs_w7[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_hrs7, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_hrs_w7[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_hrs7, include=FALSE}
rm(HRS_bmi)
```



### Wave 8

#### Study-specific variable description



| **Name** | `R8BMI`|
|-|-|
| **Label** |`W8 Body Mass Index=kg/m2`|
| **Table name** |`HRS-HRS-W8`|
| **Units** |`kg/m2`|
| **Description** |  |


```{r assign_hrs8, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-HRS-w8',
                         variables=list('R8BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_hrs8, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_hrs8}
HRS_ds_hrs_w8 <- tibble(id=HRS_bmi$id)
HRS_ds_hrs_w8$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_hrs_w8$obesity <- labelled(HRS_ds_hrs_w8[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_hrs8, echo=F}
vbl <- HRS_ds_hrs_w8[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w8, aes(x=factor(HRS_ds_hrs_w8[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_hrs8, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_hrs_w8[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_hrs8, include=FALSE}
rm(HRS_bmi)
```

### Wave 9

#### Study-specific variable description



| **Name** | `R9BMI`|
|-|-|
| **Label** |`W9 Body Mass Index=kg/m2`|
| **Table name** |`HRS-HRS-W9`|
| **Units** |`kg/m2`|
| **Description** |  |


```{r assign_hrs9, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-HRS-w9',
                         variables=list('R9BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_hrs9, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_hrs9}
HRS_ds_hrs_w9 <- tibble(id=HRS_bmi$id)
HRS_ds_hrs_w9$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_hrs_w9$obesity <- labelled(HRS_ds_hrs_w9[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_hrs9, echo=F}
vbl <- HRS_ds_hrs_w9[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w9, aes(x=factor(HRS_ds_hrs_w9[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_hrs9, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_hrs_w9[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_hrs9, include=FALSE}
rm(HRS_bmi)
```



### Wave 10

#### Study-specific variable description



| **Name** | `R10BMI`|
|-|-|
| **Label** |`W10 Body Mass Index=kg/m2`|
| **Table name** |`HRS-HRS-W10`|
| **Units** |`kg/m2`|
| **Description** |  |


```{r assign_hrs10, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-HRS-w10',
                         variables=list('R10BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_hrs10, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_hrs10}
HRS_ds_hrs_w10 <- tibble(id=HRS_bmi$id)
HRS_ds_hrs_w10$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_hrs_w10$obesity <- labelled(HRS_ds_hrs_w10[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_hrs10, echo=F}
vbl <- HRS_ds_hrs_w10[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w10, aes(x=factor(HRS_ds_hrs_w10[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_hrs10, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_hrs_w10[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_hrs10, include=FALSE}
rm(HRS_bmi)
```

### Wave 11

#### Study-specific variable description



| **Name** | `R11BMI`|
|-|-|
| **Label** |`W11 Body Mass Index=kg/m2`|
| **Table name** |`HRS-HRS-W11`|
| **Units** |`kg/m2`|
| **Description** |  |

```{r assign_hrs11, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-HRS-w11',
                         variables=list('R11BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_hrs11, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_hrs11}
HRS_ds_hrs_w11 <- tibble(id=HRS_bmi$id)
HRS_ds_hrs_w11$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_hrs_w11$obesity <- labelled(HRS_ds_hrs_w11[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_hrs11, echo=F}
vbl <- HRS_ds_hrs_w11[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w11, aes(x=factor(HRS_ds_hrs_w11[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_hrs11, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_hrs_w11[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_hrs11, include=FALSE}
rm(HRS_bmi)
```




## AHEAD

### Wave 2

#### Study-specific variable description



| **Name** | `R2BMI`|
|-|-|
| **Label** |`W2 Body Mass Index=kg/m2`|
| **Table name** |`HRS-AHEAD-W2`|
| **Units** |`kg/m2`|
| **Description** |  |


```{r assign_ahead2, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-AHEAD-w2',
                         variables=list('R2BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_ahead2, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_ahead2}
HRS_ds_ahead_w2 <- tibble(id=HRS_bmi$id)
HRS_ds_ahead_w2$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_ahead_w2$obesity <- labelled(HRS_ds_ahead_w2[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ahead2, echo=F}
vbl <- HRS_ds_ahead_w2[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w2, aes(x=factor(HRS_ds_ahead_w2[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_ahead2, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_ahead_w2[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_ahead2, include=FALSE}
rm(HRS_bmi)
```


### Wave 3

#### Study-specific variable description



| **Name** | `R3BMI`|
|-|-|
| **Label** |`W3 Body Mass Index=kg/m2`|
| **Table name** |`HRS-AHEAD-W3`|
| **Units** |`kg/m2`|
| **Description** |  |


```{r assign_ahead3, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-AHEAD-w3',
                         variables=list('R3BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_ahead3, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_ahead3}
HRS_ds_ahead_w3 <- tibble(id=HRS_bmi$id)
HRS_ds_ahead_w3$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_ahead_w3$obesity <- labelled(HRS_ds_ahead_w3[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ahead3, echo=F}
vbl <- HRS_ds_ahead_w3[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w3, aes(x=factor(HRS_ds_ahead_w3[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_ahead3, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_ahead_w3[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_ahead3, include=FALSE}
rm(HRS_bmi)
```


### Wave 4

#### Study-specific variable description



| **Name** | `R4BMI`|
|-|-|
| **Label** |`W4 Body Mass Index=kg/m2`|
| **Table name** |`HRS-AHEAD-W4`|
| **Units** |`kg/m2`|
| **Description** |  |

```{r assign_ahead4, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-AHEAD-w4',
                         variables=list('R4BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_ahead4, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_ahead4}
HRS_ds_ahead_w4 <- tibble(id=HRS_bmi$id)
HRS_ds_ahead_w4$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_ahead_w4$obesity <- labelled(HRS_ds_ahead_w4[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ahead4, echo=F}
vbl <- HRS_ds_ahead_w4[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w4, aes(x=factor(HRS_ds_ahead_w4[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_ahead4, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_ahead_w4[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_ahead4, include=FALSE}
rm(HRS_bmi)
```

### Wave 5

#### Study-specific variable description



| **Name** | `R5BMI`|
|-|-|
| **Label** |`W5 Body Mass Index=kg/m2`|
| **Table name** |`HRS-AHEAD-W5`|
| **Units** |`kg/m2`|
| **Description** |  |


```{r assign_ahead5, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-AHEAD-w5',
                         variables=list('R5BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_ahead5, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_ahead5}
HRS_ds_ahead_w5 <- tibble(id=HRS_bmi$id)
HRS_ds_ahead_w5$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_ahead_w5$obesity <- labelled(HRS_ds_ahead_w5[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ahead5, echo=F}
vbl <- HRS_ds_ahead_w5[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w5, aes(x=factor(HRS_ds_ahead_w5[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_ahead5, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_ahead_w5[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_ahead5, include=FALSE}
rm(HRS_bmi)
```




### Wave 6

#### Study-specific variable description



| **Name** | `R6BMI`|
|-|-|
| **Label** |`W6 Body Mass Index=kg/m2`|
| **Table name** |`HRS-AHEAD-W6`|
| **Units** |`kg/m2`|
| **Description** |  |


```{r assign_ahead6, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-AHEAD-w6',
                         variables=list('R6BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_ahead6, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_ahead6}
HRS_ds_ahead_w6 <- tibble(id=HRS_bmi$id)
HRS_ds_ahead_w6$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_ahead_w6$obesity <- labelled(HRS_ds_ahead_w6[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ahead6, echo=F}
vbl <- HRS_ds_ahead_w6[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w6, aes(x=factor(HRS_ds_ahead_w6[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_ahead6, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_ahead_w6[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_ahead6, include=FALSE}
rm(HRS_bmi)
```



### Wave 7

#### Study-specific variable description



| **Name** | `R7BMI`|
|-|-|
| **Label** |`W7 Body Mass Index=kg/m2`|
| **Table name** |`HRS-AHEAD-W7`|
| **Units** |`kg/m2`|
| **Description** |  |

```{r assign_ahead7, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-AHEAD-w7',
                         variables=list('R7BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_ahead7, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_ahead7}
HRS_ds_ahead_w7 <- tibble(id=HRS_bmi$id)
HRS_ds_ahead_w7$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_ahead_w7$obesity <- labelled(HRS_ds_ahead_w7[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ahead7, echo=F}
vbl <- HRS_ds_ahead_w7[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w7, aes(x=factor(HRS_ds_ahead_w7[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_ahead7, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_ahead_w7[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_ahead7, include=FALSE}
rm(HRS_bmi)
```



### Wave 8

#### Study-specific variable description



| **Name** | `R8BMI`|
|-|-|
| **Label** |`W8 Body Mass Index=kg/m2`|
| **Table name** |`HRS-AHEAD-W8`|
| **Units** |`kg/m2`|
| **Description** |  |


```{r assign_ahead8, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-AHEAD-w8',
                         variables=list('R8BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_ahead8, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_ahead8}
HRS_ds_ahead_w8 <- tibble(id=HRS_bmi$id)
HRS_ds_ahead_w8$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_ahead_w8$obesity <- labelled(HRS_ds_ahead_w8[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ahead8, echo=F}
vbl <- HRS_ds_ahead_w8[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w8, aes(x=factor(HRS_ds_ahead_w8[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_ahead8, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_ahead_w8[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_ahead8, include=FALSE}
rm(HRS_bmi)
```


### Wave 9

#### Study-specific variable description



| **Name** | `R9BMI`|
|-|-|
| **Label** |`W9 Body Mass Index=kg/m2`|
| **Table name** |`HRS-AHEAD-W9`|
| **Units** |`kg/m2`|
| **Description** |  |


```{r assign_ahead9, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-AHEAD-w9',
                         variables=list('R9BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_ahead9, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_ahead9}
HRS_ds_ahead_w9 <- tibble(id=HRS_bmi$id)
HRS_ds_ahead_w9$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_ahead_w9$obesity <- labelled(HRS_ds_ahead_w9[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ahead9, echo=F}
vbl <- HRS_ds_ahead_w9[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w9, aes(x=factor(HRS_ds_ahead_w9[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_ahead9, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_ahead_w9[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_ahead9, include=FALSE}
rm(HRS_bmi)
```



### Wave 10

#### Study-specific variable description



| **Name** | `R10BMI`|
|-|-|
| **Label** |`W10 Body Mass Index=kg/m2`|
| **Table name** |`HRS-AHEAD-W10`|
| **Units** |`kg/m2`|
| **Description** |  |


```{r assign_ahead10, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-AHEAD-w10',
                         variables=list('R10BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_ahead10, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_ahead10}
HRS_ds_ahead_w10 <- tibble(id=HRS_bmi$id)
HRS_ds_ahead_w10$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_ahead_w10$obesity <- labelled(HRS_ds_ahead_w10[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ahead10, echo=F}
vbl <- HRS_ds_ahead_w10[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w10, aes(x=factor(HRS_ds_ahead_w10[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_ahead10, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_ahead_w10[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_ahead10, include=FALSE}
rm(HRS_bmi)
```


### Wave 11

#### Study-specific variable description



| **Name** | `R11BMI`|
|-|-|
| **Label** |`W11 Body Mass Index=kg/m2`|
| **Table name** |`HRS-AHEAD-W11`|
| **Units** |`kg/m2`|
| **Description** |  |


```{r assign_ahead11, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-AHEAD-w11',
                         variables=list('R11BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_ahead11, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_ahead11}
HRS_ds_ahead_w11 <- tibble(id=HRS_bmi$id)
HRS_ds_ahead_w11$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_ahead_w11$obesity <- labelled(HRS_ds_ahead_w11[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ahead11, echo=F}
vbl <- HRS_ds_ahead_w11[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w11, aes(x=factor(HRS_ds_ahead_w11[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_ahead11, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_ahead_w11[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_ahead11, include=FALSE}
rm(HRS_bmi)
```


## CODA

### Wave 4

#### Study-specific variable description



| **Name** | `R4BMI`|
|-|-|
| **Label** |`W4 Body Mass Index=kg/m2`|
| **Table name** |`HRS-CODA-W4`|
| **Units** |`kg/m2`|
| **Description** |  |


```{r assign_coda4, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-CODA-w4',
                         variables=list('R4BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_coda4, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_coda4}
HRS_ds_coda_w4 <- tibble(id=HRS_bmi$id)
HRS_ds_coda_w4$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_coda_w4$obesity <- labelled(HRS_ds_coda_w4[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_coda4, echo=F}
vbl <- HRS_ds_coda_w4[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w4, aes(x=factor(HRS_ds_coda_w4[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_coda4, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_coda_w4[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_coda4, include=FALSE}
rm(HRS_bmi)
```



### Wave 5

#### Study-specific variable description



| **Name** | `R5BMI`|
|-|-|
| **Label** |`W5 Body Mass Index=kg/m2`|
| **Table name** |`HRS-CODA-W5`|
| **Units** |`kg/m2`|
| **Description** |  |


```{r assign_coda5, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-CODA-w5',
                         variables=list('R5BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_coda5, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_coda5}
HRS_ds_coda_w5 <- tibble(id=HRS_bmi$id)
HRS_ds_coda_w5$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_coda_w5$obesity <- labelled(HRS_ds_coda_w5[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_coda5, echo=F}
vbl <- HRS_ds_coda_w5[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w5, aes(x=factor(HRS_ds_coda_w5[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_coda5, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_coda_w5[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_coda5, include=FALSE}
rm(HRS_bmi)
```


### Wave 6

#### Study-specific variable description



| **Name** | `R6BMI`|
|-|-|
| **Label** |`W6 Body Mass Index=kg/m2`|
| **Table name** |`HRS-CODA-W6`|
| **Units** |`kg/m2`|
| **Description** |  |

```{r assign_coda6, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-CODA-w6',
                         variables=list('R6BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_coda6, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_coda6}
HRS_ds_coda_w6 <- tibble(id=HRS_bmi$id)
HRS_ds_coda_w6$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_coda_w6$obesity <- labelled(HRS_ds_coda_w6[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_coda6, echo=F}
vbl <- HRS_ds_coda_w6[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w6, aes(x=factor(HRS_ds_coda_w6[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_coda6, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_coda_w6[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_coda6, include=FALSE}
rm(HRS_bmi)
```


### Wave 7

#### Study-specific variable description



| **Name** | `R7BMI`|
|-|-|
| **Label** |`W7 Body Mass Index=kg/m2`|
| **Table name** |`HRS-CODA-W7`|
| **Units** |`kg/m2`|
| **Description** |  |

```{r assign_coda7, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-CODA-w7',
                         variables=list('R7BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_coda7, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_coda7}
HRS_ds_coda_w7 <- tibble(id=HRS_bmi$id)
HRS_ds_coda_w7$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_coda_w7$obesity <- labelled(HRS_ds_coda_w7[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_coda7, echo=F}
vbl <- HRS_ds_coda_w7[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w7, aes(x=factor(HRS_ds_coda_w7[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_coda7, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_coda_w7[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_coda7, include=FALSE}
rm(HRS_bmi)
```


### Wave 8

#### Study-specific variable description



| **Name** | `R8BMI`|
|-|-|
| **Label** |`W8 Body Mass Index=kg/m2`|
| **Table name** |`HRS-CODA-W8`|
| **Units** |`kg/m2`|
| **Description** |  |

```{r assign_coda8, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-CODA-w8',
                         variables=list('R8BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_coda8, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_coda8}
HRS_ds_coda_w8 <- tibble(id=HRS_bmi$id)
HRS_ds_coda_w8$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_coda_w8$obesity <- labelled(HRS_ds_coda_w8[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_coda8, echo=F}
vbl <- HRS_ds_coda_w8[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w8, aes(x=factor(HRS_ds_coda_w8[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_coda8, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_coda_w8[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_coda8, include=FALSE}
rm(HRS_bmi)
```

### Wave 9

#### Study-specific variable description



| **Name** | `R9BMI`|
|-|-|
| **Label** |`W9 Body Mass Index=kg/m2`|
| **Table name** |`HRS-CODA-W9`|
| **Units** |`kg/m2`|
| **Description** |  |

```{r assign_coda9, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-CODA-w9',
                         variables=list('R9BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_coda9, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_coda9}
HRS_ds_coda_w9 <- tibble(id=HRS_bmi$id)
HRS_ds_coda_w9$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_coda_w9$obesity <- labelled(HRS_ds_coda_w9[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_coda9, echo=F}
vbl <- HRS_ds_coda_w9[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w9, aes(x=factor(HRS_ds_coda_w9[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_coda9, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_coda_w9[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_coda9, include=FALSE}
rm(HRS_bmi)
```




### Wave 10

#### Study-specific variable description



| **Name** | `R10BMI`|
|-|-|
| **Label** |`W10 Body Mass Index=kg/m2`|
| **Table name** |`HRS-CODA-W10`|
| **Units** |`kg/m2`|
| **Description** |  |

```{r assign_coda10, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-CODA-w10',
                         variables=list('R10BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_coda10, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_coda10}
HRS_ds_coda_w10 <- tibble(id=HRS_bmi$id)
HRS_ds_coda_w10$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_coda_w10$obesity <- labelled(HRS_ds_coda_w10[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_coda10, echo=F}
vbl <- HRS_ds_coda_w10[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w10, aes(x=factor(HRS_ds_coda_w10[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_coda10, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_coda_w10[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_coda10, include=FALSE}
rm(HRS_bmi)
```


### Wave 11

#### Study-specific variable description



| **Name** | `R11BMI`|
|-|-|
| **Label** |`W11 Body Mass Index=kg/m2`|
| **Table name** |`HRS-CODA-W11`|
| **Units** |`kg/m2`|
| **Description** |  |

```{r assign_coda11, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-CODA-w11',
                         variables=list('R11BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_coda11, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_coda11}
HRS_ds_coda_w11 <- tibble(id=HRS_bmi$id)
HRS_ds_coda_w11$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_coda_w11$obesity <- labelled(HRS_ds_coda_w11[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_coda11, echo=F}
vbl <- HRS_ds_coda_w11[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w11, aes(x=factor(HRS_ds_coda_w11[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_coda11, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_coda_w11[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_coda11, include=FALSE}
rm(HRS_bmi)
```


## The War Baby (WB)

### Wave 4

#### Study-specific variable description



| **Name** | `R4BMI`|
|-|-|
| **Label** |`W4 Body Mass Index=kg/m2`|
| **Table name** |`HRS-WB-W4`|
| **Units** |`kg/m2`|
| **Description** |  |


```{r assign_wb4, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-WB-w4',
                         variables=list('R4BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_wb4, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_wb4}
HRS_ds_wb_w4 <- tibble(id=HRS_bmi$id)
HRS_ds_wb_w4$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_wb_w4$obesity <- labelled(HRS_ds_wb_w4[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_wb4, echo=F}
vbl <- HRS_ds_wb_w4[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w4, aes(x=factor(HRS_ds_wb_w4[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_wb4, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_wb_w4[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_wb4, include=FALSE}
rm(HRS_bmi)
```


### Wave 5

#### Study-specific variable description



| **Name** | `R5BMI`|
|-|-|
| **Label** |`W5 Body Mass Index=kg/m2`|
| **Table name** |`HRS-WB-W5`|
| **Units** |`kg/m2`|
| **Description** |  |

```{r assign_wb5, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-WB-w5',
                         variables=list('R5BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_wb5, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_wb5}
HRS_ds_wb_w5 <- tibble(id=HRS_bmi$id)
HRS_ds_wb_w5$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_wb_w5$obesity <- labelled(HRS_ds_wb_w5[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_wb5, echo=F}
vbl <- HRS_ds_wb_w5[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w5, aes(x=factor(HRS_ds_wb_w5[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_wb5, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_wb_w5[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_wb5, include=FALSE}
rm(HRS_bmi)
```


### Wave 6

#### Study-specific variable description



| **Name** | `R6BMI`|
|-|-|
| **Label** |`W6 Body Mass Index=kg/m2`|
| **Table name** |`HRS-WB-W6`|
| **Units** |`kg/m2`|
| **Description** |  |

```{r assign_wb6, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-WB-w6',
                         variables=list('R6BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_wb6, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_wb6}
HRS_ds_wb_w6 <- tibble(id=HRS_bmi$id)
HRS_ds_wb_w6$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_wb_w6$obesity <- labelled(HRS_ds_wb_w6[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_wb6, echo=F}
vbl <- HRS_ds_wb_w6[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w6, aes(x=factor(HRS_ds_wb_w6[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_wb6, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_wb_w6[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_wb6, include=FALSE}
rm(HRS_bmi)
```


### Wave 7

#### Study-specific variable description



| **Name** | `R7BMI`|
|-|-|
| **Label** |`W7 Body Mass Index=kg/m2`|
| **Table name** |`HRS-WB-W7`|
| **Units** |`kg/m2`|
| **Description** |  |

```{r assign_wb7, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-WB-w7',
                         variables=list('R7BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_wb7, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_wb7}
HRS_ds_wb_w7 <- tibble(id=HRS_bmi$id)
HRS_ds_wb_w7$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_wb_w7$obesity <- labelled(HRS_ds_wb_w7[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_wb7, echo=F}
vbl <- HRS_ds_wb_w7[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w7, aes(x=factor(HRS_ds_wb_w7[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_wb7, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_wb_w7[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_wb7, include=FALSE}
rm(HRS_bmi)
```



### Wave 8

#### Study-specific variable description



| **Name** | `R8BMI`|
|-|-|
| **Label** |`W8 Body Mass Index=kg/m2`|
| **Table name** |`HRS-WB-W8`|
| **Units** |`kg/m2`|
| **Description** |  |

```{r assign_wb8, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-WB-w8',
                         variables=list('R8BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_wb8, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_wb8}
HRS_ds_wb_w8 <- tibble(id=HRS_bmi$id)
HRS_ds_wb_w8$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_wb_w8$obesity <- labelled(HRS_ds_wb_w8[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_wb8, echo=F}
vbl <- HRS_ds_wb_w8[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w8, aes(x=factor(HRS_ds_wb_w8[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_wb8, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_wb_w8[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_wb8, include=FALSE}
rm(HRS_bmi)
```




### Wave 9

#### Study-specific variable description



| **Name** | `R9BMI`|
|-|-|
| **Label** |`W9 Body Mass Index=kg/m2`|
| **Table name** |`HRS-WB-W9`|
| **Units** |`kg/m2`|
| **Description** |  |


```{r assign_wb9, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-WB-w9',
                         variables=list('R9BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_wb9, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_wb9}
HRS_ds_wb_w9 <- tibble(id=HRS_bmi$id)
HRS_ds_wb_w9$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_wb_w9$obesity <- labelled(HRS_ds_wb_w9[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_wb9, echo=F}
vbl <- HRS_ds_wb_w9[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w9, aes(x=factor(HRS_ds_wb_w9[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_wb9, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_wb_w9[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_wb9, include=FALSE}
rm(HRS_bmi)
```


### Wave 10

#### Study-specific variable description



| **Name** | `R10BMI`|
|-|-|
| **Label** |`W10 Body Mass Index=kg/m2`|
| **Table name** |`HRS-WB-W10`|
| **Units** |`kg/m2`|
| **Description** |  |

```{r assign_wb10, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-WB-w10',
                         variables=list('R10BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_wb10, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_wb10}
HRS_ds_wb_w10 <- tibble(id=HRS_bmi$id)
HRS_ds_wb_w10$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_wb_w10$obesity <- labelled(HRS_ds_wb_w10[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_wb10, echo=F}
vbl <- HRS_ds_wb_w10[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w10, aes(x=factor(HRS_ds_wb_w10[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_wb10, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_wb_w10[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_wb10, include=FALSE}
rm(HRS_bmi)
```


### Wave 11

#### Study-specific variable description



| **Name** | `R11BMI`|
|-|-|
| **Label** |`W11 Body Mass Index=kg/m2`|
| **Table name** |`HRS-WB-W11`|
| **Units** |`kg/m2`|
| **Description** |  |

```{r assign_wb11, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-WB-w11',
                         variables=list('R11BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_wb11, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_wb11}
HRS_ds_wb_w11 <- tibble(id=HRS_bmi$id)
HRS_ds_wb_w11$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_wb_w11$obesity <- labelled(HRS_ds_wb_w11[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_wb11, echo=F}
vbl <- HRS_ds_wb_w11[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w11, aes(x=factor(HRS_ds_wb_w11[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_wb11, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_wb_w11[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_wb11, include=FALSE}
rm(HRS_bmi)
```


## The Early Baby Boomer (EBB)

### Wave 7

#### Study-specific variable description



| **Name** | `R7BMI`|
|-|-|
| **Label** |`W7 Body Mass Index=kg/m2`|
| **Table name** |`HRS-EBB-W7`|
| **Units** |`kg/m2`|
| **Description** |  |

```{r assign_ebb7, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-EBB-w7',
                         variables=list('R7BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_ebb7, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_ebb7}
HRS_ds_ebb_w7 <- tibble(id=HRS_bmi$id)
HRS_ds_ebb_w7$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_ebb_w7$obesity <- labelled(HRS_ds_ebb_w7[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ebb7, echo=F}
vbl <- HRS_ds_ebb_w7[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w7, aes(x=factor(HRS_ds_ebb_w7[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_ebb7, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_ebb_w7[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_ebb7, include=FALSE}
rm(HRS_bmi)
```

### Wave 8

#### Study-specific variable description



| **Name** | `R8BMI`|
|-|-|
| **Label** |`W8 Body Mass Index=kg/m2`|
| **Table name** |`HRS-EBB-W8`|
| **Units** |`kg/m2`|
| **Description** |  |

```{r assign_ebb8, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-EBB-w8',
                         variables=list('R8BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_ebb8, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_ebb8}
HRS_ds_ebb_w8 <- tibble(id=HRS_bmi$id)
HRS_ds_ebb_w8$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_ebb_w8$obesity <- labelled(HRS_ds_ebb_w8[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ebb8, echo=F}
vbl <- HRS_ds_ebb_w8[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w8, aes(x=factor(HRS_ds_ebb_w8[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_ebb8, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_ebb_w8[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_ebb8, include=FALSE}
rm(HRS_bmi)
```


### Wave 9

#### Study-specific variable description



| **Name** | `R9BMI`|
|-|-|
| **Label** |`W9 Body Mass Index=kg/m2`|
| **Table name** |`HRS-EBB-W9`|
| **Units** |`kg/m2`|
| **Description** |  |


```{r assign_ebb9, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-EBB-w9',
                         variables=list('R9BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_ebb9, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_ebb9}
HRS_ds_ebb_w9 <- tibble(id=HRS_bmi$id)
HRS_ds_ebb_w9$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_ebb_w9$obesity <- labelled(HRS_ds_ebb_w9[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ebb9, echo=F}
vbl <- HRS_ds_ebb_w9[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w9, aes(x=factor(HRS_ds_ebb_w9[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_ebb9, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_ebb_w9[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_ebb9, include=FALSE}
rm(HRS_bmi)
```


### Wave 10

#### Study-specific variable description



| **Name** | `R10BMI`|
|-|-|
| **Label** |`W10 Body Mass Index=kg/m2`|
| **Table name** |`HRS-EBB-W10`|
| **Units** |`kg/m2`|
| **Description** |  |

```{r assign_ebb10, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-EBB-w10',
                         variables=list('R10BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_ebb10, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_ebb10}
HRS_ds_ebb_w10 <- tibble(id=HRS_bmi$id)
HRS_ds_ebb_w10$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_ebb_w10$obesity <- labelled(HRS_ds_ebb_w10[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ebb10, echo=F}
vbl <- HRS_ds_ebb_w10[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w10, aes(x=factor(HRS_ds_ebb_w10[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_ebb10, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_ebb_w10[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_ebb10, include=FALSE}
rm(HRS_bmi)
```


### Wave 11

#### Study-specific variable description



| **Name** | `R11BMI`|
|-|-|
| **Label** |`W11 Weight in kilograms`|
| **Table name** |`HRS-EBB-W11`|
| **Units** |`kg/m2`|
| **Description** |  |


```{r assign_ebb11, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-EBB-w11',
                         variables=list('R11BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_ebb11, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_ebb11}
HRS_ds_ebb_w11 <- tibble(id=HRS_bmi$id)
HRS_ds_ebb_w11$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_ebb_w11$obesity <- labelled(HRS_ds_ebb_w11[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_ebb11, echo=F}
vbl <- HRS_ds_ebb_w11[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w11, aes(x=factor(HRS_ds_ebb_w11[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_ebb11, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_ebb_w11[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_ebb11, include=FALSE}
rm(HRS_bmi)
```



## The Mid Baby Boomer (MBB)


### Wave 10

#### Study-specific variable description



| **Name** | `R10BMI`|
|-|-|
| **Label** |`W10 Body Mass Index=kg/m2`|
| **Table name** |`HRS-MBB-W10`|
| **Units** |`kg/m2`|
| **Description** |  |


```{r assign_mbb10, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-MBB-w10',
                         variables=list('R10BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_mbb10, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_mbb10}
HRS_ds_mbb_w10 <- tibble(id=HRS_bmi$id)
HRS_ds_mbb_w10$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_mbb_w10$obesity <- labelled(HRS_ds_mbb_w10[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_mbb10, echo=F}
vbl <- HRS_ds_mbb_w10[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_mbb_w10, aes(x=factor(HRS_ds_mbb_w10[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_mbb10, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_mbb_w10[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_mbb10, include=FALSE}
rm(HRS_bmi)
```

### Wave 11

#### Study-specific variable description



| **Name** | `R11BMI`|
|-|-|
| **Label** |`W11 Body Mass Index=kg/m2`|
| **Table name** |`HRS-MBB-W11`|
| **Units** |`kg/m2`|
| **Description** |  |

```{r assign_mbb11, echo=F}
opal.assign.table.tibble(o, 'HRS_bmi','HRS.HRS-MBB-w11',
                         variables=list('R11BMI'), missings = TRUE)
HRS_bmi <- opal.execute(o,'HRS_bmi')
```

```{r local_mbb11, echo=F}
vbl <- HRS_bmi[[2]]
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attributes(vbl)$`spss::shortName`)
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_bmi, aes(x=vbl)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `NA into 999`

**R script:**
```{r harmo_mbb11}
HRS_ds_mbb_w11 <- tibble(id=HRS_bmi$id)
HRS_ds_mbb_w11$obesity <- car::recode(HRS_bmi[[2]], "lo:29.9999999=0; 30:hi=1; NA=999")
HRS_ds_mbb_w11$obesity <- labelled(HRS_ds_mbb_w11[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_mbb11, echo=F}
vbl <- HRS_ds_mbb_w11[[2]]
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HRS_ds_mbb_w11, aes(x=factor(HRS_ds_mbb_w11[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab_mbb11, echo=F}
BeforeH <- c(sum(na.omit(HRS_bmi[[2]])<30),sum(na.omit(HRS_bmi[[2]])>=30), sum(is.na(HRS_bmi[[2]])))
AfterH <- table(HRS_ds_mbb_w11[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","NA->999") 
kable(C)
```




```{r read_mbb11, include=FALSE}
rm(HRS_bmi)
```





## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.


```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```






```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


hrw.hrw.cw <- list(hrs_w1 = c("hrs_w1","HRS w1"), hrs_w2 = c("hrs_w2","HRS w2"), hrs_w3 = c("hrs_w3","HRS w3"), hrs_w4 = c("hrs_w4","HRS w4"), hrs_w5 = c("hrs_w5","HRS w5"), hrs_w6 = c("hrs_w6","HRS w6"), hrs_w7 = c("hrs_w7","HRS w7"), hrs_w8 = c("hrs_w8","HRS w8"), hrs_w9 = c("hrs_w9","HRS w9"), hrs_w10 = c("hrs_w10","HRS w10"), hrs_w11 = c("hrs_w11","HRS w11"))

hrw.ahead.cw <- list(ahead_w2 = c("ahead_w2","AHEAD w2"), ahead_w3 = c("ahead_w3","AHEAD w3"), ahead_w4 = c("ahead_w4","AHEAD w4"), ahead_w5 = c("ahead_w5","AHEAD w5"), ahead_w6 = c("ahead_w6","AHEAD w6"), ahead_w7 = c("ahead_w7","AHEAD w7"), ahead_w8 = c("ahead_w8","AHEAD w8"), ahead_w9 = c("ahead_w9","AHEAD w9"), ahead_w10 = c("ahead_w10","AHEAD w10"), ahead_w11 = c("ahead_w11","AHEAD w11"))

hrw.coda.cw <- list(coda_w4 = c("coda_w4","CODA w4"), coda_w5 = c("coda_w5","CODA w5"), coda_w6 = c("coda_w6","CODA w6"), coda_w7 = c("coda_w7","CODA w7"), coda_w8 = c("coda_w8","CODA w8"), coda_w9 = c("coda_w9","CODA w9"), coda_w10 = c("coda_w10","CODA w10"), coda_w11 = c("coda_w11","CODA w11"))

hrw.wb.cw <- list(wb_w4 = c("wb_w4","WB w4"), wb_w5 = c("wb_w5","WB w5"), wb_w6 = c("wb_w6","WB w6"), wb_w7 = c("wb_w7","WB w7"), wb_w8 = c("wb_w8","WB w8"), wb_w9 = c("wb_w9","WB w9"), wb_w10 = c("wb_w10","WB w10"), wb_w11 = c("wb_w11","WB w11"))

hrw.ebb.cw <- list(ebb_w7 = c("ebb_w7","EBB w7"), ebb_w8 = c("ebb_w8","EBB w8"), ebb_w9 = c("ebb_w9","EBB w9"), ebb_w10 = c("ebb_w10","EBB w10"), ebb_w11 = c("ebb_w11","EBB w11"))

hrw.mbb.cw <- list(mbb_w10 = c("mbb_w10","MBB w10"), mbb_w11 = c("mbb_w11","MBB w11"))



# HRS

# Consider only harmonised waves
l.hds <- lapply(hrw.hrw.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}






# AHEAD

# Consider only harmonised waves
l.hds <- lapply(hrw.ahead.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}





# CODA

# Consider only harmonised waves
l.hds <- lapply(hrw.coda.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}




# WB

# Consider only harmonised waves
l.hds <- lapply(hrw.wb.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



# EBB

# Consider only harmonised waves
l.hds <- lapply(hrw.ebb.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}




# MBB

# Consider only harmonised waves
l.hds <- lapply(hrw.mbb.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}


```






# Quality estimation
Once BMI has been calculated using weight (Kg) and Height (m^2),
Obesity was calculated by using the BMI cutoff>=30kg/m2 following the WHO 
classification. Finally, the resulting BMI variable was coded as follows: 
BMI>30kg/m2 =1 (obese); BMI<30kg/m2 =0 (not obese) to generate two categories.



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
