---
title: "Eye sight - Far vision"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `eye_far`
* Variable label: `Eyesight - far vision`
* Variable description: `Difficulties for far vision.`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## SHARE

### Wave 1 

#### Study-specific variable description




| **Name** | `ph043_`|
|-|-|
| **Label** | `eyesight distance` |
| **Table name** | `sharew1_rel2-6-0_ph` |
| **Categories** |`1 = excellent; 2 = very good; 3 = good; 4 = fair; 5 = poor`|
| **Missings** |`-1 = Don't know; -2 = Refusal; NA` |
| **Description** |  |



```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'SHARE_w1_eye_far','SHARE.sharew1_rel2-6-0_ph', variables=list('ph043_'), missings = TRUE)
```

```{r local w1, echo=F}
SHARE_w1_eye_far <- opal.execute(o,'SHARE_w1_eye_far')
vari <- SHARE_w1_eye_far$ph043_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = "ph043_")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
ggplot(SHARE_w1_eye_far, aes(x=factor(ph043_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Far Vision") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4, 5 into 0`
* `-1 into 998`
* `-2 into 997`
* `NA into 999` 

**R script:**
```{r harmo w1}
SHARE_ds_w1 <- tibble(id=SHARE_w1_eye_far$id)
SHARE_ds_w1$eye_far <- car::recode(SHARE_w1_eye_far$ph043_, "1 = '1';2 = '1';3 = '1';4 = '0'; 5 = '0';NA = '999';-2 = '997';-1 = '998' ")
SHARE_ds_w1$eye_far <- labelled(SHARE_ds_w1$eye_far, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vari <- SHARE_ds_w1$eye_far
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "eye_far")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w1, aes(x=factor(eye_far))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Far Vision") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(SHARE_ds_w1$eye_far)
X<-table(SHARE_w1_eye_far$ph043_)
BeforeH <- c(sum(X[6:7]),sum(X[3:5]),X[1:2],sum(is.na(SHARE_w1_eye_far$ph043_)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4,5->0","1,2,3->1","-2->997","-1->998","NA->999")
kable(C)
```






```{r importOPAL w1, echo=FALSE}

label(SHARE_ds_w1$eye_far) <- "Eyesight - far vision"
#opal.assign.data(o, 'SHARE_ds_w1', SHARE_ds_w1)
#opal.symbol_import(o,'SHARE_ds_w1', project='_Athlos_Harm_Dataset')
eye_far <- SHARE_ds_w1
save(eye_far, file = "../RData/w1/eye_far.RData")

SHARE_m_ds_w1 <- SHARE_ds_w1
SHARE_m_ds_w1$eye_far <- car::recode(SHARE_m_ds_w1$eye_far, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w1', SHARE_m_ds_w1)
#opal.symbol_import(o,'SHARE_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description




| **Name** | `ph043_`|
|-|-|
| **Label** | `eyesight distance` |
| **Table name** | `sharew2_rel2-6-0_ph` |
| **Categories** |`1 = excellent; 2 = very good; 3 = good; 4 = fair; 5 = poor; 6 = registered or legally blind`|
| **Missings** |`-1 = Don't know; -2 = Refusal; NA` |
| **Description** |  |



```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'SHARE_w2_eye_far','SHARE.sharew2_rel2-6-0_ph', variables=list('ph043_'), missings = TRUE)
```

```{r local w2, echo=F}
SHARE_w2_eye_far <- opal.execute(o,'SHARE_w2_eye_far')
vari <- SHARE_w2_eye_far$ph043_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = "ph043_")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
ggplot(SHARE_w2_eye_far, aes(x=factor(ph043_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Far Vision") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4, 5, 6 into 0`
* `-1 into 998`
* `-2 into 997`
* `NA into 999` 

**R script:**
```{r harmo w2}
SHARE_ds_w2 <- tibble(id=SHARE_w2_eye_far$id)
SHARE_ds_w2$eye_far <- car::recode(SHARE_w2_eye_far$ph043_, "1 = '1';2 = '1';3 = '1';4 = '0'; 5 = '0';6 = '0';NA = '999';-2 = '997';-1 = '998' ")
SHARE_ds_w2$eye_far <- labelled(SHARE_ds_w2$eye_far, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vari <- SHARE_ds_w2$eye_far
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "eye_far")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w2, aes(x=factor(eye_far))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Far Vision") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
AfterH <- table(SHARE_ds_w2$eye_far)
X<-table(SHARE_w2_eye_far$ph043_)
BeforeH <- c(sum(X[6:8]),sum(X[3:5]),X[1:2],sum(is.na(SHARE_w2_eye_far$ph043_)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4,5,6->0","1,2,3->1","-2->997","-1->998","NA->999")
kable(C)
```






```{r importOPAL w2, echo=FALSE}

label(SHARE_ds_w2$eye_far) <- "Eyesight - far vision"
#opal.assign.data(o, 'SHARE_ds_w2', SHARE_ds_w2)
#opal.symbol_import(o,'SHARE_ds_w2', project='_Athlos_Harm_Dataset')
eye_far <- SHARE_ds_w2
save(eye_far, file = "../RData/w2/eye_far.RData")

SHARE_m_ds_w2 <- SHARE_ds_w2
SHARE_m_ds_w2$eye_far <- car::recode(SHARE_m_ds_w2$eye_far, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w2', SHARE_m_ds_w2)
#opal.symbol_import(o,'SHARE_m_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 3

Not found.



### Wave 4 

#### Study-specific variable description




| **Name** | `ph043_`|
|-|-|
| **Label** | `eyesight distance` |
| **Table name** | `sharew4_rel1-1-1_ph` |
| **Categories** |`1 = excellent; 2 = very good; 3 = good; 4 = fair; 5 = poor`|
| **Missings** |`-1 = Don't know; -2 = Refusal; NA` |
| **Description** |  |


```{r assign w4, echo=F}
opal.assign.table.tibble(o, 'SHARE_w4_eye_far','SHARE.sharew4_rel1-1-1_ph', variables=list('ph043_'), missings = TRUE)
```

```{r local w4, echo=F}
SHARE_w4_eye_far <- opal.execute(o,'SHARE_w4_eye_far')
vari <- SHARE_w4_eye_far$ph043_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = "ph043_")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
ggplot(SHARE_w4_eye_far, aes(x=factor(ph043_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Far Vision") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4, 5 into 0`
* `-1 into 998`
* `-2 into 997`
* `NA into 999` 

**R script:**
```{r harmo w4}
SHARE_ds_w4 <- tibble(id=SHARE_w4_eye_far$id)
SHARE_ds_w4$eye_far <- car::recode(SHARE_w4_eye_far$ph043_, "1 = '1';2 = '1';3 = '1';4 = '0'; 5 = '0';NA = '999';-2 = '997';-1 = '998' ")
SHARE_ds_w4$eye_far <- labelled(SHARE_ds_w4$eye_far, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w4, echo=F}
vari <- SHARE_ds_w4$eye_far
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "eye_far")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w4, aes(x=factor(eye_far))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Far Vision") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w4, echo=F}
AfterH <- table(SHARE_ds_w4$eye_far)
X<-table(SHARE_w4_eye_far$ph043_)
BeforeH <- c(sum(X[6:7]),sum(X[3:5]),X[1:2],sum(is.na(SHARE_w4_eye_far$ph043_)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4,5->0","1,2,3->1","-2->997","-1->998","NA->999")
kable(C)
```






```{r importOPAL w4, echo=FALSE}

label(SHARE_ds_w4$eye_far) <- "Eyesight - far vision"
#opal.assign.data(o, 'SHARE_ds_w4', SHARE_ds_w4)
#opal.symbol_import(o,'SHARE_ds_w4', project='_Athlos_Harm_Dataset')
eye_far <- SHARE_ds_w4
save(eye_far, file = "../RData/w4/eye_far.RData")

SHARE_m_ds_w4 <- SHARE_ds_w4
SHARE_m_ds_w4$eye_far <- car::recode(SHARE_m_ds_w4$eye_far, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w4', SHARE_m_ds_w4)
#opal.symbol_import(o,'SHARE_m_ds_w4', project='_Athlos_Harm_Dataset')
```



### Wave 5

#### Study-specific variable description




| **Name** | `ph043_`|
|-|-|
| **Label** | `eyesight distance` |
| **Table name** | `sharew5_rel1-0-0_ph` |
| **Categories** |`1 = excellent; 2 = very good; 3 = good; 4 = fair; 5 = poor`|
| **Missings** |`-1 = Don't know; -2 = Refusal; NA` |
| **Description** |  |



```{r assign w5, echo=F}
opal.assign.table.tibble(o, 'SHARE_w5_eye_far','SHARE.sharew5_rel1-0-0_ph', variables=list('ph043_'), missings = TRUE)
```

```{r local w5, echo=F}
SHARE_w5_eye_far <- opal.execute(o,'SHARE_w5_eye_far')
vari <- SHARE_w5_eye_far$ph043_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = "ph043_")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
ggplot(SHARE_w5_eye_far, aes(x=factor(ph043_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Far Vision") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1, 2, 3 into 1` 
* `4, 5 into 0`
* `-1 into 998`
* `-2 into 997`
* `NA into 999` 

**R script:**
```{r harmo w5}
SHARE_ds_w5 <- tibble(id=SHARE_w5_eye_far$id)
SHARE_ds_w5$eye_far <- car::recode(SHARE_w5_eye_far$ph043_, "1 = '1';2 = '1';3 = '1';4 = '0'; 5 = '0';NA = '999';-2 = '997';-1 = '998' ")
SHARE_ds_w5$eye_far <- labelled(SHARE_ds_w5$eye_far, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w5, echo=F}
vari <- SHARE_ds_w5$eye_far
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "eye_far")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w5, aes(x=factor(eye_far))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Far Vision") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w5, echo=F}
AfterH <- table(SHARE_ds_w5$eye_far)
X<-table(SHARE_w5_eye_far$ph043_)
BeforeH <- c(sum(X[6:7]),sum(X[3:5]),X[1:2],sum(is.na(SHARE_w5_eye_far$ph043_)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4,5->0","1,2,3->1","-2->997","-1->998","NA->999")
kable(C)
```






```{r importOPAL w5, echo=FALSE}

label(SHARE_ds_w5$eye_far) <- "Eyesight - far vision"
#opal.assign.data(o, 'SHARE_ds_w5', SHARE_ds_w5)
#opal.symbol_import(o,'SHARE_ds_w5', project='_Athlos_Harm_Dataset')
eye_far <- SHARE_ds_w5
save(eye_far, file = "../RData/w5/eye_far.RData")

SHARE_m_ds_w5 <- SHARE_ds_w5
SHARE_m_ds_w5$eye_far <- car::recode(SHARE_m_ds_w5$eye_far, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w5', SHARE_m_ds_w5)
#opal.symbol_import(o,'SHARE_m_ds_w5', project='_Athlos_Harm_Dataset')
```




# Quality estimation
No comments.



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
