---
title: "Memory"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 

# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `memory`
* Variable label: `Difficulties with memory`
* Variable description: `Difficulties with memory`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Presence of difficulties with memory
1        | Absence of memory difficulties

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process 

## SHARE

### Wave 1 

#### Study-specific variable description


<!--
Overall in the last 30 days how much difficulty did you have with concentrating or remembering things? 
-->

| **Name** | `v4`|
|-|-|
| **Label** | `A4-B3 Memory self-rating` |
| **Table name** | `sharew1_rel2-6-0_vignettes` |
| **Categories** | `1 = None; 2 = Mild; 3 = Moderate; 4 = Severe; 5 = Extreme` |
| **Missings** | `NA` |
| **Description** |  |



```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'SHARE_w1_memory','SHARE.sharew1_rel2-6-0_vignettes', variables=list('v4'), missings = TRUE)
```

```{r local w1, echo=F}
SHARE_w1_memory <- opal.execute(o,'SHARE_w1_memory')
vari <- SHARE_w1_memory$v4
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "v4")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(SHARE_w1_memory, aes(x=factor(v4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("memory") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 None into 1` 
* `2 Mild into 0` 
* `3 Moderate into 0` 
* `4 Severe into 0` 
* `5 Extreme into 0`                                            
* `NA into 999`


**R script:**
```{r harmo w1}
SHARE_ds_w1 <- tibble(id=SHARE_w1_memory$id)
SHARE_ds_w1$memory <- car::recode(SHARE_w1_memory$v4, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0';NA = '999' ")
SHARE_ds_w1$memory <- labelled(SHARE_ds_w1$memory, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vari <- SHARE_ds_w1$memory
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "memory")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w1, aes(x=factor(memory))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("memory") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(SHARE_ds_w1$memory)
X<- table(SHARE_w1_memory$v4)
BeforeH <- c(sum(X[2:5]),X[1],sum(is.na(SHARE_w1_memory$v4)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","NA->999") 
kable(C)
```






```{r importOPAL w1, echo=FALSE}

label(SHARE_ds_w1$memory) <- "Difficulties with memory"
#opal.assign.data(o, 'SHARE_ds_w1', SHARE_ds_w1)
#opal.symbol_import(o,'SHARE_ds_w1', project='_Athlos_Harm_Dataset')
memory <- SHARE_ds_w1
save(memory, file = "../RData/w1/memory.RData")

SHARE_m_ds_w1 <- SHARE_ds_w1
SHARE_m_ds_w1$memory <- car::recode(SHARE_m_ds_w1$memory, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w1', SHARE_m_ds_w1)
#opal.symbol_import(o,'SHARE_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description


<!--
Overall in the last 30 days how much difficulty did you have with concentrating or remembering things? 
-->

| **Name** | `v4`|
|-|-|
| **Label** | `How would you rate your day-to-day memory at the present time?` |
| **Table name** | `sharew2_rel2-6-0_vignettes` |
| **Categories** | `1 = None; 2 = Mild; 3 = Moderate; 4 = Severe; 5 = Extreme` |
| **Missings** | `-5 = Not answered; NA` |
| **Description** |  |


```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'SHARE_w2_memory','SHARE.sharew2_rel2-6-0_vignettes', variables=list('v4'), missings = TRUE)
```

```{r local w2, echo=F}
SHARE_w2_memory <- opal.execute(o,'SHARE_w2_memory')
vari <- SHARE_w2_memory$v4
kable(Categorical_summary(vari, missing_values = c(-5))[3], caption = "v4")
kable(Categorical_summary(vari, missing_values = c(-5))[1], caption = "Category")
ggplot(SHARE_w2_memory, aes(x=factor(v4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("memory") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 None into 1` 
* `2 Mild into 0` 
* `3 Moderate into 0` 
* `4 Severe into 0` 
* `5 Extreme into 0`                                            
* `-5 Not answered into 995` 
* `NA into 999`


**R script:**
```{r harmo w2}
SHARE_ds_w2 <- tibble(id=SHARE_w2_memory$id)
SHARE_ds_w2$memory <- car::recode(SHARE_w2_memory$v4, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0';-5 = '995'; NA = '999' ")
SHARE_ds_w2$memory <- labelled(SHARE_ds_w2$memory, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vari <- SHARE_ds_w2$memory
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "memory")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w2, aes(x=factor(memory))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("memory") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
AfterH <- table(SHARE_ds_w2$memory)
X <- table(SHARE_w2_memory$v4)
BeforeH <- c(sum(X[3:6]),X[2:1],sum(is.na(SHARE_w2_memory$v4)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1->1","-5->995","NA->999") 
kable(C)
```






```{r importOPAL w2, echo=FALSE}

label(SHARE_ds_w2$memory) <- "Difficulties with memory"
#opal.assign.data(o, 'SHARE_ds_w2', SHARE_ds_w2)
#opal.symbol_import(o,'SHARE_ds_w2', project='_Athlos_Harm_Dataset')
memory <- SHARE_ds_w2
save(memory, file = "../RData/w2/memory.RData")

SHARE_m_ds_w2 <- SHARE_ds_w2
SHARE_m_ds_w2$memory <- car::recode(SHARE_m_ds_w2$memory, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w2', SHARE_m_ds_w2)
#opal.symbol_import(o,'SHARE_m_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 3

Not found.

### Wave 4

<!--
How would you rate your memory at the present time?
-->
#### Study-specific variable description

| **Name** | `cf103_`|
|-|-|
| **Label** | `memory` |
| **Table name** | `sharew4_rel1-1-1_cf` |
| **Categories** | `1 = excellent; 2 = very good; 3 = good; 4 = fair; 5 = poor` |
| **Missings** | `-2 = refusal; -1 = don't know; NA` |
| **Description** |  |

```{r assign w4, echo=F}
opal.assign.table.tibble(o, 'SHARE_w4_memory','SHARE.sharew4_rel1-1-1_cf', variables=list('cf103_'), missings = TRUE)
```

```{r local w4, echo=F}
SHARE_w4_memory <- opal.execute(o,'SHARE_w4_memory')
vari <- SHARE_w4_memory$cf103_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = "cf103_")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
ggplot(SHARE_w4_memory, aes(x=factor(cf103_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("memory") + ylab("Frequency")
```




#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 excellent into 1` 
* `2 very good into 1` 
* `3 good into 1` 
* `4 fair into 0` 
* `5 poor into 0`                                            
* `-2 refusal into 997`
* `-1 don't know into 998`
* `NA into 999`


**R script:**
```{r harmo w4}
SHARE_ds_w4 <- tibble(id=SHARE_w4_memory$id)
SHARE_ds_w4$memory <- car::recode(SHARE_w4_memory$cf103_, "1 = '1';2 = '1';3 = '1';4 = '0';5 = '0';-2 = '997';-1 = '998'; NA = '999' ")
SHARE_ds_w4$memory <- labelled(SHARE_ds_w4$memory, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w4, echo=F}
vari <- SHARE_ds_w4$memory
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "memory")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w4, aes(x=factor(memory))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("memory") + ylab("Frequency")
```



#### Validation
```{r crosstabulation w4, echo=F}
AfterH <- table(SHARE_ds_w4$memory)
X <- table(SHARE_w4_memory$cf103_)
BeforeH <- c(sum(X[6:7]),sum(X[3:5]),X[1:2],sum(is.na(SHARE_w4_memory$cf103_)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4,5->0","1,2,3->1","-2->997","-1->998","NA->999") 
kable(C)
```






```{r importOPAL w4, echo=FALSE}

label(SHARE_ds_w4$memory) <- "Difficulties with memory"
#opal.assign.data(o, 'SHARE_ds_w4', SHARE_ds_w4)
#opal.symbol_import(o,'SHARE_ds_w4', project='_Athlos_Harm_Dataset')
memory <- SHARE_ds_w4
save(memory, file = "../RData/w4/memory.RData")

SHARE_m_ds_w4 <- SHARE_ds_w4
SHARE_m_ds_w4$memory <- car::recode(SHARE_m_ds_w4$memory, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w4', SHARE_m_ds_w4)
#opal.symbol_import(o,'SHARE_m_ds_w4', project='_Athlos_Harm_Dataset')
```





### Wave 5


<!--
How would you rate your memory at the present time?
-->
#### Study-specific variable description

| **Name** | `cf103_`|
|-|-|
| **Label** | `memory` |
| **Table name** | `sharew5_rel1-0-0_cf` |
| **Categories** | `1 = Excellent; 2 = Very good; 3 = Good; 4 = Fair; 5 = Poor` |
| **Missings** | `-2 = Refusal; -1 = Don't know; NA` |
| **Description** |  |

```{r assign w5, echo=F}
opal.assign.table.tibble(o, 'SHARE_w5_memory','SHARE.sharew5_rel1-0-0_cf', variables=list('cf103_'), missings = TRUE)
```

```{r local w5, echo=F}
SHARE_w5_memory <- opal.execute(o,'SHARE_w5_memory')
vari <- SHARE_w5_memory$cf103_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = "cf103_")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
ggplot(SHARE_w5_memory, aes(x=factor(cf103_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("memory") + ylab("Frequency")
```




#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 excellent into 1` 
* `2 very good into 1` 
* `3 good into 1` 
* `4 fair into 0` 
* `5 poor into 0`                                            
* `-2 refusal into 997`
* `-1 don't know into 998`
* `NA into 999`


**R script:**
```{r harmo w5}
SHARE_ds_w5 <- tibble(id=SHARE_w5_memory$id)
SHARE_ds_w5$memory <- car::recode(SHARE_w5_memory$cf103_, "1 = '1';2 = '1';3 = '1';4 = '0';5 = '0';-2 = '997';-1 = '998'; NA = '999' ")
SHARE_ds_w5$memory <- labelled(SHARE_ds_w5$memory, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w5, echo=F}
vari <- SHARE_ds_w5$memory
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "memory")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w5, aes(x=factor(memory))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("memory") + ylab("Frequency")
```



#### Validation
```{r crosstabulation w5, echo=F}
AfterH <- table(SHARE_ds_w5$memory)
X <- table(SHARE_w5_memory$cf103_)
BeforeH <- c(sum(X[6:7]),sum(X[3:5]),X[1:2],sum(is.na(SHARE_w5_memory$cf103_)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4,5->0","1,2,3->1","-2->997","-1->998","NA->999") 
kable(C)
```






```{r importOPAL w5, echo=FALSE}

label(SHARE_ds_w5$memory) <- "Difficulties with memory"
#opal.assign.data(o, 'SHARE_ds_w5', SHARE_ds_w5)
#opal.symbol_import(o,'SHARE_ds_w5', project='_Athlos_Harm_Dataset')
memory <- SHARE_ds_w5
save(memory, file = "../RData/w5/memory.RData")

SHARE_m_ds_w5 <- SHARE_ds_w5
SHARE_m_ds_w5$memory <- car::recode(SHARE_m_ds_w5$memory, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w5', SHARE_m_ds_w5)
#opal.symbol_import(o,'SHARE_m_ds_w5', project='_Athlos_Harm_Dataset')
```




# Quality estimation
No comments (Here category 4=0: self reported memory: fair=difficulties 
with memory could be revised... not sure whether it shout be recodified as 1= no difficulties).




In the first two waves there is a higher percentage of people having problems of memory. This can be due to the 'mild' original category, which is considered as an indicator of difficulties, as it is done along other studies and variables.

```{r closeRsession, echo=FALSE}
opal.logout(o)
```

