---
title: "ADL- Moving around the home"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `adl_moving`
* Variable label: `ADL-Difficulties for moving around the home`
* Variable description: `ADL-Difficulties for moving around the home`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




<!-- ########################################################## --> 

# Data process

```{r, dataDirectory, echo=FALSE}
datafolder <- "../RData"
```

## SHARE
### Wave 1

#### Study-specific variable description

 

| **Name** | `ph049d2`|
|-|-|
| **Label** | `difficulties: walking across a room` |
| **Table name** |`sharew1_rel2-6-0_ph`|
| **Categories** |`0 = Not selected; 1 = Selected`|
| **Missings** |`-1 = Don't know; -2 = Refusal; NA`|
| **Description** |  |



* Description: 
```{r assign w1,  echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_w1_adl_moving','SHARE.sharew1_rel2-6-0_ph', variables=list('ph049d2'), missings = TRUE)
```

```{r local w1,  echo=FALSE}
SHARE_w1_adl_moving <- opal.execute(o,'SHARE_w1_adl_moving')
vari <- SHARE_w1_adl_moving$ph049d2
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
#Categorical_summary(SHARE_w1_adl_moving$ph049d2)
ggplot(SHARE_w1_adl_moving, aes(x=factor(ph049d2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Moving around the home") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `-1 into 998`
* `-2 into 997`
* `NA into 999`

**R script:** 
```{r harmo w1,   echo=TRUE}
SHARE_ds_w1 <- tibble(id=SHARE_w1_adl_moving$id)
SHARE_ds_w1$adl_moving <- car::recode(SHARE_w1_adl_moving$ph049d2, "1 = '0';0 = '1';-1 = '998';-2 = '997'; NA = '999' ")
SHARE_ds_w1$adl_moving <- labelled(SHARE_ds_w1$adl_moving, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1,  echo=FALSE}
vari <- SHARE_ds_w1$adl_moving # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_ds_w1$adl_moving, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SHARE_ds_w1, aes(x=factor(adl_moving))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Moving around the home") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1,  echo=FALSE}
AfterH <- table(SHARE_ds_w1$adl_moving)
X<-table(SHARE_w1_adl_moving$ph049d2)
BeforeH <- c(X[c(4,3,1,2)],sum(is.na(SHARE_w1_adl_moving$ph049d2)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","-2->997","-1->998","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL w1, echo=FALSE,  echo=FALSE}
val_labels(SHARE_ds_w1) <- NULL
label(SHARE_ds_w1$adl_moving) <- "Difficulties for moving around the home"
#opal.assign.data(o, 'SHARE_ds_w1', SHARE_ds_w1)
#opal.symbol_import(o,'SHARE_ds_w1', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w1 <- SHARE_ds_w1
SHARE_m_ds_w1$adl_moving <- car::recode(SHARE_m_ds_w1$adl_moving, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w1', SHARE_m_ds_w1)
#opal.symbol_import(o,'SHARE_m_ds_w1', project='_Athlos_Harm_Dataset')
```


```{r,  echo=FALSE}
adl_moving<- SHARE_ds_w1
save(adl_moving, file = paste0(datafolder, "/w1/adl_moving.RData"))
```


### Wave 2

#### Study-specific variable description

 

| **Name** | `ph049d2`|
|-|-|
| **Label** | `difficulties: walking across a room` |
| **Table name** |`sharew2_rel2-6-0_ph`|
| **Categories** |`0 = Not selected; 1 = Selected`|
| **Missings** |`-1 = Don't know; -2 = Refusal; NA`|
| **Description** |  |
 
```{r assign w2,  echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_w2_adl_moving','SHARE.sharew2_rel2-6-0_ph', variables=list('ph049d2'), missings = TRUE)
```

```{r local w2,  echo=FALSE}
SHARE_w2_adl_moving <- opal.execute(o,'SHARE_w2_adl_moving')
vari <- SHARE_w2_adl_moving$ph049d2
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
#Categorical_summary(SHARE_w2_adl_moving$ph049d2)
ggplot(SHARE_w2_adl_moving, aes(x=factor(ph049d2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Moving around the home") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `-1 into 998`
* `-2 into 997`
* `NA into 999`

**R script:** 
```{r harmo w2,   echo=TRUE}
SHARE_ds_w2 <- tibble(id=SHARE_w2_adl_moving$id)
SHARE_ds_w2$adl_moving <- car::recode(SHARE_w2_adl_moving$ph049d2, "1 = '0';0 = '1';-1 = '998';-2 = '997'; NA = '999' ")
SHARE_ds_w2$adl_moving <- labelled(SHARE_ds_w2$adl_moving, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2,  echo=FALSE}
vari <- SHARE_ds_w2$adl_moving # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_ds_w2$adl_moving, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SHARE_ds_w2, aes(x=factor(adl_moving))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Moving around the home") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2,  echo=FALSE}
AfterH <- table(SHARE_ds_w2$adl_moving)
X<-table(SHARE_w2_adl_moving$ph049d2)
BeforeH <- c(X[c(4,3,1,2)],sum(is.na(SHARE_w2_adl_moving$ph049d2)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","-2->997","-1->998","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL w2, echo=FALSE,  echo=FALSE}
val_labels(SHARE_ds_w2) <- NULL
label(SHARE_ds_w2$adl_moving) <- "Difficulties for moving around the home"
#opal.assign.data(o, 'SHARE_ds_w2', SHARE_ds_w2)
#opal.symbol_import(o,'SHARE_ds_w2', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w2 <- SHARE_ds_w2
SHARE_m_ds_w2$adl_moving <- car::recode(SHARE_m_ds_w2$adl_moving, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w2', SHARE_m_ds_w2)
#opal.symbol_import(o,'SHARE_m_ds_w2', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
adl_moving<- SHARE_ds_w2
save(adl_moving, file = paste0(datafolder, "/w2/adl_moving.RData"))
```

### Wave 3

Not found.



### Wave 4

#### Study-specific variable description

 


| **Name** | `ph049d2`|
|-|-|
| **Label** | `difficulties: walking across a room` |
| **Table name** |`sharew4_rel1-1-1_ph`|
| **Categories** |`0 = Not selected; 1 = Selected`|
| **Missings** |`-1 = Don't know; -2 = Refusal; NA`|
| **Description** |  |
  
```{r assign w4,  echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_w4_adl_moving','SHARE.sharew4_rel1-1-1_ph', variables=list('ph049d2'), missings = TRUE)
```

```{r local w4,  echo=FALSE}
SHARE_w4_adl_moving <- opal.execute(o,'SHARE_w4_adl_moving')
vari <- SHARE_w4_adl_moving$ph049d2
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
#Categorical_summary(SHARE_w4_adl_moving$ph049d2)
ggplot(SHARE_w4_adl_moving, aes(x=factor(ph049d2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Moving around the home") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `-1 into 998`
* `-2 into 997`
* `NA into 999`

**R script:** 
```{r harmo w4,   echo=TRUE}
SHARE_ds_w4 <- tibble(id=SHARE_w4_adl_moving$id)
SHARE_ds_w4$adl_moving <- car::recode(SHARE_w4_adl_moving$ph049d2, "1 = '0';0 = '1';-1 = '998';-2 = '997'; NA = '999' ")
SHARE_ds_w4$adl_moving <- labelled(SHARE_ds_w4$adl_moving, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w4,  echo=FALSE}
vari <- SHARE_ds_w4$adl_moving # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_ds_w4$adl_moving, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SHARE_ds_w4, aes(x=factor(adl_moving))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Moving around the home") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w4,  echo=FALSE}
AfterH <- table(SHARE_ds_w4$adl_moving)
X<-table(SHARE_w4_adl_moving$ph049d2)
BeforeH <- c(X[c(4,3,1,2)],sum(is.na(SHARE_w4_adl_moving$ph049d2)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","-2->997","-1->998","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL w4, echo=FALSE,  echo=FALSE}
val_labels(SHARE_ds_w4) <- NULL
label(SHARE_ds_w4$adl_moving) <- "Difficulties for moving around the home"
#opal.assign.data(o, 'SHARE_ds_w4', SHARE_ds_w4)
#opal.symbol_import(o,'SHARE_ds_w4', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w4 <- SHARE_ds_w4
SHARE_m_ds_w4$adl_moving <- car::recode(SHARE_m_ds_w4$adl_moving, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w4', SHARE_m_ds_w4)
#opal.symbol_import(o,'SHARE_m_ds_w4', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
adl_moving<- SHARE_ds_w4
save(adl_moving, file = paste0(datafolder, "/w4/adl_moving.RData"))
```

### Wave 5

#### Study-specific variable description

 


| **Name** | `ph049d2`|
|-|-|
| **Label** | `difficulties: walking across a room` |
| **Table name** |`sharew5_rel1-0-0_ph`|
| **Categories** |`0 = Not selected; 1 = Selected`|
| **Missings** |`-1 = Don't know; -2 = Refusal; NA`|
| **Description** |  |
   
```{r assign w5,  echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_w5_adl_moving','SHARE.sharew5_rel1-0-0_ph', variables=list('ph049d2'), missings = TRUE)
```

```{r local w5,  echo=FALSE}
SHARE_w5_adl_moving <- opal.execute(o,'SHARE_w5_adl_moving')
vari <- SHARE_w5_adl_moving$ph049d2
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
#Categorical_summary(SHARE_w5_adl_moving$ph049d2)
ggplot(SHARE_w5_adl_moving, aes(x=factor(ph049d2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Moving around the home") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `-1 into 998`
* `-2 into 997`
* `NA into 999`

**R script:** 
```{r harmo w5,   echo=TRUE}
SHARE_ds_w5 <- tibble(id=SHARE_w5_adl_moving$id)
SHARE_ds_w5$adl_moving <- car::recode(SHARE_w5_adl_moving$ph049d2, "1 = '0';0 = '1';-1 = '998';-2 = '997'; NA = '999' ")
SHARE_ds_w5$adl_moving <- labelled(SHARE_ds_w5$adl_moving, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w5,  echo=FALSE}
vari <- SHARE_ds_w5$adl_moving # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = SHARE_ds_w5$adl_moving, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(SHARE_ds_w5, aes(x=factor(adl_moving))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Moving around the home") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w5,  echo=FALSE}
AfterH <- table(SHARE_ds_w5$adl_moving)
X<-table(SHARE_w5_adl_moving$ph049d2)
BeforeH <- c(X[c(4,3,1,2)],sum(is.na(SHARE_w5_adl_moving$ph049d2)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","-2->997","-1->998","NA->999") 
kable(C)
```

 
 


 
```{r importOPAL w5, echo=FALSE,  echo=FALSE}
val_labels(SHARE_ds_w5) <- NULL
label(SHARE_ds_w5$adl_moving) <- "Difficulties for moving around the home"
#opal.assign.data(o, 'SHARE_ds_w5', SHARE_ds_w5)
#opal.symbol_import(o,'SHARE_ds_w5', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w5 <- SHARE_ds_w5
SHARE_m_ds_w5$adl_moving <- car::recode(SHARE_m_ds_w5$adl_moving, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w5', SHARE_m_ds_w5)
#opal.symbol_import(o,'SHARE_m_ds_w5', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
adl_moving<- SHARE_ds_w5
save(adl_moving, file = paste0(datafolder, "/w5/adl_moving.RData"))
```

# Quality estimation

No comments

```{r closeRsession, echo=FALSE,  echo=FALSE}
opal.logout(o)
```
