---
title: "Limitations in ADLs - Shopping for groceries"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `iadl_shopping`
* Variable label: `IADL - Difficulties for shopping groceries`
* Variable description: `IADL - Difficulties for shopping groceries`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:


**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not applicable
995 | Does not answer
996 | Not attempt/not done
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "IADL - Difficulties for shopping groceries"
```


# Data process

## SHARE

### Wave 1 

#### Study-specific variable description



| **Name** | `ph049d9`|
|-|-|
| **Label** | `difficulties: shopping for groceries` |
| **Table name** |`sharew1_rel2-6-0_ph`|
| **Categories** |`0 = Not selected; 1 = Selected`|
| **Missings** |`-1 = Don't know; -2 = Refusal; NA`|
| **Description** |  |


   
```{r assign w1, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_w1_iadl_shopping','SHARE.sharew1_rel2-6-0_ph', variables=list('ph049d9'), missings = TRUE)
SHARE_w1_iadl_shopping <- opal.execute(o,'SHARE_w1_iadl_shopping')
```

```{r local w1, echo=FALSE}
vari <- SHARE_w1_iadl_shopping$ph049d9
kable(Categorical_summary(vari, missing_values = c(-1, -2))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-1, -2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1, -2))[2], caption = "Type of missing")
ggplot(SHARE_w1_iadl_shopping, aes(x=factor(ph049d9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Shopping for groceries") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `-1 into 998`
* `-2 into 997`
* `NA into 999`

**R script:**

```{r harmo w1}
SHARE_ds_w1 <- tibble(id=SHARE_w1_iadl_shopping$id)
SHARE_ds_w1$iadl_shopping <- car::recode(SHARE_w1_iadl_shopping$ph049d9, "1 = '0';0 = '1';-1 = '998';-2 = '997'; NA = '999' ")
SHARE_ds_w1$iadl_shopping <- labelled(SHARE_ds_w1$iadl_shopping, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=FALSE}
vari <- SHARE_ds_w1$iadl_shopping
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w1, aes(x=factor(iadl_shopping))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Shopping for groceries") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=FALSE}
AfterH <- table(SHARE_ds_w1$iadl_shopping)
X<-table(SHARE_w1_iadl_shopping$ph049d9)
BeforeH <- c(X[c(4,3,1,2)],sum(is.na(SHARE_w1_iadl_shopping$ph049d9)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","-2->997","-1->998","NA->999") 
kable(C)
```

```{r importOPAL w1, echo=FALSE}
label(SHARE_ds_w1$iadl_shopping) <- ds_label
iadl_shopping <- SHARE_ds_w1
save(iadl_shopping, file = "../RData/w1/iadl_shopping.RData")
#opal.assign.data(o, 'SHARE_ds_w1', SHARE_ds_w1)
#opal.symbol_import(o,'SHARE_ds_w1', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w1 <- SHARE_ds_w1
SHARE_m_ds_w1$iadl_shopping <- car::recode(SHARE_m_ds_w1$iadl_shopping, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w1', SHARE_m_ds_w1)
#opal.symbol_import(o,'SHARE_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description



| **Name** | `ph049d9`|
|-|-|
| **Label** | `difficulties: shopping for groceries` |
| **Table name** |`sharew2_rel2-6-0_ph`|
| **Categories** |`0 = Not selected; 1 = Selected`|
| **Missings** |`-1 = Don't know; -2 = Refusal; NA`|
| **Description** |  |

   
```{r assign w2, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_w2_iadl_shopping','SHARE.sharew2_rel2-6-0_ph', variables=list('ph049d9'), missings = TRUE)
SHARE_w2_iadl_shopping <- opal.execute(o,'SHARE_w2_iadl_shopping')
```

```{r local w2, echo=FALSE}
vari <- SHARE_w2_iadl_shopping$ph049d9
kable(Categorical_summary(vari, missing_values = c(-1, -2))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-1, -2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1, -2))[2], caption = "Type of missing")
ggplot(SHARE_w2_iadl_shopping, aes(x=factor(ph049d9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Shopping for groceries") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `-1 into 998`
* `-2 into 997`
* `NA into 999`

**R script:**

```{r harmo w2}
SHARE_ds_w2 <- tibble(id=SHARE_w2_iadl_shopping$id)
SHARE_ds_w2$iadl_shopping <- car::recode(SHARE_w2_iadl_shopping$ph049d9, "1 = '0';0 = '1';-1 = '998';-2 = '997'; NA = '999' ")
SHARE_ds_w2$iadl_shopping <- labelled(SHARE_ds_w2$iadl_shopping, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=FALSE}
vari <- SHARE_ds_w2$iadl_shopping
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w2, aes(x=factor(iadl_shopping))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Shopping for groceries") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=FALSE}
AfterH <- table(SHARE_ds_w2$iadl_shopping)
X<-table(SHARE_w2_iadl_shopping$ph049d9)
BeforeH <- c(X[c(4,3,1,2)],sum(is.na(SHARE_w2_iadl_shopping$ph049d9)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","-2->997","-1->998","NA->999") 
kable(C)
```

```{r importOPAL w2, echo=FALSE}
label(SHARE_ds_w2$iadl_shopping) <- ds_label
iadl_shopping <- SHARE_ds_w2
save(iadl_shopping, file = "../RData/w2/iadl_shopping.RData")
#opal.assign.data(o, 'SHARE_ds_w2', SHARE_ds_w2)
#opal.symbol_import(o,'SHARE_ds_w2', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w2 <- SHARE_ds_w2
SHARE_m_ds_w2$iadl_shopping <- car::recode(SHARE_m_ds_w2$iadl_shopping, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w2', SHARE_m_ds_w2)
#opal.symbol_import(o,'SHARE_m_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 3 

#### Study-specific variable description


| **Name** | `sl_xt020d8`|
|-|-|
| **Label** | `difficulties: shopping for groceries` |
| **Table name** |`sharew3_rel1_xt`|
| **Categories** |`0 = Not selected; 1 = Selected`|
| **Missings** |`-1 = Don't know; -2 = Refusal; NA`|
| **Description** |  |

   
```{r assign w3, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_w3_iadl_shopping','SHARE.sharew3_rel1_xt', variables=list('sl_xt020d8'), missings = TRUE)
SHARE_w3_iadl_shopping <- opal.execute(o,'SHARE_w3_iadl_shopping')
```

```{r local w3, echo=FALSE}
vari <- SHARE_w3_iadl_shopping$sl_xt020d8
kable(Categorical_summary(vari, missing_values = c(-1, -2))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-1, -2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1, -2))[2], caption = "Type of missing")
ggplot(SHARE_w3_iadl_shopping, aes(x=factor(sl_xt020d8))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Shopping for groceries") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `-1 into 998`
* `-2 into 997`
* `NA into 999`

**R script:**


```{r harmo w3}
SHARE_ds_w3 <- tibble(id=SHARE_w3_iadl_shopping$id)
SHARE_ds_w3$iadl_shopping <- car::recode(SHARE_w3_iadl_shopping$sl_xt020d8, "1 = '0';0 = '1';-1 = '998';-2 = '997'; NA = '999' ")
SHARE_ds_w3$iadl_shopping <- labelled(SHARE_ds_w3$iadl_shopping, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=FALSE}
vari <- SHARE_ds_w3$iadl_shopping
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w3, aes(x=factor(iadl_shopping))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Shopping for groceries") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=FALSE}
AfterH <- table(SHARE_ds_w3$iadl_shopping)
X<-table(SHARE_w3_iadl_shopping$sl_xt020d8)
BeforeH <- c(X[c(4,3,1,2)],sum(is.na(SHARE_w3_iadl_shopping$sl_xt020d8)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","-2->997","-1->998","NA->999") 
kable(C)
```

```{r importOPAL w3, echo=FALSE}
label(SHARE_ds_w3$iadl_shopping) <- ds_label
iadl_shopping <- SHARE_ds_w3
save(iadl_shopping, file = "../RData/w3/iadl_shopping.RData")
#opal.assign.data(o, 'SHARE_ds_w3', SHARE_ds_w3)
#opal.symbol_import(o,'SHARE_ds_w3', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w3 <- SHARE_ds_w3
SHARE_m_ds_w3$iadl_shopping <- car::recode(SHARE_m_ds_w3$iadl_shopping, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w3', SHARE_m_ds_w3)
#opal.symbol_import(o,'SHARE_m_ds_w3', project='_Athlos_Harm_Dataset')
```



### Wave 4 

#### Study-specific variable description



| **Name** | `ph049d9`|
|-|-|
| **Label** | `difficulties: shopping for groceries` |
| **Table name** |`sharew4_rel1-1-1_ph`|
| **Categories** |`0 = Not selected; 1 = Selected`|
| **Missings** |`-1 = Don't know; -2 = Refusal; NA`|
| **Description** |  |


   
```{r assign w4, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_w4_iadl_shopping','SHARE.sharew4_rel1-1-1_ph', variables=list('ph049d9'), missings = TRUE)
SHARE_w4_iadl_shopping <- opal.execute(o,'SHARE_w4_iadl_shopping')
```

```{r local w4, echo=FALSE}
vari <- SHARE_w4_iadl_shopping$ph049d9
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
ggplot(SHARE_w4_iadl_shopping, aes(x=factor(ph049d9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Shopping for groceries") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `-1 into 998`
* `-2 into 997`
* `NA into 999`

**R script:**

```{r harmo w4}
SHARE_ds_w4 <- tibble(id=SHARE_w4_iadl_shopping$id)
SHARE_ds_w4$iadl_shopping <- car::recode(SHARE_w4_iadl_shopping$ph049d9, "1 = '0';0 = '1';-1 = '998';-2 = '997'; NA = '999' ")
SHARE_ds_w4$iadl_shopping <- labelled(SHARE_ds_w4$iadl_shopping, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w4, echo=FALSE}
vari <- SHARE_ds_w4$iadl_shopping
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w4, aes(x=factor(iadl_shopping))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Shopping for groceries") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w4, echo=FALSE}
AfterH <- table(SHARE_ds_w4$iadl_shopping)
X<-table(SHARE_w4_iadl_shopping$ph049d9)
BeforeH <- c(X[c(4,3,1,2)],sum(is.na(SHARE_w4_iadl_shopping$ph049d9)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","-2->997","-1->998","NA->999") 
kable(C)
```

```{r importOPAL w4, echo=FALSE}
label(SHARE_ds_w4$iadl_shopping) <- ds_label
iadl_shopping <- SHARE_ds_w4
save(iadl_shopping, file = "../RData/w4/iadl_shopping.RData")
#opal.assign.data(o, 'SHARE_ds_w4', SHARE_ds_w4)
#opal.symbol_import(o,'SHARE_ds_w4', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w4 <- SHARE_ds_w4
SHARE_m_ds_w4$iadl_shopping <- car::recode(SHARE_m_ds_w4$iadl_shopping, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w4', SHARE_m_ds_w4)
#opal.symbol_import(o,'SHARE_m_ds_w4', project='_Athlos_Harm_Dataset')
```



### Wave 5 

#### Study-specific variable description



| **Name** | `ph049d9`|
|-|-|
| **Label** | `difficulties: shopping for groceries` |
| **Table name** |`sharew5_rel1-0-0_ph`|
| **Categories** |`0 = Not selected; 1 = Selected`|
| **Missings** |`-1 = Don't know; -2 = Refusal; NA`|
| **Description** |  |


   
```{r assign w5, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_w5_iadl_shopping','SHARE.sharew5_rel1-0-0_ph', variables=list('ph049d9'), missings = TRUE)
SHARE_w5_iadl_shopping <- opal.execute(o,'SHARE_w5_iadl_shopping')
```

```{r local w5, echo=FALSE}
vari <- SHARE_w5_iadl_shopping$ph049d9
kable(Categorical_summary(vari, missing_values = c(-1, -2))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-1, -2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1, -2))[2], caption = "Type of missing")
ggplot(SHARE_w5_iadl_shopping, aes(x=factor(ph049d9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Shopping for groceries") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `0 into 1` 
* `1 into 0`
* `-1 into 998`
* `-2 into 997`
* `NA into 999`

**R script:**

```{r harmo w5}
SHARE_ds_w5 <- tibble(id=SHARE_w5_iadl_shopping$id)
SHARE_ds_w5$iadl_shopping <- car::recode(SHARE_w5_iadl_shopping$ph049d9, "1 = '0';0 = '1';-1 = '998';-2 = '997'; NA = '999' ")
SHARE_ds_w5$iadl_shopping <- labelled(SHARE_ds_w5$iadl_shopping, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w5, echo=FALSE}
vari <- SHARE_ds_w5$iadl_shopping
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w5, aes(x=factor(iadl_shopping))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Shopping for groceries") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w5, echo=FALSE}
AfterH <- table(SHARE_ds_w5$iadl_shopping)
X<-table(SHARE_w5_iadl_shopping$ph049d9)
BeforeH <- c(X[c(4,3,1,2)],sum(is.na(SHARE_w5_iadl_shopping$ph049d9)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","-2->997","-1->998","NA->999") 
kable(C)
```


```{r importOPAL w5, echo=FALSE}
label(SHARE_ds_w5$iadl_shopping) <- ds_label
iadl_shopping <- SHARE_ds_w5
save(iadl_shopping, file = "../RData/w5/iadl_shopping.RData")
#opal.assign.data(o, 'SHARE_ds_w5', SHARE_ds_w5)
#opal.symbol_import(o,'SHARE_ds_w5', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w5 <- SHARE_ds_w5
SHARE_m_ds_w5$iadl_shopping <- car::recode(SHARE_m_ds_w5$iadl_shopping, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w5', SHARE_m_ds_w5)
#opal.symbol_import(o,'SHARE_m_ds_w5', project='_Athlos_Harm_Dataset')
```

# Quality estimation

No comments

[Comments on the quality of the new harmonised variable. This section can be done in a later stage, once all variables are harmonised.]



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
