---
title: "Verbal fluency"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `cog_verb_c`
* Variable label: `Cognition - verbal fluency - Continuous`
* Variable description: `Cognition - verbal fluency - Continuous. Test that assesses verbal (semantic) fluency: name as many animals as they could think of in 1 minute`
* Domain: `Health status and functional limitations`
* Value type: `Countinous`
* Comments: `Means of all sistolic blood pressure measures.`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Short name: `cog_verb`
* Variable label: `Cognition - verbal fluency`
* Variable description: `Cognition - verbal fluency. Test that assesses verbal (semantic) fluency: name as many animals as they could think of in 1 minute. Discrete variable: value 0 = <=25%; value 1 = >25%.`
* Domain: `Health status and functional limitations`
* Value type: `Categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | <=25%
1        | >25%

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Verbal fluency"
ds_label_cog_verb_c <- "Cognition - verbal fluency - Continuous. Test that assesses verbal (semantic) fluency: name as many animals as they could think of in 1 minute"
ds_label_cog_verb <- "Cognition - verbal fluency. Test that assesses verbal (semantic) fluency: name as many animals as they could think of in 1 minute. Discrete variable: value 0 = <=25%; value 1 = >25%"
```

# Data process

## SHARE

### Wave 1 

#### Study-specific variable description



| **Name** | `cf010_`|
|-|-|
| **Label** | `verbal fluency score` |
| **Table name** |`sharew1_rel2-6-0_cf`|
| **Categories** |`Continuous Variable 0-88`|
| **Missings** |`-1 = Don't know; -2 = Refusal; NA`|
| **Description** |  |



```{r assign w1, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_w1_cog_verb','SHARE.sharew1_rel2-6-0_cf', variables=list('cf010_'), missings = TRUE)
SHARE_w1_cog_verb <- opal.execute(o,'SHARE_w1_cog_verb')
```

```{r local w1, echo=FALSE}
vari <- SHARE_w1_cog_verb$cf010_
kable(Continuous_summary(var = vari, missing_values = c(-1,-2))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(-1,-2))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-1,-2))$summary, caption = "Summary")
ggplot(SHARE_w1_cog_verb, aes(x=cf010_)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable `cog_verb_c` from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`
* `-1 into 998`
* `-2 into 997`

To compute the harmonized variable `cog_verb` from `cog_verb_c` it has to be recoded as follows:

* `cog_verb_c <=25% into 0`
* `cog_verb_c >25% into 1`

**R script:**

```{r harmo w1}
#cog_verb_c
SHARE_ds_w1 <- tibble(id=SHARE_w1_cog_verb$id)
SHARE_ds_w1$cog_verb_c <- car::recode(SHARE_w1_cog_verb$cf010_, "-2=997; -1=998; NA=999")
SHARE_ds_w1$cog_verb_c <- labelled(SHARE_ds_w1$cog_verb_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(SHARE_ds_w1$cog_verb_c, "999=NA; 997=NA; 998=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

SHARE_ds_w1$cog_verb <- car::recode(SHARE_ds_w1[[2]], "0:Q=0; (Q+1):900=1")
SHARE_ds_w1$cog_verb <- labelled(SHARE_ds_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=FALSE}
vari <- SHARE_ds_w1$cog_verb_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w1, aes(cog_verb_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")+xlim(0,90)

vari <- SHARE_ds_w1$cog_verb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w1, aes(x=factor(cog_verb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=FALSE}
Continous <- c(sum(na.omit(SHARE_ds_w1[[2]])<=Q), sum(na.omit(SHARE_ds_w1[[2]])>Q & na.omit(SHARE_ds_w1[[2]])<900), sum(na.omit(SHARE_ds_w1[[2]])==997), sum(na.omit(SHARE_ds_w1[[2]])==998), sum(na.omit(SHARE_ds_w1[[2]])==999))
Dicotomic <- table(SHARE_ds_w1[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:14->0","15:160->1", "-2->997", "-1->998", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL w1, echo=FALSE}
#label(SHARE_ds_w1$cog_verb) <- "Cognition - verbal fluency"
#opal.assign.data(o, 'SHARE_ds_w1', SHARE_ds_w1)
#opal.symbol_import(o,'SHARE_ds_w1', project='_Athlos_Harm_Dataset')

label(SHARE_ds_w1$cog_verb_c) <- ds_label_cog_verb_c
label(SHARE_ds_w1$cog_verb) <- ds_label_cog_verb
cog_verb <- SHARE_ds_w1
save(cog_verb, file = "../RData/w1/cog_verb.RData")
```



### Wave 2 

#### Study-specific variable description



| **Name** | `cf010_`|
|-|-|
| **Label** | `verbal fluency score` |
| **Table name** |`sharew2_rel2-6-0_cf`|
| **Categories** |`Continuous Variable 0-100`|
| **Missings** |`-1 = Don't know; -2 = Refusal; NA`|
| **Description** |  |




```{r assign w2, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_w2_cog_verb','SHARE.sharew2_rel2-6-0_cf', variables=list('cf010_'), missings = TRUE)
SHARE_w2_cog_verb <- opal.execute(o,'SHARE_w2_cog_verb')
```

```{r local w2, echo=FALSE}
vari <- SHARE_w2_cog_verb$cf010_
kable(Continuous_summary(var = vari, missing_values = c(-1,-2))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(-1,-2))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-1,-2))$summary, caption = "Summary")
ggplot(SHARE_w2_cog_verb, aes(x=(cf010_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable `cog_verb_c` from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`
* `-1 into 998`
* `-2 into 997`

To compute the harmonized variable `cog_verb` from `cog_verb_c` it has to be recoded as follows:

* `cog_verb_c <=25% into 0`
* `cog_verb_c >25% into 1`

**R script:**

```{r harmo w2}
#cog_verb_c
SHARE_ds_w2 <- tibble(id=SHARE_w2_cog_verb$id)
SHARE_ds_w2$cog_verb_c <- car::recode(SHARE_w2_cog_verb$cf010_, "-2=997; -1=998; NA=999")
SHARE_ds_w2$cog_verb_c <- labelled(SHARE_ds_w2$cog_verb_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(SHARE_ds_w2$cog_verb_c, "999=NA; 997=NA; 998=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

SHARE_ds_w2$cog_verb <- car::recode(SHARE_ds_w2[[2]], "0:Q=0; (Q+1):900=1")
SHARE_ds_w2$cog_verb <- labelled(SHARE_ds_w2[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=FALSE}
vari <- SHARE_ds_w2$cog_verb_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w2, aes(cog_verb_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")+xlim(0,100)

vari <- SHARE_ds_w2$cog_verb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w2, aes(x=factor(cog_verb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=FALSE}
Continous <- c(sum(na.omit(SHARE_ds_w2[[2]])<=Q), sum(na.omit(SHARE_ds_w2[[2]])>Q & na.omit(SHARE_ds_w2[[2]])<900), sum(na.omit(SHARE_ds_w2[[2]])==997), sum(na.omit(SHARE_ds_w2[[2]])==998), sum(na.omit(SHARE_ds_w2[[2]])==999))
Dicotomic <- table(SHARE_ds_w2[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:14->0","15:160->1", "-2->997", "-1->998", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL w2, echo=FALSE}
#label(SHARE_ds_w2$cog_verb) <- "Cognition - verbal fluency"
#opal.assign.data(o, 'SHARE_ds_w2', SHARE_ds_w2)
#opal.symbol_import(o,'SHARE_ds_w2', project='_Athlos_Harm_Dataset')

label(SHARE_ds_w2$cog_verb_c) <- ds_label_cog_verb_c
label(SHARE_ds_w2$cog_verb) <- ds_label_cog_verb
cog_verb <- SHARE_ds_w2
save(cog_verb, file = "../RData/w2/cog_verb.RData")
```



### Wave 3

Not found



### Wave 4 

#### Study-specific variable description


| **Name** | `cf010_`|
|-|-|
| **Label** | `verbal fluency score` |
| **Table name** |`sharew4_rel1-1-1_cf`|
| **Categories** |`Continuous Variable 0-100`|
| **Missings** |`-1 = Don't know; -2 = Refusal; NA`|
| **Description** |  |


```{r assign w4, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_w4_cog_verb','SHARE.sharew4_rel1-1-1_cf', variables=list('cf010_'), missings = TRUE)
SHARE_w4_cog_verb <- opal.execute(o,'SHARE_w4_cog_verb')
```

```{r local w4, echo=FALSE}
vari <- SHARE_w4_cog_verb$cf010_
kable(Continuous_summary(var = vari, missing_values = c(-1,-2))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(-1,-2))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-1,-2))$summary, caption = "Summary")
ggplot(SHARE_w4_cog_verb, aes(x=cf010_)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable `cog_verb_c` from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`
* `-1 into 998`
* `-2 into 997`

To compute the harmonized variable `cog_verb` from `cog_verb_c` it has to be recoded as follows:

* `cog_verb_c <=25% into 0`
* `cog_verb_c >25% into 1`

**R script:**

```{r harmo w4}
#cog_verb_c
SHARE_ds_w4 <- tibble(id=SHARE_w4_cog_verb$id)
SHARE_ds_w4$cog_verb_c <- car::recode(SHARE_w4_cog_verb$cf010_, "-2=997; -1=998; NA=999")
SHARE_ds_w4$cog_verb_c <- labelled(SHARE_ds_w4$cog_verb_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(SHARE_ds_w4$cog_verb_c, "999=NA; 997=NA; 998=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

SHARE_ds_w4$cog_verb <- car::recode(SHARE_ds_w4[[2]], "0:Q=0; (Q+1):900=1")
SHARE_ds_w4$cog_verb <- labelled(SHARE_ds_w4[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w4, echo=FALSE}
vari <- SHARE_ds_w4$cog_verb_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w4, aes(cog_verb_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")+xlim(0,100)

vari <- SHARE_ds_w4$cog_verb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w4, aes(x=factor(cog_verb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w4, echo=FALSE}
Continous <- c(sum(na.omit(SHARE_ds_w4[[2]])<=Q), sum(na.omit(SHARE_ds_w4[[2]])>Q & na.omit(SHARE_ds_w4[[2]])<900), sum(na.omit(SHARE_ds_w4[[2]])==997), sum(na.omit(SHARE_ds_w4[[2]])==998), sum(na.omit(SHARE_ds_w4[[2]])==999))
Dicotomic <- table(SHARE_ds_w4[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:15->0","16:160->1", "-2->997", "-1->998", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL w4, echo=FALSE}
#label(SHARE_ds_w4$cog_verb) <- "Cognition - verbal fluency"
#opal.assign.data(o, 'SHARE_ds_w4', SHARE_ds_w4)
#opal.symbol_import(o,'SHARE_ds_w4', project='_Athlos_Harm_Dataset')

label(SHARE_ds_w4$cog_verb_c) <- ds_label_cog_verb_c
label(SHARE_ds_w4$cog_verb) <- ds_label_cog_verb
cog_verb <- SHARE_ds_w4
save(cog_verb, file = "../RData/w4/cog_verb.RData")
```



### Wave 5 

#### Study-specific variable description


| **Name** | `cf010_`|
|-|-|
| **Label** | `verbal fluency score` |
| **Table name** |`sharew5_rel1-0-0_cf`|
| **Categories** |`Continuous Variable 0-100`|
| **Missings** |`-1 = Don't know; -2 = Refusal; NA`|
| **Description** |  |



```{r assign w5, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_w5_cog_verb','SHARE.sharew5_rel1-0-0_cf', variables=list('cf010_'), missings = TRUE)
SHARE_w5_cog_verb <- opal.execute(o,'SHARE_w5_cog_verb')
```

```{r local w5, echo=FALSE}
vari <- SHARE_w5_cog_verb$cf010_
kable(Continuous_summary(var = vari, missing_values = c(-1,-2))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(-1,-2))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-1,-2))$summary, caption = "Summary")
ggplot(SHARE_w5_cog_verb, aes(x=cf010_)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable `cog_verb_c` from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`
* `-1 into 998`
* `-2 into 997`

To compute the harmonized variable `cog_verb` from `cog_verb_c` it has to be recoded as follows:

* `cog_verb_c <=25% into 0`
* `cog_verb_c >25% into 1`

**R script:**

```{r harmo w5}
#cog_verb_c
SHARE_ds_w5 <- tibble(id=SHARE_w5_cog_verb$id)
SHARE_ds_w5$cog_verb_c <- car::recode(SHARE_w5_cog_verb$cf010_, "-2=997; -1=998; NA=999")
SHARE_ds_w5$cog_verb_c <- labelled(SHARE_ds_w5$cog_verb_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(SHARE_ds_w5$cog_verb_c, "999=NA; 997=NA; 998=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

SHARE_ds_w5$cog_verb <- car::recode(SHARE_ds_w5[[2]], "0:Q=0; (Q+1):900=1")
SHARE_ds_w5$cog_verb <- labelled(SHARE_ds_w5[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w5, echo=FALSE}
vari <- SHARE_ds_w5$cog_verb_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w5, aes(cog_verb_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")+xlim(0,100)

vari <- SHARE_ds_w5$cog_verb
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w5, aes(x=factor(cog_verb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Verbal fluency") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w5, echo=FALSE}
Continous <- c(sum(na.omit(SHARE_ds_w5[[2]])<=Q), sum(na.omit(SHARE_ds_w5[[2]])>Q & na.omit(SHARE_ds_w5[[2]])<900), sum(na.omit(SHARE_ds_w5[[2]])==997), sum(na.omit(SHARE_ds_w5[[2]])==998), sum(na.omit(SHARE_ds_w5[[2]])==999))
Dicotomic <- table(SHARE_ds_w5[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:15->0","16:160->1", "-2->997", "-1->998", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL w5, echo=FALSE}
#label(SHARE_ds_w5$cog_verb) <- "Cognition - verbal fluency"
#opal.assign.data(o, 'SHARE_ds_w5', SHARE_ds_w5)
#opal.symbol_import(o,'SHARE_ds_w5', project='_Athlos_Harm_Dataset')

label(SHARE_ds_w5$cog_verb_c) <- ds_label_cog_verb_c
label(SHARE_ds_w5$cog_verb) <- ds_label_cog_verb
cog_verb <- SHARE_ds_w5
save(cog_verb, file = "../RData/w5/cog_verb.RData")
```


# Quality estimation
[Comments on the quality of the new harmonised variable. This section can be done in a later stage, once all variables are harmonised.]

No comments

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
