---
title: "Numeracy"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `cog_num_c`
* Variable label: `Cognition - numeracy test - Continuous. It is assessed by means of a numeracy test, composed by six numeracy questions`
* Domain: `Health status and functional limitations`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



* Short name: `cog_num`
* Variable label: `Cognition - numeracy test. It is assessed by means of a numeracy test, composed by six numeracy questions. Discrete variable: value 0 = <=25%; value 1 = >25%.`
* Domain: `Health status and functional limitations`
* Value type: `Categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | <=25%
1        | >25%

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Cognition - numeracy test"
ds_label_cog_num_c <- "Cognition - numeracy test - Continuous. It is assessed by means of a numeracy test, composed by six numeracy questions"
ds_label_cog_num <- "Cognition - numeracy test. It is assessed by means of a numeracy test, composed by six numeracy questions. Discrete variable: value 0 = <=25%; value 1 = >25%"
```



<!-- ########################################################## --> 

# Data process

## SHARE

### Wave 1 

#### Study-specific variable description




| **Name** | `cf012_`| `cf013_`|`cf014_`|`cf015_`|
|-|-|-|-|-|
| **Label** | `Chance disease 10 perc. of 1000` |`Half price [of a  300 Euro sofa]` |`6000 is two-thirds what is total price` |`Amount in the savings account [on 2000 Euros after 2 years of 10% interest]` |
| **Table name** |`sharew1_rel2-6-0_cf`|`sharew1_rel2-6-0_cf`|`sharew1_rel2-6-0_cf`|`sharew1_rel2-6-0_cf`|
| **Categories** |`1 = correct answer: 100; 2 = wrong answer: 10; 3 = wrong answer: 90; 4 = wrong answer: 900; 97 = wrong answer: Other answer`|`1 = correct answer: 150; 2 = wrong answer: country-specific category 1; 3 = wrong answer: country-specific category 2; 4 = wrong answer: country-specific category 3; 5 = wrong answer: country-specific category 4; 97 = wrong answer: Other answer`|`1 = correct answer: 9000; 2 = wrong answer: country-specific category 1; 3 = wrong answer: country-specific category 2; 4 = wrong answer: country-specific category 3; 5 = wrong answer: country-specific category 4; 6 = wrong answer: country-specific category 5; 7 = wrong answer: country-specific category 6; 97 = wrong answer: Other answer`|`1 = correct answer: 2420; 2 = wrong answer: 2020; 3 = wrong answer: 2040; 4 = wrong answer: 2100; 5 = wrong answer: 2200; 6 = wrong answer: 2400; 97 = wrong answer: Other`|
| **Missings** |`-1 = don't know; -2 = refusal; NA`|`-1 = don't know; -2 = refusal; NA`|`-1 = don't know; -2 = refusal; NA`|`-1 = don't know; -2 = refusal; NA`|
| **Description** |  |  |  |  |



```{r assign w1, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_w1_cog_num','SHARE.sharew1_rel2-6-0_cf', variables=list('cf012_','cf013_','cf014_','cf015_'), missings = TRUE)
SHARE_w1_cog_num <- opal.execute(o,'SHARE_w1_cog_num')
```

```{r local w1, echo=FALSE}
vari <- SHARE_w1_cog_num$cf012_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w1_cog_num, aes(x=factor(cf012_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Numeracy") + ylab("Frequency")

vari <- SHARE_w1_cog_num$cf013_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w1_cog_num, aes(x=factor(cf013_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Numeracy") + ylab("Frequency")

vari <- SHARE_w1_cog_num$cf014_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w1_cog_num, aes(x=factor(cf014_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Numeracy") + ylab("Frequency")

vari <- SHARE_w1_cog_num$cf015_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w1_cog_num, aes(x=factor(cf015_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Numeracy") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable `cog_num_c` from the study-specific variables sum them after recoded as follows

* `keep 1 into 1`
* `recode -1, 2, 3, 4, 5, 6 and 97 into 0`

and the missing values have to be recoded as follows:

* `-2 into 997`
* `NA into 999`

To compute the harmonized variable `cog_num` from `cog_num_c` it has to be recoded as follows:

* `cog_num_c = 3 into 1` 
* `cog_num_c = 0,1,2 into 0`
* `cog_num_c = NA into 999`
* `keep cog_num_c = 997 into 997`

**R script:**

```{r harmo w1}
SHARE_w1_cog_num$cf012_2 <- car::recode(SHARE_w1_cog_num$cf012_, "2:6=0; 97=0; -1=0; -2=NA")
SHARE_w1_cog_num$cf013_2 <- car::recode(SHARE_w1_cog_num$cf013_, "2:6=0; 97=0; -1=0; -2=NA")
SHARE_w1_cog_num$cf014_2 <- car::recode(SHARE_w1_cog_num$cf014_, "2:7=0; 97=0; -1=0; -2=NA")
SHARE_w1_cog_num$cf015_2 <- car::recode(SHARE_w1_cog_num$cf015_, "2:6=0; 97=0; -1=0; -2=NA")

SHARE_w1_cog_num$sum3 <- apply(SHARE_w1_cog_num[, 6:9], MARGIN = 1, FUN = function(x) sum(x,na.rm = TRUE))
SHARE_w1_cog_num$comp3 <- apply(SHARE_w1_cog_num[, 6:9], MARGIN = 1, FUN = function(x) sum(is.na(x)) )

SHARE_w1_cog_num$zero <- apply(SHARE_w1_cog_num[, 6:9], MARGIN = 1, FUN = function(x) sum(x==0, na.rm = TRUE) )


SHARE_ds_w1 <- tibble(id=SHARE_w1_cog_num$id)
SHARE_ds_w1$cog_num_c <- NA

#if the individual has one item wrong it's 0
SHARE_ds_w1$cog_num_c[which(SHARE_w1_cog_num$zero>=1)] <- SHARE_w1_cog_num$sum3[which(SHARE_w1_cog_num$zero>=1)]

#if the individual has no items wrong and one NA it's 3
SHARE_ds_w1$cog_num_c[which(SHARE_w1_cog_num$zero==0 & SHARE_w1_cog_num$comp3==1)] <- 3

#if the indiviudal has all the items NA it's a NA
SHARE_ds_w1$cog_num_c[which(SHARE_w1_cog_num$comp3==4)] <- NA

#other it's NA (example two items good and two NA)
SHARE_ds_w1$cog_num_c <- car::recode(SHARE_ds_w1$cog_num_c, "NA=999")
SHARE_ds_w1$cog_num_c <- labelled(SHARE_ds_w1[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_num
SHARE_ds_w1$cog_num <- car::recode(SHARE_ds_w1$cog_num_c, "3=1; 1:2=0")
SHARE_ds_w1$cog_num <- labelled(SHARE_ds_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=FALSE}
vari <- SHARE_ds_w1$cog_num_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w1, aes(x=factor(cog_num_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Numeracy") + ylab("Frequency")

vari <- SHARE_ds_w1$cog_num
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w1, aes(x=factor(cog_num))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=FALSE}
Continous <- table(SHARE_ds_w1$cog_num_c)
Continous <- c(sum(Continous[1:3]),Continous[4], Continous[5])
Dicotomic <- table(SHARE_ds_w1[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("(0,1,2)","3->1", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL w1, echo=FALSE}
#opal.assign.data(o, 'SHARE_ds_w1', SHARE_ds_w1)
#opal.symbol_import(o,'SHARE_ds_w1', project='_Athlos_Harm_Dataset')

label(SHARE_ds_w1$cog_num_c) <- ds_label_cog_num_c
label(SHARE_ds_w1$cog_num) <- ds_label_cog_num
cog_num <- SHARE_ds_w1
save(cog_num, file = "../RData/w1/cog_num.RData")
```



### Wave 2 

#### Study-specific variable description


| **Name** | `cf012_`| `cf013_`|`cf014_`|`cf015_`|
|-|-|-|-|-|
| **Label** | `Chance disease 10 perc. of 1000` |`Half price [of a  300 Euro sofa]` |`6000 is two-thirds what is total price` |`Amount in the savings account [on 2000 Euros after 2 years of 10% interest]` |
| **Table name** |`sharew2_rel2-6-0_cf`|`sharew2_rel2-6-0_cf`|`sharew2_rel2-6-0_cf`|`sharew2_rel2-6-0_cf`|
| **Categories** |`1 = correct answer: 100; 2 = wrong answer: 10; 3 = wrong answer: 90; 4 = wrong answer: 900; 97 = wrong answer: Other answer`|`1 = correct answer: 150; 2 = wrong answer: country-specific category 1; 3 = wrong answer: country-specific category 2; 4 = wrong answer: country-specific category 3; 5 = wrong answer: country-specific category 4; 97 = wrong answer: Other answer`|`1 = correct answer: 9000; 2 = wrong answer: country-specific category 1; 3 = wrong answer: country-specific category 2; 4 = wrong answer: country-specific category 3; 5 = wrong answer: country-specific category 4; 6 = wrong answer: country-specific category 5; 7 = wrong answer: country-specific category 6; 97 = wrong answer: Other answer`|`1 = correct answer: 2420; 2 = wrong answer: 2020; 3 = wrong answer: 2040; 4 = wrong answer: 2100; 5 = wrong answer: 2200; 6 = wrong answer: 2400; 97 = wrong answer: Other`|
| **Missings** |`-1 = don't know; -2 = refusal; NA`|`-1 = don't know; -2 = refusal; NA`|`-1 = don't know; -2 = refusal; NA`|`-1 = don't know; -2 = refusal; NA`|
| **Description** |  |  |  |  |



```{r assign w2, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_w2_cog_num','SHARE.sharew2_rel2-6-0_cf', variables=list('cf012_','cf013_','cf014_','cf015_'), missings = TRUE)
SHARE_w2_cog_num <- opal.execute(o,'SHARE_w2_cog_num')
```

```{r local w2, echo=FALSE}
vari <- SHARE_w2_cog_num$cf012_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w2_cog_num, aes(x=factor(cf012_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Numeracy") + ylab("Frequency")

vari <- SHARE_w2_cog_num$cf013_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w2_cog_num, aes(x=factor(cf013_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Numeracy") + ylab("Frequency")

vari <- SHARE_w2_cog_num$cf014_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w2_cog_num, aes(x=factor(cf014_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Numeracy") + ylab("Frequency")

vari <- SHARE_w2_cog_num$cf015_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w2_cog_num, aes(x=factor(cf015_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Numeracy") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable `cog_num_c` from the study-specific variables sum them after recoded as follows

* `keep 1 into 1`
* `recode -1, 2, 3, 4, 5, 6 and 97 into 0`

and the missing values have to be recoded as follows:

* `-2 into 997`
* `NA into 999`

To compute the harmonized variable `cog_num` from `cog_num_c` it has to be recoded as follows:

* `cog_num_c = 3 into 1` 
* `cog_num_c = 0,1,2 into 0`
* `cog_num_c = NA into 999`
* `keep cog_num_c = 997 into 997`

**R script:**

```{r harmo w2}
SHARE_w2_cog_num$cf012_2 <- car::recode(SHARE_w2_cog_num$cf012_, "2:6=0; 97=0; -1=0; -2=NA")
SHARE_w2_cog_num$cf013_2 <- car::recode(SHARE_w2_cog_num$cf013_, "2:6=0; 97=0; -1=0; -2=NA")
SHARE_w2_cog_num$cf014_2 <- car::recode(SHARE_w2_cog_num$cf014_, "2:7=0; 97=0; -1=0; -2=NA")
SHARE_w2_cog_num$cf015_2 <- car::recode(SHARE_w2_cog_num$cf015_, "2:6=0; 97=0; -1=0; -2=NA")

SHARE_w2_cog_num$sum3 <- apply(SHARE_w2_cog_num[, 6:9], MARGIN = 1, FUN = function(x) sum(x,na.rm = TRUE))
SHARE_w2_cog_num$comp3 <- apply(SHARE_w2_cog_num[, 6:9], MARGIN = 1, FUN = function(x) sum(is.na(x)) )
SHARE_w2_cog_num$zero <- apply(SHARE_w2_cog_num[, 6:9], MARGIN = 1, FUN = function(x) sum(x==0, na.rm = TRUE) )


SHARE_ds_w2 <- tibble(id=SHARE_w2_cog_num$id)
SHARE_ds_w2$cog_num_c <- NA

#if the individual has one item wrong it's 0
SHARE_ds_w2$cog_num_c[which(SHARE_w2_cog_num$zero>=1)] <- SHARE_w2_cog_num$sum3[which(SHARE_w2_cog_num$zero>=1)]

#if the individual has no items wrong and one NA it's 3
SHARE_ds_w2$cog_num_c[which(SHARE_w2_cog_num$zero==0 & SHARE_w2_cog_num$comp3==1)] <- 3

#if the indiviudal has all the items NA it's a NA
SHARE_ds_w2$cog_num_c[which(SHARE_w2_cog_num$comp3==4)] <- NA

#other it's NA (example two items good and two NA)
SHARE_ds_w2$cog_num_c <- car::recode(SHARE_ds_w2$cog_num_c, "NA=999")
SHARE_ds_w2$cog_num_c <- labelled(SHARE_ds_w2[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_num
SHARE_ds_w2$cog_num <- car::recode(SHARE_ds_w2$cog_num_c, "3=1; 1:2=0")
SHARE_ds_w2$cog_num <- labelled(SHARE_ds_w2[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=FALSE}
vari <- SHARE_ds_w2$cog_num_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w2, aes(x=factor(cog_num_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Numeracy") + ylab("Frequency")

vari <- SHARE_ds_w2$cog_num
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w2, aes(x=factor(cog_num))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=FALSE}
Continous <- table(SHARE_ds_w2$cog_num_c)
Continous <- c(sum(Continous[1:3]),Continous[4], Continous[5])
Dicotomic <- table(SHARE_ds_w2[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("(0,1,2)","3->1", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL w2, echo=FALSE}
#opal.assign.data(o, 'SHARE_ds_w2', SHARE_ds_w2)
#opal.symbol_import(o,'SHARE_ds_w2', project='_Athlos_Harm_Dataset')

label(SHARE_ds_w2$cog_num_c) <- ds_label_cog_num_c
label(SHARE_ds_w2$cog_num) <- ds_label_cog_num
cog_num <- SHARE_ds_w2
save(cog_num, file = "../RData/w2/cog_num.RData")
```



### Wave 3 

Not found



### Wave 4 

#### Study-specific variable description



| **Name** | `cf012_`| `cf013_`|`cf014_`|`cf015_`|
|-|-|-|-|-|
| **Label** | `Chance disease 10 perc. of 1000` |`Half price [of a  300 Euro sofa]` |`6000 is two-thirds what is total price` |`Amount in the savings account [on 2000 Euros after 2 years of 10% interest]` |
| **Table name** |`sharew4_rel1-1-1_cf`|`sharew4_rel1-1-1_cf`|`sharew4_rel1-1-1_cf`|`sharew4_rel1-1-1_cf`|
| **Categories** |`1 = correct answer: 100; 2 = wrong answer: 10; 3 = wrong answer: 90; 4 = wrong answer: 900; 97 = wrong answer: Other answer`|`1 = correct answer: 150; 2 = wrong answer: country-specific category 1; 3 = wrong answer: country-specific category 2; 4 = wrong answer: country-specific category 3; 5 = wrong answer: country-specific category 4; 97 = wrong answer: Other answer`|`1 = correct answer: 9000; 2 = wrong answer: country-specific category 1; 3 = wrong answer: country-specific category 2; 4 = wrong answer: country-specific category 3; 5 = wrong answer: country-specific category 4; 6 = wrong answer: country-specific category 5; 7 = wrong answer: country-specific category 6; 97 = wrong answer: Other answer`|`1 = correct answer: 2420; 2 = wrong answer: 2020; 3 = wrong answer: 2040; 4 = wrong answer: 2100; 5 = wrong answer: 2200; 6 = wrong answer: 2400; 97 = wrong answer: Other`|
| **Missings** |`-1 = don't know; -2 = refusal; NA`|`-1 = don't know; -2 = refusal; NA`|`-1 = don't know; -2 = refusal; NA`|`-1 = don't know; -2 = refusal; NA`|
| **Description** |  |  |  |  |



```{r assign w4, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_w4_cog_num','SHARE.sharew4_rel1-1-1_cf', variables=list('cf012_','cf013_','cf014_','cf015_'), missings = TRUE)
SHARE_w4_cog_num <- opal.execute(o,'SHARE_w4_cog_num')
```

```{r local w4, echo=FALSE}
vari <- SHARE_w4_cog_num$cf012_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w4_cog_num, aes(x=factor(cf012_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Numeracy") + ylab("Frequency")

vari <- SHARE_w4_cog_num$cf013_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w4_cog_num, aes(x=factor(cf013_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Numeracy") + ylab("Frequency")

vari <- SHARE_w4_cog_num$cf014_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w4_cog_num, aes(x=factor(cf014_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Numeracy") + ylab("Frequency")

vari <- SHARE_w4_cog_num$cf015_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w4_cog_num, aes(x=factor(cf015_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Numeracy") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable `cog_num_c` from the study-specific variables sum them after recoded as follows

* `keep 1 into 1`
* `recode -1, 2, 3, 4, 5, 6 and 97 into 0`

and the missing values have to be recoded as follows:

* `-2 into 997`
* `NA into 999`

To compute the harmonized variable `cog_num` from `cog_num_c` it has to be recoded as follows:

* `cog_num_c = 3 into 1` 
* `cog_num_c = 0,1,2 into 0`
* `cog_num_c = NA into 999`
* `keep cog_num_c = 997 into 997`

**R script:**

```{r harmo w4}
SHARE_w4_cog_num$cf012_2 <- car::recode(SHARE_w4_cog_num$cf012_, "2:6=0; 97=0; -1=0; -2=NA")
SHARE_w4_cog_num$cf013_2 <- car::recode(SHARE_w4_cog_num$cf013_, "2:6=0; 97=0; -1=0; -2=NA")
SHARE_w4_cog_num$cf014_2 <- car::recode(SHARE_w4_cog_num$cf014_, "2:7=0; 97=0; -1=0; -2=NA")
SHARE_w4_cog_num$cf015_2 <- car::recode(SHARE_w4_cog_num$cf015_, "2:6=0; 97=0; -1=0; -2=NA")

SHARE_w4_cog_num$sum3 <- apply(SHARE_w4_cog_num[, 6:9], MARGIN = 1, FUN = function(x) sum(x,na.rm = TRUE))
SHARE_w4_cog_num$comp3 <- apply(SHARE_w4_cog_num[, 6:9], MARGIN = 1, FUN = function(x) sum(is.na(x)) )

SHARE_w4_cog_num$zero <- apply(SHARE_w4_cog_num[, 6:9], MARGIN = 1, FUN = function(x) sum(x==0, na.rm = TRUE) )


SHARE_ds_w4 <- tibble(id=SHARE_w4_cog_num$id)
SHARE_ds_w4$cog_num_c <- NA

#if the individual has one item wrong it's 0
SHARE_ds_w4$cog_num_c[which(SHARE_w4_cog_num$zero>=1)] <- SHARE_w4_cog_num$sum3[which(SHARE_w4_cog_num$zero>=1)]

#if the individual has no items wrong and one NA it's 3
SHARE_ds_w4$cog_num_c[which(SHARE_w4_cog_num$zero==0 & SHARE_w4_cog_num$comp3==1)] <- 3

#if the indiviudal has all the items NA it's a NA
SHARE_ds_w4$cog_num_c[which(SHARE_w4_cog_num$comp3==4)] <- NA

#other it's NA (example two items good and two NA)
SHARE_ds_w4$cog_num_c <- car::recode(SHARE_ds_w4$cog_num_c, "NA=999")
SHARE_ds_w4$cog_num_c <- labelled(SHARE_ds_w4[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_num
SHARE_ds_w4$cog_num <- car::recode(SHARE_ds_w4$cog_num_c, "3=1; 1:2=0")
SHARE_ds_w4$cog_num <- labelled(SHARE_ds_w4[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w4, echo=FALSE}
vari <- SHARE_ds_w4$cog_num_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w4, aes(x=factor(cog_num_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Numeracy") + ylab("Frequency")

vari <- SHARE_ds_w4$cog_num
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w4, aes(x=factor(cog_num))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w4, echo=FALSE}
Continous <- table(SHARE_ds_w4$cog_num_c)
Continous <- c(sum(Continous[1:3]),Continous[4], Continous[5])
Dicotomic <- table(SHARE_ds_w4[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("(0,1,2)","3->1", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL w4, echo=FALSE}
#opal.assign.data(o, 'SHARE_ds_w4', SHARE_ds_w4)
#opal.symbol_import(o,'SHARE_ds_w4', project='_Athlos_Harm_Dataset')

label(SHARE_ds_w4$cog_num_c) <- ds_label_cog_num_c
label(SHARE_ds_w4$cog_num) <- ds_label_cog_num
cog_num <- SHARE_ds_w4
save(cog_num, file = "../RData/w4/cog_num.RData")
```



### Wave 5 

#### Study-specific variable description



| **Name** | `cf012_`| `cf013_`|`cf014_`|`cf015_`|
|-|-|-|-|-|
| **Label** | `Chance disease 10 perc. of 1000` |`Half price [of a  300 Euro sofa]` |`6000 is two-thirds what is total price` |`Amount in the savings account [on 2000 Euros after 2 years of 10% interest]` |
| **Table name** |`sharew5_rel1-0-0_cf`|`sharew5_rel1-0-0_cf`|`sharew5_rel1-0-0_cf`|`sharew5_rel1-0-0_cf`|
| **Categories** |`1 = correct answer: 100; 2 = wrong answer: 10; 3 = wrong answer: 90; 4 = wrong answer: 900; 97 = wrong answer: Other answer`|`1 = correct answer: 150; 2 = wrong answer: country-specific category 1; 3 = wrong answer: country-specific category 2; 4 = wrong answer: country-specific category 3; 5 = wrong answer: country-specific category 4; 97 = wrong answer: Other answer`|`1 = correct answer: 9000; 2 = wrong answer: country-specific category 1; 3 = wrong answer: country-specific category 2; 4 = wrong answer: country-specific category 3; 5 = wrong answer: country-specific category 4; 6 = wrong answer: country-specific category 5; 7 = wrong answer: country-specific category 6; 97 = wrong answer: Other answer`|`1 = correct answer: 2420; 2 = wrong answer: 2020; 3 = wrong answer: 2040; 4 = wrong answer: 2100; 5 = wrong answer: 2200; 6 = wrong answer: 2400; 97 = wrong answer: Other`|
| **Missings** |`-1 = don't know; -2 = refusal; NA`|`-1 = don't know; -2 = refusal; NA`|`-1 = don't know; -2 = refusal; NA`|`-1 = don't know; -2 = refusal; NA`|
| **Description** |  |  |  |  |


```{r assign w5, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_w5_cog_num','SHARE.sharew5_rel1-0-0_cf', variables=list('cf012_','cf013_','cf014_','cf015_'), missings = TRUE)
SHARE_w5_cog_num <- opal.execute(o,'SHARE_w5_cog_num')
```

```{r local w5, echo=FALSE}
vari <- SHARE_w5_cog_num$cf012_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w5_cog_num, aes(x=factor(cf012_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Numeracy") + ylab("Frequency")

vari <- SHARE_w5_cog_num$cf013_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w5_cog_num, aes(x=factor(cf013_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Numeracy") + ylab("Frequency")

vari <- SHARE_w5_cog_num$cf014_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w5_cog_num, aes(x=factor(cf014_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Numeracy") + ylab("Frequency")

vari <- SHARE_w5_cog_num$cf015_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w5_cog_num, aes(x=factor(cf015_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Numeracy") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable `cog_num_c` from the study-specific variables sum them after recoded as follows

* `keep 1 into 1`
* `recode -1, 2, 3, 4, 5, 6 and 97 into 0`

and the missing values have to be recoded as follows:

* `-2 into 997`
* `NA into 999`

To compute the harmonized variable `cog_num` from `cog_num_c` it has to be recoded as follows:

* `cog_num_c = 3 into 1` 
* `cog_num_c = 0,1,2 into 0`
* `cog_num_c = NA into 999`
* `keep cog_num_c = 997 into 997`

**R script:**

```{r harmo w5}
SHARE_w5_cog_num$cf012_2 <- car::recode(SHARE_w5_cog_num$cf012_, "2:6=0; 97=0; -1=0; -2=NA")
SHARE_w5_cog_num$cf013_2 <- car::recode(SHARE_w5_cog_num$cf013_, "2:6=0; 97=0; -1=0; -2=NA")
SHARE_w5_cog_num$cf014_2 <- car::recode(SHARE_w5_cog_num$cf014_, "2:7=0; 97=0; -1=0; -2=NA")
SHARE_w5_cog_num$cf015_2 <- car::recode(SHARE_w5_cog_num$cf015_, "2:6=0; 97=0; -1=0; -2=NA")

SHARE_w5_cog_num$sum3 <- apply(SHARE_w5_cog_num[, 6:9], MARGIN = 1, FUN = function(x) sum(x,na.rm = TRUE))
SHARE_w5_cog_num$comp3 <- apply(SHARE_w5_cog_num[, 6:9], MARGIN = 1, FUN = function(x) sum(is.na(x)) )

SHARE_w5_cog_num$zero <- apply(SHARE_w5_cog_num[, 6:9], MARGIN = 1, FUN = function(x) sum(x==0, na.rm = TRUE) )


SHARE_ds_w5 <- tibble(id=SHARE_w5_cog_num$id)
SHARE_ds_w5$cog_num_c <- NA

#if the individual has one item wrong it's 0
SHARE_ds_w5$cog_num_c[which(SHARE_w5_cog_num$zero>=1)] <- SHARE_w5_cog_num$sum3[which(SHARE_w5_cog_num$zero>=1)]

#if the individual has no items wrong and one NA it's 3
SHARE_ds_w5$cog_num_c[which(SHARE_w5_cog_num$zero==0 & SHARE_w5_cog_num$comp3==1)] <- 3

#if the indiviudal has all the items NA it's a NA
SHARE_ds_w5$cog_num_c[which(SHARE_w5_cog_num$comp3==4)] <- NA

#other it's NA (example two items good and two NA)
SHARE_ds_w5$cog_num_c <- car::recode(SHARE_ds_w5$cog_num_c, "NA=999")
SHARE_ds_w5$cog_num_c <- labelled(SHARE_ds_w5[[2]], labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_num
SHARE_ds_w5$cog_num <- car::recode(SHARE_ds_w5$cog_num_c, "3=1; 1:2=0")
SHARE_ds_w5$cog_num <- labelled(SHARE_ds_w5[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w5, echo=FALSE}
vari <- SHARE_ds_w5$cog_num_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w5, aes(x=factor(cog_num_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Numeracy") + ylab("Frequency")

vari <- SHARE_ds_w5$cog_num
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w5, aes(x=factor(cog_num))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w5, echo=FALSE}
Continous <- table(SHARE_ds_w5$cog_num_c)
Continous <- c(sum(Continous[1:3]),Continous[4], Continous[5])
Dicotomic <- table(SHARE_ds_w5[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("(0,1,2)","3->1", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```


```{r importOPAL w5, echo=FALSE}
#opal.assign.data(o, 'SHARE_ds_w5', SHARE_ds_w5)
#opal.symbol_import(o,'SHARE_ds_w5', project='_Athlos_Harm_Dataset')

label(SHARE_ds_w5$cog_num_c) <- ds_label_cog_num_c
label(SHARE_ds_w5$cog_num) <- ds_label_cog_num
cog_num <- SHARE_ds_w5
save(cog_num, file = "../RData/w5/cog_num.RData")
```

# Quality estimation
All the individuals have at least 1 item missing from the four choose, after check if there is a skip or any reason to such high number of missing data, it was decided that the individuals with 1 missing and all the others good will be considered as without difficulties, the individuals with 1 or more items wrong as with difficulties and others as missing (like 2 items good and 2 missing). 



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
