---
title: "Numeracy"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/cog_numDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/cog_numDS.R')
```


# Data process

## SHARE

### Wave 1 

#### Study-specific variable description




| **Name** | `cf012_`| `cf013_`|`cf014_`|`cf015_`|
|-|-|-|-|-|
| **Label** | `Chance disease 10 perc. of 1000` |`Half price [of a  300 Euro sofa]` |`6000 is two-thirds what is total price` |`Amount in the savings account [on 2000 Euros after 2 years of 10% interest]` |
| **Table name** |`sharew1_rel2-6-0_cf`|`sharew1_rel2-6-0_cf`|`sharew1_rel2-6-0_cf`|`sharew1_rel2-6-0_cf`|
| **Categories** |`1 = correct answer: 100; 2 = wrong answer: 10; 3 = wrong answer: 90; 4 = wrong answer: 900; 97 = wrong answer: Other answer`|`1 = correct answer: 150; 2 = wrong answer: country-specific category 1; 3 = wrong answer: country-specific category 2; 4 = wrong answer: country-specific category 3; 5 = wrong answer: country-specific category 4; 97 = wrong answer: Other answer`|`1 = correct answer: 9000; 2 = wrong answer: country-specific category 1; 3 = wrong answer: country-specific category 2; 4 = wrong answer: country-specific category 3; 5 = wrong answer: country-specific category 4; 6 = wrong answer: country-specific category 5; 7 = wrong answer: country-specific category 6; 97 = wrong answer: Other answer`|`1 = correct answer: 2420; 2 = wrong answer: 2020; 3 = wrong answer: 2040; 4 = wrong answer: 2100; 5 = wrong answer: 2200; 6 = wrong answer: 2400; 97 = wrong answer: Other`|
| **Missings** |`-1 = don't know; -2 = refusal; NA`|`-1 = don't know; -2 = refusal; NA`|`-1 = don't know; -2 = refusal; NA`|`-1 = don't know; -2 = refusal; NA`|
| **Description** |  |  |  |  |



```{r assign w1, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_w1_cog_num','SHARE.sharew1_rel2-6-0_cf', variables=list('cf012_','cf013_','cf014_','cf015_'), missings = TRUE)
SHARE_w1_cog_num <- opal.execute(o,'SHARE_w1_cog_num')
```

```{r local w1, echo=FALSE}
vari <- SHARE_w1_cog_num$cf012_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = "cf012_") 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w1_cog_num, aes(x=factor(cf012_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_w1_cog_num$cf013_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = "cf013_") 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w1_cog_num, aes(x=factor(cf013_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_w1_cog_num$cf014_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = "cf014_") 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w1_cog_num, aes(x=factor(cf014_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_w1_cog_num$cf015_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = "cf015_") 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w1_cog_num, aes(x=factor(cf015_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable `cog_num_c` from the study-specific variables make the proportion of 1's over the non-missing values after recode them as follows

* `keep 1 into 1`
* `recode -1, 2, 3, 4, 5, 6 and 97 into 0`
* `-2 into NA`

and the missing values have to be recoded as follows:

* `-2 into 997`
* `NA into 999`

To compute the harmonized variable `cog_num` from `cog_num_c` it has to be recoded as follows:

* `cog_num_c > 0 into 1` 
* `cog_num_c = 0 into 0`
* `keep cog_num_c = 999 into 999`
* `keep cog_num_c = 997 into 997`

**R script:**

```{r harmo w1}

SHARE_w1_cog_num$cf012_2 <- car::recode(SHARE_w1_cog_num$cf012_, "2:6=0; 97=0; -1=0; -2=NA")
SHARE_w1_cog_num$cf013_2 <- car::recode(SHARE_w1_cog_num$cf013_, "2:6=0; 97=0; -1=0; -2=NA")
SHARE_w1_cog_num$cf014_2 <- car::recode(SHARE_w1_cog_num$cf014_, "2:7=0; 97=0; -1=0; -2=NA")
SHARE_w1_cog_num$cf015_2 <- car::recode(SHARE_w1_cog_num$cf015_, "2:6=0; 97=0; -1=0; -2=NA")
# In the 4 variables created just above the unique possible values are 0, 1, and NA

# The next variable is the sum of the non-missing values of the previous ones.(= quantity of ones)
SHARE_w1_cog_num$sum3 <- apply(SHARE_w1_cog_num[, 6:9], MARGIN = 1, FUN = function(x) sum(x,na.rm = TRUE))
# The next is the quantity of NA values in them
SHARE_w1_cog_num$comp3 <- apply(SHARE_w1_cog_num[, 6:9], MARGIN = 1, FUN = function(x) sum(is.na(x)) )
# The next keeps the quantity of zeroes in them.
SHARE_w1_cog_num$zero <- apply(SHARE_w1_cog_num[, 6:9], MARGIN = 1, FUN = function(x) sum(x==0, na.rm = TRUE))
# Number of missings -2
SHARE_w1_cog_num$tm <- apply(SHARE_w1_cog_num[, 2:5], MARGIN = 1, FUN = function(x) sum(x==-2, na.rm = TRUE))

# Therefore: sum3 + comp3 + zero = 4

SHARE_w1_cog_num$propInf <- SHARE_w1_cog_num$sum3/(4-SHARE_w1_cog_num$comp3)
SHARE_w1_cog_num$prop1 <- car::recode(SHARE_w1_cog_num$propInf,"Inf=NA")

SHARE_ds_w1 <- tibble(id=SHARE_w1_cog_num$id)
SHARE_ds_w1$cog_num_c <- SHARE_w1_cog_num$prop1
SHARE_ds_w1$cog_num_c[which(is.na(SHARE_ds_w1$cog_num_c) & SHARE_w1_cog_num$tm>=1)] <- 997

#other it's NA (example two items good and two NA)
SHARE_ds_w1$cog_num_c <- car::recode(SHARE_ds_w1$cog_num_c, "NA=999")


#cog_num
SHARE_ds_w1$cog_num <- car::recode(SHARE_ds_w1$cog_num_c, "0=0; 0.5:1=1")


```








#### Statistical description of the new harmonised variable
```{r descript w1, echo=FALSE}
vari <- SHARE_ds_w1$cog_num_c
kable(Categorical_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_num_c)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(SHARE_ds_w1 %>% filter(!vari %in% miss_values_vector), aes(x=cog_num_c)) + geom_bar(stat="count", width=0.075, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- SHARE_ds_w1$cog_num
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_num) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SHARE_ds_w1, aes(x=factor(cog_num))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=FALSE}

```



### Wave 2 

#### Study-specific variable description


| **Name** | `cf012_`| `cf013_`|`cf014_`|`cf015_`|
|-|-|-|-|-|
| **Label** | `Chance disease 10 perc. of 1000` |`Half price [of a  300 Euro sofa]` |`6000 is two-thirds what is total price` |`Amount in the savings account [on 2000 Euros after 2 years of 10% interest]` |
| **Table name** |`sharew2_rel2-6-0_cf`|`sharew2_rel2-6-0_cf`|`sharew2_rel2-6-0_cf`|`sharew2_rel2-6-0_cf`|
| **Categories** |`1 = correct answer: 100; 2 = wrong answer: 10; 3 = wrong answer: 90; 4 = wrong answer: 900; 97 = wrong answer: Other answer`|`1 = correct answer: 150; 2 = wrong answer: country-specific category 1; 3 = wrong answer: country-specific category 2; 4 = wrong answer: country-specific category 3; 5 = wrong answer: country-specific category 4; 97 = wrong answer: Other answer`|`1 = correct answer: 9000; 2 = wrong answer: country-specific category 1; 3 = wrong answer: country-specific category 2; 4 = wrong answer: country-specific category 3; 5 = wrong answer: country-specific category 4; 6 = wrong answer: country-specific category 5; 7 = wrong answer: country-specific category 6; 97 = wrong answer: Other answer`|`1 = correct answer: 2420; 2 = wrong answer: 2020; 3 = wrong answer: 2040; 4 = wrong answer: 2100; 5 = wrong answer: 2200; 6 = wrong answer: 2400; 97 = wrong answer: Other`|
| **Missings** |`-1 = don't know; -2 = refusal; NA`|`-1 = don't know; -2 = refusal; NA`|`-1 = don't know; -2 = refusal; NA`|`-1 = don't know; -2 = refusal; NA`|
| **Description** |  |  |  |  |



```{r assign w2, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_w2_cog_num','SHARE.sharew2_rel2-6-0_cf', variables=list('cf012_','cf013_','cf014_','cf015_'), missings = TRUE)
SHARE_w2_cog_num <- opal.execute(o,'SHARE_w2_cog_num')
```

```{r local w2, echo=FALSE}
vari <- SHARE_w2_cog_num$cf012_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = "cf012_") 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w2_cog_num, aes(x=factor(cf012_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_w2_cog_num$cf013_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = "cf013_") 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w2_cog_num, aes(x=factor(cf013_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_w2_cog_num$cf014_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = "cf014_") 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w2_cog_num, aes(x=factor(cf014_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_w2_cog_num$cf015_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = "cf015_") 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w2_cog_num, aes(x=factor(cf015_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable `cog_num_c` from the study-specific variables make the proportion of 1's over the non-missing values after recode them as follows

* `keep 1 into 1`
* `recode -1, 2, 3, 4, 5, 6 and 97 into 0`
* `-2 into NA`

and the missing values have to be recoded as follows:

* `-2 into 997`
* `NA into 999`

To compute the harmonized variable `cog_num` from `cog_num_c` it has to be recoded as follows:

* `cog_num_c > 0 into 1` 
* `cog_num_c = 0 into 0`
* `keep cog_num_c = 999 into 999`
* `keep cog_num_c = 997 into 997`

**R script:**

```{r harmo w2}
SHARE_w2_cog_num$cf012_2 <- car::recode(SHARE_w2_cog_num$cf012_, "2:6=0; 97=0; -1=0; -2=NA")
SHARE_w2_cog_num$cf013_2 <- car::recode(SHARE_w2_cog_num$cf013_, "2:6=0; 97=0; -1=0; -2=NA")
SHARE_w2_cog_num$cf014_2 <- car::recode(SHARE_w2_cog_num$cf014_, "2:7=0; 97=0; -1=0; -2=NA")
SHARE_w2_cog_num$cf015_2 <- car::recode(SHARE_w2_cog_num$cf015_, "2:6=0; 97=0; -1=0; -2=NA")

SHARE_w2_cog_num$sum3 <- apply(SHARE_w2_cog_num[, 6:9], MARGIN = 1, FUN = function(x) sum(x,na.rm = TRUE))
SHARE_w2_cog_num$comp3 <- apply(SHARE_w2_cog_num[, 6:9], MARGIN = 1, FUN = function(x) sum(is.na(x)) )
SHARE_w2_cog_num$zero <- apply(SHARE_w2_cog_num[, 6:9], MARGIN = 1, FUN = function(x) sum(x==0, na.rm = TRUE) )
SHARE_w2_cog_num$tm <- apply(SHARE_w2_cog_num[, 2:5], MARGIN = 1, FUN = function(x) sum(x==-2, na.rm = TRUE))







SHARE_w2_cog_num$propInf <- SHARE_w2_cog_num$sum3/(4-SHARE_w2_cog_num$comp3)
SHARE_w2_cog_num$prop1 <- car::recode(SHARE_w2_cog_num$propInf,"Inf=NA")

SHARE_ds_w2 <- tibble(id=SHARE_w2_cog_num$id)
SHARE_ds_w2$cog_num_c <- SHARE_w2_cog_num$prop1
SHARE_ds_w2$cog_num_c[which(is.na(SHARE_ds_w2$cog_num_c) & SHARE_w2_cog_num$tm>=1)] <- 997

#other it's NA (example two items good and two NA)
SHARE_ds_w2$cog_num_c <- car::recode(SHARE_ds_w2$cog_num_c, "NA=999")


#cog_num
SHARE_ds_w2$cog_num <- car::recode(SHARE_ds_w2$cog_num_c, "0=0; 0.5:1=1")







```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=FALSE}
vari <- SHARE_ds_w2$cog_num_c
kable(Categorical_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_num_c)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(SHARE_ds_w2 %>% filter(!vari %in% miss_values_vector), aes(x=cog_num_c)) + geom_bar(stat="count", width=0.075, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- SHARE_ds_w2$cog_num
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_num) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SHARE_ds_w2, aes(x=factor(cog_num))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=FALSE}

```



### Wave 3 

Not found



### Wave 4 

#### Study-specific variable description



| **Name** | `cf012_`| `cf013_`|`cf014_`|`cf015_`|
|-|-|-|-|-|
| **Label** | `Chance disease 10 perc. of 1000` |`Half price [of a  300 Euro sofa]` |`6000 is two-thirds what is total price` |`Amount in the savings account [on 2000 Euros after 2 years of 10% interest]` |
| **Table name** |`sharew4_rel1-1-1_cf`|`sharew4_rel1-1-1_cf`|`sharew4_rel1-1-1_cf`|`sharew4_rel1-1-1_cf`|
| **Categories** |`1 = correct answer: 100; 2 = wrong answer: 10; 3 = wrong answer: 90; 4 = wrong answer: 900; 97 = wrong answer: Other answer`|`1 = correct answer: 150; 2 = wrong answer: country-specific category 1; 3 = wrong answer: country-specific category 2; 4 = wrong answer: country-specific category 3; 5 = wrong answer: country-specific category 4; 97 = wrong answer: Other answer`|`1 = correct answer: 9000; 2 = wrong answer: country-specific category 1; 3 = wrong answer: country-specific category 2; 4 = wrong answer: country-specific category 3; 5 = wrong answer: country-specific category 4; 6 = wrong answer: country-specific category 5; 7 = wrong answer: country-specific category 6; 97 = wrong answer: Other answer`|`1 = correct answer: 2420; 2 = wrong answer: 2020; 3 = wrong answer: 2040; 4 = wrong answer: 2100; 5 = wrong answer: 2200; 6 = wrong answer: 2400; 97 = wrong answer: Other`|
| **Missings** |`-1 = don't know; -2 = refusal; NA`|`-1 = don't know; -2 = refusal; NA`|`-1 = don't know; -2 = refusal; NA`|`-1 = don't know; -2 = refusal; NA`|
| **Description** |  |  |  |  |



```{r assign w4, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_w4_cog_num','SHARE.sharew4_rel1-1-1_cf', variables=list('cf012_','cf013_','cf014_','cf015_'), missings = TRUE)
SHARE_w4_cog_num <- opal.execute(o,'SHARE_w4_cog_num')
```

```{r local w4, echo=FALSE}
vari <- SHARE_w4_cog_num$cf012_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = "cf012_") 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w4_cog_num, aes(x=factor(cf012_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_w4_cog_num$cf013_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = "cf013_") 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w4_cog_num, aes(x=factor(cf013_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_w4_cog_num$cf014_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = "cf014_") 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w4_cog_num, aes(x=factor(cf014_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_w4_cog_num$cf015_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = "cf015_") 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w4_cog_num, aes(x=factor(cf015_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable `cog_num_c` from the study-specific variables make the proportion of 1's over the non-missing values after recode them as follows

* `keep 1 into 1`
* `recode -1, 2, 3, 4, 5, 6 and 97 into 0`
* `-2 into NA`

and the missing values have to be recoded as follows:

* `-2 into 997`
* `NA into 999`

To compute the harmonized variable `cog_num` from `cog_num_c` it has to be recoded as follows:

* `cog_num_c > 0 into 1` 
* `cog_num_c = 0 into 0`
* `keep cog_num_c = 999 into 999`
* `keep cog_num_c = 997 into 997`

**R script:**

```{r harmo w4}
SHARE_w4_cog_num$cf012_2 <- car::recode(SHARE_w4_cog_num$cf012_, "2:6=0; 97=0; -1=0; -2=NA")
SHARE_w4_cog_num$cf013_2 <- car::recode(SHARE_w4_cog_num$cf013_, "2:6=0; 97=0; -1=0; -2=NA")
SHARE_w4_cog_num$cf014_2 <- car::recode(SHARE_w4_cog_num$cf014_, "2:7=0; 97=0; -1=0; -2=NA")
SHARE_w4_cog_num$cf015_2 <- car::recode(SHARE_w4_cog_num$cf015_, "2:6=0; 97=0; -1=0; -2=NA")

SHARE_w4_cog_num$sum3 <- apply(SHARE_w4_cog_num[, 6:9], MARGIN = 1, FUN = function(x) sum(x,na.rm = TRUE))
SHARE_w4_cog_num$comp3 <- apply(SHARE_w4_cog_num[, 6:9], MARGIN = 1, FUN = function(x) sum(is.na(x)) )

SHARE_w4_cog_num$zero <- apply(SHARE_w4_cog_num[, 6:9], MARGIN = 1, FUN = function(x) sum(x==0, na.rm = TRUE) )
SHARE_w4_cog_num$tm <- apply(SHARE_w4_cog_num[, 2:5], MARGIN = 1, FUN = function(x) sum(x==-2, na.rm = TRUE))







SHARE_w4_cog_num$propInf <- SHARE_w4_cog_num$sum3/(4-SHARE_w4_cog_num$comp3)
SHARE_w4_cog_num$prop1 <- car::recode(SHARE_w4_cog_num$propInf,"Inf=NA")

SHARE_ds_w4 <- tibble(id=SHARE_w4_cog_num$id)
SHARE_ds_w4$cog_num_c <- SHARE_w4_cog_num$prop1
SHARE_ds_w4$cog_num_c[which(is.na(SHARE_ds_w4$cog_num_c) & SHARE_w4_cog_num$tm>=1)] <- 997

#other it's NA (example two items good and two NA)
SHARE_ds_w4$cog_num_c <- car::recode(SHARE_ds_w4$cog_num_c, "NA=999")


#cog_num
SHARE_ds_w4$cog_num <- car::recode(SHARE_ds_w4$cog_num_c, "0=0; 0.5:1=1")


```

#### Statistical description of the new harmonised variable
```{r descript w4, echo=FALSE}
vari <- SHARE_ds_w4$cog_num_c
kable(Categorical_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_num_c)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(SHARE_ds_w4 %>% filter(!vari %in% miss_values_vector), aes(x=cog_num_c)) + geom_bar(stat="count", width=0.075, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- SHARE_ds_w4$cog_num
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_num) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SHARE_ds_w4, aes(x=factor(cog_num))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w4, echo=FALSE}

```





### Wave 5 

#### Study-specific variable description



| **Name** | `cf012_`| `cf013_`|`cf014_`|`cf015_`|
|-|-|-|-|-|
| **Label** | `Chance disease 10 perc. of 1000` |`Half price [of a  300 Euro sofa]` |`6000 is two-thirds what is total price` |`Amount in the savings account [on 2000 Euros after 2 years of 10% interest]` |
| **Table name** |`sharew5_rel1-0-0_cf`|`sharew5_rel1-0-0_cf`|`sharew5_rel1-0-0_cf`|`sharew5_rel1-0-0_cf`|
| **Categories** |`1 = correct answer: 100; 2 = wrong answer: 10; 3 = wrong answer: 90; 4 = wrong answer: 900; 97 = wrong answer: Other answer`|`1 = correct answer: 150; 2 = wrong answer: country-specific category 1; 3 = wrong answer: country-specific category 2; 4 = wrong answer: country-specific category 3; 5 = wrong answer: country-specific category 4; 97 = wrong answer: Other answer`|`1 = correct answer: 9000; 2 = wrong answer: country-specific category 1; 3 = wrong answer: country-specific category 2; 4 = wrong answer: country-specific category 3; 5 = wrong answer: country-specific category 4; 6 = wrong answer: country-specific category 5; 7 = wrong answer: country-specific category 6; 97 = wrong answer: Other answer`|`1 = correct answer: 2420; 2 = wrong answer: 2020; 3 = wrong answer: 2040; 4 = wrong answer: 2100; 5 = wrong answer: 2200; 6 = wrong answer: 2400; 97 = wrong answer: Other`|
| **Missings** |`-1 = don't know; -2 = refusal; NA`|`-1 = don't know; -2 = refusal; NA`|`-1 = don't know; -2 = refusal; NA`|`-1 = don't know; -2 = refusal; NA`|
| **Description** |  |  |  |  |


```{r assign w5, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_w5_cog_num','SHARE.sharew5_rel1-0-0_cf', variables=list('cf012_','cf013_','cf014_','cf015_'), missings = TRUE)
SHARE_w5_cog_num <- opal.execute(o,'SHARE_w5_cog_num')
```

```{r local w5, echo=FALSE}
vari <- SHARE_w5_cog_num$cf012_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = "cf012_") 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w5_cog_num, aes(x=factor(cf012_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_w5_cog_num$cf013_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = "cf013_") 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w5_cog_num, aes(x=factor(cf013_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_w5_cog_num$cf014_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = "cf014_") 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w5_cog_num, aes(x=factor(cf014_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_w5_cog_num$cf015_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = "cf015_") 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w5_cog_num, aes(x=factor(cf015_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable `cog_num_c` from the study-specific variables make the proportion of 1's over the non-missing values after recode them as follows

* `keep 1 into 1`
* `recode -1, 2, 3, 4, 5, 6 and 97 into 0`
* `-2 into NA`

and the missing values have to be recoded as follows:

* `-2 into 997`
* `NA into 999`

To compute the harmonized variable `cog_num` from `cog_num_c` it has to be recoded as follows:

* `cog_num_c > 0 into 1` 
* `cog_num_c = 0 into 0`
* `keep cog_num_c = 999 into 999`
* `keep cog_num_c = 997 into 997`

**R script:**

```{r harmo w5}
SHARE_w5_cog_num$cf012_2 <- car::recode(SHARE_w5_cog_num$cf012_, "2:6=0; 97=0; -1=0; -2=NA")
SHARE_w5_cog_num$cf013_2 <- car::recode(SHARE_w5_cog_num$cf013_, "2:6=0; 97=0; -1=0; -2=NA")
SHARE_w5_cog_num$cf014_2 <- car::recode(SHARE_w5_cog_num$cf014_, "2:7=0; 97=0; -1=0; -2=NA")
SHARE_w5_cog_num$cf015_2 <- car::recode(SHARE_w5_cog_num$cf015_, "2:6=0; 97=0; -1=0; -2=NA")

SHARE_w5_cog_num$sum3 <- apply(SHARE_w5_cog_num[, 6:9], MARGIN = 1, FUN = function(x) sum(x,na.rm = TRUE))
SHARE_w5_cog_num$comp3 <- apply(SHARE_w5_cog_num[, 6:9], MARGIN = 1, FUN = function(x) sum(is.na(x)) )

SHARE_w5_cog_num$zero <- apply(SHARE_w5_cog_num[, 6:9], MARGIN = 1, FUN = function(x) sum(x==0, na.rm = TRUE) )
SHARE_w5_cog_num$tm <- apply(SHARE_w5_cog_num[, 2:5], MARGIN = 1, FUN = function(x) sum(x==-2, na.rm = TRUE))







SHARE_w5_cog_num$propInf <- SHARE_w5_cog_num$sum3/(4-SHARE_w5_cog_num$comp3)
SHARE_w5_cog_num$prop1 <- car::recode(SHARE_w5_cog_num$propInf,"Inf=NA")

SHARE_ds_w5 <- tibble(id=SHARE_w5_cog_num$id)
SHARE_ds_w5$cog_num_c <- SHARE_w5_cog_num$prop1
SHARE_ds_w5$cog_num_c[which(is.na(SHARE_ds_w5$cog_num_c) & SHARE_w5_cog_num$tm>=1)] <- 997

#other it's NA (example two items good and two NA)
SHARE_ds_w5$cog_num_c <- car::recode(SHARE_ds_w5$cog_num_c, "NA=999")


#cog_num
SHARE_ds_w5$cog_num <- car::recode(SHARE_ds_w5$cog_num_c, "0=0; 0.5:1=1")


```

#### Statistical description of the new harmonised variable
```{r descript w5, echo=FALSE}
vari <- SHARE_ds_w5$cog_num_c
kable(Categorical_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_num_c)
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(SHARE_ds_w5 %>% filter(!vari %in% miss_values_vector), aes(x=cog_num_c)) + geom_bar(stat="count", width=0.075, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- SHARE_ds_w5$cog_num
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_num) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SHARE_ds_w5, aes(x=factor(cog_num))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w5, echo=FALSE}

```













## Descriptive statistics of the harmonised variable `cog_num` accross populations and waves







<!--AUXILIAR FUNCTIONS-->



```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds,vbl_name=hd_vbl,ds_lab = ds_label){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    if(vbl_name %in% names(l.hds[[name]])){
      # In the aux_object we copy the old tibble to recodify all missing values as NA.
      aux_object <- l.hds[[name]]
      # Labelling of variables
      label(l.hds[[name]][[vbl_name]]) <- label(aux_object[[vbl_name]]) <- ds_lab
      # Labelling of categories (for continues variables, only missing values)
      l.hds[[name]][[vbl_name]] <- labelled(l.hds[[name]][[vbl_name]], labels = cat_label)
      aux_object[[vbl_name]] <- car::recode(aux_object[[vbl_name]], "miss_values_vector=NA")
      # Labelling of categories (for categorical variables, only non-missing values)
      aux_object[[vbl_name]] <- labelled(aux_object[[vbl_name]], labels = cat_label[1:(length(cat_label)-9)])
      # Saving the recodified tibble in list m.hds
      m.hds[[name]] <- aux_object
      rm(aux_object)
    }
  }
  return(list(l.hds,m.hds))

}


labelling_c <- function(l.hds,m.hds,vbl_name,ds_lab=ds_label){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    if(vbl_name %in% names(l.hds[[name]])){
      # In the aux_object we copy the old tibble to recodify all missing values as NA.
      aux_object <- m.hds[[name]]
      # Labelling of variables
      label(l.hds[[name]][[vbl_name]]) <- label(aux_object[[vbl_name]]) <- ds_lab
      # Labelling of categories (for continues variables, only missing values)
      l.hds[[name]][[vbl_name]] <- labelled(l.hds[[name]][[vbl_name]], labels = cont_label)
      aux_object[[vbl_name]] <- car::recode(aux_object[[vbl_name]], "miss_values_vector=NA")
      aux_object[[vbl_name]] <- remove_val_labels(aux_object[[vbl_name]])
      # Saving the recodified tibble in list m.hds
      m.hds[[name]] <- aux_object
      rm(aux_object)
    }
  }
  return(list(l.hds,m.hds))

}


# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames,vbl_name){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][vbl_name])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][vbl_name])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[2+length(cat_label),] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}


# Creation of summary tables for continuous data

summaries_c <- function(l.hds,m.hds,lnames,vbl_name){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][vbl_name])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[vbl_name]], missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][vbl_name])[1:6]
    # Next, missing/no-missing values (the 1 in $values_table[1,] stands for absolute values, while a 2 would stand for percentages)
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[vbl_name]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][vbl_name]))[[2]],lnames)
  return(t.hds)
  
}



# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }
  
}

```



```{r populations-waves, echo=F}


# All study waves and populations with abbreviated and descriptive names

share.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"))



```


<!--Labelling and saving-->

```{r, echo=FALSE}


# Consider only waves with some variable harmonised

l.hds <- lapply(share.cw, function(wname) if(exists(paste0("SHARE_ds_",wname[1]))){wname = list(get(paste0("SHARE_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling categorical variable of tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]],hd_vbl,ds_label_cog_num)
  # Labelling continuous variable of tibbles
  lmlist <- labelling_c(lmlist[[1]],lmlist[[2]],hd_vbl_c,ds_label_cog_num_c)
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}

sharelist <- lmlist # SHARE list




```



<!--Descriptives-->



Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.

```{r summ, echo=F}


# Consider only harmonised waves
l.hds <- lapply(share.cw, function(wname) if(hd_vbl %in% names(get0(paste0("SHARE_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- sharelist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- sharelist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl),caption=ds_label_cog_num))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))

}



```






## Summary of descriptive statistics of the harmonised variable `cog_num_c` accross populations and waves






```{r summ_c, echo=F}


# Consider only harmonised waves
l.hds <- lapply(share.cw, function(wname) if(hd_vbl_c %in% names(get0(paste0("SHARE_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- sharelist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- sharelist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries_c(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl_c),caption=ds_label_cog_num_c))
}





```






# Quality estimation
All the individuals have at least 1 item missing from the four choose, after check if there is a skip or any reason to such high number of missing data, it was decided to compute `cog_num_c` as the proportion of 1's (correct answers) among all the non-missing answers. Then, since the 25% of individuals with less puntuation cuts the 0.5, we codify to `cog_num=0` only those with proportion of 1's equal to zero, otherwise `cog_num=1`.



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
