---
title: "Self Rated Health"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `srh`
* Variable label: `Respondent's self-rated/self-reported health on a Likert-type scale`
* Variable description: `Respondent's self-rated/self-reported health on a Likert-type scale`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:


**Code** | **Category Label**
-------- | ------------------
1        | Good
2        | Average/Fair/Moderate
3        | Poor

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




```{r lab, echo=FALSE}
ds_label <- "Self Rated Health"
ds_label_all <- "Respondent's self-rated/self-reported health on a Likert-type scale"
```

# Data process

## SHARE

### Wave 1 

#### Study-specific variable description




| **Name** | `ph002_`| `ph003_`|`ph052_`|`ph053_`|
|-|-|-|-|-|
| **Label** | `health in general question 1` |`health in general question 2` |`health in general question 2` |`health in general question 1` |
| **Table name** |`sharew1_rel2-6-0_ph`|`sharew1_rel2-6-0_ph`|`sharew1_rel2-6-0_ph`|`sharew1_rel2-6-0_ph`|
| **Categories** |`1 = Very Good; 2 = Good; 3 = Fair; 4 = Bad; 5 = Very bad`|`1 = Excellent; 2 = Very Good; 3 = Good; 4 = Fair; 5 = Poor`|`1 = Excellent; 2 = Very Good; 3 = Good; 4 = Fair; 5 = Poor`|`1 = Very Good; 2 = Good; 3 = Fair; 4 = Bad; 5 = Very bad`|
| **Missings** |`-1 = don't know; -2 = refusal; NA`|`-1 = don't know; -2 = refusal; NA`|`-1 = don't know; -2 = refusal; NA`|`-1 = don't know; -2 = refusal; NA`|
| **Description** |  |  |  |  |

There are two types of answer categories for the question about self-perceived health in wave 1 (one corresponding to `ph002,ph053`, and the other to `ph003,ph052`). Which type is asked at the beginning of section Physical Health (questions `ph002/003`), and which (other) type for the end of this section (questions `ph052/053`), is randomized.
So, individuals answer either `ph002` and `ph052` or `ph003` and `ph053` (each question of a different type).

```{r assign w1, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_w1_srh','SHARE.sharew1_rel2-6-0_ph', variables=list('ph002_','ph003_','ph052_','ph053_'), missings = TRUE)
SHARE_w1_srh <- opal.execute(o,'SHARE_w1_srh')
```

```{r local w1, echo=FALSE}
vari <- SHARE_w1_srh$ph002_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w1_srh, aes(x=factor(ph002_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")

vari <- SHARE_w1_srh$ph003_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w1_srh, aes(x=factor(ph003_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")

vari <- SHARE_w1_srh$ph052_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w1_srh, aes(x=factor(ph052_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")

vari <- SHARE_w1_srh$ph053_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w1_srh, aes(x=factor(ph053_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm


Along the other waves the question on self-rated health is made at the beginning of the Physical Health section, therefore we keep the data of `ph002` and `ph003` and we remark in the validation the contradictions with the other data.

To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `ph002_  == 1|2 or ph003_== 1|2|3 into 1` 
* `ph002_ == 3 or ph003_== 4 into 2`
* `ph002_ == 4|5 or ph003_== 5 into 3`
* `ph002_ == -2 or ph003_== -2 refusal into 997`
* `ph003_ == -1 or ph003_== -1 don't know into 998`
* `NA into 999`

**R script:**

```{r harmo w1}
SHARE_ds_w1 <- tibble(id=SHARE_w1_srh$id)

SHARE_ds_w1$srh <- car::recode(SHARE_w1_srh$ph003_, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA = '999';-2 = '997';-1 = '998' ")

SHARE_ds_w1$srh[is.na(SHARE_w1_srh$ph003_)] <- car::recode(SHARE_w1_srh$ph002_[is.na(SHARE_w1_srh$ph003_)], "1=1; 2=1; 3=2; 4=3; 5=3; -2=997; -1=998; NA=999")

SHARE_ds_w1$srh <- labelled(SHARE_ds_w1$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=FALSE}
vari <- SHARE_ds_w1$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w1, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=FALSE, results='asis'}
#ph003_ was selected
AfterH <- table(SHARE_ds_w1$srh)
X<-table(SHARE_w1_srh$ph003_)
Y<-table(SHARE_w1_srh$ph002_)
BeforeH <- c(sum(X[3:5],Y[3:4]),X[6]+Y[5],X[7]+sum(Y[6:7]),X[c(1,2)]+Y[c(1,2)],sum((is.na(SHARE_w1_srh$ph003_) & is.na(SHARE_w1_srh$ph002_))))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("ph002=1,2,ph003=1,2,3->1","ph002=3,ph003=4->1","ph002=4,5,ph003=5->3","-2->997","-1->998","NA->999")
kable(C)

cat("On the individuals asked ph002 and ph052:")

kable(frq(SHARE_w1_srh$ph052_[!is.na(SHARE_w1_srh$ph002_) & SHARE_w1_srh$ph002_ %in% c(1,2)]),align = 'c', caption = 'For the individuals that told their health is good (or very good) in the first question about self-rated health (ph002), which are the answers in the second question (ph052). Recall the meaning of the values: 1 = Excellent; 2 = Very Good; 3 = Good; 4 = Fair; 5 = Poor.')
kable(SHARE_w1_srh[!is.na(SHARE_w1_srh$ph002_) & SHARE_w1_srh$ph002_ %in% c(1,2)& !is.na(SHARE_w1_srh$ph052_) & SHARE_w1_srh$ph052_ == 5,],align = 'c',caption = 'The 8 individuals which told their health is good or very good at the beginning of the Physical Health questions and that at the end told their health is poor:')

kable(frq(SHARE_w1_srh$ph052_[!is.na(SHARE_w1_srh$ph002_) & SHARE_w1_srh$ph002_ %in% c(3)]),align = 'c', caption = 'For the individuals that told their health is fair in the first question about self-rated health (ph002), which are the answers in the second question (ph052). Recall the meaning of the values: 1 = Excellent; 2 = Very Good; 3 = Good; 4 = Fair; 5 = Poor.')

kable(frq(SHARE_w1_srh$ph052_[!is.na(SHARE_w1_srh$ph002_) & SHARE_w1_srh$ph002_ %in% c(4,5)]),align = 'c', caption = 'For the individuals that told their health is bad (or very bad) in the first question about self-rated health (ph002), which are the answers in the second question (ph052). Recall the meaning of the values: 1 = Excellent; 2 = Very Good; 3 = Good; 4 = Fair; 5 = Poor.')
kable(SHARE_w1_srh[!is.na(SHARE_w1_srh$ph002_) & SHARE_w1_srh$ph002_ %in% c(4,5)& !is.na(SHARE_w1_srh$ph052_) & SHARE_w1_srh$ph052_ %in% c(1,2,3),],align = 'c',caption = 'The 139 individuals which told their health is bad or very bad at the beginning of the Physical Health questions and that at the end told their health is at least good:')



cat("On the individuals asked ph003 and ph053:")


kable(frq(SHARE_w1_srh$ph053_[!is.na(SHARE_w1_srh$ph003_) & SHARE_w1_srh$ph003_ %in% c(1,2,3)]),align = 'c', caption = 'For the individuals that told their health is at least good in the first question about self-rated health (ph003), which are the answers in the second question (ph053). Recall the meaning of the values: 1 = Very Good; 2 = Good; 3 = Fair; 4 = Bad; 5 = Very bad.')
kable(SHARE_w1_srh[!is.na(SHARE_w1_srh$ph003_) & SHARE_w1_srh$ph003_ %in% c(1,2,3)& !is.na(SHARE_w1_srh$ph053_) & SHARE_w1_srh$ph053_ == 4,],align = 'c',caption = 'The 27 individuals which told their health is at least good at the beginning of the Physical Health questions and that at the end told their health is bad:')

kable(frq(SHARE_w1_srh$ph053_[!is.na(SHARE_w1_srh$ph003_) & SHARE_w1_srh$ph003_ %in% c(4)]),align = 'c', caption = 'For the individuals that told their health is fair in the first question about self-rated health (ph003), which are the answers in the second question (ph053). Recall the meaning of the values: 1 = Very Good; 2 = Good; 3 = Fair; 4 = Bad; 5 = Very bad.')

kable(frq(SHARE_w1_srh$ph053_[!is.na(SHARE_w1_srh$ph003_) & SHARE_w1_srh$ph003_ %in% c(5)]),align = 'c', caption = 'For the individuals that told their health is poor in the first question about self-rated health (ph003), which are the answers in the second question (ph053). Recall the meaning of the values: 1 = Very Good; 2 = Good; 3 = Fair; 4 = Bad; 5 = Very bad.')
kable(SHARE_w1_srh[!is.na(SHARE_w1_srh$ph003_) & SHARE_w1_srh$ph003_ %in% c(5)& !is.na(SHARE_w1_srh$ph053_) & SHARE_w1_srh$ph053_ %in% c(1,2),],align = 'c',caption = 'The 26 individuals which told their health is poor at the beginning of the Physical Health questions and that at the end told their health is at good or very good:')

```

```{r importOPAL w1, echo=FALSE}
label(SHARE_ds_w1$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- SHARE_ds_w1
save(srh, file = "../RData/w1/srh.RData")
#opal.assign.data(o, 'SHARE_ds_w1', SHARE_ds_w1)
#opal.symbol_import(o,'SHARE_ds_w1', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w1 <- SHARE_ds_w1
SHARE_m_ds_w1$srh <- car::recode(SHARE_m_ds_w1$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w1', SHARE_m_ds_w1)
#opal.symbol_import(o,'SHARE_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description


| **Name** | `ph003_`|
|-|-|
| **Label** | `health in general question 2` |
| **Table name** |`sharew2_rel2-6-0_ph`|
| **Categories** |`1 = Excellent; 2 = Very Good; 3 = Good; 4 = Fair; 5 = Poor`|
| **Missings** |`-1 = Don't know; -2 = Refusal; NA`|
| **Description** |  |


```{r assign w2, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_w2_srh','SHARE.sharew2_rel2-6-0_ph', variables=list('ph003_'), missings = TRUE)
SHARE_w2_srh <- opal.execute(o,'SHARE_w2_srh')
```

```{r local w2, echo=FALSE}
vari <- SHARE_w2_srh$ph003_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w2_srh, aes(x=factor(ph003_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 1` 
* `3 into 1`
* `4 into 2`
* `5 into 3`
* `-2 refusal into 997`
* `-1 don't know into 998`
* `NA into 999`

**R script:**

```{r harmo w2}
SHARE_ds_w2 <- tibble(id=SHARE_w2_srh$id)
SHARE_ds_w2$srh <- car::recode(SHARE_w2_srh$ph003_, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA = '999';-2 = '997';-1 = '998' ")
SHARE_ds_w2$srh <- labelled(SHARE_ds_w2$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=FALSE}
vari <- SHARE_ds_w2$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w2, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=FALSE}
AfterH <- table(SHARE_ds_w2$srh)
X<-table(SHARE_w2_srh$ph003_)
BeforeH <- c(sum(X[3:5]),X[c(6,7,1,2)],sum(is.na(SHARE_w2_srh$ph003_)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->1","5->3","-2->997","-1->998","NA->999")
kable(C)
```

```{r importOPAL w2, echo=FALSE}
label(SHARE_ds_w2$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- SHARE_ds_w2
save(srh, file = "../RData/w2/srh.RData")
#opal.assign.data(o, 'SHARE_ds_w2', SHARE_ds_w2)
#opal.symbol_import(o,'SHARE_ds_w2', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w2 <- SHARE_ds_w2
SHARE_m_ds_w2$srh <- car::recode(SHARE_m_ds_w2$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w2', SHARE_m_ds_w2)
#opal.symbol_import(o,'SHARE_m_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 3 

#### Study-specific variable description


| **Name** | `sl_ph003_`|
|-|-|
| **Label** | `health in general question for wave 3` |
| **Table name** |`sharew3_rel1_hs`|
| **Categories** |`1 = Excellent; 2 = Very Good; 3 = Good; 4 = Fair; 5 = Poor`|
| **Missings** |`-1 = Don't know; -2 = Refusal; NA`|
| **Description** |  |



```{r assign w3, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_w3_srh','SHARE.sharew3_rel1_hs', variables=list('sl_ph003_'), missings = TRUE)
SHARE_w3_srh <- opal.execute(o,'SHARE_w3_srh')
```

```{r local w3, echo=FALSE}
vari <- SHARE_w3_srh$sl_ph003_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w3_srh, aes(x=factor(sl_ph003_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 1` 
* `3 into 1`
* `4 into 2`
* `5 into 3`
* `-2 refusal into 997`
* `-1 don't know into 998`
* `NA into 999`

**R script:**

```{r harmo w3}
SHARE_ds_w3 <- tibble(id=SHARE_w3_srh$id)
SHARE_ds_w3$srh <- car::recode(SHARE_w3_srh$sl_ph003_, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA = '999';-2 = '997';-1 = '998' ")
SHARE_ds_w3$srh <- labelled(SHARE_ds_w3$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=FALSE}
vari <- SHARE_ds_w3$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w3, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=FALSE}
AfterH <- table(SHARE_ds_w3$srh)
X<-table(SHARE_w3_srh$sl_ph003_)
BeforeH <- c(sum(X[3:5]),X[c(6,7,1,2)],sum(is.na(SHARE_w3_srh$sl_ph003_)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->1","5->3","-2->997","-1->998","NA->999")
kable(C)
```

```{r importOPAL w3, echo=FALSE}
label(SHARE_ds_w3$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- SHARE_ds_w3
save(srh, file = "../RData/w3/srh.RData")
#opal.assign.data(o, 'SHARE_ds_w3', SHARE_ds_w3)
#opal.symbol_import(o,'SHARE_ds_w3', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w3 <- SHARE_ds_w3
SHARE_m_ds_w3$srh <- car::recode(SHARE_m_ds_w3$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w3', SHARE_m_ds_w3)
#opal.symbol_import(o,'SHARE_m_ds_w3', project='_Athlos_Harm_Dataset')
```



### Wave 4

#### Study-specific variable description


| **Name** | `ph003_`|
|-|-|
| **Label** | `health in general question 2` |
| **Table name** |`sharew4_rel1-1-1_ph`|
| **Categories** |`1 = Excellent; 2 = Very Good; 3 = Good; 4 = Fair; 5 = Poor`|
| **Missings** |`-1 = Don't know; -2 = Refusal; NA`|
| **Description** |  |



```{r assign w4, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_w4_srh','SHARE.sharew4_rel1-1-1_ph', variables=list('ph003_'), missings = TRUE)
SHARE_w4_srh <- opal.execute(o,'SHARE_w4_srh')
```

```{r local w4, echo=FALSE}
vari <- SHARE_w4_srh$ph003_
kable(Categorical_summary(vari, missing_values = c(-1,-2))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-1,-2))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-2))[2], caption = "Type of missing")
ggplot(SHARE_w4_srh, aes(x=factor(ph003_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 1` 
* `3 into 1`
* `4 into 2`
* `5 into 3`
* `-2 refusal into 997`
* `-1 don't know into 998`
* `NA into 999`

**R script:**

```{r harmo w4}
SHARE_ds_w4 <- tibble(id=SHARE_w4_srh$id)
SHARE_ds_w4$srh <- car::recode(SHARE_w4_srh$ph003_, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA = '999';-2 = '997';-1 = '998' ")
SHARE_ds_w4$srh <- labelled(SHARE_ds_w4$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w4, echo=FALSE}
vari <- SHARE_ds_w4$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w4, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w4, echo=FALSE}
AfterH <- table(SHARE_ds_w4$srh)
X<-table(SHARE_w4_srh$ph003_)
BeforeH <- c(sum(X[3:5]),X[c(6,7,1,2)],sum(is.na(SHARE_w4_srh$ph003_)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->1","5->3","-2->997","-1->998","NA->999")
kable(C)
```

```{r importOPAL w4, echo=FALSE}
label(SHARE_ds_w4$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- SHARE_ds_w4
save(srh, file = "../RData/w4/srh.RData")
#opal.assign.data(o, 'SHARE_ds_w4', SHARE_ds_w4)
#opal.symbol_import(o,'SHARE_ds_w4', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w4 <- SHARE_ds_w4
SHARE_m_ds_w4$srh <- car::recode(SHARE_m_ds_w4$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w4', SHARE_m_ds_w4)
#opal.symbol_import(o,'SHARE_m_ds_w4', project='_Athlos_Harm_Dataset')
```



### Wave 5 

#### Study-specific variable description


| **Name** | `ph003_`|
|-|-|
| **Label** | `health in general question 2` |
| **Table name** |`sharew5_rel1-0-0_ph`|
| **Categories** |`1 = Excellent; 2 = Very Good; 3 = Good; 4 = Fair; 5 = Poor`|
| **Missings** |`-1 = Don't know; -2 = Refusal; NA`|
| **Description** |  |



```{r assign w5, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_w5_srh','SHARE.sharew5_rel1-0-0_ph', variables=list('ph003_'), missings = TRUE)
SHARE_w5_srh <- opal.execute(o,'SHARE_w5_srh')
```

```{r local w5, echo=FALSE}
vari <- SHARE_w5_srh$ph003_
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(SHARE_w5_srh, aes(x=factor(ph003_))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2 into 1` 
* `3 into 1`
* `4 into 2`
* `5 into 3`
* `-2 refusal into 997`
* `-1 don't know into 998`
* `NA into 999`

**R script:**

```{r harmo w5}
SHARE_ds_w5 <- tibble(id=SHARE_w5_srh$id)
SHARE_ds_w5$srh <- car::recode(SHARE_w5_srh$ph003_, "1 = '1';2 = '1';3 = '1';4 = '2';5 = '3';NA = '999';-2 = '997';-1 = '998' ")
SHARE_ds_w5$srh <- labelled(SHARE_ds_w5$srh, labels = c("Good"=1, "Fair"=2, "Bad"=3,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w5, echo=FALSE}
vari <- SHARE_ds_w5$srh
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w5, aes(x=factor(srh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Self Rated Health") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w5, echo=FALSE}
AfterH <- table(SHARE_ds_w5$srh)
X<-table(SHARE_w5_srh$ph003_)
BeforeH <- c(sum(X[3:5]),X[c(6,7,1,2)],sum(is.na(SHARE_w5_srh$ph003_)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3->1","4->1","5->3","-2->997","-1->998","NA->999")
kable(C)
```

```{r importOPAL w5, echo=FALSE}
label(SHARE_ds_w5$srh) <- "Respondent's self-rated/self-reported health on a Likert-type scale"
srh <- SHARE_ds_w5
save(srh, file = "../RData/w5/srh.RData")
#opal.assign.data(o, 'SHARE_ds_w5', SHARE_ds_w5)
#opal.symbol_import(o,'SHARE_ds_w5', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w5 <- SHARE_ds_w5
SHARE_m_ds_w5$srh <- car::recode(SHARE_m_ds_w5$srh, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w5', SHARE_m_ds_w5)
#opal.symbol_import(o,'SHARE_m_ds_w5', project='_Athlos_Harm_Dataset')
```


# Quality estimation

At wave 1, two questions on self-rated health with different scales were used, and respondents were asked to rate their health status twice, once at the beginning of the relevant health section and again at the end. Question order was assigned randomly.
The PSSJD work-team has decided to take the first question which the person has answered based on the conclusions extracted in Bowling and Windsor - JECH 2008;62:81–85. 

Other waves: only one question was asked. No more comments. 

[Comments on the quality of the new harmonised variable. This section can be done in a later stage, once all variables are harmonised.]


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
