---
title: "Evaluative well-being"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE}
source("../../setup_laia.r")
```

<!-- ########################################################## --> 

```{r main, child='../../_DS_Rmd/evaluative_wbDS.Rmd'}
```


```{r global, echo=F}
source('../../_DS_Rmd/evaluative_wbDS.R')
```

<!-- ########################################################## --> 

# Data process

## SHARE 

### Wave 1 

#### Study-specific variable description

| **Name** | `q1`|
|-|-|
| **Label** | `how satisfied are you with your life in general`|
| **Table name** | `sharew1_rel2-6-0_dropoff` |
| **Categories** |`1 = very satisfied` <br/> `2 = somewhat satisfied` <br/> `3 = somewhat dissatisfied` <br/> `4 = very dissatisfied`|
| **Missing** |`-5 = not answered`| 
| **Description** |  |

```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_wb','SHARE.sharew1_rel2-6-0_dropoff',
                         variables=list('q1'), missings = TRUE)
SHARE_wb <- opal.execute(o,'SHARE_wb')
```

```{r local1, echo=FALSE}
vbl <- SHARE_wb$q1
kable(Categorical_summary(vbl, missing_values = c(-1:-2))[3], caption = label(vbl)) 
kable(Categorical_summary(vbl, missing_values = c(-1:-2))[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = c(-1:-2))[2], caption = "Type of missing")
ggplot(SHARE_wb, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 into 2`
* `2,3 into 1`
* `4 into 0` 
* `-5 into 995`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
SHARE_ds_w1 <- tibble(id=SHARE_wb$id)
SHARE_ds_w1$evaluative_wb <- car::recode(SHARE_wb[[2]], "1=2; 2=1; 3=1; 4=0; -5=995; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- SHARE_ds_w1[[2]]
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = label(vari)) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w1, aes(x=factor(evaluative_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation

```{r importOPAL1, echo=FALSE}
evaluative_wb <- SHARE_ds_w1
save(evaluative_wb, file = "../RData/w1/evaluative_wb.RData")
```





### Wave 2 

#### Study-specific variable description


| **Name** | `ac012_`|
|-|-|
| **Label** | `how satisfied with life`|
| **Table name** | `sharew2_rel2-6-0_ac` |
| **Scale** |`0 = Completely dissatisfied` <br/> `...` <br/> `10 = completely satisfied`|
| **Missing** |`-2 = refusal` <br/> `-1 = don't know`| 
| **Description** |  |

```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_wb','SHARE.sharew2_rel2-6-0_ac',
                         variables=list('ac012_'), missings = TRUE)
SHARE_wb <- opal.execute(o,'SHARE_wb')
```

```{r local2, echo=FALSE}
vbl <- SHARE_wb$ac012_
kable(Categorical_summary(vbl, missing_values = c(-1:-2))[3], caption = label(vbl)) 
kable(Categorical_summary(vbl, missing_values = c(-1:-2))[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = c(-1:-2))[2], caption = "Type of missing")
ggplot(SHARE_wb, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `First tertile into 0`
* `Second tertile into 1`
* `Third tertile into 2`
* `-2 into 997`
* `-1 into 998`

**R script:**

```{r harmo2, echo=TRUE}
qq <- quantile(SHARE_wb$ac012_, probs = c(0.33, 0.66), na.rm = TRUE )

SHARE_ds_w2 <- tibble(id=SHARE_wb$id)
SHARE_ds_w2$evaluative_wb <- car::recode(SHARE_wb$ac012_, "0:qq[1]=0; (qq[1]+0.1):qq[2]=1; (qq[2]+1):10=2; -2=997; -1=998; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- SHARE_ds_w2[[2]]
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = label(vari)) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w2, aes(x=factor(evaluative_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation

```{r importOPAL2, echo=FALSE}
evaluative_wb <- SHARE_ds_w2
save(evaluative_wb, file = "../RData/w2/evaluative_wb.RData")
```




### Wave 3 

There is no variable.





### Wave 4 

#### Study-specific variable description



| **Name** | `ac012_`|
|-|-|
| **Label** | `how satisfied with life`|
| **Table name** | `sharew4_rel1-1-1_ac` |
| **Scale** |`0 = Completely dissatisfied` <br/> `...` <br/> `10 = completely satisfied`|
| **Missing** |`-2 = refusal` <br/> `-1 = don't know`| 
| **Description** |  |


```{r assign4, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_wb','SHARE.sharew4_rel1-1-1_ac',
                         variables=list('ac012_'), missings = TRUE)
SHARE_wb <- opal.execute(o,'SHARE_wb')
```

```{r local4, echo=FALSE}
vbl <- SHARE_wb$ac012_
kable(Categorical_summary(vbl, missing_values = c(-1:-2))[3], caption = label(vbl)) 
kable(Categorical_summary(vbl, missing_values = c(-1:-2))[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = c(-1:-2))[2], caption = "Type of missing")
ggplot(SHARE_wb, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `First tertile into 0`
* `Second tertile into 1`
* `Third tertile into 2`
* `-2 into 997`
* `-1 into 998`

**R script:**

```{r harmo4, echo=TRUE}
SHARE_ds_w4 <- tibble(id=SHARE_wb$id)
SHARE_ds_w4$evaluative_wb <- car::recode(SHARE_wb$ac012_, "0:qq[1]=0; (qq[1]+1):qq[2]=1; (qq[2]+1):10=2; -2=997; -1=998; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript4, echo=FALSE}
vari <- SHARE_ds_w4[[2]]
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w4, aes(x=factor(evaluative_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation


```{r importOPAL4, echo=FALSE}
evaluative_wb <- SHARE_ds_w4
save(evaluative_wb, file = "../RData/w4/evaluative_wb.RData")
```



### Wave 5 

#### Study-specific variable description

| **Name** | `ac012_`|
|-|-|
| **Label** | `how satisfied with life`|
| **Table name** | `sharew5_rel1-0-0_ac` |
| **Scale** |`0 = Completely dissatisfied` <br/> `...` <br/> `10 = completely satisfied`|
| **Missing** |`-2 = refusal` <br/> `-1 = don't know`| 
| **Description** |  |


```{r assign5, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_wb','SHARE.sharew5_rel1-0-0_ac',
                         variables=list('ac012_'), missings = TRUE)
SHARE_wb <- opal.execute(o,'SHARE_wb')
```

```{r local5, echo=FALSE}
vbl <- SHARE_wb$ac012_
kable(Categorical_summary(vbl, missing_values = c(-1:-2))[3], caption = label(vbl)) 
kable(Categorical_summary(vbl, missing_values = c(-1:-2))[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = c(-1:-2))[2], caption = "Type of missing")
ggplot(SHARE_wb, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `First tertile into 0`
* `Second tertile into 1`
* `Third tertile into 2`
* `-2 into 997`
* `-1 into 998`

**R script:**

```{r harmo5, echo=TRUE}
SHARE_ds_w5 <- tibble(id=SHARE_wb$id)
SHARE_ds_w5$evaluative_wb <- car::recode(SHARE_wb$ac012_, "0:qq[1]=0; (qq[1]+1):qq[2]=1; (qq[2]+1):10=2; -2=997; -1=998; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript5, echo=FALSE}
vari <- SHARE_ds_w5[[2]]
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w5, aes(x=factor(evaluative_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation

```{r importOPAL5, echo=FALSE}
evaluative_wb <- SHARE_ds_w5
save(evaluative_wb, file = "../RData/w5/evaluative_wb.RData")
```


# Quality estimation

The tertile from wave 2 were also used in the next waves.

```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
