---
title: "Eudaimonic well-being"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/eudaimonic_wbDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/eudaimonic_wbDS.R')
```

# Data process

## SHARE 

### Wave 1 

#### Study-specific variable description

| **Name** | `q2_h`|
|-|-|
| **Label** | `i feel that my life has meaning`|
| **Table name** | `sharew1_rel2-6-0_dropoff` |
| **Categories** |`1 = often` <br/> `2 = sometimes` <br/> `3 = rarely` <br/> `4 = never`|
| **Missing** |`-5 = not answered`| 
| **Description** |  |

```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_wb','SHARE.sharew1_rel2-6-0_dropoff',
                         variables=list('q2_h'), missings = TRUE)
SHARE_wb <- opal.execute(o,'SHARE_wb')
```

```{r local1, echo=FALSE}
vbl <- SHARE_wb$q2_h
vbl_miss <- c(-5)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = attr(vbl, "spss::shortName")) 
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Type of missing")
ggplot(SHARE_wb, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `1 into 2`
* `2,3 into 1`
* `4 into 0` 
* `-5 into 995`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
SHARE_ds_w1 <- tibble(id=SHARE_wb$id)
SHARE_ds_w1$eudaimonic_wb <- car::recode(SHARE_wb[[2]], "1=2; 2=1; 3=1; 4=0; -5=995; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- SHARE_ds_w1[[2]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SHARE_ds_w1, aes(x=factor(eudaimonic_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation






### Wave 2 

#### Study-specific variable description


| **Name** | `ac021_`|
|-|-|
| **Label** | `casp: life has meaning`|
| **Table name** | `sharew2_rel2-6-0_ac` |
| **Categories** |`1 = often` <br/> `2 = sometimes` <br/> `3 = rarely` <br/> `4 = never`|
| **Missing** |`NA` <br/>`-2 = refusal` <br/> `-1 = don't know`| 
| **Description** |  |

```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_wb','SHARE.sharew2_rel2-6-0_ac',
                         variables=list('ac021_'), missings = TRUE)
SHARE_wb <- opal.execute(o,'SHARE_wb')
```

```{r local2, echo=FALSE}
vbl <- SHARE_wb$ac021_
kable(Categorical_summary(vbl, missing_values = c(-1:-2))[3], caption = attr(vbl, "spss::shortName")) 
kable(Categorical_summary(vbl, missing_values = c(-1:-2))[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = c(-1:-2))[2], caption = "Type of missing")
ggplot(SHARE_wb, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `4 into 0`
* `2,3 into 1`
* `1 into 2`
* `-2 into 997`
* `-1 into 998`

**R script:**

```{r harmo2, echo=TRUE}

SHARE_ds_w2 <- tibble(id=SHARE_wb$id)
SHARE_ds_w2$eudaimonic_wb <- car::recode(SHARE_wb$ac021_, "4=0; 2:3=1; 1=2; -2=997; -1=998; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- SHARE_ds_w2[[2]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SHARE_ds_w2, aes(x=factor(eudaimonic_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation





### Wave 3 

There is no variable.





### Wave 4 

#### Study-specific variable description



| **Name** | `ac021_`|
|-|-|
| **Label** | `life has meaning`|
| **Table name** | `sharew4_rel1-1-1_ac` |
| **Categories** |`1 = often` <br/> `2 = sometimes` <br/> `3 = rarely` <br/> `4 = never`|
| **Missing** |`NA` <br/>`-2 = refusal` <br/> `-1 = don't know`| 
| **Description** |  |


```{r assign4, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_wb','SHARE.sharew4_rel1-1-1_ac',
                         variables=list('ac021_'), missings = TRUE)
SHARE_wb <- opal.execute(o,'SHARE_wb')
```

```{r local4, echo=FALSE}
vbl <- SHARE_wb$ac021_
kable(Categorical_summary(vbl, missing_values = c(-1:-2))[3], caption = attr(vbl, "spss::shortName")) 
kable(Categorical_summary(vbl, missing_values = c(-1:-2))[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = c(-1:-2))[2], caption = "Type of missing")
ggplot(SHARE_wb, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `4 into 0`
* `2,3 into 1`
* `1 into 2`
* `-2 into 997`
* `-1 into 998`

**R script:**

```{r harmo4, echo=TRUE}
SHARE_ds_w4 <- tibble(id=SHARE_wb$id)
SHARE_ds_w4$eudaimonic_wb <- car::recode(SHARE_wb$ac021_, "4=0; 2:3=1; 1=2; -2=997; -1=998; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript4, echo=FALSE}
vari <- SHARE_ds_w4[[2]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SHARE_ds_w4, aes(x=factor(eudaimonic_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation




### Wave 5 

#### Study-specific variable description

| **Name** | `ac021_`|
|-|-|
| **Label** | `how satisfied with life`|
| **Table name** | `sharew5_rel1-0-0_ac` |
| **Categories** |`1 = often` <br/> `2 = sometimes` <br/> `3 = rarely` <br/> `4 = never`|
| **Missing** |`NA` <br/>`-2 = refusal` <br/> `-1 = don't know`| 
| **Description** |  |


```{r assign5, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_wb','SHARE.sharew5_rel1-0-0_ac',
                         variables=list('ac021_'), missings = TRUE)
SHARE_wb <- opal.execute(o,'SHARE_wb')
```

```{r local5, echo=FALSE}
vbl <- SHARE_wb$ac021_
kable(Categorical_summary(vbl, missing_values = c(-1:-2))[3], caption = attr(vbl, "spss::shortName")) 
kable(Categorical_summary(vbl, missing_values = c(-1:-2))[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = c(-1:-2))[2], caption = "Type of missing")
ggplot(SHARE_wb, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `4 into 0`
* `2,3 into 1`
* `1 into 2`
* `-2 into 997`
* `-1 into 998`

**R script:**

```{r harmo5, echo=TRUE}
SHARE_ds_w5 <- tibble(id=SHARE_wb$id)
SHARE_ds_w5$eudaimonic_wb <- car::recode(SHARE_wb$ac021_, "4=0; 2:3=1; 1=2; -2=997; -1=998; NA=999")
```

#### Statistical description of the new harmonised variable
```{r descript5, echo=FALSE}
vari <- SHARE_ds_w5[[2]]
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SHARE_ds_w5, aes(x=factor(eudaimonic_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation





## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.


```{r helpfunctions, echo=F}

source("../../helpfunctions.r")

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names



share.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"))

# Consider only harmonised waves
l.hds <- lapply(share.cw, function(wname) if(exists(paste0("SHARE_ds_",wname[1]))){wname = list(get(paste0("SHARE_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```





# Quality estimation



```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
