---
title: "Number of cigarettes"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/n_cigarettesDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/n_cigarettesDS.R')
```



# Data process

## Poland

### Wave 1

#### Study-specific variable description

| **Name** | `l39` | `l40` |
|-|-|-|
| **Label** | `Do you smoke cigarettes?` | `For current and past smokers: How many cigarettes a day do you smoke now (or you used to smoke, if you stopped)?` |
| **Table name** | `Po_baseline_etic` | `Po_baseline_etic` |
| **Categories:**| `Yes, regularly, at least 1 cigarette a day on average` <br/> `Yes, occasionally, less than 1 cigarette a day` <br/> `No, I smoked in the past but I stopped` <br/> `No, I have never smoked`  | `continuous` |
| **Missings:**| `NA` | `NA` |
| **Description** |  |  |


```{r assign pol w1, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_pol_w1','HAPIEE.Po_baseline_etic', variables=list('l39','l40'), missings = TRUE)
HAPIEE_pol_w1 <- opal.execute(o,'HAPIEE_pol_w1')
```

```{r local pol w1, echo=F}
vbl <- HAPIEE_pol_w1$l39
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HAPIEE_pol_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_pol_w1, aes(x=factor(l39))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+theme(axis.text.x = element_text(angle = 25))

vbl <- HAPIEE_pol_w1$l40
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "Number of cigarettes") 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HAPIEE_pol_w1, aes(l40)) + geom_histogram(stat="count", fill="steelblue") + xlab("Number of cigarettes") + ylab("Frequency") + xlim(-1,125)
```

#### Harmonisation algorithm

To compute `n_cigarettes` from the study-specific variable it has to be recoded as follows:

+ `l40*7&(l39=1,2)`  
+ `NA into 999`

**R script:**

```{r harmo pol w1}
HAPIEE_ds_pol_w1 <- tibble(id=HAPIEE_pol_w1$id)
HAPIEE_ds_pol_w1$n_cigarettes <- rep(999,length(HAPIEE_ds_pol_w1$id))
for(i in 1:length(HAPIEE_ds_pol_w1$id))
{

  if((HAPIEE_pol_w1$l39[i]=='Yes, regularly, at least 1 cigarette a day on average'|HAPIEE_pol_w1$l39[i]=='Yes, occasionally, less than 1 cigarette a day')&is.na(HAPIEE_pol_w1$l39[i])==FALSE&is.na(HAPIEE_pol_w1$l40[i])==FALSE)
    HAPIEE_ds_pol_w1$n_cigarettes[i] <- HAPIEE_pol_w1$l40[i]*7
}
```

#### Statistical description of the new harmonised variable
```{r descript pol w1, echo=F}
vbl <- HAPIEE_ds_pol_w1$n_cigarettes
kable(Continuous_summary(var = vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HAPIEE_ds_pol_w1, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(-4,570) 
```

#### Validation
```{r crosstabulation pol w1, echo=F}
```




### Wave 2

#### Study-specific variable description

| **Name** | `w2l39` | `w2l40` |
|-|-|-|
| **Label** | `Do you smoke cigarettes?` | `For current and past smokers: How many cigarettes a day do you smoke now (or you used to smoke, if you stopped)?` |
| **Table name** | `Po_reexamination_etic` | `Po_reexamination_etic` |
| **Categories:**| `Yes, regularly, at least 1 cigarette a day on average` <br/> `Yes, occasionally, less than 1 cigarette a day` <br/> `No, I smoked in the past but I stopped` <br/> `No, I have never smoked`  | `continuous` |
| **Missings:**| `8` <br/> `9` <br/> `NA` | `NA` |
| **Description** |  |  |


```{r assign pol w2, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_pol_w2','HAPIEE.Po_reexamination_etic', variables=list('w2l39','w2l40'), missings = TRUE)
HAPIEE_pol_w2 <- opal.execute(o,'HAPIEE_pol_w2')
```

```{r local pol w2, echo=F}
vbl <- HAPIEE_pol_w2$w2l39
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = names(HAPIEE_pol_w2)[2])
kable(Categorical_summary(vbl, missing_values = c(8,9))[1], caption = "Category")
ggplot(HAPIEE_pol_w2, aes(x=factor(w2l39))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+theme(axis.text.x = element_text(angle = 25))

vbl <- HAPIEE_pol_w2$w2l40
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "Number of cigarettes") 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HAPIEE_pol_w2, aes(w2l40)) + geom_histogram(stat="count", fill="steelblue") + xlab("Number of cigarettes") + ylab("Frequency") + xlim(0,105)
```

#### Harmonisation algorithm

To compute `n_cigarettes` from the study-specific variable it has to be recoded as follows:

+ `w2l40*7&(l39=1,2)`  
+ `NA into 999`

**R script:**

```{r harmo pol w2}
HAPIEE_ds_pol_w2 <- tibble(id=HAPIEE_pol_w2$id)
HAPIEE_ds_pol_w2$n_cigarettes <- rep(999,length(HAPIEE_ds_pol_w2$id))
for(i in 1:length(HAPIEE_ds_pol_w2$id))
{

  if((HAPIEE_pol_w2$w2l39[i]=='@nyes, regularly, at least one cigarette a day on average'|HAPIEE_pol_w2$w2l39[i]=='@nyes, occasionally, less than one cigarette a day')&is.na(HAPIEE_pol_w2$w2l39[i])==FALSE&is.na(HAPIEE_pol_w2$w2l40[i])==FALSE)
    HAPIEE_ds_pol_w2$n_cigarettes[i] <- HAPIEE_pol_w2$w2l40[i]*7
}
```

#### Statistical description of the new harmonised variable
```{r descript pol w2, echo=F}
vbl <- HAPIEE_ds_pol_w2$n_cigarettes
kable(Continuous_summary(var = vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HAPIEE_ds_pol_w2, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(0,430) 
```

#### Validation
```{r crosstabulation pol w2, echo=F}
```




## Czech Republic

### Wave 1

#### Study-specific variable description

| **Name** | `l39` | `l40` |
|-|-|-|
| **Label** | `Do you smoke cigarettes?` | `For current and past smokers: How many cigarettes a day do you smoke now (or you used to smoke, if you stopped)?` |
| **Table name** | `Cz_baseline_etic` | `Cz_baseline_etic` |
| **Categories:**| `Yes, regularly, at least 1 cigarette a day on average` <br/> `Yes, occasionally, less than 1 cigarette a day` <br/> `No, I smoked in the past but I stopped` <br/> `No, I have never smoked`  | `continuous` |
| **Missings:**| `NA` | `NA` |
| **Description** |  |  |


```{r assign cz w1, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_cz_w1','HAPIEE.Cz_baseline_etic', variables=list('l39','l40'), missings = TRUE)
HAPIEE_cz_w1 <- opal.execute(o,'HAPIEE_cz_w1')
```

```{r local cz w1, echo=F}
vbl <- HAPIEE_cz_w1$l39
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HAPIEE_cz_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_cz_w1, aes(x=factor(l39))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+theme(axis.text.x = element_text(angle = 25))

vbl <- HAPIEE_cz_w1$l40
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "Number of cigarettes") 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HAPIEE_cz_w1, aes(l40)) + geom_histogram(stat="count", fill="steelblue") + xlab("Number of cigarettes") + ylab("Frequency") + xlim(-1,90)
```

#### Harmonisation algorithm

To compute `n_cigarettes` from the study-specific variable it has to be recoded as follows:

+ `l40*7&(l39=1,2)`  
+ `NA into 999`

**R script:**

```{r harmo cz w1}
HAPIEE_ds_cz_w1 <- tibble(id=HAPIEE_cz_w1$id)
HAPIEE_ds_cz_w1$n_cigarettes <- rep(999,length(HAPIEE_ds_cz_w1$id))
for(i in 1:length(HAPIEE_ds_cz_w1$id))
{

  if((HAPIEE_cz_w1$l39[i]=='Yes, regularly, at least 1 cigarette a day on average'|HAPIEE_cz_w1$l39[i]=='Yes, occasionally, less than 1 cigarette a day')&is.na(HAPIEE_cz_w1$l39[i])==FALSE&is.na(HAPIEE_cz_w1$l40[i])==FALSE)
    HAPIEE_ds_cz_w1$n_cigarettes[i] <- HAPIEE_cz_w1$l40[i]*7
}
```

#### Statistical description of the new harmonised variable
```{r descript cz w1, echo=F}
vbl <- HAPIEE_ds_cz_w1$n_cigarettes
kable(Continuous_summary(var = vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HAPIEE_ds_cz_w1, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(0,600) 
```

#### Validation
```{r crosstabulation cz w1, echo=F}
```



### Wave 2

#### Study-specific variable description

| **Name** | `w2l39` | `w2l40` |
|-|-|-|
| **Label** | `Do you smoke cigarettes?` | `For current and past smokers: How many cigarettes a day do you smoke now (or you used to smoke, if you stopped)?` |
| **Table name** | `Cz_reexamination_etic` | `Cz_reexamination_etic` |
| **Categories:**| `1 = Yes, regularly, at least 1 cigarette a day on average` <br/> `2 = Yes, occasionally, less than 1 cigarette a day` <br/> `3 = No, I smoked in the past but I stopped` <br/> `4 = No, I have never smoked`  | `continuous` |
| **Missings:**| `NA` | `NA` |
| **Description** |  |  |


```{r assign cz w2, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_cz_w2','HAPIEE.Cz_reexamination_etic', variables=list('w2l39','w2l40'), missings = TRUE)
HAPIEE_cz_w2 <- opal.execute(o,'HAPIEE_cz_w2')
```

```{r local cz w2, echo=F}
vbl <- HAPIEE_cz_w2$w2l39
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HAPIEE_cz_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_cz_w2, aes(x=factor(w2l39))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+theme(axis.text.x = element_text(angle = 25))

vbl <- HAPIEE_cz_w2$w2l40
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "Number of cigarettes") 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HAPIEE_cz_w2, aes(w2l40)) + geom_histogram(stat="count", fill="steelblue") + xlab("Number of cigarettes") + ylab("Frequency") + xlim(0,105)
```

#### Harmonisation algorithm

To compute `n_cigarettes` from the study-specific variable it has to be recoded as follows:

+ `w2l40*7&(l39=1,2)`  
+ `NA into 999`

**R script:**

```{r harmo cz w2}
HAPIEE_ds_cz_w2 <- tibble(id=HAPIEE_cz_w2$id)
HAPIEE_ds_cz_w2$n_cigarettes <- rep(999,length(HAPIEE_ds_cz_w2$id))
for(i in 1:length(HAPIEE_ds_cz_w2$id))
{

  if((HAPIEE_cz_w2$w2l39[i]=='@nyes, regularly, at least one cigarette a day on average'|HAPIEE_cz_w2$w2l39[i]=='@nyes, occasionally, less than one cigarette a day')&is.na(HAPIEE_cz_w2$w2l39[i])==FALSE&is.na(HAPIEE_cz_w2$w2l40[i])==FALSE)
    HAPIEE_ds_cz_w2$n_cigarettes[i] <- HAPIEE_cz_w2$w2l40[i]*7
}
```

#### Statistical description of the new harmonised variable
```{r descript cz w2, echo=F}
vbl <- HAPIEE_ds_cz_w2$n_cigarettes
kable(Continuous_summary(var = vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HAPIEE_ds_cz_w2, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(0,570) 
```

#### Validation
```{r crosstabulation cz w2, echo=F}
```





## Lithuania

### Wave 1

#### Study-specific variable description

| **Name** | `l39` | `l40` |
|-|-|-|
| **Label** | `Do you smoke cigarettes?` | `For current and past smokers: How many cigarettes a day do you smoke now (or you used to smoke, if you stopped)?` |
| **Table name** | `Li_baseline_etic` | `Li_baseline_etic` |
| **Categories:**| `1 = Yes, regularly, at least 1 cigarette a day on average` <br/> `2 = Yes, occasionally, less than 1 cigarette a day` <br/> `3 = No, I smoked in the past but I stopped` <br/> `4 = No, I have never smoked`  | `continuous` |
| **Missings:**| `.b` <br/>`NA` | `NA` |
| **Description** |  |  |


```{r assign li w1, echo=F}
opal.assign.table.tibble(o, 'HAPIEE_li_w1','HAPIEE.Li_baseline_etic', variables=list('l39','l40'), missings = TRUE)
HAPIEE_li_w1 <- opal.execute(o,'HAPIEE_li_w1')
```

```{r local li w1, echo=F}
vbl <- HAPIEE_li_w1$l39
kable(Categorical_summary(vbl, missing_values = c('.b'))[3], caption = names(HAPIEE_li_w1)[2])
kable(Categorical_summary(vbl, missing_values = c('.b'))[1], caption = "Category")
ggplot(HAPIEE_li_w1, aes(x=factor(l39))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+theme(axis.text.x = element_text(angle = 25))

vbl <- HAPIEE_li_w1$l40
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "Number of cigarettes") 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(HAPIEE_li_w1, aes(l40)) + geom_histogram(stat="count", fill="steelblue") + xlab("Number of cigarettes") + ylab("Frequency") + xlim(0,95)
```

#### Harmonisation algorithm

To compute `n_cigarettes` from the study-specific variable it has to be recoded as follows:

+ `l40*7&(l39=1,2)`  
+ `NA into 999`

**R script:**

```{r harmo li w1}
HAPIEE_ds_li_w1 <- tibble(id=HAPIEE_li_w1$id)
HAPIEE_ds_li_w1$n_cigarettes <- rep(999,length(HAPIEE_ds_li_w1$id))
for(i in 1:length(HAPIEE_ds_li_w1$id))
{

  if((HAPIEE_li_w1$l39[i]=='Yes, regularly, at least 1 cigarette a day on average'|HAPIEE_li_w1$l39[i]=='Yes, occasionally, less than 1 cigarette a day')&is.na(HAPIEE_li_w1$l39[i])==FALSE&is.na(HAPIEE_li_w1$l40[i])==FALSE)
    HAPIEE_ds_li_w1$n_cigarettes[i] <- HAPIEE_li_w1$l40[i]*7
}
```

#### Statistical description of the new harmonised variable
```{r descript li w1, echo=F}
vbl <- HAPIEE_ds_li_w1$n_cigarettes
kable(Continuous_summary(var = vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(HAPIEE_ds_li_w1, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(0,430) 
```

#### Validation
```{r crosstabulation li w1, echo=F}
```




```{r final, echo=F}


l.hds <- list(pol_w1 = HAPIEE_ds_pol_w1, pol_w2 = HAPIEE_ds_pol_w2, cz_w1 = HAPIEE_ds_cz_w1, cz_w2 = HAPIEE_ds_cz_w2, li_w1 = HAPIEE_ds_li_w1)

for(name in names(l.hds)) {
  label(l.hds[[name]][[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
}

```


# Quality estimation
[Comments on the quality of the new harmonised variable.]


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  n_cigarettes <- l.hds[[index]]
  save(n_cigarettes, file = paste0(datafolder,names(l.hds)[index],"/n_cigarettes.RData"))
}

```
<!-- ########################################################## --> 
<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
