---
title: "Alcohol drinking"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/alcoholDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/alcoholDS.R')
```



# Data process


```{r HAPIEE categories}

HAPIEE2_categ <- c('1-2x/wk','5+/wk','3-4x/wk','Every day or almost every day')
HAPIEE1_categ <- c('1-2x/yr','3-5x/yr','6-11x/yr','1/mo','2-3x/mo')
HAPIEE0_categ <- c('Never')

```


## Poland

### Wave 1

#### Study-specific variable description

| **Name** | `d_alcfreq`|
|-|-|
| **Label** | `Drinking freq. from GF`|
| **Table name**  | `Po_baseline_etic`|
| **Categories** | `Never`<br/>`1-2x/wk`<br/>`2-3x/mo`<br/>`1/mo`<br/>`3-5x/yr`<br/>`5+/wk`<br/>`3-4x/wk`<br/>`6-11x/yr`<br/>`1-2x/yr` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign pol_w1, echo=F}

opal.assign.table.tibble(o, 'HAPIEE_pol_w1','HAPIEE.Po_baseline_etic',variables=list('d_alcfreq'), missings = T)
HAPIEE_pol_w1 <- opal.execute(o,'HAPIEE_pol_w1')

```

```{r local pol_w1, echo=F}

vbl <- HAPIEE_pol_w1$d_alcfreq
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HAPIEE_pol_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_pol_w1, aes(x=factor(d_alcfreq))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + theme(axis.text.x = element_text(angle=10))

```


#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable it has to be recoded as follows:

* `d_alcfreq == Never into 0`
* `d_alcfreq == NA into 999`
* `otherwise into 1`

To compute `freq_oh` from the study-specific variable it has to be recoded as follows:

* `d_alcfreq == Never into 0`
* `d_alcfreq == '1-2x/wk','5+/wk','3-4x/wk' into 2`
* `d_alcfreq == '1-2x/yr','3-5x/yr','6-11x/yr','1/mo','2-3x/mo' into 1`
* `NA into 999`

Past drinking cannot be harmonized.

**R script:**

```{r harmo pol_w1}

# Categorical variable harmonization
HAPIEE_ds_pol_w1 <- tibble(id=HAPIEE_pol_w1$id)
HAPIEE_ds_pol_w1$current_oh <- car::recode(HAPIEE_pol_w1$d_alcfreq, "HAPIEE2_categ = 1; HAPIEE1_categ = 1; HAPIEE0_categ = 0; NA = 999")
HAPIEE_ds_pol_w1$freq_oh <- car::recode(HAPIEE_pol_w1$d_alcfreq, "HAPIEE2_categ = 2; HAPIEE1_categ = 1; HAPIEE0_categ = 0; NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript pol_w1, echo=F}

vbl <- HAPIEE_ds_pol_w1$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HAPIEE_ds_pol_w1, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- HAPIEE_ds_pol_w1$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HAPIEE_ds_pol_w1, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

```


#### Validation

```{r crosstabulation pol_w1, echo=F}

```



### Wave 2

#### Study-specific variable description

| **Name** | `d_w2alcfreq`|`w2al9a`|
|-|-|-|
| **Label** | `Drinking freq. from GF (9 categories)`|`Have you always been a non-drinker?`|
| **Table name**  | `Po_reexamination_etic`|`Po_reexamination_etic`|
| **Categories** | `Never`<br/>`1-2x/wk`<br/>`2-3x/mo`<br/>`1/mo`<br/>`3-5x/yr`<br/>`5+/wk`<br/>`3-4x/wk`<br/>`6-11x/yr`<br/>`1-2x/yr`<br/>`Every day or almost every day` |`No`<br/>`Yes`|
| **Missings** | `NA` | `NA` |
| **Description** |  |  |

```{r assign pol_w2, echo=F}

opal.assign.table.tibble(o, 'HAPIEE_pol_w2','HAPIEE.Po_reexamination_etic',variables=list('d_w2alcfreq','w2al9a'), missings = T)
HAPIEE_pol_w2 <- opal.execute(o,'HAPIEE_pol_w2')

```

```{r local pol_w2, echo=F}

vbl <- HAPIEE_pol_w2$d_w2alcfreq
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HAPIEE_pol_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_pol_w2, aes(x=factor(d_w2alcfreq))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + theme(axis.text.x = element_text(angle=10))

vbl <- HAPIEE_pol_w2$w2al9a
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HAPIEE_pol_w2)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_pol_w2, aes(x=factor(w2al9a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + theme(axis.text.x = element_text(angle=10))

```


#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable it has to be recoded as follows:

* `d_w2alcfreq == Never into 0`
* `d_w2alcfreq == NA into 999`
* `otherwise into 1`

To compute `freq_oh` from the study-specific variable it has to be recoded as follows:

* `d_w2alcfreq == Never into 0`
* `d_w2alcfreq == '1-2x/wk','5+/wk','3-4x/wk','Every day or almost every day' into 2`
* `d_w2alcfreq == '1-2x/yr','3-5x/yr','6-11x/yr','1/mo','2-3x/mo' into 1`
* `NA into 999`

To compute `past_oh` from the study-specific variable it has to be recoded as follows:

* `w2al9a == Yes into 0`
* `w2al9a == No into 1`
* `NA into 999`

**R script:**

```{r harmo pol_w2}

# Categorical variable harmonization
HAPIEE_ds_pol_w2 <- tibble(id=HAPIEE_pol_w2$id)
HAPIEE_ds_pol_w2$current_oh <- car::recode(HAPIEE_pol_w2$d_w2alcfreq, "HAPIEE2_categ = 1; HAPIEE1_categ = 1; HAPIEE0_categ = 0; NA = 999")
HAPIEE_ds_pol_w2$freq_oh <- car::recode(HAPIEE_pol_w2$d_w2alcfreq, "HAPIEE2_categ = 2; HAPIEE1_categ = 1; HAPIEE0_categ = 0; NA = 999")
HAPIEE_ds_pol_w2$past_oh <- car::recode(HAPIEE_pol_w2$w2al9a, "'No' = 1; 'Yes' = 0; NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript pol_w2, echo=F}

vbl <- HAPIEE_ds_pol_w2$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HAPIEE_ds_pol_w2, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- HAPIEE_ds_pol_w2$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HAPIEE_ds_pol_w2, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

vbl <- HAPIEE_ds_pol_w2$past_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_past)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HAPIEE_ds_pol_w2, aes(x=factor(past_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_past) + ylab("Frequency")

```


#### Validation

```{r crosstabulation pol_w2, echo=F}

```



## Czech Republic

### Wave 1

#### Study-specific variable description

| **Name** | `d_alcfreq`|
|-|-|
| **Label** | `Drinking freq. from GF`|
| **Table name**  | `Cz_baseline_etic`|
| **Categories** | `Never`<br/>`1-2x/wk`<br/>`2-3x/mo`<br/>`1/mo`<br/>`3-5x/yr`<br/>`5+/wk`<br/>`3-4x/wk`<br/>`6-11x/yr`<br/>`1-2x/yr` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign cz_w1, echo=F}

opal.assign.table.tibble(o, 'HAPIEE_cz_w1','HAPIEE.Cz_baseline_etic',variables=list('d_alcfreq'), missings = T)
HAPIEE_cz_w1 <- opal.execute(o,'HAPIEE_cz_w1')

```

```{r local cz_w1, echo=F}

vbl <- HAPIEE_cz_w1$d_alcfreq
kable(Categorical_summary(vbl, missing_values = c('9'))[3], caption = names(HAPIEE_cz_w1)[2])
kable(Categorical_summary(vbl, missing_values = c('9'))[1], caption = "Category")
ggplot(HAPIEE_cz_w1, aes(x=factor(d_alcfreq))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + theme(axis.text.x = element_text(angle=10))

```


#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable it has to be recoded as follows:

* `d_alcfreq == Never into 0`
* `d_alcfreq == NA into 999`
* `otherwise into 1`

To compute `freq_oh` from the study-specific variable it has to be recoded as follows:

* `d_alcfreq == Never into 0`
* `d_alcfreq == '1-2x/wk','5+/wk','3-4x/wk' into 2`
* `d_alcfreq == '1-2x/yr','3-5x/yr','6-11x/yr','1/mo','2-3x/mo' into 1`
* `NA into 999`

Past drinking cannot be harmonized.

**R script:**

```{r harmo cz_w1}

# Categorical variable harmonization
HAPIEE_ds_cz_w1 <- tibble(id=HAPIEE_cz_w1$id)
HAPIEE_ds_cz_w1$current_oh <- car::recode(HAPIEE_cz_w1$d_alcfreq, "HAPIEE2_categ = 1; HAPIEE1_categ = 1; HAPIEE0_categ = 0; NA = 999")
HAPIEE_ds_cz_w1$freq_oh <- car::recode(HAPIEE_cz_w1$d_alcfreq, "HAPIEE2_categ = 2; HAPIEE1_categ = 1; HAPIEE0_categ = 0; NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript cz_w1, echo=F}

vbl <- HAPIEE_ds_cz_w1$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HAPIEE_ds_cz_w1, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- HAPIEE_ds_cz_w1$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HAPIEE_ds_cz_w1, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

```


#### Validation

```{r crosstabulation cz_w1, echo=F}

```



### Wave 2

#### Study-specific variable description

| **Name** | `d_w2alcfreq`|`w2al9a`|
|-|-|-|
| **Label** | `Drinking freq. from GF (9 categories)`|`Have you always been a non-drinker?`|
| **Table name**  | `Cz_reexamination_etic`|`Cz_reexamination_etic`|
| **Categories** | `Never`<br/>`1-2x/wk`<br/>`2-3x/mo`<br/>`1/mo`<br/>`3-5x/yr`<br/>`5+/wk`<br/>`3-4x/wk`<br/>`6-11x/yr`<br/>`1-2x/yr`<br/>`Every day or almost every day` |`No`<br/>`Yes`|
| **Missings** | `NA` | `NA` |
| **Description** |  |  |

```{r assign cz_w2, echo=F}

opal.assign.table.tibble(o, 'HAPIEE_cz_w2','HAPIEE.Cz_reexamination_etic',variables=list('d_w2alcfreq','w2al9a'), missings = T)
HAPIEE_cz_w2 <- opal.execute(o,'HAPIEE_cz_w2')

```

```{r local cz_w2, echo=F}

vbl <- HAPIEE_cz_w2$d_w2alcfreq
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HAPIEE_cz_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_cz_w2, aes(x=factor(d_w2alcfreq))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + theme(axis.text.x = element_text(angle=10))

vbl <- HAPIEE_cz_w2$w2al9a
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HAPIEE_cz_w2)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_cz_w2, aes(x=factor(w2al9a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + theme(axis.text.x = element_text(angle=10))

```


#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable it has to be recoded as follows:

* `d_w2alcfreq == Never into 0`
* `d_w2alcfreq == NA into 999`
* `otherwise into 1`

To compute `freq_oh` from the study-specific variable it has to be recoded as follows:

* `d_w2alcfreq == Never into 0`
* `d_w2alcfreq == '1-2x/wk','5+/wk','3-4x/wk','Every day or almost every day' into 2`
* `d_w2alcfreq == '1-2x/yr','3-5x/yr','6-11x/yr','1/mo','2-3x/mo' into 1`
* `NA into 999`

To compute `past_oh` from the study-specific variable it has to be recoded as follows:

* `w2al9a == Yes into 0`
* `w2al9a == No into 1`
* `NA into 999`

**R script:**

```{r harmo cz_w2}

# Categorical variable harmonization
HAPIEE_ds_cz_w2 <- tibble(id=HAPIEE_cz_w2$id)
HAPIEE_ds_cz_w2$current_oh <- car::recode(HAPIEE_cz_w2$d_w2alcfreq, "HAPIEE2_categ = 1; HAPIEE1_categ = 1; HAPIEE0_categ = 0; NA = 999")
HAPIEE_ds_cz_w2$freq_oh <- car::recode(HAPIEE_cz_w2$d_w2alcfreq, "HAPIEE2_categ = 2; HAPIEE1_categ = 1; HAPIEE0_categ = 0; NA = 999")
HAPIEE_ds_cz_w2$past_oh <- car::recode(HAPIEE_cz_w2$w2al9a, "'No' = 1; 'Yes' = 0; NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript cz_w2, echo=F}

vbl <- HAPIEE_ds_cz_w2$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HAPIEE_ds_cz_w2, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- HAPIEE_ds_cz_w2$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HAPIEE_ds_cz_w2, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

vbl <- HAPIEE_ds_cz_w2$past_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_past)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HAPIEE_ds_cz_w2, aes(x=factor(past_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_past) + ylab("Frequency")

```


#### Validation

```{r crosstabulation cz_w2, echo=F}

```





## Lithuania


#### Study-specific variable description

| **Name** | `d_alcfreq`|`w2al9a`|
|-|-|-|
| **Label** | `Drinking freq. from GF`|`Have you always been a non-drinker?`|
| **Table name**  | `Li_baseline_etic`|`Li_baseline_etic`|
| **Categories** | `Never`<br/>`1-2x/wk`<br/>`2-3x/mo`<br/>`1/mo`<br/>`3-5x/yr`<br/>`5+/wk`<br/>`3-4x/wk`<br/>`6-11x/yr`<br/>`1-2x/yr` |`No`<br/>`Yes`|
| **Missings** | `NA` | `NA` |
| **Description** |  |  |

```{r assign li_w1, echo=F}

opal.assign.table.tibble(o, 'HAPIEE_li_w1','HAPIEE.Li_baseline_etic',variables=list('d_alcfreq','w2al9a'), missings = T)
HAPIEE_li_w1 <- opal.execute(o,'HAPIEE_li_w1')

```

```{r local li_w1, echo=F}

vbl <- HAPIEE_li_w1$d_alcfreq
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HAPIEE_li_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_li_w1, aes(x=factor(d_alcfreq))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + theme(axis.text.x = element_text(angle=10))

vbl <- HAPIEE_li_w1$w2al9a
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(HAPIEE_li_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(HAPIEE_li_w1, aes(x=factor(w2al9a))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + theme(axis.text.x = element_text(angle=10))

```


#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable it has to be recoded as follows:

* `d_alcfreq == Never into 0`
* `d_alcfreq == NA into 999`
* `otherwise into 1`

To compute `freq_oh` from the study-specific variable it has to be recoded as follows:

* `d_alcfreq == Never into 0`
* `d_alcfreq == '1-2x/wk','5+/wk','3-4x/wk' into 2`
* `d_alcfreq == '1-2x/yr','3-5x/yr','6-11x/yr','1/mo','2-3x/mo' into 1`
* `NA into 999`

To compute `past_oh` from the study-specific variable it has to be recoded as follows:

* `w2al9a == Yes into 0`
* `w2al9a == No into 1`
* `NA into 999`

**R script:**

```{r harmo li_w1}

# Categorical variable harmonization
HAPIEE_ds_li_w1 <- tibble(id=HAPIEE_li_w1$id)
HAPIEE_ds_li_w1$current_oh <- car::recode(HAPIEE_li_w1$d_alcfreq, "HAPIEE2_categ = 1; HAPIEE1_categ = 1; HAPIEE0_categ = 0; NA = 999")
HAPIEE_ds_li_w1$freq_oh <- car::recode(HAPIEE_li_w1$d_alcfreq, "HAPIEE2_categ = 2; HAPIEE1_categ = 1; HAPIEE0_categ = 0; NA = 999")
HAPIEE_ds_li_w1$past_oh <- car::recode(HAPIEE_li_w1$w2al9a, "'No' = 1; 'Yes' = 0; NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript li_w1, echo=F}

vbl <- HAPIEE_ds_li_w1$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HAPIEE_ds_li_w1, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- HAPIEE_ds_li_w1$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HAPIEE_ds_li_w1, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

vbl <- HAPIEE_ds_li_w1$past_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_past)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(HAPIEE_ds_li_w1, aes(x=factor(past_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_past) + ylab("Frequency")

```


#### Validation

```{r crosstabulation li_w1, echo=F}

```





```{r final, echo=F}

lb.hds <- list(pol_w1 = HAPIEE_ds_pol_w1, cz_w1 = HAPIEE_ds_cz_w1)
lf.hds <- list(pol_w2 = HAPIEE_ds_pol_w2, cz_w2 = HAPIEE_ds_cz_w2, li_w1 = HAPIEE_ds_li_w1)

for(name in names(lb.hds)) {
  aux_object <- lb.hds[[name]]
  label(lb.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label_curr # Text value assigned at the DS description, at the top
  lb.hds[[name]][[2]] <- labelled(lb.hds[[name]][[2]], labels = cat_label)
  label(lb.hds[[name]][[3]]) <- label(aux_object[[3]]) <- ds_label_freq # Text value assigned at the DS description, at the top
  lb.hds[[name]][[3]] <- labelled(lb.hds[[name]][[3]], labels = freq_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  aux_object[[3]] <- car::recode(aux_object[[3]], "miss_values_vector=NA")
  aux_object[[3]] <- labelled(aux_object[[3]], labels = freq_label[1:3])
  m_name <- paste0("HAPIEE_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}


for(name in names(lf.hds)) {
  aux_object <- lf.hds[[name]]
  label(lf.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label_curr # Text value assigned at the DS description, at the top
  lf.hds[[name]][[2]] <- labelled(lf.hds[[name]][[2]], labels = cat_label)
  label(lf.hds[[name]][[3]]) <- label(aux_object[[3]]) <- ds_label_freq # Text value assigned at the DS description, at the top
  lf.hds[[name]][[3]] <- labelled(lf.hds[[name]][[3]], labels = freq_label)
  label(lf.hds[[name]][[4]]) <- label(aux_object[[4]]) <- ds_label_past # Text value assigned at the DS description, at the top
  lf.hds[[name]][[4]] <- labelled(lf.hds[[name]][[4]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  aux_object[[3]] <- car::recode(aux_object[[3]], "miss_values_vector=NA")
  aux_object[[3]] <- labelled(aux_object[[3]], labels = freq_label[1:3])
  aux_object[[4]] <- car::recode(aux_object[[4]], "miss_values_vector=NA")
  aux_object[[4]] <- labelled(aux_object[[4]], labels = cat_label[1:2])
  m_name <- paste0("HAPIEE_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

l.hds <- c(lb.hds,lf.hds)
ln.hds <- c("pol_w1","pol_w2","cz_w1","cz_w2","li_w1")

```


## Descriptive statistics of the harmonised variable `current_oh` accross populations and waves

Percentages of categories in each harmonised variable by cohort:

**R script:**

```{r summ current}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(ln.hds)){
  t.hds[2+i] <- frq(l.hds[[ln.hds[i]]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size",sapply(ln.hds,function(wave) length(l.hds[[wave]][[1]])))
names(t.hds)<-c("val", "label", "Poland_W1", "Poland_W2","Czech_Republic_W1","Czech_Republic_W2","Lithuania_W1")
kable(t.hds)
  
```


## Descriptive statistics of the harmonised variable `freq_oh` accross populations and waves

Percentages of categories in each harmonised variable by cohort:

**R script:**

```{r summ freq}

t.hds <- frq(l.hds[[1]][3])[[1]][,c(1,2)] 
for (i in seq_along(ln.hds)){
  t.hds[2+i] <- frq(l.hds[[ln.hds[i]]][3])[[1]][,4] 
}
t.hds[14,] <- c("n", "sample size",sapply(ln.hds,function(wave) length(l.hds[[wave]][[1]])))
names(t.hds)<-c("val", "label", "Poland_W1", "Poland_W2","Czech_Republic_W1","Czech_Republic_W2","Lithuania_W1")
kable(t.hds)
  
```


## Descriptive statistics of the harmonised variable `past_oh` accross populations and waves

Percentages of categories in each harmonised variable by cohort:

**R script:**

```{r summ past}

t.hds <- frq(lf.hds[[1]][4])[[1]][,c(1,2)] 
for (i in seq_along(lf.hds)){
  t.hds[2+i] <- frq(lf.hds[[i]][4])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size",sapply(lf.hds,function(wave) length(wave[[1]])))
names(t.hds)<-c("val", "label", "Poland_W2","Czech_Republic_W2","Lithuania_W1")
kable(t.hds)
  
```



# Quality estimation



<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(l.hds)){
  alcohol <- l.hds[[index]]
  save(alcohol, file = paste0(datafolder,names(l.hds)[index],"/alcohol.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





