---
title: "Eye sight - Far vision"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 


```{r load, echo=F}
# Loading local datasets of ELSA and domain health status:
load("ELSA_w1.rdata")
load("ELSA_w2.rdata")
load("ELSA_w3.rdata")
load("ELSA_w4.rdata")
load("ELSA_w5.rdata")
load("ELSA_w6.rdata")
load("ELSA_w7.rdata")
```


# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `eye_far`
* Variable label: `Eyesight - far vision`
* Variable description: `Difficulties for far vision.`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## England

### Wave 1 

#### Study-specific variable description




| **Name** | `hefrnd`| `heeye`|
|-|-|-|
| **Label** | `How good is your eyesight for seeing things at a distance, like recognising a friend across the street (using glasses or corrective lens as usual)? Would you say it is?` | `Is your eyesight (using glasses or corrective lens as usual) ...?` |
| **Table name** | `wave_1_core_data_v3` |`wave_1_core_data_v3` |
| **Categories** | `1 = ...excellent; 2 = very good; 3 = good; 4 = fair; 5 = or, poor?`|`1 = ...excellent; 2 = very good; 3 = good; 4 = fair; 5 = or, poor?; 6 = SPONTANEOUS: Registered or legally blind`|
| **Missings** |`-9 = Refusal; -8 = Don't Know; -1 = Not applicable` |`-9 = Refusal; -8 = Don't Know` |
| **Description** |  |  |


```{r local w1, echo=F}
ELSA_w1_eye_far <- ELSA_w1
vari <- ELSA_w1_eye_far$hefrnd
kable(Categorical_summary(vari, missing_values = c(-1,-8,-9))[3], caption = "hefrnd")
kable(Categorical_summary(vari, missing_values = c(-1,-8,-9))[1], caption = "Category")
ggplot(ELSA_w1_eye_far, aes(x=factor(hefrnd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Far Vision") + ylab("Frequency")

vari <- ELSA_w1_eye_far$heeye
kable(Categorical_summary(vari, missing_values = c(-8,-9))[3], caption = "heeye")
kable(Categorical_summary(vari, missing_values = c(-8,-9))[1], caption = "Category")
ggplot(ELSA_w1_eye_far, aes(x=factor(heeye))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Far Vision") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `hefrnd == 1, 2, 3 into 1` 
* `hefrnd == 4, 5 into 0` 
* `hefrnd == -9 Refusal into 997` 
* `hefrnd == -8 Don't know into 998` 
* `hefrnd == -1 Item not applicable into 996`
* `heeye == 6 into 0`

**R script:**
```{r harmo w1}
ELSA_ds_w1 <- tibble(id=ELSA_w1_eye_far$id)
ELSA_ds_w1$eye_far <- car::recode(ELSA_w1_eye_far$hefrnd, "1 = '1';2 = '1';3 = '1';4 = '0'; 5 = '0';-9 = '997';-8 = '998';-1 = '996' ")
ELSA_ds_w1$eye_far[!is.na(ELSA_w1_eye_far$heeye) & ELSA_w1_eye_far$heeye == 6] <- 0
ELSA_ds_w1$eye_far <- labelled(ELSA_ds_w1$eye_far, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vari <- ELSA_ds_w1$eye_far
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "eye_far")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w1, aes(x=factor(eye_far))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Far Vision") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(ELSA_ds_w1$eye_far)
X<-table(ELSA_w1_eye_far$hefrnd)
BeforeH <- c(sum(sum(X[7:8]),sum(!is.na(ELSA_w1_eye_far$heeye) & ELSA_w1_eye_far$heeye == 6)),sum(X[4:6]),sum(X[3],-sum(!is.na(ELSA_w1_eye_far$heeye) & ELSA_w1_eye_far$heeye == 6)),X[c(1,2)])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4,5,heeye==6->0","1,2,3->1","-1->996","-9->997","-8->998") 
kable(C)
```





```{r importOPAL_w1, echo=F}

label(ELSA_ds_w1$eye_far) <- "Difficulties for far vision"
#opal.assign.data(o, 'ELSA_ds_w1', ELSA_ds_w1)
#opal.symbol_import(o,'ELSA_ds_w1', project='_Athlos_Harm_Dataset')
eye_far <- ELSA_ds_w1
save(eye_far, file = "../RData/w1/eye_far.RData")

ELSA_m_ds_w1 <- ELSA_ds_w1
ELSA_m_ds_w1$eye_far <- car::recode(ELSA_m_ds_w1$eye_far, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w1', ELSA_m_ds_w1)
#opal.symbol_import(o,'ELSA_m_ds_w1', project='_Athlos_Harm_Dataset')
```


### Wave 2 

#### Study-specific variable description




| **Name** | `Hefrnd`|`Heeye`|
|-|-|-|
| **Label** | `Eyesight for recognition of friend across street?` | `Self-reported eyesight (while using lenses, if appropriate)?` | 
| **Table name** | `wave_2_core_data_v4` |`wave_2_core_data_v4` |
| **Categories** | `1 = ...excellent; 2 = very good; 3 = good; 4 = fair; 5 = or, poor?`| `1 = ...excellent; 2 = very good; 3 = good; 4 = fair; 5 = or, poor?; 6 = SPONTANEOUS: Registered or legally blind`|
| **Missings** |`-9 = Refusal; -8 = Don't Know; -1 = Not applicable` |`-9 = Refusal; -8 = Don't Know` |
| **Description** |  |  |



```{r local w2, echo=F}
ELSA_w2_eye_far <- ELSA_w2
vari <- ELSA_w2_eye_far$Hefrnd
kable(Categorical_summary(vari, missing_values = c(-1,-8,-9))[3], caption = "Hefrnd")
kable(Categorical_summary(vari, missing_values = c(-1,-8,-9))[1], caption = "Category")
ggplot(ELSA_w2_eye_far, aes(x=factor(Hefrnd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Far Vision") + ylab("Frequency")

vari <- ELSA_w2_eye_far$Heeye
kable(Categorical_summary(vari, missing_values = c(-8,-9))[3], caption = "Heeye")
kable(Categorical_summary(vari, missing_values = c(-8,-9))[1], caption = "Category")
ggplot(ELSA_w2_eye_far, aes(x=factor(Heeye))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Far Vision") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `hefrnd == 1, 2, 3 into 1` 
* `hefrnd == 4, 5 into 0` 
* `hefrnd == -9 Refusal into 997` 
* `hefrnd == -8 Don't know into 998`
* `hefrnd == -1 Item not applicable into 996`
* `heeye == 6 into 0`

**R script:**
```{r harmo w2}
ELSA_ds_w2 <- tibble(id=ELSA_w2_eye_far$id)
ELSA_ds_w2$eye_far <- car::recode(ELSA_w2_eye_far$Hefrnd, "1 = '1';2 = '1';3 = '1';4 = '0'; 5 = '0';-9 = '997';-8 = '998';-1 = '996' ")
ELSA_ds_w2$eye_far[!is.na(ELSA_w2_eye_far$Heeye) & ELSA_w2_eye_far$Heeye==6] <- 0
ELSA_ds_w2$eye_far <- labelled(ELSA_ds_w2$eye_far, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vari <- ELSA_ds_w2$eye_far
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "eye_far")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w2, aes(x=factor(eye_far))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Far Vision") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
AfterH <- table(ELSA_ds_w2$eye_far)
X<-table(ELSA_w2_eye_far$Hefrnd)
BeforeH <- c(sum(sum(X[7:8]),sum(!is.na(ELSA_w2_eye_far$Heeye) & ELSA_w2_eye_far$Heeye==6)),sum(X[4:6]),sum(X[3],-sum(!is.na(ELSA_w2_eye_far$Heeye) & ELSA_w2_eye_far$Heeye==6)),X[c(1,2)])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4,5,heeye==6->0","1,2,3->1","-1->996","-9->997","-8->998") 
kable(C)
```





```{r importOPAL_w2, echo=F}

label(ELSA_ds_w2$eye_far) <- "Difficulties for far vision"
#opal.assign.data(o, 'ELSA_ds_w2', ELSA_ds_w2)
#opal.symbol_import(o,'ELSA_ds_w2', project='_Athlos_Harm_Dataset')
eye_far <- ELSA_ds_w2
save(eye_far, file = "../RData/w2/eye_far.RData")

ELSA_m_ds_w2 <- ELSA_ds_w2
ELSA_m_ds_w2$eye_far <- car::recode(ELSA_m_ds_w2$eye_far, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w2', ELSA_m_ds_w2)
#opal.symbol_import(o,'ELSA_m_ds_w2', project='_Athlos_Harm_Dataset')
```





### Wave 3 

#### Study-specific variable description




| **Name** | `hefrnd`|`heeye`|
|-|-|-|
| **Label** | `Eyesight for recognition of friend across street?` | `Self-reported eyesight (while using lenses, if appropriate)?` |
| **Table name** | `wave_3_elsa_data_v4` | `wave_3_elsa_data_v4` |
| **Categories** | `1 = ...excellent; 2 = very good; 3 = good; 4 = fair; 5 = or, poor?`|`1 = ...excellent; 2 = very good; 3 = good; 4 = fair; 5 = or, poor?; 6 = SPONTANEOUS: Registered or legally blind`|
| **Missings** |`-9 = Refusal; -8 = Don't Know; -1 = Not applicable` |`-9 = Refusal; -8 = Don't Know` |
| **Description** |  |  |




```{r local w3, echo=F}
ELSA_w3_eye_far <- ELSA_w3
vari <- ELSA_w3_eye_far$hefrnd
kable(Categorical_summary(vari, missing_values = c(-1,-8,-9))[3], caption = "hefrnd")
kable(Categorical_summary(vari, missing_values = c(-1,-8,-9))[1], caption = "Category")
ggplot(ELSA_w3_eye_far, aes(x=factor(hefrnd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Far Vision") + ylab("Frequency")

vari <- ELSA_w3_eye_far$heeye
kable(Categorical_summary(vari, missing_values = c(-8,-9))[3], caption = "heeye")
kable(Categorical_summary(vari, missing_values = c(-8,-9))[1], caption = "Category")
ggplot(ELSA_w3_eye_far, aes(x=factor(heeye))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Far Vision") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `hefrnd == 1, 2, 3 into 1` 
* `hefrnd == 4, 5 into 0` 
* `hefrnd == -9 Refusal into 997` 
* `hefrnd == -8 Don't know into 998` 
* `hefrnd == -1 Item not applicable into 996`
* `heeye == 6 into 0`

**R script:**
```{r harmo w3}
ELSA_ds_w3 <- tibble(id=ELSA_w3_eye_far$id)
ELSA_ds_w3$eye_far <- car::recode(ELSA_w3_eye_far$hefrnd, "1 = '1';2 = '1';3 = '1';4 = '0'; 5 = '0';-9 = '997';-8 = '998';-1 = '996' ")

ELSA_ds_w3$eye_far[!is.na(ELSA_w3_eye_far$heeye) & ELSA_w3_eye_far$heeye==6] <- 0

ELSA_ds_w3$eye_far <- labelled(ELSA_ds_w3$eye_far, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}
vari <- ELSA_ds_w3$eye_far
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "eye_far")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w3, aes(x=factor(eye_far))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Far Vision") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=F}
AfterH <- table(ELSA_ds_w3$eye_far)
X<-table(ELSA_w3_eye_far$hefrnd)
BeforeH <- c(sum(sum(!is.na(ELSA_w3_eye_far$heeye) & ELSA_w3_eye_far$heeye==6),sum(X[7:8])),sum(X[4:6]),sum(X[3],-sum(!is.na(ELSA_w3_eye_far$heeye) & ELSA_w3_eye_far$heeye==6)),X[c(1,2)])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4,5,heeye==6->0","1,2,3->1","-1->996","-9->997","-8->998") 
kable(C)
```





```{r importOPAL_w3, echo=F}

label(ELSA_ds_w3$eye_far) <- "Difficulties for far vision"
#opal.assign.data(o, 'ELSA_ds_w3', ELSA_ds_w3)
#opal.symbol_import(o,'ELSA_ds_w3', project='_Athlos_Harm_Dataset')
eye_far <- ELSA_ds_w3
save(eye_far, file = "../RData/w3/eye_far.RData")

ELSA_m_ds_w3 <- ELSA_ds_w3
ELSA_m_ds_w3$eye_far <- car::recode(ELSA_m_ds_w3$eye_far, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w3', ELSA_m_ds_w3)
#opal.symbol_import(o,'ELSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```




### Wave 4 

#### Study-specific variable description




| **Name** | `hefrnd`|`heeye`|
|-|-|-|
| **Label** | `Eyesight for recognition of friend across street?` | `Self-reported eyesight (while using lenses, if appropriate)?` |
| **Table name** | `wave_4_elsa_data_v3` | `wave_4_elsa_data_v3` |
| **Categories** | `1 = ...excellent; 2 = very good; 3 = good; 4 = fair; 5 = or, poor?`| `1 = ...excellent; 2 = very good; 3 = good; 4 = fair; 5 = or, poor?; 6 = SPONTANEOUS: Registered or legally blind`|
| **Missings** |`-9 = Refusal; -8 = Don't Know; -1 = Not applicable` |`-9 = Refusal; -8 = Don't Know` |
| **Description** |  |  |



```{r local w4, echo=F}
ELSA_w4_eye_far <- ELSA_w4
vari <- ELSA_w4_eye_far$hefrnd
kable(Categorical_summary(vari, missing_values = c(-1,-8,-9))[3], caption = "hefrnd")
kable(Categorical_summary(vari, missing_values = c(-1,-8,-9))[1], caption = "Category")
ggplot(ELSA_w4_eye_far, aes(x=factor(hefrnd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Far Vision") + ylab("Frequency")

vari <- ELSA_w4_eye_far$heeye
kable(Categorical_summary(vari, missing_values = c(-8,-9))[3], caption = "heeye")
kable(Categorical_summary(vari, missing_values = c(-8,-9))[1], caption = "Category")
ggplot(ELSA_w4_eye_far, aes(x=factor(heeye))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Far Vision") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `hefrnd == 1, 2, 3 into 1` 
* `hefrnd == 4, 5 into 0` 
* `hefrnd == -9 Refusal into 997` 
* `hefrnd == -8 Don't know into 998` 
* `hefrnd == -1 Item not applicable into 996`
* `heeye == 6 into 0`

**R script:**
```{r harmo w4}
ELSA_ds_w4 <- tibble(id=ELSA_w4_eye_far$id)
ELSA_ds_w4$eye_far <- car::recode(ELSA_w4_eye_far$hefrnd, "1 = '1';2 = '1';3 = '1';4 = '0'; 5 = '0';-9 = '997';-8 = '998';-1 = '996' ")

ELSA_ds_w4$eye_far[!is.na(ELSA_w4_eye_far$heeye) & ELSA_w4_eye_far$heeye==6] <- 0

ELSA_ds_w4$eye_far <- labelled(ELSA_ds_w4$eye_far, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w4, echo=F}
vari <- ELSA_ds_w4$eye_far
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "eye_far")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w4, aes(x=factor(eye_far))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Far Vision") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w4, echo=F}
AfterH <- table(ELSA_ds_w4$eye_far)
X<-table(ELSA_w4_eye_far$hefrnd)
BeforeH <- c(sum(sum(!is.na(ELSA_w4_eye_far$heeye) & ELSA_w4_eye_far$heeye==6),sum(X[7:8])),sum(X[4:6]),sum(X[3],-sum(!is.na(ELSA_w4_eye_far$heeye) & ELSA_w4_eye_far$heeye==6)),X[c(1,2)])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4,5,heeye==6->0","1,2,3->1","-1->996","-9->997","-8->998") 
kable(C)
```






```{r importOPAL_w4, echo=F}

label(ELSA_ds_w4$eye_far) <- "Difficulties for far vision"
#opal.assign.data(o, 'ELSA_ds_w4', ELSA_ds_w4)
#opal.symbol_import(o,'ELSA_ds_w4', project='_Athlos_Harm_Dataset')
eye_far <- ELSA_ds_w4
save(eye_far, file = "../RData/w4/eye_far.RData")

ELSA_m_ds_w4 <- ELSA_ds_w4
ELSA_m_ds_w4$eye_far <- car::recode(ELSA_m_ds_w4$eye_far, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w4', ELSA_m_ds_w4)
#opal.symbol_import(o,'ELSA_m_ds_w4', project='_Athlos_Harm_Dataset')
```




### Wave 5 

#### Study-specific variable description




| **Name** | `hefrnd`|`heeye`|
|-|-|-|
| **Label** | `Eyesight for recognition of friend across street?` |`Self-reported eyesight (while using lenses, if appropriate)?` |
| **Table name** | `wave_5_elsa_data_v4` |`wave_5_elsa_data_v4` |
| **Categories** | `1 = ...excellent; 2 = very good; 3 = good; 4 = fair; 5 = or, poor?`| `1 = ...excellent; 2 = very good; 3 = good; 4 = fair; 5 = or, poor?; 6 = SPONTANEOUS: Registered or legally blind`|
| **Missings** |`-9 = Refusal; -8 = Don't Know; -1 = Not applicable` |`-9 = Refusal; -8 = Don't Know` |
| **Description** |  |  |




```{r local w5, echo=F}
ELSA_w5_eye_far <- ELSA_w5
vari <- ELSA_w5_eye_far$hefrnd
kable(Categorical_summary(vari, missing_values = c(-1,-8,-9))[3], caption = "hefrnd")
kable(Categorical_summary(vari, missing_values = c(-1,-8,-9))[1], caption = "Category")
ggplot(ELSA_w5_eye_far, aes(x=factor(hefrnd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Far Vision") + ylab("Frequency")

vari <- ELSA_w5_eye_far$heeye
kable(Categorical_summary(vari, missing_values = c(-8,-9))[3], caption = "heeye")
kable(Categorical_summary(vari, missing_values = c(-8,-9))[1], caption = "Category")
ggplot(ELSA_w5_eye_far, aes(x=factor(heeye))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Far Vision") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `hefrnd == 1, 2, 3 into 1` 
* `hefrnd == 4, 5 into 0` 
* `hefrnd == -9 Refusal into 997` 
* `hefrnd == -8 Don't know into 998` 
* `hefrnd == -1 Item not applicable into 996`
* `heeye == 6 into 0`

**R script:**
```{r harmo w5}
ELSA_ds_w5 <- tibble(id=ELSA_w5_eye_far$id)
ELSA_ds_w5$eye_far <- car::recode(ELSA_w5_eye_far$hefrnd, "1 = '1';2 = '1';3 = '1';4 = '0'; 5 = '0';-9 = '997';-8 = '998';-1 = '996' ")

ELSA_ds_w5$eye_far[!is.na(ELSA_w5_eye_far$heeye) & ELSA_w5_eye_far$heeye==6] <- 0


ELSA_ds_w5$eye_far <- labelled(ELSA_ds_w5$eye_far, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w5, echo=F}
vari <- ELSA_ds_w5$eye_far
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "eye_far")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w5, aes(x=factor(eye_far))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Far Vision") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w5, echo=F}
AfterH <- table(ELSA_ds_w5$eye_far)
X<-table(ELSA_w5_eye_far$hefrnd)
BeforeH <-c(sum(sum(!is.na(ELSA_w5_eye_far$heeye) & ELSA_w5_eye_far$heeye==6),sum(X[7:8])),sum(X[4:6]),sum(X[3],-sum(!is.na(ELSA_w5_eye_far$heeye) & ELSA_w5_eye_far$heeye==6)),X[c(1,2)])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4,5,heeye==6->0","1,2,3->1","-1->996","-9->997","-8->998") 
kable(C)
```





```{r importOPAL_w5, echo=F}

label(ELSA_ds_w5$eye_far) <- "Difficulties for far vision"
#opal.assign.data(o, 'ELSA_ds_w5', ELSA_ds_w5)
#opal.symbol_import(o,'ELSA_ds_w5', project='_Athlos_Harm_Dataset')
eye_far <- ELSA_ds_w5
save(eye_far, file = "../RData/w5/eye_far.RData")

ELSA_m_ds_w5 <- ELSA_ds_w5
ELSA_m_ds_w5$eye_far <- car::recode(ELSA_m_ds_w5$eye_far, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w5', ELSA_m_ds_w5)
#opal.symbol_import(o,'ELSA_m_ds_w5', project='_Athlos_Harm_Dataset')
```





### Wave 6 

#### Study-specific variable description




| **Name** | `HeFrnd`| `HeEye`|
|-|-|-|
| **Label** | `Eyesight for recognition of friend across street?` |`Self-reported eyesight (while using lenses, if appropriate)?` |
| **Table name** | `wave_6_elsa_data_v2` | `wave_6_elsa_data_v2` |
| **Categories** | `1 = ...excellent; 2 = very good; 3 = good; 4 = fair; 5 = or, poor?`|`1 = ...excellent; 2 = very good; 3 = good; 4 = fair; 5 = or, poor?; 6 = SPONTANEOUS: Registered or legally blind`|
| **Missings** |`-9 = Refusal; -8 = Don't Know; -1 = Not applicable` |`-9 = Refusal; -8 = Don't Know` |
| **Description** |  |  |




```{r local w6, echo=F}
ELSA_w6_eye_far <- ELSA_w6
vari <- ELSA_w6_eye_far$Hefrnd
kable(Categorical_summary(vari, missing_values = c(-1,-8,-9))[3], caption = "Hefrnd")
kable(Categorical_summary(vari, missing_values = c(-1,-8,-9))[1], caption = "Category")
ggplot(ELSA_w6_eye_far, aes(x=factor(Hefrnd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Far Vision") + ylab("Frequency")

vari <- ELSA_w6_eye_far$HeEye
kable(Categorical_summary(vari, missing_values = c(-8,-9))[3], caption = "HeEye")
kable(Categorical_summary(vari, missing_values = c(-8,-9))[1], caption = "Category")
ggplot(ELSA_w6_eye_far, aes(x=factor(HeEye))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Far Vision") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `hefrnd == 1, 2, 3 into 1` 
* `hefrnd == 4, 5 into 0` 
* `hefrnd == -9 Refusal into 997` 
* `hefrnd == -8 Don't know into 998` 
* `hefrnd == -1 Item not applicable into 996`
* `heeye == 6 into 0`

**R script:**
```{r harmo w6}
ELSA_ds_w6 <- tibble(id=ELSA_w6_eye_far$id)
ELSA_ds_w6$eye_far <- car::recode(ELSA_w6_eye_far$Hefrnd, "1 = '1';2 = '1';3 = '1';4 = '0'; 5 = '0';-9 = '997';-8 = '998';-1 = '996' ")

ELSA_ds_w6$eye_far[!is.na(ELSA_w6_eye_far$HeEye) & ELSA_w6_eye_far$HeEye==6] <- 0


ELSA_ds_w6$eye_far <- labelled(ELSA_ds_w6$eye_far, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w6, echo=F}
vari <- ELSA_ds_w6$eye_far
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "eye_far")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w6, aes(x=factor(eye_far))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Far Vision") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w6, echo=F}
AfterH <- table(ELSA_ds_w6$eye_far)
X<-table(ELSA_w6_eye_far$Hefrnd)
BeforeH <- c(sum(sum(!is.na(ELSA_w6_eye_far$HeEye) & ELSA_w6_eye_far$HeEye==6),sum(X[7:8])),sum(X[4:6]),sum(X[3],-sum(!is.na(ELSA_w6_eye_far$HeEye) & ELSA_w6_eye_far$HeEye==6)),X[c(1,2)])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4,5,heeye==6->0","1,2,3->1","-1->996","-9->997","-8->998") 
kable(C)
```





```{r importOPAL_w6, echo=F}

label(ELSA_ds_w6$eye_far) <- "Difficulties for far vision"
#opal.assign.data(o, 'ELSA_ds_w6', ELSA_ds_w6)
#opal.symbol_import(o,'ELSA_ds_w6', project='_Athlos_Harm_Dataset')
eye_far <- ELSA_ds_w6
save(eye_far, file = "../RData/w6/eye_far.RData")

ELSA_m_ds_w6 <- ELSA_ds_w6
ELSA_m_ds_w6$eye_far <- car::recode(ELSA_m_ds_w6$eye_far, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w6', ELSA_m_ds_w6)
#opal.symbol_import(o,'ELSA_m_ds_w6', project='_Athlos_Harm_Dataset')
```



### Wave 7

#### Study-specific variable description




| **Name** | `HeFrnd`| `HeEye`|
|-|-|-|
| **Label** | `Eyesight for recognition of friend across street?` |`Self-reported eyesight (while using lenses, if appropriate)?` |
| **Table name** | `wave_7_elsa_data` | `wave_7_elsa_data` |
| **Categories** | `1 = ...excellent; 2 = very good; 3 = good; 4 = fair; 5 = or, poor?`|`1 = ...excellent; 2 = very good; 3 = good; 4 = fair; 5 = or, poor?; 6 = SPONTANEOUS: Registered or legally blind`|
| **Missings** |`-8 = Don't Know; -1 = Not applicable` |`-8 = Don't Know` |
| **Description** |  |  |




```{r local w7, echo=F}
ELSA_w7_eye_far <- ELSA_w7
vari <- ELSA_w7_eye_far$Hefrnd
kable(Categorical_summary(vari, missing_values = c(-1,-8))[3], caption = "Hefrnd")
kable(Categorical_summary(vari, missing_values = c(-1,-8))[1], caption = "Category")
ggplot(ELSA_w7_eye_far, aes(x=factor(Hefrnd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Far Vision") + ylab("Frequency")

vari <- ELSA_w7_eye_far$HeEye
kable(Categorical_summary(vari, missing_values = c(-8))[3], caption = "HeEye")
kable(Categorical_summary(vari, missing_values = c(-8))[1], caption = "Category")
ggplot(ELSA_w7_eye_far, aes(x=factor(HeEye))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Far Vision") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `hefrnd == 1, 2, 3 into 1` 
* `hefrnd == 4, 5 into 0` 
* `hefrnd == -8 Don't know into 998` 
* `hefrnd == -1 Item not applicable into 996`
* `heeye == 6 into 0`

**R script:**
```{r harmo w7}
ELSA_ds_w7 <- tibble(id=ELSA_w7_eye_far$id)
ELSA_ds_w7$eye_far <- car::recode(ELSA_w7_eye_far$Hefrnd, "1 = '1';2 = '1';3 = '1';4 = '0'; 5 = '0';-8 = '998';-1 = '996' ")

ELSA_ds_w7$eye_far[!is.na(ELSA_w7_eye_far$HeEye) & ELSA_w7_eye_far$HeEye==6] <- 0


ELSA_ds_w7$eye_far <- labelled(ELSA_ds_w7$eye_far, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w7, echo=F}
vari <- ELSA_ds_w7$eye_far
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "eye_far")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w7, aes(x=factor(eye_far))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Eye Sight - Far Vision") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w7, echo=F}
AfterH <- table(ELSA_ds_w7$eye_far)
X<-table(ELSA_w7_eye_far$Hefrnd)
BeforeH <- c(sum(sum(!is.na(ELSA_w7_eye_far$HeEye) & ELSA_w7_eye_far$HeEye==6),sum(X[6:7])),sum(X[3:5]),sum(X[2],-sum(!is.na(ELSA_w7_eye_far$HeEye) & ELSA_w7_eye_far$HeEye==6)),X[c(1)])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4,5,heeye==6->0","1,2,3->1","-1->996","-8->998") 
kable(C)
```





```{r importOPAL_w7, echo=F}

label(ELSA_ds_w7$eye_far) <- "Difficulties for far vision"
#opal.assign.data(o, 'ELSA_ds_w7', ELSA_ds_w7)
#opal.symbol_import(o,'ELSA_ds_w7', project='_Athlos_Harm_Dataset')
eye_far <- ELSA_ds_w7
save(eye_far, file = "../RData/w7/eye_far.RData")

ELSA_m_ds_w7 <- ELSA_ds_w7
ELSA_m_ds_w7$eye_far <- car::recode(ELSA_m_ds_w7$eye_far, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w7', ELSA_m_ds_w7)
#opal.symbol_import(o,'ELSA_m_ds_w7', project='_Athlos_Harm_Dataset')
```

## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.

**R script:**

```{r summ}
ELSA_ds_w1$eye_far <- labelled(ELSA_ds_w1$eye_far, labels = c(Presence=0, Absence=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w2$eye_far <- labelled(ELSA_ds_w2$eye_far, labels = c(Presence=0, Absence=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w3$eye_far <- labelled(ELSA_ds_w3$eye_far, labels = c(Presence=0, Absence=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w4$eye_far <- labelled(ELSA_ds_w4$eye_far, labels = c(Presence=0, Absence=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w5$eye_far <- labelled(ELSA_ds_w5$eye_far, labels = c(Presence=0, Absence=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w6$eye_far <- labelled(ELSA_ds_w6$eye_far, labels = c(Presence=0, Absence=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w7$eye_far <- labelled(ELSA_ds_w7$eye_far, labels = c(Presence=0, Absence=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))

tt <-    frq(ELSA_ds_w1$eye_far)[[1]][,c(1:2,4)]
tt[4] <- frq(ELSA_ds_w2$eye_far)[[1]][,c(4)]
tt[5] <- frq(ELSA_ds_w3$eye_far)[[1]][,c(4)]
tt[6] <- frq(ELSA_ds_w4$eye_far)[[1]][,c(4)]
tt[7] <- frq(ELSA_ds_w5$eye_far)[[1]][,c(4)]
tt[8] <- frq(ELSA_ds_w6$eye_far)[[1]][,c(4)]
tt[9] <- frq(ELSA_ds_w7$eye_far)[[1]][,c(4)]
tt[13,] <- c("n", "sample size", 
             length(ELSA_ds_w1$eye_far), length(ELSA_ds_w2$eye_far), length(ELSA_ds_w3$eye_far),
             length(ELSA_ds_w4$eye_far), length(ELSA_ds_w5$eye_far), length(ELSA_ds_w6$eye_far),     
             length(ELSA_ds_w7$eye_far))
names(tt)<-c("val", "label", "w1", "w2", "w3", "w4", "w5", "w6", "w7")
kable(tt)

dbb <- merge(ELSA_m_ds_w1, ELSA_m_ds_w2, by="id", suffixes = c(".w1",".w2"), all=T)
dbb <- merge(dbb, ELSA_m_ds_w3, by="id", all=T)
dbb <- merge(dbb, ELSA_m_ds_w4, by="id", suffixes = c(".w3",".w4"), all=T)
dbb <- merge(dbb, ELSA_m_ds_w5, by="id", all=T)
dbb <- merge(dbb, ELSA_m_ds_w6, by="id", suffixes = c(".w5",".w6"), all=T)
dbb <- merge(dbb, ELSA_m_ds_w7, by="id", all=T)
names(dbb) <- c("id", "w1", "w2", "w3", "w4", "w5", "w6", "w7")
v.dbb <- paste(dbb[,2],dbb[,3],dbb[,4],dbb[,5],dbb[,6],dbb[,7],dbb[,8],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])
```








# Quality estimation
Npo comments.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
