---
title: "Mobility - Walking"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



```{r load,echo=FALSE}
# Loading local datasets of ELSA and domain health status:
#load("ELSA_w1.rdata")
#load("ELSA_w2.rdata")
load("ELSA_w3.rdata")
load("ELSA_w4.rdata")
load("ELSA_w5.rdata")
load("ELSA_w6.rdata")
load("ELSA_w7.rdata")
```


# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `mob_walk`
* Variable label: `Mobility - walking`
* Variable description: `Difficulty for walking by yourself and without using any special equipment`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


# Data process

## England


### Wave 1

#### Study-specific variable description



| **Name** | `hefunc`|`hemobwa`|
|-|-|-|
| **Label** |`By yourself and without using any special equipment, how much difficulty do you have walking for a quarter of a mile?`|`mobility: difficulty walking 100 yards`|
| **Table name** | `wave_1_core_data_v3` | `wave_1_ifs_derived_variables` |
| **Categories** | `1 = ... no difficulty; 2 = some difficulty; 3 = much difficulty; 4 = or, are you unable to do this?` |`0 = No; 1 = Yes`|
| **Missings** |`-9 = Refusal; -8 = Don't Know; -1 = Not applicable`|`-9 = refuse; -8 = don't know; -1 = inapplicable`|
| **Description** |  |  |


```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'o1','ELSA.wave_1_ifs_derived_variables', variables=list('hemobwa'), missings = TRUE)
ELSA_w1_ifs <- opal.execute(o,'o1')

opal.assign.table.tibble(o, 'o2','ELSA.wave_1_core_data_v3', variables=list('hefunc'), missings = TRUE)
ELSA_w1_data <- opal.execute(o,'o2')
ELSA_w1 <- merge(ELSA_w1_ifs, ELSA_w1_data, by="id", all=T)
```


```{r local w1, echo=F}
ELSA_w1_mob_walk <- ELSA_w1
vari <- ELSA_w1_mob_walk$hefunc
kable(Categorical_summary(vari, missing_values = c(-9,-8,-1))[3], caption = "hefunc")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1_mob_walk, aes(x=factor(hefunc))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking quarter of a mile") + ylab("Frequency")
vari <- ELSA_w1_mob_walk$hemobwa
kable(Categorical_summary(vari, missing_values = c(-9,-8,-1))[3], caption = "hemobwa")
kable(Categorical_summary(vari, missing_values = c(-9,-8,-1))[1], caption = "Category")
ggplot(ELSA_w1_mob_walk, aes(x=factor(hemobwa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking 100 yards") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `((hefunc==-9))&(hemobwa==-9) into 997` 
* `(hefunc==-8)&(hemobwa==-8) into 998` 
* `((hefunc==-1))&(hemobwa==-1) into 996`
* `(hefunc==1) & (hemobwa!=1) into 1` 
* `((hefunc==-9)|(hefunc==-8))&(hemobwa==0) into 1` 
* `Otherwise<-0`


**R script:**
```{r harmo w1}
ELSA_ds_w1 <- tibble(id=ELSA_w1_mob_walk$id)
ELSA_ds_w1$mob_walk <- rep(0,length(ELSA_w1_mob_walk$id))
ELSA_ds_w1$mob_walk[((ELSA_w1_mob_walk$hefunc==1)&(ELSA_w1_mob_walk$hemobwa!=1))]<-1
ELSA_ds_w1$mob_walk[(((ELSA_w1_mob_walk$hefunc==-9)|(ELSA_w1_mob_walk$hefunc==-8))&(ELSA_w1_mob_walk$hemobwa==0))]<-1
ELSA_ds_w1$mob_walk[(((ELSA_w1_mob_walk$hefunc==-1))&(ELSA_w1_mob_walk$hemobwa==-1))]<-996
ELSA_ds_w1$mob_walk[((ELSA_w1_mob_walk$hefunc==-9)&(ELSA_w1_mob_walk$hemobwa==-9))]<-997
ELSA_ds_w1$mob_walk[((ELSA_w1_mob_walk$hefunc==-8)&(ELSA_w1_mob_walk$hemobwa==-8))]<-998

ELSA_ds_w1$mob_walk <- labelled(ELSA_ds_w1$mob_walk, labels = c(Yes=0, No=1,Not_applicable=996, Refuse=997, Do_not_know=998))

```


#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vari <- ELSA_ds_w1$mob_walk
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_walk")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w1, aes(x=factor(mob_walk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
combi<-c(sum(ELSA_ds_w1$mob_walk==0),
sum(c(sum((ELSA_w1_mob_walk$hefunc==1)&(ELSA_w1_mob_walk$hemobwa!=1)),
sum(((ELSA_w1_mob_walk$hefunc==-9)|(ELSA_w1_mob_walk$hefunc==-8))&(ELSA_w1_mob_walk$hemobwa==0)))),
sum(((ELSA_w1_mob_walk$hefunc==-1))&(ELSA_w1_mob_walk$hemobwa==-1))
,sum((ELSA_w1_mob_walk$hefunc==-9)&(ELSA_w1_mob_walk$hemobwa==-9)),
sum((ELSA_w1_mob_walk$hefunc==-8)&(ELSA_w1_mob_walk$hemobwa==-8))
)
C<-rbind(combi,table(ELSA_ds_w1$mob_walk))
colnames(C) <- c("Otherwise -> 0","((hefunc=1&hemobwa!=1)|(hefunc=-9 or -8&hemobwa=0))->1","(hefunc=-1 or -9&hemobwa=-1)->996","(hefunc=-9&hemobwa=-9)->997","(hefunc=-8&hemobwa=-8)->998"
                     ) 
kable(C)
```




```{r importOPAL_w1, echo=F}

label(ELSA_ds_w1$mob_walk) <- "Difficulty for walking by yourself and without using any special equipment"
#opal.assign.data(o, 'ELSA_ds_w1', ELSA_ds_w1)
#opal.symbol_import(o,'ELSA_ds_w1', project='_Athlos_Harm_Dataset')
mob_walk <- ELSA_ds_w1
save(mob_walk, file = "../RData/w1/mob_walk.RData")

ELSA_m_ds_w1 <- ELSA_ds_w1
ELSA_m_ds_w1$mob_walk <- car::recode(ELSA_m_ds_w1$mob_walk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w1', ELSA_m_ds_w1)
#opal.symbol_import(o,'ELSA_m_ds_w1', project='_Athlos_Harm_Dataset')
```


### Wave 2

#### Study-specific variable description



| **Name** | `HeFunc`|`hemobwa`|
|-|-|-|
| **Label** |`Difficulty walking 1/4 mile unaided`|`mobility: difficulty walking 100 yards`|
| **Table name** | `wave_2_core_data_v4` | `wave_2_ifs_derived_variables` |
| **Categories** | `1 = ... no difficulty; 2 = some difficulty; 3 = much difficulty; 4 = Unable to do this` |`0 = No; 1 = Yes`|
| **Missings** |`-9 = Refusal; -8 = Don't Know`|`-9 = refuse; -8 = don't know`|
| **Description** |  |  |


```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'o1','ELSA.wave_2_ifs_derived_variables', variables=list('hemobwa'), missings = TRUE)
ELSA_w2_ifs <- opal.execute(o,'o1')

opal.assign.table.tibble(o, 'o2','ELSA.wave_2_core_data_v4', variables=list('HeFunc'), missings = TRUE)
ELSA_w2_data <- opal.execute(o,'o2')
ELSA_w2 <- merge(ELSA_w2_ifs, ELSA_w2_data, by="id", all=T)
```


```{r local w2, echo=F}
ELSA_w2_mob_walk <- ELSA_w2
vari <- ELSA_w2_mob_walk$HeFunc
kable(Categorical_summary(vari, missing_values = c(-9,-8))[3], caption = "HeFunc")
kable(Categorical_summary(vari, missing_values = c(-9,-8))[1], caption = "Category")
ggplot(ELSA_w2_mob_walk, aes(x=factor(HeFunc))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking quarter of a mile") + ylab("Frequency")
vari <- ELSA_w2_mob_walk$hemobwa
kable(Categorical_summary(vari, missing_values = c(-9,-8))[3], caption = "hemobwa")
kable(Categorical_summary(vari, missing_values = c(-9,-8))[1], caption = "Category")
ggplot(ELSA_w2_mob_walk, aes(x=factor(hemobwa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking 100 yards") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `((hefunc==-9))&(hemobwa==-9) into 997` 
* `(hefunc==-8)&(hemobwa==-8) into 998` 
* `(hefunc==1) & (hemobwa!=1) into 1` 
* `((hefunc==-9)|(hefunc==-8))&(hemobwa==0) into 1` 
* `Otherwise<-0`

**R script:**
```{r harmo w2}
ELSA_ds_w2 <- tibble(id=ELSA_w2_mob_walk$id)
ELSA_ds_w2$mob_walk <- rep(0,length(ELSA_w2_mob_walk$id))
ELSA_ds_w2$mob_walk[((ELSA_w2_mob_walk$HeFunc==1)&(ELSA_w2_mob_walk$hemobwa!=1))]<-1
ELSA_ds_w2$mob_walk[(((ELSA_w2_mob_walk$HeFunc==-9)|(ELSA_w2_mob_walk$HeFunc==-8))&(ELSA_w2_mob_walk$hemobwa==0))]<-1
ELSA_ds_w2$mob_walk[((ELSA_w2_mob_walk$HeFunc==-9)&(ELSA_w2_mob_walk$hemobwa==-9))]<-997
ELSA_ds_w2$mob_walk[((ELSA_w2_mob_walk$HeFunc==-8)&(ELSA_w2_mob_walk$hemobwa==-8))]<-998

ELSA_ds_w2$mob_walk <- labelled(ELSA_ds_w2$mob_walk, labels = c(Yes=0, No=1,Not_applicable=996, Refuse=997, Do_not_know=998))

```


#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vari <- ELSA_ds_w2$mob_walk
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_walk")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w2, aes(x=factor(mob_walk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
combi<-c(sum(ELSA_ds_w2$mob_walk==0),
sum(c(sum((ELSA_w2_mob_walk$HeFunc==1)&(ELSA_w2_mob_walk$hemobwa!=1)),
sum(((ELSA_w2_mob_walk$HeFunc==-9)|(ELSA_w2_mob_walk$HeFunc==-8))&(ELSA_w2_mob_walk$hemobwa==0)))),
sum((ELSA_w2_mob_walk$HeFunc==-9)&(ELSA_w2_mob_walk$hemobwa==-9)),
sum((ELSA_w2_mob_walk$HeFunc==-8)&(ELSA_w2_mob_walk$hemobwa==-8))
)
C<-rbind(combi,table(ELSA_ds_w2$mob_walk))
colnames(C) <- c("Otherwise -> 0","((hefunc=1&hemobwa!=1)|(hefunc=-9 or -8&hemobwa=0))->1","(hefunc=-9&hemobwa=-9)->997","(hefunc=-8&hemobwa=-8)->998"
                     ) 
kable(C)
```




```{r importOPAL_w2, echo=F}

label(ELSA_ds_w2$mob_walk) <- "Difficulty for walking by yourself and without using any special equipment"
#opal.assign.data(o, 'ELSA_ds_w2', ELSA_ds_w1)
#opal.symbol_import(o,'ELSA_ds_w2', project='_Athlos_Harm_Dataset')
mob_walk <- ELSA_ds_w2
save(mob_walk, file = "../RData/w2/mob_walk.RData")

ELSA_m_ds_w2 <- ELSA_ds_w2
ELSA_m_ds_w2$mob_walk <- car::recode(ELSA_m_ds_w2$mob_walk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w2', ELSA_m_ds_w2)
#opal.symbol_import(o,'ELSA_m_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 3 

#### Study-specific variable description



| **Name** | `hefunc`|`hemobwa`|
|-|-|-|
| **Label** |`By yourself and without using any special equipment, how much difficulty do you have walking for a quarter of a mile?`|`Mobility: difficulty walking 100 yards`|
| **Table name** | `wave_3_elsa_data_v4` | `wave_3_elsa_data_v4` |
| **Categories** | `1 = No difficulty; 2 = Some difficulty; 3 = Much difficulty; 4 = or, are you unable to do this?` |`0 = No; 1 = Yes`|
| **Missings** |`-9 = Refusal; -8 = Don't Know`|`-1 = Not applicable`|
| **Description** |  |  |


   


```{r local w3, echo=F}
ELSA_w3_mob_walk <- ELSA_w3
vari <- ELSA_w3_mob_walk$hefunc
kable(Categorical_summary(vari, missing_values = c(-9,-8))[3], caption = "hefunc")
kable(Categorical_summary(vari, missing_values = c(-9,-8))[1], caption = "Category")
ggplot(ELSA_w3_mob_walk, aes(x=factor(hefunc))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking quarter of a mile") + ylab("Frequency")
vari <- ELSA_w3_mob_walk$hemobwa
kable(Categorical_summary(vari, missing_values = c(-1))[3], caption = "hemobwa")
kable(Categorical_summary(vari, missing_values = c(-1))[1], caption = "Category")
ggplot(ELSA_w3_mob_walk, aes(x=factor(hemobwa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking 100 yards") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `(hefunc==1) & (hemobwa!=1) into 1` 
* `((hefunc==-9)|(hefunc==-8))&(hemobwa==0) into 1` 
* `((hefunc==-1)|(hefunc==-9))&(hemobwa==-1) into 996`
* `Otherwise<-0`


**R script:**
```{r harmo w3}
ELSA_ds_w3 <- tibble(id=ELSA_w3_mob_walk$id)
ELSA_ds_w3$mob_walk <- rep(0,length(ELSA_w3_mob_walk$id))
ELSA_ds_w3$mob_walk[((ELSA_w3_mob_walk$hefunc==1)&(ELSA_w3_mob_walk$hemobwa!=1))]<-1
ELSA_ds_w3$mob_walk[(((ELSA_w3_mob_walk$hefunc==-9)|(ELSA_w3_mob_walk$hefunc==-8))&(ELSA_w3_mob_walk$hemobwa==0))]<-1
ELSA_ds_w3$mob_walk[(((ELSA_w3_mob_walk$hefunc==-1)|(ELSA_w3_mob_walk$hefunc==-9))&(ELSA_w3_mob_walk$hemobwa==-1))]<-996
ELSA_ds_w3$mob_walk <- labelled(ELSA_ds_w3$mob_walk, labels = c(Yes=0, No=1,Not_applicable=996, Refuse=997, Do_not_know=998))
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}
vari <- ELSA_ds_w3$mob_walk
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_walk")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w3, aes(x=factor(mob_walk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=F}
combi<-c(sum(ELSA_ds_w3$mob_walk==0),
sum(c(sum((ELSA_w3_mob_walk$hefunc==1)&(ELSA_w3_mob_walk$hemobwa!=1)),
sum(((ELSA_w3_mob_walk$hefunc==-9)|(ELSA_w3_mob_walk$hefunc==-8))&(ELSA_w3_mob_walk$hemobwa==0)))),
sum(((ELSA_w3_mob_walk$hefunc==-1)|(ELSA_w3_mob_walk$hefunc==-9))&(ELSA_w3_mob_walk$hemobwa==-1))
#,sum((ELSA_w3_mob_walk$hefunc==-9)&(ELSA_w3_mob_walk$hemobwa==-9)),
#sum((ELSA_w3_mob_walk$hefunc==-8)&(ELSA_w3_mob_walk$hemobwa==-8))
)
C<-rbind(combi,table(ELSA_ds_w3$mob_walk))
colnames(C) <- c("Otherwise -> 0","((hefunc=1&hemobwa!=1)|(hefunc=-9 or -8&hemobwa=0))->1",#"(hefunc=-9&hemobwa=-9)->997","(hefunc=-8&hemobwa=-8)->998",
                     "(hefunc=-1  or -9&hemobwa=-1)->996") 
kable(C)
```





```{r importOPAL_w3, echo=F}

label(ELSA_ds_w3$mob_walk) <- "Difficulty for walking by yourself and without using any special equipment"
#opal.assign.data(o, 'ELSA_ds_w3', ELSA_ds_w3)
#opal.symbol_import(o,'ELSA_ds_w3', project='_Athlos_Harm_Dataset')
mob_walk <- ELSA_ds_w3
save(mob_walk, file = "../RData/w3/mob_walk.RData")

ELSA_m_ds_w3 <- ELSA_ds_w3
ELSA_m_ds_w3$mob_walk <- car::recode(ELSA_m_ds_w3$mob_walk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w3', ELSA_m_ds_w3)
#opal.symbol_import(o,'ELSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```





### Wave 4 

#### Study-specific variable description




| **Name** | `hefunc`|`hemobwa`|
|-|-|-|
| **Label** |`By yourself and without using any special equipment, how much difficulty do you have walking for a quarter of a mile?`|`Mobility: difficulty walking 100 yards`|
| **Table name** | `wave_4_elsa_data_v3` | `wave_4_elsa_data_v3` |
| **Categories** | `1 = No difficulty; 2 = Some difficulty; 3 = Much difficulty; 4 = or, are you unable to do this?` |`0 = No; 1 = Yes`|
| **Missings** |`-9 = Refusal; -8 = Don't Know`|`-9 = Refusal; -8 = Don't Know`|
| **Description** |  |  |



```{r local w4, echo=F}
ELSA_w4_mob_walk <- ELSA_w4
vari <- ELSA_w4_mob_walk$hefunc
kable(Categorical_summary(vari, missing_values = c(-9,-8))[3], caption = "hefunc")
kable(Categorical_summary(vari, missing_values = c(-9,-8))[1], caption = "Category")
ggplot(ELSA_w4_mob_walk, aes(x=factor(hefunc))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking quarter of a mile") + ylab("Frequency")
vari <- ELSA_w4_mob_walk$hemobwa
kable(Categorical_summary(vari, missing_values = c(-9,-8))[3], caption = "hemobwa")
kable(Categorical_summary(vari, missing_values = c(-9,-8))[1], caption = "Category")
ggplot(ELSA_w4_mob_walk, aes(x=factor(hemobwa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking 100 yards") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `(hefunc==1) & (hemobwa!=1)into 1` 
* `((hefunc==-9)|(hefunc==-8))&(hemobwa==0) into 1` 
* `(hefunc==-9)&(hemobwa==-9) into 997` 
* `(hefunc==-8)&(hemobwa==-8) into 998` 
* `Otherwise<-0`


**R script:**
```{r harmo w4}
ELSA_ds_w4 <- tibble(id=ELSA_w4_mob_walk$id)
ELSA_ds_w4$mob_walk <- rep(0,length(ELSA_w4_mob_walk$id))
ELSA_ds_w4$mob_walk[((ELSA_w4_mob_walk$hefunc==1)&(ELSA_w4_mob_walk$hemobwa!=1))]<-1
ELSA_ds_w4$mob_walk[(((ELSA_w4_mob_walk$hefunc==-9)|(ELSA_w4_mob_walk$hefunc==-8))&(ELSA_w4_mob_walk$hemobwa==0))]<-1
ELSA_ds_w4$mob_walk[((ELSA_w4_mob_walk$hefunc==-9)&(ELSA_w4_mob_walk$hemobwa==-9))]<-997
ELSA_ds_w4$mob_walk[((ELSA_w4_mob_walk$hefunc==-8)&(ELSA_w4_mob_walk$hemobwa==-8))]<-998
ELSA_ds_w4$mob_walk <- labelled(ELSA_ds_w4$mob_walk, labels = c(Yes=0, No=1,Not_applicable=996, Refuse=997, Do_not_know=998))
```

#### Statistical description of the new harmonised variable
```{r descript w4, echo=F}
vari <- ELSA_ds_w4$mob_walk
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_walk")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w4, aes(x=factor(mob_walk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w4, echo=F}
combi<-c(sum(ELSA_ds_w4$mob_walk==0),
sum(c(sum((ELSA_w4_mob_walk$hefunc==1)&(ELSA_w4_mob_walk$hemobwa!=1)),
sum(((ELSA_w4_mob_walk$hefunc==-9)|(ELSA_w4_mob_walk$hefunc==-8))&(ELSA_w4_mob_walk$hemobwa==0)))),
sum((ELSA_w4_mob_walk$hefunc==-9)&(ELSA_w4_mob_walk$hemobwa==-9)),
sum((ELSA_w4_mob_walk$hefunc==-8)&(ELSA_w4_mob_walk$hemobwa==-8))
)
C<-rbind(combi,table(ELSA_ds_w4$mob_walk))
colnames(C) <- c("Otherwise -> 0","((hefunc=1&hemobwa!=1)|(hefunc=-9 or -8&hemobwa=0))->1","(hefunc=-9&hemobwa=-9)->997","(hefunc=-8&hemobwa=-8)->998") 
kable(C)
```





```{r importOPAL_w4, echo=F}

label(ELSA_ds_w4$mob_walk) <- "Difficulty for walking by yourself and without using any special equipment"
#opal.assign.data(o, 'ELSA_ds_w4', ELSA_ds_w4)
#opal.symbol_import(o,'ELSA_ds_w4', project='_Athlos_Harm_Dataset')
mob_walk <- ELSA_ds_w4
save(mob_walk, file = "../RData/w4/mob_walk.RData")

ELSA_m_ds_w4 <- ELSA_ds_w4
ELSA_m_ds_w4$mob_walk <- car::recode(ELSA_m_ds_w4$mob_walk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w4', ELSA_m_ds_w4)
#opal.symbol_import(o,'ELSA_m_ds_w4', project='_Athlos_Harm_Dataset')
```





### Wave 5 

#### Study-specific variable description



| **Name** | `HeFunc`|`hemobwa`|
|-|-|-|
| **Label** |`By yourself and without using any special equipment, how much difficulty do you have walking for a quarter of a mile?`|`Mobility: difficulty walking 100 yards`|
| **Table name** | `wave_5_elsa_data_v4` | `wave_5_elsa_data_v4` |
| **Categories** | `1 = No difficulty; 2 = Some difficulty; 3 = Much difficulty; 4 = or, are you unable to do this?` |`0 = No; 1 = Yes`|
| **Missings** |`-9 = Refusal; -8 = Don't Know`|`-9 = Refusal; -8 = Don't Know`|
| **Description** |  |  |





```{r local w5, echo=F}
ELSA_w5_mob_walk <- ELSA_w5
vari <- ELSA_w5_mob_walk$HeFunc
kable(Categorical_summary(vari, missing_values = c(-9,-8))[3], caption = "HeFunc")
kable(Categorical_summary(vari, missing_values = c(-9,-8))[1], caption = "Category")
ggplot(ELSA_w5_mob_walk, aes(x=factor(HeFunc))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking quarter of a mile") + ylab("Frequency")
vari <- ELSA_w5_mob_walk$hemobwa
kable(Categorical_summary(vari, missing_values = c(-9,-8))[3], caption = "hemobwa")
kable(Categorical_summary(vari, missing_values = c(-9,-8))[1], caption = "Category")
ggplot(ELSA_w5_mob_walk, aes(x=factor(hemobwa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking 100 yards") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `(hefunc==1) & (hemobwa!=1)into 1` 
* `((hefunc==-9)|(hefunc==-8))&(hemobwa==0) into 1` 
* `((hefunc==-9)|(hefunc==-8))&(hemobwa==-9) into 997` 
* `(hefunc==-8)&(hemobwa==-8) into 998` 
* `Otherwise<-0`


**R script:**
```{r harmo w5}
ELSA_ds_w5 <- tibble(id=ELSA_w5_mob_walk$id)
ELSA_ds_w5$mob_walk <- rep(0,length(ELSA_w5_mob_walk$id))
ELSA_ds_w5$mob_walk[((ELSA_w5_mob_walk$HeFunc==1)&(ELSA_w5_mob_walk$hemobwa!=1))]<-1
ELSA_ds_w5$mob_walk[(((ELSA_w5_mob_walk$HeFunc==-9)|(ELSA_w5_mob_walk$HeFunc==-8))&(ELSA_w5_mob_walk$hemobwa==0))]<-1
ELSA_ds_w5$mob_walk[(((ELSA_w5_mob_walk$HeFunc==-9)|(ELSA_w5_mob_walk$HeFunc==-8))&(ELSA_w5_mob_walk$hemobwa==-9))]<-997
ELSA_ds_w5$mob_walk[((ELSA_w5_mob_walk$HeFunc==-8)&(ELSA_w5_mob_walk$hemobwa==-8))]<-998
ELSA_ds_w5$mob_walk <- labelled(ELSA_ds_w5$mob_walk, labels = c(Yes=0, No=1,Not_applicable=996, Refuse=997, Do_not_know=998))
```

#### Statistical description of the new harmonised variable
```{r descript w5, echo=F}
vari <- ELSA_ds_w5$mob_walk
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_walk")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w5, aes(x=factor(mob_walk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w5, echo=F}
combi<-c(sum(ELSA_ds_w5$mob_walk==0),
sum(c(sum((ELSA_w5_mob_walk$HeFunc==1)&(ELSA_w5_mob_walk$hemobwa!=1)),
sum(((ELSA_w5_mob_walk$HeFunc==-9)|(ELSA_w5_mob_walk$HeFunc==-8))&(ELSA_w5_mob_walk$hemobwa==0)))),
#sum(((ELSA_w5_mob_walk$HeFunc==1)|(ELSA_w5_mob_walk$HeFunc==4))&(ELSA_w5_mob_walk$hemobwa==-1)),
sum(((ELSA_w5_mob_walk$HeFunc==-9)|(ELSA_w5_mob_walk$HeFunc==-8))&(ELSA_w5_mob_walk$hemobwa==-9)),
sum((ELSA_w5_mob_walk$HeFunc==-8)&(ELSA_w5_mob_walk$hemobwa==-8))
)
C<-rbind(combi,table(ELSA_ds_w5$mob_walk))
colnames(C) <- c("Otherwise -> 0","((hefunc=1&hemobwa!=1)|(hefunc=-9 or -8&hemobwa=0))->1","(hefunc=-9 or -8&hemobwa=-9)->997","(hefunc=-8&hemobwa=-8)->998"#,"(hefunc=1 or #4&hemobwa=-1)->996",
                 ) 
kable(C)
```





```{r importOPAL_w5, echo=F}

label(ELSA_ds_w5$mob_walk) <- "Difficulty for walking by yourself and without using any special equipment"
#opal.assign.data(o, 'ELSA_ds_w5', ELSA_ds_w5)
#opal.symbol_import(o,'ELSA_ds_w5', project='_Athlos_Harm_Dataset')
mob_walk <- ELSA_ds_w5
save(mob_walk, file = "../RData/w5/mob_walk.RData")

ELSA_m_ds_w5 <- ELSA_ds_w5
ELSA_m_ds_w5$mob_walk <- car::recode(ELSA_m_ds_w5$mob_walk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w5', ELSA_m_ds_w5)
#opal.symbol_import(o,'ELSA_m_ds_w5', project='_Athlos_Harm_Dataset')
```




### Wave 6 

#### Study-specific variable description



| **Name** | `HeFunc`|`hemobwa`|
|-|-|-|
| **Label** |`By yourself and without using any special equipment, how much difficulty do you have walking for a quarter of a mile?`|`Mobility: difficulty walking 100 yards`|
| **Table name** | `wave_6_elsa_data_v2` | `wave_6_elsa_data_v2` |
| **Categories** | `1 = No difficulty; 2 = Some difficulty; 3 = Much difficulty; 4 = or, are you unable to do this?` |`0 = No; 1 = Yes`|
| **Missings** |`-9 = Refusal; -8 = Don't Know`|`-9 = Refusal; -8 = Don't Know`|
| **Description** |  |  |



```{r local w6, echo=F}
ELSA_w6_mob_walk <- ELSA_w6
vari <- ELSA_w6_mob_walk$HeFunc
kable(Categorical_summary(vari, missing_values = c(-9,-8))[3], caption = "HeFunc")
kable(Categorical_summary(vari, missing_values = c(-9,-8))[1], caption = "Category")
ggplot(ELSA_w6_mob_walk, aes(x=factor(HeFunc))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking quarter of a mile") + ylab("Frequency")
vari <- ELSA_w6_mob_walk$hemobwa
kable(Categorical_summary(vari, missing_values = c(-9,-8))[3], caption = "hemobwa")
kable(Categorical_summary(vari, missing_values = c(-9,-8))[1], caption = "Category")
ggplot(ELSA_w6_mob_walk, aes(x=factor(hemobwa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking 100 yards") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `(hefunc==1) & (hemobwa!=1)into 1` 
* `((hefunc==-9)|(hefunc==-8))&(hemobwa==0) into 1` 
* `(hefunc==-9)&(hemobwa==-9) into 997` 
* `(hefunc==-8)&(hemobwa==-8) into 998` 
* `Otherwise<-0`


**R script:**
```{r harmo w6}
ELSA_ds_w6 <- tibble(id=ELSA_w6_mob_walk$id)
ELSA_ds_w6$mob_walk <- rep(0,length(ELSA_w6_mob_walk$id))
ELSA_ds_w6$mob_walk[((ELSA_w6_mob_walk$HeFunc==1)&(ELSA_w6_mob_walk$hemobwa!=1))]<-1
ELSA_ds_w6$mob_walk[(((ELSA_w6_mob_walk$HeFunc==-9)|(ELSA_w6_mob_walk$HeFunc==-8))&(ELSA_w6_mob_walk$hemobwa==0))]<-1
ELSA_ds_w6$mob_walk[((ELSA_w6_mob_walk$HeFunc==-9)&(ELSA_w6_mob_walk$hemobwa==-9))]<-997
ELSA_ds_w6$mob_walk[((ELSA_w6_mob_walk$HeFunc==-8)&(ELSA_w6_mob_walk$hemobwa==-8))]<-998
ELSA_ds_w6$mob_walk <- labelled(ELSA_ds_w6$mob_walk, labels = c(Yes=0, No=1,Not_applicable=996, Refuse=997, Do_not_know=998))
```

#### Statistical description of the new harmonised variable
```{r descript w6, echo=F}
vari <- ELSA_ds_w6$mob_walk
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_walk")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w6, aes(x=factor(mob_walk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w6, echo=F}
combi<-c(sum(ELSA_ds_w6$mob_walk==0),
sum(c(sum((ELSA_w6_mob_walk$HeFunc==1)&(ELSA_w6_mob_walk$hemobwa!=1)),
sum(((ELSA_w6_mob_walk$HeFunc==-9)|(ELSA_w6_mob_walk$HeFunc==-8))&(ELSA_w6_mob_walk$hemobwa==0)))),
sum((ELSA_w6_mob_walk$HeFunc==-9)&(ELSA_w6_mob_walk$hemobwa==-9))#,
#sum((ELSA_w6_mob_walk$HeFunc==-8)&(ELSA_w6_mob_walk$hemobwa==-8))
)
C<-rbind(combi,table(ELSA_ds_w6$mob_walk))
colnames(C) <- c("Otherwise -> 0","((hefunc=1&hemobwa!=1)|(hefunc=-9 or -8&hemobwa=0))->1","(hefunc=-9&hemobwa=-9)->997"#,"(hefunc=-8&hemobwa=-8)->998","(hefunc=4&hemobwa=-8)->996"
                 ) 
kable(C)
```





```{r importOPAL_w6, echo=F}

label(ELSA_ds_w6$mob_walk) <- "Difficulty for walking by yourself and without using any special equipment"
#opal.assign.data(o, 'ELSA_ds_w6', ELSA_ds_w6)
#opal.symbol_import(o,'ELSA_ds_w6', project='_Athlos_Harm_Dataset')
mob_walk <- ELSA_ds_w6
save(mob_walk, file = "../RData/w6/mob_walk.RData")

ELSA_m_ds_w6 <- ELSA_ds_w6
ELSA_m_ds_w6$mob_walk <- car::recode(ELSA_m_ds_w6$mob_walk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w6', ELSA_m_ds_w6)
#opal.symbol_import(o,'ELSA_m_ds_w6', project='_Athlos_Harm_Dataset')
```



### Wave 7 

#### Study-specific variable description



| **Name** | `HeFunc`|`hemobwa`|
|-|-|-|
| **Label** |`By yourself and without using any special equipment, how much difficulty do you have walking for a quarter of a mile?`|`Mobility: difficulty walking 100 yards`|
| **Table name** | `wave_7_elsa_data` | `wave_7_elsa_data` |
| **Categories** | `1 = No difficulty; 2 = Some difficulty; 3 = Much difficulty; 4 = or, are you unable to do this?` |`0 = No; 1 = Yes`|
| **Missings** |`-9 = Refusal; -8 = Don't Know`|`-9 = Refusal; -8 = Don't Know`|
| **Description** |  |  |



```{r local w7, echo=F}
ELSA_w7_mob_walk <- ELSA_w7
vari <- ELSA_w7_mob_walk$HeFunc
kable(Categorical_summary(vari, missing_values = c(-9,-8))[3], caption = "HeFunc")
kable(Categorical_summary(vari, missing_values = c(-9,-8))[1], caption = "Category")
ggplot(ELSA_w7_mob_walk, aes(x=factor(HeFunc))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking quarter of a mile") + ylab("Frequency")
vari <- ELSA_w7_mob_walk$hemobwa
kable(Categorical_summary(vari, missing_values = c(-9,-8))[3], caption = "hemobwa")
kable(Categorical_summary(vari, missing_values = c(-9,-8))[1], caption = "Category")
ggplot(ELSA_w7_mob_walk, aes(x=factor(hemobwa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking 100 yards") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `(hefunc==1) & (hemobwa!=1)into 1` 
* `((hefunc==-9)|(hefunc==-8))&(hemobwa==0) into 1` 
* `(hefunc==-9)&(hemobwa==-9) into 997` 
* `(hefunc==-8)&(hemobwa==-8) into 998` 
* `Otherwise<-0`


**R script:**
```{r harmo w7}
ELSA_ds_w7 <- tibble(id=ELSA_w7_mob_walk$id)
ELSA_ds_w7$mob_walk <- rep(0,length(ELSA_w7_mob_walk$id))
ELSA_ds_w7$mob_walk[((ELSA_w7_mob_walk$HeFunc==1)&(ELSA_w7_mob_walk$hemobwa!=1))]<-1
ELSA_ds_w7$mob_walk[(((ELSA_w7_mob_walk$HeFunc==-9)|(ELSA_w7_mob_walk$HeFunc==-8))&(ELSA_w7_mob_walk$hemobwa==0))]<-1
ELSA_ds_w7$mob_walk[((ELSA_w7_mob_walk$HeFunc==-9)&(ELSA_w7_mob_walk$hemobwa==-9))]<-997
ELSA_ds_w7$mob_walk[((ELSA_w7_mob_walk$HeFunc==-8)&(ELSA_w7_mob_walk$hemobwa==-8))]<-998
ELSA_ds_w7$mob_walk <- labelled(ELSA_ds_w7$mob_walk, labels = c(Yes=0, No=1,Not_applicable=996, Refuse=997, Do_not_know=998))
```

#### Statistical description of the new harmonised variable
```{r descript w7, echo=F}
vari <- ELSA_ds_w7$mob_walk
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_walk")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w7, aes(x=factor(mob_walk))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Walking") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w7, echo=F}
combi<-c(sum(ELSA_ds_w7$mob_walk==0),
sum(c(sum((ELSA_w7_mob_walk$HeFunc==1)&(ELSA_w7_mob_walk$hemobwa!=1)),
sum(((ELSA_w7_mob_walk$HeFunc==-9)|(ELSA_w7_mob_walk$HeFunc==-8))&(ELSA_w7_mob_walk$hemobwa==0)))),
#sum(((ELSA_w7_mob_walk$HeFunc==1)|(ELSA_w7_mob_walk$HeFunc==4))&(ELSA_w7_mob_walk$hemobwa==-1)),
#sum((ELSA_w7_mob_walk$HeFunc==-9)&(ELSA_w7_mob_walk$hemobwa==-9))#,
sum((ELSA_w7_mob_walk$HeFunc==-8)&(ELSA_w7_mob_walk$hemobwa==-8))
)
C<-rbind(combi,table(ELSA_ds_w7$mob_walk))
colnames(C) <- c("Otherwise -> 0","((hefunc=1&hemobwa!=1)|(hefunc=-9 or -8&hemobwa=0))->1","(hefunc=-8&hemobwa=-8)->998"#,"(hefunc=-8&hemobwa=-8)->998","(hefunc=1 or #4&hemobwa=-1)->996",
                 ) 
kable(C)
```





```{r importOPAL_w7, echo=F}

label(ELSA_ds_w7$mob_walk) <- "Difficulty for walking by yourself and without using any special equipment"
#opal.assign.data(o, 'ELSA_ds_w7', ELSA_ds_w7)
#opal.symbol_import(o,'ELSA_ds_w7', project='_Athlos_Harm_Dataset')
mob_walk <- ELSA_ds_w7
save(mob_walk, file = "../RData/w7/mob_walk.RData")

ELSA_m_ds_w7 <- ELSA_ds_w7
ELSA_m_ds_w7$mob_walk <- car::recode(ELSA_m_ds_w7$mob_walk, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w7', ELSA_m_ds_w7)
#opal.symbol_import(o,'ELSA_m_ds_w7', project='_Athlos_Harm_Dataset')
```


## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.

**R script:**

```{r pre_summ, eval=F, echo=F}

ELSA_ds_w3$mob_walk <- labelled(ELSA_ds_w3$mob_walk, labels = c(Presence=0, Absence=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w4$mob_walk <- labelled(ELSA_ds_w4$mob_walk, labels = c(Presence=0, Absence=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w5$mob_walk <- labelled(ELSA_ds_w5$mob_walk, labels = c(Presence=0, Absence=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w6$mob_walk <- labelled(ELSA_ds_w6$mob_walk, labels = c(Presence=0, Absence=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w7$mob_walk <- labelled(ELSA_ds_w7$mob_walk, labels = c(Presence=0, Absence=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
tt <-    frq(ELSA_ds_w3$mob_walk)[[1]][,c(1:2,4)]
tt[4] <- frq(ELSA_ds_w4$mob_walk)[[1]][,c(4)]
tt[5] <- frq(ELSA_ds_w5$mob_walk)[[1]][,c(4)]
tt[6] <- frq(ELSA_ds_w6$mob_walk)[[1]][,c(4)]
tt[7] <- frq(ELSA_ds_w7$mob_walk)[[1]][,c(4)]
tt[13,] <- c("n", "sample size", 
             length(ELSA_ds_w3$mob_walk),
             length(ELSA_ds_w4$mob_walk), length(ELSA_ds_w5$mob_walk), length(ELSA_ds_w6$mob_walk),     
             length(ELSA_ds_w7$mob_walk))
names(tt)<-c("val", "label", "w3", "w4", "w5", "w6", "w7")
kable(tt)

dbb <- merge(ELSA_m_ds_w3, ELSA_m_ds_w4, by="id", suffixes = c(".w3",".w4"), all=T)
dbb <- merge(dbb, ELSA_m_ds_w5, by="id", all=T)
dbb <- merge(dbb, ELSA_m_ds_w6, by="id", suffixes = c(".w5",".w6"), all=T)
dbb <- merge(dbb, ELSA_m_ds_w7, by="id", all=T)
v.dbb <- paste(dbb[,2],dbb[,3],dbb[,4],dbb[,5],dbb[,6],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])


```




```{r summ}
ELSA_ds_w1$mob_walk <- labelled(ELSA_ds_w1$mob_walk, labels = c(Presence=0, Absence=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w2$mob_walk <- labelled(ELSA_ds_w2$mob_walk, labels = c(Presence=0, Absence=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w3$mob_walk <- labelled(ELSA_ds_w3$mob_walk, labels = c(Presence=0, Absence=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w4$mob_walk <- labelled(ELSA_ds_w4$mob_walk, labels = c(Presence=0, Absence=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w5$mob_walk <- labelled(ELSA_ds_w5$mob_walk, labels = c(Presence=0, Absence=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w6$mob_walk <- labelled(ELSA_ds_w6$mob_walk, labels = c(Presence=0, Absence=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w7$mob_walk <- labelled(ELSA_ds_w7$mob_walk, labels = c(Presence=0, Absence=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))

tt <-    frq(ELSA_ds_w1$mob_walk)[[1]][,c(1:2,4)]



tt[4] <- frq(ELSA_ds_w2$mob_walk)[[1]][,c(4)]
tt[5] <- frq(ELSA_ds_w3$mob_walk)[[1]][,c(4)]
tt[6] <- frq(ELSA_ds_w4$mob_walk)[[1]][,c(4)]
tt[7] <- frq(ELSA_ds_w5$mob_walk)[[1]][,c(4)]
tt[8] <- frq(ELSA_ds_w6$mob_walk)[[1]][,c(4)]
tt[9] <- frq(ELSA_ds_w7$mob_walk)[[1]][,c(4)]
tt[13,] <- c("n", "sample size", 
             length(ELSA_ds_w1$mob_walk),length(ELSA_ds_w2$mob_walk),length(ELSA_ds_w3$mob_walk),
             length(ELSA_ds_w4$mob_walk), length(ELSA_ds_w5$mob_walk), length(ELSA_ds_w6$mob_walk),     
             length(ELSA_ds_w7$mob_walk))
names(tt)<-c("val", "label", "w1", "w2", "w3", "w4", "w5", "w6", "w7")
kable(tt)

dbb <- merge(ELSA_m_ds_w1, ELSA_m_ds_w2, by="id", suffixes = c(".w1",".w2"), all=T)
dbb <- merge(dbb, ELSA_m_ds_w3, by="id", all=T)
dbb <- merge(dbb, ELSA_m_ds_w4, by="id", suffixes = c(".w3",".w4"), all=T)
dbb <- merge(dbb, ELSA_m_ds_w5, by="id", all=T)
dbb <- merge(dbb, ELSA_m_ds_w6, by="id", suffixes = c(".w5",".w6"), all=T)
dbb <- merge(dbb, ELSA_m_ds_w7, by="id", all=T)
v.dbb <- paste(dbb[,2],dbb[,3],dbb[,4],dbb[,5],dbb[,6],dbb[,7],dbb[,8],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])


```




# Quality estimation
Take into account that in this study the Difficulty for Walking a quarter of a mile (0.8 km) 
and the difficulty for walking 100 yards (91,4 m) is asked while the res of studies ask about 100m or 1km.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
