---
title: "ADL - Eating"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_ania.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `adl_eating`
* Variable label: `ADL-Difficulties for eating`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | yes
1        | no

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




<!-- ########################################################## --> 

# Data process

```{r, loading, echo=FALSE}
# Loading local datasets of ELSA and domain health status:
load("ELSA_w1.rdata")
load("ELSA_w2.rdata")
load("ELSA_w3.rdata")
load("ELSA_w4.rdata")
load("ELSA_w5.rdata")
load("ELSA_w6.rdata")
load("ELSA_w7.rdata")
```


```{r, dataDirectory, echo=FALSE}
datafolder <- "../RData"
``` 


## England
### Wave 1

#### Study-specific variable description

 


* Name: `headlea`
* Label: `ADL: Difficulty for eating`
* Categories:
    + `0 = Not mentioned`
    + `1 = Mentioned`
* Missings
    + `-9 = Refusal` 
    + `-8 = Don't know` 
    + `-1 = Not applicable` 


```{r local w1,  echo=FALSE}
ELSA_w1_adl_eating <- ELSA_w1
vari <- ELSA_w1_adl_eating$headlea # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(ELSA_w1_adl_eating$headlea)
ggplot(ELSA_w1_adl_eating, aes(x=factor(headlea))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty for eating") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `0 into 1` 
* `-9 Refusal into 997` 
* `-8 Don't know into 998`
* `-1 Not applicable into 996`

**R script:** 
```{r harmo w1,   echo=TRUE}
ELSA_ds_w1 <- tibble(id=ELSA_w1_adl_eating$id)
ELSA_ds_w1$adl_eating <- car::recode(ELSA_w1_adl_eating$headlea, "0 = '1';1 = '0';-9 = '997';-8 = '998';-1 = '996' ")
ELSA_ds_w1$adl_eating <- labelled(ELSA_ds_w1$adl_eating, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1,  echo=FALSE}
vari <- ELSA_ds_w1$adl_eating # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w1$adl_eating, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w1, aes(x=factor(adl_eating))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty for eating") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1,  echo=FALSE}
AfterH <- table(ELSA_ds_w1$adl_eating)
X<-table(ELSA_w1_adl_eating$headlea)
BeforeH <- X[c(5,4,3,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","-1->996","-9->997","-8->998") 
kable(C)
```

 
 

<!--- #### Import to OPAL -->
```{r importOPAL_w1, echo=FALSE,  echo=FALSE}
val_labels(ELSA_ds_w1) <- NULL
label(ELSA_ds_w1$adl_eating) <- "ADL: Difficulties for eating"
#opal.assign.data(o, 'ELSA_ds_w1', ELSA_ds_w1)
#opal.symbol_import(o,'ELSA_ds_w1', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w1 <- ELSA_ds_w1
ELSA_m_ds_w1$adl_eating <- car::recode(ELSA_m_ds_w1$adl_eating, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w1', ELSA_m_ds_w1)
#opal.symbol_import(o,'ELSA_m_ds_w1', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
adl_eating <- ELSA_ds_w1
save(adl_eating, file = paste0(datafolder, "/w1/adl_eating.RData"))
```


### Wave 2

#### Study-specific variable description

 


* Name: `headlea`
* Label: `ADL: Difficulty for eating`
* Categories:
    + `0 = Not mentioned`
    + `1 = Mentioned`
* Missings
    + `-9 = Refusal` 
    + `-8 = Don't know` 


```{r local w2,  echo=FALSE}
ELSA_w2_adl_eating <- ELSA_w2
vari <- ELSA_w2_adl_eating$headlea # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(ELSA_w2_adl_eating$headlea)
ggplot(ELSA_w2_adl_eating, aes(x=factor(headlea))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty for eating") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `0 into 1` 
* `-9 Refusal into 997` 
* `-8 Don't know into 998`

**R script:** 
```{r harmo w2,   echo=TRUE}
ELSA_ds_w2 <- tibble(id=ELSA_w2_adl_eating$id)
ELSA_ds_w2$adl_eating <- car::recode(ELSA_w2_adl_eating$headlea, "0 = '1';1 = '0';-9 = '997';-8 = '998';-1 = '996' ")
ELSA_ds_w2$adl_eating <- labelled(ELSA_ds_w2$adl_eating, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2,  echo=FALSE}
vari <- ELSA_ds_w2$adl_eating # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w2$adl_eating, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w2, aes(x=factor(adl_eating))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty for eating") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2,  echo=FALSE}
AfterH <- table(ELSA_ds_w2$adl_eating)
X<-table(ELSA_w2_adl_eating$headlea)
BeforeH <- X[c(4,3,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","-9->997","-8->998") 
kable(C)
```

 
 

<!--- #### Import to OPAL -->
```{r importOPAL_w2, echo=FALSE,  echo=FALSE}
val_labels(ELSA_ds_w2) <- NULL
label(ELSA_ds_w2$adl_eating) <- "ADL: Difficulties for eating"
#opal.assign.data(o, 'ELSA_ds_w2', ELSA_ds_w2)
#opal.symbol_import(o,'ELSA_ds_w2', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w2 <- ELSA_ds_w2
ELSA_m_ds_w2$adl_eating <- car::recode(ELSA_m_ds_w2$adl_eating, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w2', ELSA_m_ds_w2)
#opal.symbol_import(o,'ELSA_m_ds_w2', project='_Athlos_Harm_Dataset')
```


```{r,  echo=FALSE}
adl_eating <- ELSA_ds_w2
save(adl_eating, file = paste0(datafolder, "/w2/adl_eating.RData"))
```
### Wave 3 

#### Study-specific variable description

 


* Name: `headlea`
* Label: `ADL: Difficulty for eating`
* Categories:
    + `0 = Not mentioned`
    + `1 = Mentioned`
* Missings
    + `-1 = Not applicable` 


```{r local w3,  echo=FALSE}
ELSA_w3_adl_eating <- ELSA_w3
vari <- ELSA_w3_adl_eating$headlea # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(ELSA_w3_adl_eating$headlea)
ggplot(ELSA_w3_adl_eating, aes(x=factor(headlea))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty for eating") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `0 into 1` 
* `-1 Not applicable into 996`

**R script:** 
```{r harmo w3,   echo=TRUE}
ELSA_ds_w3 <- tibble(id=ELSA_w3_adl_eating$id)
ELSA_ds_w3$adl_eating <- car::recode(ELSA_w3_adl_eating$headlea, "0 = '1';1 = '0';-9 = '997';-8 = '998';-1 = '996' ")
ELSA_ds_w3$adl_eating <- labelled(ELSA_ds_w3$adl_eating, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3,  echo=FALSE}
vari <- ELSA_ds_w3$adl_eating # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w3$adl_eating, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w3, aes(x=factor(adl_eating))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty for eating") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3,  echo=FALSE}
AfterH <- table(ELSA_ds_w3$adl_eating)
X<-table(ELSA_w3_adl_eating$headlea)
BeforeH <- X[3:1]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","-1->996") 
kable(C)
```

 
 

<!--- #### Import to OPAL -->
```{r importOPAL_w3, echo=FALSE,  echo=FALSE}
val_labels(ELSA_ds_w3) <- NULL
label(ELSA_ds_w3$adl_eating) <- "ADL: Difficulties for eating"
#opal.assign.data(o, 'ELSA_ds_w3', ELSA_ds_w3)
#opal.symbol_import(o,'ELSA_ds_w3', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w3 <- ELSA_ds_w3
ELSA_m_ds_w3$adl_eating <- car::recode(ELSA_m_ds_w3$adl_eating, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w3', ELSA_m_ds_w3)
#opal.symbol_import(o,'ELSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
adl_eating <- ELSA_ds_w3
save(adl_eating, file = paste0(datafolder, "/w3/adl_eating.RData"))
```
### Wave 4 

#### Study-specific variable description

 


* Name: `headlea`
* Label: `ADL: Difficulty for eating`
* Categories:
    + `0 = Not mentioned`
    + `1 = Mentioned`
* Missings
    + `-9 = Refusal` 
    + `-8 = Don't know` 


```{r local w4,  echo=FALSE}
ELSA_w4_adl_eating <- ELSA_w4
vari <- ELSA_w4_adl_eating$headlea # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(ELSA_w4_adl_eating$headlea)
ggplot(ELSA_w4_adl_eating, aes(x=factor(headlea))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty for eating") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `0 into 1` 
* `-9 Refusal into 997` 
* `-8 Don't know into 998`

**R script:** 
```{r harmo w4,   echo=TRUE}
ELSA_ds_w4 <- tibble(id=ELSA_w4_adl_eating$id)
ELSA_ds_w4$adl_eating <- car::recode(ELSA_w4_adl_eating$headlea, "0 = '1';1 = '0';-9 = '997';-8 = '998';-1 = '996' ")
ELSA_ds_w4$adl_eating <- labelled(ELSA_ds_w4$adl_eating, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w4,  echo=FALSE}
vari <- ELSA_ds_w4$adl_eating # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w4$adl_eating, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w4, aes(x=factor(adl_eating))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty for eating") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w4,  echo=FALSE}
AfterH <- table(ELSA_ds_w4$adl_eating)
X<-table(ELSA_w4_adl_eating$headlea)
BeforeH <- X[c(4,3,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","-9->997","-8->998") 
kable(C)
```

 
 

<!--- #### Import to OPAL -->
```{r importOPAL_w4, echo=FALSE,  echo=FALSE}
val_labels(ELSA_ds_w4) <- NULL
label(ELSA_ds_w4$adl_eating) <- "ADL: Difficulties for eating"
#opal.assign.data(o, 'ELSA_ds_w4', ELSA_ds_w4)
#opal.symbol_import(o,'ELSA_ds_w4', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w4 <- ELSA_ds_w4
ELSA_m_ds_w4$adl_eating <- car::recode(ELSA_m_ds_w4$adl_eating, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w4', ELSA_m_ds_w4)
#opal.symbol_import(o,'ELSA_m_ds_w4', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
adl_eating <- ELSA_ds_w4
save(adl_eating, file = paste0(datafolder, "/w4/adl_eating.RData"))
```

### Wave 5 

#### Study-specific variable description

 


* Name: `headlea`
* Label: `ADL: Difficulty for eating`
* Categories:
    + `0 = Not mentioned`
    + `1 = Mentioned`
* Missings
    + `-9 = Refusal` 
    + `-8 = Don't know` 


```{r local w5,  echo=FALSE}
ELSA_w5_adl_eating <- ELSA_w5
vari <- ELSA_w5_adl_eating$headlea # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(ELSA_w5_adl_eating$headlea)
ggplot(ELSA_w5_adl_eating, aes(x=factor(headlea))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty for eating") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `0 into 1` 
* `-9 Refusal into 997` 
* `-8 Don't know into 998`

**R script:** 
```{r harmo w5,   echo=TRUE}
ELSA_ds_w5 <- tibble(id=ELSA_w5_adl_eating$id)
ELSA_ds_w5$adl_eating <- car::recode(ELSA_w5_adl_eating$headlea, "0 = '1';1 = '0';-9 = '997';-8 = '998';-1 = '996' ")
ELSA_ds_w5$adl_eating <- labelled(ELSA_ds_w5$adl_eating, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w5,  echo=FALSE}
vari <- ELSA_ds_w5$adl_eating # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w5$adl_eating, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w5, aes(x=factor(adl_eating))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty for eating") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w5,  echo=FALSE}
AfterH <- table(ELSA_ds_w5$adl_eating)
X<-table(ELSA_w5_adl_eating$headlea)
BeforeH <- X[c(4,3,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","-9->997","-8->998") 
kable(C)
```

 
 

<!--- #### Import to OPAL -->
```{r importOPAL_w5, echo=FALSE,  echo=FALSE}
val_labels(ELSA_ds_w5) <- NULL
label(ELSA_ds_w5$adl_eating) <- "ADL: Difficulties for eating"
#opal.assign.data(o, 'ELSA_ds_w5', ELSA_ds_w5)
#opal.symbol_import(o,'ELSA_ds_w5', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w5 <- ELSA_ds_w5
ELSA_m_ds_w5$adl_eating <- car::recode(ELSA_m_ds_w5$adl_eating, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w5', ELSA_m_ds_w5)
#opal.symbol_import(o,'ELSA_m_ds_w5', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
adl_eating <- ELSA_ds_w5
save(adl_eating, file = paste0(datafolder, "/w5/adl_eating.RData"))
```

### Wave 6 

#### Study-specific variable description

 


* Name: `headlea`
* Label: `ADL: Difficulty for eating`
* Categories:
    + `0 = Not mentioned`
    + `1 = Mentioned`
* Missings
    + `-9 = Refusal` 
    + `-8 = Don't know` 


```{r local w6,  echo=FALSE}
ELSA_w6_adl_eating <- ELSA_w6
vari <- ELSA_w6_adl_eating$headlea # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(ELSA_w6_adl_eating$headlea)
ggplot(ELSA_w6_adl_eating, aes(x=factor(headlea))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty for eating") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `0 into 1` 
* `-9 Refusal into 997` 
* `-8 Don't know into 998`

**R script:** 
```{r harmo w6,   echo=TRUE}
ELSA_ds_w6 <- tibble(id=ELSA_w6_adl_eating$id)
ELSA_ds_w6$adl_eating <- car::recode(ELSA_w6_adl_eating$headlea, "0 = '1';1 = '0';-9 = '997';-8 = '998';-1 = '996' ")
ELSA_ds_w6$adl_eating <- labelled(ELSA_ds_w6$adl_eating, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w6,  echo=FALSE}
vari <- ELSA_ds_w6$adl_eating # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w6$adl_eating, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w6, aes(x=factor(adl_eating))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty for eating") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w6,  echo=FALSE}
AfterH <- table(ELSA_ds_w6$adl_eating)
X<-table(ELSA_w6_adl_eating$headlea)
BeforeH <- X[c(4,3,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","-9->997","-8->998") 
kable(C)
```

 
 

<!--- #### Import to OPAL -->
```{r importOPAL_w6, echo=FALSE,  echo=FALSE}
val_labels(ELSA_ds_w6) <- NULL
label(ELSA_ds_w6$adl_eating) <- "ADL: Difficulties for eating"
#opal.assign.data(o, 'ELSA_ds_w6', ELSA_ds_w6)
#opal.symbol_import(o,'ELSA_ds_w6', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w6 <- ELSA_ds_w6
ELSA_m_ds_w6$adl_eating <- car::recode(ELSA_m_ds_w6$adl_eating, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w6', ELSA_m_ds_w6)
#opal.symbol_import(o,'ELSA_m_ds_w6', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
adl_eating <- ELSA_ds_w6
save(adl_eating, file = paste0(datafolder, "/w6/adl_eating.RData"))
```


### Wave 7 

#### Study-specific variable description

 


* Name: `headlea`
* Label: `ADL: Difficulty for eating`
* Categories:
    + `0 = Not mentioned`
    + `1 = Mentioned`
* Missings
    + `-8 = Don't know` 


```{r local w7,  echo=FALSE}
ELSA_w7_adl_eating <- ELSA_w7
vari <- ELSA_w7_adl_eating$headlea # VARIABLE
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(ELSA_w7_adl_eating$headlea)
ggplot(ELSA_w7_adl_eating, aes(x=factor(headlea))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty for eating") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 0` 
* `0 into 1` 
* `-8 Don't know into 998`

**R script:** 
```{r harmo w7,   echo=TRUE}
ELSA_ds_w7 <- tibble(id=ELSA_w7_adl_eating$id)
ELSA_ds_w7$adl_eating <- car::recode(ELSA_w7_adl_eating$headlea, "0 = '1';1 = '0';-9 = '997';-8 = '998';-1 = '996' ")
ELSA_ds_w7$adl_eating <- labelled(ELSA_ds_w7$adl_eating, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w7,  echo=FALSE}
vari <- ELSA_ds_w7$adl_eating # variable you want to descrive
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = ELSA_ds_w7$adl_eating, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w7, aes(x=factor(adl_eating))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("ADL - Difficulty for eating") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w7,  echo=FALSE}
AfterH <- table(ELSA_ds_w7$adl_eating)
X<-table(ELSA_w7_adl_eating$headlea)
BeforeH <- X[3:1]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","0->1","-8->998") 
kable(C)
```

 
 

<!--- #### Import to OPAL -->
```{r importOPAL_w7, echo=FALSE,  echo=FALSE}
val_labels(ELSA_ds_w7) <- NULL
label(ELSA_ds_w7$adl_eating) <- "ADL: Difficulties for eating"
#opal.assign.data(o, 'ELSA_ds_w7', ELSA_ds_w7)
#opal.symbol_import(o,'ELSA_ds_w7', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w7 <- ELSA_ds_w7
ELSA_m_ds_w7$adl_eating <- car::recode(ELSA_m_ds_w7$adl_eating, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w7', ELSA_m_ds_w7)
#opal.symbol_import(o,'ELSA_m_ds_w7', project='_Athlos_Harm_Dataset')
```

```{r,  echo=FALSE}
adl_eating <- ELSA_ds_w7
save(adl_eating, file = paste0(datafolder, "/w7/adl_eating.RData"))
```
### Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.


```{r summ,  echo=FALSE}
ELSA_ds_w1$adl_eating <- labelled(ELSA_ds_w1$adl_eating, labels = c(Presence=0, Absence=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w2$adl_eating <- labelled(ELSA_ds_w2$adl_eating, labels = c(Presence=0, Absence=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w3$adl_eating <- labelled(ELSA_ds_w3$adl_eating, labels = c(Presence=0, Absence=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w4$adl_eating <- labelled(ELSA_ds_w4$adl_eating, labels = c(Presence=0, Absence=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w5$adl_eating <- labelled(ELSA_ds_w5$adl_eating, labels = c(Presence=0, Absence=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w6$adl_eating <- labelled(ELSA_ds_w6$adl_eating, labels = c(Presence=0, Absence=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w7$adl_eating <- labelled(ELSA_ds_w7$adl_eating, labels = c(Presence=0, Absence=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))

tt <-    frq(ELSA_ds_w1$adl_eating)[[1]][,c(1:2,4)]
tt[4] <- frq(ELSA_ds_w2$adl_eating)[[1]][,c(4)]
tt[5] <- frq(ELSA_ds_w3$adl_eating)[[1]][,c(4)]
tt[6] <- frq(ELSA_ds_w4$adl_eating)[[1]][,c(4)]
tt[7] <- frq(ELSA_ds_w5$adl_eating)[[1]][,c(4)]
tt[8] <- frq(ELSA_ds_w6$adl_eating)[[1]][,c(4)]
tt[9] <- frq(ELSA_ds_w7$adl_eating)[[1]][,c(4)]
tt[13,] <- c("n", "sample size", 
             length(ELSA_ds_w1$adl_eating), length(ELSA_ds_w2$adl_eating), length(ELSA_ds_w3$adl_eating),
             length(ELSA_ds_w4$adl_eating), length(ELSA_ds_w5$adl_eating), length(ELSA_ds_w6$adl_eating),     
             length(ELSA_ds_w7$adl_eating))
names(tt)<-c("val", "label", "w1", "w2", "w3", "w4", "w5", "w6", "w7")
kable(tt)

dbb <- merge(ELSA_m_ds_w1, ELSA_m_ds_w2, by="id", suffixes = c(".w1",".w2"), all=T)
dbb <- merge(dbb, ELSA_m_ds_w3, by="id", all=T)
dbb <- merge(dbb, ELSA_m_ds_w4, by="id", suffixes = c(".w3",".w4"), all=T)
dbb <- merge(dbb, ELSA_m_ds_w5, by="id", all=T)
dbb <- merge(dbb, ELSA_m_ds_w6, by="id", suffixes = c(".w5",".w6"), all=T)
dbb <- merge(dbb, ELSA_m_ds_w7, by="id", all=T)
names(dbb) <- c("id", "w1", "w2", "w3", "w4", "w5", "w6", "w7")
v.dbb <- paste(dbb[,2],dbb[,3],dbb[,4],dbb[,5],dbb[,6],dbb[,7],dbb[,8],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])


```
#Quality estimation:

No comments.
