---
title: "Dizziness"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 




```{r load, echo=F}
# Loading local datasets of ELSA and domain health status:
load("ELSA_w1.rdata")
load("ELSA_w2.rdata")
load("ELSA_w3.rdata")
load("ELSA_w4.rdata")
load("ELSA_w5.rdata")
load("ELSA_w6.rdata")
load("ELSA_w7.rdata")
```

# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `dizziness`
* Variable label: `Dizziness problems when walking on a level surface`
* Variable description: `Dizziness problems when walking on a level surface`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process 

    
## England

### Wave 1 

#### Study-specific variable description




| **Name** | `hediz`|
|-|-|
| **Label** | `How often do you have problems with dizziness when you are walking on a level surface?` |
| **Table name** | `wave_1_core_data_v3` |
| **Categories** | `1 = Always; 2 = Very often; 3 = Often; 4 = Sometimes; 5 = Never; 6 = SPONTANEOUS: Never walks; 7 = SPONTANEOUS: Can't walk` |
| **Missings** | `-9 = Refusal; -8 = Don't Know; -1 = Not applicable` |
| **Description** |  |


```{r local w1, echo=F}
ELSA_w1_dizziness <- ELSA_w1
vari <- ELSA_w1_dizziness$hediz
kable(Categorical_summary(vari, missing_values = c(-1,-8,-9))[3], caption = "hediz")
kable(Categorical_summary(vari, missing_values = c(-1,-8,-9))[1], caption = "Category")
ggplot(ELSA_w1_dizziness, aes(x=factor(hediz))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("dizziness") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 Always into 0` 
* `2 Very often into 0` 
* `3 Often into 0` 
* `4 Sometimes into 0` 
* `5 Never into 1`   
* `6 SPONTANEOUS: Never walks into 996`
* `7 SPONTANEOUS: Can't walk into 996`
* `-9 Refusal into 997` 
* `-8 Don't know into 998` 
* `-1 Not applicable into 996` 

**R script:**
```{r harmo w1}
ELSA_ds_w1 <- tibble(id=ELSA_w1_dizziness$id)
ELSA_ds_w1$dizziness <- car::recode(ELSA_w1_dizziness$hediz, "1 = '0';2 = '0';3 = '0';4 = '0';5 = '1';6 = '996';7 = '996';-9 = '997';-8 = '998';-1 = '996' ")
ELSA_ds_w1$dizziness <- labelled(ELSA_ds_w1$dizziness, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vari <- ELSA_ds_w1$dizziness
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "dizziness")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w1, aes(x=factor(dizziness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("dizziness") + ylab("Frequency")
```

The values coded as 6 and 7 in the study are not missing from its point of view, but are missing for the harmonised variable.

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(ELSA_ds_w1$dizziness)
X<-table(ELSA_w1_dizziness$hediz)
BeforeH <- c(sum(X[4:7]),X[8],sum(X[c(9,10,3)]),X[c(1,2)])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","5->1","-1,6,7->996","-9->997","-8->998") 
kable(C)
```





```{r importOPAL_w1, echo=F}

label(ELSA_ds_w1$dizziness) <- "Dizziness problems when walking on a level surface"
#opal.assign.data(o, 'ELSA_ds_w1', ELSA_ds_w1)
#opal.symbol_import(o,'ELSA_ds_w1', project='_Athlos_Harm_Dataset')
dizziness <- ELSA_ds_w1
save(dizziness, file = "../RData/w1/dizziness.RData")

ELSA_m_ds_w1 <- ELSA_ds_w1
ELSA_m_ds_w1$dizziness <- car::recode(ELSA_m_ds_w1$dizziness, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w1', ELSA_m_ds_w1)
#opal.symbol_import(o,'ELSA_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description




| **Name** | `HeDiz`|
|-|-|
| **Label** | `Dizziness: frequency when walking on level surface` |
| **Table name** | `wave_2_core_data_v4` |
| **Categories** | `1 = Always; 2 = Very often; 3 = Often; 4 = Sometimes; 5 = Never; 6 = SPONTANEOUS: Never walks; 7 = SPONTANEOUS: Can't walk` |
| **Missings** | `-9 = Refusal; -8 = Don't Know; -1 = Not applicable` |
| **Description** |  |


```{r local w2, echo=F}
ELSA_w2_dizziness <- ELSA_w2
vari <- ELSA_w2_dizziness$HeDiz
kable(Categorical_summary(vari, missing_values = c(-1,-8,-9))[3], caption = "HeDiz")
kable(Categorical_summary(vari, missing_values = c(-1,-8,-9))[1], caption = "Category")
ggplot(ELSA_w2_dizziness, aes(x=factor(HeDiz))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("dizziness") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 Always into 0` 
* `2 Very often into 0` 
* `3 Often into 0` 
* `4 Sometimes into 0` 
* `5 Never into 1`   
* `6 SPONTANEOUS: Never walks into 996`
* `7 SPONTANEOUS: Can't walk into 996`
* `-9 Refusal into 997` 
* `-8 Don't know into 998` 
* `-1 Not applicable into 996` 

**R script:**
```{r harmo w2}
ELSA_ds_w2 <- tibble(id=ELSA_w2_dizziness$id)
ELSA_ds_w2$dizziness <- car::recode(ELSA_w2_dizziness$HeDiz, "1 = '0';2 = '0';3 = '0';4 = '0';5 = '1';6 = '996';7 = '996';-9 = '997';-8 = '998';-1 = '996' ")
ELSA_ds_w2$dizziness <- labelled(ELSA_ds_w2$dizziness, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vari <- ELSA_ds_w2$dizziness
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "dizziness")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w2, aes(x=factor(dizziness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("dizziness") + ylab("Frequency")
```

The values coded as 6 and 7 in the study are not missing from its point of view, but are missing for the harmonised variable.



#### Validation
```{r crosstabulation w2, echo=F}
AfterH <- table(ELSA_ds_w2$dizziness)
X<-table(ELSA_w2_dizziness$HeDiz)
BeforeH <- c(sum(X[4:7]),X[8],sum(X[c(9,3)]),X[c(1,2)])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","5->1","-1,6,7->996","-9->997","-8->998") 
kable(C)
```





```{r importOPAL_w2, echo=F}

label(ELSA_ds_w2$dizziness) <- "Dizziness problems when walking on a level surface"
#opal.assign.data(o, 'ELSA_ds_w2', ELSA_ds_w2)
#opal.symbol_import(o,'ELSA_ds_w2', project='_Athlos_Harm_Dataset')
dizziness <- ELSA_ds_w2
save(dizziness, file = "../RData/w2/dizziness.RData")

ELSA_m_ds_w2 <- ELSA_ds_w2
ELSA_m_ds_w2$dizziness <- car::recode(ELSA_m_ds_w2$dizziness, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w2', ELSA_m_ds_w2)
#opal.symbol_import(o,'ELSA_m_ds_w2', project='_Athlos_Harm_Dataset')
```


### Wave 3 

Not found.

### Wave 4 

#### Study-specific variable description




| **Name** | `hediz`|
|-|-|
| **Label** | `Dizziness: How often respondent has problems with dizziness when walking on level surface` |
| **Table name** | `wave_4_elsa_data_v3` |
| **Categories** | `1 = Always; 2 = Very often; 3 = Often; 4 = Sometimes; 5 = Never; 6 = SPONTANEOUS: Never walks; 7 = SPONTANEOUS: Can't walk` |
| **Missings** | `-9 = Refusal; -8 = Don't Know; -1 = Not applicable` |
| **Description** |  |



```{r local w4, echo=F}
ELSA_w4_dizziness <- ELSA_w4
vari <- ELSA_w4_dizziness$hediz
kable(Categorical_summary(vari, missing_values = c(-1,-8,-9))[3], caption = "hediz")
kable(Categorical_summary(vari, missing_values = c(-1,-8,-9))[1], caption = "Category")
ggplot(ELSA_w4_dizziness, aes(x=factor(hediz))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("dizziness") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 Always into 0` 
* `2 Very often into 0` 
* `3 Often into 0` 
* `4 Sometimes into 0` 
* `5 Never into 1`   
* `6 SPONTANEOUS: Never walks into 996`
* `7 SPONTANEOUS: Can't walk into 996`
* `-9 Refusal into 997` 
* `-8 Don't know into 998` 
* `-1 Not applicable into 996` 

**R script:**
```{r harmo w4}
ELSA_ds_w4 <- tibble(id=ELSA_w4_dizziness$id)
ELSA_ds_w4$dizziness <- car::recode(ELSA_w4_dizziness$hediz, "1 = '0';2 = '0';3 = '0';4 = '0';5 = '1';6 = '996';7 = '996';-9 = '997';-8 = '998';-1 = '996' ")
ELSA_ds_w4$dizziness <- labelled(ELSA_ds_w4$dizziness, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w4, echo=F}
vari <- ELSA_ds_w4$dizziness
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "dizziness")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w4, aes(x=factor(dizziness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("dizziness") + ylab("Frequency")
```

The values coded as 6 and 7 in the study are not missing from its point of view, but are missing for the harmonised variable.


#### Validation
```{r crosstabulation w4, echo=F}
AfterH <- table(ELSA_ds_w4$dizziness)
X<-table(ELSA_w4_dizziness$hediz)
BeforeH <- c(sum(X[4:7]),X[8],sum(X[c(9,10,3)]),X[c(1,2)])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","5->1","-1,6,7->996","-9->997","-8->998") 
kable(C)
```





```{r importOPAL_w4, echo=F}

label(ELSA_ds_w4$dizziness) <- "Dizziness problems when walking on a level surface"
#opal.assign.data(o, 'ELSA_ds_w4', ELSA_ds_w4)
#opal.symbol_import(o,'ELSA_ds_w4', project='_Athlos_Harm_Dataset')
dizziness <- ELSA_ds_w4
save(dizziness, file = "../RData/w4/dizziness.RData")

ELSA_m_ds_w4 <- ELSA_ds_w4
ELSA_m_ds_w4$dizziness <- car::recode(ELSA_m_ds_w4$dizziness, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w4', ELSA_m_ds_w4)
#opal.symbol_import(o,'ELSA_m_ds_w4', project='_Athlos_Harm_Dataset')
```


### Wave 5

Not found.

### Wave 6

Not found.


### Wave 7 

#### Study-specific variable description




| **Name** | `HeDiz`|
|-|-|
| **Label** | `Dizziness: How often respondent has problems with dizziness when walking on level surface` |
| **Table name** | `wave_7_elsa_data` |
| **Categories** | `1 = Always; 2 = Very often; 3 = Often; 4 = Sometimes; 5 = Never; 6 = SPONTANEOUS: Never walks; 7 = SPONTANEOUS: Can't walk` |
| **Missings** | `-8 = Don't Know; -1 = Not applicable` |
| **Description** |  |


```{r local w7, echo=F}
ELSA_w7_dizziness <- ELSA_w7
vari <- ELSA_w7_dizziness$HeDiz
kable(Categorical_summary(vari, missing_values = c(-1,-8))[3], caption = "HeDiz")
kable(Categorical_summary(vari, missing_values = c(-1,-8))[1], caption = "Category")
ggplot(ELSA_w7_dizziness, aes(x=factor(HeDiz))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("dizziness") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 Always into 0` 
* `2 Very often into 0` 
* `3 Often into 0` 
* `4 Sometimes into 0` 
* `5 Never into 1`   
* `6 SPONTANEOUS: Never walks into 996`
* `7 SPONTANEOUS: Can't walk into 996`
* `-8 Don't know into 998` 
* `-1 Not applicable into 996` 

**R script:**
```{r harmo w7}
ELSA_ds_w7 <- tibble(id=ELSA_w7_dizziness$id)
ELSA_ds_w7$dizziness <- car::recode(ELSA_w7_dizziness$HeDiz, "1 = '0';2 = '0';3 = '0';4 = '0';5 = '1';6 = '996';7 = '996';-9 = '997';-8 = '998';-1 = '996' ")
ELSA_ds_w7$dizziness <- labelled(ELSA_ds_w7$dizziness, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript w7, echo=F}
vari <- ELSA_ds_w7$dizziness
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "dizziness")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w7, aes(x=factor(dizziness))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("dizziness") + ylab("Frequency")
```

The values coded as 6 and 7 in the study are not missing from its point of view, but are missing for the harmonised variable.


#### Validation
```{r crosstabulation w7, echo=F}
AfterH <- table(ELSA_ds_w7$dizziness)
X<-table(ELSA_w7_dizziness$HeDiz)
BeforeH <- c(sum(X[3:6]),X[7],sum(X[c(8,9,2)]),X[1])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1,2,3,4->0","5->1","-1,6,7->996","-8->998") 
kable(C)
```





```{r importOPAL_w7, echo=F}

label(ELSA_ds_w7$dizziness) <- "Dizziness problems when walking on a level surface"
#opal.assign.data(o, 'ELSA_ds_w7', ELSA_ds_w7)
#opal.symbol_import(o,'ELSA_ds_w7', project='_Athlos_Harm_Dataset')
dizziness <- ELSA_ds_w7
save(dizziness, file = "../RData/w7/dizziness.RData")

ELSA_m_ds_w7 <- ELSA_ds_w7
ELSA_m_ds_w7$dizziness <- car::recode(ELSA_m_ds_w7$dizziness, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w7', ELSA_m_ds_w7)
#opal.symbol_import(o,'ELSA_m_ds_w7', project='_Athlos_Harm_Dataset')
```

## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.

**R script:**

```{r summ}
ELSA_ds_w1$dizziness <- labelled(ELSA_ds_w1$dizziness, labels = c(Presence=0, Absence=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w2$dizziness <- labelled(ELSA_ds_w2$dizziness, labels = c(Presence=0, Absence=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w4$dizziness <- labelled(ELSA_ds_w4$dizziness, labels = c(Presence=0, Absence=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w7$dizziness <- labelled(ELSA_ds_w7$dizziness, labels = c(Presence=0, Absence=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))

tt <-    frq(ELSA_ds_w1$dizziness)[[1]][,c(1:2,4)]
tt[4] <- frq(ELSA_ds_w2$dizziness)[[1]][,c(4)]
tt[5] <- frq(ELSA_ds_w4$dizziness)[[1]][,c(4)]
tt[6] <- frq(ELSA_ds_w7$dizziness)[[1]][,c(4)]
tt[13,] <- c("n", "sample size", 
             length(ELSA_ds_w1$dizziness), length(ELSA_ds_w2$dizziness), 
             length(ELSA_ds_w4$dizziness), length(ELSA_ds_w7$dizziness)
             )
names(tt)<-c("val", "label", "w1", "w2", "w4", "w7")
kable(tt)

dbb <- merge(ELSA_m_ds_w1, ELSA_m_ds_w2, by="id", suffixes = c(".w1",".w2"), all=T)
dbb <- merge(dbb, ELSA_m_ds_w4, by="id", suffixes = c(".w3",".w4"), all=T)
dbb <- merge(dbb, ELSA_m_ds_w7, by="id", all=T)
names(dbb) <- c("id", "w1", "w2", "w4", "w7")
v.dbb <- paste(dbb[,2],dbb[,3],dbb[,4],dbb[,5],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])
```




# Quality estimation
No comments.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```

