---
title: "Processing speed"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")

# Loading local datasets of ELSA and domain health status:
load("ELSA_w1.rdata")
load("ELSA_w2.rdata")
load("ELSA_w3.rdata")
load("ELSA_w4.rdata")
load("ELSA_w5.rdata")
load("ELSA_w6.rdata")
load("ELSA_w7.rdata")
```

# Description of DataSchema variable 

* Short name: `cog_proc_c`
* Variable label: `Cognition - processing speed - Continuous. Test which assesses processing speed`
* Domain: `Health status and functional limitations`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



* Short name: `cog_proc`
* Variable label: `Cognition - processing speed. Test which assesses processing speed. Discrete variable: value 0 = <=25%; value 1 = >25%.`
* Domain: `Health status and functional limitations`
* Value type: `Categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | <=25%
1        | >25%

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Cognition - processing speed"
ds_label_cog_proc_c <- "Cognition - processing speed - Continuous. Test which assesses processing speed"
ds_label_cog_proc <- "Cognition - processing speed. Test which assesses processing speed. Discrete variable: value 0 = <=25%; value 1 = >25%"
```



<!-- ########################################################## --> 

# Data process

## England

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `ncorrec`
* Label: `Letter cancellation task: number correct`
* Categories:
    + `Continuous Variable 0-65`
* Missings
   + `-1 = Not applicable` 

```{r local w1, echo=FALSE}
ELSA_w1_cog_proc <- ELSA_w1
vari <- ELSA_w1_cog_proc$ncorrec
kable(Continuous_summary(var = vari, missing_values = c(-1))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = -1)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = -1)$summary, caption = "Summary")
ggplot(ELSA_w1_cog_proc, aes(ncorrec)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Processing speed") + ylab("Frequency")+xlim(0,65)
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_proc_c` from the study-specific variable the missing values have to be recoded as follows:

* `-1 Not applicable into 996`
* `NA into 999`

To compute the harmonized variable `cog_proc` from `cog_proc_c` it has to be recoded as follows:

* `cog_proc_c <=25% into 0`
* `cog_proc_c >25% into 1`

**R script:**

```{r harmo w1}
#cog_proc_c
ELSA_ds_w1 <- tibble(id=ELSA_w1_cog_proc$id)
ELSA_ds_w1$cog_proc_c <- car::recode(ELSA_w1_cog_proc$ncorrec, "-1=996; NA=999")
ELSA_ds_w1$cog_proc_c <- labelled(ELSA_ds_w1$cog_proc_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(ELSA_ds_w1$cog_proc_c, "999=NA; 996=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

ELSA_ds_w1$cog_proc <- car::recode(ELSA_ds_w1[[2]], "0:Q=0; (Q+1):65=1")
ELSA_ds_w1$cog_proc <- labelled(ELSA_ds_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=FALSE}
vari <- ELSA_ds_w1$cog_proc_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w1, aes(cog_proc_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(0,65)

vari <- ELSA_ds_w1$cog_proc
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w1, aes(x=factor(cog_proc))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Processing speed") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=FALSE}
Continous <- c(sum(na.omit(ELSA_ds_w1[[2]])<=Q), sum(na.omit(ELSA_ds_w1[[2]])>Q & na.omit(ELSA_ds_w1[[2]])<900), sum(na.omit(ELSA_ds_w1[[2]])==996))
Dicotomic <- table(ELSA_ds_w1[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:15->0","16:65->1", "-1->996") 
kable(C, caption = "Continuous vs Dichotomous")
```

```{r importOPAL_w1, echo=FALSE}
#opal.assign.data(o, 'ELSA_ds_w1', ELSA_ds_w1)
#opal.symbol_import(o,'ELSA_ds_w1', project='_Athlos_Harm_Dataset')

label(ELSA_ds_w1$cog_proc_c) <- ds_label_cog_proc_c
label(ELSA_ds_w1$cog_proc) <- ds_label_cog_proc
cog_proc <- ELSA_ds_w1
save(cog_proc, file = "../RData/w1/cog_proc.RData")
```


### Wave 2 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `nncorre`
* Label: `Letter cancellation task: number correct`
* Categories:
    + `Continuous Variable 0-65`
* Missings
   + `-1 = Not applicable` 

```{r local w2, echo=FALSE}
ELSA_w2_cog_proc <- ELSA_w2
vari <- ELSA_w2_cog_proc$nncorre
kable(Continuous_summary(var = vari, missing_values = c(-1))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = -1)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = -1)$summary, caption = "Summary")
ggplot(ELSA_w2_cog_proc, aes(x=(nncorre))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Processing speed") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_proc_c` from the study-specific variable the missing values have to be recoded as follows:

* `-1 Not applicable into 996`
* `NA into 999`

To compute the harmonized variable `cog_proc` from `cog_proc_c` it has to be recoded as follows:

* `cog_proc_c <=25% into 0`
* `cog_proc_c >25% into 1`

**R script:**

```{r harmo w2}
#cog_proc_c
ELSA_ds_w2 <- tibble(id=ELSA_w2_cog_proc$id)
ELSA_ds_w2$cog_proc_c <- car::recode(ELSA_w2_cog_proc$nncorre, "-1=996; NA=999")
ELSA_ds_w2$cog_proc_c <- labelled(ELSA_ds_w2$cog_proc_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(ELSA_ds_w2$cog_proc_c, "999=NA; 996=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

ELSA_ds_w2$cog_proc <- car::recode(ELSA_ds_w2[[2]], "0:Q=0; (Q+1):65=1")
ELSA_ds_w2$cog_proc <- labelled(ELSA_ds_w2[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=FALSE}
vari <- ELSA_ds_w2$cog_proc_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w2, aes(x=(cog_proc_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Processing speed") + ylab("Frequency") + xlim(0,60)

vari <- ELSA_ds_w2$cog_proc
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w2, aes(x=factor(cog_proc))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Processing speed") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=FALSE}
Continous <- c(sum(na.omit(ELSA_ds_w2[[2]])<=Q), sum(na.omit(ELSA_ds_w2[[2]])>Q & na.omit(ELSA_ds_w2[[2]])<900), sum(na.omit(ELSA_ds_w2[[2]])==996))
Dicotomic <- table(ELSA_ds_w2[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:15->0","16:65->1", "-1->996") 
kable(C, caption = "Continuous vs Dichotomous")
```

<!--- #### Import to OPAL -->
```{r importOPAL_w2, echo=FALSE}
#opal.assign.data(o, 'ELSA_ds_w2', ELSA_ds_w2)
#opal.symbol_import(o,'ELSA_ds_w2', project='_Athlos_Harm_Dataset')

label(ELSA_ds_w2$cog_proc_c) <- ds_label_cog_proc_c
label(ELSA_ds_w2$cog_proc) <- ds_label_cog_proc
cog_proc <- ELSA_ds_w2
save(cog_proc, file = "../RData/w2/cog_proc.RData")
```



### Wave 3 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `ncorrect`
* Label: `Number of words recalled immediately`
* Categories:
    + `Continuous Variable 0-65`
* Missings
   + `-2 = Letter cancellation tasks done but booklet not received` 
   + `-1 = Not applicable` 


```{r local w3, echo=FALSE}
ELSA_w3_cog_proc <- ELSA_w3
vari <- ELSA_w3_cog_proc$ncorrect
kable(Continuous_summary(var = vari, missing_values = c(-1, -2))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(-1, -2))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-1, -2))$summary, caption = "Summary")
ggplot(ELSA_w3_cog_proc, aes(x=(ncorrect))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Processing speed") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_proc_c` from the study-specific variable the missing values have to be recoded as follows:

* `-1 Not applicable into 996`
* `-2 Letter cancellation tasks done but booklet not received into 996` 
* `NA into 999`

To compute the harmonized variable `cog_proc` from `cog_proc_c` it has to be recoded as follows:

* `cog_proc_c <=25% into 0`
* `cog_proc_c >25% into 1`

**R script:**

```{r harmo w3}
#cog_proc_c
ELSA_ds_w3 <- tibble(id=ELSA_w3_cog_proc$id)
ELSA_ds_w3$cog_proc_c <- car::recode(ELSA_w3_cog_proc$ncorrect, "-1=996; -2=996; NA=999")
ELSA_ds_w3$cog_proc_c <- labelled(ELSA_ds_w3$cog_proc_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(ELSA_ds_w3$cog_proc_c, "999=NA; 996=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

ELSA_ds_w3$cog_proc <- car::recode(ELSA_ds_w3[[2]], "0:Q=0; (Q+1):65=1")
ELSA_ds_w3$cog_proc <- labelled(ELSA_ds_w3[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=FALSE}
vari <- ELSA_ds_w3$cog_proc_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w3, aes(x=(cog_proc_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Processing speed") + ylab("Frequency") + xlim(0,60)

vari <- ELSA_ds_w3$cog_proc
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w3, aes(x=factor(cog_proc))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Processing speed") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=FALSE}
Continous <- c(sum(na.omit(ELSA_ds_w3[[2]])<=Q), sum(na.omit(ELSA_ds_w3[[2]])>Q & na.omit(ELSA_ds_w3[[2]])<900), sum(na.omit(ELSA_ds_w3[[2]])==996))
Dicotomic <- table(ELSA_ds_w3[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:15->0","16:65->1", "-1->996") 
kable(C, caption = "Continuous vs Dichotomous")
```


<!--- #### Import to OPAL -->
```{r importOPAL_w3, echo=FALSE}
#opal.assign.data(o, 'ELSA_ds_w3', ELSA_ds_w3)
#opal.symbol_import(o,'ELSA_ds_w3', project='_Athlos_Harm_Dataset')

label(ELSA_ds_w3$cog_proc_c) <- ds_label_cog_proc_c
label(ELSA_ds_w3$cog_proc) <- ds_label_cog_proc
cog_proc <- ELSA_ds_w3
save(cog_proc, file = "../RData/w3/cog_proc.RData")
```


### Wave 4 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `ncorrect`
* Label: `Number of words recalled immediately`
* Categories:
    + `Continuous Variable 0-65`
* Missings
   + `-1 = Not applicable` 


```{r local w4, echo=FALSE}
ELSA_w4_cog_proc <- ELSA_w4
vari <- ELSA_w4_cog_proc$ncorrect
kable(Continuous_summary(var = vari, missing_values = c(-1))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = -1)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = -1)$summary, caption = "Summary")
ggplot(ELSA_w4_cog_proc, aes(x=(ncorrect))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Processing speed") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_proc_c` from the study-specific variable the missing values have to be recoded as follows:

* `-1 Not applicable into 996`
* `NA into 999`

To compute the harmonized variable `cog_proc` from `cog_proc_c` it has to be recoded as follows:

* `cog_proc_c <=25% into 0`
* `cog_proc_c >25% into 1`

**R script:**

```{r harmo w4}
#cog_proc_c
ELSA_ds_w4 <- tibble(id=ELSA_w4_cog_proc$id)
ELSA_ds_w4$cog_proc_c <- car::recode(ELSA_w4_cog_proc$ncorrect, "-1=996; NA=999")
ELSA_ds_w4$cog_proc_c <- labelled(ELSA_ds_w4$cog_proc_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(ELSA_ds_w4$cog_proc_c, "999=NA; 996=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

ELSA_ds_w4$cog_proc <- car::recode(ELSA_ds_w4[[2]], "0:Q=0; (Q+1):65=1")
ELSA_ds_w4$cog_proc <- labelled(ELSA_ds_w4[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w4, echo=FALSE}
vari <- ELSA_ds_w4$cog_proc_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w4, aes(x=(cog_proc_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Processing speed") + ylab("Frequency") + xlim(0,60)

vari <- ELSA_ds_w4$cog_proc
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w4, aes(x=factor(cog_proc))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Processing speed") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w4, echo=FALSE}
Continous <- c(sum(na.omit(ELSA_ds_w4[[2]])<=Q), sum(na.omit(ELSA_ds_w4[[2]])>Q & na.omit(ELSA_ds_w4[[2]])<900), sum(na.omit(ELSA_ds_w4[[2]])==996))
Dicotomic <- table(ELSA_ds_w4[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:16->0","17:65->1", "-1->996") 
kable(C, caption = "Continuous vs Dichotomous")
```


<!--- #### Import to OPAL -->
```{r importOPAL_w4, echo=FALSE}
#opal.assign.data(o, 'ELSA_ds_w4', ELSA_ds_w4)
#opal.symbol_import(o,'ELSA_ds_w4', project='_Athlos_Harm_Dataset')

label(ELSA_ds_w4$cog_proc_c) <- ds_label_cog_proc_c
label(ELSA_ds_w4$cog_proc) <- ds_label_cog_proc
cog_proc <- ELSA_ds_w4
save(cog_proc, file = "../RData/w4/cog_proc.RData")
```


### Wave 5 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `Ncorrect`
* Label: `Number of words recalled immediately`
* Categories:
    + `Continuous Variable 0-65`
* Missings
   + `-3 = Interview/data error` 
   + `-1 = Not applicable` 


```{r local w5, echo=FALSE}
ELSA_w5_cog_proc <- ELSA_w5
vari <- ELSA_w5_cog_proc$Ncorrect
kable(Continuous_summary(var = vari, missing_values = c(-1))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = -1)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = -1)$summary, caption = "Summary")
ggplot(ELSA_w5_cog_proc, aes(x=factor(NCorrect))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Processing speed") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_proc_c` from the study-specific variable the missing values have to be recoded as follows:

* `-1 Not applicable into 996`
* `-3 Interview/data error into 991`
* `NA into 999`

To compute the harmonized variable `cog_proc` from `cog_proc_c` it has to be recoded as follows:

* `cog_proc_c <=25% into 0`
* `cog_proc_c >25% into 1`

**R script:**

```{r harmo w5}
#cog_proc_c
ELSA_ds_w5 <- tibble(id=ELSA_w5_cog_proc$id)
ELSA_ds_w5$cog_proc_c <- car::recode(ELSA_w5_cog_proc$NCorrect, "-1=996; -3=991; NA=999")
ELSA_ds_w5$cog_proc_c <- labelled(ELSA_ds_w5$cog_proc_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(ELSA_ds_w5$cog_proc_c, "999=NA; 996=NA; 991=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

ELSA_ds_w5$cog_proc <- car::recode(ELSA_ds_w5[[2]], "0:Q=0; (Q+1):65=1")
ELSA_ds_w5$cog_proc <- labelled(ELSA_ds_w5[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w5, echo=FALSE}
vari <- ELSA_ds_w5$cog_proc_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w5, aes(x=(cog_proc_c))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Processing speed") + ylab("Frequency") + xlim(0,60)

vari <- ELSA_ds_w5$cog_proc
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w5, aes(x=factor(cog_proc))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Processing speed") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w5, echo=FALSE}
Continous <- c(sum(na.omit(ELSA_ds_w5[[2]])<=Q), sum(na.omit(ELSA_ds_w5[[2]])>Q & na.omit(ELSA_ds_w5[[2]])<900), sum(na.omit(ELSA_ds_w5[[2]])==991),  sum(na.omit(ELSA_ds_w5[[2]])==996))
Dicotomic <- table(ELSA_ds_w5[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:15->0","16:65->1","-3->991", "-1->996") 
kable(C, caption = "Continuous vs Dichotomous")
```


<!--- #### Import to OPAL -->
```{r importOPAL_w5, echo=FALSE}
#opal.assign.data(o, 'ELSA_ds_w5', ELSA_ds_w5)
#opal.symbol_import(o,'ELSA_ds_w5', project='_Athlos_Harm_Dataset')

label(ELSA_ds_w5$cog_proc_c) <- ds_label_cog_proc_c
label(ELSA_ds_w5$cog_proc) <- ds_label_cog_proc
cog_proc <- ELSA_ds_w5
save(cog_proc, file = "../RData/w5/cog_proc.RData")
```



### Wave 6

Not collected at wave 6. 



### Wave 7 

Not collected at wave 7. 


# Quality estimation

No comments

[Comments on the quality of the new harmonised variable. This section can be done in a later stage, once all variables are harmonised.]


<!--- #### Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
