---
title: "Delayed recall"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")

# Loading local datasets of ELSA and domain health status:
load("ELSA_w1.rdata")
load("ELSA_w2.rdata")
load("ELSA_w3.rdata")
load("ELSA_w4.rdata")
load("ELSA_w5.rdata")
load("ELSA_w6.rdata")
load("ELSA_w7.rdata")
```


# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `cog_del_c`
* Variable label: `Cognition - delayed recall - Continuous`
* Variable description: `Delayed recall of a list previously employed for measuring Immediate recall. The number of words is exactly the same as in the study-specific variable`
* Domain: `Health status and functional limitations`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


* Short name: `cog_del`
* Variable label: `Cognition - delayed recall`
* Variable description: `Delayed recall of a list of common nouns. Discrete variable: value 0 = <=25%; value 1 = >25%.`
* Domain: `Health status and functional limitations`
* Value type: `Categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | <=25%
1        | >25%

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Delayed recall"
ds_label_cog_del_c <- "Delayed recall of a list previously employed for measuring Immediate recall. The number of words is exactly the same as in the study-specific variable"
ds_label_cog_del <- "Delayed recall of a list of common nouns. Discrete variable: value 0 = <=25%; value 1 = >25%"
```

# Data process

## England

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `cflisd`
* Label: `Record number of words correctly remembered after delay here.`
* Categories:
    + `Continuous Variable 0-10`
* Missings
   + `-9 = Refusal` 
   + `-8 = Don't know` 
   + `-1 = Not applicable` 

```{r local w1, echo=FALSE}
ELSA_w1_cog_del <- ELSA_w1

vari <- ELSA_w1_cog_del$cflisd
kable(Continuous_summary(var = vari, missing_values = c(-1,-8,-9))[3], caption = "Delayed recall continuous")
kable(Continuous_summary(vari, missing_values = c(-1,-8,-9))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-1,-8,-9))$summary, caption = "Summary")
ggplot(ELSA_w1_cog_del, aes(x=factor(cflisd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable `cog_del_c` from the study-specific variables you have to sum the total of words and the missing values have to be recoded as follows:

* `-9 Refusal into 997` 
* `-8 Don't know into 998`
* `-1 Not applicable into 996`
* `NA into 999`

To compute the harmonized variable `cog_del` from `cog_del_c` it has to be recoded as follows:

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**

```{r harmo w1}
##cog_del_c
ELSA_ds_w1 <- tibble(id=ELSA_w1_cog_del$id)
ELSA_ds_w1$cog_del_c <- car::recode(ELSA_w1_cog_del$cflisd, "-9 = '997';-8 = '998';-1 = '996' ")
ELSA_ds_w1$cog_del_c <- labelled(ELSA_ds_w1$cog_del_c, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))

##cog_del
Q <- quantile(car::recode(ELSA_ds_w1$cog_del_c, "999=NA;996=NA;997=NA;998=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

ELSA_ds_w1$cog_del <- car::recode(ELSA_ds_w1[[2]], "0:Q=0; (Q+1):10=1")
ELSA_ds_w1$cog_del <- labelled(ELSA_ds_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=FALSE}
vari <- ELSA_ds_w1$cog_del_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Delayed recall continuous")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w1, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("cog_del") + ylab("Frequency")

vari <- ELSA_ds_w1$cog_del
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Delayed recall categorical") 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w1, aes(x=factor(cog_del))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=FALSE}
Continous <- c(sum(na.omit(ELSA_ds_w1[[2]])<=Q), sum(na.omit(ELSA_ds_w1[[2]])>Q & na.omit(ELSA_ds_w1[[2]])<900), sum(na.omit(ELSA_ds_w1[[2]])==996), sum(na.omit(ELSA_ds_w1[[2]])==997), sum(na.omit(ELSA_ds_w1[[2]])==998))
Dicotomic <- table(ELSA_ds_w1[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:3->0","4:10->1","-1->996", "-9->997", "-8->998") 
kable(C, caption = "Continuous vs Dichotomous")
```


<!--- #### Import to OPAL -->
```{r importOPAL_w1, echo=FALSE}
label(ELSA_ds_w1$cog_del_c) <- ds_label_cog_del_c
label(ELSA_ds_w1$cog_del) <- ds_label_cog_del
#opal.assign.data(o, 'ELSA_ds_w1', ELSA_ds_w1)
#opal.symbol_import(o,'ELSA_ds_w1', project='_Athlos_Harm_Dataset')
cog_del <- ELSA_ds_w1
save(cog_del, file = "../RData/w1/cog_del.RData")
rm(cog_del)

ELSA_m_ds_w1 <- ELSA_ds_w1
ELSA_m_ds_w1$cog_del <- car::recode(ELSA_m_ds_w1$cog_del, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w1', ELSA_m_ds_w1)
ELSA_m_ds_w1$cog_del_c <- car::recode(ELSA_m_ds_w1$cog_del_c, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w1', ELSA_m_ds_w1)
#opal.symbol_import(o,'ELSA_m_ds_w1', project='_Athlos_Harm_Dataset')
```


### Wave 2 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `CfLisD`
* Label: `Number of words recalled after a delay`
* Categories:
    + `Continuous Variable 0-10`
* Missings
   + `-9 = Refusal` 
   + `-8 = Don't know` 
   + `-1 = Not applicable` 


```{r local w2, echo=FALSE}
ELSA_w2_cog_del <- ELSA_w2

vari <- ELSA_w2_cog_del$CfLisD
kable(Continuous_summary(var = vari, missing_values = c(-9,-8,-1))[3], caption = "Immediate recall continuous")
kable(Continuous_summary(vari, missing_values = c(-9,-8,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-9,-8,-1))$summary, caption = "Summary")
ggplot(ELSA_w2_cog_del, aes(x=factor(CfLisD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable `cog_del_c` from the study-specific variables you have to sum the total of words and the missing values have to be recoded as follows:

* `-9 Refusal into 997` 
* `-8 Don't know into 998`
* `-1 Not applicable into 996`
* `NA into 999`

To compute the harmonized variable `cog_del` from `cog_del_c` it has to be recoded as follows:

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**

```{r harmo w2}
##cog_del_c
ELSA_ds_w2 <- tibble(id=ELSA_w2_cog_del$id)
ELSA_ds_w2$cog_del_c <- car::recode(ELSA_w2_cog_del$CfLisD, "-9 = 997; -8 = 998; -1 = 996")
ELSA_ds_w2$cog_del_c <- labelled(ELSA_ds_w2$cog_del_c, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))

##cog_del
Q <- quantile(car::recode(ELSA_ds_w2$cog_del_c, "999=NA;997=NA;996=NA;998=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

ELSA_ds_w2$cog_del <- car::recode(ELSA_ds_w2[[2]], "0:Q=0; (Q+1):10=1")
ELSA_ds_w2$cog_del <- labelled(ELSA_ds_w2[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=FALSE}
vari <- ELSA_ds_w2$cog_del_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Immediate recall continuous")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w2, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- ELSA_ds_w2$cog_del
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Cognition - Immediate recall")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w2, aes(x=factor(cog_del))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=FALSE}
Continous <- c(sum(na.omit(ELSA_ds_w2[[2]])<=Q), sum(na.omit(ELSA_ds_w2[[2]])>Q & na.omit(ELSA_ds_w2[[2]])<900), sum(na.omit(ELSA_ds_w2[[2]])==996), sum(na.omit(ELSA_ds_w2[[2]])==997), sum(na.omit(ELSA_ds_w2[[2]])==998))
Dicotomic <- table(ELSA_ds_w2[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:3->0","4:10->1","-1->996", "-9->997", "-8->998") 
kable(C, caption = "Continuous vs Dichotomous")
```


<!--- #### Import to OPAL -->
```{r importOPAL_w2, echo=FALSE}
label(ELSA_ds_w2$cog_del_c) <- ds_label_cog_del_c
label(ELSA_ds_w2$cog_del) <- ds_label_cog_del
#opal.assign.data(o, 'ELSA_ds_w2', ELSA_ds_w2)
#opal.symbol_import(o,'ELSA_ds_w2', project='_Athlos_Harm_Dataset')
cog_del <- ELSA_ds_w2
save(cog_del, file = "../RData/w2/cog_del.RData")
rm(cog_del)

ELSA_m_ds_w2 <- ELSA_ds_w2
ELSA_m_ds_w2$cog_del_c <- car::recode(ELSA_m_ds_w2$cog_del, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
ELSA_m_ds_w2$cog_del_c <- car::recode(ELSA_m_ds_w2$cog_del, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w2', ELSA_m_ds_w2)
#opal.symbol_import(o,'ELSA_m_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `cflisd`
* Label: `Number of words recalled after a delay`
* Categories:
    + `Continuous Variable 0-10`
* Missings
   + `-9 = Refusal` 
   + `-1 = Not applicable` 


```{r local w3, echo=FALSE}
ELSA_w3_cog_del <- ELSA_w3

vari <- ELSA_w3_cog_del$cflisd
kable(Continuous_summary(var = vari, missing_values = c(-9,-1))[3], caption = "Immediate recall continuous")
kable(Continuous_summary(vari, missing_values = c(-9,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-9,-1))$summary, caption = "Summary")
ggplot(ELSA_w3_cog_del, aes(x=factor(cflisd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable `cog_del_c` from the study-specific variables you have to sum the total of words and the missing values have to be recoded as follows:

* `-9 Refusal into 997` 
* `-1 Not applicable into 996`
* `NA into 999`

To compute the harmonized variable `cog_del` from `cog_del_c` it has to be recoded as follows:

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**

```{r harmo w3}
##cog_del_c
ELSA_ds_w3 <- tibble(id=ELSA_w3_cog_del$id)
ELSA_ds_w3$cog_del_c <- car::recode(ELSA_w3_cog_del$cflisd, "-9 = 997; -1 = 996")
ELSA_ds_w3$cog_del_c <- labelled(ELSA_ds_w3$cog_del_c, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))

##cog_del
Q <- quantile(car::recode(ELSA_ds_w3$cog_del_c, "999=NA;997=NA;996=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

ELSA_ds_w3$cog_del <- car::recode(ELSA_ds_w3[[2]], "0:Q=0; (Q+1):10=1")
ELSA_ds_w3$cog_del <- labelled(ELSA_ds_w3[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=FALSE}
vari <- ELSA_ds_w3$cog_del_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Immediate recall continuous")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w3, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- ELSA_ds_w3$cog_del
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Cognition - Immediate recall")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w3, aes(x=factor(cog_del))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=FALSE}
Continous <- c(sum(na.omit(ELSA_ds_w3[[2]])<=Q), sum(na.omit(ELSA_ds_w3[[2]])>Q & na.omit(ELSA_ds_w3[[2]])<900), sum(na.omit(ELSA_ds_w3[[2]])==996), sum(na.omit(ELSA_ds_w3[[2]])==997))
Dicotomic <- table(ELSA_ds_w3[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:3->0","4:10->1","-1->996", "-9->997") 
kable(C, caption = "Continuous vs Dichotomous")
```


<!--- #### Import to OPAL -->
```{r importOPAL_w3, echo=FALSE}
label(ELSA_ds_w3$cog_del_c) <- ds_label_cog_del_c
label(ELSA_ds_w3$cog_del) <- ds_label_cog_del
#opal.assign.data(o, 'ELSA_ds_w3', ELSA_ds_w3)
#opal.symbol_import(o,'ELSA_ds_w3', project='_Athlos_Harm_Dataset')
cog_del <- ELSA_ds_w3
save(cog_del, file = "../RData/w3/cog_del.RData")
rm(cog_del)

ELSA_m_ds_w3 <- ELSA_ds_w3
ELSA_m_ds_w3$cog_del <- car::recode(ELSA_m_ds_w3$cog_del, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
ELSA_m_ds_w3$cog_del_c <- car::recode(ELSA_m_ds_w3$cog_del_c, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w3', ELSA_m_ds_w3)
#opal.symbol_import(o,'ELSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```


### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `cflisd`
* Label: `Number of words recalled after a delay`
* Categories:
    + `Continuous Variable 0-10`
* Missings
   + `-9 = Refusal` 
   + `-1 = Not applicable` 

```{r local w4, echo=FALSE}
ELSA_w4_cog_del <- ELSA_w4

vari <- ELSA_w4_cog_del$cflisd
kable(Continuous_summary(var = vari, missing_values = c(-9,-1))[3], caption = "Immediate recall continuous")
kable(Continuous_summary(vari, missing_values = c(-9,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-9,-1))$summary, caption = "Summary")
ggplot(ELSA_w4_cog_del, aes(x=factor(cflisd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable `cog_del_c` from the study-specific variables you have to sum the total of words and the missing values have to be recoded as follows:

* `-9 Refusal into 997` 
* `-1 Not applicable into 996`
* `NA into 999`

To compute the harmonized variable `cog_del` from `cog_del_c` it has to be recoded as follows:

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**

```{r harmo w4}
##cog_del_c
ELSA_ds_w4 <- tibble(id=ELSA_w4_cog_del$id)
ELSA_ds_w4$cog_del_c <- car::recode(ELSA_w4_cog_del$cflisd, "-9 = 997; -1 = 996")
ELSA_ds_w4$cog_del_c <- labelled(ELSA_ds_w4$cog_del_c, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))

##cog_del
Q <- quantile(car::recode(ELSA_ds_w4$cog_del_c, "999=NA;997=NA;996=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

ELSA_ds_w4$cog_del <- car::recode(ELSA_ds_w4[[2]], "0:Q=0; (Q+1):10=1")
ELSA_ds_w4$cog_del <- labelled(ELSA_ds_w4[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w4, echo=FALSE}
vari <- ELSA_ds_w4$cog_del_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Immediate recall continuous")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w4, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- ELSA_ds_w4$cog_del
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Cognition - Immediate recall")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w4, aes(x=factor(cog_del))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w4, echo=FALSE}
Continous <- c(sum(na.omit(ELSA_ds_w4[[2]])<=Q), sum(na.omit(ELSA_ds_w4[[2]])>Q & na.omit(ELSA_ds_w4[[2]])<900), sum(na.omit(ELSA_ds_w4[[2]])==996), sum(na.omit(ELSA_ds_w4[[2]])==997))
Dicotomic <- table(ELSA_ds_w4[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:3->0","4:10->1","-1->996", "-9->997") 
kable(C, caption = "Continuous vs Dichotomous")
```


<!--- #### Import to OPAL -->
```{r importOPAL_w4, echo=FALSE}
label(ELSA_ds_w4$cog_del_c) <- ds_label_cog_del_c
label(ELSA_ds_w4$cog_del) <- ds_label_cog_del
#opal.assign.data(o, 'ELSA_ds_w4', ELSA_ds_w4)
#opal.symbol_import(o,'ELSA_ds_w4', project='_Athlos_Harm_Dataset')
cog_del <- ELSA_ds_w4
save(cog_del, file = "../RData/w4/cog_del.RData")
rm(cog_del)

ELSA_m_ds_w4 <- ELSA_ds_w4
ELSA_m_ds_w4$cog_del <- car::recode(ELSA_m_ds_w4$cog_del, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
ELSA_m_ds_w4$cog_del_c <- car::recode(ELSA_m_ds_w4$cog_del_c, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w4', ELSA_m_ds_w4)
#opal.symbol_import(o,'ELSA_m_ds_w4', project='_Athlos_Harm_Dataset')
```


### Wave 5 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `cflisd`
* Label: `Number of words recalled after a delay`
* Categories:
    + `Continuous Variable 0-10`
* Missings
   + `-9 = Refusal` 
   + `-1 = Not applicable` 


```{r local w5, echo=FALSE}
ELSA_w5_cog_del <- ELSA_w5

vari <- ELSA_w5_cog_del$cflisd
kable(Continuous_summary(var = vari, missing_values = c(-9,-1))[3], caption = "Immediate recall continuous")
kable(Continuous_summary(vari, missing_values = c(-9,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-9,-1))$summary, caption = "Summary")
ggplot(ELSA_w5_cog_del, aes(x=factor(cflisd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable `cog_del_c` from the study-specific variables you have to sum the total of words and the missing values have to be recoded as follows:

* `-9 Refusal into 997` 
* `-1 Not applicable into 996`
* `NA into 999`

To compute the harmonized variable `cog_del` from `cog_del_c` it has to be recoded as follows:

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**

```{r harmo w5}
##cog_del_c
ELSA_ds_w5 <- tibble(id=ELSA_w5_cog_del$id)
ELSA_ds_w5$cog_del_c <- car::recode(ELSA_w5_cog_del$cflisd, "-9 = 997;-1 = 996")
ELSA_ds_w5$cog_del_c <- labelled(ELSA_ds_w5$cog_del_c, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))

##cog_del
Q <- quantile(car::recode(ELSA_ds_w5$cog_del_c, "999=NA;997=NA;996=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

ELSA_ds_w5$cog_del <- car::recode(ELSA_ds_w5[[2]], "0:Q=0; (Q+1):10=1")
ELSA_ds_w5$cog_del <- labelled(ELSA_ds_w5[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w5, echo=FALSE}
vari <- ELSA_ds_w5$cog_del_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Immediate recall continuous")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w5, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- ELSA_ds_w5$cog_del
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Cognition - Immediate recall")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w5, aes(x=factor(cog_del))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w5, echo=FALSE}
Continous <- c(sum(na.omit(ELSA_ds_w5[[2]])<=Q), sum(na.omit(ELSA_ds_w5[[2]])>Q & na.omit(ELSA_ds_w5[[2]])<900), sum(na.omit(ELSA_ds_w5[[2]])==996), sum(na.omit(ELSA_ds_w5[[2]])==997))
Dicotomic <- table(ELSA_ds_w5[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:3->0","4:10->1","-1->996", "-9->997") 
kable(C, caption = "Continuous vs Dichotomous")
```


<!--- #### Import to OPAL -->
```{r importOPAL_w5, echo=FALSE}
label(ELSA_ds_w5$cog_del_c) <- ds_label_cog_del_c
label(ELSA_ds_w5$cog_del) <- ds_label_cog_del
#opal.assign.data(o, 'ELSA_ds_w5', ELSA_ds_w5)
#opal.symbol_import(o,'ELSA_ds_w5', project='_Athlos_Harm_Dataset')
cog_del <- ELSA_ds_w5
save(cog_del, file = "../RData/w5/cog_del.RData")
rm(cog_del)

ELSA_m_ds_w5 <- ELSA_ds_w5
ELSA_m_ds_w5$cog_del <- car::recode(ELSA_m_ds_w5$cog_del, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
ELSA_m_ds_w5$cog_del_c <- car::recode(ELSA_m_ds_w5$cog_del_c, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w5', ELSA_m_ds_w5)
#opal.symbol_import(o,'ELSA_m_ds_w5', project='_Athlos_Harm_Dataset')
```



### Wave 6 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `CfLisD`
* Label: `Number of words recalled after a delay`
* Categories:
    + `Continuous Variable 0-10`
* Missings
   + `-9 = Refusal` 
   + `-1 = Not applicable` 


```{r local w6, echo=FALSE}
ELSA_w6_cog_del <- ELSA_w6

vari <- ELSA_w6_cog_del$CfLisD
kable(Continuous_summary(var = vari, missing_values = c(-9,-1))[3], caption = "Immediate recall continuous")
kable(Continuous_summary(vari, missing_values = c(-9,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-9,-1))$summary, caption = "Summary")
ggplot(ELSA_w6_cog_del, aes(x=factor(CfLisD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable `cog_del_c` from the study-specific variables you have to sum the total of words and the missing values have to be recoded as follows:

* `-9 Refusal into 997` 
* `-1 Not applicable into 996`
* `NA into 999`

To compute the harmonized variable `cog_del` from `cog_del_c` it has to be recoded as follows:

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**

```{r harmo w6}
##cog_del_c
ELSA_ds_w6 <- tibble(id=ELSA_w6_cog_del$id)
ELSA_ds_w6$cog_del_c <- car::recode(ELSA_w6_cog_del$CfLisD, "-9 = 997;-1 = 996")
ELSA_ds_w6$cog_del_c <- labelled(ELSA_ds_w6$cog_del_c, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))

##cog_del
Q <- quantile(car::recode(ELSA_ds_w6$cog_del_c, "999=NA;997=NA;996=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

ELSA_ds_w6$cog_del <- car::recode(ELSA_ds_w6[[2]], "0:Q=0; (Q+1):10=1")
ELSA_ds_w6$cog_del <- labelled(ELSA_ds_w6[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w6, echo=FALSE}
vari <- ELSA_ds_w6$cog_del_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Immediate recall continuous")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w6, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- ELSA_ds_w6$cog_del
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Cognition - Immediate recall")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w6, aes(x=factor(cog_del))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w6, echo=FALSE}
Continous <- c(sum(na.omit(ELSA_ds_w6[[2]])<=Q), sum(na.omit(ELSA_ds_w6[[2]])>Q & na.omit(ELSA_ds_w6[[2]])<900), sum(na.omit(ELSA_ds_w6[[2]])==996), sum(na.omit(ELSA_ds_w6[[2]])==997))
Dicotomic <- table(ELSA_ds_w6[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:4->0","5:10->1","-1->996", "-9->997") 
kable(C, caption = "Continuous vs Dichotomous")
```


<!--- #### Import to OPAL -->
```{r importOPAL_w6, echo=FALSE}
label(ELSA_ds_w6$cog_del_c) <- ds_label_cog_del_c
label(ELSA_ds_w6$cog_del) <- ds_label_cog_del
#opal.assign.data(o, 'ELSA_ds_w6', ELSA_ds_w6)
#opal.symbol_import(o,'ELSA_ds_w6', project='_Athlos_Harm_Dataset')
cog_del <- ELSA_ds_w6
save(cog_del, file = "../RData/w6/cog_del.RData")
rm(cog_del)

ELSA_m_ds_w6 <- ELSA_ds_w6
ELSA_m_ds_w6$cog_del <- car::recode(ELSA_m_ds_w6$cog_del, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
ELSA_m_ds_w6$cog_del_c <- car::recode(ELSA_m_ds_w6$cog_del_c, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w6', ELSA_m_ds_w6)
#opal.symbol_import(o,'ELSA_m_ds_w6', project='_Athlos_Harm_Dataset')
```



### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:

* Name: `CfLisD`
* Label: `Number of words recalled after a delay`
* Categories:
    + `Continuous Variable 0-10`
* Missings
   + `-9 = Refusal` 
   + `-1 = Not applicable` 


```{r local w7, echo=FALSE}
ELSA_w7_cog_del <- ELSA_w7

vari <- ELSA_w7_cog_del$CfLisD
kable(Continuous_summary(var = vari, missing_values = c(-9,-1))[3], caption = "Immediate recall continuous")
kable(Continuous_summary(vari, missing_values = c(-9,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-9,-1))$summary, caption = "Summary")
ggplot(ELSA_w7_cog_del, aes(x=factor(CfLisD))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonized variable `cog_del_c` from the study-specific variables you have to sum the total of words and the missing values have to be recoded as follows:

* `-9 Refusal into 997` 
* `-1 Not applicable into 996`
* `NA into 999`

To compute the harmonized variable `cog_del` from `cog_del_c` it has to be recoded as follows:

* `cog_del_c <=25% into 0`
* `cog_del_c >25% into 1`

**R script**

```{r harmo w7}
##cog_del_c
ELSA_ds_w7 <- tibble(id=ELSA_w7_cog_del$id)
ELSA_ds_w7$cog_del_c <- car::recode(ELSA_w7_cog_del$CfLisD, "-9 = '997';-8 = '998';-1 = '996' ")
ELSA_ds_w7$cog_del_c <- labelled(ELSA_ds_w7$cog_del_c, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))

##cog_del
Q <- quantile(car::recode(ELSA_ds_w7$cog_del_c, "999=NA;997=NA;996=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

ELSA_ds_w7$cog_del <- car::recode(ELSA_ds_w7[[2]], "0:Q=0; (Q+1):10=1")
ELSA_ds_w7$cog_del <- labelled(ELSA_ds_w7[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w7, echo=FALSE}
vari <- ELSA_ds_w7[[2]]
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Immediate recall continuous")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w7, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- ELSA_ds_w7[[3]]
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "Cognition - Immediate recall")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w7, aes(x=factor(cog_del))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Delayed recall") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w7, echo=FALSE}
Continous <- c(sum(na.omit(ELSA_ds_w7[[2]])<=Q), sum(na.omit(ELSA_ds_w7[[2]])>Q & na.omit(ELSA_ds_w7[[2]])<900), sum(na.omit(ELSA_ds_w7[[2]])==996), sum(na.omit(ELSA_ds_w7[[2]])==997))
Dicotomic <- table(ELSA_ds_w7[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:3->0","4:10->1","-1->996", "-9->997") 
kable(C, caption = "Continuous vs Dichotomous")
```


<!--- #### Import to OPAL -->
```{r importOPAL_w7, echo=FALSE}
label(ELSA_ds_w7$cog_del_c) <- ds_label_cog_del_c
label(ELSA_ds_w7$cog_del) <- ds_label_cog_del
#opal.assign.data(o, 'ELSA_ds_w7', ELSA_ds_w7)
#opal.symbol_import(o,'ELSA_ds_w7', project='_Athlos_Harm_Dataset')
cog_del <- ELSA_ds_w7
save(cog_del, file = "../RData/w7/cog_del.RData")
rm(cog_del)

ELSA_m_ds_w7 <- ELSA_ds_w7
ELSA_m_ds_w7$cog_del <- car::recode(ELSA_m_ds_w7$cog_del, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
ELSA_m_ds_w7$cog_del_c <- car::recode(ELSA_m_ds_w7$cog_del_c, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w7', ELSA_m_ds_w7)
#opal.symbol_import(o,'ELSA_m_ds_w7', project='_Athlos_Harm_Dataset')
```


### Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.


```{r summ, echo=FALSE}
ELSA_ds_w1$cog_del_c <- labelled(ELSA_ds_w1$cog_del_c, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w2$cog_del_c <- labelled(ELSA_ds_w2$cog_del_c, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w3$cog_del_c <- labelled(ELSA_ds_w3$cog_del_c, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w4$cog_del_c <- labelled(ELSA_ds_w4$cog_del_c, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w5$cog_del_c <- labelled(ELSA_ds_w5$cog_del_c, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w6$cog_del_c <- labelled(ELSA_ds_w6$cog_del_c, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w7$cog_del_c <- labelled(ELSA_ds_w7$cog_del_c, labels = c(Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))

tt <-    frq(ELSA_ds_w1$cog_del_c)[[1]][,c(1:2,4)]
tt[4] <- frq(ELSA_ds_w2$cog_del_c)[[1]][,c(4)]
tt[5] <- frq(ELSA_ds_w3$cog_del_c)[[1]][,c(4)]
tt[6] <- frq(ELSA_ds_w4$cog_del_c)[[1]][,c(4)]
tt[7] <- frq(ELSA_ds_w5$cog_del_c)[[1]][,c(4)]
tt[8] <- frq(ELSA_ds_w6$cog_del_c)[[1]][,c(4)]
tt[9] <- frq(ELSA_ds_w7$cog_del_c)[[1]][,c(4)]
tt[13,] <- c("n", "sample size", 
             length(ELSA_ds_w1$cog_del_c), length(ELSA_ds_w2$cog_del_c), length(ELSA_ds_w3$cog_del_c),
             length(ELSA_ds_w4$cog_del_c), length(ELSA_ds_w5$cog_del_c), length(ELSA_ds_w6$cog_del_c),     
             length(ELSA_ds_w7$cog_del_c))
names(tt)<-c("val", "label", "w1", "w2", "w3", "w4", "w5", "w6", "w7")
kable(tt)
```





# Quality estimation

No comments

[Comments on the quality of the new harmonised variable. This section can be done in a later stage, once all variables are harmonised.]



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
