---
title: "Recent falls"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_laia.r")

# Loading local datasets of ELSA and domain health status:
load("ELSA_w1.rdata")
load("ELSA_w2.rdata")
load("ELSA_w3.rdata")
load("ELSA_w4.rdata")
load("ELSA_w5.rdata")
load("ELSA_w6.rdata")
load("ELSA_w7.rdata")
```



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `recent_falls`
* Variable label: `Recent falls in the last 6-24 months`
* Variable description: `Recent falls in the last 6-24 months`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Recent falls"
ds_label_all <- "Recent falls in the last 6-24 months"
```


# Data process

## ELSA

### Wave 1

#### Study-specific variable description


The study-specific variables elected to be harmonised is:


* Name: `hefla`
* Label: `Have you fallen down in the last two years (for any reason)?`
* Categories:
   + `1 = Yes`
   + `2 = No`
* Missings
   + `-9 = Refusal` 
   + `-8 = Don't know` 
   + `-1 = Not applicable` 

```{r local w1, echo=FALSE}
ELSA_w1_recent_falls <- ELSA_w1
vari <- ELSA_w1_recent_falls$hefla
kable(Categorical_summary(vari, missing_values = c(-9,-8))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-9,-8))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8))[2], caption = "Type of missing")
ggplot(ELSA_w1_recent_falls, aes(x=factor(hefla))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2 into 0` 
* `-9 Refusal into 997` 
* `-8 Don't know into 998`
* `-1 Not applicable into 996`

**R script:**

```{r harmo w1}
ELSA_ds_w1 <- tibble(id=ELSA_w1_recent_falls$id)
ELSA_ds_w1$recent_falls <- recode(ELSA_w1_recent_falls$hefla, "2 = '0';-9 = '997';-8 = '998';-1 = '996' ")
ELSA_ds_w1$recent_falls <- labelled(ELSA_ds_w1$recent_falls, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=FALSE}
vari <- ELSA_ds_w1$recent_falls
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w1, aes(x=factor(recent_falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=FALSE}
AfterH <- table(ELSA_ds_w1$recent_falls)
X<-table(ELSA_w1_recent_falls$hefla)
BeforeH <- X[c(5,4,3,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1","-1->996","-9->997","-8->998") 
kable(C)
```

```{r importOPAL_w1, echo=FALSE}
label(ELSA_ds_w1$recent_falls) <- "Recent falls in the last 6-24 months"
recent_falls <- ELSA_ds_w1
save(recent_falls, file = "../RData/w1/recent_falls.RData")
#opal.assign.data(o, 'ELSA_ds_w1', ELSA_ds_w1)
#opal.symbol_import(o,'ELSA_ds_w1', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w1 <- ELSA_ds_w1
ELSA_m_ds_w1$recent_falls <- recode(ELSA_m_ds_w1$recent_falls, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w1', ELSA_m_ds_w1)
#opal.symbol_import(o,'ELSA_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2

#### Study-specific variable description


The study-specific variables elected to be harmonised is:


* Name: `hefla`
* Label: `Whether fallen down`
* Categories:
   + `1 = Yes`
   + `2 = No`
* Missings
   + `-9 = Refusal` 
   + `-8 = Don't know` 
   + `-1 = Not applicable` 


```{r local w2, echo=FALSE}
ELSA_w2_recent_falls <- ELSA_w2
vari <- ELSA_w2_recent_falls$HeFla
kable(Categorical_summary(vari, missing_values = c(-1,-9,-8))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-1,-9,-8))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-9,-8))[2], caption = "Type of missing")
ggplot(ELSA_w2_recent_falls, aes(x=factor(HeFla))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2 into 0` 
* `-9 Refusal into 997` 
* `-8 Don't know into 998`
* `-1 Not applicable into 996`

**R script:**

```{r harmo w2}
ELSA_ds_w2 <- tibble(id=ELSA_w2_recent_falls$id)
ELSA_ds_w2$recent_falls <- recode(ELSA_w2_recent_falls$HeFla, "2 = '0';-9 = '997';-8 = '998';-1 = '996' ")
ELSA_ds_w2$recent_falls <- labelled(ELSA_ds_w2$recent_falls, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=FALSE}
vari <- ELSA_ds_w2$recent_falls
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w2, aes(x=factor(recent_falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=FALSE}
AfterH <- table(ELSA_ds_w2$recent_falls)
X<-table(ELSA_w2_recent_falls$HeFla)
BeforeH <- X[c(5,4,3,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1","-1->996","-9->997","-8->998") 
kable(C)
```

<!--- #### Import to OPAL -->
```{r importOPAL_w2, echo=FALSE}
label(ELSA_ds_w2$recent_falls) <- "Recent falls in the last 6-24 months"
recent_falls <- ELSA_ds_w2
save(recent_falls, file = "../RData/w2/recent_falls.RData")
#opal.assign.data(o, 'ELSA_ds_w2', ELSA_ds_w2)
#opal.symbol_import(o,'ELSA_ds_w2', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w2 <- ELSA_ds_w2
ELSA_m_ds_w2$recent_falls <- recode(ELSA_m_ds_w2$recent_falls, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w2', ELSA_m_ds_w2)
#opal.symbol_import(o,'ELSA_m_ds_w2', project='_Athlos_Harm_Dataset')
```



### Wave 3

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `hefla`
* Label: `Whether fallen down`
* Categories:
   + `1 = Yes`
   + `2 = No`
* Missings
   + `-8 = Don't know` 
   + `-1 = Not applicable` 


```{r local w3, echo=FALSE}
ELSA_w3_recent_falls <- ELSA_w3
vari <- ELSA_w3_recent_falls$hefla
kable(Categorical_summary(vari, missing_values = c(-1,-8))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-1,-8))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-8))[2], caption = "Type of missing")
ggplot(ELSA_w3_recent_falls, aes(x=factor(hefla))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2 into 0` 
* `-8 Don't know into 998`
* `-1 Not applicable into 996`

**R script:**

```{r harmo w3}
ELSA_ds_w3 <- tibble(id=ELSA_w3_recent_falls$id)
ELSA_ds_w3$recent_falls <- recode(ELSA_w3_recent_falls$hefla, "2 = '0';-9 = '997';-8 = '998';-1 = '996' ")
ELSA_ds_w3$recent_falls <- labelled(ELSA_ds_w3$recent_falls, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=FALSE}
vari <- ELSA_ds_w3$recent_falls
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w3, aes(x=factor(recent_falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=FALSE}
AfterH <- table(ELSA_ds_w3$recent_falls)
X<-table(ELSA_w3_recent_falls$hefla)
BeforeH <- X[c(4,3,2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1","-1->996","-8->998") 
kable(C)
```


<!--- #### Import to OPAL -->
```{r importOPAL_w3, echo=FALSE}
label(ELSA_ds_w3$recent_falls) <- "Recent falls in the last 6-24 months"
recent_falls <- ELSA_ds_w3
save(recent_falls, file = "../RData/w3/recent_falls.RData")
#opal.assign.data(o, 'ELSA_ds_w3', ELSA_ds_w3)
#opal.symbol_import(o,'ELSA_ds_w3', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w3 <- ELSA_ds_w3
ELSA_m_ds_w3$recent_falls <- recode(ELSA_m_ds_w3$recent_falls, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w3', ELSA_m_ds_w3)
#opal.symbol_import(o,'ELSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```

### Wave 4

#### Study-specific variable description


The study-specific variables elected to be harmonised is:


* Name: `hefla`
* Label: `Whether fallen down in the last year`
* Categories:
   + `1 = Yes`
   + `2 = No`
* Missings
   + `-8 = Don't know` 
   + `-1 = Not applicable` 


```{r local w4, echo=FALSE}
ELSA_w4_recent_falls <- ELSA_w4
vari <- ELSA_w4_recent_falls$hefla
kable(Categorical_summary(vari, missing_values = c(-1,-8))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-1,-8))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-1,-8))[2], caption = "Type of missing")
ggplot(ELSA_w4_recent_falls, aes(x=factor(hefla))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2 into 0` 
* `-8 Don't know into 998`
* `-1 Not applicable into 996`

**R script:**

```{r harmo w4}
ELSA_ds_w4 <- tibble(id=ELSA_w4_recent_falls$id)
ELSA_ds_w4$recent_falls <- recode(ELSA_w4_recent_falls$hefla, ";2 = '0';-9 = '997';-8 = '998';-1 = '996' ")
ELSA_ds_w4$recent_falls <- labelled(ELSA_ds_w4$recent_falls, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w4, echo=FALSE}
vari <- ELSA_ds_w4$recent_falls
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w4, aes(x=factor(recent_falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w4, echo=FALSE}
AfterH <- table(ELSA_ds_w4$recent_falls)
X<-table(ELSA_w4_recent_falls$hefla)
BeforeH <- X[c(4,3,2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1","-1->996","-8->998") 
kable(C)
```



<!--- #### Import to OPAL -->
```{r importOPAL_w4, echo=FALSE}
label(ELSA_ds_w4$recent_falls) <- "Recent falls in the last 6-24 months"
recent_falls <- ELSA_ds_w4
save(recent_falls, file = "../RData/w4/recent_falls.RData")
#opal.assign.data(o, 'ELSA_ds_w4', ELSA_ds_w4)
#opal.symbol_import(o,'ELSA_ds_w4', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w4 <- ELSA_ds_w4
ELSA_m_ds_w4$recent_falls <- recode(ELSA_m_ds_w4$recent_falls, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w4', ELSA_m_ds_w4)
#opal.symbol_import(o,'ELSA_m_ds_w4', project='_Athlos_Harm_Dataset')
```


### Wave 5

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `hefla`
* Label: `Whether fallen down`
* Categories:
   + `1 = Yes`
   + `2 = No`
* Missings
   + `-9 = Refusal` 
   + `-8 = Don't know` 
   + `-2 = Capi/Interviewer Error` 
   + `-1 = Not applicable` 


```{r local w5, echo=FALSE}
ELSA_w5_recent_falls <- ELSA_w5
vari <- ELSA_w5_recent_falls$hefla
kable(Categorical_summary(vari, missing_values = c(-9,-8, -2, -1))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-9,-8, -2, -1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8, -2, -1))[2], caption = "Type of missing")
ggplot(ELSA_w5_recent_falls, aes(x=factor(hefla))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2 into 0` 
* `-9 Refusal into 997` 
* `-8 Don't know into 998`
* `-2 Capi/Interviewer Error into 991`
* `-1 Not applicable into 996`

**R script:**

```{r harmo w5}
ELSA_ds_w5 <- tibble(id=ELSA_w5_recent_falls$id)
ELSA_ds_w5$recent_falls <- recode(ELSA_w5_recent_falls$hefla, "2 = '0';-9 = '997';-8 = '998';-2 = '991';-1 = '996' ")
ELSA_ds_w5$recent_falls <- labelled(ELSA_ds_w5$recent_falls, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w5, echo=FALSE}
vari <- ELSA_ds_w5$recent_falls
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w5, aes(x=factor(recent_falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w5, echo=FALSE}
AfterH <- table(ELSA_ds_w5$recent_falls)
X<-table(ELSA_w5_recent_falls$hefla)
BeforeH <- c(X[c(6,5,3,4,1,2)])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1","-2->991","-1->996","-9->997","-8->998") 
kable(C)
```


<!--- #### Import to OPAL -->
```{r importOPAL_w5, echo=FALSE}
label(ELSA_ds_w5$recent_falls) <- "Recent falls in the last 6-24 months"
recent_falls <- ELSA_ds_w5
save(recent_falls, file = "../RData/w5/recent_falls.RData")
#opal.assign.data(o, 'ELSA_ds_w5', ELSA_ds_w5)
#opal.symbol_import(o,'ELSA_ds_w5', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w5 <- ELSA_ds_w5
ELSA_m_ds_w5$recent_falls <- recode(ELSA_m_ds_w5$recent_falls, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w5', ELSA_m_ds_w5)
#opal.symbol_import(o,'ELSA_m_ds_w5', project='_Athlos_Harm_Dataset')
```


### Wave 1

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `HeFla`
* Label: `Whether fallen down`
* Categories:
   + `1 = Yes`
   + `2 = No`
* Missings
   + `-9 = Refusal` 
   + `-8 = Don't know` 
   + `-1 = Not applicable` 


```{r local w6, echo=FALSE}
ELSA_w6_recent_falls <- ELSA_w6
vari <- ELSA_w6_recent_falls$HeFla
kable(Categorical_summary(vari, missing_values = c(-9,-8, -1))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-9,-8, -1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8, -1))[2], caption = "Type of missing")
ggplot(ELSA_w6_recent_falls, aes(x=factor(HeFla))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2 into 0` 
* `-9 Refusal into 997` 
* `-8 Don't know into 998`
* `-1 Not applicable into 996`

**R script:**

```{r harmo w6}
ELSA_ds_w6 <- tibble(id=ELSA_w6_recent_falls$id)
ELSA_ds_w6$recent_falls <- recode(ELSA_w6_recent_falls$HeFla, ";2 = '0';-9 = '997';-8 = '998';-1 = '996' ")
ELSA_ds_w6$recent_falls <- labelled(ELSA_ds_w6$recent_falls, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w6, echo=FALSE}
vari <- ELSA_ds_w6$recent_falls
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w6, aes(x=factor(recent_falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w6, echo=FALSE}
AfterH <- table(ELSA_ds_w6$recent_falls)
X<-table(ELSA_w6_recent_falls$HeFla)
BeforeH <- X[c(5,4,3,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1","-1->996","-9->997","-8->998") 
kable(C)
```


<!--- #### Import to OPAL -->
```{r importOPAL_w6, echo=FALSE}
label(ELSA_ds_w6$recent_falls) <- "Recent falls in the last 6-24 months"
recent_falls <- ELSA_ds_w6
save(recent_falls, file = "../RData/w6/recent_falls.RData")
#opal.assign.data(o, 'ELSA_ds_w6', ELSA_ds_w6)
#opal.symbol_import(o,'ELSA_ds_w6', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w6 <- ELSA_ds_w6
ELSA_m_ds_w6$recent_falls <- recode(ELSA_m_ds_w6$recent_falls, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w6', ELSA_m_ds_w6)
#opal.symbol_import(o,'ELSA_m_ds_w6', project='_Athlos_Harm_Dataset')
```



### Wave 7

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `HeFla`
* Label: `Whether fallen down`
* Categories:
   + `1 = Yes`
   + `2 = No`
* Missings
   + `-9 = Refusal` 
   + `-8 = Don't know` 
   + `-1 = Not applicable` 
   

```{r local w7, echo=FALSE}
ELSA_w7_recent_falls <- ELSA_w7
vari <- ELSA_w7_recent_falls$HeFla
kable(Categorical_summary(vari, missing_values = c(-9,-8, -1))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-9,-8, -1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-9,-8, -1))[2], caption = "Type of missing")
ggplot(ELSA_w7_recent_falls, aes(x=factor(HeFla))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2 into 0` 
* `-9 Refusal into 997` 
* `-8 Don't know into 998`
* `-1 Not applicable into 996`

**R script:**

```{r harmo w7}
ELSA_ds_w7 <- tibble(id=ELSA_w7_recent_falls$id)
ELSA_ds_w7$recent_falls <- recode(ELSA_w7_recent_falls$HeFla, "2 = '0';-9 = '997';-8 = '998';-1 = '996' ")
ELSA_ds_w7$recent_falls <- labelled(ELSA_ds_w7$recent_falls, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w7, echo=FALSE}
vari <- ELSA_ds_w7$recent_falls
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w7, aes(x=factor(recent_falls))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Recent Falls") + ylab("Frequency")
```

#### Validation
```{r crosstabulation w7, echo=FALSE}
AfterH <- table(ELSA_ds_w7$recent_falls)
X<-table(ELSA_w7_recent_falls$HeFla)
BeforeH <- X[c(5,4,3,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1","-1->996","-9->997","-8->998") 
kable(C)
```



<!--- #### Import to OPAL -->
```{r importOPAL_w7, echo=FALSE}
label(ELSA_ds_w7$recent_falls) <- "Recent falls in the last 6-24 months"
recent_falls <- ELSA_ds_w7
save(recent_falls, file = "../RData/w7/recent_falls.RData")
#opal.assign.data(o, 'ELSA_ds_w7', ELSA_ds_w7)
#opal.symbol_import(o,'ELSA_ds_w7', project='_Athlos_Harm_Dataset')

ELSA_m_ds_w7 <- ELSA_ds_w7
ELSA_m_ds_w7$recent_falls <- recode(ELSA_m_ds_w7$recent_falls, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w7', ELSA_m_ds_w7)
#opal.symbol_import(o,'ELSA_m_ds_w7', project='_Athlos_Harm_Dataset')
```

# Quality estimation
Refers to the 2 last years instead of 6-12 months as in the original variable definition.


### Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.


```{r summ}
ELSA_ds_w1$recent_falls <- labelled(ELSA_ds_w1$recent_falls, labels = c(No=0, Yes=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w2$recent_falls <- labelled(ELSA_ds_w2$recent_falls, labels = c(No=0, Yes=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w3$recent_falls <- labelled(ELSA_ds_w3$recent_falls, labels = c(No=0, Yes=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w4$recent_falls <- labelled(ELSA_ds_w4$recent_falls, labels = c(No=0, Yes=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w5$recent_falls <- labelled(ELSA_ds_w5$recent_falls, labels = c(No=0, Yes=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w6$recent_falls <- labelled(ELSA_ds_w6$recent_falls, labels = c(No=0, Yes=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w7$recent_falls <- labelled(ELSA_ds_w7$recent_falls, labels = c(No=0, Yes=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))

tt <-    frq(ELSA_ds_w1$recent_falls)[[1]][,c(1:2,4)]
tt[4] <- frq(ELSA_ds_w2$recent_falls)[[1]][,c(4)]
tt[5] <- frq(ELSA_ds_w3$recent_falls)[[1]][,c(4)]
tt[6] <- frq(ELSA_ds_w4$recent_falls)[[1]][,c(4)]
tt[7] <- frq(ELSA_ds_w5$recent_falls)[[1]][,c(4)]
tt[8] <- frq(ELSA_ds_w6$recent_falls)[[1]][,c(4)]
tt[9] <- frq(ELSA_ds_w7$recent_falls)[[1]][,c(4)]
tt[13,] <- c("n", "sample size", 
             length(ELSA_ds_w1$recent_falls), length(ELSA_ds_w2$recent_falls), length(ELSA_ds_w3$recent_falls),
             length(ELSA_ds_w4$recent_falls), length(ELSA_ds_w5$recent_falls), length(ELSA_ds_w6$recent_falls),     
             length(ELSA_ds_w7$recent_falls))
names(tt)<-c("val", "label", "w1", "w2", "w3", "w4", "w5", "w6", "w7")
kable(tt)

dbb <- merge(ELSA_m_ds_w1, ELSA_m_ds_w2, by="id", suffixes = c(".w1",".w2"), all=T)
dbb <- merge(dbb, ELSA_m_ds_w3, by="id", all=T)
dbb <- merge(dbb, ELSA_m_ds_w4, by="id", suffixes = c(".w3",".w4"), all=T)
dbb <- merge(dbb, ELSA_m_ds_w5, by="id", all=T)
dbb <- merge(dbb, ELSA_m_ds_w6, by="id", suffixes = c(".w5",".w6"), all=T)
dbb <- merge(dbb, ELSA_m_ds_w7, by="id", all=T)
names(dbb) <- c("id", "w1", "w2", "w3", "w4", "w5", "w6", "w7")
v.dbb <- paste(dbb[,2],dbb[,3],dbb[,4],dbb[,5],dbb[,6],dbb[,7],dbb[,8],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])
```


<!--- #### Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
  opal.logout(o)
```
