---
title: "Walking speed"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")

load("ELSA_w1.rdata")
load("ELSA_w2.rdata")
load("ELSA_w3.rdata")
load("ELSA_w4.rdata")
load("ELSA_w5.rdata")
load("ELSA_w6.rdata")
load("ELSA_w7.rdata")
```


# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `walking_speed_c`
* Variable label: `Walking speed - Continuous`
* Variable description: `Walking speed - Continuous. It is measured assessing the time that is taken to walk a distance.`
* Value type: `continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


* Short name: `walking_speed`
* Variable label: `Walking speed`
* Variable description: `Walking speed. It is measured assessing the time that is taken to walk a distance.Discrete variable: value 0 = <=25%; value 1 = >25%.`
* Value type: `Categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | <=25%
1        | >25%

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Walking speed"
ds_label_walking_speed_c <- "Walking speed - Continuous. It is measured assessing the time that is taken to walk a distance"
ds_label_walking_speed <- "Walking speed. It is measured assessing the time that is taken to walk a distance.Discrete variable: value 0 = <=25%; value 1 = >25%."
```

# Data process

## England

### Wave 1 

#### Study-specific variable description



| **Name** |`mmwlka`|`mmwlkb`|
|-|-|-|
| **Label** |`Time taken for first walk (seconds) in a distance of 8 feet (244cm) at their usual walking pace`|`Time taken for second walk (seconds) in a distance of 8 feet (244cm) at their usual walking pace`|
| **Table name** |`wave_1_core_data_v3`|`wave_1_core_data_v3`|
| **Missings** |`-9 = Refusal; -8 = Don't Know; -1 = Not applicable`|`-9 = Refusal; -8 = Don't Know; -1 = Not applicable`|
| **Description** |  |  |



```{r local w1, echo=F}
ELSA_w1_walking <- ELSA_w1[,c(1,36,37)]

limseconds <- 63

vari <- ELSA_w1_walking$mmwlka
kable(Continuous_summary(vari, missing_values = c(-9,-8,-1))[3], caption = "mmwlka")
kable(Continuous_summary(vari, missing_values = c(-9,-8,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-9,-8,-1))$summary, caption = "Summary")
ggplot(ELSA_w1_walking, aes(mmwlka)) + geom_bar(stat="count", width=0.1, fill="steelblue") + xlab("seconds taken for first walk") + ylab("Freq25uency")+xlim(0,limseconds)


cat("It has to be noted that there are", length(ELSA_w1_walking$mmwlka[ELSA_w1_walking$mmwlka>limseconds & !is.na(ELSA_w1_walking$mmwlka)]),"individuals reporting more than",limseconds,"seconds:")
ELSA_w1_walking$mmwlka[ELSA_w1_walking$mmwlka>limseconds & !is.na(ELSA_w1_walking$mmwlka)]


vari <- ELSA_w1_walking$mmwlkb
kable(Continuous_summary(vari, missing_values = c(-9,-8,-1))[3], caption = "mmwlkb")
kable(Continuous_summary(vari, missing_values = c(-9,-8,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-9,-8,-1))$summary, caption = "Summary")
ggplot(ELSA_w1_walking, aes(mmwlkb)) + geom_bar(stat="count", width=0.1, fill="steelblue") + xlab("seconds taken for second walk") + ylab("Freq25uency")+xlim(0,limseconds)


cat("It has to be noted that there are", length(ELSA_w1_walking$mmwlkb[ELSA_w1_walking$mmwlkb>limseconds & !is.na(ELSA_w1_walking$mmwlkb)]),"individuals reporting more than",limseconds,"seconds:")
ELSA_w1_walking$mmwlkb[ELSA_w1_walking$mmwlkb>limseconds & !is.na(ELSA_w1_walking$mmwlkb)]
```

#### Harmonisation algorithm

To compute the harmonize variable `walking_speed_c` from the study-specific variables it has to be computed the mean and 
recoded as follows:

* `-9 Refusal into 997` 
* `-8 Don't Know into 998`
* `-1 Not applicable into 996` 
* `NA into 999`

To compute the harmonized variable `walking_speed` from `walking_speed_c` it has to be recoded as follows:

* `walking_speed_c <=25% into 0`
* `walking_speed_c >25% into 1`

**R script:**

```{r harmo w1}
#walking_speed_c
ELSA_ds_w1 <- tibble(id=ELSA_w1_walking$id)
n <- length(ELSA_w1_walking$id)
mmwlk <- rep(0, length(ELSA_w1_walking$mmwlka))
for(i in 1:n)
{
  if(ELSA_w1_walking$mmwlka[i]<0 & ELSA_w1_walking$mmwlkb[i]>=0)
     mmwlk[i] <- 2.44/ELSA_w1_walking$mmwlkb[i]
  
  if(ELSA_w1_walking$mmwlkb[i]<0 & ELSA_w1_walking$mmwlka[i]>=0)
        mmwlk[i] <- 2.44/ELSA_w1_walking$mmwlka[i]
  
  if(ELSA_w1_walking$mmwlka[i]<0 & ELSA_w1_walking$mmwlkb[i]<0) {
        mmwlk[i] <- min(ELSA_w1_walking$mmwlka[i],ELSA_w1_walking$mmwlkb[i])
  }
  
  if(ELSA_w1_walking$mmwlka[i]>=0 & ELSA_w1_walking$mmwlkb[i]>=0)
        mmwlk[i] <- 2.44/mean(c(ELSA_w1_walking$mmwlka[i],ELSA_w1_walking$mmwlkb[i]))
}
rm(i)

ELSA_ds_w1 <- tibble(id=ELSA_w1_walking$id)
ELSA_ds_w1$walking_speed_c <- car::recode(as.numeric(unlist(mmwlk)), "-9=997; -8=998; -1=996")
ELSA_ds_w1$walking_speed_c <- labelled(ELSA_ds_w1$walking_speed_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#walking_speed
q25 <- quantile(car::recode(ELSA_ds_w1$walking_speed_c, "999=NA; 997=NA; 998=NA; 996=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

ELSA_ds_w1$walking_speed <- car::recode(ELSA_ds_w1[[2]], "0:q25=0; (q25+0.0000000000001):900=1")
ELSA_ds_w1$walking_speed <- labelled(ELSA_ds_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vari <- ELSA_ds_w1$walking_speed_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w1, aes(x=(round(walking_speed_c,5)))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Freq25uency") + xlim(0,70)

vari <- ELSA_ds_w1$walking_speed
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w1, aes(x=factor(walking_speed))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Freq25uency")
```

#### Validation
```{r crosstabulation w1, echo=F}
Continous <- c(sum(na.omit(ELSA_ds_w1[[2]])<=q25), sum(na.omit(ELSA_ds_w1[[2]])>q25 & na.omit(ELSA_ds_w1[[2]])<900), sum(na.omit(ELSA_ds_w1[[2]])==996), sum(na.omit(ELSA_ds_w1[[2]])==997))
Dicotomic <- table(ELSA_ds_w1[[3]], useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:q25->0","q25:900->1", "-1->996", "-9->997") 
kable(C, caption = "Continuous vs Dichotomous")
```




ALBERT: I found almost 50% of individuals with "not applicable" missing value. It may come from a skip/jump of a previous variable saying if s/he was available to walk. Actually, this missing values might be re-categorized to "presence of difficulties".



```{r importOPAL_w1, echo=F}
#opal.assign.data(o, 'ELSA_ds_w1', ELSA_ds_w1)
#opal.symbol_import(o,'ELSA_ds_w1', project='_Athlos_Harm_Dataset')
label(ELSA_ds_w1$walking_speed_c) <- ds_label_walking_speed_c
label(ELSA_ds_w1$walking_speed) <- ds_label_walking_speed
walking_speed <- ELSA_ds_w1
save(walking_speed, file = "../RData/w1/walking_speed.RData")

ELSA_m_ds_w1 <- ELSA_ds_w1
ELSA_m_ds_w1$walking_speed <- car::recode(ELSA_m_ds_w1$walking_speed, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w1', ELSA_m_ds_w1)
#opal.symbol_import(o,'ELSA_m_ds_w1', project='_Athlos_Harm_Dataset')
```



### Wave 2 

#### Study-specific variable description



| **Name** |`MMWlkA`|`MMWlkB`|
|-|-|-|
| **Label** |`Time taken for first walk (seconds) in a distance of 8 feet (244cm) at their usual walking pace`|`Time taken for second walk (seconds) in a distance of 8 feet (244cm) at their usual walking pace`|
| **Table name** |`wave_2_core_data_v4`|`wave_2_core_data_v4`|
| **Missings** |`-9 = Refusal; -8 = Don't Know; -1 = Not applicable`|`-9 = Refusal; -8 = Don't Know; -1 = Not applicable`|
| **Description** |  |  |




```{r local w2, echo=F}
ELSA_w2_walking <- ELSA_w2

vari <- ELSA_w2_walking$MMWlkA
kable(Continuous_summary(vari, missing_values = c(-9,-8,-1))[3], caption = "MMWlkA")
kable(Continuous_summary(vari, missing_values = c(-9,-8,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-9,-8,-1))$summary, caption = "Summary")
ggplot(ELSA_w2_walking, aes(MMWlkA)) + geom_bar(stat="count", width=0.1, fill="steelblue") + xlab("seconds taken for first walk") + ylab("Freq25uency") +xlim(0,31)

vari <- ELSA_w2_walking$MMWlkB
kable(Continuous_summary(vari, missing_values = c(-9,-8,-1))[3], caption = "MMWlkB")
kable(Continuous_summary(vari, missing_values = c(-9,-8,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-9,-8,-1))$summary, caption = "Summary")
ggplot(ELSA_w2_walking, aes(MMWlkB)) + geom_bar(stat="count", width=0.1, fill="steelblue") + xlab("seconds taken for second walk") + ylab("Freq25uency") + xlim(0,47)
```

#### Harmonisation algorithm

To compute the harmonize variable `walking_speed_c` from the study-specific variables it has to be computed the mean and 
recoded as follows:

* `-9 Refusal into 997` 
* `-8 Don't Know into 998`
* `-1 Not applicable into 996` 
* `NA into 999`

To compute the harmonized variable `walking_speed` from `walking_speed_c` it has to be recoded as follows:

* `walking_speed_c <=25% into 0`
* `walking_speed_c >25% into 1`

**R script:**

```{r harmo w2}
ELSA_ds_w2 <- tibble(id=ELSA_w2_walking$id)
n <- length(ELSA_w2_walking$id)
mmwlk <- rep(0, length(ELSA_w2_walking$MMWlkA))
for(i in 1:n)
{
  if(ELSA_w2_walking$MMWlkA[i]<0 & ELSA_w2_walking$MMWlkB[i]>=0)
     mmwlk[i] <- 2.44/ELSA_w2_walking$MMWlkB[i]
  
  if(ELSA_w2_walking$MMWlkB[i]<0 & ELSA_w2_walking$MMWlkA[i]>=0)
        mmwlk[i] <- 2.44/ELSA_w2_walking$MMWlkA[i]
  
  if(ELSA_w2_walking$MMWlkA[i]<0 & ELSA_w2_walking$MMWlkB[i]<0) {
        mmwlk[i] <- min(ELSA_w2_walking$MMWlkA[i],ELSA_w2_walking$MMWlkB[i])
  }
  
  if(ELSA_w2_walking$MMWlkA[i]>=0 & ELSA_w2_walking$MMWlkB[i]>=0)
        mmwlk[i] <- 2.44/mean(c(ELSA_w2_walking$MMWlkA[i],ELSA_w2_walking$MMWlkB[i]))
}
rm(i)


ELSA_ds_w2$walking_speed_c <-  ELSA_ds_w2$walking_speed <- car::recode(as.numeric(unlist(mmwlk)), "-9=997; -8=998; -1=996")

ELSA_ds_w2$walking_speed_c <- labelled(ELSA_ds_w2$walking_speed_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cut-off 25% is the R object "q2525" from wave 1.
q2525 <- quantile(car::recode(ELSA_ds_w2$walking_speed_c, "999=NA; 997=NA; 998=NA; 996=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

ELSA_ds_w2$walking_speed[ELSA_ds_w2$walking_speed_c <= q2525] <- 0
ELSA_ds_w2$walking_speed[ELSA_ds_w2$walking_speed_c > q2525 & ELSA_ds_w2$walking_speed_c < 990] <- 1
ELSA_ds_w2$walking_speed <- labelled(ELSA_ds_w2$walking_speed, labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
#hist(mmwlk[mmwlk>0 & mmwlk<3], breaks=100)

#Categorical_summary(var = ELSA_ds_w2$walking, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))


vari <- ELSA_ds_w2$walking_speed_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w2, aes(x=(round(walking_speed_c,5)))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Freq25uency") + xlim(0,70)

vari <- ELSA_ds_w2$walking_speed
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w2, aes(x=factor(walking_speed))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Freq25uency")
```

#### Validation
```{r crosstabulation w2, echo=F}
Continous <- c(sum(na.omit(ELSA_ds_w2$walking_speed_c)<=q2525), sum(na.omit(ELSA_ds_w2$walking_speed_c)>q2525 & na.omit(ELSA_ds_w2$walking_speed_c)<900), sum(na.omit(ELSA_ds_w2$walking_speed_c)==996), sum(na.omit(ELSA_ds_w2$walking_speed_c)==997), sum(na.omit(ELSA_ds_w2$walking_speed_c)==998))
Dicotomic <- table(ELSA_ds_w2$walking_speed, useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:q25->0","q25:900->1", "-1->996", "-9->997", "-8->998") 
kable(C, caption = "Continuous vs Dichotomous")
```





```{r importOPAL_w2, echo=F}
#opal.assign.data(o, 'ELSA_ds_w2', ELSA_ds_w2)
#opal.symbol_import(o,'ELSA_ds_w2', project='_Athlos_Harm_Dataset')
label(ELSA_ds_w2$walking_speed_c) <- ds_label_walking_speed_c
label(ELSA_ds_w2$walking_speed) <- ds_label_walking_speed
walking_speed <- ELSA_ds_w2
save(walking_speed, file = "../RData/w2/walking_speed.RData")

ELSA_m_ds_w2 <- ELSA_ds_w2
ELSA_m_ds_w2$walking_speed <- car::recode(ELSA_m_ds_w2$walking_speed, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w2', ELSA_m_ds_w2)
#opal.symbol_import(o,'ELSA_m_ds_w2', project='_Athlos_Harm_Dataset')
```


### Wave 3

#### Study-specific variable description




| **Name** |`mmwlka`|`mmwlkb`|
|-|-|-|
| **Label** |`Time taken for first walk (seconds) in a distance of 8 feet (244cm) at their usual walking pace`|`Time taken for second walk (seconds) in a distance of 8 feet (244cm) at their usual walking pace`|
| **Table name** |`wave_3_elsa_data_v4`|`wave_3_elsa_data_v4`|
| **Missings** |`-9 = Refusal; -8 = Don't Know; -1 = Not applicable`|`-9 = Refusal; -8 = Don't Know; -1 = Not applicable`|
| **Description** |  |  |


```{r local w3, echo=F}
ELSA_w3_walking <- ELSA_w3

vari <- ELSA_w3_walking$mmwlka
kable(Continuous_summary(vari, missing_values = c(-9,-8,-1))[3], caption = "mmwlka")
kable(Continuous_summary(vari, missing_values = c(-9,-8,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-9,-8,-1))$summary, caption = "Summary")
ggplot(ELSA_w3_walking, aes(mmwlka)) + geom_bar(stat="count", width=0.1, fill="steelblue") + xlab("seconds taken for first walk") + ylab("Freq25uency")+xlim(0,40)


vari <- ELSA_w3_walking$mmwlkb
kable(Continuous_summary(vari, missing_values = c(-9,-8,-1))[3], caption = "mmwlkb")
kable(Continuous_summary(vari, missing_values = c(-9,-8,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-9,-8,-1))$summary, caption = "Summary")
ggplot(ELSA_w3_walking, aes(mmwlkb)) + geom_bar(stat="count", width=0.1, fill="steelblue") + xlab("seconds taken for second walk") + ylab("Freq25uency")+xlim(0,39)
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:


* `-9 Refusal into 997` 
* `-8 Don't know into 998` 
* `-1 Not applicable into 996` 

**R script:**

```{r harmo w3}
ELSA_ds_w3 <- tibble(id=ELSA_w3_walking$id)
n <- length(ELSA_w3_walking$id)
mmwlk <- rep(0, length(ELSA_w3_walking$mmwlka))
for(i in 1:n)
{
  if(ELSA_w3_walking$mmwlka[i]<0 & ELSA_w3_walking$mmwlkb[i]>=0)
     mmwlk[i] <- 2.44/ELSA_w3_walking$mmwlkb[i]
  
  if(ELSA_w3_walking$mmwlkb[i]<0 & ELSA_w3_walking$mmwlka[i]>=0)
        mmwlk[i] <- 2.44/ELSA_w3_walking$mmwlka[i]
  
  if(ELSA_w3_walking$mmwlka[i]<0 & ELSA_w3_walking$mmwlkb[i]<0) {
        mmwlk[i] <- min(ELSA_w3_walking$mmwlka[i],ELSA_w3_walking$mmwlkb[i])
  }
  
  if(ELSA_w3_walking$mmwlka[i]>=0 & ELSA_w3_walking$mmwlkb[i]>=0)
        mmwlk[i] <- 2.44/mean(c(ELSA_w3_walking$mmwlka[i],ELSA_w3_walking$mmwlkb[i]))
}
rm(i)




ELSA_ds_w3$walking_speed <- ELSA_ds_w3$walking_speed_c <- car::recode(as.numeric(unlist(mmwlk)), "-9 = '997';-8 = '998';-1 = '996' ")

ELSA_ds_w3$walking_speed_c <- labelled(ELSA_ds_w3$walking_speed_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cut-off 25% is the R object "q2525" from wave 1.
q2525 <- quantile(car::recode(ELSA_ds_w3$walking_speed_c, "999=NA; 997=NA; 998=NA; 996=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

ELSA_ds_w3$walking_speed[ELSA_ds_w3$walking_speed_c <= q2525] <- 0
ELSA_ds_w3$walking_speed[ELSA_ds_w3$walking_speed_c > q2525 & ELSA_ds_w3$walking_speed_c < 990] <- 1
ELSA_ds_w3$walking_speed <- labelled(ELSA_ds_w3$walking_speed, labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}
#hist(mmwlk[mmwlk>0 & mmwlk<3], breaks=100)
#Categorical_summary(var = ELSA_ds_w3$walking, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))

vari <- ELSA_ds_w3$walking_speed_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w3, aes(x=(round(walking_speed_c,5)))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Freq25uency") + xlim(0,70)

vari <- ELSA_ds_w3$walking_speed
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w3, aes(x=factor(walking_speed))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Freq25uency")
```

#### Validation
```{r crosstabulation w3, echo=F}
Continous <- c(sum(na.omit(ELSA_ds_w3$walking_speed_c)<=q25), sum(na.omit(ELSA_ds_w3$walking_speed_c)>q25 & na.omit(ELSA_ds_w3$walking_speed_c)<900), sum(na.omit(ELSA_ds_w3$walking_speed_c)==996), sum(na.omit(ELSA_ds_w3$walking_speed_c)==998))
Dicotomic <- table(ELSA_ds_w3$walking_speed, useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:q25->0","q25:900->1", "-1->996", "-8->998") 
kable(C, caption = "Continuous vs Dichotomous")
```





```{r importOPAL_w3, echo=F}
#opal.assign.data(o, 'ELSA_ds_w3', ELSA_ds_w3)
#opal.symbol_import(o,'ELSA_ds_w3', project='_Athlos_Harm_Dataset')
label(ELSA_ds_w3$walking_speed_c) <- ds_label_walking_speed_c
label(ELSA_ds_w3$walking_speed) <- ds_label_walking_speed
walking_speed <- ELSA_ds_w3
save(walking_speed, file = "../RData/w3/walking_speed.RData")

ELSA_m_ds_w3 <- ELSA_ds_w3
ELSA_m_ds_w3$walking_speed <- car::recode(ELSA_m_ds_w3$walking_speed, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w3', ELSA_m_ds_w3)
#opal.symbol_import(o,'ELSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```



### Wave 4 

#### Study-specific variable description




| **Name** |`mmwlka`|`mmwlkb`|
|-|-|-|
| **Label** |`Time taken for first walk (seconds) in a distance of 8 feet (244cm) at their usual walking pace`|`Time taken for second walk (seconds) in a distance of 8 feet (244cm) at their usual walking pace`|
| **Table name** |`wave_4_elsa_data_v3`|`wave_4_elsa_data_v3`|
| **Missings** |`-9 = Refusal; -8 = Don't Know; -1 = Not applicable`|`-9 = Refusal; -8 = Don't Know; -1 = Not applicable`|
| **Description** |  |  |



```{r local w4, echo=F}
ELSA_w4_walking <- ELSA_w4

vari <- ELSA_w4_walking$mmwlka
kable(Continuous_summary(vari, missing_values = c(-9,-8,-1))[3], caption = "mmwlka")
kable(Continuous_summary(vari, missing_values = c(-9,-8,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-9,-8,-1))$summary, caption = "Summary")
ggplot(ELSA_w4_walking, aes(mmwlka)) + geom_bar(stat="count", width=0.1, fill="steelblue") + xlab("seconds taken for first walk") + ylab("Freq25uency")+xlim(0,38)

vari <- ELSA_w4_walking$mmwlkb
kable(Continuous_summary(vari, missing_values = c(-9,-8,-1))[3], caption = "mmwlkb")
kable(Continuous_summary(vari, missing_values = c(-9,-8,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-9,-8,-1))$summary, caption = "Summary")
ggplot(ELSA_w4_walking, aes(mmwlkb)) + geom_bar(stat="count", width=0.1, fill="steelblue") + xlab("seconds taken for second walk") + ylab("Freq25uency")+xlim(0,42)
```

#### Harmonisation algorithm

To compute the harmonize variable `walking_speed_c` from the study-specific variables it has to be computed the mean and 
recoded as follows:

* `-9 Refusal into 997` 
* `-8 Don't Know into 998`
* `-1 Not applicable into 996` 
* `NA into 999`

To compute the harmonized variable `walking_speed` from `walking_speed_c` it has to be recoded as follows:

* `walking_speed_c <=25% into 0`
* `walking_speed_c >25% into 1`

**R script:**

```{r harmo w4}
ELSA_ds_w4 <- tibble(id=ELSA_w4_walking$id)
n <- length(ELSA_w4_walking$id)
mmwlk <- rep(0, length(ELSA_w4_walking$mmwlka))
for(i in 1:n)
{
  if(ELSA_w4_walking$mmwlka[i]<0 & ELSA_w4_walking$mmwlkb[i]>=0)
     mmwlk[i] <- 2.44/ELSA_w4_walking$mmwlkb[i]
  
  if(ELSA_w4_walking$mmwlkb[i]<0 & ELSA_w4_walking$mmwlka[i]>=0)
        mmwlk[i] <- 2.44/ELSA_w4_walking$mmwlka[i]
  
  if(ELSA_w4_walking$mmwlka[i]<0 & ELSA_w4_walking$mmwlkb[i]<0) {
        mmwlk[i] <- min(ELSA_w4_walking$mmwlka[i],ELSA_w4_walking$mmwlkb[i])
  }
  
  if(ELSA_w4_walking$mmwlka[i]>=0 & ELSA_w4_walking$mmwlkb[i]>=0)
        mmwlk[i] <- 2.44/mean(c(ELSA_w4_walking$mmwlka[i],ELSA_w4_walking$mmwlkb[i]))
}
rm(i)




ELSA_ds_w4$walking_speed <- ELSA_ds_w4$walking_speed_c <- car::recode(as.numeric(unlist(mmwlk)), "-9 = '997';-8 = '998';-1 = '996';-2 = '991' ")

ELSA_ds_w4$walking_speed_c <- labelled(ELSA_ds_w4$walking_speed_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cut-off 25% is the R object "q252525" from wave 1.

ELSA_ds_w4$walking_speed[ELSA_ds_w4$walking_speed_c <= q25] <- 0
ELSA_ds_w4$walking_speed[ELSA_ds_w4$walking_speed_c > q25 & ELSA_ds_w4$walking_speed_c < 990] <- 1
ELSA_ds_w4$walking_speed <- labelled(ELSA_ds_w4$walking_speed, labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w4, echo=F}
# hist(mmwlk[mmwlk>0 & mmwlk<3], breaks=100)
# Categorical_summary(var = ELSA_ds_w4$walking, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))


vari <- ELSA_ds_w4$walking_speed_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w4, aes(x=(round(walking_speed_c,5)))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Freq25uency") + xlim(0,70)

vari <- ELSA_ds_w4$walking_speed
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w4, aes(x=factor(walking_speed))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Freq25uency")
```

#### Validation
```{r crosstabulation w4, echo=F}
Continous <- c(sum(na.omit(ELSA_ds_w4$walking_speed_c)<=q25), sum(na.omit(ELSA_ds_w4$walking_speed_c)>q25 & na.omit(ELSA_ds_w4$walking_speed_c)<900), sum(na.omit(ELSA_ds_w4$walking_speed_c)==991), sum(na.omit(ELSA_ds_w4$walking_speed_c)==996), sum(na.omit(ELSA_ds_w4$walking_speed_c)==997), sum(na.omit(ELSA_ds_w4$walking_speed_c)==998))
Dicotomic <- table(ELSA_ds_w4$walking_speed, useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:q25->0","q25:900->1","-2->991", "-1->996", "-9->997", "-8->998") 
kable(C, caption = "Continuous vs Dichotomous")
```





```{r importOPAL_w4, echo=F}
#opal.assign.data(o, 'ELSA_ds_w4', ELSA_ds_w4)
#opal.symbol_import(o,'ELSA_ds_w4', project='_Athlos_Harm_Dataset')
label(ELSA_ds_w4$walking_speed_c) <- ds_label_walking_speed_c
label(ELSA_ds_w4$walking_speed) <- ds_label_walking_speed
walking_speed <- ELSA_ds_w4
save(walking_speed, file = "../RData/w4/walking_speed.RData")

ELSA_m_ds_w4 <- ELSA_ds_w4
ELSA_m_ds_w4$walking_speed <- car::recode(ELSA_m_ds_w4$walking_speed, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w4', ELSA_m_ds_w4)
#opal.symbol_import(o,'ELSA_m_ds_w4', project='_Athlos_Harm_Dataset')
```



### Wave 5 

#### Study-specific variable description




| **Name** |`mmwlka`|`mmwlkb`|
|-|-|-|
| **Label** |`Time taken for first walk (seconds) in a distance of 8 feet (244cm) at their usual walking pace`|`Time taken for second walk (seconds) in a distance of 8 feet (244cm) at their usual walking pace`|
| **Table name** |`wave_5_elsa_data_v4`|`wave_5_elsa_data_v4`|
| **Missings** |`-8 = Don't Know; -1 = Not applicable`|`-8 = Don't Know; -1 = Not applicable`|
| **Description** |  |  |



```{r local w5, echo=F}
ELSA_w5_walking <- ELSA_w5

vari <- ELSA_w5_walking$mmwlka
kable(Continuous_summary(vari, missing_values = c(-9,-8,-1))[3], caption = "mmwlka")
kable(Continuous_summary(vari, missing_values = c(-9,-8,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-9,-8,-1))$summary, caption = "Summary")
ggplot(ELSA_w5_walking, aes(mmwlka)) + geom_bar(stat="count", width=0.1, fill="steelblue") + xlab("seconds taken for first walk") + ylab("Freq25uency")+xlim(0,39)

vari <- ELSA_w5_walking$mmwlkb
kable(Continuous_summary(vari, missing_values = c(-9,-8,-1))[3], caption = "mmwlkb")
kable(Continuous_summary(vari, missing_values = c(-9,-8,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-9,-8,-1))$summary, caption = "Summary")
ggplot(ELSA_w5_walking, aes(mmwlkb)) + geom_bar(stat="count", width=0.1, fill="steelblue") + xlab("seconds taken for second walk") + ylab("Freq25uency")+xlim(0,42)
```

#### Harmonisation algorithm

To compute the harmonize variable `walking_speed_c` from the study-specific variables it has to be computed the mean and 
recoded as follows:

* `-8 Don't Know into 998`
* `-1 Not applicable into 996` 
* `NA into 999`

To compute the harmonized variable `walking_speed` from `walking_speed_c` it has to be recoded as follows:

* `walking_speed_c <=25% into 0`
* `walking_speed_c >25% into 1`

**R script:**

**R script:**
```{r harmo w5}
ELSA_ds_w5 <- tibble(id=ELSA_w5_walking$id)
n <- length(ELSA_w5_walking$id)
mmwlk <- rep(0, length(ELSA_w5_walking$mmwlka))
for(i in 1:n)
{
  if(ELSA_w5_walking$mmwlka[i]<0 & ELSA_w5_walking$mmwlkb[i]>=0)
     mmwlk[i] <- 2.44/ELSA_w5_walking$mmwlkb[i]
  
  if(ELSA_w5_walking$mmwlkb[i]<0 & ELSA_w5_walking$mmwlka[i]>=0)
        mmwlk[i] <- 2.44/ELSA_w5_walking$mmwlka[i]
  
  if(ELSA_w5_walking$mmwlka[i]<0 & ELSA_w5_walking$mmwlkb[i]<0) {
        mmwlk[i] <- min(ELSA_w5_walking$mmwlka[i],ELSA_w5_walking$mmwlkb[i])
  }
  
  if(ELSA_w5_walking$mmwlka[i]>=0 & ELSA_w5_walking$mmwlkb[i]>=0)
        mmwlk[i] <- 2.44/mean(c(ELSA_w5_walking$mmwlka[i],ELSA_w5_walking$mmwlkb[i]))
}
rm(i)




ELSA_ds_w5$walking_speed <- ELSA_ds_w5$walking_speed_c <- car::recode(as.numeric(unlist(mmwlk)), "-8 = '998';-1 = '996' ")
ELSA_ds_w5$walking_speed_c <- labelled(ELSA_ds_w5$walking_speed_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

## cut-off 25% is the R object "q25" from wave 1.
q25 <- quantile(car::recode(ELSA_ds_w5$walking_speed_c, "999=NA; 997=NA; 998=NA; 996=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

ELSA_ds_w5$walking_speed[ELSA_ds_w5$walking_speed_c <= q25] <- 0
ELSA_ds_w5$walking_speed[ELSA_ds_w5$walking_speed_c > q25 & ELSA_ds_w5$walking_speed_c < 990] <- 1

ELSA_ds_w5$walking_speed <- labelled(ELSA_ds_w5$walking_speed, labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w5, echo=F}
# hist(mmwlk[mmwlk>0 & mmwlk<3], breaks=100)
# Categorical_summary(var = ELSA_ds_w5$walking, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))

vari <- ELSA_ds_w5$walking_speed_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w5, aes(x=(round(walking_speed_c,5)))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(0,70)

vari <- ELSA_ds_w5$walking_speed
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w5, aes(x=factor(walking_speed))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w5, echo=F}
Continous <- c(sum(na.omit(ELSA_ds_w5$walking_speed_c)<=q25), sum(na.omit(ELSA_ds_w5$walking_speed_c)>q25 & na.omit(ELSA_ds_w5$walking_speed_c)<900),  sum(na.omit(ELSA_ds_w5$walking_speed_c)==996),  sum(na.omit(ELSA_ds_w5$walking_speed_c)==998))
Dicotomic <- table(ELSA_ds_w5$walking_speed, useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:q25->0","q25:900->1","-1->996",  "-8->998") 
kable(C, caption = "Continuous vs Dichotomous")
```





```{r importOPAL_w5, echo=F}
#opal.assign.data(o, 'ELSA_ds_w5', ELSA_ds_w5)
#opal.symbol_import(o,'ELSA_ds_w5', project='_Athlos_Harm_Dataset')
label(ELSA_ds_w5$walking_speed_c) <- ds_label_walking_speed_c
label(ELSA_ds_w5$walking_speed) <- ds_label_walking_speed
walking_speed <- ELSA_ds_w5
save(walking_speed, file = "../RData/w5/walking_speed.RData")

ELSA_m_ds_w5 <- ELSA_ds_w5
ELSA_m_ds_w5$walking_speed <- car::recode(ELSA_m_ds_w5$walking_speed, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w5', ELSA_m_ds_w5)
#opal.symbol_import(o,'ELSA_m_ds_w5', project='_Athlos_Harm_Dataset')
```


### Wave 6

#### Study-specific variable description




| **Name** |`MMWlkA`|`MMWlkB`|
|-|-|-|
| **Label** |`Time taken for first walk (seconds) in a distance of 8 feet (244cm) at their usual walking pace`|`Time taken for second walk (seconds) in a distance of 8 feet (244cm) at their usual walking pace`|
| **Table name** |`wave_6_elsa_data_v2`|`wave_6_elsa_data_v2`|
| **Missings** |`-8 = Don't Know; -1 = Not applicable`|`-8 = Don't Know; -1 = Not applicable`|
| **Description** |  |  |



```{r local w6, echo=F}
ELSA_w6_walking <- ELSA_w6

vari <- ELSA_w6_walking$MMWlkA
kable(Continuous_summary(vari, missing_values = c(-8,-1))[3], caption = "MMWlkA")
kable(Continuous_summary(vari, missing_values = c(-8,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-8,-1))$summary, caption = "Summary")
ggplot(ELSA_w6_walking, aes(MMWlkA)) + geom_bar(stat="count", width=0.1, fill="steelblue") + xlab("seconds taken for first walk") + ylab("Freq25uency")+xlim(0,47)


vari <- ELSA_w6_walking$MMWlkB
kable(Continuous_summary(vari, missing_values = c(-8,-1))[3], caption = "MMWlkB")
kable(Continuous_summary(vari, missing_values = c(-8,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-8,-1))$summary, caption = "Summary")
ggplot(ELSA_w6_walking, aes(MMWlkB)) + geom_bar(stat="count", width=0.1, fill="steelblue") + xlab("seconds taken for second walk") + ylab("Freq25uency")+xlim(0,45)
```

#### Harmonisation algorithm

To compute the harmonize variable `walking_speed_c` from the study-specific variables it has to be computed the mean and 
recoded as follows:

* `-8 Don't Know into 998`
* `-1 Not applicable into 996` 
* `NA into 999`

To compute the harmonized variable `walking_speed` from `walking_speed_c` it has to be recoded as follows:

* `walking_speed_c <=25% into 0`
* `walking_speed_c >25% into 1`

**R script:**

```{r harmo w6}
ELSA_ds_w6 <- tibble(id=ELSA_w6_walking$id)
n <- length(ELSA_w6_walking$id)
mmwlk <- rep(0, length(ELSA_w6_walking$MMWlkA))
for(i in 1:n)
{
  if(ELSA_w6_walking$MMWlkA[i]<0 & ELSA_w6_walking$MMWlkB[i]>=0)
     mmwlk[i] <- 2.44/ELSA_w6_walking$MMWlkB[i]
  
  if(ELSA_w6_walking$MMWlkB[i]<0 & ELSA_w6_walking$MMWlkA[i]>=0)
        mmwlk[i] <- 2.44/ELSA_w6_walking$MMWlkA[i]
  
  if(ELSA_w6_walking$MMWlkA[i]<0 & ELSA_w6_walking$MMWlkB[i]<0) {
        mmwlk[i] <- min(ELSA_w6_walking$MMWlkA[i],ELSA_w6_walking$MMWlkB[i])
  }
  
  if(ELSA_w6_walking$MMWlkA[i]>=0 & ELSA_w6_walking$MMWlkB[i]>=0)
        mmwlk[i] <- 2.44/mean(c(ELSA_w6_walking$MMWlkA[i],ELSA_w6_walking$MMWlkB[i]))
}
rm(i)




ELSA_ds_w6$walking_speed <- ELSA_ds_w6$walking_speed_c <- car::recode(as.numeric(unlist(mmwlk)), "-8 = '998';-1 = '996' ")

ELSA_ds_w6$walking_speed_c <- labelled(ELSA_ds_w6$walking_speed_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))


## cut-off 25% is the R object "q25" from wave 1.
q25 <- quantile(car::recode(ELSA_ds_w6$walking_speed_c, "999=NA; 997=NA; 998=NA; 996=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

ELSA_ds_w6$walking_speed[ELSA_ds_w6$walking_speed_c <= q25] <- 0
ELSA_ds_w6$walking_speed[ELSA_ds_w6$walking_speed_c > q25 & ELSA_ds_w6$walking_speed_c < 990] <- 1

ELSA_ds_w6$walking_speed <- labelled(ELSA_ds_w6$walking_speed, labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistical description of the new harmonised variable
```{r descript w6, echo=F}
# hist(mmwlk[mmwlk>0 & mmwlk<3], breaks=100)
# Categorical_summary(var = ELSA_ds_w6$walking, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
vari <- ELSA_ds_w6$walking_speed_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w6, aes(x=(round(walking_speed_c,5)))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(0,70)

vari <- ELSA_ds_w6$walking_speed
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w6, aes(x=factor(walking_speed))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w6, echo=F}
Continous <- c(sum(na.omit(ELSA_ds_w6$walking_speed_c)<=q25), sum(na.omit(ELSA_ds_w6$walking_speed_c)>q25 & na.omit(ELSA_ds_w6$walking_speed_c)<900), sum(na.omit(ELSA_ds_w6$walking_speed_c)==996), sum(na.omit(ELSA_ds_w6$walking_speed_c)==998))
Dicotomic <- table(ELSA_ds_w6$walking_speed, useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:q25->0","q25:900->1", "-1->996", "-8->998") 
kable(C, caption = "Continuous vs Dichotomous")
```





```{r importOPAL_w6, echo=F}
#opal.assign.data(o, 'ELSA_ds_w6', ELSA_ds_w6)
#opal.symbol_import(o,'ELSA_ds_w6', project='_Athlos_Harm_Dataset')
label(ELSA_ds_w6$walking_speed_c) <- ds_label_walking_speed_c
label(ELSA_ds_w6$walking_speed) <- ds_label_walking_speed
walking_speed <- ELSA_ds_w6
save(walking_speed, file = "../RData/w6/walking_speed.RData")

ELSA_m_ds_w6 <- ELSA_ds_w6
ELSA_m_ds_w6$walking_speed <- car::recode(ELSA_m_ds_w6$walking_speed, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w6', ELSA_m_ds_w6)
#opal.symbol_import(o,'ELSA_m_ds_w6', project='_Athlos_Harm_Dataset')
```



### Wave 7

#### Study-specific variable description




| **Name** |`MMWlkA`|`MMWlkB`|
|-|-|-|
| **Label** |`Time taken for first walk (seconds) in a distance of 8 feet (244cm) at their usual walking pace`|`Time taken for second walk (seconds) in a distance of 8 feet (244cm) at their usual walking pace`|
| **Table name** |`wave_7_elsa_data`|`wave_7_elsa_data`|
| **Missings** |`-8 = Don't Know; -1 = Not applicable`|`-8 = Don't Know; -1 = Not applicable`|
| **Description** |  |  |



```{r local w7, echo=F}
ELSA_w7_walking <- ELSA_w7

vari <- ELSA_w7_walking$MMWlkA
kable(Continuous_summary(vari, missing_values = c(-8,-1))[3], caption = "MMWlkA")
kable(Continuous_summary(vari, missing_values = c(-8,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-8,-1))$summary, caption = "Summary")
ggplot(ELSA_w7_walking, aes(MMWlkA)) + geom_bar(stat="count", width=0.1, fill="steelblue") + xlab("seconds taken for first walk") + ylab("Freq25uency")+xlim(0,51)


vari <- ELSA_w7_walking$MMWlkB
kable(Continuous_summary(vari, missing_values = c(-8,-1))[3], caption = "MMWlkB")
kable(Continuous_summary(vari, missing_values = c(-8,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-8,-1))$summary, caption = "Summary")
ggplot(ELSA_w7_walking, aes(MMWlkB)) + geom_bar(stat="count", width=0.1, fill="steelblue") + xlab("seconds taken for second walk") + ylab("Freq25uency")+xlim(0,51)
```

#### Harmonisation algorithm

To compute the harmonize variable `walking_speed_c` from the study-specific variables it has to be computed the mean and 
recoded as follows:

* `-8 Don't Know into 998`
* `-1 Not applicable into 996` 
* `NA into 999`

To compute the harmonized variable `walking_speed` from `walking_speed_c` it has to be recoded as follows:

* `walking_speed_c <=25% into 0`
* `walking_speed_c >25% into 1`

**R script:**

```{r harmo w7}
ELSA_ds_w7 <- tibble(id=ELSA_w7_walking$id)
n <- length(ELSA_w7_walking$id)
mmwlk <- rep(0, length(ELSA_w7_walking$MMWlkA))
for(i in 1:n)
{
  if(ELSA_w7_walking$MMWlkA[i]<0 & ELSA_w7_walking$MMWlkB[i]>=0)
     mmwlk[i] <- 2.44/ELSA_w7_walking$MMWlkB[i]
  
  if(ELSA_w7_walking$MMWlkB[i]<0 & ELSA_w7_walking$MMWlkA[i]>=0)
        mmwlk[i] <- 2.44/ELSA_w7_walking$MMWlkA[i]
  
  if(ELSA_w7_walking$MMWlkA[i]<0 & ELSA_w7_walking$MMWlkB[i]<0) {
        mmwlk[i] <- min(ELSA_w7_walking$MMWlkA[i],ELSA_w7_walking$MMWlkB[i])
  }
  
  if(ELSA_w7_walking$MMWlkA[i]>=0 & ELSA_w7_walking$MMWlkB[i]>=0)
        mmwlk[i] <- 2.44/mean(c(ELSA_w7_walking$MMWlkA[i],ELSA_w7_walking$MMWlkB[i]))
}
rm(i)


ELSA_ds_w7$walking_speed <- ELSA_ds_w7$walking_speed_c <- car::recode(as.numeric(unlist(mmwlk)), "-8 = '998';-1 = '996' ")

ELSA_ds_w7$walking_speed_c <- labelled(ELSA_ds_w7$walking_speed_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))



## cut-off 25% is the R object "q25" from wave 1.
q25 <- quantile(car::recode(ELSA_ds_w7$walking_speed_c, "999=NA; 997=NA; 998=NA; 996=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

ELSA_ds_w7$walking_speed[ELSA_ds_w7$walking_speed_c <= q25] <- 0
ELSA_ds_w7$walking_speed[ELSA_ds_w7$walking_speed_c > q25 & ELSA_ds_w7$walking_speed_c < 990] <- 1

ELSA_ds_w7$walking_speed <- labelled(ELSA_ds_w7$walking_speed, labels =  c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript w7, echo=F}
# hist(mmwlk[mmwlk>0 & mmwlk<3], breaks=100)
# Categorical_summary(var = ELSA_ds_w7$walking, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))

vari <- ELSA_ds_w7$walking_speed_c
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ELSA_ds_w7, aes(x=(round(walking_speed_c,5)))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(0,70)

vari <- ELSA_ds_w7$walking_speed
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ELSA_ds_w7, aes(x=factor(walking_speed))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w7, echo=F}
Continous <- c(sum(na.omit(ELSA_ds_w7$walking_speed_c)<=q25), sum(na.omit(ELSA_ds_w7$walking_speed_c)>q25 & na.omit(ELSA_ds_w7$walking_speed_c)<900), sum(na.omit(ELSA_ds_w7$walking_speed_c)==996), sum(na.omit(ELSA_ds_w7$walking_speed_c)==998))
Dicotomic <- table(ELSA_ds_w7$walking_speed, useNA = "ifany")
C <- rbind(Continous,Dicotomic)
colnames(C) <- c("0:q25->0","q25:900->1", "-1->996", "-8->998") 
kable(C, caption = "Continuous vs Dichotomous")
```






```{r importOPAL_w7, echo=F}
#opal.assign.data(o, 'ELSA_ds_w7', ELSA_ds_w7)
#opal.symbol_import(o,'ELSA_ds_w7', project='_Athlos_Harm_Dataset')
label(ELSA_ds_w7$walking_speed_c) <- ds_label_walking_speed_c
label(ELSA_ds_w7$walking_speed) <- ds_label_walking_speed
walking_speed <- ELSA_ds_w7
save(walking_speed, file = "../RData/w7/walking_speed.RData")

ELSA_m_ds_w7 <- ELSA_ds_w7
ELSA_m_ds_w7$walking_speed <- car::recode(ELSA_m_ds_w7$walking_speed, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'ELSA_m_ds_w7', ELSA_m_ds_w7)
#opal.symbol_import(o,'ELSA_m_ds_w7', project='_Athlos_Harm_Dataset')
```


## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Freq25uencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.

**R script:**

```{r summ}
ELSA_ds_w1$walking_speed <- labelled(ELSA_ds_w1$walking_speed, labels = c(Presence=0, Absence=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w2$walking_speed <- labelled(ELSA_ds_w2$walking_speed, labels = c(Presence=0, Absence=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w3$walking_speed <- labelled(ELSA_ds_w3$walking_speed, labels = c(Presence=0, Absence=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w4$walking_speed <- labelled(ELSA_ds_w4$walking_speed, labels = c(Presence=0, Absence=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w5$walking_speed <- labelled(ELSA_ds_w5$walking_speed, labels = c(Presence=0, Absence=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w6$walking_speed <- labelled(ELSA_ds_w6$walking_speed, labels = c(Presence=0, Absence=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
ELSA_ds_w7$walking_speed <- labelled(ELSA_ds_w7$walking_speed, labels = c(Presence=0, Absence=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))

tt <-    frq(ELSA_ds_w1$walking_speed)[[1]][,c(1:2,4)]
tt[4] <- frq(ELSA_ds_w2$walking_speed)[[1]][,c(4)]
tt[5] <- frq(ELSA_ds_w3$walking_speed)[[1]][,c(4)]
tt[6] <- frq(ELSA_ds_w4$walking_speed)[[1]][,c(4)]
tt[7] <- frq(ELSA_ds_w5$walking_speed)[[1]][,c(4)]
tt[8] <- frq(ELSA_ds_w6$walking_speed)[[1]][,c(4)]
tt[9] <- frq(ELSA_ds_w7$walking_speed)[[1]][,c(4)]
tt[13,] <- c("n", "sample size", 
             length(ELSA_ds_w1$walking_speed), length(ELSA_ds_w2$walking_speed), length(ELSA_ds_w3$walking_speed),
             length(ELSA_ds_w4$walking_speed), length(ELSA_ds_w5$walking_speed), length(ELSA_ds_w6$walking_speed),     
             length(ELSA_ds_w7$walking_speed))
names(tt)<-c("val", "label", "w1", "w2", "w3", "w4", "w5", "w6", "w7")
kable(tt)

dbb <- merge(ELSA_m_ds_w1[,c("id","walking_speed")], ELSA_m_ds_w2[,c("id","walking_speed")], by="id", suffixes = c(".w1",".w2"), all=T)
dbb <- merge(dbb, ELSA_m_ds_w3[,c("id","walking_speed")], by="id", all=T)
dbb <- merge(dbb, ELSA_m_ds_w4[,c("id","walking_speed")], by="id", suffixes = c(".w3",".w4"), all=T)
dbb <- merge(dbb, ELSA_m_ds_w5[,c("id","walking_speed")], by="id", all=T)
dbb <- merge(dbb, ELSA_m_ds_w6[,c("id","walking_speed")], by="id", suffixes = c(".w5",".w6"), all=T)
dbb <- merge(dbb, ELSA_m_ds_w7[,c("id","walking_speed")], by="id", all=T)
names(dbb) <- c("id", "w1", "w2", "w3", "w4", "w5", "w6", "w7")
v.dbb <- paste(dbb[,2],dbb[,3],dbb[,4],dbb[,5],dbb[,6],dbb[,7],dbb[,8],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])
```


# Quality estimation
The measure is created averaging the times obtained in the one/two trial/s available.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
