---
title: "Day of interview"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE, echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_albert.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

The description of harmonised variable is the following:
  
* Name: `dintw`
* Label: `day of interview`
* Type of variable: `countinous`
* Missings: 
    + `991 = CAPI/interviewer error`
    + `992 = Impute`
    + `993 = Disable to measure`
    + `994 = Not attempt/not done`
    + `995 = Does not answer`
    + `996 = Not applicable`
    + `997 = Refuse`
    + `998 = Do not know`
    + `999 = Missing`


# Data process

## Wave 1 

There is no variable.

## Wave 2 

There is no variable.


## Wave 3 

### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `date10`
* Label: `Date of 10 year follow up`
* Type of variable: `countinous`

```{r assign3}
opal.assign.table.tibble(o, 'ATTICA_w3_dinter','ATTICA.ATTICA_Followup2',
                         variables=list('date10'), missings = TRUE)
```

```{r local3}
ATTICA_w3_dinter <- opal.execute(o,'ATTICA_w3_dinter')
ATTICA_w3_dinter$dinter <- as.numeric(format(ATTICA_w3_dinter$date10, '%d'))
Continuous_summary(var = ATTICA_w3_dinter$dinter, missing_values = NA)
ggplot(ATTICA_w3_dinter, aes(x=factor(dinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Day of interview") + ylab("Frequency")
```


### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo3}
ATTICA_ds_w3 <- tibble(id=ATTICA_w3_dinter$id)
ATTICA_ds_w3$dintw <- car::recode(ATTICA_w3_dinter$dinter, "NA=999")
ATTICA_ds_w3$dintw <- labelled(ATTICA_ds_w3$dintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

### Statistics of the new harmonised variable
```{r descript3}
Continuous_summary(var = ATTICA_ds_w3$dintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ATTICA_ds_w3, aes(dintw)) + geom_histogram(stat="count", fill="steelblue") + xlab("Day of birth") + ylab("Frequency") + xlim(1,31)
```

### Validation
```{r crosstabulation3}
BeforeH <- table(ATTICA_w3_dinter$dinter, useNA = "ifany")
AfterH <- table(ATTICA_ds_w3$dintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:31], "NA->999")
C
```


#### Quality estimation
No comments.


```{r save, echo=FALSE}
dintw <- ATTICA_ds_w3
save(dintw, file = "../RData/w3/dintw.RData")
rm(dintw)
```

```{r closeRsession, echo=FALSE}
opal.logout(o)
```






