---
title: "Year of interview"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE, echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_albert.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

The description of harmonised variable is the following:
  
* Name: `yintw`
* Label: `year of interview`
* Type of variable: `countinous`
* Missings: 
    + `991 = CAPI/interviewer error`
    + `992 = Impute`
    + `993 = Disable to measure`
    + `994 = Not attempt/not done`
    + `995 = Does not answer`
    + `996 = Not applicable`
    + `997 = Refuse`
    + `998 = Do not know`
    + `999 = Missing`


# Data process

## Wave 1 

### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `entry`
* Label: `Entry code`
* Type of variable: `countinous`


```{r assign1}
opal.assign.table.tibble(o, 'ATTICA_w1_yinter','ATTICA.ATTICA_Baseline',
                         variables=list('entry'), missings = TRUE)
```

```{r local1}
ATTICA_w1_yinter <- opal.execute(o,'ATTICA_w1_yinter')
Categorical_summary(var = ATTICA_w1_yinter$entry, missing_values = NA)
ggplot(ATTICA_w1_yinter, aes(x=factor(entry))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```


### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable.

R code of the ALGORITHM:

```{r harmo1}
ATTICA_ds_w1 <- tibble(id=ATTICA_w1_yinter$id)
ATTICA_ds_w1$yintw <- as.numeric(ATTICA_w1_yinter$entry)
ATTICA_ds_w1$yintw <- labelled(ATTICA_ds_w1$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

### Statistics of the new harmonised variable
```{r descript1}
Categorical_summary(var = ATTICA_ds_w1$yintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ATTICA_ds_w1, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

### Validation
```{r crosstabulation1}
BeforeH <- table(ATTICA_w1_yinter$entry, useNA = "ifany")
AfterH <- table(ATTICA_ds_w1$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
C
```


## Wave 2 

### Study-specific variables

The study-specific variable elected to be harmonised is:


```{r assign2}
opal.assign.table.tibble(o, 'ATTICA_w2_id','ATTICA.ATTICA_Followup1',
                         variables=list('FU'), missings = TRUE)
```

```{r local2}
ATTICA_w2_id <- opal.execute(o,'ATTICA_w2_id')
Continuous_summary(var = as.numeric(ATTICA_w2_id$id), missing_values = NA)
```


### Harmonisation algorithm
As we don't have the year of interview but all the interviews were in 2006 the variable year of interview is going to be computed as 2006. 

R code of the ALGORITHM:

```{r harmo2}
ATTICA_ds_w2 <- tibble(id=ATTICA_w2_id$id)
ATTICA_ds_w2$yintw <- 2006
```

### Statistics of the new harmonised variable
```{r descript2}
Categorical_summary(var = ATTICA_ds_w2$yintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ATTICA_ds_w2, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```



## Wave 3 

### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `date10`
* Label: `Date of 10 year follow up`
* Type of variable: `date`

```{r assign3}
opal.assign.table.tibble(o, 'ATTICA_w3_dinter','ATTICA.ATTICA_Followup2',
                         variables=list('date10'), missings = TRUE)
```

```{r local3}
ATTICA_w3_dinter <- opal.execute(o,'ATTICA_w3_dinter')
ATTICA_w3_dinter$yinter <- as.numeric(format(ATTICA_w3_dinter$date10, '%Y'))
Categorical_summary(var = ATTICA_w3_dinter$yinter, missing_values = NA)
ggplot(ATTICA_w3_dinter, aes(x=factor(yinter))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

There are 7 values 2103 in year of interview that are going to be recoded as 2013. 

### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as 2013 since is the most frequent value. 

R code of the ALGORITHM:

```{r harmo3}
ATTICA_ds_w3 <- tibble(id=ATTICA_w3_dinter$id)
ATTICA_ds_w3$yintw <- car::recode(ATTICA_w3_dinter$yinter, "NA=999; 2103=2013")
ATTICA_ds_w3$yintw <- labelled(ATTICA_ds_w3$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

### Statistics of the new harmonised variable
```{r descript3}
Categorical_summary(var = ATTICA_ds_w3$yintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ATTICA_ds_w3, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

### Validation
```{r crosstabulation3}
BeforeH <- table(ATTICA_w3_dinter$yinter, useNA = "ifany")
BeforeH <- c(BeforeH[1:2], sum(BeforeH[3:4]), BeforeH[5])
AfterH <- table(ATTICA_ds_w3$yintw)[c(2:4,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2011", "2012", "(2103,2013)->2013", "NA->999")
C
```


#### Quality estimation
The date was the same as the study specific variable taking into account the wave time lapse information at wave 1 and 3, taking into account that the missing values have been recoded as the most frequent year between the no missing values. 

The authors of the study do not reveal the exact date of the interview of wave 2 for harmonization purposes we assume is that of the wave (based on study time lapse information).




```{r save, echo=FALSE}
yintw <- ATTICA_ds_w1
save(yintw, file = "../RData/w1/yintw.RData")
rm(yintw)

yintw <- ATTICA_ds_w2
save(yintw, file = "../RData/w2/yintw.RData")
rm(yintw)

yintw <- ATTICA_ds_w3
save(yintw, file = "../RData/w3/yintw.RData")
rm(yintw)
```

```{r closeRsession, echo=FALSE}
opal.logout(o)
```



