---
title: "Cardiac disorders"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `cd_all`
* Variable label: `History of Cardiac disorders`
* Variable description: `The participant has been diagnosed by one or more of the following conditions: angina, myocardial infarction, heart attack, coronary heart disease, congestive heart failure, heart murmur, valve disease`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | No, the participant has not been diagnosed of any of these conditions
1        | Yes, the participant has been diagnosed by any of these conditions

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "History of Cardiac disorders"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process



## Finland


### Wave 1

#### Study-specific variable description

| **Name** | `h_angina` |`mi_ha`|`BA12A`|
|-|-|-|-|
| **Label** |`History of angina`|`Myocardial infarction or heart attack`| `Illness: other heart disease, type`|
| **Table name**  | `h_angina`|`mi_ha`| `t00_athlos_2017_02_23` |
| **Categories** | `0 = no history of angina`<br/>`1 = history of angina` |`0 = No`<br/>`1 = Yes`|`1 = congenital heart disease`<br/>`2 = valve disorder`<br/>`3 = heart nerve disorder`<br/>`4 = other heart disease`|
| **Missings** | `999 = Missing`|`999 = Missing`|`NA`|
| **Description** |  |  |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'Health20002011_w1','Health2000-2011.t00_athlos_2017_02_23',variables=list('BA12A'), missings = T)
Health20002011_w1 <- opal.execute(o,'Health20002011_w1')
load(paste0(datafolder,"w1/h_angina.RData"))
Health20002011_w1$h_angina <- h_angina$h_angina
rm(h_angina)
load(paste0(datafolder,"w1/mi_ha.RData"))
Health20002011_w1$mi_ha <- mi_ha$mi_ha
rm(mi_ha)

```

```{r local w1, echo=F}

vbl <- Health20002011_w1$BA12A
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(Health20002011_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w1, aes(x=factor(BA12A))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w1$h_angina
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(Health20002011_w1)[3])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(Health20002011_w1, aes(x=factor(h_angina))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w1$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(Health20002011_w1)[4])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(Health20002011_w1, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `cd_all` from the study-specific variable it has to be recoded as follows:

* `all 0 except BA12A and BA12A != 2 into 0`
* `some 1 into 1`
* `999, NA into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
Health20002011_ds_w1 <- tibble(id=Health20002011_w1$id)
Health20002011_ds_w1$cd_all <- rep(999,length(Health20002011_w1$id))
Health20002011_ds_w1$cd_all[which(Health20002011_w1$h_angina == 0 & Health20002011_w1$mi_ha == 0 & (Health20002011_w1$BA12A %in% c(1,3,4) | is.na(Health20002011_w1$BA12A)))] <- 0
Health20002011_ds_w1$cd_all[which(Health20002011_w1$h_angina == 1 | Health20002011_w1$mi_ha == 1 | Health20002011_w1$BA12A == 2)] <- 1

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- Health20002011_ds_w1$cd_all
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(Health20002011_ds_w1, aes(x=factor(cd_all))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}

AfterH <- table(Health20002011_ds_w1$cd_all)
X <- c(
  sum(Health20002011_w1$h_angina == 0 & Health20002011_w1$mi_ha == 0 & (Health20002011_w1$BA12A %in% c(1,3,4) | is.na(Health20002011_w1$BA12A)),na.rm=T),
  sum(Health20002011_w1$h_angina == 1 | Health20002011_w1$mi_ha == 1 | Health20002011_w1$BA12A == 2,na.rm=T)
)
BeforeH <- c(X[1:2],length(Health20002011_w1$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0 & BA12A!=2->0","some 1/BA12A==2->1","NA,999->999")
kable(C)

```



### Wave 2


#### Study-specific variable description


| **Name** | `h_angina` |`mi_ha`|
|-|-|-|
| **Label** |`History of angina`|`Myocardial infarction or heart attack`|
| **Table name**  | `h_angina`|`mi_ha`|
| **Categories** | `0 = no history of angina`<br/>`1 = history of angina` |`0 = No`<br/>`1 = Yes`|
| **Missings** | `999 = Missing`|`999 = Missing`|
| **Description** |  |  |

```{r assign w2, echo=F}

load(paste0(datafolder,"w2/h_angina.RData"))
load(paste0(datafolder,"w2/mi_ha.RData"))
Health20002011_w2 <- tibble(id=h_angina$id)
Health20002011_w2$h_angina <- h_angina$h_angina
Health20002011_w2$mi_ha <- mi_ha$mi_ha
rm(h_angina)
rm(mi_ha)
```

```{r local w2, echo=F}

vbl <- Health20002011_w2$h_angina
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(Health20002011_w2)[2])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(Health20002011_w2, aes(x=factor(h_angina))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w2$mi_ha
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = names(Health20002011_w2)[3])
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(Health20002011_w2, aes(x=factor(mi_ha))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cd_all` from the study-specific variable it has to be recoded as follows:

* `all 0 into 0`
* `some 1 into 1`
* `otherwise, keep up missing values into themselves`

**R script:**

```{r harmo w2}

# Categorical variable harmonization
Health20002011_ds_w2 <- tibble(id=Health20002011_w2$id)
Health20002011_ds_w2$cd_all <- rep(999,length(Health20002011_ds_w2$id))
Health20002011_ds_w2$cd_all[which(Health20002011_w2$h_angina == 0 & Health20002011_w2$mi_ha == 0)] <- 0
Health20002011_ds_w2$cd_all[which(Health20002011_w2$h_angina == 1 | Health20002011_w2$mi_ha == 1)] <- 1

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- Health20002011_ds_w2$cd_all
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(Health20002011_ds_w2, aes(x=factor(cd_all))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w2, echo=F, results='asis'}

AfterH <- table(Health20002011_ds_w2$cd_all)
X <- c(
  sum(Health20002011_w2$h_angina == 0 & Health20002011_w2$mi_ha == 0,na.rm = T),
  sum(Health20002011_w2$h_angina == 1 | Health20002011_w2$mi_ha == 1,na.rm=T)
)
BeforeH <- c(X[1:2],length(Health20002011_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","999->999")
kable(C)

```





## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.

**R script:**

```{r summ}
Health20002011_ds_w1$cd_all <- labelled(Health20002011_ds_w1$cd_all, labels = cat_label)
label(Health20002011_ds_w1$cd_all) <- ds_label
Health20002011_ds_w2$cd_all <- labelled(Health20002011_ds_w2$cd_all, labels = cat_label)
label(Health20002011_ds_w2$cd_all) <- ds_label

Health20002011_m_ds_w1 <- Health20002011_ds_w1
Health20002011_m_ds_w1$cd_all <- car::recode(Health20002011_m_ds_w1$cd_all, "miss_values_vector=NA")
Health20002011_m_ds_w2 <- Health20002011_ds_w2
Health20002011_m_ds_w2$cd_all <- car::recode(Health20002011_m_ds_w2$cd_all, "miss_values_vector=NA")

tt <-    frq(Health20002011_ds_w1$cd_all)[[1]][,c(1:2,4)]
tt[4] <- frq(Health20002011_ds_w2$cd_all)[[1]][,c(4)]
tt[13,] <- c("n", "sample size", 
             length(Health20002011_ds_w1$cd_all), length(Health20002011_ds_w2$cd_all)
             )
names(tt)<-c("val", "label", "w1", "w2")
kable(tt)

dbb <- merge(Health20002011_m_ds_w1[,c("id","cd_all")], Health20002011_m_ds_w2[,c("id","cd_all")], by="id", suffixes = c(".w1",".w2"), all=T)
names(dbb) <- c("id", "w1", "w2")
v.dbb <- paste(dbb[,2],dbb[,3],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])
```



# Quality estimation

The harmonized variable contains information about angina, myocardial infarction and valve disorder.


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.Health20002011 <- list(w1 = Health20002011_ds_w1, w2 = Health20002011_ds_w2)

for(index in seq_along(l.Health20002011)){
  cd_all <- l.Health20002011[[index]]
  save(cd_all, file = paste0(datafolder,names(l.Health20002011)[index],"/cd_all.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





