---
title: "Cancer"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `cancer`
* Variable label: `Any malignancy (C00-D48) / information about past or current neoplasm (benign, in situ, malignant)`
* Variable description: `cancer diagnosis since the last interview`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | no cancer
1        | cancer

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Short name: `cancer_age`
* Variable label: `Age of cancer diagnosis`
* Variable description: `Age of each episode of cancer`
* Domain: `Diseases`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "Any malignancy (C00-D48) / information about past or current neoplasm (benign, in situ, malignant)"
ds_label_age <- "Age of cancer diagnosis"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
cont_label <- cat_label[3:11]
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process



## Finland


### Wave 1

#### Study-specific variable description

| **Name** | `BA32` |`BA32A_1`|`BA32A_1`|`ybirth`|
|-|-|-|-|
| **Label** | `Illness: cancer` |`Illness: 1. cancer, year when diagnosed`|`Illness: 2. cancer, year when diagnosed`|`Year of birth`|
| **Table name**  | `t00_athlos_2017_02_23` | `t00_athlos_2017_02_23` | `t00_athlos_2017_02_23` |`ybirth`|
| **Categories** | `0 = no`<br/>`1 = yes` | `continuous` | `continuous` |`continuous` |
| **Missings** | `NA` | `NA` | `NA` |  |
| **Description** |  |  |  |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'Health20002011_w1','Health2000-2011.t00_athlos_2017_02_23',variables=list('BA32','BA32A_1','BA32A_2'), missings = T)
Health20002011_w1 <- opal.execute(o,'Health20002011_w1')
load(paste0(datafolder,"w1/ybirth.RData"))
Health20002011_w1 <- left_join(Health20002011_w1,ybirth, by="id")

```

```{r local w1, echo=F}

vbl <- Health20002011_w1$BA32
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(Health20002011_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w1, aes(x=factor(BA32))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w1$BA32A_1
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(Health20002011_w1)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(Health20002011_w1, aes(BA32A_1)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w1$BA32A_2
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(Health20002011_w1)[4])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(Health20002011_w1, aes(BA32A_2)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w1$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(Health20002011_w1)[5])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(Health20002011_w1, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1900,1970)

```

#### Harmonisation algorithm

To compute `cancer` from the study-specific variable it has to be recoded as follows:

* `keep up 0 into 0`
* `keep up 1 into 1`
* `NA into 999`

To compute `cancer_age` from the study-specific variable it has to be recoded as follows:

* `if cancer == 1, cancer_age = min(BA32A_1,BA32A_2) - ybirth`
* `if cancer == 0, cancer_age = 996`
* `BA32<ybirth into 991`
* `cancer == 999 into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
Health20002011_ds_w1 <- tibble(id=Health20002011_w1$id)
Health20002011_ds_w1$cancer <- car::recode(Health20002011_w1$BA32, "NA = 999")

# Continuous variable harmonization
Health20002011_ds_w1$cancer_age <- rep(999,length(Health20002011_w1$id))
Health20002011_ds_w1$cancer_age[which(Health20002011_ds_w1$cancer == 0)] <- 996
Health20002011_ds_w1$cancer_age[which(Health20002011_ds_w1$cancer == 1)] <- pmin(Health20002011_w1$BA32A_1[which(Health20002011_ds_w1$cancer == 1)],Health20002011_w1$BA32A_2[which(Health20002011_ds_w1$cancer == 1)],na.rm=T) - Health20002011_w1$ybirth[which(Health20002011_ds_w1$cancer == 1)]
Health20002011_ds_w1$cancer_age <- car::recode(Health20002011_ds_w1$cancer_age, "NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- Health20002011_ds_w1$cancer
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(Health20002011_ds_w1, aes(x=factor(cancer))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- Health20002011_ds_w1$cancer_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(Health20002011_ds_w1, aes(cancer_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(0,95)

```


#### Validation

```{r crosstabulation w1, echo=F}

continuous <- c(sum(Health20002011_ds_w1$cancer_age==996),sum(Health20002011_ds_w1$cancer_age!=996))
X <- table(Health20002011_ds_w1$cancer, useNA = "ifany")
dichotomous <- c(X[1],sum(X[2:3]))
C <- rbind(continuous,dichotomous)
colnames(C) <- c("0<-->996","1,NA<-->(possibly missing) age of diagnostic")
kable(C,caption = "Continuous vs Dichotomous")

```



### Wave 2


#### Study-specific variable description


| **Name** | `BA32` |`age`|`yintw (w1)`|`yintw (w2)`|
|-|-|-|-|-|
| **Label** | `Illness: cancer` |`age`|`year of interview`|`year of interview`|
| **Table name**  | `t11_athlos_2017_02_27` |`age`|`yintw`|`yintw`|
| **Categories** | `0 = no`<br/>`1 = yes` |`continuous` |`continuous` | `continuous` | 
| **Missings** | `NA` |  |  |  |
| **Description** |  |  |  |  |


```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'Health20002011_w2','Health2000-2011.t11_athlos_2017_02_27',variables=list('BA32'), missings = T)
Health20002011_w2 <- opal.execute(o,'Health20002011_w2')
load(paste0(datafolder,"w2/age.RData"))
Health20002011_w2 <- left_join(Health20002011_w2,age, by="id")
rm(age)
load(paste0(datafolder,"w1/yintw.RData"))
Health20002011_w2 <- left_join(Health20002011_w2,yintw, by="id")
names(Health20002011_w2)[4] <- "yintw_w1"
rm(yintw)
load(paste0(datafolder,"w2/yintw.RData"))
Health20002011_w2 <- left_join(Health20002011_w2,yintw, by="id")
names(Health20002011_w2)[5] <- "yintw_w2"
rm(yintw)

```

```{r local w2, echo=F}

vbl <- Health20002011_w2$BA32
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(Health20002011_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w2, aes(x=factor(BA32))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w2$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(Health20002011_w2)[3])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(Health20002011_w2, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(25,105)

vbl <- Health20002011_w2$yintw_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(Health20002011_w2)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w2, aes(x=factor(yintw_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w2$yintw_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(Health20002011_w2)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w2, aes(x=factor(yintw_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cancer` from the study-specific variable it has to be recoded as follows:

* `keep up 0 into 0`
* `BA32 (w2) == 1 & (BA32A_2 (w1) != NA | BA32 (w1) == 0)`
* `NA into 999`

To compute `cancer_age` from the study-specific variable it has to be recoded as follows:

* `if cancer == 1 in w2 and 0 in w1, cancer_age (w2) = age - (year of interview (w2) - year of interview (w1))/2`
* `if cancer ==1 and BA32A_2 (w1) != NA, cancer_age = max(BA32A_1,BA32A_2) - ybirth`
* `if cancer == 0, cancer_age = 996`
* `otherwise into 999`

**R script:**

```{r harmo w2}

# We use the harmonized variable of wave 1 instead of the study-specific variable
Health20002011_w2 <- left_join(Health20002011_w2, Health20002011_w1, by = "id",suffix=c("","_w1"))

# Categorical variable harmonization
Health20002011_ds_w2 <- tibble(id=Health20002011_w2$id)
Health20002011_ds_w2$cancer <- rep(999,length(Health20002011_w2$id))
Health20002011_ds_w2$cancer[which(Health20002011_w2$BA32==0)] <- 0
# Individuals having cancer different from the harmonized om wave 1, so they did not have cancer till then or we harmonized the other reported cancer.
Health20002011_ds_w2$cancer[which(Health20002011_w2$BA32==1 & (Health20002011_w2$BA32_w1==0 | !is.na(Health20002011_w2$BA32A_2)))] <- 1

# Continuous variable harmonization
Health20002011_ds_w2$cancer_age <- rep(999,length(Health20002011_ds_w2$id))
Health20002011_ds_w2$cancer_age[which(Health20002011_ds_w2$cancer==0)] <- 996
Health20002011_ds_w2$cancer_age[which(Health20002011_ds_w2$cancer==1 & Health20002011_w2$BA32_w1==0)] <- Health20002011_w2$age[which(Health20002011_ds_w2$cancer==1 & Health20002011_w2$BA32_w1==0)] - (Health20002011_w2$yintw_w2[which(Health20002011_ds_w2$cancer==1 & Health20002011_w2$BA32_w1==0)] - Health20002011_w2$yintw_w1[which(Health20002011_ds_w2$cancer==1 & Health20002011_w2$BA32_w1==0)])/2
Health20002011_ds_w2$cancer_age[which(Health20002011_ds_w2$cancer==1 & !is.na(Health20002011_w2$BA32_2))] <- pmax(Health20002011_w2$BA32A_1[which(Health20002011_ds_w2$cancer==1 & !is.na(Health20002011_w2$BA32_2))],Health20002011_w2$BA32A_2[which(Health20002011_ds_w2$cancer==1 & !is.na(Health20002011_w2$BA32_2))],na.rm=T) - Health20002011_w2$ybirth[which(Health20002011_ds_w2$cancer==1 & !is.na(Health20002011_w2$BA32_2))]
Health20002011_ds_w2$cancer_age <- car::recode(Health20002011_ds_w2$cancer_age, "NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- Health20002011_ds_w2$cancer
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(Health20002011_ds_w2, aes(x=factor(cancer))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- Health20002011_ds_w2$cancer_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(Health20002011_ds_w2, aes(cancer_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(35,90)

```


#### Validation

```{r crosstabulation w2, echo=F, results='asis'}

continuous <- c(sum(Health20002011_ds_w1$cancer_age==996),sum(Health20002011_ds_w1$cancer_age!=996))
X <- table(Health20002011_ds_w1$cancer, useNA = "ifany")
dichotomous <- c(X[1],sum(X[2:3]))
C <- rbind(continuous,dichotomous)
colnames(C) <- c("0<-->996","1,NA<-->(possibly missing) age of diagnostic")
kable(C,caption = "Continuous vs Dichotomous")

```





## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.

**R script:**

```{r summ}
Health20002011_ds_w1$cancer <- labelled(Health20002011_ds_w1$cancer, labels = cat_label)
label(Health20002011_ds_w1$cancer) <- ds_label
Health20002011_ds_w1$cancer_age <- labelled(Health20002011_ds_w1$cancer_age, labels = cont_label)
label(Health20002011_ds_w1$cancer_age) <- ds_label_age
Health20002011_ds_w2$cancer <- labelled(Health20002011_ds_w2$cancer, labels = cat_label)
label(Health20002011_ds_w2$cancer) <- ds_label
Health20002011_ds_w2$cancer_age <- labelled(Health20002011_ds_w2$cancer_age, labels = cont_label)
label(Health20002011_ds_w2$cancer_age) <- ds_label_age

Health20002011_m_ds_w1 <- Health20002011_ds_w1
Health20002011_m_ds_w1$cancer <- car::recode(Health20002011_m_ds_w1$cancer, "miss_values_vector=NA")
Health20002011_m_ds_w2 <- Health20002011_ds_w2
Health20002011_m_ds_w2$cancer <- car::recode(Health20002011_m_ds_w2$cancer, "miss_values_vector=NA")

tt <-    frq(Health20002011_ds_w1$cancer)[[1]][,c(1:2,4)]
tt[4] <- frq(Health20002011_ds_w2$cancer)[[1]][,c(4)]
tt[13,] <- c("n", "sample size", 
             length(Health20002011_ds_w1$cancer), length(Health20002011_ds_w2$cancer)
             )
names(tt)<-c("val", "label", "w1", "w2")
kable(tt)

dbb <- merge(Health20002011_m_ds_w1[,c("id","cancer")], Health20002011_m_ds_w2[,c("id","cancer")], by="id", suffixes = c(".w1",".w2"), all=T)
names(dbb) <- c("id", "w1", "w2")
v.dbb <- paste(dbb[,2],dbb[,3],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])
```



# Quality estimation

No comments


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.Health20002011 <- list(w1 = Health20002011_ds_w1, w2 = Health20002011_ds_w2)

for(index in seq_along(l.Health20002011)){
  cancer <- l.Health20002011[[index]]
  save(cancer, file = paste0(datafolder,names(l.Health20002011)[index],"/cancer.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





