---
title: "Diabetes"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `h_diabetes`
* Variable label: `History of  Diabetes mellitus`
* Variable description: `History of diabetes or high blood sugar`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Not Diabetes or high blood sugar
1        | Diabetes or high blood sugar

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Short name: `h_diabetes_age`
* Variable label: `Age first diagnosed diabetes`
* Variable description: `The age first told had diabetes or high blood sugar diagnosis`
* Domain: `Diseases`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "History of diabetes"
ds_label_age <- "Age first diagnosed diabetes"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
cont_label <- cat_label[3:11]
datafolder <- "../RData/"
sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process



## Finland


### Wave 1

#### Study-specific variable description

| **Name** | `BA26` |`BA26A`|`ybirth`|
|-|-|-|-|
| **Label** | `Illness: diabetes` |`Illness: diabetes, year when diagnosed`|`Year of birth`|
| **Table name**  | `t00_athlos_2017_02_23` | `t00_athlos_2017_02_23` |`ybirth`|
| **Categories** | `1 = yes; 0 = no` | `continuous` | `continuous` |
| **Missings** | `NA` | `NA` |  |
| **Description** |  |  |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'Health20002011_w1','Health2000-2011.t00_athlos_2017_02_23',variables=list('BA26','BA26A'), missings = T)
Health20002011_w1 <- opal.execute(o,'Health20002011_w1')
load(paste0(datafolder,"w1/ybirth.RData"))
Health20002011_w1 <- left_join(Health20002011_w1,ybirth, by="id")

```

```{r local w1, echo=F}

vbl <- Health20002011_w1$BA26
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(Health20002011_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w1, aes(x=factor(BA26))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w1$BA26A
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(Health20002011_w1)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(Health20002011_w1, aes(BA26A)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1915,2000)

vbl <- Health20002011_w1$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(Health20002011_w1)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(Health20002011_w1, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1900,1970)

```

#### Harmonisation algorithm

To compute `h_diabetes` from the study-specific variable it has to be recoded as follows:

* `keep up 0 into 0`
* `keep up 1 into 1`
* `NA into 999`

To compute `h_diabetes_age` from the study-specific variable it has to be recoded as follows:

* `if h_diabetes == 1, h_diabetes_age = BA26A - ybirth`
* `if h_diabetes == 0, h_diabetes_age = 996`
* `h_diabetes == 999 into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
Health20002011_ds_w1 <- tibble(id=Health20002011_w1$id)
Health20002011_ds_w1$h_diabetes <- car::recode(Health20002011_w1$BA26, "NA = 999")

# Continuous variable harmonization
diabetes_age <- Health20002011_w1$BA26A[Health20002011_ds_w1$h_diabetes == 1]-Health20002011_w1$ybirth[Health20002011_ds_w1$h_diabetes == 1]
Health20002011_ds_w1$h_diabetes_age <- car::recode(Health20002011_ds_w1$h_diabetes, "0 = 996; 1 = diabetes_age")
Health20002011_ds_w1$h_diabetes_age <- car::recode(Health20002011_ds_w1$h_diabetes_age, "NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- Health20002011_ds_w1$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(Health20002011_ds_w1, aes(x=factor(h_diabetes))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- Health20002011_ds_w1$h_diabetes_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(Health20002011_ds_w1, aes(h_diabetes_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(0,95)

```


#### Validation

```{r crosstabulation w1, echo=F}

AfterH <- table(Health20002011_ds_w1$h_diabetes)
BeforeH <- table(Health20002011_w1$BA26, useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999")
kable(C)

```



### Wave 2


#### Study-specific variable description

| **Name** | `BA26` |`BA26A`|`ybirth`|
|-|-|-|-|
| **Label** | `Illness: diabetes` |`Illness: diabetes, year when diagnosed`|`Year of birth`|
| **Table name**  | `t11_athlos_2017_02_27` | `t11_athlos_2017_02_27` |`ybirth`|
| **Categories** | `1 = yes; 0 = no` | `continuous` | `continuous` |
| **Missings** | `NA` | `NA` | `999 = Missing` |
| **Description** |  |  |  |

```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'Health20002011_w2','Health2000-2011.t11_athlos_2017_02_27',variables=list('BA26','BA26A'), missings = T)
Health20002011_w2 <- opal.execute(o,'Health20002011_w2')
load(paste0(datafolder,"w2/ybirth.RData"))
Health20002011_w2 <- left_join(Health20002011_w2,ybirth, by="id")
```

```{r local w2, echo=F}

vbl <- Health20002011_w2$BA26
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(Health20002011_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w2, aes(x=factor(BA26))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w2$BA26A
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(Health20002011_w2)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(Health20002011_w2, aes(BA26A)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1930,2015)

vbl <- Health20002011_w2$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(Health20002011_w2)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(Health20002011_w2, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1905,1970)

```


#### Harmonisation algorithm

To compute `h_diabetes` from the study-specific variable it has to be recoded as follows:

* `BA26 (w1) == 0 and BA26 (w2) == 0 into 0`
* `BA26 (w1) == 1 or BA26 (w2) == 1 into 1`
* `otherwise into 999`

To compute `h_diabetes_age` from the study-specific variable it has to be recoded as follows:

* `if h_diabetes == 1 in w2 and missing in w1, h_diabetes_age = BA26A - ybirth`
* `if h_diabetes == 1 in w2 and no-missing in w1, h_diabetes_age = as in w1`
* `if h_diabetes == 0, h_diabetes_age = 996`
* `BA26A == NA or h_diabetes == missing into 999`

**R script:**

```{r harmo w2}

# We use the harmonized variable of wave 1 instead of the study-specific variable
Health20002011_w2 <- left_join(Health20002011_w2, Health20002011_ds_w1, by = "id")

# Categorical variable harmonization
Health20002011_ds_w2 <- tibble(id=Health20002011_w2$id)
Health20002011_ds_w2$h_diabetes <- rep(999,length(Health20002011_ds_w2$id))
Health20002011_ds_w2$h_diabetes[which(((!is.na(Health20002011_w2$BA26)) & Health20002011_w2$BA26 == 0) & (Health20002011_w2$h_diabetes != 1))] <- 0
Health20002011_ds_w2$h_diabetes[which(((!is.na(Health20002011_w2$BA26)) & Health20002011_w2$BA26 == 1) | ((!is.na(Health20002011_w2$h_diabetes)) & (!is.na(Health20002011_w2$BA26)) & Health20002011_w2$h_diabetes == 1))] <- 1

# Continuous variable harmonization
Health20002011_ds_w2$h_diabetes_age <- rep(999,length(Health20002011_ds_w2$id))
Health20002011_ds_w2$h_diabetes_age[which(Health20002011_ds_w2$h_diabetes==0)] <- 996
# if h_diabetes == 1 in w2 and missing in w1, h_diabetes_age = BA26A - ybirth
# avoid missings of ybirth
Health20002011_ds_w2$h_diabetes_age[which(Health20002011_ds_w2$h_diabetes==1 & !Health20002011_w2$ybirth %in% miss_values_vector & (is.na(Health20002011_w2$h_diabetes_age) | Health20002011_w2$h_diabetes_age %in% c(999,996)))] <- Health20002011_w2$BA26A[which(Health20002011_ds_w2$h_diabetes==1 & !Health20002011_w2$ybirth %in% miss_values_vector & (is.na(Health20002011_w2$h_diabetes_age) | Health20002011_w2$h_diabetes_age %in% c(999,996)))] - Health20002011_w2$ybirth[which(Health20002011_ds_w2$h_diabetes==1 & !Health20002011_w2$ybirth %in% miss_values_vector & (is.na(Health20002011_w2$h_diabetes_age) | Health20002011_w2$h_diabetes_age %in% c(999,996)))]
# if h_diabetes == 1 in w2 and no-missing in w1, h_diabetes_age = as in w1
Health20002011_ds_w2$h_diabetes_age[which(Health20002011_ds_w2$h_diabetes==1 & !(is.na(Health20002011_w2$h_diabetes_age) | Health20002011_w2$h_diabetes_age %in% c(999,996)))] <- Health20002011_w2$h_diabetes_age[which(Health20002011_ds_w2$h_diabetes==1 & !(is.na(Health20002011_w2$h_diabetes_age) | Health20002011_w2$h_diabetes_age %in% c(999,996)))]
Health20002011_ds_w2$h_diabetes_age <- car::recode(Health20002011_ds_w2$h_diabetes_age, "NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- Health20002011_ds_w2$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(Health20002011_ds_w2, aes(x=factor(h_diabetes))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- Health20002011_ds_w2$h_diabetes_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(Health20002011_ds_w2, aes(h_diabetes_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(0,100)

```


#### Validation

```{r crosstabulation w2, echo=F, results='asis'}

AfterH <- table(Health20002011_ds_w2$h_diabetes)
X <- c(
  sum(((!is.na(Health20002011_w2$BA26)) & Health20002011_w2$BA26 == 0) & (Health20002011_w2$h_diabetes != 1),na.rm = T),
  sum(((!is.na(Health20002011_w2$BA26)) & Health20002011_w2$BA26 == 1) | ((!is.na(Health20002011_w2$h_diabetes)) & (!is.na(Health20002011_w2$BA26)) & Health20002011_w2$h_diabetes == 1))
)
BeforeH <- c(X[1:2],length(Health20002011_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 2->0","some 1->1","NA->999")
kable(C)

# Checking
cat("There are 22 individuals whose answer in the first wave is that they were diagnosed to have diabetes and in the second wave is that they do not have it. We compute them in the harmonized variable as having diabetes.")
kable(frq(Health20002011_w2$BA26[Health20002011_w2$h_diabetes==1]), align = 'c')

Health20002011_w2$age_w2 <- Health20002011_w2$BA26A - Health20002011_w2$ybirth
kable(Health20002011_w2[!is.na(Health20002011_w2$h_diabetes_age) & !is.na(Health20002011_w2$BA26A) & !Health20002011_w2$h_diabetes_age %in% c(999,996) & (Health20002011_w2$age_w2!=Health20002011_w2$h_diabetes_age),], align = 'c',caption = 'There are 62 individuals which answer different diagnostic years in the two waves. We harmonize the age from the year answered in wave 1')

```





## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.

**R script:**

```{r summ}
Health20002011_ds_w1$h_diabetes <- labelled(Health20002011_ds_w1$h_diabetes, labels = cat_label)
label(Health20002011_ds_w1$h_diabetes) <- ds_label
Health20002011_ds_w1$h_diabetes_age <- labelled(Health20002011_ds_w1$h_diabetes_age, labels = cont_label)
label(Health20002011_ds_w1$h_diabetes_age) <- ds_label_age
Health20002011_ds_w2$h_diabetes <- labelled(Health20002011_ds_w2$h_diabetes, labels = cat_label)
label(Health20002011_ds_w2$h_diabetes) <- ds_label
Health20002011_ds_w2$h_diabetes_age <- labelled(Health20002011_ds_w2$h_diabetes_age, labels = cont_label)
label(Health20002011_ds_w2$h_diabetes_age) <- ds_label_age

Health20002011_m_ds_w1 <- Health20002011_ds_w1
Health20002011_m_ds_w1$h_diabetes <- car::recode(Health20002011_m_ds_w1$h_diabetes, "miss_values_vector=NA")
Health20002011_m_ds_w2 <- Health20002011_ds_w2
Health20002011_m_ds_w2$h_diabetes <- car::recode(Health20002011_m_ds_w2$h_diabetes, "miss_values_vector=NA")

tt <-    frq(Health20002011_ds_w1$h_diabetes)[[1]][,c(1:2,4)]
tt[4] <- frq(Health20002011_ds_w2$h_diabetes)[[1]][,c(4)]
tt[13,] <- c("n", "sample size", 
             length(Health20002011_ds_w1$h_diabetes), length(Health20002011_ds_w2$h_diabetes)
             )
names(tt)<-c("val", "label", "w1", "w2")
kable(tt)

dbb <- merge(Health20002011_m_ds_w1[,c("id","h_diabetes")], Health20002011_m_ds_w2[,c("id","h_diabetes")], by="id", suffixes = c(".w1",".w2"), all=T)
names(dbb) <- c("id", "w1", "w2")
v.dbb <- paste(dbb[,2],dbb[,3],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])
```



# Quality estimation

We assume that if an individual answers it has diabetes in one wave, it has diabetes for all the next waves. Individuals with discrepancies with respect to this criterium are specified at the end of each validation.



<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.Health20002011 <- list(w1 = Health20002011_ds_w1, w2 = Health20002011_ds_w2)

for(index in seq_along(l.Health20002011)){
  h_diabetes <- l.Health20002011[[index]]
  save(h_diabetes, file = paste0(datafolder,names(l.Health20002011)[index],"/h_diabetes.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





