---
title: "Chronic pulmonary disorders"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/cpdDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/cpdDS.R')
```



# Data process




## Finland


### Wave 1

#### Study-specific variable description

| **Name** | `BA05`|`BA06`|`BA07`| `BA05A`|`BA06A`|`BA07B`|`ybirth`|
|-|-|-|-|-|-|-|-|
| **Label** |`Illness: COPD`|`Illness: chronic bronchitis`|`Illness: other respiratory disease`|`Illness: COPD, year when diagnosed`|`Illness: chronic bronchitis, year when diagnosed`|`Illness: other respiratory disease, year when diagnosed`|`Year of birth`|
| **Table name**  | `t00_athlos_2017_02_23` | `t00_athlos_2017_02_23` | `t00_athlos_2017_02_23` | `t00_athlos_2017_02_23` | `t00_athlos_2017_02_23` | `t00_athlos_2017_02_23` |`ybirth`|
| **Categories** |  `0 = no`<br/>`1 = yes` | `0 = no`<br/>`1 = yes` | `0 = no`<br/>`1 = yes` |`continuous` | `continuous` |`continuous` | `continuous` |
| **Missings** | `NA` | `NA` | `NA` | `NA` |`NA`| `NA` |  |
| **Description** |  |  |  |  |  |  |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'Health20002011_w1','Health2000-2011.t00_athlos_2017_02_23',variables=list('BA05','BA06','BA07','BA05A','BA06A','BA07B'), missings = T)
Health20002011_w1 <- opal.execute(o,'Health20002011_w1')
load(paste0(datafolder,"w1/ybirth.RData"))
Health20002011_w1 <- left_join(Health20002011_w1,ybirth, by="id")
rm(ybirth)

```

```{r local w1, echo=F}

vbl <- Health20002011_w1$BA05
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(Health20002011_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w1, aes(x=factor(BA05))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w1$BA06
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(Health20002011_w1)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w1, aes(x=factor(BA06))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w1$BA07
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(Health20002011_w1)[6])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w1, aes(x=factor(BA07))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")


vbl <- Health20002011_w1$BA05A
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(Health20002011_w1)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(Health20002011_w1, aes(BA05A)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w1$BA06A
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(Health20002011_w1)[5])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(Health20002011_w1, aes(BA06A)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w1$BA07B
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(Health20002011_w1)[7])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(Health20002011_w1, aes(BA07B)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w1$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(Health20002011_w1)[8])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(Health20002011_w1 %>% filter(!vbl %in% miss_values_vector), aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `h_cpd` from the study-specific variable it has to be recoded as follows:

* `all 0 into 0`
* `some 1 into 1`
* `NA into 999`

To compute `h_cpd_age` from the study-specific variable it has to be recoded as follows:

* `if h_cpd == 1, h_cpd_age = min(BA05A,BA06A,BA07B) - ybirth`
* `if h_cpd == 0, h_cpd_age = 996`
* `if max(BA05A,BA06A,BA07B) - ybirth < 0, h_cpd_age = 991`
* `otherwise into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
Health20002011_ds_w1 <- tibble(id=Health20002011_w1$id)
Health20002011_ds_w1$h_cpd <- rep(999,length(Health20002011_w1$id))
Health20002011_ds_w1$h_cpd[which(Health20002011_w1$BA05 == 0 & Health20002011_w1$BA06 == 0 & Health20002011_w1$BA07 == 0)] <- 0
Health20002011_ds_w1$h_cpd[which(Health20002011_w1$BA05 == 1 | Health20002011_w1$BA06 == 1 | Health20002011_w1$BA07 == 1)] <- 1

# Continuous variable harmonization
Health20002011_ds_w1$h_cpd_age <- rep(999,length(Health20002011_w1$id))
Health20002011_ds_w1$h_cpd_age[which(Health20002011_ds_w1$h_cpd == 0)] <- 996
Health20002011_ds_w1$h_cpd_age[which(Health20002011_ds_w1$h_cpd == 1)] <- pmin(Health20002011_w1$BA05A[which(Health20002011_ds_w1$h_cpd == 1)],Health20002011_w1$BA06A[which(Health20002011_ds_w1$h_cpd == 1)],Health20002011_w1$BA07B[which(Health20002011_ds_w1$h_cpd == 1)],na.rm=T) - Health20002011_w1$ybirth[which(Health20002011_ds_w1$h_cpd == 1)]
Health20002011_ds_w1$h_cpd_age <- car::recode(Health20002011_ds_w1$h_cpd_age, "NA = 999")
Health20002011_ds_w1$h_cpd_age[which(Health20002011_ds_w1$h_cpd == 1 & pmax(Health20002011_w1$BA05A,Health20002011_w1$BA06A,Health20002011_w1$BA07B,na.rm=T)<Health20002011_w1$ybirth)] <- 991

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- Health20002011_ds_w1$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(Health20002011_ds_w1, aes(x=factor(h_cpd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- Health20002011_ds_w1$h_cpd_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(Health20002011_ds_w1 %>% filter(!vbl %in% miss_values_vector), aes(h_cpd_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}

AfterH <- table(Health20002011_ds_w1$h_cpd)
X <- c(
  sum(Health20002011_w1$BA05 == 0 & Health20002011_w1$BA06 == 0 & Health20002011_w1$BA07 == 0,na.rm=T),
  sum(Health20002011_w1$BA05 == 1 | Health20002011_w1$BA06 == 1 | Health20002011_w1$BA07 == 1,na.rm=T)
)
BeforeH <- c(X[1:2],length(Health20002011_w1$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","NA->999")
kable(C)

```



### Wave 2


#### Study-specific variable description

| **Name** |`BA05`|`BA06`|`BA07`|`age`|`yintw (w1)`|`yintw (w2)`|
|-|-|-|-|-|-|-|
| **Label** |`Illness: COPD`|`Illness: chronic bronchitis`|`Illness: other respiratory disease`|`age`|`year of interview`|`year of interview`|
| **Table name**  |`t00_athlos_2017_02_23` | `t00_athlos_2017_02_23` | `t00_athlos_2017_02_23` |`age`|`yintw`|`yintw`|
| **Categories** |  `0 = no`<br/>`1 = yes` | `0 = no`<br/>`1 = yes` | `0 = no`<br/>`1 = yes` | `continuous` |`continuous` | `continuous` |
| **Missings** | `NA` | `NA` | `NA` |  |  |  |
| **Description** |  |  |  |  |  |  |

```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'Health20002011_w2','Health2000-2011.t11_athlos_2017_02_27',variables=list('BA05','BA06','BA07'), missings = T)
Health20002011_w2 <- opal.execute(o,'Health20002011_w2')
load(paste0(datafolder,"w2/age.RData"))
Health20002011_w2 <- left_join(Health20002011_w2,age, by="id")
rm(age)
load(paste0(datafolder,"w1/yintw.RData"))
Health20002011_w2 <- left_join(Health20002011_w2,yintw, by="id")
names(Health20002011_w2)[6] <- "yintw_w1"
rm(yintw)
load(paste0(datafolder,"w2/yintw.RData"))
Health20002011_w2 <- left_join(Health20002011_w2,yintw, by="id")
names(Health20002011_w2)[7] <- "yintw_w2"
rm(yintw)

```

```{r local w2, echo=F}

vbl <- Health20002011_w2$BA05
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(Health20002011_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w2, aes(x=factor(BA05))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w2$BA06
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(Health20002011_w2)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w2, aes(x=factor(BA06))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w2$BA07
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(Health20002011_w2)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w2, aes(x=factor(BA07))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w2$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(Health20002011_w2)[5])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(Health20002011_w2 %>% filter(!vbl %in% miss_values_vector), aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w2$yintw_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(Health20002011_w2)[6])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w2, aes(x=factor(yintw_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w2$yintw_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(Health20002011_w2)[7])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w2, aes(x=factor(yintw_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_cpd` from the study-specific variable it has to be recoded as follows:

* `all 0 (across waves) into 0`
* `some 1 (across waves) into 1`
* `otherwise into 999`

To compute `h_cpd_age` from the study-specific variable it has to be recoded as follows:

* `if h_cpd == 1 in w2 and 0 in w1, h_cpd_age (w2) = age - (year of interview (w2) - year of interview (w1))/2`
* `if h_cpd == 1 in w2 and h_cpd_age no-missing in w1, h_cpd_age (w2) = as in w1`
* `if h_cpd == 0, h_angina_age = 996`
* `otherwise into 999`

**R script:**

```{r harmo w2}

# We use the harmonized variable of wave 1 instead of the study-specific variables
Health20002011_w2 <- left_join(Health20002011_w2, Health20002011_ds_w1, by = "id")

# Categorical variable harmonization
Health20002011_ds_w2 <- tibble(id=Health20002011_w2$id)
Health20002011_ds_w2$h_cpd <- rep(999,length(Health20002011_ds_w2$id))
Health20002011_ds_w2$h_cpd[which(Health20002011_w2$BA05 == 0 & Health20002011_w2$BA06 == 0 & Health20002011_w2$BA07 == 0 & (Health20002011_w2$h_cpd != 1 | is.na(Health20002011_w2$h_cpd)))] <- 0
Health20002011_ds_w2$h_cpd[which(Health20002011_w2$BA05 == 1 | Health20002011_w2$BA06 == 1 | Health20002011_w2$BA07 == 1 | ((!(is.na(Health20002011_w2$BA05) & is.na(Health20002011_w2$BA06) & is.na(Health20002011_w2$BA07))) & Health20002011_w2$h_cpd == 1))] <- 1

# Continuous variable harmonization
Health20002011_ds_w2$h_cpd_age <- rep(999,length(Health20002011_ds_w2$id))
Health20002011_ds_w2$h_cpd_age[which(Health20002011_ds_w2$h_cpd==0)] <- 996
Health20002011_ds_w2$h_cpd_age[which(Health20002011_ds_w2$h_cpd==1 & Health20002011_w2$h_cpd==0)] <- floor(Health20002011_w2$age[which(Health20002011_ds_w2$h_cpd==1 & Health20002011_w2$h_cpd==0)] - (Health20002011_w2$yintw_w2[which(Health20002011_ds_w2$h_cpd==1 & Health20002011_w2$h_cpd==0)] - Health20002011_w2$yintw_w1[which(Health20002011_ds_w2$h_cpd==1 & Health20002011_w2$h_cpd==0)])/2)
Health20002011_ds_w2$h_cpd_age[which(Health20002011_ds_w2$h_cpd==1 & !is.na(Health20002011_w2$h_cpd_age) & !Health20002011_w2$h_cpd_age %in% miss_values_vector)] <- Health20002011_w2$h_cpd_age[which(Health20002011_ds_w2$h_cpd==1 & !is.na(Health20002011_w2$h_cpd_age) & !Health20002011_w2$h_cpd_age %in% miss_values_vector)]

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- Health20002011_ds_w2$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(Health20002011_ds_w2, aes(x=factor(h_cpd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- Health20002011_ds_w2$h_cpd_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(Health20002011_ds_w2 %>% filter(!vbl %in% miss_values_vector), aes(h_cpd_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w2, echo=F, results='asis'}

AfterH <- table(Health20002011_ds_w2$h_cpd)
X <- c(
  sum(Health20002011_w2$BA05 == 0 & Health20002011_w2$BA06 == 0 & Health20002011_w2$BA07 == 0 & (Health20002011_w2$h_cpd != 1 | is.na(Health20002011_w2$h_cpd)),na.rm = T),
  sum(Health20002011_w2$BA05 == 1 | Health20002011_w2$BA06 == 1 | Health20002011_w2$BA07 == 1 | ((!(is.na(Health20002011_w2$BA05) & is.na(Health20002011_w2$BA06) & is.na(Health20002011_w2$BA07))) & Health20002011_w2$h_cpd == 1),na.rm=T)
)
BeforeH <- c(X[1:2],length(Health20002011_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 2->0","some 1->1","NA->999")
kable(C)

Health20002011_w2 <- left_join(Health20002011_w2,Health20002011_w1, by="id", suffix=c("_w2","_w1"))

# Checking
cat("There are 32, 149 and 201 individuals whose answer in the first wave is that they were diagnosed to have COPD, chronic bronchitis and other respiratory diseases respectively and in the second wave is that they do not have them. We harmonize them as having chronic respiratory disorders in both waves.")
kable(frq(Health20002011_w2$BA05_w2[Health20002011_w2$BA05_w1==1]), align = 'c')
kable(frq(Health20002011_w2$BA06_w2[Health20002011_w2$BA06_w1==1]), align = 'c')
kable(frq(Health20002011_w2$BA07_w2[Health20002011_w2$BA07_w1==1]), align = 'c')

```




<!--AUXILIAR FUNCTIONS-->



```{r helpfunctions, echo=F}

source("../../helpfunctions.r")


```



```{r populations-waves, echo=F}


# All study waves and populations with abbreviated and descriptive names

health2000.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"))



```


<!--Labelling and saving-->

```{r, echo=FALSE}


# Consider only waves with some variable harmonised

l.hds <- lapply(health2000.cw, function(wname) if(exists(paste0("Health20002011_ds_",wname[1]))){wname = list(get(paste0("Health20002011_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling categorical variable of tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]],hd_vbl,ds_label)
  # Labelling continuous variable of tibbles
  lmlist <- labelling_c(lmlist[[1]],lmlist[[2]],hd_age_vbl,ds_label_age)
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}

health2000list <- lmlist # HEALTH 2000 list




```



<!--Descriptives-->

## Descriptive statistics of the harmonised variable `h_cpd` accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.


```{r summ, echo=F}


# Consider only harmonised waves
l.hds <- lapply(health2000.cw, function(wname) if(hd_vbl %in% names(get0(paste0("Health20002011_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- health2000list[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- health2000list[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))

}



```






## Summary of descriptive statistics of the harmonised variable `h_cpd_age` accross populations and waves






```{r summ_c, echo=F}


# Consider only harmonised waves
l.hds <- lapply(health2000.cw, function(wname) if(hd_age_vbl %in% names(get0(paste0("Health20002011_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- health2000list[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- health2000list[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries_c(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_age_vbl),caption=ds_label_age))
}





```




# Quality estimation

* We assume that if an individual answers it has some chronic respiratory disease in one wave, it has for all the next waves. Individuals with discrepancies with respect to this criterium are specified at the end of each validation.
* We have found three individuals which report to have been diagnosed chronic pulmonary disorders in the same year they were born. We have kept this data after harmonisation.
```{r echo=F}
kable(Health20002011_w1[which(Health20002011_ds_w1$h_cpd_age==0),])
```






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





