---
title: "Chronic pulmonary disorders"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `h_cpd`
* Variable label: `History of chronic pulmonary disorders`
* Variable description: `history of chronic pulmonary disease`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | NO chronic pulmonary disease
1        | chronic pulmonary disease

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Short name: `h_cpd_age`
* Variable label: `Age first diagnosed chronic pulmonary disease`
* Variable description: `The age first told had chronic lung disease diagnosis`
* Domain: `Diseases`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "History of chronic pulmonary disorders"
ds_label_age <- "Age first diagnosed chronic pulmonary disease"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
cont_label <- cat_label[3:11]
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process




## Finland


### Wave 1

#### Study-specific variable description

| **Name** | `BA05`|`BA06`|`BA07`| `BA05A`|`BA06A`|`BA07B`|`ybirth`|
|-|-|-|-|-|-|-|-|
| **Label** |`Illness: COPD`|`Illness: chronic bronchitis`|`Illness: other respiratory disease`|`Illness: COPD, year when diagnosed`|`Illness: chronic bronchitis, year when diagnosed`|`Illness: other respiratory disease, year when diagnosed`|`Year of birth`|
| **Table name**  | `t00_athlos_2017_02_23` | `t00_athlos_2017_02_23` | `t00_athlos_2017_02_23` | `t00_athlos_2017_02_23` | `t00_athlos_2017_02_23` | `t00_athlos_2017_02_23` |`ybirth`|
| **Categories** |  `0 = no`<br/>`1 = yes` | `0 = no`<br/>`1 = yes` | `0 = no`<br/>`1 = yes` |`continuous` | `continuous` |`continuous` | `continuous` |
| **Missings** | `NA` | `NA` | `NA` | `NA` |`NA`| `NA` |  |
| **Description** |  |  |  |  |  |  |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'Health20002011_w1','Health2000-2011.t00_athlos_2017_02_23',variables=list('BA05','BA06','BA07','BA05A','BA06A','BA07B'), missings = T)
Health20002011_w1 <- opal.execute(o,'Health20002011_w1')
load(paste0(datafolder,"w1/ybirth.RData"))
Health20002011_w1 <- left_join(Health20002011_w1,ybirth, by="id")
rm(ybirth)

```

```{r local w1, echo=F}

vbl <- Health20002011_w1$BA05
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(Health20002011_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w1, aes(x=factor(BA05))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w1$BA06
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(Health20002011_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w1, aes(x=factor(BA06))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w1$BA07
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(Health20002011_w1)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w1, aes(x=factor(BA07))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")


vbl <- Health20002011_w1$BA05A
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(Health20002011_w1)[5])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(Health20002011_w1, aes(BA05A)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w1$BA06A
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(Health20002011_w1)[6])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(Health20002011_w1, aes(BA06A)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w1$BA07B
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(Health20002011_w1)[7])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(Health20002011_w1, aes(BA07B)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w1$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(Health20002011_w1)[8])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(Health20002011_w1, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1900,1970)

```

#### Harmonisation algorithm

To compute `h_cpd` from the study-specific variable it has to be recoded as follows:

* `all 0 into 0`
* `some 1 into 1`
* `NA into 999`

To compute `h_cpd_age` from the study-specific variable it has to be recoded as follows:

* `if h_cpd == 1, h_cpd_age = min(BA05A,BA06A,BA07B) - ybirth`
* `if h_cpd == 0, h_cpd_age = 996`
* `if max(BA05A,BA06A,BA07B) - ybirth < 0, h_cpd_age = 991`
* `otherwise into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
Health20002011_ds_w1 <- tibble(id=Health20002011_w1$id)
Health20002011_ds_w1$h_cpd <- rep(999,length(Health20002011_w1$id))
Health20002011_ds_w1$h_cpd[which(Health20002011_w1$BA05 == 0 & Health20002011_w1$BA06 == 0 & Health20002011_w1$BA07 == 0)] <- 0
Health20002011_ds_w1$h_cpd[which(Health20002011_w1$BA05 == 1 | Health20002011_w1$BA06 == 1 | Health20002011_w1$BA07 == 1)] <- 1

# Continuous variable harmonization
Health20002011_ds_w1$h_cpd_age <- rep(999,length(Health20002011_w1$id))
Health20002011_ds_w1$h_cpd_age[which(Health20002011_ds_w1$h_cpd == 0)] <- 996
Health20002011_ds_w1$h_cpd_age[which(Health20002011_ds_w1$h_cpd == 1)] <- pmin(Health20002011_w1$BA05A[which(Health20002011_ds_w1$h_cpd == 1)],Health20002011_w1$BA06A[which(Health20002011_ds_w1$h_cpd == 1)],Health20002011_w1$BA07B[which(Health20002011_ds_w1$h_cpd == 1)],na.rm=T) - Health20002011_w1$ybirth[which(Health20002011_ds_w1$h_cpd == 1)]
Health20002011_ds_w1$h_cpd_age <- car::recode(Health20002011_ds_w1$h_cpd_age, "NA = 999")
Health20002011_ds_w1$h_cpd_age[which(Health20002011_ds_w1$h_cpd == 1 & pmax(Health20002011_w1$BA05A,Health20002011_w1$BA06A,Health20002011_w1$BA07B,na.rm=T)<Health20002011_w1$ybirth)] <- 991

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- Health20002011_ds_w1$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(Health20002011_ds_w1, aes(x=factor(h_cpd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- Health20002011_ds_w1$h_cpd_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(Health20002011_ds_w1, aes(h_cpd_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(0,100)

```


#### Validation

```{r crosstabulation w1, echo=F}

AfterH <- table(Health20002011_ds_w1$h_cpd)
X <- c(
  sum(Health20002011_w1$BA05 == 0 & Health20002011_w1$BA06 == 0 & Health20002011_w1$BA07 == 0,na.rm=T),
  sum(Health20002011_w1$BA05 == 1 | Health20002011_w1$BA06 == 1 | Health20002011_w1$BA07 == 1,na.rm=T)
)
BeforeH <- c(X[1:2],length(Health20002011_w1$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","NA->999")
kable(C)

```



### Wave 2


#### Study-specific variable description

| **Name** |`BA05`|`BA06`|`BA07`|`age`|`yintw (w1)`|`yintw (w2)`|
|-|-|-|-|-|-|-|
| **Label** |`Illness: COPD`|`Illness: chronic bronchitis`|`Illness: other respiratory disease`|`age`|`year of interview`|`year of interview`|
| **Table name**  |`t00_athlos_2017_02_23` | `t00_athlos_2017_02_23` | `t00_athlos_2017_02_23` |`age`|`yintw`|`yintw`|
| **Categories** |  `0 = no`<br/>`1 = yes` | `0 = no`<br/>`1 = yes` | `0 = no`<br/>`1 = yes` | `continuous` |`continuous` | `continuous` |
| **Missings** | `NA` | `NA` | `NA` |  |  |  |
| **Description** |  |  |  |  |  |  |

```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'Health20002011_w2','Health2000-2011.t11_athlos_2017_02_27',variables=list('BA05','BA06','BA07'), missings = T)
Health20002011_w2 <- opal.execute(o,'Health20002011_w2')
load(paste0(datafolder,"w2/age.RData"))
Health20002011_w2 <- left_join(Health20002011_w2,age, by="id")
rm(age)
load(paste0(datafolder,"w1/yintw.RData"))
Health20002011_w2 <- left_join(Health20002011_w2,yintw, by="id")
names(Health20002011_w2)[6] <- "yintw_w1"
rm(yintw)
load(paste0(datafolder,"w2/yintw.RData"))
Health20002011_w2 <- left_join(Health20002011_w2,yintw, by="id")
names(Health20002011_w2)[7] <- "yintw_w2"
rm(yintw)

```

```{r local w2, echo=F}

vbl <- Health20002011_w2$BA05
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(Health20002011_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w2, aes(x=factor(BA05))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w2$BA06
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(Health20002011_w2)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w2, aes(x=factor(BA06))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w2$BA07
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(Health20002011_w2)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w2, aes(x=factor(BA07))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w2$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(Health20002011_w2)[5])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(Health20002011_w2, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(25,105)

vbl <- Health20002011_w2$yintw_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(Health20002011_w2)[6])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w2, aes(x=factor(yintw_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w2$yintw_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(Health20002011_w2)[7])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w2, aes(x=factor(yintw_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_cpd` from the study-specific variable it has to be recoded as follows:

* `all 0 (across waves) into 0`
* `some 1 (across waves) into 1`
* `otherwise into 999`

To compute `h_cpd_age` from the study-specific variable it has to be recoded as follows:

* `if h_cpd == 1 in w2 and 0 in w1, h_cpd_age (w2) = age - (year of interview (w2) - year of interview (w1))/2`
* `if h_cpd == 1 in w2 and h_cpd_age no-missing in w1, h_cpd_age (w2) = as in w1`
* `if h_cpd == 0, h_angina_age = 996`
* `otherwise into 999`

**R script:**

```{r harmo w2}

# We use the harmonized variable of wave 1 instead of the study-specific variables
Health20002011_w2 <- left_join(Health20002011_w2, Health20002011_ds_w1, by = "id")

# Categorical variable harmonization
Health20002011_ds_w2 <- tibble(id=Health20002011_w2$id)
Health20002011_ds_w2$h_cpd <- rep(999,length(Health20002011_ds_w2$id))
Health20002011_ds_w2$h_cpd[which(Health20002011_w2$BA05 == 0 & Health20002011_w2$BA06 == 0 & Health20002011_w2$BA07 == 0 & (Health20002011_w2$h_cpd != 1 | is.na(Health20002011_w2$h_cpd)))] <- 0
Health20002011_ds_w2$h_cpd[which(Health20002011_w2$BA05 == 1 | Health20002011_w2$BA06 == 1 | Health20002011_w2$BA07 == 1 | ((!(is.na(Health20002011_w2$BA05) & is.na(Health20002011_w2$BA06) & is.na(Health20002011_w2$BA07))) & Health20002011_w2$h_cpd == 1))] <- 1

# Continuous variable harmonization
Health20002011_ds_w2$h_cpd_age <- rep(999,length(Health20002011_ds_w2$id))
Health20002011_ds_w2$h_cpd_age[which(Health20002011_ds_w2$h_cpd==0)] <- 996
Health20002011_ds_w2$h_cpd_age[which(Health20002011_ds_w2$h_cpd_age==1 & Health20002011_w2$h_cpd_age==0)] <- Health20002011_w2$age[which(Health20002011_ds_w2$h_cpd_age==1 & Health20002011_w2$h_cpd_age==0)] - (Health20002011_w2$yintw_w2[which(Health20002011_ds_w2$h_cpd_age==1 & Health20002011_w2$h_cpd_age==0)] - Health20002011_w2$yintw_w1[which(Health20002011_ds_w2$h_cpd_age==1 & Health20002011_w2$h_cpd_age==0)])/2
Health20002011_ds_w2$h_cpd_age[which(Health20002011_ds_w2$h_cpd==1 & !is.na(Health20002011_w2$h_cpd_age) & !Health20002011_w2$h_cpd_age %in% miss_values_vector)] <- Health20002011_w2$h_cpd_age[which(Health20002011_ds_w2$h_cpd==1 & !is.na(Health20002011_w2$h_cpd_age) & !Health20002011_w2$h_cpd_age %in% miss_values_vector)]

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- Health20002011_ds_w2$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(Health20002011_ds_w2, aes(x=factor(h_cpd))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- Health20002011_ds_w2$h_cpd_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(Health20002011_ds_w2, aes(h_cpd_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(0,100)

```


#### Validation

```{r crosstabulation w2, echo=F, results='asis'}

AfterH <- table(Health20002011_ds_w2$h_cpd)
X <- c(
  sum(Health20002011_w2$BA05 == 0 & Health20002011_w2$BA06 == 0 & Health20002011_w2$BA07 == 0 & (Health20002011_w2$h_cpd != 1 | is.na(Health20002011_w2$h_cpd)),na.rm = T),
  sum(Health20002011_w2$BA05 == 1 | Health20002011_w2$BA06 == 1 | Health20002011_w2$BA07 == 1 | ((!(is.na(Health20002011_w2$BA05) & is.na(Health20002011_w2$BA06) & is.na(Health20002011_w2$BA07))) & Health20002011_w2$h_cpd == 1),na.rm=T)
)
BeforeH <- c(X[1:2],length(Health20002011_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 2->0","some 1->1","NA->999")
kable(C)

Health20002011_w2 <- left_join(Health20002011_w2,Health20002011_w1, by="id", suffix=c("_w2","_w1"))

# Checking
cat("There are 32, 149 and 201 individuals whose answer in the first wave is that they were diagnosed to have COPD, chronic bronchitis and other respiratory diseases respectively and in the second wave is that they do not have them. We harmonize them as having chronic respiratory disorders in both waves.")
kable(frq(Health20002011_w2$BA05_w2[Health20002011_w2$BA05_w1==1]), align = 'c')
kable(frq(Health20002011_w2$BA06_w2[Health20002011_w2$BA06_w1==1]), align = 'c')
kable(frq(Health20002011_w2$BA07_w2[Health20002011_w2$BA07_w1==1]), align = 'c')

```





## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.

**R script:**

```{r summ}
Health20002011_ds_w1$h_cpd <- labelled(Health20002011_ds_w1$h_cpd, labels = cat_label)
label(Health20002011_ds_w1$h_cpd) <- ds_label
Health20002011_ds_w2$h_cpd <- labelled(Health20002011_ds_w2$h_cpd, labels = cat_label)
label(Health20002011_ds_w2$h_cpd) <- ds_label
Health20002011_ds_w1$h_cpd_age <- labelled(Health20002011_ds_w1$h_cpd_age, labels = cont_label)
label(Health20002011_ds_w1$h_cpd_age) <- ds_label_age
Health20002011_ds_w2$h_cpd_age <- labelled(Health20002011_ds_w2$h_cpd_age, labels = cont_label)
label(Health20002011_ds_w2$h_cpd_age) <- ds_label_age

Health20002011_m_ds_w1 <- Health20002011_ds_w1
Health20002011_m_ds_w1$h_cpd <- car::recode(Health20002011_m_ds_w1$h_cpd, "miss_values_vector=NA")
Health20002011_m_ds_w2 <- Health20002011_ds_w2
Health20002011_m_ds_w2$h_cpd <- car::recode(Health20002011_m_ds_w2$h_cpd, "miss_values_vector=NA")

tt <-    frq(Health20002011_ds_w1$h_cpd)[[1]][,c(1:2,4)]
tt[4] <- frq(Health20002011_ds_w2$h_cpd)[[1]][,c(4)]
tt[13,] <- c("n", "sample size", 
             length(Health20002011_ds_w1$h_cpd), length(Health20002011_ds_w2$h_cpd)
             )
names(tt)<-c("val", "label", "w1", "w2")
kable(tt)

dbb <- merge(Health20002011_m_ds_w1[,c("id","h_cpd")], Health20002011_m_ds_w2[,c("id","h_cpd")], by="id", suffixes = c(".w1",".w2"), all=T)
names(dbb) <- c("id", "w1", "w2")
v.dbb <- paste(dbb[,2],dbb[,3],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])
```



# Quality estimation

We assume that if an individual answers it has some chronic respiratory disease in one wave, it has for all the next waves. Individuals with discrepancies with respect to this criterium are specified at the end of each validation.



<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.Health20002011 <- list(w1 = Health20002011_ds_w1, w2 = Health20002011_ds_w2)

for(index in seq_along(l.Health20002011)){
  h_cpd <- l.Health20002011[[index]]
  save(h_cpd, file = paste0(datafolder,names(l.Health20002011)[index],"/h_cpd.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





