---
title: "Hypertension"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `h_hypertension`
* Variable label: `History of Hypertension`
* Variable description: `history of hypertension or high blood pressure`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | NOT High blood pressure or hypertension 
1        | High blood pressure or hypertension

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Short name: `h_hypertension_age`
* Variable label: `Age first diagnosed hypertension`
* Variable description: `The age first told had hypertension diagnosis`
* Domain: `Diseases`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "History of Hypertension"
ds_label_age <- "Age first diagnosed hypertension"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
cont_label <- cat_label[3:11]
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process



## Finland


### Wave 1

#### Study-specific variable description

| **Name** | `BA13` |`BA13A`|`ybirth`|
|-|-|-|-|
| **Label** | `Illness: hypertension` |`Illness: hypertension, year when diagnosed`|`Year of birth`|
| **Table name**  | `t00_athlos_2017_02_23` | `t00_athlos_2017_02_23` |`ybirth`|
| **Categories** | `0 = no`<br/>`1 = yes` | `continuous` | `continuous` |
| **Missings** | `NA` | `NA` |  |
| **Description** |  |  |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'Health20002011_w1','Health2000-2011.t00_athlos_2017_02_23',variables=list('BA13','BA13A'), missings = T)
Health20002011_w1 <- opal.execute(o,'Health20002011_w1')
load(paste0(datafolder,"w1/ybirth.RData"))
Health20002011_w1 <- left_join(Health20002011_w1,ybirth, by="id")

```

```{r local w1, echo=F}

vbl <- Health20002011_w1$BA13
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(Health20002011_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w1, aes(x=factor(BA13))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w1$BA13A
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(Health20002011_w1)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(Health20002011_w1, aes(BA13A)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1935,2005)

vbl <- Health20002011_w1$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(Health20002011_w1)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(Health20002011_w1, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1900,1970)

```

#### Harmonisation algorithm

To compute `h_hypertension` from the study-specific variable it has to be recoded as follows:

* `keep up 0 into 0`
* `keep up 1 into 1`
* `NA into 999`

To compute `h_hypertension_age` from the study-specific variable it has to be recoded as follows:

* `if h_hypertension == 1, h_hypertension_age = BA13A - ybirth`
* `if h_hypertension == 0, h_hypertension_age = 996`
* `BA13<ybirth into 991`
* `h_hypertension == 999 into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
Health20002011_ds_w1 <- tibble(id=Health20002011_w1$id)
Health20002011_ds_w1$h_hypertension <- car::recode(Health20002011_w1$BA13, "NA = 999")

# Continuous variable harmonization
Health20002011_ds_w1$h_hypertension_age <- rep(999,length(Health20002011_w1$id))
Health20002011_ds_w1$h_hypertension_age[which(Health20002011_ds_w1$h_hypertension == 0)] <- 996
Health20002011_ds_w1$h_hypertension_age[which(Health20002011_ds_w1$h_hypertension == 1 & Health20002011_w1$BA13A > Health20002011_w1$ybirth)] <- Health20002011_w1$BA13A[which(Health20002011_ds_w1$h_hypertension == 1 & Health20002011_w1$BA13A > Health20002011_w1$ybirth)] - Health20002011_w1$ybirth[which(Health20002011_ds_w1$h_hypertension == 1 & Health20002011_w1$BA13A > Health20002011_w1$ybirth)]
Health20002011_ds_w1$h_hypertension_age[which(Health20002011_w1$BA13A < Health20002011_w1$ybirth)] <- 991
Health20002011_ds_w1$h_hypertension_age <- car::recode(Health20002011_ds_w1$h_hypertension_age, "NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- Health20002011_ds_w1$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(Health20002011_ds_w1, aes(x=factor(h_hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- Health20002011_ds_w1$h_hypertension_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(Health20002011_ds_w1, aes(h_hypertension_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(10,100)

```


#### Validation

```{r crosstabulation w1, echo=F}

AfterH <- table(Health20002011_ds_w1$h_hypertension)
BeforeH <- table(Health20002011_w1$BA13, useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999")
kable(C)

continuous <- c(sum(Health20002011_ds_w1$h_hypertension_age==996),sum(Health20002011_ds_w1$h_hypertension_age!=996))
X <- table(Health20002011_ds_w1$h_hypertension, useNA = "ifany")
dichotomous <- c(X[1],sum(X[2:3]))
C <- rbind(continuous,dichotomous)
colnames(C) <- c("0<-->996","1,NA<-->(possibly missing) age of diagnostic")
kable(C,caption = "Continuous vs Dichotomous")

```



### Wave 2


#### Study-specific variable description


| **Name** | `BA13` |`age`|`yintw (w1)`|`yintw (w2)`|
|-|-|-|-|-|
| **Label** | `Illness: hypertension` |`age`|`year of interview`|`year of interview`|
| **Table name**  | `t11_athlos_2017_02_27` | `age`|`yintw`|`yintw`|
| **Categories** |`0 = no`<br/>`1 = yes` | `continuous` | `continuous` | `continuous` |
| **Missings** | `NA` |  |  |  |
| **Description** |  |  |  |  |

```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'Health20002011_w2','Health2000-2011.t11_athlos_2017_02_27',variables=list('BA13'), missings = T)
Health20002011_w2 <- opal.execute(o,'Health20002011_w2')
load(paste0(datafolder,"w2/age.RData"))
Health20002011_w2 <- left_join(Health20002011_w2,age, by="id")
rm(age)
load(paste0(datafolder,"w1/yintw.RData"))
Health20002011_w2 <- left_join(Health20002011_w2,yintw, by="id")
names(Health20002011_w2)[4] <- "yintw_w1"
rm(yintw)
load(paste0(datafolder,"w2/yintw.RData"))
Health20002011_w2 <- left_join(Health20002011_w2,yintw, by="id")
names(Health20002011_w2)[5] <- "yintw_w2"
rm(yintw)

```

```{r local w2, echo=F}

vbl <- Health20002011_w2$BA13
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(Health20002011_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w2, aes(x=factor(BA13))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w2$age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(Health20002011_w2)[3])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(Health20002011_w2, aes(age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(25,105)

vbl <- Health20002011_w2$yintw_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(Health20002011_w2)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w2, aes(x=factor(yintw_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w2$yintw_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(Health20002011_w2)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w2, aes(x=factor(yintw_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_hypertension` from the study-specific variable it has to be recoded as follows:

* `BA13 (w1) == 0 and BA13 (w2) == 0 into 0`
* `BA13 (w1) == 1 or BA13 (w2) == 1 into 1`
* `otherwise into 999`

To compute `h_hypertension_age` from the study-specific variable it has to be recoded as follows:

* `if h_hypertension == 1 in w2 and 0 in w1, h_hypertension_age = age - (year of interview (w2) - year of interview (w1))/2`
* `if h_hypertension == 1 in w2 and 1 in w1, h_hypertension_age = as in w1`
* `if h_hypertension == 0, h_hypertension_age = 996`
* `otherwise into 999`

**R script:**

```{r harmo w2}

# We use the harmonized variable of wave 1 instead of the study-specific variable
Health20002011_w2 <- left_join(Health20002011_w2, Health20002011_ds_w1, by = "id")

# Categorical variable harmonization
Health20002011_ds_w2 <- tibble(id=Health20002011_w2$id)
Health20002011_ds_w2$h_hypertension <- rep(999,length(Health20002011_ds_w2$id))
Health20002011_ds_w2$h_hypertension[which(Health20002011_w2$BA13 == 0 & (Health20002011_w2$h_hypertension != 1 | is.na(Health20002011_w2$h_hypertension)))] <- 0
Health20002011_ds_w2$h_hypertension[which(Health20002011_w2$BA13 == 1 | ((!is.na(Health20002011_w2$BA13)) & Health20002011_w2$h_hypertension == 1))] <- 1

# Continuous variable harmonization
Health20002011_ds_w2$h_hypertension_age <- rep(999,length(Health20002011_ds_w2$id))
Health20002011_ds_w2$h_hypertension_age[which(Health20002011_ds_w2$h_hypertension==0)] <- 996

Health20002011_ds_w2$h_hypertension_age[which(Health20002011_ds_w2$h_hypertension==1 & !is.na(Health20002011_w2$h_hypertension_age) & !Health20002011_w2$h_hypertension_age %in% miss_values_vector)] <- Health20002011_w2$h_hypertension_age[which(Health20002011_ds_w2$h_hypertension==1 & !is.na(Health20002011_w2$h_hypertension_age) & !Health20002011_w2$h_hypertension_age %in% miss_values_vector)]

Health20002011_ds_w2$h_hypertension_age[which(Health20002011_ds_w2$h_hypertension==1 & Health20002011_w2$h_hypertension==0)] <- Health20002011_w2$age[which(Health20002011_ds_w2$h_hypertension==1 & Health20002011_w2$h_hypertension==0)] - (Health20002011_w2$yintw_w2[which(Health20002011_ds_w2$h_hypertension==1 & Health20002011_w2$h_hypertension==0)] - Health20002011_w2$yintw_w1[which(Health20002011_ds_w2$h_hypertension==1 & Health20002011_w2$h_hypertension==0)])/2

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- Health20002011_ds_w2$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(Health20002011_ds_w2, aes(x=factor(h_hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- Health20002011_ds_w2$h_hypertension_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(Health20002011_ds_w2, aes(h_hypertension_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(10,95)

```


#### Validation

```{r crosstabulation w2, echo=F, results='asis'}

AfterH <- table(Health20002011_ds_w2$h_hypertension)
X <- c(
  sum(Health20002011_w2$BA13 == 0 & (Health20002011_w2$h_hypertension != 1 | is.na(Health20002011_w2$h_hypertension)),na.rm = T),
  sum(((!is.na(Health20002011_w2$BA13)) & Health20002011_w2$BA13 == 1) | ((!is.na(Health20002011_w2$h_hypertension)) & (!is.na(Health20002011_w2$BA13)) & Health20002011_w2$h_hypertension == 1))
)
BeforeH <- c(X[1:2],length(Health20002011_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","NA->999")
kable(C)

# Checking
cat("There are 264 individuals whose answer in the first wave is that they were diagnosed to have hypertension and in the second wave is that they do not have it. We compute them in the harmonized variable as having hypertension.")
kable(frq(Health20002011_w2$BA13[Health20002011_w2$h_hypertension==1]), align = 'c')

```





## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.

**R script:**

```{r summ}
Health20002011_ds_w1$h_hypertension <- labelled(Health20002011_ds_w1$h_hypertension, labels = cat_label)
label(Health20002011_ds_w1$h_hypertension) <- ds_label
Health20002011_ds_w1$h_hypertension_age <- labelled(Health20002011_ds_w1$h_hypertension_age, labels = cont_label)
label(Health20002011_ds_w1$h_hypertension_age) <- ds_label_age
Health20002011_ds_w2$h_hypertension <- labelled(Health20002011_ds_w2$h_hypertension, labels = cat_label)
label(Health20002011_ds_w2$h_hypertension) <- ds_label
Health20002011_ds_w2$h_hypertension_age <- labelled(Health20002011_ds_w2$h_hypertension_age, labels = cont_label)
label(Health20002011_ds_w2$h_hypertension_age) <- ds_label_age

Health20002011_m_ds_w1 <- Health20002011_ds_w1
Health20002011_m_ds_w1$h_hypertension <- car::recode(Health20002011_m_ds_w1$h_hypertension, "miss_values_vector=NA")
Health20002011_m_ds_w2 <- Health20002011_ds_w2
Health20002011_m_ds_w2$h_hypertension <- car::recode(Health20002011_m_ds_w2$h_hypertension, "miss_values_vector=NA")

tt <-    frq(Health20002011_ds_w1$h_hypertension)[[1]][,c(1:2,4)]
tt[4] <- frq(Health20002011_ds_w2$h_hypertension)[[1]][,c(4)]
tt[13,] <- c("n", "sample size", 
             length(Health20002011_ds_w1$h_hypertension), length(Health20002011_ds_w2$h_hypertension)
             )
names(tt)<-c("val", "label", "w1", "w2")
kable(tt)

dbb <- merge(Health20002011_m_ds_w1[,c("id","h_hypertension")], Health20002011_m_ds_w2[,c("id","h_hypertension")], by="id", suffixes = c(".w1",".w2"), all=T)
names(dbb) <- c("id", "w1", "w2")
v.dbb <- paste(dbb[,2],dbb[,3],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])
```



# Quality estimation

We assume that if an individual answers it has hypertension in one wave, it has hypertension for all the next waves. Individuals with discrepancies with respect to this criterium are specified at the end of each validation.



<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.Health20002011 <- list(w1 = Health20002011_ds_w1, w2 = Health20002011_ds_w2)

for(index in seq_along(l.Health20002011)){
  h_hypertension <- l.Health20002011[[index]]
  save(h_hypertension, file = paste0(datafolder,names(l.Health20002011)[index],"/h_hypertension.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





