---
title: "Joint disorders"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/joint_disordersDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/joint_disordersDS.R')
```




# Data process



## Finland


### Wave 1

#### Study-specific variable description

| **Name** | `BA18` |`BA18A`|`ybirth`|
|-|-|-|-|
| **Label** | `Illness: rheumatoid arthritis` |`Illness: rheumatoid arthritis, year when diagnosed`|`Year of birth`|
| **Table name**  | `t00_athlos_2017_02_23` | `t00_athlos_2017_02_23` |`ybirth`|
| **Categories** | `0 = no`<br/>`1 = yes` | `continuous` | `continuous` |
| **Missings** | `NA` | `NA` |  |
| **Description** |  |  |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'Health20002011_w1','Health2000-2011.t00_athlos_2017_02_23',variables=list('BA18','BA18A'), missings = T)
Health20002011_w1 <- opal.execute(o,'Health20002011_w1')
load(paste0(datafolder,"w1/ybirth.RData"))
Health20002011_w1 <- left_join(Health20002011_w1,ybirth, by="id")

```

```{r local w1, echo=F}

vbl <- Health20002011_w1$BA18
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(Health20002011_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w1, aes(x=factor(BA18))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w1$BA18A
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(Health20002011_w1)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(Health20002011_w1, aes(BA18A)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w1$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(Health20002011_w1)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(Health20002011_w1 %>% filter(!vbl %in% miss_values_vector), aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `h_joint_disorders` from the study-specific variable it has to be recoded as follows:

* `keep up 0 into 0`
* `keep up 1 into 1`
* `NA into 999`

To compute `h_joint_disorders_age` from the study-specific variable it has to be recoded as follows:

* `if h_joint_disorders == 1, h_joint_disorders_age = BA18A - ybirth`
* `if h_joint_disorders == 0, h_joint_disorders_age = 996`
* `BA18<ybirth into 991`
* `h_joint_disorders == 999 into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
Health20002011_ds_w1 <- tibble(id=Health20002011_w1$id)
Health20002011_ds_w1$h_joint_disorders <- car::recode(Health20002011_w1$BA18, "NA = 999")

# Continuous variable harmonization
Health20002011_ds_w1$h_joint_disorders_age <- rep(999,length(Health20002011_w1$id))
Health20002011_ds_w1$h_joint_disorders_age[which(Health20002011_ds_w1$h_joint_disorders == 0)] <- 996
Health20002011_ds_w1$h_joint_disorders_age[which(Health20002011_ds_w1$h_joint_disorders == 1 & Health20002011_w1$BA18A > Health20002011_w1$ybirth)] <- Health20002011_w1$BA18A[which(Health20002011_ds_w1$h_joint_disorders == 1 & Health20002011_w1$BA18A > Health20002011_w1$ybirth)] - Health20002011_w1$ybirth[which(Health20002011_ds_w1$h_joint_disorders == 1 & Health20002011_w1$BA18A > Health20002011_w1$ybirth)]
Health20002011_ds_w1$h_joint_disorders_age[which(Health20002011_w1$BA18A < Health20002011_w1$ybirth)] <- 991
Health20002011_ds_w1$h_joint_disorders_age <- car::recode(Health20002011_ds_w1$h_joint_disorders_age, "NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- Health20002011_ds_w1$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(Health20002011_ds_w1, aes(x=factor(h_joint_disorders))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- Health20002011_ds_w1$h_joint_disorders_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(Health20002011_ds_w1 %>% filter(!vbl %in% miss_values_vector), aes(h_joint_disorders_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}

AfterH <- table(Health20002011_ds_w1$h_joint_disorders)
BeforeH <- table(Health20002011_w1$BA18, useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999")
kable(C)

continuous <- c(sum(Health20002011_ds_w1$h_joint_disorders_age==996),sum(Health20002011_ds_w1$h_joint_disorders_age!=996))
X <- table(Health20002011_ds_w1$h_joint_disorders, useNA = "ifany")
dichotomous <- c(X[1],sum(X[2:3]))
C <- rbind(continuous,dichotomous)
colnames(C) <- c("0<-->996","1,NA<-->(possibly missing) age of diagnostic")
kable(C,caption = "Continuous vs Dichotomous")

```



### Wave 2


#### Study-specific variable description


| **Name** | `BA18` |`BA18A`|`ybirth`|
|-|-|-|-|
| **Label** | `Illness: rheumatoid arthritis` |`Illness: rheumatoid arthritis, year when diagnosed`|`Year of birth`|
| **Table name**  | `t11_athlos_2017_02_27` | `t11_athlos_2017_02_27` |`ybirth`|
| **Categories** | `0 = no`<br/>`1 = yes` | `continuous` | `continuous` |
| **Missings** | `NA` | `NA` | `999 = Missing` |
| **Description** |  |  |  |


```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'Health20002011_w2','Health2000-2011.t11_athlos_2017_02_27',variables=list('BA18','BA18A'), missings = T)
Health20002011_w2 <- opal.execute(o,'Health20002011_w2')
load(paste0(datafolder,"w2/ybirth.RData"))
Health20002011_w2 <- left_join(Health20002011_w2,ybirth, by="id")
rm(ybirth)

```

```{r local w2, echo=F}

vbl <- Health20002011_w2$BA18
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(Health20002011_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w2, aes(x=factor(BA18))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w2$BA18A
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(Health20002011_w2)[3])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(Health20002011_w2, aes(BA18A)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w2$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(Health20002011_w2)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(Health20002011_w2 %>% filter(!vbl %in% miss_values_vector), aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_joint_disorders` from the study-specific variable it has to be recoded as follows:

* `BA18 (w1) == 0 and BA18 (w2) == 0 into 0`
* `BA18 (w1) == 1 or BA18 (w2) == 1 into 1`
* `otherwise into 999`

To compute `h_joint_disorders_age` from the study-specific variable it has to be recoded as follows:

* `if h_joint_disorders == 1 in w2 and h_joint_disorders_age missing in w1, h_joint_disorders_age (w2) = BA18A - ybirth`
* `if h_joint_disorders == 1 in w2 and h_joint_disorders_age no-missing in w1, h_joint_disorders_age (w2) = as in w1`
* `if h_joint_disorders == 0, h_joint_disorders_age = 996`
* `otherwise into 999`

**R script:**

```{r harmo w2}

# We use the harmonized variable of wave 1 instead of the study-specific variable
Health20002011_w2 <- left_join(Health20002011_w2, Health20002011_ds_w1, by = "id")

# Categorical variable harmonization
Health20002011_ds_w2 <- tibble(id=Health20002011_w2$id)
Health20002011_ds_w2$h_joint_disorders <- rep(999,length(Health20002011_ds_w2$id))
Health20002011_ds_w2$h_joint_disorders[which(Health20002011_w2$BA18 == 0 & (Health20002011_w2$h_joint_disorders != 1 | is.na(Health20002011_w2$h_joint_disorders)))] <- 0
Health20002011_ds_w2$h_joint_disorders[which(Health20002011_w2$BA18 == 1 | ((!is.na(Health20002011_w2$BA18)) & Health20002011_w2$h_joint_disorders == 1))] <- 1

# Continuous variable harmonization
Health20002011_ds_w2$h_joint_disorders_age <- rep(999,length(Health20002011_ds_w2$id))
Health20002011_ds_w2$h_joint_disorders_age[which(Health20002011_ds_w2$h_joint_disorders==0)] <- 996
Health20002011_ds_w2$h_joint_disorders_age[which(Health20002011_ds_w2$h_joint_disorders==1 & !is.na(Health20002011_w2$h_joint_disorders_age) & !Health20002011_w2$h_joint_disorders_age %in% miss_values_vector)] <- Health20002011_w2$h_joint_disorders_age[which(Health20002011_ds_w2$h_joint_disorders==1 & !is.na(Health20002011_w2$h_joint_disorders_age) & !Health20002011_w2$h_joint_disorders_age %in% miss_values_vector)]
Health20002011_ds_w2$h_joint_disorders_age[which(Health20002011_ds_w2$h_joint_disorders==1 & !Health20002011_w2$ybirth %in% miss_values_vector & (is.na(Health20002011_w2$h_joint_disorders_age) | Health20002011_w2$h_joint_disorders_age %in% miss_values_vector))] <- Health20002011_w2$BA18A[which(Health20002011_ds_w2$h_joint_disorders==1 & !Health20002011_w2$ybirth %in% miss_values_vector & (is.na(Health20002011_w2$h_joint_disorders_age) | Health20002011_w2$h_joint_disorders_age %in% miss_values_vector))] - Health20002011_w2$ybirth[which(Health20002011_ds_w2$h_joint_disorders==1 & !Health20002011_w2$ybirth %in% miss_values_vector & (is.na(Health20002011_w2$h_joint_disorders_age) | Health20002011_w2$h_joint_disorders_age %in% miss_values_vector))]

Health20002011_ds_w2$h_joint_disorders_age <- car::recode(Health20002011_ds_w2$h_joint_disorders_age, "NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- Health20002011_ds_w2$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(Health20002011_ds_w2, aes(x=factor(h_joint_disorders))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- Health20002011_ds_w2$h_joint_disorders_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(Health20002011_ds_w2 %>% filter(!vbl %in% miss_values_vector), aes(h_joint_disorders_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w2, echo=F, results='asis'}

AfterH <- table(Health20002011_ds_w2$h_joint_disorders)
X <- c(
  sum(Health20002011_w2$BA18 == 0 & (Health20002011_w2$h_joint_disorders != 1 | is.na(Health20002011_w2$h_joint_disorders)),na.rm = T),
  sum(((!is.na(Health20002011_w2$BA18)) & Health20002011_w2$BA18 == 1) | ((!is.na(Health20002011_w2$h_joint_disorders)) & (!is.na(Health20002011_w2$BA18)) & Health20002011_w2$h_joint_disorders == 1))
)
BeforeH <- c(X[1:2],length(Health20002011_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","NA->999")
kable(C)

# Checking
cat("There are 31 individuals whose answer in the first wave is that they were diagnosed to have rheumatoid arthritis and in the second wave is that they do not have it. We compute them in the harmonized variable as having joint disorders")
kable(frq(Health20002011_w2$BA18[Health20002011_w2$h_joint_disorders==1]), align = 'c')

```




<!--AUXILIAR FUNCTIONS-->



```{r helpfunctions, echo=F}

source("../../helpfunctions.r")

```



```{r populations-waves, echo=F}


# All study waves and populations with abbreviated and descriptive names

health2000.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"))



```


<!--Labelling and saving-->

```{r, echo=FALSE}


# Consider only waves with some variable harmonised

l.hds <- lapply(health2000.cw, function(wname) if(exists(paste0("Health20002011_ds_",wname[1]))){wname = list(get(paste0("Health20002011_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling categorical variable of tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]],hd_vbl,ds_label)
  # Labelling continuous variable of tibbles
  lmlist <- labelling_c(lmlist[[1]],lmlist[[2]],hd_age_vbl,ds_label_age)
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}

health2000list <- lmlist # HEALTH 2000 list




```



<!--Descriptives-->

## Descriptive statistics of the harmonised variable `h_joint_disorders` accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.


```{r summ, echo=F}


# Consider only harmonised waves
l.hds <- lapply(health2000.cw, function(wname) if(hd_vbl %in% names(get0(paste0("Health20002011_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- health2000list[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- health2000list[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))

}



```






## Summary of descriptive statistics of the harmonised variable `h_joint_disorders_age` accross populations and waves






```{r summ_c, echo=F}


# Consider only harmonised waves
l.hds <- lapply(health2000.cw, function(wname) if(hd_age_vbl %in% names(get0(paste0("Health20002011_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- health2000list[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- health2000list[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries_c(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_age_vbl),caption=ds_label_age))
}





```



# Quality estimation

We assume that if an individual answers it has joint disorders in one wave, it has for all the next waves. Individuals with discrepancies with respect to this criterium are specified at the end of each validation.








<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





