---
title: "Stroke"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `stroke`
* Variable label: `Stroke`
* Variable description: `Diagnosis of stroke or cerebral vascular disease since the last wave`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | NOT A stroke (cerebral vascular disease) 
1        | A stroke (cerebral vascular disease)

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Short name: `stroke_age`
* Variable label: `Age of each episode of stroke`
* Variable description: `Age of each episode of stroke`
* Domain: `Diseases`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "Stroke"
ds_label_age <- "Age of each episode of stroke"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
cont_label <- cat_label[3:11]
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process



## Finland


### Wave 1

#### Study-specific variable description

| **Name** | `BA14` |`BA14A`|`ybirth`|
|-|-|-|-|
| **Label** | `Illness: stroke` |`Illness: stroke, year when diagnosed`|`Year of birth`|
| **Table name**  | `t00_athlos_2017_02_23` | `t00_athlos_2017_02_23` |`ybirth`|
| **Categories** | `0 = no`<br/>`1 = yes` | `continuous` | `continuous` |
| **Missings** | `NA` | `NA` |  |
| **Description** |  |  |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'Health20002011_w1','Health2000-2011.t00_athlos_2017_02_23',variables=list('BA14','BA14A'), missings = T)
Health20002011_w1 <- opal.execute(o,'Health20002011_w1')
load(paste0(datafolder,"w1/ybirth.RData"))
Health20002011_w1 <- left_join(Health20002011_w1,ybirth, by="id")

```

```{r local w1, echo=F}

vbl <- Health20002011_w1$BA14
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(Health20002011_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w1, aes(x=factor(BA14))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w1$BA14A
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(Health20002011_w1)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(Health20002011_w1, aes(BA14A)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1950,2005)

vbl <- Health20002011_w1$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(Health20002011_w1)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(Health20002011_w1, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1900,1970)

```

#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `keep up 0 into 0`
* `keep up 1 into 1`
* `NA into 999`

To compute `stroke_age` from the study-specific variable it has to be recoded as follows:

* `if stroke == 1, stroke_age = BA14A - ybirth`
* `if stroke == 0, stroke_age = 996`
* `BA14<ybirth into 991`
* `stroke == 999 into 999`

**R script:**

```{r harmo w1}

# Categorical variable harmonization
Health20002011_ds_w1 <- tibble(id=Health20002011_w1$id)
Health20002011_ds_w1$stroke <- car::recode(Health20002011_w1$BA14, "NA = 999")

#There is an individual having answered year of diagnostic:
Health20002011_ds_w1$stroke[which(!is.na(Health20002011_w1$BA14A) & is.na(Health20002011_w1$BA14))] <- 1

# Continuous variable harmonization
Health20002011_ds_w1$stroke_age <- rep(999,length(Health20002011_w1$id))
Health20002011_ds_w1$stroke_age[which(Health20002011_ds_w1$stroke == 0)] <- 996
Health20002011_ds_w1$stroke_age[which(Health20002011_ds_w1$stroke == 1 & Health20002011_w1$BA14A > Health20002011_w1$ybirth)] <- Health20002011_w1$BA14A[which(Health20002011_ds_w1$stroke == 1 & Health20002011_w1$BA14A > Health20002011_w1$ybirth)] - Health20002011_w1$ybirth[which(Health20002011_ds_w1$stroke == 1 & Health20002011_w1$BA14A > Health20002011_w1$ybirth)]
Health20002011_ds_w1$stroke_age[which(Health20002011_ds_w1$stroke == 1 & Health20002011_w1$BA14A < Health20002011_w1$ybirth)] <- 991
Health20002011_ds_w1$stroke_age <- car::recode(Health20002011_ds_w1$stroke_age, "NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- Health20002011_ds_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(Health20002011_ds_w1, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- Health20002011_ds_w1$stroke_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(Health20002011_ds_w1, aes(stroke_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(10,95)

```


#### Validation

```{r crosstabulation w1, echo=F}

continuous <- c(sum(Health20002011_ds_w1$stroke_age==996),sum(Health20002011_ds_w1$stroke_age!=996))
X <- table(Health20002011_ds_w1$stroke, useNA = "ifany")
dichotomous <- c(X[1],sum(X[2:3]))
C <- rbind(continuous,dichotomous)
colnames(C) <- c("0<-->996","1,NA<-->(possibly missing) age of diagnostic")
kable(C,caption = "Continuous vs Dichotomous")

```



### Wave 2


#### Study-specific variable description


| **Name** | `BA14` |`BA14A`|`ybirth`|
|-|-|-|-|
| **Label** | `Illness: stroke` |`Illness: stroke, year when diagnosed`|`Year of birth`|
| **Table name**  | `t11_athlos_2017_02_27` | `t11_athlos_2017_02_27` |`ybirth`|
| **Categories** | `0 = no`<br/>`1 = yes` | `continuous` | `continuous` |
| **Missings** | `NA` | `NA` | `999 = Missing` |
| **Description** |  |  |  |


```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'Health20002011_w2','Health2000-2011.t11_athlos_2017_02_27',variables=list('BA14','BA14A'), missings = T)
Health20002011_w2 <- opal.execute(o,'Health20002011_w2')
load(paste0(datafolder,"w2/ybirth.RData"))
Health20002011_w2 <- left_join(Health20002011_w2,ybirth, by="id")
rm(ybirth)

```

```{r local w2, echo=F}

vbl <- Health20002011_w2$BA14
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(Health20002011_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(Health20002011_w2, aes(x=factor(BA14))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- Health20002011_w2$BA14A
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(Health20002011_w2)[3])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(Health20002011_w2, aes(BA14A)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1975,2015)

vbl <- Health20002011_w2$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(Health20002011_w2)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(Health20002011_w2, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1905,1975)

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `keep up 0 into 0`
* `BA14 (w2) == 1 & (BA14A (w2) >= 2000 & (BA14A (w2) != BA14A (w1)) | BA14 (w1) == 0`
* `NA into 999`

To compute `stroke_age` from the study-specific variable it has to be recoded as follows:

* `if stroke == 1, stroke_age = BA14A - ybirth`
* `if stroke == 0, stroke_age = 996`
* `stroke == 999 into 999`

**R script:**

```{r harmo w2}

# We use the harmonized variable of wave 1 instead of the study-specific variable
Health20002011_w2 <- left_join(Health20002011_w2, Health20002011_w1, by = "id",suffix=c("","_w1"))

# Categorical variable harmonization
Health20002011_ds_w2 <- tibble(id=Health20002011_w2$id)
Health20002011_ds_w2$stroke <- rep(999,length(Health20002011_w2$id))
Health20002011_ds_w2$stroke[which(Health20002011_w2$BA14==0)] <- 0
# Individuals having stroke since wave 1, so their year of diagnostic is at least 2001 (wave 1 data was collected between 2001 and 2002) and distinct from answered in wave 1 or missing but until wave 1 they have no stroke.
Health20002011_ds_w2$stroke[which(Health20002011_w2$BA14==1 & ((Health20002011_w2$BA14A>=2001 & (Health20002011_w2$BA14A!=Health20002011_w2$BA14A_w1 | is.na(Health20002011_w2$BA14A_w1))) | Health20002011_w2$BA14_w1==0))] <- 1

# Continuous variable harmonization
Health20002011_ds_w2$stroke_age <- rep(999,length(Health20002011_ds_w2$id))
Health20002011_ds_w2$stroke_age[which(Health20002011_ds_w2$stroke==0)] <- 996

Health20002011_ds_w2$stroke_age[which(Health20002011_ds_w2$stroke==1 & !Health20002011_w2$ybirth %in% miss_values_vector & Health20002011_w2$BA14A>=2001)] <- Health20002011_w2$BA14A[which(Health20002011_ds_w2$stroke==1 & !Health20002011_w2$ybirth %in% miss_values_vector & Health20002011_w2$BA14A>=2001)] - Health20002011_w2$ybirth[which(Health20002011_ds_w2$stroke==1 & !Health20002011_w2$ybirth %in% miss_values_vector & Health20002011_w2$BA14A>=2001)]

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- Health20002011_ds_w2$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(Health20002011_ds_w2, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- Health20002011_ds_w2$stroke_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(Health20002011_ds_w2, aes(stroke_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(35,90)

```


#### Validation

```{r crosstabulation w2, echo=F, results='asis'}

continuous <- c(sum(Health20002011_ds_w1$stroke_age==996),sum(Health20002011_ds_w1$stroke_age!=996))
X <- table(Health20002011_ds_w1$stroke, useNA = "ifany")
dichotomous <- c(X[1],sum(X[2:3]))
C <- rbind(continuous,dichotomous)
colnames(C) <- c("0<-->996","1,NA<-->(possibly missing) age of diagnostic")
kable(C,caption = "Continuous vs Dichotomous")

cat("There are some individuals which in the first wave told they had no stroke and in the second wave told they had stroke and give year of diagnosis previous to first wave. We harmonize them as having stroke but keep missing age of diagnosis ")
kable(Health20002011_w2[which(Health20002011_w2$BA14_w1==0 & Health20002011_w2$BA14A<2001),])

```





## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.

**R script:**

```{r summ}
Health20002011_ds_w1$stroke <- labelled(Health20002011_ds_w1$stroke, labels = cat_label)
label(Health20002011_ds_w1$stroke) <- ds_label
Health20002011_ds_w1$stroke_age <- labelled(Health20002011_ds_w1$stroke_age, labels = cont_label)
label(Health20002011_ds_w1$stroke_age) <- ds_label_age
Health20002011_ds_w2$stroke <- labelled(Health20002011_ds_w2$stroke, labels = cat_label)
label(Health20002011_ds_w2$stroke) <- ds_label
Health20002011_ds_w2$stroke_age <- labelled(Health20002011_ds_w2$stroke_age, labels = cont_label)
label(Health20002011_ds_w2$stroke_age) <- ds_label_age

Health20002011_m_ds_w1 <- Health20002011_ds_w1
Health20002011_m_ds_w1$stroke <- car::recode(Health20002011_m_ds_w1$stroke, "miss_values_vector=NA")
Health20002011_m_ds_w2 <- Health20002011_ds_w2
Health20002011_m_ds_w2$stroke <- car::recode(Health20002011_m_ds_w2$stroke, "miss_values_vector=NA")

tt <-    frq(Health20002011_ds_w1$stroke)[[1]][,c(1:2,4)]
tt[4] <- frq(Health20002011_ds_w2$stroke)[[1]][,c(4)]
tt[13,] <- c("n", "sample size", 
             length(Health20002011_ds_w1$stroke), length(Health20002011_ds_w2$stroke)
             )
names(tt)<-c("val", "label", "w1", "w2")
kable(tt)

dbb <- merge(Health20002011_m_ds_w1[,c("id","stroke")], Health20002011_m_ds_w2[,c("id","stroke")], by="id", suffixes = c(".w1",".w2"), all=T)
names(dbb) <- c("id", "w1", "w2")
v.dbb <- paste(dbb[,2],dbb[,3],sep="")
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])
```



# Quality estimation

No comments


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.Health20002011 <- list(w1 = Health20002011_ds_w1, w2 = Health20002011_ds_w2)

for(index in seq_along(l.Health20002011)){
  stroke <- l.Health20002011[[index]]
  save(stroke, file = paste0(datafolder,names(l.Health20002011)[index],"/stroke.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





