---
title: "Time walking"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/t_walksDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/t_walksDS.R')
```



# Data process


## Australia

### Wave 1 

#### Study-specific variable description

| **Name** | `WALK2WKS` |
|-|-|
| **Label** | `Walking past 2 weeks` |
| **Table name** | `ALSA-Wave1` |
| **Categories:**| `1 = Yes` <br/> `2 = No`|
| **Missings:**|`9 = Missing` <br/> `NA`|
| **Description** |  |

   

```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'ALSA_w1','ALSA.ALSA-Wave1', variables=list('WALK2WKS'), missings = TRUE)
ALSA_w1 <- opal.execute(o,'ALSA_w1')
```

```{r local w1, echo=F}
vbl <- ALSA_w1$WALK2WKS
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w1, aes(x=factor(WALK2WKS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `t_walks` from the study-specific variable it has to be recoded as follows:

* `2 into 0` 
* `9 into 999` 
* `NA into 999`

**R script:**

```{r harmo w1}
ALSA_ds_w1 <- tibble(id=ALSA_w1$id)
ALSA_ds_w1$t_walks <- car::recode(ALSA_w1$WALK2WKS, "2 = 0;9 = 999;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vbl <- ALSA_ds_w1$t_walks
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w1, aes(x=factor(t_walks))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(ALSA_ds_w1$t_walks)
X<-table(ALSA_w1$WALK2WKS)
BeforeH <- c(X[2:1],X[3]+sum(is.na(ALSA_w1$WALK2WKS)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","9,NA->999") 
kable(C)
```




### Wave 2

Not found.


### Wave 3

#### Study-specific variable description

| **Name** | `HWWALKW3` |
|-|-|
| **Label** | `TIMES WALKED IN PAST TWO WEEKS` |
| **Table name** | `ALSA-Wave3` |
| **Categories:**| `continuous`|
| **Missings:**|`99` <br/> `NA`|
| **Description** |  |

   

```{r assign w3, echo=F}
opal.assign.table.tibble(o, 'ALSA_w3','ALSA.ALSA-Wave3', variables=list('HWWALKW3'), missings = TRUE)
ALSA_w3 <- opal.execute(o,'ALSA_w3')
```

```{r local w3, echo=F}
vbl <- ALSA_w3$HWWALKW3
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = label(vbl)) 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_w3, aes(HWWALKW3)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + coord_cartesian(xlim = c(-.45,45))
```

#### Harmonisation algorithm

To compute `t_walks` from the study-specific variable it has to be recoded as follows:

* `0 into 0` 
* `otherwise into 1` 
* `99 into 999`
* `NA into 999`

**R script:**

```{r harmo w3}
ALSA_ds_w3 <- tibble(id=ALSA_w3$id)
ALSA_ds_w3$t_walks <- rep(1,length(ALSA_w3$id))
ALSA_ds_w3$t_walks[ALSA_w3$HWWALKW3==0] <- 0
ALSA_ds_w3$t_walks[ALSA_w3$HWWALKW3==99] <- 999
ALSA_ds_w3$t_walks[is.na(ALSA_w3$HWWALKW3)==TRUE] <- 999
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}
vbl <- ALSA_ds_w3$t_walks
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w3, aes(x=factor(t_walks))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=F}
AfterH <- table(ALSA_ds_w3$t_walks)
X<-table(ALSA_w3$HWWALKW3)
BeforeH <- c(X[1],sum(X[2:21]),X[22]+sum(is.na(ALSA_w3$HWWALKW3)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->0","otherwise->1","99,NA->999") 
kable(C)
```





### Wave 4

#### Study-specific variable description

| **Name** | `WALK2WW4` |
|-|-|
| **Label** | `in the past two weeks, did you walk for recreation or exercise?` |
| **Table name** | `ALSA-Wave4` |
| **Categories:**| `1 = Yes` <br/> `2 = No`|
| **Missings:**|`NA`|
| **Description** |  |

   

```{r assign w4, echo=F}
opal.assign.table.tibble(o, 'ALSA_w4','ALSA.ALSA-Wave4', variables=list('WALK2WW4'), missings = TRUE)
ALSA_w4 <- opal.execute(o,'ALSA_w4')
```

```{r local w4, echo=F}
vbl <- ALSA_w4$WALK2WW4
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w4)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w4, aes(x=factor(WALK2WW4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `t_walks` from the study-specific variable it has to be recoded as follows:

* `2 into 0` 
* `NA into 999`

**R script:**

```{r harmo w4}
ALSA_ds_w4 <- tibble(id=ALSA_w4$id)
ALSA_ds_w4$t_walks <- car::recode(ALSA_w4$WALK2WW4, "2 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w4, echo=F}
vbl <- ALSA_ds_w4$t_walks
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w4, aes(x=factor(t_walks))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w4, echo=F}
```




### Wave 5

#### Study-specific variable description

| **Name** | `WALK2WW5` |
|-|-|
| **Label** | `in the past two weeks, did you walk for recreation or exercise?` |
| **Table name** | `ALSA-Wave5` |
| **Categories:**| `1 = Yes` <br/> `2 = No`|
| **Missings:**| `3 = Refused/Dont know (do not read)` <br/> `NA` |
| **Description** |  |

   

```{r assign w5, echo=F}
opal.assign.table.tibble(o, 'ALSA_w5','ALSA.ALSA-Wave5', variables=list('WALK2WW5'), missings = TRUE)
ALSA_w5 <- opal.execute(o,'ALSA_w5')
```

```{r local w5, echo=F}
vbl <- ALSA_w5$WALK2WW5
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w5)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w5, aes(x=factor(WALK2WW5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `t_walks` from the study-specific variable it has to be recoded as follows:

* `2 into 0` 
* `3 into 999`
* `NA into 999`

**R script:**

```{r harmo w5}
ALSA_ds_w5 <- tibble(id=ALSA_w5$id)
ALSA_ds_w5$t_walks <- car::recode(ALSA_w5$WALK2WW5, "2 = 0;3 = 999;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w5, echo=F}
vbl <- ALSA_ds_w5$t_walks
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w5, aes(x=factor(t_walks))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w5, echo=F}
AfterH <- table(ALSA_ds_w5$t_walks)
X<-table(ALSA_w5$WALK2WW5)
BeforeH <- c(X[2:1],X[3]+sum(is.na(ALSA_w5$WALK2WW5)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","3,NA->999") 
kable(C)
```







### Wave 6

#### Study-specific variable description

| **Name** | `WALK2WW6` |
|-|-|
| **Label** | `walk in last 2 weeks` |
| **Table name** | `ALSA-Wave6` |
| **Categories:**| `1 = Yes` <br/> `2 = No`|
| **Missings:**|`0 = no answer` <br/> `NA`|
| **Description** |  |

   

```{r assign w6, echo=F}
opal.assign.table.tibble(o, 'ALSA_w6','ALSA.ALSA-Wave6', variables=list('WALK2WW6'), missings = TRUE)
ALSA_w6 <- opal.execute(o,'ALSA_w6')
```

```{r local w6, echo=F}
vbl <- ALSA_w6$WALK2WW6
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w6)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w6, aes(x=factor(WALK2WW6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `t_walks` from the study-specific variable it has to be recoded as follows:

* `2 into 0` 
* `0 into 999` 
* `NA into 999`

**R script:**

```{r harmo w6}
ALSA_ds_w6 <- tibble(id=ALSA_w6$id)
ALSA_ds_w6$t_walks <- car::recode(ALSA_w6$WALK2WW6, "2 = 0;0 = 999;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w6, echo=F}
vbl <- ALSA_ds_w6$t_walks
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w6, aes(x=factor(t_walks))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w6, echo=F}
AfterH <- table(ALSA_ds_w6$t_walks)
X<-table(ALSA_w6$WALK2WW6)
BeforeH <- c(X[3:2],X[1]+sum(is.na(ALSA_w6$WALK2WW6)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","0,NA->999") 
kable(C)
```





### Wave 7

#### Study-specific variable description

| **Name** | `walk2ww7` |
|-|-|
| **Label** | `in the past two weeks, did you walk for recreation or exercise?` |
| **Table name** | `ALSA-Wave7` |
| **Categories:**| `1 = Yes` <br/> `2 = No`|
| **Missings:**|`0 = not answered/missing` <br/> `NA`|
| **Description** |  |

   

```{r assign w7, echo=F}
opal.assign.table.tibble(o, 'ALSA_w7','ALSA.ALSA-Wave7', variables=list('walk2ww7'), missings = TRUE)
ALSA_w7 <- opal.execute(o,'ALSA_w7')
```

```{r local w7, echo=F}
vbl <- ALSA_w7$walk2ww7
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w7)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w7, aes(x=factor(walk2ww7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `t_walks` from the study-specific variable it has to be recoded as follows:

* `2 into 0` 
* `0 into 999` 
* `NA into 999`

**R script:**

```{r harmo w7}
ALSA_ds_w7 <- tibble(id=ALSA_w7$id)
ALSA_ds_w7$t_walks <- car::recode(ALSA_w7$walk2ww7, "2 = 0;0 = 999;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w7, echo=F}
vbl <- ALSA_ds_w7$t_walks
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w7, aes(x=factor(t_walks))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w7, echo=F}
AfterH <- table(ALSA_ds_w7$t_walks)
X<-table(ALSA_w7$walk2ww7)
BeforeH <- c(X[3:2],X[1]+sum(is.na(ALSA_w7$walk2ww7)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","0,NA->999") 
kable(C)
```



### Wave 8

#### Study-specific variable description

| **Name** | `walk2ww8` |
|-|-|
| **Label** | `in the past two weeks, did you walk for recreation or exercise?` |
| **Table name** | `ALSA-Wave8` |
| **Categories:**| `1 = Yes` <br/> `2 = No`|
| **Missings:**|`0 = Not Answered` <br/> `NA`|
| **Description** |  |

   

```{r assign w8, echo=F}
opal.assign.table.tibble(o, 'ALSA_w8','ALSA.ALSA-Wave8', variables=list('walk2ww8'), missings = TRUE)
ALSA_w8 <- opal.execute(o,'ALSA_w8')
```

```{r local w8, echo=F}
vbl <- ALSA_w8$walk2ww8
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w8)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w8, aes(x=factor(walk2ww8))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `t_walks` from the study-specific variable it has to be recoded as follows:

* `2 into 0` 
* `0 into 999` 
* `NA into 999`

**R script:**

```{r harmo w8}
ALSA_ds_w8 <- tibble(id=ALSA_w8$id)
ALSA_ds_w8$t_walks <- car::recode(ALSA_w8$walk2ww8, "2 = 0;0 = 999;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w8, echo=F}
vbl <- ALSA_ds_w8$t_walks
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w8, aes(x=factor(t_walks))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w8, echo=F}
AfterH <- table(ALSA_ds_w8$t_walks)
X<-table(ALSA_w8$walk2ww8)
BeforeH <- c(X[3:2],X[1]+sum(is.na(ALSA_w8$walk2ww8)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","0,NA->999") 
kable(C)
```






### Wave 9

#### Study-specific variable description

| **Name** | `WALK2WW9` |
|-|-|
| **Label** | `in the past two weeks, did you walk for recreation or exercise?` |
| **Table name** | `ALSA-Wave9` |
| **Categories:**| `1 = Yes` <br/> `2 = No`|
| **Missings:**| `0 = Not Answered` <br/> `NA`|
| **Description** |  |

   

```{r assign w9, echo=F}
opal.assign.table.tibble(o, 'ALSA_w9','ALSA.ALSA-Wave9', variables=list('WALK2WW9'), missings = TRUE)
ALSA_w9 <- opal.execute(o,'ALSA_w9')
```

```{r local w9, echo=F}
vbl <- ALSA_w9$WALK2WW9
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w9)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w9, aes(x=factor(WALK2WW9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `t_walks` from the study-specific variable it has to be recoded as follows:

* `2 into 0` 
* `0 into 999`
* `NA into 999`

**R script:**

```{r harmo w9}
ALSA_ds_w9 <- tibble(id=ALSA_w9$id)
ALSA_ds_w9$t_walks <- car::recode(ALSA_w9$WALK2WW9, "2 = 0;0 = 999;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w9, echo=F}
vbl <- ALSA_ds_w9$t_walks
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w9, aes(x=factor(t_walks))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w9, echo=F}
AfterH <- table(ALSA_ds_w9$t_walks)
X<-table(ALSA_w9$WALK2WW9)
BeforeH <- c(X[3:2],X[1]+sum(is.na(ALSA_w9$WALK2WW9)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","0,NA->999") 
kable(C)
```




### Wave 10

#### Study-specific variable description

| **Name** | `walk2ww10` |
|-|-|
| **Label** | `in the past two weeks, did you walk for recreation or exercise?` |
| **Table name** | `ALSA-Wave10` |
| **Categories:**| `0 = No` <br/> `1 = Yes`|
| **Missings:**|  `NA`|
| **Description** |  |

   

```{r assign w10, echo=F}
opal.assign.table.tibble(o, 'ALSA_w10','ALSA.ALSA-Wave10', variables=list('walk2ww10'), missings = TRUE)
ALSA_w10 <- opal.execute(o,'ALSA_w10')
```

```{r local w10, echo=F}
vbl <- ALSA_w10$walk2ww10
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w10)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w10, aes(x=factor(walk2ww10))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo w10}
ALSA_ds_w10 <- tibble(id=ALSA_w10$id)
ALSA_ds_w10$t_walks <- car::recode(ALSA_w10$walk2ww10, "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w10, echo=F}
vbl <- ALSA_ds_w10$t_walks
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w10, aes(x=factor(t_walks))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w10, echo=F}
```



### Wave 11

#### Study-specific variable description

| **Name** | `WALK2WW11` |
|-|-|
| **Label** | `in the past two weeks, did you walk for recreation or exercise?` |
| **Table name** | `ALSA-Wave11` |
| **Categories:**| `0 = No` <br/> `1 = Yes`|
| **Missings:**|`NA`|
| **Description** |  |

   

```{r assign w11, echo=F}
opal.assign.table.tibble(o, 'ALSA_w11','ALSA.ALSA-Wave11', variables=list('WALK2WW11'), missings = TRUE)
ALSA_w11 <- opal.execute(o,'ALSA_w11')
```

```{r local w11, echo=F}
vbl <- ALSA_w11$WALK2WW11
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w11)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w11, aes(x=factor(WALK2WW11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo w11}
ALSA_ds_w11 <- tibble(id=ALSA_w11$id)
ALSA_ds_w11$t_walks <- car::recode(ALSA_w11$WALK2WW11, "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w11, echo=F}
vbl <- ALSA_ds_w11$t_walks
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w11, aes(x=factor(t_walks))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w11, echo=F}
```




### Wave 12

#### Study-specific variable description

| **Name** | `WALK2WW12` |
|-|-|
| **Label** | `in the past two weeks, did you walk for recreation or exercise?` |
| **Table name** | `ALSA-Wave12` |
| **Categories:**|`0 = No` <br/> `1 = Yes`|
| **Missings:**|`NA`|
| **Description** |  |

   

```{r assign w12, echo=F}
opal.assign.table.tibble(o, 'ALSA_w12','ALSA.ALSA-Wave12', variables=list('WALK2WW12'), missings = TRUE)
ALSA_w12 <- opal.execute(o,'ALSA_w12')
```

```{r local w12, echo=F}
vbl <- ALSA_w12$WALK2WW12
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w12)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w12, aes(x=factor(WALK2WW12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo w12}
ALSA_ds_w12 <- tibble(id=ALSA_w12$id)
ALSA_ds_w12$t_walks <- car::recode(ALSA_w12$WALK2WW12, "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w12, echo=F}
vbl <- ALSA_ds_w12$t_walks
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w12, aes(x=factor(t_walks))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w12, echo=F}
```




### Wave 13

#### Study-specific variable description

| **Name** | `WALK2WW13` |
|-|-|
| **Label** | `in the past two weeks, did you walk for recreation or exercise?` |
| **Table name** | `ALSA-Wave13` |
| **Categories:**|`0 = No` <br/> `1 = Yes`|
| **Missings:**|`NA`|
| **Description** |  |

   

```{r assign w13, echo=F}
opal.assign.table.tibble(o, 'ALSA_w13','ALSA.ALSA-Wave13', variables=list('WALK2WW13'), missings = TRUE)
ALSA_w13 <- opal.execute(o,'ALSA_w13')
```

```{r local w13, echo=F}
vbl <- ALSA_w13$WALK2WW13
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w13)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w13, aes(x=factor(WALK2WW13))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo w13}
ALSA_ds_w13 <- tibble(id=ALSA_w13$id)
ALSA_ds_w13$t_walks <- car::recode(ALSA_w13$WALK2WW13, "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w13, echo=F}
vbl <- ALSA_ds_w13$t_walks
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w13, aes(x=factor(t_walks))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w13, echo=F}
```





```{r final, echo=F}

l.hds <- list(w1 = ALSA_ds_w1, w3 = ALSA_ds_w3, w4 = ALSA_ds_w4, w5 = ALSA_ds_w5, w6 = ALSA_ds_w6, w7 = ALSA_ds_w7, w8 = ALSA_ds_w8, w9 = ALSA_ds_w9, w10 = ALSA_ds_w10, w11 = ALSA_ds_w11, w12 = ALSA_ds_w12, w13 = ALSA_ds_w13)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("ALSA_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

```

## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.


```{r summ}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",names(l.hds))
kable(t.hds)

dbb <- get(paste0("ALSA_m_ds_",names(l.hds)[1]))[,c("id","t_walks")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("ALSA_m_ds_",names(l.hds)[ind]))[,c("id","t_walks")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", names(l.hds))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])

```


# Quality estimation
[Comments on the quality of the new harmonised variable.]


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  t_walks <- l.hds[[index]]
  save(t_walks, file = paste0(datafolder,names(l.hds)[index],"/t_walks.RData"))
}

```
<!-- ########################################################## --> 



<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
