---
title: "Vigorous Physical Activity"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/vig_paDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/vig_paDS.R')
```




# Data process


## Australia

### Wave 1 

#### Study-specific variable description

| **Name** | `VIGEXCS` |
|-|-|
| **Label** | `in the past 2 weeks did you engage in vigorous exercise (such as tennis, joggig etc?)` |
| **Table name** | `ALSA-Wave1` |
| **Categories:**| `1 = Yes` <br/> `2 = No`|
| **Missings:**|`9 = Missing` <br/> `NA`|
| **Description** |  |

   

```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'ALSA_w1','ALSA.ALSA-Wave1', variables=list('VIGEXCS'), missings = TRUE)
ALSA_w1 <- opal.execute(o,'ALSA_w1')
```

```{r local w1, echo=F}
vbl <- ALSA_w1$VIGEXCS
kable(Categorical_summary(vbl, missing_values = c(9))[3], caption = names(ALSA_w1)[2])
kable(Categorical_summary(vbl, missing_values = c(9))[1], caption = "Category")
ggplot(ALSA_w1, aes(x=factor(VIGEXCS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `2 into 0` 
* `9 into 999` 
* `NA into 999`

**R script:**

```{r harmo w1}
ALSA_ds_w1 <- tibble(id=ALSA_w1$id)
ALSA_ds_w1$vig_pa <- car::recode(ALSA_w1$VIGEXCS, "2 = 0;9 = 999;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vbl <- ALSA_ds_w1$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w1, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(ALSA_ds_w1$vig_pa)
X<-table(ALSA_w1$VIGEXCS)
BeforeH <- c(X[2:1],X[3]+sum(is.na(ALSA_w1$VIGEXCS)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","9,NA->999") 
kable(C)
```



### Wave 2

Not found


### Wave 3

Not found


### Wave 4

#### Study-specific variable description

| **Name** | `VIGEXCW4` |
|-|-|
| **Label** | `Did you engage in vigorous exercise?` |
| **Table name** | `ALSA-Wave4` |
| **Categories:**| `1 = Yes` <br/> `2 = No`|
| **Missings:**|`NA`|
| **Description** |  |

   

```{r assign w4, echo=F}
opal.assign.table.tibble(o, 'ALSA_w4','ALSA.ALSA-Wave4', variables=list('VIGEXCW4'), missings = TRUE)
ALSA_w4 <- opal.execute(o,'ALSA_w4')
```

```{r local w4, echo=F}
vbl <- ALSA_w4$VIGEXCW4
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w4)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w4, aes(x=factor(VIGEXCW4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `2 into 0` 
* `NA into 999`

**R script:**

```{r harmo w4}
ALSA_ds_w4 <- tibble(id=ALSA_w4$id)
ALSA_ds_w4$vig_pa <- car::recode(ALSA_w4$VIGEXCW4, "2 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w4, echo=F}
vbl <- ALSA_ds_w4$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w4, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w4, echo=F}
```





### Wave 5

#### Study-specific variable description

| **Name** | `VIGEXCW5` |
|-|-|
| **Label** | `Q9 Now I have some questions about exercise. In the past two weeks did you engage in vigorous exercise` |
| **Table name** | `ALSA-Wave5` |
| **Categories:**| `1 = Yes` <br/> `2 = No`|
| **Missings:**| `3 = Refused/Dont know (do not read)` <br/> `NA` |
| **Description** |  |

   

```{r assign w5, echo=F}
opal.assign.table.tibble(o, 'ALSA_w5','ALSA.ALSA-Wave5', variables=list('VIGEXCW5'), missings = TRUE)
ALSA_w5 <- opal.execute(o,'ALSA_w5')
```

```{r local w5, echo=F}
vbl <- ALSA_w5$VIGEXCW5
kable(Categorical_summary(vbl, missing_values = c(3))[3], caption = names(ALSA_w5)[2])
kable(Categorical_summary(vbl, missing_values = c(3))[1], caption = "Category")
ggplot(ALSA_w5, aes(x=factor(VIGEXCW5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `2 into 0` 
* `3 into 999`
* `NA into 999`

**R script:**

```{r harmo w5}
ALSA_ds_w5 <- tibble(id=ALSA_w5$id)
ALSA_ds_w5$vig_pa <- car::recode(ALSA_w5$VIGEXCW5, "2 = 0;3 = 999;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w5, echo=F}
vbl <- ALSA_ds_w5$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w5, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w5, echo=F}
```








### Wave 6

#### Study-specific variable description

| **Name** | `VIGEXCW6` |
|-|-|
| **Label** | `vigorous exercise last 2 weeks` |
| **Table name** | `ALSA-Wave6` |
| **Categories:**| `1 = Yes` <br/> `2 = No`|
| **Missings:**|`0 = no answer` <br/> `NA`|
| **Description** |  |

   

```{r assign w6, echo=F}
opal.assign.table.tibble(o, 'ALSA_w6','ALSA.ALSA-Wave6', variables=list('VIGEXCW6'), missings = TRUE)
ALSA_w6 <- opal.execute(o,'ALSA_w6')
```

```{r local w6, echo=F}
vbl <- ALSA_w6$VIGEXCW6
kable(Categorical_summary(vbl, missing_values = c(0))[3], caption = names(ALSA_w6)[2])
kable(Categorical_summary(vbl, missing_values = c(0))[1], caption = "Category")
ggplot(ALSA_w6, aes(x=factor(VIGEXCW6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `2 into 0` 
* `0 into 995` 
* `NA into 999`

**R script:**

```{r harmo w6}
ALSA_ds_w6 <- tibble(id=ALSA_w6$id)
ALSA_ds_w6$vig_pa <- car::recode(ALSA_w6$VIGEXCW6, "2 = 0;0 = 995;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w6, echo=F}
vbl <- ALSA_ds_w6$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w6, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w6, echo=F}
```





### Wave 7

#### Study-specific variable description

| **Name** | `vigexcw7` |
|-|-|
| **Label** | `in the past 2 weeks did you engage in vigourous exercise` |
| **Table name** | `ALSA-Wave7` |
| **Categories:**| `1 = Yes` <br/> `2 = No`|
| **Missings:**|`0 = not answered/missing` <br/> `NA`|
| **Description** |  |

   

```{r assign w7, echo=F}
opal.assign.table.tibble(o, 'ALSA_w7','ALSA.ALSA-Wave7', variables=list('vigexcw7'), missings = TRUE)
ALSA_w7 <- opal.execute(o,'ALSA_w7')
```

```{r local w7, echo=F}
vbl <- ALSA_w7$vigexcw7
kable(Categorical_summary(vbl, missing_values = c(0))[3], caption = names(ALSA_w7)[2])
kable(Categorical_summary(vbl, missing_values = c(0))[1], caption = "Category")
ggplot(ALSA_w7, aes(x=factor(vigexcw7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `2 into 0` 
* `0 into 995` 
* `NA into 999`

**R script:**

```{r harmo w7}
ALSA_ds_w7 <- tibble(id=ALSA_w7$id)
ALSA_ds_w7$vig_pa <- car::recode(ALSA_w7$vigexcw7, "2 = 0;0 = 995;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w7, echo=F}
vbl <- ALSA_ds_w7$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w7, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w7, echo=F}
AfterH <- table(ALSA_ds_w7$vig_pa)
X<-table(ALSA_w7$vigexcw7)
BeforeH <- c(X[3:2],X[1],sum(is.na(ALSA_w7$vigexcw7)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","0->995","NA->999") 
kable(C)
```




### Wave 8

#### Study-specific variable description

| **Name** | `vigexcw8` |
|-|-|
| **Label** | `In the past two weeks did you engage in vigorous exercise` |
| **Table name** | `ALSA-Wave8` |
| **Categories:**| `1 = Yes` <br/> `2 = No`|
| **Missings:**|`0 = Not Answered` <br/> `NA`|
| **Description** |  |

   

```{r assign w8, echo=F}
opal.assign.table.tibble(o, 'ALSA_w8','ALSA.ALSA-Wave8', variables=list('vigexcw8'), missings = TRUE)
ALSA_w8 <- opal.execute(o,'ALSA_w8')
```

```{r local w8, echo=F}
vbl <- ALSA_w8$vigexcw8
kable(Categorical_summary(vbl, missing_values = c(0))[3], caption = names(ALSA_w8)[2])
kable(Categorical_summary(vbl, missing_values = c(0))[1], caption = "Category")
ggplot(ALSA_w8, aes(x=factor(vigexcw8))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `2 into 0` 
* `0 into 995` 
* `NA into 999`

**R script:**

```{r harmo w8}
ALSA_ds_w8 <- tibble(id=ALSA_w8$id)
ALSA_ds_w8$vig_pa <- car::recode(ALSA_w8$vigexcw8, "2 = 0;0 = 995;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w8, echo=F}
vbl <- ALSA_ds_w8$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w8, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w8, echo=F}
AfterH <- table(ALSA_ds_w8$vig_pa)
X<-table(ALSA_w8$vigexcw8)
BeforeH <- c(X[3:2],X[1],sum(is.na(ALSA_w8$vigexcw8)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","0->995","NA->999") 
kable(C)
```





### Wave 9

#### Study-specific variable description

| **Name** | `VIGEXCW9` |
|-|-|
| **Label** | `vigorous exercise in past 2 weeks` |
| **Table name** | `ALSA-Wave9` |
| **Categories:**| `1 = Yes` <br/> `2 = No`|
| **Missings:**| `0 = Not Answered` <br/> `NA`|
| **Description** |  |

   

```{r assign w9, echo=F}
opal.assign.table.tibble(o, 'ALSA_w9','ALSA.ALSA-Wave9', variables=list('VIGEXCW9'), missings = TRUE)
ALSA_w9 <- opal.execute(o,'ALSA_w9')
```

```{r local w9, echo=F}
vbl <- ALSA_w9$VIGEXCW9
kable(Categorical_summary(vbl, missing_values = c(0))[3], caption = names(ALSA_w9)[2])
kable(Categorical_summary(vbl, missing_values = c(0))[1], caption = "Category")
ggplot(ALSA_w9, aes(x=factor(VIGEXCW9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `vig_pa` from the study-specific variable it has to be recoded as follows:

* `2 into 0` 
* `0 into 995`
* `NA into 999`

**R script:**

```{r harmo w9}
ALSA_ds_w9 <- tibble(id=ALSA_w9$id)
ALSA_ds_w9$vig_pa <- car::recode(ALSA_w9$VIGEXCW9, "2 = 0;0 = 995;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w9, echo=F}
vbl <- ALSA_ds_w9$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w9, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w9, echo=F}
AfterH <- table(ALSA_ds_w9$vig_pa)
X<-table(ALSA_w9$VIGEXCW9)
BeforeH <- c(X[3:2],X[1],sum(is.na(ALSA_w9$VIGEXCW9)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","0->995","NA->999") 
kable(C)
```



### Wave 10

Not found


### Wave 11

#### Study-specific variable description

| **Name** | `VIGEXCW11` |
|-|-|
| **Label** | `vigorous exercise in past 2 weeks` |
| **Table name** | `ALSA-Wave11` |
| **Categories:**| `0 = No` <br/> `1 = Yes`|
| **Missings:**|`NA`|
| **Description** |  |

   

```{r assign w11, echo=F}
opal.assign.table.tibble(o, 'ALSA_w11','ALSA.ALSA-Wave11', variables=list('VIGEXCW11'), missings = TRUE)
ALSA_w11 <- opal.execute(o,'ALSA_w11')
```

```{r local w11, echo=F}
vbl <- ALSA_w11$VIGEXCW11
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w11)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w11, aes(x=factor(VIGEXCW11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo w11}
ALSA_ds_w11 <- tibble(id=ALSA_w11$id)
ALSA_ds_w11$vig_pa <- car::recode(ALSA_w11$VIGEXCW11, "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w11, echo=F}
vbl <- ALSA_ds_w11$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w11, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w11, echo=F}
```


### Wave 12

#### Study-specific variable description

| **Name** | `VIGEXCW12` |
|-|-|
| **Label** | `vigorous exercise in past 2 weeks` |
| **Table name** | `ALSA-Wave12` |
| **Categories:**|`0 = No` <br/> `1 = Yes`|
| **Missings:**|`NA`|
| **Description** |  |

   

```{r assign w12, echo=F}
opal.assign.table.tibble(o, 'ALSA_w12','ALSA.ALSA-Wave12', variables=list('VIGEXCW12'), missings = TRUE)
ALSA_w12 <- opal.execute(o,'ALSA_w12')
```

```{r local w12, echo=F}
vbl <- ALSA_w12$VIGEXCW12
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w12)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w12, aes(x=factor(VIGEXCW12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo w12}
ALSA_ds_w12 <- tibble(id=ALSA_w12$id)
ALSA_ds_w12$vig_pa <- car::recode(ALSA_w12$VIGEXCW12, "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w12, echo=F}
vbl <- ALSA_ds_w12$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w12, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w12, echo=F}
```


### Wave 13

Not found







## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.


```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


alsa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"), w6 = c("w6","W6"), w7 = c("w7","W7"), w8 = c("w8","W8"), w9 = c("w9","W9"), w10 = c("w10","W10"), w11 = c("w11","W11"), w12 = c("w12","W12"), w13 = c("w13","W13"))

# Consider only harmonised waves
l.hds <- lapply(alsa.cw, function(wname) if(exists(paste0("ALSA_ds_",wname[1]))){wname = list(get(paste0("ALSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```






# Quality estimation
[Comments on the quality of the new harmonised variable.]



<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
