---
title: "Frequency of Vigorous Physical Activity"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/f_vig_paDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/f_vig_paDS.R')
```




# Data process


## Australia

### Wave 1 

#### Study-specific variable description

| **Name** | `VIGEXC2W` |`vig_pa`|
|-|-|-|
| **Label** | `Vigor Sessions in past 2 weeks` |`Engage in vigorous exercise during the last 2 weeks`|
| **Table name** | `ALSA-Wave1` |`vig_pa`|
| **Categories:**| `continuous`|`0 = No`<br/>`1 = Yes`|
| **Missings:**| `NA` | `991 = CAPI/interviewer error`<br/>`992 = Impute`<br/>`993 = Disable to measure`<br/>`994 = Not attempt/not done`<br/>`995 = Does not answer`<br/>`996 = Not applicable`<br/>`997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` |
| **Description** |  |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'ALSA_w1','ALSA.ALSA-Wave1', variables=list('VIGEXC2W'), missings = TRUE)
ALSA_w1 <- opal.execute(o,'ALSA_w1')
load(paste0(datafolder,"w1/vig_pa.RData"))
ALSA_w1 <- left_join(ALSA_w1,vig_pa, by="id")
rm(vig_pa)

```

```{r local w1, echo=F}

vbl <- ALSA_w1$VIGEXC2W
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = names(ALSA_w1)[2]) 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_w1, aes(VIGEXC2W)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w1$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "vig_pa")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ALSA_w1, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `f_vig_pa` from the study-specific variable `VIGEXC2W` it has to be recoded as follows:

* `VIGEXC2W/2`
* `1 into 1`
* `2,3 into 2`
* `,4,5 into 3`
* `>5 into 4`
* `NA into 999`
* `vig_pa == 0 into 0`

**R script:**

```{r harmo w1}

ALSA_ds_w1 <- tibble(id=ALSA_w1$id)
ALSA_ds_w1$f_vig_pa <- car::recode(ceiling(ALSA_w1$VIGEXC2W/2), "c(1) = 1; c(2,3) = 2; c(4,5) = 3; 6:hi = 4; NA = 999 ")
ALSA_ds_w1$f_vig_pa[which(ALSA_w1$vig_pa == 0)] <- 0

```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vbl <- ALSA_ds_w1$f_vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w1, aes(x=factor(f_vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}

```





### Wave 2

Not found




### Wave 3

#### Study-specific variable description

| **Name** | `VIGEXCW3` |
|-|-|
| **Label** | `VIGOR SESSIONS IN PAST 2 WEEKS` |
| **Table name** | `ALSA-Wave3` |
| **Categories:**| `continuous`|
| **Missings:**| `99`<br/>`NA` |
| **Description** |  |

```{r assign w3, echo=F}
opal.assign.table.tibble(o, 'ALSA_w3','ALSA.ALSA-Wave3', variables=list('VIGEXCW3'), missings = TRUE)
ALSA_w3 <- opal.execute(o,'ALSA_w3')
```

```{r local w3, echo=F}
vbl <- ALSA_w3$VIGEXCW3
vbl_miss <- c(99)
kable(Continuous_summary(vbl, missing_values = vbl_miss)[3], caption = names(ALSA_w3)[2]) 
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(ALSA_w3, aes(VIGEXCW3)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% vbl_miss)) + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `f_vig_pa` from the study-specific variable it has to be recoded as follows:

* `VIGEXCW3/2`
* `1 into 1`
* `2,3 into 2`
* `,4,5 into 3`
* `>5 into 4`
* `NA into 999`

**R script:**

```{r harmo w3}
ALSA_ds_w3 <- tibble(id=ALSA_w3$id)
ALSA_ds_w3$f_vig_pa <- car::recode(ceiling(ALSA_w3$VIGEXCW3/2), "50 = 999; c(1) = 1; c(2,3) = 2; c(4,5) = 3; 6:hi = 4; NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}
vbl <- ALSA_ds_w3$f_vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w3, aes(x=factor(f_vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=F}

```






### Wave 4

Not found


### Wave 5

Not found




### Wave 6

#### Study-specific variable description

| **Name** | `VIGEXW6` |`vig_pa`|
|-|-|-|
| **Label** | `number of vigorous exercise sessions` |`Engage in vigorous exercise during the last 2 weeks`|
| **Table name** | `ALSA-Wave6` |`vig_pa`|
| **Categories:**| `continuous`|`0 = No`<br/>`1 = Yes`|
| **Missings:**| `NA` | `991 = CAPI/interviewer error`<br/>`992 = Impute`<br/>`993 = Disable to measure`<br/>`994 = Not attempt/not done`<br/>`995 = Does not answer`<br/>`996 = Not applicable`<br/>`997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` |
| **Description** |  |  |

```{r assign w6, echo=F}

opal.assign.table.tibble(o, 'ALSA_w6','ALSA.ALSA-Wave6', variables=list('VIGEXW6'), missings = TRUE)
ALSA_w6 <- opal.execute(o,'ALSA_w6')
load(paste0(datafolder,"w6/vig_pa.RData"))
ALSA_w6 <- left_join(ALSA_w6,vig_pa, by="id")
rm(vig_pa)

```

```{r local w6, echo=F}

vbl <- ALSA_w6$VIGEXW6
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = names(ALSA_w6)[2]) 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_w6, aes(VIGEXW6)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w6$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "vig_pa")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ALSA_w6, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `f_vig_pa` from the study-specific variable `VIGEXW6` it has to be recoded as follows:

* `VIGEXCW6/2`
* `1 into 1`
* `2,3 into 2`
* `,4,5 into 3`
* `>5 into 4`
* `NA into 999`
* `vig_pa == 0 into 0`

**R script:**

```{r harmo w6}

ALSA_ds_w6 <- tibble(id=ALSA_w6$id)
ALSA_ds_w6$f_vig_pa <- car::recode(ceiling(ALSA_w6$VIGEXW6/2), "c(1) = 1; c(2,3) = 2; c(4,5) = 3; 6:hi = 4; NA = 999 ")
ALSA_ds_w6$f_vig_pa[which(ALSA_w6$vig_pa == 0)] <- 0

```

#### Statistical description of the new harmonised variable
```{r descript w6, echo=F}
vbl <- ALSA_ds_w6$f_vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w6, aes(x=factor(f_vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w6, echo=F}

```






### Wave 7

#### Study-specific variable description

| **Name** | `vigexw7` |`vig_pa`|
|-|-|-|
| **Label** | `how many sessiosn of vigourous exercise in the past 2 weeks` |`Engage in vigorous exercise during the last 2 weeks`|
| **Table name** | `ALSA-Wave7` |`vig_pa`|
| **Categories:**| `continuous`|`0 = No`<br/>`1 = Yes`|
| **Missings:**| `0 = Not answered` <br/> `99 = No vigorous exercise` <br/> `NA` | `991 = CAPI/interviewer error`<br/>`992 = Impute`<br/>`993 = Disable to measure`<br/>`994 = Not attempt/not done`<br/>`995 = Does not answer`<br/>`996 = Not applicable`<br/>`997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` |
| **Description** |  |  |

```{r assign w7, echo=F}

opal.assign.table.tibble(o, 'ALSA_w7','ALSA.ALSA-Wave7', variables=list('vigexw7'), missings = TRUE)
ALSA_w7 <- opal.execute(o,'ALSA_w7')
load(paste0(datafolder,"w7/vig_pa.RData"))
ALSA_w7 <- left_join(ALSA_w7,vig_pa, by="id")
rm(vig_pa)

```

```{r local w7, echo=F}

vbl <- ALSA_w7$vigexw7
vbl_miss <- c(0,99)
kable(Continuous_summary(vbl, missing_values = vbl_miss)[3], caption = names(ALSA_w7)[2]) 
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(ALSA_w7, aes(vigexw7)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% vbl_miss)) + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w7$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "vig_pa")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ALSA_w7, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `f_vig_pa` from the study-specific variable `vigexw7` it has to be recoded as follows:

* `99 into 0`
* `vigexw7/2`
* `1 into 1`
* `2,3 into 2`
* `,4,5 into 3`
* `>5 into 4`
* `NA into 999`
* `0 into 995`
* `vig_pa == 0 into 0`

**R script:**

```{r harmo w7}

ALSA_ds_w7 <- tibble(id=ALSA_w7$id)
ALSA_ds_w7$f_vig_pa <- car::recode(ceiling(ALSA_w7$vigexw7/2), "50 = 0 ;c(1) = 1; c(2,3) = 2; c(4,5) = 3; 6:hi = 4; NA = 999; 0 = 995 ")
ALSA_ds_w7$f_vig_pa[which(ALSA_w7$vig_pa == 0)] <- 0

```

#### Statistical description of the new harmonised variable
```{r descript w7, echo=F}
vbl <- ALSA_ds_w7$f_vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w7, aes(x=factor(f_vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w7, echo=F}

```




### Wave 8

Not found




### Wave 9

#### Study-specific variable description

| **Name** | `VIGEXW9` |`vig_pa`|
|-|-|-|
| **Label** | `how many sessions of vigourous exercise in the past 2 weeks` |`Engage in vigorous exercise during the last 2 weeks`|
| **Table name** | `ALSA-Wave9` |`vig_pa`|
| **Categories:**| `continuous`|`0 = No`<br/>`1 = Yes`|
| **Missings:**| `NA` | `991 = CAPI/interviewer error`<br/>`992 = Impute`<br/>`993 = Disable to measure`<br/>`994 = Not attempt/not done`<br/>`995 = Does not answer`<br/>`996 = Not applicable`<br/>`997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` |
| **Description** |  |  |

```{r assign w9, echo=F}

opal.assign.table.tibble(o, 'ALSA_w9','ALSA.ALSA-Wave9', variables=list('VIGEXW9'), missings = TRUE)
ALSA_w9 <- opal.execute(o,'ALSA_w9')
load(paste0(datafolder,"w9/vig_pa.RData"))
ALSA_w9 <- left_join(ALSA_w9,vig_pa, by="id")
rm(vig_pa)

```

```{r local w9, echo=F}

vbl <- ALSA_w9$VIGEXW9
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = names(ALSA_w9)[2]) 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_w9, aes(VIGEXW9)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w9$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "vig_pa")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ALSA_w9, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `f_vig_pa` from the study-specific variable `VIGEXW9` it has to be recoded as follows:

* `VIGEXW9/2`
* `1 into 1`
* `2,3 into 2`
* `,4,5 into 3`
* `>5 into 4`
* `NA into 999`
* `vig_pa == 0 into 0`

**R script:**

```{r harmo w9}

ALSA_ds_w9 <- tibble(id=ALSA_w9$id)
ALSA_ds_w9$f_vig_pa <- car::recode(ceiling(ALSA_w9$VIGEXW9/2), "c(1) = 1; c(2,3) = 2; c(4,5) = 3; 6:hi = 4; NA = 999 ")
ALSA_ds_w9$f_vig_pa[which(ALSA_w9$vig_pa == 0)] <- 0

```

#### Statistical description of the new harmonised variable
```{r descript w9, echo=F}
vbl <- ALSA_ds_w9$f_vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w9, aes(x=factor(f_vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w9, echo=F}

```



### Wave 10

Not found





### Wave 11

#### Study-specific variable description

| **Name** | `VIGEXW11` |`vig_pa`|
|-|-|-|
| **Label** | `how many vigorous exercise sessions in past 2 weeks` |`Engage in vigorous exercise during the last 2 weeks`|
| **Table name** | `ALSA-Wave11` |`vig_pa`|
| **Categories:**| `continuous`|`0 = No`<br/>`1 = Yes`|
| **Missings:**| `NA` | `991 = CAPI/interviewer error`<br/>`992 = Impute`<br/>`993 = Disable to measure`<br/>`994 = Not attempt/not done`<br/>`995 = Does not answer`<br/>`996 = Not applicable`<br/>`997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` |
| **Description** |  |  |

```{r assign w11, echo=F}

opal.assign.table.tibble(o, 'ALSA_w11','ALSA.ALSA-Wave11', variables=list('VIGEXW11'), missings = TRUE)
ALSA_w11 <- opal.execute(o,'ALSA_w11')
load(paste0(datafolder,"w11/vig_pa.RData"))
ALSA_w11 <- left_join(ALSA_w11,vig_pa, by="id")
rm(vig_pa)

```

```{r local w11, echo=F}

vbl <- ALSA_w11$VIGEXW11
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = names(ALSA_w11)[2]) 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_w11, aes(VIGEXW11)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + scale_x_continuous(breaks = c(0,2,4,6))

vbl <- ALSA_w11$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "vig_pa")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ALSA_w11, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `f_vig_pa` from the study-specific variable `VIGEXW11` it has to be recoded as follows:

* `VIGEXW11/2`
* `1 into 1`
* `2,3 into 2`
* `,4,5 into 3`
* `>5 into 4`
* `NA into 999`
* `vig_pa == 0 into 0`

**R script:**

```{r harmo w11}

ALSA_ds_w11 <- tibble(id=ALSA_w11$id)
ALSA_ds_w11$f_vig_pa <- car::recode(ceiling(ALSA_w11$VIGEXW11/2), "c(1) = 1; c(2,3) = 2; c(4,5) = 3; 6:hi = 4; NA = 999 ")
ALSA_ds_w11$f_vig_pa[which(ALSA_w11$vig_pa == 0)] <- 0

```

#### Statistical description of the new harmonised variable
```{r descript w11, echo=F}
vbl <- ALSA_ds_w11$f_vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w11, aes(x=factor(f_vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w11, echo=F}

```



### Wave 12

#### Study-specific variable description

| **Name** | `VIGEXW12` |`vig_pa`|
|-|-|-|
| **Label** | `how many vigorous exercise sessions in past 2 weeks` |`Engage in vigorous exercise during the last 2 weeks`|
| **Table name** | `ALSA-Wave12` |`vig_pa`|`0 = No`<br/>`1 = Yes`|
| **Categories:**| `continuous`|`0 = No`<br/>`1 = Yes`|
| **Missings:**| `NA` |`991 = CAPI/interviewer error`<br/>`992 = Impute`<br/>`993 = Disable to measure`<br/>`994 = Not attempt/not done`<br/>`995 = Does not answer`<br/>`996 = Not applicable`<br/>`997 = Refuse`<br/>`998 = Do not know`<br/>`999 = Missing` |
| **Description** |  |  |

```{r assign w12, echo=F}

opal.assign.table.tibble(o, 'ALSA_w12','ALSA.ALSA-Wave12', variables=list('VIGEXW12'), missings = TRUE)
ALSA_w12 <- opal.execute(o,'ALSA_w12')
load(paste0(datafolder,"w12/vig_pa.RData"))
ALSA_w12 <- left_join(ALSA_w12,vig_pa, by="id")
rm(vig_pa)

```

```{r local w12, echo=F}

vbl <- ALSA_w12$VIGEXW12
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = names(ALSA_w12)[2]) 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_w12, aes(VIGEXW12)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") 

vbl <- ALSA_w12$vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "vig_pa")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(ALSA_w12, aes(x=factor(vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `f_vig_pa` from the study-specific variable `vig_pa` it has to be recoded as follows:

* `VIGEXW12/2`
* `1 into 1`
* `2,3 into 2`
* `,4,5 into 3`
* `>5 into 4`
* `NA into 999`
* `vig_pa == 0 into 0`

**R script:**

```{r harmo w12}

ALSA_ds_w12 <- tibble(id=ALSA_w12$id)
ALSA_ds_w12$f_vig_pa <- car::recode(ceiling(ALSA_w12$VIGEXW12/2), "c(1) = 1; c(2,3) = 2; c(4,5) = 3; 6:hi = 4; NA = 999 ")
ALSA_ds_w12$f_vig_pa[which(ALSA_w12$vig_pa == 0)] <- 0

```

#### Statistical description of the new harmonised variable
```{r descript w12, echo=F}

vbl <- ALSA_ds_w12$f_vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w12, aes(x=factor(f_vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w12, echo=F}

```



### Wave 13

Not found





## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.


```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:5])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[16,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


alsa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"), w6 = c("w6","W6"), w7 = c("w7","W7"), w8 = c("w8","W8"), w9 = c("w9","W9"), w10 = c("w10","W10"), w11 = c("w11","W11"), w12 = c("w12","W12"), w13 = c("w13","W13"))

# Consider only harmonised waves
l.hds <- lapply(alsa.cw, function(wname) if(exists(paste0("ALSA_ds_",wname[1]))){wname = list(get(paste0("ALSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],sapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```








# Quality estimation
[Comments on the quality of the new harmonised variable.]


<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
