---
title: "Ever smoked"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/ever_smokedDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/ever_smokedDS.R')
```




# Data process


## Australia

### Wave 1 

#### Study-specific variable description

| **Name** | `SMOKER` | `REGPIPCG` | `REGSMKPS` |
|-|-|-|-|
| **Label** | `Smoker` | `Have you ever regularly smoked a pipe or cigars?` | `Regular smoking in the past` |
| **Table name** | `ALSA-Wave1` | `ALSA-Wave1` | `ALSA-Wave1` |
| **Categories:**| `1 = Yes` <br/> `2 = No`| `1 = Yes` <br/> `2 = No`| `1 = Yes` <br/> `2 = No`|
| **Missings:**|`9 = Missing` <br/> `NA`| `99 = Never smoked` <br/> `NA` |  `NA` |
| **Description** |  | | |

   

```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'ALSA_w1','ALSA.ALSA-Wave1', variables=list('SMOKER','REGPIPCG','REGSMKPS'), missings = TRUE)
ALSA_w1 <- opal.execute(o,'ALSA_w1')
```

```{r local w1, echo=F}
vbl <- ALSA_w1$SMOKER
vbl_miss <- c(9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = "SMOKER")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ALSA_w1, aes(x=factor(SMOKER))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w1$REGPIPCG
vbl_miss <- c(99)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = "REGPIPCG")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(ALSA_w1, aes(x=factor(REGPIPCG))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- ALSA_w1$REGSMKPS
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = "REGSMKPS")
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w1, aes(x=factor(REGSMKPS))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `ever_smoked` from the study-specific variable it has to be recoded as follows:

* `some 1 into 1`
* `all 2 into 0` 
* `9 into 999` 
* `99 into 0`
* `NA into 999`

**R script:**

```{r harmo w1}
ALSA_ds_w1 <- tibble(id=ALSA_w1$id)
ALSA_ds_w1$ever_smoked <- rep(999,length(ALSA_w1$id))
ALSA_ds_w1$ever_smoked[which(ALSA_w1$SMOKER==2 & ALSA_w1$REGSMKPS == 2 & ALSA_w1$REGPIPCG %in% c(2,99))] <- 0
ALSA_ds_w1$ever_smoked[which(ALSA_w1$SMOKER==1|ALSA_w1$REGSMKPS==1|ALSA_w1$REGPIPCG==1)] <- 1
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vbl <- ALSA_ds_w1$ever_smoked
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w1, aes(x=factor(ever_smoked))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
```

```{r importOPAL w1, echo=F}
ever_smoked <- ALSA_ds_w1 
save(ever_smoked, file = paste0(datafolder,"w1/ever_smoked.RData"))
rm(ever_smoked)
```


### Wave 2

Not found.



### Wave 3

Not found.



### Wave 4

Not found.



### Wave 5

Not found.



### Wave 6

Not found.



### Wave 7

Not found.



### Wave 8

Not found.



### Wave 9

Not found.



### Wave 10

Not found.



### Wave 11

Not found.



### Wave 12

Not found.



### Wave 13

Not found.




# Quality estimation
[Comments on the quality of the new harmonised variable.]



<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
