---
title: "Number of cigarettes"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/n_cigarettesDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/n_cigarettesDS.R')
```



# Data process

## Australia

### Wave 1 

#### Study-specific variable description

| **Name** | `CIGSDAY` |
|-|-|
| **Label** | `Cigarettes per day` |
| **Table name** | `ALSA-Wave1` |
| **Categories:**| `continuous`|
| **Missings:**|`999 = Missing` <br/> `NA`|
| **Description** |  |

   

```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'ALSA_w1','ALSA.ALSA-Wave1', variables=list('CIGSDAY'), missings = TRUE)
ALSA_w1 <- opal.execute(o,'ALSA_w1')
```

```{r local w1, echo=F}
vbl <- ALSA_w1$CIGSDAY
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = label(vbl)) 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_w1, aes(CIGSDAY)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + xlim(0,62)
```

#### Harmonisation algorithm

To compute `n_cigarettes` from the study-specific variable it has to be recoded as follows:

* `CIGSDAY*7`
* `999 into 999`
* `NA into 999`

**R script:**

```{r harmo w1}
ALSA_ds_w1 <- tibble(id=ALSA_w1$id)
ALSA_ds_w1$n_cigarettes <- car::recode(ALSA_w1$CIGSDAY*7, "999*7 = 999;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vbl <- ALSA_ds_w1$n_cigarettes
kable(Continuous_summary(var = vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ALSA_ds_w1, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(0,430) 
```

#### Validation
```{r crosstabulation w1, echo=F}
```






### Wave 2

Not found.




### Wave 3

#### Study-specific variable description

| **Name** | `CIGDAYW3` |
|-|-|
| **Label** | `Cigarettes per day` |
| **Table name** | `ALSA-Wave3` |
| **Categories:**| `continuous`|
| **Missings:**|`NA`|
| **Description** |  |

   

```{r assign w3, echo=F}
opal.assign.table.tibble(o, 'ALSA_w3','ALSA.ALSA-Wave3', variables=list('CIGDAYW3'), missings = TRUE)
ALSA_w3 <- opal.execute(o,'ALSA_w3')
```

```{r local w3, echo=F}
vbl <- ALSA_w3$CIGDAYW3
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = label(vbl)) 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_w3, aes(CIGDAYW3)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + xlim(0,52)
```

#### Harmonisation algorithm

To compute `n_cigarettes` from the study-specific variable it has to be recoded as follows:

* `CIGDAYW3*7`
* `NA into 999`

**R script:**

```{r harmo w3}
ALSA_ds_w3 <- tibble(id=ALSA_w3$id)
ALSA_ds_w3$n_cigarettes <- car::recode(ALSA_w3$CIGDAYW3*7, "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}
vbl <- ALSA_ds_w3$n_cigarettes
kable(Continuous_summary(var = vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ALSA_ds_w3, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(0,360) 
```

#### Validation
```{r crosstabulation w3, echo=F}
```




### Wave 4

Not found.



### Wave 5

Not found.



### Wave 6

#### Study-specific variable description

| **Name** | `CIGDAYW6` |
|-|-|
| **Label** | `Cigarettes per day` |
| **Table name** | `ALSA-Wave6` |
| **Categories:**| `continuous`|
| **Missings:**|`NA`|
| **Description** |  |

   

```{r assign w6, echo=F}
opal.assign.table.tibble(o, 'ALSA_w6','ALSA.ALSA-Wave6', variables=list('CIGDAYW6'), missings = TRUE)
ALSA_w6 <- opal.execute(o,'ALSA_w6')
```

```{r local w6, echo=F}
vbl <- ALSA_w6$CIGDAYW6
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = label(vbl)) 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_w6, aes(CIGDAYW6)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + xlim(-1,42)
```

#### Harmonisation algorithm

To compute `n_cigarettes` from the study-specific variable it has to be recoded as follows:

* `CIGDAYW6*7`
* `NA into 999`

**R script:**

```{r harmo w6}
ALSA_ds_w6 <- tibble(id=ALSA_w6$id)
ALSA_ds_w6$n_cigarettes <- car::recode(ALSA_w6$CIGDAYW6*7, "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w6, echo=F}
vbl <- ALSA_ds_w6$n_cigarettes
kable(Continuous_summary(var = vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ALSA_ds_w6, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(-4,290) 
```

#### Validation
```{r crosstabulation w6, echo=F}
```




### Wave 7

#### Study-specific variable description

| **Name** | `cigdayw7` |
|-|-|
| **Label** | `How many cigarettes do you usually smoke a day?` |
| **Table name** | `ALSA-Wave7` |
| **Categories:**| `continuous`|
| **Missings:**|`0 = Not answered` <br/> `99 = Non-smoker` <br/> `NA`|
| **Description** |  |

   

```{r assign w7, echo=F}
opal.assign.table.tibble(o, 'ALSA_w7','ALSA.ALSA-Wave7', variables=list('cigdayw7'), missings = TRUE)
ALSA_w7 <- opal.execute(o,'ALSA_w7')
```

```{r local w7, echo=F}
vbl <- ALSA_w7$cigdayw7
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = label(vbl)) 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_w7, aes(cigdayw7)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + xlim(-1,32)
```

#### Harmonisation algorithm

To compute `n_cigarettes` from the study-specific variable it has to be recoded as follows:

* `cigdayw7*7`
* `0 into 998`
* `99 into 999`
* `NA into 999`

**R script:**

```{r harmo w7}
ALSA_ds_w7 <- tibble(id=ALSA_w7$id)
ALSA_ds_w7$n_cigarettes <- car::recode(ALSA_w7$cigdayw7*7, "0*7 = 998;99*7 = 999;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w7, echo=F}
vbl <- ALSA_ds_w7$n_cigarettes
kable(Continuous_summary(var = vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ALSA_ds_w7, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(0,220) 
```

#### Validation
```{r crosstabulation w7, echo=F}
```




### Wave 8

Not found.



### Wave 9

#### Study-specific variable description

| **Name** | `CIGDAYW9` |
|-|-|
| **Label** | `how many cigarettes a day` |
| **Table name** | `ALSA-Wave9` |
| **Categories:**| `continuous`|
| **Missings:**|`NA`|
| **Description** |  |

   

```{r assign w9, echo=F}
opal.assign.table.tibble(o, 'ALSA_w9','ALSA.ALSA-Wave9', variables=list('CIGDAYW9'), missings = TRUE)
ALSA_w9 <- opal.execute(o,'ALSA_w9')
```

```{r local w9, echo=F}
vbl <- ALSA_w9$CIGDAYW9
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = label(vbl)) 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_w9, aes(CIGDAYW9)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + xlim(-1,12)
```

#### Harmonisation algorithm

To compute `n_cigarettes` from the study-specific variable it has to be recoded as follows:

* `CIGDAYW9*7`
* `NA into 999`

**R script:**

```{r harmo w9}
ALSA_ds_w9 <- tibble(id=ALSA_w9$id)
ALSA_ds_w9$n_cigarettes <- car::recode(ALSA_w9$CIGDAYW9*7, "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w9, echo=F}
vbl <- ALSA_ds_w9$n_cigarettes
kable(Continuous_summary(var = vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ALSA_ds_w9, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(-4,75) 
```

#### Validation
```{r crosstabulation w9, echo=F}
```





### Wave 10

Not found.




### Wave 11

#### Study-specific variable description

| **Name** | `CIGDAYW11` |
|-|-|
| **Label** | `how many cigarettes a day` |
| **Table name** | `ALSA-Wave11` |
| **Categories:**| `continuous`|
| **Missings:**|`NA`|
| **Description** |  |

   

```{r assign w11, echo=F}
opal.assign.table.tibble(o, 'ALSA_w11','ALSA.ALSA-Wave11', variables=list('CIGDAYW11'), missings = TRUE)
ALSA_w11 <- opal.execute(o,'ALSA_w11')
```

```{r local w11, echo=F}
vbl <- ALSA_w11$CIGDAYW11
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = label(vbl)) 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_w11, aes(CIGDAYW11)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + xlim(0,2)
```

#### Harmonisation algorithm

To compute `n_cigarettes` from the study-specific variable it has to be recoded as follows:

* `CIGDAYW11*7`
* `NA into 999`

**R script:**

```{r harmo w11}
ALSA_ds_w11 <- tibble(id=ALSA_w11$id)
ALSA_ds_w11$n_cigarettes <- car::recode(ALSA_w11$CIGDAYW11*7, "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w11, echo=F}
vbl <- ALSA_ds_w11$n_cigarettes
kable(Continuous_summary(var = vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ALSA_ds_w11, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(0,10) 
```

#### Validation
```{r crosstabulation w11, echo=F}
```





### Wave 12

The variable found, `CIGDAYW12` (`how many cigarettes a day`), only contains missing data, so cannot be harmonized.




### Wave 13

Not found.



```{r final, echo=F}

l.hds <- list(w1 = ALSA_ds_w1, w3 = ALSA_ds_w3, w6 = ALSA_ds_w6, w7 = ALSA_ds_w7, w9 = ALSA_ds_w9, w11 = ALSA_ds_w11)

for(name in names(l.hds)) {
  label(l.hds[[name]][[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
}

```


# Quality estimation
[Comments on the quality of the new harmonised variable.]


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  n_cigarettes <- l.hds[[index]]
  save(n_cigarettes, file = paste0(datafolder,names(l.hds)[index],"/n_cigarettes.RData"))
}

```
<!-- ########################################################## --> 
<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
