---
title: "Number of cigarettes"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/n_cigarettesDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/n_cigarettesDS.R')
```



# Data process

## Australia

### Wave 1 

#### Study-specific variable description

| **Name** | `CIGSDAY` |
|-|-|
| **Label** | `Cigarettes per day` |
| **Table name** | `ALSA-Wave1` |
| **Categories:**| `continuous`|
| **Missings:**|`999 = Missing` <br/> `NA`|
| **Description** |  |

   

```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'ALSA_w1','ALSA.ALSA-Wave1', variables=list('CIGSDAY'), missings = TRUE)
ALSA_w1 <- opal.execute(o,'ALSA_w1')
```

```{r local w1, echo=F}
vbl <- ALSA_w1$CIGSDAY
vbl_miss <- c(999)
kable(Continuous_summary(vbl, missing_values = vbl_miss)[3], caption = "CIGSDAY") 
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(ALSA_w1, aes(CIGSDAY)) + geom_histogram(stat="count", fill="steelblue",data = .%>% filter(!vbl %in% vbl_miss)) + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_cigarettes` from the study-specific variable it has to be recoded as follows:

* `CIGSDAY*7`
* `999 into 999`
* `NA into 999`

**R script:**

```{r harmo w1}
ALSA_ds_w1 <- tibble(id=ALSA_w1$id)
ALSA_ds_w1$n_cigarettes <- car::recode(ALSA_w1$CIGSDAY*7, "999*7 = 999;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vbl <- ALSA_ds_w1$n_cigarettes
vbl_miss <- miss_values_vector
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w1, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue",data = .%>% filter(!vbl %in% vbl_miss)) + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
```






### Wave 2

Not found.




### Wave 3

#### Study-specific variable description

| **Name** | `CIGDAYW3` |
|-|-|
| **Label** | `Cigarettes per day` |
| **Table name** | `ALSA-Wave3` |
| **Categories:**| `continuous`|
| **Missings:**|`NA`|
| **Description** |  |

   

```{r assign w3, echo=F}
opal.assign.table.tibble(o, 'ALSA_w3','ALSA.ALSA-Wave3', variables=list('CIGDAYW3'), missings = TRUE)
ALSA_w3 <- opal.execute(o,'ALSA_w3')
```

```{r local w3, echo=F}
vbl <- ALSA_w3$CIGDAYW3
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "CIGDAYW3") 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_w3, aes(CIGDAYW3)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_cigarettes` from the study-specific variable it has to be recoded as follows:

* `CIGDAYW3*7`
* `NA into 999`

**R script:**

```{r harmo w3}
ALSA_ds_w3 <- tibble(id=ALSA_w3$id)
ALSA_ds_w3$n_cigarettes <- car::recode(ALSA_w3$CIGDAYW3*7, "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}
vbl <- ALSA_ds_w3$n_cigarettes
vbl_miss <- miss_values_vector
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w3, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue",data = .%>% filter(!vbl %in% vbl_miss)) + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=F}
```




### Wave 4

Not found.



### Wave 5

Not found.



### Wave 6

#### Study-specific variable description

| **Name** | `CIGDAYW6` |
|-|-|
| **Label** | `Cigarettes per day` |
| **Table name** | `ALSA-Wave6` |
| **Categories:**| `continuous`|
| **Missings:**|`NA`|
| **Description** |  |

   

```{r assign w6, echo=F}
opal.assign.table.tibble(o, 'ALSA_w6','ALSA.ALSA-Wave6', variables=list('CIGDAYW6'), missings = TRUE)
ALSA_w6 <- opal.execute(o,'ALSA_w6')
```

```{r local w6, echo=F}
vbl <- ALSA_w6$CIGDAYW6
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "CIGDAYW6") 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_w6, aes(CIGDAYW6)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_cigarettes` from the study-specific variable it has to be recoded as follows:

* `CIGDAYW6*7`
* `NA into 999`

**R script:**

```{r harmo w6}
ALSA_ds_w6 <- tibble(id=ALSA_w6$id)
ALSA_ds_w6$n_cigarettes <- car::recode(ALSA_w6$CIGDAYW6*7, "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w6, echo=F}
vbl <- ALSA_ds_w6$n_cigarettes
vbl_miss <- miss_values_vector
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w6, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue",data = .%>% filter(!vbl %in% vbl_miss)) + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w6, echo=F}
```




### Wave 7

#### Study-specific variable description

| **Name** | `cigdayw7` |
|-|-|
| **Label** | `How many cigarettes do you usually smoke a day?` |
| **Table name** | `ALSA-Wave7` |
| **Categories:**| `continuous`|
| **Missings:**|`0 = Not answered` <br/> `99 = Non-smoker` <br/> `NA`|
| **Description** |  |

   

```{r assign w7, echo=F}
opal.assign.table.tibble(o, 'ALSA_w7','ALSA.ALSA-Wave7', variables=list('cigdayw7'), missings = TRUE)
ALSA_w7 <- opal.execute(o,'ALSA_w7')
```

```{r local w7, echo=F}
vbl <- ALSA_w7$cigdayw7
vbl_miss <- c(99,0)
kable(Continuous_summary(vbl, missing_values = vbl_miss)[3], caption = "cigdayw7") 
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(ALSA_w7, aes(cigdayw7)) + geom_histogram(stat="count", fill="steelblue",data = .%>% filter(!vbl %in% vbl_miss)) + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `n_cigarettes` from the study-specific variable it has to be recoded as follows:

* `cigdayw7*7`
* `0 into 995`
* `99 into 0`
* `NA into 999`

**R script:**

```{r harmo w7}
ALSA_ds_w7 <- tibble(id=ALSA_w7$id)
ALSA_ds_w7$n_cigarettes <- car::recode(ALSA_w7$cigdayw7*7, "0 = 995;99*7 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w7, echo=F}
vbl <- ALSA_ds_w7$n_cigarettes
vbl_miss <- miss_values_vector
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w7, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue",data = .%>% filter(!vbl %in% vbl_miss)) + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w7, echo=F}
```




### Wave 8

Not found.



### Wave 9

#### Study-specific variable description

| **Name** | `CIGDAYW9` |
|-|-|
| **Label** | `how many cigarettes a day` |
| **Table name** | `ALSA-Wave9` |
| **Categories:**| `continuous`|
| **Missings:**|`NA`|
| **Description** |  |

   

```{r assign w9, echo=F}
opal.assign.table.tibble(o, 'ALSA_w9','ALSA.ALSA-Wave9', variables=list('CIGDAYW9'), missings = TRUE)
ALSA_w9 <- opal.execute(o,'ALSA_w9')
```

```{r local w9, echo=F}
vbl <- ALSA_w9$CIGDAYW9
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "CIGDAYW9") 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(ALSA_w9, aes(CIGDAYW9)) + geom_histogram(stat="count", fill="steelblue",data = .%>% filter(!vbl %in% vbl_miss)) + xlab(label(vbl)) + ylab("Frequency") +scale_x_continuous(breaks = c(0,2,4,6,8,10))
```

#### Harmonisation algorithm

To compute `n_cigarettes` from the study-specific variable it has to be recoded as follows:

* `CIGDAYW9*7`
* `NA into 999`

**R script:**

```{r harmo w9}
ALSA_ds_w9 <- tibble(id=ALSA_w9$id)
ALSA_ds_w9$n_cigarettes <- car::recode(ALSA_w9$CIGDAYW9*7, "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w9, echo=F}
vbl <- ALSA_ds_w9$n_cigarettes
vbl_miss <- miss_values_vector
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(ALSA_ds_w9, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue",data = .%>% filter(!vbl %in% vbl_miss)) + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w9, echo=F}
```





### Wave 10

Not found.




### Wave 11

The variable found, `CIGDAYW11` (`how many cigarettes a day`), only contains 1 non-missing value, so cannot be harmonized.





### Wave 12

The variable found, `CIGDAYW12` (`how many cigarettes a day`), only contains missing data, so cannot be harmonized.




### Wave 13

Not found.







## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for continuous data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][2])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[2]],missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][2])[1:6]
    # Next, missing/no-missing values
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[2]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


alsa.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"), w6 = c("w6","W6"), w7 = c("w7","W7"), w8 = c("w8","W8"), w9 = c("w9","W9"), w10 = c("w10","W10"), w11 = c("w11","W11"), w12 = c("w12","W12"), w13 = c("w13","W13"))

# Consider only harmonised waves
l.hds <- lapply(alsa.cw, function(wname) if(exists(paste0("ALSA_ds_",wname[1]))){wname = list(get(paste0("ALSA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name="n_cigarettes")
}



```



# Quality estimation

* In wave 6, value 0 of `CIGDAYW6` is probably a missing value.

<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
