---
title: "Alcohol drinking"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/alcoholDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/alcoholDS.R')
```



# Data process



## Australia


### Wave 1


#### Study-specific variable description

| **Name** | `FREQALCH`|
|-|-|
| **Label** | `Frequency alcohol`|
| **Table name**  | `ALSA-Wave1` |
| **Categories** | `1 = Never`<br/>`2 = Monthly or less`<br/>`3 = Two to four times a month`<br/>`4 = Two to three times a week`<br/>`5 = Four or more times a week` |
| **Missings** | `9`<br/>`NA` |
| **Description** |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'ALSA_w1','ALSA.ALSA-Wave1',variables=list('FREQALCH'), missings = T)
ALSA_w1 <- opal.execute(o,'ALSA_w1')

```

```{r local w1, echo=F}

vbl <- ALSA_w1$FREQALCH
kable(Categorical_summary(vbl, missing_values = c(9))[3], caption = 'FREQALCH')
kable(Categorical_summary(vbl, missing_values = c(9))[1], caption = "Category")
ggplot(ALSA_w1, aes(x=factor(FREQALCH))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable it has to be recoded as follows:

* `FREQALCH == 1 into 0`
* `FREQALCH == 2,3,4 or 5 into 1`
* `9, NA into 999`

To compute `freq_oh` from the study-specific variable it has to be recoded as follows:

* `1 into 0`
* `2,3 into 1`
* `4,5 into 2`
* `9, NA into 999`

**R script:**

```{r harmo w1}

ALSA_ds_w1 <- tibble(id=ALSA_w1$id)
ALSA_ds_w1$current_oh <- car::recode(ALSA_w1$FREQALCH, "c(1) = 0; c(2,3,4,5) = 1; c(9,NA) = 999")
ALSA_ds_w1$freq_oh <- car::recode(ALSA_w1$FREQALCH, "1 = 0; c(2,3) = 1; c(4,5) = 2; c(9,NA) = 999")

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- ALSA_ds_w1$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w1, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- ALSA_ds_w1$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w1, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}

```



### Wave 2

Not found.


### Wave 3


#### Study-specific variable description

| **Name** | `FRQALW3`|
|-|-|
| **Label** | `FREQUENCY ALCOHOL`|
| **Table name**  | `ALSA-Wave3` |
| **Categories** |  `1 = Never`<br/>`2 = Monthly or less`<br/>`3 = Two to four times a month`<br/>`4 = Two to three times a week`<br/>`5 = Four or more times a week`  |
| **Missings** | `9`<br/>`NA` |
| **Description** |  |

```{r assign w3, echo=F}

opal.assign.table.tibble(o, 'ALSA_w3','ALSA.ALSA-Wave3',variables=list('FRQALW3'), missings = T)
ALSA_w3 <- opal.execute(o,'ALSA_w3')

```

```{r local w3, echo=F}

vbl <- ALSA_w3$FRQALW3
kable(Categorical_summary(vbl, missing_values = c(9))[3], caption = names(ALSA_w3)[2])
kable(Categorical_summary(vbl, missing_values = c(9))[1], caption = "Category")
ggplot(ALSA_w3, aes(x=factor(FRQALW3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable it has to be recoded as follows:

* `1 into 0`
* `2,3,4 or 5 into 1`
* `9, NA into 999`

To compute `freq_oh` from the study-specific variable it has to be recoded as follows:

* `1 into 0`
* `2,3 into 1`
* `4,5 into 2`
* `9, NA into 999`

**R script:**

```{r harmo w3}

ALSA_ds_w3 <- tibble(id=ALSA_w3$id)
ALSA_ds_w3$current_oh <- car::recode(ALSA_w3$FRQALW3, "c(1) = 0; c(2,3,4,5) = 1; c(9,NA) = 999")
ALSA_ds_w3$freq_oh <- car::recode(ALSA_w3$FRQALW3, "1 = 0; c(2,3) = 1; c(4,5) = 2; c(9,NA) = 999")

```


#### Statistics of the new harmonized variable

```{r descript w3, echo=F}

vbl <- ALSA_ds_w3$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w3, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- ALSA_ds_w3$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w3, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w3, echo=F}

```



### Wave 4

Not found.

### Wave 5

Not found.



### Wave 6


#### Study-specific variable description

| **Name** | `FRQALW6`|
|-|-|
| **Label** | `drink alcohol` |
| **Table name**  | `ALSA-Wave6` |
| **Categories** | `1 = Never`<br/>`2 = Monthly or less`<br/>`3 = 2 to 4 times a month`<br/>`4 = 2 to 3 times a week`<br/>`5 = 4 or more times a week` |
| **Missings** | `0 = no answer`<br/>`NA` |
| **Description** |  |

```{r assign w6, echo=F}

opal.assign.table.tibble(o, 'ALSA_w6','ALSA.ALSA-Wave6',variables=list('FRQALW6'), missings = T)
ALSA_w6 <- opal.execute(o,'ALSA_w6')

```

```{r local w6, echo=F}

vbl <- ALSA_w6$FRQALW6
kable(Categorical_summary(vbl, missing_values = c(0))[3], caption = names(ALSA_w6)[2])
kable(Categorical_summary(vbl, missing_values = c(0))[1], caption = "Category")
ggplot(ALSA_w6, aes(x=factor(FRQALW6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable it has to be recoded as follows:

* `1 into 0`
* `2,3,4 or 5 into 1`
* `NA into 999`
* `0 into 995`

To compute `freq_oh` from the study-specific variable it has to be recoded as follows:

* `1 into 0`
* `2,3 into 1`
* `4,5 into 2`
* `NA into 999`
* `0 into 995`

**R script:**

```{r harmo w6}

ALSA_ds_w6 <- tibble(id=ALSA_w6$id)
ALSA_ds_w6$current_oh <- car::recode(ALSA_w6$FRQALW6, "c(1) = 0; c(2,3,4,5) = 1; NA = 999; 0 = 995")
ALSA_ds_w6$freq_oh <- car::recode(ALSA_w6$FRQALW6, "1 = 0; c(2,3) = 1; c(4,5) = 2; NA = 999; 0 = 995")

```


#### Statistics of the new harmonized variable

```{r descript w6, echo=F}

vbl <- ALSA_ds_w6$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w6, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- ALSA_ds_w6$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w6, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w6, echo=F}

```



### Wave 7


#### Study-specific variable description

| **Name** | `frqalw7`|
|-|-|
| **Label** | `how often do you have a drink containing alcohol`|
| **Table name**  | `ALSA-Wave7` |
| **Categories** | `1 = Never`<br/>`2 = Less than monthly`<br/>`3 = Monthly`<br/>`4 = Weekly`<br/>`5 = Daily or almost daily` |
| **Missings** | `0 = Not Answered`<br/>`NA` |
| **Description** |  |

```{r assign w7, echo=F}

opal.assign.table.tibble(o, 'ALSA_w7','ALSA.ALSA-Wave7',variables=list('frqalw7'), missings = T)
ALSA_w7 <- opal.execute(o,'ALSA_w7')

```

```{r local w7, echo=F}

vbl <- ALSA_w7$frqalw7
kable(Categorical_summary(vbl, missing_values = c(0))[3], caption = names(ALSA_w7)[2])
kable(Categorical_summary(vbl, missing_values = c(0))[1], caption = "Category")
ggplot(ALSA_w7, aes(x=factor(frqalw7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable it has to be recoded as follows:

* `1 into 0`
* `2,3,4 or 5 into 1`
* `NA into 999`
* `0 into 995`

To compute `freq_oh` from the study-specific variable it has to be recoded as follows:

* `1 into 0`
* `2,3 into 1`
* `4,5 into 2`
* `NA into 999`
* `0 into 995`

**R script:**

```{r harmo w7}

ALSA_ds_w7 <- tibble(id=ALSA_w7$id)
ALSA_ds_w7$current_oh <- car::recode(ALSA_w7$frqalw7, "c(1) = 0; c(2,3,4,5) = 1; NA = 999; 0 = 995")
ALSA_ds_w7$freq_oh <- car::recode(ALSA_w7$frqalw7, "1 = 0; c(2,3) = 1; c(4,5) = 2; NA = 999; 0 = 995")

```


#### Statistics of the new harmonized variable

```{r descript w7, echo=F}

vbl <- ALSA_ds_w7$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w7, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- ALSA_ds_w7$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w7, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w7, echo=F}

```




### Wave 8

Not found.



### Wave 9

#### Study-specific variable description

| **Name** | `FRQALW9`|
|-|-|
| **Label** | `how often have alcoholic drink`|
| **Table name**  | `ALSA-Wave9` |
| **Categories** | `1 = Never`<br/>`2 = Monthly or less`<br/>`3 = 2 to 4 times a month`<br/>`4 = 2 to 3 times a week`<br/>`5 = 4 or more times a week` |
| **Missings** | `0 = Not Answered`<br/>`NA` |
| **Description** |  |

```{r assign w9, echo=F}

opal.assign.table.tibble(o, 'ALSA_w9','ALSA.ALSA-Wave9',variables=list('FRQALW9'), missings = T)
ALSA_w9 <- opal.execute(o,'ALSA_w9')

```

```{r local w9, echo=F}

vbl <- ALSA_w9$FRQALW9
kable(Categorical_summary(vbl, missing_values = c(0))[3], caption = names(ALSA_w9)[2])
kable(Categorical_summary(vbl, missing_values = c(0))[1], caption = "Category")
ggplot(ALSA_w9, aes(x=factor(FRQALW9))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable it has to be recoded as follows:

* `1 into 0`
* `2,3,4 or 5 into 1`
* `NA into 999`
* `0 into 995`

To compute `freq_oh` from the study-specific variable it has to be recoded as follows:

* `1 into 0`
* `2,3 into 1`
* `4,5 into 2`
* `NA into 999`
* `0 into 995`

**R script:**

```{r harmo w9}

ALSA_ds_w9 <- tibble(id=ALSA_w9$id)
ALSA_ds_w9$current_oh <- car::recode(ALSA_w9$FRQALW9, "c(1) = 0; c(2,3,4,5) = 1; NA = 999; 0 = 995")
ALSA_ds_w9$freq_oh <- car::recode(ALSA_w9$FRQALW9, "1 = 0; c(2,3) = 1; c(4,5) = 2; NA = 999; 0 = 995")

```


#### Statistics of the new harmonized variable

```{r descript w9, echo=F}

vbl <- ALSA_ds_w9$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w9, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- ALSA_ds_w9$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w9, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w9, echo=F}

```


### Wave 10

Not found.




### Wave 11


#### Study-specific variable description

| **Name** | `FRQALW11`|
|-|-|
| **Label** | `how often have alcoholic drink`|
| **Table name**  | `ALSA-Wave11` |
| **Categories** | `1 = Never`<br/>`2 = Less than monthly`<br/>`3 = Monthly`<br/>`4 = Weekly`<br/>`5 = Daily or almost daily` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign w11, echo=F}

opal.assign.table.tibble(o, 'ALSA_w11','ALSA.ALSA-Wave11',variables=list('FRQALW11'), missings = T)
ALSA_w11 <- opal.execute(o,'ALSA_w11')

```

```{r local w11, echo=F}

vbl <- ALSA_w11$FRQALW11
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w11)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w11, aes(x=factor(FRQALW11))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable it has to be recoded as follows:

* `1 into 0`
* `2,3,4 or 5 into 1`
* `NA into 999`

To compute `freq_oh` from the study-specific variable it has to be recoded as follows:

* `1 into 0`
* `2,3 into 1`
* `4,5 into 2`
* `NA into 999`

**R script:**

```{r harmo w11}

ALSA_ds_w11 <- tibble(id=ALSA_w11$id)
ALSA_ds_w11$current_oh <- car::recode(ALSA_w11$FRQALW11, "c(1) = 0; c(2,3,4,5) = 1; NA = 999")
ALSA_ds_w11$freq_oh <- car::recode(ALSA_w11$FRQALW11, "1 = 0; c(2,3) = 1; c(4,5) = 2; NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript w11, echo=F}

vbl <- ALSA_ds_w11$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w11, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- ALSA_ds_w11$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w11, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w11, echo=F}

```




### Wave 12


#### Study-specific variable description

| **Name** | `FRQALW12`|
|-|-|
| **Label** | `how often have alcoholic drink`|
| **Table name**  | `ALSA-Wave11` |
| **Categories** | `1 = Never`<br/>`2 = Less than monthly`<br/>`3 = Monthly`<br/>`4 = Weekly`<br/>`5 = Daily or almost daily` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign w12, echo=F}

opal.assign.table.tibble(o, 'ALSA_w12','ALSA.ALSA-Wave12',variables=list('FRQALW12'), missings = T)
ALSA_w12 <- opal.execute(o,'ALSA_w12')

```

```{r local w12, echo=F}

vbl <- ALSA_w12$FRQALW12
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ALSA_w12)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ALSA_w12, aes(x=factor(FRQALW12))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable it has to be recoded as follows:

* `1 into 0`
* `3,4 or 5 into 1`
* `NA into 999`

To compute `freq_oh` from the study-specific variable it has to be recoded as follows:

* `1 into 0`
* `2,3 into 1`
* `4,5 into 2`
* `NA into 999`

**R script:**

```{r harmo w12}

ALSA_ds_w12 <- tibble(id=ALSA_w12$id)
ALSA_ds_w12$current_oh <- car::recode(ALSA_w12$FRQALW12, "c(1) = 0; c(2,3,4,5) = 1; NA = 999")
ALSA_ds_w12$freq_oh <- car::recode(ALSA_w12$FRQALW12, "1 = 0; c(2,3) = 1; c(4,5) = 2; NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript w12, echo=F}

vbl <- ALSA_ds_w11$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w11, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- ALSA_ds_w11$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ALSA_ds_w11, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w12, echo=F}

```




### Wave 13

Not found.








```{r final, echo=F}

l.hds <- list(w1 = ALSA_ds_w1, w3 = ALSA_ds_w3, w6 = ALSA_ds_w6, w7 = ALSA_ds_w7, w9 = ALSA_ds_w9, w11 = ALSA_ds_w11, w12 = ALSA_ds_w12)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label_curr # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  label(l.hds[[name]][[3]]) <- label(aux_object[[3]]) <- ds_label_freq # Text value assigned at the DS description, at the top
  l.hds[[name]][[3]] <- labelled(l.hds[[name]][[3]], labels = freq_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  aux_object[[3]] <- car::recode(aux_object[[3]], "miss_values_vector=NA")
  aux_object[[3]] <- labelled(aux_object[[3]], labels = freq_label[1:3])
  m_name <- paste0("ALSA_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

```

## Summary of descriptive statistics of the harmonised variable `current_oh` accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.


```{r summ current}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",names(l.hds))
kable(t.hds)

dbb <- get(paste0("ALSA_m_ds_",names(l.hds)[1]))[,c("id","current_oh")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("ALSA_m_ds_",names(l.hds)[ind]))[,c("id","current_oh")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", names(l.hds))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])

```



## Summary of descriptive statistics of the harmonised variable `freq_oh` accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.


```{r summ freq}

t.hds <- frq(l.hds[[1]][3])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][3])[[1]][,4] 
}
t.hds[14,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",names(l.hds))
kable(t.hds)

dbb <- get(paste0("ALSA_m_ds_",names(l.hds)[1]))[,c("id","freq_oh")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("ALSA_m_ds_",names(l.hds)[ind]))[,c("id","freq_oh")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", names(l.hds))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb[f.dbb[,3]>=0.3,])

```



<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  alcohol <- l.hds[[index]]
  save(alcohol, file = paste0(datafolder,names(l.hds)[index],"/alcohol.RData"))
}

```
<!-- ########################################################## --> 

# Quality estimation

* There are no variables to harmonize `past_oh`.

<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





