---
title: "Month of death"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ############################################ --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ############################################ --> 


# Description of DataSchema variable

The description of harmonised variable is the following:



* Short name: `mdeath`
* Variable label: `month of death`
* Variable description: `Month of death`
* Domain: `Age of death (Life expectancy)`
* Value type: `continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process


## HRS

### Wave 1 

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-HRS-w1`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_hrs1, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w1_mdeath','HRS.HRS-HRS-w1',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_hrs1, echo=F}
HRS_hrs_w1_mdeath <- opal.execute(o,'HRS_hrs_w1_mdeath')
vari <- HRS_hrs_w1_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w1_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs1}
HRS_ds_hrs_w1 <- tibble(id=HRS_hrs_w1_mdeath$id)
HRS_ds_hrs_w1$mdeath <- car::recode(HRS_hrs_w1_mdeath$RADMONTH, "NA=999")
HRS_ds_hrs_w1$mdeath <- labelled(HRS_ds_hrs_w1$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs1, echo=F}
vari <- HRS_ds_hrs_w1$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w1,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_hrs1, echo=F}
BeforeH <- table(HRS_hrs_w1_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_hrs_w1$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_hrs1, echo=F}

#opal.assign.data(o, 'HRS_ds_hrs_w1', HRS_ds_hrs_w1)
#opal.symbol_import(o,'HRS_ds_hrs_w1', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_hrs_w1
save(mdeath, file = "../RData/hrs_w1/mdeath.RData")
rm(mdeath)

HRS_m_ds_hrs_w1 <- HRS_ds_hrs_w1
HRS_m_ds_hrs_w1$mdeath <- car::recode(HRS_m_ds_hrs_w1$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w1', HRS_m_ds_hrs_w1)
#opal.symbol_import(o,'HRS_m_ds_hrs_w1', project='_Athlos_Harm_Dataset')
```








### Wave 2 

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-HRS-w2`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_hrs2, echo=F}
opal.assign.table.tibble(o,'HRS_hrs_w2_mdeath','HRS.HRS-HRS-w2',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_hrs2, echo=F}
HRS_hrs_w2_mdeath <- opal.execute(o,'HRS_hrs_w2_mdeath')
vari <- HRS_hrs_w2_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w2_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs2}
HRS_ds_hrs_w2 <- tibble(id=HRS_hrs_w2_mdeath$id)
HRS_ds_hrs_w2$mdeath <- car::recode(HRS_hrs_w2_mdeath$RADMONTH, "NA=999")
HRS_ds_hrs_w2$mdeath <- labelled(HRS_ds_hrs_w2$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs2, echo=F}
vari <- HRS_ds_hrs_w2$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w2,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_hrs2, echo=F}
BeforeH <- table(HRS_hrs_w2_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_hrs_w2$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_hrs2, echo=F}

#opal.assign.data(o, 'HRS_ds_hrs_w2', HRS_ds_hrs_w2)
#opal.symbol_import(o,'HRS_ds_hrs_w2', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_hrs_w2
save(mdeath, file = "../RData/hrs_w2/mdeath.RData")
rm(mdeath)

HRS_m_ds_hrs_w2 <- HRS_ds_hrs_w2
HRS_m_ds_hrs_w2$mdeath <- car::recode(HRS_m_ds_hrs_w2$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w2', HRS_m_ds_hrs_w2)
#opal.symbol_import(o,'HRS_m_ds_hrs_w2', project='_Athlos_Harm_Dataset')
```






### Wave 3 

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-HRS-w3`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_hrs3, echo=F}
opal.assign.table.tibble(o,'HRS_hrs_w3_mdeath','HRS.HRS-HRS-w3',variables=list('RADMONTH'), missings = TRUE)
```

```{r local_hrs3, echo=F}
HRS_hrs_w3_mdeath <- opal.execute(o,'HRS_hrs_w3_mdeath')
vari <- HRS_hrs_w3_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w3_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs3}
HRS_ds_hrs_w3 <- tibble(id=HRS_hrs_w3_mdeath$id)
HRS_ds_hrs_w3$mdeath <- car::recode(HRS_hrs_w3_mdeath$RADMONTH, "NA=999")
HRS_ds_hrs_w3$mdeath <- labelled(HRS_ds_hrs_w3$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs3, echo=F}
vari <- HRS_ds_hrs_w3$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w3,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_hrs3, echo=F}
BeforeH <- table(HRS_hrs_w3_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_hrs_w3$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_hrs3, echo=F}

#opal.assign.data(o, 'HRS_ds_hrs_w3', HRS_ds_hrs_w3)
#opal.symbol_import(o,'HRS_ds_hrs_w3', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_hrs_w3
save(mdeath, file = "../RData/hrs_w3/mdeath.RData")
rm(mdeath)

HRS_m_ds_hrs_w3 <- HRS_ds_hrs_w3
HRS_m_ds_hrs_w3$mdeath <- car::recode(HRS_m_ds_hrs_w3$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w3', HRS_m_ds_hrs_w3)
#opal.symbol_import(o,'HRS_m_ds_hrs_w3', project='_Athlos_Harm_Dataset')
```








### Wave 4 

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-HRS-w4`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign_hrs4, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w4_mdeath','HRS.HRS-HRS-w4',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_hrs4, echo=F}
HRS_hrs_w4_mdeath <- opal.execute(o,'HRS_hrs_w4_mdeath')
vari <- HRS_hrs_w4_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w4_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs4}
HRS_ds_hrs_w4 <- tibble(id=HRS_hrs_w4_mdeath$id)
HRS_ds_hrs_w4$mdeath <- car::recode(HRS_hrs_w4_mdeath$RADMONTH, "NA=999")
HRS_ds_hrs_w4$mdeath <- labelled(HRS_ds_hrs_w4$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs4, echo=F}
vari <- HRS_ds_hrs_w4$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w4,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_hrs4, echo=F}
BeforeH <- table(HRS_hrs_w4_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_hrs_w4$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_hrs4, echo=F}

#opal.assign.data(o, 'HRS_ds_hrs_w4', HRS_ds_hrs_w4)
#opal.symbol_import(o,'HRS_ds_hrs_w4', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_hrs_w4
save(mdeath, file = "../RData/hrs_w4/mdeath.RData")
rm(mdeath)

HRS_m_ds_hrs_w4 <- HRS_ds_hrs_w4
HRS_m_ds_hrs_w4$mdeath <- car::recode(HRS_m_ds_hrs_w4$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w4', HRS_m_ds_hrs_w4)
#opal.symbol_import(o,'HRS_m_ds_hrs_w4', project='_Athlos_Harm_Dataset')
```






### Wave 5

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-HRS-w5`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_hrs5, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w5_mdeath','HRS.HRS-HRS-w5',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_hrs5, echo=F}
HRS_hrs_w5_mdeath <- opal.execute(o,'HRS_hrs_w5_mdeath')
vari <- HRS_hrs_w5_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w5_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs5}
HRS_ds_hrs_w5 <- tibble(id=HRS_hrs_w5_mdeath$id)
HRS_ds_hrs_w5$mdeath <- car::recode(HRS_hrs_w5_mdeath$RADMONTH, "NA=999")
HRS_ds_hrs_w5$mdeath <- labelled(HRS_ds_hrs_w5$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs5, echo=F}
vari <- HRS_ds_hrs_w5$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w5,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_hrs5, echo=F}
BeforeH <- table(HRS_hrs_w5_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_hrs_w5$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_hrs5, echo=F}

#opal.assign.data(o, 'HRS_ds_hrs_w5', HRS_ds_hrs_w5)
#opal.symbol_import(o,'HRS_ds_hrs_w5', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_hrs_w5
save(mdeath, file = "../RData/hrs_w5/mdeath.RData")
rm(mdeath)

HRS_m_ds_hrs_w5 <- HRS_ds_hrs_w5
HRS_m_ds_hrs_w5$mdeath <- car::recode(HRS_m_ds_hrs_w5$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w5', HRS_m_ds_hrs_w5)
#opal.symbol_import(o,'HRS_m_ds_hrs_w5', project='_Athlos_Harm_Dataset')
```






### Wave 6

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-HRS-w6`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign_hrs6, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w6_mdeath','HRS.HRS-HRS-w6',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_hrs6, echo=F}
HRS_hrs_w6_mdeath <- opal.execute(o,'HRS_hrs_w6_mdeath')
vari <- HRS_hrs_w6_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w6_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs6}
HRS_ds_hrs_w6 <- tibble(id=HRS_hrs_w6_mdeath$id)
HRS_ds_hrs_w6$mdeath <- car::recode(HRS_hrs_w6_mdeath$RADMONTH, "NA=999")
HRS_ds_hrs_w6$mdeath <- labelled(HRS_ds_hrs_w6$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs6, echo=F}
vari <- HRS_ds_hrs_w6$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w6,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_hrs6, echo=F}
BeforeH <- table(HRS_hrs_w6_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_hrs_w6$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_hrs6, echo=F}

#opal.assign.data(o, 'HRS_ds_hrs_w6', HRS_ds_hrs_w6)
#opal.symbol_import(o,'HRS_ds_hrs_w6', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_hrs_w6
save(mdeath, file = "../RData/hrs_w6/mdeath.RData")
rm(mdeath)

HRS_m_ds_hrs_w6 <- HRS_ds_hrs_w6
HRS_m_ds_hrs_w6$mdeath <- car::recode(HRS_m_ds_hrs_w6$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w6', HRS_m_ds_hrs_w6)
#opal.symbol_import(o,'HRS_m_ds_hrs_w6', project='_Athlos_Harm_Dataset')
```








### Wave 7

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-HRS-w7`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_hrs7, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w7_mdeath','HRS.HRS-HRS-w7',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_hrs7, echo=F}
HRS_hrs_w7_mdeath <- opal.execute(o,'HRS_hrs_w7_mdeath')
vari <- HRS_hrs_w7_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w7_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs7}
HRS_ds_hrs_w7 <- tibble(id=HRS_hrs_w7_mdeath$id)
HRS_ds_hrs_w7$mdeath <- car::recode(HRS_hrs_w7_mdeath$RADMONTH, "NA=999")
HRS_ds_hrs_w7$mdeath <- labelled(HRS_ds_hrs_w7$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs7, echo=F}
vari <- HRS_ds_hrs_w7$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w7,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_hrs7, echo=F}
BeforeH <- table(HRS_hrs_w7_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_hrs_w7$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_hrs7, echo=F}

#opal.assign.data(o, 'HRS_ds_hrs_w7', HRS_ds_hrs_w7)
#opal.symbol_import(o,'HRS_ds_hrs_w7', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_hrs_w7
save(mdeath, file = "../RData/hrs_w7/mdeath.RData")
rm(mdeath)

HRS_m_ds_hrs_w7 <- HRS_ds_hrs_w7
HRS_m_ds_hrs_w7$mdeath <- car::recode(HRS_m_ds_hrs_w7$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w7', HRS_m_ds_hrs_w7)
#opal.symbol_import(o,'HRS_m_ds_hrs_w7', project='_Athlos_Harm_Dataset')
```








### Wave 8

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-HRS-w8`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign_hrs8, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w8_mdeath','HRS.HRS-HRS-w8',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_hrs8, echo=F}
HRS_hrs_w8_mdeath <- opal.execute(o,'HRS_hrs_w8_mdeath')
vari <- HRS_hrs_w8_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w8_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs8}
HRS_ds_hrs_w8 <- tibble(id=HRS_hrs_w8_mdeath$id)
HRS_ds_hrs_w8$mdeath <- car::recode(HRS_hrs_w8_mdeath$RADMONTH, "NA=999")
HRS_ds_hrs_w8$mdeath <- labelled(HRS_ds_hrs_w8$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs8, echo=F}
vari <- HRS_ds_hrs_w8$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w8,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_hrs8, echo=F}
BeforeH <- table(HRS_hrs_w8_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_hrs_w8$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_hrs8, echo=F}

#opal.assign.data(o, 'HRS_ds_hrs_w8', HRS_ds_hrs_w8)
#opal.symbol_import(o,'HRS_ds_hrs_w8', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_hrs_w8
save(mdeath, file = "../RData/hrs_w8/mdeath.RData")
rm(mdeath)

HRS_m_ds_hrs_w8 <- HRS_ds_hrs_w8
HRS_m_ds_hrs_w8$mdeath <- car::recode(HRS_m_ds_hrs_w8$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w8', HRS_m_ds_hrs_w8)
#opal.symbol_import(o,'HRS_m_ds_hrs_w8', project='_Athlos_Harm_Dataset')
```








### Wave 9

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-HRS-w9`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign_hrs9, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w9_mdeath','HRS.HRS-HRS-w9',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_hrs9, echo=F}
HRS_hrs_w9_mdeath <- opal.execute(o,'HRS_hrs_w9_mdeath')
vari <- HRS_hrs_w9_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w9_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs9}
HRS_ds_hrs_w9 <- tibble(id=HRS_hrs_w9_mdeath$id)
HRS_ds_hrs_w9$mdeath <- car::recode(HRS_hrs_w9_mdeath$RADMONTH, "NA=999")
HRS_ds_hrs_w9$mdeath <- labelled(HRS_ds_hrs_w9$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs9, echo=F}
vari <- HRS_ds_hrs_w9$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w9,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_hrs9, echo=F}
BeforeH <- table(HRS_hrs_w9_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_hrs_w9$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_hrs9, echo=F}

#opal.assign.data(o, 'HRS_ds_hrs_w9', HRS_ds_hrs_w9)
#opal.symbol_import(o,'HRS_ds_hrs_w9', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_hrs_w9
save(mdeath, file = "../RData/hrs_w9/mdeath.RData")
rm(mdeath)

HRS_m_ds_hrs_w9 <- HRS_ds_hrs_w9
HRS_m_ds_hrs_w9$mdeath <- car::recode(HRS_m_ds_hrs_w9$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w9', HRS_m_ds_hrs_w9)
#opal.symbol_import(o,'HRS_m_ds_hrs_w9', project='_Athlos_Harm_Dataset')
```









### Wave 10

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-HRS-w10`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_hrs10, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w10_mdeath','HRS.HRS-HRS-w10',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_hrs10, echo=F}
HRS_hrs_w10_mdeath <- opal.execute(o,'HRS_hrs_w10_mdeath')
vari <- HRS_hrs_w10_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w10_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs10}
HRS_ds_hrs_w10 <- tibble(id=HRS_hrs_w10_mdeath$id)
HRS_ds_hrs_w10$mdeath <- car::recode(HRS_hrs_w10_mdeath$RADMONTH, "NA=999")
HRS_ds_hrs_w10$mdeath <- labelled(HRS_ds_hrs_w10$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs10, echo=F}
vari <- HRS_ds_hrs_w10$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w10,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_hrs10, echo=F}
BeforeH <- table(HRS_hrs_w10_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_hrs_w10$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_hrs10, echo=F}

#opal.assign.data(o, 'HRS_ds_hrs_w10', HRS_ds_hrs_w10)
#opal.symbol_import(o,'HRS_ds_hrs_w10', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_hrs_w10
save(mdeath, file = "../RData/hrs_w10/mdeath.RData")
rm(mdeath)

HRS_m_ds_hrs_w10 <- HRS_ds_hrs_w10
HRS_m_ds_hrs_w10$mdeath <- car::recode(HRS_m_ds_hrs_w10$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w10', HRS_m_ds_hrs_w10)
#opal.symbol_import(o,'HRS_m_ds_hrs_w10', project='_Athlos_Harm_Dataset')
```








### Wave 11

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-HRS-w11`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign_hrs11, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w11_mdeath','HRS.HRS-HRS-w11',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_hrs11, echo=F}
HRS_hrs_w11_mdeath <- opal.execute(o,'HRS_hrs_w11_mdeath')
vari <- HRS_hrs_w11_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w11_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs11}
HRS_ds_hrs_w11 <- tibble(id=HRS_hrs_w11_mdeath$id)
HRS_ds_hrs_w11$mdeath <- car::recode(HRS_hrs_w11_mdeath$RADMONTH, "NA=999")
HRS_ds_hrs_w11$mdeath <- labelled(HRS_ds_hrs_w11$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs11, echo=F}
vari <- HRS_ds_hrs_w11$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w11,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_hrs11, echo=F}
BeforeH <- table(HRS_hrs_w11_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_hrs_w11$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_hrs11, echo=F}

#opal.assign.data(o, 'HRS_ds_hrs_w11', HRS_ds_hrs_w11)
#opal.symbol_import(o,'HRS_ds_hrs_w11', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_hrs_w11
save(mdeath, file = "../RData/hrs_w11/mdeath.RData")
rm(mdeath)

HRS_m_ds_hrs_w11 <- HRS_ds_hrs_w11
HRS_m_ds_hrs_w11$mdeath <- car::recode(HRS_m_ds_hrs_w11$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w11', HRS_m_ds_hrs_w11)
#opal.symbol_import(o,'HRS_m_ds_hrs_w11', project='_Athlos_Harm_Dataset')
```




## AHEAD


### Wave 2 

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-AHEAD-w2`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_ahead2, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w2_mdeath','HRS.HRS-AHEAD-w2',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_ahead2, echo=F}
HRS_ahead_w2_mdeath <- opal.execute(o,'HRS_ahead_w2_mdeath')
vari <- HRS_ahead_w2_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w2_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ahead2}
HRS_ds_ahead_w2 <- tibble(id=HRS_ahead_w2_mdeath$id)
HRS_ds_ahead_w2$mdeath <- car::recode(HRS_ahead_w2_mdeath$RADMONTH, "NA=999")
HRS_ds_ahead_w2$mdeath <- labelled(HRS_ds_ahead_w2$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead2, echo=F}
vari <- HRS_ds_ahead_w2$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w2,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_ahead2, echo=F}
BeforeH <- table(HRS_ahead_w2_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_ahead_w2$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ahead2, echo=F}

#opal.assign.data(o, 'HRS_ds_ahead_w2', HRS_ds_ahead_w2)
#opal.symbol_import(o,'HRS_ds_ahead_w2', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_ahead_w2
save(mdeath, file = "../RData/ahead_w2/mdeath.RData")
rm(mdeath)

HRS_m_ds_ahead_w2 <- HRS_ds_ahead_w2
HRS_m_ds_ahead_w2$mdeath <- car::recode(HRS_m_ds_ahead_w2$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w2', HRS_m_ds_ahead_w2)
#opal.symbol_import(o,'HRS_m_ds_ahead_w2', project='_Athlos_Harm_Dataset')
```





### Wave 3 

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-AHEAD-w3`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_ahead3, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w3_mdeath','HRS.HRS-AHEAD-w3',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_ahead3, echo=F}
HRS_ahead_w3_mdeath <- opal.execute(o,'HRS_ahead_w3_mdeath')
vari <- HRS_ahead_w3_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w3_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ahead3}
HRS_ds_ahead_w3 <- tibble(id=HRS_ahead_w3_mdeath$id)
HRS_ds_ahead_w3$mdeath <- car::recode(HRS_ahead_w3_mdeath$RADMONTH, "NA=999")
HRS_ds_ahead_w3$mdeath <- labelled(HRS_ds_ahead_w3$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead3, echo=F}
vari <- HRS_ds_ahead_w3$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w3,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_ahead3, echo=F}
BeforeH <- table(HRS_ahead_w3_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_ahead_w3$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ahead3, echo=F}

#opal.assign.data(o, 'HRS_ds_ahead_w3', HRS_ds_ahead_w3)
#opal.symbol_import(o,'HRS_ds_ahead_w3', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_ahead_w3
save(mdeath, file = "../RData/ahead_w3/mdeath.RData")
rm(mdeath)

HRS_m_ds_ahead_w3 <- HRS_ds_ahead_w3
HRS_m_ds_ahead_w3$mdeath <- car::recode(HRS_m_ds_ahead_w3$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w3', HRS_m_ds_ahead_w3)
#opal.symbol_import(o,'HRS_m_ds_ahead_w3', project='_Athlos_Harm_Dataset')
```








### Wave 4 

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-AHEAD-w4`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_ahead4, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w4_mdeath','HRS.HRS-AHEAD-w4',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_ahead4, echo=F}
HRS_ahead_w4_mdeath <- opal.execute(o,'HRS_ahead_w4_mdeath')
vari <- HRS_ahead_w4_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w4_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ahead4}
HRS_ds_ahead_w4 <- tibble(id=HRS_ahead_w4_mdeath$id)
HRS_ds_ahead_w4$mdeath <- car::recode(HRS_ahead_w4_mdeath$RADMONTH, "NA=999")
HRS_ds_ahead_w4$mdeath <- labelled(HRS_ds_ahead_w4$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead4, echo=F}
vari <- HRS_ds_ahead_w4$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w4,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_ahead4, echo=F}
BeforeH <- table(HRS_ahead_w4_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_ahead_w4$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ahead4, echo=F}

#opal.assign.data(o, 'HRS_ds_ahead_w4', HRS_ds_ahead_w4)
#opal.symbol_import(o,'HRS_ds_ahead_w4', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_ahead_w4
save(mdeath, file = "../RData/ahead_w4/mdeath.RData")
rm(mdeath)

HRS_m_ds_ahead_w4 <- HRS_ds_ahead_w4
HRS_m_ds_ahead_w4$mdeath <- car::recode(HRS_m_ds_ahead_w4$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w4', HRS_m_ds_ahead_w4)
#opal.symbol_import(o,'HRS_m_ds_ahead_w4', project='_Athlos_Harm_Dataset')
```







### Wave 5 

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-AHEAD-w5`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_ahead5, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w5_mdeath','HRS.HRS-AHEAD-w5',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_ahead5, echo=F}
HRS_ahead_w5_mdeath <- opal.execute(o,'HRS_ahead_w5_mdeath')
vari <- HRS_ahead_w5_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w5_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ahead5}
HRS_ds_ahead_w5 <- tibble(id=HRS_ahead_w5_mdeath$id)
HRS_ds_ahead_w5$mdeath <- car::recode(HRS_ahead_w5_mdeath$RADMONTH, "NA=999")
HRS_ds_ahead_w5$mdeath <- labelled(HRS_ds_ahead_w5$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead5, echo=F}
vari <- HRS_ds_ahead_w5$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w5,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_ahead5, echo=F}
BeforeH <- table(HRS_ahead_w5_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_ahead_w5$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ahead5, echo=F}

#opal.assign.data(o, 'HRS_ds_ahead_w5', HRS_ds_ahead_w5)
#opal.symbol_import(o,'HRS_ds_ahead_w5', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_ahead_w5
save(mdeath, file = "../RData/ahead_w5/mdeath.RData")
rm(mdeath)

HRS_m_ds_ahead_w5 <- HRS_ds_ahead_w5
HRS_m_ds_ahead_w5$mdeath <- car::recode(HRS_m_ds_ahead_w5$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w5', HRS_m_ds_ahead_w5)
#opal.symbol_import(o,'HRS_m_ds_ahead_w5', project='_Athlos_Harm_Dataset')
```








### Wave 6 

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-AHEAD-w6`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_ahead6, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w6_mdeath','HRS.HRS-AHEAD-w6',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_ahead6, echo=F}
HRS_ahead_w6_mdeath <- opal.execute(o,'HRS_ahead_w6_mdeath')
vari <- HRS_ahead_w6_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w6_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ahead6}
HRS_ds_ahead_w6 <- tibble(id=HRS_ahead_w6_mdeath$id)
HRS_ds_ahead_w6$mdeath <- car::recode(HRS_ahead_w6_mdeath$RADMONTH, "NA=999")
HRS_ds_ahead_w6$mdeath <- labelled(HRS_ds_ahead_w6$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead6, echo=F}
vari <- HRS_ds_ahead_w6$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w6,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_ahead6, echo=F}
BeforeH <- table(HRS_ahead_w6_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_ahead_w6$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ahead6, echo=F}

#opal.assign.data(o, 'HRS_ds_ahead_w6', HRS_ds_ahead_w6)
#opal.symbol_import(o,'HRS_ds_ahead_w6', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_ahead_w6
save(mdeath, file = "../RData/ahead_w6/mdeath.RData")
rm(mdeath)

HRS_m_ds_ahead_w6 <- HRS_ds_ahead_w6
HRS_m_ds_ahead_w6$mdeath <- car::recode(HRS_m_ds_ahead_w6$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w6', HRS_m_ds_ahead_w6)
#opal.symbol_import(o,'HRS_m_ds_ahead_w6', project='_Athlos_Harm_Dataset')
```







### Wave 7 

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-AHEAD-w7`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign_ahead7, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w7_mdeath','HRS.HRS-AHEAD-w7',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_ahead7, echo=F}
HRS_ahead_w7_mdeath <- opal.execute(o,'HRS_ahead_w7_mdeath')
vari <- HRS_ahead_w7_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w7_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ahead7}
HRS_ds_ahead_w7 <- tibble(id=HRS_ahead_w7_mdeath$id)
HRS_ds_ahead_w7$mdeath <- car::recode(HRS_ahead_w7_mdeath$RADMONTH, "NA=999")
HRS_ds_ahead_w7$mdeath <- labelled(HRS_ds_ahead_w7$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead7, echo=F}
vari <- HRS_ds_ahead_w7$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w7,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_ahead7, echo=F}
BeforeH <- table(HRS_ahead_w7_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_ahead_w7$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ahead7, echo=F}

#opal.assign.data(o, 'HRS_ds_ahead_w7', HRS_ds_ahead_w7)
#opal.symbol_import(o,'HRS_ds_ahead_w7', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_ahead_w7
save(mdeath, file = "../RData/ahead_w7/mdeath.RData")
rm(mdeath)

HRS_m_ds_ahead_w7 <- HRS_ds_ahead_w7
HRS_m_ds_ahead_w7$mdeath <- car::recode(HRS_m_ds_ahead_w7$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w7', HRS_m_ds_ahead_w7)
#opal.symbol_import(o,'HRS_m_ds_ahead_w7', project='_Athlos_Harm_Dataset')
```








### Wave 8 

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-AHEAD-w8`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_ahead8, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w8_mdeath','HRS.HRS-AHEAD-w8',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_ahead8, echo=F}
HRS_ahead_w8_mdeath <- opal.execute(o,'HRS_ahead_w8_mdeath')
vari <- HRS_ahead_w8_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w8_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ahead8}
HRS_ds_ahead_w8 <- tibble(id=HRS_ahead_w8_mdeath$id)
HRS_ds_ahead_w8$mdeath <- car::recode(HRS_ahead_w8_mdeath$RADMONTH, "NA=999")
HRS_ds_ahead_w8$mdeath <- labelled(HRS_ds_ahead_w8$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead8, echo=F}
vari <- HRS_ds_ahead_w8$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w8,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_ahead8, echo=F}
BeforeH <- table(HRS_ahead_w8_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_ahead_w8$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ahead8, echo=F}

#opal.assign.data(o, 'HRS_ds_ahead_w8', HRS_ds_ahead_w8)
#opal.symbol_import(o,'HRS_ds_ahead_w8', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_ahead_w8
save(mdeath, file = "../RData/ahead_w8/mdeath.RData")
rm(mdeath)

HRS_m_ds_ahead_w8 <- HRS_ds_ahead_w8
HRS_m_ds_ahead_w8$mdeath <- car::recode(HRS_m_ds_ahead_w8$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w8', HRS_m_ds_ahead_w8)
#opal.symbol_import(o,'HRS_m_ds_ahead_w8', project='_Athlos_Harm_Dataset')
```








### Wave 9 

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-AHEAD-w9`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign_ahead9, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w9_mdeath','HRS.HRS-AHEAD-w9',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_ahead9, echo=F}
HRS_ahead_w9_mdeath <- opal.execute(o,'HRS_ahead_w9_mdeath')
vari <- HRS_ahead_w9_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w9_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ahead9}
HRS_ds_ahead_w9 <- tibble(id=HRS_ahead_w9_mdeath$id)
HRS_ds_ahead_w9$mdeath <- car::recode(HRS_ahead_w9_mdeath$RADMONTH, "NA=999")
HRS_ds_ahead_w9$mdeath <- labelled(HRS_ds_ahead_w9$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead9, echo=F}
vari <- HRS_ds_ahead_w9$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w9,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_ahead9, echo=F}
BeforeH <- table(HRS_ahead_w9_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_ahead_w9$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ahead9, echo=F}

#opal.assign.data(o, 'HRS_ds_ahead_w9', HRS_ds_ahead_w9)
#opal.symbol_import(o,'HRS_ds_ahead_w9', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_ahead_w9
save(mdeath, file = "../RData/ahead_w9/mdeath.RData")
rm(mdeath)

HRS_m_ds_ahead_w9 <- HRS_ds_ahead_w9
HRS_m_ds_ahead_w9$mdeath <- car::recode(HRS_m_ds_ahead_w9$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w9', HRS_m_ds_ahead_w9)
#opal.symbol_import(o,'HRS_m_ds_ahead_w9', project='_Athlos_Harm_Dataset')
```








### Wave 10 

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-AHEAD-w10`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign_ahead10, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w10_mdeath','HRS.HRS-AHEAD-w10',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_ahead10, echo=F}
HRS_ahead_w10_mdeath <- opal.execute(o,'HRS_ahead_w10_mdeath')
vari <- HRS_ahead_w10_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w10_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ahead10}
HRS_ds_ahead_w10 <- tibble(id=HRS_ahead_w10_mdeath$id)
HRS_ds_ahead_w10$mdeath <- car::recode(HRS_ahead_w10_mdeath$RADMONTH, "NA=999")
HRS_ds_ahead_w10$mdeath <- labelled(HRS_ds_ahead_w10$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead10, echo=F}
vari <- HRS_ds_ahead_w10$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w10,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_ahead10, echo=F}
BeforeH <- table(HRS_ahead_w10_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_ahead_w10$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ahead10, echo=F}

#opal.assign.data(o, 'HRS_ds_ahead_w10', HRS_ds_ahead_w10)
#opal.symbol_import(o,'HRS_ds_ahead_w10', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_ahead_w10
save(mdeath, file = "../RData/ahead_w10/mdeath.RData")
rm(mdeath)

HRS_m_ds_ahead_w10 <- HRS_ds_ahead_w10
HRS_m_ds_ahead_w10$mdeath <- car::recode(HRS_m_ds_ahead_w10$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w10', HRS_m_ds_ahead_w10)
#opal.symbol_import(o,'HRS_m_ds_ahead_w10', project='_Athlos_Harm_Dataset')
```








### Wave 11 

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-AHEAD-w11`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign_ahead11, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w11_mdeath','HRS.HRS-AHEAD-w11',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_ahead11, echo=F}
HRS_ahead_w11_mdeath <- opal.execute(o,'HRS_ahead_w11_mdeath')
vari <- HRS_ahead_w11_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w11_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`


**R script:**

```{r harmo_ahead11}
HRS_ds_ahead_w11 <- tibble(id=HRS_ahead_w11_mdeath$id)
HRS_ds_ahead_w11$mdeath <- car::recode(HRS_ahead_w11_mdeath$RADMONTH, "NA=999")
HRS_ds_ahead_w11$mdeath <- labelled(HRS_ds_ahead_w11$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead11, echo=F}
vari <- HRS_ds_ahead_w11$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w11,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_ahead11, echo=F}
BeforeH <- table(HRS_ahead_w11_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_ahead_w11$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ahead11, echo=F}

#opal.assign.data(o, 'HRS_ds_ahead_w11', HRS_ds_ahead_w11)
#opal.symbol_import(o,'HRS_ds_ahead_w11', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_ahead_w11
save(mdeath, file = "../RData/ahead_w11/mdeath.RData")
rm(mdeath)

HRS_m_ds_ahead_w11 <- HRS_ds_ahead_w11
HRS_m_ds_ahead_w11$mdeath <- car::recode(HRS_m_ds_ahead_w11$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w11', HRS_m_ds_ahead_w11)
#opal.symbol_import(o,'HRS_m_ds_ahead_w11', project='_Athlos_Harm_Dataset')
```



## CODA

### Wave 4 

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-CODA-w4`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_coda4, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w4_mdeath','HRS.HRS-CODA-w4',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_coda4, echo=F}
HRS_coda_w4_mdeath <- opal.execute(o,'HRS_coda_w4_mdeath')
vari <- HRS_coda_w4_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w4_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_coda4}
HRS_ds_coda_w4 <- tibble(id=HRS_coda_w4_mdeath$id)
HRS_ds_coda_w4$mdeath <- car::recode(HRS_coda_w4_mdeath$RADMONTH, "NA=999")
HRS_ds_coda_w4$mdeath <- labelled(HRS_ds_coda_w4$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda4, echo=F}
vari <- HRS_ds_coda_w4$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w4,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_coda4, echo=F}
BeforeH <- table(HRS_coda_w4_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_coda_w4$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_coda4, echo=F}

#opal.assign.data(o, 'HRS_ds_coda_w4', HRS_ds_coda_w4)
#opal.symbol_import(o,'HRS_ds_coda_w4', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_coda_w4
save(mdeath, file = "../RData/coda_w4/mdeath.RData")
rm(mdeath)

HRS_m_ds_coda_w4 <- HRS_ds_coda_w4
HRS_m_ds_coda_w4$mdeath <- car::recode(HRS_m_ds_coda_w4$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_coda_w4', HRS_m_ds_coda_w4)
#opal.symbol_import(o,'HRS_m_ds_coda_w4', project='_Athlos_Harm_Dataset')
```








### Wave 5 

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-CODA-w5`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign_coda5, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w5_mdeath','HRS.HRS-CODA-w5',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_coda5, echo=F}
HRS_coda_w5_mdeath <- opal.execute(o,'HRS_coda_w5_mdeath')
vari <- HRS_coda_w5_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w5_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_coda5}
HRS_ds_coda_w5 <- tibble(id=HRS_coda_w5_mdeath$id)
HRS_ds_coda_w5$mdeath <- car::recode(HRS_coda_w5_mdeath$RADMONTH, "NA=999")
HRS_ds_coda_w5$mdeath <- labelled(HRS_ds_coda_w5$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda5, echo=F}
vari <- HRS_ds_coda_w5$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w5,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_coda5, echo=F}
BeforeH <- table(HRS_coda_w5_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_coda_w5$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_coda5, echo=F}

#opal.assign.data(o, 'HRS_ds_coda_w5', HRS_ds_coda_w5)
#opal.symbol_import(o,'HRS_ds_coda_w5', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_coda_w5
save(mdeath, file = "../RData/coda_w5/mdeath.RData")
rm(mdeath)

HRS_m_ds_coda_w5 <- HRS_ds_coda_w5
HRS_m_ds_coda_w5$mdeath <- car::recode(HRS_m_ds_coda_w5$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_coda_w5', HRS_m_ds_coda_w5)
#opal.symbol_import(o,'HRS_m_ds_coda_w5', project='_Athlos_Harm_Dataset')
```










### Wave 6 

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-CODA-w6`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_coda6, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w6_mdeath','HRS.HRS-CODA-w6',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_coda6, echo=F}
HRS_coda_w6_mdeath <- opal.execute(o,'HRS_coda_w6_mdeath')
vari <- HRS_coda_w6_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w6_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_coda6}
HRS_ds_coda_w6 <- tibble(id=HRS_coda_w6_mdeath$id)
HRS_ds_coda_w6$mdeath <- car::recode(HRS_coda_w6_mdeath$RADMONTH, "NA=999")
HRS_ds_coda_w6$mdeath <- labelled(HRS_ds_coda_w6$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda6, echo=F}
vari <- HRS_ds_coda_w6$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w6,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_coda6, echo=F}
BeforeH <- table(HRS_coda_w6_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_coda_w6$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_coda6, echo=F}

#opal.assign.data(o, 'HRS_ds_coda_w6', HRS_ds_coda_w6)
#opal.symbol_import(o,'HRS_ds_coda_w6', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_coda_w6
save(mdeath, file = "../RData/coda_w6/mdeath.RData")
rm(mdeath)

HRS_m_ds_coda_w6 <- HRS_ds_coda_w6
HRS_m_ds_coda_w6$mdeath <- car::recode(HRS_m_ds_coda_w6$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_coda_w6', HRS_m_ds_coda_w6)
#opal.symbol_import(o,'HRS_m_ds_coda_w6', project='_Athlos_Harm_Dataset')
```







### Wave 7 

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-CODA-w7`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_coda7, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w7_mdeath','HRS.HRS-CODA-w7',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_coda7, echo=F}
HRS_coda_w7_mdeath <- opal.execute(o,'HRS_coda_w7_mdeath')
vari <- HRS_coda_w7_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w7_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_coda7}
HRS_ds_coda_w7 <- tibble(id=HRS_coda_w7_mdeath$id)
HRS_ds_coda_w7$mdeath <- car::recode(HRS_coda_w7_mdeath$RADMONTH, "NA=999")
HRS_ds_coda_w7$mdeath <- labelled(HRS_ds_coda_w7$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```



#### Statistics of the new harmonised variable
```{r descript_coda7, echo=F}
vari <- HRS_ds_coda_w7$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w7,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_coda7, echo=F}
BeforeH <- table(HRS_coda_w7_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_coda_w7$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_coda7, echo=F}

#opal.assign.data(o, 'HRS_ds_coda_w7', HRS_ds_coda_w7)
#opal.symbol_import(o,'HRS_ds_coda_w7', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_coda_w7
save(mdeath, file = "../RData/coda_w7/mdeath.RData")
rm(mdeath)

HRS_m_ds_coda_w7 <- HRS_ds_coda_w7
HRS_m_ds_coda_w7$mdeath <- car::recode(HRS_m_ds_coda_w7$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_coda_w7', HRS_m_ds_coda_w7)
#opal.symbol_import(o,'HRS_m_ds_coda_w7', project='_Athlos_Harm_Dataset')
```







### Wave 8 

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-CODA-w8`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_coda8, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w8_mdeath','HRS.HRS-CODA-w8',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_coda8, echo=F}
HRS_coda_w8_mdeath <- opal.execute(o,'HRS_coda_w8_mdeath')
vari <- HRS_coda_w8_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w8_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_coda8}
HRS_ds_coda_w8 <- tibble(id=HRS_coda_w8_mdeath$id)
HRS_ds_coda_w8$mdeath <- car::recode(HRS_coda_w8_mdeath$RADMONTH, "NA=999")
HRS_ds_coda_w8$mdeath <- labelled(HRS_ds_coda_w8$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda8, echo=F}
vari <- HRS_ds_coda_w8$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w8,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_coda8, echo=F}
BeforeH <- table(HRS_coda_w8_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_coda_w8$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_coda8, echo=F}

#opal.assign.data(o, 'HRS_ds_coda_w8', HRS_ds_coda_w8)
#opal.symbol_import(o,'HRS_ds_coda_w8', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_coda_w8
save(mdeath, file = "../RData/coda_w8/mdeath.RData")
rm(mdeath)

HRS_m_ds_coda_w8 <- HRS_ds_coda_w8
HRS_m_ds_coda_w8$mdeath <- car::recode(HRS_m_ds_coda_w8$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_coda_w8', HRS_m_ds_coda_w8)
#opal.symbol_import(o,'HRS_m_ds_coda_w8', project='_Athlos_Harm_Dataset')
```







### Wave 9 

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-CODA-w9`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_coda9, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w9_mdeath','HRS.HRS-CODA-w9',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_coda9, echo=F}
HRS_coda_w9_mdeath <- opal.execute(o,'HRS_coda_w9_mdeath')
vari <- HRS_coda_w9_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w9_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_coda9}
HRS_ds_coda_w9 <- tibble(id=HRS_coda_w9_mdeath$id)
HRS_ds_coda_w9$mdeath <- car::recode(HRS_coda_w9_mdeath$RADMONTH, "NA=999")
HRS_ds_coda_w9$mdeath <- labelled(HRS_ds_coda_w9$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda9, echo=F}
vari <- HRS_ds_coda_w9$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w9,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_coda9, echo=F}
BeforeH <- table(HRS_coda_w9_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_coda_w9$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_coda9, echo=F}

#opal.assign.data(o, 'HRS_ds_coda_w9', HRS_ds_coda_w9)
#opal.symbol_import(o,'HRS_ds_coda_w9', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_coda_w9
save(mdeath, file = "../RData/coda_w9/mdeath.RData")
rm(mdeath)

HRS_m_ds_coda_w9 <- HRS_ds_coda_w9
HRS_m_ds_coda_w9$mdeath <- car::recode(HRS_m_ds_coda_w9$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_coda_w9', HRS_m_ds_coda_w9)
#opal.symbol_import(o,'HRS_m_ds_coda_w9', project='_Athlos_Harm_Dataset')
```








### Wave 10 

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-CODA-w10`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign_coda10, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w10_mdeath','HRS.HRS-CODA-w10',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_coda10, echo=F}
HRS_coda_w10_mdeath <- opal.execute(o,'HRS_coda_w10_mdeath')
vari <- HRS_coda_w10_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w10_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_coda10}
HRS_ds_coda_w10 <- tibble(id=HRS_coda_w10_mdeath$id)
HRS_ds_coda_w10$mdeath <- car::recode(HRS_coda_w10_mdeath$RADMONTH, "NA=999")
HRS_ds_coda_w10$mdeath <- labelled(HRS_ds_coda_w10$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda10, echo=F}
vari <- HRS_ds_coda_w10$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w10,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_coda10, echo=F}
BeforeH <- table(HRS_coda_w10_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_coda_w10$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_coda10, echo=F}

#opal.assign.data(o, 'HRS_ds_coda_w10', HRS_ds_coda_w10)
#opal.symbol_import(o,'HRS_ds_coda_w10', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_coda_w10
save(mdeath, file = "../RData/coda_w10/mdeath.RData")
rm(mdeath)

HRS_m_ds_coda_w10 <- HRS_ds_coda_w10
HRS_m_ds_coda_w10$mdeath <- car::recode(HRS_m_ds_coda_w10$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_coda_w10', HRS_m_ds_coda_w10)
#opal.symbol_import(o,'HRS_m_ds_coda_w10', project='_Athlos_Harm_Dataset')
```








### Wave 11 

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-CODA-w11`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_coda11, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w11_mdeath','HRS.HRS-CODA-w11',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_coda11, echo=F}
HRS_coda_w11_mdeath <- opal.execute(o,'HRS_coda_w11_mdeath')
vari <- HRS_coda_w11_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w11_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_coda11}
HRS_ds_coda_w11 <- tibble(id=HRS_coda_w11_mdeath$id)
HRS_ds_coda_w11$mdeath <- car::recode(HRS_coda_w11_mdeath$RADMONTH, "NA=999")
HRS_ds_coda_w11$mdeath <- labelled(HRS_ds_coda_w11$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda11, echo=F}
vari <- HRS_ds_coda_w11$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w11,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_coda11, echo=F}
BeforeH <- table(HRS_coda_w11_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_coda_w11$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_coda11, echo=F}

#opal.assign.data(o, 'HRS_ds_coda_w11', HRS_ds_coda_w11)
#opal.symbol_import(o,'HRS_ds_coda_w11', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_coda_w11
save(mdeath, file = "../RData/coda_w11/mdeath.RData")
rm(mdeath)

HRS_m_ds_coda_w11 <- HRS_ds_coda_w11
HRS_m_ds_coda_w11$mdeath <- car::recode(HRS_m_ds_coda_w11$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_coda_w11', HRS_m_ds_coda_w11)
#opal.symbol_import(o,'HRS_m_ds_coda_w11', project='_Athlos_Harm_Dataset')
```




## WB



### Wave 4  

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-WB-w4`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_wb4, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w4_mdeath','HRS.HRS-WB-w4',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_wb4, echo=F}
HRS_wb_w4_mdeath <- opal.execute(o,'HRS_wb_w4_mdeath')
vari <- HRS_wb_w4_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w4_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_wb4}
HRS_ds_wb_w4 <- tibble(id=HRS_wb_w4_mdeath$id)
HRS_ds_wb_w4$mdeath <- car::recode(HRS_wb_w4_mdeath$RADMONTH, "NA=999")
HRS_ds_wb_w4$mdeath <- labelled(HRS_ds_wb_w4$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb4, echo=F}
vari <- HRS_ds_wb_w4$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w4,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_wb4, echo=F}
BeforeH <- table(HRS_wb_w4_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_wb_w4$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_wb4, echo=F}

#opal.assign.data(o, 'HRS_ds_wb_w4', HRS_ds_wb_w4)
#opal.symbol_import(o,'HRS_ds_wb_w4', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_wb_w4
save(mdeath, file = "../RData/wb_w4/mdeath.RData")
rm(mdeath)

HRS_m_ds_wb_w4 <- HRS_ds_wb_w4
HRS_m_ds_wb_w4$mdeath <- car::recode(HRS_m_ds_wb_w4$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w4', HRS_m_ds_wb_w4)
#opal.symbol_import(o,'HRS_m_ds_wb_w4', project='_Athlos_Harm_Dataset')
```









### Wave 5  

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-WB-w5`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_wb5, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w5_mdeath','HRS.HRS-WB-w5',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_wb5, echo=F}
HRS_wb_w5_mdeath <- opal.execute(o,'HRS_wb_w5_mdeath')
vari <- HRS_wb_w5_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w5_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_wb5}
HRS_ds_wb_w5 <- tibble(id=HRS_wb_w5_mdeath$id)
HRS_ds_wb_w5$mdeath <- car::recode(HRS_wb_w5_mdeath$RADMONTH, "NA=999")
HRS_ds_wb_w5$mdeath <- labelled(HRS_ds_wb_w5$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb5, echo=F}
vari <- HRS_ds_wb_w5$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w5,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_wb5, echo=F}
BeforeH <- table(HRS_wb_w5_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_wb_w5$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_wb5, echo=F}

#opal.assign.data(o, 'HRS_ds_wb_w5', HRS_ds_wb_w5)
#opal.symbol_import(o,'HRS_ds_wb_w5', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_wb_w5
save(mdeath, file = "../RData/wb_w5/mdeath.RData")
rm(mdeath)

HRS_m_ds_wb_w5 <- HRS_ds_wb_w5
HRS_m_ds_wb_w5$mdeath <- car::recode(HRS_m_ds_wb_w5$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w5', HRS_m_ds_wb_w5)
#opal.symbol_import(o,'HRS_m_ds_wb_w5', project='_Athlos_Harm_Dataset')
```








### Wave 6  

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-WB-w6`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_wb6, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w6_mdeath','HRS.HRS-WB-w6',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_wb6, echo=F}
HRS_wb_w6_mdeath <- opal.execute(o,'HRS_wb_w6_mdeath')
vari <- HRS_wb_w6_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w6_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_wb6}
HRS_ds_wb_w6 <- tibble(id=HRS_wb_w6_mdeath$id)
HRS_ds_wb_w6$mdeath <- car::recode(HRS_wb_w6_mdeath$RADMONTH, "NA=999")
HRS_ds_wb_w6$mdeath <- labelled(HRS_ds_wb_w6$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb6, echo=F}
vari <- HRS_ds_wb_w6$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w6,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_wb6, echo=F}
BeforeH <- table(HRS_wb_w6_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_wb_w6$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_wb6, echo=F}

#opal.assign.data(o, 'HRS_ds_wb_w6', HRS_ds_wb_w6)
#opal.symbol_import(o,'HRS_ds_wb_w6', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_wb_w6
save(mdeath, file = "../RData/wb_w6/mdeath.RData")
rm(mdeath)

HRS_m_ds_wb_w6 <- HRS_ds_wb_w6
HRS_m_ds_wb_w6$mdeath <- car::recode(HRS_m_ds_wb_w6$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w6', HRS_m_ds_wb_w6)
#opal.symbol_import(o,'HRS_m_ds_wb_w6', project='_Athlos_Harm_Dataset')
```







### Wave 7  

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-WB-w7`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign_wb7, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w7_mdeath','HRS.HRS-WB-w7',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_wb7, echo=F}
HRS_wb_w7_mdeath <- opal.execute(o,'HRS_wb_w7_mdeath')
vari <- HRS_wb_w7_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w7_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_wb7}
HRS_ds_wb_w7 <- tibble(id=HRS_wb_w7_mdeath$id)
HRS_ds_wb_w7$mdeath <- car::recode(HRS_wb_w7_mdeath$RADMONTH, "NA=999")
HRS_ds_wb_w7$mdeath <- labelled(HRS_ds_wb_w7$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb7, echo=F}
vari <- HRS_ds_wb_w7$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w7,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_wb7, echo=F}
BeforeH <- table(HRS_wb_w7_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_wb_w7$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_wb7, echo=F}

#opal.assign.data(o, 'HRS_ds_wb_w7', HRS_ds_wb_w7)
#opal.symbol_import(o,'HRS_ds_wb_w7', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_wb_w7
save(mdeath, file = "../RData/wb_w7/mdeath.RData")
rm(mdeath)

HRS_m_ds_wb_w7 <- HRS_ds_wb_w7
HRS_m_ds_wb_w7$mdeath <- car::recode(HRS_m_ds_wb_w7$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w7', HRS_m_ds_wb_w7)
#opal.symbol_import(o,'HRS_m_ds_wb_w7', project='_Athlos_Harm_Dataset')
```








### Wave 8  

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-WB-w8`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_wb8, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w8_mdeath','HRS.HRS-WB-w8',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_wb8, echo=F}
HRS_wb_w8_mdeath <- opal.execute(o,'HRS_wb_w8_mdeath')
vari <- HRS_wb_w8_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w8_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_wb8}
HRS_ds_wb_w8 <- tibble(id=HRS_wb_w8_mdeath$id)
HRS_ds_wb_w8$mdeath <- car::recode(HRS_wb_w8_mdeath$RADMONTH, "NA=999")
HRS_ds_wb_w8$mdeath <- labelled(HRS_ds_wb_w8$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb8, echo=F}
vari <- HRS_ds_wb_w8$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w8,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_wb8, echo=F}
BeforeH <- table(HRS_wb_w8_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_wb_w8$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_wb8, echo=F}

#opal.assign.data(o, 'HRS_ds_wb_w8', HRS_ds_wb_w8)
#opal.symbol_import(o,'HRS_ds_wb_w8', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_wb_w8
save(mdeath, file = "../RData/wb_w8/mdeath.RData")
rm(mdeath)

HRS_m_ds_wb_w8 <- HRS_ds_wb_w8
HRS_m_ds_wb_w8$mdeath <- car::recode(HRS_m_ds_wb_w8$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w8', HRS_m_ds_wb_w8)
#opal.symbol_import(o,'HRS_m_ds_wb_w8', project='_Athlos_Harm_Dataset')
```








### Wave 9  

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-WB-w9`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_wb9, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w9_mdeath','HRS.HRS-WB-w9',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_wb9, echo=F}
HRS_wb_w9_mdeath <- opal.execute(o,'HRS_wb_w9_mdeath')
vari <- HRS_wb_w9_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w9_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_wb9}
HRS_ds_wb_w9 <- tibble(id=HRS_wb_w9_mdeath$id)
HRS_ds_wb_w9$mdeath <- car::recode(HRS_wb_w9_mdeath$RADMONTH, "NA=999")
HRS_ds_wb_w9$mdeath <- labelled(HRS_ds_wb_w9$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb9, echo=F}
vari <- HRS_ds_wb_w9$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w9,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_wb9, echo=F}
BeforeH <- table(HRS_wb_w9_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_wb_w9$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_wb9, echo=F}

#opal.assign.data(o, 'HRS_ds_wb_w9', HRS_ds_wb_w9)
#opal.symbol_import(o,'HRS_ds_wb_w9', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_wb_w9
save(mdeath, file = "../RData/wb_w9/mdeath.RData")
rm(mdeath)

HRS_m_ds_wb_w9 <- HRS_ds_wb_w9
HRS_m_ds_wb_w9$mdeath <- car::recode(HRS_m_ds_wb_w9$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w9', HRS_m_ds_wb_w9)
#opal.symbol_import(o,'HRS_m_ds_wb_w9', project='_Athlos_Harm_Dataset')
```







### Wave 10  

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-WB-w10`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_wb10, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w10_mdeath','HRS.HRS-WB-w10',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_wb10, echo=F}
HRS_wb_w10_mdeath <- opal.execute(o,'HRS_wb_w10_mdeath')
vari <- HRS_wb_w10_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w10_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_wb10}
HRS_ds_wb_w10 <- tibble(id=HRS_wb_w10_mdeath$id)
HRS_ds_wb_w10$mdeath <- car::recode(HRS_wb_w10_mdeath$RADMONTH, "NA=999")
HRS_ds_wb_w10$mdeath <- labelled(HRS_ds_wb_w10$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb10, echo=F}
vari <- HRS_ds_wb_w10$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w10,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_wb10, echo=F}
BeforeH <- table(HRS_wb_w10_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_wb_w10$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_wb10, echo=F}

#opal.assign.data(o, 'HRS_ds_wb_w10', HRS_ds_wb_w10)
#opal.symbol_import(o,'HRS_ds_wb_w10', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_wb_w10
save(mdeath, file = "../RData/wb_w10/mdeath.RData")
rm(mdeath)

HRS_m_ds_wb_w10 <- HRS_ds_wb_w10
HRS_m_ds_wb_w10$mdeath <- car::recode(HRS_m_ds_wb_w10$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w10', HRS_m_ds_wb_w10)
#opal.symbol_import(o,'HRS_m_ds_wb_w10', project='_Athlos_Harm_Dataset')
```







### Wave 11  

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-WB-w11`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_wb11, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w11_mdeath','HRS.HRS-WB-w11',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_wb11, echo=F}
HRS_wb_w11_mdeath <- opal.execute(o,'HRS_wb_w11_mdeath')
vari <- HRS_wb_w11_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w11_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_wb11}
HRS_ds_wb_w11 <- tibble(id=HRS_wb_w11_mdeath$id)
HRS_ds_wb_w11$mdeath <- car::recode(HRS_wb_w11_mdeath$RADMONTH, "NA=999")
HRS_ds_wb_w11$mdeath <- labelled(HRS_ds_wb_w11$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb11, echo=F}
vari <- HRS_ds_wb_w11$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w11,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_wb11, echo=F}
BeforeH <- table(HRS_wb_w11_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_wb_w11$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_wb11, echo=F}

#opal.assign.data(o, 'HRS_ds_wb_w11', HRS_ds_wb_w11)
#opal.symbol_import(o,'HRS_ds_wb_w11', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_wb_w11
save(mdeath, file = "../RData/wb_w11/mdeath.RData")
rm(mdeath)

HRS_m_ds_wb_w11 <- HRS_ds_wb_w11
HRS_m_ds_wb_w11$mdeath <- car::recode(HRS_m_ds_wb_w11$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w11', HRS_m_ds_wb_w11)
#opal.symbol_import(o,'HRS_m_ds_wb_w11', project='_Athlos_Harm_Dataset')
```





## EBB

### Wave 7  

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-EBB-w7`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign_ebb7, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w7_mdeath','HRS.HRS-EBB-w7',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_ebb7, echo=F}
HRS_ebb_w7_mdeath <- opal.execute(o,'HRS_ebb_w7_mdeath')
vari <- HRS_ebb_w7_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ebb_w7_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ebb7}
HRS_ds_ebb_w7 <- tibble(id=HRS_ebb_w7_mdeath$id)
HRS_ds_ebb_w7$mdeath <- car::recode(HRS_ebb_w7_mdeath$RADMONTH, "NA=999")
HRS_ds_ebb_w7$mdeath <- labelled(HRS_ds_ebb_w7$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ebb7, echo=F}
vari <- HRS_ds_ebb_w7$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w7,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_ebb7, echo=F}
BeforeH <- table(HRS_ebb_w7_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_ebb_w7$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ebb7, echo=F}

#opal.assign.data(o, 'HRS_ds_ebb_w7', HRS_ds_ebb_w7)
#opal.symbol_import(o,'HRS_ds_ebb_w7', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_ebb_w7
save(mdeath, file = "../RData/ebb_w7/mdeath.RData")
rm(mdeath)

HRS_m_ds_ebb_w7 <- HRS_ds_ebb_w7
HRS_m_ds_ebb_w7$mdeath <- car::recode(HRS_m_ds_ebb_w7$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ebb_w7', HRS_m_ds_ebb_w7)
#opal.symbol_import(o,'HRS_m_ds_ebb_w7', project='_Athlos_Harm_Dataset')
```







### Wave 8  

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-EBB-w8`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_ebb8, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w8_mdeath','HRS.HRS-EBB-w8',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_ebb8, echo=F}
HRS_ebb_w8_mdeath <- opal.execute(o,'HRS_ebb_w8_mdeath')
vari <- HRS_ebb_w8_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ebb_w8_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ebb8}
HRS_ds_ebb_w8 <- tibble(id=HRS_ebb_w8_mdeath$id)
HRS_ds_ebb_w8$mdeath <- car::recode(HRS_ebb_w8_mdeath$RADMONTH, "NA=999")
HRS_ds_ebb_w8$mdeath <- labelled(HRS_ds_ebb_w8$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ebb8, echo=F}
vari <- HRS_ds_ebb_w8$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w8,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_ebb8, echo=F}
BeforeH <- table(HRS_ebb_w8_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_ebb_w8$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ebb8, echo=F}

#opal.assign.data(o, 'HRS_ds_ebb_w8', HRS_ds_ebb_w8)
#opal.symbol_import(o,'HRS_ds_ebb_w8', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_ebb_w8
save(mdeath, file = "../RData/ebb_w8/mdeath.RData")
rm(mdeath)

HRS_m_ds_ebb_w8 <- HRS_ds_ebb_w8
HRS_m_ds_ebb_w8$mdeath <- car::recode(HRS_m_ds_ebb_w8$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ebb_w8', HRS_m_ds_ebb_w8)
#opal.symbol_import(o,'HRS_m_ds_ebb_w8', project='_Athlos_Harm_Dataset')
```







### Wave 9  

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-EBB-w9`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_ebb9, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w9_mdeath','HRS.HRS-EBB-w9',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_ebb9, echo=F}
HRS_ebb_w9_mdeath <- opal.execute(o,'HRS_ebb_w9_mdeath')
vari <- HRS_ebb_w9_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ebb_w9_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ebb9}
HRS_ds_ebb_w9 <- tibble(id=HRS_ebb_w9_mdeath$id)
HRS_ds_ebb_w9$mdeath <- car::recode(HRS_ebb_w9_mdeath$RADMONTH, "NA=999")
HRS_ds_ebb_w9$mdeath <- labelled(HRS_ds_ebb_w9$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ebb9, echo=F}
vari <- HRS_ds_ebb_w9$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w9,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_ebb9, echo=F}
BeforeH <- table(HRS_ebb_w9_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_ebb_w9$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ebb9, echo=F}

#opal.assign.data(o, 'HRS_ds_ebb_w9', HRS_ds_ebb_w9)
#opal.symbol_import(o,'HRS_ds_ebb_w9', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_ebb_w9
save(mdeath, file = "../RData/ebb_w9/mdeath.RData")
rm(mdeath)

HRS_m_ds_ebb_w9 <- HRS_ds_ebb_w9
HRS_m_ds_ebb_w9$mdeath <- car::recode(HRS_m_ds_ebb_w9$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ebb_w9', HRS_m_ds_ebb_w9)
#opal.symbol_import(o,'HRS_m_ds_ebb_w9', project='_Athlos_Harm_Dataset')
```







### Wave 10  

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-EBB-w10`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_ebb10, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w10_mdeath','HRS.HRS-EBB-w10',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_ebb10, echo=F}
HRS_ebb_w10_mdeath <- opal.execute(o,'HRS_ebb_w10_mdeath')
vari <- HRS_ebb_w10_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ebb_w10_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ebb10}
HRS_ds_ebb_w10 <- tibble(id=HRS_ebb_w10_mdeath$id)
HRS_ds_ebb_w10$mdeath <- car::recode(HRS_ebb_w10_mdeath$RADMONTH, "NA=999")
HRS_ds_ebb_w10$mdeath <- labelled(HRS_ds_ebb_w10$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ebb10, echo=F}
vari <- HRS_ds_ebb_w10$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w10,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_ebb10, echo=F}
BeforeH <- table(HRS_ebb_w10_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_ebb_w10$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ebb10, echo=F}

#opal.assign.data(o, 'HRS_ds_ebb_w10', HRS_ds_ebb_w10)
#opal.symbol_import(o,'HRS_ds_ebb_w10', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_ebb_w10
save(mdeath, file = "../RData/ebb_w10/mdeath.RData")
rm(mdeath)

HRS_m_ds_ebb_w10 <- HRS_ds_ebb_w10
HRS_m_ds_ebb_w10$mdeath <- car::recode(HRS_m_ds_ebb_w10$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ebb_w10', HRS_m_ds_ebb_w10)
#opal.symbol_import(o,'HRS_m_ds_ebb_w10', project='_Athlos_Harm_Dataset')
```







### Wave 11  

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-EBB-w11`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_ebb11, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w11_mdeath','HRS.HRS-EBB-w11',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_ebb11, echo=F}
HRS_ebb_w11_mdeath <- opal.execute(o,'HRS_ebb_w11_mdeath')
vari <- HRS_ebb_w11_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ebb_w11_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ebb11}
HRS_ds_ebb_w11 <- tibble(id=HRS_ebb_w11_mdeath$id)
HRS_ds_ebb_w11$mdeath <- car::recode(HRS_ebb_w11_mdeath$RADMONTH, "NA=999")
HRS_ds_ebb_w11$mdeath <- labelled(HRS_ds_ebb_w11$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ebb11, echo=F}
vari <- HRS_ds_ebb_w11$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w11,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_ebb11, echo=F}
BeforeH <- table(HRS_ebb_w11_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_ebb_w11$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ebb11, echo=F}

#opal.assign.data(o, 'HRS_ds_ebb_w11', HRS_ds_ebb_w11)
#opal.symbol_import(o,'HRS_ds_ebb_w11', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_ebb_w11
save(mdeath, file = "../RData/ebb_w11/mdeath.RData")
rm(mdeath)

HRS_m_ds_ebb_w11 <- HRS_ds_ebb_w11
HRS_m_ds_ebb_w11$mdeath <- car::recode(HRS_m_ds_ebb_w11$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ebb_w11', HRS_m_ds_ebb_w11)
#opal.symbol_import(o,'HRS_m_ds_ebb_w11', project='_Athlos_Harm_Dataset')
```




## MBB

### Wave 10  

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-MBB-w10`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_mbb10, echo=F}
opal.assign.table.tibble(o, 'HRS_mbb_w10_mdeath','HRS.HRS-MBB-w10',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_mbb10, echo=F}
HRS_mbb_w10_mdeath <- opal.execute(o,'HRS_mbb_w10_mdeath')
vari <- HRS_mbb_w10_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_mbb_w10_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_mbb10}
HRS_ds_mbb_w10 <- tibble(id=HRS_mbb_w10_mdeath$id)
HRS_ds_mbb_w10$mdeath <- car::recode(HRS_mbb_w10_mdeath$RADMONTH, "NA=999")
HRS_ds_mbb_w10$mdeath <- labelled(HRS_ds_mbb_w10$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_mbb10, echo=F}
vari <- HRS_ds_mbb_w10$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_mbb_w10,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_mbb10, echo=F}
BeforeH <- table(HRS_mbb_w10_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_mbb_w10$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_mbb10, echo=F}

#opal.assign.data(o, 'HRS_ds_mbb_w10', HRS_ds_mbb_w10)
#opal.symbol_import(o,'HRS_ds_mbb_w10', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_mbb_w10
save(mdeath, file = "../RData/mbb_w10/mdeath.RData")
rm(mdeath)

HRS_m_ds_mbb_w10 <- HRS_ds_mbb_w10
HRS_m_ds_mbb_w10$mdeath <- car::recode(HRS_m_ds_mbb_w10$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_mbb_w10', HRS_m_ds_mbb_w10)
#opal.symbol_import(o,'HRS_m_ds_mbb_w10', project='_Athlos_Harm_Dataset')
```







### Wave 11  

#### Study-specific variable description



| **Name** | `RADMONTH`|
|-|-|
| **Label** | `R death month` |
| **Table name** |`HRS-MBB-w11`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_mbb11, echo=F}
opal.assign.table.tibble(o, 'HRS_mbb_w11_mdeath','HRS.HRS-MBB-w11',
                         variables=list('RADMONTH'), missings = TRUE)
```

```{r local_mbb11, echo=F}
HRS_mbb_w11_mdeath <- opal.execute(o,'HRS_mbb_w11_mdeath')
vari <- HRS_mbb_w11_mdeath$RADMONTH
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "RADMONTH")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_mbb_w11_mdeath, aes(factor(RADMONTH))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_mbb11}
HRS_ds_mbb_w11 <- tibble(id=HRS_mbb_w11_mdeath$id)
HRS_ds_mbb_w11$mdeath <- car::recode(HRS_mbb_w11_mdeath$RADMONTH, "NA=999")
HRS_ds_mbb_w11$mdeath <- labelled(HRS_ds_mbb_w11$mdeath, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_mbb11, echo=F}
vari <- HRS_ds_mbb_w11$mdeath
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mdeath")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_mbb_w11,  aes(factor(mdeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Month of death") + ylab("Frequency")  
```

#### Validation
```{r crosstabulation_mbb11, echo=F}
BeforeH <- table(HRS_mbb_w11_mdeath$RADMONTH, useNA = "ifany")
AfterH <- table(HRS_ds_mbb_w11$mdeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_mbb11, echo=F}

#opal.assign.data(o, 'HRS_ds_mbb_w11', HRS_ds_mbb_w11)
#opal.symbol_import(o,'HRS_ds_mbb_w11', project='_Athlos_Harm_Dataset')
mdeath <- HRS_ds_mbb_w11
save(mdeath, file = "../RData/mbb_w11/mdeath.RData")
rm(mdeath)

HRS_m_ds_mbb_w11 <- HRS_ds_mbb_w11
HRS_m_ds_mbb_w11$mdeath <- car::recode(HRS_m_ds_mbb_w11$mdeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_mbb_w11', HRS_m_ds_mbb_w11)
#opal.symbol_import(o,'HRS_m_ds_mbb_w11', project='_Athlos_Harm_Dataset')
```

# Quality estimation

No comments

[Comments on the quality of the new harmonised variable.]

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
