---
title: "Year of Death"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/ydeathDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/ydeathDS.R')
```


# Data process

## HRS

### Wave 1 

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-HRS-w1`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign_hrs1, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w1_ydeath','HRS.HRS-HRS-w1',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_hrs1, echo=F}
HRS_hrs_w1_ydeath <- opal.execute(o,'HRS_hrs_w1_ydeath')
vari <- HRS_hrs_w1_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_hrs_w1_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs1}
HRS_ds_hrs_w1 <- tibble(id=HRS_hrs_w1_ydeath$id)
HRS_ds_hrs_w1$ydeath <- car::recode(HRS_hrs_w1_ydeath$RADYEAR, "NA=999")
HRS_ds_hrs_w1$ydeath <- labelled(HRS_ds_hrs_w1$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs1, echo=F}
vari <- HRS_ds_hrs_w1$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w1 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_hrs1, echo=F}
BeforeH <- table(HRS_hrs_w1_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_hrs_w1$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_hrs1, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_hrs_w1', HRS_ds_hrs_w1)
#opal.symbol_import(o,'HRS_ds_hrs_w1', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_hrs_w1
save(ydeath, file = "../RData/hrs_w1/ydeath.RData")
rm(ydeath)

HRS_m_ds_hrs_w1 <- HRS_ds_hrs_w1
HRS_m_ds_hrs_w1$ydeath <- car::recode(HRS_m_ds_hrs_w1$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w1', HRS_m_ds_hrs_w1)
#opal.symbol_import(o,'HRS_m_ds_hrs_w1', project='_Athlos_Harm_Dataset')
```








### Wave 2 

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-HRS-w2`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |




```{r assign_hrs2, echo=F}
opal.assign.table.tibble(o,'HRS_hrs_w2_ydeath','HRS.HRS-HRS-w2',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_hrs2, echo=F}
HRS_hrs_w2_ydeath <- opal.execute(o,'HRS_hrs_w2_ydeath')
vari <- HRS_hrs_w2_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_hrs_w2_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs2}
HRS_ds_hrs_w2 <- tibble(id=HRS_hrs_w2_ydeath$id)
HRS_ds_hrs_w2$ydeath <- car::recode(HRS_hrs_w2_ydeath$RADYEAR, "NA=999")
HRS_ds_hrs_w2$ydeath <- labelled(HRS_ds_hrs_w2$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs2, echo=F}
vari <- HRS_ds_hrs_w2$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w2 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_hrs2, echo=F}
BeforeH <- table(HRS_hrs_w2_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_hrs_w2$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_hrs2, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_hrs_w2', HRS_ds_hrs_w2)
#opal.symbol_import(o,'HRS_ds_hrs_w2', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_hrs_w2
save(ydeath, file = "../RData/hrs_w2/ydeath.RData")
rm(ydeath)

HRS_m_ds_hrs_w2 <- HRS_ds_hrs_w2
HRS_m_ds_hrs_w2$ydeath <- car::recode(HRS_m_ds_hrs_w2$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w2', HRS_m_ds_hrs_w2)
#opal.symbol_import(o,'HRS_m_ds_hrs_w2', project='_Athlos_Harm_Dataset')
```






### Wave 3 

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-HRS-w3`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign_hrs3, echo=F}
opal.assign.table.tibble(o,'HRS_hrs_w3_ydeath','HRS.HRS-HRS-w3',variables=list('RADYEAR'), missings = TRUE)
```

```{r local_hrs3, echo=F}
HRS_hrs_w3_ydeath <- opal.execute(o,'HRS_hrs_w3_ydeath')
vari <- HRS_hrs_w3_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_hrs_w3_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs3}
HRS_ds_hrs_w3 <- tibble(id=HRS_hrs_w3_ydeath$id)
HRS_ds_hrs_w3$ydeath <- car::recode(HRS_hrs_w3_ydeath$RADYEAR, "NA=999")
HRS_ds_hrs_w3$ydeath <- labelled(HRS_ds_hrs_w3$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs3, echo=F}
vari <- HRS_ds_hrs_w3$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w3 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_hrs3, echo=F}
BeforeH <- table(HRS_hrs_w3_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_hrs_w3$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_hrs3, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_hrs_w3', HRS_ds_hrs_w3)
#opal.symbol_import(o,'HRS_ds_hrs_w3', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_hrs_w3
save(ydeath, file = "../RData/hrs_w3/ydeath.RData")
rm(ydeath)

HRS_m_ds_hrs_w3 <- HRS_ds_hrs_w3
HRS_m_ds_hrs_w3$ydeath <- car::recode(HRS_m_ds_hrs_w3$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w3', HRS_m_ds_hrs_w3)
#opal.symbol_import(o,'HRS_m_ds_hrs_w3', project='_Athlos_Harm_Dataset')
```








### Wave 4 

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-HRS-w4`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_hrs4, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w4_ydeath','HRS.HRS-HRS-w4',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_hrs4, echo=F}
HRS_hrs_w4_ydeath <- opal.execute(o,'HRS_hrs_w4_ydeath')
vari <- HRS_hrs_w4_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_hrs_w4_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs4}
HRS_ds_hrs_w4 <- tibble(id=HRS_hrs_w4_ydeath$id)
HRS_ds_hrs_w4$ydeath <- car::recode(HRS_hrs_w4_ydeath$RADYEAR, "NA=999")
HRS_ds_hrs_w4$ydeath <- labelled(HRS_ds_hrs_w4$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs4, echo=F}
vari <- HRS_ds_hrs_w4$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w4 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_hrs4, echo=F}
BeforeH <- table(HRS_hrs_w4_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_hrs_w4$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_hrs4, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_hrs_w4', HRS_ds_hrs_w4)
#opal.symbol_import(o,'HRS_ds_hrs_w4', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_hrs_w4
save(ydeath, file = "../RData/hrs_w4/ydeath.RData")
rm(ydeath)

HRS_m_ds_hrs_w4 <- HRS_ds_hrs_w4
HRS_m_ds_hrs_w4$ydeath <- car::recode(HRS_m_ds_hrs_w4$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w4', HRS_m_ds_hrs_w4)
#opal.symbol_import(o,'HRS_m_ds_hrs_w4', project='_Athlos_Harm_Dataset')
```






### Wave 5

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-HRS-w5`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_hrs5, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w5_ydeath','HRS.HRS-HRS-w5',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_hrs5, echo=F}
HRS_hrs_w5_ydeath <- opal.execute(o,'HRS_hrs_w5_ydeath')
vari <- HRS_hrs_w5_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_hrs_w5_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs5}
HRS_ds_hrs_w5 <- tibble(id=HRS_hrs_w5_ydeath$id)
HRS_ds_hrs_w5$ydeath <- car::recode(HRS_hrs_w5_ydeath$RADYEAR, "NA=999")
HRS_ds_hrs_w5$ydeath <- labelled(HRS_ds_hrs_w5$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs5, echo=F}
vari <- HRS_ds_hrs_w5$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w5 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_hrs5, echo=F}
BeforeH <- table(HRS_hrs_w5_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_hrs_w5$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_hrs5, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_hrs_w5', HRS_ds_hrs_w5)
#opal.symbol_import(o,'HRS_ds_hrs_w5', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_hrs_w5
save(ydeath, file = "../RData/hrs_w5/ydeath.RData")
rm(ydeath)

HRS_m_ds_hrs_w5 <- HRS_ds_hrs_w5
HRS_m_ds_hrs_w5$ydeath <- car::recode(HRS_m_ds_hrs_w5$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w5', HRS_m_ds_hrs_w5)
#opal.symbol_import(o,'HRS_m_ds_hrs_w5', project='_Athlos_Harm_Dataset')
```






### Wave 6

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-HRS-w6`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign_hrs6, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w6_ydeath','HRS.HRS-HRS-w6',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_hrs6, echo=F}
HRS_hrs_w6_ydeath <- opal.execute(o,'HRS_hrs_w6_ydeath')
vari <- HRS_hrs_w6_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_hrs_w6_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs6}
HRS_ds_hrs_w6 <- tibble(id=HRS_hrs_w6_ydeath$id)
HRS_ds_hrs_w6$ydeath <- car::recode(HRS_hrs_w6_ydeath$RADYEAR, "NA=999")
HRS_ds_hrs_w6$ydeath <- labelled(HRS_ds_hrs_w6$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs6, echo=F}
vari <- HRS_ds_hrs_w6$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w6 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_hrs6, echo=F}
BeforeH <- table(HRS_hrs_w6_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_hrs_w6$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_hrs6, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_hrs_w6', HRS_ds_hrs_w6)
#opal.symbol_import(o,'HRS_ds_hrs_w6', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_hrs_w6
save(ydeath, file = "../RData/hrs_w6/ydeath.RData")
rm(ydeath)

HRS_m_ds_hrs_w6 <- HRS_ds_hrs_w6
HRS_m_ds_hrs_w6$ydeath <- car::recode(HRS_m_ds_hrs_w6$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w6', HRS_m_ds_hrs_w6)
#opal.symbol_import(o,'HRS_m_ds_hrs_w6', project='_Athlos_Harm_Dataset')
```








### Wave 7

##### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-HRS-w7`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign_hrs7, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w7_ydeath','HRS.HRS-HRS-w7',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_hrs7, echo=F}
HRS_hrs_w7_ydeath <- opal.execute(o,'HRS_hrs_w7_ydeath')
vari <- HRS_hrs_w7_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_hrs_w7_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs7}
HRS_ds_hrs_w7 <- tibble(id=HRS_hrs_w7_ydeath$id)
HRS_ds_hrs_w7$ydeath <- car::recode(HRS_hrs_w7_ydeath$RADYEAR, "NA=999")
HRS_ds_hrs_w7$ydeath <- labelled(HRS_ds_hrs_w7$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs7, echo=F}
vari <- HRS_ds_hrs_w7$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w7 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_hrs7, echo=F}
BeforeH <- table(HRS_hrs_w7_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_hrs_w7$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_hrs7, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_hrs_w7', HRS_ds_hrs_w7)
#opal.symbol_import(o,'HRS_ds_hrs_w7', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_hrs_w7
save(ydeath, file = "../RData/hrs_w7/ydeath.RData")
rm(ydeath)

HRS_m_ds_hrs_w7 <- HRS_ds_hrs_w7
HRS_m_ds_hrs_w7$ydeath <- car::recode(HRS_m_ds_hrs_w7$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w7', HRS_m_ds_hrs_w7)
#opal.symbol_import(o,'HRS_m_ds_hrs_w7', project='_Athlos_Harm_Dataset')
```








### Wave 8

##### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-HRS-w8`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_hrs8, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w8_ydeath','HRS.HRS-HRS-w8',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_hrs8, echo=F}
HRS_hrs_w8_ydeath <- opal.execute(o,'HRS_hrs_w8_ydeath')
vari <- HRS_hrs_w8_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_hrs_w8_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs8}
HRS_ds_hrs_w8 <- tibble(id=HRS_hrs_w8_ydeath$id)
HRS_ds_hrs_w8$ydeath <- car::recode(HRS_hrs_w8_ydeath$RADYEAR, "NA=999")
HRS_ds_hrs_w8$ydeath <- labelled(HRS_ds_hrs_w8$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs8, echo=F}
vari <- HRS_ds_hrs_w8$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w8 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_hrs8, echo=F}
BeforeH <- table(HRS_hrs_w8_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_hrs_w8$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_hrs8, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_hrs_w8', HRS_ds_hrs_w8)
#opal.symbol_import(o,'HRS_ds_hrs_w8', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_hrs_w8
save(ydeath, file = "../RData/hrs_w8/ydeath.RData")
rm(ydeath)

HRS_m_ds_hrs_w8 <- HRS_ds_hrs_w8
HRS_m_ds_hrs_w8$ydeath <- car::recode(HRS_m_ds_hrs_w8$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w8', HRS_m_ds_hrs_w8)
#opal.symbol_import(o,'HRS_m_ds_hrs_w8', project='_Athlos_Harm_Dataset')
```








### Wave 9

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-HRS-w9`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign_hrs9, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w9_ydeath','HRS.HRS-HRS-w9',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_hrs9, echo=F}
HRS_hrs_w9_ydeath <- opal.execute(o,'HRS_hrs_w9_ydeath')
vari <- HRS_hrs_w9_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_hrs_w9_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs9}
HRS_ds_hrs_w9 <- tibble(id=HRS_hrs_w9_ydeath$id)
HRS_ds_hrs_w9$ydeath <- car::recode(HRS_hrs_w9_ydeath$RADYEAR, "NA=999")
HRS_ds_hrs_w9$ydeath <- labelled(HRS_ds_hrs_w9$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs9, echo=F}
vari <- HRS_ds_hrs_w9$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w9 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_hrs9, echo=F}
BeforeH <- table(HRS_hrs_w9_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_hrs_w9$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_hrs9, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_hrs_w9', HRS_ds_hrs_w9)
#opal.symbol_import(o,'HRS_ds_hrs_w9', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_hrs_w9
save(ydeath, file = "../RData/hrs_w9/ydeath.RData")
rm(ydeath)

HRS_m_ds_hrs_w9 <- HRS_ds_hrs_w9
HRS_m_ds_hrs_w9$ydeath <- car::recode(HRS_m_ds_hrs_w9$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w9', HRS_m_ds_hrs_w9)
#opal.symbol_import(o,'HRS_m_ds_hrs_w9', project='_Athlos_Harm_Dataset')
```







### Wave 10

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-HRS-w10`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_hrs10, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w10_ydeath','HRS.HRS-HRS-w10',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_hrs10, echo=F}
HRS_hrs_w10_ydeath <- opal.execute(o,'HRS_hrs_w10_ydeath')
vari <- HRS_hrs_w10_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_hrs_w10_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs10}
HRS_ds_hrs_w10 <- tibble(id=HRS_hrs_w10_ydeath$id)
HRS_ds_hrs_w10$ydeath <- car::recode(HRS_hrs_w10_ydeath$RADYEAR, "NA=999")
HRS_ds_hrs_w10$ydeath <- labelled(HRS_ds_hrs_w10$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs10, echo=F}
vari <- HRS_ds_hrs_w10$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w10 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_hrs10, echo=F}
BeforeH <- table(HRS_hrs_w10_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_hrs_w10$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_hrs10, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_hrs_w10', HRS_ds_hrs_w10)
#opal.symbol_import(o,'HRS_ds_hrs_w10', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_hrs_w10
save(ydeath, file = "../RData/hrs_w10/ydeath.RData")
rm(ydeath)

HRS_m_ds_hrs_w10 <- HRS_ds_hrs_w10
HRS_m_ds_hrs_w10$ydeath <- car::recode(HRS_m_ds_hrs_w10$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w10', HRS_m_ds_hrs_w10)
#opal.symbol_import(o,'HRS_m_ds_hrs_w10', project='_Athlos_Harm_Dataset')
```







### Wave 11

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-HRS-w11`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign_hrs11, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w11_ydeath','HRS.HRS-HRS-w11',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_hrs11, echo=F}
HRS_hrs_w11_ydeath <- opal.execute(o,'HRS_hrs_w11_ydeath')
vari <- HRS_hrs_w11_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_hrs_w11_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_hrs11}
HRS_ds_hrs_w11 <- tibble(id=HRS_hrs_w11_ydeath$id)
HRS_ds_hrs_w11$ydeath <- car::recode(HRS_hrs_w11_ydeath$RADYEAR, "NA=999")
HRS_ds_hrs_w11$ydeath <- labelled(HRS_ds_hrs_w11$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs11, echo=F}
vari <- HRS_ds_hrs_w11$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_hrs_w11 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_hrs11, echo=F}
BeforeH <- table(HRS_hrs_w11_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_hrs_w11$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_hrs11, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_hrs_w11', HRS_ds_hrs_w11)
#opal.symbol_import(o,'HRS_ds_hrs_w11', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_hrs_w11
save(ydeath, file = "../RData/hrs_w11/ydeath.RData")
rm(ydeath)

HRS_m_ds_hrs_w11 <- HRS_ds_hrs_w11
HRS_m_ds_hrs_w11$ydeath <- car::recode(HRS_m_ds_hrs_w11$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_hrs_w11', HRS_m_ds_hrs_w11)
#opal.symbol_import(o,'HRS_m_ds_hrs_w11', project='_Athlos_Harm_Dataset')
```



## AHEAD



### Wave 2 

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-AHEAD-w2`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_ahead2, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w2_ydeath','HRS.HRS-AHEAD-w2',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_ahead2, echo=F}
HRS_ahead_w2_ydeath <- opal.execute(o,'HRS_ahead_w2_ydeath')
vari <- HRS_ahead_w2_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_ahead_w2_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ahead2}
HRS_ds_ahead_w2 <- tibble(id=HRS_ahead_w2_ydeath$id)
HRS_ds_ahead_w2$ydeath <- car::recode(HRS_ahead_w2_ydeath$RADYEAR, "NA=999")
HRS_ds_ahead_w2$ydeath <- labelled(HRS_ds_ahead_w2$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead2, echo=F}
vari <- HRS_ds_ahead_w2$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ahead_w2 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_ahead2, echo=F}
BeforeH <- table(HRS_ahead_w2_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_ahead_w2$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ahead2, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_ahead_w2', HRS_ds_ahead_w2)
#opal.symbol_import(o,'HRS_ds_ahead_w2', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_ahead_w2
save(ydeath, file = "../RData/ahead_w2/ydeath.RData")
rm(ydeath)

HRS_m_ds_ahead_w2 <- HRS_ds_ahead_w2
HRS_m_ds_ahead_w2$ydeath <- car::recode(HRS_m_ds_ahead_w2$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w2', HRS_m_ds_ahead_w2)
#opal.symbol_import(o,'HRS_m_ds_ahead_w2', project='_Athlos_Harm_Dataset')
```





### Wave 3 

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-AHEAD-w3`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign_ahead3, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w3_ydeath','HRS.HRS-AHEAD-w3',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_ahead3, echo=F}
HRS_ahead_w3_ydeath <- opal.execute(o,'HRS_ahead_w3_ydeath')
vari <- HRS_ahead_w3_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_ahead_w3_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ahead3}
HRS_ds_ahead_w3 <- tibble(id=HRS_ahead_w3_ydeath$id)
HRS_ds_ahead_w3$ydeath <- car::recode(HRS_ahead_w3_ydeath$RADYEAR, "NA=999")
HRS_ds_ahead_w3$ydeath <- labelled(HRS_ds_ahead_w3$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead3, echo=F}
vari <- HRS_ds_ahead_w3$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ahead_w3 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_ahead3, echo=F}
BeforeH <- table(HRS_ahead_w3_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_ahead_w3$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ahead3, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_ahead_w3', HRS_ds_ahead_w3)
#opal.symbol_import(o,'HRS_ds_ahead_w3', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_ahead_w3
save(ydeath, file = "../RData/ahead_w3/ydeath.RData")
rm(ydeath)

HRS_m_ds_ahead_w3 <- HRS_ds_ahead_w3
HRS_m_ds_ahead_w3$ydeath <- car::recode(HRS_m_ds_ahead_w3$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w3', HRS_m_ds_ahead_w3)
#opal.symbol_import(o,'HRS_m_ds_ahead_w3', project='_Athlos_Harm_Dataset')
```








### Wave 4 

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-AHEAD-w4`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_ahead4, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w4_ydeath','HRS.HRS-AHEAD-w4',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_ahead4, echo=F}
HRS_ahead_w4_ydeath <- opal.execute(o,'HRS_ahead_w4_ydeath')
vari <- HRS_ahead_w4_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_ahead_w4_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ahead4}
HRS_ds_ahead_w4 <- tibble(id=HRS_ahead_w4_ydeath$id)
HRS_ds_ahead_w4$ydeath <- car::recode(HRS_ahead_w4_ydeath$RADYEAR, "NA=999")
HRS_ds_ahead_w4$ydeath <- labelled(HRS_ds_ahead_w4$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead4, echo=F}
vari <- HRS_ds_ahead_w4$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ahead_w4 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_ahead4, echo=F}
BeforeH <- table(HRS_ahead_w4_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_ahead_w4$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ahead4, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_ahead_w4', HRS_ds_ahead_w4)
#opal.symbol_import(o,'HRS_ds_ahead_w4', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_ahead_w4
save(ydeath, file = "../RData/ahead_w4/ydeath.RData")
rm(ydeath)

HRS_m_ds_ahead_w4 <- HRS_ds_ahead_w4
HRS_m_ds_ahead_w4$ydeath <- car::recode(HRS_m_ds_ahead_w4$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w4', HRS_m_ds_ahead_w4)
#opal.symbol_import(o,'HRS_m_ds_ahead_w4', project='_Athlos_Harm_Dataset')
```







### Wave 5 

##### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-AHEAD-w5`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |




```{r assign_ahead5, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w5_ydeath','HRS.HRS-AHEAD-w5',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_ahead5, echo=F}
HRS_ahead_w5_ydeath <- opal.execute(o,'HRS_ahead_w5_ydeath')
vari <- HRS_ahead_w5_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_ahead_w5_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ahead5}
HRS_ds_ahead_w5 <- tibble(id=HRS_ahead_w5_ydeath$id)
HRS_ds_ahead_w5$ydeath <- car::recode(HRS_ahead_w5_ydeath$RADYEAR, "NA=999")
HRS_ds_ahead_w5$ydeath <- labelled(HRS_ds_ahead_w5$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead5, echo=F}
vari <- HRS_ds_ahead_w5$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ahead_w5 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_ahead5, echo=F}
BeforeH <- table(HRS_ahead_w5_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_ahead_w5$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ahead5, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_ahead_w5', HRS_ds_ahead_w5)
#opal.symbol_import(o,'HRS_ds_ahead_w5', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_ahead_w5
save(ydeath, file = "../RData/ahead_w5/ydeath.RData")
rm(ydeath)

HRS_m_ds_ahead_w5 <- HRS_ds_ahead_w5
HRS_m_ds_ahead_w5$ydeath <- car::recode(HRS_m_ds_ahead_w5$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w5', HRS_m_ds_ahead_w5)
#opal.symbol_import(o,'HRS_m_ds_ahead_w5', project='_Athlos_Harm_Dataset')
```








### Wave 6 

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-AHEAD-w6`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_ahead6, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w6_ydeath','HRS.HRS-AHEAD-w6',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_ahead6, echo=F}
HRS_ahead_w6_ydeath <- opal.execute(o,'HRS_ahead_w6_ydeath')
vari <- HRS_ahead_w6_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_ahead_w6_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ahead6}
HRS_ds_ahead_w6 <- tibble(id=HRS_ahead_w6_ydeath$id)
HRS_ds_ahead_w6$ydeath <- car::recode(HRS_ahead_w6_ydeath$RADYEAR, "NA=999")
HRS_ds_ahead_w6$ydeath <- labelled(HRS_ds_ahead_w6$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead6, echo=F}
vari <- HRS_ds_ahead_w6$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ahead_w6 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_ahead6, echo=F}
BeforeH <- table(HRS_ahead_w6_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_ahead_w6$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ahead6, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_ahead_w6', HRS_ds_ahead_w6)
#opal.symbol_import(o,'HRS_ds_ahead_w6', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_ahead_w6
save(ydeath, file = "../RData/ahead_w6/ydeath.RData")
rm(ydeath)

HRS_m_ds_ahead_w6 <- HRS_ds_ahead_w6
HRS_m_ds_ahead_w6$ydeath <- car::recode(HRS_m_ds_ahead_w6$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w6', HRS_m_ds_ahead_w6)
#opal.symbol_import(o,'HRS_m_ds_ahead_w6', project='_Athlos_Harm_Dataset')
```







### Wave 7 

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-AHEAD-w7`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign_ahead7, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w7_ydeath','HRS.HRS-AHEAD-w7',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_ahead7, echo=F}
HRS_ahead_w7_ydeath <- opal.execute(o,'HRS_ahead_w7_ydeath')
vari <- HRS_ahead_w7_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_ahead_w7_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ahead7}
HRS_ds_ahead_w7 <- tibble(id=HRS_ahead_w7_ydeath$id)
HRS_ds_ahead_w7$ydeath <- car::recode(HRS_ahead_w7_ydeath$RADYEAR, "NA=999")
HRS_ds_ahead_w7$ydeath <- labelled(HRS_ds_ahead_w7$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead7, echo=F}
vari <- HRS_ds_ahead_w7$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ahead_w7 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_ahead7, echo=F}
BeforeH <- table(HRS_ahead_w7_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_ahead_w7$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ahead7, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_ahead_w7', HRS_ds_ahead_w7)
#opal.symbol_import(o,'HRS_ds_ahead_w7', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_ahead_w7
save(ydeath, file = "../RData/ahead_w7/ydeath.RData")
rm(ydeath)

HRS_m_ds_ahead_w7 <- HRS_ds_ahead_w7
HRS_m_ds_ahead_w7$ydeath <- car::recode(HRS_m_ds_ahead_w7$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w7', HRS_m_ds_ahead_w7)
#opal.symbol_import(o,'HRS_m_ds_ahead_w7', project='_Athlos_Harm_Dataset')
```








### Wave 8 

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-AHEAD-w8`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_ahead8, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w8_ydeath','HRS.HRS-AHEAD-w8',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_ahead8, echo=F}
HRS_ahead_w8_ydeath <- opal.execute(o,'HRS_ahead_w8_ydeath')
vari <- HRS_ahead_w8_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_ahead_w8_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ahead8}
HRS_ds_ahead_w8 <- tibble(id=HRS_ahead_w8_ydeath$id)
HRS_ds_ahead_w8$ydeath <- car::recode(HRS_ahead_w8_ydeath$RADYEAR, "NA=999")
HRS_ds_ahead_w8$ydeath <- labelled(HRS_ds_ahead_w8$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead8, echo=F}
vari <- HRS_ds_ahead_w8$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ahead_w8 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_ahead8, echo=F}
BeforeH <- table(HRS_ahead_w8_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_ahead_w8$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ahead8, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_ahead_w8', HRS_ds_ahead_w8)
#opal.symbol_import(o,'HRS_ds_ahead_w8', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_ahead_w8
save(ydeath, file = "../RData/ahead_w8/ydeath.RData")
rm(ydeath)

HRS_m_ds_ahead_w8 <- HRS_ds_ahead_w8
HRS_m_ds_ahead_w8$ydeath <- car::recode(HRS_m_ds_ahead_w8$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w8', HRS_m_ds_ahead_w8)
#opal.symbol_import(o,'HRS_m_ds_ahead_w8', project='_Athlos_Harm_Dataset')
```








### Wave 9 

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-AHEAD-w9`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign_ahead9, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w9_ydeath','HRS.HRS-AHEAD-w9',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_ahead9, echo=F}
HRS_ahead_w9_ydeath <- opal.execute(o,'HRS_ahead_w9_ydeath')
vari <- HRS_ahead_w9_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_ahead_w9_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ahead9}
HRS_ds_ahead_w9 <- tibble(id=HRS_ahead_w9_ydeath$id)
HRS_ds_ahead_w9$ydeath <- car::recode(HRS_ahead_w9_ydeath$RADYEAR, "NA=999")
HRS_ds_ahead_w9$ydeath <- labelled(HRS_ds_ahead_w9$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead9, echo=F}
vari <- HRS_ds_ahead_w9$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ahead_w9 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_ahead9, echo=F}
BeforeH <- table(HRS_ahead_w9_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_ahead_w9$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ahead9, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_ahead_w9', HRS_ds_ahead_w9)
#opal.symbol_import(o,'HRS_ds_ahead_w9', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_ahead_w9
save(ydeath, file = "../RData/ahead_w9/ydeath.RData")
rm(ydeath)

HRS_m_ds_ahead_w9 <- HRS_ds_ahead_w9
HRS_m_ds_ahead_w9$ydeath <- car::recode(HRS_m_ds_ahead_w9$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w9', HRS_m_ds_ahead_w9)
#opal.symbol_import(o,'HRS_m_ds_ahead_w9', project='_Athlos_Harm_Dataset')
```







### Wave 10 

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-AHEAD-w10`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign_ahead10, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w10_ydeath','HRS.HRS-AHEAD-w10',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_ahead10, echo=F}
HRS_ahead_w10_ydeath <- opal.execute(o,'HRS_ahead_w10_ydeath')
vari <- HRS_ahead_w10_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_ahead_w10_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ahead10}
HRS_ds_ahead_w10 <- tibble(id=HRS_ahead_w10_ydeath$id)
HRS_ds_ahead_w10$ydeath <- car::recode(HRS_ahead_w10_ydeath$RADYEAR, "NA=999")
HRS_ds_ahead_w10$ydeath <- labelled(HRS_ds_ahead_w10$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead10, echo=F}
vari <- HRS_ds_ahead_w10$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ahead_w10 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_ahead10, echo=F}
BeforeH <- table(HRS_ahead_w10_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_ahead_w10$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ahead10, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_ahead_w10', HRS_ds_ahead_w10)
#opal.symbol_import(o,'HRS_ds_ahead_w10', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_ahead_w10
save(ydeath, file = "../RData/ahead_w10/ydeath.RData")
rm(ydeath)

HRS_m_ds_ahead_w10 <- HRS_ds_ahead_w10
HRS_m_ds_ahead_w10$ydeath <- car::recode(HRS_m_ds_ahead_w10$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w10', HRS_m_ds_ahead_w10)
#opal.symbol_import(o,'HRS_m_ds_ahead_w10', project='_Athlos_Harm_Dataset')
```







### Wave 11 

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-AHEAD-w11`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign_ahead11, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w11_ydeath','HRS.HRS-AHEAD-w11',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_ahead11, echo=F}
HRS_ahead_w11_ydeath <- opal.execute(o,'HRS_ahead_w11_ydeath')
vari <- HRS_ahead_w11_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_ahead_w11_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`


**R script:**

```{r harmo_ahead11}
HRS_ds_ahead_w11 <- tibble(id=HRS_ahead_w11_ydeath$id)
HRS_ds_ahead_w11$ydeath <- car::recode(HRS_ahead_w11_ydeath$RADYEAR, "NA=999")
HRS_ds_ahead_w11$ydeath <- labelled(HRS_ds_ahead_w11$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead11, echo=F}
vari <- HRS_ds_ahead_w11$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ahead_w11 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_ahead11, echo=F}
BeforeH <- table(HRS_ahead_w11_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_ahead_w11$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ahead11, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_ahead_w11', HRS_ds_ahead_w11)
#opal.symbol_import(o,'HRS_ds_ahead_w11', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_ahead_w11
save(ydeath, file = "../RData/ahead_w11/ydeath.RData")
rm(ydeath)

HRS_m_ds_ahead_w11 <- HRS_ds_ahead_w11
HRS_m_ds_ahead_w11$ydeath <- car::recode(HRS_m_ds_ahead_w11$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ahead_w11', HRS_m_ds_ahead_w11)
#opal.symbol_import(o,'HRS_m_ds_ahead_w11', project='_Athlos_Harm_Dataset')
```


## CODA


### Wave 4 

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-CODA-w4`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_coda4, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w4_ydeath','HRS.HRS-CODA-w4',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_coda4, echo=F}
HRS_coda_w4_ydeath <- opal.execute(o,'HRS_coda_w4_ydeath')
vari <- HRS_coda_w4_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_coda_w4_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_coda4}
HRS_ds_coda_w4 <- tibble(id=HRS_coda_w4_ydeath$id)
HRS_ds_coda_w4$ydeath <- car::recode(HRS_coda_w4_ydeath$RADYEAR, "NA=999")
HRS_ds_coda_w4$ydeath <- labelled(HRS_ds_coda_w4$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda4, echo=F}
vari <- HRS_ds_coda_w4$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_coda_w4 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_coda4, echo=F}
BeforeH <- table(HRS_coda_w4_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_coda_w4$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_coda4, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_coda_w4', HRS_ds_coda_w4)
#opal.symbol_import(o,'HRS_ds_coda_w4', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_coda_w4
save(ydeath, file = "../RData/coda_w4/ydeath.RData")
rm(ydeath)

HRS_m_ds_coda_w4 <- HRS_ds_coda_w4
HRS_m_ds_coda_w4$ydeath <- car::recode(HRS_m_ds_coda_w4$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_coda_w4', HRS_m_ds_coda_w4)
#opal.symbol_import(o,'HRS_m_ds_coda_w4', project='_Athlos_Harm_Dataset')
```








### Wave 5 

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-CODA-w5`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign_coda5, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w5_ydeath','HRS.HRS-CODA-w5',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_coda5, echo=F}
HRS_coda_w5_ydeath <- opal.execute(o,'HRS_coda_w5_ydeath')
vari <- HRS_coda_w5_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_coda_w5_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_coda5}
HRS_ds_coda_w5 <- tibble(id=HRS_coda_w5_ydeath$id)
HRS_ds_coda_w5$ydeath <- car::recode(HRS_coda_w5_ydeath$RADYEAR, "NA=999")
HRS_ds_coda_w5$ydeath <- labelled(HRS_ds_coda_w5$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda5, echo=F}
vari <- HRS_ds_coda_w5$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_coda_w5 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_coda5, echo=F}
BeforeH <- table(HRS_coda_w5_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_coda_w5$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_coda5, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_coda_w5', HRS_ds_coda_w5)
#opal.symbol_import(o,'HRS_ds_coda_w5', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_coda_w5
save(ydeath, file = "../RData/coda_w5/ydeath.RData")
rm(ydeath)

HRS_m_ds_coda_w5 <- HRS_ds_coda_w5
HRS_m_ds_coda_w5$ydeath <- car::recode(HRS_m_ds_coda_w5$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_coda_w5', HRS_m_ds_coda_w5)
#opal.symbol_import(o,'HRS_m_ds_coda_w5', project='_Athlos_Harm_Dataset')
```










### Wave 6 

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-CODA-w6`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_coda6, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w6_ydeath','HRS.HRS-CODA-w6',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_coda6, echo=F}
HRS_coda_w6_ydeath <- opal.execute(o,'HRS_coda_w6_ydeath')
vari <- HRS_coda_w6_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_coda_w6_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_coda6}
HRS_ds_coda_w6 <- tibble(id=HRS_coda_w6_ydeath$id)
HRS_ds_coda_w6$ydeath <- car::recode(HRS_coda_w6_ydeath$RADYEAR, "NA=999")
HRS_ds_coda_w6$ydeath <- labelled(HRS_ds_coda_w6$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda6, echo=F}
vari <- HRS_ds_coda_w6$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_coda_w6 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_coda6, echo=F}
BeforeH <- table(HRS_coda_w6_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_coda_w6$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_coda6, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_coda_w6', HRS_ds_coda_w6)
#opal.symbol_import(o,'HRS_ds_coda_w6', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_coda_w6
save(ydeath, file = "../RData/coda_w6/ydeath.RData")
rm(ydeath)

HRS_m_ds_coda_w6 <- HRS_ds_coda_w6
HRS_m_ds_coda_w6$ydeath <- car::recode(HRS_m_ds_coda_w6$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_coda_w6', HRS_m_ds_coda_w6)
#opal.symbol_import(o,'HRS_m_ds_coda_w6', project='_Athlos_Harm_Dataset')
```







### Wave 7 

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-CODA-w7`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_coda7, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w7_ydeath','HRS.HRS-CODA-w7',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_coda7, echo=F}
HRS_coda_w7_ydeath <- opal.execute(o,'HRS_coda_w7_ydeath')
vari <- HRS_coda_w7_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_coda_w7_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_coda7}
HRS_ds_coda_w7 <- tibble(id=HRS_coda_w7_ydeath$id)
HRS_ds_coda_w7$ydeath <- car::recode(HRS_coda_w7_ydeath$RADYEAR, "NA=999")
HRS_ds_coda_w7$ydeath <- labelled(HRS_ds_coda_w7$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```



#### Statistics of the new harmonised variable
```{r descript_coda7, echo=F}
vari <- HRS_ds_coda_w7$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_coda_w7 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_coda7, echo=F}
BeforeH <- table(HRS_coda_w7_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_coda_w7$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_coda7, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_coda_w7', HRS_ds_coda_w7)
#opal.symbol_import(o,'HRS_ds_coda_w7', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_coda_w7
save(ydeath, file = "../RData/coda_w7/ydeath.RData")
rm(ydeath)

HRS_m_ds_coda_w7 <- HRS_ds_coda_w7
HRS_m_ds_coda_w7$ydeath <- car::recode(HRS_m_ds_coda_w7$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_coda_w7', HRS_m_ds_coda_w7)
#opal.symbol_import(o,'HRS_m_ds_coda_w7', project='_Athlos_Harm_Dataset')
```







### Wave 8 

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-CODA-w8`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_coda8, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w8_ydeath','HRS.HRS-CODA-w8',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_coda8, echo=F}
HRS_coda_w8_ydeath <- opal.execute(o,'HRS_coda_w8_ydeath')
vari <- HRS_coda_w8_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_coda_w8_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_coda8}
HRS_ds_coda_w8 <- tibble(id=HRS_coda_w8_ydeath$id)
HRS_ds_coda_w8$ydeath <- car::recode(HRS_coda_w8_ydeath$RADYEAR, "NA=999")
HRS_ds_coda_w8$ydeath <- labelled(HRS_ds_coda_w8$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda8, echo=F}
vari <- HRS_ds_coda_w8$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_coda_w8 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_coda8, echo=F}
BeforeH <- table(HRS_coda_w8_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_coda_w8$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_coda8, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_coda_w8', HRS_ds_coda_w8)
#opal.symbol_import(o,'HRS_ds_coda_w8', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_coda_w8
save(ydeath, file = "../RData/coda_w8/ydeath.RData")
rm(ydeath)

HRS_m_ds_coda_w8 <- HRS_ds_coda_w8
HRS_m_ds_coda_w8$ydeath <- car::recode(HRS_m_ds_coda_w8$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_coda_w8', HRS_m_ds_coda_w8)
#opal.symbol_import(o,'HRS_m_ds_coda_w8', project='_Athlos_Harm_Dataset')
```







### Wave 9 

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-CODA-w9`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_coda9, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w9_ydeath','HRS.HRS-CODA-w9',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_coda9, echo=F}
HRS_coda_w9_ydeath <- opal.execute(o,'HRS_coda_w9_ydeath')
vari <- HRS_coda_w9_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_coda_w9_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_coda9}
HRS_ds_coda_w9 <- tibble(id=HRS_coda_w9_ydeath$id)
HRS_ds_coda_w9$ydeath <- car::recode(HRS_coda_w9_ydeath$RADYEAR, "NA=999")
HRS_ds_coda_w9$ydeath <- labelled(HRS_ds_coda_w9$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda9, echo=F}
vari <- HRS_ds_coda_w9$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_coda_w9 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_coda9, echo=F}
BeforeH <- table(HRS_coda_w9_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_coda_w9$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_coda9, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_coda_w9', HRS_ds_coda_w9)
#opal.symbol_import(o,'HRS_ds_coda_w9', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_coda_w9
save(ydeath, file = "../RData/coda_w9/ydeath.RData")
rm(ydeath)

HRS_m_ds_coda_w9 <- HRS_ds_coda_w9
HRS_m_ds_coda_w9$ydeath <- car::recode(HRS_m_ds_coda_w9$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_coda_w9', HRS_m_ds_coda_w9)
#opal.symbol_import(o,'HRS_m_ds_coda_w9', project='_Athlos_Harm_Dataset')
```







### Wave 10 

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-CODA-w10`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign_coda10, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w10_ydeath','HRS.HRS-CODA-w10',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_coda10, echo=F}
HRS_coda_w10_ydeath <- opal.execute(o,'HRS_coda_w10_ydeath')
vari <- HRS_coda_w10_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_coda_w10_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_coda10}
HRS_ds_coda_w10 <- tibble(id=HRS_coda_w10_ydeath$id)
HRS_ds_coda_w10$ydeath <- car::recode(HRS_coda_w10_ydeath$RADYEAR, "NA=999")
HRS_ds_coda_w10$ydeath <- labelled(HRS_ds_coda_w10$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda10, echo=F}
vari <- HRS_ds_coda_w10$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_coda_w10 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_coda10, echo=F}
BeforeH <- table(HRS_coda_w10_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_coda_w10$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_coda10, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_coda_w10', HRS_ds_coda_w10)
#opal.symbol_import(o,'HRS_ds_coda_w10', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_coda_w10
save(ydeath, file = "../RData/coda_w10/ydeath.RData")
rm(ydeath)

HRS_m_ds_coda_w10 <- HRS_ds_coda_w10
HRS_m_ds_coda_w10$ydeath <- car::recode(HRS_m_ds_coda_w10$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_coda_w10', HRS_m_ds_coda_w10)
#opal.symbol_import(o,'HRS_m_ds_coda_w10', project='_Athlos_Harm_Dataset')
```







### Wave 11 

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-CODA-w11`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_coda11, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w11_ydeath','HRS.HRS-CODA-w11',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_coda11, echo=F}
HRS_coda_w11_ydeath <- opal.execute(o,'HRS_coda_w11_ydeath')
vari <- HRS_coda_w11_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_coda_w11_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_coda11}
HRS_ds_coda_w11 <- tibble(id=HRS_coda_w11_ydeath$id)
HRS_ds_coda_w11$ydeath <- car::recode(HRS_coda_w11_ydeath$RADYEAR, "NA=999")
HRS_ds_coda_w11$ydeath <- labelled(HRS_ds_coda_w11$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda11, echo=F}
vari <- HRS_ds_coda_w11$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_coda_w11 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_coda11, echo=F}
BeforeH <- table(HRS_coda_w11_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_coda_w11$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_coda11, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_coda_w11', HRS_ds_coda_w11)
#opal.symbol_import(o,'HRS_ds_coda_w11', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_coda_w11
save(ydeath, file = "../RData/coda_w11/ydeath.RData")
rm(ydeath)

HRS_m_ds_coda_w11 <- HRS_ds_coda_w11
HRS_m_ds_coda_w11$ydeath <- car::recode(HRS_m_ds_coda_w11$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_coda_w11', HRS_m_ds_coda_w11)
#opal.symbol_import(o,'HRS_m_ds_coda_w11', project='_Athlos_Harm_Dataset')
```





## WB


### Wave 4  

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-WB-w4`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_wb4, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w4_ydeath','HRS.HRS-WB-w4',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_wb4, echo=F}
HRS_wb_w4_ydeath <- opal.execute(o,'HRS_wb_w4_ydeath')
vari <- HRS_wb_w4_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_wb_w4_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_wb4}
HRS_ds_wb_w4 <- tibble(id=HRS_wb_w4_ydeath$id)
HRS_ds_wb_w4$ydeath <- car::recode(HRS_wb_w4_ydeath$RADYEAR, "NA=999")
HRS_ds_wb_w4$ydeath <- labelled(HRS_ds_wb_w4$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb4, echo=F}
vari <- HRS_ds_wb_w4$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_wb_w4 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_wb4, echo=F}
BeforeH <- table(HRS_wb_w4_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_wb_w4$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_wb4, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_wb_w4', HRS_ds_wb_w4)
#opal.symbol_import(o,'HRS_ds_wb_w4', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_wb_w4
save(ydeath, file = "../RData/wb_w4/ydeath.RData")
rm(ydeath)

HRS_m_ds_wb_w4 <- HRS_ds_wb_w4
HRS_m_ds_wb_w4$ydeath <- car::recode(HRS_m_ds_wb_w4$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w4', HRS_m_ds_wb_w4)
#opal.symbol_import(o,'HRS_m_ds_wb_w4', project='_Athlos_Harm_Dataset')
```









### Wave 5  

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-WB-w5`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_wb5, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w5_ydeath','HRS.HRS-WB-w5',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_wb5, echo=F}
HRS_wb_w5_ydeath <- opal.execute(o,'HRS_wb_w5_ydeath')
vari <- HRS_wb_w5_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_wb_w5_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_wb5}
HRS_ds_wb_w5 <- tibble(id=HRS_wb_w5_ydeath$id)
HRS_ds_wb_w5$ydeath <- car::recode(HRS_wb_w5_ydeath$RADYEAR, "NA=999")
HRS_ds_wb_w5$ydeath <- labelled(HRS_ds_wb_w5$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb5, echo=F}
vari <- HRS_ds_wb_w5$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_wb_w5 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_wb5, echo=F}
BeforeH <- table(HRS_wb_w5_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_wb_w5$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_wb5, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_wb_w5', HRS_ds_wb_w5)
#opal.symbol_import(o,'HRS_ds_wb_w5', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_wb_w5
save(ydeath, file = "../RData/wb_w5/ydeath.RData")
rm(ydeath)

HRS_m_ds_wb_w5 <- HRS_ds_wb_w5
HRS_m_ds_wb_w5$ydeath <- car::recode(HRS_m_ds_wb_w5$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w5', HRS_m_ds_wb_w5)
#opal.symbol_import(o,'HRS_m_ds_wb_w5', project='_Athlos_Harm_Dataset')
```








### Wave 6  

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-WB-w6`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_wb6, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w6_ydeath','HRS.HRS-WB-w6',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_wb6, echo=F}
HRS_wb_w6_ydeath <- opal.execute(o,'HRS_wb_w6_ydeath')
vari <- HRS_wb_w6_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_wb_w6_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_wb6}
HRS_ds_wb_w6 <- tibble(id=HRS_wb_w6_ydeath$id)
HRS_ds_wb_w6$ydeath <- car::recode(HRS_wb_w6_ydeath$RADYEAR, "NA=999")
HRS_ds_wb_w6$ydeath <- labelled(HRS_ds_wb_w6$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb6, echo=F}
vari <- HRS_ds_wb_w6$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_wb_w6 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_wb6, echo=F}
BeforeH <- table(HRS_wb_w6_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_wb_w6$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_wb6, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_wb_w6', HRS_ds_wb_w6)
#opal.symbol_import(o,'HRS_ds_wb_w6', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_wb_w6
save(ydeath, file = "../RData/wb_w6/ydeath.RData")
rm(ydeath)

HRS_m_ds_wb_w6 <- HRS_ds_wb_w6
HRS_m_ds_wb_w6$ydeath <- car::recode(HRS_m_ds_wb_w6$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w6', HRS_m_ds_wb_w6)
#opal.symbol_import(o,'HRS_m_ds_wb_w6', project='_Athlos_Harm_Dataset')
```







### Wave 7  

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-WB-w7`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign_wb7, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w7_ydeath','HRS.HRS-WB-w7',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_wb7, echo=F}
HRS_wb_w7_ydeath <- opal.execute(o,'HRS_wb_w7_ydeath')
vari <- HRS_wb_w7_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_wb_w7_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_wb7}
HRS_ds_wb_w7 <- tibble(id=HRS_wb_w7_ydeath$id)
HRS_ds_wb_w7$ydeath <- car::recode(HRS_wb_w7_ydeath$RADYEAR, "NA=999")
HRS_ds_wb_w7$ydeath <- labelled(HRS_ds_wb_w7$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb7, echo=F}
vari <- HRS_ds_wb_w7$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_wb_w7 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_wb7, echo=F}
BeforeH <- table(HRS_wb_w7_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_wb_w7$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_wb7, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_wb_w7', HRS_ds_wb_w7)
#opal.symbol_import(o,'HRS_ds_wb_w7', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_wb_w7
save(ydeath, file = "../RData/wb_w7/ydeath.RData")
rm(ydeath)

HRS_m_ds_wb_w7 <- HRS_ds_wb_w7
HRS_m_ds_wb_w7$ydeath <- car::recode(HRS_m_ds_wb_w7$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w7', HRS_m_ds_wb_w7)
#opal.symbol_import(o,'HRS_m_ds_wb_w7', project='_Athlos_Harm_Dataset')
```








### Wave 8  

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-WB-w8`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_wb8, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w8_ydeath','HRS.HRS-WB-w8',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_wb8, echo=F}
HRS_wb_w8_ydeath <- opal.execute(o,'HRS_wb_w8_ydeath')
vari <- HRS_wb_w8_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_wb_w8_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_wb8}
HRS_ds_wb_w8 <- tibble(id=HRS_wb_w8_ydeath$id)
HRS_ds_wb_w8$ydeath <- car::recode(HRS_wb_w8_ydeath$RADYEAR, "NA=999")
HRS_ds_wb_w8$ydeath <- labelled(HRS_ds_wb_w8$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb8, echo=F}
vari <- HRS_ds_wb_w8$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_wb_w8 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_wb8, echo=F}
BeforeH <- table(HRS_wb_w8_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_wb_w8$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_wb8, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_wb_w8', HRS_ds_wb_w8)
#opal.symbol_import(o,'HRS_ds_wb_w8', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_wb_w8
save(ydeath, file = "../RData/wb_w8/ydeath.RData")
rm(ydeath)

HRS_m_ds_wb_w8 <- HRS_ds_wb_w8
HRS_m_ds_wb_w8$ydeath <- car::recode(HRS_m_ds_wb_w8$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w8', HRS_m_ds_wb_w8)
#opal.symbol_import(o,'HRS_m_ds_wb_w8', project='_Athlos_Harm_Dataset')
```








### Wave 9  

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-WB-w9`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_wb9, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w9_ydeath','HRS.HRS-WB-w9',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_wb9, echo=F}
HRS_wb_w9_ydeath <- opal.execute(o,'HRS_wb_w9_ydeath')
vari <- HRS_wb_w9_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_wb_w9_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_wb9}
HRS_ds_wb_w9 <- tibble(id=HRS_wb_w9_ydeath$id)
HRS_ds_wb_w9$ydeath <- car::recode(HRS_wb_w9_ydeath$RADYEAR, "NA=999")
HRS_ds_wb_w9$ydeath <- labelled(HRS_ds_wb_w9$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb9, echo=F}
vari <- HRS_ds_wb_w9$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_wb_w9 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_wb9, echo=F}
BeforeH <- table(HRS_wb_w9_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_wb_w9$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_wb9, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_wb_w9', HRS_ds_wb_w9)
#opal.symbol_import(o,'HRS_ds_wb_w9', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_wb_w9
save(ydeath, file = "../RData/wb_w9/ydeath.RData")
rm(ydeath)

HRS_m_ds_wb_w9 <- HRS_ds_wb_w9
HRS_m_ds_wb_w9$ydeath <- car::recode(HRS_m_ds_wb_w9$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w9', HRS_m_ds_wb_w9)
#opal.symbol_import(o,'HRS_m_ds_wb_w9', project='_Athlos_Harm_Dataset')
```







### Wave 10  

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-WB-w10`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_wb10, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w10_ydeath','HRS.HRS-WB-w10',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_wb10, echo=F}
HRS_wb_w10_ydeath <- opal.execute(o,'HRS_wb_w10_ydeath')
vari <- HRS_wb_w10_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_wb_w10_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_wb10}
HRS_ds_wb_w10 <- tibble(id=HRS_wb_w10_ydeath$id)
HRS_ds_wb_w10$ydeath <- car::recode(HRS_wb_w10_ydeath$RADYEAR, "NA=999")
HRS_ds_wb_w10$ydeath <- labelled(HRS_ds_wb_w10$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb10, echo=F}
vari <- HRS_ds_wb_w10$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_wb_w10 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_wb10, echo=F}
BeforeH <- table(HRS_wb_w10_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_wb_w10$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_wb10, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_wb_w10', HRS_ds_wb_w10)
#opal.symbol_import(o,'HRS_ds_wb_w10', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_wb_w10
save(ydeath, file = "../RData/wb_w10/ydeath.RData")
rm(ydeath)

HRS_m_ds_wb_w10 <- HRS_ds_wb_w10
HRS_m_ds_wb_w10$ydeath <- car::recode(HRS_m_ds_wb_w10$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w10', HRS_m_ds_wb_w10)
#opal.symbol_import(o,'HRS_m_ds_wb_w10', project='_Athlos_Harm_Dataset')
```







### Wave 11  

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-WB-w11`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_wb11, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w11_ydeath','HRS.HRS-WB-w11',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_wb11, echo=F}
HRS_wb_w11_ydeath <- opal.execute(o,'HRS_wb_w11_ydeath')
vari <- HRS_wb_w11_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_wb_w11_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_wb11}
HRS_ds_wb_w11 <- tibble(id=HRS_wb_w11_ydeath$id)
HRS_ds_wb_w11$ydeath <- car::recode(HRS_wb_w11_ydeath$RADYEAR, "NA=999")
HRS_ds_wb_w11$ydeath <- labelled(HRS_ds_wb_w11$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb11, echo=F}
vari <- HRS_ds_wb_w11$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_wb_w11 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_wb11, echo=F}
BeforeH <- table(HRS_wb_w11_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_wb_w11$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_wb11, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_wb_w11', HRS_ds_wb_w11)
#opal.symbol_import(o,'HRS_ds_wb_w11', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_wb_w11
save(ydeath, file = "../RData/wb_w11/ydeath.RData")
rm(ydeath)

HRS_m_ds_wb_w11 <- HRS_ds_wb_w11
HRS_m_ds_wb_w11$ydeath <- car::recode(HRS_m_ds_wb_w11$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_wb_w11', HRS_m_ds_wb_w11)
#opal.symbol_import(o,'HRS_m_ds_wb_w11', project='_Athlos_Harm_Dataset')
```




## EBB


### Wave 7  

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-EBB-w7`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign_ebb7, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w7_ydeath','HRS.HRS-EBB-w7',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_ebb7, echo=F}
HRS_ebb_w7_ydeath <- opal.execute(o,'HRS_ebb_w7_ydeath')
vari <- HRS_ebb_w7_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_ebb_w7_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ebb7}
HRS_ds_ebb_w7 <- tibble(id=HRS_ebb_w7_ydeath$id)
HRS_ds_ebb_w7$ydeath <- car::recode(HRS_ebb_w7_ydeath$RADYEAR, "NA=999")
HRS_ds_ebb_w7$ydeath <- labelled(HRS_ds_ebb_w7$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ebb7, echo=F}
vari <- HRS_ds_ebb_w7$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ebb_w7 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_ebb7, echo=F}
BeforeH <- table(HRS_ebb_w7_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_ebb_w7$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ebb7, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_ebb_w7', HRS_ds_ebb_w7)
#opal.symbol_import(o,'HRS_ds_ebb_w7', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_ebb_w7
save(ydeath, file = "../RData/ebb_w7/ydeath.RData")
rm(ydeath)

HRS_m_ds_ebb_w7 <- HRS_ds_ebb_w7
HRS_m_ds_ebb_w7$ydeath <- car::recode(HRS_m_ds_ebb_w7$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ebb_w7', HRS_m_ds_ebb_w7)
#opal.symbol_import(o,'HRS_m_ds_ebb_w7', project='_Athlos_Harm_Dataset')
```







### Wave 8  

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-EBB-w8`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_ebb8, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w8_ydeath','HRS.HRS-EBB-w8',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_ebb8, echo=F}
HRS_ebb_w8_ydeath <- opal.execute(o,'HRS_ebb_w8_ydeath')
vari <- HRS_ebb_w8_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_ebb_w8_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ebb8}
HRS_ds_ebb_w8 <- tibble(id=HRS_ebb_w8_ydeath$id)
HRS_ds_ebb_w8$ydeath <- car::recode(HRS_ebb_w8_ydeath$RADYEAR, "NA=999")
HRS_ds_ebb_w8$ydeath <- labelled(HRS_ds_ebb_w8$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ebb8, echo=F}
vari <- HRS_ds_ebb_w8$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ebb_w8 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_ebb8, echo=F}
BeforeH <- table(HRS_ebb_w8_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_ebb_w8$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ebb8, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_ebb_w8', HRS_ds_ebb_w8)
#opal.symbol_import(o,'HRS_ds_ebb_w8', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_ebb_w8
save(ydeath, file = "../RData/ebb_w8/ydeath.RData")
rm(ydeath)

HRS_m_ds_ebb_w8 <- HRS_ds_ebb_w8
HRS_m_ds_ebb_w8$ydeath <- car::recode(HRS_m_ds_ebb_w8$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ebb_w8', HRS_m_ds_ebb_w8)
#opal.symbol_import(o,'HRS_m_ds_ebb_w8', project='_Athlos_Harm_Dataset')
```







### Wave 9  

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-EBB-w9`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |



```{r assign_ebb9, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w9_ydeath','HRS.HRS-EBB-w9',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_ebb9, echo=F}
HRS_ebb_w9_ydeath <- opal.execute(o,'HRS_ebb_w9_ydeath')
vari <- HRS_ebb_w9_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_ebb_w9_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ebb9}
HRS_ds_ebb_w9 <- tibble(id=HRS_ebb_w9_ydeath$id)
HRS_ds_ebb_w9$ydeath <- car::recode(HRS_ebb_w9_ydeath$RADYEAR, "NA=999")
HRS_ds_ebb_w9$ydeath <- labelled(HRS_ds_ebb_w9$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ebb9, echo=F}
vari <- HRS_ds_ebb_w9$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ebb_w9 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_ebb9, echo=F}
BeforeH <- table(HRS_ebb_w9_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_ebb_w9$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ebb9, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_ebb_w9', HRS_ds_ebb_w9)
#opal.symbol_import(o,'HRS_ds_ebb_w9', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_ebb_w9
save(ydeath, file = "../RData/ebb_w9/ydeath.RData")
rm(ydeath)

HRS_m_ds_ebb_w9 <- HRS_ds_ebb_w9
HRS_m_ds_ebb_w9$ydeath <- car::recode(HRS_m_ds_ebb_w9$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ebb_w9', HRS_m_ds_ebb_w9)
#opal.symbol_import(o,'HRS_m_ds_ebb_w9', project='_Athlos_Harm_Dataset')
```







### Wave 10  

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-EBB-w10`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_ebb10, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w10_ydeath','HRS.HRS-EBB-w10',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_ebb10, echo=F}
HRS_ebb_w10_ydeath <- opal.execute(o,'HRS_ebb_w10_ydeath')
vari <- HRS_ebb_w10_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_ebb_w10_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ebb10}
HRS_ds_ebb_w10 <- tibble(id=HRS_ebb_w10_ydeath$id)
HRS_ds_ebb_w10$ydeath <- car::recode(HRS_ebb_w10_ydeath$RADYEAR, "NA=999")
HRS_ds_ebb_w10$ydeath <- labelled(HRS_ds_ebb_w10$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ebb10, echo=F}
vari <- HRS_ds_ebb_w10$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ebb_w10 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_ebb10, echo=F}
BeforeH <- table(HRS_ebb_w10_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_ebb_w10$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ebb10, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_ebb_w10', HRS_ds_ebb_w10)
#opal.symbol_import(o,'HRS_ds_ebb_w10', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_ebb_w10
save(ydeath, file = "../RData/ebb_w10/ydeath.RData")
rm(ydeath)

HRS_m_ds_ebb_w10 <- HRS_ds_ebb_w10
HRS_m_ds_ebb_w10$ydeath <- car::recode(HRS_m_ds_ebb_w10$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ebb_w10', HRS_m_ds_ebb_w10)
#opal.symbol_import(o,'HRS_m_ds_ebb_w10', project='_Athlos_Harm_Dataset')
```







### Wave 11  

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-EBB-w11`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_ebb11, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w11_ydeath','HRS.HRS-EBB-w11',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_ebb11, echo=F}
HRS_ebb_w11_ydeath <- opal.execute(o,'HRS_ebb_w11_ydeath')
vari <- HRS_ebb_w11_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_ebb_w11_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_ebb11}
HRS_ds_ebb_w11 <- tibble(id=HRS_ebb_w11_ydeath$id)
HRS_ds_ebb_w11$ydeath <- car::recode(HRS_ebb_w11_ydeath$RADYEAR, "NA=999")
HRS_ds_ebb_w11$ydeath <- labelled(HRS_ds_ebb_w11$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ebb11, echo=F}
vari <- HRS_ds_ebb_w11$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_ebb_w11 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_ebb11, echo=F}
BeforeH <- table(HRS_ebb_w11_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_ebb_w11$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_ebb11, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_ebb_w11', HRS_ds_ebb_w11)
#opal.symbol_import(o,'HRS_ds_ebb_w11', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_ebb_w11
save(ydeath, file = "../RData/ebb_w11/ydeath.RData")
rm(ydeath)

HRS_m_ds_ebb_w11 <- HRS_ds_ebb_w11
HRS_m_ds_ebb_w11$ydeath <- car::recode(HRS_m_ds_ebb_w11$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_ebb_w11', HRS_m_ds_ebb_w11)
#opal.symbol_import(o,'HRS_m_ds_ebb_w11', project='_Athlos_Harm_Dataset')
```




## MBB

### Wave 10  

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-MBB-w10`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_mbb10, echo=F}
opal.assign.table.tibble(o, 'HRS_mbb_w10_ydeath','HRS.HRS-MBB-w10',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_mbb10, echo=F}
HRS_mbb_w10_ydeath <- opal.execute(o,'HRS_mbb_w10_ydeath')
vari <- HRS_mbb_w10_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_mbb_w10_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_mbb10}
HRS_ds_mbb_w10 <- tibble(id=HRS_mbb_w10_ydeath$id)
HRS_ds_mbb_w10$ydeath <- car::recode(HRS_mbb_w10_ydeath$RADYEAR, "NA=999")
HRS_ds_mbb_w10$ydeath <- labelled(HRS_ds_mbb_w10$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_mbb10, echo=F}
vari <- HRS_ds_mbb_w10$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_mbb_w10 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_mbb10, echo=F}
BeforeH <- table(HRS_mbb_w10_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_mbb_w10$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_mbb10, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_mbb_w10', HRS_ds_mbb_w10)
#opal.symbol_import(o,'HRS_ds_mbb_w10', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_mbb_w10
save(ydeath, file = "../RData/mbb_w10/ydeath.RData")
rm(ydeath)

HRS_m_ds_mbb_w10 <- HRS_ds_mbb_w10
HRS_m_ds_mbb_w10$ydeath <- car::recode(HRS_m_ds_mbb_w10$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_mbb_w10', HRS_m_ds_mbb_w10)
#opal.symbol_import(o,'HRS_m_ds_mbb_w10', project='_Athlos_Harm_Dataset')
```







### Wave 11  

#### Study-specific variable description



| **Name** | `RADYEAR`|
|-|-|
| **Label** | `R death year` |
| **Table name** |`HRS-MBB-w11`|
| **Categories** |`continuous`|
| **Missings** |`NA`|
| **Description** |  |


```{r assign_mbb11, echo=F}
opal.assign.table.tibble(o, 'HRS_mbb_w11_ydeath','HRS.HRS-MBB-w11',
                         variables=list('RADYEAR'), missings = TRUE)
```

```{r local_mbb11, echo=F}
HRS_mbb_w11_ydeath <- opal.execute(o,'HRS_mbb_w11_ydeath')
vari <- HRS_mbb_w11_ydeath$RADYEAR
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "RADYEAR")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(HRS_mbb_w11_ydeath, aes(RADYEAR)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_mbb11}
HRS_ds_mbb_w11 <- tibble(id=HRS_mbb_w11_ydeath$id)
HRS_ds_mbb_w11$ydeath <- car::recode(HRS_mbb_w11_ydeath$RADYEAR, "NA=999")
HRS_ds_mbb_w11$ydeath <- labelled(HRS_ds_mbb_w11$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_mbb11, echo=F}
vari <- HRS_ds_mbb_w11$ydeath
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = "ydeath")
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(HRS_ds_mbb_w11 %>% filter(!vari %in% miss_values_vector), aes(ydeath)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_mbb11, echo=F}
BeforeH <- table(HRS_mbb_w11_ydeath$RADYEAR, useNA = "ifany")
AfterH <- table(HRS_ds_mbb_w11$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "NA->999")
kable(C)
```





```{r importOPAL_mbb11, echo=F, eval = FALSE}

#opal.assign.data(o, 'HRS_ds_mbb_w11', HRS_ds_mbb_w11)
#opal.symbol_import(o,'HRS_ds_mbb_w11', project='_Athlos_Harm_Dataset')
ydeath <- HRS_ds_mbb_w11
save(ydeath, file = "../RData/mbb_w11/ydeath.RData")
rm(ydeath)

HRS_m_ds_mbb_w11 <- HRS_ds_mbb_w11
HRS_m_ds_mbb_w11$ydeath <- car::recode(HRS_m_ds_mbb_w11$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'HRS_m_ds_mbb_w11', HRS_m_ds_mbb_w11)
#opal.symbol_import(o,'HRS_m_ds_mbb_w11', project='_Athlos_Harm_Dataset')
```











## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

source("../../helpfunctions.r")
rm(labelling)
labelling <- labelling_c
rm(summaries)
summaries <- summaries_c

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


hrs.hrs.cw <- list(hrs_w1 = c("hrs_w1","HRS w1"), hrs_w2 = c("hrs_w2","HRS w2"), hrs_w3 = c("hrs_w3","HRS w3"), hrs_w4 = c("hrs_w4","HRS w4"), hrs_w5 = c("hrs_w5","HRS w5"), hrs_w6 = c("hrs_w6","HRS w6"), hrs_w7 = c("hrs_w7","HRS w7"), hrs_w8 = c("hrs_w8","HRS w8"), hrs_w9 = c("hrs_w9","HRS w9"), hrs_w10 = c("hrs_w10","HRS w10"), hrs_w11 = c("hrs_w11","HRS w11"))

hrs.ahead.cw <- list(ahead_w2 = c("ahead_w2","AHEAD w2"), ahead_w3 = c("ahead_w3","AHEAD w3"), ahead_w4 = c("ahead_w4","AHEAD w4"), ahead_w5 = c("ahead_w5","AHEAD w5"), ahead_w6 = c("ahead_w6","AHEAD w6"), ahead_w7 = c("ahead_w7","AHEAD w7"), ahead_w8 = c("ahead_w8","AHEAD w8"), ahead_w9 = c("ahead_w9","AHEAD w9"), ahead_w10 = c("ahead_w10","AHEAD w10"), ahead_w11 = c("ahead_w11","AHEAD w11"))

hrs.coda.cw <- list(coda_w4 = c("coda_w4","CODA w4"), coda_w5 = c("coda_w5","CODA w5"), coda_w6 = c("coda_w6","CODA w6"), coda_w7 = c("coda_w7","CODA w7"), coda_w8 = c("coda_w8","CODA w8"), coda_w9 = c("coda_w9","CODA w9"), coda_w10 = c("coda_w10","CODA w10"), coda_w11 = c("coda_w11","CODA w11"))

hrs.wb.cw <- list(wb_w4 = c("wb_w4","WB w4"), wb_w5 = c("wb_w5","WB w5"), wb_w6 = c("wb_w6","WB w6"), wb_w7 = c("wb_w7","WB w7"), wb_w8 = c("wb_w8","WB w8"), wb_w9 = c("wb_w9","WB w9"), wb_w10 = c("wb_w10","WB w10"), wb_w11 = c("wb_w11","WB w11"))

hrs.ebb.cw <- list(ebb_w7 = c("ebb_w7","EBB w7"), ebb_w8 = c("ebb_w8","EBB w8"), ebb_w9 = c("ebb_w9","EBB w9"), ebb_w10 = c("ebb_w10","EBB w10"), ebb_w11 = c("ebb_w11","EBB w11"))

hrs.mbb.cw <- list(mbb_w10 = c("mbb_w10","MBB w10"), mbb_w11 = c("mbb_w11","MBB w11"))



# HRS

# Consider only harmonised waves
l.hds <- lapply(hrs.hrs.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}






# AHEAD

# Consider only harmonised waves
l.hds <- lapply(hrs.ahead.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)


if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}








# CODA

# Consider only harmonised waves
l.hds <- lapply(hrs.coda.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}





# WB

# Consider only harmonised waves
l.hds <- lapply(hrs.wb.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}





# EBB

# Consider only harmonised waves
l.hds <- lapply(hrs.ebb.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}




# MBB

# Consider only harmonised waves
l.hds <- lapply(hrs.mbb.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}




```






# Quality estimation

No comments


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
