---
title: "Living status"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_albert.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `living_status`
* Variable label: `Living status`
* Variable description: `The individual is dead or alive?`
* Domain: `Life expectancy`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | alive
1        | dead
2        | dropout

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## HRS

### Wave 1 

#### Study-specific variable description

| **Name** | `R1IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-HRS-w1`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |

    
    
```{r assign_hrs1, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w1_ls','HRS.HRS-HRS-w1', variables=list('R1IWSTAT'), missings = TRUE)
HRS_hrs_w1_ls <- opal.execute(o,'HRS_hrs_w1_ls')

```

```{r local_hrs1, echo=F}
vari <- HRS_hrs_w1_ls$R1IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R1IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w1_ls, aes(factor(R1IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Interview Status") + ylab("Frequency")

```

#### Harmonisation algorithm

Values are recoded as follows:

* Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive)
* Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died)
* Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout)
* Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_hrs1}
HRS_ds_hrs_w1 <- tibble(id=HRS_hrs_w1_ls$id)
HRS_ds_hrs_w1$living_status <- car::recode(HRS_hrs_w1_ls$R1IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")

HRS_ds_hrs_w1$living_status <- labelled(HRS_ds_hrs_w1$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs1, echo=F}
vari <- HRS_ds_hrs_w1$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w1, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs1, echo=F, results='asis'}
kable(table(HRS_hrs_w1_ls$R1IWSTAT, HRS_ds_hrs_w1$living_status, useNA = "ifany"), align='c', caption ='R1IWSTAT vs living_status')
#newT <- full_join( HRS_hrs_w1_ls, HRS_ds_hrs_w1, by="id")
#flat_table(newT, living_status, R1IWSTAT)
```

```{r importOPAL_hrs1, echo=F}
living_status <- HRS_ds_hrs_w1
save(living_status, file = "../RData/hrs_w1/living_status.RData")
rm(living_status)
```


### Wave 2 

#### Study-specific variable description

| **Name** | `R2IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-HRS-w2`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_hrs2, echo=F}
opal.assign.table.tibble(o,'HRS_hrs_w2_ls','HRS.HRS-HRS-w2', variables=list('R2IWSTAT'), missings = TRUE)
```

```{r local_hrs2, echo=F}
HRS_hrs_w2_ls <- opal.execute(o,'HRS_hrs_w2_ls')
vari <- HRS_hrs_w2_ls$R2IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R2IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w2_ls, aes(factor(R2IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Interview Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows:

* Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive)
* Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died)
* Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout)
* Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_hrs2}
HRS_ds_hrs_w2 <- tibble(id=HRS_hrs_w2_ls$id)
HRS_ds_hrs_w2$living_status <- car::recode(HRS_hrs_w2_ls$R2IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_hrs_w2$living_status <- labelled(HRS_ds_hrs_w2$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs2, echo=F}
vari <- HRS_ds_hrs_w2$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w2, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs2, echo=F, results='asis'}
kable(table(HRS_hrs_w2_ls$R2IWSTAT, HRS_ds_hrs_w2$living_status, useNA = "ifany"), align='c', caption ='R2IWSTAT vs living_status')
```

```{r importOPAL_hrs2, echo=F}
living_status <- HRS_ds_hrs_w2
save(living_status, file = "../RData/hrs_w2/living_status.RData")
rm(living_status)
```


### Wave 3 

#### Study-specific variable description

| **Name** | `R3IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-HRS-w3`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |



```{r assign_hrs3, echo=F}
opal.assign.table.tibble(o,'HRS_hrs_w3_ls','HRS.HRS-HRS-w3', variables=list('R3IWSTAT'), missings = TRUE)
```

```{r local_hrs3, echo=F}
HRS_hrs_w3_ls <- opal.execute(o,'HRS_hrs_w3_ls')
vari <- HRS_hrs_w3_ls$R3IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R3IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w3_ls, aes(factor(R3IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Interview Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows:

* Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive)
* Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died)
* Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout)
* Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_hrs3}
HRS_ds_hrs_w3 <- tibble(id=HRS_hrs_w3_ls$id)
HRS_ds_hrs_w3$living_status <- car::recode(HRS_hrs_w3_ls$R3IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_hrs_w3$living_status <- labelled(HRS_ds_hrs_w3$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs3, echo=F}
vari <- HRS_ds_hrs_w3$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w3, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs3, echo=F, results='asis'}
kable(table(HRS_hrs_w3_ls$R3IWSTAT, HRS_ds_hrs_w3$living_status, useNA = "ifany"), align='c', caption ='R3IWSTAT vs living_status')
```


```{r importOPAL_hrs3, echo=F}
living_status <- HRS_ds_hrs_w3
save(living_status, file = "../RData/hrs_w3/living_status.RData")
rm(living_status)
```


### Wave 4 

#### Study-specific variable description

| **Name** | `R4IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-HRS-w4`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_hrs4, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w4_ls','HRS.HRS-HRS-w4',
                         variables=list('R4IWSTAT'), missings = TRUE)
```

```{r local_hrs4, echo=F}
HRS_hrs_w4_ls <- opal.execute(o,'HRS_hrs_w4_ls')
vari <- HRS_hrs_w4_ls$R4IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R4IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w4_ls, aes(factor(R4IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm

Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.

**R script:**

```{r harmo_hrs4}
HRS_ds_hrs_w4 <- tibble(id=HRS_hrs_w4_ls$id)
HRS_ds_hrs_w4$living_status <- car::recode(HRS_hrs_w4_ls$R4IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_hrs_w4$living_status <- labelled(HRS_ds_hrs_w4$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs4, echo=F}
vari <- HRS_ds_hrs_w4$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w4, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs4, echo=F, results='asis'}
kable(table(HRS_hrs_w4_ls$R4IWSTAT, HRS_ds_hrs_w4$living_status, useNA = "ifany"), align='c', caption ='R4IWSTAT vs living_status')
```

```{r importOPAL_hrs4, echo=F}
living_status <- HRS_ds_hrs_w4
save(living_status, file = "../RData/hrs_w4/living_status.RData")
rm(living_status)
```


### Wave 5

#### Study-specific variable description

| **Name** | `R5IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-HRS-w5`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_hrs5, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w5_ls','HRS.HRS-HRS-w5',
                         variables=list('R5IWSTAT'), missings = TRUE)
```

```{r local_hrs5, echo=F}
HRS_hrs_w5_ls <- opal.execute(o,'HRS_hrs_w5_ls')
vari <- HRS_hrs_w5_ls$R5IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R5IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w5_ls, aes(factor(R5IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.



**R script:**

```{r harmo_hrs5}
HRS_ds_hrs_w5 <- tibble(id=HRS_hrs_w5_ls$id)
HRS_ds_hrs_w5$living_status <- car::recode(HRS_hrs_w5_ls$R5IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_hrs_w5$living_status <- labelled(HRS_ds_hrs_w5$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs5, echo=F}
vari <- HRS_ds_hrs_w2$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w2, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs5, echo=F, results='asis'}
kable(table(HRS_hrs_w5_ls$R5IWSTAT, HRS_ds_hrs_w5$living_status, useNA = "ifany"), align='c', caption ='R5IWSTAT vs living_status')
```


```{r importOPAL_hrs5, echo=F}
living_status <- HRS_ds_hrs_w5
save(living_status, file = "../RData/hrs_w5/living_status.RData")
rm(living_status)
```






### Wave 6

#### Study-specific variable description



| **Name** | `R6IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-HRS-w6`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_hrs6, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w6_ls','HRS.HRS-HRS-w6',
                         variables=list('R6IWSTAT'), missings = TRUE)
```

```{r local_hrs6, echo=F}
HRS_hrs_w6_ls <- opal.execute(o,'HRS_hrs_w6_ls')
vari <- HRS_hrs_w6_ls$R6IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R6IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w6_ls, aes(factor(R6IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_hrs6}
HRS_ds_hrs_w6 <- tibble(id=HRS_hrs_w6_ls$id)
HRS_ds_hrs_w6$living_status <- car::recode(HRS_hrs_w6_ls$R6IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_hrs_w6$living_status <- labelled(HRS_ds_hrs_w6$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs6, echo=F}
vari <- HRS_ds_hrs_w6$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w6, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs6, echo=F, results='asis'}
kable(table(HRS_hrs_w6_ls$R6IWSTAT, HRS_ds_hrs_w6$living_status, useNA = "ifany"), align='c', caption ='R6IWSTAT vs living_status')
```

```{r importOPAL_hrs6, echo=F}
living_status <- HRS_ds_hrs_w6
save(living_status, file = "../RData/hrs_w6/living_status.RData")
rm(living_status)
```


### Wave 7

#### Study-specific variable description

| **Name** | `R7IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-HRS-w7`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |



```{r assign_hrs7, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w7_ls','HRS.HRS-HRS-w7',
                         variables=list('R7IWSTAT'), missings = TRUE)
```

```{r local_hrs7, echo=F}
HRS_hrs_w7_ls <- opal.execute(o,'HRS_hrs_w7_ls')
vari <- HRS_hrs_w7_ls$R7IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R7IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w7_ls, aes(factor(R7IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_hrs7}
HRS_ds_hrs_w7 <- tibble(id=HRS_hrs_w7_ls$id)
HRS_ds_hrs_w7$living_status <- car::recode(HRS_hrs_w7_ls$R7IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_hrs_w7$living_status <- labelled(HRS_ds_hrs_w7$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs7, echo=F}
vari <- HRS_ds_hrs_w7$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w7, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs7, echo=F, results='asis'}
kable(table(HRS_hrs_w7_ls$R7IWSTAT, HRS_ds_hrs_w7$living_status, useNA = "ifany"), align='c', caption ='R7IWSTAT vs living_status')
```

```{r importOPAL_hrs7, echo=F}
living_status <- HRS_ds_hrs_w7
save(living_status, file = "../RData/hrs_w7/living_status.RData")
rm(living_status)
```

### Wave 8

#### Study-specific variable description

| **Name** | `R8IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-HRS-w8`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_hrs8, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w8_ls','HRS.HRS-HRS-w8',
                         variables=list('R8IWSTAT'), missings = TRUE)
```

```{r local_hrs8, echo=F}
HRS_hrs_w8_ls <- opal.execute(o,'HRS_hrs_w8_ls')
vari <- HRS_hrs_w8_ls$R8IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R8IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w8_ls, aes(factor(R8IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.



**R script:**

```{r harmo_hrs8}
HRS_ds_hrs_w8 <- tibble(id=HRS_hrs_w8_ls$id)
HRS_ds_hrs_w8$living_status <- car::recode(HRS_hrs_w8_ls$R8IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_hrs_w8$living_status <- labelled(HRS_ds_hrs_w8$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs8, echo=F}
vari <- HRS_ds_hrs_w8$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w8, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs8, echo=F, results='asis'}
kable(table(HRS_hrs_w8_ls$R8IWSTAT, HRS_ds_hrs_w8$living_status, useNA = "ifany"), align='c', caption ='R8IWSTAT vs living_status')
```

```{r importOPAL_hrs8, echo=F}
living_status <- HRS_ds_hrs_w8
save(living_status, file = "../RData/hrs_w8/living_status.RData")
rm(living_status)
```


### Wave 9

#### Study-specific variable description



| **Name** | `R9IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-HRS-w9`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_hrs9, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w9_ls','HRS.HRS-HRS-w9',
                         variables=list('R9IWSTAT'), missings = TRUE)
```

```{r local_hrs9, echo=F}
HRS_hrs_w9_ls <- opal.execute(o,'HRS_hrs_w9_ls')
vari <- HRS_hrs_w9_ls$R9IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R9IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w9_ls, aes(factor(R9IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_hrs9}
HRS_ds_hrs_w9 <- tibble(id=HRS_hrs_w9_ls$id)
HRS_ds_hrs_w9$living_status <- car::recode(HRS_hrs_w9_ls$R9IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_hrs_w9$living_status <- labelled(HRS_ds_hrs_w9$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs9, echo=F}
vari <- HRS_ds_hrs_w9$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w9, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs9, echo=F, results='asis'}
kable(table(HRS_hrs_w9_ls$R9IWSTAT, HRS_ds_hrs_w9$living_status, useNA = "ifany"), align='c', caption ='R9IWSTAT vs living_status')
```

```{r importOPAL_hrs9, echo=F}
living_status <- HRS_ds_hrs_w9
save(living_status, file = "../RData/hrs_w9/living_status.RData")
rm(living_status)
```


### Wave 10

#### Study-specific variable description

| **Name** | `R10IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-HRS-w10`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_hrs10, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w10_ls','HRS.HRS-HRS-w10', variables=list('R10IWSTAT'), missings = TRUE)
```

```{r local_hrs10, echo=F}
HRS_hrs_w10_ls <- opal.execute(o,'HRS_hrs_w10_ls')
vari <- HRS_hrs_w10_ls$R10IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R10IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w10_ls, aes(factor(R10IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_hrs10}
HRS_ds_hrs_w10 <- tibble(id=HRS_hrs_w10_ls$id)
HRS_ds_hrs_w10$living_status <- car::recode(HRS_hrs_w10_ls$R10IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_hrs_w10$living_status <- labelled(HRS_ds_hrs_w10$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs10, echo=F}
vari <- HRS_ds_hrs_w10$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w10, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs10, echo=F, results='asis'}
kable(table(HRS_hrs_w10_ls$R10IWSTAT, HRS_ds_hrs_w10$living_status, useNA = "ifany"), align='c', caption ='R10IWSTAT vs living_status')
```

```{r importOPAL_hrs10, echo=F}
living_status <- HRS_ds_hrs_w10
save(living_status, file = "../RData/hrs_w10/living_status.RData")
rm(living_status)
```


### Wave 11

#### Study-specific variable description

| **Name** | `R11IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-HRS-w11`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |



```{r assign_hrs11, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w11_ls','HRS.HRS-HRS-w11',
                         variables=list('R11IWSTAT'), missings = TRUE)
```


```{r local_hrs11, echo=F}
HRS_hrs_w11_ls <- opal.execute(o,'HRS_hrs_w11_ls')
vari <- HRS_hrs_w11_ls$R11IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R11IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w11_ls, aes(factor(R11IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_hrs11}
HRS_ds_hrs_w11 <- tibble(id=HRS_hrs_w11_ls$id)
HRS_ds_hrs_w11$living_status <- car::recode(HRS_hrs_w11_ls$R11IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_hrs_w11$living_status <- labelled(HRS_ds_hrs_w11$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs11, echo=F}
vari <- HRS_ds_hrs_w11$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w11, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs11, echo=F, results='asis'}
kable(table(HRS_hrs_w11_ls$R11IWSTAT, HRS_ds_hrs_w11$living_status, useNA = "ifany"), align='c', caption ='R11IWSTAT vs living_status')
```

```{r importOPAL_hrs11, echo=F}
living_status <- HRS_ds_hrs_w11
save(living_status, file = "../RData/hrs_w11/living_status.RData")
rm(living_status)
```

### Validation throughout waves

```{r valid_ws_hrs, echo=F}
dbb <- merge(HRS_ds_hrs_w1, HRS_ds_hrs_w2, by = "id", suffixes = c(".w1", ".w2"), all = T)
dbb <- merge(dbb, HRS_ds_hrs_w3, by = "id", all = T)
dbb <- merge(dbb, HRS_ds_hrs_w4, by = "id", suffixes = c(".w3", ".w4"), all = T)
dbb <- merge(dbb, HRS_ds_hrs_w5, by = "id", all = T)
dbb <- merge(dbb, HRS_ds_hrs_w6, by = "id", suffixes = c(".w5", ".w6"), all = T)
dbb <- merge(dbb, HRS_ds_hrs_w7, by = "id", all = T)
dbb <- merge(dbb, HRS_ds_hrs_w8, by = "id", suffixes = c(".w7", ".w8"), all = T)
dbb <- merge(dbb, HRS_ds_hrs_w9, by = "id", all = T)
dbb <- merge(dbb, HRS_ds_hrs_w10, by = "id", suffixes = c(".w9", ".w10"), all = T)
dbb <- merge(dbb, HRS_ds_hrs_w11, by = "id", all = T)
#dbb <- dbb[,-1]
dbb[dbb == 996] <- NA
names(dbb) <- c("id", "w1", "w2", "w3", "w4", "w5", "w6", "w7", "w8", "w9", "w10", "w11")
v.dbb <- paste(dbb[, 2], dbb[, 3], dbb[, 4], dbb[, 5], dbb[, 6], dbb[, 7], dbb[, 8], dbb[, 9], dbb[, 10], dbb[, 11], dbb[, 12], sep = "")
f.dbb <- frq(v.dbb)[[1]][, c(1, 2, 4)]
kable(f.dbb)
#kable(f.dbb[f.dbb[, 3] >= 0.3, ])
```


## AHEAD

### Wave 2 

#### Study-specific variable description

| **Name** | `R2IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-AHEAD-w2`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_ahead2, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w2_ls','HRS.HRS-AHEAD-w2', variables=list('R2IWSTAT'), missings = TRUE)
```

```{r local_ahead2, echo=F}
HRS_ahead_w2_ls <- opal.execute(o,'HRS_ahead_w2_ls')
vari <- HRS_ahead_w2_ls$R2IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R2IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w2_ls, aes(factor(R2IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_ahead2}
HRS_ds_ahead_w2 <- tibble(id=HRS_ahead_w2_ls$id)
HRS_ds_ahead_w2$living_status <- car::recode(HRS_ahead_w2_ls$R2IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_ahead_w2$living_status <- labelled(HRS_ds_ahead_w2$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead2, echo=F}
vari <- HRS_ds_ahead_w2$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w2, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead2, echo=F, results='asis'}
kable(table(HRS_ahead_w2_ls$R2IWSTAT, HRS_ds_ahead_w2$living_status, useNA = "ifany"), align='c', caption ='R2IWSTAT vs living_status')
```

```{r importOPAL_ahead2, echo=F}
living_status <- HRS_ds_ahead_w2
save(living_status, file = "../RData/ahead_w2/living_status.RData")
rm(living_status)
```


### Wave 3 

#### Study-specific variable description

| **Name** | `R3IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-AHEAD-w3`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_ahead3, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w3_ls','HRS.HRS-AHEAD-w3', variables=list('R3IWSTAT'), missings = TRUE)
```

```{r local_ahead3, echo=F}
HRS_ahead_w3_ls <- opal.execute(o,'HRS_ahead_w3_ls')
vari <- HRS_ahead_w3_ls$R3IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R3IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w3_ls, aes(factor(R3IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.



**R script:**

```{r harmo_ahead3}
HRS_ds_ahead_w3 <- tibble(id=HRS_ahead_w3_ls$id)
HRS_ds_ahead_w3$living_status <- car::recode(HRS_ahead_w3_ls$R3IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_ahead_w3$living_status <- labelled(HRS_ds_ahead_w3$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead3, echo=F}
vari <- HRS_ds_ahead_w3$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w3, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead3, echo=F, results='asis'}
kable(table(HRS_ahead_w3_ls$R3IWSTAT, HRS_ds_ahead_w3$living_status, useNA = "ifany"), align='c', caption ='R3IWSTAT vs living_status')
```

```{r importOPAL_ahead3, echo=F}
living_status <- HRS_ds_ahead_w3
save(living_status, file = "../RData/ahead_w3/living_status.RData")
rm(living_status)
```


### Wave 4 

#### Study-specific variable description

| **Name** | `R4IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-AHEAD-w4`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_ahead4, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w4_ls','HRS.HRS-AHEAD-w4',
                         variables=list('R4IWSTAT'), missings = TRUE)
```

```{r local_ahead4, echo=F}
HRS_ahead_w4_ls <- opal.execute(o,'HRS_ahead_w4_ls')
vari <- HRS_ahead_w4_ls$R4IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R4IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w4_ls, aes(factor(R4IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_ahead4}
HRS_ds_ahead_w4 <- tibble(id=HRS_ahead_w4_ls$id)
HRS_ds_ahead_w4$living_status <- car::recode(HRS_ahead_w4_ls$R4IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_ahead_w4$living_status <- labelled(HRS_ds_ahead_w4$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead4, echo=F}
vari <- HRS_ds_ahead_w4$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w4, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead4, echo=F, results='asis'}
kable(table(HRS_ahead_w4_ls$R4IWSTAT, HRS_ds_ahead_w4$living_status, useNA = "ifany"), align='c', caption ='R4IWSTAT vs living_status')
```


```{r importOPAL_ahead4, echo=F}
living_status <- HRS_ds_ahead_w4
save(living_status, file = "../RData/ahead_w4/living_status.RData")
rm(living_status)
```


### Wave 5 

#### Study-specific variable description

| **Name** | `R5IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-AHEAD-w5`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_ahead5, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w5_ls','HRS.HRS-AHEAD-w5',  variables=list('R5IWSTAT'), missings = TRUE)
```

```{r local_ahead5, echo=F}
HRS_ahead_w5_ls <- opal.execute(o,'HRS_ahead_w5_ls')
vari <- HRS_ahead_w5_ls$R5IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R5IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w5_ls, aes(factor(R5IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.



**R script:**

```{r harmo_ahead5}
HRS_ds_ahead_w5 <- tibble(id=HRS_ahead_w5_ls$id)
HRS_ds_ahead_w5$living_status <- car::recode(HRS_ahead_w5_ls$R5IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_ahead_w5$living_status <- labelled(HRS_ds_ahead_w5$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead5, echo=F}
vari <- HRS_ds_ahead_w5$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w5, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead5, echo=F, results='asis'}
kable(table(HRS_ahead_w5_ls$R5IWSTAT, HRS_ds_ahead_w5$living_status, useNA = "ifany"), align='c', caption ='R5IWSTAT vs living_status')
```

```{r importOPAL_ahead5, echo=F}
living_status <- HRS_ds_ahead_w5
save(living_status, file = "../RData/ahead_w5/living_status.RData")
rm(living_status)
```



### Wave 6 

#### Study-specific variable description

| **Name** | `R6IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-AHEAD-w6`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_ahead6, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w6_ls','HRS.HRS-AHEAD-w6', variables=list('R6IWSTAT'), missings = TRUE)
```

```{r local_ahead6, echo=F}
HRS_ahead_w6_ls <- opal.execute(o,'HRS_ahead_w6_ls')
vari <- HRS_ahead_w6_ls$R6IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R6IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w6_ls, aes(factor(R6IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_ahead6}
HRS_ds_ahead_w6 <- tibble(id=HRS_ahead_w6_ls$id)
HRS_ds_ahead_w6$living_status <- car::recode(HRS_ahead_w6_ls$R6IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_ahead_w6$living_status <- labelled(HRS_ds_ahead_w6$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead6, echo=F}
vari <- HRS_ds_ahead_w6$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w6, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead6, echo=F, results='asis'}
kable(table(HRS_ahead_w6_ls$R6IWSTAT, HRS_ds_ahead_w6$living_status, useNA = "ifany"), align='c', caption ='R6IWSTAT vs living_status')
```

```{r importOPAL_ahead6, echo=F}
living_status <- HRS_ds_ahead_w6
save(living_status, file = "../RData/ahead_w6/living_status.RData")
rm(living_status)
```



### Wave 7 

#### Study-specific variable description

| **Name** | `R7IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-AHEAD-w7`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_ahead7, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w7_ls','HRS.HRS-AHEAD-w7', variables=list('R7IWSTAT'), missings = TRUE)
```

```{r local_ahead7, echo=F}
HRS_ahead_w7_ls <- opal.execute(o,'HRS_ahead_w7_ls')
vari <- HRS_ahead_w7_ls$R7IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R7IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w7_ls, aes(factor(R7IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_ahead7}
HRS_ds_ahead_w7 <- tibble(id=HRS_ahead_w7_ls$id)
HRS_ds_ahead_w7$living_status <- car::recode(HRS_ahead_w7_ls$R7IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_ahead_w7$living_status <- labelled(HRS_ds_ahead_w7$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead7, echo=F}
vari <- HRS_ds_ahead_w7$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w7, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead7, echo=F, results='asis'}
kable(table(HRS_ahead_w7_ls$R7IWSTAT, HRS_ds_ahead_w7$living_status, useNA = "ifany"), align='c', caption ='R7IWSTAT vs living_status')
```

```{r importOPAL_ahead7, echo=F}
living_status <- HRS_ds_ahead_w7
save(living_status, file = "../RData/ahead_w7/living_status.RData")
rm(living_status)
```




### Wave 8 

#### Study-specific variable description

| **Name** | `R8IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-AHEAD-w8`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_ahead8, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w8_ls','HRS.HRS-AHEAD-w8',  variables=list('R8IWSTAT'), missings = TRUE)
```

```{r local_ahead8, echo=F}
HRS_ahead_w8_ls <- opal.execute(o,'HRS_ahead_w8_ls')
vari <- HRS_ahead_w8_ls$R8IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R8IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w8_ls, aes(factor(R8IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_ahead8}
HRS_ds_ahead_w8 <- tibble(id=HRS_ahead_w8_ls$id)
HRS_ds_ahead_w8$living_status <- car::recode(HRS_ahead_w8_ls$R8IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_ahead_w8$living_status <- labelled(HRS_ds_ahead_w8$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead8, echo=F}
vari <- HRS_ds_ahead_w8$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w8, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead8, echo=F, results='asis'}
kable(table(HRS_ahead_w8_ls$R8IWSTAT, HRS_ds_ahead_w8$living_status, useNA = "ifany"), align='c', caption ='R8IWSTAT vs living_status')
```


```{r importOPAL_ahead8, echo=F}
living_status <- HRS_ds_ahead_w8
save(living_status, file = "../RData/ahead_w8/living_status.RData")
rm(living_status)
```


### Wave 9 

#### Study-specific variable description

| **Name** | `R9IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-AHEAD-w9`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_ahead9, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w9_ls','HRS.HRS-AHEAD-w9', variables=list('R9IWSTAT'), missings = TRUE)
```

```{r local_ahead9, echo=F}
HRS_ahead_w9_ls <- opal.execute(o,'HRS_ahead_w9_ls')
vari <- HRS_ahead_w9_ls$R9IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R9IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w9_ls, aes(factor(R9IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.



**R script:**

```{r harmo_ahead9}
HRS_ds_ahead_w9 <- tibble(id=HRS_ahead_w9_ls$id)
HRS_ds_ahead_w9$living_status <- car::recode(HRS_ahead_w9_ls$R9IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_ahead_w9$living_status <- labelled(HRS_ds_ahead_w9$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead9, echo=F}
vari <- HRS_ds_ahead_w9$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w9, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead9, echo=F, results='asis'}
kable(table(HRS_ahead_w9_ls$R9IWSTAT, HRS_ds_ahead_w9$living_status, useNA = "ifany"), align='c', caption ='R9IWSTAT vs living_status')
```


```{r importOPAL_ahead9, echo=F}
living_status <- HRS_ds_ahead_w9
save(living_status, file = "../RData/ahead_w9/living_status.RData")
rm(living_status)
```


### Wave 10 

#### Study-specific variable description

| **Name** | `R10IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-AHEAD-w10`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_ahead10, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w10_ls','HRS.HRS-AHEAD-w10', variables=list('R10IWSTAT'), missings = TRUE)
```

```{r local_ahead10, echo=F}
HRS_ahead_w10_ls <- opal.execute(o,'HRS_ahead_w10_ls')
vari <- HRS_ahead_w10_ls$R10IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R10IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w10_ls, aes(factor(R10IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_ahead10}
HRS_ds_ahead_w10 <- tibble(id=HRS_ahead_w10_ls$id)
HRS_ds_ahead_w10$living_status <- car::recode(HRS_ahead_w10_ls$R10IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_ahead_w10$living_status <- labelled(HRS_ds_ahead_w10$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead10, echo=F}
vari <- HRS_ds_ahead_w10$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w10, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead10, echo=F, results='asis'}
kable(table(HRS_ahead_w10_ls$R10IWSTAT, HRS_ds_ahead_w10$living_status, useNA = "ifany"), align='c', caption ='R10IWSTAT vs living_status')
```

```{r importOPAL_ahead10, echo=F}
living_status <- HRS_ds_ahead_w10
save(living_status, file = "../RData/ahead_w10/living_status.RData")
rm(living_status)
```

### Wave 11 

#### Study-specific variable description

| **Name** | `R11IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-AHEAD-w11`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |

```{r assign_ahead11, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w11_ls','HRS.HRS-AHEAD-w11', variables=list('R11IWSTAT'), missings = TRUE)
```

```{r local_ahead11, echo=F}
HRS_ahead_w11_ls <- opal.execute(o,'HRS_ahead_w11_ls')
vari <- HRS_ahead_w11_ls$R11IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R11IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w11_ls, aes(factor(R11IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_ahead11}
HRS_ds_ahead_w11 <- tibble(id=HRS_ahead_w11_ls$id)
HRS_ds_ahead_w11$living_status <- car::recode(HRS_ahead_w11_ls$R11IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_ahead_w11$living_status <- labelled(HRS_ds_ahead_w11$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead11, echo=F}
vari <- HRS_ds_ahead_w11$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w11, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead11, echo=F, results='asis'}
kable(table(HRS_ahead_w11_ls$R11IWSTAT, HRS_ds_ahead_w11$living_status, useNA = "ifany"), align='c', caption ='R11IWSTAT vs living_status')
```

```{r importOPAL_ahead11, echo=F}
living_status <- HRS_ds_ahead_w11
save(living_status, file = "../RData/ahead_w11/living_status.RData")
rm(living_status)
```

### Validation throughout waves

```{r valid_ws_head, echo=F}
dbb <- merge(HRS_ds_ahead_w2, HRS_ds_ahead_w3, by = "id", suffixes = c(".w2", ".w3"), all = T)
dbb <- merge(dbb, HRS_ds_ahead_w4, by = "id", all = T)
dbb <- merge(dbb, HRS_ds_ahead_w5, by = "id", suffixes = c(".w4", ".w5"), all = T)
dbb <- merge(dbb, HRS_ds_ahead_w6, by = "id", all = T)
dbb <- merge(dbb, HRS_ds_ahead_w7, by = "id", suffixes = c(".w6", ".w7"), all = T)
dbb <- merge(dbb, HRS_ds_ahead_w8, by = "id", all = T)
dbb <- merge(dbb, HRS_ds_ahead_w9, by = "id", suffixes = c(".w8", ".w9"), all = T)
dbb <- merge(dbb, HRS_ds_ahead_w10, by = "id", all = T)
dbb <- merge(dbb, HRS_ds_ahead_w11, by = "id", suffixes = c(".w10", ".w11"), all = T)
dbb <- dbb[,-1]
dbb[dbb == 996] <- NA
names(dbb) <- c("w2", "w3", "w4", "w5", "w6", "w7", "w8", "w9", "w10", "w11")
v.dbb <- paste(dbb[, 1], dbb[, 2], dbb[, 3], dbb[, 4], dbb[, 5], dbb[, 6], dbb[, 7], dbb[, 8], dbb[, 9], dbb[, 10], sep = "")
f.dbb <- frq(v.dbb)[[1]][, c(1, 2, 4)]
kable(f.dbb)
```


## CODA

### Wave 4 

#### Study-specific variable description

| **Name** | `R4IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-CODA-w4`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |

```{r assign_coda4, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w4_ls','HRS.HRS-CODA-w4', variables=list('R4IWSTAT'), missings = TRUE)
```

```{r local_coda4, echo=F}
HRS_coda_w4_ls <- opal.execute(o,'HRS_coda_w4_ls')
vari <- HRS_coda_w4_ls$R4IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R4IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w4_ls, aes(factor(R4IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")

```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.

**R script:**

```{r harmo_coda4}
HRS_ds_coda_w4 <- tibble(id=HRS_coda_w4_ls$id)
HRS_ds_coda_w4$living_status <- car::recode(HRS_coda_w4_ls$R4IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_coda_w4$living_status <- labelled(HRS_ds_coda_w4$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda4, echo=F}
vari <- HRS_ds_coda_w4$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w4, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_coda4, echo=F, results='asis'}
kable(table(HRS_coda_w4_ls$R4IWSTAT, HRS_ds_coda_w4$living_status, useNA = "ifany"), align='c', caption ='R4IWSTAT vs living_status')
```

```{r importOPAL_coda4, echo=F}
living_status <- HRS_ds_coda_w4
save(living_status, file = "../RData/coda_w4/living_status.RData")
rm(living_status)
```


### Wave 5 

#### Study-specific variable description

| **Name** | `R5IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-CODA-w5`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |

```{r assign_coda5, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w5_ls','HRS.HRS-CODA-w5', variables=list('R5IWSTAT'), missings = TRUE)
```

```{r local_coda5, echo=F}
HRS_coda_w5_ls <- opal.execute(o,'HRS_coda_w5_ls')
vari <- HRS_coda_w5_ls$R5IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R5IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w5_ls, aes(factor(R5IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_coda5}
HRS_ds_coda_w5 <- tibble(id=HRS_coda_w5_ls$id)
HRS_ds_coda_w5$living_status <- car::recode(HRS_coda_w5_ls$R5IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_coda_w5$living_status <- labelled(HRS_ds_coda_w5$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda5, echo=F}
vari <- HRS_ds_coda_w5$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w5, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_coda5, echo=F, results='asis'}
kable(table(HRS_coda_w5_ls$R5IWSTAT, HRS_ds_coda_w5$living_status, useNA = "ifany"), align='c', caption ='R5IWSTAT vs living_status')
```

```{r importOPAL_coda5, echo=F}
living_status <- HRS_ds_coda_w5
save(living_status, file = "../RData/coda_w5/living_status.RData")
rm(living_status)
```


### Wave 6 

#### Study-specific variable description

| **Name** | `R6IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-CODA-w6`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_coda6, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w6_ls','HRS.HRS-CODA-w6', variables=list('R6IWSTAT'), missings = TRUE)
```

```{r local_coda6, echo=F}
HRS_coda_w6_ls <- opal.execute(o,'HRS_coda_w6_ls')
vari <- HRS_coda_w6_ls$R6IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R6IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w6_ls, aes(factor(R6IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_coda6}
HRS_ds_coda_w6 <- tibble(id=HRS_coda_w6_ls$id)
HRS_ds_coda_w6$living_status <- car::recode(HRS_coda_w6_ls$R6IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_coda_w6$living_status <- labelled(HRS_ds_coda_w6$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda6, echo=F}
vari <- HRS_ds_coda_w6$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w6, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_coda6, echo=F, results='asis'}
kable(table(HRS_coda_w6_ls$R6IWSTAT, HRS_ds_coda_w6$living_status, useNA = "ifany"), align='c', caption ='R6IWSTAT vs living_status')
```

```{r importOPAL_coda6, echo=F}
living_status <- HRS_ds_coda_w6
save(living_status, file = "../RData/coda_w6/living_status.RData")
rm(living_status)
```


### Wave 7 

#### Study-specific variable description

| **Name** | `R7IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-CODA-w7`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |

```{r assign_coda7, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w7_ls','HRS.HRS-CODA-w7', variables=list('R7IWSTAT'), missings = TRUE)
```

```{r local_coda7, echo=F}
HRS_coda_w7_ls <- opal.execute(o,'HRS_coda_w7_ls')
vari <- HRS_coda_w7_ls$R7IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R7IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w7_ls, aes(factor(R7IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_coda7}
HRS_ds_coda_w7 <- tibble(id=HRS_coda_w7_ls$id)
HRS_ds_coda_w7$living_status <- car::recode(HRS_coda_w7_ls$R7IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_coda_w7$living_status <- labelled(HRS_ds_coda_w7$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_coda7, echo=F}
vari <- HRS_ds_coda_w7$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w7, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_coda7, echo=F, results='asis'}
kable(table(HRS_coda_w7_ls$R7IWSTAT, HRS_ds_coda_w7$living_status, useNA = "ifany"), align='c', caption ='R7IWSTAT vs living_status')
```

```{r importOPAL_coda7, echo=F}
living_status <- HRS_ds_coda_w7
save(living_status, file = "../RData/coda_w7/living_status.RData")
rm(living_status)
```


### Wave 8 

#### Study-specific variable description

| **Name** | `R8IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-CODA-w8`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_coda8, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w8_ls','HRS.HRS-CODA-w8',
                         variables=list('R8IWSTAT'), missings = TRUE)
```

```{r local_coda8, echo=F}
HRS_coda_w8_ls <- opal.execute(o,'HRS_coda_w8_ls')
vari <- HRS_coda_w8_ls$R8IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R8IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w8_ls, aes(factor(R8IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_coda8}
HRS_ds_coda_w8 <- tibble(id=HRS_coda_w8_ls$id)
HRS_ds_coda_w8$living_status <- car::recode(HRS_coda_w8_ls$R8IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_coda_w8$living_status <- labelled(HRS_ds_coda_w8$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda8, echo=F}
vari <- HRS_ds_coda_w8$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w8, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_coda8, echo=F, results='asis'}
kable(table(HRS_coda_w8_ls$R8IWSTAT, HRS_ds_coda_w8$living_status, useNA = "ifany"), align='c', caption ='R8IWSTAT vs living_status')
```

```{r importOPAL_coda8, echo=F}
living_status <- HRS_ds_coda_w8
save(living_status, file = "../RData/coda_w8/living_status.RData")
rm(living_status)
```


### Wave 9 

#### Study-specific variable description

| **Name** | `R9IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-CODA-w9`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_coda9, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w9_ls','HRS.HRS-CODA-w9', variables=list('R9IWSTAT'), missings = TRUE)
```

```{r local_coda9, echo=F}
HRS_coda_w9_ls <- opal.execute(o,'HRS_coda_w9_ls')
vari <- HRS_coda_w9_ls$R9IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R9IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w9_ls, aes(factor(R9IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_coda9}
HRS_ds_coda_w9 <- tibble(id=HRS_coda_w9_ls$id)
HRS_ds_coda_w9$living_status <- car::recode(HRS_coda_w9_ls$R9IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_coda_w9$living_status <- labelled(HRS_ds_coda_w9$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda9, echo=F}
vari <- HRS_ds_coda_w9$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w9, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_coda9, echo=F, results='asis'}
kable(table(HRS_coda_w9_ls$R9IWSTAT, HRS_ds_coda_w9$living_status, useNA = "ifany"), align='c', caption ='R9IWSTAT vs living_status')
```

```{r importOPAL_coda9, echo=F}
living_status <- HRS_ds_coda_w9
save(living_status, file = "../RData/coda_w9/living_status.RData")
rm(living_status)
```

### Wave 10 

#### Study-specific variable description

| **Name** | `R10IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-CODA-w10`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_coda10, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w10_ls','HRS.HRS-CODA-w10', variables=list('R10IWSTAT'), missings = TRUE)
```

```{r local_coda10, echo=F}
HRS_coda_w10_ls <- opal.execute(o,'HRS_coda_w10_ls')
vari <- HRS_coda_w10_ls$R10IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R10IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w10_ls, aes(factor(R10IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_coda10}
HRS_ds_coda_w10 <- tibble(id=HRS_coda_w10_ls$id)
HRS_ds_coda_w10$living_status <- car::recode(HRS_coda_w10_ls$R10IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_coda_w10$living_status <- labelled(HRS_ds_coda_w10$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda10, echo=F}
vari <- HRS_ds_coda_w10$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w10, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_coda10, echo=F, results='asis'}
kable(table(HRS_coda_w10_ls$R10IWSTAT, HRS_ds_coda_w10$living_status, useNA = "ifany"), align='c', caption ='R10IWSTAT vs living_status')
```

```{r importOPAL_coda10, echo=F}
living_status <- HRS_ds_coda_w10
save(living_status, file = "../RData/coda_w10/living_status.RData")
rm(living_status)
```


### Wave 11 

#### Study-specific variable description

| **Name** | `R11IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-CODA-w11`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_coda11, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w11_ls','HRS.HRS-CODA-w11', variables=list('R11IWSTAT'), missings = TRUE)
```

```{r local_coda11, echo=F}
HRS_coda_w11_ls <- opal.execute(o,'HRS_coda_w11_ls')
vari <- HRS_coda_w11_ls$R11IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R11IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w11_ls, aes(factor(R11IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_coda11}
HRS_ds_coda_w11 <- tibble(id=HRS_coda_w11_ls$id)
HRS_ds_coda_w11$living_status <- car::recode(HRS_coda_w11_ls$R11IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_coda_w11$living_status <- labelled(HRS_ds_coda_w11$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda11, echo=F}
vari <- HRS_ds_coda_w11$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w11, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_coda11, echo=F, results='asis'}
kable(table(HRS_coda_w11_ls$R11IWSTAT, HRS_ds_coda_w11$living_status, useNA = "ifany"), align='c', caption ='R11IWSTAT vs living_status')
```

```{r importOPAL_coda11, echo=F}
living_status <- HRS_ds_coda_w11
save(living_status, file = "../RData/coda_w11/living_status.RData")
rm(living_status)
```

### Validation throughout waves

```{r valid_ws_coda, echo=F}
dbb <- merge(HRS_ds_coda_w4, HRS_ds_coda_w5, by = "id", suffixes = c(".w4", ".w5"), all = T)
dbb <- merge(dbb, HRS_ds_coda_w6, by = "id", all = T)
dbb <- merge(dbb, HRS_ds_coda_w7, by = "id", suffixes = c(".w6", ".w7"), all = T)
dbb <- merge(dbb, HRS_ds_coda_w8, by = "id", all = T)
dbb <- merge(dbb, HRS_ds_coda_w9, by = "id", suffixes = c(".w8", ".w9"), all = T)
dbb <- merge(dbb, HRS_ds_coda_w10, by = "id", all = T)
dbb <- merge(dbb, HRS_ds_coda_w11, by = "id", suffixes = c(".w10", ".w11"), all = T)
dbb <- dbb[,-1]
dbb[dbb == 996] <- NA
names(dbb) <- c("w4", "w5", "w6", "w7", "w8", "w9", "w10", "w11")
v.dbb <- paste(dbb[, 1], dbb[, 2], dbb[, 3], dbb[, 4], dbb[, 5], dbb[, 6], dbb[, 7], dbb[, 8], sep = "")
f.dbb <- frq(v.dbb)[[1]][, c(1, 2, 4)]
kable(f.dbb)
```


## WB

### Wave 4  

#### Study-specific variable description

| **Name** | `R4IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-WB-w4`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |

```{r assign_wb4, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w4_ls','HRS.HRS-WB-w4', variables=list('R4IWSTAT'), missings = TRUE)
```

```{r local_wb4, echo=F}
HRS_wb_w4_ls <- opal.execute(o,'HRS_wb_w4_ls')
vari <- HRS_wb_w4_ls$R4IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R4IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w4_ls, aes(factor(R4IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")

```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.

**R script:**

```{r harmo_wb4}
HRS_ds_wb_w4 <- tibble(id=HRS_wb_w4_ls$id)
HRS_ds_wb_w4$living_status <- car::recode(HRS_wb_w4_ls$R4IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_wb_w4$living_status <- labelled(HRS_ds_wb_w4$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb4, echo=F}
vari <- HRS_ds_wb_w4$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w4, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_wb4, echo=F, results='asis'}
kable(table(HRS_wb_w4_ls$R4IWSTAT, HRS_ds_wb_w4$living_status, useNA = "ifany"), align='c', caption ='R4IWSTAT vs living_status')
```

```{r importOPAL_wb4, echo=F}
living_status <- HRS_ds_wb_w4
save(living_status, file = "../RData/wb_w4/living_status.RData")
rm(living_status)
```


### Wave 5  

#### Study-specific variable description

| **Name** | `R5IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-WB-w5`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_wb5, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w5_ls','HRS.HRS-WB-w5', variables=list('R5IWSTAT'), missings = TRUE)
```

```{r local_wb5, echo=F}
HRS_wb_w5_ls <- opal.execute(o,'HRS_wb_w5_ls')
vari <- HRS_wb_w5_ls$R5IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R5IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w5_ls, aes(factor(R5IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_wb5}
HRS_ds_wb_w5 <- tibble(id=HRS_wb_w5_ls$id)
HRS_ds_wb_w5$living_status <- car::recode(HRS_wb_w5_ls$R5IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_wb_w5$living_status <- labelled(HRS_ds_wb_w5$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_wb5, echo=F}
vari <- HRS_ds_wb_w5$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w5, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_wb5, echo=F, results='asis'}
kable(table(HRS_wb_w5_ls$R5IWSTAT, HRS_ds_wb_w5$living_status, useNA = "ifany"), align='c', caption ='R5IWSTAT vs living_status')
```

```{r importOPAL_wb5, echo=F}
living_status <- HRS_ds_wb_w5
save(living_status, file = "../RData/wb_w5/living_status.RData")
rm(living_status)
```


### Wave 6  

#### Study-specific variable description

| **Name** | `R6IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-WB-w6`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_wb6, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w6_ls','HRS.HRS-WB-w6', variables=list('R6IWSTAT'), missings = TRUE)
```

```{r local_wb6, echo=F}
HRS_wb_w6_ls <- opal.execute(o,'HRS_wb_w6_ls')
vari <- HRS_wb_w6_ls$R6IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R6IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w6_ls, aes(factor(R6IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.

**R script:**

```{r harmo_wb6}
HRS_ds_wb_w6 <- tibble(id=HRS_wb_w6_ls$id)
HRS_ds_wb_w6$living_status <- car::recode(HRS_wb_w6_ls$R6IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_wb_w6$living_status <- labelled(HRS_ds_wb_w6$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_wb6, echo=F}
vari <- HRS_ds_wb_w6$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w6, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_wb6, echo=F, results='asis'}
kable(table(HRS_wb_w6_ls$R6IWSTAT, HRS_ds_wb_w6$living_status, useNA = "ifany"), align='c', caption ='R6IWSTAT vs living_status')
```

```{r importOPAL_wb6, echo=F}
living_status <- HRS_ds_wb_w6
save(living_status, file = "../RData/wb_w6/living_status.RData")
rm(living_status)
```


### Wave 7  

#### Study-specific variable description

| **Name** | `R7IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-WB-w7`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_wb7, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w7_ls','HRS.HRS-WB-w7', variables=list('R7IWSTAT'), missings = TRUE)
```

```{r local_wb7, echo=F}
HRS_wb_w7_ls <- opal.execute(o,'HRS_wb_w7_ls')
vari <- HRS_wb_w7_ls$R7IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R7IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w7_ls, aes(factor(R7IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_wb7}
HRS_ds_wb_w7 <- tibble(id=HRS_wb_w7_ls$id)
HRS_ds_wb_w7$living_status <- car::recode(HRS_wb_w7_ls$R7IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_wb_w7$living_status <- labelled(HRS_ds_wb_w7$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb7, echo=F}
vari <- HRS_ds_wb_w7$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w7, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_wb7, echo=F, results='asis'}
kable(table(HRS_wb_w7_ls$R7IWSTAT, HRS_ds_wb_w7$living_status, useNA = "ifany"), align='c', caption ='R7IWSTAT vs living_status')
```

```{r importOPAL_wb7, echo=F}
living_status <- HRS_ds_wb_w7
save(living_status, file = "../RData/wb_w7/living_status.RData")
rm(living_status)
```



### Wave 8  

#### Study-specific variable description

| **Name** | `R8IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-WB-w8`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_wb8, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w8_ls','HRS.HRS-WB-w8', variables=list('R8IWSTAT'), missings = TRUE)
```

```{r local_wb8, echo=F}
HRS_wb_w8_ls <- opal.execute(o,'HRS_wb_w8_ls')
vari <- HRS_wb_w8_ls$R8IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R8IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w8_ls, aes(factor(R8IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_wb8}
HRS_ds_wb_w8 <- tibble(id=HRS_wb_w8_ls$id)
HRS_ds_wb_w8$living_status <- car::recode(HRS_wb_w8_ls$R8IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_wb_w8$living_status <- labelled(HRS_ds_wb_w8$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_wb8, echo=F}
vari <- HRS_ds_wb_w8$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w8, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_wb8, echo=F, results='asis'}
kable(table(HRS_wb_w8_ls$R8IWSTAT, HRS_ds_wb_w8$living_status, useNA = "ifany"), align='c', caption ='R8IWSTAT vs living_status')
```

```{r importOPAL_wb8, echo=F}
living_status <- HRS_ds_wb_w8
save(living_status, file = "../RData/wb_w8/living_status.RData")
rm(living_status)
```



### Wave 9  

#### Study-specific variable description

| **Name** | `R9IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-WB-w9`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_wb9, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w9_ls','HRS.HRS-WB-w9', variables=list('R9IWSTAT'), missings = TRUE)
```

```{r local_wb9, echo=F}
HRS_wb_w9_ls <- opal.execute(o,'HRS_wb_w9_ls')
vari <- HRS_wb_w9_ls$R9IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R9IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w9_ls, aes(factor(R9IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_wb9}
HRS_ds_wb_w9 <- tibble(id=HRS_wb_w9_ls$id)
HRS_ds_wb_w9$living_status <- car::recode(HRS_wb_w9_ls$R9IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_wb_w9$living_status <- labelled(HRS_ds_wb_w9$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb9, echo=F}
vari <- HRS_ds_wb_w9$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w9, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_wb9, echo=F, results='asis'}
kable(table(HRS_wb_w9_ls$R9IWSTAT, HRS_ds_wb_w9$living_status, useNA = "ifany"), align='c', caption ='R9IWSTAT vs living_status')
```

```{r importOPAL_wb9, echo=F}
living_status <- HRS_ds_wb_w9
save(living_status, file = "../RData/wb_w9/living_status.RData")
rm(living_status)
```



### Wave 10  

#### Study-specific variable description

| **Name** | `R10IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-WB-w10`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_wb10, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w10_ls','HRS.HRS-WB-w10', variables=list('R10IWSTAT'), missings = TRUE)
```

```{r local_wb10, echo=F}
HRS_wb_w10_ls <- opal.execute(o,'HRS_wb_w10_ls')
vari <- HRS_wb_w10_ls$R10IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R10IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w10_ls, aes(factor(R10IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_wb10}
HRS_ds_wb_w10 <- tibble(id=HRS_wb_w10_ls$id)
HRS_ds_wb_w10$living_status <- car::recode(HRS_wb_w10_ls$R10IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_wb_w10$living_status <- labelled(HRS_ds_wb_w10$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb10, echo=F}
vari <- HRS_ds_wb_w10$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w10, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_wb10, echo=F, results='asis'}
kable(table(HRS_wb_w10_ls$R10IWSTAT, HRS_ds_wb_w10$living_status, useNA = "ifany"), align='c', caption ='R10IWSTAT vs living_status')
```

```{r importOPAL_wb10, echo=F}
living_status <- HRS_ds_wb_w10
save(living_status, file = "../RData/wb_w10/living_status.RData")
rm(living_status)
```


### Wave 11  

#### Study-specific variable description

| **Name** | `R11IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-WB-w11`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_wb11, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w11_ls','HRS.HRS-WB-w11', variables=list('R11IWSTAT'), missings = TRUE)
```

```{r local_wb11, echo=F}
HRS_wb_w11_ls <- opal.execute(o,'HRS_wb_w11_ls')
vari <- HRS_wb_w11_ls$R11IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R11IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w11_ls, aes(factor(R11IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.



**R script:**

```{r harmo_wb11}
HRS_ds_wb_w11 <- tibble(id=HRS_wb_w11_ls$id)
HRS_ds_wb_w11$living_status <- car::recode(HRS_wb_w11_ls$R11IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_wb_w11$living_status <- labelled(HRS_ds_wb_w11$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb11, echo=F}
vari <- HRS_ds_wb_w11$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w11, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_wb11, echo=F, results='asis'}
kable(table(HRS_wb_w11_ls$R11IWSTAT, HRS_ds_wb_w11$living_status, useNA = "ifany"), align='c', caption ='R11IWSTAT vs living_status')
```

```{r importOPAL_wb11, echo=F}
living_status <- HRS_ds_wb_w11
save(living_status, file = "../RData/wb_w11/living_status.RData")
rm(living_status)
```

### Validation throughout waves

```{r valid_ws_wb, echo=F}
dbb <- merge(HRS_ds_wb_w4, HRS_ds_wb_w5, by = "id", suffixes = c(".w4", ".w5"), all = T)
dbb <- merge(dbb, HRS_ds_wb_w6, by = "id", all = T)
dbb <- merge(dbb, HRS_ds_wb_w7, by = "id", suffixes = c(".w6", ".w7"), all = T)
dbb <- merge(dbb, HRS_ds_wb_w8, by = "id", all = T)
dbb <- merge(dbb, HRS_ds_wb_w9, by = "id", suffixes = c(".w8", ".w9"), all = T)
dbb <- merge(dbb, HRS_ds_wb_w10, by = "id", all = T)
dbb <- merge(dbb, HRS_ds_wb_w11, by = "id", suffixes = c(".w10", ".w11"), all = T)
dbb <- dbb[,-1]
dbb[dbb == 996] <- NA
names(dbb) <- c("w4", "w5", "w6", "w7", "w8", "w9", "w10", "w11")
v.dbb <- paste(dbb[, 1], dbb[, 2], dbb[, 3], dbb[, 4], dbb[, 5], dbb[, 6], dbb[, 7], dbb[, 8], sep = "")
f.dbb <- frq(v.dbb)[[1]][, c(1, 2, 4)]
kable(f.dbb)
```


## EBB

### Wave 7  

#### Study-specific variable description

| **Name** | `R7IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-EBB-w7`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |

```{r assign_ebb7, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w7_ls','HRS.HRS-EBB-w7', variables=list('R7IWSTAT'), missings = TRUE)
```

```{r local_ebb7, echo=F}
HRS_ebb_w7_ls <- opal.execute(o,'HRS_ebb_w7_ls')
vari <- HRS_ebb_w7_ls$R7IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R7IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ebb_w7_ls, aes(factor(R7IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")

```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.

**R script:**

```{r harmo_ebb7}
HRS_ds_ebb_w7 <- tibble(id=HRS_ebb_w7_ls$id)
HRS_ds_ebb_w7$living_status <- car::recode(HRS_ebb_w7_ls$R7IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_ebb_w7$living_status <- labelled(HRS_ds_ebb_w7$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ebb7, echo=F}
vari <- HRS_ds_ebb_w7$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w7, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ebb7, echo=F, results='asis'}
kable(table(HRS_ebb_w7_ls$R7IWSTAT, HRS_ds_ebb_w7$living_status, useNA = "ifany"), align='c', caption ='R7IWSTAT vs living_status')
```

```{r importOPAL_ebb7, echo=F}
living_status <- HRS_ds_ebb_w7
save(living_status, file = "../RData/ebb_w7/living_status.RData")
rm(living_status)
```


### Wave 8  

#### Study-specific variable description

| **Name** | `R8IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-EBB-w8`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_ebb8, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w8_ls','HRS.HRS-EBB-w8', variables=list('R8IWSTAT'), missings = TRUE)
```

```{r local_ebb8, echo=F}
HRS_ebb_w8_ls <- opal.execute(o,'HRS_ebb_w8_ls')
vari <- HRS_ebb_w8_ls$R8IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R8IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ebb_w8_ls, aes(factor(R8IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_ebb8}
HRS_ds_ebb_w8 <- tibble(id=HRS_ebb_w8_ls$id)
HRS_ds_ebb_w8$living_status <- car::recode(HRS_ebb_w8_ls$R8IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_ebb_w8$living_status <- labelled(HRS_ds_ebb_w8$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_ebb8, echo=F}
vari <- HRS_ds_ebb_w8$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w8, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ebb8, echo=F, results='asis'}
kable(table(HRS_ebb_w8_ls$R8IWSTAT, HRS_ds_ebb_w8$living_status, useNA = "ifany"), align='c', caption ='R8IWSTAT vs living_status')
```

```{r importOPAL_ebb8, echo=F}
living_status <- HRS_ds_ebb_w8
save(living_status, file = "../RData/ebb_w8/living_status.RData")
rm(living_status)
```


### Wave 9  

#### Study-specific variable description

| **Name** | `R9IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-EBB-w9`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_ebb9, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w9_ls','HRS.HRS-EBB-w9', variables=list('R9IWSTAT'), missings = TRUE)
```

```{r local_ebb9, echo=F}
HRS_ebb_w9_ls <- opal.execute(o,'HRS_ebb_w9_ls')
vari <- HRS_ebb_w9_ls$R9IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R9IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ebb_w9_ls, aes(factor(R9IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_ebb9}
HRS_ds_ebb_w9 <- tibble(id=HRS_ebb_w9_ls$id)
HRS_ds_ebb_w9$living_status <- car::recode(HRS_ebb_w9_ls$R9IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_ebb_w9$living_status <- labelled(HRS_ds_ebb_w9$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ebb9, echo=F}
vari <- HRS_ds_ebb_w9$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w9, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ebb9, echo=F, results='asis'}
kable(table(HRS_ebb_w9_ls$R9IWSTAT, HRS_ds_ebb_w9$living_status, useNA = "ifany"), align='c', caption ='R9IWSTAT vs living_status')
```

```{r importOPAL_ebb9, echo=F}
living_status <- HRS_ds_ebb_w9
save(living_status, file = "../RData/ebb_w9/living_status.RData")
rm(living_status)
```

### Wave 10  

#### Study-specific variable description

| **Name** | `R10IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-EBB-w10`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_ebb10, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w10_ls','HRS.HRS-EBB-w10', variables=list('R10IWSTAT', 'RADMONTH'), missings = TRUE)
```

```{r local_ebb10, echo=F}
HRS_ebb_w10_ls <- opal.execute(o,'HRS_ebb_w10_ls')
vari <- HRS_ebb_w10_ls$R10IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R10IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ebb_w10_ls, aes(factor(R10IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.



**R script:**

```{r harmo_ebb10}
HRS_ds_ebb_w10 <- tibble(id=HRS_ebb_w10_ls$id)
HRS_ds_ebb_w10$living_status <- car::recode(HRS_ebb_w10_ls$R10IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_ebb_w10$living_status <- labelled(HRS_ds_ebb_w10$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ebb10, echo=F}
vari <- HRS_ds_ebb_w10$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w10, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ebb10, echo=F, results='asis'}
kable(table(HRS_ebb_w10_ls$R10IWSTAT, HRS_ds_ebb_w10$living_status, useNA = "ifany"), align='c', caption ='R10IWSTAT vs living_status')
```

```{r importOPAL_ebb10, echo=F}
living_status <- HRS_ds_ebb_w10
save(living_status, file = "../RData/ebb_w10/living_status.RData")
rm(living_status)
```


### Wave 11  

#### Study-specific variable description

| **Name** | `R11IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-EBB-w11`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_ebb11, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w11_ls','HRS.HRS-EBB-w11', variables=list('R11IWSTAT'), missings = TRUE)
```

```{r local_ebb11, echo=F}
HRS_ebb_w11_ls <- opal.execute(o,'HRS_ebb_w11_ls')
vari <- HRS_ebb_w11_ls$R11IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R11IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ebb_w11_ls, aes(factor(R11IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.



**R script:**

```{r harmo_ebb11}
HRS_ds_ebb_w11 <- tibble(id=HRS_ebb_w11_ls$id)
HRS_ds_ebb_w11$living_status <- car::recode(HRS_ebb_w11_ls$R11IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_ebb_w11$living_status <- labelled(HRS_ds_ebb_w11$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ebb11, echo=F}
vari <- HRS_ds_ebb_w11$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w11, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ebb11, echo=F, results='asis'}
kable(table(HRS_ebb_w11_ls$R11IWSTAT, HRS_ds_ebb_w11$living_status, useNA = "ifany"), align='c', caption ='R11IWSTAT vs living_status')
```

```{r importOPAL_ebb11, echo=F}
living_status <- HRS_ds_ebb_w11
save(living_status, file = "../RData/ebb_w11/living_status.RData")
rm(living_status)
```

### Validation throughout waves

```{r valid_ws_ebb, echo=F}
dbb <- merge(HRS_ds_ebb_w7, HRS_ds_ebb_w8, by = "id", suffixes = c(".w7", ".w8"), all = T)
dbb <- merge(dbb, HRS_ds_ebb_w9, by = "id", all = T)
dbb <- merge(dbb, HRS_ds_ebb_w10, by = "id", suffixes = c(".w9", ".w10"), all = T)
dbb <- merge(dbb, HRS_ds_ebb_w11, by = "id", all = T)
dbb <- dbb[,-1]
dbb[dbb == 996] <- NA
names(dbb) <- c("w7", "w8", "w9", "w10", "w11")
v.dbb <- paste(dbb[, 1], dbb[, 2], dbb[, 3], dbb[, 4], dbb[, 5], sep = "")
f.dbb <- frq(v.dbb)[[1]][, c(1, 2, 4)]
kable(f.dbb)
```


## MBB

### Wave 10  

#### Study-specific variable description

| **Name** | `R10IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-MBB-w10`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |

```{r assign_mbb10, echo=F}
opal.assign.table.tibble(o, 'HRS_mbb_w10_ls','HRS.HRS-MBB-w10', variables=list('R10IWSTAT'), missings = TRUE)
```

```{r local_mbb10, echo=F}
HRS_mbb_w10_ls <- opal.execute(o,'HRS_mbb_w10_ls')
vari <- HRS_mbb_w10_ls$R10IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R10IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_mbb_w10_ls, aes(factor(R10IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")

```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.

**R script:**

```{r harmo_mbb10}
HRS_ds_mbb_w10 <- tibble(id=HRS_mbb_w10_ls$id)
HRS_ds_mbb_w10$living_status <- car::recode(HRS_mbb_w10_ls$R10IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_mbb_w10$living_status <- labelled(HRS_ds_mbb_w10$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_mbb10, echo=F}
vari <- HRS_ds_mbb_w10$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_mbb_w10, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_mbb10, echo=F, results='asis'}
kable(table(HRS_ebb_w11_ls$R11IWSTAT, HRS_ds_ebb_w11$living_status, useNA = "ifany"), align='c', caption ='R11IWSTAT vs living_status')
```

```{r importOPAL_mbb10, echo=F}
living_status <- HRS_ds_mbb_w10
save(living_status, file = "../RData/mbb_w10/living_status.RData")
rm(living_status)
```


### Wave 11  

#### Study-specific variable description

| **Name** | `R11IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-MBB-w11`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_mbb11, echo=F}
opal.assign.table.tibble(o, 'HRS_mbb_w11_ls','HRS.HRS-MBB-w11', variables=list('R11IWSTAT'), missings = TRUE)
```

```{r local_mbb11, echo=F}
HRS_mbb_w11_ls <- opal.execute(o,'HRS_mbb_w11_ls')
vari <- HRS_mbb_w11_ls$R11IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R11IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_mbb_w11_ls, aes(factor(R11IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.

**R script:**

```{r harmo_mbb11}
HRS_ds_mbb_w11 <- tibble(id=HRS_mbb_w11_ls$id)
HRS_ds_mbb_w11$living_status <- car::recode(HRS_mbb_w11_ls$R11IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_mbb_w11$living_status <- labelled(HRS_ds_mbb_w11$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_mbb11, echo=F}
vari <- HRS_ds_mbb_w11$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_mbb_w11, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_mbb11, echo=F, results='asis'}
kable(table(HRS_mbb_w11_ls$R11IWSTAT, HRS_ds_mbb_w11$living_status, useNA = "ifany"), align='c', caption ='R11IWSTAT vs living_status')
```

```{r importOPAL_mbb11, echo=F}
living_status <- HRS_ds_mbb_w11
save(living_status, file = "../RData/mbb_w11/living_status.RData")
rm(living_status)
```

### Validation throughout waves

```{r valid_ws_mbb, echo=F}
dbb <- merge(HRS_ds_mbb_w10, HRS_ds_mbb_w11, by = "id", suffixes = c(".w10", ".w11"), all = T)
dbb <- dbb[,-1]
dbb[dbb == 996] <- NA
names(dbb) <- c("w10", "w11")
v.dbb <- paste(dbb[, 1], dbb[, 2], sep = "")
f.dbb <- frq(v.dbb)[[1]][, c(1, 2, 4)]
kable(f.dbb)
```


# Quality estimation

Results in validations throughout waves show, in each population, that there are few people who 
died in some wave and dropped out afterwards. This issue was already present in the original HRS 
variable and we have not fixed it yet. Meanwhile, we should consider that a previous death prevails 
upon a subsequent dropout.

Moreover, we found two errors:

* HRS sub-sample, individual with "id" = "63063010", was alive in wave 1, died in wave 2, and alive in waves 3 to 11.
* AHEAD sub-sample, individual with "id" = "202147020", was alive in waves 2 to 9, died in wave 10, and alive in wave 11.

These errors have not been corrected yet.

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
