---
title: "Living Status"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup.r")
load("ID_issue_ls.Rdata")
ID_issue_ls$cohort <- substr(ID_issue_ls$athlos_id, 4,5)
ID_issue_ls$cohort <- car::recode(ID_issue_ls$cohort, "'01'='hrs'; '02'='ahead';  '03'='coda'; '04'='ebb'; '05'='mbb';
                            '06'='wb'")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/living_statusDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/living_statusDS.R')
```




# Data process

## HRS

### Wave 1 

#### Study-specific variable description

| **Name** | `R1IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-HRS-w1`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |

    
    
```{r assign_hrs1, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w1_ls','HRS.HRS-HRS-w1', variables=list('R1IWSTAT'), missings = TRUE)
HRS_hrs_w1_ls <- opal.execute(o,'HRS_hrs_w1_ls')
vari <- HRS_hrs_w1_ls$R1IWSTAT

```

```{r local_hrs1, echo=F}
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R1IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w1_ls, aes(factor(R1IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Interview Status") + ylab("Frequency")

```

#### Harmonisation algorithm

Values are recoded as follows:

* Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive)
* Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died)
* Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout)
* Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_hrs1}
HRS_ds_hrs_w1 <- tibble(id=HRS_hrs_w1_ls$id)
HRS_ds_hrs_w1$living_status <- car::recode(HRS_hrs_w1_ls$R1IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")

HRS_ds_hrs_w1$living_status <- labelled(HRS_ds_hrs_w1$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs1, echo=F}
vari <- HRS_ds_hrs_w1$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w1, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs1, echo=F, results='asis'}
kable(table(HRS_hrs_w1_ls$R1IWSTAT, HRS_ds_hrs_w1$living_status, useNA = "ifany"), align='c', caption ='R1IWSTAT vs living_status')
#newT <- full_join( HRS_hrs_w1_ls, HRS_ds_hrs_w1, by="id")
#flat_table(newT, living_status, R1IWSTAT)
```

```{r importOPAL_hrs1, echo=F}
living_status <- HRS_ds_hrs_w1
save(living_status, file = "../RData/hrs_w1/living_status.RData")
rm(living_status)
```


### Wave 2 

#### Study-specific variable description

| **Name** | `R2IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-HRS-w2`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_hrs2, echo=F}
opal.assign.table.tibble(o,'HRS_hrs_w2_ls','HRS.HRS-HRS-w2', variables=list('R2IWSTAT'), missings = TRUE)
```

```{r local_hrs2, echo=F}
HRS_hrs_w2_ls <- opal.execute(o,'HRS_hrs_w2_ls')
vari <- HRS_hrs_w2_ls$R2IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R2IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w2_ls, aes(factor(R2IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Interview Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows:

* Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive)
* Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died)
* Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout)
* Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r local_alg2, echo=F}
ids_issue_ls <- ID_issue_ls$id[which(ID_issue_ls$wave==2 & ID_issue_ls$cohort=='hrs')]
ids_death_w1 <- HRS_ds_hrs_w1$id[HRS_ds_hrs_w1$living_status == 1]

HRS_ds_hrs_w2 <- tibble(id=HRS_hrs_w2_ls$id)
HRS_ds_hrs_w2$living_status <- car::recode(HRS_hrs_w2_ls$R2IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_hrs_w2$living_status[HRS_ds_hrs_w2$id %in%  ids_death_w1] <- 1
HRS_ds_hrs_w2$living_status[which(HRS_ds_hrs_w2$id %in% ids_issue_ls)] <- 1
HRS_ds_hrs_w2$living_status <- labelled(HRS_ds_hrs_w2$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs2, echo=F}
vari <- HRS_ds_hrs_w2$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w2, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs2, echo=F, results='asis'}
kable(table(HRS_hrs_w2_ls$R2IWSTAT, HRS_ds_hrs_w2$living_status, useNA = "ifany"), align='c', caption ='R2IWSTAT vs living_status')
```

```{r importOPAL_hrs2, echo=F}
living_status <- HRS_ds_hrs_w2
save(living_status, file = "../RData/hrs_w2/living_status.RData")
rm(living_status)
```


### Wave 3 

#### Study-specific variable description

| **Name** | `R3IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-HRS-w3`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |



```{r assign_hrs3, echo=F}
opal.assign.table.tibble(o,'HRS_hrs_w3_ls','HRS.HRS-HRS-w3', variables=list('R3IWSTAT'), missings = TRUE)
```

```{r local_hrs3, echo=F}
HRS_hrs_w3_ls <- opal.execute(o,'HRS_hrs_w3_ls')
vari <- HRS_hrs_w3_ls$R3IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R3IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w3_ls, aes(factor(R3IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Interview Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows:

* Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive)
* Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died)
* Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout)
* Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_hrs3}
ids_issue_ls <- ID_issue_ls$id[which(ID_issue_ls$wave==3 & ID_issue_ls$cohort=='hrs')]
ids_death_w2 <- HRS_ds_hrs_w2$id[HRS_ds_hrs_w2$living_status == 1]

HRS_ds_hrs_w3 <- tibble(id=HRS_hrs_w3_ls$id)
HRS_ds_hrs_w3$living_status <- car::recode(HRS_hrs_w3_ls$R3IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_hrs_w3$living_status[HRS_ds_hrs_w3$id %in%  ids_death_w2] <- 1
HRS_ds_hrs_w3$living_status[which(HRS_ds_hrs_w3$id %in% ids_issue_ls)] <- 1
HRS_ds_hrs_w3$living_status <- labelled(HRS_ds_hrs_w3$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs3, echo=F}
vari <- HRS_ds_hrs_w3$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w3, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs3, echo=F, results='asis'}
kable(table(HRS_hrs_w3_ls$R3IWSTAT, HRS_ds_hrs_w3$living_status, useNA = "ifany"), align='c', caption ='R3IWSTAT vs living_status')
```


```{r importOPAL_hrs3, echo=F}
living_status <- HRS_ds_hrs_w3
save(living_status, file = "../RData/hrs_w3/living_status.RData")
rm(living_status)
```


### Wave 4 

#### Study-specific variable description

| **Name** | `R4IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-HRS-w4`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_hrs4, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w4_ls','HRS.HRS-HRS-w4',
                         variables=list('R4IWSTAT'), missings = TRUE)
```

```{r local_hrs4, echo=F}
HRS_hrs_w4_ls <- opal.execute(o,'HRS_hrs_w4_ls')
vari <- HRS_hrs_w4_ls$R4IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R4IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w4_ls, aes(factor(R4IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm

Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.

**R script:**

```{r harmo_hrs4}
ids_issue_ls <- ID_issue_ls$id[which(ID_issue_ls$wave==4 & ID_issue_ls$cohort=='hrs')]
ids_death_w3 <- HRS_ds_hrs_w3$id[HRS_ds_hrs_w3$living_status == 1]

HRS_ds_hrs_w4 <- tibble(id=HRS_hrs_w4_ls$id)
HRS_ds_hrs_w4$living_status <- car::recode(HRS_hrs_w4_ls$R4IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_hrs_w4$living_status[HRS_ds_hrs_w4$id %in%  ids_death_w3] <- 1
HRS_ds_hrs_w4$living_status[which(HRS_ds_hrs_w4$id %in% ids_issue_ls)] <- 1
HRS_ds_hrs_w4$living_status <- labelled(HRS_ds_hrs_w4$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs4, echo=F}
vari <- HRS_ds_hrs_w4$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w4, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs4, echo=F, results='asis'}
kable(table(HRS_hrs_w4_ls$R4IWSTAT, HRS_ds_hrs_w4$living_status, useNA = "ifany"), align='c', caption ='R4IWSTAT vs living_status')
```

```{r importOPAL_hrs4, echo=F}
living_status <- HRS_ds_hrs_w4
save(living_status, file = "../RData/hrs_w4/living_status.RData")
rm(living_status)
```


### Wave 5

#### Study-specific variable description

| **Name** | `R5IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-HRS-w5`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_hrs5, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w5_ls','HRS.HRS-HRS-w5',
                         variables=list('R5IWSTAT'), missings = TRUE)
```

```{r local_hrs5, echo=F}
HRS_hrs_w5_ls <- opal.execute(o,'HRS_hrs_w5_ls')
vari <- HRS_hrs_w5_ls$R5IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R5IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w5_ls, aes(factor(R5IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.



**R script:**

```{r harmo_hrs5}
ids_issue_ls <- ID_issue_ls$id[which(ID_issue_ls$wave==5 & ID_issue_ls$cohort=='hrs')]
ids_death_w4 <- HRS_ds_hrs_w4$id[which(HRS_ds_hrs_w4$living_status == 1)]

HRS_ds_hrs_w5 <- tibble(id=HRS_hrs_w5_ls$id)
HRS_ds_hrs_w5$living_status <- car::recode(HRS_hrs_w5_ls$R5IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_hrs_w5$living_status[which(HRS_ds_hrs_w5$id %in%  ids_death_w4)] <- 1
HRS_ds_hrs_w5$living_status[which(HRS_ds_hrs_w5$id %in% ids_issue_ls)] <- 1
HRS_ds_hrs_w5$living_status <- labelled(HRS_ds_hrs_w5$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs5, echo=F}
vari <- HRS_ds_hrs_w5$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w5, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs5, echo=F, results='asis'}
kable(table(HRS_hrs_w5_ls$R5IWSTAT, HRS_ds_hrs_w5$living_status, useNA = "ifany"), align='c', caption ='R5IWSTAT vs living_status')
```


```{r importOPAL_hrs5, echo=F}
living_status <- HRS_ds_hrs_w5
save(living_status, file = "../RData/hrs_w5/living_status.RData")
rm(living_status)
```






### Wave 6

#### Study-specific variable description



| **Name** | `R6IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-HRS-w6`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_hrs6, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w6_ls','HRS.HRS-HRS-w6',
                         variables=list('R6IWSTAT'), missings = TRUE)
```

```{r local_hrs6, echo=F}
HRS_hrs_w6_ls <- opal.execute(o,'HRS_hrs_w6_ls')
vari <- HRS_hrs_w6_ls$R6IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R6IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w6_ls, aes(factor(R6IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_hrs6}
ids_issue_ls <- ID_issue_ls$id[which(ID_issue_ls$wave==6 & ID_issue_ls$cohort=='hrs')]
ids_death_w5 <- HRS_ds_hrs_w5$id[HRS_ds_hrs_w5$living_status == 1]

HRS_ds_hrs_w6 <- tibble(id=HRS_hrs_w6_ls$id)
HRS_ds_hrs_w6$living_status <- car::recode(HRS_hrs_w6_ls$R6IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_hrs_w6$living_status[HRS_ds_hrs_w6$id %in%  ids_death_w5] <- 1
HRS_ds_hrs_w6$living_status[which(HRS_ds_hrs_w6$id %in% ids_issue_ls)] <- 1
HRS_ds_hrs_w6$living_status <- labelled(HRS_ds_hrs_w6$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs6, echo=F}
vari <- HRS_ds_hrs_w6$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w6, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs6, echo=F, results='asis'}
kable(table(HRS_hrs_w6_ls$R6IWSTAT, HRS_ds_hrs_w6$living_status, useNA = "ifany"), align='c', caption ='R6IWSTAT vs living_status')
```

```{r importOPAL_hrs6, echo=F}
living_status <- HRS_ds_hrs_w6
save(living_status, file = "../RData/hrs_w6/living_status.RData")
rm(living_status)
```


### Wave 7

#### Study-specific variable description

| **Name** | `R7IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-HRS-w7`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |



```{r assign_hrs7, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w7_ls','HRS.HRS-HRS-w7',
                         variables=list('R7IWSTAT'), missings = TRUE)
```

```{r local_hrs7, echo=F}
HRS_hrs_w7_ls <- opal.execute(o,'HRS_hrs_w7_ls')
vari <- HRS_hrs_w7_ls$R7IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R7IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w7_ls, aes(factor(R7IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_hrs7}
ids_issue_ls <- ID_issue_ls$id[which(ID_issue_ls$wave==7 & ID_issue_ls$cohort=='hrs')]
ids_death_w6 <- HRS_ds_hrs_w6$id[HRS_ds_hrs_w6$living_status == 1]

HRS_ds_hrs_w7 <- tibble(id=HRS_hrs_w7_ls$id)
HRS_ds_hrs_w7$living_status <- car::recode(HRS_hrs_w7_ls$R7IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_hrs_w7$living_status[HRS_ds_hrs_w7$id %in%  ids_death_w6] <- 1
HRS_ds_hrs_w7$living_status[which(HRS_ds_hrs_w7$id %in% ids_issue_ls)] <- 1
HRS_ds_hrs_w7$living_status <- labelled(HRS_ds_hrs_w7$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs7, echo=F}
vari <- HRS_ds_hrs_w7$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w7, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs7, echo=F, results='asis'}
kable(table(HRS_hrs_w7_ls$R7IWSTAT, HRS_ds_hrs_w7$living_status, useNA = "ifany"), align='c', caption ='R7IWSTAT vs living_status')
```

```{r importOPAL_hrs7, echo=F}
living_status <- HRS_ds_hrs_w7
save(living_status, file = "../RData/hrs_w7/living_status.RData")
rm(living_status)
```

### Wave 8

#### Study-specific variable description

| **Name** | `R8IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-HRS-w8`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_hrs8, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w8_ls','HRS.HRS-HRS-w8',
                         variables=list('R8IWSTAT'), missings = TRUE)
```

```{r local_hrs8, echo=F}
HRS_hrs_w8_ls <- opal.execute(o,'HRS_hrs_w8_ls')
vari <- HRS_hrs_w8_ls$R8IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R8IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w8_ls, aes(factor(R8IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.



**R script:**

```{r harmo_hrs8}
ids_issue_ls <- ID_issue_ls$id[which(ID_issue_ls$wave==8 & ID_issue_ls$cohort=='hrs')]
ids_death_w7 <- HRS_ds_hrs_w7$id[HRS_ds_hrs_w7$living_status == 1]

HRS_ds_hrs_w8 <- tibble(id=HRS_hrs_w8_ls$id)
HRS_ds_hrs_w8$living_status <- car::recode(HRS_hrs_w8_ls$R8IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_hrs_w8$living_status[HRS_ds_hrs_w8$id %in%  ids_death_w7] <- 1
HRS_ds_hrs_w8$living_status[which(HRS_ds_hrs_w8$id %in% ids_issue_ls)] <- 1
HRS_ds_hrs_w8$living_status <- labelled(HRS_ds_hrs_w8$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs8, echo=F}
vari <- HRS_ds_hrs_w8$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w8, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs8, echo=F, results='asis'}
kable(table(HRS_hrs_w8_ls$R8IWSTAT, HRS_ds_hrs_w8$living_status, useNA = "ifany"), align='c', caption ='R8IWSTAT vs living_status')
```

```{r importOPAL_hrs8, echo=F}
living_status <- HRS_ds_hrs_w8
save(living_status, file = "../RData/hrs_w8/living_status.RData")
rm(living_status)
```


### Wave 9

#### Study-specific variable description



| **Name** | `R9IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-HRS-w9`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_hrs9, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w9_ls','HRS.HRS-HRS-w9',
                         variables=list('R9IWSTAT'), missings = TRUE)
```

```{r local_hrs9, echo=F}
HRS_hrs_w9_ls <- opal.execute(o,'HRS_hrs_w9_ls')
vari <- HRS_hrs_w9_ls$R9IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R9IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w9_ls, aes(factor(R9IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_hrs9}
ids_issue_ls <- ID_issue_ls$id[which(ID_issue_ls$wave==9 & ID_issue_ls$cohort=='hrs')]
ids_death_w8 <- HRS_ds_hrs_w8$id[HRS_ds_hrs_w8$living_status == 1]

HRS_ds_hrs_w9 <- tibble(id=HRS_hrs_w9_ls$id)
HRS_ds_hrs_w9$living_status <- car::recode(HRS_hrs_w9_ls$R9IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_hrs_w9$living_status[HRS_ds_hrs_w9$id %in%  ids_death_w8] <- 1
HRS_ds_hrs_w9$living_status[which(HRS_ds_hrs_w9$id %in% ids_issue_ls)] <- 1
HRS_ds_hrs_w9$living_status <- labelled(HRS_ds_hrs_w9$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs9, echo=F}
vari <- HRS_ds_hrs_w9$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w9, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs9, echo=F, results='asis'}
kable(table(HRS_hrs_w9_ls$R9IWSTAT, HRS_ds_hrs_w9$living_status, useNA = "ifany"), align='c', caption ='R9IWSTAT vs living_status')
```

```{r importOPAL_hrs9, echo=F}
living_status <- HRS_ds_hrs_w9
save(living_status, file = "../RData/hrs_w9/living_status.RData")
rm(living_status)
```


### Wave 10

#### Study-specific variable description

| **Name** | `R10IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-HRS-w10`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_hrs10, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w10_ls','HRS.HRS-HRS-w10', variables=list('R10IWSTAT'), missings = TRUE)
```

```{r local_hrs10, echo=F}
HRS_hrs_w10_ls <- opal.execute(o,'HRS_hrs_w10_ls')
vari <- HRS_hrs_w10_ls$R10IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R10IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w10_ls, aes(factor(R10IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_hrs10}
ids_issue_ls <- ID_issue_ls$id[which(ID_issue_ls$wave==10 & ID_issue_ls$cohort=='hrs')]
ids_death_w9 <- HRS_ds_hrs_w9$id[HRS_ds_hrs_w9$living_status == 1]

HRS_ds_hrs_w10 <- tibble(id=HRS_hrs_w10_ls$id)
HRS_ds_hrs_w10$living_status <- car::recode(HRS_hrs_w10_ls$R10IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_hrs_w10$living_status[HRS_ds_hrs_w10$id %in%  ids_death_w9] <- 1
HRS_ds_hrs_w10$living_status[which(HRS_ds_hrs_w10$id %in% ids_issue_ls)] <- 1
HRS_ds_hrs_w10$living_status <- labelled(HRS_ds_hrs_w10$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs10, echo=F}
vari <- HRS_ds_hrs_w10$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w10, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs10, echo=F, results='asis'}
kable(table(HRS_hrs_w10_ls$R10IWSTAT, HRS_ds_hrs_w10$living_status, useNA = "ifany"), align='c', caption ='R10IWSTAT vs living_status')
```

```{r importOPAL_hrs10, echo=F}
living_status <- HRS_ds_hrs_w10
save(living_status, file = "../RData/hrs_w10/living_status.RData")
rm(living_status)
```


### Wave 11

#### Study-specific variable description

| **Name** | `R11IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-HRS-w11`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |



```{r assign_hrs11, echo=F}
opal.assign.table.tibble(o, 'HRS_hrs_w11_ls','HRS.HRS-HRS-w11',
                         variables=list('R11IWSTAT'), missings = TRUE)
```


```{r local_hrs11, echo=F}
HRS_hrs_w11_ls <- opal.execute(o,'HRS_hrs_w11_ls')
vari <- HRS_hrs_w11_ls$R11IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R11IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_hrs_w11_ls, aes(factor(R11IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_hrs11}
ids_issue_ls <- ID_issue_ls$id[which(ID_issue_ls$wave==11 & ID_issue_ls$cohort=='hrs')]
ids_death_w10 <- HRS_ds_hrs_w10$id[HRS_ds_hrs_w10$living_status == 1]

HRS_ds_hrs_w11 <- tibble(id=HRS_hrs_w11_ls$id)
HRS_ds_hrs_w11$living_status <- car::recode(HRS_hrs_w11_ls$R11IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_hrs_w11$living_status[HRS_ds_hrs_w11$id %in%  ids_death_w10] <- 1
HRS_ds_hrs_w11$living_status[which(HRS_ds_hrs_w11$id %in% ids_issue_ls)] <- 1
HRS_ds_hrs_w11$living_status <- labelled(HRS_ds_hrs_w11$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_hrs11, echo=F}
vari <- HRS_ds_hrs_w11$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_hrs_w11, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_hrs11, echo=F, results='asis'}
kable(table(HRS_hrs_w11_ls$R11IWSTAT, HRS_ds_hrs_w11$living_status, useNA = "ifany"), align='c', caption ='R11IWSTAT vs living_status')
```

```{r importOPAL_hrs11, echo=F}
living_status <- HRS_ds_hrs_w11
save(living_status, file = "../RData/hrs_w11/living_status.RData")
rm(living_status)
```

### Validation throughout waves

```{r valid_ws_hrs, echo=F}
dbb <- merge(HRS_ds_hrs_w1, HRS_ds_hrs_w2, by = "id", suffixes = c(".w1", ".w2"), all = T)
dbb <- merge(dbb, HRS_ds_hrs_w3, by = "id", all = T)
dbb <- merge(dbb, HRS_ds_hrs_w4, by = "id", suffixes = c(".w3", ".w4"), all = T)
dbb <- merge(dbb, HRS_ds_hrs_w5, by = "id", all = T)
dbb <- merge(dbb, HRS_ds_hrs_w6, by = "id", suffixes = c(".w5", ".w6"), all = T)
dbb <- merge(dbb, HRS_ds_hrs_w7, by = "id", all = T)
dbb <- merge(dbb, HRS_ds_hrs_w8, by = "id", suffixes = c(".w7", ".w8"), all = T)
dbb <- merge(dbb, HRS_ds_hrs_w9, by = "id", all = T)
dbb <- merge(dbb, HRS_ds_hrs_w10, by = "id", suffixes = c(".w9", ".w10"), all = T)
dbb <- merge(dbb, HRS_ds_hrs_w11, by = "id", all = T)
#dbb <- dbb[,-1]
dbb[dbb == 996] <- NA
names(dbb) <- c("id", "w1", "w2", "w3", "w4", "w5", "w6", "w7", "w8", "w9", "w10", "w11")
v.dbb <- paste(dbb[, 2], dbb[, 3], dbb[, 4], dbb[, 5], dbb[, 6], dbb[, 7], dbb[, 8], dbb[, 9], dbb[, 10], dbb[, 11], dbb[, 12], sep = "")
f.dbb <- frq(v.dbb)[[1]][, c(1, 2, 4)]
kable(f.dbb)
#kable(f.dbb[f.dbb[, 3] >= 0.3, ])
```


## AHEAD

### Wave 2 

#### Study-specific variable description

| **Name** | `R2IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-AHEAD-w2`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_ahead2, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w2_ls','HRS.HRS-AHEAD-w2', variables=list('R2IWSTAT'), missings = TRUE)
```

```{r local_ahead2, echo=F}
HRS_ahead_w2_ls <- opal.execute(o,'HRS_ahead_w2_ls')
vari <- HRS_ahead_w2_ls$R2IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R2IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w2_ls, aes(factor(R2IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_ahead2}
HRS_ds_ahead_w2 <- tibble(id=HRS_ahead_w2_ls$id)
HRS_ds_ahead_w2$living_status <- car::recode(HRS_ahead_w2_ls$R2IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_ahead_w2$living_status <- labelled(HRS_ds_ahead_w2$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead2, echo=F}
vari <- HRS_ds_ahead_w2$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w2, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead2, echo=F, results='asis'}
kable(table(HRS_ahead_w2_ls$R2IWSTAT, HRS_ds_ahead_w2$living_status, useNA = "ifany"), align='c', caption ='R2IWSTAT vs living_status')
```

```{r importOPAL_ahead2, echo=F}
living_status <- HRS_ds_ahead_w2
save(living_status, file = "../RData/ahead_w2/living_status.RData")
rm(living_status)
```


### Wave 3 

#### Study-specific variable description

| **Name** | `R3IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-AHEAD-w3`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_ahead3, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w3_ls','HRS.HRS-AHEAD-w3', variables=list('R3IWSTAT'), missings = TRUE)
```

```{r local_ahead3, echo=F}
HRS_ahead_w3_ls <- opal.execute(o,'HRS_ahead_w3_ls')
vari <- HRS_ahead_w3_ls$R3IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R3IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w3_ls, aes(factor(R3IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.



**R script:**

```{r harmo_ahead3}
ids_issue_ls <- ID_issue_ls$id[which(ID_issue_ls$wave==2 & ID_issue_ls$cohort=='ahead')]
ids_death_w2 <- HRS_ds_ahead_w2$id[HRS_ds_ahead_w2$living_status == 1]

HRS_ds_ahead_w3 <- tibble(id=HRS_ahead_w3_ls$id)
HRS_ds_ahead_w3$living_status <- car::recode(HRS_ahead_w3_ls$R3IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_ahead_w3$living_status[HRS_ds_ahead_w3$id %in%  ids_death_w2] <- 1
HRS_ds_ahead_w3$living_status[which(HRS_ds_ahead_w3$id %in% ids_issue_ls)] <- 1
HRS_ds_ahead_w3$living_status <- labelled(HRS_ds_ahead_w3$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead3, echo=F}
vari <- HRS_ds_ahead_w3$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w3, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead3, echo=F, results='asis'}
kable(table(HRS_ahead_w3_ls$R3IWSTAT, HRS_ds_ahead_w3$living_status, useNA = "ifany"), align='c', caption ='R3IWSTAT vs living_status')
```

```{r importOPAL_ahead3, echo=F}
living_status <- HRS_ds_ahead_w3
save(living_status, file = "../RData/ahead_w3/living_status.RData")
rm(living_status)
```


### Wave 4 

#### Study-specific variable description

| **Name** | `R4IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-AHEAD-w4`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_ahead4, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w4_ls','HRS.HRS-AHEAD-w4',
                         variables=list('R4IWSTAT'), missings = TRUE)
```

```{r local_ahead4, echo=F}
HRS_ahead_w4_ls <- opal.execute(o,'HRS_ahead_w4_ls')
vari <- HRS_ahead_w4_ls$R4IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R4IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w4_ls, aes(factor(R4IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_ahead4}
ids_issue_ls <- ID_issue_ls$id[which(ID_issue_ls$wave==3 & ID_issue_ls$cohort=='ahead')]
ids_death_w3 <- HRS_ds_ahead_w3$id[HRS_ds_ahead_w3$living_status == 1]

HRS_ds_ahead_w4 <- tibble(id=HRS_ahead_w4_ls$id)
HRS_ds_ahead_w4$living_status <- car::recode(HRS_ahead_w4_ls$R4IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_ahead_w4$living_status[HRS_ds_ahead_w4$id %in%  ids_death_w3] <- 1
HRS_ds_ahead_w4$living_status[which(HRS_ds_ahead_w4$id %in% ids_issue_ls)] <- 1
HRS_ds_ahead_w4$living_status <- labelled(HRS_ds_ahead_w4$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead4, echo=F}
vari <- HRS_ds_ahead_w4$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w4, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead4, echo=F, results='asis'}
kable(table(HRS_ahead_w4_ls$R4IWSTAT, HRS_ds_ahead_w4$living_status, useNA = "ifany"), align='c', caption ='R4IWSTAT vs living_status')
```


```{r importOPAL_ahead4, echo=F}
living_status <- HRS_ds_ahead_w4
save(living_status, file = "../RData/ahead_w4/living_status.RData")
rm(living_status)
```


### Wave 5 

#### Study-specific variable description

| **Name** | `R5IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-AHEAD-w5`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_ahead5, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w5_ls','HRS.HRS-AHEAD-w5',  variables=list('R5IWSTAT'), missings = TRUE)
```

```{r local_ahead5, echo=F}
HRS_ahead_w5_ls <- opal.execute(o,'HRS_ahead_w5_ls')
vari <- HRS_ahead_w5_ls$R5IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R5IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w5_ls, aes(factor(R5IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.



**R script:**

```{r harmo_ahead5}
ids_issue_ls <- ID_issue_ls$id[which(ID_issue_ls$wave==4 & ID_issue_ls$cohort=='ahead')]
ids_death_w4 <- HRS_ds_ahead_w4$id[HRS_ds_ahead_w4$living_status == 1]

HRS_ds_ahead_w5 <- tibble(id=HRS_ahead_w5_ls$id)
HRS_ds_ahead_w5$living_status <- car::recode(HRS_ahead_w5_ls$R5IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_ahead_w5$living_status[HRS_ds_ahead_w5$id %in%  ids_death_w4] <- 1
HRS_ds_ahead_w5$living_status[which(HRS_ds_ahead_w5$id %in% ids_issue_ls)] <- 1
HRS_ds_ahead_w5$living_status <- labelled(HRS_ds_ahead_w5$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead5, echo=F}
vari <- HRS_ds_ahead_w5$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w5, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead5, echo=F, results='asis'}
kable(table(HRS_ahead_w5_ls$R5IWSTAT, HRS_ds_ahead_w5$living_status, useNA = "ifany"), align='c', caption ='R5IWSTAT vs living_status')
```

```{r importOPAL_ahead5, echo=F}
living_status <- HRS_ds_ahead_w5
save(living_status, file = "../RData/ahead_w5/living_status.RData")
rm(living_status)
```



### Wave 6 

#### Study-specific variable description

| **Name** | `R6IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-AHEAD-w6`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_ahead6, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w6_ls','HRS.HRS-AHEAD-w6', variables=list('R6IWSTAT'), missings = TRUE)
```

```{r local_ahead6, echo=F}
HRS_ahead_w6_ls <- opal.execute(o,'HRS_ahead_w6_ls')
vari <- HRS_ahead_w6_ls$R6IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R6IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w6_ls, aes(factor(R6IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_ahead6}
ids_issue_ls <- ID_issue_ls$id[which(ID_issue_ls$wave==5 & ID_issue_ls$cohort=='ahead')]
ids_death_w5 <- HRS_ds_ahead_w5$id[HRS_ds_ahead_w5$living_status == 1]

HRS_ds_ahead_w6 <- tibble(id=HRS_ahead_w6_ls$id)
HRS_ds_ahead_w6$living_status <- car::recode(HRS_ahead_w6_ls$R6IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_ahead_w6$living_status[HRS_ds_ahead_w6$id %in%  ids_death_w5] <- 1
HRS_ds_ahead_w6$living_status[which(HRS_ds_ahead_w6$id %in% ids_issue_ls)] <- 1
HRS_ds_ahead_w6$living_status <- labelled(HRS_ds_ahead_w6$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead6, echo=F}
vari <- HRS_ds_ahead_w6$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w6, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead6, echo=F, results='asis'}
kable(table(HRS_ahead_w6_ls$R6IWSTAT, HRS_ds_ahead_w6$living_status, useNA = "ifany"), align='c', caption ='R6IWSTAT vs living_status')
```

```{r importOPAL_ahead6, echo=F}
living_status <- HRS_ds_ahead_w6
save(living_status, file = "../RData/ahead_w6/living_status.RData")
rm(living_status)
```



### Wave 7 

#### Study-specific variable description

| **Name** | `R7IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-AHEAD-w7`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_ahead7, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w7_ls','HRS.HRS-AHEAD-w7', variables=list('R7IWSTAT'), missings = TRUE)
```

```{r local_ahead7, echo=F}
HRS_ahead_w7_ls <- opal.execute(o,'HRS_ahead_w7_ls')
vari <- HRS_ahead_w7_ls$R7IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R7IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w7_ls, aes(factor(R7IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_ahead7}
ids_issue_ls <- ID_issue_ls$id[which(ID_issue_ls$wave==6 & ID_issue_ls$cohort=='ahead')]
ids_death_w6 <- HRS_ds_ahead_w6$id[HRS_ds_ahead_w6$living_status == 1]

HRS_ds_ahead_w7 <- tibble(id=HRS_ahead_w7_ls$id)
HRS_ds_ahead_w7$living_status <- car::recode(HRS_ahead_w7_ls$R7IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_ahead_w7$living_status[HRS_ds_ahead_w7$id %in%  ids_death_w6] <- 1
HRS_ds_ahead_w7$living_status[which(HRS_ds_ahead_w7$id %in% ids_issue_ls)] <- 1
HRS_ds_ahead_w7$living_status <- labelled(HRS_ds_ahead_w7$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead7, echo=F}
vari <- HRS_ds_ahead_w7$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w7, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead7, echo=F, results='asis'}
kable(table(HRS_ahead_w7_ls$R7IWSTAT, HRS_ds_ahead_w7$living_status, useNA = "ifany"), align='c', caption ='R7IWSTAT vs living_status')
```

```{r importOPAL_ahead7, echo=F}
living_status <- HRS_ds_ahead_w7
save(living_status, file = "../RData/ahead_w7/living_status.RData")
rm(living_status)
```




### Wave 8 

#### Study-specific variable description

| **Name** | `R8IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-AHEAD-w8`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_ahead8, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w8_ls','HRS.HRS-AHEAD-w8',  variables=list('R8IWSTAT'), missings = TRUE)
```

```{r local_ahead8, echo=F}
HRS_ahead_w8_ls <- opal.execute(o,'HRS_ahead_w8_ls')
vari <- HRS_ahead_w8_ls$R8IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R8IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w8_ls, aes(factor(R8IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_ahead8}
ids_issue_ls <- ID_issue_ls$id[which(ID_issue_ls$wave==7 & ID_issue_ls$cohort=='ahead')]
ids_death_w7 <- HRS_ds_ahead_w7$id[HRS_ds_ahead_w7$living_status == 1]

HRS_ds_ahead_w8 <- tibble(id=HRS_ahead_w8_ls$id)
HRS_ds_ahead_w8$living_status <- car::recode(HRS_ahead_w8_ls$R8IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_ahead_w8$living_status[HRS_ds_ahead_w8$id %in%  ids_death_w7] <- 1
HRS_ds_ahead_w8$living_status[which(HRS_ds_ahead_w8$id %in% ids_issue_ls)] <- 1
HRS_ds_ahead_w8$living_status <- labelled(HRS_ds_ahead_w8$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead8, echo=F}
vari <- HRS_ds_ahead_w8$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w8, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead8, echo=F, results='asis'}
kable(table(HRS_ahead_w8_ls$R8IWSTAT, HRS_ds_ahead_w8$living_status, useNA = "ifany"), align='c', caption ='R8IWSTAT vs living_status')
```


```{r importOPAL_ahead8, echo=F}
living_status <- HRS_ds_ahead_w8
save(living_status, file = "../RData/ahead_w8/living_status.RData")
rm(living_status)
```


### Wave 9 

#### Study-specific variable description

| **Name** | `R9IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-AHEAD-w9`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_ahead9, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w9_ls','HRS.HRS-AHEAD-w9', variables=list('R9IWSTAT'), missings = TRUE)
```

```{r local_ahead9, echo=F}
HRS_ahead_w9_ls <- opal.execute(o,'HRS_ahead_w9_ls')
vari <- HRS_ahead_w9_ls$R9IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R9IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w9_ls, aes(factor(R9IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.



**R script:**

```{r harmo_ahead9}
ids_issue_ls <- ID_issue_ls$id[which(ID_issue_ls$wave==8 & ID_issue_ls$cohort=='ahead')]
ids_death_w8 <- HRS_ds_ahead_w8$id[HRS_ds_ahead_w8$living_status == 1]

HRS_ds_ahead_w9 <- tibble(id=HRS_ahead_w9_ls$id)
HRS_ds_ahead_w9$living_status <- car::recode(HRS_ahead_w9_ls$R9IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_ahead_w9$living_status[HRS_ds_ahead_w9$id %in%  ids_death_w8] <- 1
HRS_ds_ahead_w9$living_status[which(HRS_ds_ahead_w9$id %in% ids_issue_ls)] <- 1
HRS_ds_ahead_w9$living_status <- labelled(HRS_ds_ahead_w9$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead9, echo=F}
vari <- HRS_ds_ahead_w9$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w9, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead9, echo=F, results='asis'}
kable(table(HRS_ahead_w9_ls$R9IWSTAT, HRS_ds_ahead_w9$living_status, useNA = "ifany"), align='c', caption ='R9IWSTAT vs living_status')
```


```{r importOPAL_ahead9, echo=F}
living_status <- HRS_ds_ahead_w9
save(living_status, file = "../RData/ahead_w9/living_status.RData")
rm(living_status)
```


### Wave 10 

#### Study-specific variable description

| **Name** | `R10IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-AHEAD-w10`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_ahead10, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w10_ls','HRS.HRS-AHEAD-w10', variables=list('R10IWSTAT'), missings = TRUE)
```

```{r local_ahead10, echo=F}
HRS_ahead_w10_ls <- opal.execute(o,'HRS_ahead_w10_ls')
vari <- HRS_ahead_w10_ls$R10IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R10IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w10_ls, aes(factor(R10IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_ahead10}
ids_issue_ls <- ID_issue_ls$id[which(ID_issue_ls$wave==9 & ID_issue_ls$cohort=='ahead')]
ids_death_w9 <- HRS_ds_ahead_w9$id[HRS_ds_ahead_w9$living_status == 1]

HRS_ds_ahead_w10 <- tibble(id=HRS_ahead_w10_ls$id)
HRS_ds_ahead_w10$living_status <- car::recode(HRS_ahead_w10_ls$R10IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_ahead_w10$living_status[HRS_ds_ahead_w10$id %in%  ids_death_w9] <- 1
HRS_ds_ahead_w10$living_status[which(HRS_ds_ahead_w10$id %in% ids_issue_ls)] <- 1
HRS_ds_ahead_w10$living_status <- labelled(HRS_ds_ahead_w10$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead10, echo=F}
vari <- HRS_ds_ahead_w10$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w10, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead10, echo=F, results='asis'}
kable(table(HRS_ahead_w10_ls$R10IWSTAT, HRS_ds_ahead_w10$living_status, useNA = "ifany"), align='c', caption ='R10IWSTAT vs living_status')
```

```{r importOPAL_ahead10, echo=F}
living_status <- HRS_ds_ahead_w10
save(living_status, file = "../RData/ahead_w10/living_status.RData")
rm(living_status)
```

### Wave 11 

#### Study-specific variable description

| **Name** | `R11IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-AHEAD-w11`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |

```{r assign_ahead11, echo=F}
opal.assign.table.tibble(o, 'HRS_ahead_w11_ls','HRS.HRS-AHEAD-w11', variables=list('R11IWSTAT'), missings = TRUE)
```

```{r local_ahead11, echo=F}
HRS_ahead_w11_ls <- opal.execute(o,'HRS_ahead_w11_ls')
vari <- HRS_ahead_w11_ls$R11IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R11IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ahead_w11_ls, aes(factor(R11IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_ahead11}
ids_issue_ls <- ID_issue_ls$id[which(ID_issue_ls$wave==10 & ID_issue_ls$cohort=='ahead')]
ids_death_w10 <- HRS_ds_ahead_w10$id[HRS_ds_ahead_w10$living_status == 1]

HRS_ds_ahead_w11 <- tibble(id=HRS_ahead_w11_ls$id)
HRS_ds_ahead_w11$living_status <- car::recode(HRS_ahead_w11_ls$R11IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_ahead_w11$living_status[HRS_ds_ahead_w11$id %in%  ids_death_w10] <- 1
HRS_ds_ahead_w11$living_status[which(HRS_ds_ahead_w11$id %in% ids_issue_ls)] <- 1
HRS_ds_ahead_w11$living_status <- labelled(HRS_ds_ahead_w11$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ahead11, echo=F}
vari <- HRS_ds_ahead_w11$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ahead_w11, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ahead11, echo=F, results='asis'}
kable(table(HRS_ahead_w11_ls$R11IWSTAT, HRS_ds_ahead_w11$living_status, useNA = "ifany"), align='c', caption ='R11IWSTAT vs living_status')
```

```{r importOPAL_ahead11, echo=F}
living_status <- HRS_ds_ahead_w11
save(living_status, file = "../RData/ahead_w11/living_status.RData")
rm(living_status)
```

### Validation throughout waves

```{r valid_ws_head, echo=F}
dbb <- merge(HRS_ds_ahead_w2, HRS_ds_ahead_w3, by = "id", suffixes = c(".w2", ".w3"), all = T)
dbb <- merge(dbb, HRS_ds_ahead_w4, by = "id", all = T)
dbb <- merge(dbb, HRS_ds_ahead_w5, by = "id", suffixes = c(".w4", ".w5"), all = T)
dbb <- merge(dbb, HRS_ds_ahead_w6, by = "id", all = T)
dbb <- merge(dbb, HRS_ds_ahead_w7, by = "id", suffixes = c(".w6", ".w7"), all = T)
dbb <- merge(dbb, HRS_ds_ahead_w8, by = "id", all = T)
dbb <- merge(dbb, HRS_ds_ahead_w9, by = "id", suffixes = c(".w8", ".w9"), all = T)
dbb <- merge(dbb, HRS_ds_ahead_w10, by = "id", all = T)
dbb <- merge(dbb, HRS_ds_ahead_w11, by = "id", suffixes = c(".w10", ".w11"), all = T)
dbb <- dbb[,-1]
dbb[dbb == 996] <- NA
names(dbb) <- c("w2", "w3", "w4", "w5", "w6", "w7", "w8", "w9", "w10", "w11")
v.dbb <- paste(dbb[, 1], dbb[, 2], dbb[, 3], dbb[, 4], dbb[, 5], dbb[, 6], dbb[, 7], dbb[, 8], dbb[, 9], dbb[, 10], sep = "")
f.dbb <- frq(v.dbb)[[1]][, c(1, 2, 4)]
kable(f.dbb)
```


## CODA

### Wave 4 

#### Study-specific variable description

| **Name** | `R4IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-CODA-w4`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |

```{r assign_coda4, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w4_ls','HRS.HRS-CODA-w4', variables=list('R4IWSTAT'), missings = TRUE)
```

```{r local_coda4, echo=F}
HRS_coda_w4_ls <- opal.execute(o,'HRS_coda_w4_ls')
vari <- HRS_coda_w4_ls$R4IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R4IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w4_ls, aes(factor(R4IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")

```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.

**R script:**

```{r harmo_coda4}
HRS_ds_coda_w4 <- tibble(id=HRS_coda_w4_ls$id)
HRS_ds_coda_w4$living_status <- car::recode(HRS_coda_w4_ls$R4IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_coda_w4$living_status <- labelled(HRS_ds_coda_w4$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda4, echo=F}
vari <- HRS_ds_coda_w4$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w4, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_coda4, echo=F, results='asis'}
kable(table(HRS_coda_w4_ls$R4IWSTAT, HRS_ds_coda_w4$living_status, useNA = "ifany"), align='c', caption ='R4IWSTAT vs living_status')
```

```{r importOPAL_coda4, echo=F}
living_status <- HRS_ds_coda_w4
save(living_status, file = "../RData/coda_w4/living_status.RData")
rm(living_status)
```


### Wave 5 

#### Study-specific variable description

| **Name** | `R5IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-CODA-w5`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |

```{r assign_coda5, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w5_ls','HRS.HRS-CODA-w5', variables=list('R5IWSTAT'), missings = TRUE)
```

```{r local_coda5, echo=F}
HRS_coda_w5_ls <- opal.execute(o,'HRS_coda_w5_ls')
vari <- HRS_coda_w5_ls$R5IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R5IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w5_ls, aes(factor(R5IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_coda5}
ids_issue_ls <- ID_issue_ls$id[which(ID_issue_ls$wave==2 & ID_issue_ls$cohort=='coda')]
ids_death_w4 <- HRS_ds_coda_w4$id[HRS_ds_coda_w4$living_status == 1]

HRS_ds_coda_w5 <- tibble(id=HRS_coda_w5_ls$id)
HRS_ds_coda_w5$living_status <- car::recode(HRS_coda_w5_ls$R5IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_coda_w5$living_status[HRS_ds_coda_w5$id %in%  ids_death_w4] <- 1
HRS_ds_coda_w5$living_status[which(HRS_ds_coda_w5$id %in% ids_issue_ls)] <- 1
HRS_ds_coda_w5$living_status <- labelled(HRS_ds_coda_w5$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda5, echo=F}
vari <- HRS_ds_coda_w5$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w5, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_coda5, echo=F, results='asis'}
kable(table(HRS_coda_w5_ls$R5IWSTAT, HRS_ds_coda_w5$living_status, useNA = "ifany"), align='c', caption ='R5IWSTAT vs living_status')
```

```{r importOPAL_coda5, echo=F}
living_status <- HRS_ds_coda_w5
save(living_status, file = "../RData/coda_w5/living_status.RData")
rm(living_status)
```


### Wave 6 

#### Study-specific variable description

| **Name** | `R6IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-CODA-w6`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_coda6, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w6_ls','HRS.HRS-CODA-w6', variables=list('R6IWSTAT'), missings = TRUE)
```

```{r local_coda6, echo=F}
HRS_coda_w6_ls <- opal.execute(o,'HRS_coda_w6_ls')
vari <- HRS_coda_w6_ls$R6IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R6IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w6_ls, aes(factor(R6IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_coda6}
ids_issue_ls <- ID_issue_ls$id[which(ID_issue_ls$wave==3 & ID_issue_ls$cohort=='coda')]
ids_death_w5 <- HRS_ds_coda_w5$id[HRS_ds_coda_w5$living_status == 1]

HRS_ds_coda_w6 <- tibble(id=HRS_coda_w6_ls$id)
HRS_ds_coda_w6$living_status <- car::recode(HRS_coda_w6_ls$R6IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_coda_w6$living_status[HRS_ds_coda_w6$id %in%  ids_death_w5] <- 1
HRS_ds_coda_w6$living_status[which(HRS_ds_coda_w6$id %in% ids_issue_ls)] <- 1
HRS_ds_coda_w6$living_status <- labelled(HRS_ds_coda_w6$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda6, echo=F}
vari <- HRS_ds_coda_w6$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w6, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_coda6, echo=F, results='asis'}
kable(table(HRS_coda_w6_ls$R6IWSTAT, HRS_ds_coda_w6$living_status, useNA = "ifany"), align='c', caption ='R6IWSTAT vs living_status')
```

```{r importOPAL_coda6, echo=F}
living_status <- HRS_ds_coda_w6
save(living_status, file = "../RData/coda_w6/living_status.RData")
rm(living_status)
```


### Wave 7 

#### Study-specific variable description

| **Name** | `R7IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-CODA-w7`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |

```{r assign_coda7, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w7_ls','HRS.HRS-CODA-w7', variables=list('R7IWSTAT'), missings = TRUE)
```

```{r local_coda7, echo=F}
HRS_coda_w7_ls <- opal.execute(o,'HRS_coda_w7_ls')
vari <- HRS_coda_w7_ls$R7IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R7IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w7_ls, aes(factor(R7IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_coda7}
ids_issue_ls <- ID_issue_ls$id[which(ID_issue_ls$wave==4 & ID_issue_ls$cohort=='coda')]
ids_death_w6 <- HRS_ds_coda_w6$id[HRS_ds_coda_w6$living_status == 1]

HRS_ds_coda_w7 <- tibble(id=HRS_coda_w7_ls$id)
HRS_ds_coda_w7$living_status <- car::recode(HRS_coda_w7_ls$R7IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_coda_w7$living_status[HRS_ds_coda_w7$id %in%  ids_death_w6] <- 1
HRS_ds_coda_w7$living_status[which(HRS_ds_coda_w7$id %in% ids_issue_ls)] <- 1
HRS_ds_coda_w7$living_status <- labelled(HRS_ds_coda_w7$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_coda7, echo=F}
vari <- HRS_ds_coda_w7$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w7, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_coda7, echo=F, results='asis'}
kable(table(HRS_coda_w7_ls$R7IWSTAT, HRS_ds_coda_w7$living_status, useNA = "ifany"), align='c', caption ='R7IWSTAT vs living_status')
```

```{r importOPAL_coda7, echo=F}
living_status <- HRS_ds_coda_w7
save(living_status, file = "../RData/coda_w7/living_status.RData")
rm(living_status)
```


### Wave 8 

#### Study-specific variable description

| **Name** | `R8IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-CODA-w8`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_coda8, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w8_ls','HRS.HRS-CODA-w8',
                         variables=list('R8IWSTAT'), missings = TRUE)
```

```{r local_coda8, echo=F}
HRS_coda_w8_ls <- opal.execute(o,'HRS_coda_w8_ls')
vari <- HRS_coda_w8_ls$R8IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R8IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w8_ls, aes(factor(R8IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_coda8}
ids_death_w7 <- HRS_ds_coda_w7$id[HRS_ds_coda_w7$living_status == 1]

HRS_ds_coda_w8 <- tibble(id=HRS_coda_w8_ls$id)
HRS_ds_coda_w8$living_status <- car::recode(HRS_coda_w8_ls$R8IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_coda_w8$living_status[HRS_ds_coda_w8$id %in%  ids_death_w7] <- 1
HRS_ds_coda_w8$living_status <- labelled(HRS_ds_coda_w8$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda8, echo=F}
vari <- HRS_ds_coda_w8$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w8, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_coda8, echo=F, results='asis'}
kable(table(HRS_coda_w8_ls$R8IWSTAT, HRS_ds_coda_w8$living_status, useNA = "ifany"), align='c', caption ='R8IWSTAT vs living_status')
```

```{r importOPAL_coda8, echo=F}
living_status <- HRS_ds_coda_w8
save(living_status, file = "../RData/coda_w8/living_status.RData")
rm(living_status)
```


### Wave 9 

#### Study-specific variable description

| **Name** | `R9IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-CODA-w9`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_coda9, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w9_ls','HRS.HRS-CODA-w9', variables=list('R9IWSTAT'), missings = TRUE)
```

```{r local_coda9, echo=F}
HRS_coda_w9_ls <- opal.execute(o,'HRS_coda_w9_ls')
vari <- HRS_coda_w9_ls$R9IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R9IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w9_ls, aes(factor(R9IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_coda9}
ids_issue_ls <- ID_issue_ls$id[which(ID_issue_ls$wave==6 & ID_issue_ls$cohort=='coda')]
ids_death_w8 <- HRS_ds_coda_w8$id[HRS_ds_coda_w8$living_status == 1]

HRS_ds_coda_w9 <- tibble(id=HRS_coda_w9_ls$id)
HRS_ds_coda_w9$living_status <- car::recode(HRS_coda_w9_ls$R9IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_coda_w9$living_status[HRS_ds_coda_w9$id %in%  ids_death_w8] <- 1
HRS_ds_coda_w9$living_status[which(HRS_ds_coda_w9$id %in% ids_issue_ls)] <- 1
HRS_ds_coda_w9$living_status <- labelled(HRS_ds_coda_w9$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda9, echo=F}
vari <- HRS_ds_coda_w9$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w9, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_coda9, echo=F, results='asis'}
kable(table(HRS_coda_w9_ls$R9IWSTAT, HRS_ds_coda_w9$living_status, useNA = "ifany"), align='c', caption ='R9IWSTAT vs living_status')
```

```{r importOPAL_coda9, echo=F}
living_status <- HRS_ds_coda_w9
save(living_status, file = "../RData/coda_w9/living_status.RData")
rm(living_status)
```

### Wave 10 

#### Study-specific variable description

| **Name** | `R10IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-CODA-w10`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_coda10, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w10_ls','HRS.HRS-CODA-w10', variables=list('R10IWSTAT'), missings = TRUE)
```

```{r local_coda10, echo=F}
HRS_coda_w10_ls <- opal.execute(o,'HRS_coda_w10_ls')
vari <- HRS_coda_w10_ls$R10IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R10IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w10_ls, aes(factor(R10IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_coda10}
ids_issue_ls <- ID_issue_ls$id[which(ID_issue_ls$wave==7 & ID_issue_ls$cohort=='coda')]
ids_death_w9 <- HRS_ds_coda_w9$id[HRS_ds_coda_w9$living_status == 1]

HRS_ds_coda_w10 <- tibble(id=HRS_coda_w10_ls$id)
HRS_ds_coda_w10$living_status <- car::recode(HRS_coda_w10_ls$R10IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_coda_w10$living_status[HRS_ds_coda_w10$id %in%  ids_death_w9] <- 1
HRS_ds_coda_w10$living_status[which(HRS_ds_coda_w10$id %in% ids_issue_ls)] <- 1
HRS_ds_coda_w10$living_status <- labelled(HRS_ds_coda_w10$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda10, echo=F}
vari <- HRS_ds_coda_w10$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w10, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_coda10, echo=F, results='asis'}
kable(table(HRS_coda_w10_ls$R10IWSTAT, HRS_ds_coda_w10$living_status, useNA = "ifany"), align='c', caption ='R10IWSTAT vs living_status')
```

```{r importOPAL_coda10, echo=F}
living_status <- HRS_ds_coda_w10
save(living_status, file = "../RData/coda_w10/living_status.RData")
rm(living_status)
```


### Wave 11 

#### Study-specific variable description

| **Name** | `R11IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-CODA-w11`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_coda11, echo=F}
opal.assign.table.tibble(o, 'HRS_coda_w11_ls','HRS.HRS-CODA-w11', variables=list('R11IWSTAT'), missings = TRUE)
```

```{r local_coda11, echo=F}
HRS_coda_w11_ls <- opal.execute(o,'HRS_coda_w11_ls')
vari <- HRS_coda_w11_ls$R11IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R11IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_coda_w11_ls, aes(factor(R11IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_coda11}
ids_death_w10 <- HRS_ds_coda_w10$id[HRS_ds_coda_w10$living_status == 1]

HRS_ds_coda_w11 <- tibble(id=HRS_coda_w11_ls$id)
HRS_ds_coda_w11$living_status <- car::recode(HRS_coda_w11_ls$R11IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_coda_w11$living_status[HRS_ds_coda_w11$id %in%  ids_death_w10] <- 1
HRS_ds_coda_w11$living_status <- labelled(HRS_ds_coda_w11$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_coda11, echo=F}
vari <- HRS_ds_coda_w11$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_coda_w11, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_coda11, echo=F, results='asis'}
kable(table(HRS_coda_w11_ls$R11IWSTAT, HRS_ds_coda_w11$living_status, useNA = "ifany"), align='c', caption ='R11IWSTAT vs living_status')
```

```{r importOPAL_coda11, echo=F}
living_status <- HRS_ds_coda_w11
save(living_status, file = "../RData/coda_w11/living_status.RData")
rm(living_status)
```

### Validation throughout waves

```{r valid_ws_coda, echo=F}
dbb <- merge(HRS_ds_coda_w4, HRS_ds_coda_w5, by = "id", suffixes = c(".w4", ".w5"), all = T)
dbb <- merge(dbb, HRS_ds_coda_w6, by = "id", all = T)
dbb <- merge(dbb, HRS_ds_coda_w7, by = "id", suffixes = c(".w6", ".w7"), all = T)
dbb <- merge(dbb, HRS_ds_coda_w8, by = "id", all = T)
dbb <- merge(dbb, HRS_ds_coda_w9, by = "id", suffixes = c(".w8", ".w9"), all = T)
dbb <- merge(dbb, HRS_ds_coda_w10, by = "id", all = T)
dbb <- merge(dbb, HRS_ds_coda_w11, by = "id", suffixes = c(".w10", ".w11"), all = T)
dbb <- dbb[,-1]
dbb[dbb == 996] <- NA
names(dbb) <- c("w4", "w5", "w6", "w7", "w8", "w9", "w10", "w11")
v.dbb <- paste(dbb[, 1], dbb[, 2], dbb[, 3], dbb[, 4], dbb[, 5], dbb[, 6], dbb[, 7], dbb[, 8], sep = "")
f.dbb <- frq(v.dbb)[[1]][, c(1, 2, 4)]
kable(f.dbb)
```


## WB

### Wave 4  

#### Study-specific variable description

| **Name** | `R4IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-WB-w4`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |

```{r assign_wb4, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w4_ls','HRS.HRS-WB-w4', variables=list('R4IWSTAT'), missings = TRUE)
```

```{r local_wb4, echo=F}
HRS_wb_w4_ls <- opal.execute(o,'HRS_wb_w4_ls')
vari <- HRS_wb_w4_ls$R4IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R4IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w4_ls, aes(factor(R4IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")

```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.

**R script:**

```{r harmo_wb4}
HRS_ds_wb_w4 <- tibble(id=HRS_wb_w4_ls$id)
HRS_ds_wb_w4$living_status <- car::recode(HRS_wb_w4_ls$R4IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_wb_w4$living_status <- labelled(HRS_ds_wb_w4$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb4, echo=F}
vari <- HRS_ds_wb_w4$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w4, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_wb4, echo=F, results='asis'}
kable(table(HRS_wb_w4_ls$R4IWSTAT, HRS_ds_wb_w4$living_status, useNA = "ifany"), align='c', caption ='R4IWSTAT vs living_status')
```

```{r importOPAL_wb4, echo=F}
living_status <- HRS_ds_wb_w4
save(living_status, file = "../RData/wb_w4/living_status.RData")
rm(living_status)
```


### Wave 5  

#### Study-specific variable description

| **Name** | `R5IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-WB-w5`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_wb5, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w5_ls','HRS.HRS-WB-w5', variables=list('R5IWSTAT'), missings = TRUE)
```

```{r local_wb5, echo=F}
HRS_wb_w5_ls <- opal.execute(o,'HRS_wb_w5_ls')
vari <- HRS_wb_w5_ls$R5IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R5IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w5_ls, aes(factor(R5IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_wb5}
ids_death_w4 <- HRS_ds_wb_w4$id[HRS_ds_wb_w4$living_status == 1]

HRS_ds_wb_w5 <- tibble(id=HRS_wb_w5_ls$id)
HRS_ds_wb_w5$living_status <- car::recode(HRS_wb_w5_ls$R5IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_wb_w5$living_status[HRS_ds_wb_w5$id %in%  ids_death_w4] <- 1
HRS_ds_wb_w5$living_status <- labelled(HRS_ds_wb_w5$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_wb5, echo=F}
vari <- HRS_ds_wb_w5$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w5, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_wb5, echo=F, results='asis'}
kable(table(HRS_wb_w5_ls$R5IWSTAT, HRS_ds_wb_w5$living_status, useNA = "ifany"), align='c', caption ='R5IWSTAT vs living_status')
```

```{r importOPAL_wb5, echo=F}
living_status <- HRS_ds_wb_w5
save(living_status, file = "../RData/wb_w5/living_status.RData")
rm(living_status)
```


### Wave 6  

#### Study-specific variable description

| **Name** | `R6IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-WB-w6`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_wb6, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w6_ls','HRS.HRS-WB-w6', variables=list('R6IWSTAT'), missings = TRUE)
```

```{r local_wb6, echo=F}
HRS_wb_w6_ls <- opal.execute(o,'HRS_wb_w6_ls')
vari <- HRS_wb_w6_ls$R6IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R6IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w6_ls, aes(factor(R6IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.

**R script:**

```{r harmo_wb6}
ids_issue_ls <- ID_issue_ls$id[which(ID_issue_ls$wave==3 & ID_issue_ls$cohort=='wb')]
ids_death_w5 <- HRS_ds_wb_w5$id[HRS_ds_wb_w5$living_status == 1]

HRS_ds_wb_w6 <- tibble(id=HRS_wb_w6_ls$id)
HRS_ds_wb_w6$living_status <- car::recode(HRS_wb_w6_ls$R6IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_wb_w6$living_status[HRS_ds_wb_w6$id %in%  ids_death_w5] <- 1
HRS_ds_wb_w6$living_status[which(HRS_ds_wb_w6$id %in% ids_issue_ls)] <- 1
HRS_ds_wb_w6$living_status <- labelled(HRS_ds_wb_w6$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_wb6, echo=F}
vari <- HRS_ds_wb_w6$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w6, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_wb6, echo=F, results='asis'}
kable(table(HRS_wb_w6_ls$R6IWSTAT, HRS_ds_wb_w6$living_status, useNA = "ifany"), align='c', caption ='R6IWSTAT vs living_status')
```

```{r importOPAL_wb6, echo=F}
living_status <- HRS_ds_wb_w6
save(living_status, file = "../RData/wb_w6/living_status.RData")
rm(living_status)
```


### Wave 7  

#### Study-specific variable description

| **Name** | `R7IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-WB-w7`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_wb7, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w7_ls','HRS.HRS-WB-w7', variables=list('R7IWSTAT'), missings = TRUE)
```

```{r local_wb7, echo=F}
HRS_wb_w7_ls <- opal.execute(o,'HRS_wb_w7_ls')
vari <- HRS_wb_w7_ls$R7IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R7IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w7_ls, aes(factor(R7IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_wb7}
ids_issue_ls <- ID_issue_ls$id[which(ID_issue_ls$wave==4 & ID_issue_ls$cohort=='wb')]
ids_death_w6 <- HRS_ds_wb_w6$id[HRS_ds_wb_w6$living_status == 1]

HRS_ds_wb_w7 <- tibble(id=HRS_wb_w7_ls$id)
HRS_ds_wb_w7$living_status <- car::recode(HRS_wb_w7_ls$R7IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_wb_w7$living_status[HRS_ds_wb_w7$id %in%  ids_death_w6] <- 1
HRS_ds_wb_w7$living_status[which(HRS_ds_wb_w7$id %in% ids_issue_ls)] <- 1
HRS_ds_wb_w7$living_status <- labelled(HRS_ds_wb_w7$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb7, echo=F}
vari <- HRS_ds_wb_w7$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w7, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_wb7, echo=F, results='asis'}
kable(table(HRS_wb_w7_ls$R7IWSTAT, HRS_ds_wb_w7$living_status, useNA = "ifany"), align='c', caption ='R7IWSTAT vs living_status')
```

```{r importOPAL_wb7, echo=F}
living_status <- HRS_ds_wb_w7
save(living_status, file = "../RData/wb_w7/living_status.RData")
rm(living_status)
```



### Wave 8  

#### Study-specific variable description

| **Name** | `R8IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-WB-w8`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_wb8, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w8_ls','HRS.HRS-WB-w8', variables=list('R8IWSTAT'), missings = TRUE)
```

```{r local_wb8, echo=F}
HRS_wb_w8_ls <- opal.execute(o,'HRS_wb_w8_ls')
vari <- HRS_wb_w8_ls$R8IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R8IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w8_ls, aes(factor(R8IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_wb8}
ids_issue_ls <- ID_issue_ls$id[which(ID_issue_ls$wave==5 & ID_issue_ls$cohort=='wb')]
ids_death_w7 <- HRS_ds_wb_w7$id[HRS_ds_wb_w7$living_status == 1]

HRS_ds_wb_w8 <- tibble(id=HRS_wb_w8_ls$id)
HRS_ds_wb_w8$living_status <- car::recode(HRS_wb_w8_ls$R8IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_wb_w8$living_status[HRS_ds_wb_w8$id %in%  ids_death_w7] <- 1
HRS_ds_wb_w8$living_status[which(HRS_ds_wb_w8$id %in% ids_issue_ls)] <- 1
HRS_ds_wb_w8$living_status <- labelled(HRS_ds_wb_w8$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_wb8, echo=F}
vari <- HRS_ds_wb_w8$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w8, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_wb8, echo=F, results='asis'}
kable(table(HRS_wb_w8_ls$R8IWSTAT, HRS_ds_wb_w8$living_status, useNA = "ifany"), align='c', caption ='R8IWSTAT vs living_status')
```

```{r importOPAL_wb8, echo=F}
living_status <- HRS_ds_wb_w8
save(living_status, file = "../RData/wb_w8/living_status.RData")
rm(living_status)
```



### Wave 9  

#### Study-specific variable description

| **Name** | `R9IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-WB-w9`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_wb9, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w9_ls','HRS.HRS-WB-w9', variables=list('R9IWSTAT'), missings = TRUE)
```

```{r local_wb9, echo=F}
HRS_wb_w9_ls <- opal.execute(o,'HRS_wb_w9_ls')
vari <- HRS_wb_w9_ls$R9IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R9IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w9_ls, aes(factor(R9IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_wb9}
ids_issue_ls <- ID_issue_ls$id[which(ID_issue_ls$wave==6 & ID_issue_ls$cohort=='wb')]
ids_death_w8 <- HRS_ds_wb_w8$id[HRS_ds_wb_w8$living_status == 1]

HRS_ds_wb_w9 <- tibble(id=HRS_wb_w9_ls$id)
HRS_ds_wb_w9$living_status <- car::recode(HRS_wb_w9_ls$R9IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_wb_w9$living_status[HRS_ds_wb_w9$id %in%  ids_death_w8] <- 1
HRS_ds_wb_w9$living_status[which(HRS_ds_wb_w9$id %in% ids_issue_ls)] <- 1
HRS_ds_wb_w9$living_status <- labelled(HRS_ds_wb_w9$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb9, echo=F}
vari <- HRS_ds_wb_w9$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w9, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_wb9, echo=F, results='asis'}
kable(table(HRS_wb_w9_ls$R9IWSTAT, HRS_ds_wb_w9$living_status, useNA = "ifany"), align='c', caption ='R9IWSTAT vs living_status')
```

```{r importOPAL_wb9, echo=F}
living_status <- HRS_ds_wb_w9
save(living_status, file = "../RData/wb_w9/living_status.RData")
rm(living_status)
```



### Wave 10  

#### Study-specific variable description

| **Name** | `R10IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-WB-w10`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_wb10, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w10_ls','HRS.HRS-WB-w10', variables=list('R10IWSTAT'), missings = TRUE)
```

```{r local_wb10, echo=F}
HRS_wb_w10_ls <- opal.execute(o,'HRS_wb_w10_ls')
vari <- HRS_wb_w10_ls$R10IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R10IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w10_ls, aes(factor(R10IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_wb10}
ids_issue_ls <- ID_issue_ls$id[which(ID_issue_ls$wave==7 & ID_issue_ls$cohort=='wb')]
ids_death_w9 <- HRS_ds_wb_w9$id[HRS_ds_wb_w9$living_status == 1]

HRS_ds_wb_w10 <- tibble(id=HRS_wb_w10_ls$id)
HRS_ds_wb_w10$living_status <- car::recode(HRS_wb_w10_ls$R10IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_wb_w10$living_status[HRS_ds_wb_w10$id %in%  ids_death_w9] <- 1
HRS_ds_wb_w10$living_status[which(HRS_ds_wb_w10$id %in% ids_issue_ls)] <- 1
HRS_ds_wb_w10$living_status <- labelled(HRS_ds_wb_w10$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb10, echo=F}
vari <- HRS_ds_wb_w10$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w10, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_wb10, echo=F, results='asis'}
kable(table(HRS_wb_w10_ls$R10IWSTAT, HRS_ds_wb_w10$living_status, useNA = "ifany"), align='c', caption ='R10IWSTAT vs living_status')
```

```{r importOPAL_wb10, echo=F}
living_status <- HRS_ds_wb_w10
save(living_status, file = "../RData/wb_w10/living_status.RData")
rm(living_status)
```


### Wave 11  

#### Study-specific variable description

| **Name** | `R11IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-WB-w11`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_wb11, echo=F}
opal.assign.table.tibble(o, 'HRS_wb_w11_ls','HRS.HRS-WB-w11', variables=list('R11IWSTAT'), missings = TRUE)
```

```{r local_wb11, echo=F}
HRS_wb_w11_ls <- opal.execute(o,'HRS_wb_w11_ls')
vari <- HRS_wb_w11_ls$R11IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R11IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_wb_w11_ls, aes(factor(R11IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.



**R script:**

```{r harmo_wb11}
ids_death_w10 <- HRS_ds_wb_w10$id[HRS_ds_wb_w10$living_status == 1]

HRS_ds_wb_w11 <- tibble(id=HRS_wb_w11_ls$id)
HRS_ds_wb_w11$living_status <- car::recode(HRS_wb_w11_ls$R11IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_wb_w11$living_status[HRS_ds_wb_w11$id %in%  ids_death_w10] <- 1
HRS_ds_wb_w11$living_status <- labelled(HRS_ds_wb_w11$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_wb11, echo=F}
vari <- HRS_ds_wb_w11$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_wb_w11, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_wb11, echo=F, results='asis'}
kable(table(HRS_wb_w11_ls$R11IWSTAT, HRS_ds_wb_w11$living_status, useNA = "ifany"), align='c', caption ='R11IWSTAT vs living_status')
```

```{r importOPAL_wb11, echo=F}
living_status <- HRS_ds_wb_w11
save(living_status, file = "../RData/wb_w11/living_status.RData")
rm(living_status)
```

### Validation throughout waves

```{r valid_ws_wb, echo=F}
dbb <- merge(HRS_ds_wb_w4, HRS_ds_wb_w5, by = "id", suffixes = c(".w4", ".w5"), all = T)
dbb <- merge(dbb, HRS_ds_wb_w6, by = "id", all = T)
dbb <- merge(dbb, HRS_ds_wb_w7, by = "id", suffixes = c(".w6", ".w7"), all = T)
dbb <- merge(dbb, HRS_ds_wb_w8, by = "id", all = T)
dbb <- merge(dbb, HRS_ds_wb_w9, by = "id", suffixes = c(".w8", ".w9"), all = T)
dbb <- merge(dbb, HRS_ds_wb_w10, by = "id", all = T)
dbb <- merge(dbb, HRS_ds_wb_w11, by = "id", suffixes = c(".w10", ".w11"), all = T)
dbb <- dbb[,-1]
dbb[dbb == 996] <- NA
names(dbb) <- c("w4", "w5", "w6", "w7", "w8", "w9", "w10", "w11")
v.dbb <- paste(dbb[, 1], dbb[, 2], dbb[, 3], dbb[, 4], dbb[, 5], dbb[, 6], dbb[, 7], dbb[, 8], sep = "")
f.dbb <- frq(v.dbb)[[1]][, c(1, 2, 4)]
kable(f.dbb)
```


## EBB

### Wave 7  

#### Study-specific variable description

| **Name** | `R7IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-EBB-w7`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |

```{r assign_ebb7, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w7_ls','HRS.HRS-EBB-w7', variables=list('R7IWSTAT'), missings = TRUE)
```

```{r local_ebb7, echo=F}
HRS_ebb_w7_ls <- opal.execute(o,'HRS_ebb_w7_ls')
vari <- HRS_ebb_w7_ls$R7IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R7IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ebb_w7_ls, aes(factor(R7IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")

```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.

**R script:**

```{r harmo_ebb7}
HRS_ds_ebb_w7 <- tibble(id=HRS_ebb_w7_ls$id)
HRS_ds_ebb_w7$living_status <- car::recode(HRS_ebb_w7_ls$R7IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_ebb_w7$living_status <- labelled(HRS_ds_ebb_w7$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ebb7, echo=F}
vari <- HRS_ds_ebb_w7$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w7, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ebb7, echo=F, results='asis'}
kable(table(HRS_ebb_w7_ls$R7IWSTAT, HRS_ds_ebb_w7$living_status, useNA = "ifany"), align='c', caption ='R7IWSTAT vs living_status')
```

```{r importOPAL_ebb7, echo=F}
living_status <- HRS_ds_ebb_w7
save(living_status, file = "../RData/ebb_w7/living_status.RData")
rm(living_status)
```


### Wave 8  

#### Study-specific variable description

| **Name** | `R8IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-EBB-w8`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_ebb8, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w8_ls','HRS.HRS-EBB-w8', variables=list('R8IWSTAT'), missings = TRUE)
```

```{r local_ebb8, echo=F}
HRS_ebb_w8_ls <- opal.execute(o,'HRS_ebb_w8_ls')
vari <- HRS_ebb_w8_ls$R8IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R8IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ebb_w8_ls, aes(factor(R8IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_ebb8}
ids_issue_ls <- ID_issue_ls$id[which(ID_issue_ls$wave==2 & ID_issue_ls$cohort=='ebb')]
ids_death_w7 <- HRS_ds_ebb_w7$id[HRS_ds_ebb_w7$living_status == 1]

HRS_ds_ebb_w8 <- tibble(id=HRS_ebb_w8_ls$id)
HRS_ds_ebb_w8$living_status <- car::recode(HRS_ebb_w8_ls$R8IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_ebb_w8$living_status[HRS_ds_ebb_w8$id %in%  ids_death_w7] <- 1
HRS_ds_ebb_w8$living_status[which(HRS_ds_ebb_w8$id %in% ids_issue_ls)] <- 1
HRS_ds_ebb_w8$living_status <- labelled(HRS_ds_ebb_w8$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_ebb8, echo=F}
vari <- HRS_ds_ebb_w8$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w8, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ebb8, echo=F, results='asis'}
kable(table(HRS_ebb_w8_ls$R8IWSTAT, HRS_ds_ebb_w8$living_status, useNA = "ifany"), align='c', caption ='R8IWSTAT vs living_status')
```

```{r importOPAL_ebb8, echo=F}
living_status <- HRS_ds_ebb_w8
save(living_status, file = "../RData/ebb_w8/living_status.RData")
rm(living_status)
```


### Wave 9  

#### Study-specific variable description

| **Name** | `R9IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-EBB-w9`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_ebb9, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w9_ls','HRS.HRS-EBB-w9', variables=list('R9IWSTAT'), missings = TRUE)
```

```{r local_ebb9, echo=F}
HRS_ebb_w9_ls <- opal.execute(o,'HRS_ebb_w9_ls')
vari <- HRS_ebb_w9_ls$R9IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R9IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ebb_w9_ls, aes(factor(R9IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.


**R script:**

```{r harmo_ebb9}
ids_issue_ls <- ID_issue_ls$id[which(ID_issue_ls$wave==3 & ID_issue_ls$cohort=='wb')]
ids_death_w8 <- HRS_ds_ebb_w8$id[HRS_ds_ebb_w8$living_status == 1]

HRS_ds_ebb_w9 <- tibble(id=HRS_ebb_w9_ls$id)
HRS_ds_ebb_w9$living_status <- car::recode(HRS_ebb_w9_ls$R9IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_ebb_w9$living_status[HRS_ds_ebb_w9$id %in%  ids_death_w8] <- 1
HRS_ds_ebb_w9$living_status[which(HRS_ds_ebb_w9$id %in% ids_issue_ls)] <- 1
HRS_ds_ebb_w9$living_status <- labelled(HRS_ds_ebb_w9$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ebb9, echo=F}
vari <- HRS_ds_ebb_w9$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w9, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ebb9, echo=F, results='asis'}
kable(table(HRS_ebb_w9_ls$R9IWSTAT, HRS_ds_ebb_w9$living_status, useNA = "ifany"), align='c', caption ='R9IWSTAT vs living_status')
```

```{r importOPAL_ebb9, echo=F}
living_status <- HRS_ds_ebb_w9
save(living_status, file = "../RData/ebb_w9/living_status.RData")
rm(living_status)
```

### Wave 10  

#### Study-specific variable description

| **Name** | `R10IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-EBB-w10`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_ebb10, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w10_ls','HRS.HRS-EBB-w10', variables=list('R10IWSTAT', 'RADMONTH'), missings = TRUE)
```

```{r local_ebb10, echo=F}
HRS_ebb_w10_ls <- opal.execute(o,'HRS_ebb_w10_ls')
vari <- HRS_ebb_w10_ls$R10IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R10IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ebb_w10_ls, aes(factor(R10IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.



**R script:**

```{r harmo_ebb10}
ids_death_w9 <- HRS_ds_ebb_w9$id[HRS_ds_ebb_w9$living_status == 1]

HRS_ds_ebb_w10 <- tibble(id=HRS_ebb_w10_ls$id)
HRS_ds_ebb_w10$living_status <- car::recode(HRS_ebb_w10_ls$R10IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_ebb_w10$living_status[HRS_ds_ebb_w10$id %in%  ids_death_w9] <- 1
HRS_ds_ebb_w10$living_status <- labelled(HRS_ds_ebb_w10$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ebb10, echo=F}
vari <- HRS_ds_ebb_w10$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w10, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ebb10, echo=F, results='asis'}
kable(table(HRS_ebb_w10_ls$R10IWSTAT, HRS_ds_ebb_w10$living_status, useNA = "ifany"), align='c', caption ='R10IWSTAT vs living_status')
```

```{r importOPAL_ebb10, echo=F}
living_status <- HRS_ds_ebb_w10
save(living_status, file = "../RData/ebb_w10/living_status.RData")
rm(living_status)
```


### Wave 11  

#### Study-specific variable description

| **Name** | `R11IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-EBB-w11`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_ebb11, echo=F}
opal.assign.table.tibble(o, 'HRS_ebb_w11_ls','HRS.HRS-EBB-w11', variables=list('R11IWSTAT'), missings = TRUE)
```

```{r local_ebb11, echo=F}
HRS_ebb_w11_ls <- opal.execute(o,'HRS_ebb_w11_ls')
vari <- HRS_ebb_w11_ls$R11IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R11IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_ebb_w11_ls, aes(factor(R11IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.



**R script:**

```{r harmo_ebb11}
ids_death_w10 <- HRS_ds_ebb_w10$id[HRS_ds_ebb_w10$living_status == 1]

HRS_ds_ebb_w11 <- tibble(id=HRS_ebb_w11_ls$id)
HRS_ds_ebb_w11$living_status <- car::recode(HRS_ebb_w11_ls$R11IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_ebb_w11$living_status[HRS_ds_ebb_w11$id %in%  ids_death_w10] <- 1
HRS_ds_ebb_w11$living_status <- labelled(HRS_ds_ebb_w11$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_ebb11, echo=F}
vari <- HRS_ds_ebb_w11$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_ebb_w11, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_ebb11, echo=F, results='asis'}
kable(table(HRS_ebb_w11_ls$R11IWSTAT, HRS_ds_ebb_w11$living_status, useNA = "ifany"), align='c', caption ='R11IWSTAT vs living_status')
```

```{r importOPAL_ebb11, echo=F}
living_status <- HRS_ds_ebb_w11
save(living_status, file = "../RData/ebb_w11/living_status.RData")
rm(living_status)
```

### Validation throughout waves

```{r valid_ws_ebb, echo=F}
dbb <- merge(HRS_ds_ebb_w7, HRS_ds_ebb_w8, by = "id", suffixes = c(".w7", ".w8"), all = T)
dbb <- merge(dbb, HRS_ds_ebb_w9, by = "id", all = T)
dbb <- merge(dbb, HRS_ds_ebb_w10, by = "id", suffixes = c(".w9", ".w10"), all = T)
dbb <- merge(dbb, HRS_ds_ebb_w11, by = "id", all = T)
dbb <- dbb[,-1]
dbb[dbb == 996] <- NA
names(dbb) <- c("w7", "w8", "w9", "w10", "w11")
v.dbb <- paste(dbb[, 1], dbb[, 2], dbb[, 3], dbb[, 4], dbb[, 5], sep = "")
f.dbb <- frq(v.dbb)[[1]][, c(1, 2, 4)]
kable(f.dbb)
```


## MBB

### Wave 10  

#### Study-specific variable description

| **Name** | `R10IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-MBB-w10`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |

```{r assign_mbb10, echo=F}
opal.assign.table.tibble(o, 'HRS_mbb_w10_ls','HRS.HRS-MBB-w10', variables=list('R10IWSTAT'), missings = TRUE)
```

```{r local_mbb10, echo=F}
HRS_mbb_w10_ls <- opal.execute(o,'HRS_mbb_w10_ls')
vari <- HRS_mbb_w10_ls$R10IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R10IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_mbb_w10_ls, aes(factor(R10IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")

```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.

**R script:**

```{r harmo_mbb10}
HRS_ds_mbb_w10 <- tibble(id=HRS_mbb_w10_ls$id)
HRS_ds_mbb_w10$living_status <- car::recode(HRS_mbb_w10_ls$R10IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_mbb_w10$living_status <- labelled(HRS_ds_mbb_w10$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_mbb10, echo=F}
vari <- HRS_ds_mbb_w10$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_mbb_w10, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_mbb10, echo=F, results='asis'}
kable(table(HRS_ebb_w11_ls$R11IWSTAT, HRS_ds_ebb_w11$living_status, useNA = "ifany"), align='c', caption ='R11IWSTAT vs living_status')
```

```{r importOPAL_mbb10, echo=F}
living_status <- HRS_ds_mbb_w10
save(living_status, file = "../RData/mbb_w10/living_status.RData")
rm(living_status)
```


### Wave 11  

#### Study-specific variable description

| **Name** | `R11IWSTAT`|
|-|-|
| **Label** | `R Interview Status` |
| **Table name** |`HRS-MBB-w11`|
| **Categories** |`0 = Inap.; 1 = Resp, alive; 2 = Resp, died after IW; 3 = Resp(proxy), died; 4 = NR, alive; 5 = NR, died this wv; 6 = NR, died prev wv; 7 = NR, dropped from samp`|
| **Missings** |`9 = NR, DK if alive or died`|
| **Description** |  |


```{r assign_mbb11, echo=F}
opal.assign.table.tibble(o, 'HRS_mbb_w11_ls','HRS.HRS-MBB-w11', variables=list('R11IWSTAT'), missings = TRUE)
```

```{r local_mbb11, echo=F}
HRS_mbb_w11_ls <- opal.execute(o,'HRS_mbb_w11_ls')
vari <- HRS_mbb_w11_ls$R11IWSTAT
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "R11IWSTAT")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(HRS_mbb_w11_ls, aes(factor(R11IWSTAT))) + geom_histogram(stat="count", fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Harmonisation algorithm
Values are recoded as follows: 

 * Values 1 (Resp, alive), 2 (Resp, died after IW) or 4 (NoResp, alive) are recoded as value 0 (alive) 
 * Values 3 (Resp proxy, died), 5 (NR, died this wv) or 6 (NR, died prev wv) are recoded as value 1 (died) 
 * Values 7 (NR, dropped) or 9 (NR, DK if alive or died) are recoded as value 2 (dropout) 
 * Value 0 (Inappropriate) is recoded as value missing 996 (Not applicable) because these individuals are probably new spouses from following waves.

**R script:**

```{r harmo_mbb11}
ids_death_w10 <- HRS_ds_mbb_w10$id[HRS_ds_mbb_w10$living_status == 1]

HRS_ds_mbb_w11 <- tibble(id=HRS_mbb_w11_ls$id)
HRS_ds_mbb_w11$living_status <- car::recode(HRS_mbb_w11_ls$R11IWSTAT, "c(1,2,4)=0; c(3,5,6)=1; c(7,9)=2; 0=996")
HRS_ds_mbb_w11$living_status[HRS_ds_mbb_w11$id %in%  ids_death_w10] <- 1
HRS_ds_mbb_w11$living_status <- labelled(HRS_ds_mbb_w11$living_status, labels = c("Alive"=0, "Dead"=1, "Dropout"=2, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```


#### Statistics of the new harmonised variable
```{r descript_mbb11, echo=F}
vari <- HRS_ds_mbb_w11$living_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_status")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(HRS_ds_mbb_w11, aes(x=factor(living_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Status") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_mbb11, echo=F, results='asis'}
kable(table(HRS_mbb_w11_ls$R11IWSTAT, HRS_ds_mbb_w11$living_status, useNA = "ifany"), align='c', caption ='R11IWSTAT vs living_status')
```

```{r importOPAL_mbb11, echo=F}
living_status <- HRS_ds_mbb_w11
save(living_status, file = "../RData/mbb_w11/living_status.RData")
rm(living_status)
```

### Validation throughout waves

```{r valid_ws_mbb, echo=F}
dbb <- merge(HRS_ds_mbb_w10, HRS_ds_mbb_w11, by = "id", suffixes = c(".w10", ".w11"), all = T)
dbb <- dbb[,-1]
dbb[dbb == 996] <- NA
names(dbb) <- c("w10", "w11")
v.dbb <- paste(dbb[, 1], dbb[, 2], sep = "")
f.dbb <- frq(v.dbb)[[1]][, c(1, 2, 4)]
kable(f.dbb)
```












## Summary of descriptive statistics of the harmonised variable accross populations and waves


Percentages of categories in each harmonised variable.



```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:3])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[14,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

# savingRD <- function(l.hds,vbl_name){
#   
#   for(index in seq_along(l.hds)){
#     assign(vbl_name,l.hds[[index]])
#     save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
#   }
# 
# }

```






```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


hrw.hrw.cw <- list(hrs_w1 = c("hrs_w1","HRS w1"), hrs_w2 = c("hrs_w2","HRS w2"), hrs_w3 = c("hrs_w3","HRS w3"), hrs_w4 = c("hrs_w4","HRS w4"), hrs_w5 = c("hrs_w5","HRS w5"), hrs_w6 = c("hrs_w6","HRS w6"), hrs_w7 = c("hrs_w7","HRS w7"), hrs_w8 = c("hrs_w8","HRS w8"), hrs_w9 = c("hrs_w9","HRS w9"), hrs_w10 = c("hrs_w10","HRS w10"), hrs_w11 = c("hrs_w11","HRS w11"))

hrw.ahead.cw <- list(ahead_w2 = c("ahead_w2","AHEAD w2"), ahead_w3 = c("ahead_w3","AHEAD w3"), ahead_w4 = c("ahead_w4","AHEAD w4"), ahead_w5 = c("ahead_w5","AHEAD w5"), ahead_w6 = c("ahead_w6","AHEAD w6"), ahead_w7 = c("ahead_w7","AHEAD w7"), ahead_w8 = c("ahead_w8","AHEAD w8"), ahead_w9 = c("ahead_w9","AHEAD w9"), ahead_w10 = c("ahead_w10","AHEAD w10"), ahead_w11 = c("ahead_w11","AHEAD w11"))

hrw.coda.cw <- list(coda_w4 = c("coda_w4","CODA w4"), coda_w5 = c("coda_w5","CODA w5"), coda_w6 = c("coda_w6","CODA w6"), coda_w7 = c("coda_w7","CODA w7"), coda_w8 = c("coda_w8","CODA w8"), coda_w9 = c("coda_w9","CODA w9"), coda_w10 = c("coda_w10","CODA w10"), coda_w11 = c("coda_w11","CODA w11"))

hrw.wb.cw <- list(wb_w4 = c("wb_w4","WB w4"), wb_w5 = c("wb_w5","WB w5"), wb_w6 = c("wb_w6","WB w6"), wb_w7 = c("wb_w7","WB w7"), wb_w8 = c("wb_w8","WB w8"), wb_w9 = c("wb_w9","WB w9"), wb_w10 = c("wb_w10","WB w10"), wb_w11 = c("wb_w11","WB w11"))

hrw.ebb.cw <- list(ebb_w7 = c("ebb_w7","EBB w7"), ebb_w8 = c("ebb_w8","EBB w8"), ebb_w9 = c("ebb_w9","EBB w9"), ebb_w10 = c("ebb_w10","EBB w10"), ebb_w11 = c("ebb_w11","EBB w11"))

hrw.mbb.cw <- list(mbb_w10 = c("mbb_w10","MBB w10"), mbb_w11 = c("mbb_w11","MBB w11"))



# HRS

# Consider only harmonised waves
l.hds <- lapply(hrw.hrw.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  #f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  #print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  #savingRD(lmlist[[1]],vbl_name=hd_vbl)
}






# AHEAD

# Consider only harmonised waves
l.hds <- lapply(hrw.ahead.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  #f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  #print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  #savingRD(lmlist[[1]],vbl_name=hd_vbl)
}





# CODA

# Consider only harmonised waves
l.hds <- lapply(hrw.coda.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  #f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  #print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  #savingRD(lmlist[[1]],vbl_name=hd_vbl)
}




# WB

# Consider only harmonised waves
l.hds <- lapply(hrw.wb.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  #f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  #print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  #savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



# EBB

# Consider only harmonised waves
l.hds <- lapply(hrw.ebb.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  #f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  #print(knitr::kable(f.dbb[f.dbb[,3]>=0.3,]))
  # Saving tibbles
  #savingRD(lmlist[[1]],vbl_name=hd_vbl)
}




# MBB

# Consider only harmonised waves
l.hds <- lapply(hrw.mbb.cw, function(wname) if(exists(paste0("HRS_ds_",wname[1]))){wname = list(get(paste0("HRS_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  #f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  #print(knitr::kable(f.dbb))
  # Saving tibbles
  #savingRD(lmlist[[1]],vbl_name=hd_vbl)
}


```







# Quality estimation

Results in validations throughout waves show, in each population, that there are few people who 
died in some wave and dropped out afterwards. This issue was already present in the original HRS 
variable and we have not fixed it yet. Meanwhile, we should consider that a previous death prevails 
upon a subsequent dropout.

Moreover, we found two errors:

* HRS sub-sample, individual with "id" = "63063010", was alive in wave 1, died in wave 2, and alive in waves 3 to 11.
* AHEAD sub-sample, individual with "id" = "202147020", was alive in waves 2 to 9, died in wave 10, and alive in wave 11.

These errors have not been corrected yet.

A general issue was detected. There are individuals that do not have date of interview and the value in the original Interview Status from HRS is 'NR, alive' but their date of interview is before the usual date of interview of the wave. Those individuals were recoded as 1 (dead).

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
