---
title: "Year of Birth"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/ybirthDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/ybirthDS.R')
```



# Data process
## Ireland



### Wave 1 

#### Study-specific variable description

| **Name** | `age` |
|----------|------------|
| **Label** | `Age at interview assuming date of birth is on the 1st of specified month` |
| **Table name** | `TILDA-AMF-v16` |
| **Description** |  |



```{r assign1, echo=F}
opal.assign.table.tibble(o, 'TILDA_w1_ybirth','TILDA.TILDA-AMF-v16',
                         variables=list('age'), missings = TRUE)
TILDA_w1_ybirth <- opal.execute(o,'TILDA_w1_ybirth')
```


```{r local1, echo=F}
# Year of interview is going to compute as 2010. 

TILDA_w1_ybirth$yinter <- rep(2010, length(TILDA_w1_ybirth$id))

vari <- TILDA_w1_ybirth$age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "Age") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(TILDA_w1_ybirth, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")
```

#### Harmonisation algorithm
To harmonize the year of birth is going to be used the following formula:
year_of_birth = Year_of_interview - age

The missing values have to be recoded as follows:

* `NA as 999`


**R script:**

```{r harmo1}
TILDA_w1_ybirth$ybirth <- TILDA_w1_ybirth$yinter - TILDA_w1_ybirth$age

TILDA_ds_w1 <- tibble(id=TILDA_w1_ybirth$id)
TILDA_ds_w1$ybirth <- car::recode(TILDA_w1_ybirth$ybirth, "NA=999")
TILDA_ds_w1$ybirth <- labelled(TILDA_ds_w1$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- TILDA_ds_w1$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(TILDA_ds_w1, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1929, 1962)
```

#### Validation
```{r crosstabulation1, echo=F}
```

```{r importOPAL EBB w7, echo=FALSE}
label(TILDA_ds_w1$ybirth) <- ds_label
ybirth <- TILDA_ds_w1
save(ybirth, file = "../RData/w1/ybirth.RData")

TILDA_m_ds_w1 <- TILDA_ds_w1
TILDA_m_ds_w1$ybirth <- car::recode(TILDA_m_ds_w1$ybirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
```







### Wave 2 

#### Study-specific variable description

| **Name** | `age` |
|----------|------------|
| **Label** | `Age of Respondent at 2nd interview` |
| **Table name** | `TILDA-AMF-v23` |
| **Description** |  |


```{r assign2, echo=F}
opal.assign.table.tibble(o, 'TILDA_w2_ybirth','TILDA.TILDA-AMF-v23',
                         variables=list('age'), missings = TRUE)
TILDA_w2_ybirth <- opal.execute(o,'TILDA_w2_ybirth')
```



```{r local2, echo=F}
# Year of interview is going to compute as 2012.
TILDA_w2_ybirth$yinter <- rep(2012, length(TILDA_w2_ybirth$id))

vari <- TILDA_w2_ybirth$age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "Age") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(TILDA_w2_ybirth, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")
```

#### Harmonisation algorithm
To harmonize the year of birth is going to be used the following formula:
year_of_birth = Year_of_interview - age
The missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo2}
TILDA_w2_ybirth$ybirth <- TILDA_w2_ybirth$yinter - TILDA_w2_ybirth$age

TILDA_ds_w2 <- tibble(id=TILDA_w2_ybirth$id)
TILDA_ds_w2$ybirth <- car::recode(TILDA_w2_ybirth$ybirth, "NA=999")
TILDA_ds_w2$ybirth <- labelled(TILDA_ds_w2$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- TILDA_ds_w2$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(TILDA_ds_w2, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
```





```{r importOPAL2, echo=F}
label(TILDA_ds_w2$ybirth) <- ds_label
ybirth <- TILDA_ds_w2
save(ybirth, file = "../RData/w2/ybirth.RData")
#opal.assign.data(o, 'TILDA_ds_w2', TILDA_ds_w2)
#opal.symbol_import(o,'TILDA_ds_w2', project='_Athlos_Harm_Dataset')

TILDA_m_ds_w2 <- TILDA_ds_w2
TILDA_m_ds_w2$ybirth <- car::recode(TILDA_m_ds_w2$ybirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'TILDA_m_ds_w2', TILDA_m_ds_w2)
#opal.symbol_import(o,'TILDA_m_ds_w2', project='_Athlos_Harm_Dataset')
```


## Summary of descriptive statistics of the harmonised variable accross populations and waves





```{r summ, echo=F}

TILDA.cw <- list(w1 = "w1", w2 = "w2")

# Consider only harmonised waves
l.hds <- lapply(TILDA.cw, function(wname) if(exists(paste0("TILDA_ds_",wname))){wname = get(paste0("TILDA_ds_",wname))})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

# Labelling of the tibbles and creating new tibbles with all missings recodified as NA

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cont_label)
  m_name <- paste0("TILDA_m_ds_",name)
  assign(m_name, aux_object)
  m.hds[[name]] <- get(paste0("TILDA_m_ds_",name))
  rm(aux_object)
}

t.summ <- summary(m.hds[[1]][2])[1:6]
t.hds <- substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1)
t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[2]],missing_values = miss_values_vector)$values_table)[[2]])
for (i in seq_along(l.hds)){
  t.summ <- summary(m.hds[[i]][2])[1:6]
  t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[2]],missing_values = miss_values_vector)$values_table[1,])))
}
t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))

dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],toupper(names(l.hds)))
kable(t.hds,caption=ds_label)



```




# Quality estimation


Calculated as: "date_birth"= "date of interview" - age
The selected variable "date of interview" is part of a cognitive test 
and therefor not relyable to account for date of interview. 
However we could not find another one.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
