---
title: "Year of Birth"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `ybirth`
* Variable label: `year of birth`
* Variable description: `Year of birth`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


```{r lab, echo=FALSE}
ds_label <- "Year of birth"
```


# Data process

## Ireland



### Wave 1 

#### Study-specific variable description

| **Name** | `age` |
|----------|------------|
| **Label** | `Age at interview assuming date of birth is on the 1st of specified month` |
| **Table name** | `TILDA-AMF-v16` |
| **Description** |  |



```{r assign1, echo=F}
opal.assign.table.tibble(o, 'TILDA_w1_ybirth','TILDA.TILDA-AMF-v16',
                         variables=list('age'), missings = TRUE)
TILDA_w1_ybirth <- opal.execute(o,'TILDA_w1_ybirth')
```


```{r local1, echo=F}
# Year of interview is going to compute as 2010. 

TILDA_w1_ybirth$yinter <- rep(2010, length(TILDA_w1_ybirth$id))

vari <- TILDA_w1_ybirth$age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "Age") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(TILDA_w1_ybirth, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")
```

#### Harmonisation algorithm
To harmonize the year of birth is going to be used the following formula:
year_of_birth = Year_of_interview - age

The missing values have to be recoded as follows:

* `NA as 999`


**R script:**

```{r harmo1}
TILDA_w1_ybirth$ybirth <- TILDA_w1_ybirth$yinter - TILDA_w1_ybirth$age

TILDA_ds_w1 <- tibble(id=TILDA_w1_ybirth$id)
TILDA_ds_w1$ybirth <- car::recode(TILDA_w1_ybirth$ybirth, "NA=999")
TILDA_ds_w1$ybirth <- labelled(TILDA_ds_w1$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- TILDA_ds_w1$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(TILDA_ds_w1, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1929, 1962)
```

#### Validation
```{r crosstabulation1, echo=F}
```

```{r importOPAL EBB w7, echo=FALSE}
label(TILDA_ds_w1$ybirth) <- ds_label
ybirth <- TILDA_ds_w1
save(ybirth, file = "../RData/w1/ybirth.RData")

TILDA_m_ds_w1 <- TILDA_ds_w1
TILDA_m_ds_w1$ybirth <- car::recode(TILDA_m_ds_w1$ybirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
```







### Wave 2 

#### Study-specific variable description

| **Name** | `age` |
|----------|------------|
| **Label** | `Age of Respondent at 2nd interview` |
| **Table name** | `TILDA-AMF-v23` |
| **Description** |  |


```{r assign2, echo=F}
opal.assign.table.tibble(o, 'TILDA_w2_ybirth','TILDA.TILDA-AMF-v23',
                         variables=list('age'), missings = TRUE)
TILDA_w2_ybirth <- opal.execute(o,'TILDA_w2_ybirth')
```



```{r local2, echo=F}
# Year of interview is going to compute as 2012.
TILDA_w2_ybirth$yinter <- rep(2012, length(TILDA_w2_ybirth$id))

vari <- TILDA_w2_ybirth$age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "Age") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(TILDA_w2_ybirth, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")
```

#### Harmonisation algorithm
To harmonize the year of birth is going to be used the following formula:
year_of_birth = Year_of_interview - age
The missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo2}
TILDA_w2_ybirth$ybirth <- TILDA_w2_ybirth$yinter - TILDA_w2_ybirth$age

TILDA_ds_w2 <- tibble(id=TILDA_w2_ybirth$id)
TILDA_ds_w2$ybirth <- car::recode(TILDA_w2_ybirth$ybirth, "NA=999")
TILDA_ds_w2$ybirth <- labelled(TILDA_ds_w2$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- TILDA_ds_w2$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(TILDA_ds_w2, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
```





```{r importOPAL2, echo=F}
label(TILDA_ds_w2$ybirth) <- ds_label
ybirth <- TILDA_ds_w2
save(ybirth, file = "../RData/w2/ybirth.RData")
#opal.assign.data(o, 'TILDA_ds_w2', TILDA_ds_w2)
#opal.symbol_import(o,'TILDA_ds_w2', project='_Athlos_Harm_Dataset')

TILDA_m_ds_w2 <- TILDA_ds_w2
TILDA_m_ds_w2$ybirth <- car::recode(TILDA_m_ds_w2$ybirth, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'TILDA_m_ds_w2', TILDA_m_ds_w2)
#opal.symbol_import(o,'TILDA_m_ds_w2', project='_Athlos_Harm_Dataset')
```



# Quality estimation


Calculated as: "date_birth"= "date of interview" - age
The selected variable "date of interview" is part of a cognitive test 
and therefor not relyable to account for date of interview. 
However we could not find another one.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
