---
title: "Age"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 






# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `age`
* Variable label: `Age`
* Variable description: `Age of participant at each wave`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


```{r lab, echo=FALSE}
ds_label <- "Age"
ds_label_all <- "Age of participant at each wave"
```


# Data process

## Ireland

### Wave 1 

#### Study-specific variable description



| **Name** | `age`|
|-|-|
| **Label** | `Age at interview assuming date of birth is on the 1st of specified month`|
| **Table name** | `TILDA-AMF-v16` |
| **Categories** |`continuous`<br/>`49 = <50`<br/>`80 = 80+`|
| **Description** |  |


```{r assign1, echo=F}
opal.assign.table.tibble(o, 'TILDA_w1_age','TILDA.TILDA-AMF-v16',variables=list('age'), missings = TRUE)
TILDA_w1_age <- opal.execute(o,'TILDA_w1_age')
```

```{r local1, echo=F}
vari <- TILDA_w1_age$age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(TILDA_w1_age, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`


**R script:**

```{r harmo1}
TILDA_ds_w1 <- tibble(id=TILDA_w1_age$id)
TILDA_ds_w1$age <- car::recode(TILDA_w1_age$age, "NA=999")
TILDA_ds_w1$age <- labelled(TILDA_ds_w1$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- TILDA_ds_w1$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(TILDA_ds_w1, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(51,82)
```

#### Validation
```{r crosstabulation1, echo=F}
```





```{r importOPAL1, echo=F}
label(TILDA_ds_w1$age) <- ds_label_all
age <- TILDA_ds_w1
save(age, file = "../RData/w1/age.RData")
#opal.assign.data(o, 'TILDA_ds_w1', TILDA_ds_w1)
#opal.symbol_import(o,'TILDA_ds_w1', project='_Athlos_Harm_Dataset')

TILDA_m_ds_w1 <- TILDA_ds_w1
TILDA_m_ds_w1$age <- car::recode(TILDA_m_ds_w1$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'TILDA_m_ds_w1', TILDA_m_ds_w1)
#opal.symbol_import(o,'TILDA_m_ds_w1', project='_Athlos_Harm_Dataset')
```




### Wave 2 

#### Study-specific variable description



| **Name** | `age`|
|-|-|
| **Label** | `Age of Respondent at 2nd interview`|
| **Table name** | `TILDA-AMF-v23` |
| **Categories** |`continuous`<br/>`51 = Less than 52`<br/>`82 = 82+`|
| **Description** |  |


```{r assign2, echo=F}
opal.assign.table.tibble(o, 'TILDA_w2_age','TILDA.TILDA-AMF-v23',variables=list('age'), missings = TRUE)
TILDA_w2_age <- opal.execute(o,'TILDA_w2_age')
```

```{r local2, echo=F}
vari <- TILDA_w2_age$age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(TILDA_w2_age, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo2}
TILDA_ds_w2 <- tibble(id=TILDA_w2_age$id)
TILDA_ds_w2$age <- car::recode(TILDA_w2_age$age, "NA=999")
TILDA_ds_w2$age <- labelled(TILDA_ds_w2$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- TILDA_ds_w2$age
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(TILDA_ds_w2, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation2, echo=F}
```





```{r importOPAL2, echo=F}
label(TILDA_ds_w2$age) <- ds_label_all
age <- TILDA_ds_w2
save(age, file = "../RData/w2/age.RData")
#opal.assign.data(o, 'TILDA_ds_w2', TILDA_ds_w2)
#opal.symbol_import(o,'TILDA_ds_w2', project='_Athlos_Harm_Dataset')

TILDA_m_ds_w2 <- TILDA_ds_w2
TILDA_m_ds_w2$age <- car::recode(TILDA_m_ds_w2$age, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'TILDA_m_ds_w2', TILDA_m_ds_w2)
#opal.symbol_import(o,'TILDA_m_ds_w2', project='_Athlos_Harm_Dataset')
```



# Quality estimation
The study 10-66 collects the date in baseline interview, 
but not all populations have the exact "date" at follow-up. 
In order to have the age at followup, we have to sum to age at baseline (age)
the number of years between baseline interview and follow-up interview. 
The number of years between waves are different for each population so some bias might be expected.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
