---
title: "Age"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/ageDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/ageDS.R')
```

# Data process

## Ireland

### Wave 1 

#### Study-specific variable description



| **Name** | `age`|
|-|-|
| **Label** | `Age at interview assuming date of birth is on the 1st of specified month`|
| **Table name** | `TILDA-AMF-v16` |
| **Categories** |`continuous`<br/>`49 = <50`<br/>`80 = 80+`|
| **Description** |  |


```{r assign1, echo=F}
opal.assign.table.tibble(o, 'TILDA_w1_age','TILDA.TILDA-AMF-v16',variables=list('age'), missings = TRUE)
TILDA_w1_age <- opal.execute(o,'TILDA_w1_age')
```

```{r local1, echo=F}
vari <- TILDA_w1_age$age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(TILDA_w1_age, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`


**R script:**

```{r harmo1}
TILDA_ds_w1 <- tibble(id=TILDA_w1_age$id)
TILDA_ds_w1$age <- car::recode(TILDA_w1_age$age, "NA=999")
TILDA_ds_w1$age <- labelled(TILDA_ds_w1$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- TILDA_ds_w1$age
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(TILDA_ds_w1, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") + xlim(51,82)
```

#### Validation
```{r crosstabulation1, echo=F}
```





### Wave 2 

#### Study-specific variable description



| **Name** | `age`|
|-|-|
| **Label** | `Age of Respondent at 2nd interview`|
| **Table name** | `TILDA-AMF-v23` |
| **Categories** |`continuous`<br/>`51 = Less than 52`<br/>`82 = 82+`|
| **Description** |  |


```{r assign2, echo=F}
opal.assign.table.tibble(o, 'TILDA_w2_age','TILDA.TILDA-AMF-v23',variables=list('age'), missings = TRUE)
TILDA_w2_age <- opal.execute(o,'TILDA_w2_age')
```

```{r local2, echo=F}
vari <- TILDA_w2_age$age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(TILDA_w2_age, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo2}
TILDA_ds_w2 <- tibble(id=TILDA_w2_age$id)
TILDA_ds_w2$age <- car::recode(TILDA_w2_age$age, "NA=999")
TILDA_ds_w2$age <- labelled(TILDA_ds_w2$age, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- TILDA_ds_w2$age
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(TILDA_ds_w2, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("age") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation2, echo=F}
```








## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

source("../../helpfunctions.r")
rm(labelling)
labelling <- labelling_c
rm(summaries)
summaries <- summaries_c

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


tilda.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"))

# Consider only harmonised waves
l.hds <- lapply(tilda.cw, function(wname) if(exists(paste0("TILDA_ds_",wname[1]))){wname = list(get(paste0("TILDA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```




# Quality estimation


```{r, echo=FALSE}

tilda_age <- Reduce(full_join, lapply(l.hds, \(.x) rename_with(.x[[1]], .fn = \(.yn) paste(.yn, .x[[2]], sep = "_"), .cols = `age`)))
tilda_age |> 
  pivot_longer(cols = -id) |> 
  mutate(value = if_else(value %in% miss_values_vector, NA_real_, as.numeric(value))) |> 
  arrange(id,name) |> 
  group_by(id) |> 
  mutate(odd = any(value<=lag(value, default = -Inf))) |> 
  ungroup() |> 
  filter(!is.na(value)) |> 
  filter(odd) |> 
  mutate(name = sub("age_", "", name)) |> 
  pivot_wider(id_cols = "id", names_from = "name") |> 
  kable(caption = "Imposible age trajectories")
```

```{r closeRsession, echo=FALSE}
opal.logout(o)
```
