---
title: "Marital Status"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable 

* Short name: `marital_status`
* Variable label: `The current marital status of the participant`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
1        | single
2        | married-cohabitating
3        | divorced-separated
4        | widow

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


```{r lab, echo=FALSE}
ds_label <- "Marital status"
ds_label_all <- "The current marital status of the participant"
```



<!-- ########################################################## --> 

# Data process

## Ireland

### Wave 1 

#### Study-specific variable description

 

| **Name** | `mar4`|
|-|-|
| **Label** | `Marital Status`|
| **Table name** | `TILDA-AMF-v16` |
| **Categories** |`1 = Married; 2 = Never married; 3 = Sep/divorced; 4 = Widowed`|
| **Description** |  |



```{r assign1,  echo=FALSE}
opal.assign.table.tibble(o, 'TILDA_w1_ms','TILDA.TILDA-AMF-v16',
                         variables=list('mar4'), missings = TRUE)
TILDA_w1_ms <- opal.execute(o,'TILDA_w1_ms')
```

```{r local1,  echo=FALSE}
vari <- TILDA_w1_ms$mar4
kable(Categorical_summary(vari, missing_values = NA)[2], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(TILDA_w1_ms, aes(x=factor(mar4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital Status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `recode 1 "Married" into 2`
* `recode 2 "Never married" into 1`
* `keep "Sep/divorced" into 3`
* `keep "Widowed" into 4`


**R script:**

```{r harmo1,   echo=TRUE}
TILDA_ds_w1 <- tibble(id=TILDA_w1_ms$id)
TILDA_ds_w1$marital_status <- car::recode(TILDA_w1_ms$mar4, "1=2; 2=1; NA=999")
TILDA_ds_w1$marital_status <- labelled(TILDA_ds_w1$marital_status, labels = c("single"=1, "married cohabitating"=2, "divorced separated"=3, "widow"=4, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1,  echo=FALSE}
vari <- TILDA_ds_w1$marital_status
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(TILDA_ds_w1, aes(x=factor(marital_status))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("sex") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1,  echo=FALSE}
BeforeH <- table(TILDA_w1_ms$mar4)[c(2, 1, 3, 4)]
AfterH <- table(TILDA_ds_w1$marital_status)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->1","1->2", "3", "4")
kable(C)
```

 
 

 
```{r importOPAL1,  echo=FALSE}
label(TILDA_ds_w1$marital_status) <- ds_label_all
marital_status <- TILDA_ds_w1
save(marital_status, file = "../RData/w1/marital_status.RData")
#opal.assign.data(o, 'TILDA_ds_w1', TILDA_ds_w1)
#opal.symbol_import(o,'TILDA_ds_w1', project='_Athlos_Harm_Dataset')

TILDA_m_ds_w1 <- TILDA_ds_w1
TILDA_m_ds_w1$marital_status <- car::recode(TILDA_m_ds_w1$marital_status, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'TILDA_m_ds_w1', TILDA_m_ds_w1)
#opal.symbol_import(o,'TILDA_m_ds_w1', project='_Athlos_Harm_Dataset')
```






### Wave 2 

There is no variable.


# Quality estimation

No comments

[Comments on the quality of the new harmonised variable. This section can be done in a later stage, once all variables are harmonised.]


```{r closeRsession, echo=FALSE,  echo=FALSE} 
opal.logout(o)
```