---
title: "Parental education"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/parenteduDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/parenteduDS.R')
```



# Data process

## Ireland

### Wave 1


#### Study-specific variable description


| **Name** | `dm009` |`dm010`|
|-|-|-|
| **Label** | `What was the highest grade of school your father completed?`| `And what was the highest grade of school your mother completed?`|
| **Table name** | `TILDA-AMF-v16`| `TILDA-AMF-v16`|
| **Categories** |`1 = Some primary (not complete)` <br/> `2 = Primary or equivalent` <br/> `3 = Intermediate/junior/group certificate or equivalent` <br/> `4 = Leaving certificate or equivalent` <br/> `5 = Diploma/certificate` <br/> `6 = Primary degree` <br/> `7 = Postgraduate/higher degree` <br/> `96 = None`|`1 = Some primary (not complete)` <br/> `2 = Primary or equivalent` <br/> `3 = Intermediate/junior/group certificate or equivalent` <br/> `4 = Leaving certificate or equivalent` <br/> `5 = Diploma/certificate` <br/> `6 = Primary degree` <br/> `7 = Postgraduate/higher degree` <br/> `96 = None`|
| **Missings** | `98 = Don't know`<br/>`99 =  Refused`<br/>`NA` |`98 = Don't know`<br/>`99 =  Refused`<br/>`NA` |
| **Description** |  |  |


```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'TILDA_w1','TILDA.TILDA-AMF-v16', variables=list('dm009','dm010'), missings = TRUE)
TILDA_w1 <- opal.execute(o,'TILDA_w1') %>% update_labelled()

```

```{r local w1, echo=F}

vbl <- TILDA_w1$dm009
vbl_miss <- c(98,99)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = attributes(vbl)$`spss::shortName`) 
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(TILDA_w1, aes(x=factor(vbl))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- TILDA_w1$dm010
vbl_miss <- c(98,99)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = attributes(vbl)$`spss::shortName`) 
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
ggplot(TILDA_w1, aes(x=factor(vbl))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `parentedu` from the study-specific variables its maximum (up to `8,9`) has to be recoded as follows:

* `1:2,96 into 2`
* `3:4 into 1`
* `5:7 into 0`
* `98 into 998`
* `99 into 997`
* `NA into 999`

**R script:**


```{r harmo w1, tidy=FALSE}


TILDA_ds_w1 <- TILDA_w1 %>%
  mutate(
    dm009 = dplyr::recode(dm009, `96` = 0L, `98` = -98L, `99` = -97L),
    dm010 = dplyr::recode(dm010, `96` = 0L, `98` = -98L, `99` = -97L)
  ) %>%
  mutate(parentedu = do.call(pmax, c(select(., dm009, dm010), na.rm = TRUE))) %>%
  mutate(
    parentedu = case_when(
      parentedu %in% c(0:2) ~ 2,
      parentedu %in% c(3:4) ~ 1,
      parentedu %in% c(5:7) ~ 0,
      parentedu %in% c(-98) ~ 998,
      parentedu %in% c(-97) ~ 997,
      TRUE ~ 999
    )
  ) %>%
  select(id, parentedu)
  

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- TILDA_ds_w1$parentedu
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(TILDA_ds_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}
```



### Wave 2


#### Study-specific variable description

Wave 1 variables

```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'TILDA_w2','TILDA.TILDA-AMF-v23', variables=list('age'), missings = TRUE)
TILDA_w2 <- opal.execute(o,'TILDA_w2') %>% 
  update_labelled() %>%
  select(id)

```



#### Harmonisation algorithm

To compute `parentedu` from the study-specific variables keep wave 1 harmonisation

**R script:**

```{r harmo w2}


TILDA_ds_w2 <- TILDA_w2 %>%
  left_join(TILDA_ds_w1, by ="id")
  

```

#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- TILDA_ds_w2$parentedu
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(TILDA_ds_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w2, echo=F}
```




## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.


```{r helpfunctions, echo=F}

source("../../helpfunctions.r")

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


tilda.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"))

# Consider only harmonised waves
l.hds <- lapply(tilda.cw, function(wname) if(exists(paste0("TILDA_ds_",wname[1]))){wname = list(get(paste0("TILDA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],sapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```



# Quality estimation


```{r closeRsession, echo=FALSE} 
opal.logout(o)
```