---
title: "Non paid work"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/nonpaid_workDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/nonpaid_workDS.R')
```



# Data process



## Ireland


### Wave 1


#### Study-specific variable description



| **Name** | `we001`|
|-|-|
| **Label** | `Which one of these would you say best describes your current situation?`|
| **Table name**  | `TILDA-AMF-v16`|
| **Categories** | `1 =  Retired`<br/>`2 = Employed`<br/>`3 = Self-employed (including farming)`<br/>`4 = Unemployed`<br/>`5 = Permanently sick or disabled`<br/>`6 = Looking after home or family`<br/>`7 = In education or training`<br/>`95 = Other`|
| **Missings** |`98 = Don't Know`<br/>`99 = Refused` |
| **Description** |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'TILDA_w1','TILDA.TILDA-AMF-v16',variables=list('we001'), missings = T)
TILDA_w1 <- opal.execute(o,'TILDA_w1')

```

```{r local w1, echo=F}

vbl <- TILDA_w1$we001
kable(Categorical_summary(vbl, missing_values = c(98,99))[3], caption = names(TILDA_w1)[2])
kable(Categorical_summary(vbl, missing_values = c(98,99))[1], caption = "Category")
ggplot(TILDA_w1, aes(x=factor(we001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `nonpaid_work` from the study-specific variable it has to be recoded as follows:

* `7  into 3`
* `6 into 1`
* `5,95,1,2,3,4 into 996`
* `98 into 998`
* `99 into 997`


**R script:**

```{r harmo w1}

# Categorical variable harmonization
TILDA_ds_w1 <- tibble(id=TILDA_w1$id)
TILDA_ds_w1$nonpaid_work <-car::recode(TILDA_w1$we001, "c(1,2,3,4,5,95)=996; c(6)=1; 7=3; 98=998; 99=997")

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- TILDA_ds_w1$nonpaid_work
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(TILDA_ds_w1, aes(x=factor(nonpaid_work))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")


```


#### Validation

```{r crosstabulation w1, echo=F}

```



### Wave 2

Not found harmonizable variable.




## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable:


**R script:**

```{r summ}
TILDA_ds_w1$nonpaid_work <- labelled(TILDA_ds_w1$nonpaid_work, labels = cat_label)
label(TILDA_ds_w1$nonpaid_work) <- ds_label

TILDA_m_ds_w1 <- TILDA_ds_w1
TILDA_m_ds_w1$nonpaid_work <- car::recode(TILDA_m_ds_w1$nonpaid_work, "miss_values_vector=NA")

tt <- frq(TILDA_ds_w1$nonpaid_work)[[1]][,c(1:2,4)]
tt[14,] <- c("n", "sample size", 
             length(TILDA_ds_w1$nonpaid_work)
             )
names(tt)<-c("val", "label", "w1")
kable(tt)


```



# Quality estimation


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.TILDA <- list(w1 = TILDA_ds_w1)

for(index in seq_along(l.TILDA)){
  nonpaid_work <- l.TILDA[[index]]
  save(nonpaid_work, file = paste0(datafolder,names(l.TILDA)[index],"/nonpaid_work.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





