---
title: "Time walking"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/t_walksDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/t_walksDS.R')
```




# Data process

## Finland

### Wave 1 


| **Name** | `KYS1_K33` |
|-|-|
| **Label** | `Exercise: walking at least 10 min/ day`|
| **Table name** | `t00_athlos_2017_02_23` |
| **Units** | `days`|
| **Missings** | `NA` |
| **Description** |  |

```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'Health20002011_w1','Health2000-2011.t00_athlos_2017_02_23', variables=list('KYS1_K33'), missings = TRUE)
Health20002011_w1 <- opal.execute(o,'Health20002011_w1')
```

```{r local w1, echo=F}

vbl <- Health20002011_w1$KYS1_K33
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = attr(vbl, "spss::shortName")) 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(Health20002011_w1, aes(KYS1_K33)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm


To compute `t_walks` from the study-specific variable it has to be recoded as follows:

* `0 into 0`
* `>0 into 1`
* `NA into 999`

**R script:**

```{r harmo w1}

Health20002011_ds_w1 <- tibble(id=Health20002011_w1$id)
Health20002011_ds_w1$t_walks <- car::recode(Health20002011_w1$KYS1_K33, "1:hi=1; 0=0; NA=999")

```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}

vbl <- Health20002011_ds_w1$t_walks
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(Health20002011_ds_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation w1, echo=F}

```


### Wave 2

There is no variable.



## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.

```{r helpfunctions, echo=F}

source("../../helpfunctions.r")


```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


health2000.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"))

# Consider only harmonised waves
l.hds <- lapply(health2000.cw, function(wname) if(exists(paste0("Health20002011_ds_",wname[1]))){wname = list(get(paste0("Health20002011_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```







# Quality estimation


```{r closeRsession, echo=FALSE}
opal.logout(o)
```

