---
title: "Frequency of Vigorous Physical Activity"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/f_vig_paDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/f_vig_paDS.R')
```



# Data process

## Finland

### Wave 1 

Not found



### Wave 2

#### Study-specific variable description

| **Name** | `T11_KYS1_K24_4PV` |
|-|-|
| **Label** | `Vigorous and strenuous aerobic type exercise: days in a week` |
| **Table name** | `t11_athlos_2017_02_27` |
| **Categories:**| `continuous`|
| **Missings:**| `NA` |
| **Description** |  |

```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'Health20002011_w2','Health2000-2011.t11_athlos_2017_02_27', variables=list('T11_KYS1_K24_4PV'), missings = TRUE)
Health20002011_w2 <- opal.execute(o,'Health20002011_w2')
```

```{r local w2, echo=F}
vbl <- Health20002011_w2$T11_KYS1_K24_4PV
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = names(Health20002011_w2)[2]) 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(Health20002011_w2, aes(T11_KYS1_K24_4PV)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") + coord_cartesian(xlim = c(0,8))
```

#### Harmonisation algorithm

To compute `f_vig_pa` from the study-specific variable it has to be recoded as follows:

* `0 into 0`
* `1 into 1`
* `2,3 into 2`
* `4,5 into 3`
* `6,7 into 4`
* `NA into 999`

**R script:**

```{r harmo w2}
Health20002011_ds_w2 <- tibble(id=Health20002011_w2$id)
Health20002011_ds_w2$f_vig_pa <- car::recode(Health20002011_w2$T11_KYS1_K24_4PV, "3 = 2;4 = 3;5 = 3;6 = 4;7 = 4;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vbl <- Health20002011_ds_w2$f_vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(Health20002011_ds_w2, aes(x=factor(f_vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
AfterH <- table(Health20002011_ds_w2$f_vig_pa)
X<-table(Health20002011_w2$T11_KYS1_K24_4PV)
BeforeH <- c(X[1],sum(X[2:3]),sum(X[4:5]),sum(X[6:7]),sum(is.na(Health20002011_w2$T11_KYS1_K24_4PV)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1->1","2,3->2","4,5->3","6,7->4","NA->999")  
kable(C)
```

```{r importOPAL w2, echo=F}
f_vig_pa <- Health20002011_ds_w2 
save(f_vig_pa, file = "../RData/w2/f_vig_pa.RData")
rm(f_vig_pa)
```



# Quality estimation


<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
