---
title: "Frequency of moderate physical activities"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/f_mod_paDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/f_mod_paDS.R')
```



# Data process


## Adachi, Kanazawa, Shirakawa, Sendai and Takikawa

### Wave 1

Not found.

### Wave 2

Not found.


### Wave 3

#### Study-specific variable description

| **Name** | `q2_2` |
|-|-|
| **Label** | `FREQUENCY OF LIGHT EXERCISE` |
| **Table name** | `jstar_2011_5cities` |
| **Categories:**| `1 = Almost every day` <br/> `2 = 2-3 times a week` <br/> `3 = Once a week` <br/> `4 = 1-2 times a month` <br/> `5 = Several times a year` <br/> `6 = Hardly or never` |
| **Missings:**|`NA`|
| **Description** |  |


```{r assign aksst w3, echo=F}
opal.assign.table.tibble(o, 'JSTAR_aksst_w3','JSTAR_datasets_restricted.jstar_2011_5cities', variables=list('q2_2'), missings = TRUE)
JSTAR_aksst_w3 <- opal.execute(o,'JSTAR_aksst_w3')
```

```{r local aksst w3, echo=F}
vbl <- JSTAR_aksst_w3$q2_2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_aksst_w3)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w3, aes(x=factor(q2_2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `f_mod_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 4` 
* `2 into 2`
* `3 into 1`
* `4 into 1`
* `5 into 0`
* `6 into 0`
* `NA into 999`

**R script:**

```{r harmo aksst w3}
JSTAR_ds_aksst_w3 <- tibble(id=JSTAR_aksst_w3$id)
JSTAR_ds_aksst_w3$f_mod_pa <- car::recode(JSTAR_aksst_w3$q2_2, "1 = 4;3 = 1;4 = 1;5 = 0;6 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript aksst w3, echo=F}
vbl <- JSTAR_ds_aksst_w3$f_mod_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w3, aes(x=factor(f_mod_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation aksst w3, echo=F}
AfterH <- table(JSTAR_ds_aksst_w3$f_mod_pa)
X<-table(JSTAR_aksst_w3$q2_2)
BeforeH <- c(sum(X[5:6]),sum(X[3:4]),X[2:1],sum(is.na(JSTAR_aksst_w3$q2_2)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5,6->0","3,4->1","2->2","1->4","NA->999") 
kable(C)
```



## Tosu and Naha

### Wave 1 

Not found.



### Wave 2

#### Study-specific variable description

| **Name** | `q2_2` |
|-|-|
| **Label** | `FREQUENCY OF LIGHT EXERCISE` |
| **Table name** | `jstar_2011_2cities` |
| **Categories:**| `1 = Almost every day` <br/> `2 = 2-3 times a week` <br/> `3 = Once a week` <br/> `4 = 1-2 times a month` <br/> `5 = Several times a year` <br/> `6 = Hardly or never` |
| **Missings:**|`NA`|
| **Description** |  |


```{r assign tn w2, echo=F}
opal.assign.table.tibble(o, 'JSTAR_tn_w2','JSTAR_datasets_restricted.jstar_2011_2cities', variables=list('q2_2'), missings = TRUE)
JSTAR_tn_w2 <- opal.execute(o,'JSTAR_tn_w2')
```

```{r local tn w2, echo=F}
vbl <- JSTAR_tn_w2$q2_2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_tn_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w2, aes(x=factor(q2_2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `f_mod_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 4` 
* `2 into 2`
* `3 into 1`
* `4 into 1`
* `5 into 0`
* `6 into 0`
* `NA into 999`

**R script:**

```{r harmo tn w2}
JSTAR_ds_tn_w2 <- tibble(id=JSTAR_tn_w2$id)
JSTAR_ds_tn_w2$f_mod_pa <- car::recode(JSTAR_tn_w2$q2_2, "1 = 4;3 = 1;4 = 1;5 = 0;6 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript tn w2, echo=F}
vbl <- JSTAR_ds_tn_w2$f_mod_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_tn_w2, aes(x=factor(f_mod_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation tn w2, echo=F}
AfterH <- table(JSTAR_ds_tn_w2$f_mod_pa)
X<-table(JSTAR_tn_w2$q2_2)
BeforeH <- c(sum(X[5:6]),sum(X[3:4]),X[2:1],sum(is.na(JSTAR_tn_w2$q2_2)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5,6->0","3,4->1","2->2","1->4","NA->999") 
kable(C)
```



## Chofu, Tondabayashi and Hiroshima

### Wave 1 

Not found


## Summary of descriptive statistics of the harmonised variable accross populations and waves


Percentages of categories in each harmonised variable.


**R script:**

```{r summ}

l.hds <- list(aksst_w3 = JSTAR_ds_aksst_w3, tn_w2 = JSTAR_ds_tn_w2)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:5])
  m_name <- paste0("JSTAR_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[16,] <- c("n", "sample size", 
             length(l.hds[[1]][[2]]), length(l.hds[[2]][[2]]))
names(t.hds)<-c("val", "label", "AKSST_W3", "TN_W2")
kable(t.hds)

```



# Quality estimation



<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(l.hds)){
  f_mod_pa <- l.hds[[index]]
  save(f_mod_pa, file = paste0(datafolder,names(l.hds)[index],"/f_mod_pa.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





