---
title: "Frequency of Vigorous Physical Activity"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/f_vig_paDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/f_vig_paDS.R')
```


# Data process


## AKSST

### Wave 1

Not found.


### Wave 2

#### Study-specific variable description

| **Name** | `tome8` |
|-|-|
| **Label** | `Q2-4:FREQUENCY OF STRENUOUS ACTIVITY` |
| **Table name** | `jstar_2009_5cities` |
| **Categories:**| `1 = Every day` <br/> `2 = 2-3 days a week` <br/> `3 = Once a week` <br/> `4 = Once or twice a month` <br/> `5 = A few times a year` <br/> `6 = Not at all` |
| **Missings:**| `NA` |
| **Description** |  |


```{r assign aksst w2, echo=F}
opal.assign.table.tibble(o, 'JSTAR_aksst_w2','JSTAR_datasets_restricted.jstar_2009_5cities', variables=list('tome8'), missings = TRUE)
JSTAR_aksst_w2 <- opal.execute(o,'JSTAR_aksst_w2')
```

```{r local aksst w2, echo=F}
vbl <- JSTAR_aksst_w2$tome8
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_aksst_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w2, aes(x=factor(tome8))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `f_vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 4` 
* `2 into 2`
* `3 into 1`
* `4 into 1`
* `5 into 0`
* `6 into 0`
* `NA into 999`

**R script:**

```{r harmo aksst w2}
JSTAR_ds_aksst_w2 <- tibble(id=JSTAR_aksst_w2$id)
JSTAR_ds_aksst_w2$f_vig_pa <- car::recode(JSTAR_aksst_w2$tome8, "1 = 4;3 = 1;4 = 1;5 = 0;6 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript aksst w2, echo=F}
vbl <- JSTAR_ds_aksst_w2$f_vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w2, aes(x=factor(f_vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation aksst w2, echo=F}
AfterH <- table(JSTAR_ds_aksst_w2$f_vig_pa)
X<-table(JSTAR_aksst_w2$tome8)
BeforeH <- c(sum(X[5:6]),sum(X[3:4]),X[2:1],sum(is.na(JSTAR_aksst_w2$tome8)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5,6->0","3,4->1","2->2","1->4","NA->999") 
kable(C)
```





### Wave 3

#### Study-specific variable description

| **Name** | `q2_4` |
|-|-|
| **Label** | `11Q2:FREQUENCY OF STRENUOUS EXERCISE` |
| **Table name** | `jstar_2011_5cities` |
| **Categories:**| `1 = Almost every day` <br/> `2 = 2-3 times a week` <br/> `3 = Once a week` <br/> `4 = 1-2 times a month` <br/> `5 = Several times a year` <br/> `6 = Hardly or never` |
| **Missings:**|`NA`|
| **Description** |  |


```{r assign aksst w3, echo=F}
opal.assign.table.tibble(o, 'JSTAR_aksst_w3','JSTAR_datasets_restricted.jstar_2011_5cities', variables=list('q2_4'), missings = TRUE)
JSTAR_aksst_w3 <- opal.execute(o,'JSTAR_aksst_w3')
```

```{r local aksst w3, echo=F}
vbl <- JSTAR_aksst_w3$q2_4
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_aksst_w3)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w3, aes(x=factor(q2_4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `f_vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 4` 
* `2 into 2`
* `3 into 1`
* `4 into 1`
* `5 into 0`
* `6 into 0`
* `NA into 999`

**R script:**

```{r harmo aksst w3}
JSTAR_ds_aksst_w3 <- tibble(id=JSTAR_aksst_w3$id)
JSTAR_ds_aksst_w3$f_vig_pa <- car::recode(JSTAR_aksst_w3$q2_4, "1 = 4;3 = 1;4 = 1;5 = 0;6 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript aksst w3, echo=F}
vbl <- JSTAR_ds_aksst_w3$f_vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w3, aes(x=factor(f_vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation aksst w3, echo=F}
AfterH <- table(JSTAR_ds_aksst_w3$f_vig_pa)
X<-table(JSTAR_aksst_w3$q2_4)
BeforeH <- c(sum(X[5:6]),sum(X[3:4]),X[2:1],sum(is.na(JSTAR_aksst_w3$q2_4)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5,6->0","3,4->1","2->2","1->4","NA->999") 
kable(C)
```




## TN

### Wave 1 

Not found.



### Wave 2

#### Study-specific variable description

| **Name** | `q2_4` |
|-|-|
| **Label** | `11Q2:FREQUENCY OF STRENUOUS EXERCISE` |
| **Table name** | `jstar_2011_2cities` |
| **Categories:**| `1 = Almost every day` <br/> `2 = 2-3 times a week` <br/> `3 = Once a week` <br/> `4 = 1-2 times a month` <br/> `5 = Several times a year` <br/> `6 = Hardly or never` |
| **Missings:**|`NA`|
| **Description** |  |


```{r assign tn w2, echo=F}
opal.assign.table.tibble(o, 'JSTAR_tn_w2','JSTAR_datasets_restricted.jstar_2011_2cities', variables=list('q2_4'), missings = TRUE)
JSTAR_tn_w2 <- opal.execute(o,'JSTAR_tn_w2')
```

```{r local tn w2, echo=F}
vbl <- JSTAR_tn_w2$q2_4
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_tn_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w2, aes(x=factor(q2_4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `f_vig_pa` from the study-specific variable it has to be recoded as follows:

* `1 into 4` 
* `2 into 2`
* `3 into 1`
* `4 into 1`
* `5 into 0`
* `6 into 0`
* `NA into 999`

**R script:**

```{r harmo tn w2}
JSTAR_ds_tn_w2 <- tibble(id=JSTAR_tn_w2$id)
JSTAR_ds_tn_w2$f_vig_pa <- car::recode(JSTAR_tn_w2$q2_4, "1 = 4;3 = 1;4 = 1;5 = 0;6 = 0;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript tn w2, echo=F}
vbl <- JSTAR_ds_tn_w2$f_vig_pa
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_tn_w2, aes(x=factor(f_vig_pa))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation tn w2, echo=F}
AfterH <- table(JSTAR_ds_tn_w2$f_vig_pa)
X<-table(JSTAR_tn_w2$q2_4)
BeforeH <- c(sum(X[5:6]),sum(X[3:4]),X[2:1],sum(is.na(JSTAR_tn_w2$q2_4)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5,6->0","3,4->1","2->2","1->4","NA->999") 
kable(C)
```




## CTH

### Wave 1 


Not found








## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable by cohort:





```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:5])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[16,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}


# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


jstar.cw <- list(aksst_w1 = c("aksst_w1","AKSST w1"), aksst_w2 = c("aksst_w2","AKSST w2"), aksst_w3 = c("aksst_w3","AKSST w3"), tn_w1 = c("tn_w1","TN w1"), tn_w2 = c("tn_w2","TN w2"), cth_w1 = c("cth_w1","CTH w1"))

# Consider only harmonised waves
l.hds <- lapply(jstar.cw, function(wname) if(exists(paste0("JSTAR_ds_",wname[1]))){wname = list(get(paste0("JSTAR_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```










# Quality estimation




<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
