---
title: "Time of Vigorous Physical Activity"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/t_vig_paDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/t_vig_paDS.R')
```



# Data process


## AKSST

### Wave 1

#### Study-specific variable description

| **Name** | `tome151` | `tome165` |
|-|-|-|
| **Label** | `Q21:TIME ALLOCATION -WEEKDAY -5- UNIT: MIN PER DAY- EXERCISE` | `Q21:TIME ALLOCATION -HOLIDAY -5- UNIT: MIN PER DAY- EXERCISE` |
| **Table name** | `jstar_2007_5cities` | `jstar_2007_5cities` |
| **Categories:**| `continuous` | `continuous` |
| **Missings:**| `NA` | `NA` |
| **Description** |  |  |


```{r assign aksst w1, echo=F}
opal.assign.table.tibble(o, 'JSTAR_aksst_w1','JSTAR_datasets_restricted.jstar_2007_5cities', variables=list('tome151','tome165'), missings = TRUE)
JSTAR_aksst_w1 <- opal.execute(o,'JSTAR_aksst_w1')
```

```{r local aksst w1, echo=F}
vbl <- JSTAR_aksst_w1$tome151
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = names(JSTAR_aksst_w1)[2])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_aksst_w1, aes(tome151)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")


vbl <- JSTAR_aksst_w1$tome165
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = names(JSTAR_aksst_w1)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_aksst_w1, aes(tome165)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `t_vig_pa` from the study-specific variable it has to be recoded as follows:

* `(tome151+tome165)*14`
* `NA into 999`

**R script:**

```{r harmo aksst w1}

JSTAR_ds_aksst_w1 <- tibble(id=JSTAR_aksst_w1$id)
JSTAR_aksst_w1$tome151[which(JSTAR_aksst_w1$tome151>1440)] <- NA # A day has 1440=24*60 minutes.
JSTAR_aksst_w1$tome165[which(JSTAR_aksst_w1$tome165>1440)] <- NA
JSTAR_ds_aksst_w1$t_vig_pa <- car::recode((JSTAR_aksst_w1$tome151*10+JSTAR_aksst_w1$tome165*4), "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript aksst w1, echo=F}
vbl <- JSTAR_ds_aksst_w1$t_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_ds_aksst_w1, aes(t_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation aksst w1, echo=F}
```






### Wave 2

#### Study-specific variable description

| **Name** | `tome222` | `tome240` |
|-|-|-|
| **Label** | `Q21:TIME ALLOCATION -WEEKDAY - UNIT: MIN PER DAY- EXERCISE` | `Q21:TIME ALLOCATION -HOLIDAY - UNIT: MIN PER DAY- EXERCISE` |
| **Table name** | `jstar_2009_5cities` | `jstar_2009_5cities` |
| **Categories:**| `continuous` | `continuous` |
| **Missings:**| `NA` | `NA` |
| **Description** |  |  |


```{r assign aksst w2, echo=F}
opal.assign.table.tibble(o, 'JSTAR_aksst_w2','JSTAR_datasets_restricted.jstar_2009_5cities', variables=list('tome222','tome240'), missings = TRUE)
JSTAR_aksst_w2 <- opal.execute(o,'JSTAR_aksst_w2')
```

```{r local aksst w2, echo=F}
vbl <- JSTAR_aksst_w2$tome222
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = names(JSTAR_aksst_w2)[2])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_aksst_w2, aes(tome222)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")


vbl <- JSTAR_aksst_w2$tome240
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = names(JSTAR_aksst_w2)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_aksst_w2, aes(tome240)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") 

```

#### Harmonisation algorithm

To compute `t_vig_pa` from the study-specific variable it has to be recoded as follows:

* `(tome222+tome240)*14`
* `NA into 999`

**R script:**

```{r harmo aksst w2}
JSTAR_ds_aksst_w2 <- tibble(id=JSTAR_aksst_w2$id)
JSTAR_aksst_w2$tome222[which(JSTAR_aksst_w2$tome222>1440)] <- NA
JSTAR_aksst_w2$tome240[which(JSTAR_aksst_w2$tome240>1440)] <- NA
JSTAR_ds_aksst_w2$t_vig_pa <- car::recode((JSTAR_aksst_w2$tome222*10+JSTAR_aksst_w2$tome240*4), "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript aksst w2, echo=F}
vbl <- JSTAR_ds_aksst_w2$t_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_ds_aksst_w2, aes(t_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation aksst w2, echo=F}
```




### Wave 3

#### Study-specific variable description

| **Name** | `q16_3_7_mm` | `q16_4_7_mm` |
|-|-|-|
| **Label** | `11Q16:TIME ALLOCATION -WEEKDAY - UNIT: MIN PER DAY- EXERCISE` | `11Q16:TIME ALLOCATION -HOLIDAY - UNIT: MIN PER DAY- EXERCISE` |
| **Table name** | `jstar_2011_5cities` | `jstar_2011_5cities` |
| **Categories:**| `continuous` | `continuous` |
| **Missings:**| `NA` | `NA` |
| **Description** |  |  |


```{r assign aksst w3, echo=F}
opal.assign.table.tibble(o, 'JSTAR_aksst_w3','JSTAR_datasets_restricted.jstar_2011_5cities', variables=list('q16_3_7_mm','q16_4_7_mm'), missings = TRUE)
JSTAR_aksst_w3 <- opal.execute(o,'JSTAR_aksst_w3')
```

```{r local aksst w3, echo=F}
vbl <- JSTAR_aksst_w3$q16_3_7_mm
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = names(JSTAR_aksst_w3)[2])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_aksst_w3, aes(q16_3_7_mm)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") 


vbl <- JSTAR_aksst_w3$q16_4_7_mm
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = names(JSTAR_aksst_w3)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_aksst_w3, aes(q16_4_7_mm)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `t_vig_pa` from the study-specific variable it has to be recoded as follows:

* `(q16_3_7_mm+q16_4_7_mm)*14`
* `NA into 999`

**R script:**

```{r harmo aksst w3}
JSTAR_ds_aksst_w3 <- tibble(id=JSTAR_aksst_w3$id)
JSTAR_aksst_w3$q16_3_7_mm[which(JSTAR_aksst_w3$q16_3_7_mm>1440)] <- NA
JSTAR_aksst_w3$q16_4_7_mm[which(JSTAR_aksst_w3$q16_4_7_mm>1440)] <- NA
JSTAR_ds_aksst_w3$t_vig_pa <- car::recode((JSTAR_aksst_w3$q16_3_7_mm*10+JSTAR_aksst_w3$q16_4_7_mm*4), "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript aksst w3, echo=F}
vbl <- JSTAR_ds_aksst_w3$t_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_ds_aksst_w3, aes(t_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation aksst w3, echo=F}

```






## TN


### Wave 1

#### Study-specific variable description

| **Name** | `tome151` | `tome165` |
|-|-|-|
| **Label** | `Q21:TIME ALLOCATION -WEEKDAY -6- UNIT: MIN PER DAY- EXERCISE` | `Q21:TIME ALLOCATION -HOLIDAY -6- UNIT: MIN PER DAY- EXERCISE` |
| **Table name** | `jstar_2009_2cities` | `jstar_2009_2cities` |
| **Categories:**| `continuous` | `continuous` |
| **Missings:**| `NA` | `NA` |
| **Description** |  |  |


```{r assign tn w1, echo=F}
opal.assign.table.tibble(o, 'JSTAR_tn_w1','JSTAR_datasets_restricted.jstar_2009_2cities', variables=list('tome151','tome165'), missings = TRUE)
JSTAR_tn_w1 <- opal.execute(o,'JSTAR_tn_w1')
```

```{r local tn w1, echo=F}
vbl <- JSTAR_tn_w1$tome151
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = names(JSTAR_tn_w1)[2])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_tn_w1, aes(tome151)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")


vbl <- JSTAR_tn_w1$tome165
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = names(JSTAR_tn_w1)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_tn_w1, aes(tome165)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency") 

```

#### Harmonisation algorithm

To compute `t_vig_pa` from the study-specific variable it has to be recoded as follows:

* `(tome151+tome165)*14`
* `NA into 999`

**R script:**

```{r harmo tn w1}

JSTAR_ds_tn_w1 <- tibble(id=JSTAR_tn_w1$id)
JSTAR_tn_w1$tome151[which(JSTAR_tn_w1$tome151>1440)] <- NA
JSTAR_tn_w1$tome165[which(JSTAR_tn_w1$tome165>1440)] <- NA
JSTAR_ds_tn_w1$t_vig_pa <- car::recode((JSTAR_tn_w1$tome151*10+JSTAR_tn_w1$tome165*4), "NA = 999 ")

```

#### Statistical description of the new harmonised variable
```{r descript tn w1, echo=F}
vbl <- JSTAR_ds_tn_w1$t_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_ds_tn_w1, aes(t_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation tn w1, echo=F}
```






### Wave 2

#### Study-specific variable description

| **Name** | `q16_3_7_mm` | `q16_4_7_mm` |
|-|-|-|
| **Label** | `11Q16:TIME ALLOCATION -WEEKDAY - UNIT: MIN PER DAY- EXERCISE` | `11Q16:TIME ALLOCATION -HOLIDAY - UNIT: MIN PER DAY- EXERCISE` |
| **Table name** | `jstar_2011_2cities` | `jstar_2011_2cities` |
| **Categories:**| `continuous` | `continuous` |
| **Missings:**| `NA` | `NA` |
| **Description** |  |  |


```{r assign tn w2, echo=F}
opal.assign.table.tibble(o, 'JSTAR_tn_w2','JSTAR_datasets_restricted.jstar_2011_2cities', variables=list('q16_3_7_mm','q16_4_7_mm'), missings = TRUE)
JSTAR_tn_w2 <- opal.execute(o,'JSTAR_tn_w2')
```

```{r local tn w2, echo=F}
vbl <- JSTAR_tn_w2$q16_3_7_mm
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = names(JSTAR_tn_w2)[2])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_tn_w2, aes(q16_3_7_mm)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")


vbl <- JSTAR_tn_w2$q16_4_7_mm
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = names(JSTAR_tn_w2)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_tn_w2, aes(q16_4_7_mm)) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `t_vig_pa` from the study-specific variable it has to be recoded as follows:

* `(q16_3_7_mm+q16_4_7_mm)*14`
* `NA into 999`

**R script:**

```{r harmo tn w2}
JSTAR_ds_tn_w2 <- tibble(id=JSTAR_tn_w2$id)
JSTAR_tn_w2$q16_3_7_mm[which(JSTAR_tn_w2$q16_3_7_mm>1440)] <- NA
JSTAR_tn_w2$q16_4_7_mm[which(JSTAR_tn_w2$q16_4_7_mm>1440)] <- NA
JSTAR_ds_tn_w2$t_vig_pa <- car::recode((JSTAR_tn_w2$q16_3_7_mm*10+JSTAR_tn_w2$q16_4_7_mm*4), "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript tn w2, echo=F}
vbl <- JSTAR_ds_tn_w2$t_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_ds_tn_w2, aes(t_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation tn w2, echo=F}

```






## CTH

### Wave 1

#### Study-specific variable description

| **Name** | `q21_1_6_h` | `q21_2_6_h` |
|-|-|-|
| **Label** | `Q21:TIME ALLOCATION -WEEKDAY -6- UNIT: HOUR PER DAY- EXERCISE` | `Q21:TIME ALLOCATION -HOLIDAY -6- UNIT: HOUR PER DAY- EXERCISE` |
| **Table name** | `jstar_2011_3cities` | `jstar_2011_3cities` |
| **Categories:**| `continuous` | `continuous` |
| **Missings:**| `NA` | `NA` |
| **Description** |  |  |


```{r assign cth w1, echo=F}
opal.assign.table.tibble(o, 'JSTAR_cth_w1','JSTAR_datasets_restricted.jstar_2011_3cities', variables=list('q21_1_6_h','q21_2_6_h'), missings = TRUE)
JSTAR_cth_w1 <- opal.execute(o,'JSTAR_cth_w1')
```

```{r local cth w1, echo=F}
vbl <- as.numeric(JSTAR_cth_w1$q21_1_6_h)
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = names(JSTAR_cth_w1)[2])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_cth_w1, aes(as.numeric(q21_1_6_h))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- as.numeric(JSTAR_cth_w1$q21_2_6_h)
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = names(JSTAR_cth_w1)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_cth_w1, aes(as.numeric(q21_2_6_h))) + geom_histogram(stat="count", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

To compute `t_vig_pa` from the study-specific variable it has to be recoded as follows:

* `(q21_1_6_h+q21_2_6_h)*14*60`
* `NA into 999`

**R script:**

```{r harmo cth w1}
JSTAR_ds_cth_w1 <- tibble(id=JSTAR_cth_w1$id)
JSTAR_cth_w1$q21_1_6_h <- as.numeric(JSTAR_cth_w1$q21_1_6_h)
JSTAR_cth_w1$q21_2_6_h <- as.numeric(JSTAR_cth_w1$q21_2_6_h)
JSTAR_cth_w1$q21_1_6_h[which(JSTAR_cth_w1$q21_1_6_h>24)] <- NA
JSTAR_cth_w1$q21_2_6_h[which(JSTAR_cth_w1$q21_2_6_h>24)] <- NA
JSTAR_ds_cth_w1$t_vig_pa <- car::recode((JSTAR_cth_w1$q21_1_6_h*10+JSTAR_cth_w1$q21_2_6_h*4)*60, "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript cth w1, echo=F}
vbl <- JSTAR_ds_cth_w1$t_vig_pa
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_ds_cth_w1, aes(t_vig_pa)) + geom_histogram(stat="count", fill="steelblue", data = .%>% filter(!vbl %in% miss_values_vector)) + xlab(ds_label) + ylab("Frequency")

```

#### Validation
```{r crosstabulation cth w1, echo=F}

```














## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for continuous data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][2])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[2]],missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][2])[1:6]
    # Next, missing/no-missing values
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[2]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


jstar.cw <- list(aksst_w1 = c("aksst_w1","AKSST w1"), aksst_w2 = c("aksst_w2","AKSST w2"), aksst_w3 = c("aksst_w3","AKSST w3"), tn_w1 = c("tn_w1","TN w1"), tn_w2 = c("tn_w2","TN w2"), cth_w1 = c("cth_w1","CTH w1"))

# Consider only harmonised waves
l.hds <- lapply(jstar.cw, function(wname) if(exists(paste0("JSTAR_ds_",wname[1]))){wname = list(get(paste0("JSTAR_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```












# Quality estimation




<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
