---
title: "Number of cigarettes"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/n_cigarettesDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/n_cigarettesDS.R')
```



# Data process


## Adachi, Kanazawa, Shirakawa, Sendai and Takikawa

### Wave 1 

#### Study-specific variable description

| **Name** | `tome23` |
|-|-|
| **Label** | `HOW MANY CIGARETTES DO/DID YOU SMOKE ON AVERAGE DAY?` |
| **Table name** | `jstar_2007_5cities` |
| **Categories:**| `continuous` |
| **Missings:**|`NA`|
| **Description** |  |


```{r assign aksst w1, echo=F}
opal.assign.table.tibble(o, 'JSTAR_aksst_w1','JSTAR_datasets_restricted.jstar_2007_5cities', variables=list('tome23'), missings = TRUE)
JSTAR_aksst_w1 <- opal.execute(o,'JSTAR_aksst_w1')
```

```{r local aksst w1, echo=F}
vbl <- JSTAR_aksst_w1$tome23
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "Number of cigarettes") 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_aksst_w1, aes(tome23)) + geom_histogram(stat="count", fill="steelblue") + xlab("Number of cigarettes") + ylab("Frequency") + xlim(0,82)
```

#### Harmonisation algorithm

To compute `n_cigarettes` from the study-specific variable it has to be recoded as follows:

* `tome23*7` 
* `NA into 999`

**R script:**

```{r harmo aksst w1}
JSTAR_ds_aksst_w1 <- tibble(id=JSTAR_aksst_w1$id)
JSTAR_ds_aksst_w1$n_cigarettes <- car::recode(JSTAR_aksst_w1$tome23*7, "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript aksst w1, echo=F}
vbl <- JSTAR_ds_aksst_w1$n_cigarettes
kable(Continuous_summary(var = vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(JSTAR_ds_aksst_w1, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(0,570)
```

#### Validation
```{r crosstabulation aksst w1, echo=F}
```




### Wave 2

#### Study-specific variable description

| **Name** | `tome10` |
|-|-|
| **Label** | `HOW MANY CIGARETTES DO/DID YOU SMOKE ON AVERAGE DAY?` |
| **Table name** | `jstar_2009_5cities` |
| **Categories:**| `continuous` |
| **Missings:**|`NA`|
| **Description** |  |


```{r assign aksst w2, echo=F}
opal.assign.table.tibble(o, 'JSTAR_aksst_w2','JSTAR_datasets_restricted.jstar_2009_5cities', variables=list('tome10'), missings = TRUE)
JSTAR_aksst_w2 <- opal.execute(o,'JSTAR_aksst_w2')
```

```{r local aksst w2, echo=F}
vbl <- JSTAR_aksst_w2$tome10
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "Number of cigarettes") 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_aksst_w2, aes(tome10)) + geom_histogram(stat="count", fill="steelblue") + xlab("Number of cigarettes") + ylab("Frequency") + xlim(0,105)
```

#### Harmonisation algorithm

To compute `n_cigarettes` from the study-specific variable it has to be recoded as follows:

* `tome10*7` 
* `NA into 999`

**R script:**

```{r harmo aksst w2}
JSTAR_ds_aksst_w2 <- tibble(id=JSTAR_aksst_w2$id)
JSTAR_ds_aksst_w2$n_cigarettes <- car::recode(JSTAR_aksst_w2$tome10*7, "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript aksst w2, echo=F}
vbl <- JSTAR_ds_aksst_w2$n_cigarettes
kable(Continuous_summary(var = vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(JSTAR_ds_aksst_w2, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(0,710)
```

#### Validation
```{r crosstabulation aksst w2, echo=F}
```



### Wave 3

Not found.



## Tosu and Naha

### Wave 1 

#### Study-specific variable description

| **Name** | `tome23` |
|-|-|
| **Label** | `HOW MANY CIGARETTES DO/DID YOU SMOKE PER DAY?` |
| **Table name** | `jstar_2009_2cities` |
| **Categories:**| `continuous` |
| **Missings:**|`NA`|
| **Description** |  |


```{r assign tn w1, echo=F}
opal.assign.table.tibble(o, 'JSTAR_tn_w1','JSTAR_datasets_restricted.jstar_2009_2cities', variables=list('tome23'), missings = TRUE)
JSTAR_tn_w1 <- opal.execute(o,'JSTAR_tn_w1')
```

```{r local tn w1, echo=F}
vbl <- JSTAR_tn_w1$tome23
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "Number of cigarettes") 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_tn_w1, aes(tome23)) + geom_histogram(stat="count", fill="steelblue") + xlab("Number of cigarettes") + ylab("Frequency") + xlim(-1,82)
```

#### Harmonisation algorithm

To compute `n_cigarettes` from the study-specific variable it has to be recoded as follows:

* `tome23*7` 
* `NA into 999`

**R script:**

```{r harmo tn w1}
JSTAR_ds_tn_w1 <- tibble(id=JSTAR_tn_w1$id)
JSTAR_ds_tn_w1$n_cigarettes <- car::recode(JSTAR_tn_w1$tome23*7, "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript tn w1, echo=F}
vbl <- JSTAR_ds_tn_w1$n_cigarettes
kable(Continuous_summary(var = vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(JSTAR_ds_tn_w1, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(-4,570)
```

#### Validation
```{r crosstabulation tn w1, echo=F}
```



### Wave 2

Not found.



## Chofu, Tondabayashi and Hiroshima

### Wave 1 

#### Study-specific variable description

| **Name** | `q4_2_1` |
|-|-|
| **Label** | `HOW MANY CIGARETTES DO/DID YOU SMOKE PER DAY?` |
| **Table name** | `jstar_2011_3cities` |
| **Categories:**| `continuous` |
| **Missings:**|`NA`|
| **Description** |  |


```{r assign cth w1, echo=F}
opal.assign.table.tibble(o, 'JSTAR_cth_w1','JSTAR_datasets_restricted.jstar_2011_3cities', variables=list('q4_2_1'), missings = TRUE)
JSTAR_cth_w1 <- opal.execute(o,'JSTAR_cth_w1')
```

```{r local cth w1, echo=F}
vbl <- JSTAR_cth_w1$q4_2_1
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "Number of cigarettes") 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_cth_w1, aes(q4_2_1)) + geom_histogram(stat="count", fill="steelblue") + xlab("Number of cigarettes") + ylab("Frequency") + xlim(-1,105)
```

#### Harmonisation algorithm

To compute `n_cigarettes` from the study-specific variable it has to be recoded as follows:

* `q4_2_1*7` 
* `NA into 999`

**R script:**

```{r harmo cth w1}
JSTAR_ds_cth_w1 <- tibble(id=JSTAR_cth_w1$id)
JSTAR_ds_cth_w1$n_cigarettes <- car::recode(JSTAR_cth_w1$q4_2_1*7, "NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript cth w1, echo=F}
vbl <- JSTAR_ds_cth_w1$n_cigarettes
kable(Continuous_summary(var = vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(JSTAR_ds_cth_w1, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(-4,710)
```

#### Validation
```{r crosstabulation cth w1, echo=F}
```


```{r final, echo=F}


l.hds <- list(aksst_w1 = JSTAR_ds_aksst_w1, aksst_w2 = JSTAR_ds_aksst_w2, tn_w1 = JSTAR_ds_tn_w1, cth_w1 = JSTAR_ds_cth_w1)

for(name in names(l.hds)) {
  label(l.hds[[name]][[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
}

```


# Quality estimation
[Comments on the quality of the new harmonised variable.]


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  n_cigarettes <- l.hds[[index]]
  save(n_cigarettes, file = paste0(datafolder,names(l.hds)[index],"/n_cigarettes.RData"))
}

```
<!-- ########################################################## --> 
<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
