---
title: "Alcohol drinking"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/alcoholDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/alcoholDS.R')
```



# Data process



## aksst


### Wave 1


#### Study-specific variable description

| **Name** | `tome27`|
|-|-|
| **Label** | `Q5:HOW OFTEN HAVE YOU DRUNK ANY ALCOHOLIC BEVERAGES LAST 6 MONTHS?`|
| **Table name**  | `jstar_2007_5cities`|
| **Categories** | `1 = Daily`<br/>`2 = 5~6 days per week`<br/>`3 = 3~4 days per week`<br/>`4 = 1~2 days per week`<br/>`5 = Several times per month`<br/>`6 = Hardly ever or never drink`|
| **Missings** | `NA` |
| **Description** |  |

```{r assign aksst_w1, echo=F}

opal.assign.table.tibble(o, 'JSTAR_aksst_w1','JSTAR_datasets_restricted.jstar_2007_5cities',variables=list('tome27'), missings = T)
JSTAR_aksst_w1 <- opal.execute(o,'JSTAR_aksst_w1')

```

```{r local aksst_w1, echo=F}

vbl <- JSTAR_aksst_w1$tome27
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_aksst_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w1, aes(x=factor(tome27))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable `tome27`, it has to be recoded as follows:

* `6 into 0`
* `1 to 5 into 1`
* `NA into 999`

To compute `freq_oh` from the study-specific variable `tome27`, it has to be recoded as follows:

* `6 into 0`
* `5 into 1`
* `1 to 4 into 2`
* `NA into 999`

**R script:**

```{r harmo aksst_w1}

# Categorical variable harmonization
JSTAR_ds_aksst_w1 <- tibble(id=JSTAR_aksst_w1$id)
JSTAR_ds_aksst_w1$current_oh <- car::recode(JSTAR_aksst_w1$tome27,"c(1,2,3,4,5) = 1; 6 = 0; NA=999")
JSTAR_ds_aksst_w1$freq_oh <- car::recode(JSTAR_aksst_w1$tome27,"c(1,2,3,4) = 2; 5 = 1; 6 = 0; NA=999")

```


#### Statistics of the new harmonized variable

```{r descript aksst_w1, echo=F}

vbl <- JSTAR_ds_aksst_w1$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w1, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- JSTAR_ds_aksst_w1$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w1, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

```


#### Validation

```{r crosstabulation aksst_w1, echo=F}

```



### Wave 2

There is no harmonizable variable.



### Wave 3


#### Study-specific variable description


| **Name** | `q4` |
|-|-|
| **Label** | `11Q4:FREQUENCY OF DRINKING`|
| **Table name**  | `jstar_2011_5cities`|
| **Categories** | `1 = Every day`<br/>`2 = 5~6 days a week`<br/>`3 = 3~4 days a week`<br/>`4 = 1~2 days a week`<br/>`5 = A few times`<br/>`6 = Hardly or never`|
| **Missings** | `NA`<br>`.l` |
| **Description** |  |

```{r assign aksst_w3, echo=F}

opal.assign.table.tibble(o, 'JSTAR_aksst_w3','JSTAR_datasets_restricted.jstar_2011_5cities',variables=list('q4'), missings = T)
JSTAR_aksst_w3 <- opal.execute(o,'JSTAR_aksst_w3')

```

```{r local aksst_w3, echo=F}

vbl <- JSTAR_aksst_w3$q4
kable(Categorical_summary(vbl, missing_values = '.l')[3], caption = names(JSTAR_aksst_w3)[2])
kable(Categorical_summary(vbl, missing_values = '.l')[1], caption = "Category")
ggplot(JSTAR_aksst_w3, aes(x=factor(q4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable `q4`, it has to be recoded as follows:

* `6 into 0`
* `1 to 5 into 1`
* `'.l',NA into 999`

To compute `freq_oh` from the study-specific variable `tome27`, it has to be recoded as follows:

* `6 into 0`
* `5 into 1`
* `1 to 4 into 2`
* `'.l',NA into 999`

**R script:**

```{r harmo aksst_w3}

# Categorical variable harmonization
JSTAR_ds_aksst_w3 <- tibble(id=JSTAR_aksst_w3$id)
JSTAR_ds_aksst_w3$current_oh <- car::recode(JSTAR_aksst_w3$q4,"c(1,2,3,4,5) = 1; 6 = 0; '.l'=999; NA=999")
JSTAR_ds_aksst_w3$freq_oh <- car::recode(JSTAR_aksst_w3$q4,"c(1,2,3,4) = 2; 5 = 1; 6 = 0; '.l'=999; NA=999")

```


#### Statistics of the new harmonized variable

```{r descript aksst_w3, echo=F}

vbl <- JSTAR_ds_aksst_w3$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w3, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- JSTAR_ds_aksst_w3$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w3, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

```


#### Validation

```{r crosstabulation aksst_w3, echo=F, results='asis'}

```



## tn

### Wave 1


#### Study-specific variable description

| **Name** | `tome27`|
|-|-|
| **Label** | `Q5:HOW OFTEN DID YOU DRINK ANY ALCOHOL LAST 6 MONTHS?`|
| **Table name**  | `jstar_2009_2cities`|
| **Categories** | `1 = Daily`<br/>`2 = 5~6 days per week`<br/>`3 = 3~4 days per week`<br/>`4 = 1~2 days per week`<br/>`5 = Several times per month`<br/>`6 = Hardly ever or never drink`|
| **Missings** | `NA` |
| **Description** |  |


```{r assign tn_w1, echo=F}

opal.assign.table.tibble(o, 'JSTAR_tn_w1','JSTAR_datasets_restricted.jstar_2009_2cities',variables=list('tome27'), missings = T)
JSTAR_tn_w1 <- opal.execute(o,'JSTAR_tn_w1')

```

```{r local tn_w1, echo=F}

vbl <- JSTAR_tn_w1$tome27
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_tn_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w1, aes(x=factor(tome27))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable `tome27`, it has to be recoded as follows:

* `6 into 0`
* `1 to 5 into 1`
* `NA into 999`

To compute `freq_oh` from the study-specific variable `tome27`, it has to be recoded as follows:

* `6 into 0`
* `5 into 1`
* `1 to 4 into 2`
* `NA into 999`

**R script:**

```{r harmo tn_w1}

# Categorical variable harmonization
JSTAR_ds_tn_w1 <- tibble(id=JSTAR_tn_w1$id)
JSTAR_ds_tn_w1$current_oh <- car::recode(JSTAR_tn_w1$tome27,"c(1,2,3,4,5) = 1; 6 = 0; NA=999")
JSTAR_ds_tn_w1$freq_oh <- car::recode(JSTAR_tn_w1$tome27,"c(1,2,3,4) = 2; 5 = 1; 6 = 0; NA=999")

```


#### Statistics of the new harmonized variable

```{r descript tn_w1, echo=F}

vbl <- JSTAR_ds_tn_w1$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_tn_w1, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- JSTAR_ds_tn_w1$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_tn_w1, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

```


#### Validation

```{r crosstabulation tn_w1, echo=F}

```



### Wave 2

#### Study-specific variable description


| **Name** | `q4` |
|-|-|
| **Label** | `11Q4:FREQUENCY OF DRINKING`|
| **Table name**  | `jstar_2011_2cities`|
| **Categories** | `1 = Every day`<br/>`2 = 5~6 days a week`<br/>`3 = 3~4 days a week`<br/>`4 = 1~2 days a week`<br/>`5 = A few times`<br/>`6 = Hardly or never`|
| **Missings** | `NA`<br/>`.l` |
| **Description** |  |



```{r assign tn_w2, echo=F}

opal.assign.table.tibble(o, 'JSTAR_tn_w2','JSTAR_datasets_restricted.jstar_2011_2cities',variables=list('q4'), missings = T)
JSTAR_tn_w2 <- opal.execute(o,'JSTAR_tn_w2')

```

```{r local tn_w2, echo=F}

vbl <- JSTAR_tn_w2$q4
kable(Categorical_summary(vbl, missing_values = '.l')[3], caption = names(JSTAR_tn_w2)[2])
kable(Categorical_summary(vbl, missing_values = '.l')[1], caption = "Category")
ggplot(JSTAR_tn_w2, aes(x=factor(q4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable `q4`, it has to be recoded as follows:

* `6 into 0`
* `1 to 5 into 1`
* `'.l',NA into 999`

To compute `freq_oh` from the study-specific variable `tome27`, it has to be recoded as follows:

* `6 into 0`
* `5 into 1`
* `1 to 4 into 2`
* `'.l',NA into 999`

**R script:**

```{r harmo tn_w2}

# Categorical variable harmonization
JSTAR_ds_tn_w2 <- tibble(id=JSTAR_tn_w2$id)
JSTAR_ds_tn_w2$current_oh <- car::recode(JSTAR_tn_w2$q4,"c(1,2,3,4,5) = 1; 6 = 0; '.l'=999; NA=999")
JSTAR_ds_tn_w2$freq_oh <- car::recode(JSTAR_tn_w2$q4,"c(1,2,3,4) = 2; 5 = 1; 6 = 0; '.l'=999; NA=999")

```


#### Statistics of the new harmonized variable

```{r descript tn_w2, echo=F}

vbl <- JSTAR_ds_tn_w2$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_tn_w2, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- JSTAR_ds_tn_w2$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_tn_w2, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

```


#### Validation

```{r crosstabulation tn_w2, echo=F, results='asis'}


```



## cth

### Wave 1


#### Study-specific variable description

| **Name** | `q5`|
|-|-|
| **Label** | `Q5:HOW OFTEN DID YOU DRINK ANY ALCOHOL LAST 6 MONTHS?`|
| **Table name**  | `jstar_2011_3cities`|
| **Categories** | `1 = Every day`<br/>`2 = 5~6 times  a week`<br/>`3 = 3~4 times  a week`<br/>`4 = 1~2 times  a week`<br/>`5 = A few times`<br/>`6 = Hardly or never`|
| **Missings** | `NA`<br/>`.l` |
| **Description** |  |

```{r assign cth_w1, echo=F}

opal.assign.table.tibble(o, 'JSTAR_cth_w1','JSTAR_datasets_restricted.jstar_2011_3cities',variables=list('q5'), missings = T)
JSTAR_cth_w1 <- opal.execute(o,'JSTAR_cth_w1')

```

```{r local cth_w1, echo=F}

vbl <- JSTAR_cth_w1$q5
kable(Categorical_summary(vbl, missing_values = '.l')[3], caption = names(JSTAR_cth_w1)[2])
kable(Categorical_summary(vbl, missing_values = '.l')[1], caption = "Category")
ggplot(JSTAR_cth_w1, aes(x=factor(q5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable `q5`, it has to be recoded as follows:

* `6 into 0`
* `1 to 5 into 1`
* `'.l',NA into 999`

To compute `freq_oh` from the study-specific variable `tome27`, it has to be recoded as follows:

* `6 into 0`
* `5 into 1`
* `1 to 4 into 2`
* `'.l',NA into 999`

**R script:**

```{r harmo cth_w1}

# Categorical variable harmonization
JSTAR_ds_cth_w1 <- tibble(id=JSTAR_cth_w1$id)
JSTAR_ds_cth_w1$current_oh <- car::recode(JSTAR_cth_w1$q5,"c(1,2,3,4,5) = 1; 6 = 0; '.l'=999; NA=999")
JSTAR_ds_cth_w1$freq_oh <- car::recode(JSTAR_cth_w1$q5,"c(1,2,3,4) = 2; 5 = 1; 6 = 0; '.l'=999; NA=999")

```


#### Statistics of the new harmonized variable

```{r descript cth_w1, echo=F}

vbl <- JSTAR_ds_cth_w1$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_cth_w1, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- JSTAR_ds_cth_w1$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_cth_w1, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

```


#### Validation

```{r crosstabulation cth_w1, echo=F}


```



```{r final, echo=F}

l.hds <- list(aksst_w1 = JSTAR_ds_aksst_w1, aksst_w3 = JSTAR_ds_aksst_w3, tn_w1 = JSTAR_ds_tn_w1, tn_w2 = JSTAR_ds_tn_w2, cth_w1 = JSTAR_ds_cth_w1)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label_curr # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  label(l.hds[[name]][[3]]) <- label(aux_object[[3]]) <- ds_label_freq # Text value assigned at the DS description, at the top
  l.hds[[name]][[3]] <- labelled(l.hds[[name]][[3]], labels = freq_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  aux_object[[3]] <- car::recode(aux_object[[3]], "miss_values_vector=NA")
  aux_object[[3]] <- labelled(aux_object[[3]], labels = freq_label[1:3])
  m_name <- paste0("JSTAR_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}
```




## Summary of descriptive statistics of the harmonised variable `current_oh` accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.

**R script:**

```{r summ current}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]])))
names(t.hds)<-c("val", "label", toupper(names(l.hds)))
kable(t.hds)

```


## Summary of descriptive statistics of the harmonised variable `freq_oh` accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.

**R script:**

```{r summ freq}

t.hds <- frq(l.hds[[1]][3])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][3])[[1]][,4] 
}
t.hds[14,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]])))
names(t.hds)<-c("val", "label", toupper(names(l.hds)))
kable(t.hds)

```



# Quality estimation

* Wave 2 for population AKSST has not harmonizable variable, since the unique related to alcohol, `tome17` (`Q4:QUIT DRINKING ALCOHOL`), does not seem appropiate.
* Past drinking cannot be harmonized.


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(l.hds)){
  alcohol <- l.hds[[index]]
  save(alcohol, file = paste0(datafolder,names(l.hds)[index],"/alcohol.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





