---
title: "Religious activity"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/religDS.Rmd'}
```


```{r global, echo=F}
source('../../_DS_Rmd/religDS.R')
```


<!-- ########################################################## --> 

# Data process

## Korea

### Wave 1

#### Study-specific variable description

The study-specific variables elected to be harmonised are:

* Name: `w01A017m01`
* Label: `Participating to the religious meeting`
* Categories: 
    + `0 = no`
    + `1 = yes`
    
* Name: `w01A019_01`
* Label: `The number of times which participates to the religious meeting`
* Categories:
    + `1 = Almost every day (more than 4 times per week)`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month (every two weeks)`
    + `6 = Once or twice a year`
    + `7 = Three or four times a year`
    + `8 = Five or six times a year`
    + `9 = Almost never a year`
    + `10 = Almost never`


* Description: 
```{r assign1, echo=F}
opal.assign.table.tibble(o,'KLOSA_w1_relig','KLOSA.w01_main_e',variables=list('w01A017m01','w01A019_01'), missings = TRUE)
```

```{r local1, echo=F}
KLOSA_w1_relig <- opal.execute(o,'KLOSA_w1_relig')
vari <- KLOSA_w1_relig$w01A017m01
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w1_relig$w01A017m01, missing_values = NA)
ggplot(KLOSA_w1_relig, aes(x=factor(w01A017m01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participating to the religious meeting") + ylab("Frequency")

vari <- KLOSA_w1_relig$w01A019_01
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w1_relig$w01A019_01, missing_values = NA)
ggplot(KLOSA_w1_relig, aes(x=factor(w01A019_01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The number of times which participates to the religious meeting") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if w01A017m01=1 and w01A019_01 in c(1,2,3,4,5,7,8) then 1`
* `if w01A017m01=0 or ( w01A017m01=1 and w01A019_01 in c(6,9,10) ) then 0`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
KLOSA_ds_w1 <- tibble(id=KLOSA_w1_relig$id)

KLOSA_w1_relig$w01A017m01 <- car::recode(as.vector(KLOSA_w1_relig$w01A017m01), "NA='-999'")
KLOSA_w1_relig$w01A019_01 <- car::recode(as.vector(KLOSA_w1_relig$w01A019_01), "NA='-999'")

KLOSA_ds_w1$relig <- c(NA)  
for(i in 1:dim(KLOSA_w1_relig)[1]){
  if( KLOSA_w1_relig$w01A017m01[i] == 1 & KLOSA_w1_relig$w01A019_01[i] %in% c(1:5,7,8) ) {
    KLOSA_ds_w1$relig[i] = 1 }
  else if( KLOSA_w1_relig$w01A017m01[i] == 0 | (KLOSA_w1_relig$w01A017m01[i] == 1 & KLOSA_w1_relig$w01A019_01[i] %in% c(6,9,10)) ) {
    KLOSA_ds_w1$relig[i] = 0 }
}

KLOSA_ds_w1$relig <- car::recode(as.vector(KLOSA_ds_w1$relig), "NA='999'")
KLOSA_ds_w1$relig <- labelled(KLOSA_ds_w1$relig, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <- KLOSA_ds_w1$relig
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w1$relig, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w1, aes(x=factor(relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Religious participation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(KLOSA_ds_w1$relig)
BeforeH <- table(KLOSA_w1_relig$w01A017m01, KLOSA_w1_relig$w01A019_01, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(sum(BeforeH[1,]), sum(BeforeH[2,c(7,10:11)]))
BeforeH1[[2]] <- sum(BeforeH[2,c(2:6,8,9)])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1")
kable(C)
```




### Wave 2

#### Study-specific variable description

The study-specific variables elected to be harmonised are:

* Name: `w02A033m01`
* Label: `Participating to the religious meeting`
* Categories: 
    + `0 = no`
    + `1 = yes`
    
* Name: `w02A035_01`
* Label: `The number of times which participates to the religious meeting`
* Categories:
    + `1 = Almost every day (more than 4 times per week)`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month (every two weeks)`
    + `6 = Once or twice a year`
    + `7 = Three or four times a year`
    + `8 = Five or six times a year`
    + `9 = Almost never a year`
    + `10 = Almost never`

* Description: 
```{r assign2, echo=F}
opal.assign.table.tibble(o,'KLOSA_w2_relig','KLOSA.w02_main_e_spss',variables=list('w02A033m01','w02A035_01'), missings = TRUE)
```

```{r local2, echo=F}
KLOSA_w2_relig <- opal.execute(o,'KLOSA_w2_relig')
vari <- KLOSA_w2_relig$w02A033m01
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w2_relig$w02A033m01, missing_values = NA)
ggplot(KLOSA_w2_relig, aes(x=factor(w02A033m01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participating to the religious meeting?") + ylab("Frequency")

vari <- KLOSA_w2_relig$w02A035_01
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w2_relig$w02A035_01, missing_values = NA)
ggplot(KLOSA_w2_relig, aes(x=factor(w02A035_01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The number of times which participates to the religious meeting") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if w02A033m01=1 and w02A035_01 in c(1,2,3,4,5,7,8) then 1`
* `if w02A033m01=0 or ( w02A033m01=1 and w02A035_01 in c(6,9,10) ) then 0`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
KLOSA_ds_w2 <- tibble(id=KLOSA_w2_relig$id)

KLOSA_w2_relig$w02A033m01 <- car::recode(as.vector(KLOSA_w2_relig$w02A033m01), "NA='-999'")
KLOSA_w2_relig$w02A035_01 <- car::recode(as.vector(KLOSA_w2_relig$w02A035_01), "NA='-999'")

KLOSA_ds_w2$relig <- c(NA)  
for(i in 1:dim(KLOSA_w2_relig)[1]){
  if( KLOSA_w2_relig$w02A033m01[i] == 1 & KLOSA_w2_relig$w02A035_01[i] %in% c(1:5,7,8) ) {
    KLOSA_ds_w2$relig[i] = 1 }
  else if( KLOSA_w2_relig$w02A033m01[i] == 0 | (KLOSA_w2_relig$w02A033m01[i] == 1 & KLOSA_w2_relig$w02A035_01[i] %in% c(6,9,10)) ) {
    KLOSA_ds_w2$relig[i] = 0 }
}

KLOSA_ds_w2$relig <- car::recode(as.vector(KLOSA_ds_w2$relig), "NA='999'")
KLOSA_ds_w2$relig <- labelled(KLOSA_ds_w2$relig, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}
vari <- KLOSA_ds_w2$relig
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w2$relig, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w2, aes(x=factor(relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Religious participation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
AfterH <- table(KLOSA_ds_w2$relig)
BeforeH <- table(KLOSA_w2_relig$w02A033m01, KLOSA_w2_relig$w02A035_01, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(sum(BeforeH[1,]), sum(BeforeH[2,c(7,10:11)]))
BeforeH1[[2]] <- sum(BeforeH[2,c(2:6,8,9)])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1")
kable(C)
```

 
 




### Wave 3

#### Study-specific variable description

The study-specific variables elected to be harmonised are:

* Name: `w03A033m01`
* Label: `Participating to the religious meeting?`
* Categories: 
    + `0 = no`
    + `1 = yes`
    
* Name: `w03A035_01`
* Label: `The number of times which participates to the religious meeting`
* Categories:
    + `1 = Almost every day (more than 4 times per week)`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month (every two weeks)`
    + `6 = Once or twice a year`
    + `7 = Three or four times a year`
    + `8 = Five or six times a year`
    + `9 = Almost never a year`
    + `10 = Almost never`


* Description: 
```{r assign3, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w3_relig','KLOSA.w03_main_e_spss_albert',variables=list('w03A033m01','w03A035_01'), missings = TRUE)
KLOSA_w3_relig <- opal.execute(o,'KLOSA_w3_relig')
# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_w3_relig$id <- substr(KLOSA_w3_relig$id,1,nchar(KLOSA_w3_relig$id)-2)
```

```{r local3, echo=F}
vari <- KLOSA_w3_relig$w03A033m01
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w3_relig$w03A033m01, missing_values = NA)
ggplot(KLOSA_w3_relig, aes(x=factor(w03A033m01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participating to the religious meeting?") + ylab("Frequency")

vari <- KLOSA_w3_relig$w03A035_01
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w3_relig$w03A035_01, missing_values = NA)
ggplot(KLOSA_w3_relig, aes(x=factor(w03A035_01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The number of times which participates to the religious meeting") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if w03A033m01=1 and w03A035_01 in c(1,2,3,4,5,7,8) then 1`
* `if w03A033m01=0 or ( w03A033m01=1 and w03A035_01 in c(6,9,10) ) then 0`
* `NA into 999`

**R script:**

```{r harmo3, echo=TRUE}
KLOSA_ds_w3 <- tibble(id=KLOSA_w3_relig$id)

KLOSA_w3_relig$w03A033m01 <- car::recode(as.vector(KLOSA_w3_relig$w03A033m01), "NA='-999'")
KLOSA_w3_relig$w03A035_01 <- car::recode(as.vector(KLOSA_w3_relig$w03A035_01), "NA='-999'")

KLOSA_ds_w3$relig <- c(NA)  
for(i in 1:dim(KLOSA_w3_relig)[1]){
  if( KLOSA_w3_relig$w03A033m01[i] == 1 & KLOSA_w3_relig$w03A035_01[i] %in% c(1:5,7,8) ) {
    KLOSA_ds_w3$relig[i] = 1 }
  else if( KLOSA_w3_relig$w03A033m01[i] == 0 | (KLOSA_w3_relig$w03A033m01[i] == 1 & KLOSA_w3_relig$w03A035_01[i] %in% c(6,9,10)) ) {
    KLOSA_ds_w3$relig[i] = 0 }
}

KLOSA_ds_w3$relig <- car::recode(as.vector(KLOSA_ds_w3$relig), "NA='999'")
KLOSA_ds_w3$relig <- labelled(KLOSA_ds_w3$relig, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=F}
vari <- KLOSA_ds_w3$relig
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w3$relig, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w3, aes(x=factor(relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Religious participation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=F}
AfterH <- table(KLOSA_ds_w3$relig)
BeforeH <- table(KLOSA_w3_relig$w03A033m01, KLOSA_w3_relig$w03A035_01, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(sum(BeforeH[1,]), sum(BeforeH[2,c(7,10:11)]))
BeforeH1[[2]] <- sum(BeforeH[2,c(2:6,8,9)])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1")
kable(C)
```

 
 



### Wave 4

#### Study-specific variable description

The study-specific variables elected to be harmonised are:

* Name: `w04A033m01`
* Label: `Participating to the religious meeting?`
* Categories: 
    + `0 = no`
    + `1 = yes`
    
* Name: `w04A035_01`
* Label: `The number of times which participates to the religious meeting`
* Categories:
    + `1 = Almost every day (more than 4 times per week)`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month (every two weeks)`
    + `6 = Once or twice a year`
    + `7 = Three or four times a year`
    + `8 = Five or six times a year`
    + `9 = Almost never a year`
    + `10 = Almost never`


* Description: 
```{r assign4, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w4_relig','KLOSA.w04_main_e_spss',variables=list('w04A033m01','w04A035_01'), missings = TRUE)
```

```{r local4, echo=F}
KLOSA_w4_relig <- opal.execute(o,'KLOSA_w4_relig')

vari <- KLOSA_w4_relig$w04A033m01
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w4_relig$w04A033m01, missing_values = NA)
ggplot(KLOSA_w4_relig, aes(x=factor(w04A033m01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participating to the religious meeting?") + ylab("Frequency")

vari <- KLOSA_w4_relig$w04A035_01
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w4_relig$w04A035_01, missing_values = NA)
ggplot(KLOSA_w4_relig, aes(x=factor(w04A035_01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The number of times which participates to the religious meeting") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if w04A033m01=1 and w04A035_01 in c(1,2,3,4,5,7,8) then 1`
* `if w04A033m01=0 or ( w04A033m01=1 and w04A035_01 in c(6,9,10) ) then 0`
* `NA into 999`

**R script:**

```{r harmo4, echo=TRUE}
KLOSA_ds_w4 <- tibble(id=KLOSA_w4_relig$id)

KLOSA_w4_relig$w04A033m01 <- car::recode(as.vector(KLOSA_w4_relig$w04A033m01), "NA='-999'")
KLOSA_w4_relig$w04A035_01 <- car::recode(as.vector(KLOSA_w4_relig$w04A035_01), "NA='-999'")

KLOSA_ds_w4$relig <- c(NA)  
for(i in 1:dim(KLOSA_w4_relig)[1]){
  if( KLOSA_w4_relig$w04A033m01[i] == 1 & KLOSA_w4_relig$w04A035_01[i] %in% c(1:5,7,8) ) {
    KLOSA_ds_w4$relig[i] = 1 }
  else if( KLOSA_w4_relig$w04A033m01[i] == 0 | (KLOSA_w4_relig$w04A033m01[i] == 1 & KLOSA_w4_relig$w04A035_01[i] %in% c(6,9,10)) ) {
    KLOSA_ds_w4$relig[i] = 0 }
}

KLOSA_ds_w4$relig <- car::recode(as.vector(KLOSA_ds_w4$relig), "NA='999'")
KLOSA_ds_w4$relig <- labelled(KLOSA_ds_w4$relig, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4, echo=F}
vari <- KLOSA_ds_w4$relig
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w4$relig, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w4, aes(x=factor(relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Religious participation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=F}
AfterH <- table(KLOSA_ds_w4$relig)
BeforeH <- table(KLOSA_w4_relig$w04A033m01, KLOSA_w4_relig$w04A035_01, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(sum(BeforeH[1,]), sum(BeforeH[2,c(7,10:11)]))
BeforeH1[[2]] <- sum(BeforeH[2,c(2:6,8,9)])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1")
kable(C)
```

 

```{r save, echo=FALSE}
relig <- KLOSA_ds_w1
save(relig, file = "../RData/w1/relig.RData")
rm(relig)

relig <- KLOSA_ds_w2
save(relig, file = "../RData/w2/relig.RData")
rm(relig)

relig <- KLOSA_ds_w3
save(relig, file = "../RData/w3/relig.RData")
rm(relig)


relig <- KLOSA_ds_w4
save(relig, file = "../RData/w4/relig.RData")
rm(relig)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```

