---
title: "Has friend(s)/confidant"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `confidant`
* Variable label: `Has friend(s)/confidant`
* Domain: `Social environment`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 

# Data process

## Korea

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w01A016`
* Label: `The Number of times that meet with the familiar`
* Categories: 
    + `1 = Almost every day (more than 4 times per week)`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month (every two weeks)`
    + `6 = Once or twice a year`
    + `7 = Three or four times a year (once every three or four months)`
    + `8 = Five or six times a year (every two months)`
    + `9 = Almost never`
    + `10 = No close friend or relative`

* Description: 
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w1_confidant','KLOSA.w01_main_e', variables=list('w01A016'), missings = TRUE)
```

```{r local1, echo=F}
KLOSA_w1_confidant <- opal.execute(o,'KLOSA_w1_confidant')
vari <- KLOSA_w1_confidant$w01A016
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w1_confidant$w01A016, missing_values = NA)
ggplot(KLOSA_w1_confidant, aes(x=factor(w01A016))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The Number of times that meet with the familiar") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1:9 into 1`
* `10 into 0`
* `NA into 999`

 

**R script:** 
```{r harmo1, echo=TRUE}
KLOSA_ds_w1 <- tibble(id=KLOSA_w1_confidant$id)
KLOSA_ds_w1$confidant <- car::recode(as.vector(KLOSA_w1_confidant$w01A016), "1:9='1'; 10='0'; NA='999'")
KLOSA_ds_w1$confidant <- labelled(KLOSA_ds_w1$confidant, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <- KLOSA_ds_w1$confidant
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w1$confidant, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w1, aes(x=factor(confidant))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has friend(s)/confidant(s)?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(KLOSA_ds_w1$confidant)
BeforeH <- table(KLOSA_w1_confidant$w01A016, useNA='ifany')
BeforeH[[2]] <- sum(BeforeH[[1]],BeforeH[[2]],BeforeH[[3]],BeforeH[[4]],BeforeH[[5]],BeforeH[[6]],BeforeH[[7]],BeforeH[[8]],BeforeH[[9]])
BeforeH <- BeforeH[c(10,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("10->0","1")
kable(C)
```

 
 


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w02A032`
* Label: `How often meeting with familiar people`
* Categories: 
    + `1 = Almost every day (more than 4 times per week)`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month (every two weeks)`
    + `6 = Once or twice a year`
    + `7 = Three or four times a year (once every three or four months)`
    + `8 = Five or six times a year (every two months)`
    + `9 = Almost never`
    + `10 = No close friend or relative`

* Description: 
```{r assign2, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w2_confidant','KLOSA.w02_main_e_spss',variables=list('w02A032'), missings = TRUE)
```

```{r local2, echo=F}
KLOSA_w2_confidant <- opal.execute(o,'KLOSA_w2_confidant')
vari <- KLOSA_w2_confidant$w02A032
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w2_confidant$w02A032, missing_values = NA)
ggplot(KLOSA_w2_confidant, aes(x=factor(w02A032))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How often meeting with familiar people") + ylab("Frequency")

```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1:9 into 1`
* `10 into 0`
* `NA into 999`

 

**R script:** 
```{r harmo2, echo=TRUE}
KLOSA_ds_w2 <- tibble(id=KLOSA_w2_confidant$id)
KLOSA_ds_w2$confidant <- car::recode(as.vector(KLOSA_w2_confidant$w02A032), "1:9='1'; 10='0'; NA='999'")
KLOSA_ds_w2$confidant <- labelled(KLOSA_ds_w2$confidant, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}
vari <- KLOSA_ds_w2$confidant
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w2$confidant, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w2, aes(x=factor(confidant))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has friend(s)/confidant(s)?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
AfterH <- table(KLOSA_ds_w2$confidant)
BeforeH <- table(KLOSA_w2_confidant$w02A032, useNA='ifany')
BeforeH[[2]] <- sum(BeforeH[[1]],BeforeH[[2]],BeforeH[[3]],BeforeH[[4]],BeforeH[[5]],BeforeH[[6]],BeforeH[[7]],BeforeH[[8]],BeforeH[[9]])
BeforeH <- BeforeH[c(10,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("10->0","1")
kable(C)
```

 
 


### Wave 3

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w03A032`
* Label: `The Number of times that meet with the familiar`
* Categories: 
    + `1 = Almost every day (more than 4 times per week)`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month (every two weeks)`
    + `6 = Once or twice a year`
    + `7 = Three or four times a year (once every three or four months)`
    + `8 = Five or six times a year (every two months)`
    + `9 = Almost never`
    + `10 = No close friend or relative`

* Description: 
```{r assign3, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w3_confidant','KLOSA.w03_main_e_spss_albert',variables=list('w03A032'), missings = TRUE)
KLOSA_w3_confidant <- opal.execute(o,'KLOSA_w3_confidant')
# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_w3_confidant$id <- substr(KLOSA_w3_confidant$id,1,nchar(KLOSA_w3_confidant$id)-2)
```

```{r local3, echo=F}
vari <- KLOSA_w3_confidant$w03A032
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w3_confidant$w03A032, missing_values = NA)
ggplot(KLOSA_w3_confidant, aes(x=factor(w03A032))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The Number of times that meet with the familiar") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1:9 into 1`
* `10 into 0`
* `NA into 999`

 

**R script:** 
```{r harmo3, echo=TRUE}
KLOSA_ds_w3 <- tibble(id=KLOSA_w3_confidant$id)
KLOSA_ds_w3$confidant <- car::recode(as.vector(KLOSA_w3_confidant$w03A032), "1:9='1'; 10='0'; NA='999'")
KLOSA_ds_w3$confidant <- labelled(KLOSA_ds_w3$confidant, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=F}
vari <- KLOSA_ds_w3$confidant
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w3$confidant, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w3, aes(x=factor(confidant))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Has friend(s)/confidant(s)?") + ylab("Frequency")
```

##### Validation
```{r crosstabulation3, echo=F}
AfterH <- table(KLOSA_ds_w3$confidant)
BeforeH <- table(KLOSA_w3_confidant$w03A032, useNA='ifany')
BeforeH[[2]] <- sum(BeforeH[[1]],BeforeH[[2]],BeforeH[[3]],BeforeH[[4]],BeforeH[[5]],BeforeH[[6]],BeforeH[[7]],BeforeH[[8]],BeforeH[[9]])
BeforeH <- BeforeH[c(10,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("10->0","1")
kable(C)
```

 
 

### Wave 4

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w04A032`
* Label: `The Number of times that meet with the familiar`
* Categories: 
    + `1 = Almost every day (more than 4 times per week)`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month (every two weeks)`
    + `6 = Once or twice a year`
    + `7 = Three or four times a year (once every three or four months)`
    + `8 = Five or six times a year (every two months)`
    + `9 = Almost never`
    + `10 = No close friend or relative`

* Description: 
```{r assign4, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w4_confidant','KLOSA.w04_main_e_spss',variables=list('w04A032'), missings = TRUE)
```

```{r local4, echo=F}
KLOSA_w4_confidant <- opal.execute(o,'KLOSA_w4_confidant')
vari <- KLOSA_w4_confidant$w04A032
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w4_confidant$w04A032, missing_values = NA)
ggplot(KLOSA_w4_confidant, aes(x=factor(w04A032))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The Number of times that meet with the familiar") + ylab("Frequency")

```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1:9 into 1`
* `10 into 0`
* `NA into 999`

 

**R script:** 
```{r harmo4, echo=TRUE}
KLOSA_ds_w4 <- tibble(id=KLOSA_w4_confidant$id)
KLOSA_ds_w4$confidant <- car::recode(as.vector(KLOSA_w4_confidant$w04A032), "1:9='1'; 10='0'; NA='999'")
KLOSA_ds_w4$confidant <- labelled(KLOSA_ds_w4$confidant, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4, echo=F}
vari <- KLOSA_ds_w4$confidant
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w4$confidant, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w4, aes(x=factor(confidant))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has friend(s)/confidant(s)?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=F}
AfterH <- table(KLOSA_ds_w4$confidant)
BeforeH <- table(KLOSA_w4_confidant$w04A032, useNA='ifany')
BeforeH[[2]] <- sum(BeforeH[[1]],BeforeH[[2]],BeforeH[[3]],BeforeH[[4]],BeforeH[[5]],BeforeH[[6]],BeforeH[[7]],BeforeH[[8]],BeforeH[[9]])
BeforeH <- BeforeH[c(10,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("10->0","1")
kable(C)
```


```{r save, echo=FALSE}
confidant <- KLOSA_ds_w1
save(confidant, file = "../RData/w1/confidant.RData")
rm(confidant)

confidant <- KLOSA_ds_w2
save(confidant, file = "../RData/w2/confidant.RData")
rm(confidant)

confidant <- KLOSA_ds_w3
save(confidant, file = "../RData/w3/confidant.RData")
rm(confidant)

confidant <- KLOSA_ds_w4
save(confidant, file = "../RData/w4/confidant.RData")
rm(confidant)
```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
