---
title: "Divorce/Separation"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/divorceDS.Rmd'}
```


```{r global, echo=F}
source('../../_DS_Rmd/divorceDS.R')
```

<!-- ########################################################## --> 

# Data process

## Korea

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w01A006`
* Label: `Currently marital status`
* Categories: 
    + `1 = Currently married or living with a partner`
    + `2 = Separated`
    + `3 = Divorced`
    + `4 = Widowed or missing (dispersed family)`
    + `5 = Never married`
* Missings:
    + `-8 = Refuse to answer`

* Description: 
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w1_divorce','KLOSA.w01_main_e',variables=list('W01A006'), missings = TRUE)
```

```{r local1, echo=F}
KLOSA_w1_divorce <- opal.execute(o,'KLOSA_w1_divorce')
vari <- KLOSA_w1_divorce$W01A006
kable(Categorical_summary(vari, missing_values = c(-8))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-8))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-8))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_w1_divorce$W01A006, missing_values = NA)
ggplot(KLOSA_w1_divorce, aes(x=factor(W01A006))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `2,3 into 1`
* `1,4,5 into 0`
* `-8 Refuse into 997`
* `NA into 999`

**R script:**

```{r harmo1}
KLOSA_ds_w1 <- tibble(id=KLOSA_w1_divorce$id)
KLOSA_ds_w1$divorce <- car::recode(as.vector(KLOSA_w1_divorce$W01A006), "2:3='1'; 1='0'; 4:5='0'; -8='997'; NA='999'")
KLOSA_ds_w1$divorce <- labelled(KLOSA_ds_w1$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <- KLOSA_ds_w1$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w1$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w1, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(KLOSA_ds_w1$divorce)
BeforeH <- table(KLOSA_w1_divorce$W01A006, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- sum(BeforeH[c(2,3)])
BeforeH1[[1]] <- sum(BeforeH[c(1,4,5)])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1&4&5->0","2&3->1")
kable(C)
```




### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w02marital`
* Label: `In 2008, currently the respondont's marital status`
* Categories: 
    + `1 = Currently married or living with a partner (i.e., common-law marriage)`
    + `2 = Separated`
    + `3 = Divorced`
    + `4 = Widowed or missing (dispersed family)`
    + `5 = Never been married`
    
* Name: `divorce` **harmonized in Wave1**  


* Description: 
```{r assign2, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w2_divorce','KLOSA.w02_main_e_spss',variables=list('w02marital'), missings = TRUE)
```

```{r local2, echo=F}
KLOSA_w2_divorce <- opal.execute(o,'KLOSA_w2_divorce')
vari <- KLOSA_w2_divorce$w02marital
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w2_divorce$w02marital, missing_values = NA)
ggplot(KLOSA_w2_divorce, aes(x=factor(w02marital))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `divorce=1 or w02marital=2 or 3 - into 1`
* `divorce=0 and w02marital in {1,4,5} - into 0`
* `NA into 999`

**R script:**

```{r harmo2}
same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  colnames(new_2) <- colnames(old)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], rep_len(NA,dim(old)[2]-1))
    }
  }
  new_2 <- data.frame(new_2)
  new_22 <- data.frame(id=new_2$id, w02marital=new$w02marital, divorce=new_2$divorce)  # divorce(W1), w02marital(W2)
  new_22
}

# old = KLOSA_ds_w1
# new = KLOSA_w2_divorce

KLOSA_merge_w12 <- same_indiv(KLOSA_ds_w1, KLOSA_w2_divorce)
KLOSA_ds_w2 <- tibble(id=KLOSA_merge_w12$id)

KLOSA_merge_w12$divorce <- car::recode(as.vector(KLOSA_merge_w12$divorce), "NA='-999'")
KLOSA_merge_w12$w02marital <- car::recode(as.vector(KLOSA_merge_w12$w02marital), "NA='-999'")

KLOSA_ds_w2$divorce <- c(NA)
for(i in 1:dim(KLOSA_merge_w12)[1]){
  if( KLOSA_merge_w12$divorce[i] == 1 | KLOSA_merge_w12$w02marital[i] %in% c(2,3) ) {
    KLOSA_ds_w2$divorce[i] = 1 }
  else if( KLOSA_merge_w12$divorce[i] == 0 & KLOSA_merge_w12$w02marital[i] %in% c(1,4,5) ) { 
    KLOSA_ds_w2$divorce[i] = 0 }
}

KLOSA_ds_w2$divorce <- car::recode(as.vector(KLOSA_ds_w2$divorce), "NA='999'")
KLOSA_ds_w2$divorce <- labelled(KLOSA_ds_w2$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}
vari <- KLOSA_ds_w2$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w2$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w2, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
AfterH <- table(KLOSA_ds_w2$divorce)
BeforeH <- table(KLOSA_merge_w12$w02marital, KLOSA_merge_w12$divorce, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- sum(sum(BeforeH[c(2,3),1]),sum(BeforeH[,2]))
BeforeH1[[1]] <- sum(BeforeH[c(1,4,5),1])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1")
kable(C)
```



### Wave 3

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w03marital`
* Label: `In 2010, the respondont's marital status`
* Categories: 
    + `1 = Currently married or living with a partner (i.e., common-law marriage)`
    + `2 = Separated`
    + `3 = Divorced`
    + `4 = Widowed or missing (dispersed family)`
    + `5 = Never been married`
    
* Name: `divorce` **harmonized in Wave2**  


* Description: 
```{r assign3, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w3_divorce','KLOSA.w03_main_e_spss_albert',variables=list('w03marital'), missings = TRUE)
KLOSA_w3_divorce <- opal.execute(o,'KLOSA_w3_divorce')
# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_w3_divorce$id <- substr(KLOSA_w3_divorce$id,1,nchar(KLOSA_w3_divorce$id)-2)
```

```{r local3, echo=F}
vari <- KLOSA_w3_divorce$w03marital
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w3_divorce$w03marital, missing_values = NA)
ggplot(KLOSA_w3_divorce, aes(x=factor(w03marital))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `divorce=1 or w03marital=2 or 3 - into 1`
* `divorce=0 and w03marital in {1,4,5} - into 0`
* `NA into 999`

**R script:**

```{r harmo3}
same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  colnames(new_2) <- colnames(old)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], rep_len(NA,dim(old)[2]-1))
    }
  }
  new_2 <- data.frame(new_2)
  new_22 <- data.frame(id=new_2$id, w03marital=new$w03marital, divorce=new_2$divorce)  # divorce(W2), w03marital(W3)
  new_22
}

# old = KLOSA_ds_w2
# new = KLOSA_w3_divorce

KLOSA_merge_w23 <- same_indiv(KLOSA_ds_w2, KLOSA_w3_divorce)
KLOSA_ds_w3 <- tibble(id=KLOSA_merge_w23$id)

KLOSA_merge_w23$divorce <- car::recode(as.vector(KLOSA_merge_w23$divorce), "NA='-999'")
KLOSA_merge_w23$w03marital <- car::recode(as.vector(KLOSA_merge_w23$w03marital), "NA='-999'")

KLOSA_ds_w3 <- tibble(id=KLOSA_w3_divorce$id)

KLOSA_ds_w3$divorce <- c(NA)
for(i in 1:dim(KLOSA_merge_w23)[1]){
  if( KLOSA_merge_w23$divorce[i] == 1 | KLOSA_merge_w23$w03marital[i] %in% c(2,3) ) {
    KLOSA_ds_w3$divorce[i] = 1 }
  else if( KLOSA_merge_w23$w03marital[i] %in% c(1,4,5) ) { 
    KLOSA_ds_w3$divorce[i] = 0 }
}

KLOSA_ds_w3$divorce <- car::recode(as.vector(KLOSA_ds_w3$divorce), "NA='999'")
KLOSA_ds_w3$divorce <- labelled(KLOSA_ds_w3$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=F}
vari <- KLOSA_ds_w3$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w3$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w3, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Experience of divorce/separation") + ylab("Frequency")
```

##### Validation
```{r crosstabulation3, echo=F}
AfterH <- table(KLOSA_ds_w3$divorce)
BeforeH <- table(KLOSA_merge_w23$w03marital, KLOSA_merge_w23$divorce, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- sum(BeforeH[c(2,3),1])
BeforeH1[[1]] <- sum(BeforeH[c(1,4,5),1])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1")
kable(C)
```


### Wave 4

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w04marital`
* Label: `In 2012, the respondont's marital status`
* Categories: 
    + `1 = Currently married or living with a partner (i.e., common-law marriage)`
    + `2 = Separated`
    + `3 = Divorced`
    + `4 = Widowed or missing (dispersed family)`
    + `5 = Never been married`
    
* Name: `divorce` **harmonized in Wave3**


* Description: 
```{r assign4, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w4_divorce','KLOSA.w04_main_e_spss',variables=list('w04marital'), missings = TRUE)
```

```{r local4, echo=F}
KLOSA_w4_divorce <- opal.execute(o,'KLOSA_w4_divorce')
vari <- KLOSA_w4_divorce$w04marital
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w4_divorce$w04marital, missing_values = NA)
ggplot(KLOSA_w4_divorce, aes(x=factor(w04marital))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `divorce=1 or w04marital=2 or 3 - into 1`
* `divorce=0 and w04marital in {1,4,5} - into 0`
* `NA into 999`

**R script:**

```{r harmo4}
same_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  colnames(new_2) <- colnames(old)
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], rep_len(NA,dim(old)[2]-1))
    }
  }
  new_2 <- data.frame(new_2)
  new_22 <- data.frame(id=new_2$id, w04marital=new$w04marital, divorce=new_2$divorce)  # divorce(W3), w04marital(W4)
  new_22
}

# old = KLOSA_ds_w3
# new = KLOSA_w4_divorce

KLOSA_merge_w34 <- same_indiv(KLOSA_ds_w3, KLOSA_w4_divorce)

KLOSA_merge_w34$divorce <- car::recode(as.vector(KLOSA_merge_w34$divorce), "NA='-999'")
KLOSA_merge_w34$w04marital <- car::recode(as.vector(KLOSA_merge_w34$w04marital), "NA='-999'")


KLOSA_ds_w4 <- tibble(id=KLOSA_w4_divorce$id)

KLOSA_ds_w4$divorce <- c(NA)
for(i in 1:dim(KLOSA_merge_w34)[1]){
  if( KLOSA_merge_w34$divorce[i] == 1 | KLOSA_merge_w34$w04marital[i] %in% c(2,3) ) {
    KLOSA_ds_w4$divorce[i] = 1 }
  else if( KLOSA_merge_w34$w04marital[i] %in% c(1,4,5) ) { 
    KLOSA_ds_w4$divorce[i] = 0 }
}

KLOSA_ds_w4$divorce <- car::recode(as.vector(KLOSA_ds_w4$divorce), "NA='999'")
KLOSA_ds_w4$divorce <- labelled(KLOSA_ds_w4$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4, echo=F}
vari <- KLOSA_ds_w4$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w4$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w4, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=F}
AfterH <- table(KLOSA_ds_w4$divorce)
BeforeH <- table(KLOSA_merge_w34$w04marital, KLOSA_merge_w34$divorce, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- sum(BeforeH[c(2,3),1])
BeforeH1[[1]] <- sum(BeforeH[c(1,4,5),1])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1")
kable(C)
```



```{r save, echo=FALSE}
divorce <- KLOSA_ds_w1
save(divorce, file = "../RData/w1/divorce.RData")
rm(divorce)

divorce <- KLOSA_ds_w2
save(divorce, file = "../RData/w2/divorce.RData")
rm(divorce)

divorce <- KLOSA_ds_w3
save(divorce, file = "../RData/w3/divorce.RData")
rm(divorce)


divorce <- KLOSA_ds_w4
save(divorce, file = "../RData/w4/divorce.RData")
rm(divorce)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```





