---
title: "Has other (living) family members (e.g. parents, siblings, in-laws, etc.)"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/oth_famDS.Rmd'}
```


```{r global, echo=F}
source('../../_DS_Rmd/oth_famDS.R')
```

<!-- ########################################################## --> 

# Data process

## Korea

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w01B001`
* Label: `The number of living siblings`
* Missings: 
    + `-8 = Refuse to answer`
    + `-9 = Do not know`
    
* Name: `w01B010`
* Label: `Father's survival`
* Categories:
    + `1 = Yes`
    + `3 = Missing (Dispersed family)`
    + `5 = No`
    
* Name: `w01B020`
* Label: `Mother's survival`
* Categories:
    + `1 = Yes`
    + `3 = Missing (Dispersed family)`
    + `5 = No`
    

* Description: 
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w1_oth_fam','KLOSA.w01_main_e', 
                        variables=list('w01B001','w01B010','w01B020'), missings = TRUE)
```

```{r local1, echo=F}
KLOSA_w1_oth_fam <- opal.execute(o,'KLOSA_w1_oth_fam')
vari <- KLOSA_w1_oth_fam$w01B001
kable(Continuous_summary(var = vari, missing_values = c(-8,-9))[3], caption = attributes(vari)$`spss::shortName`)
kable(Continuous_summary(vari, missing_values = c(-8,-9))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-8,-9))$summary, caption = "Summary")
#Continuous_summary(var = KLOSA_w1_oth_fam$w01B001, missing_values = NA)
ggplot(KLOSA_w1_oth_fam, aes(x=factor(w01B001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The number of living siblings") + ylab("Frequency")

vari <-  KLOSA_w1_oth_fam$w01B010
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w1_oth_fam$w01B010, missing_values = NA)
ggplot(KLOSA_w1_oth_fam, aes(x=factor(w01B010))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Father's survival") + ylab("Frequency")

vari <- KLOSA_w1_oth_fam$w01B020
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w1_oth_fam$w01B020, missing_values = NA)
ggplot(KLOSA_w1_oth_fam, aes(x=factor(w01B020))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mother's survival") + ylab("Frequency")


## There is a lot of NAs in w01B001
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if w01B001>0 or w01B010=1 or w01B020=1 then 1`
* `if w01B001=0 and w01B010 in {3,5} and w01B020 in {3,5} then 0`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
KLOSA_ds_w1 <- tibble(id=KLOSA_w1_oth_fam$id)

KLOSA_w1_oth_fam$w01B001 <- car::recode(as.vector(KLOSA_w1_oth_fam$w01B001), "NA='-999'")
KLOSA_w1_oth_fam$w01B010 <- car::recode(as.vector(KLOSA_w1_oth_fam$w01B010), "NA='-999'")
KLOSA_w1_oth_fam$w01B020 <- car::recode(as.vector(KLOSA_w1_oth_fam$w01B020), "NA='-999'")

KLOSA_ds_w1$oth_fam <- c(NA) 
for(i in 1:dim(KLOSA_w1_oth_fam)[1]){
  if(KLOSA_w1_oth_fam$w01B001[i] >0 | KLOSA_w1_oth_fam$w01B010[i] == 1 | KLOSA_w1_oth_fam$w01B020[i] == 1 ){
    KLOSA_ds_w1$oth_fam[i] = 1 } 
  else if(KLOSA_w1_oth_fam$w01B001[i] == 0 & KLOSA_w1_oth_fam$w01B010[i] %in% c(3,5) & KLOSA_w1_oth_fam$w01B020[i] %in% c(3,5) ){
    KLOSA_ds_w1$oth_fam[i] = 0 }
  else if(KLOSA_w1_oth_fam$w01B001[i] == -8 ){
    KLOSA_ds_w1$oth_fam[i] = 997 }
  else if(KLOSA_w1_oth_fam$w01B001[i] == -9 ){
    KLOSA_ds_w1$oth_fam[i] = 998 }
}

KLOSA_ds_w1$oth_fam <- car::recode(as.vector(KLOSA_ds_w1$oth_fam), "NA='999'")
KLOSA_ds_w1$oth_fam <- labelled(KLOSA_ds_w1$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <-  KLOSA_ds_w1$oth_fam
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w1$oth_fam, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w1, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}

```

 
 


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w02Bb001_01` UP TO `w02Bb001_14`
* Label: `1st sibling existence` UP TO `14th sibling existence`
* Categories: 
    + `1 = yes`
    + `5 = no (passed away)`
    
* Name: `w02Bb004`
* Label: `Father existence`
* Categories:
    + `1 = Yes`
    + `5 = No (passed away)`
    
* Name: `w02Bb010`
* Label: `Mother existence`
* Categories:
    + `1 = Yes`
    + `5 = No (passed away)`

* Description: 
```{r assign2, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w2_oth_fam','KLOSA.w02_main_e_spss',
                         variables=list('w02Bb001_01','w02Bb001_02','w02Bb001_03','w02Bb001_04',
                                        'w02Bb001_05','w02Bb001_06','w02Bb001_07','w02Bb001_08',
                                        'w02Bb001_09','w02Bb001_10','w02Bb001_11','w02Bb001_12',
                                        'w02Bb001_13','w02Bb001_14','w02Bb004','w02Bb010'), missings = TRUE)
```

```{r local2, echo=F}
KLOSA_w2_oth_fam <- opal.execute(o,'KLOSA_w2_oth_fam')
vari <- KLOSA_w2_oth_fam$w02Bb001_01
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w2_oth_fam$w02Bb001_01, missing_values = NA)
ggplot(KLOSA_w2_oth_fam, aes(x=factor(w02Bb001_01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("1st sibling existence") + ylab("Frequency")
vari <- KLOSA_w2_oth_fam$w02Bb004
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w2_oth_fam$w02Bb004, missing_values = NA)
ggplot(KLOSA_w2_oth_fam, aes(x=factor(w02Bb004))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Father existence") + ylab("Frequency")
vari <- KLOSA_w2_oth_fam$w02Bb010
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w2_oth_fam$w02Bb010, missing_values = NA)
ggplot(KLOSA_w2_oth_fam, aes(x=factor(w02Bb010))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mother existence") + ylab("Frequency")

## A lot of NAs in w02Bb004 and w02Bb010
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if any variable equals 1 then 1`
* `if for father and mother equals 5 and for siblings !=1 then 0`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
KLOSA_ds_w2 <- tibble(id=KLOSA_w2_oth_fam$id)

KLOSA_w2_oth_fam$w02Bb001_01 <- car::recode(as.vector(KLOSA_w2_oth_fam$w02Bb001_01), "NA='-999'")
KLOSA_w2_oth_fam$w02Bb001_02 <- car::recode(as.vector(KLOSA_w2_oth_fam$w02Bb001_02), "NA='-999'")
KLOSA_w2_oth_fam$w02Bb001_03 <- car::recode(as.vector(KLOSA_w2_oth_fam$w02Bb001_03), "NA='-999'")
KLOSA_w2_oth_fam$w02Bb001_04 <- car::recode(as.vector(KLOSA_w2_oth_fam$w02Bb001_04), "NA='-999'")
KLOSA_w2_oth_fam$w02Bb001_05 <- car::recode(as.vector(KLOSA_w2_oth_fam$w02Bb001_05), "NA='-999'")
KLOSA_w2_oth_fam$w02Bb001_06 <- car::recode(as.vector(KLOSA_w2_oth_fam$w02Bb001_06), "NA='-999'")
KLOSA_w2_oth_fam$w02Bb001_07 <- car::recode(as.vector(KLOSA_w2_oth_fam$w02Bb001_07), "NA='-999'")
KLOSA_w2_oth_fam$w02Bb001_08 <- car::recode(as.vector(KLOSA_w2_oth_fam$w02Bb001_08), "NA='-999'")
KLOSA_w2_oth_fam$w02Bb001_09 <- car::recode(as.vector(KLOSA_w2_oth_fam$w02Bb001_09), "NA='-999'")
KLOSA_w2_oth_fam$w02Bb001_10 <- car::recode(as.vector(KLOSA_w2_oth_fam$w02Bb001_10), "NA='-999'")
KLOSA_w2_oth_fam$w02Bb001_11 <- car::recode(as.vector(KLOSA_w2_oth_fam$w02Bb001_11), "NA='-999'")
KLOSA_w2_oth_fam$w02Bb001_12 <- car::recode(as.vector(KLOSA_w2_oth_fam$w02Bb001_12), "NA='-999'")
KLOSA_w2_oth_fam$w02Bb001_13 <- car::recode(as.vector(KLOSA_w2_oth_fam$w02Bb001_13), "NA='-999'")
KLOSA_w2_oth_fam$w02Bb001_14 <- car::recode(as.vector(KLOSA_w2_oth_fam$w02Bb001_14), "NA='-999'")
KLOSA_w2_oth_fam$w02Bb004 <- car::recode(as.vector(KLOSA_w2_oth_fam$w02Bb004), "NA='-999'")
KLOSA_w2_oth_fam$w02Bb010 <- car::recode(as.vector(KLOSA_w2_oth_fam$w02Bb010), "NA='-999'")

KLOSA_ds_w2$oth_fam <- c(NA) 
for(i in 1:dim(KLOSA_w2_oth_fam)[1]){
  if( KLOSA_w2_oth_fam$w02Bb001_01[i]==1 | KLOSA_w2_oth_fam$w02Bb001_02[i]==1 | KLOSA_w2_oth_fam$w02Bb001_03[i]==1 | 
      KLOSA_w2_oth_fam$w02Bb001_04[i]==1 | KLOSA_w2_oth_fam$w02Bb001_05[i]==1 | KLOSA_w2_oth_fam$w02Bb001_06[i]==1 | 
      KLOSA_w2_oth_fam$w02Bb001_07[i]==1 | KLOSA_w2_oth_fam$w02Bb001_08[i]==1 | KLOSA_w2_oth_fam$w02Bb001_09[i]==1 | 
      KLOSA_w2_oth_fam$w02Bb001_10[i]==1 | KLOSA_w2_oth_fam$w02Bb001_11[i]==1 | KLOSA_w2_oth_fam$w02Bb001_12[i]==1 | 
      KLOSA_w2_oth_fam$w02Bb001_13[i]==1 | KLOSA_w2_oth_fam$w02Bb001_14[i]==1 | 
      KLOSA_w2_oth_fam$w02Bb004[i]==1 | KLOSA_w2_oth_fam$w02Bb010[i]==1 ){
    KLOSA_ds_w2$oth_fam[i] = 1 }
  else if( KLOSA_w2_oth_fam$w02Bb001_01[i]== -999 & KLOSA_w2_oth_fam$w02Bb001_02[i]== -999 & KLOSA_w2_oth_fam$w02Bb001_03[i]== -999 & 
      KLOSA_w2_oth_fam$w02Bb001_04[i]== -999 & KLOSA_w2_oth_fam$w02Bb001_05[i]== -999 & KLOSA_w2_oth_fam$w02Bb001_06[i]== -999 & 
      KLOSA_w2_oth_fam$w02Bb001_07[i]== -999 & KLOSA_w2_oth_fam$w02Bb001_08[i]== -999 & KLOSA_w2_oth_fam$w02Bb001_09[i]== -999 & 
      KLOSA_w2_oth_fam$w02Bb001_10[i]== -999 & KLOSA_w2_oth_fam$w02Bb001_11[i]== -999 & KLOSA_w2_oth_fam$w02Bb001_12[i]== -999 & 
      KLOSA_w2_oth_fam$w02Bb001_13[i]== -999 & KLOSA_w2_oth_fam$w02Bb001_14[i]== -999 &
      KLOSA_w2_oth_fam$w02Bb004[i] == -999 & KLOSA_w2_oth_fam$w02Bb010[i] == -999 ){
    KLOSA_ds_w2$oth_fam[i] = 999 }
  else if( !(KLOSA_w2_oth_fam$w02Bb001_01[i]==1 | KLOSA_w2_oth_fam$w02Bb001_02[i]==1 | KLOSA_w2_oth_fam$w02Bb001_03[i]==1 | 
      KLOSA_w2_oth_fam$w02Bb001_04[i]==1 | KLOSA_w2_oth_fam$w02Bb001_05[i]==1 | KLOSA_w2_oth_fam$w02Bb001_06[i]==1 | 
      KLOSA_w2_oth_fam$w02Bb001_07[i]==1 | KLOSA_w2_oth_fam$w02Bb001_08[i]==1 | KLOSA_w2_oth_fam$w02Bb001_09[i]==1 | 
      KLOSA_w2_oth_fam$w02Bb001_10[i]==1 | KLOSA_w2_oth_fam$w02Bb001_11[i]==1 | KLOSA_w2_oth_fam$w02Bb001_12[i]==1 | 
      KLOSA_w2_oth_fam$w02Bb001_13[i]==1 | KLOSA_w2_oth_fam$w02Bb001_14[i]==1 |
      KLOSA_w2_oth_fam$w02Bb004[i] == 1 | KLOSA_w2_oth_fam$w02Bb010[i] == 1 ) ){
    KLOSA_ds_w2$oth_fam[i] = 0 }
}

KLOSA_ds_w2$oth_fam <- car::recode(as.vector(KLOSA_ds_w2$oth_fam), "NA='999'")
KLOSA_ds_w2$oth_fam <- labelled(KLOSA_ds_w2$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}
vari <-  KLOSA_ds_w2$oth_fam
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w2$oth_fam, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w2, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}

```

 
 


### Wave 3

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w03Bb001_01` UP TO `w03Bb001_14`
* Label: `1st sibling existence` UP TO `14th sibling existence`
* Categories: 
    + `1 = yes`
    + `5 = no (passed away)`
    
* Name: `w03Bb004`
* Label: `Father existence`
* Categories:
    + `1 = Yes`
    + `5 = No (passed away)`
    
* Name: `w03Bb010`
* Label: `Mother existence`
* Categories:
    + `1 = Yes`
    + `5 = No (passed away)`

* Description: 
```{r assign3, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w3_oth_fam','KLOSA.w03_main_e_spss_albert',
                         variables=list('w03Bb001_01','w03Bb001_02','w03Bb001_03','w03Bb001_04',
                                        'w03Bb001_05','w03Bb001_06','w03Bb001_07','w03Bb001_08',
                                        'w03Bb001_09','w03Bb001_10','w03Bb001_11','w03Bb001_12',
                                        'w03Bb001_13','w03Bb001_14','w03Bb004','w03Bb010'), missings = TRUE)
KLOSA_w3_oth_fam <- opal.execute(o,'KLOSA_w3_oth_fam')
# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_w3_oth_fam$id <- substr(KLOSA_w3_oth_fam$id,1,nchar(KLOSA_w3_oth_fam$id)-2)
```

```{r local3, echo=F}

vari <- KLOSA_w3_oth_fam$w03Bb001_01
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w3_oth_fam$w03Bb001_01, missing_values = NA)
ggplot(KLOSA_w3_oth_fam, aes(x=factor(w03Bb001_01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("1st sibling existence") + ylab("Frequency")

vari <- KLOSA_w3_oth_fam$w03Bb004
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w3_oth_fam$w03Bb004, missing_values = NA)
ggplot(KLOSA_w3_oth_fam, aes(x=factor(w03Bb004))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Father existence") + ylab("Frequency")

vari <- KLOSA_w3_oth_fam$w03Bb010
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w3_oth_fam$w03Bb010, missing_values = NA)
ggplot(KLOSA_w3_oth_fam, aes(x=factor(w03Bb010))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mother existence") + ylab("Frequency")

```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if any variable equals 1 then 1`
* `if for father and mother equals 5 and for siblings !=1 then 0`
* `NA into 999`

**R script:**

```{r harmo3, echo=TRUE}
KLOSA_ds_w3 <- tibble(id=KLOSA_w3_oth_fam$id)

KLOSA_w3_oth_fam$w03Bb001_01 <- car::recode(as.vector(KLOSA_w3_oth_fam$w03Bb001_01), "NA='-999'")
KLOSA_w3_oth_fam$w03Bb001_02 <- car::recode(as.vector(KLOSA_w3_oth_fam$w03Bb001_02), "NA='-999'")
KLOSA_w3_oth_fam$w03Bb001_03 <- car::recode(as.vector(KLOSA_w3_oth_fam$w03Bb001_03), "NA='-999'")
KLOSA_w3_oth_fam$w03Bb001_04 <- car::recode(as.vector(KLOSA_w3_oth_fam$w03Bb001_04), "NA='-999'")
KLOSA_w3_oth_fam$w03Bb001_05 <- car::recode(as.vector(KLOSA_w3_oth_fam$w03Bb001_05), "NA='-999'")
KLOSA_w3_oth_fam$w03Bb001_06 <- car::recode(as.vector(KLOSA_w3_oth_fam$w03Bb001_06), "NA='-999'")
KLOSA_w3_oth_fam$w03Bb001_07 <- car::recode(as.vector(KLOSA_w3_oth_fam$w03Bb001_07), "NA='-999'")
KLOSA_w3_oth_fam$w03Bb001_08 <- car::recode(as.vector(KLOSA_w3_oth_fam$w03Bb001_08), "NA='-999'")
KLOSA_w3_oth_fam$w03Bb001_09 <- car::recode(as.vector(KLOSA_w3_oth_fam$w03Bb001_09), "NA='-999'")
KLOSA_w3_oth_fam$w03Bb001_10 <- car::recode(as.vector(KLOSA_w3_oth_fam$w03Bb001_10), "NA='-999'")
KLOSA_w3_oth_fam$w03Bb001_11 <- car::recode(as.vector(KLOSA_w3_oth_fam$w03Bb001_11), "NA='-999'")
KLOSA_w3_oth_fam$w03Bb001_12 <- car::recode(as.vector(KLOSA_w3_oth_fam$w03Bb001_12), "NA='-999'")
KLOSA_w3_oth_fam$w03Bb001_13 <- car::recode(as.vector(KLOSA_w3_oth_fam$w03Bb001_13), "NA='-999'")
KLOSA_w3_oth_fam$w03Bb001_14 <- car::recode(as.vector(KLOSA_w3_oth_fam$w03Bb001_14), "NA='-999'")
KLOSA_w3_oth_fam$w03Bb004 <- car::recode(as.vector(KLOSA_w3_oth_fam$w03Bb004), "NA='-999'")
KLOSA_w3_oth_fam$w03Bb010 <- car::recode(as.vector(KLOSA_w3_oth_fam$w03Bb010), "NA='-999'")

KLOSA_ds_w3$oth_fam <- c(NA) 
for(i in 1:dim(KLOSA_w3_oth_fam)[1]){
  if( KLOSA_w3_oth_fam$w03Bb001_01[i]==1 | KLOSA_w3_oth_fam$w03Bb001_02[i]==1 | KLOSA_w3_oth_fam$w03Bb001_03[i]==1 | 
      KLOSA_w3_oth_fam$w03Bb001_04[i]==1 | KLOSA_w3_oth_fam$w03Bb001_05[i]==1 | KLOSA_w3_oth_fam$w03Bb001_06[i]==1 | 
      KLOSA_w3_oth_fam$w03Bb001_07[i]==1 | KLOSA_w3_oth_fam$w03Bb001_08[i]==1 | KLOSA_w3_oth_fam$w03Bb001_09[i]==1 | 
      KLOSA_w3_oth_fam$w03Bb001_10[i]==1 | KLOSA_w3_oth_fam$w03Bb001_11[i]==1 | KLOSA_w3_oth_fam$w03Bb001_12[i]==1 | 
      KLOSA_w3_oth_fam$w03Bb001_13[i]==1 | KLOSA_w3_oth_fam$w03Bb001_14[i]==1 | 
      KLOSA_w3_oth_fam$w03Bb004[i]==1 | KLOSA_w3_oth_fam$w03Bb010[i]==1 ){
    KLOSA_ds_w3$oth_fam[i] = 1 } 
  else if( KLOSA_w3_oth_fam$w03Bb001_01[i]== -999 & KLOSA_w3_oth_fam$w03Bb001_02[i]== -999 & KLOSA_w3_oth_fam$w03Bb001_03[i]== -999 & 
      KLOSA_w3_oth_fam$w03Bb001_04[i]== -999 & KLOSA_w3_oth_fam$w03Bb001_05[i]== -999 & KLOSA_w3_oth_fam$w03Bb001_06[i]== -999 & 
      KLOSA_w3_oth_fam$w03Bb001_07[i]== -999 & KLOSA_w3_oth_fam$w03Bb001_08[i]== -999 & KLOSA_w3_oth_fam$w03Bb001_09[i]== -999 & 
      KLOSA_w3_oth_fam$w03Bb001_10[i]== -999 & KLOSA_w3_oth_fam$w03Bb001_11[i]== -999 & KLOSA_w3_oth_fam$w03Bb001_12[i]== -999 & 
      KLOSA_w3_oth_fam$w03Bb001_13[i]== -999 & KLOSA_w3_oth_fam$w03Bb001_14[i]== -999 & 
      KLOSA_w3_oth_fam$w03Bb004[i] == -999 & KLOSA_w3_oth_fam$w03Bb010[i] == -999 ){
    KLOSA_ds_w3$oth_fam[i] = 999 }
  else if( !(KLOSA_w3_oth_fam$w03Bb001_01[i]==1 | KLOSA_w3_oth_fam$w03Bb001_02[i]==1 | KLOSA_w3_oth_fam$w03Bb001_03[i]==1 | 
      KLOSA_w3_oth_fam$w03Bb001_04[i]==1 | KLOSA_w3_oth_fam$w03Bb001_05[i]==1 | KLOSA_w3_oth_fam$w03Bb001_06[i]==1 | 
      KLOSA_w3_oth_fam$w03Bb001_07[i]==1 | KLOSA_w3_oth_fam$w03Bb001_08[i]==1 | KLOSA_w3_oth_fam$w03Bb001_09[i]==1 | 
      KLOSA_w3_oth_fam$w03Bb001_10[i]==1 | KLOSA_w3_oth_fam$w03Bb001_11[i]==1 | KLOSA_w3_oth_fam$w03Bb001_12[i]==1 | 
      KLOSA_w3_oth_fam$w03Bb001_13[i]==1 | KLOSA_w3_oth_fam$w03Bb001_14[i]==1 | 
      KLOSA_w3_oth_fam$w03Bb004[i] == 1 | KLOSA_w3_oth_fam$w03Bb010[i] == 1 ) ){
    KLOSA_ds_w3$oth_fam[i] = 0 }
}

KLOSA_ds_w3$oth_fam <- car::recode(as.vector(KLOSA_ds_w3$oth_fam), "NA='999'")
KLOSA_ds_w3$oth_fam <- labelled(KLOSA_ds_w3$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=F}
vari <-  KLOSA_ds_w3$oth_fam
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w3$oth_fam, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w3, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Has other family members?") + ylab("Frequency")
```

##### Validation
```{r crosstabulation3, echo=F}

```

 
 

### Wave 4

#### Study-specific variable description

The study-specific variable elected to be harmonised is:


* Name: `w04Bb001_01` UP TO `w04Bb001_14`
* Label: `1st sibling existence` UP TO `14th sibling existence`
* Categories: 
    + `1 = yes`
    + `5 = no (passed away)`
* Missings:
    + `-9 = Don't know`   
    + `-8 = Refuse to answer`
    
* Name: `w04Bb004`
* Label: `Father existence`
* Categories:
    + `1 = Yes`
    + `5 = No (passed away)`
    
* Name: `w04Bb010`
* Label: `Mother existence`
* Categories:
    + `1 = Yes`
    + `5 = No (passed away)`

* Description: 
```{r assign4, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w4_oth_fam','KLOSA.w04_main_e_spss',
                         variables=list('w04Bb001_01','w04Bb001_02','w04Bb001_03','w04Bb001_04',
                                        'w04Bb001_05','w04Bb001_06','w04Bb001_07','w04Bb001_08',
                                        'w04Bb001_09','w04Bb001_10','w04Bb001_11','w04Bb001_12',
                                        'w04Bb001_13','w04Bb001_14','w04Bb004','w04Bb010'), missings = TRUE)
```

```{r local4, echo=F}
KLOSA_w4_oth_fam <- opal.execute(o,'KLOSA_w4_oth_fam')
vari <- KLOSA_w4_oth_fam$w04Bb001_01
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w4_oth_fam$w04Bb001_01, missing_values = NA)
ggplot(KLOSA_w4_oth_fam, aes(x=factor(w04Bb001_01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("1st sibling existence") + ylab("Frequency")

vari <- KLOSA_w4_oth_fam$w04Bb004
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w4_oth_fam$w04Bb004, missing_values = NA)
ggplot(KLOSA_w4_oth_fam, aes(x=factor(w04Bb004))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Father existence") + ylab("Frequency")

vari <- KLOSA_w4_oth_fam$w04Bb010
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w4_oth_fam$w04Bb010, missing_values = NA)
ggplot(KLOSA_w4_oth_fam, aes(x=factor(w04Bb010))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mother existence") + ylab("Frequency")

```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if any variable equals 1 then 1`
* `if for father and mother equals 5 and for siblings !=1 then 0`
* `NA into 999`

**R script:**

```{r harmo4, echo=TRUE}
KLOSA_ds_w4 <- tibble(id=KLOSA_w4_oth_fam$id)

KLOSA_w4_oth_fam$w04Bb001_01 <- car::recode(as.vector(KLOSA_w4_oth_fam$w04Bb001_01), "NA='-999'")
KLOSA_w4_oth_fam$w04Bb001_02 <- car::recode(as.vector(KLOSA_w4_oth_fam$w04Bb001_02), "NA='-999'")
KLOSA_w4_oth_fam$w04Bb001_03 <- car::recode(as.vector(KLOSA_w4_oth_fam$w04Bb001_03), "NA='-999'")
KLOSA_w4_oth_fam$w04Bb001_04 <- car::recode(as.vector(KLOSA_w4_oth_fam$w04Bb001_04), "NA='-999'")
KLOSA_w4_oth_fam$w04Bb001_05 <- car::recode(as.vector(KLOSA_w4_oth_fam$w04Bb001_05), "NA='-999'")
KLOSA_w4_oth_fam$w04Bb001_06 <- car::recode(as.vector(KLOSA_w4_oth_fam$w04Bb001_06), "NA='-999'")
KLOSA_w4_oth_fam$w04Bb001_07 <- car::recode(as.vector(KLOSA_w4_oth_fam$w04Bb001_07), "NA='-999'")
KLOSA_w4_oth_fam$w04Bb001_08 <- car::recode(as.vector(KLOSA_w4_oth_fam$w04Bb001_08), "NA='-999'")
KLOSA_w4_oth_fam$w04Bb001_09 <- car::recode(as.vector(KLOSA_w4_oth_fam$w04Bb001_09), "NA='-999'")
KLOSA_w4_oth_fam$w04Bb001_10 <- car::recode(as.vector(KLOSA_w4_oth_fam$w04Bb001_10), "NA='-999'")
KLOSA_w4_oth_fam$w04Bb001_11 <- car::recode(as.vector(KLOSA_w4_oth_fam$w04Bb001_11), "NA='-999'")
KLOSA_w4_oth_fam$w04Bb001_12 <- car::recode(as.vector(KLOSA_w4_oth_fam$w04Bb001_12), "NA='-999'")
KLOSA_w4_oth_fam$w04Bb001_13 <- car::recode(as.vector(KLOSA_w4_oth_fam$w04Bb001_13), "NA='-999'")
KLOSA_w4_oth_fam$w04Bb001_14 <- car::recode(as.vector(KLOSA_w4_oth_fam$w04Bb001_14), "NA='-999'")
KLOSA_w4_oth_fam$w04Bb004 <- car::recode(as.vector(KLOSA_w4_oth_fam$w04Bb004), "NA='-999'")
KLOSA_w4_oth_fam$w04Bb010 <- car::recode(as.vector(KLOSA_w4_oth_fam$w04Bb010), "NA='-999'")

KLOSA_ds_w4$oth_fam <- c(NA) 
for(i in 1:dim(KLOSA_w4_oth_fam)[1]){
  if( KLOSA_w4_oth_fam$w04Bb001_01[i]==1 | KLOSA_w4_oth_fam$w04Bb001_02[i]==1 | KLOSA_w4_oth_fam$w04Bb001_03[i]==1 | 
      KLOSA_w4_oth_fam$w04Bb001_04[i]==1 | KLOSA_w4_oth_fam$w04Bb001_05[i]==1 | KLOSA_w4_oth_fam$w04Bb001_06[i]==1 | 
      KLOSA_w4_oth_fam$w04Bb001_07[i]==1 | KLOSA_w4_oth_fam$w04Bb001_08[i]==1 | KLOSA_w4_oth_fam$w04Bb001_09[i]==1 | 
      KLOSA_w4_oth_fam$w04Bb001_10[i]==1 | KLOSA_w4_oth_fam$w04Bb001_11[i]==1 | KLOSA_w4_oth_fam$w04Bb001_12[i]==1 | 
      KLOSA_w4_oth_fam$w04Bb001_13[i]==1 | KLOSA_w4_oth_fam$w04Bb001_14[i]==1 | 
      KLOSA_w4_oth_fam$w04Bb004[i]==1 | KLOSA_w4_oth_fam$w04Bb010[i]==1 ){
    KLOSA_ds_w4$oth_fam[i] = 1 } 
  else if( KLOSA_w4_oth_fam$w04Bb001_01[i]==-999 & KLOSA_w4_oth_fam$w04Bb001_02[i]==-999 & KLOSA_w4_oth_fam$w04Bb001_03[i]==-999 & 
      KLOSA_w4_oth_fam$w04Bb001_04[i]==-999 & KLOSA_w4_oth_fam$w04Bb001_05[i]==-999 & KLOSA_w4_oth_fam$w04Bb001_06[i]==-999 & 
      KLOSA_w4_oth_fam$w04Bb001_07[i]==-999 & KLOSA_w4_oth_fam$w04Bb001_08[i]==-999 & KLOSA_w4_oth_fam$w04Bb001_09[i]==-999 & 
      KLOSA_w4_oth_fam$w04Bb001_10[i]==-999 & KLOSA_w4_oth_fam$w04Bb001_11[i]==-999 & KLOSA_w4_oth_fam$w04Bb001_12[i]==-999 & 
      KLOSA_w4_oth_fam$w04Bb001_13[i]==-999 & KLOSA_w4_oth_fam$w04Bb001_14[i]==-999 &
      KLOSA_w4_oth_fam$w04Bb004[i] ==-999 & KLOSA_w4_oth_fam$w04Bb010[i] ==-999 ){
    KLOSA_ds_w4$oth_fam[i] = 999 }
  else if( !(KLOSA_w4_oth_fam$w04Bb001_01[i]==1 | KLOSA_w4_oth_fam$w04Bb001_02[i]==1 | KLOSA_w4_oth_fam$w04Bb001_03[i]==1 | 
      KLOSA_w4_oth_fam$w04Bb001_04[i]==1 | KLOSA_w4_oth_fam$w04Bb001_05[i]==1 | KLOSA_w4_oth_fam$w04Bb001_06[i]==1 | 
      KLOSA_w4_oth_fam$w04Bb001_07[i]==1 | KLOSA_w4_oth_fam$w04Bb001_08[i]==1 | KLOSA_w4_oth_fam$w04Bb001_09[i]==1 | 
      KLOSA_w4_oth_fam$w04Bb001_10[i]==1 | KLOSA_w4_oth_fam$w04Bb001_11[i]==1 | KLOSA_w4_oth_fam$w04Bb001_12[i]==1 | 
      KLOSA_w4_oth_fam$w04Bb001_13[i]==1 | KLOSA_w4_oth_fam$w04Bb001_14[i]==1 |
      KLOSA_w4_oth_fam$w04Bb004[i] == 1 | KLOSA_w4_oth_fam$w04Bb010[i] == 1 ) ){
    KLOSA_ds_w4$oth_fam[i] = 0 }
  else if( KLOSA_w4_oth_fam$w04Bb001_01[i]==-9 | KLOSA_w4_oth_fam$w04Bb001_02[i]==-9 & KLOSA_w4_oth_fam$w04Bb001_03[i]==-9 & 
      KLOSA_w4_oth_fam$w04Bb001_04[i]==-9 & KLOSA_w4_oth_fam$w04Bb001_05[i]==-9 & KLOSA_w4_oth_fam$w04Bb001_06[i]==-9 & 
      KLOSA_w4_oth_fam$w04Bb001_07[i]==-9 & KLOSA_w4_oth_fam$w04Bb001_08[i]==-9 & KLOSA_w4_oth_fam$w04Bb001_09[i]==-9 & 
      KLOSA_w4_oth_fam$w04Bb001_10[i]==-9 & KLOSA_w4_oth_fam$w04Bb001_11[i]==-9 & KLOSA_w4_oth_fam$w04Bb001_12[i]==-9 & 
      KLOSA_w4_oth_fam$w04Bb001_13[i]==-9 & KLOSA_w4_oth_fam$w04Bb001_14[i]==-9 ){
    KLOSA_ds_w4$oth_fam[i] = 998 }
  else if( KLOSA_w4_oth_fam$w04Bb001_01[i]==-8 | KLOSA_w4_oth_fam$w04Bb001_02[i]==-8 & KLOSA_w4_oth_fam$w04Bb001_03[i]==-8 & 
      KLOSA_w4_oth_fam$w04Bb001_04[i]==-8 & KLOSA_w4_oth_fam$w04Bb001_05[i]==-8 & KLOSA_w4_oth_fam$w04Bb001_06[i]==-8 & 
      KLOSA_w4_oth_fam$w04Bb001_07[i]==-8 & KLOSA_w4_oth_fam$w04Bb001_08[i]==-8 & KLOSA_w4_oth_fam$w04Bb001_09[i]==-8 & 
      KLOSA_w4_oth_fam$w04Bb001_10[i]==-8 & KLOSA_w4_oth_fam$w04Bb001_11[i]==-8 & KLOSA_w4_oth_fam$w04Bb001_12[i]==-8 & 
      KLOSA_w4_oth_fam$w04Bb001_13[i]==-8 & KLOSA_w4_oth_fam$w04Bb001_14[i]==-8 ){
    KLOSA_ds_w4$oth_fam[i] = 997 }
}

KLOSA_ds_w4$oth_fam <- car::recode(as.vector(KLOSA_ds_w4$oth_fam), "NA='999'")
KLOSA_ds_w4$oth_fam <- labelled(KLOSA_ds_w4$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4, echo=F}
vari <-  KLOSA_ds_w4$oth_fam
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w4$oth_fam, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w4, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=F}

```

 
```{r save, echo=FALSE}
oth_fam <- KLOSA_ds_w1
save(oth_fam, file = "../RData/w1/oth_fam.RData")
rm(oth_fam)

oth_fam <- KLOSA_ds_w2
save(oth_fam, file = "../RData/w2/oth_fam.RData")
rm(oth_fam)

oth_fam <- KLOSA_ds_w3
save(oth_fam, file = "../RData/w3/oth_fam.RData")
rm(oth_fam)

oth_fam <- KLOSA_ds_w4
save(oth_fam, file = "../RData/w4/oth_fam.RData")
rm(oth_fam)

```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```


