---
title: "Are the contacts with friends/neighbours frequent (i.e. contact once a month or more often)"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/cont_frDS.Rmd'}
```


```{r global, echo=F}
source('../../_DS_Rmd/cont_frDS.R')
```


<!-- ########################################################## --> 

# Data process

## Korea
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w01A016`
* Label: `The Number of times that meet with the familiar`
* Categories: 
    + `1 = Almost every day`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month`
    + `6 = Once or twice a year`
    + `7 = Three or for times a year`
    + `8 = Five or six times a year`
    + `9 = Almost never`
    + `10 = No close friend or relative`


* Description: 
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w1_cont_fr','KLOSA.w01_main_e',variables=list('w01A016'), missings = TRUE)
```

```{r local1, echo=F}
KLOSA_w1_cont_fr <- opal.execute(o,'KLOSA_w1_cont_fr')
vari <- KLOSA_w1_cont_fr$w01A016
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w1_cont_fr$w01A016, missing_values = NA)
ggplot(KLOSA_w1_cont_fr, aes(x=factor(w01A016))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The Number of times that meet with the familiar") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1:5 into 1`
* `6:10 into 0`
* `NA into 999`

 **R script:**

```{r harmo1, echo=TRUE}
KLOSA_ds_w1 <- tibble(id=KLOSA_w1_cont_fr$id)
KLOSA_ds_w1$cont_fr <- car::recode(as.vector(KLOSA_w1_cont_fr$w01A016), "1:5='1'; 6:10='0'; NA='999'")
KLOSA_ds_w1$cont_fr <- labelled(KLOSA_ds_w1$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <-  KLOSA_ds_w1$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w1$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w1, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(KLOSA_ds_w1$cont_fr)
BeforeH <- table(KLOSA_w1_cont_fr$w01A016, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(6:10)])
BeforeH1[[2]] <- sum(BeforeH[c(1:5)])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1")
kable(C)
```




### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w02A032`
* Label: `How often meeting with familiar people`
* Categories: 
    + `1 = Almost every day`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month`
    + `6 = Once or twice a year`
    + `7 = Three or for times a year`
    + `8 = Five or six times a year`
    + `9 = Almost never`
    + `10 = No close friend or relative`

* Description: 
```{r assign2, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w2_cont_fr','KLOSA.w02_main_e_spss',variables=list('w02A032'), missings = TRUE)
```

```{r local2, echo=F}
KLOSA_w2_cont_fr <- opal.execute(o,'KLOSA_w2_cont_fr')
vari <- KLOSA_w2_cont_fr$w02A032
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w2_cont_fr$w02A032, missing_values = NA)
ggplot(KLOSA_w2_cont_fr, aes(x=factor(w02A032))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How often meeting with familiar people") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1:5 into 1`
* `6:10 into 0`
* `NA into 999`


 **R script:**

```{r harmo2, echo=TRUE}
KLOSA_ds_w2 <- tibble(id=KLOSA_w2_cont_fr$id)
KLOSA_ds_w2$cont_fr <- car::recode(as.vector(KLOSA_w2_cont_fr$w02A032), "1:5='1'; 6:10='0'; NA='999'")
KLOSA_ds_w2$cont_fr <- labelled(KLOSA_ds_w2$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}
vari <-  KLOSA_ds_w2$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w2$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w2, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
AfterH <- table(KLOSA_ds_w2$cont_fr)
BeforeH <- table(KLOSA_w2_cont_fr$w02A032, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(6:10)])
BeforeH1[[2]] <- sum(BeforeH[c(1:5)])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1")

kable(C)
```

 
 


### Wave 3

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w03A032`
* Label: `The Number of times that meet with the familiar`
* Categories: 
    + `1 = Almost every day`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month`
    + `6 = Once or twice a year`
    + `7 = Three or for times a year`
    + `8 = Five or six times a year`
    + `9 = Almost never`
    + `10 = No close friend or relative`

* Description: 
```{r assign3, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w3_cont_fr','KLOSA.w03_main_e_spss_albert',variables=list('w03A032'), missings = TRUE)
KLOSA_w3_cont_fr <- opal.execute(o,'KLOSA_w3_cont_fr')
# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_w3_cont_fr$id <- substr(KLOSA_w3_cont_fr$id,1,nchar(KLOSA_w3_cont_fr$id)-2)
```

```{r local3, echo=F}
vari <- KLOSA_w3_cont_fr$w03A032
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w3_cont_fr$w03A032, missing_values = NA)
ggplot(KLOSA_w3_cont_fr, aes(x=factor(w03A032))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The Number of times that meet with the familiar") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1:5 into 1`
* `6:10 into 0`
* `NA into 999`

 **R script:**

```{r harmo3, echo=TRUE}
KLOSA_ds_w3 <- tibble(id=KLOSA_w3_cont_fr$id)
KLOSA_ds_w3$cont_fr <- car::recode(as.vector(KLOSA_w3_cont_fr$w03A032), "1:5='1'; 6:10='0'; NA='999'")
KLOSA_ds_w3$cont_fr <- labelled(KLOSA_ds_w3$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=F}
vari <-  KLOSA_ds_w3$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w3$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w3, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

##### Validation
```{r crosstabulation3, echo=F}
AfterH <- table(KLOSA_ds_w3$cont_fr)
BeforeH <- table(KLOSA_w3_cont_fr$w03A032, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(6:10)])
BeforeH1[[2]] <- sum(BeforeH[c(1:5)])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1")

kable(C)
```

 
 

### Wave 4

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w04A032`
* Label: `The Number of times that meet with the familiar`
* Categories: 
    + `1 = Almost every day`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month`
    + `6 = Once or twice a year`
    + `7 = Three or for times a year`
    + `8 = Five or six times a year`
    + `9 = Almost never`
    + `10 = No close friend or relative`

* Description: 
```{r assign4, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w4_cont_fr','KLOSA.w04_main_e_spss',variables=list('w04A032'), missings = TRUE)
```

```{r local4, echo=F}
KLOSA_w4_cont_fr <- opal.execute(o,'KLOSA_w4_cont_fr')
vari <- KLOSA_w4_cont_fr$w04A032
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w4_cont_fr$w04A032, missing_values = NA)
ggplot(KLOSA_w4_cont_fr, aes(x=factor(w04A032))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The Number of times that meet with the familiar") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1:5 into 1`
* `6:10 into 0`
* `NA into 999`

 **R script:**

```{r harmo4, echo=TRUE}
KLOSA_ds_w4 <- tibble(id=KLOSA_w4_cont_fr$id)
KLOSA_ds_w4$cont_fr <- car::recode(as.vector(KLOSA_w4_cont_fr$w04A032), "1:5='1'; 6:10='0'; NA='999'")
KLOSA_ds_w4$cont_fr <- labelled(KLOSA_ds_w4$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4, echo=F}
vari <-  KLOSA_ds_w4$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w4$cont_fr, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w4, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=F}
AfterH <- table(KLOSA_ds_w4$cont_fr)
BeforeH <- table(KLOSA_w4_cont_fr$w04A032, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(6:10)])
BeforeH1[[2]] <- sum(BeforeH[c(1:5)])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1")

kable(C)
```

 
 
```{r save, echo=FALSE}
cont_fr <- KLOSA_ds_w1
save(cont_fr, file = "../RData/w1/cont_fr.RData")
rm(cont_fr)

cont_fr <- KLOSA_ds_w2
save(cont_fr, file = "../RData/w2/cont_fr.RData")
rm(cont_fr)

cont_fr <- KLOSA_ds_w3
save(cont_fr, file = "../RData/w3/cont_fr.RData")
rm(cont_fr)

cont_fr <- KLOSA_ds_w4
save(cont_fr, file = "../RData/w4/cont_fr.RData")
rm(cont_fr)
```


# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```