---
title: "Are any form of contact ( face-to-face/phone/mail/Internet communicators) with family members/relatives frequent (i.e. contact once a week or more often)?"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `cont_rel`
* Variable label: `Are any form of contact ( face-to-face/phone/mail/Internet communicators) with family members/relatives frequent (i.e. contact once a week or more often)?`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process
## Korea
### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised are:

* Name: `w01Ba13_01` UP TO `w01Ba13_10`
* Label: `The frequency which 1st child meets(in person)`
* Categories: 
    + `1 = Almost every day`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month`
    + `6 = Once or twice a year`
    + `7 = Three or for times a year`
    + `8 = Five or six times a year`
    + `9 = Almost never`
    + `10 = Never`
* Missings:
    + `-8 = RF`
    + `-9 = DK`
    
* Name: `w01B031`
* Label: `The frequency which parents meet(in person)`
* Categories: 
    + `1 = Almost every day`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month`
    + `6 = Once or twice a year`
    + `7 = Three or for times a year`
    + `8 = Five or six times a year`
    + `9 = Almost never`
    + `10 = Never`
    
* Name: `w01B069`
* Label: `The frequency which father meet(in person)`
* Categories: 
    + `1 = Almost every day`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month`
    + `6 = Once or twice a year`
    + `7 = Three or for times a year`
    + `8 = Five or six times a year`
    + `9 = Almost never`
    + `10 = Never`
    
* Name: `w01B107`
* Label: `The frequency which mother meet(in person)`
* Categories: 
    + `1 = Almost every day`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month`
    + `6 = Once or twice a year`
    + `7 = Three or for times a year`
    + `8 = Five or six times a year`
    + `9 = Almost never`
    + `10 = Never`
    
* Name: `w01Ba14_01` UP TO `w01Ba14_10`
* Label: `The times which 1st child meets(by phone, mail or e-mail)`
* Categories: 
    + `1 = Almost every day`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month`
    + `6 = Once or twice a year`
    + `7 = Three or for times a year`
    + `8 = Five or six times a year`
    + `9 = Almost never`
    + `10 = Never`
* Missings:
    + `-8 = RF`
    + `-9 = DK`
    
* Name: `w01B032`
* Label: `The frequency which parents meet(by phone, mail or e-mail)`
* Categories: 
    + `1 = Almost every day`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month`
    + `6 = Once or twice a year`
    + `7 = Three or for times a year`
    + `8 = Five or six times a year`
    + `9 = Almost never`
    + `10 = Never`

* Name: `w01B070`
* Label: `The frequency which father meets(by phone, mail or e-mail)`
* Categories: 
    + `1 = Almost every day`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month`
    + `6 = Once or twice a year`
    + `7 = Three or for times a year`
    + `8 = Five or six times a year`
    + `9 = Almost never`
    + `10 = Never`

* Name: `w01B108`
* Label: `The frequency which mother meets(by phone, mail or e-mail)`
* Categories: 
    + `1 = Almost every day`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month`
    + `6 = Once or twice a year`
    + `7 = Three or for times a year`
    + `8 = Five or six times a year`
    + `9 = Almost never`
    + `10 = Never`

* Description: 
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w1_cont_rel','KLOSA.w01_main_e', 
                        variables=list('w01Ba13_01','w01Ba13_02','w01Ba13_03','w01Ba13_04','w01Ba13_05','w01Ba13_06','w01Ba13_07','w01Ba13_08','w01Ba13_09','w01Ba13_10',
                                       'w01B031','w01B069','w01B107',
                                       'w01Ba14_01','w01Ba14_02','w01Ba14_03','w01Ba14_04','w01Ba14_05','w01Ba14_06', 'w01Ba14_07','w01Ba14_08','w01Ba14_09','w01Ba14_10',
                                       'w01B032','w01B070','w01B108'), missings = TRUE)
```

```{r local1, echo=F}
KLOSA_w1_cont_rel <- opal.execute(o,'KLOSA_w1_cont_rel')

vari <- KLOSA_w1_cont_rel$w01Ba13_01
kable(Categorical_summary(vari, missing_values = c(-8,-9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-8,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-8,-9))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_w1_cont_rel$w01Ba13_01, missing_values = NA)
ggplot(KLOSA_w1_cont_rel, aes(x=factor(w01Ba13_01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The frequency which 1st child meets(in person)") + ylab("Frequency")


vari <- KLOSA_w1_cont_rel$w01B031
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w1_cont_rel$w01B031, missing_values = NA)
ggplot(KLOSA_w1_cont_rel, aes(x=factor(w01B031))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The frequency which parents meet(in person)") + ylab("Frequency")

vari <- KLOSA_w1_cont_rel$w01B069
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w1_cont_rel$w01B069, missing_values = NA)
ggplot(KLOSA_w1_cont_rel, aes(x=factor(w01B069))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The frequency which father meet(in person)") + ylab("Frequency")

vari <- KLOSA_w1_cont_rel$w01B107
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w1_cont_rel$w01B107, missing_values = NA)
ggplot(KLOSA_w1_cont_rel, aes(x=factor(w01B107))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The frequency which mother meet(in person)") + ylab("Frequency")

vari <- KLOSA_w1_cont_rel$w01Ba14_01
kable(Categorical_summary(vari, missing_values = c(-8,-9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-8,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-8,-9))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_w1_cont_rel$w01Ba13_01, missing_values = NA)
ggplot(KLOSA_w1_cont_rel, aes(x=factor(w01Ba13_01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The times which 1st child meets(by phone, mail or e-mail)") + ylab("Frequency")


vari <- KLOSA_w1_cont_rel$w01B032
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w1_cont_rel$w01B031, missing_values = NA)
ggplot(KLOSA_w1_cont_rel, aes(x=factor(w01B032))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The frequency which parents meet(by phone, mail or e-mail)") + ylab("Frequency")

vari <- KLOSA_w1_cont_rel$w01B069
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w1_cont_rel$w01B069, missing_values = NA)
ggplot(KLOSA_w1_cont_rel, aes(x=factor(w01B069))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The frequency which father meet(by phone, mail or e-mail)") + ylab("Frequency")

vari <- KLOSA_w1_cont_rel$w01B107
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w1_cont_rel$w01B107, missing_values = NA)
ggplot(KLOSA_w1_cont_rel, aes(x=factor(w01B107))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The frequency which mother meet(by phone, mail or e-mail)") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any variable from 'w01Ba13_01' to 'w01Ba13_10' or 'w01B031','w01B069','w01B107' is in 1:5 then 1`
* `if any variable from 'w01Ba14_01' to 'w01Ba14_10' or 'w01B032','w01B070','w01B108' is in 1:3 then 1`
* `there are -9 and -8 only in variables w01Ba13_i and w01Ba14_i so if every variable has values -8,-9 or NA recode into 999`


**R script:**

```{r harmo1, echo=TRUE}
KLOSA_ds_w1 <- tibble(id=KLOSA_w1_cont_rel$id)

KLOSA_w1_cont_rel$w01Ba13_01 <- car::recode(as.vector(KLOSA_w1_cont_rel$w01Ba13_01), "NA='-999'")
KLOSA_w1_cont_rel$w01Ba13_02 <- car::recode(as.vector(KLOSA_w1_cont_rel$w01Ba13_02), "NA='-999'")
KLOSA_w1_cont_rel$w01Ba13_03 <- car::recode(as.vector(KLOSA_w1_cont_rel$w01Ba13_03), "NA='-999'")
KLOSA_w1_cont_rel$w01Ba13_04 <- car::recode(as.vector(KLOSA_w1_cont_rel$w01Ba13_04), "NA='-999'")
KLOSA_w1_cont_rel$w01Ba13_05 <- car::recode(as.vector(KLOSA_w1_cont_rel$w01Ba13_05), "NA='-999'")
KLOSA_w1_cont_rel$w01Ba13_06 <- car::recode(as.vector(KLOSA_w1_cont_rel$w01Ba13_06), "NA='-999'")
KLOSA_w1_cont_rel$w01Ba13_07 <- car::recode(as.vector(KLOSA_w1_cont_rel$w01Ba13_07), "NA='-999'")
KLOSA_w1_cont_rel$w01Ba13_08 <- car::recode(as.vector(KLOSA_w1_cont_rel$w01Ba13_08), "NA='-999'")
KLOSA_w1_cont_rel$w01Ba13_09 <- car::recode(as.vector(KLOSA_w1_cont_rel$w01Ba13_09), "NA='-999'")
KLOSA_w1_cont_rel$w01Ba13_10 <- car::recode(as.vector(KLOSA_w1_cont_rel$w01Ba13_10), "NA='-999'")
KLOSA_w1_cont_rel$w01B031 <- car::recode(as.vector(KLOSA_w1_cont_rel$w01B031), "NA='-999'")
KLOSA_w1_cont_rel$w01B069 <- car::recode(as.vector(KLOSA_w1_cont_rel$w01B069), "NA='-999'")
KLOSA_w1_cont_rel$w01B107 <- car::recode(as.vector(KLOSA_w1_cont_rel$w01B107), "NA='-999'")
KLOSA_w1_cont_rel$w01Ba14_01 <- car::recode(as.vector(KLOSA_w1_cont_rel$w01Ba14_01), "NA='-999'")
KLOSA_w1_cont_rel$w01Ba14_02 <- car::recode(as.vector(KLOSA_w1_cont_rel$w01Ba14_02), "NA='-999'")
KLOSA_w1_cont_rel$w01Ba14_03 <- car::recode(as.vector(KLOSA_w1_cont_rel$w01Ba14_03), "NA='-999'")
KLOSA_w1_cont_rel$w01Ba14_04 <- car::recode(as.vector(KLOSA_w1_cont_rel$w01Ba14_04), "NA='-999'")
KLOSA_w1_cont_rel$w01Ba14_05 <- car::recode(as.vector(KLOSA_w1_cont_rel$w01Ba14_05), "NA='-999'")
KLOSA_w1_cont_rel$w01Ba14_06 <- car::recode(as.vector(KLOSA_w1_cont_rel$w01Ba14_06), "NA='-999'")
KLOSA_w1_cont_rel$w01Ba14_07 <- car::recode(as.vector(KLOSA_w1_cont_rel$w01Ba14_07), "NA='-999'")
KLOSA_w1_cont_rel$w01Ba14_08 <- car::recode(as.vector(KLOSA_w1_cont_rel$w01Ba14_08), "NA='-999'")
KLOSA_w1_cont_rel$w01Ba14_09 <- car::recode(as.vector(KLOSA_w1_cont_rel$w01Ba14_09), "NA='-999'")
KLOSA_w1_cont_rel$w01Ba14_10 <- car::recode(as.vector(KLOSA_w1_cont_rel$w01Ba14_10), "NA='-999'")
KLOSA_w1_cont_rel$w01B032 <- car::recode(as.vector(KLOSA_w1_cont_rel$w01B032), "NA='-999'")
KLOSA_w1_cont_rel$w01B070 <- car::recode(as.vector(KLOSA_w1_cont_rel$w01B070), "NA='-999'")
KLOSA_w1_cont_rel$w01B108 <- car::recode(as.vector(KLOSA_w1_cont_rel$w01B108), "NA='-999'")

KLOSA_ds_w1$cont_rel <- c(NA) 
for(i in 1:dim(KLOSA_w1_cont_rel)[1]){
  if( KLOSA_w1_cont_rel$w01Ba13_01[i] %in% c(1:5) | 
      KLOSA_w1_cont_rel$w01Ba13_02[i] %in% c(1:5) | 
      KLOSA_w1_cont_rel$w01Ba13_03[i] %in% c(1:5) |
      KLOSA_w1_cont_rel$w01Ba13_04[i] %in% c(1:5) | 
      KLOSA_w1_cont_rel$w01Ba13_05[i] %in% c(1:5) | 
      KLOSA_w1_cont_rel$w01Ba13_06[i] %in% c(1:5) | 
      KLOSA_w1_cont_rel$w01Ba13_07[i] %in% c(1:5) | 
      KLOSA_w1_cont_rel$w01Ba13_08[i] %in% c(1:5) | 
      KLOSA_w1_cont_rel$w01Ba13_09[i] %in% c(1:5) | 
      KLOSA_w1_cont_rel$w01Ba13_10[i] %in% c(1:5) | 
      KLOSA_w1_cont_rel$w01B031[i] %in% c(1:5) | 
      KLOSA_w1_cont_rel$w01B069[i] %in% c(1:5) |  
      KLOSA_w1_cont_rel$w01B107[i] %in% c(1:5) |
      KLOSA_w1_cont_rel$w01Ba14_01[i] %in% c(1:3) | 
      KLOSA_w1_cont_rel$w01Ba14_02[i] %in% c(1:3) | 
      KLOSA_w1_cont_rel$w01Ba14_03[i] %in% c(1:3) |
      KLOSA_w1_cont_rel$w01Ba14_04[i] %in% c(1:3) | 
      KLOSA_w1_cont_rel$w01Ba14_05[i] %in% c(1:3) | 
      KLOSA_w1_cont_rel$w01Ba14_06[i] %in% c(1:3) | 
      KLOSA_w1_cont_rel$w01Ba14_07[i] %in% c(1:3) | 
      KLOSA_w1_cont_rel$w01Ba14_08[i] %in% c(1:3) | 
      KLOSA_w1_cont_rel$w01Ba14_09[i] %in% c(1:3) | 
      KLOSA_w1_cont_rel$w01Ba14_10[i] %in% c(1:3) | 
      KLOSA_w1_cont_rel$w01B032[i] %in% c(1:3) | 
      KLOSA_w1_cont_rel$w01B070[i] %in% c(1:3) |  
      KLOSA_w1_cont_rel$w01B108[i] %in% c(1:3)) {
    KLOSA_ds_w1$cont_rel[i] = 1 }
  else if( KLOSA_w1_cont_rel$w01Ba13_01[i] %in% c(-9, -8, -999) & 
           KLOSA_w1_cont_rel$w01Ba13_02[i] %in% c(-9, -8, -999) & 
           KLOSA_w1_cont_rel$w01Ba13_03[i] %in% c(-9, -8, -999) & 
           KLOSA_w1_cont_rel$w01Ba13_04[i] %in% c(-9, -8, -999) & 
           KLOSA_w1_cont_rel$w01Ba13_05[i] %in% c(-9, -8, -999) & 
           KLOSA_w1_cont_rel$w01Ba13_06[i] %in% c(-9, -8, -999) & 
           KLOSA_w1_cont_rel$w01Ba13_07[i] %in% c(-9, -8, -999) & 
           KLOSA_w1_cont_rel$w01Ba13_08[i] %in% c(-9, -8, -999) & 
           KLOSA_w1_cont_rel$w01Ba13_09[i] %in% c(-9, -8, -999) & 
           KLOSA_w1_cont_rel$w01Ba13_10[i] %in% c(-9, -8, -999) & 
           KLOSA_w1_cont_rel$w01B031[i] %in% c(-9, -8, -999) & 
           KLOSA_w1_cont_rel$w01B069[i] %in% c(-9, -8, -999) & 
           KLOSA_w1_cont_rel$w01B107[i] %in% c(-9, -8, -999) &
           KLOSA_w1_cont_rel$w01Ba14_01[i] %in% c(-9, -8, -999) & 
           KLOSA_w1_cont_rel$w01Ba14_02[i] %in% c(-9, -8, -999) & 
           KLOSA_w1_cont_rel$w01Ba14_03[i] %in% c(-9, -8, -999) & 
           KLOSA_w1_cont_rel$w01Ba14_04[i] %in% c(-9, -8, -999) & 
           KLOSA_w1_cont_rel$w01Ba14_05[i] %in% c(-9, -8, -999) & 
           KLOSA_w1_cont_rel$w01Ba14_06[i] %in% c(-9, -8, -999) & 
           KLOSA_w1_cont_rel$w01Ba14_07[i] %in% c(-9, -8, -999) & 
           KLOSA_w1_cont_rel$w01Ba14_08[i] %in% c(-9, -8, -999) & 
           KLOSA_w1_cont_rel$w01Ba14_09[i] %in% c(-9, -8, -999) & 
           KLOSA_w1_cont_rel$w01Ba14_10[i] %in% c(-9, -8, -999) & 
           KLOSA_w1_cont_rel$w01B032[i] %in% c(-9, -8, -999) & 
           KLOSA_w1_cont_rel$w01B070[i] %in% c(-9, -8, -999) & 
           KLOSA_w1_cont_rel$w01B108[i] %in% c(-9, -8, -999) ) {
    KLOSA_ds_w1$cont_rel[i] = 999 }
  else if( !( KLOSA_w1_cont_rel$w01Ba13_01[i] %in% c(1:5) | 
              KLOSA_w1_cont_rel$w01Ba13_02[i] %in% c(1:5) | 
              KLOSA_w1_cont_rel$w01Ba13_03[i] %in% c(1:5) | 
              KLOSA_w1_cont_rel$w01Ba13_04[i] %in% c(1:5) | 
              KLOSA_w1_cont_rel$w01Ba13_05[i] %in% c(1:5) | 
              KLOSA_w1_cont_rel$w01Ba13_06[i] %in% c(1:5) | 
              KLOSA_w1_cont_rel$w01Ba13_07[i] %in% c(1:5) | 
              KLOSA_w1_cont_rel$w01Ba13_08[i] %in% c(1:5) | 
              KLOSA_w1_cont_rel$w01Ba13_09[i] %in% c(1:5) | 
              KLOSA_w1_cont_rel$w01Ba13_10[i] %in% c(1:5) | 
              KLOSA_w1_cont_rel$w01B031[i] %in% c(1:5) | 
              KLOSA_w1_cont_rel$w01B069[i] %in% c(1:5) | 
              KLOSA_w1_cont_rel$w01B107[i] %in% c(1:5) |
              KLOSA_w1_cont_rel$w01Ba14_01[i] %in% c(1:3) | 
              KLOSA_w1_cont_rel$w01Ba14_02[i] %in% c(1:3) | 
              KLOSA_w1_cont_rel$w01Ba14_03[i] %in% c(1:3) |
              KLOSA_w1_cont_rel$w01Ba14_04[i] %in% c(1:3) | 
              KLOSA_w1_cont_rel$w01Ba14_05[i] %in% c(1:3) | 
              KLOSA_w1_cont_rel$w01Ba14_06[i] %in% c(1:3) | 
              KLOSA_w1_cont_rel$w01Ba14_07[i] %in% c(1:3) | 
              KLOSA_w1_cont_rel$w01Ba14_08[i] %in% c(1:3) | 
              KLOSA_w1_cont_rel$w01Ba14_09[i] %in% c(1:3) | 
              KLOSA_w1_cont_rel$w01Ba14_10[i] %in% c(1:3) | 
              KLOSA_w1_cont_rel$w01B032[i] %in% c(1:3) | 
              KLOSA_w1_cont_rel$w01B070[i] %in% c(1:3) |  
              KLOSA_w1_cont_rel$w01B108[i] %in% c(1:3)) ) {
    KLOSA_ds_w1$cont_rel[i] = 0 }
}


KLOSA_ds_w1$cont_rel <- car::recode(as.vector(KLOSA_ds_w1$cont_rel), "NA='999'")
KLOSA_ds_w1$cont_rel <- labelled(KLOSA_ds_w1$cont_rel, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <- KLOSA_ds_w1$cont_rel
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w1$cont_rel, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w1, aes(x=factor(cont_rel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are contacts with family members/relatives frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}

```

 
 


### Wave 2

#### Study-specific variable description

The study-specific variables elected to be harmonised are:


* Name: `w02Ba019_01` UP TO `w02Ba019_01`
* Label: `The frequency which 1st child meets(in person)`
* Categories: 
    + `1 = Almost every day (more than 4 times per week)`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month (every two weeks)`
    + `6 = Once or twice a year`
    + `7 = Three or for times a year (once every three or four months)`
    + `8 = Five or six times a year (every two months)`
    + `9 = Almost never a year`
    + `10 = Never`
    
* Name: `w02Bb021`
* Label: `The meeting frequency with parents (term of non-coresiding)`
* Categories: 
    + `1 = Almost every day (more than 4 times per week)`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month (every two weeks)`
    + `6 = Once or twice a year`
    + `7 = Three or for times a year (once every three or four months)`
    + `8 = Five or six times a year (every two months)`
    + `9 = Almost never a year`
    + `10 = Never`
    
* Name: `w02Bb059`
* Label: `The meeting frequency with the father (term of non-coresiding)`
* Categories: 
    + `1 = Almost every day`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month`
    + `6 = Once or twice a year`
    + `7 = Three or for times a year`
    + `8 = Five or six times a year`
    + `9 = Almost never`
    + `10 = Never`
    
* Name: `w02Bb097`
* Label: `The meeting frequency with the mother (term of non-coresiding)`
* Categories: 
    + `1 = Almost every day (more than 4 times per week)`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month (every two weeks)`
    + `6 = Once or twice a year`
    + `7 = Three or for times a year (once every three or four months)`
    + `8 = Five or six times a year (every two months)`
    + `9 = Almost never a year`
    + `10 = Never`
    
* Name: `w02Ba020_01` UP TO `w02Ba020_10`
* Label: `The contact frequency with 1st child(by phone, letter or e-mail)`
* Categories: 
    + `1 = Almost every day (more than 4 times per week)`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month (every two weeks)`
    + `6 = Once or twice a year`
    + `7 = Three or for times a year (once every three or four months)`
    + `8 = Five or six times a year (every two months)`
    + `9 = Almost never a year`
    + `10 = Never`
    
* Name: `w02Bb022`
* Label: `The contact frequency with the parents(by phone, letter or e-mail)`
* Categories: 
    + `1 = Almost every day (more than 4 times per week)`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month (every two weeks)`
    + `6 = Once or twice a year`
    + `7 = Three or for times a year (once every three or four months)`
    + `8 = Five or six times a year (every two months)`
    + `9 = Almost never a year`
    + `10 = Never`
    
* Name: `w02Bb060`
* Label: `The contact frequency with the father by phone, letter or e-mail (term of non-coresiding)`
* Categories: 
    + `1 = Almost every day (more than 4 times per week)`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month (every two weeks)`
    + `6 = Once or twice a year`
    + `7 = Three or for times a year (once every three or four months)`
    + `8 = Five or six times a year (every two months)`
    + `9 = Almost never a year`
    + `10 = Never`
    
* Name: `w02Bb098`
* Label: `The contact frequency with the father by phone, letter or e-mail (term of non-coresiding)`
* Categories: 
    + `1 = Almost every day (more than 4 times per week)`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month (every two weeks)`
    + `6 = Once or twice a year`
    + `7 = Three or for times a year (once every three or four months)`
    + `8 = Five or six times a year (every two months)`
    + `9 = Almost never a year`
    + `10 = Never`
    
* Description: 
```{r assign2, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w2_cont_rel','KLOSA.w02_main_e_spss',
                         variables=list('w02Ba019_01','w02Ba019_02','w02Ba019_03','w02Ba019_04','w02Ba019_05','w02Ba019_06','w02Ba019_07','w02Ba019_08','w02Ba019_09','w02Ba019_10',
                                        'w02Bb021','w02Bb059','w02Bb097',
                                        'w02Ba020_01','w02Ba020_02','w02Ba020_03','w02Ba020_04','w02Ba020_05','w02Ba020_06','w02Ba020_07','w02Ba020_08','w02Ba020_09','w02Ba020_10',
                                        'w02Bb022','w02Bb060','w02Bb098'), missings = TRUE)
```

```{r local2, echo=F}
KLOSA_w2_cont_rel <- opal.execute(o,'KLOSA_w2_cont_rel')

vari <- KLOSA_w2_cont_rel$w02Ba019_01
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2_cont_rel, aes(x=factor(w02Ba019_01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The frequency which 1st child meets(in person)") + ylab("Frequency")


vari <- KLOSA_w2_cont_rel$w02Bb021
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2_cont_rel, aes(x=factor(w02Bb021)))+ geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The frequency which parents meet(in person)") + ylab("Frequency")

vari <- KLOSA_w2_cont_rel$w02Bb059
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2_cont_rel, aes(x=factor(w02Bb059))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The frequency which father meet(in person)") + ylab("Frequency")

vari <- KLOSA_w2_cont_rel$w02Bb097
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2_cont_rel, aes(x=factor(w02Bb097))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The frequency which mother meet(in person)") + ylab("Frequency")

vari <- KLOSA_w2_cont_rel$w02Ba020_01
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2_cont_rel, aes(x=factor(w02Ba020_01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The times which 1st child meets(by phone, mail or e-mail)") + ylab("Frequency")


vari <- KLOSA_w2_cont_rel$w02Bb022
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2_cont_rel, aes(x=factor(w02Bb022))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The frequency which parents meet(by phone, mail or e-mail)") + ylab("Frequency")

vari <- KLOSA_w2_cont_rel$w02Bb060
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2_cont_rel, aes(x=factor(w02Bb060))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The frequency which father meet(by phone, mail or e-mail)") + ylab("Frequency")

vari <- KLOSA_w2_cont_rel$w02Bb098
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w2_cont_rel, aes(x=factor(w02Bb098))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The frequency which mother meet(by phone, mail or e-mail)") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if any variable from 'w02Ba019_01' to 'w02Ba019_10' or 'w02Bb021', 'w02Bb059', 'w02Bb097' is in 1:5 then 1`
* `if any variable from 'w02Ba020_01' to 'w02Ba020_10'or 'w02Bb022','w02Bb060','w02Bb098' is in 1:3 then 1`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
KLOSA_ds_w2 <- tibble(id=KLOSA_w2_cont_rel$id)

KLOSA_w2_cont_rel$w02Ba019_01 <- car::recode(as.vector(KLOSA_w2_cont_rel$w02Ba019_01), "NA='-999'")
KLOSA_w2_cont_rel$w02Ba019_02 <- car::recode(as.vector(KLOSA_w2_cont_rel$w02Ba019_02), "NA='-999'")
KLOSA_w2_cont_rel$w02Ba019_03 <- car::recode(as.vector(KLOSA_w2_cont_rel$w02Ba019_03), "NA='-999'")
KLOSA_w2_cont_rel$w02Ba019_04 <- car::recode(as.vector(KLOSA_w2_cont_rel$w02Ba019_04), "NA='-999'")
KLOSA_w2_cont_rel$w02Ba019_05 <- car::recode(as.vector(KLOSA_w2_cont_rel$w02Ba019_05), "NA='-999'")
KLOSA_w2_cont_rel$w02Ba019_06 <- car::recode(as.vector(KLOSA_w2_cont_rel$w02Ba019_06), "NA='-999'")
KLOSA_w2_cont_rel$w02Ba019_07 <- car::recode(as.vector(KLOSA_w2_cont_rel$w02Ba019_07), "NA='-999'")
KLOSA_w2_cont_rel$w02Ba019_08 <- car::recode(as.vector(KLOSA_w2_cont_rel$w02Ba019_08), "NA='-999'")
KLOSA_w2_cont_rel$w02Ba019_09 <- car::recode(as.vector(KLOSA_w2_cont_rel$w02Ba019_09), "NA='-999'")
KLOSA_w2_cont_rel$w02Ba019_10 <- car::recode(as.vector(KLOSA_w2_cont_rel$w02Ba019_10), "NA='-999'")
KLOSA_w2_cont_rel$w02Bb021 <- car::recode(as.vector(KLOSA_w2_cont_rel$w02Bb021), "NA='-999'")
KLOSA_w2_cont_rel$w02Bb059 <- car::recode(as.vector(KLOSA_w2_cont_rel$w02Bb059), "NA='-999'")
KLOSA_w2_cont_rel$w02Bb097 <- car::recode(as.vector(KLOSA_w2_cont_rel$w02Bb097), "NA='-999'")
KLOSA_w2_cont_rel$w02Ba020_01 <- car::recode(as.vector(KLOSA_w2_cont_rel$w02Ba020_01), "NA='-999'")
KLOSA_w2_cont_rel$w02Ba020_02 <- car::recode(as.vector(KLOSA_w2_cont_rel$w02Ba020_02), "NA='-999'")
KLOSA_w2_cont_rel$w02Ba020_03 <- car::recode(as.vector(KLOSA_w2_cont_rel$w02Ba020_03), "NA='-999'")
KLOSA_w2_cont_rel$w02Ba020_04 <- car::recode(as.vector(KLOSA_w2_cont_rel$w02Ba020_04), "NA='-999'")
KLOSA_w2_cont_rel$w02Ba020_05 <- car::recode(as.vector(KLOSA_w2_cont_rel$w02Ba020_05), "NA='-999'")
KLOSA_w2_cont_rel$w02Ba020_06 <- car::recode(as.vector(KLOSA_w2_cont_rel$w02Ba020_06), "NA='-999'")
KLOSA_w2_cont_rel$w02Ba020_07 <- car::recode(as.vector(KLOSA_w2_cont_rel$w02Ba020_07), "NA='-999'")
KLOSA_w2_cont_rel$w02Ba020_08 <- car::recode(as.vector(KLOSA_w2_cont_rel$w02Ba020_08), "NA='-999'")
KLOSA_w2_cont_rel$w02Ba020_09 <- car::recode(as.vector(KLOSA_w2_cont_rel$w02Ba020_09), "NA='-999'")
KLOSA_w2_cont_rel$w02Ba020_10 <- car::recode(as.vector(KLOSA_w2_cont_rel$w02Ba020_10), "NA='-999'")
KLOSA_w2_cont_rel$w02Bb022 <- car::recode(as.vector(KLOSA_w2_cont_rel$w02Bb022), "NA='-999'")
KLOSA_w2_cont_rel$w02Bb060 <- car::recode(as.vector(KLOSA_w2_cont_rel$w02Bb060), "NA='-999'")
KLOSA_w2_cont_rel$w02Bb098 <- car::recode(as.vector(KLOSA_w2_cont_rel$w02Bb098), "NA='-999'")


KLOSA_ds_w2$cont_rel <- c(NA) 
for(i in 1:dim(KLOSA_w2_cont_rel)[1]){
  if( KLOSA_w2_cont_rel$w02Ba019_01[i] %in% c(1:5) | 
      KLOSA_w2_cont_rel$w02Ba019_02[i] %in% c(1:5) | 
      KLOSA_w2_cont_rel$w02Ba019_03[i] %in% c(1:5) | 
      KLOSA_w2_cont_rel$w02Ba019_04[i] %in% c(1:5) | 
      KLOSA_w2_cont_rel$w02Ba019_05[i] %in% c(1:5) | 
      KLOSA_w2_cont_rel$w02Ba019_06[i] %in% c(1:5) | 
      KLOSA_w2_cont_rel$w02Ba019_07[i] %in% c(1:5) | 
      KLOSA_w2_cont_rel$w02Ba019_08[i] %in% c(1:5) | 
      KLOSA_w2_cont_rel$w02Ba019_09[i] %in% c(1:5) | 
      KLOSA_w2_cont_rel$w02Ba019_10[i] %in% c(1:5) | 
      KLOSA_w2_cont_rel$w02Bb021[i] %in% c(1:5) | 
      KLOSA_w2_cont_rel$w02Bb059[i] %in% c(1:5) | 
      KLOSA_w2_cont_rel$w02Bb097[i] %in% c(1:5) |
      KLOSA_w2_cont_rel$w02Ba020_01[i] %in% c(1:5) | 
      KLOSA_w2_cont_rel$w02Ba020_02[i] %in% c(1:5) | 
      KLOSA_w2_cont_rel$w02Ba020_03[i] %in% c(1:5) | 
      KLOSA_w2_cont_rel$w02Ba020_04[i] %in% c(1:5) | 
      KLOSA_w2_cont_rel$w02Ba020_05[i] %in% c(1:5) | 
      KLOSA_w2_cont_rel$w02Ba020_06[i] %in% c(1:5) | 
      KLOSA_w2_cont_rel$w02Ba020_07[i] %in% c(1:5) | 
      KLOSA_w2_cont_rel$w02Ba020_08[i] %in% c(1:5) | 
      KLOSA_w2_cont_rel$w02Ba020_09[i] %in% c(1:5) | 
      KLOSA_w2_cont_rel$w02Ba020_10[i] %in% c(1:5) | 
      KLOSA_w2_cont_rel$w02Bb022[i] %in% c(1:5) | 
      KLOSA_w2_cont_rel$w02Bb060[i] %in% c(1:5) | 
      KLOSA_w2_cont_rel$w02Bb098[i] %in% c(1:5)) {
    KLOSA_ds_w2$cont_rel[i] = 1 }
  else if( !( KLOSA_w2_cont_rel$w02Ba019_01[i] == -999 & 
              KLOSA_w2_cont_rel$w02Ba019_02[i] == -999 & 
              KLOSA_w2_cont_rel$w02Ba019_03[i] == -999 & 
              KLOSA_w2_cont_rel$w02Ba019_04[i] == -999 & 
              KLOSA_w2_cont_rel$w02Ba019_05[i] == -999 & 
              KLOSA_w2_cont_rel$w02Ba019_06[i] == -999 & 
              KLOSA_w2_cont_rel$w02Ba019_07[i] == -999 & 
              KLOSA_w2_cont_rel$w02Ba019_08[i] == -999 & 
              KLOSA_w2_cont_rel$w02Ba019_09[i] == -999 & 
              KLOSA_w2_cont_rel$w02Ba019_10[i] == -999 & 
              KLOSA_w2_cont_rel$w02Bb021[i] == -999 & 
              KLOSA_w2_cont_rel$w02Bb059[i] == -999 & 
              KLOSA_w2_cont_rel$w02Bb097[i] == -999 &
              KLOSA_w2_cont_rel$w02Ba020_01[i] == -999 & 
              KLOSA_w2_cont_rel$w02Ba020_02[i] == -999 & 
              KLOSA_w2_cont_rel$w02Ba020_03[i] == -999 &
              KLOSA_w2_cont_rel$w02Ba020_04[i] == -999 & 
              KLOSA_w2_cont_rel$w02Ba020_05[i] == -999 & 
              KLOSA_w2_cont_rel$w02Ba020_06[i] == -999 & 
              KLOSA_w2_cont_rel$w02Ba020_07[i] == -999 &
              KLOSA_w2_cont_rel$w02Ba020_08[i] == -999 & 
              KLOSA_w2_cont_rel$w02Ba020_09[i] == -999 & 
              KLOSA_w2_cont_rel$w02Ba020_10[i]== -999 &
              KLOSA_w2_cont_rel$w02Bb022[i]== -999 & 
              KLOSA_w2_cont_rel$w02Bb060[i] == -999 & 
              KLOSA_w2_cont_rel$w02Bb098[i] == -999 ) ) {
    KLOSA_ds_w2$cont_rel[i] = 999 }
  else if( !( KLOSA_w2_cont_rel$w02Ba019_01[i] %in% c(1:5) | 
              KLOSA_w2_cont_rel$w02Ba019_02[i] %in% c(1:5) | 
              KLOSA_w2_cont_rel$w02Ba019_03[i] %in% c(1:5) | 
              KLOSA_w2_cont_rel$w02Ba019_04[i] %in% c(1:5) | 
              KLOSA_w2_cont_rel$w02Ba019_05[i] %in% c(1:5) | 
              KLOSA_w2_cont_rel$w02Ba019_06[i] %in% c(1:5) | 
              KLOSA_w2_cont_rel$w02Ba019_07[i] %in% c(1:5) | 
              KLOSA_w2_cont_rel$w02Ba019_08[i] %in% c(1:5) | 
              KLOSA_w2_cont_rel$w02Ba019_09[i] %in% c(1:5) | 
              KLOSA_w2_cont_rel$w02Ba019_10[i] %in% c(1:5) | 
              KLOSA_w2_cont_rel$w02Bb021[i] %in% c(1:5) |
              KLOSA_w2_cont_rel$w02Bb059[i] %in% c(1:5) | 
              KLOSA_w2_cont_rel$w02Bb097[i] %in% c(1:5) |
              KLOSA_w2_cont_rel$w02Ba020_01[i] %in% c(1:5) | 
              KLOSA_w2_cont_rel$w02Ba020_02[i] %in% c(1:5) | 
              KLOSA_w2_cont_rel$w02Ba020_03[i] %in% c(1:5) | 
              KLOSA_w2_cont_rel$w02Ba020_04[i] %in% c(1:5) | 
              KLOSA_w2_cont_rel$w02Ba020_05[i] %in% c(1:5) | 
              KLOSA_w2_cont_rel$w02Ba020_06[i] %in% c(1:5) | 
              KLOSA_w2_cont_rel$w02Ba020_07[i] %in% c(1:5) | 
              KLOSA_w2_cont_rel$w02Ba020_08[i] %in% c(1:5) | 
              KLOSA_w2_cont_rel$w02Ba020_09[i] %in% c(1:5) | 
              KLOSA_w2_cont_rel$w02Ba020_10[i] %in% c(1:5) | 
              KLOSA_w2_cont_rel$w02Bb022[i] %in% c(1:5) | 
              KLOSA_w2_cont_rel$w02Bb060[i] %in% c(1:5) | 
              KLOSA_w2_cont_rel$w02Bb098[i] %in% c(1:5)
              ) ) {
    KLOSA_ds_w2$cont_rel[i] = 0 }
}



KLOSA_ds_w2$cont_rel <- car::recode(as.vector(KLOSA_ds_w2$cont_rel), "NA='999'")
KLOSA_ds_w2$cont_rel <- labelled(KLOSA_ds_w2$cont_rel, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}
vari <- KLOSA_ds_w2$cont_rel
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w2$cont_rel, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w2, aes(x=factor(cont_rel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are  contacts with family members/relatives frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}

```

 
 


### Wave 3

#### Study-specific variable description

The study-specific variables elected to be harmonised are:

* Name: `w03Ba019_01` UP TO `w03Ba019_01`
* Label: `The frequency which 1st child meets(in person)`
* Categories: 
    + `1 = Almost every day (more than 4 times per week)`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month (every two weeks)`
    + `6 = Once or twice a year`
    + `7 = Three or for times a year (once every three or four months)`
    + `8 = Five or six times a year (every two months)`
    + `9 = Almost never a year`
    + `10 = Never`
* Missings:
    + `-9 = Don't know`
    
* Name: `w03Bb021`
* Label: `The frequency which parents meet(in person)`
* Categories: 
    + `1 = Almost every day (more than 4 times per week)`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month (every two weeks)`
    + `6 = Once or twice a year`
    + `7 = Three or for times a year (once every three or four months)`
    + `8 = Five or six times a year (every two months)`
    + `9 = Almost never a year`
    + `10 = Never`
    
* Name: `w03Bb059`
* Label: `The frequency which father meets(in person) (term of non-coresiding)`
* Categories: 
    + `1 = Almost every day`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month`
    + `6 = Once or twice a year`
    + `7 = Three or for times a year`
    + `8 = Five or six times a year`
    + `9 = Almost never`
    + `10 = Never`
        
* Name: `w03Bb097`
* Label: `The frequency which the mother meet(in person)`
* Categories: 
    + `1 = Almost every day (more than 4 times per week)`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month (every two weeks)`
    + `6 = Once or twice a year`
    + `7 = Three or for times a year (once every three or four months)`
    + `8 = Five or six times a year (every two months)`
    + `9 = Almost never a year`
    + `10 = Never`
   
* Name: `w03Ba020_01` UP TO `w03Ba020_10`
* Label: `The frequency which 1st child meets(by phone, mail or e-mail)`
* Categories: 
    + `1 = Almost every day (more than 4 times per week)`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month (every two weeks)`
    + `6 = Once or twice a year`
    + `7 = Three or for times a year (once every three or four months)`
    + `8 = Five or six times a year (every two months)`
    + `9 = Almost never a year`
    + `10 = Never`
* Missings: 
    + `-9, -8 = ???`
    
* Name: `w03Bb022`
* Label: `The frequency which parents meet(by phone, mail or e-mail)`
* Categories: 
    + `1 = Almost every day (more than 4 times per week)`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month (every two weeks)`
    + `6 = Once or twice a year`
    + `7 = Three or for times a year (once every three or four months)`
    + `8 = Five or six times a year (every two months)`
    + `9 = Almost never a year`
    + `10 = Never`
    
* Name: `w03Bb060`
* Label: `The frequency which father meets(by phone, mail or e-mail) (term of non-coresiding)`
* Categories: 
    + `1 = Almost every day (more than 4 times per week)`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month (every two weeks)`
    + `6 = Once or twice a year`
    + `7 = Three or for times a year (once every three or four months)`
    + `8 = Five or six times a year (every two months)`
    + `9 = Almost never a year`
    + `10 = Never`
    
* Name: `w03Bb098`
* Label: `The frequency which mother meets(by phone, mail or e-mail) (term of non-coresiding)`
* Categories: 
    + `1 = Almost every day (more than 4 times per week)`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month (every two weeks)`
    + `6 = Once or twice a year`
    + `7 = Three or for times a year (once every three or four months)`
    + `8 = Five or six times a year (every two months)`
    + `9 = Almost never a year`
    + `10 = Never`
     

* Description: 
```{r assign3, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w3_cont_rel','KLOSA.w03_main_e_spss_albert',
                         variables=list('w03Ba019_01','w03Ba019_02','w03Ba019_03','w03Ba019_04','w03Ba019_05','w03Ba019_06','w03Ba019_07','w03Ba019_08','w03Ba019_09','w03Ba019_10',
                                       'w03Bb021','w03Bb059','w03Bb097',
                                       'w03Ba020_01','w03Ba020_02','w03Ba020_03','w03Ba020_04','w03Ba020_05','w03Ba020_06','w03Ba020_07','w03Ba020_08','w03Ba020_09','w03Ba020_10',
                                       'w03Bb022','w03Bb060','w03Bb098'), missings = TRUE)
KLOSA_w3_cont_rel <- opal.execute(o,'KLOSA_w3_cont_rel')
# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_w3_cont_rel$id <- substr(KLOSA_w3_cont_rel$id,1,nchar(KLOSA_w3_cont_rel$id)-2)
```

```{r local3, echo=F}
vari <- KLOSA_w3_cont_rel$w03Ba019_01
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w3_cont_rel, aes(x=factor(w03Ba019_01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The frequency which 1st child meets(in person)") + ylab("Frequency")


vari <- KLOSA_w3_cont_rel$w03Bb021
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w3_cont_rel, aes(x=factor(w03Bb021)))+ geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The frequency which parents meet(in person)") + ylab("Frequency")

vari <- KLOSA_w3_cont_rel$w03Bb059
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w3_cont_rel, aes(x=factor(w03Bb059))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The frequency which father meet(in person)") + ylab("Frequency")

vari <- KLOSA_w3_cont_rel$w03Bb097
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w3_cont_rel, aes(x=factor(w03Bb097))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The frequency which mother meet(in person)") + ylab("Frequency")

vari <- KLOSA_w3_cont_rel$w03Ba020_01
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w3_cont_rel, aes(x=factor(w03Ba020_01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The times which 1st child meets(by phone, mail or e-mail)") + ylab("Frequency")


vari <- KLOSA_w3_cont_rel$w03Bb022
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w3_cont_rel, aes(x=factor(w03Bb022))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The frequency which parents meet(by phone, mail or e-mail)") + ylab("Frequency")

vari <- KLOSA_w3_cont_rel$w03Bb060
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w3_cont_rel, aes(x=factor(w03Bb060))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The frequency which father meet(by phone, mail or e-mail)") + ylab("Frequency")

vari <- KLOSA_w3_cont_rel$w03Bb098
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w3_cont_rel, aes(x=factor(w03Bb098))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The frequency which mother meet(by phone, mail or e-mail)") + ylab("Frequency")

```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if any variable from 'w03Ba019_01' to 'w03Ba019_10' or 'w03Bb021', 'w03Bb059', 'w03Bb097' is in 1:5 then 1`
* `if any variable from 'w03Ba020_01' to 'w03Ba020_10' or 'w03Bb022','w03Bb060','w03Bb098' is in 1:3 then 1`
* `NA into 999`

**R script:**

```{r harmo3, echo=TRUE}
KLOSA_ds_w3 <- tibble(id=KLOSA_w3_cont_rel$id)

KLOSA_w3_cont_rel$w03Ba019_01 <- car::recode(as.vector(KLOSA_w3_cont_rel$w03Ba019_01), "NA='-999'")
KLOSA_w3_cont_rel$w03Ba019_02 <- car::recode(as.vector(KLOSA_w3_cont_rel$w03Ba019_02), "NA='-999'")
KLOSA_w3_cont_rel$w03Ba019_03 <- car::recode(as.vector(KLOSA_w3_cont_rel$w03Ba019_03), "NA='-999'")
KLOSA_w3_cont_rel$w03Ba019_04 <- car::recode(as.vector(KLOSA_w3_cont_rel$w03Ba019_04), "NA='-999'")
KLOSA_w3_cont_rel$w03Ba019_05 <- car::recode(as.vector(KLOSA_w3_cont_rel$w03Ba019_05), "NA='-999'")
KLOSA_w3_cont_rel$w03Ba019_06 <- car::recode(as.vector(KLOSA_w3_cont_rel$w03Ba019_06), "NA='-999'")
KLOSA_w3_cont_rel$w03Ba019_07 <- car::recode(as.vector(KLOSA_w3_cont_rel$w03Ba019_07), "NA='-999'")
KLOSA_w3_cont_rel$w03Ba019_08 <- car::recode(as.vector(KLOSA_w3_cont_rel$w03Ba019_08), "NA='-999'")
KLOSA_w3_cont_rel$w03Ba019_09 <- car::recode(as.vector(KLOSA_w3_cont_rel$w03Ba019_09), "NA='-999'")
KLOSA_w3_cont_rel$w03Ba019_10 <- car::recode(as.vector(KLOSA_w3_cont_rel$w03Ba019_10), "NA='-999'")
KLOSA_w3_cont_rel$w03Bb021 <- car::recode(as.vector(KLOSA_w3_cont_rel$w03Bb021), "NA='-999'")
KLOSA_w3_cont_rel$w03Bb059 <- car::recode(as.vector(KLOSA_w3_cont_rel$w03Bb059), "NA='-999'")
KLOSA_w3_cont_rel$w03Bb097 <- car::recode(as.vector(KLOSA_w3_cont_rel$w03Bb097), "NA='-999'")
KLOSA_w3_cont_rel$w03Ba020_01 <- car::recode(as.vector(KLOSA_w3_cont_rel$w03Ba020_01), "NA='-999'")
KLOSA_w3_cont_rel$w03Ba020_02 <- car::recode(as.vector(KLOSA_w3_cont_rel$w03Ba020_02), "NA='-999'")
KLOSA_w3_cont_rel$w03Ba020_03 <- car::recode(as.vector(KLOSA_w3_cont_rel$w03Ba020_03), "NA='-999'")
KLOSA_w3_cont_rel$w03Ba020_04 <- car::recode(as.vector(KLOSA_w3_cont_rel$w03Ba020_04), "NA='-999'")
KLOSA_w3_cont_rel$w03Ba020_05 <- car::recode(as.vector(KLOSA_w3_cont_rel$w03Ba020_05), "NA='-999'")
KLOSA_w3_cont_rel$w03Ba020_06 <- car::recode(as.vector(KLOSA_w3_cont_rel$w03Ba020_06), "NA='-999'")
KLOSA_w3_cont_rel$w03Ba020_07 <- car::recode(as.vector(KLOSA_w3_cont_rel$w03Ba020_07), "NA='-999'")
KLOSA_w3_cont_rel$w03Ba020_08 <- car::recode(as.vector(KLOSA_w3_cont_rel$w03Ba020_08), "NA='-999'")
KLOSA_w3_cont_rel$w03Ba020_09 <- car::recode(as.vector(KLOSA_w3_cont_rel$w03Ba020_09), "NA='-999'")
KLOSA_w3_cont_rel$w03Ba020_10 <- car::recode(as.vector(KLOSA_w3_cont_rel$w03Ba020_10), "NA='-999'")
KLOSA_w3_cont_rel$w03Bb022 <- car::recode(as.vector(KLOSA_w3_cont_rel$w03Bb022), "NA='-999'")
KLOSA_w3_cont_rel$w03Bb060 <- car::recode(as.vector(KLOSA_w3_cont_rel$w03Bb060), "NA='-999'")
KLOSA_w3_cont_rel$w03Bb098 <- car::recode(as.vector(KLOSA_w3_cont_rel$w03Bb098), "NA='-999'")


KLOSA_ds_w3$cont_rel <- c(NA) 
for(i in 1:dim(KLOSA_w3_cont_rel)[1]){
  if( KLOSA_w3_cont_rel$w03Ba019_01[i] %in% c(1:5) | 
      KLOSA_w3_cont_rel$w03Ba019_02[i] %in% c(1:5) | 
      KLOSA_w3_cont_rel$w03Ba019_03[i] %in% c(1:5) | 
      KLOSA_w3_cont_rel$w03Ba019_04[i] %in% c(1:5) | 
      KLOSA_w3_cont_rel$w03Ba019_05[i] %in% c(1:5) | 
      KLOSA_w3_cont_rel$w03Ba019_06[i] %in% c(1:5) | 
      KLOSA_w3_cont_rel$w03Ba019_07[i] %in% c(1:5) | 
      KLOSA_w3_cont_rel$w03Ba019_08[i] %in% c(1:5) | 
      KLOSA_w3_cont_rel$w03Ba019_09[i] %in% c(1:5) | 
      KLOSA_w3_cont_rel$w03Ba019_10[i] %in% c(1:5) | 
      KLOSA_w3_cont_rel$w03Bb021[i] %in% c(1:5) | 
      KLOSA_w3_cont_rel$w03Bb059[i] %in% c(1:5) | 
      KLOSA_w3_cont_rel$w03Bb097[i] %in% c(1:5) |
      KLOSA_w3_cont_rel$w03Ba020_01[i] %in% c(1:5) | 
      KLOSA_w3_cont_rel$w03Ba020_02[i] %in% c(1:5) | 
      KLOSA_w3_cont_rel$w03Ba020_03[i] %in% c(1:5) | 
      KLOSA_w3_cont_rel$w03Ba020_04[i] %in% c(1:5) | 
      KLOSA_w3_cont_rel$w03Ba020_05[i] %in% c(1:5) | 
      KLOSA_w3_cont_rel$w03Ba020_06[i] %in% c(1:5) | 
      KLOSA_w3_cont_rel$w03Ba020_07[i] %in% c(1:5) | 
      KLOSA_w3_cont_rel$w03Ba020_08[i] %in% c(1:5) | 
      KLOSA_w3_cont_rel$w03Ba020_09[i] %in% c(1:5) | 
      KLOSA_w3_cont_rel$w03Ba020_10[i] %in% c(1:5) | 
      KLOSA_w3_cont_rel$w03Bb022[i] %in% c(1:5) | 
      KLOSA_w3_cont_rel$w03Bb060[i] %in% c(1:5) | 
      KLOSA_w3_cont_rel$w03Bb098[i] %in% c(1:5)) {
    KLOSA_ds_w3$cont_rel[i] = 1 }
  else if( !( KLOSA_w3_cont_rel$w03Ba019_01[i] == -999 & 
              KLOSA_w3_cont_rel$w03Ba019_02[i] == -999 & 
              KLOSA_w3_cont_rel$w03Ba019_03[i] == -999 & 
              KLOSA_w3_cont_rel$w03Ba019_04[i] == -999 & 
              KLOSA_w3_cont_rel$w03Ba019_05[i] == -999 & 
              KLOSA_w3_cont_rel$w03Ba019_06[i] == -999 & 
              KLOSA_w3_cont_rel$w03Ba019_07[i] == -999 & 
              KLOSA_w3_cont_rel$w03Ba019_08[i] == -999 & 
              KLOSA_w3_cont_rel$w03Ba019_09[i] == -999 & 
              KLOSA_w3_cont_rel$w03Ba019_10[i] == -999 & 
              KLOSA_w3_cont_rel$w03Bb021[i] == -999 & 
              KLOSA_w3_cont_rel$w03Bb059[i] == -999 & 
              KLOSA_w3_cont_rel$w03Bb097[i] == -999 &
              KLOSA_w3_cont_rel$w03Ba020_01[i] == -999 & 
              KLOSA_w3_cont_rel$w03Ba020_02[i] == -999 & 
              KLOSA_w3_cont_rel$w03Ba020_03[i] == -999 &
              KLOSA_w3_cont_rel$w03Ba020_04[i] == -999 & 
              KLOSA_w3_cont_rel$w03Ba020_05[i] == -999 & 
              KLOSA_w3_cont_rel$w03Ba020_06[i] == -999 & 
              KLOSA_w3_cont_rel$w03Ba020_07[i] == -999 &
              KLOSA_w3_cont_rel$w03Ba020_08[i] == -999 & 
              KLOSA_w3_cont_rel$w03Ba020_09[i] == -999 & 
              KLOSA_w3_cont_rel$w03Ba020_10[i]== -999 &
              KLOSA_w3_cont_rel$w03Bb022[i]== -999 & 
              KLOSA_w3_cont_rel$w03Bb060[i] == -999 & 
              KLOSA_w3_cont_rel$w03Bb098[i] == -999 ) ) {
    KLOSA_ds_w3$cont_rel[i] = 999 }
  else if( !( KLOSA_w3_cont_rel$w03Ba019_01[i] %in% c(1:5) | 
              KLOSA_w3_cont_rel$w03Ba019_02[i] %in% c(1:5) | 
              KLOSA_w3_cont_rel$w03Ba019_03[i] %in% c(1:5) | 
              KLOSA_w3_cont_rel$w03Ba019_04[i] %in% c(1:5) | 
              KLOSA_w3_cont_rel$w03Ba019_05[i] %in% c(1:5) | 
              KLOSA_w3_cont_rel$w03Ba019_06[i] %in% c(1:5) | 
              KLOSA_w3_cont_rel$w03Ba019_07[i] %in% c(1:5) | 
              KLOSA_w3_cont_rel$w03Ba019_08[i] %in% c(1:5) | 
              KLOSA_w3_cont_rel$w03Ba019_09[i] %in% c(1:5) | 
              KLOSA_w3_cont_rel$w03Ba019_10[i] %in% c(1:5) | 
              KLOSA_w3_cont_rel$w03Bb021[i] %in% c(1:5) |
              KLOSA_w3_cont_rel$w03Bb059[i] %in% c(1:5) | 
              KLOSA_w3_cont_rel$w03Bb097[i] %in% c(1:5) |
              KLOSA_w3_cont_rel$w03Ba020_01[i] %in% c(1:5) | 
              KLOSA_w3_cont_rel$w03Ba020_02[i] %in% c(1:5) | 
              KLOSA_w3_cont_rel$w03Ba020_03[i] %in% c(1:5) | 
              KLOSA_w3_cont_rel$w03Ba020_04[i] %in% c(1:5) | 
              KLOSA_w3_cont_rel$w03Ba020_05[i] %in% c(1:5) | 
              KLOSA_w3_cont_rel$w03Ba020_06[i] %in% c(1:5) | 
              KLOSA_w3_cont_rel$w03Ba020_07[i] %in% c(1:5) | 
              KLOSA_w3_cont_rel$w03Ba020_08[i] %in% c(1:5) | 
              KLOSA_w3_cont_rel$w03Ba020_09[i] %in% c(1:5) | 
              KLOSA_w3_cont_rel$w03Ba020_10[i] %in% c(1:5) | 
              KLOSA_w3_cont_rel$w03Bb022[i] %in% c(1:5) | 
              KLOSA_w3_cont_rel$w03Bb060[i] %in% c(1:5) | 
              KLOSA_w3_cont_rel$w03Bb098[i] %in% c(1:5)
              ) ) {
    KLOSA_ds_w3$cont_rel[i] = 0 }
}


KLOSA_ds_w3$cont_rel <- car::recode(as.vector(KLOSA_ds_w3$cont_rel), "NA='999'")
KLOSA_ds_w3$cont_rel <- labelled(KLOSA_ds_w3$cont_rel, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=F}
vari <- KLOSA_ds_w3$cont_rel
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w3$cont_rel, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w3, aes(x=factor(cont_rel))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Are contacts with family members/relatives frequent") + ylab("Frequency")
```

##### Validation
```{r crosstabulation3, echo=F}

```

 
 

### Wave 4

#### Study-specific variable description

The study-specific variables elected to be harmonised are:

* Name: `w04Ba019_01` UP TO `w04Ba019_01`
* Label: `The frequency which 1st child meets(in person)`
* Categories: 
    + `1 = Almost every day (more than 4 times per week)`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month (every two weeks)`
    + `6 = Once or twice a year`
    + `7 = Three or for times a year (once every three or four months)`
    + `8 = Five or six times a year (every two months)`
    + `9 = Almost never a year`
    + `10 = Never`
    
* Name: `w04Bb021`
* Label: `The frequency which parents meet(in person)`
* Categories: 
    + `1 = Almost every day (more than 4 times per week)`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month (every two weeks)`
    + `6 = Once or twice a year`
    + `7 = Three or for times a year (once every three or four months)`
    + `8 = Five or six times a year (every two months)`
    + `9 = Almost never a year`
    + `10 = Never`
    
* Name: `w04Bb059`
* Label: `The frequency which father meets(in person) (term of non-coresiding)`
* Categories: 
    + `1 = Almost every day`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month`
    + `6 = Once or twice a year`
    + `7 = Three or for times a year`
    + `8 = Five or six times a year`
    + `9 = Almost never`
    + `10 = Never`
        
* Name: `w04Bb097`
* Label: `The frequency which the mother meet(in person)`
* Categories: 
    + `1 = Almost every day (more than 4 times per week)`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month (every two weeks)`
    + `6 = Once or twice a year`
    + `7 = Three or for times a year (once every three or four months)`
    + `8 = Five or six times a year (every two months)`
    + `9 = Almost never a year`
    + `10 = Never`
    
* Name: `w04Ba020_01` UP TO `w04Ba020_10`
* Label: `The frequency which 1st child meets(by phone, mail or e-mail)`
* Categories: 
    + `1 = Almost every day (more than 4 times per week)`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month (every two weeks)`
    + `6 = Once or twice a year`
    + `7 = Three or for times a year (once every three or four months)`
    + `8 = Five or six times a year (every two months)`
    + `9 = Almost never a year`
    + `10 = Never`
    
* Name: `w04Bb022`
* Label: `The frequency which parents meet(by phone, mail or e-mail)`
* Categories: 
    + `1 = Almost every day (more than 4 times per week)`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month (every two weeks)`
    + `6 = Once or twice a year`
    + `7 = Three or for times a year (once every three or four months)`
    + `8 = Five or six times a year (every two months)`
    + `9 = Almost never a year`
    + `10 = Never`
    
* Name: `w04Bb060`
* Label: `The frequency which father meets(by phone, mail or e-mail) (term of non-coresiding)`
* Categories: 
    + `1 = Almost every day (more than 4 times per week)`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month (every two weeks)`
    + `6 = Once or twice a year`
    + `7 = Three or for times a year (once every three or four months)`
    + `8 = Five or six times a year (every two months)`
    + `9 = Almost never a year`
    + `10 = Never`
    
* Name: `w04Bb098`
* Label: `The frequency which mother meets(by phone, mail or e-mail) (term of non-coresiding)`
* Categories: 
    + `1 = Almost every day (more than 4 times per week)`
    + `2 = Once a week`
    + `3 = 2-3 times a week`
    + `4 = Once a month`
    + `5 = Twice a month (every two weeks)`
    + `6 = Once or twice a year`
    + `7 = Three or for times a year (once every three or four months)`
    + `8 = Five or six times a year (every two months)`
    + `9 = Almost never a year`
    + `10 = Never`
    
* Description: 
```{r assign4, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w4_cont_rel','KLOSA.w04_main_e_spss',
                         variables=list('w04Ba019_01','w04Ba019_02','w04Ba019_03','w04Ba019_04','w04Ba019_05','w04Ba019_06','w04Ba019_07','w04Ba019_08','w04Ba019_09','w04Ba019_10',
                                        'w04Bb021','w04Bb059','w04Bb097', 
                                        'w04Ba020_01','w04Ba020_02','w04Ba020_03','w04Ba020_04','w04Ba020_05','w04Ba020_06','w04Ba020_07','w04Ba020_08','w04Ba020_09','w04Ba020_10',
                                        'w04Bb022','w04Bb060','w04Bb098'), missings = TRUE)
```

```{r local4, echo=F}
KLOSA_w4_cont_rel <- opal.execute(o,'KLOSA_w4_cont_rel')

vari <- KLOSA_w4_cont_rel$w04Ba019_01
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w4_cont_rel, aes(x=factor(w04Ba019_01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The frequency which 1st child meets(in person)") + ylab("Frequency")


vari <- KLOSA_w4_cont_rel$w04Bb021
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w4_cont_rel, aes(x=factor(w04Bb021)))+ geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The frequency which parents meet(in person)") + ylab("Frequency")

vari <- KLOSA_w4_cont_rel$w04Bb059
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w4_cont_rel, aes(x=factor(w04Bb059))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The frequency which father meet(in person)") + ylab("Frequency")

vari <- KLOSA_w4_cont_rel$w04Bb097
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w4_cont_rel, aes(x=factor(w04Bb097))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The frequency which mother meet(in person)") + ylab("Frequency")

vari <- KLOSA_w4_cont_rel$w04Ba020_01
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w4_cont_rel, aes(x=factor(w04Ba020_01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The times which 1st child meets(by phone, mail or e-mail)") + ylab("Frequency")


vari <- KLOSA_w4_cont_rel$w04Bb022
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w4_cont_rel, aes(x=factor(w04Bb022))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The frequency which parents meet(by phone, mail or e-mail)") + ylab("Frequency")

vari <- KLOSA_w4_cont_rel$w04Bb060
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w4_cont_rel, aes(x=factor(w04Bb060))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The frequency which father meet(by phone, mail or e-mail)") + ylab("Frequency")

vari <- KLOSA_w4_cont_rel$w04Bb098
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(KLOSA_w4_cont_rel, aes(x=factor(w04Bb098))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The frequency which mother meet(by phone, mail or e-mail)") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if any variable from 'w04Ba019_01' to 'w04Ba019_10' or 'w04Bb021', 'w04Bb059', 'w04Bb097' is in 1:5 then 1`
* `if any variable from 'w04Ba020_01' to 'w04Ba020_10' or 'w04Bb022','w04Bb060','w04Bb098' is in 1:3 then 1`
* `NA into 999`

**R script:**

```{r harmo4, echo=TRUE}
KLOSA_ds_w4 <- tibble(id=KLOSA_w4_cont_rel$id)

KLOSA_w4_cont_rel$w04Ba019_01 <- car::recode(as.vector(KLOSA_w4_cont_rel$w04Ba019_01), "NA='-999'")
KLOSA_w4_cont_rel$w04Ba019_02 <- car::recode(as.vector(KLOSA_w4_cont_rel$w04Ba019_02), "NA='-999'")
KLOSA_w4_cont_rel$w04Ba019_03 <- car::recode(as.vector(KLOSA_w4_cont_rel$w04Ba019_03), "NA='-999'")
KLOSA_w4_cont_rel$w04Ba019_04 <- car::recode(as.vector(KLOSA_w4_cont_rel$w04Ba019_04), "NA='-999'")
KLOSA_w4_cont_rel$w04Ba019_05 <- car::recode(as.vector(KLOSA_w4_cont_rel$w04Ba019_05), "NA='-999'")
KLOSA_w4_cont_rel$w04Ba019_06 <- car::recode(as.vector(KLOSA_w4_cont_rel$w04Ba019_06), "NA='-999'")
KLOSA_w4_cont_rel$w04Ba019_07 <- car::recode(as.vector(KLOSA_w4_cont_rel$w04Ba019_07), "NA='-999'")
KLOSA_w4_cont_rel$w04Ba019_08 <- car::recode(as.vector(KLOSA_w4_cont_rel$w04Ba019_08), "NA='-999'")
KLOSA_w4_cont_rel$w04Ba019_09 <- car::recode(as.vector(KLOSA_w4_cont_rel$w04Ba019_09), "NA='-999'")
KLOSA_w4_cont_rel$w04Ba019_10 <- car::recode(as.vector(KLOSA_w4_cont_rel$w04Ba019_10), "NA='-999'")
KLOSA_w4_cont_rel$w04Bb021 <- car::recode(as.vector(KLOSA_w4_cont_rel$w04Bb021), "NA='-999'")
KLOSA_w4_cont_rel$w04Bb059 <- car::recode(as.vector(KLOSA_w4_cont_rel$w04Bb059), "NA='-999'")
KLOSA_w4_cont_rel$w04Bb097 <- car::recode(as.vector(KLOSA_w4_cont_rel$w04Bb097), "NA='-999'")
KLOSA_w4_cont_rel$w04Ba020_01 <- car::recode(as.vector(KLOSA_w4_cont_rel$w04Ba020_01), "NA='-999'")
KLOSA_w4_cont_rel$w04Ba020_02 <- car::recode(as.vector(KLOSA_w4_cont_rel$w04Ba020_02), "NA='-999'")
KLOSA_w4_cont_rel$w04Ba020_03 <- car::recode(as.vector(KLOSA_w4_cont_rel$w04Ba020_03), "NA='-999'")
KLOSA_w4_cont_rel$w04Ba020_04 <- car::recode(as.vector(KLOSA_w4_cont_rel$w04Ba020_04), "NA='-999'")
KLOSA_w4_cont_rel$w04Ba020_05 <- car::recode(as.vector(KLOSA_w4_cont_rel$w04Ba020_05), "NA='-999'")
KLOSA_w4_cont_rel$w04Ba020_06 <- car::recode(as.vector(KLOSA_w4_cont_rel$w04Ba020_06), "NA='-999'")
KLOSA_w4_cont_rel$w04Ba020_07 <- car::recode(as.vector(KLOSA_w4_cont_rel$w04Ba020_07), "NA='-999'")
KLOSA_w4_cont_rel$w04Ba020_08 <- car::recode(as.vector(KLOSA_w4_cont_rel$w04Ba020_08), "NA='-999'")
KLOSA_w4_cont_rel$w04Ba020_09 <- car::recode(as.vector(KLOSA_w4_cont_rel$w04Ba020_09), "NA='-999'")
KLOSA_w4_cont_rel$w04Ba020_10 <- car::recode(as.vector(KLOSA_w4_cont_rel$w04Ba020_10), "NA='-999'")
KLOSA_w4_cont_rel$w04Bb022 <- car::recode(as.vector(KLOSA_w4_cont_rel$w04Bb022), "NA='-999'")
KLOSA_w4_cont_rel$w04Bb060 <- car::recode(as.vector(KLOSA_w4_cont_rel$w04Bb060), "NA='-999'")
KLOSA_w4_cont_rel$w04Bb098 <- car::recode(as.vector(KLOSA_w4_cont_rel$w04Bb098), "NA='-999'")


KLOSA_ds_w4$cont_rel <- c(NA) 
for(i in 1:dim(KLOSA_w4_cont_rel)[1]){
  if( KLOSA_w4_cont_rel$w04Ba019_01[i] %in% c(1:5) | 
      KLOSA_w4_cont_rel$w04Ba019_02[i] %in% c(1:5) | 
      KLOSA_w4_cont_rel$w04Ba019_03[i] %in% c(1:5) | 
      KLOSA_w4_cont_rel$w04Ba019_04[i] %in% c(1:5) | 
      KLOSA_w4_cont_rel$w04Ba019_05[i] %in% c(1:5) | 
      KLOSA_w4_cont_rel$w04Ba019_06[i] %in% c(1:5) | 
      KLOSA_w4_cont_rel$w04Ba019_07[i] %in% c(1:5) | 
      KLOSA_w4_cont_rel$w04Ba019_08[i] %in% c(1:5) | 
      KLOSA_w4_cont_rel$w04Ba019_09[i] %in% c(1:5) | 
      KLOSA_w4_cont_rel$w04Ba019_10[i] %in% c(1:5) | 
      KLOSA_w4_cont_rel$w04Bb021[i] %in% c(1:5) | 
      KLOSA_w4_cont_rel$w04Bb059[i] %in% c(1:5) | 
      KLOSA_w4_cont_rel$w04Bb097[i] %in% c(1:5) |
      KLOSA_w4_cont_rel$w04Ba020_01[i] %in% c(1:5) | 
      KLOSA_w4_cont_rel$w04Ba020_02[i] %in% c(1:5) | 
      KLOSA_w4_cont_rel$w04Ba020_03[i] %in% c(1:5) | 
      KLOSA_w4_cont_rel$w04Ba020_04[i] %in% c(1:5) | 
      KLOSA_w4_cont_rel$w04Ba020_05[i] %in% c(1:5) | 
      KLOSA_w4_cont_rel$w04Ba020_06[i] %in% c(1:5) | 
      KLOSA_w4_cont_rel$w04Ba020_07[i] %in% c(1:5) | 
      KLOSA_w4_cont_rel$w04Ba020_08[i] %in% c(1:5) | 
      KLOSA_w4_cont_rel$w04Ba020_09[i] %in% c(1:5) | 
      KLOSA_w4_cont_rel$w04Ba020_10[i] %in% c(1:5) | 
      KLOSA_w4_cont_rel$w04Bb022[i] %in% c(1:5) | 
      KLOSA_w4_cont_rel$w04Bb060[i] %in% c(1:5) | 
      KLOSA_w4_cont_rel$w04Bb098[i] %in% c(1:5)) {
    KLOSA_ds_w4$cont_rel[i] = 1 }
  else if( !( KLOSA_w4_cont_rel$w04Ba019_01[i] == -999 & 
              KLOSA_w4_cont_rel$w04Ba019_02[i] == -999 & 
              KLOSA_w4_cont_rel$w04Ba019_03[i] == -999 & 
              KLOSA_w4_cont_rel$w04Ba019_04[i] == -999 & 
              KLOSA_w4_cont_rel$w04Ba019_05[i] == -999 & 
              KLOSA_w4_cont_rel$w04Ba019_06[i] == -999 & 
              KLOSA_w4_cont_rel$w04Ba019_07[i] == -999 & 
              KLOSA_w4_cont_rel$w04Ba019_08[i] == -999 & 
              KLOSA_w4_cont_rel$w04Ba019_09[i] == -999 & 
              KLOSA_w4_cont_rel$w04Ba019_10[i] == -999 & 
              KLOSA_w4_cont_rel$w04Bb021[i] == -999 & 
              KLOSA_w4_cont_rel$w04Bb059[i] == -999 & 
              KLOSA_w4_cont_rel$w04Bb097[i] == -999 &
              KLOSA_w4_cont_rel$w04Ba020_01[i] == -999 & 
              KLOSA_w4_cont_rel$w04Ba020_02[i] == -999 & 
              KLOSA_w4_cont_rel$w04Ba020_03[i] == -999 &
              KLOSA_w4_cont_rel$w04Ba020_04[i] == -999 & 
              KLOSA_w4_cont_rel$w04Ba020_05[i] == -999 & 
              KLOSA_w4_cont_rel$w04Ba020_06[i] == -999 & 
              KLOSA_w4_cont_rel$w04Ba020_07[i] == -999 &
              KLOSA_w4_cont_rel$w04Ba020_08[i] == -999 & 
              KLOSA_w4_cont_rel$w04Ba020_09[i] == -999 & 
              KLOSA_w4_cont_rel$w04Ba020_10[i]== -999 &
              KLOSA_w4_cont_rel$w04Bb022[i]== -999 & 
              KLOSA_w4_cont_rel$w04Bb060[i] == -999 & 
              KLOSA_w4_cont_rel$w04Bb098[i] == -999 ) ) {
    KLOSA_ds_w4$cont_rel[i] = 999 }
  else if( !( KLOSA_w4_cont_rel$w04Ba019_01[i] %in% c(1:5) | 
              KLOSA_w4_cont_rel$w04Ba019_02[i] %in% c(1:5) | 
              KLOSA_w4_cont_rel$w04Ba019_03[i] %in% c(1:5) | 
              KLOSA_w4_cont_rel$w04Ba019_04[i] %in% c(1:5) | 
              KLOSA_w4_cont_rel$w04Ba019_05[i] %in% c(1:5) | 
              KLOSA_w4_cont_rel$w04Ba019_06[i] %in% c(1:5) | 
              KLOSA_w4_cont_rel$w04Ba019_07[i] %in% c(1:5) | 
              KLOSA_w4_cont_rel$w04Ba019_08[i] %in% c(1:5) | 
              KLOSA_w4_cont_rel$w04Ba019_09[i] %in% c(1:5) | 
              KLOSA_w4_cont_rel$w04Ba019_10[i] %in% c(1:5) | 
              KLOSA_w4_cont_rel$w04Bb021[i] %in% c(1:5) |
              KLOSA_w4_cont_rel$w04Bb059[i] %in% c(1:5) | 
              KLOSA_w4_cont_rel$w04Bb097[i] %in% c(1:5) |
              KLOSA_w4_cont_rel$w04Ba020_01[i] %in% c(1:5) | 
              KLOSA_w4_cont_rel$w04Ba020_02[i] %in% c(1:5) | 
              KLOSA_w4_cont_rel$w04Ba020_03[i] %in% c(1:5) | 
              KLOSA_w4_cont_rel$w04Ba020_04[i] %in% c(1:5) | 
              KLOSA_w4_cont_rel$w04Ba020_05[i] %in% c(1:5) | 
              KLOSA_w4_cont_rel$w04Ba020_06[i] %in% c(1:5) | 
              KLOSA_w4_cont_rel$w04Ba020_07[i] %in% c(1:5) | 
              KLOSA_w4_cont_rel$w04Ba020_08[i] %in% c(1:5) | 
              KLOSA_w4_cont_rel$w04Ba020_09[i] %in% c(1:5) | 
              KLOSA_w4_cont_rel$w04Ba020_10[i] %in% c(1:5) | 
              KLOSA_w4_cont_rel$w04Bb022[i] %in% c(1:5) | 
              KLOSA_w4_cont_rel$w04Bb060[i] %in% c(1:5) | 
              KLOSA_w4_cont_rel$w04Bb098[i] %in% c(1:5)
              ) ) {
    KLOSA_ds_w4$cont_rel[i] = 0 }
}

KLOSA_ds_w4$cont_rel <- car::recode(as.vector(KLOSA_ds_w4$cont_rel), "NA='999'")
KLOSA_ds_w4$cont_rel <- labelled(KLOSA_ds_w4$cont_rel, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4, echo=F}
vari <- KLOSA_ds_w4$cont_rel
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w4$cont_rel, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w4, aes(x=factor(cont_rel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are contacts with family members/relatives frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=F}

```

```{r save, echo=FALSE}

cont_rel <- KLOSA_ds_w1
save(cont_rel, file = "../RData/w1/cont_rel.RData")
rm(cont_rel)

cont_rel <- KLOSA_ds_w2
save(cont_rel, file = "../RData/w2/cont_rel.RData")
rm(cont_rel)

cont_rel <- KLOSA_ds_w3
save(cont_rel, file = "../RData/w3/cont_rel.RData")
rm(cont_rel)

cont_rel <- KLOSA_ds_w4
save(cont_rel, file = "../RData/w4/cont_rel.RData")
rm(cont_rel)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```




 
