---
title: "Whether receives instrumental support (practical help) from people outside the household (relatives/friends/neighbours)"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `inst_sup`
* Variable label: `Instrumental support (practical help) from people outside the household (relatives/friends/neighbours)`
* Domain: `Social environment`
* Value type: `categorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process
## Korea

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w01Cb18`
* Label: `Nursing attendance who help most for everyday life achievement now (relation with respondent)`
* Categories: 
    + `1 = R`
    + `2 = Spouse`
    + `3 = Mother`
    + `4 = Father`
    + `5 = Mother-in-law`
    + `6 = Father-in-law`
    + `7 = 1st child`
    + `8 = 2nd child`
    + `9 = 3rd child`
    + `10 = 4th child`
    + `11 = 5th child`
    + `12 = 6th child`
    + `13 = 7th child`
    + `14 = 8th child`
    + `15 = 9th child`
    + `16 = 10th child`
    + `27 = 1st sibiling`
    + `28 = 2nd sibiling`
    + `29 = 3rd sibiling`
    + `30 = 4th sibiling`
    + `31 = 5st sibiling`
    + `32 = 6th sibiling`
    + `33 = 7th sibiling`
    + `34 = 8th sibiling`
    + `35 = 9th sibiling`
    + `36 = 10th sibiling`
    + `37 = 11th sibiling`
    + `38 = 12th sibiling`
    + `39 = 13th sibiling`
    + `40 = 14th sibiling`
    + `47 = Brother-in-law, sister-in-law`
    + `48 = Spouse of child`
    + `49 = Grandchild`
    + `50 = Other relative`
    + `55 = Helper or other non-relative`
    + `56 = No one helped`
    

* Description: 
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w1_inst_sup','KLOSA.w01_main_e', variables=list('w01Cb18'), missings = TRUE)
```

```{r local1, echo=F}
KLOSA_w1_inst_sup <- opal.execute(o,'KLOSA_w1_inst_sup')
vari <- KLOSA_w1_inst_sup$w01Cb18
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w1_inst_sup$w01Cb18, missing_values = NA)
ggplot(KLOSA_w1_inst_sup, aes(x=factor(w01Cb18))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Nursing attendance who help most for everyday life achievement now (relation with respondent)") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `50 into 1`
* `56 into 0`
* `other answers into 999 as we don't want to have information about HH members (close relatives) here`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
KLOSA_ds_w1 <- tibble(id=KLOSA_w1_inst_sup$id)
KLOSA_ds_w1$inst_sup <- car::recode(as.vector(KLOSA_w1_inst_sup$w01Cb18), "1:49='999'; 56='0'; 50='1'; 55='1'; NA='999'")
KLOSA_ds_w1$inst_sup <- labelled(KLOSA_ds_w1$inst_sup, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <-  KLOSA_ds_w1$inst_sup
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w1$inst_sup, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w1, aes(x=factor(inst_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Instrumental support (practical help) from people outside the household (relatives/friends/neighbours)") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(KLOSA_ds_w1$inst_sup)
BeforeH <- table(KLOSA_w1_inst_sup$w01Cb18, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[3]] <- sum(sum(BeforeH[c(1:(length(BeforeH)-4))]),BeforeH[length(BeforeH)])
BeforeH1[[1]] <- BeforeH[['56']]
BeforeH1[[2]] <- sum(BeforeH[c('50','55')])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("56->0","50,55->1","other&NA->999")
kable(C)
```


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w02C218_01`
* Label: `The relationship with the nursing attendance who helps the most in order`
* Categories: 
    + `1 = R`
    + `2 = Spouse`
    + `3 = Mother`
    + `4 = Father`
    + `5 = Mother-in-law`
    + `6 = Father-in-law`
    + `7 = 1st child`
    + `8 = 2nd child`
    + `9 = 3rd child`
    + `10 = 4th child`
    + `11 = 5th child`
    + `12 = 6th child`
    + `13 = 7th child`
    + `14 = 8th child`
    + `15 = 9th child`
    + `16 = 10th child`
    + `27 = 1st sibiling`
    + `28 = 2nd sibiling`
    + `29 = 3rd sibiling`
    + `30 = 4th sibiling`
    + `31 = 5st sibiling`
    + `32 = 6th sibiling`
    + `33 = 7th sibiling`
    + `34 = 8th sibiling`
    + `35 = 9th sibiling`
    + `36 = 10th sibiling`
    + `37 = 11th sibiling`
    + `38 = 12th sibiling`
    + `39 = 13th sibiling`
    + `40 = 14th sibiling`
    + `47 = Brother-in-law, sister-in-law`
    + `48 = Son-in-law/daughter-in-law`
    + `49 = Grandchild`
    + `50 = Other relative`
    + `52 = Voluntary worker`
    + `53 = Publicly provided helper`
    + `54 = Personally hired helper`
    + `55 = Helper or other non-relatives`
    + `56 = No one helped`
    

* Description: 
```{r assign2, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w2_inst_sup','KLOSA.w02_main_e_spss',variables=list('w02C218_01'), missings = TRUE)
```

```{r local2, echo=F}
KLOSA_w2_inst_sup <- opal.execute(o,'KLOSA_w2_inst_sup')
vari <- KLOSA_w2_inst_sup$w01Cb18
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w2_inst_sup$w02C218_01, missing_values = NA)
ggplot(KLOSA_w2_inst_sup, aes(x=factor(w02C218_01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The relationship with the nursing attendance who helps the most in order") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `2:55 into 1`
* `56 into 0`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
KLOSA_ds_w2 <- tibble(id=KLOSA_w2_inst_sup$id)
KLOSA_ds_w2$inst_sup <- car::recode(as.vector(KLOSA_w2_inst_sup$w02C218_01), "1:49='999'; 52:54='999'; 56='0'; 50='1'; 55='1'; NA='999'")
KLOSA_ds_w2$inst_sup <- labelled(KLOSA_ds_w2$inst_sup, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}
vari <-  KLOSA_ds_w2$inst_sup
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w2$inst_sup, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w2, aes(x=factor(inst_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Instrumental support (practical help) from people outside the household (relatives/friends/neighbours)") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
AfterH <- table(KLOSA_ds_w2$inst_sup)
BeforeH <- table(KLOSA_w2_inst_sup$w02C218_01, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[3]] <- sum(sum(BeforeH[c(1:(length(BeforeH)-7))]),sum(BeforeH[c((length(BeforeH)-5):(length(BeforeH)-3))]),BeforeH[length(BeforeH)])
BeforeH1[[1]] <- BeforeH[['56']]
BeforeH1[[2]] <- sum(BeforeH[c('50','55')])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("56->0","50,55->1","other&NA->999")
kable(C)
```


### Wave 3

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w03C218_01`
* Label: `The relationship with the nursing attendance who helps the most in order`
* Categories: 
    + `1 = R`
    + `2 = Spouse`
    + `3 = Mother`
    + `4 = Father`
    + `5 = Mother-in-law`
    + `6 = Father-in-law`
    + `7 = 1st child`
    + `8 = 2nd child`
    + `9 = 3rd child`
    + `10 = 4th child`
    + `11 = 5th child`
    + `12 = 6th child`
    + `13 = 7th child`
    + `14 = 8th child`
    + `15 = 9th child`
    + `16 = 10th child`
    + `27 = 1st sibiling`
    + `28 = 2nd sibiling`
    + `29 = 3rd sibiling`
    + `30 = 4th sibiling`
    + `31 = 5st sibiling`
    + `32 = 6th sibiling`
    + `33 = 7th sibiling`
    + `34 = 8th sibiling`
    + `35 = 9th sibiling`
    + `36 = 10th sibiling`
    + `37 = 11th sibiling`
    + `38 = 12th sibiling`
    + `39 = 13th sibiling`
    + `40 = 14th sibiling`
    + `47 = Brother-in-law, sister-in-law`
    + `48 = Son-in-law/daughter-in-law`
    + `49 = Grandchild`
    + `50 = Other relative`
    + `52 = Voluntary worker`
    + `53 = Publicly provided helper`
    + `54 = Personally hired helper`
    + `55 = Helper or other non-relatives`
    + `56 = No one helped`
    

* Description: 
```{r assign3, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w3_inst_sup','KLOSA.w03_main_e_spss_albert',variables=list('w03C218_01'), missings = TRUE)
KLOSA_w3_inst_sup <- opal.execute(o,'KLOSA_w3_inst_sup')
# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_w3_inst_sup$id <- substr(KLOSA_w3_inst_sup$id,1,nchar(KLOSA_w3_inst_sup$id)-2)
```

```{r local3, echo=F}
vari <- KLOSA_w3_inst_sup$w01Cb18
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w3_inst_sup$w03C218_01, missing_values = NA)
ggplot(KLOSA_w3_inst_sup, aes(x=factor(w03C218_01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The relationship with the nursing attendance who helps the most in order") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `2:55 into 1`
* `56 into 0`
* `NA into 999`

**R script:**

```{r harmo3, echo=TRUE}
KLOSA_ds_w3 <- tibble(id=KLOSA_w3_inst_sup$id)
KLOSA_ds_w3$inst_sup <- car::recode(as.vector(KLOSA_w3_inst_sup$w03C218_01), "1:49='999'; 52:54='999'; 56='0'; 50='1'; 55='1'; NA='999'")
KLOSA_ds_w3$inst_sup <- labelled(KLOSA_ds_w3$inst_sup, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript3, echo=F}
vari <-  KLOSA_ds_w3$inst_sup
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w3$inst_sup, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w3, aes(x=factor(inst_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue")+ xlab("Instrumental support (practical help) from people outside the household (relatives/friends/neighbours)") + ylab("Frequency")
```

##### Validation
```{r crosstabulation3, echo=F}
AfterH <- table(KLOSA_ds_w3$inst_sup)
BeforeH <- table(KLOSA_w3_inst_sup$w03C218_01, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[3]] <- sum(sum(BeforeH[c(1:(length(BeforeH)-7))]),sum(BeforeH[c((length(BeforeH)-5):(length(BeforeH)-3))]),BeforeH[length(BeforeH)])
BeforeH1[[1]] <- BeforeH[['56']]
BeforeH1[[2]] <- sum(BeforeH[c('50','55')])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("56->0","50,55->1","other&NA->999")
kable(C)
```


### Wave 4

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w04C218_01`
* Label: `The relationship with the nursing attendance who helps the most in order`
* Categories: 
    + `1 = R`
    + `2 = Spouse`
    + `3 = Mother`
    + `4 = Father`
    + `5 = Mother-in-law`
    + `6 = Father-in-law`
    + `7 = 1st child`
    + `8 = 2nd child`
    + `9 = 3rd child`
    + `10 = 4th child`
    + `11 = 5th child`
    + `12 = 6th child`
    + `13 = 7th child`
    + `14 = 8th child`
    + `15 = 9th child`
    + `16 = 10th child`
    + `27 = 1st sibiling`
    + `28 = 2nd sibiling`
    + `29 = 3rd sibiling`
    + `30 = 4th sibiling`
    + `31 = 5st sibiling`
    + `32 = 6th sibiling`
    + `33 = 7th sibiling`
    + `34 = 8th sibiling`
    + `35 = 9th sibiling`
    + `36 = 10th sibiling`
    + `37 = 11th sibiling`
    + `38 = 12th sibiling`
    + `39 = 13th sibiling`
    + `40 = 14th sibiling`
    + `47 = Brother-in-law, sister-in-law`
    + `48 = Son-in-law/daughter-in-law`
    + `49 = Grandchild`
    + `50 = Other relative`
    + `52 = Voluntary worker`
    + `53 = Publicly provided helper`
    + `54 = Personally hired helper`
    + `55 = Helper or other non-relatives`
    + `56 = No one helped`
    

* Description: 
```{r assign4, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w4_inst_sup','KLOSA.w04_main_e_spss',variables=list('w04C218_01'), missings = TRUE)
```

```{r local4, echo=F}
KLOSA_w4_inst_sup <- opal.execute(o,'KLOSA_w4_inst_sup')
vari <- KLOSA_w4_inst_sup$w01Cb18
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = KLOSA_w4_inst_sup$w04C218_01, missing_values = NA)
ggplot(KLOSA_w4_inst_sup, aes(x=factor(w04C218_01))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The relationship with the nursing attendance who helps the most in order") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `2:55 into 1`
* `56 into 0`
* `NA into 999`

**R script:**

```{r harmo4, echo=TRUE}
KLOSA_ds_w4 <- tibble(id=KLOSA_w4_inst_sup$id)
KLOSA_ds_w4$inst_sup <- car::recode(as.vector(KLOSA_w4_inst_sup$w04C218_01), "1:49='999'; 52:54='999'; 56='0'; 50='1'; 55='1'; NA='999'")
KLOSA_ds_w4$inst_sup <- labelled(KLOSA_ds_w4$inst_sup, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4, echo=F}
vari <-  KLOSA_ds_w4$inst_sup
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = KLOSA_ds_w4$inst_sup, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w4, aes(x=factor(inst_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Instrumental support (practical help) from people outside the household (relatives/friends/neighbours)") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=F}
AfterH <- table(KLOSA_ds_w4$inst_sup)
BeforeH <- table(KLOSA_w4_inst_sup$w04C218_01, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[3]] <- sum(sum(BeforeH[c(1:(length(BeforeH)-7))]),sum(BeforeH[c((length(BeforeH)-5):(length(BeforeH)-3))]),BeforeH[length(BeforeH)])
BeforeH1[[1]] <- BeforeH[['56']]
BeforeH1[[2]] <- sum(BeforeH[c('50','55')])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("56->0","50,55->1","other&NA->999")
kable(C)
```


```{r save, echo=FALSE}
inst_sup <- KLOSA_ds_w1
save(inst_sup, file = "../RData/w1/inst_sup.RData")
rm(inst_sup)

inst_sup <- KLOSA_ds_w2
save(inst_sup, file = "../RData/w2/inst_sup.RData")
rm(inst_sup)

inst_sup <- KLOSA_ds_w3
save(inst_sup, file = "../RData/w3/inst_sup.RData")
rm(inst_sup)


inst_sup <- KLOSA_ds_w4
save(inst_sup, file = "../RData/w4/inst_sup.RData")
rm(inst_sup)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```


