---
title: "Cardiac disorders"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `cd_all`
* Variable label: `History of Cardiac disorders`
* Variable description: `The participant has been diagnosed by one or more of the following conditions: angina, myocardial infarction, heart attack, coronary heart disease, congestive heart failure, heart murmur, valve disease`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | No, the participant has not been diagnosed of any of these conditions
1        | Yes, the participant has been diagnosed by any of these conditions

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "History of Cardiac disorders"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process



## aksst


### Wave 1


#### Study-specific variable description

| **Name** | `h_001_1` |
|-|-|
| **Label** | `H-001-1:HAVE A HEART DISEASE`|
| **Table name**  | `jstar_2007_5cities`|
| **Categories** | `0 = Have not been diagnosed or advised to seek care`<br/>`1 = Have been diagnosed or advised to seek care` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign aksst_w1, echo=F}

opal.assign.table.tibble(o, 'JSTAR_aksst_w1','JSTAR_datasets_restricted.jstar_2007_5cities',variables=list('h_001_1'), missings = T)
JSTAR_aksst_w1 <- opal.execute(o,'JSTAR_aksst_w1')

```

```{r local aksst_w1, echo=F}

vbl <- JSTAR_aksst_w1$h_001_1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_aksst_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w1, aes(x=factor(h_001_1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cd_all` from the study-specific variable it has to be recoded as follows:

* `keep up 0 into 0`
* `keep up 1 into 1`
* `NA into 999`

**R script:**

```{r harmo aksst_w1}

# Categorical variable harmonization
JSTAR_ds_aksst_w1 <- tibble(id=JSTAR_aksst_w1$id)
JSTAR_ds_aksst_w1$cd_all <- car::recode(JSTAR_aksst_w1$h_001_1,"NA=999")

```


#### Statistics of the new harmonized variable

```{r descript aksst_w1, echo=F}

vbl <- JSTAR_ds_aksst_w1$cd_all
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w1, aes(x=factor(cd_all))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation aksst_w1, echo=F}

AfterH <- table(JSTAR_ds_aksst_w1$cd_all)
BeforeH <- table(JSTAR_aksst_w1$h_001_1, useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999")
kable(C)

```



### Wave 2

#### Study-specific variable description


| **Name** | `h_001_1` |
|-|-|
| **Label** | `H-001-1:HAVE A HEART DISEASE`|
| **Table name**  | `jstar_2009_5cities`|
| **Categories** | `1 = Newly diagnosed with or indicated`<br/>`2 = Fully recovered once but recurred in the past 2 years`<br/>`3 = Still be treated`<br/>`4 = Fully recovered/Never diagnosed with indicated` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign aksst_w2, echo=F}

opal.assign.table.tibble(o, 'JSTAR_aksst_w2','JSTAR_datasets_restricted.jstar_2009_5cities',variables=list('h_001_1'), missings = T)
JSTAR_aksst_w2 <- opal.execute(o,'JSTAR_aksst_w2')

```

```{r local aksst_w2, echo=F}

vbl <- JSTAR_aksst_w2$h_001_1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_aksst_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w2, aes(x=factor(h_001_1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cd_all` from the study-specific variable it has to be recoded as follows:

* `h_001_1 == 4 into 0`
* `h_001_1 == 1 or 2 or 3 into 1`
* `otherwise into 999`

**R script:**

```{r harmo aksst_w2}

# Categorical variable harmonization
JSTAR_ds_aksst_w2 <- tibble(id=JSTAR_aksst_w2$id)
JSTAR_ds_aksst_w2$cd_all <- car::recode(JSTAR_aksst_w2$h_001_1,"4=0;2=1;3=1;NA=999")

```


#### Statistics of the new harmonized variable

```{r descript aksst_w2, echo=F}

vbl <- JSTAR_ds_aksst_w2$cd_all
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w2, aes(x=factor(cd_all))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation aksst_w2, echo=F, results='asis'}

AfterH <- table(JSTAR_ds_aksst_w2$cd_all)
X <- table(JSTAR_aksst_w2$h_001_1, useNA = "ifany")
BeforeH <- c(X[4],sum(X[1:3]),X[5])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4->0","1,2,3->1","NA->999")
kable(C)

```



### Wave 3


#### Study-specific variable description

| **Name** | `h_001_1` |
|-|-|
| **Label** | `11H-001-1:HAVE A HEART DISEASE`|
| **Table name**  | `jstar_2011_5cities`|
| **Categories** |`1 = Newly diagnosed with or indicated`<br/>`2 = Fully recovered once but recurred in the past 2 years`<br/>`3 = Still be treated`<br/>`4 = Fully recovered/Never diagnosed with indicated` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign aksst_w3, echo=F}

opal.assign.table.tibble(o, 'JSTAR_aksst_w3','JSTAR_datasets_restricted.jstar_2011_5cities',variables=list('h_001_1'), missings = T)
JSTAR_aksst_w3 <- opal.execute(o,'JSTAR_aksst_w3')

```

```{r local aksst_w3, echo=F}

vbl <- JSTAR_aksst_w3$h_001_1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_aksst_w3)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w3, aes(x=factor(h_001_1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cd_all` from the study-specific variable it has to be recoded as follows:

* `h_001_1 == 4 into 0`
* `h_001_1 == 1 or 2 or 3 into 1`
* `otherwise into 999`

**R script:**

```{r harmo aksst_w3}

# Categorical variable harmonization
JSTAR_ds_aksst_w3 <- tibble(id=JSTAR_aksst_w3$id)
JSTAR_ds_aksst_w3$cd_all <- car::recode(JSTAR_aksst_w3$h_001_1,"4=0;2=1;3=1;NA=999")

```


#### Statistics of the new harmonized variable

```{r descript aksst_w3, echo=F}

vbl <- JSTAR_ds_aksst_w3$cd_all
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w3, aes(x=factor(cd_all))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation aksst_w3, echo=F, results='asis'}

AfterH <- table(JSTAR_ds_aksst_w3$cd_all, useNA = "ifany")
X <- table(JSTAR_aksst_w3$h_001_1, useNA = "ifany")
BeforeH <- c(X[4],sum(X[1:3]),X[5])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4->0","1,2,3->1","NA->999")
kable(C)

```



## tn

### Wave 1


#### Study-specific variable description

| **Name** | `h_001_1` |
|-|-|
| **Label** | `H-001-1:HAVE A HEART DISEASE`|
| **Table name**  | `jstar_2009_2cities`|
| **Categories** | `0 = Have not been diagnosed or advised to seek care`<br/>`1 = Have been diagnosed or advised to seek care` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign tn_w1, echo=F}

opal.assign.table.tibble(o, 'JSTAR_tn_w1','JSTAR_datasets_restricted.jstar_2009_2cities',variables=list('h_001_1'), missings = T)
JSTAR_tn_w1 <- opal.execute(o,'JSTAR_tn_w1')

```

```{r local tn_w1, echo=F}

vbl <- JSTAR_tn_w1$h_001_1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_tn_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w1, aes(x=factor(h_001_1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cd_all` from the study-specific variable it has to be recoded as follows:

* `keep up 0 into 0`
* `keep up 1 into 1`
* `NA into 999`

**R script:**

```{r harmo tn_w1}

# Categorical variable harmonization
JSTAR_ds_tn_w1 <- tibble(id=JSTAR_tn_w1$id)
JSTAR_ds_tn_w1$cd_all <- car::recode(JSTAR_tn_w1$h_001_1,"NA=999")

```


#### Statistics of the new harmonized variable

```{r descript tn_w1, echo=F}

vbl <- JSTAR_ds_tn_w1$cd_all
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_tn_w1, aes(x=factor(cd_all))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation tn_w1, echo=F}

AfterH <- table(JSTAR_ds_tn_w1$cd_all)
BeforeH <- table(JSTAR_tn_w1$h_001_1, useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999")
kable(C)

```



### Wave 2

#### Study-specific variable description



| **Name** | `h_001_1` |
|-|-|
| **Label** | `11H-001-1:HAVE A HEART DISEASE`|
| **Table name**  | `jstar_2011_2cities`|
| **Categories** |`1 = Newly diagnosed with or indicated`<br/>`2 = Fully recovered once but recurred in the past 2 years`<br/>`3 = Still be treated`<br/>`4 = Fully recovered/Never diagnosed with indicated`|
| **Missings** | `NA` |
| **Description** |  |



```{r assign tn_w2, echo=F}

opal.assign.table.tibble(o, 'JSTAR_tn_w2','JSTAR_datasets_restricted.jstar_2011_2cities',variables=list('h_001_1'), missings = T)
JSTAR_tn_w2 <- opal.execute(o,'JSTAR_tn_w2')

```

```{r local tn_w2, echo=F}

vbl <- JSTAR_tn_w2$h_001_1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_tn_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w2, aes(x=factor(h_001_1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cd_all` from the study-specific variable it has to be recoded as follows:

* `h_001_1 == 4 into 0`
* `h_001_1 == 1 or 2 or 3 into 1`
* `otherwise into 999`

**R script:**

```{r harmo tn_w2}

# Categorical variable harmonization
JSTAR_ds_tn_w2 <- tibble(id=JSTAR_tn_w2$id)
JSTAR_ds_tn_w2$cd_all <- car::recode(JSTAR_tn_w2$h_001_1,"4=0;2=1;3=1;NA=999")

```


#### Statistics of the new harmonized variable

```{r descript tn_w2, echo=F}

vbl <- JSTAR_ds_tn_w2$cd_all
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_tn_w2, aes(x=factor(cd_all))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation tn_w2, echo=F, results='asis'}

AfterH <- table(JSTAR_ds_tn_w2$cd_all, useNA = "ifany")
X <- table(JSTAR_tn_w2$h_001_1, useNA = "ifany")
BeforeH <- c(X[3],sum(X[1:2]),X[4])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4->0","1,2,3->1","NA->999")
kable(C)

```



## cth

### Wave 1


#### Study-specific variable description

| **Name** | `h_001_1` |
|-|-|
| **Label** | `H-001-1:HAVE A HEART DISEASE`|
| **Table name**  | `jstar_2011_3cities`|
| **Categories** | `0 = Have not been diagnosed or advised to seek care`<br/>`1 = Have been diagnosed or advised to seek care` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign cth_w1, echo=F}

opal.assign.table.tibble(o, 'JSTAR_cth_w1','JSTAR_datasets_restricted.jstar_2011_3cities',variables=list('h_001_1'), missings = T)
JSTAR_cth_w1 <- opal.execute(o,'JSTAR_cth_w1')

```

```{r local cth_w1, echo=F}

vbl <- JSTAR_cth_w1$h_001_1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_cth_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_cth_w1, aes(x=factor(h_001_1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cd_all` from the study-specific variable it has to be recoded as follows:

* `keep up 0 into 0`
* `keep up 1 into 1`
* `NA into 999`

**R script:**

```{r harmo cth_w1}

# Categorical variable harmonization
JSTAR_ds_cth_w1 <- tibble(id=JSTAR_cth_w1$id)
JSTAR_ds_cth_w1$cd_all <- car::recode(JSTAR_cth_w1$h_001_1,"NA=999")

```


#### Statistics of the new harmonized variable

```{r descript cth_w1, echo=F}

vbl <- JSTAR_ds_cth_w1$cd_all
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_cth_w1, aes(x=factor(cd_all))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation cth_w1, echo=F}

AfterH <- table(JSTAR_ds_cth_w1$cd_all)
BeforeH <- table(JSTAR_cth_w1$h_001_1, useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999")
kable(C)

```








## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.

**R script:**

```{r summ}

l.hds <- list(aksst_w1 = JSTAR_ds_aksst_w1, aksst_w2 = JSTAR_ds_aksst_w2, aksst_w3 = JSTAR_ds_aksst_w3, tn_w1 = JSTAR_ds_tn_w1, tn_w2 = JSTAR_ds_tn_w2, cth_w1 = JSTAR_ds_cth_w1)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("JSTAR_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", 
             length(l.hds[[1]][[2]]), length(l.hds[[2]][[2]]) , length(l.hds[[3]][[2]]), length(l.hds[[4]][[2]]), length(l.hds[[5]][[2]]), length(l.hds[[6]][[2]]))
names(t.hds)<-c("val", "label", "AKSST_W1", "AKSST_W2", "AKSST_W3", "TN_W1", "TN_W2", "CTH_W1")
kable(t.hds)

```



# Quality estimation

The harmonized variable contains information about Heart disease (angina, heart failure, cardiac infarction, valve disease, etc.).


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(l.hds)){
  cd_all <- l.hds[[index]]
  save(cd_all, file = paste0(datafolder,names(l.hds)[index],"/cd_all.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





