---
title: "Cancer"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/cancerDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/cancerDS.R')
```



# Data process



## aksst


### Wave 1


#### Study-specific variable description

| **Name** | `h_001_20` |`h_001_20_1`|
|-|-|-|
| **Label** | `H-001-20:HAVE A DISEASE CANCER`|`H-001-20-1:DISEASE CANCER AGE`|
| **Table name**  | `jstar_2007_5cities`| `jstar_2007_5cities`|
| **Categories** | `0 = Have not been diagnosed or advised to seek care`<br/>`1 = Have been diagnosed or advised to seek care` |`continuous`|
| **Missings** | `NA` | `NA` |
| **Description** |  |  |

```{r assign aksst_w1, echo=F}

opal.assign.table.tibble(o, 'JSTAR_aksst_w1','JSTAR_datasets_restricted.jstar_2007_5cities',variables=list('h_001_20','h_001_20_1'), missings = T)
JSTAR_aksst_w1 <- opal.execute(o,'JSTAR_aksst_w1')

```

```{r local aksst_w1, echo=F}

vbl <- JSTAR_aksst_w1$h_001_20
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_aksst_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w1, aes(x=factor(h_001_20))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w1$h_001_20_1
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(JSTAR_aksst_w1)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_aksst_w1, aes(h_001_20_1)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cancer` from the study-specific variable it has to be recoded as follows:

* `keep up 0 into 0`
* `keep up 1 into 1`
* `NA into 999`

To compute `cancer_age` from the study-specific variable it has to be recoded as follows:

* `if cancer == 1, cancer_age = h_001_20_1`
* `if cancer == 0, cancer_age = 996`
* `cancer == missing into 999`

**R script:**

```{r harmo aksst_w1}

# Categorical variable harmonization
JSTAR_ds_aksst_w1 <- tibble(id=JSTAR_aksst_w1$id)
JSTAR_ds_aksst_w1$cancer <- car::recode(JSTAR_aksst_w1$h_001_20,"NA=999")

# Continuous variable harmonization
JSTAR_ds_aksst_w1$cancer_age <- rep(999,length(JSTAR_ds_aksst_w1$id))
JSTAR_ds_aksst_w1$cancer_age[which(JSTAR_ds_aksst_w1$cancer==1)] <- JSTAR_aksst_w1$h_001_20_1[which(JSTAR_ds_aksst_w1$cancer==1)]
JSTAR_ds_aksst_w1$cancer_age[which(JSTAR_ds_aksst_w1$cancer==0)] <- 996

```


#### Statistics of the new harmonized variable

```{r descript aksst_w1, echo=F}

vbl <- JSTAR_ds_aksst_w1$cancer
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w1, aes(x=factor(cancer))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- JSTAR_ds_aksst_w1$cancer_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_ds_aksst_w1 %>% filter(!vbl %in% miss_values_vector), aes(cancer_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation aksst_w1, echo=F}

AfterH <- table(JSTAR_ds_aksst_w1$cancer)
BeforeH <- table(JSTAR_aksst_w1$h_001_20, useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999")
kable(C)

```



### Wave 2

#### Study-specific variable description


| **Name** | `h_001_20` |`h_001_20_1_b`|`ybirth`|
|-|-|-|-|
| **Label** | `H-001-20:HAVE A CANCER OR OTHER MALIGNANT TUMOR`|`H-001-20-1:CANCER, YEAR`|`year of birth`|
| **Table name**  | `jstar_2009_5cities`| `jstar_2009_5cities`|`ybirth`|
| **Categories** | `1 = Newly diagnosed with or indicated`<br/>`2 = Fully recovered once but recurred in the past 2 years`<br/>`3 = Still be treated`<br/>`4 = Fully recovered/Never diagnosed with indicated` |`continuous`|`continuous`|
| **Missings** | `NA` | `NA` | `999 = Missing` |
| **Description** |  |  |  |

```{r assign aksst_w2, echo=F}

opal.assign.table.tibble(o, 'JSTAR_aksst_w2','JSTAR_datasets_restricted.jstar_2009_5cities',variables=list('h_001_20','h_001_20_1_b'), missings = T)
JSTAR_aksst_w2 <- opal.execute(o,'JSTAR_aksst_w2')
load(paste0(datafolder,"aksst_w2/ybirth.RData"))
JSTAR_aksst_w2 <- left_join(JSTAR_aksst_w2,ybirth,by="id")

```

```{r local aksst_w2, echo=F}

vbl <- JSTAR_aksst_w2$h_001_20
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_aksst_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w2, aes(x=factor(h_001_20))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w2$h_001_20_1_b
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(JSTAR_aksst_w2)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_aksst_w2, aes(h_001_20_1_b)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+scale_y_continuous(breaks=c(0,5,10,15))

vbl <- JSTAR_aksst_w2$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(JSTAR_aksst_w2)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_aksst_w2 %>% filter(!vbl %in% miss_values_vector), aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cancer` from the study-specific variable it has to be recoded as follows:

* `h_001_20 == 4 into 0`
* `h_001_20 == 1 or 2 or 3 into 1`
* `otherwise into 999`

To compute `cancer_age` from the study-specific variable it has to be recoded as follows:

* `if cancer == 1 in w2, cancer_age = h_001_20_1_b-ybirth`
* `if cancer == 0, cancer_age = 996`
* `otherwise into 999`

**R script:**

```{r harmo aksst_w2}

# Correction: The individual '2516' has already declared its cancer in the first wave, answers again with year of diagnosis previous to wave 1 (which agrees with the age answered before). We assume it corresponds to the same cancer, so:
JSTAR_aksst_w2$h_001_20[which(JSTAR_aksst_w2$id=="2516")] <- 4
# Correction: The individual '2863' has already declared its cancer in the first wave, answers now 'Fully recovered once but recurred in the past 2 years' with year of diagnosis previous to wave 1, so we change diagnostic year for the middle of the past 2 years to the year of interview (2009):
JSTAR_aksst_w2$h_001_20_1_b[which(JSTAR_aksst_w2$id=="2863")] <- 2008
#Correction: The individuals '2100' and '2768' answer for the first time newly diagnosed cancer, but give years of diagnosis previous to first wave. We codify the years as missing.
JSTAR_aksst_w2$h_001_20_1_b[which(JSTAR_aksst_w2$id %in% c("2100","2768"))] <- rep(NA,2)

# Categorical variable harmonization
JSTAR_ds_aksst_w2 <- tibble(id=JSTAR_aksst_w2$id)
JSTAR_ds_aksst_w2$cancer <- car::recode(JSTAR_aksst_w2$h_001_20,"4=0;2=1;3=1;NA=999")

# Continuous variable harmonization
JSTAR_ds_aksst_w2$cancer_age <- rep(999,length(JSTAR_aksst_w2$id))
JSTAR_ds_aksst_w2$cancer_age[which(JSTAR_ds_aksst_w2$cancer == 0)] <- 996
JSTAR_ds_aksst_w2$cancer_age[which(JSTAR_ds_aksst_w2$cancer == 1 & JSTAR_aksst_w2$ybirth != 999)] <- JSTAR_aksst_w2$h_001_20_1_b[which(JSTAR_ds_aksst_w2$cancer == 1 & JSTAR_aksst_w2$ybirth != 999)]-JSTAR_aksst_w2$ybirth[which(JSTAR_ds_aksst_w2$cancer == 1 & JSTAR_aksst_w2$ybirth != 999)]
JSTAR_ds_aksst_w2$cancer_age <- car::recode(JSTAR_ds_aksst_w2$cancer_age, "NA=999")

```


#### Statistics of the new harmonized variable

```{r descript aksst_w2, echo=F}

vbl <- JSTAR_ds_aksst_w2$cancer
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w2, aes(x=factor(cancer))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- JSTAR_ds_aksst_w2$cancer_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_ds_aksst_w2 %>% filter(!vbl %in% miss_values_vector), aes(cancer_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation aksst_w2, echo=F, results='asis'}

AfterH <- table(JSTAR_ds_aksst_w2$cancer)
X <- table(JSTAR_aksst_w2$h_001_20, useNA = "ifany")
BeforeH <- c(X[4],sum(X[1:3]),X[5])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4->0","1,2,3->1","NA->999")
kable(C)

```



### Wave 3


#### Study-specific variable description

| **Name** | `h_001_20` |`yintw (aksst_w2)`|`yintw (aksst_w3)`|`ybirth`|
|-|-|-|-|-|
| **Label** | `11H-001-20:HAVE A CANCER OR OTHER MALIGNANT TUMOR`|`year of interview`|`year of interview`|`year of birth`|
| **Table name**  | `jstar_2011_5cities`| `yintw`| `yintw`|`ybirth`|
| **Categories** |`1 = Newly diagnosed with or indicated`<br/>`2 = Fully recovered once but recurred in the past 2 years`<br/>`3 = Still be treated`<br/>`4 = Fully recovered/Never diagnosed with indicated` |`continuous`|`continuous`|`continuous`|
| **Missings** | `NA` |  |  |  `999 = Missing` |
| **Description** |  |  |  |  |

```{r assign aksst_w3, echo=F}

opal.assign.table.tibble(o, 'JSTAR_aksst_w3','JSTAR_datasets_restricted.jstar_2011_5cities',variables=list('h_001_20'), missings = T)
JSTAR_aksst_w3 <- opal.execute(o,'JSTAR_aksst_w3')
load(paste0(datafolder,"aksst_w3/ybirth.RData"))
JSTAR_aksst_w3 <- left_join(JSTAR_aksst_w3,ybirth,by="id")
rm(ybirth)
load(paste0(datafolder,"aksst_w3/yintw.RData"))
JSTAR_aksst_w3 <- left_join(JSTAR_aksst_w3,yintw,by="id")
names(JSTAR_aksst_w3)[4] <- "yintw_aksst_w3"
rm(yintw)
load(paste0(datafolder,"aksst_w2/yintw.RData"))
JSTAR_aksst_w3 <- left_join(JSTAR_aksst_w3,yintw,by="id")
names(JSTAR_aksst_w3)[5] <- "yintw_aksst_w2"
rm(yintw)

```

```{r local aksst_w3, echo=F}

vbl <- JSTAR_aksst_w3$h_001_20
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_aksst_w3)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w3, aes(x=factor(h_001_20))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w3$yintw_aksst_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_aksst_w3)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w3, aes(x=factor(yintw_aksst_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w3$yintw_aksst_w3
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_aksst_w3)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w3, aes(x=factor(yintw_aksst_w3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w3$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(JSTAR_aksst_w3)[3])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_aksst_w3 %>% filter(!vbl %in% miss_values_vector), aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cancer` from the study-specific variable it has to be recoded as follows:

* `h_001_20 == 4 into 0`
* `h_001_20 == 1 or 2 or 3 into 1`
* `otherwise into 999`

To compute `cancer_age` from the study-specific variable it has to be recoded as follows:

* `if cancer == 1 in w3, cancer_age = (year of interview w3-year of interview w2)/2 + (year of interview w2 - ybirth)`
* `if cancer == 0, cancer_age = 996`
* `cancer == missing into 999`

**R script:**

```{r harmo aksst_w3}

# Categorical variable harmonization
JSTAR_ds_aksst_w3 <- tibble(id=JSTAR_aksst_w3$id)
JSTAR_ds_aksst_w3$cancer <- car::recode(JSTAR_aksst_w3$h_001_20,"4=0;2=1;3=1;NA=999")

# Continuous variable harmonization
JSTAR_ds_aksst_w3$cancer_age <- rep(999,length(JSTAR_aksst_w3$id))
JSTAR_ds_aksst_w3$cancer_age[which(JSTAR_ds_aksst_w3$cancer == 0)] <- 996
JSTAR_ds_aksst_w3$cancer_age[which(JSTAR_ds_aksst_w3$cancer == 1 & JSTAR_aksst_w3$ybirth != 999)] <- floor((JSTAR_aksst_w3$yintw_aksst_w3[which(JSTAR_ds_aksst_w3$cancer == 1 & JSTAR_aksst_w3$ybirth != 999)] + JSTAR_aksst_w3$yintw_aksst_w2[which(JSTAR_ds_aksst_w3$cancer == 1 & JSTAR_aksst_w3$ybirth != 999)])/2 - JSTAR_aksst_w3$ybirth[which(JSTAR_ds_aksst_w3$cancer == 1 & JSTAR_aksst_w3$ybirth != 999)])
JSTAR_ds_aksst_w3$cancer_age <- car::recode(JSTAR_ds_aksst_w3$cancer_age, "NA=999")

```


#### Statistics of the new harmonized variable

```{r descript aksst_w3, echo=F}

vbl <- JSTAR_ds_aksst_w3$cancer
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w3, aes(x=factor(cancer))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- JSTAR_ds_aksst_w3$cancer_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_ds_aksst_w3 %>% filter(!vbl %in% miss_values_vector), aes(cancer_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation aksst_w3, echo=F, results='asis'}

AfterH <- table(JSTAR_ds_aksst_w3$cancer, useNA = "ifany")
X <- table(JSTAR_aksst_w3$h_001_20, useNA = "ifany")
BeforeH <- c(X[4],sum(X[1:3]),X[5])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4->0","1,2,3->1","NA->999")
kable(C)

```



## tn

### Wave 1


#### Study-specific variable description

| **Name** | `h_001_20` |`h_001_20_1`|
|-|-|-|
| **Label** | `H-001-20:HAVE A CANCER OR OTHER MALIGNANT TUMOR`|`H-001-20-1:CANCER, AGE`|
| **Table name**  | `jstar_2009_2cities`| `jstar_2009_2cities`|
| **Categories** | `0 = Have not been diagnosed or advised to seek care`<br/>`1 = Have been diagnosed or advised to seek care` |`continuous`|
| **Missings** | `NA` | `NA` |
| **Description** |  |  |

```{r assign tn_w1, echo=F}

opal.assign.table.tibble(o, 'JSTAR_tn_w1','JSTAR_datasets_restricted.jstar_2009_2cities',variables=list('h_001_20','h_001_20_1'), missings = T)
JSTAR_tn_w1 <- opal.execute(o,'JSTAR_tn_w1')

```

```{r local tn_w1, echo=F}

vbl <- JSTAR_tn_w1$h_001_20
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_tn_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w1, aes(x=factor(h_001_20))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w1$h_001_20_1
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(JSTAR_tn_w1)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_tn_w1, aes(h_001_20_1)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cancer` from the study-specific variable it has to be recoded as follows:

* `keep up 0 into 0`
* `keep up 1 into 1`
* `NA into 999`

To compute `cancer_age` from the study-specific variable it has to be recoded as follows:

* `if cancer == 1, cancer_age = h_001_20_1`
* `if cancer == 0, cancer_age = 996`
* `cancer == missing into 999`

**R script:**

```{r harmo tn_w1}

# Categorical variable harmonization
JSTAR_ds_tn_w1 <- tibble(id=JSTAR_tn_w1$id)
JSTAR_ds_tn_w1$cancer <- car::recode(JSTAR_tn_w1$h_001_20,"NA=999")

# Continuous variable harmonization
JSTAR_ds_tn_w1$cancer_age <- rep(999,length(JSTAR_ds_tn_w1$id))
JSTAR_ds_tn_w1$cancer_age[which(JSTAR_ds_tn_w1$cancer==1)] <- JSTAR_tn_w1$h_001_20_1[which(JSTAR_ds_tn_w1$cancer==1)]
JSTAR_ds_tn_w1$cancer_age[which(JSTAR_ds_tn_w1$cancer==0)] <- 996

```


#### Statistics of the new harmonized variable

```{r descript tn_w1, echo=F}

vbl <- JSTAR_ds_tn_w1$cancer
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_tn_w1, aes(x=factor(cancer))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- JSTAR_ds_tn_w1$cancer_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_ds_tn_w1 %>% filter(!vbl %in% miss_values_vector), aes(cancer_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation tn_w1, echo=F}

AfterH <- table(JSTAR_ds_tn_w1$cancer)
BeforeH <- table(JSTAR_tn_w1$h_001_20, useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999")
kable(C)

```



### Wave 2

#### Study-specific variable description



| **Name** | `h_001_20` |`yintw (tn_w2)`|`yintw (tn_w1)`|`ybirth`|
|-|-|-|-|-|
| **Label** | `11H-001-20:HAVE A CANCER OR OTHER MALIGNANT TUMOR`|`year of interview`|`year of interview`|`year of birth`|
| **Table name**  | `jstar_2011_2cities`| `yintw`| `yintw`|`ybirth`|
| **Categories** |`1 = Newly diagnosed with or indicated`<br/>`2 = Fully recovered once but recurred in the past 2 years`<br/>`3 = Still be treated`<br/>`4 = Fully recovered/Never diagnosed with indicated`|`continuous`|`continuous`|`continuous`|
| **Missings** | `NA` |  |  |  `999 = Missing` |
| **Description** |  |  |  |  |



```{r assign tn_w2, echo=F}

opal.assign.table.tibble(o, 'JSTAR_tn_w2','JSTAR_datasets_restricted.jstar_2011_2cities',variables=list('h_001_20'), missings = T)
JSTAR_tn_w2 <- opal.execute(o,'JSTAR_tn_w2')
load(paste0(datafolder,"tn_w2/ybirth.RData"))
JSTAR_tn_w2 <- left_join(JSTAR_tn_w2,ybirth,by="id")
rm(ybirth)
load(paste0(datafolder,"tn_w2/yintw.RData"))
JSTAR_tn_w2 <- left_join(JSTAR_tn_w2,yintw,by="id")
names(JSTAR_tn_w2)[4] <- "yintw_tn_w2"
rm(yintw)
load(paste0(datafolder,"tn_w1/yintw.RData"))
JSTAR_tn_w2 <- left_join(JSTAR_tn_w2,yintw,by="id")
names(JSTAR_tn_w2)[5] <- "yintw_tn_w1"
rm(yintw)

```

```{r local tn_w2, echo=F}

vbl <- JSTAR_tn_w2$h_001_20
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_tn_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w2, aes(x=factor(h_001_20))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w2$yintw_tn_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_tn_w2)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w2, aes(x=factor(yintw_tn_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w2$yintw_tn_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_tn_w2)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w2, aes(x=factor(yintw_tn_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w2$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(JSTAR_tn_w2)[3])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_tn_w2 %>% filter(!vbl %in% miss_values_vector), aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cancer` from the study-specific variable it has to be recoded as follows:

* `h_001_20 == 4 into 0`
* `h_001_20 == 1 or 2 or 3 into 1`
* `otherwise into 999`

To compute `cancer_age` from the study-specific variable it has to be recoded as follows:

* `if cancer == 1 in w2, cancer_age = (year of interview w2-year of interview w1)/2+(year of interview w1-ybirth)`
* `if cancer == 0, cancer_age = 996`
* `cancer == missing into 999`

**R script:**

```{r harmo tn_w2}

# Categorical variable harmonization
JSTAR_ds_tn_w2 <- tibble(id=JSTAR_tn_w2$id)
JSTAR_ds_tn_w2$cancer <- car::recode(JSTAR_tn_w2$h_001_20,"4=0;2=1;3=1;NA=999")

# Continuous variable harmonization
JSTAR_ds_tn_w2$cancer_age <- rep(999,length(JSTAR_tn_w2$id))
JSTAR_ds_tn_w2$cancer_age[which(JSTAR_ds_tn_w2$cancer == 0)] <- 996
JSTAR_ds_tn_w2$cancer_age[which(JSTAR_ds_tn_w2$cancer == 1 & JSTAR_tn_w2$ybirth != 999)] <- floor((JSTAR_tn_w2$yintw_tn_w2[which(JSTAR_ds_tn_w2$cancer == 1 & JSTAR_tn_w2$ybirth != 999)] + JSTAR_tn_w2$yintw_tn_w1[which(JSTAR_ds_tn_w2$cancer == 1 & JSTAR_tn_w2$ybirth != 999)])/2 - JSTAR_tn_w2$ybirth[which(JSTAR_ds_tn_w2$cancer == 1 & JSTAR_tn_w2$ybirth != 999)])

```


#### Statistics of the new harmonized variable

```{r descript tn_w2, echo=F}

vbl <- JSTAR_ds_tn_w2$cancer
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_tn_w2, aes(x=factor(cancer))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- JSTAR_ds_tn_w2$cancer_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_ds_tn_w2 %>% filter(!vbl %in% miss_values_vector), aes(cancer_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation tn_w2, echo=F, results='asis'}

AfterH <- table(JSTAR_ds_tn_w2$cancer, useNA = "ifany")
X <- table(JSTAR_tn_w2$h_001_20, useNA = "ifany")
BeforeH <- c(X[4],sum(X[1:3]),X[5])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4->0","1,2,3->1","NA->999")
kable(C)

```



## cth

### Wave 1


#### Study-specific variable description

| **Name** | `h_001_20` |`h_001_20_1`|
|-|-|-|
| **Label** | `H-001-20:HAVE A CANCER OR OTHER MALIGNANT TUMOR`|`H-001-20-1:CANCER, AGE`|
| **Table name**  | `jstar_2011_3cities`| `jstar_2011_3cities`|
| **Categories** | `0 = Have not been diagnosed or advised to seek care`<br/>`1 = Have been diagnosed or advised to seek care` |`continuous`|
| **Missings** | `NA` | `NA` |
| **Description** |  |  |

```{r assign cth_w1, echo=F}

opal.assign.table.tibble(o, 'JSTAR_cth_w1','JSTAR_datasets_restricted.jstar_2011_3cities',variables=list('h_001_20','h_001_20_1'), missings = T)
JSTAR_cth_w1 <- opal.execute(o,'JSTAR_cth_w1')

```

```{r local cth_w1, echo=F}

vbl <- JSTAR_cth_w1$h_001_20
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_cth_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_cth_w1, aes(x=factor(h_001_20))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_cth_w1$h_001_20_1
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(JSTAR_cth_w1)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_cth_w1, aes(h_001_20_1)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `cancer` from the study-specific variable it has to be recoded as follows:

* `keep up 0 into 0`
* `keep up 1 into 1`
* `NA into 999`

To compute `cancer_age` from the study-specific variable it has to be recoded as follows:

* `if cancer == 1, cancer_age = h_001_20_1`
* `if cancer == 0, cancer_age = 996`
* `cancer == missing into 999`

**R script:**

```{r harmo cth_w1}

# Categorical variable harmonization
JSTAR_ds_cth_w1 <- tibble(id=JSTAR_cth_w1$id)
JSTAR_ds_cth_w1$cancer <- car::recode(JSTAR_cth_w1$h_001_20,"NA=999")

# Continuous variable harmonization
JSTAR_ds_cth_w1$cancer_age <- rep(999,length(JSTAR_ds_cth_w1$id))
JSTAR_ds_cth_w1$cancer_age[which(JSTAR_ds_cth_w1$cancer==1)] <- JSTAR_cth_w1$h_001_20_1[which(JSTAR_ds_cth_w1$cancer==1)]
JSTAR_ds_cth_w1$cancer_age[which(JSTAR_ds_cth_w1$cancer==0)] <- 996

```


#### Statistics of the new harmonized variable

```{r descript cth_w1, echo=F}

vbl <- JSTAR_ds_cth_w1$cancer
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_cth_w1, aes(x=factor(cancer))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- JSTAR_ds_cth_w1$cancer_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_ds_cth_w1 %>% filter(!vbl %in% miss_values_vector), aes(cancer_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation cth_w1, echo=F}

AfterH <- table(JSTAR_ds_cth_w1$cancer)
BeforeH <- table(JSTAR_cth_w1$h_001_20, useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999")
kable(C)

```








<!--AUXILIAR FUNCTIONS-->



```{r helpfunctions, echo=F}

source("../../helpfunctions.r")

```



```{r populations-waves, echo=F}


# All study waves and populations with abbreviated and descriptive names

jstar.cw <- list(aksst_w1 = c("aksst_w1","AKSST w1"), aksst_w2 = c("aksst_w2","AKSST w2"), aksst_w3 = c("aksst_w3","AKSST w3"), tn_w1 = c("tn_w1","TN w1"), tn_w2 = c("tn_w2","TN w2"), cth_w1 = c("cth_w1","CTH w1"))


```


<!--Labelling and saving-->

```{r, echo=FALSE}


# Consider only waves with some variable harmonised

l.hds <- lapply(jstar.cw, function(wname) if(exists(paste0("JSTAR_ds_",wname[1]))){wname = list(get(paste0("JSTAR_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling categorical variable of tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]],hd_vbl,ds_label)
  # Labelling continuous variable of tibbles
  lmlist <- labelling_c(lmlist[[1]],lmlist[[2]],hd_age_vbl,ds_label_age)
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}

jstarlist <- lmlist # baseline list




```



<!--Descriptives-->

## Descriptive statistics of the harmonised variable `cancer` accross populations and waves

Percentages of categories in each harmonised variable:


```{r summ, echo=F}


# Consider only harmonised waves
l.hds <- lapply(jstar.cw, function(wname) if(hd_vbl %in% names(get0(paste0("JSTAR_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- jstarlist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- jstarlist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl),caption=ds_label))
}





```






## Summary of descriptive statistics of the harmonised variable `cancer_age` accross populations and waves






```{r summ_c, echo=F}


# Consider only harmonised waves
l.hds <- lapply(jstar.cw, function(wname) if(hd_age_vbl %in% names(get0(paste0("JSTAR_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- jstarlist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- jstarlist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries_c(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_age_vbl),caption=ds_label_age))
}



```



# Quality estimation

The variable doesn't include benign skin cancer.







<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





