---
title: "Multimorbidity"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/multimorbidDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/multimorbidDS.R')
```


# Data process

## AKSST


### Wave 1


#### Study-specific variable description

| **Name** |`h_diabetes`|`h_asthma`|`h_cpd`|`h_hypertension`|`h_joint_disorders`|`cvd_all`|
|-|-|-|-|-|-|-|
| **Label** |`History of diabetes mellitus`|`History of  Asthma`|`History of chronic pulmonary disorders`|`History of hypertension`|`History of arthritis, rheumatism or osteoarthritis`|`History of all Cardiovascular diseases`|
| **Table name** |`jstar_aksst_w1_hd`|`jstar_aksst_w1_hd`|`jstar_aksst_w1_hd`|`jstar_aksst_w1_hd`|`jstar_aksst_w1_hd`|`jstar_aksst_w1_hd`|
| **Categories** |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing`|`999 = Missing`|`999 = Missing`|`999 = Missing`|`999 = Missing`|`999 = Missing`|
| **Description** |  |  |  |  |  |

```{r assign aksst_w1, echo=FALSE}

opal.assign.table.tibble(o, 'JSTAR_aksst_w1','JSTAR_HD.jstar_aksst_w1_hd',variables=list('h_diabetes','h_asthma','h_cpd','h_hypertension','h_joint_disorders','cvd_all'), missings = T)
JSTAR_aksst_w1 <- opal.execute(o,'JSTAR_aksst_w1')

```

```{r local aksst_w1, echo=FALSE}

vbl <- JSTAR_aksst_w1$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_diabetes")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(JSTAR_aksst_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w1$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_asthma")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(JSTAR_aksst_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w1$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_cpd")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(JSTAR_aksst_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w1$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_hypertension")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(JSTAR_aksst_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w1$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_joint_disorders")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(JSTAR_aksst_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w1$cvd_all
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "cvd_all")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(JSTAR_aksst_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `multimorbid` from the study-specific variables they have to be recoded as follows:

* `Multimorbid_score = sum(h_diabetes, h_asthma, h_cpd, h_hypertension, h_joint_disorders, cvd_all)`
* `Multimorbid_status = 1 if multimorbid_score > = 2`
* `Multimorbid_status = 0 if multimorbid_score < 2`
* `otherwise into 999`

**R script:**

```{r harmo aksst_w1}

JSTAR_ds_aksst_w1 <- JSTAR_aksst_w1 %>% 
  mutate(dead = purrr::pmap(mutate_at(., vars(-id), `==`, 996) %>% select(., -id), all) %>% unlist()) %>%
  mutate_at(., vars(-id), ~replace(., list = which(. %in% 991:999), values = NA)) %>% 
  mutate(multimorbid_score = rowSums(select(., -1, -dead), na.rm = T)) %>%
  mutate(cardNA = rowSums(!is.na(select(., -1, -dead, -multimorbid_score)))) %>%
  mutate(cardNA = cardNA/cardNA) %>%
  mutate(multimorbid_score = multimorbid_score * cardNA) %>%
  mutate(multimorbid = case_when(multimorbid_score >= 2 ~ 1, multimorbid_score < 2 ~ 0, dead ~ 996, TRUE ~ 999)) %>%
  select(id, multimorbid)

```

#### Statistics of the new harmonized variable

```{r descript aksst_w1, echo=F}

vbl <- JSTAR_ds_aksst_w1$multimorbid
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation aksst_w1, echo=F}
```


### Wave 2


#### Study-specific variable description

| **Name** |`h_diabetes`|`h_asthma`|`h_cpd`|`h_hypertension`|`h_joint_disorders`|`cvd_all`|
|-|-|-|-|-|-|-|
| **Label** |`History of diabetes mellitus`|`History of  Asthma`|`History of chronic pulmonary disorders`|`History of hypertension`|`History of arthritis, rheumatism or osteoarthritis`|`History of all Cardiovascular diseases`|
| **Table name** |`jstar_aksst_w2_hd`|`jstar_aksst_w2_hd`|`jstar_aksst_w2_hd`|`jstar_aksst_w2_hd`|`jstar_aksst_w2_hd`|`jstar_aksst_w2_hd`|
| **Categories** |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing`|`999 = Missing`|`999 = Missing`|`999 = Missing`|`999 = Missing`|`999 = Missing`|
| **Description** |  |  |  |  |  |

```{r assign aksst_w2, echo=FALSE}

opal.assign.table.tibble(o, 'JSTAR_aksst_w2','JSTAR_HD.jstar_aksst_w2_hd',variables=list('h_diabetes','h_asthma','h_cpd','h_hypertension','h_joint_disorders','cvd_all'), missings = T)
JSTAR_aksst_w2 <- opal.execute(o,'JSTAR_aksst_w2')

```

```{r local aksst_w2, echo=FALSE}

vbl <- JSTAR_aksst_w2$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_diabetes")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(JSTAR_aksst_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w2$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_asthma")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(JSTAR_aksst_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w2$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_cpd")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(JSTAR_aksst_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w2$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_hypertension")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(JSTAR_aksst_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w2$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_joint_disorders")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(JSTAR_aksst_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w2$cvd_all
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "cvd_all")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(JSTAR_aksst_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `multimorbid` from the study-specific variables they have to be recoded as follows:

* `Multimorbid_score = sum(h_diabetes, h_asthma, h_cpd, h_hypertension, h_joint_disorders, cvd_all)`
* `Multimorbid_status = 1 if multimorbid_score > = 2`
* `Multimorbid_status = 0 if multimorbid_score < 2`
* `otherwise into 999`

**R script:**

```{r harmo aksst_w2}

JSTAR_ds_aksst_w2 <- JSTAR_aksst_w2 %>% 
  mutate(dead = purrr::pmap(mutate_at(., vars(-id), `==`, 996) %>% select(., -id), all) %>% unlist()) %>%
  mutate_at(., vars(-id), ~replace(., list = which(. %in% 991:999), values = NA)) %>% 
  mutate(multimorbid_score = rowSums(select(., -1, -dead), na.rm = T)) %>%
  mutate(cardNA = rowSums(!is.na(select(., -1, -dead, -multimorbid_score)))) %>%
  mutate(cardNA = cardNA/cardNA) %>%
  mutate(multimorbid_score = multimorbid_score * cardNA) %>%
  mutate(multimorbid = case_when(multimorbid_score >= 2 ~ 1, multimorbid_score < 2 ~ 0, dead ~ 996, TRUE ~ 999)) %>%
  select(id, multimorbid)

```

#### Statistics of the new harmonized variable

```{r descript aksst_w2, echo=F}

vbl <- JSTAR_ds_aksst_w2$multimorbid
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation aksst_w2, echo=F}
```


### Wave 3


#### Study-specific variable description

| **Name** |`h_diabetes`|`h_asthma`|`h_cpd`|`h_hypertension`|`h_joint_disorders`|`cvd_all`|
|-|-|-|-|-|-|-|
| **Label** |`History of diabetes mellitus`|`History of  Asthma`|`History of chronic pulmonary disorders`|`History of hypertension`|`History of arthritis, rheumatism or osteoarthritis`|`History of all Cardiovascular diseases`|
| **Table name** |`jstar_aksst_w3_hd`|`jstar_aksst_w3_hd`|`jstar_aksst_w3_hd`|`jstar_aksst_w3_hd`|`jstar_aksst_w3_hd`|`jstar_aksst_w3_hd`|
| **Categories** |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing`|`999 = Missing`|`999 = Missing`|`999 = Missing`|`999 = Missing`|`999 = Missing`|
| **Description** |  |  |  |  |  |

```{r assign aksst_w3, echo=FALSE}

opal.assign.table.tibble(o, 'JSTAR_aksst_w3','JSTAR_HD.jstar_aksst_w3_hd',variables=list('h_diabetes','h_asthma','h_cpd','h_hypertension','h_joint_disorders','cvd_all'), missings = T)
JSTAR_aksst_w3 <- opal.execute(o,'JSTAR_aksst_w3')

```

```{r local aksst_w3, echo=FALSE}

vbl <- JSTAR_aksst_w3$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_diabetes")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(JSTAR_aksst_w3, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w3$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_asthma")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(JSTAR_aksst_w3, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w3$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_cpd")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(JSTAR_aksst_w3, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w3$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_hypertension")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(JSTAR_aksst_w3, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w3$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_joint_disorders")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(JSTAR_aksst_w3, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w3$cvd_all
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "cvd_all")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(JSTAR_aksst_w3, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `multimorbid` from the study-specific variables they have to be recoded as follows:

* `Multimorbid_score = sum(h_diabetes, h_asthma, h_cpd, h_hypertension, h_joint_disorders, cvd_all)`
* `Multimorbid_status = 1 if multimorbid_score > = 2`
* `Multimorbid_status = 0 if multimorbid_score < 2`
* `otherwise into 999`

**R script:**

```{r harmo aksst_w3}

JSTAR_ds_aksst_w3 <- JSTAR_aksst_w3 %>% 
  mutate(dead = purrr::pmap(mutate_at(., vars(-id), `==`, 996) %>% select(., -id), all) %>% unlist()) %>%
  mutate_at(., vars(-id), ~replace(., list = which(. %in% 991:999), values = NA)) %>% 
  mutate(multimorbid_score = rowSums(select(., -1, -dead), na.rm = T)) %>%
  mutate(cardNA = rowSums(!is.na(select(., -1, -dead, -multimorbid_score)))) %>%
  mutate(cardNA = cardNA/cardNA) %>%
  mutate(multimorbid_score = multimorbid_score * cardNA) %>%
  mutate(multimorbid = case_when(multimorbid_score >= 2 ~ 1, multimorbid_score < 2 ~ 0, dead ~ 996, TRUE ~ 999)) %>%
  select(id, multimorbid)

```

#### Statistics of the new harmonized variable

```{r descript aksst_w3, echo=F}

vbl <- JSTAR_ds_aksst_w3$multimorbid
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w3, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation aksst_w3, echo=F}
```

## TN


### Wave 1


#### Study-specific variable description

| **Name** |`h_diabetes`|`h_asthma`|`h_cpd`|`h_hypertension`|`h_joint_disorders`|`cvd_all`|
|-|-|-|-|-|-|-|
| **Label** |`History of diabetes mellitus`|`History of  Asthma`|`History of chronic pulmonary disorders`|`History of hypertension`|`History of arthritis, rheumatism or osteoarthritis`|`History of all Cardiovascular diseases`|
| **Table name** |`jstar_tn_w1_hd`|`jstar_tn_w1_hd`|`jstar_tn_w1_hd`|`jstar_tn_w1_hd`|`jstar_tn_w1_hd`|`jstar_tn_w1_hd`|
| **Categories** |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing`|`999 = Missing`|`999 = Missing`|`999 = Missing`|`999 = Missing`|`999 = Missing`|
| **Description** |  |  |  |  |  |

```{r assign tn_w1, echo=FALSE}

opal.assign.table.tibble(o, 'JSTAR_tn_w1','JSTAR_HD.jstar_tn_w1_hd',variables=list('h_diabetes','h_asthma','h_cpd','h_hypertension','h_joint_disorders','cvd_all'), missings = T)
JSTAR_tn_w1 <- opal.execute(o,'JSTAR_tn_w1')

```

```{r local tn_w1, echo=FALSE}

vbl <- JSTAR_tn_w1$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_diabetes")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(JSTAR_tn_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w1$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_asthma")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(JSTAR_tn_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w1$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_cpd")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(JSTAR_tn_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w1$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_hypertension")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(JSTAR_tn_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w1$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_joint_disorders")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(JSTAR_tn_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w1$cvd_all
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "cvd_all")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(JSTAR_tn_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `multimorbid` from the study-specific variables they have to be recoded as follows:

* `Multimorbid_score = sum(h_diabetes, h_asthma, h_cpd, h_hypertension, h_joint_disorders, cvd_all)`
* `Multimorbid_status = 1 if multimorbid_score > = 2`
* `Multimorbid_status = 0 if multimorbid_score < 2`
* `otherwise into 999`

**R script:**

```{r harmo tn_w1}

JSTAR_ds_tn_w1 <- JSTAR_tn_w1 %>% 
  mutate(dead = purrr::pmap(mutate_at(., vars(-id), `==`, 996) %>% select(., -id), all) %>% unlist()) %>%
  mutate_at(., vars(-id), ~replace(., list = which(. %in% 991:999), values = NA)) %>% 
  mutate(multimorbid_score = rowSums(select(., -1, -dead), na.rm = T)) %>%
  mutate(cardNA = rowSums(!is.na(select(., -1, -dead, -multimorbid_score)))) %>%
  mutate(cardNA = cardNA/cardNA) %>%
  mutate(multimorbid_score = multimorbid_score * cardNA) %>%
  mutate(multimorbid = case_when(multimorbid_score >= 2 ~ 1, multimorbid_score < 2 ~ 0, dead ~ 996, TRUE ~ 999)) %>%
  select(id, multimorbid)

```

#### Statistics of the new harmonized variable

```{r descript tn_w1, echo=F}

vbl <- JSTAR_ds_tn_w1$multimorbid
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_tn_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation tn_w1, echo=F}
```


### Wave 2


#### Study-specific variable description

| **Name** |`h_diabetes`|`h_asthma`|`h_cpd`|`h_hypertension`|`h_joint_disorders`|`cvd_all`|
|-|-|-|-|-|-|-|
| **Label** |`History of diabetes mellitus`|`History of  Asthma`|`History of chronic pulmonary disorders`|`History of hypertension`|`History of arthritis, rheumatism or osteoarthritis`|`History of all Cardiovascular diseases`|
| **Table name** |`jstar_tn_w2_hd`|`jstar_tn_w2_hd`|`jstar_tn_w2_hd`|`jstar_tn_w2_hd`|`jstar_tn_w2_hd`|`jstar_tn_w2_hd`|
| **Categories** |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing`|`999 = Missing`|`999 = Missing`|`999 = Missing`|`999 = Missing`|`999 = Missing`|
| **Description** |  |  |  |  |  |

```{r assign tn_w2, echo=FALSE}

opal.assign.table.tibble(o, 'JSTAR_tn_w2','JSTAR_HD.jstar_tn_w2_hd',variables=list('h_diabetes','h_asthma','h_cpd','h_hypertension','h_joint_disorders','cvd_all'), missings = T)
JSTAR_tn_w2 <- opal.execute(o,'JSTAR_tn_w2')

```

```{r local tn_w2, echo=FALSE}

vbl <- JSTAR_tn_w2$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_diabetes")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(JSTAR_tn_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w2$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_asthma")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(JSTAR_tn_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w2$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_cpd")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(JSTAR_tn_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w2$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_hypertension")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(JSTAR_tn_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w2$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_joint_disorders")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(JSTAR_tn_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w2$cvd_all
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "cvd_all")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(JSTAR_tn_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `multimorbid` from the study-specific variables they have to be recoded as follows:

* `Multimorbid_score = sum(h_diabetes, h_asthma, h_cpd, h_hypertension, h_joint_disorders, cvd_all)`
* `Multimorbid_status = 1 if multimorbid_score > = 2`
* `Multimorbid_status = 0 if multimorbid_score < 2`
* `otherwise into 999`

**R script:**

```{r harmo tn_w2}

JSTAR_ds_tn_w2 <- JSTAR_tn_w2 %>% 
  mutate(dead = purrr::pmap(mutate_at(., vars(-id), `==`, 996) %>% select(., -id), all) %>% unlist()) %>%
  mutate_at(., vars(-id), ~replace(., list = which(. %in% 991:999), values = NA)) %>% 
  mutate(multimorbid_score = rowSums(select(., -1, -dead), na.rm = T)) %>%
  mutate(cardNA = rowSums(!is.na(select(., -1, -dead, -multimorbid_score)))) %>%
  mutate(cardNA = cardNA/cardNA) %>%
  mutate(multimorbid_score = multimorbid_score * cardNA) %>%
  mutate(multimorbid = case_when(multimorbid_score >= 2 ~ 1, multimorbid_score < 2 ~ 0, dead ~ 996, TRUE ~ 999)) %>%
  select(id, multimorbid)

```

#### Statistics of the new harmonized variable

```{r descript tn_w2, echo=F}

vbl <- JSTAR_ds_tn_w2$multimorbid
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_tn_w2, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation tn_w2, echo=F}
```


## CTH

### Wave 1


#### Study-specific variable description

| **Name** |`h_diabetes`|`h_asthma`|`h_cpd`|`h_hypertension`|`h_joint_disorders`|`cvd_all`|
|-|-|-|-|-|-|-|
| **Label** |`History of diabetes mellitus`|`History of  Asthma`|`History of chronic pulmonary disorders`|`History of hypertension`|`History of arthritis, rheumatism or osteoarthritis`|`History of all Cardiovascular diseases`|
| **Table name** |`jstar_cth_w1_hd`|`jstar_cth_w1_hd`|`jstar_cth_w1_hd`|`jstar_cth_w1_hd`|`jstar_cth_w1_hd`|`jstar_cth_w1_hd`|
| **Categories** |`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|`0 = No`<br/>`1 = Yes`|
| **Missings** |`999 = Missing`|`999 = Missing`|`999 = Missing`|`999 = Missing`|`999 = Missing`|`999 = Missing`|
| **Description** |  |  |  |  |  |

```{r assign cth_w1, echo=FALSE}

opal.assign.table.tibble(o, 'JSTAR_cth_w1','JSTAR_HD.jstar_cth_w1_hd',variables=list('h_diabetes','h_asthma','h_cpd','h_hypertension','h_joint_disorders','cvd_all'), missings = T)
JSTAR_cth_w1 <- opal.execute(o,'JSTAR_cth_w1')

```

```{r local cth_w1, echo=FALSE}

vbl <- JSTAR_cth_w1$h_diabetes
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_diabetes")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(JSTAR_cth_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_cth_w1$h_asthma
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_asthma")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(JSTAR_cth_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_cth_w1$h_cpd
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_cpd")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(JSTAR_cth_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_cth_w1$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_hypertension")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(JSTAR_cth_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_cth_w1$h_joint_disorders
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "h_joint_disorders")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(JSTAR_cth_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_cth_w1$cvd_all
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = "cvd_all")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
ggplot(JSTAR_cth_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `multimorbid` from the study-specific variables they have to be recoded as follows:

* `Multimorbid_score = sum(h_diabetes, h_asthma, h_cpd, h_hypertension, h_joint_disorders, cvd_all)`
* `Multimorbid_status = 1 if multimorbid_score > = 2`
* `Multimorbid_status = 0 if multimorbid_score < 2`
* `otherwise into 999`

**R script:**

```{r harmo cth_w1}

JSTAR_ds_cth_w1 <- JSTAR_cth_w1 %>% 
  mutate(dead = purrr::pmap(mutate_at(., vars(-id), `==`, 996) %>% select(., -id), all) %>% unlist()) %>%
  mutate_at(., vars(-id), ~replace(., list = which(. %in% 991:999), values = NA)) %>% 
  mutate(multimorbid_score = rowSums(select(., -1, -dead), na.rm = T)) %>%
  mutate(cardNA = rowSums(!is.na(select(., -1, -dead, -multimorbid_score)))) %>%
  mutate(cardNA = cardNA/cardNA) %>%
  mutate(multimorbid_score = multimorbid_score * cardNA) %>%
  mutate(multimorbid = case_when(multimorbid_score >= 2 ~ 1, multimorbid_score < 2 ~ 0, dead ~ 996, TRUE ~ 999)) %>%
  select(id, multimorbid)

```

#### Statistics of the new harmonized variable

```{r descript cth_w1, echo=F}

vbl <- JSTAR_ds_cth_w1$multimorbid
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_cth_w1, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation cth_w1, echo=F}
```


## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable by cohort:





```{r helpfunctions, echo=F}

source("../../helpfunctions.r")

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


jstar.cw <- list(aksst_w1 = c("aksst_w1","AKSST w1"), aksst_w2 = c("aksst_w2","AKSST w2"), aksst_w3 = c("aksst_w3","AKSST w3"), tn_w1 = c("tn_w1","TN w1"), tn_w2 = c("tn_w2","TN w2"), cth_w1 = c("cth_w1","CTH w1"))

# Consider only harmonised waves
l.hds <- lapply(jstar.cw, function(wname) if(exists(paste0("JSTAR_ds_",wname[1]))){wname = list(get(paste0("JSTAR_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```









# Quality estimation


```{r closeRsession, echo=FALSE}
opal.logout(o)
```

