---
title: "Respiratory diseases"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `h_respiratory`
* Variable label: `Chronic respiratory diseases such respiratory, CPD, COPD, bronchitis, emphysema`
* Variable description: `The participant has one or more of the following respiratory diseases: respiratory, chronic bronchitis, emphysema, chronic pulmonary disease, chronic obstructive pulmonary disease`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | no respiratory disease
1        | yes, respiratory disease

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "Chronic respiratory diseases such respiratory, CPD, COPD, bronchitis, emphysema"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process



## aksst


### Wave 1


#### Study-specific variable description

| **Name** | `h_001_7` |`h_001_6`|
|-|-|-|
| **Label** | `H-001-7:HAVE A ASTHMA`|`H-001-6:HAVE A CHRONIC LUNG DISEASE`|
| **Table name**  | `jstar_2007_5cities`| `jstar_2007_5cities`|
| **Categories** | `0 = Have not been diagnosed or advised to seek care`<br/>`1 = Have been diagnosed or advised to seek care` | `0 = Have not been diagnosed or advised to seek care`<br/>`1 = Have been diagnosed or advised to seek care`|
| **Missings** | `NA` | `NA` |
| **Description** |  |  |

```{r assign aksst_w1, echo=F}

opal.assign.table.tibble(o, 'JSTAR_aksst_w1','JSTAR_datasets_restricted.jstar_2007_5cities',variables=list('h_001_7','h_001_6'), missings = T)
JSTAR_aksst_w1 <- opal.execute(o,'JSTAR_aksst_w1')

```

```{r local aksst_w1, echo=F}

vbl <- JSTAR_aksst_w1$h_001_7
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_aksst_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w1, aes(x=factor(h_001_7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w1$h_001_6
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_aksst_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w1, aes(x=factor(h_001_6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_respiratory` from the study-specific variable it has to be recoded as follows:

* `all 0 into 0`
* `some 1 into 1`
* `NA into 999`

**R script:**

```{r harmo aksst_w1}

# Categorical variable harmonization
JSTAR_ds_aksst_w1 <- tibble(id=JSTAR_aksst_w1$id)
JSTAR_ds_aksst_w1$h_respiratory <- rep(999,length(JSTAR_aksst_w1$id))
JSTAR_ds_aksst_w1$h_respiratory[which(JSTAR_aksst_w1$h_001_7 == 0 & JSTAR_aksst_w1$h_001_6 == 0)] <- 0
JSTAR_ds_aksst_w1$h_respiratory[which(JSTAR_aksst_w1$h_001_7 == 1 | JSTAR_aksst_w1$h_001_6 == 1)] <- 1

# We build a global table in order to have updated the status of all the individuals through the different waves
JSTAR_ds_aksst <- JSTAR_ds_aksst_w1

```


#### Statistics of the new harmonized variable

```{r descript aksst_w1, echo=F}

vbl <- JSTAR_ds_aksst_w1$h_respiratory
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w1, aes(x=factor(h_respiratory))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation aksst_w1, echo=F}

AfterH <- table(JSTAR_ds_aksst_w1$h_respiratory)
X <- c(
  sum(JSTAR_aksst_w1$h_001_7 == 0 & JSTAR_aksst_w1$h_001_6 == 0,na.rm=T),
  sum(JSTAR_aksst_w1$h_001_7 == 1 | JSTAR_aksst_w1$h_001_6 == 1,na.rm=T)
)
BeforeH <- c(X[1:2],length(JSTAR_aksst_w1$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","NA->999")
kable(C)

```



### Wave 2

#### Study-specific variable description


| **Name** | `h_001_7` |`h_001_6`|
|-|-|-|
| **Label** | `H-001-7:HAVE A ASTHMA`|`H-001-6:HAVE A CHRONIC LUNG DISEASE`|
| **Table name**  | `jstar_2009_5cities`| `jstar_2009_5cities`|
| **Categories** | `1 = Newly diagnosed with or indicated`<br/>`2 = Fully recovered once but recurred in the past 2 years`<br/>`3 = Still be treated`<br/>`4 = Fully recovered/Never diagnosed with indicated` |`1 = Newly diagnosed with or indicated`<br/>`2 = Fully recovered once but recurred in the past 2 years`<br/>`3 = Still be treated`<br/>`4 = Fully recovered/Never diagnosed with indicated` |
| **Missings** | `NA` | `NA` |
| **Description** |  |  |

```{r assign aksst_w2, echo=F}

opal.assign.table.tibble(o, 'JSTAR_aksst_w2','JSTAR_datasets_restricted.jstar_2009_5cities',variables=list('h_001_7','h_001_6'), missings = T)
JSTAR_aksst_w2 <- opal.execute(o,'JSTAR_aksst_w2')

```

```{r local aksst_w2, echo=F}

vbl <- JSTAR_aksst_w2$h_001_7
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_aksst_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w2, aes(x=factor(h_001_7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w2$h_001_6
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_aksst_w2)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w2, aes(x=factor(h_001_6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_respiratory` from the study-specific variable it has to be recoded as follows:

* `h_001_7 (w1) == 0 and h_001_6 (w1) == 0 and h_001_7 (w2) == 4 and h_001_6 (w2) == 4 into 0`
* `h_001_7 (w1) == 1 or h_001_6 (w1) == 1 or h_001_7 (w2) == 1 or 2 or 3 or h_001_6 (w2) == 1 or 2 or 3 into 0`
* `otherwise into 999`

**R script:**

```{r harmo aksst_w2}

JSTAR_aksst_w2 <- left_join(JSTAR_aksst_w2, JSTAR_ds_aksst, by = "id")

# Categorical variable harmonization
JSTAR_ds_aksst_w2 <- tibble(id=JSTAR_aksst_w2$id)
JSTAR_ds_aksst_w2$h_respiratory <- rep(999,length(JSTAR_aksst_w2$id))
JSTAR_ds_aksst_w2$h_respiratory[which(JSTAR_aksst_w2$h_001_6 == 4 & JSTAR_aksst_w2$h_001_7 == 4 & (JSTAR_aksst_w2$h_respiratory != 1 | is.na(JSTAR_aksst_w2$h_respiratory)))] <- 0
JSTAR_ds_aksst_w2$h_respiratory[which(JSTAR_aksst_w2$h_001_6 %in% c(1,2,3) | JSTAR_aksst_w2$h_001_7 %in% c(1,2,3) | ((!(is.na(JSTAR_aksst_w2$h_001_7) & is.na(JSTAR_aksst_w2$h_001_6))) & JSTAR_aksst_w2$h_respiratory == 1))] <- 1

# We update the status of the individuals in the global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- left_join(endtib,sttib,by="id")
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
JSTAR_aksst_ds_prov <- JSTAR_ds_aksst[,c(1,2)]
JSTAR_aksst_ds_prov <- assign_merge(JSTAR_aksst_ds_prov,JSTAR_ds_aksst_w2,log_vec=(JSTAR_aksst_ds_prov$id %in% JSTAR_ds_aksst_w2$id),col_end_index = 2, col_st_index = 3)
JSTAR_ds_aksst$h_respiratory <- JSTAR_aksst_ds_prov$h_respiratory
rm(JSTAR_aksst_ds_prov)

```


#### Statistics of the new harmonized variable

```{r descript aksst_w2, echo=F}

vbl <- JSTAR_ds_aksst_w2$h_respiratory
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w2, aes(x=factor(h_respiratory))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation aksst_w2, echo=F, results='asis'}

AfterH <- table(JSTAR_ds_aksst_w2$h_respiratory, useNA = "ifany")
X <- c(
  sum(JSTAR_aksst_w2$h_001_6 == 4 & JSTAR_aksst_w2$h_001_7 == 4 & (JSTAR_aksst_w2$h_respiratory != 1 | is.na(JSTAR_aksst_w2$h_respiratory)),na.rm=T),
  sum(JSTAR_aksst_w2$h_001_6 %in% c(1,2,3) | JSTAR_aksst_w2$h_001_7 %in% c(1,2,3) | ((!(is.na(JSTAR_aksst_w2$h_001_7) & is.na(JSTAR_aksst_w2$h_001_6))) & JSTAR_aksst_w2$h_respiratory == 1),na.rm=T)
)
BeforeH <- c(X[1:2],length(JSTAR_aksst_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0 (w1),4 (w2)->0","1,2,3->1","NA->999")
kable(C)

JSTAR_aksst_w2 <- left_join(JSTAR_aksst_w2,JSTAR_aksst_w1, by="id", suffix = c("_w2","_w1"))

cat("There are 16 and 32 individuals who answered in wave 1 they had a chronic lung disease and asthma respectively and in wave 2 that they did not. We harmonize them as having chronic respiratory diseases.")
kable(frq(JSTAR_aksst_w2$h_001_6_w1[which(JSTAR_aksst_w2$h_001_6_w2==4)]),align='c')
kable(frq(JSTAR_aksst_w2$h_001_7_w1[which(JSTAR_aksst_w2$h_001_7_w2==4)]),align='c')

```



### Wave 3


#### Study-specific variable description

| **Name** | `h_001_7` |`h_001_6`|
|-|-|-|
| **Label** | `11H-001-7:HAVE A ASTHMA`|`11H-001-6:HAVE A CHRONIC LUNG DISEASE`|
| **Table name**  | `jstar_2011_5cities`| `jstar_2011_5cities`|
| **Categories** | `1 = Newly diagnosed with or indicated`<br/>`2 = Fully recovered once but recurred in the past 2 years`<br/>`3 = Still be treated`<br/>`4 = Fully recovered/Never diagnosed with indicated` | `1 = Newly diagnosed with or indicated`<br/>`2 = Fully recovered once but recurred in the past 2 years`<br/>`3 = Still be treated`<br/>`4 = Fully recovered/Never diagnosed with indicated` |
| **Missings** | `NA` | `NA` |
| **Description** |  |  |

```{r assign aksst_w3, echo=F}

opal.assign.table.tibble(o, 'JSTAR_aksst_w3','JSTAR_datasets_restricted.jstar_2011_5cities',variables=list('h_001_7','h_001_6'), missings = T)
JSTAR_aksst_w3 <- opal.execute(o,'JSTAR_aksst_w3')

```

```{r local aksst_w3, echo=F}

vbl <- JSTAR_aksst_w3$h_001_7
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_aksst_w3)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w3, aes(x=factor(h_001_7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w3$h_001_6
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_aksst_w3)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w3, aes(x=factor(h_001_6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_respiratory` from the study-specific variable it has to be recoded as follows:

* `h_001_7 (w1) == 0 and h_001_6 (w1) == 0 and h_001_7 (w2) == 4 and h_001_6 (w2) == 4 and h_001_7 (w3) == 4 and h_001_6 (w3) == 4 into 0`
* `h_001_7 (w1) == 1 or h_001_6 (w1) == 1 or h_001_7 (w2) == 1 or 2 or 3 or h_001_6 (w2) == 1 or 2 or 3 or h_001_7 (w3) == 1 or 2 or 3 or h_001_6 (w3) == 1 or 2 or 3 into 1`
* `otherwise into 999`

**R script:**

```{r harmo aksst_w3}

# We use the harmonized variable of previous waves instead of the study-specific variables
JSTAR_aksst_w3 <- left_join(JSTAR_aksst_w3, JSTAR_ds_aksst, by = "id")

# Categorical variable harmonization
JSTAR_ds_aksst_w3 <- tibble(id=JSTAR_aksst_w3$id)
JSTAR_ds_aksst_w3$h_respiratory <- rep(999,length(JSTAR_aksst_w3$id))
JSTAR_ds_aksst_w3$h_respiratory[which(JSTAR_aksst_w3$h_001_7 == 4 & JSTAR_aksst_w3$h_001_6 == 4 & (JSTAR_aksst_w3$h_respiratory != 1 | is.na(JSTAR_aksst_w3$h_respiratory)))] <- 0
JSTAR_ds_aksst_w3$h_respiratory[which(JSTAR_aksst_w3$h_001_7 %in% c(1,2,3) | JSTAR_aksst_w3$h_001_6 %in% c(1,2,3) | ((!(is.na(JSTAR_aksst_w3$h_001_7) & is.na(JSTAR_aksst_w3$h_001_6))) & JSTAR_aksst_w3$h_respiratory == 1))] <- 1

# We update the status of the individuals in the global table
rm(JSTAR_ds_aksst)

```


#### Statistics of the new harmonized variable

```{r descript aksst_w3, echo=F}

vbl <- JSTAR_ds_aksst_w3$h_respiratory
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w3, aes(x=factor(h_respiratory))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation aksst_w3, echo=F, results='asis'}

AfterH <- table(JSTAR_ds_aksst_w3$h_respiratory, useNA = "ifany")
X <- c(
  sum(JSTAR_aksst_w3$h_001_7 == 4 & JSTAR_aksst_w3$h_001_6 == 4 & (JSTAR_aksst_w3$h_respiratory != 1 | is.na(JSTAR_aksst_w3$h_respiratory)),na.rm=T),
  sum(JSTAR_aksst_w3$h_001_7 %in% c(1,2,3) | JSTAR_aksst_w3$h_001_6 %in% c(1,2,3) | ((!(is.na(JSTAR_aksst_w3$h_001_7) & is.na(JSTAR_aksst_w3$h_001_6))) & JSTAR_aksst_w3$h_respiratory == 1),na.rm=T)
)
BeforeH <- c(X[1:2],length(JSTAR_aksst_w3$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0 (w1),4 (w2)->0","1->1","NA->999")
kable(C)

JSTAR_aksst_w3 <- left_join(JSTAR_aksst_w3,JSTAR_aksst_w2, by="id")


cat("There are 26 and 39 individuals who answered in previous waves they had a chronic lung disease and asthma respectively and in wave 3 that they did not. We harmonize them as having chronic respiratory diseases.")
kable(frq(JSTAR_aksst_w3$h_001_6[which(JSTAR_aksst_w3$h_001_6_w1==1 | JSTAR_aksst_w3$h_001_6_w2 %in% c(1,2,3))]),align='c')
kable(frq(JSTAR_aksst_w3$h_001_7[which(JSTAR_aksst_w3$h_001_7_w1==1 | JSTAR_aksst_w3$h_001_7_w2 %in% c(1,2,3))]),align='c')

```



## tn

### Wave 1


#### Study-specific variable description

| **Name** | `h_001_7` |`h_001_6`|
|-|-|-|
| **Label** | `H-001-7:HAVE A ASTHMA`|`H-001-6:HAVE A CHRONIC LUNG DISEASE`|
| **Table name**  | `jstar_2009_2cities`| `jstar_2009_2cities`|
| **Categories** |`0 = Have not been diagnosed or advised to seek care`<br/>`1 = Have been diagnosed or advised to seek care`|`0 = Have not been diagnosed or advised to seek care`<br/>`1 = Have been diagnosed or advised to seek care`|
| **Missings** | `NA` | `NA` |
| **Description** |  |  |

```{r assign tn_w1, echo=F}

opal.assign.table.tibble(o, 'JSTAR_tn_w1','JSTAR_datasets_restricted.jstar_2009_2cities',variables=list('h_001_7','h_001_6'), missings = T)
JSTAR_tn_w1 <- opal.execute(o,'JSTAR_tn_w1')

```

```{r local tn_w1, echo=F}

vbl <- JSTAR_tn_w1$h_001_7
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_tn_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w1, aes(x=factor(h_001_7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w1$h_001_6
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_tn_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w1, aes(x=factor(h_001_6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_respiratory` from the study-specific variable it has to be recoded as follows:

* `all 0 into 0`
* `some 1 into 1`
* `NA into 999`

**R script:**

```{r harmo tn_w1}

# Categorical variable harmonization
JSTAR_ds_tn_w1 <- tibble(id=JSTAR_tn_w1$id)
JSTAR_ds_tn_w1$h_respiratory <- rep(999,length(JSTAR_tn_w1$id))
JSTAR_ds_tn_w1$h_respiratory[which(JSTAR_tn_w1$h_001_6 == 0 & JSTAR_tn_w1$h_001_7 == 0)] <- 0
JSTAR_ds_tn_w1$h_respiratory[which(JSTAR_tn_w1$h_001_6 == 1 | JSTAR_tn_w1$h_001_7 == 1)] <- 1

```


#### Statistics of the new harmonized variable

```{r descript tn_w1, echo=F}

vbl <- JSTAR_ds_tn_w1$h_respiratory
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_tn_w1, aes(x=factor(h_respiratory))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation tn_w1, echo=F}

AfterH <- table(JSTAR_ds_tn_w1$h_respiratory)
X <- c(
  sum(JSTAR_tn_w1$h_001_6 == 0 & JSTAR_tn_w1$h_001_7 == 0,na.rm=T),
  sum(JSTAR_tn_w1$h_001_6 == 1 | JSTAR_tn_w1$h_001_7 == 1,na.rm=T)
)
BeforeH <- c(X[1:2],length(JSTAR_tn_w1$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","NA->999")
kable(C)

```



### Wave 2

#### Study-specific variable description



| **Name** | `h_001_7` |`h_001_6`|
|-|-|-|
| **Label** | `H-001-7:HAVE A ASTHMA`|`H-001-6:HAVE A CHRONIC LUNG DISEASE`|
| **Table name**  | `jstar_2011_2cities`| `jstar_2011_2cities`|
| **Categories** | `1 = Newly diagnosed with or indicated`<br/>`2 = Fully recovered once but recurred in the past 2 years`<br/>`3 = Still be treated`<br/>`4 = Fully recovered/Never diagnosed with indicated`| `1 = Newly diagnosed with or indicated`<br/>`2 = Fully recovered once but recurred in the past 2 years`<br/>`3 = Still be treated`<br/>`4 = Fully recovered/Never diagnosed with indicated`|
| **Missings** | `NA` | `NA` |
| **Description** |  |  |


```{r assign tn_w2, echo=F}

opal.assign.table.tibble(o, 'JSTAR_tn_w2','JSTAR_datasets_restricted.jstar_2011_2cities',variables=list('h_001_7','h_001_6'), missings = T)
JSTAR_tn_w2 <- opal.execute(o,'JSTAR_tn_w2')

```

```{r local tn_w2, echo=F}

vbl <- JSTAR_tn_w2$h_001_7
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_tn_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w2, aes(x=factor(h_001_7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w2$h_001_6
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_tn_w2)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w2, aes(x=factor(h_001_6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_respiratory` from the study-specific variable it has to be recoded as follows:

* `h_001_7 (w1) == 0 and h_001_6 (w1) == 0 and h_001_7 (w2) == 4 and h_001_6 (w2) == 4 into 0`
* `h_001_7 (w1) == 1 or h_001_6 (w1) == 1 or h_001_7 (w2) == 1 or 2 or 3 or h_001_6 (w2) == 1 or 2 or 3 into 0`
* `otherwise into 999`

**R script:**

```{r harmo tn_w2}

JSTAR_tn_w2 <- left_join(JSTAR_tn_w2, JSTAR_ds_tn_w1, by = "id")

# Categorical variable harmonization
JSTAR_ds_tn_w2 <- tibble(id=JSTAR_tn_w2$id)
JSTAR_ds_tn_w2$h_respiratory <- rep(999,length(JSTAR_tn_w2$id))
JSTAR_ds_tn_w2$h_respiratory[which(JSTAR_tn_w2$h_001_6 == 4 & JSTAR_tn_w2$h_001_7 == 4 & (JSTAR_tn_w2$h_respiratory != 1 | is.na(JSTAR_tn_w2$h_respiratory)))] <- 0
JSTAR_ds_tn_w2$h_respiratory[which(JSTAR_tn_w2$h_001_6 %in% c(1,2,3) | JSTAR_tn_w2$h_001_7 %in% c(1,2,3) | ((!(is.na(JSTAR_tn_w2$h_001_7) & is.na(JSTAR_tn_w2$h_001_6))) & JSTAR_tn_w2$h_respiratory == 1))] <- 1

```


#### Statistics of the new harmonized variable

```{r descript tn_w2, echo=F}

vbl <- JSTAR_ds_tn_w2$h_respiratory
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_tn_w2, aes(x=factor(h_respiratory))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation tn_w2, echo=F, results='asis'}

AfterH <- table(JSTAR_ds_tn_w2$h_respiratory, useNA = "ifany")
X <- c(
  sum(JSTAR_tn_w2$h_001_6 == 4 & JSTAR_tn_w2$h_001_7 == 4 & (JSTAR_tn_w2$h_respiratory != 1 | is.na(JSTAR_tn_w2$h_respiratory)),na.rm=T),
  sum(JSTAR_tn_w2$h_001_6 %in% c(1,2,3) | JSTAR_tn_w2$h_001_7 %in% c(1,2,3) | ((!(is.na(JSTAR_tn_w2$h_001_7) & is.na(JSTAR_tn_w2$h_001_6))) & JSTAR_tn_w2$h_respiratory == 1),na.rm=T)
)
BeforeH <- c(X[1:2],length(JSTAR_tn_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0 (w1),4 (w2)->0","1,2,3->1","NA->999")
kable(C)

JSTAR_tn_w2 <- left_join(JSTAR_tn_w2,JSTAR_tn_w1, by="id", suffix = c("_w2","_w1"))

cat("There are 10 and 17 individuals who answered in wave 1 they had a chronic lung disease and asthma respectively and in wave 2 that they did not. We harmonize them as having chronic respiratory diseases.")
kable(frq(JSTAR_tn_w2$h_001_6_w1[which(JSTAR_tn_w2$h_001_6_w2==4)]),align='c')
kable(frq(JSTAR_tn_w2$h_001_7_w1[which(JSTAR_tn_w2$h_001_7_w2==4)]),align='c')
```



## cth

### Wave 1


#### Study-specific variable description

| **Name** | `h_001_7` |`h_001_6`|
|-|-|-|
| **Label** | `H-001-7:HAVE A ASTHMA`|`H-001-6:HAVE A CHRONIC LUNG DISEASE`|
| **Table name**  | `jstar_2011_3cities`| `jstar_2011_3cities`|
| **Categories** |`0 = Have not been diagnosed or advised to seek care`<br/>`1 = Have been diagnosed or advised to seek care`|`0 = Have not been diagnosed or advised to seek care`<br/>`1 = Have been diagnosed or advised to seek care`|
| **Missings** | `NA` | `NA` |
| **Description** |  |  |

```{r assign cth_w1, echo=F}

opal.assign.table.tibble(o, 'JSTAR_cth_w1','JSTAR_datasets_restricted.jstar_2011_3cities',variables=list('h_001_7','h_001_6'), missings = T)
JSTAR_cth_w1 <- opal.execute(o,'JSTAR_cth_w1')

```

```{r local cth_w1, echo=F}

vbl <- JSTAR_cth_w1$h_001_7
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_cth_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_cth_w1, aes(x=factor(h_001_7))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_cth_w1$h_001_6
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_cth_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_cth_w1, aes(x=factor(h_001_6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_respiratory` from the study-specific variable it has to be recoded as follows:

* `keep up 0 into 0`
* `keep up 1 into 1`
* `NA into 999`

**R script:**

```{r harmo cth_w1}

# Categorical variable harmonization
JSTAR_ds_cth_w1 <- tibble(id=JSTAR_cth_w1$id)
JSTAR_ds_cth_w1$h_respiratory <- rep(999,length(JSTAR_cth_w1$id))
JSTAR_ds_cth_w1$h_respiratory[which(JSTAR_cth_w1$h_001_6 == 0 & JSTAR_cth_w1$h_001_7 == 0)] <- 0
JSTAR_ds_cth_w1$h_respiratory[which(JSTAR_cth_w1$h_001_6 == 1 | JSTAR_cth_w1$h_001_7 == 1)] <- 1

```


#### Statistics of the new harmonized variable

```{r descript cth_w1, echo=F}

vbl <- JSTAR_ds_cth_w1$h_respiratory
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_cth_w1, aes(x=factor(h_respiratory))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation cth_w1, echo=F}

AfterH <- table(JSTAR_ds_cth_w1$h_respiratory)
X <- c(
  sum(JSTAR_cth_w1$h_001_6 == 0 & JSTAR_cth_w1$h_001_7 == 0,na.rm=T),
  sum(JSTAR_cth_w1$h_001_6 == 1 | JSTAR_cth_w1$h_001_7 == 1,na.rm=T)
)
BeforeH <- c(X[1:2],length(JSTAR_cth_w1$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 0->0","some 1->1","NA->999")
kable(C)

```








## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.

**R script:**

```{r summ}

l.hds <- list(aksst_w1 = JSTAR_ds_aksst_w1, aksst_w2 = JSTAR_ds_aksst_w2, aksst_w3 = JSTAR_ds_aksst_w3, tn_w1 = JSTAR_ds_tn_w1, tn_w2 = JSTAR_ds_tn_w2, cth_w1 = JSTAR_ds_cth_w1)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("JSTAR_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", 
             length(l.hds[[1]][[2]]), length(l.hds[[2]][[2]]) , length(l.hds[[3]][[2]]), length(l.hds[[4]][[2]]), length(l.hds[[5]][[2]]), length(l.hds[[6]][[2]]))
names(t.hds)<-c("val", "label", "AKSST_W1", "AKSST_W2", "AKSST_W3", "TN_W1", "TN_W2", "CTH_W1")
kable(t.hds)

```



# Quality estimation

* We assume that if an individual answers it has some chronic respiratory disease in one wave, it has for all the next waves. Individuals with discrepancies with respect to this criterium are specified at the end of each validation.
The harmonized variable contains information about asthma, chronic bronchitis and emphysema.



<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(l.hds)){
  h_respiratory <- l.hds[[index]]
  save(h_respiratory, file = paste0(datafolder,names(l.hds)[index],"/h_respiratory.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





