---
title: "Hypertension"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/hypertensionDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/hypertensionDS.R')
```



# Data process



## aksst


### Wave 1


#### Study-specific variable description

| **Name** | `h_001_2` |`h_001_2_1`|
|-|-|-|
| **Label** | `H-001-2:HAVE A HIGH BLOOD PRESSURE`|`H-001-2-1:HIGH BLOOD PRESSURE AGE`|
| **Table name**  | `jstar_2007_5cities`| `jstar_2007_5cities`|
| **Categories** | `0 = Have not been diagnosed or advised to seek care`<br/>`1 = Have been diagnosed or advised to seek care` |`continuous`|
| **Missings** | `NA` | `NA` |
| **Description** |  |  |

```{r assign aksst_w1, echo=F}

opal.assign.table.tibble(o, 'JSTAR_aksst_w1','JSTAR_datasets_restricted.jstar_2007_5cities',variables=list('h_001_2','h_001_2_1'), missings = T)
JSTAR_aksst_w1 <- opal.execute(o,'JSTAR_aksst_w1')

```

```{r local aksst_w1, echo=F}

vbl <- JSTAR_aksst_w1$h_001_2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_aksst_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w1, aes(x=factor(h_001_2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w1$h_001_2_1
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(JSTAR_aksst_w1)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_aksst_w1 %>% filter(!vbl %in% miss_values_vector), aes(h_001_2_1)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_hypertension` from the study-specific variable it has to be recoded as follows:

* `keep up 0 into 0`
* `keep up 1 into 1`
* `NA into 999`

To compute `h_hypertension_age` from the study-specific variable it has to be recoded as follows:

* `if h_hypertension == 1, h_hypertension_age = h_001_2_1`
* `if h_hypertension == 0, h_hypertension_age = 996`
* `h_hypertension == missing into 999`

**R script:**

```{r harmo aksst_w1}

# Categorical variable harmonization
JSTAR_ds_aksst_w1 <- tibble(id=JSTAR_aksst_w1$id)
JSTAR_ds_aksst_w1$h_hypertension <- car::recode(JSTAR_aksst_w1$h_001_2,"NA=999")

# Continuous variable harmonization
JSTAR_ds_aksst_w1$h_hypertension_age <- rep(999,length(JSTAR_ds_aksst_w1$id))
JSTAR_ds_aksst_w1$h_hypertension_age[which(JSTAR_ds_aksst_w1$h_hypertension==1)] <- JSTAR_aksst_w1$h_001_2_1[which(JSTAR_ds_aksst_w1$h_hypertension==1)]
JSTAR_ds_aksst_w1$h_hypertension_age[which(JSTAR_ds_aksst_w1$h_hypertension==0)] <- 996

# We build a global table in order to have updated the hypertension status of all the individuals through the different waves
JSTAR_ds_aksst <- JSTAR_ds_aksst_w1

```


#### Statistics of the new harmonized variable

```{r descript aksst_w1, echo=F}

vbl <- JSTAR_ds_aksst_w1$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w1, aes(x=factor(h_hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- JSTAR_ds_aksst_w1$h_hypertension_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_ds_aksst_w1 %>% filter(!vbl %in% miss_values_vector), aes(h_hypertension_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation aksst_w1, echo=F}

AfterH <- table(JSTAR_ds_aksst_w1$h_hypertension)
BeforeH <- table(JSTAR_aksst_w1$h_001_2, useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999")
kable(C)

```



### Wave 2

#### Study-specific variable description


| **Name** | `h_001_2` |`h_001_2_1_b`|`ybirth`|
|-|-|-|-|
| **Label** | `H-001-2:HAVE A HIGH BLOOD PRESSURE`|`H-001-2-1:HIGH BLOOD PRESSURE, YEAR`|`year of birth`|
| **Table name**  | `jstar_2009_5cities`| `jstar_2009_5cities`|`ybirth`|
| **Categories** | `1 = Newly diagnosed with or indicated`<br/>`2 = Fully recovered once but recurred in the past 2 years`<br/>`3 = Still be treated`<br/>`4 = Fully recovered/Never diagnosed with indicated` |`continuous`|`continuous`|
| **Missings** | `NA` | `NA` | `999 = Missing` |
| **Description** |  |  |  |

```{r assign aksst_w2, echo=F}

opal.assign.table.tibble(o, 'JSTAR_aksst_w2','JSTAR_datasets_restricted.jstar_2009_5cities',variables=list('h_001_2','h_001_2_1_b'), missings = T)
JSTAR_aksst_w2 <- opal.execute(o,'JSTAR_aksst_w2')
load(paste0(datafolder,"aksst_w2/ybirth.RData"))
JSTAR_aksst_w2 <- left_join(JSTAR_aksst_w2,ybirth,by="id")

```

```{r local aksst_w2, echo=F}

vbl <- JSTAR_aksst_w2$h_001_2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_aksst_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w2, aes(x=factor(h_001_2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w2$h_001_2_1_b
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(JSTAR_aksst_w2)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_aksst_w2 %>% filter(!vbl %in% miss_values_vector), aes(h_001_2_1_b)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w2$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(JSTAR_aksst_w2)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_aksst_w2 %>% filter(!vbl %in% miss_values_vector), aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_hypertension` from the study-specific variable it has to be recoded as follows:

* `h_001_2 (w1) == 0 and h_001_2 (w2) == 4 into 0`
* `h_001_2 (w1) == 1 or h_001_2 (w2) == 1 or 2 or 3 into 1`
* `otherwise into 999`

To compute `h_hypertension_age` from the study-specific variable it has to be recoded as follows:

* `if h_hypertension == 1 in w2 and 0 in w1, h_hypertension_age = h_001_2_1_b-ybirth`
* `if h_hypertension == 1 in w2 and w1, h_hypertension_age = age from wave 1`
* `if h_hypertension == 0, h_hypertension_age = 996`
* `h_hypertension == missing into 999`

**R script:**

```{r harmo aksst_w2}

JSTAR_aksst_w2 <- left_join(JSTAR_aksst_w2, JSTAR_ds_aksst, by = "id")

# Categorical variable harmonization
JSTAR_ds_aksst_w2 <- tibble(id=JSTAR_aksst_w2$id)
JSTAR_ds_aksst_w2$h_hypertension <- rep(999,length(JSTAR_aksst_w2$id))
JSTAR_ds_aksst_w2$h_hypertension[which(JSTAR_aksst_w2$h_001_2 == 4 & (JSTAR_aksst_w2$h_hypertension != 1 | is.na(JSTAR_aksst_w2$h_hypertension)))] <- 0
JSTAR_ds_aksst_w2$h_hypertension[which(JSTAR_aksst_w2$h_001_2 %in% c(1,2,3) | ((!is.na(JSTAR_aksst_w2$h_001_2)) & JSTAR_aksst_w2$h_hypertension == 1))] <- 1

# We update the hypertension status of the individuals in the global table
assign_merge <- function(endtib,sttib,log_vec=c(T),col_end_index=NULL,col_st_index=NULL){
  newtib <- left_join(endtib,sttib,by="id")
  newtib[log_vec,col_end_index] <- newtib[log_vec,col_st_index]
  id_ind <- match("id",names(newtib))
  newtib <- newtib[,c(id_ind,col_end_index)]
  names(newtib)[2] <- "x"
  newtib$x <- car::recode(newtib$x,"NA=999")
  names(newtib)[2] <- names(endtib)[col_end_index]
  newtib
}
JSTAR_aksst_ds_prov <- JSTAR_ds_aksst[,c(1,2)]
JSTAR_aksst_ds_prov <- assign_merge(JSTAR_aksst_ds_prov,JSTAR_ds_aksst_w2,log_vec=(JSTAR_aksst_ds_prov$id %in% JSTAR_ds_aksst_w2$id),col_end_index = 2, col_st_index = 3)
JSTAR_ds_aksst$h_hypertension <- JSTAR_aksst_ds_prov$h_hypertension
rm(JSTAR_aksst_ds_prov)

# Continuous variable harmonization
JSTAR_ds_aksst_w2$h_hypertension_age <- rep(999,length(JSTAR_aksst_w2$id))
JSTAR_ds_aksst_w2$h_hypertension_age[which(JSTAR_ds_aksst_w2$h_hypertension == 0)] <- 996
JSTAR_ds_aksst_w2$h_hypertension_age[which(JSTAR_ds_aksst_w2$h_hypertension == 1 & (JSTAR_aksst_w2$h_hypertension!=1 | is.na(JSTAR_aksst_w2$h_hypertension)) & JSTAR_aksst_w2$ybirth != 999)] <- JSTAR_aksst_w2$h_001_2_1_b[which(JSTAR_ds_aksst_w2$h_hypertension == 1 & (JSTAR_aksst_w2$h_hypertension!=1 | is.na(JSTAR_aksst_w2$h_hypertension)) & JSTAR_aksst_w2$ybirth != 999)]-JSTAR_aksst_w2$ybirth[which(JSTAR_ds_aksst_w2$h_hypertension == 1 & (JSTAR_aksst_w2$h_hypertension!=1 | is.na(JSTAR_aksst_w2$h_hypertension)) & JSTAR_aksst_w2$ybirth != 999)]
JSTAR_ds_aksst_w2$h_hypertension_age[which(JSTAR_ds_aksst_w2$h_hypertension == 1 & !is.na(JSTAR_aksst_w2$h_hypertension_age) & !JSTAR_aksst_w2$h_hypertension_age %in% miss_values_vector)] <- JSTAR_aksst_w2$h_hypertension_age[which(JSTAR_ds_aksst_w2$h_hypertension == 1 & !is.na(JSTAR_aksst_w2$h_hypertension_age) & !JSTAR_aksst_w2$h_hypertension_age %in% miss_values_vector)]
JSTAR_ds_aksst_w2$h_hypertension_age <- car::recode(JSTAR_ds_aksst_w2$h_hypertension_age, "NA=999")

JSTAR_ds_aksst$h_hypertension_age[which((JSTAR_ds_aksst$id %in% JSTAR_ds_aksst_w2$id) & (JSTAR_ds_aksst$h_hypertension != 999))] <- JSTAR_ds_aksst_w2$h_hypertension_age[which(JSTAR_ds_aksst_w2$h_hypertension != 999)]

```


#### Statistics of the new harmonized variable

```{r descript aksst_w2, echo=F}

vbl <- JSTAR_ds_aksst_w2$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w2, aes(x=factor(h_hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- JSTAR_ds_aksst_w2$h_hypertension_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_ds_aksst_w2 %>% filter(!vbl %in% miss_values_vector), aes(h_hypertension_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation aksst_w2, echo=F, results='asis'}

AfterH <- table(JSTAR_ds_aksst_w2$h_hypertension, useNA = "ifany")
X <- c(
  sum(((!is.na(JSTAR_aksst_w2$h_001_2)) & JSTAR_aksst_w2$h_001_2 == 4) & (JSTAR_aksst_w2$h_hypertension != 1)),
  sum(((!is.na(JSTAR_aksst_w2$h_001_2)) & JSTAR_aksst_w2$h_001_2 %in% c(1,2,3)) | ((!is.na(JSTAR_aksst_w2$h_hypertension)) & (!is.na(JSTAR_aksst_w2$h_001_2)) & JSTAR_aksst_w2$h_hypertension == 1))
)
BeforeH <- c(X[1:2],length(JSTAR_aksst_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0 (w1),4 (w2)->0","1,2,3->1","NA->999")
kable(C)


JSTAR_aksst_w2$agediff <- JSTAR_aksst_w2$h_001_2_1_b - JSTAR_aksst_w2$ybirth

cat('There are 14 individuals which answer incompatible age of diagnostic in wave 1 and year of diagnostic in wave 2. We harmonize them from the first data answered (wave 1).')
kable(JSTAR_aksst_w2[which(!is.na(JSTAR_aksst_w2$h_001_2_1_b) & !is.na(JSTAR_aksst_w2$h_hypertension_age) & !JSTAR_aksst_w2$h_hypertension_age %in% miss_values_vector & JSTAR_aksst_w2$h_hypertension_age != JSTAR_aksst_w2$agediff),],align = 'c')

cat("There are 91 individuals who answered in wave 1 they had hypertension and in wave 2 they did not. We harmonize them as having it")
kable(frq(JSTAR_aksst_w2$h_hypertension[which(JSTAR_aksst_w2$h_001_2==4)]),align='c', caption = 'Previous status of individuals who tell in wave 2 they have not high blood pressure')

```



### Wave 3


#### Study-specific variable description

| **Name** | `h_001_2` |`yintw (aksst_w2)`|`yintw (aksst_w3)`|`ybirth`|
|-|-|-|-|-|
| **Label** | `11H-001-2:HAVE A HIGH BLOOD PRESSURE`|`year of interview`|`year of interview`|`year of birth`|
| **Table name**  | `jstar_2011_5cities`| `yintw`| `yintw`|`ybirth`|
| **Categories** |`1 = Newly diagnosed with or indicated`<br/>`2 = Fully recovered once but recurred in the past 2 years`<br/>`3 = Still be treated`<br/>`4 = Fully recovered/Never diagnosed with indicated` |`continuous`|`continuous`|`continuous`||`continuous`|
| **Missings** | `NA` |  |  |  `999 = Missing` |
| **Description** |  |  |  |  |

```{r assign aksst_w3, echo=F}

opal.assign.table.tibble(o, 'JSTAR_aksst_w3','JSTAR_datasets_restricted.jstar_2011_5cities',variables=list('h_001_2'), missings = T)
JSTAR_aksst_w3 <- opal.execute(o,'JSTAR_aksst_w3')
load(paste0(datafolder,"aksst_w3/ybirth.RData"))
JSTAR_aksst_w3 <- left_join(JSTAR_aksst_w3,ybirth,by="id")
rm(ybirth)
load(paste0(datafolder,"aksst_w3/yintw.RData"))
JSTAR_aksst_w3 <- left_join(JSTAR_aksst_w3,yintw,by="id")
names(JSTAR_aksst_w3)[4] <- "yintw_aksst_w3"
rm(yintw)
load(paste0(datafolder,"aksst_w2/yintw.RData"))
JSTAR_aksst_w3 <- left_join(JSTAR_aksst_w3,yintw,by="id")
names(JSTAR_aksst_w3)[5] <- "yintw_aksst_w2"
rm(yintw)

```

```{r local aksst_w3, echo=F}

vbl <- JSTAR_aksst_w3$h_001_2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_aksst_w3)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w3, aes(x=factor(h_001_2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w3$yintw_aksst_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_aksst_w3)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w3, aes(x=factor(yintw_aksst_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w3$yintw_aksst_w3
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_aksst_w3)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w3, aes(x=factor(yintw_aksst_w3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w3$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(JSTAR_aksst_w3)[3])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_aksst_w3 %>% filter(!vbl %in% miss_values_vector), aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_hypertension` from the study-specific variable it has to be recoded as follows:

* `h_001_2 (w1) == 0 and h_001_2 (w2) == 4 and h_001_2 (w3) == 4 into 0`
* `h_001_2 (w1) == 1 or h_001_2 (w2) == 1 or 2 or 3 or h_001_2 (w3) == 1 or 2 or 3 into 1`
* `otherwise into 999`

To compute `h_hypertension_age` from the study-specific variable it has to be recoded as follows:

* `if h_hypertension == 1 in w3 and 0 in w2, h_hypertension_age = (year of interview w3-year of interview w2)/2+(year of interview w2 -ybirth)`
* `if h_hypertension == 1 in w3 and other wave, h_hypertension_age as previously`
* `if h_hypertension == 0, h_hypertension_age = 996`
* `h_hypertension == missing into 999`

**R script:**

```{r harmo aksst_w3}

# We use the harmonized variable of previous waves instead of the study-specific variables
JSTAR_aksst_w3 <- left_join(JSTAR_aksst_w3, JSTAR_ds_aksst, by = "id")

# Categorical variable harmonization
JSTAR_ds_aksst_w3 <- tibble(id=JSTAR_aksst_w3$id)
JSTAR_ds_aksst_w3$h_hypertension <- rep(999,length(JSTAR_aksst_w3$id))
JSTAR_ds_aksst_w3$h_hypertension[which(JSTAR_aksst_w3$h_001_2 == 4 & (JSTAR_aksst_w3$h_hypertension != 1 | is.na(JSTAR_aksst_w3$h_hypertension)))] <- 0
JSTAR_ds_aksst_w3$h_hypertension[which(JSTAR_aksst_w3$h_001_2 %in% c(1,2,3) | ((!is.na(JSTAR_aksst_w3$h_001_2)) & JSTAR_aksst_w3$h_hypertension == 1))] <- 1

# We update the hypertension status of the individuals in the global table
rm(JSTAR_ds_aksst)

# Continuous variable harmonization
JSTAR_ds_aksst_w3$h_hypertension_age <- rep(999,length(JSTAR_aksst_w3$id))
JSTAR_ds_aksst_w3$h_hypertension_age[which(JSTAR_ds_aksst_w3$h_hypertension == 0)] <- 996
JSTAR_ds_aksst_w3$h_hypertension_age[which(JSTAR_ds_aksst_w3$h_hypertension == 1 & !is.na(JSTAR_aksst_w3$h_hypertension_age) & !JSTAR_aksst_w3$h_hypertension_age %in% miss_values_vector)] <- JSTAR_aksst_w3$h_hypertension_age[which(JSTAR_ds_aksst_w3$h_hypertension == 1 & !is.na(JSTAR_aksst_w3$h_hypertension_age) & !JSTAR_aksst_w3$h_hypertension_age %in% miss_values_vector)]
JSTAR_ds_aksst_w3$h_hypertension_age[which(JSTAR_ds_aksst_w3$h_hypertension == 1 & JSTAR_aksst_w3$h_hypertension==0 & JSTAR_aksst_w3$ybirth != 999)] <- floor((JSTAR_aksst_w3$yintw_aksst_w3[which(JSTAR_ds_aksst_w3$h_hypertension == 1 & JSTAR_aksst_w3$h_hypertension==0 & JSTAR_aksst_w3$ybirth != 999)] + JSTAR_aksst_w3$yintw_aksst_w2[which(JSTAR_ds_aksst_w3$h_hypertension == 1 & JSTAR_aksst_w3$h_hypertension==0 & JSTAR_aksst_w3$ybirth != 999)])/2 - JSTAR_aksst_w3$ybirth[which(JSTAR_ds_aksst_w3$h_hypertension == 1 & JSTAR_aksst_w3$h_hypertension==0 & JSTAR_aksst_w3$ybirth != 999)])
JSTAR_ds_aksst_w3$h_hypertension_age <- car::recode(JSTAR_ds_aksst_w3$h_hypertension_age, "NA=999")

```


#### Statistics of the new harmonized variable

```{r descript aksst_w3, echo=F}

vbl <- JSTAR_ds_aksst_w3$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w3, aes(x=factor(h_hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- JSTAR_ds_aksst_w3$h_hypertension_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_ds_aksst_w3 %>% filter(!vbl %in% miss_values_vector), aes(h_hypertension_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation aksst_w3, echo=F, results='asis'}

AfterH <- table(JSTAR_ds_aksst_w3$h_hypertension, useNA = "ifany")
X <- c(
  sum(((!is.na(JSTAR_aksst_w3$h_001_2)) & JSTAR_aksst_w3$h_001_2 == 4) & (JSTAR_aksst_w3$h_hypertension != 1)),
  sum(((!is.na(JSTAR_aksst_w3$h_001_2)) & JSTAR_aksst_w3$h_001_2 %in% c(1,2,3)) | ((!is.na(JSTAR_aksst_w3$h_hypertension)) & (!is.na(JSTAR_aksst_w3$h_001_2)) & JSTAR_aksst_w3$h_hypertension == 1))
)
BeforeH <- c(X[1:2],length(JSTAR_aksst_w3$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0 (w1),4 (w2)->0","1,2,3->1","NA->999")
kable(C)

cat("There are 168 individuals who answered in previous waves they had hypertension and in wave 3 that they did not. We harmonize them as having it")
kable(frq(JSTAR_aksst_w3$h_hypertension[which(JSTAR_aksst_w3$h_001_2==4)]),align='c', caption = 'Previous status of individuals who tell in wave 3 they have not high blood pressure')

```



## tn

### Wave 1


#### Study-specific variable description

| **Name** | `h_001_2` |`h_001_2_1`|
|-|-|-|
| **Label** | `H-001-2:HAVE A HIGH BLOOD PRESSURE`|`H-001-2-1:HIGH BLOOD PRESSURE AGE`|
| **Table name**  | `jstar_2009_2cities`| `jstar_2009_2cities`|
| **Categories** | `0 = Have not been diagnosed or advised to seek care`<br/>`1 = Have been diagnosed or advised to seek care` |`continuous`|
| **Missings** | `NA` | `NA` |
| **Description** |  |  |

```{r assign tn_w1, echo=F}

opal.assign.table.tibble(o, 'JSTAR_tn_w1','JSTAR_datasets_restricted.jstar_2009_2cities',variables=list('h_001_2','h_001_2_1'), missings = T)
JSTAR_tn_w1 <- opal.execute(o,'JSTAR_tn_w1')

```

```{r local tn_w1, echo=F}

vbl <- JSTAR_tn_w1$h_001_2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_tn_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w1, aes(x=factor(h_001_2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w1$h_001_2_1
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(JSTAR_tn_w1)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_tn_w1 %>% filter(!vbl %in% miss_values_vector), aes(h_001_2_1)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_hypertension` from the study-specific variable it has to be recoded as follows:

* `keep up 0 into 0`
* `keep up 1 into 1`
* `NA into 999`

To compute `h_hypertension_age` from the study-specific variable it has to be recoded as follows:

* `if h_hypertension == 1, h_hypertension_age = h_001_2_1`
* `if h_hypertension == 0, h_hypertension_age = 996`
* `h_hypertension == missing into 999`

**R script:**

```{r harmo tn_w1}

# Categorical variable harmonization
JSTAR_ds_tn_w1 <- tibble(id=JSTAR_tn_w1$id)
JSTAR_ds_tn_w1$h_hypertension <- car::recode(JSTAR_tn_w1$h_001_2,"NA=999")

# Continuous variable harmonization
JSTAR_ds_tn_w1$h_hypertension_age <- rep(999,length(JSTAR_ds_tn_w1$id))
JSTAR_ds_tn_w1$h_hypertension_age[which(JSTAR_ds_tn_w1$h_hypertension==1)] <- JSTAR_tn_w1$h_001_2_1[which(JSTAR_ds_tn_w1$h_hypertension==1)]
JSTAR_ds_tn_w1$h_hypertension_age[which(JSTAR_ds_tn_w1$h_hypertension==0)] <- 996

```


#### Statistics of the new harmonized variable

```{r descript tn_w1, echo=F}

vbl <- JSTAR_ds_tn_w1$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_tn_w1, aes(x=factor(h_hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- JSTAR_ds_tn_w1$h_hypertension_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_ds_tn_w1 %>% filter(!vbl %in% miss_values_vector), aes(h_hypertension_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation tn_w1, echo=F}

AfterH <- table(JSTAR_ds_tn_w1$h_hypertension)
BeforeH <- table(JSTAR_tn_w1$h_001_2, useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999")
kable(C)

```



### Wave 2

#### Study-specific variable description



| **Name** | `h_001_2` |`yintw (tn_w2)`|`yintw (tn_w1)`|`ybirth`|
|-|-|-|-|-|
| **Label** | `11H-001-2:HAVE A HIGH BLOOD PRESSURE`|`year of interview`|`year of interview`|`year of birth`|
| **Table name**  | `jstar_2011_2cities`| `yintw`| `yintw`|`ybirth`|
| **Categories** |`1 = Newly diagnosed with or indicated`<br/>`2 = Fully recovered once but recurred in the past 2 years`<br/>`3 = Still be treated`<br/>`4 = Fully recovered/Never diagnosed with indicated`|`continuous`|`continuous`|`continuous`||`continuous`|
| **Missings** | `NA` |  |  |  `999 = Missing` |
| **Description** |  |  |  |  |



```{r assign tn_w2, echo=F}

opal.assign.table.tibble(o, 'JSTAR_tn_w2','JSTAR_datasets_restricted.jstar_2011_2cities',variables=list('h_001_2'), missings = T)
JSTAR_tn_w2 <- opal.execute(o,'JSTAR_tn_w2')
load(paste0(datafolder,"tn_w2/ybirth.RData"))
JSTAR_tn_w2 <- left_join(JSTAR_tn_w2,ybirth,by="id")
rm(ybirth)
load(paste0(datafolder,"tn_w2/yintw.RData"))
JSTAR_tn_w2 <- left_join(JSTAR_tn_w2,yintw,by="id")
names(JSTAR_tn_w2)[4] <- "yintw_tn_w2"
rm(yintw)
load(paste0(datafolder,"tn_w1/yintw.RData"))
JSTAR_tn_w2 <- left_join(JSTAR_tn_w2,yintw,by="id")
names(JSTAR_tn_w2)[5] <- "yintw_tn_w1"
rm(yintw)

```

```{r local tn_w2, echo=F}

vbl <- JSTAR_tn_w2$h_001_2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_tn_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w2, aes(x=factor(h_001_2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w2$yintw_tn_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_tn_w2)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w2, aes(x=factor(yintw_tn_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w2$yintw_tn_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_tn_w2)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w2, aes(x=factor(yintw_tn_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w2$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(JSTAR_tn_w2)[3])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_tn_w2 %>% filter(!vbl %in% miss_values_vector), aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_hypertension` from the study-specific variable it has to be recoded as follows:

* `h_001_2 (w1) == 0 and h_001_2 (w2) == 4 into 0`
* `h_001_2 (w1) == 1 or h_001_2 (w2) == 1 or 2 or 3 into 1`
* `otherwise into 999`

To compute `h_hypertension_age` from the study-specific variable it has to be recoded as follows:

* `if h_hypertension == 1 in w2 and 0 in w1, h_hypertension_age = (year of interview w2-year of interview w1)/2+(year of interview w1 -ybirth)`
* `if h_hypertension == 1 in w2 and w1, h_hypertension_age as previously`
* `if h_hypertension == 0, h_hypertension_age = 996`
* `h_hypertension == missing into 999`

**R script:**

```{r harmo tn_w2}

JSTAR_tn_w2 <- left_join(JSTAR_tn_w2, JSTAR_ds_tn_w1, by = "id")

# Categorical variable harmonization
JSTAR_ds_tn_w2 <- tibble(id=JSTAR_tn_w2$id)
JSTAR_ds_tn_w2$h_hypertension <- rep(999,length(JSTAR_tn_w2$id))
JSTAR_ds_tn_w2$h_hypertension[which(JSTAR_tn_w2$h_001_2 == 4 & (JSTAR_tn_w2$h_hypertension != 1 | is.na(JSTAR_tn_w2$h_hypertension)))] <- 0
JSTAR_ds_tn_w2$h_hypertension[which(JSTAR_tn_w2$h_001_2 %in% c(1,2,3) | ((!is.na(JSTAR_tn_w2$h_001_2)) & JSTAR_tn_w2$h_hypertension == 1))] <- 1

# Continuous variable harmonization
JSTAR_ds_tn_w2$h_hypertension_age <- rep(999,length(JSTAR_tn_w2$id))
JSTAR_ds_tn_w2$h_hypertension_age[which(JSTAR_ds_tn_w2$h_hypertension == 0)] <- 996
JSTAR_ds_tn_w2$h_hypertension_age[which(JSTAR_ds_tn_w2$h_hypertension == 1 & !JSTAR_tn_w2$h_hypertension_age %in% miss_values_vector & !is.na(JSTAR_tn_w2$h_hypertension_age))] <- JSTAR_tn_w2$h_hypertension_age[which(JSTAR_ds_tn_w2$h_hypertension == 1 & !JSTAR_tn_w2$h_hypertension_age %in% miss_values_vector & !is.na(JSTAR_tn_w2$h_hypertension_age))]
JSTAR_ds_tn_w2$h_hypertension_age[which(JSTAR_ds_tn_w2$h_hypertension == 1 & JSTAR_tn_w2$h_hypertension==0 & JSTAR_tn_w2$ybirth != 999)] <- floor((JSTAR_tn_w2$yintw_tn_w2[which(JSTAR_ds_tn_w2$h_hypertension == 1 & JSTAR_tn_w2$h_hypertension==0 & JSTAR_tn_w2$ybirth != 999)] + JSTAR_tn_w2$yintw_tn_w1[which(JSTAR_ds_tn_w2$h_hypertension == 1 & JSTAR_tn_w2$h_hypertension==0 & JSTAR_tn_w2$ybirth != 999)])/2 - JSTAR_tn_w2$ybirth[which(JSTAR_ds_tn_w2$h_hypertension == 1 & JSTAR_tn_w2$h_hypertension==0 & JSTAR_tn_w2$ybirth != 999)])

```


#### Statistics of the new harmonized variable

```{r descript tn_w2, echo=F}

vbl <- JSTAR_ds_tn_w2$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_tn_w2, aes(x=factor(h_hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- JSTAR_ds_tn_w2$h_hypertension_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_ds_tn_w2 %>% filter(!vbl %in% miss_values_vector), aes(h_hypertension_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation tn_w2, echo=F, results='asis'}

AfterH <- table(JSTAR_ds_tn_w2$h_hypertension, useNA = "ifany")
X <- c(
  sum(((!is.na(JSTAR_tn_w2$h_001_2)) & JSTAR_tn_w2$h_001_2 == 4) & (JSTAR_tn_w2$h_hypertension != 1)),
  sum(((!is.na(JSTAR_tn_w2$h_001_2)) & JSTAR_tn_w2$h_001_2 %in% c(1,2,3)) | ((!is.na(JSTAR_tn_w2$h_hypertension)) & (!is.na(JSTAR_tn_w2$h_001_2)) & JSTAR_tn_w2$h_hypertension == 1))
)
BeforeH <- c(X[1:2],length(JSTAR_tn_w2$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0 (w1),4 (w2)->0","1,2,3->1","NA->999")
kable(C)

cat("There are 54 individuals who answered in wave 1 they had high blood pressure and in wave 2 they did not. We harmonize them as having hypertension")
kable(frq(JSTAR_tn_w2$h_hypertension[which(JSTAR_tn_w2$h_001_2==4)]),align='c', caption = 'Previous status of individuals who tell in wave 2 they have not high blood pressure')

```



## cth

### Wave 1


#### Study-specific variable description

| **Name** | `h_001_2` |`h_001_2_1`|
|-|-|-|
| **Label** | `H-001-2:HAVE A HIGH BLOOD PRESSURE`|`H-001-2-1:HIGH BLOOD PRESSURE AGE`|
| **Table name**  | `jstar_2011_3cities`| `jstar_2011_3cities`|
| **Categories** | `0 = Have not been diagnosed or advised to seek care`<br/>`1 = Have been diagnosed or advised to seek care` |`continuous`|
| **Missings** | `NA` | `NA` |
| **Description** |  |  |

```{r assign cth_w1, echo=F}

opal.assign.table.tibble(o, 'JSTAR_cth_w1','JSTAR_datasets_restricted.jstar_2011_3cities',variables=list('h_001_2','h_001_2_1'), missings = T)
JSTAR_cth_w1 <- opal.execute(o,'JSTAR_cth_w1')

```

```{r local cth_w1, echo=F}

vbl <- JSTAR_cth_w1$h_001_2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_cth_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_cth_w1, aes(x=factor(h_001_2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_cth_w1$h_001_2_1
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(JSTAR_cth_w1)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_cth_w1 %>% filter(!vbl %in% miss_values_vector), aes(h_001_2_1)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_hypertension` from the study-specific variable it has to be recoded as follows:

* `keep up 0 into 0`
* `keep up 1 into 1`
* `NA into 999`

To compute `h_hypertension_age` from the study-specific variable it has to be recoded as follows:

* `if h_hypertension == 1, h_hypertension_age = h_001_2_1`
* `if h_hypertension == 0, h_hypertension_age = 996`
* `h_hypertension == missing into 999`

**R script:**

```{r harmo cth_w1}

# Categorical variable harmonization
JSTAR_ds_cth_w1 <- tibble(id=JSTAR_cth_w1$id)
JSTAR_ds_cth_w1$h_hypertension <- car::recode(JSTAR_cth_w1$h_001_2,"NA=999")

# Continuous variable harmonization
JSTAR_ds_cth_w1$h_hypertension_age <- rep(999,length(JSTAR_ds_cth_w1$id))
JSTAR_ds_cth_w1$h_hypertension_age[which(JSTAR_ds_cth_w1$h_hypertension==1)] <- JSTAR_cth_w1$h_001_2_1[which(JSTAR_ds_cth_w1$h_hypertension==1)]
JSTAR_ds_cth_w1$h_hypertension_age[which(JSTAR_ds_cth_w1$h_hypertension==0)] <- 996

```


#### Statistics of the new harmonized variable

```{r descript cth_w1, echo=F}

vbl <- JSTAR_ds_cth_w1$h_hypertension
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_cth_w1, aes(x=factor(h_hypertension))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- JSTAR_ds_cth_w1$h_hypertension_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_ds_cth_w1 %>% filter(!vbl %in% miss_values_vector), aes(h_hypertension_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")

```


#### Validation

```{r crosstabulation cth_w1, echo=F}

AfterH <- table(JSTAR_ds_cth_w1$h_hypertension)
BeforeH <- table(JSTAR_cth_w1$h_001_2, useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999")
kable(C)

```








<!--AUXILIAR FUNCTIONS-->



```{r helpfunctions, echo=F}

source("../../helpfunctions.r")

```



```{r populations-waves, echo=F}


# All study waves and populations with abbreviated and descriptive names

jstar.cw <- list(aksst_w1 = c("aksst_w1","AKSST w1"), aksst_w2 = c("aksst_w2","AKSST w2"), aksst_w3 = c("aksst_w3","AKSST w3"), tn_w1 = c("tn_w1","TN w1"), tn_w2 = c("tn_w2","TN w2"), cth_w1 = c("cth_w1","CTH w1"))


```


<!--Labelling and saving-->

```{r, echo=FALSE}


# Consider only waves with some variable harmonised

l.hds <- lapply(jstar.cw, function(wname) if(exists(paste0("JSTAR_ds_",wname[1]))){wname = list(get(paste0("JSTAR_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling categorical variable of tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]],hd_vbl,ds_label)
  # Labelling continuous variable of tibbles
  lmlist <- labelling_c(lmlist[[1]],lmlist[[2]],hd_age_vbl,ds_label_age)
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}

jstarlist <- lmlist # baseline list




```



<!--Descriptives-->

## Descriptive statistics of the harmonised variable `h_hypertension` accross populations and waves

Percentages of categories in each harmonised variable:


```{r summ, echo=F}


# Consider only harmonised waves
l.hds <- lapply(jstar.cw, function(wname) if(hd_vbl %in% names(get0(paste0("JSTAR_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- jstarlist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- jstarlist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl),caption=ds_label))
}





```






## Summary of descriptive statistics of the harmonised variable `h_hypertension_age` accross populations and waves






```{r summ_c, echo=F}


# Consider only harmonised waves
l.hds <- lapply(jstar.cw, function(wname) if(hd_age_vbl %in% names(get0(paste0("JSTAR_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- jstarlist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- jstarlist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries_c(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_age_vbl),caption=ds_label_age))
}



```



# Quality estimation

* We assume that if an individual answers it has high blood pressure in one wave, it has for all the next waves. Individuals with discrepancies with respect to this criterium are specified at the end of each validation.
* There are individuals whose harmonized diagnostic ages depend on the waves. We harmonize diagnostic age taking the first data they answer.
* In CTH subsample there is an individual which answers age of diagnostic 0. We keep this data in harmonisation.
```{r echo=F}
kable(JSTAR_cth_w1[which(JSTAR_cth_w1$h_001_2_1==0),])
```





<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





