---
title: "Stroke"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `stroke`
* Variable label: `Stroke`
* Variable description: `Diagnosis of stroke or cerebral vascular disease since the last wave`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | NOT A stroke (cerebral vascular disease) 
1        | A stroke (cerebral vascular disease)

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

* Short name: `stroke_age`
* Variable label: `Age of each episode of stroke`
* Variable description: `Age of each episode of stroke`
* Domain: `Diseases`
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "Stroke"
ds_label_age <- "Age of each episode of stroke"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
cont_label <- cat_label[3:11]
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process



## aksst


### Wave 1


#### Study-specific variable description

| **Name** | `h_001_4` |`h_001_4_1`|
|-|-|-|
| **Label** | `H-001-4:HAVE A APOPLEXY`|`H-001-4-1:APOPLEXY AGE`|
| **Table name**  | `jstar_2007_5cities`| `jstar_2007_5cities`|
| **Categories** | `0 = Have not been diagnosed or advised to seek care`<br/>`1 = Have been diagnosed or advised to seek care` |`continuous`|
| **Missings** | `NA` | `NA` |
| **Description** |  |  |

```{r assign aksst_w1, echo=F}

opal.assign.table.tibble(o, 'JSTAR_aksst_w1','JSTAR_datasets_restricted.jstar_2007_5cities',variables=list('h_001_4','h_001_4_1'), missings = T)
JSTAR_aksst_w1 <- opal.execute(o,'JSTAR_aksst_w1')

```

```{r local aksst_w1, echo=F}

vbl <- JSTAR_aksst_w1$h_001_4
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_aksst_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w1, aes(x=factor(h_001_4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w1$h_001_4_1
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(JSTAR_aksst_w1)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_aksst_w1, aes(h_001_4_1)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `keep up 0 into 0`
* `keep up 1 into 1`
* `NA into 999`

To compute `stroke_age` from the study-specific variable it has to be recoded as follows:

* `if stroke == 1, stroke_age = h_001_4_1`
* `if stroke == 0, stroke_age = 996`
* `stroke == missing into 999`

**R script:**

```{r harmo aksst_w1}

# Categorical variable harmonization
JSTAR_ds_aksst_w1 <- tibble(id=JSTAR_aksst_w1$id)
JSTAR_ds_aksst_w1$stroke <- car::recode(JSTAR_aksst_w1$h_001_4,"NA=999")

# Continuous variable harmonization
JSTAR_ds_aksst_w1$stroke_age <- rep(999,length(JSTAR_ds_aksst_w1$id))
JSTAR_ds_aksst_w1$stroke_age[which(JSTAR_ds_aksst_w1$stroke==1)] <- JSTAR_aksst_w1$h_001_4_1[which(JSTAR_ds_aksst_w1$stroke==1)]
JSTAR_ds_aksst_w1$stroke_age[which(JSTAR_ds_aksst_w1$stroke==0)] <- 996

```


#### Statistics of the new harmonized variable

```{r descript aksst_w1, echo=F}

vbl <- JSTAR_ds_aksst_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w1, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- JSTAR_ds_aksst_w1$stroke_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_ds_aksst_w1, aes(stroke_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(25,80)

```


#### Validation

```{r crosstabulation aksst_w1, echo=F}

AfterH <- table(JSTAR_ds_aksst_w1$stroke)
BeforeH <- table(JSTAR_aksst_w1$h_001_4, useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999")
kable(C)

```



### Wave 2

#### Study-specific variable description


| **Name** | `h_001_4` |`h_001_4_1_b`|`ybirth`|
|-|-|-|-|
| **Label** | `H-001-4:HAVE A CEREBRAL STROKE, CEREBROVASCULAR ACCIDENT`|`H-001-4-1:CEREBRAL STROKE, YEAR`|`year of birth`|
| **Table name**  | `jstar_2009_5cities`| `jstar_2009_5cities`|`ybirth`|
| **Categories** | `1 = Newly diagnosed with or indicated`<br/>`2 = Fully recovered once but recurred in the past 2 years`<br/>`3 = Still be treated`<br/>`4 = Fully recovered/Never diagnosed with indicated` |`continuous`|`continuous`|
| **Missings** | `NA` | `NA` | `999 = Missing` |
| **Description** |  |  |  |

```{r assign aksst_w2, echo=F}

opal.assign.table.tibble(o, 'JSTAR_aksst_w2','JSTAR_datasets_restricted.jstar_2009_5cities',variables=list('h_001_4','h_001_4_1_b'), missings = T)
JSTAR_aksst_w2 <- opal.execute(o,'JSTAR_aksst_w2')
load(paste0(datafolder,"aksst_w2/ybirth.RData"))
JSTAR_aksst_w2 <- left_join(JSTAR_aksst_w2,ybirth,by="id")

```

```{r local aksst_w2, echo=F}

vbl <- JSTAR_aksst_w2$h_001_4
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_aksst_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w2, aes(x=factor(h_001_4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w2$h_001_4_1_b
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(JSTAR_aksst_w2)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_aksst_w2, aes(h_001_4_1_b)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+scale_y_continuous(breaks=c(0,2,4,6,8,10))

vbl <- JSTAR_aksst_w2$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(JSTAR_aksst_w2)[4])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_aksst_w2, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1930,1960)

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `h_001_4 == 4 into 0`
* `h_001_4 == 1 or 2 or 3 into 1`
* `otherwise into 999`

To compute `stroke_age` from the study-specific variable it has to be recoded as follows:

* `if stroke == 1 in w2, stroke_age = h_001_4_1_b-ybirth`
* `if stroke == 0, stroke_age = 996`
* `otherwise into 999`

**R script:**

```{r harmo aksst_w2}

# Correction: The individual '1835' has already declared its stroke in the first wave, answers again with year of diagnosis previous to wave 1. We assume it corresponds to the same stroke, so:
JSTAR_aksst_w2$h_001_4[which(JSTAR_aksst_w2$id=="1835")] <- 4
# Correction: The individual '3590' has already declared its stroke in the first wave, answers now 'Fully recovered once but recurred in the past 2 years' with year of diagnosis previous to wave 1, so we change diagnostic year for the middle of the past 2 years to the year of interview (2009):
JSTAR_aksst_w2$h_001_4_1_b[which(JSTAR_aksst_w2$id=="3590")] <- 2008

# Categorical variable harmonization
JSTAR_ds_aksst_w2 <- tibble(id=JSTAR_aksst_w2$id)
JSTAR_ds_aksst_w2$stroke <- car::recode(JSTAR_aksst_w2$h_001_4,"4=0;2=1;3=1;NA=999")

# Continuous variable harmonization
JSTAR_ds_aksst_w2$stroke_age <- rep(999,length(JSTAR_aksst_w2$id))
JSTAR_ds_aksst_w2$stroke_age[which(JSTAR_ds_aksst_w2$stroke == 0)] <- 996
JSTAR_ds_aksst_w2$stroke_age[which(JSTAR_ds_aksst_w2$stroke == 1 & JSTAR_aksst_w2$ybirth != 999)] <- JSTAR_aksst_w2$h_001_4_1_b[which(JSTAR_ds_aksst_w2$stroke == 1 & JSTAR_aksst_w2$ybirth != 999)]-JSTAR_aksst_w2$ybirth[which(JSTAR_ds_aksst_w2$stroke == 1 & JSTAR_aksst_w2$ybirth != 999)]
JSTAR_ds_aksst_w2$stroke_age <- car::recode(JSTAR_ds_aksst_w2$stroke_age, "NA=999")

```


#### Statistics of the new harmonized variable

```{r descript aksst_w2, echo=F}

vbl <- JSTAR_ds_aksst_w2$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w2, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- JSTAR_ds_aksst_w2$stroke_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_ds_aksst_w2, aes(stroke_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(55,80)

```


#### Validation

```{r crosstabulation aksst_w2, echo=F, results='asis'}

AfterH <- table(JSTAR_ds_aksst_w2$stroke)
X <- table(JSTAR_aksst_w2$h_001_4, useNA = "ifany")
BeforeH <- c(X[4],sum(X[1:3]),X[5])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4->0","1,2,3->1","NA->999")
kable(C)

```



### Wave 3


#### Study-specific variable description

| **Name** | `h_001_4` |`yintw (aksst_w2)`|`yintw (aksst_w3)`|`ybirth`|
|-|-|-|-|-|
| **Label** | `11H-001-4:HAVE A CEREBRAL STROKE, CEREBROVASCULAR ACCIDENT`|`year of interview`|`year of interview`|`year of birth`|
| **Table name**  | `jstar_2011_5cities`| `yintw`| `yintw`|`ybirth`|
| **Categories** |`1 = Newly diagnosed with or indicated`<br/>`2 = Fully recovered once but recurred in the past 2 years`<br/>`3 = Still be treated`<br/>`4 = Fully recovered/Never diagnosed with indicated` |`continuous`|`continuous`|`continuous`|
| **Missings** | `NA` |  |  |  `999 = Missing` |
| **Description** |  |  |  |  |

```{r assign aksst_w3, echo=F}

opal.assign.table.tibble(o, 'JSTAR_aksst_w3','JSTAR_datasets_restricted.jstar_2011_5cities',variables=list('h_001_4'), missings = T)
JSTAR_aksst_w3 <- opal.execute(o,'JSTAR_aksst_w3')
load(paste0(datafolder,"aksst_w3/ybirth.RData"))
JSTAR_aksst_w3 <- left_join(JSTAR_aksst_w3,ybirth,by="id")
rm(ybirth)
load(paste0(datafolder,"aksst_w3/yintw.RData"))
JSTAR_aksst_w3 <- left_join(JSTAR_aksst_w3,yintw,by="id")
names(JSTAR_aksst_w3)[4] <- "yintw_aksst_w3"
rm(yintw)
load(paste0(datafolder,"aksst_w2/yintw.RData"))
JSTAR_aksst_w3 <- left_join(JSTAR_aksst_w3,yintw,by="id")
names(JSTAR_aksst_w3)[5] <- "yintw_aksst_w2"
rm(yintw)

```

```{r local aksst_w3, echo=F}

vbl <- JSTAR_aksst_w3$h_001_4
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_aksst_w3)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w3, aes(x=factor(h_001_4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w3$yintw_aksst_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_aksst_w3)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w3, aes(x=factor(yintw_aksst_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w3$yintw_aksst_w3
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_aksst_w3)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_aksst_w3, aes(x=factor(yintw_aksst_w3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_aksst_w3$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(JSTAR_aksst_w3)[3])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_aksst_w3, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1925,1965)

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `h_001_4 == 4 into 0`
* `h_001_4 == 1 or 2 or 3 into 1`
* `otherwise into 999`

To compute `stroke_age` from the study-specific variable it has to be recoded as follows:

* `if stroke == 1 in w3, stroke_age = (year of interview w3-year of interview w2)/2 + (year of interview w2 - ybirth)`
* `if stroke == 0, stroke_age = 996`
* `stroke == missing into 999`

**R script:**

```{r harmo aksst_w3}

# Categorical variable harmonization
JSTAR_ds_aksst_w3 <- tibble(id=JSTAR_aksst_w3$id)
JSTAR_ds_aksst_w3$stroke <- car::recode(JSTAR_aksst_w3$h_001_4,"4=0;2=1;3=1;NA=999")

# Continuous variable harmonization
JSTAR_ds_aksst_w3$stroke_age <- rep(999,length(JSTAR_aksst_w3$id))
JSTAR_ds_aksst_w3$stroke_age[which(JSTAR_ds_aksst_w3$stroke == 0)] <- 996
JSTAR_ds_aksst_w3$stroke_age[which(JSTAR_ds_aksst_w3$stroke == 1 & JSTAR_aksst_w3$ybirth != 999)] <- (JSTAR_aksst_w3$yintw_aksst_w3[which(JSTAR_ds_aksst_w3$stroke == 1 & JSTAR_aksst_w3$ybirth != 999)] + JSTAR_aksst_w3$yintw_aksst_w2[which(JSTAR_ds_aksst_w3$stroke == 1 & JSTAR_aksst_w3$ybirth != 999)])/2 - JSTAR_aksst_w3$ybirth[which(JSTAR_ds_aksst_w3$stroke == 1 & JSTAR_aksst_w3$ybirth != 999)]
JSTAR_ds_aksst_w3$stroke_age <- car::recode(JSTAR_ds_aksst_w3$stroke_age, "NA=999")

```


#### Statistics of the new harmonized variable

```{r descript aksst_w3, echo=F}

vbl <- JSTAR_ds_aksst_w3$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_aksst_w3, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- JSTAR_ds_aksst_w3$stroke_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_ds_aksst_w3, aes(stroke_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(50,80)

```


#### Validation

```{r crosstabulation aksst_w3, echo=F, results='asis'}

AfterH <- table(JSTAR_ds_aksst_w3$stroke, useNA = "ifany")
X <- table(JSTAR_aksst_w3$h_001_4, useNA = "ifany")
BeforeH <- c(X[4],sum(X[1:3]),X[5])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4->0","1,2,3->1","NA->999")
kable(C)

```



## tn

### Wave 1


#### Study-specific variable description

| **Name** | `h_001_4` |`h_001_4_1`|
|-|-|-|
| **Label** | `H-001-4:HAVE A CEREBRAL STROKE, CEREBROVASCULAR ACCIDENT`|`H-001-4-1:CEREBRAL STROKE, AGE`|
| **Table name**  | `jstar_2009_2cities`| `jstar_2009_2cities`|
| **Categories** | `0 = Have not been diagnosed or advised to seek care`<br/>`1 = Have been diagnosed or advised to seek care` |`continuous`|
| **Missings** | `NA` | `NA` |
| **Description** |  |  |

```{r assign tn_w1, echo=F}

opal.assign.table.tibble(o, 'JSTAR_tn_w1','JSTAR_datasets_restricted.jstar_2009_2cities',variables=list('h_001_4','h_001_4_1'), missings = T)
JSTAR_tn_w1 <- opal.execute(o,'JSTAR_tn_w1')

```

```{r local tn_w1, echo=F}

vbl <- JSTAR_tn_w1$h_001_4
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_tn_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w1, aes(x=factor(h_001_4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w1$h_001_4_1
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(JSTAR_tn_w1)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_tn_w1, aes(h_001_4_1)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `keep up 0 into 0`
* `keep up 1 into 1`
* `NA into 999`

To compute `stroke_age` from the study-specific variable it has to be recoded as follows:

* `if stroke == 1, stroke_age = h_001_4_1`
* `if stroke == 0, stroke_age = 996`
* `stroke == missing into 999`

**R script:**

```{r harmo tn_w1}

# Categorical variable harmonization
JSTAR_ds_tn_w1 <- tibble(id=JSTAR_tn_w1$id)
JSTAR_ds_tn_w1$stroke <- car::recode(JSTAR_tn_w1$h_001_4,"NA=999")

# Continuous variable harmonization
JSTAR_ds_tn_w1$stroke_age <- rep(999,length(JSTAR_ds_tn_w1$id))
JSTAR_ds_tn_w1$stroke_age[which(JSTAR_ds_tn_w1$stroke==1)] <- JSTAR_tn_w1$h_001_4_1[which(JSTAR_ds_tn_w1$stroke==1)]
JSTAR_ds_tn_w1$stroke_age[which(JSTAR_ds_tn_w1$stroke==0)] <- 996

```


#### Statistics of the new harmonized variable

```{r descript tn_w1, echo=F}

vbl <- JSTAR_ds_tn_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_tn_w1, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- JSTAR_ds_tn_w1$stroke_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_ds_tn_w1, aes(stroke_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(10,75)

```


#### Validation

```{r crosstabulation tn_w1, echo=F}

AfterH <- table(JSTAR_ds_tn_w1$stroke)
BeforeH <- table(JSTAR_tn_w1$h_001_4, useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999")
kable(C)

```



### Wave 2

#### Study-specific variable description



| **Name** | `h_001_4` |`yintw (tn_w2)`|`yintw (tn_w1)`|`ybirth`|
|-|-|-|-|-|
| **Label** | `11H-001-4:HAVE A CEREBRAL STROKE, CEREBROVASCULAR ACCIDENT`|`year of interview`|`year of interview`|`year of birth`|
| **Table name**  | `jstar_2011_2cities`| `yintw`| `yintw`|`ybirth`|
| **Categories** |`1 = Newly diagnosed with or indicated`<br/>`2 = Fully recovered once but recurred in the past 2 years`<br/>`3 = Still be treated`<br/>`4 = Fully recovered/Never diagnosed with indicated`|`continuous`|`continuous`|`continuous`|
| **Missings** | `NA` |  |  |  `999 = Missing` |
| **Description** |  |  |  |  |



```{r assign tn_w2, echo=F}

opal.assign.table.tibble(o, 'JSTAR_tn_w2','JSTAR_datasets_restricted.jstar_2011_2cities',variables=list('h_001_4'), missings = T)
JSTAR_tn_w2 <- opal.execute(o,'JSTAR_tn_w2')
load(paste0(datafolder,"tn_w2/ybirth.RData"))
JSTAR_tn_w2 <- left_join(JSTAR_tn_w2,ybirth,by="id")
rm(ybirth)
load(paste0(datafolder,"tn_w2/yintw.RData"))
JSTAR_tn_w2 <- left_join(JSTAR_tn_w2,yintw,by="id")
names(JSTAR_tn_w2)[4] <- "yintw_tn_w2"
rm(yintw)
load(paste0(datafolder,"tn_w1/yintw.RData"))
JSTAR_tn_w2 <- left_join(JSTAR_tn_w2,yintw,by="id")
names(JSTAR_tn_w2)[5] <- "yintw_tn_w1"
rm(yintw)

```

```{r local tn_w2, echo=F}

vbl <- JSTAR_tn_w2$h_001_4
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_tn_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w2, aes(x=factor(h_001_4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w2$yintw_tn_w1
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_tn_w2)[5])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w2, aes(x=factor(yintw_tn_w1))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w2$yintw_tn_w2
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_tn_w2)[4])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_tn_w2, aes(x=factor(yintw_tn_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_tn_w2$ybirth
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = names(JSTAR_tn_w2)[3])
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_tn_w2, aes(ybirth)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")+xlim(1930,1960)

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `h_001_4 == 4 into 0`
* `h_001_4 == 1 or 2 or 3 into 1`
* `otherwise into 999`

To compute `stroke_age` from the study-specific variable it has to be recoded as follows:

* `if stroke == 1 in w2, stroke_age = (year of interview w2-year of interview w1)/2+(year of interview w1-ybirth)`
* `if stroke == 0, stroke_age = 996`
* `stroke == missing into 999`

**R script:**

```{r harmo tn_w2}

# Categorical variable harmonization
JSTAR_ds_tn_w2 <- tibble(id=JSTAR_tn_w2$id)
JSTAR_ds_tn_w2$stroke <- car::recode(JSTAR_tn_w2$h_001_4,"4=0;2=1;3=1;NA=999")

# Continuous variable harmonization
JSTAR_ds_tn_w2$stroke_age <- rep(999,length(JSTAR_tn_w2$id))
JSTAR_ds_tn_w2$stroke_age[which(JSTAR_ds_tn_w2$stroke == 0)] <- 996
JSTAR_ds_tn_w2$stroke_age[which(JSTAR_ds_tn_w2$stroke == 1 & JSTAR_tn_w2$ybirth != 999)] <- (JSTAR_tn_w2$yintw_tn_w2[which(JSTAR_ds_tn_w2$stroke == 1 & JSTAR_tn_w2$ybirth != 999)] + JSTAR_tn_w2$yintw_tn_w1[which(JSTAR_ds_tn_w2$stroke == 1 & JSTAR_tn_w2$ybirth != 999)])/2 - JSTAR_tn_w2$ybirth[which(JSTAR_ds_tn_w2$stroke == 1 & JSTAR_tn_w2$ybirth != 999)]

```


#### Statistics of the new harmonized variable

```{r descript tn_w2, echo=F}

vbl <- JSTAR_ds_tn_w2$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_tn_w2, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- JSTAR_ds_tn_w2$stroke_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_ds_tn_w2, aes(stroke_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(55,80)

```


#### Validation

```{r crosstabulation tn_w2, echo=F, results='asis'}

AfterH <- table(JSTAR_ds_tn_w2$stroke, useNA = "ifany")
X <- table(JSTAR_tn_w2$h_001_4, useNA = "ifany")
BeforeH <- c(X[3],sum(X[1:2]),X[4])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("4->0","1,2,3->1","NA->999")
kable(C)

```



## cth

### Wave 1


#### Study-specific variable description

| **Name** | `h_001_4` |`h_001_4_1`|
|-|-|-|
| **Label** | `H-001-4:HAVE A CEREBRAL STROKE, CEREBROVASCULAR ACCIDENT`|`H-001-4-1:CEREBRAL STROKE, AGE`|
| **Table name**  | `jstar_2011_3cities`| `jstar_2011_3cities`|
| **Categories** | `0 = Have not been diagnosed or advised to seek care`<br/>`1 = Have been diagnosed or advised to seek care` |`continuous`|
| **Missings** | `NA` | `NA` |
| **Description** |  |  |

```{r assign cth_w1, echo=F}

opal.assign.table.tibble(o, 'JSTAR_cth_w1','JSTAR_datasets_restricted.jstar_2011_3cities',variables=list('h_001_4','h_001_4_1'), missings = T)
JSTAR_cth_w1 <- opal.execute(o,'JSTAR_cth_w1')

```

```{r local cth_w1, echo=F}

vbl <- JSTAR_cth_w1$h_001_4
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(JSTAR_cth_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(JSTAR_cth_w1, aes(x=factor(h_001_4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- JSTAR_cth_w1$h_001_4_1
kable(Continuous_summary(var = vbl, missing_values = NA)[3], caption = names(JSTAR_cth_w1)[3])
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(JSTAR_cth_w1, aes(h_001_4_1)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `stroke` from the study-specific variable it has to be recoded as follows:

* `keep up 0 into 0`
* `keep up 1 into 1`
* `NA into 999`

To compute `stroke_age` from the study-specific variable it has to be recoded as follows:

* `if stroke == 1, stroke_age = h_001_4_1`
* `if stroke == 0, stroke_age = 996`
* `stroke == missing into 999`

**R script:**

```{r harmo cth_w1}

# Categorical variable harmonization
JSTAR_ds_cth_w1 <- tibble(id=JSTAR_cth_w1$id)
JSTAR_ds_cth_w1$stroke <- car::recode(JSTAR_cth_w1$h_001_4,"NA=999")

# Continuous variable harmonization
JSTAR_ds_cth_w1$stroke_age <- rep(999,length(JSTAR_ds_cth_w1$id))
JSTAR_ds_cth_w1$stroke_age[which(JSTAR_ds_cth_w1$stroke==1)] <- JSTAR_cth_w1$h_001_4_1[which(JSTAR_ds_cth_w1$stroke==1)]
JSTAR_ds_cth_w1$stroke_age[which(JSTAR_ds_cth_w1$stroke==0)] <- 996

```


#### Statistics of the new harmonized variable

```{r descript cth_w1, echo=F}

vbl <- JSTAR_ds_cth_w1$stroke
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(JSTAR_ds_cth_w1, aes(x=factor(stroke))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vbl <- JSTAR_ds_cth_w1$stroke_age
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label_age)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(JSTAR_ds_cth_w1, aes(stroke_age)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_age) + ylab("Frequency")+xlim(25,80)

```


#### Validation

```{r crosstabulation cth_w1, echo=F}

AfterH <- table(JSTAR_ds_cth_w1$stroke)
BeforeH <- table(JSTAR_cth_w1$h_001_4, useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1->1","NA->999")
kable(C)

```








## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories. To avoid too large table, Only trajectories with percentages larger than 0.3 are shown.

**R script:**

```{r summ}

l.hds <- list(aksst_w1 = JSTAR_ds_aksst_w1, aksst_w2 = JSTAR_ds_aksst_w2, aksst_w3 = JSTAR_ds_aksst_w3, tn_w1 = JSTAR_ds_tn_w1, tn_w2 = JSTAR_ds_tn_w2, cth_w1 = JSTAR_ds_cth_w1)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  label(l.hds[[name]][[3]]) <- label(aux_object[[3]]) <- ds_label_age # Text value assigned at the DS description, at the top
  l.hds[[name]][[3]] <- labelled(l.hds[[name]][[3]], labels = cont_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("JSTAR_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", 
             length(l.hds[[1]][[2]]), length(l.hds[[2]][[2]]) , length(l.hds[[3]][[2]]), length(l.hds[[4]][[2]]), length(l.hds[[5]][[2]]), length(l.hds[[6]][[2]]))
names(t.hds)<-c("val", "label", "AKSST_W1", "AKSST_W2", "AKSST_W3", "TN_W1", "TN_W2", "CTH_W1")
kable(t.hds)

```



# Quality estimation

No comments

<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(l.hds)){
  stroke <- l.hds[[index]]
  save(stroke, file = paste0(datafolder,names(l.hds)[index],"/stroke.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





