---
title: "Any form of religious participation (religious services attendance, religious meetings, religious organization membership, etc.)"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `relig`
* Variable label: `Any form of religious participation`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process

## Irish population

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `dm021`
* Label: `About how often do you go to religious services?`
* Categories:
    + `1 = Never/almost never`
    + `2 = Once or twice a year`
    + `3 = Every few months`
    + `4 = Once or twice a month`
    + `5 = Once a week`
    + `6 = More than once a week`
* Missings:
    + `98 = Don't know`
    + `99 = Refused`
    + `-1 `

* Description:   
```{r assign1}
opal.assign.table.tibble(o, 'TILDA_w1_relig','TILDA.TILDA-AMF-v16',variables=list('dm021'), missings = TRUE)
```

```{r local1}
TILDA_w1_relig <- opal.execute(o,'TILDA_w1_relig')
vari <-  TILDA_w1_relig$dm021
kable(Categorical_summary(vari, missing_values = c(98,99,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(98,99,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(98,99,-1))[2], caption = "Type of missing")
#Categorical_summary(var = TILDA_w1_relig$dm021, missing_values = NA)
ggplot(TILDA_w1_relig, aes(x=factor(dm021))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("About how often do you go to religious services?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 0`
* `3,4,5 or 6 into 1`
* `98 into 998`
* `99 into 997`
* `-1, NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
TILDA_ds_w1 <- tibble(id=TILDA_w1_relig$id)
TILDA_ds_w1$relig <- car::recode(as.vector(TILDA_w1_relig$dm021), "1:2='0'; 3:6='1'; 98='998'; 99='997'; -1='999'; NA='999'")
TILDA_ds_w1$relig <- labelled(TILDA_ds_w1$relig, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1}
vari <- TILDA_ds_w1$relig
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = TILDA_ds_w1$relig, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(TILDA_ds_w1, aes(x=factor(relig))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any form of religious participation?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1}
AfterH <- table(TILDA_ds_w1$relig)
BeforeH <- table(TILDA_w1_relig$dm021, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(2:3)])
BeforeH1[[2]] <- sum(BeforeH[c(4:7)])
BeforeH1[[3]] <- BeforeH[[9]]
BeforeH1[[4]] <- BeforeH[[8]]
BeforeH1[[5]] <- BeforeH[[1]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:2->0","3:6->1","99->997","98->998","-1->999")
kable(C)
```


### Wave 2

Not found.

```{r save, echo=FALSE}
relig <- TILDA_ds_w1
save(relig, file = "../RData/w1/relig.RData")
rm(relig)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```

