---
title: "Any voluntary/charitable activity"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/volunDS.Rmd'}
```


```{r global, echo=F}
source('../../_DS_Rmd/volunDS.R')
```


<!-- ########################################################## --> 

# Data process

## Ireland

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `SCQsocact14`
* Label: `Charity work`
* Categories:
    + `1 = Daily, almost daily`
    + `2 = Once a week`
    + `3 = Twice a month`
    + `4 = Once a month`
    + `5 = Every few months`
    + `6 = Once or twice a year`
    + `7 = < once a year`
    + `8 = Never`
* Missings:
    + `-878 = Adjacent boxes 7&8 ticked`
    + `-867 = Adjacent boxes 6&7 ticked`
    + `-856 = Adjacent boxes 5&6 ticked`
    + `-845 = Adjacent boxes 4&5 ticked`
    + `-834 = Adjacent boxes 3&4 ticked`
    + `-823 = Adjacent boxes 2&3 ticked`
    + `-812 = Adjacent boxes 1&2 ticked`
    + `-99 = Refused`
    + `-98 = Don't Know`
    + `-9 = Refused`

    
* Description: 
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'TILDA_w1_volun','TILDA.TILDA-AMF-v16',variables=list('SCQsocact14'), missings = TRUE)
```

```{r local1, echo=F}
TILDA_w1_volun <- opal.execute(o,'TILDA_w1_volun')
vari <- TILDA_w1_volun$SCQsocact14
kable(Categorical_summary(vari, missing_values = c(-878,-867,-856,-845,-834,-823,-812,-99,-98,-9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-878,-867,-856,-845,-834,-823,-812,-99,-98,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-878,-867,-856,-845,-834,-823,-812,-99,-98,-9))[2], caption = "Type of missing")
#Categorical_summary(var = TILDA_w1_volun$SCQsocact14, missing_values = NA)
ggplot(TILDA_w1_volun, aes(x=factor(SCQsocact14))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Charity work") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `6,7,8 into 0`
* `1,2,3,4,5 into 1`
* `-99 or -9 into 997`
* `-98 into 998`
* `-878:-812 into 999`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
TILDA_ds_w1 <- tibble(id=TILDA_w1_volun$id)
TILDA_ds_w1$volun <- car::recode(as.vector(TILDA_w1_volun$SCQsocact14), "1:5='1'; 6:8='0'; -9='997'; -99='997'; -98='998'; -878:-812='999'; NA='999'")   
TILDA_ds_w1$volun <- labelled(TILDA_ds_w1$volun, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <- TILDA_ds_w1$volun
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = TILDA_ds_w1$volun, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(TILDA_ds_w1, aes(x=factor(volun))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any voluntary/charitable activity") + ylab("Frequency")

```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(TILDA_ds_w1$volun)
BeforeH <- table(TILDA_w1_volun$SCQsocact14, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(9:11)])
BeforeH1[[2]] <- sum(BeforeH[c(4:8)])
BeforeH1[[3]] <- sum(BeforeH[c(1:3, 12)])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("6:8->0","1:5->1","NA->999")
kable(C)
```



### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `SCQSocAct14`
* Label: `SCQSocAct14: Do voluntary work`
* Categories:
    + `1 = Daily, almost daily`
    + `2 = Once a week`
    + `3 = Twice a month`
    + `4 = Once a month`
    + `5 = Every few months`
    + `6 = Once or twice a year`
    + `7 = < once a year`
    + `8 = Never`
* Missings:
    + `-878 = Adjacent boxes 7&8 ticked`
    + `-867 = Adjacent boxes 6&7 ticked`
    + `-856 = Adjacent boxes 5&6 ticked`
    + `-845 = Adjacent boxes 4&5 ticked`
    + `-834 = Adjacent boxes 3&4 ticked`
    + `-823 = Adjacent boxes 2&3 ticked`
    + `-812 = Adjacent boxes 1&2 ticked`
    + `-99 = Refused`
    + `-98 = Don't Know`
    + `-9 = Refused`

    
* Description: 
```{r assign2, echo=F}
opal.assign.table.tibble(o, 'TILDA_w2_volun','TILDA.TILDA-AMF-v23', variables=list('SCQSocAct14'), missings = TRUE)
```

```{r local2, echo=F}
TILDA_w2_volun <- opal.execute(o,'TILDA_w2_volun')
vari <- TILDA_w2_volun$SCQSocAct14
kable(Categorical_summary(vari, missing_values = c(-878,-867,-856,-845,-834,-823,-812,-99,-98,-9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-878,-867,-856,-845,-834,-823,-812,-99,-98,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-878,-867,-856,-845,-834,-823,-812,-99,-98,-9))[2], caption = "Type of missing")
#Categorical_summary(var = TILDA_w2_volun$SCQSocAct14, missing_values = NA)
ggplot(TILDA_w2_volun, aes(x=factor(SCQSocAct14))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Do voluntary work") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `6,7,8 into 0`
* `1,2,3,4,5 into 1`
* `-99 or -9 into 997`
* `-98 into 998`
* `-878:-812 into 999`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
TILDA_ds_w2 <- tibble(id=TILDA_w2_volun$id)
TILDA_ds_w2$volun <- car::recode(as.vector(TILDA_w2_volun$SCQSocAct14), "1:5='1'; 6:8='0'; -9='997'; -99='997'; -98='998'; -878:-812='999'; NA='999'")   
TILDA_ds_w2$volun <- labelled(TILDA_ds_w2$volun, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}
vari <- TILDA_ds_w2$volun
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = TILDA_ds_w2$volun, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(TILDA_ds_w2, aes(x=factor(volun))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Any voluntary/charitable activity") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
AfterH <- table(TILDA_ds_w2$volun)
BeforeH <- table(TILDA_w2_volun$SCQSocAct14, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(9:11)])
BeforeH1[[2]] <- sum(BeforeH[c(4:8)])
BeforeH1[[3]] <- BeforeH[[3]]
BeforeH1[[4]] <- sum(BeforeH[c(1:2, 12)])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("6:8->0","1:5->1","-99->997","NA->999")
kable(C)
```



```{r save, echo=FALSE}
volun <- TILDA_ds_w1
save(volun, file = "../RData/w1/volun.RData")
rm(volun)

volun <- TILDA_ds_w2
save(volun, file = "../RData/w2/volun.RData")
rm(volun)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
