---
title: "Participation in club groups"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/part_clubsDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/part_clubsDS.R')
```




# Data process

## Ireland

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `SOCsocParticip`
* Label: `Social participation (Do you participate in any groups such as a sports or social group etc?)`
* Categories:
    + `1 = yes`
    + `2 = no`
* Missings:
    + `-99 = No answered`

    
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'TILDA_w1_part_clubs','TILDA.TILDA-AMF-v16',variables=list('SOCsocParticip'), missings = TRUE)
```

```{r local1, echo=F}
TILDA_w1_part_clubs <- opal.execute(o,'TILDA_w1_part_clubs')
Categorical_summary(var = TILDA_w1_part_clubs$SOCsocParticip, missing_values = NA)
ggplot(TILDA_w1_part_clubs, aes(x=factor(SOCsocParticip))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Do you participate in any groups such as a sports or social group etc?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1, 2 into 0, -99 into 995`
* `NA into 999`

**R script:**

```{r harmo1}
TILDA_ds_w1 <- tibble(id=TILDA_w1_part_clubs$id)
TILDA_ds_w1$part_clubs <- car::recode(as.vector(TILDA_w1_part_clubs$SOCsocParticip), "1='1'; 2='0'; -99='995'; NA='999'")
TILDA_ds_w1$part_clubs <- labelled(TILDA_ds_w1$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
Categorical_summary(var = TILDA_ds_w1$part_clubs, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(TILDA_ds_w1, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(TILDA_ds_w1$part_clubs)
BeforeH <- table(TILDA_w1_part_clubs$SOCsocParticip, useNA='ifany')
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1")
kable(C)
```



### TILDA - Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `cn001`
* Label: `Social participation (Do you participate in any groups such as a sports or social group etc?)`
* Categories:
    + `1 = yes`
    + `5 = no`
* Missings:
    + `98 = Don't know`
    + `99 = Refused`

```{r assign2, echo=F}
opal.assign.table.tibble(o, 'TILDA_w2_part_clubs','TILDA.TILDA-AMF-v23',variables=list('cn001'), missings = TRUE)
```

```{r local2, echo=F}
TILDA_w2_part_clubs <- opal.execute(o,'TILDA_w2_part_clubs')
Categorical_summary(var = TILDA_w2_part_clubs$cn001, missing_values = NA)
ggplot(TILDA_w2_part_clubs, aes(x=factor(cn001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Do you participate in any groups such as a sports or social group etc?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1, 5 into 0, 98 into 998, 99 into 997`
* `NA into 999`

**R script:**

```{r harmo2}
TILDA_ds_w2 <- tibble(id=TILDA_w2_part_clubs$id)
TILDA_ds_w2$part_clubs <- car::recode(as.vector(TILDA_w2_part_clubs$cn001), "1='1'; 5='0'; 98='998'; 99='997'; NA='999'")
TILDA_ds_w2$part_clubs <- labelled(TILDA_ds_w2$part_clubs, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
Categorical_summary(var = TILDA_ds_w2$part_clubs, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(TILDA_ds_w2, aes(x=factor(part_clubs))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Participation in any club/group") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
AfterH <- table(TILDA_ds_w2$part_clubs)
BeforeH <- table(TILDA_w2_part_clubs$cn001, useNA='ifany')[c(2,1,4,3)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->0","1","99->997","98->998")
kable(C)
```


```{r final, echo=F}

l.hds <- list(w1 = TILDA_ds_w1, w2 = TILDA_ds_w2)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("TILDA_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

```

## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.


```{r summ}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",names(l.hds))
kable(t.hds)

dbb <- get(paste0("TILDA_m_ds_",names(l.hds)[1]))[,c("id","part_clubs")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("TILDA_m_ds_",names(l.hds)[ind]))[,c("id","part_clubs")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", names(l.hds))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb)

```


# Quality estimation
[Comments on the quality of the new harmonised variable.]


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  part_clubs <- l.hds[[index]]
  save(part_clubs, file = paste0(datafolder,names(l.hds)[index],"/part_clubs.RData"))
}

```
<!-- ########################################################## --> 



<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
