---
title: "Experience of a loss of any close person"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variables is the following:

* Short name: `bereav`
* Variable label: `Experience of a loss of any close person`
* Domain: `Social environment`
* Value type: `cathegorical`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


<!-- ########################################################## --> 

# Data process

## Irish population


### Wave 1 

#### Study-specific variables

The study-specific variables elected to be harmonised are:

* Name: `cs006`
* Label: `Are you...?`
* Categories: 
    + `1 = Married`
    + `2 = Living with a partner as if married`
    + `3 = Single (never married)`
    + `4 = Separated`
    + `5 = Divorced`
    + `6 = Widowed`


* Name: `SCQfriendied`
* Label: `friends died in past 5 years`
* Categories:
    + `1 = yes`
    + `2 = no`
* Missings:
    + `-99 = not answered`
    
    
* Name: `SCQlifeev6`
* Label: `Child died`
* Categories:
    + `1 = yes`
    + `2 = no`
* Missings:
    + `-878 = Adjacent boxes 7&8 ticked`
    + `-867 = Adjacent boxes 6&7 ticked`
    + `-856 = Adjacent boxes 5&6 ticked`
    + `-845 = Adjacent boxes 4&5 ticked`
    + `-834 = Adjacent boxes 3&4 ticked`
    + `-823 = Adjacent boxes 2&3 ticked`
    + `-812 = Adjacent boxes 1&2 ticked`
    + `-99 = Refused`
    + `-98 = Don't Know`
    + `-9 = Refused`


* Description: 
```{r assign1}
opal.assign.table.tibble(o, 'TILDA_w1_bereav','TILDA.TILDA-AMF-v16', 
                        variables=list('cs006','SCQfriendied','SCQlifeev6'), missings = TRUE)
```

```{r local1}
TILDA_w1_bereav <- opal.execute(o,'TILDA_w1_bereav')
vari <- TILDA_w1_bereav$cs006
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = TILDA_w1_bereav$cs006, missing_values = NA)
ggplot(TILDA_w1_bereav, aes(x=factor(cs006))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")


vari <- TILDA_w1_bereav$SCQfriendied
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = TILDA_w1_bereav$SCQfriendied, missing_values = NA)
ggplot(TILDA_w1_bereav, aes(x=factor(SCQfriendied))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("friends died in past 5 years") + ylab("Frequency")


vari <- TILDA_w1_bereav$SCQlifeev6
kable(Categorical_summary(vari, missing_values = c(-99))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-99))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-99))[2], caption = "Type of missing")
#Categorical_summary(var = TILDA_w1_bereav$SCQlifeev6, missing_values = NA)
ggplot(TILDA_w1_bereav, aes(x=factor(SCQlifeev6))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Child died") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `cs006=6 or SCQfriendied=1 or SCQlifeev6=1 into 1`
* `cs006 in (1,2,3,4,5) AND SCQfriendied=2 AND SCQlifeev6=2 into 0`
* `SCQfriendied=-99 into 995`
* `SCQlifeev6 in (-878,-867,-856,-845,-834,-823,-812) into 999`
* `SCQlifeev6 in (-99, -9) into 997`
* `SCQlifeev6 = -98 into 998`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
TILDA_ds_w1 <- tibble(id=TILDA_w1_bereav$id)

TILDA_w1_bereav$cs006 <- car::recode(as.vector(TILDA_w1_bereav$cs006), "NA='-999'")
TILDA_w1_bereav$SCQfriendied <- car::recode(as.vector(TILDA_w1_bereav$SCQfriendied), "NA='-999'")
TILDA_w1_bereav$SCQlifeev6 <- car::recode(as.vector(TILDA_w1_bereav$SCQlifeev6), "NA='-999'")

TILDA_ds_w1$bereav <- c(NA)  

for(i in 1:dim(TILDA_w1_bereav)[1]){
  if(TILDA_w1_bereav$cs006[i] == 6 | TILDA_w1_bereav$SCQfriendied[i] == 1 | TILDA_w1_bereav$SCQlifeev6[i] == 1) { 
    TILDA_ds_w1$bereav[i] = 1 }
  else if(TILDA_w1_bereav$cs006[i] %in% c(1,2,3,4,5) & TILDA_w1_bereav$SCQfriendied[i]==2 & TILDA_w1_bereav$SCQlifeev6[i]==2) { 
    TILDA_ds_w1$bereav[i] = 0 }
  else if(TILDA_w1_bereav$SCQfriendied[i] == -99 ) { 
    TILDA_ds_w1$bereav[i] = 995 }
  else if(TILDA_w1_bereav$SCQlifeev6[i] %in% c(-878,-867,-856,-845,-834,-823,-812) ) { 
    TILDA_ds_w1$bereav[i] = 999 }
  else if(TILDA_w1_bereav$SCQlifeev6[i] %in% c(-99, -9) ) { 
    TILDA_ds_w1$bereav[i] = 997 }
  else if(TILDA_w1_bereav$SCQlifeev6[i] == -98 ) { 
    TILDA_ds_w1$bereav[i] = 998 }
}

TILDA_ds_w1$bereav <- car::recode(as.vector(TILDA_ds_w1$bereav), "NA='999'")
TILDA_ds_w1$bereav <- labelled(TILDA_ds_w1$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1}
vari <- TILDA_ds_w1$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = TILDA_ds_w1$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(TILDA_ds_w1, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Bereavement") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1} 

```



### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:


* Name: `SCQFriendied`
* Label: `SCQFriendied: Have any of your close friends died in the past two years?`
* Categories:
    + `1 = Yes`
    + `2 = No`
* Missings:
    + `-99 = No Response`
    

* Description: 
```{r assign2}
opal.assign.table.tibble(o, 'TILDA_w2_bereav','TILDA.TILDA-AMF-v23',variables=list('SCQFriendied'), missings = TRUE)
```

```{r local2}
TILDA_w2_bereav <- opal.execute(o,'TILDA_w2_bereav')
vari <- TILDA_w2_bereav$SCQFriendied
kable(Categorical_summary(vari, missing_values = c(-99))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-99))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-99))[2], caption = "Type of missing")
#Categorical_summary(var = TILDA_w2_bereav$SCQFriendied, missing_values = NA)
ggplot(TILDA_w2_bereav, aes(x=factor(SCQFriendied))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Have any of your close friends died in the past two years?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `SCQFriendied=1 into 1`
* `SCQFriendied=2 into 0`
* `SCQFriendied = -99 into 995`
* `NA into 999`

**R script:**

```{r harmo2.1, eval=FALSE, echo=FALSE}
### IF cs006 WAS AVAILABLE, THEN USE THIS CODE:
#
# TILDA_ds_w2 <- tibble(id=TILDA_w2_bereav$id)
# TILDA_w2_bereav$cs006 <- car::recode(as.vector(TILDA_w2_bereav$cs006), "NA='-999'")
# TILDA_w2_bereav$SCQFriendied <- car::recode(as.vector(TILDA_w2_bereav$SCQFriendied), "NA='-999'")
# TILDA_ds_w2$bereav <- c(NA)  
# for(i in 1:dim(TILDA_w2_bereav)[1]){
#   if(TILDA_w2_bereav$cs006[i] == 6 | TILDA_w2_bereav$SCQFriendied[i] == 1 ) {
#     TILDA_ds_w2$bereav[i] = 1 }
#   else if(TILDA_w2_bereav$cs006[i] %in% c(1,2,3,4,5) & TILDA_w2_bereav$SCQFriendied[i]==2) {
#     TILDA_ds_w2$bereav[i] = 0 }
#   else if(TILDA_w2_bereav$SCQFriendied[i] == -99 ) {
#     TILDA_ds_w2$bereav[i] = 995 }
# }
# TILDA_ds_w2$bereav <- car::recode(as.vector(TILDA_ds_w2$bereav), "NA='999'")
# TILDA_ds_w2$bereav <- labelled(TILDA_ds_w2$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

```{r harmo2, echo=TRUE}
TILDA_ds_w2 <- tibble(id=TILDA_w2_bereav$id)
TILDA_ds_w2$bereav <- car::recode(as.vector(TILDA_w2_bereav$SCQFriendied), "1='1'; 2='0'; -99='995'; NA='999'")
TILDA_ds_w2$bereav <- labelled(TILDA_ds_w2$bereav, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2}
vari <- TILDA_ds_w2$bereav
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = TILDA_ds_w2$bereav, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(TILDA_ds_w2, aes(x=factor(bereav))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Bereavement") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2}
AfterH <- table(TILDA_ds_w2$bereav)
BeforeH <- table(TILDA_w2_bereav$SCQFriendied, useNA='ifany')[c(3,2,1,4)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2->0","1->1","-99->995","NA->999")
kable(C)
```


```{r save, echo=FALSE}
bereav <- TILDA_ds_w1
save(bereav, file = "../RData/w1/bereav.RData")
rm(bereav)

bereav <- TILDA_ds_w2
save(bereav, file = "../RData/w2/bereav.RData")
rm(bereav)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```



