---
title: "Has friend(s)/confidant"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `confidant`
* Variable label: `Has friend(s)/confidant`
* Domain: `Social environment`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 

# Data process

## Irish population

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `cn004`
* Label: `In general, how many close friends do you have?`
* Missings:
    + `-99.0 = Refused`
    + `-98.0 = Don't know`


* Description: 
```{r assign1}
opal.assign.table.tibble(o, 'TILDA_w1_confidant','TILDA.TILDA-AMF-v16', variables=list('cn004'), missings = TRUE)
```

```{r local1}
TILDA_w1_confidant <- opal.execute(o,'TILDA_w1_confidant')
vari <- TILDA_w1_confidant$cn004
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = TILDA_w1_confidant$cn004, missing_values = NA)
ggplot(TILDA_w1_confidant, aes(x=factor(cn004))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How many close friends does he/she have") + ylab("Frequency")

```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `0 into 0`
* `Any number > 0 into 1`
* `-99 Refused into 997`
* `-98 Don't know into 998`
* `NA into 999`

 

**R script:** 
```{r harmo1, echo=TRUE}
TILDA_ds_w1 <- tibble(id=TILDA_w1_confidant$id)
TILDA_ds_w1$confidant <- car::recode(as.vector(TILDA_w1_confidant$cn004), "0='0'; -99='997'; -98='998'; NA='999'; 1:hi='1'")
TILDA_ds_w1$confidant <- labelled(TILDA_ds_w1$confidant, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1}
vari <- TILDA_ds_w1$confidant
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = TILDA_ds_w1$confidant, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(TILDA_ds_w1, aes(x=factor(confidant))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has any friend(s)/confidants(s)?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1}
AfterH <- table(TILDA_ds_w1$confidant)
BeforeH <- table(TILDA_w1_confidant$cn004, useNA='ifany')
BeforeH[[4]] <- sum(BeforeH[[4]],BeforeH[[5]],BeforeH[[6]],BeforeH[[7]],BeforeH[[8]],BeforeH[[9]],
                    BeforeH[[10]],BeforeH[[11]],BeforeH[[12]],BeforeH[[13]],BeforeH[[14]],BeforeH[[15]],BeforeH[[16]],
                    BeforeH[[17]],BeforeH[[18]],BeforeH[[19]],BeforeH[[20]],BeforeH[[21]])
BeforeH <- BeforeH[c(3,4,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","-99->997","-98->998")
kable(C)
```

 
 


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `cn004`
* Label: `In general, how many close friends do you have?`
* Missings:
    + `-99.0 = Refused`
    + `-98.0 = Don't know`

* Description: 
```{r assign2}
opal.assign.table.tibble(o, 'TILDA_w2_confidant','TILDA.TILDA-AMF-v23',variables=list('cn004'), missings = TRUE)
```

```{r local2}
TILDA_w2_confidant <- opal.execute(o,'TILDA_w2_confidant')
vari <- TILDA_w2_confidant$cn004
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = TILDA_w2_confidant$cn004, missing_values = NA)
ggplot(TILDA_w2_confidant, aes(x=factor(cn004))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How many close friends does he/she have") + ylab("Frequency")

```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `0 into 0`
* `Any number > 0 into 1`
* `-99 Refused into 997`
* `-98 Don't know into 998`
* `NA into 999`

 

**R script:** 
```{r harmo2, echo=TRUE}
TILDA_ds_w2 <- tibble(id=TILDA_w2_confidant$id)
TILDA_ds_w2$confidant <- car::recode(as.vector(TILDA_w2_confidant$cn004), "0=0; -99=997; -98=998; NA=999; 1:hi=1")
TILDA_ds_w2$confidant <- labelled(TILDA_ds_w2$confidant, labels = c('No'=0, 'Yes'=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2}
vari <- TILDA_ds_w2$confidant
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = TILDA_ds_w2$confidant, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(TILDA_ds_w2, aes(x=factor(confidant))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has any friend(s)/confidants(s)?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2}
AfterH <- table(TILDA_ds_w2$confidant)
BeforeH <- table(TILDA_w2_confidant$cn004, useNA='ifany')
BeforeH[[4]] <- sum(BeforeH[[4]],BeforeH[[5]],BeforeH[[6]],BeforeH[[7]],BeforeH[[8]],BeforeH[[9]],
                    BeforeH[[10]],BeforeH[[11]],BeforeH[[12]],BeforeH[[13]],BeforeH[[14]],BeforeH[[15]],BeforeH[[16]],
                    BeforeH[[17]],BeforeH[[18]],BeforeH[[19]],BeforeH[[20]])
BeforeH <- BeforeH[c(3,4,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1","-99->997","-98->998")
kable(C)
```

 
 
```{r save, echo=FALSE}
confidant <- TILDA_ds_w1
save(confidant, file = "../RData/w1/confidant.RData")
rm(confidant)

confidant <- TILDA_ds_w2
save(confidant, file = "../RData/w2/confidant.RData")
rm(confidant)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
