---
title: "Divorce/Separation"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/divorceDS.Rmd'}
```


```{r global, echo=F}
source('../../_DS_Rmd/divorceDS.R')
```

<!-- ########################################################## --> 

# Data process

## Ireland

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `cs006`
* Label: `Are you...?`
* Categories: 
    + `1 = Married`
    + `2 = Living with a partner as if married`
    + `3 = Single (never married)`
    + `4 = Separated`
    + `5 = Divorced`
    + `6 = Widowed`
* Description:


```{r assign1, echo=F}
opal.assign.table.tibble(o, 'TILDA_w1_divorce','TILDA.TILDA-AMF-v16', variables=list('cs006'), missings = TRUE)
```

```{r local1, echo=F}
TILDA_w1_divorce <- opal.execute(o,'TILDA_w1_divorce')
vari <- TILDA_w1_divorce$cs006
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = TILDA_w1_divorce$cs006, missing_values = NA)
ggplot(TILDA_w1_divorce, aes(x=factor(cs006))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `4,5 into 1`
* `1,2,3,6 into 0`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
TILDA_ds_w1 <- tibble(id=TILDA_w1_divorce$id)
TILDA_ds_w1$divorce <- car::recode(as.vector(TILDA_w1_divorce$cs006), "4:5='1'; 1:3='0'; 6='0'; NA='999'")
TILDA_ds_w1$divorce <- labelled(TILDA_ds_w1$divorce, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <- TILDA_ds_w1$divorce
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = TILDA_ds_w1$divorce, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(TILDA_ds_w1, aes(x=factor(divorce))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of divorce/separation") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(TILDA_ds_w1$divorce)
BeforeH <- table(TILDA_w1_divorce$cs006, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[2]] <- sum(BeforeH[c(4:5)])
BeforeH1[[1]] <- sum(BeforeH[c(1:3,6)])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("1:3&6->0","4:5->1")
kable(C)
```


### Wave 2

Not found.


```{r save, echo=FALSE}
divorce <- TILDA_ds_w1
save(divorce, file = "../RData/w1/divorce.RData")
rm(divorce)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```


