---
title: "Experience of any type of violence during the lifetime (including domestic violence and assault by a stranger)"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/violenceDS.Rmd'}
```


```{r global, echo=F}
source('../../_DS_Rmd/violenceDS.R')
```


<!-- ########################################################## --> 

# Data process

## Ireland

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `SCQlifeev3`
* Label: `Were you the victim of a serious physical attack or assault in your life?`
* Categories: 
    + `1 = yes`
    + `2 = no`
* Missings: 
    + `-878 = Adjacent boxes 7&8 ticked`
    + `-867 = Adjacent boxes 6&7 ticked`
    + `-856 = Adjacent boxes 5&6 ticked`
    + `-845 = Adjacent boxes 4&5 ticked`
    + `-834 = Adjacent boxes 3&4 ticked`
    + `-823 = Adjacent boxes 2&3 ticked`
    + `-812 = Adjacent boxes 1&2 ticked`
    + `-99 = Refused`
    + `-98 = Don't Know`
    + `-9 = Refused`
    + `-1 `

* Description: 
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'TILDA_w1_violence','TILDA.TILDA-AMF-v16',variables=list('SCQlifeev3'), missings = TRUE)
```

```{r local1, echo=F}
TILDA_w1_violence <- opal.execute(o,'TILDA_w1_violence')
vari <- TILDA_w1_violence$SCQlifeev3
kable(Categorical_summary(vari, missing_values = c(-878,-867,-856,-845,-823,812,-99,-98,-9,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-878,-867,-856,-845,-823,812,-99,-98,-9,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-878,-867,-856,-845,-823,812,-99,-98,-9,-1))[2], caption = "Type of missing")
#Categorical_summary(var = TILDA_w1_violence$SCQlifeev3, missing_values = NA)
ggplot(TILDA_w1_violence, aes(x=factor(SCQlifeev3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Were you the victim of a serious physical attack or assault in your life?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1; 2 into 0`
* `<= -812 into 999`
* `-99 or -9 into 997`
* `-98 into 998`
* `-1 and NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
TILDA_ds_w1 <- tibble(id=TILDA_w1_violence$id)
TILDA_ds_w1$violence <- car::recode(as.vector(TILDA_w1_violence$SCQlifeev3), "1='1'; 2='0'; -9='997'; -99='997'; -98='998'; -878:-812='999'; -1='999'; NA='999'")
TILDA_ds_w1$violence <- labelled(TILDA_ds_w1$violence, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <- TILDA_ds_w1$violence
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = TILDA_ds_w1$violence, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(TILDA_ds_w1, aes(x=factor(violence))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Experience of any type of violence during the lifetime") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(TILDA_ds_w1$violence)
BeforeH <- table(TILDA_w1_violence$SCQlifeev3, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[c(1,2,3)] <- BeforeH[c(4,3,1)]
BeforeH1[[4]] <- sum(BeforeH[c(2,5)])
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("2->0","1->1","-99->997","-1&NA->999")
kable(C)
```


### Wave 2

Not found.


```{r save, echo=FALSE}
violence <- TILDA_ds_w1
save(violence , file = "../RData/w1/violence.RData")
rm(violence )


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```


