---
title: "Has spouse/partner"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `spouse`
* Variable label: `Has spouse/partner`
* Domain: `Social environment`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 

# Data process

## Irish population
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `cs006`
* Label: `Are you...?`
* Categories: 
    + `1 = Married`
    + `2 = Living with a partner as if married`
    + `3 = Single (never married)`
    + `4 = Separated`
    + `5 = Divorced`
    + `6 = Widowed`
* Description: 
```{r assign1}
opal.assign.table.tibble(o, 'TILDA_w1_spouse','TILDA.TILDA-AMF-v16', variables=list('cs006'), missings = TRUE)
```

```{r local1}
TILDA_w1_spouse <- opal.execute(o,'TILDA_w1_spouse')
vari <- TILDA_w1_spouse$cs006
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = TILDA_w1_spouse$cs006, missing_values = NA)
ggplot(TILDA_w1_spouse, aes(x=factor(cs006))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Marital status") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 or 2 into 1`
* `3:6 into 0`
* `NA into 999`

**R script:**

```{r harmo1}
TILDA_ds_w1 <- tibble(id=TILDA_w1_spouse$id)
TILDA_ds_w1$spouse <- car::recode(as.vector(TILDA_w1_spouse$cs006), "1:2='1'; 3:6='0'; NA='999'")
TILDA_ds_w1$spouse <- labelled(TILDA_ds_w1$spouse, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1}
vari <- TILDA_ds_w1$spouse
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = TILDA_ds_w1$spouse, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(TILDA_ds_w1, aes(x=factor(spouse))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has spouse/partner") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1}
AfterH <- table(TILDA_ds_w1$spouse)
BeforeH <- table(TILDA_w1_spouse$cs006, useNA='ifany')
BeforeH[[1]] <- sum(BeforeH[1],BeforeH[2])
BeforeH[[2]] <- sum(BeforeH[3],BeforeH[4],BeforeH[5],BeforeH[6])
BeforeH <- BeforeH[c(2,1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3:6->0","1,2->1")

kable(C)
```

## Wave 2
Not found.


 
```{r save, echo=FALSE}
spouse <- TILDA_ds_w1
save(spouse, file = "../RData/w1/spouse.RData")
rm(spouse)

```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```

