---
title: "The number of close people: friends, neighbours or co-workers"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `clspeop`
* Variable label: `The number of close people: friends, neighbours or co-workers`
* Domain: `Social environment`
* Value type: `continuous`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | Lack of close people


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 

# Data process

## Irish population

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `cn004`
* Label: `In general, how many close friends do you have?`
* Missings:
    + `-99.0 = Refused`
    + `-98.0 = Don't know`


* Description: 
```{r assign1}
opal.assign.table.tibble(o, 'TILDA_w1_clspeop','TILDA.TILDA-AMF-v16',variables=list('cn004'), missings = TRUE)
```

```{r local1}
TILDA_w1_clspeop <- opal.execute(o,'TILDA_w1_clspeop')
vari <- TILDA_w1_clspeop$cn004
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = TILDA_w1_clspeop$cn004, missing_values = NA)
ggplot(TILDA_w1_clspeop, aes(x=factor(cn004))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How many close friends does he/she have") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:


* `-99 Refused into 997`
* `-98 Don't know into 998`
* `other values into themselves`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
TILDA_ds_w1 <- tibble(id=TILDA_w1_clspeop$id)
TILDA_ds_w1$clspeop <- car::recode(as.vector(TILDA_w1_clspeop$cn004), "-99='997'; -98='998'; NA='999'")
TILDA_ds_w1$clspeop <- labelled(TILDA_ds_w1$clspeop, labels = c("lack of close people"=0, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1}
vari <- TILDA_ds_w1$clspeop
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
#Continuous_summary(var = TILDA_ds_w1$clspeop, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(TILDA_ds_w1, aes(x=factor(clspeop))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The number of close persons: friends, neighbours or co-workers") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1}
AfterH <- table(TILDA_ds_w1$clspeop)
BeforeH <- table(TILDA_w1_clspeop$cn004, useNA='ifany')
BeforeH <- BeforeH[c(3:21,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C)[c(20,21)] <- c("-99->997","-98->998")

kable(C)
```

 
 


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `cn004`
* Label: `In general, how many close friends do you have?`
* Missings:
    + `-99.0 = Refused`
    + `-98.0 = Don't know`

* Description: 
```{r assign2}
opal.assign.table.tibble(o, 'TILDA_w2_clspeop','TILDA.TILDA-AMF-v23',variables=list('cn004'), missings = TRUE)
```

```{r local2}
TILDA_w2_clspeop <- opal.execute(o,'TILDA_w2_clspeop')
vari <- TILDA_w2_clspeop$cn004
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = TILDA_w2_clspeop$cn004, missing_values = NA)
ggplot(TILDA_w2_clspeop, aes(x=factor(cn004))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How many close friends does he/she have") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `-99 Refused into 997`
* `-98 Don't know into 998`
* `NA into 999`
* `other values into themselves`

**R script:**

```{r harmo2, echo=TRUE}
TILDA_ds_w2 <- tibble(id=TILDA_w2_clspeop$id)
TILDA_ds_w2$clspeop <- car::recode(as.vector(TILDA_w2_clspeop$cn004), "-99='997'; -98='998'; NA='999'")
TILDA_ds_w2$clspeop <- labelled(TILDA_ds_w2$clspeop, labels = c("lack of close people"=0, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2}
vari <- TILDA_ds_w2$clspeop
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
#Continuous_summary(var = TILDA_ds_w2$clspeop, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(TILDA_ds_w2, aes(x=factor(clspeop))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The number of close persons: friends, neighbours or co-workers") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2}
AfterH <- table(TILDA_ds_w2$clspeop)
BeforeH <- table(TILDA_w2_clspeop$cn004, useNA='ifany')
BeforeH <- BeforeH[c(3:20,1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C)[c(19,20)] <- c("-99->997","-98->998")

kable(C)
```

 
 
```{r save, echo=FALSE}
clspeop <- TILDA_ds_w1
save(clspeop, file = "../RData/w1/clspeop.RData")
rm(clspeop)

clspeop <- TILDA_ds_w2
save(clspeop, file = "../RData/w2/clspeop.RData")
rm(clspeop)
```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
