---
title: "The number of close relatives"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_ania.r")
```

<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `clsrel`
* Variable label: `The number of close relatives`
* Domain: `Social environment`
* Value type: `continuous`
* Categories:

**Code** | **Category Label**
-------- | ------------------
0        | Lack of close relatives


* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 

# Data process

## Irish population

### Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `cn002`
* Label: `How many of your children do you feel very close to?`
* Categories:
    + `10 = 10+`
* Missings:
    + `-99 = Refused`
    + `-98 = Don't Know`
    + `-1 = NA `
    
* Name: `cn003`
* Label: `In general (apart from your children) how many relatives do you have that you feel very close to?`
* Missings:
    + `-99 = Refused`
    + `-98 = Don't Know`


* Description: 
```{r assign1}
opal.assign.table.tibble(o, 'TILDA_w1_clsrel','TILDA.TILDA-AMF-v16', variables=list('cn002','cn003'), missings = TRUE)
```

```{r local1}
TILDA_w1_clsrel <- opal.execute(o,'TILDA_w1_clsrel')
vari <- TILDA_w1_clsrel$cn002
kable(Continuous_summary(var = vari, missing_values = c(-98,-99,-1))[3], caption = "cn002")
kable(Continuous_summary(vari, missing_values = c(-98,-99,-1))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-98,-99,-1))$summary, caption = "Summary")
#Continuous_summary(var = TILDA_w1_clsrel$cn002, missing_values = NA)
ggplot(TILDA_w1_clsrel, aes(x=factor(cn002))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How many of your children do you feel very close to?") + ylab("Frequency")

vari <- TILDA_w1_clsrel$cn003
kable(Continuous_summary(var = vari, missing_values = c(-98,-99))[3], caption = "cn003")
kable(Continuous_summary(vari, missing_values = c(-98,-99))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-98,-99))$summary, caption = "Summary")
#Continuous_summary(var = TILDA_w1_clsrel$cn003, missing_values = NA)
ggplot(TILDA_w1_clsrel, aes(x=factor(cn003))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("In general (apart from your children) how many relatives do you have that you feel very close to?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if cn002>=0 and cn003>=0 then clsrel = SUM of cn002 and cn003`
* `if only one of cn002 or cn003 is >=0 then clsrel is equal to it`
* `if any equals -99 then 997`
* `if any equals -98 then 998`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
TILDA_ds_w1 <- tibble(id=TILDA_w1_clsrel$id)

TILDA_w1_clsrel$cn002 <- car::recode(as.vector(TILDA_w1_clsrel$cn002), "NA='-999'")
TILDA_w1_clsrel$cn003 <- car::recode(as.vector(TILDA_w1_clsrel$cn003), "NA='-999'")

TILDA_ds_w1$clsrel <- c(NA)   
for(i in 1:dim(TILDA_w1_clsrel)[1]){
  if( TILDA_w1_clsrel$cn002[i] >= 0 & TILDA_w1_clsrel$cn003[i] >= 0 ) {
    TILDA_ds_w1$clsrel[i] = TILDA_w1_clsrel$cn002[i] + TILDA_w1_clsrel$cn003[i] }
  else if( TILDA_w1_clsrel$cn002[i] >= 0 & TILDA_w1_clsrel$cn003[i] < 0 ) {
    TILDA_ds_w1$clsrel[i] = TILDA_w1_clsrel$cn002[i] }
  else if( TILDA_w1_clsrel$cn002[i] < 0 & TILDA_w1_clsrel$cn003[i] >= 0 ) {
    TILDA_ds_w1$clsrel[i] = TILDA_w1_clsrel$cn003[i] }
  else if( TILDA_w1_clsrel$cn002[i] == -99 & TILDA_w1_clsrel$cn003[i] == -99 ) { 
    TILDA_ds_w1$clsrel[i] = 997 }
  else if( TILDA_w1_clsrel$cn002[i] == -98 & TILDA_w1_clsrel$cn003[i] == -98 ) { 
    TILDA_ds_w1$clsrel[i] = 998 }
}

TILDA_ds_w1$clsrel <- car::recode(as.vector(TILDA_ds_w1$clsrel), "NA='999'")
TILDA_ds_w1$clsrel <- labelled(TILDA_ds_w1$clsrel, labels = c("lack of friends"=0, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1}
vari <- TILDA_ds_w1$clsrel
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
#Continuous_summary(var = TILDA_ds_w1$clsrel, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(TILDA_ds_w1, aes(x=factor(clsrel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The number of close relatives") + ylab("Frequency") + theme(axis.text.x = element_text(angle = 45, hjust=1, vjust=1))
```

#### Validation
```{r crosstabulation1}

```

 
 


### Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `cn003`
* Label: `cn003 - In general, how many other relatives do you have that you feel close to?`
* Missings:
    + `-99 = Refused`
    + `-98 = Don't know`

* Description: 
```{r assign2}
opal.assign.table.tibble(o, 'TILDA_w2_clsrel','TILDA.TILDA-AMF-v23',variables=list('cn003'), missings = TRUE)
```

```{r local2}
TILDA_w2_clsrel <- opal.execute(o,'TILDA_w2_clsrel')
vari <- TILDA_w1_clsrel$cn003
kable(Continuous_summary(var = vari, missing_values = c(-98,-99))[3], caption = "cn003")
kable(Continuous_summary(vari, missing_values = c(-98,-99))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-98,-99))$summary, caption = "Summary")
#Continuous_summary(var = TILDA_w2_clsrel$cn003, missing_values = NA)
ggplot(TILDA_w2_clsrel, aes(x=factor(cn003))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("In general, how many other relatives do you have that you feel close to?") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `if cn003>=0 then clsrel=cn003`
* `if cn003=-99 then 997`
* `if cn003=-98 then 998`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
TILDA_ds_w2 <- tibble(id=TILDA_w2_clsrel$id)
TILDA_ds_w2$clsrel <- car::recode(as.vector(TILDA_w2_clsrel$cn003), "-99='997'; -98='998'; NA='-999'")
TILDA_ds_w2$clsrel <- labelled(TILDA_ds_w2$clsrel, labels = c("lack of friends"=0, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2}
vari <- TILDA_ds_w1$clsrel
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
#Continuous_summary(var = TILDA_ds_w2$clsrel, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(TILDA_ds_w2, aes(x=factor(clsrel))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("The number of close relatives") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2}
AfterH <- table(TILDA_ds_w2$clsrel)
BeforeH <- table(TILDA_w2_clsrel$cn003, useNA='ifany')
BeforeH <- BeforeH[c(3:(length(BeforeH)),1,2)]
C <- rbind(BeforeH,AfterH)
colnames(C)[c(21,22)] <- c("-99->997","-98->998")
kable(C)
```

 
```{r save, echo=FALSE}
clsrel <- TILDA_ds_w1
save(clsrel, file = "../RData/w1/clsrel.RData")
rm(clsrel)

clsrel <- TILDA_ds_w2
save(clsrel, file = "../RData/w2/clsrel.RData")
rm(clsrel)
```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```


