---
title: "Has other (living) family members (e.g. parents, siblings, in-laws, etc.)"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/oth_famDS.Rmd'}
```


```{r global, echo=F}
source('../../_DS_Rmd/oth_famDS.R')
```

<!-- ########################################################## --> 

# Data process
## Ireland
### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `SOCpalive`
* Label: `Living parents`
* Categories:
    + `0 = Neither alive`
    + `1 = Only mother alive`
    + `2 = Only father alive`
    + `3 = Both parents alive`

* Name: `tp036`
* Label: `How many living sisters do you have?`
* Categories:
    + `6 = 6+`
* Missings:
    + `-99 = Refused`
    + `-98 = Don't know`
    + `-1`
    
* Name: `tp037`
* Label: `How many living brothers do you have?`
* Categories:
    + `6 = 6+`
* Missings:
    + `-99 = Refused`
    + `-98 = Don't know`
    + `-1`

* Description:
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'TILDA_w1_oth_fam','TILDA.TILDA-AMF-v16',variables=list('SOCpalive','tp036','tp037'), missings = TRUE)
```

```{r local1, echo=F}
TILDA_w1_oth_fam <- opal.execute(o,'TILDA_w1_oth_fam')
vari <- TILDA_w1_oth_fam$SOCpalive
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = TILDA_w1_oth_fam$SOCpalive, missing_values = NA)
ggplot(TILDA_w1_oth_fam, aes(x=factor(SOCpalive))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living parents") + ylab("Frequency")

vari <-TILDA_w1_oth_fam$tp036
kable(Continuous_summary(var = vari, missing_values = c(-1,-98,-99))[3], caption = attributes(vari)$`spss::shortName`)
kable(Continuous_summary(vari, missing_values = c(-1,-98,-99))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-1,-98,-99))$summary, caption = "Summary")
#Continuous_summary(var = TILDA_w1_oth_fam$tp036, missing_values = NA)
ggplot(TILDA_w1_oth_fam, aes(x=factor(tp036))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How many living sisters do you have?") + ylab("Frequency")

vari <- TILDA_w1_oth_fam$tp037
kable(Continuous_summary(var = vari, missing_values = c(-1,-98,-99))[3], caption = attributes(vari)$`spss::shortName`)
kable(Continuous_summary(vari, missing_values = c(-1,-98,-99))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-1,-98,-99))$summary, caption = "Summary")
#Continuous_summary(var = TILDA_w1_oth_fam$tp037, missing_values = NA)
ggplot(TILDA_w1_oth_fam, aes(x=factor(tp037))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("How many living brothers do you have?") + ylab("Frequency")


```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if SOCpalive in {1,2,3} or tp036>0 or tp037>0 then 1`
* `if SOCpalive=0 and tp036=tp037=0 then 0`
* `-99 Refused into 997`
* `-98 Don't know into 998`
* `NA into 999`
* `tp036 and tp037 were not asked IF TP001=5 AND TP006<2008 (MOTHER DIED MORE THAN TWO YEARS AGO) AND TP007=5 AND TP012 <2008 (FATHER DIED MORE THAN TWO YEARS AGO). Then we recode tp036=-1 and tp037=-1 into 996`


**R script:**

```{r harmo1, echo=TRUE}
TILDA_ds_w1 <- tibble(id=TILDA_w1_oth_fam$id)

TILDA_w1_oth_fam$SOCpalive <- car::recode(as.vector(TILDA_w1_oth_fam$SOCpalive), "NA='-999'")
TILDA_w1_oth_fam$tp036 <- car::recode(as.vector(TILDA_w1_oth_fam$tp036), "NA='-999'")
TILDA_w1_oth_fam$tp037 <- car::recode(as.vector(TILDA_w1_oth_fam$tp037), "NA='-999'")

TILDA_ds_w1$oth_fam <- c(NA) 
for(i in 1:dim(TILDA_w1_oth_fam)[1]){
  if( TILDA_w1_oth_fam$SOCpalive[i] %in% c(1,2,3) | TILDA_w1_oth_fam$tp036[i] > 0 | TILDA_w1_oth_fam$tp037[i] > 0 ){
    TILDA_ds_w1$oth_fam[i] = 1 } 
  else if( TILDA_w1_oth_fam$SOCpalive[i] == 0 & TILDA_w1_oth_fam$tp036[i] == 0 & TILDA_w1_oth_fam$tp037[i] == 0 ){
    TILDA_ds_w1$oth_fam[i] = 0 }
  else if(TILDA_w1_oth_fam$tp036[i] == -1 & TILDA_w1_oth_fam$tp037[i] == -1 ){
    TILDA_ds_w1$oth_fam[i] = 996 }
  else if( TILDA_w1_oth_fam$tp036[i] == -99 | TILDA_w1_oth_fam$tp037[i] == -99 ){
    TILDA_ds_w1$oth_fam[i] = 997 }
  else if( TILDA_w1_oth_fam$tp036[i] == -98 | TILDA_w1_oth_fam$tp037[i] == -98 ){
    TILDA_ds_w1$oth_fam[i] = 998 }
}

TILDA_ds_w1$oth_fam <- car::recode(as.vector(TILDA_ds_w1$oth_fam), "NA='999'")
TILDA_ds_w1$oth_fam <- labelled(TILDA_ds_w1$oth_fam, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <- TILDA_ds_w1$oth_fam
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = TILDA_ds_w1$oth_fam, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(TILDA_ds_w1, aes(x=factor(oth_fam))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Has other family members?") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}

```



### Wave 2
Not found.


```{r save, echo=FALSE}
oth_fam <- TILDA_ds_w1
save(oth_fam, file = "../RData/w1/oth_fam.RData")
rm(oth_fam)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
