---
title: "Contacts with friends"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/cont_frDS.Rmd'}
```


```{r global, echo=F}
source('../../_DS_Rmd/cont_frDS.R')
```

<!-- ########################################################## --> 

# Data process

## Ireland

### Wave 1 

#### Study-specific variable description


| **Name** |`SCQsocact13`|
|-|-|
| **Label** |`Visit, phone family, friends`|
| **Table name** |`TILDA-AMF-v16`|
| **Categories** |`1 = Daily, almost daily`<br/>`2 = Once a week, +`<br/>`3 = Twice a month, +`<br/>`4 = Once a month`<br/>`5 = Every few months`<br/>`6 = Once or twice a year`<br/>`7 = < once a year`<br/>`8 = Never`|
| **Missings** |`-878 = Adjacent boxes 7&8 ticked`<br/>`-867 = Adjacent boxes 6&7 ticked`<br/>`-856 = Adjacent boxes 5&6 ticked`<br/>`-845 = Adjacent boxes 4&5 ticked`<br/>`-834 = Adjacent boxes 3&4 ticked`<br/>`-823 = Adjacent boxes 2&3 ticked`<br/>`-812 = Adjacent boxes 1&2 ticked`<br/>`-99 = Refused`<br/>`-98 = Don't Know`<br/>`-9 = Refused`|
| **Description** |  |

```{r assign1, echo=F}
opal.assign.table.tibble(o, 'TILDA_w1_cont_fr','TILDA.TILDA-AMF-v16',variables=list('SCQsocact13'), missings = TRUE)
TILDA_w1_cont_fr <- opal.execute(o,'TILDA_w1_cont_fr')
```

```{r local1, echo=F}
vari <- TILDA_w1_cont_fr$SCQsocact13
kable(Categorical_summary(vari, missing_values = c(-878,-867,-856,-845,-834,-823,-812,-99,-98,-9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-878,-867,-856,-845,-834,-823,-812,-99,-98,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-878,-867,-856,-845,-834,-823,-812,-99,-98,-9))[2], caption = "Type of missing")
ggplot(TILDA_w1_cont_fr, aes(x=factor(SCQsocact13))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Visit, phone family, friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1:4 into 1`
* `5:8 into 0`
* `-99 Refused into 997`
* `-98 Don't know into 998`
* `NA into 999`


**R script:**

```{r harmo1, echo=TRUE}
TILDA_ds_w1 <- tibble(id=TILDA_w1_cont_fr$id)
TILDA_ds_w1$cont_fr <- car::recode(as.vector(TILDA_w1_cont_fr$SCQsocact13), "1:4='1'; -834:-812=1; 5:8='0'; -99='997'; -98='998'; -878:-845='0'; NA='999'")
TILDA_ds_w1$cont_fr <- labelled(TILDA_ds_w1$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <- TILDA_ds_w1$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(TILDA_ds_w1, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
```


### Wave 2

#### Study-specific variable description

| **Name** |`SCQSocAct13`|
|-|-|
| **Label** |`Visit to or from family or friends, either in person or talking on`|
| **Table name** |`TILDA-AMF-v23`|
| **Categories** |`1 = Daily, almost daily`<br/>`2 = Once a week, or more`<br/>`3 = Twice a month, or more`<br/>`4 = about once a month`<br/>`5 = Every few months`<br/>`6 = about once or twice a year`<br/>`7 = less than once a year`<br/>`8 = Never`|
| **Missings** |`-878 = Adjacent boxes 7&8 ticked`<br/>`-867 = Adjacent boxes 6&7 ticked`<br/>`-856 = Adjacent boxes 5&6 ticked`<br/>`-845 = Adjacent boxes 4&5 ticked`<br/>`-834 = Adjacent boxes 3&4 ticked`<br/>`-823 = Adjacent boxes 2&3 ticked`<br/>`-812 = Adjacent boxes 1&2 ticked`<br/>`-99 = No Response`|
| **Description** |  |


```{r assign2, echo=F}
opal.assign.table.tibble(o, 'TILDA_w2_cont_fr','TILDA.TILDA-AMF-v23',variables=list('SCQSocAct13'), missings = TRUE)
TILDA_w2_cont_fr <- opal.execute(o,'TILDA_w2_cont_fr')
```

```{r local2, echo=F}
vari <-  TILDA_w2_cont_fr$SCQSocAct13
kable(Categorical_summary(vari, missing_values = c(-878,-867,-856,-845,-834,-823,-812,-99))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-878,-867,-856,-845,-834,-823,-812,-99))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-878,-867,-856,-845,-834,-823,-812,-99))[2], caption = "Type of missing")
ggplot(TILDA_w2_cont_fr, aes(x=factor(SCQSocAct13))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Visit to or from family or friends, either in person or talking on") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1:4 into 1`
* `5:8 into 0`
* `-99 into 995`
* `NA into 999`


**R script:**

```{r harmo2, echo=TRUE}
TILDA_ds_w2 <- tibble(id=TILDA_w2_cont_fr$id)
TILDA_ds_w2$cont_fr <- car::recode(as.vector(TILDA_w2_cont_fr$SCQSocAct13), "1:4='1'; 5:8='0';-99='995'; NA='999'")
TILDA_ds_w2$cont_fr <- labelled(TILDA_ds_w2$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}
vari <- TILDA_ds_w2$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(TILDA_ds_w2, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
AfterH <- table(TILDA_ds_w2$cont_fr)
BeforeH <- table(TILDA_w2_cont_fr$SCQSocAct13, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(6:9)])
BeforeH1[[2]] <- sum(BeforeH[c(2:5)])
BeforeH1[[3]] <- BeforeH[[1]]
BeforeH1[[4]] <- BeforeH[[10]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","-99->995","NA->999")

kable(C)
```


## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.


```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


tilda.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"))

# Consider only harmonised waves
l.hds <- lapply(tilda.cw, function(wname) if(exists(paste0("TILDA_ds_",wname[1]))){wname = list(get(paste0("TILDA_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],sapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```





# Quality estimation


<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
