---
title: "Contacts with friends"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/cont_frDS.Rmd'}
```


```{r global, echo=F}
source('../../_DS_Rmd/cont_frDS.R')
```

<!-- ########################################################## --> 

# Data process

## Ireland

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `SCQsocact13`
* Label: `Visit, phone family, friends`
* Categories:
    + `1 = Daily, almost daily`
    + `2 = Once a week, +`
    + `3 = Twice a month, +`
    + `4 = Once a month`
    + `5 = Every few months`
    + `6 = Once or twice a year`
    + `7 = < once a year`
    + `8 = Never`
* Missings:
    + `-878 = Adjacent boxes 7&8 ticked` 
    + `-867 = Adjacent boxes 6&7 ticked` 
    + `-856 = Adjacent boxes 5&6 ticked` 
    + `-845 = Adjacent boxes 4&5 ticked` 
    + `-834 = Adjacent boxes 3&4 ticked` 
    + `-823 = Adjacent boxes 2&3 ticked` 
    + `-812 = Adjacent boxes 1&2 ticked`
    + `-99 = Refused`
    + `-98 = Don't Know`
    + `-9 = Refused`

* Description: 
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'TILDA_w1_cont_fr','TILDA.TILDA-AMF-v16',variables=list('SCQsocact13'), missings = TRUE)
```

```{r local1, echo=F}
TILDA_w1_cont_fr <- opal.execute(o,'TILDA_w1_cont_fr')
vari <- TILDA_w1_cont_fr$SCQsocact13
kable(Categorical_summary(vari, missing_values = c(-878,-867,-856,-845,-834,-823,-812,-99,-98,-9))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-878,-867,-856,-845,-834,-823,-812,-99,-98,-9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-878,-867,-856,-845,-834,-823,-812,-99,-98,-9))[2], caption = "Type of missing")
ggplot(TILDA_w1_cont_fr, aes(x=factor(SCQsocact13))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Visit, phone family, friends") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1:4 into 1`
* `5:8 into 0`
* `-99 Refused into 997`
* `-98 Don't know into 998`
* `NA into 999`


**R script:**

```{r harmo1, echo=TRUE}
TILDA_ds_w1 <- tibble(id=TILDA_w1_cont_fr$id)
TILDA_ds_w1$cont_fr <- car::recode(as.vector(TILDA_w1_cont_fr$SCQsocact13), "1:4='1'; -834:-812=1; 5:8='0'; -99='997'; -98='998'; -878:-845='0'; NA='999'")
TILDA_ds_w1$cont_fr <- labelled(TILDA_ds_w1$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <- TILDA_ds_w1$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(TILDA_ds_w1, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
```


### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `SCQSocAct13`
* Label: `Visit to or from family or friends, either in person or talking on`
* Categories:
    + `1 = Daily, almost daily` 
    + `2 = Once a week, or more` 
    + `3 = Twice a month, or more`
    + `4 = about once a month`
    + `5 = Every few months` 
    + `6 = about once or twice a year`
    + `7 = less than once a year`
    + `8 = Never`
* Missings:
    + `-878 = Adjacent boxes 7&8 ticked` 
    + `-867 = Adjacent boxes 6&7 ticked` 
    + `-856 = Adjacent boxes 5&6 ticked` 
    + `-845 = Adjacent boxes 4&5 ticked` 
    + `-834 = Adjacent boxes 3&4 ticked` 
    + `-823 = Adjacent boxes 2&3 ticked` 
    + `-812 = Adjacent boxes 1&2 ticked`
    + `-99 = No Response`


* Description: 
```{r assign2, echo=F}
opal.assign.table.tibble(o, 'TILDA_w2_cont_fr','TILDA.TILDA-AMF-v23',variables=list('SCQSocAct13'), missings = TRUE)
```

```{r local2, echo=F}
TILDA_w2_cont_fr <- opal.execute(o,'TILDA_w2_cont_fr')
vari <-  TILDA_w2_cont_fr$SCQSocAct13
kable(Categorical_summary(vari, missing_values = c(-878,-867,-856,-845,-834,-823,-812,-99))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-878,-867,-856,-845,-834,-823,-812,-99))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-878,-867,-856,-845,-834,-823,-812,-99))[2], caption = "Type of missing")
ggplot(TILDA_w2_cont_fr, aes(x=factor(SCQSocAct13))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Visit to or from family or friends, either in person or talking on") + ylab("Frequency")
```

#### Harmonisation algorithm
To recode the harmonize variable from the study-specific variable it has to be recoded as follows:  

* `1:4 into 1`
* `5:8 into 0`
* `-99 into 995`
* `NA into 999`


**R script:**

```{r harmo2, echo=TRUE}
TILDA_ds_w2 <- tibble(id=TILDA_w2_cont_fr$id)
TILDA_ds_w2$cont_fr <- car::recode(as.vector(TILDA_w2_cont_fr$SCQSocAct13), "1:4='1'; 5:8='0';-99='995'; NA='999'")
TILDA_ds_w2$cont_fr <- labelled(TILDA_ds_w2$cont_fr, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}
vari <- TILDA_ds_w2$cont_fr
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(TILDA_ds_w2, aes(x=factor(cont_fr))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Are the contacts with friends/neighbours frequent") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
AfterH <- table(TILDA_ds_w2$cont_fr)
BeforeH <- table(TILDA_w2_cont_fr$SCQSocAct13, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- sum(BeforeH[c(6:9)])
BeforeH1[[2]] <- sum(BeforeH[c(2:5)])
BeforeH1[[3]] <- BeforeH[[1]]
BeforeH1[[4]] <- BeforeH[[10]]
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("0","1","-99->995","NA->999")

kable(C)
```


```{r save, echo=FALSE}
cont_fr <- TILDA_ds_w1
save(cont_fr, file = "../RData/w1/cont_fr.RData")
rm(cont_fr)

cont_fr <- TILDA_ds_w2
save(cont_fr, file = "../RData/w2/cont_fr.RData")
rm(cont_fr)
```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```

