---
title: "Instrumental support"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/inst_supDS.Rmd'}
```


```{r global, echo=F}
source('../../_DS_Rmd/inst_supDS.R')
```

<!-- ########################################################## --> 

# Data process

## Ireland

### Wave 1 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:


* Name: `tc023`
* Label: `In the last 2 years, did your relatives give you (or your spouse/partner) any help with things like practical household helps or help with paperwork?`
* Categories:
    + `1 = Yes`
    + `5 = No`
* Missings:
    + `99 = Refused`
    + `98 = Don't know`
    + `-1 `
    
* Name: `tc027`
* Label: `In the last 2 years, did your neighbours or friends give you (or your spouse/partner) any kind of help such as household help or help with paperwork?`
* Categories:
    + `1 = Yes`
    + `5 = No`
* Missings:
    + `99 = Refused`
    + `98 = Don't know`
    + `-1 `
    
    
* Description: 
```{r assign1, echo=F}
opal.assign.table.tibble(o, 'TILDA_w1_inst_sup','TILDA.TILDA-AMF-v16', variables=list('tc023','tc027'), missings = TRUE)
```

```{r local1, echo=F}
TILDA_w1_inst_sup <- opal.execute(o,'TILDA_w1_inst_sup')
vari <- TILDA_w1_inst_sup$tc023
kable(Categorical_summary(vari, missing_values = c(99,98,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(99,98,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(99,98,-1))[2], caption = "Type of missing")
#Categorical_summary(var = TILDA_w1_inst_sup$tc023, missing_values = NA)
ggplot(TILDA_w1_inst_sup, aes(x=factor(tc023))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Practical household help from relatives?") + ylab("Frequency")

vari <- TILDA_w1_inst_sup$tc027
kable(Categorical_summary(vari, missing_values = c(99,98,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(99,98,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(99,98,-1))[2], caption = "Type of missing")
#Categorical_summary(var = TILDA_w1_inst_sup$tc027, missing_values = NA)
ggplot(TILDA_w1_inst_sup, aes(x=factor(tc027))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Practical household help from neighbours or friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 then 1`
* `if all are equal 5 then 0`
* `99 Refused into 997`
* `98 Don't know into 998`
* `NA into 999`

**R script:**

```{r harmo1, echo=TRUE}
TILDA_ds_w1 <- tibble(id=TILDA_w1_inst_sup$id)

TILDA_w1_inst_sup$tc023 <- car::recode(as.vector(TILDA_w1_inst_sup$tc023), "NA='-999'")
TILDA_w1_inst_sup$tc027 <- car::recode(as.vector(TILDA_w1_inst_sup$tc027), "NA='-999'")

TILDA_ds_w1$inst_sup <- c(NA)
for(i in 1:dim(TILDA_w1_inst_sup)[1]){
  if( TILDA_w1_inst_sup$tc023[i] == 1 | TILDA_w1_inst_sup$tc027[i] == 1 ) {
    TILDA_ds_w1$inst_sup[i] = 1 }
  else if( TILDA_w1_inst_sup$tc023[i] == 5 & TILDA_w1_inst_sup$tc027[i] == 5 ) {
    TILDA_ds_w1$inst_sup[i] = 0 }
  else if( TILDA_w1_inst_sup$tc023[i] == 99 | TILDA_w1_inst_sup$tc027[i] == 99 ) {
    TILDA_ds_w1$inst_sup[i] = 997 }
  else if( TILDA_w1_inst_sup$tc023[i] == 98 | TILDA_w1_inst_sup$tc027[i] == 98 ) {
    TILDA_ds_w1$inst_sup[i] = 998 }
}

TILDA_ds_w1$inst_sup <- car::recode(as.vector(TILDA_ds_w1$inst_sup), "NA='999'")
TILDA_ds_w1$inst_sup <- labelled(TILDA_ds_w1$inst_sup, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=F}
vari <- TILDA_ds_w1$inst_sup
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = TILDA_ds_w1$inst_sup, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(TILDA_ds_w1, aes(x=factor(inst_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Instrumental support (practical help) from people outside the household (relatives/friends/neighbours)") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
AfterH <- table(TILDA_ds_w1$inst_sup)
BeforeH <- table(TILDA_w1_inst_sup$tc023, TILDA_w1_inst_sup$tc027, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH['5','5']
BeforeH1[[2]] <- sum(sum(BeforeH['1',]), sum(BeforeH[c('-1','5','99'),'1']))
BeforeH1[[3]] <- sum(BeforeH['99',c('-1','5','98','99')])
BeforeH1[[4]] <- sum(BeforeH['5','98'])
BeforeH1[[5]] <- BeforeH['-1','-1']
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("5->0","1->1","99->997", "98->998","NA->999")
kable(C)
```



### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `tc023`
* Label: `In the last 2 years, did your relatives give you (or your spouse/partner) any help with things like practical household helps or help with paperwork?`
* Categories:
    + `1 = Yes`
    + `5 = No`
* Missings:
    + `99 = Refused`
    + `98 = Don't know`
    
* Name: `tc027`
* Label: `In the last 2 years, did your neighbours or friends give you (or your spouse/partner) any kind of help such as household help or help with paperwork?`
* Categories:
    + `1 = Yes`
    + `5 = No`
* Missings:
    + `99 = Refused`
    + `98 = Don't know`
    
    
* Description: 
```{r assign2, echo=F}
opal.assign.table.tibble(o, 'TILDA_w2_inst_sup','TILDA.TILDA-AMF-v23',variables=list('tc023','tc027'), missings = TRUE)
```

```{r local2, echo=F}
TILDA_w2_inst_sup <- opal.execute(o,'TILDA_w2_inst_sup')
vari <- TILDA_w2_inst_sup$tc023
kable(Categorical_summary(vari, missing_values = c(99,98))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(99,98))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(99,98))[2], caption = "Type of missing")
#Categorical_summary(var = TILDA_w2_inst_sup$tc023, missing_values = NA)
ggplot(TILDA_w2_inst_sup, aes(x=factor(tc023))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Practical household help from relatives?") + ylab("Frequency")

vari <- TILDA_w2_inst_sup$tc027
kable(Categorical_summary(vari, missing_values = c(99,98))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(99,98))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(99,98))[2], caption = "Type of missing")
#Categorical_summary(var = TILDA_w2_inst_sup$tc027, missing_values = NA)
ggplot(TILDA_w2_inst_sup, aes(x=factor(tc027))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Practical household help from neighbours or friends?") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `if any equals 1 then 1`
* `if all are equal 5 then 0`
* `99 Refused into 997`
* `98 Don't know into 998`
* `NA into 999`

**R script:**

```{r harmo2, echo=TRUE}
TILDA_ds_w2 <- tibble(id=TILDA_w2_inst_sup$id)

TILDA_w2_inst_sup$tc023 <- car::recode(as.vector(TILDA_w2_inst_sup$tc023), "NA='-999'")
TILDA_w2_inst_sup$tc027 <- car::recode(as.vector(TILDA_w2_inst_sup$tc027), "NA='-999'")

TILDA_ds_w2$inst_sup <- c(NA)
for(i in 1:dim(TILDA_w2_inst_sup)[1]){
  if( TILDA_w2_inst_sup$tc023[i] == 1 | TILDA_w2_inst_sup$tc027[i] == 1 ) {
    TILDA_ds_w2$inst_sup[i] = 1 }
  else if( TILDA_w2_inst_sup$tc023[i] == 5 & TILDA_w2_inst_sup$tc027[i] == 5 ) {
    TILDA_ds_w2$inst_sup[i] = 0 }
  else if( TILDA_w2_inst_sup$tc023[i] == 99 | TILDA_w2_inst_sup$tc027[i] == 99 ) {
    TILDA_ds_w2$inst_sup[i] = 997 }
  else if( TILDA_w2_inst_sup$tc023[i] == 98 | TILDA_w2_inst_sup$tc027[i] == 98 ) {
    TILDA_ds_w2$inst_sup[i] = 998 }
}

TILDA_ds_w2$inst_sup <- car::recode(as.vector(TILDA_ds_w2$inst_sup), "NA='999'")
TILDA_ds_w2$inst_sup <- labelled(TILDA_ds_w2$inst_sup, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Don't answer"=995,  "Not attempt/not done/not yet recorded"=994, "Disable to measure"=993, "Impute"=992, "CAPI/interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=F}
vari <- TILDA_ds_w2$inst_sup
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3]) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = TILDA_ds_w2$inst_sup, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(TILDA_ds_w2, aes(x=factor(inst_sup))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Instrumental support (practical help) from people outside the household (relatives/friends/neighbours)") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
AfterH <- table(TILDA_ds_w2$inst_sup)
BeforeH <- table(TILDA_w2_inst_sup$tc023, TILDA_w2_inst_sup$tc027, useNA='ifany')
BeforeH1 <- c(NA)
BeforeH1[[1]] <- BeforeH['5','5']
BeforeH1[[2]] <- sum(sum(BeforeH['1',]), sum(BeforeH[c('-1','5','98'),'1']))
BeforeH1[[3]] <- sum(BeforeH['98','98'])
BeforeH1[[4]] <- BeforeH['-1','-1']
C <- rbind(BeforeH1,AfterH)
colnames(C) <- c("5->0","1->1", "98->998","NA->999")
kable(C)
```

```{r save, echo=FALSE}
inst_sup <- TILDA_ds_w1
save(inst_sup, file = "../RData/w1/inst_sup.RData")
rm(inst_sup)

inst_sup <- TILDA_ds_w2
save(inst_sup, file = "../RData/w2/inst_sup.RData")
rm(inst_sup)


```

# Quality estimation
```{r closeRsession, echo=FALSE} 
opal.logout(o)
```



