---
title: "Height"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `height`
* Variable label: `height of the participant`
* Variable description: `Anthropometric measure for height should be measured in centimeters`
* Domain: `Physical measures`
* Value type: `continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

### HAPIEE - Poland - Baseline 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `h5`
* Label: `Height in cm (self-reported)`
* Type of variable: `countinous`
* Name: `e52`
* Label: `Height (cm) (examination)`
* Type of variable: `countinous`

```{r assign_po1}
opal.assign.table.tibble(o, 'HAPIEE_pol_w1_heig','HAPIEE.Po_baseline_etic',
                         variables=list('h5', 'e52'), missings = TRUE)
```

```{r local_po1}
HAPIEE_pol_w1_heig <- opal.execute(o,'HAPIEE_pol_w1_heig')

Continuous_summary(var = HAPIEE_pol_w1_heig$h5, missing_values = NA)
ggplot(HAPIEE_pol_w1_heig, aes(h5)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")

Continuous_summary(var = HAPIEE_pol_w1_heig$e52, missing_values = NA)
ggplot(HAPIEE_pol_w1_heig, aes(e52)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

The variable 'h5' has values 0 that are going to be consider as mistakes and they will be recoded as 999. 

#### Harmonisation algorithm
The harmonized variable is a comvination of the two study-specific variables 'e52'(examination) and 'h5'(self-reported). The missing values in the medical examination variable are going to be complemented with the self-reported variable and the missings values are going to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_po1}
miss <- which(is.na(HAPIEE_pol_w1_heig$e52))
HAPIEE_pol_w1_heig$heig <- car::recode(HAPIEE_pol_w1_heig$e52, "NA=999")
HAPIEE_pol_w1_heig$h5_2 <- car::recode(HAPIEE_pol_w1_heig$h5, "NA=999; 0=999")
HAPIEE_pol_w1_heig$heig[miss] <- HAPIEE_pol_w1_heig$h5_2[miss]
Continuous_summary(var = HAPIEE_pol_w1_heig$heig, missing_values = c(999))

HAPIEE_pol_ds_w1 <- tibble(id=HAPIEE_pol_w1_heig$id)
HAPIEE_pol_ds_w1$height <- car::recode(HAPIEE_pol_w1_heig$heig, "NA=999")
HAPIEE_pol_ds_w1$height <- labelled(HAPIEE_pol_ds_w1$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_po1}
Continuous_summary(var = HAPIEE_pol_ds_w1$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_pol_ds_w1, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,250) 
```

#### Validation
```{r crosstabulation_po1}
```

#### Quality estimation
[Comments on the quality of the new harmonised variable.]

#### Import to OPAL
```{r importOPAL_po1}
#val_labels(HAPIEE_pol_ds_w1) <- NULL
#opal.assign.data(o, 'HAPIEE_pol_ds_w1', HAPIEE_pol_ds_w1)
#opal.symbol_import(o,'HAPIEE_pol_ds_w1', project='_Athlos_Harm_Dataset')
height <- HAPIEE_pol_ds_w1
save(height, file = "../RData/pol_w1/height.RData")
rm(height)
```





### HAPIEE - Poland - Reexamination

There is no variable





### HAPIEE - Czech Republic - Baseline

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `h5`
* Label: `Height in cm (self-reported)`
* Type of variable: `countinous`
* Name: `e52`
* Label: `Height (cm) (examination)`
* Type of variable: `countinous`

```{r assign_cz1}
opal.assign.table.tibble(o, 'HAPIEE_cz_w1_heig','HAPIEE.Cz_baseline_etic',
                         variables=list('h5', 'e52'), missings = TRUE)
```

```{r local_cz1}
HAPIEE_cz_w1_heig <- opal.execute(o,'HAPIEE_cz_w1_heig')
Continuous_summary(var = HAPIEE_cz_w1_heig$h5, missing_values =c(999))
ggplot(HAPIEE_cz_w1_heig, aes(h5)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")

Continuous_summary(var = HAPIEE_cz_w1_heig$e52, missing_values = NA)
ggplot(HAPIEE_cz_w1_heig, aes(e52)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

The variable 'h5' have a value 999 that is consider as a mistake and it will be recoded as missing.

#### Harmonisation algorithm
The harmonized variable is a comvination of the two study-specific variables 'e52'(examination) and 'h5'(self-reported). The missing values in the medical examination variable are going to be complemented with the self-reported variable and the missings values are going to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_cz1}
miss <- which(is.na(HAPIEE_cz_w1_heig$e52))
HAPIEE_cz_w1_heig$heig <- car::recode(HAPIEE_cz_w1_heig$e52, "NA=999")
HAPIEE_cz_w1_heig$h5_2 <- car::recode(HAPIEE_cz_w1_heig$h5, "NA=999")
HAPIEE_cz_w1_heig$heig[miss] <- HAPIEE_cz_w1_heig$h5_2[miss]
Continuous_summary(var = HAPIEE_cz_w1_heig$heig, missing_values = c(999))

HAPIEE_cz_ds_w1 <- tibble(id=HAPIEE_cz_w1_heig$id)
HAPIEE_cz_ds_w1$height <- car::recode(HAPIEE_cz_w1_heig$heig, "NA=999")
HAPIEE_cz_ds_w1$height <- labelled(HAPIEE_cz_ds_w1$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_cz1}
Continuous_summary(var = HAPIEE_cz_ds_w1$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_cz_ds_w1, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,250) 
```

#### Validation
```{r crosstabulation_cz1}
```

#### Quality estimation
[Comments on the quality of the new harmonised variable.]

#### Import to OPAL
```{r importOPAL_cz1}
#val_labels(HAPIEE_cz_ds_w1) <- NULL
#opal.assign.data(o, 'HAPIEE_cz_ds_w1', HAPIEE_cz_ds_w1)
#opal.symbol_import(o,'HAPIEE_cz_ds_w1', project='_Athlos_Harm_Dataset')
height <- HAPIEE_cz_ds_w1
save(height, file = "../RData/cz_w1/height.RData")
rm(height)
```








### HAPIEE - Czech Republic - Reexamination

There is no variable.






### HAPIEE - Lithuania - Baseline

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `h5`
* Label: `Height in cm (self-reported)`
* Type of variable: `countinous`
* Name: `e52`
* Label: `Height (cm) (examination)`
* Type of variable: `countinous`

```{r assign_li1}
opal.assign.table.tibble(o, 'HAPIEE_li_w1_heig','HAPIEE.Li_baseline_etic',
                         variables=list('h5', 'e52'), missings = TRUE)
```

```{r local_li1}
HAPIEE_li_w1_heig <- opal.execute(o,'HAPIEE_li_w1_heig')

Continuous_summary(var = HAPIEE_li_w1_heig$h5, missing_values = NA)
ggplot(HAPIEE_li_w1_heig, aes(h5)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")

Continuous_summary(var = HAPIEE_li_w1_heig$e52, missing_values = NA)
ggplot(HAPIEE_li_w1_heig, aes(e52)) + geom_histogram(stat="count", fill="steelblue") + xlab("Height") + ylab("Frequency")
```

The variable h5 has the values 100000 that is going to be considered as a mistake and it will be recoded as 999. 


#### Harmonisation algorithm
The harmonized variable is a comvination of the two study-specific variables 'e52'(examination) and 'h5'(self-reported). The missing values in the medical examination variable are going to be complemented with the self-reported variable and the missings values are going to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_li1}
miss <- which(is.na(HAPIEE_li_w1_heig$e52))
HAPIEE_li_w1_heig$heig <- car::recode(HAPIEE_li_w1_heig$e52, "NA=999")
HAPIEE_li_w1_heig$h5_2 <- car::recode(HAPIEE_li_w1_heig$h5, "NA=999; 0=999")
HAPIEE_li_w1_heig$heig[miss] <- HAPIEE_li_w1_heig$h5_2[miss]
Continuous_summary(var = HAPIEE_li_w1_heig$heig, missing_values = c(999))

HAPIEE_li_ds_w1 <- tibble(id=HAPIEE_li_w1_heig$id)
HAPIEE_li_ds_w1$height <- car::recode(HAPIEE_li_w1_heig$heig, "NA=999")
HAPIEE_li_ds_w1$height <- labelled(HAPIEE_li_ds_w1$height, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_li1}
Continuous_summary(var = HAPIEE_li_ds_w1$height, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_li_ds_w1, aes(height)) + geom_histogram(stat="count", fill="steelblue") + xlab("height") + ylab("Frequency") + xlim(100,250)
```


#### Validation
```{r crosstabulation_li1}
```

#### Quality estimation
No comments.

#### Import to OPAL
```{r importOPAL_li1}
#val_labels(HAPIEE_li_ds_w1) <- NULL
#opal.assign.data(o, 'HAPIEE_li_ds_w1', HAPIEE_li_ds_w1)
#opal.symbol_import(o,'HAPIEE_li_ds_w1', project='_Athlos_Harm_Dataset')
height <- HAPIEE_li_ds_w1
save(height, file = "../RData/li_w1/height.RData")
rm(height)
```


```{r closeRsession, echo=FALSE}
opal.logout(o)
```



