---
title: "Hip"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `hip`
* Variable label: `hip circumference of the participant`
* Variable description: `Anthropomeric measure for hip circumference should be measured in centimeters`
* Domain: `Physical measures`
* Value type: `continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process


### HAPIEE - Poland - Baseline 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `e62`
* Label: `Hip (cm)` 
* Type of variable: `countinous`

```{r assign_po1}
opal.assign.table.tibble(o, 'HAPIEE_pol_w1_hip','HAPIEE.Po_baseline_etic',
                         variables=list('e62'), missings = TRUE)
```

```{r local_po1}
HAPIEE_pol_w1_hip <- opal.execute(o,'HAPIEE_pol_w1_hip')
Continuous_summary(var = HAPIEE_pol_w1_hip$e62, missing_values = NA)
ggplot(HAPIEE_pol_w1_hip, aes(e62)) + geom_histogram(stat="count", fill="steelblue") + xlab("Hip") + ylab("Frequency")
```


#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_po1}
HAPIEE_pol_ds_w1 <- tibble(id=HAPIEE_pol_w1_hip$id)
HAPIEE_pol_ds_w1$hip <- car::recode(HAPIEE_pol_w1_hip$e62, "NA=999")
HAPIEE_pol_ds_w1$hip <- labelled(HAPIEE_pol_ds_w1$hip, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_po1}
Continuous_summary(var = HAPIEE_pol_ds_w1$hip, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_pol_ds_w1, aes(hip)) + geom_histogram(stat="count", fill="steelblue") + xlab("Hip") + ylab("Frequency") + xlim(35,165) 
```

#### Validation
```{r crosstabulation_po1}
```

#### Quality estimation
[Comments on the quality of the new harmonised variable.]

#### Import to OPAL
```{r importOPAL_po1}
#val_labels(HAPIEE_pol_ds_w1) <- NULL
#opal.assign.data(o, 'HAPIEE_pol_ds_w1', HAPIEE_pol_ds_w1)
#opal.symbol_import(o,'HAPIEE_pol_ds_w1', project='_Athlos_Harm_Dataset')
hip <- HAPIEE_pol_ds_w1
save(hip, file = "../RData/pol_w1/hip.RData")
rm(hip)
```





### HAPIEE - Poland - Reexamination

There is no variable


### HAPIEE - Czech Republic - Baseline

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `e62`
* Label: `Hip (cm)` 
* Type of variable: `countinous`

```{r assign_cz1}
opal.assign.table.tibble(o, 'HAPIEE_cz_w1_hip','HAPIEE.Cz_baseline_etic',
                         variables=list('e62'), missings = TRUE)
```

```{r local_cz1}
HAPIEE_cz_w1_hip <- opal.execute(o,'HAPIEE_cz_w1_hip')
Continuous_summary(var = HAPIEE_cz_w1_hip$e62, missing_values = NA)
ggplot(HAPIEE_cz_w1_hip, aes(e62)) + geom_histogram(stat="count", fill="steelblue") + xlab("Hip") + ylab("Frequency")
```

There is a value 999.9 that is going to be considered as missing and will be recoded as 999 (missing). 

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_cz1}
HAPIEE_cz_ds_w1 <- tibble(id=HAPIEE_cz_w1_hip$id)
HAPIEE_cz_ds_w1$hip <- car::recode(HAPIEE_cz_w1_hip$e62, "NA=999; 999.9=999")
HAPIEE_cz_ds_w1$hip <- labelled(HAPIEE_cz_ds_w1$hip, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_cz1}
Continuous_summary(var = HAPIEE_cz_ds_w1$hip, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_cz_ds_w1, aes(hip)) + geom_histogram(stat="count", fill="steelblue") + xlab("Hip") + ylab("Frequency") + xlim(35,165) 
```

#### Validation
```{r crosstabulation_cz1}
```

#### Quality estimation
[Comments on the quality of the new harmonised variable.]

#### Import to OPAL
```{r importOPAL_cz1}
#val_labels(HAPIEE_cz_ds_w1) <- NULL
#opal.assign.data(o, 'HAPIEE_cz_ds_w1', HAPIEE_cz_ds_w1)
#opal.symbol_import(o,'HAPIEE_cz_ds_w1', project='_Athlos_Harm_Dataset')
hip <- HAPIEE_cz_ds_w1
save(hip, file = "../RData/cz_w1/hip.RData")
rm(hip)
```









### HAPIEE - Czech Republic - Reexamination

There is no variable.






### HAPIEE - Lithuania - Baseline

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `e62`
* Label: `Hip (cm)` 
* Type of variable: `countinous`

```{r assign_li1}
opal.assign.table.tibble(o, 'HAPIEE_li_w1_hip','HAPIEE.Li_baseline_etic',
                         variables=list('e62'), missings = TRUE)
```

```{r local_li1}
HAPIEE_li_w1_hip <- opal.execute(o,'HAPIEE_li_w1_hip')
Continuous_summary(var = HAPIEE_li_w1_hip$e62, missing_values = NA)
ggplot(HAPIEE_li_w1_hip, aes(e62)) + geom_histogram(stat="count", fill="steelblue") + xlab("Hip") + ylab("Frequency")
```

There is a value 999.9 that is going to be considered as missing and will be recoded as 999 (missing). 

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_li1}
HAPIEE_li_ds_w1 <- tibble(id=HAPIEE_li_w1_hip$id)
HAPIEE_li_ds_w1$hip <- car::recode(HAPIEE_li_w1_hip$e62, "NA=999; 999.9=999")
HAPIEE_li_ds_w1$hip <- labelled(HAPIEE_li_ds_w1$hip, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_li1}
Continuous_summary(var = HAPIEE_li_ds_w1$hip, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(HAPIEE_li_ds_w1, aes(hip)) + geom_histogram(stat="count", fill="steelblue") + xlab("Hip") + ylab("Frequency") + xlim(35,165) 
```

#### Validation
```{r crosstabulation_li1}
```


#### Quality estimation
No coments.




#### Import to OPAL
```{r importOPAL_li1}
#val_labels(HAPIEE_li_ds_w1) <- NULL
#opal.assign.data(o, 'HAPIEE_li_ds_w1', HAPIEE_li_ds_w1)
#opal.symbol_import(o,'HAPIEE_li_ds_w1', project='_Athlos_Harm_Dataset')
hip <- HAPIEE_li_ds_w1
save(hip, file = "../RData/li_w1/hip.RData")
rm(hip)
```







```{r closeRsession, echo=FALSE}
opal.logout(o)
```
