---
title: "Hearing a conversation"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `hearing_conv`
* Variable label: `Difficulty for hearing what is said in a conversation`
* Variable description: `It measures if the participant experiences some difficulty (including total disability) for following a conversation  (i.e., if there is a background noise, or several people talking) or not, using a hearing aid as usual.`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## South Africa

### Wave 1 

##### Study-specific variable description



| **Name** | `q2052`|
|-|-|
| **Label** | `q2052: in the last 30 days, how much difficulty in conversation` |
| **Table name** | `southAfricaINDdata` |
| **Categories** | `1 = none; 2 = mild; 3 = moderate; 4 = severe; 5 = extreme` |
| **Missings** | `NA` |
| **Description** |  |



```{r assign Africa w1, echo=F}
opal.assign.table.tibble(o, 'SAGE_Africa_w1_hearing_conv','SAGE.southAfricaINDdata', variables=list('q2052'), missings = TRUE)
```

```{r local Africa w1, echo=F}
SAGE_Africa_w1_hearing_conv <- opal.execute(o,'SAGE_Africa_w1_hearing_conv')
vari <- SAGE_Africa_w1_hearing_conv$q2052
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "q2052")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(SAGE_Africa_w1_hearing_conv, aes(x=factor(q2052))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - Difficulties") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2,3,4,5 into 0`
* `NA into 999`

**R script:**

```{r harmo Africa w1}
SAGE_SA_ds_w1 <- tibble(id=SAGE_Africa_w1_hearing_conv$id)
SAGE_SA_ds_w1$hearing_conv <- car::recode(SAGE_Africa_w1_hearing_conv$q2052, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0'; NA = '999' ")
SAGE_SA_ds_w1$hearing_conv <- labelled(SAGE_SA_ds_w1$hearing_conv, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Africa w1, echo=F}
vari <- SAGE_SA_ds_w1$hearing_conv
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "hearing_conv")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SAGE_SA_ds_w1, aes(x=factor(hearing_conv))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Hearing - Difficulties") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Africa w1, echo=F}
AfterH <- table(SAGE_SA_ds_w1$hearing_conv)
X<-table(SAGE_Africa_w1_hearing_conv$q2052)
BeforeH <- c(sum(X[2:5]),X[1],sum(is.na(SAGE_Africa_w1_hearing_conv$q2052)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1","NA->999") 
kable(C)
```




```{r importOPAL Africa w1, echo=FALSE}
label(SAGE_SA_ds_w1$hearing_conv) <- "Difficulty for hearing what is said in a conversation"
#opal.assign.data(o, 'SAGE_SA_ds_w1', SAGE_SA_ds_w1)
#opal.symbol_import(o,'SAGE_SA_ds_w1', project='_Athlos_Harm_Dataset')
hearing_conv <- SAGE_SA_ds_w1
save(hearing_conv, file = "../RData/SA_w1/hearing_conv.RData")

SAGE_m_SA_ds_w1 <- SAGE_SA_ds_w1
SAGE_m_SA_ds_w1$hearing_conv <- car::recode(SAGE_m_SA_ds_w1$hearing_conv, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_m_SA_ds_w1', SAGE_m_SA_ds_w1)
#opal.symbol_import(o,'SAGE_m_SA_ds_w1', project='_Athlos_Harm_Dataset')
```


## Ghana

### Wave 1

Not found.

## China

### Wave 1

Not found.

## India

### Wave 1

Not found.

## Russia

### Wave 1

Not found.

## Mexico

### Wave 1

Not found.


# Quality estimation

Actually, the variable `q2052` appears in the datasets of all the countries, but full of missing values. 




```{r closeRsession, echo=FALSE}
opal.logout(o)
```
