---
title: "Mobility - Lifting or carrying weights"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `mob_lift`
* Variable label: `Difficulty for lifting or carrying weights`
* Variable description: `Difficulty for lifting or carrying weights`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process



## China

### Wave 1 

#### Study-specific variable description




| **Name** | `q2040`|
|-|-|
| **Label** | `q2040: carrying` |
| **Table name** |`chinaINDData`|
| **Categories** |`1 = none; 2 = mild; 3 = moderate; 4 = severe; 5 = extreme`|
| **Missings** |`8 = don't know; 9 = not applicable; NA`|
| **Description** |  |


```{r assign China w1, echo=F}
opal.assign.table.tibble(o, 'SAGE_China_w1_mob_lift','SAGE.chinaINDData', variables=list('q2040'), missings = TRUE)
```

```{r local China w1, echo=F}
SAGE_China_w1_mob_lift <- opal.execute(o,'SAGE_China_w1_mob_lift')
vari <- SAGE_China_w1_mob_lift$q2040
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = "q2040")
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
ggplot(SAGE_China_w1_mob_lift, aes(x=factor(q2040))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Lifting") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2,3,4,5 into 0`
* `8 Don't know into 998`
* `9 Not applicable into 996`
* `NA into 999`

**R script:**
```{r harmo China w1}
SAGE_china_ds_w1 <- tibble(id=SAGE_China_w1_mob_lift$id)
SAGE_china_ds_w1$mob_lift <- car::recode(SAGE_China_w1_mob_lift$q2040, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0';9 = '996';8 = '998'; NA = '999' ")
SAGE_china_ds_w1$mob_lift <- labelled(SAGE_china_ds_w1$mob_lift, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript China w1, echo=F}
vari <- SAGE_china_ds_w1$mob_lift
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_lift")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SAGE_china_ds_w1, aes(x=factor(mob_lift))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Lifting") + ylab("Frequency")
```

#### Validation
```{r crosstabulation China w1, echo=F}
AfterH <- table(SAGE_china_ds_w1$mob_lift)
X<-table(SAGE_China_w1_mob_lift$q2040)
BeforeH <- c(sum(X[2:5]),X[c(1,7,6)],sum(is.na(SAGE_China_w1_mob_lift$q2040)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1","9->996","8->998","NA->999")
kable(C)
```






```{r importOPAL China w1, echo=FALSE}

label(SAGE_china_ds_w1$mob_lift) <- "Difficulty for lifting or carrying weights"
#opal.assign.data(o, 'SAGE_china_ds_w1', SAGE_china_ds_w1)
#opal.symbol_import(o,'SAGE_china_ds_w1', project='_Athlos_Harm_Dataset')
mob_lift <- SAGE_china_ds_w1
save(mob_lift, file = "../RData/china_w1/mob_lift.RData")

SAGE_m_china_ds_w1 <- SAGE_china_ds_w1
SAGE_m_china_ds_w1$mob_lift <- car::recode(SAGE_m_china_ds_w1$mob_lift, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_m_china_ds_w1', SAGE_m_china_ds_w1)
#opal.symbol_import(o,'SAGE_m_china_ds_w1', project='_Athlos_Harm_Dataset')
```



## Ghana

### Wave 1 

#### Study-specific variable description




| **Name** | `q2040`|
|-|-|
| **Label** | `q2040: carrying` |
| **Table name** |`ghanaINDData`|
| **Categories** |`1 = none; 2 = mild; 3 = moderate; 4 = severe; 5 = extreme`|
| **Missings** |`8 = don't know; 9 = not applicable; NA`|
| **Description** |  |


```{r assign Ghana w1, echo=F}
opal.assign.table.tibble(o, 'SAGE_Ghana_w1_mob_lift','SAGE.ghanaINDData', variables=list('q2040'), missings = TRUE)
```

```{r local Ghana w1, echo=F}
SAGE_Ghana_w1_mob_lift <- opal.execute(o,'SAGE_Ghana_w1_mob_lift')
vari <- SAGE_Ghana_w1_mob_lift$q2040
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = "q2040")
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
ggplot(SAGE_Ghana_w1_mob_lift, aes(x=factor(q2040))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Lifting") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2,3,4,5 into 0`
* `8 Don't know into 998`
* `9 Not applicable into 996`
* `NA into 999`

**R script:**
```{r harmo Ghana w1}
SAGE_ghana_ds_w1 <- tibble(id=SAGE_Ghana_w1_mob_lift$id)
SAGE_ghana_ds_w1$mob_lift <- car::recode(SAGE_Ghana_w1_mob_lift$q2040, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0';9 = '996';8 = '998'; NA = '999' ")
SAGE_ghana_ds_w1$mob_lift <- labelled(SAGE_ghana_ds_w1$mob_lift, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Ghana w1, echo=F}
vari <- SAGE_ghana_ds_w1$mob_lift
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_lift")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SAGE_ghana_ds_w1, aes(x=factor(mob_lift))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Lifting") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Ghana w1, echo=F}
AfterH <- table(SAGE_ghana_ds_w1$mob_lift)
X<-table(SAGE_Ghana_w1_mob_lift$q2040)
BeforeH <- c(sum(X[2:5]),X[c(1,7,6)],sum(is.na(SAGE_Ghana_w1_mob_lift$q2040)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1","9->996","8->998","NA->999")
kable(C)
```






```{r importOPAL Ghana w1, echo=FALSE}

label(SAGE_ghana_ds_w1$mob_lift) <- "Difficulty for lifting or carrying weights"
#opal.assign.data(o, 'SAGE_ghana_ds_w1', SAGE_ghana_ds_w1)
#opal.symbol_import(o,'SAGE_ghana_ds_w1', project='_Athlos_Harm_Dataset')
mob_lift <- SAGE_ghana_ds_w1
save(mob_lift, file = "../RData/ghana_w1/mob_lift.RData")

SAGE_m_ghana_ds_w1 <- SAGE_ghana_ds_w1
SAGE_m_ghana_ds_w1$mob_lift <- car::recode(SAGE_m_ghana_ds_w1$mob_lift, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_m_ghana_ds_w1', SAGE_m_ghana_ds_w1)
#opal.symbol_import(o,'SAGE_m_ghana_ds_w1', project='_Athlos_Harm_Dataset')
```



## India

### Wave 1 

#### Study-specific variable description




| **Name** | `q2040`|
|-|-|
| **Label** | `q2040: carrying` |
| **Table name** |`indiaINDData`|
| **Categories** |`1 = none; 2 = mild; 3 = moderate; 4 = severe; 5 = extreme`|
| **Missings** |`9 = not applicable; NA`|
| **Description** |  |



```{r assign India w1, echo=F}
opal.assign.table.tibble(o, 'SAGE_India_w1_mob_lift','SAGE.indiaINDData', variables=list('q2040'), missings = TRUE)
```

```{r local India w1, echo=F}
SAGE_India_w1_mob_lift <- opal.execute(o,'SAGE_India_w1_mob_lift')
vari <- SAGE_India_w1_mob_lift$q2040
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "q2040")
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
ggplot(SAGE_India_w1_mob_lift, aes(x=factor(q2040))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Lifting") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2,3,4,5 into 0`
* `9 Not applicable into 996`
* `NA into 999`

**R script:**
```{r harmo India w1}
SAGE_india_ds_w1 <- tibble(id=SAGE_India_w1_mob_lift$id)
SAGE_india_ds_w1$mob_lift <- car::recode(SAGE_India_w1_mob_lift$q2040, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0';9 = '996'; NA = '999' ")
SAGE_india_ds_w1$mob_lift <- labelled(SAGE_india_ds_w1$mob_lift, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript India w1, echo=F}
vari <- SAGE_india_ds_w1$mob_lift
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_lift")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SAGE_india_ds_w1, aes(x=factor(mob_lift))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Lifting") + ylab("Frequency")
```

#### Validation
```{r crosstabulation India w1, echo=F}
AfterH <- table(SAGE_india_ds_w1$mob_lift)
X<-table(SAGE_India_w1_mob_lift$q2040)
BeforeH <- c(sum(X[2:5]),X[c(1,6)],sum(is.na(SAGE_India_w1_mob_lift$q2040)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1","9->996","NA->999")
kable(C)
```






```{r importOPAL India w1, echo=FALSE}

label(SAGE_india_ds_w1$mob_lift) <- "Difficulty for lifting or carrying weights"
#opal.assign.data(o, 'SAGE_india_ds_w1', SAGE_india_ds_w1)
#opal.symbol_import(o,'SAGE_india_ds_w1', project='_Athlos_Harm_Dataset')
mob_lift <- SAGE_india_ds_w1
save(mob_lift, file = "../RData/india_w1/mob_lift.RData")

SAGE_m_india_ds_w1 <- SAGE_india_ds_w1
SAGE_m_india_ds_w1$mob_lift <- car::recode(SAGE_m_india_ds_w1$mob_lift, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_m_india_ds_w1', SAGE_m_india_ds_w1)
#opal.symbol_import(o,'SAGE_m_india_ds_w1', project='_Athlos_Harm_Dataset')
```



## Mexico

### Wave 1 

#### Study-specific variable description




| **Name** | `q2040`|
|-|-|
| **Label** | `q2040: carrying` |
| **Table name** |`mexicoINDdata`|
| **Categories** |`1 = none; 2 = mild; 3 = moderate; 4 = severe; 5 = extreme`|
| **Missings** |`9 = not applicable; NA`|
| **Description** |  |



```{r assign Mexico w1, echo=F}
opal.assign.table.tibble(o, 'SAGE_Mexico_w1_mob_lift','SAGE.mexicoINDdata', variables=list('q2040'), missings = TRUE)
```

```{r local Mexico w1, echo=F}
SAGE_Mexico_w1_mob_lift <- opal.execute(o,'SAGE_Mexico_w1_mob_lift')
vari <- SAGE_Mexico_w1_mob_lift$q2040
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "q2040")
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
ggplot(SAGE_Mexico_w1_mob_lift, aes(x=factor(q2040))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Lifting") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2,3,4,5 into 0`
* `9 Not applicable into 996`
* `NA into 999`

**R script:**
```{r harmo Mexico w1}
SAGE_mexico_ds_w1 <- tibble(id=SAGE_Mexico_w1_mob_lift$id)
SAGE_mexico_ds_w1$mob_lift <- car::recode(SAGE_Mexico_w1_mob_lift$q2040, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0';9 = '996';8 = '998'; NA = '999' ")
SAGE_mexico_ds_w1$mob_lift <- labelled(SAGE_mexico_ds_w1$mob_lift, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Mexico w1, echo=F}
vari <- SAGE_mexico_ds_w1$mob_lift
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_lift")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SAGE_mexico_ds_w1, aes(x=factor(mob_lift))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Lifting") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Mexico w1, echo=F}
AfterH <- table(SAGE_mexico_ds_w1$mob_lift)
X<-table(SAGE_Mexico_w1_mob_lift$q2040)
BeforeH <- c(sum(X[2:5]),X[c(1,6)],sum(is.na(SAGE_Mexico_w1_mob_lift$q2040)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1","9->996","NA->999")
kable(C)
```






```{r importOPAL Mexico w1, echo=FALSE}

label(SAGE_mexico_ds_w1$mob_lift) <- "Difficulty for lifting or carrying weights"
#opal.assign.data(o, 'SAGE_mexico_ds_w1', SAGE_mexico_ds_w1)
#opal.symbol_import(o,'SAGE_mexico_ds_w1', project='_Athlos_Harm_Dataset')
mob_lift <- SAGE_mexico_ds_w1
save(mob_lift, file = "../RData/mexico_w1/mob_lift.RData")

SAGE_m_mexico_ds_w1 <- SAGE_mexico_ds_w1
SAGE_m_mexico_ds_w1$mob_lift <- car::recode(SAGE_m_mexico_ds_w1$mob_lift, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_m_mexico_ds_w1', SAGE_m_mexico_ds_w1)
#opal.symbol_import(o,'SAGE_m_mexico_ds_w1', project='_Athlos_Harm_Dataset')
```



## Russian Federation

### Wave 1 

#### Study-specific variable description




| **Name** | `q2040`|
|-|-|
| **Label** | `q2040: carrying` |
| **Table name** |`russiaINDdata`|
| **Categories** |`1 = none; 2 = mild; 3 = moderate; 4 = severe; 5 = extreme`|
| **Missings** |`9 = not applicable; NA`|
| **Description** |  |



```{r assign Russia w1, echo=F}
opal.assign.table.tibble(o, 'SAGE_Russia_w1_mob_lift','SAGE.russiaINDdata', variables=list('q2040'), missings = TRUE)
```

```{r local Russia w1, echo=F}
SAGE_Russia_w1_mob_lift <- opal.execute(o,'SAGE_Russia_w1_mob_lift')
vari <- SAGE_Russia_w1_mob_lift$q2040
kable(Categorical_summary(vari, missing_values = c(9))[3], caption = "q2040")
kable(Categorical_summary(vari, missing_values = c(9))[1], caption = "Category")
ggplot(SAGE_Russia_w1_mob_lift, aes(x=factor(q2040))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Lifting") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2,3,4,5 into 0`
* `9 Not applicable into 996`
* `NA into 999`

**R script:**
```{r harmo Russia w1}
SAGE_russia_ds_w1 <- tibble(id=SAGE_Russia_w1_mob_lift$id)
SAGE_russia_ds_w1$mob_lift <- car::recode(SAGE_Russia_w1_mob_lift$q2040, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0';9 = '996';8 = '998'; NA = '999' ")
SAGE_russia_ds_w1$mob_lift <- labelled(SAGE_russia_ds_w1$mob_lift, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Russia w1, echo=F}
vari <- SAGE_russia_ds_w1$mob_lift
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_lift")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SAGE_russia_ds_w1, aes(x=factor(mob_lift))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Lifting") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Russia w1, echo=F}
AfterH <- table(SAGE_russia_ds_w1$mob_lift)
X<-table(SAGE_Russia_w1_mob_lift$q2040)
BeforeH <- c(sum(X[2:5]),X[c(1,6)],sum(is.na(SAGE_Russia_w1_mob_lift$q2040)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1","9->996","NA->999")
kable(C)
```






```{r importOPAL Russia w1, echo=FALSE}

label(SAGE_russia_ds_w1$mob_lift) <- "Difficulty for lifting or carrying weights"
#opal.assign.data(o, 'SAGE_russia_ds_w1', SAGE_russia_ds_w1)
#opal.symbol_import(o,'SAGE_russia_ds_w1', project='_Athlos_Harm_Dataset')
mob_lift <- SAGE_russia_ds_w1
save(mob_lift, file = "../RData/russia_w1/mob_lift.RData")

SAGE_m_russia_ds_w1 <- SAGE_russia_ds_w1
SAGE_m_russia_ds_w1$mob_lift <- car::recode(SAGE_m_russia_ds_w1$mob_lift, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_m_russia_ds_w1', SAGE_m_russia_ds_w1)
#opal.symbol_import(o,'SAGE_m_russia_ds_w1', project='_Athlos_Harm_Dataset')
```



## South Africa

### Wave 1 

#### Study-specific variable description




| **Name** | `q2040`|
|-|-|
| **Label** | `q2040: carrying` |
| **Table name** |`southAfricaINDdata`|
| **Categories** |`1 = none; 2 = mild; 3 = moderate; 4 = severe; 5 = extreme`|
| **Missings** |`8 = don't know; 9 = not applicable; NA`|
| **Description** |  |



```{r assign Africa w1, echo=F}
opal.assign.table.tibble(o, 'SAGE_Africa_w1_mob_lift','SAGE.southAfricaINDdata', variables=list('q2040'), missings = TRUE)
```

```{r local Africa w1, echo=F}
SAGE_Africa_w1_mob_lift <- opal.execute(o,'SAGE_Africa_w1_mob_lift')
vari <- SAGE_Africa_w1_mob_lift$q2040
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = "q2040")
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
ggplot(SAGE_Africa_w1_mob_lift, aes(x=factor(q2040))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Lifting") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2,3,4,5 into 0`
* `8 Don't know into 998`
* `9 Not applicable into 996`
* `NA into 999`

**R script:**
```{r harmo Africa w1}
SAGE_SA_ds_w1 <- tibble(id=SAGE_Africa_w1_mob_lift$id)
SAGE_SA_ds_w1$mob_lift <- car::recode(SAGE_Africa_w1_mob_lift$q2040, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0';9 = '996';8 = '998'; NA = '999' ")
SAGE_SA_ds_w1$mob_lift <- labelled(SAGE_SA_ds_w1$mob_lift, labels = c(Yes=0, No=1,Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript Africa w1, echo=F}
vari <- SAGE_SA_ds_w1$mob_lift
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "mob_lift")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SAGE_SA_ds_w1, aes(x=factor(mob_lift))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Mobility - Lifting") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Africa w1, echo=F}
AfterH <- table(SAGE_SA_ds_w1$mob_lift)
X<-table(SAGE_Africa_w1_mob_lift$q2040)
BeforeH <- c(sum(X[2:5]),X[c(1,7,6)],sum(is.na(SAGE_Africa_w1_mob_lift$q2040)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1","9->996","8->998","NA->999")
kable(C)
```






```{r importOPAL Africa w1, echo=FALSE}

label(SAGE_SA_ds_w1$mob_lift) <- "Difficulty for lifting or carrying weights"
#opal.assign.data(o, 'SAGE_SA_ds_w1', SAGE_SA_ds_w1)
#opal.symbol_import(o,'SAGE_SA_ds_w1', project='_Athlos_Harm_Dataset')
mob_lift <- SAGE_SA_ds_w1
save(mob_lift, file = "../RData/SA_w1/mob_lift.RData")

SAGE_m_SA_ds_w1 <- SAGE_SA_ds_w1
SAGE_m_SA_ds_w1$mob_lift <- car::recode(SAGE_m_SA_ds_w1$mob_lift, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_m_SA_ds_w1', SAGE_m_SA_ds_w1)
#opal.symbol_import(o,'SAGE_m_SA_ds_w1', project='_Athlos_Harm_Dataset')
```


# Quality estimation
No comments.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
