---
title: "IADL - Getting out of home"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE,  echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_laia.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `iadl_outhome`
* Variable label: `IADL - Difficulties for getting out of home`
* Variable description: `IADL - Difficulties for getting out of home`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Yes
1        | No

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "IADL - Difficulties for getting out of home"
```


# Data process

## China

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `q2046`
* Label: `q2046: going out`
* Categories:
   + `1 = none` 
   + `2 = mild`
   + `3 = moderate`
   + `4 = severe`
   + `5 = extreme`
* Missings
   + `8 = don't know`
   + `9 = not applicable`
   + `NA`


```{r assign China w1, echo=FALSE}
opal.assign.table.tibble(o, 'SAGE_China_w1_iadl_outhome','SAGE.chinaINDData', variables=list('q2046'), missings = TRUE)
SAGE_China_w1_iadl_outhome <- opal.execute(o,'SAGE_China_w1_iadl_outhome')
```

```{r local China w1, echo=FALSE}
vari <- SAGE_China_w1_iadl_outhome$q2046
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(SAGE_China_w1_iadl_outhome, aes(x=factor(q2046))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2,3,4,5 into 0`
* `8 Don't know into 998`
* `9 Not applicable into 994`
* `NA into 999`

**R script:**

```{r harmo China w1}
SAGE_china_ds_w1 <- tibble(id=SAGE_China_w1_iadl_outhome$id)
SAGE_china_ds_w1$iadl_outhome <- recode(SAGE_China_w1_iadl_outhome$q2046, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0';9 = '994';8 = '998'; NA = '999' ")
SAGE_china_ds_w1$iadl_outhome <- labelled(SAGE_china_ds_w1$iadl_outhome, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript China w1, echo=FALSE}
vari <- SAGE_china_ds_w1$iadl_outhome
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SAGE_china_ds_w1, aes(x=factor(iadl_outhome))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Validation
```{r crosstabulation China w1, echo=FALSE}
AfterH <- table(SAGE_china_ds_w1$iadl_outhome)
X<-table(SAGE_China_w1_iadl_outhome$q2046)
BeforeH <- c(sum(X[2:5]),X[c(1,7,6)],sum(is.na(SAGE_China_w1_iadl_outhome$q2046)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1","9->994","8->998","NA->999")
kable(C)
```

```{r importOPAL China w1, echo=FALSE}
label(SAGE_china_ds_w1$iadl_outhome) <- ds_label
iadl_outhome <- SAGE_china_ds_w1
save(iadl_outhome, file = "../RData/china_w1/iadl_outhome.RData")
#opal.assign.data(o, 'SAGE_china_ds_w1', SAGE_china_ds_w1)
#opal.symbol_import(o,'SAGE_china_ds_w1', project='_Athlos_Harm_Dataset')

SAGE_m_china_ds_w1 <- SAGE_china_ds_w1
SAGE_m_china_ds_w1$iadl_outhome <- recode(SAGE_m_china_ds_w1$iadl_outhome, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_m_china_ds_w1', SAGE_m_china_ds_w1)
#opal.symbol_import(o,'SAGE_m_china_ds_w1', project='_Athlos_Harm_Dataset')
```





## Ghana

### Wave 1 

#### Study-specific variable description


The study-specific variables elected to be harmonised is:


* Name: `q2046`
* Label: `q2046: going out`
* Categories:
   + `1 = none` 
   + `2 = mild`
   + `3 = moderate`
   + `4 = severe`
   + `5 = extreme`
* Missings
   + `8 = don't know`
   + `9 = not applicable`
   + `NA`


```{r assign Ghana w1, echo=FALSE}
opal.assign.table.tibble(o, 'SAGE_Ghana_w1_iadl_outhome','SAGE.ghanaINDData', variables=list('q2046'), missings = TRUE)
SAGE_Ghana_w1_iadl_outhome <- opal.execute(o,'SAGE_Ghana_w1_iadl_outhome')
```

```{r local Ghana w1, echo=FALSE}
vari <- SAGE_Ghana_w1_iadl_outhome$q2046
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(SAGE_Ghana_w1_iadl_outhome, aes(x=factor(q2046))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2,3,4,5 into 0`
* `8 Don't know into 998`
* `9 Not applicable into 994`
* `NA into 999`

**R script:**

```{r harmo Ghana w1}
SAGE_ghana_ds_w1 <- tibble(id=SAGE_Ghana_w1_iadl_outhome$id)
SAGE_ghana_ds_w1$iadl_outhome <- recode(SAGE_Ghana_w1_iadl_outhome$q2046, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0';9 = '994';8 = '998'; NA = '999' ")
SAGE_ghana_ds_w1$iadl_outhome <- labelled(SAGE_ghana_ds_w1$iadl_outhome, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript Ghana w1, echo=FALSE}
vari <- SAGE_ghana_ds_w1$iadl_outhome
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SAGE_ghana_ds_w1, aes(x=factor(iadl_outhome))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Ghana w1, echo=FALSE}
AfterH <- table(SAGE_ghana_ds_w1$iadl_outhome)
X<-table(SAGE_Ghana_w1_iadl_outhome$q2046)
BeforeH <- c(sum(X[2:5]),X[c(1,7,6)],sum(is.na(SAGE_Ghana_w1_iadl_outhome$q2046)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1","9->994","8->998","NA->999")
kable(C)
```

```{r importOPAL Ghana w1, echo=FALSE}
label(SAGE_ghana_ds_w1$iadl_outhome) <- ds_label
iadl_outhome <- SAGE_ghana_ds_w1
save(iadl_outhome, file = "../RData/ghana_w1/iadl_outhome.RData")
#opal.assign.data(o, 'SAGE_ghana_ds_w1', SAGE_ghana_ds_w1)
#opal.symbol_import(o,'SAGE_ghana_ds_w1', project='_Athlos_Harm_Dataset')

SAGE_m_ghana_ds_w1 <- SAGE_ghana_ds_w1
SAGE_m_ghana_ds_w1$iadl_outhome <- recode(SAGE_m_ghana_ds_w1$iadl_outhome, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_m_ghana_ds_w1', SAGE_m_ghana_ds_w1)
#opal.symbol_import(o,'SAGE_m_ghana_ds_w1', project='_Athlos_Harm_Dataset')
```



## India

### Wave 1 

#### Study-specific variable description

The study-specific variables elected to be harmonised is:


* Name: `q2046`
* Label: `q2046: going out`
* Categories:
   + `1 = none` 
   + `2 = mild`
   + `3 = moderate`
   + `4 = severe`
   + `5 = extreme`
* Missings
   + `8 = don't know`
   + `9 = not applicable`
   + `NA`


```{r assign India w1, echo=FALSE}
opal.assign.table.tibble(o, 'SAGE_India_w1_iadl_outhome','SAGE.indiaINDData', variables=list('q2046'), missings = TRUE)
SAGE_India_w1_iadl_outhome <- opal.execute(o,'SAGE_India_w1_iadl_outhome')
```

```{r local India w1, echo=FALSE}
vari <- SAGE_India_w1_iadl_outhome$q2046
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(SAGE_India_w1_iadl_outhome, aes(x=factor(q2046))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2,3,4,5 into 0`
* `8 Don't know into 998`
* `9 Not applicable into 994`
* `NA into 999`

**R script:**

```{r harmo India w1}
SAGE_india_ds_w1 <- tibble(id=SAGE_India_w1_iadl_outhome$id)
SAGE_india_ds_w1$iadl_outhome <- recode(SAGE_India_w1_iadl_outhome$q2046, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0';9 = '994';8 = '998'; NA = '999' ")
SAGE_india_ds_w1$iadl_outhome <- labelled(SAGE_india_ds_w1$iadl_outhome, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript India w1, echo=FALSE}
vari <- SAGE_india_ds_w1$iadl_outhome
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SAGE_india_ds_w1, aes(x=factor(iadl_outhome))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Validation
```{r crosstabulation India w1, echo=FALSE}
AfterH <- table(SAGE_india_ds_w1$iadl_outhome)
X<-table(SAGE_India_w1_iadl_outhome$q2046)
BeforeH <- c(sum(X[2:5]),X[c(1,7,6)],sum(is.na(SAGE_India_w1_iadl_outhome$q2046)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1","8->998","9->994","NA->999")
kable(C)
```

```{r importOPAL India w1, echo=FALSE}
label(SAGE_india_ds_w1$iadl_outhome) <- ds_label
iadl_outhome <- SAGE_india_ds_w1
save(iadl_outhome, file = "../RData/india_w1/iadl_outhome.RData")
#opal.assign.data(o, 'SAGE_india_ds_w1', SAGE_india_ds_w1)
#opal.symbol_import(o,'SAGE_india_ds_w1', project='_Athlos_Harm_Dataset')

SAGE_m_india_ds_w1 <- SAGE_india_ds_w1
SAGE_m_india_ds_w1$iadl_outhome <- recode(SAGE_m_india_ds_w1$iadl_outhome, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_m_india_ds_w1', SAGE_m_india_ds_w1)
#opal.symbol_import(o,'SAGE_m_india_ds_w1', project='_Athlos_Harm_Dataset')
```



## Mexico

### Wave 1 

#### Study-specific variable description


The study-specific variables elected to be harmonised is:


* Name: `q2046`
* Label: `q2046: going out`
* Categories:
   + `1 = none` 
   + `2 = mild`
   + `3 = moderate`
   + `4 = severe`
   + `5 = extreme`
* Missings
   + `9 = not applicable`
   + `NA`


```{r assign Mexico w1, echo=FALSE}
opal.assign.table.tibble(o, 'SAGE_Mexico_w1_iadl_outhome','SAGE.mexicoINDdata', variables=list('q2046'), missings = TRUE)
SAGE_Mexico_w1_iadl_outhome <- opal.execute(o,'SAGE_Mexico_w1_iadl_outhome')
```

```{r local Mexico w1, echo=FALSE}
vari <- SAGE_Mexico_w1_iadl_outhome$q2046
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(SAGE_Mexico_w1_iadl_outhome, aes(x=factor(q2046))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2,3,4,5 into 0`
* `9 Not applicable into 994`
* `NA into 999`

**R script:**

```{r harmo Mexico w1}
SAGE_mexico_ds_w1 <- tibble(id=SAGE_Mexico_w1_iadl_outhome$id)
SAGE_mexico_ds_w1$iadl_outhome <- recode(SAGE_Mexico_w1_iadl_outhome$q2046, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0';9 = '994';8 = '998'; NA = '999' ")
SAGE_mexico_ds_w1$iadl_outhome <- labelled(SAGE_mexico_ds_w1$iadl_outhome, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript Mexico w1, echo=FALSE}
vari <- SAGE_mexico_ds_w1$iadl_outhome
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SAGE_mexico_ds_w1, aes(x=factor(iadl_outhome))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Mexico w1, echo=FALSE}
AfterH <- table(SAGE_mexico_ds_w1$iadl_outhome)
X<-table(SAGE_Mexico_w1_iadl_outhome$q2046)
BeforeH <- c(sum(X[2:5]),X[c(1,6)],sum(is.na(SAGE_Mexico_w1_iadl_outhome$q2046)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1","9->994","NA->999")
kable(C)
```

```{r importOPAL Mexico w1, echo=FALSE}
label(SAGE_mexico_ds_w1$iadl_outhome) <- ds_label
iadl_outhome <- SAGE_mexico_ds_w1
save(iadl_outhome, file = "../RData/mexico_w1/iadl_outhome.RData")
#opal.assign.data(o, 'SAGE_mexico_ds_w1', SAGE_mexico_ds_w1)
#opal.symbol_import(o,'SAGE_mexico_ds_w1', project='_Athlos_Harm_Dataset')

SAGE_m_mexico_ds_w1 <- SAGE_mexico_ds_w1
SAGE_m_mexico_ds_w1$iadl_outhome <- recode(SAGE_m_mexico_ds_w1$iadl_outhome, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_m_mexico_ds_w1', SAGE_m_mexico_ds_w1)
#opal.symbol_import(o,'SAGE_m_mexico_ds_w1', project='_Athlos_Harm_Dataset')
```



## Russian Federation

### Wave 1 

#### Study-specific variable description


The study-specific variables elected to be harmonised is:


* Name: `q2046`
* Label: `q2046: going out`
* Categories:
   + `1 = none` 
   + `2 = mild`
   + `3 = moderate`
   + `4 = severe`
   + `5 = extreme`
* Missings
   + `8 = don't know`
   + `9 = not applicable`
   + `NA`


```{r assign Russia w1, echo=FALSE}
opal.assign.table.tibble(o, 'SAGE_Russia_w1_iadl_outhome','SAGE.russiaINDdata', variables=list('q2046'), missings = TRUE)
SAGE_Russia_w1_iadl_outhome <- opal.execute(o,'SAGE_Russia_w1_iadl_outhome')
```

```{r local Russia w1, echo=FALSE}
vari <- SAGE_Russia_w1_iadl_outhome$q2046
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(SAGE_Russia_w1_iadl_outhome, aes(x=factor(q2046))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2,3,4,5 into 0`
* `8 Don't know into 998`
* `9 Not applicable into 994`
* `NA into 999`

**R script:**

```{r harmo Russia w1}
SAGE_russia_ds_w1 <- tibble(id=SAGE_Russia_w1_iadl_outhome$id)
SAGE_russia_ds_w1$iadl_outhome <- recode(SAGE_Russia_w1_iadl_outhome$q2046, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0';9 = '994';8 = '998'; NA = '999' ")
SAGE_russia_ds_w1$iadl_outhome <- labelled(SAGE_russia_ds_w1$iadl_outhome, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript Russia w1, echo=FALSE}
vari <- SAGE_russia_ds_w1$iadl_outhome
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SAGE_russia_ds_w1, aes(x=factor(iadl_outhome))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Russia w1, echo=FALSE}
AfterH <- table(SAGE_russia_ds_w1$iadl_outhome)
X<-table(SAGE_Russia_w1_iadl_outhome$q2046)
BeforeH <- c(sum(X[2:5]),X[c(1,7,6)],sum(is.na(SAGE_Russia_w1_iadl_outhome$q2046)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1","9->994","8->998","NA->999")
kable(C)
```

```{r importOPAL Russia w1, echo=FALSE}
label(SAGE_russia_ds_w1$iadl_outhome) <- ds_label
iadl_outhome <- SAGE_russia_ds_w1
save(iadl_outhome, file = "../RData/russia_w1/iadl_outhome.RData")
#opal.assign.data(o, 'SAGE_russia_ds_w1', SAGE_russia_ds_w1)
#opal.symbol_import(o,'SAGE_russia_ds_w1', project='_Athlos_Harm_Dataset')

SAGE_m_russia_ds_w1 <- SAGE_russia_ds_w1
SAGE_m_russia_ds_w1$iadl_outhome <- recode(SAGE_m_russia_ds_w1$iadl_outhome, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_m_russia_ds_w1', SAGE_m_russia_ds_w1)
#opal.symbol_import(o,'SAGE_m_russia_ds_w1', project='_Athlos_Harm_Dataset')
```




## South Africa

### Wave 1 

#### Study-specific variable description


The study-specific variables elected to be harmonised is:


* Name: `q2046`
* Label: `q2046: going out`
* Categories:
   + `1 = none` 
   + `2 = mild`
   + `3 = moderate`
   + `4 = severe`
   + `5 = extreme`
* Missings
   + `8 = don't know`
   + `9 = not applicable`
   + `NA`


```{r assign Africa w1, echo=FALSE}
opal.assign.table.tibble(o, 'SAGE_Africa_w1_iadl_outhome','SAGE.southAfricaINDdata', variables=list('q2046'), missings = TRUE)
SAGE_Africa_w1_iadl_outhome <- opal.execute(o,'SAGE_Africa_w1_iadl_outhome')
```

```{r local Africa w1, echo=FALSE}
vari <- SAGE_Africa_w1_iadl_outhome$q2046
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(8,9))[2], caption = "Type of missing")
ggplot(SAGE_Africa_w1_iadl_outhome, aes(x=factor(q2046))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1 into 1` 
* `2,3,4,5 into 0`
* `8 Don't know into 998`
* `9 Not applicable into 994`
* `NA into 999`

**R script:**

```{r harmo Africa w1}
SAGE_SA_ds_w1 <- tibble(id=SAGE_Africa_w1_iadl_outhome$id)
SAGE_SA_ds_w1$iadl_outhome <- recode(SAGE_Africa_w1_iadl_outhome$q2046, "1 = '1';2 = '0';3 = '0';4 = '0';5 = '0';9 = '994';8 = '998'; NA = '999' ")
SAGE_SA_ds_w1$iadl_outhome <- labelled(SAGE_SA_ds_w1$iadl_outhome, labels = c("Yes"=0, "No"=1,"Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript Africa w1, echo=FALSE}
vari <- SAGE_SA_ds_w1$iadl_outhome
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SAGE_SA_ds_w1, aes(x=factor(iadl_outhome))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("IADL - Getting out of home") + ylab("Frequency")
```

#### Validation
```{r crosstabulation Africa w1, echo=FALSE}
AfterH <- table(SAGE_SA_ds_w1$iadl_outhome)
X<-table(SAGE_Africa_w1_iadl_outhome$q2046)
BeforeH <- c(sum(X[2:5]),X[c(1,7,6)],sum(is.na(SAGE_Africa_w1_iadl_outhome$q2046)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2,3,4,5->0","1","9->994","8->998","NA->999")
kable(C)
```

```{r importOPAL Africa w1, echo=FALSE}
label(SAGE_SA_ds_w1$iadl_outhome) <- ds_label
iadl_outhome <- SAGE_SA_ds_w1
save(iadl_outhome, file = "../RData/SA_w1/iadl_outhome.RData")
#opal.assign.data(o, 'SAGE_SA_ds_w1', SAGE_SA_ds_w1)
#opal.symbol_import(o,'SAGE_SA_ds_w1', project='_Athlos_Harm_Dataset')

SAGE_m_SA_ds_w1 <- SAGE_SA_ds_w1
SAGE_m_SA_ds_w1$iadl_outhome <- recode(SAGE_m_SA_ds_w1$iadl_outhome, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_m_SA_ds_w1', SAGE_m_SA_ds_w1)
#opal.symbol_import(o,'SAGE_m_SA_ds_w1', project='_Athlos_Harm_Dataset')
```


# Quality estimation

No comments

[Comments on the quality of the new harmonised variable. This section can be done in a later stage, once all variables are harmonised.]


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
