---
title: "Verbal fluency"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---


<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/cog_verbDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/cog_verbDS.R')
```

# Data process


## South Africa

### Wave 1 

#### Study-specific variable description

| **Name** | `q2536`|
|-|-|
| **Label** | `q2536: total score - animals	`|
| **Table name** |`southAfricaINDdata`|
| **Measures** | `Continuous Variable 0-44`|
| **Missings** | `-8 = don't know`<br/>`NA`|
| **Description** |  |

```{r assign Africa w1, echo=FALSE}
opal.assign.table.tibble(o, 'SAGE_Africa_w1_cog_verb','SAGE.southAfricaINDdata', variables=list('q2536'), missings = TRUE)
SAGE_Africa_w1_cog_verb <- opal.execute(o,'SAGE_Africa_w1_cog_verb')
```

```{r local Africa w1, echo=FALSE}
vari <- SAGE_Africa_w1_cog_verb$q2536
vbl_miss <- c(-8,-9)
kable(Continuous_summary(var = vari, missing_values = vbl_miss)[3], caption = attr(vari,"spss::shortName"))
kable(Continuous_summary(vari, missing_values = c(-8,-9))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-8,-9))$summary, caption = "Summary")
ggplot(SAGE_Africa_w1_cog_verb %>% filter(!vari %in% vbl_miss), aes(x=q2536)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_verb_c` from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`
* `-9 into 996`
* `-8 into 998`

To compute the harmonized variable `cog_verb` from `cog_verb_c` it has to be recoded as follows:

* `cog_verb_c <=25% into 0`
* `cog_verb_c >25% into 1`

**R script:**

```{r harmo Africa w1}
#cog_verb_c
SAGE_ds_SA_w1 <- tibble(id=SAGE_Africa_w1_cog_verb$id)
SAGE_ds_SA_w1$cog_verb_c <- car::recode(SAGE_Africa_w1_cog_verb$q2536, "-9=996; -8=998; NA=999")
SAGE_ds_SA_w1$cog_verb_c <- labelled(SAGE_ds_SA_w1$cog_verb_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(SAGE_ds_SA_w1$cog_verb_c, "999=NA; 996=NA; 998=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

SAGE_ds_SA_w1$cog_verb <- car::recode(SAGE_ds_SA_w1[[2]], "0:Q=0; (Q+1):900=1")
SAGE_ds_SA_w1$cog_verb <- labelled(SAGE_ds_SA_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript Africa w1, echo=FALSE}
vari <- SAGE_ds_SA_w1$cog_verb_c
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_verb_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(SAGE_ds_SA_w1 %>% filter(!vari %in% miss_values_vector), aes(x=cog_verb_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- SAGE_ds_SA_w1$cog_verb
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_verb) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_SA_w1, aes(x=factor(cog_verb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation Africa w1, echo=FALSE}
Continuous <- c(sum(na.omit(SAGE_ds_SA_w1[[2]])<=Q), sum(na.omit(SAGE_ds_SA_w1[[2]])>Q & na.omit(SAGE_ds_SA_w1[[2]])<900), sum(na.omit(SAGE_ds_SA_w1[[2]])==998), sum(na.omit(SAGE_ds_SA_w1[[2]])==999))
Dichotomous <- table(SAGE_ds_SA_w1[[3]], useNA = "ifany")
C <- rbind(Continuous,Dichotomous)
colnames(C) <- c("0:8->0","9:160->1", "-8->998", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```



## China

### Wave 1 

#### Study-specific variable description


| **Name** | `q2536`|
|-|-|
| **Label** | `q2536: total score - animals	`|
| **Table name** |`chinaINDData`|
| **Measures** |`Continuous Variable 0-68`|
| **Missings** | `-9 = not applicable`<br/> `-8 = don't know`|
| **Description** |  |

```{r assign China w1, echo=FALSE}
opal.assign.table.tibble(o, 'SAGE_China_w1_cog_verb','SAGE.chinaINDData', variables=list('q2536'), missings = TRUE)
SAGE_China_w1_cog_verb <- opal.execute(o,'SAGE_China_w1_cog_verb')
```

```{r local China w1, echo=FALSE}
vari <- SAGE_China_w1_cog_verb$q2536
vbl_miss <- c(-8,-9)
kable(Continuous_summary(var = vari, missing_values = vbl_miss)[3], caption = attr(vari,"spss::shortName"))
kable(Continuous_summary(vari, missing_values = c(-8,-9))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-8,-9))$summary, caption = "Summary")
ggplot(SAGE_China_w1_cog_verb %>% filter(!vari %in% vbl_miss), aes(x=q2536)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_verb_c` from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`
* `-9 into 996`
* `-8 into 998`

To compute the harmonized variable `cog_verb` from `cog_verb_c` it has to be recoded as follows:

* `cog_verb_c <=25% into 0`
* `cog_verb_c >25% into 1`

**R script:**

```{r harmo China w1}
#cog_verb_c
SAGE_ds_china_w1 <- tibble(id=SAGE_China_w1_cog_verb$id)
SAGE_ds_china_w1$cog_verb_c <- car::recode(SAGE_China_w1_cog_verb$q2536, "-9=996; -8=998; NA=999")
SAGE_ds_china_w1$cog_verb_c <- labelled(SAGE_ds_china_w1$cog_verb_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(SAGE_ds_china_w1$cog_verb_c, "999=NA; 996=NA; 998=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

SAGE_ds_china_w1$cog_verb <- car::recode(SAGE_ds_china_w1[[2]], "0:Q=0; (Q+1):900=1")
SAGE_ds_china_w1$cog_verb <- labelled(SAGE_ds_china_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript China w1, echo=FALSE}
vari <- SAGE_ds_china_w1$cog_verb_c
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_verb_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(SAGE_ds_china_w1 %>% filter(!vari %in% miss_values_vector), aes(x=cog_verb_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- SAGE_ds_china_w1$cog_verb
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_verb) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_china_w1, aes(x=factor(cog_verb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation China w1, echo=FALSE}
Continuous <- c(sum(na.omit(SAGE_ds_china_w1[[2]])<=Q), sum(na.omit(SAGE_ds_china_w1[[2]])>Q & na.omit(SAGE_ds_china_w1[[2]])<900), sum(na.omit(SAGE_ds_china_w1[[2]])==999))
Dichotomous <- table(SAGE_ds_china_w1[[3]], useNA = "ifany")
C <- rbind(Continuous,Dichotomous)
colnames(C) <- c("0:9->0","10:160->1", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```



## Ghana

### Wave 1 

#### Study-specific variable description


| **Name** | `q2536`|
|-|-|
| **Label** | `q2536: total score - animals	`|
| **Table name** |`ghanaINDData`|
| **Measures** |`Continuous Variable 0-60`|
| **Missings** | `-9 = not applicable`<br/> `-8 = don't know`<br/>`NA`|
| **Description** |  |

```{r assign Ghana w1, echo=FALSE}
opal.assign.table.tibble(o, 'SAGE_Ghana_w1_cog_verb','SAGE.ghanaINDData', variables=list('q2536'), missings = TRUE)
SAGE_Ghana_w1_cog_verb <- opal.execute(o,'SAGE_Ghana_w1_cog_verb')
```

```{r local Ghana w1, echo=FALSE}
vari <- SAGE_Ghana_w1_cog_verb$q2536
vbl_miss <- c(-8,-9)
kable(Continuous_summary(var = vari, missing_values = vbl_miss)[3], caption = attr(vari,"spss::shortName"))
kable(Continuous_summary(vari, missing_values = c(-8,-9))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-8,-9))$summary, caption = "Summary")
ggplot(SAGE_Ghana_w1_cog_verb %>% filter(!vari %in% vbl_miss), aes(x=q2536)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_verb_c` from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`
* `-9 into 996`
* `-8 into 998`

To compute the harmonized variable `cog_verb` from `cog_verb_c` it has to be recoded as follows:

* `cog_verb_c <=25% into 0`
* `cog_verb_c >25% into 1`

**R script:**

```{r harmo Ghana w1}
#cog_verb_c
SAGE_ds_ghana_w1 <- tibble(id=SAGE_Ghana_w1_cog_verb$id)
SAGE_ds_ghana_w1$cog_verb_c <- car::recode(SAGE_Ghana_w1_cog_verb$q2536, "-9=996; -8=998; NA=999")
SAGE_ds_ghana_w1$cog_verb_c <- labelled(SAGE_ds_ghana_w1$cog_verb_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(SAGE_ds_ghana_w1$cog_verb_c, "999=NA; 996=NA; 998=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

SAGE_ds_ghana_w1$cog_verb <- car::recode(SAGE_ds_ghana_w1[[2]], "0:Q=0; (Q+1):900=1")
SAGE_ds_ghana_w1$cog_verb <- labelled(SAGE_ds_ghana_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript Ghana w1, echo=FALSE}
vari <- SAGE_ds_ghana_w1$cog_verb_c
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_verb_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(SAGE_ds_ghana_w1 %>% filter(!vari %in% miss_values_vector), aes(x=cog_verb_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- SAGE_ds_ghana_w1$cog_verb
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_verb) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_ghana_w1, aes(x=factor(cog_verb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation Ghana w1, echo=FALSE}
Continuous <- c(sum(na.omit(SAGE_ds_ghana_w1[[2]])<=Q), sum(na.omit(SAGE_ds_ghana_w1[[2]])>Q & na.omit(SAGE_ds_ghana_w1[[2]])<900), sum(na.omit(SAGE_ds_ghana_w1[[2]])==998), sum(na.omit(SAGE_ds_ghana_w1[[2]])==999))
Dichotomous <- table(SAGE_ds_ghana_w1[[3]], useNA = "ifany")
C <- rbind(Continuous,Dichotomous)
colnames(C) <- c("0:10->0","11:160->1","-8->998", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```



## India

### Wave 1 

#### Study-specific variable description


| **Name** | `q2536`|
|-|-|
| **Label** | `q2536: total score - animals	`|
| **Table name** |`indiaINDData`|
| **Measures** | `Continuous Variable 0-70`|
| **Missings** | `-9 = not applicable`<br/> `-8 = don't know`<br/>`NA`|
| **Description** |  |

```{r assign India w1, echo=FALSE}
opal.assign.table.tibble(o, 'SAGE_India_w1_cog_verb','SAGE.indiaINDData', variables=list('q2536'), missings = TRUE)
SAGE_India_w1_cog_verb <- opal.execute(o,'SAGE_India_w1_cog_verb')
```

```{r local India w1, echo=FALSE}
vari <- SAGE_India_w1_cog_verb$q2536
vbl_miss <- c(-8,-9)
kable(Continuous_summary(var = vari, missing_values = vbl_miss)[3], caption = attr(vari,"spss::shortName"))
kable(Continuous_summary(vari, missing_values = c(-8,-9))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-8,-9))$summary, caption = "Summary")
ggplot(SAGE_India_w1_cog_verb %>% filter(!vari %in% vbl_miss), aes(x=q2536)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_verb_c` from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`
* `-9 into 996`
* `-8 into 998`

To compute the harmonized variable `cog_verb` from `cog_verb_c` it has to be recoded as follows:

* `cog_verb_c <=25% into 0`
* `cog_verb_c >25% into 1`

**R script:**

```{r harmo India w1}
#cog_verb_c
SAGE_ds_india_w1 <- tibble(id=SAGE_India_w1_cog_verb$id)
SAGE_ds_india_w1$cog_verb_c <- car::recode(SAGE_India_w1_cog_verb$q2536, "-9=996; -8=998; NA=999")
SAGE_ds_india_w1$cog_verb_c <- labelled(SAGE_ds_india_w1$cog_verb_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(SAGE_ds_india_w1$cog_verb_c, "999=NA; 996=NA; 998=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

SAGE_ds_india_w1$cog_verb <- car::recode(SAGE_ds_india_w1[[2]], "0:Q=0; (Q+1):900=1")
SAGE_ds_india_w1$cog_verb <- labelled(SAGE_ds_india_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript India w1, echo=FALSE}
vari <- SAGE_ds_india_w1$cog_verb_c
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_verb_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(SAGE_ds_india_w1 %>% filter(!vari %in% miss_values_vector), aes(x=cog_verb_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- SAGE_ds_india_w1$cog_verb
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_verb) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_india_w1, aes(x=factor(cog_verb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation India w1, echo=FALSE}
Continuous <- c(sum(na.omit(SAGE_ds_india_w1[[2]])<=Q), sum(na.omit(SAGE_ds_india_w1[[2]])>Q & na.omit(SAGE_ds_india_w1[[2]])<900), sum(na.omit(SAGE_ds_india_w1[[2]])==996), sum(na.omit(SAGE_ds_india_w1[[2]])==998), sum(na.omit(SAGE_ds_india_w1[[2]])==999))
Dichotomous <- table(SAGE_ds_india_w1[[3]], useNA = "ifany")
C <- rbind(Continuous,Dichotomous)
colnames(C) <- c("0:8->0","9:160->1","-9->996", "-8->998", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```




## Mexico

### Wave 1 

#### Study-specific variable description


| **Name** | `q2536`|
|-|-|
| **Label** | `q2536: total score - animals	`|
| **Table name** |`mexicoINDdata`|
| **Measures** |`Continuous Variable 0-60`|
| **Missings** | `-9 = not applicable`<br/> `-8 = don't know`|
| **Description** |  |

```{r assign Mexico w1, echo=FALSE}
opal.assign.table.tibble(o, 'SAGE_Mexico_w1_cog_verb','SAGE.mexicoINDdata', variables=list('q2536'), missings = TRUE)
SAGE_Mexico_w1_cog_verb <- opal.execute(o,'SAGE_Mexico_w1_cog_verb')
```

```{r local Mexico w1, echo=FALSE}
vari <- SAGE_Mexico_w1_cog_verb$q2536
vbl_miss <- c(-8,-9)
kable(Continuous_summary(var = vari, missing_values = vbl_miss)[3], caption = attr(vari,"spss::shortName"))
kable(Continuous_summary(vari, missing_values = c(-8,-9))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-8,-9))$summary, caption = "Summary")
ggplot(SAGE_Mexico_w1_cog_verb %>% filter(!vari %in% vbl_miss), aes(x=q2536)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_verb_c` from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`
* `-9 into 996`
* `-8 into 998`

To compute the harmonized variable `cog_verb` from `cog_verb_c` it has to be recoded as follows:

* `cog_verb_c <=25% into 0`
* `cog_verb_c >25% into 1`

**R script:**

```{r harmo Mexico w1}
#cog_verb_c
SAGE_ds_mexico_w1 <- tibble(id=SAGE_Mexico_w1_cog_verb$id)
SAGE_ds_mexico_w1$cog_verb_c <- car::recode(SAGE_Mexico_w1_cog_verb$q2536, "-9=996; -8=998; NA=999")
SAGE_ds_mexico_w1$cog_verb_c <- labelled(SAGE_ds_mexico_w1$cog_verb_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(SAGE_ds_mexico_w1$cog_verb_c, "999=NA; 996=NA; 998=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

SAGE_ds_mexico_w1$cog_verb <- car::recode(SAGE_ds_mexico_w1[[2]], "0:Q=0; (Q+1):900=1")
SAGE_ds_mexico_w1$cog_verb <- labelled(SAGE_ds_mexico_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript Mexico w1, echo=FALSE}
vari <- SAGE_ds_mexico_w1$cog_verb_c
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_verb_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(SAGE_ds_mexico_w1 %>% filter(!vari %in% miss_values_vector), aes(x=cog_verb_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- SAGE_ds_mexico_w1$cog_verb
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_verb) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_mexico_w1, aes(x=factor(cog_verb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation Mexico w1, echo=FALSE}
Continuous <- c(sum(na.omit(SAGE_ds_mexico_w1[[2]])<=Q), sum(na.omit(SAGE_ds_mexico_w1[[2]])>Q & na.omit(SAGE_ds_mexico_w1[[2]])<900), sum(na.omit(SAGE_ds_mexico_w1[[2]])==999))
Dichotomous <- table(SAGE_ds_mexico_w1[[3]], useNA = "ifany")
C <- rbind(Continuous,Dichotomous)
colnames(C) <- c("0:11->0","12:160->1", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```





## Russian Federation

### Wave 1 

#### Study-specific variable description


| **Name** | `q2536`|
|-|-|
| **Label** | `q2536: total score - animals	`|
| **Table name** |`russiaINDdata`|
| **Measures** | `Continuous Variable 0-65`|
| **Missings** | `-9 = not applicable`<br/> `-8 = don't know`<br/>`NA`|
| **Description** |  |

```{r assign Russia w1, echo=FALSE}
opal.assign.table.tibble(o, 'SAGE_Russia_w1_cog_verb','SAGE.russiaINDdata', variables=list('q2536'), missings = TRUE)
SAGE_Russia_w1_cog_verb <- opal.execute(o,'SAGE_Russia_w1_cog_verb')
```

```{r local Russia w1, echo=FALSE}
vari <- SAGE_Russia_w1_cog_verb$q2536
vbl_miss <- c(-8,-9)
kable(Continuous_summary(var = vari, missing_values = vbl_miss)[3], caption = attr(vari,"spss::shortName"))
kable(Continuous_summary(vari, missing_values = c(-8,-9))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(-8,-9))$summary, caption = "Summary")
ggplot(SAGE_Russia_w1_cog_verb %>% filter(!vari %in% vbl_miss), aes(x=q2536)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable `cog_verb_c` from the study-specific variable the missing values have to be recoded as follows:

* `NA into 999`
* `-9 into 996`
* `-8 into 998`

To compute the harmonized variable `cog_verb` from `cog_verb_c` it has to be recoded as follows:

* `cog_verb_c <=25% into 0`
* `cog_verb_c >25% into 1`

**R script:**

```{r harmo Russia w1}
#cog_verb_c
SAGE_ds_russia_w1 <- tibble(id=SAGE_Russia_w1_cog_verb$id)
SAGE_ds_russia_w1$cog_verb_c <- car::recode(SAGE_Russia_w1_cog_verb$q2536, "-9=996; -8=998; NA=999")
SAGE_ds_russia_w1$cog_verb_c <- labelled(SAGE_ds_russia_w1$cog_verb_c, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))

#cog_verb
Q <- quantile(car::recode(SAGE_ds_russia_w1$cog_verb_c, "999=NA; 996=NA; 998=NA"), probs = 1/4, na.rm = TRUE, names = FALSE)

SAGE_ds_russia_w1$cog_verb <- car::recode(SAGE_ds_russia_w1[[2]], "0:Q=0; (Q+1):900=1")
SAGE_ds_russia_w1$cog_verb <- labelled(SAGE_ds_russia_w1[[3]], labels = c("<=25%"=0, ">25%"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript Russia w1, echo=FALSE}
vari <- SAGE_ds_russia_w1$cog_verb_c
kable(Continuous_summary(var = vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_verb_c)
kable(Continuous_summary(vari, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(SAGE_ds_russia_w1 %>% filter(!vari %in% miss_values_vector), aes(x=cog_verb_c)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

vari <- SAGE_ds_russia_w1$cog_verb
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label_cog_verb) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_russia_w1, aes(x=factor(cog_verb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation Russia w1, echo=FALSE}
Continuous <- c(sum(na.omit(SAGE_ds_russia_w1[[2]])<=Q), sum(na.omit(SAGE_ds_russia_w1[[2]])>Q & na.omit(SAGE_ds_russia_w1[[2]])<900), sum(na.omit(SAGE_ds_russia_w1[[2]])==996), sum(na.omit(SAGE_ds_russia_w1[[2]])==998), sum(na.omit(SAGE_ds_russia_w1[[2]])==999))
Dichotomous <- table(SAGE_ds_russia_w1[[3]], useNA = "ifany")
C <- rbind(Continuous,Dichotomous)
colnames(C) <- c("0:8->0","9:160->1", "-9->996", "-8->998", "NA->999") 
kable(C, caption = "Continuous vs Dichotomous")
```





<!--AUXILIAR FUNCTIONS-->



```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds,vbl_name,ds_lab = ds_label){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    if(vbl_name %in% names(l.hds[[name]])){
      # In the aux_object we copy the old tibble to recodify all missing values as NA.
      aux_object <- l.hds[[name]]
      # Labelling of variables
      label(l.hds[[name]][[vbl_name]]) <- label(aux_object[[vbl_name]]) <- ds_lab
      # Labelling of categories (for continues variables, only missing values)
      l.hds[[name]][[vbl_name]] <- labelled(l.hds[[name]][[vbl_name]], labels = cat_label)
      aux_object[[vbl_name]] <- car::recode(aux_object[[vbl_name]], "miss_values_vector=NA")
      # Labelling of categories (for categorical variables, only non-missing values)
      aux_object[[vbl_name]] <- labelled(aux_object[[vbl_name]], labels = cat_label[1:(length(cat_label)-9)])
      # Saving the recodified tibble in list m.hds
      m.hds[[name]] <- aux_object
      rm(aux_object)
    }
  }
  return(list(l.hds,m.hds))

}


labelling_c <- function(l.hds,m.hds,vbl_name,ds_lab=ds_label){
  
  # Labelling of the tibbles with continuous data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    
    if(vbl_name %in% names(l.hds[[name]])){
      # In the aux_object we copy the old tibble to recodify all missing values as NA.
      aux_object <- m.hds[[name]]
      # Labelling of variables
      label(l.hds[[name]][[vbl_name]]) <- label(aux_object[[vbl_name]]) <- ds_lab
      # Labelling of categories (for continues variables, only missing values)
      l.hds[[name]][[vbl_name]] <- labelled(l.hds[[name]][[vbl_name]], labels = cont_label)
      aux_object[[vbl_name]] <- car::recode(aux_object[[vbl_name]], "miss_values_vector=NA")
      aux_object[[vbl_name]] <- remove_val_labels(aux_object[[vbl_name]])
      # Saving the recodified tibble in list m.hds
      m.hds[[name]] <- aux_object
      rm(aux_object)
    }
  }
  return(list(l.hds,m.hds))

}


# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames,vbl_name = hd_vbl){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][vbl_name])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][vbl_name])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[2+length(cat_label),] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}


# Creation of summary tables for continuous data

summaries_c <- function(l.hds,m.hds,lnames,vbl_name){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][vbl_name])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[vbl_name]], missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][vbl_name])[1:6]
    # Next, missing/no-missing values (the 1 in $values_table[1,] stands for absolute values, while a 2 would stand for percentages)
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[vbl_name]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][vbl_name]))[[2]],lnames)
  return(t.hds)
  
}


# Save data tables

savingRD <- function(l.hds,vbl_name = hd_vbl){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }
  
}

```



```{r populations-waves, echo=F}


# All study waves and populations with abbreviated and descriptive names

sage.cw <- list(SA_w1 = c("SA_w1","South Africa w1"), ghana_w1 = c("ghana_w1","Ghana w1"), china_w1 = c("china_w1","China w1"), india_w1 = c("india_w1","India w1"), russia_w1 = c("russia_w1","Russian Federation w1"), mexico_w1 = c("mexico_w1","Mexico w1"))


```


<!--Labelling and saving-->

```{r, echo=FALSE}


# Consider only waves with some variable harmonised

l.hds <- lapply(sage.cw, function(wname) if(exists(paste0("SAGE_ds_",wname[1]))){wname = list(get(paste0("SAGE_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling categorical variable of tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]],hd_vbl,ds_label_cog_verb)
  # Labelling continuous variable of tibbles
  lmlist <- labelling_c(lmlist[[1]],lmlist[[2]],hd_vbl_c,ds_label_cog_verb_c)
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}

sagelist <- lmlist # baseline list




```



<!--Descriptives-->

## Descriptive statistics of the harmonised variable `cog_verb` accross populations and waves

Percentages of categories in each harmonised variable:


```{r summ, echo=F}


# Consider only harmonised waves
l.hds <- lapply(sage.cw, function(wname) if(hd_vbl %in% names(get0(paste0("SAGE_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- sagelist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- sagelist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl),caption=ds_label_cog_verb))
}





```






## Summary of descriptive statistics of the harmonised variable `cog_verb_c` accross populations and waves






```{r summ_c, echo=F}


# Consider only harmonised waves
l.hds <- lapply(sage.cw, function(wname) if(hd_vbl_c %in% names(get0(paste0("SAGE_ds_",wname[1])))){wname})

nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}



if(length(l.hds)>0){
  lmlist[[1]] <- sagelist[[1]][sapply(l.hds,function(x)x[[1]])]
  lmlist[[2]] <- sagelist[[2]][sapply(l.hds,function(x)x[[1]])]
  
  # Printing table of categories
  print(knitr::kable(summaries_c(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]]),hd_vbl_c),caption=ds_label_cog_verb_c))
}



```



# Quality estimation:

No comments


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
