---
title: "Eudaimonic well-being"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/eudaimonic_wbDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/eudaimonic_wbDS.R')
```


# Data process

## South Africa

### Wave 1

#### Study-specific variable description

| **Name** | `q7008b` | 
|-|-|-|
| **Label** | `q7008b: coping`| 
| **Table name**  | `southAfricaINDdata`| 
| **Categories** | `1 = never` <br/> `2 = almost never` <br/> `3 = sometimes` <br/> `4 = fairly often` <br/> `5 = very often` | 
| **Missings** | `8 = don't know` <br/> `9 = not applicable` | 
| **Description** |  | 

```{r assign SA_w1, echo=F}
opal.assign.table.tibble(o, 'SAGE_wb','SAGE.southAfricaINDdata',variables=list( 'q7008b'), missings = T)
SAGE_wb <- opal.execute(o,'SAGE_wb')
```

```{r local SA_w1, echo=F}
vbl <- SAGE_wb$q7008b
vbl_miss <- c(8,9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(SAGE_wb)[2])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Missing values")
ggplot(SAGE_wb, aes(x=factor(q7008b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```


#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 0`
* `3 into 1`
* `4,5 into 2` 
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo SA_w1}
# Categorical variable harmonization
SAGE_ds_SA_w1 <- tibble(id=SAGE_wb$id)
SAGE_ds_SA_w1$eudaimonic_wb <- car::recode(SAGE_wb$q7008b, "1=0; 2=0; 3=1; 4=2; 5=2; 8=998; 9=996; NA=999")
```


#### Statistics of the new harmonized variable

```{r descript SA_w1, echo=F}

vbl <- SAGE_ds_SA_w1$eudaimonic_wb
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_SA_w1, aes(x=factor(eudaimonic_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation SA_w1, echo=F}
```




## Ghana


### Wave 1


#### Study-specific variable description

| **Name** | `q7008b` | 
|-|-|-|
| **Label** | `q7008b: coping`| 
| **Table name**  | `ghanaINDData`| 
| **Categories** | `1 = never` <br/> `2 = almost never` <br/> `3 = sometimes` <br/> `4 = fairly often` <br/> `5 = very often` | 
| **Missings** | `8 = don't know` <br/> `9 = not applicable` | 
| **Description** |  | 

```{r assign ghana_w1, echo=F}

opal.assign.table.tibble(o, 'SAGE_wb','SAGE.ghanaINDData',variables=list('q7008b'), missings = T)
SAGE_wb <- opal.execute(o,'SAGE_wb')


```

```{r local ghana_w1, echo=F}
vbl <- SAGE_wb$q7008b
vbl_miss <- c(8,9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(SAGE_wb)[2])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Missing values")
ggplot(SAGE_wb, aes(x=factor(q7008b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```


#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 0`
* `3 into 1`
* `4,5 into 2` 
* `8 into 998`
* `9 into 996`
* `NA into 999`


**R script:**

```{r harmo ghana_w1}

# Categorical variable harmonization
SAGE_ds_ghana_w1 <- tibble(id=SAGE_wb$id)
SAGE_ds_ghana_w1$eudaimonic_wb <- car::recode(SAGE_wb$q7008b, "1=0; 2=0; 3=1; 4=2; 5=2; 8=998; 9=996; NA=999")
```


#### Statistics of the new harmonized variable

```{r descript ghana_w1, echo=F}

vbl <- SAGE_ds_ghana_w1$eudaimonic_wb
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_ghana_w1, aes(x=factor(eudaimonic_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation ghana_w1, echo=F}
```





## China


### Wave 1


#### Study-specific variable description

| **Name** | `q7008b` | 
|-|-|-|
| **Label** | `q7008b: coping`| 
| **Table name**  | `chinaINDData`| 
| **Categories** | `1 = never` <br/> `2 = almost never` <br/> `3 = sometimes` <br/> `4 = fairly often` <br/> `5 = very often` | 
| **Missings** | `8 = don't know` <br/> `9 = not applicable` | 
| **Description** |  | 

```{r assign china_w1, echo=F}

opal.assign.table.tibble(o, 'SAGE_wb','SAGE.chinaINDData',variables=list('q7008b'), missings = T)
SAGE_wb <- opal.execute(o,'SAGE_wb')

```

```{r local china_w1, echo=F}
vbl <- SAGE_wb$q7008b
vbl_miss <- c(8,9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(SAGE_wb)[2])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Missing values")
ggplot(SAGE_wb, aes(x=factor(q7008b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```


#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 0`
* `3 into 1`
* `4,5 into 2` 
* `8 into 998`
* `9 into 996`
* `NA into 999`


**R script:**

```{r harmo china_w1}

# Categorical variable harmonization
SAGE_ds_china_w1 <- tibble(id=SAGE_wb$id)
SAGE_ds_china_w1$eudaimonic_wb <- car::recode(SAGE_wb$q7008b, "1=0; 2=0; 3=1; 4=2; 5=2; 8=998; 9=996; NA=999")
```


#### Statistics of the new harmonized variable

```{r descript china_w1, echo=F}

vbl <- SAGE_ds_china_w1$eudaimonic_wb
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_china_w1, aes(x=factor(eudaimonic_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation china_w1, echo=F}
```




## India


### Wave 1


#### Study-specific variable description

| **Name** | `q7008b` | 
|-|-|-|
| **Label** | `q7008b: coping`| 
| **Table name**  | `indiaINDData`| 
| **Categories** | `1 = never` <br/> `2 = almost never` <br/> `3 = sometimes` <br/> `4 = fairly often` <br/> `5 = very often` | 
| **Missings** | `8 = don't know` <br/> `9 = not applicable` | 
| **Description** |  | 

```{r assign india_w1, echo=F}

opal.assign.table.tibble(o, 'SAGE_wb','SAGE.indiaINDData',variables=list('q7008b'), missings = T)
SAGE_wb <- opal.execute(o,'SAGE_wb')

```

```{r local india_w1, echo=F}
vbl <- SAGE_wb$q7008b
vbl_miss <- c(8,9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(SAGE_wb)[2])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Missing values")
ggplot(SAGE_wb, aes(x=factor(q7008b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```


#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 0`
* `3 into 1`
* `4,5 into 2` 
* `8 into 998`
* `9 into 996`
* `NA into 999`


**R script:**

```{r harmo india_w1}
# Categorical variable harmonization
SAGE_ds_india_w1 <- tibble(id=SAGE_wb$id)
SAGE_ds_india_w1$eudaimonic_wb <- car::recode(SAGE_wb$q7008b, "1=0; 2=0; 3=1; 4=2; 5=2; 8=998; 9=996; NA=999")
```


#### Statistics of the new harmonized variable

```{r descript india_w1, echo=F}

vbl <- SAGE_ds_india_w1$eudaimonic_wb
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_india_w1, aes(x=factor(eudaimonic_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation india_w1, echo=F}

```





## Russian Federation


### Wave 1


#### Study-specific variable description

| **Name** | `q7008b` | 
|-|-|-|
| **Label** | `q7008b: coping`| 
| **Table name**  | `russiaINDdata`| 
| **Categories** | `1 = never` <br/> `2 = almost never` <br/> `3 = sometimes` <br/> `4 = fairly often` <br/> `5 = very often` | 
| **Missings** | `8 = don't know` <br/> `9 = not applicable` | 
| **Description** |  | 


```{r assign russia_w1, echo=F}

opal.assign.table.tibble(o, 'SAGE_wb','SAGE.russiaINDdata',variables=list('q7008b'), missings = T)
SAGE_wb <- opal.execute(o,'SAGE_wb')

```

```{r local russia_w1, echo=F}

vbl <- SAGE_wb$q7008b
vbl_miss <- c(8,9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(SAGE_wb)[2])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Missing values")
ggplot(SAGE_wb, aes(x=factor(q7008b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 0`
* `3 into 1`
* `4,5 into 2` 
* `8 into 998`
* `9 into 996`
* `NA into 999`


**R script:**

```{r harmo russia_w1}

# Categorical variable harmonization
SAGE_ds_russia_w1 <- tibble(id=SAGE_wb$id)
SAGE_ds_russia_w1$eudaimonic_wb <- car::recode(SAGE_wb$q7008b, "1=0; 2=0; 3=1; 4=2; 5=2; 8=998; 9=996; NA=999")
```


#### Statistics of the new harmonized variable

```{r descript russia_w1, echo=F}

vbl <- SAGE_ds_russia_w1$eudaimonic_wb
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_russia_w1, aes(x=factor(eudaimonic_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation russia_w1, echo=F}
```




## Mexico


### Wave 1


#### Study-specific variable description

| **Name** | `q7008b` | 
|-|-|-|
| **Label** | `q7008b: coping`| 
| **Table name**  | `southAfricaINDdata`| 
| **Categories** | `1 = never` <br/> `2 = almost never` <br/> `3 = sometimes` <br/> `4 = fairly often` <br/> `5 = very often` | 
| **Missings** | `8 = don't know` <br/> `9 = not applicable` | 
| **Description** |  | 

```{r assign mexico_w1, echo=F}

opal.assign.table.tibble(o, 'SAGE_wb','SAGE.mexicoINDdata',variables=list('q7008b'), missings = T)
SAGE_wb <- opal.execute(o,'SAGE_wb')

```

```{r local mexico_w1, echo=F}
vbl <- SAGE_wb$q7008b
vbl_miss <- c(8,9)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = names(SAGE_wb)[2])
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Missing values")
ggplot(SAGE_wb, aes(x=factor(q7008b))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```


#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `1,2 into 0`
* `3 into 1`
* `4,5 into 2` 
* `8 into 998`
* `9 into 996`
* `NA into 999`


**R script:**

```{r harmo mexico_w1}

# Categorical variable harmonization
SAGE_ds_mexico_w1 <- tibble(id=SAGE_wb$id)
SAGE_ds_mexico_w1$eudaimonic_wb <- car::recode(SAGE_wb$q7008b, "1=0; 2=0; 3=1; 4=2; 5=2; 8=998; 9=996; NA=999")
```


#### Statistics of the new harmonized variable

```{r descript mexico_w1, echo=F}

vbl <- SAGE_ds_mexico_w1$eudaimonic_wb
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_mexico_w1, aes(x=factor(eudaimonic_wb))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation mexico_w1, echo=F}
```


## Summary of descriptive statistics of the harmonised variable accross populations and waves




```{r helpfunctions, echo=F}

source("../../helpfunctions.r")

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names


sage.cw <- list(SA_w1 = c("SA_w1","South Africa w1"), ghana_w1 = c("ghana_w1","Ghana w1"), china_w1 = c("china_w1","China w1"), india_w1 = c("india_w1","India w1"), russia_w1 = c("russia_w1","Russian Federation w1"), mexico_w1 = c("mexico_w1","Mexico w1"))

# Consider only harmonised waves
l.hds <- lapply(sage.cw, function(wname) if(exists(paste0("SAGE_ds_",wname[1]))){wname = list(get(paste0("SAGE_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```





# Quality estimation



<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





