---
title: "Energy"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `energy`
* Variable label: `Self-reported level of energy`
* Variable description: `Self-reported high level of energy experienced at the time of the interview. Dichotomous variable: 0 refers to lack of energy or presence of fatigue/being listless, and 1 refers to energy in a high level or most of the time`
* Domain: `Health status and functional limitations`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Lack of energy
1        | High level of energy

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process


## China

### Wave 1 

#### Study-specific variable description




| **Name** | `q7001`|
|-|-|
| **Label** | `q7001: enough energy` |
| **Table name** | `chinaINDData` |
| **Categories** | `1 = Completely; 2 = Mostly; 3 = Moderately; 4 = A little; 5 = Not at all` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign china w1, echo=F}
opal.assign.table.tibble(o, 'SAGE_China_w1_energy','SAGE.chinaINDData', variables=list('q7001'), missings = TRUE)
```

```{r local china w1, echo=F}
SAGE_China_w1_energy <- opal.execute(o,'SAGE_China_w1_energy')
vari <- SAGE_China_w1_energy$q7001
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "q7001")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(SAGE_China_w1_energy, aes(x=factor(q7001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Energy") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

  * `1,2 into 1` 
  * `3,4,5 into 0`
  * `NA into 999`

**R script:**
```{r harmo china w1}
SAGE_china_ds_w1 <- tibble(id=SAGE_China_w1_energy$id)
SAGE_china_ds_w1$energy <- car::recode(SAGE_China_w1_energy$q7001, "1 = '1';2 = '1';3 = '0';4 = '0';5 = '0'; NA = '999' ")
SAGE_china_ds_w1$energy <- labelled(SAGE_china_ds_w1$energy, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript china w1, echo=F}
vari <- SAGE_china_ds_w1$energy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "energy")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SAGE_china_ds_w1, aes(x=factor(energy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Energy") + ylab("Frequency")
```

#### Validation
```{r crosstabulation china w1, echo=F}
AfterH <- table(SAGE_china_ds_w1$energy)
X<-table(SAGE_China_w1_energy$q7001)
BeforeH <- c(sum(X[3:5]),sum(X[1:2]),sum(is.na(SAGE_China_w1_energy$q7001)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3,4,5->0","1,2->1","NA->999") 
kable(C)
```






```{r importOPAL china w1, echo=FALSE}

label(SAGE_china_ds_w1$energy) <- "Self-reported high level of energy"
#opal.assign.data(o, 'SAGE_china_ds_w1', SAGE_china_ds_w1)
#opal.symbol_import(o,'SAGE_china_ds_w1', project='_Athlos_Harm_Dataset')
energy <- SAGE_china_ds_w1
save(energy, file = "../RData/china_w1/energy.RData")

SAGE_m_china_ds_w1 <- SAGE_china_ds_w1
SAGE_m_china_ds_w1$energy <- car::recode(SAGE_m_china_ds_w1$energy, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_m_china_ds_w1', SAGE_m_china_ds_w1)
#opal.symbol_import(o,'SAGE_m_china_ds_w1', project='_Athlos_Harm_Dataset')
```



## Ghana

### Wave 1 

#### Study-specific variable description




| **Name** | `q7001`|
|-|-|
| **Label** | `q7001: enough energy` |
| **Table name** | `ghanaINDData` |
| **Categories** | `1 = Completely; 2 = Mostly; 3 = Moderately; 4 = A little; 5 = Not at all` |
| **Missings** | `8 = Don't know; 9 = Not applicable; NA` |
| **Description** |  |


```{r assign ghana w1, echo=F}
opal.assign.table.tibble(o, 'SAGE_Ghana_w1_energy','SAGE.ghanaINDData', variables=list('q7001'), missings = TRUE)
```

```{r local ghana w1, echo=F}
SAGE_Ghana_w1_energy <- opal.execute(o,'SAGE_Ghana_w1_energy')
vari <- SAGE_Ghana_w1_energy$q7001
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = "q7001")
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
ggplot(SAGE_Ghana_w1_energy, aes(x=factor(q7001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Energy") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

  * `1,2 into 1` 
  * `3,4,5 into 0`
  * `8 Don't know into 998`
  * `9 Not applicable into 996`
  * `NA into 999`

**R script:**
```{r harmo ghana w1}
SAGE_ghana_ds_w1 <- tibble(id=SAGE_Ghana_w1_energy$id)
SAGE_ghana_ds_w1$energy <- car::recode(SAGE_Ghana_w1_energy$q7001, "1 = '1';2 = '1';3 = '0';4 = '0';5 = '0';9 = '996';8 = '998'; NA = '999' ")
SAGE_ghana_ds_w1$energy <- labelled(SAGE_ghana_ds_w1$energy, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript ghana w1, echo=F}
vari <- SAGE_ghana_ds_w1$energy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "energy")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SAGE_ghana_ds_w1, aes(x=factor(energy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Energy") + ylab("Frequency")
```

#### Validation
```{r crosstabulation ghana w1, echo=F}
AfterH <- table(SAGE_ghana_ds_w1$energy)
X<-table(SAGE_Ghana_w1_energy$q7001)
BeforeH <- c(sum(X[3:5]),sum(X[1:2]),X[7:6],sum(is.na(SAGE_Ghana_w1_energy$q7001)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3,4,5->0","1,2->1","9->996","8->998","NA->999") 
kable(C)
```






```{r importOPAL ghana w1, echo=FALSE}

label(SAGE_ghana_ds_w1$energy) <- "Self-reported high level of energy"
#opal.assign.data(o, 'SAGE_ghana_ds_w1', SAGE_ghana_ds_w1)
#opal.symbol_import(o,'SAGE_ghana_ds_w1', project='_Athlos_Harm_Dataset')
energy <- SAGE_ghana_ds_w1
save(energy, file = "../RData/ghana_w1/energy.RData")

SAGE_m_ghana_ds_w1 <- SAGE_ghana_ds_w1
SAGE_m_ghana_ds_w1$energy <- car::recode(SAGE_m_ghana_ds_w1$energy, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_m_ghana_ds_w1', SAGE_m_ghana_ds_w1)
#opal.symbol_import(o,'SAGE_m_ghana_ds_w1', project='_Athlos_Harm_Dataset')
```



## India

### Wave 1 

#### Study-specific variable description




| **Name** | `q7001`|
|-|-|
| **Label** | `q7001: enough energy` |
| **Table name** | `indiaINDData` |
| **Categories** | `1 = Completely; 2 = Mostly; 3 = Moderately; 4 = A little; 5 = Not at all` |
| **Missings** | `8 = Don't know; 9 = Not applicable; NA` |
| **Description** |  |


```{r assign india w1, echo=F}
opal.assign.table.tibble(o, 'SAGE_India_w1_energy','SAGE.indiaINDData', variables=list('q7001'), missings = TRUE)
```

```{r local india w1, echo=F}
SAGE_India_w1_energy <- opal.execute(o,'SAGE_India_w1_energy')
vari <- SAGE_India_w1_energy$q7001
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = "q7001")
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
ggplot(SAGE_India_w1_energy, aes(x=factor(q7001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Energy") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

  * `1,2 into 1` 
  * `3,4,5 into 0`
  * `8 Don't know into 998`
  * `9 Not applicable into 996`
  * `NA into 999`

**R script:**
```{r harmo india w1}
SAGE_india_ds_w1 <- tibble(id=SAGE_India_w1_energy$id)
SAGE_india_ds_w1$energy <- car::recode(SAGE_India_w1_energy$q7001, "1 = '1';2 = '1';3 = '0';4 = '0';5 = '0';9 = '996';8 = '998'; NA = '999' ")
SAGE_india_ds_w1$energy <- labelled(SAGE_india_ds_w1$energy, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript india w1, echo=F}
vari <- SAGE_india_ds_w1$energy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "energy")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SAGE_india_ds_w1, aes(x=factor(energy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Energy") + ylab("Frequency")
```

#### Validation
```{r crosstabulation india w1, echo=F}
AfterH <- table(SAGE_india_ds_w1$energy)
X<-table(SAGE_India_w1_energy$q7001)
BeforeH <- c(sum(X[3:5]),sum(X[1:2]),X[7:6],sum(is.na(SAGE_India_w1_energy$q7001)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3,4,5->0","1,2->1","9->996","8->998","NA->999") 
kable(C)
```






```{r importOPAL india w1, echo=FALSE}

label(SAGE_india_ds_w1$energy) <- "Self-reported high level of energy"
#opal.assign.data(o, 'SAGE_india_ds_w1', SAGE_india_ds_w1)
#opal.symbol_import(o,'SAGE_india_ds_w1', project='_Athlos_Harm_Dataset')
energy <- SAGE_india_ds_w1
save(energy, file = "../RData/india_w1/energy.RData")

SAGE_m_india_ds_w1 <- SAGE_india_ds_w1
SAGE_m_india_ds_w1$energy <- car::recode(SAGE_m_india_ds_w1$energy, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_m_india_ds_w1', SAGE_m_india_ds_w1)
#opal.symbol_import(o,'SAGE_m_india_ds_w1', project='_Athlos_Harm_Dataset')
```



## Mexico

### Wave 1 

#### Study-specific variable description




| **Name** | `q7001`|
|-|-|
| **Label** | `q7001: enough energy` |
| **Table name** | `mexicoINDdata` |
| **Categories** | `1 = Completely; 2 = Mostly; 3 = Moderately; 4 = A little; 5 = Not at all` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign mexico w1, echo=F}
opal.assign.table.tibble(o, 'SAGE_Mexico_w1_energy','SAGE.mexicoINDdata', variables=list('q7001'), missings = TRUE)
```

```{r local mexico w1, echo=F}
SAGE_Mexico_w1_energy <- opal.execute(o,'SAGE_Mexico_w1_energy')
vari <- SAGE_Mexico_w1_energy$q7001
kable(Categorical_summary(vari, missing_values = NA)[2], caption = "q7001")
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
ggplot(SAGE_Mexico_w1_energy, aes(x=factor(q7001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Energy") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

  * `1,2 into 1` 
  * `3,4,5 into 0`
  * `NA into 999`

**R script:**
```{r harmo mexico w1}
SAGE_mexico_ds_w1 <- tibble(id=SAGE_Mexico_w1_energy$id)
SAGE_mexico_ds_w1$energy <- car::recode(SAGE_Mexico_w1_energy$q7001, "1 = '1';2 = '1';3 = '0';4 = '0';5 = '0'; NA = '999' ")
SAGE_mexico_ds_w1$energy <- labelled(SAGE_mexico_ds_w1$energy, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript mexico w1, echo=F}
vari <- SAGE_mexico_ds_w1$energy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "energy")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SAGE_mexico_ds_w1, aes(x=factor(energy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Energy") + ylab("Frequency")
```

#### Validation
```{r crosstabulation mexico w1, echo=F}
AfterH <- table(SAGE_mexico_ds_w1$energy)
X<-table(SAGE_Mexico_w1_energy$q7001)
BeforeH <- c(sum(X[3:5]),sum(X[1:2]),sum(is.na(SAGE_Mexico_w1_energy$q7001)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3,4,5->0","1,2->1","NA->999") 
kable(C)
```






```{r importOPAL mexico w1, echo=FALSE}

label(SAGE_mexico_ds_w1$energy) <- "Self-reported high level of energy"
#opal.assign.data(o, 'SAGE_mexico_ds_w1', SAGE_mexico_ds_w1)
#opal.symbol_import(o,'SAGE_mexico_ds_w1', project='_Athlos_Harm_Dataset')
energy <- SAGE_mexico_ds_w1
save(energy, file = "../RData/mexico_w1/energy.RData")

SAGE_m_mexico_ds_w1 <- SAGE_mexico_ds_w1
SAGE_m_mexico_ds_w1$energy <- car::recode(SAGE_m_mexico_ds_w1$energy, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_m_mexico_ds_w1', SAGE_m_mexico_ds_w1)
#opal.symbol_import(o,'SAGE_m_mexico_ds_w1', project='_Athlos_Harm_Dataset')
```



## Russian Federation

### Wave 1 

#### Study-specific variable description




| **Name** | `q7001`|
|-|-|
| **Label** | `q7001: enough energy` |
| **Table name** | `russiaINDdata` |
| **Categories** | `1 = Completely; 2 = Mostly; 3 = Moderately; 4 = A little; 5 = Not at all` |
| **Missings** | `8 = Don't know; 9 = Not applicable; NA` |
| **Description** |  |


```{r assign russia w1, echo=F}
opal.assign.table.tibble(o, 'SAGE_Russia_w1_energy','SAGE.russiaINDdata', variables=list('q7001'), missings = TRUE)
```

```{r local russia w1, echo=F}
SAGE_Russia_w1_energy <- opal.execute(o,'SAGE_Russia_w1_energy')
vari <- SAGE_Russia_w1_energy$q7001
kable(Categorical_summary(vari, missing_values = c(8,9))[3], caption = "q7001")
kable(Categorical_summary(vari, missing_values = c(8,9))[1], caption = "Category")
ggplot(SAGE_Russia_w1_energy, aes(x=factor(q7001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Energy") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

  * `1,2 into 1` 
  * `3,4,5 into 0`
  * `8 Don't know into 998`
  * `9 Not applicable into 996`
  * `NA into 999`

**R script:**
```{r harmo russia w1}
SAGE_russia_ds_w1 <- tibble(id=SAGE_Russia_w1_energy$id)
SAGE_russia_ds_w1$energy <- car::recode(SAGE_Russia_w1_energy$q7001, "1 = '1';2 = '1';3 = '0';4 = '0';5 = '0';9 = '996';8 = '998'; NA = '999' ")
SAGE_russia_ds_w1$energy <- labelled(SAGE_russia_ds_w1$energy, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript russia w1, echo=F}
vari <- SAGE_russia_ds_w1$energy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "energy")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SAGE_russia_ds_w1, aes(x=factor(energy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Energy") + ylab("Frequency")
```

#### Validation
```{r crosstabulation russia w1, echo=F}
AfterH <- table(SAGE_russia_ds_w1$energy)
X<-table(SAGE_Russia_w1_energy$q7001)
BeforeH <- c(sum(X[3:5]),sum(X[1:2]),X[7:6],sum(is.na(SAGE_Russia_w1_energy$q7001)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3,4,5->0","1,2->1","9->996","8->998","NA->999") 
kable(C)
```






```{r importOPAL russia w1, echo=FALSE}

label(SAGE_russia_ds_w1$energy) <- "Self-reported high level of energy"
#opal.assign.data(o, 'SAGE_russia_ds_w1', SAGE_russia_ds_w1)
#opal.symbol_import(o,'SAGE_russia_ds_w1', project='_Athlos_Harm_Dataset')
energy <- SAGE_russia_ds_w1
save(energy, file = "../RData/russia_w1/energy.RData")

SAGE_m_russia_ds_w1 <- SAGE_russia_ds_w1
SAGE_m_russia_ds_w1$energy <- car::recode(SAGE_m_russia_ds_w1$energy, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_m_russia_ds_w1', SAGE_m_russia_ds_w1)
#opal.symbol_import(o,'SAGE_m_russia_ds_w1', project='_Athlos_Harm_Dataset')
```



## South Africa

### Wave 1 

#### Study-specific variable description




| **Name** | `q7001`|
|-|-|
| **Label** | `q7001: enough energy` |
| **Table name** | `southAfricaINDdata` |
| **Categories** | `1 = Completely; 2 = Mostly; 3 = Moderately; 4 = A little; 5 = Not at all` |
| **Missings** | `8 = Don't know; NA` |
| **Description** |  |


```{r assign africa w1, echo=F}
opal.assign.table.tibble(o, 'SAGE_Africa_w1_energy','SAGE.southAfricaINDdata', variables=list('q7001'), missings = TRUE)
```

```{r local africa w1, echo=F}
SAGE_Africa_w1_energy <- opal.execute(o,'SAGE_Africa_w1_energy')
vari <- SAGE_Africa_w1_energy$q7001
kable(Categorical_summary(vari, missing_values = c(8))[3], caption = "q7001")
kable(Categorical_summary(vari, missing_values = c(8))[1], caption = "Category")
ggplot(SAGE_Africa_w1_energy, aes(x=factor(q7001))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Energy") + ylab("Frequency")
```

#### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

  * `1,2 into 1` 
  * `3,4,5 into 0`
  * `8 Don't know into 998`
  * `NA into 999`

**R script:**
```{r harmo africa w1}
SAGE_SA_ds_w1 <- tibble(id=SAGE_Africa_w1_energy$id)
SAGE_SA_ds_w1$energy <- car::recode(SAGE_Africa_w1_energy$q7001, "1 = '1';2 = '1';3 = '0';4 = '0';5 = '0';8 = '998'; NA = '999' ")
SAGE_SA_ds_w1$energy <- labelled(SAGE_SA_ds_w1$energy, labels = c(Yes=0, No=1, Missing=999, Do_not_know=998, Refuse=997, Not_applicable=996, Does_not_answer=995,  Not_attempt_not_done=994, Disable_to_measure=993, Impute=992, CAPI_interviewer_error=991))
```

#### Statistical description of the new harmonised variable
```{r descript africa w1, echo=F}
vari <- SAGE_SA_ds_w1$energy
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "energy")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SAGE_SA_ds_w1, aes(x=factor(energy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Energy") + ylab("Frequency")
```

#### Validation
```{r crosstabulation africa w1, echo=F}
AfterH <- table(SAGE_SA_ds_w1$energy)
X<-table(SAGE_Africa_w1_energy$q7001)
BeforeH <- c(sum(X[3:5]),sum(X[1:2]),X[6],sum(is.na(SAGE_Africa_w1_energy$q7001)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("3,4,5->0","1,2->1","8->998","NA->999") 
kable(C)
```






```{r importOPAL africa w1, echo=FALSE}

label(SAGE_SA_ds_w1$energy) <- "Self-reported high level of energy"
#opal.assign.data(o, 'SAGE_SA_ds_w1', SAGE_SA_ds_w1)
#opal.symbol_import(o,'SAGE_SA_ds_w1', project='_Athlos_Harm_Dataset')
energy <- SAGE_SA_ds_w1
save(energy, file = "../RData/SA_w1/energy.RData")

SAGE_m_SA_ds_w1 <- SAGE_SA_ds_w1
SAGE_m_SA_ds_w1$energy <- car::recode(SAGE_m_SA_ds_w1$energy, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SAGE_m_SA_ds_w1', SAGE_m_SA_ds_w1)
#opal.symbol_import(o,'SAGE_m_SA_ds_w1', project='_Athlos_Harm_Dataset')
```




# Quality estimation
No comments.


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
