---
title: "Diastolic blood pressure"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_albert.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:
  
* Name: `dbp`
* Label: `Diastolic blood pressure of participantat at each wave`
* Type of variable: `countinous`
* Missings: 
    + `991 = CAPI/interviewer error`
    + `992 = Impute`
    + `993 = Disable to measure`
    + `994 = Not attempt/not done`
    + `995 = Does not answer`
    + `996 = Not applicable`
    + `997 = Refuse`
    + `998 = Do not know`
    + `999 = Missing`
* Comments: `Means of all diastolic blood pressure measures.`


### 10/66 - Cuba - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `bpdias`
* Label: `diastolic bp (average)`
* Type of variable: `countinous`

```{r assign_cuba1}
opal.assign.table.tibble(o, 't1066_cuba_w1_dbp','10-66.1066-Cuba-Baseline',
                         variables=list('bpdias'), missings = TRUE)
```

```{r local_cuba1}
t1066_cuba_w1_dbp <- opal.execute(o,'t1066_cuba_w1_dbp')
Continuous_summary(var = t1066_cuba_w1_dbp$bpdias, missing_values = NA)
ggplot(t1066_cuba_w1_dbp, aes(bpdias)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency")
```


#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_cuba1}
t1066_ds_cuba_w1 <- tibble(id=t1066_cuba_w1_dbp$id)
t1066_ds_cuba_w1$dbp <- car::recode(t1066_cuba_w1_dbp$bpdias, "NA=999")
t1066_ds_cuba_w1$dbp <- labelled(t1066_ds_cuba_w1$dbp, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_cuba1}
Continuous_summary(var = t1066_ds_cuba_w1$dbp, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_cuba_w1, aes(dbp)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency") + xlim(20,160) 
```

#### Validation
There are a variable that measures the diastolic pressure standing that is not taken into account on the average used.
```{r crosstabulation_cuba1}
```






### 10/66 - Cuba - Wave 2 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `f_bpdias`
* Label: `diastolic bp (average)`
* Type of variable: `countinous`

```{r assign_cuba2}
opal.assign.table.tibble(o, 't1066_cuba_w2_dbp','10-66.1066-Cuba-Followup',
                         variables=list('f_bpdias'), missings = TRUE)
```

```{r local_cuba2}
t1066_cuba_w2_dbp <- opal.execute(o,'t1066_cuba_w2_dbp')
Continuous_summary(var = t1066_cuba_w2_dbp$f_bpdias, missing_values = NA)
ggplot(t1066_cuba_w2_dbp, aes(f_bpdias)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_cuba2}
t1066_ds_cuba_w2 <- tibble(id=t1066_cuba_w2_dbp$id)
t1066_ds_cuba_w2$dbp <- car::recode(t1066_cuba_w2_dbp$f_bpdias, "NA=999")
t1066_ds_cuba_w2$dbp <- labelled(t1066_ds_cuba_w2$dbp, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_cuba2}
Continuous_summary(var = t1066_ds_cuba_w2$dbp, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_cuba_w2, aes(dbp)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency") + xlim(20,160) 
```

#### Validation
There are a variable that measures the diastolic pressure standing that is not taken into account on the average used.

```{r crosstabulation_cuba2}
```





### 10/66 - India - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `bpdias`
* Label: `diastolic bp (average)`
* Type of variable: `countinous`

```{r assign_india1}
opal.assign.table.tibble(o, 't1066_india_w1_dbp','10-66.1066-India-Baseline',
                         variables=list('bpdias'), missings = TRUE)
```

```{r local_india1}
t1066_india_w1_dbp <- opal.execute(o,'t1066_india_w1_dbp')
Continuous_summary(var = t1066_india_w1_dbp$bpdias, missing_values = NA)
ggplot(t1066_india_w1_dbp, aes(bpdias)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_india1}
t1066_ds_india_w1 <- tibble(id=t1066_india_w1_dbp$id)
t1066_ds_india_w1$dbp <- car::recode(t1066_india_w1_dbp$bpdias, "NA=999")
t1066_ds_india_w1$dbp <- labelled(t1066_ds_india_w1$dbp, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_india1}
Continuous_summary(var = t1066_ds_india_w1$dbp, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_india_w1, aes(dbp)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency") + xlim(20,160) 
```

#### Validation
There are a variable that measures the diastolic pressure standing that is not taken into account on the average used.
```{r crosstabulation_india1}
```







### 10/66 - India - Wave 2 

There is no variable.




### 10/66 - Urban China - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `bpdias`
* Label: `diastolic bp (average)`
* Type of variable: `countinous`

```{r assign_UCh1}
opal.assign.table.tibble(o, 't1066_UCh_w1_dbp','10-66.1066-UrbanChina-Baseline',
                         variables=list('bpdias'), missings = TRUE)
```

```{r local_UCh1}
t1066_UCh_w1_dbp <- opal.execute(o,'t1066_UCh_w1_dbp')
Continuous_summary(var = t1066_UCh_w1_dbp$bpdias, missing_values = NA)
ggplot(t1066_UCh_w1_dbp, aes(bpdias)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_UCh1}
t1066_ds_UCh_w1 <- tibble(id=t1066_UCh_w1_dbp$id)
t1066_ds_UCh_w1$dbp <- car::recode(t1066_UCh_w1_dbp$bpdias, "NA=999")
t1066_ds_UCh_w1$dbp <- labelled(t1066_ds_UCh_w1$dbp, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_UCh1}
Continuous_summary(var = t1066_ds_UCh_w1$dbp, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UCh_w1, aes(dbp)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency") + xlim(20,160) 
```

#### Validation
There are a variable that measures the diastolic pressure standing that is not taken into account on the average used.
```{r crosstabulation_UCh1}
```





### 10/66 - Urban China - Wave 2 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `f_bpdias`
* Label: `diastolic bp (average)`
* Type of variable: `countinous`

```{r assign_UCh2}
opal.assign.table.tibble(o, 't1066_UCh_w2_dbp','10-66.1066-UrbanChina-Followup',
                         variables=list('f_bpdias'), missings = TRUE)
```

```{r local_UCh2}
t1066_UCh_w2_dbp <- opal.execute(o,'t1066_UCh_w2_dbp')
Continuous_summary(var = t1066_UCh_w2_dbp$f_bpdias, missing_values = NA)
ggplot(t1066_UCh_w2_dbp, aes(f_bpdias)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable plus 5 years, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_UCh2}
t1066_ds_UCh_w2 <- tibble(id=t1066_UCh_w2_dbp$id)
t1066_ds_UCh_w2$dbp <- car::recode(t1066_UCh_w2_dbp$f_bpdias, "NA=999")
t1066_ds_UCh_w2$dbp <- labelled(t1066_ds_UCh_w2$dbp, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_UCh2}
Continuous_summary(var = t1066_ds_UCh_w2$dbp, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UCh_w2, aes(dbp)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency") + xlim(20,160) 
```

#### Validation
There are a variable that measures the diastolic pressure standing that is not taken into account on the average used.

```{r crosstabulation_UCh2}
```






### 10/66 - Rural China - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `bpdias`
* Label: `diastolic bp (average)`
* Type of variable: `countinous`

```{r assign_RCh1}
opal.assign.table.tibble(o, 't1066_RCh_w1_dbp','10-66.1066-RuralChina-Baseline',
                         variables=list('bpdias'), missings = TRUE)
```

```{r local_RCh1}
t1066_RCh_w1_dbp <- opal.execute(o,'t1066_RCh_w1_dbp')
Continuous_summary(var = t1066_RCh_w1_dbp$bpdias, missing_values = NA)
ggplot(t1066_RCh_w1_dbp, aes(bpdias)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_RCh1}
t1066_ds_RCh_w1 <- tibble(id=t1066_RCh_w1_dbp$id)
t1066_ds_RCh_w1$dbp <- car::recode(t1066_RCh_w1_dbp$bpdias, "NA=999")
t1066_ds_RCh_w1$dbp <- labelled(t1066_ds_RCh_w1$dbp, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_RCh1}
Continuous_summary(var = t1066_ds_RCh_w1$dbp, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RCh_w1, aes(dbp)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency") + xlim(20,160) 
```

#### Validation
There are a variable that measures the diastolic pressure standing that is not taken into account on the average used.

```{r crosstabulation_RCh1}
```





### 10/66 - Rural China - Wave 2 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `f_bpdias`
* Label: `diastolic bp (average)`
* Type of variable: `countinous`


```{r assign_RCh2}
opal.assign.table.tibble(o, 't1066_RCh_w2_dbp','10-66.1066-RuralChina-Followup',
                         variables=list('f_bpdias'), missings = TRUE)
```

```{r local_RCh2}
t1066_RCh_w2_dbp <- opal.execute(o,'t1066_RCh_w2_dbp')
Continuous_summary(var = t1066_RCh_w2_dbp$f_bpdias, missing_values = NA)
ggplot(t1066_RCh_w2_dbp, aes(f_bpdias)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable plus 5 years, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_RCh2}
t1066_ds_RCh_w2 <- tibble(id=t1066_RCh_w2_dbp$id)
t1066_ds_RCh_w2$dbp <- car::recode(t1066_RCh_w2_dbp$f_bpdias, "NA=999")
t1066_ds_RCh_w2$dbp <- labelled(t1066_ds_RCh_w2$dbp, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_RCh2}
Continuous_summary(var = t1066_ds_RCh_w2$dbp, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RCh_w2, aes(dbp)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency") + xlim(20,160) 
```

#### Validation
There are a variable that measures the diastolic pressure standing that is not taken into account on the average used.

```{r crosstabulation_RCh2}
```




### 10/66 - Dominican Republic - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `bpdias`
* Label: `diastolic bp (average)`
* Type of variable: `countinous`

```{r assign_DR1}
opal.assign.table.tibble(o, 't1066_DR_w1_dbp','10-66.1066-DominicanRepublic-Baseline',
                         variables=list('bpdias'), missings = TRUE)
```

```{r local_DR1}
t1066_DR_w1_dbp <- opal.execute(o,'t1066_DR_w1_dbp')
Continuous_summary(var = t1066_DR_w1_dbp$bpdias, missing_values = NA)
ggplot(t1066_DR_w1_dbp, aes(bpdias)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_DR1}
t1066_ds_DR_w1 <- tibble(id=t1066_DR_w1_dbp$id)
t1066_ds_DR_w1$dbp <- car::recode(t1066_DR_w1_dbp$bpdias, "NA=999")
t1066_ds_DR_w1$dbp <- labelled(t1066_ds_DR_w1$dbp, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_DR1}
Continuous_summary(var = t1066_ds_DR_w1$dbp, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_DR_w1, aes(dbp)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency") + xlim(20,160) 
```

#### Validation
There are a variable that measures the diastolic pressure standing that is not taken into account on the average used.

```{r crosstabulation_DR1}
```






### 10/66 - Dominican Republic - Wave 2 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `f_bpdias`
* Label: `diastolic bp (average)`
* Type of variable: `countinous`


```{r assign_DR2}
opal.assign.table.tibble(o, 't1066_DR_w2_dbp','10-66.1066-DominicanRepublic-Followup',
                         variables=list('f_bpdias'), missings = TRUE)
```

```{r local_DR2}
t1066_DR_w2_dbp <- opal.execute(o,'t1066_DR_w2_dbp')
Continuous_summary(var = t1066_DR_w2_dbp$f_bpdias, missing_values = NA)
ggplot(t1066_DR_w2_dbp, aes(f_bpdias)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable plus 5 years, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_DR2}
t1066_ds_DR_w2 <- tibble(id=t1066_DR_w2_dbp$id)
t1066_ds_DR_w2$dbp <- car::recode(t1066_DR_w2_dbp$f_bpdias, "NA=999")
t1066_ds_DR_w2$dbp <- labelled(t1066_ds_DR_w2$dbp, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_DR2}
Continuous_summary(var = t1066_ds_DR_w2$dbp, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_DR_w2, aes(dbp)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency") + xlim(20,160) 
```

#### Validation
There are a variable that measures the diastolic pressure standing that is not taken into account on the average used.

```{r crosstabulation_DR2}
```






### 10/66 - Venezuela - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `bpdias`
* Label: `diastolic bp (average)`
* Type of variable: `countinous`

```{r assign_V1}
opal.assign.table.tibble(o, 't1066_Ven_w1_dbp','10-66.1066-Venezuela-Baseline',
                         variables=list('bpdias'), missings = TRUE)
```

```{r local_V1}
t1066_Ven_w1_dbp <- opal.execute(o,'t1066_Ven_w1_dbp')
Continuous_summary(var = t1066_Ven_w1_dbp$bpdias, missing_values = NA)
ggplot(t1066_Ven_w1_dbp, aes(bpdias)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_V1}
t1066_ds_Ven_w1 <- tibble(id=t1066_Ven_w1_dbp$id)
t1066_ds_Ven_w1$dbp <- car::recode(t1066_Ven_w1_dbp$bpdias, "NA=999")
t1066_ds_Ven_w1$dbp <- labelled(t1066_ds_Ven_w1$dbp, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_V1}
Continuous_summary(var = t1066_ds_Ven_w1$dbp, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_Ven_w1, aes(dbp)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency") + xlim(20,160) 
```

#### Validation
There are a variable that measures the diastolic pressure standing that is not taken into account on the average used.

```{r crosstabulation_V1}
```








### 10/66 - Venezuela - Wave 2 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `f_bpdias`
* Label: `diastolic bp (average)`
* Type of variable: `countinous`

```{r assign_V2}
opal.assign.table.tibble(o, 't1066_Ven_w2_dbp','10-66.1066-Venezuela-Followup',
                         variables=list('f_bpdias'), missings = TRUE)

```

```{r local_V2}
t1066_Ven_w2_dbp <- opal.execute(o,'t1066_Ven_w2_dbp')
Continuous_summary(var = t1066_Ven_w2_dbp$f_bpdias, missing_values = NA)
ggplot(t1066_Ven_w2_dbp, aes(f_bpdias)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable plus 4 years, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_V2}
t1066_ds_Ven_w2 <- tibble(id=t1066_Ven_w2_dbp$id)
t1066_ds_Ven_w2$dbp <- car::recode(t1066_Ven_w2_dbp$f_bpdias, "NA=999")
t1066_ds_Ven_w2$dbp <- labelled(t1066_ds_Ven_w2$dbp, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_V2}
Continuous_summary(var = t1066_ds_Ven_w2$dbp, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_Ven_w2, aes(dbp)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency") + xlim(20,160) 
```

#### Validation
There are a variable that measures the diastolic pressure standing that is not taken into account on the average used.

```{r crosstabulation_V2}
```







### 10/66 - Urban Peru - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `bpdias`
* Label: `diastolic bp (average)`
* Type of variable: `countinous`

```{r assign_UP}
opal.assign.table.tibble(o, 't1066_UP_w1_dbp','10-66.1066-UrbanPeru-Baseline',
                         variables=list('bpdias'), missings = TRUE)
```

```{r local_UP1}
t1066_UP_w1_dbp <- opal.execute(o,'t1066_UP_w1_dbp')
Continuous_summary(var = t1066_UP_w1_dbp$bpdias, missing_values = NA)
ggplot(t1066_UP_w1_dbp, aes(bpdias)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency")
```


#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_UP1}
t1066_ds_UP_w1 <- tibble(id=t1066_UP_w1_dbp$id)
t1066_ds_UP_w1$dbp <- car::recode(t1066_UP_w1_dbp$bpdias, "NA=999")
t1066_ds_UP_w1$dbp <- labelled(t1066_ds_UP_w1$dbp, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_UP1}
Continuous_summary(var = t1066_ds_UP_w1$dbp, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UP_w1, aes(dbp)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency") + xlim(20,160) 
```

#### Validation
There are a variable that measures the diastolic pressure standing that is not taken into account on the average used.

```{r crosstabulation_UP1}
```






### 10/66 - Urban Peru - Wave 2 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `f_bpdias`
* Label: `diastolic bp (average)`
* Type of variable: `countinous`

```{r assign_UP2}
opal.assign.table.tibble(o, 't1066_UP_w2_dbp','10-66.1066-UrbanPeru-Followup',
                         variables=list('f_bpdias'), missings = TRUE)
```

```{r local_UP2}
t1066_UP_w2_dbp <- opal.execute(o,'t1066_UP_w2_dbp')
Continuous_summary(var = t1066_UP_w2_dbp$f_bpdias, missing_values = NA)
ggplot(t1066_UP_w2_dbp, aes(f_bpdias)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable plus 4 years, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_UP2}
t1066_ds_UP_w2 <- tibble(id=t1066_UP_w2_dbp$id)
t1066_ds_UP_w2$dbp <- car::recode(t1066_UP_w2_dbp$f_bpdias, "NA=999")
t1066_ds_UP_w2$dbp <- labelled(t1066_ds_UP_w2$dbp, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_UP2}
Continuous_summary(var = t1066_ds_UP_w2$dbp, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UP_w2, aes(dbp)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency") + xlim(20,160) 
```

#### Validation
There are a variable that measures the diastolic pressure standing that is not taken into account on the average used.

```{r crosstabulation_UP2}
```






### 10/66 - Rural Peru - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `bpdias`
* Label: `diastolic bp (average)`
* Type of variable: `countinous`


```{r assign_RP}
opal.assign.table.tibble(o, 't1066_RP_w1_dbp','10-66.1066-RuralPeru-Baseline',
                         variables=list('bpdias'), missings = TRUE)
```

```{r local_RP1}
t1066_RP_w1_dbp <- opal.execute(o,'t1066_RP_w1_dbp')
Continuous_summary(var = t1066_RP_w1_dbp$bpdias, missing_values = NA)
ggplot(t1066_RP_w1_dbp, aes(bpdias)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_RP1}
t1066_ds_RP_w1 <- tibble(id=t1066_RP_w1_dbp$id)
t1066_ds_RP_w1$dbp <- car::recode(t1066_RP_w1_dbp$bpdias, "NA=999")
t1066_ds_RP_w1$dbp <- labelled(t1066_ds_RP_w1$dbp, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_RP1}
Continuous_summary(var = t1066_ds_RP_w1$dbp, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RP_w1, aes(dbp)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency") + xlim(20,160) 
```

#### Validation
There are a variable that measures the diastolic pressure standing that is not taken into account on the average used.

```{r crosstabulation_RP1}
```




### 10/66 - Rural Peru - Wave 2 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `f_bpdias`
* Label: `diastolic bp (average)`
* Type of variable: `countinous`

```{r assign_RP2}
opal.assign.table.tibble(o, 't1066_RP_w2_dbp','10-66.1066-RuralPeru-Followup',
                         variables=list('f_bpdias'), missings = TRUE)

```

```{r local_RP2}
t1066_RP_w2_dbp <- opal.execute(o,'t1066_RP_w2_dbp')
Continuous_summary(var = t1066_RP_w2_dbp$f_bpdias, missing_values = NA)
ggplot(t1066_RP_w2_dbp, aes(f_bpdias)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable plus 4 years, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_RP2}
t1066_ds_RP_w2 <- tibble(id=t1066_RP_w2_dbp$id)
t1066_ds_RP_w2$dbp <- car::recode(t1066_RP_w2_dbp$f_bpdias, "NA=999")
t1066_ds_RP_w2$dbp <- labelled(t1066_ds_RP_w2$dbp, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_RP2}
Continuous_summary(var = t1066_ds_RP_w2$dbp, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RP_w2, aes(dbp)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency") + xlim(20,160) 
```

#### Validation
There are a variable that measures the diastolic pressure standing that is not taken into account on the average used.

```{r crosstabulation_RP2}
```







### 10/66 - Urban Mexico - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `bpdias`
* Label: `diastolic bp (average)`
* Type of variable: `countinous`

```{r assign_UM1}
opal.assign.table.tibble(o, 't1066_UM_w1_dbp','10-66.1066-UrbanMexico-Baseline',
                         variables=list('bpdias'), missings = TRUE)
```

```{r local_UM1}
t1066_UM_w1_dbp <- opal.execute(o,'t1066_UM_w1_dbp')
Continuous_summary(var = t1066_UM_w1_dbp$bpdias, missing_values = NA)
ggplot(t1066_UM_w1_dbp, aes(bpdias)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_UM1}
t1066_ds_UM_w1 <- tibble(id=t1066_UM_w1_dbp$id)
t1066_ds_UM_w1$dbp <- car::recode(t1066_UM_w1_dbp$bpdias, "NA=999")
t1066_ds_UM_w1$dbp <- labelled(t1066_ds_UM_w1$dbp, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_UM1}
Continuous_summary(var = t1066_ds_UM_w1$dbp, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UM_w1, aes(dbp)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency") + xlim(20,160) 
```

#### Validation
There are a variable that measures the diastolic pressure standing that is not taken into account on the average used.

```{r crosstabulation_UM1}
```





### 10/66 - Urban Mexico - Wave 2

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `f_bpdias`
* Label: `diastolic bp (average)`
* Type of variable: `countinous`

```{r assign_UM2}
opal.assign.table.tibble(o, 't1066_UM_w2_dbp','10-66.1066-UrbanMexico-Followup',
                         variables=list('f_bpdias'), missings = TRUE)
```

```{r local_UM2}
t1066_UM_w2_dbp <- opal.execute(o,'t1066_UM_w2_dbp')
Continuous_summary(var = t1066_UM_w2_dbp$f_bpdias, missing_values = NA)
ggplot(t1066_UM_w2_dbp, aes(f_bpdias)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable plus 3 years, but the missing values have to be recoded as follows:

* `NA into 999`


R code of the ALGORITHM:

```{r harmo_UM2}
t1066_ds_UM_w2 <- tibble(id=t1066_UM_w2_dbp$id)
t1066_ds_UM_w2$dbp <- car::recode(t1066_UM_w2_dbp$f_bpdias, "NA=999")
t1066_ds_UM_w2$dbp <- labelled(t1066_ds_UM_w2$dbp, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_UM2}
Continuous_summary(var = t1066_ds_UM_w2$dbp, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UM_w2, aes(dbp)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency") + xlim(20,160) 
```

#### Validation
There are a variable that measures the diastolic pressure standing that is not taken into account on the average used.

```{r crosstabulation_UM2}
```







### 10/66 - Rural Mexico - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `bpdias`
* Label: `diastolic bp (average)`
* Type of variable: `countinous`

```{r assign_RM1}
opal.assign.table.tibble(o, 't1066_RM_w1_dbp','10-66.1066-RuralMexico-Baseline',
                         variables=list('bpdias'), missings = TRUE)
```

```{r local_RM1}
t1066_RM_w1_dbp <- opal.execute(o,'t1066_RM_w1_dbp')
Continuous_summary(var = t1066_RM_w1_dbp$bpdias, missing_values = NA)
ggplot(t1066_RM_w1_dbp, aes(bpdias)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_RM1}
t1066_ds_RM_w1 <- tibble(id=t1066_RM_w1_dbp$id)
t1066_ds_RM_w1$dbp <- car::recode(t1066_RM_w1_dbp$bpdias, "NA=999")
t1066_ds_RM_w1$dbp <- labelled(t1066_ds_RM_w1$dbp, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_RM1}
Continuous_summary(var = t1066_ds_RM_w1$dbp, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RM_w1, aes(dbp)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency") + xlim(20,160) 
```

#### Validation
There are a variable that measures the diastolic pressure standing that is not taken into account on the average used.

```{r crosstabulation_RM1}
```





### 10/66 - Rural Mexico - Wave 2 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `f_bpdias`
* Label: `diastolic bp (average)`
* Type of variable: `countinous`

```{r assign_RM2}
opal.assign.table.tibble(o, 't1066_RM_w2_dbp','10-66.1066-RuralMexico-Followup',
                         variables=list('f_bpdias'), missings = TRUE)
```

```{r local_RM2}
t1066_RM_w2_dbp <- opal.execute(o,'t1066_RM_w2_dbp')
Continuous_summary(var = t1066_RM_w2_dbp$f_bpdias, missing_values = NA)
ggplot(t1066_RM_w2_dbp, aes(f_bpdias)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable plus 3 years, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_RM2}
t1066_ds_RM_w2 <- tibble(id=t1066_RM_w2_dbp$id)
t1066_ds_RM_w2$dbp <- car::recode(t1066_RM_w2_dbp$f_bpdias, "NA=999")
t1066_ds_RM_w2$dbp <- labelled(t1066_ds_RM_w2$dbp, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_RM2}
Continuous_summary(var = t1066_ds_RM_w2$dbp, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RM_w2, aes(dbp)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency") + xlim(20,160) 
```

#### Validation
There are a variable that measures the diastolic pressure standing that is not taken into account on the average used.

```{r crosstabulation_RM2}
```







### 10/66 - Puerto Rico - Wave 1 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `bpdias`
* Label: `diastolic bp (average)`
* Type of variable: `countinous`

```{r assign_PR1}
opal.assign.table.tibble(o, 't1066_PR_w1_dbp','10-66.1066-PuertoRico-Baseline',
                         variables=list('bpdias'), missings = TRUE)
```

```{r local_PR1}
t1066_PR_w1_dbp <- opal.execute(o,'t1066_PR_w1_dbp')
Continuous_summary(var = t1066_PR_w1_dbp$bpdias, missing_values = NA)
ggplot(t1066_PR_w1_dbp, aes(bpdias)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_PR1}
t1066_ds_PR_w1 <- tibble(id=t1066_PR_w1_dbp$id)
t1066_ds_PR_w1$dbp <- car::recode(t1066_PR_w1_dbp$bpdias, "NA=999")
t1066_ds_PR_w1$dbp <- labelled(t1066_ds_PR_w1$dbp, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_PR1}
Continuous_summary(var = t1066_ds_PR_w1$dbp, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_PR_w1, aes(dbp)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency") + xlim(20,160) 
```

#### Validation
There are a variable that measures the diastolic pressure standing that is not taken into account on the average used.

```{r crosstabulation_PR1}
```





### 10/66 - Puerto Rico - Wave 2 

#### Study-specific variables

The study-specific variable elected to be harmonised is:

* Name: `f_bpdias`
* Label: `diastolic bp (average)`
* Type of variable: `countinous`


```{r assign_PR2}
opal.assign.table.tibble(o, 't1066_PR_w2_dbp','10-66.1066-PuertoRico-Followup',
                         variables=list('f_bpdias'), missings = TRUE)
```

```{r local_PR2}
t1066_PR_w2_dbp <- opal.execute(o,'t1066_PR_w2_dbp')
Continuous_summary(var = t1066_PR_w2_dbp$f_bpdias, missing_values = NA)
ggplot(t1066_PR_w2_dbp, aes(f_bpdias)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable plus 4 years, but the missing values have to be recoded as follows:

* `NA into 999`

R code of the ALGORITHM:

```{r harmo_PR2}
t1066_ds_PR_w2 <- tibble(id=t1066_PR_w2_dbp$id)
t1066_ds_PR_w2$dbp <- car::recode(t1066_PR_w2_dbp$f_bpdias, "NA=999")
t1066_ds_PR_w2$dbp <- labelled(t1066_ds_PR_w2$dbp, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_PR2}
Continuous_summary(var = t1066_ds_PR_w2$dbp, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_PR_w2, aes(dbp)) + geom_histogram(stat="count", fill="steelblue") + xlab("Diastolic Blood Pressure") + ylab("Frequency") + xlim(20,160) 
```

#### Validation
There are a variable that measures the diastolic pressure standing that is not taken into account on the average used.

```{r crosstabulation_PR2}
```

# Quality estimation

Diastolic  bp was calculated as the mean from the 2 available variables.




```{r save, echo=FALSE}
dbp <- t1066_ds_cuba_w1
save(dbp, file = "../RData/cuba_w1/dbp.RData")
rm(dbp)

dbp <- t1066_ds_cuba_w2
save(dbp, file = "../RData/cuba_w2/dbp.RData")
rm(dbp)

dbp <- t1066_ds_india_w1
save(dbp, file = "../RData/india_w1/dbp.RData")
rm(dbp)

dbp <- t1066_ds_UCh_w1
save(dbp, file = "../RData/UCh_w1/dbp.RData")
rm(dbp)

dbp <- t1066_ds_UCh_w2
save(dbp, file = "../RData/UCh_w2/dbp.RData")
rm(dbp)

dbp <- t1066_ds_RCh_w1
save(dbp, file = "../RData/RCh_w1/dbp.RData")
rm(dbp)

dbp <- t1066_ds_RCh_w2
save(dbp, file = "../RData/RCh_w2/dbp.RData")
rm(dbp)

dbp <- t1066_ds_DR_w1
save(dbp, file = "../RData/DR_w1/dbp.RData")
rm(dbp)

dbp <- t1066_ds_DR_w2
save(dbp, file = "../RData/DR_w2/dbp.RData")
rm(dbp)

dbp <- t1066_ds_Ven_w1
save(dbp, file = "../RData/Ven_w1/dbp.RData")
rm(dbp)

dbp <- t1066_ds_Ven_w2
save(dbp, file = "../RData/Ven_w2/dbp.RData")
rm(dbp)

dbp <- t1066_ds_UP_w1
save(dbp, file = "../RData/UP_w1/dbp.RData")
rm(dbp)

dbp <- t1066_ds_UP_w2
save(dbp, file = "../RData/UP_w2/dbp.RData")
rm(dbp)

dbp <- t1066_ds_RP_w1
save(dbp, file = "../RData/RP_w1/dbp.RData")
rm(dbp)

dbp <- t1066_ds_RP_w2
save(dbp, file = "../RData/RP_w2/dbp.RData")
rm(dbp)

dbp <- t1066_ds_UM_w1
save(dbp, file = "../RData/UM_w1/dbp.RData")
rm(dbp)

dbp <- t1066_ds_UM_w2
save(dbp, file = "../RData/UM_w2/dbp.RData")
rm(dbp)

dbp <- t1066_ds_RM_w1
save(dbp, file = "../RData/RM_w1/dbp.RData")
rm(dbp)

dbp <- t1066_ds_RM_w2
save(dbp, file = "../RData/RM_w2/dbp.RData")
rm(dbp)

dbp <- t1066_ds_PR_w1
save(dbp, file = "../RData/PR_w1/dbp.RData")
rm(dbp)

dbp <- t1066_ds_PR_w2
save(dbp, file = "../RData/PR_w2/dbp.RData")
rm(dbp)

```


```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
