---
title: "Weight"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/weightDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/weightDS.R')
```

# Data process

## Cuba

### Wave 1 

There is no variable. 



### Wave 2 

#### Study-specific variable description



| **Name** | `f_WEIGHT`|
|-|-|
| **Label** | `Weight in kilograms`|
| **Table name** |`1066-Cuba-Followup`|
| **Type of variable** |`continuous`|
| **Description** |  |

```{r assign_cuba2, echo=F}
opal.assign.table.tibble(o, 't1066_cuba_w2','10-66.1066-Cuba-Followup', variables=list('f_WEIGHT'), missings = TRUE)
t1066_cuba_w2 <- opal.execute(o,'t1066_cuba_w2')
```

```{r local_cuba2, echo=F}
vbl <- t1066_cuba_w2$f_WEIGHT
vbl_miss <- c(669, 678, 781, 999.9,999)
kable(Continuous_summary(vbl, missing_values = vbl_miss)[3], caption = "f_WEIGHT")
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(t1066_cuba_w2, aes(f_WEIGHT)) + geom_histogram(stat="count", fill="steelblue",data = .%>% filter(!vbl %in% vbl_miss)) + xlab("Weight") + ylab("Frequency")
```

There are values 0 and 9 that are going to be considered as mistakes and will be recoded as 999. There are values 669, 678, 781 and 999.9 that are going to be considered as mistakes and they will be recoded as 999. 

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_cuba2}
t1066_ds_cuba_w2 <- tibble(id=t1066_cuba_w2$id)
t1066_ds_cuba_w2$weight <- car::recode(t1066_cuba_w2$f_WEIGHT, "NA=999; c(0,9)=999; c(669, 678, 781, 999.9)=999")
t1066_ds_cuba_w2$weight <- labelled(t1066_ds_cuba_w2$weight, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_cuba2, echo=F}
vbl <- t1066_ds_cuba_w2$weight
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_cuba_w2, aes(weight)) + geom_histogram(stat="count", fill="steelblue",data = .%>% filter(!vbl %in% miss_values_vector)) + xlab("weight") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_cuba2, echo=F}
BeforeH <- sum(sum(is.na(t1066_cuba_w2$f_WEIGHT)), sum(na.omit(t1066_cuba_w2$f_WEIGHT<10)), sum(na.omit(t1066_cuba_w2$f_WEIGHT>200)))
After <- sum(t1066_ds_cuba_w2$weight==999)
C <- rbind(BeforeH, After)
colnames(C) <- c("(0,9,669, 678, 781, 999, 999.9, NA)->999")
kable(C)
```






## India

### Wave 1 

There is no variable.



## Urban China

### Wave 1 

There is no variable.



### Wave 2 

#### Study-specific variable description



| **Name** | `f_WEIGHT`|
|-|-|
| **Label** | `Weight in kilograms`|
| **Table name** |`1066-UrbanChina-Followup`|
| **Type of variable** |`continuous`|
| **Description** |  |

```{r assign_UCh2, echo=F}
opal.assign.table.tibble(o, 't1066_UCh_w2','10-66.1066-UrbanChina-Followup', variables=list('f_WEIGHT'), missings = TRUE)
t1066_UCh_w2 <- opal.execute(o,'t1066_UCh_w2')
```

```{r local_UCh2, echo=F}
vbl <- t1066_UCh_w2$f_WEIGHT
vbl_miss <- c(999)
kable(Continuous_summary(vbl, missing_values = c(999))[3], caption = "f_WEIGHT")
pander(Continuous_summary(vbl, missing_values = c(999))$summary, caption = "Summary")
ggplot(t1066_UCh_w2, aes(f_WEIGHT)) + geom_histogram(stat="count", fill="steelblue",data = .%>% filter(!vbl %in% vbl_miss)) + xlab("Weight") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_UCh2}
t1066_ds_UCh_w2 <- tibble(id=t1066_UCh_w2$id)
t1066_ds_UCh_w2$weight <- car::recode(t1066_UCh_w2$f_WEIGHT, "NA=999")
t1066_ds_UCh_w2$weight <- labelled(t1066_ds_UCh_w2$weight, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_UCh2, echo=F}
vbl <- t1066_ds_UCh_w2$weight
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_UCh_w2, aes(weight)) + geom_histogram(stat="count", fill="steelblue",data = .%>% filter(!vbl %in% miss_values_vector)) + xlab("weight") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_UCh2, echo=F}
```






## Rural China

### Wave 1 

There is no variable.



### Wave 2 

#### Study-specific variable description



| **Name** | `f_WEIGHT`|
|-|-|
| **Label** | `Weight in kilograms`|
| **Table name** |`1066-RuralChina-Followup`|
| **Type of variable** |`continuous`|
| **Description** |  |

```{r assign_RCh2, echo=F}
opal.assign.table.tibble(o, 't1066_RCh_w2','10-66.1066-RuralChina-Followup', variables=list('f_WEIGHT'), missings = TRUE)
t1066_RCh_w2 <- opal.execute(o,'t1066_RCh_w2')

```

```{r local_RCh2, echo=F}
vbl <- t1066_RCh_w2$f_WEIGHT
vbl_miss <- c(999)
kable(Continuous_summary(vbl, missing_values = c(999))[3], caption = "f_WEIGHT")
pander(Continuous_summary(vbl, missing_values = c(999))$summary, caption = "Summary")
ggplot(t1066_RCh_w2, aes(f_WEIGHT)) + geom_histogram(stat="count", fill="steelblue",data = .%>% filter(!vbl %in% vbl_miss)) + xlab("Weight") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_RCh2}
t1066_ds_RCh_w2 <- tibble(id=t1066_RCh_w2$id)
t1066_ds_RCh_w2$weight <- car::recode(t1066_RCh_w2$f_WEIGHT, "NA=999")
t1066_ds_RCh_w2$weight <- labelled(t1066_ds_RCh_w2$weight, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_RCh2, echo=F}
vbl <- t1066_ds_RCh_w2$weight
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_RCh_w2, aes(weight)) + geom_histogram(stat="count", fill="steelblue",data = .%>% filter(!vbl %in% miss_values_vector)) + xlab("weight") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_RCh2, echo=F}
```






## Dominican Republic

### Wave 1 

There is no variable.






### Wave 2 

#### Study-specific variable description



| **Name** | `f_WEIGHT`|
|-|-|
| **Label** | `Weight in kilograms`|
| **Table name** |`1066-DominicanRepublic-Followup`|
| **Type of variable** |`continuous`|
| **Description** |  |


```{r assign_DR2, echo=F}
opal.assign.table.tibble(o, 't1066_DR_w2','10-66.1066-DominicanRepublic-Followup',variables=list('f_WEIGHT'), missings = TRUE)
t1066_DR_w2 <- opal.execute(o,'t1066_DR_w2')
```

```{r local_DR2, echo=F}
vbl <- t1066_DR_w2$f_WEIGHT
vbl_miss <- c(999)
kable(Continuous_summary(vbl, missing_values = c(999))[3], caption = "f_WEIGHT")
pander(Continuous_summary(vbl, missing_values = c(999))$summary, caption = "Summary")
ggplot(t1066_DR_w2, aes(f_WEIGHT)) + geom_histogram(stat="count", fill="steelblue",data = .%>% filter(!vbl %in% vbl_miss)) + xlab("Weight") + ylab("Frequency")
```

There are 40 values 999 that are going to be consider as mistakes and they will be recoded as missing.

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_DR2}
t1066_ds_DR_w2 <- tibble(id=t1066_DR_w2$id)
t1066_ds_DR_w2$weight <- car::recode(t1066_DR_w2$f_WEIGHT, "NA=999")
t1066_ds_DR_w2$weight <- labelled(t1066_ds_DR_w2$weight, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_DR2, echo=F}
vbl <- t1066_ds_DR_w2$weight
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_DR_w2, aes(weight)) + geom_histogram(stat="count", fill="steelblue",data = .%>% filter(!vbl %in% miss_values_vector)) + xlab("weight") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_DR2, echo=F}
```






## Venezuela

### Wave 1 

There are no variable.



### Wave 2 

#### Study-specific variable description



| **Name** | `f_WEIGHT`|
|-|-|
| **Label** | `Weight in kilograms`|
| **Table name** |`1066-Venezuela-Followup`|
| **Type of variable** |`continuous`|
| **Description** |  |

```{r assign_V2, echo=F}
opal.assign.table.tibble(o, 't1066_Ven_w2','10-66.1066-Venezuela-Followup',variables=list('f_WEIGHT'), missings = TRUE)
t1066_Ven_w2 <- opal.execute(o,'t1066_Ven_w2')

```

```{r local_V2, echo=F}
vbl <- t1066_Ven_w2$f_WEIGHT
vbl_miss <- c(999)
kable(Continuous_summary(vbl, missing_values = c(999))[3], caption = "f_WEIGHT")
pander(Continuous_summary(vbl, missing_values = c(999))$summary, caption = "Summary")
ggplot(t1066_Ven_w2, aes(f_WEIGHT)) + geom_histogram(stat="count", fill="steelblue",data = .%>% filter(!vbl %in% vbl_miss)) + xlab("Weight") + ylab("Frequency") 
```



#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_V2}
t1066_ds_Ven_w2 <- tibble(id=t1066_Ven_w2$id)
t1066_ds_Ven_w2$weight <- car::recode(t1066_Ven_w2$f_WEIGHT, "NA=999")
t1066_ds_Ven_w2$weight <- labelled(t1066_ds_Ven_w2$weight, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_V2, echo=F}
vbl <- t1066_ds_Ven_w2$weight
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_Ven_w2, aes(weight)) + geom_histogram(stat="count", fill="steelblue",data = .%>% filter(!vbl %in% miss_values_vector)) + xlab("weight") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_V2, echo=F}
```






## Urban Peru

### Wave 1 

There is no variable.




### Wave 2 

#### Study-specific variable description



| **Name** | `f_WEIGHT`|
|-|-|
| **Label** | `Weight in kilograms`|
| **Table name** |`1066-UrbanPeru-Followup`|
| **Type of variable** |`continuous`|
| **Description** |  |

```{r assign_UP2, echo=F}
opal.assign.table.tibble(o, 't1066_UP_w2','10-66.1066-UrbanPeru-Followup',variables=list('f_WEIGHT'), missings = TRUE)
t1066_UP_w2 <- opal.execute(o,'t1066_UP_w2')

```

```{r local_UP2, echo=F}
vbl <- t1066_UP_w2$f_WEIGHT
vbl_miss <- c(999)
kable(Continuous_summary(vbl, missing_values = c(999))[3], caption = "f_WEIGHT")
pander(Continuous_summary(vbl, missing_values = c(999))$summary, caption = "Summary")
ggplot(t1066_UP_w2, aes(f_WEIGHT)) + geom_histogram(stat="count", fill="steelblue",data = .%>% filter(!vbl %in% vbl_miss)) + xlab("Weight") + ylab("Frequency") 
```



#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`


**R script:**

```{r harmo_UP2}
t1066_ds_UP_w2 <- tibble(id=t1066_UP_w2$id)
t1066_ds_UP_w2$weight <- car::recode(t1066_UP_w2$f_WEIGHT, "NA=999")
t1066_ds_UP_w2$weight <- labelled(t1066_ds_UP_w2$weight, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_UP2, echo=F}
vbl <- t1066_ds_UP_w2$weight
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_UP_w2, aes(weight)) + geom_histogram(stat="count", fill="steelblue",data = .%>% filter(!vbl %in% miss_values_vector)) + xlab("weight") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_UP2, echo=F}
```






## Rural Peru

### Wave 1 

There is no variable.






### Wave 2 

#### Study-specific variable description



| **Name** | `f_WEIGHT`|
|-|-|
| **Label** | `Weight in kilograms`|
| **Table name** |`1066-RuralPeru-Followup`|
| **Type of variable** |`continuous`|
| **Description** |  |


```{r assign_RP2, echo=F}
opal.assign.table.tibble(o, 't1066_RP_w2','10-66.1066-RuralPeru-Followup',variables=list('f_WEIGHT'), missings = TRUE)
t1066_RP_w2 <- opal.execute(o,'t1066_RP_w2')
```

```{r local_RP2, echo=F}
vbl <- t1066_RP_w2$f_WEIGHT
vbl_miss <- c(999)
kable(Continuous_summary(vbl, missing_values = c(999))[3], caption = "f_WEIGHT")
pander(Continuous_summary(vbl, missing_values = c(999))$summary, caption = "Summary")
ggplot(t1066_RP_w2, aes(f_WEIGHT)) + geom_histogram(stat="count", fill="steelblue",data = .%>% filter(!vbl %in% vbl_miss)) + xlab("Weight") + ylab("Frequency") 
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_RP2}
t1066_ds_RP_w2 <- tibble(id=t1066_RP_w2$id)
t1066_ds_RP_w2$weight <- car::recode(t1066_RP_w2$f_WEIGHT, "NA=999")
t1066_ds_RP_w2$weight <- labelled(t1066_ds_RP_w2$weight, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_RP2, echo=F}
vbl <- t1066_ds_RP_w2$weight
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_RP_w2, aes(weight)) + geom_histogram(stat="count", fill="steelblue",data = .%>% filter(!vbl %in% miss_values_vector)) + xlab("weight") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_RP2, echo=F}
```







## Urban Mexico

### Wave 1 

There is no variable.






### Wave 2

#### Study-specific variable description



| **Name** | `f_WEIGHT`|
|-|-|
| **Label** | `Weight in kilograms`|
| **Table name** |`1066-UrbanMexico-Followup`|
| **Type of variable** |`continuous`|
| **Description** |  |

```{r assign_UM2, echo=F}
opal.assign.table.tibble(o, 't1066_UM_w2','10-66.1066-UrbanMexico-Followup',variables=list('f_WEIGHT'), missings = TRUE)
t1066_UM_w2 <- opal.execute(o,'t1066_UM_w2')

```

```{r local_UM2, echo=F}
vbl <- t1066_UM_w2$f_WEIGHT
vbl_miss <- c(999)
kable(Continuous_summary(vbl, missing_values = c(999))[3], caption = "f_WEIGHT")
pander(Continuous_summary(vbl, missing_values = c(999))$summary, caption = "Summary")
ggplot(t1066_UM_w2, aes(f_WEIGHT)) + geom_histogram(stat="count", fill="steelblue",data = .%>% filter(!vbl %in% vbl_miss)) + xlab("Weight") + ylab("Frequency") 
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`


**R script:**

```{r harmo_UM2}
t1066_ds_UM_w2 <- tibble(id=t1066_UM_w2$id)
t1066_ds_UM_w2$weight <- car::recode(t1066_UM_w2$f_WEIGHT, "NA=999")
t1066_ds_UM_w2$weight <- labelled(t1066_ds_UM_w2$weight, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_UM2, echo=F}
vbl <- t1066_ds_UM_w2$weight
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_UM_w2, aes(weight)) + geom_histogram(stat="count", fill="steelblue",data = .%>% filter(!vbl %in% miss_values_vector)) + xlab("weight") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_UM2, echo=F}
```







## Rural Mexico

### Wave 1 

There is no variable




### Wave 2 

#### Study-specific variable description



| **Name** | `f_WEIGHT`|
|-|-|
| **Label** | `Weight in kilograms`|
| **Table name** |`1066-RuralMexico-Followup`|
| **Type of variable** |`continuous`|
| **Description** |  |


```{r assign_RM2, echo=F}
opal.assign.table.tibble(o, 't1066_RM_w2','10-66.1066-RuralMexico-Followup',variables=list('f_WEIGHT'), missings = TRUE)
t1066_RM_w2 <- opal.execute(o,'t1066_RM_w2')

```

```{r local_RM2, echo=F}
vbl <- t1066_RM_w2$f_WEIGHT
vbl_miss <- c(999)
kable(Continuous_summary(vbl, missing_values = c(999))[3], caption = "f_WEIGHT")
pander(Continuous_summary(vbl, missing_values = c(999))$summary, caption = "Summary")
ggplot(t1066_RM_w2, aes(f_WEIGHT)) + geom_histogram(stat="count", fill="steelblue",data = .%>% filter(!vbl %in% vbl_miss)) + xlab("Weight") + ylab("Frequency") 
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA as 999`

**R script:**

```{r harmo_RM2}
t1066_ds_RM_w2 <- tibble(id=t1066_RM_w2$id)
t1066_ds_RM_w2$weight <- car::recode(t1066_RM_w2$f_WEIGHT, "NA=999")
t1066_ds_RM_w2$weight <- labelled(t1066_ds_RM_w2$weight, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_RM2, echo=F}
vbl <- t1066_ds_RM_w2$weight
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_RM_w2, aes(weight)) + geom_histogram(stat="count", fill="steelblue",data = .%>% filter(!vbl %in% miss_values_vector)) + xlab("weight") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_RM2, echo=F}
```








## Puerto Rico

### Wave 1 

There are no variable.





### Wave 2 

#### Study-specific variable description



| **Name** | `f_WEIGHT`|
|-|-|
| **Label** | `Weight in kilograms`|
| **Table name** |`1066--Followup`|
| **Type of variable** |`continuous`|
| **Description** |  |

```{r assign_PR2, echo=F}
opal.assign.table.tibble(o, 't1066_PR_w2','10-66.1066-PuertoRico-Followup', variables=list('f_WEIGHT'), missings = TRUE)
t1066_PR_w2 <- opal.execute(o,'t1066_PR_w2')

```

```{r local_PR2, echo=F}
vbl <- t1066_PR_w2$f_WEIGHT
vbl_miss <- c(999)
kable(Continuous_summary(vbl, missing_values = c(999))[3], caption = "f_WEIGHT")
pander(Continuous_summary(vbl, missing_values = c(999))$summary, caption = "Summary")
ggplot(t1066_PR_w2, aes(f_WEIGHT)) + geom_histogram(stat="count", fill="steelblue",data = .%>% filter(!vbl %in% vbl_miss)) + xlab("Weight") + ylab("Frequency") 
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo_PR2}
t1066_ds_PR_w2 <- tibble(id=t1066_PR_w2$id)
t1066_ds_PR_w2$weight <- car::recode(t1066_PR_w2$f_WEIGHT, "NA=999")
t1066_ds_PR_w2$weight <- labelled(t1066_ds_PR_w2$weight, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_PR2, echo=F}
vbl <- t1066_ds_PR_w2$weight
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(t1066_ds_PR_w2, aes(weight)) + geom_histogram(stat="count", fill="steelblue",data = .%>% filter(!vbl %in% miss_values_vector)) + xlab("weight") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_PR2, echo=F}
```







## Summary of descriptive statistics of the harmonised variable accross populations and waves

```{r helpfunctions, echo=F}

labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cont_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables

summaries <- function(l.hds,m.hds,lnames){

  # Creation of column with summary table categories
  t.summ <- summary(m.hds[[1]][2])[1:6]
  # Adding of missing/no-missing values categories
  t.hds <- c(substr(t.summ,1,regexpr(":", t.summ, fixed=T)-1),labels(Continuous_summary(l.hds[[1]][[2]],missing_values = miss_values_vector)$values_table)[[2]])
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    # First, summary values
    t.summ <- summary(m.hds[[i]][2])[1:6]
    # Next, missing/no-missing values
    t.hds <- cbind(t.hds,c(as.numeric(substr(t.summ,regexpr(":", t.summ, fixed=T)+1,nchar(t.summ))),as.numeric(Continuous_summary(l.hds[[i]][[2]],missing_values = miss_values_vector)$values_table[1,])))
  }
  # Add sample size for each wave/population
  t.hds <- rbind(t.hds,c("sample size", sapply(l.hds,function(wave) length(wave[[1]]))))
  # Add wave/population names
  dimnames(t.hds)[[2]] <- c(dimnames(summary(m.hds[[1]][2]))[[2]],lnames)
  return(t.hds)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }
  
}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names

b1066.cw <- list(cuba_w1 = c("cuba_w1","Cuba w1"), india_w1 = c("india_w1","India w1"), UCh_w1 = c("UCh_w1","Urban China w1"), RCh_w1 = c("RCh_w1","Rural China w1"), DR_w1 = c("DR_w1","Dominican Republic w1"), Ven_w1 = c("Ven_w1","Venezuela w1"), UP_w1 = c("UP_w1","Urban Peru w1"), RP_w1 = c("RP_w1","Rural Peru w1"), UM_w1 = c("UM_w1","Urban Mexico w1"), RM_w1 = c("RM_w1","Rural Mexico w1"), PR_w1 = c("PR_w1","Puerto Rico w1"))

f1066.cw <- list(cuba_w2 = c("cuba_w2","Cuba w2"), UCh_w2 = c("UCh_w2","Urban China w2"), RCh_w2 = c("RCh_w2","Rural China w2"), DR_w2 = c("DR_w2","Dominican Republic w2"), Ven_w2 = c("Ven_w2","Venezuela w2"), UP_w2 = c("UP_w2","Urban Peru w2"), RP_w2 = c("RP_w2","Rural Peru w2"), UM_w2 = c("UM_w2","Urban Mexico w2"), RM_w2 = c("RM_w2","Rural Mexico w2"), PR_w2 = c("PR_w2","Puerto Rico w2"))


# Consider only harmonised waves
l.hds <- lapply(b1066.cw, function(wname) if(exists(paste0("t1066_ds_",wname[1]))){wname = list(get(paste0("t1066_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}




# Consider only harmonised waves
l.hds <- lapply(f1066.cw, function(wname) if(exists(paste0("t1066_ds_",wname[1]))){wname = list(get(paste0("t1066_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing summaries
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}




```





# Quality estimation
Anthropometric measure.


```{r closeRsession, echo=FALSE} 
opal.logout(o)
```