---
title: "Current depressive status"
output: 
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->



```{r setup, include=FALSE, echo=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_albert.r")
```

<!-- ########################################################## --> 

# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `depression`
* Variable label: `Current depressive status of the participant`
* Variable description: `Current depressive status of the participant`
* Domain: `Psycological measures`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | no depression
1        | depression

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing


```{r lab, echo=FALSE}
ds_label <- "Current depressive status"
ds_label_all <- "Current depressive status of the participant"
```

# Data process

## Metropolitan Athens area

### Wave 1

#### Study-specific variable description

The study-specific variables elected to be harmonised are:

| **Name** | `zung`|
|-|-|
| **Label** | `Zung Depression scale`|
| **Table name** | `ATTICA_Baseline` |
| **Description** |  |

```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'ATTICA_dep','ATTICA.ATTICA_Baseline',
                         variables=list('zung'), missings = TRUE)
ATTICA_dep <- opal.execute(o,'ATTICA_dep')
```

```{r local11, echo=FALSE}
vari <- ATTICA_dep[[2]]
kable(Continuous_summary(vari, missing_values = NA)[3], caption = ds_label) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(ATTICA_dep, aes(ATTICA_dep[[2]])) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

###### Harmonisation algorithm

To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `zung < 49 into 0` 
* `zung >= 50 into 1`
* `NA into 999`

```{r harmo11}
ATTICA_ds_w1 <- tibble(id=ATTICA_dep$id)
ATTICA_ds_w1$depression <- car::recode(ATTICA_dep[[2]], "lo:49=0; 50:hi=1; NA=999")
ATTICA_ds_w1$depression <- labelled(ATTICA_ds_w1[[2]], labels = c("no depression"=0, "depression"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

###### Statistical description of the new harmonised variable
```{r descript11, echo=FALSE}
vari <- ATTICA_ds_w1$depression
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(ATTICA_ds_w1, aes(x=factor(ATTICA_ds_w1[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

###### Validation
```{r crosstab11, echo=FALSE}
BeforeH <- c(sum(na.omit(ATTICA_dep[[2]])<50),sum(na.omit(ATTICA_dep[[2]])>=50), sum(is.na(ATTICA_dep[[2]])))
AfterH <- table(ATTICA_ds_w1[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<50->0",">=50->1","NA->999") 
kable(C)
```


```{r read, include=FALSE}
rm(ATTICA_dep)
```

```{r save, echo=FALSE}
depression <- ATTICA_ds_w1
save(depression, file = "../RData/w1/depression.RData")
rm(depression)
```

### Wave 2

There is no variable.

### Wave 3

There is no variable.



# Quality estimation

The Zung Self-Rating Depression Scale is used.
A ZDRS score below 50 is considered normal; a score of 50-59 indicates mild depression, a score of 60-69 indicates moderate depression, and a score of 70 or more is considered to be indicative of severe depression (paper) = 50
Variable available only in the first wave.



```{r closeRsession, echo=FALSE}
opal.logout(o)
```

