---
title: "Year of Birth"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```
<!-- ########################################################## --> 

# Description of DataSchema variable 

The description of harmonised variable is the following:


* Short name: `ybirth`
* Variable label: `year of birth`
* Variable description: `Year of birth`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

## Cuba

### Wave 1 

#### Study-specific variable description


| **Name**        | `age` | `DATE` |
|-----------------|-|-|
| **Label**       | `participant age in years` | `date of baseline interview` |
| **Table name**  | `1066-Cuba-Baseline` | `1066-Cuba-Baseline` |
| **Description** |  |  |



```{r assign_cuba1, echo=F}
opal.assign.table.tibble(o, 't1066_cuba_w1_ybirth','10-66.1066-Cuba-Baseline',
                         variables=list('age', 'DATE'), missings = TRUE)
t1066_cuba_w1_ybirth <- opal.execute(o,'t1066_cuba_w1_ybirth')
```

```{r local_cuba1, echo=F}
t1066_cuba_w1_ybirth$yinter <- as.numeric(format(t1066_cuba_w1_ybirth$DATE, '%Y'))

vari <-t1066_cuba_w1_ybirth$age # VARIABLE
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_cuba_w1_ybirth$age, missing_values = NA)
ggplot(t1066_cuba_w1_ybirth, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")

vari <- t1066_cuba_w1_ybirth$yinter # VARIABLE
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "YEAR OF INTERVIEW") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_cuba_w1_ybirth$yinter, missing_values = NA)


ggplot(t1066_cuba_w1_ybirth, aes(yinter)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of interview") + ylab("Frequency") + xlim(2002,2007)
```

The value `2206` in `year of interview` is considered a mistake and it is changed to `2006`. The value `NA` in `year or interview` is changed to `2004` as the most frecuent value. 


#### Harmonisation algorithm
The variable `year of birth` follows the formula: 
* `year of birth` = `year of interview` - `age`

Missing values is recoded as follows: 
* `NA into 999`


**R script:**
```{r harmo_cuba1}
t1066_ds_cuba_w1 <- tibble(id=t1066_cuba_w1_ybirth$id)

t1066_cuba_w1_ybirth$age <- t1066_cuba_w1_ybirth$age
t1066_cuba_w1_ybirth$year_of_interview <- t1066_cuba_w1_ybirth$yinter
t1066_cuba_w1_ybirth$year_of_interview <- car::recode(t1066_cuba_w1_ybirth$yinter, "NA=2004; 2206=2006")

t1066_ds_cuba_w1$ybirth <- t1066_cuba_w1_ybirth$year_of_interview - t1066_cuba_w1_ybirth$age
t1066_ds_cuba_w1$ybirth <- car::recode(t1066_ds_cuba_w1$ybirth, "NA=999")

t1066_ds_cuba_w1$ybirth <- labelled(t1066_ds_cuba_w1$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_cuba1, echo=F}
vari <- t1066_ds_cuba_w1$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
#Continuous_summary(var = t1066_ds_cuba_w1$ybirth, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_cuba_w1, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1904,1941)
```

#### Validation
```{r crosstabulation_cuba1, echo=F}
```


### Wave 2

#### Study-specific variable description


| **Name**        | `age` | `DATE` |
|-----------------|-|-|
| **Label**       | `participant age in years` | `date of baseline interview` |
| **Table name**  | `1066-Cuba-Baseline` | `1066-Cuba-Baseline` |
| **Description** |  |  |

```{r assign_cuba2, echo=F}
opal.assign.table.tibble(o, 't1066_cuba_w1_ybirth','10-66.1066-Cuba-Baseline',
                         variables=list('age', 'DATE'), missings = TRUE)
opal.assign.table.tibble(o, 't1066_cuba_w2_id','10-66.1066-Cuba-Followup',
                         variables=list('centreid'), missings = TRUE)
```

```{r local_cuba2, echo=F}
t1066_cuba_w1_ybirth <- opal.execute(o,'t1066_cuba_w1_ybirth')
t1066_cuba_w2_id <- opal.execute(o,'t1066_cuba_w2_id')

t1066_cuba_w1_ybirth$yinter <- as.numeric(format(t1066_cuba_w1_ybirth$DATE, '%Y'))

vari <- t1066_cuba_w1_ybirth$age # VARIABLE
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) # SI NO HAY ATRIBUTO SHORT-NAME, A MANO
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_cuba_w1_ybirth$age, missing_values = NA)
ggplot(t1066_cuba_w1_ybirth, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")

vari <- t1066_cuba_w1_ybirth$yinter # VARIABLE
kable(Continuous_summary(vari, missing_values = NA)[3], caption="YEAR OF INTERVIEW") # SI NO HAY ATRIBUTO SHORT-NAME, A MANO
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_cuba_w1_ybirth$yinter, missing_values = NA)


ggplot(t1066_cuba_w1_ybirth, aes(yinter)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of interview") + ylab("Frequency") + xlim(2002,2007)
```

There is a value 2206 in year of interview that is going to consider as a 2006 because it is consider a write mistake. The value NA in year or interview is going to be computed as 2004 since is the most frecuent value. 


#### Harmonisation algorithm
To harmonize the year of birth is going to use the following formula:
year_of_birth = Year_of_interview - age
Recoding the missing values as follows: 

* `NA into 999`

**R script:**

```{r harmo_cuba2}
t1066_cuba_w1_ybirth$year_of_interview <- car::recode(t1066_cuba_w1_ybirth$yinter, "NA=2004; 2206=2006")

t1066_cuba_w1_ybirth$year_of_birth <- t1066_cuba_w1_ybirth$year_of_interview - t1066_cuba_w1_ybirth$age

t1066_cuba_w1_ybirth <- t1066_cuba_w1_ybirth[,-c(2:5)]

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], year_of_birth=as.numeric(new_2[,2]))
  new_22
}


t1066_cuba_w2_ybirth <- Add_indiv(old = t1066_cuba_w1_ybirth, new = t1066_cuba_w2_id)

t1066_ds_cuba_w2 <- tibble(id=t1066_cuba_w2_ybirth$id)
t1066_ds_cuba_w2$ybirth <- car::recode(t1066_cuba_w2_ybirth$year_of_birth, "NA=999")
t1066_ds_cuba_w2$ybirth <- labelled(t1066_ds_cuba_w2$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_cuba2, echo=F}
vari <- t1066_ds_cuba_w2$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
#Continuous_summary(var = t1066_ds_cuba_w2$ybirth, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_cuba_w2, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1904,1941)
```

#### Validation
```{r crosstabulation_cuba2, echo=F}
```


## India

### Wave 1

#### Study-specific variable description

| **Name**        | `age` | `DATE` |
|-----------------|-|-|
| **Label**       | `participant age in years` | `date of baseline interview` |
| **Table name**  | `1066-India-Baseline` | `1066-India-Baseline` |
| **Description** |  |  |



```{r assign_india1, echo=F}
opal.assign.table.tibble(o, 't1066_india_w1_ybirth','10-66.1066-India-Baseline',
                         variables=list('age', 'DATE'), missings = TRUE)
```

```{r local_india1, echo=F}
t1066_india_w1_ybirth <- opal.execute(o,'t1066_india_w1_ybirth')

t1066_india_w1_ybirth$yinter <- as.numeric(format(t1066_india_w1_ybirth$DATE, '%Y'))

vari <- t1066_india_w1_ybirth$age # VARIABLE
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) # SI NO HAY ATRIBUTO SHORT-NAME, A MANO
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_india_w1_ybirth$age, missing_values = NA)
ggplot(t1066_india_w1_ybirth, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")

vari <- t1066_india_w1_ybirth$yinter # VARIABLE
kable(Continuous_summary(vari, missing_values = NA)[3], caption="YEAR OF INTERVIEW") # SI NO HAY ATRIBUTO SHORT-NAME, A MANO
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_india_w1_ybirth$yinter, missing_values = NA)


ggplot(t1066_india_w1_ybirth, aes(yinter)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of interview") + ylab("Frequency") + xlim(2002,2007)
```

The values NA in year or interview are going to be computed as 2004 since is the most frecuent value. 

#### Harmonisation algorithm
To harmonize the year of birth is going to use the following formula:
year_of_birth = Year_of_interview - age
Recoding the missing values as follows: 

* `NA into 999`

**R script:**

```{r harmo_india1}
t1066_india_w1_ybirth$age <- t1066_india_w1_ybirth$age
t1066_india_w1_ybirth$year_of_interview <- car::recode(t1066_india_w1_ybirth$yinter, "NA=2004")


t1066_ds_india_w1 <- tibble(id=t1066_india_w1_ybirth$id)
t1066_ds_india_w1$ybirth <- t1066_india_w1_ybirth$year_of_interview - t1066_india_w1_ybirth$age
t1066_ds_india_w1$ybirth <- car::recode(t1066_ds_india_w1$ybirth, "NA=999")
t1066_ds_india_w1$ybirth <- labelled(t1066_ds_india_w1$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_india1, echo=F}
vari <- t1066_ds_india_w1$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
#Continuous_summary(var = t1066_ds_india_w1$ybirth, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_india_w1, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1904,1941)
```

#### Validation
```{r crosstabulation_india1, echo=F}
```


### Wave 2

#### Study-specific variable description

| **Name**        | `age` | `DATE` |
|-----------------|-|-|
| **Label**       | `participant age in years` | `date of baseline interview` |
| **Table name**  | `1066-India-Baseline` | `1066-India-Baseline` |
| **Description** |  |  |




```{r assign_india2, echo=F}
opal.assign.table.tibble(o, 't1066_india_w1_ybirth','10-66.1066-India-Baseline',
                         variables=list('age', 'DATE'), missings = TRUE)
opal.assign.table.tibble(o, 't1066_india_w2_id','10-66.1066-India-Followup',
                         variables=list('fu_DATE'), missings = TRUE)
```

```{r local_india2, echo=F}
t1066_india_w1_ybirth <- opal.execute(o,'t1066_india_w1_ybirth')
t1066_india_w2_id <- opal.execute(o,'t1066_india_w2_id')

t1066_india_w1_ybirth$yinter <- as.numeric(format(t1066_india_w1_ybirth$DATE, '%Y'))

vari <- t1066_india_w1_ybirth$age # VARIABLE
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`) 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_india_w1_ybirth$age, missing_values = NA)
ggplot(t1066_india_w1_ybirth, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")

vari <- t1066_india_w1_ybirth$yinter # VARIABLE
kable(Continuous_summary(vari, missing_values = NA)[3], caption="YEAR OF INTERVIEW") 
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_india_w1_ybirth$yinter, missing_values = NA)

ggplot(t1066_india_w1_ybirth, aes(yinter)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of interview") + ylab("Frequency") + xlim(2002,2007)
```

The values NA in year or interview are going to be computed as 2004 since is the most frecuent value. 

#### Harmonisation algorithm
To harmonize the year of birth is going to use the following formula:
year_of_birth = Year_of_interview - age
Recoding the missing values as follows: 

* `NA into 999`

**R script:**

```{r harmo_india2}
t1066_india_w1_ybirth$year_of_interview <- car::recode(t1066_india_w1_ybirth$yinter, "NA=2004")

t1066_india_w1_ybirth$year_of_birth <- t1066_india_w1_ybirth$year_of_interview - t1066_india_w1_ybirth$age

t1066_india_w1_ybirth <- t1066_india_w1_ybirth[,-c(2:5)]


Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], year_of_birth=as.numeric(new_2[,2]))
  new_22
}


t1066_india_w2_ybirth <- Add_indiv(old = t1066_india_w1_ybirth, new = t1066_india_w2_id)

t1066_ds_india_w2 <- tibble(id=t1066_india_w2_ybirth$id)
t1066_ds_india_w2$ybirth <- car::recode(t1066_india_w2_ybirth$year_of_birth, "NA=999")
t1066_ds_india_w2$ybirth <- labelled(t1066_ds_india_w2$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_india2, echo=F}
vari <- t1066_ds_india_w2$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
#Continuous_summary(var = t1066_ds_india_w2$ybirth, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_india_w2, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1904,1941)
```

#### Validation
```{r crosstabulation_india2, echo=F}
```




## Urban China

### Wave 1

#### Study-specific variable description

| **Name**        | `age` | `DATE` |
|-----------------|-|-|
| **Label**       | `participant age in years` | `date of baseline interview` |
| **Table name**  | `1066-UrbanChina-Baseline` | `1066-UrbanChina-Baseline` |
| **Description** |  |  |



```{r assign_UCh1, echo=F}
opal.assign.table.tibble(o, 't1066_UCh_w1_ybirth','10-66.1066-UrbanChina-Baseline',
                         variables=list('age','DATE'), missings = TRUE)
```

```{r local_UCh1, echo=F}
t1066_UCh_w1_ybirth <- opal.execute(o,'t1066_UCh_w1_ybirth')
t1066_UCh_w1_ybirth$yinter <- as.numeric(format(t1066_UCh_w1_ybirth$DATE, '%Y'))

vari <- t1066_UCh_w1_ybirth$age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`)
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_UCh_w1_ybirth$age, missing_values = NA)
ggplot(t1066_UCh_w1_ybirth, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")

vari <- t1066_UCh_w1_ybirth$yinter
kable(Continuous_summary(vari, missing_values = NA)[3], caption="YEAR OF INTERVIEW")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_UCh_w1_ybirth$yinter, missing_values = NA)
ggplot(t1066_UCh_w1_ybirth, aes(yinter)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of interview") + ylab("Frequency") + xlim(2002,2007)
```

#### Harmonisation algorithm
To harmonize the year of birth is going to use the following formula:
year_of_birth = Year_of_interview - age
Recoding the missing values as follows: 

* `NA into 999`

**R script:**

```{r harmo_UCh1}
t1066_ds_UCh_w1 <- tibble(id=t1066_UCh_w1_ybirth$id)
t1066_UCh_w1_ybirth$age <- t1066_UCh_w1_ybirth$age
t1066_UCh_w1_ybirth$year_of_interview <- t1066_UCh_w1_ybirth$yinter

t1066_ds_UCh_w1$ybirth <- t1066_UCh_w1_ybirth$year_of_interview - t1066_UCh_w1_ybirth$age
t1066_ds_UCh_w1$ybirth <- car::recode(t1066_ds_UCh_w1$ybirth, "NA=999")
t1066_ds_UCh_w1$ybirth <- labelled(t1066_ds_UCh_w1$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_UCh1, echo=F}
vari <- t1066_ds_UCh_w1$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
#Continuous_summary(var = t1066_ds_UCh_w1$ybirth, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UCh_w1, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1904,1941)
```

#### Validation
```{r crosstabulation_UCh1, echo=F}
```


### Wave 2

#### Study-specific variable description

| **Name**        | `age` | `DATE` |
|-----------------|-|-|
| **Label**       | `participant age in years` | `date of baseline interview` | 
| **Table name**  | `1066-UrbanChina-Baseline` | `1066-UrbanChina-Baseline` |
| **Description** |  |  |


```{r assign_UCh2, echo=F}
opal.assign.table.tibble(o, 't1066_UCh_w1_ybirth','10-66.1066-UrbanChina-Baseline',
                         variables=list('age','DATE'), missings = TRUE)
opal.assign.table.tibble(o, 't1066_UCh_w2_id','10-66.1066-UrbanChina-Followup',
                         variables=list('centreid'), missings = TRUE)
```

```{r local_UCh2, echo=F}
t1066_UCh_w1_ybirth <- opal.execute(o,'t1066_UCh_w1_ybirth')
t1066_UCh_w2_id <- opal.execute(o,'t1066_UCh_w2_id')

t1066_UCh_w1_ybirth$yinter <- as.numeric(format(t1066_UCh_w1_ybirth$DATE, '%Y'))

vari <- t1066_UCh_w1_ybirth$age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`)
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_UCh_w1_ybirth$age, missing_values = NA)
ggplot(t1066_UCh_w1_ybirth, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")

vari <- t1066_UCh_w1_ybirth$yinter
kable(Continuous_summary(vari, missing_values = NA)[3], caption="YEAR OF INTERVIEW")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_UCh_w1_ybirth$yinter, missing_values = NA)


ggplot(t1066_UCh_w1_ybirth, aes(yinter)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of interview") + ylab("Frequency") + xlim(2002,2007)
```

#### Harmonisation algorithm
To harmonize the year of birth is going to use the following formula:
year_of_birth = Year_of_interview - age
Recoding the missing values as follows: 

* `NA into 999`

**R script:**

```{r harmo_UCh2}
t1066_UCh_w1_ybirth$year_of_interview <- t1066_UCh_w1_ybirth$yinter

t1066_UCh_w1_ybirth$year_of_birth <- t1066_UCh_w1_ybirth$year_of_interview - t1066_UCh_w1_ybirth$age

t1066_UCh_w1_ybirth <- t1066_UCh_w1_ybirth[,-c(2:5)]

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], year_of_birth=as.numeric(new_2[,2]))
  new_22
}


t1066_UCh_w2_ybirth <- Add_indiv(old = t1066_UCh_w1_ybirth, new = t1066_UCh_w2_id)


t1066_ds_UCh_w2 <- tibble(id=t1066_UCh_w2_ybirth$id)
t1066_ds_UCh_w2$ybirth <- car::recode(t1066_UCh_w2_ybirth$year_of_birth, "NA=999")
t1066_ds_UCh_w2$ybirth <- labelled(t1066_ds_UCh_w2$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_UCh2, echo=F}
vari <- t1066_ds_UCh_w2$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
#Continuous_summary(var = t1066_ds_UCh_w2$ybirth, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UCh_w2, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1904,1941)
```

#### Validation
```{r crosstabulation_UCh2, echo=F}
```


## Rural China

### Wave 1

#### Study-specific variable description

| **Name**        | `age` | `DATE` |
|-----------------|-|-|
| **Label**       | `participant age in years` | `date of baseline interview` |
| **Table name**  | `1066-RuralChina-Baseline` | `1066-RuralChina-Baseline` |
| **Description** |  |  |




```{r assign_RCh1, echo=F}
opal.assign.table.tibble(o, 't1066_RCh_w1_ybirth','10-66.1066-RuralChina-Baseline',
                         variables=list('age', 'DATE'), missings = TRUE)
```

```{r local_RCh1, echo=F}
t1066_RCh_w1_ybirth <- opal.execute(o,'t1066_RCh_w1_ybirth')
t1066_RCh_w1_ybirth$yinter <- as.numeric(format(t1066_RCh_w1_ybirth$DATE, '%Y'))

vari <-  t1066_RCh_w1_ybirth$age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`)
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_RCh_w1_ybirth$age, missing_values = NA)
ggplot(t1066_RCh_w1_ybirth, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")

vari <- t1066_RCh_w1_ybirth$yinter
kable(Continuous_summary(vari, missing_values = NA)[3], caption="YEAR OF INTERVIEW")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_RCh_w1_ybirth$yinter, missing_values = NA)


ggplot(t1066_RCh_w1_ybirth, aes(yinter)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of interview") + ylab("Frequency") + xlim(2002,2007)
```

#### Harmonisation algorithm
To harmonize the year of birth is going to use the following formula:
year_of_birth = Year_of_interview - age
Recoding the missing values as follows: 

* `NA into 999`

**R script:**

```{r harmo_RCh1}
t1066_RCh_w1_ybirth$age <- t1066_RCh_w1_ybirth$age
t1066_RCh_w1_ybirth$year_of_interview <- t1066_RCh_w1_ybirth$yinter

t1066_ds_RCh_w1 <- tibble(id=t1066_RCh_w1_ybirth$id)
t1066_ds_RCh_w1$ybirth <- t1066_RCh_w1_ybirth$year_of_interview - t1066_RCh_w1_ybirth$age
t1066_ds_RCh_w1$ybirth <- car::recode(t1066_ds_RCh_w1$ybirth, "NA=999")
t1066_ds_RCh_w1$ybirth <- labelled(t1066_ds_RCh_w1$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_RCh1, echo=F}
vari <- t1066_ds_RCh_w1$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
#Continuous_summary(var = t1066_ds_RCh_w1$ybirth, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RCh_w1, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_RCh1, echo=F}
```




### Wave 2

#### Study-specific variable description

| **Name**        | `age` | `DATE` |
|-----------------|-|-|
| **Label**       | `participant age in years` | `date of baseline interview` |
| **Table name**  | `1066-RuralChina-Baseline` | `1066-RuralChina-Baseline` |
| **Description** |  |  |


```{r assign_RCh2, echo=F}
opal.assign.table.tibble(o, 't1066_RCh_w1_ybirth','10-66.1066-RuralChina-Baseline',
                         variables=list('age', 'DATE'), missings = TRUE)
opal.assign.table.tibble(o, 't1066_RCh_w2_id','10-66.1066-RuralChina-Followup',
                         variables=list('centreid'), missings = TRUE)
```

```{r local_RCh2, echo=F}
t1066_RCh_w1_ybirth <- opal.execute(o,'t1066_RCh_w1_ybirth')
t1066_RCh_w2_id <- opal.execute(o,'t1066_RCh_w2_id')

t1066_RCh_w1_ybirth$yinter <- as.numeric(format(t1066_RCh_w1_ybirth$DATE, '%Y'))

vari <- t1066_RCh_w1_ybirth$age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`)
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_RCh_w1_ybirth$age, missing_values = NA)
ggplot(t1066_RCh_w1_ybirth, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")

vari <- t1066_RCh_w1_ybirth$yinter
kable(Continuous_summary(vari, missing_values = NA)[3], caption="YEAR OF INTERVIEW")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_RCh_w1_ybirth$yinter, missing_values = NA)


ggplot(t1066_RCh_w1_ybirth, aes(yinter)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of interview") + ylab("Frequency") + xlim(2002,2007)
```

#### Harmonisation algorithm
To harmonize the year of birth is going to use the following formula:
year_of_birth = Year_of_interview - age
Recoding the missing values as follows: 

* `NA into 999`

**R script:**

```{r harmo_RCh2}
t1066_RCh_w1_ybirth$year_of_interview <- t1066_RCh_w1_ybirth$yinter

t1066_RCh_w1_ybirth$year_of_birth <- t1066_RCh_w1_ybirth$year_of_interview - t1066_RCh_w1_ybirth$age

t1066_RCh_w1_ybirth <- t1066_RCh_w1_ybirth[,-c(2:5)]

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], year_of_birth=as.numeric(new_2[,2]))
  new_22
}


t1066_RCh_w2_ybirth <- Add_indiv(old = t1066_RCh_w1_ybirth, new = t1066_RCh_w2_id)



t1066_ds_RCh_w2 <- tibble(id=t1066_RCh_w2_ybirth$id)
t1066_ds_RCh_w2$ybirth <- car::recode(t1066_RCh_w2_ybirth$year_of_birth, "NA=999")
t1066_ds_RCh_w2$ybirth <- labelled(t1066_ds_RCh_w2$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_RCh2, echo=F}
vari <- t1066_ds_RCh_w2$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
#Continuous_summary(var = t1066_ds_RCh_w2$ybirth, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RCh_w2, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation_RCh2, echo=F}
```




## Dominican Republic

### Wave 1 

#### Study-specific variable description

| **Name**        | `age` | `DATE` |
|-----------------|-|-|
| **Label**       | `participant age in years` | `date of baseline interview` |
| **Table name**  | `1066-DominicanRepublic-Baseline` | `1066-DominicanRepublic-Baseline` |
| **Description** |  |  |


```{r assign_DR1, echo=F}
opal.assign.table.tibble(o, 't1066_DR_w1_ybirth','10-66.1066-DominicanRepublic-Baseline',
                         variables=list('age', 'DATE'), missings = TRUE)
```

```{r local_DR1, echo=F}
t1066_DR_w1_ybirth <- opal.execute(o,'t1066_DR_w1_ybirth')
t1066_DR_w1_ybirth$yinter <- as.numeric(format(t1066_DR_w1_ybirth$DATE, '%Y'))

vari <- t1066_DR_w1_ybirth$age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`)
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_DR_w1_ybirth$age, missing_values = NA)
ggplot(t1066_DR_w1_ybirth, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")

vari <- t1066_DR_w1_ybirth$yinter
kable(Continuous_summary(vari, missing_values = NA)[3], caption="YEAR OF INTERVIEW")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_DR_w1_ybirth$yinter, missing_values = NA)


ggplot(t1066_DR_w1_ybirth, aes(yinter)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of interview") + ylab("Frequency") + xlim(2002,2007)
```

There are the values 2204 and 5005 in year of interview that are going to consider as a 2004 and 2005 respetcively because they are consider  write mistake. The value NA in year or interview is going to be computed as 2005 since is the most frecuent value. 

#### Harmonisation algorithm
To harmonize the year of birth is going to use the following formula:
year_of_birth = Year_of_interview - age
Recoding the missing values as follows: 

* `NA into 999`

**R script:**

```{r harmo_DR1}
t1066_ds_DR_w1 <- tibble(id=t1066_DR_w1_ybirth$id)

t1066_DR_w1_ybirth$age <- t1066_DR_w1_ybirth$age
t1066_DR_w1_ybirth$year_of_interview <- car::recode(t1066_DR_w1_ybirth$yinter, "NA=2005; 2204=2004; 5005=2005")

t1066_ds_DR_w1$ybirth <- t1066_DR_w1_ybirth$year_of_interview - t1066_DR_w1_ybirth$age

t1066_ds_DR_w1$ybirth <- car::recode(t1066_ds_DR_w1$ybirth, "NA=999")


t1066_ds_DR_w1$ybirth <- labelled(t1066_ds_DR_w1$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_DR1, echo=F}
vari <- t1066_ds_DR_w1$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
#Continuous_summary(var = t1066_ds_DR_w1$ybirth, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_DR_w1, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1901,1940)
```

#### Validation
```{r crosstabulation_DR1, echo=F}
```



### Wave 2 

#### Study-specific variable description

| **Name**        | `age` | `DATE` |
|-----------------|-|-|
| **Label**       | `participant age in years` | `date of baseline interview` |
| **Table name**  | `1066-DominicanRepublic-Baseline` | `1066-DominicanRepublic-Baseline` |
| **Description** |  |  |


```{r assign_DR2, echo=F}
opal.assign.table.tibble(o, 't1066_DR_w1_ybirth','10-66.1066-DominicanRepublic-Baseline',
                         variables=list('age', 'DATE'), missings = TRUE)
opal.assign.table.tibble(o, 't1066_DR_w2_id','10-66.1066-DominicanRepublic-Followup',
                         variables=list('centreid'), missings = TRUE)
```

```{r local_DR2, echo=F}
t1066_DR_w1_ybirth <- opal.execute(o,'t1066_DR_w1_ybirth')
t1066_DR_w2_id <- opal.execute(o,'t1066_DR_w2_id')

t1066_DR_w1_ybirth$yinter <- as.numeric(format(t1066_DR_w1_ybirth$DATE, '%Y'))

vari <- t1066_DR_w1_ybirth$age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`)
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_DR_w1_ybirth$age, missing_values = NA)
ggplot(t1066_DR_w1_ybirth, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")

vari <- t1066_DR_w1_ybirth$yinter
kable(Continuous_summary(vari, missing_values = NA)[3], caption="YEAR OF INTERVIEW")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_DR_w1_ybirth$yinter, missing_values = NA)


ggplot(t1066_DR_w1_ybirth, aes(yinter)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of interview") + ylab("Frequency") + xlim(2002,2007)
```

There are the values 2204 and 5005 in year of interview that are going to consider as a 2004 and 2005 respetcively because they are consider  write mistake. The value NA in year or interview is going to be computed as 2005 since is the most frecuent value. 

#### Harmonisation algorithm
To harmonize the year of birth is going to use the following formula:
year_of_birth = Year_of_interview - age
Recoding the missing values as follows: 

* `NA into 999`

**R script:**

```{r harmo_DR2}
t1066_DR_w1_ybirth$year_of_interview <- car::recode(t1066_DR_w1_ybirth$yinter, "NA=2005; 2204=2004; 5005=2005")

t1066_DR_w1_ybirth$year_of_birth <- t1066_DR_w1_ybirth$year_of_interview - t1066_DR_w1_ybirth$age

t1066_DR_w1_ybirth <- t1066_DR_w1_ybirth[,-c(2:5)]

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], year_of_birth=as.numeric(new_2[,2]))
  new_22
}


t1066_DR_w2_ybirth <- Add_indiv(old = t1066_DR_w1_ybirth, new = t1066_DR_w2_id)


t1066_ds_DR_w2 <- tibble(id=t1066_DR_w2_ybirth$id)
t1066_ds_DR_w2$ybirth <- car::recode(t1066_DR_w2_ybirth$year_of_birth, "NA=999")
t1066_ds_DR_w2$ybirth <- labelled(t1066_ds_DR_w2$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_DR2, echo=F}
vari <- t1066_ds_DR_w2$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
#Continuous_summary(var = t1066_ds_DR_w2$ybirth, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_DR_w2, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1901,1940)
```

#### Validation
```{r crosstabulation_DR2, echo=F}
```



## Venezuela

### Wave 1 

#### Study-specific variable description

| **Name**        | `age` | `DATE` |
|-----------------|-|-|
| **Label**       | `participant age in years` | `date of baseline interview` |
| **Table name**  | `1066-Venezuela-Baseline` | `1066-Venezuela-Baseline` |
| **Description** |  |  |



```{r assign_V1, echo=F}
opal.assign.table.tibble(o, 't1066_Ven_w1_ybirth','10-66.1066-Venezuela-Baseline',
                         variables=list('age','DATE'), missings = TRUE)
```

```{r local_V1, echo=F}
t1066_Ven_w1_ybirth <- opal.execute(o,'t1066_Ven_w1_ybirth')
t1066_Ven_w1_ybirth$yinter <- as.numeric(format(t1066_Ven_w1_ybirth$DATE, '%Y'))

vari <- t1066_Ven_w1_ybirth$age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`)
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_Ven_w1_ybirth$age, missing_values = NA)
ggplot(t1066_Ven_w1_ybirth, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")

vari <- t1066_Ven_w1_ybirth$yinter
kable(Continuous_summary(vari, missing_values = NA)[3], caption="YEAR OF INTERVIEW")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_Ven_w1_ybirth$yinter, missing_values = NA)


ggplot(t1066_Ven_w1_ybirth, aes(yinter)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of interview") + ylab("Frequency") + xlim(2002,2007)
```

#### Harmonisation algorithm
To harmonize the year of birth is going to use the following formula:
year_of_birth = Year_of_interview - age
Recoding the missing values as follows: 

* `NA into 999`

**R script:**

```{r harmo_V1}
t1066_ds_Ven_w1 <- tibble(id=t1066_Ven_w1_ybirth$id)
t1066_Ven_w1_ybirth$age <- t1066_Ven_w1_ybirth$age
t1066_Ven_w1_ybirth$year_of_interview <- t1066_Ven_w1_ybirth$yinter

t1066_ds_Ven_w1$ybirth <- t1066_Ven_w1_ybirth$year_of_interview - t1066_Ven_w1_ybirth$age

t1066_ds_Ven_w1$ybirth <- car::recode(t1066_ds_Ven_w1$ybirth, "NA=999")


t1066_ds_Ven_w1$ybirth <- labelled(t1066_ds_Ven_w1$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_V1, echo=F}
vari <- t1066_ds_Ven_w1$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
#Continuous_summary(var = t1066_ds_Ven_w1$ybirth, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_Ven_w1, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1904,1941)
```

#### Validation
```{r crosstabulation_V1, echo=F}
```




### Wave 2 

#### Study-specific variable description

| **Name**        | `age` | `DATE` |
|-----------------|-|-|
| **Label**       | `participant age in years` | `date of baseline interview` | 
| **Table name**  | `1066-Venezuela-Baseline` | `1066-Venezuela-Baseline` |
| **Description** |  |  |


```{r assign_V2, echo=F}
opal.assign.table.tibble(o, 't1066_Ven_w1_ybirth','10-66.1066-Venezuela-Baseline',
                         variables=list('age','DATE'), missings = TRUE)
opal.assign.table.tibble(o, 't1066_Ven_w2_id','10-66.1066-Venezuela-Followup',
                         variables=list('centreid'), missings = TRUE)
```

```{r local_V2, echo=F}
t1066_Ven_w1_ybirth <- opal.execute(o,'t1066_Ven_w1_ybirth')
t1066_Ven_w2_id <- opal.execute(o,'t1066_Ven_w2_id')

t1066_Ven_w1_ybirth$yinter <- as.numeric(format(t1066_Ven_w1_ybirth$DATE, '%Y'))

vari <- t1066_Ven_w1_ybirth$age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`)
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_Ven_w1_ybirth$age, missing_values = NA)
ggplot(t1066_Ven_w1_ybirth, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")

vari <- t1066_Ven_w1_ybirth$yinter
kable(Continuous_summary(vari, missing_values = NA)[3], caption="YEAR OF INTERVIEW")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_Ven_w1_ybirth$yinter, missing_values = NA)


ggplot(t1066_Ven_w1_ybirth, aes(yinter)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of interview") + ylab("Frequency") + xlim(2002,2007)
```

#### Harmonisation algorithm
To harmonize the year of birth is going to use the following formula:
year_of_birth = Year_of_interview - age
Recoding the missing values as follows: 

* `NA into 999`

**R script:**

```{r harmo_V2}
t1066_Ven_w1_ybirth$year_of_interview <- t1066_Ven_w1_ybirth$yinter

t1066_Ven_w1_ybirth$year_of_birth <- t1066_Ven_w1_ybirth$year_of_interview - t1066_Ven_w1_ybirth$age

t1066_Ven_w1_ybirth <- t1066_Ven_w1_ybirth[,-c(2:5)]

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], year_of_birth=as.numeric(new_2[,2]))
  new_22
}


t1066_Ven_w2_ybirth <- Add_indiv(old = t1066_Ven_w1_ybirth, new = t1066_Ven_w2_id)


t1066_ds_Ven_w2 <- tibble(id=t1066_Ven_w2_ybirth$id)
t1066_ds_Ven_w2$ybirth <- car::recode(t1066_Ven_w2_ybirth$year_of_birth, "NA=999")
t1066_ds_Ven_w2$ybirth <- labelled(t1066_ds_Ven_w2$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_V2, echo=F}
vari <- t1066_ds_Ven_w2$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
#Continuous_summary(var = t1066_ds_Ven_w2$ybirth, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_Ven_w2, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1904,1941)
```

#### Validation
```{r crosstabulation_V2, echo=F}
```




## Urban Peru

### Wave 1 

#### Study-specific variable description

| **Name**        | `age` | `DATE` |
|-----------------|-|-|
| **Label**       | `participant age in years` | `date of baseline interview` |
| **Table name**  | `1066-UrbanPeru-Baseline` | `1066-UrbanPeru-Baseline` |
| **Description** |  |  |


```{r assign_UP, echo=F}
opal.assign.table.tibble(o, 't1066_UP_w1_ybirth','10-66.1066-UrbanPeru-Baseline',
                         variables=list('age', 'DATE'), missings = TRUE)
```

```{r local_UP1, echo=F}
t1066_UP_w1_ybirth <- opal.execute(o,'t1066_UP_w1_ybirth')
t1066_UP_w1_ybirth$yinter <- as.numeric(format(t1066_UP_w1_ybirth$DATE, '%Y'))

vari <- t1066_UP_w1_ybirth$age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`)
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_UP_w1_ybirth$age, missing_values = NA)
ggplot(t1066_UP_w1_ybirth, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")

vari <- t1066_UP_w1_ybirth$yinter
kable(Continuous_summary(vari, missing_values = NA)[3], caption="YEAR OF INTERVIEW")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_UP_w1_ybirth$yinter, missing_values = NA)


ggplot(t1066_UP_w1_ybirth, aes(yinter)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of interview") + ylab("Frequency") + xlim(2002,2007)
```

The value NA in year or interview is going to be computed as 2005 since is the most frecuent value. 

#### Harmonisation algorithm
To harmonize the year of birth is going to use the following formula:
year_of_birth = Year_of_interview - age
Recoding the missing values as follows: 

* `NA into 999`

**R script:**

```{r harmo_UP1}
t1066_ds_UP_w1 <- tibble(id=t1066_UP_w1_ybirth$id)
t1066_UP_w1_ybirth$age <- t1066_UP_w1_ybirth$age
t1066_UP_w1_ybirth$year_of_interview <- car::recode(t1066_UP_w1_ybirth$yinter, "NA=2005")

t1066_ds_UP_w1$ybirth <- t1066_UP_w1_ybirth$year_of_interview - t1066_UP_w1_ybirth$age

t1066_ds_UP_w1$ybirth <- car::recode(t1066_ds_UP_w1$ybirth, "NA=999")


t1066_ds_UP_w1$ybirth <- labelled(t1066_ds_UP_w1$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_UP1, echo=F}
vari <- t1066_ds_UP_w1$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
#Continuous_summary(var = t1066_ds_UP_w1$ybirth, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UP_w1, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1904,1941)
```

#### Validation
```{r crosstabulation_UP1, echo=F}
```



### Wave 2 

#### Study-specific variable description

| **Name**        | `age` | `DATE` |
|-----------------|-|-|
| **Label**       | `participant age in years` | `date of baseline interview` |
| **Table name**  | `1066-UrbanPeru-Baseline` | `1066-UrbanPeru-Baseline` |
| **Description** |  |  |




```{r assign_UP2, echo=F}
opal.assign.table.tibble(o, 't1066_UP_w1_ybirth','10-66.1066-UrbanPeru-Baseline',
                         variables=list('age', 'DATE'), missings = TRUE)
opal.assign.table.tibble(o, 't1066_UP_w2_id','10-66.1066-UrbanPeru-Followup',
                         variables=list('centreid'), missings = TRUE)
```

```{r local_UP2, echo=F}
t1066_UP_w1_ybirth <- opal.execute(o,'t1066_UP_w1_ybirth')
t1066_UP_w2_id <- opal.execute(o,'t1066_UP_w2_id')

t1066_UP_w1_ybirth$yinter <- as.numeric(format(t1066_UP_w1_ybirth$DATE, '%Y'))

vari <- t1066_UP_w1_ybirth$age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`)
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_UP_w1_ybirth$age, missing_values = NA)
ggplot(t1066_UP_w1_ybirth, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")

vari <- t1066_UP_w1_ybirth$yinter
kable(Continuous_summary(vari, missing_values = NA)[3], caption="YEAR OF INTERVIEW")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_UP_w1_ybirth$yinter, missing_values = NA)


ggplot(t1066_UP_w1_ybirth, aes(yinter)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of interview") + ylab("Frequency") + xlim(2002,2007)
```

The value NA in year or interview is going to be computed as 2005 since is the most frecuent value. 

#### Harmonisation algorithm
To harmonize the year of birth is going to use the following formula:
year_of_birth = Year_of_interview - age
Recoding the missing values as follows: 

* `NA into 999`

**R script:**

```{r harmo_UP2}
t1066_UP_w1_ybirth$year_of_interview <- car::recode(t1066_UP_w1_ybirth$yinter, "NA=2005")

t1066_UP_w1_ybirth$year_of_birth <- t1066_UP_w1_ybirth$year_of_interview - t1066_UP_w1_ybirth$age

t1066_UP_w1_ybirth <- t1066_UP_w1_ybirth[,-c(2:5)]

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], year_of_birth=as.numeric(new_2[,2]))
  new_22
}


t1066_UP_w2_ybirth <- Add_indiv(old = t1066_UP_w1_ybirth, new = t1066_UP_w2_id)


t1066_ds_UP_w2 <- tibble(id=t1066_UP_w2_ybirth$id)
t1066_ds_UP_w2$ybirth <- car::recode(t1066_UP_w2_ybirth$year_of_birth, "NA=999")
t1066_ds_UP_w2$ybirth <- labelled(t1066_ds_UP_w2$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_UP2, echo=F}
vari <-  t1066_ds_UP_w2$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
#Continuous_summary(var = t1066_ds_UP_w2$ybirth, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UP_w2, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1904,1941)
```

#### Validation
```{r crosstabulation_UP2, echo=F}
```




## Rural Peru

### Wave 1 

#### Study-specific variable description

| **Name**        | `age` | `DATE` |
|-----------------|-|-|
| **Label**       | `participant age in years` | `date of baseline interview` |
| **Table name**  | `1066-RuralPeru-Baseline` | `1066-RuralPeru-Baseline` |
| **Description** |  |  |


```{r assign_RP, echo=F}
opal.assign.table.tibble(o, 't1066_RP_w1_ybirth','10-66.1066-RuralPeru-Baseline',
                         variables=list('age', 'DATE'), missings = TRUE)
```

```{r local_RP1, echo=F}
t1066_RP_w1_ybirth <- opal.execute(o,'t1066_RP_w1_ybirth')
t1066_RP_w1_ybirth$yinter <- as.numeric(format(t1066_RP_w1_ybirth$DATE, '%Y'))

vari <- t1066_RP_w1_ybirth$age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`)
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_RP_w1_ybirth$age, missing_values = NA)
ggplot(t1066_RP_w1_ybirth, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")

vari <- t1066_RP_w1_ybirth$yinter
kable(Continuous_summary(vari, missing_values = NA)[3], caption="YEAR OF INTERVIEW")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_RP_w1_ybirth$yinter, missing_values = NA)


ggplot(t1066_RP_w1_ybirth, aes(yinter)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of interview") + ylab("Frequency") + xlim(2002,2007)
```

There is a value 2026 in year of interview that is going to consider as a 2006 because it is consider as a write mistake.

#### Harmonisation algorithm
To harmonize the year of birth is going to use the following formula:
year_of_birth = Year_of_interview - age
Recoding the missing values as follows: 

* `NA into 999`

**R script:**

```{r harmo_RP1}
t1066_ds_RP_w1 <- tibble(id=t1066_RP_w1_ybirth$id)
t1066_RP_w1_ybirth$age <- t1066_RP_w1_ybirth$age
t1066_RP_w1_ybirth$year_of_interview <- car::recode(t1066_RP_w1_ybirth$yinter, "2026=2006")

t1066_ds_RP_w1$ybirth <- t1066_RP_w1_ybirth$year_of_interview - t1066_RP_w1_ybirth$age

t1066_ds_RP_w1$ybirth <- car::recode(t1066_ds_RP_w1$ybirth, "NA=999")


t1066_ds_RP_w1$ybirth <- labelled(t1066_ds_RP_w1$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_RP1, echo=F}
vari <- t1066_ds_RP_w1$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
#Continuous_summary(var = t1066_ds_RP_w1$ybirth, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RP_w1, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1904,1941)
```

#### Validation
```{r crosstabulation_RP1, echo=F}
```




### Wave 2 

#### Study-specific variable description

| **Name**        | `age` | `DATE` |
|-----------------|-|-|
| **Label**       | `participant age in years` | `date of baseline interview` |
| **Table name**  | `1066-RuralPeru-Baseline` | `1066-RuralPeru-Baseline` |
| **Description** |  |  |


```{r assign_RP2, echo=F}
opal.assign.table.tibble(o, 't1066_RP_w1_ybirth','10-66.1066-RuralPeru-Baseline',
                         variables=list('age', 'DATE'), missings = TRUE)
opal.assign.table.tibble(o, 't1066_RP_w2_id','10-66.1066-RuralPeru-Followup',
                         variables=list('centreid'), missings = TRUE)
```

```{r local_RP2, echo=F}
t1066_RP_w1_ybirth <- opal.execute(o,'t1066_RP_w1_ybirth')
t1066_RP_w2_id <- opal.execute(o,'t1066_RP_w2_id')

t1066_RP_w1_ybirth$yinter <- as.numeric(format(t1066_RP_w1_ybirth$DATE, '%Y'))

vari <- t1066_RP_w1_ybirth$age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`)
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_RP_w1_ybirth$age, missing_values = NA)
ggplot(t1066_RP_w1_ybirth, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")

vari <- t1066_RP_w1_ybirth$yinter
kable(Continuous_summary(vari, missing_values = NA)[3], caption="YEAR OF INTERVIEW")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_RP_w1_ybirth$yinter, missing_values = NA)


ggplot(t1066_RP_w1_ybirth, aes(yinter)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of interview") + ylab("Frequency") + xlim(2002,2007)
```

There is a value 2026 in year of interview that is going to consider as a 2006 because it is consider as a write mistake.

#### Harmonisation algorithm
To harmonize the year of birth is going to use the following formula:
year_of_birth = Year_of_interview - age
Recoding the missing values as follows: 

* `NA into 999`

**R script:**

```{r harmo_RP2}
t1066_RP_w1_ybirth$year_of_interview <- car::recode(t1066_RP_w1_ybirth$yinter, "2026=2006")

t1066_RP_w1_ybirth$year_of_birth <- t1066_RP_w1_ybirth$year_of_interview - t1066_RP_w1_ybirth$age

t1066_RP_w1_ybirth <- t1066_RP_w1_ybirth[,-c(2:5)]

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], year_of_birth=as.numeric(new_2[,2]))
  new_22
}


t1066_RP_w2_ybirth <- Add_indiv(old = t1066_RP_w1_ybirth, new = t1066_RP_w2_id)


t1066_ds_RP_w2 <- tibble(id=t1066_RP_w2_ybirth$id)
t1066_ds_RP_w2$ybirth <- car::recode(t1066_RP_w2_ybirth$year_of_birth, "NA=999")
t1066_ds_RP_w2$ybirth <- labelled(t1066_ds_RP_w2$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_RP2, echo=F}
vari <- t1066_ds_RP_w2$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
#Continuous_summary(var = t1066_ds_RP_w2$ybirth, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RP_w2, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1904,1941)
```

#### Validation
```{r crosstabulation_RP2, echo=F}
```




## Urban Mexico

### Wave 1 

#### Study-specific variable description

| **Name**        | `age` | `DATE` |
|-----------------|-|-|
| **Label**       | `participant age in years` | `date of baseline interview` |
| **Table name**  | `1066-UrbanMexico-Baseline` | `1066-UrbanMexico-Baseline` |
| **Description** |  |  |


```{r assign_UM1, echo=F}
opal.assign.table.tibble(o, 't1066_UM_w1_ybirth','10-66.1066-UrbanMexico-Baseline',
                         variables=list('age', 'DATE'), missings = TRUE)
```

```{r local_UM1, echo=F}
t1066_UM_w1_ybirth <- opal.execute(o,'t1066_UM_w1_ybirth')
t1066_UM_w1_ybirth$yinter <- as.numeric(format(t1066_UM_w1_ybirth$DATE, '%Y'))

vari <- t1066_UM_w1_ybirth$age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`)
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_UM_w1_ybirth$age, missing_values = NA)
ggplot(t1066_UM_w1_ybirth, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")


vari <- t1066_UM_w1_ybirth$yinter
kable(Continuous_summary(vari, missing_values = NA)[3], caption="YEAR OF INTERVIEW")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_UM_w1_ybirth$yinter, missing_values = NA)


ggplot(t1066_UM_w1_ybirth, aes(yinter)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of interview") + ylab("Frequency") + xlim(2002,2007)
```

#### Harmonisation algorithm
To harmonize the year of birth is going to use the following formula:
year_of_birth = Year_of_interview - age
Recoding the missing values as follows: 

* `NA into 999`

**R script:**

```{r harmo_UM1}
t1066_ds_UM_w1 <- tibble(id=t1066_UM_w1_ybirth$id)
t1066_UM_w1_ybirth$age <- t1066_UM_w1_ybirth$age
t1066_UM_w1_ybirth$year_of_interview <- t1066_UM_w1_ybirth$yinter

t1066_ds_UM_w1$ybirth <- t1066_UM_w1_ybirth$year_of_interview - t1066_UM_w1_ybirth$age

t1066_ds_UM_w1$ybirth <- car::recode(t1066_ds_UM_w1$ybirth, "NA=999")


t1066_ds_UM_w1$ybirth <- labelled(t1066_ds_UM_w1$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_UM1, echo=F}
vari <- t1066_ds_UM_w1$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
#Continuous_summary(var = t1066_ds_UM_w1$ybirth, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UM_w1, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1904,1941)
```

#### Validation
```{r crosstabulation_UM1, echo=F}
```




### Wave 2

#### Study-specific variable description

| **Name**        | `age` | `DATE` |
|-----------------|-|-|
| **Label**       | `participant age in years` | `date of baseline interview` |
| **Table name**  | `1066-UrbanMexico-Baseline` | `1066-UrbanMexico-Baseline` |
| **Description** |  |  |


```{r assign_UM2, echo=F}
opal.assign.table.tibble(o, 't1066_UM_w1_ybirth','10-66.1066-UrbanMexico-Baseline',
                         variables=list('age', 'DATE'), missings = TRUE)
opal.assign.table.tibble(o, 't1066_UM_w2_id','10-66.1066-UrbanMexico-Followup',
                         variables=list('centreid'), missings = TRUE)
```

```{r local_UM2, echo=F}
t1066_UM_w1_ybirth <- opal.execute(o,'t1066_UM_w1_ybirth')
t1066_UM_w2_id <- opal.execute(o,'t1066_UM_w2_id')

t1066_UM_w1_ybirth$yinter <- as.numeric(format(t1066_UM_w1_ybirth$DATE, '%Y'))

vari <- t1066_UM_w1_ybirth$age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`)
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_UM_w1_ybirth$age, missing_values = NA)
ggplot(t1066_UM_w1_ybirth, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")

vari <- t1066_UM_w1_ybirth$yinter
kable(Continuous_summary(vari, missing_values = NA)[3], caption="YEAR OF INTERVIEW")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_UM_w1_ybirth$yinter, missing_values = NA)


ggplot(t1066_UM_w1_ybirth, aes(yinter)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of interview") + ylab("Frequency") + xlim(2002,2007)
```

#### Harmonisation algorithm
To harmonize the year of birth is going to use the following formula:
year_of_birth = Year_of_interview - age
Recoding the missing values as follows: 

* `NA into 999`

**R script:**

```{r harmo_UM2}
t1066_UM_w1_ybirth$year_of_interview <- t1066_UM_w1_ybirth$yinter

t1066_UM_w1_ybirth$year_of_birth <- t1066_UM_w1_ybirth$year_of_interview - t1066_UM_w1_ybirth$age

t1066_UM_w1_ybirth <- t1066_UM_w1_ybirth[,-c(2:5)]

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], year_of_birth=as.numeric(new_2[,2]))
  new_22
}


t1066_UM_w2_ybirth <- Add_indiv(old = t1066_UM_w1_ybirth, new = t1066_UM_w2_id)


t1066_ds_UM_w2 <- tibble(id=t1066_UM_w2_ybirth$id)
t1066_ds_UM_w2$ybirth <- car::recode(t1066_UM_w2_ybirth$year_of_birth, "NA=999")
t1066_ds_UM_w2$ybirth <- labelled(t1066_ds_UM_w2$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_UM2, echo=F}
vari <- t1066_ds_UM_w2$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
#Continuous_summary(var = t1066_ds_UM_w2$ybirth, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UM_w2, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1904,1941)
```

#### Validation
```{r crosstabulation_UM2, echo=F}
```




## Rural Mexico

### Wave 1 

#### Study-specific variable description


| **Name**        | `age` | `DATE` |
|-----------------|-|-|
| **Label**       | `participant age in years` | `date of baseline interview` |
| **Table name**  | `1066-RuralMexico-Baseline` | `1066-RuralMexico-Baseline` |
| **Description** |  |  |



```{r assign_RM1, echo=F}
opal.assign.table.tibble(o, 't1066_RM_w1_ybirth','10-66.1066-RuralMexico-Baseline',
                         variables=list('age', 'DATE'), missings = TRUE)
```

```{r local_RM1, echo=F}
t1066_RM_w1_ybirth <- opal.execute(o,'t1066_RM_w1_ybirth')
t1066_RM_w1_ybirth$yinter <- as.numeric(format(t1066_RM_w1_ybirth$DATE, '%Y'))

vari <- t1066_RM_w1_ybirth$age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`)
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_RM_w1_ybirth$age, missing_values = NA)
ggplot(t1066_RM_w1_ybirth, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")

vari <- t1066_RM_w1_ybirth$yinter
kable(Continuous_summary(vari, missing_values = NA)[3], caption="YEAR OF INTERVIEW")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_RM_w1_ybirth$yinter, missing_values = NA)


ggplot(t1066_RM_w1_ybirth, aes(yinter)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of interview") + ylab("Frequency") + xlim(2002,2007)
```

#### Harmonisation algorithm
To harmonize the year of birth is going to use the following formula:
year_of_birth = Year_of_interview - age
Recoding the missing values as follows: 

* `NA into 999`

**R script:**

```{r harmo_RM1}
t1066_ds_RM_w1 <- tibble(id=t1066_RM_w1_ybirth$id)
t1066_RM_w1_ybirth$age <- t1066_RM_w1_ybirth$age
t1066_RM_w1_ybirth$year_of_interview <- t1066_RM_w1_ybirth$yinter

t1066_ds_RM_w1$ybirth <- t1066_RM_w1_ybirth$year_of_interview - t1066_RM_w1_ybirth$age

t1066_ds_RM_w1$ybirth <- car::recode(t1066_ds_RM_w1$ybirth, "NA=999")


t1066_ds_RM_w1$ybirth <- labelled(t1066_ds_RM_w1$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_RM1, echo=F}
vari <- t1066_ds_RM_w1$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
#Continuous_summary(var = t1066_ds_RM_w1$ybirth, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RM_w1, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1904,1941)
```


#### Validation
```{r crosstabulation_RM1, echo=F}
```



### Wave 2 

#### Study-specific variable description

| **Name**        | `age` | `DATE` |
|-----------------|-|-|
| **Label**       | `participant age in years` | `date of baseline interview` |
| **Table name**  | `1066-RuralMexico-Baseline` | `1066-RuralMexico-Baseline` |
| **Description** |  |  |


```{r assign_RM2, echo=F}
opal.assign.table.tibble(o, 't1066_RM_w1_ybirth','10-66.1066-RuralMexico-Baseline',
                         variables=list('age', 'DATE'), missings = TRUE)
opal.assign.table.tibble(o, 't1066_RM_w2_id','10-66.1066-RuralMexico-Followup',
                         variables=list('centreid'), missings = TRUE)
```

```{r local_RM2, echo=F}
t1066_RM_w1_ybirth <- opal.execute(o,'t1066_RM_w1_ybirth')
t1066_RM_w2_id <- opal.execute(o,'t1066_RM_w2_id')

t1066_RM_w1_ybirth$yinter <- as.numeric(format(t1066_RM_w1_ybirth$DATE, '%Y'))

vari <- t1066_RM_w1_ybirth$age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`)
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_RM_w1_ybirth$age, missing_values = NA)
ggplot(t1066_RM_w1_ybirth, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")

vari <- t1066_RM_w1_ybirth$yinter
kable(Continuous_summary(vari, missing_values = NA)[3], caption="YEAR OF INTERVIEW")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_RM_w1_ybirth$yinter, missing_values = NA)


ggplot(t1066_RM_w1_ybirth, aes(yinter)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of interview") + ylab("Frequency") + xlim(2002,2007)
```

#### Harmonisation algorithm
To harmonize the year of birth is going to use the following formula:
year_of_birth = Year_of_interview - age
Recoding the missing values as follows: 

* `NA into 999`

**R script:**

```{r harmo_RM2}
t1066_RM_w1_ybirth$year_of_interview <- t1066_RM_w1_ybirth$yinter

t1066_RM_w1_ybirth$year_of_birth <- t1066_RM_w1_ybirth$year_of_interview - t1066_RM_w1_ybirth$age

t1066_RM_w1_ybirth <- t1066_RM_w1_ybirth[,-c(2:5)]

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], year_of_birth=as.numeric(new_2[,2]))
  new_22
}


t1066_RM_w2_ybirth <- Add_indiv(old = t1066_RM_w1_ybirth, new = t1066_RM_w2_id)

t1066_ds_RM_w2 <- tibble(id=t1066_RM_w2_ybirth$id)
t1066_ds_RM_w2$ybirth <- car::recode(t1066_RM_w2_ybirth$year_of_birth, "NA=999")
t1066_ds_RM_w2$ybirth <- labelled(t1066_ds_RM_w2$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_RM2, echo=F}
vari <- t1066_ds_RM_w2$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
#Continuous_summary(var = t1066_ds_RM_w2$ybirth, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RM_w2, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1904,1941)
```

#### Validation
```{r crosstabulation_RM2, echo=F}
```



## Puerto Rico

### Wave 1 

#### Study-specific variable description


| **Name**        | `age` | `DATE` |
|-----------------|-|-|
| **Label**       | `participant age in years` | `date of baseline interview` |
| **Table name**  | `1066-PuertoRico-Baseline` | `1066-PuertoRico-Baseline` |
| **Description** |  |  |


```{r assign_PR1, echo=F}
opal.assign.table.tibble(o, 't1066_PR_w1_ybirth','10-66.1066-PuertoRico-Baseline',
                         variables=list('age', 'DATE'), missings = TRUE)
```

```{r local_PR1, echo=F}
t1066_PR_w1_ybirth <- opal.execute(o,'t1066_PR_w1_ybirth')
t1066_PR_w1_ybirth$yinter <- as.numeric(format(t1066_PR_w1_ybirth$DATE, '%Y'))

vari <- t1066_PR_w1_ybirth$age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`)
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_PR_w1_ybirth$age, missing_values = NA)
ggplot(t1066_PR_w1_ybirth, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")

vari <- t1066_PR_w1_ybirth$yinter
kable(Continuous_summary(vari, missing_values = NA)[3], caption="YEAR OF INTERVIEW")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_PR_w1_ybirth$yinter, missing_values = NA)


ggplot(t1066_PR_w1_ybirth, aes(yinter)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of interview") + ylab("Frequency") + xlim(2002,2007)
```

#### Harmonisation algorithm
To harmonize the year of birth is going to use the following formula:
year_of_birth = Year_of_interview - age
Recoding the missing values as follows: 

* `NA into 999`

**R script:**

```{r harmo_PR1}
t1066_ds_PR_w1 <- tibble(id=t1066_PR_w1_ybirth$id)
t1066_PR_w1_ybirth$age <- t1066_PR_w1_ybirth$age
t1066_PR_w1_ybirth$year_of_interview <- t1066_PR_w1_ybirth$yinter

t1066_ds_PR_w1$ybirth <- t1066_PR_w1_ybirth$year_of_interview - t1066_PR_w1_ybirth$age

t1066_ds_PR_w1$ybirth <- car::recode(t1066_ds_PR_w1$ybirth, "NA=999")


t1066_ds_PR_w1$ybirth <- labelled(t1066_ds_PR_w1$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_PR1, echo=F}
vari <- t1066_ds_PR_w1$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
#Continuous_summary(var = t1066_ds_PR_w1$ybirth, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_PR_w1, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1904,1941)
```

#### Validation
```{r crosstabulation_PR1, echo=F}
```




### Wave 2 

#### Study-specific variable description

| **Name**        | `age` | `DATE` |
|-----------------|-|-|
| **Label**       | `participant age in years` | `date of baseline interview` |
| **Table name**  | `1066-PuertoRico-Baseline` | `1066-PuertoRico-Baseline` |
| **Description** |  |  |


```{r assign_PR2, echo=F}
opal.assign.table.tibble(o, 't1066_PR_w1_ybirth','10-66.1066-PuertoRico-Baseline',
                         variables=list('age', 'DATE'), missings = TRUE)
opal.assign.table.tibble(o, 't1066_PR_w2_id','10-66.1066-PuertoRico-Followup',
                         variables=list('centreid'), missings = TRUE)
```

```{r local_PR2, echo=F}
t1066_PR_w1_ybirth <- opal.execute(o,'t1066_PR_w1_ybirth')
t1066_PR_w2_id <- opal.execute(o,'t1066_PR_w2_id')

t1066_PR_w1_ybirth$yinter <- as.numeric(format(t1066_PR_w1_ybirth$DATE, '%Y'))

vari <- t1066_PR_w1_ybirth$age
kable(Continuous_summary(vari, missing_values = NA)[3], caption = attributes(vari)$`spss::shortName`)
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_PR_w1_ybirth$age, missing_values = NA)
ggplot(t1066_PR_w1_ybirth, aes(age)) + geom_histogram(stat="count", fill="steelblue") + xlab("Age") + ylab("Frequency")

vari <- t1066_PR_w1_ybirth$yinter
kable(Continuous_summary(vari, missing_values = NA)[3], caption="YEAR OF INTERVIEW")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
#Continuous_summary(var = t1066_PR_w1_ybirth$yinter, missing_values = NA)


ggplot(t1066_PR_w1_ybirth, aes(yinter)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of interview") + ylab("Frequency") + xlim(2002,2007)
```

#### Harmonisation algorithm
To harmonize the year of birth is going to use the following formula:
year_of_birth = Year_of_interview - age
Recoding the missing values as follows: 

* `NA into 999`

**R script:**

```{r harmo_PR2}
t1066_PR_w1_ybirth$year_of_interview <- t1066_PR_w1_ybirth$yinter

t1066_PR_w1_ybirth$year_of_birth <- t1066_PR_w1_ybirth$year_of_interview - t1066_PR_w1_ybirth$age

t1066_PR_w1_ybirth <- t1066_PR_w1_ybirth[,-c(2:5)]

Add_indiv <- function(old, new){
  
  new_2 <- matrix(NA, nrow = dim(new)[1], ncol=dim(old)[2])
  oldm <- as.matrix(old)
  
  for(i in 1:length(new$id)){
    if(sum(new$id[i]==old$id)>=1){
      new_2[i,] <- oldm[which(new$id[i]==old$id),]
    } else {
      new_2[i,] <- c(new$id[i], NA)
    }
  }
  
  new_22 <- data.frame(id=new_2[,1], year_of_birth=as.numeric(new_2[,2]))
  new_22
}


t1066_PR_w2_ybirth <- Add_indiv(old = t1066_PR_w1_ybirth, new = t1066_PR_w2_id)


t1066_ds_PR_w2 <- tibble(id=t1066_PR_w2_ybirth$id)
t1066_ds_PR_w2$ybirth <- car::recode(t1066_PR_w2_ybirth$year_of_birth, "NA=999")
t1066_ds_PR_w2$ybirth <- labelled(t1066_ds_PR_w2$ybirth, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_PR2, echo=F}
vari <- t1066_ds_PR_w2$ybirth
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3])
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
#Continuous_summary(var = t1066_ds_PR_w2$ybirth, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_PR_w2, aes(ybirth)) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of birth") + ylab("Frequency") + xlim(1904,1941)
```

#### Validation
```{r crosstabulation_PR2, echo=F}
```


# Quality estimation

Year of birth has to be computed by the formula: "date_birth"= "date" - "age".





```{r save, echo=FALSE}
ybirth <- t1066_ds_cuba_w1
save(ybirth, file = "../RData/cuba_w1/ybirth.RData")
rm(ybirth)

ybirth <- t1066_ds_cuba_w2
save(ybirth, file = "../RData/cuba_w2/ybirth.RData")
rm(ybirth)

ybirth <- t1066_ds_india_w1
save(ybirth, file = "../RData/india_w1/ybirth.RData")
rm(ybirth)

ybirth <- t1066_ds_india_w2
save(ybirth, file = "../RData/india_w2/ybirth.RData")
rm(ybirth)

ybirth <- t1066_ds_UCh_w1
save(ybirth, file = "../RData/UCh_w1/ybirth.RData")
rm(ybirth)

ybirth <- t1066_ds_UCh_w2
save(ybirth, file = "../RData/UCh_w2/ybirth.RData")
rm(ybirth)

ybirth <- t1066_ds_RCh_w1
save(ybirth, file = "../RData/RCh_w1/ybirth.RData")
rm(ybirth)

ybirth <- t1066_ds_RCh_w2
save(ybirth, file = "../RData/RCh_w2/ybirth.RData")
rm(ybirth)

ybirth <- t1066_ds_DR_w1
save(ybirth, file = "../RData/DR_w1/ybirth.RData")
rm(ybirth)

ybirth <- t1066_ds_DR_w2
save(ybirth, file = "../RData/DR_w2/ybirth.RData")
rm(ybirth)

ybirth <- t1066_ds_Ven_w1
save(ybirth, file = "../RData/Ven_w1/ybirth.RData")
rm(ybirth)

ybirth <- t1066_ds_Ven_w2
save(ybirth, file = "../RData/Ven_w2/ybirth.RData")
rm(ybirth)

ybirth <- t1066_ds_UP_w1
save(ybirth, file = "../RData/UP_w1/ybirth.RData")
rm(ybirth)

ybirth <- t1066_ds_UP_w2
save(ybirth, file = "../RData/UP_w2/ybirth.RData")
rm(ybirth)

ybirth <- t1066_ds_RP_w1
save(ybirth, file = "../RData/RP_w1/ybirth.RData")
rm(ybirth)

ybirth <- t1066_ds_RP_w2
save(ybirth, file = "../RData/RP_w2/ybirth.RData")
rm(ybirth)

ybirth <- t1066_ds_UM_w1
save(ybirth, file = "../RData/UM_w1/ybirth.RData")
rm(ybirth)

ybirth <- t1066_ds_UM_w2
save(ybirth, file = "../RData/UM_w2/ybirth.RData")
rm(ybirth)

ybirth <- t1066_ds_RM_w1
save(ybirth, file = "../RData/RM_w1/ybirth.RData")
rm(ybirth)

ybirth <- t1066_ds_RM_w2
save(ybirth, file = "../RData/RM_w2/ybirth.RData")
rm(ybirth)

ybirth <- t1066_ds_PR_w1
save(ybirth, file = "../RData/PR_w1/ybirth.RData")
rm(ybirth)

ybirth <- t1066_ds_PR_w2
save(ybirth, file = "../RData/PR_w2/ybirth.RData")
rm(ybirth)

```


```{r closeRsession, echo=FALSE}
opal.logout(o)
```

