---
title: "Living alone"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/Rmds/setup_ania.r")
```
<!-- ########################################################## --> 

# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `living_alone`
* Variable label: `Participant is currently living alone`
* Variable description: `Participant is currently living alone`
* Domain: `Socio-demographic and economic characteristics`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | No
1        | Yes

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process 



## Cuba

### Wave 1 

#### Study-specific variable description



| **Name** | `alone`|
|-|-|
| **Label** | `living alone` |
| **Table name** | `1066-Cuba-Baseline` |
| **Categories** | `0.0 = with others; 1.0 = alone` |
| **Description** |  |

```{r assign_cuba1, echo=F}
opal.assign.table.tibble(o, 't1066_cuba_w1_la','10-66.1066-Cuba-Baseline',
                         variables=list('alone'), missings = TRUE)
```

```{r local_cuba1, echo=F}
t1066_cuba_w1_la <- opal.execute(o,'t1066_cuba_w1_la')
vari <- t1066_cuba_w1_la$alone
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_cuba_w1_la$alone, missing_values = NA)
ggplot(t1066_cuba_w1_la, aes(x=factor(alone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `0.0 =" with others" into 0`
* `1.0 "alone" into 1`

**R script:**

```{r harmo_cuba1}
t1066_ds_cuba_w1 <- tibble(id=t1066_cuba_w1_la$id)
t1066_ds_cuba_w1$living_alone <- car::recode(t1066_cuba_w1_la$alone, "NA=999")
t1066_ds_cuba_w1$living_alone <- labelled(t1066_ds_cuba_w1$living_alone, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_cuba1, echo=F}
vari <- t1066_ds_cuba_w1$living_alone
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_alone") # EL CAPTION ES EL NOMBRE DE LA HASMONISED VARIABLE
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_cuba_w1$living_alone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_cuba_w1, aes(x=factor(living_alone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_cuba1, echo=F}
BeforeH <- table(t1066_cuba_w1_la$alone)
AfterH <- table(t1066_ds_cuba_w1$living_alone)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1")
kable(C)
```



### Wave 2 

#### Study-specific variable description



| **Name** | `f_r_cores`|
|-|-|
| **Label** | `number of coresidents` |
| **Table name** | `1066-Cuba-Followup` |
| **Description** |  |


```{r assign_cuba2, echo=F}
opal.assign.table.tibble(o, 't1066_cuba_w2_la','10-66.1066-Cuba-Followup',
                         variables=list('f_r_cores'), missings = TRUE)
```

```{r local_cuba2, echo=F}
t1066_cuba_w2_la <- opal.execute(o,'t1066_cuba_w2_la')
vari <- t1066_cuba_w2_la$f_r_cores
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_cuba_w2_la$f_r_cores, missing_values = NA)
ggplot(t1066_cuba_w2_la, aes(x=factor(f_r_cores))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `>=1 into 0`
* `NA into 999`

**R script:**

```{r harmo_cuba2}
t1066_ds_cuba_w2 <- tibble(id=t1066_cuba_w2_la$id)
t1066_ds_cuba_w2$living_alone <- car::recode(t1066_cuba_w2_la$f_r_cores, "0=1; 1:hi=0 ;NA=999")
t1066_ds_cuba_w2$living_alone <- labelled(t1066_ds_cuba_w2$living_alone, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_cuba2, echo=F}
vari <- t1066_ds_cuba_w2$living_alone
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_alone") # EL CAPTION ES EL NOMBRE DE LA HASMONISED VARIABLE
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_cuba_w2$living_alone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_cuba_w2, aes(x=factor(living_alone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_cuba2, echo=F}
BeforeH <- table(t1066_cuba_w2_la$f_r_cores)
BeforeH <- c(sum(BeforeH[2:length(BeforeH)]), BeforeH[1], sum(is.na(t1066_cuba_w2_la$f_r_cores)))
AfterH <- table(t1066_ds_cuba_w2$living_alone)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(">=1->0","0->1", "NA->999")
kable(C)
```







## India

### Wave 1 

#### Study-specific variable description



| **Name** | `alone`|
|-|-|
| **Label** | `living alone` |
| **Table name** | `1066-India-Followup` |
| **Categories** | `0.0 = with others; 1.0 = alone` |
| **Description** |  |

```{r assign_india1, echo=F}
opal.assign.table.tibble(o, 't1066_india_w1_la','10-66.1066-India-Baseline',
                         variables=list('alone'), missings = TRUE)
```

```{r local_india1, echo=F}
t1066_india_w1_la <- opal.execute(o,'t1066_india_w1_la')
vari <- t1066_india_w1_la$alone
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_india_w1_la$alone, missing_values = NA)
ggplot(t1066_india_w1_la, aes(x=factor(alone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `0.0 =" with others" into 0`
* `1.0 "alone" into 1`
* `NA into 999`

**R script:**

```{r harmo_india1}
t1066_ds_india_w1 <- tibble(id=t1066_india_w1_la$id)
t1066_ds_india_w1$living_alone <- car::recode(t1066_india_w1_la$alone, "NA=999")
t1066_ds_india_w1$living_alone <- labelled(t1066_ds_india_w1$living_alone, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_india1, echo=F}
vari <- t1066_ds_india_w1$living_alone
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_alone") # EL CAPTION ES EL NOMBRE DE LA HASMONISED VARIABLE
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_india_w1$living_alone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_india_w1, aes(x=factor(living_alone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_india1, echo=F}
BeforeH <- table(t1066_india_w1_la$alone)
AfterH <- table(t1066_ds_india_w1$living_alone)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1")
kable(C)
```






### Wave 2 

There is no variable.




## Urban China

### Wave 1 

#### Study-specific variable description



| **Name** | `alone`|
|-|-|
| **Label** | `living alone` |
| **Table name** | `1066-UrbanChina-Baseline` |
| **Categories** | `0.0 = with others; 1.0 = alone` |
| **Description** |  |


```{r assign_UCh1, echo=F}
opal.assign.table.tibble(o, 't1066_UCh_w1_la','10-66.1066-UrbanChina-Baseline',
                         variables=list('alone'), missings = TRUE)
```

```{r local_UCh1, echo=F}
t1066_UCh_w1_la <- opal.execute(o,'t1066_UCh_w1_la')
vari <- t1066_UCh_w1_la$alone
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UCh_w1_la$alone, missing_values = NA)
ggplot(t1066_UCh_w1_la, aes(x=factor(alone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `0.0 =" with others" into 0`
* `1.0 "alone" into 1`
* `NA into 999`

**R script:**

```{r harmo_UCh1}
t1066_ds_UCh_w1 <- tibble(id=t1066_UCh_w1_la$id)
t1066_ds_UCh_w1$living_alone <- car::recode(t1066_UCh_w1_la$alone, "NA=999")
t1066_ds_UCh_w1$living_alone <- labelled(t1066_ds_UCh_w1$living_alone, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_UCh1, echo=F}
vari <- t1066_ds_UCh_w1$living_alone
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_alone") # EL CAPTION ES EL NOMBRE DE LA HASMONISED VARIABLE
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UCh_w1$living_alone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UCh_w1, aes(x=factor(living_alone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_UCh1, echo=F}
BeforeH <- table(t1066_UCh_w1_la$alone)
AfterH <- table(t1066_ds_UCh_w1$living_alone)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1")
kable(C)
```




### Wave 2 

#### Study-specific variable description



| **Name** | `f_r_cores`|
|-|-|
| **Label** | `number of coresidents` |
| **Table name** | `1066-UrbanChina-Followup` |
| **Description** |  |

```{r assign_UCh2, echo=F}
opal.assign.table.tibble(o, 't1066_UCh_w2_la','10-66.1066-UrbanChina-Followup',
                         variables=list('f_r_cores'), missings = TRUE)
```

```{r local_UCh2, echo=F}
t1066_UCh_w2_la <- opal.execute(o,'t1066_UCh_w2_la')
vari <- t1066_UCh_w2_la$f_r_cores
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UCh_w2_la$f_r_cores, missing_values = NA)
ggplot(t1066_UCh_w2_la, aes(x=factor(f_r_cores))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `>=1 into 0`
* `NA into 999`

**R script:**

```{r harmo_UCh2}
t1066_ds_UCh_w2 <- tibble(id=t1066_UCh_w2_la$id)
t1066_ds_UCh_w2$living_alone <- car::recode(t1066_UCh_w2_la$f_r_cores, "0=1; 1:hi=0 ;NA=999")
t1066_ds_UCh_w2$living_alone <- labelled(t1066_ds_UCh_w2$living_alone, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_UCh2, echo=F}
vari <- t1066_ds_UCh_w2$living_alone
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_alone") # EL CAPTION ES EL NOMBRE DE LA HASMONISED VARIABLE
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UCh_w2$living_alone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UCh_w2, aes(x=factor(living_alone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_UCh2, echo=F}
BeforeH <- table(t1066_UCh_w2_la$f_r_cores)
BeforeH <- c(sum(BeforeH[2:length(BeforeH)]), BeforeH[1])
AfterH <- table(t1066_ds_UCh_w2$living_alone)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(">=1->0","0->1")
kable(C)
```







## Rural China

### Wave 1 

#### Study-specific variable description



| **Name** | `alone`|
|-|-|
| **Label** | `living alone` |
| **Table name** | `1066-RuralChina-Baseline` |
| **Categories** | `0.0 = with others; 1.0 = alone` |
| **Description** |  |


```{r assign_RCh1, echo=F}
opal.assign.table.tibble(o, 't1066_RCh_w1_la','10-66.1066-RuralChina-Baseline',
                         variables=list('alone'), missings = TRUE)
```

```{r local_RCh1, echo=F}
t1066_RCh_w1_la <- opal.execute(o,'t1066_RCh_w1_la')
vari <- t1066_RCh_w1_la$alone
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RCh_w1_la$alone, missing_values = NA)
ggplot(t1066_RCh_w1_la, aes(x=factor(alone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `0.0 =" with others" into 0`
* `1.0 "alone" into 1`
* `NA into 999`

**R script:**

```{r harmo_RCh1}
t1066_ds_RCh_w1 <- tibble(id=t1066_RCh_w1_la$id)
t1066_ds_RCh_w1$living_alone <- car::recode(t1066_RCh_w1_la$alone, "NA=999")
t1066_ds_RCh_w1$living_alone <- labelled(t1066_ds_RCh_w1$living_alone, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_RCh1, echo=F}
vari <- t1066_ds_RCh_w1$living_alone
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_alone") # EL CAPTION ES EL NOMBRE DE LA HASMONISED VARIABLE
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RCh_w1$living_alone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RCh_w1, aes(x=factor(living_alone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_RCh1, echo=F}
BeforeH <- table(t1066_RCh_w1_la$alone)
AfterH <- table(t1066_ds_RCh_w1$living_alone)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1")
kable(C)
```






### Wave 2 

#### Study-specific variable description



| **Name** | `f_r_cores`|
|-|-|
| **Label** | `number of coresidents` |
| **Table name** | `1066-RuralChina-Followup` |
| **Description** |  |

```{r assign_RCh2, echo=F}
opal.assign.table.tibble(o, 't1066_RCh_w2_la','10-66.1066-RuralChina-Followup',
                         variables=list('f_r_cores'), missings = TRUE)

```

```{r local_RCh2, echo=F}
t1066_RCh_w2_la <- opal.execute(o,'t1066_RCh_w2_la')
vari <- t1066_RCh_w2_la$f_r_cores
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RCh_w2_la$f_r_cores, missing_values = NA)
ggplot(t1066_RCh_w2_la, aes(x=factor(f_r_cores))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `>=1 into 0`
* `NA into 999`

**R script:**

```{r harmo_RCh2}
t1066_ds_RCh_w2 <- tibble(id=t1066_RCh_w2_la$id)
t1066_ds_RCh_w2$living_alone <- car::recode(t1066_RCh_w2_la$f_r_cores, "0=1; 1:hi=0 ;NA=999")
t1066_ds_RCh_w2$living_alone <- labelled(t1066_ds_RCh_w2$living_alone, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_RCh2, echo=F}
vari <- t1066_ds_RCh_w2$living_alone
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_alone") # EL CAPTION ES EL NOMBRE DE LA HASMONISED VARIABLE
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RCh_w2$living_alone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RCh_w2, aes(x=factor(living_alone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_RCh2, echo=F}
BeforeH <- table(t1066_RCh_w2_la$f_r_cores)
BeforeH <- c(sum(BeforeH[2:length(BeforeH)]), BeforeH[1])
AfterH <- table(t1066_ds_RCh_w2$living_alone)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(">=1->0","0->1")
kable(C)
```



## Dominican Republic

### Wave 1 

#### Study-specific variable description




| **Name** | `alone`|
|-|-|
| **Label** | `living alone` |
| **Table name** | `1066-DominicanRepublic-Baseline` |
| **Categories** | `0.0 = with others; 1.0 = alone` |
| **Description** |  |


```{r assign_DR1, echo=F}
opal.assign.table.tibble(o, 't1066_DR_w1_la','10-66.1066-DominicanRepublic-Baseline',
                         variables=list('alone'), missings = TRUE)
```

```{r local_DR1, echo=F}
t1066_DR_w1_la <- opal.execute(o,'t1066_DR_w1_la')
vari <- t1066_DR_w1_la$alone
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_DR_w1_la$alone, missing_values = NA)
ggplot(t1066_DR_w1_la, aes(x=factor(alone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `0.0 =" with others" into 0`
* `1.0 "alone" into 1`
* `NA into 999`

**R script:**

```{r harmo_DR1}
t1066_ds_DR_w1 <- tibble(id=t1066_DR_w1_la$id)
t1066_ds_DR_w1$living_alone <- car::recode(t1066_DR_w1_la$alone, "NA=999")
t1066_ds_DR_w1$living_alone <- labelled(t1066_ds_DR_w1$living_alone, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_DR1, echo=F}
vari <- t1066_ds_DR_w1$living_alone
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_alone") # EL CAPTION ES EL NOMBRE DE LA HASMONISED VARIABLE
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_DR_w1$living_alone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_DR_w1, aes(x=factor(living_alone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_DR1, echo=F}
BeforeH <- table(t1066_DR_w1_la$alone)
AfterH <- table(t1066_ds_DR_w1$living_alone)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1")
kable(C)
```


### Wave 2 

#### Study-specific variable description



| **Name** | `f_r_cores`|
|-|-|
| **Label** | `number of coresidents` |
| **Table name** | `1066-DominicanRepublic-Followup` |
| **Description** |  |


```{r assign_DR2, echo=F}
opal.assign.table.tibble(o, 't1066_DR_w2_la','10-66.1066-DominicanRepublic-Followup',
                         variables=list('f_r_cores'), missings = TRUE)
```

```{r local_DR2, echo=F}
t1066_DR_w2_la <- opal.execute(o,'t1066_DR_w2_la')
vari <- t1066_DR_w2_la$f_r_cores
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_DR_w2_la$f_r_cores, missing_values = NA)
ggplot(t1066_DR_w2_la, aes(x=factor(f_r_cores))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `>=1 into 0`
* `NA into 999`

**R script:**

```{r harmo_DR2}
t1066_ds_DR_w2 <- tibble(id=t1066_DR_w2_la$id)
t1066_ds_DR_w2$living_alone <- car::recode(t1066_DR_w2_la$f_r_cores, "0=1; 1:hi=0 ;NA=999")
t1066_ds_DR_w2$living_alone <- labelled(t1066_ds_DR_w2$living_alone, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_DR2, echo=F}
vari <- t1066_ds_DR_w2$living_alone
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_alone") # EL CAPTION ES EL NOMBRE DE LA HASMONISED VARIABLE
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_DR_w2$living_alone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_DR_w2, aes(x=factor(living_alone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_DR2, echo=F}
BeforeH <- table(t1066_DR_w2_la$f_r_cores)
BeforeH <- c(sum(BeforeH[2:length(BeforeH)]), BeforeH[1])
AfterH <- table(t1066_ds_DR_w2$living_alone)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(">=1->0","0->1")
kable(C)
```



## Venezuela

### Wave 1 

#### Study-specific variable description



| **Name** | `alone`|
|-|-|
| **Label** | `living alone` |
| **Table name** | `1066-Venezuela-Baseline` |
| **Categories** | `0.0 = with others; 1.0 = alone` |
| **Description** |  |

```{r assign_V2, echo=F}
opal.assign.table.tibble(o, 't1066_Ven_w1_la','10-66.1066-Venezuela-Baseline',
                         variables=list('alone'), missings = TRUE)
```

```{r local_V2, echo=F}
t1066_Ven_w1_la <- opal.execute(o,'t1066_Ven_w1_la')
vari <- t1066_Ven_w1_la$alone
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_Ven_w1_la$alone, missing_values = NA)
ggplot(t1066_Ven_w1_la, aes(x=factor(alone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `0.0 =" with others" into 0`
* `1.0 "alone" into 1`
* `NA into 999`

**R script:**

```{r harmo_V2}
t1066_ds_Ven_w1 <- tibble(id=t1066_Ven_w1_la$id)
t1066_ds_Ven_w1$living_alone <- car::recode(t1066_Ven_w1_la$alone, "NA=999")
t1066_ds_Ven_w1$living_alone <- labelled(t1066_ds_Ven_w1$living_alone, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_V2, echo=F}
vari <- t1066_ds_Ven_w1$living_alone
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_alone") # EL CAPTION ES EL NOMBRE DE LA HASMONISED VARIABLE
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_Ven_w1$living_alone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_Ven_w1, aes(x=factor(living_alone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_V2, echo=F}
BeforeH <- table(t1066_Ven_w1_la$alone)
AfterH <- table(t1066_ds_Ven_w1$living_alone)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1")
kable(C)
```




### Wave 2 

#### Study-specific variable description



| **Name** | `f_r_cores`|
|-|-|
| **Label** | `number of coresidents` |
| **Table name** | `1066-Venezuela-Followup` |
| **Description** |  |

```{r assign_V1, echo=F}
opal.assign.table.tibble(o, 't1066_Ven_w2_la','10-66.1066-Venezuela-Followup',
                         variables=list('f_r_cores'), missings = TRUE)

```

```{r local_V1, echo=F}
t1066_Ven_w2_la <- opal.execute(o,'t1066_Ven_w2_la')
vari <- t1066_Ven_w2_la$f_r_cores
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_Ven_w2_la$f_r_cores, missing_values = NA)
ggplot(t1066_Ven_w2_la, aes(x=factor(f_r_cores))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `>=1 into 0`
* `NA into 999`

**R script:**

```{r harmo_V1}
t1066_ds_Ven_w2 <- tibble(id=t1066_Ven_w2_la$id)
t1066_ds_Ven_w2$living_alone <- car::recode(t1066_Ven_w2_la$f_r_cores, "0=1; 1:hi=0 ;NA=999")
t1066_ds_Ven_w2$living_alone <- labelled(t1066_ds_Ven_w2$living_alone, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_V1, echo=F}
vari <- t1066_ds_Ven_w2$living_alone
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_alone") # EL CAPTION ES EL NOMBRE DE LA HASMONISED VARIABLE
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_Ven_w2$living_alone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_Ven_w2, aes(x=factor(living_alone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_V1, echo=F}
BeforeH <- table(t1066_Ven_w2_la$f_r_cores)
BeforeH <- c(sum(BeforeH[2:length(BeforeH)]), BeforeH[1])
AfterH <- table(t1066_ds_Ven_w2$living_alone)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(">=1->0","0->1")
kable(C)
```






## Urban Peru

### Wave 1 

#### Study-specific variable description



| **Name** | `alone`|
|-|-|
| **Label** | `living alone` |
| **Table name** | `1066-UrbanPeru-Baseline` |
| **Categories** | `0.0 = with others; 1.0 = alone` |
| **Description** |  |


```{r assign_UP, echo=F}
opal.assign.table.tibble(o, 't1066_UP_w1_la','10-66.1066-UrbanPeru-Baseline',
                         variables=list('alone'), missings = TRUE)
```

```{r local_UP1, echo=F}
t1066_UP_w1_la <- opal.execute(o,'t1066_UP_w1_la')
vari <- t1066_UP_w1_la$alone
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UP_w1_la$alone, missing_values = NA)
ggplot(t1066_UP_w1_la, aes(x=factor(alone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `0.0 =" with others" into 0`
* `1.0 "alone" into 1`
* `NA into 999`

**R script:**

```{r harmo_UP1}
t1066_ds_UP_w1 <- tibble(id=t1066_UP_w1_la$id)
t1066_ds_UP_w1$living_alone <- car::recode(t1066_UP_w1_la$alone, "NA=999")
t1066_ds_UP_w1$living_alone <- labelled(t1066_ds_UP_w1$living_alone, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_UP1, echo=F}
vari <- t1066_ds_UP_w1$living_alone
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_alone") # EL CAPTION ES EL NOMBRE DE LA HASMONISED VARIABLE
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UP_w1$living_alone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UP_w1, aes(x=factor(living_alone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_UP1, echo=F}
BeforeH <- table(t1066_UP_w1_la$alone)
AfterH <- table(t1066_ds_UP_w1$living_alone)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1")
kable(C)
```






### Wave 2 

#### Study-specific variable description



| **Name** | `f_r_cores`|
|-|-|
| **Label** | `number of coresidents` |
| **Table name** | `1066-UrbanPeru-Followup` |
| **Description** |  |


```{r assign_UP2, echo=F}
opal.assign.table.tibble(o, 't1066_UP_w2_la','10-66.1066-UrbanPeru-Followup',
                         variables=list('f_r_cores'), missings = TRUE)
```

```{r local_UP2, echo=F}
t1066_UP_w2_la <- opal.execute(o,'t1066_UP_w2_la')
vari <- t1066_UP_w2_la$f_r_cores
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UP_w2_la$f_r_cores, missing_values = NA)
ggplot(t1066_UP_w2_la, aes(x=factor(f_r_cores))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `>=1 into 0`
* `NA into 999`

**R script:**

```{r harmo_UP2}
t1066_ds_UP_w2 <- tibble(id=t1066_UP_w2_la$id)
t1066_ds_UP_w2$living_alone <- car::recode(t1066_UP_w2_la$f_r_cores, "0=1; 1:hi=0 ;NA=999")
t1066_ds_UP_w2$living_alone <- labelled(t1066_ds_UP_w2$living_alone, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_UP2, echo=F}
vari <- t1066_ds_UP_w2$living_alone
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_alone") # EL CAPTION ES EL NOMBRE DE LA HASMONISED VARIABLE
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UP_w2$living_alone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UP_w2, aes(x=factor(living_alone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_UP2, echo=F}
BeforeH <- table(t1066_UP_w2_la$f_r_cores)
BeforeH <- c(sum(BeforeH[2:length(BeforeH)]), BeforeH[1])
AfterH <- table(t1066_ds_UP_w2$living_alone)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(">=1->0","0->1")
kable(C)
```







## Rural Peru

### Wave 1 

#### Study-specific variable description



| **Name** | `alone`|
|-|-|
| **Label** | `living alone` |
| **Table name** | `1066-RuralPeru-Baseline` |
| **Categories** | `0.0 = with others; 1.0 = alone` |
| **Description** |  |


```{r assign_RP, echo=F}
opal.assign.table.tibble(o, 't1066_RP_w1_la','10-66.1066-RuralPeru-Baseline',
                         variables=list('alone'), missings = TRUE)
```

```{r local_RP1, echo=F}
t1066_RP_w1_la <- opal.execute(o,'t1066_RP_w1_la')
vari <- t1066_RP_w1_la$alone
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RP_w1_la$alone, missing_values = NA)
ggplot(t1066_RP_w1_la, aes(x=factor(alone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `0.0 =" with others" into 0`
* `1.0 "alone" into 1`
* `NA into 999`

**R script:**

```{r harmo_RP1}
t1066_ds_RP_w1 <- tibble(id=t1066_RP_w1_la$id)
t1066_ds_RP_w1$living_alone <- car::recode(t1066_RP_w1_la$alone, "NA=999")
t1066_ds_RP_w1$living_alone <- labelled(t1066_ds_RP_w1$living_alone, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_RP1, echo=F}
vari <- t1066_ds_RP_w1$living_alone
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_alone") # EL CAPTION ES EL NOMBRE DE LA HASMONISED VARIABLE
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RP_w1$living_alone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RP_w1, aes(x=factor(living_alone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_RP1, echo=F}
BeforeH <- table(t1066_RP_w1_la$alone)
AfterH <- table(t1066_ds_RP_w1$living_alone)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1")
kable(C)
```






### Wave 2 

#### Study-specific variable description



| **Name** | `f_r_cores`|
|-|-|
| **Label** | `number of coresidents` |
| **Table name** | `1066-RuralPeru-Followup` |
| **Description** |  |


```{r assign_RP2, echo=F}
opal.assign.table.tibble(o, 't1066_RP_w2_la','10-66.1066-RuralPeru-Followup',
                         variables=list('f_r_cores'), missings = TRUE)
```

```{r local_RP2, echo=F}
t1066_RP_w2_la <- opal.execute(o,'t1066_RP_w2_la')
vari <- t1066_RP_w2_la$f_r_cores
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RP_w2_la$f_r_cores, missing_values = NA)
ggplot(t1066_RP_w2_la, aes(x=factor(f_r_cores))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `>=1 into 0`
* `NA into 999`

**R script:**

```{r harmo_RP2}
t1066_ds_RP_w2 <- tibble(id=t1066_RP_w2_la$id)
t1066_ds_RP_w2$living_alone <- car::recode(t1066_RP_w2_la$f_r_cores, "0=1; 1:hi=0 ;NA=999")
t1066_ds_RP_w2$living_alone <- labelled(t1066_ds_RP_w2$living_alone, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_RP2, echo=F}
vari <- t1066_ds_RP_w2$living_alone
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_alone") # EL CAPTION ES EL NOMBRE DE LA HASMONISED VARIABLE
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RP_w2$living_alone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RP_w2, aes(x=factor(living_alone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_RP2, echo=F}
BeforeH <- table(t1066_RP_w2_la$f_r_cores)
BeforeH <- c(sum(BeforeH[2:length(BeforeH)]), BeforeH[1])
AfterH <- table(t1066_ds_RP_w2$living_alone)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(">=1->0","0->1")
kable(C)
```






## Urban Mexico

### Wave 1 

#### Study-specific variable description



| **Name** | `alone`|
|-|-|
| **Label** | `living alone` |
| **Table name** | `1066-UrbanMexico-Baseline` |
| **Categories** | `0.0 = with others; 1.0 = alone` |
| **Description** |  |


```{r assign_UM1, echo=F}
opal.assign.table.tibble(o, 't1066_UM_w1_la','10-66.1066-UrbanMexico-Baseline',
                         variables=list('alone'), missings = TRUE)
```

```{r local_UM1, echo=F}
t1066_UM_w1_la <- opal.execute(o,'t1066_UM_w1_la')
vari <- t1066_UM_w1_la$alone
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UM_w1_la$alone, missing_values = NA)
ggplot(t1066_UM_w1_la, aes(x=factor(alone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `0.0 =" with others" into 0`
* `1.0 "alone" into 1`
* `NA into 999`

**R script:**

```{r harmo_UM1}
t1066_ds_UM_w1 <- tibble(id=t1066_UM_w1_la$id)
t1066_ds_UM_w1$living_alone <- car::recode(t1066_UM_w1_la$alone, "NA=999")
t1066_ds_UM_w1$living_alone <- labelled(t1066_ds_UM_w1$living_alone, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_UM1, echo=F}
vari <- t1066_ds_UM_w1$living_alone
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_alone") # EL CAPTION ES EL NOMBRE DE LA HASMONISED VARIABLE
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UM_w1$living_alone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UM_w1, aes(x=factor(living_alone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_UM1, echo=F}
BeforeH <- table(t1066_UM_w1_la$alone)
AfterH <- table(t1066_ds_UM_w1$living_alone)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1")
kable(C)
```







### Wave 2

#### Study-specific variable description



| **Name** | `f_r_cores`|
|-|-|
| **Label** | `number of coresidents` |
| **Table name** | `1066-UrbanMexico-Followup` |
| **Description** |  |

```{r assign_UM2, echo=F}
opal.assign.table.tibble(o, 't1066_UM_w2_la','10-66.1066-UrbanMexico-Followup',
                         variables=list('f_r_cores'), missings = TRUE)
```

```{r local_UM2, echo=F}
t1066_UM_w2_la <- opal.execute(o,'t1066_UM_w2_la')
vari <- t1066_UM_w2_la$f_r_cores
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_UM_w2_la$f_r_cores, missing_values = NA)
ggplot(t1066_UM_w2_la, aes(x=factor(f_r_cores))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `>=1 into 0`
* `NA into 999`

**R script:**

```{r harmo_UM2}
t1066_ds_UM_w2 <- tibble(id=t1066_UM_w2_la$id)
t1066_ds_UM_w2$living_alone <- car::recode(t1066_UM_w2_la$f_r_cores, "0=1; 1:hi=0 ;NA=999")
t1066_ds_UM_w2$living_alone <- labelled(t1066_ds_UM_w2$living_alone, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_UM2, echo=F}
vari <- t1066_ds_UM_w2$living_alone
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_alone") # EL CAPTION ES EL NOMBRE DE LA HASMONISED VARIABLE
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_UM_w2$living_alone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_UM_w2, aes(x=factor(living_alone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_UM2, echo=F}
BeforeH <- table(t1066_UM_w2_la$f_r_cores)
BeforeH <- c(sum(BeforeH[2:length(BeforeH)]), BeforeH[1], sum(is.na(t1066_UM_w2_la$f_r_cores)))
AfterH <- table(t1066_ds_UM_w2$living_alone)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(">=1->0","0->1", "NA->999")
kable(C)
```






## Rural Mexico

### Wave 1 

#### Study-specific variable description



| **Name** | `alone`|
|-|-|
| **Label** | `living alone` |
| **Table name** | `1066-RuralMexico-Baseline` |
| **Categories** | `0.0 = with others; 1.0 = alone` |
| **Description** |  |

```{r assign_RM1, echo=F}
opal.assign.table.tibble(o, 't1066_RM_w1_la','10-66.1066-RuralMexico-Baseline',
                         variables=list('alone'), missings = TRUE)
```

```{r local_RM1, echo=F}
t1066_RM_w1_la <- opal.execute(o,'t1066_RM_w1_la')
vari <- t1066_RM_w1_la$alone
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RM_w1_la$alone, missing_values = NA)
ggplot(t1066_RM_w1_la, aes(x=factor(alone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `0.0 =" with others" into 0`
* `1.0 "alone" into 1`
* `NA into 999`

**R script:**

```{r harmo_RM1}
t1066_ds_RM_w1 <- tibble(id=t1066_RM_w1_la$id)
t1066_ds_RM_w1$living_alone <- car::recode(t1066_RM_w1_la$alone, "NA=999")
t1066_ds_RM_w1$living_alone <- labelled(t1066_ds_RM_w1$living_alone, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_RM1, echo=F}
vari <- t1066_ds_RM_w1$living_alone
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_alone") # EL CAPTION ES EL NOMBRE DE LA HASMONISED VARIABLE
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RM_w1$living_alone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RM_w1, aes(x=factor(living_alone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_RM1, echo=F}
BeforeH <- table(t1066_RM_w1_la$alone)
AfterH <- table(t1066_ds_RM_w1$living_alone)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1")
kable(C)
```







### Wave 2 

#### Study-specific variable description



| **Name** | `f_r_cores`|
|-|-|
| **Label** | `number of coresidents` |
| **Table name** | `1066-RuralMexico-Followup` |
| **Description** |  |


```{r assign_RM2, echo=F}
opal.assign.table.tibble(o, 't1066_RM_w2_la','10-66.1066-RuralMexico-Followup',
                         variables=list('f_r_cores'), missings = TRUE)

```

```{r local_RM2, echo=F}
t1066_RM_w2_la <- opal.execute(o,'t1066_RM_w2_la')
vari <- t1066_RM_w2_la$f_r_cores
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_RM_w2_la$f_r_cores, missing_values = NA)
ggplot(t1066_RM_w2_la, aes(x=factor(f_r_cores))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `>=1 into 0`
* `NA into 999`

**R script:**

```{r harmo_RM2}
t1066_ds_RM_w2 <- tibble(id=t1066_RM_w2_la$id)
t1066_ds_RM_w2$living_alone <- car::recode(t1066_RM_w2_la$f_r_cores, "0=1; 1:hi=0 ;NA=999")
t1066_ds_RM_w2$living_alone <- labelled(t1066_ds_RM_w2$living_alone, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_RM2, echo=F}
vari <- t1066_ds_RM_w2$living_alone
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_alone") # EL CAPTION ES EL NOMBRE DE LA HASMONISED VARIABLE
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_RM_w2$living_alone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_RM_w2, aes(x=factor(living_alone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_RM2, echo=F}
BeforeH <- table(t1066_RM_w2_la$f_r_cores)
BeforeH <- c(sum(BeforeH[2:length(BeforeH)]), BeforeH[1], sum(is.na(t1066_RM_w2_la$f_r_cores)))
AfterH <- table(t1066_ds_RM_w2$living_alone)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(">=1->0","0->1", "NA->999")
kable(C)
```







## Puerto Rico

### Wave 1 

#### Study-specific variable description



| **Name** | `alone`|
|-|-|
| **Label** | `living alone` |
| **Table name** | `1066-PuertoRico-Baseline` |
| **Categories** | `0.0 = with others; 1.0 = alone` |
| **Description** |  |


```{r assign_PR1, echo=F}
opal.assign.table.tibble(o, 't1066_PR_w1_la','10-66.1066-PuertoRico-Baseline',
                         variables=list('alone'), missings = TRUE)
```

```{r local_PR1, echo=F}
t1066_PR_w1_la <- opal.execute(o,'t1066_PR_w1_la')
vari <- t1066_PR_w1_la$alone
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_PR_w1_la$alone, missing_values = NA)
ggplot(t1066_PR_w1_la, aes(x=factor(alone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `0.0 =" with others" into 0`
* `1.0 "alone" into 1`
* `NA into 999`

**R script:**

```{r harmo_PR1}
t1066_ds_PR_w1 <- tibble(id=t1066_PR_w1_la$id)
t1066_ds_PR_w1$living_alone <- car::recode(t1066_PR_w1_la$alone, "NA=999")
t1066_ds_PR_w1$living_alone <- labelled(t1066_ds_PR_w1$living_alone, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_PR1, echo=F}
vari <- t1066_ds_PR_w1$living_alone
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_alone") # EL CAPTION ES EL NOMBRE DE LA HASMONISED VARIABLE
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_PR_w1$living_alone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_PR_w1, aes(x=factor(living_alone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_PR1, echo=F}
BeforeH <- table(t1066_PR_w1_la$alone)
AfterH <- table(t1066_ds_PR_w1$living_alone)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0","1")
kable(C)
```







### Wave 2 

#### Study-specific variable description



| **Name** | `f_r_cores`|
|-|-|
| **Label** | `number of coresidents` |
| **Table name** | `1066-PuertoRico-Followup` |
| **Description** |  |



```{r assign_PR2, echo=F}
opal.assign.table.tibble(o, 't1066_PR_w2_la','10-66.1066-PuertoRico-Followup',
                         variables=list('f_r_cores'), missings = TRUE)

```

```{r local_PR2, echo=F}
t1066_PR_w2_la <- opal.execute(o,'t1066_PR_w2_la')
vari <- t1066_PR_w2_la$f_r_cores
kable(Categorical_summary(vari, missing_values = NA)[2], caption = attributes(vari)$`spss::shortName`)
kable(Categorical_summary(vari, missing_values = NA)[1], caption = "Category")
#Categorical_summary(var = t1066_PR_w2_la$f_r_cores, missing_values = NA)
ggplot(t1066_PR_w2_la, aes(x=factor(f_r_cores))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variable it has to be recoded as follows:

* `0 into 1`
* `>=1 into 0`
* `NA into 999`

**R script:**

```{r harmo_PR2}
t1066_ds_PR_w2 <- tibble(id=t1066_PR_w2_la$id)
t1066_ds_PR_w2$living_alone <- car::recode(t1066_PR_w2_la$f_r_cores, "0=1; 1:hi=0 ;NA=999")
t1066_ds_PR_w2$living_alone <- labelled(t1066_ds_PR_w2$living_alone, labels = c("No"=0, "Yes"=1, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not attempt not done"=994, "Does not answer"=995,  "Not applicable"=996, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript_PR2, echo=F}
vari <- t1066_ds_PR_w2$living_alone
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "living_alone") # EL CAPTION ES EL NOMBRE DE LA HASMONISED VARIABLE
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
#Categorical_summary(var = t1066_ds_PR_w2$living_alone, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(t1066_ds_PR_w2, aes(x=factor(living_alone))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Living Alone") + ylab("Frequency")
```

#### Validation
```{r crosstabulation_PR2, echo=F}
BeforeH <- table(t1066_PR_w2_la$f_r_cores)
BeforeH <- c(sum(BeforeH[2:length(BeforeH)]), BeforeH[1], sum(is.na(t1066_PR_w2_la$f_r_cores)))
AfterH <- table(t1066_ds_PR_w2$living_alone)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(">=1->0","0->1", "NA->999")
kable(C)
```






# Quality estimation
No comments.




```{r save, echo=FALSE}
living_alone <- t1066_ds_cuba_w1
save(living_alone, file = "../RData/cuba_w1/living_alone.RData")
rm(living_alone)

living_alone <- t1066_ds_cuba_w2
save(living_alone, file = "../RData/cuba_w2/living_alone.RData")
rm(living_alone)

living_alone <- t1066_ds_india_w1
save(living_alone, file = "../RData/india_w1/living_alone.RData")
rm(living_alone)

living_alone <- t1066_ds_UCh_w1
save(living_alone, file = "../RData/UCh_w1/living_alone.RData")
rm(living_alone)

living_alone <- t1066_ds_UCh_w2
save(living_alone, file = "../RData/UCh_w2/living_alone.RData")
rm(living_alone)

living_alone <- t1066_ds_RCh_w1
save(living_alone, file = "../RData/RCh_w1/living_alone.RData")
rm(living_alone)

living_alone <- t1066_ds_RCh_w2
save(living_alone, file = "../RData/RCh_w2/living_alone.RData")
rm(living_alone)

living_alone <- t1066_ds_DR_w1
save(living_alone, file = "../RData/DR_w1/living_alone.RData")
rm(living_alone)

living_alone <- t1066_ds_DR_w2
save(living_alone, file = "../RData/DR_w2/living_alone.RData")
rm(living_alone)

living_alone <- t1066_ds_Ven_w1
save(living_alone, file = "../RData/Ven_w1/living_alone.RData")
rm(living_alone)

living_alone <- t1066_ds_Ven_w2
save(living_alone, file = "../RData/Ven_w2/living_alone.RData")
rm(living_alone)

living_alone <- t1066_ds_UP_w1
save(living_alone, file = "../RData/UP_w1/living_alone.RData")
rm(living_alone)

living_alone <- t1066_ds_UP_w2
save(living_alone, file = "../RData/UP_w2/living_alone.RData")
rm(living_alone)

living_alone <- t1066_ds_RP_w1
save(living_alone, file = "../RData/RP_w1/living_alone.RData")
rm(living_alone)

living_alone <- t1066_ds_RP_w2
save(living_alone, file = "../RData/RP_w2/living_alone.RData")
rm(living_alone)

living_alone <- t1066_ds_UM_w1
save(living_alone, file = "../RData/UM_w1/living_alone.RData")
rm(living_alone)

living_alone <- t1066_ds_UM_w2
save(living_alone, file = "../RData/UM_w2/living_alone.RData")
rm(living_alone)

living_alone <- t1066_ds_RM_w1
save(living_alone, file = "../RData/RM_w1/living_alone.RData")
rm(living_alone)

living_alone <- t1066_ds_RM_w2
save(living_alone, file = "../RData/RM_w2/living_alone.RData")
rm(living_alone)

living_alone <- t1066_ds_PR_w1
save(living_alone, file = "../RData/PR_w1/living_alone.RData")
rm(living_alone)

living_alone <- t1066_ds_PR_w2
save(living_alone, file = "../RData/PR_w2/living_alone.RData")
rm(living_alone)

```


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
