---
title: "Non paid work"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/nonpaid_workDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/nonpaid_workDS.R')
```



# Data process



## Cuba


### Wave 1


#### Study-specific variable description

| **Name** | `PJOB`|
|-|-|
| **Label** | `occupation`|
| **Table name**  | `1066-Cuba-Baseline` |
| **Categories** | `1 = paid full time work`<br/>`2 = paid part time work`<br/>`3 = unemployed (looking for work)`<br/>`4 = student`<br/>`5 = housewife/ househusband`<br/>`6 = retired` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign cuba_w1, echo=F}

opal.assign.table.tibble(o, 't1066_cuba_w1','10-66.1066-Cuba-Baseline',variables=list('PJOB'), missings = T)
t1066_cuba_w1 <- opal.execute(o,'t1066_cuba_w1')

```

```{r local cuba_w1, echo=F}

vbl <- t1066_cuba_w1$PJOB
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_cuba_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_cuba_w1, aes(x=factor(PJOB))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `nonpaid_work` from the study-specific variable it has to be recoded as follows:

* `PJOB == 1, 2, 3 or 6 into 996`
* `PJOB == 4 into 3`
* `PJOB == 5 into 1`
* `NA into 999`

**R script:**

```{r harmo cuba_w1}

t1066_ds_cuba_w1 <- tibble(id=t1066_cuba_w1$id)
t1066_ds_cuba_w1$nonpaid_work <- car::recode(t1066_cuba_w1$PJOB, "5 = 1; 4=3; c(1,2,3,6) = 996; NA = 999")
```


#### Statistics of the new harmonized variable

```{r descript cuba_w1, echo=F}

vbl <- t1066_ds_cuba_w1$nonpaid_work
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_cuba_w1, aes(x=factor(nonpaid_work))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation cuba_w1, echo=F}

AfterH <- table(t1066_ds_cuba_w1$nonpaid_work)
X <- table(t1066_cuba_w1$PJOB,useNA = "ifany")
BeforeH <- c(X[4],sum(X[c(1,2,3,5)]),X[6])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->1","1,2,3,6->996","NA->999")
kable(C)

```



### Wave 2


#### Study-specific variable description

| **Name** | `f_PJOB`|
|-|-|
| **Label** | `occupation`|
| **Table name**  | `1066-Cuba-Followup` |
| **Categories** | `1 = paid full time work`<br/>`2 = paid part time work`<br/>`3 = unemployed (looking for work)`<br/>`4 = student`<br/>`5 = housewife/ househusband`<br/>`6 = retired` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign cuba_w2, echo=F}

opal.assign.table.tibble(o, 't1066_cuba_w2','10-66.1066-Cuba-Followup',variables=list('f_PJOB'), missings = T)
t1066_cuba_w2 <- opal.execute(o,'t1066_cuba_w2')

```

```{r local cuba_w2, echo=F}

vbl <- t1066_cuba_w2$f_PJOB
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_cuba_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_cuba_w2, aes(x=factor(f_PJOB))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `nonpaid_work` from the study-specific variable it has to be recoded as follows:

* `f_PJOB == 1, 2, 3 or 6 into 996`
* `f_PJOB == 4 into 3`
* `f_PJOB == 5 into 1`
* `NA into 999`

**R script:**

```{r harmo cuba_w2}

t1066_ds_cuba_w2 <- tibble(id=t1066_cuba_w2$id)
t1066_ds_cuba_w2$nonpaid_work <- car::recode(t1066_cuba_w2$f_PJOB, "5 = 1; 4=3; c(1,2,3,6) = 996; NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript cuba_w2, echo=F}

vbl <- t1066_ds_cuba_w2$nonpaid_work
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_cuba_w2, aes(x=factor(nonpaid_work))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation cuba_w2, echo=F}

AfterH <- table(t1066_ds_cuba_w2$nonpaid_work)
X <- table(t1066_cuba_w2$f_PJOB,useNA = "ifany")
BeforeH <- c(X[4],sum(X[c(1,2,3,5)]),X[6])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->1","1,2,3,6->996","NA->999")
kable(C)

```



## India


### Wave 1


#### Study-specific variable description

| **Name** | `PJOB`|
|-|-|
| **Label** | `occupation`|
| **Table name**  | `1066-India-Baseline` |
| **Categories** | `1 = paid full time work`<br/>`2 = paid part time work`<br/>`3 = unemployed (looking for work)`<br/>`4 = student`<br/>`5 = housewife/ househusband`<br/>`6 = retired` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign india_w1, echo=F}

opal.assign.table.tibble(o, 't1066_india_w1','10-66.1066-India-Baseline',variables=list('PJOB'), missings = T)
t1066_india_w1 <- opal.execute(o,'t1066_india_w1')

```

```{r local india_w1, echo=F}

vbl <- t1066_india_w1$PJOB
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_india_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_india_w1, aes(x=factor(PJOB))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `nonpaid_work` from the study-specific variable it has to be recoded as follows:

* `PJOB == 1, 2, 3 or 6 into 996`
* `PJOB == 4 into 3`
* `PJOB == 5 into 1`
* `NA into 999`

**R script:**

```{r harmo india_w1}

t1066_ds_india_w1 <- tibble(id=t1066_india_w1$id)
t1066_ds_india_w1$nonpaid_work <- car::recode(t1066_india_w1$PJOB, "5 = 1; 4=3; c(1,2,3,6) = 996; NA = 999")
```


#### Statistics of the new harmonized variable

```{r descript india_w1, echo=F}

vbl <- t1066_ds_india_w1$nonpaid_work
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_india_w1, aes(x=factor(nonpaid_work))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation india_w1, echo=F}

AfterH <- table(t1066_ds_india_w1$nonpaid_work)
X <- table(t1066_india_w1$PJOB,useNA = "ifany")
BeforeH <- c(X[5:4],sum(X[c(1,2,3,6)]),X[7])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->1","4->3","1,2,3,6->996","NA->999")
kable(C)

```




## Urban China


### Wave 1


#### Study-specific variable description

| **Name** | `PJOB`|
|-|-|
| **Label** | `occupation`|
| **Table name**  | `1066-UrbanChina-Baseline` |
| **Categories** | `1 = paid full time work`<br/>`2 = paid part time work`<br/>`3 = unemployed (looking for work)`<br/>`4 = student`<br/>`5 = housewife/ househusband`<br/>`6 = retired` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign UCh_w1, echo=F}

opal.assign.table.tibble(o, 't1066_UCh_w1','10-66.1066-UrbanChina-Baseline',variables=list('PJOB'), missings = T)
t1066_UCh_w1 <- opal.execute(o,'t1066_UCh_w1')

```

```{r local UCh_w1, echo=F}

vbl <- t1066_UCh_w1$PJOB
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UCh_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UCh_w1, aes(x=factor(PJOB))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `nonpaid_work` from the study-specific variable it has to be recoded as follows:

* `PJOB == 1, 2, 3 or 6 into 996`
* `PJOB == 4 into 3`
* `PJOB == 5 into 1`
* `NA into 999`

**R script:**

```{r harmo UCh_w1}

t1066_ds_UCh_w1 <- tibble(id=t1066_UCh_w1$id)
t1066_ds_UCh_w1$nonpaid_work <- car::recode(t1066_UCh_w1$PJOB, "5 = 1; 4=3; c(1,2,3,6) = 996; NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript UCh_w1, echo=F}

vbl <- t1066_ds_UCh_w1$nonpaid_work
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UCh_w1, aes(x=factor(nonpaid_work))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation UCh_w1, echo=F}

AfterH <- table(t1066_ds_UCh_w1$nonpaid_work)
X <- table(t1066_UCh_w1$PJOB,useNA = "ifany")
BeforeH <- c(X[3],sum(X[c(1,2,4)]),X[5])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->1","1,2,3,6->996","NA->999")
kable(C)

```



### Wave 2


#### Study-specific variable description

| **Name** | `f_PJOB`|
|-|-|
| **Label** | `occupation`|
| **Table name**  | `1066-UrbanChina-Followup` |
| **Categories** | `1 = paid full time work`<br/>`2 = paid part time work`<br/>`3 = unemployed (looking for work)`<br/>`4 = student`<br/>`5 = housewife/ househusband`<br/>`6 = retired` |
| **Description** |  |


```{r assign UCh_w2, echo=F}

opal.assign.table.tibble(o, 't1066_UCh_w2','10-66.1066-UrbanChina-Followup',variables=list('f_PJOB'), missings = T)
t1066_UCh_w2 <- opal.execute(o,'t1066_UCh_w2')

```

```{r local UCh_w2, echo=F}

vbl <- t1066_UCh_w2$f_PJOB
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UCh_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UCh_w2, aes(x=factor(f_PJOB))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `nonpaid_work` from the study-specific variable it has to be recoded as follows:

* `f_PJOB == 1, 2, 3 or 6 into 996`
* `f_PJOB == 4 into 3`
* `f_PJOB == 5 into 1`
* `NA into 999`

**R script:**

```{r harmo UCh_w2}

t1066_ds_UCh_w2 <- tibble(id=t1066_UCh_w2$id)
t1066_ds_UCh_w2$nonpaid_work <- car::recode(t1066_UCh_w2$f_PJOB, "5 = 1; 4=3; c(1,2,3,6) = 996; NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript UCh_w2, echo=F}

vbl <- t1066_ds_UCh_w2$nonpaid_work
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UCh_w2, aes(x=factor(nonpaid_work))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation UCh_w2, echo=F}

AfterH <- table(t1066_ds_UCh_w2$nonpaid_work)
X <- table(t1066_UCh_w2$f_PJOB,useNA = "ifany")
BeforeH <- c(X[4],sum(X[c(1,2,3,5)]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->1","1,2,3,6->996")
kable(C)

```



## Rural China


### Wave 1


#### Study-specific variable description

| **Name** | `PJOB`|
|-|-|
| **Label** | `occupation`|
| **Table name**  | `1066-RuralChina-Baseline` |
| **Categories** | `1 = paid full time work`<br/>`2 = paid part time work`<br/>`3 = unemployed (looking for work)`<br/>`4 = student`<br/>`5 = housewife/ househusband`<br/>`6 = retired` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign RCh_w1, echo=F}

opal.assign.table.tibble(o, 't1066_RCh_w1','10-66.1066-RuralChina-Baseline',variables=list('PJOB'), missings = T)
t1066_RCh_w1 <- opal.execute(o,'t1066_RCh_w1')

```

```{r local RCh_w1, echo=F}

vbl <- t1066_RCh_w1$PJOB
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RCh_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RCh_w1, aes(x=factor(PJOB))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `nonpaid_work` from the study-specific variable it has to be recoded as follows:

* `PJOB == 1, 2, 3 or 6 into 996`
* `PJOB == 4 into 3`
* `PJOB == 5 into 1`
* `NA into 999`

**R script:**

```{r harmo RCh_w1}

t1066_ds_RCh_w1 <- tibble(id=t1066_RCh_w1$id)
t1066_ds_RCh_w1$nonpaid_work <- car::recode(t1066_RCh_w1$PJOB, "5 = 1; 4=3; c(1,2,3,6) = 996; NA = 999")
```


#### Statistics of the new harmonized variable

```{r descript RCh_w1, echo=F}

vbl <- t1066_ds_RCh_w1$nonpaid_work
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RCh_w1, aes(x=factor(nonpaid_work))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation RCh_w1, echo=F}

AfterH <- table(t1066_ds_RCh_w1$nonpaid_work)
X <- table(t1066_RCh_w1$PJOB,useNA = "ifany")
BeforeH <- c(X[4],sum(X[c(1,2,3,5)]),X[6])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->1","1,2,3,6->996","NA->999")
kable(C)

```



### Wave 2


#### Study-specific variable description

| **Name** | `f_PJOB`|
|-|-|
| **Label** | `occupation`|
| **Table name**  | `1066-RuralChina-Followup` |
| **Categories** | `1 = paid full time work`<br/>`2 = paid part time work`<br/>`3 = unemployed (looking for work)`<br/>`4 = student`<br/>`5 = housewife/ househusband`<br/>`6 = retired` |
| **Description** |  |

```{r assign RCh_w2, echo=F}

opal.assign.table.tibble(o, 't1066_RCh_w2','10-66.1066-RuralChina-Followup',variables=list('f_PJOB'), missings = T)
t1066_RCh_w2 <- opal.execute(o,'t1066_RCh_w2')

```

```{r local RCh_w2, echo=F}

vbl <- t1066_RCh_w2$f_PJOB
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RCh_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RCh_w2, aes(x=factor(f_PJOB))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `nonpaid_work` from the study-specific variable it has to be recoded as follows:

* `f_PJOB == 1, 2, 3 or 6 into 996`
* `f_PJOB == 4 into 3`
* `f_PJOB == 5 into 1`
* `NA into 999`

**R script:**

```{r harmo RCh_w2}

t1066_ds_RCh_w2 <- tibble(id=t1066_RCh_w2$id)
t1066_ds_RCh_w2$nonpaid_work <- car::recode(t1066_RCh_w2$f_PJOB, "5 = 1; 4=3; c(1,2,3,6) = 996; NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript RCh_w2, echo=F}

vbl <- t1066_ds_RCh_w2$nonpaid_work
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RCh_w2, aes(x=factor(nonpaid_work))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation RCh_w2, echo=F}

AfterH <- table(t1066_ds_RCh_w2$nonpaid_work)
X <- table(t1066_RCh_w2$f_PJOB,useNA = "ifany")
BeforeH <- c(X[4],sum(X[c(1,2,3,5)]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->1","1,2,3,6->996")
kable(C)

```



## Dominican Republic


### Wave 1


#### Study-specific variable description

| **Name** | `PJOB`|
|-|-|
| **Label** | `occupation`|
| **Table name**  | `1066-DominicanRepublic-Baseline` |
| **Categories** | `1 = paid full time work`<br/>`2 = paid part time work`<br/>`3 = unemployed (looking for work)`<br/>`4 = student`<br/>`5 = housewife/ househusband`<br/>`6 = retired` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign DR_w1, echo=F}

opal.assign.table.tibble(o, 't1066_DR_w1','10-66.1066-DominicanRepublic-Baseline',variables=list('PJOB'), missings = T)
t1066_DR_w1 <- opal.execute(o,'t1066_DR_w1')

```

```{r local DR_w1, echo=F}

vbl <- t1066_DR_w1$PJOB
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_DR_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_DR_w1, aes(x=factor(PJOB))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `nonpaid_work` from the study-specific variable it has to be recoded as follows:

* `PJOB == 1, 2, 3 or 6 into 996`
* `PJOB == 4 into 3`
* `PJOB == 5 into 1`
* `NA into 999`

**R script:**

```{r harmo DR_w1}

t1066_ds_DR_w1 <- tibble(id=t1066_DR_w1$id)
t1066_ds_DR_w1$nonpaid_work <- car::recode(t1066_DR_w1$PJOB, "5 = 1; 4=3; c(1,2,3,6) = 996; NA = 999")
```


#### Statistics of the new harmonized variable

```{r descript DR_w1, echo=F}

vbl <- t1066_ds_DR_w1$nonpaid_work
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_DR_w1, aes(x=factor(nonpaid_work))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation DR_w1, echo=F}

AfterH <- table(t1066_ds_DR_w1$nonpaid_work)
X <- table(t1066_DR_w1$PJOB,useNA = "ifany")
BeforeH <- c(X[5:4],sum(X[c(1,2,3,6)]),X[7])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->1","4->3","1,2,3,6->996","NA->999")
kable(C)


```



### Wave 2


#### Study-specific variable description

| **Name** | `f_PJOB`|
|-|-|
| **Label** | `occupation`|
| **Table name**  | `1066-DominicanRepublic-Followup` |
| **Categories** | `1 = paid full time work`<br/>`2 = paid part time work`<br/>`3 = unemployed (looking for work)`<br/>`4 = student`<br/>`5 = housewife/ househusband`<br/>`6 = retired` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign DR_w2, echo=F}

opal.assign.table.tibble(o, 't1066_DR_w2','10-66.1066-DominicanRepublic-Followup',variables=list('f_PJOB'), missings = T)
t1066_DR_w2 <- opal.execute(o,'t1066_DR_w2')

```

```{r local DR_w2, echo=F}

vbl <- t1066_DR_w2$f_PJOB
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_DR_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_DR_w2, aes(x=factor(f_PJOB))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `nonpaid_work` from the study-specific variable it has to be recoded as follows:

* `f_PJOB == 1, 2, 3 or 6 into 996`
* `f_PJOB == 4 into 3`
* `f_PJOB == 5 into 1`
* `NA into 999`

**R script:**

```{r harmo DR_w2}

t1066_ds_DR_w2 <- tibble(id=t1066_DR_w2$id)
t1066_ds_DR_w2$nonpaid_work <- car::recode(t1066_DR_w2$f_PJOB, "5 = 1; 4=3; c(1,2,3,6) = 996; NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript DR_w2, echo=F}

vbl <- t1066_ds_DR_w2$nonpaid_work
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_DR_w2, aes(x=factor(nonpaid_work))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation DR_w2, echo=F}

AfterH <- table(t1066_ds_DR_w2$nonpaid_work)
X <- table(t1066_DR_w2$f_PJOB,useNA = "ifany")
BeforeH <- c(X[5:4],sum(X[c(1,2,3,6)]),X[7])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->1","4->3","1,2,3,6->996","NA->999")
kable(C)

```



## Venezuela


### Wave 1


#### Study-specific variable description

| **Name** | `PJOB`|
|-|-|
| **Label** | `occupation`|
| **Table name**  | `1066-Venezuela-Baseline` |
| **Categories** | `1 = paid full time work`<br/>`2 = paid part time work`<br/>`3 = unemployed (looking for work)`<br/>`4 = student`<br/>`5 = housewife/ househusband`<br/>`6 = retired` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign Ven_w1, echo=F}

opal.assign.table.tibble(o, 't1066_Ven_w1','10-66.1066-Venezuela-Baseline',variables=list('PJOB'), missings = T)
t1066_Ven_w1 <- opal.execute(o,'t1066_Ven_w1')

```

```{r local Ven_w1, echo=F}

vbl <- t1066_Ven_w1$PJOB
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_Ven_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_Ven_w1, aes(x=factor(PJOB))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `nonpaid_work` from the study-specific variable it has to be recoded as follows:

* `PJOB == 1, 2, 3 or 6 into 996`
* `PJOB == 4 into 3`
* `PJOB == 5 into 1`
* `NA into 999`

**R script:**

```{r harmo Ven_w1}

t1066_ds_Ven_w1 <- tibble(id=t1066_Ven_w1$id)
t1066_ds_Ven_w1$nonpaid_work <- car::recode(t1066_Ven_w1$PJOB, "5 = 1; 4=3; c(1,2,3,6) = 996; NA = 999")
```


#### Statistics of the new harmonized variable

```{r descript Ven_w1, echo=F}

vbl <- t1066_ds_Ven_w1$nonpaid_work
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_Ven_w1, aes(x=factor(nonpaid_work))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation Ven_w1, echo=F}

AfterH <- table(t1066_ds_Ven_w1$nonpaid_work)
X <- table(t1066_Ven_w1$PJOB,useNA = "ifany")
BeforeH <- c(X[5:4],sum(X[c(1,2,3,6)]),X[7])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->1","4->3","1,2,3,6->996","NA->999")
kable(C)

```



### Wave 2


#### Study-specific variable description

| **Name** | `f_PJOB`|
|-|-|
| **Label** | `occupation`|
| **Table name**  | `1066-Venezuela-Followup` |
| **Categories** | `1 = paid full time work`<br/>`2 = paid part time work`<br/>`3 = unemployed (looking for work)`<br/>`4 = student`<br/>`5 = housewife/ househusband`<br/>`6 = retired` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign Ven_w2, echo=F}

opal.assign.table.tibble(o, 't1066_Ven_w2','10-66.1066-Venezuela-Followup',variables=list('f_PJOB'), missings = T)
t1066_Ven_w2 <- opal.execute(o,'t1066_Ven_w2')

```

```{r local Ven_w2, echo=F}

vbl <- t1066_Ven_w2$f_PJOB
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_Ven_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_Ven_w2, aes(x=factor(f_PJOB))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `nonpaid_work` from the study-specific variable it has to be recoded as follows:

* `f_PJOB == 1, 2, 3 or 6 into 996`
* `f_PJOB == 4 into 3`
* `f_PJOB == 5 into 1`
* `NA into 999`

**R script:**

```{r harmo Ven_w2}

t1066_ds_Ven_w2 <- tibble(id=t1066_Ven_w2$id)
t1066_ds_Ven_w2$nonpaid_work <- car::recode(t1066_Ven_w2$f_PJOB, "5 = 1; 4=3; c(1,2,3,6) = 996; NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript Ven_w2, echo=F}

vbl <- t1066_ds_Ven_w2$nonpaid_work
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_Ven_w2, aes(x=factor(nonpaid_work))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation Ven_w2, echo=F}

AfterH <- table(t1066_ds_Ven_w2$nonpaid_work)
X <- table(t1066_Ven_w2$f_PJOB,useNA = "ifany")
BeforeH <- c(X[4],sum(X[c(1,2,3,5)]),X[6])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->1","1,2,3,6->996","NA->999")
kable(C)

```



## Urban Peru


### Wave 1


#### Study-specific variable description

| **Name** | `PJOB`|
|-|-|
| **Label** | `occupation`|
| **Table name**  | `1066-UrbanPeru-Baseline` |
| **Categories** | `1 = paid full time work`<br/>`2 = paid part time work`<br/>`3 = unemployed (looking for work)`<br/>`4 = student`<br/>`5 = housewife/ househusband`<br/>`6 = retired` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign UP_w1, echo=F}

opal.assign.table.tibble(o, 't1066_UP_w1','10-66.1066-UrbanPeru-Baseline',variables=list('PJOB'), missings = T)
t1066_UP_w1 <- opal.execute(o,'t1066_UP_w1')

```

```{r local UP_w1, echo=F}

vbl <- t1066_UP_w1$PJOB
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UP_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UP_w1, aes(x=factor(PJOB))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `nonpaid_work` from the study-specific variable it has to be recoded as follows:

* `PJOB == 1, 2, 3 or 6 into 996`
* `PJOB == 4 into 3`
* `PJOB == 5 into 1`
* `NA into 999`

**R script:**

```{r harmo UP_w1}

t1066_ds_UP_w1 <- tibble(id=t1066_UP_w1$id)
t1066_ds_UP_w1$nonpaid_work <- car::recode(t1066_UP_w1$PJOB, "5 = 1; 4=3; c(1,2,3,6) = 996; NA = 999")
```


#### Statistics of the new harmonized variable

```{r descript UP_w1, echo=F}

vbl <- t1066_ds_UP_w1$nonpaid_work
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UP_w1, aes(x=factor(nonpaid_work))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation UP_w1, echo=F}

AfterH <- table(t1066_ds_UP_w1$nonpaid_work)
X <- table(t1066_UP_w1$PJOB,useNA = "ifany")
BeforeH <- c(X[5:4],sum(X[c(1,2,3,6)]),X[7])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->1","4->3","1,2,3,6->996","NA->999")
kable(C)

```



### Wave 2


#### Study-specific variable description

| **Name** | `f_PJOB`|
|-|-|
| **Label** | `occupation`|
| **Table name**  | `1066-UrbanPeru-Followup` |
| **Categories** | `1 = paid full time work`<br/>`2 = paid part time work`<br/>`3 = unemployed (looking for work)`<br/>`4 = student`<br/>`5 = housewife/ househusband`<br/>`6 = retired` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign UP_w2, echo=F}

opal.assign.table.tibble(o, 't1066_UP_w2','10-66.1066-UrbanPeru-Followup',variables=list('f_PJOB'), missings = T)
t1066_UP_w2 <- opal.execute(o,'t1066_UP_w2')

```

```{r local UP_w2, echo=F}

vbl <- t1066_UP_w2$f_PJOB
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UP_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UP_w2, aes(x=factor(f_PJOB))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `nonpaid_work` from the study-specific variable it has to be recoded as follows:

* `f_PJOB == 1, 2, 3 or 6 into 996`
* `f_PJOB == 4 into 3`
* `f_PJOB == 5 into 1`
* `NA into 999`

**R script:**

```{r harmo UP_w2}

t1066_ds_UP_w2 <- tibble(id=t1066_UP_w2$id)
t1066_ds_UP_w2$nonpaid_work <- car::recode(t1066_UP_w2$f_PJOB, "5 = 1; 4=3; c(1,2,3,6) = 996; NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript UP_w2, echo=F}

vbl <- t1066_ds_UP_w2$nonpaid_work
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UP_w2, aes(x=factor(nonpaid_work))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation UP_w2, echo=F}

AfterH <- table(t1066_ds_UP_w2$nonpaid_work)
X <- table(t1066_UP_w2$f_PJOB,useNA = "ifany")
BeforeH <- c(X[4],sum(X[c(1,2,3,5)]),X[6])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->1","1,2,3,6->996","NA->999")
kable(C)

```



## Rural Peru


### Wave 1


#### Study-specific variable description

| **Name** | `PJOB`|
|-|-|
| **Label** | `occupation`|
| **Table name**  | `1066-RuralPeru-Baseline` |
| **Categories** | `1 = paid full time work`<br/>`2 = paid part time work`<br/>`3 = unemployed (looking for work)`<br/>`4 = student`<br/>`5 = housewife/ househusband`<br/>`6 = retired` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign RP_w1, echo=F}

opal.assign.table.tibble(o, 't1066_RP_w1','10-66.1066-RuralPeru-Baseline',variables=list('PJOB'), missings = T)
t1066_RP_w1 <- opal.execute(o,'t1066_RP_w1')

```

```{r local RP_w1, echo=F}

vbl <- t1066_RP_w1$PJOB
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RP_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RP_w1, aes(x=factor(PJOB))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `nonpaid_work` from the study-specific variable it has to be recoded as follows:

* `PJOB == 1, 2, 3 or 6 into 996`
* `PJOB == 4 into 3`
* `PJOB == 5 into 1`
* `NA into 999`

**R script:**

```{r harmo RP_w1}

t1066_ds_RP_w1 <- tibble(id=t1066_RP_w1$id)
t1066_ds_RP_w1$nonpaid_work <- car::recode(t1066_RP_w1$PJOB, "5 = 1; 4=3; c(1,2,3,6) = 996; NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript RP_w1, echo=F}

vbl <- t1066_ds_RP_w1$nonpaid_work
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RP_w1, aes(x=factor(nonpaid_work))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation RP_w1, echo=F}

AfterH <- table(t1066_ds_RP_w1$nonpaid_work)
X <- table(t1066_RP_w1$PJOB,useNA = "ifany")
BeforeH <- c(X[5:4],sum(X[c(1,2,3,6)]),X[7])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->1","4->3","1,2,3,6->996","NA->999")
kable(C)

```



### Wave 2


#### Study-specific variable description

| **Name** | `f_PJOB`|
|-|-|
| **Label** | `occupation`|
| **Table name**  | `1066-RuralPeru-Followup` |
| **Categories** | `1 = paid full time work`<br/>`2 = paid part time work`<br/>`3 = unemployed (looking for work)`<br/>`4 = student`<br/>`5 = housewife/ househusband`<br/>`6 = retired` |
| **Description** |  |


```{r assign RP_w2, echo=F}

opal.assign.table.tibble(o, 't1066_RP_w2','10-66.1066-RuralPeru-Followup',variables=list('f_PJOB'), missings = T)
t1066_RP_w2 <- opal.execute(o,'t1066_RP_w2')

```

```{r local RP_w2, echo=F}

vbl <- t1066_RP_w2$f_PJOB
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RP_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RP_w2, aes(x=factor(f_PJOB))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `nonpaid_work` from the study-specific variable it has to be recoded as follows:

* `f_PJOB == 1, 2, 3 or 6 into 996`
* `f_PJOB == 4 into 3`
* `f_PJOB == 5 into 1`
* `NA into 999`

**R script:**

```{r harmo RP_w2}

t1066_ds_RP_w2 <- tibble(id=t1066_RP_w2$id)
t1066_ds_RP_w2$nonpaid_work <- car::recode(t1066_RP_w2$f_PJOB, "5 = 1; 4=3; c(1,2,3,6) = 996; NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript RP_w2, echo=F}

vbl <- t1066_ds_RP_w2$nonpaid_work
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RP_w2, aes(x=factor(nonpaid_work))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation RP_w2, echo=F}

AfterH <- table(t1066_ds_RP_w2$nonpaid_work)
X <- table(t1066_RP_w2$f_PJOB,useNA = "ifany")
BeforeH <- c(X[4],sum(X[c(1,2,3,5)]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->1","1,2,3,6->996")
kable(C)

```



## Urban Mexico


### Wave 1


#### Study-specific variable description

| **Name** | `PJOB`|
|-|-|
| **Label** | `occupation`|
| **Table name**  | `1066-UrbanMexico-Baseline` |
| **Categories** | `1 = paid full time work`<br/>`2 = paid part time work`<br/>`3 = unemployed (looking for work)`<br/>`4 = student`<br/>`5 = housewife/ househusband`<br/>`6 = retired` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign UM_w1, echo=F}

opal.assign.table.tibble(o, 't1066_UM_w1','10-66.1066-UrbanMexico-Baseline',variables=list('PJOB'), missings = T)
t1066_UM_w1 <- opal.execute(o,'t1066_UM_w1')

```

```{r local UM_w1, echo=F}

vbl <- t1066_UM_w1$PJOB
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UM_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UM_w1, aes(x=factor(PJOB))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `nonpaid_work` from the study-specific variable it has to be recoded as follows:

* `PJOB == 1, 2, 3 or 6 into 996`
* `PJOB == 4 into 3`
* `PJOB == 5 into 1`
* `NA into 999`

**R script:**

```{r harmo UM_w1}

t1066_ds_UM_w1 <- tibble(id=t1066_UM_w1$id)
t1066_ds_UM_w1$nonpaid_work <- car::recode(t1066_UM_w1$PJOB, "5 = 1; 4=3; c(1,2,3,6) = 996; NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript UM_w1, echo=F}

vbl <- t1066_ds_UM_w1$nonpaid_work
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UM_w1, aes(x=factor(nonpaid_work))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation UM_w1, echo=F}

AfterH <- table(t1066_ds_UM_w1$nonpaid_work)
X <- table(t1066_UM_w1$PJOB,useNA = "ifany")
BeforeH <- c(X[5:4],sum(X[c(1,2,3,6)]),X[7])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->1","4->3","1,2,3,6->996","NA->999")
kable(C)

```



### Wave 2


#### Study-specific variable description

| **Name** | `f_PJOB`|
|-|-|
| **Label** | `occupation`|
| **Table name**  | `1066-UrbanMexico-Followup` |
| **Categories** | `1 = paid full time work`<br/>`2 = paid part time work`<br/>`3 = unemployed (looking for work)`<br/>`4 = student`<br/>`5 = housewife/ househusband`<br/>`6 = retired` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign UM_w2, echo=F}

opal.assign.table.tibble(o, 't1066_UM_w2','10-66.1066-UrbanMexico-Followup',variables=list('f_PJOB'), missings = T)
t1066_UM_w2 <- opal.execute(o,'t1066_UM_w2')

```

```{r local UM_w2, echo=F}

vbl <- t1066_UM_w2$f_PJOB
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_UM_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_UM_w2, aes(x=factor(f_PJOB))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `nonpaid_work` from the study-specific variable it has to be recoded as follows:

* `f_PJOB == 1, 2, 3 or 6 into 996`
* `f_PJOB == 4 into 3`
* `f_PJOB == 5 into 1`
* `NA into 999`

**R script:**

```{r harmo UM_w2}

t1066_ds_UM_w2 <- tibble(id=t1066_UM_w2$id)
t1066_ds_UM_w2$nonpaid_work <- car::recode(t1066_UM_w2$f_PJOB, "5 = 1; 4=3; c(1,2,3,6) = 996; NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript UM_w2, echo=F}

vbl <- t1066_ds_UM_w2$nonpaid_work
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_UM_w2, aes(x=factor(nonpaid_work))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")


```


#### Validation

```{r crosstabulation UM_w2, echo=F}

AfterH <- table(t1066_ds_UM_w2$nonpaid_work)
X <- table(t1066_UM_w2$f_PJOB,useNA = "ifany")
BeforeH <- c(X[4],sum(X[c(1,2,3,5)]),X[6])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->1","1,2,3,6->996","NA->999")
kable(C)

```



## Rural Mexico


### Wave 1


#### Study-specific variable description

| **Name** | `PJOB`|
|-|-|
| **Label** | `occupation`|
| **Table name**  | `1066-RuralMexico-Baseline` |
| **Categories** | `1 = paid full time work`<br/>`2 = paid part time work`<br/>`3 = unemployed (looking for work)`<br/>`4 = student`<br/>`5 = housewife/ househusband`<br/>`6 = retired` |
| **Missings** | `NA` |
| **Description** |  |


```{r assign RM_w1, echo=F}

opal.assign.table.tibble(o, 't1066_RM_w1','10-66.1066-RuralMexico-Baseline',variables=list('PJOB'), missings = T)
t1066_RM_w1 <- opal.execute(o,'t1066_RM_w1')

```

```{r local RM_w1, echo=F}

vbl <- t1066_RM_w1$PJOB
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RM_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RM_w1, aes(x=factor(PJOB))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `nonpaid_work` from the study-specific variable it has to be recoded as follows:

* `PJOB == 1, 2, 3 or 6 into 996`
* `PJOB == 4 into 3`
* `PJOB == 5 into 1`
* `NA into 999`

**R script:**

```{r harmo RM_w1}

t1066_ds_RM_w1 <- tibble(id=t1066_RM_w1$id)
t1066_ds_RM_w1$nonpaid_work <- car::recode(t1066_RM_w1$PJOB, "5 = 1; 4=3; c(1,2,3,6) = 996; NA = 999")
```


#### Statistics of the new harmonized variable

```{r descript RM_w1, echo=F}

vbl <- t1066_ds_RM_w1$nonpaid_work
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RM_w1, aes(x=factor(nonpaid_work))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation RM_w1, echo=F}

AfterH <- table(t1066_ds_RM_w1$nonpaid_work)
X <- table(t1066_RM_w1$PJOB,useNA = "ifany")
BeforeH <- c(X[5:4],sum(X[c(1,2,3,6)]),X[7])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->1","4->3","1,2,3,6->996","NA->999")
kable(C)

```



### Wave 2


#### Study-specific variable description

| **Name** | `f_PJOB`|
|-|-|
| **Label** | `occupation`|
| **Table name**  | `1066-RuralMexico-Followup` |
| **Categories** | `1 = paid full time work`<br/>`2 = paid part time work`<br/>`3 = unemployed (looking for work)`<br/>`4 = student`<br/>`5 = housewife/ househusband`<br/>`6 = retired` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign RM_w2, echo=F}

opal.assign.table.tibble(o, 't1066_RM_w2','10-66.1066-RuralMexico-Followup',variables=list('f_PJOB'), missings = T)
t1066_RM_w2 <- opal.execute(o,'t1066_RM_w2')

```

```{r local RM_w2, echo=F}

vbl <- t1066_RM_w2$f_PJOB
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_RM_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_RM_w2, aes(x=factor(f_PJOB))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `nonpaid_work` from the study-specific variable it has to be recoded as follows:

* `f_PJOB == 1, 2, 3 or 6 into 996`
* `f_PJOB == 4 into 3`
* `f_PJOB == 5 into 1`
* `NA into 999`

**R script:**

```{r harmo RM_w2}

t1066_ds_RM_w2 <- tibble(id=t1066_RM_w2$id)
t1066_ds_RM_w2$nonpaid_work <- car::recode(t1066_RM_w2$f_PJOB, "5 = 1; 4=3; c(1,2,3,6) = 996; NA = 999")


```


#### Statistics of the new harmonized variable

```{r descript RM_w2, echo=F}

vbl <- t1066_ds_RM_w2$nonpaid_work
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_RM_w2, aes(x=factor(nonpaid_work))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation RM_w2, echo=F}

AfterH <- table(t1066_ds_RM_w2$nonpaid_work)
X <- table(t1066_RM_w2$f_PJOB,useNA = "ifany")
BeforeH <- c(X[5:4],sum(X[c(1,2,3,6)]),X[7])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->1","4->3","1,2,3,6->996","NA->999")
kable(C)

```



## Puerto Rico


### Wave 1


#### Study-specific variable description

| **Name** | `PJOB`|
|-|-|
| **Label** | `occupation`|
| **Table name**  | `1066-PuertoRico-Baseline` |
| **Categories** | `1 = paid full time work`<br/>`2 = paid part time work`<br/>`3 = unemployed (looking for work)`<br/>`4 = student`<br/>`5 = housewife/ househusband`<br/>`6 = retired` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign PR_w1, echo=F}

opal.assign.table.tibble(o, 't1066_PR_w1','10-66.1066-PuertoRico-Baseline',variables=list('PJOB'), missings = T)
t1066_PR_w1 <- opal.execute(o,'t1066_PR_w1')

```

```{r local PR_w1, echo=F}

vbl <- t1066_PR_w1$PJOB
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_PR_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_PR_w1, aes(x=factor(PJOB))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `nonpaid_work` from the study-specific variable it has to be recoded as follows:

* `PJOB == 1, 2, 3 or 6 into 996`
* `PJOB == 4 into 3`
* `PJOB == 5 into 1`
* `NA into 999`

**R script:**

```{r harmo PR_w1}

t1066_ds_PR_w1 <- tibble(id=t1066_PR_w1$id)
t1066_ds_PR_w1$nonpaid_work <- car::recode(t1066_PR_w1$PJOB, "5 = 1; 4=3; c(1,2,3,6) = 996; NA = 999")
```


#### Statistics of the new harmonized variable

```{r descript PR_w1, echo=F}

vbl <- t1066_ds_PR_w1$nonpaid_work
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_PR_w1, aes(x=factor(nonpaid_work))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation PR_w1, echo=F}

AfterH <- table(t1066_ds_PR_w1$nonpaid_work)
X <- table(t1066_PR_w1$PJOB,useNA = "ifany")
BeforeH <- c(X[4],sum(X[c(1,2,3,5)]),X[6])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->1","1,2,3,6->996","NA->999")
kable(C)

```



### Wave 2


#### Study-specific variable description

| **Name** | `f_PJOB`|
|-|-|
| **Label** | `occupation`|
| **Table name**  | `1066-PuertoRico-Followup` |
| **Categories** | `1 = paid full time work`<br/>`2 = paid part time work`<br/>`3 = unemployed (looking for work)`<br/>`4 = student`<br/>`5 = housewife/ househusband`<br/>`6 = retired` |
| **Missings** | `NA` |
| **Description** |  |

```{r assign PR_w2, echo=F}

opal.assign.table.tibble(o, 't1066_PR_w2','10-66.1066-PuertoRico-Followup',variables=list('f_PJOB'), missings = T)
t1066_PR_w2 <- opal.execute(o,'t1066_PR_w2')

```

```{r local PR_w2, echo=F}

vbl <- t1066_PR_w2$f_PJOB
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(t1066_PR_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(t1066_PR_w2, aes(x=factor(f_PJOB))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `nonpaid_work` from the study-specific variable it has to be recoded as follows:

* `f_PJOB == 1, 2, 3 or 6 into 996`
* `f_PJOB == 4 into 3`
* `f_PJOB == 5 into 1`
* `NA into 999`

**R script:**

```{r harmo PR_w2}

t1066_ds_PR_w2 <- tibble(id=t1066_PR_w2$id)
t1066_ds_PR_w2$nonpaid_work <- car::recode(t1066_PR_w2$f_PJOB, "5 = 1; 4=3; c(1,2,3,6) = 996; NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript PR_w2, echo=F}

vbl <- t1066_ds_PR_w2$nonpaid_work
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(t1066_ds_PR_w2, aes(x=factor(nonpaid_work))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation PR_w2, echo=F}

AfterH <- table(t1066_ds_PR_w2$nonpaid_work)
X <- table(t1066_PR_w2$f_PJOB,useNA = "ifany")
BeforeH <- c(X[5:4],sum(X[c(1,2,3,6)]),X[7])
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("5->1","4->3","1,2,3,6->996","NA->999")
kable(C)

```





## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable:






```{r summ}

lb.hds <- list(cuba_w1 = t1066_ds_cuba_w1, india_w1 = t1066_ds_india_w1, UCh_w1 = t1066_ds_UCh_w1, RCh_w1 = t1066_ds_RCh_w1, DR_w1 = t1066_ds_DR_w1, Ven_w1 = t1066_ds_Ven_w1, UP_w1 = t1066_ds_UP_w1, RP_w1 = t1066_ds_RP_w1, UM_w1 = t1066_ds_UM_w1, RM_w1 = t1066_ds_RM_w1, PR_w1 = t1066_ds_PR_w1)

lf.hds <- list(cuba_w2 = t1066_ds_cuba_w2, UCh_w2 = t1066_ds_UCh_w2, RCh_w2 = t1066_ds_RCh_w2, DR_w2 = t1066_ds_DR_w2, Ven_w2 = t1066_ds_Ven_w2, UP_w2 = t1066_ds_UP_w2, RP_w2 = t1066_ds_RP_w2, UM_w2 = t1066_ds_UM_w2, RM_w2 = t1066_ds_RM_w2, PR_w2 = t1066_ds_PR_w2)

#l.hds <- list(cuba_w1 = t1066_ds_cuba_w1, cuba_w2 = t1066_ds_cuba_w2, india_w1 = t1066_ds_india_w1, india_w2 = t1066_ds_india_w2, UCh_w1 = t1066_ds_UCh_w1, UCh_w2 = t1066_ds_UCh_w2, RCh_w1 = t1066_ds_RCh_w1, RCh_w2 = t1066_ds_RCh_w2, DR_w1 = t1066_ds_DR_w1, DR_w2 = t1066_ds_DR_w2, Ven_w1 = t1066_ds_Ven_w1, Ven_w2 = t1066_ds_Ven_w2, UP_w1 = t1066_ds_UP_w1, UP_w2 = t1066_ds_UP_w2, RP_w1 = t1066_ds_RP_w1, RP_w2 = t1066_ds_RP_w2, UM_w1 = t1066_ds_UM_w1, UM_w2 = t1066_ds_UM_w2, RM_w1 = t1066_ds_RM_w1, RM_w2 = t1066_ds_RM_w2, PR_w1 = t1066_ds_PR_w1, PR_w2 = t1066_ds_PR_w2)

for(name in names(lb.hds)) {
  aux_object <- lb.hds[[name]]
  label(lb.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  lb.hds[[name]][[2]] <- labelled(lb.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:3])
  m_name <- paste0("t1066_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

for(name in names(lf.hds)) {
  aux_object <- lf.hds[[name]]
  label(lf.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  lf.hds[[name]][[2]] <- labelled(lf.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:3])
  m_name <- paste0("t1066_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

tb.hds <- frq(lb.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(lb.hds)){
  tb.hds[2+i] <- frq(lb.hds[[i]][2])[[1]][,4] 
}
tb.hds[14,] <- c("n", "sample size", 
             length(lb.hds[[1]][[2]]), length(lb.hds[[2]][[2]]) , length(lb.hds[[3]][[2]]), length(lb.hds[[4]][[2]]), length(lb.hds[[5]][[2]]), length(lb.hds[[6]][[2]]), length(lb.hds[[7]][[2]]), length(lb.hds[[8]][[2]]), length(lb.hds[[9]][[2]]), length(lb.hds[[10]][[2]]), length(lb.hds[[11]][[2]])
             )
names(tb.hds)<-c("val", "label", "cuba_w1", "india_w1", "UCh_w1", "RCh_w1","DR_w1","Ven_w1","UP_w1","RP_w1","UM_w1","RM_w1","PR_w1")
kable(tb.hds)

tf.hds <- frq(lf.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(lf.hds)){
  tf.hds[2+i] <- frq(lf.hds[[i]][2])[[1]][,4] 
}
tf.hds[14,] <- c("n", "sample size", 
             length(lf.hds[[1]][[2]]), length(lf.hds[[2]][[2]]) , length(lf.hds[[3]][[2]]), length(lf.hds[[4]][[2]]), length(lf.hds[[5]][[2]]), length(lf.hds[[6]][[2]]), length(lf.hds[[7]][[2]]), length(lf.hds[[8]][[2]]), length(lf.hds[[9]][[2]]), length(lf.hds[[10]][[2]])
             )
names(tf.hds)<-c("val", "label", "cuba_w2", "UCh_w2", "RCh_w2","DR_w2","Ven_w2","UP_w2","RP_w2","UM_w2","RM_w2","PR_w2")
kable(tf.hds)



```


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(lb.hds)){
  nonpaid_work <- lb.hds[[index]]
  save(nonpaid_work, file = paste0(datafolder,names(lb.hds)[index],"/nonpaid_work.RData"))
}

for(index in seq_along(lf.hds)){
  nonpaid_work <- lf.hds[[index]]
  save(nonpaid_work, file = paste0(datafolder,names(lf.hds)[index],"/nonpaid_work.RData"))
}


```
<!-- ########################################################## --> 

# Quality estimation



<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





