---
title: "Ever smoked"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/ever_smokedDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/ever_smokedDS.R')
```



# Data process


## Spain

### Wave 1 

#### Study-specific variable description

| **Name** | `w1tobacco` |
|-|-|
| **Label** | `Baseline tobacco consumption` |
| **Table name** | `ENRICA_spss_wave1` |
| **Categories:**| `0 = never` <br/> `1 = ex-smoker` <br/> `2 = smoker` |
| **Missings:**| |
| **Description** |  |

   
```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w1','ENRICA.ENRICA_spss_wave1', variables=list('w1tobacco'), missings = TRUE)
ENRICA_w1 <- opal.execute(o,'ENRICA_w1')
```

```{r local w1, echo=F}
vbl <- ENRICA_w1$w1tobacco
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ENRICA_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w1, aes(x=factor(w1tobacco))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `ever_smoked` from the study-specific variable it has to be recoded as follows:

* `2 into 1`

**R script:**

```{r harmo w1}
ENRICA_ds_w1 <- tibble(id=ENRICA_w1$id)
ENRICA_ds_w1$ever_smoked <- car::recode(ENRICA_w1$w1tobacco, "2 = 1 ")
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vbl <- ENRICA_ds_w1$ever_smoked
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ENRICA_ds_w1, aes(x=factor(ever_smoked))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w1, echo=F}
AfterH <- table(ENRICA_ds_w1$ever_smoked)
X<-table(ENRICA_w1$w1tobacco)
BeforeH <- c(X[1],sum(X[2:3]))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1,2->1") 
kable(C)
```




### Wave 2

#### Study-specific variable description

| **Name** | `w2tobacco` |
|-|-|
| **Label** | `tobacco consumption` |
| **Table name** | `ENRICA_spss_wave2` |
| **Categories:**| `0 = never` <br/> `1 = ex-smoker` <br/> `2 = smoker` |
| **Missings:**| `NA` |
| **Description** |  |

   
```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w2','ENRICA.ENRICA_spss_wave2', variables=list('w2tobacco'), missings = TRUE)
ENRICA_w2 <- opal.execute(o,'ENRICA_w2')
```

```{r local w2, echo=F}
vbl <- ENRICA_w2$w2tobacco
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ENRICA_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w2, aes(x=factor(w2tobacco))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `ever_smoked` from the study-specific variable it has to be recoded as follows:

* `2 into 1`
* `NA into 999`

**R script:**

```{r harmo w2}
ENRICA_ds_w2 <- tibble(id=ENRICA_w2$id)
ENRICA_ds_w2$ever_smoked <- car::recode(ENRICA_w2$w2tobacco, "2 = 1;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vbl <- ENRICA_ds_w2$ever_smoked
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ENRICA_ds_w2, aes(x=factor(ever_smoked))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w2, echo=F}
AfterH <- table(ENRICA_ds_w2$ever_smoked)
X<-table(ENRICA_w2$w2tobacco)
BeforeH <- c(X[1],sum(X[2:3]),sum(is.na(ENRICA_w2$w2tobacco)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1,2->1","NA->999") 
kable(C)
```




### Wave 3

#### Study-specific variable description

| **Name** | `w3tobacco` |
|-|-|
| **Label** | `tobacco consumption` |
| **Table name** | `ENRICA_spss_wave3` |
| **Categories:**| `0 = never` <br/> `1 = ex-smoker` <br/> `2 = smoker` |
| **Missings:**| `NA` |
| **Description** |  |

   
```{r assign w3, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w3','ENRICA.ENRICA_spss_wave3', variables=list('w3tobacco'), missings = TRUE)
ENRICA_w3 <- opal.execute(o,'ENRICA_w3')
```

```{r local w3, echo=F}
vbl <- ENRICA_w3$w3tobacco
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ENRICA_w3)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w3, aes(x=factor(w3tobacco))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")
```

#### Harmonisation algorithm

To compute `ever_smoked` from the study-specific variable it has to be recoded as follows:

* `2 into 1`
* `NA into 999`

**R script:**

```{r harmo w3}
ENRICA_ds_w3 <- tibble(id=ENRICA_w3$id)
ENRICA_ds_w3$ever_smoked <- car::recode(ENRICA_w3$w3tobacco, "2 = 1;NA = 999 ")
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}
vbl <- ENRICA_ds_w3$ever_smoked
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ENRICA_ds_w3, aes(x=factor(ever_smoked))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

#### Validation
```{r crosstabulation w3, echo=F}
AfterH <- table(ENRICA_ds_w3$ever_smoked)
X<-table(ENRICA_w3$w3tobacco)
BeforeH <- c(X[1],sum(X[2:3]),sum(is.na(ENRICA_w3$w3tobacco)))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("0->0","1,2->1","NA->999") 
kable(C)
```






```{r final, echo=F}

l.hds <- list(w1 = ENRICA_ds_w1, w2 = ENRICA_ds_w2, w3 = ENRICA_ds_w3)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  m_name <- paste0("ENRICA_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

```

## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.


```{r summ}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",names(l.hds))
kable(t.hds)

dbb <- get(paste0("ENRICA_m_ds_",names(l.hds)[1]))[,c("id","ever_smoked")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("ENRICA_m_ds_",names(l.hds)[ind]))[,c("id","ever_smoked")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", names(l.hds))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb)

```


# Quality estimation
[Comments on the quality of the new harmonised variable.]


<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  ever_smoked <- l.hds[[index]]
  save(ever_smoked, file = paste0(datafolder,names(l.hds)[index],"/ever_smoked.RData"))
}

```
<!-- ########################################################## --> 

<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
