---
title: "Number of cigarettes"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/n_cigarettesDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/n_cigarettesDS.R')
```


# Data process


## Spain

### Wave 1 

#### Study-specific variable description

| **Name** | `w1cigarettes_wk` |
|-|-|
| **Label** | `Number of cigarettes smoked per week` |
| **Table name** | `ENRICA_spss_wave1` |
| **Categories:**| `continuous` |
| **Missings:**| `NA` |
| **Description** |  |

   
```{r assign w1, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w1','ENRICA.ENRICA_spss_wave1', variables=list('w1cigarettes_wk'), missings = TRUE)
ENRICA_w1 <- opal.execute(o,'ENRICA_w1')
```

```{r local w1, echo=F}
vbl <- ENRICA_w1$w1cigarettes_wk
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "Number of cigarettes") 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(ENRICA_w1, aes(w1cigarettes_wk)) + geom_histogram(stat="count", fill="steelblue") + xlab("Number of cigarettes") + ylab("Frequency") + xlim(0,430)
```

#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo w1}
ENRICA_ds_w1 <- tibble(id=ENRICA_w1$id)
ENRICA_ds_w1$n_cigarettes <- car::recode(ENRICA_w1$w1cigarettes_wk, "NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript w1, echo=F}
vbl <- ENRICA_ds_w1$n_cigarettes
kable(Continuous_summary(var = vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ENRICA_ds_w1, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(0,430) 
```

#### Validation
```{r crosstabulation w1, echo=F}
```




### Wave 2

#### Study-specific variable description

| **Name** | `w2cigarettes_wk` |
|-|-|
| **Label** | `Number of cigarettes smoked per week` |
| **Table name** | `ENRICA_spss_wave2` |
| **Categories:**| `continuous` |
| **Missings:**| `NA` |
| **Description** |  |

   
```{r assign w2, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w2','ENRICA.ENRICA_spss_wave2', variables=list('w2cigarettes_wk'), missings = TRUE)
ENRICA_w2 <- opal.execute(o,'ENRICA_w2')
```

```{r local w2, echo=F}
vbl <- ENRICA_w2$w2cigarettes_wk
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "Number of cigarettes") 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(ENRICA_w2, aes(w2cigarettes_wk)) + geom_histogram(stat="count", fill="steelblue") + xlab("Number of cigarettes") + ylab("Frequency") + xlim(0,290)
```

#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo w2}
ENRICA_ds_w2 <- tibble(id=ENRICA_w2$id)
ENRICA_ds_w2$n_cigarettes <- car::recode(ENRICA_w2$w2cigarettes_wk, "NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript w2, echo=F}
vbl <- ENRICA_ds_w2$n_cigarettes
kable(Continuous_summary(var = vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ENRICA_ds_w2, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(0,290) 
```

#### Validation
```{r crosstabulation w2, echo=F}
```





### Wave 3

#### Study-specific variable description

| **Name** | `w3cigarettes_wk` |
|-|-|
| **Label** | `Number of cigarettes smoked per week` |
| **Table name** | `ENRICA_spss_wave3` |
| **Categories:**| `continuous` |
| **Missings:**| `NA` |
| **Description** |  |

   
```{r assign w3, echo=F}
opal.assign.table.tibble(o, 'ENRICA_w3','ENRICA.ENRICA_spss_wave3', variables=list('w3cigarettes_wk'), missings = TRUE)
ENRICA_w3 <- opal.execute(o,'ENRICA_w3')
```

```{r local w3, echo=F}
vbl <- ENRICA_w3$w3cigarettes_wk
kable(Continuous_summary(vbl, missing_values = NA)[3], caption = "Number of cigarettes") 
pander(Continuous_summary(vbl, missing_values = NA)$summary, caption = "Summary")
ggplot(ENRICA_w3, aes(w3cigarettes_wk)) + geom_histogram(stat="count", fill="steelblue") + xlab("Number of cigarettes") + ylab("Frequency") + xlim(0,250)
```

#### Harmonisation algorithm

The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo w3}
ENRICA_ds_w3 <- tibble(id=ENRICA_w3$id)
ENRICA_ds_w3$n_cigarettes <- car::recode(ENRICA_w3$w3cigarettes_wk, "NA = 999")
```

#### Statistical description of the new harmonised variable
```{r descript w3, echo=F}
vbl <- ENRICA_ds_w3$n_cigarettes
kable(Continuous_summary(var = vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(ENRICA_ds_w3, aes(n_cigarettes)) + geom_histogram(stat="count", fill="steelblue") + xlab(ds_label) + ylab("Frequency") + xlim(0,250) 
```

#### Validation
```{r crosstabulation w3, echo=F}
```








# Quality estimation
[Comments on the quality of the new harmonised variable.]

<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.hds <- list(w1 = ENRICA_ds_w1, w2 = ENRICA_ds_w2, w3 = ENRICA_ds_w3)


for(index in seq_along(l.hds)){
  label(l.hds[[index]][[2]]) <- ds_label
  n_cigarettes <- l.hds[[index]]
  save(n_cigarettes, file = paste0(datafolder,names(l.hds)[index],"/n_cigarettes.RData"))
}

```
<!-- ########################################################## --> 


<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
