---
title: "Alcohol drinking"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/alcoholDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/alcoholDS.R')
```



# Data process



## Spain


### Wave 1


#### Study-specific variable description

| **Name** | `w1alcohol` |
|-|-|
| **Label** | `Baseline alcohol consumption`  |
| **Table name**  | `ENRICA_spss_wave1`|
| **Categories** | `0 = never drinker`<br/>`1 = former drinker`<br/>`2 = moderate drinker`<br/>`3 = excessive drinker` |
| **Description** |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'ENRICA_w1','ENRICA.ENRICA_spss_wave1',variables=list('w1alcohol'), missings = T)
ENRICA_w1 <- opal.execute(o,'ENRICA_w1')
ENRICA_w1$w1alcohol <- as.numeric(ENRICA_w1$w1alcohol)

```

```{r local w1, echo=F}

vbl <- ENRICA_w1$w1alcohol
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ENRICA_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w1, aes(x=factor(w1alcohol))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable it has to be recoded as follows:

* `w1alcohol == 0,1 into 0`
* `w1alcohol == 2,3 into 1`
* `NA into 999`

To compute `freq_oh` from the study-specific variable it has to be recoded as follows:

* `w1alcohol == 0 into 0`
* `w1alcohol == 1 into 1`
* `w1alcohol == 2,3 into 2`
* `NA into 999`

To compute `past_oh` from the study-specific variable it has to be recoded as follows:

* `w1alcohol == 0,2,3 into 0`
* `w1alcohol == 1 into 1`
* `NA into 999`


**R script:**

```{r harmo w1}

# Categorical variable harmonization
ENRICA_ds_w1 <- tibble(id=ENRICA_w1$id)
ENRICA_ds_w1$current_oh <- car::recode(ENRICA_w1$w1alcohol,"c(0,1) = 0; c(2,3) = 1; NA = 999")
ENRICA_ds_w1$freq_oh <- car::recode(ENRICA_w1$w1alcohol,"c(2,3) = 2; NA = 999")
ENRICA_ds_w1$past_oh <- car::recode(ENRICA_w1$w1alcohol,"c(2,3) = 0; NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- ENRICA_ds_w1$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ENRICA_ds_w1, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- ENRICA_ds_w1$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ENRICA_ds_w1, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

vbl <- ENRICA_ds_w1$past_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_past)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ENRICA_ds_w1, aes(x=factor(past_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_past) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}

```



### Wave 2

#### Study-specific variable description


| **Name** | `w2alcohol` |
|-|-|
| **Label** |  `Drinking Patterns`  |
| **Table name**  | `ENRICA_spss_wave2`|
| **Categories** | `0 = Non-drinkers`<br/>`1 = Ex-Drinkers`<br/>`2 = Moderate Drinkers`<br/>`3 = Heavy Drinkers` |
| **Description** |  |

```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'ENRICA_w2','ENRICA.ENRICA_spss_wave2',variables=list('w2alcohol'), missings = T)
ENRICA_w2 <- opal.execute(o,'ENRICA_w2')
ENRICA_w2$w2alcohol <- as.numeric(ENRICA_w2$w2alcohol)

```

```{r local w2, echo=F}

vbl <- ENRICA_w2$w2alcohol
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(ENRICA_w2)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(ENRICA_w2, aes(x=factor(w2alcohol))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `current_oh` from the study-specific variable it has to be recoded as follows:

* `w2alcohol == 0,1 into 0`
* `w2alcohol == 2,3 into 1`
* `NA into 999`

To compute `freq_oh` from the study-specific variable it has to be recoded as follows:

* `w2alcohol == 0 into 0`
* `w2alcohol == 1 into 1`
* `w2alcohol == 2,3 into 2`
* `NA into 999`

To compute `past_oh` from the study-specific variable it has to be recoded as follows:

* `w2alcohol == 0,2,3 into 0`
* `w2alcohol == 1 into 1`
* `NA into 999`

**R script:**

```{r harmo w2}

ENRICA_ds_w2 <- tibble(id=ENRICA_w2$id)
ENRICA_ds_w2$current_oh <- car::recode(ENRICA_w2$w2alcohol,"c(2,3) = 1; c(0,1) = 0; NA = 999")
ENRICA_ds_w2$freq_oh <- car::recode(ENRICA_w2$w2alcohol,"c(2,3) = 2; NA = 999")
ENRICA_ds_w2$past_oh <- car::recode(ENRICA_w2$w2alcohol,"c(2,3) = 0; NA = 999")

```


#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- ENRICA_ds_w2$current_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_curr)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ENRICA_ds_w2, aes(x=factor(current_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_curr) + ylab("Frequency")

vbl <- ENRICA_ds_w2$freq_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_freq)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ENRICA_ds_w2, aes(x=factor(freq_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_freq) + ylab("Frequency")

vbl <- ENRICA_ds_w2$past_oh
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label_past)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(ENRICA_ds_w2, aes(x=factor(past_oh))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label_past) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w2, echo=F}

```



### Wave 3

Not found.




```{r final, echo=F}

l.hds <- list(w1 = ENRICA_ds_w1, w2 = ENRICA_ds_w2)

for(name in names(l.hds)) {
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label_curr # Text value assigned at the DS description, at the top
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  label(l.hds[[name]][[3]]) <- label(aux_object[[3]]) <- ds_label_freq # Text value assigned at the DS description, at the top
  l.hds[[name]][[3]] <- labelled(l.hds[[name]][[3]], labels = freq_label)
  label(l.hds[[name]][[4]]) <- label(aux_object[[4]]) <- ds_label_past # Text value assigned at the DS description, at the top
  l.hds[[name]][[4]] <- labelled(l.hds[[name]][[4]], labels = cat_label)
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  aux_object[[3]] <- car::recode(aux_object[[3]], "miss_values_vector=NA")
  aux_object[[3]] <- labelled(aux_object[[3]], labels = freq_label[1:3])
  aux_object[[4]] <- car::recode(aux_object[[4]], "miss_values_vector=NA")
  aux_object[[4]] <- labelled(aux_object[[4]], labels = cat_label[1:2])
  m_name <- paste0("ENRICA_m_ds_",name)
  assign(m_name, aux_object)
  rm(aux_object)
}

```




## Summary of descriptive statistics of the harmonised variable `current_oh` accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.

**R script:**

```{r summ current}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",names(l.hds))
kable(t.hds)


dbb <- get(paste0("ENRICA_m_ds_",names(l.hds)[1]))[,c("id","current_oh")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("ENRICA_m_ds_",names(l.hds)[ind]))[,c("id","current_oh")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", names(l.hds))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb)

```




## Summary of descriptive statistics of the harmonised variable `freq_oh` accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.

**R script:**

```{r summ freq}

t.hds <- frq(l.hds[[1]][3])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][3])[[1]][,4] 
}
t.hds[14,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",names(l.hds))
kable(t.hds)


dbb <- get(paste0("ENRICA_m_ds_",names(l.hds)[1]))[,c("id","freq_oh")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("ENRICA_m_ds_",names(l.hds)[ind]))[,c("id","freq_oh")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", names(l.hds))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb)

```




## Summary of descriptive statistics of the harmonised variable `past_oh` accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.

**R script:**

```{r summ past}

t.hds <- frq(l.hds[[1]][4])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][4])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
             )
names(t.hds)<-c("val", "label",names(l.hds))
kable(t.hds)


dbb <- get(paste0("ENRICA_m_ds_",names(l.hds)[1]))[,c("id","past_oh")]
for(ind in 2:length(l.hds)){
  dbb <- merge(dbb, get(paste0("ENRICA_m_ds_",names(l.hds)[ind]))[,c("id","past_oh")], by = "id", suffixes = c("", paste0(".",names(l.hds)[ind])), all = T)
}
names(dbb) <- c("id", names(l.hds))

v.dbb <- dbb[,2]
for(ind in 2:length(l.hds)){
  v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
}
f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
kable(f.dbb)

```






# Quality estimation




<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}


for(index in seq_along(l.hds)){
  alcohol <- l.hds[[index]]
  save(alcohol, file = paste0(datafolder,names(l.hds)[index],"/alcohol.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





