---
title: "Year of death"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:



* Short name: `ydeath`
* Variable label: `year of death`
* Variable description: `Year of death`
* Domain: `Age of death (Life expectancy)`
* Value type: `continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

# Data process

### Wave 1 

There is no variable.





### Wave 2 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w02Xa010y`
* Label: `The time of the respondent's death (unit : yyyy)`
* Type of variable: `countinous`
* Missings: 
    + `-9 = Don't know`


```{r assign2, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w2_ydeath','KLOSA.w02_exit_e_spss_modifAlbert',  variables=list('w02Xa010y'), missings = TRUE)
```

```{r local2, echo=F}
KLOSA_w2_ydeath <- opal.execute(o,'KLOSA_w2_ydeath')
Categorical_summary(var = KLOSA_w2_ydeath$w02Xa010y, missing_values = c(-9))
ggplot(KLOSA_w2_ydeath, aes(factor(w02Xa010y))) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is the same of the study-specific variable but the missings values have to be recoded as follows:

* `-9 "Don't know" into 998`
* `NA into 999`

**R script:**

```{r harmo2}
KLOSA_ds_w2 <- tibble(id=KLOSA_w2_ydeath$id)
KLOSA_ds_w2$ydeath <- car::recode(KLOSA_w2_ydeath$w02Xa010y, "NA=999; -9=998")
KLOSA_ds_w2$ydeath <- labelled(KLOSA_ds_w2$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
Categorical_summary(var = KLOSA_ds_w2$ydeath, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w2, aes(factor(ydeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
BeforeH <- table(KLOSA_w2_ydeath$w02Xa010y, useNA = "ifany")
BeforeH <- BeforeH[c(2:length(BeforeH),1)]
AfterH <- table(KLOSA_ds_w2$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "-9->998")
kable(C)
```

```{r importOPAL2, echo=F}
val_labels(KLOSA_ds_w2) <- NULL
#opal.assign.data(o, 'KLOSA_ds_w2', KLOSA_ds_w2)
#opal.symbol_import(o,'KLOSA_ds_w2', project='_Athlos_Harm_Dataset')
ydeath <- KLOSA_ds_w2
save(ydeath, file = "../RData/w2/ydeath.RData")
rm(ydeath)

KLOSA_m_ds_w2 <- KLOSA_ds_w2
KLOSA_m_ds_w2$ydeath <- car::recode(KLOSA_m_ds_w2$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w2', KLOSA_m_ds_w2)
#opal.symbol_import(o,'KLOSA_m_ds_w2', project='_Athlos_Harm_Dataset')
```






### Wave 3 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w03Xa010y`
* Label: `The time of the respondent's death (unit : yyyy)`
* Type of variable: `countinous`
* Missings: 
    + `-9 = Don't know`

```{r assign3, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w3_ydeath','KLOSA.w03_exit_v12e_modifLaia',variables=list('w03Xa010y'), missings = TRUE)
KLOSA_w3_ydeath <- opal.execute(o,'KLOSA_w3_ydeath')
# The id's in the third wave add a '.0' at the end of the id's at the previous waves. We correct this. Note that gregexpr("\\.0",ids) == nchar(ids)-1
KLOSA_w3_ydeath$id <- substr(KLOSA_w3_ydeath$id,1,nchar(KLOSA_w3_ydeath$id)-2)

```

```{r local3, echo=F}
Categorical_summary(var = KLOSA_w3_ydeath$w03Xa010y, missing_values = c(-9))
ggplot(KLOSA_w3_ydeath, aes(factor(w03Xa010y))) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is the same of the study-specific variable but the missings values have to be recoded as follows:

* `-9 "Don't know" into 998`
* `NA into 999`


**R script:**

```{r harmo3}
KLOSA_ds_w3 <- tibble(id=KLOSA_w3_ydeath$id)
KLOSA_ds_w3$ydeath <- car::recode(KLOSA_w3_ydeath$w03Xa010y, "NA=999; -9=998")
KLOSA_ds_w3$ydeath <- labelled(KLOSA_ds_w3$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}
Categorical_summary(var = KLOSA_ds_w3$ydeath, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w3, aes(factor(ydeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=F}
BeforeH <- table(KLOSA_w3_ydeath$w03Xa010y, useNA = "ifany")
AfterH <- table(KLOSA_ds_w3$ydeath)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```


```{r importOPAL3, echo=F}
val_labels(KLOSA_ds_w3) <- NULL
#opal.assign.data(o, 'KLOSA_ds_w3', KLOSA_ds_w3)
#opal.symbol_import(o,'KLOSA_ds_w3', project='_Athlos_Harm_Dataset')
ydeath <- KLOSA_ds_w3
save(ydeath, file = "../RData/w3/ydeath.RData")
rm(ydeath)

KLOSA_m_ds_w3 <- KLOSA_ds_w3
KLOSA_m_ds_w3$ydeath <- car::recode(KLOSA_m_ds_w3$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w3', KLOSA_m_ds_w3)
#opal.symbol_import(o,'KLOSA_m_ds_w3', project='_Athlos_Harm_Dataset')
```







### Wave 4 

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `w04Xa010y`
* Label: `The time of the respondent's death (unit : yyyy)`
* Type of variable: `countinous`
* Missings: 
    + `-9 = Don't know`

```{r assign4, echo=F}
opal.assign.table.tibble(o, 'KLOSA_w4_ydeath','KLOSA.w04_exit_v12e',
                         variables=list('w04Xa010y'), missings = TRUE)
```

```{r local4, echo=F}
KLOSA_w4_ydeath <- opal.execute(o,'KLOSA_w4_ydeath')
Categorical_summary(var = KLOSA_w4_ydeath$w04Xa010y, missing_values = c(-9))
ggplot(KLOSA_w4_ydeath, aes(factor(w04Xa010y))) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonize variable is the same of the study-specific variable but the missings values have to be recoded as follows:

* `-9 "Don't know" into 998`
* `NA into 999`

**R script:**

```{r harmo4}
KLOSA_ds_w4 <- tibble(id=KLOSA_w4_ydeath$id)
KLOSA_ds_w4$ydeath <- car::recode(KLOSA_w4_ydeath$w04Xa010y, "NA=999; -9=998")
KLOSA_ds_w4$ydeath <- labelled(KLOSA_ds_w4$ydeath, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript4, echo=F}
Categorical_summary(var = KLOSA_ds_w4$ydeath, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(KLOSA_ds_w4, aes(factor(ydeath))) + geom_histogram(stat="count", fill="steelblue") + xlab("Year of death") + ylab("Frequency") 
```

#### Validation
```{r crosstabulation4, echo=F}
BeforeH <- table(KLOSA_w4_ydeath$w04Xa010y, useNA = "ifany")
BeforeH <- BeforeH[c(2:length(BeforeH),1)]
AfterH <- table(KLOSA_ds_w4$ydeath)
AfterH <- AfterH[c(2:length(AfterH),1)]
C <- rbind(BeforeH,AfterH)
colnames(C) <- c(names(AfterH)[1:(length(AfterH)-1)], "-9->998")
kable(C)
```



```{r importOPAL4, echo=F}
val_labels(KLOSA_ds_w4) <- NULL
#opal.assign.data(o, 'KLOSA_ds_w4', KLOSA_ds_w4)
#opal.symbol_import(o,'KLOSA_ds_w4', project='_Athlos_Harm_Dataset')
ydeath <- KLOSA_ds_w4
save(ydeath, file = "../RData/w4/ydeath.RData")
rm(ydeath)

KLOSA_m_ds_w4 <- KLOSA_ds_w4
KLOSA_m_ds_w4$ydeath <- car::recode(KLOSA_m_ds_w4$ydeath, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'KLOSA_m_ds_w4', KLOSA_m_ds_w4)
#opal.symbol_import(o,'KLOSA_m_ds_w4', project='_Athlos_Harm_Dataset')
```


```{r closeRsession, echo=FALSE}
opal.logout(o)
```

# Quality estimation

No comments