---
title: "Respondent"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_laia.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/respondentDS.Rmd'}
```

```{r global, echo=F}
source('../../_DS_Rmd/respondentDS.R')
```

<!-- ########################################################## --> 

# Data process

## aksst 

### Wave 1 

#### Study-specific variable description

```{r assign_aksst1, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_aksst_w1','JSTAR_datasets_restricted.jstar_2007_5cities',
                         variables=list('a_000_0'), missings = TRUE)
JSTAR_aksst_w1 <- opal.execute(o,'JSTAR_aksst_w1')
```


#### Harmonisation algorithm
All the interviewed individuals are considered as participants. 

**R script:**

```{r harmo_aksst1, echo=TRUE}
JSTAR_aksst_ds_w1 <- tibble(id=JSTAR_aksst_w1$id)
JSTAR_aksst_ds_w1$respondent <- 0
JSTAR_aksst_ds_w1$respondent <- labelled(JSTAR_aksst_ds_w1$respondent, labels = cat_label)
label(JSTAR_aksst_ds_w1$respondent) <- ds_label
```

#### Statistical description of the new harmonised variable
```{r descript_aksst1, echo=FALSE}
vari <- JSTAR_aksst_ds_w1$respondent
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_aksst_ds_w1, aes(x=factor(respondent))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```



```{r importOPAL_aksst1, echo=FALSE}
#opal.assign.data(o, 'JSTAR_aksst_ds_w1', JSTAR_aksst_ds_w1)
#opal.symbol_import(o,'JSTAR_aksst_ds_w1', project='_Athlos_Harm_Dataset')
respondent <- JSTAR_aksst_ds_w1
save(respondent, file = "../RData/aksst_w1/respondent.RData")
rm(respondent)
```





### Wave 2 

#### Study-specific variable description

```{r assign_aksst2, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_aksst_w2','JSTAR_datasets_restricted.jstar_2009_5cities',
                         variables=list('a_001_a'), missings = TRUE)
JSTAR_aksst_w2 <- opal.execute(o,'JSTAR_aksst_w2')
```

#### Harmonisation algorithm
All the interviewed individuals are considered as participants. 

**R script:**

```{r harmo_aksst2, echo=TRUE}
JSTAR_aksst_ds_w2 <- tibble(id=JSTAR_aksst_w2$id)
JSTAR_aksst_ds_w2$respondent <- 0
JSTAR_aksst_ds_w2$respondent <- labelled(JSTAR_aksst_ds_w2$respondent, labels = cat_label)
label(JSTAR_aksst_ds_w2$respondent) <- ds_label
```

#### Statistical description of the new harmonised variable
```{r descript_aksst2, echo=FALSE}
vari <- JSTAR_aksst_ds_w2$respondent
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_aksst_ds_w2, aes(x=factor(respondent))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL_aksst2, echo=FALSE}
#opal.assign.data(o, 'JSTAR_aksst_ds_w2', JSTAR_aksst_ds_w2)
#opal.symbol_import(o,'JSTAR_aksst_ds_w2', project='_Athlos_Harm_Dataset')
respondent <- JSTAR_aksst_ds_w2
save(respondent, file = "../RData/aksst_w2/respondent.RData")
rm(respondent)
```







### Wave 3 

#### Study-specific variable description

```{r assign_aksst3, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_aksst_w3','JSTAR_datasets_restricted.jstar_2011_5cities',
                         variables=list('a'), missings = TRUE)
JSTAR_aksst_w3 <- opal.execute(o,'JSTAR_aksst_w3')
```


#### Harmonisation algorithm
All the interviewed individuals are considered as participants. 

**R script:**

```{r harmo_aksst3, echo=TRUE}
JSTAR_aksst_ds_w3 <- tibble(id=JSTAR_aksst_w3$id)
JSTAR_aksst_ds_w3$respondent <- 0
JSTAR_aksst_ds_w3$respondent <- labelled(JSTAR_aksst_ds_w3$respondent, labels = cat_label)
label(JSTAR_aksst_ds_w3$respondent) <- ds_label
```

#### Statistical description of the new harmonised variable
```{r descript_aksst3, echo=FALSE}
vari <- JSTAR_aksst_ds_w3$respondent
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_aksst_ds_w3, aes(x=factor(respondent))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL_aksst3, echo=FALSE}
#opal.assign.data(o, 'JSTAR_aksst_ds_w3', JSTAR_aksst_ds_w3)
#opal.symbol_import(o,'JSTAR_aksst_ds_w3', project='_Athlos_Harm_Dataset')
respondent <- JSTAR_aksst_ds_w3
save(respondent, file = "../RData/aksst_w3/respondent.RData")
rm(respondent)
```





## tn 

### Wave 1 

#### Study-specific variable description

```{r assign_tn1, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_tn_w1','JSTAR_datasets_restricted.jstar_2009_2cities',
                         variables=list('a_000_0'), missings = TRUE)
JSTAR_tn_w1 <- opal.execute(o,'JSTAR_tn_w1')
```


#### Harmonisation algorithm
All the interviewed individuals are considered as participants. 

**R script:**

```{r harmo_tn1, echo=TRUE}
JSTAR_tn_ds_w1 <- tibble(id=JSTAR_tn_w1$id)
JSTAR_tn_ds_w1$respondent <- 0
JSTAR_tn_ds_w1$respondent <- labelled(JSTAR_tn_ds_w1$respondent, labels = cat_label)
label(JSTAR_tn_ds_w1$respondent) <- ds_label
```

#### Statistical description of the new harmonised variable
```{r descript_tn1, echo=FALSE}
vari <- JSTAR_tn_ds_w1$respondent
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_tn_ds_w1, aes(x=factor(respondent))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


```{r importOPAL_tn1, echo=FALSE}
#opal.assign.data(o, 'JSTAR_tn_ds_w1', JSTAR_tn_ds_w1)
#opal.symbol_import(o,'JSTAR_tn_ds_w1', project='_Athlos_Harm_Dataset')
respondent <- JSTAR_tn_ds_w1
save(respondent, file = "../RData/tn_w1/respondent.RData")
rm(respondent)
```







### Wave 2 

#### Study-specific variable description

```{r assign_tn2, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_tn_w2','JSTAR_datasets_restricted.jstar_2011_2cities',
                         variables=list('a'), missings = TRUE)
JSTAR_tn_w2 <- opal.execute(o,'JSTAR_tn_w2')
```


#### Harmonisation algorithm
All the interviewed individuals are considered as participants. 

**R script:**

```{r harmo_tn2, echo=TRUE}
JSTAR_tn_ds_w2 <- tibble(id=JSTAR_tn_w2$id)
JSTAR_tn_ds_w2$respondent <- 0
JSTAR_tn_ds_w2$respondent <- labelled(JSTAR_tn_ds_w2$respondent, labels = cat_label)
label(JSTAR_tn_ds_w2$respondent) <- ds_label
```

#### Statistical description of the new harmonised variable
```{r descript_tn2, echo=FALSE}
vari <- JSTAR_tn_ds_w2$respondent
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_tn_ds_w2, aes(x=factor(respondent))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```



```{r importOPAL_tn2, echo=FALSE}
#opal.assign.data(o, 'JSTAR_tn_ds_w2', JSTAR_tn_ds_w2)
#opal.symbol_import(o,'JSTAR_tn_ds_w2', project='_Athlos_Harm_Dataset')
respondent <- JSTAR_tn_ds_w2
save(respondent, file = "../RData/tn_w2/respondent.RData")
rm(respondent)
```





## cth 

### Wave 1 

#### Study-specific variable description

```{r assign_cth1, echo=FALSE}
opal.assign.table.tibble(o, 'JSTAR_cth_w1','JSTAR_datasets_restricted.jstar_2011_3cities',
                         variables=list('a_000_0'), missings = TRUE)
JSTAR_cth_w1 <- opal.execute(o,'JSTAR_cth_w1')
```


#### Harmonisation algorithm
All the interviewed individuals are considered as participants. 

**R script:**

```{r harmo_cth1, echo=TRUE}
JSTAR_cth_ds_w1 <- tibble(id=JSTAR_cth_w1$id)
JSTAR_cth_ds_w1$respondent <- 0
JSTAR_cth_ds_w1$respondent <- labelled(JSTAR_cth_ds_w1$respondent, labels = cat_label)
label(JSTAR_cth_ds_w1$respondent) <- ds_label
```

#### Statistical description of the new harmonised variable
```{r descript_cth1, echo=FALSE}
vari <- JSTAR_cth_ds_w1$respondent
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(JSTAR_cth_ds_w1, aes(x=factor(respondent))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```



```{r importOPAL_cth1, echo=FALSE}
#opal.assign.data(o, 'JSTAR_cth_ds_w1', JSTAR_cth_ds_w1)
#opal.symbol_import(o,'JSTAR_cth_ds_w1', project='_Athlos_Harm_Dataset')
respondent <- JSTAR_cth_ds_w1
save(respondent, file = "../RData/cth_w1/respondent.RData")
rm(respondent)
```

# Quality estimation
No comments.


```{r closeRsession, echo=FALSE} 
opal.logout(o)
```