---
title: "Respiratory diseases"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```
<!-- ########################################################## --> 




# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `h_respiratory`
* Variable label: `Chronic respiratory diseases such respiratory, CPD, COPD, bronchitis, emphysema`
* Variable description: `The participant has one or more of the following respiratory diseases: respiratory, chronic bronchitis, emphysema, chronic pulmonary disease, chronic obstructive pulmonary disease`
* Domain: `Diseases`
* Value type: `categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | no respiratory disease
1        | yes, respiratory disease

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 
<!-- # Global variables -->
```{r global, include=FALSE, echo=F}
miss_values_vector <- c(991, 992, 993, 994, 995, 996, 997, 998, 999)
ds_label <- "Chronic respiratory diseases such respiratory, CPD, COPD, bronchitis, emphysema"
cat_label <- c("No" = 0, "Yes" = 1, "Missing" = 999, "Do not know" = 998, "Refuse" = 997, "Not applicable" = 996, "Does not answer" = 995, "Not attempt not done" = 994, "Disable to measure" = 993, "Impute" = 992, "CAPI interviewer error" = 991)
datafolder <- "../RData/"
#sing_idlist <- c()
```
<!-- ########################################################## --> 



# Data process




## South Africa


### Wave 1


#### Study-specific variable description

| **Name** | `q4033` |`q4025`|
|-|-|-|
| **Label** | `q4033: asthma`|`q4025: chronic lung disease`|
| **Table name**  | `southAfricaINDdata`| `southAfricaINDdata`|
| **Categories** | `1 = yes`<br/>`2 = no` | `1 = yes`<br/>`2 = no` |
| **Missings** | `NA`<br/>`8 = don't know` | `NA`<br/>`8 = don't know` |
| **Description** |  |  |

```{r assign SA_w1, echo=F}

opal.assign.table.tibble(o, 'SAGE_SA_w1','SAGE.southAfricaINDdata',variables=list('q4033','q4025'), missings = T)
SAGE_SA_w1 <- opal.execute(o,'SAGE_SA_w1')

```

```{r local SA_w1, echo=F}

vbl <- SAGE_SA_w1$q4033
kable(Categorical_summary(vbl, missing_values = c(8))[3], caption = names(SAGE_SA_w1)[2])
kable(Categorical_summary(vbl, missing_values = c(8))[1], caption = "Category")
ggplot(SAGE_SA_w1, aes(x=factor(q4033))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_SA_w1$q4025
kable(Categorical_summary(vbl, missing_values = c(8))[3], caption = names(SAGE_SA_w1)[3])
kable(Categorical_summary(vbl, missing_values = c(8))[1], caption = "Category")
ggplot(SAGE_SA_w1, aes(x=factor(q4025))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_respiratory` from the study-specific variable it has to be recoded as follows:

* `all 2 into 0`
* `some 1 into 1`
* `8 into 998`
* `NA into 999`

**R script:**

```{r harmo SA_w1}

# Categorical variable harmonization
SAGE_ds_SA_w1 <- tibble(id=SAGE_SA_w1$id)
SAGE_ds_SA_w1$h_respiratory <- rep(999,length(SAGE_SA_w1$id))
SAGE_ds_SA_w1$h_respiratory[which(SAGE_SA_w1$q4033 == 2 & SAGE_SA_w1$q4025 == 2)] <- 0
SAGE_ds_SA_w1$h_respiratory[which(SAGE_SA_w1$q4033 == 1 | SAGE_SA_w1$q4025 == 1)] <- 1
SAGE_ds_SA_w1$h_respiratory[which((SAGE_SA_w1$q4033 == 8 & (SAGE_SA_w1$q4025 != 1 | is.na(SAGE_SA_w1$q4025))) | (SAGE_SA_w1$q4025 == 8 & (SAGE_SA_w1$q4033 != 1 | is.na(SAGE_SA_w1$q4033))))] <- 998

```


#### Statistics of the new harmonized variable

```{r descript SA_w1, echo=F}

vbl <- SAGE_ds_SA_w1$h_respiratory
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_SA_w1, aes(x=factor(h_respiratory))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation SA_w1, echo=F}

AfterH <- table(SAGE_ds_SA_w1$h_respiratory)
X <- c(
  sum(SAGE_SA_w1$q4033 == 2 & SAGE_SA_w1$q4025 == 2,na.rm=T),
  sum(SAGE_SA_w1$q4033 == 1 | SAGE_SA_w1$q4025 == 1,na.rm=T),
  sum((SAGE_SA_w1$q4033 == 8 & (SAGE_SA_w1$q4025 != 1 | is.na(SAGE_SA_w1$q4025))) | (SAGE_SA_w1$q4025 == 8 & (SAGE_SA_w1$q4033 != 1 | is.na(SAGE_SA_w1$q4033))),na.rm=T)
)
BeforeH <- c(X[1:3],length(SAGE_SA_w1$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 2->0","some 1->1","8->998","NA->999")
kable(C)

```




## Ghana


### Wave 1


#### Study-specific variable description

| **Name** | `q4033` |`q4025`|
|-|-|-|
| **Label** | `q4033: asthma`|`q4025: chronic lung disease`|
| **Table name**  | `ghanaINDData`| `ghanaINDData`|
| **Categories** | `1 = yes`<br/>`2 = no` | `1 = yes`<br/>`2 = no` |
| **Missings** | `NA`<br/>`8 = don't know` | `NA`<br/>`8 = don't know` |
| **Description** |  |  |

```{r assign ghana_w1, echo=F}

opal.assign.table.tibble(o, 'SAGE_ghana_w1','SAGE.ghanaINDData',variables=list('q4033','q4025'), missings = T)
SAGE_ghana_w1 <- opal.execute(o,'SAGE_ghana_w1')

```

```{r local ghana_w1, echo=F}

vbl <- SAGE_ghana_w1$q4033
kable(Categorical_summary(vbl, missing_values = c(8))[3], caption = names(SAGE_ghana_w1)[2])
kable(Categorical_summary(vbl, missing_values = c(8))[1], caption = "Category")
ggplot(SAGE_ghana_w1, aes(x=factor(q4033))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_ghana_w1$q4025
kable(Categorical_summary(vbl, missing_values = c(8))[3], caption = names(SAGE_ghana_w1)[3])
kable(Categorical_summary(vbl, missing_values = c(8))[1], caption = "Category")
ggplot(SAGE_ghana_w1, aes(x=factor(q4025))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_respiratory` from the study-specific variable it has to be recoded as follows:

* `all 2 into 0`
* `some 1 into 1`
* `8 into 998`
* `NA into 999`

**R script:**

```{r harmo ghana_w1}

# Categorical variable harmonization
SAGE_ds_ghana_w1 <- tibble(id=SAGE_ghana_w1$id)
SAGE_ds_ghana_w1$h_respiratory <- rep(999,length(SAGE_ghana_w1$id))
SAGE_ds_ghana_w1$h_respiratory[which(SAGE_ghana_w1$q4033 == 2 & SAGE_ghana_w1$q4025 == 2)] <- 0
SAGE_ds_ghana_w1$h_respiratory[which(SAGE_ghana_w1$q4033 == 1 | SAGE_ghana_w1$q4025 == 1)] <- 1
SAGE_ds_ghana_w1$h_respiratory[which((SAGE_ghana_w1$q4033 == 8 & (SAGE_ghana_w1$q4025 != 1 | is.na(SAGE_ghana_w1$q4025))) | (SAGE_ghana_w1$q4025 == 8 & (SAGE_ghana_w1$q4033 != 1 | is.na(SAGE_ghana_w1$q4033))))] <- 998
```


#### Statistics of the new harmonized variable

```{r descript ghana_w1, echo=F}

vbl <- SAGE_ds_ghana_w1$h_respiratory
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_ghana_w1, aes(x=factor(h_respiratory))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation ghana_w1, echo=F}

AfterH <- table(SAGE_ds_ghana_w1$h_respiratory)
X <- c(
  sum(SAGE_ghana_w1$q4033 == 2 & SAGE_ghana_w1$q4025 == 2,na.rm=T),
  sum(SAGE_ghana_w1$q4033 == 1 | SAGE_ghana_w1$q4025 == 1,na.rm=T),
  sum((SAGE_ghana_w1$q4033 == 8 & (SAGE_ghana_w1$q4025 != 1 | is.na(SAGE_ghana_w1$q4025))) | (SAGE_ghana_w1$q4025 == 8 & (SAGE_ghana_w1$q4033 != 1 | is.na(SAGE_ghana_w1$q4033))),na.rm=T)
)
BeforeH <- c(X[1:3],length(SAGE_ghana_w1$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 2->0","some 1->1","8->998","NA->999")
kable(C)

```





## China


### Wave 1


#### Study-specific variable description

| **Name** | `q4033` |`q4025`|
|-|-|-|
| **Label** | `q4033: asthma`|`q4025: chronic lung disease`|
| **Table name**  | `chinaINDData`| `chinaINDData`|
| **Categories** | `1 = yes`<br/>`2 = no` | `1 = yes`<br/>`2 = no` |
| **Missings** | `NA`| `NA` |
| **Description** |  |  |

```{r assign china_w1, echo=F}

opal.assign.table.tibble(o, 'SAGE_china_w1','SAGE.chinaINDData',variables=list('q4033','q4025'), missings = T)
SAGE_china_w1 <- opal.execute(o,'SAGE_china_w1')

```

```{r local china_w1, echo=F}

vbl <- SAGE_china_w1$q4033
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(SAGE_china_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(SAGE_china_w1, aes(x=factor(q4033))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_china_w1$q4025
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(SAGE_china_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(SAGE_china_w1, aes(x=factor(q4025))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_respiratory` from the study-specific variable it has to be recoded as follows:

* `all 2 into 0`
* `some 1 into 1`
* `NA into 999`

**R script:**

```{r harmo china_w1}

# Categorical variable harmonization
SAGE_ds_china_w1 <- tibble(id=SAGE_china_w1$id)
SAGE_ds_china_w1$h_respiratory <- rep(999,length(SAGE_china_w1$id))
SAGE_ds_china_w1$h_respiratory[which(SAGE_china_w1$q4033 == 2 & SAGE_china_w1$q4025 == 2)] <- 0
SAGE_ds_china_w1$h_respiratory[which(SAGE_china_w1$q4033 == 1 | SAGE_china_w1$q4025 == 1)] <- 1
```


#### Statistics of the new harmonized variable

```{r descript china_w1, echo=F}

vbl <- SAGE_ds_china_w1$h_respiratory
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_china_w1, aes(x=factor(h_respiratory))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation china_w1, echo=F}

AfterH <- table(SAGE_ds_china_w1$h_respiratory)
X <- c(
  sum(SAGE_china_w1$q4033 == 2 & SAGE_china_w1$q4025 == 2,na.rm=T),
  sum(SAGE_china_w1$q4033 == 1 | SAGE_china_w1$q4025 == 1,na.rm=T)
)
BeforeH <- c(X[1:2],length(SAGE_china_w1$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 2->0","some 1->1","NA->999")
kable(C)

```




## India


### Wave 1


#### Study-specific variable description

| **Name** | `q4033` |`q4025`|
|-|-|-|
| **Label** | `Q4033: Asthma`|`Q4025: Chronic lung disease`|
| **Table name**  | `indiaINDData`|`indiaINDData`|
| **Categories** | `1 = yes`<br/>`2 = no` | `1 = yes`<br/>`2 = no` |
| **Missings** | `NA`<br/>`9 = Not applicable` | `NA`<br/>`9 = Not applicable` |
| **Description** |  |  |

```{r assign india_w1, echo=F}

opal.assign.table.tibble(o, 'SAGE_india_w1','SAGE.indiaINDData',variables=list('q4033','q4025'), missings = T)
SAGE_india_w1 <- opal.execute(o,'SAGE_india_w1')

```

```{r local india_w1, echo=F}

vbl <- SAGE_india_w1$q4033
kable(Categorical_summary(vbl, missing_values = c(9))[3], caption = names(SAGE_india_w1)[2])
kable(Categorical_summary(vbl, missing_values = c(9))[1], caption = "Category")
ggplot(SAGE_india_w1, aes(x=factor(q4033))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_india_w1$q4025
kable(Categorical_summary(vbl, missing_values = c(9))[3], caption = names(SAGE_india_w1)[3])
kable(Categorical_summary(vbl, missing_values = c(9))[1], caption = "Category")
ggplot(SAGE_india_w1, aes(x=factor(q4025))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_respiratory` from the study-specific variable it has to be recoded as follows:

* `all 2 into 0`
* `some 1 into 1`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo india_w1}

# Categorical variable harmonization
SAGE_ds_india_w1 <- tibble(id=SAGE_india_w1$id)
SAGE_ds_india_w1$h_respiratory <- rep(999,length(SAGE_india_w1$id))
SAGE_ds_india_w1$h_respiratory[which(SAGE_india_w1$q4033 == 2 & SAGE_india_w1$q4025 == 2)] <- 0
SAGE_ds_india_w1$h_respiratory[which(SAGE_india_w1$q4033 == 1 | SAGE_india_w1$q4025 == 1)] <- 1
SAGE_ds_india_w1$h_respiratory[which((SAGE_india_w1$q4033 == 9 & (SAGE_india_w1$q4025 != 1 | is.na(SAGE_india_w1$q4025))) | (SAGE_india_w1$q4025 == 9 & (SAGE_india_w1$q4033 != 1 | is.na(SAGE_india_w1$q4033))))] <- 996
```


#### Statistics of the new harmonized variable

```{r descript india_w1, echo=F}

vbl <- SAGE_ds_india_w1$h_respiratory
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_india_w1, aes(x=factor(h_respiratory))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation india_w1, echo=F}

AfterH <- table(SAGE_ds_india_w1$h_respiratory)
X <- c(
  sum(SAGE_india_w1$q4033 == 2 & SAGE_india_w1$q4025 == 2,na.rm=T),
  sum(SAGE_india_w1$q4033 == 1 | SAGE_india_w1$q4025 == 1,na.rm=T),
  sum((SAGE_india_w1$q4033 == 9 & (SAGE_india_w1$q4025 != 1 | is.na(SAGE_india_w1$q4025))) | (SAGE_india_w1$q4025 == 9 & (SAGE_india_w1$q4033 != 1 | is.na(SAGE_india_w1$q4033))),na.rm=T)
)
BeforeH <- c(X[1:3],length(SAGE_india_w1$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 2->0","some 1->1","9->996","NA->999")
kable(C)

```





## Russian Federation


### Wave 1


#### Study-specific variable description

| **Name** | `q4033` |`q4025`|
|-|-|-|
| **Label** | `q4033: asthma`|`q4025: chronic lung disease`|
| **Table name**  | `russiaINDdata`| `russiaINDdata`|
| **Categories** | `1 = yes`<br/>`2 = no` | `1 = yes`<br/>`2 = no` |
| **Missings** | `NA`<br/>`8 = don't know`<br/>`9 = Not applicable` | `NA`<br/>`8 = don't know`<br/>`9 = Not applicable` |
| **Description** |  |  |

```{r assign russia_w1, echo=F}

opal.assign.table.tibble(o, 'SAGE_russia_w1','SAGE.russiaINDdata',variables=list('q4033','q4025'), missings = T)
SAGE_russia_w1 <- opal.execute(o,'SAGE_russia_w1')

```

```{r local russia_w1, echo=F}

vbl <- SAGE_russia_w1$q4033
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = names(SAGE_russia_w1)[2])
kable(Categorical_summary(vbl, missing_values = c(9,8))[1], caption = "Category")
ggplot(SAGE_russia_w1, aes(x=factor(q4033))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_russia_w1$q4025
kable(Categorical_summary(vbl, missing_values = c(8,9))[3], caption = names(SAGE_russia_w1)[3])
kable(Categorical_summary(vbl, missing_values = c(9,8))[1], caption = "Category")
ggplot(SAGE_russia_w1, aes(x=factor(q4025))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_respiratory` from the study-specific variable it has to be recoded as follows:

* `all 2 into 0`
* `some 1 into 1`
* `8 into 998`
* `9 into 996`
* `NA into 999`

**R script:**

```{r harmo russia_w1}

# Categorical variable harmonization
SAGE_ds_russia_w1 <- tibble(id=SAGE_russia_w1$id)
SAGE_ds_russia_w1$h_respiratory <- rep(999,length(SAGE_russia_w1$id))
SAGE_ds_russia_w1$h_respiratory[which(SAGE_russia_w1$q4033 == 2 & SAGE_russia_w1$q4025 == 2)] <- 0
SAGE_ds_russia_w1$h_respiratory[which(SAGE_russia_w1$q4033 == 1 | SAGE_russia_w1$q4025 == 1)] <- 1
SAGE_ds_russia_w1$h_respiratory[which((SAGE_russia_w1$q4033 == 8 & (SAGE_russia_w1$q4025 != 1 | is.na(SAGE_russia_w1$q4025))) | (SAGE_russia_w1$q4025 == 8 & (SAGE_russia_w1$q4033 != 1 | is.na(SAGE_russia_w1$q4033))))] <- 998
SAGE_ds_russia_w1$h_respiratory[which((SAGE_russia_w1$q4033 == 9 & (SAGE_russia_w1$q4025 != 1 | is.na(SAGE_russia_w1$q4025))) | (SAGE_russia_w1$q4025 == 9 & (SAGE_russia_w1$q4033 != 1 | is.na(SAGE_russia_w1$q4033))))] <- 996
```


#### Statistics of the new harmonized variable

```{r descript russia_w1, echo=F}

vbl <- SAGE_ds_russia_w1$h_respiratory
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_russia_w1, aes(x=factor(h_respiratory))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation russia_w1, echo=F}

AfterH <- table(SAGE_ds_russia_w1$h_respiratory)
X <- c(
  sum(SAGE_russia_w1$q4033 == 2 & SAGE_russia_w1$q4025 == 2,na.rm=T),
  sum(SAGE_russia_w1$q4033 == 1 | SAGE_russia_w1$q4025 == 1,na.rm=T),
  sum((SAGE_russia_w1$q4033 == 9 & (SAGE_russia_w1$q4025 != 1 | is.na(SAGE_russia_w1$q4025))) | (SAGE_russia_w1$q4025 == 9 & (SAGE_russia_w1$q4033 != 1 | is.na(SAGE_russia_w1$q4033))),na.rm=T),
  sum((SAGE_russia_w1$q4033 == 8 & (SAGE_russia_w1$q4025 != 1 | is.na(SAGE_russia_w1$q4025))) | (SAGE_russia_w1$q4025 == 8 & (SAGE_russia_w1$q4033 != 1 | is.na(SAGE_russia_w1$q4033))),na.rm=T)
)
BeforeH <- c(X[1:4],length(SAGE_russia_w1$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 2->0","some 1->1","9->996","8->998","NA->999")
kable(C)

```




## Mexico


### Wave 1


#### Study-specific variable description

| **Name** | `q4033` |`q4025`|
|-|-|-|
| **Label** | `q4033: asthma`|`q4025: chronic lung disease`|
| **Table name**  | `mexicoINDdata`| `mexicoINDdata`|
| **Categories** | `1 = yes`<br/>`2 = no` | `1 = yes`<br/>`2 = no` |
| **Missings** | `NA` | `NA` |
| **Description** |  |  |


```{r assign mexico_w1, echo=F}

opal.assign.table.tibble(o, 'SAGE_mexico_w1','SAGE.mexicoINDdata',variables=list('q4033','q4025'), missings = T)
SAGE_mexico_w1 <- opal.execute(o,'SAGE_mexico_w1')

```

```{r local mexico_w1, echo=F}

vbl <- SAGE_mexico_w1$q4033
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(SAGE_mexico_w1)[2])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(SAGE_mexico_w1, aes(x=factor(q4033))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SAGE_mexico_w1$q4025
kable(Categorical_summary(vbl, missing_values = NA)[2], caption = names(SAGE_mexico_w1)[3])
kable(Categorical_summary(vbl, missing_values = NA)[1], caption = "Category")
ggplot(SAGE_mexico_w1, aes(x=factor(q4025))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute `h_respiratory` from the study-specific variable it has to be recoded as follows:

* `all 2 into 0`
* `some 1 into 1`
* `NA into 999`

**R script:**

```{r harmo mexico_w1}

# Categorical variable harmonization
SAGE_ds_mexico_w1 <- tibble(id=SAGE_mexico_w1$id)
SAGE_ds_mexico_w1$h_respiratory <- rep(999,length(SAGE_mexico_w1$id))
SAGE_ds_mexico_w1$h_respiratory[which(SAGE_mexico_w1$q4033 == 2 & SAGE_mexico_w1$q4025 == 2)] <- 0
SAGE_ds_mexico_w1$h_respiratory[which(SAGE_mexico_w1$q4033 == 1 | SAGE_mexico_w1$q4025 == 1)] <- 1
```


#### Statistics of the new harmonized variable

```{r descript mexico_w1, echo=F}

vbl <- SAGE_ds_mexico_w1$h_respiratory
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SAGE_ds_mexico_w1, aes(x=factor(h_respiratory))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation mexico_w1, echo=F}

AfterH <- table(SAGE_ds_mexico_w1$h_respiratory)
X <- c(
  sum(SAGE_mexico_w1$q4033 == 2 & SAGE_mexico_w1$q4025 == 2,na.rm=T),
  sum(SAGE_mexico_w1$q4033 == 1 | SAGE_mexico_w1$q4025 == 1,na.rm=T)
)
BeforeH <- c(X[1:2],length(SAGE_mexico_w1$id)-sum(X))
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("all 2->0","some 1->1","NA->999")
kable(C)

```





## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable:


**R script:**

```{r summ}

l.hds <- list(SA_w1 = SAGE_ds_SA_w1 , ghana_w1 = SAGE_ds_ghana_w1, china_w1 = SAGE_ds_china_w1, india_w1=SAGE_ds_india_w1, russia_w1=SAGE_ds_russia_w1, mexico_w1=SAGE_ds_mexico_w1)

for(name in names(l.hds)) {
  m_name <- paste0("SAGE_m_ds_",name)
  aux_object <- l.hds[[name]]
  label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label # Text value assigned at the DS description, at the top
  aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
  l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
  aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  assign(m_name, aux_object)
  rm(aux_object)
}

t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
for (i in seq_along(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", 
             length(l.hds[[1]][[2]]), length(l.hds[[2]][[2]]) , length(l.hds[[3]][[2]]), length(l.hds[[4]][[2]]), length(l.hds[[5]][[2]]), length(l.hds[[6]][[2]]) )
names(t.hds)<-c("val", "label", "South_Africa_w1", "Ghana_W1", "China_W1", "India_W1", "Russia_W1", "Mexico_W1")
kable(t.hds)

```



# Quality estimation

Includes information about asthma and emphysema.

<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

for(index in seq_along(l.hds)){
  h_respiratory <- l.hds[[index]]
  save(h_respiratory, file = paste0(datafolder,names(l.hds)[index],"/h_respiratory.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





