---
title: "Obesity"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:

* Short name: `obesity`
* Variable label: `Precense of obesity based in Body Mass Index classification according to the WHO BMI classification (http://apps.who.int/bmi/index.jsp?introPage=intro_3.html): BMI value equal to or above 30Kg/m^2.`
* Variable description: `the BMI variable should be created by dividing weight and hiegh variables by means of the following equation= weight (kg)/height(m)^2. Then, the Obesity variable should be generated according to the WHO cutoff point for BMI classification.`
* Domain: `Physical measures`
* Value type: `Categorical`
* Category coding:

**Code** | **Category Label**
-------- | ------------------
0        | Not obese
1        | Obese

* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




<!-- ########################################################## --> 

# Data process




```{r, dataDirectory, echo=FALSE}
datafolder <- "../RData"
```



```{r lab, echo=FALSE}
ds_label <- "Precense of obesity based in Body Mass Index classification according to the WHO BMI classification (http://apps.who.int/bmi/index.jsp?introPage=intro_3.html): BMI value equal to or above 30Kg/m^2"
```


## England

### Wave 1

There is no variable.


### Wave 2

#### Study-specific variable description

The study-specific variables elected to be harmonised are:

* Name: `bmival`
* Label: `(D) Valid BMI - inc estimated>130kg`
* Type of variable: `countinous`
* Missings
    + `-1 = Not Applicable`


```{r assign2, echo=F}
opal.assign.table.tibble(o, 'ELSA_bmi','ELSA.wave_2_nurse_data_v2',
                         variables=list('bmival'), missings = TRUE)
ELSA_bmi <- opal.execute(o,'ELSA_bmi')
```

```{r local_aksst1, echo=F}
Continuous_summary(ELSA_bmi[[2]], missing_values = -1)
ggplot(filter(ELSA_bmi,!ELSA_bmi$bmival==-1), aes(bmival)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency") 
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `recode -1 "Not Applicable" into 996`
* `NA into 999`


**R script:**

```{r harmo1}
ELSA_ds_w2 <- tibble(id=ELSA_bmi$id)
ELSA_ds_w2$obesity <- car::recode(ELSA_bmi[[2]], "0:29.9999999=0; 30:900=1; -1=996; NA=999")
ELSA_ds_w2$obesity <- labelled(ELSA_ds_w2[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript_aksst1, echo=F}
Categorical_summary(var = ELSA_ds_w2[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w2, aes(x=factor(ELSA_ds_w2[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab1, echo=F}
BeforeH <- c(sum(na.omit(ELSA_bmi[[2]])<30 & na.omit(ELSA_bmi[[2]])>0),sum(na.omit(ELSA_bmi[[2]])>=30 & na.omit(ELSA_bmi[[2]])<=900), sum(na.omit(ELSA_bmi[[2]])==-1))
AfterH <- table(ELSA_ds_w2[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","-1->994") 
kable(C)
```


```{r read1, include=FALSE, echo=F}
rm(ELSA_bmi)
```


### Wave 3

There is no variable.


### Wave 4

#### Study-specific variable description

* Name: `bmival`
* Label: `(D) Valid BMI - inc estimated>130kg`
* Type of variable: `countinous`
* Missings
    + `-1 = Not Applicable`

```{r assign4, echo=F}
opal.assign.table.tibble(o, 'ELSA_bmi','ELSA.wave_4_nurse_data',
                         variables=list('bmival'), missings = TRUE)
ELSA_bmi <- opal.execute(o,'ELSA_bmi')
```

```{r local_4, echo=F}
Continuous_summary(ELSA_bmi[[2]], missing_values = -1)
ggplot(filter(ELSA_bmi,!ELSA_bmi$bmival==-1), aes(bmival)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `recode -1 "Not Applicable" into 996`
* `NA into 999`

```{r harmo4}
ELSA_ds_w4 <- tibble(id=ELSA_bmi$id)
ELSA_ds_w4$obesity <- car::recode(ELSA_bmi[[2]], "0:29.9999999=0; 30:900=1; -1=996; NA=999")
ELSA_ds_w4$obesity <- labelled(ELSA_ds_w4[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript4, echo=F}
Categorical_summary(var = ELSA_ds_w4[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w4, aes(x=factor(ELSA_ds_w4[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab4, echo=F}
BeforeH <- c(sum(na.omit(ELSA_bmi[[2]])<30 & na.omit(ELSA_bmi[[2]])>0),sum(na.omit(ELSA_bmi[[2]])>=30 & na.omit(ELSA_bmi[[2]])<=900), sum(na.omit(ELSA_bmi[[2]])==-1))
AfterH <- table(ELSA_ds_w4[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","-1->994") 
kable(C)
```


```{r read4, include=FALSE, echo=F}
rm(ELSA_bmi)
```



### Wave 5

There is no variable.


### Wave 6

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `BMIVAL`
* Label: `(D) Valid BMI - inc estimated>130kg`
* Type of variable: `countinous`
* Missings
    + `-1 = Not Applicable`

```{r assign6, echo=F}
opal.assign.table.tibble(o, 'ELSA_bmi','ELSA.wave_6_elsa_nurse_data_v2',
                         variables=list('BMIVAL'), missings = TRUE)
ELSA_bmi <- opal.execute(o,'ELSA_bmi')
```

```{r local_6, echo=F}
Continuous_summary(ELSA_bmi[[2]], missing_values = -1)
ggplot(filter(ELSA_bmi,!ELSA_bmi$BMIVAL==-1), aes(BMIVAL)) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("BMI") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `BMI<30 into 0` 
* `BMI>=30 into 1`
* `recode -1 "Not Applicable" into 996`
* `NA into 999`

```{r harmo6}
ELSA_ds_w6 <- tibble(id=ELSA_bmi$id)
ELSA_ds_w6$obesity <- car::recode(ELSA_bmi[[2]], "0:29.9999999=0; 30:900=1; -1=996; NA=999")
ELSA_ds_w6$obesity <- labelled(ELSA_ds_w6[[2]], labels = c("not obese"=0, "obese"=1,  "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistical description of the new harmonised variable
```{r descript6, echo=F}
Categorical_summary(var = ELSA_ds_w6[[2]], missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w6, aes(x=factor(ELSA_ds_w6[[2]]))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Obesity") + ylab("Frequency")
```

#### Validation
```{r crosstab6, echo=F}
BeforeH <- c(sum(na.omit(ELSA_bmi[[2]])<30 & na.omit(ELSA_bmi[[2]])>0),sum(na.omit(ELSA_bmi[[2]])>=30 & na.omit(ELSA_bmi[[2]])<=900), sum(na.omit(ELSA_bmi[[2]])==-1))
AfterH <- table(ELSA_ds_w6[[2]], useNA = "ifany")
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("<30->0",">=30->1","-1->994") 
kable(C)
```


```{r read6, include=FALSE, echo=F}
rm(ELSA_bmi)
```


### Wave 7

Not found.


<!--- ############################################### Import to OPAL ###########################################-->
```{r importOPAL, echo=FALSE, eval=FALSE}
ELSA_m_ds_w2 <- ELSA_ds_w2
ELSA_m_ds_w4 <- ELSA_ds_w4
ELSA_m_ds_w6 <- ELSA_ds_w6

l.hds <- list(ELSA_ds_w2 = ELSA_ds_w2 , ELSA_ds_w4 = ELSA_ds_w4, ELSA_ds_w6=ELSA_ds_w6)

m.hds <- list(ELSA_m_ds_w2 = ELSA_m_ds_w2 , ELSA_m_ds_w4 = ELSA_m_ds_w4, ELSA_m_ds_w6=ELSA_m_ds_w6)


for(i in 1:length(l.hds)) {
  label(l.hds[[i]][[2]]) <- label(m.hds[[i]][[2]]) <- ds_label # Text value assigned at the DS description, at the top.
    
  m.hds[[i]][[2]] <- car::recode(m.hds[[i]][[2]], "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
  m.hds[[i]][[2]] <- labelled(m.hds[[i]][[2]], labels = c("not obese"=0, "obese"=1, "Respond, died after this wave"=2, "Respond(proxy), died"=3, "No respond, alive"=4, "No respond, died this wave"=5, "No respond, died previous waves"=6, "No respond, dropped from sample"=7))

  nl <- names(l.hds[i])
  #opal.assign.data(o, nl , l.hds[[i]])
  #opal.symbol_import(o, nl , project='_Athlos_Harm_Dataset')  
  obesity <- l.hds[[i]]
  ml <- names(m.hds[i])
  #opal.assign.data(o, ml , m.hds[[i]]) 
  #opal.symbol_import(o, ml , project='_Athlos_Harm_Dataset')  

}




```


```{r save, echo=F}
l.hds <- list(ELSA_ds_w2, ELSA_ds_w4, ELSA_ds_w6)
for(i in 1:3)
{
  obesity <- l.hds[[i]]
  save(obesity, file = paste0(datafolder, "/",paste0("w",2*i),"/obesity.RData"))
}

```


## Descriptive statistics of the harmonised variable accross populations and waves

Percentages of categories in each harmonised variable by cohort and wave:

```{r summ}

# Table HRS
t.hds <- frq(l.hds[[2]][2])[[1]][,c(1,2)] 
for (i in 1:length(l.hds)){
  t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
}
t.hds[13,] <- c("n", "sample size", 
             length(l.hds[[1]][[2]]), length(l.hds[[2]][[2]]), length(l.hds[[3]][[2]]))
names(t.hds)<-c("val", "label", "Wave2", "Wave4", "Wave6")
kable(t.hds)
```

# Quality estimation
Once BMI has been calculated using weight (Kg) and Height (m^2),
Obesity was calculated by using the BMI cutoff>=30kg/m2 following the WHO 
classification. Finally, the resulting BMI variable was coded as follows: 
BMI>30kg/m2 =1 (obese); BMI<30kg/m2 =0 (not obese) to generate two categories.


<!--- #### Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```
