---
title: "Waist"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 



# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `Waist`
* Variable label: `Waist circumference of the participant`
* Variable description: `Anthropomeric measure for waist circumference should be measured in centimeters.`
* Domain: `Physical measures `
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing




<!-- ########################################################## --> 

# Data process






```{r, dataDirectory, echo=FALSE}
datafolder <- "../RData"
```

## England

### Wave 1 

There is no variable. 



### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `wstval`
* Label: `(D) Valid Mean Waist (cm)`
* Type of variable: `countinous`
* Missings
    + `-1 = Not Applicable`


```{r assign2, echo=F}
opal.assign.table.tibble(o, 'ELSA_w2_waist','ELSA.wave_2_nurse_data_v2',
                         variables=list('wstval'), missings = TRUE)
```

```{r local2, echo=F}
ELSA_w2_waist <- opal.execute(o,'ELSA_w2_waist')
Continuous_summary(var = ELSA_w2_waist$wstval, missing_values = c(-1))
ggplot(ELSA_w2_waist, aes(wstval)) + geom_histogram(stat="count", fill="steelblue") + xlab("Waist") + ylab("Frequency") + xlim(30,130)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `recode -1 "Not Applicable" into 996`
* `NA into 999`

**R script:**

```{r harmo2}
ELSA_ds_w2 <- tibble(id=ELSA_w2_waist$id)
ELSA_ds_w2$waist <- car::recode(ELSA_w2_waist$wstval, "NA=999; -1=996")
ELSA_ds_w2$waist <- labelled(ELSA_ds_w2$waist, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
Continuous_summary(var = ELSA_ds_w2$waist, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w2, aes(waist)) + geom_histogram(stat="count", fill="steelblue") + xlab("Waist") + ylab("Frequency") + xlim(35,165) 
```

#### Validation
```{r crosstabulation2, echo=F}
```

```{r importOPAL2, echo=F}
#val_labels(ELSA_ds_w2) <- NULL
#opal.assign.data(o, 'ELSA_ds_w2', ELSA_ds_w2)
#opal.symbol_import(o,'ELSA_ds_w2', project='_Athlos_Harm_Dataset')
```







### Wave 3

There is no variable.



### Wave 4

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `wstval`
* Label: `(D) Valid Mean Waist (cm)`
* Type of variable: `countinous`
* Missings
    + `-1 = Not Applicable`

```{r assign4, echo=F}
opal.assign.table.tibble(o, 'ELSA_w4_waist','ELSA.wave_4_nurse_data',
                         variables=list('wstval'), missings = TRUE)
```

```{r local4, echo=F}
ELSA_w4_waist <- opal.execute(o,'ELSA_w4_waist')
Continuous_summary(var = ELSA_w4_waist$wstval, missing_values = c(-1))
ggplot(ELSA_w4_waist, aes(wstval)) + geom_histogram(stat="count", fill="steelblue") + xlab("Waist") + ylab("Frequency") + xlim(30,130)
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `recode -1 "Not Applicable" into 996`
* `NA into 999`

**R script:**

```{r harmo4}
ELSA_ds_w4 <- tibble(id=ELSA_w4_waist$id)
ELSA_ds_w4$waist <- car::recode(ELSA_w4_waist$wstval, "NA=999; -1=996")
ELSA_ds_w4$waist <- labelled(ELSA_ds_w4$waist, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript4, echo=F}
Continuous_summary(var = ELSA_ds_w4$waist, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w4, aes(waist)) + geom_histogram(stat="count", fill="steelblue") + xlab("Waist") + ylab("Frequency") + xlim(35,165) 
```

#### Validation
```{r crosstabulation4, echo=F}
```


```{r importOPAL4, echo=F}
#val_labels(ELSA_ds_w4) <- NULL
#opal.assign.data(o, 'ELSA_ds_w4', ELSA_ds_w4)
#opal.symbol_import(o,'ELSA_ds_w4', project='_Athlos_Harm_Dataset')
```






### Wave 5

There is no varibale.


### Wave 6

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `WSTVAL`
* Label: `(D) Valid Mean Waist (cm)`
* Type of variable: `countinous`
* Missings
    + `-1 = Not Applicable`

```{r assign6, echo=F}
opal.assign.table.tibble(o, 'ELSA_w6_waist','ELSA.wave_6_elsa_nurse_data_v2',
                         variables=list('WSTVAL'), missings = TRUE)
```

```{r local6, echo=F}
ELSA_w6_waist <- opal.execute(o,'ELSA_w6_waist')
Continuous_summary(var = ELSA_w6_waist$WSTVAL, missing_values = c(-1))
ggplot(ELSA_w6_waist, aes(WSTVAL)) + geom_histogram(stat="count", fill="steelblue") + xlab("Waist") + ylab("Frequency") + xlim(30,130)
```

There are values 999.9 that are going to be considered as mistakes and will be recoded as 999 (missing).

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `recode -1 "Not Applicable" into 996`
* `NA into 999`

**R script:**

```{r harmo6}
ELSA_ds_w6 <- tibble(id=ELSA_w6_waist$id)
ELSA_ds_w6$waist <- car::recode(ELSA_w6_waist$WSTVAL, "NA=999; -1=996; 999.9=999")
ELSA_ds_w6$waist <- labelled(ELSA_ds_w6$waist, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript6, echo=F}
Continuous_summary(var = ELSA_ds_w6$waist, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w6, aes(waist)) + geom_histogram(stat="count", fill="steelblue") + xlab("Waist") + ylab("Frequency") + xlim(35,165) 
```

#### Validation
```{r crosstabulation6, echo=F}
```

```{r importOPAL6, echo=F}
#val_labels(ELSA_ds_w6) <- NULL
#opal.assign.data(o, 'ELSA_ds_w6', ELSA_ds_w6)
#opal.symbol_import(o,'ELSA_ds_w6', project='_Athlos_Harm_Dataset')
```


### Wave 7

Not found.


# Quality estimation




```{r save, echo=F}
s <- list(ELSA_ds_w2, ELSA_ds_w4, ELSA_ds_w6)
for(i in 1:3)
{
  waist <- s[[i]]
  save(waist, file = paste0(datafolder, "/",paste0("w",2*i),"/waist.RData"))
}

```



```{r closeRsession, echo=FALSE}
opal.logout(o)
```
