---
title: "Hip"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 

<!-- # Installation, loading packages -->
<!-- **R script:** -->

```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 


# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `hip`
* Variable label: `Hip circumference of the participant`
* Variable `Anthropomeric measure for hip circumference should be measured in centimeters.`
* Domain: `Physical measures `
* Value type: `Continuous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing



<!-- ########################################################## --> 

# Data process






```{r, dataDirectory, echo=FALSE}
datafolder <- "../RData"
```


## England

### Wave 1 

There is no variable. 






### Wave 2

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `hipval`
* Label: `(D) Valid Mean Hip (cm)`
* Type of variable: `countinous`
* Missings
    + `-1 = Not Applicable`


```{r assign2, echo=F}
opal.assign.table.tibble(o, 'ELSA_w2_hip','ELSA.wave_2_nurse_data_v2',
                         variables=list('hipval'), missings = TRUE)
```

```{r local2, echo=F}
ELSA_w2_hip <- opal.execute(o,'ELSA_w2_hip')
Continuous_summary(var = ELSA_w2_hip$hipval, missing_values = c(-1))
ggplot(filter(ELSA_w2_hip,!ELSA_w2_hip$hipval==-1), aes(hipval)) + geom_histogram(stat="count", fill="steelblue") + xlab("Hip") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `recode -1 "Not Applicable" into 996`
* `NA into 999`

**R script:**

```{r harmo2}
ELSA_ds_w2 <- tibble(id=ELSA_w2_hip$id)
ELSA_ds_w2$hip <- car::recode(ELSA_w2_hip$hipval, "NA=999; -1=996")
ELSA_ds_w2$hip <- labelled(ELSA_ds_w2$hip, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
Continuous_summary(var = ELSA_ds_w2$hip, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w2, aes(hip)) + geom_histogram(stat="count", fill="steelblue") + xlab("Hip") + ylab("Frequency") + xlim(35,165) 
```

#### Validation
```{r crosstabulation2, echo=F}
```

```{r importOPAL2, echo=F}
#val_labels(ELSA_ds_w2) <- NULL
#opal.assign.data(o, 'ELSA_ds_w2', ELSA_ds_w2)
#opal.symbol_import(o,'ELSA_ds_w2', project='_Athlos_Harm_Dataset')
```







### Wave 3

There is no variable.



### Wave 4

#### Study-specific variable description

The study-specific variable elected to be harmonised is:

* Name: `hipval`
* Label: `(D) Valid Mean Hip (cm)`
* Type of variable: `countinous`
* Missings
    + `-1 = Not Applicable`

```{r assign4, echo=F}
opal.assign.table.tibble(o, 'ELSA_w4_hip','ELSA.wave_4_nurse_data',
                         variables=list('hipval'), missings = TRUE)
```

```{r local4, echo=F}
ELSA_w4_hip <- opal.execute(o,'ELSA_w4_hip')
Continuous_summary(var = ELSA_w4_hip$hipval, missing_values = c(-1))
ggplot(filter(ELSA_w4_hip,!ELSA_w4_hip$hipval==-1), aes(hipval)) + geom_histogram(stat="count", fill="steelblue") + xlab("Hip") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same than the study-specific variable, but the missing values have to be recoded as follows:

* `recode -1 "Not Applicable" into 996`
* `NA into 999`

**R script:**

```{r harmo4}
ELSA_ds_w4 <- tibble(id=ELSA_w4_hip$id)
ELSA_ds_w4$hip <- car::recode(ELSA_w4_hip$hipval, "NA=999; -1=996")
ELSA_ds_w4$hip <- labelled(ELSA_ds_w4$hip, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996,  "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript4, echo=F}
Continuous_summary(var = ELSA_ds_w4$hip, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
ggplot(ELSA_ds_w4, aes(hip)) + geom_histogram(stat="count", fill="steelblue") + xlab("Hip") + ylab("Frequency") + xlim(35,165) 
```

#### Validation
```{r crosstabulation4, echo=F}
```

```{r importOPAL4, echo=F}
#val_labels(ELSA_ds_w4) <- NULL
#opal.assign.data(o, 'ELSA_ds_w4', ELSA_ds_w4)
#opal.symbol_import(o,'ELSA_ds_w4', project='_Athlos_Harm_Dataset')
```






### Wave 5

There is no varibale.


### Wave 6

There is no variable. 


### Wave 7

There is no variable. 



#### Quality estimation
No coments.





```{r save, echo=F}
s <- list(ELSA_ds_w2, ELSA_ds_w4)
for(i in 1:2)
{
  hip <- s[[i]]
  save(hip, file = paste0(datafolder, "/",paste0("w",2*i),"/hip.RData"))
}

```


```{r closeRsession, echo=FALSE}
opal.logout(o)
```
