---
title: "Month of interview"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```

# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `mintw`
* Variable label: `Month of interview`
* Variable description: `Month of interview`
* Domain: `Other administrative variables`
* Value type: `Categorical`
* Categories: 

**Code** | **Category Label**
----| ------------------
1   | january
2   | february
3   | march 
4   | april 
5   | may
6   | june
7   | july
8   | august
9   | september
10  | october
11  | november
12  | december



* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Month of interview"
```

# Data process

## SHARE

### Wave 1 

#### Study-specific variable description


| **Name** | `int_month` |
|----------|------------|
| **Label** | `interview month` |
| **Table name** | `sharew1_rel2-6-0_cv_r_whitout_nointw1` |
| **Missings** | `-2 = refusal; -1 = don't know` |
| **Categories** | `1 = january; 2 = february; 3 = march; 4 = april; 5 = may; 6 = june; 7 = july; 8 = august; 9 = september; 10 = october; 11 = november; 12 = december; 13 = today` |
| **Description** |  |


```{r assign1, echo=F}
opal.assign.table.tibble(o, 'SHARE_w1_minterview','SHARE.sharew1_rel2-6-0_cv_r_whitout_nointw1',
                         variables=list('int_month'), missings = TRUE)
SHARE_w1_minterview <- opal.execute(o,'SHARE_w1_minterview')
```

```{r local1, echo=F}
vari <- SHARE_w1_minterview$int_month
#Categorical_summary(var = SHARE_w1_minterview$int_month, missing_values = c(-2,-1))

kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_w1_minterview, aes(x=factor(int_month))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be 
recoded as follows:

* `keep "january" into 1`
* `keep "february" into 2`
* `keep "march" into 3`
* `keep "april" into 4`
* `keep "may" into 5`
* `keep "june" into 6`
* `keep "july" into 7`
* `keep "august" into 8`
* `keep "september" into 9`
* `keep "october" into 10`
* `keep "november" into 11`
* `keep "december" into 12`
* `recode 13 "today" into 999`
* `recode -2 "refusal" into 997`
* `recode -1 "don't know" into 998`

**R script:**

```{r harmo1}
SHARE_ds_w1 <- tibble(id=SHARE_w1_minterview$id)
SHARE_ds_w1$mintw <- car::recode(SHARE_w1_minterview$int_month, "-2=997; -1=998;  c(13,NA)='999'")
SHARE_ds_w1$mintw <- labelled(SHARE_ds_w1$mintw, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
#Categorical_summary(var = SHARE_ds_w1$mintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
vari <- SHARE_ds_w1$mintw
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w1, aes(x=factor(mintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
BeforeH <- table(SHARE_w1_minterview$int_month)
AfterH <- table(SHARE_ds_w1$mintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12")
kable(C)
```

```{r importOPAL_po1, echo=F}
label(SHARE_ds_w1$mintw) <- ds_label
mintw <- SHARE_ds_w1
save(mintw, file = "../RData/w1/mintw.RData")
#opal.assign.data(o, 'SHARE_ds_w1', SHARE_ds_w1)
#opal.symbol_import(o,'SHARE_ds_w1', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w1 <- SHARE_ds_w1
SHARE_m_ds_w1$mintw <- car::recode(SHARE_m_ds_w1$mintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w1', SHARE_m_ds_w1)
#opal.symbol_import(o,'SHARE_m_ds_w1', project='_Athlos_Harm_Dataset')
```




### Wave  2

#### Study-specific variable description



| **Name** | `int_month_w2` |
|----------|------------|
| **Label** | `interview month` |
| **Table name** | `sharew2_rel2-6-0_cv_r_without_noint` |
| **Missings** | `-2 = refusal; -1 = don't know` |
| **Categories** | `1 = january; 2 = february; 3 = march; 4 = april; 5 = may; 6 = june; 7 = july; 8 = august; 9 = september; 10 = october; 11 = november; 12 = december; 13 = today` |
| **Description** |  |



```{r assign2, echo=F}
opal.assign.table.tibble(o, 'SHARE_w2_minterview','SHARE.sharew2_rel2-6-0_cv_r_without_noint',
                         variables=list('int_month_w2'), missings = TRUE)
SHARE_w2_minterview <- opal.execute(o,'SHARE_w2_minterview')
```

```{r local2, echo=F}
#Categorical_summary(var = SHARE_w2_minterview$int_month_w2, missing_values = c(-2,-1))
vari <- SHARE_w2_minterview$int_month_w2
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_w2_minterview, aes(x=factor(int_month_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "january" into 1`
* `keep "february" into 2`
* `keep "march" into 3`
* `keep "april" into 4`
* `keep "may" into 5`
* `keep "june" into 6`
* `keep "july" into 7`
* `keep "august" into 8`
* `keep "september" into 9`
* `keep "october" into 10`
* `keep "november" into 11`
* `keep "december" into 12`
* `recode 13 "today" into 999`
* `recode -2 "refusal" into 997`
* `recode -1 "don't know" into 998`

**R script:**

```{r harmo2}
SHARE_ds_w2 <- tibble(id=SHARE_w2_minterview$id)
SHARE_ds_w2$mintw <- car::recode(SHARE_w2_minterview$int_month_w2, "-2=997; -1=998;  c(13,NA)=999")
SHARE_ds_w2$mintw <- labelled(SHARE_ds_w2$mintw, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
#Categorical_summary(var = SHARE_ds_w2$mintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
vari <- SHARE_ds_w2$mintw
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w2, aes(x=factor(mintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
BeforeH <- table(SHARE_w2_minterview$int_month_w2)
AfterH <- table(SHARE_ds_w2$mintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12")
kable(C)
```

```{r importOPAL_po2, echo=F}
label(SHARE_ds_w2$mintw) <- ds_label
mintw <- SHARE_ds_w2
save(mintw, file = "../RData/w2/mintw.RData")
#opal.assign.data(o, 'SHARE_ds_w2', SHARE_ds_w2)
#opal.symbol_import(o,'SHARE_ds_w2', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w2 <- SHARE_ds_w2
SHARE_m_ds_w2$mintw <- car::recode(SHARE_m_ds_w2$mintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w2', SHARE_m_ds_w2)
#opal.symbol_import(o,'SHARE_m_ds_w2', project='_Athlos_Harm_Dataset')
```






### Wave 3 

#### Study-specific variable description



| **Name** | `int_month_w3` |
|----------|------------|
| **Label** | `interview month` |
| **Table name** | `sharew3_rel1_cv_r_without_noint` |
| **Missings** | `-2 = refusal; -1 = don't know` |
| **Categories** | `1 = january; 2 = february; 3 = march; 4 = april; 5 = may; 6 = june; 7 = july; 8 = august; 9 = september; 10 = october; 11 = november; 12 = december; 13 = today` |
| **Description** |  |



```{r assign3, echo=F}
opal.assign.table.tibble(o, 'SHARE_w3_minterview','SHARE.sharew3_rel1_cv_r_without_noint',
                         variables=list('int_month_w3'), missings = TRUE)
SHARE_w3_minterview <- opal.execute(o,'SHARE_w3_minterview')
```

```{r local3, echo=F}
#Categorical_summary(var = SHARE_w3_minterview$int_month_w3, missing_values = c(-2,-1))
vari <- SHARE_w3_minterview$int_month_w3
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_w3_minterview, aes(x=factor(int_month_w3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "january" into 1`
* `keep "february" into 2`
* `keep "march" into 3`
* `keep "april" into 4`
* `keep "may" into 5`
* `keep "june" into 6`
* `keep "july" into 7`
* `keep "august" into 8`
* `keep "september" into 9`
* `keep "october" into 10`
* `keep "november" into 11`
* `keep "december" into 12`
* `recode 13 "today" into 999`
* `recode -2 "refusal" into 997`
* `recode -1 "don't know" into 998`

**R script:**

```{r harmo3}
SHARE_ds_w3 <- tibble(id=SHARE_w3_minterview$id)
SHARE_ds_w3$mintw <- car::recode(SHARE_w3_minterview$int_month_w3, "-2=997; -1=998;  c(13,NA)=999")
SHARE_ds_w3$mintw <- labelled(SHARE_ds_w3$ mintw, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}
#Categorical_summary(var = SHARE_ds_w3$mintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
vari <- SHARE_ds_w3$mintw
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w3, aes(x=factor(mintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=F}
BeforeH <- c(table(SHARE_w3_minterview$int_month_w3), sum(is.na(SHARE_w3_minterview$int_month_w3)))
AfterH <- table(SHARE_ds_w3$mintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "NA->999")
kable(C)
```

```{r importOPAL_po3, echo=F}
label(SHARE_ds_w3$mintw) <- ds_label
mintw <- SHARE_ds_w3
save(mintw, file = "../RData/w3/mintw.RData")
#opal.assign.data(o, 'SHARE_ds_w3', SHARE_ds_w3)
#opal.symbol_import(o,'SHARE_ds_w3', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w3 <- SHARE_ds_w3
SHARE_m_ds_w3$mintw <- car::recode(SHARE_m_ds_w3$mintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w3', SHARE_m_ds_w3)
#opal.symbol_import(o,'SHARE_m_ds_w3', project='_Athlos_Harm_Dataset')
```







### Wave 4 

#### Study-specific variable description



| **Name** | `int_month_w4` |
|----------|------------|
| **Label** | `interview month` |
| **Table name** | `sharew4_rel1-1-1_cv_r_without_noint` |
| **Missings** | `-2 = refusal; -1 = don't know` |
| **Categories** | `1 = january; 2 = february; 3 = march; 4 = april; 5 = may; 6 = june; 7 = july; 8 = august; 9 = september; 10 = october; 11 = november; 12 = december; 13 = today` |
| **Description** |  |



```{r assign4, echo=F}
opal.assign.table.tibble(o, 'SHARE_w4_minterview','SHARE.sharew4_rel1-1-1_cv_r_without_noint',
                         variables=list('int_month_w4'), missings = TRUE)
SHARE_w4_minterview <- opal.execute(o,'SHARE_w4_minterview')
```

```{r local4, echo=F}
#Categorical_summary(var = SHARE_w4_minterview$int_month_w4, missing_values = c(-2,-1))
vari <- SHARE_w4_minterview$int_month_w4
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_w4_minterview, aes(x=factor(int_month_w4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "january" into 1`
* `keep "february" into 2`
* `keep "march" into 3`
* `keep "april" into 4`
* `keep "may" into 5`
* `keep "june" into 6`
* `keep "july" into 7`
* `keep "august" into 8`
* `keep "september" into 9`
* `keep "october" into 10`
* `keep "november" into 11`
* `keep "december" into 12`
* `recode 13 "today" into 999`
* `recode -2 "refusal" into 997`
* `recode -1 "don't know" into 998`

**R script:**

```{r harmo4}
SHARE_ds_w4 <- tibble(id=SHARE_w4_minterview$id)
SHARE_ds_w4$mintw <- car::recode(SHARE_w4_minterview$int_month_w4, "-2=997; -1=998;  c(13,NA)=999")
SHARE_ds_w4$mintw <- labelled(SHARE_ds_w4$ mintw, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript4, echo=F}
#Categorical_summary(var = SHARE_ds_w4$mintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
vari <- SHARE_ds_w4$mintw
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w4, aes(x=factor(mintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=F}
BeforeH <- c(table(SHARE_w4_minterview$int_month_w4), sum(is.na(SHARE_w4_minterview$int_month_w4)))
AfterH <- table(SHARE_ds_w4$mintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "NA->999")
kable(C)
```

```{r importOPAL_po4, echo=F}
label(SHARE_ds_w4$mintw) <- ds_label
mintw <- SHARE_ds_w4
save(mintw, file = "../RData/w4/mintw.RData")
#opal.assign.data(o, 'SHARE_ds_w4', SHARE_ds_w4)
#opal.symbol_import(o,'SHARE_ds_w4', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w4 <- SHARE_ds_w4
SHARE_m_ds_w4$mintw <- car::recode(SHARE_m_ds_w4$mintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w4', SHARE_m_ds_w4)
#opal.symbol_import(o,'SHARE_m_ds_w4', project='_Athlos_Harm_Dataset')
```









### Wave 5 

#### Study-specific variable description


| **Name** | `int_month_w5` |
|----------|------------|
| **Label** | `interview month` |
| **Table name** | `sharew5_rel1-0-0_cv_r_without_noint` |
| **Missings** | `-2 = refusal; -1 = don't know` |
| **Categories** | `1 = january; 2 = february; 3 = march; 4 = april; 5 = may; 6 = june; 7 = july; 8 = august; 9 = september; 10 = october; 11 = november; 12 = december; 13 = today` |
| **Description** |  |


```{r assign5, echo=F}
opal.assign.table.tibble(o, 'SHARE_w5_minterview','SHARE.sharew5_rel1-0-0_cv_r_without_noint',
                         variables=list('int_month_w5'), missings = TRUE)
SHARE_w5_minterview <- opal.execute(o,'SHARE_w5_minterview')
```

```{r local5, echo=F}
#Categorical_summary(var = SHARE_w5_minterview$int_month_w5, missing_values = c(-2,-1))
vari <- SHARE_w5_minterview$int_month_w5
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_w5_minterview, aes(x=factor(int_month_w5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonize variable from the study-specific variable it has to be recoded as follows:

* `keep "january" into 1`
* `keep "february" into 2`
* `keep "march" into 3`
* `keep "april" into 4`
* `keep "may" into 5`
* `keep "june" into 6`
* `keep "july" into 7`
* `keep "august" into 8`
* `keep "september" into 9`
* `keep "october" into 10`
* `keep "november" into 11`
* `keep "december" into 12`
* `recode 13 "today" into 999`
* `recode -2 "refusal" into 997`
* `recode -1 "don't know" into 998`

**R script:**

```{r harmo5}
SHARE_ds_w5 <- tibble(id=SHARE_w5_minterview$id)
SHARE_ds_w5$mintw <- car::recode(SHARE_w5_minterview$int_month_w5, "-2=997; -1=998;  c(13,NA)=999")
SHARE_ds_w5$mintw <- labelled(SHARE_ds_w5$ mintw, labels = c("january"=1, "february"=2, "march"=3, "april"=4, "may"=5, "june"=6, "july"=7, "august"=8, "september"=9, "october"=10, "november"=11, "december"=12, "Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript5, echo=F}
#Categorical_summary(var = SHARE_ds_w5$mintw, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))
vari <- SHARE_ds_w5$mintw
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "Type of missing")
ggplot(SHARE_ds_w5, aes(x=factor(mintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Month of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation5, echo=F}
BeforeH <- table(SHARE_w5_minterview$int_month_w5)
AfterH <- table(SHARE_ds_w5$mintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12")
kable(C)
```

```{r importOPAL_po5, echo=F}
label(SHARE_ds_w5$mintw) <- ds_label
mintw <- SHARE_ds_w5
save(mintw, file = "../RData/w5/mintw.RData")
#opal.assign.data(o, 'SHARE_ds_w5', SHARE_ds_w5)
#opal.symbol_import(o,'SHARE_ds_w5', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w5 <- SHARE_ds_w5
SHARE_m_ds_w5$mintw <- car::recode(SHARE_m_ds_w5$mintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w5', SHARE_m_ds_w5)
#opal.symbol_import(o,'SHARE_m_ds_w5', project='_Athlos_Harm_Dataset')
```


# Quality estimation
No comments.



<!--- #### Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```

