---
title: "Year of interview"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---
  
```{r setup, include=FALSE}
source("M:/WPs/WP1/Maelstrom/data_process/athlos-project.github.io/setup_iago.r")
```

# Description of DataSchema variable

The description of harmonised variable is the following:


* Short name: `yintw`
* Variable label: `Year of interview`
* Variable description: `year of interview`
* Domain: `Other administrative variables`
* Value type: `countinous`
* Category missings: 

**Code** | **Category Label**
----| ------------------
991 | CAPI/interviewer error
992 | Impute
993 | Disable to measure
994 | Not attempt/not done
995 | Does not answer
996 | Not applicable
997 | Refuse
998 | Do not know
999 | Missing

```{r lab, echo=FALSE}
ds_label <- "Year of interview"
```

# Data process

## SHARE

### Wave 1 

#### Study-specific variable description


| **Name** | `int_year` |
|----------|------------|
| **Label** | `interview year` |
| **Table name** | `sharew1_rel2-6-0_cv_r_whitout_nointw1` |
| **Categories** | `continuous` |
| **Description** |  |



```{r assign1, echo=F}
opal.assign.table.tibble(o, 'SHARE_w1_yinterview','SHARE.sharew1_rel2-6-0_cv_r_whitout_nointw1',
                         variables=list('int_year'), missings = TRUE)
```

```{r local1, echo=F}
SHARE_w1_yinterview <- opal.execute(o,'SHARE_w1_yinterview')
vari <- SHARE_w1_yinterview$int_year
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "int_year")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(SHARE_w1_yinterview, aes(x=factor(int_year))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable 
but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo1}
SHARE_ds_w1 <- tibble(id=SHARE_w1_yinterview$id)
SHARE_ds_w1$yintw <- car::recode(SHARE_w1_yinterview$int_year, "NA=999")
SHARE_ds_w1$yintw <- labelled(SHARE_ds_w1$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript1, echo=F}
vari <- SHARE_ds_w1$yintw
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "yintw")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w1, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation1, echo=F}
BeforeH <- table(SHARE_w1_yinterview$int_year)
AfterH <- table(SHARE_ds_w1$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2004", "2005", "2006")
kable(C)
```


```{r importOPAL_po1, echo=F}
label(SHARE_ds_w1$yintw) <- ds_label
yintw <- SHARE_ds_w1
save(yintw, file = "../RData/w1/yintw.RData")
#opal.assign.data(o, 'SHARE_ds_w1', SHARE_ds_w1)
#opal.symbol_import(o,'SHARE_ds_w1', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w1 <- SHARE_ds_w1
SHARE_m_ds_w1$yintw <- car::recode(SHARE_m_ds_w1$yintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w1', SHARE_m_ds_w1)
#opal.symbol_import(o,'SHARE_m_ds_w1', project='_Athlos_Harm_Dataset')
```




### Wave 2 

#### Study-specific variable description


| **Name** | `int_year_w2` |
|----------|------------|
| **Label** | `interview year` |
| **Table name** | `sharew2_rel2-6-0_cv_r_without_noint` |
| **Categories** | `continuous` |
| **Description** |  |


```{r assign2, echo=F}
opal.assign.table.tibble(o, 'SHARE_w2_yinterview','SHARE.sharew2_rel2-6-0_cv_r_without_noint',
                         variables=list('int_year_w2'), missings = TRUE)
```

```{r local2, echo=F}
SHARE_w2_yinterview <- opal.execute(o,'SHARE_w2_yinterview')
vari <- SHARE_w2_yinterview$int_year_w2
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "int_year_w2")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(SHARE_w2_yinterview, aes(x=factor(int_year_w2))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `NA into 999`

**R script:**

```{r harmo2}
SHARE_ds_w2 <- tibble(id=SHARE_w2_yinterview$id)
SHARE_ds_w2$yintw <- car::recode(SHARE_w2_yinterview$int_year_w2, "NA=999")
SHARE_ds_w2$yintw <- labelled(SHARE_ds_w2$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript2, echo=F}
vari <- SHARE_ds_w2$yintw
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "yintw")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w2, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation2, echo=F}
BeforeH <- table(SHARE_w2_yinterview$int_year_w2)
AfterH <- table(SHARE_ds_w2$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- names(AfterH)
kable(C)
```

```{r importOPAL_po2, echo=F}
label(SHARE_ds_w2$yintw) <- ds_label
yintw <- SHARE_ds_w2
save(yintw, file = "../RData/w2/yintw.RData")
#opal.assign.data(o, 'SHARE_ds_w2', SHARE_ds_w2)
#opal.symbol_import(o,'SHARE_ds_w2', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w2 <- SHARE_ds_w2
SHARE_m_ds_w2$yintw <- car::recode(SHARE_m_ds_w2$yintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w2', SHARE_m_ds_w2)
#opal.symbol_import(o,'SHARE_m_ds_w2', project='_Athlos_Harm_Dataset')
```






### Wave 3 

#### Study-specific variable description


| **Name** | `int_year_w3` |
|----------|------------|
| **Label** | `interview year` |
| **Table name** | `sharew3_rel1_cv_r_without_noint` |
| **Categories** | `continuous` |
| **Description** |  |



```{r assign3, echo=F}
opal.assign.table.tibble(o, 'SHARE_w3_yinterview','SHARE.sharew3_rel1_cv_r_without_noint',
                         variables=list('int_year_w3'), missings = TRUE)
SHARE_w3_yinterview <- opal.execute(o,'SHARE_w3_yinterview')
```

```{r local3, echo=F}
vari <- SHARE_w3_yinterview$int_year_w3
kable(Continuous_summary(vari, missing_values = NA)[3], caption = "int_year_w3")
pander(Continuous_summary(vari, missing_values = NA)$summary, caption = "Summary")
ggplot(SHARE_w3_yinterview, aes(x=factor(int_year_w3))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values are imputed to a 2009 since the majority of the interviews were in this year between the 2008 and 2009 that are the two years that the interviews were did. Therefore the missing values has to be recoded as follows: 

* `NA into 2009`

**R script:**

```{r harmo3}
SHARE_ds_w3 <- tibble(id=SHARE_w3_yinterview$id)
SHARE_ds_w3$yintw <- car::recode(SHARE_w3_yinterview$int_year_w3, "NA=2009")
SHARE_ds_w3$yintw <- labelled(SHARE_ds_w3$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript3, echo=F}
vari <- SHARE_ds_w3$yintw
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "yintw")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w3, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation3, echo=F}
BeforeH <- c(table(SHARE_w3_yinterview$int_year_w3)[1], table(SHARE_w3_yinterview$int_year_w3)[2]+sum(is.na(SHARE_w3_yinterview$int_year_w3)))
AfterH <- table(SHARE_ds_w3$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2008", "2009")
kable(C)
```



```{r importOPAL_po3, echo=F}
label(SHARE_ds_w3$yintw) <- ds_label
yintw <- SHARE_ds_w3
save(yintw, file = "../RData/w3/yintw.RData")
#opal.assign.data(o, 'SHARE_ds_w3', SHARE_ds_w3)
#opal.symbol_import(o,'SHARE_ds_w3', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w3 <- SHARE_ds_w3
SHARE_m_ds_w3$yintw <- car::recode(SHARE_m_ds_w3$yintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w3', SHARE_m_ds_w3)
#opal.symbol_import(o,'SHARE_m_ds_w3', project='_Athlos_Harm_Dataset')
```




### Wave 4 

#### Study-specific variable description


| **Name** | `int_year_w4` |
|----------|------------|
| **Label** | `interview year` |
| **Table name** | `sharew4_rel1-1-1_cv_r_without_noint` |
| **Categories** | `continuous` |
| **Missings** | `-3 = implausible/ suspected wrong` |
| **Description** |  |


```{r assign4, echo=F}
opal.assign.table.tibble(o, 'SHARE_w4_yinterview','SHARE.sharew4_rel1-1-1_cv_r_without_noint',
                         variables=list('int_year_w4'), missings = TRUE)
SHARE_w4_yinterview <- opal.execute(o,'SHARE_w4_yinterview')
```

```{r local4, echo=F}
vari <- SHARE_w4_yinterview$int_year_w4
kable(Continuous_summary(vari, missing_values = c(-3))[3], caption = "int_year_w4")
pander(Continuous_summary(vari, missing_values = c(-3))$summary, caption = "Summary")
ggplot(SHARE_w4_yinterview, aes(x=factor(int_year_w4))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values 'NA' are imputed to a 2011 since the majority of the interviews were in this year between the 2010, 2011 and 2012 that are the tree years that the interviews were did. Therefore the missing values has to be recoded as follows: 

* `recode -3 "implausible/ suspected wrong" into 999`
* `NA into 2011`

**R script:**

```{r harmo4}
SHARE_ds_w4 <- tibble(id=SHARE_w4_yinterview$id)
SHARE_ds_w4$yintw <- car::recode(SHARE_w4_yinterview$int_year_w4, "-3=999; NA=2011")
SHARE_ds_w4$yintw <- labelled(SHARE_ds_w4$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript4, echo=F}
vari <- SHARE_ds_w4$yintw
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "yintw")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w4, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation4, echo=F}
BeforeH <- c(table(SHARE_w4_yinterview$int_year_w4)[1],table(SHARE_w4_yinterview$int_year_w4)[2]+sum(is.na(SHARE_w4_yinterview$int_year_w4)),table(SHARE_w4_yinterview$int_year_w4)[3])
AfterH <- table(SHARE_ds_w4$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2010", "2011", "2012")
kable(C)
```

```{r importOPAL_po4, echo=F}
label(SHARE_ds_w4$yintw) <- ds_label
yintw <- SHARE_ds_w4
save(yintw, file = "../RData/w4/yintw.RData")
#opal.assign.data(o, 'SHARE_ds_w4', SHARE_ds_w4)
#opal.symbol_import(o,'SHARE_ds_w4', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w4 <- SHARE_ds_w4
SHARE_m_ds_w4$yintw <- car::recode(SHARE_m_ds_w4$yintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w4', SHARE_m_ds_w4)
#opal.symbol_import(o,'SHARE_m_ds_w4', project='_Athlos_Harm_Dataset')
```








### Wave 5 

#### Study-specific variable description


| **Name** | `int_year_w5` |
|----------|------------|
| **Label** | `interview year` |
| **Table name** | `sharew5_rel1-0-0_cv_r_without_noint` |
| **Categories** | `continuous` |
| **Missings** | `-2 = refusal; -1 = don't know` |
| **Description** |  |


```{r assign5, echo=F}
opal.assign.table.tibble(o, 'SHARE_w5_yinterview','SHARE.sharew5_rel1-0-0_cv_r_without_noint',
                         variables=list('int_year_w5'), missings = TRUE)
SHARE_w5_yinterview <- opal.execute(o,'SHARE_w5_yinterview')
```

```{r local5, echo=F}
vari <- SHARE_w5_yinterview$int_year_w5
kable(Continuous_summary(vari, missing_values = c(-2,-1))[3], caption = "int_year_w5")
pander(Continuous_summary(vari, missing_values = c(-2,-1))$summary, caption = "Summary")
ggplot(SHARE_w5_yinterview, aes(x=factor(int_year_w5))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Harmonisation algorithm
The harmonized variable is the same of the study-specific variable but the missing values have to be recoded as follows:

* `recode -2 "refusal" into 997`
* `recode -1 "don't know" into 998`
* `recode NA into 999`

**R script:**

```{r harmo5}
SHARE_ds_w5 <- tibble(id=SHARE_w5_yinterview$id)
SHARE_ds_w5$yintw <- car::recode(SHARE_w5_yinterview$int_year_w5, "-2=997; -1=998; NA=999")
SHARE_ds_w5$yintw <- labelled(SHARE_ds_w5$yintw, labels = c("Missing"=999, "Do not know"=998, "Refuse"=997, "Not applicable"=996, "Does not answer"=995,  "Not attempt not done"=994, "Disable to measure"=993, "Impute"=992, "CAPI interviewer error"=991))
```

#### Statistics of the new harmonised variable
```{r descript5, echo=F}
vari <- SHARE_ds_w5$yintw
kable(Continuous_summary(var = vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[3], caption = "yintw")
kable(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))[2], caption = "values")
pander(Continuous_summary(vari, missing_values = c(991, 992, 993, 994, 995, 996, 997, 998, 999))$summary, caption = "Summary")
ggplot(SHARE_ds_w5, aes(x=factor(yintw))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab("Year of interview") + ylab("Frequency")
```

#### Validation
```{r crosstabulation5, echo=F}
BeforeH <- table(SHARE_w5_yinterview$int_year_w5)
AfterH <- table(SHARE_ds_w5$yintw)
C <- rbind(BeforeH,AfterH)
colnames(C) <- c("2013")
kable(C)
```

```{r importOPAL_po5, echo=F}
label(SHARE_ds_w5$yintw) <- ds_label
yintw <- SHARE_ds_w5
save(yintw, file = "../RData/w5/yintw.RData")
#opal.assign.data(o, 'SHARE_ds_w5', SHARE_ds_w5)
#opal.symbol_import(o,'SHARE_ds_w5', project='_Athlos_Harm_Dataset')

SHARE_m_ds_w5 <- SHARE_ds_w5
SHARE_m_ds_w5$yintw <- car::recode(SHARE_m_ds_w5$yintw, "c(991, 992, 993, 994, 995, 996, 997,998, 999)=NA")
#opal.assign.data(o, 'SHARE_m_ds_w5', SHARE_m_ds_w5)
#opal.symbol_import(o,'SHARE_m_ds_w5', project='_Athlos_Harm_Dataset')
```


# Quality estimation
The harmonized variable is the same of the study-specific variable taking into account the time lapse in between waves. Missing values were recoded as the most frecuent value. 


<!--- #### Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```

