---
title: "Sample weights"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/weightsDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/weightsDS.R')
```


# Data process



## SHARE


### Wave 1

#### Study-specific variable description

| **Name** | `w1aci`|
|-|-|
| **Label** | `Calibrated weights wave 1 - individual - all/joint sample`|
| **Table name**  | `sharew1_rel2-6-0_gv_weights`|
| **Categories** | `continuous`|
| **Missings** | `NA` |
| **Description** |  |  |  |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'SHARE_w1','SHARE.sharew1_rel2-6-0_gv_weights',variables=list('w1aci'), missings = T)
SHARE_w1 <- opal.execute(o,'SHARE_w1')

```

```{r local w1, echo=F}

vbl <- SHARE_w1$w1aci
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'w1aci')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(SHARE_w1,!vbl %in% vbl_miss), aes(w1aci)) + geom_bar(stat="bin", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```

#### Harmonisation algorithm

**R script:**

```{r harmo w1}

SHARE_ds_w1 <- tibble(id=SHARE_w1$id)
n <- length(SHARE_w1$id[which(!is.na(SHARE_w1$w1aci))])
N <- sum(SHARE_w1$w1aci,na.rm = T)
SHARE_ds_w1$w <- car::recode(SHARE_w1$w1aci*n/N,"NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w1, echo=F}

vbl <- SHARE_ds_w1$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(SHARE_ds_w1,!vbl %in% miss_values_vector), aes(w)) + geom_bar(stat="count", width=0.1, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w1, echo=F}

```



### Wave 2


#### Study-specific variable description

| **Name** | `w2aci`|
|-|-|
| **Label** | `Calibrated weights wave 2 - individual - all/joint sample`|
| **Table name**  | `sharew2_rel2-6-0_gv_weights`|
| **Categories** | `continuous`|
| **Missings** | `NA` |
| **Description** |  |

```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'SHARE_w2','SHARE.sharew2_rel2-6-0_gv_weights',variables=list('w2aci'), missings = T)
SHARE_w2 <- opal.execute(o,'SHARE_w2')

opal.assign.table.tibble(o, 'SHARE_w2_id','SHARE.sharew2_rel2-6-0_mh',variables=list('hhid2'), missings = T)
SHARE_w2_id <- opal.execute(o,'SHARE_w2_id')

SHARE_w2 <- left_join(SHARE_w2_id,SHARE_w2,by="id")

```

```{r local w2, echo=F}

vbl <- SHARE_w2$w2aci
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'w2aci')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(SHARE_w2,!vbl %in% vbl_miss), aes(w2aci)) + geom_bar(stat="bin", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

**R script:**

```{r harmo w2}

SHARE_ds_w2 <- tibble(id=SHARE_w2$id)
n <- length(SHARE_w2$id[which(!is.na(SHARE_w2$w2aci))])
N <- sum(SHARE_w2$w2aci,na.rm = T)
SHARE_ds_w2$w <- car::recode(SHARE_w2$w2aci*n/N,"NA=999")

```

#### Statistics of the new harmonized variable

```{r descript w2, echo=F}

vbl <- SHARE_ds_w2$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(SHARE_ds_w2,!vbl %in% miss_values_vector), aes(w)) + geom_bar(stat="count", width=0.1, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation

```{r crosstabulation w2, echo=F}

```


### Wave 3

#### Study-specific variable description

| **Name** | `w3aci`|
|-|-|
| **Label** | `Calibrated weights wave 3 - individual - joint sample`|
| **Table name**  | `sharew3_rel1_gv_weights`|
| **Categories** | `continuous`|
| **Missings** | `NA` |
| **Description** |  |

```{r assign w3, echo=F}

opal.assign.table.tibble(o, 'SHARE_w3','SHARE.sharew3_rel1_gv_weights',variables=list('w3aci'), missings = T)
SHARE_w3 <- opal.execute(o,'SHARE_w3')

opal.assign.table.tibble(o, 'SHARE_w3_id','SHARE.sharew3_rel1_cv_r_without_noint',variables=list('hhid3'), missings = T)
SHARE_w3_id <- opal.execute(o,'SHARE_w3_id')

SHARE_w3 <- full_join(SHARE_w3_id,SHARE_w3,by="id")

```

```{r local w3, echo=F}

vbl <- SHARE_w3$w3aci
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'w3aci')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(SHARE_w3,!vbl %in% vbl_miss), aes(w3aci)) + geom_bar(stat="bin", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

**R script:**

```{r harmo w3}

SHARE_ds_w3 <- tibble(id=SHARE_w3$id)
n <- length(SHARE_w3$id[which(!is.na(SHARE_w3$w3aci))])
N <- sum(SHARE_w3$w3aci,na.rm = T)
SHARE_ds_w3$w <- car::recode(SHARE_w3$w3aci*n/N,"NA=999")

```

#### Statistics of the new harmonized variable

```{r descript w3, echo=F}

vbl <- SHARE_ds_w3$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(SHARE_ds_w3,!vbl %in% miss_values_vector), aes(w)) + geom_bar(stat="count", width=0.1, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```

#### Validation

```{r crosstabulation w3, echo=F}

```


### Wave 4

#### Study-specific variable description

| **Name** | `ciw_w4`|
|-|-|
| **Label** | `Calibrated individual weight wave 4`|
| **Table name**  | `sharew4_rel1-1-1_gv_weights`|
| **Categories** |`continuous`|
| **Missings** | `NA` |
| **Description** |  |

```{r assign w4, echo=F}

opal.assign.table.tibble(o, 'SHARE_w4','SHARE.sharew4_rel1-1-1_gv_weights',variables=list('ciw_w4'), missings = T)
SHARE_w4 <- opal.execute(o,'SHARE_w4')

opal.assign.table.tibble(o, 'SHARE_w4_id','SHARE.sharew4_rel1-1-1_cv_r_without_noint',variables=list('hhid4'), missings = T)
SHARE_w4_id <- opal.execute(o,'SHARE_w4_id')

SHARE_w4 <- left_join(SHARE_w4_id,SHARE_w4, by="id")

```

```{r local w4, echo=F}

vbl <- SHARE_w4$ciw_w4
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'ciw_w4')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(SHARE_w4,!vbl %in% vbl_miss), aes(ciw_w4)) + geom_bar(stat="bin", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm


**R script:**

```{r harmo w4}

SHARE_ds_w4 <- tibble(id=SHARE_w4$id)
n <- length(SHARE_w4$id[which(!is.na(SHARE_w4$ciw_w4))])
N <- sum(SHARE_w4$ciw_w4,na.rm = T)
SHARE_ds_w4$w <- car::recode(SHARE_w4$ciw_w4*n/N,"NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w4, echo=F}

vbl <- SHARE_ds_w4$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(SHARE_ds_w4,!vbl %in% miss_values_vector), aes(w)) + geom_bar(stat="count", width=0.1, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w4, echo=F, results='asis'}

```




### Wave 5

#### Study-specific variable description

| **Name** | `ciw_w5`|
|-|-|
| **Label** | `Calibrated individual weight wave 5`|
| **Table name**  |`sharew5_rel1-0-0_gv_weights`|
| **Categories** | `continuous`|
| **Missings** | `NA` |
| **Description** |  |

```{r assign w5, echo=F}

opal.assign.table.tibble(o, 'SHARE_w5','SHARE.sharew5_rel1-0-0_gv_weights',variables=list('ciw_w5'), missings = T)
SHARE_w5 <- opal.execute(o,'SHARE_w5')

opal.assign.table.tibble(o, 'SHARE_w5_id','SHARE.sharew5_rel1-0-0_cv_r_without_noint',variables=list('hhid5'), missings = T)
SHARE_w5_id <- opal.execute(o,'SHARE_w5_id')

SHARE_w5 <- left_join(SHARE_w5_id,SHARE_w5, by="id")

```

```{r local w5, echo=F}

vbl <- SHARE_w5$ciw_w5
vbl_miss <- NA
kable(Continuous_summary(var = vbl, missing_values = vbl_miss)[3], caption = 'ciw_w5')
pander(Continuous_summary(vbl, missing_values = vbl_miss)$summary, caption = "Summary")
ggplot(filter(SHARE_w5,!vbl %in% vbl_miss), aes(ciw_w5)) + geom_bar(stat="bin", fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm


**R script:**

```{r harmo w5}

SHARE_ds_w5 <- tibble(id=SHARE_w5$id)
n <- length(SHARE_w5$id[which(!is.na(SHARE_w5$ciw_w5))])
N <- sum(SHARE_w5$ciw_w5,na.rm = T)
SHARE_ds_w5$w <- car::recode(SHARE_w5$ciw_w5*n/N,"NA=999")

```


#### Statistics of the new harmonized variable

```{r descript w5, echo=F}

vbl <- SHARE_ds_w5$w
kable(Continuous_summary(var = vbl, missing_values = miss_values_vector)[3], caption = ds_label)
kable(Continuous_summary(vbl, missing_values = miss_values_vector)[2], caption = "Values")
pander(Continuous_summary(vbl, missing_values = miss_values_vector)$summary, caption = "Summary")
ggplot(filter(SHARE_ds_w5,!vbl %in% miss_values_vector), aes(w)) + geom_bar(stat="count", width=0.1, fill="steelblue") + xlab(ds_label) + ylab("Frequency")

```


#### Validation

```{r crosstabulation w5, echo=F, results='asis'}

```






# Quality estimation

<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.hds <- list(w1 = SHARE_ds_w1, w2 = SHARE_ds_w2, w3 = SHARE_ds_w3, w4 = SHARE_ds_w4, w5 = SHARE_ds_w5)

for(index in seq_along(l.hds)){
  label(l.hds[[index]][[2]]) <- ds_label
  w <- l.hds[[index]]
  save(w, file = paste0(datafolder,names(l.hds)[index],"/w.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





