---
title: "Proxy"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/proxyDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/proxyDS.R')
```

<!-- ########################################################## --> 

# Data process

## SHARE 

### Wave 1 

#### Study-specific variable description

| **Name** | `hh014_`| `ho041_` | `ft021_` | `sp022_` | `ch023_` | `ep210_` | `hc063_` | `br017_` | `ph054_` | `dn038_` | `as057_` | `co009_` |
|-|-|-|-|-|-|-|-|-|-|-|-|-|
| **Label** | `who answered the questions in hh`| `who answered the questions in ho` | `who answered the questions in ft` | `who answered the questions in sp` | `who answered questions in section ch` | `who answered section ep` | `who answered the questions in hc` | `interviewer check br` | `who answered the questions in ph` | `interviewer check dn` | `who answered the questions in as` | `who answered the questions in co` |
| **Table name** | `sharew1_rel2-6-0_hh` | `sharew1_rel2-6-0_ho` | `sharew1_rel2-6-0_ft`| `sharew1_rel2-6-0_sp` | `sharew1_rel2-6-0_ch` | `sharew1_rel2-6-0_ep` | `sharew1_rel2-6-0_hc` | `sharew1_rel2-6-0_br` | `sharew1_rel2-6-0_ph` | `sharew1_rel2-6-0_dn` | `sharew1_rel2-6-0_as` | `sharew1_rel2-6-0_co` | 
| **Categories** |`1 = respondent only`|`1 = respondent only`|`1 = respondent only`|`1 = respondent only`|`1 = respondent only`| `1 = respondent only`|`1 = respondent only`|`1 = respondent only`|`1 = respondent only`|`1 = respondent only`|`1 = respondent only`|`1 = respondent only`|
| | `2 = respondent and proxy` | `2 = respondent and proxy` |`2 = respondent and proxy` |`2 = respondent and proxy` |`2 = respondent and proxy` |`2 = respondent and proxy` |`2 = respondent and proxy` |`2 = respondent and proxy` |`2 = respondent and proxy` |`2 = respondent and proxy` |`2 = respondent and proxy` |`2 = respondent and proxy` |
| | `3 = proxy only` |`3 = proxy only` |`3 = proxy only` |`3 = proxy only` |`3 = proxy only` |`3 = proxy only` |`3 = proxy only` |`3 = proxy only` |`3 = proxy only` |`3 = proxy only` |`3 = proxy only` |
| **Category missings** | `-1 = don't know` | `-1 = don't know` | `-1 = don't know` | `-1 = don't know` |  `-1 = don't know` |  `-1 = don't know` |  `-1 = don't know` |  `-1 = don't know` | `-1 = don't know` |  `-1 = don't know` | `-1 = don't know` | 
| | `-2 = refusal`|`-2 = refusal`|`-2 = refusal`|`-2 = refusal`|`-2 = refusal`|`-2 = refusal`|`-2 = refusal`|`-2 = refusal`|`-2 = refusal`|`-2 = refusal`|`-2 = refusal`|
| **Description** |  |  |  |  |  |  |  |  |  |  |  |

```{r assign1, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_p1','SHARE.sharew1_rel2-6-0_hh',
                         variables=list('hh014_'), missings = TRUE)
SHARE_p1 <- opal.execute(o,'SHARE_p1')

opal.assign.table.tibble(o, 'SHARE_p2','SHARE.sharew1_rel2-6-0_ho',
                         variables=list('ho041_'), missings = TRUE)
SHARE_p2 <- opal.execute(o,'SHARE_p2')

SHARE_proxy <- full_join(SHARE_p1, SHARE_p2, by='id')

opal.assign.table.tibble(o, 'SHARE_p3','SHARE.sharew1_rel2-6-0_ft',
                         variables=list('ft021_'), missings = TRUE)
SHARE_p3 <- opal.execute(o,'SHARE_p3')
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p3)

opal.assign.table.tibble(o, 'SHARE_p4','SHARE.sharew1_rel2-6-0_sp',
                         variables=list('sp022_'), missings = TRUE)
SHARE_p4 <- opal.execute(o,'SHARE_p4')
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p4)


opal.assign.table.tibble(o, 'SHARE_p5','SHARE.sharew1_rel2-6-0_ch',
                         variables=list('ch023_'), missings = TRUE)
SHARE_p5 <- opal.execute(o,'SHARE_p5')
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p5)

opal.assign.table.tibble(o, 'SHARE_p6','SHARE.sharew1_rel2-6-0_ep',
                         variables=list('ep210_'), missings = TRUE)
SHARE_p6 <- opal.execute(o,'SHARE_p6')
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p6)

opal.assign.table.tibble(o, 'SHARE_p7','SHARE.sharew1_rel2-6-0_hc',
                         variables=list('hc063_'), missings = TRUE)
SHARE_p7 <- opal.execute(o,'SHARE_p7')
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p7)

opal.assign.table.tibble(o, 'SHARE_p8','SHARE.sharew1_rel2-6-0_br',
                         variables=list('br017_'), missings = TRUE)
SHARE_p8 <- opal.execute(o,'SHARE_p8')
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p8)

opal.assign.table.tibble(o, 'SHARE_p9','SHARE.sharew1_rel2-6-0_ph',
                         variables=list('ph054_'), missings = TRUE)
SHARE_p9 <- opal.execute(o,'SHARE_p9')
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p9)

opal.assign.table.tibble(o, 'SHARE_p10','SHARE.sharew1_rel2-6-0_dn',
                         variables=list('dn038_'), missings = TRUE)
SHARE_p10 <- opal.execute(o,'SHARE_p10')
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p10)

opal.assign.table.tibble(o, 'SHARE_p11','SHARE.sharew1_rel2-6-0_as',
                         variables=list('as057_'), missings = TRUE)
SHARE_p11 <- opal.execute(o,'SHARE_p11')
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p11)

opal.assign.table.tibble(o, 'SHARE_p12','SHARE.sharew1_rel2-6-0_co',
                         variables=list('co009_'), missings = TRUE)
SHARE_p12 <- opal.execute(o,'SHARE_p12')
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p12)
```

```{r local1, echo=FALSE}
vari <- SHARE_proxy$hh014_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$ho041_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$ft021_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$sp022_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$ch023_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$ep210_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$hc063_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$br017_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$ph054_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$dn038_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$as057_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$co009_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variables they has to be recoded as follows:

First of all: 

* `recode 2,3 into 2`
* `reocde -1, -2 into NA`

Secondly, 

* `if any of the variables is equal to 2 recode proxy = 1`
* `otherwise proxy = 0`
* `unless all the variables are missing values `

**R script:**


```{r harmo1, echo=TRUE}
SHARE_proxy$hh014_ <- car::recode(SHARE_proxy$hh014_, "2:3=2; -2:-1=NA")
SHARE_proxy$ho041_ <- car::recode(SHARE_proxy$ho041_, "2:3=2; -2:-1=NA")
SHARE_proxy$ft021_ <- car::recode(SHARE_proxy$ft021_, "2:3=2; -2:-1=NA")
SHARE_proxy$sp022_ <- car::recode(SHARE_proxy$sp022_, "2:3=2; -2:-1=NA")
SHARE_proxy$ch023_ <- car::recode(SHARE_proxy$ch023_, "2:3=2; -2:-1=NA")
SHARE_proxy$ep210_ <- car::recode(SHARE_proxy$ep210_, "2:3=2; -2:-1=NA")
SHARE_proxy$hc063_ <- car::recode(SHARE_proxy$hc063_, "2:3=2; -2:-1=NA")
SHARE_proxy$br017_ <- car::recode(SHARE_proxy$br017_, "2:3=2; -2:-1=NA")
SHARE_proxy$ph054_ <- car::recode(SHARE_proxy$ph054_, "2:3=2; -2:-1=NA")
SHARE_proxy$dn038_ <- car::recode(SHARE_proxy$dn038_, "2:3=2; -2:-1=NA")
SHARE_proxy$as057_ <- car::recode(SHARE_proxy$as057_, "2:3=2; -2:-1=NA")
SHARE_proxy$co009_ <- car::recode(SHARE_proxy$co009_, "2:3=2; -2:-1=NA")

SHARE_proxy$have2 <- apply(SHARE_proxy[,-1], MARGIN = 1, FUN = function(x) sum(x==2, na.rm = TRUE)>=1)
SHARE_proxy$nmis <- apply(SHARE_proxy[,-1], MARGIN = 1, FUN = function(x) sum(is.na(x)))

SHARE_ds_w1 <- tibble(id=SHARE_proxy$id)
SHARE_ds_w1$proxy <- 0
SHARE_ds_w1$proxy[SHARE_proxy$have2] <- 1
SHARE_ds_w1$proxy[SHARE_proxy$nmis==12] <- 999
SHARE_ds_w1$proxy <- labelled(SHARE_ds_w1$proxy, labels = cat_label)
label(SHARE_ds_w1$proxy) <- ds_label_all
```

#### Statistical description of the new harmonised variable
```{r descript1, echo=FALSE}
vari <- SHARE_ds_w1$proxy
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SHARE_ds_w1, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```
 
 





### Wave 2 

#### Study-specific variable description


| **Name** | `hh014_`| `ho041_` | `ft021_` | `sp022_` | `ch023_` | `ep210_` | `hc063_` | `br017_` | `ph054_` | `dn038_` | `as057_` | `co009_` |
|-|-|-|-|-|-|-|-|-|-|-|-|-|
| **Label** | `who answered the questions in hh`| `who answered the questions in ho` | `who answered the questions in ft` | `who answered the questions in sp` | `who answered questions in section ch` | `who answered section ep` | `who answered the questions in hc` | `interviewer check br` | `who answered the questions in ph` | `interviewer check dn` | `who answered the questions in as` | `who answered the questions in co` |
| **Table name** | `sharew2_rel2-6-0_hh` | `sharew2_rel2-6-0_ho` | `sharew2_rel2-6-0_ft`| `sharew2_rel2-6-0_sp` | `sharew2_rel2-6-0_ch` | `sharew2_rel2-6-0_ep` | `sharew2_rel2-6-0_hc` | `sharew2_rel2-6-0_br` | `sharew2_rel2-6-0_ph` | `sharew2_rel2-6-0_dn` | `sharew2_rel2-6-0_as` | `sharew2_rel2-6-0_co` | 
| **Categories** |`1 = respondent only`|`1 = respondent only`|`1 = respondent only`|`1 = respondent only`|`1 = respondent only`| `1 = respondent only`|`1 = respondent only`|`1 = respondent only`|`1 = respondent only`|`1 = respondent only`|`1 = respondent only`|`1 = respondent only`|
| | `2 = respondent and proxy` | `2 = respondent and proxy` |`2 = respondent and proxy` |`2 = respondent and proxy` |`2 = respondent and proxy` |`2 = respondent and proxy` |`2 = respondent and proxy` |`2 = respondent and proxy` |`2 = respondent and proxy` |`2 = respondent and proxy` |`2 = respondent and proxy` |`2 = respondent and proxy` |
| | `3 = proxy only` |`3 = proxy only` |`3 = proxy only` |`3 = proxy only` |`3 = proxy only` |`3 = proxy only` |`3 = proxy only` |`3 = proxy only` |`3 = proxy only` |`3 = proxy only` |`3 = proxy only` |
| **Category missings** | `-1 = don't know` | `-1 = don't know` | `-1 = don't know` | `-1 = don't know` |  `-1 = don't know` |  `-1 = don't know` |  `-1 = don't know` |  `-1 = don't know` | `-1 = don't know` |  `-1 = don't know` | `-1 = don't know` | 
| | `-2 = refusal`|`-2 = refusal`|`-2 = refusal`|`-2 = refusal`|`-2 = refusal`|`-2 = refusal`|`-2 = refusal`|`-2 = refusal`|`-2 = refusal`|`-2 = refusal`|`-2 = refusal`|
| **Description** |  |  |  |  |  |  |  |  |  |  |  |

```{r assign2, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_p1','SHARE.sharew2_rel2-6-0_hh',
                         variables=list('hh014_'), missings = TRUE)
SHARE_p1 <- opal.execute(o,'SHARE_p1')

opal.assign.table.tibble(o, 'SHARE_p2','SHARE.sharew2_rel2-6-0_ho',
                         variables=list('ho041_'), missings = TRUE)
SHARE_p2 <- opal.execute(o,'SHARE_p2')

SHARE_proxy <- full_join(SHARE_p1, SHARE_p2, by='id')

opal.assign.table.tibble(o, 'SHARE_p3','SHARE.sharew2_rel2-6-0_ft',
                         variables=list('ft021_'), missings = TRUE)
SHARE_p3 <- opal.execute(o,'SHARE_p3')
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p3)

opal.assign.table.tibble(o, 'SHARE_p4','SHARE.sharew2_rel2-6-0_sp',
                         variables=list('sp022_'), missings = TRUE)
SHARE_p4 <- opal.execute(o,'SHARE_p4')
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p4)


opal.assign.table.tibble(o, 'SHARE_p5','SHARE.sharew2_rel2-6-0_ch',
                         variables=list('ch023_'), missings = TRUE)
SHARE_p5 <- opal.execute(o,'SHARE_p5')
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p5)

opal.assign.table.tibble(o, 'SHARE_p6','SHARE.sharew2_rel2-6-0_ep',
                         variables=list('ep210_'), missings = TRUE)
SHARE_p6 <- opal.execute(o,'SHARE_p6')
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p6)

opal.assign.table.tibble(o, 'SHARE_p7','SHARE.sharew2_rel2-6-0_hc',
                         variables=list('hc063_'), missings = TRUE)
SHARE_p7 <- opal.execute(o,'SHARE_p7')
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p7)

opal.assign.table.tibble(o, 'SHARE_p8','SHARE.sharew2_rel2-6-0_br',
                         variables=list('br017_'), missings = TRUE)
SHARE_p8 <- opal.execute(o,'SHARE_p8')
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p8)

opal.assign.table.tibble(o, 'SHARE_p9','SHARE.sharew2_rel2-6-0_ph',
                         variables=list('ph054_'), missings = TRUE)
SHARE_p9 <- opal.execute(o,'SHARE_p9')
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p9)

opal.assign.table.tibble(o, 'SHARE_p10','SHARE.sharew2_rel2-6-0_dn',
                         variables=list('dn038_'), missings = TRUE)
SHARE_p10 <- opal.execute(o,'SHARE_p10')
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p10)

opal.assign.table.tibble(o, 'SHARE_p11','SHARE.sharew2_rel2-6-0_as',
                         variables=list('as057_'), missings = TRUE)
SHARE_p11 <- opal.execute(o,'SHARE_p11')
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p11)

opal.assign.table.tibble(o, 'SHARE_p12','SHARE.sharew2_rel2-6-0_co',
                         variables=list('co009_'), missings = TRUE)
SHARE_p12 <- opal.execute(o,'SHARE_p12')
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p12)
```

```{r local2, echo=FALSE}
vari <- SHARE_proxy$hh014_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$ho041_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$ft021_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$sp022_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$ch023_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$ep210_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$hc063_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$br017_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$ph054_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$dn038_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$as057_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$co009_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variables they has to be recoded as follows:

First of all: 

* `recode 2,3 into 2`
* `reocde -1, -2 into NA`

Secondly, 

* `if any of the variables is equal to 2 recode proxy = 1`
* `otherwise proxy = 0`
* `unless all the variables are missing values `

**R script:**

```{r harmo2, echo=TRUE}
SHARE_proxy$hh014_ <- car::recode(SHARE_proxy$hh014_, "2:3=2; -2:-1=NA")
SHARE_proxy$ho041_ <- car::recode(SHARE_proxy$ho041_, "2:3=2; -2:-1=NA")
SHARE_proxy$ft021_ <- car::recode(SHARE_proxy$ft021_, "2:3=2; -2:-1=NA")
SHARE_proxy$sp022_ <- car::recode(SHARE_proxy$sp022_, "2:3=2; -2:-1=NA")
SHARE_proxy$ch023_ <- car::recode(SHARE_proxy$ch023_, "2:3=2; -2:-1=NA")
SHARE_proxy$ep210_ <- car::recode(SHARE_proxy$ep210_, "2:3=2; -2:-1=NA")
SHARE_proxy$hc063_ <- car::recode(SHARE_proxy$hc063_, "2:3=2; -2:-1=NA")
SHARE_proxy$br017_ <- car::recode(SHARE_proxy$br017_, "2:3=2; -2:-1=NA")
SHARE_proxy$ph054_ <- car::recode(SHARE_proxy$ph054_, "2:3=2; -2:-1=NA")
SHARE_proxy$dn038_ <- car::recode(SHARE_proxy$dn038_, "2:3=2; -2:-1=NA")
SHARE_proxy$as057_ <- car::recode(SHARE_proxy$as057_, "2:3=2; -2:-1=NA")
SHARE_proxy$co009_ <- car::recode(SHARE_proxy$co009_, "2:3=2; -2:-1=NA")

SHARE_proxy$have2 <- apply(SHARE_proxy[,-1], MARGIN = 1, FUN = function(x) sum(x==2, na.rm = TRUE)>=1)
SHARE_proxy$nmis <- apply(SHARE_proxy[,-1], MARGIN = 1, FUN = function(x) sum(is.na(x)))

SHARE_ds_w2 <- tibble(id=SHARE_proxy$id)
SHARE_ds_w2$proxy <- 0
SHARE_ds_w2$proxy[SHARE_proxy$have2] <- 1
SHARE_ds_w2$proxy[SHARE_proxy$nmis==12] <- 999
SHARE_ds_w2$proxy <- labelled(SHARE_ds_w2$proxy, labels = cat_label)
label(SHARE_ds_w2$proxy) <- ds_label_all
```

#### Statistical description of the new harmonised variable
```{r descript2, echo=FALSE}
vari <- SHARE_ds_w2$proxy
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SHARE_ds_w2, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```





### Wave 3 

#### Study-specific variable description

| **Name** |`sl_st016_`|`sl_ac027_`|`sl_cs012_`|`sl_gl036_`|`sl_hc098_`|`sl_hs066_`|`sl_rc061_`|`sl_re048_`|`sl_rp023_`|
|-|-|-|-|-|-|-|-|-|-|
| **Label** |`proxy check`|`proxy check`|`proxy check`|`proxy check`|`proxy check`|`proxy check`|`proxy check`|`proxy check`|`proxy check`|
| **Table name** |`sharew3_rel1_st`|`sharew3_rel1_ac`|`sharew3_rel1_cs`|`sharew3_rel1_gl`|`sharew3_rel1_hc`|`sharew3_rel1_hs`|`sharew3_rel1_rc`|`sharew3_rel1_re`|`sharew3_rel1_rp`|
| **Categories** |`1 = respondent only`<br/>`2 = respondent and proxy`<br/>`3 = proxy only`|`1 = respondent only`<br/>`2 = respondent and proxy`<br/>`3 = proxy only`|`1 = respondent only`<br/>`2 = respondent and proxy`<br/>`3 = proxy only`|`1 = respondent only`<br/>`2 = respondent and proxy`<br/>`3 = proxy only`|`1 = respondent only`<br/>`2 = respondent and proxy`<br/>`3 = proxy only`|`1 = respondent only`<br/>`2 = respondent and proxy`<br/>`3 = proxy only`|`1 = respondent only`<br/>`2 = respondent and proxy`<br/>`3 = proxy only`|`1 = respondent only`<br/>`2 = respondent and proxy`<br/>`3 = proxy only`|`1 = respondent only`<br/>`2 = respondent and proxy`<br/>`3 = proxy only`|
| **Missings** |`-1 = don't know`<br/>`-2 = refusal`<br/>`NA`|`-1 = don't know`<br/>`-2 = refusal`<br/>`NA`|`-1 = don't know`<br/>`-2 = refusal`<br/>`NA`|`-1 = don't know`<br/>`-2 = refusal`<br/>`NA`|`-1 = don't know`<br/>`-2 = refusal`<br/>`NA`|`-1 = don't know`<br/>`-2 = refusal`<br/>`NA`|`-1 = don't know`<br/>`-2 = refusal`<br/>`NA`|`-1 = don't know`<br/>`-2 = refusal`<br/>`NA`|`-1 = don't know`<br/>`-2 = refusal`<br/>`NA`|
| **Description** |  |  |  |  |  |  |  |  |  |


```{r assign w3, echo=F}

opal.assign.table.tibble(o, 'SHARE_p1','SHARE.sharew3_rel1_st', variables=list('sl_st016_'), missings = TRUE)
SHARE_p1 <- opal.execute(o,'SHARE_p1')

opal.assign.table.tibble(o, 'SHARE_p2','SHARE.sharew3_rel1_ac', variables=list('sl_ac027_'), missings = TRUE)
SHARE_p2 <- opal.execute(o,'SHARE_p2')

opal.assign.table.tibble(o, 'SHARE_p3','SHARE.sharew3_rel1_cs', variables=list('sl_cs012_'), missings = TRUE)
SHARE_p3 <- opal.execute(o,'SHARE_p3')

opal.assign.table.tibble(o, 'SHARE_p4','SHARE.sharew3_rel1_gl', variables=list('sl_gl036_'), missings = TRUE)
SHARE_p4 <- opal.execute(o,'SHARE_p4')

opal.assign.table.tibble(o, 'SHARE_p5','SHARE.sharew3_rel1_hc', variables=list('sl_hc098_'), missings = TRUE)
SHARE_p5 <- opal.execute(o,'SHARE_p5')

opal.assign.table.tibble(o, 'SHARE_p6','SHARE.sharew3_rel1_hs', variables=list('sl_hs066_'), missings = TRUE)
SHARE_p6 <- opal.execute(o,'SHARE_p6')

opal.assign.table.tibble(o, 'SHARE_p7','SHARE.sharew3_rel1_rc', variables=list('sl_rc061_'), missings = TRUE)
SHARE_p7 <- opal.execute(o,'SHARE_p7')

opal.assign.table.tibble(o, 'SHARE_p8','SHARE.sharew3_rel1_re', variables=list('sl_re048_'), missings = TRUE)
SHARE_p8 <- opal.execute(o,'SHARE_p8')

opal.assign.table.tibble(o, 'SHARE_p9','SHARE.sharew3_rel1_rp', variables=list('sl_rp023_'), missings = TRUE)
SHARE_p9 <- opal.execute(o,'SHARE_p9')

SHARE_proxy <- full_join(SHARE_p1, SHARE_p2, by='id')
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p3)
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p4)
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p5)
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p6)
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p7)
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p8)
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p9)

```

```{r local w3, echo=FALSE}

vbl <- SHARE_proxy$sl_st016_
vbl_miss <- c(-2,-1)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = attributes(vbl)$`spss::shortName`) 
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SHARE_proxy$sl_ac027_
vbl_miss <- c(-2,-1)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = attributes(vbl)$`spss::shortName`) 
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SHARE_proxy$sl_cs012_
vbl_miss <- c(-2,-1)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = attributes(vbl)$`spss::shortName`) 
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SHARE_proxy$sl_gl036_
vbl_miss <- c(-2,-1)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = attributes(vbl)$`spss::shortName`) 
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SHARE_proxy$sl_hc098_
vbl_miss <- c(-2,-1)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = attributes(vbl)$`spss::shortName`) 
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SHARE_proxy$sl_hs066_
vbl_miss <- c(-2,-1)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = attributes(vbl)$`spss::shortName`) 
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SHARE_proxy$sl_rc061_
vbl_miss <- c(-2,-1)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = attributes(vbl)$`spss::shortName`) 
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SHARE_proxy$sl_re048_
vbl_miss <- c(-2,-1)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = attributes(vbl)$`spss::shortName`) 
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

vbl <- SHARE_proxy$sl_rp023_
vbl_miss <- c(-2,-1)
kable(Categorical_summary(vbl, missing_values = vbl_miss)[3], caption = attributes(vbl)$`spss::shortName`) 
kable(Categorical_summary(vbl, missing_values = vbl_miss)[1], caption = "Category")
kable(Categorical_summary(vbl, missing_values = vbl_miss)[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vbl))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vbl)) + ylab("Frequency")

```


#### Harmonisation algorithm

To compute the harmonised variable from the study-specific variables they have to be recoded as follows:

First of all: 

* `recode 2,3 into 2`
* `reocde -1, -2 into NA`

Secondly, 

* `if any of the variables is equal to 2 recode proxy = 1`
* `otherwise proxy = 0`
* `unless all the variables are missing values `

```{r harmo w3}

SHARE_proxy$sl_st016_ <- car::recode(SHARE_proxy$sl_st016_, "2:3=2")
SHARE_proxy$sl_ac027_ <- car::recode(SHARE_proxy$sl_ac027_, "2:3=2")
SHARE_proxy$sl_cs012_ <- car::recode(SHARE_proxy$sl_cs012_, "2:3=2")
SHARE_proxy$sl_gl036_ <- car::recode(SHARE_proxy$sl_gl036_, "2:3=2")
SHARE_proxy$sl_hc098_ <- car::recode(SHARE_proxy$sl_hc098_, "2:3=2")
SHARE_proxy$sl_hs066_ <- car::recode(SHARE_proxy$sl_hs066_, "2:3=2")
SHARE_proxy$sl_rc061_ <- car::recode(SHARE_proxy$sl_rc061_, "2:3=2")
SHARE_proxy$sl_re048_ <- car::recode(SHARE_proxy$sl_re048_, "2:3=2")
SHARE_proxy$sl_rp023_ <- car::recode(SHARE_proxy$sl_rp023_, "2:3=2")

SHARE_proxy$have2 <- apply(SHARE_proxy[,-1], MARGIN = 1, FUN = function(x) sum(x==2, na.rm = TRUE)>=1)
SHARE_proxy$nmis <- apply(SHARE_proxy[,-1], MARGIN = 1, FUN = function(x) sum(is.na(x)))

SHARE_ds_w3 <- tibble(id=SHARE_proxy$id)
SHARE_ds_w3$proxy <- 0
SHARE_ds_w3$proxy[which(SHARE_proxy$have2)] <- 1
SHARE_ds_w3$proxy[SHARE_proxy$nmis==9] <- 999


```


#### Statistical description of the new harmonised variable
```{r descript w3, echo=FALSE}
vari <- SHARE_ds_w3$proxy
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SHARE_ds_w3, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```


### Wave 4 

#### Study-specific variable description

| **Name** | `hh014_`| `ho041_` | `ft021_` | `sp022_` | `ch023_` | `ep210_` | `br017_` | `ph054_` | `as057_` | `co009_` |
|-|-|-|-|-|-|-|-|-|-|-|-|
| **Label** | `who answered the questions in hh`| `who answered the questions in ho` | `who answered the questions in ft` | `who answered the questions in sp` | `who answered questions in section ch` | `who answered section ep` | `interviewer check br` | `who answered the questions in ph` | `who answered the questions in as` | `who answered the questions in co` |
| **Table name** | `sharew4_rel1-1-1_hh` | `sharew4_rel1-1-1_ho` | `sharew4_rel1-1-1_ft`| `sharew4_rel1-1-1_sp` | `sharew4_rel1-1-1_ch` | `sharew4_rel1-1-1_ep` | `sharew4_rel1-1-1_br` | `sharew4_rel1-1-1_ph` | `sharew4_rel1-1-1_as` | `sharew4_rel1-1-1_co` | 
| **Categories** |`1 = respondent only`|`1 = respondent only`|`1 = respondent only`|`1 = respondent only`|`1 = respondent only`| `1 = respondent only`|`1 = respondent only`|`1 = respondent only`|`1 = respondent only`|`1 = respondent only`|
| | `2 = respondent and proxy` | `2 = respondent and proxy` |`2 = respondent and proxy` |`2 = respondent and proxy` |`2 = respondent and proxy` |`2 = respondent and proxy` |`2 = respondent and proxy` |`2 = respondent and proxy` |`2 = respondent and proxy` |`2 = respondent and proxy` |
| | `3 = proxy only` |`3 = proxy only` |`3 = proxy only` |`3 = proxy only` |`3 = proxy only` |`3 = proxy only` |`3 = proxy only` |`3 = proxy only` |`3 = proxy only` |`
| **Category missings** | `-1 = don't know` | `-1 = don't know` | `-1 = don't know` | `-1 = don't know` |  `-1 = don't know` |  `-1 = don't know` |  `-1 = don't know` |  `-1 = don't know` | `-1 = don't know` |
| | `-2 = refusal`|`-2 = refusal`|`-2 = refusal`|`-2 = refusal`|`-2 = refusal`|`-2 = refusal`|`-2 = refusal`|`-2 = refusal`|`-2 = refusal`|
| **Description** |  |  |  |  |  |  |  |  |  |


```{r assign4, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_p1','SHARE.sharew4_rel1-1-1_hh',
                         variables=list('hh014_'), missings = TRUE)
SHARE_p1 <- opal.execute(o,'SHARE_p1')

opal.assign.table.tibble(o, 'SHARE_p2','SHARE.sharew4_rel1-1-1_ho',
                         variables=list('ho041_'), missings = TRUE)
SHARE_p2 <- opal.execute(o,'SHARE_p2')

SHARE_proxy <- full_join(SHARE_p1, SHARE_p2, by='id')

opal.assign.table.tibble(o, 'SHARE_p3','SHARE.sharew4_rel1-1-1_ft',
                         variables=list('ft021_'), missings = TRUE)
SHARE_p3 <- opal.execute(o,'SHARE_p3')
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p3)

opal.assign.table.tibble(o, 'SHARE_p4','SHARE.sharew4_rel1-1-1_sp',
                         variables=list('sp022_'), missings = TRUE)
SHARE_p4 <- opal.execute(o,'SHARE_p4')
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p4)


opal.assign.table.tibble(o, 'SHARE_p5','SHARE.sharew4_rel1-1-1_ch',
                         variables=list('ch023_'), missings = TRUE)
SHARE_p5 <- opal.execute(o,'SHARE_p5')
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p5)

opal.assign.table.tibble(o, 'SHARE_p6','SHARE.sharew4_rel1-1-1_ep',
                         variables=list('ep210_'), missings = TRUE)
SHARE_p6 <- opal.execute(o,'SHARE_p6')
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p6)

opal.assign.table.tibble(o, 'SHARE_p8','SHARE.sharew4_rel1-1-1_br',
                         variables=list('br017_'), missings = TRUE)
SHARE_p8 <- opal.execute(o,'SHARE_p8')
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p8)

opal.assign.table.tibble(o, 'SHARE_p9','SHARE.sharew4_rel1-1-1_ph',
                         variables=list('ph054_'), missings = TRUE)
SHARE_p9 <- opal.execute(o,'SHARE_p9')
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p9)

opal.assign.table.tibble(o, 'SHARE_p11','SHARE.sharew4_rel1-1-1_as',
                         variables=list('as057_'), missings = TRUE)
SHARE_p11 <- opal.execute(o,'SHARE_p11')
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p11)

opal.assign.table.tibble(o, 'SHARE_p12','SHARE.sharew4_rel1-1-1_co',
                         variables=list('co009_'), missings = TRUE)
SHARE_p12 <- opal.execute(o,'SHARE_p12')
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p12)
```

```{r local4, echo=FALSE}
vari <- SHARE_proxy$hh014_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$ho041_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$ft021_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$sp022_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$ch023_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$ep210_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$br017_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$ph054_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$as057_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$co009_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variables they has to be recoded as follows:

First of all: 

* `recode 2,3 into 2`
* `reocde -1, -2 into NA`

Secondly, 

* `if any of the variables is equal to 2 recode proxy = 1`
* `otherwise proxy = 0`
* `unless all the variables are missing values `

**R script:**

```{r harmo4, echo=TRUE}
SHARE_proxy$hh014_ <- car::recode(SHARE_proxy$hh014_, "2:3=2")
SHARE_proxy$ho041_ <- car::recode(SHARE_proxy$ho041_, "2:3=2")
SHARE_proxy$ft021_ <- car::recode(SHARE_proxy$ft021_, "2:3=2")
SHARE_proxy$sp022_ <- car::recode(SHARE_proxy$sp022_, "2:3=2")
SHARE_proxy$ch023_ <- car::recode(SHARE_proxy$ch023_, "2:3=2")
SHARE_proxy$ep210_ <- car::recode(SHARE_proxy$ep210_, "2:3=2")
SHARE_proxy$br017_ <- car::recode(SHARE_proxy$br017_, "2:3=2")
SHARE_proxy$ph054_ <- car::recode(SHARE_proxy$ph054_, "2:3=2")
SHARE_proxy$as057_ <- car::recode(SHARE_proxy$as057_, "2:3=2")
SHARE_proxy$co009_ <- car::recode(SHARE_proxy$co009_, "2:3=2")

SHARE_proxy$have2 <- apply(SHARE_proxy[,-1], MARGIN = 1, FUN = function(x) sum(x==2, na.rm = TRUE)>=1)
SHARE_proxy$nmis <- apply(SHARE_proxy[,-1], MARGIN = 1, FUN = function(x) sum(is.na(x)))

SHARE_ds_w4 <- tibble(id=SHARE_proxy$id)
SHARE_ds_w4$proxy <- 0
SHARE_ds_w4$proxy[SHARE_proxy$have2] <- 1
SHARE_ds_w4$proxy[SHARE_proxy$nmis==10] <- 999
SHARE_ds_w4$proxy <- labelled(SHARE_ds_w4$proxy, labels = cat_label)
label(SHARE_ds_w4$proxy) <- ds_label_all
```

#### Statistical description of the new harmonised variable
```{r descript4, echo=FALSE}
vari <- SHARE_ds_w4$proxy
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SHARE_ds_w4, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```







### Wave 5 

#### Study-specific variable description

| **Name** | `hh014_`| `ho041_` | `ft021_` | `sp022_` | `ch023_` | `ep210_` | `br017_` | `ph054_` | `as057_` | `co009_` |
|-|-|-|-|-|-|-|-|-|-|-|-|
| **Label** | `who answered the questions in hh`| `who answered the questions in ho` | `who answered the questions in ft` | `who answered the questions in sp` | `who answered questions in section ch` | `who answered section ep` | `interviewer check br` | `who answered the questions in ph` | `who answered the questions in as` | `who answered the questions in co` |
| **Table name** | `sharew5_rel1-0-0_hh` | `sharew5_rel1-0-0_ho` | `sharew5_rel1-0-0_ft`| `sharew5_rel1-0-0_sp` | `sharew5_rel1-0-0_ch` | `sharew5_rel1-0-0_ep` | `sharew5_rel1-0-0_br` | `sharew5_rel1-0-0_ph` | `sharew5_rel1-0-0_as` | `sharew5_rel1-0-0_co` | 
| **Categories** |`1 = respondent only`|`1 = respondent only`|`1 = respondent only`|`1 = respondent only`|`1 = respondent only`| `1 = respondent only`|`1 = respondent only`|`1 = respondent only`|`1 = respondent only`|`1 = respondent only`|
| | `2 = respondent and proxy` | `2 = respondent and proxy` |`2 = respondent and proxy` |`2 = respondent and proxy` |`2 = respondent and proxy` |`2 = respondent and proxy` |`2 = respondent and proxy` |`2 = respondent and proxy` |`2 = respondent and proxy` |`2 = respondent and proxy` |
| | `3 = proxy only` |`3 = proxy only` |`3 = proxy only` |`3 = proxy only` |`3 = proxy only` |`3 = proxy only` |`3 = proxy only` |`3 = proxy only` |`3 = proxy only` |`
| **Category missings** | `-1 = don't know` | `-1 = don't know` | `-1 = don't know` | `-1 = don't know` |  `-1 = don't know` |  `-1 = don't know` |  `-1 = don't know` |  `-1 = don't know` | `-1 = don't know` |
| | `-2 = refusal`|`-2 = refusal`|`-2 = refusal`|`-2 = refusal`|`-2 = refusal`|`-2 = refusal`|`-2 = refusal`|`-2 = refusal`|`-2 = refusal`|
| **Description** |  |  |  |  |  |  |  |  |  |



```{r assign5, echo=FALSE}
opal.assign.table.tibble(o, 'SHARE_p1','SHARE.sharew5_rel1-0-0_hh',
                         variables=list('hh014_'), missings = TRUE)
SHARE_p1 <- opal.execute(o,'SHARE_p1')

opal.assign.table.tibble(o, 'SHARE_p2','SHARE.sharew5_rel1-0-0_ho',
                         variables=list('ho041_'), missings = TRUE)
SHARE_p2 <- opal.execute(o,'SHARE_p2')

SHARE_proxy <- full_join(SHARE_p1, SHARE_p2, by='id')

opal.assign.table.tibble(o, 'SHARE_p3','SHARE.sharew5_rel1-0-0_ft',
                         variables=list('ft021_'), missings = TRUE)
SHARE_p3 <- opal.execute(o,'SHARE_p3')
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p3)

opal.assign.table.tibble(o, 'SHARE_p4','SHARE.sharew5_rel1-0-0_sp',
                         variables=list('sp022_'), missings = TRUE)
SHARE_p4 <- opal.execute(o,'SHARE_p4')
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p4)


opal.assign.table.tibble(o, 'SHARE_p5','SHARE.sharew5_rel1-0-0_ch',
                         variables=list('ch023_'), missings = TRUE)
SHARE_p5 <- opal.execute(o,'SHARE_p5')
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p5)

opal.assign.table.tibble(o, 'SHARE_p6','SHARE.sharew5_rel1-0-0_ep',
                         variables=list('ep210_'), missings = TRUE)
SHARE_p6 <- opal.execute(o,'SHARE_p6')
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p6)

opal.assign.table.tibble(o, 'SHARE_p8','SHARE.sharew5_rel1-0-0_br',
                         variables=list('br017_'), missings = TRUE)
SHARE_p8 <- opal.execute(o,'SHARE_p8')
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p8)

opal.assign.table.tibble(o, 'SHARE_p9','SHARE.sharew5_rel1-0-0_ph',
                         variables=list('ph054_'), missings = TRUE)
SHARE_p9 <- opal.execute(o,'SHARE_p9')
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p9)

opal.assign.table.tibble(o, 'SHARE_p11','SHARE.sharew5_rel1-0-0_as',
                         variables=list('as057_'), missings = TRUE)
SHARE_p11 <- opal.execute(o,'SHARE_p11')
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p11)

opal.assign.table.tibble(o, 'SHARE_p12','SHARE.sharew5_rel1-0-0_co',
                         variables=list('co009_'), missings = TRUE)
SHARE_p12 <- opal.execute(o,'SHARE_p12')
SHARE_proxy <- full_join(SHARE_proxy, SHARE_p12)
```

```{r local5, echo=FALSE}
vari <- SHARE_proxy$hh014_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$ho041_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$ft021_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$sp022_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$ch023_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$ep210_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$br017_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$ph054_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$as057_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")

vari <- SHARE_proxy$co009_
kable(Categorical_summary(vari, missing_values = c(-2,-1))[3], caption = attributes(vari)$`spss::shortName`) 
kable(Categorical_summary(vari, missing_values = c(-2,-1))[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = c(-2,-1))[2], caption = "Type of missing")
ggplot(SHARE_proxy, aes(x=factor(vari))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(label(vari)) + ylab("Frequency")
```

#### Harmonisation algorithm
To compute the harmonized variable from the study-specific variables they has to be recoded as follows:

First of all: 

* `recode 2,3 into 2`
* `reocde -1, -2 into NA`

Secondly, 

* `if any of the variables is equal to 2 recode proxy = 1`
* `otherwise proxy = 0`
* `unless all the variables are missing values `

**R script:**

```{r harmo5, echo=TRUE}
SHARE_proxy$hh014_ <- car::recode(SHARE_proxy$hh014_, "2:3=2")
SHARE_proxy$ho041_ <- car::recode(SHARE_proxy$ho041_, "2:3=2")
SHARE_proxy$ft021_ <- car::recode(SHARE_proxy$ft021_, "2:3=2")
SHARE_proxy$sp022_ <- car::recode(SHARE_proxy$sp022_, "2:3=2")
SHARE_proxy$ch023_ <- car::recode(SHARE_proxy$ch023_, "2:3=2")
SHARE_proxy$ep210_ <- car::recode(SHARE_proxy$ep210_, "2:3=2")
SHARE_proxy$br017_ <- car::recode(SHARE_proxy$br017_, "2:3=2")
SHARE_proxy$ph054_ <- car::recode(SHARE_proxy$ph054_, "2:3=2")
SHARE_proxy$as057_ <- car::recode(SHARE_proxy$as057_, "2:3=2")
SHARE_proxy$co009_ <- car::recode(SHARE_proxy$co009_, "2:3=2")

SHARE_proxy$have2 <- apply(SHARE_proxy[,-1], MARGIN = 1, FUN = function(x) sum(x==2, na.rm = TRUE)>=1)
SHARE_proxy$nmis <- apply(SHARE_proxy[,-1], MARGIN = 1, FUN = function(x) sum(is.na(x)))

SHARE_ds_w5 <- tibble(id=SHARE_proxy$id)
SHARE_ds_w5$proxy <- 0
SHARE_ds_w5$proxy[SHARE_proxy$have2] <- 1
SHARE_ds_w5$proxy[SHARE_proxy$nmis==10] <- 999
SHARE_ds_w5$proxy <- labelled(SHARE_ds_w5$proxy, labels = cat_label)
label(SHARE_ds_w5$proxy) <- ds_label_all
```

#### Statistical description of the new harmonised variable
```{r descript5, echo=FALSE}
vari <- SHARE_ds_w5$proxy
kable(Categorical_summary(vari, missing_values = miss_values_vector)[3], caption = ds_label) 
kable(Categorical_summary(vari, missing_values = miss_values_vector)[1], caption = "Category")
kable(Categorical_summary(vari, missing_values = miss_values_vector)[2], caption = "Type of missing")
ggplot(SHARE_ds_w5, aes(x=factor(proxy))) + geom_bar(stat="count", width=0.4, fill="steelblue") + xlab(ds_label) + ylab("Frequency")
```

 



## Summary of descriptive statistics of the harmonised variable accross populations and waves

Two tables are generated: 

1. Percentages of categories in each harmonised variable.

2. Frequencies and percentages of individuals with different trajectories.


```{r helpfunctions, echo=F}


labelling <- function(l.hds,m.hds){
  
  # Labelling of the tibbles with categorical data and creating new tibbles with all missings recodified as NA

  for(name in names(l.hds)) {
    # In the aux_object we copy the old tibble to recodify all missing values as NA.
    aux_object <- l.hds[[name]]
    # Labelling of variables
    label(l.hds[[name]][[2]]) <- label(aux_object[[2]]) <- ds_label
    # Labelling of categories (for continues variables, only missing values)
    l.hds[[name]][[2]] <- labelled(l.hds[[name]][[2]], labels = cat_label)
    aux_object[[2]] <- car::recode(aux_object[[2]], "miss_values_vector=NA")
    # Labelling of categories (for categorical variables, only non-missing values)
    aux_object[[2]] <- labelled(aux_object[[2]], labels = cat_label[1:2])
  # Saving the recodified tibble in list m.hds
    m.hds[[name]] <- aux_object
    rm(aux_object)
  }
  return(list(l.hds,m.hds))

}

# Creation of summary tables for categorical data

summaries <- function(l.hds,m.hds,lnames){

  # Creation of columns with categories and labels
  t.hds <- frq(l.hds[[1]][2])[[1]][,c(1,2)] 
  # For each wave/population in l.hds, add the correponding values
  for (i in seq_along(l.hds)){
    t.hds[2+i] <- frq(l.hds[[i]][2])[[1]][,4] 
  }
  # Add sample size for each wave/population
  t.hds[13,] <- c("n", "sample size", sapply(l.hds,function(wave) length(wave[[1]]))
  )
  # Add wave/population names
  names(t.hds)<-c("val", "label",lnames)
  return(t.hds)
  
}

# Creation of trajectories table for each population

trajectories <- function(m.hds,vbl_name){
  
  # First wave data
  dbb <- m.hds[[1]][,c("id",vbl_name)]
  # Merge with next waves data
  for(ind in 2:length(m.hds)){
    dbb <- merge(dbb, m.hds[[ind]][,c("id",vbl_name)], by = "id", suffixes = c("", paste0(".",names(m.hds)[ind])), all = T)
  }
  names(dbb) <- c("id", names(m.hds))
  
  # Glue individual data through all waves into trajectories
  v.dbb <- dbb[,2]
  for(ind in 2:length(m.hds)){
    v.dbb <- paste(v.dbb,dbb[,ind+1],sep="")
  }
  # Trajectories and frequencies
  f.dbb <- frq(v.dbb)[[1]][,c(1,2,4)]
  return(f.dbb)
  
}

# Save data tables

savingRD <- function(l.hds,vbl_name){
  
  for(index in seq_along(l.hds)){
    assign(vbl_name,l.hds[[index]])
    save(vbl_name,list = vbl_name, file = paste0(datafolder,names(l.hds)[index],"/",vbl_name,".RData"))
  }

}

```




```{r summ, echo=F}

# All study waves and populations with abbreviated and descriptive names



share.cw <- list(w1 = c("w1","W1"), w2 = c("w2","W2"), w3 = c("w3","W3"), w4 = c("w4","W4"), w5 = c("w5","W5"))

# Consider only harmonised waves
l.hds <- lapply(share.cw, function(wname) if(exists(paste0("SHARE_ds_",wname[1]))){wname = list(get(paste0("SHARE_ds_",wname[1])),wname[2])})
nullw <- which(sapply(l.hds, is.null))

if(length(nullw)!=0){
  l.hds <- l.hds[-nullw]
}

m.hds <- list()

lmlist <- list(lapply(l.hds,function(x)x[[1]]),m.hds)

if(length(l.hds)>0){
  # Labelling tibbles
  lmlist <- labelling(lmlist[[1]],lmlist[[2]])
  # Printing table of categories
  print(knitr::kable(summaries(lmlist[[1]],lmlist[[2]],lapply(l.hds,function(x)x[[2]])),caption=ds_label))
  # Printing table of trajectories
  f.dbb <- trajectories(lmlist[[2]],vbl_name=hd_vbl)
  print(knitr::kable(f.dbb))
  # Saving tibbles
  savingRD(lmlist[[1]],vbl_name=hd_vbl)
}



```






# Quality estimation

No comments.


```{r closeRsession, echo=FALSE} 
opal.logout(o)
```
