---
title: "Household ID"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

<!-- ########################################################## --> 
<!-- # Installation, loading packages -->
```{r setup, include=FALSE}
source("../../setup_iago.r")
```
<!-- ########################################################## --> 
<!-- # Loading DS description -->
```{r main, child='../../_DS_Rmd/household_idDS.Rmd'}
```
```{r global, echo=F}
source('../../_DS_Rmd/household_idDS.R')
```



# Data process




## SHARE


### Wave 1

#### Study-specific variable description

| **Name** | `hhid1`|
|-|-|
| **Label** | `household identifier wave 1`|
| **Table name**  | `sharew1_rel2-6-0_dn` |
| **Categories** | `text` |

```{r assign w1, echo=F}

opal.assign.table.tibble(o, 'SHARE_w1','SHARE.sharew1_rel2-6-0_dn',variables=list('hhid1'), missings = T)
SHARE_w1 <- opal.execute(o,'SHARE_w1')

```

#### Harmonisation algorithm

**R script:**

```{r harmo w1}

# Categorical variable harmonization
SHARE_ds_w1 <- tibble(id=SHARE_w1$id)
SHARE_ds_w1$household_id <- as.character(SHARE_w1$hhid1)

```




### Wave 2


#### Study-specific variable description

| **Name** | `hhid2`|
|-|-|
| **Label** | `household identifier wave 2`|
| **Table name**  | `sharew2_rel2-6-0_mh` |
| **Categories** | `text` |


```{r assign w2, echo=F}

opal.assign.table.tibble(o, 'SHARE_w2','SHARE.sharew2_rel2-6-0_mh',variables=list('hhid2'), missings = T)
SHARE_w2 <- opal.execute(o,'SHARE_w2')


```


#### Harmonisation algorithm


**R script:**

```{r harmo w2}

# Categorical variable harmonization
SHARE_ds_w2 <- tibble(id=SHARE_w2$id)
SHARE_ds_w2$household_id <- as.character(SHARE_w2$hhid2)

```



### Wave 3

#### Study-specific variable description

| **Name** | `hhid3` |`hhid3` |
|-|-|-|
| **Label** | `household identifier wave 3` | `household identifier wave 3` |
| **Table name** | `sharew3_rel1_gv_weights` |`sharew3_rel1_cv_r_without_noint`|
| **Categories** | `text` | `text` |



```{r assign w3, echo=F}

opal.assign.table.tibble(o, 'SHARE_w3_gv','SHARE.sharew3_rel1_gv_weights',variables=list('hhid3'), missings = T)
SHARE_w3_gv <- opal.execute(o,'SHARE_w3_gv')

opal.assign.table.tibble(o, 'SHARE_w3_cv','SHARE.sharew3_rel1_cv_r_without_noint',variables=list('hhid3'), missings = T)
SHARE_w3_cv <- opal.execute(o,'SHARE_w3_cv')

SHARE_w3 <- full_join(SHARE_w3_gv,SHARE_w3_cv,by="id", suffix=c(".gv",".cv"))

```

#### Harmonisation algorithm




```{r harmo w3}

# Categorical variable harmonization
SHARE_ds_w3 <- tibble(id=SHARE_w3$id)
SHARE_ds_w3$household_id <- as.character(SHARE_w3$hhid3.gv)
SHARE_ds_w3$household_id[which(is.na(SHARE_ds_w3$household_id))] <- as.character(SHARE_w3$hhid3.cv[which(is.na(SHARE_ds_w3$household_id))])

```



### Wave 4


#### Study-specific variable description

| **Name** | `hhid4`|
|-|-|
| **Label** | `household identifier wave 4`|
| **Table name**  | `sharew4_rel1-1-1_cv_r_without_noint` |
| **Categories** | `text` |

```{r assign w4, echo=F}

opal.assign.table.tibble(o, 'SHARE_w4','SHARE.sharew4_rel1-1-1_cv_r_without_noint',variables=list('hhid4'), missings = T)
SHARE_w4 <- opal.execute(o,'SHARE_w4')

```


#### Harmonisation algorithm



**R script:**

```{r harmo w4}

# Categorical variable harmonization
SHARE_ds_w4 <- tibble(id=SHARE_w4$id)
SHARE_ds_w4$household_id <- as.character(SHARE_w4$hhid4)

```



### Wave 5


#### Study-specific variable description

| **Name** | `hhid5`|
|-|-|
| **Label** | `Household identifier wave 5`|
| **Table name**  |`sharew5_rel1-0-0_cv_r_without_noint` |
| **Categories** | `text` |


```{r assign w5, echo=F}

opal.assign.table.tibble(o, 'SHARE_w5','SHARE.sharew5_rel1-0-0_cv_r_without_noint',variables=list('hhid5'), missings = T)
SHARE_w5 <- opal.execute(o,'SHARE_w5')

```


#### Harmonisation algorithm



**R script:**

```{r harmo w5}

# Categorical variable harmonization
SHARE_ds_w5 <- tibble(id=SHARE_w5$id)
SHARE_ds_w5$household_id <- as.character(SHARE_w5$hhid5)

```














<!-- ########################################################## --> 
<!-- # Save -->
```{r save, include=FALSE, echo=F}

l.hds <- list(w1 = SHARE_ds_w1, w2 = SHARE_ds_w2, w3 = SHARE_ds_w3, w4 = SHARE_ds_w4, w5 = SHARE_ds_w5)

for(index in seq_along(l.hds)){
  label(l.hds[[index]][[2]]) <- ds_label
  household_id <- l.hds[[index]]
  save(household_id, file = paste0(datafolder,names(l.hds)[index],"/household_id.RData"))
}

```
<!-- ########################################################## --> 






<!-- ########################################################## -->
<!--- # Close OPAL R Session -->
```{r closeRsession, echo=FALSE}
opal.logout(o)
```





